### 2018-04-20 General WLD combinatorics.tex
initial commit for the github version

\documentclass[11pt]{article}

\usepackage{amssymb, amsmath, verbatim, amsthm,url, multirow,fullpage,mathtools}
\usepackage{longtable, rotating,makecell,array}
\usepackage[aligntableaux=top]{ytableau}

\setlength{\parindent}{0pt}
\setlength{\parskip}{1.5ex plus 0.5ex minus 0.2ex}

%***************************
%Frontmatter Table of contents
%***************************
% Annotations
%xypic packages
%WLD tkx program
%Useful numeric rings and fields
%Other useful mathematical operations and functions
%Equation display shortcuts
%Shortcuts for frequently used special characters
%Theorem environments
%***************************

%*****************
% Annotations
\usepackage{soul}
\usepackage[colorinlistoftodos,textsize=footnotesize]{todonotes}
\newcommand{\hlfix}[2]{\texthl{#1}\todo{#2}}
\newcommand{\hlnew}[2]{\texthl{#1}\todo[color=green!40]{#2}}
\newcommand{\note}{\todo[color=green!40]}
\newcommand{\newstart}{\note{The inserted text starts here}}
\newcommand{\newfinish}{\note{The inserted text finishes here}}
\setstcolor{red}
%***************************

%*****************
%xypic packages
\usepackage[all]{xy}
\xyoption{poly}
\xyoption{arc}
%*****************

%*****************
%%% WLD drawing and 2,6 shortcuts

\usetikzlibrary{decorations.pathmorphing,calc}
\usetikzlibrary{intersections}

\definecolor{light-gray}{gray}{0.6}

\tikzstyle{propagator}=[decorate,decoration={snake,amplitude=0.8mm}]
\tikzstyle{smallpropagator}=[decorate,decoration={snake,segment length=3mm,amplitude=0.5mm}]

% these two for drawing partial propagators
\tikzstyle{firstdash}=[dashed,line cap=round, dash pattern=on 2pt off 1pt]
\tikzstyle{seconddash}=[dashed,line cap=round, dash pattern=on 0.5pt off 1pt]

% vertices, radius
\newcommand{\drawWLD}[2]{

\pgfmathsetmacro{\n}{#1}
\pgfmathsetmacro{\radius}{#2}
\pgfmathsetmacro{\angle}{360/\n}
    \foreach \i in {1,2,...,\n} {
      \pgfmathsetmacro{\x}{\angle*\i}
        \draw[-,shorten >=-\radius*0.1 cm,shorten <=-\radius*0.1 cm]  (\x:\radius cm)-- (\x + \angle: \radius cm);
    }

\draw (\angle:\radius) node {$\bullet$};
}

% r, bumpr, s, bumps: r, s are start/end vertices, bumpr and bumps are how many steps to bump the start/end for multiple props on one edge
\newcommand{\drawprop}[4]{
\pgfmathsetmacro{\r}{#1}
\pgfmathsetmacro{\bumpr}{#2}
\pgfmathsetmacro{\s}{#3}
\pgfmathsetmacro{\bumps}{#4}
\pgfmathsetmacro{\perturbe}{\angle/\n}

\begin{scope}
\clip (\angle*\r:\radius) -- (\angle + \angle*\r:\radius) -- (\angle*\s:\radius) -- (\angle + \angle*\s:\radius) -- (\angle*\r:\radius);
\draw[propagator] (\angle*\r + \angle/2 + \bumpr*\perturbe:\radius) -- (\angle*\s + \angle/2 + \bumps*\perturbe:\radius);
\end{scope}
}

% for anything that requires modifying the propagator, e.g. colour, different amplitude,etc
% 5th argument should be {propagator,<other stuff>} or {smallpropagator,<otherstuff>} otherwise you'll get a straight line
\newcommand{\modifiedprop}[5]{
\pgfmathsetmacro{\r}{#1}
\pgfmathsetmacro{\bumpr}{#2}
\pgfmathsetmacro{\s}{#3}
\pgfmathsetmacro{\bumps}{#4}
\pgfmathsetmacro{\perturbe}{\angle/\n}

\begin{scope}
\clip (\angle*\r:\radius) -- (\angle + \angle*\r:\radius) -- (\angle*\s:\radius) -- (\angle + \angle*\s:\radius) -- (\angle*\r:\radius);
\draw[#5] (\angle*\r + \angle/2 + \bumpr*\perturbe:\radius) -- (\angle*\s + \angle/2 + \bumps*\perturbe:\radius);
\end{scope}
}

\newcommand{\boundaryprop}[4]{
\pgfmathsetmacro{\r}{#1}
\pgfmathsetmacro{\bumpr}{#2}
\pgfmathsetmacro{\s}{#3}
\pgfmathsetmacro{\perturbe}{\angle/\n}

\begin{scope}
\clip (\angle*\r:\radius) -- (\angle + \angle*\r:\radius) -- (\angle*\s - \angle:\radius) -- (\angle*\s:\radius) -- (\angle + \angle*\s:\radius) -- (\angle*\r:\radius);
\draw[#4] (\angle*\r + \angle/2 + \bumpr*\perturbe:\radius) -- (\angle*\s:\radius);
\end{scope}

}

\newcommand{\drawnumbers}{
  \foreach \i in {1,2,...,\n} {
  \pgfmathsetmacro{\x}{\angle*\i}
  \draw (\x:\radius*1.15) node {\footnotesize \i};
}
}

\newcommand{\boundA}[3]{
	\pgfmathsetmacro{\r}{#1}
	\pgfmathsetmacro{\bumpr}{#2}
	\pgfmathsetmacro{\destination}{#3}
	\pgfmathsetmacro{\perturbe}{\angle/\n}
	\path [name path=polyedge1] (\angle*\r:\radius) -- (\angle*\r + \angle:\radius);
	\path [name path=radius1] (0:0) -- (\angle*\r + \angle/2 + \bumpr*\perturbe:\radius);
	\draw[->,
	name intersections={of=polyedge1 and radius1,by=p},
	shorten >=\radius*0.1 cm] (p) ++(\angle*\r + \angle/2 + \bumpr*\perturbe:\radius*0.15) -- (\angle*\destination: \radius*1.15);

}

\newcommand{\boundB}[3]{
	\pgfmathsetmacro{\rangle}{#1*\angle + \angle/2 + #2*\angle/\n}
	\pgfmathsetmacro{\sangle}{#1*\angle + \angle/2 + #3*\angle/\n}

	\draw[->,shorten <=\radius*0.02cm,shorten >=\radius*0.05cm] (\rangle:\radius*1.05) -- (\sangle:\radius*1.05);

}

\newcommand{\makediag}[8]{
	\begin{tikzpicture}[rotate=60,baseline=(current bounding box.east)]
	\begin{scope}
	\drawWLD{6}{0.8}
	%\drawnumbers
	\drawprop{#1}{#2}{#3}{#4}
	\drawprop{#5}{#6}{#7}{#8}
	\end{scope}
	\end{tikzpicture}
}

%*****************

%*****************
%Useful numeric rings and fields
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\RP}{\mathbb{R}\mathbb{P}}
\newcommand{\id}{\mathbb{I}}
\newcommand{\Gr}{\mathbb{G}_{\R, \geq 0}}
\newcommand{\Grtnn}{\mathbb{G}_{\R, +}}
\newcommand{\CW}{\overline{\mathcal{W}}} % CW complex of W(k,n)
\newcommand{\BW}{\widehat{\mathcal{W}}} % complex minus bald spots
%*****************

%*****************
%Other useful mathematical operations and functions
\newcommand{\D}{\partial}
\newcommand{\rk}{\textrm{rk }}
\newcommand{\spn}{\textrm{span }}
\newcommand{\rd}{\textrm{d}}
\newcommand{\Res}{\textrm{Res}}
%*****************

%*****************
%Equation display shortcuts
\def\ba #1\ea{\begin{align} #1 \end{align}}
\def\bas #1\eas{\begin{align*} #1 \end{align*}}
\def\bml #1\eml{\begin{multline} #1 \end{multline}}
\def\bmls #1\emls{\begin{multline*} #1 \end{multline*}}
%*****************

%*****************
%Shortcuts for frequently used special characters
\newcommand{\fB}{\mathfrak{B}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\fZ}{\mathfrak{Z}}
\newcommand{\cM}{\mathcal{M}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cI}{\mathcal{I}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\G}{\mathbb{G}}
\newcommand{\Prop}{\textrm{Prop}}
\newcommand{\cW}{\mathcal{W}}
\newcommand{\bM}{\mathbb{M}}
\newcommand{\cZ}{\mathcal{Z}}
\newcommand{\cY}{\mathcal{Y}}
\newcommand{\Dom}{\textrm{Dom}}
\newcommand{\detzr}[1] {\langle (\cZ_*^\mu|V_p)^{#1} \rangle}
\newcommand{\II}{\mathcal{I}}
\newcommand{\PP}{\mathcal{P}}
\newcommand{\BB}{\mathcal{B}}
\newcommand{\CS}{\mathcal{S}}
\newcommand{\interval}[2]{[\![#1,#2]\!]}
\newcommand{\gale}[1]{\preccurlyeq_{#1}}
\newcommand{\sgale}[1]{\prec_{#1}}
%*****************

%*****************
%Theorem environments
\newtheorem{thm}{Theorem}[section]
\newtheorem{conj}[thm]{Conjecture}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{algorithm}[thm]{Algorithm}

\theoremstyle{remark}
\newtheorem{eg}[thm]{Example}
\newtheorem{claim}[thm]{Claim}

\theoremstyle{definition}
\newtheorem{dfn}[thm]{Definition}
\newtheorem{rmk}[thm]{Remark}
\newtheorem{ntn}[thm]{Notation}
%*****************

\begin{document}

This paper studies the combinatorics of Wilson Loop Diagrams.
\section{Wilson Loop diagrams}

What are Wilson loop diagrams and their integrals.

\begin{dfn}\label{WLdfn}
A Wilson loop diagram is given by the following data: a cyclicly ordered set $V$, and $k$ pairs $\{p_r = (i_r, j_r)\}_{r=1}^k$ ordered such that $i_r +1 < j_r$. \end{dfn}

We depict this data as a convex polygon, with vertices labeled by $V$ (preserving the cyclic ordering), and $k$ wavy lines in the interior of the diagrams. The pair $p_r$ defines a wavy line from the $i_r^{th}$ edge (between $i_r$ and $i_r+1$) and the $j_r^{th}$ edge. These are called propagators.  The condition on $i_r$ and $j_r$ means that the propagator does not go between adjascent edges. Let $\cP = \{p_r\}_{r=1}^k$ be the set of propagators. Then we write \bas W = (\cP, V) \;.\eas

Often we take $V$ to be $[n]$, the cyclically ordered set of integers, $1 \ldots n$. In this case, we write $W = (\cP, n)$. We introduce some notation to speak of vertices supporting a propagator, and the set of propagators supported on a vertex set.

\begin{dfn} \label{VPropdfn}
Let $W = (\cP, n)$.
\begin{enumerate}
\item For $p \in \cP$, let $V_p = \{i_p, i_p+1, j_r, j_r+1\}$ be the set of vertices supporting $p$. Then, for $P \subset \cP$, the set $V_P = \cup_{p \in P} V_p$ is the vertex support of $P$.
\item For $V \subset [n]$, write $\Prop(V) = \{ p \in \cP | V_p \cap V \neq \emptyset \} $.
\end{enumerate}
\end{dfn}

\begin{dfn}\label{admisdfn}
A Wilson loop diagram is admissible if \begin{enumerate}
\item $|V| \geq |\cP| + 4$
\item There does not exists a set of propagators, $P \subset \cP$ such that $|V(P)| < |P| + 3$.
\item There does not exist a pair of propagators, $p, q \subset \cP$ such that $i_p < i_q < j_p <j_q$.
\end{enumerate}
 \end{dfn}

The first conditions states that there are at least four more vertices than propagators in an admissible Wilson Loop Diagram. The second imposes an upper bound on how densely the propagators can be fitted in the diagram. The third ensures that ensures that no propagators cross in the interior of the diagram. In other words, a Wilson loop diagram, $(\cP, n)$ is admissible if and only if $n > \cP +4$, and has neither crossing propagators nor any pairs of propagators that start and end on the same pair of non-adjacent edges.

In what follows, we will talk about admissible Wilson Loop diagrams and subdiagrams thereof.

\begin{dfn} \label{subdiagramdfn}
Let $W = (\cP, n)$ be an admissible Wilson loop diagram. A subdiagram of $W$ is defined by a a subset of propagators of $W$. For $P \subset \cP$, write $W|_P = (P, V(P))$. 
\end{dfn}

Note that a subdiagram of an admissible diagram need not be admissible. In particular, the condition $|V(P)| > |P| +4$ need not hold.

There is one particular type subdiagram that deserves special attention.

\begin{dfn}
For $W$ an admissible diagram, $(P, V(P))$ is exact if $|V(P)| = |P| + 3$. 
\end{dfn}

The exact subdiagrams define an equivalence relation amongst Wilson loop diagrams.

\begin{dfn}\label{equivdfn}
Two admissible Wilson loops diagrams, $W = (\cP, n)$ and $W'= (\cP', n)$ are equivalent if
\begin{enumerate}
\item There exist two different exact subdiagrams, $(P, V(P))$ and $(P', V(P'))$ of $W$ and $W'$ respectively such that $V(P) =  V(P')$.
\item The complementary subdiagrams are identical: $(\cP \setminus P, [n] \setminus V(P)) = (\cP' \setminus P', [n] \setminus V(P'))$.
\end{enumerate}
\end{dfn}

\section{Wilson Loop diagrams as matroids}

In \cite{wilsonloop}, Amat and Agarwala show that admissible Wilson loop diagrams with $k$ propagators corresponds to positroids of rank $k$ (a matroid that can be represented by an element of $\Gr(k, n)$. )

\begin{thm}\cite{wilsonloop}An admissible Wilson loop diagram, $W =(\cP, n)$, defines a matroid with base set $[n]$. The independent sets are exactly those subsets $V \subseteq [n]$ such that $\not \exists U\subseteq V$ satisfying $|\Prop(U)|> |U|$. \label{thm:WLDmatroid}\end{thm}

Recall the definition of the rank of a subset $C \subset [n]$.

This does not, however, show that the matroids associated to each Wilson loop diagram is unique. In fact, in \cite{wilsonloop}, the authors show that if two diagrams are equivalent then they define the same matroid [cite theorem here].

Next, we show that this is the only condition under which two Wilson loop diagrams define the same matroid.

\begin{thm}
Two Wilson loop diagrams define the same matroid if and only if the are equivalent.
\end{thm}

To this end, we recall some definitions and go through a series of new intermediary steps.

First we recall a few facts about matroids.

\begin{dfn} For a Wilson Loop diagram $W = (\cP, [n])$, the associated matroid $M(W)$ can be defined by any of the following sets of subsets
\begin{enumerate}
\item A basis of $W$ is any independent set, $B \subset [n]$ of size $|B| = |\cP|$.
\item The rank of a set $|V| \subset [n]$, is bounded above by $\rk(V) \leq \min\{ |V| , |\Prop(V)|\}$. If $V$ is an independent set, then $\rk(V) = |V|$. Furthermore, if $v \in [n]$, and $q \in \Prop(v)$, then for any $V \subset [n]$ such that $q \not \in \Prop(V)$, $\rk(V \cup v) = \rk(V) +1$. That is, adding a vertex that supports a new propagator to a set increases the rank of the set.
\item A circuit of a matroid is any set $C \subset [n]$ such that every proper subset $U \subsetneq C$ is independent. That is, $\rk(C) = |C|-1$. The union of circuits is called a cycle. If $C$ is a circuit of an admissible Wilson loop diagram, and $e \in C$, \bas |\Prop(C\setminus e))| \leq |C\setminus e| = \rk(C) \leq \min\{|C|, |\Prop(C\setminus e)|\}\;.\eas
    In other words, if $C$ is a circuit of a Wilson loop diagram, then \bas \rk(C) = |C|-1 = |\Prop(C)| \;. \eas
\item A flat, $F$, of a matroid is a maximally dependent set. That is, for all $e \not \in F$ $\rk(F \cup e) = \rk(F) +1$. If $W$ is an admissible Wilson loop diagram, any group of propagators defines a flat, $F(P) = = V(P^c)^c$, called a propagator flat. It consists of all vertices of $W$ that do not support any propagators outside of $P \subset \cP$. To see that this is flat, let $v \in V(P^c)$. We have that  This consists of the vertices that only support propagators in $P$. For example, if $W$ contains with no vertices of rank $0$, we may write $F(P) = V(P^c)^c$.
\end{enumerate}
\end{dfn}

It is worth noting that it is not necessary to list all the flats in a matroid to defined it completely, only the cyclic flats, and those that are independent sets. Namely, if $F$ is a dependent flat, it contains a circuit. Let $C \subset F$ be the largest cycle contained in $F$. Then two things are true. \begin{enumerate}
\item $C = F(\Prop (C))$
\item $F \setminus C$ is an independent flat
\end{enumerate}

To see the first point, note that $\rk(C) = |\Prop(C)|= \rk (F(\Prop(C)))$. For any $v\in C$ such that $\Prop(v) \subset \Prop(C)$, then $v \in F(\Prop(C))$. Therefore $S \subset F(\Prop(C))$. Suppose there is a $v \in  F(\Prop(C)) \setminus C$. Let $B$ be an independent subset of $C$ of maximal rank. The set $B \cup v$ is dependent and therefore contains a circuit. Therefore, $C \cup b$ is a cycle, which is a contradiction to $C$ being the maximal cycle in $F$.

To see the second point, note that $F \setminus C$ is independent (as it contains no circuits). Furthermore, it is a flat. For any $e \not \in F$, $\rk (F \setminus C \cup e) = \rk (F\setminus C) +1$, since $F$ is a flat. For any $e \in C$,  $\rk (F \setminus C \cup e) \neq \rk (F\setminus C)$. Otherwise $F\setminus C \cup e$ would be a dependent set and therefore would contain a circuit, which contradicts the hypothesis that $C$ is the largest cycle in $F$.

Therefore, in the sequel, one only needs worry about cyclic and independent flats.

Finally, I recall a result from the previous paper about contracted diagrams and matroids.

\begin{lem}
For $W = (\cP, [n])$, write the contracted diagram $W/P = (P^c, V(P)^c)$. If $\rk F(P) = |P|$, we may identify \bas M(W/P) = \left(M(W)/ F(P)\right)|V(P)^c \;. \eas
\end{lem}

\subsection{Exact subdiagrams and matroids}

It has been proved that if two Wilson loop diagrams are equivalent, then the define the same matroid in ``Matroids and Wilson Loop Diagrams''. In this section, we prove the converse. Therefore, we prove several results about exact subdiagrams.

\begin{lem} \label{exactcircuitlem}
Let $(P, V(P))$ be an exact subdiagram of $W= (\cP, [n])$. The set $V(P)$ contains no circuits, $C$ such that  $\rk C< |P|$.
\end{lem}

\begin{proof}
Recall that a circuit of rank $m$ is a set $C$ of rank $m$ and size $m+1$ such that every proper subset of $C$ is independent. I.e., \emph{a circuit is a minimal dependent set.}

Consider a subdiagram $(P, V(P))$ of $W$. Suppose there is a circuit, $C \subset V(P)$ such that $\rk C = m < |P|$. Write $\Prop (C) = Q \subsetneq P$. Here, $|Q| = m$. The size of the complement of $C$ is $|V(P) \setminus C| = |V(P)| -(m+1)$. However, since $C$ does not contain any propagators outside of $Q$, the set $V(P \setminus Q) \subset V(P )\setminus C$. In otherwords, there are $|P| - m$ propagators (the number of propagators in $P \setminus Q$) supported on (at most) $|V(P)|-m -1$ vertices: \bas |V(P \setminus Q)| \leq |V(P)| - m-1\;. \eas Since $(P, V(P))$ is an exact subdiagram of an admissible Wilson loop, $W$, we know that $|P| + 3 = |V(P)|$, and for any subset, $R$, of propagators of $W$, $|R|+3 \leq |V(R)|$. On there otherhand, there is a subset of propagators, $P\setminus Q$ satisfying \bas |V(P \setminus Q)| \leq |P| + 3 - m-1 = |P\setminus Q| + 2\;. \eas But this violates admissibility of $W$.
\end{proof}

\begin{eg}
The converse does not hold. Consider, for instance, the diagram

\begin{tikzpicture}[rotate=68] % change rotation manually as needed
\begin{scope}
\drawWLD{8}{2} % vertices, radius
\drawprop{1}{0}{4}{1} % this draws a prop from (4,5) to (6,7); {0} means *centre* of the edge 4--5, {n} bumps it n "steps" clockwise from centre (for use when you have several props on one edge)
\drawprop{2}{0}{4}{-1}
\drawprop{8}{0}{5}{-1}
\drawprop{7}{0}{5}{1}
\end{scope}
\end{tikzpicture}

The subdiagram $( \{(1, 4), (5, 8)\}, \{1, 2, 4, 5, 6, 8\})$ is not exact, but it has no cycles of rank $2$.
\end{eg}

However, all is not lost. To avoid the issue of exact diagrams being subdiagrams of other exact subdiagrams (for instance, any subdiagram $(q, V_q)$, for $q \in \cP$ is exact), I introduce a definition.

\begin{dfn}
We say $(P, V(P))$ is a maximal exact subdiagram of $W$ if there is not other exact subdiagram $(Q, V(Q))$ containing it.
\end{dfn}

Then we have the following statement about the structure of circuits and Wilson Loop diagram.

\begin{cor}
Let $W$ be a Wilson Loop Diagram. No maximal exact subdiagram $(P, V(P))$ contains a circuit $C \subset V(P)$ of rank $\rk(C) \leq |P|$.
\end{cor}

\begin{lem}
Let $W = (\cP, [n])$ be a Wilson loop diagram, and $(P, V(P))$ a maximal exact subdiagram with $P \subsetneq \cP$. Then the set $V(P)^c = F(P^c)$ is a propagator flat with rank  \bas \rk F(P^c) = |P^c| \;. \eas
\end{lem}

\begin{proof}
To see that $V(P)^c$ is a propagators flat by construction. It remains to check that this this has maximal rank.

Notice that $n= |V(P)| + |F(P^c)| \geq |P| + |P^c| +4$, and $|V(P)| = |P| +3$. Therefore \bas |F(P^c)| > |P^c| \;.\eas In other words, $F(P^c)$ is a dependent flat.

We claim that if $C$ is the largest cycle in $F(P^c)$, then $\Prop(C) = P^c$. In other words, $\rk F(P^c) = |P^c|$. Otherwise, $F(P^c) = C \cup F$, where $F$ is an independent flat. In other words, $\rk (F) = i < |P^c| - \rk (C)$. Then $F \cup V(P) = V(Q)$ where $|Q| \geq |P| +i$ while $F \cup V(P) \leq |P| + 3 + i$. Therefore, either $W$ is not a Wilson loop diagram, or $(P, V(P))$ is not a maximal exact subdiagram.
\end{proof}

There are several corollaries of Lemma \ref{exactcircuitlem} that are useful. There are many more than I list here, we can find a corollary for each equivalent way of representing these positroids.

\begin{cor} \label{exactindepcor}
If the subdiagram $(P, V(P))$ is exact in $W= (\cP, [n])$, every subset $S \subset V(P)$ of size $|S| \leq |P|$ is independent.
\end{cor}

\begin{proof}
Since $V(P)$ has no circuits of rank $< |P|$, no set of size $|S| \leq |P|$ contains a circuit, and is therefore, independent.
\end{proof}

\begin{cor} \label{exactposcor}
If the subdiagram $(P, V(P))$ is exact in $W= (\cP, [n])$, it represents a totally positive $\Grtnn(|P|, |V(P)|)$ cell of the matroid represented by $W$.
\end{cor}

\begin{proof}
Since there are no circuits of rank $m < |P|$, every subset of size $|P|$ is a basis. This defines the totally positive cell $\Grtnn(|P|, |V(P)|)$.
\end{proof}

%\begin{rmk}
%Sian: Your observation that every Grassman Necklace sees the exact subdiagrams as "gapless strings" on $V(P)$ is also a corrollary of this. (The gaps in a Grassmann necklace come from the existance of circuits. No circuits $\Leftrightarrow$ no gaps in necklace.) However, I can't come up with a clean enough statement of your idea to write it as a corrollary. Feel free to feed me a statement and I will happily write it up.
%\end{rmk}

It is worth noting that all of these have converses if when we consider diagrams, and stop considering subdiagrams. Namely:

\begin{lem}\label{exactequivs}
Let $W = (\cP, [n])$ be a Wilson loop diagram. Then the following are equivalent. \begin{enumerate}
\item $W$ is exact.
\item All subsets $V$ of size $|V| = |\cP|$ are bases.
\item The only cycles in $W$ have rank $|\cP|$.
\item The only dependent flat of $W$ is $F(\cP)$. This is also a cyclic flat.
\end{enumerate}
\end{lem}

\begin{proof}
Obvious?
\end{proof}

Now I am ready to prove the main theorem of this section.

\begin{thm}
Let $W= (\cP, [n])$ and $W'= (\cP', [n])$ be two Wilson Loop diagrams. They define the same matroid if and only if $W \sim W'$.
\end{thm}

\begin{proof}
One direction has been proved in previous work, but I give a different proof here to be consistent with the method of this document.

Write $W = (P \cup R, [n])$ and $W' = (P \cup R', [n])$, where $P = \cP \cap \cP'$.

Assume that $W$ and $W'$ are equivalent. Let $(\{Q_i, V(Q_i)\})$ and $(\{Q'_i, V(Q'_i)\})$ be the sets of maximal exact subdiagrams that intersect $V(R)$ and $V(R')$ respectively. By Lemma \ref{exactcircuitlem}, if there is a circuit in any $C_i \subset V(R_i)$, it is of rank $|R_i|$ and there is a corresponding circuit $C'_i \subset V(R'_i)$ such that $C_i = C'_i$. Any other circuits of $W$ and $W'$ lie entirely within the complementary set of vertices, \bas(\cup_i V(R_i))^c = \cap_i F(R_i^c) = \cap_i F(R^{' c}_i) \;.\eas As this depends wholely on the propagators in $P$, which is common to both diagrams, these circuits are also the same. Since all circuits are the same, $M(W) = M(W')$.

For the converse, assume that $M(W) = M(W')$. Then the cyclic flats of $W$ correspond to the cyclic flats of $W'$. Let $Q \subset P$ be the largest subset of propagators such that $F(Q)$ is a cyclic flat. This may be an empty set. Let $Q^c$ and $Q^{c'}$ be the complementary set of propagators in $\cP$ and $\cP'$ respectively. They contain $R$ and $R'$ respectively. We see that $V(Q^c) = V(Q^{c'})$.

Since $F(Q)$ is a cyclic flat, it has maximal rank. Therefore, we can write \bas M(W)/F(Q) = M(Q^c, V(Q^c)) = M(W')/F(Q) = (Q^{c'}, V(Q^{c'})) \;. \eas Therefore, it is sufficient to compare the contracted Wilson loop diagrams $W/Q = M(Q^c, V(Q^c))$ and $ W'/Q = (Q^{c'}, V(Q^{c'}))$. We do so iteratively by quotienting by the cyclic flats.

If there do not exist a $T \subsetneq Q^c$ and $T' \subsetneq Q^{c'}$ such that $F(T) = F(T')$ are cyclic, then, by \ref{exactequivs}, $W/Q$ and $W'/Q$ are exact. Therefore, they are equivalent, as are $W$ and $W'$.

If there do exist $T \subsetneq Q^c$ and $T' \subsetneq Q^{c'}$, such that $F(T) = F(T')$ are cyclic, chose $T$ and $T'$ such that they do not contain any other proper subset of propagators that define cyclic flats. Then the Wilson loop diagram $(T, V(T))$ and $(T', V(T'))$ are both exact, and correspond to maximal exact subdiagrams of $(W/Q)$ and $(W'/Q')$. Furthermore, $V(T) = V(T')$. Otherwise, $F(Q^c \setminus T) \neq F(Q^{c'} \setminus T')$, with contradicts that the corresponding matroids are equal; $M(W/Q)=M(W'/Q')$. Therefore, and differences in the propagators structure between the subdiagrams $(T, V(T))$ and $(T', V(T'))$ correspond to different representations of equivalent subdiagrams.

We next consider $(W/Q)/T$ and $(W'/Q')/T'$.

\end{proof}

\subsection{Counting exact subdiagrams}

Since equivalent Wislon loop diagrams are the only ones that define the same matroid as each other, it is useful to enumerate the number of equivalent diagrams any Wilson loop diagram has.

\begin{dfn}
  Let $W$ be an admissible Wilson loop diagram.  The \emph{polygon partition} associated to $W$, denotes $\tau(W)$ is defined as follows.
  \begin{itemize}
  \item The vertices of $\tau(W)$ correspond to the edges of $W$.
  \item The polygon of $\tau(W)$ is the graph theoretic cycle made of the vertices of $\tau(W)$ and where two vertices are adjacent if the corresponding edges of $W$ meet at a vertex of $W$.
  \item There is a chord edge of $\tau(W)$ for each propagator of $W$.  Given a propagator fo $W$, this edge of $\tau(W)$ joins the two vertices of $\tau(W)$ corresponding to the edges of $W$ where the two ends of the propagator lie.
  \end{itemize}
\end{dfn}

For an admissible $W$ no propagators cross and so no chord edges of $\tau(W)$ cross.  Thus, in graph theoretic language, we can view $\tau(W)$ as a planar embedding of a graph with no cut vertices, where all vertices lie on the infinite face, along with a distinguished start vertex and direction around the infinite face.  From this viewpoint the polygon of $tau(W)$ is the boundary of the infinite face.

***draw some examples***

A planar embedding of a graph is a \emph{triangulation} if all faces, except possibly the infinite, face are triangles.

\begin{dfn}
  Let $W$ be an admissible Wilson loop diagram and $\tau(W)$ its polygon partition.
  A \emph{triangulated piece} of $\tau(W)$ is a 2-connected subgraph of $\tau(W)$ which is a triangulation and which is maximal with respect to that property.  We will take the convention that a subgraph consisting of two vertices joined by an edge which is in no triangle is also a triangulated piece, called a \emph{trivial} triangulated piece.
\end{dfn}

A decomposition of a polygon partition $\tau(W)$ is a set of 2-connected induced subgraphs of $\tau(W)$ which partition the edges of $\tau(W)$.

\begin{lem}
  Every polygon partition $\tau(W)$ has a unique decomposition into triangulated pieces.
\end{lem}

***draw an example***

\begin{proof}
  First consider the weaker notion of decompositions of $\tau(W)$ into 2-connected pieces which are either triangulations (but not necessarily maximal) or subgraphs consisting of two vertices joined at an edge.  At least one such decomposition must exist as we can simply take each edge as defining it's own subgraph.

  Now suppose we have two distinct such decompositions.  Since they are distinct there must be some edge $e$ of $\tau(W)$ for which the subgraph containing this edge are differs between the decompositions.  Let $T_1$ and $T_2$ be these two subgraphs.  The graph $T_1\cup T_2$ defined by taking the union of the vertex sets of $T_1$ and $T_2$ along with the union of the edge sets of $T_1$ and $T_2$ is still a subgraph of $\tau(W)$.  Furthermore, since all vertices of $\tau(W)$ lie on the external face, and $T_1$ and $T_2$ are 2-connected, then $T_1$ and $T_2$ can share at most two vertices and these must be on the external faces of $T_1$ and of $T_2$.  Therefore $T_1\cup T_2$ is the result of gluing two triangulations along edges on each of their external faces and hence is also a triangulation.  Combining all subgraphs which share edges we obtain a decomposition containing both original decompositions.

  Therefore the set of such decompositions of $\tau(W)$ is not just a poset under containment but is a finite directed set and thus has a unique maximal element.

Also, the subgraphs making up this maximal element are themselves maximal as if not then taking the union with the decomposition formed from a single triangulation which properly contains one of the triangulations of the maximal element along with the remaining edges as individual subgraphs, would give a decompositions containing the purported maximal one.  Furthermore, no non-maximal decomposition can be a decomposition into maximal triangulations because since it is properly contained in the maximal element some subgraph of this decomposition must be properly contained in some subgraph of the maximal decomposisiton and hence not be a maximal triangulation.

  Thus the maximal decomposition is the desired unique decomposition into (maximal by definition) triangulated pieces.
\end{proof}

That previous proof is rather belaboured, so it will probably want to be cut down, but I'm not sure which parts will be obvious to our audience and which will not be.

\begin{lem}\label{lem triang to exact}
  Let $W$ be an admissible Wilson loop diagram and $\tau(W)$ its polygon partition.  The nontrivial triangulated pieces of $\tau(W)$ correspond to the maximal connected exact subdiagrams of $W$.
\end{lem}

\begin{proof}
  Let us first record a few standard facts about polygon triangulations (that is about triangulations with all vertices on the outer face).  If such a triangulation has $n$ vertices then it has $n$ edges on the polygon (that is on the outer face) and $n-3$ edges which are not.  No planar graph with the same vertices and the same outer face can have more edges than the triangulation and every such simple graph with $n-3$ edges off the outer face is a triangulation.

  Since $W$ is admissible, $\tau(W)$ has no double edges and so is a simple graph.
  Let $t$ be a nontrivial triangulated piece of $\tau(W)$ and suppose $t$ has $n$ vertices.  We want to count how many edges of $t$ are not on the outer face of $\tau(W)$.  Consider the intersection of $t$ with the outer face of $\tau(W)$.  This is a subgraph with $n$ vertices of the polygon of $\tau(W)$, call it $S$.  Let $k$ be the number of connected components of $S$.  Also $S$ is a spanning subgraph of the outer face of $t$ and $S$ has $n$ edges.  To join the components $S$ must have $k$ edges not in the outer face of $\tau(W)$.  Furthermore $t$ has $n-3$ edges not in its outer face and so also not in the outer face of $\tau(W)$.  Thus there are $n-3+k$ edges of $t$ not in the outer face of $\tau(W)$.

  These edges correspond to propagators in $W$, so the open subdiagram of $W$ corresponding to $\tau(W)$ has $n-3+k$ propagators.  Next let's count the vertices of this subdiagram.  Each of the $n$ vertices in the outer face of $t$ corresponds to an edge of the open subdiagram and the edges of this open subdiagram form $k$ connected compnents of the outer polygon.  Thus the open subdiagram has $n+k$ vertices.  So we see that the open subdiagram corresponding to $t$ has exactly three more vertices than propagators.  Propagators can never be supported at higher density than this by admissibility and so the support of the propagators of the subdiagram is all the vertices of the subdiagram and hence the subdiagram is exact.  We have not used the maximality of the triangulation in the above and so any triangulated subgraph corresponds to an exact subdiagram.

  Conversely if we have an exact subdiagram of $W$ with $n$ edges forming $k$ connected components of the outer polygon then the corresponding subgraph of $\tau(W)$ has $n$ vertices and $n-k+(n-3+k) = 2n-3$ edges, of which $n$ are in the outer face and hence is a triangulation.

  The statement of the lemma then follows form the fact that inclusion is preserved under $\tau$ and so maximality also corresponds under $\tau$.
\end{proof}

\begin{dfn}
  Say two admissible Wilson loop diagrams $W_1$ and $W_2$ are \emph{triangulation-equivalent} if there is a bijection $\alpha$ between the set of triangulated pieces in the decomposition of $\tau(W_1)$ and the set of triangulated pieces in the decomposition of $\tau(W_2)$, where $t$ and $\alpha(t)$ have the same vertex set for all triangulated pieces $t$ of $\tau(W_1)$.
\end{dfn}

***draw an example***

\begin{thm}
  Two admissible Wilson loop diagrams have the same matroid iff they are triangulation equivalent
\end{thm}

Again do I want matroid or positroid in this theorem?

\begin{proof}
  By Lemma~\ref{lem triang to exact} two admissible Wilson loop diagrams are triangulation equivalent iff their decompositions into maximal connected exact subdiagrams have matching supports, that is if they are equivalent.
  Theorem~\ref{thm orig equiv} then gives the result.
\end{proof}

It is a classical fact the the number of triangulations of an $n$-gon is the $n-2$ Catalan number, namely $\frac{1}{n-1}\binom{2(n-2)}{n-2}$.  Thus we can count the number of equivalent diagrams.

\begin{cor}
  Let $W$ be an admissible Wilson loop diagram where the sizes of the supports of the maximal connected exact subdiagrams are $n_1, n_2, \ldots, n_j$.  Then the number of admissible Wilson loop diagrams equivalent to $W$ (including $W$ itself) is
  \[
  \prod_{i=1}^{j} \frac{1}{n_i-1}\binom{2(n_i-2)}{n_i-2}
  \]
\end{cor}

\section{Geometry of Wilson Loop diagram}
Since Wilson loop diagrams correspond to positroids, it is natural to understand the subspace of $\Gr(|\cP|, n)$ they define.

Talk about Grassmann Necklaces and how it defines a cell in a CW complex of $\Gr(k,n)$. Also talk about how this is exactly all the non-negative matrices that represent a particular positroid.

Also talk about Le diagrams.

\subsection{From Wilson Loop diagrams to Grassmann Necklaces}

Here, we give an algorithm for passing from Wilson loop diagrams to Grassmann Necklaces.

Let $\interval{1}{n}$ denote the set of integers $\{1,2, \dots, n\}$, and $\binom{[n]}{k}$ the set of all $k$-subsets of $\interval{1}{n}$.  For each $j \in \interval{1}{n}$, we can define a total order $\leq_j$ on the interval $\interval{1}{n}$ by
\[ j <_j j+1 <_j \dots <_j n <_j 1 \dots <_j j-1.\]
This in turn induces a total order on $\binom{[n]}{k}$, namely the lexicographic order with respect to $<_j$.  It also induces a separate partial order $\gale{j}$ on $\binom{[n]}{k}$ (the \textit{Gale order}), which is defined as follows: if $A = [a_1 <_j a_2 <_j \dots <_j a_k]$,  $B = [b_1 <_j b_2 <_j \dots <_j b_k] \in \binom{[n]}{k}$, then
\[A \gale{j} B \text{ if and only if } a_r \leq_j b_r \text{ for all }1 \leq r \leq k.\]
For example, in $\binom{[6]}{3}$ we have $[2,5,6]\gale{2} [2,6,1]$ but $[2,5,6]\not\gale{2}[3,4,6]$.

\begin{dfn}\label{def:grassmann necklace}
A Grassmann necklace of type $(k,n)$ is a sequence $\II = (I_1, \dots, I_n)$ of $n$ elements $I_i \in \binom{[n]}{k}$, such that
\begin{itemize}
\item if $i \in I_i$, then $I_{i+1} = \big(I_i \backslash \{i\}\big) \cup \{j\}$ for some $j \in \interval{1}{n}$.
\item if $i \not\in I_i$, then $I_{i+1} = I_i$.
\end{itemize}
\end{dfn}

By [ref], the Grassmann necklaces of type $(k,n)$ are in 1-1 correspondence with the positroid cells in $Gr(k,n)^{tnn}$.  Further, if $\II$ is the Grassmann necklace associated to a cell $\PP$, then the bases of $\PP$ can be computed using the Gale order $\gale{i}$ for each $i \in \interval{1}{n}$:
\[\BB(\PP) = \left\{J \in \binom{[n]}{k}\ :\ I_i \gale{i} J \ \forall i \in \interval{1}{n}\right\}.\]
We now describe an algorithm that, when applied to an admissible Wilson loop diagram, produces exactly the Grassmann necklace of the corresponding positroid.

\begin{algorithm}\label{alg:put GN on WLD}
Let $W$ be a Wilson loop diagram with $n$ vertices.  Note that whenever the algorithm below refers to the ``rightmost'' propagator supported on a vertex $i$, we mean the rightmost from the point of view of standing in the middle of the diagram and looking directly at $i$.

\begin{enumerate}
\item Fix a vertex $s \in \interval{1}{n}$, and set $i:=s$.
\begin{enumerate}
\item \textbf{Step $i$ for vertex $s$}: If there is at least one propagator in the current diagram supported on $i$, add the label $i$ to the edge $(s,s+1)$ and delete the rightmost propagator supported on $i$; otherwise do nothing.
\item If there are no propagators left in the diagram at this point, go to (2) below.
\item Otherwise, increment $i$ by 1 and repeat from (a).
\end{enumerate}
\item Replace all propagators in the diagram, and repeat from (1) for a new vertex $s$.  Continue until the algorithm has been applied to all vertices.
\end{enumerate}
\end{algorithm}

\begin{prop}\label{res:alg k labels}
If $W$ is an admissible Wilson loop diagram, then Algorithm~\ref{alg:put GN on WLD} puts exactly $k$ distinct labels on each edge.
\end{prop}
\begin{proof}
It is enough to show that the algorithm terminates in at most $n$ steps for each vertex.  Suppose this doesn't happen, i.e. there is a propagator $P$ which survives the first $n$ steps of the algorithm for some starting vertex $s$.  We will show that this always gives a contradiction in an admissible diagram by constructing an inductive sequence of propagators on strictly decreasing regions of the diagram.

Rotating and cyclically renumbering if necessary, we can assume that $s=1$ and that $P$ is supported on $(a,a+1,b,b+1)$ with $1 \leq a < b$.  Since $P$ is not removed at step $b+1$, there is another propagator $p_1$ to its right which is also supported on $b+1$: see Figure~\ref{fig:base step of alg induction}.

\begin{figure}
\begin{tikzpicture}[rotate=15]
\begin{scope}
\drawWLD{12}{2}
\drawprop{3}{2}{10}{2} % P
% number vertices a,a+1,b,b+1 for prop P

% clip these
\drawprop{3}{-2}{12}{-2}
\drawprop{2}{0}{12}{2}
\drawprop{6}{0}{10}{-2} % p1

\end{scope}
\end{tikzpicture}
\caption{Base step: if $P$ survives $n$ steps of the algorithm, there must be another propagator $p_1$ to its right on edge $(b,b+1)$.}
\label{fig:base step of alg induction}
\end{figure}

The propagator $p_1$ forms the base step for the following induction:

Suppose that $p_r$ is a propagator supported on $(i,i+1,m,m+1)$ and removed at step $m+1$ of the algorithm; we will show that there must also be a propagator $p_{r+1}$ supported on $(i',i'+1,m',m'+1)$ with $i \leq i'$ and $m \geq m'$, which is removed at step $m'+1$.  Since we can't have both $i' = i$ and $m'=m$, $p_{r+1}$ bounds a region containing strictly fewer vertices than $p_r$.

Notice that if we restrict our attention to the region bounded by $p_r$ and the edges of the diagram from $i$ to $m+1$, then propagators outside of this region can affect the algorithm only at vertices $i$, $i+1$.  (The starting vertex 1 lies outside this region, by assumption.)

Given a propagator $p_r$ supported on $(i,i+1,m,m+1)$ and removed at step $m+1$, we must also have a propagator $q$ to its right which is removed at step $m$ (``protecting'' $p_r$ at step $m$).  This splits into two cases:

\textbf{Case I}: If $q$ is supported on $(k,k+1,m-1,m)$ for some $k \geq i$, then $p_{r+1}:=q$  satisfies the conditions of the induction step.

\textbf{Case II}: Suppose $q$ is supported on $(k,k+1,m,m+1)$ for some $k$; since the diagram is admissible, we have $k > i$.  In particular, anything that happens at vertex $k+1$ is unaffected by propagators outside the region bounded by $p_r$, since $k+1 > i+1$.  But $q$ must survive until step $m$, so there must be another propagator $q'$ to the right of $q$, which protects $q$ at step $k+1$.  The admissibility of $W$ implies that $q'$ is supported on $(j,j+1,k,k+1)$ for some $j \geq i$, and we can take $p_{r+1}:=q'$.

\begin{figure}
\begin{tabular}{ccc}
\begin{tikzpicture}[rotate=15]
\begin{scope}
\drawWLD{12}{2}
\drawprop{3}{0}{10}{0} % p_r
% number vertices i,i+1,m,m+1

%clip these
\drawprop{6}{0}{9}{0} % q
\end{scope}
\end{tikzpicture}

& \qquad \qquad &
\begin{tikzpicture}[rotate=15]
\begin{scope}
\drawWLD{12}{2}
\drawprop{3}{0}{10}{2} % p_r
% number vertices i, i+1, m, m+1

\drawprop{7}{2}{10}{-2} %q
% vertices k,k+1, m,m+1

% clip this one
\drawprop{4}{0}{7}{-2} % q'
% vertices j,j+1,k, k+1

\end{scope}
\end{tikzpicture}
\\
Case I & & Case II
\end{tabular}

\caption{Inductive step: if propagator $q$ is removed at step $m$, then it lies on either edge $(m-1,m)$ (Case I) or $(m,m+1)$ (Case II).}
\label{fig: cases for inductive step, algorithm}
\end{figure}

By induction, we will eventually find a propagator on a region with 3 or fewer vertices, which is inadmissible.
\end{proof}

To prove that this algorithm gives the Grassmann necklace of the diagram we need a lemma.

\begin{lem}\label{lem susama}
  \note{this lemma should be rephrased to be more in your language, it was just copied from the rank section, also it needs a cite or a proof}
  Given a WLD and a propagator $p$,  each covered vertex of $p$ is contributed to a non-empty cyclic interval in the Gra\ss mann necklace.
\end{lem}

\begin{prop}\label{res:alg gives GN}
The sequence of $k$-subsets obtained by applying Algorithm~\ref{alg:put GN on WLD} to an admissible diagram $W$ is exactly the Grassmann necklace of the positroid associated to $W$.
\end{prop}

\note{I think the statement should be clearer about what this sequence is, in the way that the first line of the proof currently is.}

\begin{proof}
Let $I_i$ be the set of labels on edge $(i,i+1)$; the sequence $\II = (I_1, \dots, I_n)$ is a Grassmann necklace if and only if $I_{i+1} \supseteq I_i \backslash \{i\}$ for all $i \in \{1, \dots, n\}$.

Suppose for a contradition that there exists an admissible diagram for which there exists an $i$ with $k\in I_{i\backslash\{i\}}$ and $k \not\in I_{i+1}$.  Fix $n$.  Let the triple $(W, i, k)$ be such a counterexample on $n$ vertices which is minimal with respect to the number of propagators. %, and among all those counterexamples on $n$ vertices with the same number of propagators, let $(W,i,k)$ be minimal with respect to the distance from $i$ to $k$ in the $\leq _i$ order.

If $i \not\in I_i$, then there are no propagators supported on $i$ at all.  In this case it is clear that applying Algorithm~\ref{alg:put GN on WLD} at vertex $i$ and vertex $i+1$ produces exactly the same result, i.e. $I_{i+1} = I_i$, and so $(W, i, k)$ is not a counterexample at all.

Now suppose that $i \in I_i$.  Let $p$ be the propagator which contributes $i$ to $I_i$.  Either $p$ has one end on the edge $(i-1, i)$ or it has one end on the edge $(i, i+1)$.  In both cases let $(b, b+1)$ be the edge with the other end of $p$.

\textbf{case I}:  Suppose $p$ has one end on $(i-1, i)$.  Then $p$ is not supported on $i+1$, so in building $I_{i+1}$ we will take the same propagators as in the construction of $I_i$ from vertices $i+1$ up to $b-1$, that is $I_{i+1} \cap \interval{i+1}{b-1} = I_{i} \cap \interval{i+1}{b-1}$.  Furthermore, by Lemma~\ref{lem susama}, in building $I_{i+1}$, it must be that $p$ is taken at vertex $b$, as otherwise $b$ would never be contributed by $p$.    Consequently, in building $I_{i+1}$, when at vertex $b$ no propagator still remaining is before $p$.  This is also true in building $I_i$ when at $b$ since the same propagators have been taken beforehand.  Additionally $k\geq_i b+1$.

Let $W'$ be the diagram obtained from $W$ by removing $p$ and all propagators under it in the sense of supported between $i+1$ and $b-1$.

By the above observations when we are in $W'$ at $b$ then we are in the same situation with respect to the remaining propagators as if we began at $i$ in $W$ and moved to $b$ following the algorithm; the propagators we took in the latter case are exactly the ones removed to build $W'$.  Similarly starting at $i+1$ in $W$ and moving to $b+1$ leaves us in the same situations with respect to the remaining propagators as beginning at $b+1$ in $W'$.  This gives the equations
\begin{align*}
  I_i^W \cap \interval{b}{i-1} & = I_b^{W'} \\
  I_{i+1}^W \cap \interval{b+1}{i-1} & = I_{b+1}^{W'}
\end{align*}
where the diagram is indicated in the superscript.
Thus we have $k\in I_b^{W'}\backslash\{b\}$ and $k\not\in I_{b+1}^{W'}$ contradicting the minimality of $(W, i, k)$.

\textbf{case II}: Suppose $p$ has one end on $(i, i+1)$.  Note that by definition $p$ is the propagator contributing $i$ to $I_i$ and so it must be the first propagator in $(i, i+1)$ and hence $p$ contributes $i+1$ to $I_{i+1}$.  Observe that $k\geq_i i+2$ since $i+1\in I_{i+1}$.

Let $W'$ be the diagram obtained from $W$ just by removing $p$.  Then
\begin{align*}
  I_i^W \backslash \{i\} & = I_{i+1}^{W'} \\
  I_{i+1}^W \backslash \{i+1\} & = I_{i+2}^{W'}
\end{align*}
since in both cases in $W'$ we are simply taking the remaining propagators in the same way as we would have in $W$ after taking $p$ for the previous vertex.  Since $k \neq i+1$, we have $k\in I_{i+1}^{W'}\backslash\{i+1\}$ but $k\not\in I_{i+2}^{W'}$ contradicting the minimiality of $(W, i, k)$

%If $i \not\in I_i$, then there are no propagators supported on $i$ at all.  In this case it is clear that applying Algorithm~\ref{alg:put GN on WLD} at vertex $i$ and vertex $i+1$ produces exactly the same result, i.e. $I_{i+1} = I_i$.
%
%Now suppose that $i \in I_i$.  Order $I_i$ and $I_{i+1}$ with respect to $\leq_{i+1}$; in particular, $i$ is the last term in $I_i$ with respect to this ordering.
%
%Let $p_1$ be the rightmost propagator supported on $i$, and suppose it is removed at step $a$ with respect to vertex $i+1$.  This is the first point at which $I_{i+1}$ can differ from $I_i$, i.e. we have $I_{i+1} \cap \interval{i+1}{a-1} = I_{i} \cap \interval{i+1}{a-1}$.  If $a \not\in I_i$, then $p_1$ is the only propagator supported on $a$ at step $a$ with respect to vertex $i+1$.  All remaining steps are unchanged and we conclude that $I_{i+1} = I_i \backslash \{i\} \cup \{a\}$.
%
%If $a \in I_i$, then at step $a$ with respect to vertex $i+1$ there must be another propagator $p_2$ which lies to the left of $p_1$.  We have $I_{i+1} \cap \interval{i+1}{a} = I_i \cap \interval{i+1}{a}$, and the next possible difference
%
%{\color{red}[argh]}
%
%Although there are many different subcases to consider, the idea is always the same: we look for the first entry where $I_{i+1}$ and $I_i \backslash \{i\}$ differ (with respect to $<_{i+1}$), and show that this is the only possible difference.
%
%The reader should keep in mind that due to Proposition~\ref{res:alg k labels}, the following process cannot double back on itself.
%
%\begin{enumerate}
%\item If $p_1$ contributes $k$ to $I_{i+1}$ and $k \in I_i$, then there is another propagator $p_2$ which was deleted at step $k$ with respect to vertex $i$, but now survives at step $k$ with respect to vertex $i+1$.  All intermediate steps of the algorithm are unchanged, so $I_{i+1}$ and $I_i \backslash \{i\}$ agree up to (and including) $k$.
%\item We now look at which label $p_2$ contributes in $I_{i+1}$, and apply the same argument.  Iterate this process until we find a propagator $p_r$ which is deleted at step $j$ with respect to vertex $i+1$, but $j \not\in I_i$.
%\item $j \not\in I_i$ implies that $p_r$ is the \textit{only} propagator supported on vertex $j$ at this step.  There is therefore no knock-on effect, and any remaining propagators in the diagram contribute the same label to both $I_i$ and $I_{i+1}$. We conclude that $I_{i+1} = I_i \backslash \{i\} \cup \{j\}$.
%\end{enumerate}

\note{I tried to make the first part of this proof a bit tidier by using contradiction.  I will do the same for the second part (what is currently below) and also finish the proof, when I have a chance}

We have shown that $\II$ is a Grassmann necklace; it remains to check that this Grassmann necklace defines the positroid $\PP_W$ associated to $W$.  We need to show that:
\begin{itemize}
\item For each $i \in \interval{1}{n}$, $I_i$ is a basis for $\PP_W$.
\item If $J$ is lexicographically smaller than $I_i$ with respect to $<_i$, then $J$ is not a basis for $\PP_W$.
\end{itemize}
Recall from [ref] that a $k$-subset $J \in \binom{[n]}{k}$ is a basis for $\PP_W$ if and only if it has no subset $U \subseteq J$ such that $|U| > |Prop(U)|$.  It is immediately clear from the construction that $I_i$ is a basis for each $i$: the algorithm is effectively pairing each $j \in I_i$ with a unique propagator supported on that vertex, so $|Prop(U)| \geq U$ for all $U \subseteq I_i$.

If $\exists l \in J$ with $Prop(l) = \emptyset$ then $J$ is clearly not a basis, so suppose otherwise.  Write
\[I_i = [i_1 <_i i_2 <_i \dots <_i i_r <_i \dots <_i i_k], \quad J = [i_1 <_i i_2 <_i \dots <_i j_r <_i \dots <_i j_k],\]
so that $I_i$ and $J$ differ for the first time in the $r$th position.  Then
\[r-1 \geq |Prop(\{i_1, \dots, i_{r-1}\})| = |Prop(\{i_1, \dots, i_{r+1},j_r\})|,\]
If $|Prop(\{i_1, \dots, i_{r-1}|\}| = r-1$ then we are done; otherwise

\end{proof}

\subsection{Dimension of the Wilson Loop cells}

In \cite{reversingOh}, Agarwala and Fryer give an algorithm for passing from a Grassmann Necklace to a Le diagram. We use this algorithm here to pass from a Wilson loop diagram to its associated Le diagram. In this manner, we show that the positroid cell defined by a Wilson loop diagram has dimension $3|\cP|$. Maybe say something about Amplituhedra having $4k$ dimension, but this is not quite what we have, since we are ignoring one column.

When I speak of a \emph{WLD}, I mean one which satisfies your density hypothesis and other standard hypotheses.  When I speak of a propagator \emph{contributing} a vertex to an element of the Gra\ss mann\footnote{I suppose it is a bit of an affectation to use an eszett when writing in English, and actually the eszett is kind of ugly in this font, but since I've started to I'll stick with it for now but you certainly shouldn't feel obliged to do it too.} necklace I mean that according to the rule you guys have to build the Gra\ss mann necklace from the diagram by starting at a vertex and taking the clockwise-most covering propagator which hasn't already been taken, when a propagator is taken then it is contributing that vertex.  Also, I will be using your algorithm to convert the Gra\ss mann necklace into a Le diagram by non-intersecting paths.

We need four lemmas from stuff you guys have already figured out.  The first one is a corollary of your lemma characterizing intervals contributed by each covered vertex of a propagator.

The first lemma is Lemma~\ref{lem susama} and I moved it up to a previous section.

The second lemma is the fact that we understand uncovered vertices.  You probably see many ways to prove this from things you already know.  One would be to say that from your algorithm the column of the uncovered vertex simply plays no role.

\begin{lem}\label{lem uncovered}
  Let $D$ be a WLD with an uncovered vertex $i$.  Let $C$ be $D$ with $i$ removed.  Then the Le diagram of $D$ is the Le diagram of $C$ with an extra column of all $0$s inserted in the $|D|-i+1$th position from the left.
\end{lem}

The third lemma is Sian's result.

\begin{lem}\label{lem sian}
  Let $D$ be a WLD with all vertices covered by at least two propagators.  Then There exist two propagators in $D$ with the following properties.
  \begin{itemize}
  \item The first propagator goes from the edge $i$, $i+1$ to the edge $i+2$, $i+3$.
  \item The second propagator goes from the edge $i+2$, $i+3$ to the edge $i+4$, $i+5$
  \item No other propagator is on the edge $i+2$, $i+3$.
  \end{itemize}
\end{lem}

Actually the result I need is not exactly Sian's result and what I will actually use is her proof.  Thus I will use notation and definitions (including length of a propagator and the specific $p_i$ and $q_i$ construction from the proof) from her note without further discussion.  The result I will actually use will be that in place of the hypothesis that $D$ has all vertices covered by at least two propagators I have that all vertices are covered by at least 1 propagator and there are no propagators of length 3.

The fourth lemma is that we can rotate or reflect without changing the number of plusses.  The best way to see this is probably geometrically so I leave that up to you.

\begin{lem}\label{lem dihedral}
  If two WLDs differ by a dihedral transformation then their Le diagrams have same number of plusses.
\end{lem}

Now we're ready to go.

\subsubsection{Changes in Gra\ss mann necklaces for nice configurations}

Given a propagator $p$ in a WLD $D$, note that $p$ divides remaining propagators of $D$ into two sets depending on which side of $p$ they live.

\begin{lem}\label{lem good p}
  Let $D$ be a WLD with $n\geq 1$ propagators.  Then there is some dihedral transformation $D'$ of $D$ such that there is a propagator $p$ with the following properties.
  \begin{itemize}
  \item $p$ goes between the edge $i$, $i+1$ and the edge $n-1$, $n$ in $D'$.
  \item $i+2, \ldots, n-2$ are not covered by any propagators in $D'$ (which is trivially true if $\{i+1, \ldots, n-2\}=\varnothing$).
  \item Either $i+1$ in $D'$ is only covered by $p$, or $i+1$ is covered by exactly one other propagator $q$.
  \item If we are in the second case above then $q$ goes between the edge $j$, $j+1$ and the edge $i$, $i+1$ and $j+2, \ldots, i-1$ are not covered by any propagators.
  \end{itemize}
\end{lem}

\begin{proof}
  Since $n\geq 1$ the dual tree of $D$ has at least two vertices and so has at least two leaves.  Each edge going to a leaf of the dual tree corresponds to a propagator which has no other propagators on one side of it, so there is at least one such propagator in $D$.  There are two cases to consider.

  First suppose there is a propagator which has no other propagators on one side of it and for which one of its ends is on an edge with no other propagators.  Let this propagator be $p$.  Rotate and reflect $D$ as necessary so that the end of $p$ which does not share its edge comes first, then the side of $p$ with no other propagators, and then the other end of $p$ which is on edge $n-1$, $n$.  Call this WLD $D'$.  It is a straightforward check that the properties in the statement are satisfied with $i+1$ only covered by $p$.

  Next suppose there is no propagator which has no other propagators on one side of it and for which one of its ends is on an edge with no other propagators.  Let $C$ be $D$ with all uncovered vertices removed.  Suppose $C$ contains two propagators one of length 2 and one of length 3 with the length 2 propagator on the small side of the length 3 propagator.  Then we are in the case already considered because we can rotate and reflect $C$ so that these two propagators both have one end on the edge $|C|-1$,$|C|$, and have their other ends on the edge $|C|-2$, $|C|-3$ and the edge $|C|-3$, $|C|-4$, so taking the length 2 edge as $p$ we satisfy the properties of the statement, and this remains true in $D$.  Thus we now assume this does not occur, so in particular every propagator of length 3 in $C$ has no other propagators on its small side.  But then the middle vertex on this small side is uncovered contradicting the construction of $C$.  Thus $C$ has no propagators of size 3.

  The claim then is that in $C$ there must exist two propagators as in Lemma~\ref{lem sian}.  The proof of the claim follows by Sian's proof.  We do not have the hypothesis that all vertices are covered by at least two propagators, but this is only used in the proof of Lemma~\ref{lem sian} to force certain propagators (the $q_i$) to have length at least 4, so our this case we instead use that $C$ has no propagators of size $3$.

  Now rotate and flip $C$ so that the two propagators as in Lemma~\ref{lem sian} cover $\{|C|-5, \ldots, |C|\}$ and let $p$ be the propagator covering $\{|C|-3, \ldots, |C|\}$ and let $q$ be the other one.  Return to $D$ with a corresponding rotation and flip so that vertex $n$ in $D$ corresponds to vertex $|C|$ in $C$ and direction in the polygon is preserved.  Let this dihedral transformation of $D$ be $D'$.  Then the propagator $p$ satisfies the conditions of the statement with propagator $q$.
\end{proof}

Given a WLD $D$, $I_i^{D}$ denotes the $i$th Gra\ss mann necklace element corresponding to $D$.

\begin{lem}\label{lem I}
  Let $D$ be a WLD with $n\geq 1$ propagators and let $p$ be a propagator of $D$ so that the properties of Lemma~\ref{lem good p} are satisfied for $p$ in $D$ (that is $D$ is already appropriately transformed).  Furthermore suppose that that $p$ has length $2$, as does $q$ if we are in the case of Lemma~\ref{lem good p} involving $q$.  Let $C$ be $D$ with $p$ removed but no change in the vertices.  Then
  \begin{align*}
    I_1^{D} & = I_1^{C} \cup \{n-3\} \\
    I_n^{D} & = I_1^{C} \cup \{n\} \\
    I_{n-1}^{D} & = I_n^{C} \cup \{n-1\} \\
    I_{n-2}^{D} & =
    \begin{cases}
      I_{n-2}^{C}\cup \{n-2\} & \text{if $n-2\not\in I_{n-2}^{C}$} \\
      I_{n-2}^{C}\cup \{n-1\} & \text{if $n-2\in I_{n-2}^{C}$, $n-1\not\in I_{n-2}^{C}$} \\
      (I_{n}^{C} - \{n-5\})\cup \{n-1,n-2\} & \text{if $n-1, n-2\in I_{n-2}^{C}$}
    \end{cases} \\
    I_{k}^{D} & =
    \begin{cases}
      I_k^{C}\cup \{n-3\} & \text{if $n-3 \not\in I_k^{C}$}\\
      I_k^{C}\cup\{n-2\} & \text{if $n-3\in I_k^{C}$}
    \end{cases} \\
    & \text{for $1<k<n-2$}
  \end{align*}
\end{lem}

\begin{figure}
  \includegraphics{specialp}
  \caption{The different possibilities for $D$ and $p$.  No other propagators can end in the fat red sections.  Other segments may have additional propagators ending in them.}\label{fig special p}
\end{figure}

\begin{proof}
  The two possible situations are illustrated in Figure~\ref{fig special p}.

  If $n-3\in I_1^{C}$ then $n-3\not\in I_1^{D}$, but then $p$ never contributes $n-3$ contradicting Lemma~\ref{lem susama}.  Thus $n-3\not\in I_1^{C}$ and so in building the Gra\ss mann necklace when we get to vertex $n-3$ any other covering propagators of $C$ have already been taken and so we can now take $p$.  Therefore $I_1^{D}= I_1^{C}\cup \{n-3\}$.

  In constructing $I_n^{D}$, first for vertex $n$ we take propagator $p$.  Then we are at vertex $1$ and precisely the propagators of $C$ remain.  Thus the rest of the construction will give $I_1^{C}$.  Therefore $I_n^{D} = I_1^{C}\cup \{n\}$.  Essentially the same reasoning gives $I_{n-1}^{D} = I_n^{C}\cup \{n-1\}$.

  Now consider $I_{n-2}^{D}$.  If $n-2\not\in I_{n-2}^{C}$ then at vertex $n-2$ we take $p$ and this does not affect the rest of the construction of $I_{n-2}^{C}$, so $I_{n-2}^{D} = I_{n-2}^{C}\cup \{n-2\}$.  An analogous argument takes care of the first case for $I_k^{D}$.  Suppose $n-2\in I_{n-2}^{C}$ but $n-1\not\in I_{n-2}^{C}$.  Then at vertex $n-2$ we take the same propagator in $C$ as in $D$ (in particular not $p$) because $p$ is the counterclockwisemost propagator covering $n-2$ and so the last propagator the algorithm would choose at this vertex, and by hypothesis $n-2$ is covered in $C$.  Howver, $n-1$ is untaken in $I_{n-2}^{C}$ so at this vertex we will take $p$ in $I_{n-2}^{D}$.  Following this, now that $p$ is out of the way without bumping any other propagators, the construction continues as in $I_{n-2}^{C}$.  Therefore $I_{n-2}^{D} = I_{n-2}^{C}\cup \{n-1\}$.  An analogous argument takes care of the case when we have $1<k<n-2$ and $n-3\in I_k^{C}$ but $n-2\not\in I_{k}^{C}$.  Furthermore, either $n-2$ is uncovered in $C$ or only $q$ covers $n-2$ in $C$ and $q$ is also the only propagator covering $n-3$.  Thus it is not possible for $n-3$ and $n-2$ to both be in $I_{k}^{C}$.  This means that all the cases for $I_k^{D}$ are now proved.

  The remaining case is when $n-1,n-2\in I_{n-2}^{C}$ for the construction of $I_{n-2}^{D}$.  We must then have a propagator $q$ as in the right hand side of Figure~\ref{fig special p}.  In the construction of $I_{n-2}^{D}$, at vertex $n-2$ we take propagator $q$, as in $I_{n-2}^{C}$.  Then at vertex $n-1$ we take propagator $p$ which is different from what occurs in $I_{n-2}^{C}$.  Next we are at vertex $n$ and propagators $p$ and $q$ have been taken.  Thus we are proceeding like $I_{n}^{C}$ but without propagator $q$.  Fortunately we can determine explicitely how propagator $q$ contributes to $I_{n}^{C}$.  By Lemma~\ref{lem susama} propagator $q$ contributes $n-5$ to $I_{n}^{C}$, and the only way this can occur is if all other propagators of $C$ were already taken by the time we got to vertex $n-5$.  Therefore $I_{n-2}^{D} = (I_{n}^{C} - \{n-5\}) \cup \{n-1, n-2\}$.  This covers all cases and hence completes the proof.
\end{proof}

\subsubsection{The number of plusses from Gra\ss mann necklaces in nice configurations}

\begin{lem}\label{lem shape}
  Let $C$ and $D$ be as in Lemma~\ref{lem I}.
  The shape of the Le diagram of $C$ can be built from left to right of the following blocks: a rectangle with 3 columns, one more column of the same length, a partition shape with at most as many rows as the rectangle.
  The shape of the Le diagram of $D$ can be built from left to right of the following blocks: a rectangle with 3 columns and one more row than the first rectangle of $C$, the same partition shape as in $C$.
\end{lem}

\begin{proof}
  $I_1$ determines the shape of the Le diagram.
  By Lemma~\ref{lem I}, $I_1^{D} = I_1^{C}\cup \{n-3\}$.  This implies that the right hand boundary of the shape of $C$ is the same as the right hand boundary of the shape of $D$ except that $D$ has one additional row of 3 boxes while $C$ has an additional column in the $n-3$ position, that is a new column fourth from the left.
\end{proof}

The shapes of the Le diagrams of $C$ and $D$ are illustrated in Figure~\ref{fig Le}.  The pieces of the Le diagrams will be called $\mathcal{A}$ and $\mathcal{B}$ in what follows, as in the figure.  Over the course of the next few lemmas we will prove that the plusses in the $\mathcal{B}$ parts of the Le diagrams of $C$ and $D$ are identical and the plusses in the $\mathcal{A}$ parts are very closely related.  When we speak of a plus in the Le diagram of $D$ being the same as in $D$ or vice versa, we mean that the plus' position in $\mathcal{A}$ or $\mathcal{B}$ is the same.  Because of the column insertion the absolute indices may differ.

\begin{figure}
  \includegraphics{Le_diagrams}
  \caption{Le diagrams for $C$ (left) and $D$ (right).}\label{fig Le}
\end{figure}

Suppose we are following the Gra\ss mann necklace to Le diagram algorithm, and we put a plus in a box because of a path from vertical boundary edge $i$ to bottom boundary edge $j$.  Then say this plus is in the $i\rightarrow j$ position.

\begin{lem}\label{lem n and n-1}
  Let $C$ and $D$ be as in Lemma~\ref{lem I}.
  The $I_n^{D}$ and $I_{n-1}^{D}$ elements of the Gra\ss mann necklace of $D$ give all the same plusses as $I_n^{C}$ along with plusses in the leftmost two boxes of the bottom row of the Le diagram of $D$.
\end{lem}

\begin{proof}
  By Lemma~\ref{lem I} $I_n^{D}= I_1^{C} \cup \{n\}$, so by the Gra\ss mann necklace to Le diagram algorithm the only plus this builds in the Le diagram of $D$ is  the one in the $n-3\rightarrow n$ position, that is in the leftmost box of the bottom row.

  Also by Lemma~\ref{lem I} $I_{n-1}^{D} = I_n^{C} \cup \{n-1\}$.  Additionally $n-3\not\in I_{n}^{C}$ since if it were then $n-3$ would also be in $I_1^{C}$ and hence propagator $p$ could not contribute $n-3$ to $I_1^{D}$ in contradiction to Lemma~\ref{lem susama}.  Similarly $n-1, n-2\not\in I_n^{C}$.  Thus the paths putting the plusses in from $I_n^{C}$ lie completely in $\mathcal{B}$ or take some vertical boundary edge $>n-3$ to $n$.   Now view these paths in the Le diagram of $D$ and note that the path $n-3\rightarrow n-1$ is compatible, and so these paths together build the plusses that $I_{n-1}^{D}$ contributes.  That is, we get all the plusses from $I_{n}^{C}$ along with a $n-3\rightarrow n-1$ plus, that is a plus in the second to the right box of the bottom row.
\end{proof}

\begin{lem}\label{lem n-2 good}
  Let $C$ and $D$ be as in Lemma~\ref{lem I} with $n-2 \not\in I_{n-2}^{C}$.

  The $I_{n-2}^{D}$ element of the Gra\ss mann necklace of $D$ gives
  an $n-3\rightarrow n-2$ plus and
  all the $I_{n-1}^{C}=I_{n-2}^{C}$ plusses.
\end{lem}

\begin{proof}
  If $n-2\not\in I_{n-2}^{C}$ then $I_{n-1}^{C}=I_{n-2}^{C}$ and by Lemma~\ref{lem I} $I_{n-2}^{D} = I_{n-1}^{C} \cup \{n-2\}$.  Note that $n-3\not\in I_{n-2}^{C}$ by Lemma~\ref{lem susama}.  Therefore the paths for $I_{n-2}^{D}$ are the paths for $I_{n-1}^{C}$ along with the $n-3\rightarrow n-2$ path.  This gives the statement of the lemma.

\end{proof}

\begin{lem}\label{lem n-2 bad}
  Let $C$ and $D$ be as in Lemma~\ref{lem I} with $n-2,n-1 \in I_{n-2}^{C}$.

  The $I_{n-2}^{D}$ and $I_{n-3}^{D}$ elements of the Gra\ss mann necklace of $D$ gives the following plusses:
  \begin{itemize}
  \item An $n-3\rightarrow n-2$ plus and an $n-5\rightarrow n-1$ plus.
  \item All the $I_{n-1}^{C}$ plusses.
  \item $I_{n-2}^{C}$ gives an $n-5\rightarrow n-2$ plus and no other term in the Gra\ss mann necklace of $C$ gives a plus in this column.  This $+$ does not appear in $D$ from $I_{n-2}^{D}$ but an $n-5\rightarrow n-1$ plus does instead.
  \item All other plusses of $I_{n-2}^{C}$.
  \item $I_{n-3}^{C}$ gives a plus in the $n-3$ column.  This $+$ is shifted over into the $n-2$ column in $D$.
  \item All other plusses of $I_{n-3}^{C}$.
  \end{itemize}
  Furthermore, no element of the Gra\ss mann necklace of $C$ gives an $n-5\rightarrow n-1$ plus.
\end{lem}

\begin{proof}
  By Lemma~\ref{lem I} $I_{n-2}^{D}= (I_{n}^{C} - \{n-5\})\cup \{n-1,n-2\}$.  Also, by the location of $q$ in the WLD,  $n-2\not\in I_{n-3}^{C}$ and and $n-5$ is the index of the lowest vertical edge in $\mathcal{B}$.  Thus this section of the Gra\ss mann necklace of $C$ looks like
  \begin{equation}\label{eq necklace}
  I_{n-3}^{C} \underset{\substack{n-3\text{ out}\\n-2\text{ in}}}{\rightarrow} I_{n-2}^{C} \underset{\substack{n-2\text{ out}\\n-5\text{ in}}}{\rightarrow} I_{n-1}^{C} \underset{\substack{n-1\text{ out}\\\text{something in}}}{\rightarrow} I_{n}^{C} \underset{\substack{n \text{ out}\\\text{something in}}}{\rightarrow} I_1^{C}
  \end{equation}
  where the first ``something'' is either $n$ or an element of $I_1^{C}$ and the second ``something'' is an element of $I_1^{C}$.  Additionally all elements not explicitly mentioned must be in $I_1^{C}$ as they remain unchanged through this portion of the necklace.

  Using this information now determine the symmetric difference of $I_{n-2}^{C}$ and $I_1^{C}$: $n-1, n-2$ and possibly $n$ are in $I_{n-2}^{C}$ but not in $I_1^{C}$.  $n-5$ is in $I_1^{C}$ as are at least one and at most two other elements.  If there is one such element call it $a$.  If there are two call them $a$ and $b$ with $a>b$.  This means that the plusses in the Le diagram of $C$ coming from $I_{n-2}^{C}$ are as in the first part of Figure~\ref{fig messy}.  Stepping to $I_{n-1}^{C}$ simply removes the $n-5\rightarrow n-2$ path, see the second part of Figure~\ref{fig messy}.

  \begin{figure}
    \includegraphics{messy}
    \caption{Plusses coming from $I_{n-2}^{C}$ (top left),  $I_{n-1}^{C}$ (top right) and $I_{n}^{C}$ bottom when $n-1, n-2\in I_{n-1}^{C}$.  The blue lines are the non-intersecting paths.  The dashed blue lines may or may not appear, but if one appears then they both do.}\label{fig messy}
  \end{figure}

  Stepping to $I_{n}^{C}$, $n-1$ is taken out and either $n$ is put in if it was not there before, or one of $a$ or $b$ is put in and hence no longer available as a right end for a path.  This gives two possible configurations illustrated in the bottom two parts of Figure~\ref{fig messy}.

  Now we know that $I_{n-2}^{D}  = (I_{n}^{C} - \{n-5\})\cup \{n-1,n-2\}$ so the paths for building plusses from $I_{n-2}^{D}$ go from the set $\{n-5, n-3\}$ along with whichever of $a$ and $b$ is not in $I_{n}^{C}$ to $\{n-2, n-1, n\}$.  This means that we get plusses as in Figure~\ref{fig messyD} where the left and right cases correspond to the left and right cases in the bottom parts of Figure~\ref{fig messy}

  \begin{figure}
    \includegraphics{messyD}
    \caption{Plusses coming from $I_{n-2}^{D}$.}\label{fig messyD}
  \end{figure}

  This proves the first item of statement of the lemma.

  Now consider $I_{n-3}^{C}$.  By \eqref{eq necklace} $I_{n-3}^{C}$ contributes the same plusses as $I_{n_2}^{C}$ except that it contributes an $n-5\rightarrow n-3$ plus in place of the $n-5\rightarrow n-2$ plus.  Also, we have $n-3\in I_{n-3}^{C}$ be the location of $q$ and so $I_{k}^{D} = I_k^{C}\cup\{n-2\}$.  Thus the paths for $I^{D}_{n-3}$ are the same as for $I^{C}_{n-3}$ except that the path that did go to $n-3$ now goes to $n-2$.  This cannot conflict with another path since \eqref{eq necklace} shows that $n-2$ only appears in $I_{n-2}^{C}$ among the necklace elements of $C$.

  Also note that $I_{n-3}^{C}, I_{n-2}^{C}$, and $I_{n-1}^{C}$ share their plusses outside of the $n-3$ and $n-2$ columns.  This proves the remaining statements of the lemma except the furthermore.

  Finally, suppose there were a $n-5\rightarrow n-1$ plus in the Le diagram of $C$.  By the algorithm, it would have to come when $n-5 \not\in I_j^{C}$.  By \eqref{eq necklace} this means that it would have to come from $I_{n-4}^{C}$, $I_{n-3}^{C}$, or $I_{n-2}^{C}$. The analysis above shows it does not come from $I_{n-3}^{C}$ or $I_{n-2}^{C}$.   Now, $n-4\in I_{n-4}^{C}$ by the location of $q$ and so $I_{n-4}^{C}$ must give an $n-5\rightarrow n-4$ plus and so cannot give an $n-5\rightarrow n-1$ plus.

\end{proof}

\begin{lem}\label{lem other k}
  Let $C$ and $D$ be as in Lemma~\ref{lem I} and take $1<k<n-2$.  Suppose that if $n-2\in I_{n-2}^{C}$ then also $n-1\in I_{n-2}^{C}$.
  The $I_k^{D}$ element of the Gra\ss mann necklace of $D$ gives the same plusses as $I_{k}^{C}$ except that if there is a plus in the $n-3$ column for $I_{k}^{C}$ then this plus is shifted into the $n-2$ column and no plus was already in that location.
\end{lem}

\begin{proof}
  If $n-3\not\in I_{k}^{C}$ then by Lemma~\ref{lem I} $I_{k}^{D} = I_k^{C}\cup \{n-3\}$.  Then since $n-3$ is the largest element of $I_1^{D}$ this transformation leaves the disjoint paths unchanged and so the plusses carry over from $C$ to $D$ directly.

  If $n-3\in I_{k}^{C}$ then by Lemma~\ref{lem I} $I_{k}^{D} = I_k^{C}\cup \{n-2\}$.  If $n-2$ is not covered in $C$ then certainly no pluses appear in the $n-2$ column of the Le diagram of $C$.  If $n-2$ is covered in $C$ then by hypothesis so is $n-1$ and so we satisfy the hypotheses of Lemma~\ref{lem n-2 bad}.  Thus the only necklace element of $C$ containing $n-2$ is $I_{n-2}^{C}$ and this particular plus is not contributed to the Le diagram of $D$ by $I_{n-2}^{D}$.

  {}From $I_{k}^{C}$ there is a path from some vertical edge to the bottom edge $n-3$.  In $I_{k}^{D}$, $n-3$ is a vertical edge with no path and instead there must be a path to $n-2$.  By the previous paragraph no other path can end in $n-2$, so shifting the path that did go to $n-3$ to go to $n-2$ while leaving the others the same maintains non-crossingness and so must be the paths for $I_{k}^{D}$.  Thus the plus in the $n-3$ column for $C$ is shifted into the $n-2$ column, where there was no plus before, and no other plusses are changed.
\end{proof}

\begin{thm}
  The number of plusses in the Le diagram of a WLD is three times the number of propagators.
\end{thm}

\begin{proof}
  The proof is by induction on the number of propagators.

  First note that a WLD $D$ with one propagator covering vertices $i<j<k<\ell$ has Le diagram a single row with $|D|-i$ boxes.  Labelling them from left to right by $|D|, \ldots, |D|-i+1$, by the algorithm there are plusses in the $j$, $k$, and $\ell$ positions.

  Now consider WLDs with $k>1$ propagators.  By Lemma~\ref{lem uncovered} it suffices to prove the result for WLDs with $k$ propagators and no uncovered vertices.  By Lemma~\ref{lem dihedral} it suffices to prove the result for at least one WLD from each dihedral orbit.  Take a WLD diagram $D$ with $k$ propagators.  Make a dihedral transformation of $D$ if necessary so that $D$ has a propagator $p$ with the properties in Lemma~\ref{lem good p} relative to $D$.  If $n-1$ is only covered by $p$ but $n-2$ is covered by at least one other propagator, then flip $D$ on the line perpendicular to the edge from $n-2$ to $n-1$.  This will be our $D$ for the rest of the proof.

  Let $C$ be $D$ with $p$ removed but no change in the vertices.  Note that if $n-2$ is covered in $C$ then so is $n-1$ by the end of the previous paragraph and so if $n-2$ is covered in $C$ then the hypotheses of Lemma~\ref{lem n-2 bad} are satisfied.

  {}From Lemma~\ref{lem shape} we know how the shapes of the Le diagrams of $C$ and $D$ relate; let $\mathcal{A}$ and $\mathcal{B}$ be as described after that lemma.  Lemmas~\ref{lem n and n-1}, \ref{lem n-2 good}, and \ref{lem n-2 bad} tell us that the three boxes of the bottom row of the Le diagram of $D$ each have a plus.  Lemmas~\ref{lem n and n-1}, \ref{lem n-2 good}, \ref{lem n-2 bad}, and \ref{lem other k} show that there is a bijection between the plusses of the Le diagram of $C$ and the plusses of the Le diagram of $D$ that are not in the bottom row which can be described as follows.
  \begin{itemize}
  \item Plusses from $\mathcal{B}$ for $C$ maintain their positions in $\mathcal{B}$ for $D$.
  \item Plusses from the first two columns (the $n$ and the $n-1$ columns) of $\mathcal{A}$ for $C$ maintain their positions in $\mathcal{A}$ for $D$.
  \item If there is a plus in the $n-2$ column of $\mathcal{A}$ in  then Lemma~\ref{lem n-2 bad} applies, so there is exactly one such plus.  This plus maps to the $n-5\rightarrow n-1$ plus for $D$.
  \item The plusses in the $n-3$ column for $C$ shift over to the third column (the $n-2$ column) of $\mathcal{A}$ in $D$.
  \end{itemize}
  This map is clearly reversible and hence bijective except possibly for the $n-5\rightarrow n-1$ plus for $D$.   If the Le diagram of $D$ has an $n-5\rightarrow n-1$ plus then look at the Le diagram for $C$.  If the Le diagram for $C$ has a plus in the $n-2$ column then Lemma~\ref{lem n-2 bad} applies and so there is no $n-5\rightarrow n-1$ plus in the Le diagram of $C$ and the $n-5\rightarrow n-1$ plus of $D$ can be uniquely mapped to the plus in the $n-2$ column of the Le diagram of $C$.  If the Le diagram for $C$ has no plus in the $n-2$ column, then leave the $n-5\rightarrow n-1$ plus where it is in moving back to $C$.  This reverses the map.

  From all of this we get that the number of plusses in the Le diagram for $D$ is three more than the number of plusses in the Le diagram for $C$.  Applying induction completes the proof.
\end{proof}

{\color{red}Maybe proved that inadmissible diagrams, while they correspond to matroids, can't be mapped to the positroids of the correct dimension? }

\section{Poles of Wilson Loop Integrals}

I'd like to end this paper with a proof of a conjecture (that I think I need for a subsequent paper, and this seems the natural place to put it. This is as follows:

\begin{conj}
Given any admissibly Wilson loop diagram $W$, let $GN(W) = \{I_1, \ldots I_n\}$ be the associated Grasmann necklace. Then the denominator of the integral $I(W)$ is the \hlfix{find correct word for this} is the minimal polynomial of $\prod_{i=1}^n \Delta_{I_i}$, where $\Delta_{I_i}$ is the determinant of the $k \times k$ minor indicated by $I_i$.
\end{conj}

\end{document}

### 2018-04-25 General WLD combinatorics.tex
finished completing Sian's proof that the GN is correct

@@
 
-To prove that this algorithm gives the Grassmann necklace of the diagram we need a lemma.
+To prove that this algorithm gives the Grassmann necklace of the diagram we need two lemmas.
 
@@
 
+\begin{lem}\label{lem basis as perm}
+Let $W$ be an admissible Wilson loop diagram and let $\PP_W$ be the positroid associated to $W$.
+A $k$-subset $J \in \binom{[n]}{k}$ is a basis for $\PP_W$ if and only if there is a set bijection between $J$ and the set of propagators of $W$ such that for each $j\in J$ the propagator associated to $j$ is supported on vertex $j$.
+\end{lem}
+
+\begin{proof}
+\note{I don't know if you already have this in your previous papers or not; but it is important so I wanted to extract it as a lemma.
+The proof of the next proposition originally contained the lines ``Recall from [ref] that a $k$-subset $J \in \binom{[n]}{k}$ is a basis for $\PP_W$ if and only if it has no subset $U \subseteq J$ such that $|U| > |Prop(U)|$.'' but I don't know what that ref is nor whether that ref would also prove this lemma.}
+\end{proof}
+
 \begin{prop}\label{res:alg gives GN}
-The sequence of $k$-subsets obtained by applying Algorithm~\ref{alg:put GN on WLD} to an admissible diagram $W$ is exactly the Grassmann necklace of the positroid associated to $W$.
+The sequence of $k$-subsets obtained by applying Algorithm~\ref{alg:put GN on WLD} to an admissible diagram $W$ is exactly the Grassmann necklace of the positroid associated to $W$; specifically if we let  $I_i$ be the set of labels on edge $(i,i+1)$ then the sequence $\II = (I_1, \dots, I_n)$ is the Grassmann necklace of the positroid associated to $W$.
 \end{prop}
-
-\note{I think the statement should be clearer about what this sequence is, in the way that the first line of the proof currently is.}
 
@@
 
-\note{I tried to make the first part of this proof a bit tidier by using contradiction.
-I will do the same for the second part (what is currently below) and also finish the proof, when I have a chance}
+\medskip
 
@@
 \end{itemize}
-Recall from [ref] that a $k$-subset $J \in \binom{[n]}{k}$ is a basis for $\PP_W$ if and only if it has no subset $U \subseteq J$ such that $|U| > |Prop(U)|$.
-It is immediately clear from the construction that $I_i$ is a basis for each $i$: the algorithm is effectively pairing each $j \in I_i$ with a unique propagator supported on that vertex, so $|Prop(U)| \geq U$ for all $U \subseteq I_i$.
-
-If $\exists l \in J$ with $Prop(l) = \emptyset$ then $J$ is clearly not a basis, so suppose otherwise.  Write
-\[I_i = [i_1 <_i i_2 <_i \dots <_i i_r <_i \dots <_i i_k], \quad J = [i_1 <_i i_2 <_i \dots <_i j_r <_i \dots <_i j_k],\]
-so that $I_i$ and $J$ differ for the first time in the $r$th position.  Then
-\[r-1 \geq |Prop(\{i_1, \dots, i_{r-1}\})| = |Prop(\{i_1, \dots, i_{r+1},j_r\})|,\]
-If $|Prop(\{i_1, \dots, i_{r-1}|\}| = r-1$ then we are done; otherwise
+The algorithm is pairing each $j \in I_i$ with a unique propagator supported on that vertex so by Lemma~\ref{lem basis as perm} $I_i$ is a basis for $\PP_W$.
+%%Recall from [ref] that a $k$-subset $J \in \binom{[n]}{k}$ is a basis for $\PP_W$ if and only if it has no subset $U \subseteq J$ such that $|U| > |Prop(U)|$.
+It is immediately clear from the construction that $I_i$ is a basis for each $i$: the algorithm is pairing each $j \in I_i$ with a unique propagator supported on that vertex, so $|Prop(U)| \geq U$ for all $U \subseteq I_i$.
+
+%%If $\exists l \in J$ with $Prop(l) = \emptyset$ then $J$ is clearly not a basis, so suppose otherwise.  Write
+%%\[I_i = [i_1 <_i i_2 <_i \dots <_i i_r <_i \dots <_i i_k], \quad J = [i_1 <_i i_2 <_i \dots <_i j_r <_i \dots <_i j_k],\]
+%%so that $I_i$ and $J$ differ for the first time in the $r$th position.  Then
+%%\[r-1 \geq |Prop(\{i_1, \dots, i_{r-1}\})| = |Prop(\{i_1, \dots, i_{r+1},j_r\})|,\]
+%%If $|Prop(\{i_1, \dots, i_{r-1}|\}| = r-1$ then we are done; otherwise
+
+Suppose we have $J$ such that $J$ is a basis and yet is lexicographically less than $I_i$ with respect to $<_i$.
+By Lemma~\ref{lem basis as perm} there is a set bijection between $J$ and the propagators of $W$ such that the propagator associated to $j$ is supported on vertex $j$.
+Choose one such bijection.
+For a propagator $p$ of $W$ write $J(p)$ for the associated $j$ according to this bijection.
+Similarly write $I_i(p)$ for the vertex assigned to $p$ by the algorithm.
+Since $J$ is lexicographically smaller than $I_i$, the $<_i$-smallest element of the symmetric difference of $J$ and $I_i$ is some $j_0\in J$, $j_0 \not\in I_i$.
+
+Let $p$ be the propagator such that $J(p)=j_0$.
+Since $j_0\not\in I_i$ but $p$ is supported at $j_0$, then $I_i(p) <_i j_0$.
+Thus the propagator $p$ has the following property: $I_i(p) <_i J(p)$ and $I_i\cap \interval{i}{I_i(p)} = J\cap \interval{i}{I_i(p)}$.
+Call this property $A$.
+
+{}From the previous paragraph we conclude that if we ever had a $J$ which is lexicographically less than $I_i$ and yet a basis of $\PP_W$ then there exists a propagator $p$ which has property $A$.
+
+Finally, we will prove that whenever there is a propagator $p$ which has property $A$ then there is another propagator $r$ which also has property $A$ and for which $I_i(r) <_i I_i(p)$.
+Since $I_i$ is finite this would lead to infinte regress and hence is impossible and thus there can be no such $J$ which will complete the proof of the proposition.
+
+So suppose $p$ has property $A$.
+The same vertices in $\interval{i}{I_i(p)}$ are in the image of the assignment from $J$ and the image of the assignment from $I_i$ so the same number of propagators are assigned to vertices in this interval by each assignment.
+However $p$ is one of the propagators assigned to a vertex in this interval in $I_i$ but not in $J$.
+Thus there exists a propagator $q$ for which $J(q)\in \interval{i}{I_i(p)}$ but $I_i(q) >_i I_i(p)$.
+Therefore $J(q)<_i I_i(q)$ and  $I_i\cap \interval{i}{J(q)} = J\cap \interval{i}{J(q)}$.
+This is analogous to property $A$ but with the roles of $J$ and $I_i$ switched.
+Thus by the same argument we must have a propagator $r$ for which $I_i(r)\in \interval{i}{J(q)}$ but $J(r)>_i J(q)$.
+Therefore $r$ has property $A$ which is what we wanted to prove.
 

### 2018-04-25 General WLD combinatorics.tex
put in the algorithm for the denominator but haven't proved it yet

@@
 
-I'd like to end this paper with a proof of a conjecture (that I think I need for a subsequent paper, and this seems the natural place to put it. This is as follows:
-
-\begin{conj}
-Given any admissibly Wilson loop diagram $W$, let $GN(W) = \{I_1, \ldots I_n\}$ be the associated Grasmann necklace.
+Put some exposition here about Theorem~\ref{thm denom}.
+
+We can also use the ideas of the above constructions to understand the denominator of the integral $I(W)$.
+
+\begin{algorithm}\label{alg WLD to denom via GN}
+Let $W$ be a Wilson loop diagram with $n$ vertices.  Let $C(W)$ be the matrix \hlfix{which has some actual name and a ref to where you define it}.
+\begin{itemize}
+  \item For each $i \in \interval{1}{n}$, we construct a factor $r_i$ as follows
+    \begin{itemize}
+      \item Use Algorithm~\label{alg:put GN on WLD} to obtain a bijection between the propagators and the $i-1$st Grassmann necklace element, $I_{i-1}$.
+Write $I_{i-1}(p)$ for the vertex associated to propagator $p$ under this bijection.
+      \item Use Algorithm~\label{alg:put GN on WLD} to obtain a bijection between the propagators and the $i$th Grassmann necklace element, $I_{i}$.
+Write $I_{i}(p)$ for the vertex associated to propagator $p$ under this bijection.
+      \item Let $S_i$ be the set of propagators $p$ such that $I_{i-1}(p) \neq I_{i}(p)$.
+      \item $\Delta_{I_i}$ is the determinant of the $k \times k$ minor of $C(W)$ indicated by $I_i$.
+      \item Let $r_i$ be $\Delta_{I_i}$ with all variables from rows associated to $p\not\in S_i$ set to $1$.
+    \end{itemize}
+  \item $R = \prod_{i=1}^n r_i$.
+\end{itemize}
+\end{algorithm}
+
+\begin{prop}\label{prop alg gives rad}
+  With notation as in Algorithm~\ref{alg WLD to denom via GN} we have the following:
+  \begin{enumerate}
+    \item Each $\Delta_{I_i}$ is homogeneous and splits into linear and quadratic factors.  
+    \item All linear factors of  $\Delta_{I_i}$ are single variables and all quadratic factors are $2\times 2$ determinants of single variables.
+    \item Quadratic factors in $r_i$ arise precisely when propagators $p$ and $q$ are supported on a common edge $(a,b)$ and $I_i(p)=a$, $I_i(q)=b$.
+    \item $r_i$ divides $\Delta_{I_i}$.
+    \item $R$ is the radical of $\prod_{i=1}^{n}\Delta_{I_i}$.
+  \end{enumerate}
+\end{prop}
+
+\begin{proof}
+\note{This is the next thing I plan to work on.  If you could tell me how many of these things you already have proved elsewhere that would be helpful to me.}
+\end{proof}
+
+\begin{thm}\label{thm denom}
+Given any admissible Wilson loop diagram $W$, let $GN(W) = \{I_1, \ldots I_n\}$ be the associated Grasmann necklace.
 Then the denominator of the integral $I(W)$ is the \hlfix{find correct word for this} is the minimal polynomial of $\prod_{i=1}^n \Delta_{I_i}$, where $\Delta_{I_i}$ is the determinant of the $k \times k$ minor indicated by $I_i$.
-\end{conj}
+\end{thm}
+
+\begin{proof}
+In view of Proposition~\ref{prop alg gives rad} it remains to prove that the $R$ of Algorithm~\ref{alg WLD to denom via GN} is $R(W)$, the denominator of the integral $I(W)$.
+
+\note{I don't want to write the rest of this right now because we need to somewhere (probably much earlier in the document) define $R(W)$ and exactly how we do so makes a difference.
+The definition I would most like is if we define it as the product of the prop together and prop to vertex limits, if we define it some other way I'll probably want a lemma to get to that formulation.}
+
+\end{proof}
 

### 2018-04-26 General WLD combinatorics.tex
commit
Changes to section 1. Math should be (mostly) correct now.

--- 2018-04-20 General WLD combinatorics.tex
@@
 \begin{dfn}\label{equivdfn}
-Two admissible Wilson loops diagrams, $W = (\cP, n)$ and $W'= (\cP', n)$ are equivalent if
+There is an equivalence relationship on the set of admissible Wilson loops diagrams: $W = (\cP, n)$ and $W'= (\cP', n)$ are equivalent if
 \begin{enumerate}
 \item There exist two different exact subdiagrams, $(P, V(P))$ and $(P', V(P'))$ of $W$ and $W'$ respectively such that $V(P) =  V(P')$.
-\item The complementary subdiagrams are identical: $(\cP \setminus P, [n] \setminus V(P)) = (\cP' \setminus P', [n] \setminus V(P'))$.
+\item The complementary subdiagrams are identical: $(\cP \setminus P, V(P)^c) = (\cP' \setminus P', V(P')^c)$.
 \end{enumerate}
 \end{dfn}
+
+\begin{eg}
+Note that since this is an equivalence relation, we may find that two Wilson loop diagrams are equivalent, even if they do not have complements of (non-trivial) exact subdiagrams in common.
+Consider the following three Wilson loop diagrams,
+\bas
+W_1 = \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
+	\begin{scope}
+	\drawWLD{8}{1.5}
+	\drawnumbers
+	\drawprop{1}{0}{4}{0}
+	\drawprop{2}{0}{4}{-1}
+    \drawprop{5}{0}{8}{0}
+    \drawprop{5}{1}{7}{0}
+		\end{scope}
+	\end{tikzpicture} \quad
+W_2 = \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
+	\begin{scope}
+	\drawWLD{8}{1.5}
+	\drawnumbers
+	\drawprop{1}{0}{4}{0}
+	\drawprop{2}{0}{4}{-1}
+    \drawprop{5}{0}{8}{0}
+    \drawprop{6}{0}{8}{-1}
+		\end{scope}
+	\end{tikzpicture} \quad
+W_3 = \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
+	\begin{scope}
+	\drawWLD{8}{1.5}
+	\drawnumbers
+	\drawprop{1}{0}{4}{0}
+	\drawprop{1}{1}{3}{0}
+    \drawprop{5}{0}{8}{0}
+    \drawprop{6}{0}{8}{-1}
+		\end{scope}
+	\end{tikzpicture} .
+\eas
+
+The diagrams $W_1 \equiv W_2$ because $(\{(5,8), (5,7), \{5,6,7,8,1\})$ and $(\{(5,8), (7,8), \{5,6,7,8,1\})$ are the corresponding differing subdiagrams.
+Furthermore, there is the equivalence $W_2 \equiv W_3$ due to the exact subdiagrams $(\{(1,4), (3,4)\}, \{1,2,3,4,5\})$ and $(\{(1,4), (1,3)\}, \{1,2,3,4,5\})$.
+This forces an equivalence between $W_1$ and $W_3$, even though one cannot partition the propagators of each into a an exact subdiagram (that may vary between the diagrams) and a complement that is fixed.
+\end{eg}
 
@@
 
-Recall the definition of the rank of a subset $C \subset [n]$.
-
 This does not, however, show that the matroids associated to each Wilson loop diagram is unique.
@@
 
-First we recall a few facts about matroids.
+First we recall a few facts about matroids, with particulars about those defined by Wilson loop diagrams.
 
@@
 That is, for all $e \not \in F$ $\rk(F \cup e) = \rk(F) +1$.
-If $W$ is an admissible Wilson loop diagram, any group of propagators defines a flat, $F(P) = = V(P^c)^c$, called a propagator flat.
+If $W$ is an admissible Wilson loop diagram, any group of propagators defines a flat, $F(P) = V(P^c)^c$, called a propagator flat.
 It consists of all vertices of $W$ that do not support any propagators outside of $P \subset \cP$.
 To see that this is flat, let $v \in V(P^c)$.
-We have that  This consists of the vertices that only support propagators in $P$.
-For example, if $W$ contains with no vertices of rank $0$, we may write $F(P) = V(P^c)^c$.
+We have that there is a $q \not \in P$ such that $q \in \Prop(v)$.
+Therefore, by the rank function, $\rk( F(P) \cup v))> \rk(F(P))$.
 \end{enumerate}
 \end{dfn}
+
+Furthermore, in \cite{wilsonloops}, the authors show that if $F$ is a cyclic flat, then there is a $P \subset \cP$ such that $F = F(P)$.
 
@@
 Then two things are true.
+
+\begin{lem} Let $W$ be a Wilson loop diagram, and $F$ is a flat. Let $C \subset F$ be the largest cycle contained in $F$. Then the following is true:
 \begin{enumerate}
-\item $C = F(\Prop (C))$
-\item $F \setminus C$ is an independent flat
+\item $C = F(\Prop (C))$ is a cyclic flat.
+\item $F \setminus C$ is an independent set. If $W$ does not contain any vertices of rank $0$, that is, all vertices support at least $1$ propagator, then $F \setminus C$ is an independent flat.
 \end{enumerate}
-
-To see the first point, note that $\rk(C) = |\Prop(C)|= \rk (F(\Prop(C)))$.
-For any $v\in C$ such that $\Prop(v) \subset \Prop(C)$, then $v \in F(\Prop(C))$.
-Therefore $S \subset F(\Prop(C))$.
+\end{lem}
+
+\begin{proof}
+If $F$ is an independent flat, then $C = \emptyset$ and the statement is trivially true.
+
+If $F$ is a dependent set, $F$ contains a circuit.
+
+To see the first point, note that $\rk(C) = |\Prop(C)| \geq F(\Prop (C)|$.
+For any $v\in C$ we have that $\Prop(v) \subset \Prop(C)$.
+This implies that $v \in F(\Prop(C))$.
+Therefore $C \subset F(\Prop(C))$.
+This implies that $|\Prop(C)| = F(\Prop (C)|$.
 Suppose there is a $v \in  F(\Prop(C)) \setminus C$.
@@
 For any $e \not \in F$, $\rk (F \setminus C \cup e) = \rk (F\setminus C) +1$, since $F$ is a flat.
-For any $e \in C$,  $\rk (F \setminus C \cup e) \neq \rk (F\setminus C)$.
-Otherwise $F\setminus C \cup e$ would be a dependent set and therefore would contain a circuit, which contradicts the hypothesis that $C$ is the largest cycle in $F$.
+For any $e \in C$,  if $\rk (F \setminus C \cup e) = \rk (F\setminus C)$, the set $F \setminus C \cup e$ is a dependent set.
+This occures either if $\rk{e} = 0$, or $F\setminus C \cup e$ contains a circuit of at least $2$ elements, which contradicts the hypothesis that $C$ is the largest cycle in $F$.
+\end{proof}
 
@@
 
-Finally, I recall a result from the previous paper about contracted diagrams and matroids.
-
-\begin{lem}
-For $W = (\cP, [n])$, write the contracted diagram $W/P = (P^c, V(P)^c)$. If $\rk F(P) = |P|$, we may identify \bas M(W/P) = \left(M(W)/ F(P)\right)|V(P)^c \;. \eas
-\end{lem}
+\begin{cor} \label{classifyflats}
+If $F$ is a flat of a Wilson loop diagram, it can be written as the union of a cyclic flat, and thus a propagator flat, and an independent flat.
+\end{cor}
+From this we see that any propagator flat can be written as a union of a cyclic propagator flat and an independent flat.
+
+Given any matroid, one may restrict it to a subset of the base set.
+The bases of the restricted matroid come from intersecting bases of the original with the subset.
+It is worth noting that a the matroid defined by a subdiagram is different from the restriction of the matroid of a Wilson loop diagram to a set of vertices.
+
+\begin{dfn} \label{restrictiondfn}
+For $W = (\cP, n)$, the restricted diagram, $W|_V$ is the matroid defined by only looking at the vertices $V \subset [n]$.
+\end{dfn}
+
+The key difference between a subdiagram and a restriction is that the propagator support function does not change in the case of restriction, while it may in the case of a subdiagram.
+In particular, for $v \in V$, $\Prop_W(v) = \Prop_{W|_V}(v)$, while $\Prop_{(P, V(P))} (v) = \Prop_W(v) \cap P$.
+
+In the sequel, I conflate a Wilson loop diagram with the matroid it defines.
 
@@
 
-\begin{lem} \label{exactcircuitlem}
-Let $(P, V(P))$ be an exact subdiagram of $W= (\cP, [n])$. The set $V(P)$ contains no circuits, $C$ such that  $\rk C< |P|$.
-\end{lem}
-
-\begin{proof}
-Recall that a circuit of rank $m$ is a set $C$ of rank $m$ and size $m+1$ such that every proper subset of $C$ is independent. I.e., \emph{a circuit is a minimal dependent set.}
+\begin{thm} \label{exactcircuitlem}
+Let $(P, V(P))$ be a subdiagram of $W= (\cP, [n])$. This is an exact subdiagram if and only if it defines a uniform matroid of rank $|P|$.
+\end{thm}
+
+\begin{proof}
+A uniform matroid of rank $r$ is one in which any set of size $ \leq r$ is independent.
+A circuit of rank $m$ is a set $C$ of rank $m$ and size $m+1$ such that every proper subset of $C$ is independent.
+I.e., \emph{a circuit is a minimal dependent set.} In other words, a matroid of rank $r$ is uniform if and only if all circuits have rank $r$.
+If $C$ is a circuit, then $|C| = r+1$.
+
+We prove the following claim: The set $V(P)$ contains no circuits, $C$, such that  $\rk C< |P|$ in $(P, V(P))$.
+Since the $V(P) = |P|+3$, $\rk V(P) \leq |P|$.
+This implies that all circuits $C$ of $(P, V(P))$ are of maximal rank, as desired.
 
 Consider a subdiagram $(P, V(P))$ of $W$.
-Suppose there is a circuit, $C \subset V(P)$ such that $\rk C = m < |P|$.
-Write $\Prop (C) = Q \subsetneq P$.
-Here, $|Q| = m$.
+Suppose there is a circuit, $C \subset V(P)$ such that $\rk C = |\Prop (C) | = m < |P|$.
 The size of the complement of $C$ is $|V(P) \setminus C| = |V(P)| -(m+1)$.
-However, since $C$ does not contain any propagators outside of $Q$, the set $V(P \setminus Q) \subset V(P )\setminus C$.
-In otherwords, there are $|P| - m$ propagators (the number of propagators in $P \setminus Q$) supported on (at most) $|V(P)|-m -1$ vertices: \bas |V(P \setminus Q)| \leq |V(P)| - m-1\;.
-\eas Since $(P, V(P))$ is an exact subdiagram of an admissible Wilson loop, $W$, we know that $|P| + 3 = |V(P)|$, and for any subset, $R$, of propagators of $W$, $|R|+3 \leq |V(R)|$.
-On there otherhand, there is a subset of propagators, $P\setminus Q$ satisfying \bas |V(P \setminus Q)| \leq |P| + 3 - m-1 = |P\setminus Q| + 2\;.
-\eas But this violates admissibility of $W$.
-\end{proof}
-
-\begin{eg}
-The converse does not hold. Consider, for instance, the diagram
-
-\begin{tikzpicture}[rotate=68] % change rotation manually as needed
-\begin{scope}
-\drawWLD{8}{2} % vertices, radius
-\drawprop{1}{0}{4}{1} % this draws a prop from (4,5) to (6,7); {0} means *centre* of the edge 4--5, {n} bumps it n "steps" clockwise from centre (for use when you have several props on one edge)
-\drawprop{2}{0}{4}{-1}
-\drawprop{8}{0}{5}{-1}
-\drawprop{7}{0}{5}{1}
-\end{scope}
-\end{tikzpicture}
-
-The subdiagram $( \{(1, 4), (5, 8)\}, \{1, 2, 4, 5, 6, 8\})$ is not exact, but it has no cycles of rank $2$.
-\end{eg}
-
-However, all is not lost.
+However, since $C$ does not contain any propagators outside of $\Prop (C)$, the set $V(P \setminus \Prop(C)) \subset V(P )\setminus C$.
+In otherwords, there are $|P| - m$ propagators supported on (at most) $|V(P)|-m -1$ vertices: \bas |V(P \setminus \Prop (C))| \leq |V(P)| - m-1\;.
+\eas Since $W$ is an admissible Wilson loop diagram, the subdiagram $(P, V(P))$ satisfies $|R| +3 \leq |V(R)|$ for all $R \subset P$.
+This gives \bas |P| - m +3 \leq V(P \setminus \Prop(C))\;.
+\eas These two inequalities are compatible if and only if \bas |P| +3 < |V(P)| \;.
+\eas
+
+In other words, the matroid associated to thet subdiagram $(P, V(P))$ is not uniform if and only if $(P, V(P))$ is not exact.
+\end{proof}
+
+In \cite{wilsonloops}, the authors show that all exact Wislon loop diagrams correspond to positroids.
+That is, they correspond to matroids that can be represented by elements of the positive Grassmannians $\Gr(|\cP|, |V|)$.
+
+\begin{dfn}
+Given a Wilson loop diagram $W$, define the positroid cell associated to a Wislon loop diagram, $\Sigma(W)$, to be the cell in the CW complex on $\Gr(|\cP|, |V|)$ defined by the realizations of $W$ that lie in $\Gr(|\cP|, |V|)$.
+\end{dfn}
+
+With this definition in mind, we have the following corrolary:
+
+\begin{cor}
+Let $(P, V(P))$ be an exact subdiagram of $W$. The matroid associated to this subdiagram corresponds to the top dimensional cell in $\Gr(|P|, |V(P)|)$.
+\end{cor}
+
+\begin{proof}
+The unique top dimensional cell of $\Gr(|P|, |V(P)|)$ is defined by all points in $\Gr(|P|, |V(P)|)$ such that all Plucker coordinates are strictly greater than $0$.
+Since $(P, V(P))$ is an exact subdiagram, this all $|P| \times |P|$ minors are non-zero.
+Intersecting these with the cases with the positive Grassmannians demands that all minors be strictly positive.
+\end{proof}
+
 To avoid the issue of exact diagrams being subdiagrams of other exact subdiagrams (for instance, any subdiagram $(q, V_q)$, for $q \in \cP$ is exact), I introduce a definition.
@@
 
-Then we have the following statement about the structure of circuits and Wilson Loop diagram.
-
-\begin{cor}
-Let $W$ be a Wilson Loop Diagram. No maximal exact subdiagram $(P, V(P))$ contains a circuit $C \subset V(P)$ of rank $\rk(C) \leq |P|$.
-\end{cor}
+Since the matroids defined by the subdiagram $(P , V(P)$ is not the same as the matroid associated to $W_{V(P)}$, one cannot say that the $W_{V(P)}$ is a uniform matroid.
+Infact, for any subset $U \subset V(P)$, $\rk_{W_{V(P)}}(U) \geq \rk_{(P , V(P)}(U)$.
+This is because adding propagators to vertices can only increase the rank.
+In particular this implies that, for any subset $U \subset V(P)$, if $|U| \leq |P|$, then $U$ is independent in both the restricted matroid $W_{V(P)}$, and the original, $W$.
+
+In what follows, maximal exact subdiagrams play a significant role. First, we show that maximal exact subdiagrams of an admissible Wilson loop diagram are disjoint.
 
 \begin{lem}
-Let $W = (\cP, [n])$ be a Wilson loop diagram, and $(P, V(P))$ a maximal exact subdiagram with $P \subsetneq \cP$.
-Then the set $V(P)^c = F(P^c)$ is a propagator flat with rank  \bas \rk F(P^c) = |P^c| \;.
-\eas
-\end{lem}
-
-\begin{proof}
-To see that $V(P)^c$ is a propagators flat by construction. It remains to check that this this has maximal rank.
-
-Notice that $n= |V(P)| + |F(P^c)| \geq |P| + |P^c| +4$, and $|V(P)| = |P| +3$. Therefore \bas |F(P^c)| > |P^c| \;.\eas In other words, $F(P^c)$ is a dependent flat.
-
-We claim that if $C$ is the largest cycle in $F(P^c)$, then $\Prop(C) = P^c$.
-In other words, $\rk F(P^c) = |P^c|$.
-Otherwise, $F(P^c) = C \cup F$, where $F$ is an independent flat.
-In other words, $\rk (F) = i < |P^c| - \rk (C)$.
-Then $F \cup V(P) = V(Q)$ where $|Q| \geq |P| +i$ while $F \cup V(P) \leq |P| + 3 + i$.
-Therefore, either $W$ is not a Wilson loop diagram, or $(P, V(P))$ is not a maximal exact subdiagram.
-\end{proof}
-
-There are several corollaries of Lemma \ref{exactcircuitlem} that are useful. There are many more than I list here, we can find a corollary for each equivalent way of representing these positroids.
-
-\begin{cor} \label{exactindepcor}
-If the subdiagram $(P, V(P))$ is exact in $W= (\cP, [n])$, every subset $S \subset V(P)$ of size $|S| \leq |P|$ is independent.
-\end{cor}
-
-\begin{proof}
-Since $V(P)$ has no circuits of rank $< |P|$, no set of size $|S| \leq |P|$ contains a circuit, and is therefore, independent.
-\end{proof}
-
-\begin{cor} \label{exactposcor}
-If the subdiagram $(P, V(P))$ is exact in $W= (\cP, [n])$, it represents a totally positive $\Grtnn(|P|, |V(P)|)$ cell of the matroid represented by $W$.
-\end{cor}
-
-\begin{proof}
-Since there are no circuits of rank $m < |P|$, every subset of size $|P|$ is a basis. This defines the totally positive cell $\Grtnn(|P|, |V(P)|)$.
-\end{proof}
-
-%\begin{rmk}
-%Sian: Your observation that every Grassman Necklace sees the exact subdiagrams as "gapless strings" on $V(P)$ is also a corrollary of this.
-(The gaps in a Grassmann necklace come from the existance of circuits.
-No circuits $\Leftrightarrow$ no gaps in necklace.) However, I can't come up with a clean enough statement of your idea to write it as a corrollary.
-Feel free to feed me a statement and I will happily write it up.
-%\end{rmk}
-
-It is worth noting that all of these have converses if when we consider diagrams, and stop considering subdiagrams. Namely:
-
-\begin{lem}\label{exactequivs}
-Let $W = (\cP, [n])$ be a Wilson loop diagram. Then the following are equivalent. \begin{enumerate}
-\item $W$ is exact.
-\item All subsets $V$ of size $|V| = |\cP|$ are bases.
-\item The only cycles in $W$ have rank $|\cP|$.
-\item The only dependent flat of $W$ is $F(\cP)$. This is also a cyclic flat.
-\end{enumerate}
-\end{lem}
-
-\begin{proof}
-Obvious?
-\end{proof}
+Let $W = (\cP, n)$ be an admissible Wilson loop diagram, and $(Q, V(Q))$, $(R, V(R))$ two maximal exact subdiagrams. Then $Q\cap R = \emptyset$.
+\end{lem}
+
+\begin{proof}
+Consider an exact subset of a maximally exact subdiagram, $T \subset Q$.
+For $p \in Q \setminus T$, $|V(T \cup p)| = |T| +1 +3  = |V(T)| +1$.
+That is, by extending an exact subdiagram to a larger one, one extends the vertex set by exactly on vertex per proppagator.
+Therefore, if $T \neq \emptyset = Q \cap R$, \bas |V(Q \cup R)| = |T| +3 + |Q \setminus T| + |R \setminus T| = |Q \cup R| + 3\;.\eas Therefore, if $(Q, V(Q))$ and $(R, V(R))$ are two exact subdiagrams such that $Q\cap R \neq \emptyset$, then $(Q \cup R, V(Q \cup R))$ is exact.
+\end{proof}
+
+\begin{lem} \label{maxexactcomplementrank}
+Let $W = (\cP, [n])$ be a Wilson loop diagram, and $(P, V(P))$ an exact subdiagram with $P \subsetneq \cP$.
+Then the set $V(P)^c = F(P^c)$ is a propagator flat of maximal rank  \bas \rk F(P^c) = |P^c| \;.
+\eas If $(P, V(P))$ is maximal, then $F(P^c)$ is cyclic.
+\end{lem}
+
+\begin{proof}
+By construction, $V(P)^c$ is a propagator flat.
+Furthermore, it is not empty.
+In particular, since $(P, V(P))$ is an exact subdiagram, the vertices $V(P)$ cannot support a larger set of propagators (otherwise $W$ would no longer be admissible).
+Therefore, since $P \subsetneq \cP$, $V(P)^c = F(P^c)$ is not an empty set.
+
+Notice that $n= |V(P)| + |F(P^c)| \geq |P| + |P^c| +4$, and $|V(P)| = |P| +3$.
+Therefore \bas |F(P^c)| > |P^c| \;.\eas In other words, $F(P^c)$ is a dependent flat.
+By corollary \ref{classifyflats} $F(P^c)$ is the union of a cyclic flat and an independent flat.
+
+Let $(P, V(P))$ be maximal exact subdiagram.
+Suppose $F(P^c) = C \cup F$, where $C$ is the largest cyclic flat contained in $F(P^c)$ and $F$ is a non-empty independent set.
+Since $C = F(\Prop(C))$, we can write $V(Q)^c = F(\Prop(C))$, with \ba Q = (\Prop(C))^c \label{Qdef}\;.
+\ea Furthermore, \ba \rk(F) = |F| \leq \rk(F(P^c)) - \rk(C)  \leq |P^c| - \rk(C) \;.
+\label{increasingrank}\ea The first equality comes from the fact that $F$ is an independent set.
+Combining \eqref{Qdef} and \eqref{increasingrank} gives \ba |P| + |F| \leq |P| + |P^c| - \rk(C) = |Q| \;.
+\label{Qsizebound}\ea Furthermore, since $V(Q) = F \cup V(P)$, we may write  \ba |V(Q)| = |F| + |V(P)| = |F| + |P| +3 \label{VQsize} \;.\ea Combining this with \eqref{Qsizebound} gives $|V(Q)| - 3 \leq |Q|$.
+That is, either $W$ was not admissible, or $(P,V(P))$ was not a maximal exact subdiagram.
+In otherwords, $F$ cannot be non-empty, proving that $F(P^c)$ is a cyclic flat, and therefore of maximal rank.
+
+Let $(Q, V(Q))$ be an exact subdiagram that is not maximal, with $Q \subset P$ defining he maximal exact subdiagram above.
+Then by lemma \ref{??} $|V(P)| = |V(Q)| + |P \setminus Q|$.
+Let $F(P^c)$ be the cyclic set defined as the complement of $V(P)$.
+Then $V(Q)^c = F(P^c) \cup F$, where $F$ is an independent set of size $|P \setminus Q|$ and with $(P \setminus Q) \subset \Prop (F)$.
+Thereofore, $\rk (F) = |Q^c|$.
+\end{proof}
+
+While one still cannot equate a subdiagram with a restriction, this lemma allows one to write a maximal exact subdiagram as a contraction.
+First, recall a result from \cite{wilsonloops} about contracted diagrams and matroids.
+
+\begin{lem}
+For $W = (\cP, [n])$, write the contracted diagram $W/P = (P^c, V(P)^c)$. If $\rk F(P) = |P|$, we may identify \bas M(W/P) = M(W)/ F(P) \;. \eas
+\end{lem}
+
+In other words, a maximally exact subdiagram $(P, V(P))$  can be written as a contraction by the complementary propagator flat: \bas (P, V(P)) = W/F(P^c) \;.\eas
 
@@
 
-Write $W = (P \cup R, [n])$ and $W' = (P \cup R', [n])$, where $P = \cP \cap \cP'$.
-
 Assume that $W$ and $W'$ are equivalent.
-Let $(\{Q_i, V(Q_i)\})$ and $(\{Q'_i, V(Q'_i)\})$ be the sets of maximal exact subdiagrams that intersect $V(R)$ and $V(R')$ respectively.
-By Lemma \ref{exactcircuitlem}, if there is a circuit in any $C_i \subset V(R_i)$, it is of rank $|R_i|$ and there is a corresponding circuit $C'_i \subset V(R'_i)$ such that $C_i = C'_i$.
-Any other circuits of $W$ and $W'$ lie entirely within the complementary set of vertices, \bas(\cup_i V(R_i))^c = \cap_i F(R_i^c) = \cap_i F(R^{' c}_i) \;.\eas As this depends wholely on the propagators in $P$, which is common to both diagrams, these circuits are also the same.
-Since all circuits are the same, $M(W) = M(W')$.
-
-For the converse, assume that $M(W) = M(W')$.
-Then the cyclic flats of $W$ correspond to the cyclic flats of $W'$.
-Let $Q \subset P$ be the largest subset of propagators such that $F(Q)$ is a cyclic flat.
-This may be an empty set.
-Let $Q^c$ and $Q^{c'}$ be the complementary set of propagators in $\cP$ and $\cP'$ respectively.
-They contain $R$ and $R'$ respectively.
-We see that $V(Q^c) = V(Q^{c'})$.
-
-Since $F(Q)$ is a cyclic flat, it has maximal rank.
-Therefore, we can write \bas M(W)/F(Q) = M(Q^c, V(Q^c)) = M(W')/F(Q) = (Q^{c'}, V(Q^{c'})) \;.
-\eas Therefore, it is sufficient to compare the contracted Wilson loop diagrams $W/Q = M(Q^c, V(Q^c))$ and $ W'/Q = (Q^{c'}, V(Q^{c'}))$.
-We do so iteratively by quotienting by the cyclic flats.
-
-If there do not exist a $T \subsetneq Q^c$ and $T' \subsetneq Q^{c'}$ such that $F(T) = F(T')$ are cyclic, then, by \ref{exactequivs}, $W/Q$ and $W'/Q$ are exact.
-Therefore, they are equivalent, as are $W$ and $W'$.
-
-If there do exist $T \subsetneq Q^c$ and $T' \subsetneq Q^{c'}$, such that $F(T) = F(T')$ are cyclic, chose $T$ and $T'$ such that they do not contain any other proper subset of propagators that define cyclic flats.
-Then the Wilson loop diagram $(T, V(T))$ and $(T', V(T'))$ are both exact, and correspond to maximal exact subdiagrams of $(W/Q)$ and $(W'/Q')$.
-Furthermore, $V(T) = V(T')$.
-Otherwise, $F(Q^c \setminus T) \neq F(Q^{c'} \setminus T')$, with contradicts that the corresponding matroids are equal; $M(W/Q)=M(W'/Q')$.
-Therefore, and differences in the propagators structure between the subdiagrams $(T, V(T))$ and $(T', V(T'))$ correspond to different representations of equivalent subdiagrams.
-
-We next consider $(W/Q)/T$ and $(W'/Q')/T'$.
-
+Without loss of generality, write $W = (P \cup R, [n])$ and $W' = (P \cup R', [n])$, where $P \subset \cP \cap \cP'$ and $(R, V(R))$ and $(R', V(R'))$ are two maximally exact subdiagrams, with $R \neq R'$, but $V(R) = V(R')$.
+If this is not the case, one may always find a family of diagram, $\{W_i\}$ satisfying this condition and forming a transitive chain connecting $W$ to $W'$ in the equivalence class.
+
+Let $U \subset V(R)$ be any subset of size $|U| = |R|$.
+The set $U$ is independent in the subdiagram $(R, V(R))$, and thus in $W$.
+The complementary set $F(P)$ is a flat of maximal rank by lemma \ref{maxexactcomplementrank} ($\rk(F(P)) = |P|$).
+Let $B \subset F(P)$ be a maximal indpendent set ($\rk B = |P|$) in $F(P)$.
+Since $F(P)$ is a flat, adding any element of $V(R)$ to $B$ increases the rank.
+Therefore, any basis of $W$ can be written as $B \cup U$.
+However, since $F(P)$ is common to both $W$ and $W'$, and $V(R) = V(R')$, any any basis of $W'$ can also be written $B \cup U$.
+Thus both matroids have the same bases sets, proving that they are the same.
+
+For the converse, assume that the matroids associated to $W$ and $W'$ are the same: $M(W) = M(W')= M$.
+Let $\{(P_i, V(P_i)\}_{i=1}^k$ and $\{(P'_i, V(P'_i)\}_{i=1}^l$ be the sets of maximally exact subdiagrams of $W$ and $W'$.
+Write $F_i = F(P_i)$ and $F'_i = F(P^{'c}_i)$ to be the complementary cyclic flats.
+By Lemma \ref{??} $M/F_i$ is a uniform matroid.
+Thereofore, $k = l$, and we may write $V(P_i) = V(P'_i)$.
+
+Reorganize the vertex sets as follows: \ba \cup_{P_i \neq P_i'} V(P_i) = V(\cup_{P_i \neq P'_i} P_i)  \label{vertexsets}\; .\ea Since maximal exact subdiagrams are disjoint, and single propapagators may define maximal subdiagrams, $\cup_{i = 1}^k P_i = \cup_{i = 1}^k P'_i = \cP$.
+Then equation \eqref{vertexsets} becomes \bas \cap_{P_i \neq P_i'} (F(P_i^c))^c = F(\cup_{P_j = P'_j} P_j)^c \;.\eas These flats may, of course, be empty.\todo{Is this paragraph necessary?}
+
+Define a family of Wilson loop diagrams, $W_0$ to $W_k$ defined such that $W_0 = W$ and $W_i$ is derived from $W_{i-1}$ by replacing the propagator set $P_i$ with $P'_i$.
+In this manner, $W' = W_k$ and $W_i \sim W_{i+1}$, making $W \sim W'$.
 \end{proof}

### 2018-05-01 General WLD combinatorics.tex
some typos and comments in sections 1, 2.1 and 2.2

@@
 These are called propagators.
-The condition on $i_r$ and $j_r$ means that the propagator does not go between adjascent edges.
+The condition on $i_r$ and $j_r$ means that the propagator does not go between adjacent edges.
 Let $\cP = \{p_r\}_{r=1}^k$ be the set of propagators.
@@
 \begin{enumerate}
-\item For $p \in \cP$, let $V_p = \{i_p, i_p+1, j_r, j_r+1\}$ be the set of vertices supporting $p$. Then, for $P \subset \cP$, the set $V_P = \cup_{p \in P} V_p$ is the vertex support of $P$.
+\item For $p \in \cP$, let $V_p = \{i_p, i_p+1, j_r, j_r+1\}$\note{This has a notational problem, should $p$ be the subscript or $r$.
+I think $p$ is better and is entirely clear, but strictly speaking that's not what Definition~\ref{WLdfn} says (though in this case since we don't know the index of $p$ we don't have any way to write $p$'s ends by a strict interpretation of Definition~\ref{WLdfn}).} be the set of vertices supporting $p$.
+Then, for $P \subset \cP$, the set $V_P = \cup_{p \in P} V_p$ is the vertex support of $P$.\note{I don't like using $\subset$ in a mixed audience because whether or not $\subset$ is strict depends on whether you are an algebraic geometer (and some other related areas) or not so in a mixed audience it is unclear.}
 \item For $V \subset [n]$, write $\Prop(V) = \{ p \in \cP | V_p \cap V \neq \emptyset \} $.
@@
 \end{dfn}
+\note{Later I will also want a different kind of subobject, one with a subset of the propagators but where the vertex set contains $V(P)$ but may be larger (the most important instance being when it is $[n]$.)  This kind of subobject doesn't need a particular name, nor does it need to be defined up here, but I wanted to mention it so we have it in mind.}
 
@@
 
-\begin{dfn}\label{equivdfn}
+\begin{dfn}\label{equivdfn}\note{Maybe it would be clearer to say the equivalence relation generated by $W$ and $W'$ which satisfy $1$ and $2$; this helps the note in the next example be less awkward too.}
 There is an equivalence relationship on the set of admissible Wilson loops diagrams: $W = (\cP, n)$ and $W'= (\cP', n)$ are equivalent if
@@
 
-In \cite{wilsonloop}, Amat and Agarwala show that admissible Wilson loop diagrams with $k$ propagators corresponds to positroids of rank $k$ (a matroid that can be represented by an element of $\Gr(k, n)$.
-)
-
-\begin{thm}\cite{wilsonloop}An admissible Wilson loop diagram, $W =(\cP, n)$, defines a matroid with base set $[n]$.
+In \cite{wilsonloop}, Amat and Agarwala show that admissible Wilson loop diagrams with $k$ propagators corresponds to positroids of rank $k$ (a matroid that can be represented by an element of $\Gr(k, n)$.)
+
+\begin{thm}[\cite{wilsonloop}] An admissible Wilson loop diagram, $W =(\cP, n)$, defines a matroid with base set $[n]$.
 The independent sets are exactly those subsets $V \subseteq [n]$ such that $\not \exists U\subseteq V$ satisfying $|\Prop(U)|> |U|$.
@@
 
-This does not, however, show that the matroids associated to each Wilson loop diagram is unique.
+This does not, however, show that the matroid associated to each Wilson loop diagram is unique.
 In fact, in \cite{wilsonloop}, the authors show that if two diagrams are equivalent then they define the same matroid [cite theorem here].
@@
 \item The rank of a set $|V| \subset [n]$, is bounded above by $\rk(V) \leq \min\{ |V| , |\Prop(V)|\}$.
-If $V$ is an independent set, then $\rk(V) = |V|$.
+If $V$ is an independent set, then $\rk(V) = |V|$\note{The spacing is weird in $\rk$.
+Looking at your definition I think it is on purpose, so I think I'm missing something as to why.
+It looks particularly odd when there is a subscript to the rank eg after Def 2.10}.
 Furthermore, if $v \in [n]$, and $q \in \Prop(v)$, then for any $V \subset [n]$ such that $q \not \in \Prop(V)$, $\rk(V \cup v) = \rk(V) +1$.
@@
     In other words, if $C$ is a circuit of a Wilson loop diagram, then \bas \rk(C) = |C|-1 = |\Prop(C)| \;. \eas
-\item A flat, $F$, of a matroid is a maximally dependent set.
+\item A flat, $F$, of a matroid is a maximally dependent set \note{Maximal for its rank is better than maximally dependent.
+Alternately maybe maximal for dependence would be better, but in that case I would really just be meaning rank again}.
 That is, for all $e \not \in F$ $\rk(F \cup e) = \rk(F) +1$.
@@
 \begin{cor} \label{classifyflats}
-If $F$ is a flat of a Wilson loop diagram, it can be written as the union of a cyclic flat, and thus a propagator flat, and an independent flat.
+If $F$ is a flat of a Wilson loop diagram, it can be written as the union of a cyclic flat, and thus a propagator flat, and an independent flat.\note{What would you think of putting ``and thus a propagator flat'' in parentheses or something; otherwise I'm concerned that the nesting structure of this sentence is not sufficiently clear.}
 \end{cor}
@@
 
-Since the matroids defined by the subdiagram $(P , V(P)$ is not the same as the matroid associated to $W_{V(P)}$, one cannot say that the $W_{V(P)}$ is a uniform matroid.
-Infact, for any subset $U \subset V(P)$, $\rk_{W_{V(P)}}(U) \geq \rk_{(P , V(P)}(U)$.
+Since the matroid defined by the subdiagram $(P , V(P))$ is not the same as the matroid associated to $W_{V(P)}$, one cannot say that the $W_{V(P)}$ is a uniform matroid.
+In fact, for any subset $U \subset V(P)$, $\rk_{W_{V(P)}}(U) \geq \rk_{(P , V(P))}(U)$.
 This is because adding propagators to vertices can only increase the rank.
@@
 \begin{lem} \label{maxexactcomplementrank}
-Let $W = (\cP, [n])$ be a Wilson loop diagram, and $(P, V(P))$ an exact subdiagram with $P \subsetneq \cP$.
+Let $W = (\cP, n)$ be a Wilson loop diagram, and $(P, V(P))$ an exact subdiagram with $P \subsetneq \cP$.
 Then the set $V(P)^c = F(P^c)$ is a propagator flat of maximal rank  \bas \rk F(P^c) = |P^c| \;.
@@
 Then $V(Q)^c = F(P^c) \cup F$, where $F$ is an independent set of size $|P \setminus Q|$ and with $(P \setminus Q) \subset \Prop (F)$.
-Thereofore, $\rk (F) = |Q^c|$.
+Therefore, $\rk (F) = |Q^c|$.
 \end{proof}
@@
 \end{thm}
+\note{I don't understand how this section (and this theorem) relate to the preivous section, which has the same content in its main theorem.}
 

### 2018-05-01 General WLD combinatorics.tex
working on prop 4.2 and some typos elsewhere in sec 4

@@
     \begin{itemize}
-      \item Use Algorithm~\label{alg:put GN on WLD} to obtain a bijection between the propagators and the $i-1$st Grassmann necklace element, $I_{i-1}$.
+      \item Use Algorithm~\ref{alg:put GN on WLD} to obtain a bijection between the propagators and the $i-1$st Grassmann necklace element, $I_{i-1}$.
 Write $I_{i-1}(p)$ for the vertex associated to propagator $p$ under this bijection.
-      \item Use Algorithm~\label{alg:put GN on WLD} to obtain a bijection between the propagators and the $i$th Grassmann necklace element, $I_{i}$.
+      \item Use Algorithm~\ref{alg:put GN on WLD} to obtain a bijection between the propagators and the $i$th Grassmann necklace element, $I_{i}$.
 Write $I_{i}(p)$ for the vertex associated to propagator $p$ under this bijection.
@@
   \begin{enumerate}
-    \item Each $\Delta_{I_i}$ is homogeneous and splits into linear and quadratic factors.  
-    \item All linear factors of  $\Delta_{I_i}$ are single variables and all quadratic factors are $2\times 2$ determinants of single variables.
+    \item Each $\Delta_{I_i}$ is homogeneous.
+    \item Each $\Delta_{I_i}$ splits into linear and quadratic factors.
+All linear factors of  $\Delta_{I_i}$ are single variables and all quadratic factors are $2\times 2$ determinants of single variables.
     \item Quadratic factors in $r_i$ arise precisely when propagators $p$ and $q$ are supported on a common edge $(a,b)$ and $I_i(p)=a$, $I_i(q)=b$.
@@
 \begin{proof}  
-\note{This is the next thing I plan to work on.  If you could tell me how many of these things you already have proved elsewhere that would be helpful to me.}
+\begin{enumerate}
+    \item The nonzero entries of $C(W)$ are independent indeterminates and so every $i\times i$ minor of $C(W)$ is homogeneous of degree $i$ or is $0$.  Thus each $\Delta_{I_i}$ is homogeneous.  
+    \item Using the expression for the determinant as a sum over permutations we see that $\Delta_{I_i}$ is a sum over bijections between $I_i$ and $\mathcal{P}$.
+The nonzero terms in this sum are precisely those bijections such that each propagator is associated to one of its supporting vertices in $I_i$, since only those locations in $C(W)$ are nonzero.
+Since the nonzero entries of $C(W)$ are independent there can be no cancellation between terms in this expansion.
+
+Suppose $\Delta_{I_i}$ has an irreducible factor $f$.
+Let $\mathcal{P}'$ be the set of propagators which contribute a variable to $f$ and let $J$ be the set of vertices which contribute a variable to $f$.
+
+The first claim is that the minor of $C(W)$ associated to $\mathcal{P}'$ and $J$ is precisely $f$.
+
+Proof of claim: By the structure of determinants $\Delta_{I_i} = fg$ where $g$ involves only variables associated to propagators not in $\mathcal{P}'$ and associated to vertices not in $J$.
+Expanding out $fg$, then, we get a signed sum of monomials where in each monomial $f$ contributes those variables associated both to a propagator in $\mathcal{P}'$ and to a vertex in $J$ and $g$ contributes those variables associated both to a propagator not in $\mathcal{P}'$ and to a vertex not in $J$ and no other variables appear.
+Since there is no cancellation between terms, this means that $\Delta_{I_i}$ contains no other variables.
+Therefore $\Delta_{I_i}$ is the same as the determinant of the matrix obtained by taking the submatrix of $C(W)$ which gave $\Delta_{I_i}$ and setting all these other variables to $0$.
+This new matrix is, up to permutations of rows and columns, a block matrix with one block for $\mathcal{P}'$ and $J$ and the other block for the complements.
+Thus its determinant, and hence also $\Delta_{I_i}$, is the product of the minors for these two blocks.
+By which variables appear, these two factors are also $f$ and $g$ and so in particular $f$ is the minor of $C(W)$ associated to $\mathcal{P}'$ and $J$.
+
+Now suppose for a contradiction that $f$ has degree $\geq 3$. \note{This is where I'm working next and maybe the result isn't true.  I will send you an example unless I figure it out myself.}
+
+    \item 
+    \item 
+    \item 
+  \end{enumerate}
 \end{proof}

### 2018-05-10 General WLD combinatorics.tex
Combined section 2.1 and 2.2 into a more coherent stream

@@
 \newcommand{\D}{\partial}
-\newcommand{\rk}{\textrm{rk }}
+\newcommand{\rk}{\textrm{rk}}
 \newcommand{\spn}{\textrm{span }}
@@
 \begin{enumerate}
-\item For $p \in \cP$, let $V_p = \{i_p, i_p+1, j_r, j_r+1\}$\note{This has a notational problem, should $p$ be the subscript or $r$.
-I think $p$ is better and is entirely clear, but strictly speaking that's not what Definition~\ref{WLdfn} says (though in this case since we don't know the index of $p$ we don't have any way to write $p$'s ends by a strict interpretation of Definition~\ref{WLdfn}).} be the set of vertices supporting $p$.
-Then, for $P \subset \cP$, the set $V_P = \cup_{p \in P} V_p$ is the vertex support of $P$.\note{I don't like using $\subset$ in a mixed audience because whether or not $\subset$ is strict depends on whether you are an algebraic geometer (and some other related areas) or not so in a mixed audience it is unclear.}
-\item For $V \subset [n]$, write $\Prop(V) = \{ p \in \cP | V_p \cap V \neq \emptyset \} $.
+\item For $p \in \cP$, let $V_p = \{i_p, i_p+1, j_p, j_p+1\}$ be the set of vertices supporting $p$. Then, for $P \subseteq \cP$, the set $V_P = \cup_{p \in P} V_p$ is the vertex support of $P$.
+\item For $V \subseteq [n]$, write $\Prop(V) = \{ p \in \cP | V_p \cap V \neq \emptyset \} $.
+\item For $P \subseteq \cP$, define $F(P) = V(P^c)^c$ to be the set of vertices in $[n]$ that only support propagators in the set $P$. 
 \end{enumerate}
 \end{dfn}
+
+It is sometimes useful to discuss propagators in terms of the edges supporting them, rather than the vertices.
+
+\begin{dfn}
+The $i^{th}$ edge of $W$ is the edge of the external polygon that lies between the vertices $i$ and $i+1$. 
+\end{dfn}
+
+In this manner, the propagator $p = (i, j)$ is supported by the $i^{th}$ and $j^{th}$ edges.
 
@@
 
-\begin{dfn}\label{equivdfn}\note{Maybe it would be clearer to say the equivalence relation generated by $W$ and $W'$ which satisfy $1$ and $2$; this helps the note in the next example be less awkward too.}
-There is an equivalence relationship on the set of admissible Wilson loops diagrams: $W = (\cP, n)$ and $W'= (\cP', n)$ are equivalent if
+\begin{dfn}\label{equivdfn}
+There is an equivalence relationship on the set of admissible Wilson loops diagrams generated by the following binary relation: $W = (\cP, n) \sim W'= (\cP', n)$ if
 \begin{enumerate}
@@
 
-The diagrams $W_1 \equiv W_2$ because $(\{(5,8), (5,7), \{5,6,7,8,1\})$ and $(\{(5,8), (7,8), \{5,6,7,8,1\})$ are the corresponding differing subdiagrams.
-Furthermore, there is the equivalence $W_2 \equiv W_3$ due to the exact subdiagrams $(\{(1,4), (3,4)\}, \{1,2,3,4,5\})$ and $(\{(1,4), (1,3)\}, \{1,2,3,4,5\})$.
+The diagrams $W_1 \sim W_2$ because $(\{(5,8), (5,7), \{5,6,7,8,1\})$ and $(\{(5,8), (7,8), \{5,6,7,8,1\})$ are the corresponding differing subdiagrams.
+Furthermore, there is the equivalence $W_2 \sim W_3$ due to the exact subdiagrams $(\{(1,4), (3,4)\}, \{1,2,3,4,5\})$ and $(\{(1,4), (1,3)\}, \{1,2,3,4,5\})$.
 This forces an equivalence between $W_1$ and $W_3$, even though one cannot partition the propagators of each into a an exact subdiagram (that may vary between the diagrams) and a complement that is fixed.
-\end{eg}
+\end{eg} \note{Did you change $\sim$ to $\equiv$?
+Or was I being flaky?
+If you prefer different notation, lets discuss.}
 
@@
 
-Next, we show that this is the only condition under which two Wilson loop diagrams define the same matroid.
-
-\begin{thm}
-Two Wilson loop diagrams define the same matroid if and only if the are equivalent.
-\end{thm}
+In the remainder of this section, we show that two admissible Wilson loop diagrams define the same matroid if an only if they are equivalent.
+Furthermore, we count the number of Wilson loop diagrams in each equivalence class.
+The first of these are done by considering Wilson loop diagrams as matroids.
+The second, by considering polygon partitions of Wilson Loop Diagrams.
 
@@
 \begin{enumerate}
-\item A basis of $W$ is any independent set, $B \subset [n]$ of size $|B| = |\cP|$.
+\item An set $V \subseteq [n]$ is independent if there is no subset that supports fewer propagators than vertices of that subset: \bas \not \exists U \subseteq V \; \textrm{s.t.
+} |\Prop (U)| < |U|\;.
+\eas A basis of $W$ is any independent set, $B \subset [n]$ of size $|B| = |\cP|$.
 \item The rank of a set $|V| \subset [n]$, is bounded above by $\rk(V) \leq \min\{ |V| , |\Prop(V)|\}$.
-If $V$ is an independent set, then $\rk(V) = |V|$\note{The spacing is weird in $\rk$.
-Looking at your definition I think it is on purpose, so I think I'm missing something as to why.
-It looks particularly odd when there is a subscript to the rank eg after Def 2.10}.
+If $V$ is an independent set, then $\rk(V) = |V|$.
 Furthermore, if $v \in [n]$, and $q \in \Prop(v)$, then for any $V \subset [n]$ such that $q \not \in \Prop(V)$, $\rk(V \cup v) = \rk(V) +1$.
@@
     In other words, if $C$ is a circuit of a Wilson loop diagram, then \bas \rk(C) = |C|-1 = |\Prop(C)| \;. \eas
-\item A flat, $F$, of a matroid is a maximally dependent set \note{Maximal for its rank is better than maximally dependent.
-Alternately maybe maximal for dependence would be better, but in that case I would really just be meaning rank again}.
+\item A flat, $F$, of a matroid is a set that is maximal for its rank.
 That is, for all $e \not \in F$ $\rk(F \cup e) = \rk(F) +1$.
 If $W$ is an admissible Wilson loop diagram, any group of propagators defines a flat, $F(P) = V(P^c)^c$, called a propagator flat.
-It consists of all vertices of $W$ that do not support any propagators outside of $P \subset \cP$.
 To see that this is flat, let $v \in V(P^c)$.
@@
 Therefore, by the rank function, $\rk( F(P) \cup v))> \rk(F(P))$.
+Furthermore, in \cite{wilsonloops}, the authors show that if $F$ is a cyclic flat, then there is a $P \subset \cP$ such that $F = F(P)$.
+
 \end{enumerate}
 \end{dfn}
-
-Furthermore, in \cite{wilsonloops}, the authors show that if $F$ is a cyclic flat, then there is a $P \subset \cP$ such that $F = F(P)$.
 
@@
 \begin{cor} \label{classifyflats}
-If $F$ is a flat of a Wilson loop diagram, it can be written as the union of a cyclic flat, and thus a propagator flat, and an independent flat.\note{What would you think of putting ``and thus a propagator flat'' in parentheses or something; otherwise I'm concerned that the nesting structure of this sentence is not sufficiently clear.}
-\end{cor}
-From this we see that any propagator flat can be written as a union of a cyclic propagator flat and an independent flat.
+If $F$ is a flat of a Wilson loop diagram, it can be written as the union of a cyclic propagato flat and an independent flat. \end{cor}
+
+In particular, any propagator flat can be written as a union of a cyclic propagator flat and an independent flat.
+
+Finally, we note the differences between subdiagrams of Wilson loop diagrams, and restrictions or contractions of the associated matroids.
 
@@
 
-In the sequel, I conflate a Wilson loop diagram with the matroid it defines.
-
-\subsection{Exact subdiagrams and matroids}
-
-It has been proved that if two Wilson loop diagrams are equivalent, then the define the same matroid in ``Matroids and Wilson Loop Diagrams''.
-In this section, we prove the converse.
-Therefore, we prove several results about exact subdiagrams.
+A subdiagram is more closely related to a contracted matroid.
+
+\begin{lem} \label{contractsubdiaglem}
+For $W = (\cP, [n])$, consider a subdiagram $(P^c, V(P^c))$.
+The complementary set of vertices is a propagator flat: $F(P) = V(P^c)^c$.
+If this has maximal rank, $\rk F(P) = |P|$, then the subdiagram defines the same matroid as is formed by contracting the original matroid by $F(P)$: \bas M((P^c, V(P^c))) = M(W)/ F(P) \;.
+\eas
+\end{lem}
+
+In the sequel, where it doesn't cause confusion, I conflate a Wilson loop diagram with the matroid it defines.
+
+\subsection{Polygon partitions of Wilson loop diagrams}
+
+In order to study exact Wilson loop diagrams, we further introduce the notion of a polygon partition of $W$.
+
+\begin{dfn}
+  Let $W = (\cP, n)$ be an admissible Wilson loop diagram.  The \emph{polygon partition} associated to $W$, denotes $\tau(W)$ is defined as follows.
+  \begin{itemize}
+  \item The vertices of $\tau(W)$ correspond to the edges of $W$. 
+  \item Labeling the edges of $\tau(W)$ with the edge number gives a cyclic order to the vertices. Connecting consecutive vertices gives a graph theoretic cycle called the polygon of $\tau(W)$.
+  \item Each propagator of $W$ defines a chord edge of $\tau(W)$ for each propagator of $W$.  If $p= (i,j) \in \cP$, it defines a chord connecting the verices $i$ and $j$
+  \end{itemize}
+\end{dfn}
+
+\begin{lem}\label{tausimpleplanarlem}
+If $W = (\cP, n)$ is an admissible Wilson loop diagram, $\tau(W)$ is a simple planar graph with cyclically ordered vertices. It is embedded such that the vertices all like on the infinite face.
+\end{lem}
+
+\begin{proof}
+Since the vertices of $\tau(W)$ are labeled by the edges of $W$, which are cyclically ordered, this gives an ordering to the vertices.
+Since $W$ is admissible, no pairs of propagators cross.
+Thereofore, it is a planar embedding.
+There are no propagators $p = (i, i+1)$.
+Therefore, there is exactly one edge connecting any two adjacent edges of $\tau(W)$.
+Similarly, there are not two propagators such that both $p$ and $q$ start and end at the edges $i$ and $j$.
+Therefore, no other two vertices of $\tau(W)$ can be connected by more than one edge.
+Finally, the embedding of $\tau(W)$ is induced from embedding of the graph $W$.
+ \end{proof}
+
+\hlfix{For an admissible $W$ no propagators cross and so no chord edges of $\tau(W)$ cross.  Thus, in graph theoretic language, we can view $\tau(W)$ as a planar embedding of a
+graph with no cut vertices, where all vertices lie on the infinite face, along with a distinguished start vertex and direction around the infinite face.
+From this viewpoint the polygon of $tau(W)$ is the boundary of the infinite face.}{I've smushed this together a bit in the prev.
+lem.
+Tell me if I've missed anything.
+Its a lemma for emphasis, not difficulty}
+
+***draw some examples***
+
+A planar embedding of a graph is a \emph{triangulation} if all faces, except possibly the infinite, face are triangles.
+
+\begin{dfn}
+  Let $W$ be an admissible Wilson loop diagram and $\tau(W)$ its polygon partition.
+A \emph{triangulated piece} of $\tau(W)$ is a 2-connected subgraph of $\tau(W)$ which is a triangulation.
+We will take the convention that a subgraph consisting of {\color{red}two non-adjascent} vertices joined by an edge  is also a triangulated piece, called a \emph{trivial} triangulated piece.
+\end{dfn}
+
+A decomposition of a polygon partition $\tau(W)$ is a set of 2-connected induced subgraphs of $\tau(W)$ which partition the edges of $\tau(W)$.
+
+\begin{lem} \label{decompositionlem}
+  For $W$ an admissible Wilson loop diagram, the polygon partition $\tau(W)$ has a unique decomposition into maximal triangulated pieces, and boundary edges. 
+\end{lem}
+
+***draw an example***
+
+\begin{proof}
+We begin by giving an algorithm for the decomposition, then prove its uniqueness.
+
+Let $T(W)$ be a the dual graph of $\tau(W)$ with the vertex corresponding the to the infinite face removed.
+In other words, place a vertex on each finite face of $\tau(W)$.
+These vertices are connected if there is a chord edge separating the edges.
+Furthermore, if the face is bounded by an edge of the polygonal cycle of $\tau(W)$, the corresponding vertex gets a leaf edge for each such boundary.
+Since, by Lemma \ref{tausimpleplanarlem}, $\tau(W)$ is a simple planar graph, this \hlfix{$T(W)$ is an uniquely defined tree.}{Why do I know it is a tree?
+}
+
+By construction, each face of $\tau(W)$ is a polygon.
+Therefore, each vertex of $T(W)$ is at least 3 valent (one for each edge of the polygon).
+If split each vertex of $T(W)$ if it is strictly greater than $3$ valent.
+(In other words, we fail to split exactly when the face is a triangle).
+The connected components of $T(W)$ correspond to the decomposition of $\tau(W)$ into maximal triangulated pieces.
+The the vertices of the forest thus obtained have valence 1, corresponding to root or leaf vertices, or 3, corresponding to triangulated faces.
+Subtrees with no trivalent vertices correspond to either edges of the boundary of $\tau(W)$, if they were originally leaves of $T(W)$, or to maximal trivial triangulations.
+\hlfix{Splitting at all the faces that are not triangles ensures maximality of the decomposition.}{more words?}
+
+\hlfix{To see uniqueness, consider the uniqueness of $T(W)$.
+If there were two different decompositions of $\tau(W)$, this would imply that there are two different ways to split a vertex of $T(W)$, which implies the n0n-uniqueness of the valency of the vertices of $T(W)$, which contradicts the uniqueness of $T(W)$.}{Your proof was much more complicated.
+What am I missing?}
+\end{proof}
+
+\subsection{Exact subdiagrams}
+
+It has been proved that if two Wilson loop diagrams are equivalent, then the define the same matroid in \cite{wilsonloops}.
+In this section, we prove that two Wilson loop diagrams are equivalent if and only if they define the same matroid.
+Furthermore, we count the admissible elements of each equivalence class.
+
+We begin by relating triangulations and exact subdiagrams.
+
+\begin{lem}\label{lem triang to exact}
+  Let $W$ be an admissible Wilson loop diagram and $\tau(W)$ its polygon partition.  The triangulated pieces of $\tau(W)$ correspond to the exact subdiagrams of $W$.
+\end{lem}
+
+\begin{proof}
+  Let us first record a few standard facts about polygon triangulations (that is about triangulations with all vertices on the outer face).
+If such a triangulation has $n$ vertices then it has $n$ edges on the polygon (that is on the outer face) and $n-3$ edges which are not.
+No planar graph with the same vertices and the same outer face can have more edges than the triangulation and every such simple graph with $n-3$ edges off the outer face is a triangulation.
+
+  Since $W$ is admissible, by lemma \ref{} $\tau(W)$ is a simple graph. Furthermore, $t$ is not all of $\tau(W)$.
+  Let $t$ be a triangulated piece of the decomposition of $\tau(W)$ given in Lemma \ref{decomplem} and suppose $t$ has $n>2$ vertices.
+We want to count how many edges of $t$ are not on the outer face of $\tau(W)$.
+Consider the intersection of $t$ with the outer face of $\tau(W)$.
+This is a possibly disconnected subgraph of the polygon of $\tau(W)$ with $n$ vertices, call it $S$.
+Let $k$ be the number of connected components of $S$.
+\hlfix{Also $S$ is a spanning subgraph of the outer face of $t$ and $S$ has $n$ edges.}{Not sure what this means.
+There are 4 edges in the picture you sent.}  To join the components $S$ must have $k$ edges not in the outer face of $\tau(W)$.
+Furthermore $t$ has $n-3$ edges not in its outer face and so also not in the outer face of $\tau(W)$.
+Thus there are $n-3+k$ edges of $t$ not in the outer face of $\tau(W)$.
+
+  Each of these $n-3-k$ internal edges correspond to propagators in $W$, call this set $P$.
+Next we count the size of $V(P)$.
+Each of the $n$ vertices in the outer face of $t$ corresponds to an edge of $W$.
+These $n$ edges define $k$ connected compnents of the outer polygon of $W$.
+Thus the set$V(P)$ has $n+k$ vertices.
+In other words, \bas |V(P)| = n+k = |P| -3\;.\eas
+
+If $n=2$, then $t$ has two connected componenents. Therefore, $t$ corresponds to a propagator that connects two non-adjacent edges. Therefore, the trivial triangulation is a trivial exact subdiagram.
+
+  Conversely if we have an exact subdiagram $(P, V(P))$ of $W = (\cP, n)$ supported on $|V(P)| = |P|+3$ vertices.
+Let $|P| = k>1$ and $k+3 = m$.
+Suppose the set $V(P)$ defines $c$ disjoint cyclic intervals of $[n]$.
+Then the corresponding subgraph of $\tau(W)$ has $m-c$ vertices.
+Call it $t$.
+If $t$ were a triangulated component, $t$ would have $k -c$ internal edges.
+
+  The graph $t$ has $k$ edges that come from propagators, and $m - 2c$ edges that come from the boundary polygon of $\tau(W)$.
+Since $t$ has $m-c$ vertices, it has $m-c$ external edges, of which $c$ come from propagators.
+Therefore, of the $k$ edges of $t$ that come from propagators, $k-c$ are internal to the connected component.
+Therefore, this is triangulated.
+
+  If $k=1$, and $(P, V(P))$ is a trivially exact subdiagram. Then $t$ is an edge internal to $\tau(W)$ connecting two boundary edges, which, by definition is a triangulation.
+
+%  The statement of the lemma then follows form the fact that inclusion is preserved under $\tau$ and so maximality also corresponds under $\tau$.
+\end{proof}
+
+Next, we prove a few theorems about matroidal properties of exact subdiagrams.
 
@@
 
-To avoid the issue of exact diagrams being subdiagrams of other exact subdiagrams (for instance, any subdiagram $(q, V_q)$, for $q \in \cP$ is exact), I introduce a definition.
-
-\begin{dfn}
-We say $(P, V(P))$ is a maximal exact subdiagram of $W$ if there is not other exact subdiagram $(Q, V(Q))$ containing it.
-\end{dfn}
-
 Since the matroid defined by the subdiagram $(P , V(P))$ is not the same as the matroid associated to $W_{V(P)}$, one cannot say that the $W_{V(P)}$ is a uniform matroid.
@@
 
-In what follows, maximal exact subdiagrams play a significant role. First, we show that maximal exact subdiagrams of an admissible Wilson loop diagram are disjoint.
-
-\begin{lem}
+To avoid the issue of exact diagrams being subdiagrams of other exact subdiagrams (for instance, any subdiagram $(q, V_q)$, for $q \in \cP$ is exact), I introduce a definition.
+
+\begin{dfn}
+We say $(P, V(P))$ is a maximal exact subdiagram of $W$ if there is not other exact subdiagram $(Q, V(Q))$ containing it.
+\end{dfn}
+
+Therefore, in keeping with Lemma \ref{lem triang to exact}, maximal exact subdiagrams of $W$ correspond to maximal triangular components of $\tau(W)$.
+In what follows, maximal exact subdiagrams/ maximal triangulations play a significant role.
+First, we show that maximal exact subdiagrams of an admissible Wilson loop diagram are disjoint.
+
+\begin{cor}
+For $W = (\cP, n)$ can be uniquely decomposed into maximal exact subdiagrams.
+\end{cor}
+
+\begin{proof}
+This is a corollary to Lemma \ref{decompositionlem}, that gives a unique decomposition of polygon partitions, $\tau(W)$,  into maximal triangulated pieces, and Lemma \ref{lem triang to exact}, which gives a correspondence between triangulated components and exact subdiagrams.
+\end{proof}
+
+Furthermore, we can show that maximal triangulated pieces are disjoint in $\tau(W)$. \note{do we have this already?}
+
+\begin{lem} \label{disjointexactsubdiagslem}
 Let $W = (\cP, n)$ be an admissible Wilson loop diagram, and $(Q, V(Q))$, $(R, V(R))$ two maximal exact subdiagrams. Then $Q\cap R = \emptyset$.
@@
 \end{proof}
+
+Finally, we discuss some flats formed by the complement of the propagators defining an exact subdiagram.
 
@@
 
-While one still cannot equate a subdiagram with a restriction, this lemma allows one to write a maximal exact subdiagram as a contraction.
-First, recall a result from \cite{wilsonloops} about contracted diagrams and matroids.
-
-\begin{lem}
-For $W = (\cP, [n])$, write the contracted diagram $W/P = (P^c, V(P)^c)$. If $\rk F(P) = |P|$, we may identify \bas M(W/P) = M(W)/ F(P) \;. \eas
-\end{lem}
-
-In other words, a maximally exact subdiagram $(P, V(P))$  can be written as a contraction by the complementary propagator flat: \bas (P, V(P)) = W/F(P^c) \;.\eas
+In other words, by Lemma \ref{contractsubdiaglem}a maximally exact subdiagram $(P, V(P))$  can be written as a contraction by the complementary propagator flat: \bas (P, V(P)) = W/F(P^c) \;.\eas
 
@@
 \end{thm}
-\note{I don't understand how this section (and this theorem) relate to the preivous section, which has the same content in its main theorem.}
 
@@
 Reorganize the vertex sets as follows: \ba \cup_{P_i \neq P_i'} V(P_i) = V(\cup_{P_i \neq P'_i} P_i)  \label{vertexsets}\; .\ea Since maximal exact subdiagrams are disjoint, and single propapagators may define maximal subdiagrams, $\cup_{i = 1}^k P_i = \cup_{i = 1}^k P'_i = \cP$.
-Then equation \eqref{vertexsets} becomes \bas \cap_{P_i \neq P_i'} (F(P_i^c))^c = F(\cup_{P_j = P'_j} P_j)^c \;.\eas These flats may, of course, be empty.\todo{Is this paragraph necessary?}
+Then equation \eqref{vertexsets} becomes \bas \cap_{P_i \neq P_i'} (F(P_i^c))^c = F(\cup_{P_j = P'_j} P_j)^c \;.\eas These flats may, of course, be empty.
+
+Thus, we have partitioned the vertices of $W$ and $W'$ into a single set that supports a union of maximal exact subdiagrams whose propagators between $W$ and $W'$, and the complementary propagator flats that support the propagators in common between $W$ and $W'$.
+As mentioned above, the latter may be empty.
 
@@
 In this manner, $W' = W_k$ and $W_i \sim W_{i+1}$, making $W \sim W'$.
-\end{proof}
-
-\subsection{Counting exact subdiagrams}
-
-Since equivalent Wislon loop diagrams are the only ones that define the same matroid as each other, it is useful to enumerate the number of equivalent diagrams any Wilson loop diagram has.
-
-\begin{dfn}
-  Let $W$ be an admissible Wilson loop diagram.  The \emph{polygon partition} associated to $W$, denotes $\tau(W)$ is defined as follows.
-  \begin{itemize}
-  \item The vertices of $\tau(W)$ correspond to the edges of $W$.
-  \item The polygon of $\tau(W)$ is the graph theoretic cycle made of the vertices of $\tau(W)$ and where two vertices are adjacent if the corresponding edges of $W$ meet at a vertex of $W$.
-  \item There is a chord edge of $\tau(W)$ for each propagator of $W$.
-Given a propagator fo $W$, this edge of $\tau(W)$ joins the two vertices of $\tau(W)$ corresponding to the edges of $W$ where the two ends of the propagator lie.
-  \end{itemize}
-\end{dfn}
-
-For an admissible $W$ no propagators cross and so no chord edges of $\tau(W)$ cross.
-Thus, in graph theoretic language, we can view $\tau(W)$ as a planar embedding of a graph with no cut vertices, where all vertices lie on the infinite face, along with a distinguished start vertex and direction around the infinite face.
-From this viewpoint the polygon of $tau(W)$ is the boundary of the infinite face.
-
-***draw some examples***
-
-A planar embedding of a graph is a \emph{triangulation} if all faces, except possibly the infinite, face are triangles.
-
-\begin{dfn}
-  Let $W$ be an admissible Wilson loop diagram and $\tau(W)$ its polygon partition.
-  A \emph{triangulated piece} of $\tau(W)$ is a 2-connected subgraph of $\tau(W)$ which is a triangulation and which is maximal with respect to that property.
-We will take the convention that a subgraph consisting of two vertices joined by an edge which is in no triangle is also a triangulated piece, called a \emph{trivial} triangulated piece.
-\end{dfn}
-
-A decomposition of a polygon partition $\tau(W)$ is a set of 2-connected induced subgraphs of $\tau(W)$ which partition the edges of $\tau(W)$.
-
-\begin{lem}
-  Every polygon partition $\tau(W)$ has a unique decomposition into triangulated pieces.
-\end{lem}
-
-***draw an example***
-
-\begin{proof}
-  First consider the weaker notion of decompositions of $\tau(W)$ into 2-connected pieces which are either triangulations (but not necessarily maximal) or subgraphs consisting of two vertices joined at an edge.
-At least one such decomposition must exist as we can simply take each edge as defining it's own subgraph.
-
-  Now suppose we have two distinct such decompositions.
-Since they are distinct there must be some edge $e$ of $\tau(W)$ for which the subgraph containing this edge are differs between the decompositions.
-Let $T_1$ and $T_2$ be these two subgraphs.
-The graph $T_1\cup T_2$ defined by taking the union of the vertex sets of $T_1$ and $T_2$ along with the union of the edge sets of $T_1$ and $T_2$ is still a subgraph of $\tau(W)$.
-Furthermore, since all vertices of $\tau(W)$ lie on the external face, and $T_1$ and $T_2$ are 2-connected, then $T_1$ and $T_2$ can share at most two vertices and these must be on the external faces of $T_1$ and of $T_2$.
-Therefore $T_1\cup T_2$ is the result of gluing two triangulations along edges on each of their external faces and hence is also a triangulation.
-Combining all subgraphs which share edges we obtain a decomposition containing both original decompositions.
-
-  Therefore the set of such decompositions of $\tau(W)$ is not just a poset under containment but is a finite directed set and thus has a unique maximal element.
-
-Also, the subgraphs making up this maximal element are themselves maximal as if not then taking the union with the decomposition formed from a single triangulation which properly contains one of the triangulations of the maximal element along with the remaining edges as individual subgraphs, would give a decompositions containing the purported maximal one.
-Furthermore, no non-maximal decomposition can be a decomposition into maximal triangulations because since it is properly contained in the maximal element some subgraph of this decomposition must be properly contained in some subgraph of the maximal decomposisiton and hence not be a maximal triangulation.
-
-  Thus the maximal decomposition is the desired unique decomposition into (maximal by definition) triangulated pieces.
-\end{proof}
-
-That previous proof is rather belaboured, so it will probably want to be cut down, but I'm not sure which parts will be obvious to our audience and which will not be.
-
-\begin{lem}\label{lem triang to exact}
-  Let $W$ be an admissible Wilson loop diagram and $\tau(W)$ its polygon partition.  The nontrivial triangulated pieces of $\tau(W)$ correspond to the maximal connected exact subdiagrams of $W$.
-\end{lem}
-
-\begin{proof}
-  Let us first record a few standard facts about polygon triangulations (that is about triangulations with all vertices on the outer face).
-If such a triangulation has $n$ vertices then it has $n$ edges on the polygon (that is on the outer face) and $n-3$ edges which are not.
-No planar graph with the same vertices and the same outer face can have more edges than the triangulation and every such simple graph with $n-3$ edges off the outer face is a triangulation.
-
-  Since $W$ is admissible, $\tau(W)$ has no double edges and so is a simple graph.
-  Let $t$ be a nontrivial triangulated piece of $\tau(W)$ and suppose $t$ has $n$ vertices.
-We want to count how many edges of $t$ are not on the outer face of $\tau(W)$.
-Consider the intersection of $t$ with the outer face of $\tau(W)$.
-This is a subgraph with $n$ vertices of the polygon of $\tau(W)$, call it $S$.
-Let $k$ be the number of connected components of $S$.
-Also $S$ is a spanning subgraph of the outer face of $t$ and $S$ has $n$ edges.
-To join the components $S$ must have $k$ edges not in the outer face of $\tau(W)$.
-Furthermore $t$ has $n-3$ edges not in its outer face and so also not in the outer face of $\tau(W)$.
-Thus there are $n-3+k$ edges of $t$ not in the outer face of $\tau(W)$.
-
-  These edges correspond to propagators in $W$, so the open subdiagram of $W$ corresponding to $\tau(W)$ has $n-3+k$ propagators.
-Next let's count the vertices of this subdiagram.
-Each of the $n$ vertices in the outer face of $t$ corresponds to an edge of the open subdiagram and the edges of this open subdiagram form $k$ connected compnents of the outer polygon.
-Thus the open subdiagram has $n+k$ vertices.
-So we see that the open subdiagram corresponding to $t$ has exactly three more vertices than propagators.
-Propagators can never be supported at higher density than this by admissibility and so the support of the propagators of the subdiagram is all the vertices of the subdiagram and hence the subdiagram is exact.
-We have not used the maximality of the triangulation in the above and so any triangulated subgraph corresponds to an exact subdiagram.
-
-  Conversely if we have an exact subdiagram of $W$ with $n$ edges forming $k$ connected components of the outer polygon then the corresponding subgraph of $\tau(W)$ has $n$ vertices and $n-k+(n-3+k) = 2n-3$ edges, of which $n$ are in the outer face and hence is a triangulation.
-
-  The statement of the lemma then follows form the fact that inclusion is preserved under $\tau$ and so maximality also corresponds under $\tau$.
-\end{proof}
-
-\begin{dfn}
-  Say two admissible Wilson loop diagrams $W_1$ and $W_2$ are \emph{triangulation-equivalent} if there is a bijection $\alpha$ between the set of triangulated pieces in the decomposition of $\tau(W_1)$ and the set of triangulated pieces in the decomposition of $\tau(W_2)$, where $t$ and $\alpha(t)$ have the same vertex set for all triangulated pieces $t$ of $\tau(W_1)$.
-\end{dfn}
-
-***draw an example***
-
-\begin{thm}
-  Two admissible Wilson loop diagrams have the same matroid iff they are triangulation equivalent
-\end{thm}
-
-Again do I want matroid or positroid in this theorem?
-
-\begin{proof}
-  By Lemma~\ref{lem triang to exact} two admissible Wilson loop diagrams are triangulation equivalent iff their decompositions into maximal connected exact subdiagrams have matching supports, that is if they are equivalent.
-  Theorem~\ref{thm orig equiv} then gives the result.
 \end{proof}
@@
 \end{cor}
+
+\begin{comment}
+\subsection{Counting exact subdiagrams}
+
+\begin{dfn}
+  Say two admissible Wilson loop diagrams $W_1$ and $W_2$ are \emph{triangulation-equivalent} if there is a bijection $\alpha$ between the set of triangulated pieces in the decomposition of $\tau(W_1)$ and the set of triangulated pieces in the decomposition of $\tau(W_2)$, where $t$ and $\alpha(t)$ have the same vertex set for all triangulated pieces $t$ of $\tau(W_1)$.
+\end{dfn}
+
+***draw an example***
+
+\begin{thm}
+  Two admissible Wilson loop diagrams have the same matroid iff they are triangulation equivalent
+\end{thm}
+
+Again do I want matroid or positroid in this theorem?
+
+\begin{proof}
+  By Lemma~\ref{lem triang to exact} two admissible Wilson loop diagrams are triangulation equivalent iff their decompositions into maximal connected exact subdiagrams have matching supports, that is if they are equivalent.
+  Theorem~\ref{thm orig equiv} then gives the result.
+\end{proof}
+
+\end{comment}
 

### 2018-05-11 General WLD combinatorics.tex
Incorporated notes from May 10 discussion

@@
 \begin{dfn}\label{WLdfn}
-A Wilson loop diagram is given by the following data: a cyclicly ordered set $V$, and $k$ pairs $\{p_r = (i_r, j_r)\}_{r=1}^k$ ordered such that $i_r +1 < j_r$. \end{dfn}
+A Wilson loop diagram is given by the following data: a cyclicly ordered set $V$, along with a choice of first vertex, and $k$ pairs $\{p_r = (i_r, j_r)\}_{r=1}^k$ ordered such that $i_r +1 < j_r$.
+\end{dfn}
 
 We depict this data as a convex polygon, with vertices labeled by $V$ (preserving the cyclic ordering), and $k$ wavy lines in the interior of the diagrams.
+We depict the choice of first vertex on $V$ by a $\bullet$.
+Note that the polygon gives the verices of $W$ a cyclic ordering, which the choice of first vertex gives it a compatible linear order.
+Both the cyclic and the linear order become the correct perspective at various points in this paper.
 The pair $p_r$ defines a wavy line from the $i_r^{th}$ edge (between $i_r$ and $i_r+1$) and the $j_r^{th}$ edge.
@@
 
-\begin{dfn}\label{equivdfn}
+\begin{dfn}\label{equivdfn} \todo{I feel like I need some sort of uniqueness of partition result to even be able to define this well. Or something. Can we discuss?}
 There is an equivalence relationship on the set of admissible Wilson loops diagrams generated by the following binary relation: $W = (\cP, n) \sim W'= (\cP', n)$ if
@@
 This forces an equivalence between $W_1$ and $W_3$, even though one cannot partition the propagators of each into a an exact subdiagram (that may vary between the diagrams) and a complement that is fixed.
-\end{eg} \note{Did you change $\sim$ to $\equiv$?
-Or was I being flaky?
-If you prefer different notation, lets discuss.}
+\end{eg}
 
@@
   \item The vertices of $\tau(W)$ correspond to the edges of $W$.
-  \item Labeling the edges of $\tau(W)$ with the edge number gives a cyclic order to the vertices. Connecting consecutive vertices gives a graph theoretic cycle called the polygon of $\tau(W)$.
+  \item Labeling the vertices of $\tau(W)$ with the edge number of $W$gives a cyclic order to the vertices.
+Connecting consecutive vertices gives a graph theoretic cycle called the polygon of $\tau(W)$.
   \item Each propagator of $W$ defines a chord edge of $\tau(W)$ for each propagator of $W$.  If $p= (i,j) \in \cP$, it defines a chord connecting the verices $i$ and $j$
@@
 \begin{lem}\label{tausimpleplanarlem}
-If $W = (\cP, n)$ is an admissible Wilson loop diagram, $\tau(W)$ is a simple planar graph with cyclically ordered vertices. It is embedded such that the vertices all like on the infinite face.
+If $W = (\cP, n)$ is an admissible Wilson loop diagram, $\tau(W)$ is a simple planar graph wihose outer face is a cycle.
+It is embedded such that the vertices all like on this infinite face.
+These vertices are cyclically ordered, with a coice of first vertex, giving it an additional compatible linear order.
 \end{lem}
@@
 Since the vertices of $\tau(W)$ are labeled by the edges of $W$, which are cyclically ordered, this gives an ordering to the vertices.
+Furthermore, since the outer polygon of $W$ is a cycle, the outer face of $\tau(W)$ is also a cycle.
 Since $W$ is admissible, no pairs of propagators cross.
@@
 
+\begin{comment}
 \hlfix{For an admissible $W$ no propagators cross and so no chord edges of $\tau(W)$ cross.  Thus, in graph theoretic language, we can view $\tau(W)$ as a planar embedding of a
@@
 Its a lemma for emphasis, not difficulty}
+\end{comment}
 
@@
 A \emph{triangulated piece} of $\tau(W)$ is a 2-connected subgraph of $\tau(W)$ which is a triangulation.
-We will take the convention that a subgraph consisting of {\color{red}two non-adjascent} vertices joined by an edge  is also a triangulated piece, called a \emph{trivial} triangulated piece.
+We will take the convention that a subgraph consisting of a single chord edge is called a \emph{trivial} triangulated piece.
 \end{dfn}
@@
 \begin{lem} \label{decompositionlem}
-  For $W$ an admissible Wilson loop diagram, the polygon partition $\tau(W)$ has a unique decomposition into maximal triangulated pieces, and boundary edges. 
+  For $W$ an admissible Wilson loop diagram, the polygon partition $\tau(W)$ has a unique decomposition into maximal triangulated pieces, and edges in the polygon of $\tau(W)$.
 \end{lem}
@@
 \begin{proof}
-We begin by giving an algorithm for the decomposition, then prove its uniqueness.
-
-Let $T(W)$ be a the dual graph of $\tau(W)$ with the vertex corresponding the to the infinite face removed.
+We begin by giving an algorithm for the decomposition, then prove its uniqueness. Let $W = (\cP, n)$, with $|\cP| = k$.
+
+Let $T(W)$ be a the dual graph of $\tau(W)$ with the vertex corresponding the to the infinite face split.
 In other words, place a vertex on each finite face of $\tau(W)$.
@@
 Furthermore, if the face is bounded by an edge of the polygonal cycle of $\tau(W)$, the corresponding vertex gets a leaf edge for each such boundary.
-Since, by Lemma \ref{tausimpleplanarlem}, $\tau(W)$ is a simple planar graph, this \hlfix{$T(W)$ is an uniquely defined tree.}{Why do I know it is a tree?
-}
+Since, by Lemma \ref{tausimpleplanarlem}, $\tau(W)$ is a simple planar graph, $T(W)$ is an uniquely defined graph.
+
+We claim that $T(W)$ is a tree.
+Since $\tau(W)$ is a planar graph with $k$ chord edges and no internal vertices, there are $k+1$ internal faces of $\tau(W)$.
+Each of these internal faces correspond to a vertex of $T(W)$, and there are $n$ vertices of $T(W)$ from the splitting of the dual graph, we see that $T(W)$ has $n+k+1$ vertices.
+On the other hand, $T(W)$ has $n+k$ edges, corresponding to the $n +k$edts of $\tau(W)$.
+Therefore, $T(W)$is a tree.
 
@@
 (In other words, we fail to split exactly when the face is a triangle).
-The connected components of $T(W)$ correspond to the decomposition of $\tau(W)$ into maximal triangulated pieces.
-The the vertices of the forest thus obtained have valence 1, corresponding to root or leaf vertices, or 3, corresponding to triangulated faces.
-Subtrees with no trivalent vertices correspond to either edges of the boundary of $\tau(W)$, if they were originally leaves of $T(W)$, or to maximal trivial triangulations.
-\hlfix{Splitting at all the faces that are not triangles ensures maximality of the decomposition.}{more words?}
-
-\hlfix{To see uniqueness, consider the uniqueness of $T(W)$.
-If there were two different decompositions of $\tau(W)$, this would imply that there are two different ways to split a vertex of $T(W)$, which implies the n0n-uniqueness of the valency of the vertices of $T(W)$, which contradicts the uniqueness of $T(W)$.}{Your proof was much more complicated.
-What am I missing?}
+The connected components of $T(W)$ correspond to the decomposition of $\tau(W)$ into maximal triangulated pieces and edges orinignaly in the polygon of $\tau(W)$.
+Let $f$ be the forest thus obtained.
+The vertices of $f$ either have valence 1, (if they correspond leaf vertices) or 3,  (if they correspond to triangulated faces).
+Subtrees with no trivalent vertices correspond to either edges in the polygon of $\tau(W)$, if they were originally leaves of $T(W)$, or to maximal trivial triangulations.
+Splitting at all the faces that are not triangles ensures maximality of the decomposition.
+If the splitting were not maximal, then one could add a triangle to a connected component of the splitting, but this would imply that that splitting happened at a valence $3$ vertex.
+
+To see uniqueness, consider a different maximal decomposition of $\tau(W)$.
+This induces a splitting on $T(W)$, where each connected component of the new decomposition corresponds to a subtree.
+Call this forest $f'$.
+Since $f' \neq f$, there are two trees, $t$ and $t'$ in $f$ and $f'$ that are distinct, but share at least one edge of $T(W)$.
+Since $f'$ is also maximal, $t'$ is not a subtree of $t$.
+Therefore, the edges of $t'$ can be found in at least two trees in the forest $f$.
+In particular, there is a vertex $v$ in $t'$ that corresponds to a split vertex of $T(W)$ in the original decomposition.
+This implies that $v$ has valence greater than $3$ in $T(W)$, and thus the corresonding face of $\tau(W)$ is not a triangle.
+In otherwords, the decomposition corresponding to $f'$ is not a triangulation.
+\note{This is a variant of what you wrote in the e-mail.
+Let me know if you like it.}
+\end{proof}
+
+\begin{cor} \label{maxtriangdisjointcor}
+Given a maximal decomposition of $\tau(W)$, the maximal triangulated pieces are edge disjoint.
+\end{cor}
+
+\begin{proof}
+If two maximal triangulated pieces were not disjoint, then one could take the union of the edges involved to get a larger triangulated piece.
+\note{Is it this simple?
+This is a variant of the proof on propagators}
 \end{proof}
@@
 Let $k$ be the number of connected components of $S$.
-\hlfix{Also $S$ is a spanning subgraph of the outer face of $t$ and $S$ has $n$ edges.}{Not sure what this means.
-There are 4 edges in the picture you sent.}  To join the components $S$ must have $k$ edges not in the outer face of $\tau(W)$.
+To join the components $S$ must have $k$ edges not in the outer face of $\tau(W)$.
 Furthermore $t$ has $n-3$ edges not in its outer face and so also not in the outer face of $\tau(W)$.
@@
 
-\begin{cor}
-For $W = (\cP, n)$ can be uniquely decomposed into maximal exact subdiagrams.
+\begin{cor} \label{uniqueproppartitioncor}
+For $W = (\cP, n)$ can be uniquely decomposed into maximal exact subdiagrams. These subdiagrams maximal subdiagrams partition $\cP$.
 \end{cor}
@@
 This is a corollary to Lemma \ref{decompositionlem}, that gives a unique decomposition of polygon partitions, $\tau(W)$,  into maximal triangulated pieces, and Lemma \ref{lem triang to exact}, which gives a correspondence between triangulated components and exact subdiagrams.
-\end{proof}
-
-Furthermore, we can show that maximal triangulated pieces are disjoint in $\tau(W)$. \note{do we have this already?}
-
-\begin{lem} \label{disjointexactsubdiagslem}
-Let $W = (\cP, n)$ be an admissible Wilson loop diagram, and $(Q, V(Q))$, $(R, V(R))$ two maximal exact subdiagrams. Then $Q\cap R = \emptyset$.
-\end{lem}
-
-\begin{proof}
-Consider an exact subset of a maximally exact subdiagram, $T \subset Q$.
-For $p \in Q \setminus T$, $|V(T \cup p)| = |T| +1 +3  = |V(T)| +1$.
-That is, by extending an exact subdiagram to a larger one, one extends the vertex set by exactly on vertex per proppagator.
-Therefore, if $T \neq \emptyset = Q \cap R$, \bas |V(Q \cup R)| = |T| +3 + |Q \setminus T| + |R \setminus T| = |Q \cup R| + 3\;.\eas Therefore, if $(Q, V(Q))$ and $(R, V(R))$ are two exact subdiagrams such that $Q\cap R \neq \emptyset$, then $(Q \cup R, V(Q \cup R))$ is exact.
+Futhermore, corrollary \ref{maxtriangdisjointcor} shows that the maximal triangulations are edge disjoint, and thus the propagators defining maximal exact subsets are also disjoint.
+Combining this with the fact that by construction, the decomposition of $\tau(W)$ accounts for all chord edges, gives the desired unique partition of propagators.
 \end{proof}
@@
 \begin{proof}
-One direction has been proved in previous work, but I give a different proof here to be consistent with the method of this document.
+One direction has been proved in previous work, but we give a different proof here to be consistent with the method of this document.
 
@@
 
-Reorganize the vertex sets as follows: \ba \cup_{P_i \neq P_i'} V(P_i) = V(\cup_{P_i \neq P'_i} P_i)  \label{vertexsets}\; .\ea Since maximal exact subdiagrams are disjoint, and single propapagators may define maximal subdiagrams, $\cup_{i = 1}^k P_i = \cup_{i = 1}^k P'_i = \cP$.
+Reorganize the vertex sets as follows: \ba \cup_{P_i \neq P_i'} V(P_i) = V(\cup_{P_i \neq P'_i} P_i)  \label{vertexsets}\; .\ea Since maximal exact subdiagrams partition $\cP$, by Lemma \ref{uniqueproppartitioncor}, write $cup_{i = 1}^k P_i = \cup_{i = 1}^k P'_i = \cP$.
 Then equation \eqref{vertexsets} becomes \bas \cap_{P_i \neq P_i'} (F(P_i^c))^c = F(\cup_{P_j = P'_j} P_j)^c \;.\eas These flats may, of course, be empty.
@@
 
-It is a classical fact the the number of triangulations of an $n$-gon is the $n-2$ Catalan number, namely $\frac{1}{n-1}\binom{2(n-2)}{n-2}$.  Thus we can count the number of equivalent diagrams.
+Since there is a unique way to decompose $W$ into maximal exact subdiagrams, it is logical to ask how many diagrams there are in an equivalence class.
+It is a classical fact the the number of triangulations of an $n$-gon is the $n-2$ Catalan number, namely $\frac{1}{n-1}\binom{2(n-2)}{n-2}$.
+Thus we can count the number of equivalent diagrams.
 
@@
 \begin{figure}
-  \includegraphics{specialp}
+ % \includegraphics{specialp}
   \caption{The different possibilities for $D$ and $p$.  No other propagators can end in the fat red sections.  Other segments may have additional propagators ending in them.}\label{fig special p}
@@
 \begin{figure}
-  \includegraphics{Le_diagrams}
+%  \includegraphics{Le_diagrams}
   \caption{Le diagrams for $C$ (left) and $D$ (right).}\label{fig Le}
@@
   \begin{figure}
-    \includegraphics{messy}
+ %   \includegraphics{messy}
     \caption{Plusses coming from $I_{n-2}^{C}$ (top left),  $I_{n-1}^{C}$ (top right) and $I_{n}^{C}$ bottom when $n-1, n-2\in I_{n-1}^{C}$.
@@
   \begin{figure}
-    \includegraphics{messyD}
+    % \includegraphics{messyD}
     \caption{Plusses coming from $I_{n-2}^{D}$.}\label{fig messyD}

### 2018-05-14 General WLD combinatorics.tex
Slogging through the no cubic or higher factors.  Not done yet.

@@
 
-Now suppose for a contradiction that $f$ has degree $\geq 3$. \note{This is where I'm working next and maybe the result isn't true.  I will send you an example unless I figure it out myself.}
+A consequence of this claim is that every linear factor of $\Delta_{I_i}$ is a $1\times 1$ minor of $C(W)$, hence is a single variable, and every irreducible quadratic factor of $\Delta_{I_i}$ is a $2\times 2$ minor of $C(W)$, hence is a $2\times 2$ determinant of single variables.
+
+The final thing to prove for this item is that there are no irreducible factors $f$ of degree 3 or more.
+Now suppose for a contradiction that $f$ has degree $\geq 3$.
+Note that by removing the propagators which do not contribute to $f$ and changing $i$ to be the first vertex which contributes to $f$ we obtain a different admissible diagram for which $f=\Delta_{I_i}$ and $i\in I_i$.
+Showing that this different admissible diagram gives a contradiction is sufficient, and so we may assume that $W$ has $\Delta_{I_i}$ irreducible of degree 3 or more and $i\in I_i$.
+
+Let $p$ be the propagator such that $I_i(p) = i$. There are two cases to consider.
+
+\textbf{Case I}: Suppose $p$ is supported on $(i-1, i, m, m+1)$ for some $m >_i i$.
+Then $I_{i+1}(p) = m$ by Lemma~\ref{lem susama}.
+Call the propagators which appear before $p$ is closed the propagators inside $p$.
+\note{It might be nice to have general language for this inside/outside idea.
+What do you think.}  The construction of $I_{i+1}$ begins as for $I_i$ after the first step; they can only differ once $p$ contributes to $I_{i+1}$.
+Thus if a propagator contributes $m$ in $I_i$ then it cannot be a propagator inside $p$ (nor $p$ itself).
+Let $S$ be the set of propagators inside $p$ along with $p$ itself.
+Two things can now happen; if neither $m$ nor $m+1$ appear in $I_i$ then the only vertex in the support of $p$ in $I_i$ is $i$, and so the row of $p$ in the matrix of $\Delta_{I_i}$ has only one nonzero entry; hence $\Delta_{I_i}$ has a linear factor which is a contradiction.
+The other think which can happen is that at least one of $m$ and $m+1$ is in $I_i$.
+However, all the propagators in $S$ are mapped by the bijection of $I_{i}$ to vertices strictly before $m$ so the matrix giving $\Delta_{I_i}$ has the form
+\[
+\begin{bmatrix} A & B \\ 0 & C\end{bmatrix}
+\]
+where $A$ is the matrix for the propagators in $S$ and the vertices in $I_i(S)$ which is square of size $|S|\times |S|$.
+No other propagators can be supported on these vertices since all other propagators are outside of $p$ and $p$ is the first propagator supported at $i$.
+This explains the zero block.
+Therefore $\Delta_{I_i} = \det A \det C$ and both factors are nontrivial since $m$ appears in $I_i$.
+This contradicts the irreducibility of $\Delta_{I_i}$.
+
+\textbf{Case II}:
+
+\note{I am here}
+
+\note{Proving that there are no factors larger than quadratic has been much tougher than I anticipated.  Maybe you have a better idea of how to approach it.}
 

### 2018-05-15 General WLD combinatorics.tex
first version of the proof of no factors of degree 3 or more

@@
     \item Each $\Delta_{I_i}$ splits into linear and quadratic factors.
-All linear factors of  $\Delta_{I_i}$ are single variables and all quadratic factors are $2\times 2$ determinants of single variables.
+All linear factors of  $\Delta_{I_i}$ are single variables and all irreducible quadratic factors are $2\times 2$ determinants of single variables.
     \item Quadratic factors in $r_i$ arise precisely when propagators $p$ and $q$ are supported on a common edge $(a,b)$ and $I_i(p)=a$, $I_i(q)=b$.
@@
 
-Let $p$ be the propagator such that $I_i(p) = i$. There are two cases to consider.
-
-\textbf{Case I}: Suppose $p$ is supported on $(i-1, i, m, m+1)$ for some $m >_i i$.
+Let $p$ be the propagator such that $I_i(p) = i$. There are two cases to consider.  These are illustrated in Figure~\ref{fig no big factors}
+
+\begin{figure}
+  \includegraphics{no_big_factors}
+  \caption{The two cases in the proof that no factors of $\Delta_{I_i}$ have degree 3 or more.}\label{fig no big factors}
+\end{figure}
+
+\textbf{Case I}: Suppose $p$ has one end on the edge $(i-1, i)$.
+Thus $p$ is supported on $(i-1, i, m, m+1)$ for some $m >_i i$.
 Then $I_{i+1}(p) = m$ by Lemma~\ref{lem susama}.
@@
 
-\textbf{Case II}:
-
-\note{I am here}
-
-\note{Proving that there are no factors larger than quadratic has been much tougher than I anticipated.  Maybe you have a better idea of how to approach it.}
+\textbf{Case II}: Suppose $p$ has one end on the edge $(i, i+1)$.
+If no other propagators are supported on $i$ then the column for vertex $i$ has only one nonzero entry in it and so $\Delta_{I_i}$ has a linear factor which is a contradiction.
+Thus we can take $q$ to be the propagator such that $I_i(q)=i+1$ and we know that $q$ has one end on the edge $(i, i+1)$ and is adjacent to $p$ on that edge in the counterclockwise direction.
+Write $(i, i+1, j, j+1)$ for the support of $q$.
+The situation for $q$ is very similar to case I, in particular $I_{i+1}(q) = j$ by Lemma~\ref{lem susama} and so if $j\in I_i$ then the propagator which contributes it is outside of $q$.
+Thus similarly to case I, if we let $S$ be the set of propagators inside $q$ along with $p$ and $q$ themselves then all propagators in $S$ are mapped by $I_i$ to vertices strictly before $j$ and no other propagators cover vertices strictly before $j$.
+Thus the matrix giving $\Delta_{I_i}$ has the form
+\[
+\begin{bmatrix} A & B \\ 0 & C\end{bmatrix}
+\]
+where $A$ is the matrix for the propagators in $S$ and the vertices in $I_i(S)$.
+Again two things can now happen.
+If some vertex $j$ or larger in $>_i$ appears in $I_i$ then $B$ and $C$ have at least one column and so the block form of the matrix gives a nontrivial factorization of $\Delta_{I_i}$ which is a contradiction.
+If no vertex $j$ or larger is in $I_i$ then the matrix giving $\Delta_{I_i}$ is just $A$.
+Looking in more detail into $A$, note that of supports of $p$ and $q$, only $i$ and $i+1$ are in $I_i$ and hence
+\[
+A = \begin{bmatrix} D & 0 \\ E & F\end{bmatrix}
+\]
+where $D$ is the $2\times 2$ matrix indexed by the propagators $p$ and $q$ and the vertices $i$ and $i+1$.
+By assumption $\Delta_{I_i}$ had degree 3 or more and so this matrix decomposition gives that $\Delta_{I_i}$ factors into nontrivial factors contradicting our assumptions.
+
+All cases have now been covered and so $\Delta_{I_i}$ has only irreducible factors of degree $2$ or less.
 

### 2018-05-15 General WLD combinatorics.tex
Fixed a problem and proved the next part of the annoying proof about the properties of alg 4.1

@@
 Now suppose for a contradiction that $f$ has degree $\geq 3$.
-Note that by removing the propagators which do not contribute to $f$ and changing $i$ to be the first vertex which contributes to $f$ we obtain a different admissible diagram for which $f=\Delta_{I_i}$ and $i\in I_i$.
-Showing that this different admissible diagram gives a contradiction is sufficient, and so we may assume that $W$ has $\Delta_{I_i}$ irreducible of degree 3 or more and $i\in I_i$.
+Note that by removing the propagators which come before those contributing to $f$ and changing $i$ to be the first vertex which contributes to $f$ we obtain a different admissible diagram for which $f$ still divides $\Delta_{I_i}$ but also $i\in I_i$ and $i$ contributes to $f$.
+Showing that this different admissible diagram gives a contradiction is sufficient, and so we may assume that $i\in I_i$ and $i$ contributes to $f$.
+Finally, we can suppose that $W$ is minimal in number of propagators with the above occuring.
 
@@
 Let $S$ be the set of propagators inside $p$ along with $p$ itself.
-Two things can now happen; if neither $m$ nor $m+1$ appear in $I_i$ then the only vertex in the support of $p$ in $I_i$ is $i$, and so the row of $p$ in the matrix of $\Delta_{I_i}$ has only one nonzero entry; hence $\Delta_{I_i}$ has a linear factor which is a contradiction.
-The other think which can happen is that at least one of $m$ and $m+1$ is in $I_i$.
+Two things can now happen; if neither $m$ nor $m+1$ appear in $I_i$ then the only vertex in the support of $p$ in $I_i$ is $i$, and so the row of $p$ in the matrix of $\Delta_{I_i}$ has only one nonzero entry; hence $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$ which is a contradiction.
+The other thin which can happen is that at least one of $m$ and $m+1$ is in $I_i$.
 However, all the propagators in $S$ are mapped by the bijection of $I_{i}$ to vertices strictly before $m$ so the matrix giving $\Delta_{I_i}$ has the form
@@
 Therefore $\Delta_{I_i} = \det A \det C$ and both factors are nontrivial since $m$ appears in $I_i$.
-This contradicts the irreducibility of $\Delta_{I_i}$.
+If we remove the propagator outside of $p$ we get a smaller diagram for which $\Delta_{I_i} = \det A$, this contradicts the minimality of our choices unless $\det A$ is quadratic which in turn contradicts that $i$ and $p$ contribute to an irreducible factor $f$ of degree at least 3.
 
@@
 Again two things can now happen.
-If some vertex $j$ or larger in $>_i$ appears in $I_i$ then $B$ and $C$ have at least one column and so the block form of the matrix gives a nontrivial factorization of $\Delta_{I_i}$ which is a contradiction.
-If no vertex $j$ or larger is in $I_i$ then the matrix giving $\Delta_{I_i}$ is just $A$.
+If some vertex $j$ or larger in $>_i$ appears in $I_i$ then $B$ and $C$ have at least one column and so the block form of the matrix gives a nontrivial factorization of $\Delta_{I_i}$.
+Hence, as in case I either this contradicts minimality by removing those propagators not contributing to $A$, or $\det A$ is quadratic which contradicts that $p$ and $i$ contribute to $f$, an irreducible factor of degree at least 3.
+On the other hand, if no vertex $j$ or larger is in $I_i$ then the matrix giving $\Delta_{I_i}$ is just $A$.
 Looking in more detail into $A$, note that of supports of $p$ and $q$, only $i$ and $i+1$ are in $I_i$ and hence
@@
 where $D$ is the $2\times 2$ matrix indexed by the propagators $p$ and $q$ and the vertices $i$ and $i+1$.
-By assumption $\Delta_{I_i}$ had degree 3 or more and so this matrix decomposition gives that $\Delta_{I_i}$ factors into nontrivial factors contradicting our assumptions.
+Thus $p$ and $i$ contribute to a quadratic factor of $\Delta_{I_i}$ contradicting our assumptions.
 
@@
 
-    \item
+    \item Suppose propagators $p$ and $q$ are supported on a common edge $(a,b)$ and $I_i(p)=a$, $I_i(q)=b$.
+For any fixed bijection $\sigma$ of the propagators other than $p$ and $q$ to $I_i -\{a,b\}$ for which each propagator is supported on its image under the bijection, we can extend $\sigma$ to a bijection of all propagators with $I_i$ in two ways, either $p\rightarrow a$ and $q\rightarrow b$ or $p\rightarrow b$ and $q\rightarrow a$.
+The sum of the contributions of all these bijections to $\Delta_{I_i}$ is the product of the minor of $C(W)$ coming from $p, q$ and $a,b$ with the minor coming from the other propagators and $I_i - \{a,b\}$.
+Since there is no cancellation of terms in the expansion of $\Delta_{I_i}$, if any other terms appear then they will cause a factor which is not in the form described in the previous part.
+Therefore no such terms exist and $x_1x_4-x_2x_3$ is a factor of $\Delta_{I_i}$.
+
+Now let $f$ be a quadratic factor of $\Delta_{I_i}$.
+By the previous part we know that $f$ is a $2\times 2$ minor coming from two propagators, call them $p$ and $q$, and two vertices, call them $a <_i b$.
+It remains to show that $a$ and $b$ are adjacent.
+From this we can conclude that $p$ and $q$ each have one end on $(a,b)$, as any other way for both $p$ and $q$ to be supported on two consecutive vertices would contradict noncrossing or the density requirement of admissibility.
+
+As in the proof of the previous part, make a new admissible diagram by removing the propagators which come before $f$ and set $i=a$.
+The cases in the proof of the previous part show how $\Delta_{I_i}$ factors; in particular the vertices covering the second end of $p$ either do not appear in $I_i$ or contribute to a different factor of $\Delta_{I_i}$ than $p$ and $a$ do.
+By assumption $b$ contributes to the same factor as $a$.
+Therefore $(a,b)$ is an edge.
     \item

### 2018-05-15 General WLD combinatorics.tex
working on the next part, left it in the middle because I ran out of time for the moment

@@
   \begin{enumerate}
-    \item Each $\Delta_{I_i}$ is homogeneous.
+    \item Each $\Delta_{I_i}$ is homogeneous as is each $r_i$.
     \item Each $\Delta_{I_i}$ splits into linear and quadratic factors.
@@
 \begin{enumerate}
-    \item The nonzero entries of $C(W)$ are independent indeterminates and so every $i\times i$ minor of $C(W)$ is homogeneous of degree $i$ or is $0$.  Thus each $\Delta_{I_i}$ is homogeneous.
+    \item The nonzero entries of $C(W)$ are independent indeterminates and so every $i\times i$ minor of $C(W)$ is homogeneous of degree $i$ or is $0$.
+Thus each $\Delta_{I_i}$ is homogeneous.
+Furthermore, each row contributes one factor to each term in the expansion of $\Delta_{I_i}$ so the result of setting the variables from a subset of rows to $1$ is still homogeneous.
+Thus each $r_i$ is homogeneous.
     \item Using the expression for the determinant as a sum over permutations we see that $\Delta_{I_i}$ is a sum over bijections between $I_i$ and $\mathcal{P}$.
@@
 Two things can now happen; if neither $m$ nor $m+1$ appear in $I_i$ then the only vertex in the support of $p$ in $I_i$ is $i$, and so the row of $p$ in the matrix of $\Delta_{I_i}$ has only one nonzero entry; hence $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$ which is a contradiction.
-The other thin which can happen is that at least one of $m$ and $m+1$ is in $I_i$.
+The other thing which can happen is that at least one of $m$ and $m+1$ is in $I_i$.
 However, all the propagators in $S$ are mapped by the bijection of $I_{i}$ to vertices strictly before $m$ so the matrix giving $\Delta_{I_i}$ has the form
@@
 Therefore $(a,b)$ is an edge.
-    \item
+    \item Consider $p\in S_i$.
+$\Delta_{I_i}$ is homogeneous linear in the variables of the row corresponding to $p$.
+By the second statement of the proposition, either exactly one variable in the row corresponding to $p$ appears in $\Delta_{I_i}$ and this variable is a factor of $\Delta_{I_i}$, or exactly two variables from the row corresponding to $p$ appear in $\Delta_{I_i}$ and they appear as part of a quadratic factor.
+In the first case, let the variable be $x$, then $x$ is a factor of both $r_i$ and $\Delta_{I_i}$ and is the only variable from this row in either polynomial.
+Now suppose two variables from the row $p$ appear in a quadratic factor.
+By the previous part, there is another propagator $q$ and an edge $(a,b)$ such that the factor involving the variables of $p$ in $\Delta_{I_i}$ is the $2\times 2$ minor coming from $p, q$ and $a, b$, and $I_i(p)=a$, $I_i(q)=b$.
+Let this minor be $x_1x_4-x_2x_3$ with $x_1, x_2$ from $p$ and $x_3,x_4$ from $q$.
+There are two situations which can occur, both illustrated in Figure~\ref{fig quadratic}.
+
+\begin{figure}
+  \includegraphics{quadratic}
+  \caption{The situations giving a quadratic factor with variables appearing in $r_i$.}\label{fig quadratic}
+\end{figure}
+
+By Lemma~\ref{lem susama}, since $I_{i-1}(p)\neq a$, then $I_{i-1} <_{i-1} a$ and no other vertex covered by $p$ lies between them.
+In the case that $b<_i a$ and $q$ is taken before $p$ in $I_i$, this means that $I_{i-1}(p)=b$ and so $I_{i-1}(q)\neq b$.
+Thus $q\in S_i$ and so $x_1x_4-x_2x_3$ is a factor of $r_i$.
+Now suppose $a<_i b$ and $p$ is taken before $q$ in $I_i$.
+If $I_{i-1}(q)=a$ then $a\in S_i$ and so again $x_1x_4-x_2x_3$ is a factor of $r_i$.
+If not, then $I_{i-1}(q) = b$ by Lemma~\ref{lem susama}.
+This implies that some other propagator $s$ is associated to $a$ by $I_{i-1}$.
+If $s$ also has one end on $(a,b)$ then by Lemma~\ref{lem susama}, immediately after $s$ contributes $a$ it must contribute $b$.
+However we know $I_i(s) \neq a$ because $I_i(p)=a$, so $I_i(s)=b$ which is also impossible as $I_i(q)=b$.
+Thus $s$ is supported on $a$ but does not have an edge on $(a,b)$ and so $s$ must have an end on $(a-1, a)$ and so be inside $p$ from the point of view of $i-1$.
+Say $s$ is supported on $(j, j+1, a-1, a)$ and $p$ is supported on $(k, k+1, a, b)$ with $i-1 \leq_{i-1} k+1 \leq_{i-1} j+1$.
+Again by Lemma~\ref{lem susama}, immediately after $s$ contributes $a$ it must contribute $j$ and so $I_i(a)=j$.
+
+Finally, then we claim that $I_i(a)\neq j$.
+If $i-1=k+1$ then $I_{i-1}(p) = i-1$ and so the construction $I_i$ proceeds as for $I_{i-1}$ without $p$ and cannot differ until $p$, thus the contribution of $a$ cannot change between $I_{i-1}$ and $I_i$.
+Now suppose $i-1 \leq_{i-1} k$, then $i \leq_{i} j+1$ \note{I am here, sorry to leave it in the middle but I have things to do with other visitors now}
+
     \item

### 2018-05-15 General WLD combinatorics.tex
finished the proof of that horrible proposition, up to something that should be a lemma and maybe already is

@@
       \item Use Algorithm~\ref{alg:put GN on WLD} to obtain a bijection between the propagators and the $i-1$st Grassmann necklace element, $I_{i-1}$.
-Write $I_{i-1}(p)$ for the vertex associated to propagator $p$ under this bijection.
+(By convention set $I_{-1}=I_n$.)  Write $I_{i-1}(p)$ for the vertex associated to propagator $p$ under this bijection.
       \item Use Algorithm~\ref{alg:put GN on WLD} to obtain a bijection between the propagators and the $i$th Grassmann necklace element, $I_{i}$.
@@
 Say $s$ is supported on $(j, j+1, a-1, a)$ and $p$ is supported on $(k, k+1, a, b)$ with $i-1 \leq_{i-1} k+1 \leq_{i-1} j+1$.
-Again by Lemma~\ref{lem susama}, immediately after $s$ contributes $a$ it must contribute $j$ and so $I_i(a)=j$.
-
-Finally, then we claim that $I_i(a)\neq j$.
-If $i-1=k+1$ then $I_{i-1}(p) = i-1$ and so the construction $I_i$ proceeds as for $I_{i-1}$ without $p$ and cannot differ until $p$, thus the contribution of $a$ cannot change between $I_{i-1}$ and $I_i$.
-Now suppose $i-1 \leq_{i-1} k$, then $i \leq_{i} j+1$ \note{I am here, sorry to leave it in the middle but I have things to do with other visitors now}
-
-    \item
+Again by Lemma~\ref{lem susama}, immediately after $s$ contributes $a$ it must contribute $j$ and so $I_i(s)=j$.
+
+Finally we want to show $I_i(s)=j$ gives a contradiction.
+If $k=j$ then $I_{i}(s)= k$, but $p$ has not yet been taken as $I_i(p)=a$ and $p$ comes before $s$ around $k$, so this is a contradiction.
+If $k+1=j$ then similarly $I_{i}(s)=k+1$ and yet $p$ comes before $s$ around $k$, a contradiction to $I_i(p)=a$.
+Now suppose $k+1 <_{i-1} j$ then we have $i-1 \leq_{i-1} k+1 <_{i-1} I_i(s) = j$ so $i\leq_{i} I_i(s)$ which gives that
+\[
+I_i(s) <_i I_{i-1}(s) \qquad \text{and} \qquad I_i(s) <_{i-1} I_{i-1}(s)
+\]
+\note{Is this known to be impossible by the proof sketch of Lemma~\ref{lem susama} that you emailed or something similar.
+I'm thinking this proof is already too long and the fact that this is impossible would be better as a lemma.}
+
+    \item If $W$ has zero propagators then all $I_i=\emptyset$ and both $R$ and $\prod_{i=1}^n \Delta_{I_i}$ are equal to $1$ so the result holds.  Now assume $W$ has at least one propagator.
+
+First we'll show that every factor of $\prod_{i=1}^n \Delta_{I_i}$ divides $R$.
+Take an irreducible factor $f$ of $\prod_{i=1}^n \Delta_{I_i}$.
+There exists some $i$ such that $f|\Delta_{I_i}$ but $f\not| \Delta_{I_{i-1}}$ as otherwise the variables corresponding to the propagators contributing to $f$ which do not themselves appear in $f$ could never appear, contradicting Lemma~\ref{lem susama}.
+If $f$ is a linear factor, say from associating propagator $p$ to vertex $a$, then $I_{i}(p)=a$ and $I_{i-1}(p)\neq a$ so this factor appears in $r_i$.
+If $f$ is a quadratic factor, say from associating propagators $p$ and $q$ to vertices $a$ and $b$ respectively, then by the first direction of the previous part, $I_{i-1}$ cannot make the same association for both propagators $p$ and $q$, but then by the second direction of the previous part, both $p$ and $q$ must be differently assigned between $I_{i-1}$ and $I_i$.
+Thus $f$ divides $r_i$.
+
+Next we need to show that $R$ is squarefree.
+Suppose $f^2|R$.
+If $f$ is a linear factor, say from associating propagator $p$ to vertex $a$, then twice in the Grassmann necklace $p$ must change from not being associated to vertex $a$ to being associated to vertex $a$.
+This contradicts Lemma~\ref{lem susama}.
+Now suppose $f$ is a quadratic factor say from associating propagators $p$ and $q$ to vertices $a$ and $b$ respectively.
+Since $p$ comes before $q$ on edge $(a,b)$ it is not possible for any $I_i$ to associate $p$ to $b$ and $q$ to $a$.
+Furthermore, we know by the second direction of the previous part that $p$ changes from not being associated to $a$ to being associated to $a$ if and only if $q$ changes from not being associated to $b$ to being associate to $b$.
+Thus $f^2|R$ implies that twice in the Grassmann necklace $p$ must change from not being associated to vertex $a$ to being associated to vertex $a$.
+This is again a contradiction, and so $R$ is squarefree.
+
+Taking everything together we have that $R|\prod_{i=1}^n \Delta_{I_i}$, $R$ contains all factors of $\prod_{i=1}^n \Delta_{I_i}$ and $R$ is squarefree.
+Therefore $R$ is the radical of $\prod_{i=1}^n \Delta_{I_i}$.
   \end{enumerate}

### 2018-05-15 General WLD combinatorics.tex
Some changes made to section 3. proof of cyclic intervals is broken.

--- 2018-05-15 General WLD combinatorics.tex
@@
 \begin{proof}
-If two maximal triangulated pieces were not disjoint, then one could take the union of the edges involved to get a larger triangulated piece.
-\note{Is it this simple?
-This is a variant of the proof on propagators}
+Consider any two disctinct maximal triangulations of $\tau(W)$.
+These two triangulations correspond to subtrees of $T(W)$.
+These subtrees intersect, at most, at a vertex in an interior of $\tau(W)$.
+Since the subtrees corresponding to the maximal subtrees are edge disjoint, and the edges of $T(W)$ correspond to the edges of $\tau(W)$, this forces the maximal triangulations to be edge disjoint as well.
 \end{proof}
@@
 
-Let $\interval{1}{n}$ denote the set of integers $\{1,2, \dots, n\}$, and $\binom{[n]}{k}$ the set of all $k$-subsets of $\interval{1}{n}$.
-For each $j \in \interval{1}{n}$, we can define a total order $\leq_j$ on the interval $\interval{1}{n}$ by
-\[ j <_j j+1 <_j \dots <_j n <_j 1 \dots <_j j-1.\]
+Let $\binom{[n]}{k}$ be the set of all $k$-subsets of the cyclically ordered set $[n]$.  For each $j \in [n]$, we can define a total order $\leq_j$ on the interval $[n]$ by
+\bas j <_j j+1 <_j \dots <_j n <_j 1 \dots <_j j-1\;.\eas
 This in turn induces a total order on $\binom{[n]}{k}$, namely the lexicographic order with respect to $<_j$.
@@
 By [ref], the Grassmann necklaces of type $(k,n)$ are in 1-1 correspondence with the positroid cells in $Gr(k,n)^{tnn}$.
-Further, if $\II$ is the Grassmann necklace associated to a cell $\PP$, then the bases of $\PP$ can be computed using the Gale order $\gale{i}$ for each $i \in \interval{1}{n}$:
-\[\BB(\PP) = \left\{J \in \binom{[n]}{k}\ :\ I_i \gale{i} J \ \forall i \in \interval{1}{n}\right\}.\]
+Further, if $\II$ is the Grassmann necklace associated to a cell $\PP$, then the bases of $\PP$ can be computed using the Gale order $\gale{i}$ for each $i \in [n]$:
+\[\BB(\PP) = \left\{J \in \binom{[n]}{k}\ :\ I_i \gale{i} J \ \forall i \in [n]\right\}.\]
 We now describe an algorithm that, when applied to an admissible Wilson loop diagram, produces exactly the Grassmann necklace of the corresponding positroid.
@@
 \begin{algorithm}\label{alg:put GN on WLD}
-Let $W$ be a Wilson loop diagram with $n$ vertices.
-Note that whenever the algorithm below refers to the ``rightmost'' propagator supported on a vertex $i$, we mean the rightmost from the point of view of standing in the middle of the diagram and looking directly at $i$.
+Let $W = (\cP, n)$ be an admissible Wilson loop diagram. This gives an algorithm for calculating the set $I_a$, for $a \in [n]$.
 
 \begin{enumerate}
-\item Fix a vertex $s \in \interval{1}{n}$, and set $i:=s$.
+\item Fix a vertex $a \in [n]$. Set $i:=a$ and $I_a = \emptyset$.
+\item While $\cP \neq \emptyset$, perform the following steps.
 \begin{enumerate}
-\item \textbf{Step $i$ for vertex $s$}: If there is at least one propagator in the current diagram supported on $i$, add the label $i$ to the edge $(s,s+1)$ and delete the rightmost propagator supported on $i$; otherwise do nothing.
-\item If there are no propagators left in the diagram at this point, go to (2) below.
-\item Otherwise, increment $i$ by 1 and repeat from (a).
+\item \textbf{Step $i$ for vertex $s$}: If $\Prop(i) \neq \emptyset$ in $W$, write $I_a = I_a \cup i$.
+Let $p \in \Prop(p)$ be the clockwise most propagator supported on $i$.
+Write $W = (\cP \setminus p, n)$.
+\item If $Prop(i) = \emptyset$ do nothing.
+\item Increment $i$ by 1 and repeat from (a).
 \end{enumerate}
-\item Replace all propagators in the diagram, and repeat from (1) for a new vertex $s$.  Continue until the algorithm has been applied to all vertices.
 \end{enumerate}
-\end{algorithm}
+\end{algorithm} \note{I don't like how this is written. Any ideas?}
 
 \begin{prop}\label{res:alg k labels}
-If $W$ is an admissible Wilson loop diagram, then Algorithm~\ref{alg:put GN on WLD} puts exactly $k$ distinct labels on each edge.
-\end{prop}
-\begin{proof}
-It is enough to show that the algorithm terminates in at most $n$ steps for each vertex.
+If $W = (\cP, n)$ is an admissible Wilson loop diagram with $|\cP| = k$, then Algorithm~\ref{alg:put GN on WLD} puts exactly $k$ distinct labels on each edge.
+\end{prop} \note{is there a way to do this theorem using the chords and polygons?}
+\begin{proof}
+It is enough to show that the algorithm terminates in at most $n$ steps for each $a \in [n]$.
+In other words, that all $k$ propagators of $W$ are removed by the time the algorithm has cycled through all the vertices, starting at $a$.
 Suppose this doesn't happen, i.e.
-there is a propagator $P$ which survives the first $n$ steps of the algorithm for some starting vertex $s$.
+there is a propagator $p_0 \in \cP$ which survives the first $n$ steps of the algorithm for some starting vertex $s$.
 We will show that this always gives a contradiction in an admissible diagram by constructing an inductive sequence of propagators on strictly decreasing regions of the diagram.
 
-Rotating and cyclically renumbering if necessary, we can assume that $s=1$ and that $P$ is supported on $(a,a+1,b,b+1)$ with $1 \leq a < b$.
-Since $P$ is not removed at step $b+1$, there is another propagator $p_1$ to its right which is also supported on $b+1$: see Figure~\ref{fig:base step of alg induction}.
+Fix an $a \in [n]$. Write $V_{p_0} = (i_{p_0},i_{p_0}+1,j_{p_0},j_{p_0}+1)$ with $a \leq_a i_{p_0} <_a j_{p_0}$.
+
+Since $p$ is not removed by step $j_{p_0}+1$, there are $4$ propagators $q_1, r_1, s_1, t_1$ that are removed at step $i_{p_0},i_{p_0}+1,j_{p_0}$ , or $j_{p_0}+1$ respectively, allowing $p_0$ to remain after $n$ steps.
+Let us consider the propagators $s_1$ and $t_1$, preventing $p_0$ from being eliminated at steps $b_0$ and $b_0+1$.
+Let $s_1 = (i_{s_1}, j_{s_1})$, and $t_1 = (i_{t_1}, j_{t_1})$, where \bas i_{p_0} <_a i_{t_1} <_a i_{s_1} < j_{s_1} \leq_a j_{t_1} = j_{p_0}\;.\eas Note that $j_{r_1}$ must either be $j_{p_0}-1$ or $j_{p_0}$.
+Otherwise, it would not be removed at the $j_{p_0}^{th}$ step.
+Admissibility prevents $i_{p_0} = i_{t_1}$ as this would imply that both $p_0 = (i_{p_0}, j_{p_0})$ and $t_1 = (i_{p_0}, j_{p_0})$.
+
+In order for $t_1$ and $s_1$ to be removed at step $j_{p_0}$ and $j_{p_0}+1$ respectively, they cannot be removed at steps $i_{t_1}$ and $i_{t_1} +1$ or $i_{s_1}$ and $i_{s_1}+1$ respectively.
+Therefore, there needs to be two pairs of propagators, $q_2$, $r_2$ which are removed at step $i_{s_1}$ and $i_{s_1}+1$, and $q_3$, $r_3$ which are removed at step $i_{t_1}$ and $i_{t_1}+1$.
+Note that this implies that $i_{p_0}+2 <_a i_{t_1}$.
+Otherwise, there is not room to place both the propagators $q_3$, $r_3$.
+
+For each $q_m$ and $r_m$ thus identified, there must be other pairs of propagators, $p_{m'}$ and $q_{m'}$ (with $m'> m$) that are removed at steps $i_{q_m}$ and $i_{q_m} +1$ or $i_{r_m}$ and $i_{r_m}+1$.
+Note that under this construction, $i_{r_m} <_a i_{q_m}$.
+
+There are now three cases to be considered. Let $p_k$ indicate a propagator identified at an earlier stage of this construction ($p_k \in \{q_k, r_k, s_k, t_k\}$, or $k=0$).
+
+ \begin{description}
+\item[$i_{r_m} = i_{p_k}+2$] Then there is not room to place both the propagators $q_{m'}$, and $r_{m'}$.
+Thus $r_m$ is removed at the step $i_{r_m} + 1$.
+Therefore, $p_0$ contributes at either $j_{p_0}$ or $j_{p_0}+1$.
+ \item[$i_{r_m} = i_{p_k}+1$] Then there is not room to place either the propagators $q_{m'}$, and $r_{m'}$.
+Thus $r_m$ is removed at the step $i_{r_m}$.
+Therefore, $p_0$ contributes at either $j_{p_0}$ or $j_{p_0}+1$.
+ \item[$i_{r_m} = i_{p_k}$] Since $k < m$, the propagator $p_k$ is not removed at step $i_{p_k}$ or $i_{p_k}+1$.
+Therefore consider the propagators that ensure that $q_m$ is not removed at $i_{q_m}$ or $i_{q_m}+1$.
+By the above argument, there exists an $r_{m'}$ such that $i_{r_m'} = i_{r_m}$.
+This requires the existence of propagators that that $q_m'$ is not removed at $i_{q_m'}$ or $i_{q_m'}+1$.
+This argument continues at infinitum, contradicting both the fact that there are only a finite number of propagators in $W$, and that at most $i_{q_m} - i_{r_m}-1$ propagators can be supported on the cyclic interval $\{i_{r_m}, i_{q_m}+1\}$.
+ \end{description}
+
+\todo{can this be simplified? Does it just need a picture?}
+
+\begin{comment}
+such that $b+1 \in V_{p_1}$, with an endpoint more clockwise on $W$ than the endpoint of $p$ supported by $b+1$: see Figure~\ref{fig:base step of alg induction}.
 
@@
 By induction, we will eventually find a propagator on a region with 3 or fewer vertices, which is inadmissible.
-\end{proof}
-
-To prove that this algorithm gives the Grassmann necklace of the diagram we need two lemmas.
+\end{comment}
+\end{proof}
+
+Infact, we have proved more than the fact that each propagator contributes to the $I_a$ by the $n^{th}$ step.
+We have shown the each vertex $v \in V_p$ is contributed to some $I_{a_{p,v}}$ by $p$ for some $a_{p,v} \in [n]$
+
+\begin{cor}\label{every vertex contributed cor}
+For each propagator $p \in \cP$, and vertex $v \in V_p$, there is an $a_{p,v}$ such that $p$ contributes $v$ to $I_{a_{p,v}}$.
+\end{cor}
+
+\begin{proof}
+Fix $p = (i, j)$. By symmetry, we need only consider the vertices $j$, $j+1$.
+
+Suppose $p$ never contributed $j$ via Algorithm \ref{alg:put GN on WLD}.
+There there would be at least one propagator $s_1 = (i_{s_1}, j_{s_1})$ that contributed $j$ for all vertices $a \in [n]$.
+The vertex $j_{s_1} \in \{j, j-1\}$.
+Then there would have to be propagators $q_2$, $r_2$ that contributed $i_{s_1}$ and $i_{s_2}$ for all $a \in [n]$.
+But this is would create the need for an infinite number of propagators in a finite Wilson Loop diagram, which is impossible.
+
+The same argument holds for $j+1$, except that one has to add the existence of a second propagator $t_1 = (i_{t_1}, j)$ to the construction above.
+
+By cyclic symmetry, this is sufficient to prove that $p$ must also contribute $i$ and $i+1$ at some point.
+
+\end{proof}
+
+For $W = (\cP, n)$, let $W' = (P, V_P)$ be a subdiagram.
+Write $\cI^{W'}$ be the set of $|P|$ tuples defined by \ref{alg:put GN on WLD} on $W'$.
+Furthermore, for any $p = (i, j) \in \cP$, write $\cP_{i,j} =  \{ q = (i_q, j_q)\in \cP | i \leq_i i_q <_i j_q \leq_i j\}$ to be the set of propagators supported on the cyclic interval $[i, j]$.
+Similarly, write $\cP_{j,i} =  \{ q = (i_q, j_q)\in \cP | j \leq_j i_q <_j j_q \leq_j i\}$ to be the set of propagators supported on the cyclic interval $[j,i]$.
+Note that $p = \cP_{i,j} \cap \cP_{j,i}$.
+
+We then have the following corrollary:
+
+\begin{cor} \label{rightmost prop last cor}
+Given any Wilson loop diagram, $W = (\cP, n)$, and $p = (i,j) \in \cP$, consider the subdiagrams $W_L  = (\cP_{i,j}, n)$ and $W_R = (\cP_{j,i}, n)$.
+Then the propagator $p$ contributes last to the entries $I_{i+2}^{W_L}$ and $I_{j+2}^{W_R}$ respectively.
+\end{cor}
+
+\begin{proof}
+Consider $W_L$.
+Since every propagator in a Wilson loop diagram must contribute to $I_{i+2}^{W_L}$, it remains to check that no propagator can contribute after $p$.
+This could only happen if there were a different propagator, $q$ with an endpoint on edge $i$.
+If $q = (i , i+2)$, then it would be the first propagators to be removed, with contribution $i+2$.
+If it $q = (i, l)$, with $l > i+2$, then it would contribute either $l$ or $l+1$.
+Otherwise, one would need the existence of an infinite set of other propagators, as above.
+
+A similar argument works for $W_R$. 
+\end{proof}
+
+\begin{lem} \label{vertex cyclic int lem}
+For every $v \in V_p$, there is a cyclic interval such that $p$ contributes $v$ to all $I_{a}$ for in said interval.
+\end{lem}
+
+\begin{proof}
+
+Fix $p \in \cP$, with $p = (i,j)$.
+Consider two subsets of propagators in $\cP$, $Q = \{q_m\}$, $R = \{r_n\}$.
+Let $Q \subseteq \cP_{i,j}$ be the set of propagators with one end point either on the edge $j-1$ or $j$.
+Label the other endpoint of $q_m$ as the edge $k_m$, with $i \leq_i k_1 <_i k_2 <_i \ldots \leq_i j$.
+In other words, they are ordered from closest to furthest away from $p$.
+
+Similarly, define $R \subset \cP_{j,i}$ be the set of propagators with one end point either on the edge $i-1$ or $i$.
+I label the other endpoint of $r_n$ as the edge $l_n$, with $j \leq_j l_1 <_j l_2 <_j \ldots \leq_j i$.
+In other words, they are ordered from closest to furthest away from $p$.
+
+\todo{Insert picture here}
+
+For any $m >|Q|$ (resp. $m > |R|$), write $k_m= j$ (resp. $l_n = i$).
+
+We make the following four claims:
+
+\begin{enumerate}
+\item The propagator $p$ contributes $i$ for all $I_a$ for $a \in [a_{p,i} = k_2+2, b_{p,i} = l_1+1]$ 
+\item The propagator $p$ contributes $i+1$ for all $I_a$ for $a \in [b_{p,i} +1, a_{p, j} -1]$. 
+\item The propagator $p$ contributes $j$ for all $I_a$ for $a \in [a_{p,j} = l_2+2, b_{p,j} = k_1+1 ]$
+\item The propagator $p$ contributes $j+1$ for all $I_a$ for $a \in [k_1+2, k_2+1 ]$
+\end{enumerate}
+
+This proof follows from the argument in Corollary \ref{rightmost prop last cor}, and Corrollary \ref{every vertex contributed cor} that show that $p$ contributes last to $I_{i+2}^{W_L}$.
+In particular, $p$ contributes after all the propagators in $Q$ in $I_{i+2}$.
+Furthermore, it contributes either $j$ or $j+1$ to this entry.
+If $q_1 \neq (k_1 = i, j-1)$, then $p$ contributes $j$.
+This is because $i+2 \leq_i k_m+1$ for all $m > 0$, which forces the propagators $q_m$ to contribute at the $k_m$ or $k_m+1$ vertex.
+
+\note{there seems to be a problem with the proof as written, namely, it isn't consistent with itself if you change from $p$ to $q_1$.}
+
+\end{proof}
 
@@
     \item Each $\Delta_{I_i}$ splits into linear and quadratic factors.
-All linear factors of  $\Delta_{I_i}$ are single variables and all irreducible quadratic factors are $2\times 2$ determinants of single variables.
+All linear factors of  $\Delta_{I_i}$ are single variables and all quadratic factors are $2\times 2$ determinants of single variables.
     \item Quadratic factors in $r_i$ arise precisely when propagators $p$ and $q$ are supported on a common edge $(a,b)$ and $I_i(p)=a$, $I_i(q)=b$.
@@
 
-A consequence of this claim is that every linear factor of $\Delta_{I_i}$ is a $1\times 1$ minor of $C(W)$, hence is a single variable, and every irreducible quadratic factor of $\Delta_{I_i}$ is a $2\times 2$ minor of $C(W)$, hence is a $2\times 2$ determinant of single variables.
-
-The final thing to prove for this item is that there are no irreducible factors $f$ of degree 3 or more.
-Now suppose for a contradiction that $f$ has degree $\geq 3$.
-Note that by removing the propagators which come before those contributing to $f$ and changing $i$ to be the first vertex which contributes to $f$ we obtain a different admissible diagram for which $f$ still divides $\Delta_{I_i}$ but also $i\in I_i$ and $i$ contributes to $f$.
-Showing that this different admissible diagram gives a contradiction is sufficient, and so we may assume that $i\in I_i$ and $i$ contributes to $f$.
-Finally, we can suppose that $W$ is minimal in number of propagators with the above occuring.
-
-Let $p$ be the propagator such that $I_i(p) = i$. There are two cases to consider.  These are illustrated in Figure~\ref{fig no big factors}
-
-\begin{figure}
-  \includegraphics{no_big_factors}
-  \caption{The two cases in the proof that no factors of $\Delta_{I_i}$ have degree 3 or more.}\label{fig no big factors}
-\end{figure}
-
-\textbf{Case I}: Suppose $p$ has one end on the edge $(i-1, i)$.
-Thus $p$ is supported on $(i-1, i, m, m+1)$ for some $m >_i i$.
-Then $I_{i+1}(p) = m$ by Lemma~\ref{lem susama}.
-Call the propagators which appear before $p$ is closed the propagators inside $p$.
-\note{It might be nice to have general language for this inside/outside idea.
-What do you think.}  The construction of $I_{i+1}$ begins as for $I_i$ after the first step; they can only differ once $p$ contributes to $I_{i+1}$.
-Thus if a propagator contributes $m$ in $I_i$ then it cannot be a propagator inside $p$ (nor $p$ itself).
-Let $S$ be the set of propagators inside $p$ along with $p$ itself.
-Two things can now happen; if neither $m$ nor $m+1$ appear in $I_i$ then the only vertex in the support of $p$ in $I_i$ is $i$, and so the row of $p$ in the matrix of $\Delta_{I_i}$ has only one nonzero entry; hence $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$ which is a contradiction.
-The other thin which can happen is that at least one of $m$ and $m+1$ is in $I_i$.
-However, all the propagators in $S$ are mapped by the bijection of $I_{i}$ to vertices strictly before $m$ so the matrix giving $\Delta_{I_i}$ has the form
-\[
-\begin{bmatrix} A & B \\ 0 & C\end{bmatrix}
-\]
-where $A$ is the matrix for the propagators in $S$ and the vertices in $I_i(S)$ which is square of size $|S|\times |S|$.
-No other propagators can be supported on these vertices since all other propagators are outside of $p$ and $p$ is the first propagator supported at $i$.
-This explains the zero block.
-Therefore $\Delta_{I_i} = \det A \det C$ and both factors are nontrivial since $m$ appears in $I_i$.
-If we remove the propagator outside of $p$ we get a smaller diagram for which $\Delta_{I_i} = \det A$, this contradicts the minimality of our choices unless $\det A$ is quadratic which in turn contradicts that $i$ and $p$ contribute to an irreducible factor $f$ of degree at least 3.
-
-\textbf{Case II}: Suppose $p$ has one end on the edge $(i, i+1)$.
-If no other propagators are supported on $i$ then the column for vertex $i$ has only one nonzero entry in it and so $\Delta_{I_i}$ has a linear factor which is a contradiction.
-Thus we can take $q$ to be the propagator such that $I_i(q)=i+1$ and we know that $q$ has one end on the edge $(i, i+1)$ and is adjacent to $p$ on that edge in the counterclockwise direction.
-Write $(i, i+1, j, j+1)$ for the support of $q$.
-The situation for $q$ is very similar to case I, in particular $I_{i+1}(q) = j$ by Lemma~\ref{lem susama} and so if $j\in I_i$ then the propagator which contributes it is outside of $q$.
-Thus similarly to case I, if we let $S$ be the set of propagators inside $q$ along with $p$ and $q$ themselves then all propagators in $S$ are mapped by $I_i$ to vertices strictly before $j$ and no other propagators cover vertices strictly before $j$.
-Thus the matrix giving $\Delta_{I_i}$ has the form
-\[
-\begin{bmatrix} A & B \\ 0 & C\end{bmatrix}
-\]
-where $A$ is the matrix for the propagators in $S$ and the vertices in $I_i(S)$.
-Again two things can now happen.
-If some vertex $j$ or larger in $>_i$ appears in $I_i$ then $B$ and $C$ have at least one column and so the block form of the matrix gives a nontrivial factorization of $\Delta_{I_i}$.
-Hence, as in case I either this contradicts minimality by removing those propagators not contributing to $A$, or $\det A$ is quadratic which contradicts that $p$ and $i$ contribute to $f$, an irreducible factor of degree at least 3.
-On the other hand, if no vertex $j$ or larger is in $I_i$ then the matrix giving $\Delta_{I_i}$ is just $A$.
-Looking in more detail into $A$, note that of supports of $p$ and $q$, only $i$ and $i+1$ are in $I_i$ and hence
-\[
-A = \begin{bmatrix} D & 0 \\ E & F\end{bmatrix}
-\]
-where $D$ is the $2\times 2$ matrix indexed by the propagators $p$ and $q$ and the vertices $i$ and $i+1$.
-Thus $p$ and $i$ contribute to a quadratic factor of $\Delta_{I_i}$ contradicting our assumptions.
-
-All cases have now been covered and so $\Delta_{I_i}$ has only irreducible factors of degree $2$ or less.
-
-    \item Suppose propagators $p$ and $q$ are supported on a common edge $(a,b)$ and $I_i(p)=a$, $I_i(q)=b$.
-For any fixed bijection $\sigma$ of the propagators other than $p$ and $q$ to $I_i -\{a,b\}$ for which each propagator is supported on its image under the bijection, we can extend $\sigma$ to a bijection of all propagators with $I_i$ in two ways, either $p\rightarrow a$ and $q\rightarrow b$ or $p\rightarrow b$ and $q\rightarrow a$.
-The sum of the contributions of all these bijections to $\Delta_{I_i}$ is the product of the minor of $C(W)$ coming from $p, q$ and $a,b$ with the minor coming from the other propagators and $I_i - \{a,b\}$.
-Since there is no cancellation of terms in the expansion of $\Delta_{I_i}$, if any other terms appear then they will cause a factor which is not in the form described in the previous part.
-Therefore no such terms exist and $x_1x_4-x_2x_3$ is a factor of $\Delta_{I_i}$.
-
-Now let $f$ be a quadratic factor of $\Delta_{I_i}$.
-By the previous part we know that $f$ is a $2\times 2$ minor coming from two propagators, call them $p$ and $q$, and two vertices, call them $a <_i b$.
-It remains to show that $a$ and $b$ are adjacent.
-From this we can conclude that $p$ and $q$ each have one end on $(a,b)$, as any other way for both $p$ and $q$ to be supported on two consecutive vertices would contradict noncrossing or the density requirement of admissibility.
-
-As in the proof of the previous part, make a new admissible diagram by removing the propagators which come before $f$ and set $i=a$.
-The cases in the proof of the previous part show how $\Delta_{I_i}$ factors; in particular the vertices covering the second end of $p$ either do not appear in $I_i$ or contribute to a different factor of $\Delta_{I_i}$ than $p$ and $a$ do.
-By assumption $b$ contributes to the same factor as $a$.
-Therefore $(a,b)$ is an edge.
+Now suppose for a contradiction that $f$ has degree $\geq 3$. \note{This is where I'm working next and maybe the result isn't true.  I will send you an example unless I figure it out myself.}
+
+    \item
     \item

### 2018-05-17 General WLD combinatorics.tex
C(W) and R(W) dfns added in

@@
 
-The diagrams $W_1 \sim W_2$ because $(\{(5,8), (5,7), \{5,6,7,8,1\})$ and $(\{(5,8), (7,8), \{5,6,7,8,1\})$ are the corresponding differing subdiagrams.
+The diagrams $W_1 \sim W_2$ because $(\{(5,8), (5,7)\}, \{5,6,7,8,1\})$ and $(\{(5,8), (7,8)\}, \{5,6,7,8,1\})$ are the corresponding differing subdiagrams.
 Furthermore, there is the equivalence $W_2 \sim W_3$ due to the exact subdiagrams $(\{(1,4), (3,4)\}, \{1,2,3,4,5\})$ and $(\{(1,4), (1,3)\}, \{1,2,3,4,5\})$.
@@
 \end{eg}
+
+Each Wilson loop diagram, $W = (\cP, n)$ with $|\cP| = k$ is associated to a $k \times n$ matrix with non-zero real variable entries, called $C(W)$:
+
+\ba C(W)_{p,q} = \begin{cases} c_{p,q} & \textrm{ if } q \in V(p) \\
+0  & \textrm{ if } q \not \in V(p)  \end{cases}
+\;. \label{C(W) dfn}\ea
+
+\begin{eg}
+For example, ordering the propagators of $W_1$ above as follows: \bas (1,4), \, (2,4), \, (5,7), \, (5,8) \eas we may write 
+\bas C(W_1) = \left(
+\begin{array}{cccccccc}
+c_{1,1} & c_{1,2} & 0 & c_{1,4} & c_{1,5} & 0 & 0 & 0 \\
+0 & c_{2,2} & c_{2,3} & c_{2,4} & c_{2,5} & 0 & 0 & 0 \\
+0 & 0 & 0 & 0 & c_{3,5} & c_{3,6} & c_{3,7} & c_{3,8} \\
+c_{4,1} & 0 & 0 & 0 & c_{4,5} & c_{4,6} & 0 & c_{4,8}  \\
+\end{array}
+\right) \;.\eas
+
+\end{eg}
+
+These $C(W)$ parametrize a subspace of $\Gr(k, n)$ as shown in \cite{wilsonloops}, call it $\Sigma(W)$.
+The Wilson loop diagrams also define a volume form on $\Sigma(W)$: \bas \Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V_{p_r}} \textrm{d}c_{p_r}}{R(W)} \;.
+\eas The denominator $R(W)$ is a polynomial defined by $2 \times 2$ and $1 times 1$ minors of $C(W)$ as defined below.
+
+\begin{dfn}
+For $W = (\cP, n)$, $R(W) = \prod_{e=1}^n R_e$, with $R_e$ defined by the propagators ending on it.
+For any edge $e$ of $W$, order the propagators incident on $e$ as $\{p_1 \ldots p_r\}$, ordered such that $p_1$ is closest to the vertex $e$, $p_r$ closest to $e+1$, and $p_i$ is closer to $e$ than $p_{i+1}$.
+Then \bas R_e =  c_{p_1,e+1} \prod_{j= 1}{s-1} \left((c_{p_j,e} c_{p_{j+1},e+1} - c_{p_{j+1},e} c_{p_{j},e+1} ) \right) c_{p_s,e}\;.\eas Note that in this notation, if $s = 1$, $R_e = c_{p,e} c_{p,e+1}$.
+\end{dfn}
 
@@
 
+Note that one may substitute values into $C(W)$ to realize the matroid assoicated to $W$ in this manner.
+
 It is worth noting that it is not necessary to list all the flats in a matroid to defined it completely, only the cyclic flats, and those that are independent sets.
@@
 \begin{cor} \label{classifyflats}
-If $F$ is a flat of a Wilson loop diagram, it can be written as the union of a cyclic propagato flat and an independent flat. \end{cor}
+If $F$ is a flat of a Wilson loop diagram, it can be written as the union of a cyclic propagator flat and an independent flat. \end{cor}
 
@@
 
-Finally, we note the differences between subdiagrams of Wilson loop diagrams, and restrictions or contractions of the associated matroids.
+Finally, we note the differences between subdiagrams of Wilson loop diagrams, and restrictions or cotractions of the associated matroids.
 
@@
 \begin{figure}
- % \includegraphics{specialp}
+ \includegraphics{specialp}
   \caption{The different possibilities for $D$ and $p$.  No other propagators can end in the fat red sections.  Other segments may have additional propagators ending in them.}\label{fig special p}
@@
 \begin{figure}
-%  \includegraphics{Le_diagrams}
+  \includegraphics{Le_diagrams}
   \caption{Le diagrams for $C$ (left) and $D$ (right).}\label{fig Le}
@@
   \begin{figure}
- %   \includegraphics{messy}
+    \includegraphics{messy}
     \caption{Plusses coming from $I_{n-2}^{C}$ (top left),  $I_{n-1}^{C}$ (top right) and $I_{n}^{C}$ bottom when $n-1, n-2\in I_{n-1}^{C}$.
@@
   \begin{figure}
-    % \includegraphics{messyD}
+     \includegraphics{messyD}
     \caption{Plusses coming from $I_{n-2}^{D}$.}\label{fig messyD}

### 2018-06-12 General WLD combinatorics.tex
cyclic interval proof implemented, hopefully correctly this time.

@@
 \newcommand{\D}{\partial}
-\newcommand{\rk}{\textrm{rk}}
+\newcommand{\rk}{\textrm{rk }}
 \newcommand{\spn}{\textrm{span }}
@@
 %*****************
+
+\title{Put Title here}
+%\author{}
+%\date{}
 
@@
 \begin{enumerate}
-\item \textbf{Step $i$ for vertex $s$}: If $\Prop(i) \neq \emptyset$ in $W$, write $I_a = I_a \cup i$.
+\item \textbf{Step $i$ for vertex $a$}: If $\Prop(i) \neq \emptyset$ in $W$, write $I_a = I_a \cup i$.
 Let $p \in \Prop(p)$ be the clockwise most propagator supported on $i$.
@@
 
+If the propagator $p$ is removed at vertex $i$ according to the algorithm for $I_a$, we say that $p$ \emph{contributes} $i$ to $I_a$.
+
+Next we prove that this algorithm actually gives a Grassmann Necklace as claimed. We begin with some useful definitions and lemmas
+
+\begin{dfn}
+Let $W = (\cP,n)$ be an admissible diagram and $a \in[n]$ a vertex.
+For $p= (i,j) \in \cP$ an a propagator of $W$  and $v \in \{i, j\}$ (or $w \in \{i+1, j+1\}$)a vertex of $W$, let $P_{v}$ (or $P_w$) to be a \emph{protecting set of $p$ at $v$ (or $w$) at $a$} be a set of up to $3$ propagators defined as follows: \begin{enumerate}
+\item Work under the linear order on $[n]$, $<_{v+1}$ or $<_w$, every propagator is now written as $p = (i_p, j_p)$ such that $i_p <_{v+1} j_p$. 
+\item There is a propagator $s_1 \in P_v$ and $s_4 \in P_w$ defined such that $s_4 = (i_{s_4}, v)$ and $s_1 = (i_{s_1}, v)$. One may also have $s_1 = (i_{s_1}, v-1)$. Furthermore, $s_m \in [i_p, v]$.
+\item For the given $a$, either $a-3 <_{v+1} i_{s_1}$ or there exist $2$ propagators $s_2$ and $s_3 \in P_v$ such that $s_3 = (i_{s_3}, i_{s_1})$ and $s_2 = (i_{s_2}, i_{s_1})$.
+One may also have $s_2 = (i_{s_2}, i_{s_1}-1)$.
+Furthermore, $a-3 <_{v+1} s_m$.
+Similarly, for the given $a$, either $a-3 <_{v+1} i_{s_4}$ or there exist $2$ propagators $s_5$ and $s_6 \in P_w$ such that $s_5 = (i_{s_5}, i_{s_4})$ and $s_6 = (i_{s_6}, i_{s_4})$.
+One may also have $s_6 = (i_{s_6}, i_{s_4}-1)$.
+Furthermore, $a-3 <_w s_m$.
+\end{enumerate}
+\end{dfn}
+
+\begin{comment}
+\begin{dfn}
+Let $W = (\cP,n)$ be an admissible diagram and $a \in[n]$ a vertex.
+For $p= (i,j) \in \cP$ an a propagator of $W$  and $v \in \{i, j\}$ (or $w \in \{i+1, j+1\}$) an edge of $W$, let $P_{v}$ (or $P_w$) to be a \emph{protecting set of $p$ at $v$ (or $w$) at $a$} defined as follows: \begin{enumerate}
+\item Work under the linear order on $[n]$, $<_{v+1}$, every propagator is now written as $p = (i_p, j_p)$ such that $i_p <_{v+1} j_p$. 
+\item The sets $P_v$ and $P_w$ are disjoint. 
+\item There is an $r \in P_{v}$ such that $j_r \in \{v, v-1\}$ and $ i_r \in [i_p, j_p]$.
+If $j_r = v-1$, then $r$ is the clockwise most propagator on the edge $v$.
+Similarly, there is a $r \in P_{w}$ such that $j_r =v$ and $ i_r \in [i_p, j_p]$.
+\item For every $q = (i_q, j_q) \in P_{v}$, or $P_w$, if there are at least two propatagors $s$ and $t$ $\in \cP$ satisfying $s = (i_s, i_q)$ or $s = (i_s, i_q-1 )$ (in which case $s$ is the clockwise most propagator on the edge $i_q$) and $t = (i_t, i_t)$ then all such $s$ and $t$ are also in $P_v$ or $P_w$.
+These are called the daughter propagators of $q$.
+If two such propagators don't exist, then $q$ is called a terminal propagator.
+\item For the $a$ given above, there is a propagator $q$ with a set of daughters $\{s_m\}$ satisfying $a-3 <_{v+1} i_{s_m}$.
+\end{enumerate} 
+\end{dfn}
+\end{comment}
+
+\begin{lem}\label{protecting lem}
+Let $W = (\cP, n)$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$, and $a \in [n]$ be a vertex.
+If there exists a $P_v$, for $v \in \{i,j\}$, then $p$ does not contribute $v$ to $I_a$.
+If there are two sets $P_v$ and $P_w$, for $w \in \{i+1, j+1\}$, then $p$ does not contribute $w$ to $I_a$.
+\end{lem}
+
+\begin{proof}
+We consider first the case of $p$ not contributing $v$ to $I_a$.
+
+The set $P_v$ is constructed such that, $s_1$ if it exists at step $v$ of Algorithm \ref{alg:put GN on WLD}, prevents $p$ from contributing $v$ to $I_a$.
+By the positioning of $a$, either the algorithm does not encounter the propagators $s_1$ before vertex $v$ or $v-1$, or it encounters it at $i_{s_1}$.
+In this case, the existence of $s_2$ and $s_3$ prevent $s_1$ from contributing at vertices $i_{s_1}$ or $i_{s_1}+1$.
+Therefore, $s_1$ remains in the diagram at step $v$.
+
+If both $P_v$ and $P_w$ exists, then if $s_1$ and $s_3$ exist at step $v$ of Algorithm \ref{alg:put GN on WLD}, prevents $p$ from contributing $v$ and $w$ to $I_a$.
+By the positioning of $a$, either the algorithm does not encounter the propagators $s_1$ and $s_4$ before vertex $v$ or $v-1$, or it encounters only $s_1$ before $v$ or $v-1$.
+By the above argument, $s_1$ remains in the diagram at step $v$.
+Finally, the algorithm may encounter $s_4$ at $i_{s_4}$.
+In this case, the existence of $s_5$ and $s_6$ prevent $s_4$ from contributing at vertices $i_{s_4}$ or $i_{s_4}+1$.
+Therefore, $s_4$ remains in the diagram at step $v$.
+Thereofre, in this case, $p$ cannot contribute either $v$ or $v+1$ to $I_a$.
+\end{proof}
+
+There is an easy corrollary to this, describing when propagators cannot contribute certain vertices to elements of the Grassman necklace.
+
+\begin{cor} \label{protecting cor}
+Let $W = (\cP, n)$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$.
+Picking a $v \in \{i, j\}$ write $p = (i_p, j_p)$ with $i_p <_{v+1} j_p$.
+If $a \in [j_p+1, i_p+1]$ then no protecting set $P_v$ or $P_w$ can protect $p$ at $v$ or $v+1$ from $a$.
+\end{cor}
+
+\begin{proof}
+Since $W$ is admissible, it cannot have crossing propagators. Therefore niether $P_v$ cannot have the requisite propagator $s$ with $a-3 <_{v+1} i_s$.
+\end{proof}
+
+\begin{comment}
+\begin{lem}\label{protecting lem}
+Let $W = (\cP, n)$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$.
+Then $p$ does not contribute $i$ or $j$ to $I_a$ if there is a subtree protecting $i$ or $j$ from $a$ in $\tau(W)$.
+Furthermore, $p$ does not contribute $i+1$ or $j+1$ if there are two protecting subtrees, at least one of which has a leaf vertex at $v$.
+\end{lem}
+
+\begin{proof}
+It is sufficient to prove this for $i$ and $i+1$. The other two can be proved by switching the roles of $i$ and $j$. We show this by contradiction.
+
+Assume that $p$ does not contribute $i$ to $I_a$.
+Furthermore, that there is a binary tree $T$ protecting $p$ at $i$ from $a$.
+Then, there is some propagator $q= (i_q, j_q) \in \cP$ corresponding to a leaf of $T$ such that $i_q \in \{i, i-1\}$ and $j +1 \leq_j j_q \leq_j i$.
+Further, there are two propagators, $s_1 = (i_{s_1}, j_{s_1})$ and $t_1 = (i_{t_1}, j_{t_1})$ that contribute $i_q$ and $i_q +1$ respectively to $I_v$.
+Namely, we write \bas j \leq_j i_{t_1} <_j i_{s_1} <_j j_{s_1} \leq_j j_{t_1} = i_q\;,\eas with $j_{s_1} \in \{i_q, i_q-1\}$.
+
+In order for $i_{s_1}$ and $i_{t_1}$ to respectively contribute $i_q$ and $i_q +1$, there must be $4$ other propagators, $i_{s_2}$, $i_{t_2}$, $i_{s_3}$, and $i_{t_3}$ that contribute $i_{s_1}$, $i_{s_1}+1$, $i_{t_1}$ and $i_{t_1}+1$ respectively.
+
+For each $s_m$ and $t_m$ thus identified, t here must be other pairs of propagators, $s_{m'}$ and $s_{m'}$ (with $m'> m$) that are removed at steps $i_{s_m}$ and $i_{s_m} +1$ or $i_{t_m}$ and $i_{t_m}+1$.
+Note that under this construction, $i_{t_m} <_j i_{s_m}$.
+By construction, each of these propagators must have endpoints in $[a,i] \cap [j,i]$.
+
+There are now three cases to be considered.
+Let $p_k$ indicate a propagator identified at an earlier stage of this construction (that is, $ m\geq k > 0$ and $p_k \in \{s_k, t_k\}$, or $p_k$ is the first propagator of $T$ lying counterclockwise from $a$.).
+
+ \begin{description}
+\item[$i_{t_m} = i_{p_k}+2$] Then there is not room to place both the propagators $s_{m'}$, and $t_{m'}$.
+Thus $t_m$ is removed at the step $i_{t_m} + 1$.
+Therefore, $q$ contributes at either $i_q$ or $i_q+1$.
+ \item[$i_{t_m} = i_{p_k}+1$] Then there is not room to place either the propagators $s_{m'}$, and $t_{m'}$.
+Thus $t_m$ is removed at the step $i_{t_m}$.
+Therefore, $q$ contributes at either $i_{a}$ or $j_{q}+1$.
+ \item[$i_{t_m} = i_{p_k}$] Since $k < m$, the propagator $p_k$ is not removed at step $i_{p_k}$ or $i_{p_k}+1$.
+Therefore consider the propagators that ensure that $s_m$ is not removed at $i_{s_m}$ or $i_{s_m}+1$.
+By the above argument, there exists an $t_{m'}$ such that $i_{t_m'} = i_{t_m}$.
+This requires the existence of propagators such that $s_m'$ is not removed at $i_{s_m'}$ or $i_{s_m'}+1$.
+This argument continues at infinitum, contradicting both the fact that there are only a finite number of propagators in $W$, and that at most $i_{s_m} - i_{t_m}-1$ propagators can be supported on the cyclic interval $\{i_{t_m}, i_{s_m}+1\}$.
+ \end{description}
+
+Since all of these cases lead to a contradiction, one cannot both have $p$ not contribute $j$ to $I_a$ and not have a binary tree $T$ protecting $p$ at $j$ from $a$.
+
+The argument for $j+1$ is the same with two trees, $T_1$ and $T_2$, one leaf of $T_1$ preventing $p$ from contributing $j$ to $I_a$, and the corresponding leaf of $T_2$ preventing $p$ from contributing $j+1$.
+
+\end{proof}
+
+\end{comment}
+
+The converse, howevever requires an extra condition.
+
+\begin{lem} \label{protect conv lem}
+For $W = (\cP, n)$, $p = (i,j)$, and $v \in \{i, j\}$, $w \in \{i+1, j+1\}$ and $ a \in [n]$ a vertex of $W$, if $v$ (resp.
+$w$) is the first vertex of $V_p$ in the $<_a$ order such that $P_v$ (resp.
+neither $P_v$ nor $P_w$) does not exsist, then $p$ contributes $v$ (resp.
+$w$) to $I_a$.
+\end{lem}
+
+\begin{proof}
+If $p$ doesn't contribute $v$ or $w$ $I_a$, then either $p$ contributes a different supporting vertex $u$ earlier in the $<_a$ order or there is a propagator at $s_1$ preventing $p$ from contributing $v$ (or $w$) to $I_a$, or there is a pair of propagators $s_1$ (resp.
+and $s_4$) preventing $p$ from contributing $w$, or $v$, at $I_a$.
+
+If there is a propagator $s_1 \in \cP$ that are still in the diagram at step $v$, (write them $s_1 = (i_{s_1}, j_{s_1})$ with $j_{s_1} \in \{v, v-1\}$), then $s_1$ did not contribute $i_{s_1}$ or $i_{s_1} +1 $ to $I_a$.
+Therefore, $s_1$ cannot contribute $i_{s_1}$ $i_{s_1}+1$ to $I_a$.
+In other words, either $a-3 <_{v+1} i_{s_1}$ or there must be two other propagators $s_2 = (i_{s_2}, j_{s_2})$ and $s_3 = (i_{s_3}, j_{s_3})$, with $j_{s_2} \in \{i_{s_1}, i_{s_1}-1\}$ and $i_{s_3} <_{s_1} i_{s_2} <_{s_1} j_{s_2} \leq_{s_1} j_{s_3} = j_{s_1}$ that prevent this.
+We show that, if $a-3 \not <_{v+1} i_{s_1}$, then $a-3 <_{v+1} i_{s_2} <_{v+1} s_3$.
+That is, there is a set $P_v$ preventing $p$ from contributing $v$.
+
+The argument for showing that there must be two sets $P_v$ and $P_w$ is simlar, and is not made explicit here.
+
+We proceed by contradiction.
+Suppose $a-3 \not <_{v+1} i_{s_2}$.
+Then, there exists two propagators $s_4$ and $s_5$ such that $s_4 = (i_{s_4}, j_{s_4})$ and $s_5 = (i_{s_5}, j_{s_5})$, with $j_{s_4} \in \{i_{s_2}, i_{s_2}-1\}$ and $i_{s_5} <_{s_2} i_{s_4} <_{s_2} j_{s_4} \leq_{s_2} j_{s_5} = j_{s_2}$.
+If $a-3 <_{v+1} i_{s_4} <_{v+1} s_5$, we may assume without loss of generality that there are no futher propagators of the form $t = (i_t, j_t)$ with $j_t \in \{i_{s_1}, j_{s_1}-1\}$ or $i_t \in [ i_{s_4}, i_{s_1}]$.
+Otherwise, one may replace $p$ with $s_1$ in this argument.
+Therefore, $s_1$ contributes $i_{s_1}$ to $I_a$, which is a contradiction.
+Therefore, we must again suppose that $a-3 \not <_{v+1} i_{s_4}$.
+
+In order for $s_1$ to exists at step $v$ of algorithm \ref{Alg:put GN on WLD}, one must continue to find pairs of propagators $s_{m'}$, $s_{m'+1}$ in $\cP$ that sheild the initial endpoint of a previously defined propagator, $s_m$.
+There are three cases to consider.
+Let $s_k$ indicate a propagator identified at an earlier stage of this construction where $i_{p_0} = \min{i_p, a}$.
+
+ \begin{description}
+\item[$i_{s_m} = i_{p_k}+2$] By admissibility, there is not room to place both the propagators $s_{m'}$, and $s_{m'+1}$.
+Thus $s_m$ is removed at the step $i_{s_m}$ or $i_{s_m} + 1$.
+Therefore, $s_1$ contributes at either $i_{s_1}$ or $i_{s_1}+1$.
+ \item[$i_{s_m} = i_{p_k}+1$] By admissibility, there is not room to place either the propagators $s_{m'}$, or $s_{m'+1}$.
+Thus $s_m$ is removed at the step $i_{s_m}$.
+Therefore, $s_1$ contributes at either $i_{s_1}$ or $i_{s_1}+1$.
+ \item[$i_{t_m} = i_{p_k}$] Since $k < m$, the propagator $p_k$ is not removed at step $i_{p_k}$ or $i_{p_k}+1$.
+Therefore neither is $s_{m'}$.
+Furthermore, there cannot be propagators that prevent $s_{m'}$ from being removed at $j_{s_m}$ or $j_{s_m}+1$.
+Otherwise, we could replace $p$ with $sm_{m'}$ and repeat this argument.
+Since $\cP$ is finite, this replacement process must terminate, forcing $s_{m'}$ to contribute $j_{s_m}$ or $j_{s_m}+1$, and thereby, $s_1$ contributes at either $i_{s_1}$ or $i_{s_1}+1$.
+ \end{description}
+\end{proof}
+
+\begin{comment}
+
+\begin{lem}\label{useful lem for GN alg}
+Let $W = (\cP, n)$ be an admissible Wilson loop diagram, and $p = (i, j) \in \cP$.
+Let $v$ be a vertex such that $i +1 \leq_i v \leq_i j$ (resp.
+$j +1 \leq_j v \leq_j i$).
+If there exists another propagator $q = (i_q, j_q)$ such that $i_q \in \{i, i-1\}$ and $j +1 \leq_j j_q \leq_j i$, (resp.
+$j_q \in \{j, j-1\}$ and $i +1 \leq_i i_q \leq_i j$), then $q$ contributes $m_v$ to $I_v$, where $m_v \in \{j, j+1\}$, (resp.
+$m_v \in \{i, i+1\}$).
+\end{lem}
+
+\begin{proof}
+In this proof, we consider the case where $i +1 \leq_i v \leq_i j$. The situation when $j +1 \leq_j v \leq_j i$ is similarly proved by exchanging the roles of $i$ and $j$.
+
+Suppose the statement doesn't hold.
+Then, for some propagator $q= (i_q, j_q) \in \cP$ such that $i_q \in \{i, i+1\}$ and $j +1 \leq_j j_q \leq_j i$, there are two propagators, $s_1 = (i_{s_1}, j_{s_1})$ and $t_1 = (i_{t_1}, j_{t_1})$ that contribute $i_q$ and $i_q +1$ respectively to $I_v$.
+Namely, we write \bas j \leq_j i_{t_1} <_j i_{s_1} <_j j_{s_1} \leq_j j_{t_1} = i_q\;,\eas with $j_{s_1} \in \{i_q, i_q-1\}$.
+
+In order for $i_{s_1}$ and $i_{t_1}$ to respectively contribute $i_q$ and $i_q +1$, there must be $4$ other propagators, $i_{s_2}$, $i_{t_2}$, $i_{s_3}$, and $i_{t_3}$ that contribute $i_{s_1}$, $i_{s_1}+1$, $i_{t_1}$ and $i_{t_1}+1$ respectively.
+
+For each $s_m$ and $t_m$ thus identified, t here must be other pairs of propagators, $s_{m'}$ and $s_{m'}$ (with $m'> m$) that are removed at steps $i_{s_m}$ and $i_{s_m} +1$ or $i_{t_m}$ and $i_{t_m}+1$.
+Note that under this construction, $i_{t_m} <_j i_{s_m}$.
+
+There are now three cases to be considered. Let $p_k$ indicate a propagator identified at an earlier stage of this construction (that is, $ m\geq k > 0$ and $p_k \in \{s_k, t_k\}$, or $p_k = p$).
+
+ \begin{description}
+\item[$i_{t_m} = i_{p_k}+2$] Then there is not room to place both the propagators $s_{m'}$, and $t_{m'}$.
+Thus $t_m$ is removed at the step $i_{t_m} + 1$.
+Therefore, $q$ contributes at either $i_q$ or $i_q+1$.
+ \item[$i_{t_m} = i_{p_k}+1$] Then there is not room to place either the propagators $s_{m'}$, and $t_{m'}$.
+Thus $t_m$ is removed at the step $i_{t_m}$.
+Therefore, $q$ contributes at either $i_{a}$ or $j_{q}+1$.
+ \item[$i_{t_m} = i_{p_k}$] Since $k < m$, the propagator $p_k$ is not removed at step $i_{p_k}$ or $i_{p_k}+1$.
+Therefore consider the propagators that ensure that $s_m$ is not removed at $i_{s_m}$ or $i_{s_m}+1$.
+By the above argument, there exists an $t_{m'}$ such that $i_{t_m'} = i_{t_m}$.
+This requires the existence of propagators such that $s_m'$ is not removed at $i_{s_m'}$ or $i_{s_m'}+1$.
+This argument continues at infinitum, contradicting both the fact that there are only a finite number of propagators in $W$, and that at most $i_{s_m} - i_{t_m}-1$ propagators can be supported on the cyclic interval $\{i_{t_m}, i_{s_m}+1\}$.
+ \end{description}
+
+\end{proof}
+
+\begin{cor} \label{useful cor for GN alg}
+The above lemma also holds for $v = j+1$ (resp. $v = i+1$, unless $q = (i-1, j)$ (resp. $q = (j-1, i)$).
+\end{cor}
+\begin{proof}
+The proof is exactly as above. This statement is not included in the statement of the previous lemma only out of concerns for linguistic clarity.
+\end{proof}
+\end{comment}
+
+We use these results to prove some properties about the Algorithm \ref{alg:put GN on WLD}. 
 \begin{prop}\label{res:alg k labels}
 If $W = (\cP, n)$ is an admissible Wilson loop diagram with $|\cP| = k$, then Algorithm~\ref{alg:put GN on WLD} puts exactly $k$ distinct labels on each edge.
-\end{prop} \note{is there a way to do this theorem using the chords and polygons?}
+\end{prop} 
 \begin{proof}
@@
 Suppose this doesn't happen, i.e.
-there is a propagator $p_0 \in \cP$ which survives the first $n$ steps of the algorithm for some starting vertex $s$.
-We will show that this always gives a contradiction in an admissible diagram by constructing an inductive sequence of propagators on strictly decreasing regions of the diagram.
-
-Fix an $a \in [n]$. Write $V_{p_0} = (i_{p_0},i_{p_0}+1,j_{p_0},j_{p_0}+1)$ with $a \leq_a i_{p_0} <_a j_{p_0}$.
-
-Since $p$ is not removed by step $j_{p_0}+1$, there are $4$ propagators $q_1, r_1, s_1, t_1$ that are removed at step $i_{p_0},i_{p_0}+1,j_{p_0}$ , or $j_{p_0}+1$ respectively, allowing $p_0$ to remain after $n$ steps.
-Let us consider the propagators $s_1$ and $t_1$, preventing $p_0$ from being eliminated at steps $b_0$ and $b_0+1$.
-Let $s_1 = (i_{s_1}, j_{s_1})$, and $t_1 = (i_{t_1}, j_{t_1})$, where \bas i_{p_0} <_a i_{t_1} <_a i_{s_1} < j_{s_1} \leq_a j_{t_1} = j_{p_0}\;.\eas Note that $j_{r_1}$ must either be $j_{p_0}-1$ or $j_{p_0}$.
-Otherwise, it would not be removed at the $j_{p_0}^{th}$ step.
-Admissibility prevents $i_{p_0} = i_{t_1}$ as this would imply that both $p_0 = (i_{p_0}, j_{p_0})$ and $t_1 = (i_{p_0}, j_{p_0})$.
-
-In order for $t_1$ and $s_1$ to be removed at step $j_{p_0}$ and $j_{p_0}+1$ respectively, they cannot be removed at steps $i_{t_1}$ and $i_{t_1} +1$ or $i_{s_1}$ and $i_{s_1}+1$ respectively.
-Therefore, there needs to be two pairs of propagators, $q_2$, $r_2$ which are removed at step $i_{s_1}$ and $i_{s_1}+1$, and $q_3$, $r_3$ which are removed at step $i_{t_1}$ and $i_{t_1}+1$.
-Note that this implies that $i_{p_0}+2 <_a i_{t_1}$.
-Otherwise, there is not room to place both the propagators $q_3$, $r_3$.
-
-For each $q_m$ and $r_m$ thus identified, there must be other pairs of propagators, $p_{m'}$ and $q_{m'}$ (with $m'> m$) that are removed at steps $i_{q_m}$ and $i_{q_m} +1$ or $i_{r_m}$ and $i_{r_m}+1$.
-Note that under this construction, $i_{r_m} <_a i_{q_m}$.
-
-There are now three cases to be considered. Let $p_k$ indicate a propagator identified at an earlier stage of this construction ($p_k \in \{q_k, r_k, s_k, t_k\}$, or $k=0$).
-
- \begin{description}
-\item[$i_{r_m} = i_{p_k}+2$] Then there is not room to place both the propagators $q_{m'}$, and $r_{m'}$.
-Thus $r_m$ is removed at the step $i_{r_m} + 1$.
-Therefore, $p_0$ contributes at either $j_{p_0}$ or $j_{p_0}+1$.
- \item[$i_{r_m} = i_{p_k}+1$] Then there is not room to place either the propagators $q_{m'}$, and $r_{m'}$.
-Thus $r_m$ is removed at the step $i_{r_m}$.
-Therefore, $p_0$ contributes at either $j_{p_0}$ or $j_{p_0}+1$.
- \item[$i_{r_m} = i_{p_k}$] Since $k < m$, the propagator $p_k$ is not removed at step $i_{p_k}$ or $i_{p_k}+1$.
-Therefore consider the propagators that ensure that $q_m$ is not removed at $i_{q_m}$ or $i_{q_m}+1$.
-By the above argument, there exists an $r_{m'}$ such that $i_{r_m'} = i_{r_m}$.
-This requires the existence of propagators that that $q_m'$ is not removed at $i_{q_m'}$ or $i_{q_m'}+1$.
-This argument continues at infinitum, contradicting both the fact that there are only a finite number of propagators in $W$, and that at most $i_{q_m} - i_{r_m}-1$ propagators can be supported on the cyclic interval $\{i_{r_m}, i_{q_m}+1\}$.
- \end{description}
-
-\todo{can this be simplified? Does it just need a picture?}
-
+there is a propagator $p= (i,j)\in \cP$ which survives the first $n$ steps of the algorithm for some starting vertex $a$.
+Without loss of generality, assume $a \leq_a i <_a j$.
+Otherwise, change the roles of $i$ and $j$.
+
+Since $p$ is not removed by step $j+1$, by Lemma \ref{protect dfn lem} there are $4$ protecting sets, $P_i,P_{i+1}, P_{j}$ , and $P_{j+1}$ respectively, allowing $p$ to remain after $n$ steps.
+
+However, since the cyclic interval $[i,j] \subseteq [a,j]$, $P_j$ and $P_{j+1}$ cannot be protecting sets by Corrollary \ref{protecting cor}.
+\end{proof}
 \begin{comment}
@@
 By induction, we will eventually find a propagator on a region with 3 or fewer vertices, which is inadmissible.
+
+\end{proof}
 \end{comment}
-\end{proof}
-
-Infact, we have proved more than the fact that each propagator contributes to the $I_a$ by the $n^{th}$ step.
-We have shown the each vertex $v \in V_p$ is contributed to some $I_{a_{p,v}}$ by $p$ for some $a_{p,v} \in [n]$
-
-\begin{cor}\label{every vertex contributed cor}
-For each propagator $p \in \cP$, and vertex $v \in V_p$, there is an $a_{p,v}$ such that $p$ contributes $v$ to $I_{a_{p,v}}$.
-\end{cor}
+
+\begin{lem} \label{vertex cyclic int lem}
+For every $v \in V_p$, there is a non-empty cyclic interval such that $p$ contributes $v$ to all $I_{a}$ for in said interval.
+\end{lem}
 
@@
 
-Suppose $p$ never contributed $j$ via Algorithm \ref{alg:put GN on WLD}.
-There there would be at least one propagator $s_1 = (i_{s_1}, j_{s_1})$ that contributed $j$ for all vertices $a \in [n]$.
-The vertex $j_{s_1} \in \{j, j-1\}$.
-Then there would have to be propagators $q_2$, $r_2$ that contributed $i_{s_1}$ and $i_{s_2}$ for all $a \in [n]$.
-But this is would create the need for an infinite number of propagators in a finite Wilson Loop diagram, which is impossible.
-
-The same argument holds for $j+1$, except that one has to add the existence of a second propagator $t_1 = (i_{t_1}, j)$ to the construction above.
-
-By cyclic symmetry, this is sufficient to prove that $p$ must also contribute $i$ and $i+1$ at some point.
-
-\end{proof}
-
-For $W = (\cP, n)$, let $W' = (P, V_P)$ be a subdiagram.
+Let $k_1 \ldots k_r$ be the set of propagators ending on edge $j$ or $j-1$, ordered such that $k_1$ is the first propagators clockwise from $p$, and $k_r$ is the clockwisemost propagator on edge $j-1$.
+For each $k_x$, write $P_{x} = \{k_x, s_x, t_x\}$, where $s_x$ and $t_x$, if they  exist, to be the two clockwise most propagators preventing $k_x$ from contributing $j$ to $I_{i+2}$.
+Similarly, let $l_1 \ldots l_m$ be the set of propagators ending on edge $i$ or $i-1$, ordered such that $l_1$ is the first propagators clockwise from $p$, and $l_m$ is the clockwisemost propagator on edge $i-1$.
+For each $l_y$, write $Q_{y} = \{l_x, s_y, t_y\}$, where $s_y$ and $t_y$, if they  exist, to be the two clockwise most propagators preventing $l_y$ from contributing $i$ to $I_{j+2}$.
+
+Define $b_1 = \min{k_1+1, s_1+1}$.
+We see that, if $r >0$, for all $a \in [i+2, b_1]$, $p$ contributes $j$ to $I_a$.
+(If $b_1 <_{j+1} i+2$ then this interval is empty.) This is because in this range, $j$ is the first vertex of $p$ encountered by Algorithm \ref{Alg: put GN on WLD}.
+Furthermore, by Lemma \ref{protect conv lem}, and definition \ref{protect dfn} if $b_1 \not <_{j+1} i+2$ $P_1$ does not protect $p$ at $j$ for $a$ in this range.
+If $r = 0$ then $p$ contributes $j$ for all $a \in [i+2, j]$.
+In this case, we say $b_1= j$.
+
+Define $b_2 = \min{k_2+1, s_2+1}$.
+If $r > 1$, and $j_{k_2}=j$, for all $a \in [b_1+1, b_2]$ $p$ contributes $j+1$ to $I_a$.
+In this range, $P_1$ is a protective set for $p$ at $j$, but $P_2$ is not a protective set for $j+1$ in this range.
+Therefore, in this range, $j+1$ is the first vertex of $p$ without a protective set.
+If the stated condidtions do not hold, then $p$ contributes $j+1$ for all $a \in [b_1 +1, j+1]$.
+
+Finally, for $r > 1$, and $j_{k_2}=j$,$a \in [b2+1, j+1]$, $p$ contributes $i$ to $I_a$.
+Again, for all $a$ in this range, both $P_1$ and $P_2$ are protective sets of $p$ at $j$ and $j+1$.
+Furthermore, by Corrollary \ref{protect cor}, no set $Q_y$ can be a protective set for $p$ at $i$ or $i+1$ for $a$ in this range.
+
+By switching the roles of $i$ and $j$, we see that for every element of $V_p$, there is a non-empty cyclic interval such that $p$ contributes $v$ to all $I_{a}$ for in said interval.
+\end{proof}
+
+{\color{red}For $W = (\cP, n)$, let $W' = (P, V_P)$ be a subdiagram.
 Write $\cI^{W'}$ be the set of $|P|$ tuples defined by \ref{alg:put GN on WLD} on $W'$.
@@
 Similarly, write $\cP_{j,i} =  \{ q = (i_q, j_q)\in \cP | j \leq_j i_q <_j j_q \leq_j i\}$ to be the set of propagators supported on the cyclic interval $[j,i]$.
-Note that $p = \cP_{i,j} \cap \cP_{j,i}$.
+Note that $p = \cP_{i,j} \cap \cP_{j,i}$.}
 
@@
 Then the propagator $p$ contributes last to the entries $I_{i+2}^{W_L}$ and $I_{j+2}^{W_R}$ respectively.
-\end{cor}
-
-\begin{proof}
-Consider $W_L$.
-Since every propagator in a Wilson loop diagram must contribute to $I_{i+2}^{W_L}$, it remains to check that no propagator can contribute after $p$.
-This could only happen if there were a different propagator, $q$ with an endpoint on edge $i$.
-If $q = (i , i+2)$, then it would be the first propagators to be removed, with contribution $i+2$.
-If it $q = (i, l)$, with $l > i+2$, then it would contribute either $l$ or $l+1$.
-Otherwise, one would need the existence of an infinite set of other propagators, as above.
-
-A similar argument works for $W_R$.
-\end{proof}
-
-\begin{lem} \label{vertex cyclic int lem}
-For every $v \in V_p$, there is a cyclic interval such that $p$ contributes $v$ to all $I_{a}$ for in said interval.
-\end{lem}
-
-\begin{proof}
-
-Fix $p \in \cP$, with $p = (i,j)$.
-Consider two subsets of propagators in $\cP$, $Q = \{q_m\}$, $R = \{r_n\}$.
-Let $Q \subseteq \cP_{i,j}$ be the set of propagators with one end point either on the edge $j-1$ or $j$.
-Label the other endpoint of $q_m$ as the edge $k_m$, with $i \leq_i k_1 <_i k_2 <_i \ldots \leq_i j$.
-In other words, they are ordered from closest to furthest away from $p$.
-
-Similarly, define $R \subset \cP_{j,i}$ be the set of propagators with one end point either on the edge $i-1$ or $i$.
-I label the other endpoint of $r_n$ as the edge $l_n$, with $j \leq_j l_1 <_j l_2 <_j \ldots \leq_j i$.
-In other words, they are ordered from closest to furthest away from $p$.
-
-\todo{Insert picture here}
-
-For any $m >|Q|$ (resp. $m > |R|$), write $k_m= j$ (resp. $l_n = i$).
-
-We make the following four claims:
-
-\begin{enumerate}
-\item The propagator $p$ contributes $i$ for all $I_a$ for $a \in [a_{p,i} = k_2+2, b_{p,i} = l_1+1]$
-\item The propagator $p$ contributes $i+1$ for all $I_a$ for $a \in [b_{p,i} +1, a_{p, j} -1]$.
-\item The propagator $p$ contributes $j$ for all $I_a$ for $a \in [a_{p,j} = l_2+2, b_{p,j} = k_1+1 ]$
-\item The propagator $p$ contributes $j+1$ for all $I_a$ for $a \in [k_1+2, k_2+1 ]$
-\end{enumerate}
-
-This proof follows from the argument in Corollary \ref{rightmost prop last cor}, and Corrollary \ref{every vertex contributed cor} that show that $p$ contributes last to $I_{i+2}^{W_L}$.
-In particular, $p$ contributes after all the propagators in $Q$ in $I_{i+2}$.
-Furthermore, it contributes either $j$ or $j+1$ to this entry.
-If $q_1 \neq (k_1 = i, j-1)$, then $p$ contributes $j$.
-This is because $i+2 \leq_i k_m+1$ for all $m > 0$, which forces the propagators $q_m$ to contribute at the $k_m$ or $k_m+1$ vertex.
-
-\note{there seems to be a problem with the proof as written, namely, it isn't consistent with itself if you change from $p$ to $q_1$.}
-
-\end{proof}
-
-\begin{lem}\label{lem susama}
-  \note{this lemma should be rephrased to be more in your language, it was just copied from the rank section, also it needs a cite or a proof}
-  Given a WLD and a propagator $p$,  each covered vertex of $p$ is contributed to a non-empty cyclic interval in the Gra\ss mann necklace.
-\end{lem}
-
-\begin{lem}\label{lem basis as perm}
-Let $W$ be an admissible Wilson loop diagram and let $\PP_W$ be the positroid associated to $W$.
-A $k$-subset $J \in \binom{[n]}{k}$ is a basis for $\PP_W$ if and only if there is a set bijection between $J$ and the set of propagators of $W$ such that for each $j\in J$ the propagator associated to $j$ is supported on vertex $j$.
-\end{lem}
-
-\begin{proof}
-\note{I don't know if you already have this in your previous papers or not; but it is important so I wanted to extract it as a lemma.
-The proof of the next proposition originally contained the lines ``Recall from [ref] that a $k$-subset $J \in \binom{[n]}{k}$ is a basis for $\PP_W$ if and only if it has no subset $U \subseteq J$ such that $|U| > |Prop(U)|$.'' but I don't know what that ref is nor whether that ref would also prove this lemma.}
-\end{proof}
+\end{cor} \todo{do you need this}
+
+{\color{red}\begin{proof}
+The support vertices of $p$, $V_p = \{i, i+1, j, j+1\}$ are the last four vertices supporting any propagators at all in the $<_{i+2}$ linear order on $[n]$.
+Since $p$ contributes to $I_{i+2}^{W_L}$, it must contribute at one of these $4$ vertices.
+
+The only possible configuration in which this result cannot hold is if $i$ or $i+1$ were in $I_{i+2}^{W_L}$ but not contributed by $p$.
+
+\end{proof}}\todo{currently rubbish}
 
@@
 
-We need four lemmas from stuff you guys have already figured out.  The first one is a corollary of your lemma characterizing intervals contributed by each covered vertex of a propagator.
+We need four lemmas from stuff you guys have already figured out.  The first one is a corollary of your lemma characterizing intervals contributed by each covered vertex of a
+propagator.
 

### 2018-06-12 General WLD combinatorics.tex
some typos fixed

@@
 
-\begin{dfn}
+\begin{dfn}\label{protect dfn}
 Let $W = (\cP,n)$ be an admissible diagram and $a \in[n]$ a vertex.
@@
 One may also have $s_2 = (i_{s_2}, i_{s_1}-1)$.
-Furthermore, $a-3 <_{v+1} s_m$.
-Similarly, for the given $a$, either $a-3 <_{v+1} i_{s_4}$ or there exist $2$ propagators $s_5$ and $s_6 \in P_w$ such that $s_5 = (i_{s_5}, i_{s_4})$ and $s_6 = (i_{s_6}, i_{s_4})$.
-One may also have $s_6 = (i_{s_6}, i_{s_4}-1)$.
-Furthermore, $a-3 <_w s_m$.
-\end{enumerate}
+Furthermore, $a-3 <_{v+1} s_m$.\end{enumerate}
 \end{dfn}
-
-\begin{comment}
-\begin{dfn}
-Let $W = (\cP,n)$ be an admissible diagram and $a \in[n]$ a vertex.
-For $p= (i,j) \in \cP$ an a propagator of $W$  and $v \in \{i, j\}$ (or $w \in \{i+1, j+1\}$) an edge of $W$, let $P_{v}$ (or $P_w$) to be a \emph{protecting set of $p$ at $v$ (or $w$) at $a$} defined as follows: \begin{enumerate}
-\item Work under the linear order on $[n]$, $<_{v+1}$, every propagator is now written as $p = (i_p, j_p)$ such that $i_p <_{v+1} j_p$. 
-\item The sets $P_v$ and $P_w$ are disjoint. 
-\item There is an $r \in P_{v}$ such that $j_r \in \{v, v-1\}$ and $ i_r \in [i_p, j_p]$.
-If $j_r = v-1$, then $r$ is the clockwise most propagator on the edge $v$.
-Similarly, there is a $r \in P_{w}$ such that $j_r =v$ and $ i_r \in [i_p, j_p]$.
-\item For every $q = (i_q, j_q) \in P_{v}$, or $P_w$, if there are at least two propatagors $s$ and $t$ $\in \cP$ satisfying $s = (i_s, i_q)$ or $s = (i_s, i_q-1 )$ (in which case $s$ is the clockwise most propagator on the edge $i_q$) and $t = (i_t, i_t)$ then all such $s$ and $t$ are also in $P_v$ or $P_w$.
-These are called the daughter propagators of $q$.
-If two such propagators don't exist, then $q$ is called a terminal propagator.
-\item For the $a$ given above, there is a propagator $q$ with a set of daughters $\{s_m\}$ satisfying $a-3 <_{v+1} i_{s_m}$.
-\end{enumerate} 
-\end{dfn}
-\end{comment}
 
@@
 \end{proof}
-
-\begin{comment}
-\begin{lem}\label{protecting lem}
-Let $W = (\cP, n)$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$.
-Then $p$ does not contribute $i$ or $j$ to $I_a$ if there is a subtree protecting $i$ or $j$ from $a$ in $\tau(W)$.
-Furthermore, $p$ does not contribute $i+1$ or $j+1$ if there are two protecting subtrees, at least one of which has a leaf vertex at $v$.
-\end{lem}
-
-\begin{proof}
-It is sufficient to prove this for $i$ and $i+1$. The other two can be proved by switching the roles of $i$ and $j$. We show this by contradiction.
-
-Assume that $p$ does not contribute $i$ to $I_a$.
-Furthermore, that there is a binary tree $T$ protecting $p$ at $i$ from $a$.
-Then, there is some propagator $q= (i_q, j_q) \in \cP$ corresponding to a leaf of $T$ such that $i_q \in \{i, i-1\}$ and $j +1 \leq_j j_q \leq_j i$.
-Further, there are two propagators, $s_1 = (i_{s_1}, j_{s_1})$ and $t_1 = (i_{t_1}, j_{t_1})$ that contribute $i_q$ and $i_q +1$ respectively to $I_v$.
-Namely, we write \bas j \leq_j i_{t_1} <_j i_{s_1} <_j j_{s_1} \leq_j j_{t_1} = i_q\;,\eas with $j_{s_1} \in \{i_q, i_q-1\}$.
-
-In order for $i_{s_1}$ and $i_{t_1}$ to respectively contribute $i_q$ and $i_q +1$, there must be $4$ other propagators, $i_{s_2}$, $i_{t_2}$, $i_{s_3}$, and $i_{t_3}$ that contribute $i_{s_1}$, $i_{s_1}+1$, $i_{t_1}$ and $i_{t_1}+1$ respectively.
-
-For each $s_m$ and $t_m$ thus identified, t here must be other pairs of propagators, $s_{m'}$ and $s_{m'}$ (with $m'> m$) that are removed at steps $i_{s_m}$ and $i_{s_m} +1$ or $i_{t_m}$ and $i_{t_m}+1$.
-Note that under this construction, $i_{t_m} <_j i_{s_m}$.
-By construction, each of these propagators must have endpoints in $[a,i] \cap [j,i]$.
-
-There are now three cases to be considered.
-Let $p_k$ indicate a propagator identified at an earlier stage of this construction (that is, $ m\geq k > 0$ and $p_k \in \{s_k, t_k\}$, or $p_k$ is the first propagator of $T$ lying counterclockwise from $a$.).
-
- \begin{description}
-\item[$i_{t_m} = i_{p_k}+2$] Then there is not room to place both the propagators $s_{m'}$, and $t_{m'}$.
-Thus $t_m$ is removed at the step $i_{t_m} + 1$.
-Therefore, $q$ contributes at either $i_q$ or $i_q+1$.
- \item[$i_{t_m} = i_{p_k}+1$] Then there is not room to place either the propagators $s_{m'}$, and $t_{m'}$.
-Thus $t_m$ is removed at the step $i_{t_m}$.
-Therefore, $q$ contributes at either $i_{a}$ or $j_{q}+1$.
- \item[$i_{t_m} = i_{p_k}$] Since $k < m$, the propagator $p_k$ is not removed at step $i_{p_k}$ or $i_{p_k}+1$.
-Therefore consider the propagators that ensure that $s_m$ is not removed at $i_{s_m}$ or $i_{s_m}+1$.
-By the above argument, there exists an $t_{m'}$ such that $i_{t_m'} = i_{t_m}$.
-This requires the existence of propagators such that $s_m'$ is not removed at $i_{s_m'}$ or $i_{s_m'}+1$.
-This argument continues at infinitum, contradicting both the fact that there are only a finite number of propagators in $W$, and that at most $i_{s_m} - i_{t_m}-1$ propagators can be supported on the cyclic interval $\{i_{t_m}, i_{s_m}+1\}$.
- \end{description}
-
-Since all of these cases lead to a contradiction, one cannot both have $p$ not contribute $j$ to $I_a$ and not have a binary tree $T$ protecting $p$ at $j$ from $a$.
-
-The argument for $j+1$ is the same with two trees, $T_1$ and $T_2$, one leaf of $T_1$ preventing $p$ from contributing $j$ to $I_a$, and the corresponding leaf of $T_2$ preventing $p$ from contributing $j+1$.
-
-\end{proof}
-
-\end{comment}
 
@@
 \end{proof}
-
-\begin{comment}
-
-\begin{lem}\label{useful lem for GN alg}
-Let $W = (\cP, n)$ be an admissible Wilson loop diagram, and $p = (i, j) \in \cP$.
-Let $v$ be a vertex such that $i +1 \leq_i v \leq_i j$ (resp.
-$j +1 \leq_j v \leq_j i$).
-If there exists another propagator $q = (i_q, j_q)$ such that $i_q \in \{i, i-1\}$ and $j +1 \leq_j j_q \leq_j i$, (resp.
-$j_q \in \{j, j-1\}$ and $i +1 \leq_i i_q \leq_i j$), then $q$ contributes $m_v$ to $I_v$, where $m_v \in \{j, j+1\}$, (resp.
-$m_v \in \{i, i+1\}$).
-\end{lem}
-
-\begin{proof}
-In this proof, we consider the case where $i +1 \leq_i v \leq_i j$. The situation when $j +1 \leq_j v \leq_j i$ is similarly proved by exchanging the roles of $i$ and $j$.
-
-Suppose the statement doesn't hold.
-Then, for some propagator $q= (i_q, j_q) \in \cP$ such that $i_q \in \{i, i+1\}$ and $j +1 \leq_j j_q \leq_j i$, there are two propagators, $s_1 = (i_{s_1}, j_{s_1})$ and $t_1 = (i_{t_1}, j_{t_1})$ that contribute $i_q$ and $i_q +1$ respectively to $I_v$.
-Namely, we write \bas j \leq_j i_{t_1} <_j i_{s_1} <_j j_{s_1} \leq_j j_{t_1} = i_q\;,\eas with $j_{s_1} \in \{i_q, i_q-1\}$.
-
-In order for $i_{s_1}$ and $i_{t_1}$ to respectively contribute $i_q$ and $i_q +1$, there must be $4$ other propagators, $i_{s_2}$, $i_{t_2}$, $i_{s_3}$, and $i_{t_3}$ that contribute $i_{s_1}$, $i_{s_1}+1$, $i_{t_1}$ and $i_{t_1}+1$ respectively.
-
-For each $s_m$ and $t_m$ thus identified, t here must be other pairs of propagators, $s_{m'}$ and $s_{m'}$ (with $m'> m$) that are removed at steps $i_{s_m}$ and $i_{s_m} +1$ or $i_{t_m}$ and $i_{t_m}+1$.
-Note that under this construction, $i_{t_m} <_j i_{s_m}$.
-
-There are now three cases to be considered. Let $p_k$ indicate a propagator identified at an earlier stage of this construction (that is, $ m\geq k > 0$ and $p_k \in \{s_k, t_k\}$, or $p_k = p$).
-
- \begin{description}
-\item[$i_{t_m} = i_{p_k}+2$] Then there is not room to place both the propagators $s_{m'}$, and $t_{m'}$.
-Thus $t_m$ is removed at the step $i_{t_m} + 1$.
-Therefore, $q$ contributes at either $i_q$ or $i_q+1$.
- \item[$i_{t_m} = i_{p_k}+1$] Then there is not room to place either the propagators $s_{m'}$, and $t_{m'}$.
-Thus $t_m$ is removed at the step $i_{t_m}$.
-Therefore, $q$ contributes at either $i_{a}$ or $j_{q}+1$.
- \item[$i_{t_m} = i_{p_k}$] Since $k < m$, the propagator $p_k$ is not removed at step $i_{p_k}$ or $i_{p_k}+1$.
-Therefore consider the propagators that ensure that $s_m$ is not removed at $i_{s_m}$ or $i_{s_m}+1$.
-By the above argument, there exists an $t_{m'}$ such that $i_{t_m'} = i_{t_m}$.
-This requires the existence of propagators such that $s_m'$ is not removed at $i_{s_m'}$ or $i_{s_m'}+1$.
-This argument continues at infinitum, contradicting both the fact that there are only a finite number of propagators in $W$, and that at most $i_{s_m} - i_{t_m}-1$ propagators can be supported on the cyclic interval $\{i_{t_m}, i_{s_m}+1\}$.
- \end{description}
-
-\end{proof}
-
-\begin{cor} \label{useful cor for GN alg}
-The above lemma also holds for $v = j+1$ (resp. $v = i+1$, unless $q = (i-1, j)$ (resp. $q = (j-1, i)$).
-\end{cor}
-\begin{proof}
-The proof is exactly as above. This statement is not included in the statement of the previous lemma only out of concerns for linguistic clarity.
-\end{proof}
-\end{comment}
 

### 2018-06-21 General WLD combinatorics.tex
minor things

@@
 The Wilson loop diagrams also define a volume form on $\Sigma(W)$: \bas \Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V_{p_r}} \textrm{d}c_{p_r}}{R(W)} \;.
-\eas The denominator $R(W)$ is a polynomial defined by $2 \times 2$ and $1 times 1$ minors of $C(W)$ as defined below.
-
-\begin{dfn}
+\eas The denominator $R(W)$ is a polynomial defined by $2 \times 2$ and $1 \times 1$ minors of $C(W)$ as defined below.
+
+\begin{dfn}\label{def R(W)}
 For $W = (\cP, n)$, $R(W) = \prod_{e=1}^n R_e$, with $R_e$ defined by the propagators ending on it.
 For any edge $e$ of $W$, order the propagators incident on $e$ as $\{p_1 \ldots p_r\}$, ordered such that $p_1$ is closest to the vertex $e$, $p_r$ closest to $e+1$, and $p_i$ is closer to $e$ than $p_{i+1}$.
-Then \bas R_e =  c_{p_1,e+1} \prod_{j= 1}{s-1} \left((c_{p_j,e} c_{p_{j+1},e+1} - c_{p_{j+1},e} c_{p_{j},e+1} ) \right) c_{p_s,e}\;.\eas Note that in this notation, if $s = 1$, $R_e = c_{p,e} c_{p,e+1}$.
+Then \bas R_e =  c_{p_1,e+1} \prod_{j= 1}(r-1) \left((c_{p_j,e} c_{p_{j+1},e+1} - c_{p_{j+1},e} c_{p_{j},e+1} ) \right) c_{p_s,e}\;.\eas Note that in this notation, if $r = 1$, $R_e = c_{p,e} c_{p,e+1}$.
 \end{dfn}
@@
 
-A planar embedding of a graph is a \emph{triangulation} if all faces, except possibly the infinite, face are triangles.
+A planar embedding of a graph is a \emph{triangulation} if all faces, except possibly the infinite face, are triangles.
 
@@
 \begin{cor}
-  Let $W$ be an admissible Wilson loop diagram where the sizes of the supports of the maximal connected exact subdiagrams are $n_1, n_2, \ldots, n_j$.
+  Let $W$ be an admissible Wilson loop diagram where the sizes of the supports of the nontrivial maximal connected exact subdiagrams are $n_1, n_2, \ldots, n_j$.
 Then the number of admissible Wilson loop diagrams equivalent to $W$ (including $W$ itself) is
@@
 
-Define $b_1 = \min{k_1+1, s_1+1}$.
+Define $b_1 = \min\{k_1+1, s_1+1\}$.
 We see that, if $r >0$, for all $a \in [i+2, b_1]$, $p$ contributes $j$ to $I_a$.
@@
 \begin{algorithm}\label{alg WLD to denom via GN}
-Let $W$ be a Wilson loop diagram with $n$ vertices.  Let $C(W)$ be the matrix \hlfix{which has some actual name and a ref to where you define it}.
+Let $W$ be a Wilson loop diagram with $n$ vertices.  Let $C(W)$ be the matrix of $W$ as defined in \eqref{C(W) dfn}.
 \begin{itemize}
@@
     \item $r_i$ divides $\Delta_{I_i}$.
-    \item $R$ is the radical of $\prod_{i=1}^{n}\Delta_{I_i}$.
+    \item The ideal generated by $R$ is the radical of the ideal generated by $\prod_{i=1}^{n}\Delta_{I_i}$.
   \end{enumerate}
@@
 Taking everything together we have that $R|\prod_{i=1}^n \Delta_{I_i}$, $R$ contains all factors of $\prod_{i=1}^n \Delta_{I_i}$ and $R$ is squarefree.
-Therefore $R$ is the radical of $\prod_{i=1}^n \Delta_{I_i}$.
+Therefore the ideal generated by $R$ is the radical of the ideal generated by $\prod_{i=1}^n \Delta_{I_i}$.
   \end{enumerate}
@@
 Given any admissible Wilson loop diagram $W$, let $GN(W) = \{I_1, \ldots I_n\}$ be the associated Grasmann necklace.
-Then the denominator of the integral $I(W)$ is the \hlfix{find correct word for this} is the minimal polynomial of $\prod_{i=1}^n \Delta_{I_i}$, where $\Delta_{I_i}$ is the determinant of the $k \times k$ minor indicated by $I_i$.
+Then the denominator of the integral, $R(W)$ (see Definition~\ref{def R(W)}), is an integer multiple of the radical of $\prod_{i=1}^n \Delta_{I_i}$, where $\Delta_{I_i}$ is the determinant of the $k \times k$ minor indicated by $I_i$.
 \end{thm}

### 2018-06-21 General WLD combinatorics.tex
proof of final theorem and example

@@
 
+\begin{figure}
+\includegraphics{egWLD_forR}
+\caption{Example WLD for illustrating Algorithm~\ref{alg WLD to denom via GN} and bijections between propagators and vertices for each Grassmann necklace element.}\label{fig R eg}
+\end{figure}
+
+For example consider the Wilson loop diagram in Figure~\ref{fig R eg}.  
+\[
+C(W) = \begin{bmatrix} a & b & 0 & 0 & 0 & c & d \\ e & f & 0 & 0 & g & h & 0 \\ i & j & 0 & k & l & 0 & 0 \end{bmatrix}
+\]
+The Grassmann necklace is $I_1 = \{1,2,4\}, I_2 = \{2,4,5\}, I_3 = \{4,5,6\}, I_4=\{4,5,6\}, I_5=\{5,6,7\}, I_6 = \{6,7,1\}, I_7=\{7,1,2\}$.
+The bijection between propagators and vertices for each necklace element is also in Figure~\ref{fig R eg}.
+Between $I_1$ and $I_2$, two propagators change which vertex they are assigned to and these are the propagators associated to rows 1 and 2 of $C(W)$ as given above.
+Then
+\[
+\Delta_{I_2}=\det\begin{bmatrix} b & 0 & 0 \\ f & 0 & g \\ j & k & l \end{bmatrix} = kgb
+\]
+and so $r_2 = gb$.
+From $I_2$ to $I_3$ only one propagator changes its vertex association and we get $r_3 = c$.
+$I_3=I_4$ and so $r_4=1$.
+Continuing likewise we get $r_5 = lhd$ and $r_6 = i$.
+From $I_6$ to $I_7$ the propagators associated to the second and third rows change, thus from $\Delta_{I_7} = d(ej-fi)$ we get $r_7 = ej-fi$.
+Note that as proved in the next proposition, this quadratic factor arises when the two edges whose vertex association changed are associated with the two ends of the edge on which they are both supported.
+Finally, $r_1 = (af-be)k$.
+Together we obtain
+\[
+R = (af-be)kgbclhdi(ej-fi)
+\]
+which is squarefree and contains all factors of $\prod_{i=1}^{n}\Delta_{I_i}$.
+
 \begin{prop}\label{prop alg gives rad}
@@
 
-\note{I don't want to write the rest of this right now because we need to somewhere (probably much earlier in the document) define $R(W)$ and exactly how we do so makes a difference.
-The definition I would most like is if we define it as the product of the prop together and prop to vertex limits, if we define it some other way I'll probably want a lemma to get to that formulation.}
-
-\end{proof}
+To this end, first note that $R(W)$ and $R$ both have total degree $4|\mathcal{P}|$; the degree of $R(W)$ is immediate from the definition while that of $R$ follows from Lemma~\ref{lem susama}.
+By Proposition~\ref{prop alg gives rad} every factor of $R$ is either a single variable or a quadratic factor coming from two propagators supported on a common edge and hence every factor of $R$ divides $R(w)$.
+Finally, since $R$ is squarefree and monic, this implies that $R(W)$ is an integer multiple of $R$.
+\end{proof}
+
+***explain why this result was interesting***
 

### 2018-06-27 General WLD combinatorics.tex
some pictures added and material involving protecting sets fixed

@@
 \pgfmathsetmacro{\angle}{360/\n}
+\draw (0,0) circle (\radius);
     \foreach \i in {1,2,...,\n} {
-      \pgfmathsetmacro{\x}{\angle*\i}
-        \draw[-,shorten >=-\radius*0.1 cm,shorten <=-\radius*0.1 cm]  (\x:\radius cm)-- (\x + \angle: \radius cm);
+      \draw (\angle*\i:\radius) node {$\bullet$};
+       %\pgfmathsetmacro{\x}{\angle*\i}
+       %\draw[-,shorten >=-\radius*0.1 cm,shorten <=-\radius*0.1 cm]  (\x:\radius cm)-- (\x + \angle: \radius cm);
     }
 
-\draw (\angle:\radius) node {$\bullet$};
+}
+
+\newcommand{\drawpolypart}[2]{
+\pgfmathsetmacro{\n}{#1}
+\pgfmathsetmacro{\radius}{#2}
+\pgfmathsetmacro{\angle}{360/\n}
+    \foreach \i in {1,2,...,\n} {
+      \draw (\angle*\i+ \angle/2:\radius) node {$\bullet$};
+      \pgfmathsetmacro{\x}{\angle*\i - \angle/2}
+      \pgfmathsetmacro{\concave}{((\n-1.5)/\n)}
+      \draw (\x:\radius cm) .. controls (\angle *\i: \concave* \radius cm) .. (\x + \angle:\radius cm);
+      %\draw (\angle *\i: .8* \radius cm) node {$\bullet$};
+    }
+
 }
@@
 \begin{scope}
-\clip (\angle*\r:\radius) -- (\angle + \angle*\r:\radius) -- (\angle*\s:\radius) -- (\angle + \angle*\s:\radius) -- (\angle*\r:\radius);
+%\clip (\angle*\r:\radius) -- (\angle + \angle*\r:\radius) -- (\angle*\s:\radius) -- (\angle + \angle*\s:\radius) -- (\angle*\r:\radius);
 \draw[propagator] (\angle*\r + \angle/2 + \bumpr*\perturbe:\radius) -- (\angle*\s + \angle/2 + \bumps*\perturbe:\radius);
+\end{scope}
+}
+
+\newcommand{\drawlabeledprop}[5]{
+\pgfmathsetmacro{\r}{#1}
+\pgfmathsetmacro{\bumpr}{#2}
+\pgfmathsetmacro{\s}{#3}
+\pgfmathsetmacro{\bumps}{#4}
+\pgfmathsetmacro{\perturbe}{\angle/\n}
+
+\begin{scope}
+%\clip (\angle*\r:\radius) -- (\angle + \angle*\r:\radius) -- (\angle*\s:\radius) -- (\angle + \angle*\s:\radius) -- (\angle*\r:\radius);
+\draw[propagator] (\angle*\r + \angle/2 + \bumpr*\perturbe:\radius) -- (\angle*\s + \angle/2 + \bumps*\perturbe:\radius) node[midway, below] {#5};
+\end{scope}
+}
+
+\newcommand{\drawchord}[2]{
+\pgfmathsetmacro{\r}{#1}
+\pgfmathsetmacro{\s}{#2}
+
+\begin{scope}
+%\clip (\angle*\r:\radius) -- (\angle + \angle*\r:\radius) -- (\angle*\s:\radius) -- (\angle + \angle*\s:\radius) -- (\angle*\r:\radius);
+\draw (\angle*\r + \angle/2:\radius) -- (\angle*\s + \angle/2:\radius);
 \end{scope}
@@
   \pgfmathsetmacro{\x}{\angle*\i}
+  \draw (\x:\radius*1.15) node {\footnotesize \i};
+}
+}
+
+\newcommand{\drawnumbersshift}{
+  \foreach \i in {1,2,...,\n} {
+  \pgfmathsetmacro{\x}{\angle*\i + \angle/2}
   \draw (\x:\radius*1.15) node {\footnotesize \i};
@@
 
-\begin{eg}
+\begin{eg} \label{eg:equivdiags}
 Note that since this is an equivalence relation, we may find that two Wilson loop diagrams are equivalent, even if they do not have complements of (non-trivial) exact subdiagrams in common.
@@
 \begin{eg}
-For example, ordering the propagators of $W_1$ above as follows: \bas (1,4), \, (2,4), \, (5,7), \, (5,8) \eas we may write
+For example, ordering the propagators of $W_1$ from Example \ref{eg:equivdiags}: \bas (1,4), \, (2,4), \, (5,7), \, (5,8) \eas we may write
 \bas C(W_1) = \left(
@@
 
-***draw some examples***
+\begin{eg}\label{WLDtopolygonpartition}
+In this example we return to the Wilson loop diagrams in Example \ref{eg:equivdiags}. We can pair diagrams with their polygon partitions as follows:
+\bas W_1 = \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
+	\begin{scope}
+	\drawWLD{8}{1.5}
+	\drawnumbers
+	\drawprop{1}{0}{4}{0}
+	\drawprop{2}{0}{4}{-1}
+    \drawprop{5}{0}{8}{0}
+    \drawprop{5}{1}{7}{0}
+		\end{scope}
+	\end{tikzpicture} \quad; \quad
+\tau(W_1) = \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
+	\begin{scope}
+	\drawpolypart{8}{1.5}
+    \drawnumbersshift
+    \drawchord{1}{4}
+    \drawchord{2}{4}
+    \drawchord{5}{8}
+    \drawchord{5}{7}
+	\end{scope}
+	\end{tikzpicture}
+\eas and
+\bas W_3 = \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
+	\begin{scope}
+	\drawWLD{8}{1.5}
+	\drawnumbers
+    \drawprop{1}{0}{4}{0}
+	\drawprop{1}{1}{3}{0}
+    \drawprop{5}{0}{8}{0}
+    \drawprop{6}{0}{8}{-1}	
+		\end{scope}
+	\end{tikzpicture}\quad; \quad
+\tau(W_3) = \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
+	\begin{scope}
+	\drawpolypart{8}{1.5}
+    \drawnumbersshift
+    \drawchord{1}{4}
+    \drawchord{1}{3}
+    \drawchord{5}{8}
+    \drawchord{6}{8}
+	\end{scope}
+	\end{tikzpicture} .
+\eas
+
+\end{eg}
 
@@
 
-***draw an example***
+\begin{eg} \label{eg: unique decomposition} For the Wilson loop diagrams and polygon partitions in example \ref{WLDtopolygonpartition}, the vertex sets $\{1, 2, 3,4\}$ and $\{5, 6, 7, 8\}$ are maximal triangulated pieces for both $\tau(W_1)$ and $\tau(W_3)$.
+The vertex set $\{4,5, 8, 1\}$ is not a triangulation in either polygon partition.
+\note{do we want a picture of a dual tree here?
+Being lazy}
+\end{eg}
 
@@
 
-If $n=2$, then $t$ has two connected componenents. Therefore, $t$ corresponds to a propagator that connects two non-adjacent edges. Therefore, the trivial triangulation is a trivial exact subdiagram.
+If $n=2$, then $t$ has two connected components. Therefore, $t$ corresponds to a propagator that connects two non-adjacent edges. Therefore, the trivial triangulation is a trivial exact subdiagram.
 
@@
 \end{enumerate}
-\end{algorithm} \note{I don't like how this is written. Any ideas?}
+\end{algorithm}
 
@@
 Let $W = (\cP,n)$ be an admissible diagram and $a \in[n]$ a vertex.
-For $p= (i,j) \in \cP$ an a propagator of $W$  and $v \in \{i, j\}$ (or $w \in \{i+1, j+1\}$)a vertex of $W$, let $P_{v}$ (or $P_w$) to be a \emph{protecting set of $p$ at $v$ (or $w$) at $a$} be a set of up to $3$ propagators defined as follows: \begin{enumerate}
-\item Work under the linear order on $[n]$, $<_{v+1}$ or $<_w$, every propagator is now written as $p = (i_p, j_p)$ such that $i_p <_{v+1} j_p$.
-\item There is a propagator $s_1 \in P_v$ and $s_4 \in P_w$ defined such that $s_4 = (i_{s_4}, v)$ and $s_1 = (i_{s_1}, v)$. One may also have $s_1 = (i_{s_1}, v-1)$. Furthermore, $s_m \in [i_p, v]$.
-\item For the given $a$, either $a-3 <_{v+1} i_{s_1}$ or there exist $2$ propagators $s_2$ and $s_3 \in P_v$ such that $s_3 = (i_{s_3}, i_{s_1})$ and $s_2 = (i_{s_2}, i_{s_1})$.
-One may also have $s_2 = (i_{s_2}, i_{s_1}-1)$.
-Furthermore, $a-3 <_{v+1} s_m$.\end{enumerate}
+For $p= (i,j) \in \cP$ an a propagator of $W$  and $v \in \{i, j\}$ a vertex of $W$, let $P_{v}(p)$ or $P_{v+1}(p)$ to be two \emph{protecting sets of $p$ at $v$ and ${v+1}$} be a set of propagators defined as follows: \begin{enumerate}
+\item Work under the linear order on $[n]$, $<_{v+1}$, every propagator is now written as $p = (i_p, j_p)$ such that $i_p <_{v+1} j_p$.
+\item If there is a propagator $s_1 \in \cP$ such that $s_1 = (i_{s_1}, v)$ or $s_1 = (i_{s_1}, v-1)$, then $s_1 \in P_v(p)$.
+\item If $s_1$ as above does not exists, then $P_v(p) = \emptyset$.
+In this case, $P_w(p) = \emptyset$.
+When $P_v(p) \neq \emptyset$, if there exists a propagator $t_1 \in \cP$ defined such that $t_1 = (i_{t_1}, v)$ and $s_1 = (i_{s_1}, v)$ with $i_p <_{v+1} i_{t_1} <_{v+1} i_{s_1}$, $P_w(p) = t_1$.
+\item If $s_1 = (i_{s_1}, v)$ then \bas P_v(p)=  \begin{cases} \{s_1\} \cup P_{i_{s_1}}(s_1) \cup P_{i_{s_1}+1}(s_1) & \textrm{ if } P_{i_{s_1}+1}(s_1) \neq \emptyset \\ s_1 &  \textrm{ else } \end{cases}.
+\eas  If $s_1 = (i_{s_1}, v-1)$ then \bas P_v(p)=  \begin{cases}  \emptyset & \textrm{ if } P_{v-1}(s_1) = \emptyset \\ \{s_1\} \cup P_{v-1}(s_1) & \textrm{ else } \end{cases} \eas.
+\end{enumerate}
 \end{dfn}
+
+The protective sets $P_\cdot(p)$ are designed to prevent $p$ from contributing the vertex indicated in the subscript at certain points in the Grassmann Necklace, $I_a$.
+Write $P_v(p) = \{s_1, \ldots s_r, t_2,  \ldots t_r\}$ with the $t_x = P_{i_{s_{x-1}}+1}(s_{x-1})$ and $s_x \in P_{i_{s_{x-1}}}(s_{x-1})$ for $x \geq 2$.
+We place the restrictions on the vertex $a$ as follows: \begin{enumerate} \item $P_v$ prevents $p$ from contributing to $I_a$ if \bas i_{s_r}  <_{v+1} a-1 <_{v+1} v\eas \item $P_{v+1}(p)$ prevents $p$ from contributing to $I_a$ only if $P_v(p)$ prevents $p$ from contributing $v$ to $I_a$.
+\end{enumerate}
+
+\begin{eg} \label{eg: protective sets}
+Consider the admissible Wilson loop diagram
+\bas W=\begin{tikzpicture}[rotate=120,baseline=(current bounding box.east)]
+	\begin{scope}
+	\drawWLD{17}{3}
+	\drawnumbers
+	\drawprop{1}{0}{16}{0}
+	\drawlabeledprop{2}{0}{15}{1}{p}
+    \drawprop{6}{2}{15}{0}
+    \drawprop{3}{0}{6}{1}
+    \drawprop{4}{0}{6}{0}
+    \drawprop{7}{0}{11}{0}
+    \drawprop{8}{0}{10}{0}
+    \drawprop{11}{1}{14}{1}
+    \drawprop{12}{0}{14}{0}
+		\end{scope}
+	\end{tikzpicture}
+\eas Consider the two sets of propagators $Q = \{(3, 6), (4, 6), (6,15)\}$ and $R = \{ (7, 11), (8, 10), (11, 14), (12, 14)\}$.
+The propagator $p = (2, 15)$ is protected at $a = 5$ from contributing $15$ to $I_5$ by the set $P_{15} = Q$.
+There is no set preventing $p$ from contributing $16$ to $I_{15}$.
+At $a = 9$, the set $P_{15} = \{(6,15)\} \subset Q$.
+We may just as easily right $P_{15} = Q$, though the other two propagators in the set prove unnecessary to keep $p$ from contributing $15$ to $I_{9}$.
+At $a = 14$, both $P_{15}$ and $P_{16}$ exists, with $P_{15} = \{(11, 14), (12, 14)\} \subset R $ and $P_{16}= \{(6,15)\} \subset Q$.
+We may just as easily right $P_{15} = R$ and $P_{16} = R$, though the other two propagators in each set are unnecessary.
+
+Note that for $a=1$, the propagator $p$ contributes $2$ to $I_1$. However, in this case, we say that neither $P_{15}$ or $P_{16}$ exist.
+\end{eg}
 
@@
 Let $W = (\cP, n)$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$, and $a \in [n]$ be a vertex.
-If there exists a $P_v$, for $v \in \{i,j\}$, then $p$ does not contribute $v$ to $I_a$.
-If there are two sets $P_v$ and $P_w$, for $w \in \{i+1, j+1\}$, then $p$ does not contribute $w$ to $I_a$.
+For $v \in \{i,j\}$, if $P_v(p) \neq \emptyset$, write $P_v(p) = \{s_1 \ldots s_r, t_2, \ldots t_r\}$ as above.
+Then $p$ does not contribute $v$ to $I_a$ if $i_{s_r} +1 <_{v+1} a <_{v+1} v+1 $.
+If both $P_v(p)$ and $P_{v+1}(p)$ are non empty, then $p$ also does not contribute $v+1$ to $I_a$.
 \end{lem}
@@
 \begin{proof}
-We consider first the case of $p$ not contributing $v$ to $I_a$.
-
-The set $P_v$ is constructed such that, $s_1$ if it exists at step $v$ of Algorithm \ref{alg:put GN on WLD}, prevents $p$ from contributing $v$ to $I_a$.
-By the positioning of $a$, either the algorithm does not encounter the propagators $s_1$ before vertex $v$ or $v-1$, or it encounters it at $i_{s_1}$.
-In this case, the existence of $s_2$ and $s_3$ prevent $s_1$ from contributing at vertices $i_{s_1}$ or $i_{s_1}+1$.
-Therefore, $s_1$ remains in the diagram at step $v$.
-
-If both $P_v$ and $P_w$ exists, then if $s_1$ and $s_3$ exist at step $v$ of Algorithm \ref{alg:put GN on WLD}, prevents $p$ from contributing $v$ and $w$ to $I_a$.
-By the positioning of $a$, either the algorithm does not encounter the propagators $s_1$ and $s_4$ before vertex $v$ or $v-1$, or it encounters only $s_1$ before $v$ or $v-1$.
-By the above argument, $s_1$ remains in the diagram at step $v$.
-Finally, the algorithm may encounter $s_4$ at $i_{s_4}$.
-In this case, the existence of $s_5$ and $s_6$ prevent $s_4$ from contributing at vertices $i_{s_4}$ or $i_{s_4}+1$.
-Therefore, $s_4$ remains in the diagram at step $v$.
-Thereofre, in this case, $p$ cannot contribute either $v$ or $v+1$ to $I_a$.
-\end{proof}
-
-There is an easy corrollary to this, describing when propagators cannot contribute certain vertices to elements of the Grassman necklace.
+Note that if $s_1 \in P_v(p)$ exists at step $v$ of Algorithm \ref{alg:put GN on WLD}, then $p$ cannot contribute $p$ to $I_a$.
+Further, if $P_{v+1}(p) \neq \emptyset$, $p$ cannot contribute $v+1$ to $I_a$ either.
+
+Next we show that if $P_v(p)$ is as above, with $i_{s_r}+1 <_{v+1} a$, then the propagator $s_1$ exists at step $v$ of Algorithm \ref{alg:put GN on WLD}.
+Let $x$ be the largest integer that such that $a <_{v_1} j_{x}+1$.
+Then $s_x$ cannot contribute to $I_a$ before vertex $v$.
+By construction $P_{i_{s_x}+1}(s_{x-1})\subset P_v(p)$.
+Therefore, $s_{x-1}$ does not contribute $i_{s_x}+1$ to $I_a$.
+Thus we conclude that $s_1$ does not contribute $i_{s_1}$ or $i_{s_1}+1$ to $I_a$.
+In other words, $s_1$ has not been removed from the diagram at vertex $v$.
+
+\end{proof}
+
+Thus we say that $P_v(p)$ protects $p$ at $v$ from $a$, for $a \in [i_{s_r}+2, v]$. There is an easy corollary to this, describing when such a protecting set cannot exist.
 
@@
 Picking a $v \in \{i, j\}$ write $p = (i_p, j_p)$ with $i_p <_{v+1} j_p$.
-If $a \in [j_p+1, i_p+1]$ then no protecting set $P_v$ or $P_w$ can protect $p$ at $v$ or $v+1$ from $a$.
+If $a \in [j_p+1, i_p+1]$ then there can be no protecting set $P_v$ or $P_{v+1}$ protecting $p$ at $v$ or $v+1$ from $a$.
 \end{cor}
@@
 \begin{proof}
-Since $W$ is admissible, it cannot have crossing propagators. Therefore niether $P_v$ cannot have the requisite propagator $s$ with $a-3 <_{v+1} i_s$.
-\end{proof}
-
-The converse, howevever requires an extra condition.
+Since $W$ is admissible, it cannot have crossing propagators. Therefore neither $P_v$ cannot have the requisite propagator $s_r$ with $i_{s_r}+1  <_{v+1} a$.
+\end{proof}
+
+The converse, however requires an extra condition.
 
 \begin{lem} \label{protect conv lem}
-For $W = (\cP, n)$, $p = (i,j)$, and $v \in \{i, j\}$, $w \in \{i+1, j+1\}$ and $ a \in [n]$ a vertex of $W$, if $v$ (resp.
-$w$) is the first vertex of $V_p$ in the $<_a$ order such that $P_v$ (resp.
-neither $P_v$ nor $P_w$) does not exsist, then $p$ contributes $v$ (resp.
-$w$) to $I_a$.
+For $W = (\cP, n)$, $p = (i,j)$, and $v \in \{i, j\}$ and $ a \in [n]$ a vertex of $W$, if $v$ (resp.
+$v+1$) is the first vertex of $V_p$ in the $<_a$ order such that $P_v$ (resp.
+neither $P_v$ nor $P_{v+1}$) does not exist, then $p$ contributes $v$ (resp.
+$v+1$) to $I_a$.
 \end{lem}
@@
 \begin{proof}
-If $p$ doesn't contribute $v$ or $w$ $I_a$, then either $p$ contributes a different supporting vertex $u$ earlier in the $<_a$ order or there is a propagator at $s_1$ preventing $p$ from contributing $v$ (or $w$) to $I_a$, or there is a pair of propagators $s_1$ (resp.
-and $s_4$) preventing $p$ from contributing $w$, or $v$, at $I_a$.
-
-If there is a propagator $s_1 \in \cP$ that are still in the diagram at step $v$, (write them $s_1 = (i_{s_1}, j_{s_1})$ with $j_{s_1} \in \{v, v-1\}$), then $s_1$ did not contribute $i_{s_1}$ or $i_{s_1} +1 $ to $I_a$.
-Therefore, $s_1$ cannot contribute $i_{s_1}$ $i_{s_1}+1$ to $I_a$.
-In other words, either $a-3 <_{v+1} i_{s_1}$ or there must be two other propagators $s_2 = (i_{s_2}, j_{s_2})$ and $s_3 = (i_{s_3}, j_{s_3})$, with $j_{s_2} \in \{i_{s_1}, i_{s_1}-1\}$ and $i_{s_3} <_{s_1} i_{s_2} <_{s_1} j_{s_2} \leq_{s_1} j_{s_3} = j_{s_1}$ that prevent this.
-We show that, if $a-3 \not <_{v+1} i_{s_1}$, then $a-3 <_{v+1} i_{s_2} <_{v+1} s_3$.
-That is, there is a set $P_v$ preventing $p$ from contributing $v$.
-
-The argument for showing that there must be two sets $P_v$ and $P_w$ is simlar, and is not made explicit here.
-
-We proceed by contradiction.
-Suppose $a-3 \not <_{v+1} i_{s_2}$.
-Then, there exists two propagators $s_4$ and $s_5$ such that $s_4 = (i_{s_4}, j_{s_4})$ and $s_5 = (i_{s_5}, j_{s_5})$, with $j_{s_4} \in \{i_{s_2}, i_{s_2}-1\}$ and $i_{s_5} <_{s_2} i_{s_4} <_{s_2} j_{s_4} \leq_{s_2} j_{s_5} = j_{s_2}$.
-If $a-3 <_{v+1} i_{s_4} <_{v+1} s_5$, we may assume without loss of generality that there are no futher propagators of the form $t = (i_t, j_t)$ with $j_t \in \{i_{s_1}, j_{s_1}-1\}$ or $i_t \in [ i_{s_4}, i_{s_1}]$.
-Otherwise, one may replace $p$ with $s_1$ in this argument.
-Therefore, $s_1$ contributes $i_{s_1}$ to $I_a$, which is a contradiction.
-Therefore, we must again suppose that $a-3 \not <_{v+1} i_{s_4}$.
-
-In order for $s_1$ to exists at step $v$ of algorithm \ref{Alg:put GN on WLD}, one must continue to find pairs of propagators $s_{m'}$, $s_{m'+1}$ in $\cP$ that sheild the initial endpoint of a previously defined propagator, $s_m$.
-There are three cases to consider.
-Let $s_k$ indicate a propagator identified at an earlier stage of this construction where $i_{p_0} = \min{i_p, a}$.
-
+Write $p = (i_p, j_p)$ with $i_p <_{v+1} j_p$.
+
+If $p$ doesn't contribute $v$ (or $v+1$) to $I_a$, then either $p$ contributes a different supporting vertex $u$ earlier in the $<_a$ order or there is a propagator $s_1$ at step $v$ of the algorithm \ref{alg:put GN on WLD} preventing $p$ from contributing $v$ to $I_a$, (or there are a pair of propagators $s_1$ and $t_1$ at step $v$ preventing $p$ from contributing $v+1$ at $I_a$.)
+
+If there are propagators $s_1, t_1 \in \cP$ that are still in the diagram at step $v$, (write them $s_1 = (i_{s_1}, j_{s_1})$, and $t_1 = (i_{t_1}, j_{t_1})$) with $j_{s_1} \in \{v, v-1\}$, and $i_p \leq_{v+1} i_{t_1} <_v i_{s_1} <_v j_{s_1} \leq_{v} j_{t_1} = v$) then $s_1$ or $t_1$ did not contribute $i_{s_1}$ or  $i_{s_1} +1 $ (resp.
+$i_{t_1}$ or $i_{t_1}+1$) to $I_a$.
+Then one of the following three situations hold: \begin{enumerate} \item $i_{s_1}+1 <_{v+1} a$ and $j_{s_1} = v$: In this case, $s_1$ cannot be removed until $v$.
+\item $i_{s_1}+1 <_{v+1} a$ and $j_{s_1} = v-1$: in this case there exists a propagator $s_2 = (i_{s_2}, j_{s_2})$ with $i_{s_1} \leq_{v+1} i_{s_2} <_{v+1} j_{s_2}$ and $j_{s_2} \in \{j_{s_1}-1, j_{s_1}\}$.
+\item $i_{s_1}+1 \not <_{v+1} a$ and $j_{s_1} = v$: and there must be two other propagators $s_2 = (i_{s_2}, j_{s_2})$ and $t_2 = (i_{t_2}, j_{t_2})$, with $j_{s_2} \in \{i_{s_1}, i_{s_1}-1\}$ and $i_{s_1} \leq_{v+1} i_{t_2} <_{v+1} i_{s_2} <_{v+1} j_{s_2} \leq_{v+1} j_{t_2} = j_{s_1}$   \end{enumerate}
+
+However, now one must ensure that the newly identified propagators $s_2$ and $t_3$ do not contribute to $I_a$ before $i_{s_1}$.
+One does this by a similar construction to above.
+In this manner, we begin to build the sets $P_v(p)$ and $P_{v+1}(p)$.
+By finiteness and admissiblity of the Wilson loop diagram, both these sets are finite; one cannot continue to add propagators $s_i$, $t_i$ ad infinitum.
+
+We claim that this implies that at some point there is a terminal propagator, $s_m \in P_v(p)$ such that $i_{s_m} + 1 <_{v+1} a$, and \bas  \textrm{ either }= \begin{cases} j_{s_m}=i_{s_{m-1}} & \textrm{ }\\ j_{s_m}=j_{s_{m-1}} & \textrm{ } \end{cases} .\eas We show that all other possibilities lead to a contradiction.
+For the remainder of this proof, indicate by $p_k$ some propagator identified at an earlier stage of this construction.
+That is, for $0 < k < m$, $p_k \in \{s_k, t_k\}$.
+Futher define $p_0 = p$.
+
+%\begin{cases} j_{s_{m}=i_{s_{m-1}} & \textrm{ } \\  j_{s_m}=j_{s_{m-1}} & \text{ }\end{cases}
+
+If $j_{s_m} \in \{i_{s_{m-1}}-1, j_{s_{m-1}}-1\}$, then, this cannot be the final propagator added to $P_v(p)$, as one would need a means of preventing $s_m$ from contributing $i_{s_{m-1}}-1$ or $j_{s_{m-1}}-1$ to $I_a$.
+
+If $i_{s_m} + 1 \not <_{v+1} a$, then there are two.
  \begin{description}
-\item[$i_{s_m} = i_{p_k}+2$] By admissibility, there is not room to place both the propagators $s_{m'}$, and $s_{m'+1}$.
+
+\item[$j_{s_m} = i_{s_{m-1}}$ and $i_{s_m} \in \{i_{p_k}+2, i_{p_k}+1\}$] for some $k<m$.
+By admissibility, there is not room to place both the propagators $s_{m+1}$, and $t_{m+1}$.
 Thus $s_m$ is removed at the step $i_{s_m}$ or $i_{s_m} + 1$.
 Therefore, $s_1$ contributes at either $i_{s_1}$ or $i_{s_1}+1$.
- \item[$i_{s_m} = i_{p_k}+1$] By admissibility, there is not room to place either the propagators $s_{m'}$, or $s_{m'+1}$.
-Thus $s_m$ is removed at the step $i_{s_m}$.
-Therefore, $s_1$ contributes at either $i_{s_1}$ or $i_{s_1}+1$.
- \item[$i_{t_m} = i_{p_k}$] Since $k < m$, the propagator $p_k$ is not removed at step $i_{p_k}$ or $i_{p_k}+1$.
-Therefore neither is $s_{m'}$.
-Furthermore, there cannot be propagators that prevent $s_{m'}$ from being removed at $j_{s_m}$ or $j_{s_m}+1$.
-Otherwise, we could replace $p$ with $sm_{m'}$ and repeat this argument.
-Since $\cP$ is finite, this replacement process must terminate, forcing $s_{m'}$ to contribute $j_{s_m}$ or $j_{s_m}+1$, and thereby, $s_1$ contributes at either $i_{s_1}$ or $i_{s_1}+1$.
- \end{description}
+This leads to a contradiction.
+\item[$j_{s_m} = i_{s_{m-1}}$ and $i_{s_m} = i_{p_k}+2$] for some $k<m$. This requires either crossing propagators or propagators starting and ending at the same edge, which violates admissibility.
+ \end{description} \note{correct but clear as mud? Help?}
 \end{proof}
@@
 
-Since $p$ is not removed by step $j+1$, by Lemma \ref{protect dfn lem} there are $4$ protecting sets, $P_i,P_{i+1}, P_{j}$ , and $P_{j+1}$ respectively, allowing $p$ to remain after $n$ steps.
+Since $p$ is not removed by step $j+1$, by Lemma \ref{protecting lem} there are $4$ protecting sets, $P_i,P_{i+1}, P_{j}$ , and $P_{j+1}$ respectively, allowing $p$ to remain after $n$ steps.
 
@@
 \begin{lem} \label{vertex cyclic int lem}
-For every $v \in V_p$, there is a non-empty cyclic interval such that $p$ contributes $v$ to all $I_{a}$ for in said interval.
+For every $v \in V_p$, Let $A_v \subset [n]$ be the set of vertices where $p$ contributes $v$ to $I_a$. Then $A_v$ is a non-empty cyclic interval.
 \end{lem}
@@
 
-Let $k_1 \ldots k_r$ be the set of propagators ending on edge $j$ or $j-1$, ordered such that $k_1$ is the first propagators clockwise from $p$, and $k_r$ is the clockwisemost propagator on edge $j-1$.
-For each $k_x$, write $P_{x} = \{k_x, s_x, t_x\}$, where $s_x$ and $t_x$, if they  exist, to be the two clockwise most propagators preventing $k_x$ from contributing $j$ to $I_{i+2}$.
-Similarly, let $l_1 \ldots l_m$ be the set of propagators ending on edge $i$ or $i-1$, ordered such that $l_1$ is the first propagators clockwise from $p$, and $l_m$ is the clockwisemost propagator on edge $i-1$.
-For each $l_y$, write $Q_{y} = \{l_x, s_y, t_y\}$, where $s_y$ and $t_y$, if they  exist, to be the two clockwise most propagators preventing $l_y$ from contributing $i$ to $I_{j+2}$.
-
-Define $b_1 = \min\{k_1+1, s_1+1\}$.
+Let $k_1 \ldots k_r$ be the set of propagators of the form $k_x = (i_{k_x}, j)$, with $i <_{j+1} k_1 <_{j+1} \ldots k_r <_{j+1} j$.
+Write $k_{r+1}$ to be the counterclockwise most propagator with an end on the edge $j-1$, if it exists.
+If $r \geq 2$ or $r+1 = 2$, then both $P_j(p)$ and $P_{j+1}(p)$ exists for some subset of $a \in [n]$.
+If $r=1$ or $r+1= 2$ then only $P_j(p)$ exists.
+Otherwise, $P_j(p) = \emptyset$.
+
+Consider a protecting set $P_j(p) \subset \cP$ such that $k_1 \in P_j(p)$, if it exists.
+Write it \bas P_j(p) = \{s_1 \ldots s_r, t_2, \ldots t_r\} \;.\eas Define $b_1 = i_{s_r}+1$.
+By construction, $P_j(p)$ prevents $p$ from contributing $j$ to $I_a$ for all $a \in [b_1+1, j]$.
 We see that, if $r >0$, for all $a \in [i+2, b_1]$, $p$ contributes $j$ to $I_a$.
-(If $b_1 <_{j+1} i+2$ then this interval is empty.) This is because in this range, $j$ is the first vertex of $p$ encountered by Algorithm \ref{Alg: put GN on WLD}.
-Furthermore, by Lemma \ref{protect conv lem}, and definition \ref{protect dfn} if $b_1 \not <_{j+1} i+2$ $P_1$ does not protect $p$ at $j$ for $a$ in this range.
+(\hlfix{Note that by construction, one cannot have $i_{s_r}+1 <_{j+1} i+2$.}{verify}) This is because in this range, $j$ is the first vertex of $p$ encountered by Algorithm \ref{Alg: put GN on WLD}.
+Furthermore, by Lemma \ref{protect conv lem}, and definition \ref{protect dfn} if $i_{s_r}+1 \not <_{j+1} i+2$ $P_1$ does not protect $p$ at $j$ for $a$ in this range.
 If $r = 0$ then $p$ contributes $j$ for all $a \in [i+2, j]$.
-In this case, we say $b_1= j$.
-
-Define $b_2 = \min{k_2+1, s_2+1}$.
-If $r > 1$, and $j_{k_2}=j$, for all $a \in [b_1+1, b_2]$ $p$ contributes $j+1$ to $I_a$.
-In this range, $P_1$ is a protective set for $p$ at $j$, but $P_2$ is not a protective set for $j+1$ in this range.
+In this case, we say $b_1 = j$.
+
+Now suppose $r$ is such that both $P_j(p)$ and $P_{j+1}(p)$ exists for some $a$.
+This time $k_2 \subset P_j(p)$.
+Define $b_2 = i_{s_r}+1$, where now we use $s_r$ to indicate the last propagator in this new protecting set.
+By construction, $P_{j+1}(p)$ prevents $p$ from contributing $j+1$ to $I_a$ for all $a \in [b_2+2, j+1]$.
+Therefore, if both protecting sets exist, for all $a \in [b_1+1, b_2]$ $p$ contributes $j+1$ to $I_a$.
+This is exactly the range in which there is exactly one valid protecting set.
 Therefore, in this range, $j+1$ is the first vertex of $p$ without a protective set.
-If the stated condidtions do not hold, then $p$ contributes $j+1$ for all $a \in [b_1 +1, j+1]$.
+If there is no $a$ such that both $P_j(p)$ and $P_{j+1}(p)$ do not hold, then  $p$ contributes $j+1$ for all $a \in [b_1 +1, j+1]$.
 
 Finally, for $r > 1$, and $j_{k_2}=j$,$a \in [b2+1, j+1]$, $p$ contributes $i$ to $I_a$.
-Again, for all $a$ in this range, both $P_1$ and $P_2$ are protective sets of $p$ at $j$ and $j+1$.
-Furthermore, by Corrollary \ref{protect cor}, no set $Q_y$ can be a protective set for $p$ at $i$ or $i+1$ for $a$ in this range.
+Again, for all $a$ in this range, both sets $P_j(p)$ and $P_{j+1}(p)$ protect $p$ at $j$ and $j+1$ from $a$.
+Furthermore, by Corrollary \ref{protect cor}, there can be no protective sets of $i$ or $i+1$ in this range.
 
@@
 \end{proof}
-
-{\color{red}For $W = (\cP, n)$, let $W' = (P, V_P)$ be a subdiagram.
-Write $\cI^{W'}$ be the set of $|P|$ tuples defined by \ref{alg:put GN on WLD} on $W'$.
-Furthermore, for any $p = (i, j) \in \cP$, write $\cP_{i,j} =  \{ q = (i_q, j_q)\in \cP | i \leq_i i_q <_i j_q \leq_i j\}$ to be the set of propagators supported on the cyclic interval $[i, j]$.
-Similarly, write $\cP_{j,i} =  \{ q = (i_q, j_q)\in \cP | j \leq_j i_q <_j j_q \leq_j i\}$ to be the set of propagators supported on the cyclic interval $[j,i]$.
-Note that $p = \cP_{i,j} \cap \cP_{j,i}$.}
-
-We then have the following corrollary:
-
-\begin{cor} \label{rightmost prop last cor}
-Given any Wilson loop diagram, $W = (\cP, n)$, and $p = (i,j) \in \cP$, consider the subdiagrams $W_L  = (\cP_{i,j}, n)$ and $W_R = (\cP_{j,i}, n)$.
-Then the propagator $p$ contributes last to the entries $I_{i+2}^{W_L}$ and $I_{j+2}^{W_R}$ respectively.
-\end{cor} \todo{do you need this}
-
-{\color{red}\begin{proof}
-The support vertices of $p$, $V_p = \{i, i+1, j, j+1\}$ are the last four vertices supporting any propagators at all in the $<_{i+2}$ linear order on $[n]$.
-Since $p$ contributes to $I_{i+2}^{W_L}$, it must contribute at one of these $4$ vertices.
-
-The only possible configuration in which this result cannot hold is if $i$ or $i+1$ were in $I_{i+2}^{W_L}$ but not contributed by $p$.
-
-\end{proof}}\todo{currently rubbish}
 

### 2018-07-30 General WLD combinatorics.tex
tidied up and edited section 4

@@
 This paper studies the combinatorics of Wilson Loop Diagrams.
-\section{Wilson Loop diagrams}
+\section{Wilson Loop diagrams}\label{section background}
 
@@
 
-\section{Geometry of Wilson Loop diagram}
+\section{Geometry of Wilson Loop diagram}\label{sec GN algorithm}
 Since Wilson loop diagrams correspond to positroids, it is natural to understand the subspace of $\Gr(|\cP|, n)$ they define.
@@
 
-Put some exposition here about Theorem~\ref{thm denom}.
-
-We can also use the ideas of the above constructions to understand the denominator of the integral $I(W)$.
+\subsection{Some definitions and results that should probably be moved to section 3 but I don't know if anyone's editing that right now}
+
+It will often be useful to refer to the vertex label contributed by a propagator to a Grassmann necklace term.
+Notationally, we represent this by allowing the $I_i$ symbol to represent a function as well as a set, as follows:
+\begin{dfn}\label{def I_i as a function}
+Let $W = (\cP, n)$ be an admissible Wilson loop diagram. For each $i \in \interval{1}{n}$, define a function $I_i : \cP \longrightarrow \interval{1}{n}$ by
+\[I_i(p) := \text{the vertex label that $p$ contributes to $I_i$ in Algorithm~\ref{alg:put GN on WLD},}\]
+for each $p \in \cP$.
+\end{dfn}
+\todo{Depending where this ends up, possibly include an example here.}
+
+\begin{dfn}\label{props inside p}
+Let $p$ be a propagator supported on $(i,j)$.
+The region bounded by $p$ and the edge of the Wilson loop diagram from $i$ to $j+1$ is refered to as the region {\bf inside} $p$, and the complement is the region {\bf outside }$p$.
+The set of propagators inside (resp.
+outside) $p$ are those lying in the region inside (resp.
+outside) $p$, excluding $p$ itself.
+\end{dfn}
+Note that this depends on the order of $i$ and $j$: if we view $p$ as supported on $(j,i)$ then the regions inside and outside $p$ are swapped.
+
+\begin{lem}\label{lem no fourth vertex}
+Let $W$ be an admissible Wilson loop diagram containing at least one propagator. For any $i \in [n]$ and for any $p=(a,b)$ with $i\leq_i a <_i b$, we have $I_i(p) \neq b+1$.
+\end{lem}
+\begin{proof}
+Suppose for contradiction that we have $p = (a,b)$ with $i\leq_i a <_i b$ and $I_{i}(p) = b+1$. We may choose $p$ such that $|\interval{a+1}{b}|$ is minimal amongst propagators with this property.
+
+Since $I_i(p) \neq b$, there must exist a propagator $q$ inside of $p$ with $I_i(q) = b$.
+The propagator $q$ cannot end on the edge $(b-1,b)$, as this would contradict the minimality of $p$, so $q = (c,c+1,b,b+1)$ with $a <_i c <_i b$, and $I_i(q) = b$.
+
+In order for $q$ to remain unassigned until vertex $b$, there must be another propagator $r$ with an end on $(c,c+1)$ and $I_i(r) = c+1$; the only way this can occur is if $r$ is outside $q$ but inside $p$.
+Now $r$ contributes its fourth vertex to $I_i$, again contradicting the minimality of $p$.
+\end{proof}
+
+\begin{cor}\label{GN alg well defined}
+If $W$ is an admissible Wilson loop diagram with $k$ propagators, then Algorithm~\ref{alg:put GN on WLD} assigns exactly $k$ vertices to each $I_i$.
+\end{cor}
+\begin{proof}
+It follows from the proof of Lemma~\ref{lem no fourth vertex} that Algorithm~\ref{alg:put GN on WLD} can never reach the fourth vertex of a propagator's support (with respect to the starting vertex).
+Therefore if the algorithm starts at vertex $i$, it must have assigned vertices to all propagators by the time it reaches $i-1$, ensuring that $I_i$ contains exactly $k$ distinct vertices.
+\end{proof}
+
+\begin{cor}\label{no coloops}
+Grassmann necklaces coming from admissible Wilson loop diagrams have no coloops, that is no indices $a$ such that $a \in I_i$ for all $i$.
+\end{cor}
+\begin{proof}
+For any $a \in [n]$, $a-1$ is maximal with respect to the $<_{a}$ order. Therefore there is no propagator $p$ with $I_{a}(p) = a-1$ by Lemma~\ref{lem no fourth vertex}, i.e. $a-1 \not\in I_{a}$.
+\end{proof}
+
+\subsection{actual beginning of section 4; this subsection header can go away once the results above have found their place}
+
+The results of Section~\ref{sec GN algorithm} allow us to relate the position of propagators in a Wilson loop diagram $W$ to minors of $C(W)$, which we use in this section to understand the denominator of the integral $I(W)$ associated to a Wilson loop diagram (see Definition~\ref{def R(W)}).
+
+The main result of this section is Theorem~\ref{thm denom}, which expresses the denominator $R(W)$ in terms of the Grassmann necklace of $W$.
+This simplifies the computation of $R(W)$ and allows us to directly relate the poles of the integral to the combinatorics of the diagram.
+
+We first give an algorithm which extracts the required minors from the Grassmann necklace.
 
 \begin{algorithm}\label{alg WLD to denom via GN}
-Let $W$ be a Wilson loop diagram with $n$ vertices.  Let $C(W)$ be the matrix of $W$ as defined in \eqref{C(W) dfn}.
+Let $W = (\cP,n)$ be a Wilson loop diagram, and let $C(W)$ be the matrix of $W$ as defined in \eqref{C(W) dfn} (see Section~\ref{section background}).
 \begin{itemize}
-  \item For each $i \in \interval{1}{n}$, we construct a factor $r_i$ as follows
+  \item For each $i \in \interval{1}{n}$, we construct a factor $r_i$ as follows:
     \begin{itemize}
-      \item Use Algorithm~\ref{alg:put GN on WLD} to obtain a bijection between the propagators and the $i-1$st Grassmann necklace element, $I_{i-1}$.
+      %\item Use Algorithm~\ref{alg:put GN on WLD} to obtain a bijection between the propagators and the $i-1$st Grassmann necklace element, $I_{i-1}$.
 (By convention set $I_{-1}=I_n$.)  Write $I_{i-1}(p)$ for the vertex associated to propagator $p$ under this bijection.
-      \item Use Algorithm~\ref{alg:put GN on WLD} to obtain a bijection between the propagators and the $i$th Grassmann necklace element, $I_{i}$.
+      %\item Use Algorithm~\ref{alg:put GN on WLD} to obtain a bijection between the propagators and the $i$th Grassmann necklace element, $I_{i}$.
 Write $I_{i}(p)$ for the vertex associated to propagator $p$ under this bijection.
-      \item Let $S_i$ be the set of propagators $p$ such that $I_{i-1}(p) \neq I_{i}(p)$.
-      \item $\Delta_{I_i}$ is the determinant of the $k \times k$ minor of $C(W)$ indicated by $I_i$.
+      \item Let $S_i = \{p \in \cP \ | \ I_{i-1}(p) \neq I_i(p)\}$. (By convention, set $I_{-1} = I_n$.)
+	  \item Write $\Delta_{I_i}$ for the determinant of the $k \times k$ minor of $C(W)$ with columns indexed by $I_i$.
       \item Let $r_i$ be $\Delta_{I_i}$ with all variables from rows associated to $p\not\in S_i$ set to $1$.
     \end{itemize}
-  \item $R = \prod_{i=1}^n r_i$.
+  \item Define $R = \prod_{i=1}^n r_i$.
 \end{itemize}
 \end{algorithm}
+\note{What are we doing about the sign of the determinants?}
 
@@
 \end{figure}
-
-For example consider the Wilson loop diagram in Figure~\ref{fig R eg}.
+\todo{I've named the propagators $p$, $q$, $s$; could whoever codes up the figure please add that?}
+
+\begin{eg}
+Consider the Wilson loop diagram in Figure~\ref{fig R eg}. Assigning propagators $p$, $q$, $s$ to rows $1,2,3$ respectively, we obtain the matrix
 \[
@@
 \]
-The Grassmann necklace is $I_1 = \{1,2,4\}, I_2 = \{2,4,5\}, I_3 = \{4,5,6\}, I_4=\{4,5,6\}, I_5=\{5,6,7\}, I_6 = \{6,7,1\}, I_7=\{7,1,2\}$.
-The bijection between propagators and vertices for each necklace element is also in Figure~\ref{fig R eg}.
-Between $I_1$ and $I_2$, two propagators change which vertex they are assigned to and these are the propagators associated to rows 1 and 2 of $C(W)$ as given above.
-Then
+The Grassmann necklace of this diagram is 
+\begin{gather*}I_1 = \{1,2,4\}, I_2 = \{2,4,5\}, I_3 = \{4,5,6\}, I_4=\{4,5,6\},\\ I_5=\{5,6,7\}, I_6 = \{6,7,1\}, I_7=\{7,1,2\}. \end{gather*}  
+Figure~\ref{fig R eg} also indicates the pairings between propagators and vertices for each $i \in \interval{1}{7}$.
+
+From $I_1$ to $I_2$, the propagators $p$ and $q$ change which vertex they are assigned to but $r$ is assigned to vertex 4 in both, so $S_2 = \{p,q\}$.  Then
 \[
-\Delta_{I_2}=\det\begin{bmatrix} b & 0 & 0 \\ f & 0 & g \\ j & k & l \end{bmatrix} = kgb
+\Delta_{I_2}=\det\begin{bmatrix} b & 0 & 0 \\ f & 0 & g \\ j & k & l \end{bmatrix} = kgb, \qquad r_2 = \det\begin{bmatrix} b & 0 & 0 \\ f & 0 & g \\ 1 & 1 & 1 \end{bmatrix} = gb.
 \]
-and so $r_2 = gb$.
-From $I_2$ to $I_3$ only one propagator changes its vertex association and we get $r_3 = c$.
-$I_3=I_4$ and so $r_4=1$.
-Continuing likewise we get $r_5 = lhd$ and $r_6 = i$.
-From $I_6$ to $I_7$ the propagators associated to the second and third rows change, thus from $\Delta_{I_7} = d(ej-fi)$ we get $r_7 = ej-fi$.
-Note that as proved in the next proposition, this quadratic factor arises when the two edges whose vertex association changed are associated with the two ends of the edge on which they are both supported.
-Finally, $r_1 = (af-be)k$.
-Together we obtain
+where the 1s in the third row of the second matrix correspond to the fact that $I_1(s) = I_2(s)$.  Continuing likewise, we get $r_3 = c$, $r_4=1$ (since $I_4 = I_3$), $r_5 = lhd$, and $r_6 = i$.
+
+At $I_7$ the situation is more complicated: we have $S_7 = \{q,s\}$, so we find that $\Delta_{I_7} = d(ej-fi)$ and $r_7 = ej-fi$.
+This quadratic factor corresponds to the fact that $q$ and $s$ share an edge {\em and} contribute both endpoints of that edge to $I_7$; see Proposition~\ref{prop alg gives rad} below.
+
+Finally, we have $r_1 = (af-be)k$.  Putting everything together, we obtain
 \[
@@
 which is squarefree and contains all factors of $\prod_{i=1}^{n}\Delta_{I_i}$.
+If one were to construct the denominator $R(W)$ associated to this Wilson loop diagram as per Definition~\ref{def R(W)}, we would find that (up to integer multiples) we have $R(W) = R$.
+\end{eg}
 
@@
   \begin{enumerate}
-    \item Each $\Delta_{I_i}$ is homogeneous as is each $r_i$.
+    \item Each $\Delta_{I_i}$ is homogeneous, as is each $r_i$.
     \item Each $\Delta_{I_i}$ splits into linear and quadratic factors.
 All linear factors of  $\Delta_{I_i}$ are single variables and all irreducible quadratic factors are $2\times 2$ determinants of single variables.
-    \item Quadratic factors in $r_i$ arise precisely when propagators $p$ and $q$ are supported on a common edge $(a,b)$ and $I_i(p)=a$, $I_i(q)=b$.
+    \item Quadratic factors in $r_i$ arise precisely when propagators $p$ and $q$ are supported on a common edge $(a,b)$ with $I_i(p)=a$ and $I_i(q)=b$.
     \item $r_i$ divides $\Delta_{I_i}$.
@@
 \begin{enumerate}
-    \item The nonzero entries of $C(W)$ are independent indeterminates and so every $i\times i$ minor of $C(W)$ is homogeneous of degree $i$ or is $0$.
+    \item The nonzero entries of $C(W)$ are independent indeterminates and so every $i\times i$ minor of $C(W)$ is either homogeneous of degree $i$ or is $0$.
 Thus each $\Delta_{I_i}$ is homogeneous.
@@
 
-Proof of claim: By the structure of determinants $\Delta_{I_i} = fg$ where $g$ involves only variables associated to propagators not in $\mathcal{P}'$ and associated to vertices not in $J$.
-Expanding out $fg$, then, we get a signed sum of monomials where in each monomial $f$ contributes those variables associated both to a propagator in $\mathcal{P}'$ and to a vertex in $J$ and $g$ contributes those variables associated both to a propagator not in $\mathcal{P}'$ and to a vertex not in $J$ and no other variables appear.
-Since there is no cancellation between terms, this means that $\Delta_{I_i}$ contains no other variables.
-Therefore $\Delta_{I_i}$ is the same as the determinant of the matrix obtained by taking the submatrix of $C(W)$ which gave $\Delta_{I_i}$ and setting all these other variables to $0$.
+{\em Proof of claim}: By the structure of determinants we know that $\Delta_{I_i} = fg$, where $g$ involves only variables associated to propagators not in $\mathcal{P}'$ and associated to vertices not in $J$.
+
+Expanding out $fg$ yields a signed sum of monomials.
+In each of these monomials, $f$ contributes those variables associated both to a propagator in $\mathcal{P}'$ and to a vertex in $J$, and $g$ contributes those variables associated both to a propagator not in $\mathcal{P}'$ and to a vertex not in $J$, and no other variables appear.
+
+Since there is no cancellation between terms, this means that $\Delta_{I_i}$ itself contains no other variables.
+Therefore $\Delta_{I_i}$ is equal to the determinant of the matrix obtained by taking the submatrix of $C(W)$ with columns indexed by $I_i$ and setting any variables not appearing in $\Delta_{I_i}$ to $0$.
 This new matrix is, up to permutations of rows and columns, a block matrix with one block for $\mathcal{P}'$ and $J$ and the other block for the complements.
 Thus its determinant, and hence also $\Delta_{I_i}$, is the product of the minors for these two blocks.
-By which variables appear, these two factors are also $f$ and $g$ and so in particular $f$ is the minor of $C(W)$ associated to $\mathcal{P}'$ and $J$.
+By considering which variables appear, these two factors must also be $f$ and $g$, and so in particular $f$ is the minor of $C(W)$ associated to $\mathcal{P}'$ and $J$.
 
@@
 
-The final thing to prove for this item is that there are no irreducible factors $f$ of degree 3 or more.
-Now suppose for a contradiction that $f$ has degree $\geq 3$.
-Note that by removing the propagators which come before those contributing to $f$ and changing $i$ to be the first vertex which contributes to $f$ we obtain a different admissible diagram for which $f$ still divides $\Delta_{I_i}$ but also $i\in I_i$ and $i$ contributes to $f$.
+All that remains is to prove that $\Delta_{I_i}$ has no irreducible factors of degree 3 or more.
+Suppose for a contradiction that $f$ is a factor of $\Delta_{I_i}$ of degree $\geq 3$.
+Note that by removing the propagators which come before those contributing to $f$ and changing $i$ to be the first vertex which contributes to $f$, we obtain a different admissible diagram for which $f$ still divides $\Delta_{I_i}$ but also $i\in I_i$ and \note{would it be neater to note at the beginning that removing uncovered vertices has no effect so we assume there are no redundant vertices, and hence $i \in I_i$ for each $i$?} $i$ contributes to $f$.
 Showing that this different admissible diagram gives a contradiction is sufficient, and so we may assume that $i\in I_i$ and $i$ contributes to $f$.
@@
 
-Let $p$ be the propagator such that $I_i(p) = i$. There are two cases to consider.  These are illustrated in Figure~\ref{fig no big factors}
+Let $p$ be the propagator such that $I_i(p) = i$. There are two cases to consider, depending on which edge $p$ is supported on.  These are illustrated in Figure~\ref{fig no big factors}
 
@@
 
-\textbf{Case I}: Suppose $p$ has one end on the edge $(i-1, i)$.
-Thus $p$ is supported on $(i-1, i, m, m+1)$ for some $m >_i i$.
-Then $I_{i+1}(p) = m$ by Lemma~\ref{lem susama}.
-Call the propagators which appear before $p$ is closed the propagators inside $p$.
-\note{It might be nice to have general language for this inside/outside idea.
-What do you think.}  The construction of $I_{i+1}$ begins as for $I_i$ after the first step; they can only differ once $p$ contributes to $I_{i+1}$.
-Thus if a propagator contributes $m$ in $I_i$ then it cannot be a propagator inside $p$ (nor $p$ itself).
+\textbf{Case 1}: Suppose $p$ has one end on the edge $(i-1, i)$.  Thus $p$ is supported on $(i-1, i, m, m+1)$ for some $m >_i i$, and $I_{i+1}(p) = m$ by Lemma~\ref{lem susama}.  
+%Call the propagators which appear before $p$ is closed the propagators inside $p$. \note{It might be nice to have general language for this inside/outside idea.  What do you think.}
+
 Let $S$ be the set of propagators inside $p$ along with $p$ itself.
-Two things can now happen; if neither $m$ nor $m+1$ appear in $I_i$ then the only vertex in the support of $p$ in $I_i$ is $i$, and so the row of $p$ in the matrix of $\Delta_{I_i}$ has only one nonzero entry; hence $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$ which is a contradiction.
-The other thing which can happen is that at least one of $m$ and $m+1$ is in $I_i$.
-However, all the propagators in $S$ are mapped by the bijection of $I_{i}$ to vertices strictly before $m$ so the matrix giving $\Delta_{I_i}$ has the form
+$I_i$ and $I_{i+1}$ can only differ once $p$ contributes to $I_{i+1}$, so $I_i(q) = I_{i+1}(q)$ for each $q \in S \backslash \{p\}$.
+Thus if a propagator contributes $m$ in $I_i$ then it must lie outside $p$.
+
+If neither $m$ nor $m+1$ appear in $I_i$ then $V(p) \cap I_i = \{i\}$,\note{check: is it obvious that $i-1 \not\in I_i$ or are we using the no coloops result?} and so the row of $p$ in the matrix of $\Delta_{I_i}$ has only one nonzero entry; hence $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$, which is a contradiction.
+So we must have at least one of $m$ and $m+1$ in $I_i$.
+However, all propagators in $S$ are mapped by the function $I_{i}(\cdot)$ to vertices strictly before $m$, so the matrix giving $\Delta_{I_i}$ has the form
 \[
@@
 \]
-where $A$ is the matrix for the propagators in $S$ and the vertices in $I_i(S)$ which is square of size $|S|\times |S|$.
-No other propagators can be supported on these vertices since all other propagators are outside of $p$ and $p$ is the first propagator supported at $i$.
-This explains the zero block.
-Therefore $\Delta_{I_i} = \det A \det C$ and both factors are nontrivial since $m$ appears in $I_i$.
-If we remove the propagator outside of $p$ we get a smaller diagram for which $\Delta_{I_i} = \det A$, this contradicts the minimality of our choices unless $\det A$ is quadratic which in turn contradicts that $i$ and $p$ contribute to an irreducible factor $f$ of degree at least 3.
-
-\textbf{Case II}: Suppose $p$ has one end on the edge $(i, i+1)$.
-If no other propagators are supported on $i$ then the column for vertex $i$ has only one nonzero entry in it and so $\Delta_{I_i}$ has a linear factor which is a contradiction.
-Thus we can take $q$ to be the propagator such that $I_i(q)=i+1$ and we know that $q$ has one end on the edge $(i, i+1)$ and is adjacent to $p$ on that edge in the counterclockwise direction.
+where $A$ is the $|S|\times |S|$ matrix indexed by the propagators in $S$ and the vertices in $I_i(S)$.
+No other propagators can be supported on these vertices since all other propagators are outside of $p$, and $p$ is the first propagator supported at $i$; this explains the zero block.
+Therefore $\Delta_{I_i} = \det A \det C$, and both factors are nontrivial since at least one of $m$ and $m+1$ appear in $I_i$.
+If we remove the propagator outside of $p$ that contributes $m$ or $m+1$, we get a smaller diagram for which $\Delta_{I_i} = \det A$.
+This contradicts the minimality of our choices unless $\det A$ is quadratic, which in turn contradicts our assumption that $i$ and $p$ contribute to an irreducible factor $f$ of degree at least 3.
+
+\textbf{Case 2}: Suppose $p$ has one end on the edge $(i, i+1)$.
+If no other propagators are supported on $i$ then the column of $C(W)$ corresponding to vertex $i$ has only one nonzero entry in it, and so $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$; as above, this is a contradiction.
+Thus we can take $q$ to be the propagator such that $I_i(q)=i+1$.
+We know that $q$ has one end on the edge $(i, i+1)$ and is adjacent to $p$ on that edge in the counterclockwise direction (see Figure \ref{fig no big factors}).
 Write $(i, i+1, j, j+1)$ for the support of $q$.
-The situation for $q$ is very similar to case I, in particular $I_{i+1}(q) = j$ by Lemma~\ref{lem susama} and so if $j\in I_i$ then the propagator which contributes it is outside of $q$.
-Thus similarly to case I, if we let $S$ be the set of propagators inside $q$ along with $p$ and $q$ themselves then all propagators in $S$ are mapped by $I_i$ to vertices strictly before $j$ and no other propagators cover vertices strictly before $j$.
+The situation for $q$ is very similar to case 1: in particular, we have $I_{i+1}(q) = j$ by Lemma~\ref{lem susama} and so if $j\in I_i$ then the propagator which contributes $j$ is outside of $q$.
+
+Similarly to Case 1, let $S$ be the set of propagators inside $q$ along with $p$ and $q$ themselves.
+Then all propagators in $S$ are mapped by $I_i(\cdot)$ to vertices strictly before $j$ and no other propagators are supported on vertices strictly before $j$.
 Thus the matrix giving $\Delta_{I_i}$ has the form
@@
 \]
-where $A$ is the matrix for the propagators in $S$ and the vertices in $I_i(S)$.
+where $A$ is the submatrix indexed by the propagators in $S$ and the vertices in $I_i(S)$.
 Again two things can now happen.
-If some vertex $j$ or larger in $>_i$ appears in $I_i$ then $B$ and $C$ have at least one column and so the block form of the matrix gives a nontrivial factorization of $\Delta_{I_i}$.
-Hence, as in case I either this contradicts minimality by removing those propagators not contributing to $A$, or $\det A$ is quadratic which contradicts that $p$ and $i$ contribute to $f$, an irreducible factor of degree at least 3.
-On the other hand, if no vertex $j$ or larger is in $I_i$ then the matrix giving $\Delta_{I_i}$ is just $A$.
-Looking in more detail into $A$, note that of supports of $p$ and $q$, only $i$ and $i+1$ are in $I_i$ and hence
+If some vertex $j$ or larger (with respect to $>_i$) belongs to $I_i$ then $B$ and $C$ are at least one column wide, and so the block form of the matrix gives a nontrivial factorization of $\Delta_{I_i}$.
+This yields a contradiction as in Case 1: either $W$ contains unnecessary propagators which contradicts our minimality assumption, or $\det A$ is quadratic which contradicts the assumption that $p$ and $i$ contribute to $f$, an irreducible factor of degree at least 3.
+
+On the other hand, if no vertex $\geq_i j$ is in $I_i$ then $\Delta_{I_i} = \det A$.
+Looking in more detail into $A$, note that the only vertices in the support of $p$ and $q$ which belong to $I_i$ are $i$ and $i+1$, and hence
 \[
@@
 where $D$ is the $2\times 2$ matrix indexed by the propagators $p$ and $q$ and the vertices $i$ and $i+1$.
-Thus $p$ and $i$ contribute to a quadratic factor of $\Delta_{I_i}$ contradicting our assumptions.
+Thus $p$ and $i$ contribute to a quadratic factor of $\Delta_{I_i}$, once again contradicting our assumptions.
 
@@
 
-    \item Suppose propagators $p$ and $q$ are supported on a common edge $(a,b)$ and $I_i(p)=a$, $I_i(q)=b$.
-For any fixed bijection $\sigma$ of the propagators other than $p$ and $q$ to $I_i -\{a,b\}$ for which each propagator is supported on its image under the bijection, we can extend $\sigma$ to a bijection of all propagators with $I_i$ in two ways, either $p\rightarrow a$ and $q\rightarrow b$ or $p\rightarrow b$ and $q\rightarrow a$.
-The sum of the contributions of all these bijections to $\Delta_{I_i}$ is the product of the minor of $C(W)$ coming from $p, q$ and $a,b$ with the minor coming from the other propagators and $I_i - \{a,b\}$.
+\item Suppose propagators $p$ and $q$ are supported on a common edge $(a,b)$, with $I_i(p)=a$ and $I_i(q)=b$.
+Let $x_{p,a},x_{p,b},x_{q,a},x_{q,b}$ be the associated variables in $C(W)$.
+For any fixed bijection $\sigma$ from $\cP-\{p,q\}$ to $I_i -\{a,b\}$ for which each propagator is supported on its image under the bijection, we can extend $\sigma$ to a bijection of all propagators with $I_i$ in two ways: either $p\mapsto a$ and $q\mapsto b$ or $p\mapsto b$ and $q\mapsto a$.
+The sum of the contributions of all these bijections to $\Delta_{I_i}$ is therefore the product of $x_{p,a}x_{q,b}-x_{p,b}x_{q,a}$ with the minor coming from the remaining propagators and $I_i - \{a,b\}$.
 Since there is no cancellation of terms in the expansion of $\Delta_{I_i}$, if any other terms appear then they will cause a factor which is not in the form described in the previous part.
-Therefore no such terms exist and $x_1x_4-x_2x_3$ is a factor of $\Delta_{I_i}$.
+Therefore no such terms exist and $x_{p,a}x_{q,b}-x_{p,b}x_{q,a}$ is a factor of $\Delta_{I_i}$.
 
 Now let $f$ be a quadratic factor of $\Delta_{I_i}$.
-By the previous part we know that $f$ is a $2\times 2$ minor coming from two propagators, call them $p$ and $q$, and two vertices, call them $a <_i b$.
+By part (2) we know that $f$ is a $2\times 2$ minor coming from two propagators, call them $p$ and $q$, and two vertices, call them $a <_i b$.
 It remains to show that $a$ and $b$ are adjacent.
@@
 
-As in the proof of the previous part, make a new admissible diagram by removing the propagators which come before $f$ and set $i=a$.
-The cases in the proof of the previous part show how $\Delta_{I_i}$ factors; in particular the vertices covering the second end of $p$ either do not appear in $I_i$ or contribute to a different factor of $\Delta_{I_i}$ than $p$ and $a$ do.
+As in the proof of part (2), make a new admissible diagram by removing the propagators which come before $f$ and set $i=a$.
+The cases in the proof of part (2) show how $\Delta_{I_i}$ factors: in particular the vertices supporting the other end of $p$ either do not appear in $I_i$, or they contribute to a different factor of $\Delta_{I_i}$ than $p$ and $a$ do.
 By assumption $b$ contributes to the same factor as $a$.
 Therefore $(a,b)$ is an edge.
-    \item Consider $p\in S_i$.
-$\Delta_{I_i}$ is homogeneous linear in the variables of the row corresponding to $p$.
-By the second statement of the proposition, either exactly one variable in the row corresponding to $p$ appears in $\Delta_{I_i}$ and this variable is a factor of $\Delta_{I_i}$, or exactly two variables from the row corresponding to $p$ appear in $\Delta_{I_i}$ and they appear as part of a quadratic factor.
-In the first case, let the variable be $x$, then $x$ is a factor of both $r_i$ and $\Delta_{I_i}$ and is the only variable from this row in either polynomial.
-Now suppose two variables from the row $p$ appear in a quadratic factor.
-By the previous part, there is another propagator $q$ and an edge $(a,b)$ such that the factor involving the variables of $p$ in $\Delta_{I_i}$ is the $2\times 2$ minor coming from $p, q$ and $a, b$, and $I_i(p)=a$, $I_i(q)=b$.
-Let this minor be $x_1x_4-x_2x_3$ with $x_1, x_2$ from $p$ and $x_3,x_4$ from $q$.
-There are two situations which can occur, both illustrated in Figure~\ref{fig quadratic}.
+
+\item Consider $p\in S_i$, and note that $\Delta_{I_i}$ is homogeneous linear in the variables of the row corresponding to $p$.
+By part (2), either exactly one variable in the row corresponding to $p$ appears in $\Delta_{I_i}$ and this variable is a factor of $\Delta_{I_i}$, or exactly two variables from the row corresponding to $p$ appear in $\Delta_{I_i}$ and they appear as part of a quadratic factor.
+In the first case: let the variable be $x$, then $x$ is a factor of both $r_i$ and $\Delta_{I_i}$ and is the only variable from this row in either polynomial.
+
+Now suppose two variables from the row $p$ appear in a quadratic factor $f$.
+By part (3), there is another propagator $q$ and an edge $(a,b)$ such that $f$ is the $2\times 2$ minor coming from $p, q$ and $a, b$, with $I_i(p)=a$, $I_i(q)=b$.
+There are two situations which can occur, both illustrated in Figure~\ref{fig quadratic}; we show that in both cases it follows that $q \in S_i$ as well.
 
@@
 
-By Lemma~\ref{lem susama}, since $I_{i-1}(p)\neq a$, then $I_{i-1} <_{i-1} a$ and no other vertex covered by $p$ lies between them.
+In both cases, since $I_{i-1}(p)\neq a$ by assumption it follows from Lemma~\ref{lem susama} that $I_{i-1}(p) <_{i-1} a$ and no other vertex supporting $p$ lies between $I_{i-1}(p)$ and $a$.
 In the case that $b<_i a$ and $q$ is taken before $p$ in $I_i$, this means that $I_{i-1}(p)=b$ and so $I_{i-1}(q)\neq b$.
-Thus $q\in S_i$ and so $x_1x_4-x_2x_3$ is a factor of $r_i$.
-Now suppose $a<_i b$ and $p$ is taken before $q$ in $I_i$.
-If $I_{i-1}(q)=a$ then $a\in S_i$ and so again $x_1x_4-x_2x_3$ is a factor of $r_i$.
-If not, then $I_{i-1}(q) = b$ by Lemma~\ref{lem susama}.
-This implies that some other propagator $s$ is associated to $a$ by $I_{i-1}$.
-If $s$ also has one end on $(a,b)$ then by Lemma~\ref{lem susama}, immediately after $s$ contributes $a$ it must contribute $b$.
-However we know $I_i(s) \neq a$ because $I_i(p)=a$, so $I_i(s)=b$ which is also impossible as $I_i(q)=b$.
-Thus $s$ is supported on $a$ but does not have an edge on $(a,b)$ and so $s$ must have an end on $(a-1, a)$ and so be inside $p$ from the point of view of $i-1$.
+Thus $q\in S_i$ and so $f$ is a factor of $r_i$.
+
+Now consider the case where $a<_i b$, and suppose for contradiction that $q \not\in S_i$, i.e.
+that $I_{i-1}(q) = b$.
+Since $I_{i-1}(p) \neq a$, there must be some other propagator $s$ with $I_{i-1}(s) = a$ (else $I_{i-1}$ assigns $q$ to $a$).
+This propagator cannot lie on edge $(a,b)$ since by Lemma~\ref{lem susama} we must have $I_i(s) = a$ or $b$, contradicting the fact that $I_i(p) = a$ and $I_i(q) = b$; thus $s$ has an end on $(a-1,a)$ and is inside $p$ from the point of view of $i-1$.
+
+Say $s$ is supported on $(j, j+1, a-1, a)$ and $p$ is supported on $(k, k+1, a, b)$ with $i-1 \leq_{i-1} k+1 \leq_{i-1} j+1$.
+But by Lemma~\ref{lem no fourth vertex}, if $I_{i-1}(s) = a$ then $a$ cannot be maximal in the support of $s$ with respect to $<_{i-1}$; thus we must have $i-1 = j+1$, and we are in the situation in figure~\ref{fig part 4}.
+
+\begin{figure}
+  \includegraphics[scale=0.5]{part4}
+  \caption{In order to obtain $I_{i-1}(s) = a$, propagators $s$ and $p$ must each have an end on the edge $(i-2,i-1)$.}\label{fig part 4}
+\end{figure}
+
+Since $p$ changed its association from $I_{i-1}$ to $I_i$, we have $I_{i-1}(p) = i-1$ by Lemma~\ref{lem susama}.
+From figure~\ref{fig part 4} it follows that $I_{i-1}$ assigns $p$ to $i-1$ and then proceeds identically to $I_i$ for all vertices inside $p$, implying that $I_{i-1}(s) = I_i(s)$.
+Since $I_{i-1}(s) = a$ and $I_i(s) \neq a$, this is a contradiction.
+
+Thus $q\in S_i$ after all, and so again $f$ is a factor of $r_i$ as required.
+
+% Thus $s$ is supported on $a$ but does not have an edge on $(a,b)$ and so $s$ must have an end on $(a-1, a)$ and so be inside $p$ from the point of view of $i-1$.
 Say $s$ is supported on $(j, j+1, a-1, a)$ and $p$ is supported on $(k, k+1, a, b)$ with $i-1 \leq_{i-1} k+1 \leq_{i-1} j+1$.
@@
 
-Finally we want to show $I_i(s)=j$ gives a contradiction.
+% Finally we want to show $I_i(s)=j$ gives a contradiction.
 If $k=j$ then $I_{i}(s)= k$, but $p$ has not yet been taken as $I_i(p)=a$ and $p$ comes before $s$ around $k$, so this is a contradiction.
@@
 Now suppose $k+1 <_{i-1} j$ then we have $i-1 \leq_{i-1} k+1 <_{i-1} I_i(s) = j$ so $i\leq_{i} I_i(s)$ which gives that
-\[
-I_i(s) <_i I_{i-1}(s) \qquad \text{and} \qquad I_i(s) <_{i-1} I_{i-1}(s)
-\]
-\note{Is this known to be impossible by the proof sketch of Lemma~\ref{lem susama} that you emailed or something similar.
+% \[
+% I_i(s) <_i I_{i-1}(s) \qquad \text{and} \qquad I_i(s) <_{i-1} I_{i-1}(s)
+% \]
+% \note{Is this known to be impossible by the proof sketch of Lemma~\ref{lem susama} that you emailed or something similar.
 I'm thinking this proof is already too long and the fact that this is impossible would be better as a lemma.}
 
-    \item If $W$ has zero propagators then all $I_i=\emptyset$ and both $R$ and $\prod_{i=1}^n \Delta_{I_i}$ are equal to $1$ so the result holds.  Now assume $W$ has at least one propagator.
-
-First we'll show that every factor of $\prod_{i=1}^n \Delta_{I_i}$ divides $R$.
+\item If $W$ has zero propagators then all $I_i=\emptyset$ and both $R$ and $\prod_{i=1}^n \Delta_{I_i}$ are equal to $1$, so the result holds in this case.
+Now assume $W$ has at least one propagator.
+
+First we show that every factor of $\prod_{i=1}^n \Delta_{I_i}$ divides $R$.
 Take an irreducible factor $f$ of $\prod_{i=1}^n \Delta_{I_i}$.
-There exists some $i$ such that $f|\Delta_{I_i}$ but $f\not| \Delta_{I_{i-1}}$ as otherwise the variables corresponding to the propagators contributing to $f$ which do not themselves appear in $f$ could never appear, contradicting Lemma~\ref{lem susama}.
+There exists some $i$ such that $f|\Delta_{I_i}$ but $f\!\!\nmid\!\!
+\Delta_{I_{i-1}}$, since otherwise the variables corresponding to the propagators contributing to $f$ which do not themselves appear in $f$ could never appear, contradicting Lemma~\ref{lem susama}.
 If $f$ is a linear factor, say from associating propagator $p$ to vertex $a$, then $I_{i}(p)=a$ and $I_{i-1}(p)\neq a$ so this factor appears in $r_i$.
-If $f$ is a quadratic factor, say from associating propagators $p$ and $q$ to vertices $a$ and $b$ respectively, then by the first direction of the previous part, $I_{i-1}$ cannot make the same association for both propagators $p$ and $q$, but then by the second direction of the previous part, both $p$ and $q$ must be differently assigned between $I_{i-1}$ and $I_i$.
+If $f$ is a quadratic factor, say from associating propagators $p$ and $q$ to vertices $a$ and $b$ respectively, then again we cannot have both $I_{i-1}(p) = a$ and $I_{i-1}(q) = b$, else $f$ divides $\Delta_{i-1}$.
+However, by the proof of part (4), if one of $p,q$ belongs to $S_i$ then the other does as well.
 Thus $f$ divides $r_i$.
@@
 Suppose $f^2|R$.
-If $f$ is a linear factor, say from associating propagator $p$ to vertex $a$, then twice in the Grassmann necklace $p$ must change from not being associated to vertex $a$ to being associated to vertex $a$.
+If $f$ is a linear factor, say from associating propagator $p$ to vertex $a$, then there must be two distinct points in the Grassmann necklace algorithm where $p$ changes from not being associated to vertex $a$ to being associated to vertex $a$.
 This contradicts Lemma~\ref{lem susama}.
-Now suppose $f$ is a quadratic factor say from associating propagators $p$ and $q$ to vertices $a$ and $b$ respectively.
-Since $p$ comes before $q$ on edge $(a,b)$ it is not possible for any $I_i$ to associate $p$ to $b$ and $q$ to $a$.
-Furthermore, we know by the second direction of the previous part that $p$ changes from not being associated to $a$ to being associated to $a$ if and only if $q$ changes from not being associated to $b$ to being associate to $b$.
+Now suppose $f$ is a quadratic factor, say from associating propagators $p$ and $q$ to vertices $a$ and $b$ respectively.
+\hlfix{Since $p$ comes before $q$ on edge $(a,b)$}{I can't figure out why this happens; what am I missing?} it is not possible for any $I_i$ to associate $p$ to $b$ and $q$ to $a$.
+Furthermore, we know by part (4) that $p$ changes from not being associated to $a$ to being associated to $a$ if and only if $q$ changes from not being associated to $b$ to being associated to $b$.
 Thus $f^2|R$ implies that twice in the Grassmann necklace $p$ must change from not being associated to vertex $a$ to being associated to vertex $a$.
@@
 To this end, first note that $R(W)$ and $R$ both have total degree $4|\mathcal{P}|$; the degree of $R(W)$ is immediate from the definition while that of $R$ follows from Lemma~\ref{lem susama}.
-By Proposition~\ref{prop alg gives rad} every factor of $R$ is either a single variable or a quadratic factor coming from two propagators supported on a common edge and hence every factor of $R$ divides $R(w)$.
+By Proposition~\ref{prop alg gives rad} every factor of $R$ is either a single variable or a quadratic factor coming from two propagators supported on a common edge and \hlfix{hence every factor of $R$ divides $R(W)$}{Is this obvious?
+Or does it follow from a previous result?}.
 Finally, since $R$ is squarefree and monic, this implies that $R(W)$ is an integer multiple of $R$.

### 2018-09-11 General WLD combinatorics.tex
tidied up and edited section 2

@@
 
-\section{Wilson Loop diagrams as matroids}
-
-In \cite{wilsonloop}, Amat and Agarwala show that admissible Wilson loop diagrams with $k$ propagators corresponds to positroids of rank $k$ (a matroid that can be represented by an element of $\Gr(k, n)$.)
-
-\begin{thm}[\cite{wilsonloop}] An admissible Wilson loop diagram, $W =(\cP, n)$, defines a matroid with base set $[n]$.
-The independent sets are exactly those subsets $V \subseteq [n]$ such that $\not \exists U\subseteq V$ satisfying $|\Prop(U)|> |U|$.
+\section{Equivalence classes of Wilson loop diagrams}
+
+In \cite{wilsonloop}, Agarwala and Amat show that Wilson loop diagrams can be interpreted as positroids, a certain well behaved class of realizable matroids (this correspondence is stated precisely in Theorem \ref{thm WLD defines matroid} below).
+This opens up the study of Wilson loop diagrams to techniques from geometry and combinatorics.
+
+[outline of section, postponed until section structure is finalised]
+
+The main results of this section are the following: we show that two admissible Wilson loop diagrams define the same matroid if and only if they are equivalent (Theorem \ref{same matroid iff equiv}), and we obtain a formula for the number of admissible Wilson loop diagrams in each equivalence class (Corollary \ref{number of equiv diagrams}).
+[sentence about why this matters]
+
+\subsection{Wilson loop diagrams as matroids}\label{sec matroid background}
+
+We first give a quick summary of the matroid terminology that we will need; it is not intended as a comprehensive introduction to matroids and the interested reader is referred to [ref].
+
+A {\em matroid} $M = (E,\cB)$ consists of a finite ground set $E$ and a non-empty family $\cB \subseteq \cP(E)$ whose elements satisfy the {\em basis exchange property}: for any distinct $B_1,B_2 \in \cB$ and any $a \in B_1 \setminus B_2$, there exists some $b \in B_2 \setminus B_1$ such that $(B_1 \setminus \{a\})\cup \{b\} \in \cB$ as well.
+The elements of $\cB$ are called the {\em bases} of the matroid.
+Note that the basis exchange property immediately implies that all bases have the same size.
+
+A subset $A \subseteq E$ is called {\em independent} in $M$ if $A \subseteq B$ for some $B \in \cB$, and {\em dependent} else.
+The {\em rank}  $\rk(A)$ of a subset $A \subseteq E$ is the size of the largest independent set contained in $A$.
+The rank of the matroid itself is defined to be $\rk(E)$.
+
+A {\em circuit} in $M$ is a minimally dependent set.
+That is, it is a set $C \subseteq E$ such that $C$ is dependent but $C \setminus \{e\}$ is independent for any $e \in C$.
+A union of circuits is called a {\em cycle}.
+On the other hand, a {\em flat} is a maximally dependent set, i.e.
+a set $F \subseteq E$ such that $\rk(F \cup \{e\}) = \rk(F) + 1$ for any $e \in E \setminus F$.
+Unsurprisingly, a {\em cyclic flat} is a set which is both a flat and a cycle.
+The set of circuits in a matroid uniquely defines that matroid, as does the set of flats; thus one could specify a matroid by listing its independent sets, bases, circuits, or flats.
+[ref]
+
+Finally, we describe several important types of matroid.
+A matroid of rank $k$ with a ground set of size $n$ is called {\em realizable} if there exists some $A \in Gr(k,n)$ whose non-zero $k\times k$ minors are exactly those with columns indexed by elements of $\cB$.
+A {\em positroid} is a matroid which can be realized by an element of the totally nonnegative Grassmannian $\Gr(k,n)$.
+Finally, a {\em uniform matroid} of rank $r$ is a matroid in which any set of size $\leq r$ is independent.
+
+Matroid theory relates to the study of Wilson loop diagrams as follows.
+In \cite{wilsonloop}, Agarwala and Amat show that every admissible Wilson loop diagram with $k$ propagators defines a positroid of rank $k$, and that the independent sets can be read directly from the diagram:
+
+\begin{thm} \label{thm WLD defines matroid} \cite[Theorem 3.6]{wilsonloop} Any admissible Wilson loop diagram $W =(\cP, n)$ defines a matroid $M(W)$ with ground set $[n]$.
+The independent sets are exactly those subsets $V \subseteq [n]$ such that $\nexists U\subseteq V$ satisfying $|\Prop(U)| < |U|$.
 \label{thm:WLDmatroid}\end{thm}
-
-This does not, however, show that the matroid associated to each Wilson loop diagram is unique.
-In fact, in \cite{wilsonloop}, the authors show that if two diagrams are equivalent then they define the same matroid [cite theorem here].
-
-In the remainder of this section, we show that two admissible Wilson loop diagrams define the same matroid if an only if they are equivalent.
-Furthermore, we count the number of Wilson loop diagrams in each equivalence class.
-The first of these are done by considering Wilson loop diagrams as matroids.
-The second, by considering polygon partitions of Wilson Loop Diagrams.
-
-To this end, we recall some definitions and go through a series of new intermediary steps.
-
-First we recall a few facts about matroids, with particulars about those defined by Wilson loop diagrams.
-
-\begin{dfn} For a Wilson Loop diagram $W = (\cP, [n])$, the associated matroid $M(W)$ can be defined by any of the following sets of subsets
+In other words, the independent sets of $M(W)$ correspond to the sets of vertices in $W$ such that no subset supports fewer propagators than the vertices it contains.
+
+Throughout, we take the {\em matroid defined by $W$} to be the matroid $M(W)$ of Theorem \ref{thm WLD defines matroid}.
+Note that since vertices of the diagram $W$ correspond to columns of the associated matrix $C(W)$, $M(W)$ can also be thought of as the matroid realized by $C(W)$.
+
+% The identification of Theorem \ref{thm WLD defines matroid} is not 1-1: by \cite[Theorem 1.18]{wilsonloop}, if two admissible Wilson loop diagrams are equivalent (as in Definition~\ref{equivdfn}) then they define the same matroid.
+
+Let $W = (\cP,n)$ be an admissible Wilson loop diagram, and $M(W)$ its associated matroid.
+Where it will not cause confusion we conflate the two objects, identifying vertices of $W$ with elements of the ground set $[n]$ in $M(W)$.
+
+In particular, this allows us to prove results about $M(W)$ by considering the behavior of propagators in $W$.
+We record a few elementary facts about the rank and cycles of $M(W)$ here as an example of this.\note{It would be nice to have a few more; do we need any others, and/or are there any cool ones?}
+
+\begin{lem}\label{lem facts about WLD matroids}
+Let $W = (\cP,n)$ be an admissible Wilson loop diagram. Then:
 \begin{enumerate}
-\item An set $V \subseteq [n]$ is independent if there is no subset that supports fewer propagators than vertices of that subset: \bas \not \exists U \subseteq V \; \textrm{s.t.
-} |\Prop (U)| < |U|\;.
-\eas A basis of $W$ is any independent set, $B \subset [n]$ of size $|B| = |\cP|$.
-\item The rank of a set $|V| \subset [n]$, is bounded above by $\rk(V) \leq \min\{ |V| , |\Prop(V)|\}$.
-If $V$ is an independent set, then $\rk(V) = |V|$.
-Furthermore, if $v \in [n]$, and $q \in \Prop(v)$, then for any $V \subset [n]$ such that $q \not \in \Prop(V)$, $\rk(V \cup v) = \rk(V) +1$.
-That is, adding a vertex that supports a new propagator to a set increases the rank of the set.
-\item A circuit of a matroid is any set $C \subset [n]$ such that every proper subset $U \subsetneq C$ is independent.
-That is, $\rk(C) = |C|-1$.
-The union of circuits is called a cycle.
-If $C$ is a circuit of an admissible Wilson loop diagram, and $e \in C$, \bas |\Prop(C\setminus e))| \leq |C\setminus e| = \rk(C) \leq \min\{|C|, |\Prop(C\setminus e)|\}\;.\eas
-    In other words, if $C$ is a circuit of a Wilson loop diagram, then \bas \rk(C) = |C|-1 = |\Prop(C)| \;. \eas
-\item A flat, $F$, of a matroid is a set that is maximal for its rank.
-That is, for all $e \not \in F$ $\rk(F \cup e) = \rk(F) +1$.
-If $W$ is an admissible Wilson loop diagram, any group of propagators defines a flat, $F(P) = V(P^c)^c$, called a propagator flat.
-To see that this is flat, let $v \in V(P^c)$.
-We have that there is a $q \not \in P$ such that $q \in \Prop(v)$.
-Therefore, by the rank function, $\rk( F(P) \cup v))> \rk(F(P))$.
-Furthermore, in \cite{wilsonloops}, the authors show that if $F$ is a cyclic flat, then there is a $P \subset \cP$ such that $F = F(P)$.
-
-\end{enumerate}
-\end{dfn}
-
-Note that one may substitute values into $C(W)$ to realize the matroid assoicated to $W$ in this manner.
-
-It is worth noting that it is not necessary to list all the flats in a matroid to defined it completely, only the cyclic flats, and those that are independent sets.
-Namely, if $F$ is a dependent flat, it contains a circuit.
-Let $C \subset F$ be the largest cycle contained in $F$.
-Then two things are true.
-
-\begin{lem} Let $W$ be a Wilson loop diagram, and $F$ is a flat. Let $C \subset F$ be the largest cycle contained in $F$. Then the following is true:
-\begin{enumerate}
-\item $C = F(\Prop (C))$ is a cyclic flat.
-\item $F \setminus C$ is an independent set. If $W$ does not contain any vertices of rank $0$, that is, all vertices support at least $1$ propagator, then $F \setminus C$ is an independent flat.
+\item The rank of a set $V \subseteq [n]$ is bounded above by $\min\{|V|,|\Prop(V)|\}$, with $\rk(V) = |V|$ if and only if $V$ is an independent set.
+%\item Let $v \in [n]$ and $q \in \Prop(v)$.
+Then for any $V \subset [n]$ such that $q \not \in \Prop(V)$, we have $\rk(V \cup \{v\}) = \rk(V) +1$, i.e.
+adding a vertex that supports a new propagator to a set increases the rank of the set.
+\item If $C \subseteq [n]$ is a cycle, then $\rk(C) = |Prop(C)|$.
 \end{enumerate}
 \end{lem}
-
-\begin{proof}
-If $F$ is an independent flat, then $C = \emptyset$ and the statement is trivially true.
-
-If $F$ is a dependent set, $F$ contains a circuit.
-
-To see the first point, note that $\rk(C) = |\Prop(C)| \geq F(\Prop (C)|$.
-For any $v\in C$ we have that $\Prop(v) \subset \Prop(C)$.
-This implies that $v \in F(\Prop(C))$.
-Therefore $C \subset F(\Prop(C))$.
-This implies that $|\Prop(C)| = F(\Prop (C)|$.
-Suppose there is a $v \in  F(\Prop(C)) \setminus C$.
-Let $B$ be an independent subset of $C$ of maximal rank.
-The set $B \cup v$ is dependent and therefore contains a circuit.
-Therefore, $C \cup b$ is a cycle, which is a contradiction to $C$ being the maximal cycle in $F$.
-
-To see the second point, note that $F \setminus C$ is independent (as it contains no circuits).
-Furthermore, it is a flat.
-For any $e \not \in F$, $\rk (F \setminus C \cup e) = \rk (F\setminus C) +1$, since $F$ is a flat.
-For any $e \in C$,  if $\rk (F \setminus C \cup e) = \rk (F\setminus C)$, the set $F \setminus C \cup e$ is a dependent set.
-This occures either if $\rk{e} = 0$, or $F\setminus C \cup e$ contains a circuit of at least $2$ elements, which contradicts the hypothesis that $C$ is the largest cycle in $F$.
-\end{proof}
-
-Therefore, in the sequel, one only needs worry about cyclic and independent flats.
-
-\begin{cor} \label{classifyflats}
-If $F$ is a flat of a Wilson loop diagram, it can be written as the union of a cyclic propagator flat and an independent flat. \end{cor}
-
-In particular, any propagator flat can be written as a union of a cyclic propagator flat and an independent flat.
-
-Finally, we note the differences between subdiagrams of Wilson loop diagrams, and restrictions or cotractions of the associated matroids.
-
-Given any matroid, one may restrict it to a subset of the base set.
-The bases of the restricted matroid come from intersecting bases of the original with the subset.
-It is worth noting that a the matroid defined by a subdiagram is different from the restriction of the matroid of a Wilson loop diagram to a set of vertices.
-
-\begin{dfn} \label{restrictiondfn}
-For $W = (\cP, n)$, the restricted diagram, $W|_V$ is the matroid defined by only looking at the vertices $V \subset [n]$.
-\end{dfn}
-
-The key difference between a subdiagram and a restriction is that the propagator support function does not change in the case of restriction, while it may in the case of a subdiagram.
-In particular, for $v \in V$, $\Prop_W(v) = \Prop_{W|_V}(v)$, while $\Prop_{(P, V(P))} (v) = \Prop_W(v) \cap P$.
-
-A subdiagram is more closely related to a contracted matroid.
-
-\begin{lem} \label{contractsubdiaglem}
-For $W = (\cP, [n])$, consider a subdiagram $(P^c, V(P^c))$.
-The complementary set of vertices is a propagator flat: $F(P) = V(P^c)^c$.
-If this has maximal rank, $\rk F(P) = |P|$, then the subdiagram defines the same matroid as is formed by contracting the original matroid by $F(P)$: \bas M((P^c, V(P^c))) = M(W)/ F(P) \;.
-\eas
-\end{lem}
-
-In the sequel, where it doesn't cause confusion, I conflate a Wilson loop diagram with the matroid it defines.
+\begin{proof}
+The first part of (1) is \cite[Equation (9)]{wilsonloop} and surrounding discussion, and the second part is standard matroid theory. (2) is \cite[Lemma 3.27]{wilsonloop}.
+\end{proof}
 
@@
 
-In order to study exact Wilson loop diagrams, we further introduce the notion of a polygon partition of $W$.
+The equivalence relation on Wilson loop diagrams is defined in terms of exact subdiagrams; thus in order to understand the equivalence, we need a way to extract and compare exact subdiagrams.
+We do this via the notion of a polygon partition of $W$.
 
 \begin{dfn}
-  Let $W = (\cP, n)$ be an admissible Wilson loop diagram.  The \emph{polygon partition} associated to $W$, denotes $\tau(W)$ is defined as follows.
+  Let $W = (\cP, n)$ be an admissible Wilson loop diagram.  The \emph{polygon partition} associated to $W$, denoted $\tau(W)$, is defined as follows.
   \begin{itemize}
@@
 Connecting consecutive vertices gives a graph theoretic cycle called the polygon of $\tau(W)$.
-  \item Each propagator of $W$ defines a chord edge of $\tau(W)$ for each propagator of $W$.  If $p= (i,j) \in \cP$, it defines a chord connecting the verices $i$ and $j$
+  \item Each propagator of $W$ defines a chord edge of $\tau(W)$; specifically,  a propagator $(i,j) \in \cP$ defines a chord connecting the vertices $i$ and $j$ in $\tau(W)$.
   \end{itemize}
@@
 \begin{lem}\label{tausimpleplanarlem}
-If $W = (\cP, n)$ is an admissible Wilson loop diagram, $\tau(W)$ is a simple planar graph wihose outer face is a cycle.
-It is embedded such that the vertices all like on this infinite face.
-These vertices are cyclically ordered, with a coice of first vertex, giving it an additional compatible linear order.
+If $W = (\cP, n)$ is an admissible Wilson loop diagram, then $\tau(W)$ is a simple planar graph whose outer face is a cycle.
+It is embedded such that the vertices all lie on this infinite face.
+These vertices are cyclically ordered, with a choice of first vertex giving it an additional compatible linear order.
 \end{lem}
@@
 Since $W$ is admissible, no pairs of propagators cross.
-Thereofore, it is a planar embedding.
-There are no propagators $p = (i, i+1)$.
-Therefore, there is exactly one edge connecting any two adjacent edges of $\tau(W)$.
-Similarly, there are not two propagators such that both $p$ and $q$ start and end at the edges $i$ and $j$.
+Therefore, it is a planar embedding.
+Similarly, $W$ does not admit any propagators of the form $p = (i, i+1)$; therefore there is exactly one edge connecting any two adjacent edges of $\tau(W)$.
+Finally, there does not exist two propagators $p,q$ such that both $p$ and $q$ start at edge $i$ and end at edge $j$.
 Therefore, no other two vertices of $\tau(W)$ can be connected by more than one edge.
-Finally, the embedding of $\tau(W)$ is induced from embedding of the graph $W$.
+Finally, the embedding of $\tau(W)$ is induced from the embedding of the graph $W$.
  \end{proof}
@@
 \begin{eg}\label{WLDtopolygonpartition}
-In this example we return to the Wilson loop diagrams in Example \ref{eg:equivdiags}. We can pair diagrams with their polygon partitions as follows:
+In this example we return to two of the Wilson loop diagrams in Example \ref{eg:equivdiags}. We can pair diagrams with their polygon partitions as follows:
 \bas W_1 = \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
@@
 
-A planar embedding of a graph is a \emph{triangulation} if all faces, except possibly the infinite face, are triangles.
+Recall that a planar embedding of a graph is a \emph{triangulation} if all faces, except possibly the infinite face, are triangles.
 
@@
 We will take the convention that a subgraph consisting of a single chord edge is called a \emph{trivial} triangulated piece.
+A {\em maximal} triangulated piece is one which is not contained in any strictly larger triangulated piece.
 \end{dfn}
 
-A decomposition of a polygon partition $\tau(W)$ is a set of 2-connected induced subgraphs of $\tau(W)$ which partition the edges of $\tau(W)$.
-
-\begin{lem} \label{decompositionlem}
-  For $W$ an admissible Wilson loop diagram, the polygon partition $\tau(W)$ has a unique decomposition into maximal triangulated pieces, and edges in the polygon of $\tau(W)$.
-\end{lem}
-
-\begin{eg} \label{eg: unique decomposition} For the Wilson loop diagrams and polygon partitions in example \ref{WLDtopolygonpartition}, the vertex sets $\{1, 2, 3,4\}$ and $\{5, 6, 7, 8\}$ are maximal triangulated pieces for both $\tau(W_1)$ and $\tau(W_3)$.
+\begin{dfn}
+ A {\em decomposition} of a polygon partition $\tau(W)$ is a set of 2-connected induced subgraphs of $\tau(W)$ which partition the edges of $\tau(W)$.  
+\end{dfn}
+
+\begin{eg} \label{eg: unique decomposition} For the Wilson loop diagrams and polygon partitions in Example \ref{WLDtopolygonpartition}, the vertex sets $\{1, 2, 3,4\}$ and $\{5, 6, 7, 8\}$ are maximal triangulated pieces for both $\tau(W_1)$ and $\tau(W_3)$.
 The vertex set $\{4,5, 8, 1\}$ is not a triangulation in either polygon partition.
@@
 
+\begin{lem} \label{decompositionlem}
+  For $W$ an admissible Wilson loop diagram, the polygon partition $\tau(W)$ has a unique decomposition into maximal triangulated pieces, and edges in the polygon of $\tau(W)$.
+\end{lem}
+
 \begin{proof}
@@
 
-Let $T(W)$ be a the dual graph of $\tau(W)$ with the vertex corresponding the to the infinite face split.
+Let $T(W)$ be the dual graph of $\tau(W)$ with the vertex corresponding to the infinite face split.
 In other words, place a vertex on each finite face of $\tau(W)$.
@@
 Furthermore, if the face is bounded by an edge of the polygonal cycle of $\tau(W)$, the corresponding vertex gets a leaf edge for each such boundary.
-Since, by Lemma \ref{tausimpleplanarlem}, $\tau(W)$ is a simple planar graph, $T(W)$ is an uniquely defined graph.
+Since $\tau(W)$ is a simple planar graph by Lemma \ref{tausimpleplanarlem}, $T(W)$ is an uniquely defined graph.
 
@@
 Since $\tau(W)$ is a planar graph with $k$ chord edges and no internal vertices, there are $k+1$ internal faces of $\tau(W)$.
-Each of these internal faces correspond to a vertex of $T(W)$, and there are $n$ vertices of $T(W)$ from the splitting of the dual graph, we see that $T(W)$ has $n+k+1$ vertices.
-On the other hand, $T(W)$ has $n+k$ edges, corresponding to the $n +k$edts of $\tau(W)$.
-Therefore, $T(W)$is a tree.
+Each of these internal faces corresponds to a vertex of $T(W)$, and there are $n$ vertices of $T(W)$ from the splitting of the dual graph, so $T(W)$ has $n+k+1$ vertices in total.
+On the other hand, $T(W)$ has $n+k$ edges, corresponding to the $n +k$ edges of $\tau(W)$.
+Therefore, $T(W)$ is a tree.
 
@@
 Therefore, each vertex of $T(W)$ is at least 3 valent (one for each edge of the polygon).
-If split each vertex of $T(W)$ if it is strictly greater than $3$ valent.
-(In other words, we fail to split exactly when the face is a triangle).
-The connected components of $T(W)$ correspond to the decomposition of $\tau(W)$ into maximal triangulated pieces and edges orinignaly in the polygon of $\tau(W)$.
+\hlfix{If split each vertex of $T(W)$ if it is strictly greater than $3$ valent.}{???} (In other words, we fail to split exactly when the face is a triangle).
+The connected components of $T(W)$ correspond to the decomposition of $\tau(W)$ into maximal triangulated pieces and edges originally in the polygon of $\tau(W)$.
 Let $f$ be the forest thus obtained.
@@
 In particular, there is a vertex $v$ in $t'$ that corresponds to a split vertex of $T(W)$ in the original decomposition.
-This implies that $v$ has valence greater than $3$ in $T(W)$, and thus the corresonding face of $\tau(W)$ is not a triangle.
-In otherwords, the decomposition corresponding to $f'$ is not a triangulation.
-\note{This is a variant of what you wrote in the e-mail.
-Let me know if you like it.}
+This implies that $v$ has valence greater than $3$ in $T(W)$, and thus the corresponding face of $\tau(W)$ is not a triangle.
+In other words, the decomposition corresponding to $f'$ is not a triangulation.
 \end{proof}
@@
 \begin{proof}
-Consider any two disctinct maximal triangulations of $\tau(W)$.
-These two triangulations correspond to subtrees of $T(W)$.
-These subtrees intersect, at most, at a vertex in an interior of $\tau(W)$.
-Since the subtrees corresponding to the maximal subtrees are edge disjoint, and the edges of $T(W)$ correspond to the edges of $\tau(W)$, this forces the maximal triangulations to be edge disjoint as well.
-\end{proof}
-
-\subsection{Exact subdiagrams}
-
-It has been proved that if two Wilson loop diagrams are equivalent, then the define the same matroid in \cite{wilsonloops}.
-In this section, we prove that two Wilson loop diagrams are equivalent if and only if they define the same matroid.
-Furthermore, we count the admissible elements of each equivalence class.
-
-We begin by relating triangulations and exact subdiagrams.
+Consider any two distinct maximal triangulated pieces of $\tau(W)$.
+These two pieces correspond to subtrees of $T(W)$ and intersect, at most, at a vertex in the interior of $\tau(W)$.
+Since the subtrees corresponding to the maximal triangulated pieces are edge disjoint, and the edges of $T(W)$ correspond to the edges of $\tau(W)$, this forces the maximal triangulated pieces to be edge disjoint as well.
+\end{proof}
+
+We are now in a position to relate the triangulated pieces of $\tau(W)$ to exact subdiagrams of $W$.
 
@@
 \begin{proof}
-  Let us first record a few standard facts about polygon triangulations (that is about triangulations with all vertices on the outer face).
-If such a triangulation has $n$ vertices then it has $n$ edges on the polygon (that is on the outer face) and $n-3$ edges which are not.
-No planar graph with the same vertices and the same outer face can have more edges than the triangulation and every such simple graph with $n-3$ edges off the outer face is a triangulation.
-
-  Since $W$ is admissible, by lemma \ref{} $\tau(W)$ is a simple graph. Furthermore, $t$ is not all of $\tau(W)$.
-  Let $t$ be a triangulated piece of the decomposition of $\tau(W)$ given in Lemma \ref{decomplem} and suppose $t$ has $n>2$ vertices.
-We want to count how many edges of $t$ are not on the outer face of $\tau(W)$.
-Consider the intersection of $t$ with the outer face of $\tau(W)$.
-This is a possibly disconnected subgraph of the polygon of $\tau(W)$ with $n$ vertices, call it $S$.
+Let us first record a few standard facts about polygon triangulations (that is, about triangulations with all vertices on the outer face).
+If such a triangulation has $n$ vertices then it has $n$ edges on the polygon (that is, on the outer face) and $n-3$ edges which are not.
+No planar graph with the same vertices and the same outer face can have more edges than the triangulation, and every such simple graph with $n-3$ edges off the outer face is a triangulation.
+
+Since $W$ is admissible, by Lemma \ref{tausimpleplanarlem} $\tau(W)$ is a simple graph. Furthermore, $t$ is not all of $\tau(W)$.
+
+Let $t$ be a triangulated piece of the decomposition of $\tau(W)$ given in Lemma \ref{decompositionlem}; note that $t$ cannot be equal to $\tau(W)$ by the definition of admissible diagrams.
+
+If $t$ has 2 vertices, then $t$ has two connected components.
+Therefore, $t$ corresponds to a propagator that connects two non-adjacent edges.
+Therefore, the trivial triangulation is a trivial exact subdiagram.
+
+Now suppose that $t$ has $m>2$ vertices; we count how many edges of $t$ are not on the outer face of $\tau(W)$.
+Consider the intersection of $t$ with the outer face of $\tau(W)$: this is a possibly disconnected subgraph of the polygon of $\tau(W)$ with $m$ vertices, call it $S$.
 Let $k$ be the number of connected components of $S$.
 To join the components $S$ must have $k$ edges not in the outer face of $\tau(W)$.
-Furthermore $t$ has $n-3$ edges not in its outer face and so also not in the outer face of $\tau(W)$.
-Thus there are $n-3+k$ edges of $t$ not in the outer face of $\tau(W)$.
-
-  Each of these $n-3-k$ internal edges correspond to propagators in $W$, call this set $P$.
+Furthermore $t$ has $m-3$ edges not in its outer face and so also not in the outer face of $\tau(W)$.
+Thus there are $m-3+k$ edges of $t$ not in the outer face of $\tau(W)$.
+
+Each of these $m-3+k$ internal edges correspond to propagators in $W$, call this set $P$.
 Next we count the size of $V(P)$.
-Each of the $n$ vertices in the outer face of $t$ corresponds to an edge of $W$.
-These $n$ edges define $k$ connected compnents of the outer polygon of $W$.
-Thus the set$V(P)$ has $n+k$ vertices.
-In other words, \bas |V(P)| = n+k = |P| -3\;.\eas
-
-If $n=2$, then $t$ has two connected components. Therefore, $t$ corresponds to a propagator that connects two non-adjacent edges. Therefore, the trivial triangulation is a trivial exact subdiagram.
-
-  Conversely if we have an exact subdiagram $(P, V(P))$ of $W = (\cP, n)$ supported on $|V(P)| = |P|+3$ vertices.
-Let $|P| = k>1$ and $k+3 = m$.
+Each of the $m$ vertices in the outer face of $t$ corresponds to an edge of $W$.
+These $m$ edges define $k$ connected compnents of the outer polygon of $W$.
+Thus the set $V(P)$ has $m+k$ vertices.
+In other words,
+\[|V(P)| = m+k = |P| -3\;.\]
+
+Conversely, suppose we have an exact subdiagram $(P, V(P))$ of $W = (\cP, n)$ supported on $|V(P)| = |P|+3$ vertices, and let $t$ be the subgraph of $\tau(W)$ corresponding to $(P,V(P))$.
+
+If $|P|=1$, then $(P, V(P))$ is a trivially exact subdiagram. In this case $t$ is an edge internal to $\tau(W)$ connecting two boundary edges, which by definition is a triangulation.
+
 Suppose the set $V(P)$ defines $c$ disjoint cyclic intervals of $[n]$.
@@
 
-  If $k=1$, and $(P, V(P))$ is a trivially exact subdiagram. Then $t$ is an edge internal to $\tau(W)$ connecting two boundary edges, which, by definition is a triangulation.
-
 %  The statement of the lemma then follows form the fact that inclusion is preserved under $\tau$ and so maximality also corresponds under $\tau$.
@@
 
-Next, we prove a few theorems about matroidal properties of exact subdiagrams.
+To avoid the issue of exact diagrams being subdiagrams of other exact subdiagrams (for instance, any subdiagram $(q, V_q)$, for $q \in \cP$ is exact), we introduce the notion of maximal exact subdiagrams.
+
+\begin{dfn}
+An exact subdiagram $(P, V(P))$ is a {\em maximal exact subdiagram} of $W$ if there is no other exact subdiagram $(Q, V(Q))$ in $W$ that contains $(P,V(P))$ as a strict subdiagram.
+\end{dfn}
+
+\begin{cor} \label{uniqueproppartitioncor}
+Any admissible Wilson loop diagram $W = (\cP, n)$ can be uniquely decomposed into maximal exact subdiagrams. These maximal subdiagrams partition $\cP$.
+\end{cor}
+
+\begin{proof}
+Combining Lemmas \ref{decompositionlem} and \ref{lem triang to exact} yields the unique decomposition into maximal exact subdiagrams, and Corollary \ref{maxtriangdisjointcor} ensures that no propagator appears in more than one subdiagram in this decomposition.
+Since the chord edges of $\tau(W)$ correspond to the propagators of $W$, the decomposition of $\tau(W)$ induces a partition of $\cP$.
+\end{proof}
+
+\subsection{Matroid properties of exact subdiagrams}
+
+Since Corollary \ref{uniqueproppartitioncor} allows us to decompose any admissible Wilson loop diagram into a collection of maximal exact subdiagrams, in this section we examine the matroid properties of exact subdiagrams more closely.
+
+\begin{dfn}\label{matroid contraction}
+Let $M = (E,\cB)$ be a matroid, and $S \subseteq E$. The {\em contraction} of $M$ by $S$ is the matroid $M/S = (E \setminus S, \cB / S)$, where
+\[\cB / S = \{B \setminus S \ \big| \ |B\cap S | \text{ is maximal amonst all }B \in \cB\}.\]
+\end{dfn}
+
+In \cite{wilsonloop}, Agarwala and Amat show that certain subdiagrams of $W$ can be realized as contractions of $M(W)$:
+
+\begin{lem} \label{contractsubdiaglem} \cite[Theorem 3.33]{wilsonloop} 
+Let $W = (\cP, n)$ be an admissible Wilson loop diagram and $P \subseteq \cP$.
+If the set $V(P)^c$ has rank $|P^c|$, then the matroid defined by the subdiagram $(P, V(P))$ is equal to the contraction $M(W)/V(P)^c$.
+\end{lem}
+
+In Lemma \ref{maxexactcomplementrank} below we show that every exact subdiagram satisfies the rank condition of Lemma \ref{contractsubdiaglem}.
+In order to do this, we first examine the properties of the set by which we contract.
+
+\begin{dfn}\label{def prop flat}
+Let $W = (\cP,n)$ be an admissible Wilson loop diagram and $P \subseteq \cP$. The set $F(P) := V(P^c)^c$ is called the {\em propagator flat} of $P$.
+\end{dfn}
+Thus in Lemma \ref{contractsubdiaglem} above we would contract $M(W)$ by the propagator flat $F(P^c)$ of the {\em complement} of $P$ in order to study $(P,V(P))$.
+The justification for this notation is given by (1) of the next lemma: the set $F(P)$ consists of exactly those vertices which {\em only} support propagators in $P$.
+
+\begin{lem}\label{lem properties of prop flats}
+Let $F(P)$ be a propagator flat as defined above. Then
+\begin{enumerate}
+\item $F(P) = V(P) \setminus V(P^c)$.
+\item If $Q\subseteq P$ then $F(Q) \subseteq F(P)$.
+\item $F(P)$ is a flat of $M(W)$, thus justifying the name ``propagator flat''.
+\end{enumerate}
+\end{lem}
+\begin{proof}
+The proof of (1) and (2) are routine applications of the definition and are omitted.
+
+To prove (3), we need to show that $F(P)$ is maximally dependent.
+If $F(P) = [n]$ then this is automatic, so suppose not and let $v \in [n] \setminus F(P)$.
+In other words, $v \in V(P^c)$ and so $v$ supports some propagator $q \not\in P$.
+Let $S \subseteq F(P)$ be an independent set of maximal size.
+Then $\Prop(S) \subseteq P$ by (1), and no subset of $S$ supports fewer propagators than the number of vertices it contains (this is the definition of an independent set in $M(W)$).
+Since $v$ supports a new propagator $q \not\in P$, the set $S \cup \{v\} \subseteq F(P) \cup\{v\}$ also satisfies this independence condition.
+Thus $\rk(F(P) \cup\{v\}) = \rk(F(P)) + 1$, as required.
+\end{proof}
+
+\begin{lem} \label{lem decompose flat}Let $F$ be a flat in $M(W)$, and let $C \subseteq F$ be the union of all circuits contained in $F$. Then the following are true:
+\begin{enumerate}
+\item $C = F(\Prop (C))$, i.e. $C$ is a propagator flat.
+\item $F \setminus C$ is an independent set. Further, if $W$ does not contain any vertices of rank $0$, i.e. all vertices support at least $1$ propagator, then $F \setminus C$ is an independent flat.
+\end{enumerate}
+\end{lem}
+
+\begin{proof}
+(1) If $F$ is an independent flat, then $C = \emptyset$ and the statement is trivially true. Now suppose that $F$ is a dependent set, so $C$ is non-empty.
+
+Let $v \in C$.
+Clearly $\Prop(v) \subseteq \Prop(C)$, and so by Lemma \ref{lem properties of prop flats} we have $F(\Prop(v)) \subseteq F(\Prop(C))$.
+Since $v \in F(\Prop(v))$ by the definition of propagator flat, we have $v \in F(\Prop(C))$ as required.
+
+Now suppose there exists some $w \in  F(\Prop(C)) \setminus C$.
+Let $B$ be an independent subset of $C$ of maximal rank; we first show that $B \cup \{w\}$ is a dependent set in $M(W)$.
+Indeed, by \cite[Proposition 3.10]{wilsonloop}, there exists some $Q \subseteq \Prop(B)$ with $|Q| = |B|$ and such that $B$ is a basis in $M(Q,V(Q))$.
+We therefore have
+\[Q \subseteq \Prop(B) \subseteq \Prop(C),\]
+with $|\Prop(C)| = \rk(C)$ by Lemma \ref{lem facts about WLD matroids} and $|Q| = |B| = \rk(C)$ by the choice of $B$.
+Thus $Q = \Prop(C)$, and so $B$ is a basis in the matroid defined by $W' := (\Prop(C),V(\Prop(C)))$.
+All that remains is to note that $w \in F(\Prop(C)) \subseteq V(\Prop(C))$, i.e.
+$w$ is a vertex in $W'$; thus $B \cup\{w\}$ is dependent in $W'$, and hence also in $W$.
+
+Returning our attention to $M(W)$, the dependent set $B \cup \{w\}$ must contain a circuit $C'$, with $w \in C'$ since $B$ was an independent set.
+Now $C \cup C' = C \cup \{w\} \supsetneq C$ is a cycle, \hlfix{which contradicts the maximality of $C$}{as long as $w \in F$.
+I can't figure out why this has to be true?}
+
+For part (2), first note that $F \setminus C$ is automatically independent as it contains no circuits. Now suppose that all vertices in $W$ have rank $\geq 1$.
+
+For any $e \not\in F$, we certainly have $\rk((F\setminus C)\cup\{e\}) = \rk(F\setminus C) +1$ since $F$ is a flat.
+Now let $e \in C$, and suppose that $\rk((F\setminus C)\cup\{e\}) = \rk(F\setminus C)$.
+This implies that $(F\setminus C)\cup \{e\}$ is dependent, and hence contains a circuit.
+This circuit must contain at least two elements (since all vertices support at least one propagator), but this contradicts the fact that $C$ was the union of all circuits in $F$.
+
+Thus $\rk((F\setminus C)\cup \{e\}) = \rk(F\setminus C) + 1$ for any $e \not\in F\setminus C$, and hence $F\setminus C$ is a flat.
+\end{proof}
+
+\begin{cor} \label{classifyflats}
+If $F$ is a flat of a Wilson loop diagram, it can be written as the disjoint union of a cyclic propagator flat and an independent flat. \end{cor}
+
+In particular, any propagator flat can be written as a union of a cyclic propagator flat and an independent flat.
+
+%Finally, we note the differences between subdiagrams of Wilson loop diagrams, and restrictions or cotractions of the associated matroids.
+
+%Given any matroid, one may restrict it to a subset of the base set.
+The bases of the restricted matroid come from intersecting bases of the original with the subset.
+It is worth noting that a the matroid defined by a subdiagram is different from the restriction of the matroid of a Wilson loop diagram to a set of vertices.
+
+% \begin{dfn} \label{restrictiondfn}
+% For $W = (\cP, n)$, the restricted diagram, $W|_V$ is the matroid defined by only looking at the vertices $V \subset [n]$.
+% \end{dfn}
+
+% The key difference between a subdiagram and a restriction is that the propagator support function does not change in the case of restriction, while it may in the case of a subdiagram.
+In particular, for $v \in V$, $\Prop_W(v) = \Prop_{W|_V}(v)$, while $\Prop_{(P, V(P))} (v) = \Prop_W(v) \cap P$.
+
+% A subdiagram is more closely related to a contracted matroid.
+
+\begin{lem} \label{maxexactcomplementrank}
+Let $W = (\cP, n)$ be a Wilson loop diagram, and $P \subsetneq \cP$. Then:
+\begin{enumerate}
+\item If $(P,V(P))$ is an exact subdiagram in $W$, then $\rk(F(P^c)) = |P^c|$.
+\item If $(P,V(P))$ is a maximal exact subdiagram in $W$, then $F(P^c)$ is a cyclic flat.
+\end{enumerate}
+\end{lem}
+
+\begin{proof}
+We first verify that $F(P^c) = V(P)^c$ is non-empty and dependent for any exact subdiagram $(P,V(P))$.
+The definition of exactness means that the vertices $V(P)$ cannot support a larger set of propagators (otherwise $W$ would no longer be admissible).
+Therefore, since $P \subsetneq \cP$, there must be at least one propagator supported on $V(P)^c$, i.e.
+it cannot be empty.
+
+Since $W$ is admissible, we have $n \geq |\cP| + 4$. Rewriting this as
+\[|V(P)| + |F(P^c)|  \geq  |P| + |P^c| +4,\]
+and combining it with the fact that $|V(P)| = |P| + 3$ (from the exactness of $(P,V(P))$), we obtain
+\begin{equation}\label{eq F is dependent}|F(P^c)| > |P^c| \;.\end{equation}
+By Lemma \ref{lem properties of prop flats}, $F(P^c)$ is the set of vertices that {\em only} supports propagators in $P^c$, so in particular we have $\Prop(F(P^c)) = P^c$.
+Equation \eqref{eq F is dependent} is therefore saying that $F(P^c)$ supports fewer propagators than the number of vertices it contains, i.e.
+$F(P^c)$ is dependent.
+
+We address part (2) first. Suppose that $(P, V(P))$ is a maximal exact subdiagram; by Corollary \ref{classifyflats} we can decompose $F(P^c)$ as
+\begin{equation}\label{eq decompose F}F(P^c) = C \sqcup S,\end{equation}
+where $C$ is the largest cyclic flat contained in $F(P^c)$ and $S$ is an  independent set. Note that $C$ must be non-empty since $F(P^c)$ is dependent.
+
+Since $C = F(\Prop(C))$ by Lemma \ref{lem decompose flat}, define $Q := \Prop(C)^c$ so that we may write $C = F(Q^c) = V(Q)^c$. Furthermore, we have 
+\begin{equation}\rk(S) = |S| \leq \rk(F(P^c)) - \rk(C)  \leq |P^c| - \rk(C) \;, \label{increasingrank}\end{equation}
+where first equality comes from the fact that $S$ is an independent set, and the final inequality comes from Lemma \ref{lem facts about WLD matroids}(1).
+Since $\rk(C) = |\Prop(C)| = |Q^c|$ by Lemma \ref{lem facts about WLD matroids}(2), we can rearrange \eqref{increasingrank} to obtain the inequality
+\begin{equation} |P| + |S| \leq |P| + |P^c| - \rk(C) = |Q| \;. \label{Qsizebound}\end{equation}
+Furthermore, since $V(Q) = S \sqcup V(P)$ (by equation [ref] and the definition of $Q$) we may write  
+\begin{equation} |V(Q)| = |S| + |V(P)| = |S| + |P| +3 \label{VQsize} \;.\end{equation} 
+Combining this with \eqref{Qsizebound} gives $|V(Q)| - 3 \leq |Q|$.
+That is, either $W$ was not admissible, \hlfix{or $(P,V(P))$ was not a maximal exact subdiagram.}{This only follows if $P \subseteq Q$, which I can't see?
+We don't ever seem to use the fact that $S$ is empty/nonempty} In other words, $S$ cannot be non-empty, proving that $F(P^c)$ is a cyclic flat, and therefore of maximal rank.
+
+Let $(Q, V(Q))$ be an exact subdiagram that is not maximal, with \hlfix{$Q \subset P$ defining the maximal exact subdiagram above}{If I've understood this right, we would need to show that any exact subdiagram appears as $\Prop(C)^c$ for some maximal exact $P$ first} .
+
+Using the fact that $P$ and $Q$ are both exact diagrams, we have $|V(P)| = |V(Q)| + |P \setminus Q|$.
+Then $V(Q)^c = F(P^c) \cup S$, where $S$ is an independent set of size $|P \setminus Q|$ and with $(P \setminus Q) \subset \Prop (S)$.
+Therefore, \hlfix{$\rk (S) = |Q^c|$.}{I'm lost here.}
+\end{proof}
+
+In particular, any exact subdiagram $(P,V(P))$ satisfies the conditions of Lemma \ref{contractsubdiaglem} and can therefore be written as a contraction of $M(W)$ by the complementary propagator flat $F(P^c)$.
+
+Matroids coming from exact subdiagrams have an especially nice structure, as we now show.
+Recall from Section \ref{sec matroid background} that a uniform matroid of rank $r$ is one in which all sets of size $ \leq r$ are independent.
 
 \begin{thm} \label{exactcircuitlem}
-Let $(P, V(P))$ be a subdiagram of $W= (\cP, [n])$. This is an exact subdiagram if and only if it defines a uniform matroid of rank $|P|$.
+Let $W':= (P, V(P))$ be a subdiagram of an admissible Wilson loop diagram $W= (\cP, n)$. Then $W'$ is an exact subdiagram if and only if $M(W')$ is a uniform matroid of rank $|P|$.
 \end{thm}
@@
 \begin{proof}
-A uniform matroid of rank $r$ is one in which any set of size $ \leq r$ is independent.
-A circuit of rank $m$ is a set $C$ of rank $m$ and size $m+1$ such that every proper subset of $C$ is independent.
-I.e., \emph{a circuit is a minimal dependent set.} In other words, a matroid of rank $r$ is uniform if and only if all circuits have rank $r$.
-If $C$ is a circuit, then $|C| = r+1$.
-
-We prove the following claim: The set $V(P)$ contains no circuits, $C$, such that  $\rk C< |P|$ in $(P, V(P))$.
-Since the $V(P) = |P|+3$, $\rk V(P) \leq |P|$.
-This implies that all circuits $C$ of $(P, V(P))$ are of maximal rank, as desired.
-
-Consider a subdiagram $(P, V(P))$ of $W$.
-Suppose there is a circuit, $C \subset V(P)$ such that $\rk C = |\Prop (C) | = m < |P|$.
-The size of the complement of $C$ is $|V(P) \setminus C| = |V(P)| -(m+1)$.
-However, since $C$ does not contain any propagators outside of $\Prop (C)$, the set $V(P \setminus \Prop(C)) \subset V(P )\setminus C$.
-In otherwords, there are $|P| - m$ propagators supported on (at most) $|V(P)|-m -1$ vertices: \bas |V(P \setminus \Prop (C))| \leq |V(P)| - m-1\;.
-\eas Since $W$ is an admissible Wilson loop diagram, the subdiagram $(P, V(P))$ satisfies $|R| +3 \leq |V(R)|$ for all $R \subset P$.
-This gives \bas |P| - m +3 \leq V(P \setminus \Prop(C))\;.
-\eas These two inequalities are compatible if and only if \bas |P| +3 < |V(P)| \;.
-\eas
-
-In other words, the matroid associated to thet subdiagram $(P, V(P))$ is not uniform if and only if $(P, V(P))$ is not exact.
-\end{proof}
-
-In \cite{wilsonloops}, the authors show that all exact Wislon loop diagrams correspond to positroids.
-That is, they correspond to matroids that can be represented by elements of the positive Grassmannians $\Gr(|\cP|, |V|)$.
+It follows directly from the definitions that a matroid of rank $r$ is uniform if and only if all circuits have rank $r$; we therefore focus on the circuits of $M(W')$.
+
+We prove the following claim: $W'$ is exact if and only if $V(P)$ contains no circuits $C$ with $\rk C< |P|$ in $(P, V(P))$. Since $\rk(M(W')$ is bounded above by $|P|$, the result follows.
+
+Suppose $C \subseteq V(P)$ is a circuit of rank $m < |P|$; by Lemma \ref{lem facts about WLD matroids}, we know that $|\Prop(C)| = m$ as well, \hlfix{where we take $\Prop(C)$ in $W'$ rather than $W$}{I don't know if this caveat is necessary but we need $\Prop(C) \subseteq P$ later on}.
+The set $P \setminus \Prop(C)$ is thus nonempty, and we can consider the subdiagram $W'':= (P\setminus \Prop(C),V(P\setminus\Prop(C))$.
+By the density condition on subdiagrams of admissible diagrams, we have
+\[|V(P\setminus\Prop(C))| \geq |P\setminus\Prop(C)| + 3.\]
+It is easy to verify that $V(P\setminus\Prop(C)) \subseteq V(P)\setminus C$; since $C \subseteq V(P)$ and $\Prop(C) \subseteq P$, we can therefore rewrite the previous inequality as
+\[|V(P)| - (m+1) \geq |V(P\setminus\Prop(C))| \geq |P| - m + 3.\]
+Simplifying, we obtain $|V(P)| \geq |P| + 4$, i.e. $(P,V(P))$ is not an exact diagram.
+
+Conversely, suppose that $(P,V(P))$ is not exact, i.e. $|V(P)| \geq |P| +4$. We have 
+\[|V(P)| - (m+1) \geq |P| - m + 3\]
+as above, but \hlfix{we need to know that $P\setminus\Prop(C)$ is non-empty before we can complete the argument.}{and if we knew this, it would be immediate that $\rk(C) < |P|$}
+\end{proof}
+
+Before proving the main theorems of this section, we make a few observations about the geometry of matroids defined by exact diagrams.
+
+In \cite{wilsonloops}, the authors show that all exact Wilson loop diagrams correspond to positroids.
+That is, they correspond to matroids that can be represented by elements of the positive Grassmannians $\Gr(|\cP|, |V|)$.\todo{Check: positroids or totally positive?
+Why specify exactness?}
 
 \begin{dfn}
-Given a Wilson loop diagram $W$, define the positroid cell associated to a Wislon loop diagram, $\Sigma(W)$, to be the cell in the CW complex on $\Gr(|\cP|, |V|)$ defined by the realizations of $W$ that lie in $\Gr(|\cP|, |V|)$.
+Given a Wilson loop diagram $W$, define the positroid cell associated to a Wilson loop diagram, $\Sigma(W)$, to be the cell in the CW complex on $\Gr(|\cP|, |V|)$ defined by the \hlfix{realizations}{we haven't specified what this means}  of $W$ that lie in $\Gr(|\cP|, |V|)$.
 \end{dfn}
 
-With this definition in mind, we have the following corrolary:
+With this definition in mind, we have the following corollary:
 
@@
 
-Since the matroid defined by the subdiagram $(P , V(P))$ is not the same as the matroid associated to $W_{V(P)}$, one cannot say that the $W_{V(P)}$ is a uniform matroid.
+%Since the matroid defined by the subdiagram $(P , V(P))$ is not the same as the matroid associated to $W_{V(P)}$, one cannot say that the $W_{V(P)}$ is a uniform matroid.
 In fact, for any subset $U \subset V(P)$, $\rk_{W_{V(P)}}(U) \geq \rk_{(P , V(P))}(U)$.
@@
 
-To avoid the issue of exact diagrams being subdiagrams of other exact subdiagrams (for instance, any subdiagram $(q, V_q)$, for $q \in \cP$ is exact), I introduce a definition.
-
-\begin{dfn}
-We say $(P, V(P))$ is a maximal exact subdiagram of $W$ if there is not other exact subdiagram $(Q, V(Q))$ containing it.
-\end{dfn}
-
-Therefore, in keeping with Lemma \ref{lem triang to exact}, maximal exact subdiagrams of $W$ correspond to maximal triangular components of $\tau(W)$.
-In what follows, maximal exact subdiagrams/ maximal triangulations play a significant role.
-First, we show that maximal exact subdiagrams of an admissible Wilson loop diagram are disjoint.
-
-\begin{cor} \label{uniqueproppartitioncor}
-For $W = (\cP, n)$ can be uniquely decomposed into maximal exact subdiagrams. These subdiagrams maximal subdiagrams partition $\cP$.
-\end{cor}
-
-\begin{proof}
-This is a corollary to Lemma \ref{decompositionlem}, that gives a unique decomposition of polygon partitions, $\tau(W)$,  into maximal triangulated pieces, and Lemma \ref{lem triang to exact}, which gives a correspondence between triangulated components and exact subdiagrams.
-Futhermore, corrollary \ref{maxtriangdisjointcor} shows that the maximal triangulations are edge disjoint, and thus the propagators defining maximal exact subsets are also disjoint.
-Combining this with the fact that by construction, the decomposition of $\tau(W)$ accounts for all chord edges, gives the desired unique partition of propagators.
-\end{proof}
-
-Finally, we discuss some flats formed by the complement of the propagators defining an exact subdiagram.
-
-\begin{lem} \label{maxexactcomplementrank}
-Let $W = (\cP, n)$ be a Wilson loop diagram, and $(P, V(P))$ an exact subdiagram with $P \subsetneq \cP$.
-Then the set $V(P)^c = F(P^c)$ is a propagator flat of maximal rank  \bas \rk F(P^c) = |P^c| \;.
-\eas If $(P, V(P))$ is maximal, then $F(P^c)$ is cyclic.
-\end{lem}
-
-\begin{proof}
-By construction, $V(P)^c$ is a propagator flat.
-Furthermore, it is not empty.
-In particular, since $(P, V(P))$ is an exact subdiagram, the vertices $V(P)$ cannot support a larger set of propagators (otherwise $W$ would no longer be admissible).
-Therefore, since $P \subsetneq \cP$, $V(P)^c = F(P^c)$ is not an empty set.
-
-Notice that $n= |V(P)| + |F(P^c)| \geq |P| + |P^c| +4$, and $|V(P)| = |P| +3$.
-Therefore \bas |F(P^c)| > |P^c| \;.\eas In other words, $F(P^c)$ is a dependent flat.
-By corollary \ref{classifyflats} $F(P^c)$ is the union of a cyclic flat and an independent flat.
-
-Let $(P, V(P))$ be maximal exact subdiagram.
-Suppose $F(P^c) = C \cup F$, where $C$ is the largest cyclic flat contained in $F(P^c)$ and $F$ is a non-empty independent set.
-Since $C = F(\Prop(C))$, we can write $V(Q)^c = F(\Prop(C))$, with \ba Q = (\Prop(C))^c \label{Qdef}\;.
-\ea Furthermore, \ba \rk(F) = |F| \leq \rk(F(P^c)) - \rk(C)  \leq |P^c| - \rk(C) \;.
-\label{increasingrank}\ea The first equality comes from the fact that $F$ is an independent set.
-Combining \eqref{Qdef} and \eqref{increasingrank} gives \ba |P| + |F| \leq |P| + |P^c| - \rk(C) = |Q| \;.
-\label{Qsizebound}\ea Furthermore, since $V(Q) = F \cup V(P)$, we may write  \ba |V(Q)| = |F| + |V(P)| = |F| + |P| +3 \label{VQsize} \;.\ea Combining this with \eqref{Qsizebound} gives $|V(Q)| - 3 \leq |Q|$.
-That is, either $W$ was not admissible, or $(P,V(P))$ was not a maximal exact subdiagram.
-In otherwords, $F$ cannot be non-empty, proving that $F(P^c)$ is a cyclic flat, and therefore of maximal rank.
-
-Let $(Q, V(Q))$ be an exact subdiagram that is not maximal, with $Q \subset P$ defining he maximal exact subdiagram above.
-Then by lemma \ref{??} $|V(P)| = |V(Q)| + |P \setminus Q|$.
-Let $F(P^c)$ be the cyclic set defined as the complement of $V(P)$.
-Then $V(Q)^c = F(P^c) \cup F$, where $F$ is an independent set of size $|P \setminus Q|$ and with $(P \setminus Q) \subset \Prop (F)$.
-Therefore, $\rk (F) = |Q^c|$.
-\end{proof}
-
-In other words, by Lemma \ref{contractsubdiaglem}a maximally exact subdiagram $(P, V(P))$  can be written as a contraction by the complementary propagator flat: \bas (P, V(P)) = W/F(P^c) \;.\eas
-
-Now I am ready to prove the main theorem of this section.
-
-\begin{thm}
+\subsection{Matroids and equivalent diagrams}
+\note{Si\^an postponed reading this section until the earlier ones are fixed.}
+Now we are ready to prove the main results of this section, namely that two Wilson loop diagrams define the same matroid if and only if they are equivalent (Theorem [ref]) and a formula for the number of Wilson loop diagrams in a given equivalence class (Corollary [ref]).
+
+\begin{thm}\label{same matroid iff equiv}
 Let $W= (\cP, [n])$ and $W'= (\cP', [n])$ be two Wilson Loop diagrams. They define the same matroid if and only if $W \sim W'$.
@@
 Write $F_i = F(P_i)$ and $F'_i = F(P^{'c}_i)$ to be the complementary cyclic flats.
-By Lemma \ref{??} $M/F_i$ is a uniform matroid.
+By Lemma \ref{exactcircuitlem} $M/F_i$ is a uniform matroid.
 Thereofore, $k = l$, and we may write $V(P_i) = V(P'_i)$.
@@
 
-\begin{cor}
+\begin{cor}\label{number of equiv diagrams}
   Let $W$ be an admissible Wilson loop diagram where the sizes of the supports of the nontrivial maximal connected exact subdiagrams are $n_1, n_2, \ldots, n_j$.

### 2018-09-26 General WLD combinatorics.tex
hopefully clarified proof of lem 2.9

@@
 If $W = (\cP, n)$ is an admissible Wilson loop diagram, then $\tau(W)$ is a simple planar graph whose outer face is a cycle.
-It is embedded such that the vertices all lie on this infinite face.
+It is embedded such that the vertices all lie on this infinite face\footnote{That is, it is an \emph{outerplanar} graph}.
 These vertices are cyclically ordered, with a choice of first vertex giving it an additional compatible linear order.
@@
 
+By \emph{splitting} a vertex $v$ we will mean replacing $v$ by new vertice $v_1, v_2,\ldots, v_{\text{deg}(v)}$ such that each $v_i$ as exactly one neighbour and the union of the neighbourhoods of the $v_i$ is the neighbourhood of $v$.
+
 Let $T(W)$ be the dual graph of $\tau(W)$ with the vertex corresponding to the infinite face split.
-In other words, place a vertex on each finite face of $\tau(W)$.
+%In other words, place a vertex on each finite face of $\tau(W)$.
 These vertices are connected if there is a chord edge separating the edges.
 Furthermore, if the face is bounded by an edge of the polygonal cycle of $\tau(W)$, the corresponding vertex gets a leaf edge for each such boundary.
-Since $\tau(W)$ is a simple planar graph by Lemma \ref{tausimpleplanarlem}, $T(W)$ is an uniquely defined graph.
-
-We claim that $T(W)$ is a tree.
+Since $\tau(W)$ is an embedded graph (with a fixed distinguished embedding) by Lemma \ref{tausimpleplanarlem}, $T(W)$ is an uniquely defined graph.\note{The fixed embedding is important, because otherwise you only have a unique planar dual if the graph is 3-connected which this one isn't.
+I'm just noting that here so that everyone knows why I added the part about the embedding and then we can take this comment out.}
+
+Furthermore $T(W)$ is a tree because it is connected, has $n+k+1$ vertices ($k+1$ from the internal faces of $\tau(W)$ and $n$ from the outer face) and $n+k$ edges (since $\tau(W)$ has $n+k$ edges).
+Additionally, since $\tau(W)$ is simple, $T(W)$ has no vertices of degree $2$.
+
+%We claim that $T(W)$ is a tree.
 Since $\tau(W)$ is a planar graph with $k$ chord edges and no internal vertices, there are $k+1$ internal faces of $\tau(W)$.
@@
 
-By construction, each face of $\tau(W)$ is a polygon.
+Split every vertex of $T(W)$ which has degree $>3$.
+%By construction, each face of $\tau(W)$ is a polygon.
 Therefore, each vertex of $T(W)$ is at least 3 valent (one for each edge of the polygon).
 \hlfix{If split each vertex of $T(W)$ if it is strictly greater than $3$ valent.}{???} (In other words, we fail to split exactly when the face is a triangle).
-The connected components of $T(W)$ correspond to the decomposition of $\tau(W)$ into maximal triangulated pieces and edges originally in the polygon of $\tau(W)$.
-Let $f$ be the forest thus obtained.
-The vertices of $f$ either have valence 1, (if they correspond leaf vertices) or 3,  (if they correspond to triangulated faces).
-Subtrees with no trivalent vertices correspond to either edges in the polygon of $\tau(W)$, if they were originally leaves of $T(W)$, or to maximal trivial triangulations.
+The connected components of $T(W)$ correspond to the decomposition of $\tau(W)$ into maximal triangulated pieces and edges originally in the polygon of $\tau(W)$.  Let $f$ be the forest thus obtained.
+The vertices of $f$ either have degree 1 or 3.
+%, (if they correspond leaf vertices) or 3,  (if they correspond to triangular faces).
+Trees of $f$ with no trivalent vertices correspond to either edges in the polygon of $\tau(W)$, if they were originally leaves of $T(W)$, or to maximal trivial triangulated pieces.
 Splitting at all the faces that are not triangles ensures maximality of the decomposition.

### 2018-09-28 General WLD combinatorics.tex
responding to some of Sian's comments on 2.19 and 2.21

@@
 $w$ is a vertex in $W'$; thus $B \cup\{w\}$ is dependent in $W'$, and hence also in $W$.
+This also implies that $\rk(F\cup w) = \rk(F)$ since $B\subseteq F$ and so since $F$ is a flat we must have $w\in F$.
 
 Returning our attention to $M(W)$, the dependent set $B \cup \{w\}$ must contain a circuit $C'$, with $w \in C'$ since $B$ was an independent set.
-Now $C \cup C' = C \cup \{w\} \supsetneq C$ is a cycle, \hlfix{which contradicts the maximality of $C$}{as long as $w \in F$.
-I can't figure out why this has to be true?}
+Now $C \cup C' = C \cup \{w\} \supsetneq C$ is a cycle which, since $w\in F$, contradicts the maximality of $C$.
 
@@
 
-Suppose $C \subseteq V(P)$ is a circuit of rank $m < |P|$; by Lemma \ref{lem facts about WLD matroids}, we know that $|\Prop(C)| = m$ as well, \hlfix{where we take $\Prop(C)$ in $W'$ rather than $W$}{I don't know if this caveat is necessary but we need $\Prop(C) \subseteq P$ later on}.
-The set $P \setminus \Prop(C)$ is thus nonempty, and we can consider the subdiagram $W'':= (P\setminus \Prop(C),V(P\setminus\Prop(C))$.
+Suppose $C \subseteq V(P)$ is a circuit of rank $m < |P|$; by Lemma \ref{lem facts about WLD matroids}, we know that $|\Prop_{W'}(C)| = m$ as well, where the subscript to $\Prop$ specifies the diagram we are working in.
+Observe that $\Prop_{W'}(C)\subseteq P$ by definition.
+The set $P \setminus \Prop_{W'}(C)$ is thus nonempty, and we can consider the subdiagram $W'':= (P\setminus \Prop_{W'}(C),V(P\setminus\Prop_{W'}(C))$.
 By the density condition on subdiagrams of admissible diagrams, we have
-\[|V(P\setminus\Prop(C))| \geq |P\setminus\Prop(C)| + 3.\]
-It is easy to verify that $V(P\setminus\Prop(C)) \subseteq V(P)\setminus C$; since $C \subseteq V(P)$ and $\Prop(C) \subseteq P$, we can therefore rewrite the previous inequality as
+\[|V(P\setminus\Prop_{W'}(C))| \geq |P\setminus\Prop_{W'}(C)| + 3.\]
+It is easy to verify that $V(P\setminus\Prop_{W'}(C)) \subseteq V(P)\setminus C$; since $C \subseteq V(P)$ and $\Prop_{W'}(C) \subseteq P$, we can therefore rewrite the previous inequality as
 \[|V(P)| - (m+1) \geq |V(P\setminus\Prop(C))| \geq |P| - m + 3.\]
@@
 
-Conversely, suppose that $(P,V(P))$ is not exact, i.e. $|V(P)| \geq |P| +4$. We have 
-\[|V(P)| - (m+1) \geq |P| - m + 3\]
-as above, but \hlfix{we need to know that $P\setminus\Prop(C)$ is non-empty before we can complete the argument.}{and if we knew this, it would be immediate that $\rk(C) < |P|$}
+Conversely, suppose that $W'$ is not exact and for a contradiction suppose also that $M(W')$ is uniform of rank $|P|$.
+Take $p \in P$.
+Then $|V(P)\setminus V(p)| = |V(P)| - 4 \geq |P|$ by non-exactness.
+By uniformity there is an independent set of size $|P|$ in $V(P)\setminus V(p)$.
+This is impossible because the submatrix corresponding to this independent set has $|P|$ rows but the one corresponding to $p$ is all $0$ one of them is all 0 so it cannot be full rank.
+%suppose that $(P,V(P))$ is not exact, i.e. $|V(P)| \geq |P| +4$. We have 
+%\[|V(P)| - (m+1) \geq |P| - m + 3\]
+%as above, but \hlfix{we need to know that $P\setminus\Prop(C)$ is non-empty before we can complete the argument.}{and if we knew this, it would be immediate that $\rk(C) < |P|$}
 \end{proof}

### 2018-10-29 General WLD combinatorics.tex
Comment response 2.17-2.20
All my added material is in violet. Will not change until approved, pending master discussion.

@@
 \newcommand{\hlnew}[2]{\texthl{#1}\todo[color=green!40]{#2}}
+\newcommand{\sanote}{\todo[color=violet!30]}
 \newcommand{\note}{\todo[color=green!40]}
@@
 \item $C = F(\Prop (C))$, i.e. $C$ is a propagator flat.
-\item $F \setminus C$ is an independent set. Further, if $W$ does not contain any vertices of rank $0$, i.e. all vertices support at least $1$ propagator, then $F \setminus C$ is an independent flat.
+\item $F \setminus C$ is an independent \st{set.
+Further, if $W$ does not contain any vertices of rank $0$, i.e.
+all vertices support at least $1$ propagator, then $F \setminus C$ is an independent} flat.
+\sanote{$F$ and $C$ both contain all vertices of rank $0$ by definition}
 \end{enumerate}
@@
 
-For part (2), first note that $F \setminus C$ is automatically independent as it contains no circuits. Now suppose that all vertices in $W$ have rank $\geq 1$.
+For part (2), first note that $F \setminus C$ is automatically independent as it contains no circuits. Now suppose that all vertices in $W$ have rank $\geq 1$. \sanote{can get rid of?}
 
@@
 \begin{lem} \label{maxexactcomplementrank}
-Let $W = (\cP, n)$ be a Wilson loop diagram, and $P \subsetneq \cP$. Then:
+Let $W = (\cP, n)$ be a Wilson loop diagram, and $P \subsetneq \cP$. Then: \note{should hold if $P = \cP$.}
 \begin{enumerate}
@@
 \end{lem}
+
+{\color{violet} Note that by definition, since $F(P^c)$ has at $|P^c|$ propagators in it, this is an upper bound on the rank. However, showing equality on the first part is harder.}
 
@@
 \begin{equation}\label{eq decompose F}F(P^c) = C \sqcup S,\end{equation}
-where $C$ is the largest cyclic flat contained in $F(P^c)$ and $S$ is an  independent set. Note that $C$ must be non-empty since $F(P^c)$ is dependent.
-
-Since $C = F(\Prop(C))$ by Lemma \ref{lem decompose flat}, define $Q := \Prop(C)^c$ so that we may write $C = F(Q^c) = V(Q)^c$. Furthermore, we have 
+where $C$ is the largest cyclic flat contained in $F(P^c)$ and $S$ is an  independent set.
+Note that $C$ must be non-empty since $F(P^c)$ is dependent.
+{\color{violet}We proceed by showing that $S$ must be empty, forcing $F(P^c)$ to be a cyclic flat.} \sanote{Does this fix confusion later?}
+
+Since $C = F(\Prop(C))$ by Lemma \ref{lem decompose flat}, define $Q := \Prop(C)^c$ so that we may write $C = F(Q^c) = V(Q)^c$.
+{\color{violet}Note that since $C \subseteq F(P^c)$, $P \subseteq Q$.
+}Furthermore, we have
 \begin{equation}\rk(S) = |S| \leq \rk(F(P^c)) - \rk(C)  \leq |P^c| - \rk(C) \;, \label{increasingrank}\end{equation}
@@
 
+{\color{violet}REPLACE BELOW WITH: Let $P$ be a maximal exact subdiagram as above, and let $(R, V(R))$ be an exact subdiagram that is not maximal. That is, $R \subsetneq P$. }
+
 Let $(Q, V(Q))$ be an exact subdiagram that is not maximal, with \hlfix{$Q \subset P$ defining the maximal exact subdiagram above}{If I've understood this right, we would need to show that any exact subdiagram appears as $\Prop(C)^c$ for some maximal exact $P$ first} .
+\sanote{why?
+I don't understand your confusion}
+
+{\color{violet}POSSIBLY REPLACE BELOW WITH: Since $R \subset P$, $V(P) = V(R) \sqcup S$.
+Since $P$ and $R$ both define exact subdiagrams, we may write $|V(P)| = |V(R)| + |P \setminus R|$, where $S$ is a vertex set of size $|P \setminus R|$ with $(P \setminus R \subset \Prop(S)$.
+Since $\rk V(P) =  \rk V(R) + |P \setminus R|$, $S$ is independent.
+Taking the complements, we may write \bas F(R^c ) = F(P^c) \sqcup S \;.\eas Since $S$ is an independent set of vertices of the correct size supporting the appropriate propagators, this gives $ \rk F(R^c ) = |R^c|$.}
 
@@
 Then $V(Q)^c = F(P^c) \cup S$, where $S$ is an independent set of size $|P \setminus Q|$ and with $(P \setminus Q) \subset \Prop (S)$.
-Therefore, \hlfix{$\rk (S) = |Q^c|$.}{I'm lost here.}
+Therefore, \hlfix{$\rk (F(Q^c)) = |Q^c|$.}{I'm lost here.} \sanote{better if I fix typo?}
 \end{proof}

### 2018-10-30 General WLD combinatorics.tex
some changes while talking

@@
 
-\begin{dfn}\label{equivdfn} \todo{I feel like I need some sort of uniqueness of partition result to even be able to define this well. Or something. Can we discuss?}
-There is an equivalence relationship on the set of admissible Wilson loops diagrams generated by the following binary relation: $W = (\cP, n) \sim W'= (\cP', n)$ if
+\begin{dfn}\label{equivdfn} 
+There is an equivalence relationship on the set of admissible Wilson loops diagrams given by the transititve closure the following binary relation: $W = (\cP, n) \sim W'= (\cP', n)$ if
 \begin{enumerate}
@@
 The vertex set $\{4,5, 8, 1\}$ is not a triangulation in either polygon partition.
-\note{do we want a picture of a dual tree here?
-Being lazy}
+\note{Put a picture of a dual tree.
+Make a comment that the embedding is required to obtain uniqueness of the dual}
 \end{eg}
@@
 Furthermore, if the face is bounded by an edge of the polygonal cycle of $\tau(W)$, the corresponding vertex gets a leaf edge for each such boundary.
-Since $\tau(W)$ is an embedded graph (with a fixed distinguished embedding) by Lemma \ref{tausimpleplanarlem}, $T(W)$ is an uniquely defined graph.\note{The fixed embedding is important, because otherwise you only have a unique planar dual if the graph is 3-connected which this one isn't.
-I'm just noting that here so that everyone knows why I added the part about the embedding and then we can take this comment out.}
+Since $\tau(W)$ is an embedded graph (with a fixed distinguished embedding) by Lemma \ref{tausimpleplanarlem}, $T(W)$ is an uniquely defined graph.
 

### 2018-10-30 General WLD combinatorics.tex
added a new section 3.1 (containing Sian's lemma) and a few small results to section 3.2 (which used to be 3.1)

@@
 \section{Geometry of Wilson Loop diagram}\label{sec GN algorithm}
-Since Wilson loop diagrams correspond to positroids, it is natural to understand the subspace of $\Gr(|\cP|, n)$ they define.
+Since Wilson loop diagrams correspond to positroids, it is natural to study the subspace of $\Gr(|\cP|, n)$ they define.
 
@@
 Also talk about Le diagrams.
+
+Throughout this section, $W = (\cP,n)$ is an admissible Wilson loop diagram with $k$ propagators.
+
+\subsection{Some setup results about propagators}
+
+\note{rank probably isn't a good word; do we have a better one?}
+\begin{dfn}\label{vertex rank}
+Let $i$ be a vertex in $W$. We define the {\bf rank} of $i$ to be $|Prop(i)|$, i.e. the number of propagators supported on $i$.
+\end{dfn}
+
+\begin{dfn}\label{props inside p}
+Let $p$ be a propagator supported on $(i,j)$ in $W$.
+The region bounded by $p$ and the edge of the Wilson loop diagram from $i$ to $j+1$ is refered to as the region {\bf inside} $p$, and the complement is the region {\bf outside }$p$.
+The set of propagators inside (resp.
+outside) $p$ are those lying in the region inside (resp.
+outside) $p$, excluding $p$ itself.
+\end{dfn}
+Note that this depends on the order of $i$ and $j$: if we view $p$ as supported on $(j,i)$ (for example, if we are working with the $<_j$ order on vertices) then the regions inside and outside $p$ are swapped.
+
+\begin{dfn}\note{right now this doesn't depend on the order of $i$ and $j$, but that might matter later on?}
+Let $p$ be a propagator supported on the vertices $(i,i+1,j,j+1)$.  Define the \textit{length} of $p$ to be 
+\[\ell(p) = min\big\{|[i+1,j]|,|[j+1,i]|\big\}.\]
+\end{dfn}
+
+\begin{rmk}\label{rem:props of length 2 and 3}
+The following observations about propagators of short length in $W$ are easily verified:
+\begin{itemize}
+\item If every vertex in $W$ supports at least one propagator, then $W$ admits at least one propagator of length 2.
+\item If $p = (i,i+1,i+3,i+4)$ is a propagator of length 3, then the middle vertex $i+2$ supports at most one propagator.
+\end{itemize}
+\end{rmk}
+
+\begin{dfn}
+Define the restriction of $W$ to a region $[i,j]$ to be the subdiagram obtained by forgetting all propagators not wholly supported on vertices in the cyclic interval $[i,j]$.
+Denote this diagram by $W_{[i,j]}$.
+\end{dfn}
+
+If $p$ is a propagator supported on $(i,i+1,j,j+1)$, then we can consider two obvious restrictions of $D$, namely $D_{[i,j+1]}$ and $D_{[j,i+1]}$.
+Clearly all other propagators $q\neq p$ appear in exactly one of these subdiagrams, while $p$ appears in both.
+In this case, we will say that $p$ \textit{bounds the regions} $[i,j+1]$ and $[j,i+1]$; the ordering of the start and end points allow us to identify one or the other region unambiguously.
+
+The following lemma establishes certain configurations of propagators that must exist in any admissible diagram with no unsupported vertices.
+We make use of this result in several induction proofs below.
+
+\begin{lem}\label{lem sian}
+  Let $W$ be an admissible WLD in which each vertex supports at least one propagator.  Then exactly one of the following things occurs.
+  \begin{enumerate}
+    \item $W$ has a propagator of length 3, say $p =  (i,i+3)$, with a propagator of length 2 inside it.
+    \item $W$ admits no propagators of length 3, and there exists a pair of propagators with the property that the first propagator is $(i, i+1, i+2, i+3)$, the second is $(i+2, i+3, i+4, i+5)$, and no other propagator ends on the edge $(i+2, i+3)$.
+  \end{enumerate}
+\end{lem}
+
+\note{This is the proof of the old result pasted without modification so we can identify where it needs editing. For some reason the WLD was named $D$ instead of $W$.}
+\begin{proof}
+We will prove the following stronger result: that $D$ admits a pair of propagators of length 2 in the following configuration:
+\begin{equation}\label{eq:2 prop config}
+\begin{tikzpicture}[baseline=(current bounding box.east)]
+\pgfmathsetmacro{\radius}{2}
+\pgfmathsetmacro{\angle}{20}
+
+\begin{scope}
+\clip (-\radius*1.1,\radius*0.25) rectangle (\radius*1.1,\radius*1.25);
+
+\begin{scope}
+\clip (-\radius*1.1,\radius*0.45) rectangle (\radius*1.1,\radius*1.1);
+\draw[-] (0,0) circle[radius=\radius cm];
+\end{scope}
+
+% vertices
+\foreach \i in {2,3,...,7}{
+	\draw (\angle*\i:\radius*0.98) --  (\angle*\i:\radius*1.02);
+}
+
+\begin{scope}
+\clip (0,0) circle[radius=\radius];
+\draw[propagator] (2.5*\angle:\radius*1.1 cm) to [bend left=90] (4.35*\angle:\radius*1.1 cm);
+\draw[propagator] (4.65*\angle:\radius*1.1 cm) to [bend left=90] (6.5*\angle:\radius*1.1 cm);
+
+\end{scope}
+
+\node at (80:\radius*1.1) {\tiny $j$};
+\node at (100:\radius*1.1) {\tiny $j+1$};
+\node at (90:\radius*0.5) {\small $s_j = s_{j+1} = 2$};
+
+\end{scope}
+\end{tikzpicture}
+\end{equation}
+
+We will inductively construct a sequence of pairs of propagators $(p_r,q_r)$ satisfying: $\ell(p_r) = 2$, and $p_r$ either forms part of a configuration \eqref{eq:2 prop config} in $D$ or there is a propagator $q_r$ satisfying
+\begin{itemize}
+\item $\ell(q_r) \geq 4$.
+\item $q_r$ bounds a region of $D$ which contains strictly fewer vertices than that bounded by $q_{r-1}$ and the restriction of $D$ to this region does not contain any of the propagators $p_1, \dots, p_r$.
+\end{itemize}
+Since $D$ contains finitely many vertices, this must eventually terminate in a configuration of the form \eqref{eq:2 prop config}.
+
+Start by choosing a propagator $p_1$ of length 2 in $D$ (which exists by Remark~\ref{rem:props of length 2 and 3}), and write $(j_1,j_1+1,j_1+2,j_1+3)$ for its support.
+If it is part of a configuration \eqref{eq:2 prop config} we are done, so suppose otherwise: since $s_{j_1} \geq 2$, there must exist a second propagator $q_1$ of length $\geq 4$ which starts on edge $(j_1,j_1+1)$.
+This bounds a region $[i_1,j_1+1]$ which does not contain $p_1$.
+
+Now suppose $q_{r}$ exists by the induction hypothesis and bounds a region $[i_r,j_r+1]$.
+Consider the restricted diagram $D_r:=D_{[i_r,j_r+1]}$; clearly we must have $s_l \geq 2$ for all $l \in [i_r+2,j_r-1]$ (which is a non-empty interval since $\ell(q_r) \geq 4$), while $s_l\geq 1$ for $l \in \{i_r,i_r+1,j_r,j_r+1\}$.
+
+By Remark~\ref{rem:props of length 2 and 3}, $D_r$ admits at least one propagator of length 2 and none of length 3.
+Let $p_{r+1}$ be a propagator of length 2 in $D_r$; if it forms part of the configuration \eqref{eq:2 prop config} then we are done.
+Otherwise, at least one endpoint of $p_{r+1}$ lies on an edge contained in the non-empty interval $[i_r+2,j_r-1]$, and so there is at least one other propagator connected to this edge.
+Up to symmetry, there are three possibilities:
+
+% this was 100% a productive use of my time
+
+\[\begin{tabular}{ccc}
+% possibility 1
+\begin{tikzpicture}
+\pgfmathsetmacro{\radius}{2}
+\pgfmathsetmacro{\angle}{15}
+\begin{scope}
+\clip (-\radius*1.1,0) rectangle (\radius*1.1,\radius*1.1);
+
+% vertices 
+\foreach \i in {2,3,4,6,7,8,9,10}{
+	\draw (\angle*\i:\radius*0.98) --  (\angle*\i:\radius*1.02);
+}
+
+% \dots 
+\foreach \i in {1,2,3}{
+	\node at (65 + \i*5:\radius cm) {$\cdot$};
+}
+
+\begin{scope} % this scope contains the propagators
+\clip (0,0) circle[radius=\radius];
+
+\draw[propagator] (\angle*2.4:\radius*1.2 cm) to [bend left=30] (\angle*9.7:\radius*1.2 cm); % q_r
+\draw[propagator] (\angle*7.7:\radius*1.1 cm) to [bend left=90] (\angle*9.45:\radius*1.1 cm); % p_{r+1}
+
+% grey prop begins here
+
+\begin{scope}
+\clip (\angle*7.5:\radius cm) circle[radius=\radius*0.45cm];
+\draw[light-gray,propagator,seconddash] (\angle*6:\radius*1.02 cm) circle[x radius=\radius*0.4cm, y radius = \radius*0.3cm];
+\end{scope}
+
+\begin{scope}
+\clip (0,0) circle[radius=\radius];
+\clip (\angle*7.5:\radius cm) circle[radius=\radius*0.4cm];
+\draw[light-gray,propagator,firstdash] (\angle*6:\radius*1.02 cm) circle[x radius=\radius*0.4cm, y radius = \radius*0.3cm];
+\end{scope}
+
+\begin{scope}
+\clip (\angle*7.5:\radius cm) circle[radius=\radius*0.3cm];
+\clip (0,0) circle[radius=\radius];
+\draw[light-gray,propagator] (\angle*6:\radius*1.02 cm) circle[x radius=\radius*0.4cm, y radius = \radius*0.3cm];
+\end{scope}
+% end gray prop
+
+\end{scope}
+
+\node at (90:\radius*0.30 cm) {\tiny $q_r$};
+\node at (\angle*8:\radius*0.73) {\tiny $p_{r+1}$};
+\node[light-gray] at (\angle*4.9:\radius*0.77 cm) {\tiny $q_{r+1}$};
+\node at (2*\angle:\radius*1.1) {\tiny $i_r$};
+\node at (9*\angle:\radius*1.1) {\tiny $j_r$};
+
+% circle/edges; needs to happen last to overlap gray
+\begin{scope}
+\clip (-\radius*1.1,0.9) rectangle (\radius*1.1,\radius*1.1);
+\draw[-] (0,0) circle[radius=\radius cm];
+\end{scope}
+
+\end{scope} % ends the overall rectangle clipping
+\end{tikzpicture}
+
+&
+
+% possibility 2
+\begin{tikzpicture}
+\pgfmathsetmacro{\radius}{2}
+\pgfmathsetmacro{\angle}{15}
+\begin{scope}
+% overall clipping to make the size sensible
+\clip (-\radius*1.1,0) rectangle (\radius*1.1,\radius*1.1);
+
+% vertices
+\foreach \i in {2,3,4,6,7,8,9,10}{
+	\draw (\angle*\i:\radius*0.98) --  (\angle*\i:\radius*1.02);
+}
+
+% \dots
+\foreach \i in {1,2,3}{
+	\node at (65 + \i*5:\radius cm) {$\cdot$};
+}
+
+\begin{scope} % props
+\clip (0,0) circle[radius=\radius cm]; 
+\draw[propagator] (\angle*2.4:\radius*1.2 cm) to [bend left=30] (\angle*9.6:\radius*1.2 cm); % q_r
+\draw[propagator] (\angle*6.7:\radius*1.1 cm) to [bend left=90] (\angle*8.6:\radius*1.1 cm); % p_{r+1}
+
+%% grey prop starts here
+
+\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.45cm];
+\draw[light-gray,propagator,seconddash] (\angle*4.5:\radius*1.3 cm) circle[y radius = 0.5*\radius cm,x radius=\radius*0.7cm];
+\end{scope}
+
+\begin{scope}
+\clip (0,0) circle[radius=\radius];
+\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.4cm];
+\draw[light-gray,propagator,firstdash] (\angle*4.5:\radius*1.3 cm) circle[y radius = 0.5*\radius cm,x radius=\radius*0.7cm];
+\end{scope}
+
+\begin{scope}
+\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.3cm];
+\clip (0,0) circle[radius=\radius];
+\draw[light-gray,propagator] (\angle*4.5:\radius*1.3 cm) circle[y radius = 0.5*\radius cm,x radius=\radius*0.7cm];
+\end{scope}
+% grey prop ends here
+
+\node at (90:\radius*0.32 cm) {\tiny $q_r$};
+\node at (\angle*7.75:\radius*0.75) {\tiny $p_{r+1}$};
+\node[light-gray] at (\angle*4.5:\radius*0.7 cm) {\tiny $q_{r+1}$};
+\node at (2*\angle:\radius*1.1) {\tiny $i_r$};
+\node at (9*\angle:\radius*1.1) {\tiny $j_r$};
+
+% circle/edges
+\begin{scope}
+\clip (-\radius*1.1,0.9) rectangle (\radius*1.1,\radius*1.1);
+\draw[-] (0,0) circle[radius=\radius cm];
+\end{scope}
+
+\end{scope} % ends overall clip
+\end{tikzpicture}
+
+&
+
+% possiblitiy 3
+\begin{tikzpicture}
+\pgfmathsetmacro{\radius}{2}
+\pgfmathsetmacro{\angle}{12}
+\begin{scope}
+\clip (-\radius*1.1,0) rectangle (\radius*1.1,\radius*1.1);
+
+% vertices
+\foreach \i in {2,3,6,7,8,9,12,13}{
+	\draw (\angle*\i:\radius*0.98) --  (\angle*\i:\radius*1.02);
+}
+
+% \dots
+\foreach \i in {1,2,3}{
+	\node at (44 + \i*5:\radius cm) {$\cdot$};
+	\node at (116 + \i*5:\radius cm) {$\cdot$};
+}
+
+\begin{scope} % props
+\clip (0,0) circle[radius=\radius cm];
+\draw[propagator] (\angle*2.4:\radius*1.2 cm) to [bend left=30] (\angle*12.6:\radius*1.2 cm); % q_r
+\draw[propagator] (\angle*6.5:\radius*1.1 cm) to [bend left=100] (\angle*8.5:\radius*1.05 cm); % p_{r+1}
+
+%  grey prop 1
+% not q_{r+1}
+\begin{scope}
+\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.45cm];
+\draw[light-gray,propagator,seconddash] (\angle*6.5:\radius*1.1 cm) to [bend left=90] (\angle*12.5:\radius*1.1cm);
+\end{scope}
+
+\begin{scope}
+\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.4cm];
+\draw[light-gray,propagator,firstdash] (\angle*6.5:\radius*1.1 cm) to [bend left=90] (\angle*12.5:\radius*1.1cm);
+\end{scope}
+\begin{scope}
+\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.3cm];
+\draw[light-gray,propagator] (\angle*6.5:\radius*1.1 cm) to [bend left=90] (\angle*12.5:\radius*1.1cm);
+\end{scope}
+% grey prop 1 ends here
+
+% grey prop 2
+% this is q_{r+1}
+\begin{scope}
+\clip (\angle*8.5:\radius cm) circle[radius=\radius*0.45cm];
+\draw[propagator,seconddash,light-gray] (\angle*8.8:\radius*1.1 cm) to [bend left=90] (\angle*12:\radius*1.1cm);
+\end{scope}
+
+\begin{scope}
+\clip (\angle*8.5:\radius cm) circle[radius=\radius*0.4cm];
+\draw[propagator,firstdash,light-gray] (\angle*8.8:\radius*1.1 cm) to [bend left=90] (\angle*12:\radius*1.1cm);
+\end{scope}
+
+\begin{scope}
+\clip (\angle*8.5:\radius cm) circle[radius=\radius*0.3cm];
+\draw[light-gray,propagator] (\angle*8.8:\radius*1.1 cm) to [bend left=90] (\angle*12:\radius*1.1cm);
+\end{scope}
+
+% grey prop 2 ends here
+
+\end{scope}
+
+\node at (90:\radius*0.15 cm) {\tiny $q_r$};
+\node at (\angle*7.5:\radius*0.83) {\tiny $p_{r+1}$};
+\node[light-gray] at (\angle*11:\radius*0.75 cm) {\tiny $q_{r+1}$};
+
+\node at (2*\angle:\radius*1.1) {\tiny $i_r$};
+\node at (12*\angle:\radius*1.1) {\tiny $j_r$};
+
+% overall circle
+\begin{scope}
+\clip (-\radius*1.1,0.7) rectangle (\radius*1.1,\radius*1.1);
+\draw[-] (0,0) circle[radius=\radius cm];
+\end{scope}
+
+\end{scope} % ends overall clip
+\end{tikzpicture}
+
+\end{tabular}
+\]
+In each case, the diagram indicates how to choose $q_{r+1}$ satisfying the induction hypothesis.
+In the third case, note that \textit{both} ends of $p_{r+1}$ must share their edge with a propagator of length $\geq 4$; the non-crossing hypothesis on propagators guarantees that at least one will bound a region not containing $p_{r+1}$.
+\end{proof}
 
@@
 If the propagator $p$ is removed at vertex $i$ according to the algorithm for $I_a$, we say that $p$ \emph{contributes} $i$ to $I_a$.
+Notationally, we represent this by allowing the $I_i$ symbol to represent a function as well as a set, as follows:
+\begin{dfn}\label{def I_i as a function}
+Let $W = (\cP, n)$ be an admissible Wilson loop diagram. For each $a \in [n]$, define a function $I_a : \cP \longrightarrow [n]$ by
+\[I_a(p) := \text{the vertex label that $p$ contributes to $I_a$ in Algorithm~\ref{alg:put GN on WLD},}\]
+for each $p \in \cP$.
+\end{dfn}
+
+\begin{lem}\label{lem no fourth vertex}
+Let $W$ be an admissible Wilson loop diagram containing at least one propagator. For any $i \in [n]$ and for any $p=(a,b)$ with $i\leq_i a <_i b$, we have $I_i(p) \neq b+1$.
+\end{lem}
+\begin{proof}
+Suppose for contradiction that we have $p = (a,b)$ with $i\leq_i a <_i b$ and $I_{i}(p) = b+1$. We may choose $p$ such that $|\interval{a+1}{b}|$ is minimal amongst propagators with this property.
+
+Since $I_i(p) \neq b$, there must exist a propagator $q$ inside of $p$ with $I_i(q) = b$.
+The propagator $q$ cannot end on the edge $(b-1,b)$, as this would contradict the minimality of $p$, so $q = (c,c+1,b,b+1)$ with $a <_i c <_i b$, and $I_i(q) = b$.
+
+In order for $q$ to remain unassigned until vertex $b$, there must be another propagator $r$ with an end on $(c,c+1)$ and $I_i(r) = c+1$; the only way this can occur is if $r$ is outside $q$ but inside $p$.
+Now $r$ contributes its fourth vertex to $I_i$, again contradicting the minimality of $p$.
+\end{proof}
+
+\begin{cor}\label{GN alg well defined}
+If $W$ is an admissible Wilson loop diagram with $k$ propagators, then Algorithm~\ref{alg:put GN on WLD} assigns exactly $k$ vertices to each $I_i$.
+\end{cor}
+\begin{proof}
+It follows from the proof of Lemma~\ref{lem no fourth vertex} that Algorithm~\ref{alg:put GN on WLD} can never reach the fourth vertex of a propagator's support (with respect to the starting vertex).
+Therefore if the algorithm starts at vertex $i$, it must have assigned vertices to all propagators by the time it reaches $i-1$, ensuring that $I_i$ contains exactly $k$ distinct vertices.
+\end{proof}
 
@@
 
+In an arbitrary Grassmann necklace, it is possible for an index $i$ to appear in no terms of the Grassmann necklace (a {\em loop}) or in all terms of the necklace (a {\em coloop}).
+Clearly any vertex of $W$ that supports no propagators will yield a loop [ref][check: is this iff?], but with Theorem [ref][cyclic intervals thm] in hand we can now easily verify that admissible Wilson loop diagrams do not admit coloops.
+
+\begin{cor}\label{no coloops}
+Grassmann necklaces coming from admissible Wilson loop diagrams have no coloops, that is no indices $a$ such that $a \in I_i$ for all $i$.
+\end{cor}
+\begin{proof}
+For any $a \in [n]$, $a-1$ is maximal with respect to the $<_{a}$ order. Therefore there is no propagator $p$ with $I_{a}(p) = a-1$ by Lemma~\ref{lem no fourth vertex}, i.e. $a-1 \not\in I_{a}$.
+\end{proof}
+
 \subsection{Dimension of the Wilson Loop cells}
@@
 
-\subsection{Some definitions and results that should probably be moved to section 3 but I don't know if anyone's editing that right now}
-
-It will often be useful to refer to the vertex label contributed by a propagator to a Grassmann necklace term.
-Notationally, we represent this by allowing the $I_i$ symbol to represent a function as well as a set, as follows:
-\begin{dfn}\label{def I_i as a function}
-Let $W = (\cP, n)$ be an admissible Wilson loop diagram. For each $i \in \interval{1}{n}$, define a function $I_i : \cP \longrightarrow \interval{1}{n}$ by
-\[I_i(p) := \text{the vertex label that $p$ contributes to $I_i$ in Algorithm~\ref{alg:put GN on WLD},}\]
-for each $p \in \cP$.
-\end{dfn}
-\todo{Depending where this ends up, possibly include an example here.}
-
-\begin{dfn}\label{props inside p}
-Let $p$ be a propagator supported on $(i,j)$.
-The region bounded by $p$ and the edge of the Wilson loop diagram from $i$ to $j+1$ is refered to as the region {\bf inside} $p$, and the complement is the region {\bf outside }$p$.
-The set of propagators inside (resp.
-outside) $p$ are those lying in the region inside (resp.
-outside) $p$, excluding $p$ itself.
-\end{dfn}
-Note that this depends on the order of $i$ and $j$: if we view $p$ as supported on $(j,i)$ then the regions inside and outside $p$ are swapped.
-
-\begin{lem}\label{lem no fourth vertex}
-Let $W$ be an admissible Wilson loop diagram containing at least one propagator. For any $i \in [n]$ and for any $p=(a,b)$ with $i\leq_i a <_i b$, we have $I_i(p) \neq b+1$.
-\end{lem}
-\begin{proof}
-Suppose for contradiction that we have $p = (a,b)$ with $i\leq_i a <_i b$ and $I_{i}(p) = b+1$. We may choose $p$ such that $|\interval{a+1}{b}|$ is minimal amongst propagators with this property.
-
-Since $I_i(p) \neq b$, there must exist a propagator $q$ inside of $p$ with $I_i(q) = b$.
-The propagator $q$ cannot end on the edge $(b-1,b)$, as this would contradict the minimality of $p$, so $q = (c,c+1,b,b+1)$ with $a <_i c <_i b$, and $I_i(q) = b$.
-
-In order for $q$ to remain unassigned until vertex $b$, there must be another propagator $r$ with an end on $(c,c+1)$ and $I_i(r) = c+1$; the only way this can occur is if $r$ is outside $q$ but inside $p$.
-Now $r$ contributes its fourth vertex to $I_i$, again contradicting the minimality of $p$.
-\end{proof}
-
-\begin{cor}\label{GN alg well defined}
-If $W$ is an admissible Wilson loop diagram with $k$ propagators, then Algorithm~\ref{alg:put GN on WLD} assigns exactly $k$ vertices to each $I_i$.
-\end{cor}
-\begin{proof}
-It follows from the proof of Lemma~\ref{lem no fourth vertex} that Algorithm~\ref{alg:put GN on WLD} can never reach the fourth vertex of a propagator's support (with respect to the starting vertex).
-Therefore if the algorithm starts at vertex $i$, it must have assigned vertices to all propagators by the time it reaches $i-1$, ensuring that $I_i$ contains exactly $k$ distinct vertices.
-\end{proof}
-
-\begin{cor}\label{no coloops}
-Grassmann necklaces coming from admissible Wilson loop diagrams have no coloops, that is no indices $a$ such that $a \in I_i$ for all $i$.
-\end{cor}
-\begin{proof}
-For any $a \in [n]$, $a-1$ is maximal with respect to the $<_{a}$ order. Therefore there is no propagator $p$ with $I_{a}(p) = a-1$ by Lemma~\ref{lem no fourth vertex}, i.e. $a-1 \not\in I_{a}$.
-\end{proof}
-
-\subsection{actual beginning of section 4; this subsection header can go away once the results above have found their place}
-
 The results of Section~\ref{sec GN algorithm} allow us to relate the position of propagators in a Wilson loop diagram $W$ to minors of $C(W)$, which we use in this section to understand the denominator of the integral $I(W)$ associated to a Wilson loop diagram (see Definition~\ref{def R(W)}).

### 2018-11-02 General WLD combinatorics.tex
fixing the short propagator configuration lemma

@@
 
-\note{rank probably isn't a good word; do we have a better one?}
-\begin{dfn}\label{vertex rank}
-Let $i$ be a vertex in $W$. We define the {\bf rank} of $i$ to be $|Prop(i)|$, i.e. the number of propagators supported on $i$.
-\end{dfn}
+\note{I don't think rank of a vertex (in the sense of number of propagators supported on it) was ever used, so I removed the definition}
+%\note{rank probably isn't a good word; do we have a better one?}
+%\begin{dfn}\label{vertex rank}
+%Let $i$ be a vertex in $W$. We define the {\bf rank} of $i$ to be $|Prop(i)|$, i.e. the number of propagators supported on $i$.
+%\end{dfn}
 
@@
 
+\note{Are the next few definitions used outside the proof of Lemma~\ref{lem sian}?  If not, then perhaps they could go inside the proof so as not to clutter the document with temporary definitions?}
 \begin{dfn}
@@
 \end{dfn}
+\note{I think there's an issue here about what we mean by subdiagram; in def 1.5 we say a subdiagram is of the form $(P, V(P))$ which is certainly not what we want here; in fact I think we want the subdiagram where the vertex set is unchanged and only the propagator set is restricted (the other possibility would be to restrict the vertex set to $[i, j]$, but then the lengths of propagators can change and in the way we want to use it (see paragraph below) $p$ will become very non-admissible).
+I think def 1.5 should be removed and we should say that for a WLD $(P, V)$ subdiagrams are any $(P', V')$ with $P'\subseteq P$, $V'\subseteq V$ and all supporting vertices of elements of $P'$ in $V'$; this seems to me to be the natural notion of subobject.}
 
@@
 \begin{lem}\label{lem sian}
-  Let $W$ be an admissible WLD in which each vertex supports at least one propagator.  Then exactly one of the following things occurs.
+  Let $W$ be an admissible WLD in which each vertex supports at least one propagator.  Then exactly one of the following two things occurs.
   \begin{enumerate}
-    \item $W$ has a propagator of length 3, say $p =  (i,i+3)$, with a propagator of length 2 inside it.
-    \item $W$ admits no propagators of length 3, and there exists a pair of propagators with the property that the first propagator is $(i, i+1, i+2, i+3)$, the second is $(i+2, i+3, i+4, i+5)$, and no other propagator ends on the edge $(i+2, i+3)$.
+    \item $W$ has a propagator of length 3 with a propagator of length 2 inside it.
+    \item $W$ admits no propagators of length 3, and one or both of the following two things occurs.
+      \begin{enumerate}
+        \item There is a propagator of length $2$, say $(i, i+1, i+2, i+3)$ such that no other propagators ends on either the edge $(i, i+1)$ or the edge $(i+2, i+3)$.\label{item lonely 2}
+        \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+1, i+2, i+3)$, the second is $(i+2, i+3, i+4, i+5)$, and no other propagator ends on the edge $(i+2, i+3)$.\label{item pair of 2s}
+      \end{enumerate}
   \end{enumerate}
@@
 
-\note{This is the proof of the old result pasted without modification so we can identify where it needs editing. For some reason the WLD was named $D$ instead of $W$.}
-\begin{proof}
-We will prove the following stronger result: that $D$ admits a pair of propagators of length 2 in the following configuration:
-\begin{equation}\label{eq:2 prop config}
-\begin{tikzpicture}[baseline=(current bounding box.east)]
-\pgfmathsetmacro{\radius}{2}
-\pgfmathsetmacro{\angle}{20}
-
-\begin{scope}
-\clip (-\radius*1.1,\radius*0.25) rectangle (\radius*1.1,\radius*1.25);
-
-\begin{scope}
-\clip (-\radius*1.1,\radius*0.45) rectangle (\radius*1.1,\radius*1.1);
-\draw[-] (0,0) circle[radius=\radius cm];
-\end{scope}
-
-% vertices
-\foreach \i in {2,3,...,7}{
-	\draw (\angle*\i:\radius*0.98) --  (\angle*\i:\radius*1.02);
-}
-
-\begin{scope}
-\clip (0,0) circle[radius=\radius];
-\draw[propagator] (2.5*\angle:\radius*1.1 cm) to [bend left=90] (4.35*\angle:\radius*1.1 cm);
-\draw[propagator] (4.65*\angle:\radius*1.1 cm) to [bend left=90] (6.5*\angle:\radius*1.1 cm);
-
-\end{scope}
-
-\node at (80:\radius*1.1) {\tiny $j$};
-\node at (100:\radius*1.1) {\tiny $j+1$};
-\node at (90:\radius*0.5) {\small $s_j = s_{j+1} = 2$};
-
-\end{scope}
-\end{tikzpicture}
-\end{equation}
-
-We will inductively construct a sequence of pairs of propagators $(p_r,q_r)$ satisfying: $\ell(p_r) = 2$, and $p_r$ either forms part of a configuration \eqref{eq:2 prop config} in $D$ or there is a propagator $q_r$ satisfying
+\begin{proof}
+  Suppose first that $W$ has a propagator of length $3$, $p=(i, i+1, i+3, i+4)$.
+By Remark~\ref{rm:props of length 2 and 3} along with the fact that every vertex of $W$ supports at least one propagator, we have that $i+1$ supports exactly one propagator and this propagator must have length 2 by noncrossingness.
+
+  Now suppose $W$ has no propagators of length $3$.
+%  We will prove the following stronger result: that $D$ admits a pair of propagators of length 2 in the following configuration:
+%\begin{equation}\label{eq:2 prop config}
+%\begin{tikzpicture}[baseline=(current bounding box.east)]
+%\pgfmathsetmacro{\radius}{2}
+%\pgfmathsetmacro{\angle}{20}
+%
+%\begin{scope}
+%\clip (-\radius*1.1,\radius*0.25) rectangle (\radius*1.1,\radius*1.25);
+%
+%\begin{scope}
+%\clip (-\radius*1.1,\radius*0.45) rectangle (\radius*1.1,\radius*1.1);
+%\draw[-] (0,0) circle[radius=\radius cm];
+%\end{scope}
+%
+%% vertices
+%\foreach \i in {2,3,...,7}{
+%	\draw (\angle*\i:\radius*0.98) --  (\angle*\i:\radius*1.02);
+%}
+%
+%\begin{scope}
+%\clip (0,0) circle[radius=\radius];
+%\draw[propagator] (2.5*\angle:\radius*1.1 cm) to [bend left=90] (4.35*\angle:\radius*1.1 cm);
+%\draw[propagator] (4.65*\angle:\radius*1.1 cm) to [bend left=90] (6.5*\angle:\radius*1.1 cm);
+%
+%\end{scope}
+%
+%\node at (80:\radius*1.1) {\tiny $j$};
+%\node at (100:\radius*1.1) {\tiny $j+1$};
+%\node at (90:\radius*0.5) {\small $s_j = s_{j+1} = 2$};
+%
+%\end{scope}
+%\end{tikzpicture}
+%\end{equation}
+
+  We will inductively construct a sequence of pairs of propagators $(p_r,q_r)$ satisfying: $\ell(p_r) = 2$, and $p_r$ either forms part of configuration \ref{item lonely 2} or \ref{item pair of 2s} from the statement
+  %a configuration \eqref{eq:2 prop config} in $D$
+  or there is a propagator $q_r$ satisfying
 \begin{itemize}
@@
 \end{itemize}
-Since $D$ contains finitely many vertices, this must eventually terminate in a configuration of the form \eqref{eq:2 prop config}.
-
-Start by choosing a propagator $p_1$ of length 2 in $D$ (which exists by Remark~\ref{rem:props of length 2 and 3}), and write $(j_1,j_1+1,j_1+2,j_1+3)$ for its support.
-If it is part of a configuration \eqref{eq:2 prop config} we are done, so suppose otherwise: since $s_{j_1} \geq 2$, there must exist a second propagator $q_1$ of length $\geq 4$ which starts on edge $(j_1,j_1+1)$.
+Since $D$ contains finitely many vertices, this must eventually terminate in one of the two desired configurations. %a configuration of the form \eqref{eq:2 prop config}.
+
+Start by choosing a propagator $p_1$ of length 2 in $W$ (which exists by Remark~\ref{rem:props of length 2 and 3}), and write $(j_1,j_1+1,j_1+2,j_1+3)$ for its support.
+If it is part of one of the two configurations we are looking for then we are done,
+%a configuration \eqref{eq:2 prop config} we are done,
+so suppose otherwise: since $p_1$ is not in configuration \ref{item lonely 2} then there must be a second propagator starting either on edge $(j_1, j_1+1)$ or $(j_1+2, j_1+3)$.
+Flipping the diagram if necessary, assume the former.
+Since $p_1$ is not in configuration \ref{item pair of 2s} then there must exist a second propagator $q_1$ of length $\geq 4$ which starts on edge $(j_1,j_1+1)$.
 This bounds a region $[i_1,j_1+1]$ which does not contain $p_1$.
@@
 Now suppose $q_{r}$ exists by the induction hypothesis and bounds a region $[i_r,j_r+1]$.
-Consider the restricted diagram $D_r:=D_{[i_r,j_r+1]}$; clearly we must have $s_l \geq 2$ for all $l \in [i_r+2,j_r-1]$ (which is a non-empty interval since $\ell(q_r) \geq 4$), while $s_l\geq 1$ for $l \in \{i_r,i_r+1,j_r,j_r+1\}$.
-
-By Remark~\ref{rem:props of length 2 and 3}, $D_r$ admits at least one propagator of length 2 and none of length 3.
-Let $p_{r+1}$ be a propagator of length 2 in $D_r$; if it forms part of the configuration \eqref{eq:2 prop config} then we are done.
+Consider the restricted diagram $W_r:=W_{[i_r,j_r+1]}$; clearly we must have $s_l \geq 2$ for all $l \in [i_r+2,j_r-1]$ (which is a non-empty interval since $\ell(q_r) \geq 4$), while $s_l\geq 1$ for $l \in \{i_r,i_r+1,j_r,j_r+1\}$.
+
+By Remark~\ref{rem:props of length 2 and 3}, $W_r$ admits at least one propagator of length 2 and none of length 3.
+Let $p_{r+1}$ be a propagator of length 2 in $D_r$; if it forms part of either configuration \ref{item lonely 2} or \ref{item pair of 2s}
+%the configuration \eqref{eq:2 prop config}
+then we are done.
 Otherwise, at least one endpoint of $p_{r+1}$ lies on an edge contained in the non-empty interval $[i_r+2,j_r-1]$, and so there is at least one other propagator connected to this edge.

### 2018-11-19 General WLD combinatorics.tex
maybe the small config result is correct now

@@
 
-\note{Are the next few definitions used outside the proof of Lemma~\ref{lem sian}?  If not, then perhaps they could go inside the proof so as not to clutter the document with temporary definitions?}
+\note{Are the next few definitions used outside the proof of Lemma~\ref{lem sian 1}?  If not, then perhaps they could go inside the proof so as not to clutter the document with temporary definitions?}
 \begin{dfn}
@@
 
-\begin{lem}\label{lem sian}
+\begin{lem}\label{lem sian 1}
   Let $W$ be an admissible WLD in which each vertex supports at least one propagator.  Then exactly one of the following two things occurs.
@@
     \item $W$ has a propagator of length 3 with a propagator of length 2 inside it.
-    \item $W$ admits no propagators of length 3, and one or both of the following two things occurs.
+    \item $W$ admits no propagators of length 3, and one or more of the following things occurs.
       \begin{enumerate}
         \item There is a propagator of length $2$, say $(i, i+1, i+2, i+3)$ such that no other propagators ends on either the edge $(i, i+1)$ or the edge $(i+2, i+3)$.\label{item lonely 2}
-        \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+1, i+2, i+3)$, the second is $(i+2, i+3, i+4, i+5)$, and no other propagator ends on the edge $(i+2, i+3)$.\label{item pair of 2s}
+        \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+1, i+2, i+3)$, the second is $(j, j+1, j+2, j+3)$, no other propagator ends between $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
+        \item There exists a propagator of length exactly 4 with only a propagator of length 2 inside it.\label{item 4 and 2}
       \end{enumerate}
@@
   Suppose first that $W$ has a propagator of length $3$, $p=(i, i+1, i+3, i+4)$.
-By Remark~\ref{rm:props of length 2 and 3} along with the fact that every vertex of $W$ supports at least one propagator, we have that $i+1$ supports exactly one propagator and this propagator must have length 2 by noncrossingness.
+By Remark~\ref{rem:props of length 2 and 3} along with the fact that every vertex of $W$ supports at least one propagator, we have that $i+2$ supports exactly one propagator and this propagator must have length 2 by noncrossingness.
 
@@
 
-  We will inductively construct a sequence of pairs of propagators $(p_r,q_r)$ satisfying: $\ell(p_r) = 2$, and $p_r$ either forms part of configuration \ref{item lonely 2} or \ref{item pair of 2s} from the statement
+  We will inductively construct a sequence of pairs of propagators $(p_r,q_r)$ satisfying: $\ell(p_r) = 2$, and $p_r$ either forms part of configuration \ref{item lonely 2}, \ref{item pair of 2s}, or \ref{item 4 and 2} from the statement,
   %a configuration \eqref{eq:2 prop config} in $D$
@@
 \item $\ell(q_r) \geq 4$.
-\item $q_r$ bounds a region of $D$ which contains strictly fewer vertices than that bounded by $q_{r-1}$ and the restriction of $D$ to this region does not contain any of the propagators $p_1, \dots, p_r$.
+\item $q_r$ bounds a region of $W$ which contains strictly fewer vertices than that bounded by $q_{r-1}$ and the restriction of $W$ to this region does not contain any of the propagators $p_1, \dots, p_r$.
 \end{itemize}
-Since $D$ contains finitely many vertices, this must eventually terminate in one of the two desired configurations. %a configuration of the form \eqref{eq:2 prop config}.
+Since $W$ contains finitely many vertices, this must eventually terminate in one of the three desired configurations. %a configuration of the form \eqref{eq:2 prop config}.
 
 Start by choosing a propagator $p_1$ of length 2 in $W$ (which exists by Remark~\ref{rem:props of length 2 and 3}), and write $(j_1,j_1+1,j_1+2,j_1+3)$ for its support.
-If it is part of one of the two configurations we are looking for then we are done,
+If it is part of one of the configurations we are looking for then we are done,
 %a configuration \eqref{eq:2 prop config} we are done,
@@
 Flipping the diagram if necessary, assume the former.
-Since $p_1$ is not in configuration \ref{item pair of 2s} then there must exist a second propagator $q_1$ of length $\geq 4$ which starts on edge $(j_1,j_1+1)$.
-This bounds a region $[i_1,j_1+1]$ which does not contain $p_1$.
-
-Now suppose $q_{r}$ exists by the induction hypothesis and bounds a region $[i_r,j_r+1]$.
-Consider the restricted diagram $W_r:=W_{[i_r,j_r+1]}$; clearly we must have $s_l \geq 2$ for all $l \in [i_r+2,j_r-1]$ (which is a non-empty interval since $\ell(q_r) \geq 4$), while $s_l\geq 1$ for $l \in \{i_r,i_r+1,j_r,j_r+1\}$.
-
-By Remark~\ref{rem:props of length 2 and 3}, $W_r$ admits at least one propagator of length 2 and none of length 3.
-Let $p_{r+1}$ be a propagator of length 2 in $D_r$; if it forms part of either configuration \ref{item lonely 2} or \ref{item pair of 2s}
+Since $p_1$ is not in configuration \ref{item pair of 2s} and every vertex is supported then there must exist a propagator $q_1$ of length $\geq 4$ with one end on edge $(j_1,j_1+1)$ or on edge $(j_1-1, j_1)$ or on edge $(j_1-2, j_1-1)$.
+This bounds a region $[i_1,k_1]$ (where $k_1 \in \{j_1-1, j_1, j_1+1\}$) which does not contain $p_1$.
+
+Now suppose $q_{r}$ exists by the induction hypothesis and bounds a region $[i_r,k_r]$.
+Consider the restricted diagram $W_r:=W_{[i_r,k_r]}$; by the original hypotheses on $W$ every vertex $l \in [i_r+2,k_r-2]$ (which is a non-empty interval since $\ell(q_r) \geq 4$) must have support $\geq 1$, while the same is true for $l \in \{i_r,i_r+1,k_r-1,k_r\}$ because of $q_r$.
+
+By Remark~\ref{rem:props of length 2 and 3}, $W_r$ admits at least one propagator of length 2.
+$W_r$ has no propagators of length $3$ since $W$ has none.
+\note{now the question really is important about what length means in the restricted diagram; as written the restricted diagram has the same vertex set so length is unchanged.}   Let $p_{r+1}$ be a propagator of length 2 in $W_r$; if it forms part of configuration \ref{item lonely 2}, \ref{item pair of 2s}, or \ref{item 4 and 2}
 %the configuration \eqref{eq:2 prop config}
-then we are done.
-Otherwise, at least one endpoint of $p_{r+1}$ lies on an edge contained in the non-empty interval $[i_r+2,j_r-1]$, and so there is at least one other propagator connected to this edge.
-Up to symmetry, there are three possibilities:
-
-% this was 100% a productive use of my time
-
-\[\begin{tabular}{ccc}
-% possibility 1
-\begin{tikzpicture}
-\pgfmathsetmacro{\radius}{2}
-\pgfmathsetmacro{\angle}{15}
-\begin{scope}
-\clip (-\radius*1.1,0) rectangle (\radius*1.1,\radius*1.1);
-
-% vertices 
-\foreach \i in {2,3,4,6,7,8,9,10}{
-	\draw (\angle*\i:\radius*0.98) --  (\angle*\i:\radius*1.02);
-}
-
-% \dots 
-\foreach \i in {1,2,3}{
-	\node at (65 + \i*5:\radius cm) {$\cdot$};
-}
-
-\begin{scope} % this scope contains the propagators
-\clip (0,0) circle[radius=\radius];
-
-\draw[propagator] (\angle*2.4:\radius*1.2 cm) to [bend left=30] (\angle*9.7:\radius*1.2 cm); % q_r
-\draw[propagator] (\angle*7.7:\radius*1.1 cm) to [bend left=90] (\angle*9.45:\radius*1.1 cm); % p_{r+1}
-
-% grey prop begins here
-
-\begin{scope}
-\clip (\angle*7.5:\radius cm) circle[radius=\radius*0.45cm];
-\draw[light-gray,propagator,seconddash] (\angle*6:\radius*1.02 cm) circle[x radius=\radius*0.4cm, y radius = \radius*0.3cm];
-\end{scope}
-
-\begin{scope}
-\clip (0,0) circle[radius=\radius];
-\clip (\angle*7.5:\radius cm) circle[radius=\radius*0.4cm];
-\draw[light-gray,propagator,firstdash] (\angle*6:\radius*1.02 cm) circle[x radius=\radius*0.4cm, y radius = \radius*0.3cm];
-\end{scope}
-
-\begin{scope}
-\clip (\angle*7.5:\radius cm) circle[radius=\radius*0.3cm];
-\clip (0,0) circle[radius=\radius];
-\draw[light-gray,propagator] (\angle*6:\radius*1.02 cm) circle[x radius=\radius*0.4cm, y radius = \radius*0.3cm];
-\end{scope}
-% end gray prop
-
-\end{scope}
-
-\node at (90:\radius*0.30 cm) {\tiny $q_r$};
-\node at (\angle*8:\radius*0.73) {\tiny $p_{r+1}$};
-\node[light-gray] at (\angle*4.9:\radius*0.77 cm) {\tiny $q_{r+1}$};
-\node at (2*\angle:\radius*1.1) {\tiny $i_r$};
-\node at (9*\angle:\radius*1.1) {\tiny $j_r$};
-
-% circle/edges; needs to happen last to overlap gray
-\begin{scope}
-\clip (-\radius*1.1,0.9) rectangle (\radius*1.1,\radius*1.1);
-\draw[-] (0,0) circle[radius=\radius cm];
-\end{scope}
-
-\end{scope} % ends the overall rectangle clipping
-\end{tikzpicture}
-
-&
-
-% possibility 2
-\begin{tikzpicture}
-\pgfmathsetmacro{\radius}{2}
-\pgfmathsetmacro{\angle}{15}
-\begin{scope}
-% overall clipping to make the size sensible
-\clip (-\radius*1.1,0) rectangle (\radius*1.1,\radius*1.1);
-
-% vertices
-\foreach \i in {2,3,4,6,7,8,9,10}{
-	\draw (\angle*\i:\radius*0.98) --  (\angle*\i:\radius*1.02);
-}
-
-% \dots
-\foreach \i in {1,2,3}{
-	\node at (65 + \i*5:\radius cm) {$\cdot$};
-}
-
-\begin{scope} % props
-\clip (0,0) circle[radius=\radius cm]; 
-\draw[propagator] (\angle*2.4:\radius*1.2 cm) to [bend left=30] (\angle*9.6:\radius*1.2 cm); % q_r
-\draw[propagator] (\angle*6.7:\radius*1.1 cm) to [bend left=90] (\angle*8.6:\radius*1.1 cm); % p_{r+1}
-
-%% grey prop starts here
-
-\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.45cm];
-\draw[light-gray,propagator,seconddash] (\angle*4.5:\radius*1.3 cm) circle[y radius = 0.5*\radius cm,x radius=\radius*0.7cm];
-\end{scope}
-
-\begin{scope}
-\clip (0,0) circle[radius=\radius];
-\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.4cm];
-\draw[light-gray,propagator,firstdash] (\angle*4.5:\radius*1.3 cm) circle[y radius = 0.5*\radius cm,x radius=\radius*0.7cm];
-\end{scope}
-
-\begin{scope}
-\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.3cm];
-\clip (0,0) circle[radius=\radius];
-\draw[light-gray,propagator] (\angle*4.5:\radius*1.3 cm) circle[y radius = 0.5*\radius cm,x radius=\radius*0.7cm];
-\end{scope}
-% grey prop ends here
-
-\node at (90:\radius*0.32 cm) {\tiny $q_r$};
-\node at (\angle*7.75:\radius*0.75) {\tiny $p_{r+1}$};
-\node[light-gray] at (\angle*4.5:\radius*0.7 cm) {\tiny $q_{r+1}$};
-\node at (2*\angle:\radius*1.1) {\tiny $i_r$};
-\node at (9*\angle:\radius*1.1) {\tiny $j_r$};
-
-% circle/edges
-\begin{scope}
-\clip (-\radius*1.1,0.9) rectangle (\radius*1.1,\radius*1.1);
-\draw[-] (0,0) circle[radius=\radius cm];
-\end{scope}
-
-\end{scope} % ends overall clip
-\end{tikzpicture}
-
-&
-
-% possiblitiy 3
-\begin{tikzpicture}
-\pgfmathsetmacro{\radius}{2}
-\pgfmathsetmacro{\angle}{12}
-\begin{scope}
-\clip (-\radius*1.1,0) rectangle (\radius*1.1,\radius*1.1);
-
-% vertices
-\foreach \i in {2,3,6,7,8,9,12,13}{
-	\draw (\angle*\i:\radius*0.98) --  (\angle*\i:\radius*1.02);
-}
-
-% \dots
-\foreach \i in {1,2,3}{
-	\node at (44 + \i*5:\radius cm) {$\cdot$};
-	\node at (116 + \i*5:\radius cm) {$\cdot$};
-}
-
-\begin{scope} % props
-\clip (0,0) circle[radius=\radius cm];
-\draw[propagator] (\angle*2.4:\radius*1.2 cm) to [bend left=30] (\angle*12.6:\radius*1.2 cm); % q_r
-\draw[propagator] (\angle*6.5:\radius*1.1 cm) to [bend left=100] (\angle*8.5:\radius*1.05 cm); % p_{r+1}
-
-%  grey prop 1
-% not q_{r+1}
-\begin{scope}
-\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.45cm];
-\draw[light-gray,propagator,seconddash] (\angle*6.5:\radius*1.1 cm) to [bend left=90] (\angle*12.5:\radius*1.1cm);
-\end{scope}
-
-\begin{scope}
-\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.4cm];
-\draw[light-gray,propagator,firstdash] (\angle*6.5:\radius*1.1 cm) to [bend left=90] (\angle*12.5:\radius*1.1cm);
-\end{scope}
-\begin{scope}
-\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.3cm];
-\draw[light-gray,propagator] (\angle*6.5:\radius*1.1 cm) to [bend left=90] (\angle*12.5:\radius*1.1cm);
-\end{scope}
-% grey prop 1 ends here
-
-% grey prop 2
-% this is q_{r+1}
-\begin{scope}
-\clip (\angle*8.5:\radius cm) circle[radius=\radius*0.45cm];
-\draw[propagator,seconddash,light-gray] (\angle*8.8:\radius*1.1 cm) to [bend left=90] (\angle*12:\radius*1.1cm);
-\end{scope}
-
-\begin{scope}
-\clip (\angle*8.5:\radius cm) circle[radius=\radius*0.4cm];
-\draw[propagator,firstdash,light-gray] (\angle*8.8:\radius*1.1 cm) to [bend left=90] (\angle*12:\radius*1.1cm);
-\end{scope}
-
-\begin{scope}
-\clip (\angle*8.5:\radius cm) circle[radius=\radius*0.3cm];
-\draw[light-gray,propagator] (\angle*8.8:\radius*1.1 cm) to [bend left=90] (\angle*12:\radius*1.1cm);
-\end{scope}
-
-% grey prop 2 ends here
-
-\end{scope}
-
-\node at (90:\radius*0.15 cm) {\tiny $q_r$};
-\node at (\angle*7.5:\radius*0.83) {\tiny $p_{r+1}$};
-\node[light-gray] at (\angle*11:\radius*0.75 cm) {\tiny $q_{r+1}$};
-
-\node at (2*\angle:\radius*1.1) {\tiny $i_r$};
-\node at (12*\angle:\radius*1.1) {\tiny $j_r$};
-
-% overall circle
-\begin{scope}
-\clip (-\radius*1.1,0.7) rectangle (\radius*1.1,\radius*1.1);
-\draw[-] (0,0) circle[radius=\radius cm];
-\end{scope}
-
-\end{scope} % ends overall clip
-\end{tikzpicture}
-
-\end{tabular}
-\]
-In each case, the diagram indicates how to choose $q_{r+1}$ satisfying the induction hypothesis.
+then we are done, so assume otherwise.
+
+Note we may replace $q_r$ by any other propagator of length $\geq 4$ in $W_r$ which contains $p_{r+1}$ while still satisfying all the hypotheses, and so, without loss of generality we may assume that $q_r$ has minimal length among propagators of length $\geq 4$ which contain $p_{r+1}$.
+
+There are two cases to consider.
+The first case is that neither end of $p_{r+1}$ lies on an edge contained in the possibly empty interval $[i_r+3,k_r-3]$, then since $p_{r+1}$ has length 2, it must be that $[i_r+3,k_r-3]$ is at most a single edge, and so $q_r$ has length $\leq 6$.
+Since $p_{r+1}$ has one end before $i_r+3$ and the other after $k_r-3$, the only propagators inside $q_r$ that do not also contain $p_{r+1}$ must have both ends in $[i_r, i_r+3]$ or both ends in $[k_r-3, k_r]$ and hence be of length 2.
+Therefore, if $q_r$ contains a propagator $t$ of length $\leq 4$, this propagator must also contain $p_{r+1}$ which is impossible my minimality.
+Therefore, if $q_r$ contains another propagator of length $2$ we would have configuration \ref{item pair of 2s} which we have already assumed does not occur.
+Consequently, $q_r$ contains only $p_{r+1}$; if $q_r$ is of length $4$ then we have \ref{item 4 and 2} and if $q_r$ is of length $5$ or $6$ then we have either \ref{item lonely 2} or an unsupported vertex, all of which are impossible.
+Therefore the first case cannot occur.
+
+The second case is that at least one endpoint of $p_{r+1}$ lies on an edge contained in the interval $[i_r+3,k_r-3]$.
+Up to symmetry we can write $p_{r+1} = (j_{r+1}, j_{r+1}+1, j_{r+1}+2, j_{r+1}+3)$ where $(j_{r+1}+2, j_{r+1}+3)$ is contained in $[i_r+3, k_r-3]$.
+Since $p_{r+1}$ is not part of configuration \ref{item pair of 2s} and vertex $j_{r+1}+4$ is supported (and not by $q_r$ since $j_{r+1}+4 \leq k_r-2$), there is some propagator $t$ with one end in $[j_{r+1}+2, j_{r+1}+4]$ and length $\geq 4$.
+By noncrossingness $t$ is contained in $q_{r}$.
+$t$ does not contain $p_{r+1}$ by minimality and so we may set $q_{r+1} = t$ to continue the induction.
+
+The overall result, then follows by induction.
+
+\note{The picture didn't apply any longer, but perhaps a new one would be nice?}
+\note{Also, the way you had it set out, you never needed a minimality argument; this was essentially beacause in your third picture, you could choose the side which didn't contain $p_{r+1}$.
+The same argument could work here, but I was finding it was getting a bit heavy to explain it that way, and the minimality approach seemed like it was lighter.
+See what you think}
+%% this was 100% a productive use of my time
+%
+%\[\begin{tabular}{ccc}
+%% possibility 1
+%\begin{tikzpicture}
+%\pgfmathsetmacro{\radius}{2}
+%\pgfmathsetmacro{\angle}{15}
+%\begin{scope}
+%\clip (-\radius*1.1,0) rectangle (\radius*1.1,\radius*1.1);
+%
+%% vertices 
+%\foreach \i in {2,3,4,6,7,8,9,10}{
+%	\draw (\angle*\i:\radius*0.98) --  (\angle*\i:\radius*1.02);
+%}
+%
+%% \dots 
+%\foreach \i in {1,2,3}{
+%	\node at (65 + \i*5:\radius cm) {$\cdot$};
+%}
+%
+%\begin{scope} % this scope contains the propagators
+%\clip (0,0) circle[radius=\radius];
+%
+%\draw[propagator] (\angle*2.4:\radius*1.2 cm) to [bend left=30] (\angle*9.7:\radius*1.2 cm); % q_r
+%\draw[propagator] (\angle*7.7:\radius*1.1 cm) to [bend left=90] (\angle*9.45:\radius*1.1 cm); % p_{r+1}
+%
+%% grey prop begins here
+%
+%\begin{scope}
+%\clip (\angle*7.5:\radius cm) circle[radius=\radius*0.45cm];
+%\draw[light-gray,propagator,seconddash] (\angle*6:\radius*1.02 cm) circle[x radius=\radius*0.4cm, y radius = \radius*0.3cm];
+%\end{scope}
+%
+%\begin{scope}
+%\clip (0,0) circle[radius=\radius];
+%\clip (\angle*7.5:\radius cm) circle[radius=\radius*0.4cm];
+%\draw[light-gray,propagator,firstdash] (\angle*6:\radius*1.02 cm) circle[x radius=\radius*0.4cm, y radius = \radius*0.3cm];
+%\end{scope}
+%
+%\begin{scope}
+%\clip (\angle*7.5:\radius cm) circle[radius=\radius*0.3cm];
+%\clip (0,0) circle[radius=\radius];
+%\draw[light-gray,propagator] (\angle*6:\radius*1.02 cm) circle[x radius=\radius*0.4cm, y radius = \radius*0.3cm];
+%\end{scope}
+%% end gray prop
+%
+%\end{scope}
+%
+%
+%\node at (90:\radius*0.30 cm) {\tiny $q_r$};
+%\node at (\angle*8:\radius*0.73) {\tiny $p_{r+1}$};
+%\node[light-gray] at (\angle*4.9:\radius*0.77 cm) {\tiny $q_{r+1}$};
+%\node at (2*\angle:\radius*1.1) {\tiny $i_r$};
+%\node at (9*\angle:\radius*1.1) {\tiny $j_r$};
+%
+%
+%% circle/edges; needs to happen last to overlap gray
+%\begin{scope}
+%\clip (-\radius*1.1,0.9) rectangle (\radius*1.1,\radius*1.1);
+%\draw[-] (0,0) circle[radius=\radius cm];
+%\end{scope}
+%
+%\end{scope} % ends the overall rectangle clipping
+%\end{tikzpicture}
+%
+%&
+%
+%% possibility 2
+%\begin{tikzpicture}
+%\pgfmathsetmacro{\radius}{2}
+%\pgfmathsetmacro{\angle}{15}
+%\begin{scope}
+%% overall clipping to make the size sensible
+%\clip (-\radius*1.1,0) rectangle (\radius*1.1,\radius*1.1);
+%
+%
+%% vertices
+%\foreach \i in {2,3,4,6,7,8,9,10}{
+%	\draw (\angle*\i:\radius*0.98) --  (\angle*\i:\radius*1.02);
+%}
+%
+%% \dots
+%\foreach \i in {1,2,3}{
+%	\node at (65 + \i*5:\radius cm) {$\cdot$};
+%}
+%
+%\begin{scope} % props
+%\clip (0,0) circle[radius=\radius cm]; 
+%\draw[propagator] (\angle*2.4:\radius*1.2 cm) to [bend left=30] (\angle*9.6:\radius*1.2 cm); % q_r
+%\draw[propagator] (\angle*6.7:\radius*1.1 cm) to [bend left=90] (\angle*8.6:\radius*1.1 cm); % p_{r+1}
+%
+%%% grey prop starts here
+%
+%\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.45cm];
+%\draw[light-gray,propagator,seconddash] (\angle*4.5:\radius*1.3 cm) circle[y radius = 0.5*\radius cm,x radius=\radius*0.7cm];
+%\end{scope}
+%
+%\begin{scope}
+%\clip (0,0) circle[radius=\radius];
+%\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.4cm];
+%\draw[light-gray,propagator,firstdash] (\angle*4.5:\radius*1.3 cm) circle[y radius = 0.5*\radius cm,x radius=\radius*0.7cm];
+%\end{scope}
+%
+%\begin{scope}
+%\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.3cm];
+%\clip (0,0) circle[radius=\radius];
+%\draw[light-gray,propagator] (\angle*4.5:\radius*1.3 cm) circle[y radius = 0.5*\radius cm,x radius=\radius*0.7cm];
+%\end{scope}
+%% grey prop ends here
+%
+%
+%\node at (90:\radius*0.32 cm) {\tiny $q_r$};
+%\node at (\angle*7.75:\radius*0.75) {\tiny $p_{r+1}$};
+%\node[light-gray] at (\angle*4.5:\radius*0.7 cm) {\tiny $q_{r+1}$};
+%\node at (2*\angle:\radius*1.1) {\tiny $i_r$};
+%\node at (9*\angle:\radius*1.1) {\tiny $j_r$};
+%
+%% circle/edges
+%\begin{scope}
+%\clip (-\radius*1.1,0.9) rectangle (\radius*1.1,\radius*1.1);
+%\draw[-] (0,0) circle[radius=\radius cm];
+%\end{scope}
+%
+%\end{scope} % ends overall clip
+%\end{tikzpicture}
+%
+%&
+%
+%% possiblitiy 3
+%\begin{tikzpicture}
+%\pgfmathsetmacro{\radius}{2}
+%\pgfmathsetmacro{\angle}{12}
+%\begin{scope}
+%\clip (-\radius*1.1,0) rectangle (\radius*1.1,\radius*1.1);
+%
+%% vertices
+%\foreach \i in {2,3,6,7,8,9,12,13}{
+%	\draw (\angle*\i:\radius*0.98) --  (\angle*\i:\radius*1.02);
+%}
+%
+%% \dots
+%\foreach \i in {1,2,3}{
+%	\node at (44 + \i*5:\radius cm) {$\cdot$};
+%	\node at (116 + \i*5:\radius cm) {$\cdot$};
+%}
+%
+%\begin{scope} % props
+%\clip (0,0) circle[radius=\radius cm];
+%\draw[propagator] (\angle*2.4:\radius*1.2 cm) to [bend left=30] (\angle*12.6:\radius*1.2 cm); % q_r
+%\draw[propagator] (\angle*6.5:\radius*1.1 cm) to [bend left=100] (\angle*8.5:\radius*1.05 cm); % p_{r+1}
+%
+%%  grey prop 1
+%% not q_{r+1}
+%\begin{scope}
+%\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.45cm];
+%\draw[light-gray,propagator,seconddash] (\angle*6.5:\radius*1.1 cm) to [bend left=90] (\angle*12.5:\radius*1.1cm);
+%\end{scope}
+%
+%\begin{scope}
+%\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.4cm];
+%\draw[light-gray,propagator,firstdash] (\angle*6.5:\radius*1.1 cm) to [bend left=90] (\angle*12.5:\radius*1.1cm);
+%\end{scope}
+%\begin{scope}
+%\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.3cm];
+%\draw[light-gray,propagator] (\angle*6.5:\radius*1.1 cm) to [bend left=90] (\angle*12.5:\radius*1.1cm);
+%\end{scope}
+%% grey prop 1 ends here
+%
+%% grey prop 2
+%% this is q_{r+1}
+%\begin{scope}
+%\clip (\angle*8.5:\radius cm) circle[radius=\radius*0.45cm];
+%\draw[propagator,seconddash,light-gray] (\angle*8.8:\radius*1.1 cm) to [bend left=90] (\angle*12:\radius*1.1cm);
+%\end{scope}
+%
+%\begin{scope}
+%\clip (\angle*8.5:\radius cm) circle[radius=\radius*0.4cm];
+%\draw[propagator,firstdash,light-gray] (\angle*8.8:\radius*1.1 cm) to [bend left=90] (\angle*12:\radius*1.1cm);
+%\end{scope}
+%
+%\begin{scope}
+%\clip (\angle*8.5:\radius cm) circle[radius=\radius*0.3cm];
+%\draw[light-gray,propagator] (\angle*8.8:\radius*1.1 cm) to [bend left=90] (\angle*12:\radius*1.1cm);
+%\end{scope}
+%
+%% grey prop 2 ends here
+%
+%
+%
+%\end{scope}
+%
+%\node at (90:\radius*0.15 cm) {\tiny $q_r$};
+%\node at (\angle*7.5:\radius*0.83) {\tiny $p_{r+1}$};
+%\node[light-gray] at (\angle*11:\radius*0.75 cm) {\tiny $q_{r+1}$};
+%
+%\node at (2*\angle:\radius*1.1) {\tiny $i_r$};
+%\node at (12*\angle:\radius*1.1) {\tiny $j_r$};
+%
+%
+%
+%% overall circle
+%\begin{scope}
+%\clip (-\radius*1.1,0.7) rectangle (\radius*1.1,\radius*1.1);
+%\draw[-] (0,0) circle[radius=\radius cm];
+%\end{scope}
+%
+%
+%\end{scope} % ends overall clip
+%\end{tikzpicture}
+%
+%\end{tabular}
+%\]
+%In each case, the diagram indicates how to choose $q_{r+1}$ satisfying the induction hypothesis.
 In the third case, note that \textit{both} ends of $p_{r+1}$ must share their edge with a propagator of length $\geq 4$; the non-crossing hypothesis on propagators guarantees that at least one will bound a region not containing $p_{r+1}$.
 \end{proof}
+
+\begin{rmk}
+In the case that all vertices of an admissible WLD $W$ support at least two propagators, then Lemma~\ref{lem sian 1} substantially simplifies.
+By Remark~\ref{rem:props of length 2 and 3}, $W$ has no propagators of length $3$, so the first item of Lemma~\ref{lem sian 1} cannot occur at all.
+Configurations \ref{item lonely 2} and \ref{item 4 and 2} also necessarily entail vertices with support $1$ as does configuration \ref{item pair of 2s} unless $j=i+2$.
+So in the case that $W$ has all vertices with support at least two then $W$ must contain a pair of propagators of length $2$  with the property that the first propagator is $(i, i+1, i+2, i+3)$, the second is $(i+2, i+3, i+4, i+5)$ and no other propagator ends on the edge $(i+2, i+3)$.
+\end{rmk}
 

### 2018-11-20 General WLD combinatorics.tex
Not sure what I've changed. Trying to pull

--- 2018-10-30 General WLD combinatorics.tex
@@
 
-\begin{dfn}\label{equivdfn} 
-There is an equivalence relationship on the set of admissible Wilson loops diagrams given by the transititve closure the following binary relation: $W = (\cP, n) \sim W'= (\cP', n)$ if
+\begin{dfn}\label{equivdfn} \todo{I feel like I need some sort of uniqueness of partition result to even be able to define this well. Or something. Can we discuss?}
+There is an equivalence relationship on the set of admissible Wilson loops diagrams generated by the following binary relation: $W = (\cP, n) \sim W'= (\cP', n)$ if
 \begin{enumerate}
@@
 The vertex set $\{4,5, 8, 1\}$ is not a triangulation in either polygon partition.
-\note{Put a picture of a dual tree.
-Make a comment that the embedding is required to obtain uniqueness of the dual}
+\note{do we want a picture of a dual tree here?
+Being lazy}
 \end{eg}
@@
 Furthermore, if the face is bounded by an edge of the polygonal cycle of $\tau(W)$, the corresponding vertex gets a leaf edge for each such boundary.
-Since $\tau(W)$ is an embedded graph (with a fixed distinguished embedding) by Lemma \ref{tausimpleplanarlem}, $T(W)$ is an uniquely defined graph.
+Since $\tau(W)$ is an embedded graph (with a fixed distinguished embedding) by Lemma \ref{tausimpleplanarlem}, $T(W)$ is an uniquely defined graph.\note{The fixed embedding is important, because otherwise you only have a unique planar dual if the graph is 3-connected which this one isn't.
+I'm just noting that here so that everyone knows why I added the part about the embedding and then we can take this comment out.}
 
@@
 
-In \cite{wilsonloops}, the authors show that all exact Wilson loop diagrams correspond to positroids.
+In \cite{wilsonloops}, the authors show that all {\color{violet}admissible} Wilson loop diagrams correspond to positroids.
 That is, they correspond to matroids that can be represented by elements of the positive Grassmannians $\Gr(|\cP|, |V|)$.\todo{Check: positroids or totally positive?
@@
 Given a Wilson loop diagram $W$, define the positroid cell associated to a Wilson loop diagram, $\Sigma(W)$, to be the cell in the CW complex on $\Gr(|\cP|, |V|)$ defined by the \hlfix{realizations}{we haven't specified what this means}  of $W$ that lie in $\Gr(|\cP|, |V|)$.
+{\color{violet} Comment: Realizable matroids are those that can be written as a matrix.
+A realization is one such matrix.
+I think this is standard nomenclature?}
 \end{dfn}
@@
 \section{Geometry of Wilson Loop diagram}\label{sec GN algorithm}
-Since Wilson loop diagrams correspond to positroids, it is natural to study the subspace of $\Gr(|\cP|, n)$ they define.
+Since Wilson loop diagrams correspond to positroids, it is natural to understand the subspace of $\Gr(|\cP|, n)$ they define.
 
@@
 Also talk about Le diagrams.
-
-Throughout this section, $W = (\cP,n)$ is an admissible Wilson loop diagram with $k$ propagators.
-
-\subsection{Some setup results about propagators}
-
-\note{rank probably isn't a good word; do we have a better one?}
-\begin{dfn}\label{vertex rank}
-Let $i$ be a vertex in $W$. We define the {\bf rank} of $i$ to be $|Prop(i)|$, i.e. the number of propagators supported on $i$.
-\end{dfn}
-
-\begin{dfn}\label{props inside p}
-Let $p$ be a propagator supported on $(i,j)$ in $W$.
-The region bounded by $p$ and the edge of the Wilson loop diagram from $i$ to $j+1$ is refered to as the region {\bf inside} $p$, and the complement is the region {\bf outside }$p$.
-The set of propagators inside (resp.
-outside) $p$ are those lying in the region inside (resp.
-outside) $p$, excluding $p$ itself.
-\end{dfn}
-Note that this depends on the order of $i$ and $j$: if we view $p$ as supported on $(j,i)$ (for example, if we are working with the $<_j$ order on vertices) then the regions inside and outside $p$ are swapped.
-
-\begin{dfn}\note{right now this doesn't depend on the order of $i$ and $j$, but that might matter later on?}
-Let $p$ be a propagator supported on the vertices $(i,i+1,j,j+1)$.  Define the \textit{length} of $p$ to be 
-\[\ell(p) = min\big\{|[i+1,j]|,|[j+1,i]|\big\}.\]
-\end{dfn}
-
-\begin{rmk}\label{rem:props of length 2 and 3}
-The following observations about propagators of short length in $W$ are easily verified:
-\begin{itemize}
-\item If every vertex in $W$ supports at least one propagator, then $W$ admits at least one propagator of length 2.
-\item If $p = (i,i+1,i+3,i+4)$ is a propagator of length 3, then the middle vertex $i+2$ supports at most one propagator.
-\end{itemize}
-\end{rmk}
-
-\begin{dfn}
-Define the restriction of $W$ to a region $[i,j]$ to be the subdiagram obtained by forgetting all propagators not wholly supported on vertices in the cyclic interval $[i,j]$.
-Denote this diagram by $W_{[i,j]}$.
-\end{dfn}
-
-If $p$ is a propagator supported on $(i,i+1,j,j+1)$, then we can consider two obvious restrictions of $D$, namely $D_{[i,j+1]}$ and $D_{[j,i+1]}$.
-Clearly all other propagators $q\neq p$ appear in exactly one of these subdiagrams, while $p$ appears in both.
-In this case, we will say that $p$ \textit{bounds the regions} $[i,j+1]$ and $[j,i+1]$; the ordering of the start and end points allow us to identify one or the other region unambiguously.
-
-The following lemma establishes certain configurations of propagators that must exist in any admissible diagram with no unsupported vertices.
-We make use of this result in several induction proofs below.
-
-\begin{lem}\label{lem sian}
-  Let $W$ be an admissible WLD in which each vertex supports at least one propagator.  Then exactly one of the following things occurs.
-  \begin{enumerate}
-    \item $W$ has a propagator of length 3, say $p =  (i,i+3)$, with a propagator of length 2 inside it.
-    \item $W$ admits no propagators of length 3, and there exists a pair of propagators with the property that the first propagator is $(i, i+1, i+2, i+3)$, the second is $(i+2, i+3, i+4, i+5)$, and no other propagator ends on the edge $(i+2, i+3)$.
-  \end{enumerate}
-\end{lem}
-
-\note{This is the proof of the old result pasted without modification so we can identify where it needs editing. For some reason the WLD was named $D$ instead of $W$.}
-\begin{proof}
-We will prove the following stronger result: that $D$ admits a pair of propagators of length 2 in the following configuration:
-\begin{equation}\label{eq:2 prop config}
-\begin{tikzpicture}[baseline=(current bounding box.east)]
-\pgfmathsetmacro{\radius}{2}
-\pgfmathsetmacro{\angle}{20}
-
-\begin{scope}
-\clip (-\radius*1.1,\radius*0.25) rectangle (\radius*1.1,\radius*1.25);
-
-\begin{scope}
-\clip (-\radius*1.1,\radius*0.45) rectangle (\radius*1.1,\radius*1.1);
-\draw[-] (0,0) circle[radius=\radius cm];
-\end{scope}
-
-% vertices
-\foreach \i in {2,3,...,7}{
-	\draw (\angle*\i:\radius*0.98) --  (\angle*\i:\radius*1.02);
-}
-
-\begin{scope}
-\clip (0,0) circle[radius=\radius];
-\draw[propagator] (2.5*\angle:\radius*1.1 cm) to [bend left=90] (4.35*\angle:\radius*1.1 cm);
-\draw[propagator] (4.65*\angle:\radius*1.1 cm) to [bend left=90] (6.5*\angle:\radius*1.1 cm);
-
-\end{scope}
-
-\node at (80:\radius*1.1) {\tiny $j$};
-\node at (100:\radius*1.1) {\tiny $j+1$};
-\node at (90:\radius*0.5) {\small $s_j = s_{j+1} = 2$};
-
-\end{scope}
-\end{tikzpicture}
-\end{equation}
-
-We will inductively construct a sequence of pairs of propagators $(p_r,q_r)$ satisfying: $\ell(p_r) = 2$, and $p_r$ either forms part of a configuration \eqref{eq:2 prop config} in $D$ or there is a propagator $q_r$ satisfying
-\begin{itemize}
-\item $\ell(q_r) \geq 4$.
-\item $q_r$ bounds a region of $D$ which contains strictly fewer vertices than that bounded by $q_{r-1}$ and the restriction of $D$ to this region does not contain any of the propagators $p_1, \dots, p_r$.
-\end{itemize}
-Since $D$ contains finitely many vertices, this must eventually terminate in a configuration of the form \eqref{eq:2 prop config}.
-
-Start by choosing a propagator $p_1$ of length 2 in $D$ (which exists by Remark~\ref{rem:props of length 2 and 3}), and write $(j_1,j_1+1,j_1+2,j_1+3)$ for its support.
-If it is part of a configuration \eqref{eq:2 prop config} we are done, so suppose otherwise: since $s_{j_1} \geq 2$, there must exist a second propagator $q_1$ of length $\geq 4$ which starts on edge $(j_1,j_1+1)$.
-This bounds a region $[i_1,j_1+1]$ which does not contain $p_1$.
-
-Now suppose $q_{r}$ exists by the induction hypothesis and bounds a region $[i_r,j_r+1]$.
-Consider the restricted diagram $D_r:=D_{[i_r,j_r+1]}$; clearly we must have $s_l \geq 2$ for all $l \in [i_r+2,j_r-1]$ (which is a non-empty interval since $\ell(q_r) \geq 4$), while $s_l\geq 1$ for $l \in \{i_r,i_r+1,j_r,j_r+1\}$.
-
-By Remark~\ref{rem:props of length 2 and 3}, $D_r$ admits at least one propagator of length 2 and none of length 3.
-Let $p_{r+1}$ be a propagator of length 2 in $D_r$; if it forms part of the configuration \eqref{eq:2 prop config} then we are done.
-Otherwise, at least one endpoint of $p_{r+1}$ lies on an edge contained in the non-empty interval $[i_r+2,j_r-1]$, and so there is at least one other propagator connected to this edge.
-Up to symmetry, there are three possibilities:
-
-% this was 100% a productive use of my time
-
-\[\begin{tabular}{ccc}
-% possibility 1
-\begin{tikzpicture}
-\pgfmathsetmacro{\radius}{2}
-\pgfmathsetmacro{\angle}{15}
-\begin{scope}
-\clip (-\radius*1.1,0) rectangle (\radius*1.1,\radius*1.1);
-
-% vertices 
-\foreach \i in {2,3,4,6,7,8,9,10}{
-	\draw (\angle*\i:\radius*0.98) --  (\angle*\i:\radius*1.02);
-}
-
-% \dots 
-\foreach \i in {1,2,3}{
-	\node at (65 + \i*5:\radius cm) {$\cdot$};
-}
-
-\begin{scope} % this scope contains the propagators
-\clip (0,0) circle[radius=\radius];
-
-\draw[propagator] (\angle*2.4:\radius*1.2 cm) to [bend left=30] (\angle*9.7:\radius*1.2 cm); % q_r
-\draw[propagator] (\angle*7.7:\radius*1.1 cm) to [bend left=90] (\angle*9.45:\radius*1.1 cm); % p_{r+1}
-
-% grey prop begins here
-
-\begin{scope}
-\clip (\angle*7.5:\radius cm) circle[radius=\radius*0.45cm];
-\draw[light-gray,propagator,seconddash] (\angle*6:\radius*1.02 cm) circle[x radius=\radius*0.4cm, y radius = \radius*0.3cm];
-\end{scope}
-
-\begin{scope}
-\clip (0,0) circle[radius=\radius];
-\clip (\angle*7.5:\radius cm) circle[radius=\radius*0.4cm];
-\draw[light-gray,propagator,firstdash] (\angle*6:\radius*1.02 cm) circle[x radius=\radius*0.4cm, y radius = \radius*0.3cm];
-\end{scope}
-
-\begin{scope}
-\clip (\angle*7.5:\radius cm) circle[radius=\radius*0.3cm];
-\clip (0,0) circle[radius=\radius];
-\draw[light-gray,propagator] (\angle*6:\radius*1.02 cm) circle[x radius=\radius*0.4cm, y radius = \radius*0.3cm];
-\end{scope}
-% end gray prop
-
-\end{scope}
-
-\node at (90:\radius*0.30 cm) {\tiny $q_r$};
-\node at (\angle*8:\radius*0.73) {\tiny $p_{r+1}$};
-\node[light-gray] at (\angle*4.9:\radius*0.77 cm) {\tiny $q_{r+1}$};
-\node at (2*\angle:\radius*1.1) {\tiny $i_r$};
-\node at (9*\angle:\radius*1.1) {\tiny $j_r$};
-
-% circle/edges; needs to happen last to overlap gray
-\begin{scope}
-\clip (-\radius*1.1,0.9) rectangle (\radius*1.1,\radius*1.1);
-\draw[-] (0,0) circle[radius=\radius cm];
-\end{scope}
-
-\end{scope} % ends the overall rectangle clipping
-\end{tikzpicture}
-
-&
-
-% possibility 2
-\begin{tikzpicture}
-\pgfmathsetmacro{\radius}{2}
-\pgfmathsetmacro{\angle}{15}
-\begin{scope}
-% overall clipping to make the size sensible
-\clip (-\radius*1.1,0) rectangle (\radius*1.1,\radius*1.1);
-
-% vertices
-\foreach \i in {2,3,4,6,7,8,9,10}{
-	\draw (\angle*\i:\radius*0.98) --  (\angle*\i:\radius*1.02);
-}
-
-% \dots
-\foreach \i in {1,2,3}{
-	\node at (65 + \i*5:\radius cm) {$\cdot$};
-}
-
-\begin{scope} % props
-\clip (0,0) circle[radius=\radius cm]; 
-\draw[propagator] (\angle*2.4:\radius*1.2 cm) to [bend left=30] (\angle*9.6:\radius*1.2 cm); % q_r
-\draw[propagator] (\angle*6.7:\radius*1.1 cm) to [bend left=90] (\angle*8.6:\radius*1.1 cm); % p_{r+1}
-
-%% grey prop starts here
-
-\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.45cm];
-\draw[light-gray,propagator,seconddash] (\angle*4.5:\radius*1.3 cm) circle[y radius = 0.5*\radius cm,x radius=\radius*0.7cm];
-\end{scope}
-
-\begin{scope}
-\clip (0,0) circle[radius=\radius];
-\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.4cm];
-\draw[light-gray,propagator,firstdash] (\angle*4.5:\radius*1.3 cm) circle[y radius = 0.5*\radius cm,x radius=\radius*0.7cm];
-\end{scope}
-
-\begin{scope}
-\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.3cm];
-\clip (0,0) circle[radius=\radius];
-\draw[light-gray,propagator] (\angle*4.5:\radius*1.3 cm) circle[y radius = 0.5*\radius cm,x radius=\radius*0.7cm];
-\end{scope}
-% grey prop ends here
-
-\node at (90:\radius*0.32 cm) {\tiny $q_r$};
-\node at (\angle*7.75:\radius*0.75) {\tiny $p_{r+1}$};
-\node[light-gray] at (\angle*4.5:\radius*0.7 cm) {\tiny $q_{r+1}$};
-\node at (2*\angle:\radius*1.1) {\tiny $i_r$};
-\node at (9*\angle:\radius*1.1) {\tiny $j_r$};
-
-% circle/edges
-\begin{scope}
-\clip (-\radius*1.1,0.9) rectangle (\radius*1.1,\radius*1.1);
-\draw[-] (0,0) circle[radius=\radius cm];
-\end{scope}
-
-\end{scope} % ends overall clip
-\end{tikzpicture}
-
-&
-
-% possiblitiy 3
-\begin{tikzpicture}
-\pgfmathsetmacro{\radius}{2}
-\pgfmathsetmacro{\angle}{12}
-\begin{scope}
-\clip (-\radius*1.1,0) rectangle (\radius*1.1,\radius*1.1);
-
-% vertices
-\foreach \i in {2,3,6,7,8,9,12,13}{
-	\draw (\angle*\i:\radius*0.98) --  (\angle*\i:\radius*1.02);
-}
-
-% \dots
-\foreach \i in {1,2,3}{
-	\node at (44 + \i*5:\radius cm) {$\cdot$};
-	\node at (116 + \i*5:\radius cm) {$\cdot$};
-}
-
-\begin{scope} % props
-\clip (0,0) circle[radius=\radius cm];
-\draw[propagator] (\angle*2.4:\radius*1.2 cm) to [bend left=30] (\angle*12.6:\radius*1.2 cm); % q_r
-\draw[propagator] (\angle*6.5:\radius*1.1 cm) to [bend left=100] (\angle*8.5:\radius*1.05 cm); % p_{r+1}
-
-%  grey prop 1
-% not q_{r+1}
-\begin{scope}
-\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.45cm];
-\draw[light-gray,propagator,seconddash] (\angle*6.5:\radius*1.1 cm) to [bend left=90] (\angle*12.5:\radius*1.1cm);
-\end{scope}
-
-\begin{scope}
-\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.4cm];
-\draw[light-gray,propagator,firstdash] (\angle*6.5:\radius*1.1 cm) to [bend left=90] (\angle*12.5:\radius*1.1cm);
-\end{scope}
-\begin{scope}
-\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.3cm];
-\draw[light-gray,propagator] (\angle*6.5:\radius*1.1 cm) to [bend left=90] (\angle*12.5:\radius*1.1cm);
-\end{scope}
-% grey prop 1 ends here
-
-% grey prop 2
-% this is q_{r+1}
-\begin{scope}
-\clip (\angle*8.5:\radius cm) circle[radius=\radius*0.45cm];
-\draw[propagator,seconddash,light-gray] (\angle*8.8:\radius*1.1 cm) to [bend left=90] (\angle*12:\radius*1.1cm);
-\end{scope}
-
-\begin{scope}
-\clip (\angle*8.5:\radius cm) circle[radius=\radius*0.4cm];
-\draw[propagator,firstdash,light-gray] (\angle*8.8:\radius*1.1 cm) to [bend left=90] (\angle*12:\radius*1.1cm);
-\end{scope}
-
-\begin{scope}
-\clip (\angle*8.5:\radius cm) circle[radius=\radius*0.3cm];
-\draw[light-gray,propagator] (\angle*8.8:\radius*1.1 cm) to [bend left=90] (\angle*12:\radius*1.1cm);
-\end{scope}
-
-% grey prop 2 ends here
-
-\end{scope}
-
-\node at (90:\radius*0.15 cm) {\tiny $q_r$};
-\node at (\angle*7.5:\radius*0.83) {\tiny $p_{r+1}$};
-\node[light-gray] at (\angle*11:\radius*0.75 cm) {\tiny $q_{r+1}$};
-
-\node at (2*\angle:\radius*1.1) {\tiny $i_r$};
-\node at (12*\angle:\radius*1.1) {\tiny $j_r$};
-
-% overall circle
-\begin{scope}
-\clip (-\radius*1.1,0.7) rectangle (\radius*1.1,\radius*1.1);
-\draw[-] (0,0) circle[radius=\radius cm];
-\end{scope}
-
-\end{scope} % ends overall clip
-\end{tikzpicture}
-
-\end{tabular}
-\]
-In each case, the diagram indicates how to choose $q_{r+1}$ satisfying the induction hypothesis.
-In the third case, note that \textit{both} ends of $p_{r+1}$ must share their edge with a propagator of length $\geq 4$; the non-crossing hypothesis on propagators guarantees that at least one will bound a region not containing $p_{r+1}$.
-\end{proof}
 
@@
 If the propagator $p$ is removed at vertex $i$ according to the algorithm for $I_a$, we say that $p$ \emph{contributes} $i$ to $I_a$.
-Notationally, we represent this by allowing the $I_i$ symbol to represent a function as well as a set, as follows:
-\begin{dfn}\label{def I_i as a function}
-Let $W = (\cP, n)$ be an admissible Wilson loop diagram. For each $a \in [n]$, define a function $I_a : \cP \longrightarrow [n]$ by
-\[I_a(p) := \text{the vertex label that $p$ contributes to $I_a$ in Algorithm~\ref{alg:put GN on WLD},}\]
-for each $p \in \cP$.
-\end{dfn}
-
-\begin{lem}\label{lem no fourth vertex}
-Let $W$ be an admissible Wilson loop diagram containing at least one propagator. For any $i \in [n]$ and for any $p=(a,b)$ with $i\leq_i a <_i b$, we have $I_i(p) \neq b+1$.
-\end{lem}
-\begin{proof}
-Suppose for contradiction that we have $p = (a,b)$ with $i\leq_i a <_i b$ and $I_{i}(p) = b+1$. We may choose $p$ such that $|\interval{a+1}{b}|$ is minimal amongst propagators with this property.
-
-Since $I_i(p) \neq b$, there must exist a propagator $q$ inside of $p$ with $I_i(q) = b$.
-The propagator $q$ cannot end on the edge $(b-1,b)$, as this would contradict the minimality of $p$, so $q = (c,c+1,b,b+1)$ with $a <_i c <_i b$, and $I_i(q) = b$.
-
-In order for $q$ to remain unassigned until vertex $b$, there must be another propagator $r$ with an end on $(c,c+1)$ and $I_i(r) = c+1$; the only way this can occur is if $r$ is outside $q$ but inside $p$.
-Now $r$ contributes its fourth vertex to $I_i$, again contradicting the minimality of $p$.
-\end{proof}
-
-\begin{cor}\label{GN alg well defined}
-If $W$ is an admissible Wilson loop diagram with $k$ propagators, then Algorithm~\ref{alg:put GN on WLD} assigns exactly $k$ vertices to each $I_i$.
-\end{cor}
-\begin{proof}
-It follows from the proof of Lemma~\ref{lem no fourth vertex} that Algorithm~\ref{alg:put GN on WLD} can never reach the fourth vertex of a propagator's support (with respect to the starting vertex).
-Therefore if the algorithm starts at vertex $i$, it must have assigned vertices to all propagators by the time it reaches $i-1$, ensuring that $I_i$ contains exactly $k$ distinct vertices.
-\end{proof}
 
@@
 
-In an arbitrary Grassmann necklace, it is possible for an index $i$ to appear in no terms of the Grassmann necklace (a {\em loop}) or in all terms of the necklace (a {\em coloop}).
-Clearly any vertex of $W$ that supports no propagators will yield a loop [ref][check: is this iff?], but with Theorem [ref][cyclic intervals thm] in hand we can now easily verify that admissible Wilson loop diagrams do not admit coloops.
-
-\begin{cor}\label{no coloops}
-Grassmann necklaces coming from admissible Wilson loop diagrams have no coloops, that is no indices $a$ such that $a \in I_i$ for all $i$.
-\end{cor}
-\begin{proof}
-For any $a \in [n]$, $a-1$ is maximal with respect to the $<_{a}$ order. Therefore there is no propagator $p$ with $I_{a}(p) = a-1$ by Lemma~\ref{lem no fourth vertex}, i.e. $a-1 \not\in I_{a}$.
-\end{proof}
-
 \subsection{Dimension of the Wilson Loop cells}
@@
 
+\subsection{Some definitions and results that should probably be moved to section 3 but I don't know if anyone's editing that right now}
+
+It will often be useful to refer to the vertex label contributed by a propagator to a Grassmann necklace term.
+Notationally, we represent this by allowing the $I_i$ symbol to represent a function as well as a set, as follows:
+\begin{dfn}\label{def I_i as a function}
+Let $W = (\cP, n)$ be an admissible Wilson loop diagram. For each $i \in \interval{1}{n}$, define a function $I_i : \cP \longrightarrow \interval{1}{n}$ by
+\[I_i(p) := \text{the vertex label that $p$ contributes to $I_i$ in Algorithm~\ref{alg:put GN on WLD},}\]
+for each $p \in \cP$.
+\end{dfn}
+\todo{Depending where this ends up, possibly include an example here.}
+
+\begin{dfn}\label{props inside p}
+Let $p$ be a propagator supported on $(i,j)$.
+The region bounded by $p$ and the edge of the Wilson loop diagram from $i$ to $j+1$ is refered to as the region {\bf inside} $p$, and the complement is the region {\bf outside }$p$.
+The set of propagators inside (resp.
+outside) $p$ are those lying in the region inside (resp.
+outside) $p$, excluding $p$ itself.
+\end{dfn}
+Note that this depends on the order of $i$ and $j$: if we view $p$ as supported on $(j,i)$ then the regions inside and outside $p$ are swapped.
+
+\begin{lem}\label{lem no fourth vertex}
+Let $W$ be an admissible Wilson loop diagram containing at least one propagator. For any $i \in [n]$ and for any $p=(a,b)$ with $i\leq_i a <_i b$, we have $I_i(p) \neq b+1$.
+\end{lem}
+\begin{proof}
+Suppose for contradiction that we have $p = (a,b)$ with $i\leq_i a <_i b$ and $I_{i}(p) = b+1$. We may choose $p$ such that $|\interval{a+1}{b}|$ is minimal amongst propagators with this property.
+
+Since $I_i(p) \neq b$, there must exist a propagator $q$ inside of $p$ with $I_i(q) = b$.
+The propagator $q$ cannot end on the edge $(b-1,b)$, as this would contradict the minimality of $p$, so $q = (c,c+1,b,b+1)$ with $a <_i c <_i b$, and $I_i(q) = b$.
+
+In order for $q$ to remain unassigned until vertex $b$, there must be another propagator $r$ with an end on $(c,c+1)$ and $I_i(r) = c+1$; the only way this can occur is if $r$ is outside $q$ but inside $p$.
+Now $r$ contributes its fourth vertex to $I_i$, again contradicting the minimality of $p$.
+\end{proof}
+
+\begin{cor}\label{GN alg well defined}
+If $W$ is an admissible Wilson loop diagram with $k$ propagators, then Algorithm~\ref{alg:put GN on WLD} assigns exactly $k$ vertices to each $I_i$.
+\end{cor}
+\begin{proof}
+It follows from the proof of Lemma~\ref{lem no fourth vertex} that Algorithm~\ref{alg:put GN on WLD} can never reach the fourth vertex of a propagator's support (with respect to the starting vertex).
+Therefore if the algorithm starts at vertex $i$, it must have assigned vertices to all propagators by the time it reaches $i-1$, ensuring that $I_i$ contains exactly $k$ distinct vertices.
+\end{proof}
+
+\begin{cor}\label{no coloops}
+Grassmann necklaces coming from admissible Wilson loop diagrams have no coloops, that is no indices $a$ such that $a \in I_i$ for all $i$.
+\end{cor}
+\begin{proof}
+For any $a \in [n]$, $a-1$ is maximal with respect to the $<_{a}$ order. Therefore there is no propagator $p$ with $I_{a}(p) = a-1$ by Lemma~\ref{lem no fourth vertex}, i.e. $a-1 \not\in I_{a}$.
+\end{proof}
+
+\subsection{actual beginning of section 4; this subsection header can go away once the results above have found their place}
+
 The results of Section~\ref{sec GN algorithm} allow us to relate the position of propagators in a Wilson loop diagram $W$ to minors of $C(W)$, which we use in this section to understand the denominator of the integral $I(W)$ associated to a Wilson loop diagram (see Definition~\ref{def R(W)}).

### 2018-11-21 General WLD combinatorics.tex
one tiny typo
edited proof of lemma 3.5

--- 2018-11-19 General WLD combinatorics.tex
@@
 
-\note{I don't think rank of a vertex (in the sense of number of propagators supported on it) was ever used, so I removed the definition}
+%\note{I don't think rank of a vertex (in the sense of number of propagators supported on it) was ever used, so I removed the definition}
 %\note{rank probably isn't a good word; do we have a better one?}
@@
 \begin{dfn}\note{right now this doesn't depend on the order of $i$ and $j$, but that might matter later on?}
-Let $p$ be a propagator supported on the vertices $(i,i+1,j,j+1)$.  Define the \textit{length} of $p$ to be 
+Let $p$ be a propagator supported on $(i,j)$.  Define the \textit{length} of $p$ to be 
 \[\ell(p) = min\big\{|[i+1,j]|,|[j+1,i]|\big\}.\]
@@
 \item If every vertex in $W$ supports at least one propagator, then $W$ admits at least one propagator of length 2.
-\item If $p = (i,i+1,i+3,i+4)$ is a propagator of length 3, then the middle vertex $i+2$ supports at most one propagator.
+\item If $p = (i,i+3)$ is a propagator of length 3, then the middle vertex $i+2$ supports at most one propagator.
 \end{itemize}
 \end{rmk}
-
-\note{Are the next few definitions used outside the proof of Lemma~\ref{lem sian 1}?  If not, then perhaps they could go inside the proof so as not to clutter the document with temporary definitions?}
-\begin{dfn}
-Define the restriction of $W$ to a region $[i,j]$ to be the subdiagram obtained by forgetting all propagators not wholly supported on vertices in the cyclic interval $[i,j]$.
-Denote this diagram by $W_{[i,j]}$.
-\end{dfn}
-\note{I think there's an issue here about what we mean by subdiagram; in def 1.5 we say a subdiagram is of the form $(P, V(P))$ which is certainly not what we want here; in fact I think we want the subdiagram where the vertex set is unchanged and only the propagator set is restricted (the other possibility would be to restrict the vertex set to $[i, j]$, but then the lengths of propagators can change and in the way we want to use it (see paragraph below) $p$ will become very non-admissible).
-I think def 1.5 should be removed and we should say that for a WLD $(P, V)$ subdiagrams are any $(P', V')$ with $P'\subseteq P$, $V'\subseteq V$ and all supporting vertices of elements of $P'$ in $V'$; this seems to me to be the natural notion of subobject.}
-
-If $p$ is a propagator supported on $(i,i+1,j,j+1)$, then we can consider two obvious restrictions of $D$, namely $D_{[i,j+1]}$ and $D_{[j,i+1]}$.
-Clearly all other propagators $q\neq p$ appear in exactly one of these subdiagrams, while $p$ appears in both.
-In this case, we will say that $p$ \textit{bounds the regions} $[i,j+1]$ and $[j,i+1]$; the ordering of the start and end points allow us to identify one or the other region unambiguously.
 
@@
       \begin{enumerate}
-        \item There is a propagator of length $2$, say $(i, i+1, i+2, i+3)$ such that no other propagators ends on either the edge $(i, i+1)$ or the edge $(i+2, i+3)$.\label{item lonely 2}
-        \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+1, i+2, i+3)$, the second is $(j, j+1, j+2, j+3)$, no other propagator ends between $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
-        \item There exists a propagator of length exactly 4 with only a propagator of length 2 inside it.\label{item 4 and 2}
+        \item There is a propagator of length $2$, say $(i, i+2)$ such that no other propagators ends on either the edge $i$ or the edge $i+2)$.\label{item lonely 2}
+        \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator ends between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
+        \item There exists a propagator of length 4 with only a propagator of length 2 inside it.\label{item 4 and 2}
       \end{enumerate}
@@
 \begin{proof}
-  Suppose first that $W$ has a propagator of length $3$, $p=(i, i+1, i+3, i+4)$.
+  Suppose first that $W$ has a propagator of length $3$, $p=(i, i+3)$.
 By Remark~\ref{rem:props of length 2 and 3} along with the fact that every vertex of $W$ supports at least one propagator, we have that $i+2$ supports exactly one propagator and this propagator must have length 2 by noncrossingness.
@@
 %\end{equation}
+
+We need a bit of notation:
+Define the restriction of $W$ to a region $[i,j]$ to be the subdiagram obtained by forgetting all propagators not wholly supported on vertices in the cyclic interval $[i,j]$; the vertex set remains the same as in $W$.
+Denote this diagram by $W_{[i,j]}$.
+
+Note that if $p$ is a propagator supported on $(i,j)$, then we can consider two obvious restrictions of $W$, namely $W_{[i,j+1]}$ and $W_{[j,i+1]}$.
+Clearly all other propagators $q\neq p$ appear in exactly one of these subdiagrams, while $p$ appears in both.
+In this case, we will say that $p$ \textit{bounds the regions} $[i,j+1]$ and $[j,i+1]$; the ordering of the start and end points allow us to identify one or the other region unambiguously.
+
+With these observations in mind we can return to the proof.
 
@@
 
-Start by choosing a propagator $p_1$ of length 2 in $W$ (which exists by Remark~\ref{rem:props of length 2 and 3}), and write $(j_1,j_1+1,j_1+2,j_1+3)$ for its support.
+Start by choosing a propagator $p_1$ of length 2 in $W$ (which exists by Remark~\ref{rem:props of length 2 and 3}), and write $(j_1,j_1+2)$ for its support.
 If it is part of one of the configurations we are looking for then we are done,
 %a configuration \eqref{eq:2 prop config} we are done,
-so suppose otherwise: since $p_1$ is not in configuration \ref{item lonely 2} then there must be a second propagator starting either on edge $(j_1, j_1+1)$ or $(j_1+2, j_1+3)$.
+so suppose otherwise: since $p_1$ is not in configuration \ref{item lonely 2} then there must be a second propagator starting either on edge $j_1)$ or $j_1+2$.
 Flipping the diagram if necessary, assume the former.
-Since $p_1$ is not in configuration \ref{item pair of 2s} and every vertex is supported then there must exist a propagator $q_1$ of length $\geq 4$ with one end on edge $(j_1,j_1+1)$ or on edge $(j_1-1, j_1)$ or on edge $(j_1-2, j_1-1)$.
+Since $p_1$ is not in configuration \ref{item pair of 2s} and every vertex is supported then there must exist a propagator $q_1$ of length $\geq 4$ with one end on edge $j_1$ or on edge $j_1-1$ or on edge $j_1-2$.
 This bounds a region $[i_1,k_1]$ (where $k_1 \in \{j_1-1, j_1, j_1+1\}$) which does not contain $p_1$.
 
-Now suppose $q_{r}$ exists by the induction hypothesis and bounds a region $[i_r,k_r]$.
+Now suppose $q_{r}$ exists by the induction hypothesis and bounds a region $[i_r,k_r]$ not containing any $p_i$ for $i\leq r$.
 Consider the restricted diagram $W_r:=W_{[i_r,k_r]}$; by the original hypotheses on $W$ every vertex $l \in [i_r+2,k_r-2]$ (which is a non-empty interval since $\ell(q_r) \geq 4$) must have support $\geq 1$, while the same is true for $l \in \{i_r,i_r+1,k_r-1,k_r\}$ because of $q_r$.
@@
 $W_r$ has no propagators of length $3$ since $W$ has none.
-\note{now the question really is important about what length means in the restricted diagram; as written the restricted diagram has the same vertex set so length is unchanged.}   Let $p_{r+1}$ be a propagator of length 2 in $W_r$; if it forms part of configuration \ref{item lonely 2}, \ref{item pair of 2s}, or \ref{item 4 and 2}
+Let $p_{r+1}$ be a propagator of length 2 in $W_r$; if it forms part of configuration \ref{item lonely 2}, \ref{item pair of 2s}, or \ref{item 4 and 2}
 %the configuration \eqref{eq:2 prop config}
@@
 
-Note we may replace $q_r$ by any other propagator of length $\geq 4$ in $W_r$ which contains $p_{r+1}$ while still satisfying all the hypotheses, and so, without loss of generality we may assume that $q_r$ has minimal length among propagators of length $\geq 4$ which contain $p_{r+1}$.
+Note we may replace $q_r$ by any other propagator of length $\geq 4$ in $W_r$ which contains $p_{r+1}$ and such a new $q_r$ still satisfies all the hypotheses, and so, without loss of generality we may assume that $q_r$ has minimal length among propagators of length $\geq 4$ which contain $p_{r+1}$.
 
 There are two cases to consider.
-The first case is that neither end of $p_{r+1}$ lies on an edge contained in the possibly empty interval $[i_r+3,k_r-3]$, then since $p_{r+1}$ has length 2, it must be that $[i_r+3,k_r-3]$ is at most a single edge, and so $q_r$ has length $\leq 6$.
-Since $p_{r+1}$ has one end before $i_r+3$ and the other after $k_r-3$, the only propagators inside $q_r$ that do not also contain $p_{r+1}$ must have both ends in $[i_r, i_r+3]$ or both ends in $[k_r-3, k_r]$ and hence be of length 2.
+The first case is that $p_{r+1}$ has one end before $i_r+3$ and the other after $k_r-3$.
+Then since $p_{r+1}$ has length 2, it must be that $[i_r+3,k_r-3]$ is at most a single edge, and so $q_r$ has length $\leq 6$.
+The only propagators inside $q_r$ that do not also contain $p_{r+1}$ must have both ends in $[i_r, i_r+3]$ or both ends in $[k_r-3, k_r]$ and hence be of length 2.
 Therefore, if $q_r$ contains a propagator $t$ of length $\leq 4$, this propagator must also contain $p_{r+1}$ which is impossible my minimality.
@@
 
-The second case is that at least one endpoint of $p_{r+1}$ lies on an edge contained in the interval $[i_r+3,k_r-3]$.
-Up to symmetry we can write $p_{r+1} = (j_{r+1}, j_{r+1}+1, j_{r+1}+2, j_{r+1}+3)$ where $(j_{r+1}+2, j_{r+1}+3)$ is contained in $[i_r+3, k_r-3]$.
-Since $p_{r+1}$ is not part of configuration \ref{item pair of 2s} and vertex $j_{r+1}+4$ is supported (and not by $q_r$ since $j_{r+1}+4 \leq k_r-2$), there is some propagator $t$ with one end in $[j_{r+1}+2, j_{r+1}+4]$ and length $\geq 4$.
+The second case is that either at least one endpoint of $p_{r+1}$ lies on an edge contained in the interval $[i_r+3,k_r-3]$, or both ends lie in $[i_r, i_r+3]$ or $[k_r-3, k_r]$; these situations all behave similarly.
+Up to symmetry we can write $p_{r+1} = (j_{r+1}, j_{r+1}+2)$ where either the edge $j_{r+1}+2$ is contained in $[i_r+3, k_r-3]$ or $j_{r+1}+2 = i_r+2$.
+Since $p_{r+1}$ is not part of configuration \ref{item pair of 2s} and vertex $j_{r+1}+4$ is supported (and not by $q_r$ since $j_{r+1}+4 \leq k_r-2$ in both situations), there is some propagator $t$ with one end in $[j_{r+1}+3, j_{r+1}+5]$ and length $\geq 4$.
 By noncrossingness $t$ is contained in $q_{r}$.

### 2018-11-21 General WLD combinatorics.tex
copied in the recursive cyclic intervals, but haven't edited it yet

@@
 Configurations \ref{item lonely 2} and \ref{item 4 and 2} also necessarily entail vertices with support $1$ as does configuration \ref{item pair of 2s} unless $j=i+2$.
-So in the case that $W$ has all vertices with support at least two then $W$ must contain a pair of propagators of length $2$  with the property that the first propagator is $(i, i+1, i+2, i+3)$, the second is $(i+2, i+3, i+4, i+5)$ and no other propagator ends on the edge $(i+2, i+3)$.
+So in the case that $W$ has all vertices with support at least two then $W$ must contain a pair of propagators of length $2$  with the property that the first propagator is $(i, i+2)$, the second is $(i+2, i+4)$ and no other propagator ends on the edge $i+2$.
 \end{rmk}
@@
 
-Next we prove that this algorithm actually gives a Grassmann Necklace as claimed. We begin with some useful definitions and lemmas
-
-\begin{dfn}\label{protect dfn}
-Let $W = (\cP,n)$ be an admissible diagram and $a \in[n]$ a vertex.
+%Next we prove that this algorithm actually gives a Grassmann Necklace as claimed. We begin with some useful definitions and lemmas
+%
+%\begin{dfn}\label{protect dfn}
+%Let $W = (\cP,n)$ be an admissible diagram and $a \in[n]$ a vertex.
 For $p= (i,j) \in \cP$ an a propagator of $W$  and $v \in \{i, j\}$ a vertex of $W$, let $P_{v}(p)$ or $P_{v+1}(p)$ to be two \emph{protecting sets of $p$ at $v$ and ${v+1}$} be a set of propagators defined as follows: \begin{enumerate}
-\item Work under the linear order on $[n]$, $<_{v+1}$, every propagator is now written as $p = (i_p, j_p)$ such that $i_p <_{v+1} j_p$.
-\item If there is a propagator $s_1 \in \cP$ such that $s_1 = (i_{s_1}, v)$ or $s_1 = (i_{s_1}, v-1)$, then $s_1 \in P_v(p)$.
-\item If $s_1$ as above does not exists, then $P_v(p) = \emptyset$.
+%\item Work under the linear order on $[n]$, $<_{v+1}$, every propagator is now written as $p = (i_p, j_p)$ such that $i_p <_{v+1} j_p$.
+%\item If there is a propagator $s_1 \in \cP$ such that $s_1 = (i_{s_1}, v)$ or $s_1 = (i_{s_1}, v-1)$, then $s_1 \in P_v(p)$.
+%\item If $s_1$ as above does not exists, then $P_v(p) = \emptyset$.
 In this case, $P_w(p) = \emptyset$.
 When $P_v(p) \neq \emptyset$, if there exists a propagator $t_1 \in \cP$ defined such that $t_1 = (i_{t_1}, v)$ and $s_1 = (i_{s_1}, v)$ with $i_p <_{v+1} i_{t_1} <_{v+1} i_{s_1}$, $P_w(p) = t_1$.
-\item If $s_1 = (i_{s_1}, v)$ then \bas P_v(p)=  \begin{cases} \{s_1\} \cup P_{i_{s_1}}(s_1) \cup P_{i_{s_1}+1}(s_1) & \textrm{ if } P_{i_{s_1}+1}(s_1) \neq \emptyset \\ s_1 &  \textrm{ else } \end{cases}.
+%\item If $s_1 = (i_{s_1}, v)$ then \bas P_v(p)=  \begin{cases} \{s_1\} \cup P_{i_{s_1}}(s_1) \cup P_{i_{s_1}+1}(s_1) & \textrm{ if } P_{i_{s_1}+1}(s_1) \neq \emptyset \\ s_1 &  \textrm{ else } \end{cases}.
 \eas  If $s_1 = (i_{s_1}, v-1)$ then \bas P_v(p)=  \begin{cases}  \emptyset & \textrm{ if } P_{v-1}(s_1) = \emptyset \\ \{s_1\} \cup P_{v-1}(s_1) & \textrm{ else } \end{cases} \eas.
-\end{enumerate}
-\end{dfn}
-
-The protective sets $P_\cdot(p)$ are designed to prevent $p$ from contributing the vertex indicated in the subscript at certain points in the Grassmann Necklace, $I_a$.
+%\end{enumerate}
+%\end{dfn}
+%
+%The protective sets $P_\cdot(p)$ are designed to prevent $p$ from contributing the vertex indicated in the subscript at certain points in the Grassmann Necklace, $I_a$.
 Write $P_v(p) = \{s_1, \ldots s_r, t_2,  \ldots t_r\}$ with the $t_x = P_{i_{s_{x-1}}+1}(s_{x-1})$ and $s_x \in P_{i_{s_{x-1}}}(s_{x-1})$ for $x \geq 2$.
@@
 \end{enumerate}
-
-\begin{eg} \label{eg: protective sets}
-Consider the admissible Wilson loop diagram
-\bas W=\begin{tikzpicture}[rotate=120,baseline=(current bounding box.east)]
-	\begin{scope}
-	\drawWLD{17}{3}
-	\drawnumbers
-	\drawprop{1}{0}{16}{0}
-	\drawlabeledprop{2}{0}{15}{1}{p}
-    \drawprop{6}{2}{15}{0}
-    \drawprop{3}{0}{6}{1}
-    \drawprop{4}{0}{6}{0}
-    \drawprop{7}{0}{11}{0}
-    \drawprop{8}{0}{10}{0}
-    \drawprop{11}{1}{14}{1}
-    \drawprop{12}{0}{14}{0}
-		\end{scope}
-	\end{tikzpicture}
-\eas Consider the two sets of propagators $Q = \{(3, 6), (4, 6), (6,15)\}$ and $R = \{ (7, 11), (8, 10), (11, 14), (12, 14)\}$.
+%
+%
+%\begin{eg} \label{eg: protective sets}
+%Consider the admissible Wilson loop diagram
+%\bas W=\begin{tikzpicture}[rotate=120,baseline=(current bounding box.east)]
+%	\begin{scope}
+%	\drawWLD{17}{3}
+%	\drawnumbers
+%	\drawprop{1}{0}{16}{0}
+%	\drawlabeledprop{2}{0}{15}{1}{p}
+%    \drawprop{6}{2}{15}{0}
+%    \drawprop{3}{0}{6}{1}
+%    \drawprop{4}{0}{6}{0}
+%    \drawprop{7}{0}{11}{0}
+%    \drawprop{8}{0}{10}{0}
+%    \drawprop{11}{1}{14}{1}
+%    \drawprop{12}{0}{14}{0}
+%		\end{scope}
+%	\end{tikzpicture}
+%\eas Consider the two sets of propagators $Q = \{(3, 6), (4, 6), (6,15)\}$ and $R = \{ (7, 11), (8, 10), (11, 14), (12, 14)\}$.
 The propagator $p = (2, 15)$ is protected at $a = 5$ from contributing $15$ to $I_5$ by the set $P_{15} = Q$.
@@
 We may just as easily right $P_{15} = R$ and $P_{16} = R$, though the other two propagators in each set are unnecessary.
-
-Note that for $a=1$, the propagator $p$ contributes $2$ to $I_1$. However, in this case, we say that neither $P_{15}$ or $P_{16}$ exist.
-\end{eg}
-
-\begin{lem}\label{protecting lem}
-Let $W = (\cP, n)$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$, and $a \in [n]$ be a vertex.
+%
+%Note that for $a=1$, the propagator $p$ contributes $2$ to $I_1$. However, in this case, we say that neither $P_{15}$ or $P_{16}$ exist.
+%\end{eg}
+%
+%
+%\begin{lem}\label{protecting lem}
+%Let $W = (\cP, n)$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$, and $a \in [n]$ be a vertex.
 For $v \in \{i,j\}$, if $P_v(p) \neq \emptyset$, write $P_v(p) = \{s_1 \ldots s_r, t_2, \ldots t_r\}$ as above.
@@
 If both $P_v(p)$ and $P_{v+1}(p)$ are non empty, then $p$ also does not contribute $v+1$ to $I_a$.
-\end{lem}
-
-\begin{proof}
-Note that if $s_1 \in P_v(p)$ exists at step $v$ of Algorithm \ref{alg:put GN on WLD}, then $p$ cannot contribute $p$ to $I_a$.
+%\end{lem}
+%
+%\begin{proof}
+%Note that if $s_1 \in P_v(p)$ exists at step $v$ of Algorithm \ref{alg:put GN on WLD}, then $p$ cannot contribute $p$ to $I_a$.
 Further, if $P_{v+1}(p) \neq \emptyset$, $p$ cannot contribute $v+1$ to $I_a$ either.
-
-Next we show that if $P_v(p)$ is as above, with $i_{s_r}+1 <_{v+1} a$, then the propagator $s_1$ exists at step $v$ of Algorithm \ref{alg:put GN on WLD}.
+%
+%Next we show that if $P_v(p)$ is as above, with $i_{s_r}+1 <_{v+1} a$, then the propagator $s_1$ exists at step $v$ of Algorithm \ref{alg:put GN on WLD}.
 Let $x$ be the largest integer that such that $a <_{v_1} j_{x}+1$.
@@
 In other words, $s_1$ has not been removed from the diagram at vertex $v$.
-
-\end{proof}
-
-Thus we say that $P_v(p)$ protects $p$ at $v$ from $a$, for $a \in [i_{s_r}+2, v]$. There is an easy corollary to this, describing when such a protecting set cannot exist.
-
-\begin{cor} \label{protecting cor}
-Let $W = (\cP, n)$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$.
+%
+%\end{proof}
+%
+%Thus we say that $P_v(p)$ protects $p$ at $v$ from $a$, for $a \in [i_{s_r}+2, v]$. There is an easy corollary to this, describing when such a protecting set cannot exist.
+%
+%\begin{cor} \label{protecting cor}
+%Let $W = (\cP, n)$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$.
 Picking a $v \in \{i, j\}$ write $p = (i_p, j_p)$ with $i_p <_{v+1} j_p$.
 If $a \in [j_p+1, i_p+1]$ then there can be no protecting set $P_v$ or $P_{v+1}$ protecting $p$ at $v$ or $v+1$ from $a$.
-\end{cor}
-
-\begin{proof}
-Since $W$ is admissible, it cannot have crossing propagators. Therefore neither $P_v$ cannot have the requisite propagator $s_r$ with $i_{s_r}+1  <_{v+1} a$.
-\end{proof}
-
-The converse, however requires an extra condition.
-
-\begin{lem} \label{protect conv lem}
-For $W = (\cP, n)$, $p = (i,j)$, and $v \in \{i, j\}$ and $ a \in [n]$ a vertex of $W$, if $v$ (resp.
+%\end{cor}
+%
+%\begin{proof}
+%Since $W$ is admissible, it cannot have crossing propagators. Therefore neither $P_v$ cannot have the requisite propagator $s_r$ with $i_{s_r}+1  <_{v+1} a$.
+%\end{proof}
+%
+%The converse, however requires an extra condition.
+%
+%\begin{lem} \label{protect conv lem}
+%For $W = (\cP, n)$, $p = (i,j)$, and $v \in \{i, j\}$ and $ a \in [n]$ a vertex of $W$, if $v$ (resp.
 $v+1$) is the first vertex of $V_p$ in the $<_a$ order such that $P_v$ (resp.
@@
 $v+1$) to $I_a$.
-\end{lem}
-
-\begin{proof}
-Write $p = (i_p, j_p)$ with $i_p <_{v+1} j_p$.
-
-If $p$ doesn't contribute $v$ (or $v+1$) to $I_a$, then either $p$ contributes a different supporting vertex $u$ earlier in the $<_a$ order or there is a propagator $s_1$ at step $v$ of the algorithm \ref{alg:put GN on WLD} preventing $p$ from contributing $v$ to $I_a$, (or there are a pair of propagators $s_1$ and $t_1$ at step $v$ preventing $p$ from contributing $v+1$ at $I_a$.)
-
-If there are propagators $s_1, t_1 \in \cP$ that are still in the diagram at step $v$, (write them $s_1 = (i_{s_1}, j_{s_1})$, and $t_1 = (i_{t_1}, j_{t_1})$) with $j_{s_1} \in \{v, v-1\}$, and $i_p \leq_{v+1} i_{t_1} <_v i_{s_1} <_v j_{s_1} \leq_{v} j_{t_1} = v$) then $s_1$ or $t_1$ did not contribute $i_{s_1}$ or  $i_{s_1} +1 $ (resp.
+%\end{lem}
+%
+%\begin{proof}
+%Write $p = (i_p, j_p)$ with $i_p <_{v+1} j_p$.
+%
+%
+%If $p$ doesn't contribute $v$ (or $v+1$) to $I_a$, then either $p$ contributes a different supporting vertex $u$ earlier in the $<_a$ order or there is a propagator $s_1$ at step $v$ of the algorithm \ref{alg:put GN on WLD} preventing $p$ from contributing $v$ to $I_a$, (or there are a pair of propagators $s_1$ and $t_1$ at step $v$ preventing $p$ from contributing $v+1$ at $I_a$.)
+%
+%If there are propagators $s_1, t_1 \in \cP$ that are still in the diagram at step $v$, (write them $s_1 = (i_{s_1}, j_{s_1})$, and $t_1 = (i_{t_1}, j_{t_1})$) with $j_{s_1} \in \{v, v-1\}$, and $i_p \leq_{v+1} i_{t_1} <_v i_{s_1} <_v j_{s_1} \leq_{v} j_{t_1} = v$) then $s_1$ or $t_1$ did not contribute $i_{s_1}$ or  $i_{s_1} +1 $ (resp.
 $i_{t_1}$ or $i_{t_1}+1$) to $I_a$.
@@
 \item $i_{s_1}+1 \not <_{v+1} a$ and $j_{s_1} = v$: and there must be two other propagators $s_2 = (i_{s_2}, j_{s_2})$ and $t_2 = (i_{t_2}, j_{t_2})$, with $j_{s_2} \in \{i_{s_1}, i_{s_1}-1\}$ and $i_{s_1} \leq_{v+1} i_{t_2} <_{v+1} i_{s_2} <_{v+1} j_{s_2} \leq_{v+1} j_{t_2} = j_{s_1}$   \end{enumerate}
-
-However, now one must ensure that the newly identified propagators $s_2$ and $t_3$ do not contribute to $I_a$ before $i_{s_1}$.
+%
+%However, now one must ensure that the newly identified propagators $s_2$ and $t_3$ do not contribute to $I_a$ before $i_{s_1}$.
 One does this by a similar construction to above.
@@
 By finiteness and admissiblity of the Wilson loop diagram, both these sets are finite; one cannot continue to add propagators $s_i$, $t_i$ ad infinitum.
-
-We claim that this implies that at some point there is a terminal propagator, $s_m \in P_v(p)$ such that $i_{s_m} + 1 <_{v+1} a$, and \bas  \textrm{ either }= \begin{cases} j_{s_m}=i_{s_{m-1}} & \textrm{ }\\ j_{s_m}=j_{s_{m-1}} & \textrm{ } \end{cases} .\eas We show that all other possibilities lead to a contradiction.
+%
+%We claim that this implies that at some point there is a terminal propagator, $s_m \in P_v(p)$ such that $i_{s_m} + 1 <_{v+1} a$, and \bas  \textrm{ either }= \begin{cases} j_{s_m}=i_{s_{m-1}} & \textrm{ }\\ j_{s_m}=j_{s_{m-1}} & \textrm{ } \end{cases} .\eas We show that all other possibilities lead to a contradiction.
 For the remainder of this proof, indicate by $p_k$ some propagator identified at an earlier stage of this construction.
@@
 Futher define $p_0 = p$.
-
-%\begin{cases} j_{s_{m}=i_{s_{m-1}} & \textrm{ } \\  j_{s_m}=j_{s_{m-1}} & \text{ }\end{cases}
-
-If $j_{s_m} \in \{i_{s_{m-1}}-1, j_{s_{m-1}}-1\}$, then, this cannot be the final propagator added to $P_v(p)$, as one would need a means of preventing $s_m$ from contributing $i_{s_{m-1}}-1$ or $j_{s_{m-1}}-1$ to $I_a$.
-
-If $i_{s_m} + 1 \not <_{v+1} a$, then there are two.
- \begin{description}
-
-\item[$j_{s_m} = i_{s_{m-1}}$ and $i_{s_m} \in \{i_{p_k}+2, i_{p_k}+1\}$] for some $k<m$.
+%
+%
+%%\begin{cases} j_{s_{m}=i_{s_{m-1}} & \textrm{ } \\  j_{s_m}=j_{s_{m-1}} & \text{ }\end{cases}
+%
+%If $j_{s_m} \in \{i_{s_{m-1}}-1, j_{s_{m-1}}-1\}$, then, this cannot be the final propagator added to $P_v(p)$, as one would need a means of preventing $s_m$ from contributing $i_{s_{m-1}}-1$ or $j_{s_{m-1}}-1$ to $I_a$.
+%
+%If $i_{s_m} + 1 \not <_{v+1} a$, then there are two.
+% \begin{description}
+%
+%\item[$j_{s_m} = i_{s_{m-1}}$ and $i_{s_m} \in \{i_{p_k}+2, i_{p_k}+1\}$] for some $k<m$.
 By admissibility, there is not room to place both the propagators $s_{m+1}$, and $t_{m+1}$.
@@
 This leads to a contradiction.
-\item[$j_{s_m} = i_{s_{m-1}}$ and $i_{s_m} = i_{p_k}+2$] for some $k<m$. This requires either crossing propagators or propagators starting and ending at the same edge, which violates admissibility.
- \end{description} \note{correct but clear as mud? Help?}
-\end{proof}
-
-We use these results to prove some properties about the Algorithm \ref{alg:put GN on WLD}.
-\begin{prop}\label{res:alg k labels}
-If $W = (\cP, n)$ is an admissible Wilson loop diagram with $|\cP| = k$, then Algorithm~\ref{alg:put GN on WLD} puts exactly $k$ distinct labels on each edge.
-\end{prop}
-\begin{proof}
-It is enough to show that the algorithm terminates in at most $n$ steps for each $a \in [n]$.
+%\item[$j_{s_m} = i_{s_{m-1}}$ and $i_{s_m} = i_{p_k}+2$] for some $k<m$. This requires either crossing propagators or propagators starting and ending at the same edge, which violates admissibility.
+% \end{description} \note{correct but clear as mud? Help?}
+%\end{proof}
+%
+%We use these results to prove some properties about the Algorithm \ref{alg:put GN on WLD}.
+%\begin{prop}\label{res:alg k labels}
+%If $W = (\cP, n)$ is an admissible Wilson loop diagram with $|\cP| = k$, then Algorithm~\ref{alg:put GN on WLD} puts exactly $k$ distinct labels on each edge.
+%\end{prop}
+%\begin{proof}
+%It is enough to show that the algorithm terminates in at most $n$ steps for each $a \in [n]$.
 In other words, that all $k$ propagators of $W$ are removed by the time the algorithm has cycled through all the vertices, starting at $a$.
@@
 Otherwise, change the roles of $i$ and $j$.
-
-Since $p$ is not removed by step $j+1$, by Lemma \ref{protecting lem} there are $4$ protecting sets, $P_i,P_{i+1}, P_{j}$ , and $P_{j+1}$ respectively, allowing $p$ to remain after $n$ steps.
-
-However, since the cyclic interval $[i,j] \subseteq [a,j]$, $P_j$ and $P_{j+1}$ cannot be protecting sets by Corrollary \ref{protecting cor}.
-\end{proof}
-\begin{comment}
+%
+%Since $p$ is not removed by step $j+1$, by Lemma \ref{protecting lem} there are $4$ protecting sets, $P_i,P_{i+1}, P_{j}$ , and $P_{j+1}$ respectively, allowing $p$ to remain after $n$ steps.
+
+%However, since the cyclic interval $[i,j] \subseteq [a,j]$, $P_j$ and $P_{j+1}$ cannot be protecting sets by Corrollary \ref{protecting cor}.
+%\end{proof}
+
+\note{This is a mess for now; protecting sets commented out, and 1.5 versions of the induction copied in by not yet edited}
+
+This is the lemma from the email with the proof copied from the email.
+\begin{lem}\label{lem last vert}
+  Let W be an admissible WLD on $n$ vertices with Grassmann necklace $I_1, \ldots, I_n$.
+Then for all $1\leq a \leq n$, $a-1 \not\in I_a$ interpreted cyclically (that is for $a=1$, $a-1$ is interpreted to be $n$.)
+\end{lem}
+
+\begin{proof}
+Without loss of generality we can suppose $a=1$, so it suffices to show that $C(W)$ with the $n$th column removed is full rank.
+(This suffices because if $C(W)$ with the $n$th column removed had full rank but the lexicographically minimal basis of $C(W)$ included the $n$th column, then we'd obtain a contradiction by taking this minimal basis with the $n$th column removed and extending it to a basis using a column from the first $n-1$ columns of $C(W)$ which is possible by the full rank assumption.)
+
+Because the nonzero entries of $C(W)$ are independent indeterminants, it suffices to show that there is some choice of nonzero entries of $C(W)$, one in each row, each in different columns, and none of which are the $n$th column.
+This is equivalent to an assignment of all propagators to supporting vertices so that no two are assigned to the same vertex and none are assigned to vertex $n$.
+The lemma is proved if we show such an assignment exists.
+
+Consider an assignment $f$ of a subset of propagators to vertices not including vertex $n$ with the maximal number of propagators.
+If $f$ assigns $n$ propagators then we are done.
+Otherwise there is a propagator $p$ which is not assigned but, by maximality, all of $p$s supporting vertices (other than possibly $n$) are assigned.
+Build a sequence of sets $S_i$ of propagators and $T_i$ of vertices as follows.
+
+\begin{enumerate}
+  \item $S_0={p}$ and $T_0$ is the support of $p$ except for $n$.  Set $i=0$.
+  \item Let $R$ be the set of propagators which are assigned to a vertex in $T_i$ by $f$. Let $S_{i+1}= S_i \cup R$.  Let $T_{i+1} = T_i \sup (\text{supp}(R) - \{n\})$.\label{item loop step}
+  \item If there is a vertex $v_{i+1}$ in $T_{i+1}$ which has not yet been assigned then by construction there is a propagator $q_{i+1} \in S_{i+1}-S_i$ which can be assigned to $v_{i+1}$.
+Do so, removing $q_{i+1}$'s old assignment.
+This frees up a vertex $v_{i}$ in $T_i$ and so there is a propagator $q_{i} \in S_{i}$ which can be assigned to this vertex freeing up an earlier vertex and so on until $p$ has been assigned.
+This new assignment contradicts the maximality of $f$.
+  \item  If nothing changed in step \ref{item loop step} then all vertices of $T_{i+1}$ are assigned to propagators in $S_{i+1}-\{p\}$ and vice versa.
+Thus $|S_{i+1}| = |T_{i+1}|+1$.
+Also all the support of propagators in $S_{i+1}$ is in $T_{i+1} \cup \{n\}$, which is a set of size $|T_{i+1}|+1 = |S_{i+1}|$.
+Thus we have $|S_{i+1}|$ propagators supported on $|S_{i+1}|$ vertices contradicting admissibility.
+  \item Increment $i$ and go to \label{itemp loop step}
+\end{enumerate}
+
+This procedure must be finite as either a contradiction is found or $S_i$ grows at each step but $W$ has finitely many propagators.
+However, the only way for the process to end is by reaching a contradiction.
+Therefore any maximal assignment is a basis not including column $n$ which proves the lemma.
+\end{proof}
+
+\note{This was commented out in the file: some (old?) version of the inductive argument?}
 such that $b+1 \in V_{p_1}$, with an endpoint more clockwise on $W$ than the endpoint of $p$ supported by $b+1$: see Figure~\ref{fig:base step of alg induction}.
@@
 
-\end{proof}
-\end{comment}
+\note{end of the piece that was commented out in the file}
 
@@
   For every $v \in V_p$, Let $A_v \subset [n]$ be the set of vertices where $p$ contributes $v$ to $I_a$. Then $A_v$ is a non-empty cyclic interval.
+
+  \note{the above is the statement that was in this file, the below is the version of the statement from last july}
+
+Let $p$ be a propagator of an admissible WLD $W$ on $n$ vertices.
+Let $p = (i,j,k,l)$.
+Let $J_p^{(W)}(i)$ be the indices $m$ where $I_m(p)=i$ and likewise for $J_p^{(W)}(j)$, $J_p^{(W)}(k)$, and $J_p^{(W)}(l)$.
+Then $J_p^{(W)}(i)$, $J_p^{(W)}(j)$, $J_p^{(W)}(k)$, and $J_p^{(W)}(l)$ are each non-empty cyclic intervals of $\{1, \ldots, n\}$ which partition $\{1, \ldots, n\}$ and occur in the given cyclic order.
 \end{lem}
@@
 \begin{proof}
-Fix $p = (i, j)$. By symmetry, we need only consider the vertices $j$, $j+1$.
-
-Let $k_1 \ldots k_r$ be the set of propagators of the form $k_x = (i_{k_x}, j)$, with $i <_{j+1} k_1 <_{j+1} \ldots k_r <_{j+1} j$.
+    We will prove the result by induction on the number of propagators.
+If $W$ has one propagator then the result is immediate.
+Now suppose $W$ has more than one propagator.
+Since unsupported vertices have no effect on the Grassmann necklace algorithm, it suffices to prove the result for $W$ with no unsupported vertices.
+Then by Lemma~\ref{lem sian} $W$ has at least one of the three situations illustrated in figure~\ref{fig 3 cases}
+
+  \begin{figure}
+    \includegraphics[scale=0.8]{3cases}
+    \caption{Three cases for admissible WLDs with no unsupported vertices.
+The blue highlighted region cannot support other propagators.
+The green half-propagators illustrate where propagators may occur, but are not required to exist.}\label{fig 3 cases}
+  \end{figure}
+
+In each of the three cases, when we remove the propagator labelled $p$ we obtain a diagram which satisfies the statement of the theorem by the induction hypothesis, and contains a propagator $q$ with no other propagators inside it (although this region may or may not contain an unsupported vertex $b$).
+Call this diagram $V$ (figure \ref{fig V diagram}).
+
+\begin{figure}
+\includegraphics[scale=0.8]{Vdiagram}
+\caption{Diagram $V$ is $W$ with $p$ removed; there are no propagators inside $q$. Vertex $b$ is omitted if we are considering the right hand case.}
+\label{fig V diagram}
+\end{figure}
+
+We first describe $J_q^{(V)}(*)$: since there are no propagators inside $q$, we see from the diagram that
+\[b,c \in J^{(V)}_q(c) \text{ (if $b$ exists) and }  c+1 \in J^{(V)}_q(c+1).\]
+Note that $c+2 \not\in J^{(V)}_q(c+1)$ by Lemma~\ref{lem last vert}, so $J^{(V)}_q(c+1) = \{c+1\}$ and $c+2 \in J^{(V)}_q(a-1)$ by the induction hypothesis.
+Thus there exist vertices $d,e \in [c+2,a]$ with $d <e$, such that
+\[J^{(V)}_q(a-1) = [c+2,d-1], \quad J^{(V)}_q(a) = [d,e-1], \quad J^{(V)}_q(c) = [e,c], \quad J^{(V)}_q(c+1) = \{c+1\},\]
+and all intervals are non-empty.
+
+We now examine what happens in each of the three cases.
+
+%%%%%%%%%
+
+\textbf{Left and middle cases}: In both of these cases, $p$ has limited effect on the Grassmann necklace of $W$ due to the presence of the previously unsupported vertex $b$.
+We first calculate $I^{(W)}_w$ for a starting vertex ${w \in [n]\backslash \{b,c,c+1\}}$: if $w\in J_q^{(V)}(a-1)$ then
+    \[
+    I_w^{(W)}(r) =  \begin{cases}
+        a & \text{if } r=p \\
+        I_{w}^{(V)}(r) & \text{if } r\neq p
+      \end{cases} 
+    \]
+    while if $w\in J_q^{(V)}(a)$ or $w\in J_q^{(V)}(c)$ then
+    \[
+    I_w^{(W)}(r) =  \begin{cases}
+        b & \text{if } r=p \\
+        I_{w}^{(V)}(r) & \text{if } r\neq p
+      \end{cases} 
+      \]
+For the majority of the remaining vertices, we use the following observation: if $p$ is the first propagator to contribute to a Grassmann necklace term $I_w^{(W)}$, then the remainder of $I_w^{(W)}$ proceeds identically to the assignments of $I^{(V)}_{w+1}$.
+Thus in both cases, we have
+    \begin{align*}
+       I_b^{(W)}(r) & = \begin{cases}
+        b & \text{if } r=p\\
+        I_b^{(V)}(r) & \text{if } r\neq p
+       \end{cases}\\
+       I_c^{(W)}(r) & = \begin{cases}
+         c & \text{if } r=p \\
+         I_{c+1}^{(V)}(r) & \text{if } r\neq p
+       \end{cases}
+    \end{align*}
+The left and middle cases differ only at the starting vertex $c+1$. In the left hand case, we obtain
+\[
+       I_{c+1}^{(W)}(r)  = \begin{cases}
+         c+1 & \text{if } r=p\\
+         I_{c+2}^{(V)}(r) & \text{if } r\neq p
+       \end{cases}
+\]
+by the same arguments as above; thus the intervals $J^{(W)}_r(*)$ are still cyclic for all $r \neq p$, and
+\[J^{(W)}_p(a) = [c+2,d-1], \quad J^{(W)}_p(b) = [d,b], \quad J^{(W)}_p(c) = \{c\}, \quad J^{(W)}_p(c+1) = \{c+1\}\]
+also satisfies the statement of the theorem.
+
+In the middle case, if we start at $c+1$ we need to know whether any other propagators remain on edge $(a-1,a)$ when we reach vertex $a-1$.
+We already know that $J_q^{(V)}(c+1) = \{c+1\}$; in particular this means that $q$ contributes $a-1$ in $I_{c+2}^{(V)}$.
+However the construction of $I^{(V)}_{c+1}$ first associates $q$ to $c+1$ and then proceeds identically to $I^{(V)}_{c+2}$.
+In particular if $a-1$ was assigned in $I^{(V)}_{c+1}$, then it would not be available to assign to $q$ in $I^{(V)}_{c+2}$ as all other propagators supported at $a-1$ in $V$ come before $q$.
+    Therefore $p$ is the only unassigned propagator on edge $(a-1,a)$ when we reach $a-1$ in $W$, and
+    \[
+    I_{c+1}^{(W)}(r)  = \begin{cases}
+      a-1 & \text{if } r=p\\
+      I_{c+1}^{(V)}(r) & \text{if } r\neq p
+    \end{cases}
+    \]
+Assembling the intervals, we have
+\[J^{(W)}_p(a-1) = \{c+1\}, \quad J^{(W)}_p(a) = [c+2,d-1], \quad J^{(W)}_p(b) = [d,b], \quad J^{(W)}_p(c) = \{c\},\]
+as required.
+
+\textbf{Right hand case}: In this case there is no vertex $b$, and $p$ is supported on ${(c,c+1,c+2,c+3)}$ in $W$.
+For $w \in [n]\backslash\{c,c+1,c+2,c+3\}$: if $w\in J_q^{(V)}(a-1)$ or $w\in J_q^{(V)}(a)$ then
+    \[
+    I_w^{(W)}(r) =  \begin{cases}
+        c & \text{if } r=p \\
+        I_{w}^{(V)}(r) & \text{if } r\neq p
+      \end{cases} 
+    \]
+    while if $w\in J_q^{(V)}(c)$ then
+    \[
+    I_w^{(W)}(r) =  \begin{cases}
+        c+1 & \text{if } r=p \\
+        I_{w}^{(V)}(r) & \text{if } r\neq p
+      \end{cases} 
+    \]
+
+Finally, for the vertices in the support of $p$, we have
+
+            \begin{align*}
+      I_c^{(W)}(r) &= \begin{cases}
+        c & \text{if } r=q\\
+        c+1 & \text{if } r=p\\
+        I_c^{(V)}(r) & \text{if } r\neq p,q
+      \end{cases}\\
+      I_{c+1}^{(W)}(r) & = \begin{cases}
+        c+1 & \text{if } r=q \\
+        c+2 & \text{if } r=p \\
+        I_{c+3}^{(V)}(r) & \text{if } r\neq p,q
+      \end{cases}\\
+      I_{c+2}^{(W)}(r) & = \begin{cases}
+        c+2 & \text{if } r=p \\
+        I_{c+3}^{(V)}(r) & \text{if } r\neq p
+      \end{cases}\\
+      I_{c+3}^{(W)}(r) & = \begin{cases}
+        c+3 & \text{if } r=p \\
+        I_{c+4}^{(V)}(r) & \text{if } r\neq p
+      \end{cases}
+\end{align*}
+Note that $I_{c+2}^{(V)}(r) = I_{c+3}^{(V)}(r)$ for all propagators $r$ in $V$. Once again we can see that the $J_r^{(W)}(*)$ are cyclic for all $r$ in $V$, and
+\[J_p^{(W)}(c) = [c+4,e-1], \quad J_p^{(W)}(c+1) = [e,c], \quad J_p^{(W)}(c+2) = \{c+1,c+2\}, \quad J_p^{(W)}(c+3) = \{c+3\}.\]
+
+The result now follows by induction.
+
+%Fix $p = (i, j)$. By symmetry, we need only consider the vertices $j$, $j+1$.
+%
+%Let $k_1 \ldots k_r$ be the set of propagators of the form $k_x = (i_{k_x}, j)$, with $i <_{j+1} k_1 <_{j+1} \ldots k_r <_{j+1} j$.
 Write $k_{r+1}$ to be the counterclockwise most propagator with an end on the edge $j-1$, if it exists.
@@
 Otherwise, $P_j(p) = \emptyset$.
-
-Consider a protecting set $P_j(p) \subset \cP$ such that $k_1 \in P_j(p)$, if it exists.
+%
+%Consider a protecting set $P_j(p) \subset \cP$ such that $k_1 \in P_j(p)$, if it exists.
 Write it \bas P_j(p) = \{s_1 \ldots s_r, t_2, \ldots t_r\} \;.\eas Define $b_1 = i_{s_r}+1$.
@@
 In this case, we say $b_1 = j$.
-
-Now suppose $r$ is such that both $P_j(p)$ and $P_{j+1}(p)$ exists for some $a$.
+%
+%Now suppose $r$ is such that both $P_j(p)$ and $P_{j+1}(p)$ exists for some $a$.
 This time $k_2 \subset P_j(p)$.
@@
 If there is no $a$ such that both $P_j(p)$ and $P_{j+1}(p)$ do not hold, then  $p$ contributes $j+1$ for all $a \in [b_1 +1, j+1]$.
-
-Finally, for $r > 1$, and $j_{k_2}=j$,$a \in [b2+1, j+1]$, $p$ contributes $i$ to $I_a$.
+%
+%Finally, for $r > 1$, and $j_{k_2}=j$,$a \in [b2+1, j+1]$, $p$ contributes $i$ to $I_a$.
 Again, for all $a$ in this range, both sets $P_j(p)$ and $P_{j+1}(p)$ protect $p$ at $j$ and $j+1$ from $a$.
 Furthermore, by Corrollary \ref{protect cor}, there can be no protective sets of $i$ or $i+1$ in this range.
-
-By switching the roles of $i$ and $j$, we see that for every element of $V_p$, there is a non-empty cyclic interval such that $p$ contributes $v$ to all $I_{a}$ for in said interval.
+%
+%By switching the roles of $i$ and $j$, we see that for every element of $V_p$, there is a non-empty cyclic interval such that $p$ contributes $v$ to all $I_{a}$ for in said interval.
+
 \end{proof}

### 2018-11-21 General WLD combinatorics.tex
actually get rid of that commented out fragment

@@
 
-\note{This was commented out in the file: some (old?) version of the inductive argument?}
-such that $b+1 \in V_{p_1}$, with an endpoint more clockwise on $W$ than the endpoint of $p$ supported by $b+1$: see Figure~\ref{fig:base step of alg induction}.
-
-\begin{figure}
-\begin{tikzpicture}[rotate=15]
-\begin{scope}
-\drawWLD{12}{2}
-\drawprop{3}{2}{10}{2} % P
-% number vertices a,a+1,b,b+1 for prop P
-
-% clip these
-\drawprop{3}{-2}{12}{-2}
-\drawprop{2}{0}{12}{2}
-\drawprop{6}{0}{10}{-2} % p1
-
-\end{scope}
-\end{tikzpicture}
-\caption{Base step: if $P$ survives $n$ steps of the algorithm, there must be another propagator $p_1$ to its right on edge $(b,b+1)$.}
-\label{fig:base step of alg induction}
-\end{figure}
-
-The propagator $p_1$ forms the base step for the following induction:
-
-Suppose that $p_r$ is a propagator supported on $(i,i+1,m,m+1)$ and removed at step $m+1$ of the algorithm; we will show that there must also be a propagator $p_{r+1}$ supported on $(i',i'+1,m',m'+1)$ with $i \leq i'$ and $m \geq m'$, which is removed at step $m'+1$.
+%such that $b+1 \in V_{p_1}$, with an endpoint more clockwise on $W$ than the endpoint of $p$ supported by $b+1$: see Figure~\ref{fig:base step of alg induction}.
+%
+%\begin{figure}
+%\begin{tikzpicture}[rotate=15]
+%\begin{scope}
+%\drawWLD{12}{2}
+%\drawprop{3}{2}{10}{2} % P
+%% number vertices a,a+1,b,b+1 for prop P
+%
+%% clip these
+%\drawprop{3}{-2}{12}{-2}
+%\drawprop{2}{0}{12}{2}
+%\drawprop{6}{0}{10}{-2} % p1
+%
+%
+%\end{scope}
+%\end{tikzpicture}
+%\caption{Base step: if $P$ survives $n$ steps of the algorithm, there must be another propagator $p_1$ to its right on edge $(b,b+1)$.}
+%\label{fig:base step of alg induction}
+%\end{figure}
+%
+%The propagator $p_1$ forms the base step for the following induction:
+%
+%Suppose that $p_r$ is a propagator supported on $(i,i+1,m,m+1)$ and removed at step $m+1$ of the algorithm; we will show that there must also be a propagator $p_{r+1}$ supported on $(i',i'+1,m',m'+1)$ with $i \leq i'$ and $m \geq m'$, which is removed at step $m'+1$.
 Since we can't have both $i' = i$ and $m'=m$, $p_{r+1}$ bounds a region containing strictly fewer vertices than $p_r$.
-
-Notice that if we restrict our attention to the region bounded by $p_r$ and the edges of the diagram from $i$ to $m+1$, then propagators outside of this region can affect the algorithm only at vertices $i$, $i+1$.
+%
+%Notice that if we restrict our attention to the region bounded by $p_r$ and the edges of the diagram from $i$ to $m+1$, then propagators outside of this region can affect the algorithm only at vertices $i$, $i+1$.
 (The starting vertex 1 lies outside this region, by assumption.)
-
-Given a propagator $p_r$ supported on $(i,i+1,m,m+1)$ and removed at step $m+1$, we must also have a propagator $q$ to its right which is removed at step $m$ (``protecting'' $p_r$ at step $m$).
+%
+%Given a propagator $p_r$ supported on $(i,i+1,m,m+1)$ and removed at step $m+1$, we must also have a propagator $q$ to its right which is removed at step $m$ (``protecting'' $p_r$ at step $m$).
 This splits into two cases:
-
-\textbf{Case I}: If $q$ is supported on $(k,k+1,m-1,m)$ for some $k \geq i$, then $p_{r+1}:=q$  satisfies the conditions of the induction step.
-
-\textbf{Case II}: Suppose $q$ is supported on $(k,k+1,m,m+1)$ for some $k$; since the diagram is admissible, we have $k > i$.
+%
+%\textbf{Case I}: If $q$ is supported on $(k,k+1,m-1,m)$ for some $k \geq i$, then $p_{r+1}:=q$  satisfies the conditions of the induction step.
+%
+%\textbf{Case II}: Suppose $q$ is supported on $(k,k+1,m,m+1)$ for some $k$; since the diagram is admissible, we have $k > i$.
 In particular, anything that happens at vertex $k+1$ is unaffected by propagators outside the region bounded by $p_r$, since $k+1 > i+1$.
@@
 The admissibility of $W$ implies that $q'$ is supported on $(j,j+1,k,k+1)$ for some $j \geq i$, and we can take $p_{r+1}:=q'$.
-
-\begin{figure}
-\begin{tabular}{ccc}
-\begin{tikzpicture}[rotate=15]
-\begin{scope}
-\drawWLD{12}{2}
-\drawprop{3}{0}{10}{0} % p_r
-% number vertices i,i+1,m,m+1
-
-%clip these
-\drawprop{6}{0}{9}{0} % q
-\end{scope}
-\end{tikzpicture}
-
-& \qquad \qquad &
-\begin{tikzpicture}[rotate=15]
-\begin{scope}
-\drawWLD{12}{2}
-\drawprop{3}{0}{10}{2} % p_r
-% number vertices i, i+1, m, m+1
-
-\drawprop{7}{2}{10}{-2} %q
-% vertices k,k+1, m,m+1
-
-% clip this one
-\drawprop{4}{0}{7}{-2} % q'
-% vertices j,j+1,k, k+1
-
-\end{scope}
-\end{tikzpicture}
-\\
-Case I & & Case II
-\end{tabular}
-
-\caption{Inductive step: if propagator $q$ is removed at step $m$, then it lies on either edge $(m-1,m)$ (Case I) or $(m,m+1)$ (Case II).}
-\label{fig: cases for inductive step, algorithm}
-\end{figure}
-
-By induction, we will eventually find a propagator on a region with 3 or fewer vertices, which is inadmissible.
-
-\note{end of the piece that was commented out in the file}
+%
+%\begin{figure}
+%\begin{tabular}{ccc}
+%\begin{tikzpicture}[rotate=15]
+%\begin{scope}
+%\drawWLD{12}{2}
+%\drawprop{3}{0}{10}{0} % p_r
+%% number vertices i,i+1,m,m+1
+%
+%%clip these
+%\drawprop{6}{0}{9}{0} % q
+%\end{scope}
+%\end{tikzpicture}
+%
+%& \qquad \qquad &
+%\begin{tikzpicture}[rotate=15]
+%\begin{scope}
+%\drawWLD{12}{2}
+%\drawprop{3}{0}{10}{2} % p_r
+%% number vertices i, i+1, m, m+1
+%
+%\drawprop{7}{2}{10}{-2} %q
+%% vertices k,k+1, m,m+1
+%
+%% clip this one
+%\drawprop{4}{0}{7}{-2} % q'
+%% vertices j,j+1,k, k+1
+%
+%\end{scope}
+%\end{tikzpicture}
+%\\
+%Case I & & Case II
+%\end{tabular}
+%
+%\caption{Inductive step: if propagator $q$ is removed at step $m$, then it lies on either edge $(m-1,m)$ (Case I) or $(m,m+1)$ (Case II).}
+%\label{fig: cases for inductive step, algorithm}
+%\end{figure}
+%
+%By induction, we will eventually find a propagator on a region with 3 or fewer v%ertices, which is inadmissible.
 

### 2018-11-23 General WLD combinatorics.tex

--- 2018-11-21 General WLD combinatorics.tex
@@
 \item If $C \subseteq [n]$ is a cycle, then $\rk(C) = |Prop(C)|$.
+\item If $[n]$ can be partitioned into at least two non-empty sets, each of which support different sets of propagators, \bas [n] = \cup_i V(P_i) \quad \textrm{s.t.} \quad \cup P_i = \cP; \quad  P_i \cap P_j = \emptyset \;, \eas the the matroid $M(W)$ is seperable, \bas M(W) = \bigoplus_i M(P_i, V(P_i)) \;.\eas
 \end{enumerate}
@@
 \begin{proof}
-The first part of (1) is \cite[Equation (9)]{wilsonloop} and surrounding discussion, and the second part is standard matroid theory. (2) is \cite[Lemma 3.27]{wilsonloop}.
+The first part of (1) is \cite[Equation (9)]{wilsonloop} and surrounding discussion, and the second part is standard matroid theory.
+(2) is \cite[Lemma 3.27]{wilsonloop}.
+(3) is also in \cite[Lemma FIND]{wilsonloop}.
 \end{proof}
@@
 \item $C = F(\Prop (C))$, i.e. $C$ is a propagator flat.
-\item $F \setminus C$ is an independent \st{set.
-Further, if $W$ does not contain any vertices of rank $0$, i.e.
-all vertices support at least $1$ propagator, then $F \setminus C$ is an independent} flat.
-\sanote{$F$ and $C$ both contain all vertices of rank $0$ by definition}
+\item $F \setminus C$ is an independent  flat.  
 \end{enumerate}
@@
 Let $v \in C$.
-Clearly $\Prop(v) \subseteq \Prop(C)$, and so by Lemma \ref{lem properties of prop flats} we have $F(\Prop(v)) \subseteq F(\Prop(C))$.
+Clearly $\Prop(v) \subseteq \Prop(C)$, and so by Lemma \ref{lem properties of prop flatfs} we have $F(\Prop(v)) \subseteq F(\Prop(C))$.
 Since $v \in F(\Prop(v))$ by the definition of propagator flat, we have $v \in F(\Prop(C))$ as required.
@@
 
-For part (2), first note that $F \setminus C$ is automatically independent as it contains no circuits. Now suppose that all vertices in $W$ have rank $\geq 1$. \sanote{can get rid of?}
+For part (2), first note that $F \setminus C$ is automatically independent as it contains no circuits.
 
@@
 \begin{lem} \label{maxexactcomplementrank}
-Let $W = (\cP, n)$ be a Wilson loop diagram, and $P \subsetneq \cP$. Then: \note{should hold if $P = \cP$.}
-\begin{enumerate}
+Let $W = (\cP, n)$ be a Wilson loop diagram, and $P \subseteq \cP$. Then: \begin{enumerate}
 \item If $(P,V(P))$ is an exact subdiagram in $W$, then $\rk(F(P^c)) = |P^c|$.
@@
 
-{\color{violet} Note that by definition, since $F(P^c)$ has at $|P^c|$ propagators in it, this is an upper bound on the rank. However, showing equality on the first part is harder.}
+Note that by definition, since $F(P^c)$ has at $|P^c|$ propagators in it, this is an upper bound on the rank. However, showing equality on the first part is harder.
 
@@
 Note that $C$ must be non-empty since $F(P^c)$ is dependent.
-{\color{violet}We proceed by showing that $S$ must be empty, forcing $F(P^c)$ to be a cyclic flat.} \sanote{Does this fix confusion later?}
+We proceed by showing that $S$ must be empty, forcing $F(P^c)$ to be a cyclic flat.
 
 Since $C = F(\Prop(C))$ by Lemma \ref{lem decompose flat}, define $Q := \Prop(C)^c$ so that we may write $C = F(Q^c) = V(Q)^c$.
-{\color{violet}Note that since $C \subseteq F(P^c)$, $P \subseteq Q$.
-}Furthermore, we have
+Note that since $C \subseteq F(P^c)$, $P \subseteq Q$.
+Furthermore, we have
 \begin{equation}\rk(S) = |S| \leq \rk(F(P^c)) - \rk(C)  \leq |P^c| - \rk(C) \;, \label{increasingrank}\end{equation}
@@
 Combining this with \eqref{Qsizebound} gives $|V(Q)| - 3 \leq |Q|$.
-That is, either $W$ was not admissible, \hlfix{or $(P,V(P))$ was not a maximal exact subdiagram.}{This only follows if $P \subseteq Q$, which I can't see?
-We don't ever seem to use the fact that $S$ is empty/nonempty} In other words, $S$ cannot be non-empty, proving that $F(P^c)$ is a cyclic flat, and therefore of maximal rank.
-
-{\color{violet}REPLACE BELOW WITH: Let $P$ be a maximal exact subdiagram as above, and let $(R, V(R))$ be an exact subdiagram that is not maximal. That is, $R \subsetneq P$. }
-
-Let $(Q, V(Q))$ be an exact subdiagram that is not maximal, with \hlfix{$Q \subset P$ defining the maximal exact subdiagram above}{If I've understood this right, we would need to show that any exact subdiagram appears as $\Prop(C)^c$ for some maximal exact $P$ first} .
-\sanote{why?
-I don't understand your confusion}
-
-{\color{violet}POSSIBLY REPLACE BELOW WITH: Since $R \subset P$, $V(P) = V(R) \sqcup S$.
+That is, either $W$ was not admissible, or $(P,V(P))$ was not a maximal exact subdiagram.
+In other words, $S$ cannot be non-empty, proving that $F(P^c)$ is a cyclic flat, and therefore of maximal rank.
+
+Let $P$ be a maximal exact subdiagram as above, and let $(R, V(R))$ be an exact subdiagram that is not maximal. That is, $R \subsetneq P$.
+
+Since $R \subset P$, $V(P) = V(R) \sqcup S$.
 Since $P$ and $R$ both define exact subdiagrams, we may write $|V(P)| = |V(R)| + |P \setminus R|$, where $S$ is a vertex set of size $|P \setminus R|$ with $(P \setminus R \subset \Prop(S)$.
 Since $\rk V(P) =  \rk V(R) + |P \setminus R|$, $S$ is independent.
-Taking the complements, we may write \bas F(R^c ) = F(P^c) \sqcup S \;.\eas Since $S$ is an independent set of vertices of the correct size supporting the appropriate propagators, this gives $ \rk F(R^c ) = |R^c|$.}
-
-Using the fact that $P$ and $Q$ are both exact diagrams, we have $|V(P)| = |V(Q)| + |P \setminus Q|$.
-Then $V(Q)^c = F(P^c) \cup S$, where $S$ is an independent set of size $|P \setminus Q|$ and with $(P \setminus Q) \subset \Prop (S)$.
-Therefore, \hlfix{$\rk (F(Q^c)) = |Q^c|$.}{I'm lost here.} \sanote{better if I fix typo?}
+Taking the complements, we may write \bas F(R^c ) = F(P^c) \sqcup S \;.\eas Since $S$ is an independent set of vertices of the correct size supporting the appropriate propagators, this gives $ \rk F(R^c ) = |R^c|$.
+
 \end{proof}
@@
 
-In \cite{wilsonloops}, the authors show that all exact Wilson loop diagrams correspond to positroids.
-That is, they correspond to matroids that can be represented by elements of the positive Grassmannians $\Gr(|\cP|, |V|)$.\todo{Check: positroids or totally positive?
-Why specify exactness?}
+In \cite{wilsonloops}, the authors show that all violet Wilson loop diagrams correspond to positroids.
+That is, they correspond to matroids that can be represented by elements of the positive Grassmannians $\Gr(|\cP|, |V|)$.
+Any positroid of rank $k$ on $n$ elements defines a subspace of the positive Grassmannians $\Gr(k, n)$, namely the points which represent it.
+These subspaces give a CW structure on $\Gr(k,n)$, with each positroid defining a cell.
 
 \begin{dfn}
-Given a Wilson loop diagram $W$, define the positroid cell associated to a Wilson loop diagram, $\Sigma(W)$, to be the cell in the CW complex on $\Gr(|\cP|, |V|)$ defined by the \hlfix{realizations}{we haven't specified what this means}  of $W$ that lie in $\Gr(|\cP|, |V|)$.
+Given a Wilson loop diagram $W = (\cP, [n])$, define the positroid cell associated to a Wilson loop diagram, $\Sigma(W)$, to be the cell in the CW complex on $\Gr(|\cP|, n)$ defined by the positroid $M(W)$.
 \end{dfn}
@@
 
-%\note{I don't think rank of a vertex (in the sense of number of propagators supported on it) was ever used, so I removed the definition}
+\note{I don't think rank of a vertex (in the sense of number of propagators supported on it) was ever used, so I removed the definition}
 %\note{rank probably isn't a good word; do we have a better one?}
@@
 \begin{dfn}\note{right now this doesn't depend on the order of $i$ and $j$, but that might matter later on?}
-Let $p$ be a propagator supported on $(i,j)$.  Define the \textit{length} of $p$ to be 
+Let $p$ be a propagator supported on the vertices $(i,i+1,j,j+1)$.  Define the \textit{length} of $p$ to be 
 \[\ell(p) = min\big\{|[i+1,j]|,|[j+1,i]|\big\}.\]
@@
 \item If every vertex in $W$ supports at least one propagator, then $W$ admits at least one propagator of length 2.
-\item If $p = (i,i+3)$ is a propagator of length 3, then the middle vertex $i+2$ supports at most one propagator.
+\item If $p = (i,i+1,i+3,i+4)$ is a propagator of length 3, then the middle vertex $i+2$ supports at most one propagator.
 \end{itemize}
 \end{rmk}
+
+\note{Are the next few definitions used outside the proof of Lemma~\ref{lem sian 1}?  If not, then perhaps they could go inside the proof so as not to clutter the document with temporary definitions?}
+\begin{dfn}
+Define the restriction of $W$ to a region $[i,j]$ to be the subdiagram obtained by forgetting all propagators not wholly supported on vertices in the cyclic interval $[i,j]$.
+Denote this diagram by $W_{[i,j]}$.
+\end{dfn}
+\note{I think there's an issue here about what we mean by subdiagram; in def 1.5 we say a subdiagram is of the form $(P, V(P))$ which is certainly not what we want here; in fact I think we want the subdiagram where the vertex set is unchanged and only the propagator set is restricted (the other possibility would be to restrict the vertex set to $[i, j]$, but then the lengths of propagators can change and in the way we want to use it (see paragraph below) $p$ will become very non-admissible).
+I think def 1.5 should be removed and we should say that for a WLD $(P, V)$ subdiagrams are any $(P', V')$ with $P'\subseteq P$, $V'\subseteq V$ and all supporting vertices of elements of $P'$ in $V'$; this seems to me to be the natural notion of subobject.}
+
+If $p$ is a propagator supported on $(i,i+1,j,j+1)$, then we can consider two obvious restrictions of $D$, namely $D_{[i,j+1]}$ and $D_{[j,i+1]}$.
+Clearly all other propagators $q\neq p$ appear in exactly one of these subdiagrams, while $p$ appears in both.
+In this case, we will say that $p$ \textit{bounds the regions} $[i,j+1]$ and $[j,i+1]$; the ordering of the start and end points allow us to identify one or the other region unambiguously.
 
@@
       \begin{enumerate}
-        \item There is a propagator of length $2$, say $(i, i+2)$ such that no other propagators ends on either the edge $i$ or the edge $i+2)$.\label{item lonely 2}
-        \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator ends between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
-        \item There exists a propagator of length 4 with only a propagator of length 2 inside it.\label{item 4 and 2}
+        \item There is a propagator of length $2$, say $(i, i+1, i+2, i+3)$ such that no other propagators ends on either the edge $(i, i+1)$ or the edge $(i+2, i+3)$.\label{item lonely 2}
+        \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+1, i+2, i+3)$, the second is $(j, j+1, j+2, j+3)$, no other propagator ends between $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
+        \item There exists a propagator of length exactly 4 with only a propagator of length 2 inside it.\label{item 4 and 2}
       \end{enumerate}
@@
 \begin{proof}
-  Suppose first that $W$ has a propagator of length $3$, $p=(i, i+3)$.
+  Suppose first that $W$ has a propagator of length $3$, $p=(i, i+1, i+3, i+4)$.
 By Remark~\ref{rem:props of length 2 and 3} along with the fact that every vertex of $W$ supports at least one propagator, we have that $i+2$ supports exactly one propagator and this propagator must have length 2 by noncrossingness.
@@
 %\end{equation}
-
-We need a bit of notation:
-Define the restriction of $W$ to a region $[i,j]$ to be the subdiagram obtained by forgetting all propagators not wholly supported on vertices in the cyclic interval $[i,j]$; the vertex set remains the same as in $W$.
-Denote this diagram by $W_{[i,j]}$.
-
-Note that if $p$ is a propagator supported on $(i,j)$, then we can consider two obvious restrictions of $W$, namely $W_{[i,j+1]}$ and $W_{[j,i+1]}$.
-Clearly all other propagators $q\neq p$ appear in exactly one of these subdiagrams, while $p$ appears in both.
-In this case, we will say that $p$ \textit{bounds the regions} $[i,j+1]$ and $[j,i+1]$; the ordering of the start and end points allow us to identify one or the other region unambiguously.
-
-With these observations in mind we can return to the proof.
 
@@
 
-Start by choosing a propagator $p_1$ of length 2 in $W$ (which exists by Remark~\ref{rem:props of length 2 and 3}), and write $(j_1,j_1+2)$ for its support.
+Start by choosing a propagator $p_1$ of length 2 in $W$ (which exists by Remark~\ref{rem:props of length 2 and 3}), and write $(j_1,j_1+1,j_1+2,j_1+3)$ for its support.
 If it is part of one of the configurations we are looking for then we are done,
 %a configuration \eqref{eq:2 prop config} we are done,
-so suppose otherwise: since $p_1$ is not in configuration \ref{item lonely 2} then there must be a second propagator starting either on edge $j_1)$ or $j_1+2$.
+so suppose otherwise: since $p_1$ is not in configuration \ref{item lonely 2} then there must be a second propagator starting either on edge $(j_1, j_1+1)$ or $(j_1+2, j_1+3)$.
 Flipping the diagram if necessary, assume the former.
-Since $p_1$ is not in configuration \ref{item pair of 2s} and every vertex is supported then there must exist a propagator $q_1$ of length $\geq 4$ with one end on edge $j_1$ or on edge $j_1-1$ or on edge $j_1-2$.
+Since $p_1$ is not in configuration \ref{item pair of 2s} and every vertex is supported then there must exist a propagator $q_1$ of length $\geq 4$ with one end on edge $(j_1,j_1+1)$ or on edge $(j_1-1, j_1)$ or on edge $(j_1-2, j_1-1)$.
 This bounds a region $[i_1,k_1]$ (where $k_1 \in \{j_1-1, j_1, j_1+1\}$) which does not contain $p_1$.
 
-Now suppose $q_{r}$ exists by the induction hypothesis and bounds a region $[i_r,k_r]$ not containing any $p_i$ for $i\leq r$.
+Now suppose $q_{r}$ exists by the induction hypothesis and bounds a region $[i_r,k_r]$.
 Consider the restricted diagram $W_r:=W_{[i_r,k_r]}$; by the original hypotheses on $W$ every vertex $l \in [i_r+2,k_r-2]$ (which is a non-empty interval since $\ell(q_r) \geq 4$) must have support $\geq 1$, while the same is true for $l \in \{i_r,i_r+1,k_r-1,k_r\}$ because of $q_r$.
@@
 $W_r$ has no propagators of length $3$ since $W$ has none.
-Let $p_{r+1}$ be a propagator of length 2 in $W_r$; if it forms part of configuration \ref{item lonely 2}, \ref{item pair of 2s}, or \ref{item 4 and 2}
+\note{now the question really is important about what length means in the restricted diagram; as written the restricted diagram has the same vertex set so length is unchanged.}   Let $p_{r+1}$ be a propagator of length 2 in $W_r$; if it forms part of configuration \ref{item lonely 2}, \ref{item pair of 2s}, or \ref{item 4 and 2}
 %the configuration \eqref{eq:2 prop config}
@@
 
-Note we may replace $q_r$ by any other propagator of length $\geq 4$ in $W_r$ which contains $p_{r+1}$ and such a new $q_r$ still satisfies all the hypotheses, and so, without loss of generality we may assume that $q_r$ has minimal length among propagators of length $\geq 4$ which contain $p_{r+1}$.
+Note we may replace $q_r$ by any other propagator of length $\geq 4$ in $W_r$ which contains $p_{r+1}$ while still satisfying all the hypotheses, and so, without loss of generality we may assume that $q_r$ has minimal length among propagators of length $\geq 4$ which contain $p_{r+1}$.
 
 There are two cases to consider.
-The first case is that $p_{r+1}$ has one end before $i_r+3$ and the other after $k_r-3$.
-Then since $p_{r+1}$ has length 2, it must be that $[i_r+3,k_r-3]$ is at most a single edge, and so $q_r$ has length $\leq 6$.
-The only propagators inside $q_r$ that do not also contain $p_{r+1}$ must have both ends in $[i_r, i_r+3]$ or both ends in $[k_r-3, k_r]$ and hence be of length 2.
+The first case is that neither end of $p_{r+1}$ lies on an edge contained in the possibly empty interval $[i_r+3,k_r-3]$, then since $p_{r+1}$ has length 2, it must be that $[i_r+3,k_r-3]$ is at most a single edge, and so $q_r$ has length $\leq 6$.
+Since $p_{r+1}$ has one end before $i_r+3$ and the other after $k_r-3$, the only propagators inside $q_r$ that do not also contain $p_{r+1}$ must have both ends in $[i_r, i_r+3]$ or both ends in $[k_r-3, k_r]$ and hence be of length 2.
 Therefore, if $q_r$ contains a propagator $t$ of length $\leq 4$, this propagator must also contain $p_{r+1}$ which is impossible my minimality.
@@
 
-The second case is that either at least one endpoint of $p_{r+1}$ lies on an edge contained in the interval $[i_r+3,k_r-3]$, or both ends lie in $[i_r, i_r+3]$ or $[k_r-3, k_r]$; these situations all behave similarly.
-Up to symmetry we can write $p_{r+1} = (j_{r+1}, j_{r+1}+2)$ where either the edge $j_{r+1}+2$ is contained in $[i_r+3, k_r-3]$ or $j_{r+1}+2 = i_r+2$.
-Since $p_{r+1}$ is not part of configuration \ref{item pair of 2s} and vertex $j_{r+1}+4$ is supported (and not by $q_r$ since $j_{r+1}+4 \leq k_r-2$ in both situations), there is some propagator $t$ with one end in $[j_{r+1}+3, j_{r+1}+5]$ and length $\geq 4$.
+The second case is that at least one endpoint of $p_{r+1}$ lies on an edge contained in the interval $[i_r+3,k_r-3]$.
+Up to symmetry we can write $p_{r+1} = (j_{r+1}, j_{r+1}+1, j_{r+1}+2, j_{r+1}+3)$ where $(j_{r+1}+2, j_{r+1}+3)$ is contained in $[i_r+3, k_r-3]$.
+Since $p_{r+1}$ is not part of configuration \ref{item pair of 2s} and vertex $j_{r+1}+4$ is supported (and not by $q_r$ since $j_{r+1}+4 \leq k_r-2$), there is some propagator $t$ with one end in $[j_{r+1}+2, j_{r+1}+4]$ and length $\geq 4$.
 By noncrossingness $t$ is contained in $q_{r}$.

### 2018-11-24 General WLD combinatorics.tex
put my changes back

--- 2018-11-21 General WLD combinatorics.tex
@@
       \begin{enumerate}
-        \item There is a propagator of length $2$, say $(i, i+2)$ such that no other propagators ends on either the edge $i$ or the edge $i+2)$.\label{item lonely 2}
+        \item There is a propagator of length $2$, say $(i, i+2)$ such that no other propagators ends on either the edge $i$ or the edge $i+2$.\label{item lonely 2}
         \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator ends between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
@@
 Thus we have $|S_{i+1}|$ propagators supported on $|S_{i+1}|$ vertices contradicting admissibility.
-  \item Increment $i$ and go to \label{itemp loop step}
+  \item Increment $i$ and go to \ref{item loop step}
 \end{enumerate}

### 2018-11-24 General WLD combinatorics.tex
small wording changes in lemma 2.11

@@
   \item $S_0={p}$ and $T_0$ is the support of $p$ except for $n$.  Set $i=0$.
-  \item Let $R$ be the set of propagators which are assigned to a vertex in $T_i$ by $f$. Let $S_{i+1}= S_i \cup R$.  Let $T_{i+1} = T_i \sup (\text{supp}(R) - \{n\})$.\label{item loop step}
-  \item If there is a vertex $v_{i+1}$ in $T_{i+1}$ which has not yet been assigned then by construction there is a propagator $q_{i+1} \in S_{i+1}-S_i$ which can be assigned to $v_{i+1}$.
+  \item Let $R$ be the set of propagators which are assigned to a vertex in $T_i$ by $f$. Let $S_{i+1}= S_i \cup R$.  Let $T_{i+1} = T_i \cup (\text{supp}(R) - \{n\})$.\label{item loop step}
+  \item If there is a vertex $v_{i+1}$ in $T_{i+1}$ which has not been assigned by $f$ then by construction there is a propagator $q_{i+1} \in S_{i+1}-S_i$ which can be assigned to $v_{i+1}$.
 Do so, removing $q_{i+1}$'s old assignment.

### 2018-11-24 General WLD combinatorics.tex
in the middle of changing over the argument

@@
 Let $p$ be a propagator of an admissible WLD $W$ on $n$ vertices.
-Let $p = (i,j,k,l)$.
-Let $J_p^{(W)}(i)$ be the indices $m$ where $I_m(p)=i$ and likewise for $J_p^{(W)}(j)$, $J_p^{(W)}(k)$, and $J_p^{(W)}(l)$.
-Then $J_p^{(W)}(i)$, $J_p^{(W)}(j)$, $J_p^{(W)}(k)$, and $J_p^{(W)}(l)$ are each non-empty cyclic intervals of $\{1, \ldots, n\}$ which partition $\{1, \ldots, n\}$ and occur in the given cyclic order.
+Let $p = (i,j)$.
+For $l\in \{i, i+1, j, j+1\}$, let $J_p^{(W)}(l)$ be the indices $m$ where $I_m(p)=l$.
+Then $J_p^{(W)}(i)$, $J_p^{(W)}(i+1)$, $J_p^{(W)}(j)$, and $J_p^{(W)}(j+1)$ are each non-empty cyclic intervals of $\{1, \ldots, n\}$ which partition $\{1, \ldots, n\}$ and occur in the given cyclic order.
 \end{lem}
@@
 Since unsupported vertices have no effect on the Grassmann necklace algorithm, it suffices to prove the result for $W$ with no unsupported vertices.
-Then by Lemma~\ref{lem sian} $W$ has at least one of the three situations illustrated in figure~\ref{fig 3 cases}
+Then by Lemma~\ref{lem sian} $W$ has at least one of the four situations illustrated in figure~\ref{fig 3 cases}
 
@@
     \includegraphics[scale=0.8]{3cases}
-    \caption{Three cases for admissible WLDs with no unsupported vertices.
-The blue highlighted region cannot support other propagators.
-The green half-propagators illustrate where propagators may occur, but are not required to exist.}\label{fig 3 cases}
+    \caption{Four cases for admissible WLDs with no unsupported vertices.
+The green half-propagators illustrate where propagators may occur, but are not required to exist; no other regions illustrated may support additional propagators.}\label{fig 3 cases}
   \end{figure}
 
-In each of the three cases, when we remove the propagator labelled $p$ we obtain a diagram which satisfies the statement of the theorem by the induction hypothesis, and contains a propagator $q$ with no other propagators inside it (although this region may or may not contain an unsupported vertex $b$).
+In each of the four cases, when we remove the propagator labelled $p$ we obtain a diagram which satisfies the statement of the theorem by the induction hypothesis, and contains a propagator $q = (i,j)$ with no other propagators inside it (although this region may or may not contain unsupported vertices which we will call $l, l+1, \ldots$ as necessary).
 Call this diagram $V$ (figure \ref{fig V diagram}).
@@
 \includegraphics[scale=0.8]{Vdiagram}
-\caption{Diagram $V$ is $W$ with $p$ removed; there are no propagators inside $q$. Vertex $b$ is omitted if we are considering the right hand case.}
+\caption{Diagram $V$ is $W$ with $p$ removed; there are no propagators inside $q = (i,j)$, though there may be up to 4 unsupported vertices labelled $l, l+1, \ldots$.}
 \label{fig V diagram}
@@
 
+Consider the fourth case of Figure~\ref{fig 3 cases} first, as it is the easiest.
+In this case the support of $p$ is unsupported in $V$ so for every propagator $r$ in $V$ (including $q$) $J_r^{(V)} = J_r^{(W)}$.
+Additionally, $J_p^{(W)}(l+t) = l+a$ for $a\in\{1,2,3\}$ and $J_p^{(W)}(l) = [n] \backslash \{l+1, l+2, l+3\}$ which proves the result in this case.
+
+Now we proceed to consider the first three cases of Figure~\ref{fig 3 cases}.
 We first describe $J_q^{(V)}(*)$: since there are no propagators inside $q$, we see from the diagram that
-\[b,c \in J^{(V)}_q(c) \text{ (if $b$ exists) and }  c+1 \in J^{(V)}_q(c+1).\]
-Note that $c+2 \not\in J^{(V)}_q(c+1)$ by Lemma~\ref{lem last vert}, so $J^{(V)}_q(c+1) = \{c+1\}$ and $c+2 \in J^{(V)}_q(a-1)$ by the induction hypothesis.
-Thus there exist vertices $d,e \in [c+2,a]$ with $d <e$, such that
-\[J^{(V)}_q(a-1) = [c+2,d-1], \quad J^{(V)}_q(a) = [d,e-1], \quad J^{(V)}_q(c) = [e,c], \quad J^{(V)}_q(c+1) = \{c+1\},\]
+\[l, l+1, \ldots ,j \in J^{(V)}_q(j) \text{ (if $l$ exists) and }  j+1 \in J^{(V)}_q(j+1).\]
+Note that $j+2 \not\in J^{(V)}_q(j+1)$ by Lemma~\ref{lem last vert}, so $J^{(V)}_q(j+1) = \{j+1\}$ and $j+2 \in J^{(V)}_q(i)$ by the induction hypothesis.
+Thus there exist vertices $d,e \in [j+2,i+1]$ with $d <e$, such that
+\[J^{(V)}_q(i) = [j+2,d-1], \quad J^{(V)}_q(i+1) = [d,e-1], \quad J^{(V)}_q(j) = [e,j], \quad J^{(V)}_q(j+1) = \{j+1\},\]
 and all intervals are non-empty.
@@
 
-\textbf{Left and middle cases}: In both of these cases, $p$ has limited effect on the Grassmann necklace of $W$ due to the presence of the previously unsupported vertex $b$.
-We first calculate $I^{(W)}_w$ for a starting vertex ${w \in [n]\backslash \{b,c,c+1\}}$: if $w\in J_q^{(V)}(a-1)$ then
+\textbf{Left two cases}: In both of these cases, $p$ has limited effect on the Grassmann necklace of $W$ due to the presence of at least one previously unsupported vertex $l$.
+Let $1\leq a\leq 3$ be the number of unsupported vertices inside $q$ in $V$; so these vertices are $l, \ldots, l+a-1$.
+Write $p=(m,m+2)$ where $m\in \{i, i+1, l\}$.
+Note that $l, \ldota, l+a-1$ are all in the support of $p$.
+We first calculate $I^{(W)}_w$ for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$: if $w\in J_q^{(V)}(i)$ then
     \[
     I_w^{(W)}(r) =  \begin{cases}
-        a & \text{if } r=p \\
+        \max\{i+1, m\} & \text{if } r=p \\
         I_{w}^{(V)}(r) & \text{if } r\neq p
@@
     \]
-    while if $w\in J_q^{(V)}(a)$ or $w\in J_q^{(V)}(c)$ then
+    while if $w\in J_q^{(V)}(i+1)$ or $w\in J_q^{(V)}(j)$ then
     \[
     I_w^{(W)}(r) =  \begin{cases}
-        b & \text{if } r=p \\
+        l & \text{if } r=p \\
         I_{w}^{(V)}(r) & \text{if } r\neq p
@@
 For the majority of the remaining vertices, we use the following observation: if $p$ is the first propagator to contribute to a Grassmann necklace term $I_w^{(W)}$, then the remainder of $I_w^{(W)}$ proceeds identically to the assignments of $I^{(V)}_{w+1}$.
-Thus in both cases, we have
-    \begin{align*}
-       I_b^{(W)}(r) & = \begin{cases}
-        b & \text{if } r=p\\
-        I_b^{(V)}(r) & \text{if } r\neq p
-       \end{cases}\\
-       I_c^{(W)}(r) & = \begin{cases}
-         c & \text{if } r=p \\
-         I_{c+1}^{(V)}(r) & \text{if } r\neq p
-       \end{cases}
-    \end{align*}
-The left and middle cases differ only at the starting vertex $c+1$. In the left hand case, we obtain
+Thus in both cases, we have for any $0\leq b <a$
     \[
-       I_{c+1}^{(W)}(r)  = \begin{cases}
-         c+1 & \text{if } r=p\\
-         I_{c+2}^{(V)}(r) & \text{if } r\neq p
+    I_{l+b}^{(W)}(r) & = \begin{cases}
+      l+b & \text{if } r=p\\
+      I_{l+b}^{(V)}(r) & \text{if } r\neq p
     \end{cases}
     \]
-by the same arguments as above; thus the intervals $J^{(W)}_r(*)$ are still cyclic for all $r \neq p$, and
+    If $j$ is in the support of $p$ which occurs in all cases except the second case with two vertices in the right hand region then
+     \[
+       I_j^{(W)}(r) & = \begin{cases}
+         j & \text{if } r=p \text{ and $j$ is in the suport of $p$} \\
+         I_{j+1}^{(V)}(r) & \text{if } r\neq p
+       \end{cases}
+       \]
+       If $j$ is not in the support of $p$,  then we must be in the second case with two vertices in the right hand region.
+Then if we start at $j$ we need to know whether propagators other than $p$ will remain around $i$ and $i+1$ when we reach vertex $i$ in the Grassmann necklace algorithm.
+****this part needs work, and it affects the rest potentially too, since $p$ is not taken first***
+
+For these two cases, it remains to consider the starting vertex $j+1$. If $j+1$ is in the support of $p$ then we can argue as above to get
+\[
+       I_{j+1}^{(W)}(r)  = \begin{cases}
+         j+1 & \text{if } r=p \text{ and $j+1$ is in the support of $p$}\\
+         I_{j+2}^{(V)}(r) & \text{if } r\neq p
+       \end{cases}
+\]
+by the same arguments as above.  Thus the intervals $J^{(W)}_r(*)$ are still cyclic for all $r \neq p$, and
 \[J^{(W)}_p(a) = [c+2,d-1], \quad J^{(W)}_p(b) = [d,b], \quad J^{(W)}_p(c) = \{c\}, \quad J^{(W)}_p(c+1) = \{c+1\}\]
@@
 
-In the middle case, if we start at $c+1$ we need to know whether any other propagators remain on edge $(a-1,a)$ when we reach vertex $a-1$.
+In the ***This also needs adjusting and I haven't started it yet, nor what comes after*** middle case, if we start at $c+1$ we need to know whether any other propagators remain on edge $(a-1,a)$ when we reach vertex $a-1$.
 We already know that $J_q^{(V)}(c+1) = \{c+1\}$; in particular this means that $q$ contributes $a-1$ in $I_{c+2}^{(V)}$.

### 2018-11-24 General WLD combinatorics.tex
mostly done the updates to the proof of the cyclic intervals but not quite

@@
 Write $p=(m,m+2)$ where $m\in \{i, i+1, l\}$.
-Note that $l, \ldota, l+a-1$ are all in the support of $p$.
+Note that $l, \ldots, l+a-1$ are all in the support of $p$.
 We first calculate $I^{(W)}_w$ for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$: if $w\in J_q^{(V)}(i)$ then
@@
     \[
-    I_{l+b}^{(W)}(r) & = \begin{cases}
+    I_{l+b}^{(W)}(r) = \begin{cases}
       l+b & \text{if } r=p\\
@@
      \[
-       I_j^{(W)}(r) & = \begin{cases}
-         j & \text{if } r=p \text{ and $j$ is in the suport of $p$} \\
-         I_{j+1}^{(V)}(r) & \text{if } r\neq p
+       I_j^{(W)}(r) = \begin{cases}
+         j & \text{if $r=p$ and $j$ is in the support of $p$}\\
+         I_{j+1}^{(V)}(r) & \text{if $r\neq p$ and $j$ is in the support of $p$}\\
+         I_{j}^{(V)}(r) & \text{if $r\neq p$ and $j$ is not in the support of $p$}
        \end{cases}
@@
        If $j$ is not in the support of $p$, then we must be in the second case with two vertices in the right hand region.
-Then if we start at $j$ we need to know whether propagators other than $p$ will remain around $i$ and $i+1$ when we reach vertex $i$ in the Grassmann necklace algorithm.
-****this part needs work, and it affects the rest potentially too, since $p$ is not taken first***
-
-For these two cases, it remains to consider the starting vertex $j+1$. If $j+1$ is in the support of $p$ then we can argue as above to get
+In this case if we start at $j$ we need to know whether propagators other than $p$ will remain around $i$ and $i+1$ when we reach vertex $i$ in the Grassmann necklace algorithm so as to know what $p$ contributes.
+Consider the WLD $X$ formed from $V$ by moving the second end of $q$ to the edge $j-1$ instead of $j$.
+$X$ is still admissible since we have not decreased the support of any set of propagators, so the induction hypothesis applies to it as well.
+Note that $J_{j}^{(V)}(r) = J_{j}^{(X)}(r)$ for all $r\neq p$ and $J_{j}^{(X)}(r) = J_{j+1}^{(X)}(r)$ for $r\neq q,p$.
+Additionally $I_{j+1}^{(X)}(q) = i$ by the induction hypothesis applied to $X$, and so starting at $j+1$ and assigning propagators to vertices according to the Grassmann necklace algorithm, when we get to the vertex $i$ in $X$ all propagators other than $q$ must have been assigned.
+Starting then at $j$ in $W$ we first assign $q$ to $j$, then proceed to assign as in $X$ starting at $j+1$ and then when we get to $i$ the only propagator left to assign is $j$.
+Therefore
+       \[
+       I_j^{(W)}(p) = m \text{if $j$ is not in the support of $p$}
+       \]
+
+For the left two cases of Figure~\ref{fig 3 cases} it remains to consider the starting vertex $j+1$. If $j+1$ is in the support of $p$ then we can argue as above to get
 \[
        I_{j+1}^{(W)}(r)  = \begin{cases}
-         j+1 & \text{if } r=p \text{ and $j+1$ is in the support of $p$}\\
-         I_{j+2}^{(V)}(r) & \text{if } r\neq p
+         j+1 & \text{if $r=p$ and $j+1$ is in the support of $p$}\\
+         I_{j+2}^{(V)}(r) & \text{if $r\neq p$ and $j+1$ is in the support of $p$}.
+       \end{cases}
+       \]  Thus if $j+1$ is in the support of $p$ then $m=j-2$, the intervals $J^{(W)}_r(*)$ are still cyclic for all $r \neq p$, and
+       ***these intervals need checking***
+\[J^{(W)}_p(j-2) = [j+2,c], \quad J^{(W)}_p(j-1) = [c+1,j-1], \quad J^{(W)}_p(j) = \{j\}, \quad J^{(W)}_p(j+1) = \{j+1\}\]
+  where
+  \[
+  c = \begin{cases} d-1 & \text{if } m=i+1 \\
+    j-2 & \text{otherwise}
       \end{cases}
   \]
-by the same arguments as above.  Thus the intervals $J^{(W)}_r(*)$ are still cyclic for all $r \neq p$, and
-\[J^{(W)}_p(a) = [c+2,d-1], \quad J^{(W)}_p(b) = [d,b], \quad J^{(W)}_p(c) = \{c\}, \quad J^{(W)}_p(c+1) = \{c+1\}\]
 also satisfies the statement of the theorem.
 
-In the ***This also needs adjusting and I haven't started it yet, nor what comes after*** middle case, if we start at $c+1$ we need to know whether any other propagators remain on edge $(a-1,a)$ when we reach vertex $a-1$.
-We already know that $J_q^{(V)}(c+1) = \{c+1\}$; in particular this means that $q$ contributes $a-1$ in $I_{c+2}^{(V)}$.
-However the construction of $I^{(V)}_{c+1}$ first associates $q$ to $c+1$ and then proceeds identically to $I^{(V)}_{c+2}$.
-In particular if $a-1$ was assigned in $I^{(V)}_{c+1}$, then it would not be available to assign to $q$ in $I^{(V)}_{c+2}$ as all other propagators supported at $a-1$ in $V$ come before $q$.
-    Therefore $p$ is the only unassigned propagator on edge $(a-1,a)$ when we reach $a-1$ in $W$, and
+Now suppose $j+1$ is not in the support of $p$.
+If we start at $j+1$ we need to know whether any other propagators remain on edge $i$ when we reach vertex $i$.
+We already know that $J_q^{(V)}(j+1) = \{j+1\}$; in particular this means that $q$ contributes $i$ in $I_{j+2}^{(V)}$.
+However the construction of $I^{(V)}_{j+1}$ first associates $q$ to $j+1$ and then proceeds identically to $I^{(V)}_{j+2}$.
+In particular if $i$ was assigned in $I^{(V)}_{j+1}$, then it would not be available to assign to $q$ in $I^{(V)}_{j+2}$ as all other propagators supported at $i$ in $V$ come before $q$.
+    Therefore $p$ is the only potentially unassigned propagator on edge $i$ when we reach vertex $i$ in $W$, and
     \[
-    I_{c+1}^{(W)}(r)  = \begin{cases}
-      a-1 & \text{if } r=p\\
-      I_{c+1}^{(V)}(r) & \text{if } r\neq p
+    I_{j+1}^{(W)}(r)  = \begin{cases}
+      m & \text{if  $r=p$ and $j+1$ is not in the support of $p$}\\
+      I_{j+1}^{(V)}(r) & \text{if  $r\neq p$ and $j+1$ is not in the support of $p$}
     \end{cases}
     \]
+    ***I have to redo assembling the intervals***
     Assembling the intervals, we have
-\[J^{(W)}_p(a-1) = \{c+1\}, \quad J^{(W)}_p(a) = [c+2,d-1], \quad J^{(W)}_p(b) = [d,b], \quad J^{(W)}_p(c) = \{c\},\]
-as required.
-
-\textbf{Right hand case}: In this case there is no vertex $b$, and $p$ is supported on ${(c,c+1,c+2,c+3)}$ in $W$.
-For $w \in [n]\backslash\{c,c+1,c+2,c+3\}$: if $w\in J_q^{(V)}(a-1)$ or $w\in J_q^{(V)}(a)$ then
+\[J^{(W)}_p(m) = [m+4, ], \quad J^{(W)}_p(m+1) = [j+2,d-1], \quad J^{(W)}_p(m+2) = [d,m+2], \quad J^{(W)}_p(m+3) = \{m+3\},\]
+which are nonempty and otherwise as required.
+
+\textbf{Right hand case}: In this case there are no unsupported vertices $l, \ldots$ inside $q$.
+Again write $p=(m, m+2)$ where $m\in \{j, j+1, j+2\}$.
+For $w \in [n]\backslash\{j+1,m,m+1,m+2,m+3\}$: if $w\in J_q^{(V)}(i)$ or $w\in J_q^{(V)}(i+1)$ then
     \[
     I_w^{(W)}(r) =  \begin{cases}
-        c & \text{if } r=p \\
+        m & \text{if } r=p \\
         I_{w}^{(V)}(r) & \text{if } r\neq p
@@
     \]
-    while if $w\in J_q^{(V)}(c)$ then
+    while if $w\in J_q^{(V)}(j)$ then
     \[
     I_w^{(W)}(r) =  \begin{cases}
-        c+1 & \text{if } r=p \\
+        \max\{m, j+1\} & \text{if } r=p \\
         I_{w}^{(V)}(r) & \text{if } r\neq p
@@
 
-Finally, for the vertices in the support of $p$, we have
+Finally, for $j+1$ and the vertices in the support of $p$, we have
 
 \begin{align*}
-      I_c^{(W)}(r) &= \begin{cases}
-        c & \text{if } r=q\\
-        c+1 & \text{if } r=p\\
-        I_c^{(V)}(r) & \text{if } r\neq p,q
+      I_{j+1}^{(W)}(r) &= \begin{cases}
+        \max\{j+2, m\} & \text{if } r=p\\
+        I_{j+1}^{(V)}(r) & \text{if } r\neq p
       \end{cases}\\
-      I_{c+1}^{(W)}(r) & = \begin{cases}
-        c+1 & \text{if } r=q \\
-        c+2 & \text{if } r=p \\
-        I_{c+3}^{(V)}(r) & \text{if } r\neq p,q
+      I_m^{(W)}(r) &= \begin{cases}
+        m & \text{if $r=p$ and $q$ not supported on $m$}\\
+        m+1 & \text{if $r=p$ and $q$ supported on $m$}\\
+        I_{m}^{(V)}(r) & \text{if } r\neq p
       \end{cases}\\
-      I_{c+2}^{(W)}(r) & = \begin{cases}
-        c+2 & \text{if } r=p \\
-        I_{c+3}^{(V)}(r) & \text{if } r\neq p
+      I_{m+1}^{(W)}(r) & = \begin{cases}
+        m+1 & \text{if $r=p$ and $q$ not supported on $m+1$} \\
+        m+2 & \text{if $r=p$ and $q$ supported on $m+1$} \\
+        I_{m+1}^{(V)}(r) & \text{if } r\neq p,q
       \end{cases}\\
-      I_{c+3}^{(W)}(r) & = \begin{cases}
-        c+3 & \text{if } r=p \\
-        I_{c+4}^{(V)}(r) & \text{if } r\neq p
+      I_{m+2}^{(W)}(r) & = \begin{cases}
+        m+2 & \text{if } r=p \\
+        I_{m+3}^{(V)}(r) & \text{if } r\neq p
+      \end{cases}\\
+      I_{m+3}^{(W)}(r) & = \begin{cases}
+        m+3 & \text{if } r=p \\
+        I_{m+4}^{(V)}(r) & \text{if } r\neq p
       \end{cases}
 \end{align*}
-Note that $I_{c+2}^{(V)}(r) = I_{c+3}^{(V)}(r)$ for all propagators $r$ in $V$. Once again we can see that the $J_r^{(W)}(*)$ are cyclic for all $r$ in $V$, and
+Note that $I_{m+2}^{(V)}(r) = I_{m+3}^{(V)}(r)$ for all propagators $r$ in $V$. Once again we can see that the $J_r^{(W)}(*)$ are cyclic for all $r$ in $V$, and
+***Fix these intervals again***
 \[J_p^{(W)}(c) = [c+4,e-1], \quad J_p^{(W)}(c+1) = [e,c], \quad J_p^{(W)}(c+2) = \{c+1,c+2\}, \quad J_p^{(W)}(c+3) = \{c+3\}.\]

### 2018-11-26 General WLD combinatorics.tex
fixed the intervals in the first two cases

@@
 Since unsupported vertices have no effect on the Grassmann necklace algorithm, it suffices to prove the result for $W$ with no unsupported vertices.
-Then by Lemma~\ref{lem sian} $W$ has at least one of the four situations illustrated in figure~\ref{fig 3 cases}
+Then by Lemma~\ref{lem sian} $W$ has at least one of the four situations illustrated in figure~\ref{fig 3 cases}.
 
@@
 In this case the support of $p$ is unsupported in $V$ so for every propagator $r$ in $V$ (including $q$) $J_r^{(V)} = J_r^{(W)}$.
-Additionally, $J_p^{(W)}(l+t) = l+a$ for $a\in\{1,2,3\}$ and $J_p^{(W)}(l) = [n] \backslash \{l+1, l+2, l+3\}$ which proves the result in this case.
+Additionally, $J_p^{(W)}(l+a) = \{l+a\}$ for $a\in\{1,2,3\}$ and $J_p^{(W)}(l) = [n] \backslash \{l+1, l+2, l+3\}$ which proves the result in this case.
 
@@
        \[
-       I_j^{(W)}(p) = m \text{if $j$ is not in the support of $p$}
+       I_j^{(W)}(p) = m \text{ if $j$ is not in the support of $p$}
        \]
@@
        \end{cases}
-       \]  Thus if $j+1$ is in the support of $p$ then $m=j-2$, the intervals $J^{(W)}_r(*)$ are still cyclic for all $r \neq p$, and
-       ***these intervals need checking***
-\[J^{(W)}_p(j-2) = [j+2,c], \quad J^{(W)}_p(j-1) = [c+1,j-1], \quad J^{(W)}_p(j) = \{j\}, \quad J^{(W)}_p(j+1) = \{j+1\}\]
-  where
-  \[
-  c = \begin{cases} d-1 & \text{if } m=i+1 \\
-    j-2 & \text{otherwise}
-      \end{cases}
        \]
-also satisfies the statement of the theorem.
+%Thus if $j+1$ is in the support of $p$ then $m=j-2$, the intervals $J^{(W)}_r(*)$ are still cyclic for all $r \neq p$, and
+%       ***these intervals need checking***
+%\[J^{(W)}_p(j-2) = [j+2,c], \quad J^{(W)}_p(j-1) = [c+1,j-1], \quad J^{(W)}_p(j) = \{j\}, \quad J^{(W)}_p(j+1) = \{j+1\}\]
+%  where
+%  \[
+%  c = \begin{cases} d-1 & \text{if } m=i+1 \\
+%    j-2 & \text{otherwise}
+%      \end{cases}
+%  \]
+%also satisfies the statement of the theorem.
 
@@
     \]
-    ***I have to redo assembling the intervals***
-    Assembling the intervals, we have
-\[J^{(W)}_p(m) = [m+4, ], \quad J^{(W)}_p(m+1) = [j+2,d-1], \quad J^{(W)}_p(m+2) = [d,m+2], \quad J^{(W)}_p(m+3) = \{m+3\},\]
+
+    Taking all the possibilities for the left two cases of Figure~\ref{fig 3 cases}, the intervals $J^{(W)}_r(*)$ are still cyclic for all $r \neq p$, and we can assemble the intervals for the $J_p^{(W)}(*)$ as follows.
+    \begin{itemize}
+      \item 
+    If $m=l$ then either $a=2$ (so $l+1=m+1$, $j=m+2$, and $j+1=m+3$) or $a=3$ (so $l+1=m+1$, $l+2=m+2$, $j=m+3$, and $j+1$ is not in the support of $p$), and in both cases
+    \[
+    J^{(W)}_p(m) = [m+4, m], \quad J^{(W)}_p(m+1) = \{m+1\}, \quad J^{(W)}_p(m+2) = \{m+2\}, \quad J^{(W)}_p(m+3) = \{m+3\},
+    \]
     which are nonempty and otherwise as required.
-
-\textbf{Right hand case}: In this case there are no unsupported vertices $l, \ldots$ inside $q$.
+  \item
+        If $m=i+1$ then checking each of the three different possibilities for $a$ we likewise get
+    \[
+    J^{(W)}_p(m) = [m+4, d-1], \quad J^{(W)}_p(m+1) = [d, m+1], \quad J^{(W)}_p(m+2) = \{m+2\}, \quad J^{(W)}_p(m+3) = \{m+3\},
+    \]
+    which are nonempty and otherwise as required.
+  \item If $m=i$ then $a=1$ or $a=2$, in the former case $l=m+2$, $j=m+3$ and $j+1$ is not in the support of $p$ so
+    \[
+    J^{(W)}_p(m) = \{m+3\}, \quad J^{(W)}_p(m+1) = [m+4, d-1], \quad J^{(W)}_p(m+2) = [d, m+1], \quad J^{(W)}_p(m+3) = \{m+2\},
+    \]
+    while in the latter $l=m+2$, $l+1=m+3$, and $j$ and $j+1$ are not in the support of $p$ so
+    \[
+    J^{(W)}_p(m) = [m+4, j+1], \quad J^{(W)}_p(m+1) = [j+2, d-1], \quad J^{(W)}_p(m+2) = [d, m+1], \quad J^{(W)}_p(m+3) = \{m+3\},
+    \]
+    which are again as required.
+    \end{itemize}
+
+\textbf{Third case}: In this case there are no unsupported vertices $l, \ldots$ inside $q$.
 Again write $p=(m, m+2)$ where $m\in \{j, j+1, j+2\}$.
@@
   I_{j+1}^{(W)}(r) &= \begin{cases}
-        \max\{j+2, m\} & \text{if } r=p\\
-        I_{j+1}^{(V)}(r) & \text{if } r\neq p
+    j+1 & \text{if } r=q\\
+    j+2 & \text{if } r=p\\
+    I_{j+3}^{(V)}(r) & \text{if } r\neq p,q
   \end{cases}\\
@@
 \end{align*}
-Note that $I_{m+2}^{(V)}(r) = I_{m+3}^{(V)}(r)$ for all propagators $r$ in $V$. Once again we can see that the $J_r^{(W)}(*)$ are cyclic for all $r$ in $V$, and
-***Fix these intervals again***
+Note that $I_{m+2}^{(V)}(r) = I_{m+3}^{(V)}(r)$ for all propagators $r$ in $V$, and that if $j+1\not\in\{m, m+1, m+2, m+3\}$ then $j+2$ and $j+3$ are unsupported in $V$ so in that case $I_{j+2}^{(V)}(r) = I_{j+3}^{(V)}(r) = I_{j+4}^{(V)}(r)$ for $r$ in $V$.
+Therefore, once again we can see that the $J_r^{(W)}(*)$ are cyclic for all $r$ in $V$.
+Assembling the intervals for $p$ we get, and
+***I still have to fix these intervals***
 \[J_p^{(W)}(c) = [c+4,e-1], \quad J_p^{(W)}(c+1) = [e,c], \quad J_p^{(W)}(c+2) = \{c+1,c+2\}, \quad J_p^{(W)}(c+3) = \{c+3\}.\]

### 2018-11-27 General WLD combinatorics.tex
finished first draft of cyclic intervals, changed lemma 3.4 accordingly and added def of weakly admissible.

@@
 \end{enumerate}
+A Wilson loop diagram is weakly admissible if the second and third conditions hold.
  \end{dfn}
@@
 \begin{lem}\label{lem sian 1}
-  Let $W$ be an admissible WLD in which each vertex supports at least one propagator.  Then exactly one of the following two things occurs.
+  Let $W$ be a weakly admissible WLD with at least 5 vertices and in which each vertex supports at least one propagator.  Then at least one of the following two things occurs.
   \begin{enumerate}
-    \item $W$ has a propagator of length 3 with a propagator of length 2 inside it.
-    \item $W$ admits no propagators of length 3, and one or more of the following things occurs.
-      \begin{enumerate}
-        \item There is a propagator of length $2$, say $(i, i+2)$ such that no other propagators ends on either the edge $i$ or the edge $i+2$.\label{item lonely 2}
+    \item $W$ has a propagator of length $\leq 6$ with a propagator of length 2 inside it and nothing else inside it.\label{item big and 2}
     \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator ends between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
-        \item There exists a propagator of length 4 with only a propagator of length 2 inside it.\label{item 4 and 2}
   \end{enumerate}
-  \end{enumerate}
+  %Then exactly one of the following two things occurs.
+  %\begin{enumerate}
+  %  \item $W$ has a propagator of length 3 with a propagator of length 2 inside it.
+  %  \item $W$ admits no propagators of length 3, and one or more of the following things occurs.
+  %    \begin{enumerate}
+  %      \item There is a propagator of length $2$, say $(i, i+2)$ such that no other propagators ends on either the edge $i$ or the edge $i+2$.\label{item lonely 2}
+  %      \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator ends between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
+  %      \item There exists a propagator of length 4 with only a propagator of length 2 inside it.\label{item 4 and 2}
+  %    \end{enumerate}
+  %\end{enumerate}
 \end{lem}
@@
 By Remark~\ref{rem:props of length 2 and 3} along with the fact that every vertex of $W$ supports at least one propagator, we have that $i+2$ supports exactly one propagator and this propagator must have length 2 by noncrossingness.
+This gives us an instance of configuration~\ref{item big and 2} from the statement.
 
@@
 
-  We will inductively construct a sequence of pairs of propagators $(p_r,q_r)$ satisfying: $\ell(p_r) = 2$, and $p_r$ either forms part of configuration \ref{item lonely 2}, \ref{item pair of 2s}, or \ref{item 4 and 2} from the statement,
+  We will inductively construct a sequence of pairs of propagators $(p_r,q_r)$ satisfying: $\ell(p_r) = 2$, and $p_r$ either forms part of configuration \ref{item big and 2} or \ref{item pair of 2s} from the statement,
   %a configuration \eqref{eq:2 prop config} in $D$
@@
 \end{itemize}
-Since $W$ contains finitely many vertices, this must eventually terminate in one of the three desired configurations. %a configuration of the form \eqref{eq:2 prop config}.
+Since $W$ contains finitely many vertices, this must eventually terminate in one of the desired configurations. %a configuration of the form \eqref{eq:2 prop config}.
 
@@
 %a configuration \eqref{eq:2 prop config} we are done,
-so suppose otherwise: since $p_1$ is not in configuration \ref{item lonely 2} then there must be a second propagator starting either on edge $j_1)$ or $j_1+2$.
-Flipping the diagram if necessary, assume the former.
-Since $p_1$ is not in configuration \ref{item pair of 2s} and every vertex is supported then there must exist a propagator $q_1$ of length $\geq 4$ with one end on edge $j_1$ or on edge $j_1-1$ or on edge $j_1-2$.
+so suppose otherwise: 
+Since $p_1$ is not in configuration \ref{item pair of 2s}, there are no propagators of length $3$, and every vertex is supported then there must exist a propagator $q_1$ of length $\geq 4$ with one end on edge $j_1$ or on edge $j_1-1$ or on edge $j_1-2$.
 This bounds a region $[i_1,k_1]$ (where $k_1 \in \{j_1-1, j_1, j_1+1\}$) which does not contain $p_1$.
@@
 $W_r$ has no propagators of length $3$ since $W$ has none.
-Let $p_{r+1}$ be a propagator of length 2 in $W_r$; if it forms part of configuration \ref{item lonely 2}, \ref{item pair of 2s}, or \ref{item 4 and 2}
+Let $p_{r+1}$ be a propagator of length 2 in $W_r$; if it forms part of configuration \ref{item big and 2} or \ref{item pair of 2s}
 %the configuration \eqref{eq:2 prop config}
@@
 
-Note we may replace $q_r$ by any other propagator of length $\geq 4$ in $W_r$ which contains $p_{r+1}$ and such a new $q_r$ still satisfies all the hypotheses, and so, without loss of generality we may assume that $q_r$ has minimal length among propagators of length $\geq 4$ which contain $p_{r+1}$.
+Note we may replace $q_r$ by any other propagator of length $\geq 4$ in $W_r$ which contains $p_{r+1}$; such a new $q_r$ still satisfies all the hypotheses, and so, without loss of generality we may assume that $q_r$ has minimal length among propagators of length $\geq 4$ which contain $p_{r+1}$.
 
@@
 Therefore, if $q_r$ contains another propagator of length $2$ we would have configuration \ref{item pair of 2s} which we have already assumed does not occur.
-Consequently, $q_r$ contains only $p_{r+1}$; if $q_r$ is of length $4$ then we have \ref{item 4 and 2} and if $q_r$ is of length $5$ or $6$ then we have either \ref{item lonely 2} or an unsupported vertex, all of which are impossible.
+Consequently, $q_r$ contains only $p_{r+1}$ and so we have \ref{item big and 2} which again we have assumed does not occur.
 Therefore the first case cannot occur.
@@
 \begin{figure}
-\includegraphics[scale=0.8]{Vdiagram}
+\includegraphics[scale=0.8]{Vdiagram_modified}
 \caption{Diagram $V$ is $W$ with $p$ removed; there are no propagators inside $q = (i,j)$, though there may be up to 4 unsupported vertices labelled $l, l+1, \ldots$.}
@@
     \[
-    J^{(W)}_p(m) = [m+4, m], \quad J^{(W)}_p(m+1) = \{m+1\}, \quad J^{(W)}_p(m+2) = \{m+2\}, \quad J^{(W)}_p(m+3) = \{m+3\},
+    J^{(W)}_p(m) = [m+4, m], \  J^{(W)}_p(m+1) = \{m+1\}, \  J^{(W)}_p(m+2) = \{m+2\}, \  J^{(W)}_p(m+3) = \{m+3\},
     \]
@@
     \[
-    J^{(W)}_p(m) = [m+4, d-1], \quad J^{(W)}_p(m+1) = [d, m+1], \quad J^{(W)}_p(m+2) = \{m+2\}, \quad J^{(W)}_p(m+3) = \{m+3\},
+    J^{(W)}_p(m) = [m+4, d-1], \  J^{(W)}_p(m+1) = [d, m+1], \  J^{(W)}_p(m+2) = \{m+2\}, \  J^{(W)}_p(m+3) = \{m+3\},
     \]
@@
     \[
-    J^{(W)}_p(m) = \{m+3\}, \quad J^{(W)}_p(m+1) = [m+4, d-1], \quad J^{(W)}_p(m+2) = [d, m+1], \quad J^{(W)}_p(m+3) = \{m+2\},
+    J^{(W)}_p(m) = \{m+3\}, \  J^{(W)}_p(m+1) = [m+4, d-1], \  J^{(W)}_p(m+2) = [d, m+1], \  J^{(W)}_p(m+3) = \{m+2\},
     \]
@@
     \[
-    J^{(W)}_p(m) = [m+4, j+1], \quad J^{(W)}_p(m+1) = [j+2, d-1], \quad J^{(W)}_p(m+2) = [d, m+1], \quad J^{(W)}_p(m+3) = \{m+3\},
+    J^{(W)}_p(m) = [m+4, j+1], \  J^{(W)}_p(m+1) = [j+2, d-1], \  J^{(W)}_p(m+2) = [d, m+1], \  J^{(W)}_p(m+3) = \{m+3\},
     \]
@@
 Therefore, once again we can see that the $J_r^{(W)}(*)$ are cyclic for all $r$ in $V$.
-Assembling the intervals for $p$ we get, and
-***I still have to fix these intervals***
-\[J_p^{(W)}(c) = [c+4,e-1], \quad J_p^{(W)}(c+1) = [e,c], \quad J_p^{(W)}(c+2) = \{c+1,c+2\}, \quad J_p^{(W)}(c+3) = \{c+3\}.\]
-
+Assembling the intervals for $p$ we get,
+ if $m=j$ then
+\[J_p^{(W)}(m) = [m+4,e-1], \  J_p^{(W)}(m+1) = [e,m], \  J_p^{(W)}(m+2) = [m+1,m+2], \  J_p^{(W)}(m+3) = \{m+3\},\]
+ if $m=j+1$ then
+\[J_p^{(W)}(m) = [m+4,m-1], \ J_p^{(W)}(m+1) = [m,m+1], \  J_p^{(W)}(m+2) = \{m+2\}, \  J_p^{(W)}(m+3) = \{m+3\},\]
+and if $m=j+2$ then
+\[J_p^{(W)}(m) = [m+4,m], \  J_p^{(W)}(m+1) = \{m+1\}, \  J_p^{(W)}(m+2) = \{m+2\}, \  J_p^{(W)}(m+3) = \{m+3\}.\]
 The result now follows by induction.

### 2018-11-27 General WLD combinatorics.tex
just some little things

@@
 In other words, a Wilson loop diagram, $(\cP, n)$ is admissible if and only if $n > \cP +4$, and has neither crossing propagators nor any pairs of propagators that start and end on the same pair of non-adjacent edges.
+
+Note that if we take any admissible Wilson loop diagram and remove the unsupported vertices then we will obtain a weakly admissible Wilson loop diagram that may or may not be admissible itself.
 
@@
 
-\begin{lem}\label{lem sian 1}
+\begin{lem}\label{lem sian}
   Let $W$ be a weakly admissible WLD with at least 5 vertices and in which each vertex supports at least one propagator.  Then at least one of the following two things occurs.
@@
 \begin{rmk}
-In the case that all vertices of an admissible WLD $W$ support at least two propagators, then Lemma~\ref{lem sian 1} substantially simplifies.
-By Remark~\ref{rem:props of length 2 and 3}, $W$ has no propagators of length $3$, so the first item of Lemma~\ref{lem sian 1} cannot occur at all.
-Configurations \ref{item lonely 2} and \ref{item 4 and 2} also necessarily entail vertices with support $1$ as does configuration \ref{item pair of 2s} unless $j=i+2$.
+In the case that all vertices of an admissible WLD $W$ support at least two propagators, then Lemma~\ref{lem sian} substantially simplifies.
+By Remark~\ref{rem:props of length 2 and 3}, $W$ has no propagators of length $3$.
+Configuration \ref{item big and 2} necessarily entails vertices with support $1$ as does configuration \ref{item pair of 2s} unless $j=i+2$.
 So in the case that $W$ has all vertices with support at least two then $W$ must contain a pair of propagators of length $2$  with the property that the first propagator is $(i, i+2)$, the second is $(i+2, i+4)$ and no other propagator ends on the edge $i+2$.
@@
 
-\note{This is a mess for now; protecting sets commented out, and 1.5 versions of the induction copied in by not yet edited}
-
-This is the lemma from the email with the proof copied from the email.
+Given a propagator $p$ and a vertex $i$ in its support, it will be very useful in the following to understand on what set of vertices the Grassmann necklace algorithm assigns $i$ to $p$.
+The answer is that the set is a non-empty cyclic interval.
+Lemma~\ref{vertex cyclic int lem} establishes this, but first we need a preliminary lemma which is also useful in its own right.
+
 \begin{lem}\label{lem last vert}
@@
 Then $p$ is not supported on $i+1$, so in building $I_{i+1}$ we will take the same propagators as in the construction of $I_i$ from vertices $i+1$ up to $b-1$, that is $I_{i+1} \cap \interval{i+1}{b-1} = I_{i} \cap \interval{i+1}{b-1}$.
-Furthermore, by Lemma~\ref{lem susama}, in building $I_{i+1}$, it must be that $p$ is taken at vertex $b$, as otherwise $b$ would never be contributed by $p$.
+Furthermore, by Lemma~\ref{vertex cyclic int lem}, in building $I_{i+1}$, it must be that $p$ is taken at vertex $b$, as otherwise $b$ would never be contributed by $p$.
 Consequently, in building $I_{i+1}$, when at vertex $b$ no propagator still remaining is before $p$.
@@
 
-The first lemma is Lemma~\ref{lem susama} and I moved it up to a previous section.
+The first lemma is Lemma~\ref{vertex cyclic int lem} and I moved it up to a previous section.
 
@@
 
-The third lemma is Sian's result.
-
-\begin{lem}\label{lem sian}
-  Let $D$ be a WLD with all vertices covered by at least two propagators.  Then There exist two propagators in $D$ with the following properties.
-  \begin{itemize}
-  \item The first propagator goes from the edge $i$, $i+1$ to the edge $i+2$, $i+3$.
-  \item The second propagator goes from the edge $i+2$, $i+3$ to the edge $i+4$, $i+5$
-  \item No other propagator is on the edge $i+2$, $i+3$.
-  \end{itemize}
-\end{lem}
-
-Actually the result I need is not exactly Sian's result and what I will actually use is her proof.
+The third lemma is now lemma~\ref{lem sian}.
+
+Here is some old text: Actually the result I need is not exactly Sian's result and what I will actually use is her proof.
 Thus I will use notation and definitions (including length of a propagator and the specific $p_i$ and $q_i$ construction from the proof) from her note without further discussion.
@@
 
-  If $n-3\in I_1^{C}$ then $n-3\not\in I_1^{D}$, but then $p$ never contributes $n-3$ contradicting Lemma~\ref{lem susama}.
+  If $n-3\in I_1^{C}$ then $n-3\not\in I_1^{D}$, but then $p$ never contributes $n-3$ contradicting Lemma~\ref{vertex cyclic int lem}.
 Thus $n-3\not\in I_1^{C}$ and so in building the Gra\ss mann necklace when we get to vertex $n-3$ any other covering propagators of $C$ have already been taken and so we can now take $p$.
@@
 Fortunately we can determine explicitely how propagator $q$ contributes to $I_{n}^{C}$.
-By Lemma~\ref{lem susama} propagator $q$ contributes $n-5$ to $I_{n}^{C}$, and the only way this can occur is if all other propagators of $C$ were already taken by the time we got to vertex $n-5$.
+By Lemma~\ref{vertex cyclic int lem} propagator $q$ contributes $n-5$ to $I_{n}^{C}$, and the only way this can occur is if all other propagators of $C$ were already taken by the time we got to vertex $n-5$.
 Therefore $I_{n-2}^{D} = (I_{n}^{C} - \{n-5\}) \cup \{n-1, n-2\}$.
@@
   Also by Lemma~\ref{lem I} $I_{n-1}^{D} = I_n^{C} \cup \{n-1\}$.
-Additionally $n-3\not\in I_{n}^{C}$ since if it were then $n-3$ would also be in $I_1^{C}$ and hence propagator $p$ could not contribute $n-3$ to $I_1^{D}$ in contradiction to Lemma~\ref{lem susama}.
+Additionally $n-3\not\in I_{n}^{C}$ since if it were then $n-3$ would also be in $I_1^{C}$ and hence propagator $p$ could not contribute $n-3$ to $I_1^{D}$ in contradiction to Lemma~\ref{vertex cyclic int lem}.
 Similarly $n-1, n-2\not\in I_n^{C}$.
@@
   If $n-2\not\in I_{n-2}^{C}$ then $I_{n-1}^{C}=I_{n-2}^{C}$ and by Lemma~\ref{lem I} $I_{n-2}^{D} = I_{n-1}^{C} \cup \{n-2\}$.
-Note that $n-3\not\in I_{n-2}^{C}$ by Lemma~\ref{lem susama}.
+Note that $n-3\not\in I_{n-2}^{C}$ by Lemma~\ref{vertex cyclic int lem}.
 Therefore the paths for $I_{n-2}^{D}$ are the paths for $I_{n-1}^{C}$ along with the $n-3\rightarrow n-2$ path.
@@
 
-\textbf{Case 1}: Suppose $p$ has one end on the edge $(i-1, i)$.  Thus $p$ is supported on $(i-1, i, m, m+1)$ for some $m >_i i$, and $I_{i+1}(p) = m$ by Lemma~\ref{lem susama}.  
+\textbf{Case 1}: Suppose $p$ has one end on the edge $(i-1, i)$.  Thus $p$ is supported on $(i-1, i, m, m+1)$ for some $m >_i i$, and $I_{i+1}(p) = m$ by Lemma~\ref{vertex cyclic int lem}.  
 %Call the propagators which appear before $p$ is closed the propagators inside $p$. \note{It might be nice to have general language for this inside/outside idea.  What do you think.}
@@
 Write $(i, i+1, j, j+1)$ for the support of $q$.
-The situation for $q$ is very similar to case 1: in particular, we have $I_{i+1}(q) = j$ by Lemma~\ref{lem susama} and so if $j\in I_i$ then the propagator which contributes $j$ is outside of $q$.
+The situation for $q$ is very similar to case 1: in particular, we have $I_{i+1}(q) = j$ by Lemma~\ref{vertex cyclic int lem} and so if $j\in I_i$ then the propagator which contributes $j$ is outside of $q$.
 
@@
 
-In both cases, since $I_{i-1}(p)\neq a$ by assumption it follows from Lemma~\ref{lem susama} that $I_{i-1}(p) <_{i-1} a$ and no other vertex supporting $p$ lies between $I_{i-1}(p)$ and $a$.
+In both cases, since $I_{i-1}(p)\neq a$ by assumption it follows from Lemma~\ref{vertex cyclic int lem} that $I_{i-1}(p) <_{i-1} a$ and no other vertex supporting $p$ lies between $I_{i-1}(p)$ and $a$.
 In the case that $b<_i a$ and $q$ is taken before $p$ in $I_i$, this means that $I_{i-1}(p)=b$ and so $I_{i-1}(q)\neq b$.
@@
 Since $I_{i-1}(p) \neq a$, there must be some other propagator $s$ with $I_{i-1}(s) = a$ (else $I_{i-1}$ assigns $q$ to $a$).
-This propagator cannot lie on edge $(a,b)$ since by Lemma~\ref{lem susama} we must have $I_i(s) = a$ or $b$, contradicting the fact that $I_i(p) = a$ and $I_i(q) = b$; thus $s$ has an end on $(a-1,a)$ and is inside $p$ from the point of view of $i-1$.
+This propagator cannot lie on edge $(a,b)$ since by Lemma~\ref{vertex cyclic int lem} we must have $I_i(s) = a$ or $b$, contradicting the fact that $I_i(p) = a$ and $I_i(q) = b$; thus $s$ has an end on $(a-1,a)$ and is inside $p$ from the point of view of $i-1$.
 
@@
 
-Since $p$ changed its association from $I_{i-1}$ to $I_i$, we have $I_{i-1}(p) = i-1$ by Lemma~\ref{lem susama}.
+Since $p$ changed its association from $I_{i-1}$ to $I_i$, we have $I_{i-1}(p) = i-1$ by Lemma~\ref{vertex cyclic int lem}.
 From figure~\ref{fig part 4} it follows that $I_{i-1}$ assigns $p$ to $i-1$ and then proceeds identically to $I_i$ for all vertices inside $p$, implying that $I_{i-1}(s) = I_i(s)$.
@@
 There exists some $i$ such that $f|\Delta_{I_i}$ but $f\!\!\nmid\!\!
-\Delta_{I_{i-1}}$, since otherwise the variables corresponding to the propagators contributing to $f$ which do not themselves appear in $f$ could never appear, contradicting Lemma~\ref{lem susama}.
+\Delta_{I_{i-1}}$, since otherwise the variables corresponding to the propagators contributing to $f$ which do not themselves appear in $f$ could never appear, contradicting Lemma~\ref{vertex cyclic int lem}.
 If $f$ is a linear factor, say from associating propagator $p$ to vertex $a$, then $I_{i}(p)=a$ and $I_{i-1}(p)\neq a$ so this factor appears in $r_i$.
@@
 If $f$ is a linear factor, say from associating propagator $p$ to vertex $a$, then there must be two distinct points in the Grassmann necklace algorithm where $p$ changes from not being associated to vertex $a$ to being associated to vertex $a$.
-This contradicts Lemma~\ref{lem susama}.
+This contradicts Lemma~\ref{vertex cyclic int lem}.
 Now suppose $f$ is a quadratic factor, say from associating propagators $p$ and $q$ to vertices $a$ and $b$ respectively.
@@
 
-To this end, first note that $R(W)$ and $R$ both have total degree $4|\mathcal{P}|$; the degree of $R(W)$ is immediate from the definition while that of $R$ follows from Lemma~\ref{lem susama}.
+To this end, first note that $R(W)$ and $R$ both have total degree $4|\mathcal{P}|$; the degree of $R(W)$ is immediate from the definition while that of $R$ follows from Lemma~\ref{vertex cyclic int lem}.
 By Proposition~\ref{prop alg gives rad} every factor of $R$ is either a single variable or a quadratic factor coming from two propagators supported on a common edge and \hlfix{hence every factor of $R$ divides $R(W)$}{Is this obvious?

### 2018-12-11 General WLD combinatorics.tex
Minor notes on section 2.2 and 2.3

@@
 
-We first give a quick summary of the matroid terminology that we will need; it is not intended as a comprehensive introduction to matroids and the interested reader is referred to [ref].
+We first give a quick summary of the matroid terminology that we will need; it is not intended as a comprehensive introduction to matroids and the interested reader is referred to [ref][find a good matroid reference].
 
@@
 In particular, this allows us to prove results about $M(W)$ by considering the behavior of propagators in $W$.
-We record a few elementary facts about the rank and cycles of $M(W)$ here as an example of this.\note{It would be nice to have a few more; do we need any others, and/or are there any cool ones?}
+We record a few elementary facts about the rank and cycles of $M(W)$ here as an example of this.
 
@@
 \item If $C \subseteq [n]$ is a cycle, then $\rk(C) = |Prop(C)|$.
-\item If $[n]$ can be partitioned into at least two non-empty sets, each of which support different sets of propagators, \bas [n] = \cup_i V(P_i) \quad \textrm{s.t.} \quad \cup P_i = \cP; \quad  P_i \cap P_j = \emptyset \;, \eas the the matroid $M(W)$ is seperable, \bas M(W) = \bigoplus_i M(P_i, V(P_i)) \;.\eas
+\item If $[n]$ can be partitioned into at least two non-empty sets, each of which support different sets of propagators, \bas [n] = \cup_i V(P_i) \quad \textrm{s.t.} \quad \cup P_i = \cP; \quad  P_i \cap P_j = \emptyset \;, \eas the the matroid $M(W)$ is seperable, \bas M(W) = \bigoplus_i M(P_i, V(P_i)) \;.\eas \note{Closest reference I could find for this was Theorem 3.23 of Agarwala/Amit, which relates to $F(P_i)$ instead of $V(P_i)$; check if there's a better reference?}
 \end{enumerate}
@@
 \begin{proof}
-We begin by giving an algorithm for the decomposition, then prove its uniqueness. Let $W = (\cP, n)$, with $|\cP| = k$.
+We begin by giving an algorithm for the decomposition, then prove its uniqueness. Let $W = (\cP, [n])$, with $|\cP| = k$.
 
@@
 
-Since $W$ is admissible, by Lemma \ref{tausimpleplanarlem} $\tau(W)$ is a simple graph. Furthermore, $t$ is not all of $\tau(W)$.
-
+Since $W$ is admissible, by Lemma \ref{tausimpleplanarlem} $\tau(W)$ is a simple graph.
 Let $t$ be a triangulated piece of the decomposition of $\tau(W)$ given in Lemma \ref{decompositionlem}; note that $t$ cannot be equal to $\tau(W)$ by the definition of admissible diagrams.
 
-If $t$ has 2 vertices, then $t$ has two connected components.
-Therefore, $t$ corresponds to a propagator that connects two non-adjacent edges.
+If $t$ has 2 vertices, \hlfix{then $t$ has two connected components.}{I'm not sure what this is meant to say?} Therefore, $t$ corresponds to a propagator that connects two non-adjacent edges.
 Therefore, the trivial triangulation is a trivial exact subdiagram.
@@
 Now suppose that $t$ has $m>2$ vertices; we count how many edges of $t$ are not on the outer face of $\tau(W)$.
-Consider the intersection of $t$ with the outer face of $\tau(W)$: this is a possibly disconnected subgraph of the polygon of $\tau(W)$ with $m$ vertices, call it $S$.
-Let $k$ be the number of connected components of $S$.
-To join the components $S$ must have $k$ edges not in the outer face of $\tau(W)$.
+Consider the intersection of $t$ with the outer face of $\tau(W)$: this is a possibly disconnected subgraph of the polygon of $\tau(W)$ with $m$ vertices.
+Call this new subgraph $S$, and let $j$ be the number of connected components of $S$.
+To join the components \hlfix{$S$}{check: is this $S$ or $t$?} must have $j$ edges not in the outer face of $\tau(W)$.
 Furthermore $t$ has $m-3$ edges not in its outer face and so also not in the outer face of $\tau(W)$.
-Thus there are $m-3+k$ edges of $t$ not in the outer face of $\tau(W)$.
-
-Each of these $m-3+k$ internal edges correspond to propagators in $W$, call this set $P$.
+Thus there are $m-3+j$ edges of $t$ not in the outer face of $\tau(W)$.
+
+Each of these $m-3+j$ internal edges correspond to a propagator in $W$; call this set of propagators $P$.
 Next we count the size of $V(P)$.
 Each of the $m$ vertices in the outer face of $t$ corresponds to an edge of $W$.
-These $m$ edges define $k$ connected compnents of the outer polygon of $W$.
-Thus the set $V(P)$ has $m+k$ vertices.
+These $m$ edges define $j$ connected components of the outer polygon of $W$.
+Thus the set $V(P)$ has $m+j$ vertices.
 In other words,
-\[|V(P)| = m+k = |P| -3\;.\]
+\[|V(P)| = m+j = |P| +3\;.\]
+Thus the subdiagram $(P,V(P))$ defined by $t$ is exact.
 
@@
 Then the corresponding subgraph of $\tau(W)$ has $m-c$ vertices.
-Call it $t$.
-If $t$ were a triangulated component, $t$ would have $k -c$ internal edges.
-
-The graph $t$ has $k$ edges that come from propagators, and $m - 2c$ edges that come from the boundary polygon of $\tau(W)$.
+\hlfix{Call it $t$.}{$t$ is defined twice, and I'm not sure what $m$ and $j$ are for this direction of the proof.} If $t$ were a triangulated component, $t$ would have $j -c$ internal edges.
+
+The graph $t$ has $j$ edges that come from propagators, and $m - 2c$ edges that come from the boundary polygon of $\tau(W)$.
 Since $t$ has $m-c$ vertices, it has $m-c$ external edges, of which $c$ come from propagators.
-Therefore, of the $k$ edges of $t$ that come from propagators, $k-c$ are internal to the connected component.
+Therefore, of the $j$ edges of $t$ that come from propagators, $j-c$ are internal to the connected component.
 Therefore, this is triangulated.
@@
 \begin{cor} \label{uniqueproppartitioncor}
-Any admissible Wilson loop diagram $W = (\cP, n)$ can be uniquely decomposed into maximal exact subdiagrams. These maximal subdiagrams partition $\cP$.
+Any admissible Wilson loop diagram $W = (\cP, [n])$ can be uniquely decomposed into maximal exact subdiagrams. These maximal subdiagrams partition $\cP$.
 \end{cor}
@@
 \begin{lem} \label{contractsubdiaglem} \cite[Theorem 3.33]{wilsonloop} 
-Let $W = (\cP, n)$ be an admissible Wilson loop diagram and $P \subseteq \cP$.
+Let $W = (\cP, [n])$ be an admissible Wilson loop diagram and $P \subseteq \cP$.
 If the set $V(P)^c$ has rank $|P^c|$, then the matroid defined by the subdiagram $(P, V(P))$ is equal to the contraction $M(W)/V(P)^c$.
@@
 \begin{dfn}\label{def prop flat}
-Let $W = (\cP,n)$ be an admissible Wilson loop diagram and $P \subseteq \cP$. The set $F(P) := V(P^c)^c$ is called the {\em propagator flat} of $P$.
+Let $W = (\cP,[n])$ be an admissible Wilson loop diagram and $P \subseteq \cP$. The set $F(P) := V(P^c)^c$ is called the {\em propagator flat} of $P$.
 \end{dfn}
 Thus in Lemma \ref{contractsubdiaglem} above we would contract $M(W)$ by the propagator flat $F(P^c)$ of the {\em complement} of $P$ in order to study $(P,V(P))$.
-The justification for this notation is given by (1) of the next lemma: the set $F(P)$ consists of exactly those vertices which {\em only} support propagators in $P$.
+The justification for this notation is given by (1) of the next lemma: the set $F(P)$ consists of vertices which {\em only} support propagators in $P$ (or no propagators at all).
 
@@
 \begin{enumerate}
-\item $F(P) = V(P) \setminus V(P^c)$.
+\item $F(\emptyset)$ is exactly the set of vertices which support no propagators, while for $P \neq \emptyset$ we have \[F(P) = \big(V(P) \setminus V(P^c)\big) \cup F(\emptyset).\] \note{updated (1) to match new definition of $F(P)$; }
 \item If $Q\subseteq P$ then $F(Q) \subseteq F(P)$.
@@
 Let $v \in C$.
-Clearly $\Prop(v) \subseteq \Prop(C)$, and so by Lemma \ref{lem properties of prop flatfs} we have $F(\Prop(v)) \subseteq F(\Prop(C))$.
+Clearly $\Prop(v) \subseteq \Prop(C)$, and so by Lemma \ref{lem properties of prop flats} we have $F(\Prop(v)) \subseteq F(\Prop(C))$.
 Since $v \in F(\Prop(v))$ by the definition of propagator flat, we have $v \in F(\Prop(C))$ as required.
@@
 This implies that $(F\setminus C)\cup \{e\}$ is dependent, and hence contains a circuit.
-This circuit must contain at least two elements (since all vertices support at least one propagator), but this contradicts the fact that $C$ was the union of all circuits in $F$.
+This circuit must contain at least two elements \note{What if $e \in C$ supported no propagators?
+$\{e\}$ would then be a circuit on its own}(since all vertices support at least one propagator), but this contradicts the fact that $C$ was the union of all circuits in $F$.
 
@@
 \begin{lem} \label{maxexactcomplementrank}
-Let $W = (\cP, n)$ be a Wilson loop diagram, and $P \subseteq \cP$. Then: \begin{enumerate}
+Let $W = (\cP, [n])$ be a Wilson loop diagram, and $P \subseteq \cP$. Then: \begin{enumerate}
 \item If $(P,V(P))$ is an exact subdiagram in $W$, then $\rk(F(P^c)) = |P^c|$.
@@
 
-Note that by definition, since $F(P^c)$ has at $|P^c|$ propagators in it, this is an upper bound on the rank. However, showing equality on the first part is harder.
-
-\begin{proof}
-We first verify that $F(P^c) = V(P)^c$ is non-empty and dependent for any exact subdiagram $(P,V(P))$.
-The definition of exactness means that the vertices $V(P)$ cannot support a larger set of propagators (otherwise $W$ would no longer be admissible).
-Therefore, since $P \subsetneq \cP$, there must be at least one propagator supported on $V(P)^c$, i.e.
-it cannot be empty.
+Note that $|P^c|$ is always an upper bound on the rank of $F(P^c)$ for any $P \subseteq \cP$, since $F(P^c)$ supports at most $P^c$ propagators. However, showing equality is far harder.
+
+\begin{proof}
+First note that if $(P,V(P))$ is exact then the admissiblity of $W$ guarantees that $F(P^c)$ is non-empty.
 
@@
 \begin{equation}\label{eq F is dependent}|F(P^c)| > |P^c| \;.\end{equation}
-By Lemma \ref{lem properties of prop flats}, $F(P^c)$ is the set of vertices that {\em only} supports propagators in $P^c$, so in particular we have $\Prop(F(P^c)) = P^c$.
+By Lemma \ref{lem properties of prop flats}, $F(P^c)$ is a set of vertices that supports only propagators in $P^c$, so in particular we have $\Prop(F(P^c)) = P^c$.
 Equation \eqref{eq F is dependent} is therefore saying that $F(P^c)$ supports fewer propagators than the number of vertices it contains, i.e.
@@
 where $C$ is the largest cyclic flat contained in $F(P^c)$ and $S$ is an  independent set.
-Note that $C$ must be non-empty since $F(P^c)$ is dependent.
+Note that $C$ must be non-empty since $F(P^c)$ is non-empty and dependent.
 We proceed by showing that $S$ must be empty, forcing $F(P^c)$ to be a cyclic flat.
@@
 Furthermore, we have
-\begin{equation}\rk(S) = |S| \leq \rk(F(P^c)) - \rk(C)  \leq |P^c| - \rk(C) \;, \label{increasingrank}\end{equation}
-where first equality comes from the fact that $S$ is an independent set, and the final inequality comes from Lemma \ref{lem facts about WLD matroids}(1).
+\begin{equation}|S| = \rk(S) \leq \rk(F(P^c)) - \rk(C)  \leq |P^c| - \rk(C) \;, \label{increasingrank}\end{equation}
+where first equality comes from the fact that $S$ is an independent set,\note{Did we ever address the question of where the middle inequality comes from?
+Can we argue by number of propagators?} and the final inequality comes from Lemma \ref{lem facts about WLD matroids}(1).
 Since $\rk(C) = |\Prop(C)| = |Q^c|$ by Lemma \ref{lem facts about WLD matroids}(2), we can rearrange \eqref{increasingrank} to obtain the inequality
 \begin{equation} |P| + |S| \leq |P| + |P^c| - \rk(C) = |Q| \;. \label{Qsizebound}\end{equation}
-Furthermore, since $V(Q) = S \sqcup V(P)$ (by equation [ref] and the definition of $Q$) we may write  
+Furthermore, since $V(Q) = S \sqcup V(P)$ (by equation \eqref{eq decompose F} and the definition of $Q$) we may write  
 \begin{equation} |V(Q)| = |S| + |V(P)| = |S| + |P| +3 \label{VQsize} \;.\end{equation} 
-Combining this with \eqref{Qsizebound} gives $|V(Q)| - 3 \leq |Q|$.
-That is, either $W$ was not admissible, or $(P,V(P))$ was not a maximal exact subdiagram.
-In other words, $S$ cannot be non-empty, proving that $F(P^c)$ is a cyclic flat, and therefore of maximal rank.
-
-Let $P$ be a maximal exact subdiagram as above, and let $(R, V(R))$ be an exact subdiagram that is not maximal. That is, $R \subsetneq P$.
+Combining this with \eqref{Qsizebound} gives $|V(Q)| \leq |Q| + 3$.
+Since $W$ is admissible, we conclude that $(Q,V(Q))$ is exact; since $V(Q) = V(P) \sqcup S$ and $(P,V(P))$ is maximal exact, it follows that $S = \emptyset$.
+It now follows from \eqref{eq decompose F} that $F(P^c)$ is a cyclic flat, and hence from Lemma \ref{lem facts about WLD matroids} that
+\[\rk(F(P^c)) = |Prop(F(P^c))| = |P^c|.\]
+
+Let $P$ be a maximal exact subdiagram as above, and let $(R,V(R))$ be an exact subdiagram that is not maximal. That is, $R \subsetneq P$.
 
@@
 \begin{thm} \label{exactcircuitlem}
-Let $W':= (P, V(P))$ be a subdiagram of an admissible Wilson loop diagram $W= (\cP, n)$. Then $W'$ is an exact subdiagram if and only if $M(W')$ is a uniform matroid of rank $|P|$.
+Let $W':= (P, V(P))$ be a subdiagram of an admissible Wilson loop diagram $W= (\cP, [n])$. Then $W'$ is an exact subdiagram if and only if $M(W')$ is a uniform matroid of rank $|P|$.
 \end{thm}

### 2018-12-11 General WLD combinatorics.tex
answering some of Sian's questions

@@
 We depict the choice of first vertex on $V$ by a $\bullet$.
-Note that the polygon gives the verices of $W$ a cyclic ordering, which the choice of first vertex gives it a compatible linear order.
+\note{If we look at the pictures we have later (at least some of them), we don't do that.
+Instead all the vertices are $\bullet$.} Note that the polygon gives the verices of $W$ a cyclic ordering, which the choice of first vertex gives it a compatible linear order.
 Both the cyclic and the linear order become the correct perspective at various points in this paper.
@@
 
-If $t$ has 2 vertices, \hlfix{then $t$ has two connected components.}{I'm not sure what this is meant to say?} Therefore, $t$ corresponds to a propagator that connects two non-adjacent edges.
-Therefore, the trivial triangulation is a trivial exact subdiagram.
-
-Now suppose that $t$ has $m>2$ vertices; we count how many edges of $t$ are not on the outer face of $\tau(W)$.
-Consider the intersection of $t$ with the outer face of $\tau(W)$: this is a possibly disconnected subgraph of the polygon of $\tau(W)$ with $m$ vertices.
+If $t$ has 2 vertices then $t$ corresponds to a propagator that connects two non-adjacent edges. Therefore, the trivial triangulation is a trivial exact subdiagram.
+
+Now suppose that $t$ has $m>2$ vertices.
+We count how many edges of $t$ are not on the outer face of $\tau(W)$.
+Consider the intersection of $t$ with the outer face of $\tau(W)$: this is a possibly disconnected subgraph of the polygon of $\tau(W)$ and this subgraph has $m$ vertices.
 Call this new subgraph $S$, and let $j$ be the number of connected components of $S$.
-To join the components \hlfix{$S$}{check: is this $S$ or $t$?} must have $j$ edges not in the outer face of $\tau(W)$.
+To join the components of $S$ into the outer face of $t$, $t$ must have $j$ edges in its outer face which are not in the outer face of $\tau(W)$.
 Furthermore $t$ has $m-3$ edges not in its outer face and so also not in the outer face of $\tau(W)$.
@@
 
-Each of these $m-3+j$ internal edges correspond to a propagator in $W$; call this set of propagators $P$.
+Each of these $m-3+j$ internal edges corresponds to a propagator in $W$; call this set of propagators $P$.
 Next we count the size of $V(P)$.
@@
 
-If $|P|=1$, then $(P, V(P))$ is a trivially exact subdiagram. In this case $t$ is an edge internal to $\tau(W)$ connecting two boundary edges, which by definition is a triangulation.
-
-Suppose the set $V(P)$ defines $c$ disjoint cyclic intervals of $[n]$.
-Then the corresponding subgraph of $\tau(W)$ has $m-c$ vertices.
-\hlfix{Call it $t$.}{$t$ is defined twice, and I'm not sure what $m$ and $j$ are for this direction of the proof.} If $t$ were a triangulated component, $t$ would have $j -c$ internal edges.
+Suppose $|P|=1$.
+Then $(P, V(P))$ is a trivially exact subdiagram.
+In this case $t$ is an edge internal to $\tau(W)$.
+The exactness condition on $(P, V(P))$ says that the four supporting vertices of the element of $P$ are distinct and no other propagators are supported on those vertices.
+Translating this to $\tau(W)$ gives that the vertices which are the ends of $t$ are separated by at least two vertices along the cycle and no other internal edges connect to the ends of $t$.
+This implies that $t$ is a trivial triangulation.
+
+Now suppose $|P|>1$.  Let $j=|P|$, $m=|V(P)|$, and 
+suppose that the set $V(P)$ defines $c$ disjoint cyclic intervals of $[n]$. Then $t$ has $m-c$ vertices.  If $t$ were a triangulated component, $t$ would have $j -c$ internal edges.
 
@@
 Therefore, of the $j$ edges of $t$ that come from propagators, $j-c$ are internal to the connected component.
-Therefore, this is triangulated.
+Therefore, $t$ is a triangulation.
 

### 2018-12-11 General WLD combinatorics.tex
various stuff I was supposed to do in section 3

@@
 so suppose otherwise: 
-Since $p_1$ is not in configuration \ref{item pair of 2s}, there are no propagators of length $3$, and every vertex is supported then there must exist a propagator $q_1$ of length $\geq 4$ with one end on edge $j_1$ or on edge $j_1-1$ or on edge $j_1-2$.
+By assumption $p_1$ is not in configuration \ref{item pair of 2s}, there are no propagators of length $3$, and every vertex is supported.
+Therefore there must exist a propagator $q_1$ of length $\geq 4$ with one end on edge $j_1$ or on edge $j_1-1$ or on edge $j_1-2$.
 This bounds a region $[i_1,k_1]$ (where $k_1 \in \{j_1-1, j_1, j_1+1\}$) which does not contain $p_1$.
@@
 
-\begin{lem}\label{lem last vert}
-  Let W be an admissible WLD on $n$ vertices with Grassmann necklace $I_1, \ldots, I_n$.
+%\begin{lem}\label{lem last vert}
+%  Let W be an admissible WLD on $n$ vertices with Grassmann necklace $I_1, \ldots, I_n$.
 Then for all $1\leq a \leq n$, $a-1 \not\in I_a$ interpreted cyclically (that is for $a=1$, $a-1$ is interpreted to be $n$.)
-\end{lem}
-
-\begin{proof}
-Without loss of generality we can suppose $a=1$, so it suffices to show that $C(W)$ with the $n$th column removed is full rank.
+%\end{lem}
+%
+%\begin{proof}
+%Without loss of generality we can suppose $a=1$, so it suffices to show that $C(W)$ with the $n$th column removed is full rank.
 (This suffices because if $C(W)$ with the $n$th column removed had full rank but the lexicographically minimal basis of $C(W)$ included the $n$th column, then we'd obtain a contradiction by taking this minimal basis with the $n$th column removed and extending it to a basis using a column from the first $n-1$ columns of $C(W)$ which is possible by the full rank assumption.)
-
-Because the nonzero entries of $C(W)$ are independent indeterminants, it suffices to show that there is some choice of nonzero entries of $C(W)$, one in each row, each in different columns, and none of which are the $n$th column.
+%
+%Because the nonzero entries of $C(W)$ are independent indeterminants, it suffices to show that there is some choice of nonzero entries of $C(W)$, one in each row, each in different columns, and none of which are the $n$th column.
 This is equivalent to an assignment of all propagators to supporting vertices so that no two are assigned to the same vertex and none are assigned to vertex $n$.
 The lemma is proved if we show such an assignment exists.
-
-Consider an assignment $f$ of a subset of propagators to vertices not including vertex $n$ with the maximal number of propagators.
+%
+%Consider an assignment $f$ of a subset of propagators to vertices not including vertex $n$ with the maximal number of propagators.
 If $f$ assigns $n$ propagators then we are done.
@@
 Build a sequence of sets $S_i$ of propagators and $T_i$ of vertices as follows.
-
-\begin{enumerate}
-  \item $S_0={p}$ and $T_0$ is the support of $p$ except for $n$.  Set $i=0$.
-  \item Let $R$ be the set of propagators which are assigned to a vertex in $T_i$ by $f$. Let $S_{i+1}= S_i \cup R$.  Let $T_{i+1} = T_i \cup (\text{supp}(R) - \{n\})$.\label{item loop step}
-  \item If there is a vertex $v_{i+1}$ in $T_{i+1}$ which has not been assigned by $f$ then by construction there is a propagator $q_{i+1} \in S_{i+1}-S_i$ which can be assigned to $v_{i+1}$.
+%
+%\begin{enumerate}
+%  \item $S_0={p}$ and $T_0$ is the support of $p$ except for $n$.  Set $i=0$.
+%  \item Let $R$ be the set of propagators which are assigned to a vertex in $T_i$ by $f$. Let $S_{i+1}= S_i \cup R$.  Let $T_{i+1} = T_i \cup (\text{supp}(R) - \{n\})$.\label{item loop step}
+%  \item If there is a vertex $v_{i+1}$ in $T_{i+1}$ which has not been assigned by $f$ then by construction there is a propagator $q_{i+1} \in S_{i+1}-S_i$ which can be assigned to $v_{i+1}$.
 Do so, removing $q_{i+1}$'s old assignment.
@@
 This new assignment contradicts the maximality of $f$.
-  \item  If nothing changed in step \ref{item loop step} then all vertices of $T_{i+1}$ are assigned to propagators in $S_{i+1}-\{p\}$ and vice versa.
+%  \item  If nothing changed in step \ref{item loop step} then all vertices of $T_{i+1}$ are assigned to propagators in $S_{i+1}-\{p\}$ and vice versa.
 Thus $|S_{i+1}| = |T_{i+1}|+1$.
@@
 Thus we have $|S_{i+1}|$ propagators supported on $|S_{i+1}|$ vertices contradicting admissibility.
-  \item Increment $i$ and go to \ref{item loop step}
-\end{enumerate}
-
-This procedure must be finite as either a contradiction is found or $S_i$ grows at each step but $W$ has finitely many propagators.
+%  \item Increment $i$ and go to \ref{item loop step}
+%\end{enumerate}
+%
+%This procedure must be finite as either a contradiction is found or $S_i$ grows at each step but $W$ has finitely many propagators.
 However, the only way for the process to end is by reaching a contradiction.
 Therefore any maximal assignment is a basis not including column $n$ which proves the lemma.
-\end{proof}
-
-%such that $b+1 \in V_{p_1}$, with an endpoint more clockwise on $W$ than the endpoint of $p$ supported by $b+1$: see Figure~\ref{fig:base step of alg induction}.
-%
-%\begin{figure}
-%\begin{tikzpicture}[rotate=15]
-%\begin{scope}
-%\drawWLD{12}{2}
-%\drawprop{3}{2}{10}{2} % P
-%% number vertices a,a+1,b,b+1 for prop P
-%
-%% clip these
-%\drawprop{3}{-2}{12}{-2}
-%\drawprop{2}{0}{12}{2}
-%\drawprop{6}{0}{10}{-2} % p1
-%
-%
-%\end{scope}
-%\end{tikzpicture}
-%\caption{Base step: if $P$ survives $n$ steps of the algorithm, there must be another propagator $p_1$ to its right on edge $(b,b+1)$.}
-%\label{fig:base step of alg induction}
-%\end{figure}
-%
-%The propagator $p_1$ forms the base step for the following induction:
-%
-%Suppose that $p_r$ is a propagator supported on $(i,i+1,m,m+1)$ and removed at step $m+1$ of the algorithm; we will show that there must also be a propagator $p_{r+1}$ supported on $(i',i'+1,m',m'+1)$ with $i \leq i'$ and $m \geq m'$, which is removed at step $m'+1$.
-Since we can't have both $i' = i$ and $m'=m$, $p_{r+1}$ bounds a region containing strictly fewer vertices than $p_r$.
-%
-%Notice that if we restrict our attention to the region bounded by $p_r$ and the edges of the diagram from $i$ to $m+1$, then propagators outside of this region can affect the algorithm only at vertices $i$, $i+1$.
-(The starting vertex 1 lies outside this region, by assumption.)
-%
-%Given a propagator $p_r$ supported on $(i,i+1,m,m+1)$ and removed at step $m+1$, we must also have a propagator $q$ to its right which is removed at step $m$ (``protecting'' $p_r$ at step $m$).
-This splits into two cases:
-%
-%\textbf{Case I}: If $q$ is supported on $(k,k+1,m-1,m)$ for some $k \geq i$, then $p_{r+1}:=q$  satisfies the conditions of the induction step.
-%
-%\textbf{Case II}: Suppose $q$ is supported on $(k,k+1,m,m+1)$ for some $k$; since the diagram is admissible, we have $k > i$.
-In particular, anything that happens at vertex $k+1$ is unaffected by propagators outside the region bounded by $p_r$, since $k+1 > i+1$.
-But $q$ must survive until step $m$, so there must be another propagator $q'$ to the right of $q$, which protects $q$ at step $k+1$.
-The admissibility of $W$ implies that $q'$ is supported on $(j,j+1,k,k+1)$ for some $j \geq i$, and we can take $p_{r+1}:=q'$.
-%
-%\begin{figure}
-%\begin{tabular}{ccc}
-%\begin{tikzpicture}[rotate=15]
-%\begin{scope}
-%\drawWLD{12}{2}
-%\drawprop{3}{0}{10}{0} % p_r
-%% number vertices i,i+1,m,m+1
-%
-%%clip these
-%\drawprop{6}{0}{9}{0} % q
-%\end{scope}
-%\end{tikzpicture}
-%
-%& \qquad \qquad &
-%\begin{tikzpicture}[rotate=15]
-%\begin{scope}
-%\drawWLD{12}{2}
-%\drawprop{3}{0}{10}{2} % p_r
-%% number vertices i, i+1, m, m+1
-%
-%\drawprop{7}{2}{10}{-2} %q
-%% vertices k,k+1, m,m+1
-%
-%% clip this one
-%\drawprop{4}{0}{7}{-2} % q'
-%% vertices j,j+1,k, k+1
-%
-%\end{scope}
-%\end{tikzpicture}
-%\\
-%Case I & & Case II
-%\end{tabular}
-%
-%\caption{Inductive step: if propagator $q$ is removed at step $m$, then it lies on either edge $(m-1,m)$ (Case I) or $(m,m+1)$ (Case II).}
-%\label{fig: cases for inductive step, algorithm}
-%\end{figure}
-%
-%By induction, we will eventually find a propagator on a region with 3 or fewer v%ertices, which is inadmissible.
+%\end{proof}
+
+Given a propagator $p$ of an admissible WLD $W$ and a vertex $i$ in the support of $p$ we will use the notation $J_p^{(W)}(i)$ for the set of indices $m$ where $I_m(p) = l$ where the $I_m$ are the sets calculated by Algorithm~\ref{alg:put GN on WLD}, and using the notation of Definition~\ref{def I_i as a function}.
 
 \begin{lem} \label{vertex cyclic int lem}
-  For every $v \in V_p$, Let $A_v \subset [n]$ be the set of vertices where $p$ contributes $v$ to $I_a$. Then $A_v$ is a non-empty cyclic interval.
-
-  \note{the above is the statement that was in this file, the below is the version of the statement from last july}
-
-Let $p$ be a propagator of an admissible WLD $W$ on $n$ vertices.
-Let $p = (i,j)$.
-For $l\in \{i, i+1, j, j+1\}$, let $J_p^{(W)}(l)$ be the indices $m$ where $I_m(p)=l$.
+
+Let $p=(i,j)$ be a propagator of an admissible WLD $W$ on $n$ vertices.
 Then $J_p^{(W)}(i)$, $J_p^{(W)}(i+1)$, $J_p^{(W)}(j)$, and $J_p^{(W)}(j+1)$ are each non-empty cyclic intervals of $\{1, \ldots, n\}$ which partition $\{1, \ldots, n\}$ and occur in the given cyclic order.
@@
 \[l, l+1, \ldots ,j \in J^{(V)}_q(j) \text{ (if $l$ exists) and }  j+1 \in J^{(V)}_q(j+1).\]
-Note that $j+2 \not\in J^{(V)}_q(j+1)$ by Lemma~\ref{lem last vert}, so $J^{(V)}_q(j+1) = \{j+1\}$ and $j+2 \in J^{(V)}_q(i)$ by the induction hypothesis.
+Note that $j+2 \not\in J^{(V)}_q(j+1)$ by Lemma~\ref{lem no fourth vertex}, so $J^{(V)}_q(j+1) = \{j+1\}$ and $j+2 \in J^{(V)}_q(i)$ by the induction hypothesis.
 Thus there exist vertices $d,e \in [j+2,i+1]$ with $d <e$, such that
@@
 
+We need one more lemma before we can prove that Algorithm~\ref{alg:put GN on WLD} does in fact give the Grassmann necklace of the positroid associated to $W$.
+
+\begin{lem}\label{lem basis as perm}
+Let $W = (\cP,[n])$ be an admissible Wilson loop diagram and let $M(W)$ be its associated matroid.
+A subset $J \subseteq [n]$ is an independent set of $M(W)$ if and only if there exists an injective set map $f : J \rightarrow \cP$ with the property that for each $s\in S$ we have $s \in V(f(s))$.
+\end{lem}
+
+One of the most important uses of this lemma is for bases.
+The lemma says that a subset $J$ of $[n]$ is a basis of $M(W)$ if and only if there is a set bijection between $J$ and $\cP$ with the property that for each $j\in J$ the propagator associated to $j$ under the bijection is supported on vertex $j$.
+
+\begin{proof}
+  Because the nonzero entries of $C(W)$ are independent indeterminants,
+  $J$ is an independent set is if and only if there is some choice of $|J|$ nonzero entries of $C(W)$ one in each row associated to an element of $J$ and each in different columns.
+
+  Each entry in $C(W)$ identifies a propagator by the row of the entry and a vertex by the column of the entry.  The entry is nonzero if and only if the propagator is supported on that vertex.
+
+  Consequently, a choice of $|J|$ nonzero entries of $C(W)$ one in each row associated to an element of $J$ and each in different columns is equivalent to an assignment of the propagators of $J$ to supporting vertices so that no two are assigned to the same vertex.
+Such an assignment of the propagators of $J$ to supporting vertices is exactly a map $f$ as described in the statment, hence proving the result.
+\end{proof}
+
 \begin{prop}\label{res:alg gives GN}

### 2018-12-12 General WLD combinatorics.tex
minor typo fix

@@
 Let $W = (\cP,[n])$ be an admissible Wilson loop diagram and let $M(W)$ be its associated matroid.
-A subset $J \subseteq [n]$ is an independent set of $M(W)$ if and only if there exists an injective set map $f : J \rightarrow \cP$ with the property that for each $s\in S$ we have $s \in V(f(s))$.
+A subset $J \subseteq [n]$ is an independent set of $M(W)$ if and only if there exists an injective set map $f : J \rightarrow \cP$ with the property that for each $j\in J$ we have $j \in V(f(j))$.
 \end{lem}

### 2018-12-12 General WLD combinatorics.tex
corrections based on Sian's comments and a def of the correspondence between triangulated pieces and subdiagrams

@@
 
-\begin{eg} \label{eg: unique decomposition} For the Wilson loop diagrams and polygon partitions in Example \ref{WLDtopolygonpartition}, the vertex sets $\{1, 2, 3,4\}$ and $\{5, 6, 7, 8\}$ are maximal triangulated pieces for both $\tau(W_1)$ and $\tau(W_3)$.
+\begin{eg} \label{eg: unique decomposition} For the Wilson loop diagrams and polygon partitions in Example \ref{WLDtopolygonpartition}, the vertex sets $\{1, 2, 3,4\}$ and $\{5, 6, 7, 8\}$ give maximal triangulated pieces for both $\tau(W_1)$ and $\tau(W_3)$.
 The vertex set $\{4,5, 8, 1\}$ is not a triangulation in either polygon partition.
@@
 
+Every triangulated piece $t$ of an admissible Wilson loop diagram $W$ corresponds to a subdiagram of $W$ by taking the set of propagators $P$ corresponding to edges of $t$ and then taking the subdiagram $(P, V(P))$.
+Conversely, given a subdiagram $(P, V(P))$ of $W$ we can obtain a subgraph of $\tau(W)$ as follows:
+\begin{itemize}
+\item The vertex set of the subgraph is
+  \begin{itemize}
+  \item the vertices of $\tau(W)$ corresponding to edges on which propagators of $P$ are supported
+  \item along with any other vertices of $\tau(W)$ for which both neighbours are as described in the previous point.
+  \end{itemize}
+\item The edge set of the subgraph is
+  \begin{itemize}
+  \item the edges of $\tau(W)$ corresponding to propagators of $P$
+  \item along with the outer edges of $\tau(W)$ for which both their end points are in the vertex set
+  \end{itemize}
+\end{itemize}
+Note that the subgraph only depends on $P$, not the vertex set of the subdiagram, but it is not the subgraph of $\tau(W)$ consisting only of edges corresponding to propagators of $P$.
+
 \begin{lem}\label{lem triang to exact}
-  Let $W$ be an admissible Wilson loop diagram and $\tau(W)$ its polygon partition.  The triangulated pieces of $\tau(W)$ correspond to the exact subdiagrams of $W$.
+  Let $W$ be an admissible Wilson loop diagram and $\tau(W)$ its polygon partition.
+The triangulated pieces of $\tau(W)$ correspond to the exact subdiagrams of $W$ using the correspondence described above.
 \end{lem}
@@
 Suppose $|P|=1$.
-Then $(P, V(P))$ is a trivially exact subdiagram.
-In this case $t$ is an edge internal to $\tau(W)$.
-The exactness condition on $(P, V(P))$ says that the four supporting vertices of the element of $P$ are distinct and no other propagators are supported on those vertices.
-Translating this to $\tau(W)$ gives that the vertices which are the ends of $t$ are separated by at least two vertices along the cycle and no other internal edges connect to the ends of $t$.
-This implies that $t$ is a trivial triangulation.
+Let $p$ be the element of $P$.
+The exactness condition on $(P, V(P))$ says that the four supporting vertices of $p$ are distinct.
+If the support of $p$ is four consecutive vertices, then the ends of the edge corresponding to $p$ in $\tau(W)$ have a common neighbour and so $t$ is a single triangle, hence a triangulated piece.
+If the support of $p$ is not four consecutive vertices, then the vertices which are the ends of $t$ are separated by at least two vertices along the cycle.
+This implies that $t$ is a trivial triangulated piece.
 
 Now suppose $|P|>1$.  Let $j=|P|$, $m=|V(P)|$, and 
-suppose that the set $V(P)$ defines $c$ disjoint cyclic intervals of $[n]$. Then $t$ has $m-c$ vertices.  If $t$ were a triangulated component, $t$ would have $j -c$ internal edges.
+suppose that the set $V(P)$ defines $c$ disjoint cyclic intervals of $[n]$. Then $t$ has $m-c$ vertices.  If $t$ were a triangulation, $t$ would have $j -c$ internal edges.
 
@@
 Therefore, of the $j$ edges of $t$ that come from propagators, $j-c$ are internal to the connected component.
-Therefore, $t$ is a triangulation.
+Therefore, $t$ is a triangulated piece.
 

### 2018-12-12 General WLD combinatorics.tex
recovered lost changes
Made changes to section 1 that had been lost.

@@
 \newcommand{\Dom}{\textrm{Dom}}
-\newcommand{\detzr}[1] {\langle (\cZ_*^\mu|V_p)^{#1} \rangle}
+\newcommand{\detzr}[1] {\langle (\cZ_*^\mu|V(p))^{#1} \rangle}
 \newcommand{\II}{\mathcal{I}}
@@
 \begin{dfn}\label{WLdfn}
-A Wilson loop diagram is given by the following data: a cyclicly ordered set $V$, along with a choice of first vertex, and $k$ pairs $\{p_r = (i_r, j_r)\}_{r=1}^k$ ordered such that $i_r +1 < j_r$.
+A Wilson loop diagram is given by the following data: a cyclicly ordered set $V$, along with a choice of first vertex (labeled $1$), and $k$ pairs, called propagators, written $\{p_r = (i_r, j_r)\}_{r=1}^k$ with labels ordered such that $i_r +1 < j_r$ relative to the fisrt vertex.
 \end{dfn}
 
-We depict this data as a convex polygon, with vertices labeled by $V$ (preserving the cyclic ordering), and $k$ wavy lines in the interior of the diagrams.
-We depict the choice of first vertex on $V$ by a $\bullet$.
-\note{If we look at the pictures we have later (at least some of them), we don't do that.
-Instead all the vertices are $\bullet$.} Note that the polygon gives the verices of $W$ a cyclic ordering, which the choice of first vertex gives it a compatible linear order.
-Both the cyclic and the linear order become the correct perspective at various points in this paper.
-The pair $p_r$ defines a wavy line from the $i_r^{th}$ edge (between $i_r$ and $i_r+1$) and the $j_r^{th}$ edge.
-These are called propagators.
+We depict this data as a circle with marked points, called vertices.
+The vertices are labeled by $V$ (preserving the cyclic ordering).
+The arc between consecutive vertices are called edges.
+There are $k$ wavy lines in the interior of the diagram, depicting the proagators, with endpoints on the edges.
+A propagator, $p =(i,j)$ has one endpoint on the edge between the vertex labeled $i$ and $i+1$ and another endpoint on the edge defined by $j$ and $j+1$.
 The condition on $i_r$ and $j_r$ means that the propagator does not go between adjacent edges.
@@
 
+Note that the marked circle gives the vertices of $W$ a cyclic ordering.
+The choice of first vertex gives it a compatible linear order.
+Both the cyclic and the linear order become the correct perspective at various points in this paper.
+
 Often we take $V$ to be $[n]$, the cyclically ordered set of integers, $1 \ldots n$.
-In this case, we write $W = (\cP, n)$.
+In this case, we write $W = (\cP, [n])$.
 We introduce some notation to speak of vertices supporting a propagator, and the set of propagators supported on a vertex set.
@@
 \begin{dfn} \label{VPropdfn}
-Let $W = (\cP, n)$.
+Let $W = (\cP, [n])$.
 \begin{enumerate}
-\item For $p \in \cP$, let $V_p = \{i_p, i_p+1, j_p, j_p+1\}$ be the set of vertices supporting $p$. Then, for $P \subseteq \cP$, the set $V_P = \cup_{p \in P} V_p$ is the vertex support of $P$.
-\item For $V \subseteq [n]$, write $\Prop(V) = \{ p \in \cP | V_p \cap V \neq \emptyset \} $.
+\item For $p \in \cP$, let $V(p) = \{i_p, i_p+1, j_p, j_p+1\}$ be the set of vertices supporting $p$. Then, for $P \subseteq \cP$, the set $V(P) = \cup_{p \in P} V(p)$ is the vertex support of $P$.
+\item For $V \subseteq [n]$, write $\Prop(V) = \{ p \in \cP | V(p) \cap V \neq \emptyset \} $.
 \item For $P \subseteq \cP$, define $F(P) = V(P^c)^c$ to be the set of vertices in $[n]$ that only support propagators in the set $P$.
@@
 
+Note that $F(\emptyset)$ is the set of vertices that are not in the support of any propagators. \sanote{did we settle on a term here? I'd like to make this a definition}
+
 It is sometimes useful to discuss propagators in terms of the edges supporting them, rather than the vertices.
@@
 \item $|V| \geq |\cP| + 4$
-\item There does not exists a set of propagators, $P \subset \cP$ such that $|V(P)| < |P| + 3$.
-\item There does not exist a pair of propagators, $p, q \subset \cP$ such that $i_p < i_q < j_p <j_q$.
+\item There does not exists a set of propagators, $P \subseteq \cP$ such that $|V(P)| < |P| + 3$.
+\item There does not exist a pair of propagators, $p, q \subseteq \cP$ such that $i_p < i_q < j_p <j_q$.
 \end{enumerate}
@@
 The third ensures that ensures that no propagators cross in the interior of the diagram.
-In other words, a Wilson loop diagram, $(\cP, n)$ is admissible if and only if $n > \cP +4$, and has neither crossing propagators nor any pairs of propagators that start and end on the same pair of non-adjacent edges.
+In other words, a Wilson loop diagram, $(\cP, [n])$ is admissible if and only if $n > \cP +4$, and has neither crossing propagators nor any pairs of propagators that start and end on the same pair of non-adjacent edges.
 
@@
 \begin{dfn} \label{subdiagramdfn}
-Let $W = (\cP, n)$ be an admissible Wilson loop diagram. A subdiagram of $W$ is defined by a a subset of propagators of $W$. For $P \subset \cP$, write $W|_P = (P, V(P))$.
+Let $W = (\cP, [n])$ be an admissible Wilson loop diagram.
+The weakly admissible diagram, $W'$ is a subdiagram of $W$, written $W' \subseteq W$, if \bas W' = (P, V); \quad P \subseteq \cP ; \quad V(P) \subseteq V \subseteq [n]\;.\eas
 \end{dfn}
-\note{Later I will also want a different kind of subobject, one with a subset of the propagators but where the vertex set contains $V(P)$ but may be larger (the most important instance being when it is $[n]$.)  This kind of subobject doesn't need a particular name, nor does it need to be defined up here, but I wanted to mention it so we have it in mind.}
-
-Note that a subdiagram of an admissible diagram need not be admissible. In particular, the condition $|V(P)| > |P| +4$ need not hold.
 
@@
 \begin{dfn}\label{equivdfn} 
-There is an equivalence relationship on the set of admissible Wilson loops diagrams given by the transititve closure the following binary relation: $W = (\cP, n) \sim W'= (\cP', n)$ if
+There is an equivalence relationship on the set of admissible Wilson loops diagrams given by the transititve closure the following binary relation: $W = (\cP, [n]) \sim W'= (\cP', n)$ if
 \begin{enumerate}
@@
 
-Each Wilson loop diagram, $W = (\cP, n)$ with $|\cP| = k$ is associated to a $k \times n$ matrix with non-zero real variable entries, called $C(W)$:
+Each Wilson loop diagram, $W = (\cP, [n])$ with $|\cP| = k$ is associated to a $k \times n$ matrix with non-zero real variable entries, called $C(W)$:
 
@@
 \begin{dfn}\label{def R(W)}
-For $W = (\cP, n)$, $R(W) = \prod_{e=1}^n R_e$, with $R_e$ defined by the propagators ending on it.
+For $W = (\cP, [n])$, $R(W) = \prod_{e=1}^n R_e$, with $R_e$ defined by the propagators ending on it.
 For any edge $e$ of $W$, order the propagators incident on $e$ as $\{p_1 \ldots p_r\}$, ordered such that $p_1$ is closest to the vertex $e$, $p_r$ closest to $e+1$, and $p_i$ is closer to $e$ than $p_{i+1}$.
@@
 
-Finally, we describe several important types of matroid.
+Finally, we describe several important types of matroids.
 A matroid of rank $k$ with a ground set of size $n$ is called {\em realizable} if there exists some $A \in Gr(k,n)$ whose non-zero $k\times k$ minors are exactly those with columns indexed by elements of $\cB$.
@@
 
-\begin{thm} \label{thm WLD defines matroid} \cite[Theorem 3.6]{wilsonloop} Any admissible Wilson loop diagram $W =(\cP, n)$ defines a matroid $M(W)$ with ground set $[n]$.
+\begin{thm} \label{thm WLD defines matroid} \cite[Theorem 3.6]{wilsonloop} Any admissible Wilson loop diagram $W =(\cP, [n])$ defines a matroid $M(W)$ with ground set $[n]$.
 The independent sets are exactly those subsets $V \subseteq [n]$ such that $\nexists U\subseteq V$ satisfying $|\Prop(U)| < |U|$.
@@
 \item If $C \subseteq [n]$ is a cycle, then $\rk(C) = |Prop(C)|$.
-\item If $[n]$ can be partitioned into at least two non-empty sets, each of which support different sets of propagators, \bas [n] = \cup_i V(P_i) \quad \textrm{s.t.} \quad \cup P_i = \cP; \quad  P_i \cap P_j = \emptyset \;, \eas the the matroid $M(W)$ is seperable, \bas M(W) = \bigoplus_i M(P_i, V(P_i)) \;.\eas \note{Closest reference I could find for this was Theorem 3.23 of Agarwala/Amit, which relates to $F(P_i)$ instead of $V(P_i)$; check if there's a better reference?}
+\item If $[n]$ can be partitioned into at least two non-empty sets, each of which support different sets of propagators that form a partition of the propagotor set, \bas [n] = \sqcup_i V(P_i) \quad \textrm{s.t.} \quad \sqcup P_i = \cP; \quad V(P_i) \cap V(P_j) = \emptyset; \quad  P_i \cap P_j = \emptyset \;, \eas then the matroid $M(W)$ is seperable, \bas M(W) = \bigoplus_i M(P_i, V(P_i)) \;.\eas
 \end{enumerate}
@@
 (2) is \cite[Lemma 3.27]{wilsonloop}.
-(3) is also in \cite[Lemma FIND]{wilsonloop}.
+(3) is a direct consequence of \cite[Lemma 3.20]{wilsonloop} and the fact that $F(P_1)^c = V(P_1^c)$
 \end{proof}
@@
 \begin{dfn}
-  Let $W = (\cP, n)$ be an admissible Wilson loop diagram.  The \emph{polygon partition} associated to $W$, denoted $\tau(W)$, is defined as follows.
+  Let $W = (\cP, [n])$ be an admissible Wilson loop diagram.  The \emph{polygon partition} associated to $W$, denoted $\tau(W)$, is defined as follows.
   \begin{itemize}
@@
 \begin{lem}\label{tausimpleplanarlem}
-If $W = (\cP, n)$ is an admissible Wilson loop diagram, then $\tau(W)$ is a simple planar graph whose outer face is a cycle.
+If $W = (\cP, [n])$ is an admissible Wilson loop diagram, then $\tau(W)$ is a simple planar graph whose outer face is a cycle.
 It is embedded such that the vertices all lie on this infinite face\footnote{That is, it is an \emph{outerplanar} graph}.
@@
 
-Conversely, suppose we have an exact subdiagram $(P, V(P))$ of $W = (\cP, n)$ supported on $|V(P)| = |P|+3$ vertices, and let $t$ be the subgraph of $\tau(W)$ corresponding to $(P,V(P))$.
+Conversely, suppose we have an exact subdiagram $(P, V(P))$ of $W = (\cP, [n])$ supported on $|V(P)| = |P|+3$ vertices, and let $t$ be the subgraph of $\tau(W)$ corresponding to $(P,V(P))$.
 
@@
 % \begin{dfn} \label{restrictiondfn}
-% For $W = (\cP, n)$, the restricted diagram, $W|_V$ is the matroid defined by only looking at the vertices $V \subset [n]$.
+% For $W = (\cP, [n])$, the restricted diagram, $W|_V$ is the matroid defined by only looking at the vertices $V \subset [n]$.
 % \end{dfn}
@@
 \begin{algorithm}\label{alg:put GN on WLD}
-Let $W = (\cP, n)$ be an admissible Wilson loop diagram. This gives an algorithm for calculating the set $I_a$, for $a \in [n]$.
+Let $W = (\cP, [n])$ be an admissible Wilson loop diagram. This gives an algorithm for calculating the set $I_a$, for $a \in [n]$.
 
@@
 \begin{dfn}\label{def I_i as a function}
-Let $W = (\cP, n)$ be an admissible Wilson loop diagram. For each $a \in [n]$, define a function $I_a : \cP \longrightarrow [n]$ by
+Let $W = (\cP, [n])$ be an admissible Wilson loop diagram. For each $a \in [n]$, define a function $I_a : \cP \longrightarrow [n]$ by
 \[I_a(p) := \text{the vertex label that $p$ contributes to $I_a$ in Algorithm~\ref{alg:put GN on WLD},}\]
@@
 %\begin{lem}\label{protecting lem}
-%Let $W = (\cP, n)$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$, and $a \in [n]$ be a vertex.
+%Let $W = (\cP, [n])$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$, and $a \in [n]$ be a vertex.
 For $v \in \{i,j\}$, if $P_v(p) \neq \emptyset$, write $P_v(p) = \{s_1 \ldots s_r, t_2, \ldots t_r\}$ as above.
@@
 %\begin{cor} \label{protecting cor}
-%Let $W = (\cP, n)$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$.
+%Let $W = (\cP, [n])$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$.
 Picking a $v \in \{i, j\}$ write $p = (i_p, j_p)$ with $i_p <_{v+1} j_p$.
@@
 %\begin{lem} \label{protect conv lem}
-%For $W = (\cP, n)$, $p = (i,j)$, and $v \in \{i, j\}$ and $ a \in [n]$ a vertex of $W$, if $v$ (resp.
-$v+1$) is the first vertex of $V_p$ in the $<_a$ order such that $P_v$ (resp.
+%For $W = (\cP, [n])$, $p = (i,j)$, and $v \in \{i, j\}$ and $ a \in [n]$ a vertex of $W$, if $v$ (resp.
+$v+1$) is the first vertex of $V(p)$ in the $<_a$ order such that $P_v$ (resp.
 neither $P_v$ nor $P_{v+1}$) does not exist, then $p$ contributes $v$ (resp.
@@
 %\begin{prop}\label{res:alg k labels}
-%If $W = (\cP, n)$ is an admissible Wilson loop diagram with $|\cP| = k$, then Algorithm~\ref{alg:put GN on WLD} puts exactly $k$ distinct labels on each edge.
+%If $W = (\cP, [n])$ is an admissible Wilson loop diagram with $|\cP| = k$, then Algorithm~\ref{alg:put GN on WLD} puts exactly $k$ distinct labels on each edge.
 %\end{prop}
@@
 %
-%By switching the roles of $i$ and $j$, we see that for every element of $V_p$, there is a non-empty cyclic interval such that $p$ contributes $v$ to all $I_{a}$ for in said interval.
+%By switching the roles of $i$ and $j$, we see that for every element of $V(p)$, there is a non-empty cyclic interval such that $p$ contributes $v$ to all $I_{a}$ for in said interval.
 

### 2018-12-13 General WLD combinatorics.tex
Susama's changes

@@
 
+Note that this means that the set $F(\emptyset)$ is the maximal subset of vertices of $W$ of rank $0$.
+That is, it is the unique flat of rank $0$ in $M(W)$.
+\sanote{I'm sprinkling comments about $F(\emptyset)$ throughout until we can come up with a better name than unsupportive vertices.}
+
 \subsection{Polygon partitions of Wilson loop diagrams}
@@
 Since the vertices of $\tau(W)$ are labeled by the edges of $W$, which are cyclically ordered, this gives an ordering to the vertices.
-Furthermore, since the outer polygon of $W$ is a cycle, the outer face of $\tau(W)$ is also a cycle.
+Furthermore, since the outer \hlfix{circle of $W$ is a cycle}{sounds awkward in the new notation}, the outer face of $\tau(W)$ is also a cycle.
 Since $W$ is admissible, no pairs of propagators cross.
@@
 The vertex set $\{4,5, 8, 1\}$ is not a triangulation in either polygon partition.
-\note{Put a picture of a dual tree.
-Make a comment that the embedding is required to obtain uniqueness of the dual}
 \end{eg}
@@
 
-By \emph{splitting} a vertex $v$ we will mean replacing $v$ by new vertice $v_1, v_2,\ldots, v_{\text{deg}(v)}$ such that each $v_i$ as exactly one neighbour and the union of the neighbourhoods of the $v_i$ is the neighbourhood of $v$.
+By \emph{splitting} a vertex $v$ we will mean replacing $v$ by new vertice $v_1, v_2,\ldots, v_{\text{deg}(v)}$ such that each $v_i$ has exactly one neighbour and the union of the \hlfix{neighbourhoods}{neigbors?
+Or a separate definition of neigborhood?} of the $v_i$ is the neighbourhood of $v$.
 
@@
 If the splitting were not maximal, then one could add a triangle to a connected component of the splitting, but this would imply that that splitting happened at a valence $3$ vertex.
+
+\bas 
+\begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
+	\begin{scope}
+	\drawpolypart{8}{1.5}
+    \drawnumbersshift
+    \drawchord{1}{4}
+    \drawchord{1}{3}
+    \drawchord{5}{8}
+    \drawchord{6}{8}
+ \draw (0,0) node {$\bullet$};
+\draw (-1,.2) node {$\bullet$};	
+\draw (-.5,1.1) node {$\bullet$};
+\draw (.8,-.3) node {$\bullet$};	
+\draw (1.1,-.5) node {$\bullet$};
+\draw(1.1,-.5) -- (.8,-.3) --(0,0)--(-1,.2) -- (-.5,1.1);
+\foreach \i in {1,2,...,8} {
+      \draw (45*\i:2) node {$\bullet$};
+    }
+\draw (45*1:2) --(0,0) -- (45*5:2);
+\draw (45*6:2) -- (.8,-.3);
+\draw (45*8:2) -- (1.1,-.5) -- (45*7:2);
+\draw (45*2:2) -- (-.5,1.1) -- (45*3:2);
+\draw (45*4:2) -- (-1,.2);
+	\end{scope}
+	\end{tikzpicture} \rightarrow 
+\begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
+	\begin{scope}
+	\drawpolypart{8}{1.5}
+    \drawnumbersshift
+    \drawchord{1}{4}
+    \drawchord{1}{3}
+    \drawchord{5}{8}
+    \drawchord{6}{8}
+ \draw (.1,.1) node {$\bullet$};
+\draw (.1,-.1) node {$\bullet$};
+\draw (-.1,-.1) node {$\bullet$};
+\draw (-.1,.1) node {$\bullet$};
+\draw (-1,.2) node {$\bullet$};	
+\draw (-.5,1.1) node {$\bullet$};
+\draw (.8,-.3) node {$\bullet$};	
+\draw (1.1,-.5) node {$\bullet$};
+\draw(1.1,-.5) -- (.8,-.3) --(.1,-.1); 
+\draw (-.1, .1) --(-1,.2) -- (-.5,1.1);
+\foreach \i in {1,2,...,8} {
+      \draw (45*\i:2) node {$\bullet$};
+    }
+\draw (45*1:2) --(.1,.1);
+\draw (-.1, -.1) -- (45*5:2);
+\draw (45*6:2) -- (.8,-.3);
+\draw (45*8:2) -- (1.1,-.5) -- (45*7:2);
+\draw (45*2:2) -- (-.5,1.1) -- (45*3:2);
+\draw (45*4:2) -- (-1,.2);
+	\end{scope}
+	\end{tikzpicture}
+\eas
 
@@
 
+We need one more lemma before we can prove that Algorithm~\ref{alg:put GN on WLD} does in fact give the Grassmann necklace of the positroid associated to $W$.
+
+\begin{lem}\label{lem basis as perm}
+Let $W = (\cP,[n])$ be an admissible Wilson loop diagram and let $M(W)$ be its associated matroid.
+A subset $J \subseteq [n]$ is an independent set of $M(W)$ if and only if there exists an injective set map $f : J \rightarrow \cP$ with the property that for each $j\in J$ we have $j \in V(f(j))$.
+\end{lem}
+
+One of the most important uses of this lemma is for bases.
+The lemma says that a subset $J$ of $[n]$ is a basis of $M(W)$ if and only if there is a set bijection between $J$ and $\cP$ with the property that for each $j\in J$ the propagator associated to $j$ under the bijection is supported on vertex $j$.
+
+\begin{proof}
+  Because the nonzero entries of $C(W)$ are independent indeterminants,
+  $J$ is an independent set is if and only if there is some choice of $|J|$ nonzero entries of $C(W)$ one in each row associated to an element of $J$ and each in different columns.
+
+  Each entry in $C(W)$ identifies a propagator by the row of the entry and a vertex by the column of the entry.  The entry is nonzero if and only if the propagator is supported on that vertex.
+
+  Consequently, a choice of $|J|$ nonzero entries of $C(W)$ one in each row associated to an element of $J$ and each in different columns is equivalent to an assignment of the propagators of $J$ to supporting vertices so that no two are assigned to the same vertex.
+Such an assignment of the propagators of $J$ to supporting vertices is exactly a map $f$ as described in the statment, hence proving the result.
+\end{proof}
+
 \begin{prop}\label{res:alg gives GN}

### 2018-12-13 General WLD combinatorics.tex
added a def of neighbourhood in the graph theory sense in a footnote

@@
 
-By \emph{splitting} a vertex $v$ we will mean replacing $v$ by new vertice $v_1, v_2,\ldots, v_{\text{deg}(v)}$ such that each $v_i$ has exactly one neighbour and the union of the \hlfix{neighbourhoods}{neigbors?
-Or a separate definition of neigborhood?} of the $v_i$ is the neighbourhood of $v$.
+By \emph{splitting} a vertex $v$ we will mean replacing $v$ by new vertice $v_1, v_2,\ldots, v_{\text{deg}(v)}$ such that each $v_i$ has exactly one neighbour and the union of the of the $v_i$ is the neighbourhood\footnote{The neighbourhood of a vertex is the set of adjacent vertices} of $v$.
 

### 2018-12-13 General WLD combinatorics.tex
removed a doubling (maybe from the bad merge) and started cleaning up 3.3

@@
 
-We need one more lemma before we can prove that Algorithm~\ref{alg:put GN on WLD} does in fact give the Grassmann necklace of the positroid associated to $W$.
-
-\begin{lem}\label{lem basis as perm}
-Let $W = (\cP,[n])$ be an admissible Wilson loop diagram and let $M(W)$ be its associated matroid.
-A subset $J \subseteq [n]$ is an independent set of $M(W)$ if and only if there exists an injective set map $f : J \rightarrow \cP$ with the property that for each $j\in J$ we have $j \in V(f(j))$.
-\end{lem}
-
-One of the most important uses of this lemma is for bases.
-The lemma says that a subset $J$ of $[n]$ is a basis of $M(W)$ if and only if there is a set bijection between $J$ and $\cP$ with the property that for each $j\in J$ the propagator associated to $j$ under the bijection is supported on vertex $j$.
-
-\begin{proof}
-  Because the nonzero entries of $C(W)$ are independent indeterminants,
-  $J$ is an independent set is if and only if there is some choice of $|J|$ nonzero entries of $C(W)$ one in each row associated to an element of $J$ and each in different columns.
-
-  Each entry in $C(W)$ identifies a propagator by the row of the entry and a vertex by the column of the entry.  The entry is nonzero if and only if the propagator is supported on that vertex.
-
-  Consequently, a choice of $|J|$ nonzero entries of $C(W)$ one in each row associated to an element of $J$ and each in different columns is equivalent to an assignment of the propagators of $J$ to supporting vertices so that no two are assigned to the same vertex.
-Such an assignment of the propagators of $J$ to supporting vertices is exactly a map $f$ as described in the statment, hence proving the result.
-\end{proof}
-
 \begin{prop}\label{res:alg gives GN}
@@
 
-In \cite{reversingOh}, Agarwala and Fryer give an algorithm for passing from a Grassmann Necklace to a Le diagram.
+Agarwala and Marcott show that the dimension of the positroid cell defined by a Wilson loop diagram $(\cP, [n])$ has dimension $3|\cP|$.
+Their proof is geometric and elegant, but it is not easy to track the effect of a particular propagator.
+
+The dimension of a positroid cell is the same as the number of plusses in the associated Le diagram ***cite something***, and so with Algorithm~\ref{alg:put GN on WLD} along with the algorithm for passing from a Grassmann necklace to a Le diagram (reversing Oh's algorithm) described by some of us in \cite{reversingOh}, we can, at the cost of a bit of messy grunt work, give a different recursive proof of the $3|\cP|$-dimensionality that explicitly describes the changes in the positions of the plusses in the Le diagram.
+
+%In \cite{reversingOh}, Agarwala and Fryer give an algorithm for passing from a Grassmann Necklace to a Le diagram.
 We use this algorithm here to pass from a Wilson loop diagram to its associated Le diagram.
@@
 Maybe say something about Amplituhedra having $4k$ dimension, but this is not quite what we have, since we are ignoring one column.
-
-When I speak of a \emph{WLD}, I mean one which satisfies your density hypothesis and other standard hypotheses.
+%
+%When I speak of a \emph{WLD}, I mean one which satisfies your density hypothesis and other standard hypotheses.
 When I speak of a propagator \emph{contributing} a vertex to an element of the Gra\ss mann\footnote{I suppose it is a bit of an affectation to use an eszett when writing in English, and actually the eszett is kind of ugly in this font, but since I've started to I'll stick with it for now but you certainly shouldn't feel obliged to do it too.} necklace I mean that according to the rule you guys have to build the Gra\ss mann necklace from the diagram by starting at a vertex and taking the clockwise-most covering propagator which hasn't already been taken, when a propagator is taken then it is contributing that vertex.
 Also, I will be using your algorithm to convert the Gra\ss mann necklace into a Le diagram by non-intersecting paths.
-
-We need four lemmas from stuff you guys have already figured out.  The first one is a corollary of your lemma characterizing intervals contributed by each covered vertex of a
-propagator.
-
-The first lemma is Lemma~\ref{vertex cyclic int lem} and I moved it up to a previous section.
-
-The second lemma is the fact that we understand uncovered vertices.
+%
+%
+%We need four lemmas from stuff you guys have already figured out.  The first one is a corollary of your lemma characterizing intervals contributed by each covered vertex of a
+%propagator.
+%
+%The first lemma is Lemma~\ref{vertex cyclic int lem} and I moved it up to a previous section.
+%
+%The second lemma is the fact that we understand uncovered vertices.
 You probably see many ways to prove this from things you already know.
@@
 
+We need a number of lemmas, of roughly increasing degree of technicality.
+
 \begin{lem}\label{lem uncovered}
-  Let $D$ be a WLD with an uncovered vertex $i$.
-Let $C$ be $D$ with $i$ removed.
-Then the Le diagram of $D$ is the Le diagram of $C$ with an extra column of all $0$s inserted in the $|D|-i+1$th position from the left.
+  Let $W$ be an admissible Wilson loop diagram with $k$ propagators and with a vertex $i$ which supports no propagators.
+Let $V$ be $W$ with $i$ removed.
+Then the Le diagram of $W$ is the Le diagram of $V$ with an extra column of all $0$s inserted so as to be labelled $i$ on its bottom in the Oh labelling of the border of the shape of the Le diagram
 \end{lem}
 
-The third lemma is now lemma~\ref{lem sian}.
-
-Here is some old text: Actually the result I need is not exactly Sian's result and what I will actually use is her proof.
-Thus I will use notation and definitions (including length of a propagator and the specific $p_i$ and $q_i$ construction from the proof) from her note without further discussion.
-The result I will actually use will be that in place of the hypothesis that $D$ has all vertices covered by at least two propagators I have that all vertices are covered by at least 1 propagator and there are no propagators of length 3.
-
-The fourth lemma is that we can rotate or reflect without changing the number of plusses.  The best way to see this is probably geometrically so I leave that up to you.
+\note{I'm not sure how much I should assume here in terms of what the reader already knows}
+
+\begin{proof}
+  By Algorithm~\ref{alg:put GN on WLD} the Grassmann necklace of $W$ is obtained from the Grassmann necklace of $V$ by duplicating the $i$th element of the Grassmann necklace of $V$ (shifting indices as appropriate), and incrementing all indices greater than $i$ in each Grassmann necklace element.
+Formally, if $I_1^{(V)}, \ldots, I_{n-1}^{(V)}$ and $I_1^{(W)}, \ldots, I_n^{(W)}$ are the Grassmann necklaces of $V$ and $W$ respectively then
+  \[
+  I_j^{(W)} =
+  \begin{cases}
+    \{\ell \in I_j^{(V)} : \ell < i\} \cup \{\ell+1 \in I_j^{(V)} : \ell \geq i\} & \text{if $j\leq i$} \\
+    \{\ell \in I_{j-1}^{(V)} : \ell < i\} \cup \{\ell+1 \in I_{j-1}^{(V)} : \ell \geq i\} & \text{if $j > i$.}
+  \end{cases}
+  \]
+
+  Since $i$ does not appear in the Grassmann necklace of $W$, in particular it is not in the first element of the necklace, and so in the Oh labelling of the boundary of the partition shape for the Le diagram (inside the rectangle $(k, n-k)$), $i$ labels a horizontal edge or equivalently the bottom of a column of boxes.
+The shapes of the Le diagrams of $V$ and $W$ are the same except for the insertion of this column since the first Grassmann necklace elements are the same except for the incrementation of the indices $\geq i$ in the transition from the neccklace for $V$ to the necklace for $W$.
+
+  By the algorithm of \cite{reversingOh}, since $i$ never appears in the Grassmann necklace of $W$, the column labelled $i$ is filled with all $0$s.
+Otherwise the algorithm of \cite{reversingOh} behaves identically on $V$ and $W$ with the plusses for the incremented indices shifted one column to the left, thus skipping over column $i$ in the Le diagram for $W$.
+\end{proof}
+
+%The third lemma is now lemma~\ref{lem sian}.
+
+%The fourth lemma is that we can rotate or reflect without changing the number of plusses.  The best way to see this is probably geometrically so I leave that up to you.
 
 \begin{lem}\label{lem dihedral}
-  If two WLDs differ by a dihedral transformation then their Le diagrams have same number of plusses.
+  If two Wilson loop diagrams differ by a dihedral transformation then their Le diagrams have same number of plusses.
 \end{lem}
 
-Now we're ready to go.
-
-\subsubsection{Changes in Gra\ss mann necklaces for nice configurations}
+\note{Can I just cite something for this, or can one of you provide a quick geometric proof.  It would be a horrible mess to do by hand combinatorially}
+
+%\subsubsection{Changes in Gra\ss mann necklaces for nice configurations}
+
+\note{Karen got to here}
 

### 2018-12-14 General WLD combinatorics.tex
fixed the use of lem sian in the plus counting proof

@@
 
-\note{Karen got to here}
-
-Given a propagator $p$ in a WLD $D$, note that $p$ divides remaining propagators of $D$ into two sets depending on which side of $p$ they live.
+%Given a propagator $p$ in a WLD $D$, note that $p$ divides remaining propagators of $D$ into two sets depending on which side of $p$ they live.
 
 \begin{lem}\label{lem good p}
-  Let $D$ be a WLD with $n\geq 1$ propagators.  Then there is some dihedral transformation $D'$ of $D$ such that there is a propagator $p$ with the following properties.
+  Let $W$ be an admissible Wilson loop diagram with $n\geq 1$ propagators.
+Then there is some dihedral transformation $W'$ of $W$ such that there is a propagator $p$ of $W'$ with the following properties.
   \begin{itemize}
-  \item $p$ goes between the edge $i$, $i+1$ and the edge $n-1$, $n$ in $D'$.
-  \item $i+2, \ldots, n-2$ are not covered by any propagators in $D'$ (which is trivially true if $\{i+1, \ldots, n-2\}=\varnothing$).
-  \item Either $i+1$ in $D'$ is only covered by $p$, or $i+1$ is covered by exactly one other propagator $q$.
-  \item If we are in the second case above then $q$ goes between the edge $j$, $j+1$ and the edge $i$, $i+1$ and $j+2, \ldots, i-1$ are not covered by any propagators.
+  \item $p = (i, n-1)$ with no propagators inside it (that is $i+2, \ldots, n-2$ do not support any propagators in $W'$).
+  \item Either the edges $i$ in $W'$ only supports $p$ or the edge $i$ in $W'$ supports exactly one other propagator $q = (j ,i)$ with no other propagators inside $q$.
   \end{itemize}
@@
 \begin{proof}
-  Since $n\geq 1$ the dual tree of $D$ has at least two vertices and so has at least two leaves.
-Each edge going to a leaf of the dual tree corresponds to a propagator which has no other propagators on one side of it, so there is at least one such propagator in $D$.
-There are two cases to consider.
-
-  First suppose there is a propagator which has no other propagators on one side of it and for which one of its ends is on an edge with no other propagators.
-Let this propagator be $p$.
-Rotate and reflect $D$ as necessary so that the end of $p$ which does not share its edge comes first, then the side of $p$ with no other propagators, and then the other end of $p$ which is on edge $n-1$, $n$.
-Call this WLD $D'$.
-It is a straightforward check that the properties in the statement are satisfied with $i+1$ only covered by $p$.
-
-  Next suppose there is no propagator which has no other propagators on one side of it and for which one of its ends is on an edge with no other propagators.
-Let $C$ be $D$ with all uncovered vertices removed.
-Suppose $C$ contains two propagators one of length 2 and one of length 3 with the length 2 propagator on the small side of the length 3 propagator.
-Then we are in the case already considered because we can rotate and reflect $C$ so that these two propagators both have one end on the edge $|C|-1$,$|C|$, and have their other ends on the edge $|C|-2$, $|C|-3$ and the edge $|C|-3$, $|C|-4$, so taking the length 2 edge as $p$ we satisfy the properties of the statement, and this remains true in $D$.
-Thus we now assume this does not occur, so in particular every propagator of length 3 in $C$ has no other propagators on its small side.
-But then the middle vertex on this small side is uncovered contradicting the construction of $C$.
-Thus $C$ has no propagators of size 3.
-
-  The claim then is that in $C$ there must exist two propagators as in Lemma~\ref{lem sian}.
-The proof of the claim follows by Sian's proof.
-We do not have the hypothesis that all vertices are covered by at least two propagators, but this is only used in the proof of Lemma~\ref{lem sian} to force certain propagators (the $q_i$) to have length at least 4, so our this case we instead use that $C$ has no propagators of size $3$.
-
-  Now rotate and flip $C$ so that the two propagators as in Lemma~\ref{lem sian} cover $\{|C|-5, \ldots, |C|\}$ and let $p$ be the propagator covering $\{|C|-3, \ldots, |C|\}$ and let $q$ be the other one.
-Return to $D$ with a corresponding rotation and flip so that vertex $n$ in $D$ corresponds to vertex $|C|$ in $C$ and direction in the polygon is preserved.
-Let this dihedral transformation of $D$ be $D'$.
-Then the propagator $p$ satisfies the conditions of the statement with propagator $q$.
-\end{proof}
-
-Given a WLD $D$, $I_i^{D}$ denotes the $i$th Gra\ss mann necklace element corresponding to $D$.
+  Remove all vertices of $W$ which do not support any propagators to get a weakly admissible Wilson loop diagram $V$.
+Lemma~\ref{lem sian} applied to $V$ gives a length 2 propagator $p$ in $V$ for which either no other propagator is supported on one of the supporting edges of $p$ or there is a second length 2 propagator which is the only other propagator supported on one of the supporting edges of $p$.
+Figure~\ref{fig 3 cases} shows the possible cases, and the reader can easily check that in each case $p$ must be in one of the two situations described above.
+
+  By Lemma~\ref{lem dihedral} there is a dihedral transformation of $V$ satisfying the statement of the lemma with $p$ and $q$ both length 2.
+Restoring the vertices which do not support any propagators, we obtain a dihedral transformation $W'$ of $W$ as desired (with potentially longer lengths for $p$ and $q$).
+\end{proof}
+
+%Given an admissible Wilson loop diagram $W$, $I_i^{D}$ denotes the $i$th Grass mann necklace element corresponding to $W$.
+
+\note{Karen got to here, but there are no other uses of Lemma~\ref{lem sian}, so the rest just needs notational/style updates (unless we find problems)}
 

### 2018-12-18 General WLD combinatorics.tex
updated the notation in the proof of the number of plusses

@@
 
-Agarwala and Marcott show that the dimension of the positroid cell defined by a Wilson loop diagram $(\cP, [n])$ has dimension $3|\cP|$.
+Agarwala and Marcott show ***cite this*** that the dimension of the positroid cell defined by a Wilson loop diagram $(\cP, [n])$ has dimension $3|\cP|$.
 Their proof is geometric and elegant, but it is not easy to track the effect of a particular propagator.
@@
 
-\note{Karen got to here, but there are no other uses of Lemma~\ref{lem sian}, so the rest just needs notational/style updates (unless we find problems)}
-
 \begin{lem}\label{lem I}
-  Let $D$ be a WLD with $n\geq 1$ propagators and let $p$ be a propagator of $D$ so that the properties of Lemma~\ref{lem good p} are satisfied for $p$ in $D$ (that is $D$ is already appropriately transformed).
-Furthermore suppose that that $p$ has length $2$, as does $q$ if we are in the case of Lemma~\ref{lem good p} involving $q$.
-Let $C$ be $D$ with $p$ removed but no change in the vertices.
+  Let $W$ be an admissible Wilson loop diagram with $n\geq 1$ propagators.
+Suppose $p$ is a propagator of $W$ so that the properties of Lemma~\ref{lem good p} are satisfied for $p$ in $W$ and that $p$ has length $2$, as does $q$ if we are in the case of Lemma~\ref{lem good p} involving $q$.
+Let $V$ be $W$ with $p$ removed.
 Then
   \begin{align*}
-    I_1^{D} & = I_1^{C} \cup \{n-3\} \\
-    I_n^{D} & = I_1^{C} \cup \{n\} \\
-    I_{n-1}^{D} & = I_n^{C} \cup \{n-1\} \\
-    I_{n-2}^{D} & =
+    I_1^{W} & = I_1^{V} \cup \{n-3\} \\
+    I_n^{W} & = I_1^{V} \cup \{n\} \\
+    I_{n-1}^{W} & = I_n^{V} \cup \{n-1\} \\
+    I_{n-2}^{W} & =
     \begin{cases}
-      I_{n-2}^{C}\cup \{n-2\} & \text{if $n-2\not\in I_{n-2}^{C}$} \\
-      I_{n-2}^{C}\cup \{n-1\} & \text{if $n-2\in I_{n-2}^{C}$, $n-1\not\in I_{n-2}^{C}$} \\
-      (I_{n}^{C} - \{n-5\})\cup \{n-1,n-2\} & \text{if $n-1, n-2\in I_{n-2}^{C}$}
+      I_{n-2}^{V}\cup \{n-2\} & \text{if $n-2\not\in I_{n-2}^{V}$} \\
+      I_{n-2}^{V}\cup \{n-1\} & \text{if $n-2\in I_{n-2}^{V}$, $n-1\not\in I_{n-2}^{V}$} \\
+      (I_{n}^{V} - \{n-5\})\cup \{n-1,n-2\} & \text{if $n-1, n-2\in I_{n-2}^{V}$}
     \end{cases} \\
-    I_{k}^{D} & =
+    I_{k}^{W} & =
     \begin{cases}
-      I_k^{C}\cup \{n-3\} & \text{if $n-3 \not\in I_k^{C}$}\\
-      I_k^{C}\cup\{n-2\} & \text{if $n-3\in I_k^{C}$}
+      I_k^{V}\cup \{n-3\} & \text{if $n-3 \not\in I_k^{V}$}\\
+      I_k^{V}\cup\{n-2\} & \text{if $n-3\in I_k^{V}$}
     \end{cases} \\
@@
  \includegraphics{specialp}
-  \caption{The different possibilities for $D$ and $p$.  No other propagators can end in the fat red sections.  Other segments may have additional propagators ending in them.}\label{fig special p}
+  \caption{The different possibilities for $W$ and $p$.  No other propagators can end in the fat red sections.  Other segments may have additional propagators ending in them.}\label{fig special p}
 \end{figure}
@@
 
-  If $n-3\in I_1^{C}$ then $n-3\not\in I_1^{D}$, but then $p$ never contributes $n-3$ contradicting Lemma~\ref{vertex cyclic int lem}.
-Thus $n-3\not\in I_1^{C}$ and so in building the Gra\ss mann necklace when we get to vertex $n-3$ any other covering propagators of $C$ have already been taken and so we can now take $p$.
-Therefore $I_1^{D}= I_1^{C}\cup \{n-3\}$.
-
-  In constructing $I_n^{D}$, first for vertex $n$ we take propagator $p$.
-Then we are at vertex $1$ and precisely the propagators of $C$ remain.
-Thus the rest of the construction will give $I_1^{C}$.
-Therefore $I_n^{D} = I_1^{C}\cup \{n\}$.
-Essentially the same reasoning gives $I_{n-1}^{D} = I_n^{C}\cup \{n-1\}$.
-
-  Now consider $I_{n-2}^{D}$.
-If $n-2\not\in I_{n-2}^{C}$ then at vertex $n-2$ we take $p$ and this does not affect the rest of the construction of $I_{n-2}^{C}$, so $I_{n-2}^{D} = I_{n-2}^{C}\cup \{n-2\}$.
-An analogous argument takes care of the first case for $I_k^{D}$.
-Suppose $n-2\in I_{n-2}^{C}$ but $n-1\not\in I_{n-2}^{C}$.
-Then at vertex $n-2$ we take the same propagator in $C$ as in $D$ (in particular not $p$) because $p$ is the counterclockwisemost propagator covering $n-2$ and so the last propagator the algorithm would choose at this vertex, and by hypothesis $n-2$ is covered in $C$.
-Howver, $n-1$ is untaken in $I_{n-2}^{C}$ so at this vertex we will take $p$ in $I_{n-2}^{D}$.
-Following this, now that $p$ is out of the way without bumping any other propagators, the construction continues as in $I_{n-2}^{C}$.
-Therefore $I_{n-2}^{D} = I_{n-2}^{C}\cup \{n-1\}$.
-An analogous argument takes care of the case when we have $1<k<n-2$ and $n-3\in I_k^{C}$ but $n-2\not\in I_{k}^{C}$.
-Furthermore, either $n-2$ is uncovered in $C$ or only $q$ covers $n-2$ in $C$ and $q$ is also the only propagator covering $n-3$.
-Thus it is not possible for $n-3$ and $n-2$ to both be in $I_{k}^{C}$.
-This means that all the cases for $I_k^{D}$ are now proved.
-
-  The remaining case is when $n-1,n-2\in I_{n-2}^{C}$ for the construction of $I_{n-2}^{D}$.
+  If $n-3\in I_1^{V}$ then $n-3\not\in I_1^{W}$, but then $p$ never contributes $n-3$ contradicting Lemma~\ref{vertex cyclic int lem}.
+Thus $n-3\not\in I_1^{V}$ and so in building the Grassmann necklace when we get to vertex $n-3$ any other propagators of $V$ which are supported at $n-3$ have already been taken and so we take $p$.
+Therefore $I_1^{W}= I_1^{V}\cup \{n-3\}$.
+
+  In constructing $I_n^{W}$, first for vertex $n$ we take propagator $p$.
+Then we are at vertex $1$ and precisely the propagators of $V$ remain.
+Thus the rest of the construction will give $I_1^{V}$.
+Therefore $I_n^{W} = I_1^{V}\cup \{n\}$.
+Essentially the same reasoning gives $I_{n-1}^{W} = I_n^{V}\cup \{n-1\}$.
+
+  Now consider $I_{n-2}^{W}$.
+If $n-2\not\in I_{n-2}^{V}$ then at vertex $n-2$ we take $p$ and this does not affect the rest of the construction of $I_{n-2}^{V}$, so $I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-2\}$.
+An analogous argument takes care of the first case for $I_k^{W}$.
+Suppose $n-2\in I_{n-2}^{V}$ but $n-1\not\in I_{n-2}^{V}$.
+Then at vertex $n-2$ we take the same propagator in $V$ as in $W$ (in particular not $p$) because $p$ is the counterclockwisemost propagator supported on $n-2$ and so the last propagator the algorithm would choose at this vertex, and by hypothesis $n-2$ does support at least one propagator in $V$.
+However, $n-1$ is not yet taken in $I_{n-2}^{V}$, so at this vertex we will take $p$ in $I_{n-2}^{W}$.
+Following this the construction continues as in $I_{n-2}^{V}$.
+Therefore $I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-1\}$.
+An analogous argument takes care of the case when we have $1<k<n-2$ and $n-3\in I_k^{V}$ but $n-2\not\in I_{k}^{V}$.
+Furthermore, either $n-2$ supports no propagators in $V$ or only $q$ is supported by $n-2$ in $V$ and $q$ is also the only propagator supported by $n-3$.
+Thus it is not possible for $n-3$ and $n-2$ to both be in $I_{k}^{V}$.
+This means that all the cases for $I_k^{W}$ are now proved.
+
+  The remaining case is when $n-1,n-2\in I_{n-2}^{V}$ for the construction of $I_{n-2}^{W}$.
 We must then have a propagator $q$ as in the right hand side of Figure~\ref{fig special p}.
-In the construction of $I_{n-2}^{D}$, at vertex $n-2$ we take propagator $q$, as in $I_{n-2}^{C}$.
-Then at vertex $n-1$ we take propagator $p$ which is different from what occurs in $I_{n-2}^{C}$.
+In the construction of $I_{n-2}^{W}$, at vertex $n-2$ we take propagator $q$, as in $I_{n-2}^{V}$.
+Then at vertex $n-1$ we take propagator $p$ which is different from what occurs in $I_{n-2}^{V}$.
 Next we are at vertex $n$ and propagators $p$ and $q$ have been taken.
-Thus we are proceeding like $I_{n}^{C}$ but without propagator $q$.
-Fortunately we can determine explicitely how propagator $q$ contributes to $I_{n}^{C}$.
-By Lemma~\ref{vertex cyclic int lem} propagator $q$ contributes $n-5$ to $I_{n}^{C}$, and the only way this can occur is if all other propagators of $C$ were already taken by the time we got to vertex $n-5$.
-Therefore $I_{n-2}^{D} = (I_{n}^{C} - \{n-5\}) \cup \{n-1, n-2\}$.
+Thus we are proceeding like $I_{n}^{V}$ but without propagator $q$.
+Fortunately we can determine explicitely how propagator $q$ contributes to $I_{n}^{V}$.
+By Lemma~\ref{vertex cyclic int lem} propagator $q$ contributes $n-5$ to $I_{n}^{V}$, and the only way this can occur is if all other propagators of $V$ were already taken by the time we got to vertex $n-5$.
+Therefore $I_{n-2}^{W} = (I_{n}^{V} - \{n-5\}) \cup \{n-1, n-2\}$.
 This covers all cases and hence completes the proof.
@@
 
-\subsubsection{The number of plusses from Gra\ss mann necklaces in nice configurations}
-
 \begin{lem}\label{lem shape}
-  Let $C$ and $D$ be as in Lemma~\ref{lem I}.
-  The shape of the Le diagram of $C$ can be built from left to right of the following blocks: a rectangle with 3 columns, one more column of the same length, a partition shape with at most as many rows as the rectangle.
-  The shape of the Le diagram of $D$ can be built from left to right of the following blocks: a rectangle with 3 columns and one more row than the first rectangle of $C$, the same partition shape as in $C$.
+  Let $V$ and $W$ be as in Lemma~\ref{lem I}.
+  The shape of the Le diagram of $V$ can be built from left to right of the following blocks: a rectangle with 3 columns, one more column of the same length, a partition shape with at most as many rows as the rectangle.
+  The shape of the Le diagram of $W$ can be built from left to right of the following blocks: a rectangle with 3 columns and one more row than the first rectangle of $V$, the same partition shape as in $V$.
 \end{lem}
@@
   $I_1$ determines the shape of the Le diagram.
-  By Lemma~\ref{lem I}, $I_1^{D} = I_1^{C}\cup \{n-3\}$.
-This implies that the right hand boundary of the shape of $C$ is the same as the right hand boundary of the shape of $D$ except that $D$ has one additional row of 3 boxes while $C$ has an additional column in the $n-3$ position, that is a new column fourth from the left.
-\end{proof}
-
-The shapes of the Le diagrams of $C$ and $D$ are illustrated in Figure~\ref{fig Le}.
+  By Lemma~\ref{lem I}, $I_1^{W} = I_1^{V}\cup \{n-3\}$.
+This implies that the right hand boundary of the shape of $V$ is the same as the right hand boundary of the shape of $W$ except that $W$ has one additional row of 3 boxes while $V$ has an additional column in the $n-3$ position; that is, a new column fourth from the left.
+\end{proof}
+
+The shapes of the Le diagrams of $V$ and $W$ are illustrated in Figure~\ref{fig Le}.
 The pieces of the Le diagrams will be called $\mathcal{A}$ and $\mathcal{B}$ in what follows, as in the figure.
-Over the course of the next few lemmas we will prove that the plusses in the $\mathcal{B}$ parts of the Le diagrams of $C$ and $D$ are identical and the plusses in the $\mathcal{A}$ parts are very closely related.
-When we speak of a plus in the Le diagram of $D$ being the same as in $D$ or vice versa, we mean that the plus' position in $\mathcal{A}$ or $\mathcal{B}$ is the same.
+Over the course of the next few lemmas we will prove that the plusses in the $\mathcal{B}$ parts of the Le diagrams of $V$ and $W$ are identical and the plusses in the $\mathcal{A}$ parts are very closely related.
+When we speak of a plus in the Le diagram of $V$ being the same as in $W$ or vice versa, we mean that the plus' position in $\mathcal{A}$ or $\mathcal{B}$ is the same.
 Because of the column insertion the absolute indices may differ.
@@
   \includegraphics{Le_diagrams}
-  \caption{Le diagrams for $C$ (left) and $D$ (right).}\label{fig Le}
+  \caption{Le diagrams for $V$ (left) and $W$ (right).}\label{fig Le}
 \end{figure}
 
-Suppose we are following the Gra\ss mann necklace to Le diagram algorithm, and we put a plus in a box because of a path from vertical boundary edge $i$ to bottom boundary edge $j$.
+Suppose we are following the Grassmann necklace to Le diagram algorithm, and we put a plus in a box because of a path from vertical boundary edge $i$ to bottom boundary edge $j$.
 Then say this plus is in the $i\rightarrow j$ position.
@@
 \begin{lem}\label{lem n and n-1}
-  Let $C$ and $D$ be as in Lemma~\ref{lem I}.
-  The $I_n^{D}$ and $I_{n-1}^{D}$ elements of the Gra\ss mann necklace of $D$ give all the same plusses as $I_n^{C}$ along with plusses in the leftmost two boxes of the bottom row of the Le diagram of $D$.
+  Let $V$ and $W$ be as in Lemma~\ref{lem I}.
+  Then $I_n^{W}$ and $I_{n-1}^{W}$ give all the same plusses as $I_n^{V}$ along with plusses in the leftmost two boxes of the bottom row of the Le diagram of $W$.
 \end{lem}
@@
 \begin{proof}
-  By Lemma~\ref{lem I} $I_n^{D}= I_1^{C} \cup \{n\}$, so by the Gra\ss mann necklace to Le diagram algorithm the only plus this builds in the Le diagram of $D$ is  the one in the $n-3\rightarrow n$ position, that is in the leftmost box of the bottom row.
-
-  Also by Lemma~\ref{lem I} $I_{n-1}^{D} = I_n^{C} \cup \{n-1\}$.
-Additionally $n-3\not\in I_{n}^{C}$ since if it were then $n-3$ would also be in $I_1^{C}$ and hence propagator $p$ could not contribute $n-3$ to $I_1^{D}$ in contradiction to Lemma~\ref{vertex cyclic int lem}.
-Similarly $n-1, n-2\not\in I_n^{C}$.
-Thus the paths putting the plusses in from $I_n^{C}$ lie completely in $\mathcal{B}$ or take some vertical boundary edge $>n-3$ to $n$.
-Now view these paths in the Le diagram of $D$ and note that the path $n-3\rightarrow n-1$ is compatible, and so these paths together build the plusses that $I_{n-1}^{D}$ contributes.
-That is, we get all the plusses from $I_{n}^{C}$ along with a $n-3\rightarrow n-1$ plus, that is a plus in the second to the right box of the bottom row.
+  By Lemma~\ref{lem I} $I_n^{W}= I_1^{V} \cup \{n\}$, so by the Grassmann necklace to Le diagram algorithm the only plus this builds in the Le diagram of $W$ is  the one in the $n-3\rightarrow n$ position, that is in the leftmost box of the bottom row.
+
+  Also by Lemma~\ref{lem I} $I_{n-1}^{W} = I_n^{V} \cup \{n-1\}$.
+Additionally $n-3\not\in I_{n}^{V}$ since if it were then $n-3$ would also be in $I_1^{V}$ and hence propagator $p$ could not contribute $n-3$ to $I_1^{W}$ in contradiction to Lemma~\ref{vertex cyclic int lem}.
+Similarly $n-1, n-2\not\in I_n^{V}$.
+Thus the paths putting the plusses in from $I_n^{V}$ lie completely in $\mathcal{B}$ or take some vertical boundary edge $>n-3$ to $n$.
+Now view these paths in the Le diagram of $W$ and note that the path $n-3\rightarrow n-1$ is compatible, and so these paths together build the plusses that $I_{n-1}^{W}$ contributes.
+That is, we get all the plusses from $I_{n}^{V}$ along with a $n-3\rightarrow n-1$ plus, that is a plus in the second to the right box of the bottom row.
 \end{proof}
@@
 \begin{lem}\label{lem n-2 good}
-  Let $C$ and $D$ be as in Lemma~\ref{lem I} with $n-2 \not\in I_{n-2}^{C}$.
-
-  The $I_{n-2}^{D}$ element of the Gra\ss mann necklace of $D$ gives
+  Let $V$ and $W$ be as in Lemma~\ref{lem I} with $n-2 \not\in I_{n-2}^{V}$.
+
+  Then $I_{n-2}^{W}$ gives
   an $n-3\rightarrow n-2$ plus and
-  all the $I_{n-1}^{C}=I_{n-2}^{C}$ plusses.
+  all the $I_{n-1}^{V}=I_{n-2}^{V}$ plusses.
 \end{lem}
@@
 \begin{proof}
-  If $n-2\not\in I_{n-2}^{C}$ then $I_{n-1}^{C}=I_{n-2}^{C}$ and by Lemma~\ref{lem I} $I_{n-2}^{D} = I_{n-1}^{C} \cup \{n-2\}$.
-Note that $n-3\not\in I_{n-2}^{C}$ by Lemma~\ref{vertex cyclic int lem}.
-Therefore the paths for $I_{n-2}^{D}$ are the paths for $I_{n-1}^{C}$ along with the $n-3\rightarrow n-2$ path.
+  If $n-2\not\in I_{n-2}^{V}$ then $I_{n-1}^{V}=I_{n-2}^{V}$ and by Lemma~\ref{lem I} $I_{n-2}^{W} = I_{n-1}^{V} \cup \{n-2\}$.
+Note that $n-3\not\in I_{n-2}^{V}$ by Lemma~\ref{vertex cyclic int lem}.
+Therefore the paths for $I_{n-2}^{W}$ are the paths for $I_{n-1}^{V}$ along with the $n-3\rightarrow n-2$ path.
 This gives the statement of the lemma.
@@
 \begin{lem}\label{lem n-2 bad}
-  Let $C$ and $D$ be as in Lemma~\ref{lem I} with $n-2,n-1 \in I_{n-2}^{C}$.
-
-  The $I_{n-2}^{D}$ and $I_{n-3}^{D}$ elements of the Gra\ss mann necklace of $D$ gives the following plusses:
+  Let $V$ and $W$ be as in Lemma~\ref{lem I} with $n-2,n-1 \in I_{n-2}^{V}$.
+
+  Then $I_{n-2}^{W}$ and $I_{n-3}^{W}$ give the following plusses:
   \begin{itemize}
   \item An $n-3\rightarrow n-2$ plus and an $n-5\rightarrow n-1$ plus.
-  \item All the $I_{n-1}^{C}$ plusses.
-  \item $I_{n-2}^{C}$ gives an $n-5\rightarrow n-2$ plus and no other term in the Gra\ss mann necklace of $C$ gives a plus in this column.
-This $+$ does not appear in $D$ from $I_{n-2}^{D}$ but an $n-5\rightarrow n-1$ plus does instead.
-  \item All other plusses of $I_{n-2}^{C}$.
-  \item $I_{n-3}^{C}$ gives a plus in the $n-3$ column.  This $+$ is shifted over into the $n-2$ column in $D$.
-  \item All other plusses of $I_{n-3}^{C}$.
+  \item All the $I_{n-1}^{V}$ plusses.
+  \item $I_{n-2}^{V}$ gives an $n-5\rightarrow n-2$ plus and no other term in the Gramann necklace of $V$ gives a plus in this column.
+This $+$ does not appear in $W$ from $I_{n-2}^{W}$ but an $n-5\rightarrow n-1$ plus does instead.
+  \item All other plusses of $I_{n-2}^{V}$.
+  \item $I_{n-3}^{V}$ gives a plus in the $n-3$ column.  This $+$ is shifted over into the $n-2$ column in $W$.
+  \item All other plusses of $I_{n-3}^{V}$.
   \end{itemize}
-  Furthermore, no element of the Gra\ss mann necklace of $C$ gives an $n-5\rightarrow n-1$ plus.
+  Furthermore, no element of the Gramann necklace of $V$ gives an $n-5\rightarrow n-1$ plus.
 \end{lem}
@@
 \begin{proof}
-  By Lemma~\ref{lem I} $I_{n-2}^{D}= (I_{n}^{C} - \{n-5\})\cup \{n-1,n-2\}$.
-Also, by the location of $q$ in the WLD,  $n-2\not\in I_{n-3}^{C}$ and and $n-5$ is the index of the lowest vertical edge in $\mathcal{B}$.
-Thus this section of the Gra\ss mann necklace of $C$ looks like
+  By Lemma~\ref{lem I} $I_{n-2}^{W}= (I_{n}^{V} - \{n-5\})\cup \{n-1,n-2\}$.
+Also, by the location of $q$ in the WLD,  $n-2\not\in I_{n-3}^{V}$ and and $n-5$ is the index of the lowest vertical edge in $\mathcal{B}$.
+Thus this section of the Gramann necklace of $V$ looks like
   \begin{equation}\label{eq necklace}
-  I_{n-3}^{C} \underset{\substack{n-3\text{ out}\\n-2\text{ in}}}{\rightarrow} I_{n-2}^{C} \underset{\substack{n-2\text{ out}\\n-5\text{ in}}}{\rightarrow} I_{n-1}^{C} \underset{\substack{n-1\text{ out}\\\text{something in}}}{\rightarrow} I_{n}^{C} \underset{\substack{n \text{ out}\\\text{something in}}}{\rightarrow} I_1^{C}
+  I_{n-3}^{V} \underset{\substack{n-3\text{ out}\\n-2\text{ in}}}{\rightarrow} I_{n-2}^{V} \underset{\substack{n-2\text{ out}\\n-5\text{ in}}}{\rightarrow} I_{n-1}^{V} \underset{\substack{n-1\text{ out}\\\text{something in}}}{\rightarrow} I_{n}^{V} \underset{\substack{n \text{ out}\\\text{something in}}}{\rightarrow} I_1^{V}
   \end{equation}
-  where the first ``something'' is either $n$ or an element of $I_1^{C}$ and the second ``something'' is an element of $I_1^{C}$.
-Additionally all elements not explicitly mentioned must be in $I_1^{C}$ as they remain unchanged through this portion of the necklace.
-
-  Using this information now determine the symmetric difference of $I_{n-2}^{C}$ and $I_1^{C}$: $n-1, n-2$ and possibly $n$ are in $I_{n-2}^{C}$ but not in $I_1^{C}$.
-$n-5$ is in $I_1^{C}$ as are at least one and at most two other elements.
+  where the first ``something'' is either $n$ or an element of $I_1^{V}$ and the second ``something'' is an element of $I_1^{V}$.
+Additionally all elements not explicitly mentioned must be in $I_1^{V}$ as they remain unchanged through this portion of the necklace.
+
+  Using this information now determine the symmetric difference of $I_{n-2}^{V}$ and $I_1^{V}$: $n-1, n-2$ and possibly $n$ are in $I_{n-2}^{V}$ but not in $I_1^{V}$.
+$n-5$ is in $I_1^{V}$ as are at least one and at most two other elements.
 If there is one such element call it $a$.
 If there are two call them $a$ and $b$ with $a>b$.
-This means that the plusses in the Le diagram of $C$ coming from $I_{n-2}^{C}$ are as in the first part of Figure~\ref{fig messy}.
-Stepping to $I_{n-1}^{C}$ simply removes the $n-5\rightarrow n-2$ path, see the second part of Figure~\ref{fig messy}.
+This means that the plusses in the Le diagram of $V$ coming from $I_{n-2}^{V}$ are as in the first part of Figure~\ref{fig messy}.
+Stepping to $I_{n-1}^{V}$ simply removes the $n-5\rightarrow n-2$ path, see the second part of Figure~\ref{fig messy}.
 
@@
     \includegraphics{messy}
-    \caption{Plusses coming from $I_{n-2}^{C}$ (top left),  $I_{n-1}^{C}$ (top right) and $I_{n}^{C}$ bottom when $n-1, n-2\in I_{n-1}^{C}$.
+    \caption{Plusses coming from $I_{n-2}^{V}$ (top left),  $I_{n-1}^{V}$ (top right) and $I_{n}^{V}$ bottom when $n-1, n-2\in I_{n-1}^{V}$.
 The blue lines are the non-intersecting paths.
@@
 
-  Stepping to $I_{n}^{C}$, $n-1$ is taken out and either $n$ is put in if it was not there before, or one of $a$ or $b$ is put in and hence no longer available as a right end for a path.
+  Stepping to $I_{n}^{V}$, $n-1$ is taken out and either $n$ is put in if it was not there before, or one of $a$ or $b$ is put in and hence no longer available as a right end for a path.
 This gives two possible configurations illustrated in the bottom two parts of Figure~\ref{fig messy}.
 
-  Now we know that $I_{n-2}^{D}  = (I_{n}^{C} - \{n-5\})\cup \{n-1,n-2\}$ so the paths for building plusses from $I_{n-2}^{D}$ go from the set $\{n-5, n-3\}$ along with whichever of $a$ and $b$ is not in $I_{n}^{C}$ to $\{n-2, n-1, n\}$.
+  Now we know that $I_{n-2}^{W}  = (I_{n}^{V} - \{n-5\})\cup \{n-1,n-2\}$ so the paths for building plusses from $I_{n-2}^{W}$ go from the set $\{n-5, n-3\}$ along with whichever of $a$ and $b$ is not in $I_{n}^{V}$ to $\{n-2, n-1, n\}$.
 This means that we get plusses as in Figure~\ref{fig messyD} where the left and right cases correspond to the left and right cases in the bottom parts of Figure~\ref{fig messy}
@@
      \includegraphics{messyD}
-    \caption{Plusses coming from $I_{n-2}^{D}$.}\label{fig messyD}
+    \caption{Plusses coming from $I_{n-2}^{W}$.}\label{fig messyD}
   \end{figure}
@@
 
-  Now consider $I_{n-3}^{C}$.
-By \eqref{eq necklace} $I_{n-3}^{C}$ contributes the same plusses as $I_{n_2}^{C}$ except that it contributes an $n-5\rightarrow n-3$ plus in place of the $n-5\rightarrow n-2$ plus.
-Also, we have $n-3\in I_{n-3}^{C}$ be the location of $q$ and so $I_{k}^{D} = I_k^{C}\cup\{n-2\}$.
-Thus the paths for $I^{D}_{n-3}$ are the same as for $I^{C}_{n-3}$ except that the path that did go to $n-3$ now goes to $n-2$.
-This cannot conflict with another path since \eqref{eq necklace} shows that $n-2$ only appears in $I_{n-2}^{C}$ among the necklace elements of $C$.
-
-  Also note that $I_{n-3}^{C}, I_{n-2}^{C}$, and $I_{n-1}^{C}$ share their plusses outside of the $n-3$ and $n-2$ columns.  This proves the remaining statements of the lemma except the furthermore.
-
-  Finally, suppose there were a $n-5\rightarrow n-1$ plus in the Le diagram of $C$.
-By the algorithm, it would have to come when $n-5 \not\in I_j^{C}$.
-By \eqref{eq necklace} this means that it would have to come from $I_{n-4}^{C}$, $I_{n-3}^{C}$, or $I_{n-2}^{C}$.
-The analysis above shows it does not come from $I_{n-3}^{C}$ or $I_{n-2}^{C}$.
-Now, $n-4\in I_{n-4}^{C}$ by the location of $q$ and so $I_{n-4}^{C}$ must give an $n-5\rightarrow n-4$ plus and so cannot give an $n-5\rightarrow n-1$ plus.
+  Now consider $I_{n-3}^{V}$.
+By \eqref{eq necklace} $I_{n-3}^{V}$ contributes the same plusses as $I_{n_2}^{V}$ except that it contributes an $n-5\rightarrow n-3$ plus in place of the $n-5\rightarrow n-2$ plus.
+Also, we have $n-3\in I_{n-3}^{V}$ be the location of $q$ and so $I_{k}^{W} = I_k^{V}\cup\{n-2\}$.
+Thus the paths for $I^{W}_{n-3}$ are the same as for $I^{V}_{n-3}$ except that the path that did go to $n-3$ now goes to $n-2$.
+This cannot conflict with another path since \eqref{eq necklace} shows that $n-2$ only appears in $I_{n-2}^{V}$ among the necklace elements of $V$.
+
+  Also note that $I_{n-3}^{V}, I_{n-2}^{V}$, and $I_{n-1}^{V}$ share their plusses outside of the $n-3$ and $n-2$ columns.  This proves the remaining statements of the lemma except the furthermore.
+
+  Finally, suppose there were a $n-5\rightarrow n-1$ plus in the Le diagram of $V$.
+By the algorithm, it would have to come when $n-5 \not\in I_j^{V}$.
+By \eqref{eq necklace} this means that it would have to come from $I_{n-4}^{V}$, $I_{n-3}^{V}$, or $I_{n-2}^{V}$.
+The analysis above shows it does not come from $I_{n-3}^{V}$ or $I_{n-2}^{V}$.
+Now, $n-4\in I_{n-4}^{V}$ by the location of $q$ and so $I_{n-4}^{V}$ must give an $n-5\rightarrow n-4$ plus and so cannot give an $n-5\rightarrow n-1$ plus.
 
@@
 \begin{lem}\label{lem other k}
-  Let $C$ and $D$ be as in Lemma~\ref{lem I} and take $1<k<n-2$.  Suppose that if $n-2\in I_{n-2}^{C}$ then also $n-1\in I_{n-2}^{C}$.
-  The $I_k^{D}$ element of the Gra\ss mann necklace of $D$ gives the same plusses as $I_{k}^{C}$ except that if there is a plus in the $n-3$ column for $I_{k}^{C}$ then this plus is shifted into the $n-2$ column and no plus was already in that location.
+  Let $V$ and $W$ be as in Lemma~\ref{lem I} and take $1<k<n-2$.  Suppose that if $n-2\in I_{n-2}^{V}$ then also $n-1\in I_{n-2}^{V}$.
+  Then $I_k^{W}$ gives the same plusses as $I_{k}^{V}$ except that if there is a plus in the $n-3$ column for $I_{k}^{V}$ then this plus is shifted into the $n-2$ column and no plus was already in that location.
 \end{lem}
@@
 \begin{proof}
-  If $n-3\not\in I_{k}^{C}$ then by Lemma~\ref{lem I} $I_{k}^{D} = I_k^{C}\cup \{n-3\}$.
-Then since $n-3$ is the largest element of $I_1^{D}$ this transformation leaves the disjoint paths unchanged and so the plusses carry over from $C$ to $D$ directly.
-
-  If $n-3\in I_{k}^{C}$ then by Lemma~\ref{lem I} $I_{k}^{D} = I_k^{C}\cup \{n-2\}$.
-If $n-2$ is not covered in $C$ then certainly no pluses appear in the $n-2$ column of the Le diagram of $C$.
-If $n-2$ is covered in $C$ then by hypothesis so is $n-1$ and so we satisfy the hypotheses of Lemma~\ref{lem n-2 bad}.
-Thus the only necklace element of $C$ containing $n-2$ is $I_{n-2}^{C}$ and this particular plus is not contributed to the Le diagram of $D$ by $I_{n-2}^{D}$.
-
-  {}From $I_{k}^{C}$ there is a path from some vertical edge to the bottom edge $n-3$.
-In $I_{k}^{D}$, $n-3$ is a vertical edge with no path and instead there must be a path to $n-2$.
-By the previous paragraph no other path can end in $n-2$, so shifting the path that did go to $n-3$ to go to $n-2$ while leaving the others the same maintains non-crossingness and so must be the paths for $I_{k}^{D}$.
+  If $n-3\not\in I_{k}^{V}$ then by Lemma~\ref{lem I} $I_{k}^{W} = I_k^{V}\cup \{n-3\}$.
+Then since $n-3$ is the largest element of $I_1^{W}$ this transformation leaves the disjoint paths unchanged and so the plusses carry over from $V$ to $W$ directly.
+
+  If $n-3\in I_{k}^{V}$ then by Lemma~\ref{lem I} $I_{k}^{W} = I_k^{V}\cup \{n-2\}$.
+If $n-2$ supports no propagators in $V$ then certainly no pluses appear in the $n-2$ column of the Le diagram of $V$.
+If $n-2$ supports at least one propagator in $V$ then by hypothesis so is $n-1$ and so we satisfy the hypotheses of Lemma~\ref{lem n-2 bad}.
+Thus the only necklace element of $V$ containing $n-2$ is $I_{n-2}^{V}$ and this particular plus is not contributed to the Le diagram of $D$ by $I_{n-2}^{W}$.
+
+  {}From $I_{k}^{V}$ there is a path from some vertical edge to the bottom edge $n-3$.
+In $I_{k}^{W}$, $n-3$ is a vertical edge with no path and instead there must be a path to $n-2$.
+By the previous paragraph no other path can end in $n-2$, so shifting the path that did go to $n-3$ to go to $n-2$ while leaving the others the same maintains non-crossingness and so must be the paths for $I_{k}^{W}$.
 Thus the plus in the $n-3$ column for $C$ is shifted into the $n-2$ column, where there was no plus before, and no other plusses are changed.
@@
 \begin{thm}
-  The number of plusses in the Le diagram of a WLD is three times the number of propagators.
+  The number of plusses in the Le diagram of an admissible Wilson loop diagram is three times the number of propagators.
 \end{thm}
@@
 
-  First note that a WLD $D$ with one propagator covering vertices $i<j<k<\ell$ has Le diagram a single row with $|D|-i$ boxes.
-Labelling them from left to right by $|D|, \ldots, |D|-i+1$, by the algorithm there are plusses in the $j$, $k$, and $\ell$ positions.
-
-  Now consider WLDs with $k>1$ propagators.
-By Lemma~\ref{lem uncovered} it suffices to prove the result for WLDs with $k$ propagators and no uncovered vertices.
-By Lemma~\ref{lem dihedral} it suffices to prove the result for at least one WLD from each dihedral orbit.
-Take a WLD diagram $D$ with $k$ propagators.
-Make a dihedral transformation of $D$ if necessary so that $D$ has a propagator $p$ with the properties in Lemma~\ref{lem good p} relative to $D$.
-If $n-1$ is only covered by $p$ but $n-2$ is covered by at least one other propagator, then flip $D$ on the line perpendicular to the edge from $n-2$ to $n-1$.
-This will be our $D$ for the rest of the proof.
-
-  Let $C$ be $D$ with $p$ removed but no change in the vertices.
-Note that if $n-2$ is covered in $C$ then so is $n-1$ by the end of the previous paragraph and so if $n-2$ is covered in $C$ then the hypotheses of Lemma~\ref{lem n-2 bad} are satisfied.
-
-  {}From Lemma~\ref{lem shape} we know how the shapes of the Le diagrams of $C$ and $D$ relate; let $\mathcal{A}$ and $\mathcal{B}$ be as described after that lemma.
-Lemmas~\ref{lem n and n-1}, \ref{lem n-2 good}, and \ref{lem n-2 bad} tell us that the three boxes of the bottom row of the Le diagram of $D$ each have a plus.
-Lemmas~\ref{lem n and n-1}, \ref{lem n-2 good}, \ref{lem n-2 bad}, and \ref{lem other k} show that there is a bijection between the plusses of the Le diagram of $C$ and the plusses of the Le diagram of $D$ that are not in the bottom row which can be described as follows.
+  First note that a Wilson loop diagram $W$ with one propagator supported on vertices $i<j<k<\ell$ has Le diagram a single row with $|W|-i$ boxes.
+Labelling them from left to right by $|W|, \ldots, |W|-i+1$, by the algorithm there are plusses in the $j$, $k$, and $\ell$ positions.
+
+  Now consider Wilson loop diagrams with $k>1$ propagators.
+By Lemma~\ref{lem uncovered} it suffices to prove the result for weakly admissible Wilson loop diagrams with $k$ propagators and no vertices that do not support at least one propagator.
+By Lemma~\ref{lem dihedral} it suffices to prove the result for at least one Wilson loop diagram from each dihedral orbit.
+Take a weakly admissible Wilson loop diagram $W$ with $k$ propagators and no vertices which do not support at least one propagator.
+Make a dihedral transformation of $W$ if necessary so that $W$ has a propagator $p$ with the properties in Lemma~\ref{lem good p} relative to $W$.
+If $n-1$ supports only $p$ but $n-2$ supports at least one other propagator, then flip $W$ on the line perpendicular to the edge from $n-2$ to $n-1$.
+This will be our $W$ for the rest of the proof.
+
+  Let $V$ be $W$ with $p$ removed.
+Note that if $n-2$ supports at least one propagator in $V$ then so is $n-1$ by the end of the previous paragraph and so if $n-2$ supports at least one propagator in $V$ then the hypotheses of Lemma~\ref{lem n-2 bad} are satisfied.
+
+  {}From Lemma~\ref{lem shape} we know how the shapes of the Le diagrams of $V$ and $W$ relate; let $\mathcal{A}$ and $\mathcal{B}$ be as described after that lemma.
+Lemmas~\ref{lem n and n-1}, \ref{lem n-2 good}, and \ref{lem n-2 bad} tell us that the three boxes of the bottom row of the Le diagram of $W$ each have a plus.
+Lemmas~\ref{lem n and n-1}, \ref{lem n-2 good}, \ref{lem n-2 bad}, and \ref{lem other k} show that there is a bijection between the plusses of the Le diagram of $V$ and the plusses of the Le diagram of $W$ that are not in the bottom row.
+This bijection can be described as follows.
   \begin{itemize}
-  \item Plusses from $\mathcal{B}$ for $C$ maintain their positions in $\mathcal{B}$ for $D$.
-  \item Plusses from the first two columns (the $n$ and the $n-1$ columns) of $\mathcal{A}$ for $C$ maintain their positions in $\mathcal{A}$ for $D$.
-  \item If there is a plus in the $n-2$ column of $\mathcal{A}$ in  then Lemma~\ref{lem n-2 bad} applies, so there is exactly one such plus.  This plus maps to the $n-5\rightarrow n-1$ plus for $D$.
-  \item The plusses in the $n-3$ column for $C$ shift over to the third column (the $n-2$ column) of $\mathcal{A}$ in $D$.
+  \item Plusses from $\mathcal{B}$ for $V$ maintain their positions in $\mathcal{B}$ for $W$.
+  \item Plusses from the first two columns (the $n$ and the $n-1$ columns) of $\mathcal{A}$ for $V$ maintain their positions in $\mathcal{A}$ for $W$.
+  \item If there is a plus in the $n-2$ column of $\mathcal{A}$ in $V$ then Lemma~\ref{lem n-2 bad} applies, so there is exactly one such plus.
+This plus maps to the $n-5\rightarrow n-1$ plus for $W$.
+  \item The plusses in the $n-3$ column for $V$ shift over to the third column (the $n-2$ column) of $\mathcal{A}$ in $W$.
   \end{itemize}
-  This map is clearly reversible and hence bijective except possibly for the $n-5\rightarrow n-1$ plus for $D$.
-If the Le diagram of $D$ has an $n-5\rightarrow n-1$ plus then look at the Le diagram for $C$.
-If the Le diagram for $C$ has a plus in the $n-2$ column then Lemma~\ref{lem n-2 bad} applies and so there is no $n-5\rightarrow n-1$ plus in the Le diagram of $C$ and the $n-5\rightarrow n-1$ plus of $D$ can be uniquely mapped to the plus in the $n-2$ column of the Le diagram of $C$.
-If the Le diagram for $C$ has no plus in the $n-2$ column, then leave the $n-5\rightarrow n-1$ plus where it is in moving back to $C$.
+  This map is clearly reversible and hence bijective except possibly for the $n-5\rightarrow n-1$ plus for $W$.
+If the Le diagram of $W$ has an $n-5\rightarrow n-1$ plus then look at the Le diagram for $V$.
+If the Le diagram for $V$ has a plus in the $n-2$ column then Lemma~\ref{lem n-2 bad} applies and so there is no $n-5\rightarrow n-1$ plus in the Le diagram of $V$ and the $n-5\rightarrow n-1$ plus of $W$ can be uniquely mapped to the plus in the $n-2$ column of the Le diagram of $V$.
+If the Le diagram for $V$ has no plus in the $n-2$ column, then leave the $n-5\rightarrow n-1$ plus where it is in moving back to $V$.
 This reverses the map.
 
-  From all of this we get that the number of plusses in the Le diagram for $D$ is three more than the number of plusses in the Le diagram for $C$.  Applying induction completes the proof.
+  From all of this we get that the number of plusses in the Le diagram for $W$ is three more than the number of plusses in the Le diagram for $V$.  Applying induction completes the proof.
 \end{proof}
@@
 Suppose for a contradiction that $f$ is a factor of $\Delta_{I_i}$ of degree $\geq 3$.
-Note that by removing the propagators which come before those contributing to $f$ and changing $i$ to be the first vertex which contributes to $f$, we obtain a different admissible diagram for which $f$ still divides $\Delta_{I_i}$ but also $i\in I_i$ and \note{would it be neater to note at the beginning that removing uncovered vertices has no effect so we assume there are no redundant vertices, and hence $i \in I_i$ for each $i$?} $i$ contributes to $f$.
+Note that by removing the propagators which come before those contributing to $f$ and changing $i$ to be the first vertex which contributes to $f$, we obtain a different admissible diagram for which $f$ still divides $\Delta_{I_i}$ but also $i\in I_i$ and \note{would it be neater to note at the beginning that removing vertices which do not support any propagator has no effect so we assume there are no redundant vertices, and hence $i \in I_i$ for each $i$?} $i$ contributes to $f$.
 Showing that this different admissible diagram gives a contradiction is sufficient, and so we may assume that $i\in I_i$ and $i$ contributes to $f$.

### 2018-12-19 General WLD combinatorics.tex
corrected (hopefully) some indexing in some intervals
fixed some notational things in section 2 see higlighted notes

@@
 
-Every triangulated piece $t$ of an admissible Wilson loop diagram $W$ corresponds to a subdiagram of $W$ by taking the set of propagators $P$ corresponding to edges of $t$ and then taking the subdiagram $(P, V(P))$.
-Conversely, given a subdiagram $(P, V(P))$ of $W$ we can obtain a subgraph of $\tau(W)$ as follows:
+Every triangulated piece $t$ of an admissible Wilson loop diagram $W$ corresponds to a subdiagram of $W$ by taking the set of propagators $P$ corresponding to edges of $t$ and then taking the subdiagram $W_P = (P, V(P))$.
+Conversely, given a subdiagram $W_P = (P, V(P))$ of $W$ we can obtain a subgraph of $\tau(W)$, called $t$, as follows:
 \begin{itemize}
-\item The vertex set of the subgraph is
+\item The vertex set of the subgraph $t$ is
   \begin{itemize}
-  \item the vertices of $\tau(W)$ corresponding to edges on which propagators of $P$ are supported
-  \item along with any other vertices of $\tau(W)$ for which both neighbours are as described in the previous point.
+  \item \hlfix{the vertices of $\tau(W)$ corresponding to edges of $W$ defined by cyclically consecutive elements of $V(P)$ as a subset of $[n]$}{changed to simplify with existing notation, but now it contradicts below}
   \end{itemize}
@@
 \end{itemize}
-Note that the subgraph only depends on $P$, not the vertex set of the subdiagram, but it is not the subgraph of $\tau(W)$ consisting only of edges corresponding to propagators of $P$.
+Note that the subgraph $t$ only depends on $P$, \hlfix{not the vertex set of the subdiagram $W_P$}{really?
+why?}, but it is not the subgraph of $\tau(W)$ consisting only of edges corresponding to propagators of $P$.
 
@@
 We count how many edges of $t$ are not on the outer face of $\tau(W)$.
+These are exactly the edges of $t$ defined by propagators of $W$.
 Consider the intersection of $t$ with the outer face of $\tau(W)$: this is a possibly disconnected subgraph of the polygon of $\tau(W)$ and this subgraph has $m$ vertices.
@@
 The exactness condition on $(P, V(P))$ says that the four supporting vertices of $p$ are distinct.
-If the support of $p$ is four consecutive vertices, then the ends of the edge corresponding to $p$ in $\tau(W)$ have a common neighbour and so $t$ is a single triangle, hence a triangulated piece.
+If the support of $p$ is four consecutive vertices, then $V(p)$ defines three consecutive boundary edges of $W$, so $t$ is a single triangle, hence a triangulated piece.
 If the support of $p$ is not four consecutive vertices, then the vertices which are the ends of $t$ are separated by at least two vertices along the cycle.
@@
 
-To avoid the issue of exact diagrams being subdiagrams of other exact subdiagrams (for instance, any subdiagram $(q, V_q)$, for $q \in \cP$ is exact), we introduce the notion of maximal exact subdiagrams.
+To avoid the issue of exact diagrams being subdiagrams of other exact subdiagrams (for instance, any subdiagram $(q, V(q))$, for $q \in \cP$ is exact), we introduce the notion of maximal exact subdiagrams.
 
@@
 Since Corollary \ref{uniqueproppartitioncor} allows us to decompose any admissible Wilson loop diagram into a collection of maximal exact subdiagrams, in this section we examine the matroid properties of exact subdiagrams more closely.
+In particular, we show that the matroids associated to exact subdiagrams are uniform (Theorem \ref{??}) and that
 
@@
 
-\begin{lem}\label{lem properties of prop flats}
+\begin{lem}\label{lem properties of prop flats} \sanote{do we need the first 2? They follow directly from the definition 1.2. Do we use them later?}
 Let $F(P)$ be a propagator flat as defined above. Then

### 2018-12-19 General WLD combinatorics.tex
Made changes to section 2.3, stopping after 2.14

@@
 
-[outline of section, postponed until section structure is finalised]
-
-The main results of this section are the following: we show that two admissible Wilson loop diagrams define the same matroid if and only if they are equivalent (Theorem \ref{same matroid iff equiv}), and we obtain a formula for the number of admissible Wilson loop diagrams in each equivalence class (Corollary \ref{number of equiv diagrams}).
-[sentence about why this matters]
-
-\subsection{Wilson loop diagrams as matroids}\label{sec matroid background}
+In subsection 2.1, we discuss a few matroidal facts about Wilson loop diagrams.
+In section 2.2, we show that there is a one to one correspondence between exact subdiagrams of Wilson loop diagrams and triangulated pieces of the corresponding polygon partion.
+In section 2.3, we return to some matroidal facts about Wilson loop diagrams, and exact subdiagrams in partuclar.
+We show that a subdiagram of $W$ defines a uniform matroid if and only if the subdiagram is exact.
+This is then used to prove the main result of section 2.3, which is that that two admissible Wilson loop diagrams define the same matroid if and only if they are equivalent (Theorem \ref{same matroid iff equiv}), and we obtain a formula for the number of admissible Wilson loop diagrams in each equivalence class (Corollary \ref{number of equiv diagrams}).
+[sentence about why this matters] \todo{much of the above is just text.
+PUT REFERENCES IN}
+
+\subsection{Wilson loop diagrams as matroids\label{sec matroid background}}
 
@@
 \item If $[n]$ can be partitioned into at least two non-empty sets, each of which support different sets of propagators that form a partition of the propagotor set, \bas [n] = \sqcup_i V(P_i) \quad \textrm{s.t.} \quad \sqcup P_i = \cP; \quad V(P_i) \cap V(P_j) = \emptyset; \quad  P_i \cap P_j = \emptyset \;, \eas then the matroid $M(W)$ is seperable, \bas M(W) = \bigoplus_i M(P_i, V(P_i)) \;.\eas
+\item $F(P)$ is a flat of $M(W)$, thus justifying the name ``propagator flat''.
 \end{enumerate}
@@
 (3) is a direct consequence of \cite[Lemma 3.20]{wilsonloop} and the fact that $F(P_1)^c = V(P_1^c)$
+
+To prove (4), we need to show that $F(P)$ is maximally dependent.
+If $F(P) = [n]$ then this is automatic, so suppose not and let $v \in [n] \setminus F(P)$.
+In other words, $v \in V(P^c)$ and so $v$ supports some propagator $q \not\in P$.
+Let $S \subseteq F(P)$ be an independent set of maximal size.
+Then $\Prop(S) \subseteq P$ by (1), and no subset of $S$ supports fewer propagators than the number of vertices it contains (this is the definition of an independent set in $M(W)$).
+Since $v$ supports a new propagator $q \not\in P$, the set $S \cup \{v\} \subseteq F(P) \cup\{v\}$ also satisfies this independence condition.
+Thus $\rk(F(P) \cup\{v\}) = \rk(F(P)) + 1$, as required.
 \end{proof}
@@
 
-\subsection{Polygon partitions of Wilson loop diagrams}
+\subsection{Polygon partitions of Wilson loop diagrams\label{sec: polygon partitions}}
 
@@
 
-\subsection{Matroid properties of exact subdiagrams}
+\subsection{Matroidal properties of exact subdiagrams \label{sec: exact diagram matroidal props}}
 
 Since Corollary \ref{uniqueproppartitioncor} allows us to decompose any admissible Wilson loop diagram into a collection of maximal exact subdiagrams, in this section we examine the matroid properties of exact subdiagrams more closely.
-In particular, we show that the matroids associated to exact subdiagrams are uniform (Theorem \ref{??}) and that
+In particular, we show that given an exact subdiagram $(P, V(P))$, it can be written as the contraction of the matroid $M(W)$ by the complementary propagator flat, $F(P^c)$.
+Furthermore, if $(P, V(P))$ is a maximal exact subdiagrams, its complementary propagator flat is a cyclic flat.
+Finally, we show that matroids associated to exact subdiagrams are uniform (Theorem \ref{exactuniformthm}).
+
+We begin by proving some useful facts about flats of matroids associated to admissible Wilson loop diagrams.
+
+\begin{comment}
 
@@
 \end{enumerate}
-\end{lem}
+\end{lem} \sanote{I'd like to attach this to the "generic facts about matroids" in lemma 2.2?}
 \begin{proof}
@@
 
+\end{comment}
+
 \begin{lem} \label{lem decompose flat}Let $F$ be a flat in $M(W)$, and let $C \subseteq F$ be the union of all circuits contained in $F$. Then the following are true:
@@
 Let $v \in C$.
-Clearly $\Prop(v) \subseteq \Prop(C)$, and so by Lemma \ref{lem properties of prop flats} we have $F(\Prop(v)) \subseteq F(\Prop(C))$.
-Since $v \in F(\Prop(v))$ by the definition of propagator flat, we have $v \in F(\Prop(C))$ as required.
+Clearly $\Prop(v) \subseteq \Prop(C)$.
+Since $F(P)  = V(P^c)^c$, we have $F(\Prop(v)) \subseteq F(\Prop(C))$.
+Since $v \in F(\Prop(v))$ by the definition of propagator flat, we have $v \in F(\Prop(C))$ as required, and $C \subseteq F(\Prop(C))$.
 
@@
 Let $B$ be an independent subset of $C$ of maximal rank; we first show that $B \cup \{w\}$ is a dependent set in $M(W)$.
-Indeed, by \cite[Proposition 3.10]{wilsonloop}, there exists some $Q \subseteq \Prop(B)$ with $|Q| = |B|$ and such that $B$ is a basis in $M(Q,V(Q))$.
-We therefore have
-\[Q \subseteq \Prop(B) \subseteq \Prop(C),\]
-with $|\Prop(C)| = \rk(C)$ by Lemma \ref{lem facts about WLD matroids} and $|Q| = |B| = \rk(C)$ by the choice of $B$.
-Thus $Q = \Prop(C)$, and so $B$ is a basis in the matroid defined by $W' := (\Prop(C),V(\Prop(C)))$.
-All that remains is to note that $w \in F(\Prop(C)) \subseteq V(\Prop(C))$, i.e.
-$w$ is a vertex in $W'$; thus $B \cup\{w\}$ is dependent in $W'$, and hence also in $W$.
-This also implies that $\rk(F\cup w) = \rk(F)$ since $B\subseteq F$ and so since $F$ is a flat we must have $w\in F$.
-
-Returning our attention to $M(W)$, the dependent set $B \cup \{w\}$ must contain a circuit $C'$, with $w \in C'$ since $B$ was an independent set.
-Now $C \cup C' = C \cup \{w\} \supsetneq C$ is a cycle which, since $w\in F$, contradicts the maximality of $C$.
+By Lemma \ref{lem facts about WLD matroids}, \bas |\Prop(C)| = \rk(C) = |B| = \rk(B) .\eas Since $B \subseteq C$ implies that  $\Prop(B) \subseteq \Prop(C)$, this implies that $\Prop(B) = \Prop(C)$.
+Furthermore, since $w \in F(Prop(C)$, $\Prop(B\cup w) \subseteq \Prop(B)$.
+By Lemma \ref{lem facts about WLD matroids} $\rk (B \cup w) \leq \min\{|B\cup w|, |\Prop(B\cup w)|\}$, and therefore $\rk (B \cup w) < |B\cup w|$.
+That is, $B\cup w$ is a circuit in $F(\Prop(C))$.
+Therefore, $B \cup w \subset C$, leading to a contradiction.
 
@@
 Now let $e \in C$, and suppose that $\rk((F\setminus C)\cup\{e\}) = \rk(F\setminus C)$.
-This implies that $(F\setminus C)\cup \{e\}$ is dependent, and hence contains a circuit.
-This circuit must contain at least two elements \note{What if $e \in C$ supported no propagators?
-$\{e\}$ would then be a circuit on its own}(since all vertices support at least one propagator), but this contradicts the fact that $C$ was the union of all circuits in $F$.
+This implies that $(F\setminus C)\cup \{e\}$ is dependent, and hence contains a circuit, $S$.
+This circuit must contain at least one element but this contradicts the fact that $C$ was the union of all circuits in $F$.
 
@@
 
-\begin{thm} \label{exactcircuitlem}
+\begin{thm} \label{exactuniformthm}
 Let $W':= (P, V(P))$ be a subdiagram of an admissible Wilson loop diagram $W= (\cP, [n])$. Then $W'$ is an exact subdiagram if and only if $M(W')$ is a uniform matroid of rank $|P|$.
@@
     \[
-    J^{(W)}_p(m) = \{m+3\}, \  J^{(W)}_p(m+1) = [m+4, d-1], \  J^{(W)}_p(m+2) = [d, m+1], \  J^{(W)}_p(m+3) = \{m+2\},
+    J^{(W)}_p(m) = \{m+4\}, \  J^{(W)}_p(m+1) = [m+5, d-1], \  J^{(W)}_p(m+2) = [d, m+2], \  J^{(W)}_p(m+3) = \{m+3\},
     \]
@@
     \[
-    J^{(W)}_p(m) = [m+4, j+1], \  J^{(W)}_p(m+1) = [j+2, d-1], \  J^{(W)}_p(m+2) = [d, m+1], \  J^{(W)}_p(m+3) = \{m+3\},
+    J^{(W)}_p(m) = [m+4, j+1], \  J^{(W)}_p(m+1) = [j+2, d-1], \  J^{(W)}_p(m+2) = [d, m+2], \  J^{(W)}_p(m+3) = \{m+3\},
     \]

### 2018-12-19 General WLD combinatorics.tex
changes I shouldn't have made while others were working

--- 2018-12-19 General WLD combinatorics.tex
@@
 
-\title{Put Title here}
-%\author{}
+\title{Combinatorics of the geometry of Wilson loop diagrams}
+\author{Susama Agarwala, Si\^an Fryer, and Karen Yeats}
 %\date{}
@@
 \begin{document}
+\maketitle
 
@@
 \item For $V \subseteq [n]$, write $\Prop(V) = \{ p \in \cP | V(p) \cap V \neq \emptyset \} $.
-\item For $P \subseteq \cP$, define $F(P) = V(P^c)^c$ to be the set of vertices in $[n]$ that only support propagators in the set $P$.
+\item For $P \subseteq \cP$, define $F(P) = V(P^c)^c$ to be the set of vertices in $[n]$ that do not support any propagators outside the set $P$.
 \end{enumerate}
@@
 
-Note that $F(\emptyset)$ is the set of vertices that are not in the support of any propagators. \sanote{did we settle on a term here? I'd like to make this a definition}
+Note that $F(\emptyset)$ is the set of vertices that are not in the support of any propagators.
+\note{mention that $F(\emptyset)$ is also called nonsupporting and also phrase as a note that old lemma about $F(P) = stuff - stuff$.}
 
@@
 \begin{proof}
-Since the vertices of $\tau(W)$ are labeled by the edges of $W$, which are cyclically ordered, this gives an ordering to the vertices.
-Furthermore, since the outer \hlfix{circle of $W$ is a cycle}{sounds awkward in the new notation}, the outer face of $\tau(W)$ is also a cycle.
+Since the vertices of $\tau(W)$ are labeled by the edges of $W$, which are cyclically ordered, this gives an ordering to the vertices and the outer face of $\tau(W)$ is a cycle.
 Since $W$ is admissible, no pairs of propagators cross.
@@
   \begin{itemize}
-  \item \hlfix{the vertices of $\tau(W)$ corresponding to edges of $W$ defined by cyclically consecutive elements of $V(P)$ as a subset of $[n]$}{changed to simplify with existing notation, but now it contradicts below}
+  \item the vertices of $\tau(W)$ corresponding to edges of $W$ defined by cyclically consecutive elements of $V(P)$ as a subset of $[n]$
   \end{itemize}
@@
 \end{itemize}
-Note that the subgraph $t$ only depends on $P$, \hlfix{not the vertex set of the subdiagram $W_P$}{really?
-why?}, but it is not the subgraph of $\tau(W)$ consisting only of edges corresponding to propagators of $P$.
+Note that the subgraph $t$ depends on how the propagators of $P$ sit inside $[n]$, not on how they sit in $W_P$ itself.
+In particular $t$ is not the subgraph of $\tau(W)$ consisting only of edges corresponding to propagators of $P$.
 
@@
 
-Agarwala and Marcott show ***cite this*** that the dimension of the positroid cell defined by a Wilson loop diagram $(\cP, [n])$ has dimension $3|\cP|$.
-Their proof is geometric and elegant, but it is not easy to track the effect of a particular propagator.
-
-The dimension of a positroid cell is the same as the number of plusses in the associated Le diagram ***cite something***, and so with Algorithm~\ref{alg:put GN on WLD} along with the algorithm for passing from a Grassmann necklace to a Le diagram (reversing Oh's algorithm) described by some of us in \cite{reversingOh}, we can, at the cost of a bit of messy grunt work, give a different recursive proof of the $3|\cP|$-dimensionality that explicitly describes the changes in the positions of the plusses in the Le diagram.
+Our next goal is to show that the dimension of the positroid cell defined by a Wilson loop diagram $(\cP, [n])$ has dimension $3|\cP|$.
+Marcott in ***cite this*** has a different proof which is geometric and more elegant, bit it is not easy to track the effect of a particular propagator.
+Our approach is much more explicit.
+
+The dimension of a positroid cell is the same as the number of plusses in the associated Le diagram ***cite something***, and so with Algorithm~\ref{alg:put GN on WLD} along with the algorithm for passing from a Grassmann necklace to a Le diagram (reversing Oh's algorithm) described by some of us in \cite{reversingOh}, we can, at the cost of a bit of messy grunt work, give a recursive proof of the $3|\cP|$-dimensionality that explicitly describes the changes in the positions of the plusses in the Le diagram.
 
@@
 
-{\color{red}Maybe proved that inadmissible diagrams, while they correspond to matroids, can't be mapped to the positroids of the correct dimension? }
-
 \section{Poles of Wilson Loop Integrals}

### 2018-12-21 General WLD combinatorics.tex
is this ok now (with comment)
a few small things at the beginning of section 4

@@
 
+\note{the one element could be e so this doesn't work}
 For any $e \not\in F$, we certainly have $\rk((F\setminus C)\cup\{e\}) = \rk(F\setminus C) +1$ since $F$ is a flat.
@@
 \begin{itemize}
-  \item For each $i \in \interval{1}{n}$, we construct a factor $r_i$ as follows:
+  \item For each $i \in [n]$, we construct a factor $r_i$ as follows:
     \begin{itemize}
@@
 \end{algorithm}
-\note{What are we doing about the sign of the determinants?}
+\note{What are we doing about the sign of the determinants?
+--- in the end we are making a denominator, so an object that probably makes the most sense as being defined up to sign; I would suggest having all this be up to an overall sign, but perhaps we can discuss in our next meeting.}
 
@@
 \end{figure}
-\todo{I've named the propagators $p$, $q$, $s$; could whoever codes up the figure please add that?}
 
@@
 \begin{gather*}I_1 = \{1,2,4\}, I_2 = \{2,4,5\}, I_3 = \{4,5,6\}, I_4=\{4,5,6\},\\ I_5=\{5,6,7\}, I_6 = \{6,7,1\}, I_7=\{7,1,2\}. \end{gather*}  
-Figure~\ref{fig R eg} also indicates the pairings between propagators and vertices for each $i \in \interval{1}{7}$.
+Figure~\ref{fig R eg} indicates the pairings between propagators and vertices for each $i \in [1,7]$.
 

### 2018-12-21 General WLD combinatorics.tex
some work on section 4

@@
 \end{algorithm}
-\note{What are we doing about the sign of the determinants?
---- in the end we are making a denominator, so an object that probably makes the most sense as being defined up to sign; I would suggest having all this be up to an overall sign, but perhaps we can discuss in our next meeting.}
+
+As we take each $\Delta_{I_i}$ to simply be the determinant of a particular submatrix of $C(W)$, the overall sign of each $\Delta_{I_i}$ is well-defined.
+However, we will not be interested in these signs as they only contribute an overall sign to $R$ and our main theorem in this section (Theorem~\ref{thm denom}) will simply be to show that $R$ is equal up to a $\mathbb{Q}$-multiple to the denominator of the Wilson loop diagram (see Definition~\ref{def R(W)}).
 
@@
 \begin{prop}\label{prop alg gives rad}
-  With notation as in Algorithm~\ref{alg WLD to denom via GN} we have the following:
+  With notation as in Algorithm~\ref{alg WLD to denom via GN} and working over the field $\mathbb{Q}$ we have the following:
   \begin{enumerate}
@@
 All linear factors of  $\Delta_{I_i}$ are single variables and all irreducible quadratic factors are $2\times 2$ determinants of single variables.
-    \item Quadratic factors in $r_i$ arise precisely when propagators $p$ and $q$ are supported on a common edge $(a,b)$ with $I_i(p)=a$ and $I_i(q)=b$.
+    \item Quadratic factors in $\Delta_{I_i}$ arise precisely when propagators $p$ and $q$ are supported on a common edge $(a,b)$ with $I_i(p)=a$ and $I_i(q)=b$.
     \item $r_i$ divides $\Delta_{I_i}$.
@@
 
-Since there is no cancellation between terms, this means that $\Delta_{I_i}$ itself contains no other variables.
+Since there is no cancellation between terms, this means that the full expansion over permutations of $\Delta_{I_i}$ contains no other nonzero terms and hence no other variables.
 Therefore $\Delta_{I_i}$ is equal to the determinant of the matrix obtained by taking the submatrix of $C(W)$ with columns indexed by $I_i$ and setting any variables not appearing in $\Delta_{I_i}$ to $0$.
@@
 By considering which variables appear, these two factors must also be $f$ and $g$, and so in particular $f$ is the minor of $C(W)$ associated to $\mathcal{P}'$ and $J$.
+This proves the claim.
 
@@
 Suppose for a contradiction that $f$ is a factor of $\Delta_{I_i}$ of degree $\geq 3$.
-Note that by removing the propagators which come before those contributing to $f$ and changing $i$ to be the first vertex which contributes to $f$, we obtain a different admissible diagram for which $f$ still divides $\Delta_{I_i}$ but also $i\in I_i$ and \note{would it be neater to note at the beginning that removing vertices which do not support any propagator has no effect so we assume there are no redundant vertices, and hence $i \in I_i$ for each $i$?} $i$ contributes to $f$.
+Note that by removing the propagators which come before those contributing to $f$ and changing $i$ to be the first vertex which contributes to $f$, we obtain a different admissible diagram for which $f$ still divides $\Delta_{I_i}$ but also $i\in I_i$ and \note{would it be neater to note at the beginning that removing vertices which do not support any propagator has no effect so we assume there are no redundant vertices, and hence $i \in I_i$ for each $i$?
+No, the point is that we can make it so that $i$ is the first index where a propagator of $f$ contributes, not just that it is in $I_i$.} $i$ contributes to $f$.
 Showing that this different admissible diagram gives a contradiction is sufficient, and so we may assume that $i\in I_i$ and $i$ contributes to $f$.
@@
 \textbf{Case 1}: Suppose $p$ has one end on the edge $(i-1, i)$.  Thus $p$ is supported on $(i-1, i, m, m+1)$ for some $m >_i i$, and $I_{i+1}(p) = m$ by Lemma~\ref{vertex cyclic int lem}.
-%Call the propagators which appear before $p$ is closed the propagators inside $p$. \note{It might be nice to have general language for this inside/outside idea.  What do you think.}
 
@@
 
-If neither $m$ nor $m+1$ appear in $I_i$ then $V(p) \cap I_i = \{i\}$,\note{check: is it obvious that $i-1 \not\in I_i$ or are we using the no coloops result?} and so the row of $p$ in the matrix of $\Delta_{I_i}$ has only one nonzero entry; hence $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$, which is a contradiction.
+If neither $m$ nor $m+1$ appear in $I_i$ then by Corollary~\ref{no coloops} $V(p) \cap I_i = \{i\}$, and so the row of $p$ in the matrix of $\Delta_{I_i}$ has only one nonzero entry; hence $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$, which is a contradiction.
 So we must have at least one of $m$ and $m+1$ in $I_i$.
@@
 For any fixed bijection $\sigma$ from $\cP-\{p,q\}$ to $I_i -\{a,b\}$ for which each propagator is supported on its image under the bijection, we can extend $\sigma$ to a bijection of all propagators with $I_i$ in two ways: either $p\mapsto a$ and $q\mapsto b$ or $p\mapsto b$ and $q\mapsto a$.
-The sum of the contributions of all these bijections to $\Delta_{I_i}$ is therefore the product of $x_{p,a}x_{q,b}-x_{p,b}x_{q,a}$ with the minor coming from the remaining propagators and $I_i - \{a,b\}$.
+The sum of the contributions of all these bijections to $\Delta_{I_i}$ is therefore the product of $x_{p,a}x_{q,b}-x_{p,b}x_{q,a}$ with the minor coming from $\cP-\{p, q\}$ and $I_i - \{a,b\}$.
 Since there is no cancellation of terms in the expansion of $\Delta_{I_i}$, if any other terms appear then they will cause a factor which is not in the form described in the previous part.
@@
 By part (2), either exactly one variable in the row corresponding to $p$ appears in $\Delta_{I_i}$ and this variable is a factor of $\Delta_{I_i}$, or exactly two variables from the row corresponding to $p$ appear in $\Delta_{I_i}$ and they appear as part of a quadratic factor.
-In the first case: let the variable be $x$, then $x$ is a factor of both $r_i$ and $\Delta_{I_i}$ and is the only variable from this row in either polynomial.
+In the first case let the variable be $x$, then $x$ is a factor of both $r_i$ and $\Delta_{I_i}$ and is the only variable from this row in either polynomial.
 
@@
 This contradicts Lemma~\ref{vertex cyclic int lem}.
-Now suppose $f$ is a quadratic factor, say from associating propagators $p$ and $q$ to vertices $a$ and $b$ respectively.
-\hlfix{Since $p$ comes before $q$ on edge $(a,b)$}{I can't figure out why this happens; what am I missing?} it is not possible for any $I_i$ to associate $p$ to $b$ and $q$ to $a$.
+Now suppose $f$ is a quadratic factor, say from propagators $p$ and $q$ supported on the edge $(a, b)$ with $p$ before $q$ on the edge.
+In this case it is not possible for any $I_i$ to associate $p$ to $b$ and $q$ to $a$.
 Furthermore, we know by part (4) that $p$ changes from not being associated to $a$ to being associated to $a$ if and only if $q$ changes from not being associated to $b$ to being associated to $b$.
@@
 \begin{thm}\label{thm denom}
-Given any admissible Wilson loop diagram $W$, let $GN(W) = \{I_1, \ldots I_n\}$ be the associated Grasmann necklace.
-Then the denominator of the integral, $R(W)$ (see Definition~\ref{def R(W)}), is an integer multiple of the radical of $\prod_{i=1}^n \Delta_{I_i}$, where $\Delta_{I_i}$ is the determinant of the $k \times k$ minor indicated by $I_i$.
+Given any admissible Wilson loop diagram $W$, let $\{I_1, \ldots I_n\}$ be the associated Grasmann necklace.
+Then the denominator of the integral, $R(W)$ (see Definition~\ref{def R(W)}), is a $\mathbb{Q}$-multiple of the radical of $\prod_{i=1}^n \Delta_{I_i}$, where $\Delta_{I_i}$ is the determinant of the $k \times k$ minor indicated by $I_i$.
+Equivalently, $R(W)$ is a $\mathbb{Q}$-multiple of the $R$ of Algorithm~\ref{alg WLD to denom via GN}.
 \end{thm}
@@
 \begin{proof}
-In view of Proposition~\ref{prop alg gives rad} it remains to prove that the $R$ of Algorithm~\ref{alg WLD to denom via GN} is $R(W)$, the denominator of the integral $I(W)$.
+The equivalence of the final statement of the theorem is due to Proposition~\ref{prop alg gives rad}.
+It remains to prove that $R(W)$ is an integer multiple of the $R$ of Algorithm~\ref{alg WLD to denom via GN}.
 
 To this end, first note that $R(W)$ and $R$ both have total degree $4|\mathcal{P}|$; the degree of $R(W)$ is immediate from the definition while that of $R$ follows from Lemma~\ref{vertex cyclic int lem}.
-By Proposition~\ref{prop alg gives rad} every factor of $R$ is either a single variable or a quadratic factor coming from two propagators supported on a common edge and \hlfix{hence every factor of $R$ divides $R(W)$}{Is this obvious?
-Or does it follow from a previous result?}.
-Finally, since $R$ is squarefree and monic, this implies that $R(W)$ is an integer multiple of $R$.
-\end{proof}
+By Proposition~\ref{prop alg gives rad} every factor of $R$ is either a single variable or a quadratic factor coming from two propagators supported on a common edge.
+The factors of each $R_e$ making up $R(W)$ in the notation of Definition~\ref{def R(W)} are all of this form and hence every factor of $R$ divides $R(W)$.
+Finally, since $R$ is squarefree, this implies that $R(W)$ is a $\mathbb{Q}$-multiple of $R$.
+\end{proof}
+
+\note{Is there any point in working out the $\mathbb{Q}$-coefficient, or otherwise discussing the field?}
 

### 2019-01-01 General WLD combinatorics.tex
addressed a few comments from the last meeting

@@
 \item For $P \subseteq \cP$, define $F(P) = V(P^c)^c$ to be the set of vertices in $[n]$ that do not support any propagators outside the set $P$.
+\item The set of vertices that are not in the support of any propagotors is denoted  $F(\emptyset)$. Vertices in this set are called non-supporting.  
 \end{enumerate}
@@
 
-Note that $F(\emptyset)$ is the set of vertices that are not in the support of any propagators.
-\note{mention that $F(\emptyset)$ is also called nonsupporting and also phrase as a note that old lemma about $F(P) = stuff - stuff$.}
+\begin{rmk}\label{alt F(P) rmk}
+Note that a more explicit definition of $F(P)$ is \bas F(P)  = \big(V(P) \setminus V(P^c) \big) \cup F(\emptyset) \eas
+\end{rmk}
 
@@
 
-Note that this means that the set $F(\emptyset)$ is the maximal subset of vertices of $W$ of rank $0$.
-That is, it is the unique flat of rank $0$ in $M(W)$.
-\sanote{I'm sprinkling comments about $F(\emptyset)$ throughout until we can come up with a better name than unsupportive vertices.}
+Note that this means that the set, $F(\emptyset)$, of non-supporting vertices is the maximal subset of vertices of $W$ of rank $0$. That is, it is the unique flat of rank $0$ in $M(W)$.
 
@@
 \item $C = F(\Prop (C))$, i.e. $C$ is a propagator flat.
-\item $F \setminus C$ is an independent  flat.  
+\item $F \setminus C$ is an independent set. Furthermore, If $F\setminus C$ is an independent flat if and only if $F(\emptyset) = \emptyset$, that is $W$ has no non-supporting vertices.  
 \end{enumerate}
@@
 
-\note{the one element could be e so this doesn't work}
-For any $e \not\in F$, we certainly have $\rk((F\setminus C)\cup\{e\}) = \rk(F\setminus C) +1$ since $F$ is a flat.
+Note that since $F(\emptyset)$ has rank $0$, $F(\emptyset)$ is contained in every flat of $W$. Therefore, if $F(\emptyset) \neq \emptyset$, then $F\setminus C$ cannot be a flat.
+
+If $F(\emptyset) = \emptyset$, for any $e \not\in F$, we certainly have $\rk((F\setminus C)\cup\{e\}) = \rk(F\setminus C) +1$ since $F$ is a flat.
 Now let $e \in C$, and suppose that $\rk((F\setminus C)\cup\{e\}) = \rk(F\setminus C)$.
 This implies that $(F\setminus C)\cup \{e\}$ is dependent, and hence contains a circuit, $S$.
-This circuit must contain at least one element but this contradicts the fact that $C$ was the union of all circuits in $F$.
+Since $F(\emptyset) = \emptyset$, this circuit must contain at least two elements but this contradicts the fact that $C$ was the union of all circuits in $F$.
 

### 2019-01-04 General WLD combinatorics.tex
readability edits to cyclic intervals proof

@@
 
+Given a propagator $p$ and a vertex $i$ in its support, it will be very useful in the following to understand on what set of vertices the Grassmann necklace algorithm assigns $i$ to $p$.
+The answer is that the set is a non-empty cyclic interval.
+Lemma~\ref{vertex cyclic int lem} establishes this, but first we need a preliminary lemma which is also useful in its own right.
+
 \begin{lem}\label{lem no fourth vertex}
@@
 
-Given a propagator $p$ and a vertex $i$ in its support, it will be very useful in the following to understand on what set of vertices the Grassmann necklace algorithm assigns $i$ to $p$.
-The answer is that the set is a non-empty cyclic interval.
-Lemma~\ref{vertex cyclic int lem} establishes this, but first we need a preliminary lemma which is also useful in its own right.
-
 %\begin{lem}\label{lem last vert}
@@
 
-Given a propagator $p$ of an admissible WLD $W$ and a vertex $i$ in the support of $p$ we will use the notation $J_p^{(W)}(i)$ for the set of indices $m$ where $I_m(p) = l$ where the $I_m$ are the sets calculated by Algorithm~\ref{alg:put GN on WLD}, and using the notation of Definition~\ref{def I_i as a function}.
+Given a propagator $p$ of an admissible WLD $W$ and a vertex $i$ in the support of $p$, define
+\[J_p^{(W)}(i) = \{m \in [n] \ : \ I^{(W)}_m(p) = i \},\]
+i.e.
+the set of indices $m$ for which Algorithm [ref] assigns the value $i$ to the propagator $p$ in $W$.
+The following lemma establishes that these sets behave in a simple and predictable manner, a fact which we will repeatedly use in subsequent proofs.
 
@@
 Let $p=(i,j)$ be a propagator of an admissible WLD $W$ on $n$ vertices.
-Then $J_p^{(W)}(i)$, $J_p^{(W)}(i+1)$, $J_p^{(W)}(j)$, and $J_p^{(W)}(j+1)$ are each non-empty cyclic intervals of $\{1, \ldots, n\}$ which partition $\{1, \ldots, n\}$ and occur in the given cyclic order.
+Then $J_p^{(W)}(i)$, $J_p^{(W)}(i+1)$, $J_p^{(W)}(j)$, and $J_p^{(W)}(j+1)$ are each non-empty cyclic intervals which partition $[n]$ and occur in the given cyclic order.
 \end{lem}
@@
 Now suppose $W$ has more than one propagator.
-Since unsupported vertices have no effect on the Grassmann necklace algorithm, it suffices to prove the result for $W$ with no unsupported vertices.
-Then by Lemma~\ref{lem sian} $W$ has at least one of the four situations illustrated in figure~\ref{fig 3 cases}.
+Since non-supporting vertices have no effect on the Grassmann necklace algorithm, it suffices to prove the result for $W$ with $F(\emptyset) = \emptyset$.
+Then by Lemma~\ref{lem sian}, $W$ has at least one of the four situations illustrated in Figure~\ref{fig 3 cases}.
 
@@
     \includegraphics[scale=0.8]{3cases}
-    \caption{Four cases for admissible WLDs with no unsupported vertices.
+    \caption{Four cases for admissible WLDs with no non-supporting vertices.
 The green half-propagators illustrate where propagators may occur, but are not required to exist; no other regions illustrated may support additional propagators.}\label{fig 3 cases}
@@
 
-In each of the four cases, when we remove the propagator labelled $p$ we obtain a diagram which satisfies the statement of the theorem by the induction hypothesis, and contains a propagator $q = (i,j)$ with no other propagators inside it (although this region may or may not contain unsupported vertices which we will call $l, l+1, \ldots$ as necessary).
-Call this diagram $V$ (figure \ref{fig V diagram}).
+In each of the four cases, when we remove the propagator labelled $p$ we obtain a diagram which satisfies the statement of the theorem by the induction hypothesis, and contains a propagator ${q = (i,j)}$ with no other propagators inside it (although this region may or may not contain non-supporting vertices, which we will call $l, l+1, \ldots$ as necessary).
+Let $V$ be the diagram obtained by removing the propagator $p$ from $W$ (Figure \ref{fig V diagram}).
 
@@
 \includegraphics[scale=0.8]{Vdiagram_modified}
-\caption{Diagram $V$ is $W$ with $p$ removed; there are no propagators inside $q = (i,j)$, though there may be up to 4 unsupported vertices labelled $l, l+1, \ldots$.}
+\caption{Diagram $V$ is $W$ with $p$ removed; there are no propagators inside $q = (i,j)$, though there may be up to 4 non-supporting vertices labelled $l, l+1, \ldots$.}
 \label{fig V diagram}
@@
 Consider the fourth case of Figure~\ref{fig 3 cases} first, as it is the easiest.
-In this case the support of $p$ is unsupported in $V$ so for every propagator $r$ in $V$ (including $q$) $J_r^{(V)} = J_r^{(W)}$.
-Additionally, $J_p^{(W)}(l+a) = \{l+a\}$ for $a\in\{1,2,3\}$ and $J_p^{(W)}(l) = [n] \backslash \{l+1, l+2, l+3\}$ which proves the result in this case.
+In this case, the vertices $\{l,l+1,l+2,l+3 \}$ which support $p$ in $W$ are non-supporting in $V$, so for every propagator $r$ in $V$ (including $q$) we have $J_r^{(V)} = J_r^{(W)}$; these are non-empty cyclic intervals in the correct order by the induction hypothesis.
+Additionally, it is clear from Figure~\ref{fig 3 cases} that $J_p^{(W)}(l+a) = \{l+a\}$ for $a\in\{1,2,3\}$ and $J_p^{(W)}(l) = [n] \backslash \{l+1, l+2, l+3\}$.
+The result therefore holds in this case.
 
 Now we proceed to consider the first three cases of Figure~\ref{fig 3 cases}.
-We first describe $J_q^{(V)}(*)$: since there are no propagators inside $q$, we see from the diagram that
+We first describe $J_q^{(V)}(*)$, which can be handled identically for all three cases.
+
+In $V$ there are no propagators inside $q$, so we see from Figure~\ref{fig V diagram} that
 \[l, l+1, \ldots ,j \in J^{(V)}_q(j) \text{ (if $l$ exists) and }  j+1 \in J^{(V)}_q(j+1).\]
-Note that $j+2 \not\in J^{(V)}_q(j+1)$ by Lemma~\ref{lem no fourth vertex}, so $J^{(V)}_q(j+1) = \{j+1\}$ and $j+2 \in J^{(V)}_q(i)$ by the induction hypothesis.
+Note that $j+2 \not\in J^{(V)}_q(j+1)$ by Lemma~\ref{lem no fourth vertex}, so by the induction hypothesis we must have $J^{(V)}_q(j+1) = \{j+1\}$ and $j+2 \in J^{(V)}_q(i)$.
 Thus there exist vertices $d,e \in [j+2,i+1]$ with $d <e$, such that
@@
 
-We now examine what happens in each of the three cases.
+We now consider what happens as we move from $V$ to each of the three remaining cases for $W$.
+We need to consider both $J^{(W)}_p$ and $J^{(W)}_r$ for $r \neq p$, since the addition of $p$ can have a knock-on effect on later steps in the algorithm.
 
@@
 
-\textbf{Left two cases}: In both of these cases, $p$ has limited effect on the Grassmann necklace of $W$ due to the presence of at least one previously unsupported vertex $l$.
+\textbf{Left two cases}: These cases behave essentially identically (except when $j$ or $j+1$ are not in the support of $p$, which can occur in the second case only; see below) so we handle the majority of the proof for these two cases simultaneously.
 Let $1\leq a\leq 3$ be the number of unsupported vertices inside $q$ in $V$; so these vertices are $l, \ldots, l+a-1$.
@@
 Note that $l, \ldots, l+a-1$ are all in the support of $p$.
-We first calculate $I^{(W)}_w$ for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$: if $w\in J_q^{(V)}(i)$ then
+
+We first calculate $I^{(W)}_w$ for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$.
+Note that $p$ has no effect on other propagators for starting vertices in this range, while the value of $I^{(W)}_w(p)$ depends on how soon $q$ is assigned to a vertex, i.e.
+on the value of $I^{(V)}_w(q)$.
+Thus, if $w\in J_q^{(V)}(i)$ then
     \[
@@
       \]
-For the majority of the remaining vertices, we use the following observation: if $p$ is the first propagator to contribute to a Grassmann necklace term $I_w^{(W)}$, then the remainder of $I_w^{(W)}$ proceeds identically to the assignments of $I^{(V)}_{w+1}$.
-Thus in both cases, we have for any $0\leq b <a$
+We also need to understand $I^{(W)}_w$ for $w \in \{l,l+1,\ldots,j,j+1\}$.
+For the majority of these vertices, we use the following observation: if $p$ is the first propagator to be assigned a value by $I_w^{(W)}$, then the remainder of $I_w^{(W)}$ proceeds identically to the assignments of $I^{(V)}_{w+1}$.
+Thus we have for any $0\leq b <a$
     \[
@@
       l+b & \text{if } r=p\\
-      I_{l+b}^{(V)}(r) & \text{if } r\neq p
+      I_{l+b+1}^{(V)}(r) & \text{if } r\neq p
     \end{cases}
     \]
-    If $j$ is in the support of $p$ which occurs in all cases except the second case with two vertices in the right hand region then
+Similarly, if $j$ is in the support of $p$, then we have
      \[
@@
          I_{j+1}^{(V)}(r) & \text{if $r\neq p$ and $j$ is in the support of $p$}\\
-         I_{j}^{(V)}(r) & \text{if $r\neq p$ and $j$ is not in the support of $p$}
        \end{cases}
        \]
-       If $j$ is not in the support of $p$, then we must be in the second case with two vertices in the right hand region.
-In this case if we start at $j$ we need to know whether propagators other than $p$ will remain around $i$ and $i+1$ when we reach vertex $i$ in the Grassmann necklace algorithm so as to know what $p$ contributes.
+If $j$ is not in the support of $p$, then we must be in the second case of Figure~\ref{fig 3 cases} with two vertices in the right hand region.
+In this case, if we start the algorithm at $j$ we need to know whether there will be any unassigned propagators other than $p$ when we reach vertex $i$, so as to know what $p$ contributes.
+
 Consider the WLD $X$ formed from $V$ by moving the second end of $q$ to the edge $j-1$ instead of $j$.
@@
 Note that $J_{j}^{(V)}(r) = J_{j}^{(X)}(r)$ for all $r\neq p$ and $J_{j}^{(X)}(r) = J_{j+1}^{(X)}(r)$ for $r\neq q,p$.
-Additionally $I_{j+1}^{(X)}(q) = i$ by the induction hypothesis applied to $X$, and so starting at $j+1$ and assigning propagators to vertices according to the Grassmann necklace algorithm, when we get to the vertex $i$ in $X$ all propagators other than $q$ must have been assigned.
-Starting then at $j$ in $W$ we first assign $q$ to $j$, then proceed to assign as in $X$ starting at $j+1$ and then when we get to $i$ the only propagator left to assign is $j$.
+Additionally $I_{j+1}^{(X)}(q) = i$ by the induction hypothesis applied to $X$, and so if we start at $j+1$ and assign propagators to vertices according to the algorithm, when we reach vertex $i$ in $X$ all propagators other than $q$ must have been assigned.
+Therefore if we start at $j$ in $W$, we first assign $q$ to $j$ then proceed to assign as in $X$ starting at $j+1$, and hence when we get to $i$ the only remaining unassigned propagator is $p$.
 Therefore
        \[
-       I_j^{(W)}(p) = m \text{ if $j$ is not in the support of $p$}
+       I_j^{(W)}(r) = \begin{cases}
+
+       m & \text{if $r =p$ and $j$ is not in the support of $p$} \\
+       I_{j}^{(V)}(r) & \text{if $r\neq p$ and $j$ is not in the support of $p$}\end{cases}
        \] 
-
-For the left two cases of Figure~\ref{fig 3 cases} it remains to consider the starting vertex $j+1$. If $j+1$ is in the support of $p$ then we can argue as above to get
+Finally, we consider what happens when we start the algorithm at vertex $j+1$. If $j+1$ is in the support of $p$ then we can argue as above to get
 \[
@@
        \]
-%Thus if $j+1$ is in the support of $p$ then $m=j-2$, the intervals $J^{(W)}_r(*)$ are still cyclic for all $r \neq p$, and
-%       ***these intervals need checking***
-%\[J^{(W)}_p(j-2) = [j+2,c], \quad J^{(W)}_p(j-1) = [c+1,j-1], \quad J^{(W)}_p(j) = \{j\}, \quad J^{(W)}_p(j+1) = \{j+1\}\]
-%  where
-%  \[
-%  c = \begin{cases} d-1 & \text{if } m=i+1 \\
-%    j-2 & \text{otherwise}
-%      \end{cases}
-%  \]
-%also satisfies the statement of the theorem.
-
 Now suppose $j+1$ is not in the support of $p$.
-If we start at $j+1$ we need to know whether any other propagators remain on edge $i$ when we reach vertex $i$.
+If we start at $j+1$ we need to know whether there are any unassigned propagators supported on edge $i$ when we reach vertex $i$.
 We already know that $J_q^{(V)}(j+1) = \{j+1\}$; in particular this means that $q$ contributes $i$ in $I_{j+2}^{(V)}$.
@@
 In particular if $i$ was assigned in $I^{(V)}_{j+1}$, then it would not be available to assign to $q$ in $I^{(V)}_{j+2}$ as all other propagators supported at $i$ in $V$ come before $q$.
+
 Therefore $p$ is the only potentially unassigned propagator on edge $i$ when we reach vertex $i$ in $W$, and
@@
     \]
-
-    Taking all the possibilities for the left two cases of Figure~\ref{fig 3 cases}, the intervals $J^{(W)}_r(*)$ are still cyclic for all $r \neq p$, and we can assemble the intervals for the $J_p^{(W)}(*)$ as follows.
+We can now describe the intervals $J^{(W)}_r(*)$ for the first two cases of Figure~\ref{fig 3 cases}.
+For $r \neq p$ the intervals are clearly still cyclic and appear in the correct order, and we can assemble the intervals for the $J_p^{(W)}(*)$ as follows.
     \begin{itemize}
@@
     If $m=l$ then either $a=2$ (so $l+1=m+1$, $j=m+2$, and $j+1=m+3$) or $a=3$ (so $l+1=m+1$, $l+2=m+2$, $j=m+3$, and $j+1$ is not in the support of $p$), and in both cases
-    \[
-    J^{(W)}_p(m) = [m+4, m], \  J^{(W)}_p(m+1) = \{m+1\}, \  J^{(W)}_p(m+2) = \{m+2\}, \  J^{(W)}_p(m+3) = \{m+3\},
-    \]
+    \begin{gather*}
+    J^{(W)}_p(m) = [m+4, m], \qquad  J^{(W)}_p(m+1) = \{m+1\}, \\ J^{(W)}_p(m+2) = \{m+2\}, \qquad  J^{(W)}_p(m+3) = \{m+3\},
+    \end{gather*}
     which are nonempty and otherwise as required.
@@
         If $m=i+1$ then checking each of the three different possibilities for $a$ we likewise get
-    \[
-    J^{(W)}_p(m) = [m+4, d-1], \  J^{(W)}_p(m+1) = [d, m+1], \  J^{(W)}_p(m+2) = \{m+2\}, \  J^{(W)}_p(m+3) = \{m+3\},
-    \]
+    \begin{gather*}
+    J^{(W)}_p(m) = [m+4, d-1], \qquad  J^{(W)}_p(m+1) = [d, m+1], \\  J^{(W)}_p(m+2) = \{m+2\}, \qquad  J^{(W)}_p(m+3) = \{m+3\},
+    \end{gather*}
     which are nonempty and otherwise as required.
   \item If $m=i$ then $a=1$ or $a=2$, in the former case $l=m+2$, $j=m+3$ and $j+1$ is not in the support of $p$ so
-    \[
-    J^{(W)}_p(m) = \{m+4\}, \  J^{(W)}_p(m+1) = [m+5, d-1], \  J^{(W)}_p(m+2) = [d, m+2], \  J^{(W)}_p(m+3) = \{m+3\},
-    \]
+    \begin{gather*}
+    J^{(W)}_p(m) = \{m+4\}, \qquad  J^{(W)}_p(m+1) = [m+5, d-1], \\  J^{(W)}_p(m+2) = [d, m+2], \qquad  J^{(W)}_p(m+3) = \{m+3\},
+    \end{gather*}
     while in the latter $l=m+2$, $l+1=m+3$, and $j$ and $j+1$ are not in the support of $p$ so
-    \[
-    J^{(W)}_p(m) = [m+4, j+1], \  J^{(W)}_p(m+1) = [j+2, d-1], \  J^{(W)}_p(m+2) = [d, m+2], \  J^{(W)}_p(m+3) = \{m+3\},
-    \]
+    \begin{gather*}
+    J^{(W)}_p(m) = [m+4, j+1], \qquad  J^{(W)}_p(m+1) = [j+2, d-1], \\  J^{(W)}_p(m+2) = [d, m+2], \qquad  J^{(W)}_p(m+3) = \{m+3\},
+    \end{gather*}
     which are again as required.
@@
 
-\textbf{Third case}: In this case there are no unsupported vertices $l, \ldots$ inside $q$.
+\textbf{Third case}: In this case there are no unsupported vertices $l, l+1, \ldots$ inside $q$.
 Again write $p=(m, m+2)$ where $m\in \{j, j+1, j+2\}$.
+We proceed as in the previous cases, by computing $I^{(W)}_w$ for vertices $w$ in roughly increasing order of difficulty.
+
 For $w \in [n]\backslash\{j+1,m,m+1,m+2,m+3\}$: if $w\in J_q^{(V)}(i)$ or $w\in J_q^{(V)}(i+1)$ then
@@
 Note that $I_{m+2}^{(V)}(r) = I_{m+3}^{(V)}(r)$ for all propagators $r$ in $V$, and that if $j+1\not\in\{m, m+1, m+2, m+3\}$ then $j+2$ and $j+3$ are unsupported in $V$ so in that case $I_{j+2}^{(V)}(r) = I_{j+3}^{(V)}(r) = I_{j+4}^{(V)}(r)$ for $r$ in $V$.
-Therefore, once again we can see that the $J_r^{(W)}(*)$ are cyclic for all $r$ in $V$.
-Assembling the intervals for $p$ we get,
- if $m=j$ then
-\[J_p^{(W)}(m) = [m+4,e-1], \  J_p^{(W)}(m+1) = [e,m], \  J_p^{(W)}(m+2) = [m+1,m+2], \  J_p^{(W)}(m+3) = \{m+3\},\]
- if $m=j+1$ then
-\[J_p^{(W)}(m) = [m+4,m-1], \ J_p^{(W)}(m+1) = [m,m+1], \  J_p^{(W)}(m+2) = \{m+2\}, \  J_p^{(W)}(m+3) = \{m+3\},\]
-and if $m=j+2$ then
-\[J_p^{(W)}(m) = [m+4,m], \  J_p^{(W)}(m+1) = \{m+1\}, \  J_p^{(W)}(m+2) = \{m+2\}, \  J_p^{(W)}(m+3) = \{m+3\}.\]
+
+Therefore, once again we can see that the $J_r^{(W)}(*)$ are cyclic for all $r\neq p$ in $W$.  Assembling the intervals for $p$ we have:
+\begin{itemize}
+\item if $m=j$ then
+\begin{gather*}J_p^{(W)}(m) = [m+4,e-1], \qquad  J_p^{(W)}(m+1) = [e,m], \\  J_p^{(W)}(m+2) = [m+1,m+2], \qquad  J_p^{(W)}(m+3) = \{m+3\},\end{gather*}
+\item if $m=j+1$ then
+\begin{gather*}J_p^{(W)}(m) = [m+4,m-1], \qquad J_p^{(W)}(m+1) = [m,m+1], \\  J_p^{(W)}(m+2) = \{m+2\}, \qquad  J_p^{(W)}(m+3) = \{m+3\},\end{gather*}
+\item if $m=j+2$ then
+\begin{gather*}J_p^{(W)}(m) = [m+4,m], \qquad  J_p^{(W)}(m+1) = \{m+1\}, \\  J_p^{(W)}(m+2) = \{m+2\}, \qquad  J_p^{(W)}(m+3) = \{m+3\}.\end{gather*}
 The result now follows by induction.

### 2019-01-04 General WLD combinatorics.tex
now with all tex tags actually closed

@@
 
-Talk about Grassmann Necklaces and how it defines a cell in a CW complex of $\Gr(k,n)$. Also talk about how this is exactly all the non-negative matrices that represent a particular positroid.
-
-Also talk about Le diagrams.
+% Talk about Grassmann Necklaces and how it defines a cell in a CW complex of $\Gr(k,n)$. Also talk about how this is exactly all the non-negative matrices that represent a particular positroid.
+
+% Also talk about Le diagrams.
+
+[We probably need a subsection for background here.
+Probably move the definition of Grassmann necklace up to here, a few words about positroids and Postnikov's work, def of Le diagrams and GNs, why it's useful to be able to translate between WLD, GN, Le diagrams at will.
+]
 
@@
 \begin{gather*}J_p^{(W)}(m) = [m+4,m], \qquad  J_p^{(W)}(m+1) = \{m+1\}, \\  J_p^{(W)}(m+2) = \{m+2\}, \qquad  J_p^{(W)}(m+3) = \{m+3\}.\end{gather*}
+\end{itemize}
 The result now follows by induction.

### 2019-01-04 General WLD combinatorics.tex
Some general tweaks to 2.3

--- 2019-01-01 General WLD combinatorics.tex
@@
 
-We begin by proving some useful facts about flats of matroids associated to admissible Wilson loop diagrams.
+We begin by proving some useful facts about propagator flats, and flats of matroids associated to admissible Wilson loop diagrams more generally.
 
@@
 \begin{cor} \label{classifyflats}
-If $F$ is a flat of a Wilson loop diagram, it can be written as the disjoint union of a cyclic propagator flat and an independent flat. \end{cor}
-
-In particular, any propagator flat can be written as a union of a cyclic propagator flat and an independent flat.
-
+If $F$ is a flat of a Wilson loop diagram, it can be written as the disjoint union of a cyclic propagator flat and an independent set and the set of non-supportive vertices. \end{cor}
+
+In particular, any propagator flat can be written as a union of a cyclic propagator flat, an independent set and $F(\emptyset)$ for the appropriate Wilson loop diagram.
+
+Next we examine properties of propagator flats associated to the complement of Wilson Loop diagrams.
 %Finally, we note the differences between subdiagrams of Wilson loop diagrams, and restrictions or cotractions of the associated matroids.

### 2019-01-04 General WLD combinatorics.tex
readability/notation updates to section 3.1 and 3.2

--- 2019-01-04 General WLD combinatorics.tex
@@
 
-%\note{I don't think rank of a vertex (in the sense of number of propagators supported on it) was ever used, so I removed the definition}
-%\note{rank probably isn't a good word; do we have a better one?}
-%\begin{dfn}\label{vertex rank}
-%Let $i$ be a vertex in $W$. We define the {\bf rank} of $i$ to be $|Prop(i)|$, i.e. the number of propagators supported on $i$.
-%\end{dfn}
-
 \begin{dfn}\label{props inside p}
 Let $p$ be a propagator supported on $(i,j)$ in $W$.
-The region bounded by $p$ and the edge of the Wilson loop diagram from $i$ to $j+1$ is refered to as the region {\bf inside} $p$, and the complement is the region {\bf outside }$p$.
+The region of $W$ bounded by $p$ and the edge of the Wilson loop diagram from $i$ to $j+1$ is refered to as the region {\bf inside} $p$, and the complement is the region {\bf outside }$p$.
 The set of propagators inside (resp.
@@
 \end{dfn}
+In other words, the length of $p$ is the number of vertices inside $p$.
 
@@
 The following observations about propagators of short length in $W$ are easily verified:
-\begin{itemize}
+\begin{enumerate}
+\item If $p = (i,i+3)$ is a propagator of length 3, then the middle vertex $i+2$ supports at most one propagator.
 \item If every vertex in $W$ supports at least one propagator, then $W$ admits at least one propagator of length 2.
-\item If $p = (i,i+3)$ is a propagator of length 3, then the middle vertex $i+2$ supports at most one propagator.
-\end{itemize}
+\end{enumerate}
 \end{rmk}
 
-The following lemma establishes certain configurations of propagators that must exist in any admissible diagram with no unsupported vertices.
+The following lemma establishes certain configurations of propagators that must exist in any admissible diagram with no non-supporting vertices (i.e.
+with $F(\emptyset) = \emptyset$).
 We make use of this result in several induction proofs below.
+Recall from Definition~\ref{admisdfn} that a {\em weakly admissible} diagram is one that satisfies the density and non-crossing conditions but does not require that $|V(\cP)| \geq |\cP| + 4$.
 
@@
   \end{enumerate}
-  %Then exactly one of the following two things occurs.
-  %\begin{enumerate}
-  %  \item $W$ has a propagator of length 3 with a propagator of length 2 inside it.
-  %  \item $W$ admits no propagators of length 3, and one or more of the following things occurs.
-  %    \begin{enumerate}
-  %      \item There is a propagator of length $2$, say $(i, i+2)$ such that no other propagators ends on either the edge $i$ or the edge $i+2$.\label{item lonely 2}
-  %      \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator ends between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
-  %      \item There exists a propagator of length 4 with only a propagator of length 2 inside it.\label{item 4 and 2}
-  %    \end{enumerate}
-  %\end{enumerate}
 \end{lem}
@@
 \begin{proof}
-  Suppose first that $W$ has a propagator of length $3$, $p=(i, i+3)$.
-By Remark~\ref{rem:props of length 2 and 3} along with the fact that every vertex of $W$ supports at least one propagator, we have that $i+2$ supports exactly one propagator and this propagator must have length 2 by noncrossingness.
+Suppose first that $W$ has a propagator of length $3$, say $p=(i, i+3)$.
+By Remark~\ref{rem:props of length 2 and 3} and the fact that every vertex of $W$ supports at least one propagator, we have that $i+2$ supports exactly one propagator and this propagator must have length 2 by noncrossingness.
 This gives us an instance of configuration~\ref{item big and 2} from the statement.
@@
 %a configuration \eqref{eq:2 prop config} we are done,
-so suppose otherwise: 
-By assumption $p_1$ is not in configuration \ref{item pair of 2s}, there are no propagators of length $3$, and every vertex is supported.
+so suppose otherwise. 
+By assumption: $p_1$ is not in configuration \ref{item pair of 2s}, there are no propagators of length $3$, and every vertex is supported.
 Therefore there must exist a propagator $q_1$ of length $\geq 4$ with one end on edge $j_1$ or on edge $j_1-1$ or on edge $j_1-2$.
@@
 Now suppose $q_{r}$ exists by the induction hypothesis and bounds a region $[i_r,k_r]$ not containing any $p_i$ for $i\leq r$.
-Consider the restricted diagram $W_r:=W_{[i_r,k_r]}$; by the original hypotheses on $W$ every vertex $l \in [i_r+2,k_r-2]$ (which is a non-empty interval since $\ell(q_r) \geq 4$) must have support $\geq 1$, while the same is true for $l \in \{i_r,i_r+1,k_r-1,k_r\}$ because of $q_r$.
+Consider the restricted diagram $W_r:=W_{[i_r,k_r]}$; by the original hypotheses on $W$ every vertex $l \in [i_r+2,k_r-2]$ (which is a non-empty interval since $\ell(q_r) \geq 4$) must have support $\geq 1$, while the same is true for $l \in \{i_r,i_r+1,k_r-1,k_r\}$ because these vertices support $q_r$.
 
@@
 
-The overall result, then follows by induction.
+The overall result then follows by induction.
 
 \note{The picture didn't apply any longer, but perhaps a new one would be nice?}
-\note{Also, the way you had it set out, you never needed a minimality argument; this was essentially beacause in your third picture, you could choose the side which didn't contain $p_{r+1}$.
-The same argument could work here, but I was finding it was getting a bit heavy to explain it that way, and the minimality approach seemed like it was lighter.
-See what you think}
+\end{proof}
+
 %% this was 100% a productive use of my time
@@
 In the third case, note that \textit{both} ends of $p_{r+1}$ must share their edge with a propagator of length $\geq 4$; the non-crossing hypothesis on propagators guarantees that at least one will bound a region not containing $p_{r+1}$.
-\end{proof}
 
@@
 
-Here, we give an algorithm for passing from Wilson loop diagrams to Grassmann Necklaces.
+Until now, the positroid associated to a Wilson loop diagram $W$ could only be obtained by computing the matrix $C(W)$ associated to $W$, listing all bases of the induced matroid $M(W)$, and constructing the Le diagram or Grassmann necklace of the positroid ``by eye'' from this list.
+
+In this section, we give an algorithm for passing directly from the Wilson loop diagrams to its Grassmann necklace.
+This not only greatly simplifies the process above, but will also allow us to relate the behavior of the positroid $M(W)$ directly to the configuration of progators in $W$.
 
@@
 This in turn induces a total order on $\binom{[n]}{k}$, namely the lexicographic order with respect to $<_j$.
-It also induces a separate partial order $\gale{j}$ on $\binom{[n]}{k}$ (the \textit{Gale order}), which is defined as follows: if $A = [a_1 <_j a_2 <_j \dots <_j a_k]$,  $B = [b_1 <_j b_2 <_j \dots <_j b_k] \in \binom{[n]}{k}$, then
+It also induces a separate partial order $\gale{j}$ on $\binom{[n]}{k}$ (the \textit{Gale order} [ref]), which is defined as follows: for
+\[A = \{a_1 <_j a_2 <_j \dots <_j a_k\} \text{ and } B = \{b_1 <_j b_2 <_j \dots <_j b_k\} \in \binom{[n]}{k},\] we say that
 \[A \gale{j} B \text{ if and only if } a_r \leq_j b_r \text{ for all }1 \leq r \leq k.\]
-For example, in $\binom{[6]}{3}$ we have $[2,5,6]\gale{2} [2,6,1]$ but $[2,5,6]\not\gale{2}[3,4,6]$.
+For example, in $\binom{[6]}{3}$ we have $\{2,5,6\}\gale{2} \{2,6,1\}$ but $\{2,5,6\}\not\gale{2}\{3,4,6\}$.
 
 \begin{dfn}\label{def:grassmann necklace}
-A Grassmann necklace of type $(k,n)$ is a sequence $\II = (I_1, \dots, I_n)$ of $n$ elements $I_i \in \binom{[n]}{k}$, such that
+A Grassmann necklace of type $(k,n)$ is a sequence $(I_1, \dots, I_n)$ of $n$ sets $I_i \in \binom{[n]}{k}$ such that for each $i \in [n]$:
 \begin{itemize}
-\item if $i \in I_i$, then $I_{i+1} = \big(I_i \backslash \{i\}\big) \cup \{j\}$ for some $j \in \interval{1}{n}$.
+\item if $i \in I_i$, then $I_{i+1} = \big(I_i \backslash \{i\}\big) \cup \{j\}$ for some $j \in[n]$.
 \item if $i \not\in I_i$, then $I_{i+1} = I_i$.
 \end{itemize}
+By convention, we set $I_{n+1} = I_1$.
 \end{dfn}
 
-By [ref], the Grassmann necklaces of type $(k,n)$ are in 1-1 correspondence with the positroid cells in $Gr(k,n)^{tnn}$.
-Further, if $\II$ is the Grassmann necklace associated to a cell $\PP$, then the bases of $\PP$ can be computed using the Gale order $\gale{i}$ for each $i \in [n]$:
-\[\BB(\PP) = \left\{J \in \binom{[n]}{k}\ :\ I_i \gale{i} J \ \forall i \in [n]\right\}.\]
-We now describe an algorithm that, when applied to an admissible Wilson loop diagram, produces exactly the Grassmann necklace of the corresponding positroid.
+By [ref][Oh or Postnikov?], the Grassmann necklaces of type $(k,n)$ are in 1-1 correspondence with the positroid cells in $\Gr(k,n)$.
+Further, if $(I_1, \dots, I_n)$ is the Grassmann necklace associated to a positroid $M = ([n],\cB)$, then by [ref][Oh] the bases of $M$ can be computed using the Gale order $\gale{i}$ for each $i \in [n]$:
+\[\cB = \left\{J \in \binom{[n]}{k}\ :\ I_i \gale{i} J \ \forall i \in [n]\right\}.\]
+We now describe an algorithm that constructs the Grassmann necklace of an admissible Wilson loop diagram from the diagram.
+The fact that Algorithm~\ref{alg:put GN on WLD} does construct the required Grassmann necklace is proved in Theorem~\ref{res:alg gives GN}.
 
@@
 
-If the propagator $p$ is removed at vertex $i$ according to the algorithm for $I_a$, we say that $p$ \emph{contributes} $i$ to $I_a$.
+If the algorithm assigns vertex $j$ to propagator $p$ from starting vertex $i$, we say that $p$ \emph{contributes} $j$ to $I_i$.
 Notationally, we represent this by allowing the $I_i$ symbol to represent a function as well as a set, as follows:
 \begin{dfn}\label{def I_i as a function}
-Let $W = (\cP, [n])$ be an admissible Wilson loop diagram. For each $a \in [n]$, define a function $I_a : \cP \longrightarrow [n]$ by
-\[I_a(p) := \text{the vertex label that $p$ contributes to $I_a$ in Algorithm~\ref{alg:put GN on WLD},}\]
+Let $W = (\cP, [n])$ be an admissible Wilson loop diagram. For each $i \in [n]$, define a function $I_i : \cP \longrightarrow [n]$ by
+\[I_i(p) := \text{the vertex label that $p$ contributes to $I_i$ in Algorithm~\ref{alg:put GN on WLD},}\]
 for each $p \in \cP$.
@@
 \begin{proof}
-Suppose for contradiction that we have $p = (a,b)$ with $i\leq_i a <_i b$ and $I_{i}(p) = b+1$. We may choose $p$ such that $|\interval{a+1}{b}|$ is minimal amongst propagators with this property.
+Suppose for contradiction that we have $p = (a,b)$ with $i\leq_i a <_i b$ and $I_{i}(p) = b+1$. We may choose $p$ such that $|[a+1,b]|$ is minimal amongst propagators with this property.
 
@@
 Now suppose $W$ has more than one propagator.
-Since non-supporting vertices have no effect on the Grassmann necklace algorithm, it suffices to prove the result for $W$ with $F(\emptyset) = \emptyset$.
+Since non-supporting vertices play no role in Algorithm~\ref{alg:put GN on WLD}, it suffices to prove the result for $W$ with $F(\emptyset) = \emptyset$.
 Then by Lemma~\ref{lem sian}, $W$ has at least one of the four situations illustrated in Figure~\ref{fig 3 cases}.
@@
 The result now follows by induction.
-
-%Fix $p = (i, j)$. By symmetry, we need only consider the vertices $j$, $j+1$.
-%
-%Let $k_1 \ldots k_r$ be the set of propagators of the form $k_x = (i_{k_x}, j)$, with $i <_{j+1} k_1 <_{j+1} \ldots k_r <_{j+1} j$.
-Write $k_{r+1}$ to be the counterclockwise most propagator with an end on the edge $j-1$, if it exists.
-If $r \geq 2$ or $r+1 = 2$, then both $P_j(p)$ and $P_{j+1}(p)$ exists for some subset of $a \in [n]$.
-If $r=1$ or $r+1= 2$ then only $P_j(p)$ exists.
-Otherwise, $P_j(p) = \emptyset$.
-%
-%Consider a protecting set $P_j(p) \subset \cP$ such that $k_1 \in P_j(p)$, if it exists.
-Write it \bas P_j(p) = \{s_1 \ldots s_r, t_2, \ldots t_r\} \;.\eas Define $b_1 = i_{s_r}+1$.
-By construction, $P_j(p)$ prevents $p$ from contributing $j$ to $I_a$ for all $a \in [b_1+1, j]$.
-We see that, if $r >0$, for all $a \in [i+2, b_1]$, $p$ contributes $j$ to $I_a$.
-(\hlfix{Note that by construction, one cannot have $i_{s_r}+1 <_{j+1} i+2$.}{verify}) This is because in this range, $j$ is the first vertex of $p$ encountered by Algorithm \ref{Alg: put GN on WLD}.
-Furthermore, by Lemma \ref{protect conv lem}, and definition \ref{protect dfn} if $i_{s_r}+1 \not <_{j+1} i+2$ $P_1$ does not protect $p$ at $j$ for $a$ in this range.
-If $r = 0$ then $p$ contributes $j$ for all $a \in [i+2, j]$.
-In this case, we say $b_1 = j$.
-%
-%Now suppose $r$ is such that both $P_j(p)$ and $P_{j+1}(p)$ exists for some $a$.
-This time $k_2 \subset P_j(p)$.
-Define $b_2 = i_{s_r}+1$, where now we use $s_r$ to indicate the last propagator in this new protecting set.
-By construction, $P_{j+1}(p)$ prevents $p$ from contributing $j+1$ to $I_a$ for all $a \in [b_2+2, j+1]$.
-Therefore, if both protecting sets exist, for all $a \in [b_1+1, b_2]$ $p$ contributes $j+1$ to $I_a$.
-This is exactly the range in which there is exactly one valid protecting set.
-Therefore, in this range, $j+1$ is the first vertex of $p$ without a protective set.
-If there is no $a$ such that both $P_j(p)$ and $P_{j+1}(p)$ do not hold, then  $p$ contributes $j+1$ for all $a \in [b_1 +1, j+1]$.
-%
-%Finally, for $r > 1$, and $j_{k_2}=j$,$a \in [b2+1, j+1]$, $p$ contributes $i$ to $I_a$.
-Again, for all $a$ in this range, both sets $P_j(p)$ and $P_{j+1}(p)$ protect $p$ at $j$ and $j+1$ from $a$.
-Furthermore, by Corrollary \ref{protect cor}, there can be no protective sets of $i$ or $i+1$ in this range.
-%
-%By switching the roles of $i$ and $j$, we see that for every element of $V(p)$, there is a non-empty cyclic interval such that $p$ contributes $v$ to all $I_{a}$ for in said interval.
-
 \end{proof}
@@
 \begin{proof}
-  Because the nonzero entries of $C(W)$ are independent indeterminants,
-  $J$ is an independent set is if and only if there is some choice of $|J|$ nonzero entries of $C(W)$ one in each row associated to an element of $J$ and each in different columns.
+Because the nonzero entries of $C(W)$ are independent indeterminants, $J$ is an independent set is if and only if there is some choice of $|J|$ nonzero entries of $C(W)$ one in each row associated to an element of $J$ and each in different columns.
 
@@
 
-\begin{prop}\label{res:alg gives GN}
-The sequence of $k$-subsets obtained by applying Algorithm~\ref{alg:put GN on WLD} to an admissible diagram $W$ is exactly the Grassmann necklace of the positroid associated to $W$; specifically if we let  $I_i$ be the set of labels on edge $(i,i+1)$ then the sequence $\II = (I_1, \dots, I_n)$ is the Grassmann necklace of the positroid associated to $W$.
-\end{prop}
-
-\begin{proof}
-Let $I_i$ be the set of labels on edge $(i,i+1)$; the sequence $\II = (I_1, \dots, I_n)$ is a Grassmann necklace if and only if $I_{i+1} \supseteq I_i \backslash \{i\}$ for all $i \in \{1, \dots, n\}$.
+\begin{thm}\label{res:alg gives GN}
+The sequence of $k$-subsets $(I_1,\dots,I_n)$ obtained by applying Algorithm~\ref{alg:put GN on WLD} to all vertices of an admissible diagram $W$ is exactly the Grassmann necklace of $M(W)$.
+\end{thm}
+
+\begin{proof}
+For each $i \in [n]$, let $I_i$ be the set of vertices assigned to the propagators of $W$ by Algorithm~\ref{alg:put GN on WLD} with starting vertex $i$.
+By Lemma~\ref{GN alg well defined}, we know that $|I_i| = k$ for each $i \in [n]$.
+By [ref], the sequence $(I_1, \dots, I_n)$ is a Grassmann necklace if and only if $I_{i+1} \supseteq I_i \backslash \{i\}$ for all $i \in [n]$.
 
@@
 Now suppose that $i \in I_i$.
-Let $p$ be the propagator which contributes $i$ to $I_i$.
-Either $p$ has one end on the edge $(i-1, i)$ or it has one end on the edge $(i, i+1)$.
-In both cases let $(b, b+1)$ be the edge with the other end of $p$.
-
-\textbf{case I}:  Suppose $p$ has one end on $(i-1, i)$.
-Then $p$ is not supported on $i+1$, so in building $I_{i+1}$ we will take the same propagators as in the construction of $I_i$ from vertices $i+1$ up to $b-1$, that is $I_{i+1} \cap \interval{i+1}{b-1} = I_{i} \cap \interval{i+1}{b-1}$.
-Furthermore, by Lemma~\ref{vertex cyclic int lem}, in building $I_{i+1}$, it must be that $p$ is taken at vertex $b$, as otherwise $b$ would never be contributed by $p$.
-Consequently, in building $I_{i+1}$, when at vertex $b$ no propagator still remaining is before $p$.
-This is also true in building $I_i$ when at $b$ since the same propagators have been taken beforehand.
-Additionally $k\geq_i b+1$.
-
-Let $W'$ be the diagram obtained from $W$ by removing $p$ and all propagators under it in the sense of supported between $i+1$ and $b-1$.
-
-By the above observations when we are in $W'$ at $b$ then we are in the same situation with respect to the remaining propagators as if we began at $i$ in $W$ and moved to $b$ following the algorithm; the propagators we took in the latter case are exactly the ones removed to build $W'$.
-Similarly starting at $i+1$ in $W$ and moving to $b+1$ leaves us in the same situations with respect to the remaining propagators as beginning at $b+1$ in $W'$.
+Let $p$ be the propagator which contributes $i$ to $I_i$; thus one end of $p$ must lie on either edge $i-1$ or edge $i$.
+In both cases let $b$ denote the edge supporting the other end of $p$.
+
+\textbf{Case I}:  Suppose $p$ has one end on edge $i-1$.
+Then $p$ is not supported on $i+1$, so in building $I_{i+1}$ we will take the same propagators as in the construction of $I_i$ from vertices $i+1$ up to $b-1$, that is $I_{i+1} \cap [i+1,b-1] = I_{i} \cap [i+1,b-1]$.
+Furthermore, by Lemma~\ref{vertex cyclic int lem}, when building $I_{i+1}$ it must happen that $p$ is taken at vertex $b$, as otherwise $b$ would never be contributed by $p$.
+Consequently, in building $I_{i+1}$, when the algorithm reaches vertex $b$ there cannot be any unassigned propagators remaining that are before $p$.
+This is also true in when the algorithm constructing $I_i$ reaches $b$, since the same propagators have been assigned beforehand.
+Finally, we also note that $k\geq_i b+1$.
+
+Let $W'$ be the diagram obtained from $W$ by removing both $p$ and all propagators inside of $p$ (recall Definition~\ref{props inside p}).
+
+By the above observations, if we commence Algorithm~\ref{alg:put GN on WLD} in $W'$ from vertex $b$, then we are in the same situation with respect to unassigned propagators as if we began at $i$ in $W$ and proceeded to $b$ following the algorithm; the propagators we assigned in the latter case are exactly the ones removed to build $W'$.
+Similarly, starting at $i+1$ in $W$ and moving to $b+1$ leaves us in the same situation with respect to unassigned propagators as beginning at $b+1$ in $W'$ would.
 This gives the equations
 \begin{align*}
-  I_i^W \cap \interval{b}{i-1} & = I_b^{W'} \\
-  I_{i+1}^W \cap \interval{b+1}{i-1} & = I_{b+1}^{W'}
+  I_i^{(W)} \cap [b,i-1] & = I_b^{(W')} \\
+  I_{i+1}^{(W)} \cap [b+1,i-1] & = I_{b+1}^{(W')}
 \end{align*}
 where the diagram is indicated in the superscript.
-Thus we have $k\in I_b^{W'}\backslash\{b\}$ and $k\not\in I_{b+1}^{W'}$ contradicting the minimality of $(W, i, k)$.
-
-\textbf{case II}: Suppose $p$ has one end on $(i, i+1)$.
-Note that by definition $p$ is the propagator contributing $i$ to $I_i$ and so it must be the first propagator in $(i, i+1)$ and hence $p$ contributes $i+1$ to $I_{i+1}$.
-Observe that $k\geq_i i+2$ since $i+1\in I_{i+1}$.
-
-Let $W'$ be the diagram obtained from $W$ just by removing $p$.  Then
+Thus we have $k\in I_b^{(W')}\setminus\{b\}$ and $k\not\in I_{b+1}^{(W')}$, contradicting the minimality of $(W, i, k)$.
+
+\textbf{Case II}: Suppose $p$ has one end on edge $i$.
+Note that by assumption we have $I_i(p) = i$; this means that $p$ must be the first propagator lying on edge $i$, and hence we must have $I_{i+1}(p) = i+1$ as well.
+Observe also that $k\geq_i i+2$ since $i+1\in I_{i+1}$.
+
+Let $W'$ be the diagram obtained from $W$ by removing only the propagator $p$.  Then we have
 \begin{align*}
-  I_i^W \backslash \{i\} & = I_{i+1}^{W'} \\
-  I_{i+1}^W \backslash \{i+1\} & = I_{i+2}^{W'}
+  I_i^{(W)} \backslash \{i\} & = I_{i+1}^{(W')} \\
+  I_{i+1}^{(W)} \backslash \{i+1\} & = I_{i+2}^{(W')}
 \end{align*}
-since in both cases in $W'$ we are simply taking the remaining propagators in the same way as we would have in $W$ after taking $p$ for the previous vertex.
-Since $k \neq i+1$, we have $k\in I_{i+1}^{W'}\backslash\{i+1\}$ but $k\not\in I_{i+2}^{W'}$ contradicting the minimiality of $(W, i, k)$
+since in both cases the algorithm in $W'$ proceeds identically to that in $W$ after assigning $p$.
+Since $k \neq i+1$, we have $k\in I_{i+1}^{(W')}\setminus\{i+1\}$ but $k\not\in I_{i+2}^{(W')}$, contradicting the minimiality of $(W, i, k)$
 
@@
 
-We have shown that $\II$ is a Grassmann necklace; it remains to check that this Grassmann necklace defines the positroid $\PP_W$ associated to $W$.  We need to show that:
+We have shown that $(I_1,\dots,I_n)$ is a Grassmann necklace; it remains to check that this Grassmann necklace corresponds to the positroid $M(W)$.  We need to show that:
 \begin{itemize}
-\item For each $i \in \interval{1}{n}$, $I_i$ is a basis for $\PP_W$.
-\item If $J$ is lexicographically smaller than $I_i$ with respect to $<_i$, then $J$ is not a basis for $\PP_W$.
+\item For each $i \in [n]$, $I_i$ is a basis for $M(W)$.
+\item If $J$ is lexicographically smaller than $I_i$ with respect to $<_i$, then $J$ is not a basis for $M(W)$.\note{Si\^an note to self: check whether it's lex smaller or Gale smaller}
 \end{itemize}
-The algorithm is pairing each $j \in I_i$ with a unique propagator supported on that vertex so by Lemma~\ref{lem basis as perm} $I_i$ is a basis for $\PP_W$.
+The algorithm is pairing each $j \in I_i$ with a unique propagator supported on that vertex so by Lemma~\ref{lem basis as perm} $I_i$ is a basis for $M(W)$.
 %%Recall from [ref] that a $k$-subset $J \in \binom{[n]}{k}$ is a basis for $\PP_W$ if and only if it has no subset $U \subseteq J$ such that $|U| > |Prop(U)|$.
@@
 
-Suppose we have $J$ such that $J$ is a basis and yet is lexicographically less than $I_i$ with respect to $<_i$.
-By Lemma~\ref{lem basis as perm} there is a set bijection between $J$ and the propagators of $W$ such that the propagator associated to $j$ is supported on vertex $j$.
+Suppose we have a $k$-set $J$ such that $J$ is a basis for $M(W)$ and yet is lexicographically less than $I_i$ with respect to $<_i$.
+By Lemma~\ref{lem basis as perm} there is a set bijection between $J$ and the propagators of $W$ such that for each $j \in J$, the propagator associated to $j$ is supported on vertex $j$.
 Choose one such bijection.
 For a propagator $p$ of $W$ write $J(p)$ for the associated $j$ according to this bijection.
-Similarly write $I_i(p)$ for the vertex assigned to $p$ by the algorithm.
+
 Since $J$ is lexicographically smaller than $I_i$, the $<_i$-smallest element of the symmetric difference of $J$ and $I_i$ is some $j_0\in J$, $j_0 \not\in I_i$.
-
 Let $p$ be the propagator such that $J(p)=j_0$.
-Since $j_0\not\in I_i$ but $p$ is supported at $j_0$, then $I_i(p) <_i j_0$.
-Thus the propagator $p$ has the following property: $I_i(p) <_i J(p)$ and $I_i\cap \interval{i}{I_i(p)} = J\cap \interval{i}{I_i(p)}$.
-Call this property $A$.
-
-{}From the previous paragraph we conclude that if we ever had a $J$ which is lexicographically less than $I_i$ and yet a basis of $\PP_W$ then there exists a propagator $p$ which has property $A$.
+Since $j_0\not\in I_i$ but $p$ is supported at $j_0$, then $p$ must have been assigned to an earlier vertex by $I_i$, i.e.
+we have $I_i(p) <_i j_0$.
+Thus the propagator $p$ has the following property, which we call property $A$:
+\begin{equation}\label{propertyA}\tag{A}I_i(p) <_i J(p) \text{ \ and \ }I_i\cap [i,I_i(p)] = J\cap [i,I_i(p)]. \end{equation}
+
+{}From the previous paragraph we conclude that if we ever had a $J$ which is lexicographically less than $I_i$ and yet a basis of $M(W)$, then there exists a propagator $p$ which has property $A$.
 
 Finally, we will prove that whenever there is a propagator $p$ which has property $A$ then there is another propagator $r$ which also has property $A$ and for which $I_i(r) <_i I_i(p)$.
-Since $I_i$ is finite this would lead to infinte regress and hence is impossible and thus there can be no such $J$ which will complete the proof of the proposition.
+This would lead to an infinte regress, contradicting the finiteness of $I_i$; thus there could be no such $J$, which will complete the proof of the proposition.
 
 So suppose $p$ has property $A$.
-The same vertices in $\interval{i}{I_i(p)}$ are in the image of the assignment from $J$ and the image of the assignment from $I_i$ so the same number of propagators are assigned to vertices in this interval by each assignment.
+The same vertices in $[i,I_i(p)]$ are in the image of the assignment from $J$ and the image of the assignment from $I_i$ so the same number of propagators are assigned to vertices in this interval by each assignment.
 However $p$ is one of the propagators assigned to a vertex in this interval in $I_i$ but not in $J$.
-Thus there exists a propagator $q$ for which $J(q)\in \interval{i}{I_i(p)}$ but $I_i(q) >_i I_i(p)$.
-Therefore $J(q)<_i I_i(q)$ and  $I_i\cap \interval{i}{J(q)} = J\cap \interval{i}{J(q)}$.
+Thus there exists a propagator $q$ for which $J(q)\in [i,I_i(p)]$ but $I_i(q) >_i I_i(p)$.
+Therefore $J(q)<_i I_i(q)$ and  $I_i\cap [i,J(q)] = J\cap [i,J(q)]$.
 This is analogous to property $A$ but with the roles of $J$ and $I_i$ switched.
-Thus by the same argument we must have a propagator $r$ for which $I_i(r)\in \interval{i}{J(q)}$ but $J(r)>_i J(q)$.
-Therefore $r$ has property $A$ which is what we wanted to prove.
-
+Thus by the same argument we must have a propagator $r$ for which $I_i(r)\in[i,J(q)]$ but $J(r)>_i J(q)$.
+It follows that $r$ also has property $A$ and that
+\[I_i(r) \leq_i J(q) \leq_i I_i(p)\]
+\hlfix{as required.}{We need $I_i(r) <_i I_i(p)$ but I'm having trouble seeing it?}
 \end{proof}
@@
 In an arbitrary Grassmann necklace, it is possible for an index $i$ to appear in no terms of the Grassmann necklace (a {\em loop}) or in all terms of the necklace (a {\em coloop}).
-Clearly any vertex of $W$ that supports no propagators will yield a loop [ref][check: is this iff?], but with Theorem [ref][cyclic intervals thm] in hand we can now easily verify that admissible Wilson loop diagrams do not admit coloops.
+Using Theorem~\ref{res:alg gives GN}, a characterization of the loops and coloops of the Grassmann necklace associated to a Wilson loop diagram follows easily.
 
 \begin{cor}\label{no coloops}
-Grassmann necklaces coming from admissible Wilson loop diagrams have no coloops, that is no indices $a$ such that $a \in I_i$ for all $i$.
+Grassmann necklaces coming from admissible Wilson loop diagrams have no coloops. A vertex $j$ is a loop if and only if $j$ supports no propagators. 
 \end{cor}
 \begin{proof}
-For any $a \in [n]$, $a-1$ is maximal with respect to the $<_{a}$ order. Therefore there is no propagator $p$ with $I_{a}(p) = a-1$ by Lemma~\ref{lem no fourth vertex}, i.e. $a-1 \not\in I_{a}$.
+For any $i \in [n]$, $i-1$ is maximal with respect to the $<_{i}$ order.
+Therefore there can be no propagator $p$ with $I_{i}(p) = i-1$ by Lemma~\ref{lem no fourth vertex}, i.e.
+$i-1 \not\in I_{i}$.
+Thus the Grassmann necklace admis no coloops.
+
+If $j \in [n]$ is a loop then $j \not\in I_j$, which can only happen if there are no propagators supported on vertex $j$.
+Conversely, if $j$ supports no propagators, then Algorithm ~\ref{alg:put GN on WLD} never assigns a propagator to $j$ and hence $j \not\in I_i$ for all $i \in [n]$.
 \end{proof}

### 2019-01-04 General WLD combinatorics.tex

@@
 
-% Talk about Grassmann Necklaces and how it defines a cell in a CW complex of $\Gr(k,n)$. Also talk about how this is exactly all the non-negative matrices that represent a particular positroid.
-
-% Also talk about Le diagrams.
-
-[We probably need a subsection for background here.
-Probably move the definition of Grassmann necklace up to here, a few words about positroids and Postnikov's work, def of Le diagrams and GNs, why it's useful to be able to translate between WLD, GN, Le diagrams at will.
-]
+Talk about Grassmann Necklaces and how it defines a cell in a CW complex of $\Gr(k,n)$. Also talk about how this is exactly all the non-negative matrices that represent a particular positroid.
+
+Also talk about Le diagrams.
 
@@
 \end{dfn}
-
-Given a propagator $p$ and a vertex $i$ in its support, it will be very useful in the following to understand on what set of vertices the Grassmann necklace algorithm assigns $i$ to $p$.
-The answer is that the set is a non-empty cyclic interval.
-Lemma~\ref{vertex cyclic int lem} establishes this, but first we need a preliminary lemma which is also useful in its own right.
 
@@
 
+Given a propagator $p$ and a vertex $i$ in its support, it will be very useful in the following to understand on what set of vertices the Grassmann necklace algorithm assigns $i$ to $p$.
+The answer is that the set is a non-empty cyclic interval.
+Lemma~\ref{vertex cyclic int lem} establishes this, but first we need a preliminary lemma which is also useful in its own right.
+
 %\begin{lem}\label{lem last vert}
@@
 
-Given a propagator $p$ of an admissible WLD $W$ and a vertex $i$ in the support of $p$, define
-\[J_p^{(W)}(i) = \{m \in [n] \ : \ I^{(W)}_m(p) = i \},\]
-i.e.
-the set of indices $m$ for which Algorithm [ref] assigns the value $i$ to the propagator $p$ in $W$.
-The following lemma establishes that these sets behave in a simple and predictable manner, a fact which we will repeatedly use in subsequent proofs.
+Given a propagator $p$ of an admissible WLD $W$ and a vertex $i$ in the support of $p$ we will use the notation $J_p^{(W)}(i)$ for the set of indices $m$ where $I_m(p) = l$ where the $I_m$ are the sets calculated by Algorithm~\ref{alg:put GN on WLD}, and using the notation of Definition~\ref{def I_i as a function}.
 
@@
 Let $p=(i,j)$ be a propagator of an admissible WLD $W$ on $n$ vertices.
-Then $J_p^{(W)}(i)$, $J_p^{(W)}(i+1)$, $J_p^{(W)}(j)$, and $J_p^{(W)}(j+1)$ are each non-empty cyclic intervals which partition $[n]$ and occur in the given cyclic order.
+Then $J_p^{(W)}(i)$, $J_p^{(W)}(i+1)$, $J_p^{(W)}(j)$, and $J_p^{(W)}(j+1)$ are each non-empty cyclic intervals of $\{1, \ldots, n\}$ which partition $\{1, \ldots, n\}$ and occur in the given cyclic order.
 \end{lem}
@@
 \begin{proof}
+
 We will prove the result by induction on the number of propagators.
@@
     \includegraphics[scale=0.8]{3cases}
-    \caption{Four cases for admissible WLDs with no non-supporting vertices.
+    \caption{Four cases for admissible WLDs with no unsupported vertices.
 The green half-propagators illustrate where propagators may occur, but are not required to exist; no other regions illustrated may support additional propagators.}\label{fig 3 cases}
@@
 
-In each of the four cases, when we remove the propagator labelled $p$ we obtain a diagram which satisfies the statement of the theorem by the induction hypothesis, and contains a propagator ${q = (i,j)}$ with no other propagators inside it (although this region may or may not contain non-supporting vertices, which we will call $l, l+1, \ldots$ as necessary).
-Let $V$ be the diagram obtained by removing the propagator $p$ from $W$ (Figure \ref{fig V diagram}).
+In each of the four cases, when we remove the propagator labelled $p$ we obtain a diagram which satisfies the statement of the theorem by the induction hypothesis, and contains a propagator $q = (i,j)$ with no other propagators inside it (although this region may or may not contain unsupported vertices which we will call $l, l+1, \ldots$ as necessary).
+Call this diagram $V$ (figure \ref{fig V diagram}).
 
@@
 \includegraphics[scale=0.8]{Vdiagram_modified}
-\caption{Diagram $V$ is $W$ with $p$ removed; there are no propagators inside $q = (i,j)$, though there may be up to 4 non-supporting vertices labelled $l, l+1, \ldots$.}
+\caption{Diagram $V$ is $W$ with $p$ removed; there are no propagators inside $q = (i,j)$, though there may be up to 4 unsupported vertices labelled $l, l+1, \ldots$.}
 \label{fig V diagram}
@@
 Consider the fourth case of Figure~\ref{fig 3 cases} first, as it is the easiest.
-In this case, the vertices $\{l,l+1,l+2,l+3 \}$ which support $p$ in $W$ are non-supporting in $V$, so for every propagator $r$ in $V$ (including $q$) we have $J_r^{(V)} = J_r^{(W)}$; these are non-empty cyclic intervals in the correct order by the induction hypothesis.
-Additionally, it is clear from Figure~\ref{fig 3 cases} that $J_p^{(W)}(l+a) = \{l+a\}$ for $a\in\{1,2,3\}$ and $J_p^{(W)}(l) = [n] \backslash \{l+1, l+2, l+3\}$.
-The result therefore holds in this case.
+In this case the support of $p$ is unsupported in $V$ so for every propagator $r$ in $V$ (including $q$) $J_r^{(V)} = J_r^{(W)}$.
+Additionally, $J_p^{(W)}(l+a) = \{l+a\}$ for $a\in\{1,2,3\}$ and $J_p^{(W)}(l) = [n] \backslash \{l+1, l+2, l+3\}$ which proves the result in this case.
 
 Now we proceed to consider the first three cases of Figure~\ref{fig 3 cases}.
-We first describe $J_q^{(V)}(*)$, which can be handled identically for all three cases.
-
-In $V$ there are no propagators inside $q$, so we see from Figure~\ref{fig V diagram} that
+We first describe $J_q^{(V)}(*)$: since there are no propagators inside $q$, we see from the diagram that
 \[l, l+1, \ldots ,j \in J^{(V)}_q(j) \text{ (if $l$ exists) and }  j+1 \in J^{(V)}_q(j+1).\]
-Note that $j+2 \not\in J^{(V)}_q(j+1)$ by Lemma~\ref{lem no fourth vertex}, so by the induction hypothesis we must have $J^{(V)}_q(j+1) = \{j+1\}$ and $j+2 \in J^{(V)}_q(i)$.
+Note that $j+2 \not\in J^{(V)}_q(j+1)$ by Lemma~\ref{lem no fourth vertex}, so $J^{(V)}_q(j+1) = \{j+1\}$ and $j+2 \in J^{(V)}_q(i)$ by the induction hypothesis.
 Thus there exist vertices $d,e \in [j+2,i+1]$ with $d <e$, such that
@@
 
-We now consider what happens as we move from $V$ to each of the three remaining cases for $W$.
-We need to consider both $J^{(W)}_p$ and $J^{(W)}_r$ for $r \neq p$, since the addition of $p$ can have a knock-on effect on later steps in the algorithm.
+We now examine what happens in each of the three cases.
 
@@
 
-\textbf{Left two cases}: These cases behave essentially identically (except when $j$ or $j+1$ are not in the support of $p$, which can occur in the second case only; see below) so we handle the majority of the proof for these two cases simultaneously.
+\textbf{Left two cases}: In both of these cases, $p$ has limited effect on the Grassmann necklace of $W$ due to the presence of at least one previously unsupported vertex $l$.
 Let $1\leq a\leq 3$ be the number of unsupported vertices inside $q$ in $V$; so these vertices are $l, \ldots, l+a-1$.
@@
 Note that $l, \ldots, l+a-1$ are all in the support of $p$.
-
-We first calculate $I^{(W)}_w$ for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$.
-Note that $p$ has no effect on other propagators for starting vertices in this range, while the value of $I^{(W)}_w(p)$ depends on how soon $q$ is assigned to a vertex, i.e.
-on the value of $I^{(V)}_w(q)$.
-Thus, if $w\in J_q^{(V)}(i)$ then
+We first calculate $I^{(W)}_w$ for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$: if $w\in J_q^{(V)}(i)$ then
     \[
@@
       \]
-We also need to understand $I^{(W)}_w$ for $w \in \{l,l+1,\ldots,j,j+1\}$.
-For the majority of these vertices, we use the following observation: if $p$ is the first propagator to be assigned a value by $I_w^{(W)}$, then the remainder of $I_w^{(W)}$ proceeds identically to the assignments of $I^{(V)}_{w+1}$.
-Thus we have for any $0\leq b <a$
+For the majority of the remaining vertices, we use the following observation: if $p$ is the first propagator to contribute to a Grassmann necklace term $I_w^{(W)}$, then the remainder of $I_w^{(W)}$ proceeds identically to the assignments of $I^{(V)}_{w+1}$.
+Thus in both cases, we have for any $0\leq b <a$
     \[
@@
       l+b & \text{if } r=p\\
-      I_{l+b+1}^{(V)}(r) & \text{if } r\neq p
+      I_{l+b}^{(V)}(r) & \text{if } r\neq p
     \end{cases}
     \]
-Similarly, if $j$ is in the support of $p$, then we have
+    If $j$ is in the support of $p$ which occurs in all cases except the second case with two vertices in the right hand region then
      \[
@@
          I_{j+1}^{(V)}(r) & \text{if $r\neq p$ and $j$ is in the support of $p$}\\
+         I_{j}^{(V)}(r) & \text{if $r\neq p$ and $j$ is not in the support of $p$}
        \end{cases}
        \]
-If $j$ is not in the support of $p$, then we must be in the second case of Figure~\ref{fig 3 cases} with two vertices in the right hand region.
-In this case, if we start the algorithm at $j$ we need to know whether there will be any unassigned propagators other than $p$ when we reach vertex $i$, so as to know what $p$ contributes.
-
+       If $j$ is not in the support of $p$, then we must be in the second case with two vertices in the right hand region.
+In this case if we start at $j$ we need to know whether propagators other than $p$ will remain around $i$ and $i+1$ when we reach vertex $i$ in the Grassmann necklace algorithm so as to know what $p$ contributes.
 Consider the WLD $X$ formed from $V$ by moving the second end of $q$ to the edge $j-1$ instead of $j$.
@@
 Note that $J_{j}^{(V)}(r) = J_{j}^{(X)}(r)$ for all $r\neq p$ and $J_{j}^{(X)}(r) = J_{j+1}^{(X)}(r)$ for $r\neq q,p$.
-Additionally $I_{j+1}^{(X)}(q) = i$ by the induction hypothesis applied to $X$, and so if we start at $j+1$ and assign propagators to vertices according to the algorithm, when we reach vertex $i$ in $X$ all propagators other than $q$ must have been assigned.
-Therefore if we start at $j$ in $W$, we first assign $q$ to $j$ then proceed to assign as in $X$ starting at $j+1$, and hence when we get to $i$ the only remaining unassigned propagator is $p$.
+Additionally $I_{j+1}^{(X)}(q) = i$ by the induction hypothesis applied to $X$, and so starting at $j+1$ and assigning propagators to vertices according to the Grassmann necklace algorithm, when we get to the vertex $i$ in $X$ all propagators other than $q$ must have been assigned.
+Starting then at $j$ in $W$ we first assign $q$ to $j$, then proceed to assign as in $X$ starting at $j+1$ and then when we get to $i$ the only propagator left to assign is $j$.
 Therefore
        \[
-       I_j^{(W)}(r) = \begin{cases}
-
-       m & \text{if $r =p$ and $j$ is not in the support of $p$} \\
-       I_{j}^{(V)}(r) & \text{if $r\neq p$ and $j$ is not in the support of $p$}\end{cases}
+       I_j^{(W)}(p) = m \text{ if $j$ is not in the support of $p$}
        \]
-Finally, we consider what happens when we start the algorithm at vertex $j+1$. If $j+1$ is in the support of $p$ then we can argue as above to get
+
+For the left two cases of Figure~\ref{fig 3 cases} it remains to consider the starting vertex $j+1$. If $j+1$ is in the support of $p$ then we can argue as above to get
 \[
@@
        \]
+%Thus if $j+1$ is in the support of $p$ then $m=j-2$, the intervals $J^{(W)}_r(*)$ are still cyclic for all $r \neq p$, and
+%       ***these intervals need checking***
+%\[J^{(W)}_p(j-2) = [j+2,c], \quad J^{(W)}_p(j-1) = [c+1,j-1], \quad J^{(W)}_p(j) = \{j\}, \quad J^{(W)}_p(j+1) = \{j+1\}\]
+%  where
+%  \[
+%  c = \begin{cases} d-1 & \text{if } m=i+1 \\
+%    j-2 & \text{otherwise}
+%      \end{cases}
+%  \]
+%also satisfies the statement of the theorem.
+
 Now suppose $j+1$ is not in the support of $p$.
-If we start at $j+1$ we need to know whether there are any unassigned propagators supported on edge $i$ when we reach vertex $i$.
+If we start at $j+1$ we need to know whether any other propagators remain on edge $i$ when we reach vertex $i$.
 We already know that $J_q^{(V)}(j+1) = \{j+1\}$; in particular this means that $q$ contributes $i$ in $I_{j+2}^{(V)}$.
@@
 In particular if $i$ was assigned in $I^{(V)}_{j+1}$, then it would not be available to assign to $q$ in $I^{(V)}_{j+2}$ as all other propagators supported at $i$ in $V$ come before $q$.
-
     Therefore $p$ is the only potentially unassigned propagator on edge $i$ when we reach vertex $i$ in $W$, and
@@
     \]
-We can now describe the intervals $J^{(W)}_r(*)$ for the first two cases of Figure~\ref{fig 3 cases}.
-For $r \neq p$ the intervals are clearly still cyclic and appear in the correct order, and we can assemble the intervals for the $J_p^{(W)}(*)$ as follows.
+
+    Taking all the possibilities for the left two cases of Figure~\ref{fig 3 cases}, the intervals $J^{(W)}_r(*)$ are still cyclic for all $r \neq p$, and we can assemble the intervals for the $J_p^{(W)}(*)$ as follows.
     \begin{itemize}
@@
     If $m=l$ then either $a=2$ (so $l+1=m+1$, $j=m+2$, and $j+1=m+3$) or $a=3$ (so $l+1=m+1$, $l+2=m+2$, $j=m+3$, and $j+1$ is not in the support of $p$), and in both cases
-    \begin{gather*}
-    J^{(W)}_p(m) = [m+4, m], \qquad  J^{(W)}_p(m+1) = \{m+1\}, \\ J^{(W)}_p(m+2) = \{m+2\}, \qquad  J^{(W)}_p(m+3) = \{m+3\},
-    \end{gather*}
+    \[
+    J^{(W)}_p(m) = [m+4, m], \  J^{(W)}_p(m+1) = \{m+1\}, \  J^{(W)}_p(m+2) = \{m+2\}, \  J^{(W)}_p(m+3) = \{m+3\},
+    \]
     which are nonempty and otherwise as required.
@@
         If $m=i+1$ then checking each of the three different possibilities for $a$ we likewise get
-    \begin{gather*}
-    J^{(W)}_p(m) = [m+4, d-1], \qquad  J^{(W)}_p(m+1) = [d, m+1], \\  J^{(W)}_p(m+2) = \{m+2\}, \qquad  J^{(W)}_p(m+3) = \{m+3\},
-    \end{gather*}
+    \[
+    J^{(W)}_p(m) = [m+4, d-1], \  J^{(W)}_p(m+1) = [d, m+1], \  J^{(W)}_p(m+2) = \{m+2\}, \  J^{(W)}_p(m+3) = \{m+3\},
+    \]
     which are nonempty and otherwise as required.
   \item If $m=i$ then $a=1$ or $a=2$, in the former case $l=m+2$, $j=m+3$ and $j+1$ is not in the support of $p$ so
-    \begin{gather*}
-    J^{(W)}_p(m) = \{m+4\}, \qquad  J^{(W)}_p(m+1) = [m+5, d-1], \\  J^{(W)}_p(m+2) = [d, m+2], \qquad  J^{(W)}_p(m+3) = \{m+3\},
-    \end{gather*}
+    \[
+    J^{(W)}_p(m) = \{m+4\}, \  J^{(W)}_p(m+1) = [m+5, d-1], \  J^{(W)}_p(m+2) = [d, m+2], \  J^{(W)}_p(m+3) = \{m+3\},
+    \]
     while in the latter $l=m+2$, $l+1=m+3$, and $j$ and $j+1$ are not in the support of $p$ so
-    \begin{gather*}
-    J^{(W)}_p(m) = [m+4, j+1], \qquad  J^{(W)}_p(m+1) = [j+2, d-1], \\  J^{(W)}_p(m+2) = [d, m+2], \qquad  J^{(W)}_p(m+3) = \{m+3\},
-    \end{gather*}
+    \[
+    J^{(W)}_p(m) = [m+4, j+1], \  J^{(W)}_p(m+1) = [j+2, d-1], \  J^{(W)}_p(m+2) = [d, m+2], \  J^{(W)}_p(m+3) = \{m+3\},
+    \]
     which are again as required.
@@
 
-\textbf{Third case}: In this case there are no unsupported vertices $l, l+1, \ldots$ inside $q$.
+\textbf{Third case}: In this case there are no unsupported vertices $l, \ldots$ inside $q$.
 Again write $p=(m, m+2)$ where $m\in \{j, j+1, j+2\}$.
-We proceed as in the previous cases, by computing $I^{(W)}_w$ for vertices $w$ in roughly increasing order of difficulty.
-
 For $w \in [n]\backslash\{j+1,m,m+1,m+2,m+3\}$: if $w\in J_q^{(V)}(i)$ or $w\in J_q^{(V)}(i+1)$ then
@@
 Note that $I_{m+2}^{(V)}(r) = I_{m+3}^{(V)}(r)$ for all propagators $r$ in $V$, and that if $j+1\not\in\{m, m+1, m+2, m+3\}$ then $j+2$ and $j+3$ are unsupported in $V$ so in that case $I_{j+2}^{(V)}(r) = I_{j+3}^{(V)}(r) = I_{j+4}^{(V)}(r)$ for $r$ in $V$.
-
-Therefore, once again we can see that the $J_r^{(W)}(*)$ are cyclic for all $r\neq p$ in $W$.  Assembling the intervals for $p$ we have:
-\begin{itemize}
-\item if $m=j$ then
-\begin{gather*}J_p^{(W)}(m) = [m+4,e-1], \qquad  J_p^{(W)}(m+1) = [e,m], \\  J_p^{(W)}(m+2) = [m+1,m+2], \qquad  J_p^{(W)}(m+3) = \{m+3\},\end{gather*}
-\item if $m=j+1$ then
-\begin{gather*}J_p^{(W)}(m) = [m+4,m-1], \qquad J_p^{(W)}(m+1) = [m,m+1], \\  J_p^{(W)}(m+2) = \{m+2\}, \qquad  J_p^{(W)}(m+3) = \{m+3\},\end{gather*}
-\item if $m=j+2$ then
-\begin{gather*}J_p^{(W)}(m) = [m+4,m], \qquad  J_p^{(W)}(m+1) = \{m+1\}, \\  J_p^{(W)}(m+2) = \{m+2\}, \qquad  J_p^{(W)}(m+3) = \{m+3\}.\end{gather*}
-\end{itemize}
+Therefore, once again we can see that the $J_r^{(W)}(*)$ are cyclic for all $r$ in $V$.
+Assembling the intervals for $p$ we get,
+ if $m=j$ then
+\[J_p^{(W)}(m) = [m+4,e-1], \  J_p^{(W)}(m+1) = [e,m], \  J_p^{(W)}(m+2) = [m+1,m+2], \  J_p^{(W)}(m+3) = \{m+3\},\]
+ if $m=j+1$ then
+\[J_p^{(W)}(m) = [m+4,m-1], \ J_p^{(W)}(m+1) = [m,m+1], \  J_p^{(W)}(m+2) = \{m+2\}, \  J_p^{(W)}(m+3) = \{m+3\},\]
+and if $m=j+2$ then
+\[J_p^{(W)}(m) = [m+4,m], \  J_p^{(W)}(m+1) = \{m+1\}, \  J_p^{(W)}(m+2) = \{m+2\}, \  J_p^{(W)}(m+3) = \{m+3\}.\]
 The result now follows by induction.

### 2019-01-08 General WLD combinatorics.tex
Finished going through 2.3

@@
 \begin{rmk}\label{alt F(P) rmk}
-Note that a more explicit definition of $F(P)$ is \bas F(P)  = \big(V(P) \setminus V(P^c) \big) \cup F(\emptyset) \eas
+Note that a more explicit definition of $F(P)$ is \bas F(P)  = \big(V(P) \setminus V(P^c) \big) \cup F(\emptyset) \;.\eas Furthermore, note that by construction $\Prop(F(P)) \subseteq P$.  
 \end{rmk}
@@
 Since Corollary \ref{uniqueproppartitioncor} allows us to decompose any admissible Wilson loop diagram into a collection of maximal exact subdiagrams, in this section we examine the matroid properties of exact subdiagrams more closely.
-In particular, we show that given an exact subdiagram $(P, V(P))$, it can be written as the contraction of the matroid $M(W)$ by the complementary propagator flat, $F(P^c)$.
-Furthermore, if $(P, V(P))$ is a maximal exact subdiagrams, its complementary propagator flat is a cyclic flat.
-Finally, we show that matroids associated to exact subdiagrams are uniform (Theorem \ref{exactuniformthm}).
+In this section, we show prove two results:
+\begin{enumerate}
+\item The matriod assoicated to an exact subdiagram of $W$ can be written as a contraction of the matroid $M(W)$ by the complementary propagator flat (Theorem \ref{exact diagrams contractions}). 
+\item The matroid associated to an exact subdiagram is uniform (Theorem \ref{exactuniformthm} ).
+\end{enumerate}
 
@@
 \begin{comment}
-
-\begin{dfn}\label{matroid contraction}
-Let $M = (E,\cB)$ be a matroid, and $S \subseteq E$. The {\em contraction} of $M$ by $S$ is the matroid $M/S = (E \setminus S, \cB / S)$, where
-\[\cB / S = \{B \setminus S \ \big| \ |B\cap S | \text{ is maximal amonst all }B \in \cB\}.\]
-\end{dfn}
-
-In \cite{wilsonloop}, Agarwala and Amat show that certain subdiagrams of $W$ can be realized as contractions of $M(W)$:
-
-\begin{lem} \label{contractsubdiaglem} \cite[Theorem 3.33]{wilsonloop} 
-Let $W = (\cP, [n])$ be an admissible Wilson loop diagram and $P \subseteq \cP$.
-If the set $V(P)^c$ has rank $|P^c|$, then the matroid defined by the subdiagram $(P, V(P))$ is equal to the contraction $M(W)/V(P)^c$.
-\end{lem}
-
-In Lemma \ref{maxexactcomplementrank} below we show that every exact subdiagram satisfies the rank condition of Lemma \ref{contractsubdiaglem}.
-In order to do this, we first examine the properties of the set by which we contract.
 
@@
 Let $W = (\cP, [n])$ be a Wilson loop diagram, and $P \subseteq \cP$. Then: \begin{enumerate}
+\item If $(P,V(P))$ is an exact subdiagram in $W$, then $F(P^c)$ is not an independent flat.
+\item If $(P,V(P))$ is a maximal exact subdiagram in $W$, then $F(P^c)$ is a cyclic flat.
 \item If $(P,V(P))$ is an exact subdiagram in $W$, then $\rk(F(P^c)) = |P^c|$.
-\item If $(P,V(P))$ is a maximal exact subdiagram in $W$, then $F(P^c)$ is a cyclic flat.
 \end{enumerate}
@@
 
-Note that $|P^c|$ is always an upper bound on the rank of $F(P^c)$ for any $P \subseteq \cP$, since $F(P^c)$ supports at most $P^c$ propagators. However, showing equality is far harder.
-
-\begin{proof}
-First note that if $(P,V(P))$ is exact then the admissiblity of $W$ guarantees that $F(P^c)$ is non-empty.
+\begin{proof}
+%Note that $|P^c|$ is always an upper bound on the rank of $F(P^c)$ for any $P \subseteq \cP$, since $F(P^c)$ supports at most $P^c$ propagators (see Remark \ref{alt F(P) rmk}), and $\rk (F(P^c)) = \min\{ |F(P^c)|, |\Prop(F(P^c))|\}$.
+To show equality, we need to show that $F(P^c)$ is not an independent set and that $\Prop(F(P^c)) = P^c$.
+
+First note that if $(P,V(P))$ is exact then the admissiblity of $W$ guarantees that $F(P^c)$ is a non-empty flat. That is, $V(P) \subsetneq [n]$.
 
@@
 \begin{equation}\label{eq F is dependent}|F(P^c)| > |P^c| \;.\end{equation}
-By Lemma \ref{lem properties of prop flats}, $F(P^c)$ is a set of vertices that supports only propagators in $P^c$, so in particular we have $\Prop(F(P^c)) = P^c$.
-Equation \eqref{eq F is dependent} is therefore saying that $F(P^c)$ supports fewer propagators than the number of vertices it contains, i.e.
-$F(P^c)$ is dependent.
-
-We address part (2) first. Suppose that $(P, V(P))$ is a maximal exact subdiagram; by Corollary \ref{classifyflats} we can decompose $F(P^c)$ as
-\begin{equation}\label{eq decompose F}F(P^c) = C \sqcup S,\end{equation}
-where $C$ is the largest cyclic flat contained in $F(P^c)$ and $S$ is an  independent set.
-Note that $C$ must be non-empty since $F(P^c)$ is non-empty and dependent.
-We proceed by showing that $S$ must be empty, forcing $F(P^c)$ to be a cyclic flat.
-
-Since $C = F(\Prop(C))$ by Lemma \ref{lem decompose flat}, define $Q := \Prop(C)^c$ so that we may write $C = F(Q^c) = V(Q)^c$.
-Note that since $C \subseteq F(P^c)$, $P \subseteq Q$.
-Furthermore, we have
-\begin{equation}|S| = \rk(S) \leq \rk(F(P^c)) - \rk(C)  \leq |P^c| - \rk(C) \;, \label{increasingrank}\end{equation}
-where first equality comes from the fact that $S$ is an independent set,\note{Did we ever address the question of where the middle inequality comes from?
-Can we argue by number of propagators?} and the final inequality comes from Lemma \ref{lem facts about WLD matroids}(1).
-Since $\rk(C) = |\Prop(C)| = |Q^c|$ by Lemma \ref{lem facts about WLD matroids}(2), we can rearrange \eqref{increasingrank} to obtain the inequality
-\begin{equation} |P| + |S| \leq |P| + |P^c| - \rk(C) = |Q| \;. \label{Qsizebound}\end{equation}
-Furthermore, since $V(Q) = S \sqcup V(P)$ (by equation \eqref{eq decompose F} and the definition of $Q$) we may write  
-\begin{equation} |V(Q)| = |S| + |V(P)| = |S| + |P| +3 \label{VQsize} \;.\end{equation} 
-Combining this with \eqref{Qsizebound} gives $|V(Q)| \leq |Q| + 3$.
-Since $W$ is admissible, we conclude that $(Q,V(Q))$ is exact; since $V(Q) = V(P) \sqcup S$ and $(P,V(P))$ is maximal exact, it follows that $S = \emptyset$.
-It now follows from \eqref{eq decompose F} that $F(P^c)$ is a cyclic flat, and hence from Lemma \ref{lem facts about WLD matroids} that
-\[\rk(F(P^c)) = |Prop(F(P^c))| = |P^c|.\]
-
-Let $P$ be a maximal exact subdiagram as above, and let $(R,V(R))$ be an exact subdiagram that is not maximal. That is, $R \subsetneq P$.
-
-Since $R \subset P$, $V(P) = V(R) \sqcup S$.
+Equation \eqref{eq F is dependent} is therefore saying that $F(P^c)$ supports fewer propagators than the number of vertices it contains, i.e. $F(P^c)$ is not an independent set.
+
+For part (2), suppose that $(P, V(P))$ is a maximal exact subdiagram. By Corollary \ref{classifyflats} we can decompose $F(P^c)$ as
+\begin{equation}\label{eq decompose F}V(P)^c = F(P^c) = C \sqcup S = F(\Prop(C)) \sqcup S,\end{equation}
+where $C$ is the largest cyclic flat contained in $F(P^c)$ and $S$ is an  independent set. Note that $C$ must be non-empty since $F(P^c)$ is non-empty and dependent (by part (1)).
+
+Since $S$ is an independent set, $\rk(S) = |S|$, and every element of $S$ is independent of $C$, $\rk\big(F(P^c)\big) = \rk(C) + \rk(S)$.
+By Lemma \ref{lem facts about WLD matroids}(2), \ba \rk(S) = \rk\big(F(P^c)\big) -  \rk(S) \leq |P^c| - \rk(C) \;.
+\label{increasingrank} \ea
+
+Let $Q^c = \Prop(C)$.
+Then $C = F(Q^c)$ and, by Lemma \ref{lem facts about WLD matroids}(1), $\rk(C) = |Q^c|$.
+By equation \eqref{increasingrank}, \ba |P| + |S| \leq |P| + |P^c| - \rk(C) = |\cP| - |Q^c| = |Q| \;.
+\label{Qsizebound}\ea From equation \eqref{eq decompose F}, \bas |V(Q)| = V(P) \sqcup S = C^c = F(\Prop(C))^c = F(Q^c)^c = V(Q) \;.
+\eas Combining this with equation \eqref{increasingrank} gives \ba |V(Q)| = | V(P) | + |S| = | V(P) | + 3 + |S| \leq |Q| +3 \;.
+\label{Q defines exact}\ea Since $W$ is admissible, one must have $V(Q) = |Q| +3$, that is the subdiagram $(Q, V(Q))$ is exact.
+
+Next, note that \bas C = F(Q^c) = V(Q)^c \subset F(P^c) = V(P)^c \;,\eas which implies that $P \subseteq Q$.
+That is, $(P, V(P))$ is a subdiagram of $(Q, V(Q))$.
+Since $(P, V(P))$ is maximally exact by hypothesis, and $(Q, V(Q))$ is exact by \eqref{Q defines exact}, we are forced to have $S = \emptyset$.
+Therefore, $F(P^c)$ is a cyclic flat.
+
+To see (3), first note that the second point of this Lemma, combined with Lemma \ref{lem facts about WLD matroids} that
+\bas\rk(F(P^c)) = |\Prop(F(P^c))| = |P^c|.\eas
+
+To prove this in the general case, let let $(R,V(R))$ be an exact subdiagram that is not maximal and $P$ be the maximal exact subdiagram containing it. That is, $R \subsetneq P$.
+
+Since $R \subset P$, $V(P) = V(R) \sqcup S$, where $S = V(P) \setminus V(R)$.
 Since $P$ and $R$ both define exact subdiagrams, we may write $|V(P)| = |V(R)| + |P \setminus R|$, where $S$ is a vertex set of size $|P \setminus R|$ with $(P \setminus R \subset \Prop(S)$.
-Since $\rk V(P) =  \rk V(R) + |P \setminus R|$, $S$ is independent.
-Taking the complements, we may write \bas F(R^c ) = F(P^c) \sqcup S \;.\eas Since $S$ is an independent set of vertices of the correct size supporting the appropriate propagators, this gives $ \rk F(R^c ) = |R^c|$.
-
-\end{proof}
-
-In particular, any exact subdiagram $(P,V(P))$ satisfies the conditions of Lemma \ref{contractsubdiaglem} and can therefore be written as a contraction of $M(W)$ by the complementary propagator flat $F(P^c)$.
-
-Matroids coming from exact subdiagrams have an especially nice structure, as we now show.
+Since  $|S| = |V(P) \setminus V(R)| = |P \setminus R| \leq |\Prop(S) |$, by Lemma \ref{lem facts about WLD matroids}, $\rk(S) = |S|$, implying that $S$ is independent.
+Taking the complements, we may write \bas F(R^c ) = F(P^c) \sqcup S \;.\eas Taking the rank of both sides, \bas \rk(F(R^c )) = \rk(F(P^c) \sqcup S ) \leq \rk(F(P^c)) + |S| = |P^c| + |\Prop(S)| \leq |R^c| \;.\eas Combining this with \eqref{eq F is dependent} gives the desired result.
+
+\end{proof}
+
+We are now ready to show that any exact subdiagram $(P, V(P)$ of $W$ can be written as a contraction of $M(W)$ by $F(P^c)$. We begin with a definition.
+
+\begin{dfn}\label{matroid contraction}
+Let $M = (E,\cB)$ be a matroid, and $S \subseteq E$. The {\em contraction} of $M$ by $S$ is the matroid $M/S = (E \setminus S, \cB / S)$, where
+\[\cB / S = \{B \setminus S \ \big| \ |B\cap S | \text{ is maximal amonst all }B \in \cB\}.\]
+\end{dfn}
+
+In \cite{wilsonloop}, Agarwala and Amat show that certain subdiagrams of $W$ can be realized as contractions of $M(W)$:
+
+\begin{lem} \label{contractsubdiaglem} \cite[Theorem 3.33]{wilsonloop} 
+Let $W = (\cP, [n])$ be an admissible Wilson loop diagram and $P \subseteq \cP$.
+If the set $V(P)^c$ has rank $|P^c|$, then the matroid defined by the subdiagram $(P, V(P))$ is equal to the contraction $M(W)/V(P)^c$.
+\end{lem}
+
+\begin{thm} \label{exact diagrams contractions}
+If $(P, V(P)$ is an exact subdiagram of of $W$, one may write \bas M\big((P, V(P))\big) = M(W)  / F(P^c) \;.\eas 
+\end{thm}
+
+\begin{proof}
+This follows from Lemma \ref{matroid contraction}. Lemma \ref{maxexactcomplementrank} shows that the supports of exact subdiagrams satisfy the conditions of this lemma.
+\end{proof}
+
+\begin{rmk}
+Let $M^*$ denote the dual of a matroid.
+The the dual of a contraction of a matroid is the same as the restriction of the dual matroid by the complement: \bas M / S = M^*|_{S^c} \;.\eas Then Theorem \ref{exact diagrams contractions} implies that, for $(P, V(P))$ an exact subdiagram of $W$ \bas M\big((P, V(P))\big) = M(W)  / F(P^c) = M(W)^*|_{V(P)} \;.\eas
+\end{rmk}
+
+Matroids coming from exact subdiagrams have an especially nice structure, namely, they are uniform.
 Recall from Section \ref{sec matroid background} that a uniform matroid of rank $r$ is one in which all sets of size $ \leq r$ are independent.
@@
 
-We prove the following claim: $W'$ is exact if and only if $V(P)$ contains no circuits $C$ with $\rk C< |P|$ in $(P, V(P))$. Since $\rk(M(W')$ is bounded above by $|P|$, the result follows.
+We prove the following claim: $W'$ is exact if and only if $V(P)$ contains no circuits $C$ with $\rk C< |P|$ in $(P, V(P))$. Since $\rk(M(W'))$ is bounded above by $|P|$, the result follows.
 
@@
 
-Before proving the main theorems of this section, we make a few observations about the geometry of matroids defined by exact diagrams.
-
-In \cite{wilsonloops}, the authors show that all violet Wilson loop diagrams correspond to positroids.
-That is, they correspond to matroids that can be represented by elements of the positive Grassmannians $\Gr(|\cP|, |V|)$.
+\sanote{Should the rest of this section be stuck in the next section?}
+We now make a few observations about the geometry of matroids defined by exact diagrams.
+
+In \cite{wilsonloops}, the authors show that all admissible Wilson loop diagrams correspond to positroids.
+That is, they correspond to matroids that can be represented by elements of the positive Grassmannians $\Gr(|\cP|, n)$.
 Any positroid of rank $k$ on $n$ elements defines a subspace of the positive Grassmannians $\Gr(k, n)$, namely the points which represent it.

### 2019-01-08 General WLD combinatorics.tex
Updates to cyclic intervals lemma

--- 2019-01-04 General WLD combinatorics.tex
@@
 Since Corollary \ref{uniqueproppartitioncor} allows us to decompose any admissible Wilson loop diagram into a collection of maximal exact subdiagrams, in this section we examine the matroid properties of exact subdiagrams more closely.
-In particular, we show that given an exact subdiagram $(P, V(P))$, it can be written as the contraction of the matroid $M(W)$ by the complementary propagator flat, $F(P^c)$.
-Furthermore, if $(P, V(P))$ is a maximal exact subdiagrams, its complementary propagator flat is a cyclic flat.
-Finally, we show that matroids associated to exact subdiagrams are uniform (Theorem \ref{exactuniformthm}).
-
-We begin by proving some useful facts about flats of matroids associated to admissible Wilson loop diagrams.
+In this section, we show prove two results:
+\begin{enumerate}
+\item The matriod assoicated to an exact subdiagram of $W$ can be written as a contraction of the matroid $M(W)$ by the complementary propagator flat (Theorem \ref{exact diagrams contractions}). 
+\item The matroid associated to an exact subdiagram is uniform (Theorem \ref{exactuniformthm} ).
+\end{enumerate}
+
+We begin by proving some useful facts about propagator flats, and flats of matroids associated to admissible Wilson loop diagrams more generally.
 
 \begin{comment}
-
-\begin{dfn}\label{matroid contraction}
-Let $M = (E,\cB)$ be a matroid, and $S \subseteq E$. The {\em contraction} of $M$ by $S$ is the matroid $M/S = (E \setminus S, \cB / S)$, where
-\[\cB / S = \{B \setminus S \ \big| \ |B\cap S | \text{ is maximal amonst all }B \in \cB\}.\]
-\end{dfn}
-
-In \cite{wilsonloop}, Agarwala and Amat show that certain subdiagrams of $W$ can be realized as contractions of $M(W)$:
-
-\begin{lem} \label{contractsubdiaglem} \cite[Theorem 3.33]{wilsonloop} 
-Let $W = (\cP, [n])$ be an admissible Wilson loop diagram and $P \subseteq \cP$.
-If the set $V(P)^c$ has rank $|P^c|$, then the matroid defined by the subdiagram $(P, V(P))$ is equal to the contraction $M(W)/V(P)^c$.
-\end{lem}
-
-In Lemma \ref{maxexactcomplementrank} below we show that every exact subdiagram satisfies the rank condition of Lemma \ref{contractsubdiaglem}.
-In order to do this, we first examine the properties of the set by which we contract.
 
@@
 Now suppose $W$ has more than one propagator.
-Since non-supporting vertices play no role in Algorithm~\ref{alg:put GN on WLD}, it suffices to prove the result for $W$ with $F(\emptyset) = \emptyset$.
+Since non-supporting vertices have no effect on the Grassmann necklace algorithm, it suffices to prove the result for $W$ with $F(\emptyset) = \emptyset$.
 Then by Lemma~\ref{lem sian}, $W$ has at least one of the four situations illustrated in Figure~\ref{fig 3 cases}.
@@
 \textbf{Left two cases}: These cases behave essentially identically (except when $j$ or $j+1$ are not in the support of $p$, which can occur in the second case only; see below) so we handle the majority of the proof for these two cases simultaneously.
-Let $1\leq a\leq 3$ be the number of unsupported vertices inside $q$ in $V$; so these vertices are $l, \ldots, l+a-1$.
+Let $1\leq a\leq 3$ be the number of non-supporting vertices inside $q$ in $V$; so these vertices are $l, \ldots, l+a-1$.
 Write $p=(m,m+2)$ where $m\in \{i, i+1, l\}$.
@@
 
-\textbf{Third case}: In this case there are no unsupported vertices $l, l+1, \ldots$ inside $q$.
+\textbf{Third case}: In this case there are no non-supporting vertices $l, l+1, \ldots$ inside $q$.
 Again write $p=(m, m+2)$ where $m\in \{j, j+1, j+2\}$.
@@
 \end{align*}
-Note that $I_{m+2}^{(V)}(r) = I_{m+3}^{(V)}(r)$ for all propagators $r$ in $V$, and that if $j+1\not\in\{m, m+1, m+2, m+3\}$ then $j+2$ and $j+3$ are unsupported in $V$ so in that case $I_{j+2}^{(V)}(r) = I_{j+3}^{(V)}(r) = I_{j+4}^{(V)}(r)$ for $r$ in $V$.
+Note that $I_{m+2}^{(V)}(r) = I_{m+3}^{(V)}(r)$ for all propagators $r$ in $V$, and that if $j+1\not\in\{m, m+1, m+2, m+3\}$ then $j+2$ and $j+3$ are non-supporting vertices in $V$, so in that case $I_{j+2}^{(V)}(r) = I_{j+3}^{(V)}(r) = I_{j+4}^{(V)}(r)$ for $r$ in $V$.
 
@@
 since in both cases the algorithm in $W'$ proceeds identically to that in $W$ after assigning $p$.
-Since $k \neq i+1$, we have $k\in I_{i+1}^{(W')}\setminus\{i+1\}$ but $k\not\in I_{i+2}^{(W')}$, contradicting the minimiality of $(W, i, k)$
+Since $k \neq i+1$, we have $k\in I_{i+1}^{(W')}\setminus\{i+1\}$ but $k\not\in I_{i+2}^{(W')}$, contradicting the minimiality of $(W, i, k)$.
 

### 2019-01-10 General WLD combinatorics.tex
section 3 lemma refs, and the beginnings of a bibliography

@@
 This in turn induces a total order on $\binom{[n]}{k}$, namely the lexicographic order with respect to $<_j$.
-It also induces a separate partial order $\gale{j}$ on $\binom{[n]}{k}$ (the \textit{Gale order} [ref]), which is defined as follows: for
+It also induces a separate partial order $\gale{j}$ on $\binom{[n]}{k}$ (the \textit{Gale order} \cite{Gale}), which is defined as follows: for
 \[A = \{a_1 <_j a_2 <_j \dots <_j a_k\} \text{ and } B = \{b_1 <_j b_2 <_j \dots <_j b_k\} \in \binom{[n]}{k},\] we say that
@@
 
-By [ref][Oh or Postnikov?], the Grassmann necklaces of type $(k,n)$ are in 1-1 correspondence with the positroid cells in $\Gr(k,n)$.
-Further, if $(I_1, \dots, I_n)$ is the Grassmann necklace associated to a positroid $M = ([n],\cB)$, then by [ref][Oh] the bases of $M$ can be computed using the Gale order $\gale{i}$ for each $i \in [n]$:
+By \cite[Theorem 17.1]{Postnikov}, the Grassmann necklaces of type $(k,n)$ are in 1-1 correspondence with the positroid cells in $\Gr(k,n)$.
+Further, if $(I_1, \dots, I_n)$ is the Grassmann necklace associated to a positroid $M = ([n],\cB)$, then by \cite[Theorem 8]{Oh} the bases of $M$ can be computed using the Gale order $\gale{i}$ for each $i \in [n]$:
 \[\cB = \left\{J \in \binom{[n]}{k}\ :\ I_i \gale{i} J \ \forall i \in [n]\right\}.\]
@@
 i.e.
-the set of indices $m$ for which Algorithm [ref] assigns the value $i$ to the propagator $p$ in $W$.
+the set of indices $m$ for which Algorithm~\ref{alg:put GN on WLD} assigns the value $i$ to the propagator $p$ in $W$.
 The following lemma establishes that these sets behave in a simple and predictable manner, a fact which we will repeatedly use in subsequent proofs.
@@
 
-The dimension of a positroid cell is the same as the number of plusses in the associated Le diagram ***cite something***, and so with Algorithm~\ref{alg:put GN on WLD} along with the algorithm for passing from a Grassmann necklace to a Le diagram (reversing Oh's algorithm) described by some of us in \cite{reversingOh}, we can, at the cost of a bit of messy grunt work, give a recursive proof of the $3|\cP|$-dimensionality that explicitly describes the changes in the positions of the plusses in the Le diagram.
+The dimension of a positroid cell is the same as the number of plusses in the associated Le diagram \cite[Theorem 6.5]{Postnikov}, and so with Algorithm~\ref{alg:put GN on WLD} along with the algorithm for passing from a Grassmann necklace to a Le diagram (reversing Oh's algorithm) described by some of us in \cite{reversingOh}, we can, at the cost of a bit of messy grunt work, give a recursive proof of the $3|\cP|$-dimensionality that explicitly describes the changes in the positions of the plusses in the Le diagram.
 
@@
 \end{lem}
-
-\note{Can I just cite something for this, or can one of you provide a quick geometric proof.  It would be a horrible mess to do by hand combinatorially}
+\begin{proof}
+By \cite[Proposition 17.10]{Postnikov}, the dimension of a positroid (and hence the number of plusses in its Le diagram) is $k(n-k) - A(\pi_W)$, where $A(\pi_W)$ denotes the number of alignments (see \cite[Figure 17.1]{Postnikov} and preceding discussion) of the decorated permutation $\pi_W$ of the positroid associated to $W$.
+
+Since it is clear that dihedral transformations of a Wilson loop diagram $W$ correspond to dihedral transformations of the chord diagram representation of $\pi_W$, and that the number of alignments in a chord diagram is preserved under dihedral transformations, the result follows.
+\end{proof}
 
@@
 
+\begin{thebibliography}{10}
+
+\bibitem{wilsonloop}
+S. Agarwala, E. M. Amat.
+\newblock Wilson loop diagrams and positroids.
+\newblock {\em Commun. Math. Phys.} 2016.
+
+\bibitem{reversingOh}
+S. Agarwala, S. Fryer.
+\newblock An algorithm to construct the Le diagram associated to a Grassmann necklace
+\newblock \url{arXiv:1803.01726}
+
+\bibitem{Gale}
+D. Gale.
+\newblock Optimal assignments in an ordered set: {A}n application of matroid theory.
+\newblock {\em J. Combinatorial Theory}, 4: 176 - 180 (1968).
+
+\bibitem{Oh}
+S. Oh.
+\newblock Positroids and {S}chubert matroids.
+\newblock {\em J. Combin. Theory Ser. A}, 118(8):2426--2435, (2011)
+
+\bibitem{Postnikov}
+A.~Postnikov.
+\newblock Total positivity, {G}rassmannians, and networks.
+\newblock \url{arXiv:math/0609764}.
+
+\end{thebibliography}
+
 \end{document}

### 2019-01-10 General WLD combinatorics.tex
some work on section 3 background

@@
 \section{Geometry of Wilson Loop diagram}\label{sec GN algorithm}
+
 Since Wilson loop diagrams correspond to positroids, it is natural to study the subspace of $\Gr(|\cP|, n)$ they define.
 
-% Talk about Grassmann Necklaces and how it defines a cell in a CW complex of $\Gr(k,n)$. Also talk about how this is exactly all the non-negative matrices that represent a particular positroid.
-
-% Also talk about Le diagrams.
-
-[We probably need a subsection for background here.
-Probably move the definition of Grassmann necklace up to here, a few words about positroids and Postnikov's work, def of Le diagrams and GNs, why it's useful to be able to translate between WLD, GN, Le diagrams at will.
-]
-
-Throughout this section, $W = (\cP,n)$ is an admissible Wilson loop diagram with $k$ propagators.
-
-\subsection{Some setup results about propagators}
+[words about what's in this section]
+
+Throughout this section, $W = (\cP,[n])$ is an admissible Wilson loop diagram with $k$ propagators.
+
+\subsection{Background}\label{sec:positroid background}
+
+[positroids]
+
+Let $\binom{[n]}{k}$ be the set of all $k$-subsets of the cyclically ordered set $[n]$.  For each $j \in [n]$, we can define a total order $\leq_j$ on the interval $[n]$ by
+\[] j <_j j+1 <_j \dots <_j n <_j 1 \dots <_j j-1\;.\]
+This in turn induces a total order on $\binom{[n]}{k}$, namely the lexicographic order with respect to $<_j$.
+It also induces a separate partial order $\gale{j}$ on $\binom{[n]}{k}$ (the \textit{Gale order} \cite{Gale}), which is defined as follows: for
+\[A = \{a_1 <_j a_2 <_j \dots <_j a_k\} \text{ and } B = \{b_1 <_j b_2 <_j \dots <_j b_k\} \in \binom{[n]}{k},\] we say that
+\[A \gale{j} B \text{ if and only if } a_r \leq_j b_r \text{ for all }1 \leq r \leq k.\]
+For example, in $\binom{[6]}{3}$ we have $\{2,5,6\}\gale{2} \{2,6,1\}$ but $\{2,5,6\}\not\gale{2}\{3,4,6\}$.
+
+\begin{dfn}\label{def:grassmann necklace}
+A Grassmann necklace of type $(k,n)$ is a sequence $(I_1, \dots, I_n)$ of $n$ sets $I_i \in \binom{[n]}{k}$ such that for each $i \in [n]$:
+\begin{itemize}
+\item if $i \in I_i$, then $I_{i+1} = \big(I_i \backslash \{i\}\big) \cup \{j\}$ for some $j \in[n]$.
+\item if $i \not\in I_i$, then $I_{i+1} = I_i$.
+\end{itemize}
+By convention, we set $I_{n+1} = I_1$.
+\end{dfn}
+
+By \cite[Theorem 17.1]{Postnikov}, the Grassmann necklaces of type $(k,n)$ are in 1-1 correspondence with the positroid cells in $\Gr(k,n)$.
+This correspondence is given explicitly in \cite[Theorem 8]{Oh}: if $(I_1, \dots, I_n)$ is the Grassmann necklace associated to a positroid $M = ([n],\cB)$, then the bases of $M$ are exactly
+\[\cB = \left\{J \in \binom{[n]}{k}\ :\ I_i \gale{i} J \ \forall i \in [n]\right\}.\]
+
+[Le diagrams]
+
+\subsection{Propagator configurations in admissible Wilson loop diagrams}\label{sec:propagator configs}
+
+Before we can describe the algorithm for extracting the Grassmann necklace of $M(W)$ from the Wilson loop diagram $W$, we require some initial results about the behavior of propagators in admissible WLD.
 
@@
 
-\subsection{From Wilson Loop diagrams to Grassmann Necklaces}
+\subsection{From Wilson Loop diagrams to Grassmann Necklaces}\label{sec:GN alg}
 
@@
 
-Let $\binom{[n]}{k}$ be the set of all $k$-subsets of the cyclically ordered set $[n]$.  For each $j \in [n]$, we can define a total order $\leq_j$ on the interval $[n]$ by
-\bas j <_j j+1 <_j \dots <_j n <_j 1 \dots <_j j-1\;.\eas
-This in turn induces a total order on $\binom{[n]}{k}$, namely the lexicographic order with respect to $<_j$.
-It also induces a separate partial order $\gale{j}$ on $\binom{[n]}{k}$ (the \textit{Gale order} \cite{Gale}), which is defined as follows: for
-\[A = \{a_1 <_j a_2 <_j \dots <_j a_k\} \text{ and } B = \{b_1 <_j b_2 <_j \dots <_j b_k\} \in \binom{[n]}{k},\] we say that
-\[A \gale{j} B \text{ if and only if } a_r \leq_j b_r \text{ for all }1 \leq r \leq k.\]
-For example, in $\binom{[6]}{3}$ we have $\{2,5,6\}\gale{2} \{2,6,1\}$ but $\{2,5,6\}\not\gale{2}\{3,4,6\}$.
-
-\begin{dfn}\label{def:grassmann necklace}
-A Grassmann necklace of type $(k,n)$ is a sequence $(I_1, \dots, I_n)$ of $n$ sets $I_i \in \binom{[n]}{k}$ such that for each $i \in [n]$:
-\begin{itemize}
-\item if $i \in I_i$, then $I_{i+1} = \big(I_i \backslash \{i\}\big) \cup \{j\}$ for some $j \in[n]$.
-\item if $i \not\in I_i$, then $I_{i+1} = I_i$.
-\end{itemize}
-By convention, we set $I_{n+1} = I_1$.
-\end{dfn}
-
-By \cite[Theorem 17.1]{Postnikov}, the Grassmann necklaces of type $(k,n)$ are in 1-1 correspondence with the positroid cells in $\Gr(k,n)$.
-Further, if $(I_1, \dots, I_n)$ is the Grassmann necklace associated to a positroid $M = ([n],\cB)$, then by \cite[Theorem 8]{Oh} the bases of $M$ can be computed using the Gale order $\gale{i}$ for each $i \in [n]$:
-\[\cB = \left\{J \in \binom{[n]}{k}\ :\ I_i \gale{i} J \ \forall i \in [n]\right\}.\]
-We now describe an algorithm that constructs the Grassmann necklace of an admissible Wilson loop diagram from the diagram.
 The fact that Algorithm~\ref{alg:put GN on WLD} does construct the required Grassmann necklace is proved in Theorem~\ref{res:alg gives GN}.

### 2019-01-16 General WLD combinatorics.tex
Ammended theorem 2.24 to make clearer. Read through rest of 2.4.

@@
 \begin{proof}
-One direction has been proved in previous work, but we give a different proof here to be consistent with the method of this document.
+One direction has been proved in \ref[Theorem 1.18]{wilsonloops}, but we give a different proof here to be consistent with the method of this document.
 
@@
 Let $U \subset V(R)$ be any subset of size $|U| = |R|$.
-The set $U$ is independent in the subdiagram $(R, V(R))$, and thus in $W$.
+Since $(R, V(R))$ defines a uniform matroid, by Lemma \ref{exactuniformthm}, the set $U$ is independent in the subdiagram $(R, V(R))$, and thus in $W$.
 The complementary set $F(P)$ is a flat of maximal rank by lemma \ref{maxexactcomplementrank} ($\rk(F(P)) = |P|$).
@@
 Since $F(P)$ is a flat, adding any element of $V(R)$ to $B$ increases the rank.
-Therefore, any basis of $W$ can be written as $B \cup U$.
+Therefore, any basis of $W$ can be written as $B \cup U$ for some $B$ and $U$ of the form indicated.
 However, since $F(P)$ is common to both $W$ and $W'$, and $V(R) = V(R')$, any any basis of $W'$ can also be written $B \cup U$.
@@
 For the converse, assume that the matroids associated to $W$ and $W'$ are the same: $M(W) = M(W')= M$.
-Let $\{(P_i, V(P_i)\}_{i=1}^k$ and $\{(P'_i, V(P'_i)\}_{i=1}^l$ be the sets of maximally exact subdiagrams of $W$ and $W'$.
-Write $F_i = F(P_i)$ and $F'_i = F(P^{'c}_i)$ to be the complementary cyclic flats.
-By Lemma \ref{exactcircuitlem} $M/F_i$ is a uniform matroid.
-Thereofore, $k = l$, and we may write $V(P_i) = V(P'_i)$.
-
-Reorganize the vertex sets as follows: \ba \cup_{P_i \neq P_i'} V(P_i) = V(\cup_{P_i \neq P'_i} P_i)  \label{vertexsets}\; .\ea Since maximal exact subdiagrams partition $\cP$, by Lemma \ref{uniqueproppartitioncor}, write $cup_{i = 1}^k P_i = \cup_{i = 1}^k P'_i = \cP$.
-Then equation \eqref{vertexsets} becomes \bas \cap_{P_i \neq P_i'} (F(P_i^c))^c = F(\cup_{P_j = P'_j} P_j)^c \;.\eas These flats may, of course, be empty.
-
-Thus, we have partitioned the vertices of $W$ and $W'$ into a single set that supports a union of maximal exact subdiagrams whose propagators between $W$ and $W'$, and the complementary propagator flats that support the propagators in common between $W$ and $W'$.
-As mentioned above, the latter may be empty.
-
-Define a family of Wilson loop diagrams, $W_0$ to $W_k$ defined such that $W_0 = W$ and $W_i$ is derived from $W_{i-1}$ by replacing the propagator set $P_i$ with $P'_i$.
+Let $\mathcal{R} = \{(P_i, V(P_i)\}_{i=1}^k$ and $\mathcal{R}' = \{(P'_i, V(P'_i)\}_{i=1}^l$ be the sets of maximally exact subdiagrams of $W$ and $W'$.
+Write $F_i = F(P_i^c)$ and $F'_i = F(P^{'c}_i)$ to be the complementary cyclic flats.
+By Theorem \ref{exactuniformthm} and Theorem \ref{exact diagrams contractions},  $M/F_i$ and $M/F_i'$ are uniform matroids.
+Since, by Theorem \ref{exactuniformthm}, any subset $V$ of $M$ such that $M/(V^c)$ is uniform defines an exact subdiagram of both $W$ and $W'$.
+If $U \subset V$ are two such thsets, then the corresponding exact subdiagrams are also subsets.
+Therefore, $|\mathcal{R}| = |\mathcal{R}'|$, and we write $V(P_i) = V(P'_i)$, after possibly reindexing $\mathcal{R}$ and $\mathcal{R}'$.
+
+Since the sets of propagators defining maximal exact subdiagrams partition $\cP$, by Lemma \ref{uniqueproppartitioncor}, write $\cup_{i = 1}^k P_i = \cup_{i = 1}^k P'_i = \cP$.
+Reorganize the vertex sets of maximal exact subdiagrams as follows: \ba \cup_{P_i \not \in \mathcal{R}'} V(P_i) = V(\cup_{P_i \not \in \mathcal{R}'} P_i)  = F(\cup_{P_i \in \mathcal{R}'} P_i)^c\label{vertexsets}\; .\ea The final flat may, of course, be empty.
+
+Thus, we have partitioned the vertices of $W$ and $W'$ into two complementary sets.
+The first, $ \cup_{P_i \not \in \mathcal{R}'} V(P_i)$,  is comprised of the union of supports of maximal exact subdiagrams whose propagators differ between $W$ and $W'$.
+The second, $ F(\cup_{P_i \in \mathcal{R}'} P_i)$,  is the propagator flat of all propagators in common between $W$ and $W'$.
+
+Without loss of generality, assume that $|\mathcal{R}| = |\mathcal{R}'| = 1$.
+Then the two Wilson loop diagrams are equivalent.
+If  $|\mathcal{R}| = |\mathcal{R}'| > 1$, then one may define a family of Wilson loop diagrams, $W_0$ to $W_k$ defined such that $W_0 = W$ and $W_i$ is derived from $W_{i-1}$ by replacing the propagator set $P_i$ with $P'_i$.
 In this manner, $W' = W_k$ and $W_i \sim W_{i+1}$, making $W \sim W'$.
@@
 Thus we can count the number of equivalent diagrams.
+[CITATION?]
 

### 2019-01-25 General WLD combinatorics.tex

@@
 For any edge $e$ of $W$, order the propagators incident on $e$ as $\{p_1 \ldots p_r\}$, ordered such that $p_1$ is closest to the vertex $e$, $p_r$ closest to $e+1$, and $p_i$ is closer to $e$ than $p_{i+1}$.
-Then \bas R_e =  c_{p_1,e+1} \prod_{j= 1}(r-1) \left((c_{p_j,e} c_{p_{j+1},e+1} - c_{p_{j+1},e} c_{p_{j},e+1} ) \right) c_{p_s,e}\;.\eas Note that in this notation, if $r = 1$, $R_e = c_{p,e} c_{p,e+1}$.
+Then \bas R_e =  c_{p_1,e+1} \prod_{j= 1}^{r-1} \left((c_{p_j,e} c_{p_{j+1},e+1} - c_{p_{j+1},e} c_{p_{j},e+1} ) \right) c_{p_s,e}\;.\eas Note that in this notation, if $r = 1$, $R_e = c_{p,e} c_{p,e+1}$.
 \end{dfn}
@@
 
-As we take each $\Delta_{I_i}$ to simply be the determinant of a particular submatrix of $C(W)$, the overall sign of each $\Delta_{I_i}$ is well-defined.
-However, we will not be interested in these signs as they only contribute an overall sign to $R$ and our main theorem in this section (Theorem~\ref{thm denom}) will simply be to show that $R$ is equal up to a $\mathbb{Q}$-multiple to the denominator of the Wilson loop diagram (see Definition~\ref{def R(W)}).
+As we take each $\Delta_{I_i}$ to simply be the determinant of a particular submatrix of $C(W)$, the sign of each $\Delta_{I_i}$ is well-defined.
+The goal is to show that $R$ is equal to the denominator of the Wilson loop diagram as defined in Definition~\ref{def R(W)}.
+%  However, we will not be interested in these signs as they only contribute an overall sign to $R$ and our main theorem in this section (Theorem~\ref{thm denom}) will simply be to show that $R$ is equal up to a $\mathbb{Q}$-multiple to the denominator of the Wilson loop diagram (see Definition~\ref{def R(W)}).
 
@@
 \begin{prop}\label{prop alg gives rad}
-  With notation as in Algorithm~\ref{alg WLD to denom via GN} and working over the field $\mathbb{Q}$ we have the following:
+  With notation as in Algorithm~\ref{alg WLD to denom via GN} we have the following:
   \begin{enumerate}
@@
 Suppose for a contradiction that $f$ is a factor of $\Delta_{I_i}$ of degree $\geq 3$.
-Note that by removing the propagators which come before those contributing to $f$ and changing $i$ to be the first vertex which contributes to $f$, we obtain a different admissible diagram for which $f$ still divides $\Delta_{I_i}$ but also $i\in I_i$ and \note{would it be neater to note at the beginning that removing vertices which do not support any propagator has no effect so we assume there are no redundant vertices, and hence $i \in I_i$ for each $i$?
-No, the point is that we can make it so that $i$ is the first index where a propagator of $f$ contributes, not just that it is in $I_i$.} $i$ contributes to $f$.
+Note that by removing the propagators which come before those contributing to $f$ and changing $i$ to be the first vertex which contributes to $f$, we obtain a different admissible diagram for which $f$ still divides $\Delta_{I_i}$ but also $i\in I_i$ and
+$i$ contributes to $f$.
 Showing that this different admissible diagram gives a contradiction is sufficient, and so we may assume that $i\in I_i$ and $i$ contributes to $f$.

### 2019-01-25 General WLD combinatorics.tex
Expositional changes to section 2 and 2.4

@@
 This opens up the study of Wilson loop diagrams to techniques from geometry and combinatorics.
-
-In subsection 2.1, we discuss a few matroidal facts about Wilson loop diagrams.
-In section 2.2, we show that there is a one to one correspondence between exact subdiagrams of Wilson loop diagrams and triangulated pieces of the corresponding polygon partion.
-In section 2.3, we return to some matroidal facts about Wilson loop diagrams, and exact subdiagrams in partuclar.
-We show that a subdiagram of $W$ defines a uniform matroid if and only if the subdiagram is exact.
-This is then used to prove the main result of section 2.3, which is that that two admissible Wilson loop diagrams define the same matroid if and only if they are equivalent (Theorem \ref{same matroid iff equiv}), and we obtain a formula for the number of admissible Wilson loop diagrams in each equivalence class (Corollary \ref{number of equiv diagrams}).
-[sentence about why this matters] \todo{much of the above is just text.
-PUT REFERENCES IN}
+In particular we examine the partial result shown in \cite{wilsonloop}, that shows that equivalent Wilson Loop Diagrams define the same matroid.
+In section 2.4, we make the relationship between Wilson Loop diagrams and matroids explicit.
+We count the size of each equivalence class, and enumerate the {\color{violet} the number of said classes}.
+We also show that two Wilson Loop diagrams map to the same matroid if and only if they are equivalent.
+
+In subsection \ref{sec matroid background}, we discuss a few matroidal facts about Wilson loop diagrams.
+In section \ref{sec: polygon partitions}, we show that there is a one to one correspondence between exact subdiagrams of Wilson loop diagrams and triangulated pieces of the corresponding polygon partion.
+In section \ref{sec: exact diagram matroidal props}, we prove some matroidal properties of exact subdiagrams.
+We show that a subdiagram of $W$ defines a uniform matroid if and only if the subdiagram is exact (Theorem \ref{exactuniformthm}).
+Furthermore, this uniform matroid is the restriction of the dual matriod of $W$ restricted to the exact subdiagram (Remark \ref{remark exact dual restiction}).
+The main result of section \ref{sec: matroids and equivalence} shows that that two admissible Wilson loop diagrams define the same matroid if and only if they are equivalent (Theorem \ref{same matroid iff equiv}).
+We obtain a formula for the number of admissible Wilson loop diagrams in each equivalence class (Corollary \ref{number of equiv diagrams}) {\color{violet}as well as the number of equivalence classes}.
+In this way, we give a comple characterization of the relationship between Wilson Loop diagrams and their associated matroids.
+
+asdf
 
@@
 
-\begin{rmk}
+\begin{rmk} \label{remark exact dual restiction}
 Let $M^*$ denote the dual of a matroid.
@@
 
-\sanote{Should the rest of this section be stuck in the next section?}
 We now make a few observations about the geometry of matroids defined by exact diagrams.
 
-In \cite{wilsonloops}, the authors show that all admissible Wilson loop diagrams correspond to positroids.
+In \cite{wilsonloop}, the authors show that all admissible Wilson loop diagrams correspond to positroids.
 That is, they correspond to matroids that can be represented by elements of the positive Grassmannians $\Gr(|\cP|, n)$.
@@
 
-\subsection{Matroids and equivalent diagrams}
+\subsection{Matroids and equivalent diagrams \label{sec: matroids and equivalence}}
 \note{Si\^an postponed reading this section until the earlier ones are fixed.}
-Now we are ready to prove the main results of this section, namely that two Wilson loop diagrams define the same matroid if and only if they are equivalent (Theorem [ref]) and a formula for the number of Wilson loop diagrams in a given equivalence class (Corollary [ref]).
+Now we are ready to prove the main results of this section, namely that two Wilson loop diagrams define the same matroid if and only if they are equivalent (Theorem \ref{same matroid iff equiv}).
+We also {\color{violet}count the number of equivalence classes amongst Wilon Loop diagrams with $n$ vertices and $k$ propagators and} give a formula for the number of Wilson loop diagrams in a given equivalence class (Corollary \ref{number of equiv diagrams}), completing the characterization of the correspondence between Wilson Loop diagrams and matroids starting in \cite{wilsonloop}.
 
@@
 \begin{proof}
-One direction has been proved in \ref[Theorem 1.18]{wilsonloops}, but we give a different proof here to be consistent with the method of this document.
+One direction has been proved in \cite[Theorem 1.18]{wilsonloop}, but we give a different proof here to be consistent with the method of this document.
 
@@
 \end{cor}
+
+In this section we have characterized the correspondence between Wilson loop diagrams and positroids, showing that Wilson Loop diagrams define the same matroid if and only if they are equivalent (Theorem \ref{same matroid iff equiv}).
+Corollary \ref{number of equiv diagrams} enumerates the fibres of the map from Wilson Loop diagrams to positroids.
+{\color{violet} By counting the number of equivalence classes (Theorem \ref{}), we enumerate the number of positroids defined by Wilson Loop diagrams.
+In section \ref{}, Theorem \ref{}, we show that each Wilson Loop diagram with $n$ vertices and $k$ propagators define a positroid cell of dimension $3k$.
+Comparing the result of Theorem \ref{} to the number of positroid cells of a particular dimension in $\Grtnn(n, k)$, [CITE AND FIND FORMULA HERE], we see that \emph{Wilson loop diagrams do not map onto all positroids of the correct dimension.}}
 

### 2019-01-29 General WLD combinatorics.tex
started poking at section 3.1 ... namely length discussion

@@
 \begin{dfn}\label{props inside p}
-Let $p$ be a propagator supported on $(i,j)$ in $W$.
+Let $W = (\cP, n)$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$ be a propagator.
+As always, we use the convention $i+1 <_1 j$.
 The region of $W$ bounded by $p$ and the edge of the Wilson loop diagram from $i$ to $j+1$ is refered to as the region {\bf inside} $p$, and the complement is the region {\bf outside }$p$.
@@
 outside) $p$, excluding $p$ itself.
-\end{dfn}
-Note that this depends on the order of $i$ and $j$: if we view $p$ as supported on $(j,i)$ (for example, if we are working with the $<_j$ order on vertices) then the regions inside and outside $p$ are swapped.
+\end{dfn} \sanote{changed dfn to match notation} \sanote{do we really mean $i$ to $j+1$, or $i+1$ to $j$, as in length}
+
+Note that this depends on the convention that $i+1 <_1 j$: if we work with the $<_j$ order on vertices then the regions inside and outside $p$ are swapped.
+\sanote{Is this remark needed?
+or does is obfuscate?}
 
 \begin{dfn}\note{right now this doesn't depend on the order of $i$ and $j$, but that might matter later on?}
-Let $p$ be a propagator supported on $(i,j)$.  Define the \textit{length} of $p$ to be 
+Let $p = (i,j) \in cP$ be a propagator in $W$.  Define the \textit{length} of $p$ to be 
 \[\ell(p) = min\big\{|[i+1,j]|,|[j+1,i]|\big\}.\]
 \end{dfn}
-In other words, the length of $p$ is the number of vertices inside $p$.
+In other words, given that $p$ partitions the vertices of $W$, $\ell(p)$ is the size of the smaller of the two partitions.
 

### 2019-01-29 General WLD combinatorics.tex
Minor edits to section 3.4 (dimension)

--- 2019-01-25 General WLD combinatorics.tex
@@
   Let $W$ be an admissible Wilson loop diagram with $k$ propagators and with a vertex $i$ which supports no propagators.
-Let $V$ be $W$ with $i$ removed.
+Let $V$ be $W$ with vertex $i$ removed.
 Then the Le diagram of $W$ is the Le diagram of $V$ with an extra column of all $0$s inserted so as to be labelled $i$ on its bottom in the Oh labelling of the border of the shape of the Le diagram
@@
 
-  Since $i$ does not appear in the Grassmann necklace of $W$, in particular it is not in the first element of the necklace, and so in the Oh labelling of the boundary of the partition shape for the Le diagram (inside the rectangle $(k, n-k)$), $i$ labels a horizontal edge or equivalently the bottom of a column of boxes.
-The shapes of the Le diagrams of $V$ and $W$ are the same except for the insertion of this column since the first Grassmann necklace elements are the same except for the incrementation of the indices $\geq i$ in the transition from the neccklace for $V$ to the necklace for $W$.
-
-  By the algorithm of \cite{reversingOh}, since $i$ never appears in the Grassmann necklace of $W$, the column labelled $i$ is filled with all $0$s.
+By Lemma~\ref{no coloops} we know that $i \not\in I_1^{(W)}$, and so $i$ must label a horizontal edge on the boundary of the Le diagram of $W$, i.e.
+it must be a column label.
+The shapes of the Le diagrams of $V$ and $W$ are the same except for the insertion of this column since the first Grassmann necklace elements are the same except for the incrementation of the indices $\geq i$ in the transition from the necklace for $V$ to the necklace for $W$.
+
+By the algorithm of \cite{reversingOh} [ref][Sian: update this when/if you put this alg in section 3.1], since $i$ never appears in the Grassmann necklace of $W$, the column labelled $i$ is filled with all $0$s.
 Otherwise the algorithm of \cite{reversingOh} behaves identically on $V$ and $W$ with the plusses for the incremented indices shifted one column to the left, thus skipping over column $i$ in the Le diagram for $W$.
@@
 
-Since it is clear that dihedral transformations of a Wilson loop diagram $W$ correspond to dihedral transformations of the chord diagram representation of $\pi_W$, and that the number of alignments in a chord diagram is preserved under dihedral transformations, the result follows.
+It can easily be seen from \cite[Section 17]{Postnikov} and Algorithm \ref{alg:put GN on WLD} that dihedral transformations of a Wilson loop diagram $W$ correspond to dihedral transformations of the chord diagram representation of $\pi_W$.
+Since the number of alignments in a chord diagram is preserved under dihedral transformations, the result follows.
 \end{proof}
@@
   \item $p = (i, n-1)$ with no propagators inside it (that is $i+2, \ldots, n-2$ do not support any propagators in $W'$).
-  \item Either the edges $i$ in $W'$ only supports $p$ or the edge $i$ in $W'$ supports exactly one other propagator $q = (j ,i)$ with no other propagators inside $q$.
+  \item Either the edge $i$ in $W'$ only supports $p$ or the edge $i$ in $W'$ supports exactly one other propagator $q = (j ,i)$ with no other propagators inside $q$.
   \end{itemize}
@@
 
-  By Lemma~\ref{lem dihedral} there is a dihedral transformation of $V$ satisfying the statement of the lemma with $p$ and $q$ both length 2.
+  By Lemma~\ref{lem dihedral} there is a dihedral transformation of $V$ which yields a diagram satisfying the statement of the lemma with $p$ and $q$ both length 2.
 Restoring the vertices which do not support any propagators, we obtain a dihedral transformation $W'$ of $W$ as desired (with potentially longer lengths for $p$ and $q$).
@@
 
+Our goal is to compute the dimension of the positroid associated to an arbitrary admissible Wilson loop diagram.
+By Lemmas \ref{lem uncovered}, \ref{lem dihedral}, and \ref{lem good p}, it suffices to study the Le diagrams of \hlfix{weakly}{check} admissible Wilson loop diagrams admitting one of the configurations described in Lemma~\ref{lem good p} with propagators $p$ and $q$ (if it exists) both of length 2.
+Diagrams of this type are the subject of the next few lemmas, and are illustrated in Figure~\ref{fig special p}.
+
 \begin{lem}\label{lem I}
-  Let $W$ be an admissible Wilson loop diagram with $n\geq 1$ propagators.
-Suppose $p$ is a propagator of $W$ so that the properties of Lemma~\ref{lem good p} are satisfied for $p$ in $W$ and that $p$ has length $2$, as does $q$ if we are in the case of Lemma~\ref{lem good p} involving $q$.
+Let $W$ be an admissible Wilson loop diagram with $n\geq 1$ propagators, and suppose that $W$ admits one of the configurations described in Lemma~\ref{lem good p} with $p$ and $q$ (if it exists) both of length 2.
 Let $V$ be $W$ with $p$ removed.
@@
 \begin{proof}
-  The two possible situations are illustrated in Figure~\ref{fig special p}.
-
-  If $n-3\in I_1^{V}$ then $n-3\not\in I_1^{W}$, but then $p$ never contributes $n-3$ contradicting Lemma~\ref{vertex cyclic int lem}.
-Thus $n-3\not\in I_1^{V}$ and so in building the Grassmann necklace when we get to vertex $n-3$ any other propagators of $V$ which are supported at $n-3$ have already been taken and so we take $p$.
-Therefore $I_1^{W}= I_1^{V}\cup \{n-3\}$.
-
-  In constructing $I_n^{W}$, first for vertex $n$ we take propagator $p$.
-Then we are at vertex $1$ and precisely the propagators of $V$ remain.
-Thus the rest of the construction will give $I_1^{V}$.
-Therefore $I_n^{W} = I_1^{V}\cup \{n\}$.
-Essentially the same reasoning gives $I_{n-1}^{W} = I_n^{V}\cup \{n-1\}$.
+The two possible situations are illustrated in Figure~\ref{fig special p}. The arguments proceed in a similar manner to Lemma~\ref{vertex cyclic int lem}.
+
+We first consider $I_1^{(W)}$.
+Note that $n-3 \not\in I_1^{(V)}$: for the right hand case this is clear from the diagram (since Algorithm~\ref{alg:put GN on WLD} would assign $q$ no later than vertex $n-4$), while for the left hand case it follows from Lemma \ref{lem no fourth vertex}.
+Therefore when we start at vertex 1 and apply the Grassmann necklace algorithm to $W$, $p$ is the only unassigned propagator when we reach vertex $n-3$ and we have $ I_1^{(W)}(p) = n-3$.
+
+Next, consider $I_n^{(W)}$, i.e.
+we apply the Grassmann necklace algorithm with starting vertex $n$.
+In both cases$I_n^{(W)}(p) = n$.
+We are now at vertex 1, and the unassigned propagators are exactly those that appear in $V$.
+Therefore the algorithm continues as in $I_1^{(V)}$, i.e.
+we have $I_n^{W} = I_1^{V} \cup \{n\}$.
+Similarly, we must have $I_{n-1}^{W} = I_n^{V} \cup \{n-1\}$.
 
 Now consider $I_{n-2}^{W}$.
-If $n-2\not\in I_{n-2}^{V}$ then at vertex $n-2$ we take $p$ and this does not affect the rest of the construction of $I_{n-2}^{V}$, so $I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-2\}$.
-An analogous argument takes care of the first case for $I_k^{W}$.
-Suppose $n-2\in I_{n-2}^{V}$ but $n-1\not\in I_{n-2}^{V}$.
-Then at vertex $n-2$ we take the same propagator in $V$ as in $W$ (in particular not $p$) because $p$ is the counterclockwisemost propagator supported on $n-2$ and so the last propagator the algorithm would choose at this vertex, and by hypothesis $n-2$ does support at least one propagator in $V$.
-However, $n-1$ is not yet taken in $I_{n-2}^{V}$, so at this vertex we will take $p$ in $I_{n-2}^{W}$.
-Following this the construction continues as in $I_{n-2}^{V}$.
-Therefore $I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-1\}$.
-An analogous argument takes care of the case when we have $1<k<n-2$ and $n-3\in I_k^{V}$ but $n-2\not\in I_{k}^{V}$.
-Furthermore, either $n-2$ supports no propagators in $V$ or only $q$ is supported by $n-2$ in $V$ and $q$ is also the only propagator supported by $n-3$.
-Thus it is not possible for $n-3$ and $n-2$ to both be in $I_{k}^{V}$.
-This means that all the cases for $I_k^{W}$ are now proved.
-
-  The remaining case is when $n-1,n-2\in I_{n-2}^{V}$ for the construction of $I_{n-2}^{W}$.
-We must then have a propagator $q$ as in the right hand side of Figure~\ref{fig special p}.
-In the construction of $I_{n-2}^{W}$, at vertex $n-2$ we take propagator $q$, as in $I_{n-2}^{V}$.
-Then at vertex $n-1$ we take propagator $p$ which is different from what occurs in $I_{n-2}^{V}$.
-Next we are at vertex $n$ and propagators $p$ and $q$ have been taken.
-Thus we are proceeding like $I_{n}^{V}$ but without propagator $q$.
-Fortunately we can determine explicitely how propagator $q$ contributes to $I_{n}^{V}$.
-By Lemma~\ref{vertex cyclic int lem} propagator $q$ contributes $n-5$ to $I_{n}^{V}$, and the only way this can occur is if all other propagators of $V$ were already taken by the time we got to vertex $n-5$.
-Therefore $I_{n-2}^{W} = (I_{n}^{V} - \{n-5\}) \cup \{n-1, n-2\}$.
+If $n-2\not\in I_{n-2}^{V}$ (i.e.
+$n-2$ supports no propagators in $V$), then in $W$ the algorithm assigns $p$ to $n-2$ and this does not affect the rest of the construction of $I_{n-2}^{V}$, so we obtain $I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-2\}$ as above.
+
+On the other hand, if $n-2\in I_{n-2}^{V}$ then we must be in the right hand case of Figure~\ref{fig special p} and the algorithm assigns $q$ to vertex $n-2$ in both $V$ and $W$ (since $p$ is always the counterclockwise-most propagator supported on vertex $n-2$).
+If $n-1 \not\in I_{n-2}^{(V)}$, then in $W$ the algorithm assigns $p$ to $n-2$ and then proceeds identically to the remainder $I_{n-2}^{(V)}$; thus $I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-1\}$ in this case.
+
+Finally, if $n-2,n-1 \in I_{n-2}^{(V)}$ then the algorithm in $W$ assigns $q$ to $n-2$ and $p$ to $n-1$ as above, but this is different to what occurs in $I_{n-2}^{(V)}$ so we cannot argue as above.
+We are now at vertex $n$ and only propagators $p$ and $q$ have been assigned; thus we are proceeding as in the construction of $I_n^{(V)}$ but without propagator $q$.
+By Lemma~\ref{vertex cyclic int lem} we know that $q$ was assigned to $n-5$ by $I_n^{(V)}$, and the only way this could occur is if all other propagators in $V$ had already been assigned when we reached vertex $n-5$.
+Therefore $I_{n-2}^{W} = (I_{n}^{V} \setminus \{n-5\}) \cup \{n-1, n-2\}$; this completes all cases for $I_{n-2}^{(W)}$.
+
+The arguments for $I_k^{(W)}$ ($1< k < n-2$) proceed analagously to those of $I_{n-2}^{(W)}$, with one simplification: we cannot have both $n-3$ and $n-2$ in $I_k^{(V)}$ since $q$ is the only propagator that could be assigned to either of them, and it cannot be assigned to both.
+
 This covers all cases and hence completes the proof.

### 2019-02-04 General WLD combinatorics.tex
Signed-off-by: Amasus <susama@alum.mit.edu> changed definitions in secton 3.2, as discussed wtih Karen

--- 2019-01-29 General WLD combinatorics.tex
@@
 \newcommand{\sgale}[1]{\prec_{#1}}
+\renewcommand\vec[1]{\overrightarrow{#1}}
+\newcommand\cev[1]{\overleftarrow{#1}}
 %*****************
@@
 \begin{dfn}\label{WLdfn}
-A Wilson loop diagram is given by the following data: a cyclicly ordered set $V$, along with a choice of first vertex (labeled $1$), and $k$ pairs, called propagators, written $\{p_r = (i_r, j_r)\}_{r=1}^k$ with labels ordered such that $i_r +1 < j_r$ relative to the fisrt vertex.
+A Wilson loop diagram is given by the following data: a cyclicly ordered set $V$, along with a choice of first vertex (labeled $1$), and $k$ pairs, called propagators, written $\{p_r = (i_r, j_r)\}_{r=1}^k$.
 \end{dfn}
+
+Generally speaking, the propagators are undirected, so $p = (i,j) = (j,i)$.
+In order to fix a convention, we write $p = (i,j)$ with  $i +1 < j$ relative to the first vertex.
+However, at times (section \ref{sec:propagator configs}), we consider directed propagators, where $p= (i,j)$ denotes a particular propagator flowing in one direction, while $p= (j,i)$ denotes the \emph{same} propagators flowing in the opposite direction.
+\sanote{Addendum 1}
 
@@
 In this way, we give a comple characterization of the relationship between Wilson Loop diagrams and their associated matroids.
-
-asdf
 
@@
 
+ \sanote{can we use the notation directed propagator here? to emphasize the notational change?}
+
 \begin{dfn}\label{props inside p}
-Let $W = (\cP, n)$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$ be a propagator.
-As always, we use the convention $i+1 <_1 j$.
-The region of $W$ bounded by $p$ and the edge of the Wilson loop diagram from $i$ to $j+1$ is refered to as the region {\bf inside} $p$, and the complement is the region {\bf outside }$p$.
+Let $W = (\cP, n)$ be an admissible Wilson loop diagram, and $\vec{p} = (i,j) \in \cP$ be a directional propagator and $\cev{p} = (j,i)$ be the same propagator with the opposite directionality.
+Call the vertices of $W$ \bas V_{in}(\vec{p}) = \{a \in [n] | i <_i a <_i j\} \cup V(p) \eas the region of $W$ {\bf inside} $\vec{p}$, and \bas V_{out}(\vec{p}) = \{a \in [n] | j <_j a <_j i\} \cup V(p) \;.\eas the region {\bf outside }$\vec{p}$.
 The set of propagators inside (resp.
-outside) $p$ are those lying in the region inside (resp.
-outside) $p$, excluding $p$ itself.
-\end{dfn} \sanote{changed dfn to match notation} \sanote{do we really mean $i$ to $j+1$, or $i+1$ to $j$, as in length}
-
-Note that this depends on the convention that $i+1 <_1 j$: if we work with the $<_j$ order on vertices then the regions inside and outside $p$ are swapped.
-\sanote{Is this remark needed?
-or does is obfuscate?}
+outside) $\vec{p}$ are those lying in the region inside (resp.
+outside) are the $q \neq p \in \cP$ such that  $V(q) \subset V_{in}(p)$ (resp.
+$V(q) \subset V_{out}(p)$) .
+\end{dfn}
+
+Note that under this definiton, $V_{in}(\vec{p}) = V_{out}(\cev{p})$ and $V_{out}(\vec{p}) = V_{in}(\cev{p})$.
+That is, the regions inside and outside of a propagator switch depending on the direction imposed on the propagators $p$.
 
@@
 Let $p = (i,j) \in cP$ be a propagator in $W$.  Define the \textit{length} of $p$ to be 
-\[\ell(p) = min\big\{|[i+1,j]|,|[j+1,i]|\big\}.\]
+\[\ell(p) = min\big\{|V_(in)(\vec{p})|,|V_(in)(\cev{p})|\big\}-2 = min\big\{|[i+1,j]|,|[j+1,i]|\big\}.\]
 \end{dfn}

### 2019-02-06 General WLD combinatorics.tex
continuing slow progress on dimension lemmas

--- 2019-01-29 General WLD combinatorics.tex
@@
 Let $\binom{[n]}{k}$ be the set of all $k$-subsets of the cyclically ordered set $[n]$.  For each $j \in [n]$, we can define a total order $\leq_j$ on the interval $[n]$ by
-\[] j <_j j+1 <_j \dots <_j n <_j 1 \dots <_j j-1\;.\]
+\[ j <_j j+1 <_j \dots <_j n <_j 1 \dots <_j j-1\;.\]
 This in turn induces a total order on $\binom{[n]}{k}$, namely the lexicographic order with respect to $<_j$.
-It also induces a separate partial order $\gale{j}$ on $\binom{[n]}{k}$ (the \textit{Gale order} \cite{Gale}), which is defined as follows: for
-\[A = \{a_1 <_j a_2 <_j \dots <_j a_k\} \text{ and } B = \{b_1 <_j b_2 <_j \dots <_j b_k\} \in \binom{[n]}{k},\] we say that
+It also induces a separate partial order $\gale{j}$ on $\binom{[n]}{k}$ (the {\bf Gale order} \cite{Gale}), which is defined as follows: for
+\[A = \{a_1 <_j a_2 <_j \dots <_j a_k\} \text{ and } B = \{b_1 <_j b_2 <_j \dots <_j b_k\} \in \binom{[n]}{k},\] we define
 \[A \gale{j} B \text{ if and only if } a_r \leq_j b_r \text{ for all }1 \leq r \leq k.\]
@@
 \begin{dfn}\label{def:grassmann necklace}
-A Grassmann necklace of type $(k,n)$ is a sequence $(I_1, \dots, I_n)$ of $n$ sets $I_i \in \binom{[n]}{k}$ such that for each $i \in [n]$:
+A {\bf Grassmann necklace} of type $(k,n)$ is a sequence $(I_1, \dots, I_n)$ of $n$ sets $I_i \in \binom{[n]}{k}$ such that for each $i \in [n]$:
 \begin{itemize}
@@
 
-[Le diagrams]
+\begin{dfn}\label{def:le diagram}
+A {\bf Le diagram} is a Young diagram in which every square contains either a $+$ or a $0$, subject to the rule that if a square contains a $0$ then either all squares to its left (in the same row) must also contain a $0$, or all squares above it (in the same column) must also contain a $0$, or both.
+\end{dfn}
+
+By [ref], the set of all Le diagrams that fit within a $k\times(n-k)$ rectangle is in 1-1 correspondence with the positroid cells of $\Gr(k,n)$.
+The dimension of a positroid cell is equal to the number of $+$ squares in its Le diagram [ref].
+
+The rows and columns of a Le diagram are labelled as follows: given a Le diagram fitting inside a $k\times (n-k)$ box, arrange the numbers $1,2, \dots, n$ along its southeast border, starting from the top-right corner.
+See Figure \ref{fig:row column numbering} for examples.
+
+\begin{figure}[h!]
+\[\begin{tikzpicture}[baseline=(current bounding box.east),scale=0.75]
+\draw (1,0) grid (2,3);
+\draw (2,1) grid (4,3);
+\draw (4,2) grid (5,3);
+\draw[dotted] (2,0) -- (5,0) -- (5,2);
+
+\node at (5.15,2.5) {\footnotesize$1$};
+\node at (4.5,1.85) {\footnotesize$2$};
+\node at (4.15,1.5) {\footnotesize$3$};
+\node at (3.5,0.85) {\footnotesize$4$};
+\node at (2.5,0.85) {\footnotesize$5$};
+\node at (2.15,0.5) {\footnotesize$6$};
+\node at (1.5,-0.15) {\footnotesize$7$};
+%\node at (0.5,-0.15) {\footnotesize$8$};
+\end{tikzpicture}
+\qquad \qquad
+\begin{tikzpicture}[baseline=(current bounding box.east),scale=0.75]
+\draw (1,0) grid (2,3);
+\draw (2,1) grid (4,3);
+\draw (4,2) grid (5,3);
+\draw[dotted] (2,0) -- (6,0) -- (6,3) -- (5,3);
+
+\node at (5.5,2.85) {\footnotesize$1$};
+\node at (5.15,2.5) {\footnotesize$2$};
+\node at (4.5,1.85) {\footnotesize$3$};
+\node at (4.15,1.5) {\footnotesize$4$};
+\node at (3.5,0.85) {\footnotesize$5$};
+\node at (2.5,0.85) {\footnotesize$6$};
+\node at (2.15,0.5) {\footnotesize$7$};
+\node at (1.5,-0.15) {\footnotesize$8$};
+%\node at (0.5,-0.15) {\footnotesize$9$};
+\end{tikzpicture}
+\]
+\caption{Row and column numbering for a Young diagram with $k = 3$, $n = 7$ (left) and $k = 3$, $n = 8$ (right).
+The top left box in each diagram has coordinates $(1,7)$ (left diagram), $(2,8)$ (right diagram).}
+\label{fig:row column numbering}
+\end{figure}
+
+An algorithm for constructing the Le diagram associated to a Grassmann necklace was given by Agarwala and Fryer in [ref].
+Since we will make use of this algorithm in Section [ref] below, we summarise the process here.
+\begin{algorithm}\label{alg:GN to Le} \ [ref]
+Let $(I_1,\dots,I_n)$ be a Grassmann necklace of type $(k,n)$. Within a $k \times(n-k)$ square, draw the Young diagram whose rows are labelled by $I_1$ (as per the convention above).
+
+For each $i$, $2 \leq i \leq n$:
+\begin{itemize}
+\item Write \[I_1 \setminus I_i = \{a_1 > a_2 > \dots > a_r\}, \quad I_i \setminus I_1 = \{b_1 < b_2 < \dots < b_r\},\]
+where the inequalities denote the $<_1$ order (subscripts suppressed for clarity).
+\item For $1 \leq j \leq r$ , place a $+$ in square $(a_j,b_j)$ of the diagram. (We will sometimes refer to this $+$ as being {\em in the $a_j \rightarrow b_j$ position}.)
+\end{itemize}
+After performing the above for $2 \leq i \leq n$, place a $0$ in any remaining unfilled boxes.
+\end{algorithm}
+
+An algorithm for constructing the Grassmann necklace of a Le diagram also exists; this was given by Oh in [ref].
+A method for using the Le diagram to test whether a given $k$-subset is a basis for the corresponding positroid or not was given by Casteels in [ref].
 
@@
 If $j \in [n]$ is a loop then $j \not\in I_j$, which can only happen if there are no propagators supported on vertex $j$.
-Conversely, if $j$ supports no propagators, then Algorithm ~\ref{alg:put GN on WLD} never assigns a propagator to $j$ and hence $j \not\in I_i$ for all $i \in [n]$.
+Conversely, if $j$ supports no propagators, then Algorithm~\ref{alg:put GN on WLD} never assigns a propagator to $j$ and hence $j \not\in I_i$ for all $i \in [n]$.
 \end{proof}
@@
 Our next goal is to show that the dimension of the positroid cell defined by a Wilson loop diagram $(\cP, [n])$ has dimension $3|\cP|$.
-Marcott in ***cite this*** has a different proof which is geometric and more elegant, bit it is not easy to track the effect of a particular propagator.
+Marcott in ***cite this*** has a different proof which is geometric and more elegant, but it is not easy to track the effect of a particular propagator.
 Our approach is much more explicit.
 
-The dimension of a positroid cell is the same as the number of plusses in the associated Le diagram \cite[Theorem 6.5]{Postnikov}, and so with Algorithm~\ref{alg:put GN on WLD} along with the algorithm for passing from a Grassmann necklace to a Le diagram (reversing Oh's algorithm) described by some of us in \cite{reversingOh}, we can, at the cost of a bit of messy grunt work, give a recursive proof of the $3|\cP|$-dimensionality that explicitly describes the changes in the positions of the plusses in the Le diagram.
-
-%In \cite{reversingOh}, Agarwala and Fryer give an algorithm for passing from a Grassmann Necklace to a Le diagram.
-We use this algorithm here to pass from a Wilson loop diagram to its associated Le diagram.
-In this manner, we show that the positroid cell defined by a Wilson loop diagram has dimension $3|\cP|$.
-Maybe say something about Amplituhedra having $4k$ dimension, but this is not quite what we have, since we are ignoring one column.
-%
-%When I speak of a \emph{WLD}, I mean one which satisfies your density hypothesis and other standard hypotheses.
-When I speak of a propagator \emph{contributing} a vertex to an element of the Gra\ss mann\footnote{I suppose it is a bit of an affectation to use an eszett when writing in English, and actually the eszett is kind of ugly in this font, but since I've started to I'll stick with it for now but you certainly shouldn't feel obliged to do it too.} necklace I mean that according to the rule you guys have to build the Gra\ss mann necklace from the diagram by starting at a vertex and taking the clockwise-most covering propagator which hasn't already been taken, when a propagator is taken then it is contributing that vertex.
-Also, I will be using your algorithm to convert the Gra\ss mann necklace into a Le diagram by non-intersecting paths.
-%
-%
-%We need four lemmas from stuff you guys have already figured out.  The first one is a corollary of your lemma characterizing intervals contributed by each covered vertex of a
-%propagator.
-%
-%The first lemma is Lemma~\ref{vertex cyclic int lem} and I moved it up to a previous section.
-%
-%The second lemma is the fact that we understand uncovered vertices.
-You probably see many ways to prove this from things you already know.
-One would be to say that from your algorithm the column of the uncovered vertex simply plays no role.
-
-We need a number of lemmas, of roughly increasing degree of technicality.
+Recall that the dimension of a positroid cell is equal to the number of plusses in the associated Le diagram \cite[Theorem 6.5]{Postnikov}.
+By combining Algorithms~\ref{alg:put GN on WLD} and \ref{alg:GN to Le} (converting from WLD to Grassmann necklace to Le diagram) we explicitly describe the effect of adding another propagator to a Wilson loop diagram in terms of the plusses of the associated Le diagrams, and hence give a recursive proof of the $3|\cP|$-dimensionality of the cells.
+
+We start with several lemmas, of roughly increasing degree of technicality.
 
 \begin{lem}\label{lem uncovered}
-  Let $W$ be an admissible Wilson loop diagram with $k$ propagators and with a vertex $i$ which supports no propagators.
+Let $W$ be an admissible Wilson loop diagram with $k$ propagators, and with a vertex $i$ which supports no propagators.
 Let $V$ be $W$ with vertex $i$ removed.
-Then the Le diagram of $W$ is the Le diagram of $V$ with an extra column of all $0$s inserted so as to be labelled $i$ on its bottom in the Oh labelling of the border of the shape of the Le diagram
+Then the Le diagram of $W$ is obtained from the Le diagram of $V$ by inserting an extra column containing all $0$s in position $i$ (i.e.
+such that the new column has the label $i$).
 \end{lem}
-
-\note{I'm not sure how much I should assume here in terms of what the reader already knows}
 
@@
 
-By the algorithm of \cite{reversingOh} [ref][Sian: update this when/if you put this alg in section 3.1], since $i$ never appears in the Grassmann necklace of $W$, the column labelled $i$ is filled with all $0$s.
+By Algorithm~\ref{alg:GN to Le}, since $i$ never appears in the Grassmann necklace of $W$ we know that the column labelled $i$ contains only $0$ boxes.
 Otherwise the algorithm of \cite{reversingOh} behaves identically on $V$ and $W$ with the plusses for the incremented indices shifted one column to the left, thus skipping over column $i$ in the Le diagram for $W$.
 \end{proof}
-
-%The third lemma is now lemma~\ref{lem sian}.
-
-%The fourth lemma is that we can rotate or reflect without changing the number of plusses.  The best way to see this is probably geometrically so I leave that up to you.
 
@@
 \end{proof}
-
-%\subsubsection{Changes in Gra\ss mann necklaces for nice configurations}
-
-%Given a propagator $p$ in a WLD $D$, note that $p$ divides remaining propagators of $D$ into two sets depending on which side of $p$ they live.
 
@@
 
-%Given an admissible Wilson loop diagram $W$, $I_i^{D}$ denotes the $i$th Grass mann necklace element corresponding to $W$.
-
-Our goal is to compute the dimension of the positroid associated to an arbitrary admissible Wilson loop diagram.
-By Lemmas \ref{lem uncovered}, \ref{lem dihedral}, and \ref{lem good p}, it suffices to study the Le diagrams of \hlfix{weakly}{check} admissible Wilson loop diagrams admitting one of the configurations described in Lemma~\ref{lem good p} with propagators $p$ and $q$ (if it exists) both of length 2.
-Diagrams of this type are the subject of the next few lemmas, and are illustrated in Figure~\ref{fig special p}.
+Combining Lemmas \ref{lem uncovered}, \ref{lem dihedral}, and \ref{lem good p}, it therefore suffices to study the Le diagrams of \hlfix{weakly}{check} admissible Wilson loop diagrams admitting one of the configurations described in Lemma~\ref{lem good p} with propagators $p$ and $q$ (if $q$ exists) both of length 2.
+See Figure~\ref{fig special p} for an illustration of the two possibilities.
+
+The next few lemmas describe how diagrams of this type are related to the corresponding diagram with propagator $p$ removed, first in terms of the Grassmann necklaces and then in terms of the Le diagrams.
+These technical lemmas will form the backbone of the inductive step in the main dimensionality argument.
 
 \begin{lem}\label{lem I}
-Let $W$ be an admissible Wilson loop diagram with $n\geq 1$ propagators, and suppose that $W$ admits one of the configurations described in Lemma~\ref{lem good p} with $p$ and $q$ (if it exists) both of length 2.
+Let $W$ be an admissible Wilson loop diagram with $n\geq 1$ propagators, and suppose that $W$ admits one of the configurations described in Lemma~\ref{lem good p}, with $p$ and $q$ (if $q$ exists) both of length 2.
 Let $V$ be $W$ with $p$ removed.
@@
 we apply the Grassmann necklace algorithm with starting vertex $n$.
-In both cases$I_n^{(W)}(p) = n$.
+In both cases we have $I_n^{(W)}(p) = n$.
 We are now at vertex 1, and the unassigned propagators are exactly those that appear in $V$.
@@
   The shape of the Le diagram of $V$ can be built from left to right of the following blocks: a rectangle with 3 columns, one more column of the same length, a partition shape with at most as many rows as the rectangle.
-  The shape of the Le diagram of $W$ can be built from left to right of the following blocks: a rectangle with 3 columns and one more row than the first rectangle of $V$, the same partition shape as in $V$.
+  The shape of the Le diagram of $W$ can be built from left to right of the following blocks: a rectangle with 3 columns and one more row than the first rectangle of $V$, and the same partition shape as in $V$.
 \end{lem}
@@
 \begin{proof}
-  $I_1$ determines the shape of the Le diagram.
-  By Lemma~\ref{lem I}, $I_1^{W} = I_1^{V}\cup \{n-3\}$.
-This implies that the right hand boundary of the shape of $V$ is the same as the right hand boundary of the shape of $W$ except that $W$ has one additional row of 3 boxes while $V$ has an additional column in the $n-3$ position; that is, a new column fourth from the left.
-\end{proof}
-
-The shapes of the Le diagrams of $V$ and $W$ are illustrated in Figure~\ref{fig Le}.
-The pieces of the Le diagrams will be called $\mathcal{A}$ and $\mathcal{B}$ in what follows, as in the figure.
-Over the course of the next few lemmas we will prove that the plusses in the $\mathcal{B}$ parts of the Le diagrams of $V$ and $W$ are identical and the plusses in the $\mathcal{A}$ parts are very closely related.
-When we speak of a plus in the Le diagram of $V$ being the same as in $W$ or vice versa, we mean that the plus' position in $\mathcal{A}$ or $\mathcal{B}$ is the same.
-Because of the column insertion the absolute indices may differ.
+See Figure~\ref{fig Le} for an illustration of the shapes described in the statement of the lemma.
+
+Recall that $I_1$ determines the shape of the Le diagram.
+By Lemma~\ref{lem I}, we know that $I_1^{W} = I_1^{V}\cup \{n-3\}$, and that $n,n-1,n-2, n-3 \not\in I_1^{(V)}$.
+This implies that the right hand boundary of the shape of $V$ is the same as the right hand boundary of the shape of $W$ except that $W$ has one additional row of 3 boxes while $V$ has an additional column in the $n-3$ position; that is, an extra column fourth from the left.
+\end{proof}
+
+The pieces of the Le diagrams of $V$ and $W$ will be called $\mathcal{A}$ and $\mathcal{B}$ in what follows, as in Figure~\ref{fig Le}.
+Over the course of the next few lemmas we will prove that the plusses in the $\mathcal{B}$ parts of each diagram are identical, and that the plusses in the $\mathcal{A}$ parts are very closely related.
+
+Note that when we speak of a plus in the Le diagram of $V$ being the same as in $W$ or vice versa, we mean that the position of the plus in $\mathcal{A}$ or $\mathcal{B}$ is the same; because of the column insertion the absolute indices may differ.
 
@@
 
-Suppose we are following the Grassmann necklace to Le diagram algorithm, and we put a plus in a box because of a path from vertical boundary edge $i$ to bottom boundary edge $j$.
-Then say this plus is in the $i\rightarrow j$ position.
+%Recall Algorithm~\ref{alg:GN to Le}, which constructs the Le diagram associated to a Grassmann necklace.
+As described in Section [ref], if Algorithm~\ref{alg:GN to Le} places a $+$ in the box with row index $i$ and column index $j$, we say that this plus is in the $i \rightarrow j$ position.
 
@@
 Let $V$ and $W$ be as in Lemma~\ref{lem I}.
-  Then $I_n^{W}$ and $I_{n-1}^{W}$ give all the same plusses as $I_n^{V}$ along with plusses in the leftmost two boxes of the bottom row of the Le diagram of $W$.
+Then $I_n^{W}$ and $I_{n-1}^{W}$ together yield the same plusses as $I_n^{V}$ did, along with extra plusses in the leftmost two boxes of the bottom row of the Le diagram of $W$.
 \end{lem}
@@
 \begin{proof}
-  By Lemma~\ref{lem I} $I_n^{W}= I_1^{V} \cup \{n\}$, so by the Grassmann necklace to Le diagram algorithm the only plus this builds in the Le diagram of $W$ is  the one in the $n-3\rightarrow n$ position, that is in the leftmost box of the bottom row.
-
-  Also by Lemma~\ref{lem I} $I_{n-1}^{W} = I_n^{V} \cup \{n-1\}$.
-Additionally $n-3\not\in I_{n}^{V}$ since if it were then $n-3$ would also be in $I_1^{V}$ and hence propagator $p$ could not contribute $n-3$ to $I_1^{W}$ in contradiction to Lemma~\ref{vertex cyclic int lem}.
+By Lemma~\ref{lem I} we have $I_n^{W}= I_1^{V} \cup \{n\}$ and $I_1^{(W)} = I_1^{(V)} \cup \{n-3\}$. Thus 
+\[I_1^{(W)} \setminus I_n^{(W)} = \{n-3\}, \qquad \qquad I_n^{(W)} \setminus I_1^{(W)} = \{n\},\]
+and so by Algorithm~\ref{alg:GN to Le} we have a plus in the $(n-3) \rightarrow n$ position, i.e. in the leftmost box of the bottom row.
+
+Also by Lemma~\ref{lem I} we have $I_{n-1}^{W} = I_n^{V} \cup \{n-1\}$.
+Recall from the proof of Lemma~\ref{lem I} that $n-3,n-2,n-1,n \not\in I_1^V$; therefore $I_1^W\setminus I_{n-1}^W = (I_1^V \setminus I_n^V) \cup\{n-3\}$, and $n-3$ is maximal in this set.
+Similarly,
+\[I_{n-1}^W \setminus I_1^W = (I_n^V \setminus I_1^V) \cup \{n-1\} \subseteq \{n-1,n\},\]
+where the final inclusion follows from the definition of Grassmann necklace.
+In particular, $n-1$ is minimal in this set, so Algorithm~\ref{alg:GN to Le} yields a plus in the $(n-3) \rightarrow (n-1)$ position (i.e.
+the second box in the bottom row of the Le diagram of $W$) along with any plusses yielded by $I_n^V$.
+
+% Additionally $n-3\not\in I_{n}^{V}$ since if it were then $n-3$ would also be in $I_1^{V}$ and hence propagator $p$ could not contribute $n-3$ to $I_1^{W}$ in contradiction to Lemma~\ref{vertex cyclic int lem}.
 Similarly $n-1, n-2\not\in I_n^{V}$.
@@
 \begin{lem}\label{lem n-2 good}
-  Let $V$ and $W$ be as in Lemma~\ref{lem I} with $n-2 \not\in I_{n-2}^{V}$.
-
-  Then $I_{n-2}^{W}$ gives
-  an $n-3\rightarrow n-2$ plus and
-  all the $I_{n-1}^{V}=I_{n-2}^{V}$ plusses.
+  Let $V$ and $W$ be as in Lemma~\ref{lem I}, with $n-2 \not\in I_{n-2}^{V}$. Then $I_{n-2}^{W}$ contributes an $(n-3)\rightarrow (n-2)$ plus, and all of the $I_{n-1}^{V}=I_{n-2}^{V}$ plusses.
 \end{lem}
@@
 \begin{proof}
-  If $n-2\not\in I_{n-2}^{V}$ then $I_{n-1}^{V}=I_{n-2}^{V}$ and by Lemma~\ref{lem I} $I_{n-2}^{W} = I_{n-1}^{V} \cup \{n-2\}$.
-Note that $n-3\not\in I_{n-2}^{V}$ by Lemma~\ref{vertex cyclic int lem}.
-Therefore the paths for $I_{n-2}^{W}$ are the paths for $I_{n-1}^{V}$ along with the $n-3\rightarrow n-2$ path.
+If $n-2\not\in I_{n-2}^{V}$ then $I_{n-1}^{V}=I_{n-2}^{V}$ and by Lemma~\ref{lem I} we have $I_{n-2}^{W} = I_{n-1}^{V} \cup \{n-2\}$.
+Note that $n-3\not\in I_{n-2}^{V}$ by Lemma~\ref{lem no fourth vertex}.
+Therefore the paths for $I_{n-2}^{W}$ are the paths for $I_{n-1}^{V}$ along with the $(n-3)\rightarrow (n-2)$ path.
 This gives the statement of the lemma.
@@
 \begin{lem}\label{lem n-2 bad}
-  Let $V$ and $W$ be as in Lemma~\ref{lem I} with $n-2,n-1 \in I_{n-2}^{V}$.
-
-  Then $I_{n-2}^{W}$ and $I_{n-3}^{W}$ give the following plusses:
+Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that $n-2,n-1 \in I_{n-2}^{V}$.
+
+Then $I_{n-2}^{W}$ and $I_{n-3}^{W}$ contribute the following plusses to the Le diagram of $W$
   \begin{itemize}
-  \item An $n-3\rightarrow n-2$ plus and an $n-5\rightarrow n-1$ plus.
-  \item All the $I_{n-1}^{V}$ plusses.
-  \item $I_{n-2}^{V}$ gives an $n-5\rightarrow n-2$ plus and no other term in the Gramann necklace of $V$ gives a plus in this column.
-This $+$ does not appear in $W$ from $I_{n-2}^{W}$ but an $n-5\rightarrow n-1$ plus does instead.
+  \item An $(n-3)\rightarrow (n-2)$ plus and an $(n-5)\rightarrow (n-1)$ plus.
+  \item All of the $I_{n-1}^{V}$ plusses.
+  \item In the Le diagram of $V$, $I_{n-2}^{V}$ contributes an $n-5\rightarrow n-2$ plus and no other term in the Grassmann necklace of $V$ gives a plus in this column.
+$I_{n-2}^W$ does not contribute this $+$ but yields an $n-5\rightarrow n-1$ plus instead.
   \item All other plusses of $I_{n-2}^{V}$.
-  \item $I_{n-3}^{V}$ gives a plus in the $n-3$ column.  This $+$ is shifted over into the $n-2$ column in $W$.
+  \item In the Le diagram of $V$, $I_{n-3}^{V}$ gives a plus in the $n-3$ column.  This $+$ is shifted over into the $n-2$ column in $W$.
   \item All other plusses of $I_{n-3}^{V}$.

### 2019-02-06 General WLD combinatorics.tex

@@
 \begin{lem}\label{lem uncovered}
+
 Let $W$ be an admissible Wilson loop diagram with $k$ propagators, and with a vertex $i$ which supports no propagators.
@@
 
-By Lemma~\ref{no coloops} we know that $i \not\in I_1^{(W)}$, and so $i$ must label a horizontal edge on the boundary of the Le diagram of $W$, i.e.
-it must be a column label.
-The shapes of the Le diagrams of $V$ and $W$ are the same except for the insertion of this column since the first Grassmann necklace elements are the same except for the incrementation of the indices $\geq i$ in the transition from the necklace for $V$ to the necklace for $W$.
-
 By Algorithm~\ref{alg:GN to Le}, since $i$ never appears in the Grassmann necklace of $W$ we know that the column labelled $i$ contains only $0$ boxes.
 Otherwise the algorithm of \cite{reversingOh} behaves identically on $V$ and $W$ with the plusses for the incremented indices shifted one column to the left, thus skipping over column $i$ in the Le diagram for $W$.
+By Lemma~\ref{no coloops} we know that $i \not\in I_w^W$, and so $i$ must label a horizontal edge on the boundary of the Le diagram of $W$, i.e.
+it must be a column label.
+The shapes of the Le diagram of $V$ and $W$ are the same except for the insertion of this column since $I_1^*$ is the same for $V$ and $W$ except for the incrementation of the indices $\geq i$ in the transition from the necklace for $V$ to the necklace for $W$.
 \end{proof}
@@
   \item $p = (i, n-1)$ with no propagators inside it (that is $i+2, \ldots, n-2$ do not support any propagators in $W'$).
-  \item Either the edge $i$ in $W'$ only supports $p$ or the edge $i$ in $W'$ supports exactly one other propagator $q = (j ,i)$ with no other propagators inside $q$.
+  \item Either the edge $i$ in $W'$ only supports $p$ or the edge $i$ in $W'$ supports exactly one other propagator $q = (j, i)$ with no other propagators inside $q$.
   \end{itemize}
@@
 Then
+
   \begin{align*}
@@
 \begin{proof}
+
 The two possible situations are illustrated in Figure~\ref{fig special p}. The arguments proceed in a similar manner to Lemma~\ref{vertex cyclic int lem}.
@@
 
-On the other hand, if $n-2\in I_{n-2}^{V}$ then we must be in the right hand case of Figure~\ref{fig special p} and the algorithm assigns $q$ to vertex $n-2$ in both $V$ and $W$ (since $p$ is always the counterclockwise-most propagator supported on vertex $n-2$).
-If $n-1 \not\in I_{n-2}^{(V)}$, then in $W$ the algorithm assigns $p$ to $n-2$ and then proceeds identically to the remainder $I_{n-2}^{(V)}$; thus $I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-1\}$ in this case.
-
-Finally, if $n-2,n-1 \in I_{n-2}^{(V)}$ then the algorithm in $W$ assigns $q$ to $n-2$ and $p$ to $n-1$ as above, but this is different to what occurs in $I_{n-2}^{(V)}$ so we cannot argue as above.
-We are now at vertex $n$ and only propagators $p$ and $q$ have been assigned; thus we are proceeding as in the construction of $I_n^{(V)}$ but without propagator $q$.
-By Lemma~\ref{vertex cyclic int lem} we know that $q$ was assigned to $n-5$ by $I_n^{(V)}$, and the only way this could occur is if all other propagators in $V$ had already been assigned when we reached vertex $n-5$.
-Therefore $I_{n-2}^{W} = (I_{n}^{V} \setminus \{n-5\}) \cup \{n-1, n-2\}$; this completes all cases for $I_{n-2}^{(W)}$.
-
-The arguments for $I_k^{(W)}$ ($1< k < n-2$) proceed analagously to those of $I_{n-2}^{(W)}$, with one simplification: we cannot have both $n-3$ and $n-2$ in $I_k^{(V)}$ since $q$ is the only propagator that could be assigned to either of them, and it cannot be assigned to both.
-
-This covers all cases and hence completes the proof.
+% sian will fix this missing part shortly
 \end{proof}

### 2019-02-06 General WLD combinatorics.tex
more minor edits to section 3.4 (dimension)

@@
 
-By Algorithm~\ref{alg:GN to Le}, since $i$ never appears in the Grassmann necklace of $W$ we know that the column labelled $i$ contains only $0$ boxes.
-Otherwise the algorithm of \cite{reversingOh} behaves identically on $V$ and $W$ with the plusses for the incremented indices shifted one column to the left, thus skipping over column $i$ in the Le diagram for $W$.
-By Lemma~\ref{no coloops} we know that $i \not\in I_w^W$, and so $i$ must label a horizontal edge on the boundary of the Le diagram of $W$, i.e.
+By Lemma~\ref{no coloops} we know that $i \not\in I_1^W$, and so $i$ must label a horizontal edge on the boundary of the Le diagram of $W$, i.e.
 it must be a column label.
@@
 
-% sian will fix this missing part shortly
+On the other hand, if $n-2\in I_{n-2}^{V}$ then we must be in the right hand case of Figure~\ref{fig special p} and the algorithm assigns $q$ to vertex $n-2$ in both $V$ and $W$ (since $p$ is always the counterclockwise-most propagator supported on vertex $n-2$).
+If $n-1 \not\in I_{n-2}^{(V)}$, then in $W$ the algorithm assigns $p$ to $n-2$ and then proceeds identically to the remainder $I_{n-2}^{(V)}$; thus $I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-1\}$ in this case.
+
+Finally, if $n-2,n-1 \in I_{n-2}^{(V)}$ then the algorithm in $W$ assigns $q$ to $n-2$ and $p$ to $n-1$ as above, but this is different to what occurs in $I_{n-2}^{(V)}$ so we cannot argue as above.
+We are now at vertex $n$ and only propagators $p$ and $q$ have been assigned; thus we are proceeding as in the construction of $I_n^{(V)}$ but without propagator $q$.
+By Lemma~\ref{vertex cyclic int lem} we know that $q$ was assigned to $n-5$ by $I_n^{(V)}$, and the only way this could occur is if all other propagators in $V$ had already been assigned when we reached vertex $n-5$.
+Therefore $I_{n-2}^{W} = (I_{n}^{V} \setminus \{n-5\}) \cup \{n-1, n-2\}$; this completes all cases for $I_{n-2}^{(W)}$.
+
+The arguments for $I_k^{(W)}$ ($1< k < n-2$) proceed analagously to those of $I_{n-2}^{(W)}$, with one simplification: we cannot have both $n-3$ and $n-2$ in $I_k^{(V)}$ since $q$ is the only propagator that could be assigned to either of them, and it cannot be assigned to both.
+
+This covers all cases and hence completes the proof.
 \end{proof}

### 2019-02-06 General WLD combinatorics.tex
take 2 on inside and outside

@@
 
+Note that for any Wilson loop diagram, $W = (\cP, n)$, each propagator $P$ partions $n$ into two sets, $\{V_{in}(p), V_{out}(p)\}$, where $V_{in}(p)$ and $V_{out}(p)$ correspond to the two  cyclic subintervals of $[n]$ that lie on either side of $p$.
+This in turn defines three sets of propagators, $\{\cP_{in}, p, \cP_{out}\}$, where (for $\bullet \in \{in, \; out\}$) \bas \cP_{\bullet} = \{ q \in (\cP \setminus p) | V(q) \cap V_{\bullet}(p)  \neq \emptyset \} \;.\eas If $W$ has no propagators crossing $p$ and no other propagator supported on $V(p)$, then the set $\{\cP_{in}, p, \cP_{out}\}$ partitions $\cP$.
+The set $\cP_{in}$ defines the propagators with end points on one side of $p$, while $\cP_{out}$ defines the propagators with end points on the other side.
+In particular, for (weakly) admissible Wilson loop diagrams, the set $\{\cP_{in}, p, \cP_{out}\}$ is a partition for every propagators $p \in \cP$.
+
+It remains to determine with set of propagators/vertices are refered to as on the inside of $p$ and which are on the outside. To do this, we impose a direction on $p$.
+
  \sanote{can we use the notation directed propagator here? to emphasize the notational change?}
@@
 \begin{dfn}\label{props inside p}
-Let $W = (\cP, n)$ be an admissible Wilson loop diagram, and $\vec{p} = (i,j) \in \cP$ be a directional propagator and $\cev{p} = (j,i)$ be the same propagator with the opposite directionality.
-Call the vertices of $W$ \bas V_{in}(\vec{p}) = \{a \in [n] | i <_i a <_i j\} \cup V(p) \eas the region of $W$ {\bf inside} $\vec{p}$, and \bas V_{out}(\vec{p}) = \{a \in [n] | j <_j a <_j i\} \cup V(p) \;.\eas the region {\bf outside }$\vec{p}$.
-The set of propagators inside (resp.
-outside) $\vec{p}$ are those lying in the region inside (resp.
-outside) are the $q \neq p \in \cP$ such that  $V(q) \subset V_{in}(p)$ (resp.
-$V(q) \subset V_{out}(p)$) .
+Let $W = (\cP, n)$ be an admissible Wilson loop diagram, with $p = (i,j) \in \cP$.
+Write $(p, <_i)$ be the same propagator with a direction induced by the linear ordering $<_i$.
+Then \bas V_{in}(p, <_i) = \{a \in [n] | i+1 <_i a <_i j \}\eas the region of $W$ {\bf inside} $p$, and \bas V_{out}(p, <_i) = \{a \in [n] | j+1 <_j a <_j i \} \;.\eas the region {\bf outside }$p$.
 \end{dfn}
 
-Note that under this definiton, $V_{in}(\vec{p}) = V_{out}(\cev{p})$ and $V_{out}(\vec{p}) = V_{in}(\cev{p})$.
-That is, the regions inside and outside of a propagator switch depending on the direction imposed on the propagators $p$.
+We may associate the propagators on the inside and outside of $p$ accordingly.
+
+Note that under this definiton, $V_{in}(p, <_i) = V_{out}(p, <_j)$. That is, which set of propagators lie inside and outside of $p$ switch depending on the direction imposed $p$.
 
@@
 Let $p = (i,j) \in cP$ be a propagator in $W$.  Define the \textit{length} of $p$ to be 
-\[\ell(p) = min\big\{|V_(in)(\vec{p})|,|V_(in)(\cev{p})|\big\}-2 = min\big\{|[i+1,j]|,|[j+1,i]|\big\}.\]
+\[\ell(p) = min\big\{|V_{in}(p)|,|V_{out}(p)|\big\} = min\big\{|[i+1,j]|,|[j+1,i]|\big\}.\]
 \end{dfn}
-In other words, given that $p$ partitions the vertices of $W$, $\ell(p)$ is the size of the smaller of the two partitions.
+In other words, $\ell(p)$ is the size of the smaller of the two sets $V_{in}(p)$ and $V_{out}(p)$ defined above.
 

### 2019-02-07 General WLD combinatorics.tex
fixed the issue with the def of r_i in the last section, and at the same time fixed the scalar multiple

@@
       \item Let $S_i = \{p \in \cP \ | \ I_{i-1}(p) \neq I_i(p)\}$. (By convention, set $I_{-1} = I_n$.)
-	  \item Write $\Delta_{I_i}$ for the determinant of the $k \times k$ minor of $C(W)$ with columns indexed by $I_i$.
-      \item Let $r_i$ be $\Delta_{I_i}$ with all variables from rows associated to $p\not\in S_i$ set to $1$.
+	  %\item Write $\Delta_{I_i}$ for the determinant of the $k \times k$ minor of $C(W)$ with columns indexed by $I_i$.
+      \item Let $r_i$ be the determinant of the $|S_i|\times |S_i|$ minor of $C(W)$ with rows indexed by $S_i$ and columns indexed by $I_i(S_i)$.
+%$\Delta_{I_i}$ with all variables from rows associated to $p\not\in S_i$ set to $1$.
     \end{itemize}
@@
 
-As we take each $\Delta_{I_i}$ to simply be the determinant of a particular submatrix of $C(W)$, the sign of each $\Delta_{I_i}$ is well-defined.
+As we discuss the algorithm it will also be useful to have the notation $\Delta_{I_i}$ for the determinant of the $k\times k$ minor of $C(W)$ with columned indexed by $I_i$.
+
+As we take each $r_i$ to simply be the determinant of a particular submatrix of $C(W)$, the sign of each $r_i$ is well-defined.
 The goal is to show that $R$ is equal to the denominator of the Wilson loop diagram as defined in Definition~\ref{def R(W)}.
@@
 which is squarefree and contains all factors of $\prod_{i=1}^{n}\Delta_{I_i}$.
-If one were to construct the denominator $R(W)$ associated to this Wilson loop diagram as per Definition~\ref{def R(W)}, we would find that (up to integer multiples) we have $R(W) = R$.
+If one were to construct the denominator $R(W)$ associated to this Wilson loop diagram as per Definition~\ref{def R(W)}, we would find that we have $R(W) = R$.
 \end{eg}
@@
     \item The nonzero entries of $C(W)$ are independent indeterminates and so every $i\times i$ minor of $C(W)$ is either homogeneous of degree $i$ or is $0$.
-Thus each $\Delta_{I_i}$ is homogeneous.
-Furthermore, each row contributes one factor to each term in the expansion of $\Delta_{I_i}$ so the result of setting the variables from a subset of rows to $1$ is still homogeneous.
+Thus each $\Delta_{I_i}$ and each $r_i$ is homogeneous.
+%Furthermore, each row contributes one factor to each term in the expansion of $\Delta_{I_i}$ so the result of setting the variables from a subset of rows to $1$ is still homogeneous.
 Thus each $r_i$ is homogeneous.
@@
 By part (2), either exactly one variable in the row corresponding to $p$ appears in $\Delta_{I_i}$ and this variable is a factor of $\Delta_{I_i}$, or exactly two variables from the row corresponding to $p$ appear in $\Delta_{I_i}$ and they appear as part of a quadratic factor.
-In the first case let the variable be $x$, then $x$ is a factor of both $r_i$ and $\Delta_{I_i}$ and is the only variable from this row in either polynomial.
+In the first case let the variable be $x$.
+Then $x$ is a factor of $\Delta_{I_i}$ and so in particular the monomial in $\Delta_{I_i}$ corresponding to the bijection between propagators and vertices of $I_i$ associates the column of $x$ to $p$.
+Thus $x$ also appears in $r_i$ and since the matrix for $r_i$ is a minor of the matrix for $\Delta_{I_i}$ and every term in $\Delta_{I_i}$ involves $x$, we also have that every term in $r_i$ involves $x$ so $x$ is a factor of both $r_i$ and $\Delta_{I_i}$ and is the only variable from this row in either polynomial.
 
@@
 
-Thus $q\in S_i$ after all, and so again $f$ is a factor of $r_i$ as required.
+Thus $q\in S_i$ after all, and so $f$ is a factor of $r_i$ as required.
 
@@
   Given any admissible Wilson loop diagram $W$, let $\{I_1, \ldots I_n\}$ be the associated Grasmann necklace.
-Then the denominator of the integral, $R(W)$ (see Definition~\ref{def R(W)}), is a $\mathbb{Q}$-multiple of the radical of $\prod_{i=1}^n \Delta_{I_i}$, where $\Delta_{I_i}$ is the determinant of the $k \times k$ minor indicated by $I_i$.
-Equivalently, $R(W)$ is a $\mathbb{Q}$-multiple of the $R$ of Algorithm~\ref{alg WLD to denom via GN}.
+Then the denominator of the integral, $R(W)$ (see Definition~\ref{def R(W)}), the $R$ of Algorithm~\ref{alg WLD to denom via GN}, which is also up to scalar multiple the radical of $\prod_{i=1}^n \Delta_{I_i}$, where $\Delta_{I_i}$ is the determinant of the $k \times k$ minor indicated by $I_i$.
 \end{thm}
 
-\begin{proof}
-The equivalence of the final statement of the theorem is due to Proposition~\ref{prop alg gives rad}.
-It remains to prove that $R(W)$ is an integer multiple of the $R$ of Algorithm~\ref{alg WLD to denom via GN}.
+\note{Note that there is still a mention of scalar multiple in this theorem because it seems to me that the def of radical is only up to scalar multiple, but the part relating $R(W)$ to $R$ is exact with no scalar multiples.}
+
+\begin{proof}
+The equivalence up to scalar multiple of $R$ and the radical of $\prod_{i=1}^n \Delta_{I_i}$ is due to Proposition~\ref{prop alg gives rad}.
+It remains to prove that $R(W)$ is the $R$ of Algorithm~\ref{alg WLD to denom via GN}.
 
@@
 The factors of each $R_e$ making up $R(W)$ in the notation of Definition~\ref{def R(W)} are all of this form and hence every factor of $R$ divides $R(W)$.
-Finally, since $R$ is squarefree, this implies that $R(W)$ is a $\mathbb{Q}$-multiple of $R$.
-\end{proof}
-
-\note{Is there any point in working out the $\mathbb{Q}$-coefficient, or otherwise discussing the field?}
+Finally, since $R$ is squarefree, this implies that $R(W)$ is a scalar multiple of $R$.
+
+Finally then we need to check the scalar.
+By Definition~\ref{def R(W)} each linear factor appears with coefficient $1$ and each $2\times 2$ deteriminant factor appears with the same sign as the determinant of the corresponding minor in $C(W)$.
+Therefore $R=R(W)$.
+\end{proof}
 

### 2019-02-07 General WLD combinatorics.tex
inside/outside definition version 2.1

@@
 
-Note that for any Wilson loop diagram, $W = (\cP, n)$, each propagator $P$ partions $n$ into two sets, $\{V_{in}(p), V_{out}(p)\}$, where $V_{in}(p)$ and $V_{out}(p)$ correspond to the two  cyclic subintervals of $[n]$ that lie on either side of $p$.
-This in turn defines three sets of propagators, $\{\cP_{in}, p, \cP_{out}\}$, where (for $\bullet \in \{in, \; out\}$) \bas \cP_{\bullet} = \{ q \in (\cP \setminus p) | V(q) \cap V_{\bullet}(p)  \neq \emptyset \} \;.\eas If $W$ has no propagators crossing $p$ and no other propagator supported on $V(p)$, then the set $\{\cP_{in}, p, \cP_{out}\}$ partitions $\cP$.
-The set $\cP_{in}$ defines the propagators with end points on one side of $p$, while $\cP_{out}$ defines the propagators with end points on the other side.
-In particular, for (weakly) admissible Wilson loop diagrams, the set $\{\cP_{in}, p, \cP_{out}\}$ is a partition for every propagators $p \in \cP$.
-
-It remains to determine with set of propagators/vertices are refered to as on the inside of $p$ and which are on the outside. To do this, we impose a direction on $p$.
-
- \sanote{can we use the notation directed propagator here? to emphasize the notational change?}
+Note that for any Wilson loop diagram, $W = (\cP, n)$, each propagator $p$ partions $[n]$ into two cyclic subintervals of $[n]$, $\{[i+1, j], [j+1, i]\}$ that lie on either side of $p$.
+In the sequel we refer to these intervals as an interval inside and outside of $p$, depending on a ordering we associate to the propagator.
 
@@
 
-We may associate the propagators on the inside and outside of $p$ accordingly.
-
-Note that under this definiton, $V_{in}(p, <_i) = V_{out}(p, <_j)$. That is, which set of propagators lie inside and outside of $p$ switch depending on the direction imposed $p$.
+Similarly, we may associate the ordering $<_j$ to $p$, in which case $V_{in}(p, <_i) = V_{out}(p, <_j)$ and $V_{out}(p, <_i) = V_{in}(p, <_j)$.
+
+This in turn defines two sets of propagators, $\{\cP_{in}, \cP_{out}\}$, where (for $\bullet \in \{in, \; out\}$) \bas \cP_{\bullet} = \{ q \in (\cP \setminus p) | V(q) \cap V_{\bullet}(p)  \neq \emptyset \} \;.\eas The set $\cP_{in}$ (resp.
+$\cP_{out}$) is the set of propagators, not equal to $p$ \hlfix{whose support contains points in $V_{in}(p, <_*)$ (resp.
+$V_{in}(p, <_*)$), where $<_*$ refers to the appropriate ordering.}{Note, this means that paralell propagators are both on the inside and outside of $p$.
+Is that okay?} If $W$ has no propagators crossing $p$ and no other propagator supported entirely on $V(p)$, then the set $\{\cP_{in}, p, \cP_{out}\}$ partitions $\cP$.
+Under these circumstances, the set $\cP_{in}$ defines the propagators with end points on one side of $p$, while $\cP_{out}$ defines the propagators with end points on the other side.
+In particular, for (weakly) admissible Wilson loop diagrams, the set $\{\cP_{in}, p, \cP_{out}\}$ is a partition for every propagators $p \in \cP$.
+
+As with the vertex sets,  which set of propagators lie inside and outside of $p$ switch depending on the direction imposed $p$.
 

### 2019-02-07 General WLD combinatorics.tex
fixed one tiny typo that none the less affected meaning

@@
   Given any admissible Wilson loop diagram $W$, let $\{I_1, \ldots I_n\}$ be the associated Grasmann necklace.
-Then the denominator of the integral, $R(W)$ (see Definition~\ref{def R(W)}), the $R$ of Algorithm~\ref{alg WLD to denom via GN}, which is also up to scalar multiple the radical of $\prod_{i=1}^n \Delta_{I_i}$, where $\Delta_{I_i}$ is the determinant of the $k \times k$ minor indicated by $I_i$.
+Then the denominator of the integral, $R(W)$ (see Definition~\ref{def R(W)}), is the $R$ of Algorithm~\ref{alg WLD to denom via GN}, which is also, up to scalar multiple, the radical of $\prod_{i=1}^n \Delta_{I_i}$, where $\Delta_{I_i}$ is the determinant of the $k \times k$ minor indicated by $I_i$.
 \end{thm}

### 2019-02-07 General WLD combinatorics.tex
Inside/outside dfn version 2.2

@@
 
-Note that for any Wilson loop diagram, $W = (\cP, n)$, each propagator $p$ partions $[n]$ into two cyclic subintervals of $[n]$, $\{[i+1, j], [j+1, i]\}$ that lie on either side of $p$.
-In the sequel we refer to these intervals as an interval inside and outside of $p$, depending on a ordering we associate to the propagator.
+Note that for any Wilson loop diagram, $W = (\cP, n)$, each propagator $p$ partions $[n]$ into three subsets of $[n]$, $\{[i+2, j-1], V(p), [j+2, i-1]\}$, the support of $p$ and the vertices that lie on either side of $p$.
+In the sequel we refer to the latter two intervals as an interval inside and outside of $p$, depending on a ordering we associate to the propagator.
 

### 2019-02-07 General WLD combinatorics.tex
Inside/outside dfn version 2.2.1

@@
 $\cP_{out}$) is the set of propagators, not equal to $p$ \hlfix{whose support contains points in $V_{in}(p, <_*)$ (resp.
-$V_{in}(p, <_*)$), where $<_*$ refers to the appropriate ordering.}{Note, this means that paralell propagators are both on the inside and outside of $p$.
+$V_{in}(p, <_*)$), where $<_*$ refers to the appropriate ordering.}{Note, this means that paralell propagators are neither on the inside and outside of $p$.
 Is that okay?} If $W$ has no propagators crossing $p$ and no other propagator supported entirely on $V(p)$, then the set $\{\cP_{in}, p, \cP_{out}\}$ partitions $\cP$.

### 2019-02-18 General WLD combinatorics.tex
Inside/outside dfn version 2.2.2
made some changes to section 3.1... especially regards to notation

@@
 In particular, for (weakly) admissible Wilson loop diagrams, the set $\{\cP_{in}, p, \cP_{out}\}$ is a partition for every propagators $p \in \cP$.
+Recall from Definition~\ref{admisdfn} that a {\em weakly admissible} diagram is one that satisfies the density and non-crossing conditions but does not require that $|V(\cP)| \geq |\cP| + 4$.
 
@@
 Let $p = (i,j) \in cP$ be a propagator in $W$.  Define the \textit{length} of $p$ to be 
-\[\ell(p) = min\big\{|V_{in}(p)|,|V_{out}(p)|\big\} = min\big\{|[i+1,j]|,|[j+1,i]|\big\}.\]
+\[\ell(p) = min\big\{|V_{in}(p)|,|V_{out}(p)|\big\} +2 = min\big\{|[i+1,j]|,|[j+1,i]|\big\}.\]
 \end{dfn}
-In other words, $\ell(p)$ is the size of the smaller of the two sets $V_{in}(p)$ and $V_{out}(p)$ defined above.
-
-\begin{rmk}\label{rem:props of length 2 and 3}
-The following observations about propagators of short length in $W$ are easily verified:
+In other words, $\ell(p)$ is the size of the smaller of the number of vertices that lie on either side of the progator $p$.
+
+\begin{rmk}\label{rem:props of length 2 and 3} \sanote{change remark to "Configurations"?}
+The following observations about propagators of short length in an (weakly) admissibly Wilson loop diagram, $W$, are easily verified:
 \begin{enumerate}
@@
 We make use of this result in several induction proofs below.
-Recall from Definition~\ref{admisdfn} that a {\em weakly admissible} diagram is one that satisfies the density and non-crossing conditions but does not require that $|V(\cP)| \geq |\cP| + 4$.
 
@@
   \begin{enumerate}
-    \item $W$ has a propagator of length $\leq 6$ with a propagator of length 2 inside it and nothing else inside it.\label{item big and 2}
+    \item $W$ has a propagator of length $\leq 6$ with a propagator of length 2 inside it and nothing else inside it.\label{item big and 2} \sanote{doesn't this depend on which side you call inside?
+Should we say ``on one side''?}
     \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator ends between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
@@
 
-\begin{proof}
+\begin{proof} \sanote{fixed misuse of the word support in lemma}
 Suppose first that $W$ has a propagator of length $3$, say $p=(i, i+3)$.
@@
 
-Note that if $p$ is a propagator supported on $(i,j)$, then we can consider two obvious restrictions of $W$, namely $W_{[i,j+1]}$ and $W_{[j,i+1]}$.
+Note that if $p = (i, j)$, then we can consider two obvious restrictions of $W$, namely $W_{[i,j+1]}$ and $W_{[j,i+1]}$.
 Clearly all other propagators $q\neq p$ appear in exactly one of these subdiagrams, while $p$ appears in both.
 In this case, we will say that $p$ \textit{bounds the regions} $[i,j+1]$ and $[j,i+1]$; the ordering of the start and end points allow us to identify one or the other region unambiguously.
+\sanote{see e-mail about contracted WLD}
 
@@
 \item $q_r$ bounds a region of $W$ which contains strictly fewer vertices than that bounded by $q_{r-1}$ and the restriction of $W$ to this region does not contain any of the propagators $p_1, \dots, p_r$.
+\sanote{so I understand, $q_r$ on the other side of $q_{r-1}$ than the $\{p_i\}$?}
 \end{itemize}
@@
 
-Start by choosing a propagator $p_1$ of length 2 in $W$ (which exists by Remark~\ref{rem:props of length 2 and 3}), and write $(j_1,j_1+2)$ for its support.
+Start by choosing a propagator $p_1 = (j_1,j_1+2)$ of length 2 in $W$ (which exists by Remark~\ref{rem:props of length 2 and 3}).
 If it is part of one of the configurations we are looking for then we are done,
@@
 This bounds a region $[i_1,k_1]$ (where $k_1 \in \{j_1-1, j_1, j_1+1\}$) which does not contain $p_1$.
+
+INSERT PICTURE HERE?
 

### 2019-02-22 General WLD combinatorics.tex
Few more changes to Lemma 3.7

@@
 Denote this diagram by $W_{[i,j]}$.
-
-Note that if $p = (i, j)$, then we can consider two obvious restrictions of $W$, namely $W_{[i,j+1]}$ and $W_{[j,i+1]}$.
-Clearly all other propagators $q\neq p$ appear in exactly one of these subdiagrams, while $p$ appears in both.
-In this case, we will say that $p$ \textit{bounds the regions} $[i,j+1]$ and $[j,i+1]$; the ordering of the start and end points allow us to identify one or the other region unambiguously.
-\sanote{see e-mail about contracted WLD}
+That is, if $W = (\cP, n)$ is a Wilson loop diagram, \bas W_{[i,j]} = (\cP \setminus \Prop([i,j]^c), n)\eas
+
+{\color{blue} If we denote $Q = \Prop([i,j]^c)$, then we can write \bas M(W_{[i,j]}) = M(W)/F(Q) \oplus M_{\emptyset, n-|i-j+1|} \eas where  $M_{\emptyset, k}$ is the matroid of rank $0$ on a set of $k$.
+That is $M_{\emptyset, n-|i-j+1|} =M((\emptyset, n-|i-j+1|))$.
+} \sanote{If we like this idea, I can incorporate the necessary nomenclature earlier.}
+
+Note that if $p = (i, j)$, then we can consider two obvious restrictions of $W$, namely \bas W_{[i,j+1]} = W_{V_{in}(p, <_i) \cup V(p)} \quad \textrm{and} \quad  W_{[j,i+1]}  = W_{V_{out}(p, <_i) \cup V(p)} \eas corresponding to the regions inside and outside of $(p,<_i)$.
+They contain the propagators on the inside and outside of $(p, <_i)$ respectfully, as well as $p$ itself.
+We say that $p$ \textit{bounds the regions} $[i,j+1]$ and $[j,i+1]$ which we call outside and inside respectively.
+The ordering of the start and end points allow us to identify one or the other region unambiguously.
 
@@
 \item $\ell(q_r) \geq 4$.
-\item $q_r$ bounds a region of $W$ which contains strictly fewer vertices than that bounded by $q_{r-1}$ and the restriction of $W$ to this region does not contain any of the propagators $p_1, \dots, p_r$.
-\sanote{so I understand, $q_r$ on the other side of $q_{r-1}$ than the $\{p_i\}$?}
+\item If we orient the $q_r$ such that the $\{p_1 \ldots p_r\}$ are on the inside.
+The outer region of $W$ that is bounded by $q_r$ is strictly contained in the region of $W$ bounded by $q_{r-1}$ on the outside.
+Thus the restriction of $W$ to this region does not contain any of the propagators $p_1, \dots, p_r$.
+\sanote{changed, have I broken it?}
 \end{itemize}
@@
 By assumption: $p_1$ is not in configuration \ref{item pair of 2s}, there are no propagators of length $3$, and every vertex is supported.
-Therefore there must exist a propagator $q_1$ of length $\geq 4$ with one end on edge $j_1$ or on edge $j_1-1$ or on edge $j_1-2$.
-This bounds a region $[i_1,k_1]$ (where $k_1 \in \{j_1-1, j_1, j_1+1\}$) which does not contain $p_1$.
+Therefore there must exist a propagator $q_1$ outside of $(p_1, <_j)$ of length $\geq 4$ with one end on edge $j_1$ or on edge $j_1-1$ or on edge $j_1-2$.
+This bounds a region $[i_1,k_1]$ on the outside (where $k_1 \in \{j_1-1, j_1, j_1+1\}$) which does not contain $p_1$.
 
@@
 
-Now suppose $q_{r}$ exists by the induction hypothesis and bounds a region $[i_r,k_r]$ not containing any $p_i$ for $i\leq r$.
-Consider the restricted diagram $W_r:=W_{[i_r,k_r]}$; by the original hypotheses on $W$ every vertex $l \in [i_r+2,k_r-2]$ (which is a non-empty interval since $\ell(q_r) \geq 4$) must have support $\geq 1$, while the same is true for $l \in \{i_r,i_r+1,k_r-1,k_r\}$ because these vertices support $q_r$.
+Now suppose $q_{r}$ exists by the induction hypothesis, oriented such that $(q_r, <_{k_r-1})$ and bounds a region $[i_r,k_r]$ on the outside.
+This region not containing any $p_i$ for $i\leq r$.
+\sanote{Know what $p_1$ is.
+What are the others?}  Consider the restricted diagram $W_r:=W_{[i_r,k_r]}$; by the original hypotheses on $W$ every vertex $l \in [i_r+2,k_r-2]$ (which is a non-empty interval since $\ell(q_r) \geq 4$) must have support $\geq 1$, while the same is true for $l \in \{i_r,i_r+1,k_r-1,k_r\}$ because these vertices support $q_r$.
 
@@
 %the configuration \eqref{eq:2 prop config}
-then we are done, so assume otherwise.
+then we are done, so assume otherwise. \sanote{What if $p_{r+1}$ outside of $(q_r, <_{k_r-1})$?}
 
@@
 The overall result then follows by induction.
-
-\note{The picture didn't apply any longer, but perhaps a new one would be nice?}
 \end{proof}

### 2019-02-22 General WLD combinatorics.tex
Few more changes to Lemma 3.7

@@
 
-Now suppose $W$ has no propagators of length $3$.
+Now suppose $W$ has no propagators of length $3$. \sanote{when do we deal with this restriction?}
 %  We will prove the following stronger result: that $D$ admits a pair of propagators of length 2 in the following configuration:
@@
 \item $\ell(q_r) \geq 4$.
-\item If we orient the $q_r$ such that the $\{p_1 \ldots p_r\}$ are on the inside.
-The outer region of $W$ that is bounded by $q_r$ is strictly contained in the region of $W$ bounded by $q_{r-1}$ on the outside.
+\item If we orient the $q_r$ such that the $\{p_1 \ldots p_r\}$ are on the outside.
+The inner region of $W$ that is bounded by $q_r$ is strictly contained in the region of $W$ bounded by $q_{r-1}$ on the inside.
 Thus the restriction of $W$ to this region does not contain any of the propagators $p_1, \dots, p_r$.
@@
 Therefore there must exist a propagator $q_1$ outside of $(p_1, <_j)$ of length $\geq 4$ with one end on edge $j_1$ or on edge $j_1-1$ or on edge $j_1-2$.
-This bounds a region $[i_1,k_1]$ on the outside (where $k_1 \in \{j_1-1, j_1, j_1+1\}$) which does not contain $p_1$.
+This bounds a region $[i_1,k_1] = V_{out}(q_1) \cup V(q_1)$ on the outside of $(q_1, <_{i_1})$ (where $k_1 \in \{j_1-1, j_1, j_1+1\}$) which does not contain $p_1$.
 
@@
 
-Now suppose $q_{r}$ exists by the induction hypothesis, oriented such that $(q_r, <_{k_r-1})$ and bounds a region $[i_r,k_r]$ on the outside.
-This region not containing any $p_i$ for $i\leq r$.
+Now suppose $q_{r}$ exists by the induction hypothesis, oriented such that $(q_r, <_{i_r})$ and bounds a region $[i_r,k_r]$ on the outside.
+This region does not contain any $p_i$ for $i\leq r$.
 \sanote{Know what $p_1$ is.
@@
 $W_r$ has no propagators of length $3$ since $W$ has none.
-Let $p_{r+1}$ be a propagator of length 2 in $W_r$; if it forms part of configuration \ref{item big and 2} or \ref{item pair of 2s}
+Let $p_{r+1}$ be a propagator of length 2 in $W_r$ (i.e.
+outside of $(q_r, <_{k_r-2})$; if it forms part of configuration \ref{item big and 2} or \ref{item pair of 2s}
 %the configuration \eqref{eq:2 prop config}
-then we are done, so assume otherwise. \sanote{What if $p_{r+1}$ outside of $(q_r, <_{k_r-1})$?}
-
-Note we may replace $q_r$ by any other propagator of length $\geq 4$ in $W_r$ which contains $p_{r+1}$; such a new $q_r$ still satisfies all the hypotheses, and so, without loss of generality we may assume that $q_r$ has minimal length among propagators of length $\geq 4$ which contain $p_{r+1}$.
+then we are done, so assume otherwise.
+
+Note we may replace $q_r$ by any other propagator, $q'_{r}$ of length $\geq 4$ in $W_r$ such that $p_{r+1}$ and $q_r$ are on opposite sides; such a new $q'_{r}$ still satisfies all the hypotheses, and so, without loss of generality we may assume that $(q_r, <_{k_r-1})$ has minimal length among propagators of length $\geq 4$ which contain $p_{r+1}$ on the outside.
 

### 2019-02-25 General WLD combinatorics.tex
some comments on the comments in lemma 3.7

@@
 
-\begin{rmk}\label{rem:props of length 2 and 3} \sanote{change remark to "Configurations"?}
-The following observations about propagators of short length in an (weakly) admissibly Wilson loop diagram, $W$, are easily verified:
+\begin{rmk}\label{rem:props of length 2 and 3} 
+The following observations about configurations of propagators of short length in an (weakly) admissibly Wilson loop diagram, $W$, are easily verified:
 \begin{enumerate}
@@
     \item $W$ has a propagator of length $\leq 6$ with a propagator of length 2 inside it and nothing else inside it.\label{item big and 2} \sanote{doesn't this depend on which side you call inside?
-Should we say ``on one side''?}
+Should we say ``on one side''?
+-- the point is that the inside should be the length 6 side.
+Now there could be two length 6 sides in which case, yes there should exist one of the length 6 sides with the desired property.
+I'm not sure how you want to phrase all this}
     \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator ends between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
@@
 
-\begin{proof} \sanote{fixed misuse of the word support in lemma}
+\begin{proof}
 Suppose first that $W$ has a propagator of length $3$, say $p=(i, i+3)$.
@@
 
-Now suppose $W$ has no propagators of length $3$. \sanote{when do we deal with this restriction?}
+Now suppose $W$ has no propagators of length $3$.
 %  We will prove the following stronger result: that $D$ admits a pair of propagators of length 2 in the following configuration:
@@
 \sanote{Know what $p_1$ is.
-What are the others?}  Consider the restricted diagram $W_r:=W_{[i_r,k_r]}$; by the original hypotheses on $W$ every vertex $l \in [i_r+2,k_r-2]$ (which is a non-empty interval since $\ell(q_r) \geq 4$) must have support $\geq 1$, while the same is true for $l \in \{i_r,i_r+1,k_r-1,k_r\}$ because these vertices support $q_r$.
+What are the others?, they are the things we are inductively constructing and so they are about to be defined inductively (see the next paragraph)}  Consider the restricted diagram $W_r:=W_{[i_r,k_r]}$; by the original hypotheses on $W$ every vertex $l \in [i_r+2,k_r-2]$ (which is a non-empty interval since $\ell(q_r) \geq 4$) must have support $\geq 1$, while the same is true for $l \in \{i_r,i_r+1,k_r-1,k_r\}$ because these vertices support $q_r$.
 

### 2019-02-26 General WLD combinatorics.tex
General WLD combinatorics.tex

@@
 
-This in turn defines two sets of propagators, $\{\cP_{in}, \cP_{out}\}$, where (for $\bullet \in \{in, \; out\}$) \bas \cP_{\bullet} = \{ q \in (\cP \setminus p) | V(q) \cap V_{\bullet}(p)  \neq \emptyset \} \;.\eas The set $\cP_{in}$ (resp.
-$\cP_{out}$) is the set of propagators, not equal to $p$ \hlfix{whose support contains points in $V_{in}(p, <_*)$ (resp.
+This in turn defines two sets of propagators, $\{\cP_{in}(p, <_i), \cP_{out}(p, <_i)\}$, where (for $\bullet \in \{in, \; out\}$) \bas \cP_{\bullet} = \{ q \in (\cP \setminus p) | V(q) \cap V_{\bullet}(p)  \neq \emptyset \} \;.\eas When clear, we drop the parentetical and just write $\cP_{in}$ (resp.
+$\cP_{out}$).
+These sets are the sets of propagators, not equal to $p$, \hlfix{whose support contains points in $V_{in}(p, <_*)$ (resp.
 $V_{in}(p, <_*)$), where $<_*$ refers to the appropriate ordering.}{Note, this means that paralell propagators are neither on the inside and outside of $p$.
@@
   \begin{enumerate}
-    \item $W$ has a propagator of length $\leq 6$ with a propagator of length 2 inside it and nothing else inside it.\label{item big and 2} \sanote{doesn't this depend on which side you call inside?
-Should we say ``on one side''?
--- the point is that the inside should be the length 6 side.
-Now there could be two length 6 sides in which case, yes there should exist one of the length 6 sides with the desired property.
-I'm not sure how you want to phrase all this}
+    \item $W$ has a propagator of length $\leq 6$ with a propagator of length 2 on one side it and nothing else on that side.\label{item big and 2} \sanote{tweaked}
     \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator ends between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
@@
 
-We need a bit of notation:
-Define the restriction of $W$ to a region $[i,j]$ to be the subdiagram obtained by forgetting all propagators not wholly supported on vertices in the cyclic interval $[i,j]$; the vertex set remains the same as in $W$.
+We need a bit of notation: Let $W = (\cP, n)$ a weakly admissible Wilson loop diagram, and $Q \subseteq \cP$.
+Define the restriction $W|_Q$ to be the diagram $W$ with the propagators not in $Q$ removed.
+That is , \bas W|_Q = (Q, n).
+\eas  \footnote{If we denote $V \subset [n]$ and $Q = \Prop(V^c)$, then we can write \bas M(W|_{Q^c}) = M(W)/F(Q) \oplus M_{\emptyset, n-|i-j+1|} \eas where  $M_{\emptyset, k}$ is the matroid of rank $0$ on a set of $k$.
+That is $M_{\emptyset, n-|i-j+1|} =M((\emptyset, n-|i-j+1|))$.
+} \sanote{tweaked this para and the next}
+
+%to a region $[i,j]$ to be the subdiagram obtained by forgetting all propagators not wholly supported on vertices in the cyclic interval $[i,j]$; the vertex set remains the same as in $W$.
 Denote this diagram by $W_{[i,j]}$.
@@
 
-{\color{blue} If we denote $Q = \Prop([i,j]^c)$, then we can write \bas M(W_{[i,j]}) = M(W)/F(Q) \oplus M_{\emptyset, n-|i-j+1|} \eas where  $M_{\emptyset, k}$ is the matroid of rank $0$ on a set of $k$.
-That is $M_{\emptyset, n-|i-j+1|} =M((\emptyset, n-|i-j+1|))$.
-} \sanote{If we like this idea, I can incorporate the necessary nomenclature earlier.}
-
-Note that if $p = (i, j)$, then we can consider two obvious restrictions of $W$, namely \bas W_{[i,j+1]} = W_{V_{in}(p, <_i) \cup V(p)} \quad \textrm{and} \quad  W_{[j,i+1]}  = W_{V_{out}(p, <_i) \cup V(p)} \eas corresponding to the regions inside and outside of $(p,<_i)$.
-They contain the propagators on the inside and outside of $(p, <_i)$ respectfully, as well as $p$ itself.
-We say that $p$ \textit{bounds the regions} $[i,j+1]$ and $[j,i+1]$ which we call outside and inside respectively.
+Note that if $p = (i, j)$, then we can consider two obvious restrictions of $W$, namely \bas W|_{\cP_{in} \cup p} \quad \textrm{and} \quad  W|_{\cP_{out}\cup p}, \eas where the set of non-supportive vertices of  $W|_{\cP_{in} \cup p}$ is $V_{out}$ and  the set of non-supportive vertices of  $W|_{\cP_{out} \cup p}$ is $V_{in}$.
+That is, these restrictions contain the propagators on the inside and outside of $(p, <_i)$ respectfully, as well as $p$ itself.
+
+%We say that $p$ \textit{bounds the regions} $[i,j+1]$ and $[j,i+1]$ which we call outside and inside respectively.
 The ordering of the start and end points allow us to identify one or the other region unambiguously.
@@
 \item $\ell(q_r) \geq 4$.
-\item If we orient the $q_r$ such that the $\{p_1 \ldots p_r\}$ are on the outside.
-The inner region of $W$ that is bounded by $q_r$ is strictly contained in the region of $W$ bounded by $q_{r-1}$ on the inside.
-Thus the restriction of $W$ to this region does not contain any of the propagators $p_1, \dots, p_r$.
+\item If we orient the $q_r = (i_1, k_1)$ such that the $\{p_1 \ldots p_r\} \subseteq \cP_{out}(q_r)$ are on the outside.
+Furthermore, we have have $\cP_{in}(q_r) \subsetneq \cP_{in}(q_{r-1})$.
+That is, the propagators on the inside of $q_r$ are strictly contained in the set of propagators inside of $q_{r-1}$.
+In particular, $W_{\cP_{in}(q_r) \cup q_r}$ does not contain any of the propagators $p_1, \dots, p_r$.
 \sanote{changed, have I broken it?}
@@
 By assumption: $p_1$ is not in configuration \ref{item pair of 2s}, there are no propagators of length $3$, and every vertex is supported.
-Therefore there must exist a propagator $q_1$ outside of $(p_1, <_j)$ of length $\geq 4$ with one end on edge $j_1$ or on edge $j_1-1$ or on edge $j_1-2$.
-This bounds a region $[i_1,k_1] = V_{out}(q_1) \cup V(q_1)$ on the outside of $(q_1, <_{i_1})$ (where $k_1 \in \{j_1-1, j_1, j_1+1\}$) which does not contain $p_1$.
+Therefore there must exist a propagator $q_1$ of length $\geq 4$ with one end on edge $j_1$ or on edge $j_1-1$ or on edge $j_1-2$ (that is, $k_1 \in \{j_1-1, j_1, j_1+1\}$).
+Orient $q_1$ such that  $p_1 \in \cP_{out}(q_1)$, (that is $(q_1, <_{i_1})$).
+
+%This bounds a region $[i_1,k_1] = V_{out}(q_1) \cup V(q_1)$ on the outside of $(q_1, <_{i_1})$ (where $k_1 \in \{j_1-1, j_1, j_1+1\}$) which does not contain $p_1$.
 

### 2019-02-26 General WLD combinatorics.tex
A few more paragraphs on Lemma 3.7 changed

@@
 That is , \bas W|_Q = (Q, n).
-\eas  \footnote{If we denote $V \subset [n]$ and $Q = \Prop(V^c)$, then we can write \bas M(W|_{Q^c}) = M(W)/F(Q) \oplus M_{\emptyset, n-|i-j+1|} \eas where  $M_{\emptyset, k}$ is the matroid of rank $0$ on a set of $k$.
-That is $M_{\emptyset, n-|i-j+1|} =M((\emptyset, n-|i-j+1|))$.
-} \sanote{tweaked this para and the next}
+\eas  \sanote{tweaked this para and the next}
 
@@
 That is, these restrictions contain the propagators on the inside and outside of $(p, <_i)$ respectfully, as well as $p$ itself.
+\footnote{If we denote $V \subset [n]$ and $Q = \Prop(V^c)$, then we can write \bas M(W|_{Q^c}) = M(W)/F(Q) \oplus M_{\emptyset, n-|i-j+1|} \eas where  $M_{\emptyset, k}$ is the matroid of rank $0$ on a set of $k$.
+That is $M_{\emptyset, n-|i-j+1|} =M((\emptyset, n-|i-j+1|))$.
+}
 
@@
 In particular, $W_{\cP_{in}(q_r) \cup q_r}$ does not contain any of the propagators $p_1, \dots, p_r$.
-\sanote{changed, have I broken it?}
+\sanote{changed, have I broken it?
+In particular, $k_i +1$ now used to be called $k_i$ before}
 \end{itemize}
@@
 By assumption: $p_1$ is not in configuration \ref{item pair of 2s}, there are no propagators of length $3$, and every vertex is supported.
-Therefore there must exist a propagator $q_1$ of length $\geq 4$ with one end on edge $j_1$ or on edge $j_1-1$ or on edge $j_1-2$ (that is, $k_1 \in \{j_1-1, j_1, j_1+1\}$).
+Therefore there must exist a propagator $q_1$ of length $\geq 4$ with one end on edge $j_1$ or on edge $j_1-1$ or on edge $j_1-2$.
 Orient $q_1$ such that  $p_1 \in \cP_{out}(q_1)$, (that is $(q_1, <_{i_1})$).
@@
 
-Now suppose $q_{r}$ exists by the induction hypothesis, oriented such that $(q_r, <_{i_r})$ and bounds a region $[i_r,k_r]$ on the outside.
-This region does not contain any $p_i$ for $i\leq r$.
-\sanote{Know what $p_1$ is.
-What are the others?, they are the things we are inductively constructing and so they are about to be defined inductively (see the next paragraph)}  Consider the restricted diagram $W_r:=W_{[i_r,k_r]}$; by the original hypotheses on $W$ every vertex $l \in [i_r+2,k_r-2]$ (which is a non-empty interval since $\ell(q_r) \geq 4$) must have support $\geq 1$, while the same is true for $l \in \{i_r,i_r+1,k_r-1,k_r\}$ because these vertices support $q_r$.
+Now suppose $q_{r} = (i_r, k_r) $ exists by the induction hypothesis, oriented $(q_r, <_{i_r})$ as above.
+Call the restriction to the propagators inside $q_r$ in this orientation (including itself) $W_r := W|_{\cP_{in} \cup q_r}$ does not contain any $p_i$ for $i\leq r$.
+By the original hypotheses on $W$ every vertex in $V_{in}(q_r)$ (which is a non-empty interval since $\ell(q_r) \geq 4$) must have support $\geq 1$, while the same is true for $V(q_r)$ because these vertices support $q_r$.
+By construction, the remaining vertices of $W|_{\cP_{in} \cup p}$, i.e.
+$V_{out}(q_r)$ are non-supporting.
 
@@
 $W_r$ has no propagators of length $3$ since $W$ has none.
-Let $p_{r+1}$ be a propagator of length 2 in $W_r$ (i.e.
-outside of $(q_r, <_{k_r-2})$; if it forms part of configuration \ref{item big and 2} or \ref{item pair of 2s}
+Let $p_{r+1}$ be a propagator of length 2 in $W_r$; if it forms part of configuration \ref{item big and 2} or \ref{item pair of 2s}
 %the configuration \eqref{eq:2 prop config}
@@
 
-Note we may replace $q_r$ by any other propagator, $q'_{r}$ of length $\geq 4$ in $W_r$ such that $p_{r+1}$ and $q_r$ are on opposite sides; such a new $q'_{r}$ still satisfies all the hypotheses, and so, without loss of generality we may assume that $(q_r, <_{k_r-1})$ has minimal length among propagators of length $\geq 4$ which contain $p_{r+1}$ on the outside.
+Note we may replace $q_r$ by any other propagator, $q'_{r}$ of length $\geq 4$ in $W_r$ such that $p_{r+1}$ and $q_r$ are on opposite sides; such a new $q'_{r}$ still satisfies all the hypotheses, and so, without loss of generality we may assume that $q_r$ has minimal length among propagators of length $\geq 4$ such that $p_{r+1}\in \cP_{out}(q_r, <_{i_r})$ on the outside.
+
+*******STOPPED HERE (OLD K BELOW)********
 
 There are two cases to consider.
-The first case is that $p_{r+1}$ has one end before $i_r+3$ and the other after $k_r-3$.
+The first case is that $p_{r+1}$ has one end before $i_r+3$ and the other after $k_r-2$.
 Then since $p_{r+1}$ has length 2, it must be that $[i_r+3,k_r-3]$ is at most a single edge, and so $q_r$ has length $\leq 6$.

### 2019-02-26 General WLD combinatorics.tex
working on proof of thm 3.15

@@
 Since $J$ is lexicographically smaller than $I_i$, the $<_i$-smallest element of the symmetric difference of $J$ and $I_i$ is some $j_0\in J$, $j_0 \not\in I_i$.
+Let $p_1$ be the propagator such that $J(p_1)=j_0$.
+Since $j_0\not\in I_i$ but $p_1$ is supported at $j_0$, then $p_1$ must have been assigned to an earlier vertex by $I_i$, i.e.
+we have $I_i(p_1) <_i j_0$.
+Let $j_1 = I_i(p_1)$.
+
+However, $j_0$ is the $<_i$-smallest element in the symmetric difference of $J$ and $I_i$, so in particular there is some propagator $p_2$ such that $J(p_2)=I_i(p_1)$.
+Now, let $j_2 = I_i(p_2)$ and note that $j_2 \neq J(p_2)$ (since $I_i(p_1)=J(p_2)$), so either $I_i(p_2) \not\in J$ or there is a propagator $p_3$ such that $J(p_3) = I_i(p_2)$.
+Continuing likewise we get a list of vertices $j_k$ and propagators $p_k$ such that $J(p_k) = I_i(p_{k-1}) = j_{k-1}$.
+
+We claim that the propagators and vertices in this list are distinct.
+The claim is proved by induction.
+The definition of $j_0$ gives that $j_0$ and $j_1$ are distinct and that $p_1$ and $p_2$ are distinct.
+Now, suppose we have $p_k$ and $j_k$ with $I_i(p_k)=j_k$ and with $j_k\in J$.
+Then $p_{k+1}$ is the propagator associated to $j_k$ by the fixed bijection we have chosed for $J$.
+Since $j_k$ is distinct from the previous $j_j$, $p_{k+1}$ is distinct from the previous $p_j$.
+Then $j_{k+1} = I_i(p_{k+1})$, but $I_i$ is also a bijection, so since $p_{k+1}$ is distinct from the other $p_j$ we have that $j_{k+1}$ is distinct from the other $j_j$ for $1\leq j\leq k$.
+Additionally $j_{k+1}\neq j_0$ since $j_0\not\in I_i$ but $j_{k+1}\in I_i$.
+This proves the claim.
+
+By finiteness the list must end, and the only way it can end is with some $p_k$ such that $j_k = I_i(p_k)\not\in J$, so in particular $j_k >_i j_0$.
+
+Next we will prove that $j_k <_i j_0$ for all $k > 0$.
+This gives a contradiction to the exisitence of $J$ and completes the proof of the theorem.
+This proof will also be by induction.
+We already observed that $j_1 <_i j_0$.
+Suppose we have $j_{j} <_i j_0$ for $j<k$.
+Then $p_{k-1}$ and $p_{k}$ are both supported at $j_{k-1}$, but $I_{i}(p_{k-1}) = j_{k-1}$.
+Thus either $p_{k-1}$ appears before $p_k$ in the neighbourhood of $j_{k-1}$ or $p_k$ was taken earlier by $I_i$ so $I_i(p_k) <_i I_i(p_{k-1})$.
+In the latter case we already have $j_k = I_i(p_k) <_i j_{k-1} <_i j_0$ which is what we want.
+So we now assume that $p_{k-1}$ appears before $p_k$ in the neighbourhood of $j_{k-1}$.
+
+There are two cases to consider.
+First is if $I_i(p_{k-1}) = J(p_{k-1})-1$ and $p_{k-1}$ has an end on the edge $(I_i(p_{k-1}), J(p_{k-1}))$.
+In this case consider the neighbourhood of $I_i(p_{k-2}) = J(p_{k-1})$.
+As the $p_j$ are disjoint we know that at this vertex either $p_{k}$ was taken before $p_{k-2}$ (and so $I_i(p_k) <_i I_i(p_{k-2})$ and we are again done), or $p_k$ comes after $p_{k-2}$ around this vertex.
+
+***Karen is here in this file (and her commute ended for the day)***
+
+Since $J$ is lexicographically smaller than $I_i$, the $<_i$-smallest element of the symmetric difference of $J$ and $I_i$ is some $j_0\in J$, $j_0 \not\in I_i$.
 Let $p$ be the propagator such that $J(p)=j_0$.

### 2019-02-26 General WLD combinatorics.tex
finish propagator pov for Lem 3.7

@@
 Let $W = (\cP, n)$ be an admissible Wilson loop diagram, with $p = (i,j) \in \cP$.
-Write $(p, <_i)$ be the same propagator with a direction induced by the linear ordering $<_i$.
-Then \bas V_{in}(p, <_i) = \{a \in [n] | i+1 <_i a <_i j \}\eas the region of $W$ {\bf inside} $p$, and \bas V_{out}(p, <_i) = \{a \in [n] | j+1 <_j a <_j i \} \;.\eas the region {\bf outside }$p$.
+Write $(p, <_a)$ be the same propagator with a direction induced by the linear ordering $<_a$.
+Then \bas V_{in}(p, <_a) = \{b \in [n] | i+1 <_a b <_a j \}\eas the region of $W$ {\bf inside} $p$, and \bas V_{out}(p, <_a) = \{b \in [n] | j+1 <_a b <_a i \} \;.\eas the region {\bf outside }$p$.
 \end{dfn}
 
-Similarly, we may associate the ordering $<_j$ to $p$, in which case $V_{in}(p, <_i) = V_{out}(p, <_j)$ and $V_{out}(p, <_i) = V_{in}(p, <_j)$.
+Depending on the ordering associated to $p$, the vertices on the inside and outside chagne. In particular, for $p = (i,j)$, $V_{in}(p, <_i) = V_{out}(p, <_j)$ and $V_{out}(p, <_i) = V_{in}(p, <_j)$.
 
@@
 Now suppose $q_{r} = (i_r, k_r) $ exists by the induction hypothesis, oriented $(q_r, <_{i_r})$ as above.
+For the rest of this proof, we assume this orientation as read, and drop the $<_{i_r}$ from the notation.
 Call the restriction to the propagators inside $q_r$ in this orientation (including itself) $W_r := W|_{\cP_{in} \cup q_r}$ does not contain any $p_i$ for $i\leq r$.
@@
 
-Note we may replace $q_r$ by any other propagator, $q'_{r}$ of length $\geq 4$ in $W_r$ such that $p_{r+1}$ and $q_r$ are on opposite sides; such a new $q'_{r}$ still satisfies all the hypotheses, and so, without loss of generality we may assume that $q_r$ has minimal length among propagators of length $\geq 4$ such that $p_{r+1}\in \cP_{out}(q_r, <_{i_r})$ on the outside.
-
-*******STOPPED HERE (OLD K BELOW)********
+Note we may replace $q_r$ by any other propagator, $q'_{r}$ of length $\geq 4$ in $W_r$ such that $p_{r+1}$ and $q_r$ are on opposite sides; such a new $q'_{r}$ still satisfies all the hypotheses, and so, without loss of generality we may assume that $q_r$ has minimal length among propagators of length $\geq 4$ such that $p_{r+1}\in \cP_{out}(q_r)$ is on the outside.
 
 There are two cases to consider.
-The first case is that $p_{r+1}$ has one end before $i_r+3$ and the other after $k_r-2$.
-Then since $p_{r+1}$ has length 2, it must be that $[i_r+3,k_r-3]$ is at most a single edge, and so $q_r$ has length $\leq 6$.
-The only propagators inside $q_r$ that do not also contain $p_{r+1}$ must have both ends in $[i_r, i_r+3]$ or both ends in $[k_r-3, k_r]$ and hence be of length 2.
-Therefore, if $q_r$ contains a propagator $t$ of length $\leq 4$, this propagator must also contain $p_{r+1}$ which is impossible my minimality.
-Therefore, if $q_r$ contains another propagator of length $2$ we would have configuration \ref{item pair of 2s} which we have already assumed does not occur.
-Consequently, $q_r$ contains only $p_{r+1}$ and so we have \ref{item big and 2} which again we have assumed does not occur.
+In the first case define $p_{r+1} = (j_{r+1}, j_{r+1}+2)$  with $i_r \leq j_{r+1} \leq i_r+2$ and $k_r-2 \leq j_{r+1} \leq k_{r}$.
+Then since $p_{r+1}$ has length 2, it must be that $(i_r+3)+1 \geq k_r-2$ and so $q_r$ has length $\leq 6$.
+Let $s$ be a propagators in $\cP_{in}(q_r)$ such that $p_{r+1}$ is not an interior propagator in the $<_{i_r}$ ordering: $p_{r+1} \not \in \cP_{in}(s, <{i_r})$.
+If it exists, $s = (i_s, j_s)$ must satisfy $i_r \leq i_s \leq j_s \leq i_r+2$ or $k_r-2 \leq i_s \leq j_s \leq k_r$ and hence be of length 2.
+Therefore, if $\cP_{in}(q_r)$ contains a propagator $t$ of length $\leq 4$, $p_{r+1}$ must lie on its inside in the $<i_r$ ordering ( $p_{r+1} \in \cP_{in}(q_r, <_{i_r})$) which is impossible my minimality.
+Therefore, if $\cP_{in}(q_r)$ contains another propagator of length $2$ we would have configuration \ref{item pair of 2s} which we have already assumed does not occur.
+Consequently, $\cP_{in}(q_r)$ contains only $p_{r+1}$ and so we have \ref{item big and 2} which again we have assumed does not occur.
 Therefore the first case cannot occur.
 
-The second case is that either at least one endpoint of $p_{r+1}$ lies on an edge contained in the interval $[i_r+3,k_r-3]$, or both ends lie in $[i_r, i_r+3]$ or $[k_r-3, k_r]$; these situations all behave similarly.
-Up to symmetry we can write $p_{r+1} = (j_{r+1}, j_{r+1}+2)$ where either the edge $j_{r+1}+2$ is contained in $[i_r+3, k_r-3]$ or $j_{r+1}+2 = i_r+2$.
-Since $p_{r+1}$ is not part of configuration \ref{item pair of 2s} and vertex $j_{r+1}+4$ is supported (and not by $q_r$ since $j_{r+1}+4 \leq k_r-2$ in both situations), there is some propagator $t$ with one end in $[j_{r+1}+3, j_{r+1}+5]$ and length $\geq 4$.
-By noncrossingness $t$ is contained in $q_{r}$.
-$t$ does not contain $p_{r+1}$ by minimality and so we may set $q_{r+1} = t$ to continue the induction.
+In the second case, write $p_{r+1} = (j_{r+1}, j_{r+1}+2)$.
+Either at least $i_r+3 \leq j_{r+1} +2 \leq k_r-3$, or $i_r = j_{r+1}$ or $k_r-2 = j_{r+1}$; these situations all behave similarly.
+By symmetry we consider only the first two cases.
+Not that since $j_{r+1}+4 \leq k_r-1$ in both cases, $j_{r+1}+4 \in V_{in}(q_r)$, and is thus supported.
+Since $p_{r+1}$ is not part of configuration \ref{item pair of 2s}, there is some propagator $t \in \Prop(j_{r+1}+4)$ with \hlfix{length $\geq 4$.
+By noncrossingness $t$ is inside $q_r$, $t \in \cP_{in}(q_r)$, and $p_{r+1}$ is outside $t$, $p_{r+1} \not \in \cP_{in}(t, <_{i,r})$ by minimality.
+So we may set $q_{r+1} = t$ to continue the induction.
+}{Hope I haven't broken things, but I don't follow why $\ell(t)\geq 4$ or $p_{r+1} \not \in \cP_{in}(t, <_{i,r})$}
 

### 2019-02-27 General WLD combinatorics.tex
hopefully correct end of thm 3.15, sorry for the messy illustrations

@@
 This gives a contradiction to the exisitence of $J$ and completes the proof of the theorem.
-This proof will also be by induction.
-We already observed that $j_1 <_i j_0$.
-Suppose we have $j_{j} <_i j_0$ for $j<k$.
-Then $p_{k-1}$ and $p_{k}$ are both supported at $j_{k-1}$, but $I_{i}(p_{k-1}) = j_{k-1}$.
+This proof will also be by induction, however, for the induction to go through nicely we will need to prove the following slightly stronger statement:
+for all $k>0$ in the list
+\begin{itemize}
+\item $j_k <_i j_0$ and
+\item either
+  \begin{itemize}
+  \item $I_i(p_k) <_i J(p_k)$, or
+  \item there exists an $ell<k$ such that $I_i(p_\ell) <_i J(p_\ell)$, those two vertices are supported by distinct ends of $p_\ell$ and $p_k$ is on the side of $p_l$ which runs from $I_i(p_\ell)$ to $J(p_\ell)$.
+  \end{itemize}
+\end{itemize}
+
+We already observed that $j_1 <_i j_0$ and $I_i(p_1) <_k J(p_1)$ so we have the base case for the induction.
+Suppose we have the inductive hypothesis for all indices less than $k>1$ and that $p_k$ exists.
+
+By definition $J(p_k) = I_i(p_{k-1}) = j_{k-1}$, so $p_{k-1}$ and $p_{k}$ are both supported at $j_{k-1}$, but $I_{i}(p_{k-1}) = j_{k-1}$.
 Thus either $p_{k-1}$ appears before $p_k$ in the neighbourhood of $j_{k-1}$ or $p_k$ was taken earlier by $I_i$ so $I_i(p_k) <_i I_i(p_{k-1})$.
-In the latter case we already have $j_k = I_i(p_k) <_i j_{k-1} <_i j_0$ which is what we want.
+In the latter case we are done as $j_k = I_i(p_k) <_i j_{k-1} <_i j_0$ which is what we want.
 So we now assume that $p_{k-1}$ appears before $p_k$ in the neighbourhood of $j_{k-1}$.
 
-There are two cases to consider.
-First is if $I_i(p_{k-1}) = J(p_{k-1})-1$ and $p_{k-1}$ has an end on the edge $(I_i(p_{k-1}), J(p_{k-1}))$.
-In this case consider the neighbourhood of $I_i(p_{k-2}) = J(p_{k-1})$.
-As the $p_j$ are disjoint we know that at this vertex either $p_{k}$ was taken before $p_{k-2}$ (and so $I_i(p_k) <_i I_i(p_{k-2})$ and we are again done), or $p_k$ comes after $p_{k-2}$ around this vertex.
-
-***Karen is here in this file (and her commute ended for the day)***
-
-Since $J$ is lexicographically smaller than $I_i$, the $<_i$-smallest element of the symmetric difference of $J$ and $I_i$ is some $j_0\in J$, $j_0 \not\in I_i$.
+If $I_i(p_{k-1}) <_i J(p_{k-1})$ and these are vertices supported by distinct ends of $p_{k-1}$ then $p_{k}$ coming after $p_{k-1}$ around $j_{k-1}$ implies that $p_k$ is on the $I_i(p_{k-1})$ to $J(p_{k-1})$ side of $p_{k-1}$.
+Therefore $j_k = I_i(p_k) \leq_i J(P_{k-1}) + 1$.
+If $k-1 \neq 1$ then this gives $j_k \leq_i I_i(p_{k-2}) + 1 <_i j_0$ so $j_k \leq_i j_0$, but $j_0\not\in I_i$ so $j_k<_i j_0$.
+If $k-1= 1$ then either $j_k <_i j_0$ or we have the configuration
+\[
+\includegraphics{impossible_config}
+\]
+which is impossible as $p_2$ is supported at $j_0$ but not taken in $I_i$ until after $j_0$ even though $j_0\not\in I_i$.
+Taking all of this paragraph together we are done unless $I_i(p_{k-1})\not<_i J(p_{k-1})$ so now assume this.
+
+By the induction hypothesis,  $I_i(p_{k-1})\not<_i J(p_{k-1})$ implies that there exists and $\ell < k-1$ such that $p_{k-1}$ is on the side of $p_{\ell}$ that goes from $I_i(p_\ell)$ to $J(p_\ell)$.
+If $j_{k-1}$ is not in the support of the $J(p_\ell)$ end of $p_\ell$ then $p_{k-1}$ before $p_{k}$ around $j_{k-1}$ implies that $p_k$ is on the same side of $p_\ell$ as $p_{k-1}$ is.
+Then the same arguments as above with $\ell$ in place of $k-1$ give $j_k \leq_i J(P_\ell)+1$ implying $j_k <_i j_0$ which is everything we need.
+
+It remains to consider when $j_{k-1}$ is in the support of the $J(p_\ell)$ end of $p_\ell$, call this case $(*)$.
+Since $J(p_\ell) = j_{\ell-1}$ and the $j_i$ are distinct this means that we have one of the following two configurations
+\[
+\includegraphics{induction_conf}
+\]
+If $p_\ell=p_1$ then $j_{\ell-1}=j_0$ and then as $j_0\not\in I_i$ but $p_k$ is supported at $j_0$ we get $I_i(p_k) <_i j_0$ and also $I_i(p_k) <_i j_{k-1} = J(p_k)$ as the only vertices not yet taken for $I_i(p_k)$ must be before both labelled vertices in the illustration.
+
+If $p_\ell \neq p_1$ then we argue as above with $\ell-1$ in place of $k-1$: in particular $J(p_\ell) = I_i(p_{\ell-1})$ but $p_k$ is supported at $p_{\ell-1}$, so either $I_i(p_k) <_i I_i(p_{\ell-1})$ in which case as before we get desired conclusion, or $p_k$ comes before $p_{\ell-1}$ at $j_{\ell-1}$.
+Then again argue as before getting a new $p_{\ell'}$ in place of $p_{\ell}$, except that then case $(*)$ must occur simultaneously for both $p_{\ell'}$ and $p_{\ell}$ with respect to $p_{k}$.
+This can only occur if $j_{\ell-1}, j_{k-1}, j_{\ell'-1}$ are consecutive.
+Iterating the argument one more time we finally cannot have case $(*)$ as then all neighbouring vertices of $j_{k-1}$ are used up.
+
+This completes the induction and thence the proof of the theorem.
+
+%Since $J$ is lexicographically smaller than $I_i$, the $<_i$-smallest element of the symmetric difference of $J$ and $I_i$ is some $j_0\in J$, $j_0 \not\in I_i$.
 Let $p$ be the propagator such that $J(p)=j_0$.
@@
 Thus the propagator $p$ has the following property, which we call property $A$:
-\begin{equation}\label{propertyA}\tag{A}I_i(p) <_i J(p) \text{ \ and \ }I_i\cap [i,I_i(p)] = J\cap [i,I_i(p)]. \end{equation}
-
-{}From the previous paragraph we conclude that if we ever had a $J$ which is lexicographically less than $I_i$ and yet a basis of $M(W)$, then there exists a propagator $p$ which has property $A$.
-
-Finally, we will prove that whenever there is a propagator $p$ which has property $A$ then there is another propagator $r$ which also has property $A$ and for which $I_i(r) <_i I_i(p)$.
+%\begin{equation}\label{propertyA}\tag{A}I_i(p) <_i J(p) \text{ \ and \ }I_i\cap [i,I_i(p)] = J\cap [i,I_i(p)]. \end{equation}
+%
+%{}From the previous paragraph we conclude that if we ever had a $J$ which is lexicographically less than $I_i$ and yet a basis of $M(W)$, then there exists a propagator $p$ which has property $A$.
+%
+%Finally, we will prove that whenever there is a propagator $p$ which has property $A$ then there is another propagator $r$ which also has property $A$ and for which $I_i(r) <_i I_i(p)$.
 This would lead to an infinte regress, contradicting the finiteness of $I_i$; thus there could be no such $J$, which will complete the proof of the proposition.
-
-So suppose $p$ has property $A$.
+%
+%So suppose $p$ has property $A$.
 The same vertices in $[i,I_i(p)]$ are in the image of the assignment from $J$ and the image of the assignment from $I_i$ so the same number of propagators are assigned to vertices in this interval by each assignment.
@@
 It follows that $r$ also has property $A$ and that
-\[I_i(r) \leq_i J(q) \leq_i I_i(p)\]
-\hlfix{as required.}{We need $I_i(r) <_i I_i(p)$ but I'm having trouble seeing it?}
+%\[I_i(r) \leq_i J(q) \leq_i I_i(p)\]
+%\hlfix{as required.}{We need $I_i(r) <_i I_i(p)$ but I'm having trouble seeing it?}
 \end{proof}

### 2019-03-01 General WLD combinatorics.tex
tried to satisfy Susama's concerns in lem 3.7

@@
   \begin{enumerate}
-    \item $W$ has a propagator of length $\leq 6$ with a propagator of length 2 on one side it and nothing else on that side.\label{item big and 2} \sanote{tweaked}
+    \item $W$ has a propagator of length $\leq 6$ with a propagator of length 2 on one side it and nothing else on that side.\label{item big and 2}
     \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator ends between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
@@
 That is , \bas W|_Q = (Q, n).
-\eas  \sanote{tweaked this para and the next}
+\eas
 
@@
 Note that if $p = (i, j)$, then we can consider two obvious restrictions of $W$, namely \bas W|_{\cP_{in} \cup p} \quad \textrm{and} \quad  W|_{\cP_{out}\cup p}, \eas where the set of non-supportive vertices of  $W|_{\cP_{in} \cup p}$ is $V_{out}$ and  the set of non-supportive vertices of  $W|_{\cP_{out} \cup p}$ is $V_{in}$.
-That is, these restrictions contain the propagators on the inside and outside of $(p, <_i)$ respectfully, as well as $p$ itself.
+That is, these restrictions contain the propagators on the inside and outside of $(p, <_i)$ respectively, as well as $p$ itself.
 \footnote{If we denote $V \subset [n]$ and $Q = \Prop(V^c)$, then we can write \bas M(W|_{Q^c}) = M(W)/F(Q) \oplus M_{\emptyset, n-|i-j+1|} \eas where  $M_{\emptyset, k}$ is the matroid of rank $0$ on a set of $k$.
@@
 \item $\ell(q_r) \geq 4$.
-\item If we orient the $q_r = (i_1, k_1)$ such that the $\{p_1 \ldots p_r\} \subseteq \cP_{out}(q_r)$ are on the outside.
-Furthermore, we have have $\cP_{in}(q_r) \subsetneq \cP_{in}(q_{r-1})$.
-That is, the propagators on the inside of $q_r$ are strictly contained in the set of propagators inside of $q_{r-1}$.
-In particular, $W_{\cP_{in}(q_r) \cup q_r}$ does not contain any of the propagators $p_1, \dots, p_r$.
-\sanote{changed, have I broken it?
-In particular, $k_i +1$ now used to be called $k_i$ before}
+\item $\{p_1, \ldots, p_r\}$ and $\{q_1, \ldots, q_{r-1}\}$ are all on the same side of $q_r$.  
 \end{itemize}
-Since $W$ contains finitely many vertices, this must eventually terminate in one of the desired configurations. %a configuration of the form \eqref{eq:2 prop config}.
+Note that we will be interested in the orientation of $q_r$ so that the previous $p_i$ and $q_i$ are on the outside of $q_r$.
+By the finiteness of $W$ this must eventually terminate in one of the desired configurations. %a configuration of the form \eqref{eq:2 prop config}.
 
@@
 Therefore there must exist a propagator $q_1$ of length $\geq 4$ with one end on edge $j_1$ or on edge $j_1-1$ or on edge $j_1-2$.
-Orient $q_1$ such that  $p_1 \in \cP_{out}(q_1)$, (that is $(q_1, <_{i_1})$).
+Orient $q_1 = (i_1, k_1)$ such that  $p_1 \in \cP_{out}(q_1)$, (that is $(q_1, <_{i_1})$).
 
@@
 
-Now suppose $q_{r} = (i_r, k_r) $ exists by the induction hypothesis, oriented $(q_r, <_{i_r})$ as above.
-For the rest of this proof, we assume this orientation as read, and drop the $<_{i_r}$ from the notation.
-Call the restriction to the propagators inside $q_r$ in this orientation (including itself) $W_r := W|_{\cP_{in} \cup q_r}$ does not contain any $p_i$ for $i\leq r$.
+Now suppose $q_{r} = (i_r, k_r)$ exists by the induction hypothesis and is oriented $(q_r, <_{i_r})$ so that the previous $p_i$ and $q_i$ are on the outside.
+For the rest of this proof, we assume this orientation and drop the $<_{i_r}$ from the notation.
+
+Call let $W_r := W|_{\cP_{in} \cup q_r}$.
 By the original hypotheses on $W$ every vertex in $V_{in}(q_r)$ (which is a non-empty interval since $\ell(q_r) \geq 4$) must have support $\geq 1$, while the same is true for $V(q_r)$ because these vertices support $q_r$.
@@
 
-Note we may replace $q_r$ by any other propagator, $q'_{r}$ of length $\geq 4$ in $W_r$ such that $p_{r+1}$ and $q_r$ are on opposite sides; such a new $q'_{r}$ still satisfies all the hypotheses, and so, without loss of generality we may assume that $q_r$ has minimal length among propagators of length $\geq 4$ such that $p_{r+1}\in \cP_{out}(q_r)$ is on the outside.
-
+Note we may replace $q_r$ by any other propagator, $q'_{r}$ of length $\geq 4$ in $W_r$ such that $p_{r+1}$ and $q_r$ are on opposite sides; such a new $q'_{r}$ still satisfies all the hypotheses, and so, without loss of generality we may assume that $q_r$ has minimal length among propagators of length $\geq 4$ which have $p_{r+1}$ on their inside.
+
+Write $p_{r+1} = (j_{r+1}, j_{r+1}+2)$.
 There are two cases to consider.
-In the first case define $p_{r+1} = (j_{r+1}, j_{r+1}+2)$  with $i_r \leq j_{r+1} \leq i_r+2$ and $k_r-2 \leq j_{r+1} \leq k_{r}$.
+The first case is that $i_r \leq j_{r+1} \leq i_r+2$ and $k_r-2 \leq j_{r+1}+2 \leq k_{r}$ (so $p_{r+1}$ has one end before $i_{r} + 3$ and the
+other after $k_{r} - 2$).
 Then since $p_{r+1}$ has length 2, it must be that $(i_r+3)+1 \geq k_r-2$ and so $q_r$ has length $\leq 6$.
-Let $s$ be a propagators in $\cP_{in}(q_r)$ such that $p_{r+1}$ is not an interior propagator in the $<_{i_r}$ ordering: $p_{r+1} \not \in \cP_{in}(s, <{i_r})$.
-If it exists, $s = (i_s, j_s)$ must satisfy $i_r \leq i_s \leq j_s \leq i_r+2$ or $k_r-2 \leq i_s \leq j_s \leq k_r$ and hence be of length 2.
-Therefore, if $\cP_{in}(q_r)$ contains a propagator $t$ of length $\leq 4$, $p_{r+1}$ must lie on its inside in the $<i_r$ ordering ( $p_{r+1} \in \cP_{in}(q_r, <_{i_r})$) which is impossible my minimality.
-Therefore, if $\cP_{in}(q_r)$ contains another propagator of length $2$ we would have configuration \ref{item pair of 2s} which we have already assumed does not occur.
+By the minimality assumption on $q_r$ no propagator in $W_r$ has $q_r$ on one sid eand $p_{r+1}$ on the other side, so there is any propagator in $W_r$ other than $p_{r+1}$ itself must be of the form $(i,j)$ with $i_r\leq i, j\leq i_r+2$ or $k_r-1 \leq i,j\leq k_r$ and hence be of length 2, and so we have configuration \ref{item pair of 2s} which we have already assumed does not occur.
 Consequently, $\cP_{in}(q_r)$ contains only $p_{r+1}$ and so we have \ref{item big and 2} which again we have assumed does not occur.
@@
 
-In the second case, write $p_{r+1} = (j_{r+1}, j_{r+1}+2)$.
-Either at least $i_r+3 \leq j_{r+1} +2 \leq k_r-3$, or $i_r = j_{r+1}$ or $k_r-2 = j_{r+1}$; these situations all behave similarly.
-By symmetry we consider only the first two cases.
-Not that since $j_{r+1}+4 \leq k_r-1$ in both cases, $j_{r+1}+4 \in V_{in}(q_r)$, and is thus supported.
-Since $p_{r+1}$ is not part of configuration \ref{item pair of 2s}, there is some propagator $t \in \Prop(j_{r+1}+4)$ with \hlfix{length $\geq 4$.
-By noncrossingness $t$ is inside $q_r$, $t \in \cP_{in}(q_r)$, and $p_{r+1}$ is outside $t$, $p_{r+1} \not \in \cP_{in}(t, <_{i,r})$ by minimality.
-So we may set $q_{r+1} = t$ to continue the induction.
-}{Hope I haven't broken things, but I don't follow why $\ell(t)\geq 4$ or $p_{r+1} \not \in \cP_{in}(t, <_{i,r})$}
+The second case is that one of the following three things happen
+\begin{itemize}
+\item $i_r+3 \leq j_{r+1}\leq k_r-3$ or $i_r+3 \leq j_{r+1}+2\leq k_r-3$,
+\item $i_r = j_{r+1}$, or 
+\item $k_r-2 = j_{r+1}$
+\end{itemize}
+(Phrased more causually, this is that $p_{r+1}$ has either at least one end on an edge in the interval $[i_r+3, k_r-2]$ or both ends lie in $[i_r, i_r+3]$ or both ends lie in $[k_r-2, k_r+1]$.)
+These situations all behave similarly.
+By symmetry it suffices to only consider the second situation and the second possiblity of the first situation.
+Note that since $j_{r+1}+4 \leq k_r-1$ in both situations, and $j_{r+1}+4 \in V_{in}(q_r)$, thus $j_{r+1}+4$ is supported by a propagator in $W_r$ other than $q_r$.
+Let $t$ be this propagator.
+Since $p_{r+1}$ is not part of configuration \ref{item pair of 2s} and $W_r$ has no propagators of length 3, we must have that the length of $t$ is $\geq 4$.
+If $q_r$ and $p_{r+1}$ were on different sides of $t$ then this would contradict the minimal length hypothesis on $q_r$.
+Therefore $t$ has all the previous $q_i$ and $p_i$ on the same side and length $\geq 4$ and so we may set $q_{r+1} = t$ to continue the induction.
 

### 2019-03-05 General WLD combinatorics.tex
mostly grammatical changes to 3.7

@@
 
-Note that if $p = (i, j)$, then we can consider two obvious restrictions of $W$, namely \bas W|_{\cP_{in} \cup p} \quad \textrm{and} \quad  W|_{\cP_{out}\cup p}, \eas where the set of non-supportive vertices of  $W|_{\cP_{in} \cup p}$ is $V_{out}$ and  the set of non-supportive vertices of  $W|_{\cP_{out} \cup p}$ is $V_{in}$.
+Given a propagator $p = (i, j)$ oriented $(p, <_i)$,  we can consider two obvious restrictions of $W$, namely \bas W|_{\cP_{in} \cup p} \quad \textrm{and} \quad  W|_{\cP_{out}\cup p}, \eas where the set of non-supportive vertices of  $W|_{\cP_{in} \cup p}$ is $V_{out}$ and  the set of non-supportive vertices of  $W|_{\cP_{out} \cup p}$ is $V_{in}$.
 That is, these restrictions contain the propagators on the inside and outside of $(p, <_i)$ respectively, as well as $p$ itself.
@@
 so suppose otherwise. 
-By assumption: $p_1$ is not in configuration \ref{item pair of 2s}, there are no propagators of length $3$, and every vertex is supported.
+By assumption: $p_1$ is not in configuration \ref{item pair of 2s}, there are no propagators of length $3$, and every vertex supports at least one propagator.
 Therefore there must exist a propagator $q_1$ of length $\geq 4$ with one end on edge $j_1$ or on edge $j_1-1$ or on edge $j_1-2$.
@@
 Call let $W_r := W|_{\cP_{in} \cup q_r}$.
-By the original hypotheses on $W$ every vertex in $V_{in}(q_r)$ (which is a non-empty interval since $\ell(q_r) \geq 4$) must have support $\geq 1$, while the same is true for $V(q_r)$ because these vertices support $q_r$.
-By construction, the remaining vertices of $W|_{\cP_{in} \cup p}$, i.e.
-$V_{out}(q_r)$ are non-supporting.
+By the original hypotheses on $W$ every vertex in $v \in V_{in}(q_r)$ (which is a non-empty interval since $\ell(q_r) \geq 4$) must have support at least one propagator ($|\Prop(v)| \geq 1$), while the same is true for $V(q_r)$ because these vertices support $q_r$.
+By construction, the remaining vertices of $W|_{\cP_{in} \cup {q_r}}$, i.e.
+$V_{out}(q_r)$, are non-supporting.
 
@@
 Then since $p_{r+1}$ has length 2, it must be that $(i_r+3)+1 \geq k_r-2$ and so $q_r$ has length $\leq 6$.
-By the minimality assumption on $q_r$ no propagator in $W_r$ has $q_r$ on one sid eand $p_{r+1}$ on the other side, so there is any propagator in $W_r$ other than $p_{r+1}$ itself must be of the form $(i,j)$ with $i_r\leq i, j\leq i_r+2$ or $k_r-1 \leq i,j\leq k_r$ and hence be of length 2, and so we have configuration \ref{item pair of 2s} which we have already assumed does not occur.
-Consequently, $\cP_{in}(q_r)$ contains only $p_{r+1}$ and so we have \ref{item big and 2} which again we have assumed does not occur.
-Therefore the first case cannot occur.
-
-The second case is that one of the following three things happen
+By the minimality assumption on $q_r$ no propagator in $W_r$ has $q_r$ on one side and $p_{r+1}$ on the other side.
+Therefore, any propagator in $W_r$ other than $p_{r+1}$ itself must be of the form $(i,j)$ with $i_r\leq i, j\leq i_r+2$ or $k_r-2 \leq i,j\leq k_r$.
+That is, this propagator must be of length 2, and so we have configuration \ref{item pair of 2s} which we have already assumed does not occur.
+Consequently, $\cP_{in}(q_r)$ contains only $p_{r+1}$ and so we have congifuratin  \ref{item big and 2} from the lemma statement which again we have assumed does not occur.
+Therefore this first case cannot occur.
+
+The second case is that one of the following three things happen (we continue to write $p_{r+1} = (j_{r+1}, j_{r+1}+2)$) 
 \begin{itemize}
@@
 \end{itemize}
-(Phrased more causually, this is that $p_{r+1}$ has either at least one end on an edge in the interval $[i_r+3, k_r-2]$ or both ends lie in $[i_r, i_r+3]$ or both ends lie in $[k_r-2, k_r+1]$.)
+(Phrased more causually, this is that $p_{r+1}$ has either at least one end on an edge bounded by the vertices in the interval $[i_r+3, k_r-2]$ or both ends lie in $[i_r, i_r+3]$ or both ends lie in $[k_r-2, k_r+1]$.)
 These situations all behave similarly.

### 2019-03-21 General WLD combinatorics.tex
progress on the 3k dimension proof section

@@
   By Algorithm~\ref{alg:put GN on WLD} the Grassmann necklace of $W$ is obtained from the Grassmann necklace of $V$ by duplicating the $i$th element of the Grassmann necklace of $V$ (shifting indices as appropriate), and incrementing all indices greater than $i$ in each Grassmann necklace element.
-Formally, if $I_1^{(V)}, \ldots, I_{n-1}^{(V)}$ and $I_1^{(W)}, \ldots, I_n^{(W)}$ are the Grassmann necklaces of $V$ and $W$ respectively then
+Formally, if $I_1^{V}, \ldots, I_{n-1}^{V}$ and $I_1^{W}, \ldots, I_n^{W}$ are the Grassmann necklaces of $V$ and $W$ respectively then
   \[
-  I_j^{(W)} =
+  I_j^{W} =
   \begin{cases}
-    \{\ell \in I_j^{(V)} : \ell < i\} \cup \{\ell+1 \in I_j^{(V)} : \ell \geq i\} & \text{if $j\leq i$} \\
-    \{\ell \in I_{j-1}^{(V)} : \ell < i\} \cup \{\ell+1 \in I_{j-1}^{(V)} : \ell \geq i\} & \text{if $j > i$.}
+    \{\ell \in I_j^{V} : \ell < i\} \cup \{\ell+1 \in I_j^{V} : \ell \geq i\} & \text{if $j\leq i$} \\
+    \{\ell \in I_{j-1}^{V} : \ell < i\} \cup \{\ell+1 \in I_{j-1}^{V} : \ell \geq i\} & \text{if $j > i$.}
   \end{cases}
@@
  \includegraphics{specialp}
-  \caption{The different possibilities for $W$ and $p$.  No other propagators can end in the fat red sections.  Other segments may have additional propagators ending in them.}\label{fig special p}
+  \caption{The two cases for $W$ and $p$.  No other propagators can end in the fat red sections.  Other segments may have additional propagators ending in them.}\label{fig special p}
 \end{figure}
@@
 
-We first consider $I_1^{(W)}$.
-Note that $n-3 \not\in I_1^{(V)}$: for the right hand case this is clear from the diagram (since Algorithm~\ref{alg:put GN on WLD} would assign $q$ no later than vertex $n-4$), while for the left hand case it follows from Lemma \ref{lem no fourth vertex}.
-Therefore when we start at vertex 1 and apply the Grassmann necklace algorithm to $W$, $p$ is the only unassigned propagator when we reach vertex $n-3$ and we have $ I_1^{(W)}(p) = n-3$.
-
-Next, consider $I_n^{(W)}$, i.e.
-we apply the Grassmann necklace algorithm with starting vertex $n$.
-In both cases we have $I_n^{(W)}(p) = n$.
+We first consider $I_1^{W}$.
+Note that $n-3 \not\in I_1^{V}$: for the right hand case this is clear from the diagram (since Algorithm~\ref{alg:put GN on WLD} would assign $q$ no later than vertex $n-4$), while for the left hand case it follows from Lemma \ref{lem no fourth vertex}.
+Therefore when we start at vertex 1 and apply the Grassmann necklace algorithm to $W$, $p$ is the only unassigned propagator when we reach vertex $n-3$ and we have $ I_1^{W}(p) = n-3$.
+
+Next consider $I_n^{W}$, i.e.
+the set obtained when we apply the Grassmann necklace algorithm with starting vertex $n$.
+In both cases we have $I_n^{W}(p) = n$.
 We are now at vertex 1, and the unassigned propagators are exactly those that appear in $V$.
-Therefore the algorithm continues as in $I_1^{(V)}$, i.e.
+Therefore the algorithm continues as in $I_1^{V}$, i.e.
 we have $I_n^{W} = I_1^{V} \cup \{n\}$.
-Similarly, we must have $I_{n-1}^{W} = I_n^{V} \cup \{n-1\}$.
+By a similar argument, we must have $I_{n-1}^{W} = I_n^{V} \cup \{n-1\}$.
 
@@
 
-On the other hand, if $n-2\in I_{n-2}^{V}$ then we must be in the right hand case of Figure~\ref{fig special p} and the algorithm assigns $q$ to vertex $n-2$ in both $V$ and $W$ (since $p$ is always the counterclockwise-most propagator supported on vertex $n-2$).
-If $n-1 \not\in I_{n-2}^{(V)}$, then in $W$ the algorithm assigns $p$ to $n-2$ and then proceeds identically to the remainder $I_{n-2}^{(V)}$; thus $I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-1\}$ in this case.
-
-Finally, if $n-2,n-1 \in I_{n-2}^{(V)}$ then the algorithm in $W$ assigns $q$ to $n-2$ and $p$ to $n-1$ as above, but this is different to what occurs in $I_{n-2}^{(V)}$ so we cannot argue as above.
-We are now at vertex $n$ and only propagators $p$ and $q$ have been assigned; thus we are proceeding as in the construction of $I_n^{(V)}$ but without propagator $q$.
-By Lemma~\ref{vertex cyclic int lem} we know that $q$ was assigned to $n-5$ by $I_n^{(V)}$, and the only way this could occur is if all other propagators in $V$ had already been assigned when we reached vertex $n-5$.
-Therefore $I_{n-2}^{W} = (I_{n}^{V} \setminus \{n-5\}) \cup \{n-1, n-2\}$; this completes all cases for $I_{n-2}^{(W)}$.
-
-The arguments for $I_k^{(W)}$ ($1< k < n-2$) proceed analagously to those of $I_{n-2}^{(W)}$, with one simplification: we cannot have both $n-3$ and $n-2$ in $I_k^{(V)}$ since $q$ is the only propagator that could be assigned to either of them, and it cannot be assigned to both.
+On the other hand, if $n-2\in I_{n-2}^{V}$ then we must be in the right hand case of Figure~\ref{fig special p} and the algorithm assigns $q$ to vertex $n-2$ in both $V$ and $W$ (since $q$ is always the clockwise-most propagator supported on vertex $n-2$; see Figure~\ref{fig special p}).
+If $n-1 \not\in I_{n-2}^{V}$, then in $W$ the algorithm assigns $p$ to $n-1$ and then proceeds identically to $I_{n-2}^{V}$ for the remainder of its steps; thus $I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-1\}$ in this case.
+
+Finally, if $n-2,n-1 \in I_{n-2}^{V}$ then the algorithm in $W$ assigns $q$ to $n-2$ and $p$ to $n-1$ as above, but this is different to what occurs in $I_{n-2}^{V}$ so we cannot use the same argument as above.
+We are now at vertex $n$ and only propagators $p$ and $q$ have been assigned; thus we are proceeding as in the construction of $I_n^{V}$ but without propagator $q$.
+By Lemma~\ref{vertex cyclic int lem} we know that $q$ was assigned to $n-5$ by $I_n^{V}$, and the only way this could occur is if all other propagators in $V$ had already been assigned when we reached vertex $n-5$ (see Figure~\ref{fig special p}); thus $q$ was the final propagator to be assigned in $I_n^{V}$.
+Therefore $I_{n-2}^{W} = (I_{n}^{V} \setminus \{n-5\}) \cup \{n-1, n-2\}$; this completes all cases for $I_{n-2}^{W}$.
+
+The arguments for $I_k^{W}$ ($1< k < n-2$) proceed analagously to those of $I_{n-2}^{W}$, with one simplification: we cannot have both $n-3$ and $n-2$ in $I_k^{V}$ since $q$ is the only propagator that could be assigned to either of them, and it cannot be assigned to both.
 
@@
   Let $V$ and $W$ be as in Lemma~\ref{lem I}.
-  The shape of the Le diagram of $V$ can be built from left to right of the following blocks: a rectangle with 3 columns, one more column of the same length, a partition shape with at most as many rows as the rectangle.
+  The shape of the Le diagram of $V$ can be built from left to right of the following blocks: a rectangle which is 3 columns wide, one more column of the same height, and a partition shape with at most as many rows as the rectangle.
   The shape of the Le diagram of $W$ can be built from left to right of the following blocks: a rectangle with 3 columns and one more row than the first rectangle of $V$, and the same partition shape as in $V$.
@@
 Recall that $I_1$ determines the shape of the Le diagram.
-By Lemma~\ref{lem I}, we know that $I_1^{W} = I_1^{V}\cup \{n-3\}$, and that $n,n-1,n-2, n-3 \not\in I_1^{(V)}$.
+By Lemma~\ref{lem I} we know that $n,n-1,n-2, n-3 \not\in I_1^{V}$ (which yields the leftmost four columns of the diagram for $V$) and that $I_1^{W} = I_1^{V}\cup \{n-3\}$.
 This implies that the right hand boundary of the shape of $V$ is the same as the right hand boundary of the shape of $W$ except that $W$ has one additional row of 3 boxes while $V$ has an additional column in the $n-3$ position; that is, an extra column fourth from the left.
@@
 
-The pieces of the Le diagrams of $V$ and $W$ will be called $\mathcal{A}$ and $\mathcal{B}$ in what follows, as in Figure~\ref{fig Le}.
-Over the course of the next few lemmas we will prove that the plusses in the $\mathcal{B}$ parts of each diagram are identical, and that the plusses in the $\mathcal{A}$ parts are very closely related.
+As illustrated in Figure~\ref{fig Le}, the pieces of the Le diagrams of $V$ and $W$ will be called $\mathcal{A}$ and $\mathcal{B}$ in what follows.
+Over the course of the next few lemmas we will prove that the plusses in the $\mathcal{B}$ parts of each diagram are identical, and that the relationship between the plusses in the $\mathcal{A}$ regions can be described explicitly.
 
@@
 Let $V$ and $W$ be as in Lemma~\ref{lem I}.
-Then $I_n^{W}$ and $I_{n-1}^{W}$ together yield the same plusses as $I_n^{V}$ did, along with extra plusses in the leftmost two boxes of the bottom row of the Le diagram of $W$.
+Then $I_n^{W}$ and $I_{n-1}^{W}$ together yield the same plusses as $I_n^{V}$ did, along with two extra plusses which appear in the leftmost two boxes of the bottom row of the Le diagram of $W$.
 \end{lem}
@@
 \begin{proof}
-By Lemma~\ref{lem I} we have $I_n^{W}= I_1^{V} \cup \{n\}$ and $I_1^{(W)} = I_1^{(V)} \cup \{n-3\}$. Thus 
-\[I_1^{(W)} \setminus I_n^{(W)} = \{n-3\}, \qquad \qquad I_n^{(W)} \setminus I_1^{(W)} = \{n\},\]
+By Lemma~\ref{lem I} we have $I_n^{W}= I_1^{V} \cup \{n\}$ and $I_1^{W} = I_1^{V} \cup \{n-3\}$. Thus 
+\[I_1^{W} \setminus I_n^{W} = \{n-3\}, \qquad \qquad I_n^{W} \setminus I_1^{W} = \{n\},\]
 and so by Algorithm~\ref{alg:GN to Le} we have a plus in the $(n-3) \rightarrow n$ position, i.e. in the leftmost box of the bottom row.
@@
 \begin{lem}\label{lem n-2 good}
-  Let $V$ and $W$ be as in Lemma~\ref{lem I}, with $n-2 \not\in I_{n-2}^{V}$. Then $I_{n-2}^{W}$ contributes an $(n-3)\rightarrow (n-2)$ plus, and all of the $I_{n-1}^{V}=I_{n-2}^{V}$ plusses.
+  Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that $n-2 \not\in I_{n-2}^{V}$.
+Then $I_{n-2}^{W}$ contributes all of the same plusses as $I_{n-1}^{V}=I_{n-2}^{V}$, along with a new $(n-3)\rightarrow (n-2)$ plus.
 \end{lem}
@@
 Note that $n-3\not\in I_{n-2}^{V}$ by Lemma~\ref{lem no fourth vertex}.
-Therefore the paths for $I_{n-2}^{W}$ are the paths for $I_{n-1}^{V}$ along with the $(n-3)\rightarrow (n-2)$ path.
+Therefore the paths controlling the plusses contributed by $I_{n-2}^{W}$ are exactly the paths for $I_{n-1}^{V}$ along with the $(n-3)\rightarrow (n-2)$ path.
 This gives the statement of the lemma.
@@
 
-Then $I_{n-2}^{W}$ and $I_{n-3}^{W}$ contribute the following plusses to the Le diagram of $W$
+Then $I_{n-2}^{W}$ and $I_{n-3}^{W}$ contribute the following plusses to the Le diagram of $W$:
   \begin{itemize}
-  \item An $(n-3)\rightarrow (n-2)$ plus and an $(n-5)\rightarrow (n-1)$ plus.
   \item All of the $I_{n-1}^{V}$ plusses.
+  \item An $(n-3)\rightarrow (n-2)$ plus and a $(n-1)\rightarrow (n-1)$ plus.
   \item In the Le diagram of $V$, $I_{n-2}^{V}$ contributes an $n-5\rightarrow n-2$ plus and no other term in the Grassmann necklace of $V$ gives a plus in this column.
-$I_{n-2}^W$ does not contribute this $+$ but yields an $n-5\rightarrow n-1$ plus instead.
+$I_{n-2}^W$ does not contribute this $+$ but yields an $(n-5)\rightarrow (n-1)$ plus instead.
   \item All other plusses of $I_{n-2}^{V}$.
-  \item In the Le diagram of $V$, $I_{n-3}^{V}$ gives a plus in the $n-3$ column.  This $+$ is shifted over into the $n-2$ column in $W$.
+  \item In the Le diagram of $V$, $I_{n-3}^{V}$ gives a plus in the $n-3$ column.  This $+$ is shifted one square to the left (into the $n-2$ column) in the Le diagram of $W$.
   \item All other plusses of $I_{n-3}^{V}$.
   \end{itemize}
-Furthermore, no element of the Gramann necklace of $V$ gives an $n-5\rightarrow n-1$ plus.
+Furthermore, no element of the Grassmann necklace of $V$ contributes a $(n-5)\rightarrow (n-1)$ plus.
 \end{lem}
@@
 \begin{proof}
-  By Lemma~\ref{lem I} $I_{n-2}^{W}= (I_{n}^{V} - \{n-5\})\cup \{n-1,n-2\}$.
-Also, by the location of $q$ in the WLD,  $n-2\not\in I_{n-3}^{V}$ and and $n-5$ is the index of the lowest vertical edge in $\mathcal{B}$.
+  By Lemma~\ref{lem I} we have $I_{n-2}^{W}= (I_{n}^{V} \setminus \{n-5\})\cup \{n-1,n-2\}$.
+We are necessarily in the case where $W$ admits a propagator $q$ (Case 2 of Figure~\ref{fig special p}) and we can see from the location of $q$ that $n-2\not\in I_{n-3}^{V}$ and that $n-5$ is the largest row index in $\mathcal{B}$.
 Thus this section of the Gramann necklace of $V$ looks like
@@
   where the first ``something'' is either $n$ or an element of $I_1^{V}$ and the second ``something'' is an element of $I_1^{V}$.
-Additionally all elements not explicitly mentioned must be in $I_1^{V}$ as they remain unchanged through this portion of the necklace.
-
-  Using this information now determine the symmetric difference of $I_{n-2}^{V}$ and $I_1^{V}$: $n-1, n-2$ and possibly $n$ are in $I_{n-2}^{V}$ but not in $I_1^{V}$.
-$n-5$ is in $I_1^{V}$ as are at least one and at most two other elements.
+%Additionally all elements not explicitly mentioned must be in $I_1^{V}$ as they remain unchanged through this portion of the necklace.
+
+  Using this information we can determine the symmetric difference of $I_{n-2}^{V}$ and $I_1^{V}$, which has size $\leq 3$ by the definition of a Grassmann necklace.
+We have $n-1, n-2 \in I_{n-2}^{V} \setminus I_1^V$ for certain, and the third element (if it exists) must be $n$.
+On the other hand, we have $n-5 \in I_1^{V} \setminus I_{n-2}^V$, along with at least one and at most two other elements.
 If there is one such element call it $a$.
 If there are two call them $a$ and $b$ with $a>b$.
+
   This means that the plusses in the Le diagram of $V$ coming from $I_{n-2}^{V}$ are as in the first part of Figure~\ref{fig messy}.
-Stepping to $I_{n-1}^{V}$ simply removes the $n-5\rightarrow n-2$ path, see the second part of Figure~\ref{fig messy}.
+Stepping to $I_{n-1}^{V}$ simply removes the $n-5\rightarrow n-2$ path (equation \eqref{eq necklace}); this is illustrated in the second part of Figure~\ref{fig messy}.
 
@@
     \includegraphics{messy}
-    \caption{Plusses coming from $I_{n-2}^{V}$ (top left),  $I_{n-1}^{V}$ (top right) and $I_{n}^{V}$ bottom when $n-1, n-2\in I_{n-1}^{V}$.
-The blue lines are the non-intersecting paths.
+    \caption{Plusses coming from $I_{n-2}^{V}$ (top left),  $I_{n-1}^{V}$ (top right) and $I_{n}^{V}$ (bottom), in the case where $n-1, n-2\in I_{n-2}^{V}$.
+The blue lines are the non-intersecting paths defining the position of the plusses.
 The dashed blue lines may or may not appear, but if one appears then they both do.}\label{fig messy}
@@
 
-  Stepping to $I_{n}^{V}$, $n-1$ is taken out and either $n$ is put in if it was not there before, or one of $a$ or $b$ is put in and hence no longer available as a right end for a path.
+  Stepping to $I_{n}^{V}$, $n-1$ is removed and either $n$ is put in if it was not there before, or one of $a$ or $b$ is put in and hence is no longer available as the starting point for a path.
 This gives two possible configurations illustrated in the bottom two parts of Figure~\ref{fig messy}.
@@
   Now consider $I_{n-3}^{V}$.
-By \eqref{eq necklace} $I_{n-3}^{V}$ contributes the same plusses as $I_{n_2}^{V}$ except that it contributes an $n-5\rightarrow n-3$ plus in place of the $n-5\rightarrow n-2$ plus.
-Also, we have $n-3\in I_{n-3}^{V}$ be the location of $q$ and so $I_{k}^{W} = I_k^{V}\cup\{n-2\}$.
+By \eqref{eq necklace} $I_{n-3}^{V}$ contributes almost the same plusses as $I_{n_2}^{V}$: the only difference is that it contributes an $(n-5)\rightarrow (n-3)$ plus in place of the $(n-5)\rightarrow (n-2)$ plus.
+Since we must have $n-3\in I_{n-3}^{V}$ (because propagator $q$ exists in $V$), it follows from Lemma\ref{lem I} that $I_{n-3}^{W} = I_{n-3}^{V}\cup\{n-2\}$.
 Thus the paths for $I^{W}_{n-3}$ are the same as for $I^{V}_{n-3}$ except that the path that did go to $n-3$ now goes to $n-2$.
@@
 
-  Also note that $I_{n-3}^{V}, I_{n-2}^{V}$, and $I_{n-1}^{V}$ share their plusses outside of the $n-3$ and $n-2$ columns.  This proves the remaining statements of the lemma except the furthermore.
-
-  Finally, suppose there were a $n-5\rightarrow n-1$ plus in the Le diagram of $V$.
-By the algorithm, it would have to come when $n-5 \not\in I_j^{V}$.
-By \eqref{eq necklace} this means that it would have to come from $I_{n-4}^{V}$, $I_{n-3}^{V}$, or $I_{n-2}^{V}$.
-The analysis above shows it does not come from $I_{n-3}^{V}$ or $I_{n-2}^{V}$.
-Now, $n-4\in I_{n-4}^{V}$ by the location of $q$ and so $I_{n-4}^{V}$ must give an $n-5\rightarrow n-4$ plus and so cannot give an $n-5\rightarrow n-1$ plus.
+  Also note that $I_{n-3}^{V}, I_{n-2}^{V}$, and $I_{n-1}^{V}$ share their plusses outside of the $n-3$ and $n-2$ columns.
+This proves the remaining bullet points of the lemma, leaving only the claim about the $(n-5)\rightarrow (n-1)$ plus.
+
+  So suppose there were a $n-5\rightarrow n-1$ plus in the Le diagram of $V$.
+By Algorithm~\ref{alg:GN to Le}, this plus could only be contributed by a necklace term that satisfies $n-5 \not\in I_*^{V}$.
+By \eqref{eq necklace}, the only terms that could have this property are $I_{n-4}^{V}$, $I_{n-3}^{V}$, and $I_{n-2}^{V}$.
+The analysis above shows that it does not come from $I_{n-2}^V$ or $I_{n-3}^V$.
+
+  Recall that $n-5$ is the largest row index in the Le diagram of $V$, and $n-5 \in I_1^V \setminus I_{n-4}^V$ so we do have a path starting at $n-5$.
+Since $n-4 \in I_{n-4}^V$ by the location of the propagator $q$, we must have a path ending at $n-4$.
+Since the paths cannot cross, this implies that $_{n-4}^V$ must contribute a $(n-5) \rightarrow (n-4)$ plus, and hence cannot contribute a $(n-5)\rightarrow (n-1)$ plus.
 
@@
 \begin{lem}\label{lem other k}
-  Let $V$ and $W$ be as in Lemma~\ref{lem I} and take $1<k<n-2$.  Suppose that if $n-2\in I_{n-2}^{V}$ then also $n-1\in I_{n-2}^{V}$.
-  Then $I_k^{W}$ gives the same plusses as $I_{k}^{V}$ except that if there is a plus in the $n-3$ column for $I_{k}^{V}$ then this plus is shifted into the $n-2$ column and no plus was already in that location.
+  Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that if $n-2\in I_{n-2}^{V}$ then also $n-1\in I_{n-2}^{V}$.
+Fix a $k$ in the range $1<k<n-2$.
+Then $I_k^{W}$ contributes the same plusses as $I_{k}^{V}$, except that if $I_{k}^{V}$ contributed a plus in the $n-3$ column then this plus is shifted one square left into the $n-2$ column, and no plus was already in that location in the Le diagram of $W$.
 \end{lem}
@@
 \begin{proof}
-  If $n-3\not\in I_{k}^{V}$ then by Lemma~\ref{lem I} $I_{k}^{W} = I_k^{V}\cup \{n-3\}$.
+Recall that $I_1^W = I_1^V\cup \{n-3\}$ and that $n-2,n-1,n \not\in I_1^W$.
+
+  If $n-3\not\in I_{k}^{V}$ then by Lemma~\ref{lem I} we have $I_{k}^{W} = I_k^{V}\cup \{n-3\}$.
 Then since $n-3$ is the largest element of $I_1^{W}$ this transformation leaves the disjoint paths unchanged and so the plusses carry over from $V$ to $W$ directly.
 
-  If $n-3\in I_{k}^{V}$ then by Lemma~\ref{lem I} $I_{k}^{W} = I_k^{V}\cup \{n-2\}$.
+  If $n-3\in I_{k}^{V}$ then $I_k^V$ must contribute a plus in the $n-3$ column of the Le diagram of $V$, and by Lemma~\ref{lem I} we have $I_{k}^{W} = I_k^{V}\cup \{n-2\}$.
 If $n-2$ supports no propagators in $V$ then certainly no pluses appear in the $n-2$ column of the Le diagram of $V$.
-If $n-2$ supports at least one propagator in $V$ then by hypothesis so is $n-1$ and so we satisfy the hypotheses of Lemma~\ref{lem n-2 bad}.
-Thus the only necklace element of $V$ containing $n-2$ is $I_{n-2}^{V}$ and this particular plus is not contributed to the Le diagram of $D$ by $I_{n-2}^{W}$.
-
-  {}From $I_{k}^{V}$ there is a path from some vertical edge to the bottom edge $n-3$.
-In $I_{k}^{W}$, $n-3$ is a vertical edge with no path and instead there must be a path to $n-2$.
-By the previous paragraph no other path can end in $n-2$, so shifting the path that did go to $n-3$ to go to $n-2$ while leaving the others the same maintains non-crossingness and so must be the paths for $I_{k}^{W}$.
-Thus the plus in the $n-3$ column for $C$ is shifted into the $n-2$ column, where there was no plus before, and no other plusses are changed.
+If $n-2$ supports at least one propagator in $V$ then $n-2 \in I_{n-2}^V$ and so by hypothesis $n-1 \in I_{n-2}^V$ as well.
+By Lemma~\ref{lem n-2 bad}, the only necklace element of $V$ containing $n-2$ is $I_{n-2}^{V}$ and the corresponding plus is not contributed to the Le diagram of $W$ by $I_{n-2}^{W}$.
+
+  Since $n-3 \in I_k^V \setminus I_1^V$, we must have a path from some vertical edge $i$ to the bottom edge $n-3$ in the Le diagram of $V$.
+In the Le diagram of $W$, the index $n-3$ labels a vertical edge with no path starting at it (since $n-3$ belongs to both $I_1^W$ and $I_k^W$), and there must be a path leading to $n-2$ since $n-2 \in I_k^W \setminus I_1^W$.
+By the previous paragraph no other path from $I_k^V$ could end at $n-2$, so since the paths cannot cross we conclude that the $i\rightarrow (n-3)$ path in the Le diagram of $V$ must become a $i\rightarrow (n-2)$ path in the Le diagram of $W$.
+
+   Thus the plus contributed by $I_k^V$ in the $n-3$ column of the Le diagram of $V$ is shifted into the $n-2$ column in the Le diagram for $W$, where there was no plus before, and no other plusses are changed.
 \end{proof}
@@
   First note that a Wilson loop diagram $W$ with one propagator supported on vertices $i<j<k<\ell$ has Le diagram a single row with $|W|-i$ boxes.
-Labelling them from left to right by $|W|, \ldots, |W|-i+1$, by the algorithm there are plusses in the $j$, $k$, and $\ell$ positions.
+Labelling the columns from left to right by $|W|, \ldots, |W|-i+1$, by the algorithm there are plusses in the $j$, $k$, and $\ell$ positions.
 
   Now consider Wilson loop diagrams with $k>1$ propagators.
-By Lemma~\ref{lem uncovered} it suffices to prove the result for weakly admissible Wilson loop diagrams with $k$ propagators and no vertices that do not support at least one propagator.
+By Lemma~\ref{lem uncovered} it suffices to prove the result for weakly admissible Wilson loop diagrams with $k$ propagators and no non-supporting vertices.
 By Lemma~\ref{lem dihedral} it suffices to prove the result for at least one Wilson loop diagram from each dihedral orbit.
-Take a weakly admissible Wilson loop diagram $W$ with $k$ propagators and no vertices which do not support at least one propagator.
+Take a weakly admissible Wilson loop diagram $W$ with $k$ propagators and no non-supporting vertices.
 Make a dihedral transformation of $W$ if necessary so that $W$ has a propagator $p$ with the properties in Lemma~\ref{lem good p} relative to $W$.
-If $n-1$ supports only $p$ but $n-2$ supports at least one other propagator, then flip $W$ on the line perpendicular to the edge from $n-2$ to $n-1$.
-This will be our $W$ for the rest of the proof.
-
-  Let $V$ be $W$ with $p$ removed.
-Note that if $n-2$ supports at least one propagator in $V$ then so is $n-1$ by the end of the previous paragraph and so if $n-2$ supports at least one propagator in $V$ then the hypotheses of Lemma~\ref{lem n-2 bad} are satisfied.
-
-  {}From Lemma~\ref{lem shape} we know how the shapes of the Le diagrams of $V$ and $W$ relate; let $\mathcal{A}$ and $\mathcal{B}$ be as described after that lemma.
+
+  We make one further simplification: if our $W$ is in Case 2 of Figure~\ref{fig special p} and $n-1$ supports only $p$ but $n-2$ supports at least one other propagator, then flip $W$ on the line perpendicular to the edge from $n-2$ to $n-1$ to obtain a diagram with the configuration of Case 1.
+This eliminates the possibility that we could have $n-2 \in I_{n-2}^W$ but $n-1 \not\in I_{n-2}^W$.
+
+  This diagram will be our $W$ for the remainder of the proof. Let $V$ be $W$ with $p$ removed.
+
+  From Lemma~\ref{lem shape} we know how the shapes of the Le diagrams of $V$ and $W$ relate; let $\mathcal{A}$ and $\mathcal{B}$ be as described after that lemma.
 Lemmas~\ref{lem n and n-1}, \ref{lem n-2 good}, and \ref{lem n-2 bad} tell us that the three boxes of the bottom row of the Le diagram of $W$ each have a plus.
@@
   \begin{itemize}
-  \item Plusses from $\mathcal{B}$ for $V$ maintain their positions in $\mathcal{B}$ for $W$.
-  \item Plusses from the first two columns (the $n$ and the $n-1$ columns) of $\mathcal{A}$ for $V$ maintain their positions in $\mathcal{A}$ for $W$.
+  \item All plusses from $\mathcal{B}$ for $V$ maintain their positions in $\mathcal{B}$ for $W$.
+  \item All plusses from the leftmost two columns (the $n$ and the $n-1$ columns) of $\mathcal{A}$ for $V$ maintain their positions in $\mathcal{A}$ for $W$.
   \item If there is a plus in the $n-2$ column of $\mathcal{A}$ in $V$ then Lemma~\ref{lem n-2 bad} applies, so there is exactly one such plus.
-This plus maps to the $n-5\rightarrow n-1$ plus for $W$.
-  \item The plusses in the $n-3$ column for $V$ shift over to the third column (the $n-2$ column) of $\mathcal{A}$ in $W$.
+This plus is mapped to the $(n-5)\rightarrow (n-1)$ plus for $W$.
+  \item All plusses in the $n-3$ column for $V$ are shifted one square to the left in $\mathcal{A}$ for $W$, i.e. into the $n-2$ column.
   \end{itemize}
-  This map is clearly reversible and hence bijective except possibly for the $n-5\rightarrow n-1$ plus for $W$.
-If the Le diagram of $W$ has an $n-5\rightarrow n-1$ plus then look at the Le diagram for $V$.
-If the Le diagram for $V$ has a plus in the $n-2$ column then Lemma~\ref{lem n-2 bad} applies and so there is no $n-5\rightarrow n-1$ plus in the Le diagram of $V$ and the $n-5\rightarrow n-1$ plus of $W$ can be uniquely mapped to the plus in the $n-2$ column of the Le diagram of $V$.
+  Note that this map is reversible and hence bijective.
+Indeed, the only possible ambiguity is at the $(n-5)\rightarrow (n-1)$ plus in $W$ (if it exists), which could have come from either of the first or third bullet points.
+However, if the third bullet point applies then by Lemma~\ref{lem n-2 bad} there is no $(n-5)\rightarrow (n-1)$ plus in $V$, i.e.
+the first bullet point does not apply.
+
+  % If the Le diagram for $V$ has a plus in the $n-2$ column then Lemma~\ref{lem n-2 bad} applies.
+By the final part of Lemma~\ref{lem n-2 bad} there is no $n-5\rightarrow n-1$ plus in the Le diagram of $V$, and so the $n-5\rightarrow n-1$ plus of $W$ can be uniquely mapped to the plus in the $n-2$ column of the Le diagram of $V$.
 If the Le diagram for $V$ has no plus in the $n-2$ column, then leave the $n-5\rightarrow n-1$ plus where it is in moving back to $V$.
@@
 
-  From all of this we get that the number of plusses in the Le diagram for $W$ is three more than the number of plusses in the Le diagram for $V$.  Applying induction completes the proof.
+  By Lemmas~\ref{lem n and n-1}, \ref{lem n-2 good}, and \ref{lem n-2 bad}, the bottom row of the diagram of $W$ always contains 3 new plusses; thus $W$ admits $3k + 3$ plusses in total.
+Applying induction completes the proof.
+
 \end{proof}

### 2019-03-22 General WLD combinatorics.tex
dimension proof

@@
 
-Let $W$ be an admissible Wilson loop diagram with $k$ propagators, and with a vertex $i$ which supports no propagators.
+Let $W$ be an admissible Wilson loop diagram with $k$ propagators, and with a vertex $i$ that supports no propagators.
 Let $V$ be $W$ with vertex $i$ removed.
@@
 \begin{proof}
-By \cite[Proposition 17.10]{Postnikov}, the dimension of a positroid (and hence the number of plusses in its Le diagram) is $k(n-k) - A(\pi_W)$, where $A(\pi_W)$ denotes the number of alignments (see \cite[Figure 17.1]{Postnikov} and preceding discussion) of the decorated permutation $\pi_W$ of the positroid associated to $W$.
+By \cite[Proposition 17.10]{Postnikov}, the dimension of a positroid (and hence the number of plusses in its Le diagram) is $k(n-k) - A(\pi_W)$, where $A(\pi_W)$ denotes the number of alignments of the decorated permutation $\pi_W$ of the positroid associated to $W$.
+(See \cite[Figure 17.1]{Postnikov} and preceding discussion.)
 
@@
 \begin{lem}\label{lem good p}
-  Let $W$ be an admissible Wilson loop diagram with $n\geq 1$ propagators.
-Then there is some dihedral transformation $W'$ of $W$ such that there is a propagator $p$ of $W'$ with the following properties.
+  Let $W$ be an admissible Wilson loop diagram with $n\geq 1$ propagators.  Then there is some dihedral transformation $W'$ of $W$ such that $W'$ has a propagator $p$ with the following properties.
   \begin{itemize}
-  \item $p = (i, n-1)$ with no propagators inside it (that is $i+2, \ldots, n-2$ do not support any propagators in $W'$).
+  \item $p = (i, n-1)$ for some $i$, and $p$ has no propagators inside it (that is $i+2, \ldots, n-2$ do not support any propagators in $W'$).
   \item Either the edge $i$ in $W'$ only supports $p$ or the edge $i$ in $W'$ supports exactly one other propagator $q = (j, i)$ with no other propagators inside $q$.
@@
 Lemma~\ref{lem sian} applied to $V$ gives a length 2 propagator $p$ in $V$ for which either no other propagator is supported on one of the supporting edges of $p$ or there is a second length 2 propagator which is the only other propagator supported on one of the supporting edges of $p$.
-Figure~\ref{fig 3 cases} shows the possible cases, and the reader can easily check that in each case $p$ must be in one of the two situations described above.
-
-  By Lemma~\ref{lem dihedral} there is a dihedral transformation of $V$ which yields a diagram satisfying the statement of the lemma with $p$ and $q$ both length 2.
+(Figure~\ref{fig 3 cases} shows the possible configurations arising from Lemma~\ref{lem sian}, and the reader can easily check that in each case $p$ must be in one of the two situations described above.)
+
+  We can now make a dihedral transformation of $V$ to obtain a diagram satisfying the statement of the lemma with $p$ and $q$ both length 2.
 Restoring the vertices which do not support any propagators, we obtain a dihedral transformation $W'$ of $W$ as desired (with potentially longer lengths for $p$ and $q$).
@@
 
-Combining Lemmas \ref{lem uncovered}, \ref{lem dihedral}, and \ref{lem good p}, it therefore suffices to study the Le diagrams of \hlfix{weakly}{check} admissible Wilson loop diagrams admitting one of the configurations described in Lemma~\ref{lem good p} with propagators $p$ and $q$ (if $q$ exists) both of length 2.
+Combining Lemmas \ref{lem uncovered}, \ref{lem dihedral}, and \ref{lem good p}, it therefore suffices to study the Le diagrams of weakly admissible Wilson loop diagrams admitting one of the configurations described in Lemma~\ref{lem good p} with propagators $p$ and $q$ (if $q$ exists) both of length 2.
 See Figure~\ref{fig special p} for an illustration of the two possibilities.
@@
     \begin{cases}
-      I_k^{V}\cup \{n-3\} & \text{if $n-3 \not\in I_k^{V}$}\\
-      I_k^{V}\cup\{n-2\} & \text{if $n-3\in I_k^{V}$}
+      I_k^{V}\cup \{n-3\} & \qquad \qquad \qquad \qquad \text{if $n-3 \not\in I_k^{V}$}\\
+      I_k^{V}\cup\{n-2\} & \qquad \qquad \qquad \qquad \text{if $n-3\in I_k^{V}$}
     \end{cases} \\
@@
 
-The two possible situations are illustrated in Figure~\ref{fig special p}. The arguments proceed in a similar manner to Lemma~\ref{vertex cyclic int lem}.
-
-We first consider $I_1^{W}$.
+The two possible cases for $W$ are illustrated in Figure~\ref{fig special p}; all references to the ``left hand case'' or ``right hand case'' below refer to the diagrams in this figure.
+
+We first consider $I_1^{W}$, i.e.
+the set obtained by applying the Grassmann necklace algorithm to $W$ with starting vertex 1.
 Note that $n-3 \not\in I_1^{V}$: for the right hand case this is clear from the diagram (since Algorithm~\ref{alg:put GN on WLD} would assign $q$ no later than vertex $n-4$), while for the left hand case it follows from Lemma \ref{lem no fourth vertex}.
-Therefore when we start at vertex 1 and apply the Grassmann necklace algorithm to $W$, $p$ is the only unassigned propagator when we reach vertex $n-3$ and we have $ I_1^{W}(p) = n-3$.
-
-Next consider $I_n^{W}$, i.e.
-the set obtained when we apply the Grassmann necklace algorithm with starting vertex $n$.
-In both cases we have $I_n^{W}(p) = n$.
+Therefore when we start at vertex 1 and apply the Grassmann necklace algorithm to $W$, $p$ is the only remaining unassigned propagator when we reach vertex $n-3$, and so we have $ I_1^{W}(p) = n-3$ and $I_1^W = I_1^V\cup \{n-3\}$.
+
+Next consider $I_n^{W}$.
+From the figure we see that in both cases we have $I_n^{W}(p) = n$.
 We are now at vertex 1, and the unassigned propagators are exactly those that appear in $V$.
@@
 
-Finally, if $n-2,n-1 \in I_{n-2}^{V}$ then the algorithm in $W$ assigns $q$ to $n-2$ and $p$ to $n-1$ as above, but this is different to what occurs in $I_{n-2}^{V}$ so we cannot use the same argument as above.
+Finally, if $n-2,n-1 \in I_{n-2}^{V}$ then in $W$ the algorithm assigns $q$ to $n-2$ and $p$ to $n-1$ as above, but this is different to what occured in $I_{n-2}^{V}$ so we cannot use the same argument as above.
 We are now at vertex $n$ and only propagators $p$ and $q$ have been assigned; thus we are proceeding as in the construction of $I_n^{V}$ but without propagator $q$.
-By Lemma~\ref{vertex cyclic int lem} we know that $q$ was assigned to $n-5$ by $I_n^{V}$, and the only way this could occur is if all other propagators in $V$ had already been assigned when we reached vertex $n-5$ (see Figure~\ref{fig special p}); thus $q$ was the final propagator to be assigned in $I_n^{V}$.
-Therefore $I_{n-2}^{W} = (I_{n}^{V} \setminus \{n-5\}) \cup \{n-1, n-2\}$; this completes all cases for $I_{n-2}^{W}$.
+By Lemma~\ref{vertex cyclic int lem} we know that $q$ was assigned to $n-5$ by $I_n^{V}$, and from the diagram we see that the only way this could occur is if all other propagators in $V$ had already been assigned when we reached vertex $n-5$; thus $q$ was the final propagator to be assigned in $I_n^{V}$.
+Therefore $I_{n-2}^{W} = (I_{n}^{V} \setminus \{n-5\}) \cup \{n-1, n-2\}$ in this case.
+This completes all cases for $I_{n-2}^{W}$.
 
@@
 
+\begin{figure}
+  \includegraphics{Le_diagrams}
+  \caption{Le diagrams for $V$ (left) and $W$ (right).}\label{fig Le}
+\end{figure}
+
+\note{When doing the final formatting, try to ensure that Figure \ref{fig Le} and Lemma \ref{lem shape} are on the same page}
 \begin{lem}\label{lem shape}
@@
 Recall that $I_1$ determines the shape of the Le diagram.
-By Lemma~\ref{lem I} we know that $n,n-1,n-2, n-3 \not\in I_1^{V}$ (which yields the leftmost four columns of the diagram for $V$) and that $I_1^{W} = I_1^{V}\cup \{n-3\}$.
+By Lemma~\ref{lem I} we know that ${n,n-1,n-2, n-3 \not\in I_1^{V}}$ (which yields the leftmost four columns of the diagram for $V$) and that $I_1^{W} = I_1^{V}\cup \{n-3\}$.
 This implies that the right hand boundary of the shape of $V$ is the same as the right hand boundary of the shape of $W$ except that $W$ has one additional row of 3 boxes while $V$ has an additional column in the $n-3$ position; that is, an extra column fourth from the left.
@@
 
-Note that when we speak of a plus in the Le diagram of $V$ being the same as in $W$ or vice versa, we mean that the position of the plus in $\mathcal{A}$ or $\mathcal{B}$ is the same; because of the column insertion the absolute indices may differ.
-
-\begin{figure}
-  \includegraphics{Le_diagrams}
-  \caption{Le diagrams for $V$ (left) and $W$ (right).}\label{fig Le}
-\end{figure}
-
-%Recall Algorithm~\ref{alg:GN to Le}, which constructs the Le diagram associated to a Grassmann necklace.
-As described in Section [ref], if Algorithm~\ref{alg:GN to Le} places a $+$ in the box with row index $i$ and column index $j$, we say that this plus is in the $i \rightarrow j$ position.
+We do this by applying Algorithm~\ref{alg:GN to Le}, which constructs the Le diagram associated to a Grassmann necklace, to the Grassmann necklaces of $V$ and $W$.
+As described in Section [ref], if Algorithm~\ref{alg:GN to Le} places a $+$ in the box with row index $i$ and column index $j$, we say that this plus is in the $i \rightarrow j$ position, and refer to it as the plus defined by ``the (hook) path from $i$ to $j$''.
+Note that the collection of paths contributed by a single Grassmann necklace term  must be non-crossing.
+
+Finally, we also note that when we speak of a plus in the Le diagram of $V$ being the same as in $W$ or vice versa, we mean that the position of the plus in $\mathcal{A}$ or $\mathcal{B}$ is the same; because of the column insertion the absolute indices may differ.
 
@@
 the second box in the bottom row of the Le diagram of $W$) along with any plusses yielded by $I_n^V$.
+\end{proof}
 
@@
 That is, we get all the plusses from $I_{n}^{V}$ along with a $n-3\rightarrow n-1$ plus, that is a plus in the second to the right box of the bottom row.
-\end{proof}
 
@@
 \begin{proof}
-If $n-2\not\in I_{n-2}^{V}$ then $I_{n-1}^{V}=I_{n-2}^{V}$ and by Lemma~\ref{lem I} we have $I_{n-2}^{W} = I_{n-1}^{V} \cup \{n-2\}$.
+If $n-2\not\in I_{n-2}^{V}$ then $I_{n-1}^{V}=I_{n-2}^{V}$ by definition, and by Lemma~\ref{lem I} we have $I_{n-2}^{W} = I_{n-1}^{V} \cup \{n-2\}$.
 Note that $n-3\not\in I_{n-2}^{V}$ by Lemma~\ref{lem no fourth vertex}.
@@
 This gives the statement of the lemma.
-
 \end{proof}
@@
 \begin{lem}\label{lem other k}
-  Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that if $n-2\in I_{n-2}^{V}$ then also $n-1\in I_{n-2}^{V}$.
-Fix a $k$ in the range $1<k<n-2$.
-Then $I_k^{W}$ contributes the same plusses as $I_{k}^{V}$, except that if $I_{k}^{V}$ contributed a plus in the $n-3$ column then this plus is shifted one square left into the $n-2$ column, and no plus was already in that location in the Le diagram of $W$.
+  Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that if $n-2\in I_{n-2}^{V}$ then $n-1\in I_{n-2}^{V}$ also.
+Then for each $k$ in the range $1<k<n-2$, $I_k^{W}$ contributes the same plusses as $I_{k}^{V}$, except that if $I_{k}^{V}$ contributed a plus in the $n-3$ column of the Le diagram of $V$ then this plus is shifted one square left in the Le diagram of $W$, and no plus was already in that location in the Le diagram of $W$.
 \end{lem}
@@
 In the Le diagram of $W$, the index $n-3$ labels a vertical edge with no path starting at it (since $n-3$ belongs to both $I_1^W$ and $I_k^W$), and there must be a path leading to $n-2$ since $n-2 \in I_k^W \setminus I_1^W$.
-By the previous paragraph no other path from $I_k^V$ could end at $n-2$, so since the paths cannot cross we conclude that the $i\rightarrow (n-3)$ path in the Le diagram of $V$ must become a $i\rightarrow (n-2)$ path in the Le diagram of $W$.
+By the previous paragraph no other path from $I_k^V$ could end at $n-2$, and since the paths cannot cross we conclude that the $i\rightarrow (n-3)$ path in the Le diagram of $V$ must become a $i\rightarrow (n-2)$ path in the Le diagram of $W$.
+All other paths are unchanged.
 
@@
 Take a weakly admissible Wilson loop diagram $W$ with $k$ propagators and no non-supporting vertices.
-Make a dihedral transformation of $W$ if necessary so that $W$ has a propagator $p$ with the properties in Lemma~\ref{lem good p} relative to $W$.
+Make a dihedral transformation of $W$ if necessary so that $W$ has a propagator $p$ with the properties in Lemma~\ref{lem good p}.
 
@@
 
-  From Lemma~\ref{lem shape} we know how the shapes of the Le diagrams of $V$ and $W$ relate; let $\mathcal{A}$ and $\mathcal{B}$ be as described after that lemma.
+  From Lemma~\ref{lem shape} we know how the shapes of the Le diagrams of $V$ and $W$ are related; let $\mathcal{A}$ and $\mathcal{B}$ be as described after that lemma.
 Lemmas~\ref{lem n and n-1}, \ref{lem n-2 good}, and \ref{lem n-2 bad} tell us that the three boxes of the bottom row of the Le diagram of $W$ each have a plus.
-Lemmas~\ref{lem n and n-1}, \ref{lem n-2 good}, \ref{lem n-2 bad}, and \ref{lem other k} show that there is a bijection between the plusses of the Le diagram of $V$ and the plusses of the Le diagram of $W$ that are not in the bottom row.
-This bijection can be described as follows.
+Lemmas~\ref{lem n and n-1} through \ref{lem other k} show that there is a bijection between the plusses of the Le diagram of $V$ and the plusses of the Le diagram of $W$ that are not in the bottom row.
+This bijection can be described as follows:
   \begin{itemize}
@@
 
-  By Lemmas~\ref{lem n and n-1}, \ref{lem n-2 good}, and \ref{lem n-2 bad}, the bottom row of the diagram of $W$ always contains 3 new plusses; thus $W$ admits $3k + 3$ plusses in total.
+Therefore the Le diagram of $W$ contains $3(k-1)$ plusses in bijection with the plusses from the Le diagram of $V$ and 3 new plusses in the bottom row, yielding $3k$ in total.
 Applying induction completes the proof.
-
 \end{proof}

### 2019-03-22 General WLD combinatorics.tex
finished with the dimension proof!

@@
 
-Recall that $I_1$ determines the shape of the Le diagram.
-By Lemma~\ref{lem I} we know that ${n,n-1,n-2, n-3 \not\in I_1^{V}}$ (which yields the leftmost four columns of the diagram for $V$) and that $I_1^{W} = I_1^{V}\cup \{n-3\}$.
+Recall that $I_1$ determines the shape of the Le diagram. By Lemma~\ref{lem I} we know that
+\newline ${n,n-1,n-2, n-3 \not\in I_1^{V}}$ (which yields the leftmost four columns of the diagram for $V$) and that $I_1^{W} = I_1^{V}\cup \{n-3\}$.
 This implies that the right hand boundary of the shape of $V$ is the same as the right hand boundary of the shape of $W$ except that $W$ has one additional row of 3 boxes while $V$ has an additional column in the $n-3$ position; that is, an extra column fourth from the left.
@@
 
-Then $I_{n-2}^{W}$ and $I_{n-3}^{W}$ contribute the following plusses to the Le diagram of $W$:
+Then $I_{n-2}^{W}$ and $I_{n-3}^{W}$ contribute the following plusses to the Le diagram of $W$
   \begin{itemize}
+  \item An $(n-3)\rightarrow (n-2)$ plus and an $(n-5)\rightarrow (n-1)$ plus.
   \item All of the $I_{n-1}^{V}$ plusses.
-  \item An $(n-3)\rightarrow (n-2)$ plus and a $(n-1)\rightarrow (n-1)$ plus.
   \item In the Le diagram of $V$, $I_{n-2}^{V}$ contributes an $n-5\rightarrow n-2$ plus and no other term in the Grassmann necklace of $V$ gives a plus in this column.
-$I_{n-2}^W$ does not contribute this $+$ but yields an $(n-5)\rightarrow (n-1)$ plus instead.
+$I_{n-2}^W$ does not contribute this $+$ but yields an $n-5\rightarrow n-1$ plus instead.
   \item All other plusses of $I_{n-2}^{V}$.
-  \item In the Le diagram of $V$, $I_{n-3}^{V}$ gives a plus in the $n-3$ column.  This $+$ is shifted one square to the left (into the $n-2$ column) in the Le diagram of $W$.
+  \item In the Le diagram of $V$, $I_{n-3}^{V}$ gives a plus in the $n-3$ column.  This $+$ is shifted over into the $n-2$ column in $W$.
   \item All other plusses of $I_{n-3}^{V}$.
   \end{itemize}
-Furthermore, no element of the Grassmann necklace of $V$ contributes a $(n-5)\rightarrow (n-1)$ plus.
+Furthermore, no element of the Gramann necklace of $V$ gives an $n-5\rightarrow n-1$ plus.
 \end{lem}
@@
 \begin{proof}
-  By Lemma~\ref{lem I} we have $I_{n-2}^{W}= (I_{n}^{V} \setminus \{n-5\})\cup \{n-1,n-2\}$.
-We are necessarily in the case where $W$ admits a propagator $q$ (Case 2 of Figure~\ref{fig special p}) and we can see from the location of $q$ that $n-2\not\in I_{n-3}^{V}$ and that $n-5$ is the largest row index in $\mathcal{B}$.
+  By Lemma~\ref{lem I} $I_{n-2}^{W}= (I_{n}^{V} - \{n-5\})\cup \{n-1,n-2\}$.
+Also, by the location of $q$ in the WLD,  $n-2\not\in I_{n-3}^{V}$ and and $n-5$ is the index of the lowest vertical edge in $\mathcal{B}$.
 Thus this section of the Gramann necklace of $V$ looks like
@@
   where the first ``something'' is either $n$ or an element of $I_1^{V}$ and the second ``something'' is an element of $I_1^{V}$.
-%Additionally all elements not explicitly mentioned must be in $I_1^{V}$ as they remain unchanged through this portion of the necklace.
-
-  Using this information we can determine the symmetric difference of $I_{n-2}^{V}$ and $I_1^{V}$, which has size $\leq 3$ by the definition of a Grassmann necklace.
-We have $n-1, n-2 \in I_{n-2}^{V} \setminus I_1^V$ for certain, and the third element (if it exists) must be $n$.
-On the other hand, we have $n-5 \in I_1^{V} \setminus I_{n-2}^V$, along with at least one and at most two other elements.
+Additionally all elements not explicitly mentioned must be in $I_1^{V}$ as they remain unchanged through this portion of the necklace.
+
+  Using this information now determine the symmetric difference of $I_{n-2}^{V}$ and $I_1^{V}$: $n-1, n-2$ and possibly $n$ are in $I_{n-2}^{V}$ but not in $I_1^{V}$.
+$n-5$ is in $I_1^{V}$ as are at least one and at most two other elements.
 If there is one such element call it $a$.
 If there are two call them $a$ and $b$ with $a>b$.
-
 This means that the plusses in the Le diagram of $V$ coming from $I_{n-2}^{V}$ are as in the first part of Figure~\ref{fig messy}.
-Stepping to $I_{n-1}^{V}$ simply removes the $n-5\rightarrow n-2$ path (equation \eqref{eq necklace}); this is illustrated in the second part of Figure~\ref{fig messy}.
+Stepping to $I_{n-1}^{V}$ simply removes the $n-5\rightarrow n-2$ path, see the second part of Figure~\ref{fig messy}.
 
@@
     \includegraphics{messy}
-    \caption{Plusses coming from $I_{n-2}^{V}$ (top left),  $I_{n-1}^{V}$ (top right) and $I_{n}^{V}$ (bottom), in the case where $n-1, n-2\in I_{n-2}^{V}$.
-The blue lines are the non-intersecting paths defining the position of the plusses.
+    \caption{Plusses coming from $I_{n-2}^{V}$ (top left),  $I_{n-1}^{V}$ (top right) and $I_{n}^{V}$ bottom when $n-1, n-2\in I_{n-1}^{V}$.
+The blue lines are the non-intersecting paths.
 The dashed blue lines may or may not appear, but if one appears then they both do.}\label{fig messy}
@@
 
-  Stepping to $I_{n}^{V}$, $n-1$ is removed and either $n$ is put in if it was not there before, or one of $a$ or $b$ is put in and hence is no longer available as the starting point for a path.
+  Stepping to $I_{n}^{V}$, $n-1$ is taken out and either $n$ is put in if it was not there before, or one of $a$ or $b$ is put in and hence no longer available as a right end for a path.
 This gives two possible configurations illustrated in the bottom two parts of Figure~\ref{fig messy}.
@@
   Now consider $I_{n-3}^{V}$.
-By \eqref{eq necklace} $I_{n-3}^{V}$ contributes almost the same plusses as $I_{n_2}^{V}$: the only difference is that it contributes an $(n-5)\rightarrow (n-3)$ plus in place of the $(n-5)\rightarrow (n-2)$ plus.
-Since we must have $n-3\in I_{n-3}^{V}$ (because propagator $q$ exists in $V$), it follows from Lemma\ref{lem I} that $I_{n-3}^{W} = I_{n-3}^{V}\cup\{n-2\}$.
+By \eqref{eq necklace} $I_{n-3}^{V}$ contributes the same plusses as $I_{n_2}^{V}$ except that it contributes an $n-5\rightarrow n-3$ plus in place of the $n-5\rightarrow n-2$ plus.
+Also, we have $n-3\in I_{n-3}^{V}$ be the location of $q$ and so $I_{k}^{W} = I_k^{V}\cup\{n-2\}$.
 Thus the paths for $I^{W}_{n-3}$ are the same as for $I^{V}_{n-3}$ except that the path that did go to $n-3$ now goes to $n-2$.
@@
 
-  Also note that $I_{n-3}^{V}, I_{n-2}^{V}$, and $I_{n-1}^{V}$ share their plusses outside of the $n-3$ and $n-2$ columns.
-This proves the remaining bullet points of the lemma, leaving only the claim about the $(n-5)\rightarrow (n-1)$ plus.
-
-  So suppose there were a $n-5\rightarrow n-1$ plus in the Le diagram of $V$.
-By Algorithm~\ref{alg:GN to Le}, this plus could only be contributed by a necklace term that satisfies $n-5 \not\in I_*^{V}$.
-By \eqref{eq necklace}, the only terms that could have this property are $I_{n-4}^{V}$, $I_{n-3}^{V}$, and $I_{n-2}^{V}$.
-The analysis above shows that it does not come from $I_{n-2}^V$ or $I_{n-3}^V$.
-
-  Recall that $n-5$ is the largest row index in the Le diagram of $V$, and $n-5 \in I_1^V \setminus I_{n-4}^V$ so we do have a path starting at $n-5$.
-Since $n-4 \in I_{n-4}^V$ by the location of the propagator $q$, we must have a path ending at $n-4$.
-Since the paths cannot cross, this implies that $_{n-4}^V$ must contribute a $(n-5) \rightarrow (n-4)$ plus, and hence cannot contribute a $(n-5)\rightarrow (n-1)$ plus.
-
+  Also note that $I_{n-3}^{V}, I_{n-2}^{V}$, and $I_{n-1}^{V}$ share their plusses outside of the $n-3$ and $n-2$ columns.  This proves the remaining statements of the lemma except the furthermore.
+
+  Finally, suppose there were a $n-5\rightarrow n-1$ plus in the Le diagram of $V$.
+By the algorithm, it would have to come when $n-5 \not\in I_j^{V}$.
+By \eqref{eq necklace} this means that it would have to come from $I_{n-4}^{V}$, $I_{n-3}^{V}$, or $I_{n-2}^{V}$.
+The analysis above shows it does not come from $I_{n-3}^{V}$ or $I_{n-2}^{V}$.
+Now, $n-4\in I_{n-4}^{V}$ by the location of $q$ and so $I_{n-4}^{V}$ must give an $n-5\rightarrow n-4$ plus and so cannot give an $n-5\rightarrow n-1$ plus.
+
+\end{proof}
+
+\note{This is a reorganised version of the previous lemma, keeping both in place for now for comparison.}
+\begin{lem}\label{lem n-2 bad v2}
+Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that $n-2,n-1 \in I_{n-2}^{V}$. Then:
+  \begin{enumerate}
+  \item $I_{n-2}^W$ contributes an $(n-3)\rightarrow (n-2)$ plus and an $(n-5)\rightarrow (n-1)$ plus, along with any plusses contributed by $I_n^V$.
+  \item $I_{n-3}^W$ contributes the same plusses as $I_{n-3}^V$, except that the plus in the $n-3$ column is shifted one square left into the $n-2$ column.
+  \item In the Le diagram of $V$, $I_{n-2}^{V}$ contributes an $(n-5)\rightarrow (n-2)$ plus and no other term in the Grassmann necklace of $V$ gives a plus in this column.
+$I_{n-2}^W$ does not contribute this $+$ but yields the $(n-5)\rightarrow (n-1)$ plus from point (1) instead.
+  \item All other plusses from $I_{n-2}^{V}$ and all plusses from $I_{n-1}^V$ were already contributed by $I_{n-3}^V$, so they yield no new information.
+  \item No element of the Grassmann necklace of $V$ contributes a $(n-5)\rightarrow (n-1)$ plus.
+  \end{enumerate} 
+\end{lem}
+
+\begin{proof}
+  By Lemma~\ref{lem I} we have $I_{n-2}^{W}= (I_{n}^{V} \setminus \{n-5\})\cup \{n-1,n-2\}$ and $I_1^W = I_1^V\cup \{n-3\}$.
+We are necessarily in the case where $W$ admits a propagator $q$ (the right hand case of Figure~\ref{fig special p}) and we can see from the location of $q$ that $n-2\not\in I_{n-3}^{V}$ and that $n-5$ is the index of the lowest vertical edge in $\mathcal{B}$.
+Thus this section of the Gramann necklace of $V$ looks like
+
+  \begin{equation}\label{eq necklace}
+  I_{n-3}^{V} \xrightarrow[\substack{n-3\text{ out}\\n-2\text{ in}}]{} I_{n-2}^{V} \xrightarrow[\substack{n-2\text{ out}\\n-5\text{ in}}]{} I_{n-1}^{V} \xrightarrow[\substack{n-1\text{ out}\\\text{something in}}]{} I_{n}^{V}  \xrightarrow[\substack{n \text{ out}\\\text{something in}}]{\text{\ no change, {\em or}\ }} I_1^{V}
+  \end{equation}
+  where the first ``something'' is either $n$ or an element of $I_1^{V}$, and the second ``something'' (if it exists) is an element of $I_1^{V}$. If $n\not\in I_n^V$ then $I_n^V = I_1^V$.
+
+  Using this information we can determine the symmetric difference of $I_{n-2}^{V}$ and $I_1^{V}$, which has size $\leq 3$ by the definition of a Grassmann necklace.
+We have $n-1, n-2 \in I_{n-2}^{V} \setminus I_1^V$ for certain, and the third element (if it exists) must be $n$.
+On the other hand we have $n-5 \in I_1^{V} \setminus I_{n-2}^V$, along with at least one and at most two other elements.
+If there is one such element call it $a$.
+If there are two call them $a$ and $b$ with $a>b$.
+
+  This means that the plusses in the Le diagram of $V$ coming from $I_{n-2}^{V}$ are as in the first part of Figure~\ref{fig messy}.
+Stepping to $I_{n-1}^{V}$ simply removes the $(n-5)\rightarrow (n-2)$ path (second part of Figure~\ref{fig messy}), so $I_{n-1}^V$ contributes no new information about the Le diagram of $V$.
+
+  \begin{figure}
+    \includegraphics{messy}
+    \caption{Plusses coming from $I_{n-2}^{V}$ (left) and  $I_{n-1}^{V}$ (right), in the case where $n-1, n-2\in I_{n-2}^{V}$.
+The blue lines are the non-intersecting paths defining the position of the plusses.
+The dashed blue lines may or may not appear, but if one appears then they both do.}\label{fig messy}
+  \end{figure}
+
+  \note{Remove the $I_n^V$ diagrams}
+
+  %Stepping to $I_{n}^{V}$, $n-1$ is removed and either $n$ is put in if it was not there before, or one of $a$ or $b$ is put in and hence is no longer available as the starting point for a path.
+This gives two possible configurations illustrated in the bottom two parts of Figure~\ref{fig messy}.
+
+  With this information in hand, we can now tackle the points in the statement of the lemma. We know that 
+  \[I_{n-2}^{W}  = (I_{n}^{V} - \{n-5\})\cup \{n-1,n-2\}, \quad n-5 \in I_1^W, \quad n-3\not\in I_{n-2}^W,\]
+ and so the paths for building plusses from $I_{n-2}^{W}$ start at
+ \[I_1^W \setminus I_{n-2}^W = \{n-3,n-5\} \cup (I_1^V \setminus I_n^V)\]
+ and end at
+ \[I_{n-2}^W \setminus I_1^W = \{n-2,n-1\}\cup(I_n^V \setminus I_1^V).\]
+This means that $I_{n-2}^W$ contributes plusses as in Figure~\ref{fig messyD}, which proves point (1) and most of point (3).
+From equation \eqref{eq necklace} we see that $n-2$ appears only in $I_{n-2}^V$, so no other Grassmann necklace term for $V$ can contribute a plus in the $n-2$ column; this completes the proof of item (3).
+
+  \begin{figure}
+     \includegraphics{messyD}
+    \caption{Plusses coming from $I_{n-2}^{W}$.}\label{fig messyD}
+  \end{figure}
+
+\note{Modify this figure to include the case where there's no plus for column $n$.}
+
+Now consider $I_{n-3}^{V}$.
+By \eqref{eq necklace} $I_{n-3}^{V}$ contributes almost the same plusses as $I_{n-2}^{V}$: the only difference is that it contributes an $(n-5)\rightarrow (n-3)$ plus in place of the $(n-5)\rightarrow (n-2)$ plus.
+Since we must have $n-3\in I_{n-3}^{V}$ (because the propagator $q$ exists in $V$), it follows from Lemma~\ref{lem I} that $I_{n-3}^{W} = I_{n-3}^{V}\cup\{n-2\}$.
+Thus the paths for $I^{W}_{n-3}$ are the same as those for $I^{V}_{n-3}$ except that the path that did go to $n-3$ now goes to $n-2$.
+This cannot conflict with another path since \eqref{eq necklace} shows that $n-2$ only appears in $I_{n-2}^{V}$ among the necklace elements of $V$.
+
+This proves point (2), and combined with the observation above that $I_{n-1}^V$ contributes no new plusses compared to $I_{n-2}^V$, we also obtain item (4).
+
+  Finally, if the Le diagram of $V$ did admit a $(n-5)\rightarrow (n-1)$ plus, it could only have been contributed by a necklace term that doesn't contain $n-5$.
+By equation \eqref{eq necklace} the only terms that could have this property are $I_{n-2}^{V}$, $I_{n-3}^{V}$, and $I_{n-4}^{V}$, and the analysis above shows that $I_{n-2}^V$ and $I_{n-3}^V$ do not contribute a plus in this position.
+
+  Recall that $n-5$ is the largest row index in the Le diagram of $V$, and $n-5 \in I_1^V \setminus I_{n-4}^V$ so $I_{n-4}^V$ does contribute a path starting at $n-5$.
+Since $n-4 \in I_{n-4}^V$ by the location of the propagator $q$, we must also have a path ending at $n-4$.
+Since the paths cannot cross, this implies that $I_{n-4}^V$ must contribute a $(n-5) \rightarrow (n-4)$ plus, and hence cannot contribute a $(n-5)\rightarrow (n-1)$ plus.
+This proves point (5) and completes the proof of the lemma.
 \end{proof}

### 2019-03-25 GWLDCI.tex
split into two papers

--- 2019-03-21 General WLD combinatorics.tex
@@
 
-\title{Combinatorics of the geometry of Wilson loop diagrams}
+\title{Combinatorics of the geometry of Wilson loop diagrams I: equivalence classes via matroids and polytopes}
 \author{Susama Agarwala, Si\^an Fryer, and Karen Yeats}
@@
 
-This paper studies the combinatorics of Wilson Loop Diagrams.
-\section{Wilson Loop diagrams}\label{section background}
-
-What are Wilson loop diagrams and their integrals.
+\section{Introduction}
+
+***Some general intro to WLDs perhaps similar to the end of p2 and top of p3 of \cite{wilsonloop}.
+For this paper we don't need the integral, so for the moment they are not defined below, but for motivation may want to be glossed a bit here ***
+
+Furthermore, in \cite{wilsonloop}, Agarwala and Amat show that Wilson loop diagrams can be interpreted as positroids, a certain well behaved class of realizable matroids.
+This opens up the study of Wilson loop diagrams to techniques from geometry and combinatorics.
+We pursue this direction here and in the companion paper ***cite the other paper***.
+
+In the present paper we focus on the combinatorics and geometry of an equivalence relation on Wilson loop diagrams.
+The main results are that Wilson loop diagrams are equivalent if and only if they define the same matroid, that the equivalence can be rephrased in terms of retriangulations in polygon dissections, and from there that the sizes of the equivalence classes can be enumerated, and the set of equivalence classes is related to directions in associahedra.
+
+\subsection{Roadmap}
+
+We proceed in Section~\ref{section overall background} with the required definitions for Wilson loop diagrams (subsection~\ref{section WLD background}) and matroids (subsection~\ref{sec matroid background}.
+Wilson loop diagrams will be said to be admissible when they correspond to the physical situation of ***something***, or mathematically according to Definition~\ref{admisdfn}.
+With this, the key definition is Definition~\ref{equivdfn} giving the equivalence relation on admissible Wilson loop diagrams.
+The connection to matroids is stated precisely in Theorem \ref{thm WLD defines matroid}.
+
+The main result of Section~\ref{sec equiv} is Theorem~\ref{same matroid iff equiv}.
+To arrive at those results, we first show how certain subdiagrams, called exact subdiagrams, relate to triangulations in polygons in subsection~\ref{sec: polygon partitions}, and then consider the matroidal properties of the exact subdiagrams in subsection~\ref{sec: exact diagram matroidal props}.
+Specifically, a subdiagram of a Wilson loop diagrams $W$ defines a uniform matroid if and only if the subdiagram is exact (Theorem \ref{exactuniformthm}), and this uniform matroid is the restriction of the dual matriod of $W$ restricted to the exact subdiagram (Remark \ref{remark exact dual restiction}).
+The main result of the section, Theorem~\ref{same matroid iff equiv}, then appears in subsection~\ref{sec: matroids and equivalence}.
+A consequence of this is the formula for the size of an equivalence class given in Corollary~\ref{number of equiv diagrams}.
+
+The next natural question, then is the number of inequivalent diagrams under this equivalence relation.
+The main result of Section~\ref{sec associahedron} is to show that the set of admissible Wilson loop diagrams up to equivalence is in bijection with the set of faces in the associahedron up to paralellness.
+Towards this result we go over some relevant background on polytopes in subsection~\ref{sec polytope background}, and then give the main result in subsection~\ref{sec associahedron results} in the form of two propositions, Propositions~\ref{prop easy way} and~\ref{prop hard way}.
+
+\section{Background}\label{section overall background}
+
+\subsection{Wilson Loop diagrams}\label{section WLD background}
+
+%What are Wilson loop diagrams and their integrals.
 
@@
 
-Generally speaking, the propagators are undirected, so $p = (i,j) = (j,i)$.
-In order to fix a convention, we write $p = (i,j)$ with  $i +1 < j$ relative to the first vertex.
-However, at times (section \ref{sec:propagator configs}), we consider directed propagators, where $p= (i,j)$ denotes a particular propagator flowing in one direction, while $p= (j,i)$ denotes the \emph{same} propagators flowing in the opposite direction.
-\sanote{Addendum 1}
+Propagators are undirected, so $p = (i,j) = (j,i)$. In order to fix a convention, we write $p = (i,j)$ with  $i +1 < j$ relative to the first vertex.
 
@@
 
-These $C(W)$ parametrize a subspace of $\Gr(k, n)$ as shown in \cite{wilsonloops}, call it $\Sigma(W)$.
-The Wilson loop diagrams also define a volume form on $\Sigma(W)$: \bas \Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V_{p_r}} \textrm{d}c_{p_r}}{R(W)} \;.
+These $C(W)$ parametrize a subspace of $\Gr(k, n)$ as shown in \cite{wilsonloop}, call it $\Sigma(W)$.
+
+%The Wilson loop diagrams also define a volume form on $\Sigma(W)$: \bas \Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V_{p_r}} \textrm{d}c_{p_r}}{R(W)} \;.
 \eas The denominator $R(W)$ is a polynomial defined by $2 \times 2$ and $1 \times 1$ minors of $C(W)$ as defined below.
-
-\begin{dfn}\label{def R(W)}
-For $W = (\cP, [n])$, $R(W) = \prod_{e=1}^n R_e$, with $R_e$ defined by the propagators ending on it.
+%
+%\begin{dfn}\label{def R(W)}
+%For $W = (\cP, [n])$, $R(W) = \prod_{e=1}^n R_e$, with $R_e$ defined by the propagators ending on it.
 For any edge $e$ of $W$, order the propagators incident on $e$ as $\{p_1 \ldots p_r\}$, ordered such that $p_1$ is closest to the vertex $e$, $p_r$ closest to $e+1$, and $p_i$ is closer to $e$ than $p_{i+1}$.
 Then \bas R_e =  c_{p_1,e+1} \prod_{j= 1}^{r-1} \left((c_{p_j,e} c_{p_{j+1},e+1} - c_{p_{j+1},e} c_{p_{j},e+1} ) \right) c_{p_s,e}\;.\eas Note that in this notation, if $r = 1$, $R_e = c_{p,e} c_{p,e+1}$.
-\end{dfn}
-
-\section{Equivalence classes of Wilson loop diagrams}
-
-In \cite{wilsonloop}, Agarwala and Amat show that Wilson loop diagrams can be interpreted as positroids, a certain well behaved class of realizable matroids (this correspondence is stated precisely in Theorem \ref{thm WLD defines matroid} below).
-This opens up the study of Wilson loop diagrams to techniques from geometry and combinatorics.
-In particular we examine the partial result shown in \cite{wilsonloop}, that shows that equivalent Wilson Loop Diagrams define the same matroid.
-In section 2.4, we make the relationship between Wilson Loop diagrams and matroids explicit.
-We count the size of each equivalence class, and enumerate the {\color{violet} the number of said classes}.
-We also show that two Wilson Loop diagrams map to the same matroid if and only if they are equivalent.
-
-In subsection \ref{sec matroid background}, we discuss a few matroidal facts about Wilson loop diagrams.
-In section \ref{sec: polygon partitions}, we show that there is a one to one correspondence between exact subdiagrams of Wilson loop diagrams and triangulated pieces of the corresponding polygon partion.
-In section \ref{sec: exact diagram matroidal props}, we prove some matroidal properties of exact subdiagrams.
-We show that a subdiagram of $W$ defines a uniform matroid if and only if the subdiagram is exact (Theorem \ref{exactuniformthm}).
-Furthermore, this uniform matroid is the restriction of the dual matriod of $W$ restricted to the exact subdiagram (Remark \ref{remark exact dual restiction}).
-The main result of section \ref{sec: matroids and equivalence} shows that that two admissible Wilson loop diagrams define the same matroid if and only if they are equivalent (Theorem \ref{same matroid iff equiv}).
-We obtain a formula for the number of admissible Wilson loop diagrams in each equivalence class (Corollary \ref{number of equiv diagrams}) {\color{violet}as well as the number of equivalence classes}.
-In this way, we give a comple characterization of the relationship between Wilson Loop diagrams and their associated matroids.
+%\end{dfn}
 
@@
 
-We first give a quick summary of the matroid terminology that we will need; it is not intended as a comprehensive introduction to matroids and the interested reader is referred to [ref][find a good matroid reference].
+We first give a quick summary of the matroid terminology that we will need; it is not intended as a comprehensive introduction to matroids and the interested reader is referred to [ref][find a good matroid reference].\note{Oxley is always my go to reference for matroids, but perhaps it has the wrong focus for you?}
 
@@
 
-\subsection{Polygon partitions of Wilson loop diagrams\label{sec: polygon partitions}}
+\section{Matroids, triangulations, and equivalence classes of Wilson loop diagrams}\label{sec equiv}
+
+\subsection{Polygon dissections of Wilson loop diagrams\label{sec: polygon partitions}}
 
 The equivalence relation on Wilson loop diagrams is defined in terms of exact subdiagrams; thus in order to understand the equivalence, we need a way to extract and compare exact subdiagrams.
-We do this via the notion of a polygon partition of $W$.
+We do this via the notion of a polygon dissection of $W$.
 
 \begin{dfn}
-  Let $W = (\cP, [n])$ be an admissible Wilson loop diagram.  The \emph{polygon partition} associated to $W$, denoted $\tau(W)$, is defined as follows.
+  Let $W = (\cP, [n])$ be an admissible Wilson loop diagram.  The \emph{polygon dissection} associated to $W$, denoted $\tau(W)$, is defined as follows.
   \begin{itemize}
@@
 \end{dfn}
+
+\emph{Polygon dissection} is a common term in combinatorics for a decomposition of a convect polygon into smaller polygons by means of noncrossing diagonals, see \cite{PSpolygon}.
+Each $\tau(W)$ is such an object.
 
@@
 
-\begin{comment}
-\hlfix{For an admissible $W$ no propagators cross and so no chord edges of $\tau(W)$ cross.  Thus, in graph theoretic language, we can view $\tau(W)$ as a planar embedding of a
-graph with no cut vertices, where all vertices lie on the infinite face, along with a distinguished start vertex and direction around the infinite face.
-From this viewpoint the polygon of $tau(W)$ is the boundary of the infinite face.}{I've smushed this together a bit in the prev.
-lem.
-Tell me if I've missed anything.
-Its a lemma for emphasis, not difficulty}
-\end{comment}
-
 \begin{eg}\label{WLDtopolygonpartition}
-In this example we return to two of the Wilson loop diagrams in Example \ref{eg:equivdiags}. We can pair diagrams with their polygon partitions as follows:
+In this example we return to two of the Wilson loop diagrams in Example \ref{eg:equivdiags}. We can pair diagrams with their polygon dissections as follows:
 \bas W_1 = \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
@@
 \begin{dfn}
-  Let $W$ be an admissible Wilson loop diagram and $\tau(W)$ its polygon partition.
+  Let $W$ be an admissible Wilson loop diagram and $\tau(W)$ its polygon dissection.
 A \emph{triangulated piece} of $\tau(W)$ is a 2-connected subgraph of $\tau(W)$ which is a triangulation.
@@
 \begin{dfn}
- A {\em decomposition} of a polygon partition $\tau(W)$ is a set of 2-connected induced subgraphs of $\tau(W)$ which partition the edges of $\tau(W)$.  
-\end{dfn}
-
-\begin{eg} \label{eg: unique decomposition} For the Wilson loop diagrams and polygon partitions in Example \ref{WLDtopolygonpartition}, the vertex sets $\{1, 2, 3,4\}$ and $\{5, 6, 7, 8\}$ give maximal triangulated pieces for both $\tau(W_1)$ and $\tau(W_3)$.
-The vertex set $\{4,5, 8, 1\}$ is not a triangulation in either polygon partition.
+ A {\em decomposition} of a polygon dissection $\tau(W)$ is a set of 2-connected induced subgraphs of $\tau(W)$ which partition the edges of $\tau(W)$.  
+\end{dfn}
+
+\begin{eg} \label{eg: unique decomposition} For the Wilson loop diagrams and polygon dissections in Example \ref{WLDtopolygonpartition}, the vertex sets $\{1, 2, 3,4\}$ and $\{5, 6, 7, 8\}$ give maximal triangulated pieces for both $\tau(W_1)$ and $\tau(W_3)$.
+The vertex set $\{4,5, 8, 1\}$ is not a triangulation in either polygon dissection.
 \end{eg}
@@
 \begin{lem} \label{decompositionlem}
-  For $W$ an admissible Wilson loop diagram, the polygon partition $\tau(W)$ has a unique decomposition into maximal triangulated pieces, and edges in the polygon of $\tau(W)$.
+  For $W$ an admissible Wilson loop diagram, the polygon dissection $\tau(W)$ has a unique decomposition into maximal triangulated pieces, and edges in the polygon of $\tau(W)$.
 \end{lem}
@@
 \begin{lem}\label{lem triang to exact}
-  Let $W$ be an admissible Wilson loop diagram and $\tau(W)$ its polygon partition.
+  Let $W$ be an admissible Wilson loop diagram and $\tau(W)$ its polygon dissection.
 The triangulated pieces of $\tau(W)$ correspond to the exact subdiagrams of $W$ using the correspondence described above.
@@
 Now we are ready to prove the main results of this section, namely that two Wilson loop diagrams define the same matroid if and only if they are equivalent (Theorem \ref{same matroid iff equiv}).
-We also {\color{violet}count the number of equivalence classes amongst Wilon Loop diagrams with $n$ vertices and $k$ propagators and} give a formula for the number of Wilson loop diagrams in a given equivalence class (Corollary \ref{number of equiv diagrams}), completing the characterization of the correspondence between Wilson Loop diagrams and matroids starting in \cite{wilsonloop}.
+We also
+give a formula for the number of Wilson loop diagrams in a given equivalence class (Corollary \ref{number of equiv diagrams}), completing the characterization of the correspondence between Wilson Loop diagrams and matroids starting in \cite{wilsonloop}.
 
@@
 Since there is a unique way to decompose $W$ into maximal exact subdiagrams, it is logical to ask how many diagrams there are in an equivalence class.
-It is a classical fact the the number of triangulations of an $n$-gon is the $n-2$ Catalan number, namely $\frac{1}{n-1}\binom{2(n-2)}{n-2}$.
+It is a classical fact (see for instance Chapter 6 of \cite{Stanley}) that the number of triangulations of a convex $n$-gon is the $n-2$ Catalan number, namely $\frac{1}{n-1}\binom{2(n-2)}{n-2}$.
 Thus we can count the number of equivalent diagrams.
-[CITATION?]
 
@@
 Corollary \ref{number of equiv diagrams} enumerates the fibres of the map from Wilson Loop diagrams to positroids.
-{\color{violet} By counting the number of equivalence classes (Theorem \ref{}), we enumerate the number of positroids defined by Wilson Loop diagrams.
-In section \ref{}, Theorem \ref{}, we show that each Wilson Loop diagram with $n$ vertices and $k$ propagators define a positroid cell of dimension $3k$.
-Comparing the result of Theorem \ref{} to the number of positroid cells of a particular dimension in $\Grtnn(n, k)$, [CITE AND FIND FORMULA HERE], we see that \emph{Wilson loop diagrams do not map onto all positroids of the correct dimension.}}
-
-\begin{comment}
-\subsection{Counting exact subdiagrams}
+The obvious next question would be to enumerate the number of equivlence classes.
+We do not obtain a formula for this, but do obtain an alternate characterization of the equvalence classes which is the subject of the next section.
+
+\section{Associahedra and inequivalent Wilson loop diagrams}\label{sec associahedron}
+
+The connection between admissible Wilson loop diagrams and polytope dissections suggests a connection to associahedra. First we need some background.
+
+\subsection{Polytope background}\label{sec polytope background}
+
+A \emph{polytope} can equivalently be defined as the convex hull of a finite set of points in some $\mathbb{R}^d$ or as the intersection of finitely many closed half spaces in $\mathbb{R}^d$ with the additional property that this intersection is bounded in the sense of not containing any ray (see chapter 0 of \cite{Ziegler}).
+
+A \emph{face} of a polytope is the intersection of the polytope with any hyperplane for which the entire polytope is in one of the closed half-spaces defined by the hyperplane.
+The polytope itself is also considered a face (in the case that that polytope is of full dimension, this definition can be unified by considering linear equalities (including the trivial one) in place of hyperplanes and the corresponding linear inequalities in place of the half-spaces defined by the hyperplane, see chapter 2 of \cite{Ziegler}).
+Two faces are \emph{parallel} if one can be mapped to the other by a translation in $\mathbb{R}^d$.
+In particular parallel faces must be of the same dimension and any pair of vertices are parallel.
+
+There are many important polytopes in combinatorics, including, of primary importance to us, the associahedron.
+
+Two polytopes are \emph{combinatorially equivalent} if there is a bijection between their faces which preserves inclusion of faces.
+Often in combinatorics one is primarily interested in the combinatorial equivalence classes, and common names, including the associahedron, refer to these equivalence classes.
+A particular polytope in the class is then known as a \emph{realization}.
+
+Associahedra can also be viewed in terms of polygon dissections.
+Let's fix $n$ and consider dissections of a convex $n$-gon.
+The $n-1$ asociahedron can be given in terms of the dissections of this $n$-gon; the vertices of the associahedron are the triangulations of the $n$-gon while the dimension $k$ faces are the dissections which are $k$ diagonals away from being a triangulation.
+One face is included in another if the first dissection is a refinement of the second.
+
+It turns out that this defines a class of combinatorially equivalent polytopes, which can be proved by giving a realization.
+There are many interesting realizations of the associahedron \cite{}; the following will be the one which we will use.
 
 \begin{dfn}
-  Say two admissible Wilson loop diagrams $W_1$ and $W_2$ are \emph{triangulation-equivalent} if there is a bijection $\alpha$ between the set of triangulated pieces in the decomposition of $\tau(W_1)$ and the set of triangulated pieces in the decomposition of $\tau(W_2)$, where $t$ and $\alpha(t)$ have the same vertex set for all triangulated pieces $t$ of $\tau(W_1)$.
-\end{dfn}
-
-***draw an example***
-
-\begin{thm}
-  Two admissible Wilson loop diagrams have the same matroid iff they are triangulation equivalent
-\end{thm}
-
-Again do I want matroid or positroid in this theorem?
-
-\begin{proof}
-  By Lemma~\ref{lem triang to exact} two admissible Wilson loop diagrams are triangulation equivalent iff their decompositions into maximal connected exact subdiagrams have matching supports, that is if they are equivalent.
-  Theorem~\ref{thm orig equiv} then gives the result.
-\end{proof}
-
-\end{comment}
-
-\section{Geometry of Wilson Loop diagram}\label{sec GN algorithm}
-
-Since Wilson loop diagrams correspond to positroids, it is natural to study the subspace of $\Gr(|\cP|, n)$ they define.
-
-[words about what's in this section]
-
-Throughout this section, $W = (\cP,[n])$ is an admissible Wilson loop diagram with $k$ propagators.
-
-\subsection{Background}\label{sec:positroid background}
-
-[positroids]
-
-Let $\binom{[n]}{k}$ be the set of all $k$-subsets of the cyclically ordered set $[n]$.  For each $j \in [n]$, we can define a total order $\leq_j$ on the interval $[n]$ by
-\[ j <_j j+1 <_j \dots <_j n <_j 1 \dots <_j j-1\;.\]
-This in turn induces a total order on $\binom{[n]}{k}$, namely the lexicographic order with respect to $<_j$.
-It also induces a separate partial order $\gale{j}$ on $\binom{[n]}{k}$ (the {\bf Gale order} \cite{Gale}), which is defined as follows: for
-\[A = \{a_1 <_j a_2 <_j \dots <_j a_k\} \text{ and } B = \{b_1 <_j b_2 <_j \dots <_j b_k\} \in \binom{[n]}{k},\] we define
-\[A \gale{j} B \text{ if and only if } a_r \leq_j b_r \text{ for all }1 \leq r \leq k.\]
-For example, in $\binom{[6]}{3}$ we have $\{2,5,6\}\gale{2} \{2,6,1\}$ but $\{2,5,6\}\not\gale{2}\{3,4,6\}$.
-
-\begin{dfn}\label{def:grassmann necklace}
-A {\bf Grassmann necklace} of type $(k,n)$ is a sequence $(I_1, \dots, I_n)$ of $n$ sets $I_i \in \binom{[n]}{k}$ such that for each $i \in [n]$:
-\begin{itemize}
-\item if $i \in I_i$, then $I_{i+1} = \big(I_i \backslash \{i\}\big) \cup \{j\}$ for some $j \in[n]$.
-\item if $i \not\in I_i$, then $I_{i+1} = I_i$.
-\end{itemize}
-By convention, we set $I_{n+1} = I_1$.
-\end{dfn}
-
-By \cite[Theorem 17.1]{Postnikov}, the Grassmann necklaces of type $(k,n)$ are in 1-1 correspondence with the positroid cells in $\Gr(k,n)$.
-This correspondence is given explicitly in \cite[Theorem 8]{Oh}: if $(I_1, \dots, I_n)$ is the Grassmann necklace associated to a positroid $M = ([n],\cB)$, then the bases of $M$ are exactly
-\[\cB = \left\{J \in \binom{[n]}{k}\ :\ I_i \gale{i} J \ \forall i \in [n]\right\}.\]
-
-\begin{dfn}\label{def:le diagram}
-A {\bf Le diagram} is a Young diagram in which every square contains either a $+$ or a $0$, subject to the rule that if a square contains a $0$ then either all squares to its left (in the same row) must also contain a $0$, or all squares above it (in the same column) must also contain a $0$, or both.
-\end{dfn}
-
-By [ref], the set of all Le diagrams that fit within a $k\times(n-k)$ rectangle is in 1-1 correspondence with the positroid cells of $\Gr(k,n)$.
-The dimension of a positroid cell is equal to the number of $+$ squares in its Le diagram [ref].
-
-The rows and columns of a Le diagram are labelled as follows: given a Le diagram fitting inside a $k\times (n-k)$ box, arrange the numbers $1,2, \dots, n$ along its southeast border, starting from the top-right corner.
-See Figure \ref{fig:row column numbering} for examples.
-
-\begin{figure}[h!]
-\[\begin{tikzpicture}[baseline=(current bounding box.east),scale=0.75]
-\draw (1,0) grid (2,3);
-\draw (2,1) grid (4,3);
-\draw (4,2) grid (5,3);
-\draw[dotted] (2,0) -- (5,0) -- (5,2);
-
-\node at (5.15,2.5) {\footnotesize$1$};
-\node at (4.5,1.85) {\footnotesize$2$};
-\node at (4.15,1.5) {\footnotesize$3$};
-\node at (3.5,0.85) {\footnotesize$4$};
-\node at (2.5,0.85) {\footnotesize$5$};
-\node at (2.15,0.5) {\footnotesize$6$};
-\node at (1.5,-0.15) {\footnotesize$7$};
-%\node at (0.5,-0.15) {\footnotesize$8$};
-\end{tikzpicture}
-\qquad \qquad
-\begin{tikzpicture}[baseline=(current bounding box.east),scale=0.75]
-\draw (1,0) grid (2,3);
-\draw (2,1) grid (4,3);
-\draw (4,2) grid (5,3);
-\draw[dotted] (2,0) -- (6,0) -- (6,3) -- (5,3);
-
-\node at (5.5,2.85) {\footnotesize$1$};
-\node at (5.15,2.5) {\footnotesize$2$};
-\node at (4.5,1.85) {\footnotesize$3$};
-\node at (4.15,1.5) {\footnotesize$4$};
-\node at (3.5,0.85) {\footnotesize$5$};
-\node at (2.5,0.85) {\footnotesize$6$};
-\node at (2.15,0.5) {\footnotesize$7$};
-\node at (1.5,-0.15) {\footnotesize$8$};
-%\node at (0.5,-0.15) {\footnotesize$9$};
-\end{tikzpicture}
+  Let $x_1, \ldots, x_n$ define a convex $n$-gon.
+Let $T$ be the set of triangulations of this $n$-gon.
+For each $t\in T$ define $s_t$ to be the point in $\mathbb{R}^n$ whose $i$th coordinate is the sum of the areas of all triangles of $t$ which are incident to $x_i$.
+Let $A_n$ be the convex hull of the $s_t$.
+\end{dfn}
+This is the construction of the secondary polytope (so $A_n$ is the secondary polytope of $x_1, \ldots, x_n$), see \cite{Ziegler} Definition 9.9.
+In general the $x_1, \ldots, x_n$ may be any points in any $\mathbb{R}^d$.
+Triangulations in the more general context are a decomposition into simplices and the areas of the triangles is replaced by the volume of the simplices.
+
+$A_n$ defined in this way is a realization of the $n-1$ associahedron (\cite{Ziegler}, Example 9.11).
+Note that we get a realization for any convex $n$-gon, but these realizations are all equally good for our purposes, and so we fix $x_1, \ldots, x_n$ from now on.
+
+\subsection{Non-parallel faces in the associahedron and inequivalent Wilson loop diagrams}\label{sec associahedron results}
+
+With the choice of $n$-gon and hence of $A_n$ fixed, view the $\tau$ map as taking values in the set of dissections of this particular convex $n$-gon, and so each weakly admissible Wilson loop diagram is associated via $\tau$ with a face (in some dimension) of $A_n$.
+
+Note that Wilson loop diagrams which are weakly admissible but not admissible have $\tau$ graphs which are triangulations, hence dimension 0 faces (vertices) in $A_n$.
+All of these are equivalent in the sense that they are only retriangulations away from each other.
+It will be convenient in what follows, to include these diagrams.
+The next two propositions would be identical in the case of admissible instead of weakly admissible, while the corollary could be changed to involve admissible diagrams only by subtracting one from the number of non parallel faces in order to account for the missing dimension 0 faces.
+
+\begin{prop}\label{prop easy way}
+  If two weakly admissible Wilson loop diagrams are equivalent then their faces in $A_n$ are parallel.
+\end{prop}
+
+\begin{proof}
+  Let $W$ and $X$ be equivalent.  From results in the paper we're working on we know that $\tau(W)$ and $\tau(X)$ differ from each other only by retriangulations of their triangulated pieces.
+
+  All edges of $A_n$ are polygon dissections which are only one diagonal away from being triangulations.
+Such dissections consist of triangles and exactly one quadrilateral.
+Consider the edges of $A_n$ bounding the faces corresponding to $\tau(W)$ and $\tau(X)$.
+These edges have their one quadrilateral within the nontriangulated parts of $\tau(W)$ or $\tau(X)$, but these nontriangulated parts are the same in $\tau(W)$ and $\tau(X)$, so we get a bijection between the edges bounding the face of $\tau(W)$ and the edges bounding the face of $\tau(X)$ which matches edges with the same quadrilateral.
+
+  Consider now an edge whose quadrilateral has corners $x_i$, $x_j$, $x_k$, and $x_l$ in that order.
+Let $t_1$ and $t_2$ be the triangulations corresponding to the two ends of the edge where $t_1$ has a diagonal from $x_j$ to $x_l$ and $t_2$ has a diagonal from $x_i$ to $x_k$.
+From the definition of $A_n$ we see that $s_{t_1}$ and $s_{t_2}$ only differ at coordinates $i$, $j$, $k$, and $l$, and all of the triangles incident to any of these vertices other than the one coming from triangulating $x_i, x_j, x_k, x_l$ are the same in both $t_1$ and $t_2$.
+Let $a$ be the area of the quadrilateral and let $a(i,j,k)$ be the area of the triangle with corners $x_i$, $x_j$ and $x_k$, and similarly for other indices then $s_{t_1}$ on coordinates $i$, $j$, $k$, $l$ is $(a(i,j,l) + b_i, a+b_j, a(k,l,j)+b_k, a+b_l)$ and $s_{t_2}$ on these coordinates is $(a + b_i, a(j,k,i)+b_j, a+b_k, a(l,i,k)+b_l$, where the $b_i$ are the sums of the areas of the relevant triangles which are common to both triangulations.
+Thus a vector parallel to this edge is the vector which is $(a(i,j,l) - a, a-a(j,k,i), a(k,l,j)-a, a-a(l,i,k)) = (-a(j,k,l), a(i,k,l), -a(i,j,l), a(i,j,k))$ on $i$, $j$, $k$, $l$ and $0$ in all other coordinates.
+
+  Returning to $\tau(W)$ and $\tau(X)$ since the direction vector of an edge in $A_n$ depends only on its quadrilateral and the bijection between the edges bounding $\tau(W)$ and the edges bounding $\tau(X)$ preserves the quadrilateral, we have the same direction vectors bounding $\tau(W)$ as $\tau(X)$.
+Furthermore, the bijection also maintains the relative configuration of the edges and so $\tau(W)$ and $\tau(X)$ are parallel.
+\end{proof}
+
+The following lemma is useful for the second proposition.
+
+\begin{lem}\label{lem good quads}
+  Let $D_1$ and $D_2$ be two dissections of the convex polygon defined by the vertices $x_1, \ldots, x_n$.
+Suppose the vertices incident to at least one non-triangle face are the same in both dissections, but that the $D_1$ and $D_2$ do not have the same set of non-triangle faces.
+Then there are four vertices $x_i$, $x_j$, $x_k$, $x_l$ such that in one of $D_1$ or $D_2$ all four vertices are on the same non-triangle face while in the other there is a diagonal of the dissection such that there is one side of the diagonal with exactly one of $\{x_i, x_j, x_k, x_l\}$ (so the others are end points of this diagonal or strictly on the other side).
+\end{lem}
+
+\note{I wonder if either of you see a shorter or more conceptual way to prove this.}
+
+\begin{proof}
+  Since $D_1$ and $D_2$ do not have the same set of non-triangle faces, there must be some diagonal $d$ of $D_1$ that crosses through a non-triangle face $f$ of $D_2$.
+If that face of $D_2$ has degree at least 5 then it must contain four vertices as in the statement.
+
+  Suppose this never occurs.
+Then all the non-triangle faces of $D_2$ which are crossed by a diagonal of $D_1$ must be quadrilaterals and likewise for $D_1$.
+This means that any non-triangle and non-quadrilateral faces must be common between $D_1$ and $D_2$.
+These common faces are irrelevant for the statement, and so by triangulating any common non-triangle faces, we may assume that $D_1$ and $D_2$ have only quadrilateral and triangle faces.
+
+  Assume for a contradiction that no quadrilateral as in the statement exists, and let $d$ and $f$ be as above.
+Then $f$ must have two vertices strictly on each side of $d$, say $x_i$ and $x_j$ on one side and $x_k$, $x_l$ on the other side (and in that order).
+Consider the face incident to $d$ on the $x_i, x_j$ side of $d$.
+Suppose this face is a triangle, then its other vertex cannot be in $[x_i, x_j]$ as otherwise taking one of the other edges of the triangles would give a configuration as in the statement.
+Suppose now that this face is a quadrilateral, again no other vertex of this face can be in $(x_i, x_j)$ as otherwise again taking one of the other edges of the face as $d$ we'd get a quadrilateral as in the statement, the same holds if one of the other vertices of the face is $x_i$ or $x_j$ but the other is not.
+If the two other vertices of the face are $x_i$ and $x_j$, then we also get a configuration as in the statement but now with the four vertices being the two ende of $q$ and $x_i, x_j$ and with one of the edges of $f$ as the diagonal.
+Thus we can conclude that none of the vertices of this face are in $[x_i, x_j]$.
+Also if the face has three vertices on one side of $f$ and one on the other then we get a quadrilateral as in the statement again with this face giving the four vertices and the diagonal a side of $f$.
+, so the face is either a triangle with its third vertex of the triangle must be in $(x_j,x_k)$ or in $(x_l,x_i)$ or a quadrilateral with one more vertex in $(x_j, x_k)$ and one more vertex in $(x_l, x_i)$.
+Taking all this together, whether the face is a triangle or a quadrilateral, replacing $d$ with one of the other edges of the face we get a new diagonal $d'$ which also separates $f$ into $x_i, x_j$ and $x_k, x_l$ but is strictly closer to $[x_i, x_j]$ than $d$ was.
+The same argument holds for $d'$, but the polygon is finite, so this process cannot go on indefinitely, contradicting that no quadtilateral as in the statement exists.
+\end{proof}
+
+\begin{prop}\label{prop hard way}
+  If two weakly admissible Wilson loop diagrams are not equivalent then their faces in $A_n$ are not parallel
+\end{prop}
+
+\begin{proof}
+  Let $W$ and $X$ be inequivalent.
+If $\tau(W)$ and $\tau(X)$ do not have the same number of diagonals (hence their faces in $A_n$ having the same dimension) then they are not parallel, so we can assume $\tau(W)$ and $\tau(X)$ do have the same number of diagonals and hence their faces in $A_n$ have the same dimension.
+Let the face associated to $\tau(W)$ be $f_W$ and the face associated to $\tau(X)$ be $f_X$.
+
+  As observed in the proof of Proposition~\ref{prop easy way}, the support of any nonzero vector parallel to an edge is on the indices corresponding to the four vertices bounding the quadrilateral of the dissection associated with the edge.
+Thus $\tau(W)$ and $\tau(X)$ do not have the same set of vertices incident to at least one non-triangle face then the span of the vectors parallel to their edes has different support and so they cannot be parallel.
+So we can assume that $\tau(W)$ and $\tau(X)$ have the same set of vertices incident to at least one non-triangle face.
+
+    Since $\tau(W)$ and $\tau(X)$ do not have the same set of non-triangle faces, there must be some diagonal $d$ of $\tau(W)$ that crosses through a non-triangle face $f$ of $\tau(X)$. 
+    It will be most convenient to look at normal vectors and to use the choice of normal vector discussed in the many realizations paper on p8, namely pick one side of $d$ to be positive and define the $i$th coordinate of the $\omega^+_d$ to be
+    \[
+    \omega^+_d(i) = \begin{cases} \text{dist}(x_i, d) & \text{if $x$ is on the positive side of $d$}\\ 0 & \text{otherwise} \end{cases}
     \]
-\caption{Row and column numbering for a Young diagram with $k = 3$, $n = 7$ (left) and $k = 3$, $n = 8$ (right).
-The top left box in each diagram has coordinates $(1,7)$ (left diagram), $(2,8)$ (right diagram).}
-\label{fig:row column numbering}
-\end{figure}
-
-An algorithm for constructing the Le diagram associated to a Grassmann necklace was given by Agarwala and Fryer in [ref].
-Since we will make use of this algorithm in Section [ref] below, we summarise the process here.
-\begin{algorithm}\label{alg:GN to Le} \ [ref]
-Let $(I_1,\dots,I_n)$ be a Grassmann necklace of type $(k,n)$. Within a $k \times(n-k)$ square, draw the Young diagram whose rows are labelled by $I_1$ (as per the convention above).
-
-For each $i$, $2 \leq i \leq n$:
-\begin{itemize}
-\item Write \[I_1 \setminus I_i = \{a_1 > a_2 > \dots > a_r\}, \quad I_i \setminus I_1 = \{b_1 < b_2 < \dots < b_r\},\]
-where the inequalities denote the $<_1$ order (subscripts suppressed for clarity).
-\item For $1 \leq j \leq r$ , place a $+$ in square $(a_j,b_j)$ of the diagram. (We will sometimes refer to this $+$ as being {\em in the $a_j \rightarrow b_j$ position}.)
-\end{itemize}
-After performing the above for $2 \leq i \leq n$, place a $0$ in any remaining unfilled boxes.
-\end{algorithm}
-
-An algorithm for constructing the Grassmann necklace of a Le diagram also exists; this was given by Oh in [ref].
-A method for using the Le diagram to test whether a given $k$-subset is a basis for the corresponding positroid or not was given by Casteels in [ref].
-
-\subsection{Propagator configurations in admissible Wilson loop diagrams}\label{sec:propagator configs}
-
-Before we can describe the algorithm for extracting the Grassmann necklace of $M(W)$ from the Wilson loop diagram $W$, we require some initial results about the behavior of propagators in admissible WLD.
-
-Note that for any Wilson loop diagram, $W = (\cP, n)$, each propagator $p$ partions $[n]$ into three subsets of $[n]$, $\{[i+2, j-1], V(p), [j+2, i-1]\}$, the support of $p$ and the vertices that lie on either side of $p$.
-In the sequel we refer to the latter two intervals as an interval inside and outside of $p$, depending on a ordering we associate to the propagator.
-
-\begin{dfn}\label{props inside p}
-Let $W = (\cP, n)$ be an admissible Wilson loop diagram, with $p = (i,j) \in \cP$.
-Write $(p, <_a)$ be the same propagator with a direction induced by the linear ordering $<_a$.
-Then \bas V_{in}(p, <_a) = \{b \in [n] | i+1 <_a b <_a j \}\eas the region of $W$ {\bf inside} $p$, and \bas V_{out}(p, <_a) = \{b \in [n] | j+1 <_a b <_a i \} \;.\eas the region {\bf outside }$p$.
-\end{dfn}
-
-Depending on the ordering associated to $p$, the vertices on the inside and outside chagne. In particular, for $p = (i,j)$, $V_{in}(p, <_i) = V_{out}(p, <_j)$ and $V_{out}(p, <_i) = V_{in}(p, <_j)$.
-
-This in turn defines two sets of propagators, $\{\cP_{in}(p, <_i), \cP_{out}(p, <_i)\}$, where (for $\bullet \in \{in, \; out\}$) \bas \cP_{\bullet} = \{ q \in (\cP \setminus p) | V(q) \cap V_{\bullet}(p)  \neq \emptyset \} \;.\eas When clear, we drop the parentetical and just write $\cP_{in}$ (resp.
-$\cP_{out}$).
-These sets are the sets of propagators, not equal to $p$, \hlfix{whose support contains points in $V_{in}(p, <_*)$ (resp.
-$V_{in}(p, <_*)$), where $<_*$ refers to the appropriate ordering.}{Note, this means that paralell propagators are neither on the inside and outside of $p$.
-Is that okay?} If $W$ has no propagators crossing $p$ and no other propagator supported entirely on $V(p)$, then the set $\{\cP_{in}, p, \cP_{out}\}$ partitions $\cP$.
-Under these circumstances, the set $\cP_{in}$ defines the propagators with end points on one side of $p$, while $\cP_{out}$ defines the propagators with end points on the other side.
-In particular, for (weakly) admissible Wilson loop diagrams, the set $\{\cP_{in}, p, \cP_{out}\}$ is a partition for every propagators $p \in \cP$.
-Recall from Definition~\ref{admisdfn} that a {\em weakly admissible} diagram is one that satisfies the density and non-crossing conditions but does not require that $|V(\cP)| \geq |\cP| + 4$.
-
-As with the vertex sets,  which set of propagators lie inside and outside of $p$ switch depending on the direction imposed $p$.
-
-\begin{dfn}\note{right now this doesn't depend on the order of $i$ and $j$, but that might matter later on?}
-Let $p = (i,j) \in cP$ be a propagator in $W$.  Define the \textit{length} of $p$ to be 
-\[\ell(p) = min\big\{|V_{in}(p)|,|V_{out}(p)|\big\} +2 = min\big\{|[i+1,j]|,|[j+1,i]|\big\}.\]
-\end{dfn}
-In other words, $\ell(p)$ is the size of the smaller of the number of vertices that lie on either side of the progator $p$.
-
-\begin{rmk}\label{rem:props of length 2 and 3} 
-The following observations about configurations of propagators of short length in an (weakly) admissibly Wilson loop diagram, $W$, are easily verified:
-\begin{enumerate}
-\item If $p = (i,i+3)$ is a propagator of length 3, then the middle vertex $i+2$ supports at most one propagator.
-\item If every vertex in $W$ supports at least one propagator, then $W$ admits at least one propagator of length 2.
-\end{enumerate}
-\end{rmk}
-
-The following lemma establishes certain configurations of propagators that must exist in any admissible diagram with no non-supporting vertices (i.e.
-with $F(\emptyset) = \emptyset$).
-We make use of this result in several induction proofs below.
-
-\begin{lem}\label{lem sian}
-  Let $W$ be a weakly admissible WLD with at least 5 vertices and in which each vertex supports at least one propagator.  Then at least one of the following two things occurs.
-  \begin{enumerate}
-    \item $W$ has a propagator of length $\leq 6$ with a propagator of length 2 on one side it and nothing else on that side.\label{item big and 2}
-    \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator ends between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
-  \end{enumerate}
-\end{lem}
-
-\begin{proof}
-Suppose first that $W$ has a propagator of length $3$, say $p=(i, i+3)$.
-By Remark~\ref{rem:props of length 2 and 3} and the fact that every vertex of $W$ supports at least one propagator, we have that $i+2$ supports exactly one propagator and this propagator must have length 2 by noncrossingness.
-This gives us an instance of configuration~\ref{item big and 2} from the statement.
-
-Now suppose $W$ has no propagators of length $3$.
-%  We will prove the following stronger result: that $D$ admits a pair of propagators of length 2 in the following configuration:
-%\begin{equation}\label{eq:2 prop config}
-%\begin{tikzpicture}[baseline=(current bounding box.east)]
-%\pgfmathsetmacro{\radius}{2}
-%\pgfmathsetmacro{\angle}{20}
-%
-%\begin{scope}
-%\clip (-\radius*1.1,\radius*0.25) rectangle (\radius*1.1,\radius*1.25);
-%
-%\begin{scope}
-%\clip (-\radius*1.1,\radius*0.45) rectangle (\radius*1.1,\radius*1.1);
-%\draw[-] (0,0) circle[radius=\radius cm];
-%\end{scope}
-%
-%% vertices
-%\foreach \i in {2,3,...,7}{
-%	\draw (\angle*\i:\radius*0.98) --  (\angle*\i:\radius*1.02);
-%}
-%
-%\begin{scope}
-%\clip (0,0) circle[radius=\radius];
-%\draw[propagator] (2.5*\angle:\radius*1.1 cm) to [bend left=90] (4.35*\angle:\radius*1.1 cm);
-%\draw[propagator] (4.65*\angle:\radius*1.1 cm) to [bend left=90] (6.5*\angle:\radius*1.1 cm);
-%
-%\end{scope}
-%
-%\node at (80:\radius*1.1) {\tiny $j$};
-%\node at (100:\radius*1.1) {\tiny $j+1$};
-%\node at (90:\radius*0.5) {\small $s_j = s_{j+1} = 2$};
-%
-%\end{scope}
-%\end{tikzpicture}
-%\end{equation}
-
-We need a bit of notation: Let $W = (\cP, n)$ a weakly admissible Wilson loop diagram, and $Q \subseteq \cP$.
-Define the restriction $W|_Q$ to be the diagram $W$ with the propagators not in $Q$ removed.
-That is , \bas W|_Q = (Q, n).
-\eas
-
-%to a region $[i,j]$ to be the subdiagram obtained by forgetting all propagators not wholly supported on vertices in the cyclic interval $[i,j]$; the vertex set remains the same as in $W$.
-Denote this diagram by $W_{[i,j]}$.
-That is, if $W = (\cP, n)$ is a Wilson loop diagram, \bas W_{[i,j]} = (\cP \setminus \Prop([i,j]^c), n)\eas
-
-Given a propagator $p = (i, j)$ oriented $(p, <_i)$,  we can consider two obvious restrictions of $W$, namely \bas W|_{\cP_{in} \cup p} \quad \textrm{and} \quad  W|_{\cP_{out}\cup p}, \eas where the set of non-supportive vertices of  $W|_{\cP_{in} \cup p}$ is $V_{out}$ and  the set of non-supportive vertices of  $W|_{\cP_{out} \cup p}$ is $V_{in}$.
-That is, these restrictions contain the propagators on the inside and outside of $(p, <_i)$ respectively, as well as $p$ itself.
-\footnote{If we denote $V \subset [n]$ and $Q = \Prop(V^c)$, then we can write \bas M(W|_{Q^c}) = M(W)/F(Q) \oplus M_{\emptyset, n-|i-j+1|} \eas where  $M_{\emptyset, k}$ is the matroid of rank $0$ on a set of $k$.
-That is $M_{\emptyset, n-|i-j+1|} =M((\emptyset, n-|i-j+1|))$.
-}
-
-%We say that $p$ \textit{bounds the regions} $[i,j+1]$ and $[j,i+1]$ which we call outside and inside respectively.
-The ordering of the start and end points allow us to identify one or the other region unambiguously.
-
-With these observations in mind we can return to the proof.
-
-We will inductively construct a sequence of pairs of propagators $(p_r,q_r)$ satisfying: $\ell(p_r) = 2$, and $p_r$ either forms part of configuration \ref{item big and 2} or \ref{item pair of 2s} from the statement,
-  %a configuration \eqref{eq:2 prop config} in $D$
-or there is a propagator $q_r$ satisfying
-\begin{itemize}
-\item $\ell(q_r) \geq 4$.
-\item $\{p_1, \ldots, p_r\}$ and $\{q_1, \ldots, q_{r-1}\}$ are all on the same side of $q_r$.  
-\end{itemize}
-Note that we will be interested in the orientation of $q_r$ so that the previous $p_i$ and $q_i$ are on the outside of $q_r$.
-By the finiteness of $W$ this must eventually terminate in one of the desired configurations. %a configuration of the form \eqref{eq:2 prop config}.
-
-Start by choosing a propagator $p_1 = (j_1,j_1+2)$ of length 2 in $W$ (which exists by Remark~\ref{rem:props of length 2 and 3}).
-If it is part of one of the configurations we are looking for then we are done,
-%a configuration \eqref{eq:2 prop config} we are done,
-so suppose otherwise. 
-By assumption: $p_1$ is not in configuration \ref{item pair of 2s}, there are no propagators of length $3$, and every vertex supports at least one propagator.
-Therefore there must exist a propagator $q_1$ of length $\geq 4$ with one end on edge $j_1$ or on edge $j_1-1$ or on edge $j_1-2$.
-Orient $q_1 = (i_1, k_1)$ such that  $p_1 \in \cP_{out}(q_1)$, (that is $(q_1, <_{i_1})$).
-
-%This bounds a region $[i_1,k_1] = V_{out}(q_1) \cup V(q_1)$ on the outside of $(q_1, <_{i_1})$ (where $k_1 \in \{j_1-1, j_1, j_1+1\}$) which does not contain $p_1$.
-
-INSERT PICTURE HERE?
-
-Now suppose $q_{r} = (i_r, k_r)$ exists by the induction hypothesis and is oriented $(q_r, <_{i_r})$ so that the previous $p_i$ and $q_i$ are on the outside.
-For the rest of this proof, we assume this orientation and drop the $<_{i_r}$ from the notation.
-
-Call let $W_r := W|_{\cP_{in} \cup q_r}$.
-By the original hypotheses on $W$ every vertex in $v \in V_{in}(q_r)$ (which is a non-empty interval since $\ell(q_r) \geq 4$) must have support at least one propagator ($|\Prop(v)| \geq 1$), while the same is true for $V(q_r)$ because these vertices support $q_r$.
-By construction, the remaining vertices of $W|_{\cP_{in} \cup {q_r}}$, i.e.
-$V_{out}(q_r)$, are non-supporting.
-
-By Remark~\ref{rem:props of length 2 and 3}, $W_r$ admits at least one propagator of length 2.
-$W_r$ has no propagators of length $3$ since $W$ has none.
-Let $p_{r+1}$ be a propagator of length 2 in $W_r$; if it forms part of configuration \ref{item big and 2} or \ref{item pair of 2s}
-%the configuration \eqref{eq:2 prop config}
-then we are done, so assume otherwise.
-
-Note we may replace $q_r$ by any other propagator, $q'_{r}$ of length $\geq 4$ in $W_r$ such that $p_{r+1}$ and $q_r$ are on opposite sides; such a new $q'_{r}$ still satisfies all the hypotheses, and so, without loss of generality we may assume that $q_r$ has minimal length among propagators of length $\geq 4$ which have $p_{r+1}$ on their inside.
-
-Write $p_{r+1} = (j_{r+1}, j_{r+1}+2)$.
-There are two cases to consider.
-The first case is that $i_r \leq j_{r+1} \leq i_r+2$ and $k_r-2 \leq j_{r+1}+2 \leq k_{r}$ (so $p_{r+1}$ has one end before $i_{r} + 3$ and the
-other after $k_{r} - 2$).
-Then since $p_{r+1}$ has length 2, it must be that $(i_r+3)+1 \geq k_r-2$ and so $q_r$ has length $\leq 6$.
-By the minimality assumption on $q_r$ no propagator in $W_r$ has $q_r$ on one side and $p_{r+1}$ on the other side.
-Therefore, any propagator in $W_r$ other than $p_{r+1}$ itself must be of the form $(i,j)$ with $i_r\leq i, j\leq i_r+2$ or $k_r-2 \leq i,j\leq k_r$.
-That is, this propagator must be of length 2, and so we have configuration \ref{item pair of 2s} which we have already assumed does not occur.
-Consequently, $\cP_{in}(q_r)$ contains only $p_{r+1}$ and so we have congifuratin  \ref{item big and 2} from the lemma statement which again we have assumed does not occur.
-Therefore this first case cannot occur.
-
-The second case is that one of the following three things happen (we continue to write $p_{r+1} = (j_{r+1}, j_{r+1}+2)$) 
-\begin{itemize}
-\item $i_r+3 \leq j_{r+1}\leq k_r-3$ or $i_r+3 \leq j_{r+1}+2\leq k_r-3$,
-\item $i_r = j_{r+1}$, or 
-\item $k_r-2 = j_{r+1}$
-\end{itemize}
-(Phrased more causually, this is that $p_{r+1}$ has either at least one end on an edge bounded by the vertices in the interval $[i_r+3, k_r-2]$ or both ends lie in $[i_r, i_r+3]$ or both ends lie in $[k_r-2, k_r+1]$.)
-These situations all behave similarly.
-By symmetry it suffices to only consider the second situation and the second possiblity of the first situation.
-Note that since $j_{r+1}+4 \leq k_r-1$ in both situations, and $j_{r+1}+4 \in V_{in}(q_r)$, thus $j_{r+1}+4$ is supported by a propagator in $W_r$ other than $q_r$.
-Let $t$ be this propagator.
-Since $p_{r+1}$ is not part of configuration \ref{item pair of 2s} and $W_r$ has no propagators of length 3, we must have that the length of $t$ is $\geq 4$.
-If $q_r$ and $p_{r+1}$ were on different sides of $t$ then this would contradict the minimal length hypothesis on $q_r$.
-Therefore $t$ has all the previous $q_i$ and $p_i$ on the same side and length $\geq 4$ and so we may set $q_{r+1} = t$ to continue the induction.
-
-The overall result then follows by induction.
-\end{proof}
-
-%% this was 100% a productive use of my time
-%
-%\[\begin{tabular}{ccc}
-%% possibility 1
-%\begin{tikzpicture}
-%\pgfmathsetmacro{\radius}{2}
-%\pgfmathsetmacro{\angle}{15}
-%\begin{scope}
-%\clip (-\radius*1.1,0) rectangle (\radius*1.1,\radius*1.1);
-%
-%% vertices 
-%\foreach \i in {2,3,4,6,7,8,9,10}{
-%	\draw (\angle*\i:\radius*0.98) --  (\angle*\i:\radius*1.02);
-%}
-%
-%% \dots 
-%\foreach \i in {1,2,3}{
-%	\node at (65 + \i*5:\radius cm) {$\cdot$};
-%}
-%
-%\begin{scope} % this scope contains the propagators
-%\clip (0,0) circle[radius=\radius];
-%
-%\draw[propagator] (\angle*2.4:\radius*1.2 cm) to [bend left=30] (\angle*9.7:\radius*1.2 cm); % q_r
-%\draw[propagator] (\angle*7.7:\radius*1.1 cm) to [bend left=90] (\angle*9.45:\radius*1.1 cm); % p_{r+1}
-%
-%% grey prop begins here
-%
-%\begin{scope}
-%\clip (\angle*7.5:\radius cm) circle[radius=\radius*0.45cm];
-%\draw[light-gray,propagator,seconddash] (\angle*6:\radius*1.02 cm) circle[x radius=\radius*0.4cm, y radius = \radius*0.3cm];
-%\end{scope}
-%
-%\begin{scope}
-%\clip (0,0) circle[radius=\radius];
-%\clip (\angle*7.5:\radius cm) circle[radius=\radius*0.4cm];
-%\draw[light-gray,propagator,firstdash] (\angle*6:\radius*1.02 cm) circle[x radius=\radius*0.4cm, y radius = \radius*0.3cm];
-%\end{scope}
-%
-%\begin{scope}
-%\clip (\angle*7.5:\radius cm) circle[radius=\radius*0.3cm];
-%\clip (0,0) circle[radius=\radius];
-%\draw[light-gray,propagator] (\angle*6:\radius*1.02 cm) circle[x radius=\radius*0.4cm, y radius = \radius*0.3cm];
-%\end{scope}
-%% end gray prop
-%
-%\end{scope}
-%
-%
-%\node at (90:\radius*0.30 cm) {\tiny $q_r$};
-%\node at (\angle*8:\radius*0.73) {\tiny $p_{r+1}$};
-%\node[light-gray] at (\angle*4.9:\radius*0.77 cm) {\tiny $q_{r+1}$};
-%\node at (2*\angle:\radius*1.1) {\tiny $i_r$};
-%\node at (9*\angle:\radius*1.1) {\tiny $j_r$};
-%
-%
-%% circle/edges; needs to happen last to overlap gray
-%\begin{scope}
-%\clip (-\radius*1.1,0.9) rectangle (\radius*1.1,\radius*1.1);
-%\draw[-] (0,0) circle[radius=\radius cm];
-%\end{scope}
-%
-%\end{scope} % ends the overall rectangle clipping
-%\end{tikzpicture}
-%
-%&
-%
-%% possibility 2
-%\begin{tikzpicture}
-%\pgfmathsetmacro{\radius}{2}
-%\pgfmathsetmacro{\angle}{15}
-%\begin{scope}
-%% overall clipping to make the size sensible
-%\clip (-\radius*1.1,0) rectangle (\radius*1.1,\radius*1.1);
-%
-%
-%% vertices
-%\foreach \i in {2,3,4,6,7,8,9,10}{
-%	\draw (\angle*\i:\radius*0.98) --  (\angle*\i:\radius*1.02);
-%}
-%
-%% \dots
-%\foreach \i in {1,2,3}{
-%	\node at (65 + \i*5:\radius cm) {$\cdot$};
-%}
-%
-%\begin{scope} % props
-%\clip (0,0) circle[radius=\radius cm]; 
-%\draw[propagator] (\angle*2.4:\radius*1.2 cm) to [bend left=30] (\angle*9.6:\radius*1.2 cm); % q_r
-%\draw[propagator] (\angle*6.7:\radius*1.1 cm) to [bend left=90] (\angle*8.6:\radius*1.1 cm); % p_{r+1}
-%
-%%% grey prop starts here
-%
-%\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.45cm];
-%\draw[light-gray,propagator,seconddash] (\angle*4.5:\radius*1.3 cm) circle[y radius = 0.5*\radius cm,x radius=\radius*0.7cm];
-%\end{scope}
-%
-%\begin{scope}
-%\clip (0,0) circle[radius=\radius];
-%\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.4cm];
-%\draw[light-gray,propagator,firstdash] (\angle*4.5:\radius*1.3 cm) circle[y radius = 0.5*\radius cm,x radius=\radius*0.7cm];
-%\end{scope}
-%
-%\begin{scope}
-%\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.3cm];
-%\clip (0,0) circle[radius=\radius];
-%\draw[light-gray,propagator] (\angle*4.5:\radius*1.3 cm) circle[y radius = 0.5*\radius cm,x radius=\radius*0.7cm];
-%\end{scope}
-%% grey prop ends here
-%
-%
-%\node at (90:\radius*0.32 cm) {\tiny $q_r$};
-%\node at (\angle*7.75:\radius*0.75) {\tiny $p_{r+1}$};
-%\node[light-gray] at (\angle*4.5:\radius*0.7 cm) {\tiny $q_{r+1}$};
-%\node at (2*\angle:\radius*1.1) {\tiny $i_r$};
-%\node at (9*\angle:\radius*1.1) {\tiny $j_r$};
-%
-%% circle/edges
-%\begin{scope}
-%\clip (-\radius*1.1,0.9) rectangle (\radius*1.1,\radius*1.1);
-%\draw[-] (0,0) circle[radius=\radius cm];
-%\end{scope}
-%
-%\end{scope} % ends overall clip
-%\end{tikzpicture}
-%
-%&
-%
-%% possiblitiy 3
-%\begin{tikzpicture}
-%\pgfmathsetmacro{\radius}{2}
-%\pgfmathsetmacro{\angle}{12}
-%\begin{scope}
-%\clip (-\radius*1.1,0) rectangle (\radius*1.1,\radius*1.1);
-%
-%% vertices
-%\foreach \i in {2,3,6,7,8,9,12,13}{
-%	\draw (\angle*\i:\radius*0.98) --  (\angle*\i:\radius*1.02);
-%}
-%
-%% \dots
-%\foreach \i in {1,2,3}{
-%	\node at (44 + \i*5:\radius cm) {$\cdot$};
-%	\node at (116 + \i*5:\radius cm) {$\cdot$};
-%}
-%
-%\begin{scope} % props
-%\clip (0,0) circle[radius=\radius cm];
-%\draw[propagator] (\angle*2.4:\radius*1.2 cm) to [bend left=30] (\angle*12.6:\radius*1.2 cm); % q_r
-%\draw[propagator] (\angle*6.5:\radius*1.1 cm) to [bend left=100] (\angle*8.5:\radius*1.05 cm); % p_{r+1}
-%
-%%  grey prop 1
-%% not q_{r+1}
-%\begin{scope}
-%\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.45cm];
-%\draw[light-gray,propagator,seconddash] (\angle*6.5:\radius*1.1 cm) to [bend left=90] (\angle*12.5:\radius*1.1cm);
-%\end{scope}
-%
-%\begin{scope}
-%\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.4cm];
-%\draw[light-gray,propagator,firstdash] (\angle*6.5:\radius*1.1 cm) to [bend left=90] (\angle*12.5:\radius*1.1cm);
-%\end{scope}
-%\begin{scope}
-%\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.3cm];
-%\draw[light-gray,propagator] (\angle*6.5:\radius*1.1 cm) to [bend left=90] (\angle*12.5:\radius*1.1cm);
-%\end{scope}
-%% grey prop 1 ends here
-%
-%% grey prop 2
-%% this is q_{r+1}
-%\begin{scope}
-%\clip (\angle*8.5:\radius cm) circle[radius=\radius*0.45cm];
-%\draw[propagator,seconddash,light-gray] (\angle*8.8:\radius*1.1 cm) to [bend left=90] (\angle*12:\radius*1.1cm);
-%\end{scope}
-%
-%\begin{scope}
-%\clip (\angle*8.5:\radius cm) circle[radius=\radius*0.4cm];
-%\draw[propagator,firstdash,light-gray] (\angle*8.8:\radius*1.1 cm) to [bend left=90] (\angle*12:\radius*1.1cm);
-%\end{scope}
-%
-%\begin{scope}
-%\clip (\angle*8.5:\radius cm) circle[radius=\radius*0.3cm];
-%\draw[light-gray,propagator] (\angle*8.8:\radius*1.1 cm) to [bend left=90] (\angle*12:\radius*1.1cm);
-%\end{scope}
-%
-%% grey prop 2 ends here
-%
-%
-%
-%\end{scope}
-%
-%\node at (90:\radius*0.15 cm) {\tiny $q_r$};
-%\node at (\angle*7.5:\radius*0.83) {\tiny $p_{r+1}$};
-%\node[light-gray] at (\angle*11:\radius*0.75 cm) {\tiny $q_{r+1}$};
-%
-%\node at (2*\angle:\radius*1.1) {\tiny $i_r$};
-%\node at (12*\angle:\radius*1.1) {\tiny $j_r$};
-%
-%
-%
-%% overall circle
-%\begin{scope}
-%\clip (-\radius*1.1,0.7) rectangle (\radius*1.1,\radius*1.1);
-%\draw[-] (0,0) circle[radius=\radius cm];
-%\end{scope}
-%
-%
-%\end{scope} % ends overall clip
-%\end{tikzpicture}
-%
-%\end{tabular}
-%\]
-%In each case, the diagram indicates how to choose $q_{r+1}$ satisfying the induction hypothesis.
-In the third case, note that \textit{both} ends of $p_{r+1}$ must share their edge with a propagator of length $\geq 4$; the non-crossing hypothesis on propagators guarantees that at least one will bound a region not containing $p_{r+1}$.
-
-\begin{rmk}
-In the case that all vertices of an admissible WLD $W$ support at least two propagators, then Lemma~\ref{lem sian} substantially simplifies.
-By Remark~\ref{rem:props of length 2 and 3}, $W$ has no propagators of length $3$.
-Configuration \ref{item big and 2} necessarily entails vertices with support $1$ as does configuration \ref{item pair of 2s} unless $j=i+2$.
-So in the case that $W$ has all vertices with support at least two then $W$ must contain a pair of propagators of length $2$  with the property that the first propagator is $(i, i+2)$, the second is $(i+2, i+4)$ and no other propagator ends on the edge $i+2$.
-\end{rmk}
-
-\subsection{From Wilson Loop diagrams to Grassmann Necklaces}\label{sec:GN alg}
-
-Until now, the positroid associated to a Wilson loop diagram $W$ could only be obtained by computing the matrix $C(W)$ associated to $W$, listing all bases of the induced matroid $M(W)$, and constructing the Le diagram or Grassmann necklace of the positroid ``by eye'' from this list.
-
-In this section, we give an algorithm for passing directly from the Wilson loop diagrams to its Grassmann necklace.
-This not only greatly simplifies the process above, but will also allow us to relate the behavior of the positroid $M(W)$ directly to the configuration of progators in $W$.
-
-The fact that Algorithm~\ref{alg:put GN on WLD} does construct the required Grassmann necklace is proved in Theorem~\ref{res:alg gives GN}.
-
-\begin{algorithm}\label{alg:put GN on WLD}
-Let $W = (\cP, [n])$ be an admissible Wilson loop diagram. This gives an algorithm for calculating the set $I_a$, for $a \in [n]$.
-
-\begin{enumerate}
-\item Fix a vertex $a \in [n]$. Set $i:=a$ and $I_a = \emptyset$.
-\item While $\cP \neq \emptyset$, perform the following steps.
-\begin{enumerate}
-\item \textbf{Step $i$ for vertex $a$}: If $\Prop(i) \neq \emptyset$ in $W$, write $I_a = I_a \cup i$.
-Let $p \in \Prop(p)$ be the clockwise most propagator supported on $i$.
-Write $W = (\cP \setminus p, n)$.
-\item If $Prop(i) = \emptyset$ do nothing.
-\item Increment $i$ by 1 and repeat from (a).
-\end{enumerate}
-\end{enumerate}
-\end{algorithm}
-
-If the algorithm assigns vertex $j$ to propagator $p$ from starting vertex $i$, we say that $p$ \emph{contributes} $j$ to $I_i$.
-Notationally, we represent this by allowing the $I_i$ symbol to represent a function as well as a set, as follows:
-\begin{dfn}\label{def I_i as a function}
-Let $W = (\cP, [n])$ be an admissible Wilson loop diagram. For each $i \in [n]$, define a function $I_i : \cP \longrightarrow [n]$ by
-\[I_i(p) := \text{the vertex label that $p$ contributes to $I_i$ in Algorithm~\ref{alg:put GN on WLD},}\]
-for each $p \in \cP$.
-\end{dfn}
-
-Given a propagator $p$ and a vertex $i$ in its support, it will be very useful in the following to understand on what set of vertices the Grassmann necklace algorithm assigns $i$ to $p$.
-The answer is that the set is a non-empty cyclic interval.
-Lemma~\ref{vertex cyclic int lem} establishes this, but first we need a preliminary lemma which is also useful in its own right.
-
-\begin{lem}\label{lem no fourth vertex}
-Let $W$ be an admissible Wilson loop diagram containing at least one propagator. For any $i \in [n]$ and for any $p=(a,b)$ with $i\leq_i a <_i b$, we have $I_i(p) \neq b+1$.
-\end{lem}
-\begin{proof}
-Suppose for contradiction that we have $p = (a,b)$ with $i\leq_i a <_i b$ and $I_{i}(p) = b+1$. We may choose $p$ such that $|[a+1,b]|$ is minimal amongst propagators with this property.
-
-Since $I_i(p) \neq b$, there must exist a propagator $q$ inside of $p$ with $I_i(q) = b$.
-The propagator $q$ cannot end on the edge $(b-1,b)$, as this would contradict the minimality of $p$, so $q = (c,c+1,b,b+1)$ with $a <_i c <_i b$, and $I_i(q) = b$.
-
-In order for $q$ to remain unassigned until vertex $b$, there must be another propagator $r$ with an end on $(c,c+1)$ and $I_i(r) = c+1$; the only way this can occur is if $r$ is outside $q$ but inside $p$.
-Now $r$ contributes its fourth vertex to $I_i$, again contradicting the minimality of $p$.
-\end{proof}
-
-\begin{cor}\label{GN alg well defined}
-If $W$ is an admissible Wilson loop diagram with $k$ propagators, then Algorithm~\ref{alg:put GN on WLD} assigns exactly $k$ vertices to each $I_i$.
+    The many realizations paper explains why $\omega^+_d$ is a normal vector for any face with $d$ as a diagonal in a way which is short and clean but relies on some earlier definitions.
+We can instead check that it is a normal vector in a completely elementary way using the shoelace formula for the area of a triangle which says that if $(x_1, y_1), (x_2, y_2), (x_3, y_3)$ are the coordinates of the corners of a triangle in counterclockwise order then the area of the triangle is $(x_1y_2 - x_1y_3 + x_2y_3 - x_2y_1 + x_3y_1 - x_3y_2)/2$.
+
+    Proceed now to check that $\omega^+_d$ is a normal vector for any face associated to a dissection including $d$.
+We will do this by showing it is normal to every edge bounding the face.
+To do so, choose the coordinate system for the polygon so that $d$ is along the $x$-axis.
+Let $(a_i, h_i)$, $i=1,2,3,4$ be the coordinates of the vertices of a quadrilateral in counterclockwise order and which corresponds to an edge bounding the face.
+Since the dissection includes $d$ either all four points are on the negative side of $d$, and so the dot product of $\omega^+_d$ with the direction vector for the quadrilateral is immediately $0$, or, by the formula in the proof of the previous proposition and the shoelace formula, the dot product of $\omega^+_d$ with the vector associated to the quadrilateral is
+    \begin{align*}
+      & h_1(a_2h_3-a_2h_4+a_3h_4-a_3h_2+a_4h_2-a_4h_3)/2 - h_2(a_1h_3-a_1h_4+a_3h_4-a_3h_1+a_4h_1-a_4h_3)/2 \\
+      & + h_3(a_1h_2-a_1h_4+a_2h_4-a_2h_1+a_4h_1-a_4h_2)/2 - h_4(a_1h_2-a_1h_3+a_2h_3-a_2h_1+a_3h_1-a_3h_2)/2 \\
+      & = 0
+    \end{align*}
+
+    Now, $\tau(W)$ and $\tau(X)$ satisfy the hypotheses of Lemma~\ref{lem good quads}, so we can assume that $f$ and $d$ have the property that there is one side of $d$, which we will call the positive side, so that exactly one vertex of $f$ is strictly on that side.
+Then $\omega^+_d$ with the direction vector of $d$ have common support exactly on that one vertex and so their dot product is nonzero.
+Since the direction vector of $d$ is contained in the direction of $\tau(X)$ but is not orthogonal to $\omega^+_d$, while $\omega^+_d$ is normal to the face of $\tau(W)$, it follows that the faces associated to $\tau(W)$ and $\tau(X)$ are not parallel, as desired.
+\end{proof}
+
+The two propositions imply
+\begin{cor}
+  The number of inequivalent weakly admissible Wilson loop diagrams on $n$ is the number of non-parallel faces in the associahedron $A_n$.
 \end{cor}
-\begin{proof}
-It follows from the proof of Lemma~\ref{lem no fourth vertex} that Algorithm~\ref{alg:put GN on WLD} can never reach the fourth vertex of a propagator's support (with respect to the starting vertex).
-Therefore if the algorithm starts at vertex $i$, it must have assigned vertices to all propagators by the time it reaches $i-1$, ensuring that $I_i$ contains exactly $k$ distinct vertices.
-\end{proof}
-
-%Next we prove that this algorithm actually gives a Grassmann Necklace as claimed. We begin with some useful definitions and lemmas
-%
-%\begin{dfn}\label{protect dfn}
-%Let $W = (\cP,n)$ be an admissible diagram and $a \in[n]$ a vertex.
-For $p= (i,j) \in \cP$ an a propagator of $W$  and $v \in \{i, j\}$ a vertex of $W$, let $P_{v}(p)$ or $P_{v+1}(p)$ to be two \emph{protecting sets of $p$ at $v$ and ${v+1}$} be a set of propagators defined as follows: \begin{enumerate}
-%\item Work under the linear order on $[n]$, $<_{v+1}$, every propagator is now written as $p = (i_p, j_p)$ such that $i_p <_{v+1} j_p$.
-%\item If there is a propagator $s_1 \in \cP$ such that $s_1 = (i_{s_1}, v)$ or $s_1 = (i_{s_1}, v-1)$, then $s_1 \in P_v(p)$.
-%\item If $s_1$ as above does not exists, then $P_v(p) = \emptyset$.
-In this case, $P_w(p) = \emptyset$.
-When $P_v(p) \neq \emptyset$, if there exists a propagator $t_1 \in \cP$ defined such that $t_1 = (i_{t_1}, v)$ and $s_1 = (i_{s_1}, v)$ with $i_p <_{v+1} i_{t_1} <_{v+1} i_{s_1}$, $P_w(p) = t_1$.
-%\item If $s_1 = (i_{s_1}, v)$ then \bas P_v(p)=  \begin{cases} \{s_1\} \cup P_{i_{s_1}}(s_1) \cup P_{i_{s_1}+1}(s_1) & \textrm{ if } P_{i_{s_1}+1}(s_1) \neq \emptyset \\ s_1 &  \textrm{ else } \end{cases}.
-\eas  If $s_1 = (i_{s_1}, v-1)$ then \bas P_v(p)=  \begin{cases}  \emptyset & \textrm{ if } P_{v-1}(s_1) = \emptyset \\ \{s_1\} \cup P_{v-1}(s_1) & \textrm{ else } \end{cases} \eas.
-%\end{enumerate}
-%\end{dfn}
-%
-%The protective sets $P_\cdot(p)$ are designed to prevent $p$ from contributing the vertex indicated in the subscript at certain points in the Grassmann Necklace, $I_a$.
-Write $P_v(p) = \{s_1, \ldots s_r, t_2,  \ldots t_r\}$ with the $t_x = P_{i_{s_{x-1}}+1}(s_{x-1})$ and $s_x \in P_{i_{s_{x-1}}}(s_{x-1})$ for $x \geq 2$.
-We place the restrictions on the vertex $a$ as follows: \begin{enumerate} \item $P_v$ prevents $p$ from contributing to $I_a$ if \bas i_{s_r}  <_{v+1} a-1 <_{v+1} v\eas \item $P_{v+1}(p)$ prevents $p$ from contributing to $I_a$ only if $P_v(p)$ prevents $p$ from contributing $v$ to $I_a$.
-\end{enumerate}
-%
-%
-%\begin{eg} \label{eg: protective sets}
-%Consider the admissible Wilson loop diagram
-%\bas W=\begin{tikzpicture}[rotate=120,baseline=(current bounding box.east)]
-%	\begin{scope}
-%	\drawWLD{17}{3}
-%	\drawnumbers
-%	\drawprop{1}{0}{16}{0}
-%	\drawlabeledprop{2}{0}{15}{1}{p}
-%    \drawprop{6}{2}{15}{0}
-%    \drawprop{3}{0}{6}{1}
-%    \drawprop{4}{0}{6}{0}
-%    \drawprop{7}{0}{11}{0}
-%    \drawprop{8}{0}{10}{0}
-%    \drawprop{11}{1}{14}{1}
-%    \drawprop{12}{0}{14}{0}
-%		\end{scope}
-%	\end{tikzpicture}
-%\eas Consider the two sets of propagators $Q = \{(3, 6), (4, 6), (6,15)\}$ and $R = \{ (7, 11), (8, 10), (11, 14), (12, 14)\}$.
-The propagator $p = (2, 15)$ is protected at $a = 5$ from contributing $15$ to $I_5$ by the set $P_{15} = Q$.
-There is no set preventing $p$ from contributing $16$ to $I_{15}$.
-At $a = 9$, the set $P_{15} = \{(6,15)\} \subset Q$.
-We may just as easily right $P_{15} = Q$, though the other two propagators in the set prove unnecessary to keep $p$ from contributing $15$ to $I_{9}$.
-At $a = 14$, both $P_{15}$ and $P_{16}$ exists, with $P_{15} = \{(11, 14), (12, 14)\} \subset R $ and $P_{16}= \{(6,15)\} \subset Q$.
-We may just as easily right $P_{15} = R$ and $P_{16} = R$, though the other two propagators in each set are unnecessary.
-%
-%Note that for $a=1$, the propagator $p$ contributes $2$ to $I_1$. However, in this case, we say that neither $P_{15}$ or $P_{16}$ exist.
-%\end{eg}
-%
-%
-%\begin{lem}\label{protecting lem}
-%Let $W = (\cP, [n])$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$, and $a \in [n]$ be a vertex.
-For $v \in \{i,j\}$, if $P_v(p) \neq \emptyset$, write $P_v(p) = \{s_1 \ldots s_r, t_2, \ldots t_r\}$ as above.
-Then $p$ does not contribute $v$ to $I_a$ if $i_{s_r} +1 <_{v+1} a <_{v+1} v+1 $.
-If both $P_v(p)$ and $P_{v+1}(p)$ are non empty, then $p$ also does not contribute $v+1$ to $I_a$.
-%\end{lem}
-%
-%\begin{proof}
-%Note that if $s_1 \in P_v(p)$ exists at step $v$ of Algorithm \ref{alg:put GN on WLD}, then $p$ cannot contribute $p$ to $I_a$.
-Further, if $P_{v+1}(p) \neq \emptyset$, $p$ cannot contribute $v+1$ to $I_a$ either.
-%
-%Next we show that if $P_v(p)$ is as above, with $i_{s_r}+1 <_{v+1} a$, then the propagator $s_1$ exists at step $v$ of Algorithm \ref{alg:put GN on WLD}.
-Let $x$ be the largest integer that such that $a <_{v_1} j_{x}+1$.
-Then $s_x$ cannot contribute to $I_a$ before vertex $v$.
-By construction $P_{i_{s_x}+1}(s_{x-1})\subset P_v(p)$.
-Therefore, $s_{x-1}$ does not contribute $i_{s_x}+1$ to $I_a$.
-Thus we conclude that $s_1$ does not contribute $i_{s_1}$ or $i_{s_1}+1$ to $I_a$.
-In other words, $s_1$ has not been removed from the diagram at vertex $v$.
-%
-%\end{proof}
-%
-%Thus we say that $P_v(p)$ protects $p$ at $v$ from $a$, for $a \in [i_{s_r}+2, v]$. There is an easy corollary to this, describing when such a protecting set cannot exist.
-%
-%\begin{cor} \label{protecting cor}
-%Let $W = (\cP, [n])$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$.
-Picking a $v \in \{i, j\}$ write $p = (i_p, j_p)$ with $i_p <_{v+1} j_p$.
-If $a \in [j_p+1, i_p+1]$ then there can be no protecting set $P_v$ or $P_{v+1}$ protecting $p$ at $v$ or $v+1$ from $a$.
-%\end{cor}
-%
-%\begin{proof}
-%Since $W$ is admissible, it cannot have crossing propagators. Therefore neither $P_v$ cannot have the requisite propagator $s_r$ with $i_{s_r}+1  <_{v+1} a$.
-%\end{proof}
-%
-%The converse, however requires an extra condition.
-%
-%\begin{lem} \label{protect conv lem}
-%For $W = (\cP, [n])$, $p = (i,j)$, and $v \in \{i, j\}$ and $ a \in [n]$ a vertex of $W$, if $v$ (resp.
-$v+1$) is the first vertex of $V(p)$ in the $<_a$ order such that $P_v$ (resp.
-neither $P_v$ nor $P_{v+1}$) does not exist, then $p$ contributes $v$ (resp.
-$v+1$) to $I_a$.
-%\end{lem}
-%
-%\begin{proof}
-%Write $p = (i_p, j_p)$ with $i_p <_{v+1} j_p$.
-%
-%
-%If $p$ doesn't contribute $v$ (or $v+1$) to $I_a$, then either $p$ contributes a different supporting vertex $u$ earlier in the $<_a$ order or there is a propagator $s_1$ at step $v$ of the algorithm \ref{alg:put GN on WLD} preventing $p$ from contributing $v$ to $I_a$, (or there are a pair of propagators $s_1$ and $t_1$ at step $v$ preventing $p$ from contributing $v+1$ at $I_a$.)
-%
-%If there are propagators $s_1, t_1 \in \cP$ that are still in the diagram at step $v$, (write them $s_1 = (i_{s_1}, j_{s_1})$, and $t_1 = (i_{t_1}, j_{t_1})$) with $j_{s_1} \in \{v, v-1\}$, and $i_p \leq_{v+1} i_{t_1} <_v i_{s_1} <_v j_{s_1} \leq_{v} j_{t_1} = v$) then $s_1$ or $t_1$ did not contribute $i_{s_1}$ or  $i_{s_1} +1 $ (resp.
-$i_{t_1}$ or $i_{t_1}+1$) to $I_a$.
-Then one of the following three situations hold: \begin{enumerate} \item $i_{s_1}+1 <_{v+1} a$ and $j_{s_1} = v$: In this case, $s_1$ cannot be removed until $v$.
-\item $i_{s_1}+1 <_{v+1} a$ and $j_{s_1} = v-1$: in this case there exists a propagator $s_2 = (i_{s_2}, j_{s_2})$ with $i_{s_1} \leq_{v+1} i_{s_2} <_{v+1} j_{s_2}$ and $j_{s_2} \in \{j_{s_1}-1, j_{s_1}\}$.
-\item $i_{s_1}+1 \not <_{v+1} a$ and $j_{s_1} = v$: and there must be two other propagators $s_2 = (i_{s_2}, j_{s_2})$ and $t_2 = (i_{t_2}, j_{t_2})$, with $j_{s_2} \in \{i_{s_1}, i_{s_1}-1\}$ and $i_{s_1} \leq_{v+1} i_{t_2} <_{v+1} i_{s_2} <_{v+1} j_{s_2} \leq_{v+1} j_{t_2} = j_{s_1}$   \end{enumerate}
-%
-%However, now one must ensure that the newly identified propagators $s_2$ and $t_3$ do not contribute to $I_a$ before $i_{s_1}$.
-One does this by a similar construction to above.
-In this manner, we begin to build the sets $P_v(p)$ and $P_{v+1}(p)$.
-By finiteness and admissiblity of the Wilson loop diagram, both these sets are finite; one cannot continue to add propagators $s_i$, $t_i$ ad infinitum.
-%
-%We claim that this implies that at some point there is a terminal propagator, $s_m \in P_v(p)$ such that $i_{s_m} + 1 <_{v+1} a$, and \bas  \textrm{ either }= \begin{cases} j_{s_m}=i_{s_{m-1}} & \textrm{ }\\ j_{s_m}=j_{s_{m-1}} & \textrm{ } \end{cases} .\eas We show that all other possibilities lead to a contradiction.
-For the remainder of this proof, indicate by $p_k$ some propagator identified at an earlier stage of this construction.
-That is, for $0 < k < m$, $p_k \in \{s_k, t_k\}$.
-Futher define $p_0 = p$.
-%
-%
-%%\begin{cases} j_{s_{m}=i_{s_{m-1}} & \textrm{ } \\  j_{s_m}=j_{s_{m-1}} & \text{ }\end{cases}
-%
-%If $j_{s_m} \in \{i_{s_{m-1}}-1, j_{s_{m-1}}-1\}$, then, this cannot be the final propagator added to $P_v(p)$, as one would need a means of preventing $s_m$ from contributing $i_{s_{m-1}}-1$ or $j_{s_{m-1}}-1$ to $I_a$.
-%
-%If $i_{s_m} + 1 \not <_{v+1} a$, then there are two.
-% \begin{description}
-%
-%\item[$j_{s_m} = i_{s_{m-1}}$ and $i_{s_m} \in \{i_{p_k}+2, i_{p_k}+1\}$] for some $k<m$.
-By admissibility, there is not room to place both the propagators $s_{m+1}$, and $t_{m+1}$.
-Thus $s_m$ is removed at the step $i_{s_m}$ or $i_{s_m} + 1$.
-Therefore, $s_1$ contributes at either $i_{s_1}$ or $i_{s_1}+1$.
-This leads to a contradiction.
-%\item[$j_{s_m} = i_{s_{m-1}}$ and $i_{s_m} = i_{p_k}+2$] for some $k<m$. This requires either crossing propagators or propagators starting and ending at the same edge, which violates admissibility.
-% \end{description} \note{correct but clear as mud? Help?}
-%\end{proof}
-%
-%We use these results to prove some properties about the Algorithm \ref{alg:put GN on WLD}.
-%\begin{prop}\label{res:alg k labels}
-%If $W = (\cP, [n])$ is an admissible Wilson loop diagram with $|\cP| = k$, then Algorithm~\ref{alg:put GN on WLD} puts exactly $k$ distinct labels on each edge.
-%\end{prop}
-%\begin{proof}
-%It is enough to show that the algorithm terminates in at most $n$ steps for each $a \in [n]$.
-In other words, that all $k$ propagators of $W$ are removed by the time the algorithm has cycled through all the vertices, starting at $a$.
-Suppose this doesn't happen, i.e.
-there is a propagator $p= (i,j)\in \cP$ which survives the first $n$ steps of the algorithm for some starting vertex $a$.
-Without loss of generality, assume $a \leq_a i <_a j$.
-Otherwise, change the roles of $i$ and $j$.
-%
-%Since $p$ is not removed by step $j+1$, by Lemma \ref{protecting lem} there are $4$ protecting sets, $P_i,P_{i+1}, P_{j}$ , and $P_{j+1}$ respectively, allowing $p$ to remain after $n$ steps.
-
-%However, since the cyclic interval $[i,j] \subseteq [a,j]$, $P_j$ and $P_{j+1}$ cannot be protecting sets by Corrollary \ref{protecting cor}.
-%\end{proof}
-
-%\begin{lem}\label{lem last vert}
-%  Let W be an admissible WLD on $n$ vertices with Grassmann necklace $I_1, \ldots, I_n$.
-Then for all $1\leq a \leq n$, $a-1 \not\in I_a$ interpreted cyclically (that is for $a=1$, $a-1$ is interpreted to be $n$.)
-%\end{lem}
-%
-%\begin{proof}
-%Without loss of generality we can suppose $a=1$, so it suffices to show that $C(W)$ with the $n$th column removed is full rank.
-(This suffices because if $C(W)$ with the $n$th column removed had full rank but the lexicographically minimal basis of $C(W)$ included the $n$th column, then we'd obtain a contradiction by taking this minimal basis with the $n$th column removed and extending it to a basis using a column from the first $n-1$ columns of $C(W)$ which is possible by the full rank assumption.)
-%
-%Because the nonzero entries of $C(W)$ are independent indeterminants, it suffices to show that there is some choice of nonzero entries of $C(W)$, one in each row, each in different columns, and none of which are the $n$th column.
-This is equivalent to an assignment of all propagators to supporting vertices so that no two are assigned to the same vertex and none are assigned to vertex $n$.
-The lemma is proved if we show such an assignment exists.
-%
-%Consider an assignment $f$ of a subset of propagators to vertices not including vertex $n$ with the maximal number of propagators.
-If $f$ assigns $n$ propagators then we are done.
-Otherwise there is a propagator $p$ which is not assigned but, by maximality, all of $p$s supporting vertices (other than possibly $n$) are assigned.
-Build a sequence of sets $S_i$ of propagators and $T_i$ of vertices as follows.
-%
-%\begin{enumerate}
-%  \item $S_0={p}$ and $T_0$ is the support of $p$ except for $n$.  Set $i=0$.
-%  \item Let $R$ be the set of propagators which are assigned to a vertex in $T_i$ by $f$. Let $S_{i+1}= S_i \cup R$.  Let $T_{i+1} = T_i \cup (\text{supp}(R) - \{n\})$.\label{item loop step}
-%  \item If there is a vertex $v_{i+1}$ in $T_{i+1}$ which has not been assigned by $f$ then by construction there is a propagator $q_{i+1} \in S_{i+1}-S_i$ which can be assigned to $v_{i+1}$.
-Do so, removing $q_{i+1}$'s old assignment.
-This frees up a vertex $v_{i}$ in $T_i$ and so there is a propagator $q_{i} \in S_{i}$ which can be assigned to this vertex freeing up an earlier vertex and so on until $p$ has been assigned.
-This new assignment contradicts the maximality of $f$.
-%  \item  If nothing changed in step \ref{item loop step} then all vertices of $T_{i+1}$ are assigned to propagators in $S_{i+1}-\{p\}$ and vice versa.
-Thus $|S_{i+1}| = |T_{i+1}|+1$.
-Also all the support of propagators in $S_{i+1}$ is in $T_{i+1} \cup \{n\}$, which is a set of size $|T_{i+1}|+1 = |S_{i+1}|$.
-Thus we have $|S_{i+1}|$ propagators supported on $|S_{i+1}|$ vertices contradicting admissibility.
-%  \item Increment $i$ and go to \ref{item loop step}
-%\end{enumerate}
-%
-%This procedure must be finite as either a contradiction is found or $S_i$ grows at each step but $W$ has finitely many propagators.
-However, the only way for the process to end is by reaching a contradiction.
-Therefore any maximal assignment is a basis not including column $n$ which proves the lemma.
-%\end{proof}
-
-Given a propagator $p$ of an admissible WLD $W$ and a vertex $i$ in the support of $p$, define
-\[J_p^{(W)}(i) = \{m \in [n] \ : \ I^{(W)}_m(p) = i \},\]
-i.e.
-the set of indices $m$ for which Algorithm~\ref{alg:put GN on WLD} assigns the value $i$ to the propagator $p$ in $W$.
-The following lemma establishes that these sets behave in a simple and predictable manner, a fact which we will repeatedly use in subsequent proofs.
-
-\begin{lem} \label{vertex cyclic int lem}
-
-Let $p=(i,j)$ be a propagator of an admissible WLD $W$ on $n$ vertices.
-Then $J_p^{(W)}(i)$, $J_p^{(W)}(i+1)$, $J_p^{(W)}(j)$, and $J_p^{(W)}(j+1)$ are each non-empty cyclic intervals which partition $[n]$ and occur in the given cyclic order.
-\end{lem}
-
-\begin{proof}
-We will prove the result by induction on the number of propagators.
-If $W$ has one propagator then the result is immediate.
-Now suppose $W$ has more than one propagator.
-Since non-supporting vertices have no effect on the Grassmann necklace algorithm, it suffices to prove the result for $W$ with $F(\emptyset) = \emptyset$.
-Then by Lemma~\ref{lem sian}, $W$ has at least one of the four situations illustrated in Figure~\ref{fig 3 cases}.
-
-\begin{figure}
-    \includegraphics[scale=0.8]{3cases}
-    \caption{Four cases for admissible WLDs with no non-supporting vertices.
-The green half-propagators illustrate where propagators may occur, but are not required to exist; no other regions illustrated may support additional propagators.}\label{fig 3 cases}
-  \end{figure}
-
-In each of the four cases, when we remove the propagator labelled $p$ we obtain a diagram which satisfies the statement of the theorem by the induction hypothesis, and contains a propagator ${q = (i,j)}$ with no other propagators inside it (although this region may or may not contain non-supporting vertices, which we will call $l, l+1, \ldots$ as necessary).
-Let $V$ be the diagram obtained by removing the propagator $p$ from $W$ (Figure \ref{fig V diagram}).
-
-\begin{figure}
-\includegraphics[scale=0.8]{Vdiagram_modified}
-\caption{Diagram $V$ is $W$ with $p$ removed; there are no propagators inside $q = (i,j)$, though there may be up to 4 non-supporting vertices labelled $l, l+1, \ldots$.}
-\label{fig V diagram}
-\end{figure}
-
-Consider the fourth case of Figure~\ref{fig 3 cases} first, as it is the easiest.
-In this case, the vertices $\{l,l+1,l+2,l+3 \}$ which support $p$ in $W$ are non-supporting in $V$, so for every propagator $r$ in $V$ (including $q$) we have $J_r^{(V)} = J_r^{(W)}$; these are non-empty cyclic intervals in the correct order by the induction hypothesis.
-Additionally, it is clear from Figure~\ref{fig 3 cases} that $J_p^{(W)}(l+a) = \{l+a\}$ for $a\in\{1,2,3\}$ and $J_p^{(W)}(l) = [n] \backslash \{l+1, l+2, l+3\}$.
-The result therefore holds in this case.
-
-Now we proceed to consider the first three cases of Figure~\ref{fig 3 cases}.
-We first describe $J_q^{(V)}(*)$, which can be handled identically for all three cases.
-
-In $V$ there are no propagators inside $q$, so we see from Figure~\ref{fig V diagram} that
-\[l, l+1, \ldots ,j \in J^{(V)}_q(j) \text{ (if $l$ exists) and }  j+1 \in J^{(V)}_q(j+1).\]
-Note that $j+2 \not\in J^{(V)}_q(j+1)$ by Lemma~\ref{lem no fourth vertex}, so by the induction hypothesis we must have $J^{(V)}_q(j+1) = \{j+1\}$ and $j+2 \in J^{(V)}_q(i)$.
-Thus there exist vertices $d,e \in [j+2,i+1]$ with $d <e$, such that
-\[J^{(V)}_q(i) = [j+2,d-1], \quad J^{(V)}_q(i+1) = [d,e-1], \quad J^{(V)}_q(j) = [e,j], \quad J^{(V)}_q(j+1) = \{j+1\},\]
-and all intervals are non-empty.
-
-We now consider what happens as we move from $V$ to each of the three remaining cases for $W$.
-We need to consider both $J^{(W)}_p$ and $J^{(W)}_r$ for $r \neq p$, since the addition of $p$ can have a knock-on effect on later steps in the algorithm.
-
-%%%%%%%%%
-
-\textbf{Left two cases}: These cases behave essentially identically (except when $j$ or $j+1$ are not in the support of $p$, which can occur in the second case only; see below) so we handle the majority of the proof for these two cases simultaneously.
-Let $1\leq a\leq 3$ be the number of non-supporting vertices inside $q$ in $V$; so these vertices are $l, \ldots, l+a-1$.
-Write $p=(m,m+2)$ where $m\in \{i, i+1, l\}$.
-Note that $l, \ldots, l+a-1$ are all in the support of $p$.
-
-We first calculate $I^{(W)}_w$ for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$.
-Note that $p$ has no effect on other propagators for starting vertices in this range, while the value of $I^{(W)}_w(p)$ depends on how soon $q$ is assigned to a vertex, i.e.
-on the value of $I^{(V)}_w(q)$.
-Thus, if $w\in J_q^{(V)}(i)$ then
-    \[
-    I_w^{(W)}(r) =  \begin{cases}
-        \max\{i+1, m\} & \text{if } r=p \\
-        I_{w}^{(V)}(r) & \text{if } r\neq p
-      \end{cases} 
-    \]
-    while if $w\in J_q^{(V)}(i+1)$ or $w\in J_q^{(V)}(j)$ then
-    \[
-    I_w^{(W)}(r) =  \begin{cases}
-        l & \text{if } r=p \\
-        I_{w}^{(V)}(r) & \text{if } r\neq p
-      \end{cases} 
-      \]
-We also need to understand $I^{(W)}_w$ for $w \in \{l,l+1,\ldots,j,j+1\}$.
-For the majority of these vertices, we use the following observation: if $p$ is the first propagator to be assigned a value by $I_w^{(W)}$, then the remainder of $I_w^{(W)}$ proceeds identically to the assignments of $I^{(V)}_{w+1}$.
-Thus we have for any $0\leq b <a$
-    \[
-    I_{l+b}^{(W)}(r) = \begin{cases}
-      l+b & \text{if } r=p\\
-      I_{l+b+1}^{(V)}(r) & \text{if } r\neq p
-    \end{cases}
-    \]
-Similarly, if $j$ is in the support of $p$, then we have
-     \[
-       I_j^{(W)}(r) = \begin{cases}
-         j & \text{if $r=p$ and $j$ is in the support of $p$}\\
-         I_{j+1}^{(V)}(r) & \text{if $r\neq p$ and $j$ is in the support of $p$}\\
-       \end{cases}
-       \]
-If $j$ is not in the support of $p$, then we must be in the second case of Figure~\ref{fig 3 cases} with two vertices in the right hand region.
-In this case, if we start the algorithm at $j$ we need to know whether there will be any unassigned propagators other than $p$ when we reach vertex $i$, so as to know what $p$ contributes.
-
-Consider the WLD $X$ formed from $V$ by moving the second end of $q$ to the edge $j-1$ instead of $j$.
-$X$ is still admissible since we have not decreased the support of any set of propagators, so the induction hypothesis applies to it as well.
-Note that $J_{j}^{(V)}(r) = J_{j}^{(X)}(r)$ for all $r\neq p$ and $J_{j}^{(X)}(r) = J_{j+1}^{(X)}(r)$ for $r\neq q,p$.
-Additionally $I_{j+1}^{(X)}(q) = i$ by the induction hypothesis applied to $X$, and so if we start at $j+1$ and assign propagators to vertices according to the algorithm, when we reach vertex $i$ in $X$ all propagators other than $q$ must have been assigned.
-Therefore if we start at $j$ in $W$, we first assign $q$ to $j$ then proceed to assign as in $X$ starting at $j+1$, and hence when we get to $i$ the only remaining unassigned propagator is $p$.
-Therefore
-       \[
-       I_j^{(W)}(r) = \begin{cases}
-
-       m & \text{if $r =p$ and $j$ is not in the support of $p$} \\
-       I_{j}^{(V)}(r) & \text{if $r\neq p$ and $j$ is not in the support of $p$}\end{cases}
-       \] 
-Finally, we consider what happens when we start the algorithm at vertex $j+1$. If $j+1$ is in the support of $p$ then we can argue as above to get
-\[
-       I_{j+1}^{(W)}(r)  = \begin{cases}
-         j+1 & \text{if $r=p$ and $j+1$ is in the support of $p$}\\
-         I_{j+2}^{(V)}(r) & \text{if $r\neq p$ and $j+1$ is in the support of $p$}.
-       \end{cases}
-       \]
-Now suppose $j+1$ is not in the support of $p$.
-If we start at $j+1$ we need to know whether there are any unassigned propagators supported on edge $i$ when we reach vertex $i$.
-We already know that $J_q^{(V)}(j+1) = \{j+1\}$; in particular this means that $q$ contributes $i$ in $I_{j+2}^{(V)}$.
-However the construction of $I^{(V)}_{j+1}$ first associates $q$ to $j+1$ and then proceeds identically to $I^{(V)}_{j+2}$.
-In particular if $i$ was assigned in $I^{(V)}_{j+1}$, then it would not be available to assign to $q$ in $I^{(V)}_{j+2}$ as all other propagators supported at $i$ in $V$ come before $q$.
-
-Therefore $p$ is the only potentially unassigned propagator on edge $i$ when we reach vertex $i$ in $W$, and
-    \[
-    I_{j+1}^{(W)}(r)  = \begin{cases}
-      m & \text{if  $r=p$ and $j+1$ is not in the support of $p$}\\
-      I_{j+1}^{(V)}(r) & \text{if  $r\neq p$ and $j+1$ is not in the support of $p$}
-    \end{cases}
-    \]
-We can now describe the intervals $J^{(W)}_r(*)$ for the first two cases of Figure~\ref{fig 3 cases}.
-For $r \neq p$ the intervals are clearly still cyclic and appear in the correct order, and we can assemble the intervals for the $J_p^{(W)}(*)$ as follows.
-    \begin{itemize}
-      \item 
-    If $m=l$ then either $a=2$ (so $l+1=m+1$, $j=m+2$, and $j+1=m+3$) or $a=3$ (so $l+1=m+1$, $l+2=m+2$, $j=m+3$, and $j+1$ is not in the support of $p$), and in both cases
-    \begin{gather*}
-    J^{(W)}_p(m) = [m+4, m], \qquad  J^{(W)}_p(m+1) = \{m+1\}, \\ J^{(W)}_p(m+2) = \{m+2\}, \qquad  J^{(W)}_p(m+3) = \{m+3\},
-    \end{gather*}
-    which are nonempty and otherwise as required.
-  \item
-        If $m=i+1$ then checking each of the three different possibilities for $a$ we likewise get
-    \begin{gather*}
-    J^{(W)}_p(m) = [m+4, d-1], \qquad  J^{(W)}_p(m+1) = [d, m+1], \\  J^{(W)}_p(m+2) = \{m+2\}, \qquad  J^{(W)}_p(m+3) = \{m+3\},
-    \end{gather*}
-    which are nonempty and otherwise as required.
-  \item If $m=i$ then $a=1$ or $a=2$, in the former case $l=m+2$, $j=m+3$ and $j+1$ is not in the support of $p$ so
-    \begin{gather*}
-    J^{(W)}_p(m) = \{m+4\}, \qquad  J^{(W)}_p(m+1) = [m+5, d-1], \\  J^{(W)}_p(m+2) = [d, m+2], \qquad  J^{(W)}_p(m+3) = \{m+3\},
-    \end{gather*}
-    while in the latter $l=m+2$, $l+1=m+3$, and $j$ and $j+1$ are not in the support of $p$ so
-    \begin{gather*}
-    J^{(W)}_p(m) = [m+4, j+1], \qquad  J^{(W)}_p(m+1) = [j+2, d-1], \\  J^{(W)}_p(m+2) = [d, m+2], \qquad  J^{(W)}_p(m+3) = \{m+3\},
-    \end{gather*}
-    which are again as required.
-    \end{itemize}
-
-\textbf{Third case}: In this case there are no non-supporting vertices $l, l+1, \ldots$ inside $q$.
-Again write $p=(m, m+2)$ where $m\in \{j, j+1, j+2\}$.
-We proceed as in the previous cases, by computing $I^{(W)}_w$ for vertices $w$ in roughly increasing order of difficulty.
-
-For $w \in [n]\backslash\{j+1,m,m+1,m+2,m+3\}$: if $w\in J_q^{(V)}(i)$ or $w\in J_q^{(V)}(i+1)$ then
-    \[
-    I_w^{(W)}(r) =  \begin{cases}
-        m & \text{if } r=p \\
-        I_{w}^{(V)}(r) & \text{if } r\neq p
-      \end{cases} 
-    \]
-    while if $w\in J_q^{(V)}(j)$ then
-    \[
-    I_w^{(W)}(r) =  \begin{cases}
-        \max\{m, j+1\} & \text{if } r=p \\
-        I_{w}^{(V)}(r) & \text{if } r\neq p
-      \end{cases} 
-    \]
-
-Finally, for $j+1$ and the vertices in the support of $p$, we have
-
-\begin{align*}
-  I_{j+1}^{(W)}(r) &= \begin{cases}
-    j+1 & \text{if } r=q\\
-    j+2 & \text{if } r=p\\
-    I_{j+3}^{(V)}(r) & \text{if } r\neq p,q
-  \end{cases}\\
-  I_m^{(W)}(r) &= \begin{cases}
-    m & \text{if $r=p$ and $q$ not supported on $m$}\\
-    m+1 & \text{if $r=p$ and $q$ supported on $m$}\\
-    I_{m}^{(V)}(r) & \text{if } r\neq p
-  \end{cases}\\
-  I_{m+1}^{(W)}(r) & = \begin{cases}
-    m+1 & \text{if $r=p$ and $q$ not supported on $m+1$} \\
-    m+2 & \text{if $r=p$ and $q$ supported on $m+1$} \\
-    I_{m+1}^{(V)}(r) & \text{if } r\neq p,q
-  \end{cases}\\
-  I_{m+2}^{(W)}(r) & = \begin{cases}
-    m+2 & \text{if } r=p \\
-    I_{m+3}^{(V)}(r) & \text{if } r\neq p
-  \end{cases}\\
-  I_{m+3}^{(W)}(r) & = \begin{cases}
-    m+3 & \text{if } r=p \\
-    I_{m+4}^{(V)}(r) & \text{if } r\neq p
-  \end{cases}
-\end{align*}
-Note that $I_{m+2}^{(V)}(r) = I_{m+3}^{(V)}(r)$ for all propagators $r$ in $V$, and that if $j+1\not\in\{m, m+1, m+2, m+3\}$ then $j+2$ and $j+3$ are non-supporting vertices in $V$, so in that case $I_{j+2}^{(V)}(r) = I_{j+3}^{(V)}(r) = I_{j+4}^{(V)}(r)$ for $r$ in $V$.
-
-Therefore, once again we can see that the $J_r^{(W)}(*)$ are cyclic for all $r\neq p$ in $W$.  Assembling the intervals for $p$ we have:
-\begin{itemize}
-\item if $m=j$ then
-\begin{gather*}J_p^{(W)}(m) = [m+4,e-1], \qquad  J_p^{(W)}(m+1) = [e,m], \\  J_p^{(W)}(m+2) = [m+1,m+2], \qquad  J_p^{(W)}(m+3) = \{m+3\},\end{gather*}
-\item if $m=j+1$ then
-\begin{gather*}J_p^{(W)}(m) = [m+4,m-1], \qquad J_p^{(W)}(m+1) = [m,m+1], \\  J_p^{(W)}(m+2) = \{m+2\}, \qquad  J_p^{(W)}(m+3) = \{m+3\},\end{gather*}
-\item if $m=j+2$ then
-\begin{gather*}J_p^{(W)}(m) = [m+4,m], \qquad  J_p^{(W)}(m+1) = \{m+1\}, \\  J_p^{(W)}(m+2) = \{m+2\}, \qquad  J_p^{(W)}(m+3) = \{m+3\}.\end{gather*}
-\end{itemize}
-The result now follows by induction.
-\end{proof}
-
-We need one more lemma before we can prove that Algorithm~\ref{alg:put GN on WLD} does in fact give the Grassmann necklace of the positroid associated to $W$.
-
-\begin{lem}\label{lem basis as perm}
-Let $W = (\cP,[n])$ be an admissible Wilson loop diagram and let $M(W)$ be its associated matroid.
-A subset $J \subseteq [n]$ is an independent set of $M(W)$ if and only if there exists an injective set map $f : J \rightarrow \cP$ with the property that for each $j\in J$ we have $j \in V(f(j))$.
-\end{lem}
-
-One of the most important uses of this lemma is for bases.
-The lemma says that a subset $J$ of $[n]$ is a basis of $M(W)$ if and only if there is a set bijection between $J$ and $\cP$ with the property that for each $j\in J$ the propagator associated to $j$ under the bijection is supported on vertex $j$.
-
-\begin{proof}
-Because the nonzero entries of $C(W)$ are independent indeterminants, $J$ is an independent set is if and only if there is some choice of $|J|$ nonzero entries of $C(W)$ one in each row associated to an element of $J$ and each in different columns.
-
-Each entry in $C(W)$ identifies a propagator by the row of the entry and a vertex by the column of the entry.  The entry is nonzero if and only if the propagator is supported on that vertex.
-
-Consequently, a choice of $|J|$ nonzero entries of $C(W)$ one in each row associated to an element of $J$ and each in different columns is equivalent to an assignment of the propagators of $J$ to supporting vertices so that no two are assigned to the same vertex.
-Such an assignment of the propagators of $J$ to supporting vertices is exactly a map $f$ as described in the statment, hence proving the result.
-\end{proof}
-
-\begin{thm}\label{res:alg gives GN}
-The sequence of $k$-subsets $(I_1,\dots,I_n)$ obtained by applying Algorithm~\ref{alg:put GN on WLD} to all vertices of an admissible diagram $W$ is exactly the Grassmann necklace of $M(W)$.
-\end{thm}
-
-\begin{proof}
-For each $i \in [n]$, let $I_i$ be the set of vertices assigned to the propagators of $W$ by Algorithm~\ref{alg:put GN on WLD} with starting vertex $i$.
-By Lemma~\ref{GN alg well defined}, we know that $|I_i| = k$ for each $i \in [n]$.
-By [ref], the sequence $(I_1, \dots, I_n)$ is a Grassmann necklace if and only if $I_{i+1} \supseteq I_i \backslash \{i\}$ for all $i \in [n]$.
-
-Suppose for a contradition that there exists an admissible diagram for which there exists an $i$ with $k\in I_{i\backslash\{i\}}$ and $k \not\in I_{i+1}$.
-Fix $n$.
-Let the triple $(W, i, k)$ be such a counterexample on $n$ vertices which is minimal with respect to the number of propagators.
-%, and among all those counterexamples on $n$ vertices with the same number of propagators, let $(W,i,k)$ be minimal with respect to the distance from $i$ to $k$ in the $\leq _i$ order.
-
-If $i \not\in I_i$, then there are no propagators supported on $i$ at all.
-In this case it is clear that applying Algorithm~\ref{alg:put GN on WLD} at vertex $i$ and vertex $i+1$ produces exactly the same result, i.e.
-$I_{i+1} = I_i$, and so $(W, i, k)$ is not a counterexample at all.
-
-Now suppose that $i \in I_i$.
-Let $p$ be the propagator which contributes $i$ to $I_i$; thus one end of $p$ must lie on either edge $i-1$ or edge $i$.
-In both cases let $b$ denote the edge supporting the other end of $p$.
-
-\textbf{Case I}:  Suppose $p$ has one end on edge $i-1$.
-Then $p$ is not supported on $i+1$, so in building $I_{i+1}$ we will take the same propagators as in the construction of $I_i$ from vertices $i+1$ up to $b-1$, that is $I_{i+1} \cap [i+1,b-1] = I_{i} \cap [i+1,b-1]$.
-Furthermore, by Lemma~\ref{vertex cyclic int lem}, when building $I_{i+1}$ it must happen that $p$ is taken at vertex $b$, as otherwise $b$ would never be contributed by $p$.
-Consequently, in building $I_{i+1}$, when the algorithm reaches vertex $b$ there cannot be any unassigned propagators remaining that are before $p$.
-This is also true in when the algorithm constructing $I_i$ reaches $b$, since the same propagators have been assigned beforehand.
-Finally, we also note that $k\geq_i b+1$.
-
-Let $W'$ be the diagram obtained from $W$ by removing both $p$ and all propagators inside of $p$ (recall Definition~\ref{props inside p}).
-
-By the above observations, if we commence Algorithm~\ref{alg:put GN on WLD} in $W'$ from vertex $b$, then we are in the same situation with respect to unassigned propagators as if we began at $i$ in $W$ and proceeded to $b$ following the algorithm; the propagators we assigned in the latter case are exactly the ones removed to build $W'$.
-Similarly, starting at $i+1$ in $W$ and moving to $b+1$ leaves us in the same situation with respect to unassigned propagators as beginning at $b+1$ in $W'$ would.
-This gives the equations
-\begin{align*}
-  I_i^{(W)} \cap [b,i-1] & = I_b^{(W')} \\
-  I_{i+1}^{(W)} \cap [b+1,i-1] & = I_{b+1}^{(W')}
-\end{align*}
-where the diagram is indicated in the superscript.
-Thus we have $k\in I_b^{(W')}\setminus\{b\}$ and $k\not\in I_{b+1}^{(W')}$, contradicting the minimality of $(W, i, k)$.
-
-\textbf{Case II}: Suppose $p$ has one end on edge $i$.
-Note that by assumption we have $I_i(p) = i$; this means that $p$ must be the first propagator lying on edge $i$, and hence we must have $I_{i+1}(p) = i+1$ as well.
-Observe also that $k\geq_i i+2$ since $i+1\in I_{i+1}$.
-
-Let $W'$ be the diagram obtained from $W$ by removing only the propagator $p$.  Then we have
-\begin{align*}
-  I_i^{(W)} \backslash \{i\} & = I_{i+1}^{(W')} \\
-  I_{i+1}^{(W)} \backslash \{i+1\} & = I_{i+2}^{(W')}
-\end{align*}
-since in both cases the algorithm in $W'$ proceeds identically to that in $W$ after assigning $p$.
-Since $k \neq i+1$, we have $k\in I_{i+1}^{(W')}\setminus\{i+1\}$ but $k\not\in I_{i+2}^{(W')}$, contradicting the minimiality of $(W, i, k)$.
-
-%If $i \not\in I_i$, then there are no propagators supported on $i$ at all.
-In this case it is clear that applying Algorithm~\ref{alg:put GN on WLD} at vertex $i$ and vertex $i+1$ produces exactly the same result, i.e.
-$I_{i+1} = I_i$.
-%
-%Now suppose that $i \in I_i$.  Order $I_i$ and $I_{i+1}$ with respect to $\leq_{i+1}$; in particular, $i$ is the last term in $I_i$ with respect to this ordering.
-%
-%Let $p_1$ be the rightmost propagator supported on $i$, and suppose it is removed at step $a$ with respect to vertex $i+1$.
-This is the first point at which $I_{i+1}$ can differ from $I_i$, i.e.
-we have $I_{i+1} \cap \interval{i+1}{a-1} = I_{i} \cap \interval{i+1}{a-1}$.
-If $a \not\in I_i$, then $p_1$ is the only propagator supported on $a$ at step $a$ with respect to vertex $i+1$.
-All remaining steps are unchanged and we conclude that $I_{i+1} = I_i \backslash \{i\} \cup \{a\}$.
-%
-%If $a \in I_i$, then at step $a$ with respect to vertex $i+1$ there must be another propagator $p_2$ which lies to the left of $p_1$.
-We have $I_{i+1} \cap \interval{i+1}{a} = I_i \cap \interval{i+1}{a}$, and the next possible difference
-%
-%{\color{red}[argh]}
-%
-%Although there are many different subcases to consider, the idea is always the same: we look for the first entry where $I_{i+1}$ and $I_i \backslash \{i\}$ differ (with respect to $<_{i+1}$), and show that this is the only possible difference.
-%
-%The reader should keep in mind that due to Proposition~\ref{res:alg k labels}, the following process cannot double back on itself.
-%
-%\begin{enumerate}
-%\item If $p_1$ contributes $k$ to $I_{i+1}$ and $k \in I_i$, then there is another propagator $p_2$ which was deleted at step $k$ with respect to vertex $i$, but now survives at step $k$ with respect to vertex $i+1$.
-All intermediate steps of the algorithm are unchanged, so $I_{i+1}$ and $I_i \backslash \{i\}$ agree up to (and including) $k$.
-%\item We now look at which label $p_2$ contributes in $I_{i+1}$, and apply the same argument.
-Iterate this process until we find a propagator $p_r$ which is deleted at step $j$ with respect to vertex $i+1$, but $j \not\in I_i$.
-%\item $j \not\in I_i$ implies that $p_r$ is the \textit{only} propagator supported on vertex $j$ at this step.
-There is therefore no knock-on effect, and any remaining propagators in the diagram contribute the same label to both $I_i$ and $I_{i+1}$.
-We conclude that $I_{i+1} = I_i \backslash \{i\} \cup \{j\}$.
-%\end{enumerate}
-
-\medskip
-
-We have shown that $(I_1,\dots,I_n)$ is a Grassmann necklace; it remains to check that this Grassmann necklace corresponds to the positroid $M(W)$.  We need to show that:
-\begin{itemize}
-\item For each $i \in [n]$, $I_i$ is a basis for $M(W)$.
-\item If $J$ is lexicographically smaller than $I_i$ with respect to $<_i$, then $J$ is not a basis for $M(W)$.\note{Si\^an note to self: check whether it's lex smaller or Gale smaller}
-\end{itemize}
-The algorithm is pairing each $j \in I_i$ with a unique propagator supported on that vertex so by Lemma~\ref{lem basis as perm} $I_i$ is a basis for $M(W)$.
-%%Recall from [ref] that a $k$-subset $J \in \binom{[n]}{k}$ is a basis for $\PP_W$ if and only if it has no subset $U \subseteq J$ such that $|U| > |Prop(U)|$.
-It is immediately clear from the construction that $I_i$ is a basis for each $i$: the algorithm is pairing each $j \in I_i$ with a unique propagator supported on that vertex, so $|Prop(U)| \geq U$ for all $U \subseteq I_i$.
-
-%%If $\exists l \in J$ with $Prop(l) = \emptyset$ then $J$ is clearly not a basis, so suppose otherwise.  Write
-%%\[I_i = [i_1 <_i i_2 <_i \dots <_i i_r <_i \dots <_i i_k], \quad J = [i_1 <_i i_2 <_i \dots <_i j_r <_i \dots <_i j_k],\]
-%%so that $I_i$ and $J$ differ for the first time in the $r$th position.  Then
-%%\[r-1 \geq |Prop(\{i_1, \dots, i_{r-1}\})| = |Prop(\{i_1, \dots, i_{r+1},j_r\})|,\]
-%%If $|Prop(\{i_1, \dots, i_{r-1}|\}| = r-1$ then we are done; otherwise
-
-Suppose we have a $k$-set $J$ such that $J$ is a basis for $M(W)$ and yet is lexicographically less than $I_i$ with respect to $<_i$.
-By Lemma~\ref{lem basis as perm} there is a set bijection between $J$ and the propagators of $W$ such that for each $j \in J$, the propagator associated to $j$ is supported on vertex $j$.
-Choose one such bijection.
-For a propagator $p$ of $W$ write $J(p)$ for the associated $j$ according to this bijection.
-
-Since $J$ is lexicographically smaller than $I_i$, the $<_i$-smallest element of the symmetric difference of $J$ and $I_i$ is some $j_0\in J$, $j_0 \not\in I_i$.
-Let $p_1$ be the propagator such that $J(p_1)=j_0$.
-Since $j_0\not\in I_i$ but $p_1$ is supported at $j_0$, then $p_1$ must have been assigned to an earlier vertex by $I_i$, i.e.
-we have $I_i(p_1) <_i j_0$.
-Let $j_1 = I_i(p_1)$.
-
-However, $j_0$ is the $<_i$-smallest element in the symmetric difference of $J$ and $I_i$, so in particular there is some propagator $p_2$ such that $J(p_2)=I_i(p_1)$.
-Now, let $j_2 = I_i(p_2)$ and note that $j_2 \neq J(p_2)$ (since $I_i(p_1)=J(p_2)$), so either $I_i(p_2) \not\in J$ or there is a propagator $p_3$ such that $J(p_3) = I_i(p_2)$.
-Continuing likewise we get a list of vertices $j_k$ and propagators $p_k$ such that $J(p_k) = I_i(p_{k-1}) = j_{k-1}$.
-
-We claim that the propagators and vertices in this list are distinct.
-The claim is proved by induction.
-The definition of $j_0$ gives that $j_0$ and $j_1$ are distinct and that $p_1$ and $p_2$ are distinct.
-Now, suppose we have $p_k$ and $j_k$ with $I_i(p_k)=j_k$ and with $j_k\in J$.
-Then $p_{k+1}$ is the propagator associated to $j_k$ by the fixed bijection we have chosed for $J$.
-Since $j_k$ is distinct from the previous $j_j$, $p_{k+1}$ is distinct from the previous $p_j$.
-Then $j_{k+1} = I_i(p_{k+1})$, but $I_i$ is also a bijection, so since $p_{k+1}$ is distinct from the other $p_j$ we have that $j_{k+1}$ is distinct from the other $j_j$ for $1\leq j\leq k$.
-Additionally $j_{k+1}\neq j_0$ since $j_0\not\in I_i$ but $j_{k+1}\in I_i$.
-This proves the claim.
-
-By finiteness the list must end, and the only way it can end is with some $p_k$ such that $j_k = I_i(p_k)\not\in J$, so in particular $j_k >_i j_0$.
-
-Next we will prove that $j_k <_i j_0$ for all $k > 0$.
-This gives a contradiction to the exisitence of $J$ and completes the proof of the theorem.
-This proof will also be by induction, however, for the induction to go through nicely we will need to prove the following slightly stronger statement:
-for all $k>0$ in the list
-\begin{itemize}
-\item $j_k <_i j_0$ and
-\item either
-  \begin{itemize}
-  \item $I_i(p_k) <_i J(p_k)$, or
-  \item there exists an $ell<k$ such that $I_i(p_\ell) <_i J(p_\ell)$, those two vertices are supported by distinct ends of $p_\ell$ and $p_k$ is on the side of $p_l$ which runs from $I_i(p_\ell)$ to $J(p_\ell)$.
-  \end{itemize}
-\end{itemize}
-
-We already observed that $j_1 <_i j_0$ and $I_i(p_1) <_k J(p_1)$ so we have the base case for the induction.
-Suppose we have the inductive hypothesis for all indices less than $k>1$ and that $p_k$ exists.
-
-By definition $J(p_k) = I_i(p_{k-1}) = j_{k-1}$, so $p_{k-1}$ and $p_{k}$ are both supported at $j_{k-1}$, but $I_{i}(p_{k-1}) = j_{k-1}$.
-Thus either $p_{k-1}$ appears before $p_k$ in the neighbourhood of $j_{k-1}$ or $p_k$ was taken earlier by $I_i$ so $I_i(p_k) <_i I_i(p_{k-1})$.
-In the latter case we are done as $j_k = I_i(p_k) <_i j_{k-1} <_i j_0$ which is what we want.
-So we now assume that $p_{k-1}$ appears before $p_k$ in the neighbourhood of $j_{k-1}$.
-
-If $I_i(p_{k-1}) <_i J(p_{k-1})$ and these are vertices supported by distinct ends of $p_{k-1}$ then $p_{k}$ coming after $p_{k-1}$ around $j_{k-1}$ implies that $p_k$ is on the $I_i(p_{k-1})$ to $J(p_{k-1})$ side of $p_{k-1}$.
-Therefore $j_k = I_i(p_k) \leq_i J(P_{k-1}) + 1$.
-If $k-1 \neq 1$ then this gives $j_k \leq_i I_i(p_{k-2}) + 1 <_i j_0$ so $j_k \leq_i j_0$, but $j_0\not\in I_i$ so $j_k<_i j_0$.
-If $k-1= 1$ then either $j_k <_i j_0$ or we have the configuration
-\[
-\includegraphics{impossible_config}
-\]
-which is impossible as $p_2$ is supported at $j_0$ but not taken in $I_i$ until after $j_0$ even though $j_0\not\in I_i$.
-Taking all of this paragraph together we are done unless $I_i(p_{k-1})\not<_i J(p_{k-1})$ so now assume this.
-
-By the induction hypothesis,  $I_i(p_{k-1})\not<_i J(p_{k-1})$ implies that there exists and $\ell < k-1$ such that $p_{k-1}$ is on the side of $p_{\ell}$ that goes from $I_i(p_\ell)$ to $J(p_\ell)$.
-If $j_{k-1}$ is not in the support of the $J(p_\ell)$ end of $p_\ell$ then $p_{k-1}$ before $p_{k}$ around $j_{k-1}$ implies that $p_k$ is on the same side of $p_\ell$ as $p_{k-1}$ is.
-Then the same arguments as above with $\ell$ in place of $k-1$ give $j_k \leq_i J(P_\ell)+1$ implying $j_k <_i j_0$ which is everything we need.
-
-It remains to consider when $j_{k-1}$ is in the support of the $J(p_\ell)$ end of $p_\ell$, call this case $(*)$.
-Since $J(p_\ell) = j_{\ell-1}$ and the $j_i$ are distinct this means that we have one of the following two configurations
-\[
-\includegraphics{induction_conf}
-\]
-If $p_\ell=p_1$ then $j_{\ell-1}=j_0$ and then as $j_0\not\in I_i$ but $p_k$ is supported at $j_0$ we get $I_i(p_k) <_i j_0$ and also $I_i(p_k) <_i j_{k-1} = J(p_k)$ as the only vertices not yet taken for $I_i(p_k)$ must be before both labelled vertices in the illustration.
-
-If $p_\ell \neq p_1$ then we argue as above with $\ell-1$ in place of $k-1$: in particular $J(p_\ell) = I_i(p_{\ell-1})$ but $p_k$ is supported at $p_{\ell-1}$, so either $I_i(p_k) <_i I_i(p_{\ell-1})$ in which case as before we get desired conclusion, or $p_k$ comes before $p_{\ell-1}$ at $j_{\ell-1}$.
-Then again argue as before getting a new $p_{\ell'}$ in place of $p_{\ell}$, except that then case $(*)$ must occur simultaneously for both $p_{\ell'}$ and $p_{\ell}$ with respect to $p_{k}$.
-This can only occur if $j_{\ell-1}, j_{k-1}, j_{\ell'-1}$ are consecutive.
-Iterating the argument one more time we finally cannot have case $(*)$ as then all neighbouring vertices of $j_{k-1}$ are used up.
-
-This completes the induction and thence the proof of the theorem.
-
-%Since $J$ is lexicographically smaller than $I_i$, the $<_i$-smallest element of the symmetric difference of $J$ and $I_i$ is some $j_0\in J$, $j_0 \not\in I_i$.
-Let $p$ be the propagator such that $J(p)=j_0$.
-Since $j_0\not\in I_i$ but $p$ is supported at $j_0$, then $p$ must have been assigned to an earlier vertex by $I_i$, i.e.
-we have $I_i(p) <_i j_0$.
-Thus the propagator $p$ has the following property, which we call property $A$:
-%\begin{equation}\label{propertyA}\tag{A}I_i(p) <_i J(p) \text{ \ and \ }I_i\cap [i,I_i(p)] = J\cap [i,I_i(p)]. \end{equation}
-%
-%{}From the previous paragraph we conclude that if we ever had a $J$ which is lexicographically less than $I_i$ and yet a basis of $M(W)$, then there exists a propagator $p$ which has property $A$.
-%
-%Finally, we will prove that whenever there is a propagator $p$ which has property $A$ then there is another propagator $r$ which also has property $A$ and for which $I_i(r) <_i I_i(p)$.
-This would lead to an infinte regress, contradicting the finiteness of $I_i$; thus there could be no such $J$, which will complete the proof of the proposition.
-%
-%So suppose $p$ has property $A$.
-The same vertices in $[i,I_i(p)]$ are in the image of the assignment from $J$ and the image of the assignment from $I_i$ so the same number of propagators are assigned to vertices in this interval by each assignment.
-However $p$ is one of the propagators assigned to a vertex in this interval in $I_i$ but not in $J$.
-Thus there exists a propagator $q$ for which $J(q)\in [i,I_i(p)]$ but $I_i(q) >_i I_i(p)$.
-Therefore $J(q)<_i I_i(q)$ and  $I_i\cap [i,J(q)] = J\cap [i,J(q)]$.
-This is analogous to property $A$ but with the roles of $J$ and $I_i$ switched.
-Thus by the same argument we must have a propagator $r$ for which $I_i(r)\in[i,J(q)]$ but $J(r)>_i J(q)$.
-It follows that $r$ also has property $A$ and that
-%\[I_i(r) \leq_i J(q) \leq_i I_i(p)\]
-%\hlfix{as required.}{We need $I_i(r) <_i I_i(p)$ but I'm having trouble seeing it?}
-\end{proof}
-
-In an arbitrary Grassmann necklace, it is possible for an index $i$ to appear in no terms of the Grassmann necklace (a {\em loop}) or in all terms of the necklace (a {\em coloop}).
-Using Theorem~\ref{res:alg gives GN}, a characterization of the loops and coloops of the Grassmann necklace associated to a Wilson loop diagram follows easily.
-
-\begin{cor}\label{no coloops}
-Grassmann necklaces coming from admissible Wilson loop diagrams have no coloops. A vertex $j$ is a loop if and only if $j$ supports no propagators. 
-\end{cor}
-\begin{proof}
-For any $i \in [n]$, $i-1$ is maximal with respect to the $<_{i}$ order.
-Therefore there can be no propagator $p$ with $I_{i}(p) = i-1$ by Lemma~\ref{lem no fourth vertex}, i.e.
-$i-1 \not\in I_{i}$.
-Thus the Grassmann necklace admis no coloops.
-
-If $j \in [n]$ is a loop then $j \not\in I_j$, which can only happen if there are no propagators supported on vertex $j$.
-Conversely, if $j$ supports no propagators, then Algorithm~\ref{alg:put GN on WLD} never assigns a propagator to $j$ and hence $j \not\in I_i$ for all $i \in [n]$.
-\end{proof}
-
-\subsection{Dimension of the Wilson Loop cells}
-
-Our next goal is to show that the dimension of the positroid cell defined by a Wilson loop diagram $(\cP, [n])$ has dimension $3|\cP|$.
-Marcott in ***cite this*** has a different proof which is geometric and more elegant, but it is not easy to track the effect of a particular propagator.
-Our approach is much more explicit.
-
-Recall that the dimension of a positroid cell is equal to the number of plusses in the associated Le diagram \cite[Theorem 6.5]{Postnikov}.
-By combining Algorithms~\ref{alg:put GN on WLD} and \ref{alg:GN to Le} (converting from WLD to Grassmann necklace to Le diagram) we explicitly describe the effect of adding another propagator to a Wilson loop diagram in terms of the plusses of the associated Le diagrams, and hence give a recursive proof of the $3|\cP|$-dimensionality of the cells.
-
-We start with several lemmas, of roughly increasing degree of technicality.
-
-\begin{lem}\label{lem uncovered}
-
-Let $W$ be an admissible Wilson loop diagram with $k$ propagators, and with a vertex $i$ which supports no propagators.
-Let $V$ be $W$ with vertex $i$ removed.
-Then the Le diagram of $W$ is obtained from the Le diagram of $V$ by inserting an extra column containing all $0$s in position $i$ (i.e.
-such that the new column has the label $i$).
-\end{lem}
-
-\begin{proof}
-  By Algorithm~\ref{alg:put GN on WLD} the Grassmann necklace of $W$ is obtained from the Grassmann necklace of $V$ by duplicating the $i$th element of the Grassmann necklace of $V$ (shifting indices as appropriate), and incrementing all indices greater than $i$ in each Grassmann necklace element.
-Formally, if $I_1^{V}, \ldots, I_{n-1}^{V}$ and $I_1^{W}, \ldots, I_n^{W}$ are the Grassmann necklaces of $V$ and $W$ respectively then
-  \[
-  I_j^{W} =
-  \begin{cases}
-    \{\ell \in I_j^{V} : \ell < i\} \cup \{\ell+1 \in I_j^{V} : \ell \geq i\} & \text{if $j\leq i$} \\
-    \{\ell \in I_{j-1}^{V} : \ell < i\} \cup \{\ell+1 \in I_{j-1}^{V} : \ell \geq i\} & \text{if $j > i$.}
-  \end{cases}
-  \]
-
-By Lemma~\ref{no coloops} we know that $i \not\in I_1^W$, and so $i$ must label a horizontal edge on the boundary of the Le diagram of $W$, i.e.
-it must be a column label.
-The shapes of the Le diagram of $V$ and $W$ are the same except for the insertion of this column since $I_1^*$ is the same for $V$ and $W$ except for the incrementation of the indices $\geq i$ in the transition from the necklace for $V$ to the necklace for $W$.
-\end{proof}
-
-\begin{lem}\label{lem dihedral}
-If two Wilson loop diagrams differ by a dihedral transformation then their Le diagrams have same number of plusses.
-\end{lem}
-\begin{proof}
-By \cite[Proposition 17.10]{Postnikov}, the dimension of a positroid (and hence the number of plusses in its Le diagram) is $k(n-k) - A(\pi_W)$, where $A(\pi_W)$ denotes the number of alignments (see \cite[Figure 17.1]{Postnikov} and preceding discussion) of the decorated permutation $\pi_W$ of the positroid associated to $W$.
-
-It can easily be seen from \cite[Section 17]{Postnikov} and Algorithm \ref{alg:put GN on WLD} that dihedral transformations of a Wilson loop diagram $W$ correspond to dihedral transformations of the chord diagram representation of $\pi_W$.
-Since the number of alignments in a chord diagram is preserved under dihedral transformations, the result follows.
-\end{proof}
-
-\begin{lem}\label{lem good p}
-  Let $W$ be an admissible Wilson loop diagram with $n\geq 1$ propagators.
-Then there is some dihedral transformation $W'$ of $W$ such that there is a propagator $p$ of $W'$ with the following properties.
-  \begin{itemize}
-  \item $p = (i, n-1)$ with no propagators inside it (that is $i+2, \ldots, n-2$ do not support any propagators in $W'$).
-  \item Either the edge $i$ in $W'$ only supports $p$ or the edge $i$ in $W'$ supports exactly one other propagator $q = (j, i)$ with no other propagators inside $q$.
-  \end{itemize}
-\end{lem}
-
-\begin{proof}
-  Remove all vertices of $W$ which do not support any propagators to get a weakly admissible Wilson loop diagram $V$.
-Lemma~\ref{lem sian} applied to $V$ gives a length 2 propagator $p$ in $V$ for which either no other propagator is supported on one of the supporting edges of $p$ or there is a second length 2 propagator which is the only other propagator supported on one of the supporting edges of $p$.
-Figure~\ref{fig 3 cases} shows the possible cases, and the reader can easily check that in each case $p$ must be in one of the two situations described above.
-
-  By Lemma~\ref{lem dihedral} there is a dihedral transformation of $V$ which yields a diagram satisfying the statement of the lemma with $p$ and $q$ both length 2.
-Restoring the vertices which do not support any propagators, we obtain a dihedral transformation $W'$ of $W$ as desired (with potentially longer lengths for $p$ and $q$).
-\end{proof}
-
-Combining Lemmas \ref{lem uncovered}, \ref{lem dihedral}, and \ref{lem good p}, it therefore suffices to study the Le diagrams of \hlfix{weakly}{check} admissible Wilson loop diagrams admitting one of the configurations described in Lemma~\ref{lem good p} with propagators $p$ and $q$ (if $q$ exists) both of length 2.
-See Figure~\ref{fig special p} for an illustration of the two possibilities.
-
-The next few lemmas describe how diagrams of this type are related to the corresponding diagram with propagator $p$ removed, first in terms of the Grassmann necklaces and then in terms of the Le diagrams.
-These technical lemmas will form the backbone of the inductive step in the main dimensionality argument.
-
-\begin{lem}\label{lem I}
-Let $W$ be an admissible Wilson loop diagram with $n\geq 1$ propagators, and suppose that $W$ admits one of the configurations described in Lemma~\ref{lem good p}, with $p$ and $q$ (if $q$ exists) both of length 2.
-Let $V$ be $W$ with $p$ removed.
-Then
-
-  \begin{align*}
-    I_1^{W} & = I_1^{V} \cup \{n-3\} \\
-    I_n^{W} & = I_1^{V} \cup \{n\} \\
-    I_{n-1}^{W} & = I_n^{V} \cup \{n-1\} \\
-    I_{n-2}^{W} & =
-    \begin{cases}
-      I_{n-2}^{V}\cup \{n-2\} & \text{if $n-2\not\in I_{n-2}^{V}$} \\
-      I_{n-2}^{V}\cup \{n-1\} & \text{if $n-2\in I_{n-2}^{V}$, $n-1\not\in I_{n-2}^{V}$} \\
-      (I_{n}^{V} - \{n-5\})\cup \{n-1,n-2\} & \text{if $n-1, n-2\in I_{n-2}^{V}$}
-    \end{cases} \\
-    I_{k}^{W} & =
-    \begin{cases}
-      I_k^{V}\cup \{n-3\} & \text{if $n-3 \not\in I_k^{V}$}\\
-      I_k^{V}\cup\{n-2\} & \text{if $n-3\in I_k^{V}$}
-    \end{cases} \\
-    & \text{for $1<k<n-2$}
-  \end{align*}
-\end{lem}
-
-\begin{figure}
- \includegraphics{specialp}
-  \caption{The two cases for $W$ and $p$.  No other propagators can end in the fat red sections.  Other segments may have additional propagators ending in them.}\label{fig special p}
-\end{figure}
-
-\begin{proof}
-
-The two possible situations are illustrated in Figure~\ref{fig special p}. The arguments proceed in a similar manner to Lemma~\ref{vertex cyclic int lem}.
-
-We first consider $I_1^{W}$.
-Note that $n-3 \not\in I_1^{V}$: for the right hand case this is clear from the diagram (since Algorithm~\ref{alg:put GN on WLD} would assign $q$ no later than vertex $n-4$), while for the left hand case it follows from Lemma \ref{lem no fourth vertex}.
-Therefore when we start at vertex 1 and apply the Grassmann necklace algorithm to $W$, $p$ is the only unassigned propagator when we reach vertex $n-3$ and we have $ I_1^{W}(p) = n-3$.
-
-Next consider $I_n^{W}$, i.e.
-the set obtained when we apply the Grassmann necklace algorithm with starting vertex $n$.
-In both cases we have $I_n^{W}(p) = n$.
-We are now at vertex 1, and the unassigned propagators are exactly those that appear in $V$.
-Therefore the algorithm continues as in $I_1^{V}$, i.e.
-we have $I_n^{W} = I_1^{V} \cup \{n\}$.
-By a similar argument, we must have $I_{n-1}^{W} = I_n^{V} \cup \{n-1\}$.
-
-Now consider $I_{n-2}^{W}$.
-If $n-2\not\in I_{n-2}^{V}$ (i.e.
-$n-2$ supports no propagators in $V$), then in $W$ the algorithm assigns $p$ to $n-2$ and this does not affect the rest of the construction of $I_{n-2}^{V}$, so we obtain $I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-2\}$ as above.
-
-On the other hand, if $n-2\in I_{n-2}^{V}$ then we must be in the right hand case of Figure~\ref{fig special p} and the algorithm assigns $q$ to vertex $n-2$ in both $V$ and $W$ (since $q$ is always the clockwise-most propagator supported on vertex $n-2$; see Figure~\ref{fig special p}).
-If $n-1 \not\in I_{n-2}^{V}$, then in $W$ the algorithm assigns $p$ to $n-1$ and then proceeds identically to $I_{n-2}^{V}$ for the remainder of its steps; thus $I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-1\}$ in this case.
-
-Finally, if $n-2,n-1 \in I_{n-2}^{V}$ then the algorithm in $W$ assigns $q$ to $n-2$ and $p$ to $n-1$ as above, but this is different to what occurs in $I_{n-2}^{V}$ so we cannot use the same argument as above.
-We are now at vertex $n$ and only propagators $p$ and $q$ have been assigned; thus we are proceeding as in the construction of $I_n^{V}$ but without propagator $q$.
-By Lemma~\ref{vertex cyclic int lem} we know that $q$ was assigned to $n-5$ by $I_n^{V}$, and the only way this could occur is if all other propagators in $V$ had already been assigned when we reached vertex $n-5$ (see Figure~\ref{fig special p}); thus $q$ was the final propagator to be assigned in $I_n^{V}$.
-Therefore $I_{n-2}^{W} = (I_{n}^{V} \setminus \{n-5\}) \cup \{n-1, n-2\}$; this completes all cases for $I_{n-2}^{W}$.
-
-The arguments for $I_k^{W}$ ($1< k < n-2$) proceed analagously to those of $I_{n-2}^{W}$, with one simplification: we cannot have both $n-3$ and $n-2$ in $I_k^{V}$ since $q$ is the only propagator that could be assigned to either of them, and it cannot be assigned to both.
-
-This covers all cases and hence completes the proof.
-\end{proof}
-
-\begin{lem}\label{lem shape}
-  Let $V$ and $W$ be as in Lemma~\ref{lem I}.
-  The shape of the Le diagram of $V$ can be built from left to right of the following blocks: a rectangle which is 3 columns wide, one more column of the same height, and a partition shape with at most as many rows as the rectangle.
-  The shape of the Le diagram of $W$ can be built from left to right of the following blocks: a rectangle with 3 columns and one more row than the first rectangle of $V$, and the same partition shape as in $V$.
-\end{lem}
-
-\begin{proof}
-See Figure~\ref{fig Le} for an illustration of the shapes described in the statement of the lemma.
-
-Recall that $I_1$ determines the shape of the Le diagram.
-By Lemma~\ref{lem I} we know that $n,n-1,n-2, n-3 \not\in I_1^{V}$ (which yields the leftmost four columns of the diagram for $V$) and that $I_1^{W} = I_1^{V}\cup \{n-3\}$.
-This implies that the right hand boundary of the shape of $V$ is the same as the right hand boundary of the shape of $W$ except that $W$ has one additional row of 3 boxes while $V$ has an additional column in the $n-3$ position; that is, an extra column fourth from the left.
-\end{proof}
-
-As illustrated in Figure~\ref{fig Le}, the pieces of the Le diagrams of $V$ and $W$ will be called $\mathcal{A}$ and $\mathcal{B}$ in what follows.
-Over the course of the next few lemmas we will prove that the plusses in the $\mathcal{B}$ parts of each diagram are identical, and that the relationship between the plusses in the $\mathcal{A}$ regions can be described explicitly.
-
-Note that when we speak of a plus in the Le diagram of $V$ being the same as in $W$ or vice versa, we mean that the position of the plus in $\mathcal{A}$ or $\mathcal{B}$ is the same; because of the column insertion the absolute indices may differ.
-
-\begin{figure}
-  \includegraphics{Le_diagrams}
-  \caption{Le diagrams for $V$ (left) and $W$ (right).}\label{fig Le}
-\end{figure}
-
-%Recall Algorithm~\ref{alg:GN to Le}, which constructs the Le diagram associated to a Grassmann necklace.
-As described in Section [ref], if Algorithm~\ref{alg:GN to Le} places a $+$ in the box with row index $i$ and column index $j$, we say that this plus is in the $i \rightarrow j$ position.
-
-\begin{lem}\label{lem n and n-1}
-Let $V$ and $W$ be as in Lemma~\ref{lem I}.
-Then $I_n^{W}$ and $I_{n-1}^{W}$ together yield the same plusses as $I_n^{V}$ did, along with two extra plusses which appear in the leftmost two boxes of the bottom row of the Le diagram of $W$.
-\end{lem}
-
-\begin{proof}
-By Lemma~\ref{lem I} we have $I_n^{W}= I_1^{V} \cup \{n\}$ and $I_1^{W} = I_1^{V} \cup \{n-3\}$. Thus 
-\[I_1^{W} \setminus I_n^{W} = \{n-3\}, \qquad \qquad I_n^{W} \setminus I_1^{W} = \{n\},\]
-and so by Algorithm~\ref{alg:GN to Le} we have a plus in the $(n-3) \rightarrow n$ position, i.e. in the leftmost box of the bottom row.
-
-Also by Lemma~\ref{lem I} we have $I_{n-1}^{W} = I_n^{V} \cup \{n-1\}$.
-Recall from the proof of Lemma~\ref{lem I} that $n-3,n-2,n-1,n \not\in I_1^V$; therefore $I_1^W\setminus I_{n-1}^W = (I_1^V \setminus I_n^V) \cup\{n-3\}$, and $n-3$ is maximal in this set.
-Similarly,
-\[I_{n-1}^W \setminus I_1^W = (I_n^V \setminus I_1^V) \cup \{n-1\} \subseteq \{n-1,n\},\]
-where the final inclusion follows from the definition of Grassmann necklace.
-In particular, $n-1$ is minimal in this set, so Algorithm~\ref{alg:GN to Le} yields a plus in the $(n-3) \rightarrow (n-1)$ position (i.e.
-the second box in the bottom row of the Le diagram of $W$) along with any plusses yielded by $I_n^V$.
-
-% Additionally $n-3\not\in I_{n}^{V}$ since if it were then $n-3$ would also be in $I_1^{V}$ and hence propagator $p$ could not contribute $n-3$ to $I_1^{W}$ in contradiction to Lemma~\ref{vertex cyclic int lem}.
-Similarly $n-1, n-2\not\in I_n^{V}$.
-Thus the paths putting the plusses in from $I_n^{V}$ lie completely in $\mathcal{B}$ or take some vertical boundary edge $>n-3$ to $n$.
-Now view these paths in the Le diagram of $W$ and note that the path $n-3\rightarrow n-1$ is compatible, and so these paths together build the plusses that $I_{n-1}^{W}$ contributes.
-That is, we get all the plusses from $I_{n}^{V}$ along with a $n-3\rightarrow n-1$ plus, that is a plus in the second to the right box of the bottom row.
-\end{proof}
-
-\begin{lem}\label{lem n-2 good}
-  Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that $n-2 \not\in I_{n-2}^{V}$.
-Then $I_{n-2}^{W}$ contributes all of the same plusses as $I_{n-1}^{V}=I_{n-2}^{V}$, along with a new $(n-3)\rightarrow (n-2)$ plus.
-\end{lem}
-
-\begin{proof}
-If $n-2\not\in I_{n-2}^{V}$ then $I_{n-1}^{V}=I_{n-2}^{V}$ and by Lemma~\ref{lem I} we have $I_{n-2}^{W} = I_{n-1}^{V} \cup \{n-2\}$.
-Note that $n-3\not\in I_{n-2}^{V}$ by Lemma~\ref{lem no fourth vertex}.
-Therefore the paths controlling the plusses contributed by $I_{n-2}^{W}$ are exactly the paths for $I_{n-1}^{V}$ along with the $(n-3)\rightarrow (n-2)$ path.
-This gives the statement of the lemma.
-
-\end{proof}
-
-\begin{lem}\label{lem n-2 bad}
-Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that $n-2,n-1 \in I_{n-2}^{V}$.
-
-Then $I_{n-2}^{W}$ and $I_{n-3}^{W}$ contribute the following plusses to the Le diagram of $W$:
-  \begin{itemize}
-  \item All of the $I_{n-1}^{V}$ plusses.
-  \item An $(n-3)\rightarrow (n-2)$ plus and a $(n-1)\rightarrow (n-1)$ plus.
-  \item In the Le diagram of $V$, $I_{n-2}^{V}$ contributes an $n-5\rightarrow n-2$ plus and no other term in the Grassmann necklace of $V$ gives a plus in this column.
-$I_{n-2}^W$ does not contribute this $+$ but yields an $(n-5)\rightarrow (n-1)$ plus instead.
-  \item All other plusses of $I_{n-2}^{V}$.
-  \item In the Le diagram of $V$, $I_{n-3}^{V}$ gives a plus in the $n-3$ column.  This $+$ is shifted one square to the left (into the $n-2$ column) in the Le diagram of $W$.
-  \item All other plusses of $I_{n-3}^{V}$.
-  \end{itemize}
-Furthermore, no element of the Grassmann necklace of $V$ contributes a $(n-5)\rightarrow (n-1)$ plus.
-\end{lem}
-
-\begin{proof}
-  By Lemma~\ref{lem I} we have $I_{n-2}^{W}= (I_{n}^{V} \setminus \{n-5\})\cup \{n-1,n-2\}$.
-We are necessarily in the case where $W$ admits a propagator $q$ (Case 2 of Figure~\ref{fig special p}) and we can see from the location of $q$ that $n-2\not\in I_{n-3}^{V}$ and that $n-5$ is the largest row index in $\mathcal{B}$.
-Thus this section of the Gramann necklace of $V$ looks like
-  \begin{equation}\label{eq necklace}
-  I_{n-3}^{V} \underset{\substack{n-3\text{ out}\\n-2\text{ in}}}{\rightarrow} I_{n-2}^{V} \underset{\substack{n-2\text{ out}\\n-5\text{ in}}}{\rightarrow} I_{n-1}^{V} \underset{\substack{n-1\text{ out}\\\text{something in}}}{\rightarrow} I_{n}^{V} \underset{\substack{n \text{ out}\\\text{something in}}}{\rightarrow} I_1^{V}
-  \end{equation}
-  where the first ``something'' is either $n$ or an element of $I_1^{V}$ and the second ``something'' is an element of $I_1^{V}$.
-%Additionally all elements not explicitly mentioned must be in $I_1^{V}$ as they remain unchanged through this portion of the necklace.
-
-  Using this information we can determine the symmetric difference of $I_{n-2}^{V}$ and $I_1^{V}$, which has size $\leq 3$ by the definition of a Grassmann necklace.
-We have $n-1, n-2 \in I_{n-2}^{V} \setminus I_1^V$ for certain, and the third element (if it exists) must be $n$.
-On the other hand, we have $n-5 \in I_1^{V} \setminus I_{n-2}^V$, along with at least one and at most two other elements.
-If there is one such element call it $a$.
-If there are two call them $a$ and $b$ with $a>b$.
-
-  This means that the plusses in the Le diagram of $V$ coming from $I_{n-2}^{V}$ are as in the first part of Figure~\ref{fig messy}.
-Stepping to $I_{n-1}^{V}$ simply removes the $n-5\rightarrow n-2$ path (equation \eqref{eq necklace}); this is illustrated in the second part of Figure~\ref{fig messy}.
-
-  \begin{figure}
-    \includegraphics{messy}
-    \caption{Plusses coming from $I_{n-2}^{V}$ (top left),  $I_{n-1}^{V}$ (top right) and $I_{n}^{V}$ (bottom), in the case where $n-1, n-2\in I_{n-2}^{V}$.
-The blue lines are the non-intersecting paths defining the position of the plusses.
-The dashed blue lines may or may not appear, but if one appears then they both do.}\label{fig messy}
-  \end{figure}
-
-  Stepping to $I_{n}^{V}$, $n-1$ is removed and either $n$ is put in if it was not there before, or one of $a$ or $b$ is put in and hence is no longer available as the starting point for a path.
-This gives two possible configurations illustrated in the bottom two parts of Figure~\ref{fig messy}.
-
-  Now we know that $I_{n-2}^{W}  = (I_{n}^{V} - \{n-5\})\cup \{n-1,n-2\}$ so the paths for building plusses from $I_{n-2}^{W}$ go from the set $\{n-5, n-3\}$ along with whichever of $a$ and $b$ is not in $I_{n}^{V}$ to $\{n-2, n-1, n\}$.
-This means that we get plusses as in Figure~\ref{fig messyD} where the left and right cases correspond to the left and right cases in the bottom parts of Figure~\ref{fig messy}
-
-  \begin{figure}
-     \includegraphics{messyD}
-    \caption{Plusses coming from $I_{n-2}^{W}$.}\label{fig messyD}
-  \end{figure}
-
-  This proves the first item of statement of the lemma.
-
-  Now consider $I_{n-3}^{V}$.
-By \eqref{eq necklace} $I_{n-3}^{V}$ contributes almost the same plusses as $I_{n_2}^{V}$: the only difference is that it contributes an $(n-5)\rightarrow (n-3)$ plus in place of the $(n-5)\rightarrow (n-2)$ plus.
-Since we must have $n-3\in I_{n-3}^{V}$ (because propagator $q$ exists in $V$), it follows from Lemma\ref{lem I} that $I_{n-3}^{W} = I_{n-3}^{V}\cup\{n-2\}$.
-Thus the paths for $I^{W}_{n-3}$ are the same as for $I^{V}_{n-3}$ except that the path that did go to $n-3$ now goes to $n-2$.
-This cannot conflict with another path since \eqref{eq necklace} shows that $n-2$ only appears in $I_{n-2}^{V}$ among the necklace elements of $V$.
-
-  Also note that $I_{n-3}^{V}, I_{n-2}^{V}$, and $I_{n-1}^{V}$ share their plusses outside of the $n-3$ and $n-2$ columns.
-This proves the remaining bullet points of the lemma, leaving only the claim about the $(n-5)\rightarrow (n-1)$ plus.
-
-  So suppose there were a $n-5\rightarrow n-1$ plus in the Le diagram of $V$.
-By Algorithm~\ref{alg:GN to Le}, this plus could only be contributed by a necklace term that satisfies $n-5 \not\in I_*^{V}$.
-By \eqref{eq necklace}, the only terms that could have this property are $I_{n-4}^{V}$, $I_{n-3}^{V}$, and $I_{n-2}^{V}$.
-The analysis above shows that it does not come from $I_{n-2}^V$ or $I_{n-3}^V$.
-
-  Recall that $n-5$ is the largest row index in the Le diagram of $V$, and $n-5 \in I_1^V \setminus I_{n-4}^V$ so we do have a path starting at $n-5$.
-Since $n-4 \in I_{n-4}^V$ by the location of the propagator $q$, we must have a path ending at $n-4$.
-Since the paths cannot cross, this implies that $_{n-4}^V$ must contribute a $(n-5) \rightarrow (n-4)$ plus, and hence cannot contribute a $(n-5)\rightarrow (n-1)$ plus.
-
-\end{proof}
-
-\begin{lem}\label{lem other k}
-  Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that if $n-2\in I_{n-2}^{V}$ then also $n-1\in I_{n-2}^{V}$.
-Fix a $k$ in the range $1<k<n-2$.
-Then $I_k^{W}$ contributes the same plusses as $I_{k}^{V}$, except that if $I_{k}^{V}$ contributed a plus in the $n-3$ column then this plus is shifted one square left into the $n-2$ column, and no plus was already in that location in the Le diagram of $W$.
-\end{lem}
-
-\begin{proof}
-Recall that $I_1^W = I_1^V\cup \{n-3\}$ and that $n-2,n-1,n \not\in I_1^W$.
-
-  If $n-3\not\in I_{k}^{V}$ then by Lemma~\ref{lem I} we have $I_{k}^{W} = I_k^{V}\cup \{n-3\}$.
-Then since $n-3$ is the largest element of $I_1^{W}$ this transformation leaves the disjoint paths unchanged and so the plusses carry over from $V$ to $W$ directly.
-
-  If $n-3\in I_{k}^{V}$ then $I_k^V$ must contribute a plus in the $n-3$ column of the Le diagram of $V$, and by Lemma~\ref{lem I} we have $I_{k}^{W} = I_k^{V}\cup \{n-2\}$.
-If $n-2$ supports no propagators in $V$ then certainly no pluses appear in the $n-2$ column of the Le diagram of $V$.
-If $n-2$ supports at least one propagator in $V$ then $n-2 \in I_{n-2}^V$ and so by hypothesis $n-1 \in I_{n-2}^V$ as well.
-By Lemma~\ref{lem n-2 bad}, the only necklace element of $V$ containing $n-2$ is $I_{n-2}^{V}$ and the corresponding plus is not contributed to the Le diagram of $W$ by $I_{n-2}^{W}$.
-
-  Since $n-3 \in I_k^V \setminus I_1^V$, we must have a path from some vertical edge $i$ to the bottom edge $n-3$ in the Le diagram of $V$.
-In the Le diagram of $W$, the index $n-3$ labels a vertical edge with no path starting at it (since $n-3$ belongs to both $I_1^W$ and $I_k^W$), and there must be a path leading to $n-2$ since $n-2 \in I_k^W \setminus I_1^W$.
-By the previous paragraph no other path from $I_k^V$ could end at $n-2$, so since the paths cannot cross we conclude that the $i\rightarrow (n-3)$ path in the Le diagram of $V$ must become a $i\rightarrow (n-2)$ path in the Le diagram of $W$.
-
-   Thus the plus contributed by $I_k^V$ in the $n-3$ column of the Le diagram of $V$ is shifted into the $n-2$ column in the Le diagram for $W$, where there was no plus before, and no other plusses are changed.
-\end{proof}
-
-\begin{thm}
-  The number of plusses in the Le diagram of an admissible Wilson loop diagram is three times the number of propagators.
-\end{thm}
-
-\begin{proof}
-  The proof is by induction on the number of propagators.
-
-  First note that a Wilson loop diagram $W$ with one propagator supported on vertices $i<j<k<\ell$ has Le diagram a single row with $|W|-i$ boxes.
-Labelling the columns from left to right by $|W|, \ldots, |W|-i+1$, by the algorithm there are plusses in the $j$, $k$, and $\ell$ positions.
-
-  Now consider Wilson loop diagrams with $k>1$ propagators.
-By Lemma~\ref{lem uncovered} it suffices to prove the result for weakly admissible Wilson loop diagrams with $k$ propagators and no non-supporting vertices.
-By Lemma~\ref{lem dihedral} it suffices to prove the result for at least one Wilson loop diagram from each dihedral orbit.
-Take a weakly admissible Wilson loop diagram $W$ with $k$ propagators and no non-supporting vertices.
-Make a dihedral transformation of $W$ if necessary so that $W$ has a propagator $p$ with the properties in Lemma~\ref{lem good p} relative to $W$.
-
-  We make one further simplification: if our $W$ is in Case 2 of Figure~\ref{fig special p} and $n-1$ supports only $p$ but $n-2$ supports at least one other propagator, then flip $W$ on the line perpendicular to the edge from $n-2$ to $n-1$ to obtain a diagram with the configuration of Case 1.
-This eliminates the possibility that we could have $n-2 \in I_{n-2}^W$ but $n-1 \not\in I_{n-2}^W$.
-
-  This diagram will be our $W$ for the remainder of the proof. Let $V$ be $W$ with $p$ removed.
-
-  From Lemma~\ref{lem shape} we know how the shapes of the Le diagrams of $V$ and $W$ relate; let $\mathcal{A}$ and $\mathcal{B}$ be as described after that lemma.
-Lemmas~\ref{lem n and n-1}, \ref{lem n-2 good}, and \ref{lem n-2 bad} tell us that the three boxes of the bottom row of the Le diagram of $W$ each have a plus.
-Lemmas~\ref{lem n and n-1}, \ref{lem n-2 good}, \ref{lem n-2 bad}, and \ref{lem other k} show that there is a bijection between the plusses of the Le diagram of $V$ and the plusses of the Le diagram of $W$ that are not in the bottom row.
-This bijection can be described as follows.
-  \begin{itemize}
-  \item All plusses from $\mathcal{B}$ for $V$ maintain their positions in $\mathcal{B}$ for $W$.
-  \item All plusses from the leftmost two columns (the $n$ and the $n-1$ columns) of $\mathcal{A}$ for $V$ maintain their positions in $\mathcal{A}$ for $W$.
-  \item If there is a plus in the $n-2$ column of $\mathcal{A}$ in $V$ then Lemma~\ref{lem n-2 bad} applies, so there is exactly one such plus.
-This plus is mapped to the $(n-5)\rightarrow (n-1)$ plus for $W$.
-  \item All plusses in the $n-3$ column for $V$ are shifted one square to the left in $\mathcal{A}$ for $W$, i.e. into the $n-2$ column.
-  \end{itemize}
-  Note that this map is reversible and hence bijective.
-Indeed, the only possible ambiguity is at the $(n-5)\rightarrow (n-1)$ plus in $W$ (if it exists), which could have come from either of the first or third bullet points.
-However, if the third bullet point applies then by Lemma~\ref{lem n-2 bad} there is no $(n-5)\rightarrow (n-1)$ plus in $V$, i.e.
-the first bullet point does not apply.
-
-  % If the Le diagram for $V$ has a plus in the $n-2$ column then Lemma~\ref{lem n-2 bad} applies.
-By the final part of Lemma~\ref{lem n-2 bad} there is no $n-5\rightarrow n-1$ plus in the Le diagram of $V$, and so the $n-5\rightarrow n-1$ plus of $W$ can be uniquely mapped to the plus in the $n-2$ column of the Le diagram of $V$.
-If the Le diagram for $V$ has no plus in the $n-2$ column, then leave the $n-5\rightarrow n-1$ plus where it is in moving back to $V$.
-This reverses the map.
-
-  By Lemmas~\ref{lem n and n-1}, \ref{lem n-2 good}, and \ref{lem n-2 bad}, the bottom row of the diagram of $W$ always contains 3 new plusses; thus $W$ admits $3k + 3$ plusses in total.
-Applying induction completes the proof.
-
-\end{proof}
-
-\section{Poles of Wilson Loop Integrals}
-
-The results of Section~\ref{sec GN algorithm} allow us to relate the position of propagators in a Wilson loop diagram $W$ to minors of $C(W)$, which we use in this section to understand the denominator of the integral $I(W)$ associated to a Wilson loop diagram (see Definition~\ref{def R(W)}).
-
-The main result of this section is Theorem~\ref{thm denom}, which expresses the denominator $R(W)$ in terms of the Grassmann necklace of $W$.
-This simplifies the computation of $R(W)$ and allows us to directly relate the poles of the integral to the combinatorics of the diagram.
-
-We first give an algorithm which extracts the required minors from the Grassmann necklace.
-
-\begin{algorithm}\label{alg WLD to denom via GN}
-Let $W = (\cP,n)$ be a Wilson loop diagram, and let $C(W)$ be the matrix of $W$ as defined in \eqref{C(W) dfn} (see Section~\ref{section background}).
-\begin{itemize}
-  \item For each $i \in [n]$, we construct a factor $r_i$ as follows:
-    \begin{itemize}
-      %\item Use Algorithm~\ref{alg:put GN on WLD} to obtain a bijection between the propagators and the $i-1$st Grassmann necklace element, $I_{i-1}$.
-(By convention set $I_{-1}=I_n$.)  Write $I_{i-1}(p)$ for the vertex associated to propagator $p$ under this bijection.
-      %\item Use Algorithm~\ref{alg:put GN on WLD} to obtain a bijection between the propagators and the $i$th Grassmann necklace element, $I_{i}$.
-Write $I_{i}(p)$ for the vertex associated to propagator $p$ under this bijection.
-      \item Let $S_i = \{p \in \cP \ | \ I_{i-1}(p) \neq I_i(p)\}$. (By convention, set $I_{-1} = I_n$.)
-	  %\item Write $\Delta_{I_i}$ for the determinant of the $k \times k$ minor of $C(W)$ with columns indexed by $I_i$.
-      \item Let $r_i$ be the determinant of the $|S_i|\times |S_i|$ minor of $C(W)$ with rows indexed by $S_i$ and columns indexed by $I_i(S_i)$.
-%$\Delta_{I_i}$ with all variables from rows associated to $p\not\in S_i$ set to $1$.
-    \end{itemize}
-  \item Define $R = \prod_{i=1}^n r_i$.
-\end{itemize}
-\end{algorithm}
-
-As we discuss the algorithm it will also be useful to have the notation $\Delta_{I_i}$ for the determinant of the $k\times k$ minor of $C(W)$ with columned indexed by $I_i$.
-
-As we take each $r_i$ to simply be the determinant of a particular submatrix of $C(W)$, the sign of each $r_i$ is well-defined.
-The goal is to show that $R$ is equal to the denominator of the Wilson loop diagram as defined in Definition~\ref{def R(W)}.
-%  However, we will not be interested in these signs as they only contribute an overall sign to $R$ and our main theorem in this section (Theorem~\ref{thm denom}) will simply be to show that $R$ is equal up to a $\mathbb{Q}$-multiple to the denominator of the Wilson loop diagram (see Definition~\ref{def R(W)}).
-
-\begin{figure}
-\includegraphics{egWLD_forR}
-\caption{Example WLD for illustrating Algorithm~\ref{alg WLD to denom via GN} and bijections between propagators and vertices for each Grassmann necklace element.}\label{fig R eg}
-\end{figure}
-
-\begin{eg}
-Consider the Wilson loop diagram in Figure~\ref{fig R eg}. Assigning propagators $p$, $q$, $s$ to rows $1,2,3$ respectively, we obtain the matrix
-\[
-C(W) = \begin{bmatrix} a & b & 0 & 0 & 0 & c & d \\ e & f & 0 & 0 & g & h & 0 \\ i & j & 0 & k & l & 0 & 0 \end{bmatrix}
-\]
-The Grassmann necklace of this diagram is 
-\begin{gather*}I_1 = \{1,2,4\}, I_2 = \{2,4,5\}, I_3 = \{4,5,6\}, I_4=\{4,5,6\},\\ I_5=\{5,6,7\}, I_6 = \{6,7,1\}, I_7=\{7,1,2\}. \end{gather*}  
-Figure~\ref{fig R eg} indicates the pairings between propagators and vertices for each $i \in [1,7]$.
-
-From $I_1$ to $I_2$, the propagators $p$ and $q$ change which vertex they are assigned to but $r$ is assigned to vertex 4 in both, so $S_2 = \{p,q\}$.  Then
-\[
-\Delta_{I_2}=\det\begin{bmatrix} b & 0 & 0 \\ f & 0 & g \\ j & k & l \end{bmatrix} = kgb, \qquad r_2 = \det\begin{bmatrix} b & 0 & 0 \\ f & 0 & g \\ 1 & 1 & 1 \end{bmatrix} = gb.
-\]
-where the 1s in the third row of the second matrix correspond to the fact that $I_1(s) = I_2(s)$.  Continuing likewise, we get $r_3 = c$, $r_4=1$ (since $I_4 = I_3$), $r_5 = lhd$, and $r_6 = i$.
-
-At $I_7$ the situation is more complicated: we have $S_7 = \{q,s\}$, so we find that $\Delta_{I_7} = d(ej-fi)$ and $r_7 = ej-fi$.
-This quadratic factor corresponds to the fact that $q$ and $s$ share an edge {\em and} contribute both endpoints of that edge to $I_7$; see Proposition~\ref{prop alg gives rad} below.
-
-Finally, we have $r_1 = (af-be)k$.  Putting everything together, we obtain
-\[
-R = (af-be)kgbclhdi(ej-fi)
-\]
-which is squarefree and contains all factors of $\prod_{i=1}^{n}\Delta_{I_i}$.
-If one were to construct the denominator $R(W)$ associated to this Wilson loop diagram as per Definition~\ref{def R(W)}, we would find that we have $R(W) = R$.
-\end{eg}
-
-\begin{prop}\label{prop alg gives rad}
-  With notation as in Algorithm~\ref{alg WLD to denom via GN} we have the following:
-  \begin{enumerate}
-    \item Each $\Delta_{I_i}$ is homogeneous, as is each $r_i$.
-    \item Each $\Delta_{I_i}$ splits into linear and quadratic factors.
-All linear factors of  $\Delta_{I_i}$ are single variables and all irreducible quadratic factors are $2\times 2$ determinants of single variables.
-    \item Quadratic factors in $\Delta_{I_i}$ arise precisely when propagators $p$ and $q$ are supported on a common edge $(a,b)$ with $I_i(p)=a$ and $I_i(q)=b$.
-    \item $r_i$ divides $\Delta_{I_i}$.
-    \item The ideal generated by $R$ is the radical of the ideal generated by $\prod_{i=1}^{n}\Delta_{I_i}$.
-  \end{enumerate}
-\end{prop}
-
-\begin{proof}
-\begin{enumerate}
-    \item The nonzero entries of $C(W)$ are independent indeterminates and so every $i\times i$ minor of $C(W)$ is either homogeneous of degree $i$ or is $0$.
-Thus each $\Delta_{I_i}$ and each $r_i$ is homogeneous.
-%Furthermore, each row contributes one factor to each term in the expansion of $\Delta_{I_i}$ so the result of setting the variables from a subset of rows to $1$ is still homogeneous.
-Thus each $r_i$ is homogeneous.
-    \item Using the expression for the determinant as a sum over permutations we see that $\Delta_{I_i}$ is a sum over bijections between $I_i$ and $\mathcal{P}$.
-The nonzero terms in this sum are precisely those bijections such that each propagator is associated to one of its supporting vertices in $I_i$, since only those locations in $C(W)$ are nonzero.
-Since the nonzero entries of $C(W)$ are independent there can be no cancellation between terms in this expansion.
-
-Suppose $\Delta_{I_i}$ has an irreducible factor $f$.
-Let $\mathcal{P}'$ be the set of propagators which contribute a variable to $f$ and let $J$ be the set of vertices which contribute a variable to $f$.
-
-The first claim is that the minor of $C(W)$ associated to $\mathcal{P}'$ and $J$ is precisely $f$.
-
-{\em Proof of claim}: By the structure of determinants we know that $\Delta_{I_i} = fg$, where $g$ involves only variables associated to propagators not in $\mathcal{P}'$ and associated to vertices not in $J$.
-
-Expanding out $fg$ yields a signed sum of monomials.
-In each of these monomials, $f$ contributes those variables associated both to a propagator in $\mathcal{P}'$ and to a vertex in $J$, and $g$ contributes those variables associated both to a propagator not in $\mathcal{P}'$ and to a vertex not in $J$, and no other variables appear.
-
-Since there is no cancellation between terms, this means that the full expansion over permutations of $\Delta_{I_i}$ contains no other nonzero terms and hence no other variables.
-Therefore $\Delta_{I_i}$ is equal to the determinant of the matrix obtained by taking the submatrix of $C(W)$ with columns indexed by $I_i$ and setting any variables not appearing in $\Delta_{I_i}$ to $0$.
-This new matrix is, up to permutations of rows and columns, a block matrix with one block for $\mathcal{P}'$ and $J$ and the other block for the complements.
-Thus its determinant, and hence also $\Delta_{I_i}$, is the product of the minors for these two blocks.
-By considering which variables appear, these two factors must also be $f$ and $g$, and so in particular $f$ is the minor of $C(W)$ associated to $\mathcal{P}'$ and $J$.
-This proves the claim.
-
-A consequence of this claim is that every linear factor of $\Delta_{I_i}$ is a $1\times 1$ minor of $C(W)$, hence is a single variable, and every irreducible quadratic factor of $\Delta_{I_i}$ is a $2\times 2$ minor of $C(W)$, hence is a $2\times 2$ determinant of single variables.
-
-All that remains is to prove that $\Delta_{I_i}$ has no irreducible factors of degree 3 or more.
-Suppose for a contradiction that $f$ is a factor of $\Delta_{I_i}$ of degree $\geq 3$.
-Note that by removing the propagators which come before those contributing to $f$ and changing $i$ to be the first vertex which contributes to $f$, we obtain a different admissible diagram for which $f$ still divides $\Delta_{I_i}$ but also $i\in I_i$ and
-$i$ contributes to $f$.
-Showing that this different admissible diagram gives a contradiction is sufficient, and so we may assume that $i\in I_i$ and $i$ contributes to $f$.
-Finally, we can suppose that $W$ is minimal in number of propagators with the above occuring.
-
-Let $p$ be the propagator such that $I_i(p) = i$. There are two cases to consider, depending on which edge $p$ is supported on.  These are illustrated in Figure~\ref{fig no big factors}
-
-\begin{figure}
-  \includegraphics{no_big_factors}
-  \caption{The two cases in the proof that no factors of $\Delta_{I_i}$ have degree 3 or more.}\label{fig no big factors}
-\end{figure}
-
-\textbf{Case 1}: Suppose $p$ has one end on the edge $(i-1, i)$.  Thus $p$ is supported on $(i-1, i, m, m+1)$ for some $m >_i i$, and $I_{i+1}(p) = m$ by Lemma~\ref{vertex cyclic int lem}.
-
-Let $S$ be the set of propagators inside $p$ along with $p$ itself.
-$I_i$ and $I_{i+1}$ can only differ once $p$ contributes to $I_{i+1}$, so $I_i(q) = I_{i+1}(q)$ for each $q \in S \backslash \{p\}$.
-Thus if a propagator contributes $m$ in $I_i$ then it must lie outside $p$.
-
-If neither $m$ nor $m+1$ appear in $I_i$ then by Corollary~\ref{no coloops} $V(p) \cap I_i = \{i\}$, and so the row of $p$ in the matrix of $\Delta_{I_i}$ has only one nonzero entry; hence $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$, which is a contradiction.
-So we must have at least one of $m$ and $m+1$ in $I_i$.
-However, all propagators in $S$ are mapped by the function $I_{i}(\cdot)$ to vertices strictly before $m$, so the matrix giving $\Delta_{I_i}$ has the form
-\[
-\begin{bmatrix} A & B \\ 0 & C\end{bmatrix}
-\]
-where $A$ is the $|S|\times |S|$ matrix indexed by the propagators in $S$ and the vertices in $I_i(S)$.
-No other propagators can be supported on these vertices since all other propagators are outside of $p$, and $p$ is the first propagator supported at $i$; this explains the zero block.
-Therefore $\Delta_{I_i} = \det A \det C$, and both factors are nontrivial since at least one of $m$ and $m+1$ appear in $I_i$.
-If we remove the propagator outside of $p$ that contributes $m$ or $m+1$, we get a smaller diagram for which $\Delta_{I_i} = \det A$.
-This contradicts the minimality of our choices unless $\det A$ is quadratic, which in turn contradicts our assumption that $i$ and $p$ contribute to an irreducible factor $f$ of degree at least 3.
-
-\textbf{Case 2}: Suppose $p$ has one end on the edge $(i, i+1)$.
-If no other propagators are supported on $i$ then the column of $C(W)$ corresponding to vertex $i$ has only one nonzero entry in it, and so $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$; as above, this is a contradiction.
-Thus we can take $q$ to be the propagator such that $I_i(q)=i+1$.
-We know that $q$ has one end on the edge $(i, i+1)$ and is adjacent to $p$ on that edge in the counterclockwise direction (see Figure \ref{fig no big factors}).
-Write $(i, i+1, j, j+1)$ for the support of $q$.
-The situation for $q$ is very similar to case 1: in particular, we have $I_{i+1}(q) = j$ by Lemma~\ref{vertex cyclic int lem} and so if $j\in I_i$ then the propagator which contributes $j$ is outside of $q$.
-
-Similarly to Case 1, let $S$ be the set of propagators inside $q$ along with $p$ and $q$ themselves.
-Then all propagators in $S$ are mapped by $I_i(\cdot)$ to vertices strictly before $j$ and no other propagators are supported on vertices strictly before $j$.
-Thus the matrix giving $\Delta_{I_i}$ has the form
-\[
-\begin{bmatrix} A & B \\ 0 & C\end{bmatrix}
-\]
-where $A$ is the submatrix indexed by the propagators in $S$ and the vertices in $I_i(S)$.
-Again two things can now happen.
-If some vertex $j$ or larger (with respect to $>_i$) belongs to $I_i$ then $B$ and $C$ are at least one column wide, and so the block form of the matrix gives a nontrivial factorization of $\Delta_{I_i}$.
-This yields a contradiction as in Case 1: either $W$ contains unnecessary propagators which contradicts our minimality assumption, or $\det A$ is quadratic which contradicts the assumption that $p$ and $i$ contribute to $f$, an irreducible factor of degree at least 3.
-
-On the other hand, if no vertex $\geq_i j$ is in $I_i$ then $\Delta_{I_i} = \det A$.
-Looking in more detail into $A$, note that the only vertices in the support of $p$ and $q$ which belong to $I_i$ are $i$ and $i+1$, and hence
-\[
-A = \begin{bmatrix} D & 0 \\ E & F\end{bmatrix}
-\]
-where $D$ is the $2\times 2$ matrix indexed by the propagators $p$ and $q$ and the vertices $i$ and $i+1$.
-Thus $p$ and $i$ contribute to a quadratic factor of $\Delta_{I_i}$, once again contradicting our assumptions.
-
-All cases have now been covered and so $\Delta_{I_i}$ has only irreducible factors of degree $2$ or less.
-
-\item Suppose propagators $p$ and $q$ are supported on a common edge $(a,b)$, with $I_i(p)=a$ and $I_i(q)=b$.
-Let $x_{p,a},x_{p,b},x_{q,a},x_{q,b}$ be the associated variables in $C(W)$.
-For any fixed bijection $\sigma$ from $\cP-\{p,q\}$ to $I_i -\{a,b\}$ for which each propagator is supported on its image under the bijection, we can extend $\sigma$ to a bijection of all propagators with $I_i$ in two ways: either $p\mapsto a$ and $q\mapsto b$ or $p\mapsto b$ and $q\mapsto a$.
-The sum of the contributions of all these bijections to $\Delta_{I_i}$ is therefore the product of $x_{p,a}x_{q,b}-x_{p,b}x_{q,a}$ with the minor coming from $\cP-\{p, q\}$ and $I_i - \{a,b\}$.
-Since there is no cancellation of terms in the expansion of $\Delta_{I_i}$, if any other terms appear then they will cause a factor which is not in the form described in the previous part.
-Therefore no such terms exist and $x_{p,a}x_{q,b}-x_{p,b}x_{q,a}$ is a factor of $\Delta_{I_i}$.
-
-Now let $f$ be a quadratic factor of $\Delta_{I_i}$.
-By part (2) we know that $f$ is a $2\times 2$ minor coming from two propagators, call them $p$ and $q$, and two vertices, call them $a <_i b$.
-It remains to show that $a$ and $b$ are adjacent.
-From this we can conclude that $p$ and $q$ each have one end on $(a,b)$, as any other way for both $p$ and $q$ to be supported on two consecutive vertices would contradict noncrossing or the density requirement of admissibility.
-
-As in the proof of part (2), make a new admissible diagram by removing the propagators which come before $f$ and set $i=a$.
-The cases in the proof of part (2) show how $\Delta_{I_i}$ factors: in particular the vertices supporting the other end of $p$ either do not appear in $I_i$, or they contribute to a different factor of $\Delta_{I_i}$ than $p$ and $a$ do.
-By assumption $b$ contributes to the same factor as $a$.
-Therefore $(a,b)$ is an edge.
-
-\item Consider $p\in S_i$, and note that $\Delta_{I_i}$ is homogeneous linear in the variables of the row corresponding to $p$.
-By part (2), either exactly one variable in the row corresponding to $p$ appears in $\Delta_{I_i}$ and this variable is a factor of $\Delta_{I_i}$, or exactly two variables from the row corresponding to $p$ appear in $\Delta_{I_i}$ and they appear as part of a quadratic factor.
-In the first case let the variable be $x$.
-Then $x$ is a factor of $\Delta_{I_i}$ and so in particular the monomial in $\Delta_{I_i}$ corresponding to the bijection between propagators and vertices of $I_i$ associates the column of $x$ to $p$.
-Thus $x$ also appears in $r_i$ and since the matrix for $r_i$ is a minor of the matrix for $\Delta_{I_i}$ and every term in $\Delta_{I_i}$ involves $x$, we also have that every term in $r_i$ involves $x$ so $x$ is a factor of both $r_i$ and $\Delta_{I_i}$ and is the only variable from this row in either polynomial.
-
-Now suppose two variables from the row $p$ appear in a quadratic factor $f$.
-By part (3), there is another propagator $q$ and an edge $(a,b)$ such that $f$ is the $2\times 2$ minor coming from $p, q$ and $a, b$, with $I_i(p)=a$, $I_i(q)=b$.
-There are two situations which can occur, both illustrated in Figure~\ref{fig quadratic}; we show that in both cases it follows that $q \in S_i$ as well.
-
-\begin{figure}
-  \includegraphics{quadratic}
-  \caption{The situations giving a quadratic factor with variables appearing in $r_i$.}\label{fig quadratic}
-\end{figure}
-
-In both cases, since $I_{i-1}(p)\neq a$ by assumption it follows from Lemma~\ref{vertex cyclic int lem} that $I_{i-1}(p) <_{i-1} a$ and no other vertex supporting $p$ lies between $I_{i-1}(p)$ and $a$.
-In the case that $b<_i a$ and $q$ is taken before $p$ in $I_i$, this means that $I_{i-1}(p)=b$ and so $I_{i-1}(q)\neq b$.
-Thus $q\in S_i$ and so $f$ is a factor of $r_i$.
-
-Now consider the case where $a<_i b$, and suppose for contradiction that $q \not\in S_i$, i.e.
-that $I_{i-1}(q) = b$.
-Since $I_{i-1}(p) \neq a$, there must be some other propagator $s$ with $I_{i-1}(s) = a$ (else $I_{i-1}$ assigns $q$ to $a$).
-This propagator cannot lie on edge $(a,b)$ since by Lemma~\ref{vertex cyclic int lem} we must have $I_i(s) = a$ or $b$, contradicting the fact that $I_i(p) = a$ and $I_i(q) = b$; thus $s$ has an end on $(a-1,a)$ and is inside $p$ from the point of view of $i-1$.
-
-Say $s$ is supported on $(j, j+1, a-1, a)$ and $p$ is supported on $(k, k+1, a, b)$ with $i-1 \leq_{i-1} k+1 \leq_{i-1} j+1$.
-But by Lemma~\ref{lem no fourth vertex}, if $I_{i-1}(s) = a$ then $a$ cannot be maximal in the support of $s$ with respect to $<_{i-1}$; thus we must have $i-1 = j+1$, and we are in the situation in figure~\ref{fig part 4}.
-
-\begin{figure}
-  \includegraphics[scale=0.5]{part4}
-  \caption{In order to obtain $I_{i-1}(s) = a$, propagators $s$ and $p$ must each have an end on the edge $(i-2,i-1)$.}\label{fig part 4}
-\end{figure}
-
-Since $p$ changed its association from $I_{i-1}$ to $I_i$, we have $I_{i-1}(p) = i-1$ by Lemma~\ref{vertex cyclic int lem}.
-From figure~\ref{fig part 4} it follows that $I_{i-1}$ assigns $p$ to $i-1$ and then proceeds identically to $I_i$ for all vertices inside $p$, implying that $I_{i-1}(s) = I_i(s)$.
-Since $I_{i-1}(s) = a$ and $I_i(s) \neq a$, this is a contradiction.
-
-Thus $q\in S_i$ after all, and so $f$ is a factor of $r_i$ as required.
-
-% Thus $s$ is supported on $a$ but does not have an edge on $(a,b)$ and so $s$ must have an end on $(a-1, a)$ and so be inside $p$ from the point of view of $i-1$.
-Say $s$ is supported on $(j, j+1, a-1, a)$ and $p$ is supported on $(k, k+1, a, b)$ with $i-1 \leq_{i-1} k+1 \leq_{i-1} j+1$.
-Again by Lemma~\ref{lem susama}, immediately after $s$ contributes $a$ it must contribute $j$ and so $I_i(s)=j$.
-
-% Finally we want to show $I_i(s)=j$ gives a contradiction.
-If $k=j$ then $I_{i}(s)= k$, but $p$ has not yet been taken as $I_i(p)=a$ and $p$ comes before $s$ around $k$, so this is a contradiction.
-If $k+1=j$ then similarly $I_{i}(s)=k+1$ and yet $p$ comes before $s$ around $k$, a contradiction to $I_i(p)=a$.
-Now suppose $k+1 <_{i-1} j$ then we have $i-1 \leq_{i-1} k+1 <_{i-1} I_i(s) = j$ so $i\leq_{i} I_i(s)$ which gives that
-% \[
-% I_i(s) <_i I_{i-1}(s) \qquad \text{and} \qquad I_i(s) <_{i-1} I_{i-1}(s)
-% \]
-% \note{Is this known to be impossible by the proof sketch of Lemma~\ref{lem susama} that you emailed or something similar.
-I'm thinking this proof is already too long and the fact that this is impossible would be better as a lemma.}
-
-\item If $W$ has zero propagators then all $I_i=\emptyset$ and both $R$ and $\prod_{i=1}^n \Delta_{I_i}$ are equal to $1$, so the result holds in this case.
-Now assume $W$ has at least one propagator.
-
-First we show that every factor of $\prod_{i=1}^n \Delta_{I_i}$ divides $R$.
-Take an irreducible factor $f$ of $\prod_{i=1}^n \Delta_{I_i}$.
-There exists some $i$ such that $f|\Delta_{I_i}$ but $f\!\!\nmid\!\!
-\Delta_{I_{i-1}}$, since otherwise the variables corresponding to the propagators contributing to $f$ which do not themselves appear in $f$ could never appear, contradicting Lemma~\ref{vertex cyclic int lem}.
-If $f$ is a linear factor, say from associating propagator $p$ to vertex $a$, then $I_{i}(p)=a$ and $I_{i-1}(p)\neq a$ so this factor appears in $r_i$.
-If $f$ is a quadratic factor, say from associating propagators $p$ and $q$ to vertices $a$ and $b$ respectively, then again we cannot have both $I_{i-1}(p) = a$ and $I_{i-1}(q) = b$, else $f$ divides $\Delta_{i-1}$.
-However, by the proof of part (4), if one of $p,q$ belongs to $S_i$ then the other does as well.
-Thus $f$ divides $r_i$.
-
-Next we need to show that $R$ is squarefree.
-Suppose $f^2|R$.
-If $f$ is a linear factor, say from associating propagator $p$ to vertex $a$, then there must be two distinct points in the Grassmann necklace algorithm where $p$ changes from not being associated to vertex $a$ to being associated to vertex $a$.
-This contradicts Lemma~\ref{vertex cyclic int lem}.
-Now suppose $f$ is a quadratic factor, say from propagators $p$ and $q$ supported on the edge $(a, b)$ with $p$ before $q$ on the edge.
-In this case it is not possible for any $I_i$ to associate $p$ to $b$ and $q$ to $a$.
-Furthermore, we know by part (4) that $p$ changes from not being associated to $a$ to being associated to $a$ if and only if $q$ changes from not being associated to $b$ to being associated to $b$.
-Thus $f^2|R$ implies that twice in the Grassmann necklace $p$ must change from not being associated to vertex $a$ to being associated to vertex $a$.
-This is again a contradiction, and so $R$ is squarefree.
-
-Taking everything together we have that $R|\prod_{i=1}^n \Delta_{I_i}$, $R$ contains all factors of $\prod_{i=1}^n \Delta_{I_i}$ and $R$ is squarefree.
-Therefore the ideal generated by $R$ is the radical of the ideal generated by $\prod_{i=1}^n \Delta_{I_i}$.
-  \end{enumerate}
-\end{proof}
-
-\begin{thm}\label{thm denom}
-  Given any admissible Wilson loop diagram $W$, let $\{I_1, \ldots I_n\}$ be the associated Grasmann necklace.
-Then the denominator of the integral, $R(W)$ (see Definition~\ref{def R(W)}), is the $R$ of Algorithm~\ref{alg WLD to denom via GN}, which is also, up to scalar multiple, the radical of $\prod_{i=1}^n \Delta_{I_i}$, where $\Delta_{I_i}$ is the determinant of the $k \times k$ minor indicated by $I_i$.
-\end{thm}
-
-\note{Note that there is still a mention of scalar multiple in this theorem because it seems to me that the def of radical is only up to scalar multiple, but the part relating $R(W)$ to $R$ is exact with no scalar multiples.}
-
-\begin{proof}
-The equivalence up to scalar multiple of $R$ and the radical of $\prod_{i=1}^n \Delta_{I_i}$ is due to Proposition~\ref{prop alg gives rad}.
-It remains to prove that $R(W)$ is the $R$ of Algorithm~\ref{alg WLD to denom via GN}.
-
-To this end, first note that $R(W)$ and $R$ both have total degree $4|\mathcal{P}|$; the degree of $R(W)$ is immediate from the definition while that of $R$ follows from Lemma~\ref{vertex cyclic int lem}.
-By Proposition~\ref{prop alg gives rad} every factor of $R$ is either a single variable or a quadratic factor coming from two propagators supported on a common edge.
-The factors of each $R_e$ making up $R(W)$ in the notation of Definition~\ref{def R(W)} are all of this form and hence every factor of $R$ divides $R(W)$.
-Finally, since $R$ is squarefree, this implies that $R(W)$ is a scalar multiple of $R$.
-
-Finally then we need to check the scalar.
-By Definition~\ref{def R(W)} each linear factor appears with coefficient $1$ and each $2\times 2$ deteriminant factor appears with the same sign as the determinant of the corresponding minor in $C(W)$.
-Therefore $R=R(W)$.
-\end{proof}
-
-***explain why this result was interesting***
+
+\note{Do we want a conclusion section?}
 
@@
 
+\bibitem{PSpolygon}
+  J\'ozef H. Przytycki and Adam S. Sikora.
+  \newblock Polygon dissections and {E}uler, {F}uss, {K}irkman and {C}ayley numbers.
+  \newblock {\em J. Combin. Theory Ser. A}, 92(1):68--76, (2000). \url{arXiv:math/9811086}.
+
+\bibitem{Stanley}
+  R. P. Stanley,
+  \newblock Enumerative Combinatorics, Vol. 2
+  \newblock Wadsworth (1999)
+
+\bibitem{Ziegler}
+  G. M. Ziegler,
+  \newblock Lectures on Polytopes
+  \newblock Springer GTM 152, (1995)
+
+\bibitem{CSZinequivalent}
+  Cesar Ceballos, Francisco Santos, and G\"unter M. Ziegler,
+  \newblock Many non-equivalent realizations of the associahedron
+  \newblock {\em Combinatorica}, 35(5):513--551, (2015).  \url{arxiv:1109.5544}
+
 \end{thebibliography}

### 2019-03-25 GWLDCII.tex
split into two papers

--- 2019-03-22 General WLD combinatorics.tex
@@
 
-\title{Combinatorics of the geometry of Wilson loop diagrams}
+\title{Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators}
 \author{Susama Agarwala, Si\^an Fryer, and Karen Yeats}
@@
 
-This paper studies the combinatorics of Wilson Loop Diagrams.
-\section{Wilson Loop diagrams}\label{section background}
-
-What are Wilson loop diagrams and their integrals.
+\section{Introduction}
+
+***Some general intro to WLDs.
+It can probably gloss over most of what is already in the other paper, but this time we are going to talk about the denominator, so for context we should probably say something about the integral, and its poles in this intro.
+Possibly also more about the integral should go at the end of the background section.***
+
+In \cite{wilsonloop}, Agarwala and Amat show that Wilson loop diagrams can be interpreted as positroids, a certain well behaved class of realizable matroids.
+This opens up the study of Wilson loop diagrams to techniques from geometry and combinatorics.
+In the companion paper to this one ***cite it*** we looked at equivalence classes of diagrams using matroidal and polytopal tools.
+However, the combinatorial richness of positroids comes from more than just their matroidal nature, but from their many bijections with other interesting combinatorial structures, including plabic graphs, decorated permutations, and Le diagrams, see for instance \cite{Oh2}.
+
+In this paper we will focus on implications of the Le diagrams on the mathematics and physics of Wilson loop diagrams.
+
+\subsection{Roadmap}
+
+Section~\ref{section general background} gives the required background for Wilson loop diagrams (subsection~\ref{section WLD background}) and for positroids and some of their many combinatorial versions (subsection~\ref{sec:positroid background}).
+
+Section~\ref{sec GN algorithm} proceeds to give an algorithm to go directly from a Wilson loop diagram to its Grassmann necklace (Algorithm~\ref{alg:put GN on WLD} and the proof that it is correct in Theorem~\ref{res:alg gives GN}).
+In view of the known combinatorial equivalences, it was already possible to get the Grassmann necklace of a Wilson loop diagram, but it involved going through the matrix $C(W)$ and the positroid as a matroid.
+The direct algorithm shows us directly how each propagator contributes to each element of the Grassmann necklace.
+This idea is crucial for all the arguments of the present paper.
+Along with the algorithm, Section~\ref{sec GN algorithm} contains two key techincal lemmas, Lemma~\ref{lem sian}, the focus of subsection~\ref{sec:propagator configs}, and the cyclic interval lemma, Lemma~\ref{vertex cyclic int lem} in subsection~\ref{sec:GN alg}, which leads into the proof of Theorem~\ref{res:alg gives GN} as well as being important in subsequent sections.
+
+Section~\ref{sec dim} proceeds to show that the dimension of the positroid cell defined by a Wilson loop diagram has dimension three times the number of propagators, Theorem~\ref{thm dim}.
+The proof here is very explicit, keeping track of how a propagator contributes $+$s to the Le diagram, and correspondingly somewhat technical.
+Section~\ref{sec poles} characterizes the denominator of the integral of a Wilson loop diagram in terms of how propagators contribute to the Grassmann necklace.
+This result is also given by an algorithm, Algorithm~\ref{alg WLD to denom via GN}, and theorem, Theorem~\ref{thm denom}.
+
+\section{Background}\label{section general background}
+
+\subsection{Wilson Loop diagrams}\label{section WLD background}
+
+\note{We should be a bit careful about text overlap between the two papers in the WLD background section, as some bits are copied (and potentially also for the intro depending on what we do)}
 
@@
 \end{dfn}
-
-There is one particular type subdiagram that deserves special attention.
-
-\begin{dfn}
-For $W$ an admissible diagram, $(P, V(P))$ is exact if $|V(P)| = |P| + 3$.
-\end{dfn}
-
-The exact subdiagrams define an equivalence relation amongst Wilson loop diagrams.
-
-\begin{dfn}\label{equivdfn} 
-There is an equivalence relationship on the set of admissible Wilson loops diagrams given by the transititve closure the following binary relation: $W = (\cP, [n]) \sim W'= (\cP', n)$ if
-\begin{enumerate}
-\item There exist two different exact subdiagrams, $(P, V(P))$ and $(P', V(P'))$ of $W$ and $W'$ respectively such that $V(P) =  V(P')$.
-\item The complementary subdiagrams are identical: $(\cP \setminus P, V(P)^c) = (\cP' \setminus P', V(P')^c)$.
-\end{enumerate}
-\end{dfn}
-
-\begin{eg} \label{eg:equivdiags}
-Note that since this is an equivalence relation, we may find that two Wilson loop diagrams are equivalent, even if they do not have complements of (non-trivial) exact subdiagrams in common.
-Consider the following three Wilson loop diagrams,
-\bas
-W_1 = \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
-	\begin{scope}
-	\drawWLD{8}{1.5}
-	\drawnumbers
-	\drawprop{1}{0}{4}{0}
-	\drawprop{2}{0}{4}{-1}
-    \drawprop{5}{0}{8}{0}
-    \drawprop{5}{1}{7}{0}
-		\end{scope}
-	\end{tikzpicture} \quad
-W_2 = \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
-	\begin{scope}
-	\drawWLD{8}{1.5}
-	\drawnumbers
-	\drawprop{1}{0}{4}{0}
-	\drawprop{2}{0}{4}{-1}
-    \drawprop{5}{0}{8}{0}
-    \drawprop{6}{0}{8}{-1}
-		\end{scope}
-	\end{tikzpicture} \quad
-W_3 = \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
-	\begin{scope}
-	\drawWLD{8}{1.5}
-	\drawnumbers
-	\drawprop{1}{0}{4}{0}
-	\drawprop{1}{1}{3}{0}
-    \drawprop{5}{0}{8}{0}
-    \drawprop{6}{0}{8}{-1}
-		\end{scope}
-	\end{tikzpicture} .
-\eas
-
-The diagrams $W_1 \sim W_2$ because $(\{(5,8), (5,7)\}, \{5,6,7,8,1\})$ and $(\{(5,8), (7,8)\}, \{5,6,7,8,1\})$ are the corresponding differing subdiagrams.
-Furthermore, there is the equivalence $W_2 \sim W_3$ due to the exact subdiagrams $(\{(1,4), (3,4)\}, \{1,2,3,4,5\})$ and $(\{(1,4), (1,3)\}, \{1,2,3,4,5\})$.
-This forces an equivalence between $W_1$ and $W_3$, even though one cannot partition the propagators of each into a an exact subdiagram (that may vary between the diagrams) and a complement that is fixed.
-\end{eg}
 
@@
 
-\section{Equivalence classes of Wilson loop diagrams}
-
-In \cite{wilsonloop}, Agarwala and Amat show that Wilson loop diagrams can be interpreted as positroids, a certain well behaved class of realizable matroids (this correspondence is stated precisely in Theorem \ref{thm WLD defines matroid} below).
-This opens up the study of Wilson loop diagrams to techniques from geometry and combinatorics.
-In particular we examine the partial result shown in \cite{wilsonloop}, that shows that equivalent Wilson Loop Diagrams define the same matroid.
-In section 2.4, we make the relationship between Wilson Loop diagrams and matroids explicit.
-We count the size of each equivalence class, and enumerate the {\color{violet} the number of said classes}.
-We also show that two Wilson Loop diagrams map to the same matroid if and only if they are equivalent.
-
-In subsection \ref{sec matroid background}, we discuss a few matroidal facts about Wilson loop diagrams.
-In section \ref{sec: polygon partitions}, we show that there is a one to one correspondence between exact subdiagrams of Wilson loop diagrams and triangulated pieces of the corresponding polygon partion.
-In section \ref{sec: exact diagram matroidal props}, we prove some matroidal properties of exact subdiagrams.
-We show that a subdiagram of $W$ defines a uniform matroid if and only if the subdiagram is exact (Theorem \ref{exactuniformthm}).
-Furthermore, this uniform matroid is the restriction of the dual matriod of $W$ restricted to the exact subdiagram (Remark \ref{remark exact dual restiction}).
-The main result of section \ref{sec: matroids and equivalence} shows that that two admissible Wilson loop diagrams define the same matroid if and only if they are equivalent (Theorem \ref{same matroid iff equiv}).
-We obtain a formula for the number of admissible Wilson loop diagrams in each equivalence class (Corollary \ref{number of equiv diagrams}) {\color{violet}as well as the number of equivalence classes}.
-In this way, we give a comple characterization of the relationship between Wilson Loop diagrams and their associated matroids.
-
-\subsection{Wilson loop diagrams as matroids\label{sec matroid background}}
-
-We first give a quick summary of the matroid terminology that we will need; it is not intended as a comprehensive introduction to matroids and the interested reader is referred to [ref][find a good matroid reference].
-
-A {\em matroid} $M = (E,\cB)$ consists of a finite ground set $E$ and a non-empty family $\cB \subseteq \cP(E)$ whose elements satisfy the {\em basis exchange property}: for any distinct $B_1,B_2 \in \cB$ and any $a \in B_1 \setminus B_2$, there exists some $b \in B_2 \setminus B_1$ such that $(B_1 \setminus \{a\})\cup \{b\} \in \cB$ as well.
-The elements of $\cB$ are called the {\em bases} of the matroid.
-Note that the basis exchange property immediately implies that all bases have the same size.
-
-A subset $A \subseteq E$ is called {\em independent} in $M$ if $A \subseteq B$ for some $B \in \cB$, and {\em dependent} else.
-The {\em rank}  $\rk(A)$ of a subset $A \subseteq E$ is the size of the largest independent set contained in $A$.
-The rank of the matroid itself is defined to be $\rk(E)$.
-
-A {\em circuit} in $M$ is a minimally dependent set.
-That is, it is a set $C \subseteq E$ such that $C$ is dependent but $C \setminus \{e\}$ is independent for any $e \in C$.
-A union of circuits is called a {\em cycle}.
-On the other hand, a {\em flat} is a maximally dependent set, i.e.
-a set $F \subseteq E$ such that $\rk(F \cup \{e\}) = \rk(F) + 1$ for any $e \in E \setminus F$.
-Unsurprisingly, a {\em cyclic flat} is a set which is both a flat and a cycle.
-The set of circuits in a matroid uniquely defines that matroid, as does the set of flats; thus one could specify a matroid by listing its independent sets, bases, circuits, or flats.
-[ref]
-
-Finally, we describe several important types of matroids.
-A matroid of rank $k$ with a ground set of size $n$ is called {\em realizable} if there exists some $A \in Gr(k,n)$ whose non-zero $k\times k$ minors are exactly those with columns indexed by elements of $\cB$.
-A {\em positroid} is a matroid which can be realized by an element of the totally nonnegative Grassmannian $\Gr(k,n)$.
-Finally, a {\em uniform matroid} of rank $r$ is a matroid in which any set of size $\leq r$ is independent.
-
-Matroid theory relates to the study of Wilson loop diagrams as follows.
-In \cite{wilsonloop}, Agarwala and Amat show that every admissible Wilson loop diagram with $k$ propagators defines a positroid of rank $k$, and that the independent sets can be read directly from the diagram:
-
-\begin{thm} \label{thm WLD defines matroid} \cite[Theorem 3.6]{wilsonloop} Any admissible Wilson loop diagram $W =(\cP, [n])$ defines a matroid $M(W)$ with ground set $[n]$.
-The independent sets are exactly those subsets $V \subseteq [n]$ such that $\nexists U\subseteq V$ satisfying $|\Prop(U)| < |U|$.
-\label{thm:WLDmatroid}\end{thm}
-In other words, the independent sets of $M(W)$ correspond to the sets of vertices in $W$ such that no subset supports fewer propagators than the vertices it contains.
-
-Throughout, we take the {\em matroid defined by $W$} to be the matroid $M(W)$ of Theorem \ref{thm WLD defines matroid}.
-Note that since vertices of the diagram $W$ correspond to columns of the associated matrix $C(W)$, $M(W)$ can also be thought of as the matroid realized by $C(W)$.
-
-% The identification of Theorem \ref{thm WLD defines matroid} is not 1-1: by \cite[Theorem 1.18]{wilsonloop}, if two admissible Wilson loop diagrams are equivalent (as in Definition~\ref{equivdfn}) then they define the same matroid.
-
-Let $W = (\cP,n)$ be an admissible Wilson loop diagram, and $M(W)$ its associated matroid.
-Where it will not cause confusion we conflate the two objects, identifying vertices of $W$ with elements of the ground set $[n]$ in $M(W)$.
-
-In particular, this allows us to prove results about $M(W)$ by considering the behavior of propagators in $W$.
-We record a few elementary facts about the rank and cycles of $M(W)$ here as an example of this.
-
-\begin{lem}\label{lem facts about WLD matroids}
-Let $W = (\cP,n)$ be an admissible Wilson loop diagram. Then:
-\begin{enumerate}
-\item The rank of a set $V \subseteq [n]$ is bounded above by $\min\{|V|,|\Prop(V)|\}$, with $\rk(V) = |V|$ if and only if $V$ is an independent set.
-%\item Let $v \in [n]$ and $q \in \Prop(v)$.
-Then for any $V \subset [n]$ such that $q \not \in \Prop(V)$, we have $\rk(V \cup \{v\}) = \rk(V) +1$, i.e.
-adding a vertex that supports a new propagator to a set increases the rank of the set.
-\item If $C \subseteq [n]$ is a cycle, then $\rk(C) = |Prop(C)|$.
-\item If $[n]$ can be partitioned into at least two non-empty sets, each of which support different sets of propagators that form a partition of the propagotor set, \bas [n] = \sqcup_i V(P_i) \quad \textrm{s.t.} \quad \sqcup P_i = \cP; \quad V(P_i) \cap V(P_j) = \emptyset; \quad  P_i \cap P_j = \emptyset \;, \eas then the matroid $M(W)$ is seperable, \bas M(W) = \bigoplus_i M(P_i, V(P_i)) \;.\eas
-\item $F(P)$ is a flat of $M(W)$, thus justifying the name ``propagator flat''.
-\end{enumerate}
-\end{lem}
-\begin{proof}
-The first part of (1) is \cite[Equation (9)]{wilsonloop} and surrounding discussion, and the second part is standard matroid theory.
-(2) is \cite[Lemma 3.27]{wilsonloop}.
-(3) is a direct consequence of \cite[Lemma 3.20]{wilsonloop} and the fact that $F(P_1)^c = V(P_1^c)$
-
-To prove (4), we need to show that $F(P)$ is maximally dependent.
-If $F(P) = [n]$ then this is automatic, so suppose not and let $v \in [n] \setminus F(P)$.
-In other words, $v \in V(P^c)$ and so $v$ supports some propagator $q \not\in P$.
-Let $S \subseteq F(P)$ be an independent set of maximal size.
-Then $\Prop(S) \subseteq P$ by (1), and no subset of $S$ supports fewer propagators than the number of vertices it contains (this is the definition of an independent set in $M(W)$).
-Since $v$ supports a new propagator $q \not\in P$, the set $S \cup \{v\} \subseteq F(P) \cup\{v\}$ also satisfies this independence condition.
-Thus $\rk(F(P) \cup\{v\}) = \rk(F(P)) + 1$, as required.
-\end{proof}
-
-Note that this means that the set, $F(\emptyset)$, of non-supporting vertices is the maximal subset of vertices of $W$ of rank $0$. That is, it is the unique flat of rank $0$ in $M(W)$.
-
-\subsection{Polygon partitions of Wilson loop diagrams\label{sec: polygon partitions}}
-
-The equivalence relation on Wilson loop diagrams is defined in terms of exact subdiagrams; thus in order to understand the equivalence, we need a way to extract and compare exact subdiagrams.
-We do this via the notion of a polygon partition of $W$.
-
-\begin{dfn}
-  Let $W = (\cP, [n])$ be an admissible Wilson loop diagram.  The \emph{polygon partition} associated to $W$, denoted $\tau(W)$, is defined as follows.
-  \begin{itemize}
-  \item The vertices of $\tau(W)$ correspond to the edges of $W$.
-  \item Labeling the vertices of $\tau(W)$ with the edge number of $W$gives a cyclic order to the vertices.
-Connecting consecutive vertices gives a graph theoretic cycle called the polygon of $\tau(W)$.
-  \item Each propagator of $W$ defines a chord edge of $\tau(W)$; specifically,  a propagator $(i,j) \in \cP$ defines a chord connecting the vertices $i$ and $j$ in $\tau(W)$.
-  \end{itemize}
-\end{dfn}
-
-\begin{lem}\label{tausimpleplanarlem}
-If $W = (\cP, [n])$ is an admissible Wilson loop diagram, then $\tau(W)$ is a simple planar graph whose outer face is a cycle.
-It is embedded such that the vertices all lie on this infinite face\footnote{That is, it is an \emph{outerplanar} graph}.
-These vertices are cyclically ordered, with a choice of first vertex giving it an additional compatible linear order.
-\end{lem}
-
-\begin{proof}
-Since the vertices of $\tau(W)$ are labeled by the edges of $W$, which are cyclically ordered, this gives an ordering to the vertices and the outer face of $\tau(W)$ is a cycle.
-Since $W$ is admissible, no pairs of propagators cross.
-Therefore, it is a planar embedding.
-Similarly, $W$ does not admit any propagators of the form $p = (i, i+1)$; therefore there is exactly one edge connecting any two adjacent edges of $\tau(W)$.
-Finally, there does not exist two propagators $p,q$ such that both $p$ and $q$ start at edge $i$ and end at edge $j$.
-Therefore, no other two vertices of $\tau(W)$ can be connected by more than one edge.
-Finally, the embedding of $\tau(W)$ is induced from the embedding of the graph $W$.
- \end{proof}
-
-\begin{comment}
-\hlfix{For an admissible $W$ no propagators cross and so no chord edges of $\tau(W)$ cross.  Thus, in graph theoretic language, we can view $\tau(W)$ as a planar embedding of a
-graph with no cut vertices, where all vertices lie on the infinite face, along with a distinguished start vertex and direction around the infinite face.
-From this viewpoint the polygon of $tau(W)$ is the boundary of the infinite face.}{I've smushed this together a bit in the prev.
-lem.
-Tell me if I've missed anything.
-Its a lemma for emphasis, not difficulty}
-\end{comment}
-
-\begin{eg}\label{WLDtopolygonpartition}
-In this example we return to two of the Wilson loop diagrams in Example \ref{eg:equivdiags}. We can pair diagrams with their polygon partitions as follows:
-\bas W_1 = \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
-	\begin{scope}
-	\drawWLD{8}{1.5}
-	\drawnumbers
-	\drawprop{1}{0}{4}{0}
-	\drawprop{2}{0}{4}{-1}
-    \drawprop{5}{0}{8}{0}
-    \drawprop{5}{1}{7}{0}
-		\end{scope}
-	\end{tikzpicture} \quad; \quad
-\tau(W_1) = \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
-	\begin{scope}
-	\drawpolypart{8}{1.5}
-    \drawnumbersshift
-    \drawchord{1}{4}
-    \drawchord{2}{4}
-    \drawchord{5}{8}
-    \drawchord{5}{7}
-	\end{scope}
-	\end{tikzpicture}
-\eas and
-\bas W_3 = \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
-	\begin{scope}
-	\drawWLD{8}{1.5}
-	\drawnumbers
-    \drawprop{1}{0}{4}{0}
-	\drawprop{1}{1}{3}{0}
-    \drawprop{5}{0}{8}{0}
-    \drawprop{6}{0}{8}{-1}	
-		\end{scope}
-	\end{tikzpicture}\quad; \quad
-\tau(W_3) = \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
-	\begin{scope}
-	\drawpolypart{8}{1.5}
-    \drawnumbersshift
-    \drawchord{1}{4}
-    \drawchord{1}{3}
-    \drawchord{5}{8}
-    \drawchord{6}{8}
-	\end{scope}
-	\end{tikzpicture} .
-\eas
-
-\end{eg}
-
-Recall that a planar embedding of a graph is a \emph{triangulation} if all faces, except possibly the infinite face, are triangles.
-
-\begin{dfn}
-  Let $W$ be an admissible Wilson loop diagram and $\tau(W)$ its polygon partition.
-A \emph{triangulated piece} of $\tau(W)$ is a 2-connected subgraph of $\tau(W)$ which is a triangulation.
-We will take the convention that a subgraph consisting of a single chord edge is called a \emph{trivial} triangulated piece.
-A {\em maximal} triangulated piece is one which is not contained in any strictly larger triangulated piece.
-\end{dfn}
-
-\begin{dfn}
- A {\em decomposition} of a polygon partition $\tau(W)$ is a set of 2-connected induced subgraphs of $\tau(W)$ which partition the edges of $\tau(W)$.  
-\end{dfn}
-
-\begin{eg} \label{eg: unique decomposition} For the Wilson loop diagrams and polygon partitions in Example \ref{WLDtopolygonpartition}, the vertex sets $\{1, 2, 3,4\}$ and $\{5, 6, 7, 8\}$ give maximal triangulated pieces for both $\tau(W_1)$ and $\tau(W_3)$.
-The vertex set $\{4,5, 8, 1\}$ is not a triangulation in either polygon partition.
-\end{eg}
-
-\begin{lem} \label{decompositionlem}
-  For $W$ an admissible Wilson loop diagram, the polygon partition $\tau(W)$ has a unique decomposition into maximal triangulated pieces, and edges in the polygon of $\tau(W)$.
-\end{lem}
-
-\begin{proof}
-We begin by giving an algorithm for the decomposition, then prove its uniqueness. Let $W = (\cP, [n])$, with $|\cP| = k$.
-
-By \emph{splitting} a vertex $v$ we will mean replacing $v$ by new vertice $v_1, v_2,\ldots, v_{\text{deg}(v)}$ such that each $v_i$ has exactly one neighbour and the union of the of the $v_i$ is the neighbourhood\footnote{The neighbourhood of a vertex is the set of adjacent vertices} of $v$.
-
-Let $T(W)$ be the dual graph of $\tau(W)$ with the vertex corresponding to the infinite face split.
-%In other words, place a vertex on each finite face of $\tau(W)$.
-These vertices are connected if there is a chord edge separating the edges.
-Furthermore, if the face is bounded by an edge of the polygonal cycle of $\tau(W)$, the corresponding vertex gets a leaf edge for each such boundary.
-Since $\tau(W)$ is an embedded graph (with a fixed distinguished embedding) by Lemma \ref{tausimpleplanarlem}, $T(W)$ is an uniquely defined graph.
-
-Furthermore $T(W)$ is a tree because it is connected, has $n+k+1$ vertices ($k+1$ from the internal faces of $\tau(W)$ and $n$ from the outer face) and $n+k$ edges (since $\tau(W)$ has $n+k$ edges).
-Additionally, since $\tau(W)$ is simple, $T(W)$ has no vertices of degree $2$.
-
-%We claim that $T(W)$ is a tree.
-Since $\tau(W)$ is a planar graph with $k$ chord edges and no internal vertices, there are $k+1$ internal faces of $\tau(W)$.
-Each of these internal faces corresponds to a vertex of $T(W)$, and there are $n$ vertices of $T(W)$ from the splitting of the dual graph, so $T(W)$ has $n+k+1$ vertices in total.
-On the other hand, $T(W)$ has $n+k$ edges, corresponding to the $n +k$ edges of $\tau(W)$.
-Therefore, $T(W)$ is a tree.
-
-Split every vertex of $T(W)$ which has degree $>3$.
-%By construction, each face of $\tau(W)$ is a polygon.
-Therefore, each vertex of $T(W)$ is at least 3 valent (one for each edge of the polygon).
-\hlfix{If split each vertex of $T(W)$ if it is strictly greater than $3$ valent.}{???} (In other words, we fail to split exactly when the face is a triangle).
-The connected components of $T(W)$ correspond to the decomposition of $\tau(W)$ into maximal triangulated pieces and edges originally in the polygon of $\tau(W)$.  Let $f$ be the forest thus obtained.
-The vertices of $f$ either have degree 1 or 3.
-%, (if they correspond leaf vertices) or 3,  (if they correspond to triangular faces).
-Trees of $f$ with no trivalent vertices correspond to either edges in the polygon of $\tau(W)$, if they were originally leaves of $T(W)$, or to maximal trivial triangulated pieces.
-Splitting at all the faces that are not triangles ensures maximality of the decomposition.
-If the splitting were not maximal, then one could add a triangle to a connected component of the splitting, but this would imply that that splitting happened at a valence $3$ vertex.
-
-\bas 
-\begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
-	\begin{scope}
-	\drawpolypart{8}{1.5}
-    \drawnumbersshift
-    \drawchord{1}{4}
-    \drawchord{1}{3}
-    \drawchord{5}{8}
-    \drawchord{6}{8}
- \draw (0,0) node {$\bullet$};
-\draw (-1,.2) node {$\bullet$};	
-\draw (-.5,1.1) node {$\bullet$};
-\draw (.8,-.3) node {$\bullet$};	
-\draw (1.1,-.5) node {$\bullet$};
-\draw(1.1,-.5) -- (.8,-.3) --(0,0)--(-1,.2) -- (-.5,1.1);
-\foreach \i in {1,2,...,8} {
-      \draw (45*\i:2) node {$\bullet$};
-    }
-\draw (45*1:2) --(0,0) -- (45*5:2);
-\draw (45*6:2) -- (.8,-.3);
-\draw (45*8:2) -- (1.1,-.5) -- (45*7:2);
-\draw (45*2:2) -- (-.5,1.1) -- (45*3:2);
-\draw (45*4:2) -- (-1,.2);
-	\end{scope}
-	\end{tikzpicture} \rightarrow 
-\begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
-	\begin{scope}
-	\drawpolypart{8}{1.5}
-    \drawnumbersshift
-    \drawchord{1}{4}
-    \drawchord{1}{3}
-    \drawchord{5}{8}
-    \drawchord{6}{8}
- \draw (.1,.1) node {$\bullet$};
-\draw (.1,-.1) node {$\bullet$};
-\draw (-.1,-.1) node {$\bullet$};
-\draw (-.1,.1) node {$\bullet$};
-\draw (-1,.2) node {$\bullet$};	
-\draw (-.5,1.1) node {$\bullet$};
-\draw (.8,-.3) node {$\bullet$};	
-\draw (1.1,-.5) node {$\bullet$};
-\draw(1.1,-.5) -- (.8,-.3) --(.1,-.1); 
-\draw (-.1, .1) --(-1,.2) -- (-.5,1.1);
-\foreach \i in {1,2,...,8} {
-      \draw (45*\i:2) node {$\bullet$};
-    }
-\draw (45*1:2) --(.1,.1);
-\draw (-.1, -.1) -- (45*5:2);
-\draw (45*6:2) -- (.8,-.3);
-\draw (45*8:2) -- (1.1,-.5) -- (45*7:2);
-\draw (45*2:2) -- (-.5,1.1) -- (45*3:2);
-\draw (45*4:2) -- (-1,.2);
-	\end{scope}
-	\end{tikzpicture}
-\eas
-
-To see uniqueness, consider a different maximal decomposition of $\tau(W)$.
-This induces a splitting on $T(W)$, where each connected component of the new decomposition corresponds to a subtree.
-Call this forest $f'$.
-Since $f' \neq f$, there are two trees, $t$ and $t'$ in $f$ and $f'$ that are distinct, but share at least one edge of $T(W)$.
-Since $f'$ is also maximal, $t'$ is not a subtree of $t$.
-Therefore, the edges of $t'$ can be found in at least two trees in the forest $f$.
-In particular, there is a vertex $v$ in $t'$ that corresponds to a split vertex of $T(W)$ in the original decomposition.
-This implies that $v$ has valence greater than $3$ in $T(W)$, and thus the corresponding face of $\tau(W)$ is not a triangle.
-In other words, the decomposition corresponding to $f'$ is not a triangulation.
-\end{proof}
-
-\begin{cor} \label{maxtriangdisjointcor}
-Given a maximal decomposition of $\tau(W)$, the maximal triangulated pieces are edge disjoint.
-\end{cor}
-
-\begin{proof}
-Consider any two distinct maximal triangulated pieces of $\tau(W)$.
-These two pieces correspond to subtrees of $T(W)$ and intersect, at most, at a vertex in the interior of $\tau(W)$.
-Since the subtrees corresponding to the maximal triangulated pieces are edge disjoint, and the edges of $T(W)$ correspond to the edges of $\tau(W)$, this forces the maximal triangulated pieces to be edge disjoint as well.
-\end{proof}
-
-We are now in a position to relate the triangulated pieces of $\tau(W)$ to exact subdiagrams of $W$.
-
-Every triangulated piece $t$ of an admissible Wilson loop diagram $W$ corresponds to a subdiagram of $W$ by taking the set of propagators $P$ corresponding to edges of $t$ and then taking the subdiagram $W_P = (P, V(P))$.
-Conversely, given a subdiagram $W_P = (P, V(P))$ of $W$ we can obtain a subgraph of $\tau(W)$, called $t$, as follows:
-\begin{itemize}
-\item The vertex set of the subgraph $t$ is
-  \begin{itemize}
-  \item the vertices of $\tau(W)$ corresponding to edges of $W$ defined by cyclically consecutive elements of $V(P)$ as a subset of $[n]$
-  \end{itemize}
-\item The edge set of the subgraph is
-  \begin{itemize}
-  \item the edges of $\tau(W)$ corresponding to propagators of $P$
-  \item along with the outer edges of $\tau(W)$ for which both their end points are in the vertex set
-  \end{itemize}
-\end{itemize}
-Note that the subgraph $t$ depends on how the propagators of $P$ sit inside $[n]$, not on how they sit in $W_P$ itself.
-In particular $t$ is not the subgraph of $\tau(W)$ consisting only of edges corresponding to propagators of $P$.
-
-\begin{lem}\label{lem triang to exact}
-  Let $W$ be an admissible Wilson loop diagram and $\tau(W)$ its polygon partition.
-The triangulated pieces of $\tau(W)$ correspond to the exact subdiagrams of $W$ using the correspondence described above.
-\end{lem}
-
-\begin{proof}
-Let us first record a few standard facts about polygon triangulations (that is, about triangulations with all vertices on the outer face).
-If such a triangulation has $n$ vertices then it has $n$ edges on the polygon (that is, on the outer face) and $n-3$ edges which are not.
-No planar graph with the same vertices and the same outer face can have more edges than the triangulation, and every such simple graph with $n-3$ edges off the outer face is a triangulation.
-
-Since $W$ is admissible, by Lemma \ref{tausimpleplanarlem} $\tau(W)$ is a simple graph.
-Let $t$ be a triangulated piece of the decomposition of $\tau(W)$ given in Lemma \ref{decompositionlem}; note that $t$ cannot be equal to $\tau(W)$ by the definition of admissible diagrams.
-
-If $t$ has 2 vertices then $t$ corresponds to a propagator that connects two non-adjacent edges. Therefore, the trivial triangulation is a trivial exact subdiagram.
-
-Now suppose that $t$ has $m>2$ vertices.
-We count how many edges of $t$ are not on the outer face of $\tau(W)$.
-These are exactly the edges of $t$ defined by propagators of $W$.
-Consider the intersection of $t$ with the outer face of $\tau(W)$: this is a possibly disconnected subgraph of the polygon of $\tau(W)$ and this subgraph has $m$ vertices.
-Call this new subgraph $S$, and let $j$ be the number of connected components of $S$.
-To join the components of $S$ into the outer face of $t$, $t$ must have $j$ edges in its outer face which are not in the outer face of $\tau(W)$.
-Furthermore $t$ has $m-3$ edges not in its outer face and so also not in the outer face of $\tau(W)$.
-Thus there are $m-3+j$ edges of $t$ not in the outer face of $\tau(W)$.
-
-Each of these $m-3+j$ internal edges corresponds to a propagator in $W$; call this set of propagators $P$.
-Next we count the size of $V(P)$.
-Each of the $m$ vertices in the outer face of $t$ corresponds to an edge of $W$.
-These $m$ edges define $j$ connected components of the outer polygon of $W$.
-Thus the set $V(P)$ has $m+j$ vertices.
-In other words,
-\[|V(P)| = m+j = |P| +3\;.\]
-Thus the subdiagram $(P,V(P))$ defined by $t$ is exact.
-
-Conversely, suppose we have an exact subdiagram $(P, V(P))$ of $W = (\cP, [n])$ supported on $|V(P)| = |P|+3$ vertices, and let $t$ be the subgraph of $\tau(W)$ corresponding to $(P,V(P))$.
-
-Suppose $|P|=1$.
-Let $p$ be the element of $P$.
-The exactness condition on $(P, V(P))$ says that the four supporting vertices of $p$ are distinct.
-If the support of $p$ is four consecutive vertices, then $V(p)$ defines three consecutive boundary edges of $W$, so $t$ is a single triangle, hence a triangulated piece.
-If the support of $p$ is not four consecutive vertices, then the vertices which are the ends of $t$ are separated by at least two vertices along the cycle.
-This implies that $t$ is a trivial triangulated piece.
-
-Now suppose $|P|>1$.  Let $j=|P|$, $m=|V(P)|$, and 
-suppose that the set $V(P)$ defines $c$ disjoint cyclic intervals of $[n]$. Then $t$ has $m-c$ vertices.  If $t$ were a triangulation, $t$ would have $j -c$ internal edges.
-
-The graph $t$ has $j$ edges that come from propagators, and $m - 2c$ edges that come from the boundary polygon of $\tau(W)$.
-Since $t$ has $m-c$ vertices, it has $m-c$ external edges, of which $c$ come from propagators.
-Therefore, of the $j$ edges of $t$ that come from propagators, $j-c$ are internal to the connected component.
-Therefore, $t$ is a triangulated piece.
-
-%  The statement of the lemma then follows form the fact that inclusion is preserved under $\tau$ and so maximality also corresponds under $\tau$.
-\end{proof}
-
-To avoid the issue of exact diagrams being subdiagrams of other exact subdiagrams (for instance, any subdiagram $(q, V(q))$, for $q \in \cP$ is exact), we introduce the notion of maximal exact subdiagrams.
-
-\begin{dfn}
-An exact subdiagram $(P, V(P))$ is a {\em maximal exact subdiagram} of $W$ if there is no other exact subdiagram $(Q, V(Q))$ in $W$ that contains $(P,V(P))$ as a strict subdiagram.
-\end{dfn}
-
-\begin{cor} \label{uniqueproppartitioncor}
-Any admissible Wilson loop diagram $W = (\cP, [n])$ can be uniquely decomposed into maximal exact subdiagrams. These maximal subdiagrams partition $\cP$.
-\end{cor}
-
-\begin{proof}
-Combining Lemmas \ref{decompositionlem} and \ref{lem triang to exact} yields the unique decomposition into maximal exact subdiagrams, and Corollary \ref{maxtriangdisjointcor} ensures that no propagator appears in more than one subdiagram in this decomposition.
-Since the chord edges of $\tau(W)$ correspond to the propagators of $W$, the decomposition of $\tau(W)$ induces a partition of $\cP$.
-\end{proof}
-
-\subsection{Matroidal properties of exact subdiagrams \label{sec: exact diagram matroidal props}}
-
-Since Corollary \ref{uniqueproppartitioncor} allows us to decompose any admissible Wilson loop diagram into a collection of maximal exact subdiagrams, in this section we examine the matroid properties of exact subdiagrams more closely.
-In this section, we show prove two results:
-\begin{enumerate}
-\item The matriod assoicated to an exact subdiagram of $W$ can be written as a contraction of the matroid $M(W)$ by the complementary propagator flat (Theorem \ref{exact diagrams contractions}). 
-\item The matroid associated to an exact subdiagram is uniform (Theorem \ref{exactuniformthm} ).
-\end{enumerate}
-
-We begin by proving some useful facts about propagator flats, and flats of matroids associated to admissible Wilson loop diagrams more generally.
-
-\begin{comment}
-
-\begin{dfn}\label{def prop flat} 
-Let $W = (\cP,[n])$ be an admissible Wilson loop diagram and $P \subseteq \cP$. The set $F(P) := V(P^c)^c$ is called the {\em propagator flat} of $P$.
-\end{dfn}
-Thus in Lemma \ref{contractsubdiaglem} above we would contract $M(W)$ by the propagator flat $F(P^c)$ of the {\em complement} of $P$ in order to study $(P,V(P))$.
-The justification for this notation is given by (1) of the next lemma: the set $F(P)$ consists of vertices which {\em only} support propagators in $P$ (or no propagators at all).
-
-\begin{lem}\label{lem properties of prop flats} \sanote{do we need the first 2? They follow directly from the definition 1.2. Do we use them later?}
-Let $F(P)$ be a propagator flat as defined above. Then
-\begin{enumerate}
-\item $F(\emptyset)$ is exactly the set of vertices which support no propagators, while for $P \neq \emptyset$ we have \[F(P) = \big(V(P) \setminus V(P^c)\big) \cup F(\emptyset).\] \note{updated (1) to match new definition of $F(P)$; }
-\item If $Q\subseteq P$ then $F(Q) \subseteq F(P)$.
-\item $F(P)$ is a flat of $M(W)$, thus justifying the name ``propagator flat''.
-\end{enumerate}
-\end{lem} \sanote{I'd like to attach this to the "generic facts about matroids" in lemma 2.2?}
-\begin{proof}
-The proof of (1) and (2) are routine applications of the definition and are omitted.
-
-To prove (3), we need to show that $F(P)$ is maximally dependent.
-If $F(P) = [n]$ then this is automatic, so suppose not and let $v \in [n] \setminus F(P)$.
-In other words, $v \in V(P^c)$ and so $v$ supports some propagator $q \not\in P$.
-Let $S \subseteq F(P)$ be an independent set of maximal size.
-Then $\Prop(S) \subseteq P$ by (1), and no subset of $S$ supports fewer propagators than the number of vertices it contains (this is the definition of an independent set in $M(W)$).
-Since $v$ supports a new propagator $q \not\in P$, the set $S \cup \{v\} \subseteq F(P) \cup\{v\}$ also satisfies this independence condition.
-Thus $\rk(F(P) \cup\{v\}) = \rk(F(P)) + 1$, as required.
-\end{proof}
-
-\end{comment}
-
-\begin{lem} \label{lem decompose flat}Let $F$ be a flat in $M(W)$, and let $C \subseteq F$ be the union of all circuits contained in $F$. Then the following are true:
-\begin{enumerate}
-\item $C = F(\Prop (C))$, i.e. $C$ is a propagator flat.
-\item $F \setminus C$ is an independent set. Furthermore, If $F\setminus C$ is an independent flat if and only if $F(\emptyset) = \emptyset$, that is $W$ has no non-supporting vertices.  
-\end{enumerate}
-\end{lem}
-
-\begin{proof}
-(1) If $F$ is an independent flat, then $C = \emptyset$ and the statement is trivially true. Now suppose that $F$ is a dependent set, so $C$ is non-empty.
-
-Let $v \in C$.
-Clearly $\Prop(v) \subseteq \Prop(C)$.
-Since $F(P)  = V(P^c)^c$, we have $F(\Prop(v)) \subseteq F(\Prop(C))$.
-Since $v \in F(\Prop(v))$ by the definition of propagator flat, we have $v \in F(\Prop(C))$ as required, and $C \subseteq F(\Prop(C))$.
-
-Now suppose there exists some $w \in  F(\Prop(C)) \setminus C$.
-Let $B$ be an independent subset of $C$ of maximal rank; we first show that $B \cup \{w\}$ is a dependent set in $M(W)$.
-By Lemma \ref{lem facts about WLD matroids}, \bas |\Prop(C)| = \rk(C) = |B| = \rk(B) .\eas Since $B \subseteq C$ implies that  $\Prop(B) \subseteq \Prop(C)$, this implies that $\Prop(B) = \Prop(C)$.
-Furthermore, since $w \in F(Prop(C)$, $\Prop(B\cup w) \subseteq \Prop(B)$.
-By Lemma \ref{lem facts about WLD matroids} $\rk (B \cup w) \leq \min\{|B\cup w|, |\Prop(B\cup w)|\}$, and therefore $\rk (B \cup w) < |B\cup w|$.
-That is, $B\cup w$ is a circuit in $F(\Prop(C))$.
-Therefore, $B \cup w \subset C$, leading to a contradiction.
-
-For part (2), first note that $F \setminus C$ is automatically independent as it contains no circuits.
-
-Note that since $F(\emptyset)$ has rank $0$, $F(\emptyset)$ is contained in every flat of $W$. Therefore, if $F(\emptyset) \neq \emptyset$, then $F\setminus C$ cannot be a flat.
-
-If $F(\emptyset) = \emptyset$, for any $e \not\in F$, we certainly have $\rk((F\setminus C)\cup\{e\}) = \rk(F\setminus C) +1$ since $F$ is a flat.
-Now let $e \in C$, and suppose that $\rk((F\setminus C)\cup\{e\}) = \rk(F\setminus C)$.
-This implies that $(F\setminus C)\cup \{e\}$ is dependent, and hence contains a circuit, $S$.
-Since $F(\emptyset) = \emptyset$, this circuit must contain at least two elements but this contradicts the fact that $C$ was the union of all circuits in $F$.
-
-Thus $\rk((F\setminus C)\cup \{e\}) = \rk(F\setminus C) + 1$ for any $e \not\in F\setminus C$, and hence $F\setminus C$ is a flat.
-\end{proof}
-
-\begin{cor} \label{classifyflats}
-If $F$ is a flat of a Wilson loop diagram, it can be written as the disjoint union of a cyclic propagator flat and an independent set and the set of non-supportive vertices. \end{cor}
-
-In particular, any propagator flat can be written as a union of a cyclic propagator flat, an independent set and $F(\emptyset)$ for the appropriate Wilson loop diagram.
-
-Next we examine properties of propagator flats associated to the complement of Wilson Loop diagrams.
-%Finally, we note the differences between subdiagrams of Wilson loop diagrams, and restrictions or cotractions of the associated matroids.
-
-%Given any matroid, one may restrict it to a subset of the base set.
-The bases of the restricted matroid come from intersecting bases of the original with the subset.
-It is worth noting that a the matroid defined by a subdiagram is different from the restriction of the matroid of a Wilson loop diagram to a set of vertices.
-
-% \begin{dfn} \label{restrictiondfn}
-% For $W = (\cP, [n])$, the restricted diagram, $W|_V$ is the matroid defined by only looking at the vertices $V \subset [n]$.
-% \end{dfn}
-
-% The key difference between a subdiagram and a restriction is that the propagator support function does not change in the case of restriction, while it may in the case of a subdiagram.
-In particular, for $v \in V$, $\Prop_W(v) = \Prop_{W|_V}(v)$, while $\Prop_{(P, V(P))} (v) = \Prop_W(v) \cap P$.
-
-% A subdiagram is more closely related to a contracted matroid.
-
-\begin{lem} \label{maxexactcomplementrank}
-Let $W = (\cP, [n])$ be a Wilson loop diagram, and $P \subseteq \cP$. Then: \begin{enumerate}
-\item If $(P,V(P))$ is an exact subdiagram in $W$, then $F(P^c)$ is not an independent flat.
-\item If $(P,V(P))$ is a maximal exact subdiagram in $W$, then $F(P^c)$ is a cyclic flat.
-\item If $(P,V(P))$ is an exact subdiagram in $W$, then $\rk(F(P^c)) = |P^c|$.
-\end{enumerate}
-\end{lem}
-
-\begin{proof}
-%Note that $|P^c|$ is always an upper bound on the rank of $F(P^c)$ for any $P \subseteq \cP$, since $F(P^c)$ supports at most $P^c$ propagators (see Remark \ref{alt F(P) rmk}), and $\rk (F(P^c)) = \min\{ |F(P^c)|, |\Prop(F(P^c))|\}$.
-To show equality, we need to show that $F(P^c)$ is not an independent set and that $\Prop(F(P^c)) = P^c$.
-
-First note that if $(P,V(P))$ is exact then the admissiblity of $W$ guarantees that $F(P^c)$ is a non-empty flat. That is, $V(P) \subsetneq [n]$.
-
-Since $W$ is admissible, we have $n \geq |\cP| + 4$. Rewriting this as
-\[|V(P)| + |F(P^c)|  \geq  |P| + |P^c| +4,\]
-and combining it with the fact that $|V(P)| = |P| + 3$ (from the exactness of $(P,V(P))$), we obtain
-\begin{equation}\label{eq F is dependent}|F(P^c)| > |P^c| \;.\end{equation}
-Equation \eqref{eq F is dependent} is therefore saying that $F(P^c)$ supports fewer propagators than the number of vertices it contains, i.e. $F(P^c)$ is not an independent set.
-
-For part (2), suppose that $(P, V(P))$ is a maximal exact subdiagram. By Corollary \ref{classifyflats} we can decompose $F(P^c)$ as
-\begin{equation}\label{eq decompose F}V(P)^c = F(P^c) = C \sqcup S = F(\Prop(C)) \sqcup S,\end{equation}
-where $C$ is the largest cyclic flat contained in $F(P^c)$ and $S$ is an  independent set. Note that $C$ must be non-empty since $F(P^c)$ is non-empty and dependent (by part (1)).
-
-Since $S$ is an independent set, $\rk(S) = |S|$, and every element of $S$ is independent of $C$, $\rk\big(F(P^c)\big) = \rk(C) + \rk(S)$.
-By Lemma \ref{lem facts about WLD matroids}(2), \ba \rk(S) = \rk\big(F(P^c)\big) -  \rk(S) \leq |P^c| - \rk(C) \;.
-\label{increasingrank} \ea
-
-Let $Q^c = \Prop(C)$.
-Then $C = F(Q^c)$ and, by Lemma \ref{lem facts about WLD matroids}(1), $\rk(C) = |Q^c|$.
-By equation \eqref{increasingrank}, \ba |P| + |S| \leq |P| + |P^c| - \rk(C) = |\cP| - |Q^c| = |Q| \;.
-\label{Qsizebound}\ea From equation \eqref{eq decompose F}, \bas |V(Q)| = V(P) \sqcup S = C^c = F(\Prop(C))^c = F(Q^c)^c = V(Q) \;.
-\eas Combining this with equation \eqref{increasingrank} gives \ba |V(Q)| = | V(P) | + |S| = | V(P) | + 3 + |S| \leq |Q| +3 \;.
-\label{Q defines exact}\ea Since $W$ is admissible, one must have $V(Q) = |Q| +3$, that is the subdiagram $(Q, V(Q))$ is exact.
-
-Next, note that \bas C = F(Q^c) = V(Q)^c \subset F(P^c) = V(P)^c \;,\eas which implies that $P \subseteq Q$.
-That is, $(P, V(P))$ is a subdiagram of $(Q, V(Q))$.
-Since $(P, V(P))$ is maximally exact by hypothesis, and $(Q, V(Q))$ is exact by \eqref{Q defines exact}, we are forced to have $S = \emptyset$.
-Therefore, $F(P^c)$ is a cyclic flat.
-
-To see (3), first note that the second point of this Lemma, combined with Lemma \ref{lem facts about WLD matroids} that
-\bas\rk(F(P^c)) = |\Prop(F(P^c))| = |P^c|.\eas
-
-To prove this in the general case, let let $(R,V(R))$ be an exact subdiagram that is not maximal and $P$ be the maximal exact subdiagram containing it. That is, $R \subsetneq P$.
-
-Since $R \subset P$, $V(P) = V(R) \sqcup S$, where $S = V(P) \setminus V(R)$.
-Since $P$ and $R$ both define exact subdiagrams, we may write $|V(P)| = |V(R)| + |P \setminus R|$, where $S$ is a vertex set of size $|P \setminus R|$ with $(P \setminus R \subset \Prop(S)$.
-Since  $|S| = |V(P) \setminus V(R)| = |P \setminus R| \leq |\Prop(S) |$, by Lemma \ref{lem facts about WLD matroids}, $\rk(S) = |S|$, implying that $S$ is independent.
-Taking the complements, we may write \bas F(R^c ) = F(P^c) \sqcup S \;.\eas Taking the rank of both sides, \bas \rk(F(R^c )) = \rk(F(P^c) \sqcup S ) \leq \rk(F(P^c)) + |S| = |P^c| + |\Prop(S)| \leq |R^c| \;.\eas Combining this with \eqref{eq F is dependent} gives the desired result.
-
-\end{proof}
-
-We are now ready to show that any exact subdiagram $(P, V(P)$ of $W$ can be written as a contraction of $M(W)$ by $F(P^c)$. We begin with a definition.
-
-\begin{dfn}\label{matroid contraction}
-Let $M = (E,\cB)$ be a matroid, and $S \subseteq E$. The {\em contraction} of $M$ by $S$ is the matroid $M/S = (E \setminus S, \cB / S)$, where
-\[\cB / S = \{B \setminus S \ \big| \ |B\cap S | \text{ is maximal amonst all }B \in \cB\}.\]
-\end{dfn}
-
-In \cite{wilsonloop}, Agarwala and Amat show that certain subdiagrams of $W$ can be realized as contractions of $M(W)$:
-
-\begin{lem} \label{contractsubdiaglem} \cite[Theorem 3.33]{wilsonloop} 
-Let $W = (\cP, [n])$ be an admissible Wilson loop diagram and $P \subseteq \cP$.
-If the set $V(P)^c$ has rank $|P^c|$, then the matroid defined by the subdiagram $(P, V(P))$ is equal to the contraction $M(W)/V(P)^c$.
-\end{lem}
-
-\begin{thm} \label{exact diagrams contractions}
-If $(P, V(P)$ is an exact subdiagram of of $W$, one may write \bas M\big((P, V(P))\big) = M(W)  / F(P^c) \;.\eas 
-\end{thm}
-
-\begin{proof}
-This follows from Lemma \ref{matroid contraction}. Lemma \ref{maxexactcomplementrank} shows that the supports of exact subdiagrams satisfy the conditions of this lemma.
-\end{proof}
-
-\begin{rmk} \label{remark exact dual restiction}
-Let $M^*$ denote the dual of a matroid.
-The the dual of a contraction of a matroid is the same as the restriction of the dual matroid by the complement: \bas M / S = M^*|_{S^c} \;.\eas Then Theorem \ref{exact diagrams contractions} implies that, for $(P, V(P))$ an exact subdiagram of $W$ \bas M\big((P, V(P))\big) = M(W)  / F(P^c) = M(W)^*|_{V(P)} \;.\eas
-\end{rmk}
-
-Matroids coming from exact subdiagrams have an especially nice structure, namely, they are uniform.
-Recall from Section \ref{sec matroid background} that a uniform matroid of rank $r$ is one in which all sets of size $ \leq r$ are independent.
-
-\begin{thm} \label{exactuniformthm}
-Let $W':= (P, V(P))$ be a subdiagram of an admissible Wilson loop diagram $W= (\cP, [n])$. Then $W'$ is an exact subdiagram if and only if $M(W')$ is a uniform matroid of rank $|P|$.
-\end{thm}
-
-\begin{proof}
-It follows directly from the definitions that a matroid of rank $r$ is uniform if and only if all circuits have rank $r$; we therefore focus on the circuits of $M(W')$.
-
-We prove the following claim: $W'$ is exact if and only if $V(P)$ contains no circuits $C$ with $\rk C< |P|$ in $(P, V(P))$. Since $\rk(M(W'))$ is bounded above by $|P|$, the result follows.
-
-Suppose $C \subseteq V(P)$ is a circuit of rank $m < |P|$; by Lemma \ref{lem facts about WLD matroids}, we know that $|\Prop_{W'}(C)| = m$ as well, where the subscript to $\Prop$ specifies the diagram we are working in.
-Observe that $\Prop_{W'}(C)\subseteq P$ by definition.
-The set $P \setminus \Prop_{W'}(C)$ is thus nonempty, and we can consider the subdiagram $W'':= (P\setminus \Prop_{W'}(C),V(P\setminus\Prop_{W'}(C))$.
-By the density condition on subdiagrams of admissible diagrams, we have
-\[|V(P\setminus\Prop_{W'}(C))| \geq |P\setminus\Prop_{W'}(C)| + 3.\]
-It is easy to verify that $V(P\setminus\Prop_{W'}(C)) \subseteq V(P)\setminus C$; since $C \subseteq V(P)$ and $\Prop_{W'}(C) \subseteq P$, we can therefore rewrite the previous inequality as
-\[|V(P)| - (m+1) \geq |V(P\setminus\Prop(C))| \geq |P| - m + 3.\]
-Simplifying, we obtain $|V(P)| \geq |P| + 4$, i.e. $(P,V(P))$ is not an exact diagram.
-
-Conversely, suppose that $W'$ is not exact and for a contradiction suppose also that $M(W')$ is uniform of rank $|P|$.
-Take $p \in P$.
-Then $|V(P)\setminus V(p)| = |V(P)| - 4 \geq |P|$ by non-exactness.
-By uniformity there is an independent set of size $|P|$ in $V(P)\setminus V(p)$.
-This is impossible because the submatrix corresponding to this independent set has $|P|$ rows but the one corresponding to $p$ is all $0$ one of them is all 0 so it cannot be full rank.
-%suppose that $(P,V(P))$ is not exact, i.e. $|V(P)| \geq |P| +4$. We have 
-%\[|V(P)| - (m+1) \geq |P| - m + 3\]
-%as above, but \hlfix{we need to know that $P\setminus\Prop(C)$ is non-empty before we can complete the argument.}{and if we knew this, it would be immediate that $\rk(C) < |P|$}
-\end{proof}
-
-We now make a few observations about the geometry of matroids defined by exact diagrams.
-
-In \cite{wilsonloop}, the authors show that all admissible Wilson loop diagrams correspond to positroids.
-That is, they correspond to matroids that can be represented by elements of the positive Grassmannians $\Gr(|\cP|, n)$.
-Any positroid of rank $k$ on $n$ elements defines a subspace of the positive Grassmannians $\Gr(k, n)$, namely the points which represent it.
-These subspaces give a CW structure on $\Gr(k,n)$, with each positroid defining a cell.
-
-\begin{dfn}
-Given a Wilson loop diagram $W = (\cP, [n])$, define the positroid cell associated to a Wilson loop diagram, $\Sigma(W)$, to be the cell in the CW complex on $\Gr(|\cP|, n)$ defined by the positroid $M(W)$.
-\end{dfn}
-
-With this definition in mind, we have the following corollary:
-
-\begin{cor}
-Let $(P, V(P))$ be an exact subdiagram of $W$. The matroid associated to this subdiagram corresponds to the top dimensional cell in $\Gr(|P|, |V(P)|)$.
-\end{cor}
-
-\begin{proof}
-The unique top dimensional cell of $\Gr(|P|, |V(P)|)$ is defined by all points in $\Gr(|P|, |V(P)|)$ such that all Plucker coordinates are strictly greater than $0$.
-Since $(P, V(P))$ is an exact subdiagram, this all $|P| \times |P|$ minors are non-zero.
-Intersecting these with the cases with the positive Grassmannians demands that all minors be strictly positive.
-\end{proof}
-
-%Since the matroid defined by the subdiagram $(P , V(P))$ is not the same as the matroid associated to $W_{V(P)}$, one cannot say that the $W_{V(P)}$ is a uniform matroid.
-In fact, for any subset $U \subset V(P)$, $\rk_{W_{V(P)}}(U) \geq \rk_{(P , V(P))}(U)$.
-This is because adding propagators to vertices can only increase the rank.
-In particular this implies that, for any subset $U \subset V(P)$, if $|U| \leq |P|$, then $U$ is independent in both the restricted matroid $W_{V(P)}$, and the original, $W$.
-
-\subsection{Matroids and equivalent diagrams \label{sec: matroids and equivalence}}
-\note{Si\^an postponed reading this section until the earlier ones are fixed.}
-Now we are ready to prove the main results of this section, namely that two Wilson loop diagrams define the same matroid if and only if they are equivalent (Theorem \ref{same matroid iff equiv}).
-We also {\color{violet}count the number of equivalence classes amongst Wilon Loop diagrams with $n$ vertices and $k$ propagators and} give a formula for the number of Wilson loop diagrams in a given equivalence class (Corollary \ref{number of equiv diagrams}), completing the characterization of the correspondence between Wilson Loop diagrams and matroids starting in \cite{wilsonloop}.
-
-\begin{thm}\label{same matroid iff equiv}
-Let $W= (\cP, [n])$ and $W'= (\cP', [n])$ be two Wilson Loop diagrams. They define the same matroid if and only if $W \sim W'$.
-\end{thm}
-
-\begin{proof}
-One direction has been proved in \cite[Theorem 1.18]{wilsonloop}, but we give a different proof here to be consistent with the method of this document.
-
-Assume that $W$ and $W'$ are equivalent.
-Without loss of generality, write $W = (P \cup R, [n])$ and $W' = (P \cup R', [n])$, where $P \subset \cP \cap \cP'$ and $(R, V(R))$ and $(R', V(R'))$ are two maximally exact subdiagrams, with $R \neq R'$, but $V(R) = V(R')$.
-If this is not the case, one may always find a family of diagram, $\{W_i\}$ satisfying this condition and forming a transitive chain connecting $W$ to $W'$ in the equivalence class.
-
-Let $U \subset V(R)$ be any subset of size $|U| = |R|$.
-Since $(R, V(R))$ defines a uniform matroid, by Lemma \ref{exactuniformthm}, the set $U$ is independent in the subdiagram $(R, V(R))$, and thus in $W$.
-The complementary set $F(P)$ is a flat of maximal rank by lemma \ref{maxexactcomplementrank} ($\rk(F(P)) = |P|$).
-Let $B \subset F(P)$ be a maximal indpendent set ($\rk B = |P|$) in $F(P)$.
-Since $F(P)$ is a flat, adding any element of $V(R)$ to $B$ increases the rank.
-Therefore, any basis of $W$ can be written as $B \cup U$ for some $B$ and $U$ of the form indicated.
-However, since $F(P)$ is common to both $W$ and $W'$, and $V(R) = V(R')$, any any basis of $W'$ can also be written $B \cup U$.
-Thus both matroids have the same bases sets, proving that they are the same.
-
-For the converse, assume that the matroids associated to $W$ and $W'$ are the same: $M(W) = M(W')= M$.
-Let $\mathcal{R} = \{(P_i, V(P_i)\}_{i=1}^k$ and $\mathcal{R}' = \{(P'_i, V(P'_i)\}_{i=1}^l$ be the sets of maximally exact subdiagrams of $W$ and $W'$.
-Write $F_i = F(P_i^c)$ and $F'_i = F(P^{'c}_i)$ to be the complementary cyclic flats.
-By Theorem \ref{exactuniformthm} and Theorem \ref{exact diagrams contractions},  $M/F_i$ and $M/F_i'$ are uniform matroids.
-Since, by Theorem \ref{exactuniformthm}, any subset $V$ of $M$ such that $M/(V^c)$ is uniform defines an exact subdiagram of both $W$ and $W'$.
-If $U \subset V$ are two such thsets, then the corresponding exact subdiagrams are also subsets.
-Therefore, $|\mathcal{R}| = |\mathcal{R}'|$, and we write $V(P_i) = V(P'_i)$, after possibly reindexing $\mathcal{R}$ and $\mathcal{R}'$.
-
-Since the sets of propagators defining maximal exact subdiagrams partition $\cP$, by Lemma \ref{uniqueproppartitioncor}, write $\cup_{i = 1}^k P_i = \cup_{i = 1}^k P'_i = \cP$.
-Reorganize the vertex sets of maximal exact subdiagrams as follows: \ba \cup_{P_i \not \in \mathcal{R}'} V(P_i) = V(\cup_{P_i \not \in \mathcal{R}'} P_i)  = F(\cup_{P_i \in \mathcal{R}'} P_i)^c\label{vertexsets}\; .\ea The final flat may, of course, be empty.
-
-Thus, we have partitioned the vertices of $W$ and $W'$ into two complementary sets.
-The first, $ \cup_{P_i \not \in \mathcal{R}'} V(P_i)$,  is comprised of the union of supports of maximal exact subdiagrams whose propagators differ between $W$ and $W'$.
-The second, $ F(\cup_{P_i \in \mathcal{R}'} P_i)$,  is the propagator flat of all propagators in common between $W$ and $W'$.
-
-Without loss of generality, assume that $|\mathcal{R}| = |\mathcal{R}'| = 1$.
-Then the two Wilson loop diagrams are equivalent.
-If  $|\mathcal{R}| = |\mathcal{R}'| > 1$, then one may define a family of Wilson loop diagrams, $W_0$ to $W_k$ defined such that $W_0 = W$ and $W_i$ is derived from $W_{i-1}$ by replacing the propagator set $P_i$ with $P'_i$.
-In this manner, $W' = W_k$ and $W_i \sim W_{i+1}$, making $W \sim W'$.
-\end{proof}
-
-Since there is a unique way to decompose $W$ into maximal exact subdiagrams, it is logical to ask how many diagrams there are in an equivalence class.
-It is a classical fact the the number of triangulations of an $n$-gon is the $n-2$ Catalan number, namely $\frac{1}{n-1}\binom{2(n-2)}{n-2}$.
-Thus we can count the number of equivalent diagrams.
-[CITATION?]
-
-\begin{cor}\label{number of equiv diagrams}
-  Let $W$ be an admissible Wilson loop diagram where the sizes of the supports of the nontrivial maximal connected exact subdiagrams are $n_1, n_2, \ldots, n_j$.
-Then the number of admissible Wilson loop diagrams equivalent to $W$ (including $W$ itself) is
-  \[
-  \prod_{i=1}^{j} \frac{1}{n_i-1}\binom{2(n_i-2)}{n_i-2}
-  \]
-\end{cor}
-
-In this section we have characterized the correspondence between Wilson loop diagrams and positroids, showing that Wilson Loop diagrams define the same matroid if and only if they are equivalent (Theorem \ref{same matroid iff equiv}).
-Corollary \ref{number of equiv diagrams} enumerates the fibres of the map from Wilson Loop diagrams to positroids.
-{\color{violet} By counting the number of equivalence classes (Theorem \ref{}), we enumerate the number of positroids defined by Wilson Loop diagrams.
-In section \ref{}, Theorem \ref{}, we show that each Wilson Loop diagram with $n$ vertices and $k$ propagators define a positroid cell of dimension $3k$.
-Comparing the result of Theorem \ref{} to the number of positroid cells of a particular dimension in $\Grtnn(n, k)$, [CITE AND FIND FORMULA HERE], we see that \emph{Wilson loop diagrams do not map onto all positroids of the correct dimension.}}
-
-\begin{comment}
-\subsection{Counting exact subdiagrams}
-
-\begin{dfn}
-  Say two admissible Wilson loop diagrams $W_1$ and $W_2$ are \emph{triangulation-equivalent} if there is a bijection $\alpha$ between the set of triangulated pieces in the decomposition of $\tau(W_1)$ and the set of triangulated pieces in the decomposition of $\tau(W_2)$, where $t$ and $\alpha(t)$ have the same vertex set for all triangulated pieces $t$ of $\tau(W_1)$.
-\end{dfn}
-
-***draw an example***
-
-\begin{thm}
-  Two admissible Wilson loop diagrams have the same matroid iff they are triangulation equivalent
-\end{thm}
-
-Again do I want matroid or positroid in this theorem?
-
-\begin{proof}
-  By Lemma~\ref{lem triang to exact} two admissible Wilson loop diagrams are triangulation equivalent iff their decompositions into maximal connected exact subdiagrams have matching supports, that is if they are equivalent.
-  Theorem~\ref{thm orig equiv} then gives the result.
-\end{proof}
-
-\end{comment}
-
-\section{Geometry of Wilson Loop diagram}\label{sec GN algorithm}
-
-Since Wilson loop diagrams correspond to positroids, it is natural to study the subspace of $\Gr(|\cP|, n)$ they define.
-
-[words about what's in this section]
-
-Throughout this section, $W = (\cP,[n])$ is an admissible Wilson loop diagram with $k$ propagators.
-
-\subsection{Background}\label{sec:positroid background}
+\subsection{Positroid background}\label{sec:positroid background}
 
@@
 A method for using the Le diagram to test whether a given $k$-subset is a basis for the corresponding positroid or not was given by Casteels in [ref].
+
+\section{Wilson Loop diagrams and their Grassmann necklaces}\label{sec GN algorithm}
+
+Since Wilson loop diagrams correspond to positroids, it is natural to study the subspace of $\Gr(|\cP|, n)$ they define.
+
+In this section we will give an algorithm to go directly from a Wilson loop diagram to the Grassmann necklace of its positroid.
+As well as the result itself, the techniques developped will be useful throughout.
+One of the key insights is that an element of the Grassmann necklace can be viewed as a function from the propagators of the diagram to the vertices in the Grassmann necklace element.
+This is captured in Definition~\ref{def I_i as a function}, and used throughout the paper.
+
+Throughout this section, $W = (\cP,[n])$ is an admissible Wilson loop diagram with $k$ propagators.
 
@@
 
-\subsection{Dimension of the Wilson Loop cells}
+\section{Dimension of the Wilson Loop cells}\label{sec dim}
 
@@
 
-\begin{thm}
+\begin{thm}\label{thm dim}
   The number of plusses in the Le diagram of an admissible Wilson loop diagram is three times the number of propagators.
@@
 
-\section{Poles of Wilson Loop Integrals}
+\section{Poles of Wilson Loop Integrals}\label{sec poles}
 
@@
 \begin{algorithm}\label{alg WLD to denom via GN}
-Let $W = (\cP,n)$ be a Wilson loop diagram, and let $C(W)$ be the matrix of $W$ as defined in \eqref{C(W) dfn} (see Section~\ref{section background}).
+Let $W = (\cP,n)$ be a Wilson loop diagram, and let $C(W)$ be the matrix of $W$ as defined in \eqref{C(W) dfn} (see Section~\ref{section WLD background}).
 \begin{itemize}
@@
 
+\bibitem{Oh2}
+  S. Oh.
+  \newblock Combinatorics of positroids.
+  \newblock {\em DMTCS Proceedings vol. AK},(FPSAC 2009), 721--732
+
 \bibitem{Postnikov}

### 2019-03-26 GWLDCI.tex
added intro and bibliographical stubs

@@
 
-***Some general intro to WLDs perhaps similar to the end of p2 and top of p3 of \cite{wilsonloop}.
-For this paper we don't need the integral, so for the moment they are not defined below, but for motivation may want to be glossed a bit here ***
-
-Furthermore, in \cite{wilsonloop}, Agarwala and Amat show that Wilson loop diagrams can be interpreted as positroids, a certain well behaved class of realizable matroids.
-This opens up the study of Wilson loop diagrams to techniques from geometry and combinatorics.
-We pursue this direction here and in the companion paper ***cite the other paper***.
-
-In the present paper we focus on the combinatorics and geometry of an equivalence relation on Wilson loop diagrams.
-The main results are that Wilson loop diagrams are equivalent if and only if they define the same matroid, that the equivalence can be rephrased in terms of retriangulations in polygon dissections, and from there that the sizes of the equivalence classes can be enumerated, and the set of equivalence classes is related to directions in associahedra.
+This paper is the first in a two part series investigating the combinatorics and geometry underlying SYM $N=4$ theory.
+This series lays out several results about the relationship between the Wilson loop diagrams and the positroid cells that give a CW complex structure to the positive Grassmanian.
+This paper expands on an observation from \cite{wilsonloops}, that shows that certain families of Wilson loop diagrams correspond to the same positroid cell.
+This paper gives a way of enumerating the number of different Wilson loop diagrams that correspond to a given positroid cell.
+Furthermore, it shows that that the number of cells in the image of the map to positive Grassmannians is given by counting the directions of associahedrons.
+
+The second paper in this series identifies which positroid cell is associated to which Wilson loop diagram \cite{GWLDCII}.
+It proves that a Wilson loop diagram with $k$ propagators corresponds to a $3k$ dimensional positroid cell.
+Furthermore, it gives an algorithm for passing from a Wilson loop diagram to the Grassman necklace that identifies the associated positroid cell.
+In this manner the authors give a means of identifying which positroid cell is associate to which Wilson loop diagram that circumvents the painstaking process of examining bases sets.
+Finally, the authors characterize the the volume forms that Wilson loop diagrams associate to each positroid cells.
+
+In recent years, there has been a an active program researching the geometric and combinatorics underlying SYM $N=4$ theory \cite{wilsonloops, amplituhedron, correlahedron, karpwilliams, galashinlam}.
+This body of work started with the observation that the on shell amplitudes of this theory correspond to the volume of a subspace of a positive Grasmannian, called an Amplituhedron \cite{amplituhedron}.
+Since then, there has been significant work to study the structure of the amplituhedron, geometrically and combinatorially, for instance \cite{amplituhedron2, karpwilliams, galashinlam}.
+
+Meanwhile, there has been a different body of work studying SYM $N=4$ theory from the point of view of Feynman integrals \cite{BullimoreSkinner, AldayMaldecena, others}.
+The first author and Amat uncovered a connection between the Feynman integrals developed in this literature and the positive Grassmannians \cite{wilsonloops}.
+Others have tried to define a geometric space associated to these integrals in a manner similar to the Amplituhedron \cite{correlahedron, non-orientable}.
+
+In this paper, we expand on map between Wilson loop diagrams and positroids, first defined in \cite{wilsonloops}.
+Each Wilson loop diagram, $W$, has associated to it a real-variable valued matrix $C(W)$, which defines positroid, i.e.
+a matroid that can be realized as an element of $\Gr(k,n)$.
+The subspace of $\Gr(k,n)$ parametrized by each $C(W)$ is the positroid cell defined by $W$, called $\Sigma(W)$.
+Lemma ??
+of \cite{wilsonloops} identifies that certain Wilson loop diagrams define the same positroid cells.
+In particular, the authors define a subset of Wilson loop diagrams, called exact diagrams, and show that if two Wilson loop diagrams only differ by an exact subdiagram, they define the same positroid cell.
+
+In the current work we study exact subdiagrams in greater detail, identifying several matroidal properties.
+Furthermore, we enumerate how many different Wilson loop diagrams map to any positroid cell, $\Sigma(W)$.
+Furthermore, we show that counting the number of distinct $\Sigma(W)$, positroid cells that correspond to Wilson loop diagrams, corresponds to counting the number of directions of an associahedron.
 
@@
 We proceed in Section~\ref{section overall background} with the required definitions for Wilson loop diagrams (subsection~\ref{section WLD background}) and matroids (subsection~\ref{sec matroid background}.
-Wilson loop diagrams will be said to be admissible when they correspond to the physical situation of ***something***, or mathematically according to Definition~\ref{admisdfn}.
+Wilson loop diagrams  are said to be admissible when they correspond to $N^kMHV$ diagrams, or mathematically according to Definition~\ref{admisdfn}.
 With this, the key definition is Definition~\ref{equivdfn} giving the equivalence relation on admissible Wilson loop diagrams.
@@
 Let $\cP = \{p_r\}_{r=1}^k$ be the set of propagators.
-Then we write \bas W = (\cP, V) \;.\eas
+Then we write \bas W = (\cP, V) \;.\eas \sanote{picture}
 
@@
 
-\begin{dfn}
+\begin{dfn}\label{WLDtriangulationdfn}
   Let $W = (\cP, [n])$ be an admissible Wilson loop diagram.  The \emph{polygon dissection} associated to $W$, denoted $\tau(W)$, is defined as follows.
@@
 
-The connection between admissible Wilson loop diagrams and polytope dissections suggests a connection to associahedra. First we need some background.
+The connection between admissible Wilson loop diagrams and polytope dissections suggests a connection to associahedra. First we need some background. \sanote{expand}
 
@@
 There are many interesting realizations of the associahedron \cite{}; the following will be the one which we will use.
+\sanote{picture of an associahedron somewhere?
+or do people know what it is?}
 
@@
 
-With the choice of $n$-gon and hence of $A_n$ fixed, view the $\tau$ map as taking values in the set of dissections of this particular convex $n$-gon, and so each weakly admissible Wilson loop diagram is associated via $\tau$ with a face (in some dimension) of $A_n$.
+The map $\tau$ defined in Definition \ref{WLDtriangulationdfn} assigns a dissection of an $n$-gon to a Wilson loop diagram $W = (\cP, n)$.
+Recall that if $|\cP| = k$, then $\tau(W)$ is a dissection with $k$ chords.
+Therefore, the map $\tau$ associates to each weakly admissible Wilson loop diagram a $n-3 - k$ dimensional face of the associahedron $A_n$.
+\sanote{picture of $\tau(W)$ for $k =1$, $n = 5$?}
 
@@
 \begin{proof}
-  Let $W$ and $X$ be equivalent.  From results in the paper we're working on we know that $\tau(W)$ and $\tau(X)$ differ from each other only by retriangulations of their triangulated pieces.
+  Let $W$ and $X$ be two equivalent Wilson loop diagrams.
+From \hlfix{Lemma {\ref{??}}}{Do we actually have this explicitly?
+Feels like we should}, we know that $\tau(W)$ and $\tau(X)$ differ from each other only by retriangulations of their triangulated pieces.
 
@@
 Thus a vector parallel to this edge is the vector which is $(a(i,j,l) - a, a-a(j,k,i), a(k,l,j)-a, a-a(l,i,k)) = (-a(j,k,l), a(i,k,l), -a(i,j,l), a(i,j,k))$ on $i$, $j$, $k$, $l$ and $0$ in all other coordinates.
+\sanote{definitely need a picture}
 
@@
 
-The following lemma is useful for the second proposition.
+The following lemma is useful for proving the converse of the above.
 
@@
   Let $D_1$ and $D_2$ be two dissections of the convex polygon defined by the vertices $x_1, \ldots, x_n$.
-Suppose the vertices incident to at least one non-triangle face are the same in both dissections, but that the $D_1$ and $D_2$ do not have the same set of non-triangle faces.
+\hlfix{Suppose the vertices incident to at least one non-triangle face are the same in both dissections}{relevant?}, but that the $D_1$ and $D_2$ do not have the same set of non-triangle faces.
 Then there are four vertices $x_i$, $x_j$, $x_k$, $x_l$ such that in one of $D_1$ or $D_2$ all four vertices are on the same non-triangle face while in the other there is a diagonal of the dissection such that there is one side of the diagonal with exactly one of $\{x_i, x_j, x_k, x_l\}$ (so the others are end points of this diagonal or strictly on the other side).
-\end{lem}
+\end{lem} \sanote{picture?}
 
@@
 This means that any non-triangle and non-quadrilateral faces must be common between $D_1$ and $D_2$.
-These common faces are irrelevant for the statement, and so by triangulating any common non-triangle faces, we may assume that $D_1$ and $D_2$ have only quadrilateral and triangle faces.
+\hlfix{These common faces are irrelevant for the statement}{then why in the statement of thm?}, and so by triangulating any common non-triangle faces, we may assume that $D_1$ and $D_2$ have only quadrilateral and triangle faces.
 

### 2019-03-28 GWLDCI.tex
intro to first extended

@@
 This body of work started with the observation that the on shell amplitudes of this theory correspond to the volume of a subspace of a positive Grasmannian, called an Amplituhedron \cite{amplituhedron}.
-Since then, there has been significant work to study the structure of the amplituhedron, geometrically and combinatorially, for instance \cite{amplituhedron2, karpwilliams, galashinlam}.
-
-Meanwhile, there has been a different body of work studying SYM $N=4$ theory from the point of view of Feynman integrals \cite{BullimoreSkinner, AldayMaldecena, others}.
-The first author and Amat uncovered a connection between the Feynman integrals developed in this literature and the positive Grassmannians \cite{wilsonloops}.
-Others have tried to define a geometric space associated to these integrals in a manner similar to the Amplituhedron \cite{correlahedron, non-orientable}.
-
-In this paper, we expand on map between Wilson loop diagrams and positroids, first defined in \cite{wilsonloops}.
-Each Wilson loop diagram, $W$, has associated to it a real-variable valued matrix $C(W)$, which defines positroid, i.e.
-a matroid that can be realized as an element of $\Gr(k,n)$.
-The subspace of $\Gr(k,n)$ parametrized by each $C(W)$ is the positroid cell defined by $W$, called $\Sigma(W)$.
-Lemma ??
-of \cite{wilsonloops} identifies that certain Wilson loop diagrams define the same positroid cells.
-In particular, the authors define a subset of Wilson loop diagrams, called exact diagrams, and show that if two Wilson loop diagrams only differ by an exact subdiagram, they define the same positroid cell.
-
-In the current work we study exact subdiagrams in greater detail, identifying several matroidal properties.
-Furthermore, we enumerate how many different Wilson loop diagrams map to any positroid cell, $\Sigma(W)$.
-Furthermore, we show that counting the number of distinct $\Sigma(W)$, positroid cells that correspond to Wilson loop diagrams, corresponds to counting the number of directions of an associahedron.
+Since then, there has been significant work to study the structure of the amplituhedron, geometrically and combinatorially, for instance \cite{amplituhedron2, bigamplituhedronpaper, karpwilliams, galashinlam}.
+The focus of much of this work has been to understand the relationship between the combinatorial objects from the physics of the system, BCFW diagrams, and their corresponding natural object for studying the positive Grassmannians, positroid cells.
+
+Meanwhile, there has been a different body of work studying SYM $N=4$ theory from the point of view of Feynman integrals in twistor space\cite{BullimoreSkinner, AldayMaldecena?, Wittenpaper}.
+These integrasl are calculated via Wilson loops.
+The first author and Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that can be realized as an element of $\Gr(k,n)$ \cite{wilsonloops}.
+With the second author and others, this work was extended to study these Feynman integrals in terms of positroid cells and the positive Grassmanians \cite{casestudy, non-orientable}.
+Others have tried different approaches to define a geometric space associated to these integrals in a manner similar to the Amplituhedron \cite{correlahedron, HeslopStewart}.
+
+Both the Amplituhedron literature and the Wilson loop literature associate $n$ particle, $N^kMHV$ interaction in SYM $N=4$ theory to volume forms on a set of positroid cells of $\Gr(k,n)$.
+This gives a CW complex of some submanifold in $\Gr(k,n)$.
+Understanding the geometry and topology of this space is the subject of ongoing research.
+For Wilson loop diagrams with $k=2$ and $n=6$, one knows that the manifold is not contractible \cite{casestudy}.
+Furthermore, the spaces defined by the Amplituhedron and the Wilson loop diagrams are not the same \cite{correlahedron}.
+In particular, it it more natural to consider Deodhar cells of $\mathbb{G}(k, n+1)$ for Wilson loop diagrams.
+In this case, one gets that the manifold represented by the diagrams is not orientable \cite{non-orientable}.
+
+In this paper, we focus on the correspondence between Wilson loop diagrams and positroids, first defined in \cite{wilsonloops}.
+In that paper, the authors show that there are certain families of diagrams, specifically those with exact subdiagrams, that do map to the same positroid cell.
+In \cite{casestudy} the authors explictly show that not every positroid cell of a given dimension corresponds to a Wilson loop diagram.
+In this paper, we better enumerate this correspondence.
+We show that the map from Wilson loop diagrams to postroid cells is one to one exactly on the subset of diagrams with no non-trivial exact subdiagrams.
+We show that exact diagrams correspond to uniform matroids, and that contraction by exact subdiagrams has special matroidal properties.
+Further, given a Wilson loop diagram with a non-trivial exact subdiagram, we count the total number of Wilson loop diagrams that correspond to that same positroid cell.
+While we do not count the number of distint positroid cells that correspond to Wilson loop diagrams, we do show that this enumeration is equivalent to enumerating the number of directions of an associahedron.
 

### 2019-03-28 GWLDCI.tex
typos in sections 1 and 2.1, and clarified things in the associahedron proof as discussed with Susama yesterday

@@
 
-In recent years, there has been a an active program researching the geometric and combinatorics underlying SYM $N=4$ theory \cite{wilsonloops, amplituhedron, correlahedron, karpwilliams, galashinlam}.
+In recent years, there has been a an active program researching the geometry and combinatorics underlying SYM $N=4$ theory \cite{wilsonloops, amplituhedron, correlahedron, karpwilliams, galashinlam}.
 This body of work started with the observation that the on shell amplitudes of this theory correspond to the volume of a subspace of a positive Grasmannian, called an Amplituhedron \cite{amplituhedron}.
@@
 Meanwhile, there has been a different body of work studying SYM $N=4$ theory from the point of view of Feynman integrals in twistor space\cite{BullimoreSkinner, AldayMaldecena?, Wittenpaper}.
-These integrasl are calculated via Wilson loops.
+These integrals are calculated via Wilson loops.
 The first author and Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that can be realized as an element of $\Gr(k,n)$ \cite{wilsonloops}.
@@
 
-We proceed in Section~\ref{section overall background} with the required definitions for Wilson loop diagrams (subsection~\ref{section WLD background}) and matroids (subsection~\ref{sec matroid background}.
+We proceed in Section~\ref{section overall background} with the required definitions for Wilson loop diagrams (subsection~\ref{section WLD background}) and matroids (subsection~\ref{sec matroid background}).
 Wilson loop diagrams  are said to be admissible when they correspond to $N^kMHV$ diagrams, or mathematically according to Definition~\ref{admisdfn}.
@@
 A propagator, $p =(i,j)$ has one endpoint on the edge between the vertex labeled $i$ and $i+1$ and another endpoint on the edge defined by $j$ and $j+1$.
-The condition on $i_r$ and $j_r$ means that the propagator does not go between adjacent edges.
+The condition\note{which condition is this referring to; I think it is talking about one of the admissibility conditions, so maybe this is in the wrong place, alternately the condition might have gotten deleted at some point} on $i_r$ and $j_r$ means that the propagator does not go between adjacent edges.
 Let $\cP = \{p_r\}_{r=1}^k$ be the set of propagators.
@@
 Note that a more explicit definition of $F(P)$ is \bas F(P)  = \big(V(P) \setminus V(P^c) \big) \cup F(\emptyset) \;.\eas Furthermore, note that by construction $\Prop(F(P)) \subseteq P$.
+This containment is strict if there is any propagator $p$ in $P$ with the property that every vertex in the support of $p$ also supports a propagator not in $P$.
 \end{rmk}
@@
 
-Note that if we take any admissible Wilson loop diagram and remove the unsupported vertices then we will obtain a weakly admissible Wilson loop diagram that may or may not be admissible itself.
+Note that if we take any admissible Wilson loop diagram and remove the non-supporting vertices then we will obtain a weakly admissible Wilson loop diagram that may or may not be admissible itself.
 
@@
 Note that since vertices of the diagram $W$ correspond to columns of the associated matrix $C(W)$, $M(W)$ can also be thought of as the matroid realized by $C(W)$.
+\note{Can this note have a ref to your earlier paper?
+If not then perhaps expand slightly as although I agree that it is true, I don't think it is quite so trivial.
+Also, I think ``is also'' woulc be fine in place of ``can also be thought of as''}
 
@@
 
+It will be important in the subsequent section to consider retriangulations.
+\begin{dfn}
+  If $W$ and $W'$ are weakly admissible Wilson loop diagrams on the same vertex set then $\tau(W)$ and $\tau(W')$  differ by a \emph{retriangulation} if there is a bijection $f$ between the maximal triangulated pieces of $\tau(W)$ and the maximal triangulated pieces of $\tau(W')$ such that for any triangulated piece $t$ of $\tau(W)$ the vertex sets of $t$ and $f(t)$ are the same.
+\end{dfn}
+More casually this definition says that the triangulated pieces of $\tau(W)$ and $\tau(W')$ are the same (so far as their vertex sets are concerned) but that some or all of the triangulated pieces may be differently triangulated while the region being triangulated by each piece (which is defined by the vertex set) remains unchanged.
+
+The previous definition makes sense, in fact, for any two polygon dissections of the same polygon.
+
+\medskip
+
 We are now in a position to relate the triangulated pieces of $\tau(W)$ to exact subdiagrams of $W$.
@@
 There are many interesting realizations of the associahedron \cite{}; the following will be the one which we will use.
-\sanote{picture of an associahedron somewhere?
-or do people know what it is?}
+\sanote{picture of an associahedron somewhere?}\note{Yes, I agree that there should be a picture}
 
@@
   Let $W$ and $X$ be two equivalent Wilson loop diagrams.
-From \hlfix{Lemma {\ref{??}}}{Do we actually have this explicitly?
-Feels like we should}, we know that $\tau(W)$ and $\tau(X)$ differ from each other only by retriangulations of their triangulated pieces.
+From Lemma~\ref{lem triang to exact} along with the definitions of $\sim$ and retriangulation, we know that $\tau(W)$ and $\tau(X)$ differ from each other only by retriangulations of their triangulated pieces.
 
@@
 
-  Returning to $\tau(W)$ and $\tau(X)$ since the direction vector of an edge in $A_n$ depends only on its quadrilateral and the bijection between the edges bounding $\tau(W)$ and the edges bounding $\tau(X)$ preserves the quadrilateral, we have the same direction vectors bounding $\tau(W)$ as $\tau(X)$.
+  Returning to $\tau(W)$ and $\tau(X)$, since the direction vector of an edge in $A_n$ depends only on its quadrilateral and the bijection between the edges bounding $\tau(W)$ and the edges bounding $\tau(X)$ preserves the quadrilateral, we have the same direction vectors bounding $\tau(W)$ as $\tau(X)$.
 Furthermore, the bijection also maintains the relative configuration of the edges and so $\tau(W)$ and $\tau(X)$ are parallel.
@@
 The following lemma is useful for proving the converse of the above.
+We also need the following notation.
+Given a polygon dissection $D$ let $V_{>3}(D)$ be the set of vertices of the polygon which are on at least one non-triangle face of $D$.
+Note that $D$ may have many non-triangle faces and so $V_{>3}(D)$ will be the union of the vertices of each non-triangle face.
 
@@
   Let $D_1$ and $D_2$ be two dissections of the convex polygon defined by the vertices $x_1, \ldots, x_n$.
-\hlfix{Suppose the vertices incident to at least one non-triangle face are the same in both dissections}{relevant?}, but that the $D_1$ and $D_2$ do not have the same set of non-triangle faces.
+Suppose $V_{>3}(D_1) = V_{>3}(D_2)$, but that the $D_1$ and $D_2$ do not have the same set of non-triangle faces.
 Then there are four vertices $x_i$, $x_j$, $x_k$, $x_l$ such that in one of $D_1$ or $D_2$ all four vertices are on the same non-triangle face while in the other there is a diagonal of the dissection such that there is one side of the diagonal with exactly one of $\{x_i, x_j, x_k, x_l\}$ (so the others are end points of this diagonal or strictly on the other side).
@@
 This means that any non-triangle and non-quadrilateral faces must be common between $D_1$ and $D_2$.
-\hlfix{These common faces are irrelevant for the statement}{then why in the statement of thm?}, and so by triangulating any common non-triangle faces, we may assume that $D_1$ and $D_2$ have only quadrilateral and triangle faces.
+These common faces are irrelevant for the statement as none of them can be the face containing $x_i, x_j, x_k, x_l$, and so by triangulating any common non-triangle faces, we may assume that $D_1$ and $D_2$ have only quadrilateral and triangle faces.
 
@@
 Thus we can conclude that none of the vertices of this face are in $[x_i, x_j]$.
-Also if the face has three vertices on one side of $f$ and one on the other then we get a quadrilateral as in the statement again with this face giving the four vertices and the diagonal a side of $f$.
-, so the face is either a triangle with its third vertex of the triangle must be in $(x_j,x_k)$ or in $(x_l,x_i)$ or a quadrilateral with one more vertex in $(x_j, x_k)$ and one more vertex in $(x_l, x_i)$.
+Also if the face has three vertices on one side of $f$ and one on the other then we get a quadrilateral as in the statement again with this face giving the four vertices and the diagonal is a side of $f$.
+In this case the face is either a triangle with its third vertex of the triangle must be in $(x_j,x_k)$ or in $(x_l,x_i)$ or a quadrilateral with one more vertex in $(x_j, x_k)$ and one more vertex in $(x_l, x_i)$.
 Taking all this together, whether the face is a triangle or a quadrilateral, replacing $d$ with one of the other edges of the face we get a new diagonal $d'$ which also separates $f$ into $x_i, x_j$ and $x_k, x_l$ but is strictly closer to $[x_i, x_j]$ than $d$ was.
 The same argument holds for $d'$, but the polygon is finite, so this process cannot go on indefinitely, contradicting that no quadtilateral as in the statement exists.
+\note{That huge paragraph also needs a picture}
 \end{proof}
@@
   Let $W$ and $X$ be inequivalent.
-If $\tau(W)$ and $\tau(X)$ do not have the same number of diagonals (hence their faces in $A_n$ having the same dimension) then they are not parallel, so we can assume $\tau(W)$ and $\tau(X)$ do have the same number of diagonals and hence their faces in $A_n$ have the same dimension.
+If $\tau(W)$ and $\tau(X)$ do not have the same number of diagonals (hence their faces in $A_n$ not having the same dimension) then they are not parallel, so we can assume $\tau(W)$ and $\tau(X)$ do have the same number of diagonals and hence their faces in $A_n$ have the same dimension.
 Let the face associated to $\tau(W)$ be $f_W$ and the face associated to $\tau(X)$ be $f_X$.
@@
   As observed in the proof of Proposition~\ref{prop easy way}, the support of any nonzero vector parallel to an edge is on the indices corresponding to the four vertices bounding the quadrilateral of the dissection associated with the edge.
-Thus $\tau(W)$ and $\tau(X)$ do not have the same set of vertices incident to at least one non-triangle face then the span of the vectors parallel to their edes has different support and so they cannot be parallel.
-So we can assume that $\tau(W)$ and $\tau(X)$ have the same set of vertices incident to at least one non-triangle face.
+Thus $V_{>3}(\tau(W)) \neq V_{>3}(\tau(X))$ (notation as defined before Lemma~\ref{lem good quads}) then the span of the vectors parallel to their edes has different support and so they cannot be parallel.
+So we can assume that $V_{>3}(\tau(W)) = V_{>3}(\tau(X))$.
 
     Since $\tau(W)$ and $\tau(X)$ do not have the same set of non-triangle faces, there must be some diagonal $d$ of $\tau(W)$ that crosses through a non-triangle face $f$ of $\tau(X)$. 
-    It will be most convenient to look at normal vectors and to use the choice of normal vector discussed in the many realizations paper on p8, namely pick one side of $d$ to be positive and define the $i$th coordinate of the $\omega^+_d$ to be
+    It will be most convenient to look at normal vectors and to use the choice of normal vector discussed on p8 of \cite{CSZinequivalent}, namely pick one side of $d$ to be positive and define the $i$th coordinate of the $\omega^+_d$ to be
     \[
@@
     \]
-    The many realizations paper explains why $\omega^+_d$ is a normal vector for any face with $d$ as a diagonal in a way which is short and clean but relies on some earlier definitions.
-We can instead check that it is a normal vector in a completely elementary way using the shoelace formula for the area of a triangle which says that if $(x_1, y_1), (x_2, y_2), (x_3, y_3)$ are the coordinates of the corners of a triangle in counterclockwise order then the area of the triangle is $(x_1y_2 - x_1y_3 + x_2y_3 - x_2y_1 + x_3y_1 - x_3y_2)/2$.
+    We have from \cite{CSZinequivalent} that $\omega^+_d$ is a normal vector for any face with $d$ as a diagonal, however we can also check this fact in a completely elementary way using the shoelace formula for the area of a triangle.
+The shoelace formula says that if $(x_1, y_1), (x_2, y_2), (x_3, y_3)$ are the coordinates of the corners of a triangle in counterclockwise order then the area of the triangle is $(x_1y_2 - x_1y_3 + x_2y_3 - x_2y_1 + x_3y_1 - x_3y_2)/2$.
 

### 2019-03-31 GWLDCII.tex
agree with Sian's new version of lem 4.8 (with some small mods)

@@
 
-These $C(W)$ parametrize a subspace of $\Gr(k, n)$ as shown in \cite{wilsonloops}, call it $\Sigma(W)$.
+These $C(W)$ parametrize a subspace of $\Gr(k, n)$ as shown in \cite{wilsonloop}, call it $\Sigma(W)$.
 The Wilson loop diagrams also define a volume form on $\Sigma(W)$: \bas \Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V_{p_r}} \textrm{d}c_{p_r}}{R(W)} \;.
@@
 
-\begin{lem}\label{lem n-2 bad}
-Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that $n-2,n-1 \in I_{n-2}^{V}$.
-
-Then $I_{n-2}^{W}$ and $I_{n-3}^{W}$ contribute the following plusses to the Le diagram of $W$
-  \begin{itemize}
-  \item An $(n-3)\rightarrow (n-2)$ plus and an $(n-5)\rightarrow (n-1)$ plus.
-  \item All of the $I_{n-1}^{V}$ plusses.
-  \item In the Le diagram of $V$, $I_{n-2}^{V}$ contributes an $n-5\rightarrow n-2$ plus and no other term in the Grassmann necklace of $V$ gives a plus in this column.
+%\begin{lem}\label{lem n-2 bad}
+%Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that $n-2,n-1 \in I_{n-2}^{V}$.
+%
+%Then $I_{n-2}^{W}$ and $I_{n-3}^{W}$ contribute the following plusses to the Le diagram of $W$
+%  \begin{itemize}
+%  \item An $(n-3)\rightarrow (n-2)$ plus and an $(n-5)\rightarrow (n-1)$ plus.
+%  \item All of the $I_{n-1}^{V}$ plusses.
+%  \item In the Le diagram of $V$, $I_{n-2}^{V}$ contributes an $n-5\rightarrow n-2$ plus and no other term in the Grassmann necklace of $V$ gives a plus in this column.
 $I_{n-2}^W$ does not contribute this $+$ but yields an $n-5\rightarrow n-1$ plus instead.
-  \item All other plusses of $I_{n-2}^{V}$.
-  \item In the Le diagram of $V$, $I_{n-3}^{V}$ gives a plus in the $n-3$ column.  This $+$ is shifted over into the $n-2$ column in $W$.
-  \item All other plusses of $I_{n-3}^{V}$.
-  \end{itemize}
-Furthermore, no element of the Gramann necklace of $V$ gives an $n-5\rightarrow n-1$ plus.
-\end{lem}
-
-\begin{proof}
-  By Lemma~\ref{lem I} $I_{n-2}^{W}= (I_{n}^{V} - \{n-5\})\cup \{n-1,n-2\}$.
+%  \item All other plusses of $I_{n-2}^{V}$.
+%  \item In the Le diagram of $V$, $I_{n-3}^{V}$ gives a plus in the $n-3$ column.  This $+$ is shifted over into the $n-2$ column in $W$.
+%  \item All other plusses of $I_{n-3}^{V}$.
+%  \end{itemize}
+%Furthermore, no element of the Gramann necklace of $V$ gives an $n-5\rightarrow n-1$ plus.
+%\end{lem}
+%
+%\begin{proof}
+%  By Lemma~\ref{lem I} $I_{n-2}^{W}= (I_{n}^{V} - \{n-5\})\cup \{n-1,n-2\}$.
 Also, by the location of $q$ in the WLD,  $n-2\not\in I_{n-3}^{V}$ and and $n-5$ is the index of the lowest vertical edge in $\mathcal{B}$.
 Thus this section of the Gramann necklace of $V$ looks like
-  \begin{equation}\label{eq necklace}
-  I_{n-3}^{V} \underset{\substack{n-3\text{ out}\\n-2\text{ in}}}{\rightarrow} I_{n-2}^{V} \underset{\substack{n-2\text{ out}\\n-5\text{ in}}}{\rightarrow} I_{n-1}^{V} \underset{\substack{n-1\text{ out}\\\text{something in}}}{\rightarrow} I_{n}^{V} \underset{\substack{n \text{ out}\\\text{something in}}}{\rightarrow} I_1^{V}
-  \end{equation}
-  where the first ``something'' is either $n$ or an element of $I_1^{V}$ and the second ``something'' is an element of $I_1^{V}$.
+%  \begin{equation}\label{eq necklace}
+%  I_{n-3}^{V} \underset{\substack{n-3\text{ out}\\n-2\text{ in}}}{\rightarrow} I_{n-2}^{V} \underset{\substack{n-2\text{ out}\\n-5\text{ in}}}{\rightarrow} I_{n-1}^{V} \underset{\substack{n-1\text{ out}\\\text{something in}}}{\rightarrow} I_{n}^{V} \underset{\substack{n \text{ out}\\\text{something in}}}{\rightarrow} I_1^{V}
+%  \end{equation}
+%  where the first ``something'' is either $n$ or an element of $I_1^{V}$ and the second ``something'' is an element of $I_1^{V}$.
 Additionally all elements not explicitly mentioned must be in $I_1^{V}$ as they remain unchanged through this portion of the necklace.
-
-  Using this information now determine the symmetric difference of $I_{n-2}^{V}$ and $I_1^{V}$: $n-1, n-2$ and possibly $n$ are in $I_{n-2}^{V}$ but not in $I_1^{V}$.
+%
+%  Using this information now determine the symmetric difference of $I_{n-2}^{V}$ and $I_1^{V}$: $n-1, n-2$ and possibly $n$ are in $I_{n-2}^{V}$ but not in $I_1^{V}$.
 $n-5$ is in $I_1^{V}$ as are at least one and at most two other elements.
@@
 Stepping to $I_{n-1}^{V}$ simply removes the $n-5\rightarrow n-2$ path, see the second part of Figure~\ref{fig messy}.
-
-  \begin{figure}
-    \includegraphics{messy}
-    \caption{Plusses coming from $I_{n-2}^{V}$ (top left),  $I_{n-1}^{V}$ (top right) and $I_{n}^{V}$ bottom when $n-1, n-2\in I_{n-1}^{V}$.
+%
+%  \begin{figure}
+%    \includegraphics{messy}
+%    \caption{Plusses coming from $I_{n-2}^{V}$ (top left),  $I_{n-1}^{V}$ (top right) and $I_{n}^{V}$ bottom when $n-1, n-2\in I_{n-1}^{V}$.
 The blue lines are the non-intersecting paths.
 The dashed blue lines may or may not appear, but if one appears then they both do.}\label{fig messy}
-  \end{figure}
-
-  Stepping to $I_{n}^{V}$, $n-1$ is taken out and either $n$ is put in if it was not there before, or one of $a$ or $b$ is put in and hence no longer available as a right end for a path.
+%  \end{figure}
+%
+%  Stepping to $I_{n}^{V}$, $n-1$ is taken out and either $n$ is put in if it was not there before, or one of $a$ or $b$ is put in and hence no longer available as a right end for a path.
 This gives two possible configurations illustrated in the bottom two parts of Figure~\ref{fig messy}.
-
-  Now we know that $I_{n-2}^{W}  = (I_{n}^{V} - \{n-5\})\cup \{n-1,n-2\}$ so the paths for building plusses from $I_{n-2}^{W}$ go from the set $\{n-5, n-3\}$ along with whichever of $a$ and $b$ is not in $I_{n}^{V}$ to $\{n-2, n-1, n\}$.
+%
+%  Now we know that $I_{n-2}^{W}  = (I_{n}^{V} - \{n-5\})\cup \{n-1,n-2\}$ so the paths for building plusses from $I_{n-2}^{W}$ go from the set $\{n-5, n-3\}$ along with whichever of $a$ and $b$ is not in $I_{n}^{V}$ to $\{n-2, n-1, n\}$.
 This means that we get plusses as in Figure~\ref{fig messyD} where the left and right cases correspond to the left and right cases in the bottom parts of Figure~\ref{fig messy}
-
-  \begin{figure}
-     \includegraphics{messyD}
-    \caption{Plusses coming from $I_{n-2}^{W}$.}\label{fig messyD}
-  \end{figure}
-
-  This proves the first item of statement of the lemma.
-
-  Now consider $I_{n-3}^{V}$.
+%
+%  \begin{figure}
+%     \includegraphics{messyD}
+%    \caption{Plusses coming from $I_{n-2}^{W}$.}\label{fig messyD}
+%  \end{figure}
+%
+%  This proves the first item of statement of the lemma.
+%
+%  Now consider $I_{n-3}^{V}$.
 By \eqref{eq necklace} $I_{n-3}^{V}$ contributes the same plusses as $I_{n_2}^{V}$ except that it contributes an $n-5\rightarrow n-3$ plus in place of the $n-5\rightarrow n-2$ plus.
@@
 This cannot conflict with another path since \eqref{eq necklace} shows that $n-2$ only appears in $I_{n-2}^{V}$ among the necklace elements of $V$.
-
-  Also note that $I_{n-3}^{V}, I_{n-2}^{V}$, and $I_{n-1}^{V}$ share their plusses outside of the $n-3$ and $n-2$ columns.  This proves the remaining statements of the lemma except the furthermore.
-
-  Finally, suppose there were a $n-5\rightarrow n-1$ plus in the Le diagram of $V$.
+%
+%  Also note that $I_{n-3}^{V}, I_{n-2}^{V}$, and $I_{n-1}^{V}$ share their plusses outside of the $n-3$ and $n-2$ columns.  This proves the remaining statements of the lemma except the furthermore.
+%
+%  Finally, suppose there were a $n-5\rightarrow n-1$ plus in the Le diagram of $V$.
 By the algorithm, it would have to come when $n-5 \not\in I_j^{V}$.
@@
 Now, $n-4\in I_{n-4}^{V}$ by the location of $q$ and so $I_{n-4}^{V}$ must give an $n-5\rightarrow n-4$ plus and so cannot give an $n-5\rightarrow n-1$ plus.
-
-\end{proof}
-
-\note{This is a reorganised version of the previous lemma, keeping both in place for now for comparison.}
-\begin{lem}\label{lem n-2 bad v2}
+%
+%\end{proof}
+
+\begin{lem}\label{lem n-2 bad}
 Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that $n-2,n-1 \in I_{n-2}^{V}$. Then:
@@
   \item $I_{n-2}^W$ contributes an $(n-3)\rightarrow (n-2)$ plus and an $(n-5)\rightarrow (n-1)$ plus, along with any plusses contributed by $I_n^V$.
-  \item $I_{n-3}^W$ contributes the same plusses as $I_{n-3}^V$, except that the plus in the $n-3$ column is shifted one square left into the $n-2$ column.
+  \item $I_{n-3}^W$ contributes the same plusses as $I_{n-3}^V$, except that the plus in the $n-3$ column (which necessarily exists) is shifted one square left into the $n-2$ column.
   \item In the Le diagram of $V$, $I_{n-2}^{V}$ contributes an $(n-5)\rightarrow (n-2)$ plus and no other term in the Grassmann necklace of $V$ gives a plus in this column.
@@
 We are necessarily in the case where $W$ admits a propagator $q$ (the right hand case of Figure~\ref{fig special p}) and we can see from the location of $q$ that $n-2\not\in I_{n-3}^{V}$ and that $n-5$ is the index of the lowest vertical edge in $\mathcal{B}$.
+Also note that by Lemma~\ref{vertex cyclic int lem} and Corollary~\ref{no coloops} we must have $n\in I_n^V$.
 Thus this section of the Gramann necklace of $V$ looks like
@@
   \begin{equation}\label{eq necklace}
-  I_{n-3}^{V} \xrightarrow[\substack{n-3\text{ out}\\n-2\text{ in}}]{} I_{n-2}^{V} \xrightarrow[\substack{n-2\text{ out}\\n-5\text{ in}}]{} I_{n-1}^{V} \xrightarrow[\substack{n-1\text{ out}\\\text{something in}}]{} I_{n}^{V}  \xrightarrow[\substack{n \text{ out}\\\text{something in}}]{\text{\ no change, {\em or}\ }} I_1^{V}
+  I_{n-3}^{V} \xrightarrow[\substack{n-3\text{ out}\\n-2\text{ in}}]{} I_{n-2}^{V} \xrightarrow[\substack{n-2\text{ out}\\n-5\text{ in}}]{} I_{n-1}^{V} \xrightarrow[\substack{n-1\text{ out}\\\text{something in}}]{} I_{n}^{V}  \xrightarrow[\substack{n \text{ out}\\\text{something in}}]{} I_1^{V}
   \end{equation}
-  where the first ``something'' is either $n$ or an element of $I_1^{V}$, and the second ``something'' (if it exists) is an element of $I_1^{V}$. If $n\not\in I_n^V$ then $I_n^V = I_1^V$.
-
-  Using this information we can determine the symmetric difference of $I_{n-2}^{V}$ and $I_1^{V}$, which has size $\leq 3$ by the definition of a Grassmann necklace.
-We have $n-1, n-2 \in I_{n-2}^{V} \setminus I_1^V$ for certain, and the third element (if it exists) must be $n$.
-On the other hand we have $n-5 \in I_1^{V} \setminus I_{n-2}^V$, along with at least one and at most two other elements.
-If there is one such element call it $a$.
-If there are two call them $a$ and $b$ with $a>b$.
-
-  This means that the plusses in the Le diagram of $V$ coming from $I_{n-2}^{V}$ are as in the first part of Figure~\ref{fig messy}.
-Stepping to $I_{n-1}^{V}$ simply removes the $(n-5)\rightarrow (n-2)$ path (second part of Figure~\ref{fig messy}), so $I_{n-1}^V$ contributes no new information about the Le diagram of $V$.
+  where the first ``something'' is either $n$ or an element of $I_1^{V}$, and the second ``something'' is an element of $I_1^{V}$.
 
@@
 
-  \note{Remove the $I_n^V$ diagrams}
+  Using this information we can determine the symmetric difference of $I_{n-2}^{V}$ and $I_1^{V}$.
+Note that $I_{n-2}^V\setminus I_1^V$ and $I_1^V\setminus I_{n-2}^V$ each have size $\leq 3$ by the definition of a Grassmann necklace.
+We have $n-1, n-2 \in I_{n-2}^{V} \setminus I_1^V$ for certain, and the third element (if it exists) must be $n$.
+On the other hand we have $n-5 \in I_1^{V} \setminus I_{n-2}^V$, along with at least one and at most two other elements.
+If there is one such element call it $a$.
+If there are two call them $a$ and $b$ with $a>b$.
+
+  This means that the plusses in the Le diagram of $V$ coming from $I_{n-2}^{V}$ are as in the first part of Figure~\ref{fig messy}.
+Stepping to $I_{n-1}^{V}$ simply removes the $(n-5)\rightarrow (n-2)$ path (second part of Figure~\ref{fig messy}), so $I_{n-1}^V$ contributes no new information about the Le diagram of $V$.
 
@@
  \[I_{n-2}^W \setminus I_1^W = \{n-2,n-1\}\cup(I_n^V \setminus I_1^V).\]
-This means that $I_{n-2}^W$ contributes plusses as in Figure~\ref{fig messyD}, which proves point (1) and most of point (3).
+This means that $I_{n-2}^W$ contributes plusses as in Figure~\ref{fig messyD}, while $I_n^V$ contributes as in the bottom line of Figure~\ref{fig messy}, which proves point (1) and most of point (3).
 From equation \eqref{eq necklace} we see that $n-2$ appears only in $I_{n-2}^V$, so no other Grassmann necklace term for $V$ can contribute a plus in the $n-2$ column; this completes the proof of item (3).
@@
   \end{figure}
-
-\note{Modify this figure to include the case where there's no plus for column $n$.}
 

### 2019-03-31 GWLDCII.tex
some use of the GN function notation

@@
 If $n-2\not\in I_{n-2}^{V}$ (i.e.
-$n-2$ supports no propagators in $V$), then in $W$ the algorithm assigns $p$ to $n-2$ and this does not affect the rest of the construction of $I_{n-2}^{V}$, so we obtain $I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-2\}$ as above.
-
-On the other hand, if $n-2\in I_{n-2}^{V}$ then we must be in the right hand case of Figure~\ref{fig special p} and the algorithm assigns $q$ to vertex $n-2$ in both $V$ and $W$ (since $q$ is always the clockwise-most propagator supported on vertex $n-2$; see Figure~\ref{fig special p}).
-If $n-1 \not\in I_{n-2}^{V}$, then in $W$ the algorithm assigns $p$ to $n-1$ and then proceeds identically to $I_{n-2}^{V}$ for the remainder of its steps; thus $I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-1\}$ in this case.
-
-Finally, if $n-2,n-1 \in I_{n-2}^{V}$ then in $W$ the algorithm assigns $q$ to $n-2$ and $p$ to $n-1$ as above, but this is different to what occured in $I_{n-2}^{V}$ so we cannot use the same argument as above.
+$n-2$ supports no propagators in $V$), then $I_{n-2}^W(p) = n-2$ and this assignment of $p$ does not affect the rest of the construction of $I_{n-2}^{V}$, so we obtain $I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-2\}$ as above.
+
+On the other hand, if $n-2\in I_{n-2}^{V}$ then we must be in the right hand case of Figure~\ref{fig special p} and $I_{n-2}^V(q) = I_{n-2}^W(q) = n-2$ (since $q$ is always the clockwise-most propagator supported on vertex $n-2$; see Figure~\ref{fig special p}).
+If $n-1 \not\in I_{n-2}^{V}$, then $I_{n-2}^W(p) = n-1$ and then the algorithm proceeds identically to $I_{n-2}^{V}$ for the remainder of its steps; thus $I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-1\}$ in this case.
+
+Finally, if $n-2,n-1 \in I_{n-2}^{V}$ then $I_{n-2}^W(q) = n-2$ and $I_{n-2}^W(p) = n-1$ as above, but this is different to what occured in $I_{n-2}^{V}$ so we cannot use the same argument as above.
 We are now at vertex $n$ and only propagators $p$ and $q$ have been assigned; thus we are proceeding as in the construction of $I_n^{V}$ but without propagator $q$.
-By Lemma~\ref{vertex cyclic int lem} we know that $q$ was assigned to $n-5$ by $I_n^{V}$, and from the diagram we see that the only way this could occur is if all other propagators in $V$ had already been assigned when we reached vertex $n-5$; thus $q$ was the final propagator to be assigned in $I_n^{V}$.
+By Lemma~\ref{vertex cyclic int lem} we know that $I_n^V(q) = n-5$, and from the diagram we see that the only way this could occur is if all other propagators in $V$ had already been assigned when we reached vertex $n-5$; thus $q$ was the final propagator to be assigned in $I_n^{V}$.
 Therefore $I_{n-2}^{W} = (I_{n}^{V} \setminus \{n-5\}) \cup \{n-1, n-2\}$ in this case.

### 2019-04-01 GWLDCII.tex
second intro attempted

--- 2019-03-25 GWLDCII.tex
@@
 
-***Some general intro to WLDs.
-It can probably gloss over most of what is already in the other paper, but this time we are going to talk about the denominator, so for context we should probably say something about the integral, and its poles in this intro.
-Possibly also more about the integral should go at the end of the background section.***
-
-In \cite{wilsonloop}, Agarwala and Amat show that Wilson loop diagrams can be interpreted as positroids, a certain well behaved class of realizable matroids.
-This opens up the study of Wilson loop diagrams to techniques from geometry and combinatorics.
-In the companion paper to this one ***cite it*** we looked at equivalence classes of diagrams using matroidal and polytopal tools.
-However, the combinatorial richness of positroids comes from more than just their matroidal nature, but from their many bijections with other interesting combinatorial structures, including plabic graphs, decorated permutations, and Le diagrams, see for instance \cite{Oh2}.
-
-In this paper we will focus on implications of the Le diagrams on the mathematics and physics of Wilson loop diagrams.
+This paper is the second in a two part series investigating the combinatorics and geometry underlying SYM $N=4$ theory.
+This series lays out several results about the relationship between the Wilson loop diagrams and the positroid cells that give a CW complex structure to the positive Grassmanian.
+This paper is concerned with identifying which positroid cells correspond to which Wilson loop diagrams, and how this translates to a geometric tiling of a subspace of the positive Grassmannians.
+Wilson loop diagrams associate a volume form to a positroid cell.
+In this paper, we give an algorithm to identify which cell corresponds to which diagram, via Grassmann Necklaces.
+Using the Le diagram representation of positroid cells, we prove results about the dimensions of these cells.
+Finally, we state some results about the structures of the volume forms defined on these positroid cells by the Wilson loop diagrams.
+
+In contrast, the first paper in this series is about combinatorial and matroidal properties of the Wilson loop diagrams.
+The main focus of that paper was to enumerate the positroid cells that appeared in the image of the association between diagrams and cells, as well as the size of the number of Wilson loop diagrams in the pre-image of any positroid cell under this association.s is given by counting the directions of associahedrons.
+
+In recent years, there has been a some interest in understanding the geometry and combinatorics underlying the field theory SYM $N=4$ \cite{wilsonloops, amplituhedron, correlahedron, karpwilliams, galashinlam}.
+This started with the observation BCFW diagrams, which represent the on shell interactions of this theory correspond to plabic graphs \cite{bigamplituhedronpaper.} Plabic graphs are one of the many equivalent ways to identify positroid cells of the positie Grassmannians \cite{Postnikov}.
+This work led to the representation of the on shell integrals associated this theory in terms of a geometric space embedded in $\Gr(k,n)$, called the Amplituhedron \cite{amplituhedron, amplituhedron2}.
+More over, inegrals associated to the BCFW diagrams define a volume form on the Amplituhedron Since then, there has been significant work to understand the volume form and its physical implications \cite{galashinlam, others}.
+
+Meanwhile, a different body of work has studied SYM $N=4$ theory from the point of view of Feynman integrals in twistor space \cite{BullimoreSkinner, AldayMaldecena?, Wittenpaper}.
+These integrals are calculated via holomorphic Wilson loops.
+As with the Amplituhedron, each Wilson loop represents the sum of a family of $N^kMHV$ Feynman diagrams.
+The sum of the corresponding sum of Feynman integrals associate a volume form to space \cite{Hodges?}.
+The first author and Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that can be realized as an element of $\Gr(k,n)$ \cite{wilsonloops}, while other work has shown a connection between the space parametrized by Wilson loop diagrams and the Amplituhedron \cite{casestudy, correlahedron}.
+
+In the above work and elsewhere, it is clear that while the space parametrized by the Wilson loop diagrams is related to the Amplituhedron.
+They are not the same.
+For in stance, \cite{non-orientable} shows that the space parametrized by the Wilson loop diagrams can be seen as a non-orientable vector bundle over some submanifold of $\Gr(k,n)$, while it is conjectured that the Amplituhedron is orientable.
+Furthermore, the cells associated to the Wilson loop diagrams are different from the cells associated to BCFW diagrams, as one sees from counting arguments in comparing the results of \cite{KarpWiliams} and \cite{casestudy}.
+This is not too alarming, as one expects space parametrized by the Wilson loop diagrams to project down to something close to the Amplituhedron \cite{wilsonloops, correlahedron}.
+
+This paper continues this work by identifying which positroid cells are associated to which Wilson loop diagram.
+Where the BCFW diagrams identify positroid cells via plabic graphs, in this paper, we give an algorithm to read off of a Wilson loop diagram the associated Grassmann Necklace.
+Furthermore, while the BCFW cells are all 4k dimensional, we show that the positroid cells associated to Wilson loop diagrams are $3k$ dimensional.
+Again, this is not alarming, as \cite{non-orientable} has shown that the actual geometric space parametrized by the Wilson loop diagrams is a non-orientable $k$ dimensional bundle over this $3k$ dimensional manifold in $\Gr(k,n)$.
+
+Finally, when computing a finite volume to a geometric object defined by the Wilson loop diagrams, one must ensure at any singularities cancel.
+This has been expicitly shown in a few cases \cite{casestudy, HeslopStewart}, but it has been hard to prove exactly due to the non-one to one or onto relationship between Wilson loop diagrams and $3k$ dimensional positroid cells of $\Gr(k,n)$.
+In this paper, we give a characterisation of the denominator of the Feynman integral defined by a Wilson loop diagram in terms of the algorithm that associated the same diagram to a Grassman Necklace.
 

### 2019-04-02 GWLDCI.tex
added bibliography to both articles

@@
 This series lays out several results about the relationship between the Wilson loop diagrams and the positroid cells that give a CW complex structure to the positive Grassmanian.
-This paper expands on an observation from \cite{wilsonloops}, that shows that certain families of Wilson loop diagrams correspond to the same positroid cell.
+This paper expands on an observation from \cite{wilsonloop}, that shows that certain families of Wilson loop diagrams correspond to the same positroid cell.
 This paper gives a way of enumerating the number of different Wilson loop diagrams that correspond to a given positroid cell.
@@
 
-The second paper in this series identifies which positroid cell is associated to which Wilson loop diagram \cite{GWLDCII}.
+The second paper in this series identifies which positroid cell is associated to which Wilson loop diagram \cite{generalcombinatoricsI}.
 It proves that a Wilson loop diagram with $k$ propagators corresponds to a $3k$ dimensional positroid cell.
@@
 
-In recent years, there has been a an active program researching the geometry and combinatorics underlying SYM $N=4$ theory \cite{wilsonloops, amplituhedron, correlahedron, karpwilliams, galashinlam}.
-This body of work started with the observation that the on shell amplitudes of this theory correspond to the volume of a subspace of a positive Grasmannian, called an Amplituhedron \cite{amplituhedron}.
-Since then, there has been significant work to study the structure of the amplituhedron, geometrically and combinatorially, for instance \cite{amplituhedron2, bigamplituhedronpaper, karpwilliams, galashinlam}.
+In recent years, there has been a an active program researching the geometry and combinatorics underlying SYM $N=4$ theory \cite{wilsonloop, Arkani-Hamed:2013jha, Amplituhedronsquared, AmplituhedronDecomposition, galashinlam}.
+This body of work started with the observation that the on shell amplitudes of this theory correspond to the volume of a subspace of a positive Grasmannian, called an Amplituhedron \cite{Arkani-Hamed:2013jha}.
+Since then, there has been significant work to study the structure of the amplituhedron, geometrically and combinatorially, for instance \cite{Arkani-Hamed:2013kca, arkani:2012nw, AmplituhedronDecomposition, galashinlam}.
 The focus of much of this work has been to understand the relationship between the combinatorial objects from the physics of the system, BCFW diagrams, and their corresponding natural object for studying the positive Grassmannians, positroid cells.
 
-Meanwhile, there has been a different body of work studying SYM $N=4$ theory from the point of view of Feynman integrals in twistor space\cite{BullimoreSkinner, AldayMaldecena?, Wittenpaper}.
+Meanwhile, there has been a different body of work studying SYM $N=4$ theory from the point of view of Feynman integrals in twistor space\cite{Adamo:2011pv, Britto:2005fq, Cachazo:2004kj}.
 These integrals are calculated via Wilson loops.
-The first author and Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that can be realized as an element of $\Gr(k,n)$ \cite{wilsonloops}.
+The first author and Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that can be realized as an element of $\Gr(k,n)$ \cite{wilsonloop}.
 With the second author and others, this work was extended to study these Feynman integrals in terms of positroid cells and the positive Grassmanians \cite{casestudy, non-orientable}.
-Others have tried different approaches to define a geometric space associated to these integrals in a manner similar to the Amplituhedron \cite{correlahedron, HeslopStewart}.
+Others have tried different approaches to define a geometric space associated to these integrals in a manner similar to the Amplituhedron \cite{Amplituhedronsquared, HeslopStewart}.
 
@@
 For Wilson loop diagrams with $k=2$ and $n=6$, one knows that the manifold is not contractible \cite{casestudy}.
-Furthermore, the spaces defined by the Amplituhedron and the Wilson loop diagrams are not the same \cite{correlahedron}.
+Furthermore, the spaces defined by the Amplituhedron and the Wilson loop diagrams are not the same \cite{Amplituhedronsquared}.
 In particular, it it more natural to consider Deodhar cells of $\mathbb{G}(k, n+1)$ for Wilson loop diagrams.
@@
 
-In this paper, we focus on the correspondence between Wilson loop diagrams and positroids, first defined in \cite{wilsonloops}.
+In this paper, we focus on the correspondence between Wilson loop diagrams and positroids, first defined in \cite{wilsonloop}.
 In that paper, the authors show that there are certain families of diagrams, specifically those with exact subdiagrams, that do map to the same positroid cell.
@@
 
-\begin{thebibliography}{10}
+%\begin{thebibliography}{10}
+%\bibliographystyle{plain}
+%\bibliography{C:/Users/agarws1/Documents/GitHub/OldWLDPapers/Bibliography}
+
+\begin{thebibliography}{50}
+
+\bibitem{Adamo:2011pv}
+Tim Adamo, Mathew Bullimore, Lionel Mason, and David Skinner.
+\newblock {Scattering Amplitudes and Wilson Loops in Twistor Space}.
+\newblock {\em J.Phys.A}, A44:454008, 2011.
 
 \bibitem{wilsonloop}
-S. Agarwala, E. M. Amat.
+Susama Agarwala and Eloi~Marin Amat.
 \newblock Wilson loop diagrams and positroids.
-\newblock {\em Commun. Math. Phys.} 2016.
-
-\bibitem{reversingOh}
-S. Agarwala, S. Fryer.
-\newblock An algorithm to construct the Le diagram associated to a Grassmann necklace
-\newblock \url{arXiv:1803.01726}
+\newblock {\em Communications in Mathematical Physics}, 2016.
+\newblock arXiv:1509.06150.
+
+\bibitem{casestudy}
+Susama Agarwala and Sian Fryer.
+\newblock A study in $\textrm{Gr}_{\geq 0}(2,6)$: from the geometric case book
+  of {W}ilson loop diagrams and {SYM} $n=4$.
+\newblock arXiv:1803.00958.
+
+\bibitem{generalcombinatoricsI}
+Susama Agarwala, Sian Fryer, and Karen Yeats.
+\newblock Combinatorics and geometry of wilson loop diagrams.
+\newblock manuscript in progress.
+
+\bibitem{non-orientable}
+Susama Agarwala and Cameron Marcott.
+\newblock Wilson loops in sym $n=4$ do not parametrize an orientable space.
+\newblock arXiv:1807.05397.
+
+\bibitem{arkani:2012nw}
+Nima Arkani-Hamed, Jacob~L. Bourjaily, Freddy Cachazo, Alexander~B Goncharov,
+  Alexander Postnikov, and Jaroslav Trnka.
+\newblock Scattering amplitudes and the positive {G}rassmannian.
+\newblock arXiv:1212.5605, 2012.
+
+\bibitem{Arkani-Hamed:2013kca}
+Nima Arkani-Hamed and Jaroslav Trnka.
+\newblock {Into the Amplituhedron}.
+\newblock {\em JHEP}, 12:182, 2014.
+
+\bibitem{Arkani-Hamed:2013jha}
+Nima Arkani-Hamed and Jaroslav Trnka.
+\newblock {The Amplituhedron}.
+\newblock {\em JHEP}, 10:30, 2014.
+
+\bibitem{Britto:2005fq}
+Ruth Britto, Freddy Cachazo, Bo~Feng, and Edward Witten.
+\newblock {Direct proof of tree-level recursion relation in Yang-Mills theory}.
+\newblock {\em Phys.Rev.Lett.}, 94:181602, 2005.
+
+\bibitem{Cachazo:2004kj}
+Freddy Cachazo, Peter Svrcek, and Edward Witten.
+\newblock {MHV vertices and tree amplitudes in gauge theory}.
+\newblock {\em JHEP}, 0409:006, 2004.
+
+\bibitem{Amplituhedronsquared}
+Burkhard Eden, Paul Heslop, and Lionel Mason.
+\newblock The correlahedron.
+\newblock 2017.
+\newblock arxiv:1701.00453.
+
+\bibitem{galashinlam}
+P.~{Galashin} and T.~{Lam}.
+\newblock {Parity duality for the amplituhedron}.
+\newblock {\em arXiv e-prints}, May 2018.
+
+\bibitem{HeslopStewart}
+Paul Heslop and Alastair Stewart.
+\newblock The twistor wilson loop and the amplituhedron.
+\newblock {\em Journal of High Energy Physics}, 2018(10):142, Oct 2018.
+
+\bibitem{AmplituhedronDecomposition}
+Steven~N. Karp, Lauren~K. Williams, and Yan~X. Zhang.
+\newblock Decompostions of amplituhedra.
+\newblock arXiv:1708.09525.
 
@@
 \bibitem{Stanley}
-  R. P. Stanley,
+  R. P. Stanley.
   \newblock Enumerative Combinatorics, Vol. 2
@@
 \bibitem{Ziegler}
-  G. M. Ziegler,
+  G. M. Ziegler.
   \newblock Lectures on Polytopes
@@
 \bibitem{CSZinequivalent}
-  Cesar Ceballos, Francisco Santos, and G\"unter M. Ziegler,
+  Cesar Ceballos, Francisco Santos, and G\"unter M. Ziegler.
   \newblock Many non-equivalent realizations of the associahedron

### 2019-04-02 GWLDCII.tex
added bibliography to both articles

@@
 
-In recent years, there has been a some interest in understanding the geometry and combinatorics underlying the field theory SYM $N=4$ \cite{wilsonloops, amplituhedron, correlahedron, karpwilliams, galashinlam}.
-This started with the observation BCFW diagrams, which represent the on shell interactions of this theory correspond to plabic graphs \cite{bigamplituhedronpaper.} Plabic graphs are one of the many equivalent ways to identify positroid cells of the positie Grassmannians \cite{Postnikov}.
-This work led to the representation of the on shell integrals associated this theory in terms of a geometric space embedded in $\Gr(k,n)$, called the Amplituhedron \cite{amplituhedron, amplituhedron2}.
-More over, inegrals associated to the BCFW diagrams define a volume form on the Amplituhedron Since then, there has been significant work to understand the volume form and its physical implications \cite{galashinlam, others}.
-
-Meanwhile, a different body of work has studied SYM $N=4$ theory from the point of view of Feynman integrals in twistor space \cite{BullimoreSkinner, AldayMaldecena?, Wittenpaper}.
+In recent years, there has been a some interest in understanding the geometry and combinatorics underlying the field theory SYM $N=4$ \cite{wilsonloop, Arkani-Hamed:2013jha, Amplituhedronsquared, AmplituhedronDecomposition, galashinlam}.
+This started with the observation BCFW diagrams, which represent the on shell interactions of this theory correspond to plabic graphs \cite{GrassmannAmplitudebook}.
+Plabic graphs are one of the many equivalent ways to identify positroid cells of the positie Grassmannians \cite{Postnikov}.
+This work led to the representation of the on shell integrals associated this theory in terms of a geometric space embedded in $\Gr(k,n)$, called the Amplituhedron \cite{Arkani-Hamed:2013jha, Arkani-Hamed:2013kca}.
+More over, inegrals associated to the BCFW diagrams define a volume form on the Amplituhedron.
+Since then, there has been significant work to understand the volume form and its physical implications \cite{galashinlam, UnwindingAmplituhedron}.
+
+Meanwhile, a different body of work has studied SYM $N=4$ theory from the point of view of Feynman integrals in twistor space \cite{Adamo:2012xe, Adamo:2011pv,  Boels:2007qn, Bullimore:2010pj}.
 These integrals are calculated via holomorphic Wilson loops.
 As with the Amplituhedron, each Wilson loop represents the sum of a family of $N^kMHV$ Feynman diagrams.
-The sum of the corresponding sum of Feynman integrals associate a volume form to space \cite{Hodges?}.
-The first author and Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that can be realized as an element of $\Gr(k,n)$ \cite{wilsonloops}, while other work has shown a connection between the space parametrized by Wilson loop diagrams and the Amplituhedron \cite{casestudy, correlahedron}.
+The sum of the corresponding sum of Feynman integrals associate a volume form to space \cite{Hodges:2012ym}.
+The first author and Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that can be realized as an element of $\Gr(k,n)$ \cite{wilsonloop}, while other work has shown a connection between the space parametrized by Wilson loop diagrams and the Amplituhedron \cite{casestudy, Amplituhedronsquared}.
 
@@
 For in stance, \cite{non-orientable} shows that the space parametrized by the Wilson loop diagrams can be seen as a non-orientable vector bundle over some submanifold of $\Gr(k,n)$, while it is conjectured that the Amplituhedron is orientable.
-Furthermore, the cells associated to the Wilson loop diagrams are different from the cells associated to BCFW diagrams, as one sees from counting arguments in comparing the results of \cite{KarpWiliams} and \cite{casestudy}.
-This is not too alarming, as one expects space parametrized by the Wilson loop diagrams to project down to something close to the Amplituhedron \cite{wilsonloops, correlahedron}.
+Furthermore, the cells associated to the Wilson loop diagrams are different from the cells associated to BCFW diagrams, as one sees from counting arguments in comparing the results of \cite{AmplituhedronDecomposition} and \cite{casestudy}.
+This is not too alarming, as one expects space parametrized by the Wilson loop diagrams to project down to something close to the Amplituhedron \cite{wilsonloop, Amplituhedronsquared}.
 
@@
 
+%\bibliographystyle{plain}
+%\bibliography{C:/Users/agarws1/Documents/GitHub/OldWLDPapers/Bibliography}
+
 \begin{thebibliography}{10}
+\bibitem{Adamo:2011pv}
+Tim Adamo, Mathew Bullimore, Lionel Mason, and David Skinner.
+\newblock {Scattering Amplitudes and Wilson Loops in Twistor Space}.
+\newblock {\em J.Phys.A}, A44:454008, 2011.
+
+\bibitem{Adamo:2012xe}
+Tim Adamo and Lionel Mason.
+\newblock {Twistor-strings and gravity tree amplitudes}.
+\newblock {\em Class.Quant.Grav.}, 30:075020, 2013.
 
 \bibitem{wilsonloop}
-S. Agarwala, E. M. Amat.
+Susama Agarwala and Eloi~Marin Amat.
 \newblock Wilson loop diagrams and positroids.
-\newblock {\em Commun. Math. Phys.} 2016.
+\newblock {\em Communications in Mathematical Physics}, 2016.
+\newblock arXiv:1509.06150.
+
+\bibitem{casestudy}
+Susama Agarwala and Sian Fryer.
+\newblock A study in $\textrm{Gr}_{\geq 0}(2,6)$: from the geometric case book
+  of {W}ilson loop diagrams and {SYM} $n=4$.
+\newblock arXiv:1803.00958.
+
+\bibitem{non-orientable}
+Susama Agarwala and Cameron Marcott.
+\newblock Wilson loops in sym $n=4$ do not parametrize an orientable space.
+\newblock arXiv:1807.05397.
+
+\bibitem{UnwindingAmplituhedron}
+Nima Arkani-Hamed, Hugh Thomas, and Jaroslav Trnka.
+\newblock Unwinding the amplituhedron in binary.
+\newblock {\em Journal of High Energy Physics}, 2018(1):16, Jan 2018.
+\newblock arXiv:1704.05069.
+
+\bibitem{Arkani-Hamed:2013kca}
+Nima Arkani-Hamed and Jaroslav Trnka.
+\newblock {Into the Amplituhedron}.
+\newblock {\em JHEP}, 12:182, 2014.
+
+\bibitem{Arkani-Hamed:2013jha}
+Nima Arkani-Hamed and Jaroslav Trnka.
+\newblock {The Amplituhedron}.
+\newblock {\em JHEP}, 10:30, 2014.
+
+\bibitem{Boels:2007qn}
+Rutger Boels, Lionel Mason, and David Skinner.
+\newblock {From twistor actions to MHV diagrams}.
+\newblock {\em Phys.Lett.}, B648:90--96, 2007.
+
+\bibitem{Bullimore:2010pj}
+Mathew Bullimore, Lionel Mason, and David Skinner.
+\newblock {MHV Diagrams in Momentum Twistor Space}.
+\newblock {\em JHEP}, 1012:032, 2010.
+
+\bibitem{Amplituhedronsquared}
+Burkhard Eden, Paul Heslop, and Lionel Mason.
+\newblock The correlahedron.
+\newblock 2017.
+\newblock arxiv:1701.00453.
+
+\bibitem{galashinlam}
+P.~{Galashin} and T.~{Lam}.
+\newblock {Parity duality for the amplituhedron}.
+\newblock {\em arXiv e-prints}, May 2018.
+
+\bibitem{HeslopStewart}
+Paul Heslop and Alastair Stewart.
+\newblock The twistor wilson loop and the amplituhedron.
+\newblock {\em Journal of High Energy Physics}, 2018(10):142, Oct 2018.
+
+\bibitem{Hodges:2012ym}
+Andrew Hodges.
+\newblock {A simple formula for gravitational MHV amplitudes}.
+\newblock 2012.
+
+\bibitem{AmplituhedronDecomposition}
+Steven~N. Karp, Lauren~K. Williams, and Yan~X. Zhang.
+\newblock Decompostions of amplituhedra.
+\newblock arXiv:1708.09525.
+
+\bibitem{GrassmannAmplitudebook}
+Freddy Cachazo Alexander Goncharov Alexander Postnikov Jaroslav~Trnka
+  Nima~{A}rkani {H}amed, Jacob~Bourjaily.
+\newblock {\em Grassmannian Geometry of Scattering Amplitudes}.
+\newblock Cambridge University Press, Cambridge, UK, 2016.
 

### 2019-04-05 GWLDCII.tex
fixed text overlap in section 2.1

@@
 
-\note{We should be a bit careful about text overlap between the two papers in the WLD background section, as some bits are copied (and potentially also for the intro depending on what we do)}
-
 \begin{dfn}\label{WLdfn}
-A Wilson loop diagram is given by the following data: a cyclicly ordered set $V$, along with a choice of first vertex (labeled $1$), and $k$ pairs, called propagators, written $\{p_r = (i_r, j_r)\}_{r=1}^k$.
+A {\bf Wilson loop diagram} $W = (\cP,V)$ consists of a cyclically ordered set $V$ with one distinguished element (this plays the role of the ``first'' element when we need a compatible linear ordering on $V$), and a set $\cP \subseteq V \times V$.
+The elements of $V$ are the {\bf vertices} of $W$, and elements of $\cP$ are the {\bf propagators} of $W$.
 \end{dfn}
 
-Generally speaking, the propagators are undirected, so $p = (i,j) = (j,i)$.
-In order to fix a convention, we write $p = (i,j)$ with  $i +1 < j$ relative to the first vertex.
-However, at times (section \ref{sec:propagator configs}), we consider directed propagators, where $p= (i,j)$ denotes a particular propagator flowing in one direction, while $p= (j,i)$ denotes the \emph{same} propagators flowing in the opposite direction.
-\sanote{Addendum 1}
-
-We depict this data as a circle with marked points, called vertices.
-The vertices are labeled by $V$ (preserving the cyclic ordering).
-The arc between consecutive vertices are called edges.
-There are $k$ wavy lines in the interior of the diagram, depicting the proagators, with endpoints on the edges.
-A propagator, $p =(i,j)$ has one endpoint on the edge between the vertex labeled $i$ and $i+1$ and another endpoint on the edge defined by $j$ and $j+1$.
-The condition on $i_r$ and $j_r$ means that the propagator does not go between adjacent edges.
-Let $\cP = \{p_r\}_{r=1}^k$ be the set of propagators.
-Then we write \bas W = (\cP, V) \;.\eas
-
-Note that the marked circle gives the vertices of $W$ a cyclic ordering.
-The choice of first vertex gives it a compatible linear order.
-Both the cyclic and the linear order become the correct perspective at various points in this paper.
-
-Often we take $V$ to be $[n]$, the cyclically ordered set of integers, $1 \ldots n$.
-In this case, we write $W = (\cP, [n])$.
-We introduce some notation to speak of vertices supporting a propagator, and the set of propagators supported on a vertex set.
+A Wilson loop diagram is depicted as a circle, with the vertices $V$ equally spaced along the edge of the circle and listed counterclockwise in their cyclic order.
+The arc between two consecutive vertices is referred to as an {\bf edge} of the diagram, and the $i$th edge of $W$ is the edge from vertex $i$ to its successor.
+Each propagator $(i,j) \in \cP$ is denoted by a wavy line inside the circle joining edge $i$ and edge $j$.
+
+Generally speaking the propagators are undirected, so $(i,j)$ and $(j,i)$ represent the same propagator.
+As a general convention, we write $p = (i,j)$ with  $i < j$ relative to the first vertex.
+However, in Section~\ref{sec:propagator configs} we will need to give the propagators a direction (in order to refer to vertices ``inside'' and ``outside'' the propagator); in this setting, we impose the convention that $p= (i,j)$ denotes a propagator flowing from $i$ to $j$, and $p= (j,i)$ denotes the \emph{same} propagator flowing in the opposite direction.
+
+Let $[n]$ denote the set of integers $\{1,\dots,n\}$ with the obvious cyclic and linear orders.
+Our primary focus is Wilson loop diagrams with $V = [n]$, so in order to simplify the exposition we will often use $i+1$ as shorthand for ``the successor of vertex $i$''.
+
+We first introduce some definitions that will allow us to talk about subsets of the vertices of $W$, subsets of the propagators of $W$, and what it means to be a ``subdiagram'' of $W$.
 
 \begin{dfn} \label{VPropdfn}
-Let $W = (\cP, [n])$.
+Let $W = (\cP, V)$ be a Wilson loop diagram.
 \begin{enumerate}
-\item For $p \in \cP$, let $V(p) = \{i_p, i_p+1, j_p, j_p+1\}$ be the set of vertices supporting $p$. Then, for $P \subseteq \cP$, the set $V(P) = \cup_{p \in P} V(p)$ is the vertex support of $P$.
-\item For $V \subseteq [n]$, write $\Prop(V) = \{ p \in \cP | V(p) \cap V \neq \emptyset \} $.
-\item For $P \subseteq \cP$, define $F(P) = V(P^c)^c$ to be the set of vertices in $[n]$ that do not support any propagators outside the set $P$.
-\item The set of vertices that are not in the support of any propagotors is denoted  $F(\emptyset)$. Vertices in this set are called non-supporting.  
+\item For $p = (i,j) \in \cP$, let $V(p) = \{i, i+1, j, j+1\}$ denote the set of vertices supporting $p$. For a set of propagators $P \subseteq \cP$, define 
+\[V(P) = \bigcup_{p \in P} V(p)\]
+to be the vertex support of $P$.
+\item For $U \subseteq V$, the set of propagators supported on $U$ is denoted by
+\[\Prop(U) = \{ p \in \cP\ |\ V(p) \cap U \neq \emptyset \}.\]
+\item Vertices of $W$ that do not support any propagators are called non-supporting. The set of all non-supporting vertices in $W$ is denoted $F(\emptyset)$. 
 \end{enumerate}
@@
 
-\begin{rmk}\label{alt F(P) rmk}
-Note that a more explicit definition of $F(P)$ is \bas F(P)  = \big(V(P) \setminus V(P^c) \big) \cup F(\emptyset) \;.\eas Furthermore, note that by construction $\Prop(F(P)) \subseteq P$.  
-\end{rmk}
-
-It is sometimes useful to discuss propagators in terms of the edges supporting them, rather than the vertices.
-
-\begin{dfn}
-The $i^{th}$ edge of $W$ is the edge of the external polygon that lies between the vertices $i$ and $i+1$.
+\begin{dfn} \label{subdiagramdfn}
+Let $W = (\cP, V)$ be an admissible Wilson loop diagram. Then $W' = (Q,U)$ is a subdiagram of $W$ if 
+\[ Q \subseteq \cP \quad \text{ and }\quad V(Q) \subseteq U \subseteq V\;.\]
 \end{dfn}
 
-In this manner, the propagator $p = (i, j)$ is supported by the $i^{th}$ and $j^{th}$ edges.
+With these definitions in hand, we can impose some conditions on the density and behavior of the propagators of Wilson loop diagrams.
 
 \begin{dfn}\label{admisdfn}
-A Wilson loop diagram is admissible if \begin{enumerate}
-\item $|V| \geq |\cP| + 4$
-\item There does not exists a set of propagators, $P \subseteq \cP$ such that $|V(P)| < |P| + 3$.
-\item There does not exist a pair of propagators, $p, q \subseteq \cP$ such that $i_p < i_q < j_p <j_q$.
+A Wilson loop diagram $W = (\cP, V)$ is called {\bf admissible} if:
+\begin{enumerate}
+\item $|V| \geq |\cP| + 4$.
+\item There does not exist a non-empty set of propagators $Q \subseteq \cP$ such that $|V(Q)| < |Q| + 3$.
+\item There does not exist a pair of propagators $\{(i,j),(k,l)\} \subseteq \cP$ such that $i < k < j < l$.
 \end{enumerate}
-A Wilson loop diagram is weakly admissible if the second and third conditions hold.
  \end{dfn}
 
-The first conditions states that there are at least four more vertices than propagators in an admissible Wilson Loop Diagram.
-The second imposes an upper bound on how densely the propagators can be fitted in the diagram.
-The third ensures that ensures that no propagators cross in the interior of the diagram.
-In other words, a Wilson loop diagram, $(\cP, [n])$ is admissible if and only if $n > \cP +4$, and has neither crossing propagators nor any pairs of propagators that start and end on the same pair of non-adjacent edges.
-
-Note that if we take any admissible Wilson loop diagram and remove the unsupported vertices then we will obtain a weakly admissible Wilson loop diagram that may or may not be admissible itself.
-
-In what follows, we will talk about admissible Wilson Loop diagrams and subdiagrams thereof.
-
-\begin{dfn} \label{subdiagramdfn}
-Let $W = (\cP, [n])$ be an admissible Wilson loop diagram.
-The weakly admissible diagram, $W'$ is a subdiagram of $W$, written $W' \subseteq W$, if \bas W' = (P, V); \quad P \subseteq \cP ; \quad V(P) \subseteq V \subseteq [n]\;.\eas
-\end{dfn}
-
-Each Wilson loop diagram, $W = (\cP, [n])$ with $|\cP| = k$ is associated to a $k \times n$ matrix with non-zero real variable entries, called $C(W)$:
-
-\ba C(W)_{p,q} = \begin{cases} c_{p,q} & \textrm{ if } q \in V(p) \\
+The first condition bounds the total number of propagators in the diagram, while the second limits how densely propagators can be fitted into any part of the diagram; in particular, it prohibits both propagators that connect two adjacent edges and parallel propagators that start and end on the same pair of edges.
+The third condition simply requires that propagators are non-crossing.
+
+These conditions are imposed by the physical interpretation of Wilson loop diagrams (see for example [ref]).
+We therefore restrict our attention in this paper to admissible Wilson loop diagrams and their subdiagrams only.
+
+Note that a subdiagram $(Q,U)$ of an admissible Wilson loop diagram need not be admissible itself: it inherits conditions 2 and 3 automatically, but we could have $|V(Q)| = |Q| + 3$.
+We call diagrams of this type {\bf weakly admissible}; in the context of this paper, they occur only when we take an admissible diagram and delete one or more non-supporting vertices.
+
+Due to the physical motivation behind these diagrams, we can associate to each Wilson loop diagram $W$ a matrix $C(W)$, which is defined by
+
+\begin{equation} C(W)_{p,q} = \begin{cases} c_{p,q} & \textrm{ if } q \in V(p) \\
 0  & \textrm{ if } q \not \in V(p)  \end{cases}
-\;. \label{C(W) dfn}\ea
+\;. \label{C(W) dfn}\end{equation}
+
+The entries $c_{p,q}$ are non-zero real variables.
+The columns of $C(W)$ correspond to the vertices of $W$ listed in their linear order, and the rows correspond to the propagators of $W$.
+$C(W)$ is therefore only defined up to rearrangement of the rows, which will not matter in this setting since we will only interpret it as carving out a family of elements of the $|\cP| \times |V|$ real Grassmannian.
 
 \begin{eg}
-For example, ordering the propagators of $W_1$ from Example \ref{eg:equivdiags}: \bas (1,4), \, (2,4), \, (5,7), \, (5,8) \eas we may write
-\bas C(W_1) = \left(
+Consider the admissible Wilson loop diagram 
+\[W = (\{(1,4), (2,4), (5,7), (5,8)\},[8]),\]
+which is represented graphically by the diagram
+\[W = \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
+	\begin{scope}
+	\drawWLD{8}{1.5}
+	\drawnumbers
+	\drawprop{1}{0}{4}{0}
+	\drawprop{2}{0}{4}{-1}
+    \drawprop{5}{0}{8}{0}
+    \drawprop{5}{1}{7}{0}
+		\end{scope}
+	\end{tikzpicture}\]
+Ordering the propagators as listed above, we obtain the associated matrix
+\[ C(W) = \left(
 \begin{array}{cccccccc}
@@
 \end{array}
-\right) \;.\eas
-
+\right) \;.\]
 \end{eg}
 
-These $C(W)$ parametrize a subspace of $\Gr(k, n)$ as shown in \cite{wilsonloop}, call it $\Sigma(W)$.
-The Wilson loop diagrams also define a volume form on $\Sigma(W)$: \bas \Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V_{p_r}} \textrm{d}c_{p_r}}{R(W)} \;.
-\eas The denominator $R(W)$ is a polynomial defined by $2 \times 2$ and $1 \times 1$ minors of $C(W)$ as defined below.
+The matrix $C(W)$ parametrizes a subspace of $\Gr(k, n)$ as shown in \cite{wilsonloop}; we denote this subspace by $\Sigma(W)$.
+
+From $C(W)$ we obtain the matroid $M(W)$ associated to $W$, which is simply the matroid represented by $C(W)$: its ground set is the set $V$ of vertices of $W$, and the independent sets are exactly the sets $U \subseteq V$ such that the columns of $C(W)$ indexed by $U$ are linearly independent.
+More detail on this is given in Section~\ref{sec:positroid background} below.
+
+The Wilson loop diagram also define a volume form on $\Sigma(W)$, namely 
+\[ \Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V_{p_r}} \textrm{d}c_{p_r}}{R(W)} \;. \]
+The interested reader is referred to [ref] for more information about the volume form. Of interest to us in this paper is the denominator $R(W)$, which we define next.
 
 \begin{dfn}\label{def R(W)}
-For $W = (\cP, [n])$, $R(W) = \prod_{e=1}^n R_e$, with $R_e$ defined by the propagators ending on it.
-For any edge $e$ of $W$, order the propagators incident on $e$ as $\{p_1 \ldots p_r\}$, ordered such that $p_1$ is closest to the vertex $e$, $p_r$ closest to $e+1$, and $p_i$ is closer to $e$ than $p_{i+1}$.
-Then \bas R_e =  c_{p_1,e+1} \prod_{j= 1}^{r-1} \left((c_{p_j,e} c_{p_{j+1},e+1} - c_{p_{j+1},e} c_{p_{j},e+1} ) \right) c_{p_s,e}\;.\eas Note that in this notation, if $r = 1$, $R_e = c_{p,e} c_{p,e+1}$.
+Let $W = (\cP,V)$ be an admissible Wilson loop diagram, and fix an edge $e \in V$.
+Let $\{p_1 \ldots p_r\}$ be the propagators with one end lying on edge $e$, ordered so that $p_1$ is closest to the vertex $e$, $p_r$ closest to $e+1$, and $p_i$ is closer to $e$ than $p_{i+1}$ is.
+Then we define
+\[ R_e =  c_{p_1,e+1} \prod_{j= 1}^{r-1} \left((c_{p_j,e} c_{p_{j+1},e+1} - c_{p_{j+1},e} c_{p_{j},e+1} ) \right) c_{p_r,e}\;.\]
+Note that if $r = 1$ (i.e. there is exactly one propagator lying on edge $e$) then $R_e = c_{p,e} c_{p,e+1}$. The denominator $R(W)$ is defined to be the product of all of the $R_e$, i.e. 
+\[R(W) = \prod_{e \in V} R_e.\]
 \end{dfn}
+It is this polynomial $R(W)$ that we characterize in Section~\ref{sec poles}, where we give a simple algorithm to read $R(W)$ directly from the Wilson loop diagram.
 
@@
 
-By [ref], the set of all Le diagrams that fit within a $k\times(n-k)$ rectangle is in 1-1 correspondence with the positroid cells of $\Gr(k,n)$.
-The dimension of a positroid cell is equal to the number of $+$ squares in its Le diagram [ref].
+By \cite[Theorem 6.5]{Postnikov}, the set of all Le diagrams that fit within a $k\times(n-k)$ rectangle is in 1-1 correspondence with the positroid cells of $\Gr(k,n)$.
+The dimension of a positroid cell is equal to the number of $+$ squares in its Le diagram \cite[Theorem 6.5]{Postnikov}.
 
@@
 
-An algorithm for constructing the Le diagram associated to a Grassmann necklace was given by Agarwala and Fryer in [ref].
-Since we will make use of this algorithm in Section [ref] below, we summarise the process here.
-\begin{algorithm}\label{alg:GN to Le} \ [ref]
+An algorithm for constructing the Le diagram associated to a Grassmann necklace was given by Agarwala and Fryer in \cite{ReversingOh}.
+Since we will make use of this algorithm in Section~\ref{sec dim} below, we summarise the process here.
+\begin{algorithm}\label{alg:GN to Le} \ \cite[Algorithm 2]{ReversingOh}
 Let $(I_1,\dots,I_n)$ be a Grassmann necklace of type $(k,n)$. Within a $k \times(n-k)$ square, draw the Young diagram whose rows are labelled by $I_1$ (as per the convention above).
@@
 
-An algorithm for constructing the Grassmann necklace of a Le diagram also exists; this was given by Oh in [ref].
-A method for using the Le diagram to test whether a given $k$-subset is a basis for the corresponding positroid or not was given by Casteels in [ref].
+An algorithm for constructing the Grassmann necklace of a Le diagram also exists; this was given by Oh in \cite{Oh}.
+A method for using the Le diagram to test whether a given $k$-subset is a basis for the corresponding positroid or not was given by Casteels in \cite{CasteelsPaths}.
 
@@
 By Lemma~\ref{GN alg well defined}, we know that $|I_i| = k$ for each $i \in [n]$.
-By [ref], the sequence $(I_1, \dots, I_n)$ is a Grassmann necklace if and only if $I_{i+1} \supseteq I_i \backslash \{i\}$ for all $i \in [n]$.
+It is easy to verify that the sequence $(I_1, \dots, I_n)$ is a Grassmann necklace if and only if $I_{i+1} \supseteq I_i \backslash \{i\}$ for all $i \in [n]$; this is the characterization we will use in this proof.
 
@@
 We do this by applying Algorithm~\ref{alg:GN to Le}, which constructs the Le diagram associated to a Grassmann necklace, to the Grassmann necklaces of $V$ and $W$.
-As described in Section [ref], if Algorithm~\ref{alg:GN to Le} places a $+$ in the box with row index $i$ and column index $j$, we say that this plus is in the $i \rightarrow j$ position, and refer to it as the plus defined by ``the (hook) path from $i$ to $j$''.
+As described in Section~\ref{sec:positroid background}, if Algorithm~\ref{alg:GN to Le} places a $+$ in the box with row index $i$ and column index $j$, we say that this plus is in the $i \rightarrow j$ position, and refer to it as the plus defined by ``the (hook) path from $i$ to $j$''.
 Note that the collection of paths contributed by a single Grassmann necklace term  must be non-crossing.
@@
 
+\bibitem{CasteelsPaths}
+K. Casteels.
+\newblock Quantum matrices by paths.
+\newblock {\em Algebra Number Theory}, 8(8):1857--1912, 2014.
+
 \bibitem{Amplituhedronsquared}

### 2019-04-06 GWLDCI.tex
some picures and edits in section 1 and 2 (paper 1)

@@
 
-Propagators are undirected, so $p = (i,j) = (j,i)$. In order to fix a convention, we write $p = (i,j)$ with  $i +1 < j$ relative to the first vertex.
+Propagators are undirected, so $p = (i,j) = (j,i)$. In order to fix a convention, we write $p = (i,j)$ with  $i +1 \leq j$ relative to the first vertex.
 
@@
 A propagator, $p =(i,j)$ has one endpoint on the edge between the vertex labeled $i$ and $i+1$ and another endpoint on the edge defined by $j$ and $j+1$.
-The condition\note{which condition is this referring to; I think it is talking about one of the admissibility conditions, so maybe this is in the wrong place, alternately the condition might have gotten deleted at some point} on $i_r$ and $j_r$ means that the propagator does not go between adjacent edges.
-Let $\cP = \{p_r\}_{r=1}^k$ be the set of propagators.
-Then we write \bas W = (\cP, V) \;.\eas \sanote{picture}
+Then we write \bas W = (\cP, V) \;.\eas
 
@@
 Both the cyclic and the linear order become the correct perspective at various points in this paper.
+
+For instance, 
+\bas W = (\cP, [8]) = \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
+	\begin{scope}
+	\drawWLD{8}{1.5}
+	\drawnumbers
+	\drawprop{1}{0}{4}{0}
+	\drawprop{2}{0}{4}{-1}
+\drawprop{5}{0}{8}{0}
+		\end{scope}
+	\end{tikzpicture}  \eas with $\cP = \{ (1,4), (2, 4), (5, 8)\}$ is a Wilson loop diagram.
 
@@
 \end{dfn}
+
+\begin{eg}
+The Wilson loop diagram $W$ shown above is exact.
+There is a single non-supporting vertex in $W$, $F(\emptyset) = \{7\}$.
+The subdiagram $(\{(2, 4), (1, 4)\}, \{1, 2, 3, 4, 5, \})$ is an exact subdiagram of $W$.
+For $p = (5, 8)$ $F(p) = \{6, 7,8\}$.
+\end{eg}
 
@@
 
-We first give a quick summary of the matroid terminology that we will need; it is not intended as a comprehensive introduction to matroids and the interested reader is referred to [ref][find a good matroid reference].\note{Oxley is always my go to reference for matroids, but perhaps it has the wrong focus for you?}
+We first give a quick summary of the matroid terminology that we will need; it is not intended as a comprehensive introduction to matroids and the interested reader is referred to \cite{OxleyMatroidBook}
 
@@
 
-%\begin{thebibliography}{10}
 %\bibliographystyle{plain}
@@
 
+\bibitem{OxleyMatroidBook}
+James~G. Oxley.
+\newblock {\em Matroid Theory}, volume~21 of {\em Oxford graduate texts in
+  mathematics}.
+\newblock Oxford University Press, New York, 2011.
+
 \bibitem{CSZinequivalent}

### 2019-04-08 GWLDCI.tex
a few comments and tiny changes as I begin to read through

@@
 The third ensures that ensures that no propagators cross in the interior of the diagram.
-In other words, a Wilson loop diagram, $(\cP, [n])$ is admissible if and only if $n > \cP +4$, and has neither crossing propagators nor any pairs of propagators that start and end on the same pair of non-adjacent edges.
+\note{This ``in other words'' doesn't seem to me to be true as condition 2 could fail for a set of more than two propagators but not for a set of two propagators, and also condition 1 is $\geq$ not $>$}In other words, a Wilson loop diagram, $(\cP, [n])$ is admissible if and only if $n > \cP +4$, and has neither crossing propagators nor any pairs of propagators that start and end on the same pair of non-adjacent edges.
 
@@
 adding a vertex that supports a new propagator to a set increases the rank of the set.
-\item If $C \subseteq [n]$ is a cycle, then $\rk(C) = |Prop(C)|$.
+\item If $C \subseteq [n]$ is a cycle in the matroid, then $\rk(C) = |Prop(C)|$.
 \item If $[n]$ can be partitioned into at least two non-empty sets, each of which support different sets of propagators that form a partition of the propagotor set, \bas [n] = \sqcup_i V(P_i) \quad \textrm{s.t.} \quad \sqcup P_i = \cP; \quad V(P_i) \cap V(P_j) = \emptyset; \quad  P_i \cap P_j = \emptyset \;, \eas then the matroid $M(W)$ is seperable, \bas M(W) = \bigoplus_i M(P_i, V(P_i)) \;.\eas
@@
 Let $S \subseteq F(P)$ be an independent set of maximal size.
-Then $\Prop(S) \subseteq P$ by (1), and no subset of $S$ supports fewer propagators than the number of vertices it contains (this is the definition of an independent set in $M(W)$).
+Then $\Prop(S) \subseteq P$ and no subset of $S$ supports fewer propagators than the number of vertices it contains (by (1) this is one characterization of an independent set in $M(W)$).
 Since $v$ supports a new propagator $q \not\in P$, the set $S \cup \{v\} \subseteq F(P) \cup\{v\}$ also satisfies this independence condition.
@@
 In particular $t$ is not the subgraph of $\tau(W)$ consisting only of edges corresponding to propagators of $P$.
+\note{This clarification arose because of a discussion with Susama, but maybe it would be clearer to the reader if an example, like we had in that discussion, were included here}
 

### 2019-04-09 GWLDCII.tex
paper 2 positroid background

@@
 
-Generally speaking the propagators are undirected, so $(i,j)$ and $(j,i)$ represent the same propagator.
-As a general convention, we write $p = (i,j)$ with  $i < j$ relative to the first vertex.
-However, in Section~\ref{sec:propagator configs} we will need to give the propagators a direction (in order to refer to vertices ``inside'' and ``outside'' the propagator); in this setting, we impose the convention that $p= (i,j)$ denotes a propagator flowing from $i$ to $j$, and $p= (j,i)$ denotes the \emph{same} propagator flowing in the opposite direction.
-
-Let $[n]$ denote the set of integers $\{1,\dots,n\}$ with the obvious cyclic and linear orders.
-Our primary focus is Wilson loop diagrams with $V = [n]$, so in order to simplify the exposition we will often use $i+1$ as shorthand for ``the successor of vertex $i$''.
-
-We first introduce some definitions that will allow us to talk about subsets of the vertices of $W$, subsets of the propagators of $W$, and what it means to be a ``subdiagram'' of $W$.
-
-\begin{dfn} \label{VPropdfn}
-Let $W = (\cP, V)$ be a Wilson loop diagram.
-\begin{enumerate}
-\item For $p = (i,j) \in \cP$, let $V(p) = \{i, i+1, j, j+1\}$ denote the set of vertices supporting $p$. For a set of propagators $P \subseteq \cP$, define 
-\[V(P) = \bigcup_{p \in P} V(p)\]
-to be the vertex support of $P$.
-\item For $U \subseteq V$, the set of propagators supported on $U$ is denoted by
-\[\Prop(U) = \{ p \in \cP\ |\ V(p) \cap U \neq \emptyset \}.\]
-\item Vertices of $W$ that do not support any propagators are called non-supporting. The set of all non-supporting vertices in $W$ is denoted $F(\emptyset)$. 
-\end{enumerate}
-\end{dfn}
-
-\begin{dfn} \label{subdiagramdfn}
-Let $W = (\cP, V)$ be an admissible Wilson loop diagram. Then $W' = (Q,U)$ is a subdiagram of $W$ if 
-\[ Q \subseteq \cP \quad \text{ and }\quad V(Q) \subseteq U \subseteq V\;.\]
-\end{dfn}
-
-With these definitions in hand, we can impose some conditions on the density and behavior of the propagators of Wilson loop diagrams.
-
-\begin{dfn}\label{admisdfn}
-A Wilson loop diagram $W = (\cP, V)$ is called {\bf admissible} if:
-\begin{enumerate}
-\item $|V| \geq |\cP| + 4$.
-\item There does not exist a non-empty set of propagators $Q \subseteq \cP$ such that $|V(Q)| < |Q| + 3$.
-\item There does not exist a pair of propagators $\{(i,j),(k,l)\} \subseteq \cP$ such that $i < k < j < l$.
-\end{enumerate}
- \end{dfn}
-
-The first condition bounds the total number of propagators in the diagram, while the second limits how densely propagators can be fitted into any part of the diagram; in particular, it prohibits both propagators that connect two adjacent edges and parallel propagators that start and end on the same pair of edges.
-The third condition simply requires that propagators are non-crossing.
-
-These conditions are imposed by the physical interpretation of Wilson loop diagrams (see for example [ref]).
-We therefore restrict our attention in this paper to admissible Wilson loop diagrams and their subdiagrams only.
-
-Note that a subdiagram $(Q,U)$ of an admissible Wilson loop diagram need not be admissible itself: it inherits conditions 2 and 3 automatically, but we could have $|V(Q)| = |Q| + 3$.
-We call diagrams of this type {\bf weakly admissible}; in the context of this paper, they occur only when we take an admissible diagram and delete one or more non-supporting vertices.
-
-Due to the physical motivation behind these diagrams, we can associate to each Wilson loop diagram $W$ a matrix $C(W)$, which is defined by
-
-\begin{equation} C(W)_{p,q} = \begin{cases} c_{p,q} & \textrm{ if } q \in V(p) \\
-0  & \textrm{ if } q \not \in V(p)  \end{cases}
-\;. \label{C(W) dfn}\end{equation}
-
-The entries $c_{p,q}$ are non-zero real variables.
-The columns of $C(W)$ correspond to the vertices of $W$ listed in their linear order, and the rows correspond to the propagators of $W$.
-$C(W)$ is therefore only defined up to rearrangement of the rows, which will not matter in this setting since we will only interpret it as carving out a family of elements of the $|\cP| \times |V|$ real Grassmannian.
-
-\begin{eg}
-Consider the admissible Wilson loop diagram 
-\[W = (\{(1,4), (2,4), (5,7), (5,8)\},[8]),\]
-which is represented graphically by the diagram
-\[W = \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
+\begin{figure}[h]
+\[W\ =\ \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
 	\begin{scope}
@@
 	\end{tikzpicture}\]
-Ordering the propagators as listed above, we obtain the associated matrix
+
+\caption{The Wilson loop diagram $W = \big(\{(1,4), (2,4), (5,7), (5,8)\},[8]\big)$ which has four propagators and eight vertices.}
+\label{fig:ex of WLD}
+\end{figure}
+
+Generally speaking the propagators are undirected, so $(i,j)$ and $(j,i)$ represent the same propagator.
+As a general convention, we write $p = (i,j)$ with  $i < j$ relative to the first vertex.
+However, in Section~\ref{sec:propagator configs} we will need to give the propagators a direction (in order to refer to vertices ``inside'' and ``outside'' the propagator); in this setting, we impose the convention that $p= (i,j)$ denotes a propagator flowing from $i$ to $j$, and $p= (j,i)$ denotes the \emph{same} propagator flowing in the opposite direction.
+
+Let $[n]$ denote the set of integers $\{1,\dots,n\}$ with the obvious cyclic and linear orders.
+Our primary focus is Wilson loop diagrams with $V = [n]$, so in order to simplify the exposition we will often use $i+1$ as shorthand for ``the successor of vertex $i$''.
+
+We first introduce some definitions that will allow us to talk about subsets of the vertices of $W$, subsets of the propagators of $W$, and what it means to be a ``subdiagram'' of $W$.
+
+\begin{dfn} \label{VPropdfn}
+Let $W = (\cP, V)$ be a Wilson loop diagram.
+\begin{enumerate}
+\item For $p = (i,j) \in \cP$, let $V(p) = \{i, i+1, j, j+1\}$ denote the set of vertices supporting $p$. For a set of propagators $P \subseteq \cP$, define 
+\[V(P) = \bigcup_{p \in P} V(p)\]
+to be the vertex support of $P$.
+\item For $U \subseteq V$, the set of propagators supported on $U$ is denoted by
+\[\Prop(U) = \{ p \in \cP\ |\ V(p) \cap U \neq \emptyset \}.\]
+Note that a propagator does not need to have its entire support contained in $U$. $\Prop(U)$ is the set of all propagators that would be affected by removing the set $U$.
+\item Vertices of $W$ that do not support any propagators are called {\bf non-supporting}. The set of all non-supporting vertices in $W$ is denoted $F(\emptyset)$. 
+\end{enumerate}
+\end{dfn}
+
+\begin{dfn} \label{subdiagramdfn}
+Let $W = (\cP, V)$ be an admissible Wilson loop diagram. Then $W' = (Q,U)$ is a {\bf subdiagram} of $W$ if $Q \subseteq \cP$ and $V(Q) \subseteq U \subseteq V$.
+\end{dfn}
+
+With these definitions in hand, we can impose some conditions on the density and behavior of the propagators of Wilson loop diagrams.
+
+\begin{dfn}\label{admisdfn}
+A Wilson loop diagram $W = (\cP, V)$ is called {\bf admissible} if:
+\begin{enumerate}
+\item $|V| \geq |\cP| + 4$.
+\item There does not exist a non-empty set of propagators $Q \subseteq \cP$ such that $|V(Q)| < |Q| + 3$.
+\item There does not exist a pair of propagators $\{(i,j),(k,l)\} \subseteq \cP$ such that $i < k < j < l$.
+\end{enumerate}
+ \end{dfn}
+
+The first condition bounds the total number of propagators in the diagram, while the second limits how densely propagators can be fitted into any part of the diagram; in particular, it prohibits propagators that connect two adjacent edges and parallel propagators that start and end on the same pair of edges.
+The third condition simply requires that propagators are non-crossing.
+
+These conditions are imposed by the physical interpretation of Wilson loop diagrams (see for example \hlfix{[ref]}{probably for Susama: is there a sensible paper to cite here?}).
+We therefore restrict our attention in this paper to admissible Wilson loop diagrams and their subdiagrams only.
+
+Note that a subdiagram $(Q,U)$ of an admissible Wilson loop diagram need not be admissible itself: it inherits conditions 2 and 3 automatically, but we could have $|V(Q)| = |Q| + 3$.
+We call diagrams of this type {\bf weakly admissible}; in the context of this paper, they occur only when we take an admissible diagram and delete one or more non-supporting vertices.
+
+Due to the physical motivation behind these diagrams, we can associate to each Wilson loop diagram $W$ a matrix $C(W)$, which is defined by
+
+\begin{equation} C(W)_{p,q} = \begin{cases} c_{p,q} & \textrm{ if } q \in V(p) \\
+0  & \textrm{ if } q \not \in V(p)  \end{cases}
+\;. \label{C(W) dfn}\end{equation}
+
+The entries $c_{p,q}$ are non-zero real variables.
+The columns of $C(W)$ correspond to the vertices of $W$ listed in their linear order, and the rows correspond to the propagators of $W$.
+$C(W)$ is therefore only defined up to rearrangement of the rows, which will not matter in this setting since we will only interpret it as carving out a family of elements of the $|\cP| \times |V|$ real Grassmannian.
+
+\begin{eg}
+Consider the admissible Wilson loop diagram 
+\[W = \big(\{(1,4), (2,4), (5,7), (5,8)\},[8]\big),\]
+from Figure~\ref{fig:ex of WLD}. Ordering the propagators as listed above, we obtain the associated matrix
 \[ C(W) = \left(
@@
 
-The matrix $C(W)$ parametrizes a subspace of $\Gr(k, n)$ as shown in \cite{wilsonloop}; we denote this subspace by $\Sigma(W)$.
+The matrix $C(W)$ parametrizes a subspace of $\Gr(k, n)$, as shown in \cite{wilsonloop}; we denote this subspace by $\Sigma(W)$.
 
 From $C(W)$ we obtain the matroid $M(W)$ associated to $W$, which is simply the matroid represented by $C(W)$: its ground set is the set $V$ of vertices of $W$, and the independent sets are exactly the sets $U \subseteq V$ such that the columns of $C(W)$ indexed by $U$ are linearly independent.
-More detail on this is given in Section~\ref{sec:positroid background} below.
-
-The Wilson loop diagram also define a volume form on $\Sigma(W)$, namely 
+More detail on this is given in Section~\ref{sec:M(W)} below.
+
+The Wilson loop diagram also defines a volume form on $\Sigma(W)$, namely 
 \[ \Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V_{p_r}} \textrm{d}c_{p_r}}{R(W)} \;. \]
-The interested reader is referred to [ref] for more information about the volume form. Of interest to us in this paper is the denominator $R(W)$, which we define next.
+The interested reader is referred to \hlfix{[ref]}{any paper that talks about the volume form} for more information about the volume form.
+Of interest to us in this paper is the denominator $R(W)$, which we define next.
 
 \begin{dfn}\label{def R(W)}
-Let $W = (\cP,V)$ be an admissible Wilson loop diagram, and fix an edge $e \in V$.
+Let $W = (\cP,V)$ be an admissible Wilson loop diagram, and fix an edge $e$.
 Let $\{p_1 \ldots p_r\}$ be the propagators with one end lying on edge $e$, ordered so that $p_1$ is closest to the vertex $e$, $p_r$ closest to $e+1$, and $p_i$ is closer to $e$ than $p_{i+1}$ is.
-Then we define
-\[ R_e =  c_{p_1,e+1} \prod_{j= 1}^{r-1} \left((c_{p_j,e} c_{p_{j+1},e+1} - c_{p_{j+1},e} c_{p_{j},e+1} ) \right) c_{p_r,e}\;.\]
-Note that if $r = 1$ (i.e. there is exactly one propagator lying on edge $e$) then $R_e = c_{p,e} c_{p,e+1}$. The denominator $R(W)$ is defined to be the product of all of the $R_e$, i.e. 
+Define
+\[ R_e =  c_{p_1,e+1} \prod_{j= 1}^{r-1} \left((c_{p_j,e} c_{p_{j+1},e+1} - c_{p_{j+1},e} c_{p_{j},e+1} ) \right) c_{p_r,e}\;\]
+to be the component of $R(W)$ associated to edge $e$.
+Note that if $r = 1$ (i.e.
+there is exactly one propagator lying on edge $e$) then this expression simplifies to $R_e = c_{p,e} c_{p,e+1}$.
+The denominator $R(W)$ is defined to be the product of all of the $R_e$, i.e.
 \[R(W) = \prod_{e \in V} R_e.\]
 \end{dfn}
-It is this polynomial $R(W)$ that we characterize in Section~\ref{sec poles}, where we give a simple algorithm to read $R(W)$ directly from the Wilson loop diagram.
-
-\subsection{Positroid background}\label{sec:positroid background}
-
-[positroids]
-
-Let $\binom{[n]}{k}$ be the set of all $k$-subsets of the cyclically ordered set $[n]$.  For each $j \in [n]$, we can define a total order $\leq_j$ on the interval $[n]$ by
+Understanding the polynomial $R(W)$ (and hence the singularities of the volume form $\Omega(W)$) \hlfix{is important for the physics}{help?}.
+In Section~\ref{sec poles} we give a simple algorithm to read $R(W)$ directly from the Wilson loop diagram.
+
+\subsection{Positroids, Grassmann necklaces, and Le diagrams}\label{sec:positroid background}
+
+Let $\binom{[n]}{k}$ denote the set of all $k$-subsets of the cyclically ordered set $[n]$.
+
+For our purposes, a {\bf positroid} is a matroid $M$ with ground set $[n]$ and bases $\cB \subseteq \binom{[n]}{k}$ which can be represented by an element of the positive Grassmannian $\Gr(k,n)$, i.e.
+such that there exists a real full-rank $k\times n$ matrix whose $k\times k$ minors are all nonnegative and such that the minor $[[k]|J]$ is positive if and only if $J \in \cB$.
+
+The interested reader is referred to \cite{Postnikov} for an introduction to the geometry and combinatorics of positroid cells in the positive Grassmannian.
+Postnikov shows in \cite{Postnikov} that the positroids of $\Gr(k,n)$ are indexed by many interesting collections of objects, including Le diagrams, Grassmann necklaces, decorated permutations, and plabic graphs.
+The two most suited to our purposes are the Grassmann necklaces and the Le diagrams, which we introduce below.
+In order to do so, we first need some preliminary definitions.
+
+For each $j \in [n]$, we can define a total order $\leq_j$ on the interval $[n]$ by
 \[ j <_j j+1 <_j \dots <_j n <_j 1 \dots <_j j-1\;.\]
@@
 \[\cB = \left\{J \in \binom{[n]}{k}\ :\ I_i \gale{i} J \ \forall i \in [n]\right\}.\]
+Thus the Grassmann necklace is well suited to testing whether a given $k$-set is a basis for $M$, or for generating a list of all bases of $M$.
 
@@
 By \cite[Theorem 6.5]{Postnikov}, the set of all Le diagrams that fit within a $k\times(n-k)$ rectangle is in 1-1 correspondence with the positroid cells of $\Gr(k,n)$.
-The dimension of a positroid cell is equal to the number of $+$ squares in its Le diagram \cite[Theorem 6.5]{Postnikov}.
+Le diagrams are particularly useful for comparing dimensions of positroids, since the dimension of a positroid is equal to the number of $+$ squares in its Le diagram \cite[Theorem 6.5]{Postnikov}.
 
@@
 
+\subsection{The positroid associated to an admissible Wilson loop diagram}\label{sec:M(W)}
+
+words go here
+
 \section{Wilson Loop diagrams and their Grassmann necklaces}\label{sec GN algorithm}
@@
 In this section we will give an algorithm to go directly from a Wilson loop diagram to the Grassmann necklace of its positroid.
-As well as the result itself, the techniques developped will be useful throughout.
-One of the key insights is that an element of the Grassmann necklace can be viewed as a function from the propagators of the diagram to the vertices in the Grassmann necklace element.
+This is a useful result in and of itself, as it greatly simplifies the process of identifying the positroid associated to a given WLD.
+It also allows us to examine how the positroid changes as we make minor changes to the Wilson loop diagram; indeed, the techniques we develop in this section to verify that our algorithm produces the correct Grassmann necklace will also be used repeatedly in later sections.
+
+One of the key insights is that each element of the Grassmann necklace can be viewed as a function from the propagators of the diagram to the vertices in the Grassmann necklace element.
 This is captured in Definition~\ref{def I_i as a function}, and used throughout the paper.

### 2019-04-10 GWLDCII.tex
paper 2: added an example of the GN algorithm

@@
 
-We first introduce some definitions that will allow us to talk about subsets of the vertices of $W$, subsets of the propagators of $W$, and what it means to be a ``subdiagram'' of $W$.
+We first introduce some definitions that will allow us to talk about subsets of the vertices of $W$, subsets of the propagators of $W$, and what it means to be a subdiagram of $W$.
 
@@
 \begin{enumerate}
-\item For $p = (i,j) \in \cP$, let $V(p) = \{i, i+1, j, j+1\}$ denote the set of vertices supporting $p$. For a set of propagators $P \subseteq \cP$, define 
+\item For $p = (i,j) \in \cP$, let $V(p) = \{i, i+1, j, j+1\}$ denote the set of {\bf vertices supporting $p$}. For a set of propagators $P \subseteq \cP$, define 
 \[V(P) = \bigcup_{p \in P} V(p)\]
 to be the vertex support of $P$.
-\item For $U \subseteq V$, the set of propagators supported on $U$ is denoted by
+\item For $U \subseteq V$, the set of {\bf propagators supported on $U$} is denoted by
 \[\Prop(U) = \{ p \in \cP\ |\ V(p) \cap U \neq \emptyset \}.\]
-Note that a propagator does not need to have its entire support contained in $U$. $\Prop(U)$ is the set of all propagators that would be affected by removing the set $U$.
+Note that a propagator in $\Prop(U)$ does not need to have its entire support contained in $U$. 
 \item Vertices of $W$ that do not support any propagators are called {\bf non-supporting}. The set of all non-supporting vertices in $W$ is denoted $F(\emptyset)$. 
@@
 
-Note that a subdiagram $(Q,U)$ of an admissible Wilson loop diagram need not be admissible itself: it inherits conditions 2 and 3 automatically, but we could have $|V(Q)| = |Q| + 3$.
+Note that a subdiagram $(Q,U)$ of an admissible Wilson loop diagram need not be admissible itself: it inherits conditions 2 and 3 automatically, but we could have $|U| = |Q| + 3$.
 We call diagrams of this type {\bf weakly admissible}; in the context of this paper, they occur only when we take an admissible diagram and delete one or more non-supporting vertices.
 
-Due to the physical motivation behind these diagrams, we can associate to each Wilson loop diagram $W$ a matrix $C(W)$, which is defined by
+Due to the physical motivation behind these diagrams, we can associate a matrix $C(W)$ to each Wilson loop diagram $W$, which is defined elementwise by
 
@@
 
-The matrix $C(W)$ parametrizes a subspace of $\Gr(k, n)$, as shown in \cite{wilsonloop}; we denote this subspace by $\Sigma(W)$.
-
 From $C(W)$ we obtain the matroid $M(W)$ associated to $W$, which is simply the matroid represented by $C(W)$: its ground set is the set $V$ of vertices of $W$, and the independent sets are exactly the sets $U \subseteq V$ such that the columns of $C(W)$ indexed by $U$ are linearly independent.
-More detail on this is given in Section~\ref{sec:M(W)} below.
+
+It was shown in \cite{wilsonloop} that $M(W)$ is actually a positroid whenever $W$ is admissible; the matrix $C(W)$ therefore parametrizes a subspace $\Sigma(W)$ of the totally nonnegative real Grassmannian $\Gr(k, n)$.
+
+Many geometric and combinatorial techniques exist to study the behavior of positroids in $\Gr(k,n)$; more detail on this is given in Section~\ref{sec:positroid background} below.
+Our perspective in this paper is to study the Wilson loop diagrams by studying the positroids they define.
 
@@
 
-Let $\binom{[n]}{k}$ denote the set of all $k$-subsets of the cyclically ordered set $[n]$.
-
-For our purposes, a {\bf positroid} is a matroid $M$ with ground set $[n]$ and bases $\cB \subseteq \binom{[n]}{k}$ which can be represented by an element of the positive Grassmannian $\Gr(k,n)$, i.e.
-such that there exists a real full-rank $k\times n$ matrix whose $k\times k$ minors are all nonnegative and such that the minor $[[k]|J]$ is positive if and only if $J \in \cB$.
-
-The interested reader is referred to \cite{Postnikov} for an introduction to the geometry and combinatorics of positroid cells in the positive Grassmannian.
-Postnikov shows in \cite{Postnikov} that the positroids of $\Gr(k,n)$ are indexed by many interesting collections of objects, including Le diagrams, Grassmann necklaces, decorated permutations, and plabic graphs.
-The two most suited to our purposes are the Grassmann necklaces and the Le diagrams, which we introduce below.
+Let $\binom{[n]}{k}$ denote the set of all $k$-subsets of $[n]$.
+
+For our purposes, a {\bf positroid} is a matroid $M$ (with ground set $[n]$ and bases $\cB \subseteq \binom{[n]}{k}$) which can be represented by an element of the totally nonnegative Grassmannian $\Gr(k,n)$.
+In other words, there exists a full-rank $k\times n$ real matrix whose $k\times k$ minors are all nonnegative and such that the minor $[[k]|J]$ is positive if and only if $J \in \cB$.
+
+The interested reader is referred to \cite{Postnikov} for an introduction to the geometry and combinatorics of positroid cells in the totally nonnegative Grassmannian.
+Postnikov shows in \cite{Postnikov} that the positroids of $\Gr(k,n)$ are indexed by many different collections of objects, each with their own advantages and disadvantages.
+The two most suited to our purposes are Grassmann necklaces and Le diagrams, which we introduce below.
 In order to do so, we first need some preliminary definitions.
@@
 \[\cB = \left\{J \in \binom{[n]}{k}\ :\ I_i \gale{i} J \ \forall i \in [n]\right\}.\]
-Thus the Grassmann necklace is well suited to testing whether a given $k$-set is a basis for $M$, or for generating a list of all bases of $M$.
+Thus the Grassmann necklace is well suited to testing whether a given $k$-set is a basis for $M$, and for generating a list of all bases of $M$.
 
@@
 \caption{Row and column numbering for a Young diagram with $k = 3$, $n = 7$ (left) and $k = 3$, $n = 8$ (right).
-The top left box in each diagram has coordinates $(1,7)$ (left diagram), $(2,8)$ (right diagram).}
+The top left box has coordinates $(1,7)$ in the left diagram, and $(2,8)$ in the right diagram.}
 \label{fig:row column numbering}
@@
 
-An algorithm for constructing the Le diagram associated to a Grassmann necklace was given by Agarwala and Fryer in \cite{ReversingOh}.
+Specifying a $k$-subset $J \subseteq [n]$ therefore uniquely determines the shape of the Le diagram, by taking the elements of $J$ to be the row indices of the diagram.
+
+An algorithm for constructing the Le diagram associated to a Grassmann necklace was given by Agarwala and Fryer in \cite{reversingOh}.
 Since we will make use of this algorithm in Section~\ref{sec dim} below, we summarise the process here.
-\begin{algorithm}\label{alg:GN to Le} \ \cite[Algorithm 2]{ReversingOh}
+\begin{algorithm}\label{alg:GN to Le} \ \cite[Algorithm 2]{reversingOh}
 Let $(I_1,\dots,I_n)$ be a Grassmann necklace of type $(k,n)$. Within a $k \times(n-k)$ square, draw the Young diagram whose rows are labelled by $I_1$ (as per the convention above).
@@
 A method for using the Le diagram to test whether a given $k$-subset is a basis for the corresponding positroid or not was given by Casteels in \cite{CasteelsPaths}.
-
-\subsection{The positroid associated to an admissible Wilson loop diagram}\label{sec:M(W)}
-
-words go here
 
@@
 The fact that Algorithm~\ref{alg:put GN on WLD} does construct the required Grassmann necklace is proved in Theorem~\ref{res:alg gives GN}.
+An worked example of Algorithm~\ref{alg:put GN on WLD} is given after Definition~\ref{def I_i as a function}.
 
 \begin{algorithm}\label{alg:put GN on WLD}
-Let $W = (\cP, [n])$ be an admissible Wilson loop diagram. This gives an algorithm for calculating the set $I_a$, for $a \in [n]$.
+Let $W = (\cP, [n])$ be an admissible Wilson loop diagram. This gives an algorithm for calculating the set $I_i$, for $i \in [n]$.
 
 \begin{enumerate}
-\item Fix a vertex $a \in [n]$. Set $i:=a$ and $I_a = \emptyset$.
+\item Fix a vertex $i \in [n]$. Set $a:=i$ and $I_i = \emptyset$.
 \item While $\cP \neq \emptyset$, perform the following steps.
 \begin{enumerate}
-\item \textbf{Step $i$ for vertex $a$}: If $\Prop(i) \neq \emptyset$ in $W$, write $I_a = I_a \cup i$.
-Let $p \in \Prop(p)$ be the clockwise most propagator supported on $i$.
-Write $W = (\cP \setminus p, n)$.
+\item \textbf{Step $a$ for vertex $i$}: If $\Prop(a) \neq \emptyset$ in $W$, write $I_i = I_i \cup \{a\}$.
+Let $p \in \Prop(a)$ be the clockwise most propagator supported on $a$.
+Write $W = (\cP \setminus \{p\}, [n])$.
 \item If $Prop(i) = \emptyset$ do nothing.
-\item Increment $i$ by 1 and repeat from (a).
+\item Increment $a$ by 1 and repeat from (a).
 \end{enumerate}
@@
 
-Given a propagator $p$ and a vertex $i$ in its support, it will be very useful in the following to understand on what set of vertices the Grassmann necklace algorithm assigns $i$ to $p$.
+\begin{eg}Consider the admissible Wilson loop diagram
+\[W\ =\ \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
+	\begin{scope}
+	\drawWLD{8}{1.5}
+	\drawnumbers
+	\drawlabeledprop{1}{0}{4}{0}{\footnotesize $q\ $}
+	\drawlabeledprop{2}{0}{4}{-1}{\footnotesize $p$}
+    \drawlabeledprop{5}{0}{8}{0}{\footnotesize $r\ \ $}
+    \drawlabeledprop{5}{1}{7}{0}{\footnotesize $\ \ \ s$}
+
+		\end{scope}
+	\end{tikzpicture}\]
+
+To construct $I_1$ we start at vertex 1, so we begin with $i=1$, $a = 1$, and $I_1 = \emptyset$. 
+\begin{itemize}
+\item $a = 1$: Since $\Prop(1) = \{q,r\}$ and $r$ is the clockwise-most of these propagators, we let $I_1 = \{1\}$ and remove propagator $r$ from the diagram. 
+\item $a = 2$: $\Prop(2) = \{p,q\}$, with $q$ being the clockwise-most of these propagators. So $I_1 = \{1,2\}$ and propagator $q$ is removed.
+\item $a = 3$: $\Prop(3) = \{p\}$, so now $I_1 = \{1,2,3\}$ and propagator $p$ is removed. The only remaining propagator in the diagram is $s$.
+\item $a = 4$: Since $p$ and $q$ were removed in earlier steps, we now have $\Prop(4) = \emptyset$.
+\item $a = 5$: $\Prop(5) = \{s\}$, and we have $I_1 = \{1,2,3,5\}$.
+\end{itemize}
+There are no propagators left in the diagram, so the algorithm terminates and we have ${I_1 = \{1,2,3,5\}}$, or $1235$ for short. Viewed as a function, we have
+\[I_1: \cP \longrightarrow [n] : \quad I_1(p) = 3,\quad I_1(q) = 2, \quad I_1(r) = 1, \quad I_1(s) = 5.\]
+Applying the algorithm for all 8 starting vertices, we obtain the sets
+\[1235, 2356, 3456, 4567, 5671, 6712, 7812, 8123.\]
+The reader can easily verify that this sequence of $k$-sets satisfies the definition of a Grassmann necklace, and can (with significantly more work) also verify that this Grassmann necklace defines the positroid associated to the Wilson loop diagram $W$ given above.
+\end{eg}
+
+Given a propagator $p$ and a vertex $i$ in its support, it will be very useful in the following to understand on what set of vertices the algorithm assigns $i$ to $p$.
 The answer is that the set is a non-empty cyclic interval.
@@
 Given a propagator $p$ of an admissible WLD $W$ and a vertex $i$ in the support of $p$, define
-\[J_p^{(W)}(i) = \{m \in [n] \ : \ I^{(W)}_m(p) = i \},\]
+\[J_p^{(W)}(i) = \{m \in [n] \ | \ I^{(W)}_m(p) = i \},\]
 i.e.

### 2019-04-11 GWLDCI.tex
added pictures and responded to comments in sections 1-3

--- 2019-04-06 GWLDCI.tex
@@
 Often we take $V$ to be $[n]$, the cyclically ordered set of integers, $1 \ldots n$.
-In this case, we write $W = (\cP, [n])$.
+In this case, we write $W = (\cP, n)$.
 We introduce some notation to speak of vertices supporting a propagator, and the set of propagators supported on a vertex set.
@@
 \begin{dfn} \label{VPropdfn}
-Let $W = (\cP, [n])$.
+Let $W = (\cP, n)$.
 \begin{enumerate}
@@
 
-The first conditions states that there are at least four more vertices than propagators in an admissible Wilson Loop Diagram.
+The first conditions states that there are at least four more vertices than propagators in an admissible Wilson loop diagram.
 The second imposes an upper bound on how densely the propagators can be fitted in the diagram.
 The third ensures that ensures that no propagators cross in the interior of the diagram.
-In other words, a Wilson loop diagram, $(\cP, [n])$ is admissible if and only if $n > \cP +4$, and has neither crossing propagators nor any pairs of propagators that start and end on the same pair of non-adjacent edges.
+\note{fixed?
+earlier, we had $i + 1 < j$ in the definition.
+When that was fixed, I didn't propagate forward.
+Or am I missing something else?}In other words, a Wilson loop diagram, $(\cP, n)$ is admissible if and only if $n \geq \cP +4$, and has no crossing propagators, no propagators of the form $p = (i, i+1)$, and no pairs of propagators that start and end on the same pair of non-adjacent edges.
 
@@
 \begin{dfn} \label{subdiagramdfn}
-Let $W = (\cP, [n])$ be an admissible Wilson loop diagram.
+Let $W = (\cP, n)$ be an admissible Wilson loop diagram.
 The weakly admissible diagram, $W'$ is a subdiagram of $W$, written $W' \subseteq W$, if \bas W' = (P, V); \quad P \subseteq \cP ; \quad V(P) \subseteq V \subseteq [n]\;.\eas
@@
 \begin{dfn}\label{equivdfn} 
-There is an equivalence relationship on the set of admissible Wilson loops diagrams given by the transititve closure the following binary relation: $W = (\cP, [n]) \sim W'= (\cP', n)$ if
+There is an equivalence relationship on the set of admissible Wilson loops diagrams given by the transititve closure the following binary relation: $W = (\cP, n) \sim W'= (\cP', n)$ if
 \begin{enumerate}
@@
 
-Each Wilson loop diagram, $W = (\cP, [n])$ with $|\cP| = k$ is associated to a $k \times n$ matrix with non-zero real variable entries, called $C(W)$:
+Each Wilson loop diagram, $W = (\cP, n)$ with $|\cP| = k$ is associated to a $k \times n$ matrix with non-zero real variable entries, called $C(W)$:
 
@@
 
-\begin{thm} \label{thm WLD defines matroid} \cite[Theorem 3.6]{wilsonloop} Any admissible Wilson loop diagram $W =(\cP, [n])$ defines a matroid $M(W)$ with ground set $[n]$.
+\begin{thm} \label{thm WLD defines matroid} \cite[Theorem 3.6]{wilsonloop} Any admissible Wilson loop diagram $W =(\cP, n)$ defines a matroid $M(W)$ with ground set $[n]$.
 The independent sets are exactly those subsets $V \subseteq [n]$ such that $\nexists U\subseteq V$ satisfying $|\Prop(U)| < |U|$.
@@
 Throughout, we take the {\em matroid defined by $W$} to be the matroid $M(W)$ of Theorem \ref{thm WLD defines matroid}.
-Note that since vertices of the diagram $W$ correspond to columns of the associated matrix $C(W)$, $M(W)$ can also be thought of as the matroid realized by $C(W)$.
-\note{Can this note have a ref to your earlier paper?
-If not then perhaps expand slightly as although I agree that it is true, I don't think it is quite so trivial.
-Also, I think ``is also'' woulc be fine in place of ``can also be thought of as''}
+Note from equation \eqref{C(W) dfn}that the vertices of the diagram $W$ correspond to columns of the associated matrix $C(W)$.
+Therefore, for any subset of vertices $V \subset [n]$,  then one can write $C(W)|_V$ is the restriction of $C(W)$ to the columns corresponding to $V$.
+Since the non-zero entries of $C(W)$ are real variables, the matrix $C(W)|_V$ does not have full rank if and only if there are fewer rows with non-zero entries than $|V|$.
+This is equivalent to saying that $V$ is a set of dependent columns of $C(W)$ if and only if $|\Prop(V)| < |V|$.
+Comparing this to Theorem \ref{thm:WLDmatroid}, we see that $M(W)$ is also the matroid realized by $C(W)$.
+\sanote{Is this suffient for an explanation?}
 
@@
 \begin{dfn}\label{WLDtriangulationdfn}
-  Let $W = (\cP, [n])$ be an admissible Wilson loop diagram.  The \emph{polygon dissection} associated to $W$, denoted $\tau(W)$, is defined as follows.
+  Let $W = (\cP, n)$ be an admissible Wilson loop diagram.  The \emph{polygon dissection} associated to $W$, denoted $\tau(W)$, is defined as follows.
   \begin{itemize}
@@
 \begin{lem}\label{tausimpleplanarlem}
-If $W = (\cP, [n])$ is an admissible Wilson loop diagram, then $\tau(W)$ is a simple planar graph whose outer face is a cycle.
+If $W = (\cP, n)$ is an admissible Wilson loop diagram, then $\tau(W)$ is a simple planar graph whose outer face is a cycle.
 It is embedded such that the vertices all lie on this infinite face\footnote{That is, it is an \emph{outerplanar} graph}.
@@
 \begin{proof}
-We begin by giving an algorithm for the decomposition, then prove its uniqueness. Let $W = (\cP, [n])$, with $|\cP| = k$.
+We begin by giving an algorithm for the decomposition, then prove its uniqueness. Let $W = (\cP, n)$, with $|\cP| = k$.
 
@@
 \end{itemize}
+
+\begin{eg}
+For example, consider the following Wilson loop diagram, $W$, and its corresponding chord diagram, $\tau(W)$. 
+\bas W = \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
+	\begin{scope}
+	\drawWLD{10}{1.5}
+	\drawnumbers
+	\drawprop{1}{0}{4}{0}
+	\drawprop{2}{0}{4}{-1}
+	\drawprop{4}{1}{8}{0}
+	\drawprop{8}{1}{1}{-1}
+	\drawprop{5}{0}{7}{0}
+		\end{scope}
+	\end{tikzpicture}  \; \quad
+\tau(W) = \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
+	\begin{scope}
+	\drawpolypart{10}{1.5}
+    \drawnumbersshift
+    \drawchord{1}{4}
+    \drawchord{2}{4}
+    \drawchord{4}{8}
+    \drawchord{8}{1}
+    \drawchord{5}{7}
+	\end{scope}
+	\end{tikzpicture} \eas
+
+The set of propagators $P= \{(1,4), (4, 8), (1,8) \}$, define an exact subdiagram of $W$. The vertex set of $t$ are the vertices labeled $\{1, 2,3, 4, 5, 8\}$. The subgraph $t$ is then
+
+\bas t = 
+\begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
+	\begin{scope}
+\pgfmathsetmacro{\n}{10}
+\pgfmathsetmacro{\radius}{1.5}
+\pgfmathsetmacro{\angle}{360/\n}
+    \foreach \i in {1,2,3,4} {
+      \draw (\angle*\i+ \angle/2:\radius) node {$\bullet$}; }
+    \foreach \i in {2,3,4} {
+     \pgfmathsetmacro{\x}{\angle*\i - \angle/2}
+      \pgfmathsetmacro{\concave}{((\n-1.5)/\n)}
+      \draw (\x:\radius cm) .. controls (\angle *\i: \concave* \radius cm) .. (\x + \angle:\radius cm);
+      \draw (\angle*8+ \angle/2:\radius) node {$\bullet$};
+}    
+\foreach \i in {1,2,3,4,8} {
+  \pgfmathsetmacro{\x}{\angle*\i + \angle/2}
+  \draw (\x:\radius*1.15) node {\footnotesize \i};
+}
+    \drawchord{1}{4}
+    \drawchord{2}{4}
+    \drawchord{4}{8}
+    \drawchord{8}{1}
+	\end{scope}
+	\end{tikzpicture} \eas
+
 Note that the subgraph $t$ depends on how the propagators of $P$ sit inside $[n]$, not on how they sit in $W_P$ itself.
 In particular $t$ is not the subgraph of $\tau(W)$ consisting only of edges corresponding to propagators of $P$.
+\end{eg}
 
@@
 
-Conversely, suppose we have an exact subdiagram $(P, V(P))$ of $W = (\cP, [n])$ supported on $|V(P)| = |P|+3$ vertices, and let $t$ be the subgraph of $\tau(W)$ corresponding to $(P,V(P))$.
+Conversely, suppose we have an exact subdiagram $(P, V(P))$ of $W = (\cP, n)$ supported on $|V(P)| = |P|+3$ vertices, and let $t$ be the subgraph of $\tau(W)$ corresponding to $(P,V(P))$.
 
@@
 \begin{cor} \label{uniqueproppartitioncor}
-Any admissible Wilson loop diagram $W = (\cP, [n])$ can be uniquely decomposed into maximal exact subdiagrams. These maximal subdiagrams partition $\cP$.
+Any admissible Wilson loop diagram $W = (\cP, n)$ can be uniquely decomposed into maximal exact subdiagrams. These maximal subdiagrams partition $\cP$.
 \end{cor}
@@
 \begin{dfn}\label{def prop flat} 
-Let $W = (\cP,[n])$ be an admissible Wilson loop diagram and $P \subseteq \cP$. The set $F(P) := V(P^c)^c$ is called the {\em propagator flat} of $P$.
+Let $W = (\cP,n)$ be an admissible Wilson loop diagram and $P \subseteq \cP$. The set $F(P) := V(P^c)^c$ is called the {\em propagator flat} of $P$.
 \end{dfn}
@@
 \begin{lem} \label{maxexactcomplementrank}
-Let $W = (\cP, [n])$ be a Wilson loop diagram, and $P \subseteq \cP$. Then: \begin{enumerate}
+Let $W = (\cP, n)$ be a Wilson loop diagram, and $P \subseteq \cP$. Then: \begin{enumerate}
 \item If $(P,V(P))$ is an exact subdiagram in $W$, then $F(P^c)$ is not an independent flat.
@@
 \begin{lem} \label{contractsubdiaglem} \cite[Theorem 3.33]{wilsonloop} 
-Let $W = (\cP, [n])$ be an admissible Wilson loop diagram and $P \subseteq \cP$.
+Let $W = (\cP, n)$ be an admissible Wilson loop diagram and $P \subseteq \cP$.
 If the set $V(P)^c$ has rank $|P^c|$, then the matroid defined by the subdiagram $(P, V(P))$ is equal to the contraction $M(W)/V(P)^c$.
@@
 \begin{thm} \label{exactuniformthm}
-Let $W':= (P, V(P))$ be a subdiagram of an admissible Wilson loop diagram $W= (\cP, [n])$. Then $W'$ is an exact subdiagram if and only if $M(W')$ is a uniform matroid of rank $|P|$.
+Let $W':= (P, V(P))$ be a subdiagram of an admissible Wilson loop diagram $W= (\cP, n)$. Then $W'$ is an exact subdiagram if and only if $M(W')$ is a uniform matroid of rank $|P|$.
 \end{thm}
@@
 \begin{dfn}
-Given a Wilson loop diagram $W = (\cP, [n])$, define the positroid cell associated to a Wilson loop diagram, $\Sigma(W)$, to be the cell in the CW complex on $\Gr(|\cP|, n)$ defined by the positroid $M(W)$.
+Given a Wilson loop diagram $W = (\cP, n)$, define the positroid cell associated to a Wilson loop diagram, $\Sigma(W)$, to be the cell in the CW complex on $\Gr(|\cP|, n)$ defined by the positroid $M(W)$.
 \end{dfn}
@@
 \begin{thm}\label{same matroid iff equiv}
-Let $W= (\cP, [n])$ and $W'= (\cP', [n])$ be two Wilson Loop diagrams. They define the same matroid if and only if $W \sim W'$.
+Let $W= (\cP, n)$ and $W'= (\cP', n)$ be two Wilson Loop diagrams. They define the same matroid if and only if $W \sim W'$.
 \end{thm}
@@
 Assume that $W$ and $W'$ are equivalent.
-Without loss of generality, write $W = (P \cup R, [n])$ and $W' = (P \cup R', [n])$, where $P \subset \cP \cap \cP'$ and $(R, V(R))$ and $(R', V(R'))$ are two maximally exact subdiagrams, with $R \neq R'$, but $V(R) = V(R')$.
+Without loss of generality, write $W = (P \cup R, n)$ and $W' = (P \cup R', n)$, where $P \subset \cP \cap \cP'$ and $(R, V(R))$ and $(R', V(R'))$ are two maximally exact subdiagrams, with $R \neq R'$, but $V(R) = V(R')$.
 If this is not the case, one may always find a family of diagram, $\{W_i\}$ satisfying this condition and forming a transitive chain connecting $W$ to $W'$ in the equivalence class.

### 2019-04-11 GWLDCI.tex
fixed notation

--- 2019-04-06 GWLDCI.tex
@@
 
-The first conditions states that there are at least four more vertices than propagators in an admissible Wilson Loop Diagram.
+The first conditions states that there are at least four more vertices than propagators in an admissible Wilson loop diagram.
 The second imposes an upper bound on how densely the propagators can be fitted in the diagram.
 The third ensures that ensures that no propagators cross in the interior of the diagram.
-In other words, a Wilson loop diagram, $(\cP, [n])$ is admissible if and only if $n > \cP +4$, and has neither crossing propagators nor any pairs of propagators that start and end on the same pair of non-adjacent edges.
+\note{fixed?
+earlier, we had $i + 1 < j$ in the definition.
+When that was fixed, I didn't propagate forward.
+Or am I missing something else?}In other words, a Wilson loop diagram, $(\cP, [n])$ is admissible if and only if $n \geq \cP +4$, and has no crossing propagators, no propagators of the form $p = (i, i+1)$, and no pairs of propagators that start and end on the same pair of non-adjacent edges.
 
@@
 \begin{dfn}\label{equivdfn} 
-There is an equivalence relationship on the set of admissible Wilson loops diagrams given by the transititve closure the following binary relation: $W = (\cP, [n]) \sim W'= (\cP', n)$ if
+There is an equivalence relationship on the set of admissible Wilson loops diagrams given by the transititve closure the following binary relation: $W = (\cP, [n]) \sim W'= (\cP', [n])$ if
 \begin{enumerate}
@@
 \begin{thm}\label{same matroid iff equiv}
-Let $W= (\cP, [n])$ and $W'= (\cP', [n])$ be two Wilson Loop diagrams. They define the same matroid if and only if $W \sim W'$.
+Let $W= (\cP, [n])$ and $W'= (\cP', n)$ be two Wilson Loop diagrams. They define the same matroid if and only if $W \sim W'$.
 \end{thm}
@@
 
-The map $\tau$ defined in Definition \ref{WLDtriangulationdfn} assigns a dissection of an $n$-gon to a Wilson loop diagram $W = (\cP, n)$.
+The map $\tau$ defined in Definition \ref{WLDtriangulationdfn} assigns a dissection of an $n$-gon to a Wilson loop diagram $W = (\cP, [n])$.
 Recall that if $|\cP| = k$, then $\tau(W)$ is a dissection with $k$ chords.

### 2019-04-13 GWLDCI.tex
Added corollary and reference in section 3

@@
 It will be important in the subsequent section to consider retriangulations.
-\begin{dfn}
-  If $W$ and $W'$ are weakly admissible Wilson loop diagrams on the same vertex set then $\tau(W)$ and $\tau(W')$  differ by a \emph{retriangulation} if there is a bijection $f$ between the maximal triangulated pieces of $\tau(W)$ and the maximal triangulated pieces of $\tau(W')$ such that for any triangulated piece $t$ of $\tau(W)$ the vertex sets of $t$ and $f(t)$ are the same.
+\begin{dfn} \label{retriangulation}
+  If $W = (\cP, [n])$ and $W' = (\cP', [n])$ are weakly admissible Wilson loop diagrams, then $\tau(W)$ and $\tau(W')$  differ by a \emph{retriangulation} if there is a bijection $f$ between the maximal triangulated pieces of $\tau(W)$ and the maximal triangulated pieces of $\tau(W')$ such that for any triangulated piece $t$ of $\tau(W)$ the vertex sets of $t$ and $f(t)$ are the same.
 \end{dfn}
-More casually this definition says that the triangulated pieces of $\tau(W)$ and $\tau(W')$ are the same (so far as their vertex sets are concerned) but that some or all of the triangulated pieces may be differently triangulated while the region being triangulated by each piece (which is defined by the vertex set) remains unchanged.
+More casually this definition says that the maximal triangulated pieces of $\tau(W)$ and $\tau(W')$ are the same (so far as their vertex sets are concerned) but that some or all of the triangulated pieces may be differently triangulated while the region being triangulated by each piece (which is defined by the vertex set) remains unchanged.
+Note that these maximal triangulations correspond to non-crossing partitions of the Wilson loop diagram, in the sense discussed in \cite{positroids13}.
 
@@
 
+Finally, we may express equivalent Wilson loop diagrams in terms of retriangulations.
+
+\begin{cor}\label{equialentretriangulation}
+Two Wilson loop diagrams, $W$ and $W'$ are equivalent if and only if $\tau(W)$ and $\tau(W')$ differ by retriangulations.
+\end{cor}
+
+\begin{proof}
+This follows from the definition of equivalent Wilson loop diagrams, Definition \ref{equivdfn}, the definition of retriangulations, Definition \ref{retriangulation}, and Lemma\ref{lem triang to exact}.
+\end{proof}
+
 \subsection{Matroidal properties of exact subdiagrams \label{sec: exact diagram matroidal props}}
@@
   Let $W$ and $X$ be two equivalent Wilson loop diagrams.
-From Lemma~\ref{lem triang to exact} along with the definitions of $\sim$ and retriangulation, we know that $\tau(W)$ and $\tau(X)$ differ from each other only by retriangulations of their triangulated pieces.
+From Corrolary \ref{equialentretriangulation} we know that $\tau(W)$ and $\tau(X)$ differ from each other only by retriangulations of their triangulated pieces.
 
@@
 
+\bibitem{positroids13}
+Federico Ardila, Felipe Rinc{\'{o}}n, and Lauren Williams.
+\newblock Positroids and non-crossing partitions.
+\newblock {\em Transactions of the American Mathematical Society}, 2015.
+\newblock arXiv:1308.2698v2.
+
 \bibitem{Adamo:2011pv}

### 2019-04-16 GWLDCI.tex
various little things and comments

@@
 \newcommand{\D}{\partial}
-\newcommand{\rk}{\textrm{rk }}
+\newcommand{\rk}{\textrm{rk} }
 \newcommand{\spn}{\textrm{span }}
@@
 This paper gives a way of enumerating the number of different Wilson loop diagrams that correspond to a given positroid cell.
-Furthermore, it shows that that the number of cells in the image of the map to positive Grassmannians is given by counting the directions of associahedrons.
+Furthermore, it shows that the number of cells in the image of the map to positive Grassmannians is given by counting the directions in associahedra.
 
@@
 Furthermore, it gives an algorithm for passing from a Wilson loop diagram to the Grassman necklace that identifies the associated positroid cell.
-In this manner the authors give a means of identifying which positroid cell is associate to which Wilson loop diagram that circumvents the painstaking process of examining bases sets.
+In this manner the authors give a means of identifying which positroid cell is associated to which Wilson loop diagram that circumvents the painstaking process of examining bases sets.
 Finally, the authors characterize the the volume forms that Wilson loop diagrams associate to each positroid cells.
 
-In recent years, there has been a an active program researching the geometry and combinatorics underlying SYM $N=4$ theory \cite{wilsonloop, Arkani-Hamed:2013jha, Amplituhedronsquared, AmplituhedronDecomposition, galashinlam}.
-This body of work started with the observation that the on shell amplitudes of this theory correspond to the volume of a subspace of a positive Grasmannian, called an Amplituhedron \cite{Arkani-Hamed:2013jha}.
-Since then, there has been significant work to study the structure of the amplituhedron, geometrically and combinatorially, for instance \cite{Arkani-Hamed:2013kca, arkani:2012nw, AmplituhedronDecomposition, galashinlam}.
-The focus of much of this work has been to understand the relationship between the combinatorial objects from the physics of the system, BCFW diagrams, and their corresponding natural object for studying the positive Grassmannians, positroid cells.
-
-Meanwhile, there has been a different body of work studying SYM $N=4$ theory from the point of view of Feynman integrals in twistor space\cite{Adamo:2011pv, Britto:2005fq, Cachazo:2004kj}.
+In recent years, there has been an active program researching the geometry and combinatorics underlying SYM $N=4$ theory \cite{wilsonloop, Arkani-Hamed:2013jha, Amplituhedronsquared, AmplituhedronDecomposition, galashinlam}.
+This body of work started with the observation that the on shell amplitudes\note{Is this for tree level amplitudes?
+If so, we should say that} of this theory correspond to the volume of a subspace of a positive Grasmannian, called an Amplituhedron \cite{Arkani-Hamed:2013jha}.
+Since then, there has been significant work studying the structure of the amplituhedron, geometrically and combinatorially, for instance \cite{Arkani-Hamed:2013kca, arkani:2012nw, AmplituhedronDecomposition, galashinlam}.
+The focus of much of this work has been on understanding the relationship between the combinatorial objects from the physics of the system, BCFW diagrams, and their corresponding natural object for studying the positive Grassmannians, positroid cells.
+
+Meanwhile, there has been a different body of work studying SYM $N=4$ theory from the point of view of Feynman integrals in twistor space \cite{Adamo:2011pv, Britto:2005fq, Cachazo:2004kj}.
 These integrals are calculated via Wilson loops.
@@
 This gives a CW complex of some submanifold in $\Gr(k,n)$.
-Understanding the geometry and topology of this space is the subject of ongoing research.
-For Wilson loop diagrams with $k=2$ and $n=6$, one knows that the manifold is not contractible \cite{casestudy}.
+Understanding the geometry and topology of these spaces is the subject of ongoing research.
+For Wilson loop diagrams with $k=2$ and $n=6$, past work of some of us shows that the manifold is not contractible \cite{casestudy}.
 Furthermore, the spaces defined by the Amplituhedron and the Wilson loop diagrams are not the same \cite{Amplituhedronsquared}.
@@
 In this paper, we focus on the correspondence between Wilson loop diagrams and positroids, first defined in \cite{wilsonloop}.
-In that paper, the authors show that there are certain families of diagrams, specifically those with exact subdiagrams, that do map to the same positroid cell.
-In \cite{casestudy} the authors explictly show that not every positroid cell of a given dimension corresponds to a Wilson loop diagram.
+In that paper, one of us with Amat show that there are certain families of diagrams, specifically those with exact subdiagrams, that do map to the same positroid cell.
+In \cite{casestudy} some of us explictly show that not every positroid cell of a given dimension corresponds to a Wilson loop diagram.
 In this paper, we better enumerate this correspondence.
@@
 The main result of Section~\ref{sec equiv} is Theorem~\ref{same matroid iff equiv}.
-To arrive at those results, we first show how certain subdiagrams, called exact subdiagrams, relate to triangulations in polygons in subsection~\ref{sec: polygon partitions}, and then consider the matroidal properties of the exact subdiagrams in subsection~\ref{sec: exact diagram matroidal props}.
+To arrive at those results, we first show, in subsection~\ref{sec: polygon partitions}, how certain subdiagrams, called exact subdiagrams, relate to triangulations in polygons and then consider the matroidal properties of the exact subdiagrams in subsection~\ref{sec: exact diagram matroidal props}.
 Specifically, a subdiagram of a Wilson loop diagrams $W$ defines a uniform matroid if and only if the subdiagram is exact (Theorem \ref{exactuniformthm}), and this uniform matroid is the restriction of the dual matriod of $W$ restricted to the exact subdiagram (Remark \ref{remark exact dual restiction}).
 The main result of the section, Theorem~\ref{same matroid iff equiv}, then appears in subsection~\ref{sec: matroids and equivalence}.
-A consequence of this is the formula for the size of an equivalence class given in Corollary~\ref{number of equiv diagrams}.
+A consequence of this result is the formula for the size of an equivalence class given in Corollary~\ref{number of equiv diagrams}.
 
@@
 The vertices are labeled by $V$ (preserving the cyclic ordering).
-The arc between consecutive vertices are called edges.
+The arcs between consecutive vertices are called edges.
 There are $k$ wavy lines in the interior of the diagram, depicting the proagators, with endpoints on the edges.
-A propagator, $p =(i,j)$ has one endpoint on the edge between the vertex labeled $i$ and $i+1$ and another endpoint on the edge defined by $j$ and $j+1$.
+A propagator, $p =(i,j)$ has one endpoint on the edge between the vertex labeled $i$ and $i+1$ and another endpoint on the edge defined by $j$ and $j+1$, where $j+1$ is taken, as always, modulo $n$.
 Then we write \bas W = (\cP, V) \;.\eas
@@
 \item For $V \subseteq [n]$, write $\Prop(V) = \{ p \in \cP | V(p) \cap V \neq \emptyset \} $.
-\item For $P \subseteq \cP$, define $F(P) = V(P^c)^c$ to be the set of vertices in $[n]$ that do not support any propagators outside the set $P$.
+\item For $P \subseteq \cP$, define $F(P) = V(P^c)^c$ to be\footnote{Here, as throughout, we are using the subscript $c$ for the set theoretic complement.} the set of vertices in $[n]$ that do not support any propagators outside the set $P$.
 \item The set of vertices that are not in the support of any propagotors is denoted  $F(\emptyset)$. Vertices in this set are called non-supporting.  
@@
 The first conditions states that there are at least four more vertices than propagators in an admissible Wilson loop diagram.
-The second imposes an upper bound on how densely the propagators can be fitted in the diagram.
+The second imposes an upper bound on how densely the propagators can be fitted in any portion of the diagram.
 The third ensures that ensures that no propagators cross in the interior of the diagram.
-\note{fixed?
-earlier, we had $i + 1 < j$ in the definition.
-When that was fixed, I didn't propagate forward.
-Or am I missing something else?}In other words, a Wilson loop diagram, $(\cP, [n])$ is admissible if and only if $n \geq \cP +4$, and has no crossing propagators, no propagators of the form $p = (i, i+1)$, and no pairs of propagators that start and end on the same pair of non-adjacent edges.
+In other words, a Wilson loop diagram, $(\cP, [n])$ is admissible if and only if $n \geq |\cP| +4$, and has no crossing propagators, no propagators of the form $p = (i, i+1)$, and no pairs of propagators that start and end on the same pair of non-adjacent edges.
+\note{My concern here is with this last sentence.
+I think it is in fact true, but I don't see that it is obvious from the definitions.
+It is saying that if any set of propagators is too dense according to condition 2, then either a single propagator in that set or a pair of them is already too dense (or condition 3 fails).
+That seems nontrivial to me, even interesting.
+Probably you proved this in your first paper on the topic and it is so old hat you don't even think about it any more, but in that case the appropriate lemma should be cited, rather than implying it is just a rephrasing of the definition itself}
 
@@
 \begin{eg}
-The Wilson loop diagram $W$ shown above is exact.
+The Wilson loop diagram $W$ shown above is admissible.
 There is a single non-supporting vertex in $W$, $F(\emptyset) = \{7\}$.
@@
 These $C(W)$ parametrize a subspace of $\Gr(k, n)$ as shown in \cite{wilsonloop}, call it $\Sigma(W)$.
+\note{I don't think this sentence stands properly alone: What set precisely is ``These'' running over?
+$\Sigma(W)$ is not the whole subspace of $\Gr(k,n)$ it is just the part corresponding to $C(W)$, so the obvious ``it'' in the sentence (namely the subspace) is not the correct one.
+Also, $\Sigma(W)$ appears only one other time in this paper (in a more formal definiiton later which is essentially saying the same thing as this sentence but in more detail), perhaps we should refer forwards; perhaps we don't need this notation in this paper?}
 
@@
 
-A subset $A \subseteq E$ is called {\em independent} in $M$ if $A \subseteq B$ for some $B \in \cB$, and {\em dependent} else.
+A subset $A \subseteq E$ is called {\em independent} in $M$ if $A \subseteq B$ for some $B \in \cB$, and {\em dependent} otherwise.
 The {\em rank}  $\rk(A)$ of a subset $A \subseteq E$ is the size of the largest independent set contained in $A$.
@@
 The set of circuits in a matroid uniquely defines that matroid, as does the set of flats; thus one could specify a matroid by listing its independent sets, bases, circuits, or flats.
-[ref]
 
@@
 Therefore, for any subset of vertices $V \subset [n]$,  then one can write $C(W)|_V$ is the restriction of $C(W)$ to the columns corresponding to $V$.
-Since the non-zero entries of $C(W)$ are real variables, the matrix $C(W)|_V$ does not have full rank if and only if there are fewer rows with non-zero entries than $|V|$.
+Since the non-zero entries of $C(W)$ are independant real variables, the matrix $C(W)|_V$ does not have full rank if and only if there are fewer rows with non-zero entries than $|V|$.
 This is equivalent to saying that $V$ is a set of dependent columns of $C(W)$ if and only if $|\Prop(V)| < |V|$.
 Comparing this to Theorem \ref{thm:WLDmatroid}, we see that $M(W)$ is also the matroid realized by $C(W)$.
-\sanote{Is this suffient for an explanation?}
 
@@
 \item If $C \subseteq [n]$ is a cycle in the matroid, then $\rk(C) = |Prop(C)|$.
-\item If $[n]$ can be partitioned into at least two non-empty sets, each of which support different sets of propagators that form a partition of the propagotor set, \bas [n] = \sqcup_i V(P_i) \quad \textrm{s.t.} \quad \sqcup P_i = \cP; \quad V(P_i) \cap V(P_j) = \emptyset; \quad  P_i \cap P_j = \emptyset \;, \eas then the matroid $M(W)$ is seperable, \bas M(W) = \bigoplus_i M(P_i, V(P_i)) \;.\eas
-\item $F(P)$ is a flat of $M(W)$, thus justifying the name ``propagator flat''.
+\item If $[n]$ can be partitioned into at least two non-empty sets, each of which support different sets of propagators, and that form a partition of the propagotor set, \bas [n] = \sqcup_i V(P_i) \quad \textrm{s.t.} \quad \sqcup P_i = \cP; \quad V(P_i) \cap V(P_j) = \emptyset; \quad  P_i \cap P_j = \emptyset \;, \eas then the matroid $M(W)$ is seperable, \bas M(W) = \bigoplus_i M(P_i, V(P_i)) \;.\eas
+\item $F(P)$ is a flat of $M(W)$ which we call the \emph{propagator flat} of $P$.
 \end{enumerate}
@@
 
-Note that this means that the set, $F(\emptyset)$, of non-supporting vertices is the maximal subset of vertices of $W$ of rank $0$. That is, it is the unique flat of rank $0$ in $M(W)$.
+Note that this means that the set, $F(\emptyset)$, of non-supporting vertices is the maximal subset of vertices of $W$ of rank $0$.
+That is, it is the unique flat of rank $0$ in $M(W)$.
+Also, every element of $F(\emptyset)$ is a circuit and all other circuits of $M(W)$ contain at least two elements.
 
@@
 Since the vertices of $\tau(W)$ are labeled by the edges of $W$, which are cyclically ordered, this gives an ordering to the vertices and the outer face of $\tau(W)$ is a cycle.
-Since $W$ is admissible, no pairs of propagators cross.
+Since $W$ does not admit any propagators of the form $p = (i, i+1)$, there is exactly one edge connecting any two adjacent edges of $\tau(W)$.
+There does not exist two propagators $p,q$ such that both $p$ and $q$ start at edge $i$ and end at edge $j$.
+Therefore, no other two vertices of $\tau(W)$ can be connected by more than one edge.
+Therefore $\tau(W)$ is a simple graph.
+Finally, the embedding of $\tau(W)$ is induced from the embedding of the graph $W$ and since $W$ is admissible, no pairs of propagators cross.
 Therefore, it is a planar embedding.
-Similarly, $W$ does not admit any propagators of the form $p = (i, i+1)$; therefore there is exactly one edge connecting any two adjacent edges of $\tau(W)$.
-Finally, there does not exist two propagators $p,q$ such that both $p$ and $q$ start at edge $i$ and end at edge $j$.
-Therefore, no other two vertices of $\tau(W)$ can be connected by more than one edge.
-Finally, the embedding of $\tau(W)$ is induced from the embedding of the graph $W$.
  \end{proof}
@@
 
-Recall that a planar embedding of a graph is a \emph{triangulation} if all faces, except possibly the infinite face, are triangles.
+A planar embedding of a graph is a \emph{triangulation} if all faces, except possibly the infinite face, are triangles.
 
@@
 \begin{lem} \label{decompositionlem}
-  For $W$ an admissible Wilson loop diagram, the polygon dissection $\tau(W)$ has a unique decomposition into maximal triangulated pieces, and edges in the polygon of $\tau(W)$.
+  For $W$ an admissible Wilson loop diagram, the polygon dissection $\tau(W)$ has a unique decomposition into maximal triangulated pieces and edges in the polygon of $\tau(W)$.
 \end{lem}
@@
 
-By \emph{splitting} a vertex $v$ we will mean replacing $v$ by new vertice $v_1, v_2,\ldots, v_{\text{deg}(v)}$ such that each $v_i$ has exactly one neighbour and the union of the of the $v_i$ is the neighbourhood\footnote{The neighbourhood of a vertex is the set of adjacent vertices} of $v$.
+By \emph{splitting} a vertex $v$ we will mean replacing $v$ by new vertices $v_1, v_2,\ldots, v_{\text{deg}(v)}$ such that each $v_i$ has exactly one neighbour and the union of the of the $v_i$ is the neighbourhood\footnote{The neighbourhood of a vertex is the set of adjacent vertices} of $v$.
 
@@
 \hlfix{If split each vertex of $T(W)$ if it is strictly greater than $3$ valent.}{???} (In other words, we fail to split exactly when the face is a triangle).
-The connected components of $T(W)$ correspond to the decomposition of $\tau(W)$ into maximal triangulated pieces and edges originally in the polygon of $\tau(W)$.  Let $f$ be the forest thus obtained.
+We claim that the connected components of $T(W)$ correspond to the decomposition of $\tau(W)$ into maximal triangulated pieces and edges originally in the polygon of $\tau(W)$.
+To see this let $f$ be the forest thus obtained.
 The vertices of $f$ either have degree 1 or 3.
@@
 Splitting at all the faces that are not triangles ensures maximality of the decomposition.
-If the splitting were not maximal, then one could add a triangle to a connected component of the splitting, but this would imply that that splitting happened at a valence $3$ vertex.
+If the splitting were not maximal, then one could add a triangle to a connected component of the splitting, but this would imply that that splitting happened at a degree $3$ vertex.
 
@@
 In particular, there is a vertex $v$ in $t'$ that corresponds to a split vertex of $T(W)$ in the original decomposition.
-This implies that $v$ has valence greater than $3$ in $T(W)$, and thus the corresponding face of $\tau(W)$ is not a triangle.
-In other words, the decomposition corresponding to $f'$ is not a triangulation.
+This implies that $v$ has degree greater than $3$ in $T(W)$, and thus the corresponding face of $\tau(W)$ is not a triangle.
+In other words, the piece of $\tau(W)$ corresponding to $f'$ is not a triangulation.
 \end{proof}
@@
 Consider any two distinct maximal triangulated pieces of $\tau(W)$.
-These two pieces correspond to subtrees of $T(W)$ and intersect, at most, at a vertex in the interior of $\tau(W)$.
+Using notation as in the previous proof, these two pieces correspond to subtrees of $T(W)$ and intersect, at most, at a vertex in the interior of $\tau(W)$.
 Since the subtrees corresponding to the maximal triangulated pieces are edge disjoint, and the edges of $T(W)$ correspond to the edges of $\tau(W)$, this forces the maximal triangulated pieces to be edge disjoint as well.
@@
 \begin{dfn} \label{retriangulation}
-  If $W = (\cP, [n])$ and $W' = (\cP', [n])$ are weakly admissible Wilson loop diagrams, then $\tau(W)$ and $\tau(W')$  differ by a \emph{retriangulation} if there is a bijection $f$ between the maximal triangulated pieces of $\tau(W)$ and the maximal triangulated pieces of $\tau(W')$ such that for any triangulated piece $t$ of $\tau(W)$ the vertex sets of $t$ and $f(t)$ are the same.
+  If $W = (\cP, [n])$ and $W' = (\cP', [n])$ are weakly admissible Wilson loop diagrams, then $\tau(W)$ and $\tau(W')$  differ by a \emph{retriangulation} if there is a bijection $f$ between the maximal triangulated pieces of $\tau(W)$ and the maximal triangulated pieces of $\tau(W')$ such that for any maximal triangulated piece $t$ of $\tau(W)$ the vertex sets of $t$ and $f(t)$ are the same.
 \end{dfn}
@@
 
-The previous definition makes sense, in fact, for any two polygon dissections of the same polygon.
+The previous definition makes sense, in fact, for any two polygon dissections of the same polygon, not just for those in the image of $\tau$..
 
@@
   \begin{itemize}
-  \item the vertices of $\tau(W)$ corresponding to edges of $W$ defined by cyclically consecutive elements of $V(P)$ as a subset of $[n]$
+  \item the vertices of $\tau(W)$ corresponding to edges of $W$ whose end points are elements of $V(P)$ which are cyclically consecutive in $[n]$
   \end{itemize}
@@
 
-The set of propagators $P= \{(1,4), (4, 8), (1,8) \}$, define an exact subdiagram of $W$. The vertex set of $t$ are the vertices labeled $\{1, 2,3, 4, 5, 8\}$. The subgraph $t$ is then
+The set of propagators $P= \{(1,4), (2,4), (4, 8), (1,8) \}$, define an exact subdiagram of $W$. The vertex set of $t$ are the vertices labeled $\{1, 2,3, 4, 5, 8\}$. The subgraph $t$ is then
 
@@
 If such a triangulation has $n$ vertices then it has $n$ edges on the polygon (that is, on the outer face) and $n-3$ edges which are not.
-No planar graph with the same vertices and the same outer face can have more edges than the triangulation, and every such simple graph with $n-3$ edges off the outer face is a triangulation.
+No planar simple graph with the same vertices and the same outer face can have more edges than a triangulation, and every such simple graph with $n-3$ edges off the outer face is a triangulation.
 
@@
 Consider the intersection of $t$ with the outer face of $\tau(W)$: this is a possibly disconnected subgraph of the polygon of $\tau(W)$ and this subgraph has $m$ vertices.
-Call this new subgraph $S$, and let $j$ be the number of connected components of $S$.
+Call this subgraph $S$, and let $j$ be the number of connected components of $S$.
 To join the components of $S$ into the outer face of $t$, $t$ must have $j$ edges in its outer face which are not in the outer face of $\tau(W)$.
@@
 
-Since Corollary \ref{uniqueproppartitioncor} allows us to decompose any admissible Wilson loop diagram into a collection of maximal exact subdiagrams, in this section we examine the matroid properties of exact subdiagrams more closely.
+Since Corollary \ref{uniqueproppartitioncor} allows us to decompose any admissible Wilson loop diagram into a collection of maximal exact subdiagrams, we are motivated to examine the matroid properties of exact subdiagrams more closely.
 In this section, we show prove two results:
@@
 \item $C = F(\Prop (C))$, i.e. $C$ is a propagator flat.
-\item $F \setminus C$ is an independent set. Furthermore, If $F\setminus C$ is an independent flat if and only if $F(\emptyset) = \emptyset$, that is $W$ has no non-supporting vertices.  
+\item $F \setminus C$ is an independent set. Furthermore, $F\setminus C$ is an independent flat if and only if $F(\emptyset) = \emptyset$, that is $W$ has no non-supporting vertices.  
 \end{enumerate}
@@
 Since $F(P)  = V(P^c)^c$, we have $F(\Prop(v)) \subseteq F(\Prop(C))$.
-Since $v \in F(\Prop(v))$ by the definition of propagator flat, we have $v \in F(\Prop(C))$ as required, and $C \subseteq F(\Prop(C))$.
+Since $v \in F(\Prop(v))$ by the definition of propagator flat, we have $v \in F(\Prop(C))$, and so $C \subseteq F(\Prop(C))$.
 
@@
 Let $B$ be an independent subset of $C$ of maximal rank; we first show that $B \cup \{w\}$ is a dependent set in $M(W)$.
-By Lemma \ref{lem facts about WLD matroids}, \bas |\Prop(C)| = \rk(C) = |B| = \rk(B) .\eas Since $B \subseteq C$ implies that  $\Prop(B) \subseteq \Prop(C)$, this implies that $\Prop(B) = \Prop(C)$.
-Furthermore, since $w \in F(Prop(C)$, $\Prop(B\cup w) \subseteq \Prop(B)$.
-By Lemma \ref{lem facts about WLD matroids} $\rk (B \cup w) \leq \min\{|B\cup w|, |\Prop(B\cup w)|\}$, and therefore $\rk (B \cup w) < |B\cup w|$.
-That is, $B\cup w$ is a circuit in $F(\Prop(C))$.
-Therefore, $B \cup w \subset C$, leading to a contradiction.
+By Lemma \ref{lem facts about WLD matroids}, \bas |\Prop(C)| = \rk(C) = |B| = \rk(B) .\eas Since $\rk(B) \leq |\Prop(B)|$ and $B \subseteq C$ implies that  $\Prop(B) \subseteq \Prop(C)$, this implies that $\Prop(B) = \Prop(C)$.
+Furthermore, since $w \in F(Prop(C))$, we have $\Prop(B\cup w) \subseteq \Prop(B)$.
+By Lemma \ref{lem facts about WLD matroids}
+\[
+\rk (B \cup w) \leq \min\{|B\cup w|, |\Prop(B\cup w)|\},
+\]
+but $\rk (B\cup w) \leq \rk(C) = |B|$, and therefore $\rk (B \cup w) < |B\cup w|$.
+That is, $B\cup w$ contains a circuit containing $w$ and this circuit is in $F(\Prop(C))$.
+Therefore, $w \in C$, leading to a contradiction.
 
@@
   If $F$ is a flat of a Wilson loop diagram, it can be written as the disjoint union of a cyclic propagator flat and an independent set and the set of non-supportive vertices. \end{cor}
+\note{I don't understand this corollary because the non supporting vertices are in $C$}
 
@@
 Since $S$ is an independent set, $\rk(S) = |S|$, and every element of $S$ is independent of $C$, $\rk\big(F(P^c)\big) = \rk(C) + \rk(S)$.
-By Lemma \ref{lem facts about WLD matroids}(2), \ba \rk(S) = \rk\big(F(P^c)\big) -  \rk(S) \leq |P^c| - \rk(C) \;.
+By Lemma \ref{lem facts about WLD matroids}(1), \ba \rk(S) = \rk\big(F(P^c)\big) -  \rk(C) \leq |P^c| - \rk(C) \;.
 \label{increasingrank} \ea
@@
 Let $Q^c = \Prop(C)$.
-Then $C = F(Q^c)$ and, by Lemma \ref{lem facts about WLD matroids}(1), $\rk(C) = |Q^c|$.
+The goal will be to show that $Q=P$ and hence that $S=0$ so $F(P^c)$ is a cyclic flat.
+From the definition of $Q$, we obtain $C = F(Q^c)$ and, by Lemma \ref{lem facts about WLD matroids}(2), $\rk(C) = |Q^c|$.
 By equation \eqref{increasingrank}, \ba |P| + |S| \leq |P| + |P^c| - \rk(C) = |\cP| - |Q^c| = |Q| \;.
-\label{Qsizebound}\ea From equation \eqref{eq decompose F}, \bas |V(Q)| = V(P) \sqcup S = C^c = F(\Prop(C))^c = F(Q^c)^c = V(Q) \;.
-\eas Combining this with equation \eqref{increasingrank} gives \ba |V(Q)| = | V(P) | + |S| = | V(P) | + 3 + |S| \leq |Q| +3 \;.
-\label{Q defines exact}\ea Since $W$ is admissible, one must have $V(Q) = |Q| +3$, that is the subdiagram $(Q, V(Q))$ is exact.
-
-Next, note that \bas C = F(Q^c) = V(Q)^c \subset F(P^c) = V(P)^c \;,\eas which implies that $P \subseteq Q$.
+\label{Qsizebound}\ea From equation \eqref{eq decompose F}, \bas V(P) \sqcup S = C^c = F(\Prop(C))^c = F(Q^c)^c = V(Q) \;.
+\eas Combining this with equation \eqref{increasingrank} gives \ba |V(Q)| = | V(P) | + |S| = | P | + 3 + |S| \leq |Q| +3 \;.
+\label{Q defines exact}\ea Since $W$ is admissible, one must have $|V(Q)| = |Q| +3$, that is the subdiagram $(Q, V(Q))$ is exact.
+
+Next, note that \bas C = F(Q^c) = V(Q)^c \subseteq F(P^c) = V(P)^c \;,\eas which implies that $P \subseteq Q$.
 That is, $(P, V(P))$ is a subdiagram of $(Q, V(Q))$.
@@
 
-To see (3), first note that the second point of this Lemma, combined with Lemma \ref{lem facts about WLD matroids} that
-\bas\rk(F(P^c)) = |\Prop(F(P^c))| = |P^c|.\eas
-
-To prove this in the general case, let let $(R,V(R))$ be an exact subdiagram that is not maximal and $P$ be the maximal exact subdiagram containing it. That is, $R \subsetneq P$.
+To see (3), first note that the second point of this Lemma, combined with Lemma \ref{lem facts about WLD matroids} gives that
+\bas\rk(F(P^c)) = |\Prop(F(P^c))| = |P^c|\eas
+in the case that $(P, V(P))$ is maximal exact.
+
+To prove the result in the general case, let let $(R,V(R))$ be an exact subdiagram that is not maximal and $P$ be the maximal exact subdiagram containing it. That is, $R \subsetneq P$.
 
 Since $R \subset P$, $V(P) = V(R) \sqcup S$, where $S = V(P) \setminus V(R)$.
-Since $P$ and $R$ both define exact subdiagrams, we may write $|V(P)| = |V(R)| + |P \setminus R|$, where $S$ is a vertex set of size $|P \setminus R|$ with $(P \setminus R \subset \Prop(S)$.
-Since  $|S| = |V(P) \setminus V(R)| = |P \setminus R| \leq |\Prop(S) |$, by Lemma \ref{lem facts about WLD matroids}, $\rk(S) = |S|$, implying that $S$ is independent.
+Since $P$ and $R$ both define exact subdiagrams, we may write $|V(P)| = |V(R)| + |P \setminus R|$, and we have that $S$ is a vertex set of size $|P \setminus R|$ with $(P \setminus R) \subseteq \Prop(S)$.
+Since  $|S| = |V(P) \setminus V(R)| = |P \setminus R| \leq |\Prop(S) |$, by Lemma \ref{lem facts about WLD matroids}, $\rk(S) = |S|$\note{I don't see why $\rk(S) = |S|$}, implying that $S$ is independent.
 Taking the complements, we may write \bas F(R^c ) = F(P^c) \sqcup S \;.\eas Taking the rank of both sides, \bas \rk(F(R^c )) = \rk(F(P^c) \sqcup S ) \leq \rk(F(P^c)) + |S| = |P^c| + |\Prop(S)| \leq |R^c| \;.\eas Combining this with \eqref{eq F is dependent} gives the desired result.

### 2019-04-16 GWLDCII.tex
not-quite-right definition of inside/outside

@@
 As a general convention, we write $p = (i,j)$ with  $i < j$ relative to the first vertex.
-However, in Section~\ref{sec:propagator configs} we will need to give the propagators a direction (in order to refer to vertices ``inside'' and ``outside'' the propagator); in this setting, we impose the convention that $p= (i,j)$ denotes a propagator flowing from $i$ to $j$, and $p= (j,i)$ denotes the \emph{same} propagator flowing in the opposite direction.
+However, in Section~\ref{sec:propagator configs} we will need to give the propagators a direction (in order to refer to the regions ``inside'' and ``outside'' the propagator); in this setting, we write $(p,<_i)$ to indicate that $p$ is directed from $i$ to $j$, and $(p,<_j)$ for the same propagator directed from $j$ to $i$.
 
@@
 This correspondence is given explicitly in \cite[Theorem 8]{Oh}: if $(I_1, \dots, I_n)$ is the Grassmann necklace associated to a positroid $M = ([n],\cB)$, then the bases of $M$ are exactly
-\[\cB = \left\{J \in \binom{[n]}{k}\ :\ I_i \gale{i} J \ \forall i \in [n]\right\}.\]
+\[\cB = \left\{J \in \binom{[n]}{k}\ |\ I_i \gale{i} J \ \forall i \in [n]\right\}.\]
 Thus the Grassmann necklace is well suited to testing whether a given $k$-set is a basis for $M$, and for generating a list of all bases of $M$.
@@
 
+\subsection{Wilson loop diagrams as positroids}\label{sec:WLD as positroids}
+
 \section{Wilson Loop diagrams and their Grassmann necklaces}\label{sec GN algorithm}
@@
 
-Note that for any Wilson loop diagram, $W = (\cP, n)$, each propagator $p$ partions $[n]$ into three subsets of $[n]$, $\{[i+2, j-1], V(p), [j+2, i-1]\}$, the support of $p$ and the vertices that lie on either side of $p$.
-In the sequel we refer to the latter two intervals as an interval inside and outside of $p$, depending on a ordering we associate to the propagator.
-
 \begin{dfn}\label{props inside p}
-Let $W = (\cP, n)$ be an admissible Wilson loop diagram, with $p = (i,j) \in \cP$.
-Write $(p, <_a)$ be the same propagator with a direction induced by the linear ordering $<_a$.
-Then \bas V_{in}(p, <_a) = \{b \in [n] | i+1 <_a b <_a j \}\eas the region of $W$ {\bf inside} $p$, and \bas V_{out}(p, <_a) = \{b \in [n] | j+1 <_a b <_a i \} \;.\eas the region {\bf outside }$p$.
+Let $W = (\cP, [n])$ be a weakly admissible Wilson loop diagram, with $p \in \cP$ supported on edges $i$ and $j$.
+Write $(p, <_i)$ to be the same propagator with a direction induced by the linear ordering $<_i$.
+Then
+\begin{gather*}\cP_{in}(p,<_i) = \{ q \in \cP \ |\ (q,<_i) = (k,l) \text{ and }i \leq_i k <_i l \leq_i j \} \\
+\cP_{out}(p,<_i) = \{ q \in \cP \ | \ (q,<_i) = (k,l) \text{ and } j \leq_i k <_i l  \} \;\end{gather*}
+are the sets of propagators inside (resp. outside) $p$. \note{by this definition, $p \not\in \cP_{out}$}
 \end{dfn}
 
-Depending on the ordering associated to $p$, the vertices on the inside and outside chagne. In particular, for $p = (i,j)$, $V_{in}(p, <_i) = V_{out}(p, <_j)$ and $V_{out}(p, <_i) = V_{in}(p, <_j)$.
-
-This in turn defines two sets of propagators, $\{\cP_{in}(p, <_i), \cP_{out}(p, <_i)\}$, where (for $\bullet \in \{in, \; out\}$) \bas \cP_{\bullet} = \{ q \in (\cP \setminus p) | V(q) \cap V_{\bullet}(p)  \neq \emptyset \} \;.\eas When clear, we drop the parentetical and just write $\cP_{in}$ (resp.
-$\cP_{out}$).
-These sets are the sets of propagators, not equal to $p$, \hlfix{whose support contains points in $V_{in}(p, <_*)$ (resp.
-$V_{in}(p, <_*)$), where $<_*$ refers to the appropriate ordering.}{Note, this means that paralell propagators are neither on the inside and outside of $p$.
-Is that okay?} If $W$ has no propagators crossing $p$ and no other propagator supported entirely on $V(p)$, then the set $\{\cP_{in}, p, \cP_{out}\}$ partitions $\cP$.
-Under these circumstances, the set $\cP_{in}$ defines the propagators with end points on one side of $p$, while $\cP_{out}$ defines the propagators with end points on the other side.
-In particular, for (weakly) admissible Wilson loop diagrams, the set $\{\cP_{in}, p, \cP_{out}\}$ is a partition for every propagators $p \in \cP$.
-Recall from Definition~\ref{admisdfn} that a {\em weakly admissible} diagram is one that satisfies the density and non-crossing conditions but does not require that $|V(\cP)| \geq |\cP| + 4$.
-
-As with the vertex sets,  which set of propagators lie inside and outside of $p$ switch depending on the direction imposed $p$.
-
-\begin{dfn}\note{right now this doesn't depend on the order of $i$ and $j$, but that might matter later on?}
-Let $p = (i,j) \in cP$ be a propagator in $W$.  Define the \textit{length} of $p$ to be 
-\[\ell(p) = min\big\{|V_{in}(p)|,|V_{out}(p)|\big\} +2 = min\big\{|[i+1,j]|,|[j+1,i]|\big\}.\]
+% Observe that changing the direction of the propagator simply swaps the inside and outside sets, i.e. for $p = (i,j)$ we have 
+% \[\cP_{in}(p, <_i) = \cP_{out}(p, <_j)\quad \text{ and } \quad \cP_{out}(p, <_i) = \cP_{in}(p, <_j).\]
+
+\begin{dfn}
+Let $p = (i,j) \in \cP$ be a propagator in $W$.  Define the {\bf length} of $p$ to be 
+\[\ell(p) \  =\ \min\big\{|[i+1,j]|,|[j+1,i]|\big\}.\]
 \end{dfn}
-In other words, $\ell(p)$ is the size of the smaller of the number of vertices that lie on either side of the progator $p$.
+In other words, $\ell(p)$ is the size of the smaller of the sets of vertices on either side of the propagator $p$.
 
 \begin{rmk}\label{rem:props of length 2 and 3} 
-The following observations about configurations of propagators of short length in an (weakly) admissibly Wilson loop diagram, $W$, are easily verified:
+The following observations about configurations of propagators of short length in a weakly admissibly Wilson loop diagram $W$ are easily verified:
 \begin{enumerate}
@@
 Now suppose $W$ has no propagators of length $3$.
-%  We will prove the following stronger result: that $D$ admits a pair of propagators of length 2 in the following configuration:
-%\begin{equation}\label{eq:2 prop config}
-%\begin{tikzpicture}[baseline=(current bounding box.east)]
-%\pgfmathsetmacro{\radius}{2}
-%\pgfmathsetmacro{\angle}{20}
-%
-%\begin{scope}
-%\clip (-\radius*1.1,\radius*0.25) rectangle (\radius*1.1,\radius*1.25);
-%
-%\begin{scope}
-%\clip (-\radius*1.1,\radius*0.45) rectangle (\radius*1.1,\radius*1.1);
-%\draw[-] (0,0) circle[radius=\radius cm];
-%\end{scope}
-%
-%% vertices
-%\foreach \i in {2,3,...,7}{
-%	\draw (\angle*\i:\radius*0.98) --  (\angle*\i:\radius*1.02);
-%}
-%
-%\begin{scope}
-%\clip (0,0) circle[radius=\radius];
-%\draw[propagator] (2.5*\angle:\radius*1.1 cm) to [bend left=90] (4.35*\angle:\radius*1.1 cm);
-%\draw[propagator] (4.65*\angle:\radius*1.1 cm) to [bend left=90] (6.5*\angle:\radius*1.1 cm);
-%
-%\end{scope}
-%
-%\node at (80:\radius*1.1) {\tiny $j$};
-%\node at (100:\radius*1.1) {\tiny $j+1$};
-%\node at (90:\radius*0.5) {\small $s_j = s_{j+1} = 2$};
-%
-%\end{scope}
-%\end{tikzpicture}
-%\end{equation}
-
-We need a bit of notation: Let $W = (\cP, n)$ a weakly admissible Wilson loop diagram, and $Q \subseteq \cP$.
-Define the restriction $W|_Q$ to be the diagram $W$ with the propagators not in $Q$ removed.
-That is , \bas W|_Q = (Q, n).
-\eas
-
-%to a region $[i,j]$ to be the subdiagram obtained by forgetting all propagators not wholly supported on vertices in the cyclic interval $[i,j]$; the vertex set remains the same as in $W$.
-Denote this diagram by $W_{[i,j]}$.
-That is, if $W = (\cP, n)$ is a Wilson loop diagram, \bas W_{[i,j]} = (\cP \setminus \Prop([i,j]^c), n)\eas
-
-Given a propagator $p = (i, j)$ oriented $(p, <_i)$,  we can consider two obvious restrictions of $W$, namely \bas W|_{\cP_{in} \cup p} \quad \textrm{and} \quad  W|_{\cP_{out}\cup p}, \eas where the set of non-supportive vertices of  $W|_{\cP_{in} \cup p}$ is $V_{out}$ and  the set of non-supportive vertices of  $W|_{\cP_{out} \cup p}$ is $V_{in}$.
+
+Given a propagator $p = (i, j)$ oriented $(p, <_i)$,  we can construct two obvious subdiagrams of $W$ by removing all of the propagators on one side of $p$ and leaving the vertices intact, i.e.
+the subdiagrams
+\[  (\cP_{in}\cup\{p\}, [n])  \quad \textrm{and} \quad  (\cP_{out}\cup \{p\}, [n]).\]
+
+%where the set of non-supportive vertices of  $W|_{\cP_{in} \cup p}$ is $V_{out}$ and  the set of non-supportive vertices of  $W|_{\cP_{out} \cup p}$ is $V_{in}$.
 That is, these restrictions contain the propagators on the inside and outside of $(p, <_i)$ respectively, as well as $p$ itself.
-\footnote{If we denote $V \subset [n]$ and $Q = \Prop(V^c)$, then we can write \bas M(W|_{Q^c}) = M(W)/F(Q) \oplus M_{\emptyset, n-|i-j+1|} \eas where  $M_{\emptyset, k}$ is the matroid of rank $0$ on a set of $k$.
+%\footnote{If we denote $V \subset [n]$ and $Q = \Prop(V^c)$, then we can write \bas M(W|_{Q^c}) = M(W)/F(Q) \oplus M_{\emptyset, n-|i-j+1|} \eas where  $M_{\emptyset, k}$ is the matroid of rank $0$ on a set of $k$.
 That is $M_{\emptyset, n-|i-j+1|} =M((\emptyset, n-|i-j+1|))$.
@@
 
-With these observations in mind we can return to the proof.
+%With these observations in mind we can return to the proof.
 
@@
 \end{itemize}
-Note that we will be interested in the orientation of $q_r$ so that the previous $p_i$ and $q_i$ are on the outside of $q_r$.
+We can then choose the orientation of $q_r$ so that the previous $p_i$ and $q_i$ are all on the outside of $q_r$, and 
 By the finiteness of $W$ this must eventually terminate in one of the desired configurations. %a configuration of the form \eqref{eq:2 prop config}.
@@
 
-INSERT PICTURE HERE?
+\hlfix{INSERT PICTURE HERE?}{note highlighting this for anyone skimming through looking for pictures to add}
 
@@
 
-%% this was 100% a productive use of my time
-%
-%\[\begin{tabular}{ccc}
-%% possibility 1
-%\begin{tikzpicture}
-%\pgfmathsetmacro{\radius}{2}
-%\pgfmathsetmacro{\angle}{15}
-%\begin{scope}
-%\clip (-\radius*1.1,0) rectangle (\radius*1.1,\radius*1.1);
-%
-%% vertices 
-%\foreach \i in {2,3,4,6,7,8,9,10}{
-%	\draw (\angle*\i:\radius*0.98) --  (\angle*\i:\radius*1.02);
-%}
-%
-%% \dots 
-%\foreach \i in {1,2,3}{
-%	\node at (65 + \i*5:\radius cm) {$\cdot$};
-%}
-%
-%\begin{scope} % this scope contains the propagators
-%\clip (0,0) circle[radius=\radius];
-%
-%\draw[propagator] (\angle*2.4:\radius*1.2 cm) to [bend left=30] (\angle*9.7:\radius*1.2 cm); % q_r
-%\draw[propagator] (\angle*7.7:\radius*1.1 cm) to [bend left=90] (\angle*9.45:\radius*1.1 cm); % p_{r+1}
-%
-%% grey prop begins here
-%
-%\begin{scope}
-%\clip (\angle*7.5:\radius cm) circle[radius=\radius*0.45cm];
-%\draw[light-gray,propagator,seconddash] (\angle*6:\radius*1.02 cm) circle[x radius=\radius*0.4cm, y radius = \radius*0.3cm];
-%\end{scope}
-%
-%\begin{scope}
-%\clip (0,0) circle[radius=\radius];
-%\clip (\angle*7.5:\radius cm) circle[radius=\radius*0.4cm];
-%\draw[light-gray,propagator,firstdash] (\angle*6:\radius*1.02 cm) circle[x radius=\radius*0.4cm, y radius = \radius*0.3cm];
-%\end{scope}
-%
-%\begin{scope}
-%\clip (\angle*7.5:\radius cm) circle[radius=\radius*0.3cm];
-%\clip (0,0) circle[radius=\radius];
-%\draw[light-gray,propagator] (\angle*6:\radius*1.02 cm) circle[x radius=\radius*0.4cm, y radius = \radius*0.3cm];
-%\end{scope}
-%% end gray prop
-%
-%\end{scope}
-%
-%
-%\node at (90:\radius*0.30 cm) {\tiny $q_r$};
-%\node at (\angle*8:\radius*0.73) {\tiny $p_{r+1}$};
-%\node[light-gray] at (\angle*4.9:\radius*0.77 cm) {\tiny $q_{r+1}$};
-%\node at (2*\angle:\radius*1.1) {\tiny $i_r$};
-%\node at (9*\angle:\radius*1.1) {\tiny $j_r$};
-%
-%
-%% circle/edges; needs to happen last to overlap gray
-%\begin{scope}
-%\clip (-\radius*1.1,0.9) rectangle (\radius*1.1,\radius*1.1);
-%\draw[-] (0,0) circle[radius=\radius cm];
-%\end{scope}
-%
-%\end{scope} % ends the overall rectangle clipping
-%\end{tikzpicture}
-%
-%&
-%
-%% possibility 2
-%\begin{tikzpicture}
-%\pgfmathsetmacro{\radius}{2}
-%\pgfmathsetmacro{\angle}{15}
-%\begin{scope}
-%% overall clipping to make the size sensible
-%\clip (-\radius*1.1,0) rectangle (\radius*1.1,\radius*1.1);
-%
-%
-%% vertices
-%\foreach \i in {2,3,4,6,7,8,9,10}{
-%	\draw (\angle*\i:\radius*0.98) --  (\angle*\i:\radius*1.02);
-%}
-%
-%% \dots
-%\foreach \i in {1,2,3}{
-%	\node at (65 + \i*5:\radius cm) {$\cdot$};
-%}
-%
-%\begin{scope} % props
-%\clip (0,0) circle[radius=\radius cm]; 
-%\draw[propagator] (\angle*2.4:\radius*1.2 cm) to [bend left=30] (\angle*9.6:\radius*1.2 cm); % q_r
-%\draw[propagator] (\angle*6.7:\radius*1.1 cm) to [bend left=90] (\angle*8.6:\radius*1.1 cm); % p_{r+1}
-%
-%%% grey prop starts here
-%
-%\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.45cm];
-%\draw[light-gray,propagator,seconddash] (\angle*4.5:\radius*1.3 cm) circle[y radius = 0.5*\radius cm,x radius=\radius*0.7cm];
-%\end{scope}
-%
-%\begin{scope}
-%\clip (0,0) circle[radius=\radius];
-%\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.4cm];
-%\draw[light-gray,propagator,firstdash] (\angle*4.5:\radius*1.3 cm) circle[y radius = 0.5*\radius cm,x radius=\radius*0.7cm];
-%\end{scope}
-%
-%\begin{scope}
-%\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.3cm];
-%\clip (0,0) circle[radius=\radius];
-%\draw[light-gray,propagator] (\angle*4.5:\radius*1.3 cm) circle[y radius = 0.5*\radius cm,x radius=\radius*0.7cm];
-%\end{scope}
-%% grey prop ends here
-%
-%
-%\node at (90:\radius*0.32 cm) {\tiny $q_r$};
-%\node at (\angle*7.75:\radius*0.75) {\tiny $p_{r+1}$};
-%\node[light-gray] at (\angle*4.5:\radius*0.7 cm) {\tiny $q_{r+1}$};
-%\node at (2*\angle:\radius*1.1) {\tiny $i_r$};
-%\node at (9*\angle:\radius*1.1) {\tiny $j_r$};
-%
-%% circle/edges
-%\begin{scope}
-%\clip (-\radius*1.1,0.9) rectangle (\radius*1.1,\radius*1.1);
-%\draw[-] (0,0) circle[radius=\radius cm];
-%\end{scope}
-%
-%\end{scope} % ends overall clip
-%\end{tikzpicture}
-%
-%&
-%
-%% possiblitiy 3
-%\begin{tikzpicture}
-%\pgfmathsetmacro{\radius}{2}
-%\pgfmathsetmacro{\angle}{12}
-%\begin{scope}
-%\clip (-\radius*1.1,0) rectangle (\radius*1.1,\radius*1.1);
-%
-%% vertices
-%\foreach \i in {2,3,6,7,8,9,12,13}{
-%	\draw (\angle*\i:\radius*0.98) --  (\angle*\i:\radius*1.02);
-%}
-%
-%% \dots
-%\foreach \i in {1,2,3}{
-%	\node at (44 + \i*5:\radius cm) {$\cdot$};
-%	\node at (116 + \i*5:\radius cm) {$\cdot$};
-%}
-%
-%\begin{scope} % props
-%\clip (0,0) circle[radius=\radius cm];
-%\draw[propagator] (\angle*2.4:\radius*1.2 cm) to [bend left=30] (\angle*12.6:\radius*1.2 cm); % q_r
-%\draw[propagator] (\angle*6.5:\radius*1.1 cm) to [bend left=100] (\angle*8.5:\radius*1.05 cm); % p_{r+1}
-%
-%%  grey prop 1
-%% not q_{r+1}
-%\begin{scope}
-%\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.45cm];
-%\draw[light-gray,propagator,seconddash] (\angle*6.5:\radius*1.1 cm) to [bend left=90] (\angle*12.5:\radius*1.1cm);
-%\end{scope}
-%
-%\begin{scope}
-%\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.4cm];
-%\draw[light-gray,propagator,firstdash] (\angle*6.5:\radius*1.1 cm) to [bend left=90] (\angle*12.5:\radius*1.1cm);
-%\end{scope}
-%\begin{scope}
-%\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.3cm];
-%\draw[light-gray,propagator] (\angle*6.5:\radius*1.1 cm) to [bend left=90] (\angle*12.5:\radius*1.1cm);
-%\end{scope}
-%% grey prop 1 ends here
-%
-%% grey prop 2
-%% this is q_{r+1}
-%\begin{scope}
-%\clip (\angle*8.5:\radius cm) circle[radius=\radius*0.45cm];
-%\draw[propagator,seconddash,light-gray] (\angle*8.8:\radius*1.1 cm) to [bend left=90] (\angle*12:\radius*1.1cm);
-%\end{scope}
-%
-%\begin{scope}
-%\clip (\angle*8.5:\radius cm) circle[radius=\radius*0.4cm];
-%\draw[propagator,firstdash,light-gray] (\angle*8.8:\radius*1.1 cm) to [bend left=90] (\angle*12:\radius*1.1cm);
-%\end{scope}
-%
-%\begin{scope}
-%\clip (\angle*8.5:\radius cm) circle[radius=\radius*0.3cm];
-%\draw[light-gray,propagator] (\angle*8.8:\radius*1.1 cm) to [bend left=90] (\angle*12:\radius*1.1cm);
-%\end{scope}
-%
-%% grey prop 2 ends here
-%
-%
-%
-%\end{scope}
-%
-%\node at (90:\radius*0.15 cm) {\tiny $q_r$};
-%\node at (\angle*7.5:\radius*0.83) {\tiny $p_{r+1}$};
-%\node[light-gray] at (\angle*11:\radius*0.75 cm) {\tiny $q_{r+1}$};
-%
-%\node at (2*\angle:\radius*1.1) {\tiny $i_r$};
-%\node at (12*\angle:\radius*1.1) {\tiny $j_r$};
-%
-%
-%
-%% overall circle
-%\begin{scope}
-%\clip (-\radius*1.1,0.7) rectangle (\radius*1.1,\radius*1.1);
-%\draw[-] (0,0) circle[radius=\radius cm];
-%\end{scope}
-%
-%
-%\end{scope} % ends overall clip
-%\end{tikzpicture}
-%
-%\end{tabular}
-%\]
-%In each case, the diagram indicates how to choose $q_{r+1}$ satisfying the induction hypothesis.
-In the third case, note that \textit{both} ends of $p_{r+1}$ must share their edge with a propagator of length $\geq 4$; the non-crossing hypothesis on propagators guarantees that at least one will bound a region not containing $p_{r+1}$.
-
 \begin{rmk}
@@
 
-Given a propagator $p$ and a vertex $i$ in its support, it will be very useful in the following to understand on what set of vertices the algorithm assigns $i$ to $p$.
+Given a propagator $p$ and a vertex $i$ in its support, it will be very useful in the following to understand on what set of vertices the Grassmann necklace algorithm assigns $i$ to $p$.
 The answer is that the set is a non-empty cyclic interval.
@@
 \end{proof}
-
-%Next we prove that this algorithm actually gives a Grassmann Necklace as claimed. We begin with some useful definitions and lemmas
-%
-%\begin{dfn}\label{protect dfn}
-%Let $W = (\cP,n)$ be an admissible diagram and $a \in[n]$ a vertex.
-For $p= (i,j) \in \cP$ an a propagator of $W$  and $v \in \{i, j\}$ a vertex of $W$, let $P_{v}(p)$ or $P_{v+1}(p)$ to be two \emph{protecting sets of $p$ at $v$ and ${v+1}$} be a set of propagators defined as follows: \begin{enumerate}
-%\item Work under the linear order on $[n]$, $<_{v+1}$, every propagator is now written as $p = (i_p, j_p)$ such that $i_p <_{v+1} j_p$.
-%\item If there is a propagator $s_1 \in \cP$ such that $s_1 = (i_{s_1}, v)$ or $s_1 = (i_{s_1}, v-1)$, then $s_1 \in P_v(p)$.
-%\item If $s_1$ as above does not exists, then $P_v(p) = \emptyset$.
-In this case, $P_w(p) = \emptyset$.
-When $P_v(p) \neq \emptyset$, if there exists a propagator $t_1 \in \cP$ defined such that $t_1 = (i_{t_1}, v)$ and $s_1 = (i_{s_1}, v)$ with $i_p <_{v+1} i_{t_1} <_{v+1} i_{s_1}$, $P_w(p) = t_1$.
-%\item If $s_1 = (i_{s_1}, v)$ then \bas P_v(p)=  \begin{cases} \{s_1\} \cup P_{i_{s_1}}(s_1) \cup P_{i_{s_1}+1}(s_1) & \textrm{ if } P_{i_{s_1}+1}(s_1) \neq \emptyset \\ s_1 &  \textrm{ else } \end{cases}.
-\eas  If $s_1 = (i_{s_1}, v-1)$ then \bas P_v(p)=  \begin{cases}  \emptyset & \textrm{ if } P_{v-1}(s_1) = \emptyset \\ \{s_1\} \cup P_{v-1}(s_1) & \textrm{ else } \end{cases} \eas.
-%\end{enumerate}
-%\end{dfn}
-%
-%The protective sets $P_\cdot(p)$ are designed to prevent $p$ from contributing the vertex indicated in the subscript at certain points in the Grassmann Necklace, $I_a$.
-Write $P_v(p) = \{s_1, \ldots s_r, t_2,  \ldots t_r\}$ with the $t_x = P_{i_{s_{x-1}}+1}(s_{x-1})$ and $s_x \in P_{i_{s_{x-1}}}(s_{x-1})$ for $x \geq 2$.
-We place the restrictions on the vertex $a$ as follows: \begin{enumerate} \item $P_v$ prevents $p$ from contributing to $I_a$ if \bas i_{s_r}  <_{v+1} a-1 <_{v+1} v\eas \item $P_{v+1}(p)$ prevents $p$ from contributing to $I_a$ only if $P_v(p)$ prevents $p$ from contributing $v$ to $I_a$.
-\end{enumerate}
-%
-%
-%\begin{eg} \label{eg: protective sets}
-%Consider the admissible Wilson loop diagram
-%\bas W=\begin{tikzpicture}[rotate=120,baseline=(current bounding box.east)]
-%	\begin{scope}
-%	\drawWLD{17}{3}
-%	\drawnumbers
-%	\drawprop{1}{0}{16}{0}
-%	\drawlabeledprop{2}{0}{15}{1}{p}
-%    \drawprop{6}{2}{15}{0}
-%    \drawprop{3}{0}{6}{1}
-%    \drawprop{4}{0}{6}{0}
-%    \drawprop{7}{0}{11}{0}
-%    \drawprop{8}{0}{10}{0}
-%    \drawprop{11}{1}{14}{1}
-%    \drawprop{12}{0}{14}{0}
-%		\end{scope}
-%	\end{tikzpicture}
-%\eas Consider the two sets of propagators $Q = \{(3, 6), (4, 6), (6,15)\}$ and $R = \{ (7, 11), (8, 10), (11, 14), (12, 14)\}$.
-The propagator $p = (2, 15)$ is protected at $a = 5$ from contributing $15$ to $I_5$ by the set $P_{15} = Q$.
-There is no set preventing $p$ from contributing $16$ to $I_{15}$.
-At $a = 9$, the set $P_{15} = \{(6,15)\} \subset Q$.
-We may just as easily right $P_{15} = Q$, though the other two propagators in the set prove unnecessary to keep $p$ from contributing $15$ to $I_{9}$.
-At $a = 14$, both $P_{15}$ and $P_{16}$ exists, with $P_{15} = \{(11, 14), (12, 14)\} \subset R $ and $P_{16}= \{(6,15)\} \subset Q$.
-We may just as easily right $P_{15} = R$ and $P_{16} = R$, though the other two propagators in each set are unnecessary.
-%
-%Note that for $a=1$, the propagator $p$ contributes $2$ to $I_1$. However, in this case, we say that neither $P_{15}$ or $P_{16}$ exist.
-%\end{eg}
-%
-%
-%\begin{lem}\label{protecting lem}
-%Let $W = (\cP, [n])$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$, and $a \in [n]$ be a vertex.
-For $v \in \{i,j\}$, if $P_v(p) \neq \emptyset$, write $P_v(p) = \{s_1 \ldots s_r, t_2, \ldots t_r\}$ as above.
-Then $p$ does not contribute $v$ to $I_a$ if $i_{s_r} +1 <_{v+1} a <_{v+1} v+1 $.
-If both $P_v(p)$ and $P_{v+1}(p)$ are non empty, then $p$ also does not contribute $v+1$ to $I_a$.
-%\end{lem}
-%
-%\begin{proof}
-%Note that if $s_1 \in P_v(p)$ exists at step $v$ of Algorithm \ref{alg:put GN on WLD}, then $p$ cannot contribute $p$ to $I_a$.
-Further, if $P_{v+1}(p) \neq \emptyset$, $p$ cannot contribute $v+1$ to $I_a$ either.
-%
-%Next we show that if $P_v(p)$ is as above, with $i_{s_r}+1 <_{v+1} a$, then the propagator $s_1$ exists at step $v$ of Algorithm \ref{alg:put GN on WLD}.
-Let $x$ be the largest integer that such that $a <_{v_1} j_{x}+1$.
-Then $s_x$ cannot contribute to $I_a$ before vertex $v$.
-By construction $P_{i_{s_x}+1}(s_{x-1})\subset P_v(p)$.
-Therefore, $s_{x-1}$ does not contribute $i_{s_x}+1$ to $I_a$.
-Thus we conclude that $s_1$ does not contribute $i_{s_1}$ or $i_{s_1}+1$ to $I_a$.
-In other words, $s_1$ has not been removed from the diagram at vertex $v$.
-%
-%\end{proof}
-%
-%Thus we say that $P_v(p)$ protects $p$ at $v$ from $a$, for $a \in [i_{s_r}+2, v]$. There is an easy corollary to this, describing when such a protecting set cannot exist.
-%
-%\begin{cor} \label{protecting cor}
-%Let $W = (\cP, [n])$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$.
-Picking a $v \in \{i, j\}$ write $p = (i_p, j_p)$ with $i_p <_{v+1} j_p$.
-If $a \in [j_p+1, i_p+1]$ then there can be no protecting set $P_v$ or $P_{v+1}$ protecting $p$ at $v$ or $v+1$ from $a$.
-%\end{cor}
-%
-%\begin{proof}
-%Since $W$ is admissible, it cannot have crossing propagators. Therefore neither $P_v$ cannot have the requisite propagator $s_r$ with $i_{s_r}+1  <_{v+1} a$.
-%\end{proof}
-%
-%The converse, however requires an extra condition.
-%
-%\begin{lem} \label{protect conv lem}
-%For $W = (\cP, [n])$, $p = (i,j)$, and $v \in \{i, j\}$ and $ a \in [n]$ a vertex of $W$, if $v$ (resp.
-$v+1$) is the first vertex of $V(p)$ in the $<_a$ order such that $P_v$ (resp.
-neither $P_v$ nor $P_{v+1}$) does not exist, then $p$ contributes $v$ (resp.
-$v+1$) to $I_a$.
-%\end{lem}
-%
-%\begin{proof}
-%Write $p = (i_p, j_p)$ with $i_p <_{v+1} j_p$.
-%
-%
-%If $p$ doesn't contribute $v$ (or $v+1$) to $I_a$, then either $p$ contributes a different supporting vertex $u$ earlier in the $<_a$ order or there is a propagator $s_1$ at step $v$ of the algorithm \ref{alg:put GN on WLD} preventing $p$ from contributing $v$ to $I_a$, (or there are a pair of propagators $s_1$ and $t_1$ at step $v$ preventing $p$ from contributing $v+1$ at $I_a$.)
-%
-%If there are propagators $s_1, t_1 \in \cP$ that are still in the diagram at step $v$, (write them $s_1 = (i_{s_1}, j_{s_1})$, and $t_1 = (i_{t_1}, j_{t_1})$) with $j_{s_1} \in \{v, v-1\}$, and $i_p \leq_{v+1} i_{t_1} <_v i_{s_1} <_v j_{s_1} \leq_{v} j_{t_1} = v$) then $s_1$ or $t_1$ did not contribute $i_{s_1}$ or  $i_{s_1} +1 $ (resp.
-$i_{t_1}$ or $i_{t_1}+1$) to $I_a$.
-Then one of the following three situations hold: \begin{enumerate} \item $i_{s_1}+1 <_{v+1} a$ and $j_{s_1} = v$: In this case, $s_1$ cannot be removed until $v$.
-\item $i_{s_1}+1 <_{v+1} a$ and $j_{s_1} = v-1$: in this case there exists a propagator $s_2 = (i_{s_2}, j_{s_2})$ with $i_{s_1} \leq_{v+1} i_{s_2} <_{v+1} j_{s_2}$ and $j_{s_2} \in \{j_{s_1}-1, j_{s_1}\}$.
-\item $i_{s_1}+1 \not <_{v+1} a$ and $j_{s_1} = v$: and there must be two other propagators $s_2 = (i_{s_2}, j_{s_2})$ and $t_2 = (i_{t_2}, j_{t_2})$, with $j_{s_2} \in \{i_{s_1}, i_{s_1}-1\}$ and $i_{s_1} \leq_{v+1} i_{t_2} <_{v+1} i_{s_2} <_{v+1} j_{s_2} \leq_{v+1} j_{t_2} = j_{s_1}$   \end{enumerate}
-%
-%However, now one must ensure that the newly identified propagators $s_2$ and $t_3$ do not contribute to $I_a$ before $i_{s_1}$.
-One does this by a similar construction to above.
-In this manner, we begin to build the sets $P_v(p)$ and $P_{v+1}(p)$.
-By finiteness and admissiblity of the Wilson loop diagram, both these sets are finite; one cannot continue to add propagators $s_i$, $t_i$ ad infinitum.
-%
-%We claim that this implies that at some point there is a terminal propagator, $s_m \in P_v(p)$ such that $i_{s_m} + 1 <_{v+1} a$, and \bas  \textrm{ either }= \begin{cases} j_{s_m}=i_{s_{m-1}} & \textrm{ }\\ j_{s_m}=j_{s_{m-1}} & \textrm{ } \end{cases} .\eas We show that all other possibilities lead to a contradiction.
-For the remainder of this proof, indicate by $p_k$ some propagator identified at an earlier stage of this construction.
-That is, for $0 < k < m$, $p_k \in \{s_k, t_k\}$.
-Futher define $p_0 = p$.
-%
-%
-%%\begin{cases} j_{s_{m}=i_{s_{m-1}} & \textrm{ } \\  j_{s_m}=j_{s_{m-1}} & \text{ }\end{cases}
-%
-%If $j_{s_m} \in \{i_{s_{m-1}}-1, j_{s_{m-1}}-1\}$, then, this cannot be the final propagator added to $P_v(p)$, as one would need a means of preventing $s_m$ from contributing $i_{s_{m-1}}-1$ or $j_{s_{m-1}}-1$ to $I_a$.
-%
-%If $i_{s_m} + 1 \not <_{v+1} a$, then there are two.
-% \begin{description}
-%
-%\item[$j_{s_m} = i_{s_{m-1}}$ and $i_{s_m} \in \{i_{p_k}+2, i_{p_k}+1\}$] for some $k<m$.
-By admissibility, there is not room to place both the propagators $s_{m+1}$, and $t_{m+1}$.
-Thus $s_m$ is removed at the step $i_{s_m}$ or $i_{s_m} + 1$.
-Therefore, $s_1$ contributes at either $i_{s_1}$ or $i_{s_1}+1$.
-This leads to a contradiction.
-%\item[$j_{s_m} = i_{s_{m-1}}$ and $i_{s_m} = i_{p_k}+2$] for some $k<m$. This requires either crossing propagators or propagators starting and ending at the same edge, which violates admissibility.
-% \end{description} \note{correct but clear as mud? Help?}
-%\end{proof}
-%
-%We use these results to prove some properties about the Algorithm \ref{alg:put GN on WLD}.
-%\begin{prop}\label{res:alg k labels}
-%If $W = (\cP, [n])$ is an admissible Wilson loop diagram with $|\cP| = k$, then Algorithm~\ref{alg:put GN on WLD} puts exactly $k$ distinct labels on each edge.
-%\end{prop}
-%\begin{proof}
-%It is enough to show that the algorithm terminates in at most $n$ steps for each $a \in [n]$.
-In other words, that all $k$ propagators of $W$ are removed by the time the algorithm has cycled through all the vertices, starting at $a$.
-Suppose this doesn't happen, i.e.
-there is a propagator $p= (i,j)\in \cP$ which survives the first $n$ steps of the algorithm for some starting vertex $a$.
-Without loss of generality, assume $a \leq_a i <_a j$.
-Otherwise, change the roles of $i$ and $j$.
-%
-%Since $p$ is not removed by step $j+1$, by Lemma \ref{protecting lem} there are $4$ protecting sets, $P_i,P_{i+1}, P_{j}$ , and $P_{j+1}$ respectively, allowing $p$ to remain after $n$ steps.
-
-%However, since the cyclic interval $[i,j] \subseteq [a,j]$, $P_j$ and $P_{j+1}$ cannot be protecting sets by Corrollary \ref{protecting cor}.
-%\end{proof}
-
-%\begin{lem}\label{lem last vert}
-%  Let W be an admissible WLD on $n$ vertices with Grassmann necklace $I_1, \ldots, I_n$.
-Then for all $1\leq a \leq n$, $a-1 \not\in I_a$ interpreted cyclically (that is for $a=1$, $a-1$ is interpreted to be $n$.)
-%\end{lem}
-%
-%\begin{proof}
-%Without loss of generality we can suppose $a=1$, so it suffices to show that $C(W)$ with the $n$th column removed is full rank.
-(This suffices because if $C(W)$ with the $n$th column removed had full rank but the lexicographically minimal basis of $C(W)$ included the $n$th column, then we'd obtain a contradiction by taking this minimal basis with the $n$th column removed and extending it to a basis using a column from the first $n-1$ columns of $C(W)$ which is possible by the full rank assumption.)
-%
-%Because the nonzero entries of $C(W)$ are independent indeterminants, it suffices to show that there is some choice of nonzero entries of $C(W)$, one in each row, each in different columns, and none of which are the $n$th column.
-This is equivalent to an assignment of all propagators to supporting vertices so that no two are assigned to the same vertex and none are assigned to vertex $n$.
-The lemma is proved if we show such an assignment exists.
-%
-%Consider an assignment $f$ of a subset of propagators to vertices not including vertex $n$ with the maximal number of propagators.
-If $f$ assigns $n$ propagators then we are done.
-Otherwise there is a propagator $p$ which is not assigned but, by maximality, all of $p$s supporting vertices (other than possibly $n$) are assigned.
-Build a sequence of sets $S_i$ of propagators and $T_i$ of vertices as follows.
-%
-%\begin{enumerate}
-%  \item $S_0={p}$ and $T_0$ is the support of $p$ except for $n$.  Set $i=0$.
-%  \item Let $R$ be the set of propagators which are assigned to a vertex in $T_i$ by $f$. Let $S_{i+1}= S_i \cup R$.  Let $T_{i+1} = T_i \cup (\text{supp}(R) - \{n\})$.\label{item loop step}
-%  \item If there is a vertex $v_{i+1}$ in $T_{i+1}$ which has not been assigned by $f$ then by construction there is a propagator $q_{i+1} \in S_{i+1}-S_i$ which can be assigned to $v_{i+1}$.
-Do so, removing $q_{i+1}$'s old assignment.
-This frees up a vertex $v_{i}$ in $T_i$ and so there is a propagator $q_{i} \in S_{i}$ which can be assigned to this vertex freeing up an earlier vertex and so on until $p$ has been assigned.
-This new assignment contradicts the maximality of $f$.
-%  \item  If nothing changed in step \ref{item loop step} then all vertices of $T_{i+1}$ are assigned to propagators in $S_{i+1}-\{p\}$ and vice versa.
-Thus $|S_{i+1}| = |T_{i+1}|+1$.
-Also all the support of propagators in $S_{i+1}$ is in $T_{i+1} \cup \{n\}$, which is a set of size $|T_{i+1}|+1 = |S_{i+1}|$.
-Thus we have $|S_{i+1}|$ propagators supported on $|S_{i+1}|$ vertices contradicting admissibility.
-%  \item Increment $i$ and go to \ref{item loop step}
-%\end{enumerate}
-%
-%This procedure must be finite as either a contradiction is found or $S_i$ grows at each step but $W$ has finitely many propagators.
-However, the only way for the process to end is by reaching a contradiction.
-Therefore any maximal assignment is a basis not including column $n$ which proves the lemma.
-%\end{proof}
 

### 2019-04-17 GWLDCI.tex
addressed concerns in Karen's e-mail

@@
 \begin{cor} \label{classifyflats}
-  If $F$ is a flat of a Wilson loop diagram, it can be written as the disjoint union of a cyclic propagator flat and an independent set and the set of non-supportive vertices. \end{cor}
-\note{I don't understand this corollary because the non supporting vertices are in $C$}
-
-In particular, any propagator flat can be written as a union of a cyclic propagator flat, an independent set and $F(\emptyset)$ for the appropriate Wilson loop diagram.
+  If $F$ is a flat of a Wilson loop diagram, it can be written as the disjoint union of a cyclic propagator flat and an independent set: \bas F =C \sqcup S \eas where $C$ the union of all circuits in S.
+\end{cor}
+
+\begin{proof}
+By Lemma \ref{lem decompose flat}, the set $C$ is a propagator flat. Furthermore, $S = F \setminus C$, which is independent.
+\end{proof}
+
+In particular, any propagator flat can be written as a union of a cyclic propagator flat and an independent set.
 
@@
 Since $P$ and $R$ both define exact subdiagrams, we may write $|V(P)| = |V(R)| + |P \setminus R|$, and we have that $S$ is a vertex set of size $|P \setminus R|$ with $(P \setminus R) \subseteq \Prop(S)$.
-Since  $|S| = |V(P) \setminus V(R)| = |P \setminus R| \leq |\Prop(S) |$, by Lemma \ref{lem facts about WLD matroids}, $\rk(S) = |S|$\note{I don't see why $\rk(S) = |S|$}, implying that $S$ is independent.
+Since  $|S| = |V(P) \setminus V(R)| = |P \setminus R| \leq |\Prop(S) |$, by Lemma \ref{lem facts about WLD matroids}(1), $\rk(S) \leq |S|$.
+
+Furthermore, by the properties of the rank function, we have that \bas \rk(S) \geq \rk(V(P)) - \rk(V(R)) \geq |V(P) \setminus V(R)| = |S| \; .
+\eas In otherwords, $\rk(S) = |S|$, implying that $S$ is independent.
 Taking the complements, we may write \bas F(R^c ) = F(P^c) \sqcup S \;.\eas Taking the rank of both sides, \bas \rk(F(R^c )) = \rk(F(P^c) \sqcup S ) \leq \rk(F(P^c)) + |S| = |P^c| + |\Prop(S)| \leq |R^c| \;.\eas Combining this with \eqref{eq F is dependent} gives the desired result.

### 2019-04-18 GWLDCI.tex
comments on positroid

@@
 These integrals are calculated via Wilson loops.
-The first author and Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that can be realized as an element of $\Gr(k,n)$ \cite{wilsonloop}.
+The first author and Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that are realized as an element of $\Gr(k,n)$ \cite{wilsonloop}.
 With the second author and others, this work was extended to study these Feynman integrals in terms of positroid cells and the positive Grassmanians \cite{casestudy, non-orientable}.
@@
 A matroid of rank $k$ with a ground set of size $n$ is called {\em realizable} if there exists some $A \in Gr(k,n)$ whose non-zero $k\times k$ minors are exactly those with columns indexed by elements of $\cB$.
-A {\em positroid} is a matroid which can be realized by an element of the totally nonnegative Grassmannian $\Gr(k,n)$.
+If all the maximal minors of the matrix are nonnegative then the matroid realized by this matrix is a {\em positroid}.
+In other words a positroid is a matroid\footnote{Note that matroid isomorphism allows arbitrary permutations of the ground set, while positroid isomorphism only allows cyclic permutations in order to preserve the nonnegativity of the minors.
+In particular, the property of being a positroid is not preserved under matroid isomorphism.} that is realized by an element of the totally nonnegative Grassmannian $\Gr(k,n)$.
 Finally, a {\em uniform matroid} of rank $r$ is a matroid in which any set of size $\leq r$ is independent.

### 2019-04-18 GWLDCI.tex
edits from the rest of my read through

@@
 \begin{proof}
-This follows from Lemma \ref{matroid contraction}. Lemma \ref{maxexactcomplementrank} shows that the supports of exact subdiagrams satisfy the conditions of this lemma.
+This follows from Lemma \ref{contractsubdiaglem}. Lemma \ref{maxexactcomplementrank} shows that the supports of exact subdiagrams satisfy the conditions of this lemma.
 \end{proof}
@@
 
-Suppose $C \subseteq V(P)$ is a circuit of rank $m < |P|$; by Lemma \ref{lem facts about WLD matroids}, we know that $|\Prop_{W'}(C)| = m$ as well, where the subscript to $\Prop$ specifies the diagram we are working in.
+Suppose $C \subseteq V(P)$ is a circuit of rank $m < |P|$.
+By Lemma \ref{lem facts about WLD matroids}, we know that $|\Prop_{W'}(C)| = m$ as well, where the subscript to $\Prop$ specifies the diagram we are working in.
 Observe that $\Prop_{W'}(C)\subseteq P$ by definition.
@@
 In \cite{wilsonloop}, the authors show that all admissible Wilson loop diagrams correspond to positroids.
-That is, they correspond to matroids that can be represented by elements of the positive Grassmannians $\Gr(|\cP|, n)$.
+That is, they correspond to matroids represented by elements of the positive Grassmannians $\Gr(|\cP|, n)$.
 Any positroid of rank $k$ on $n$ elements defines a subspace of the positive Grassmannians $\Gr(k, n)$, namely the points which represent it.
@@
 \begin{proof}
-The unique top dimensional cell of $\Gr(|P|, |V(P)|)$ is defined by all points in $\Gr(|P|, |V(P)|)$ such that all Plucker coordinates are strictly greater than $0$.
-Since $(P, V(P))$ is an exact subdiagram, this all $|P| \times |P|$ minors are non-zero.
-Intersecting these with the cases with the positive Grassmannians demands that all minors be strictly positive.
+The unique top dimensional cell of $\Gr(|P|, |V(P)|)$ is defined by precisely those points in $\Gr(|P|, |V(P)|)$ with the property that all Pl\"ucker coordinates are strictly greater than $0$.
+Since $(P, V(P))$ is an exact subdiagram, the matroid is uniform, and so all $|P| \times |P|$ minors are non-zero.
+Intersecting these with the cases with the positive Grassmannians demands that all minors be strictly positive.\note{I don't understand this last sentence.}
 \end{proof}
@@
 Assume that $W$ and $W'$ are equivalent.
-Without loss of generality, write $W = (P \cup R, [n])$ and $W' = (P \cup R', [n])$, where $P \subset \cP \cap \cP'$ and $(R, V(R))$ and $(R', V(R'))$ are two maximally exact subdiagrams, with $R \neq R'$, but $V(R) = V(R')$.
+Without loss of generality, write $W = (P \cup R, [n])$ and $W' = (P \cup R', [n])$, where $P \subset \cP \cap \cP'$ and $(R, V(R))$ and $(R', V(R'))$ are two maximal exact subdiagrams, with $R \neq R'$, but $V(R) = V(R')$.
 If this is not the case, one may always find a family of diagram, $\{W_i\}$ satisfying this condition and forming a transitive chain connecting $W$ to $W'$ in the equivalence class.
@@
 Since $(R, V(R))$ defines a uniform matroid, by Lemma \ref{exactuniformthm}, the set $U$ is independent in the subdiagram $(R, V(R))$, and thus in $W$.
-The complementary set $F(P)$ is a flat of maximal rank by lemma \ref{maxexactcomplementrank} ($\rk(F(P)) = |P|$).
-Let $B \subset F(P)$ be a maximal indpendent set ($\rk B = |P|$) in $F(P)$.
+The complementary set $F(R^c) = F(P)$ is a flat of maximal rank by lemma \ref{maxexactcomplementrank} ($\rk(F(P)) = |P|$).
+Let $B \subset F(P)$ be a maximal independent set ($\rk B = |P|$) in $F(P)$.
 Since $F(P)$ is a flat, adding any element of $V(R)$ to $B$ increases the rank.
@@
 For the converse, assume that the matroids associated to $W$ and $W'$ are the same: $M(W) = M(W')= M$.
-Let $\mathcal{R} = \{(P_i, V(P_i)\}_{i=1}^k$ and $\mathcal{R}' = \{(P'_i, V(P'_i)\}_{i=1}^l$ be the sets of maximally exact subdiagrams of $W$ and $W'$.
+Let $\mathcal{R} = \{(P_i, V(P_i)\}_{i=1}^k$ and $\mathcal{R}' = \{(P'_i, V(P'_i)\}_{i=1}^l$ be the sets of maximal exact subdiagrams of $W$ and $W'$.
 Write $F_i = F(P_i^c)$ and $F'_i = F(P^{'c}_i)$ to be the complementary cyclic flats.
@@
 Since, by Theorem \ref{exactuniformthm}, any subset $V$ of $M$ such that $M/(V^c)$ is uniform defines an exact subdiagram of both $W$ and $W'$.
-If $U \subset V$ are two such thsets, then the corresponding exact subdiagrams are also subsets.
+If $U \subset V$ are two such sets, then the corresponding exact subdiagrams are also subsets.
 Therefore, $|\mathcal{R}| = |\mathcal{R}'|$, and we write $V(P_i) = V(P'_i)$, after possibly reindexing $\mathcal{R}$ and $\mathcal{R}'$.
@@
 
+\note{Two comments on this proof.
+First I think it was written before other things and so doesn't quite match in style and language; I have improved this a bit but it would benefit from more editing with that in mind.
+Second, I feel that both directions essentially come down to the fact that there is a unique uniform matroid of each dimension and rank.}
+
 Since there is a unique way to decompose $W$ into maximal exact subdiagrams, it is logical to ask how many diagrams there are in an equivalence class.
@@
 \begin{cor}\label{number of equiv diagrams}
-  Let $W$ be an admissible Wilson loop diagram where the sizes of the supports of the nontrivial maximal connected exact subdiagrams are $n_1, n_2, \ldots, n_j$.
+  Let $W$ be an admissible Wilson loop diagram where the sizes of the supports of the nontrivial maximal exact subdiagrams are $n_1, n_2, \ldots, n_j$.
 Then the number of admissible Wilson loop diagrams equivalent to $W$ (including $W$ itself) is
@@
 Two faces are \emph{parallel} if one can be mapped to the other by a translation in $\mathbb{R}^d$.
-In particular parallel faces must be of the same dimension and any pair of vertices are parallel.
+In particular parallel faces must be of the same dimension and any two vertices are parallel to each other.
 
@@
 Associahedra can also be viewed in terms of polygon dissections.
-Let's fix $n$ and consider dissections of a convex $n$-gon.
+Fix $n$ and consider dissections of a convex $n$-gon.
 The $n-1$ asociahedron can be given in terms of the dissections of this $n$-gon; the vertices of the associahedron are the triangulations of the $n$-gon while the dimension $k$ faces are the dissections which are $k$ diagonals away from being a triangulation.
@@
 It turns out that this defines a class of combinatorially equivalent polytopes, which can be proved by giving a realization.
-There are many interesting realizations of the associahedron \cite{}; the following will be the one which we will use.
+There are many interesting realizations of the associahedron \cite{CSZinequivalent}; the following will be the one which we will use.
 \sanote{picture of an associahedron somewhere?}\note{Yes, I agree that there should be a picture}
@@
 In general the $x_1, \ldots, x_n$ may be any points in any $\mathbb{R}^d$.
-Triangulations in the more general context are a decomposition into simplices and the areas of the triangles is replaced by the volume of the simplices.
+Triangulations in this more general context are decompositions into simplices and the area of the triangles is replaced by the volume of the simplices.
 
 $A_n$ defined in this way is a realization of the $n-1$ associahedron (\cite{Ziegler}, Example 9.11).
-Note that we get a realization for any convex $n$-gon, but these realizations are all equally good for our purposes, and so we fix $x_1, \ldots, x_n$ from now on.
+Note that we get a realization for any convex $n$-gon, but these realizations are all equally good for our purposes, and so we fix $x_1, \ldots, x_n$ defining a particular convex $n$-gon from now on.
 
@@
 Recall that if $|\cP| = k$, then $\tau(W)$ is a dissection with $k$ chords.
-Therefore, the map $\tau$ associates to each weakly admissible Wilson loop diagram a $n-3 - k$ dimensional face of the associahedron $A_n$.
+Therefore, the map $\tau$ associates to each weakly admissible Wilson loop diagram an $n-3 - k$ dimensional face of the associahedron $A_n$.
 \sanote{picture of $\tau(W)$ for $k =1$, $n = 5$?}
 
-Note that Wilson loop diagrams which are weakly admissible but not admissible have $\tau$ graphs which are triangulations, hence dimension 0 faces (vertices) in $A_n$.
+Note that Wilson loop diagrams which are weakly admissible but not admissible are necessarily exact and hence have $\tau$ graphs which are triangulations, hence dimension 0 faces (vertices) in $A_n$.
 All of these are equivalent in the sense that they are only retriangulations away from each other.
@@
 Suppose now that this face is a quadrilateral, again no other vertex of this face can be in $(x_i, x_j)$ as otherwise again taking one of the other edges of the face as $d$ we'd get a quadrilateral as in the statement, the same holds if one of the other vertices of the face is $x_i$ or $x_j$ but the other is not.
-If the two other vertices of the face are $x_i$ and $x_j$, then we also get a configuration as in the statement but now with the four vertices being the two ende of $q$ and $x_i, x_j$ and with one of the edges of $f$ as the diagonal.
+If the two other vertices of the face are $x_i$ and $x_j$, then we also get a configuration as in the statement but now with the four vertices being the two ends of $q$ and $x_i, x_j$ and with one of the edges of $f$ as the diagonal.
 Thus we can conclude that none of the vertices of this face are in $[x_i, x_j]$.
@@
   Let $W$ and $X$ be inequivalent.
-If $\tau(W)$ and $\tau(X)$ do not have the same number of diagonals (hence their faces in $A_n$ not having the same dimension) then they are not parallel, so we can assume $\tau(W)$ and $\tau(X)$ do have the same number of diagonals and hence their faces in $A_n$ have the same dimension.
+If $\tau(W)$ and $\tau(X)$ do not have the same number of diagonals (hence their faces in $A_n$ do not have the same dimension) then they are not parallel, so we can assume $\tau(W)$ and $\tau(X)$ do have the same number of diagonals and hence their faces in $A_n$ have the same dimension.
 Let the face associated to $\tau(W)$ be $f_W$ and the face associated to $\tau(X)$ be $f_X$.
@@
   As observed in the proof of Proposition~\ref{prop easy way}, the support of any nonzero vector parallel to an edge is on the indices corresponding to the four vertices bounding the quadrilateral of the dissection associated with the edge.
-Thus $V_{>3}(\tau(W)) \neq V_{>3}(\tau(X))$ (notation as defined before Lemma~\ref{lem good quads}) then the span of the vectors parallel to their edes has different support and so they cannot be parallel.
+Thus if $V_{>3}(\tau(W)) \neq V_{>3}(\tau(X))$ (notation as defined before Lemma~\ref{lem good quads}) then the span of the vectors parallel to their edes has different support and so they cannot be parallel.
 So we can assume that $V_{>3}(\tau(W)) = V_{>3}(\tau(X))$.
@@
 \bibitem{casestudy}
-Susama Agarwala and Sian Fryer.
+Susama Agarwala and Si\^an Fryer.
 \newblock A study in $\textrm{Gr}_{\geq 0}(2,6)$: from the geometric case book
-  of {W}ilson loop diagrams and {SYM} $n=4$.
+  of {W}ilson loop diagrams and {SYM} $N=4$.
 \newblock arXiv:1803.00958.
@@
 \bibitem{generalcombinatoricsI}
-Susama Agarwala, Sian Fryer, and Karen Yeats.
-\newblock Combinatorics and geometry of wilson loop diagrams.
+Susama Agarwala, Si\^an Fryer, and Karen Yeats.
+\newblock Combinatorics of the geometry of {W}ilson loop diagrams {II}: {G}rassmann necklaces, dimensions, and denominators.
 \newblock manuscript in progress.
@@
 Susama Agarwala and Cameron Marcott.
-\newblock Wilson loops in sym $n=4$ do not parametrize an orientable space.
+\newblock Wilson loops in {SYM} $N=4$ do not parametrize an orientable space.
 \newblock arXiv:1807.05397.
@@
 Paul Heslop and Alastair Stewart.
-\newblock The twistor wilson loop and the amplituhedron.
+\newblock The twistor {W}ilson loop and the amplituhedron.
 \newblock {\em Journal of High Energy Physics}, 2018(10):142, Oct 2018.
@@
   R. P. Stanley.
-  \newblock Enumerative Combinatorics, Vol. 2
+  \newblock Enumerative Combinatorics, Vol. 2.
   \newblock Wadsworth (1999)
@@
   G. M. Ziegler.
-  \newblock Lectures on Polytopes
+  \newblock Lectures on Polytopes.
   \newblock Springer GTM 152, (1995)

### 2019-04-23 GWLDCI.tex
fix 3.17 take 2

--- 2019-04-17 GWLDCI.tex
@@
 Since $R \subset P$, $V(P) = V(R) \sqcup S$, where $S = V(P) \setminus V(R)$.
-Since $P$ and $R$ both define exact subdiagrams, we may write $|V(P)| = |V(R)| + |P \setminus R|$, and we have that $S$ is a vertex set of size $|P \setminus R|$ with $(P \setminus R) \subseteq \Prop(S)$.
-Since  $|S| = |V(P) \setminus V(R)| = |P \setminus R| \leq |\Prop(S) |$, by Lemma \ref{lem facts about WLD matroids}(1), $\rk(S) \leq |S|$.
-
-Furthermore, by the properties of the rank function, we have that \bas \rk(S) \geq \rk(V(P)) - \rk(V(R)) \geq |V(P) \setminus V(R)| = |S| \; .
-\eas In otherwords, $\rk(S) = |S|$, implying that $S$ is independent.
-Taking the complements, we may write \bas F(R^c ) = F(P^c) \sqcup S \;.\eas Taking the rank of both sides, \bas \rk(F(R^c )) = \rk(F(P^c) \sqcup S ) \leq \rk(F(P^c)) + |S| = |P^c| + |\Prop(S)| \leq |R^c| \;.\eas Combining this with \eqref{eq F is dependent} gives the desired result.
+Since $P$ and $R$ both define exact subdiagrams, we may write $|V(P)| = |V(R)| + |P \setminus R|$, and we have that $S$ is a vertex set of size $|P \setminus R|$.
+Furthermore, $F(R^c) = F(P^c) \sqcup S$.
+We show that $S$ is an independent set in the subdiagram $(P, V(P))$, and thus in $W$.
+Independence in $(P, V(P))$ implies that for any maximal independent set $\mathfrak{B} \subset F(P^c)$, the set $\mathfrak{B} \sqcup S$ is independent in $F(R^c)$.
+Therefore, \bas \rk (F(R^c)) \geq \rk (F(P^c)) + |S| = |P^c| + |P\setminus R| = |R^c|  \;.\eas By Lemma \ref{lem facts about WLD matroids}, $\rk (F(R^c)) \leq |R^c|$.
+Thus $\rk (F(R^c)) = |R^c|$ as desired.
+
+It remains to show that $S$ is an independent set in the subdiagram $(P, V(P))$.
+Suppose not.
+Then, by Theorem \ref{thm WLD defines matroid} there is a subset $U \subset S$ such that $|\Prop(U)| < |U|$.
+Then the remaining propagators, $P \setminus \Prop(U)$ are supported entirely on $V(P) \setminus U$.
+That is \bas  V(P \setminus \Prop(U)) = V(P) \setminus U\; .\eas Comparing sizes of these sets, we get \bas |V(P \setminus \Prop(U))| = |V(P)| - |U| = |P| +3 -|U| > |P| +3 -|\Prop(U)| = |P \setminus \Prop(U)| +3\; ,\eas which violates admissibility.
+Therefore, $S$ is independent in $(P, V(P))$.
 

### 2019-04-23 GWLDCII.tex
some progress on the GN theorem

@@
 The columns of $C(W)$ correspond to the vertices of $W$ listed in their linear order, and the rows correspond to the propagators of $W$.
-$C(W)$ is therefore only defined up to rearrangement of the rows, which will not matter in this setting since we will only interpret it as carving out a family of elements of the $|\cP| \times |V|$ real Grassmannian.
+$C(W)$ is therefore only defined up to rearrangement of the rows, which will not matter in this setting since we will only interpret it as parametrizing a family of elements of the $|\cP| \times |V|$ real Grassmannian.
 
@@
 \end{eg}
-
-From $C(W)$ we obtain the matroid $M(W)$ associated to $W$, which is simply the matroid represented by $C(W)$: its ground set is the set $V$ of vertices of $W$, and the independent sets are exactly the sets $U \subseteq V$ such that the columns of $C(W)$ indexed by $U$ are linearly independent.
-
-It was shown in \cite{wilsonloop} that $M(W)$ is actually a positroid whenever $W$ is admissible; the matrix $C(W)$ therefore parametrizes a subspace $\Sigma(W)$ of the totally nonnegative real Grassmannian $\Gr(k, n)$.
-
-Many geometric and combinatorial techniques exist to study the behavior of positroids in $\Gr(k,n)$; more detail on this is given in Section~\ref{sec:positroid background} below.
-Our perspective in this paper is to study the Wilson loop diagrams by studying the positroids they define.
 
@@
 
+Let $W = (\cP,[n])$ be an admissible Wilson loop diagram with $k$ propagators, and $C(W)$ the associated matrix defined in \eqref{C(W) dfn}.
+Let $M(W)$ be the matroid realized by $C(W)$, i.e.
+the matroid with ground set $[n]$ whose independent sets are exactly the sets $V \subseteq [n]$ such that the columns of $C(W)$ indexed by $V$ are linearly independent.
+
+In \cite{wilsonloop}, Agarwala and Amat show that $M(W)$ is also characterized by the Wilson loop diagram itself:
+
+\begin{thm} \label{thm WLD defines matroid} \cite[Theorem 3.6]{wilsonloop} The independent sets of the matroid $M(W)$ associated to an admissible Wilson loop diagram $W = (\cP,[n])$ and realized by $C(W)$ are exactly those subsets $V \subseteq [n]$ such that $\nexists U\subseteq V$ satisfying $|\Prop(U)| < |U|$.
+\end{thm}
+In other words, the independent sets of $M(W)$ correspond to the sets of vertices in $W$ such that no subset supports fewer propagators than the vertices it contains.
+
+By studying $M(W)$ in terms of the behavior of the propagators in $W$, Agarwala and Amat show that $M(W)$ is in fact a positroid whenever $W$ is admissible \cite[Corollary 3.39]{wilsonloop}.
+
 \section{Wilson Loop diagrams and their Grassmann necklaces}\label{sec GN algorithm}
-
-Since Wilson loop diagrams correspond to positroids, it is natural to study the subspace of $\Gr(|\cP|, n)$ they define.
 
@@
 Write $(p, <_i)$ to be the same propagator with a direction induced by the linear ordering $<_i$.
-Then
-\begin{gather*}\cP_{in}(p,<_i) = \{ q \in \cP \ |\ (q,<_i) = (k,l) \text{ and }i \leq_i k <_i l \leq_i j \} \\
-\cP_{out}(p,<_i) = \{ q \in \cP \ | \ (q,<_i) = (k,l) \text{ and } j \leq_i k <_i l  \} \;\end{gather*}
-are the sets of propagators inside (resp. outside) $p$. \note{by this definition, $p \not\in \cP_{out}$}
+Then the set of propagators {\bf inside} $(p,<_i)$ is defined to be
+\[\cP_{in}(p,<_i) = \{ q \in \cP \ |\ (q,<_i) = (k,l) \text{ and }i \leq_i k <_i l \leq_i j \} \]
+and the set of propagators {\bf outside} $(p,<_i)$ is
+\[\cP_{out}(p,<_i) = \cP\setminus \cP_{in}(p,<_i).\]
 \end{dfn}
@@
 
-Suppose for a contradition that there exists an admissible diagram for which there exists an $i$ with $k\in I_{i\backslash\{i\}}$ and $k \not\in I_{i+1}$.
+Suppose for a contradition that there exists an admissible diagram for which there exists an $i$ with $k\in I_i\setminus \{i\}$ and $k \not\in I_{i+1}$.
 Fix $n$.
@@
 \item For each $i \in [n]$, $I_i$ is a basis for $M(W)$.
-\item If $J$ is lexicographically smaller than $I_i$ with respect to $<_i$, then $J$ is not a basis for $M(W)$.\note{Si\^an note to self: check whether it's lex smaller or Gale smaller}
+\item If $J$ is lexicographically smaller than $I_i$ with respect to $<_i$, then $J$ is not a basis for $M(W)$.
 \end{itemize}
-The algorithm is pairing each $j \in I_i$ with a unique propagator supported on that vertex so by Lemma~\ref{lem basis as perm} $I_i$ is a basis for $M(W)$.
-%%Recall from [ref] that a $k$-subset $J \in \binom{[n]}{k}$ is a basis for $\PP_W$ if and only if it has no subset $U \subseteq J$ such that $|U| > |Prop(U)|$.
-It is immediately clear from the construction that $I_i$ is a basis for each $i$: the algorithm is pairing each $j \in I_i$ with a unique propagator supported on that vertex, so $|Prop(U)| \geq U$ for all $U \subseteq I_i$.
-
-%%If $\exists l \in J$ with $Prop(l) = \emptyset$ then $J$ is clearly not a basis, so suppose otherwise.  Write
-%%\[I_i = [i_1 <_i i_2 <_i \dots <_i i_r <_i \dots <_i i_k], \quad J = [i_1 <_i i_2 <_i \dots <_i j_r <_i \dots <_i j_k],\]
-%%so that $I_i$ and $J$ differ for the first time in the $r$th position.  Then
-%%\[r-1 \geq |Prop(\{i_1, \dots, i_{r-1}\})| = |Prop(\{i_1, \dots, i_{r+1},j_r\})|,\]
-%%If $|Prop(\{i_1, \dots, i_{r-1}|\}| = r-1$ then we are done; otherwise
+The algorithm is pairing each $j \in I_i$ with a unique propagator supported on that vertex so by Lemma~\ref{lem basis as perm} it immediately follows that $I_i$ is a basis for $M(W)$.
 
@@
 
-However, $j_0$ is the $<_i$-smallest element in the symmetric difference of $J$ and $I_i$, so in particular there is some propagator $p_2$ such that $J(p_2)=I_i(p_1)$.
-Now, let $j_2 = I_i(p_2)$ and note that $j_2 \neq J(p_2)$ (since $I_i(p_1)=J(p_2)$), so either $I_i(p_2) \not\in J$ or there is a propagator $p_3$ such that $J(p_3) = I_i(p_2)$.
-Continuing likewise we get a list of vertices $j_k$ and propagators $p_k$ such that $J(p_k) = I_i(p_{k-1}) = j_{k-1}$.
-
-We claim that the propagators and vertices in this list are distinct.
+However, $j_0$ is the $<_i$-smallest element in the symmetric difference of $J$ and $I_i$, so we must have $j_1 \in J$ as well; in particular, there is some propagator $p_2$ such that $J(p_2)=I_i(p_1)$.
+Let $j_2 = I_i(p_2)$ and note that $j_2 \neq J(p_2)$ (since $I_i(p_1)=J(p_2)$), so either $I_i(p_2) \not\in J$ or there is a propagator $p_3$ such that $J(p_3) = I_i(p_2)$.
+Continue this process for as many steps as possible (i.e.
+for as long as $I_i(p_*) \in J$); this produces a list of vertices $j_k$ and propagators $p_k$ such that
+\[J(p_k) = I_i(p_{k-1}) = j_{k-1}.\]
+
+We claim that the propagators and vertices in this list are distinct; this will show that the process must eventually terminate.
 The claim is proved by induction.
@@
 Now, suppose we have $p_k$ and $j_k$ with $I_i(p_k)=j_k$ and with $j_k\in J$.
-Then $p_{k+1}$ is the propagator associated to $j_k$ by the fixed bijection we have chosed for $J$.
-Since $j_k$ is distinct from the previous $j_j$, $p_{k+1}$ is distinct from the previous $p_j$.
-Then $j_{k+1} = I_i(p_{k+1})$, but $I_i$ is also a bijection, so since $p_{k+1}$ is distinct from the other $p_j$ we have that $j_{k+1}$ is distinct from the other $j_j$ for $1\leq j\leq k$.
+Then there must exist a propagator $p_{k+1}$ with $J(p_{k+1}) = j_k$.
+Since $J: \cP \longrightarrow [n]$ is injective and $j_k$ is not equal to any of the previous vertices $j_0, \dots, j_{k-1}$ by assumption, $p_{k+1}$ must be distinct from the previous $p_j$.
+Define $j_{k+1} = I_i(p_{k+1})$, but since $I_i$ is also a bijection and $p_{k+1}$ is distinct from the earlier $p_j$, it follows that $j_{k+1}$ is distinct from the other $j_j$ for $1\leq j\leq k$.
 Additionally $j_{k+1}\neq j_0$ since $j_0\not\in I_i$ but $j_{k+1}\in I_i$.
@@
 
-By finiteness the list must end, and the only way it can end is with some $p_k$ such that $j_k = I_i(p_k)\not\in J$, so in particular $j_k >_i j_0$.
-
-Next we will prove that $j_k <_i j_0$ for all $k > 0$.
-This gives a contradiction to the exisitence of $J$ and completes the proof of the theorem.
-This proof will also be by induction, however, for the induction to go through nicely we will need to prove the following slightly stronger statement:
+By finiteness the list must end, and the only way it can end is with some $p_k$ such that $j_k = I_i(p_k)\not\in J$. In particular, this implies that $j_k >_i j_0$.
+
+Next we will prove that $j_k <_i j_0$ for all $k > 0$; this gives a contradiction to the existence of $J$ and completes the proof of the theorem.
+This proof will also be by induction; however, for the induction to go through nicely we will need to prove the following slightly stronger statement:
 for all $k>0$ in the list
@@
   \item $I_i(p_k) <_i J(p_k)$, or
-  \item there exists an $ell<k$ such that $I_i(p_\ell) <_i J(p_\ell)$, those two vertices are supported by distinct ends of $p_\ell$ and $p_k$ is on the side of $p_l$ which runs from $I_i(p_\ell)$ to $J(p_\ell)$.
+  \item there exists an $\ell<k$ such that $I_i(p_\ell) <_i J(p_\ell)$, those two vertices support distinct ends of $p_\ell$, and $p_k$ is inside $p_l$ when $p_l$ is directed from $I_i(p_\ell)$ to $J(p_\ell)$.
   \end{itemize}
@@
 
-We already observed that $j_1 <_i j_0$ and $I_i(p_1) <_k J(p_1)$ so we have the base case for the induction.
-Suppose we have the inductive hypothesis for all indices less than $k>1$ and that $p_k$ exists.
-
-By definition $J(p_k) = I_i(p_{k-1}) = j_{k-1}$, so $p_{k-1}$ and $p_{k}$ are both supported at $j_{k-1}$, but $I_{i}(p_{k-1}) = j_{k-1}$.
-Thus either $p_{k-1}$ appears before $p_k$ in the neighbourhood of $j_{k-1}$ or $p_k$ was taken earlier by $I_i$ so $I_i(p_k) <_i I_i(p_{k-1})$.
-In the latter case we are done as $j_k = I_i(p_k) <_i j_{k-1} <_i j_0$ which is what we want.
-So we now assume that $p_{k-1}$ appears before $p_k$ in the neighbourhood of $j_{k-1}$.
+We observed above that $j_1 <_i j_0$ and $I_i(p_1) <_i J(p_1)$ so we have the base case for the induction.
+Now fix $k > 1$ and suppose that the inductive hypothesis holds for all indices less than $k$ and that $p_k$ exists.
+
+By definition $J(p_k) = I_i(p_{k-1}) = j_{k-1}$, so $p_{k-1}$ and $p_{k}$ are both supported at vertex $j_{k-1}$.
+
+Since $I_i$ always chooses the earliest unassigned propagator supported at a vertex, it follows that either $p_{k-1}$ appears before $p_k$ in the neighbourhood of $j_{k-1}$, or that $p_k$ was assigned earlier than $p_{k-1}$ by the algorithm for $I_i$; note that the ordering $p_1,p_2,\dots,p_k$ need not match the order in which Algorithm~\ref{alg:put GN on WLD} assigns propagators to vertices.
+
+In the latter case we are done, since $p_k$ being assigned earlier than $p_{k-1}$ by $I_i$ means exactly that $I_i(p_k) <_i I_i(p_{k-1})$.
+Recalling that $I_i(p_{k-1}) = J(p_k) = j_{k-1}$, we obtain $I_i(p_k) <_i J(p_k)$ and $j_k = I_i(p_k) <_i j_{k-1} <_i j_0$, as required.
+
+Now assume that $p_{k-1}$ appears before $p_k$ in the neighbourhood of $j_{k-1}$.
+
+\hlfix{[picture]}{picture}
 

### 2019-04-26 GWLDCII.tex
copyedits to section 1 and 2 of paper 2

@@
 This paper is concerned with identifying which positroid cells correspond to which Wilson loop diagrams, and how this translates to a geometric tiling of a subspace of the positive Grassmannians.
-Wilson loop diagrams associate a volume form to a positroid cell.
-In this paper, we give an algorithm to identify which cell corresponds to which diagram, via Grassmann Necklaces.
+
+% Wilson loop diagrams associate a volume form to a positroid cell.
+
+% In this paper, we give an algorithm to identify which cell corresponds to which diagram, via Grassmann Necklaces.
 Using the Le diagram representation of positroid cells, we prove results about the dimensions of these cells.
@@
 
-In contrast, the first paper in this series is about combinatorial and matroidal properties of the Wilson loop diagrams.
-The main focus of that paper was to enumerate the positroid cells that appeared in the image of the association between diagrams and cells, as well as the size of the number of Wilson loop diagrams in the pre-image of any positroid cell under this association.s is given by counting the directions of associahedrons.
-
-In recent years, there has been a some interest in understanding the geometry and combinatorics underlying the field theory SYM $N=4$ \cite{wilsonloop, Arkani-Hamed:2013jha, Amplituhedronsquared, AmplituhedronDecomposition, galashinlam}.
-This started with the observation BCFW diagrams, which represent the on shell interactions of this theory correspond to plabic graphs \cite{GrassmannAmplitudebook}.
-Plabic graphs are one of the many equivalent ways to identify positroid cells of the positie Grassmannians \cite{Postnikov}.
-This work led to the representation of the on shell integrals associated this theory in terms of a geometric space embedded in $\Gr(k,n)$, called the Amplituhedron \cite{Arkani-Hamed:2013jha, Arkani-Hamed:2013kca}.
-More over, inegrals associated to the BCFW diagrams define a volume form on the Amplituhedron.
-Since then, there has been significant work to understand the volume form and its physical implications \cite{galashinlam, UnwindingAmplituhedron}.
-
-Meanwhile, a different body of work has studied SYM $N=4$ theory from the point of view of Feynman integrals in twistor space \cite{Adamo:2012xe, Adamo:2011pv,  Boels:2007qn, Bullimore:2010pj}.
+In contrast, the first paper in this series focuses on combinatorial and matroidal properties of the Wilson loop diagrams.
+The main focus of that paper was to enumerate the positroid cells that could be associated to Wilson loop diagrams with a fixed number of vertices and propagators, as well as counting the number of Wilson loop diagrams in the pre-image of any positroid cell under this association.
+
+In recent years, there has been significant interest in understanding the geometry and combinatorics underlying the field theory SYM $N=4$ \cite{wilsonloop, Arkani-Hamed:2013jha, Amplituhedronsquared, galashinlam, AmplituhedronDecomposition}.
+This started with the observation that BCFW diagrams, which represent the on shell interactions of this theory, correspond to plabic graphs \cite{GrassmannAmplitudebook}.
+Plabic graphs were introduced by Postnikov in \cite{Postnikov}, and provide one of the many equivalent ways to classify the positroid cells of the positive real Grassmannian $\Gr(k,n)$.
+This led to the representation of the on shell integrals associated to this theory in terms of a geometric space (the Amplituhedron) embedded in $\Gr(k,n)$ \cite{Arkani-Hamed:2013kca,Arkani-Hamed:2013jha}.
+Moreover, integrals associated to the BCFW diagrams define a volume form on the Amplituhedron, \hlfix{which is useful for ...}{we need a vague one-line description here}.
+Since then, there has been significant work to understand the volume form and its physical implications \cite{UnwindingAmplituhedron,galashinlam}.
+
+Meanwhile, a different body of work has studied SYM $N=4$ theory from the point of view of Feynman integrals in twistor space \cite{Adamo:2011pv,Adamo:2012xe,  Boels:2007qn, Bullimore:2010pj}.
 These integrals are calculated via holomorphic Wilson loops.
-As with the Amplituhedron, each Wilson loop represents the sum of a family of $N^kMHV$ Feynman diagrams.
-The sum of the corresponding sum of Feynman integrals associate a volume form to space \cite{Hodges:2012ym}.
+As with the Amplituhedron, each Wilson loop represents the sum of a family of $N^kMHV$ Feynman diagrams, and adding up the corresponding sums of Feynman integrals associates a volume form to \hlfix{space}{I don't know if this was supposed to say ``space'' or ``this space'', and if ``this space'' I don't know which space it's referring to.} \cite{Hodges:2012ym}.
 The first author and Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that can be realized as an element of $\Gr(k,n)$ \cite{wilsonloop}, while other work has shown a connection between the space parametrized by Wilson loop diagrams and the Amplituhedron \cite{casestudy, Amplituhedronsquared}.
 
-In the above work and elsewhere, it is clear that while the space parametrized by the Wilson loop diagrams is related to the Amplituhedron.
-They are not the same.
-For in stance, \cite{non-orientable} shows that the space parametrized by the Wilson loop diagrams can be seen as a non-orientable vector bundle over some submanifold of $\Gr(k,n)$, while it is conjectured that the Amplituhedron is orientable.
+In the above work and elsewhere, it is clear that while the space parametrized by the Wilson loop diagrams is related to the Amplituhedron, they are not the same space.
+For instance, it is conjectured that the Amplituhedron is orientable, whereas the first author and Marcott show in \cite{non-orientable} that the space parametrized by the Wilson loop diagrams can be seen as a non-orientable vector bundle over some submanifold of $\Gr(k,n)$.
 Furthermore, the cells associated to the Wilson loop diagrams are different from the cells associated to BCFW diagrams, as one sees from counting arguments in comparing the results of \cite{AmplituhedronDecomposition} and \cite{casestudy}.
-This is not too alarming, as one expects space parametrized by the Wilson loop diagrams to project down to something close to the Amplituhedron \cite{wilsonloop, Amplituhedronsquared}.
-
-This paper continues this work by identifying which positroid cells are associated to which Wilson loop diagram.
-Where the BCFW diagrams identify positroid cells via plabic graphs, in this paper, we give an algorithm to read off of a Wilson loop diagram the associated Grassmann Necklace.
-Furthermore, while the BCFW cells are all 4k dimensional, we show that the positroid cells associated to Wilson loop diagrams are $3k$ dimensional.
-Again, this is not alarming, as \cite{non-orientable} has shown that the actual geometric space parametrized by the Wilson loop diagrams is a non-orientable $k$ dimensional bundle over this $3k$ dimensional manifold in $\Gr(k,n)$.
-
-Finally, when computing a finite volume to a geometric object defined by the Wilson loop diagrams, one must ensure at any singularities cancel.
-This has been expicitly shown in a few cases \cite{casestudy, HeslopStewart}, but it has been hard to prove exactly due to the non-one to one or onto relationship between Wilson loop diagrams and $3k$ dimensional positroid cells of $\Gr(k,n)$.
+This is not too alarming, as \hlfix{one expects}{can we call this a conjecture?} the space parametrized by the Wilson loop diagrams to project down to something close to the Amplituhedron \cite{wilsonloop, Amplituhedronsquared}.
+
+This paper continues this work by identifying which positroid cells are associated to which Wilson loop diagram: specifically, we give an algorithm to read off the Grassmann necklace of the associated positroid cell from the Wilson loop diagram.
+We also show that the positroid cells associated to Wilson loop diagrams are all $3k$ dimensional; by contrast, the BCFW cells are all $4k$ dimensional \hlfix{[ref]}{someone actually proved this, right?}.
+Again, this is not too alarming, as it was shown in \cite{non-orientable} that the actual geometric space parametrized by the Wilson loop diagrams is a non-orientable $k$-dimensional bundle over this $3k$ dimensional manifold in $\Gr(k,n)$.
+
+As noted above, the sum of the Feynman integrals associated to Wilson loop diagrams gives the volume of \hlfix{the space}{help?}; if this volume is to be finite, then any singularities appearing in individual integrals must cancel out in the overall sum.
+This has been verified explicitly in a few cases \cite{casestudy, HeslopStewart}, but it is hard to prove in general due to the fact that the relationship between Wilson loop diagrams and $3k$ dimensional positroid cells of $\Gr(k,n)$ is neither one-to-one nor onto.
+In this paper, we give a characterization of the factors appearing in the denominator of these Feynman integrals in terms of the Grassmann necklace of the associated positroid, thus providing a much simpler and more tractable link between the singularities and the diagrams.
+
+% when computing a finite volume to a geometric object defined by the Wilson loop diagrams, one must ensure that any singularities cancel.
+This has been verified explicitly in a few cases \cite{casestudy, HeslopStewart}, but it has been hard to prove in general due to the fact that the relationship between Wilson loop diagrams and $3k$ dimensional positroid cells of $\Gr(k,n)$ is neither one-to-one nor onto.
 In this paper, we give a characterisation of the denominator of the Feynman integral defined by a Wilson loop diagram in terms of the algorithm that associated the same diagram to a Grassman Necklace.
@@
 
-Section~\ref{section general background} gives the required background for Wilson loop diagrams (subsection~\ref{section WLD background}) and for positroids and some of their many combinatorial versions (subsection~\ref{sec:positroid background}).
-
-Section~\ref{sec GN algorithm} proceeds to give an algorithm to go directly from a Wilson loop diagram to its Grassmann necklace (Algorithm~\ref{alg:put GN on WLD} and the proof that it is correct in Theorem~\ref{res:alg gives GN}).
-In view of the known combinatorial equivalences, it was already possible to get the Grassmann necklace of a Wilson loop diagram, but it involved going through the matrix $C(W)$ and the positroid as a matroid.
-The direct algorithm shows us directly how each propagator contributes to each element of the Grassmann necklace.
-This idea is crucial for all the arguments of the present paper.
-Along with the algorithm, Section~\ref{sec GN algorithm} contains two key techincal lemmas, Lemma~\ref{lem sian}, the focus of subsection~\ref{sec:propagator configs}, and the cyclic interval lemma, Lemma~\ref{vertex cyclic int lem} in subsection~\ref{sec:GN alg}, which leads into the proof of Theorem~\ref{res:alg gives GN} as well as being important in subsequent sections.
-
-Section~\ref{sec dim} proceeds to show that the dimension of the positroid cell defined by a Wilson loop diagram has dimension three times the number of propagators, Theorem~\ref{thm dim}.
-The proof here is very explicit, keeping track of how a propagator contributes $+$s to the Le diagram, and correspondingly somewhat technical.
-Section~\ref{sec poles} characterizes the denominator of the integral of a Wilson loop diagram in terms of how propagators contribute to the Grassmann necklace.
-This result is also given by an algorithm, Algorithm~\ref{alg WLD to denom via GN}, and theorem, Theorem~\ref{thm denom}.
+In Section~\ref{section general background}, we summarize the required background for Wilson loop diagrams (subsection~\ref{section WLD background}), the theory of positroids in $\Gr(k,n)$ and their characterization in terms of Grassmann necklaces and Le diagrams (subsection~\ref{sec:positroid background}), and the link between Wilson loop diagrams and positroids (subsection~\ref{sec:WLD as positroids}).
+
+In Section~\ref{sec GN algorithm} we state an algorithm for constructing the Grassmann necklace of the positroid associated to a Wilson loop diagram (Algorithm~\ref{alg:put GN on WLD}) and prove its correctness (Theorem~\ref{res:alg gives GN}).
+While it was already possible to construct the Grassmann necklace of a Wilson loop diagram via existing bijections between some of the various combinatorial objects that index the positroid cells, this process was convoluted and involved multiple steps; our algorithm allows us to track directly how each propagator in the Wilson loop diagram contributes to each term in the Grassmann necklace.
+Many of the technical lemmas required to prove Theorem~\ref{res:alg gives GN} continue to be important in subsequent sections: in particular we have Lemma~\ref{lem sian}, which identifies certain configurations of propagators which must appear in any admissible Wilson loop diagram, and Lemma~\ref{vertex cyclic int lem}, which shows that the pattern of values that a propagator contributes to each term of the Grassmann necklace is both simple and predictable.
+
+In Section~\ref{sec dim} we examine the dimension of positroids associated to Wilson loop diagrams, and show that the dimension is always equal to three times the number of propagators in the diagram (Theorem~\ref{thm dim}).
+While this has been proved by Marcott in \hlfix{[ref]}{Did this get published yet?} using geometric methods, our proof is constructive and explicitly relates the position of the plusses in the Le diagram to the propagators in the Wilson loop diagram.
+
+Finally in Section~\ref{sec poles} we characterize the denominator of the integral of a Wilson loop diagram in terms of how propagators contribute to the Grassmann necklace.
+This characterization is given explicitly by Algorithm~\ref{alg WLD to denom via GN} and Theorem~\ref{thm denom}.
 
@@
 
-Generally speaking the propagators are undirected, so $(i,j)$ and $(j,i)$ represent the same propagator.
-As a general convention, we write $p = (i,j)$ with  $i < j$ relative to the first vertex.
-However, in Section~\ref{sec:propagator configs} we will need to give the propagators a direction (in order to refer to the regions ``inside'' and ``outside'' the propagator); in this setting, we write $(p,<_i)$ to indicate that $p$ is directed from $i$ to $j$, and $(p,<_j)$ for the same propagator directed from $j$ to $i$.
-
 Let $[n]$ denote the set of integers $\{1,\dots,n\}$ with the obvious cyclic and linear orders.
@@
 
-We first introduce some definitions that will allow us to talk about subsets of the vertices of $W$, subsets of the propagators of $W$, and what it means to be a subdiagram of $W$.
+Generally speaking the propagators in a Wilson loop diagram are undirected, so $(i,j)$ and $(j,i)$ represent the same propagator.
+If we need to impose a direction on a propagator $p = (i,j)$, for example in order to consider the region ``inside'' or ``outside'' of $p$, we write $(p,<_i)$ to indicate that $p$ is directed from edge $i$ to edge $j$, and $(p,<_j)$ for the opposite direction.
+
+We also impose the convention that all vertices should always be interpreted in terms of the cyclic order on $V$; for example, if $V = [n]$ then $(n,n+3)$ means the propagator connecting edges $3$ and $n$.
+This viewpoint is beneficial for us since many of our proofs rely on restricting our attention to a region of the diagram bounded by a given propagator, or to short propagators such as $(i,i+2)$, and these behave the same regardless of whether we cross the ``first'' vertex or not; however, we emphasize that this is different to the standard convention in the physics literature, where propagators are written $(i,j)$ with $1 \leq i<j \leq n$.
 
@@
 
-For our purposes, a {\bf positroid} is a matroid $M$ (with ground set $[n]$ and bases $\cB \subseteq \binom{[n]}{k}$) which can be represented by an element of the totally nonnegative Grassmannian $\Gr(k,n)$.
+For our purposes, a {\bf positroid} is a matroid $M$ (with ground set $[n]$ and bases $\cB \subseteq \binom{[n]}{k}$) which can be represented by an element of the positive Grassmannian $\Gr(k,n)$.
 In other words, there exists a full-rank $k\times n$ real matrix whose $k\times k$ minors are all nonnegative and such that the minor $[[k]|J]$ is positive if and only if $J \in \cB$.
 
-The interested reader is referred to \cite{Postnikov} for an introduction to the geometry and combinatorics of positroid cells in the totally nonnegative Grassmannian.
+We summarize here only the subset of positroid theory that we require in this paper; the interested reader is referred to \cite{Postnikov} for more details.
 Postnikov shows in \cite{Postnikov} that the positroids of $\Gr(k,n)$ are indexed by many different collections of objects, each with their own advantages and disadvantages.
@@
 By \cite[Theorem 17.1]{Postnikov}, the Grassmann necklaces of type $(k,n)$ are in 1-1 correspondence with the positroid cells in $\Gr(k,n)$.
-This correspondence is given explicitly in \cite[Theorem 8]{Oh}: if $(I_1, \dots, I_n)$ is the Grassmann necklace associated to a positroid $M = ([n],\cB)$, then the bases of $M$ are exactly
+Each term $I_i$ is simply the minimal (with respect to the $<_i$-lex order) basis of the positroid.
+A characterization of all bases of the positroid in terms of the Grassmann necklace and the Gale order was given by Oh in \cite[Theorem 8]{Oh}: if $(I_1, \dots, I_n)$ is the Grassmann necklace associated to a positroid $M = ([n],\cB)$, then the bases of $M$ are exactly
 \[\cB = \left\{J \in \binom{[n]}{k}\ |\ I_i \gale{i} J \ \forall i \in [n]\right\}.\]
@@
 An algorithm for constructing the Le diagram associated to a Grassmann necklace was given by Agarwala and Fryer in \cite{reversingOh}.
-Since we will make use of this algorithm in Section~\ref{sec dim} below, we summarise the process here.
+Since we will make use of this algorithm in Section~\ref{sec dim} below, we summarize the process here.
 \begin{algorithm}\label{alg:GN to Le} \ \cite[Algorithm 2]{reversingOh}
@@
 \end{thm}
-In other words, the independent sets of $M(W)$ correspond to the sets of vertices in $W$ such that no subset supports fewer propagators than the vertices it contains.
-
-By studying $M(W)$ in terms of the behavior of the propagators in $W$, Agarwala and Amat show that $M(W)$ is in fact a positroid whenever $W$ is admissible \cite[Corollary 3.39]{wilsonloop}.
+In other words, the independent sets of $M(W)$ correspond to sets of vertices in $W$ in which no subset supports fewer propagators than the vertices it contains.
+
+By studying $M(W)$ in terms of the behavior of the propagators in $W$, Agarwala and Amat also showed that $M(W)$ is in fact a positroid whenever $W$ is admissible \cite[Corollary 3.39]{wilsonloop}.
+In theory, this allows us to leverage geometric and combinatorial results about $\Gr(k,n)$ to study Wilson loop diagrams.
+
+However, in order to identify the positroid associated to a given Wilson loop diagram $W$ we first have to construct $C(W)$, then make a list of all its non-zero $k\times k$ minors and extract the Le diagram or Grassmann necklace via the methods described in Section~\ref{sec:positroid background}.
+Alternatively, one could obtain the decorated permutation of the positroid from $C(W)$ as in \hlfix{[ref]}{Sian needs to go find this reference} and then convert it into a Grassmann necklace as described in \cite[Section 16]{Postnikov}.
+
+In \cite{casestudy}, Agarwala and Fryer apply this process in the smallest non-trivial case: admissible Wilson loop diagrams with two propagators on six vertices.
+Even in this simple case, we see that the mapping from admissible WLD to positroid cells is neither one-to-one nor onto, and the relationship between the original Wilson loop diagram and the resulting positroid is obscured to the point of invisibility.
+
+Our first goal is therefore to find a better method of obtaining the positroid associated to a given Wilson loop diagram; this is the focus of the next section.
 
@@
 Let $W = (\cP, [n])$ be a weakly admissible Wilson loop diagram, with $p \in \cP$ supported on edges $i$ and $j$.
-Write $(p, <_i)$ to be the same propagator with a direction induced by the linear ordering $<_i$.
-Then the set of propagators {\bf inside} $(p,<_i)$ is defined to be
-\[\cP_{in}(p,<_i) = \{ q \in \cP \ |\ (q,<_i) = (k,l) \text{ and }i \leq_i k <_i l \leq_i j \} \]
-and the set of propagators {\bf outside} $(p,<_i)$ is
-\[\cP_{out}(p,<_i) = \cP\setminus \cP_{in}(p,<_i).\]
+Write $(p, <_i)$ to represent the same propagator directed from $i$ to $j$.
+Then the sets of propagators {\bf inside} and {\bf outside} of $(p,<_i)$ are defined to be
+\begin{gather*}\cP_{in}(p,<_i) = \{ (k,l) \in \cP \ |\ i \leq_i k <_i l \leq_i j \}, \\
+\cP_{out}(p,<_i) = \cP\setminus \cP_{in}(p,<_i),
+\end{gather*}
+respectively.
 \end{dfn}

### 2019-04-30 GWLDCII.tex
minor progress on paper 2

@@
 
+We summarize here only the subset of positroid theory that we require in this paper; the interested reader is referred to \cite{Postnikov} for more details.
+
 Let $\binom{[n]}{k}$ denote the set of all $k$-subsets of $[n]$.
@@
 
-We summarize here only the subset of positroid theory that we require in this paper; the interested reader is referred to \cite{Postnikov} for more details.
 Postnikov shows in \cite{Postnikov} that the positroids of $\Gr(k,n)$ are indexed by many different collections of objects, each with their own advantages and disadvantages.
@@
 In \cite{casestudy}, Agarwala and Fryer apply this process in the smallest non-trivial case: admissible Wilson loop diagrams with two propagators on six vertices.
-Even in this simple case, we see that the mapping from admissible WLD to positroid cells is neither one-to-one nor onto, and the relationship between the original Wilson loop diagram and the resulting positroid is obscured to the point of invisibility.
+Even in this simple case, we see that the mapping from admissible WLD to positroid cells is neither one-to-one nor onto, and the process described above makes it almost impossible to track the relationship between the original Wilson loop diagram and the resulting positroid.
 
@@
 
-Given a propagator $p = (i, j)$ oriented $(p, <_i)$,  we can construct two obvious subdiagrams of $W$ by removing all of the propagators on one side of $p$ and leaving the vertices intact, i.e.
+%Given a propagator $p = (i, j)$ oriented $(p, <_i)$,  we can construct two obvious subdiagrams of $W$ by just removing all of the propagators on one side of $p$ and leaving the vertices intact, i.e.
 the subdiagrams
-\[  (\cP_{in}\cup\{p\}, [n])  \quad \textrm{and} \quad  (\cP_{out}\cup \{p\}, [n]).\]
-
-%where the set of non-supportive vertices of  $W|_{\cP_{in} \cup p}$ is $V_{out}$ and  the set of non-supportive vertices of  $W|_{\cP_{out} \cup p}$ is $V_{in}$.
-That is, these restrictions contain the propagators on the inside and outside of $(p, <_i)$ respectively, as well as $p$ itself.
-%\footnote{If we denote $V \subset [n]$ and $Q = \Prop(V^c)$, then we can write \bas M(W|_{Q^c}) = M(W)/F(Q) \oplus M_{\emptyset, n-|i-j+1|} \eas where  $M_{\emptyset, k}$ is the matroid of rank $0$ on a set of $k$.
-That is $M_{\emptyset, n-|i-j+1|} =M((\emptyset, n-|i-j+1|))$.
-}
-
-%We say that $p$ \textit{bounds the regions} $[i,j+1]$ and $[j,i+1]$ which we call outside and inside respectively.
-The ordering of the start and end points allow us to identify one or the other region unambiguously.
-
-%With these observations in mind we can return to the proof.
+%\[  (\cP_{in}(p,<_i), [n])  \quad \textrm{and} \quad  (]cP_{out}(p,<_i), [n]).\]
 
@@
 \end{itemize}
-We can then choose the orientation of $q_r$ so that the previous $p_i$ and $q_i$ are all on the outside of $q_r$, and 
-By the finiteness of $W$ this must eventually terminate in one of the desired configurations. %a configuration of the form \eqref{eq:2 prop config}.
+We can then choose the orientation of $q_r$ so that the previous $p_i$ and $q_i$ are all on the outside of $q_r$, and restrict our attention to the subdiagram $(\cP_{in}(q_r),[n])$.
+By the finiteness of $W$ this must eventually terminate in one of the desired configurations.
+%a configuration of the form \eqref{eq:2 prop config}.
 
@@
 so suppose otherwise.
-By assumption: $p_1$ is not in configuration \ref{item pair of 2s}, there are no propagators of length $3$, and every vertex supports at least one propagator.
-Therefore there must exist a propagator $q_1$ of length $\geq 4$ with one end on edge $j_1$ or on edge $j_1-1$ or on edge $j_1-2$.
-Orient $q_1 = (i_1, k_1)$ such that  $p_1 \in \cP_{out}(q_1)$, (that is $(q_1, <_{i_1})$).
-
-%This bounds a region $[i_1,k_1] = V_{out}(q_1) \cup V(q_1)$ on the outside of $(q_1, <_{i_1})$ (where $k_1 \in \{j_1-1, j_1, j_1+1\}$) which does not contain $p_1$.
+
+From our existing assumptions, we know the following facts: $p_1$ is not in configuration \ref{item pair of 2s}, there are no propagators of length $3$, and every vertex supports at least one propagator.
+Therefore there must be a propagator of length $\geq 4$ with one end on edge $j_1$ or on edge $j_1-1$ or on edge $j_1-2$.
+Let $q_1 = (i_1, k_1)$ be this propagator, oriented such that $p_1 \in \cP_{out}(q_1,<_{i_1})$.
+This completes the base case.
 
@@
 
-Call let $W_r := W|_{\cP_{in} \cup q_r}$.
-By the original hypotheses on $W$ every vertex in $v \in V_{in}(q_r)$ (which is a non-empty interval since $\ell(q_r) \geq 4$) must have support at least one propagator ($|\Prop(v)| \geq 1$), while the same is true for $V(q_r)$ because these vertices support $q_r$.
-By construction, the remaining vertices of $W|_{\cP_{in} \cup {q_r}}$, i.e.
-$V_{out}(q_r)$, are non-supporting.
-
-By Remark~\ref{rem:props of length 2 and 3}, $W_r$ admits at least one propagator of length 2.
-$W_r$ has no propagators of length $3$ since $W$ has none.
-Let $p_{r+1}$ be a propagator of length 2 in $W_r$; if it forms part of configuration \ref{item big and 2} or \ref{item pair of 2s}
+Let $W_r := (\cP_{in}(q_r),[n])$ be the subdiagram of $W$ consisting only of those propagators inside $q_r$ (including $q_r$ itself); in particular $W_r$ contains none of the previous $p_i$ or $q_i$.
+By the original hypotheses on $W$, every vertex in $[i_r,k_{r+1}]$ (which is a non-empty interval since $\ell(q_r) \geq 4$) must support at least one propagator.
+Therefore $W_r$ admits at least one propagator of length 2 (by Remark~\ref{rem:props of length 2 and 3}) and no propagators of length $3$ (by our assumption on $W$).
+
+Let $p_{r+1} = (j_{r+1}, j_{r+1}+2)$ be a propagator of length 2 in $W_r$; if it forms part of configuration \ref{item big and 2} or \ref{item pair of 2s}
 %the configuration \eqref{eq:2 prop config}
@@
 
-Note we may replace $q_r$ by any other propagator, $q'_{r}$ of length $\geq 4$ in $W_r$ such that $p_{r+1}$ and $q_r$ are on opposite sides; such a new $q'_{r}$ still satisfies all the hypotheses, and so, without loss of generality we may assume that $q_r$ has minimal length among propagators of length $\geq 4$ which have $p_{r+1}$ on their inside.
-
-Write $p_{r+1} = (j_{r+1}, j_{r+1}+2)$.
+Note that we could replace $q_r$ by another propagator $q'_{r}$ of length $\geq 4$ in $W_r$, as long as $p_{r+1}$ and $q_r$ are on opposite sides of $q_r'$, and such a new $q'_{r}$ would still satisfy all of the induction hypotheses.
+Therefore without loss of generality we may assume that $q_r$ has minimal length among propagators of length $\geq 4$ in $W_r$ which have $p_{r+1}$ on their inside.
+
 There are two cases to consider.
-The first case is that $i_r \leq j_{r+1} \leq i_r+2$ and $k_r-2 \leq j_{r+1}+2 \leq k_{r}$ (so $p_{r+1}$ has one end before $i_{r} + 3$ and the
-other after $k_{r} - 2$).
+
+The first case is that $i_r \leq j_{r+1} \leq i_r+2$ and $k_r-2 \leq j_{r+1}+2 \leq k_{r}$ (so $p_{r+1}$ has one end before $i_{r} + 3$ and the other after $k_{r} - 2$, i.e.
+both ends of $p_{r+1}$ are close to the ends of $q_r$).
 Then since $p_{r+1}$ has length 2, it must be that $(i_r+3)+1 \geq k_r-2$ and so $q_r$ has length $\leq 6$.
-By the minimality assumption on $q_r$ no propagator in $W_r$ has $q_r$ on one side and $p_{r+1}$ on the other side.
-Therefore, any propagator in $W_r$ other than $p_{r+1}$ itself must be of the form $(i,j)$ with $i_r\leq i, j\leq i_r+2$ or $k_r-2 \leq i,j\leq k_r$.
-That is, this propagator must be of length 2, and so we have configuration \ref{item pair of 2s} which we have already assumed does not occur.
-Consequently, $\cP_{in}(q_r)$ contains only $p_{r+1}$ and so we have congifuratin  \ref{item big and 2} from the lemma statement which again we have assumed does not occur.
+By the minimality assumption on $q_r$, no propagator in $W_r$ has $q_r$ on one side and $p_{r+1}$ on the other side.
+Therefore, any propagator in $W_r$ other than $q_r$ and $p_{r+1}$ must be of the form $(i,j)$ with $i_r\leq i < j\leq i_r+2$ or $k_r-2 \leq i < j\leq k_r$.
+Both of these require that $(i,j)$ has length 2, and so we have configuration \ref{item pair of 2s} which we have already assumed does not occur.
+Consequently, $W_r$ contains only the two propagators $q_r$ and $p_{r+1}$, yielding configuration \ref{item big and 2} from the lemma statement and again contradicting our assumption.
 Therefore this first case cannot occur.
 
-The second case is that one of the following three things happen (we continue to write $p_{r+1} = (j_{r+1}, j_{r+1}+2)$) 
+The second case is that (at least) one of the following four things happen:
 \begin{itemize}
-\item $i_r+3 \leq j_{r+1}\leq k_r-3$ or $i_r+3 \leq j_{r+1}+2\leq k_r-3$,
+\item $i_r+3 \leq j_{r+1}\leq k_r-3$, or
+\item $i_r+3 \leq j_{r+1}+2\leq k_r-3$, or
 \item $i_r = j_{r+1}$, or 
@@
 \end{itemize}
-(Phrased more causually, this is that $p_{r+1}$ has either at least one end on an edge bounded by the vertices in the interval $[i_r+3, k_r-2]$ or both ends lie in $[i_r, i_r+3]$ or both ends lie in $[k_r-2, k_r+1]$.)
-These situations all behave similarly.
-By symmetry it suffices to only consider the second situation and the second possiblity of the first situation.
-Note that since $j_{r+1}+4 \leq k_r-1$ in both situations, and $j_{r+1}+4 \in V_{in}(q_r)$, thus $j_{r+1}+4$ is supported by a propagator in $W_r$ other than $q_r$.
-Let $t$ be this propagator.
-Since $p_{r+1}$ is not part of configuration \ref{item pair of 2s} and $W_r$ has no propagators of length 3, we must have that the length of $t$ is $\geq 4$.
+In other words, at least one end of $p_{r+1}$ is supported entirely by vertices in the interval $[i_r+3,k_r+2]$ (the first two bullet points) or both ends lie in $[i_r, i_r+3]$ (third point) or both ends lie in $[k_r-2, k_r+1]$ (fourth point).
+These situations all behave similarly, and by symmetry it suffices to only consider the second and third possibilities.
+
+Note that since $j_{r+1}+4 \leq k_r-1$ in both of these situations, the vertex $j_{r+1}+4$ is inside $q_r$ but does not support either $p_r$ or $q_{r+1}$, and must therefore support some other propagator $t$.
+Since $p_{r+1}$ is not part of configuration \ref{item pair of 2s} and $W_r$ has no propagators of length 3, it follows that $\ell(t) \geq 4$.
 If $q_r$ and $p_{r+1}$ were on different sides of $t$ then this would contradict the minimal length hypothesis on $q_r$.
-Therefore $t$ has all the previous $q_i$ and $p_i$ on the same side and length $\geq 4$ and so we may set $q_{r+1} = t$ to continue the induction.
+Therefore we can orient $t$ so that all previous $q_i$ and $p_i$ belong to $\cP_{out}(t)$, and set $q_{r+1} = t$ to continue the induction.
 
@@
 The fact that Algorithm~\ref{alg:put GN on WLD} does construct the required Grassmann necklace is proved in Theorem~\ref{res:alg gives GN}.
-An worked example of Algorithm~\ref{alg:put GN on WLD} is given after Definition~\ref{def I_i as a function}.
+An worked example of Algorithm~\ref{alg:put GN on WLD} is given in Example~\ref{eg:apply GN alg}.
 
 \begin{algorithm}\label{alg:put GN on WLD}
-Let $W = (\cP, [n])$ be an admissible Wilson loop diagram. This gives an algorithm for calculating the set $I_i$, for $i \in [n]$.
+Let $W = (\cP, [n])$ be an admissible Wilson loop diagram. This gives an algorithm for constructing the set $I_j$, for $j \in [n]$.
 
 \begin{enumerate}
-\item Fix a vertex $i \in [n]$. Set $a:=i$ and $I_i = \emptyset$.
-\item While $\cP \neq \emptyset$, perform the following steps.
+\item Fix a vertex $j \in [n]$. Set $j:=i$ and $I_i = \emptyset$.
+\item While $\cP \neq \emptyset$, perform the following steps:
 \begin{enumerate}
-\item \textbf{Step $a$ for vertex $i$}: If $\Prop(a) \neq \emptyset$ in $W$, write $I_i = I_i \cup \{a\}$.
-Let $p \in \Prop(a)$ be the clockwise most propagator supported on $a$.
-Write $W = (\cP \setminus \{p\}, [n])$.
-\item If $Prop(i) = \emptyset$ do nothing.
-\item Increment $a$ by 1 and repeat from (a).
+\item \textbf{Step $j$ for vertex $i$}: If $\Prop(j) = \emptyset$, do nothing.
+Else, let $p \in \Prop(j)$ be the clockwise most propagator supported on $j$.
+Write $I_i = I_i\cup \{j\}$, and delete propagator $p$ from the diagram.
+\item Increment $j$ by 1 and repeat from (a).
 \end{enumerate}
@@
 
+Informally: one starts at $i$ and moves counterclockwise around the vertices of $W$, at each step removing the clockwise-most propagator supported on that vertex (if it exists).
+The set $I_i$ lists the vertices at which a propagator was deleted.
+
 If the algorithm assigns vertex $j$ to propagator $p$ from starting vertex $i$, we say that $p$ \emph{contributes} $j$ to $I_i$.
@@
 \begin{dfn}\label{def I_i as a function}
-Let $W = (\cP, [n])$ be an admissible Wilson loop diagram. For each $i \in [n]$, define a function $I_i : \cP \longrightarrow [n]$ by
-\[I_i(p) := \text{the vertex label that $p$ contributes to $I_i$ in Algorithm~\ref{alg:put GN on WLD},}\]
-for each $p \in \cP$.
+Let $W = (\cP, [n])$ be an admissible Wilson loop diagram. For each $i \in [n]$, define a function $I_i^W : \cP \longrightarrow [n]$ by
+\[I_i^W(p) := \text{the vertex label that $p$ contributes to $I_i$ in Algorithm~\ref{alg:put GN on WLD},}\]
+for each $p \in \cP$. When the diagram $W$ is clear from context, we drop the superscript and simply write $I_i$.
 \end{dfn}
 
-\begin{eg}Consider the admissible Wilson loop diagram
+\begin{eg}\label{eg:apply GN alg}Consider the admissible Wilson loop diagram
 \[W\ =\ \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
@@
 
-To construct $I_1$ we start at vertex 1, so we begin with $i=1$, $a = 1$, and $I_1 = \emptyset$. 
+To construct $I_1$ we start at vertex 1, so we begin with $i=1$, $m = 1$, and $I_1 = \emptyset$. 
 \begin{itemize}
-\item $a = 1$: Since $\Prop(1) = \{q,r\}$ and $r$ is the clockwise-most of these propagators, we let $I_1 = \{1\}$ and remove propagator $r$ from the diagram. 
-\item $a = 2$: $\Prop(2) = \{p,q\}$, with $q$ being the clockwise-most of these propagators. So $I_1 = \{1,2\}$ and propagator $q$ is removed.
-\item $a = 3$: $\Prop(3) = \{p\}$, so now $I_1 = \{1,2,3\}$ and propagator $p$ is removed. The only remaining propagator in the diagram is $s$.
-\item $a = 4$: Since $p$ and $q$ were removed in earlier steps, we now have $\Prop(4) = \emptyset$.
-\item $a = 5$: $\Prop(5) = \{s\}$, and we have $I_1 = \{1,2,3,5\}$.
+\item $j = 1$: Since $\Prop(1) = \{q,r\}$ and $r$ is the clockwise-most of these propagators, we let $I_1 = \{1\}$ and remove propagator $r$ from the diagram. 
+\item $j = 2$: $\Prop(2) = \{p,q\}$, with $q$ being the clockwise-most of these propagators. So $I_1 = \{1,2\}$ and propagator $q$ is removed.
+\item $j = 3$: $\Prop(3) = \{p\}$, so now $I_1 = \{1,2,3\}$ and propagator $p$ is removed. The only remaining propagator in the diagram is $s$.
+\item $j = 4$: Since $p$ and $q$ were removed in earlier steps, we now have $\Prop(4) = \emptyset$.
+\item $j = 5$: $\Prop(5) = \{s\}$, and we have $I_1 = \{1,2,3,5\}$.
 \end{itemize}
@@
 \[1235, 2356, 3456, 4567, 5671, 6712, 7812, 8123.\]
-The reader can easily verify that this sequence of $k$-sets satisfies the definition of a Grassmann necklace, and can (with significantly more work) also verify that this Grassmann necklace defines the positroid associated to the Wilson loop diagram $W$ given above.
+The reader can easily verify that this sequence of $k$-sets satisfies the definition of a Grassmann necklace, and can (with significantly more work) also verify that this Grassmann necklace defines the positroid $M(W)$ associated to the Wilson loop diagram $W$ above.
 \end{eg}
 
-Given a propagator $p$ and a vertex $i$ in its support, it will be very useful in the following to understand on what set of vertices the Grassmann necklace algorithm assigns $i$ to $p$.
-The answer is that the set is a non-empty cyclic interval.
-Lemma~\ref{vertex cyclic int lem} establishes this, but first we need a preliminary lemma which is also useful in its own right.
+We first verify that this algorithm always terminates in fewer than $n$ steps.
 
@@
 
-Since $I_i(p) \neq b$, there must exist a propagator $q$ inside of $p$ with $I_i(q) = b$.
-The propagator $q$ cannot end on the edge $(b-1,b)$, as this would contradict the minimality of $p$, so $q = (c,c+1,b,b+1)$ with $a <_i c <_i b$, and $I_i(q) = b$.
+Since $I_i(p) \neq b$, there must exist a propagator $q$ inside of $(p,<_i)$ with $I_i(q) = b$.
+The propagator $q$ cannot end on the edge $(b-1,b)$, as this would contradict the minimality of $p$, so we have $q = (c,c+1,b,b+1)$ with $a <_i c <_i b$, and $I_i(q) = b$.
 
@@
 
-Given a propagator $p$ of an admissible WLD $W$ and a vertex $i$ in the support of $p$, define
+We now reverse our perspective and ask: given a propagator $p$ and a vertex $i$ in the support of $p$, for which set of starting vertices does the algorithm assign $p$ to $i$?
+
+Specifically, for each $i$ in the support of $p$, define the set
 \[J_p^{(W)}(i) = \{m \in [n] \ | \ I^{(W)}_m(p) = i \},\]
-i.e.
-the set of indices $m$ for which Algorithm~\ref{alg:put GN on WLD} assigns the value $i$ to the propagator $p$ in $W$.
+the set of starting vertices $m$ such that $I_m^{(W)}$ assigns $p$ to $i$.
+
 The following lemma establishes that these sets behave in a simple and predictable manner, a fact which we will repeatedly use in subsequent proofs.
@@
 
-Let $p=(i,j)$ be a propagator of an admissible WLD $W$ on $n$ vertices.
+Let $p=(i,j)$ be a propagator in an admissible WLD $W$ on $n$ vertices.
 Then $J_p^{(W)}(i)$, $J_p^{(W)}(i+1)$, $J_p^{(W)}(j)$, and $J_p^{(W)}(j+1)$ are each non-empty cyclic intervals which partition $[n]$ and occur in the given cyclic order.
@@
 Now suppose $W$ has more than one propagator.
-Since non-supporting vertices have no effect on the Grassmann necklace algorithm, it suffices to prove the result for $W$ with $F(\emptyset) = \emptyset$.
+Since non-supporting vertices have no effect on Algorithm~\ref{alg:put GN on WLD}, it suffices to prove the result for $W$ with $F(\emptyset) = \emptyset$.
 Then by Lemma~\ref{lem sian}, $W$ has at least one of the four situations illustrated in Figure~\ref{fig 3 cases}.
@@
 
-In each of the four cases, when we remove the propagator labelled $p$ we obtain a diagram which satisfies the statement of the theorem by the induction hypothesis, and contains a propagator ${q = (i,j)}$ with no other propagators inside it (although this region may or may not contain non-supporting vertices, which we will call $l, l+1, \ldots$ as necessary).
+In each of the four cases, when we remove the propagator labelled $p$ we obtain a diagram which satisfies the statement of the theorem by the induction hypothesis, and contains a propagator ${q = (i,j)}$ with no other propagators inside it (with respect to the $<_i$ orientation), although this region may or may not contain non-supporting vertices which we will call $l, l+1, \ldots$ as necessary.
 Let $V$ be the diagram obtained by removing the propagator $p$ from $W$ (Figure \ref{fig V diagram}).
@@
 \end{thm}
-
+\note{Sian replaced all occurences of $k$ as an index with other letters: someone please proofread this specifically to check that none were missed! (then remove this note)}
 \begin{proof}
@@
 By Lemma~\ref{GN alg well defined}, we know that $|I_i| = k$ for each $i \in [n]$.
-It is easy to verify that the sequence $(I_1, \dots, I_n)$ is a Grassmann necklace if and only if $I_{i+1} \supseteq I_i \backslash \{i\}$ for all $i \in [n]$; this is the characterization we will use in this proof.
-
-Suppose for a contradition that there exists an admissible diagram for which there exists an $i$ with $k\in I_i\setminus \{i\}$ and $k \not\in I_{i+1}$.
+We first prove that $I_{i+1} \supseteq I_i \backslash \{i\}$ for all $i \in [n]$; this is equivalent to the definition of Grassmann necklace given in Definition~\ref{def:grassmann necklace}.
+
+Suppose for a contradition that there exists an admissible diagram for which there exists an $i$ with $m\in I_i\setminus \{i\}$ and $m \not\in I_{i+1}$.
 Fix $n$.
-Let the triple $(W, i, k)$ be such a counterexample on $n$ vertices which is minimal with respect to the number of propagators.
+Let the triple $(W, i, m)$ be such a counterexample on $n$ vertices which is minimal with respect to the number of propagators.
 %, and among all those counterexamples on $n$ vertices with the same number of propagators, let $(W,i,k)$ be minimal with respect to the distance from $i$ to $k$ in the $\leq _i$ order.
@@
 In this case it is clear that applying Algorithm~\ref{alg:put GN on WLD} at vertex $i$ and vertex $i+1$ produces exactly the same result, i.e.
-$I_{i+1} = I_i$, and so $(W, i, k)$ is not a counterexample at all.
+$I_{i+1} = I_i$, and so $(W, i, m)$ is not a counterexample at all.
 
@@
 This is also true in when the algorithm constructing $I_i$ reaches $b$, since the same propagators have been assigned beforehand.
-Finally, we also note that $k\geq_i b+1$.
-
-Let $W'$ be the diagram obtained from $W$ by removing both $p$ and all propagators inside of $p$ (recall Definition~\ref{props inside p}).
+Finally, we also note that $m\geq_i b+1$.
+
+Let $W' = (\cP_{out}(p,<_i), [n])$, i.e. the diagram obtained from $W$ by removing both $p$ and all propagators inside of $p$.
 
@@
 where the diagram is indicated in the superscript.
-Thus we have $k\in I_b^{(W')}\setminus\{b\}$ and $k\not\in I_{b+1}^{(W')}$, contradicting the minimality of $(W, i, k)$.
+Thus we have $m\in I_b^{(W')}\setminus\{b\}$ and $m\not\in I_{b+1}^{(W')}$, contradicting the minimality of $(W, i, m)$.
 
@@
 Note that by assumption we have $I_i(p) = i$; this means that $p$ must be the first propagator lying on edge $i$, and hence we must have $I_{i+1}(p) = i+1$ as well.
-Observe also that $k\geq_i i+2$ since $i+1\in I_{i+1}$.
+Observe also that $m\geq_i i+2$ since $i+1\in I_{i+1}$.
 
@@
 since in both cases the algorithm in $W'$ proceeds identically to that in $W$ after assigning $p$.
-Since $k \neq i+1$, we have $k\in I_{i+1}^{(W')}\setminus\{i+1\}$ but $k\not\in I_{i+2}^{(W')}$, contradicting the minimiality of $(W, i, k)$.
+Since $m \neq i+1$, we have $m\in I_{i+1}^{(W')}\setminus\{i+1\}$ but $m\not\in I_{i+2}^{(W')}$, contradicting the minimiality of $(W, i, m)$.
 
@@
 \end{itemize}
-The algorithm is pairing each $j \in I_i$ with a unique propagator supported on that vertex so by Lemma~\ref{lem basis as perm} it immediately follows that $I_i$ is a basis for $M(W)$.
-
-Suppose we have a $k$-set $J$ such that $J$ is a basis for $M(W)$ and yet is lexicographically less than $I_i$ with respect to $<_i$.
+The first point follows immediately: since the algorithm is pairing each $j \in I_i$ with a unique propagator supported on that vertex, $I_i$ is a basis for $M(W)$ by Lemma~\ref{lem basis as perm}.
+
+Now suppose we have a $k$-set $J$ such that $J$ is a basis for $M(W)$ and yet is lexicographically less than $I_i$ with respect to $<_i$.
 By Lemma~\ref{lem basis as perm} there is a set bijection between $J$ and the propagators of $W$ such that for each $j \in J$, the propagator associated to $j$ is supported on vertex $j$.
 Choose one such bijection.
-For a propagator $p$ of $W$ write $J(p)$ for the associated $j$ according to this bijection.
+For each propagator $p$ of $W$, write $J(p)$ for the vertex $j$ associated to $p$ according to this bijection.
 
@@
 Continue this process for as many steps as possible (i.e.
-for as long as $I_i(p_*) \in J$); this produces a list of vertices $j_k$ and propagators $p_k$ such that
-\[J(p_k) = I_i(p_{k-1}) = j_{k-1}.\]
-
-We claim that the propagators and vertices in this list are distinct; this will show that the process must eventually terminate.
+for as long as $I_i(p_*) \in J$); this produces a list of vertices $j_r$ and propagators $p_r$ such that
+\[J(p_r) = I_i(p_{r-1}) = j_{r-1}.\]
+
+We claim that there is no repetition of propagators or vertices in this list; this will show that the process must eventually terminate.
 The claim is proved by induction.
 The definition of $j_0$ gives that $j_0$ and $j_1$ are distinct and that $p_1$ and $p_2$ are distinct.
-Now, suppose we have $p_k$ and $j_k$ with $I_i(p_k)=j_k$ and with $j_k\in J$.
-Then there must exist a propagator $p_{k+1}$ with $J(p_{k+1}) = j_k$.
-Since $J: \cP \longrightarrow [n]$ is injective and $j_k$ is not equal to any of the previous vertices $j_0, \dots, j_{k-1}$ by assumption, $p_{k+1}$ must be distinct from the previous $p_j$.
-Define $j_{k+1} = I_i(p_{k+1})$, but since $I_i$ is also a bijection and $p_{k+1}$ is distinct from the earlier $p_j$, it follows that $j_{k+1}$ is distinct from the other $j_j$ for $1\leq j\leq k$.
-Additionally $j_{k+1}\neq j_0$ since $j_0\not\in I_i$ but $j_{k+1}\in I_i$.
+Now, suppose we have $p_r$ and $j_r$ with $I_i(p_r)=j_r$ and with $j_r\in J$.
+Then there must exist a propagator $p_{r+1}$ with $J(p_{r+1}) = j_r$.
+Since $J: \cP \longrightarrow [n]$ is injective and $j_r$ is not equal to any of the previous vertices $j_0, \dots, j_{r-1}$ by assumption, $p_{r+1}$ must be distinct from the previous propagators $p_1,\dots,p_r$.
+Following the pattern, define $j_{r+1} = I_i(p_{r+1})$.
+Since $I_i: \cP \longrightarrow [n]$ is also injective and $p_{r+1}$ is distinct from the earlier $p_*$, it follows that $j_{r+1}$ is distinct from the other $j_s$ for $1\leq s\leq r$.
+Finally, we have $j_{r+1}\neq j_0$ since $j_0\not\in I_i$ but $j_{r+1}\in I_i$.
 This proves the claim.
 
-By finiteness the list must end, and the only way it can end is with some $p_k$ such that $j_k = I_i(p_k)\not\in J$. In particular, this implies that $j_k >_i j_0$.
-
-Next we will prove that $j_k <_i j_0$ for all $k > 0$; this gives a contradiction to the existence of $J$ and completes the proof of the theorem.
+Therefore the list must end, and the only way it can end is with some $p_r$ such that $j_r = I_i(p_r)\not\in J$. In particular, this implies that $j_r >_i j_0$.
+
+Next we will prove that $j_r <_i j_0$ for all $r > 0$; this gives a contradiction to the existence of $J$ and completes the proof of the theorem.
 This proof will also be by induction; however, for the induction to go through nicely we will need to prove the following slightly stronger statement:
-for all $k>0$ in the list
+for all $r>0$ in the list
 \begin{itemize}
-\item $j_k <_i j_0$ and
+\item $j_r <_i j_0$ and
 \item either
   \begin{itemize}
-  \item $I_i(p_k) <_i J(p_k)$, or
-  \item there exists an $\ell<k$ such that $I_i(p_\ell) <_i J(p_\ell)$, those two vertices support distinct ends of $p_\ell$, and $p_k$ is inside $p_l$ when $p_l$ is directed from $I_i(p_\ell)$ to $J(p_\ell)$.
+  \item $I_i(p_r) <_i J(p_r)$, or
+  \item there exists an $\ell<r$ such that $I_i(p_\ell) <_i J(p_\ell)$, those two vertices support distinct ends of $p_\ell$, and $p_r$ is inside $p_l$ when $p_l$ is directed from $I_i(p_\ell)$ to $J(p_\ell)$.\note{Should I replace this with ``$p_r$ is inside $(p_l,<_i)$''?
+It matches previous notation but maybe is less clear?}
   \end{itemize}
@@
 We observed above that $j_1 <_i j_0$ and $I_i(p_1) <_i J(p_1)$ so we have the base case for the induction.
-Now fix $k > 1$ and suppose that the inductive hypothesis holds for all indices less than $k$ and that $p_k$ exists.
-
-By definition $J(p_k) = I_i(p_{k-1}) = j_{k-1}$, so $p_{k-1}$ and $p_{k}$ are both supported at vertex $j_{k-1}$.
-
-Since $I_i$ always chooses the earliest unassigned propagator supported at a vertex, it follows that either $p_{k-1}$ appears before $p_k$ in the neighbourhood of $j_{k-1}$, or that $p_k$ was assigned earlier than $p_{k-1}$ by the algorithm for $I_i$; note that the ordering $p_1,p_2,\dots,p_k$ need not match the order in which Algorithm~\ref{alg:put GN on WLD} assigns propagators to vertices.
-
-In the latter case we are done, since $p_k$ being assigned earlier than $p_{k-1}$ by $I_i$ means exactly that $I_i(p_k) <_i I_i(p_{k-1})$.
-Recalling that $I_i(p_{k-1}) = J(p_k) = j_{k-1}$, we obtain $I_i(p_k) <_i J(p_k)$ and $j_k = I_i(p_k) <_i j_{k-1} <_i j_0$, as required.
-
-Now assume that $p_{k-1}$ appears before $p_k$ in the neighbourhood of $j_{k-1}$.
-
-\hlfix{[picture]}{picture}
-
-If $I_i(p_{k-1}) <_i J(p_{k-1})$ and these are vertices supported by distinct ends of $p_{k-1}$ then $p_{k}$ coming after $p_{k-1}$ around $j_{k-1}$ implies that $p_k$ is on the $I_i(p_{k-1})$ to $J(p_{k-1})$ side of $p_{k-1}$.
-Therefore $j_k = I_i(p_k) \leq_i J(P_{k-1}) + 1$.
-If $k-1 \neq 1$ then this gives $j_k \leq_i I_i(p_{k-2}) + 1 <_i j_0$ so $j_k \leq_i j_0$, but $j_0\not\in I_i$ so $j_k<_i j_0$.
-If $k-1= 1$ then either $j_k <_i j_0$ or we have the configuration
+Now fix $r > 1$ and suppose that the inductive hypothesis holds for all indices less than $r$ and that $p_r$ exists.
+
+By definition $J(p_r) = I_i(p_{r-1}) = j_{r-1}$, so $p_{r-1}$ and $p_{r}$ are both supported at vertex $j_{r-1}$.
+
+Since $I_i$ always chooses the earliest unassigned propagator supported at a vertex, we have two possibilities (which are not mutually exclusive): either $p_{r-1}$ appears before $p_r$ in the neighbourhood of $j_{r-1}$, or $p_r$ was assigned earlier than $p_{r-1}$ by the algorithm for $I_i$.
+(Note that the ordering $p_1,p_2,\dots,p_r$ need not match the order in which Algorithm~\ref{alg:put GN on WLD} assigns propagators to vertices.)
+
+In the latter case we are done, since $p_r$ being assigned earlier than $p_{r-1}$ by $I_i$ means exactly that $I_i(p_r) <_i I_i(p_{r-1})$.
+Recalling that $I_i(p_{r-1}) = J(p_r) = j_{r-1}$, this implies that $I_i(p_r) <_i J(p_r)$ and $j_r = I_i(p_r) <_i j_{r-1} <_i j_0$, as required.
+
+Now assume that $p_{r-1}$ appears before $p_r$ in the neighbourhood of $j_{r-1}$, and that $I_i$ assigns $p_{r-1}$ before $p_r$.
+
+\hlfix{If $I_i(p_{r-1}) <_i J(p_{r-1})$ and these are vertices supported by distinct ends of $p_{r-1}$}{Sian is confused by this sentence}, then by our assumption above $p_r$ must lie inside $p_{r-1}$ when directed from $I_i(p_{r-1})$ to $J(p_{r-1})$.
+Therefore $j_r = I_i(p_r) \leq_i J(p_{r-1}) + 1$.
+If $r > 2$ then this gives $j_r \leq_i I_i(p_{r-2}) + 1 \leq_i j_0$, but we know that $j_0\not\in I_i$ so in fact we have a strict inequality $j_r<_i j_0$.
+If $r=2$ then either $j_r <_i j_0$ or we have the configuration
 \[
@@
 \]
-which is impossible as $p_2$ is supported at $j_0$ but not taken in $I_i$ until after $j_0$ even though $j_0\not\in I_i$.
-Taking all of this paragraph together we are done unless $I_i(p_{k-1})\not<_i J(p_{k-1})$ so now assume this.
-
-By the induction hypothesis,  $I_i(p_{k-1})\not<_i J(p_{k-1})$ implies that there exists and $\ell < k-1$ such that $p_{k-1}$ is on the side of $p_{\ell}$ that goes from $I_i(p_\ell)$ to $J(p_\ell)$.
-If $j_{k-1}$ is not in the support of the $J(p_\ell)$ end of $p_\ell$ then $p_{k-1}$ before $p_{k}$ around $j_{k-1}$ implies that $p_k$ is on the same side of $p_\ell$ as $p_{k-1}$ is.
-Then the same arguments as above with $\ell$ in place of $k-1$ give $j_k \leq_i J(P_\ell)+1$ implying $j_k <_i j_0$ which is everything we need.
-
-It remains to consider when $j_{k-1}$ is in the support of the $J(p_\ell)$ end of $p_\ell$, call this case $(*)$.
-Since $J(p_\ell) = j_{\ell-1}$ and the $j_i$ are distinct this means that we have one of the following two configurations
+which is impossible as $p_2$ is supported at $j_0$ but not assigned by $I_i$ until after $j_0$ even though $j_0\not\in I_i$.
+Taking all of this paragraph together we are done unless $I_i(p_{r-1})\not<_i J(p_{r-1})$ so now assume this.
+
+By the induction hypothesis,  $I_i(p_{r-1})\not<_i J(p_{r-1})$ implies that there exists and $\ell < r-1$ such that $p_{r-1}$ is on the side of $p_{\ell}$ that goes from $I_i(p_\ell)$ to $J(p_\ell)$.
+If $j_{r-1}$ is not in the support of the $J(p_\ell)$ end of $p_\ell$ then $p_{r-1}$ before $p_{r}$ around $j_{r-1}$ implies that $p_r$ is on the same side of $p_\ell$ as $p_{r-1}$ is.
+Then the same arguments as above with $\ell$ in place of $r-1$ give $j_r \leq_i J(p_\ell)+1$ implying $j_r <_i j_0$ which is everything we need.
+
+It remains to consider when $j_{r-1}$ is in the support of the $J(p_\ell)$ end of $p_\ell$, call this case $(*)$.
+Since $J(p_\ell) = j_{\ell-1}$ and the vertices $j_1,\dots,j_r$ are distinct, this means that we have one of the following two configurations
 \[
@@
 \]
-If $p_\ell=p_1$ then $j_{\ell-1}=j_0$ and then as $j_0\not\in I_i$ but $p_k$ is supported at $j_0$ we get $I_i(p_k) <_i j_0$ and also $I_i(p_k) <_i j_{k-1} = J(p_k)$ as the only vertices not yet taken for $I_i(p_k)$ must be before both labelled vertices in the illustration.
-
-If $p_\ell \neq p_1$ then we argue as above with $\ell-1$ in place of $k-1$: in particular $J(p_\ell) = I_i(p_{\ell-1})$ but $p_k$ is supported at $p_{\ell-1}$, so either $I_i(p_k) <_i I_i(p_{\ell-1})$ in which case as before we get desired conclusion, or $p_k$ comes before $p_{\ell-1}$ at $j_{\ell-1}$.
-Then again argue as before getting a new $p_{\ell'}$ in place of $p_{\ell}$, except that then case $(*)$ must occur simultaneously for both $p_{\ell'}$ and $p_{\ell}$ with respect to $p_{k}$.
-This can only occur if $j_{\ell-1}, j_{k-1}, j_{\ell'-1}$ are consecutive.
-Iterating the argument one more time we finally cannot have case $(*)$ as then all neighbouring vertices of $j_{k-1}$ are used up.
+If $p_\ell=p_1$ then $j_{\ell-1}=j_0$ and then as $j_0\not\in I_i$ but $p_r$ is supported at $j_0$ we get $I_i(p_r) <_i j_0$ and also $I_i(p_r) <_i j_{r-1} = J(p_r)$ as the only vertices not yet taken for $I_i(p_r)$ must be before both labelled vertices in the illustration.
+
+If $p_\ell \neq p_1$ then we argue as above with $\ell-1$ in place of $r-1$: in particular $J(p_\ell) = I_i(p_{\ell-1})$ but $p_r$ is supported at $p_{\ell-1}$, so either $I_i(p_r) <_i I_i(p_{\ell-1})$ in which case as before we get desired conclusion, or $p_r$ comes before $p_{\ell-1}$ at $j_{\ell-1}$.
+Then again argue as before getting a new $p_{\ell'}$ in place of $p_{\ell}$, except that then case $(*)$ must occur simultaneously for both $p_{\ell'}$ and $p_{\ell}$ with respect to $p_{r}$.
+This can only occur if $j_{\ell-1}, j_{r-1}, j_{\ell'-1}$ are consecutive.
+Iterating the argument one more time we finally cannot have case $(*)$ as then all neighbouring vertices of $j_{r-1}$ are used up.
 
@@
 
+We can now unambiguously refer to Algorithm~\ref{alg:put GN on WLD} as the Grassmann necklace algorithm.
+We close this section with a simple observation about the Grassmann necklaces of positroids associated to Wilson loop diagrams.
+
 In an arbitrary Grassmann necklace, it is possible for an index $i$ to appear in no terms of the Grassmann necklace (a {\em loop}) or in all terms of the necklace (a {\em coloop}).
@@
 Our next goal is to show that the dimension of the positroid cell defined by a Wilson loop diagram $(\cP, [n])$ has dimension $3|\cP|$.
-Marcott in ***cite this*** has a different proof which is geometric and more elegant, but it is not easy to track the effect of a particular propagator.
+Marcott in \hlfix{***cite this***}{highlighted for anyone skimming through} has a different proof which is geometric and more elegant, but it is not easy to track the effect of a particular propagator.
 Our approach is much more explicit.

### 2019-05-03 GWLDCI.tex
some little typos and putting admissible in the statement and now I'm happy with 3.17

@@
 \item For $V \subseteq [n]$, write $\Prop(V) = \{ p \in \cP | V(p) \cap V \neq \emptyset \} $.
-\item For $P \subseteq \cP$, define $F(P) = V(P^c)^c$ to be\footnote{Here, as throughout, we are using the subscript $c$ for the set theoretic complement.} the set of vertices in $[n]$ that do not support any propagators outside the set $P$.
+\item For $P \subseteq \cP$, define $F(P) = V(P^c)^c$ to be\footnote{Here, as throughout, we are using the superscript $c$ for the set theoretic complement.} the set of vertices in $[n]$ that do not support any propagators outside the set $P$.
 \item The set of vertices that are not in the support of any propagotors is denoted  $F(\emptyset)$. Vertices in this set are called non-supporting.  
@@
 
-The previous definition makes sense, in fact, for any two polygon dissections of the same polygon, not just for those in the image of $\tau$..
+The previous definition makes sense, in fact, for any two polygon dissections of the same polygon, not just for those in the image of $\tau$.
 
@@
 \begin{proof}
-This follows from the definition of equivalent Wilson loop diagrams, Definition \ref{equivdfn}, the definition of retriangulations, Definition \ref{retriangulation}, and Lemma\ref{lem triang to exact}.
+This follows from the definition of equivalent Wilson loop diagrams, Definition \ref{equivdfn}, the definition of retriangulations, Definition \ref{retriangulation}, and Lemma \ref{lem triang to exact}.
 \end{proof}
@@
 \begin{cor} \label{classifyflats}
-  If $F$ is a flat of a Wilson loop diagram, it can be written as the disjoint union of a cyclic propagator flat and an independent set: \bas F =C \sqcup S \eas where $C$ the union of all circuits in S.
+  If $F$ is a flat of an admissible Wilson loop diagram, it can be written as the disjoint union of a cyclic propagator flat and an independent set: \bas F =C \sqcup S \eas where $C$ the union of all circuits in S.
 \end{cor}
@@
 \begin{lem} \label{maxexactcomplementrank}
-Let $W = (\cP, [n])$ be a Wilson loop diagram, and $P \subseteq \cP$. Then: \begin{enumerate}
+Let $W = (\cP, [n])$ be an admissible Wilson loop diagram, and $P \subseteq \cP$. Then: \begin{enumerate}
 \item If $(P,V(P))$ is an exact subdiagram in $W$, then $F(P^c)$ is not an independent flat.
@@
 Furthermore, $F(R^c) = F(P^c) \sqcup S$.
-We show that $S$ is an independent set in the subdiagram $(P, V(P))$, and thus in $W$.
-Independence in $(P, V(P))$ implies that for any maximal independent set $\mathfrak{B} \subset F(P^c)$, the set $\mathfrak{B} \sqcup S$ is independent in $F(R^c)$.
-Therefore, \bas \rk (F(R^c)) \geq \rk (F(P^c)) + |S| = |P^c| + |P\setminus R| = |R^c|  \;.\eas By Lemma \ref{lem facts about WLD matroids}, $\rk (F(R^c)) \leq |R^c|$.
+We will show that $S$ is an independent set in the subdiagram $(P, V(P))$, and thus in $W$.
+Supposing for the moment that $S$ is independent in $(P, V(P)$ this implies that for any maximal independent set $\mathfrak{B} \subset F(P^c)$, the set $\mathfrak{B} \sqcup S$ is independent in $F(R^c)$.
+Therefore, \bas \rk (F(R^c)) \geq |\mathcal{B}| + |S| = \rk (F(P^c)) + |S| = |P^c| + |P\setminus R| = |R^c|  \;.\eas By Lemma \ref{lem facts about WLD matroids}, $\rk (F(R^c)) \leq |R^c|$.
 Thus $\rk (F(R^c)) = |R^c|$ as desired.
@@
 Suppose not.
-Then, by Theorem \ref{thm WLD defines matroid} there is a subset $U \subset S$ such that $|\Prop(U)| < |U|$.
+Then, by Theorem \ref{thm WLD defines matroid} there is a subset $U \subseteq S$ such that $|\Prop(U)| < |U|$.
 Then the remaining propagators, $P \setminus \Prop(U)$ are supported entirely on $V(P) \setminus U$.

### 2019-05-03 GWLDCII.tex
fixed 3.4, addressed most of the notes in Susama's file

@@
 
-A Wilson loop diagram is depicted as a circle, with the vertices $V$ equally spaced along the edge of the circle and listed counterclockwise in their cyclic order.
+A Wilson loop diagram is depicted as a circle, with the vertices $V$ arranged along the edge of the circle and listed counterclockwise in their cyclic order.
 The arc between two consecutive vertices is referred to as an {\bf edge} of the diagram, and the $i$th edge of $W$ is the edge from vertex $i$ to its successor.
@@
 
+In particular, we will see in later sections that all four vertices in the support of a propagator are important in understanding the contribution of that propagator to the overall diagram.
+This motivates the following definition of a subdiagram, which can consist of any subset $Q$ of the propagators and any subset $U$ of the vertices of $W$ {\em as long as we retain all vertices in the support of $Q$}.
+
 \begin{dfn} \label{subdiagramdfn}
-Let $W = (\cP, V)$ be an admissible Wilson loop diagram. Then $W' = (Q,U)$ is a {\bf subdiagram} of $W$ if $Q \subseteq \cP$ and $V(Q) \subseteq U \subseteq V$.
+Let $W = (\cP, V)$ be a Wilson loop diagram. Then $W' = (Q,U)$ is a {\bf subdiagram} of $W$ if $Q \subseteq \cP$ and $V(Q) \subseteq U \subseteq V$.
 \end{dfn}
@@
 
-These conditions are imposed by the physical interpretation of Wilson loop diagrams (see for example \hlfix{[ref]}{probably for Susama: is there a sensible paper to cite here?}).
+These conditions are imposed by the physical interpretation of Wilson loop diagrams (see for example \cite{Adamo:2011pv,Adamo:2012xe,wilsonloop,LipsteinMason}).
 We therefore restrict our attention in this paper to admissible Wilson loop diagrams and their subdiagrams only.
@@
 Note that a subdiagram $(Q,U)$ of an admissible Wilson loop diagram need not be admissible itself: it inherits conditions 2 and 3 automatically, but we could have $|U| = |Q| + 3$.
-We call diagrams of this type {\bf weakly admissible}; in the context of this paper, they occur only when we take an admissible diagram and delete one or more non-supporting vertices.
+If a Wilson loop diagrams satisfies conditions 2 and 3 of Definition~\ref{admisdfn}, we call it {\bf weakly admissible}.
 
@@
 \[ \Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V_{p_r}} \textrm{d}c_{p_r}}{R(W)} \;. \]
-The interested reader is referred to \hlfix{[ref]}{any paper that talks about the volume form} for more information about the volume form.
+The interested reader is referred to \cite{Adamo:2012xe,HeslopStewart,LipsteinMason} for more information about the volume form.
 Of interest to us in this paper is the denominator $R(W)$, which we define next.
@@
 \end{dfn}
-Understanding the polynomial $R(W)$ (and hence the singularities of the volume form $\Omega(W)$) \hlfix{is important for the physics}{help?}.
-In Section~\ref{sec poles} we give a simple algorithm to read $R(W)$ directly from the Wilson loop diagram.
+We expect the volume form associated to the tree amplitudes to be finite \cite{Adamo:2011pv,Adamo:2012xe,Arkani-Hamed:2013jha}.
+Therefore, we expect that the singularities of $\Omega(W)$ will cancel on the boundaries of the simpleses the diagrams define, analogous to the analysis in \cite{Arkani-Hamed:2013jha}.
+While there has been work in this area in special cases \cite{Amplituhedronsquared,HeslopStewart,casestudy} there has not been a systematic study of the pole structure of these integrals.
+
+In Section~\ref{sec poles} we give a simple algorithm to read $R(W)$ directly from the Wilson loop diagram, paving the way for a general study of these poles in future.
 
@@
 
-For each $j \in [n]$, we can define a total order $\leq_j$ on the interval $[n]$ by
+For each $j \in [n]$, we can define a total order $<_j$ on the interval $[n]$ by
 \[ j <_j j+1 <_j \dots <_j n <_j 1 \dots <_j j-1\;.\]
@@
 
-By studying $M(W)$ in terms of the behavior of the propagators in $W$, Agarwala and Amat also showed that $M(W)$ is in fact a positroid whenever $W$ is admissible \cite[Corollary 3.39]{wilsonloop}.
-In theory, this allows us to leverage geometric and combinatorial results about $\Gr(k,n)$ to study Wilson loop diagrams.
+By relating the behavior of the propagators in $W$ to the matroidal properties of $M(W)$, Agarwala and Amat also showed that $M(W)$ is in fact a positroid whenever $W$ is admissible \cite[Corollary 3.39]{wilsonloop}.
 
@@
 
+\begin{rmk}
+While this paper primarily approaches proofs from a combinatorial point of view, readers with a background in matroid theory are encouraged to keep the matroidal viewpoint in mind throughout; we expect that the two approaches will be complementary and will build upon each other.
+See [ref][paper 1] for some related results concerning the positroids of Wilson loop diagrams obtained by viewing them primarily as matroids.
+\end{rmk}
+
 \section{Wilson Loop diagrams and their Grassmann necklaces}\label{sec GN algorithm}
 
-In this section we will give an algorithm to go directly from a Wilson loop diagram to the Grassmann necklace of its positroid.
+In this section we will give an algorithm (Algorithm~\ref{alg:put GN on WLD}) to go directly from a Wilson loop diagram to the Grassmann necklace of its positroid.
 This is a useful result in and of itself, as it greatly simplifies the process of identifying the positroid associated to a given WLD.
@@
 This is captured in Definition~\ref{def I_i as a function}, and used throughout the paper.
+
+\note{Sian thinks that a section roadmap here would be overkill: we gave a roadmap in section 1, each subsection has its own little intro roadmap, and I've added a ref to the algorithm above so that people can skip straight to it if they want}
+%In Section~\ref{sec:propagator configs} we examine the structure of admissible Wilson loop diagrams and prove several technical lemmas about configurations of propagators appearing in these diagrams.
+In Section~\ref{sec:GN alg} we state the algorithm that extracts the Grassmann necklace of a given diagram (see Algorithm~\ref{alg:put GN on WLD}) and
 
@@
 % \[\cP_{in}(p, <_i) = \cP_{out}(p, <_j)\quad \text{ and } \quad \cP_{out}(p, <_i) = \cP_{in}(p, <_j).\]
+
+\hlfix{[picture]}{is it worth including a picture here?}
 
@@
 \begin{algorithm}\label{alg:put GN on WLD}
-Let $W = (\cP, [n])$ be an admissible Wilson loop diagram. This gives an algorithm for constructing the set $I_j$, for $j \in [n]$.
+Let $W = (\cP, [n])$ be an admissible Wilson loop diagram. This gives an algorithm for constructing the set $I_i$, for $i \in [n]$.
 
 \begin{enumerate}
-\item Fix a vertex $j \in [n]$. Set $j:=i$ and $I_i = \emptyset$.
+\item Fix a vertex $i \in [n]$, the {\bf starting vertex}. Set $j:=i$ and $I_i = \emptyset$.
 \item While $\cP \neq \emptyset$, perform the following steps:
 \begin{enumerate}
-\item \textbf{Step $j$ for vertex $i$}: If $\Prop(j) = \emptyset$, do nothing.
+\item {\em Step $j$ for starting vertex $i$}: If $\Prop(j) = \emptyset$, do nothing.
 Else, let $p \in \Prop(j)$ be the clockwise most propagator supported on $j$.
@@
 
-To construct $I_1$ we start at vertex 1, so we begin with $i=1$, $m = 1$, and $I_1 = \emptyset$. 
+To construct $I_1$ we start at vertex 1, so we set $i=1$, $j = 1$, and $I_1 = \emptyset$. 
 \begin{itemize}
@@
 
-We first verify that this algorithm always terminates in fewer than $n$ steps.
+\medskip
+
+We first show that the algorithm can never reach the final vertex in a propagator's support without having already assigned that propagator; in particular, this guarantees that the construction of $I_i$ always terminates in fewer than $n$ steps.
 
 \begin{lem}\label{lem no fourth vertex}
-Let $W$ be an admissible Wilson loop diagram containing at least one propagator. For any $i \in [n]$ and for any $p=(a,b)$ with $i\leq_i a <_i b$, we have $I_i(p) \neq b+1$.
+Let $W$ be an admissible Wilson loop diagram containing at least one propagator.
+For any $i \in [n]$ and for any $p \in \cP$, $I_i(p)$ is not maximal (with respect to $<_i$) amongst the vertices that support $p$.
 \end{lem}
 \begin{proof}
-Suppose for contradiction that we have $p = (a,b)$ with $i\leq_i a <_i b$ and $I_{i}(p) = b+1$. We may choose $p$ such that $|[a+1,b]|$ is minimal amongst propagators with this property.
+Suppose for contradiction that we have $i \in [n]$ and $p \in \cP$ such that $I_i(p)$ is $<_i$-maximal in $V(p)$.
+There are two possibilities: either $p = (i-1,b)$ for some $b$ (so $i$ and $I_i(p) = i-1$ are the two ends of a single edge), or $p = (a,b)$ with $i\leq_i a <_i b$ and $I_i(p) = b+1$.
+
+\includegraphics[width=15cm]{4th_vertex}
+
+In the first case, observe that we must have another propagator $q = (c,b)$ with $c<_i b$ and $I_i(q) = b+1$, because otherwise $p$ would not survive until vertex $i-1$.
+Now $q$ also contributes its 4th vertex to $I_i$ and is an instance of the second case listed above, so it suffices to show that no admissible Wilson loop diagram admits this type of configuration.
+
+So let $p = (a,b)$ with $a<_ib$ and $I_i(p) = b+1$, and choose $p$ such that $|[a+1,b]|$ is minimal amongst propagators of $W$ with this property.
 
 Since $I_i(p) \neq b$, there must exist a propagator $q$ inside of $(p,<_i)$ with $I_i(q) = b$.
-The propagator $q$ cannot end on the edge $(b-1,b)$, as this would contradict the minimality of $p$, so we have $q = (c,c+1,b,b+1)$ with $a <_i c <_i b$, and $I_i(q) = b$.
-
-In order for $q$ to remain unassigned until vertex $b$, there must be another propagator $r$ with an end on $(c,c+1)$ and $I_i(r) = c+1$; the only way this can occur is if $r$ is outside $q$ but inside $p$.
-Now $r$ contributes its fourth vertex to $I_i$, again contradicting the minimality of $p$.
+The propagator $q$ cannot end on the edge $b-1$, as this would contradict the minimality of $p$, so we have $q = (d,b)$ with $a <_i d <_i b$, and $I_i(q) = b$.
+
+In order for $q$ to remain unassigned until vertex $b$, there must be another propagator $r$ with an end on edge $d$ and $I_i(r) = d+1$; the only way this can occur is if $r$ is outside of $(q,<_i)$ but inside $(p,<_i)$.
+But now $r$ contributes its fourth vertex to $I_i$, again contradicting the minimality of $p$.
 \end{proof}
@@
 \begin{proof}
-It follows from the proof of Lemma~\ref{lem no fourth vertex} that Algorithm~\ref{alg:put GN on WLD} can never reach the fourth vertex of a propagator's support (with respect to the starting vertex).
-Therefore if the algorithm starts at vertex $i$, it must have assigned vertices to all propagators by the time it reaches $i-1$, ensuring that $I_i$ contains exactly $k$ distinct vertices.
+Fix $i \in [n]$.
+It follows from the proof of Lemma~\ref{lem no fourth vertex} that in applying Algorithm~\ref{alg:put GN on WLD} to construct the set $I_i$, the algorithm can never reach the fourth vertex of a propagator's support (ordered with respect to $<_i$) without having already assigned $p$.
+Therefore if the algorithm starts at vertex $i$, all propagators must have been eliminated by the time it gets to vertex $i-1$, ensuring that the algorithm terminates and that $I_i$ contains exactly $k$ distinct elements.
 \end{proof}
@@
 Specifically, for each $i$ in the support of $p$, define the set
-\[J_p^{(W)}(i) = \{m \in [n] \ | \ I^{(W)}_m(p) = i \},\]
-the set of starting vertices $m$ such that $I_m^{(W)}$ assigns $p$ to $i$.
+\[J_p^{W}(i) = \{m \in [n] \ | \ I^{W}_m(p) = i \},\]
+the set of starting vertices $m$ such that $I_m^{W}$ assigns $p$ to $i$.
 
@@
 
-Let $p=(i,j)$ be a propagator in an admissible WLD $W$ on $n$ vertices.
-Then $J_p^{(W)}(i)$, $J_p^{(W)}(i+1)$, $J_p^{(W)}(j)$, and $J_p^{(W)}(j+1)$ are each non-empty cyclic intervals which partition $[n]$ and occur in the given cyclic order.
+Let $W = (\cP,[n])$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$.
+Then $J_p^{W}(i)$, $J_p^{W}(i+1)$, $J_p^{W}(j)$, and $J_p^{W}(j+1)$ are each non-empty cyclic intervals which partition $[n]$ and occur in the given cyclic order.
 \end{lem}
@@
 Consider the fourth case of Figure~\ref{fig 3 cases} first, as it is the easiest.
-In this case, the vertices $\{l,l+1,l+2,l+3 \}$ which support $p$ in $W$ are non-supporting in $V$, so for every propagator $r$ in $V$ (including $q$) we have $J_r^{(V)} = J_r^{(W)}$; these are non-empty cyclic intervals in the correct order by the induction hypothesis.
-Additionally, it is clear from Figure~\ref{fig 3 cases} that $J_p^{(W)}(l+a) = \{l+a\}$ for $a\in\{1,2,3\}$ and $J_p^{(W)}(l) = [n] \backslash \{l+1, l+2, l+3\}$.
+In this case, the vertices $\{l,l+1,l+2,l+3 \}$ which support $p$ in $W$ are non-supporting in $V$, so for every propagator $r$ in $V$ (including $q$) we have $J_r^{V} = J_r^{W}$; these are non-empty cyclic intervals in the correct order by the induction hypothesis.
+Additionally, it is clear from Figure~\ref{fig 3 cases} that $J_p^{W}(l+a) = \{l+a\}$ for $a\in\{1,2,3\}$ and $J_p^{W}(l) = [n] \backslash \{l+1, l+2, l+3\}$.
 The result therefore holds in this case.
@@
 Now we proceed to consider the first three cases of Figure~\ref{fig 3 cases}.
-We first describe $J_q^{(V)}(*)$, which can be handled identically for all three cases.
+We first describe $J_q^{V}(*)$, which can be handled identically for all three cases.
 
 In $V$ there are no propagators inside $q$, so we see from Figure~\ref{fig V diagram} that
-\[l, l+1, \ldots ,j \in J^{(V)}_q(j) \text{ (if $l$ exists) and }  j+1 \in J^{(V)}_q(j+1).\]
-Note that $j+2 \not\in J^{(V)}_q(j+1)$ by Lemma~\ref{lem no fourth vertex}, so by the induction hypothesis we must have $J^{(V)}_q(j+1) = \{j+1\}$ and $j+2 \in J^{(V)}_q(i)$.
+\[l, l+1, \ldots ,j \in J^{V}_q(j) \text{ (if $l$ exists) and }  j+1 \in J^{V}_q(j+1).\]
+Note that $j+2 \not\in J^{V}_q(j+1)$ by Lemma~\ref{lem no fourth vertex}, so by the induction hypothesis we must have $J^{V}_q(j+1) = \{j+1\}$ and $j+2 \in J^{V}_q(i)$.
 Thus there exist vertices $d,e \in [j+2,i+1]$ with $d <e$, such that
-\[J^{(V)}_q(i) = [j+2,d-1], \quad J^{(V)}_q(i+1) = [d,e-1], \quad J^{(V)}_q(j) = [e,j], \quad J^{(V)}_q(j+1) = \{j+1\},\]
+\[J^{V}_q(i) = [j+2,d-1], \quad J^{V}_q(i+1) = [d,e-1], \quad J^{V}_q(j) = [e,j], \quad J^{V}_q(j+1) = \{j+1\},\]
 and all intervals are non-empty.
@@
 We now consider what happens as we move from $V$ to each of the three remaining cases for $W$.
-We need to consider both $J^{(W)}_p$ and $J^{(W)}_r$ for $r \neq p$, since the addition of $p$ can have a knock-on effect on later steps in the algorithm.
+We need to consider both $J^{W}_p$ and $J^{W}_r$ for $r \neq p$, since the addition of $p$ can have a knock-on effect on later steps in the algorithm.
 
@@
 
-We first calculate $I^{(W)}_w$ for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$.
-Note that $p$ has no effect on other propagators for starting vertices in this range, while the value of $I^{(W)}_w(p)$ depends on how soon $q$ is assigned to a vertex, i.e.
-on the value of $I^{(V)}_w(q)$.
-Thus, if $w\in J_q^{(V)}(i)$ then
+We first calculate $I^{W}_w$ for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$.
+Note that $p$ has no effect on other propagators for starting vertices in this range, while the value of $I^{W}_w(p)$ depends on how soon $q$ is assigned to a vertex, i.e.
+on the value of $I^{V}_w(q)$.
+Thus, if $w\in J_q^{V}(i)$ then
     \[
-    I_w^{(W)}(r) =  \begin{cases}
+    I_w^{W}(r) =  \begin{cases}
         \max\{i+1, m\} & \text{if } r=p \\
-        I_{w}^{(V)}(r) & \text{if } r\neq p
+        I_{w}^{V}(r) & \text{if } r\neq p
       \end{cases} 
     \]
-    while if $w\in J_q^{(V)}(i+1)$ or $w\in J_q^{(V)}(j)$ then
+    while if $w\in J_q^{V}(i+1)$ or $w\in J_q^{V}(j)$ then
     \[
-    I_w^{(W)}(r) =  \begin{cases}
+    I_w^{W}(r) =  \begin{cases}
         l & \text{if } r=p \\
-        I_{w}^{(V)}(r) & \text{if } r\neq p
+        I_{w}^{V}(r) & \text{if } r\neq p
       \end{cases} 
       \]
-We also need to understand $I^{(W)}_w$ for $w \in \{l,l+1,\ldots,j,j+1\}$.
-For the majority of these vertices, we use the following observation: if $p$ is the first propagator to be assigned a value by $I_w^{(W)}$, then the remainder of $I_w^{(W)}$ proceeds identically to the assignments of $I^{(V)}_{w+1}$.
+We also need to understand $I^{W}_w$ for $w \in \{l,l+1,\ldots,j,j+1\}$.
+For the majority of these vertices, we use the following observation: if $p$ is the first propagator to be assigned a value by $I_w^{W}$, then the remainder of $I_w^{W}$ proceeds identically to the assignments of $I^{V}_{w+1}$.
 Thus we have for any $0\leq b <a$
     \[
-    I_{l+b}^{(W)}(r) = \begin{cases}
+    I_{l+b}^{W}(r) = \begin{cases}
       l+b & \text{if } r=p\\
-      I_{l+b+1}^{(V)}(r) & \text{if } r\neq p
+      I_{l+b+1}^{V}(r) & \text{if } r\neq p
     \end{cases}
@@
      \[
-       I_j^{(W)}(r) = \begin{cases}
+       I_j^{W}(r) = \begin{cases}
          j & \text{if $r=p$ and $j$ is in the support of $p$}\\
-         I_{j+1}^{(V)}(r) & \text{if $r\neq p$ and $j$ is in the support of $p$}\\
+         I_{j+1}^{V}(r) & \text{if $r\neq p$ and $j$ is in the support of $p$}\\
        \end{cases}
@@
 $X$ is still admissible since we have not decreased the support of any set of propagators, so the induction hypothesis applies to it as well.
-Note that $J_{j}^{(V)}(r) = J_{j}^{(X)}(r)$ for all $r\neq p$ and $J_{j}^{(X)}(r) = J_{j+1}^{(X)}(r)$ for $r\neq q,p$.
-Additionally $I_{j+1}^{(X)}(q) = i$ by the induction hypothesis applied to $X$, and so if we start at $j+1$ and assign propagators to vertices according to the algorithm, when we reach vertex $i$ in $X$ all propagators other than $q$ must have been assigned.
+Note that $J_{j}^{V}(r) = J_{j}^{X}(r)$ for all $r\neq p$ and $J_{j}^{X}(r) = J_{j+1}^{X}(r)$ for $r\neq q,p$.
+Additionally $I_{j+1}^{X}(q) = i$ by the induction hypothesis applied to $X$, and so if we start at $j+1$ and assign propagators to vertices according to the algorithm, when we reach vertex $i$ in $X$ all propagators other than $q$ must have been assigned.
 Therefore if we start at $j$ in $W$, we first assign $q$ to $j$ then proceed to assign as in $X$ starting at $j+1$, and hence when we get to $i$ the only remaining unassigned propagator is $p$.
@@
        \[
-       I_j^{(W)}(r) = \begin{cases}
+       I_j^{W}(r) = \begin{cases}
 
        m & \text{if $r =p$ and $j$ is not in the support of $p$} \\
-       I_{j}^{(V)}(r) & \text{if $r\neq p$ and $j$ is not in the support of $p$}\end{cases}
+       I_{j}^{V}(r) & \text{if $r\neq p$ and $j$ is not in the support of $p$}\end{cases}
        \] 
@@
 \[
-       I_{j+1}^{(W)}(r)  = \begin{cases}
+       I_{j+1}^{W}(r)  = \begin{cases}
          j+1 & \text{if $r=p$ and $j+1$ is in the support of $p$}\\
-         I_{j+2}^{(V)}(r) & \text{if $r\neq p$ and $j+1$ is in the support of $p$}.
+         I_{j+2}^{V}(r) & \text{if $r\neq p$ and $j+1$ is in the support of $p$}.
        \end{cases}
@@
 If we start at $j+1$ we need to know whether there are any unassigned propagators supported on edge $i$ when we reach vertex $i$.
-We already know that $J_q^{(V)}(j+1) = \{j+1\}$; in particular this means that $q$ contributes $i$ in $I_{j+2}^{(V)}$.
-However the construction of $I^{(V)}_{j+1}$ first associates $q$ to $j+1$ and then proceeds identically to $I^{(V)}_{j+2}$.
-In particular if $i$ was assigned in $I^{(V)}_{j+1}$, then it would not be available to assign to $q$ in $I^{(V)}_{j+2}$ as all other propagators supported at $i$ in $V$ come before $q$.
+We already know that $J_q^{V}(j+1) = \{j+1\}$; in particular this means that $q$ contributes $i$ in $I_{j+2}^{V}$.
+However the construction of $I^{V}_{j+1}$ first associates $q$ to $j+1$ and then proceeds identically to $I^{V}_{j+2}$.
+In particular if $i$ was assigned in $I^{V}_{j+1}$, then it would not be available to assign to $q$ in $I^{V}_{j+2}$ as all other propagators supported at $i$ in $V$ come before $q$.
 
@@
     \[
-    I_{j+1}^{(W)}(r)  = \begin{cases}
+    I_{j+1}^{W}(r)  = \begin{cases}
       m & \text{if  $r=p$ and $j+1$ is not in the support of $p$}\\
-      I_{j+1}^{(V)}(r) & \text{if  $r\neq p$ and $j+1$ is not in the support of $p$}
+      I_{j+1}^{V}(r) & \text{if  $r\neq p$ and $j+1$ is not in the support of $p$}
     \end{cases}
     \]
-We can now describe the intervals $J^{(W)}_r(*)$ for the first two cases of Figure~\ref{fig 3 cases}.
-For $r \neq p$ the intervals are clearly still cyclic and appear in the correct order, and we can assemble the intervals for the $J_p^{(W)}(*)$ as follows.
+We can now describe the intervals $J^{W}_r(*)$ for the first two cases of Figure~\ref{fig 3 cases}.
+For $r \neq p$ the intervals are clearly still cyclic and appear in the correct order, and we can assemble the intervals for the $J_p^{W}(*)$ as follows.
     \begin{itemize}
@@
     \begin{gather*}
-    J^{(W)}_p(m) = [m+4, m], \qquad  J^{(W)}_p(m+1) = \{m+1\}, \\ J^{(W)}_p(m+2) = \{m+2\}, \qquad  J^{(W)}_p(m+3) = \{m+3\},
+    J^{W}_p(m) = [m+4, m], \qquad  J^{W}_p(m+1) = \{m+1\}, \\ J^{W}_p(m+2) = \{m+2\}, \qquad  J^{W}_p(m+3) = \{m+3\},
     \end{gather*}
@@
     \begin{gather*}
-    J^{(W)}_p(m) = [m+4, d-1], \qquad  J^{(W)}_p(m+1) = [d, m+1], \\  J^{(W)}_p(m+2) = \{m+2\}, \qquad  J^{(W)}_p(m+3) = \{m+3\},
+    J^{W}_p(m) = [m+4, d-1], \qquad  J^{W}_p(m+1) = [d, m+1], \\  J^{W}_p(m+2) = \{m+2\}, \qquad  J^{W}_p(m+3) = \{m+3\},
     \end{gather*}
@@
     \begin{gather*}
-    J^{(W)}_p(m) = \{m+4\}, \qquad  J^{(W)}_p(m+1) = [m+5, d-1], \\  J^{(W)}_p(m+2) = [d, m+2], \qquad  J^{(W)}_p(m+3) = \{m+3\},
+    J^{W}_p(m) = \{m+4\}, \qquad  J^{W}_p(m+1) = [m+5, d-1], \\  J^{W}_p(m+2) = [d, m+2], \qquad  J^{W}_p(m+3) = \{m+3\},
     \end{gather*}
@@
     \begin{gather*}
-    J^{(W)}_p(m) = [m+4, j+1], \qquad  J^{(W)}_p(m+1) = [j+2, d-1], \\  J^{(W)}_p(m+2) = [d, m+2], \qquad  J^{(W)}_p(m+3) = \{m+3\},
+    J^{W}_p(m) = [m+4, j+1], \qquad  J^{W}_p(m+1) = [j+2, d-1], \\  J^{W}_p(m+2) = [d, m+2], \qquad  J^{W}_p(m+3) = \{m+3\},
     \end{gather*}
@@
 Again write $p=(m, m+2)$ where $m\in \{j, j+1, j+2\}$.
-We proceed as in the previous cases, by computing $I^{(W)}_w$ for vertices $w$ in roughly increasing order of difficulty.
-
-For $w \in [n]\backslash\{j+1,m,m+1,m+2,m+3\}$: if $w\in J_q^{(V)}(i)$ or $w\in J_q^{(V)}(i+1)$ then
+We proceed as in the previous cases, by computing $I^{W}_w$ for vertices $w$ in roughly increasing order of difficulty.
+
+For $w \in [n]\backslash\{j+1,m,m+1,m+2,m+3\}$: if $w\in J_q^{V}(i)$ or $w\in J_q^{V}(i+1)$ then
     \[
-    I_w^{(W)}(r) =  \begin{cases}
+    I_w^{W}(r) =  \begin{cases}
         m & \text{if } r=p \\
-        I_{w}^{(V)}(r) & \text{if } r\neq p
+        I_{w}^{V}(r) & \text{if } r\neq p
       \end{cases} 
     \]
-    while if $w\in J_q^{(V)}(j)$ then
+    while if $w\in J_q^{V}(j)$ then
     \[
-    I_w^{(W)}(r) =  \begin{cases}
+    I_w^{W}(r) =  \begin{cases}
         \max\{m, j+1\} & \text{if } r=p \\
-        I_{w}^{(V)}(r) & \text{if } r\neq p
+        I_{w}^{V}(r) & \text{if } r\neq p
       \end{cases} 
@@
 \begin{align*}
-  I_{j+1}^{(W)}(r) &= \begin{cases}
+  I_{j+1}^{W}(r) &= \begin{cases}
     j+1 & \text{if } r=q\\
     j+2 & \text{if } r=p\\
-    I_{j+3}^{(V)}(r) & \text{if } r\neq p,q
+    I_{j+3}^{V}(r) & \text{if } r\neq p,q
   \end{cases}\\
-  I_m^{(W)}(r) &= \begin{cases}
+  I_m^{W}(r) &= \begin{cases}
     m & \text{if $r=p$ and $q$ not supported on $m$}\\
     m+1 & \text{if $r=p$ and $q$ supported on $m$}\\
-    I_{m}^{(V)}(r) & \text{if } r\neq p
+    I_{m}^{V}(r) & \text{if } r\neq p
   \end{cases}\\
-  I_{m+1}^{(W)}(r) & = \begin{cases}
+  I_{m+1}^{W}(r) & = \begin{cases}
     m+1 & \text{if $r=p$ and $q$ not supported on $m+1$} \\
     m+2 & \text{if $r=p$ and $q$ supported on $m+1$} \\
-    I_{m+1}^{(V)}(r) & \text{if } r\neq p,q
+    I_{m+1}^{V}(r) & \text{if } r\neq p,q
   \end{cases}\\
-  I_{m+2}^{(W)}(r) & = \begin{cases}
+  I_{m+2}^{W}(r) & = \begin{cases}
     m+2 & \text{if } r=p \\
-    I_{m+3}^{(V)}(r) & \text{if } r\neq p
+    I_{m+3}^{V}(r) & \text{if } r\neq p
   \end{cases}\\
-  I_{m+3}^{(W)}(r) & = \begin{cases}
+  I_{m+3}^{W}(r) & = \begin{cases}
     m+3 & \text{if } r=p \\
-    I_{m+4}^{(V)}(r) & \text{if } r\neq p
+    I_{m+4}^{V}(r) & \text{if } r\neq p
   \end{cases}
 \end{align*}
-Note that $I_{m+2}^{(V)}(r) = I_{m+3}^{(V)}(r)$ for all propagators $r$ in $V$, and that if $j+1\not\in\{m, m+1, m+2, m+3\}$ then $j+2$ and $j+3$ are non-supporting vertices in $V$, so in that case $I_{j+2}^{(V)}(r) = I_{j+3}^{(V)}(r) = I_{j+4}^{(V)}(r)$ for $r$ in $V$.
-
-Therefore, once again we can see that the $J_r^{(W)}(*)$ are cyclic for all $r\neq p$ in $W$.  Assembling the intervals for $p$ we have:
+Note that $I_{m+2}^{V}(r) = I_{m+3}^{V}(r)$ for all propagators $r$ in $V$, and that if $j+1\not\in\{m, m+1, m+2, m+3\}$ then $j+2$ and $j+3$ are non-supporting vertices in $V$, so in that case $I_{j+2}^{V}(r) = I_{j+3}^{V}(r) = I_{j+4}^{V}(r)$ for $r$ in $V$.
+
+Therefore, once again we can see that the $J_r^{W}(*)$ are cyclic for all $r\neq p$ in $W$.  Assembling the intervals for $p$ we have:
 \begin{itemize}
 \item if $m=j$ then
-\begin{gather*}J_p^{(W)}(m) = [m+4,e-1], \qquad  J_p^{(W)}(m+1) = [e,m], \\  J_p^{(W)}(m+2) = [m+1,m+2], \qquad  J_p^{(W)}(m+3) = \{m+3\},\end{gather*}
+\begin{gather*}J_p^{W}(m) = [m+4,e-1], \qquad  J_p^{W}(m+1) = [e,m], \\  J_p^{W}(m+2) = [m+1,m+2], \qquad  J_p^{W}(m+3) = \{m+3\},\end{gather*}
 \item if $m=j+1$ then
-\begin{gather*}J_p^{(W)}(m) = [m+4,m-1], \qquad J_p^{(W)}(m+1) = [m,m+1], \\  J_p^{(W)}(m+2) = \{m+2\}, \qquad  J_p^{(W)}(m+3) = \{m+3\},\end{gather*}
+\begin{gather*}J_p^{W}(m) = [m+4,m-1], \qquad J_p^{W}(m+1) = [m,m+1], \\  J_p^{W}(m+2) = \{m+2\}, \qquad  J_p^{W}(m+3) = \{m+3\},\end{gather*}
 \item if $m=j+2$ then
-\begin{gather*}J_p^{(W)}(m) = [m+4,m], \qquad  J_p^{(W)}(m+1) = \{m+1\}, \\  J_p^{(W)}(m+2) = \{m+2\}, \qquad  J_p^{(W)}(m+3) = \{m+3\}.\end{gather*}
+\begin{gather*}J_p^{W}(m) = [m+4,m], \qquad  J_p^{W}(m+1) = \{m+1\}, \\  J_p^{W}(m+2) = \{m+2\}, \qquad  J_p^{W}(m+3) = \{m+3\}.\end{gather*}
 \end{itemize}
@@
 \begin{align*}
-  I_i^{(W)} \cap [b,i-1] & = I_b^{(W')} \\
-  I_{i+1}^{(W)} \cap [b+1,i-1] & = I_{b+1}^{(W')}
+  I_i^{W} \cap [b,i-1] & = I_b^{W'} \\
+  I_{i+1}^{W} \cap [b+1,i-1] & = I_{b+1}^{W'}
 \end{align*}
 where the diagram is indicated in the superscript.
-Thus we have $m\in I_b^{(W')}\setminus\{b\}$ and $m\not\in I_{b+1}^{(W')}$, contradicting the minimality of $(W, i, m)$.
+Thus we have $m\in I_b^{W'}\setminus\{b\}$ and $m\not\in I_{b+1}^{W'}$, contradicting the minimality of $(W, i, m)$.
 
@@
 \begin{align*}
-  I_i^{(W)} \backslash \{i\} & = I_{i+1}^{(W')} \\
-  I_{i+1}^{(W)} \backslash \{i+1\} & = I_{i+2}^{(W')}
+  I_i^{W} \backslash \{i\} & = I_{i+1}^{W'} \\
+  I_{i+1}^{W} \backslash \{i+1\} & = I_{i+2}^{W'}
 \end{align*}
 since in both cases the algorithm in $W'$ proceeds identically to that in $W$ after assigning $p$.
-Since $m \neq i+1$, we have $m\in I_{i+1}^{(W')}\setminus\{i+1\}$ but $m\not\in I_{i+2}^{(W')}$, contradicting the minimiality of $(W, i, m)$.
+Since $m \neq i+1$, we have $m\in I_{i+1}^{W'}\setminus\{i+1\}$ but $m\not\in I_{i+2}^{W'}$, contradicting the minimiality of $(W, i, m)$.
 
@@
 \begin{proof}
-For any $i \in [n]$, $i-1$ is maximal with respect to the $<_{i}$ order.
-Therefore there can be no propagator $p$ with $I_{i}(p) = i-1$ by Lemma~\ref{lem no fourth vertex}, i.e.
-$i-1 \not\in I_{i}$.
-Thus the Grassmann necklace admis no coloops.
-
-If $j \in [n]$ is a loop then $j \not\in I_j$, which can only happen if there are no propagators supported on vertex $j$.
+For any $i \in [n]$, $i-1$ is maximal with respect to the $<_{i}$ order and so by Lemma~\ref{lem no fourth vertex} there can be no propagator $p$ with $I_{i}(p) = i-1$.
+Thus $i-1 \not\in I_{i}$, so $i-1$ is not a coloop.
+Since this holds for any $i \in [n]$, the Grassmann necklace admis no coloops.
+
+If $j \in [n]$ is a loop then in particular we have $j \not\in I_j$, which can only happen if there are no propagators supported on vertex $j$.
 Conversely, if $j$ supports no propagators, then Algorithm~\ref{alg:put GN on WLD} never assigns a propagator to $j$ and hence $j \not\in I_i$ for all $i \in [n]$.
@@
 
+\bibitem{LipsteinMason}
+Arthur E. Lipstein, Lionel Mason
+\newblock From dlogs to dilogs; the super Yang-Mills MHV amplitude revisited
+\newblock J. High Energ. Phys. (2014) 2014: 169.
+
 \bibitem{reversingOh}

### 2019-05-06 GWLDCII.tex
very minor edit to 3.4

@@
 
-We will inductively construct a sequence of pairs of propagators $(p_r,q_r)$ satisfying: $\ell(p_r) = 2$, and $p_r$ either forms part of configuration \ref{item big and 2} or \ref{item pair of 2s} from the statement,
+We will inductively construct a sequence of propagators $p_r$ and $q_r$, with $\ell(p_r) = 2$ for each $r$ and either:
+\begin{itemize}
+\item $p_r$ forms part of configuration \ref{item big and 2} or \ref{item pair of 2s} from the statement, at which point the induction terminates, 
   %a configuration \eqref{eq:2 prop config} in $D$
-or there is a propagator $q_r$ satisfying
-\begin{itemize}
-\item $\ell(q_r) \geq 4$.
-\item $\{p_1, \ldots, p_r\}$ and $\{q_1, \ldots, q_{r-1}\}$ are all on the same side of $q_r$.  
+{\em or} 
+\item there is a propagator $q_r$ satisfying $\ell(q_r) \geq 4$, and $\{p_1, \ldots, p_r, q_1, \ldots, q_{r-1}\}$ are all on the same side of $q_r$.  
 \end{itemize}
@@
 
-Note that since $j_{r+1}+4 \leq k_r-1$ in both of these situations, the vertex $j_{r+1}+4$ is inside $q_r$ but does not support either $p_r$ or $q_{r+1}$, and must therefore support some other propagator $t$.
+Note that since $j_{r+1}+4 \leq k_r-1$ in both of these situations, the vertex $j_{r+1}+4$ is inside $q_r$ but does not support either $q_r$ or $p_{r+1}$, and must therefore support some other propagator $t$.
 Since $p_{r+1}$ is not part of configuration \ref{item pair of 2s} and $W_r$ has no propagators of length 3, it follows that $\ell(t) \geq 4$.

### 2019-05-06 GWLDCII.tex
minor changes to 3.9

@@
 Suppose for contradiction that we have $i \in [n]$ and $p \in \cP$ such that $I_i(p)$ is $<_i$-maximal in $V(p)$.
-There are two possibilities: either $p = (i-1,b)$ for some $b$ (so $i$ and $I_i(p) = i-1$ are the two ends of a single edge), or $p = (a,b)$ with $i\leq_i a <_i b$ and $I_i(p) = b+1$.
-
+There are two possibilities, which are illustrated in Figure~\ref{fig:no fourth vertex}: either $p = (i-1,b)$ for some $b$ (so $i$ and $I_i(p) = i-1$ are the two ends of a single edge), or $p = (a,b)$ with $i\leq_i a <_i b$ and $I_i(p) = b+1$.
+
+\begin{figure}
 \includegraphics[width=15cm]{4th_vertex}
-
-In the first case, observe that we must have another propagator $q = (c,b)$ with $c<_i b$ and $I_i(q) = b+1$, because otherwise $p$ would not survive until vertex $i-1$.
-Now $q$ also contributes its 4th vertex to $I_i$ and is an instance of the second case listed above, so it suffices to show that no admissible Wilson loop diagram admits this type of configuration.
+\caption{The two possible configurations in which a propagator can contribute its $<_i$-maximal support vertex to $I_i$.}
+\label{fig:no fourth vertex}
+\end{figure}
+
+In the left hand case, observe that we must have another propagator $q = (c,b)$ with $c<_i b$ and $I_i(q) = b+1$, because otherwise $I_i$ would assign $p$ to $b+1$.
+Now $q$ also contributes the $<_i$-maximal vertex in its support to $I_i$ and is an instance of the right hand case listed above.
+Therefore it suffices to show that no admissible Wilson loop diagram admits the configuration illustrated in the right hand case of Figure~\ref{fig:no fourth vertex}.
 

### 2019-05-07 GWLDCII.tex
Sian may or may not have improved Theorem 3.13

@@
 \begin{figure}
-\includegraphics[scale=0.8]{Vdiagram_modified}
+\includegraphics[width=10cm]{V_diagram}
 \caption{Diagram $V$ is $W$ with $p$ removed; there are no propagators inside $q = (i,j)$, though there may be up to 4 non-supporting vertices labelled $l, l+1, \ldots$.}
@@
 
-\hlfix{If $I_i(p_{r-1}) <_i J(p_{r-1})$ and these are vertices supported by distinct ends of $p_{r-1}$}{Sian is confused by this sentence}, then by our assumption above $p_r$ must lie inside $p_{r-1}$ when directed from $I_i(p_{r-1})$ to $J(p_{r-1})$.
-Therefore $j_r = I_i(p_r) \leq_i J(p_{r-1}) + 1$.
+\hlfix{If $I_i(p_{r-1}) <_i J(p_{r-1})$ and these are vertices supported by distinct ends of $p_{r-1}$}{Sian was unsure about this sentence, and added the blue text below which may or may not be necessary}, then by our assumption that $p_{r-1}$ appears before $p_r$ in the neighbourhood of $j_{r-1}$ it follows that $p_r$ must lie inside $p_{r-1}$ when directed from $I_i(p_{r-1})$ to $J(p_{r-1})$.
+Therefore
+\[j_r = I_i(p_r) \leq_i J(p_{r-1}) + 1.\]
 If $r > 2$ then this gives $j_r \leq_i I_i(p_{r-2}) + 1 \leq_i j_0$, but we know that $j_0\not\in I_i$ so in fact we have a strict inequality $j_r<_i j_0$.
-If $r=2$ then either $j_r <_i j_0$ or we have the configuration
+If $r=2$ then the inequality reads $j_2 \leq_i J(p_1) + 1 = j_0 + 1$, so either $j_2 <_i j_0$ or we have the configuration
 \[
@@
 \]
-which is impossible as $p_2$ is supported at $j_0$ but not assigned by $I_i$ until after $j_0$ even though $j_0\not\in I_i$.
-Taking all of this paragraph together we are done unless $I_i(p_{r-1})\not<_i J(p_{r-1})$ so now assume this.
-
-By the induction hypothesis,  $I_i(p_{r-1})\not<_i J(p_{r-1})$ implies that there exists and $\ell < r-1$ such that $p_{r-1}$ is on the side of $p_{\ell}$ that goes from $I_i(p_\ell)$ to $J(p_\ell)$.
-If $j_{r-1}$ is not in the support of the $J(p_\ell)$ end of $p_\ell$ then $p_{r-1}$ before $p_{r}$ around $j_{r-1}$ implies that $p_r$ is on the same side of $p_\ell$ as $p_{r-1}$ is.
+However, this is impossible because now $p_2$ is supported at $j_0$ but not assigned by $I_i$ until after $j_0$, even though $j_0\not\in I_i$.
+Thus we always have $j_r <_i j_0$ and the inductive step is complete in this case (with $p_{r-1}$ playing the role of $p_l$ here).
+
+\textcolor{blue}{
+On the other hand, if $I_i(p_{r-1}) <_i J(p_{r-1})$ and these vertices are on the same end of $p_{r-1}$, then we must have 
+\[
+\includegraphics[width=10cm]{extra_config}
+\]
+If $r = 2$, then $J(p_{r-1}) = j_0$ and our assumption that $p_{r-1}$ is assigned before $p_r$ means that $I_i$ assigns $p_2$ to $j_0$, which is again a contradiction.
+If $r>2$ then $J(p_{r-1}) = I_i(p_{r-2})$ implies we have another propagator $p_{r-2}$ on this same edge, which must lie between $p_{r-1}$ and $p_r$ to ensure that $I_i$ assigns everything in the correct order.
+Now $J(p_{r-2})$ must support the other end of $p_{r-2}$, and we can apply the same argument as above with $p_{r-2}$ instead of $p_{r-1}$.}
+
+The only remaining possibility is that $I_i(p_{r-1})\not<_i J(p_{r-1})$, so now assume this.
+We continue to assume that $p_{r-1}$ appears before $p_r$ in the neighbourhood of $j_{r-1}$ and that $I_i$ assigns $p_{r-1}$ before $p_r$.
+
+By the induction hypothesis,  $I_i(p_{r-1})\not<_i J(p_{r-1})$ implies that there exists an $\ell < r-1$ such that $p_{r-1}$ lies inside $p_{\ell}$ when directed from $I_i(p_\ell)$ to $J(p_\ell)$.
+Since $p_{r-1}$ and $p_r$ are both supported on vertex $j_{r-1}$, either $p_r$ is also inside $p_l$ (in which case we apply the arguments above with $l$ instead of $r-1$) or $p_l$ lies between $p_{r-1}$ and $p_r$ in the neighbourhood of $j_{r-1}$.
+
+Since $I_i(p_{r-1}) = j_{r-1}$ and $p_{r-1}$ is inside $p_l$, the fact that no propagator can contribute its 4th vertex to $I_i$ (Lemma~\ref{lem no fourth vertex}) means that we have the following configuration:
+\[
+\includegraphics[width=10cm]{new_induction_conf}
+\]
+If $l=1$ then $J(p_l) = j_0$, and $p_r$ is supported on $j_0$ but assigned by $I_i$ later than $j_0$, which is a contradiction.
+If $l>1$ then $J(p_l) = I_i(p_{l-1})$, and propagator $p_{l-1}$ must appear before $p_r$ in the neighbourhood of $j_{r-1}$ to ensure that $I_i$ assigns $p_{l-1}$ correctly.
+But now $J(p_{l-1})$ must be on the other end of $p_{l-1}$, since the vertices on this end are $J(p_r)$ and $J(p_l)$ and we know that $l-1 < l < r$.
+Finally, we must have $I_i(p_{l-1}) <_i J(p_{l-1})$ so that $I_i$ does not assign $p_{l-1}$ to its fourth vertex.
+Now $p_r$ lies inside $p_{l-1}$ and we argue as above.
+
+%  If $j_{r-1}$ is not in the support of the $J(p_\ell)$ end of $p_\ell$ then $p_{r-1}$ before $p_{r}$ around $j_{r-1}$ implies that $p_r$ is on the same side of $p_\ell$ as $p_{r-1}$ is.
 Then the same arguments as above with $\ell$ in place of $r-1$ give $j_r \leq_i J(p_\ell)+1$ implying $j_r <_i j_0$ which is everything we need.
 
-It remains to consider when $j_{r-1}$ is in the support of the $J(p_\ell)$ end of $p_\ell$, call this case $(*)$.
+% It remains to consider when $j_{r-1}$ is in the support of the $J(p_\ell)$ end of $p_\ell$, call this case $(*)$.
 Since $J(p_\ell) = j_{\ell-1}$ and the vertices $j_1,\dots,j_r$ are distinct, this means that we have one of the following two configurations
-\[
-\includegraphics{induction_conf}
-\]
-If $p_\ell=p_1$ then $j_{\ell-1}=j_0$ and then as $j_0\not\in I_i$ but $p_r$ is supported at $j_0$ we get $I_i(p_r) <_i j_0$ and also $I_i(p_r) <_i j_{r-1} = J(p_r)$ as the only vertices not yet taken for $I_i(p_r)$ must be before both labelled vertices in the illustration.
-
-If $p_\ell \neq p_1$ then we argue as above with $\ell-1$ in place of $r-1$: in particular $J(p_\ell) = I_i(p_{\ell-1})$ but $p_r$ is supported at $p_{\ell-1}$, so either $I_i(p_r) <_i I_i(p_{\ell-1})$ in which case as before we get desired conclusion, or $p_r$ comes before $p_{\ell-1}$ at $j_{\ell-1}$.
+% \[
+% \includegraphics{induction_conf}
+% \]
+% If $p_\ell=p_1$ then $j_{\ell-1}=j_0$ and then as $j_0\not\in I_i$ but $p_r$ is supported at $j_0$ we get $I_i(p_r) <_i j_0$ and also $I_i(p_r) <_i j_{r-1} = J(p_r)$ as the only vertices not yet taken for $I_i(p_r)$ must be before both labelled vertices in the illustration.
+
+% If $p_\ell \neq p_1$ then we argue as above with $\ell-1$ in place of $r-1$: in particular $J(p_\ell) = I_i(p_{\ell-1})$ but $p_r$ is supported at $p_{\ell-1}$, so either $I_i(p_r) <_i I_i(p_{\ell-1})$ in which case as before we get desired conclusion, or $p_r$ comes before $p_{\ell-1}$ at $j_{\ell-1}$.
 Then again argue as before getting a new $p_{\ell'}$ in place of $p_{\ell}$, except that then case $(*)$ must occur simultaneously for both $p_{\ell'}$ and $p_{\ell}$ with respect to $p_{r}$.
@@
 
-This completes the induction and thence the proof of the theorem.
-
-%Since $J$ is lexicographically smaller than $I_i$, the $<_i$-smallest element of the symmetric difference of $J$ and $I_i$ is some $j_0\in J$, $j_0 \not\in I_i$.
-Let $p$ be the propagator such that $J(p)=j_0$.
-Since $j_0\not\in I_i$ but $p$ is supported at $j_0$, then $p$ must have been assigned to an earlier vertex by $I_i$, i.e.
-we have $I_i(p) <_i j_0$.
-Thus the propagator $p$ has the following property, which we call property $A$:
-%\begin{equation}\label{propertyA}\tag{A}I_i(p) <_i J(p) \text{ \ and \ }I_i\cap [i,I_i(p)] = J\cap [i,I_i(p)]. \end{equation}
-%
-%{}From the previous paragraph we conclude that if we ever had a $J$ which is lexicographically less than $I_i$ and yet a basis of $M(W)$, then there exists a propagator $p$ which has property $A$.
-%
-%Finally, we will prove that whenever there is a propagator $p$ which has property $A$ then there is another propagator $r$ which also has property $A$ and for which $I_i(r) <_i I_i(p)$.
-This would lead to an infinte regress, contradicting the finiteness of $I_i$; thus there could be no such $J$, which will complete the proof of the proposition.
-%
-%So suppose $p$ has property $A$.
-The same vertices in $[i,I_i(p)]$ are in the image of the assignment from $J$ and the image of the assignment from $I_i$ so the same number of propagators are assigned to vertices in this interval by each assignment.
-However $p$ is one of the propagators assigned to a vertex in this interval in $I_i$ but not in $J$.
-Thus there exists a propagator $q$ for which $J(q)\in [i,I_i(p)]$ but $I_i(q) >_i I_i(p)$.
-Therefore $J(q)<_i I_i(q)$ and  $I_i\cap [i,J(q)] = J\cap [i,J(q)]$.
-This is analogous to property $A$ but with the roles of $J$ and $I_i$ switched.
-Thus by the same argument we must have a propagator $r$ for which $I_i(r)\in[i,J(q)]$ but $J(r)>_i J(q)$.
-It follows that $r$ also has property $A$ and that
-%\[I_i(r) \leq_i J(q) \leq_i I_i(p)\]
-%\hlfix{as required.}{We need $I_i(r) <_i I_i(p)$ but I'm having trouble seeing it?}
+This covers all cases and completes the induction, and thence the proof of the theorem.
+
 \end{proof}

### 2019-05-07 GWLDCI.tex
put in one figure
put in the rest of the associahedron figures

@@
 There are many interesting realizations of the associahedron \cite{CSZinequivalent}; the following will be the one which we will use.
-\sanote{picture of an associahedron somewhere?}\note{Yes, I agree that there should be a picture}
+See Figure~\ref{associahedron5gon} for examples.
 
@@
 Therefore, the map $\tau$ associates to each weakly admissible Wilson loop diagram an $n-3 - k$ dimensional face of the associahedron $A_n$.
-\sanote{picture of $\tau(W)$ for $k =1$, $n = 5$?}
+This is illustrated for $n=5$ on the left in Figure~\ref{associahedron5gon}.
+
+\begin{figure}
+\includegraphics{associahedron5gon} \hspace{1cm} \includegraphics{associahedron3d}
+\caption{Two associahedra labelled by all and some (respectively) of their polygon dissections.}\label{associahedron5gon}
+\end{figure}
 
@@
 Thus a vector parallel to this edge is the vector which is $(a(i,j,l) - a, a-a(j,k,i), a(k,l,j)-a, a-a(l,i,k)) = (-a(j,k,l), a(i,k,l), -a(i,j,l), a(i,j,k))$ on $i$, $j$, $k$, $l$ and $0$ in all other coordinates.
-\sanote{definitely need a picture}
+This is illustrated in Figure~\ref{triangulate}.
+
+\begin{figure}
+\includegraphics{triangulate} 
+\caption{The shaded regions are triangulated regions which are the same in $t_1$ and $t_2$.
+Consider $s_{t_1}$ and $s_{t_2}$ at coordinate $i$.
+In $s_{t_1}$ this coordinate is given by the area of those shaded triangles incident to $x_i$ along with $a(i,j,l)$.
+In $s_{t_2}$ this coordinate is given by the area of those shaded triangles incident to $x_i$ along with $a(i,l,k) + a(i,j,k) = a$.}\label{triangulate}
+\end{figure}
 
@@
 Then there are four vertices $x_i$, $x_j$, $x_k$, $x_l$ such that in one of $D_1$ or $D_2$ all four vertices are on the same non-triangle face while in the other there is a diagonal of the dissection such that there is one side of the diagonal with exactly one of $\{x_i, x_j, x_k, x_l\}$ (so the others are end points of this diagonal or strictly on the other side).
-\end{lem} \sanote{picture?}
+\end{lem}
+
+The situation described in the lemma is illustrated in Figure~\ref{configs}.
+
+\begin{figure}
+\includegraphics{configs} 
+\caption{Up to reflection and to rotation of $x_i$, $x_j$, $x_k$, $x_l$, the possible configurations of the quadrilateral from one dissection and diagonal from the other dissection (thick edge) illustrated together on the same vertex set.}\label{configs}
+\end{figure}
 
@@
 In this case the face is either a triangle with its third vertex of the triangle must be in $(x_j,x_k)$ or in $(x_l,x_i)$ or a quadrilateral with one more vertex in $(x_j, x_k)$ and one more vertex in $(x_l, x_i)$.
+The three possibilities are illustrated in Figure~\ref{inductive_step}.
 Taking all this together, whether the face is a triangle or a quadrilateral, replacing $d$ with one of the other edges of the face we get a new diagonal $d'$ which also separates $f$ into $x_i, x_j$ and $x_k, x_l$ but is strictly closer to $[x_i, x_j]$ than $d$ was.
 The same argument holds for $d'$, but the polygon is finite, so this process cannot go on indefinitely, contradicting that no quadtilateral as in the statement exists.
-\note{That huge paragraph also needs a picture}
-\end{proof}
+\end{proof}
+
+\begin{figure}
+\includegraphics{inductive_step} 
+\caption{The three possible configurations in the final part of the proof of Lemma~\ref{lem good quads}.
+The thin lines come from the polygon dissection with $f$ as a face while the thick lines come from the polygon dissection with $d$ as an edge.}\label{inductive_step}
+\end{figure}
 

### 2019-05-07 GWLDCII.tex

@@
 Let $W_r := (\cP_{in}(q_r),[n])$ be the subdiagram of $W$ consisting only of those propagators inside $q_r$ (including $q_r$ itself); in particular $W_r$ contains none of the previous $p_i$ or $q_i$.
-By the original hypotheses on $W$, every vertex in $[i_r,k_{r+1}]$ (which is a non-empty interval since $\ell(q_r) \geq 4$) must support at least one propagator.
+By the original hypotheses on $W$, every vertex in $[i_r,k_{r+1}]$ (of which there are at least 4, since $\ell(q_r) \geq 4$) must support at least one propagator.
 Therefore $W_r$ admits at least one propagator of length 2 (by Remark~\ref{rem:props of length 2 and 3}) and no propagators of length $3$ (by our assumption on $W$).
@@
 
-Note that we could replace $q_r$ by another propagator $q'_{r}$ of length $\geq 4$ in $W_r$, as long as $p_{r+1}$ and $q_r$ are on opposite sides of $q_r'$, and such a new $q'_{r}$ would still satisfy all of the induction hypotheses.
-Therefore without loss of generality we may assume that $q_r$ has minimal length among propagators of length $\geq 4$ in $W_r$ which have $p_{r+1}$ on their inside.
+Note that we could replace $q_r$ by another propagator $q'_{r}$ in $W_r$, as long as $p_{r+1}$ and $q_r$ are on opposite sides of $q_r'$: such a new $q'_{r}$ would still satisfy all of the induction hypotheses.
+Therefore without loss of generality we may assume that $q_r$ is the innermost propagator of length $\geq 4$ in $W_r$ which satisfies the induction hypotheses, i.e.
+we assume that there are no other propagators with $p_{r+1}$ on one side and $q_r$ on the other.
 
@@
 Since $p_{r+1}$ is not part of configuration \ref{item pair of 2s} and $W_r$ has no propagators of length 3, it follows that $\ell(t) \geq 4$.
-If $q_r$ and $p_{r+1}$ were on different sides of $t$ then this would contradict the minimal length hypothesis on $q_r$.
+If $q_r$ and $p_{r+1}$ were on different sides of $t$ then this would contradict the minimality of $q_r$.
 Therefore we can orient $t$ so that all previous $q_i$ and $p_i$ belong to $\cP_{out}(t)$, and set $q_{r+1} = t$ to continue the induction.

### 2019-05-16 GWLDCII.tex
minor wording change
made comments up through theore 3.11

@@
 Note that we could replace $q_r$ by another propagator $q'_{r}$ in $W_r$, as long as $p_{r+1}$ and $q_r$ are on opposite sides of $q_r'$: such a new $q'_{r}$ would still satisfy all of the induction hypotheses.
-Therefore without loss of generality we may assume that $q_r$ is the innermost propagator of length $\geq 4$ in $W_r$ which satisfies the induction hypotheses, i.e.
+Therefore without loss of generality we may assume that {\color{violet}$\cP_{in}(q_r)$ does not contain a propagator (other than $q_r$ itself)} \st{$q_r$ is the innermost propagator of length $\geq 4$ in $W_r$} which satisfies the induction hypotheses, i.e.
 we assume that there are no other propagators with $p_{r+1}$ on one side and $q_r$ on the other.
@@
 \label{fig:no fourth vertex}
-\end{figure}
+\end{figure}f
 
@@
 Now suppose $W$ has more than one propagator.
-Since non-supporting vertices have no effect on Algorithm~\ref{alg:put GN on WLD}, it suffices to prove the result for $W$ with $F(\emptyset) = \emptyset$.
+Since non-supporting vertices have no effect on Algorithm~\ref{alg:put GN on WLD}, it suffices to prove the result for $W$ {\color{violet} (possibly weakly admissible)} with $F(\emptyset) = \emptyset$.
 Then by Lemma~\ref{lem sian}, $W$ has at least one of the four situations illustrated in Figure~\ref{fig 3 cases}.
@@
 
-In $V$ there are no propagators inside $q$, so we see from Figure~\ref{fig V diagram} that
+In $V$ there are no propagators inside $q$, so we see from Figure \ref{fig V diagram} that
 \[l, l+1, \ldots ,j \in J^{V}_q(j) \text{ (if $l$ exists) and }  j+1 \in J^{V}_q(j+1).\]
-Note that $j+2 \not\in J^{V}_q(j+1)$ by Lemma~\ref{lem no fourth vertex}, so by the induction hypothesis we must have $J^{V}_q(j+1) = \{j+1\}$ and $j+2 \in J^{V}_q(i)$.
+Note that $j+2 \not\in J^{V}_q(j+1)$ by Lemma~\ref{lem no fourth vertex}, so  $J^{V}_q(j+1) = \{j+1\}$ and \hlfix{by the induction hypothesis we must have}{moved} $j+2 \in J^{V}_q(i)$.
 Thus there exist vertices $d,e \in [j+2,i+1]$ with $d <e$, such that
-\[J^{V}_q(i) = [j+2,d-1], \quad J^{V}_q(i+1) = [d,e-1], \quad J^{V}_q(j) = [e,j], \quad J^{V}_q(j+1) = \{j+1\},\]
+\ba J^{V}_q(i) = [j+2,d-1], \quad J^{V}_q(i+1) = [d,e-1], \quad J^{V}_q(j) = [e,j], \quad J^{V}_q(j+1) = \{j+1\}, \label{deeqs}\ea
 and all intervals are non-empty.
@@
 \textbf{Left two cases}: These cases behave essentially identically (except when $j$ or $j+1$ are not in the support of $p$, which can occur in the second case only; see below) so we handle the majority of the proof for these two cases simultaneously.
-Let $1\leq a\leq 3$ be the number of non-supporting vertices inside $q$ in $V$; so these vertices are $l, \ldots, l+a-1$.
-Write $p=(m,m+2)$ where $m\in \{i, i+1, l\}$.
-Note that $l, \ldots, l+a-1$ are all in the support of $p$.
-
-We first calculate $I^{W}_w$ for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$.
-Note that $p$ has no effect on other propagators for starting vertices in this range, while the value of $I^{W}_w(p)$ depends on how soon $q$ is assigned to a vertex, i.e.
-on the value of $I^{V}_w(q)$.
+\hlfix{Write $p=(m,m+2)$ where $m\in \{i, i+1, l\}$.}{moved} Let $1\leq a\leq 3$ be the number of non-supporting vertices inside $q$ in $V$ (note that there is at least 1); so these vertices are $l, \ldots, l+a-1$.
+Note that these non-supporting vertices are all in the support of $p$.
+
+We first calculate \hlfix{$I^{W}_w(?)$}{which prop(s), as a function?} for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$.
+Note that $p$ has no effect on other propagators for starting vertices in this range, {\color{violet}(if $r \neq p$, $I_w^W(r) = I_w^V(r)$)} while the value of $I^{W}_w(p)$ depends on \st{how soon $q$ is assigned to a vertex, i.e.
+on}\sanote{don't like the phrasing ``soon''} the value of $I^{V}_w(q)$.
 Thus, if $w\in J_q^{V}(i)$ then
@@
 We also need to understand $I^{W}_w$ for $w \in \{l,l+1,\ldots,j,j+1\}$.
-For the majority of these vertices, we use the following observation: if $p$ is the first propagator to be assigned a value by $I_w^{W}$, then the remainder of $I_w^{W}$ proceeds identically to the assignments of $I^{V}_{w+1}$.
+For the \hlfix{majority}{$w \in [l, l+a-1]$} of these vertices, we use the following observation: if $p$ is the first propagator to be assigned a value by \hlfix{$I_w^{W}$, then the remainder of $I_w^{W}$}{algorithm instead of $I_w^W$?} proceeds identically to the assignments of $I^{V}_{w+1}$.
 Thus we have for any $0\leq b <a$
@@
 
-Consider the WLD $X$ formed from $V$ by moving the second end of $q$ to the edge $j-1$ instead of $j$.
-$X$ is still admissible since we have not decreased the support of any set of propagators, so the induction hypothesis applies to it as well.
-Note that $J_{j}^{V}(r) = J_{j}^{X}(r)$ for all $r\neq p$ and $J_{j}^{X}(r) = J_{j+1}^{X}(r)$ for $r\neq q,p$.
-Additionally $I_{j+1}^{X}(q) = i$ by the induction hypothesis applied to $X$, and so if we start at $j+1$ and assign propagators to vertices according to the algorithm, when we reach vertex $i$ in $X$ all propagators other than $q$ must have been assigned.
+Consider the \st{WLD} {\color{violet} weakly admissible Wilson loop diagram}\sanote{actually, I think this is admissible, because we are removing a propagator from a weakly admissible.
+But it needs a few words?} $X$ formed from $V$ by \st{moving the second end of $q$ to the edge $j-1$ instead of $j$} {\color{violet} replacing the propagator $q = (i,j)$ with $q = (i, j-1)$}.
+$X$ is still {\color{violet}weakly} admissible since we have not decreased the support of any set of propagators, so the induction hypothesis applies to it as well.
+Note that $J_{j}^{V}(r) = J_{j}^{X}(r)$ for all $r\neq p$ {\color{violet}and in particular for $r=q$.
+Further, } \st{and} $J_{j}^{X}(r) = J_{j+1}^{X}(r)$ for $r\neq q,p$.
+Additionally $I_{j+1}^{X}(q) = i$ \st{by the induction hypothesis applied to $X$}, {\color{violet}because} \st{and so} if we start at $j+1$ and assign propagators to vertices according to the algorithm, when we reach vertex $i$ in $X$ all propagators other than $q$ must have been assigned.
 Therefore if we start at $j$ in $W$, we first assign $q$ to $j$ then proceed to assign as in $X$ starting at $j+1$, and hence when we get to $i$ the only remaining unassigned propagator is $p$.
@@
 If we start at $j+1$ we need to know whether there are any unassigned propagators supported on edge $i$ when we reach vertex $i$.
-We already know that $J_q^{V}(j+1) = \{j+1\}$; in particular this means that $q$ contributes $i$ in $I_{j+2}^{V}$.
-However the construction of $I^{V}_{j+1}$ first associates $q$ to $j+1$ and then proceeds identically to $I^{V}_{j+2}$.
-In particular if $i$ was assigned in $I^{V}_{j+1}$, then it would not be available to assign to $q$ in $I^{V}_{j+2}$ as all other propagators supported at $i$ in $V$ come before $q$.
-
-Therefore $p$ is the only potentially unassigned propagator on edge $i$ when we reach vertex $i$ in $W$, and
+We already know that $J_q^{V}(j+1) = \{j+1\}$; \hlfix{in particular this means that $q$ contributes $i$ in $I_{j+2}^{V}$}{why?
+It is true but what does it follow from?
+The next few lines?}.
+However the construction of $I^{V}_{j+1}$ first associates $q$ to $j+1$ and \hlfix{then proceeds identically to $I^{V}_{j+2}$.}{We use this fact a lot should it be a lemma?}  In particular if $i$ was assigned in $I^{V}_{j+1}$, then it would not be available to assign to $q$ in $I^{V}_{j+2}$ as all other propagators supported at $i$ in $V$ come before $q$.
+
+Therefore $p$ is the only potentially unassigned propagator on edge $i$ when we reach vertex $i$ in $W$ {\color{violet} in the algorithm for $I_{j+1}^W$}, and
     \[
@@
     \end{gather*}
-    which are nonempty and otherwise as required.
+    which are nonempty and otherwise as required. {\color{violet}Here, $d$ is as in display \eqref{deeqs}.}
   \item If $m=i$ then $a=1$ or $a=2$, in the former case $l=m+2$, $j=m+3$ and $j+1$ is not in the support of $p$ so

### 2019-05-16 GWLDCII.tex
What's up with 3.12?

@@
 
+{\color{violet} This is a rephrasing of my theorem with Amat (Lemma 3.5 / Theorem 3.6): A set of vertices $V \subset [n]$ is independent if and only if it does not contain a $U \subsetneq V$ such that $|\Prop(U)| > |U|$, which is your injection condition.
+Is this second proof necessary?
+If so, should we at least cite that theorem?}
+
 One of the most important uses of this lemma is for bases.
@@
 The definition of $j_0$ gives that $j_0$ and $j_1$ are distinct and that $p_1$ and $p_2$ are distinct.
-Now, suppose we have $p_r$ and $j_r$ with $I_i(p_r)=j_r$ and with $j_r\in J$.
+Now, suppose we have $p_r$ and $j_r$ with $I_i(p_r)=j_r$, with $j_r$ distinct from all previous $j_*$ and with $j_r\in J$.
 Then there must exist a propagator $p_{r+1}$ with $J(p_{r+1}) = j_r$.

### 2019-05-16 GWLDCII.tex
through case I of 3.13

@@
 We also need to understand $I^{W}_w$ for $w \in \{l,l+1,\ldots,j,j+1\}$.
-For the \hlfix{majority}{$w \in [l, l+a-1]$} of these vertices, we use the following observation: if $p$ is the first propagator to be assigned a value by \hlfix{$I_w^{W}$, then the remainder of $I_w^{W}$}{algorithm instead of $I_w^W$?} proceeds identically to the assignments of $I^{V}_{w+1}$.
+For the \hlfix{majority}{$w \in [l, l+a-1]$} of these vertices, we use the following observation: if $p$ is the first propagator to be assigned a value by \hlfix{$I_w^{W}$, then the remainder of $I_w^{W}$}{$I_w$ instead of $I_w^W$?} proceeds identically to the assignments of $I^{V}_{w+1}$.
 Thus we have for any $0\leq b <a$
@@
 
-Suppose for a contradition that there exists an admissible diagram for which there exists an $i$ with $m\in I_i\setminus \{i\}$ and $m \not\in I_{i+1}$.
+Suppose for a contradiction that there exists an admissible diagram for which there exists an $i$ with $m\in I_i\setminus \{i\}$ and $m \not\in I_{i+1}$.
 Fix $n$.
@@
 Now suppose that $i \in I_i$.
-Let $p$ be the propagator which contributes $i$ to $I_i$; thus one end of $p$ must lie on either edge $i-1$ or edge $i$.
-In both cases let $b$ denote the edge supporting the other end of $p$.
+Let $p$ be the propagator which contributes $i$ to $I_i$, that is, {\color{violet} $I^W_i(p) = i$}; thus one end of $p$ must lie on either edge $i-1$ or edge $i$.
+In both cases let $b$ denote the edge supporting the other end of $p$, {\color{violet}that is, $p = (i, b)$ or $p = (i-1, b)$.}
+\sanote{We use taking and contributing interchangably. Do we want to normalize? I vote for contributing}
 
 \textbf{Case I}:  Suppose $p$ has one end on edge $i-1$.
-Then $p$ is not supported on $i+1$, so in building $I_{i+1}$ we will take the same propagators as in the construction of $I_i$ from vertices $i+1$ up to $b-1$, that is $I_{i+1} \cap [i+1,b-1] = I_{i} \cap [i+1,b-1]$.
-Furthermore, by Lemma~\ref{vertex cyclic int lem}, when building $I_{i+1}$ it must happen that $p$ is taken at vertex $b$, as otherwise $b$ would never be contributed by $p$.
-Consequently, in building $I_{i+1}$, when the algorithm reaches vertex $b$ there cannot be any unassigned propagators remaining that are before $p$.
-This is also true in when the algorithm constructing $I_i$ reaches $b$, since the same propagators have been assigned beforehand.
+Then $p$ is not supported on $i+1$, so in building $I_{i+1}$ \hlfix{we will take the same propagators as in the construction of $I_i$}{what does this mean?
+Isn't it possible to take the same propagators but in a different order to get different numbers?
+If not, is there a proof?} \hlfix{from vertices $i+1$ up to $b-1$, that is $I_{i+1} \cap [i+1,b-1] = I_{i} \cap [i+1,b-1]$}{is this the same fact that is used without proof in 3.11?}.
+Furthermore, by Lemma~\ref{vertex cyclic int lem}, when building $I_{i+1}$ it must happen that $p$ is taken \st{at} {\color{violet} by?} vertex $b$, as otherwise $b$ would never be contributed by $p$.
+Consequently, in building $I_{i+1}$, when the algorithm reaches vertex $b$ there cannot be any unassigned propagators remaining that are \hlfix{before}{do we have an ordering on $\cP$?} $p$.
+This is also true in when the algorithm constructing $I_i$ reaches $b$, since the \hlfix{same propagators have been assigned beforehand}{see above.}.
 Finally, we also note that $m\geq_i b+1$.
@@
 
-By the above observations, if we commence Algorithm~\ref{alg:put GN on WLD} in $W'$ from vertex $b$, then we are in the same situation with respect to unassigned propagators as if we began at $i$ in $W$ and proceeded to $b$ following the algorithm; the propagators we assigned in the latter case are exactly the ones removed to build $W'$.
+By the above observations, if we commence Algorithm~\ref{alg:put GN on WLD} in $W'$ from vertex $b$, then we are in the same situation with respect to unassigned propagators as if we began at $i$ in $W$ and proceeded to $b$ following the algorithm {\color{violet}(recall that $I^W_i(p) =i$)}\st{; the propagators we assigned in the latter case}{\color{violet}.
+The propagators contributing to $I_{i}$ for $W$ before the vertex $b$} are exactly the ones removed to build $W'$.
 Similarly, starting at $i+1$ in $W$ and moving to $b+1$ leaves us in the same situation with respect to unassigned propagators as beginning at $b+1$ in $W'$ would.
@@
   I_{i+1}^{W} \cap [b+1,i-1] & = I_{b+1}^{W'}
-\end{align*}
+\end{align*} \sanote{ $I_i^{W}$ is a map not a $k$-tuple. Do we mean $I_i$ for $W$? or $I_i^{W}(\cP)$ because we want the image set?}
 where the diagram is indicated in the superscript.

### 2019-05-18 GWLDCII.tex
ammendement to 3.12 and more on 3.13

@@
 A characterization of all bases of the positroid in terms of the Grassmann necklace and the Gale order was given by Oh in \cite[Theorem 8]{Oh}: if $(I_1, \dots, I_n)$ is the Grassmann necklace associated to a positroid $M = ([n],\cB)$, then the bases of $M$ are exactly
-\[\cB = \left\{J \in \binom{[n]}{k}\ |\ I_i \gale{i} J \ \forall i \in [n]\right\}.\]
+\ba \cB = \left\{J \in \binom{[n]}{k}\ |\ I_i \gale{i} J \ \forall i \in [n]\right\}. \label{basesofmatroids}\ea
 Thus the Grassmann necklace is well suited to testing whether a given $k$-set is a basis for $M$, and for generating a list of all bases of $M$.
@@
 \begin{dfn}\label{def:le diagram}
-A {\bf Le diagram} is a Young diagram in which every square contains either a $+$ or a $0$, subject to the rule that if a square contains a $0$ then either all squares to its left (in the same row) must also contain a $0$, or all squares above it (in the same column) must also contain a $0$, or both.
+A {\bf Le diagram} is a Young diagram in which every square contains either a $+$ or a $0$, subject to the rule that if a square contains a $0$ then either all squares to its left (in the same row) must also contain a $0$, or all squares above it (in the same column) mustbasesofmatroids\ also contain a $0$, or both.
 \end{dfn}
@@
 
-{\color{violet} This is a rephrasing of my theorem with Amat (Lemma 3.5 / Theorem 3.6): A set of vertices $V \subset [n]$ is independent if and only if it does not contain a $U \subsetneq V$ such that $|\Prop(U)| > |U|$, which is your injection condition.
-Is this second proof necessary?
-If so, should we at least cite that theorem?}
-
-One of the most important uses of this lemma is for bases.
-The lemma says that a subset $J$ of $[n]$ is a basis of $M(W)$ if and only if there is a set bijection between $J$ and $\cP$ with the property that for each $j\in J$ the propagator associated to $j$ under the bijection is supported on vertex $j$.
-
-\begin{proof}
+\st{One of the most important uses of this lemma is for bases.}  The lemma says that a subset $J$ of $[n]$ is a basis of $M(W)$ if and only if there is a set bijection between $J$ and $\cP$ with the property that for each $j\in J$ the propagator associated to $j$ under the bijection is supported on vertex $j$.
+
+{\color{violet} This is equivalent to the condition for a set to be independent  or a basis established in Lemma 3.5 and Theorem 3.6 of \cite{wilsonloop}.
+The equivalence can ben seen by applications of the the pigeon hole principle directly in one direction, and inductively in the other.
+Below, we provide a different proof of this condition for independence.
+Note that either definition of independence and bases corresponds to the sets independent columns and bases of $C(W)$.}
+
+\begin{proof} \sanote{ I would still argue that this should be moved to section 2.
+That is the only place we talk about matroids and positroid associated to Wilson loop diagrams.
+While this is a general linear algebra result, it does reference $C(W)$ several times in the proof.}
 Because the nonzero entries of $C(W)$ are independent indeterminants, $J$ is an independent set is if and only if there is some choice of $|J|$ nonzero entries of $C(W)$ one in each row associated to an element of $J$ and each in different columns.
@@
 \textbf{Case I}:  Suppose $p$ has one end on edge $i-1$.
-Then $p$ is not supported on $i+1$, so in building $I_{i+1}$ \hlfix{we will take the same propagators as in the construction of $I_i$}{what does this mean?
-Isn't it possible to take the same propagators but in a different order to get different numbers?
-If not, is there a proof?} \hlfix{from vertices $i+1$ up to $b-1$, that is $I_{i+1} \cap [i+1,b-1] = I_{i} \cap [i+1,b-1]$}{is this the same fact that is used without proof in 3.11?}.
-Furthermore, by Lemma~\ref{vertex cyclic int lem}, when building $I_{i+1}$ it must happen that $p$ is taken \st{at} {\color{violet} by?} vertex $b$, as otherwise $b$ would never be contributed by $p$.
+\st{Then} {\color{violet}If} $p$ is not supported on $i+1$, \st{so} in building $I_{i+1}$ \hlfix{we will take the same propagators as in the construction of $I_i$from vertices $i+1$ up to $b-1$, that is $I_{i+1} \cap [i+1,b-1] = I_{i} \cap [i+1,b-1]$}{Lemma-ize?}.
+{\color{violet} (If $p$ is supported on $i+1$, $b= i+1$ and the interval $[i+1,b-1]$ is emptry.)} Furthermore, by Lemma~\ref{vertex cyclic int lem}, when building $I_{i+1}$ it must happen that $p$ is taken \st{at} {\color{violet} by?} vertex $b$, as otherwise $b$ would never be contributed by $p$.
 Consequently, in building $I_{i+1}$, when the algorithm reaches vertex $b$ there cannot be any unassigned propagators remaining that are \hlfix{before}{do we have an ordering on $\cP$?} $p$.
@@
 \textbf{Case II}: Suppose $p$ has one end on edge $i$.
-Note that by assumption we have $I_i(p) = i$; this means that $p$ must be the first propagator lying on edge $i$, and hence we must have $I_{i+1}(p) = i+1$ as well.
+Note that by assumption we have $I_i(p) = i$; this means that $p$ must be the \st{first} {\color{violet} counterclockwise most} propagator lying on edge $i$, and hence we must have $I_{i+1}(p) = i+1$ as well.
 Observe also that $m\geq_i i+2$ since $i+1\in I_{i+1}$.
@@
 
-\medskip
-
-We have shown that $(I_1,\dots,I_n)$ is a Grassmann necklace; it remains to check that this Grassmann necklace corresponds to the positroid $M(W)$.  We need to show that:
+\medskip  \sanote{Suggested breakpoint of theorem}
+
+We have shown that $(I_1,\dots,I_n)$ is a Grassmann necklace; it remains to check that this Grassmann necklace corresponds to the positroid $M(W)$.
+{\color{violet} By equation \eqref{basesofmatroids}, w}e need to show that: \sanote{added a number to this eq.
+make it a dfn?}
 \begin{itemize}
 \item For each $i \in [n]$, $I_i$ is a basis for $M(W)$.
-\item If $J$ is lexicographically smaller than $I_i$ with respect to $<_i$, then $J$ is not a basis for $M(W)$.
+\item If $J$ is lexicographically smaller than {\color{violet} any} $I_i$ with respect to $<_i$, then $J$ is not a basis for $M(W)$. 
 \end{itemize}

### 2019-05-20 GWLDCII.tex
read up to 4.4

@@
 
-\begin{cor}\label{no coloops}
+\begin{cor}\label{no coloops}\sanote{cite more prominently in frontmatter}
 Grassmann necklaces coming from admissible Wilson loop diagrams have no coloops. A vertex $j$ is a loop if and only if $j$ supports no propagators. 
@@
 \begin{proof}
-  By Algorithm~\ref{alg:put GN on WLD} the Grassmann necklace of $W$ is obtained from the Grassmann necklace of $V$ by duplicating the $i$th element of the Grassmann necklace of $V$ (shifting indices as appropriate), and incrementing all indices greater than $i$ in each Grassmann necklace element.
+  By Algorithm~\ref{alg:put GN on WLD} the Grassmann necklace of $W$ is obtained from the Grassmann necklace of $V$ by duplicating the $i$th element of the Grassmann necklace of $V$ (shifting indices by $1$ for all indices greater than $i$) \sanote{changed a bit of wording on the proof}, and incrementing all indices greater than $i$ by $1$ in each Grassmann necklace element.
 Formally, if $I_1^{V}, \ldots, I_{n-1}^{V}$ and $I_1^{W}, \ldots, I_n^{W}$ are the Grassmann necklaces of $V$ and $W$ respectively then
@@
   \item $p = (i, n-1)$ for some $i$, and $p$ has no propagators inside it (that is $i+2, \ldots, n-2$ do not support any propagators in $W'$).
-  \item Either the edge $i$ in $W'$ only supports $p$ or the edge $i$ in $W'$ supports exactly one other propagator $q = (j, i)$ with no other propagators inside $q$.
+  \item Either the edge $i$ in $W'$ only supports $p$ or the edge $i$ in $W'$ supports exactly one other propagator \hlfix{$q = (i, j)$ with no other propagators inside $q$ in the $<_i$ ordering, and $j <_1 i$.}{changed.
+Correct?
+Explicitly, not letting $i <_i j <_i n-1$.
+Also made this change below.
+}
   \end{itemize}
@@
 
-Combining Lemmas \ref{lem uncovered}, \ref{lem dihedral}, and \ref{lem good p}, it therefore suffices to study the Le diagrams of weakly admissible Wilson loop diagrams admitting one of the configurations described in Lemma~\ref{lem good p} with propagators $p$ and $q$ (if $q$ exists) both of length 2.
+Combining Lemmas \ref{lem uncovered}, \ref{lem dihedral}, and \ref{lem good p}, it therefore suffices to study the Le diagrams of weakly admissible Wilson loop diagrams with $F(\emptyset)  = \emptyset$, admitting one of the configurations described in Lemma \ref{lem good p} with propagators \hlfix{$p = (n-3, n-1)$ and $q= (n-5, n-3)$}{changed.
+correct?} (if $q$ exists) both of length 2.
 See Figure~\ref{fig special p} for an illustration of the two possibilities.

### 2019-05-21 GWLDCII.tex
finshed reading section 4. added some exposition

@@
 
-Our next goal is to show that the dimension of the positroid cell defined by a Wilson loop diagram $(\cP, [n])$ has dimension $3|\cP|$.
-Marcott in \hlfix{***cite this***}{highlighted for anyone skimming through} has a different proof which is geometric and more elegant, but it is not easy to track the effect of a particular propagator.
+Our next goal is to show that the dimension of the positroid cell defined by a Wilson loop diagram $(\cP, [n])$ has dimension $3|\cP|$ (Theorem \ref{thm dim}).
+The positroid cells associated to the Amplituhedron are of dimension $4|\cP|$.
+In \cite{orientation}, Marcott and the first author show that the dimension of the Deodhar component is $|\cP| +$ the dimension of associated positroid cell.
+In otherwords, the Deodhar component associated to a Wilson loop diagram is $4|\cP|$, showing that the geometry underlying the Wilson loop diagrams is consistent with the geometry underlying the Amplituhedron.
+
+Marcott in \hlfix{***cite this***}{highlighted for anyone skimming through} has a different proof of the dimension of the positroid cell assicated to a Wilson loop diagram, which is geometric and more elegant, but it is not easy to track the effect of a particular propagator.
 Our approach is much more explicit.
@@
 We start with several lemmas, of roughly increasing degree of technicality.
+Lemma \ref{lem uncovered} shows that non-supporting vertices corresopond to columns of $0$s in the associated Le diagram.
+The proof of Theorem \ref{thm dim} depends on being able to act on Wilson loop diagrams by elements of the dihedral group to position propagators in certain positions.
+Lemma \ref{lem dihedral} shows that the dihedral group action does not change the dimension of of the associated Le diagram.
 
@@
 
-The next few lemmas describe how diagrams of this type are related to the corresponding diagram with propagator $p$ removed, first in terms of the Grassmann necklaces and then in terms of the Le diagrams.
+The next few lemmas describe how diagrams of this type are related to the corresponding diagram with propagator $p$ removed, first in terms of the Grassmann necklaces (Lemma \ref{lem I}) and then in terms of the Le diagrams (Lemmas \ref{lem shape} to Lemma \ref{lem other k}) .
 These technical lemmas will form the backbone of the inductive step in the main dimensionality argument.
@@
 From the figure we see that in both cases we have $I_n^{W}(p) = n$.
-We are now at vertex 1, and the unassigned propagators are exactly those that appear in $V$.
-Therefore the algorithm continues as in $I_1^{V}$, i.e.
+At vertex 1 of the algorithm $I_n$, the unassigned propagators are exactly those that appear in $V$.\sanote{same invisible lemma} Therefore the algorithm continues as in $I_1^{V}$, i.e.
 we have $I_n^{W} = I_1^{V} \cup \{n\}$.
@@
 Finally, if $n-2,n-1 \in I_{n-2}^{V}$ then $I_{n-2}^W(q) = n-2$ and $I_{n-2}^W(p) = n-1$ as above, but this is different to what occured in $I_{n-2}^{V}$ so we cannot use the same argument as above.
-We are now at vertex $n$ and only propagators $p$ and $q$ have been assigned; thus we are proceeding as in the construction of $I_n^{V}$ but without propagator $q$.
+When the algorithm $I_{n-2}^W$ reaches vertex $n$, the only propagators $p$ and $q$ have contributed; thus we proceed as in the construction of $I_n^{V}$ but without propagator $q$.
 By Lemma~\ref{vertex cyclic int lem} we know that $I_n^V(q) = n-5$, and from the diagram we see that the only way this could occur is if all other propagators in $V$ had already been assigned when we reached vertex $n-5$; thus $q$ was the final propagator to be assigned in $I_n^{V}$.
@@
   Let $V$ and $W$ be as in Lemma~\ref{lem I}.
-  The shape of the Le diagram of $V$ can be built from left to right of the following blocks: a rectangle which is 3 columns wide, one more column of the same height, and a partition shape with at most as many rows as the rectangle.
+  The shape of the Le diagram of $V$ can be built from left to right of the following blocks: a rectangle which is 3 columns wide, one more column of the same height, and a \hl{partition shape}\sanote{Is this defined?
+shape defined by $I_i$?} with at most as many rows as the rectangle.
   The shape of the Le diagram of $W$ can be built from left to right of the following blocks: a rectangle with 3 columns and one more row than the first rectangle of $V$, and the same partition shape as in $V$.
@@
 
-Recall that $I_1$ determines the shape of the Le diagram. By Lemma~\ref{lem I} we know that
-\newline ${n,n-1,n-2, n-3 \not\in I_1^{V}}$ (which yields the leftmost four columns of the diagram for $V$) and that $I_1^{W} = I_1^{V}\cup \{n-3\}$.
+Recall that $I_1$ determines the shape of the Le diagram.
+By the arguments in Lemma~\ref{lem I} we know that ${n,n-1,n-2, n-3 \not\in I_1^{V}}$ (which yields the leftmost four columns of the diagram for $V$) and that $I_1^{W} = I_1^{V}\cup \{n-3\}$.
 This implies that the right hand boundary of the shape of $V$ is the same as the right hand boundary of the shape of $W$ except that $W$ has one additional row of 3 boxes while $V$ has an additional column in the $n-3$ position; that is, an extra column fourth from the left.
+\sanote{Can we rephrase this in terms of row and column numbers (as in section 2) rather than use shape?}
 \end{proof}
@@
 As illustrated in Figure~\ref{fig Le}, the pieces of the Le diagrams of $V$ and $W$ will be called $\mathcal{A}$ and $\mathcal{B}$ in what follows.
-Over the course of the next few lemmas we will prove that the plusses in the $\mathcal{B}$ parts of each diagram are identical, and that the relationship between the plusses in the $\mathcal{A}$ regions can be described explicitly.
+\hlfix{Explicitly, $\mathcal(B)$ is the set of columns with labels $v < n-3$ and $\mathcal{A}$ the set of columns labeled by $n$, $n-1$ and $n-2$.}{is this accurate?} Over the course of the next few lemmas we will prove that the plusses in the $\mathcal{B}$ parts of each diagram are identical, and that the relationship between the plusses in the $\mathcal{A}$ regions can be described explicitly.
 
@@
   By Lemma~\ref{lem I} we have $I_{n-2}^{W}= (I_{n}^{V} \setminus \{n-5\})\cup \{n-1,n-2\}$ and $I_1^W = I_1^V\cup \{n-3\}$.
-We are necessarily in the case where $W$ admits a propagator $q$ (the right hand case of Figure~\ref{fig special p}) and we can see from the location of $q$ that $n-2\not\in I_{n-3}^{V}$ and that $n-5$ is the index of the lowest vertical edge in $\mathcal{B}$.
+We are necessarily in the case where $W$ admits a propagator $q$ (the right hand case of Figure~\ref{fig special p}) and we can see from the location of $q$ that $n-2\not\in I_{n-3}^{V}$ and that $n-5$ \hlfix{is the label of the last row in}{would like to propagate changes like this through.} $\mathcal{B}$.
 Also note that by Lemma~\ref{vertex cyclic int lem} and Corollary~\ref{no coloops} we must have $n\in I_n^V$.
-Thus this section of the Gramann necklace of $V$ looks like
+Thus this section of the Grassmann necklace of $V$ looks like
 
@@
 
+We are now ready to prove the main result of this section, showing that the dimension of the positroid cell associated to each Wilson loop diagram is $3|\cP|$.
+
 \begin{thm}\label{thm dim}
@@
 
-  We make one further simplification: if our $W$ is in Case 2 of Figure~\ref{fig special p} and $n-1$ supports only $p$ but $n-2$ supports at least one other propagator, then flip $W$ on the line perpendicular to the edge from $n-2$ to $n-1$ to obtain a diagram with the configuration of Case 1.
+  We make one further simplification: if our $W$ is in Case 2 of Figure~\ref{fig special p} and $n-1$ supports only $p$ but $n-2$ supports at least one other propagator, then flip $W$ on the line perpendicular to the $(n-2)^{th}$ edge to obtain a diagram with the configuration of Case 1.
 This eliminates the possibility that we could have $n-2 \in I_{n-2}^W$ but $n-1 \not\in I_{n-2}^W$.
@@
 
-  From Lemma~\ref{lem shape} we know how the shapes of the Le diagrams of $V$ and $W$ are related; let $\mathcal{A}$ and $\mathcal{B}$ be as described after that lemma.
+  From Lemma~\ref{lem shape} we know how the shapes of the Le diagrams of $V$ and $W$ are related; let $\mathcal{A}$ and $\mathcal{B}$ be as described above.
 Lemmas~\ref{lem n and n-1}, \ref{lem n-2 good}, and \ref{lem n-2 bad} tell us that the three boxes of the bottom row of the Le diagram of $W$ each have a plus.

### 2019-05-31 GWLDCI.tex
created a bib file for paper 1

@@
 
-%\bibliographystyle{plain}
-%\bibliography{C:/Users/agarws1/Documents/GitHub/OldWLDPapers/Bibliography}
-
-\begin{thebibliography}{50}
-
-\bibitem{positroids13}
-Federico Ardila, Felipe Rinc{\'{o}}n, and Lauren Williams.
-\newblock Positroids and non-crossing partitions.
-\newblock {\em Transactions of the American Mathematical Society}, 2015.
-\newblock arXiv:1308.2698v2.
-
-\bibitem{Adamo:2011pv}
-Tim Adamo, Mathew Bullimore, Lionel Mason, and David Skinner.
-\newblock {Scattering Amplitudes and Wilson Loops in Twistor Space}.
-\newblock {\em J.Phys.A}, A44:454008, 2011.
-
-\bibitem{wilsonloop}
-Susama Agarwala and Eloi~Marin Amat.
-\newblock Wilson loop diagrams and positroids.
-\newblock {\em Communications in Mathematical Physics}, 2016.
-\newblock arXiv:1509.06150.
-
-\bibitem{casestudy}
-Susama Agarwala and Si\^an Fryer.
-\newblock A study in $\textrm{Gr}_{\geq 0}(2,6)$: from the geometric case book
-  of {W}ilson loop diagrams and {SYM} $N=4$.
-\newblock arXiv:1803.00958.
-
-\bibitem{generalcombinatoricsI}
-Susama Agarwala, Si\^an Fryer, and Karen Yeats.
-\newblock Combinatorics of the geometry of {W}ilson loop diagrams {II}: {G}rassmann necklaces, dimensions, and denominators.
-\newblock manuscript in progress.
-
-\bibitem{non-orientable}
-Susama Agarwala and Cameron Marcott.
-\newblock Wilson loops in {SYM} $N=4$ do not parametrize an orientable space.
-\newblock arXiv:1807.05397.
-
-\bibitem{arkani:2012nw}
-Nima Arkani-Hamed, Jacob~L. Bourjaily, Freddy Cachazo, Alexander~B Goncharov,
-  Alexander Postnikov, and Jaroslav Trnka.
-\newblock Scattering amplitudes and the positive {G}rassmannian.
-\newblock arXiv:1212.5605, 2012.
-
-\bibitem{Arkani-Hamed:2013kca}
-Nima Arkani-Hamed and Jaroslav Trnka.
-\newblock {Into the Amplituhedron}.
-\newblock {\em JHEP}, 12:182, 2014.
-
-\bibitem{Arkani-Hamed:2013jha}
-Nima Arkani-Hamed and Jaroslav Trnka.
-\newblock {The Amplituhedron}.
-\newblock {\em JHEP}, 10:30, 2014.
-
-\bibitem{Britto:2005fq}
-Ruth Britto, Freddy Cachazo, Bo~Feng, and Edward Witten.
-\newblock {Direct proof of tree-level recursion relation in Yang-Mills theory}.
-\newblock {\em Phys.Rev.Lett.}, 94:181602, 2005.
-
-\bibitem{Cachazo:2004kj}
-Freddy Cachazo, Peter Svrcek, and Edward Witten.
-\newblock {MHV vertices and tree amplitudes in gauge theory}.
-\newblock {\em JHEP}, 0409:006, 2004.
-
-\bibitem{Amplituhedronsquared}
-Burkhard Eden, Paul Heslop, and Lionel Mason.
-\newblock The correlahedron.
-\newblock 2017.
-\newblock arxiv:1701.00453.
-
-\bibitem{galashinlam}
-P.~{Galashin} and T.~{Lam}.
-\newblock {Parity duality for the amplituhedron}.
-\newblock {\em arXiv e-prints}, May 2018.
-
-\bibitem{HeslopStewart}
-Paul Heslop and Alastair Stewart.
-\newblock The twistor {W}ilson loop and the amplituhedron.
-\newblock {\em Journal of High Energy Physics}, 2018(10):142, Oct 2018.
-
-\bibitem{AmplituhedronDecomposition}
-Steven~N. Karp, Lauren~K. Williams, and Yan~X. Zhang.
-\newblock Decompostions of amplituhedra.
-\newblock arXiv:1708.09525.
-
-\bibitem{Gale}
-D. Gale.
-\newblock Optimal assignments in an ordered set: {A}n application of matroid theory.
-\newblock {\em J. Combinatorial Theory}, 4: 176 - 180 (1968).
-
-\bibitem{Oh}
-S. Oh.
-\newblock Positroids and {S}chubert matroids.
-\newblock {\em J. Combin. Theory Ser. A}, 118(8):2426--2435, (2011)
-
-\bibitem{Postnikov}
-A.~Postnikov.
-\newblock Total positivity, {G}rassmannians, and networks.
-\newblock \url{arXiv:math/0609764}.
-
-\bibitem{PSpolygon}
-  J\'ozef H. Przytycki and Adam S. Sikora.
-  \newblock Polygon dissections and {E}uler, {F}uss, {K}irkman and {C}ayley numbers.
-  \newblock {\em J. Combin. Theory Ser. A}, 92(1):68--76, (2000). \url{arXiv:math/9811086}.
-
-\bibitem{Stanley}
-  R. P. Stanley.
-  \newblock Enumerative Combinatorics, Vol. 2.
-  \newblock Wadsworth (1999)
-
-\bibitem{Ziegler}
-  G. M. Ziegler.
-  \newblock Lectures on Polytopes.
-  \newblock Springer GTM 152, (1995)
-
-\bibitem{OxleyMatroidBook}
-James~G. Oxley.
-\newblock {\em Matroid Theory}, volume~21 of {\em Oxford graduate texts in
-  mathematics}.
-\newblock Oxford University Press, New York, 2011.
-
-\bibitem{CSZinequivalent}
-  Cesar Ceballos, Francisco Santos, and G\"unter M. Ziegler.
-  \newblock Many non-equivalent realizations of the associahedron
-  \newblock {\em Combinatorica}, 35(5):513--551, (2015).  \url{arxiv:1109.5544}
-
-\end{thebibliography}
+\bibliographystyle{abbrv}
+\bibliography{WLDbib}
+
+%\begin{thebibliography}{50}
+
+% \bibitem{positroids13}
+% Federico Ardila, Felipe Rinc{\'{o}}n, and Lauren Williams.
+% \newblock Positroids and non-crossing partitions.
+% \newblock {\em Transactions of the American Mathematical Society}, 2015.
+% \newblock arXiv:1308.2698v2.
+
+% \bibitem{Adamo:2011pv}
+% Tim Adamo, Mathew Bullimore, Lionel Mason, and David Skinner.
+% \newblock {Scattering Amplitudes and Wilson Loops in Twistor Space}.
+% \newblock {\em J.Phys.A}, A44:454008, 2011.
+
+% \bibitem{wilsonloop}
+% Susama Agarwala and Eloi~Marin Amat.
+% \newblock Wilson loop diagrams and positroids.
+% \newblock {\em Communications in Mathematical Physics}, 2016.
+% \newblock arXiv:1509.06150.
+
+% \bibitem{casestudy}
+% Susama Agarwala and Si\^an Fryer.
+% \newblock A study in $\textrm{Gr}_{\geq 0}(2,6)$: from the geometric case book
+%   of {W}ilson loop diagrams and {SYM} $N=4$.
+% \newblock arXiv:1803.00958.
+
+% \bibitem{generalcombinatoricsI}
+% Susama Agarwala, Si\^an Fryer, and Karen Yeats.
+% \newblock Combinatorics of the geometry of {W}ilson loop diagrams {II}: {G}rassmann necklaces, dimensions, and denominators.
+% \newblock manuscript in progress.
+
+% \bibitem{non-orientable}
+% Susama Agarwala and Cameron Marcott.
+% \newblock Wilson loops in {SYM} $N=4$ do not parametrize an orientable space.
+% \newblock arXiv:1807.05397.
+
+% \bibitem{arkani:2012nw}
+% Nima Arkani-Hamed, Jacob~L. Bourjaily, Freddy Cachazo, Alexander~B Goncharov,
+%   Alexander Postnikov, and Jaroslav Trnka.
+% \newblock Scattering amplitudes and the positive {G}rassmannian.
+% \newblock arXiv:1212.5605, 2012.
+
+% \bibitem{Arkani-Hamed:2013kca}
+% Nima Arkani-Hamed and Jaroslav Trnka.
+% \newblock {Into the Amplituhedron}.
+% \newblock {\em JHEP}, 12:182, 2014.
+
+% \bibitem{Arkani-Hamed:2013jha}
+% Nima Arkani-Hamed and Jaroslav Trnka.
+% \newblock {The Amplituhedron}.
+% \newblock {\em JHEP}, 10:30, 2014.
+
+% \bibitem{Britto:2005fq}
+% Ruth Britto, Freddy Cachazo, Bo~Feng, and Edward Witten.
+% \newblock {Direct proof of tree-level recursion relation in Yang-Mills theory}.
+% \newblock {\em Phys.Rev.Lett.}, 94:181602, 2005.
+
+% \bibitem{Cachazo:2004kj}
+% Freddy Cachazo, Peter Svrcek, and Edward Witten.
+% \newblock {MHV vertices and tree amplitudes in gauge theory}.
+% \newblock {\em JHEP}, 0409:006, 2004.
+
+% \bibitem{Amplituhedronsquared}
+% Burkhard Eden, Paul Heslop, and Lionel Mason.
+% \newblock The correlahedron.
+% \newblock 2017.
+% \newblock arxiv:1701.00453.
+
+% \bibitem{galashinlam}
+% P.~{Galashin} and T.~{Lam}.
+% \newblock {Parity duality for the amplituhedron}.
+% \newblock {\em arXiv e-prints}, May 2018.
+
+% \bibitem{HeslopStewart}
+% Paul Heslop and Alastair Stewart.
+% \newblock The twistor {W}ilson loop and the amplituhedron.
+% \newblock {\em Journal of High Energy Physics}, 2018(10):142, Oct 2018.
+
+% \bibitem{AmplituhedronDecomposition}
+% Steven~N. Karp, Lauren~K. Williams, and Yan~X. Zhang.
+% \newblock Decompostions of amplituhedra.
+% \newblock arXiv:1708.09525.
+
+% \bibitem{Gale}
+% D. Gale.
+% \newblock Optimal assignments in an ordered set: {A}n application of matroid theory.
+% \newblock {\em J. Combinatorial Theory}, 4: 176 - 180 (1968).
+
+% \bibitem{Oh}
+% S. Oh.
+% \newblock Positroids and {S}chubert matroids.
+% \newblock {\em J. Combin. Theory Ser. A}, 118(8):2426--2435, (2011)
+
+% \bibitem{Postnikov}
+% A.~Postnikov.
+% \newblock Total positivity, {G}rassmannians, and networks.
+% \newblock \url{arXiv:math/0609764}.
+
+% \bibitem{PSpolygon}
+%   J\'ozef H. Przytycki and Adam S. Sikora.
+%   \newblock Polygon dissections and {E}uler, {F}uss, {K}irkman and {C}ayley numbers.
+%   \newblock {\em J. Combin. Theory Ser. A}, 92(1):68--76, (2000). \url{arXiv:math/9811086}.
+
+% \bibitem{Stanley}
+%   R. P. Stanley.
+%   \newblock Enumerative Combinatorics, Vol. 2.
+%   \newblock Wadsworth (1999)
+
+% \bibitem{Ziegler}
+%   G. M. Ziegler.
+%   \newblock Lectures on Polytopes.
+%   \newblock Springer GTM 152, (1995)
+
+% \bibitem{OxleyMatroidBook}
+% James~G. Oxley.
+% \newblock {\em Matroid Theory}, volume~21 of {\em Oxford graduate texts in
+%   mathematics}.
+% \newblock Oxford University Press, New York, 2011.
+
+% \bibitem{CSZinequivalent}
+%   Cesar Ceballos, Francisco Santos, and G\"unter M. Ziegler.
+%   \newblock Many non-equivalent realizations of the associahedron
+%   \newblock {\em Combinatorica}, 35(5):513--551, (2015).  \url{arxiv:1109.5544}
+
+%\end{thebibliography}
 

### 2019-05-31 GWLDCI.tex
Edits to section 2 and 3 of paper 1

@@
 
-The main result of Section~\ref{sec equiv} is Theorem~\ref{same matroid iff equiv}.
-To arrive at those results, we first show, in subsection~\ref{sec: polygon partitions}, how certain subdiagrams, called exact subdiagrams, relate to triangulations in polygons and then consider the matroidal properties of the exact subdiagrams in subsection~\ref{sec: exact diagram matroidal props}.
-Specifically, a subdiagram of a Wilson loop diagrams $W$ defines a uniform matroid if and only if the subdiagram is exact (Theorem \ref{exactuniformthm}), and this uniform matroid is the restriction of the dual matriod of $W$ restricted to the exact subdiagram (Remark \ref{remark exact dual restiction}).
-The main result of the section, Theorem~\ref{same matroid iff equiv}, then appears in subsection~\ref{sec: matroids and equivalence}.
-A consequence of this result is the formula for the size of an equivalence class given in Corollary~\ref{number of equiv diagrams}.
-
-The next natural question, then is the number of inequivalent diagrams under this equivalence relation.
-The main result of Section~\ref{sec associahedron} is to show that the set of admissible Wilson loop diagrams up to equivalence is in bijection with the set of faces in the associahedron up to paralellness.
-Towards this result we go over some relevant background on polytopes in subsection~\ref{sec polytope background}, and then give the main result in subsection~\ref{sec associahedron results} in the form of two propositions, Propositions~\ref{prop easy way} and~\ref{prop hard way}.
+The main result of Section~\ref{sec equiv} is Theorem~\ref{same matroid iff equiv}, which says that two Wilson loop diagrams define the same matroid if and only if they are equivalent.
+In subsection~\ref{sec: polygon partitions} we relate certain subdiagrams (the {\em exact} subdiagrams, Definition~\ref{def:exact diagram}) of Wilson loop diagrams to triangulations of polygons, and then in subsection~\ref{sec: exact diagram matroidal props} we examine the matroidal properties of the exact subdiagrams.
+Specifically, we show that a subdiagram of a Wilson loop diagrams $W$ defines a uniform matroid if and only if the subdiagram is exact (Theorem \ref{exactuniformthm}), and that this uniform matroid \hlfix{is isomorphic to}{isomorphic or equal?} the dual matriod of $W$ restricted to the exact subdiagram (Remark \ref{remark exact dual restiction}).
+Subsection~\ref{sec: matroids and equivalence} is devoted to the proof of Theorem~\ref{same matroid iff equiv}, along with an easy corollary which gives a formula for the size of each equivalence class (Corollary~\ref{number of equiv diagrams}).
+
+Having identified the equivalence classes and their sizes, the next natural question is to identify the number of inequivalent diagrams under this equivalence relation.
+The main result of Section~\ref{sec associahedron} is to show that the set of admissible Wilson loop diagrams (up to equivalence) is in bijection with the set of faces in the associahedron (up to paralellness).
+Towards this result we go over some relevant background on polytopes in subsection~\ref{sec polytope background}, and then give the main result in subsection~\ref{sec associahedron results} in the form of two propositions: Propositions~\ref{prop easy way} and~\ref{prop hard way}.
 
@@
 \begin{dfn}\label{WLdfn}
-A Wilson loop diagram is given by the following data: a cyclicly ordered set $V$, along with a choice of first vertex (labeled $1$), and $k$ pairs, called propagators, written $\{p_r = (i_r, j_r)\}_{r=1}^k$.
+A {\em Wilson loop diagram} is given by the following data: a cyclicly ordered set $V$, along with a choice of first vertex (labeled $1$), and a set $\cP$ of $k$ pairs called {\em propagators}, written $\{p_r = (i_r, j_r)\}_{r=1}^k$.
+We write $W = (\cP,V)$ to denote the Wilson loop diagram.
 \end{dfn}
@@
 The vertices are labeled by $V$ (preserving the cyclic ordering).
-The arcs between consecutive vertices are called edges.
-There are $k$ wavy lines in the interior of the diagram, depicting the proagators, with endpoints on the edges.
-A propagator, $p =(i,j)$ has one endpoint on the edge between the vertex labeled $i$ and $i+1$ and another endpoint on the edge defined by $j$ and $j+1$, where $j+1$ is taken, as always, modulo $n$.
-Then we write \bas W = (\cP, V) \;.\eas
-
-Note that the marked circle gives the vertices of $W$ a cyclic ordering.
-The choice of first vertex gives it a compatible linear order.
+The arcs between consecutive vertices are called {\em edges}.
+There are $k$ wavy lines in the interior of the diagram depicting the propagators, whose endpoints lie on the edges: specifically, a propagator $p =(i,j)$ has one endpoint on the edge joining vertices $i$ and $i+1$ and another endpoint on the edge joining $j$ and $j+1$, where $i+1$ and $j+1$ denote the successor of $i$ and $j$ respectively in the cyclic order on $V$.
+
+Note that the marked circle captures the cyclic ordering on $V$, and the choice of a first vertex gives it a compatible linear order.
 Both the cyclic and the linear order become the correct perspective at various points in this paper.
 
-For instance, 
-\bas W = (\cP, [8]) = \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
+Often we take $V$ to be the cyclically ordered set of integers $1 \ldots n$, denoted $[n]$. In this case we write $W = (\cP, [n])$, and all indices are considered modulo $n$.
+
+\begin{eg}\label{eg of WLD} Let $V = [8]$ and $\cP = \{ (1,4), (2, 4), (5, 8)\}$. Then $W = (\cP,[8])$ is the Wilson loop diagram
+\bas \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
 	\begin{scope}
@@
 		\end{scope}
-	\end{tikzpicture}  \eas with $\cP = \{ (1,4), (2, 4), (5, 8)\}$ is a Wilson loop diagram.
-
-Often we take $V$ to be $[n]$, the cyclically ordered set of integers, $1 \ldots n$.
-In this case, we write $W = (\cP, [n])$.
+	\end{tikzpicture}  \eas 
+\end{eg}
+
+\medskip
+
 We introduce some notation to speak of vertices supporting a propagator, and the set of propagators supported on a vertex set.
@@
 \begin{enumerate}
-\item For $p \in \cP$, let $V(p) = \{i_p, i_p+1, j_p, j_p+1\}$ be the set of vertices supporting $p$. Then, for $P \subseteq \cP$, the set $V(P) = \cup_{p \in P} V(p)$ is the vertex support of $P$.
-\item For $V \subseteq [n]$, write $\Prop(V) = \{ p \in \cP | V(p) \cap V \neq \emptyset \} $.
-\item For $P \subseteq \cP$, define $F(P) = V(P^c)^c$ to be\footnote{Here, as throughout, we are using the superscript $c$ for the set theoretic complement.} the set of vertices in $[n]$ that do not support any propagators outside the set $P$.
-\item The set of vertices that are not in the support of any propagotors is denoted  $F(\emptyset)$. Vertices in this set are called non-supporting.  
+\item For $p = (i_p,j_p) \in \cP$, define $V(p) = \{i_p, i_p+1, j_p, j_p+1\}$ to be the set of vertices supporting $p$.
+Similarly, for $P \subseteq \cP$ we define the set $V(P) = \cup_{p \in P} V(p)$ to be the vertex support of $P$.
+\item For $U \subseteq [n]$, write $\Prop(U) = \{ p \in \cP  \ | \ V(p) \cap U \neq \emptyset \} $ to denote the set of propagators which are at least partially supported on $U$.
+\item For $P \subseteq \cP$, define $F(P) = V(P^c)^c$ to be\footnote{Here, as throughout, we are using the superscript $c$ for the set theoretic complement.} the set of vertices in $[n]$ that do not support any propagators outside of the set $P$.
+\item The set of vertices that do not support any propagators is denoted $F(\emptyset)$. Vertices in this set are called {\em non-supporting}.  
 \end{enumerate}
@@
 \begin{rmk}\label{alt F(P) rmk}
-Note that a more explicit definition of $F(P)$ is \bas F(P)  = \big(V(P) \setminus V(P^c) \big) \cup F(\emptyset) \;.\eas Furthermore, note that by construction $\Prop(F(P)) \subseteq P$.
+An equivalent definition of $F(P)$ \note{Sian note to self: doublecheck that these {\em are} equiv definitions now} is \bas F(P)  = \big(V(P) \setminus V(P^c) \big) \cup F(\emptyset) \;,\eas 
+i.e.
+$F(P)$ can be thought of as the set of vertices that either only support propagators in $P$ or do not support any propagators at all.
+Furthermore, note that by construction $\Prop(F(P)) \subseteq P$.
 This containment is strict if there is any propagator $p$ in $P$ with the property that every vertex in the support of $p$ also supports a propagator not in $P$.
@@
 
-\begin{dfn}
-The $i^{th}$ edge of $W$ is the edge of the external polygon that lies between the vertices $i$ and $i+1$.
+\begin{dfn}\label{def:edges}
+The $i$th edge of $W$ is the edge of the external polygon that lies between the vertices $i$ and $i+1$.
 \end{dfn}
 
-In this manner, the propagator $p = (i, j)$ is supported by the $i^{th}$ and $j^{th}$ edges.
+In this manner, the propagator $p = (i, j)$ is supported by the $i$th and $j$th edges.
+
+We now define the notion of an admissible diagram, which imposes certain density and non-crossing conditions on the configuration of the propagators.
 
 \begin{dfn}\label{admisdfn}
-A Wilson loop diagram is admissible if \begin{enumerate}
+A Wilson loop diagram $W = (\cP,V)$ is {\em admissible} if \begin{enumerate}
 \item $|V| \geq |\cP| + 4$
-\item There does not exists a set of propagators, $P \subseteq \cP$ such that $|V(P)| < |P| + 3$.
-\item There does not exist a pair of propagators, $p, q \subseteq \cP$ such that $i_p < i_q < j_p <j_q$.
+\item There does not exists a set of propagators $Q \subseteq \cP$ such that $|V(Q)| < |Q| + 3$.
+\item There does not exist a pair of propagators $p, q \in \cP$ such that $i_p < i_q < j_p <j_q$.
 \end{enumerate}
-A Wilson loop diagram is weakly admissible if the second and third conditions hold.
+A Wilson loop diagram is called {\em weakly admissible} if the second and third conditions hold.
  \end{dfn}
 
-The first conditions states that there are at least four more vertices than propagators in an admissible Wilson loop diagram.
-The second imposes an upper bound on how densely the propagators can be fitted in any portion of the diagram.
+The first condition restricts the overall density of propagators in the diagram, while the second imposes an upper bound on how densely the propagators can be fitted in any portion of the diagram.
 The third ensures that ensures that no propagators cross in the interior of the diagram.
+
 In other words, a Wilson loop diagram, $(\cP, [n])$ is admissible if and only if $n \geq |\cP| +4$, and has no crossing propagators, no propagators of the form $p = (i, i+1)$, and no pairs of propagators that start and end on the same pair of non-adjacent edges.
@@
 
-Note that if we take any admissible Wilson loop diagram and remove the non-supporting vertices then we will obtain a weakly admissible Wilson loop diagram that may or may not be admissible itself.
-
-In what follows, we will talk about admissible Wilson Loop diagrams and subdiagrams thereof.
+Note that if we take any admissible Wilson loop diagram and remove the non-supporting vertices, we obtain a weakly admissible Wilson loop diagram that may or may not be admissible itself.
+
+In what follows, we will restrict our attention to admissible Wilson loop diagrams and subdiagrams thereof.
 
@@
 Let $W = (\cP, [n])$ be an admissible Wilson loop diagram.
-The weakly admissible diagram, $W'$ is a subdiagram of $W$, written $W' \subseteq W$, if \bas W' = (P, V); \quad P \subseteq \cP ; \quad V(P) \subseteq V \subseteq [n]\;.\eas
+The weakly admissible diagram $W' = (P,V)$ is a {\em subdiagram} of $W$, written $W' \subseteq W$, if \bas P \subseteq \cP \text{ and } \quad V(P) \subseteq V \subseteq [n]\;.\eas
 \end{dfn}
 
-There is one particular type subdiagram that deserves special attention.
-
-\begin{dfn}
-For $W$ an admissible diagram, $(P, V(P))$ is exact if $|V(P)| = |P| + 3$.
+There is one particular type of subdiagram that deserves special attention:
+
+\begin{dfn}\label{def:exact diagram}
+For $W$ an admissible diagram, $(P, V(P))$ is {\em exact} if $|V(P)| = |P| + 3$.
 \end{dfn}
 
+We will see in Section~\ref{sec equiv} that the exact diagrams play an important role in classifying admissible Wilson loop diagrams.
+
 \begin{eg}
-The Wilson loop diagram $W$ shown above is admissible.
-There is a single non-supporting vertex in $W$, $F(\emptyset) = \{7\}$.
-The subdiagram $(\{(2, 4), (1, 4)\}, \{1, 2, 3, 4, 5, \})$ is an exact subdiagram of $W$.
-For $p = (5, 8)$ $F(p) = \{6, 7,8\}$.
+The Wilson loop diagram $W$ in Example~\ref{eg of WLD} is an example of an admissible diagram.
+It has a single non-supporting vertex, namely the vertex labeled 7, so we have $F(\emptyset) = \{7\}$.
+For $p = (5, 8)$, we have $V(p) = \{5,6,8,1\}$ and $F(p) = \{6, 7,8\}$: the vertices 1 and 5 are excluded from $F(p)$ since they support other propagators as well, and 7 is included (despite not being in the support of $p$) since it supports no propagators at all.
+Finally, the subdiagram $(\{(2, 4), (1, 4)\}, \{1, 2, 3, 4, 5, \})$ is an example of an exact subdiagram; in fact it is the only non-trivial exact subdiagram in $W$.
 \end{eg}
 
-The exact subdiagrams define an equivalence relation amongst Wilson loop diagrams.
+The exact subdiagrams define an equivalence relation amongst Wilson loop diagrams as follows.
 
 \begin{dfn}\label{equivdfn} 
-There is an equivalence relationship on the set of admissible Wilson loops diagrams given by the transititve closure the following binary relation: $W = (\cP, [n]) \sim W'= (\cP', [n])$ if
+Let $W = (\cP,[n])$ and $W' = (\cP',[n])$.
+Define an equivalence relation $\sim$ on the set of admissible Wilson loop diagrams with vertex set $[n]$ by taking the transitive closure of the following relation: $W \sim W'$ if
 \begin{enumerate}
-\item There exist two different exact subdiagrams, $(P, V(P))$ and $(P', V(P'))$ of $W$ and $W'$ respectively such that $V(P) =  V(P')$.
-\item The complementary subdiagrams are identical: $(\cP \setminus P, V(P)^c) = (\cP' \setminus P', V(P')^c)$.
+\item There exist exact subdiagrams $(P, V(P)) \subseteq W$ and $(P', V(P')) \subseteq W'$ with $V(P) =  V(P')$.
+\item The complementary subdiagrams are identical, i.e. $(\cP \setminus P, V(P)^c) = (\cP' \setminus P', V(P')^c)$.
 \end{enumerate}
@@
 \begin{eg} \label{eg:equivdiags}
-Note that since this is an equivalence relation, we may find that two Wilson loop diagrams are equivalent, even if they do not have complements of (non-trivial) exact subdiagrams in common.
-Consider the following three Wilson loop diagrams,
+Note that we genuinely do need to take the transitive closure of this relation in order to obtain an equivalence relation. For example, consider the following three Wilson loop diagrams:
 \bas
@@
 
-The diagrams $W_1 \sim W_2$ because $(\{(5,8), (5,7)\}, \{5,6,7,8,1\})$ and $(\{(5,8), (7,8)\}, \{5,6,7,8,1\})$ are the corresponding differing subdiagrams.
-Furthermore, there is the equivalence $W_2 \sim W_3$ due to the exact subdiagrams $(\{(1,4), (3,4)\}, \{1,2,3,4,5\})$ and $(\{(1,4), (1,3)\}, \{1,2,3,4,5\})$.
-This forces an equivalence between $W_1$ and $W_3$, even though one cannot partition the propagators of each into a an exact subdiagram (that may vary between the diagrams) and a complement that is fixed.
-\end{eg}
-
-Each Wilson loop diagram, $W = (\cP, [n])$ with $|\cP| = k$ is associated to a $k \times n$ matrix with non-zero real variable entries, called $C(W)$:
-
-\ba C(W)_{p,q} = \begin{cases} c_{p,q} & \textrm{ if } q \in V(p) \\
+We have $W_1 \sim W_2$ because they agree except on the exact subdiagrams 
+\[(\{(5,8), (5,7)\}, \{5,6,7,8,1\}) \text{ and }(\{(5,8), (7,8)\}, \{5,6,7,8,1\})\] respectively. We also have $W_2 \sim W_3$ due to the exact subdiagrams 
+\[(\{(1,4), (3,4)\}, \{1,2,3,4,5\}) \text{ and }(\{(1,4), (1,3)\}, \{1,2,3,4,5\}).\] 
+However, the difference between $W_1$ and $W_3$ is the union of two exact subdiagrams, which is not itself exact. \end{eg}
+
+As described in the introduction, Wilson loop diagrams come from the study of SYM $N = 4$ in the physics literature, and therefore each diagram is associated to a matrix of data which we now describe.
+
+\begin{dfn}\label{def:CWmatrix}
+Each Wilson loop diagram $W = (\cP, [n])$ with $|\cP| = k$ is associated to a $k \times n$ matrix $C(W)$ with non-zero real variable entries, defined by:
+
+\bas C(W)_{p,q} = \begin{cases} c_{p,q} & \textrm{ if } q \in V(p) \\
 0  & \textrm{ if } q \not \in V(p)  \end{cases}
-\;. \label{C(W) dfn}\ea
+\;. \eas
+\end{dfn}
 
 \begin{eg}
-For example, ordering the propagators of $W_1$ from Example \ref{eg:equivdiags}: \bas (1,4), \, (2,4), \, (5,7), \, (5,8) \eas we may write
+For example, if we order the propagators of $W_1$ from Example \ref{eg:equivdiags}as follows: \bas (1,4), \, (2,4), \, (5,7), \, (5,8) \eas we obtain the corresponding matrix
 \bas C(W_1) = \left(
@@
 Throughout, we take the {\em matroid defined by $W$} to be the matroid $M(W)$ of Theorem \ref{thm WLD defines matroid}.
-Note from equation \eqref{C(W) dfn}that the vertices of the diagram $W$ correspond to columns of the associated matrix $C(W)$.
-Therefore, for any subset of vertices $V \subset [n]$,  then one can write $C(W)|_V$ is the restriction of $C(W)$ to the columns corresponding to $V$.
-Since the non-zero entries of $C(W)$ are independant real variables, the matrix $C(W)|_V$ does not have full rank if and only if there are fewer rows with non-zero entries than $|V|$.
+Note from Definition~\ref{def:CWmatrix} that the vertices of the diagram $W$ correspond to columns of the associated matrix $C(W)$.
+Therefore, for any subset of vertices $V \subseteq [n]$, we can consider the restriction $C(W)|_V$ of $C(W)$ consisting of the columns corresponding to $V$.
+Since the non-zero entries of $C(W)$ are independent real variables, the matrix $C(W)|_V$ does not have full rank if and only if there are fewer than $||V$ rows with non-zero entries.
 This is equivalent to saying that $V$ is a set of dependent columns of $C(W)$ if and only if $|\Prop(V)| < |V|$.
@@
 
-Let $W = (\cP,n)$ be an admissible Wilson loop diagram, and $M(W)$ its associated matroid.
+Let $W = (\cP,[n])$ be an admissible Wilson loop diagram, and $M(W)$ its associated matroid.
 Where it will not cause confusion we conflate the two objects, identifying vertices of $W$ with elements of the ground set $[n]$ in $M(W)$.
@@
 adding a vertex that supports a new propagator to a set increases the rank of the set.
-\item If $C \subseteq [n]$ is a cycle in the matroid, then $\rk(C) = |Prop(C)|$.
-\item If $[n]$ can be partitioned into at least two non-empty sets, each of which support different sets of propagators, and that form a partition of the propagotor set, \bas [n] = \sqcup_i V(P_i) \quad \textrm{s.t.} \quad \sqcup P_i = \cP; \quad V(P_i) \cap V(P_j) = \emptyset; \quad  P_i \cap P_j = \emptyset \;, \eas then the matroid $M(W)$ is seperable, \bas M(W) = \bigoplus_i M(P_i, V(P_i)) \;.\eas
-\item $F(P)$ is a flat of $M(W)$ which we call the \emph{propagator flat} of $P$.
+\item If $C \subseteq [n]$ is a cycle in $M(W)$, then $\rk(C) = |Prop(C)|$.
+\item If $[n]$ can be partitioned into at least two non-empty sets, each of which support disjoint sets of propagators and in such a way that we obtain a partition of the propagator set, i.e.
+if we have \bas [n] = \sqcup_i V(P_i) \quad \textrm{ such that } \quad \sqcup P_i = \cP;  \text{ with }V(P_i) \cap V(P_j) = \emptyset \text{ and } P_i \cap P_j = \emptyset \quad \forall i \neq j\;, \eas then the matroid $M(W)$ is separable, i.e.
+\bas M(W) = \bigoplus_i M(P_i, V(P_i)) \;.\eas
+\item $F(P)$ is a flat of $M( W)$, which we call the \emph{propagator flat} of $P$.
 \end{enumerate}
@@
 Let $S \subseteq F(P)$ be an independent set of maximal size.
-Then $\Prop(S) \subseteq P$ and no subset of $S$ supports fewer propagators than the number of vertices it contains (by (1) this is one characterization of an independent set in $M(W)$).
+Then $\Prop(S) \subseteq P$ (from the definition of $F(P)$) and no subset of $S$ supports fewer propagators than the number of vertices it contains (by Theorem~\ref{thm WLD defines matroid} this is one characterization of an independent set in $M(W)$).
 Since $v$ supports a new propagator $q \not\in P$, the set $S \cup \{v\} \subseteq F(P) \cup\{v\}$ also satisfies this independence condition.
@@
 
-Note that this means that the set, $F(\emptyset)$, of non-supporting vertices is the maximal subset of vertices of $W$ of rank $0$.
+\note{sian note to self: come back and package this as a remark, and make sure it follows from the previous result}
+Note that this means that the set $F(\emptyset)$ of non-supporting vertices is the maximal subset of vertices of $W$ of rank $0$.
 That is, it is the unique flat of rank $0$ in $M(W)$.
-Also, every element of $F(\emptyset)$ is a circuit and all other circuits of $M(W)$ contain at least two elements.
+This also implies that every element of $F(\emptyset)$ is a circuit, and all other circuits of $M(W)$ contain at least two elements.
 
@@
 
-\emph{Polygon dissection} is a common term in combinatorics for a decomposition of a convect polygon into smaller polygons by means of noncrossing diagonals, see \cite{PSpolygon}.
+\emph{Polygon dissection} is a common term in combinatorics for a decomposition of a convex polygon into smaller polygons by means of noncrossing diagonals, see \cite{PSpolygon}.
 Each $\tau(W)$ is such an object.
@@
 
-Split every vertex of $T(W)$ which has degree $>3$.
+Split every vertex of $T(W)$ which has degree $>3$ (see Figure~\ref{fig:vertex splitting in the dual graph} for an example of this).
 %By construction, each face of $\tau(W)$ is a polygon.
@@
 We claim that the connected components of $T(W)$ correspond to the decomposition of $\tau(W)$ into maximal triangulated pieces and edges originally in the polygon of $\tau(W)$.
-To see this let $f$ be the forest thus obtained.
+To see this, let $f$ be the forest thus obtained.
 The vertices of $f$ either have degree 1 or 3.
@@
 
+\begin{figure}[h]
 \bas 
@@
 	\end{scope}
-	\end{tikzpicture} \rightarrow 
+	\end{tikzpicture} \qquad \longrightarrow \qquad 
 \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
@@
 
+\caption{The polygon dissection $\tau(W_3)$ overlaid with its dual graph $T(W_3)$ (left diagram), and the forest obtained by splitting at all vertices of degree $>3$ (right diagram).}
+\label{fig:vertex splitting in the dual graph}
+\end{figure}
+
 To see uniqueness, consider a different maximal decomposition of $\tau(W)$.
@@
   \begin{itemize}
-  \item the vertices of $\tau(W)$ corresponding to edges of $W$ whose end points are elements of $V(P)$ which are cyclically consecutive in $[n]$
+  \item the vertices of $\tau(W)$ corresponding to edges of $W$ whose end points are elements of $V(P)$ which are cyclically consecutive in $[n]$.
+(This is significantly easier to interpret in picture form: see Example~\ref{eg:subtrees} below.)
   \end{itemize}
@@
   \begin{itemize}
-  \item the edges of $\tau(W)$ corresponding to propagators of $P$
-  \item along with the outer edges of $\tau(W)$ for which both their end points are in the vertex set
+  \item the edges of $\tau(W)$ corresponding to propagators of $P$,
+  \item along with the outer edges of $\tau(W)$ for which both their end points are in the vertex set.
   \end{itemize}
@@
 
-\begin{eg}
-For example, consider the following Wilson loop diagram, $W$, and its corresponding chord diagram, $\tau(W)$. 
+\begin{eg}\label{eg:subtrees}
+Consider the following Wilson loop diagram $W$ and its corresponding chord diagram $\tau(W)$. 
 \bas W = \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
@@
 
-The set of propagators $P= \{(1,4), (2,4), (4, 8), (1,8) \}$, define an exact subdiagram of $W$. The vertex set of $t$ are the vertices labeled $\{1, 2,3, 4, 5, 8\}$. The subgraph $t$ is then
+The set of propagators $P= \{(1,4), (2,4), (4, 8), (1,8) \}$ defines an exact subdiagram of $W$, with $V(P) = \{1,2,3,4,5,8,9\}$.
+The corresponding subgraph $t$ of $\tau(W)$ has vertex set $\{1, 2,3, 4, 8\}$.
+Note that we don't include vertex 5 because it corresponds to the edge in $W$ that connects vertices 5 and 6, but 6 does not belong to $V(P)$.
+Vertex 9 is excluded for similar reasons.
+
+The subgraph $t$ is then
 
@@
 
-Note that the subgraph $t$ depends on how the propagators of $P$ sit inside $[n]$, not on how they sit in $W_P$ itself.
-In particular $t$ is not the subgraph of $\tau(W)$ consisting only of edges corresponding to propagators of $P$.
+The key point to note is that the subgraph $t$ depends on how the propagators of $P$ sit inside $[n]$, not on how they sit in $W_P$ itself.
+In particular, $t$ is not the subgraph of $\tau(W)$ consisting only of edges corresponding to propagators of $P$ (as it may also include some of the outer edges of $\tau(W)$), nor is it the polygon dissection of $(P,V(P))$ (which would contain the extra vertices 5 and 9).
 \end{eg}
@@
 
-To avoid the issue of exact diagrams being subdiagrams of other exact subdiagrams (for instance, any subdiagram $(q, V(q))$, for $q \in \cP$ is exact), we introduce the notion of maximal exact subdiagrams.
+To avoid the issue of exact diagrams being subdiagrams of other exact subdiagrams (for instance, any subdiagram $(q, V(q))$ for $q \in \cP$ is exact), we introduce the notion of maximal exact subdiagrams.
 
@@
 \begin{proof}
-This follows from the definition of equivalent Wilson loop diagrams, Definition \ref{equivdfn}, the definition of retriangulations, Definition \ref{retriangulation}, and Lemma \ref{lem triang to exact}.
-\end{proof}
-
+This follows from the definition of equivalent Wilson loop diagrams (Definition \ref{equivdfn}), the definition of retriangulations (Definition \ref{retriangulation}), and Lemma \ref{lem triang to exact}.
+\end{proof}
+
+\note{sian note to self: reading/editing has reached this point}
 \subsection{Matroidal properties of exact subdiagrams \label{sec: exact diagram matroidal props}}
@@
 Since Corollary \ref{uniqueproppartitioncor} allows us to decompose any admissible Wilson loop diagram into a collection of maximal exact subdiagrams, we are motivated to examine the matroid properties of exact subdiagrams more closely.
-In this section, we show prove two results:
+In this section, we prove two main results:
 \begin{enumerate}
-\item The matriod assoicated to an exact subdiagram of $W$ can be written as a contraction of the matroid $M(W)$ by the complementary propagator flat (Theorem \ref{exact diagrams contractions}). 
+\item The matroid assoicated to an exact subdiagram of $W$ can be written as a contraction of the matroid $M(W)$ by the complementary propagator flat (Theorem \ref{exact diagrams contractions}). 
 \item The matroid associated to an exact subdiagram is uniform (Theorem \ref{exactuniformthm} ).

### 2019-05-31 GWLDCII.tex
from Susama: Read through section 5. Added exposition. Have lots of questions.

@@
 
-The results of Section~\ref{sec GN algorithm} allow us to relate the position of propagators in a Wilson loop diagram $W$ to minors of $C(W)$, which we use in this section to understand the denominator of the integral $I(W)$ associated to a Wilson loop diagram (see Definition~\ref{def R(W)}).
+In this section, we investigate the poles of the integrand for $I(W)$, that is $R(W)$ as defined in Definition~\ref{def R(W)}.
+It is conjectured that for a fixed number of propagators and a given set of external twistors $\cZ$, [cite] \bas \sum_{W | |\cP| = k} I(W)(\cZ) <\infty \;.\eas In otherwords, all poles of the intergrals must cancel.
+As a step towards this, in this section, we prove some results about $R(W)$.
+
+The results of Section~\ref{sec GN algorithm} allow us to relate the position of propagators in a Wilson loop diagram $W$ to minors of $C(W)$, $R(W)$.
 
@@
 \begin{algorithm}\label{alg WLD to denom via GN}
-Let $W = (\cP,n)$ be a Wilson loop diagram, and let $C(W)$ be the matrix of $W$ as defined in \eqref{C(W) dfn} (see Section~\ref{section WLD background}).
+Let $W = (\cP,n)$ be a Wilson loop diagram, and let $C(W)$ be the matrix of $W$ as defined in \eqref{C(W) dfn} with a fixed ordering on $\cP$. (see Section~\ref{section WLD background}).
 \begin{itemize}
@@
 Write $I_{i}(p)$ for the vertex associated to propagator $p$ under this bijection.
-      \item Let $S_i = \{p \in \cP \ | \ I_{i-1}(p) \neq I_i(p)\}$. (By convention, set $I_{-1} = I_n$.)
+      \item Let $S_i = \{p \in \cP \ | \ I_{i-1}(p) \neq I_i(p)\}$. (By convention, set \hlfix{$I_{0} = I_n$}{changed. correct?}.)
 	  %\item Write $\Delta_{I_i}$ for the determinant of the $k \times k$ minor of $C(W)$ with columns indexed by $I_i$.
@@
 
+\hlfix{That is, each $r_i$ is the determinant of the minor determined by the propagators (rows) that contribute different values (columns) to the $i^{th}$ element of the Grassmann necklace than they did to the $i-1^{th}$.}{added.
+accurate?}
+
 As we discuss the algorithm it will also be useful to have the notation $\Delta_{I_i}$ for the determinant of the $k\times k$ minor of $C(W)$ with columned indexed by $I_i$.
@@
 As we take each $r_i$ to simply be the determinant of a particular submatrix of $C(W)$, the sign of each $r_i$ is well-defined.
-The goal is to show that $R$ is equal to the denominator of the Wilson loop diagram as defined in Definition~\ref{def R(W)}.
+Before proving the main results of this section, we given an illustrative example.
+Below, we show that $R$ is equal to the denominator of the Wilson loop diagram as defined in Definition~\ref{def R(W)}, and is the radical of the product $\prod_{i=1}^n \Delta_{I_i}$.
 %  However, we will not be interested in these signs as they only contribute an overall sign to $R$ and our main theorem in this section (Theorem~\ref{thm denom}) will simply be to show that $R$ is equal up to a $\mathbb{Q}$-multiple to the denominator of the Wilson loop diagram (see Definition~\ref{def R(W)}).
@@
 \begin{eg}
-Consider the Wilson loop diagram in Figure~\ref{fig R eg}. Assigning propagators $p$, $q$, $s$ to rows $1,2,3$ respectively, we obtain the matrix
+Consider the Wilson loop diagram in Figure~\ref{fig R eg}. Assigning propagators $p$, $q$, $s$\todo{$s = r$ in pictures} to rows $1,2,3$ respectively, we obtain the matrix
 \[
@@
 
-From $I_1$ to $I_2$, the propagators $p$ and $q$ change which vertex they are assigned to but $r$ is assigned to vertex 4 in both, so $S_2 = \{p,q\}$.  Then
+From $I_1$ to $I_2$, the propagators $p$ and $q$ change \hlfix{which vertex they are assigned to}{Can we change this language to which vertices they contribute?}.
+That is $I_1(p) = 1$, $I_1(q)= 2$ while $I_2(p) = 2$, $I_2(q)= 5$.
+However, $r$ contributes  4 to both $I_1$ and $I_2$, so $S_2 = \{p,q\}$.
+Then
 \[
 \Delta_{I_2}=\det\begin{bmatrix} b & 0 & 0 \\ f & 0 & g \\ j & k & l \end{bmatrix} = kgb, \qquad r_2 = \det\begin{bmatrix} b & 0 & 0 \\ f & 0 & g \\ 1 & 1 & 1 \end{bmatrix} = gb.
-\]
-where the 1s in the third row of the second matrix correspond to the fact that $I_1(s) = I_2(s)$.  Continuing likewise, we get $r_3 = c$, $r_4=1$ (since $I_4 = I_3$), $r_5 = lhd$, and $r_6 = i$.
-
-At $I_7$ the situation is more complicated: we have $S_7 = \{q,s\}$, so we find that $\Delta_{I_7} = d(ej-fi)$ and $r_7 = ej-fi$.
-This quadratic factor corresponds to the fact that $q$ and $s$ share an edge {\em and} contribute both endpoints of that edge to $I_7$; see Proposition~\ref{prop alg gives rad} below.
+\] {\color{violet} shouldn't $r_2$ be a $2 \times 2$ matrix? i.e. $r_2 = \det\begin{bmatrix} b & 0 \\ f &  g \end{bmatrix} = gb.$}
+\hlfix{where the 1s in the third row of the second matrix correspond to the fact that $I_1(s) = I_2(s)$.}{This doesn't seem to match with what is said in the algorithm.}  Continuing likewise, we get $r_3 = c$, $r_4=1$ (since $I_4 = I_3$), $r_5 = lhd$, and $r_6 = i$.
+
+At $I_7$ the situation \hlfix{is more complicated}{It seems to be exactly what we expect from the alg?}: we have $S_7 = \{q,s\}$ with $I_7(S_7) = \{ 1,2\}$, $\Delta_{I_7} = d(ej-fi)$ and $r_7 = ej-fi$.
+
+Note that unlike the previous $r_i$, $r_7$ an irriducible quadratic factor.
+This corresponds to the fact that $q$ and $s$ share an edge {\em and} contribute both endpoints of that edge to $I_7$; see Proposition~\ref{prop alg gives rad} below.
 
@@
 \end{eg}
+
+We are now ready to begin proving the main result of this section. We begin with a proposition stating several facts about $\Delta_{I_i}$ and their relationship to $r_i$.
 
@@
 Thus each $r_i$ is homogeneous.
-    \item Using the expression for the determinant as a sum over permutations we see that $\Delta_{I_i}$ is a sum over bijections between $I_i$ and $\mathcal{P}$.
+    \item Using the expression for the determinant as a sum over permutations from Lemma \ref{lem basis as perm} we see that $\Delta_{I_i}$ is a sum over bijections between $I_i$ and $\mathcal{P}$.
 The nonzero terms in this sum are precisely those bijections such that each propagator is associated to one of its supporting vertices in $I_i$, since only those locations in $C(W)$ are nonzero.
@@
 {\em Proof of claim}: By the structure of determinants we know that $\Delta_{I_i} = fg$, where $g$ involves only variables associated to propagators not in $\mathcal{P}'$ and associated to vertices not in $J$.
+\todo{Is the heart of this proof due to the fact that there are no cancelations?
+It feels tautological to me, but I'm clearly not following}
 
 Expanding out $fg$ yields a signed sum of monomials.
-In each of these monomials, $f$ contributes those variables associated both to a propagator in $\mathcal{P}'$ and to a vertex in $J$, and $g$ contributes those variables associated both to a propagator not in $\mathcal{P}'$ and to a vertex not in $J$, and no other variables appear.
+\hlfix{In each of these monomials, $f$ contributes those variables associated both to a propagator in $\mathcal{P}'$ and to a vertex in $J$, and $g$ contributes those variables associated both to a propagator not in $\mathcal{P}'$ and to a vertex not in $J$, and no other variables appear.
+}{Isn't this redundant with the previous paragraph?}
 
@@
 Suppose for a contradiction that $f$ is a factor of $\Delta_{I_i}$ of degree $\geq 3$.
-Note that by removing the propagators which come before those contributing to $f$ and changing $i$ to be the first vertex which contributes to $f$, we obtain a different admissible diagram for which $f$ still divides $\Delta_{I_i}$ but also $i\in I_i$ and
+Note that by removing the propagators which come \hlfix{before}{ordering?} those contributing to $f$ and \hlfix{changing $i$ to be the first vertex}{does this generalize to other $i$?} which contributes to $f$, we obtain a \hlfix{different admissible diagram}{Is this just the diagram gotten by removing certain props?} for which $f$ still divides $\Delta_{I_i}$ but also $i\in I_i$ and
 $i$ contributes to $f$.
@@
 
-Let $S$ be the set of propagators inside $p$ along with $p$ itself.
+Let $S = \cP_{in}(p)$ be the set of propagators inside $p$ in the $<_i$ order.
 $I_i$ and $I_{i+1}$ can only differ once $p$ contributes to $I_{i+1}$, so $I_i(q) = I_{i+1}(q)$ for each $q \in S \backslash \{p\}$.
@@
 
-If neither $m$ nor $m+1$ appear in $I_i$ then by Corollary~\ref{no coloops} $V(p) \cap I_i = \{i\}$, and so the row of $p$ in the matrix of $\Delta_{I_i}$ has only one nonzero entry; hence $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$, which is a contradiction.
+If neither $m$ nor $m+1$ appear in $I_i$ then by Corollary~\ref{no coloops} $V(p) \cap I_i = \{i\}$, and so the row of $p$ in the matrix of $\Delta_{I_i}$ has only one nonzero entry; hence $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$, which \hlfix{is a contradiction}{Why?
+because $i$ contributes to $f$?}.
 So we must have at least one of $m$ and $m+1$ in $I_i$.
@@
 Therefore $\Delta_{I_i} = \det A \det C$, and both factors are nontrivial since at least one of $m$ and $m+1$ appear in $I_i$.
-If we remove the propagator outside of $p$ that contributes $m$ or $m+1$, we get a smaller diagram for which $\Delta_{I_i} = \det A$.
+If we remove the propagator outside of $p$ that contributes $m$ or $m+1$, we get a smaller diagram for which $\Delta_{I_i} = \det A$ {\color{violet}why not $\det A \det C'$ with $C'$a minor of $C$?}.
 This contradicts the minimality of our choices unless $\det A$ is quadratic, which in turn contradicts our assumption that $i$ and $p$ contribute to an irreducible factor $f$ of degree at least 3.
@@
 Thus we can take $q$ to be the propagator such that $I_i(q)=i+1$.
-We know that $q$ has one end on the edge $(i, i+1)$ and is adjacent to $p$ on that edge in the counterclockwise direction (see Figure \ref{fig no big factors}).
+{\color{violet} How do we know this exists?
+Why can't we solve this by having $r$ supported on the $i-1^{th}$ edge?} We know that $q$ has one end on the edge $(i, i+1)$ and is adjacent to $p$ on that edge in the counterclockwise direction (see Figure \ref{fig no big factors}).
 Write $(i, i+1, j, j+1)$ for the support of $q$.
@@
 
-Similarly to Case 1, let $S$ be the set of propagators inside $q$ along with $p$ and $q$ themselves.
-Then all propagators in $S$ are mapped by $I_i(\cdot)$ to vertices strictly before $j$ and no other propagators are supported on vertices strictly before $j$.
-Thus the matrix giving $\Delta_{I_i}$ has the form
+Similarly to Case 1, let \st{$S$ be the set of propagators inside $q$ along with $p$ and $q$ themselves.}{\color{violet}$S = \cP_{in}(q)$ in the $<_i$ order.
+Note that $p \in S$.}\hlfix{Then all propagators in $S$ are mapped by $I_i(\cdot)$ to vertices strictly before $j$ and no other propagators are supported on vertices strictly before $j$.}{???}  Thus the matrix giving $\Delta_{I_i}$ has the form
 \[
@@
 For any fixed bijection $\sigma$ from $\cP-\{p,q\}$ to $I_i -\{a,b\}$ for which each propagator is supported on its image under the bijection, we can extend $\sigma$ to a bijection of all propagators with $I_i$ in two ways: either $p\mapsto a$ and $q\mapsto b$ or $p\mapsto b$ and $q\mapsto a$.
-The sum of the contributions of all these bijections to $\Delta_{I_i}$ is therefore the product of $x_{p,a}x_{q,b}-x_{p,b}x_{q,a}$ with the minor coming from $\cP-\{p, q\}$ and $I_i - \{a,b\}$.
+The sum of the contributions of all these bijections to $\Delta_{I_i}$ is therefore the product of \hlfix{$x_{p,a}x_{q,b}-x_{p,b}x_{q,a}$}{why?
+terms in determinant come from bijections.
+Why should all bijections appear in det?} with the minor coming from $\cP-\{p, q\}$ and $I_i - \{a,b\}$.
 Since there is no cancellation of terms in the expansion of $\Delta_{I_i}$, if any other terms appear then they will cause a factor which is not in the form described in the previous part.
@@
   Given any admissible Wilson loop diagram $W$, let $\{I_1, \ldots I_n\}$ be the associated Grasmann necklace.
-Then the denominator of the integral, $R(W)$ (see Definition~\ref{def R(W)}), is the $R$ of Algorithm~\ref{alg WLD to denom via GN}, which is also, up to scalar multiple, the radical of $\prod_{i=1}^n \Delta_{I_i}$, where $\Delta_{I_i}$ is the determinant of the $k \times k$ minor indicated by $I_i$.
+Then the denominator of the integral, $R(W)$ (see Definition~\ref{def R(W)}), is the $R$ of Algorithm~\ref{alg WLD to denom via GN}.
+Furthermore, the ideal generated by $R(W)$ is the radical of the ideal generated by $\prod_{i=1}^n \Delta_{I_i}$, where $\Delta_{I_i}$ is the determinant of the $k \times k$ minor indicated by $I_i$.
 \end{thm}
 
-\note{Note that there is still a mention of scalar multiple in this theorem because it seems to me that the def of radical is only up to scalar multiple, but the part relating $R(W)$ to $R$ is exact with no scalar multiples.}
+{\color{violet} Got rid of need for scalar multiples by talking about radicals.}
 
@@
 Therefore $R=R(W)$.
+\todo{I'm pretty sure that there isn't a sign issue here.
+But do we have a proof?}
 \end{proof}
 
-***explain why this result was interesting***
+Thus we have shown a deep relationship between the physically derived poles of the integrals $I(W)$ and the geometry and combinatorics associated to the diagrams $W$.
+At the very least, this is yet another piece of circumstantial evidence indicating that the positroid representation of Wilson loop diagrams is the correct geometric object to be considering when considering the Wilson loop amplitudes geometrically.
+
+While the authors cannot yet offer a proof that the appropriate sum of the Wilson loop diagrams are, in fact, finite, as conjectured [cite], we do hope that this relationship to the Grassmann Necklace elements will provide a different avenue for answering that and related questions.
 

### 2019-06-01 GWLDCI.tex
Sian continues to poke gently at paper 1

@@
 \item For $U \subseteq [n]$, write $\Prop(U) = \{ p \in \cP  \ | \ V(p) \cap U \neq \emptyset \} $ to denote the set of propagators which are at least partially supported on $U$.
-\item For $P \subseteq \cP$, define $F(P) = V(P^c)^c$ to be\footnote{Here, as throughout, we are using the superscript $c$ for the set theoretic complement.} the set of vertices in $[n]$ that do not support any propagators outside of the set $P$.
+\item For $P \subseteq \cP$, define the {\em propagator flat} $F(P) = V(P^c)^c$ to be\footnote{Here, as throughout, we are using the superscript $c$ for the set theoretic complement.} the set of vertices in $[n]$ that do not support any propagators outside of the set $P$.
+(This choice of terminology is justified in Lemma~\ref{lem facts about WLD matroids} below.)
 \item The set of vertices that do not support any propagators is denoted $F(\emptyset)$. Vertices in this set are called {\em non-supporting}.  
@@
 The key point to note is that the subgraph $t$ depends on how the propagators of $P$ sit inside $[n]$, not on how they sit in $W_P$ itself.
-In particular, $t$ is not the subgraph of $\tau(W)$ consisting only of edges corresponding to propagators of $P$ (as it may also include some of the outer edges of $\tau(W)$), nor is it the polygon dissection of $(P,V(P))$ (which would contain the extra vertices 5 and 9).
+In particular, $t$ is not the subgraph of $\tau(W)$ consisting only of edges corresponding to propagators of $P$ (as it may also include some of the outer edges of $\tau(W)$), nor is it the polygon dissection of $(P,V(P))$ viewed as a Wilson loop diagram in its own right (which would have vertex set equal to $V(P)$).
 \end{eg}
@@
 
-\note{sian note to self: reading/editing has reached this point}
 \subsection{Matroidal properties of exact subdiagrams \label{sec: exact diagram matroidal props}}
@@
 We begin by proving some useful facts about propagator flats, and flats of matroids associated to admissible Wilson loop diagrams more generally.
-
-\begin{comment}
-
-\begin{dfn}\label{def prop flat} 
-Let $W = (\cP,n)$ be an admissible Wilson loop diagram and $P \subseteq \cP$. The set $F(P) := V(P^c)^c$ is called the {\em propagator flat} of $P$.
-\end{dfn}
-Thus in Lemma \ref{contractsubdiaglem} above we would contract $M(W)$ by the propagator flat $F(P^c)$ of the {\em complement} of $P$ in order to study $(P,V(P))$.
+Recall from Definition~\ref{VPropdfn} that the propagator flat $F(P)$ of $P \subseteq \cP$ denotes the set $V(P^c)^c$ of vertices that do not support any propagators not in $P$.
+
+% \begin{comment}
+
+% \begin{dfn}\label{def prop flat} 
+% Let $W = (\cP,n)$ be an admissible Wilson loop diagram and $P \subseteq \cP$. The set $F(P) := V(P^c)^c$ is called the {\em propagator flat} of $P$.
+% \end{dfn}
+% Thus in Lemma \ref{contractsubdiaglem} above we would contract $M(W)$ by the propagator flat $F(P^c)$ of the {\em complement} of $P$ in order to study $(P,V(P))$.
 The justification for this notation is given by (1) of the next lemma: the set $F(P)$ consists of vertices which {\em only} support propagators in $P$ (or no propagators at all).
 
-\begin{lem}\label{lem properties of prop flats} \sanote{do we need the first 2? They follow directly from the definition 1.2. Do we use them later?}
-Let $F(P)$ be a propagator flat as defined above. Then
-\begin{enumerate}
-\item $F(\emptyset)$ is exactly the set of vertices which support no propagators, while for $P \neq \emptyset$ we have \[F(P) = \big(V(P) \setminus V(P^c)\big) \cup F(\emptyset).\] \note{updated (1) to match new definition of $F(P)$; }
-\item If $Q\subseteq P$ then $F(Q) \subseteq F(P)$.
-\item $F(P)$ is a flat of $M(W)$, thus justifying the name ``propagator flat''.
-\end{enumerate}
-\end{lem} \sanote{I'd like to attach this to the "generic facts about matroids" in lemma 2.2?}
-\begin{proof}
-The proof of (1) and (2) are routine applications of the definition and are omitted.
-
-To prove (3), we need to show that $F(P)$ is maximally dependent.
+% \begin{lem}\label{lem properties of prop flats} \sanote{do we need the first 2? They follow directly from the definition 1.2. Do we use them later?}
+% Let $F(P)$ be a propagator flat as defined above. Then
+% \begin{enumerate}
+% \item $F(\emptyset)$ is exactly the set of vertices which support no propagators, while for $P \neq \emptyset$ we have \[F(P) = \big(V(P) \setminus V(P^c)\big) \cup F(\emptyset).\] \note{updated (1) to match new definition of $F(P)$; }
+% \item If $Q\subseteq P$ then $F(Q) \subseteq F(P)$.
+% \item $F(P)$ is a flat of $M(W)$, thus justifying the name ``propagator flat''.
+% \end{enumerate}
+% \end{lem} \note{I'd like to attach this to the "generic facts about matroids" in lemma 2.2?}
+% \begin{proof}
+% The proof of (1) and (2) are routine applications of the definition and are omitted.
+
+% To prove (3), we need to show that $F(P)$ is maximally dependent.
 If $F(P) = [n]$ then this is automatic, so suppose not and let $v \in [n] \setminus F(P)$.
@@
 Thus $\rk(F(P) \cup\{v\}) = \rk(F(P)) + 1$, as required.
-\end{proof}
-
-\end{comment}
+% \end{proof}
+
+% \end{comment}
 
@@
 Let $v \in C$.
-Clearly $\Prop(v) \subseteq \Prop(C)$.
-Since $F(P)  = V(P^c)^c$, we have $F(\Prop(v)) \subseteq F(\Prop(C))$.
-Since $v \in F(\Prop(v))$ by the definition of propagator flat, we have $v \in F(\Prop(C))$, and so $C \subseteq F(\Prop(C))$.
+Clearly $\Prop(v) \subseteq \Prop(C)$, and hence $F(\Prop(v)) \subseteq F(\Prop(C))$ (this is easily verified by applying the definition and simplifying out all of the complements).
+Since $v \in F(\Prop(v))$ by the definition of propagator flat, it follows that $v \in F(\Prop(C))$.
+Thus $C \subseteq F(\Prop(C))$.
 
@@
 Let $B$ be an independent subset of $C$ of maximal rank; we first show that $B \cup \{w\}$ is a dependent set in $M(W)$.
-By Lemma \ref{lem facts about WLD matroids}, \bas |\Prop(C)| = \rk(C) = |B| = \rk(B) .\eas Since $\rk(B) \leq |\Prop(B)|$ and $B \subseteq C$ implies that  $\Prop(B) \subseteq \Prop(C)$, this implies that $\Prop(B) = \Prop(C)$.
-Furthermore, since $w \in F(Prop(C))$, we have $\Prop(B\cup w) \subseteq \Prop(B)$.
-By Lemma \ref{lem facts about WLD matroids}
+By Lemma \ref{lem facts about WLD matroids}, we have
+\begin{equation}\label{eq:equality in lem decompose flat} |\Prop(C)| = \rk(C) = |B| = \rk(B) .\end{equation}
+Since $\rk(B) \leq |\Prop(B)|$, and $B \subseteq C$ implies that  $\Prop(B) \subseteq \Prop(C)$, it follows that $\Prop(B) = \Prop(C)$.
+Combining this with the fact that $w \in F(\Prop(C))$, we have $\Prop(B\cup \{w\}) \subseteq \Prop(B)$.
+We can now say something about $\rk(B\cup \{w\})$: by Lemma \ref{lem facts about WLD matroids}, we have
 \[
-\rk (B \cup w) \leq \min\{|B\cup w|, |\Prop(B\cup w)|\},
+\rk (B \cup \{w\}) \leq \min\{|B\cup \{w\}|, |\Prop(B\cup \{w\})|\} \leq \min\{|B|+1,|Prop(B)|\},
 \]
-but $\rk (B\cup w) \leq \rk(C) = |B|$, and therefore $\rk (B \cup w) < |B\cup w|$.
-That is, $B\cup w$ contains a circuit containing $w$ and this circuit is in $F(\Prop(C))$.
-Therefore, $w \in C$, leading to a contradiction.
+which becomes 
+\[\rk(B\cup \{w\}) \leq \min\{|B|+1,|B|\} = |B| < |B \cup\{w\}|\]
+via equation \eqref{eq:equality in lem decompose flat}.
+Therefore $B\cup\{w\}$ is a dependent set, which implies that $B\cup \{w\}$ contains a circuit $D$.
+We must have $w \in D$ (since $B$ was an independent set), and \hlfix{$D \subseteq F(\Prop(C))$}{I know we've talked about this before and I can't remember why this is true} $\subseteq F$.
+Since $C$ was the union of all circuits in $F$, we finally obtain $w \in C$, which is a contradiction.
+This completes the proof of (1).
 
@@
 
-If $F(\emptyset) = \emptyset$, for any $e \not\in F$, we certainly have $\rk((F\setminus C)\cup\{e\}) = \rk(F\setminus C) +1$ since $F$ is a flat.
+Now suppose that $F(\emptyset) = \emptyset$; we must show that $F\setminus C$ is a flat.
+For any $e \not\in F$ we certainly have $\rk((F\setminus C)\cup\{e\}) = \rk(F\setminus C) +1$, since $F$ is a flat.
 Now let $e \in C$, and suppose that $\rk((F\setminus C)\cup\{e\}) = \rk(F\setminus C)$.
-This implies that $(F\setminus C)\cup \{e\}$ is dependent, and hence contains a circuit, $S$.
-Since $F(\emptyset) = \emptyset$, this circuit must contain at least two elements but this contradicts the fact that $C$ was the union of all circuits in $F$.
+This implies that $(F\setminus C)\cup \{e\}$ is dependent, and hence contains a circuit.
+Since $F(\emptyset) = \emptyset$ this circuit must contain at least two elements: one of these elements is $e$, but any others must come from $F \setminus C$.
+This contradicts the fact that $C$ was the union of all circuits in $F$.
 
@@
 \begin{cor} \label{classifyflats}
-  If $F$ is a flat of an admissible Wilson loop diagram, it can be written as the disjoint union of a cyclic propagator flat and an independent set: \bas F =C \sqcup S \eas where $C$ the union of all circuits in S.
+  If $F$ is a flat of an admissible Wilson loop diagram, it can be written as the disjoint union of a cyclic propagator flat and an independent set: \bas F =C \sqcup S \eas where $C$ the union of all circuits in $F$.
 \end{cor}
@@
 \begin{proof}
-By Lemma \ref{lem decompose flat}, the set $C$ is a propagator flat. Furthermore, $S = F \setminus C$, which is independent.
+By Lemma \ref{lem decompose flat} the set $C = F(\Prop(C))$ is a propagator flat, and $S := F \setminus C$ is independent.
 \end{proof}
@@
 Let $W = (\cP, [n])$ be an admissible Wilson loop diagram, and $P \subseteq \cP$. Then: \begin{enumerate}
-\item If $(P,V(P))$ is an exact subdiagram in $W$, then $F(P^c)$ is not an independent flat.
+\item If $(P,V(P))$ is an exact subdiagram in $W$, then $F(P^c)$ is a dependent flat.
 \item If $(P,V(P))$ is a maximal exact subdiagram in $W$, then $F(P^c)$ is a cyclic flat.
@@
 
-First note that if $(P,V(P))$ is exact then the admissiblity of $W$ guarantees that $F(P^c)$ is a non-empty flat. That is, $V(P) \subsetneq [n]$.
-
-Since $W$ is admissible, we have $n \geq |\cP| + 4$. Rewriting this as
+First note that if $(P,V(P))$ is exact then the admissiblity of $W$ guarantees that $V(P) \neq [n]$, so $F(P^c) = V(P)^c$ is not empty.
+
+We know from Lemma~\ref{lem facts about WLD matroids} that $F(P^c)$ is always a flat, so for part (1) we only need to show that $F(P^c)$ is dependent.
+
+Since $W$ is admissible, we have $n \geq |\cP| + 4$. Rewriting this inequality as
 \[|V(P)| + |F(P^c)|  \geq  |P| + |P^c| +4,\]
@@
 \begin{equation}\label{eq F is dependent}|F(P^c)| > |P^c| \;.\end{equation}
-Equation \eqref{eq F is dependent} is therefore saying that $F(P^c)$ supports fewer propagators than the number of vertices it contains, i.e. $F(P^c)$ is not an independent set.
+Equation \eqref{eq F is dependent} implies that $F(P^c)$ supports fewer propagators than the number of vertices it contains, i.e. $F(P^c)$ is not an independent set.
 
@@
 
-Since $S$ is an independent set, $\rk(S) = |S|$, and every element of $S$ is independent of $C$, $\rk\big(F(P^c)\big) = \rk(C) + \rk(S)$.
-By Lemma \ref{lem facts about WLD matroids}(1), \ba \rk(S) = \rk\big(F(P^c)\big) -  \rk(C) \leq |P^c| - \rk(C) \;.
+By similar arguments to Lemma~\ref{lem decompose flat}, the fact that $S$ is independent and that $C$ is the union of all circuits in $F(P^c)$ implies that every element of $S$ is independent of $C$, and therefore ${\rk\big(F(P^c)\big) = \rk(C) + \rk(S)}$.
+We also know that $\rk(S) = |S|$, by the independence of $S$.
+Combining these with Lemma~\ref{lem facts about WLD matroids}(1), we get \ba |S| = \rk(S) = \rk\big(F(P^c)\big) -  \rk(C) \leq |P^c| - \rk(C) \;.
 \label{increasingrank} \ea
 
-Let $Q^c = \Prop(C)$.
-The goal will be to show that $Q=P$ and hence that $S=0$ so $F(P^c)$ is a cyclic flat.
-From the definition of $Q$, we obtain $C = F(Q^c)$ and, by Lemma \ref{lem facts about WLD matroids}(2), $\rk(C) = |Q^c|$.
-By equation \eqref{increasingrank}, \ba |P| + |S| \leq |P| + |P^c| - \rk(C) = |\cP| - |Q^c| = |Q| \;.
-\label{Qsizebound}\ea From equation \eqref{eq decompose F}, \bas V(P) \sqcup S = C^c = F(\Prop(C))^c = F(Q^c)^c = V(Q) \;.
-\eas Combining this with equation \eqref{increasingrank} gives \ba |V(Q)| = | V(P) | + |S| = | P | + 3 + |S| \leq |Q| +3 \;.
-\label{Q defines exact}\ea Since $W$ is admissible, one must have $|V(Q)| = |Q| +3$, that is the subdiagram $(Q, V(Q))$ is exact.
-
-Next, note that \bas C = F(Q^c) = V(Q)^c \subseteq F(P^c) = V(P)^c \;,\eas which implies that $P \subseteq Q$.
-That is, $(P, V(P))$ is a subdiagram of $(Q, V(Q))$.
-Since $(P, V(P))$ is maximally exact by hypothesis, and $(Q, V(Q))$ is exact by \eqref{Q defines exact}, we are forced to have $S = \emptyset$.
-Therefore, $F(P^c)$ is a cyclic flat.
-
-To see (3), first note that the second point of this Lemma, combined with Lemma \ref{lem facts about WLD matroids} gives that
-\bas\rk(F(P^c)) = |\Prop(F(P^c))| = |P^c|\eas
-in the case that $(P, V(P))$ is maximal exact.
-
-To prove the result in the general case, let let $(R,V(R))$ be an exact subdiagram that is not maximal and $P$ be the maximal exact subdiagram containing it. That is, $R \subsetneq P$.
-
-Since $R \subset P$, $V(P) = V(R) \sqcup S$, where $S = V(P) \setminus V(R)$.
-Since $P$ and $R$ both define exact subdiagrams, we may write $|V(P)| = |V(R)| + |P \setminus R|$, and we have that $S$ is a vertex set of size $|P \setminus R|$.
-Furthermore, $F(R^c) = F(P^c) \sqcup S$.
+Define $Q = \Prop(C)^c$. We will show that $Q=P$, which will imply that $S=\emptyset$ and that ${F(P^c) = F(Q^c) = F(\Prop(C))}$ is a cyclic flat.
+
+From the definition of $Q$ we obtain $C = F(Q^c)$, and, by Lemma \ref{lem facts about WLD matroids}(2), it follows that $\rk(C) = |Q^c|$. By equation \eqref{increasingrank}, we obtain
+\ba |P| + |S| \leq |P| + |P^c| - \rk(C) = |\cP| - |Q^c| = |Q| \;. \label{Qsizebound}\ea 
+Meanwhile, from equation \eqref{eq decompose F} we have
+\bas V(P) \sqcup S = C^c = F(\Prop(C))^c = F(Q^c)^c = V(Q) \;. \eas
+Combining this with equation \eqref{Qsizebound} gives 
+\ba |V(Q)| = | V(P) | + |S| = | P | + 3 + |S| \leq |Q| +3 \;. \label{Q defines exact}\ea
+Since $W$ is admissible this cannot be a strict inequality, so we have $|V(Q)| = |Q| +3$ and the subdiagram $(Q, V(Q))$ is exact.
+
+Finally, note that 
+\bas C = F(Q^c) = V(Q)^c \subseteq F(P^c) = V(P)^c \;,\eas
+where the $\subseteq$ follows from equation~\eqref{eq decompose F}.
+This implies that \hlfix{$P \subseteq Q$}{sian should go look up why this is true}, and hence $(P, V(P))$ is a subdiagram of $(Q, V(Q))$.
+Since $(P, V(P))$ is maximally exact by hypothesis, and $(Q, V(Q))$ is exact by equation \eqref{Q defines exact}, we must have $P = Q$.
+Therefore $S = \emptyset$ and $F(P^c)$ is a cyclic flat.
+
+To see (3), first note that when $(P,V(P))$ is maximal exact, part (2) of this lemma combined with Lemma \ref{lem facts about WLD matroids} gives that
+\bas\rk(F(P^c)) = |\Prop(F(P^c))| = |P^c|.\eas
+
+To prove the result in the general case, let $(R,V(R))$ be an exact subdiagram of $W$ that is not maximal and let $P$ be the maximal exact subdiagram containing it. That is, $R \subsetneq P$.
+
+Since $R \subsetneq P$ we can write 
+\begin{equation}\label{eq: relate P and R diagrams}V(P) = V(R) \sqcup S, \quad \text{ where } S := V(P) \setminus V(R).\end{equation}
+Since $P$ and $R$ both define exact subdiagrams, it follows that $|V(P)| = |V(R)| + |P \setminus R|$, and hence that $S$ is a vertex set of size $|P \setminus R|$.
+Furthermore, by taking complements of both sides of equation~\eqref{eq: relate P and R diagrams}, we see that $F(R^c) = F(P^c) \sqcup S$.
+
 We will show that $S$ is an independent set in the subdiagram $(P, V(P))$, and thus in $W$.
-Supposing for the moment that $S$ is independent in $(P, V(P)$ this implies that for any maximal independent set $\mathfrak{B} \subset F(P^c)$, the set $\mathfrak{B} \sqcup S$ is independent in $F(R^c)$.
-Therefore, \bas \rk (F(R^c)) \geq |\mathcal{B}| + |S| = \rk (F(P^c)) + |S| = |P^c| + |P\setminus R| = |R^c|  \;.\eas By Lemma \ref{lem facts about WLD matroids}, $\rk (F(R^c)) \leq |R^c|$.
-Thus $\rk (F(R^c)) = |R^c|$ as desired.
-
-It remains to show that $S$ is an independent set in the subdiagram $(P, V(P))$.
-Suppose not.
-Then, by Theorem \ref{thm WLD defines matroid} there is a subset $U \subseteq S$ such that $|\Prop(U)| < |U|$.
-Then the remaining propagators, $P \setminus \Prop(U)$ are supported entirely on $V(P) \setminus U$.
-That is \bas  V(P \setminus \Prop(U)) = V(P) \setminus U\; .\eas Comparing sizes of these sets, we get \bas |V(P \setminus \Prop(U))| = |V(P)| - |U| = |P| +3 -|U| > |P| +3 -|\Prop(U)| = |P \setminus \Prop(U)| +3\; ,\eas which violates admissibility.
-Therefore, $S$ is independent in $(P, V(P))$.
+This will imply that for any maximal independent set $T \subseteq F(P^c)$, the set $T \sqcup S$ is independent in $F(R^c)$, and hence that
+\bas \rk (F(R^c)) \geq |T| + |S| = \rk (F(P^c)) + |S| = |P^c| + |P\setminus R| = |R^c|  \;.\eas 
+The reverse inequality $\rk (F(R^c)) \leq |R^c|$ always holds (see Lemma \ref{lem facts about WLD matroids}), so if $S$ is independent in $(P,V(P))$ we obtain $\rk (F(R^c)) = |R^c|$ as desired.
+
+It remains to show that $S$ is an independent set in the subdiagram $(P, V(P))$, so for a contradition suppose otherwise.
+Then by Theorem \ref{thm WLD defines matroid} there is a subset $U \subseteq S$ such that $|\Prop(U)| < |U|$.
+Then the remaining propagators $P \setminus \Prop(U)$ are supported entirely on $V(P) \setminus U$, i.e.
+\bas  V(P \setminus \Prop(U)) \subseteq V(P) \setminus U\; .\eas Comparing sizes of these sets, we get \bas |V(P \setminus \Prop(U))| \leq |V(P)| - |U| = |P| +3 -|U| < |P| +3 -|\Prop(U)| = |P \setminus \Prop(U)| +3\; ,\eas which violates admissibility.
+Therefore $S$ must be independent in $(P, V(P))$ after all, and (as described above) it follows that $\rk(F(R^c)) = |R^c|$.
 
@@
 
-We are now ready to show that any exact subdiagram $(P, V(P)$ of $W$ can be written as a contraction of $M(W)$ by $F(P^c)$. We begin with a definition.
+We are now in a position to describe the matroid structure of exact subdiagrams $(P, V(P))$ of $W$ in terms of $M(W)$ and $F(P^c)$. We begin with a definition.
 
@@
 
+Putting all of this together, we obtain our first major theorem of this section:
+
 \begin{thm} \label{exact diagrams contractions}
-If $(P, V(P)$ is an exact subdiagram of of $W$, one may write \bas M\big((P, V(P))\big) = M(W)  / F(P^c) \;.\eas 
+If $(P, V(P)$ is an exact subdiagram of of $W$, the matroid of $(P,V(P))$ is the contraction of $M(W)$ by the propagator flat $F(P^c)$, i.e. \bas M\big((P, V(P))\big) = M(W)  / F(P^c) \;.\eas 
 \end{thm}
@@
 
-\begin{rmk} \label{remark exact dual restiction}
-Let $M^*$ denote the dual of a matroid.
-The the dual of a contraction of a matroid is the same as the restriction of the dual matroid by the complement: \bas M / S = M^*|_{S^c} \;.\eas Then Theorem \ref{exact diagrams contractions} implies that, for $(P, V(P))$ an exact subdiagram of $W$ \bas M\big((P, V(P))\big) = M(W)  / F(P^c) = M(W)^*|_{V(P)} \;.\eas
+\begin{rmk} \label{remark exact dual restiction} For readers familiar with duals and complements of matroids, we reinterpret Theorem~\ref{exact diagrams contractions} in these terms.
+If $M^*$ denotes the dual of a matroid, then by standard matroid theory \hlfix{[ref]}{if we're not going to define them here (and we really shouldn't!) then it's probably polite to give a reference} the dual of a contraction of a matroid is the same as the restriction of the dual matroid by the complement: \bas M / S = M^*|_{S^c} \;.\eas Then Theorem \ref{exact diagrams contractions} implies that, for $(P, V(P))$ an exact subdiagram of $W$, we have \bas M\big((P, V(P))\big) = M(W)  / F(P^c) = M(W)^*|_{V(P)} \;.\eas
 \end{rmk}
 
-Matroids coming from exact subdiagrams have an especially nice structure, namely, they are uniform.
+We now show that matroids coming from exact subdiagrams have an especially nice structure, namely, they are uniform.
 Recall from Section \ref{sec matroid background} that a uniform matroid of rank $r$ is one in which all sets of size $ \leq r$ are independent.
+
+\note{sian note to self: editing has reached this point}
 
@@
 \subsection{Matroids and equivalent diagrams \label{sec: matroids and equivalence}}
-\note{Si\^an postponed reading this section until the earlier ones are fixed.}
+
 Now we are ready to prove the main results of this section, namely that two Wilson loop diagrams define the same matroid if and only if they are equivalent (Theorem \ref{same matroid iff equiv}).

### 2019-06-03 GWLDCII.tex
Susama: xposition about integrals added to section 2

@@
 
-Due to the physical motivation behind these diagrams, we can associate a matrix $C(W)$ to each Wilson loop diagram $W$, which is defined elementwise by
+These diagrams correspond to (tree level) amplitudes of SYM N=4 theory in twistor space.
+As such, it associates a real value to $n$ particles, one for each vertex.
+Each particle is represented as a section of a $|\cP|$-vector bundle over twistor space, projected onto a real subspace in a process called bosonization \cite{Arkani-Hamed:2013jha}.
+In otherwords, each Wilson loop diagram defines a functional on external particles.
+This is represented as an integral $I(W)$, which is the equalent of a Feynman integral in this setting.
+
+A $n \times |\cP|$ matrix $C(W)$ represents the (tree level) particle interactions.
+Each row of $C(W)$ corresponds to an internal propagator, each column to an external particle.
+Each row only has zero entries on every external particle it does not interact with.
+In particular,
 
@@
 0  & \textrm{ if } q \not \in V(p)  \end{cases}
-\;. \label{C(W) dfn}\end{equation}
+\;. \label{C(W) dfn}\end{equation} \todo{$c_{p,q}$ or $x_{p,q}$? Should be consistent}
 
 The entries $c_{p,q}$ are non-zero real variables.
-The columns of $C(W)$ correspond to the vertices of $W$ listed in their linear order, and the rows correspond to the propagators of $W$.
-$C(W)$ is therefore only defined up to rearrangement of the rows, which will not matter in this setting since we will only interpret it as parametrizing a family of elements of the $|\cP| \times |V|$ real Grassmannian.
-
-\begin{eg}
+This matrix can be interpreted as a parametrization of the positroid cell in the positive Grassmannian $\Gr(n, |\cP|)$ assoiciated to the $W$, call it $\Sigma(W)$ \cite{wilsonloops}.
+Most of the work in this paper, and in \cite{GWLDI} focuses on characterizing the positroid cell assoicated to eash Wilson loop diagram $W$.
+An example of $C(W)$ is given in example \ref{integraldetails}.
+
+Note that, since there is no ordering on the propagators of $W$, $C(W)$ is only defined up to rearrangement of the rows.
+This will not matter as this does not effect the parametrization of $\Sigma(W)$.
+
+One may also interpret functional $I(W)$ as a associating a volume to each $\Sigma(W)$ \cite{wilsonloops, AmplituhedronSquared, HeslopStewart}.
+The volume form is written in terms of the elements of $C(W)$as  \[ \Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V_{p_r}} \textrm{d}c_{p_r}}{R(W)} \;.
+\]
+The interested reader is referred to \cite{Adamo:2012xe,HeslopStewart,LipsteinMason} for more information about the volume form.
+
+For a fixed number of propagators and particles, the tree level amplitude of the Wilson loop diagrams is finite \cite{Adamo:2011pv,Adamo:2012xe,Arkani-Hamed:2013jha}: \bas \mathcal{A}_{k, n}^{tree} = \sum_{(\cP, [n]), |\cP| = k} I(W) <\infty \eas for all sets of external particles.Therefore, any singularities in the integral $I(W)$ must cancel in the sum.
+In particular, they must cancel on the boundaries of the positroid cells $\Sigma(W)$, analogous to the analysis in \cite{Arkani-Hamed:2013jha}.
+This has been checked for particular classes of examples, \cite{casestudy, AmplituhedronSquared, HeslopStewart}, but has not been proven in general.
+
+In this paper, we consider the denominator $R(W)$, which we define next.
+
+\begin{dfn}\label{def R(W)}
+Let $W = (\cP,V)$ be an admissible Wilson loop diagram, and fix an edge $e$.
+Let $\{p_1 \ldots p_r\}$ be the propagators with one end lying on edge $e$, ordered so that $p_1$ is closest to the vertex $e$, $p_r$ closest to $e+1$, and $p_i$ is closer to $e$ than $p_{i+1}$ is.
+Define
+\[ R_e =  c_{p_1,e+1} \prod_{j= 1}^{r-1} \left((c_{p_j,e} c_{p_{j+1},e+1} - c_{p_{j+1},e} c_{p_{j},e+1} ) \right) c_{p_r,e}\;\]
+to be the component of $R(W)$ associated to edge $e$.
+Note that if $r = 1$ (i.e.
+there is exactly one propagator lying on edge $e$) then this expression simplifies to $R_e = c_{p,e} c_{p,e+1}$.
+If $r=0$, set $R_e = 1$.
+The denominator $R(W)$ is defined to be the product of all of the $R_e$, i.e.
+\[R(W) = \prod_{e \in V} R_e.\]
+\end{dfn}
+
+In section \ref{sec poles}, we show that the denominator $R(W)$ is determined by the positroid cell $\Sigma(W)$ the structure of $W$, as encapulated by $C(W)$.
+In fact, it can be read directly off of $C(W)$, given a characterizeation of $\Sigma(W)$ called the Grassmann necklace.
+We also give an algorithm to read $R(W)$ directly from the Wilson loop diagram, paving the way for a general study of these poles in future.
+
+We end this section with an example illustration $C(W)$ $R(W)$.
+
+\begin{eg} \label{integraldetails}
 Consider the admissible Wilson loop diagram 
@@
 \right) \;.\]
+
+To calculate $R(W)$, write \bmls R_1 = c_{1,1} c_{1, 2}\quad R_2 = c_{2,2} c_{2,3} \quad R_4 = c_{2,5} (c_{2,4}c_{1,5} - c_{2,5}c_{1,4})c_{1,4} \\ R_5 = c_{4,6} (c_{4,6}c_{3,5} - c_{3,6}c_{4,5})c_{3,5} \quad R_7 = c_{3,7} c_{3,8} \quad R_8 = c_{4,8} c_{4,1} \;.\emls All other $R_e$ are $1$.
+Finally, the integran associated to this Wilson loop diagram is \bas \Omega(W) = \frac{\textrm{d}c_{1,1}\textrm{d}c_{1,1}\textrm{d}c_{1,1}\textrm{d}c_{1,2}\textrm{d}c_{1,4}\textrm{d}c_{1,5}\textrm{d}c_{2,1}\textrm{d}c_{2,3}\textrm{d}c_{2,4}\textrm{d}c_{2,5}\textrm{d}c_{3,5}\textrm{d}c_{3,6}\textrm{d}c_{3,7}\textrm{d}c_{3,7}\textrm{d}c_{4,5}\textrm{d}c_{4,6}\textrm{d}c_{4,8}\textrm{d}c_{4,1}}{c_{1,1} c_{1, 2}c_{2,2} c_{2,3}c_{2,5} (c_{2,4}c_{1,5} - c_{2,5}c_{1,4})c_{1,4}c_{4,6} (c_{4,6}c_{3,5} - c_{3,6}c_{4,5})c_{3,5}c_{3,7} c_{3,8}c_{4,8} c_{4,1}} \;.
+\]\eas
 \end{eg}
-
-The Wilson loop diagram also defines a volume form on $\Sigma(W)$, namely 
-\[ \Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V_{p_r}} \textrm{d}c_{p_r}}{R(W)} \;. \]
-The interested reader is referred to \cite{Adamo:2012xe,HeslopStewart,LipsteinMason} for more information about the volume form.
-Of interest to us in this paper is the denominator $R(W)$, which we define next.
-
-\begin{dfn}\label{def R(W)}
-Let $W = (\cP,V)$ be an admissible Wilson loop diagram, and fix an edge $e$.
-Let $\{p_1 \ldots p_r\}$ be the propagators with one end lying on edge $e$, ordered so that $p_1$ is closest to the vertex $e$, $p_r$ closest to $e+1$, and $p_i$ is closer to $e$ than $p_{i+1}$ is.
-Define
-\[ R_e =  c_{p_1,e+1} \prod_{j= 1}^{r-1} \left((c_{p_j,e} c_{p_{j+1},e+1} - c_{p_{j+1},e} c_{p_{j},e+1} ) \right) c_{p_r,e}\;\]
-to be the component of $R(W)$ associated to edge $e$.
-Note that if $r = 1$ (i.e.
-there is exactly one propagator lying on edge $e$) then this expression simplifies to $R_e = c_{p,e} c_{p,e+1}$.
-The denominator $R(W)$ is defined to be the product of all of the $R_e$, i.e.
-\[R(W) = \prod_{e \in V} R_e.\]
-\end{dfn}
-We expect the volume form associated to the tree amplitudes to be finite \cite{Adamo:2011pv,Adamo:2012xe,Arkani-Hamed:2013jha}.
-Therefore, we expect that the singularities of $\Omega(W)$ will cancel on the boundaries of the simpleses the diagrams define, analogous to the analysis in \cite{Arkani-Hamed:2013jha}.
-While there has been work in this area in special cases \cite{Amplituhedronsquared,HeslopStewart,casestudy} there has not been a systematic study of the pole structure of these integrals.
-
-In Section~\ref{sec poles} we give a simple algorithm to read $R(W)$ directly from the Wilson loop diagram, paving the way for a general study of these poles in future.
 
@@
 Burkhard Eden, Paul Heslop, and Lionel Mason.
-\newblock The correlahedron.
+\newblock The AmplituhedronSquared.
 \newblock 2017.

### 2019-06-06 GWLDCI.tex
continuing minor edits to paper 1

@@
 
-\note{sian note to self: editing has reached this point}
-
 \begin{thm} \label{exactuniformthm}
@@
 
-We prove the following claim: $W'$ is exact if and only if $V(P)$ contains no circuits $C$ with $\rk C< |P|$ in $(P, V(P))$. Since $\rk(M(W'))$ is bounded above by $|P|$, the result follows.
-
-Suppose $C \subseteq V(P)$ is a circuit of rank $m < |P|$.
-By Lemma \ref{lem facts about WLD matroids}, we know that $|\Prop_{W'}(C)| = m$ as well, where the subscript to $\Prop$ specifies the diagram we are working in.
-Observe that $\Prop_{W'}(C)\subseteq P$ by definition.
-The set $P \setminus \Prop_{W'}(C)$ is thus nonempty, and we can consider the subdiagram $W'':= (P\setminus \Prop_{W'}(C),V(P\setminus\Prop_{W'}(C))$.
+We prove the following claim: $W'$ is exact if and only if $V(P)$ contains no circuits $C$ with $\rk (C)< |P|$ in $(P, V(P))$. Since $\rk(M(W'))$ is bounded above by $|P|$, the result follows.
+
+First suppose $C \subseteq V(P)$ is a circuit of rank $m < |P|$.
+Observe that $\Prop_{W'}(C)\subseteq P$ by definition, where the subscript to $\Prop$ specifies the diagram we are working in.
+By Lemma \ref{lem facts about WLD matroids} we know that ${|\Prop_{W'}(C)| = m}$; thus the set $P \setminus \Prop_{W'}(C)$ must be nonempty, and we can consider the subdiagram $W'':= (P\setminus \Prop_{W'}(C),V(P\setminus\Prop_{W'}(C))$.
 By the density condition on subdiagrams of admissible diagrams, we have
 \[|V(P\setminus\Prop_{W'}(C))| \geq |P\setminus\Prop_{W'}(C)| + 3.\]
-It is easy to verify that $V(P\setminus\Prop_{W'}(C)) \subseteq V(P)\setminus C$; since $C \subseteq V(P)$ and $\Prop_{W'}(C) \subseteq P$, we can therefore rewrite the previous inequality as
+It is easy to verify that $V(P\setminus\Prop_{W'}(C)) \subseteq V(P)\setminus C$. Since $C \subseteq V(P)$ and $\Prop_{W'}(C) \subseteq P$, it follows from the previous inequality that
 \[|V(P)| - (m+1) \geq |V(P\setminus\Prop(C))| \geq |P| - m + 3.\]
@@
 Then $|V(P)\setminus V(p)| = |V(P)| - 4 \geq |P|$ by non-exactness.
-By uniformity there is an independent set of size $|P|$ in $V(P)\setminus V(p)$.
-This is impossible because the submatrix corresponding to this independent set has $|P|$ rows but the one corresponding to $p$ is all $0$ one of them is all 0 so it cannot be full rank.
+By uniformity there must be an independent set of size $|P|$ in $V(P)\setminus V(p)$.
+However, this is impossible because the submatrix of $C(W')$ corresponding to this independent set has $|P|$ rows but the one corresponding to $p$ is all $0$, so it cannot be full rank.
 %suppose that $(P,V(P))$ is not exact, i.e. $|V(P)| \geq |P| +4$. We have 
@@
 \begin{dfn}
-Given a Wilson loop diagram $W = (\cP, [n])$, define the positroid cell associated to a Wilson loop diagram, $\Sigma(W)$, to be the cell in the CW complex on $\Gr(|\cP|, n)$ defined by the positroid $M(W)$.
+Given a Wilson loop diagram $W = (\cP, [n])$ and its associated positroid $M(W)$, let $\Sigma(W)$ denote the corresponding positroid cell in the CW complex on $\Gr(|\cP|, n)$.
 \end{dfn}
@@
 We also
-give a formula for the number of Wilson loop diagrams in a given equivalence class (Corollary \ref{number of equiv diagrams}), completing the characterization of the correspondence between Wilson Loop diagrams and matroids starting in \cite{wilsonloop}.
+give a formula for the number of Wilson loop diagrams in a given equivalence class (Corollary \ref{number of equiv diagrams}), completing the characterization of the correspondence between Wilson loop diagrams and matroids starting in \cite{wilsonloop}.
 
@@
 
-In this section we have characterized the correspondence between Wilson loop diagrams and positroids, showing that Wilson Loop diagrams define the same matroid if and only if they are equivalent (Theorem \ref{same matroid iff equiv}).
-Corollary \ref{number of equiv diagrams} enumerates the fibres of the map from Wilson Loop diagrams to positroids.
-The obvious next question would be to enumerate the number of equivlence classes.
-We do not obtain a formula for this, but do obtain an alternate characterization of the equvalence classes which is the subject of the next section.
+The obvious next step would be to enumerate the number of equivalence classes.
+We do not obtain a formula for this, but in the next section we give an alternate characterization of the equivalence classes in terms of faces in associahedra.
 
@@
 
-A \emph{polytope} can equivalently be defined as the convex hull of a finite set of points in some $\mathbb{R}^d$ or as the intersection of finitely many closed half spaces in $\mathbb{R}^d$ with the additional property that this intersection is bounded in the sense of not containing any ray (see chapter 0 of \cite{Ziegler}).
+We first give a quick summary of the polytope terminology we will use in this section; the interested reader is referred to \cite{Ziegler} for more details.
+
+A \emph{polytope} can equivalently be defined as the convex hull of a finite set of points in some $\mathbb{R}^d$, or as the intersection of finitely many closed half spaces in $\mathbb{R}^d$ with the additional property that this intersection is bounded in the sense of not containing any ray (see chapter 0 of \cite{Ziegler}).
 
 A \emph{face} of a polytope is the intersection of the polytope with any hyperplane for which the entire polytope is in one of the closed half-spaces defined by the hyperplane.
-The polytope itself is also considered a face (in the case that that polytope is of full dimension, this definition can be unified by considering linear equalities (including the trivial one) in place of hyperplanes and the corresponding linear inequalities in place of the half-spaces defined by the hyperplane, see chapter 2 of \cite{Ziegler}).
+The polytope itself is also considered a face; in the case that that polytope is of full dimension, this definition can be unified by considering linear equalities (including the trivial one) in place of hyperplanes and the corresponding linear inequalities in place of the half-spaces defined by the hyperplane (see chapter 2 of \cite{Ziegler}).
+
 Two faces are \emph{parallel} if one can be mapped to the other by a translation in $\mathbb{R}^d$.
@@
 
-There are many important polytopes in combinatorics, including, of primary importance to us, the associahedron.
-
-Two polytopes are \emph{combinatorially equivalent} if there is a bijection between their faces which preserves inclusion of faces.
+Finally, two polytopes are \emph{combinatorially equivalent} if there is a bijection between their faces which preserves inclusion of faces.
 Often in combinatorics one is primarily interested in the combinatorial equivalence classes, and common names, including the associahedron, refer to these equivalence classes.
@@
 
-Associahedra can also be viewed in terms of polygon dissections.
+There are many important polytopes in combinatorics, including, of primary importance to us, the associahedron. The associahedron can be characterized in many different ways; here is one definition.
+
+\begin{dfn}\label{def:associahedron}
 Fix $n$ and consider dissections of a convex $n$-gon.
-The $n-1$ asociahedron can be given in terms of the dissections of this $n$-gon; the vertices of the associahedron are the triangulations of the $n$-gon while the dimension $k$ faces are the dissections which are $k$ diagonals away from being a triangulation.
+The $n-1$ {\em associahedron} can be given in terms of the dissections of this $n$-gon; the vertices of the associahedron are the triangulations of the $n$-gon while the $k$-dimensional faces are the dissections which are $k$ diagonals away from being a triangulation.
 One face is included in another if the first dissection is a refinement of the second.
+\end{dfn}
 
 It turns out that this defines a class of combinatorially equivalent polytopes, which can be proved by giving a realization.
-There are many interesting realizations of the associahedron \cite{CSZinequivalent}; the following will be the one which we will use.
-See Figure~\ref{associahedron5gon} for examples.
-
-\begin{dfn}
-  Let $x_1, \ldots, x_n$ define a convex $n$-gon.
-Let $T$ be the set of triangulations of this $n$-gon.
+There are many interesting realizations of the associahedron \cite{CSZinequivalent}; the following realization will be the one which we will use.
+
+\begin{dfn}\label{def:secondary polytope}
+  Let $x_1, \ldots, x_n$ define a convex $n$-gon, and let $T$ be the set of triangulations of this $n$-gon.
 For each $t\in T$ define $s_t$ to be the point in $\mathbb{R}^n$ whose $i$th coordinate is the sum of the areas of all triangles of $t$ which are incident to $x_i$.
-Let $A_n$ be the convex hull of the $s_t$.
+Let $A_n$ be the convex hull of the $s_t$; then $A_n$ a realization of the $n-1$ associahedron (\cite{Ziegler}, Example 9.11)
 \end{dfn}
-This is the construction of the secondary polytope (so $A_n$ is the secondary polytope of $x_1, \ldots, x_n$), see \cite{Ziegler} Definition 9.9.
+Note that this construction works for any convex $n$-gon, but these realizations are all equally good for our purposes, and so we fix $x_1, \ldots, x_n$ defining a particular convex $n$-gon from now on.
+
+Definition~\ref{def:secondary polytope} is a special case of the {\em secondary polytope} construction; see \cite[Definition 9.9]{Ziegler} for more details.
 In general the $x_1, \ldots, x_n$ may be any points in any $\mathbb{R}^d$.
 Triangulations in this more general context are decompositions into simplices and the area of the triangles is replaced by the volume of the simplices.
-
-$A_n$ defined in this way is a realization of the $n-1$ associahedron (\cite{Ziegler}, Example 9.11).
-Note that we get a realization for any convex $n$-gon, but these realizations are all equally good for our purposes, and so we fix $x_1, \ldots, x_n$ defining a particular convex $n$-gon from now on.
 
@@
 \includegraphics{associahedron5gon} \hspace{1cm} \includegraphics{associahedron3d}
-\caption{Two associahedra labelled by all and some (respectively) of their polygon dissections.}\label{associahedron5gon}
+\caption{Two associahedra, labelled by all and some (respectively) of their polygon dissections.}\label{associahedron5gon}
 \end{figure}
 
-Note that Wilson loop diagrams which are weakly admissible but not admissible are necessarily exact and hence have $\tau$ graphs which are triangulations, hence dimension 0 faces (vertices) in $A_n$.
-All of these are equivalent in the sense that they are only retriangulations away from each other.
-It will be convenient in what follows, to include these diagrams.
-The next two propositions would be identical in the case of admissible instead of weakly admissible, while the corollary could be changed to involve admissible diagrams only by subtracting one from the number of non parallel faces in order to account for the missing dimension 0 faces.
+Note that Wilson loop diagrams which are weakly admissible but not admissible are necessarily exact, and hence have $\tau$ graphs which are triangulations, i.e.
+dimension 0 faces (vertices) in $A_n$.
+All of these are equivalent (as Wilson loop diagrams) in the sense that they are only retriangulations away from each other; meanwhile, as noted above, all vertices of $A_n$ are parallel to each other.
+It will be convenient in what follows to include these diagrams, but the results are easily modified to remove them if needed: Propositions~\ref{prop easy way} and \ref{prop hard way} would be identical if we replaced ``weakly admissible'' by ``admissible'', while Corollary~\ref{cor:count inequiv diagrams} could be changed to consider only admissible diagrams by subtracting 1 from the number of non-parallel faces in order to account for the missing dimension 0 faces.
 
@@
   Let $W$ and $X$ be two equivalent Wilson loop diagrams.
-From Corrolary \ref{equialentretriangulation} we know that $\tau(W)$ and $\tau(X)$ differ from each other only by retriangulations of their triangulated pieces.
+From Corollary \ref{equialentretriangulation} we know that $\tau(W)$ and $\tau(X)$ differ from each other only by retriangulations of their triangulated pieces.
 
@@
 Let $a$ be the area of the quadrilateral and let $a(i,j,k)$ be the area of the triangle with corners $x_i$, $x_j$ and $x_k$, and similarly for other indices then $s_{t_1}$ on coordinates $i$, $j$, $k$, $l$ is $(a(i,j,l) + b_i, a+b_j, a(k,l,j)+b_k, a+b_l)$ and $s_{t_2}$ on these coordinates is $(a + b_i, a(j,k,i)+b_j, a+b_k, a(l,i,k)+b_l$, where the $b_i$ are the sums of the areas of the relevant triangles which are common to both triangulations.
-Thus a vector parallel to this edge is the vector which is $(a(i,j,l) - a, a-a(j,k,i), a(k,l,j)-a, a-a(l,i,k)) = (-a(j,k,l), a(i,k,l), -a(i,j,l), a(i,j,k))$ on $i$, $j$, $k$, $l$ and $0$ in all other coordinates.
-This is illustrated in Figure~\ref{triangulate}.
+Thus a vector parallel to this edge is the vector which is
+  \[(a(i,j,l) - a, a-a(j,k,i), a(k,l,j)-a, a-a(l,i,k)) = (-a(j,k,l), a(i,k,l), -a(i,j,l), a(i,j,k))\]
+  on $i$, $j$, $k$, $l$ and $0$ in all other coordinates.  This is illustrated in Figure~\ref{triangulate}.
 
@@
     We have from \cite{CSZinequivalent} that $\omega^+_d$ is a normal vector for any face with $d$ as a diagonal, however we can also check this fact in a completely elementary way using the shoelace formula for the area of a triangle.
-The shoelace formula says that if $(x_1, y_1), (x_2, y_2), (x_3, y_3)$ are the coordinates of the corners of a triangle in counterclockwise order then the area of the triangle is $(x_1y_2 - x_1y_3 + x_2y_3 - x_2y_1 + x_3y_1 - x_3y_2)/2$.
+The shoelace formula says that if $(x_1, y_1), (x_2, y_2), (x_3, y_3)$ are the coordinates of the corners of a triangle in counterclockwise order then the area of the triangle is
+    \[(x_1y_2 - x_1y_3 + x_2y_3 - x_2y_1 + x_3y_1 - x_3y_2)/2.\]
 
@@
     \begin{align*}
-      & h_1(a_2h_3-a_2h_4+a_3h_4-a_3h_2+a_4h_2-a_4h_3)/2 - h_2(a_1h_3-a_1h_4+a_3h_4-a_3h_1+a_4h_1-a_4h_3)/2 \\
-      & + h_3(a_1h_2-a_1h_4+a_2h_4-a_2h_1+a_4h_1-a_4h_2)/2 - h_4(a_1h_2-a_1h_3+a_2h_3-a_2h_1+a_3h_1-a_3h_2)/2 \\
-      & = 0
+       & \hspace{1cm}\textstyle\frac{1}{2}h_1(a_2h_3-a_2h_4+a_3h_4-a_3h_2+a_4h_2-a_4h_3) \\
+       &\hspace{3cm} - \textstyle\frac{1}{2} h_2(a_1h_3-a_1h_4+a_3h_4-a_3h_1+a_4h_1-a_4h_3) \\
+       &\hspace{5cm}+ \textstyle\frac{1}{2}h_3(a_1h_2-a_1h_4+a_2h_4-a_2h_1+a_4h_1-a_4h_2) \\
+       &\hspace{7cm}- \textstyle\frac{1}{2}h_4(a_1h_2-a_1h_3+a_2h_3-a_2h_1+a_3h_1-a_3h_2), 
     \end{align*}
+    which evaluates to 0.
 
@@
 
-The two propositions imply
-\begin{cor}
+Propositions~\ref{prop easy way} and \ref{prop hard way} together imply:
+\begin{cor}\label{cor:count inequiv diagrams}
   The number of inequivalent weakly admissible Wilson loop diagrams on $n$ is the number of non-parallel faces in the associahedron $A_n$.

### 2019-06-07 GWLDCI.tex
ignore:testing
edits in section 4 of paper 1

--- 2019-06-01 GWLDCI.tex
@@
 
-\begin{dfn}
+\begin{dfn} \label{Andfn}
   Let $x_1, \ldots, x_n$ define a convex $n$-gon.
@@
 
-  Consider now an edge whose quadrilateral has corners $x_i$, $x_j$, $x_k$, and $x_l$ in that order.
+Consider now an edge in $A_n$ whose quadrilateral is defined by the vertices of $\tau(W)$ or $\tau(X), $x_i$, $x_j$, $x_k$, and $x_l$ in that order.
 Let $t_1$ and $t_2$ be the triangulations corresponding to the two ends of the edge where $t_1$ has a diagonal from $x_j$ to $x_l$ and $t_2$ has a diagonal from $x_i$ to $x_k$.
-From the definition of $A_n$ we see that $s_{t_1}$ and $s_{t_2}$ only differ at coordinates $i$, $j$, $k$, and $l$, and all of the triangles incident to any of these vertices other than the one coming from triangulating $x_i, x_j, x_k, x_l$ are the same in both $t_1$ and $t_2$.
+From Definition \ref{Andfn}, defining $A_n$,  we see that $s_{t_1}$ and $s_{t_2}$ only differ at coordinates $i$, $j$, $k$, and $l$.
+All of the triangles incident to any of these vertices other than the one coming from triangulating $x_i, x_j, x_k, x_l$ are the same in both $t_1$ and $t_2$.
 Let $a$ be the area of the quadrilateral and let $a(i,j,k)$ be the area of the triangle with corners $x_i$, $x_j$ and $x_k$, and similarly for other indices then $s_{t_1}$ on coordinates $i$, $j$, $k$, $l$ is $(a(i,j,l) + b_i, a+b_j, a(k,l,j)+b_k, a+b_l)$ and $s_{t_2}$ on these coordinates is $(a + b_i, a(j,k,i)+b_j, a+b_k, a(l,i,k)+b_l$, where the $b_i$ are the sums of the areas of the relevant triangles which are common to both triangulations.
@@
   Returning to $\tau(W)$ and $\tau(X)$, since the direction vector of an edge in $A_n$ depends only on its quadrilateral and the bijection between the edges bounding $\tau(W)$ and the edges bounding $\tau(X)$ preserves the quadrilateral, we have the same direction vectors bounding $\tau(W)$ as $\tau(X)$.
-Furthermore, the bijection also maintains the relative configuration of the edges and so $\tau(W)$ and $\tau(X)$ are parallel.
+Furthermore, the bijection also maintains the relative configuration of the edges and so the edges corresponding to $\tau(W)$ and $\tau(X)$ are parallel.
 \end{proof}
@@
 We also need the following notation.
-Given a polygon dissection $D$ let $V_{>3}(D)$ be the set of vertices of the polygon which are on at least one non-triangle face of $D$.
+Given a polygon dissection $D$ of an $n$-gon, let $V_{>3}(D)$ be the set of vertices of the polygon which are on at least one non-triangle face of $D$.
 Note that $D$ may have many non-triangle faces and so $V_{>3}(D)$ will be the union of the vertices of each non-triangle face.
@@
 \begin{lem}\label{lem good quads}
-  Let $D_1$ and $D_2$ be two dissections of the convex polygon defined by the vertices $x_1, \ldots, x_n$.
+Let $D_1$ and $D_2$ be two dissections of a convex $n$-gon defined by the vertices $x_1, \ldots, x_n$.
 Suppose $V_{>3}(D_1) = V_{>3}(D_2)$, but that the $D_1$ and $D_2$ do not have the same set of non-triangle faces.
-Then there are four vertices $x_i$, $x_j$, $x_k$, $x_l$ such that in one of $D_1$ or $D_2$ all four vertices are on the same non-triangle face while in the other there is a diagonal of the dissection such that there is one side of the diagonal with exactly one of $\{x_i, x_j, x_k, x_l\}$ (so the others are end points of this diagonal or strictly on the other side).
+Then there are four vertices $x_i$, $x_j$, $x_k$, $x_l$ satisfying the following conditions:\begin{enumerate} \item in either $D_1$ or $D_2$ all four vertices are on the same non-triangle face \item in the other disection, there is a diagonal of the dissection such that exactly one of $\{x_i, x_j, x_k, x_l\}$ lies on one side (so the others are either end points of this diagonal or strictly on the other side).
+\end{enumerate}
 \end{lem}
@@
 
+This proof is by a symmetrical consruction, where we give a proof with respect to a single edge in $f$, leaving the rest of the argument as read due to the symmetry.
+
 Assume for a contradiction that no quadrilateral as in the statement exists, and let $d$ and $f$ be as above.
 Then $f$ must have two vertices strictly on each side of $d$, say $x_i$ and $x_j$ on one side and $x_k$, $x_l$ on the other side (and in that order).
-Consider the face incident to $d$ on the $x_i, x_j$ side of $d$.
-Suppose this face is a triangle, then its other vertex cannot be in $[x_i, x_j]$ as otherwise taking one of the other edges of the triangles would give a configuration as in the statement.
-Suppose now that this face is a quadrilateral, again no other vertex of this face can be in $(x_i, x_j)$ as otherwise again taking one of the other edges of the face as $d$ we'd get a quadrilateral as in the statement, the same holds if one of the other vertices of the face is $x_i$ or $x_j$ but the other is not.
-If the two other vertices of the face are $x_i$ and $x_j$, then we also get a configuration as in the statement but now with the four vertices being the two ends of $q$ and $x_i, x_j$ and with one of the edges of $f$ as the diagonal.
+Consider the face in $D_1$ incident to $d$ on the $x_i, x_j$ side of $d$.
+Call this $g$.
+Suppose this face is a triangle, then its other vertex cannot be in \st{$[x_i, x_j]$} the cyclic interval bounded by $x_i$ and $x_j$ (i.e.
+$[x_i, x_j]$) as in this case taking one of the other edges of the triangle $g$ would give a configuration as in the statement.
+Suppose then that this face, $g$, is a quadrilateral.
+Again no other vertex of this face can be in $(x_i, x_j)$ as otherwise again replacing $d$ with one of the other edges of $g$ gives a quadrilateral as in the statement.
+The same holds if one of the other vertices of $g$ is $x_i$ or $x_j$ but the other is not.
+If both the other vertices of $g$ are $x_i$ and $x_j$, then we also get a configuration as in the statement but now with the four vertices being those defining $g$ and the diagonal is one of the edges of $f$.
+(For instance $d$ can now be the edge connecting $x_l$ to $x_i$ or $x_j$ to $x_k$.
 Thus we can conclude that none of the vertices of this face are in $[x_i, x_j]$.
-Also if the face has three vertices on one side of $f$ and one on the other then we get a quadrilateral as in the statement again with this face giving the four vertices and the diagonal is a side of $f$.
-In this case the face is either a triangle with its third vertex of the triangle must be in $(x_j,x_k)$ or in $(x_l,x_i)$ or a quadrilateral with one more vertex in $(x_j, x_k)$ and one more vertex in $(x_l, x_i)$.
-The three possibilities are illustrated in Figure~\ref{inductive_step}.
-Taking all this together, whether the face is a triangle or a quadrilateral, replacing $d$ with one of the other edges of the face we get a new diagonal $d'$ which also separates $f$ into $x_i, x_j$ and $x_k, x_l$ but is strictly closer to $[x_i, x_j]$ than $d$ was.
+
+Suppose the face $g$ has one vertex in $(x_j, ,x_k)$ and the rest in $(x_l, x_i)$ (or vice versa).
+If $g$ is a quadrilateral, its four vertices satisfy the condition with the edge between $x_k$ and $x_j$ in $f$ serving as an example we get a quadrilateral as in the statement again with this face giving the four vertices and the diagonal is a side of $f$.
+If $g$ a triangle, let $d'$ be the other diagonal across $f$.
+These are the first two cases illustrated in Figure~\ref{inductive_step}.
+
+Finally, if the face $g$ has two vertices in $(x_j, x_k)$ and two in $(x_l, x_i)$, let $d'$ be the the other edge of $g$ that forms a diagonal across $f$.
+In these last two cases (those represented in Figure~\ref{inductive_step}), replace $d$ with $d'$, which also separates $f$ into $x_i, x_j$ and $x_k, x_l$ \hlfix{but is strictly closer to $[x_i, x_j]$ than $d$ was}{why is this the case?}.
 The same argument holds for $d'$, but the polygon is finite, so this process cannot go on indefinitely, contradicting that no quadtilateral as in the statement exists.

### 2019-06-07 GWLDCI.tex
Fixed what of Sian's changes I overwrote

@@
 \begin{thm}\label{same matroid iff equiv}
-Let $W= (\cP, [n])$ and $W'= (\cP', n)$ be two Wilson Loop diagrams. They define the same matroid if and only if $W \sim W'$.
+Let $W= (\cP, [n])$ and $W'= (\cP', n)$ be two Wilson loop diagrams. They define the same matroid if and only if $W \sim W'$.
 \end{thm}
@@
 
-In this section we have characterized the correspondence between Wilson loop diagrams and positroids, showing that Wilson Loop diagrams define the same matroid if and only if they are equivalent (Theorem \ref{same matroid iff equiv}).
+\sanote{I undid Sian's edit here.
+I like "saying what i'm about to say.
+Saying it.
+Summarizing what I said"}In this section we have characterized the correspondence between Wilson loop diagrams and positroids, showing that Wilson Loop diagrams define the same matroid if and only if they are equivalent (Theorem \ref{same matroid iff equiv}).
 Corollary \ref{number of equiv diagrams} enumerates the fibres of the map from Wilson Loop diagrams to positroids.
@@
 \subsection{Polytope background}\label{sec polytope background}
+We first give a quick summary of the polytope terminology we will use in this section; the interested reader is referred to \cite{Ziegler} for more details.
 
@@
 Two faces are \emph{parallel} if one can be mapped to the other by a translation in $\mathbb{R}^d$.
+
+Two faces are \emph{parallel} if one can be mapped to the other by a translation in $\mathbb{R}^d$.
 In particular parallel faces must be of the same dimension and any two vertices are parallel to each other.
-
 There are many important polytopes in combinatorics, including, of primary importance to us, the associahedron.
 
-Two polytopes are \emph{combinatorially equivalent} if there is a bijection between their faces which preserves inclusion of faces.
+Finally, two polytopes are \emph{combinatorially equivalent} if there is a bijection between their faces which preserves inclusion of faces.
 Often in combinatorics one is primarily interested in the combinatorial equivalence classes, and common names, including the associahedron, refer to these equivalence classes.
@@
 
-Associahedra can also be viewed in terms of polygon dissections.
+There are many important polytopes in combinatorics, including, of primary importance to us, the associahedron. The associahedron can be characterized in many different ways; here is one definition.
+
+\begin{dfn}\label{def:associahedron}
 Fix $n$ and consider dissections of a convex $n$-gon.
-The $n-1$ asociahedron can be given in terms of the dissections of this $n$-gon; the vertices of the associahedron are the triangulations of the $n$-gon while the dimension $k$ faces are the dissections which are $k$ diagonals away from being a triangulation.
+The $n-1$ {\em associahedron} can be given in terms of the dissections of this $n$-gon; the vertices of the associahedron are the triangulations of the $n$-gon while the $k$-dimensional faces are the dissections which are $k$ diagonals away from being a triangulation.
 One face is included in another if the first dissection is a refinement of the second.
+\end{dfn}
 
@@
 
-\begin{dfn} \label{Andfn}
-  Let $x_1, \ldots, x_n$ define a convex $n$-gon.
-Let $T$ be the set of triangulations of this $n$-gon.
+\begin{dfn} \label{def:secondary polytope}
+  Let $x_1, \ldots, x_n$ define a convex $n$-gon and let $T$ be the set of triangulations of this $n$-gon.
 For each $t\in T$ define $s_t$ to be the point in $\mathbb{R}^n$ whose $i$th coordinate is the sum of the areas of all triangles of $t$ which are incident to $x_i$.
-Let $A_n$ be the convex hull of the $s_t$.
+Let $A_n$ be the convex hull of the $s_t$; then $A_n$ a realization of the $n-1$ associahedron (\cite{Ziegler}, Example 9.11)
 \end{dfn}
+
+Note that this construction works for any convex $n$-gon, but these realizations are all equally good for our purposes, and so we fix $x_1, \ldots, x_n$ defining a particular convex $n$-gon from now on.
+
+Definition~\ref{def:secondary polytope} is a special case of the {\em secondary polytope} construction; see \cite[Definition 9.9]{Ziegler} for more details.
+In general the $x_1, \ldots, x_n$ may be any points in any $\mathbb{R}^d$.
+Triangulations in this more general context are decompositions into simplices and the area of the triangles is replaced by the volume of the simplices.
 This is the construction of the secondary polytope (so $A_n$ is the secondary polytope of $x_1, \ldots, x_n$), see \cite{Ziegler} Definition 9.9.
@@
 Triangulations in this more general context are decompositions into simplices and the area of the triangles is replaced by the volume of the simplices.
-
-$A_n$ defined in this way is a realization of the $n-1$ associahedron (\cite{Ziegler}, Example 9.11).
-Note that we get a realization for any convex $n$-gon, but these realizations are all equally good for our purposes, and so we fix $x_1, \ldots, x_n$ defining a particular convex $n$-gon from now on.
 
@@
 \includegraphics{associahedron5gon} \hspace{1cm} \includegraphics{associahedron3d}
-\caption{Two associahedra labelled by all and some (respectively) of their polygon dissections.}\label{associahedron5gon}
+\caption{Two associahedra, labelled by all and some (respectively) of their polygon dissections.}\label{associahedron5gon}
 \end{figure}
 
-Note that Wilson loop diagrams which are weakly admissible but not admissible are necessarily exact and hence have $\tau$ graphs which are triangulations, hence dimension 0 faces (vertices) in $A_n$.
-All of these are equivalent in the sense that they are only retriangulations away from each other.
-It will be convenient in what follows, to include these diagrams.
-The next two propositions would be identical in the case of admissible instead of weakly admissible, while the corollary could be changed to involve admissible diagrams only by subtracting one from the number of non parallel faces in order to account for the missing dimension 0 faces.
+Note that Wilson loop diagrams which are weakly admissible but not admissible are necessarily exact, and hence have $\tau$ graphs which are triangulations, i.e.
+dimension 0 faces (vertices) in $A_n$.
+All of these are equivalent (as Wilson loop diagrams) in the sense that they are only retriangulations away from each other; meanwhile, as noted above, all vertices of $A_n$ are parallel to each other.
+It will be convenient in what follows to include these diagrams, but the results are easily modified to remove them if needed: Propositions~\ref{prop easy way} and \ref{prop hard way} would be identical if we replaced ``weakly admissible'' by ``admissible'', while Corollary~\ref{cor:count inequiv diagrams} could be changed to consider only admissible diagrams by subtracting 1 from the number of non-parallel faces in order to account for the missing dimension 0 faces.Note that Wilson loop diagrams which are weakly admissible but not admissible are necessarily exact, and hence have $\tau$ graphs which are triangulations, i.e.
+dimension 0 faces (vertices) in $A_n$.
+All of these are equivalent (as Wilson loop diagrams) in the sense that they are only retriangulations away from each other; meanwhile, as noted above, all vertices of $A_n$ are parallel to each other.
+It will be convenient in what follows to include these diagrams, but the results are easily modified to remove them if needed: Propositions~\ref{prop easy way} and \ref{prop hard way} would be identical if we replaced ``weakly admissible'' by ``admissible'', while Corollary~\ref{cor:count inequiv diagrams} could be changed to consider only admissible diagrams by subtracting 1 from the number of non-parallel faces in order to account for the missing dimension 0 faces.
 
@@
   Let $W$ and $X$ be two equivalent Wilson loop diagrams.
-From Corrolary \ref{equialentretriangulation} we know that $\tau(W)$ and $\tau(X)$ differ from each other only by retriangulations of their triangulated pieces.
+From Corrollary \ref{equialentretriangulation} we know that $\tau(W)$ and $\tau(X)$ differ from each other only by retriangulations of their triangulated pieces.
 
@@
 Let $t_1$ and $t_2$ be the triangulations corresponding to the two ends of the edge where $t_1$ has a diagonal from $x_j$ to $x_l$ and $t_2$ has a diagonal from $x_i$ to $x_k$.
-From Definition \ref{Andfn}, defining $A_n$,  we see that $s_{t_1}$ and $s_{t_2}$ only differ at coordinates $i$, $j$, $k$, and $l$.
+From Definition \ref{def:secondary polytope}, defining $A_n$,  we see that $s_{t_1}$ and $s_{t_2}$ only differ at coordinates $i$, $j$, $k$, and $l$.
 All of the triangles incident to any of these vertices other than the one coming from triangulating $x_i, x_j, x_k, x_l$ are the same in both $t_1$ and $t_2$.

### 2019-06-10 GWLDCI.tex
fixed the rest of the overwritten changes

@@
 Saying it.
-Summarizing what I said"}In this section we have characterized the correspondence between Wilson loop diagrams and positroids, showing that Wilson Loop diagrams define the same matroid if and only if they are equivalent (Theorem \ref{same matroid iff equiv}).
+Summarizing what I said"}\note{Sian: sure.
+I'll push back if it gets too repetitive, but it works here.}In this section we have characterized the correspondence between Wilson loop diagrams and positroids, showing that Wilson Loop diagrams define the same matroid if and only if they are equivalent (Theorem \ref{same matroid iff equiv}).
 Corollary \ref{number of equiv diagrams} enumerates the fibres of the map from Wilson Loop diagrams to positroids.
@@
 
-\section{Associahedra and inequivalent Wilson loop diagrams}\label{sec associahedron}
-
-The connection between admissible Wilson loop diagrams and polytope dissections suggests a connection to associahedra. First we need some background. \sanote{expand}
-
 \subsection{Polytope background}\label{sec polytope background}
+
 We first give a quick summary of the polytope terminology we will use in this section; the interested reader is referred to \cite{Ziegler} for more details.
@@
 A \emph{face} of a polytope is the intersection of the polytope with any hyperplane for which the entire polytope is in one of the closed half-spaces defined by the hyperplane.
-The polytope itself is also considered a face (in the case that that polytope is of full dimension, this definition can be unified by considering linear equalities (including the trivial one) in place of hyperplanes and the corresponding linear inequalities in place of the half-spaces defined by the hyperplane, see chapter 2 of \cite{Ziegler}).
-Two faces are \emph{parallel} if one can be mapped to the other by a translation in $\mathbb{R}^d$.
+The polytope itself is also considered a face; in the case that that polytope is of full dimension, this definition can be unified by considering linear equalities (including the trivial one) in place of hyperplanes and the corresponding linear inequalities in place of the half-spaces defined by the hyperplane (see chapter 2 of \cite{Ziegler}).
 
@@
 In particular parallel faces must be of the same dimension and any two vertices are parallel to each other.
-There are many important polytopes in combinatorics, including, of primary importance to us, the associahedron.
 
 Finally, two polytopes are \emph{combinatorially equivalent} if there is a bijection between their faces which preserves inclusion of faces.
-Often in combinatorics one is primarily interested in the combinatorial equivalence classes, and common names, including the associahedron, refer to these equivalence classes.
+Often in combinatorics one is primarily interested in the combinatorial equivalence classes, and common polytope names (including the associahedron) refer to these equivalence classes.
 A particular polytope in the class is then known as a \emph{realization}.
@@
 It turns out that this defines a class of combinatorially equivalent polytopes, which can be proved by giving a realization.
-There are many interesting realizations of the associahedron \cite{CSZinequivalent}; the following will be the one which we will use.
-See Figure~\ref{associahedron5gon} for examples.
-
-\begin{dfn} \label{def:secondary polytope}
-  Let $x_1, \ldots, x_n$ define a convex $n$-gon and let $T$ be the set of triangulations of this $n$-gon.
-For each $t\in T$ define $s_t$ to be the point in $\mathbb{R}^n$ whose $i$th coordinate is the sum of the areas of all triangles of $t$ which are incident to $x_i$.
-Let $A_n$ be the convex hull of the $s_t$; then $A_n$ a realization of the $n-1$ associahedron (\cite{Ziegler}, Example 9.11)
+There are many interesting realizations of the associahedron \cite{CSZinequivalent}; the following realization will be the one which we will use.
+
+\begin{dfn}\label{def:secondary polytope}
+  Let $x_1, \ldots, x_n$ define a convex $n$-gon, and let $T$ be the set of triangulations of this $n$-gon.
+For each $t\in T$, define $s_t$ to be the point in $\mathbb{R}^n$ whose $i$th coordinate is the sum of the areas of all triangles of $t$ which are incident to $x_i$.
+Let $A_n$ be the convex hull of the $s_t$; then $A_n$ a realization of the $n-1$ associahedron (\cite[Example 9.11]{Ziegler}).
 \end{dfn}
-
 Note that this construction works for any convex $n$-gon, but these realizations are all equally good for our purposes, and so we fix $x_1, \ldots, x_n$ defining a particular convex $n$-gon from now on.
@@
 Definition~\ref{def:secondary polytope} is a special case of the {\em secondary polytope} construction; see \cite[Definition 9.9]{Ziegler} for more details.
-In general the $x_1, \ldots, x_n$ may be any points in any $\mathbb{R}^d$.
-Triangulations in this more general context are decompositions into simplices and the area of the triangles is replaced by the volume of the simplices.
-This is the construction of the secondary polytope (so $A_n$ is the secondary polytope of $x_1, \ldots, x_n$), see \cite{Ziegler} Definition 9.9.
 In general the $x_1, \ldots, x_n$ may be any points in any $\mathbb{R}^d$.
@@
 All of these are equivalent (as Wilson loop diagrams) in the sense that they are only retriangulations away from each other; meanwhile, as noted above, all vertices of $A_n$ are parallel to each other.
-It will be convenient in what follows to include these diagrams, but the results are easily modified to remove them if needed: Propositions~\ref{prop easy way} and \ref{prop hard way} would be identical if we replaced ``weakly admissible'' by ``admissible'', while Corollary~\ref{cor:count inequiv diagrams} could be changed to consider only admissible diagrams by subtracting 1 from the number of non-parallel faces in order to account for the missing dimension 0 faces.Note that Wilson loop diagrams which are weakly admissible but not admissible are necessarily exact, and hence have $\tau$ graphs which are triangulations, i.e.
-dimension 0 faces (vertices) in $A_n$.
-All of these are equivalent (as Wilson loop diagrams) in the sense that they are only retriangulations away from each other; meanwhile, as noted above, all vertices of $A_n$ are parallel to each other.
 It will be convenient in what follows to include these diagrams, but the results are easily modified to remove them if needed: Propositions~\ref{prop easy way} and \ref{prop hard way} would be identical if we replaced ``weakly admissible'' by ``admissible'', while Corollary~\ref{cor:count inequiv diagrams} could be changed to consider only admissible diagrams by subtracting 1 from the number of non-parallel faces in order to account for the missing dimension 0 faces.
@@
 
-Consider now an edge in $A_n$ whose quadrilateral is defined by the vertices of $\tau(W)$ or $\tau(X), $x_i$, $x_j$, $x_k$, and $x_l$ in that order.
+Consider now an edge in $A_n$ whose quadrilateral is defined by the vertices of $\tau(W)$ or $\tau(X)$, $x_i$, $x_j$, $x_k$, and $x_l$ in that order.
 Let $t_1$ and $t_2$ be the triangulations corresponding to the two ends of the edge where $t_1$ has a diagonal from $x_j$ to $x_l$ and $t_2$ has a diagonal from $x_i$ to $x_k$.
@@
    \begin{align*}
-      & h_1(a_2h_3-a_2h_4+a_3h_4-a_3h_2+a_4h_2-a_4h_3)/2 - h_2(a_1h_3-a_1h_4+a_3h_4-a_3h_1+a_4h_1-a_4h_3)/2 \\
-      & + h_3(a_1h_2-a_1h_4+a_2h_4-a_2h_1+a_4h_1-a_4h_2)/2 - h_4(a_1h_2-a_1h_3+a_2h_3-a_2h_1+a_3h_1-a_3h_2)/2 \\
-      & = 0
+       & \hspace{1cm}\textstyle\frac{1}{2}h_1(a_2h_3-a_2h_4+a_3h_4-a_3h_2+a_4h_2-a_4h_3) \\
+       &\hspace{3cm} - \textstyle\frac{1}{2} h_2(a_1h_3-a_1h_4+a_3h_4-a_3h_1+a_4h_1-a_4h_3) \\
+       &\hspace{5cm}+ \textstyle\frac{1}{2}h_3(a_1h_2-a_1h_4+a_2h_4-a_2h_1+a_4h_1-a_4h_2) \\
+       &\hspace{7cm}- \textstyle\frac{1}{2}h_4(a_1h_2-a_1h_3+a_2h_3-a_2h_1+a_3h_1-a_3h_2), 
     \end{align*}
+    which evaluates to 0.
 

### 2019-06-10 GWLDCII.tex
initial pictures added

@@
 To calculate $R(W)$, write \bmls R_1 = c_{1,1} c_{1, 2}\quad R_2 = c_{2,2} c_{2,3} \quad R_4 = c_{2,5} (c_{2,4}c_{1,5} - c_{2,5}c_{1,4})c_{1,4} \\ R_5 = c_{4,6} (c_{4,6}c_{3,5} - c_{3,6}c_{4,5})c_{3,5} \quad R_7 = c_{3,7} c_{3,8} \quad R_8 = c_{4,8} c_{4,1} \;.\emls All other $R_e$ are $1$.
-Finally, the integran associated to this Wilson loop diagram is \bas \Omega(W) = \frac{\textrm{d}c_{1,1}\textrm{d}c_{1,1}\textrm{d}c_{1,1}\textrm{d}c_{1,2}\textrm{d}c_{1,4}\textrm{d}c_{1,5}\textrm{d}c_{2,1}\textrm{d}c_{2,3}\textrm{d}c_{2,4}\textrm{d}c_{2,5}\textrm{d}c_{3,5}\textrm{d}c_{3,6}\textrm{d}c_{3,7}\textrm{d}c_{3,7}\textrm{d}c_{4,5}\textrm{d}c_{4,6}\textrm{d}c_{4,8}\textrm{d}c_{4,1}}{c_{1,1} c_{1, 2}c_{2,2} c_{2,3}c_{2,5} (c_{2,4}c_{1,5} - c_{2,5}c_{1,4})c_{1,4}c_{4,6} (c_{4,6}c_{3,5} - c_{3,6}c_{4,5})c_{3,5}c_{3,7} c_{3,8}c_{4,8} c_{4,1}} \;.
-\]\eas
+Finally, the integrand associated to this Wilson loop diagram is \bas \Omega(W) = \frac{\textrm{d}c_{1,1}\textrm{d}c_{1,1}\textrm{d}c_{1,1}\textrm{d}c_{1,2}\textrm{d}c_{1,4}\textrm{d}c_{1,5}\textrm{d}c_{2,1}\textrm{d}c_{2,3}\textrm{d}c_{2,4}\textrm{d}c_{2,5}\textrm{d}c_{3,5}\textrm{d}c_{3,6}\textrm{d}c_{3,7}\textrm{d}c_{3,7}\textrm{d}c_{4,5}\textrm{d}c_{4,6}\textrm{d}c_{4,8}\textrm{d}c_{4,1}}{c_{1,1} c_{1, 2}c_{2,2} c_{2,3}c_{2,5} (c_{2,4}c_{1,5} - c_{2,5}c_{1,4})c_{1,4}c_{4,6} (c_{4,6}c_{3,5} - c_{3,6}c_{4,5})c_{3,5}c_{3,7} c_{3,8}c_{4,8} c_{4,1}} \;.
+\eas
 \end{eg}
@@
 
-\hlfix{[picture]}{is it worth including a picture here?}
+\begin{eg}
+Let $W$ be the Wilson loop diagram from Figure \ref{fig:ex of WLD}, reproduced here for convenience.  \[W\ =\ \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
+	\begin{scope}
+	\drawWLD{8}{1.5}
+	\drawnumbers
+	\drawlabeledprop{1}{0}{4}{0}{\footnotesize $p$}
+	\drawprop{2}{0}{4}{-1}
+    \drawprop{5}{0}{8}{0}
+    \drawprop{5}{1}{7}{0}
+		\end{scope}
+	\end{tikzpicture}\]
+
+Let $p$ be the propatagor $p = (1, 4)$. Then $\cP_{in}(p, <_4) = \{(1,4), (5, 8), (5, 7) \}$ and $\cP_{out}(p, <_4) = \{(2,4) \}$
+\end{eg}
 
@@
 This completes the base case.
+
+\bas \begin{tikzpicture}[rotate=15,baseline=(current bounding box.east)]
+	\begin{scope}
+	\drawWLD{20}{1.5}
+	%\drawnumbers
+	%\drawprop{1}{0}{4}{0}
+	\drawlabeledprop{5}{0}{7}{0}{\footnotesize $p_1$}
+    \drawlabeledprop{3}{0}{12}{0}{\footnotesize $q_1$}
+		\end{scope}
+	\end{tikzpicture}\eas
 

### 2019-06-11 GWLDCI.tex
Sian is finished with paper 1 for now
Edited all but "equivalent diagrams iff equal matroids" proof

@@
 \begin{rmk}\label{alt F(P) rmk}
-An equivalent definition of $F(P)$ \note{Sian note to self: doublecheck that these {\em are} equiv definitions now} is \bas F(P)  = \big(V(P) \setminus V(P^c) \big) \cup F(\emptyset) \;,\eas 
+An equivalent definition of $F(P)$ is \bas F(P)  = \big(V(P) \setminus V(P^c) \big) \cup \{\text{ all non-supporting vertices in $W$ }\} \;,\eas 
+\note{replaced $F(\emptyset)$ with words in this definition because we were defining $F(P)$ in terms of $F(\emptyset)$ and it was mildly inelegant/recursive)}
 i.e.
@@
 
-\note{sian note to self: come back and package this as a remark, and make sure it follows from the previous result}
-Note that this means that the set $F(\emptyset)$ of non-supporting vertices is the maximal subset of vertices of $W$ of rank $0$.
-That is, it is the unique flat of rank $0$ in $M(W)$.
-This also implies that every element of $F(\emptyset)$ is a circuit, and all other circuits of $M(W)$ contain at least two elements.
+\begin{rmk}
+By point (4) of Lemma~\ref{lem facts about WLD matroids}, the set $F(\emptyset)$ of non-supporting vertices in $W$ is a flat; indeed, it is the unique flat of rank 0 in $M(W)$.
+Every element of $F(\emptyset)$ defines a circuit of size 1, and all other circuits of $M(W)$ must contain at least two elements.
+\end{rmk}
 
@@
 Therefore $B\cup\{w\}$ is a dependent set, which implies that $B\cup \{w\}$ contains a circuit $D$.
-We must have $w \in D$ (since $B$ was an independent set), and \hlfix{$D \subseteq F(\Prop(C))$}{I know we've talked about this before and I can't remember why this is true} $\subseteq F$.
-Since $C$ was the union of all circuits in $F$, we finally obtain $w \in C$, which is a contradiction.
-This completes the proof of (1).
+In particular we must have $w \in D$ (since $B$ was an independent set), and since we have already shown that $C \subseteq F(\Prop(C))$, we also have the chain of inclusions
+\[D \subseteq B\cup \{w\} \subseteq F(\Prop(C)) \subseteq F.\]
+Since $C$ was the union of all circuits in $F$, we finally obtain $w \in C$, which is a contradiction. This completes the proof of (1).
 
@@
 
-Finally, note that 
-\bas C = F(Q^c) = V(Q)^c \subseteq F(P^c) = V(P)^c \;,\eas
-where the $\subseteq$ follows from equation~\eqref{eq decompose F}.
-This implies that \hlfix{$P \subseteq Q$}{sian should go look up why this is true}, and hence $(P, V(P))$ is a subdiagram of $(Q, V(Q))$.
+Finally, note that since $F(P^c) = C \sqcup S$ (equation~\eqref{eq decompose F}), we have
+\[\Prop(C) \subseteq \Prop(F(P^c)) \subseteq P^c.\]
+Taking complements, we obtain $P \subseteq \Prop(C)^c = Q$, and hence that $(P, V(P))$ is a subdiagram of $(Q, V(Q))$.
 Since $(P, V(P))$ is maximally exact by hypothesis, and $(Q, V(Q))$ is exact by equation \eqref{Q defines exact}, we must have $P = Q$.
@@
 
-To see (3), first note that when $(P,V(P))$ is maximal exact, part (2) of this lemma combined with Lemma \ref{lem facts about WLD matroids} gives that
+To see point (3), first note that when $(P,V(P))$ is maximal exact, part (2) of this lemma combined with Lemma \ref{lem facts about WLD matroids} gives that
 \bas\rk(F(P^c)) = |\Prop(F(P^c))| = |P^c|.\eas
@@
 
+\section{Associahedra and inequivalent Wilson loop diagrams}\label{sec associahedron}
+
+The connection between admissible Wilson loop diagrams and polytope dissections suggests a connection to associahedra. First we need some background. \sanote{expand}
+
 \subsection{Polytope background}\label{sec polytope background}
@@
   Let $W$ and $X$ be two equivalent Wilson loop diagrams.
-From Corrollary \ref{equialentretriangulation} we know that $\tau(W)$ and $\tau(X)$ differ from each other only by retriangulations of their triangulated pieces.
+From Corollary \ref{equialentretriangulation} we know that $\tau(W)$ and $\tau(X)$ differ from each other only by retriangulations of their triangulated pieces.
 
@@
 
-Consider now an edge in $A_n$ whose quadrilateral is defined by the vertices of $\tau(W)$ or $\tau(X)$, $x_i$, $x_j$, $x_k$, and $x_l$ in that order.
+Consider now an edge in $A_n$ whose quadrilateral is defined by the vertices of $\tau(W)$ or $\tau(X)$, which we label $x_i$, $x_j$, $x_k$, and $x_l$ in that order (see Figure \ref{triangulate} below).
 Let $t_1$ and $t_2$ be the triangulations corresponding to the two ends of the edge where $t_1$ has a diagonal from $x_j$ to $x_l$ and $t_2$ has a diagonal from $x_i$ to $x_k$.
-From Definition \ref{def:secondary polytope}, defining $A_n$,  we see that $s_{t_1}$ and $s_{t_2}$ only differ at coordinates $i$, $j$, $k$, and $l$.
-All of the triangles incident to any of these vertices other than the one coming from triangulating $x_i, x_j, x_k, x_l$ are the same in both $t_1$ and $t_2$.
-Let $a$ be the area of the quadrilateral and let $a(i,j,k)$ be the area of the triangle with corners $x_i$, $x_j$ and $x_k$, and similarly for other indices then $s_{t_1}$ on coordinates $i$, $j$, $k$, $l$ is $(a(i,j,l) + b_i, a+b_j, a(k,l,j)+b_k, a+b_l)$ and $s_{t_2}$ on these coordinates is $(a + b_i, a(j,k,i)+b_j, a+b_k, a(l,i,k)+b_l$, where the $b_i$ are the sums of the areas of the relevant triangles which are common to both triangulations.
-Thus a vector parallel to this edge is the vector which is $(a(i,j,l) - a, a-a(j,k,i), a(k,l,j)-a, a-a(l,i,k)) = (-a(j,k,l), a(i,k,l), -a(i,j,l), a(i,j,k))$ on $i$, $j$, $k$, $l$ and $0$ in all other coordinates.
+From the construction of the secondary polytope $A_n$ in \ref{def:secondary polytope}, we see that $s_{t_1}$ and $s_{t_2}$ only differ at coordinates $i$, $j$, $k$, and $l$: all of the triangles incident to any of these vertices other than the one coming from triangulating $x_i, x_j, x_k, x_l$ are the same in both $t_1$ and $t_2$.
+
+Let $a$ be the area of the quadrilateral and let $a(i,j,k)$ be the area of the triangle with corners $x_i$, $x_j$ and $x_k$ (and similarly for other indices), and let $b_*$ denote the sum of the areas of triangles incident to vertex $*$ which are common to both triangulations.
+Then $s_{t_1}$ on coordinates $i$, $j$, $k$, $l$ is
+\[(a(i,j,l) + b_i, a+b_j, a(k,l,j)+b_k, a+b_l),\]
+and $s_{t_2}$ on these coordinates is 
+\[(a + b_i, a(j,k,i)+b_j, a+b_k, a(l,i,k)+b_l).\] 
 This is illustrated in Figure~\ref{triangulate}.
+
+Thus a vector parallel to this edge is the vector which is 
+\begin{equation}\label{eq:direction vector for quadrilateral}(a(i,j,l) - a, a-a(j,k,i), a(k,l,j)-a, a-a(l,i,k)) = (-a(j,k,l), a(i,k,l), -a(i,j,l), a(i,j,k))\end{equation}
+on $i$, $j$, $k$, $l$, and $0$ in all other coordinates.
 
@@
 Consider $s_{t_1}$ and $s_{t_2}$ at coordinate $i$.
-In $s_{t_1}$ this coordinate is given by the area of those shaded triangles incident to $x_i$ along with $a(i,j,l)$.
-In $s_{t_2}$ this coordinate is given by the area of those shaded triangles incident to $x_i$ along with $a(i,l,k) + a(i,j,k) = a$.}\label{triangulate}
+In $s_{t_1}$ this coordinate is given by the area of those shaded triangles incident to $x_i$ (denoted by $b_i$ in the proof) along with $a(i,j,l)$.
+In $s_{t_2}$ this coordinate is given by $b_i$ along with $a(i,l,k) + a(i,j,k) = a$.}\label{triangulate}
 \end{figure}
@@
 
-The following lemma is useful for proving the converse of the above.
-We also need the following notation.
-Given a polygon dissection $D$ of an $n$-gon, let $V_{>3}(D)$ be the set of vertices of the polygon which are on at least one non-triangle face of $D$.
-Note that $D$ may have many non-triangle faces and so $V_{>3}(D)$ will be the union of the vertices of each non-triangle face.
+In order to prove the converse of Proposition~\ref{prop easy way}, we first require a preliminary lemma.
+
+We also need the following notation: given a polygon dissection $D$ of an $n$-gon, let $V_{>3}(D)$ be the set of vertices of the polygon which are on at least one non-triangle face of $D$.
+(Note that $D$ may have many non-triangle faces and so $V_{>3}(D)$ will be the union of the vertices of each non-triangle face.) We also write $[x_i,x_j]$ for the set of vertices from $x_i$ to $x_j$ including the endpoints, and $(x_i,x_j)$ for the same set but excluding the endpoints.
 
@@
 Let $D_1$ and $D_2$ be two dissections of a convex $n$-gon defined by the vertices $x_1, \ldots, x_n$.
-Suppose $V_{>3}(D_1) = V_{>3}(D_2)$, but that the $D_1$ and $D_2$ do not have the same set of non-triangle faces.
-Then there are four vertices $x_i$, $x_j$, $x_k$, $x_l$ satisfying the following conditions:\begin{enumerate} \item in either $D_1$ or $D_2$ all four vertices are on the same non-triangle face \item in the other disection, there is a diagonal of the dissection such that exactly one of $\{x_i, x_j, x_k, x_l\}$ lies on one side (so the others are either end points of this diagonal or strictly on the other side).
+\hlfix{Suppose that $V_{>3}(D_1) = V_{>3}(D_2)$}{we probably use this implicitly somewhere in the proof but I can't see it; can we make it explicit?}, but that the $D_1$ and $D_2$ do not have the same set of non-triangle faces.
+Then there are four vertices $x_i$, $x_j$, $x_k$, $x_l$ satisfying the following conditions:\begin{enumerate} \item In either $D_1$ or $D_2$ all four vertices are on the same non-triangle face; \item In the other dissection, there is a diagonal of the dissection such that exactly one of $\{x_i, x_j, x_k, x_l\}$ lies on one side of the diagonal (so the others are either end points of this diagonal or strictly on the other side).
 \end{enumerate}
@@
   Since $D_1$ and $D_2$ do not have the same set of non-triangle faces, there must be some diagonal $d$ of $D_1$ that crosses through a non-triangle face $f$ of $D_2$.
-If that face of $D_2$ has degree at least 5 then it must contain four vertices as in the statement.
+If that face of $D_2$ has degree at least 5 then it must contain four vertices in the configuration described in the statement.
 
@@
 Assume for a contradiction that no quadrilateral as in the statement exists, and let $d$ and $f$ be as above.
-Then $f$ must have two vertices strictly on each side of $d$, say $x_i$ and $x_j$ on one side and $x_k$, $x_l$ on the other side (and in that order).
-Consider the face in $D_1$ incident to $d$ on the $x_i, x_j$ side of $d$.
-Call this $g$.
-Suppose this face is a triangle, then its other vertex cannot be in \st{$[x_i, x_j]$} the cyclic interval bounded by $x_i$ and $x_j$ (i.e.
-$[x_i, x_j]$) as in this case taking one of the other edges of the triangle $g$ would give a configuration as in the statement.
-Suppose then that this face, $g$, is a quadrilateral.
-Again no other vertex of this face can be in $(x_i, x_j)$ as otherwise again replacing $d$ with one of the other edges of $g$ gives a quadrilateral as in the statement.
-The same holds if one of the other vertices of $g$ is $x_i$ or $x_j$ but the other is not.
-If both the other vertices of $g$ are $x_i$ and $x_j$, then we also get a configuration as in the statement but now with the four vertices being those defining $g$ and the diagonal is one of the edges of $f$.
-(For instance $d$ can now be the edge connecting $x_l$ to $x_i$ or $x_j$ to $x_k$.
-Thus we can conclude that none of the vertices of this face are in $[x_i, x_j]$.
-
-Suppose the face $g$ has one vertex in $(x_j, ,x_k)$ and the rest in $(x_l, x_i)$ (or vice versa).
-If $g$ is a quadrilateral, its four vertices satisfy the condition with the edge between $x_k$ and $x_j$ in $f$ serving as an example we get a quadrilateral as in the statement again with this face giving the four vertices and the diagonal is a side of $f$.
-If $g$ a triangle, let $d'$ be the other diagonal across $f$.
-These are the first two cases illustrated in Figure~\ref{inductive_step}.
-
-Finally, if the face $g$ has two vertices in $(x_j, x_k)$ and two in $(x_l, x_i)$, let $d'$ be the the other edge of $g$ that forms a diagonal across $f$.
-In these last two cases (those represented in Figure~\ref{inductive_step}), replace $d$ with $d'$, which also separates $f$ into $x_i, x_j$ and $x_k, x_l$ \hlfix{but is strictly closer to $[x_i, x_j]$ than $d$ was}{why is this the case?}.
-The same argument holds for $d'$, but the polygon is finite, so this process cannot go on indefinitely, contradicting that no quadtilateral as in the statement exists.
+Then $f$ must have two vertices strictly on each side of $d$: name the vertices on one side of $d$ as $x_i$ and $x_j$, and those on the other side as $x_k$, $x_l$ (and in that order; see Figure~\ref{inductive_step}).
+Let $g$ be the face in $D_1$ that is incident to $d$ on the $x_i, x_j$ side of $d$.
+
+We first show that none of the vertices defining $g$ can lie in the cyclic interval $[x_i,x_j]$.
+Indeed, if $g$ is a triangle then we immediately see that its third vertex cannot lie in the interval $[x_i,x_j]$, as we could obtain a configuration as described in the statement by replacing $d$ with one of the other edges of $g$.
+
+Similarly, if $g$ is a quadrilateral then immediately by the same argument none of its vertices can lie in the interval $(x_i, x_j)$, nor can we have exactly one of $x_i$ or $x_j$ being a vertex of $g$ for the same reason.
+If both the other vertices of $g$ are $x_i$ and $x_j$ (so $g$ is the quadrilateral defined by $x_i$, $x_j$, and the two endpoints of $d$) then we still obtain a configuration as described in the lemma statement by swapping the roles of $f$ and $g$: now the four vertices would be the ones defining $g$, and the diagonal would be one of the edges of $f$.
+(For instance $d$ can now be the edge connecting $x_l$ to $x_i$ or $x_j$ to $x_k$.) Thus we can conclude that none of the vertices of the face $g$ are in the interval $[x_i, x_j]$.
+
+There are now two possibilities for $g$: either it has one vertex in the interval $(x_j, x_k)$ and the rest in $(x_l, x_i)$ (or vice versa), or it has two vertices in $(x_j, x_k)$ and two in $(x_l, x_i)$.
+In the first case, $g$ must be a triangle since if $g$ was a quadrilateral then its four vertices provide the desired configuration (with the edge of $f$ that connects $x_j$ and $x_k$ providing the desired diagonal); in the second case, $g$ has four vertices and is therefore a quadrilateral.
+
+These cases are illustrated in Figure~\ref{inductive_step}.
+If $g$ is a triangle then let $d'$ be the other diagonal across $f$ (leftmost two cases in the figure), while if $g$ is a quadrilateral let $d'$ be the other diagonal that crosses $f$.
+In all cases, note that $d'$ is strictly closer to $[x_i,x_j]$ than $d$ was, since we chose $g$ to be the face incident to $d$ on the $x_i,x_j$ side.
+
+Now $d'$ is also a diagonal of $D_1$ that crosses the non-triangle face $f$ of $D_2$, and we can repeat the above argument with $d'$ instead of $d$.
+This process can be repeated indefinitely but the polygon is finite, yielding a contradiction to our assumption that no quadrilateral with the configuration described in the statement exists.
 \end{proof}
@@
 \begin{prop}\label{prop hard way}
-  If two weakly admissible Wilson loop diagrams are not equivalent then their faces in $A_n$ are not parallel
+  If two weakly admissible Wilson loop diagrams are not equivalent then their faces in $A_n$ are not parallel.
 \end{prop}
@@
   Let $W$ and $X$ be inequivalent.
-If $\tau(W)$ and $\tau(X)$ do not have the same number of diagonals (hence their faces in $A_n$ do not have the same dimension) then they are not parallel, so we can assume $\tau(W)$ and $\tau(X)$ do have the same number of diagonals and hence their faces in $A_n$ have the same dimension.
-Let the face associated to $\tau(W)$ be $f_W$ and the face associated to $\tau(X)$ be $f_X$.
+If $\tau(W)$ and $\tau(X)$ do not have the same number of diagonals (hence their faces in $A_n$ do not have the same dimension) then they are not parallel by definition.
+Now suppose that $\tau(W)$ and $\tau(X)$ do have the same number of diagonals and hence their faces in $A_n$ have the same dimension.
+Let the face associated to $\tau(W)$ in $A_n$ be $f_W$ and the face associated to $\tau(X)$ be $f_X$.
 
   As observed in the proof of Proposition~\ref{prop easy way}, the support of any nonzero vector parallel to an edge is on the indices corresponding to the four vertices bounding the quadrilateral of the dissection associated with the edge.
-Thus if $V_{>3}(\tau(W)) \neq V_{>3}(\tau(X))$ (notation as defined before Lemma~\ref{lem good quads}) then the span of the vectors parallel to their edes has different support and so they cannot be parallel.
+Thus if $V_{>3}(\tau(W)) \neq V_{>3}(\tau(X))$ (notation as defined before Lemma~\ref{lem good quads}) then the span of the vectors parallel to their edges has different support and so they cannot be parallel.
 So we can assume that $V_{>3}(\tau(W)) = V_{>3}(\tau(X))$.
@@
     Since $\tau(W)$ and $\tau(X)$ do not have the same set of non-triangle faces, there must be some diagonal $d$ of $\tau(W)$ that crosses through a non-triangle face $f$ of $\tau(X)$. 
-    It will be most convenient to look at normal vectors and to use the choice of normal vector discussed on p8 of \cite{CSZinequivalent}, namely pick one side of $d$ to be positive and define the $i$th coordinate of the $\omega^+_d$ to be
+    It will be most convenient to consider faces in terms of their normal vectors.
+We make use of the construction discussed on p8 of \cite{CSZinequivalent}: namely, pick one side of $d$ to be positive and define the $i$th coordinate of the vector $\omega^+_d$ to be
     \[
@@
     \]
-    We have from \cite{CSZinequivalent} that $\omega^+_d$ is a normal vector for any face with $d$ as a diagonal, however we can also check this fact in a completely elementary way using the shoelace formula for the area of a triangle.
-The shoelace formula says that if $(x_1, y_1), (x_2, y_2), (x_3, y_3)$ are the coordinates of the corners of a triangle in counterclockwise order then the area of the triangle is $(x_1y_2 - x_1y_3 + x_2y_3 - x_2y_1 + x_3y_1 - x_3y_2)/2$.
-
-    Proceed now to check that $\omega^+_d$ is a normal vector for any face associated to a dissection including $d$.
-We will do this by showing it is normal to every edge bounding the face.
+    We have from \cite{CSZinequivalent} that $\omega^+_d$ is a normal vector for any face with $d$ as a diagonal; however we can also check this fact in a completely elementary way using the shoelace formula for the area of a triangle.
+The shoelace formula says that if $(x_1, y_1), (x_2, y_2), (x_3, y_3)$ are the coordinates of the corners of a triangle in counterclockwise order then the area of the triangle is \[\textstyle\frac{1}{2}(x_1y_2 - x_1y_3 + x_2y_3 - x_2y_1 + x_3y_1 - x_3y_2).\]
+
+    We now check that $\omega^+_d$ is a normal vector for any face associated to a dissection including $d$, which we accomplish by showing it is normal to every edge bounding the face.
 To do so, choose the coordinate system for the polygon so that $d$ is along the $x$-axis.
-Let $(a_i, h_i)$, $i=1,2,3,4$ be the coordinates of the vertices of a quadrilateral in counterclockwise order and which corresponds to an edge bounding the face.
-Since the dissection includes $d$ either all four points are on the negative side of $d$, and so the dot product of $\omega^+_d$ with the direction vector for the quadrilateral is immediately $0$, or, by the formula in the proof of the previous proposition and the shoelace formula, the dot product of $\omega^+_d$ with the vector associated to the quadrilateral is
+Let $(a_i, h_i)$, $i\in \{1,2,3,4\}$ be the coordinates of the vertices of a quadrilateral in counterclockwise order and which corresponds to an edge bounding the face.
+Since the dissection includes $d$, either all four points are on the negative side of $d$ and so the dot product of $\omega^+_d$ with the direction vector for the quadrilateral is immediately $0$, or, by the formula in equation \eqref{eq:direction vector for quadrilateral} and the shoelace formula, the dot product of $\omega^+_d$ with the vector associated to the quadrilateral is
    \begin{align*}
@@
     \end{align*}
-    which evaluates to 0.
-
-    Now, $\tau(W)$ and $\tau(X)$ satisfy the hypotheses of Lemma~\ref{lem good quads}, so we can assume that $f$ and $d$ have the property that there is one side of $d$, which we will call the positive side, so that exactly one vertex of $f$ is strictly on that side.
-Then $\omega^+_d$ with the direction vector of $d$ have common support exactly on that one vertex and so their dot product is nonzero.
+    which also evaluates to 0.
+
+    Now, $\tau(W)$ and $\tau(X)$ satisfy the hypotheses of Lemma~\ref{lem good quads}, so we can assume that $f$ and $d$ have the property that we can choose a side of $d$ to be the positive side in such a way that exactly one vertex of $f$ is strictly on the positive side.
+Then $\omega^+_d$ and the direction vector of $d$ have common support exactly on that one vertex and so their dot product is nonzero.
 Since the direction vector of $d$ is contained in the direction of $\tau(X)$ but is not orthogonal to $\omega^+_d$, while $\omega^+_d$ is normal to the face of $\tau(W)$, it follows that the faces associated to $\tau(W)$ and $\tau(X)$ are not parallel, as desired.

### 2019-06-12 GWLDCI.tex
Paper 1 edited up to section 4

@@
 In recent years, there has been an active program researching the geometry and combinatorics underlying SYM $N=4$ theory \cite{wilsonloop, Arkani-Hamed:2013jha, Amplituhedronsquared, AmplituhedronDecomposition, galashinlam}.
-This body of work started with the observation that the on shell amplitudes\note{Is this for tree level amplitudes?
-If so, we should say that} of this theory correspond to the volume of a subspace of a positive Grasmannian, called an Amplituhedron \cite{Arkani-Hamed:2013jha}.
+This body of work started with the observation that the on shell (tree level) amplitudes of this theory correspond to the volume of a subspace of a positive Grasmannian, called an Amplituhedron \cite{Arkani-Hamed:2013jha}.
 Since then, there has been significant work studying the structure of the amplituhedron, geometrically and combinatorially, for instance \cite{Arkani-Hamed:2013kca, arkani:2012nw, AmplituhedronDecomposition, galashinlam}.
@@
 In subsection~\ref{sec: polygon partitions} we relate certain subdiagrams (the {\em exact} subdiagrams, Definition~\ref{def:exact diagram}) of Wilson loop diagrams to triangulations of polygons, and then in subsection~\ref{sec: exact diagram matroidal props} we examine the matroidal properties of the exact subdiagrams.
-Specifically, we show that a subdiagram of a Wilson loop diagrams $W$ defines a uniform matroid if and only if the subdiagram is exact (Theorem \ref{exactuniformthm}), and that this uniform matroid \hlfix{is isomorphic to}{isomorphic or equal?} the dual matriod of $W$ restricted to the exact subdiagram (Remark \ref{remark exact dual restiction}).
+Specifically, we show that a subdiagram of a Wilson loop diagrams $W$ defines a uniform matroid if and only if the subdiagram is exact (Theorem \ref{exactuniformthm}), and that this uniform matroid is equal to the dual of the matriod associated to $W$ restricted to the exact subdiagram (Remark \ref{remark exact dual restiction}).
 Subsection~\ref{sec: matroids and equivalence} is devoted to the proof of Theorem~\ref{same matroid iff equiv}, along with an easy corollary which gives a formula for the size of each equivalence class (Corollary~\ref{number of equiv diagrams}).
@@
 An equivalent definition of $F(P)$ is \bas F(P)  = \big(V(P) \setminus V(P^c) \big) \cup \{\text{ all non-supporting vertices in $W$ }\} \;,\eas 
-\note{replaced $F(\emptyset)$ with words in this definition because we were defining $F(P)$ in terms of $F(\emptyset)$ and it was mildly inelegant/recursive)}
 i.e.
@@
 
-In other words, a Wilson loop diagram, $(\cP, [n])$ is admissible if and only if $n \geq |\cP| +4$, and has no crossing propagators, no propagators of the form $p = (i, i+1)$, and no pairs of propagators that start and end on the same pair of non-adjacent edges.
-\note{My concern here is with this last sentence.
-I think it is in fact true, but I don't see that it is obvious from the definitions.
-It is saying that if any set of propagators is too dense according to condition 2, then either a single propagator in that set or a pair of them is already too dense (or condition 3 fails).
-That seems nontrivial to me, even interesting.
-Probably you proved this in your first paper on the topic and it is so old hat you don't even think about it any more, but in that case the appropriate lemma should be cited, rather than implying it is just a rephrasing of the definition itself}
+In other words, a Wilson loop diagram, $(\cP, [n])$ is admissible only if $n \geq |\cP| +4$, and has no crossing propagators, no propagators of the form $p = (i, i+1)$, and no pairs of propagators that start and end on the same pair of non-adjacent edges.
+
+{\color{violet} INTERNAL NOTE ONLY.
+(I've removed the offending "if" above: The other direction of the above is best seen from the point of view of triangulations.
+Any exact subdiagram corresponds to a triangulation.
+$n>1$ or more propagators forms a minimal violation the the density condition if one can remove one propagator to get an exact subdiagram on $n-1$ propagators, and thus a triangulation.
+The only way this can happen is to cross propagators/ diagonals, or two have the diagonal start and end at the same vertex (parallell propagators).
+A single violator violates the density condition if it starts and ends on adjascent edges of the Wilson loop diagram/ vertices of the triangulation.}
 
@@
 
-These $C(W)$ parametrize a subspace of $\Gr(k, n)$ as shown in \cite{wilsonloop}, call it $\Sigma(W)$.
-\note{I don't think this sentence stands properly alone: What set precisely is ``These'' running over?
-$\Sigma(W)$ is not the whole subspace of $\Gr(k,n)$ it is just the part corresponding to $C(W)$, so the obvious ``it'' in the sentence (namely the subspace) is not the correct one.
-Also, $\Sigma(W)$ appears only one other time in this paper (in a more formal definiiton later which is essentially saying the same thing as this sentence but in more detail), perhaps we should refer forwards; perhaps we don't need this notation in this paper?}
-
 %The Wilson loop diagrams also define a volume form on $\Sigma(W)$: \bas \Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V_{p_r}} \textrm{d}c_{p_r}}{R(W)} \;.
@@
 In particular, this allows us to prove results about $M(W)$ by considering the behavior of propagators in $W$.
-We record a few elementary facts about the rank and cycles of $M(W)$ here as an example of this.
+We record a few facts about the ranks cycles and flats of $M(W)$ here as an example of this.
 
@@
 \item $F(P)$ is a flat of $M( W)$, which we call the \emph{propagator flat} of $P$.
+\item If $F$ is a cyclic flat of $M(W)$, then it is a propagator flat.
 \end{enumerate}
@@
 Thus $\rk(F(P) \cup\{v\}) = \rk(F(P)) + 1$, as required.
+
+Point (5) is given in \cite[Lemma 3.28]{wilsonloop}.
 \end{proof}
@@
 \begin{rmk} \label{remark exact dual restiction} For readers familiar with duals and complements of matroids, we reinterpret Theorem~\ref{exact diagrams contractions} in these terms.
-If $M^*$ denotes the dual of a matroid, then by standard matroid theory \hlfix{[ref]}{if we're not going to define them here (and we really shouldn't!) then it's probably polite to give a reference} the dual of a contraction of a matroid is the same as the restriction of the dual matroid by the complement: \bas M / S = M^*|_{S^c} \;.\eas Then Theorem \ref{exact diagrams contractions} implies that, for $(P, V(P))$ an exact subdiagram of $W$, we have \bas M\big((P, V(P))\big) = M(W)  / F(P^c) = M(W)^*|_{V(P)} \;.\eas
+If $M^*$ denotes the dual of a matroid, then by standard matroid theory \cite{OxleyMatroidBook} the dual of a contraction of a matroid is the same as the restriction of the dual matroid by the complement: \bas M / S = M^*|_{S^c} \;.\eas Then Theorem \ref{exact diagrams contractions} implies that, for $(P, V(P))$ an exact subdiagram of $W$, we have \bas M\big((P, V(P))\big) = M(W)  / F(P^c) = M(W)^*|_{V(P)} \;.\eas
 \end{rmk}
@@
 \begin{dfn}
-Given a Wilson loop diagram $W = (\cP, [n])$ and its associated positroid $M(W)$, let $\Sigma(W)$ denote the corresponding positroid cell in the CW complex on $\Gr(|\cP|, n)$.
+Given a Wilson loop diagram $W = (\cP, [n])$, its associated matroid $M(W)$ corresponds to positroid cells in the CW complex on $\Gr(|\cP|, n)$.
 \end{dfn}
@@
 Since $(P, V(P))$ is an exact subdiagram, the matroid is uniform, and so all $|P| \times |P|$ minors are non-zero.
-Intersecting these with the cases with the positive Grassmannians demands that all minors be strictly positive.\note{I don't understand this last sentence.}
+Since $(P, V(P))$ is weakly admissible, the matroid associated to it can be realized by an element of the totally nonnegative Grassmannian $\Gr(k,n)$, by Theorem \ref{thm WLD defines matroid}.
 \end{proof}
@@
 Assume that $W$ and $W'$ are equivalent.
-Without loss of generality, write $W = (P \cup R, [n])$ and $W' = (P \cup R', [n])$, where $P \subset \cP \cap \cP'$ and $(R, V(R))$ and $(R', V(R'))$ are two maximal exact subdiagrams, with $R \neq R'$, but $V(R) = V(R')$.
-If this is not the case, one may always find a family of diagram, $\{W_i\}$ satisfying this condition and forming a transitive chain connecting $W$ to $W'$ in the equivalence class.
-
-Let $U \subset V(R)$ be any subset of size $|U| = |R|$.
-Since $(R, V(R))$ defines a uniform matroid, by Lemma \ref{exactuniformthm}, the set $U$ is independent in the subdiagram $(R, V(R))$, and thus in $W$.
-The complementary set $F(R^c) = F(P)$ is a flat of maximal rank by lemma \ref{maxexactcomplementrank} ($\rk(F(P)) = |P|$).
-Let $B \subset F(P)$ be a maximal independent set ($\rk B = |P|$) in $F(P)$.
+Without loss of generality, write $W = (P \sqcup R, [n])$ and $W' = (P \sqcup R', [n])$, where $P \subset \cP \cap \cP'$ and $(R, V(R))$ and $(R', V(R'))$ are two maximal exact subdiagrams, with $R \neq R'$, but $V(R) = V(R')$.
+If one cannot find this partition of $\cP$ and $\cP'$, one may always find a family of diagrams, $\{W_1 \ldots W_n\}$ such that $W_{i-1}$ and $W_i$ satisfy this contion, and with $W = W_0$ and $W' = W_{n+1}$.
+That is, we can find a  transitive chain ($\{W_1 \ldots W_n\}$) between $W$ and $W'$ in the equivalence class.
+
+By Theorem \ref{exactuniformthm}, $(R, V(R))$ defines a uniform matroid. Therefore, any set $U$ of size $|R|$ is independent in the subdiagram $(R, V(R))$, and thus in $W$.
+
+By the third point of Lemma \ref{maxexactcomplementrank}, the complementary flat, $F(P)$ has full rank: $\rk(F(P)) = |P|$.
+Let $B \subset F(P)$ be a maximal independent subset of $F(P)$: $\rk (B) = |P|$.
 Since $F(P)$ is a flat, adding any element of $V(R)$ to $B$ increases the rank.
@@
 For the converse, assume that the matroids associated to $W$ and $W'$ are the same: $M(W) = M(W')= M$.
-Let $\mathcal{R} = \{(P_i, V(P_i)\}_{i=1}^k$ and $\mathcal{R}' = \{(P'_i, V(P'_i)\}_{i=1}^l$ be the sets of maximal exact subdiagrams of $W$ and $W'$.
-Write $F_i = F(P_i^c)$ and $F'_i = F(P^{'c}_i)$ to be the complementary cyclic flats.
-By Theorem \ref{exactuniformthm} and Theorem \ref{exact diagrams contractions},  $M/F_i$ and $M/F_i'$ are uniform matroids.
-Since, by Theorem \ref{exactuniformthm}, any subset $V$ of $M$ such that $M/(V^c)$ is uniform defines an exact subdiagram of both $W$ and $W'$.
-If $U \subset V$ are two such sets, then the corresponding exact subdiagrams are also subsets.
-Therefore, $|\mathcal{R}| = |\mathcal{R}'|$, and we write $V(P_i) = V(P'_i)$, after possibly reindexing $\mathcal{R}$ and $\mathcal{R}'$.
-
-Since the sets of propagators defining maximal exact subdiagrams partition $\cP$, by Lemma \ref{uniqueproppartitioncor}, write $\cup_{i = 1}^k P_i = \cup_{i = 1}^k P'_i = \cP$.
-Reorganize the vertex sets of maximal exact subdiagrams as follows: \ba \cup_{P_i \not \in \mathcal{R}'} V(P_i) = V(\cup_{P_i \not \in \mathcal{R}'} P_i)  = F(\cup_{P_i \in \mathcal{R}'} P_i)^c\label{vertexsets}\; .\ea The final flat may, of course, be empty.
-
-Thus, we have partitioned the vertices of $W$ and $W'$ into two complementary sets.
-The first, $ \cup_{P_i \not \in \mathcal{R}'} V(P_i)$,  is comprised of the union of supports of maximal exact subdiagrams whose propagators differ between $W$ and $W'$.
-The second, $ F(\cup_{P_i \in \mathcal{R}'} P_i)$,  is the propagator flat of all propagators in common between $W$ and $W'$.
-
-Without loss of generality, assume that $|\mathcal{R}| = |\mathcal{R}'| = 1$.
-Then the two Wilson loop diagrams are equivalent.
-If  $|\mathcal{R}| = |\mathcal{R}'| > 1$, then one may define a family of Wilson loop diagrams, $W_0$ to $W_k$ defined such that $W_0 = W$ and $W_i$ is derived from $W_{i-1}$ by replacing the propagator set $P_i$ with $P'_i$.
-In this manner, $W' = W_k$ and $W_i \sim W_{i+1}$, making $W \sim W'$.
+Let $\mathcal{R} = \{(P_i, V(P_i)\}_{i=1}^m$ and $\mathcal{R}' = \{(P'_i, V(P'_i)\}_{i=1}^l$ be the sets of maximal exact subdiagrams of $W$ and $W'$.
+Recall that these sets $\{P_i\}$ and $\{P_i'\}$ partition the propagator sets $\cP$ and $\cP'$ of $W$ and $W'$ respectivley.
+Let $\mathcal{F}$ and $\mathcal{F}'$ the respective complementary vertices: \bas \mathcal{F} = \{F_i = V(P_i)^c | (P_i, V(P_i)) \in \mathcal{R}\} \quad  \mathcal{F}' = \{F_i' = V(P'_i)^c | (P'_i, V(P'_i)) \in \mathcal{R}\} \;.\eas By Theorem \ref{maxexactcomplementrank}, every $F_i$ and $F_i'$ is a cyclic flat of full rank in $M$.
+We claim that $\mathcal{F} = \mathcal{F'}$.
+
+If not, there would be a cyclic flat $F_j$ of $M$.
+Without loss of generality, write $F_j \in \mathcal{F} \setminus \mathcal{F'}$.
+We may write $F_j = V(P_j)^c$, with $(P_j, V(P_j))$ a maximal exact subdiagram in $W$.
+By Lemma \ref{lem facts about WLD matroids} (5), we may write $F_j= F(Q)$ as a propagator flat.
+By Lemma \ref{contractsubdiaglem}, $M/F(Q) = F/F_j = M(Q^c, V(Q^c))$, which is uniform, by construction of $F_j$.
+Theorem \ref{exactuniformthm} $(Q^c, V(Q^c))$ is exact.
+Since this exact subdiagram is not in $\mathcal{R}'$ by construction of $F_j$, it is not a maximal exact subdiagram of $W'$.
+That is, there is a maximal exact subdiagram containing it: $(Q^c, V(Q^c)) \subset (P_j', V(P_j'))$.
+Suppose $|P_j' \setminus Q^c| = m$.
+By counting vertices of the two nested sets $F_j' \subset F_j$ we see that  \bas |F_j| = n -|Q^c| -3  \textrm{ while } |F_j'| = n -|P_j'| -3 = n -|Q^c| -m -3\;.\eas That is, $F_j'$ has $m$ more vertices than $F_j$.
+Furthermore, by construction $\rk(F_j) + m = \rk (F_j')$.
+This violates the assumption that both $F_j$ and $F_j'$ are cyclic flats.
+
+Therefore, we see that $\mathcal{F} = \mathcal{F'}$, which implies that the maximally exact subdiagrams of $W$ and $W'$, are supported on the same vertex sets.
+All propagators of $W$ and $W'$ are accounted for in these sets.
+There there exists a transitive chain of equivalent diagrams that put $W$ and $W'$ in the same equivalence class.
 \end{proof}
-
-\note{Two comments on this proof.
-First I think it was written before other things and so doesn't quite match in style and language; I have improved this a bit but it would benefit from more editing with that in mind.
-Second, I feel that both directions essentially come down to the fact that there is a unique uniform matroid of each dimension and rank.}
 
@@
 
-\sanote{I undid Sian's edit here.
-I like "saying what i'm about to say.
-Saying it.
-Summarizing what I said"}\note{Sian: sure.
-I'll push back if it gets too repetitive, but it works here.}In this section we have characterized the correspondence between Wilson loop diagrams and positroids, showing that Wilson Loop diagrams define the same matroid if and only if they are equivalent (Theorem \ref{same matroid iff equiv}).
+In this section we have characterized the correspondence between Wilson loop diagrams and positroids, showing that Wilson Loop diagrams define the same matroid if and only if they are equivalent (Theorem \ref{same matroid iff equiv}).
 Corollary \ref{number of equiv diagrams} enumerates the fibres of the map from Wilson Loop diagrams to positroids.

### 2019-06-13 GWLDCII.tex
assimilating some of Susama's edits into paper 2

@@
 
-These diagrams correspond to (tree level) amplitudes of SYM N=4 theory in twistor space.
+These diagrams correspond to (tree level) amplitudes of SYM $N=4$ theory in twistor space.
 As such, it associates a real value to $n$ particles, one for each vertex.
 Each particle is represented as a section of a $|\cP|$-vector bundle over twistor space, projected onto a real subspace in a process called bosonization \cite{Arkani-Hamed:2013jha}.
-In otherwords, each Wilson loop diagram defines a functional on external particles.
-This is represented as an integral $I(W)$, which is the equalent of a Feynman integral in this setting.
-
-A $n \times |\cP|$ matrix $C(W)$ represents the (tree level) particle interactions.
+In other words, each Wilson loop diagram defines a functional on external particles.
+This is represented as an integral $I(W)$, which is the equivalent of a Feynman integral in this setting.
+
+A $|\cP| \times n$ matrix $C(W)$ represents the (tree level) particle interactions.
 Each row of $C(W)$ corresponds to an internal propagator, each column to an external particle.
-Each row only has zero entries on every external particle it does not interact with.
-In particular,
+$C(W)$ is defined as follows:
 
@@
 The entries $c_{p,q}$ are non-zero real variables.
-This matrix can be interpreted as a parametrization of the positroid cell in the positive Grassmannian $\Gr(n, |\cP|)$ assoiciated to the $W$, call it $\Sigma(W)$ \cite{wilsonloops}.
-Most of the work in this paper, and in \cite{GWLDI} focuses on characterizing the positroid cell assoicated to eash Wilson loop diagram $W$.
-An example of $C(W)$ is given in example \ref{integraldetails}.
-
-Note that, since there is no ordering on the propagators of $W$, $C(W)$ is only defined up to rearrangement of the rows.
-This will not matter as this does not effect the parametrization of $\Sigma(W)$.
-
-One may also interpret functional $I(W)$ as a associating a volume to each $\Sigma(W)$ \cite{wilsonloops, AmplituhedronSquared, HeslopStewart}.
-The volume form is written in terms of the elements of $C(W)$as  \[ \Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V_{p_r}} \textrm{d}c_{p_r}}{R(W)} \;.
+Thus the zero entries in row $p$ correspond to the external particles that the propagator $p$ does not interact with.
+See \ref{integraldetails} for an example of a diagram $W$ and its associated matrix.
+
+The matrix $C(W)$ can be interpreted as a parametrization of the positroid cell in the positive Grassmannian $\Gr(n, |\cP|)$ associated to the $W$, which we denote by $\Sigma(W)$ \cite{wilsonloop}.
+Most of the work in this paper, and in \cite{generalcombinatoricsI} focuses on characterizing the positroid cell assoicated to eash Wilson loop diagram $W$.
+
+Note that since there is no ordering on the propagators of $W$, $C(W)$ is only defined up to rearrangement of the rows.
+This will not matter here, as it does not affect the parametrization of $\Sigma(W)$.
+
+One may also interpret the functional $I(W)$ as associating a volume to each cell $\Sigma(W)$ \cite{wilsonloop, Amplituhedronsquared, HeslopStewart}.
+The volume form is written in terms of the elements of $C(W)$ as  \[ \Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V_{p_r}} \textrm{d}c_{p_r}}{R(W)} \;.
 \]
@@
 
-For a fixed number of propagators and particles, the tree level amplitude of the Wilson loop diagrams is finite \cite{Adamo:2011pv,Adamo:2012xe,Arkani-Hamed:2013jha}: \bas \mathcal{A}_{k, n}^{tree} = \sum_{(\cP, [n]), |\cP| = k} I(W) <\infty \eas for all sets of external particles.Therefore, any singularities in the integral $I(W)$ must cancel in the sum.
+For a fixed number of propagators and particles, the tree level amplitude of the Wilson loop diagrams is computed as the sum of the $I(W)$ for all $W$ of the correct size.
+By \cite{Adamo:2011pv,Adamo:2012xe,Arkani-Hamed:2013jha} this sum is finite for all sets of external particles, i.e.
+we have \bas \mathcal{A}_{k, n}^{tree} = \sum_{(\cP, [n]), |\cP| = k} I(W) <\infty.
+\eas
+
+In particular, this implies that any singularities in the integrals $I(W)$ must cancel out in the sum.
 In particular, they must cancel on the boundaries of the positroid cells $\Sigma(W)$, analogous to the analysis in \cite{Arkani-Hamed:2013jha}.
-This has been checked for particular classes of examples, \cite{casestudy, AmplituhedronSquared, HeslopStewart}, but has not been proven in general.
-
-In this paper, we consider the denominator $R(W)$, which we define next.
+This has been checked for particular classes of examples (e.g.
+\cite{casestudy, Amplituhedronsquared, HeslopStewart}) but has not been proven in general.
+
+With this motivation in mind, in this paper we study the denominator $R(W)$ of the volume form $\Omega(W)$, which we define next.
 
@@
 
-In section \ref{sec poles}, we show that the denominator $R(W)$ is determined by the positroid cell $\Sigma(W)$ the structure of $W$, as encapulated by $C(W)$.
-In fact, it can be read directly off of $C(W)$, given a characterizeation of $\Sigma(W)$ called the Grassmann necklace.
+In Section \ref{sec poles}, we show that the denominator $R(W)$ is determined by the positroid cell $\Sigma(W)$ and the structure of $W$, as encapsulated by $C(W)$.
+In fact, it can be read directly off of $C(W)$, in terms of characterization of $\Sigma(W)$ called the Grassmann necklace (see Definition~\ref{def:grassmann necklace}).
 We also give an algorithm to read $R(W)$ directly from the Wilson loop diagram, paving the way for a general study of these poles in future.
 
-We end this section with an example illustration $C(W)$ $R(W)$.
+We end this section with an example of computing $C(W)$ and $R(W)$ for a particular Wilson loop diagram $W$.
 
@@
 \eas
+\note{Is the numerator just supposed to be the product of $dc_{pq}$ for each $c_{pq}$ in the matrix? Also I think $c_{46}c_{35} - c_{36}c_{45}$ in the denominator is the wrong way around?}
 \end{eg}
@@
 While this paper primarily approaches proofs from a combinatorial point of view, readers with a background in matroid theory are encouraged to keep the matroidal viewpoint in mind throughout; we expect that the two approaches will be complementary and will build upon each other.
-See [ref][paper 1] for some related results concerning the positroids of Wilson loop diagrams obtained by viewing them primarily as matroids.
+See \cite{generalcombinatoricsI} for some related results concerning the positroids of Wilson loop diagrams obtained by viewing them primarily as matroids.
 \end{rmk}
@@
 
-\note{Sian thinks that a section roadmap here would be overkill: we gave a roadmap in section 1, each subsection has its own little intro roadmap, and I've added a ref to the algorithm above so that people can skip straight to it if they want}
+%\note{Sian thinks that a section roadmap here would be overkill: we gave a roadmap in section 1, each subsection has its own little intro roadmap, and I've added a ref to the algorithm above so that people can skip straight to it if they want}
+
 %In Section~\ref{sec:propagator configs} we examine the structure of admissible Wilson loop diagrams and prove several technical lemmas about configurations of propagators appearing in these diagrams.
@@
 
-% Observe that changing the direction of the propagator simply swaps the inside and outside sets, i.e. for $p = (i,j)$ we have 
-% \[\cP_{in}(p, <_i) = \cP_{out}(p, <_j)\quad \text{ and } \quad \cP_{out}(p, <_i) = \cP_{in}(p, <_j).\]
-
 \begin{eg}
@@
 	\drawnumbers
-	\drawlabeledprop{1}{0}{4}{0}{\footnotesize $p$}
+	\drawlabeledprop{1}{0}{4}{0}{\footnotesize \qquad \ $p$}
 	\drawprop{2}{0}{4}{-1}
@@
 Now suppose $W$ has no propagators of length $3$.
-
-%Given a propagator $p = (i, j)$ oriented $(p, <_i)$,  we can construct two obvious subdiagrams of $W$ by just removing all of the propagators on one side of $p$ and leaving the vertices intact, i.e.
-the subdiagrams
-%\[  (\cP_{in}(p,<_i), [n])  \quad \textrm{and} \quad  (]cP_{out}(p,<_i), [n]).\]
 
@@
 	\begin{scope}
-	\drawWLD{20}{1.5}
+	\drawWLD{15}{2}
 	%\drawnumbers
 	%\drawprop{1}{0}{4}{0}
-	\drawlabeledprop{5}{0}{7}{0}{\footnotesize $p_1$}
-    \drawlabeledprop{3}{0}{12}{0}{\footnotesize $q_1$}
+	\begin{scope}
+	\clip (0,0) circle (\radius cm);
+	\draw[propagator] (\angle*5.3:\radius*1.2cm) to [bend left=50] (\angle*7.7:\radius*1.2cm);
+	\node at (\angle*6.5:\radius*0.6cm) {\footnotesize $p_1$};
+	\end{scope}
+    \drawlabeledprop{3}{0}{10}{0}{\footnotesize \qquad $q_1$}
+    	\node at (\angle*5:\radius*1.15cm) {\footnotesize $j_1$};
+    	\node at (\angle*10:\radius*1.15cm) {\footnotesize $i_1$};
 		\end{scope}
@@
 
-\hlfix{INSERT PICTURE HERE?}{note highlighting this for anyone skimming through looking for pictures to add}
+\note{Sian note to self: come back and check this later, if we end up with code for drawing partial diagrams then that might make a better diagram}
 
@@
 Note that we could replace $q_r$ by another propagator $q'_{r}$ in $W_r$, as long as $p_{r+1}$ and $q_r$ are on opposite sides of $q_r'$: such a new $q'_{r}$ would still satisfy all of the induction hypotheses.
-Therefore without loss of generality we may assume that {\color{violet}$\cP_{in}(q_r)$ does not contain a propagator (other than $q_r$ itself)} \st{$q_r$ is the innermost propagator of length $\geq 4$ in $W_r$} which satisfies the induction hypotheses, i.e.
+Therefore without loss of generality we may assume that $\cP_{in}(q_r)$ does not contain any propagators (other than $q_r$ itself) which satisfy the induction hypotheses, i.e.
 we assume that there are no other propagators with $p_{r+1}$ on one side and $q_r$ on the other.
@@
 
-Specifically, for each $i$ in the support of $p$, define the set
+Specifically, for each $i$ in the support of $p$ we define the set
 \[J_p^{W}(i) = \{m \in [n] \ | \ I^{W}_m(p) = i \},\]
@@
 Now suppose $W$ has more than one propagator.
-Since non-supporting vertices have no effect on Algorithm~\ref{alg:put GN on WLD}, it suffices to prove the result for $W$ {\color{violet} (possibly weakly admissible)} with $F(\emptyset) = \emptyset$.
+Since non-supporting vertices have no effect on Algorithm~\ref{alg:put GN on WLD}, it suffices to prove the result for $W$  (possibly weakly admissible) with $F(\emptyset) = \emptyset$.
 Then by Lemma~\ref{lem sian}, $W$ has at least one of the four situations illustrated in Figure~\ref{fig 3 cases}.
@@
 
-In each of the four cases, when we remove the propagator labelled $p$ we obtain a diagram which satisfies the statement of the theorem by the induction hypothesis, and contains a propagator ${q = (i,j)}$ with no other propagators inside it (with respect to the $<_i$ orientation), although this region may or may not contain non-supporting vertices which we will call $l, l+1, \ldots$ as necessary.
+In each of the four cases, when we remove the propagator labelled $p$ we obtain a diagram which satisfies the statement of the theorem by the induction hypothesis, and contains a propagator ${q = (i,j)}$ with no other propagators inside it (with respect to the $<_i$ orientation).
+Note that this region may or may not contain non-supporting vertices, which we will call $l, l+1, \ldots$ as necessary.
 Let $V$ be the diagram obtained by removing the propagator $p$ from $W$ (Figure \ref{fig V diagram}).
+$V$ is guaranteed to be an admissible diagram, since it was formed by removing a propagator from a diagram that was at least weakly admissible.
 
@@
 Consider the fourth case of Figure~\ref{fig 3 cases} first, as it is the easiest.
-In this case, the vertices $\{l,l+1,l+2,l+3 \}$ which support $p$ in $W$ are non-supporting in $V$, so for every propagator $r$ in $V$ (including $q$) we have $J_r^{V} = J_r^{W}$; these are non-empty cyclic intervals in the correct order by the induction hypothesis.
+In this case, the vertices ${\{l,l+1,l+2,l+3\}}$ which support $p$ in $W$ are non-supporting in $V$, so for every propagator $r$ in $V$ (including $q$) we have $J_r^{V} = J_r^{W}$; these are non-empty cyclic intervals in the correct order by the induction hypothesis.
 Additionally, it is clear from Figure~\ref{fig 3 cases} that $J_p^{W}(l+a) = \{l+a\}$ for $a\in\{1,2,3\}$ and $J_p^{W}(l) = [n] \backslash \{l+1, l+2, l+3\}$.
@@
 
-In $V$ there are no propagators inside $q$, so we see from Figure \ref{fig V diagram} that
+In $V$ there are no propagators inside $q$ by construction, so we see from Figure \ref{fig V diagram} that
 \[l, l+1, \ldots ,j \in J^{V}_q(j) \text{ (if $l$ exists) and }  j+1 \in J^{V}_q(j+1).\]
-Note that $j+2 \not\in J^{V}_q(j+1)$ by Lemma~\ref{lem no fourth vertex}, so  $J^{V}_q(j+1) = \{j+1\}$ and \hlfix{by the induction hypothesis we must have}{moved} $j+2 \in J^{V}_q(i)$.
+Note that $j+2 \not\in J^{V}_q(j+1)$ by Lemma~\ref{lem no fourth vertex}, so  $J^{V}_q(j+1) = \{j+1\}$ and by the induction hypothesis we must have $j+2 \in J^{V}_q(i)$.
 Thus there exist vertices $d,e \in [j+2,i+1]$ with $d <e$, such that
@@
 \textbf{Left two cases}: These cases behave essentially identically (except when $j$ or $j+1$ are not in the support of $p$, which can occur in the second case only; see below) so we handle the majority of the proof for these two cases simultaneously.
-\hlfix{Write $p=(m,m+2)$ where $m\in \{i, i+1, l\}$.}{moved} Let $1\leq a\leq 3$ be the number of non-supporting vertices inside $q$ in $V$ (note that there is at least 1); so these vertices are $l, \ldots, l+a-1$.
+Write $p=(m,m+2)$ where $m\in \{i, i+1, l\}$.
+Let $1\leq a\leq 3$ be the number of non-supporting vertices inside $q$ in $V$ (note that there is at least 1); so these vertices are $l, \ldots, l+a-1$.
 Note that these non-supporting vertices are all in the support of $p$.
 
-We first calculate \hlfix{$I^{W}_w(?)$}{which prop(s), as a function?} for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$.
-Note that $p$ has no effect on other propagators for starting vertices in this range, {\color{violet}(if $r \neq p$, $I_w^W(r) = I_w^V(r)$)} while the value of $I^{W}_w(p)$ depends on \st{how soon $q$ is assigned to a vertex, i.e.
-on}\sanote{don't like the phrasing ``soon''} the value of $I^{V}_w(q)$.
+We first calculate $I^{W}_w$ for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$.
+Note that $p$ has no effect on other propagators for starting vertices in this range, so if $r \neq p$, then $I_w^W(r) = I_w^V(r)$.
+Meanwhile, the value of $I^{W}_w(p)$ depends on which step in the algorithm the propagator $q$ is assigned to a vertex, i.e.
+on the value of $I^{V}_w(q)$.
 Thus, if $w\in J_q^{V}(i)$ then
@@
       \]
-We also need to understand $I^{W}_w$ for $w \in \{l,l+1,\ldots,j,j+1\}$.
-For the \hlfix{majority}{$w \in [l, l+a-1]$} of these vertices, we use the following observation: if $p$ is the first propagator to be assigned a value by \hlfix{$I_w^{W}$, then the remainder of $I_w^{W}$}{$I_w$ instead of $I_w^W$?} proceeds identically to the assignments of $I^{V}_{w+1}$.
+We also need to understand $I^{W}_w$ for $w \in \{l,l+1,\ldots,j,j+1\}$. For the majority 
+%$w \in [l, l+a-1]$} 
+%I left this as a comment so we can add it in if necessary, but I don't think we need this level of precision in this sentence: we're just signposting what we're going to do in detail shortly.
+of these vertices, we use the following observation: if $p$ is the first propagator to be assigned a value by $I_w^{W}$, then the remainder of $I_w^{W}$ proceeds identically to the assignments of $I^{V}_{w+1}$.
 Thus we have for any $0\leq b <a$
@@
 
-Consider the \st{WLD} {\color{violet} weakly admissible Wilson loop diagram}\sanote{actually, I think this is admissible, because we are removing a propagator from a weakly admissible.
-But it needs a few words?} $X$ formed from $V$ by \st{moving the second end of $q$ to the edge $j-1$ instead of $j$} {\color{violet} replacing the propagator $q = (i,j)$ with $q = (i, j-1)$}.
-$X$ is still {\color{violet}weakly} admissible since we have not decreased the support of any set of propagators, so the induction hypothesis applies to it as well.
-Note that $J_{j}^{V}(r) = J_{j}^{X}(r)$ for all $r\neq p$ {\color{violet}and in particular for $r=q$.
-Further, } \st{and} $J_{j}^{X}(r) = J_{j+1}^{X}(r)$ for $r\neq q,p$.
-Additionally $I_{j+1}^{X}(q) = i$ \st{by the induction hypothesis applied to $X$}, {\color{violet}because} \st{and so} if we start at $j+1$ and assign propagators to vertices according to the algorithm, when we reach vertex $i$ in $X$ all propagators other than $q$ must have been assigned.
+Consider the Wilson loop diagram $X$ formed from $V$ by replacing the propagator $q = (i,j)$ with $q = (i, j-1)$; \note{Added a note about $V$ being admissible when we defined it, so we can use $X$ admissible here without comment} $X$ is still admissible since we have not decreased the support of any set of propagators.
+% From the diagram we can see that $J_{j}^{V}(r) = J_{j}^{X}(r)$ for all $r\neq p$ (and in particular for $r=q$) and $J_{j}^{X}(r) = J_{j+1}^{X}(r)$ for $r\neq q,p$.  
+It follows from the position of $q$ in $X$ that $I_j^X(q) = j$, and from Lemma~\ref{lem no fourth vertex} that $I_{j+1}^X(q) \neq j$.
+By the induction hypothesis, we must therefore have $I_{j+1}^X(q) = i$; in particular, this means that if we start at $j+1$ and assign propagators to vertices according to the algorithm, when we reach vertex $i$ in $X$ all propagators other than $q$ must have been assigned.
+
 Therefore if we start at $j$ in $W$, we first assign $q$ to $j$ then proceed to assign as in $X$ starting at $j+1$, and hence when we get to $i$ the only remaining unassigned propagator is $p$.
-Therefore
+We obtain
        \[
@@
        \] 
-Finally, we consider what happens when we start the algorithm at vertex $j+1$. If $j+1$ is in the support of $p$ then we can argue as above to get
+This completes the analysis of $I_j^W$. Finally, we consider what happens when we start the algorithm at vertex $j+1$. If $j+1$ is in the support of $p$ then we can argue as above to get
 \[
@@
 If we start at $j+1$ we need to know whether there are any unassigned propagators supported on edge $i$ when we reach vertex $i$.
-We already know that $J_q^{V}(j+1) = \{j+1\}$; \hlfix{in particular this means that $q$ contributes $i$ in $I_{j+2}^{V}$}{why?
-It is true but what does it follow from?
-The next few lines?}.
-However the construction of $I^{V}_{j+1}$ first associates $q$ to $j+1$ and \hlfix{then proceeds identically to $I^{V}_{j+2}$.}{We use this fact a lot should it be a lemma?}  In particular if $i$ was assigned in $I^{V}_{j+1}$, then it would not be available to assign to $q$ in $I^{V}_{j+2}$ as all other propagators supported at $i$ in $V$ come before $q$.
-
-Therefore $p$ is the only potentially unassigned propagator on edge $i$ when we reach vertex $i$ in $W$ {\color{violet} in the algorithm for $I_{j+1}^W$}, and
+We already know that $J_q^{V}(j+1) = \{j+1\}$; in particular this means that $q$ contributes $i$ in $I_{j+2}^{V}$, by the induction hypothesis applied to $V$.
+However the construction of $I^{V}_{j+1}$ first assigns $q$ to $j+1$ and then proceeds identically to $I^{V}_{j+2}$.
+In particular if $i$ was assigned in $I^{V}_{j+1}$, then it would not be available to assign to $q$ in $I^{V}_{j+2}$ as all other propagators supported at $i$ in $V$ come before $q$.
+
+Therefore $p$ is the only potentially unassigned propagator on edge $i$ when we reach vertex $i$ in the algorithm for $I_{j+1}^W$, and
     \[
@@
 For $r \neq p$ the intervals are clearly still cyclic and appear in the correct order, and we can assemble the intervals for the $J_p^{W}(*)$ as follows.
+Recall that $p = (m,m+2)$, $1 \leq a \leq 3$ is the number of non-supporting vertices inside $q$ in $V$, and these non-supporting vertices are denoted $\{l,l+1, \dots\}$.
     \begin{itemize}
@@
     \end{gather*}
-    which are nonempty and otherwise as required. {\color{violet}Here, $d$ is as in display \eqref{deeqs}.}
+    which are nonempty and otherwise as required. Recall that $d$ was defined in equation \eqref{deeqs}.
   \item If $m=i$ then $a=1$ or $a=2$, in the former case $l=m+2$, $j=m+3$ and $j+1$ is not in the support of $p$ so
@@
 \begin{itemize}
-\item if $m=j$ then
+\item If $m=j$ then
 \begin{gather*}J_p^{W}(m) = [m+4,e-1], \qquad  J_p^{W}(m+1) = [e,m], \\  J_p^{W}(m+2) = [m+1,m+2], \qquad  J_p^{W}(m+3) = \{m+3\},\end{gather*}
-\item if $m=j+1$ then
+Recall that $e$ was defined in equation \eqref{deeqs}.
+\item If $m=j+1$ then
 \begin{gather*}J_p^{W}(m) = [m+4,m-1], \qquad J_p^{W}(m+1) = [m,m+1], \\  J_p^{W}(m+2) = \{m+2\}, \qquad  J_p^{W}(m+3) = \{m+3\},\end{gather*}
-\item if $m=j+2$ then
+\item If $m=j+2$ then
 \begin{gather*}J_p^{W}(m) = [m+4,m], \qquad  J_p^{W}(m+1) = \{m+1\}, \\  J_p^{W}(m+2) = \{m+2\}, \qquad  J_p^{W}(m+3) = \{m+3\}.\end{gather*}
@@
 
-\st{One of the most important uses of this lemma is for bases.}  The lemma says that a subset $J$ of $[n]$ is a basis of $M(W)$ if and only if there is a set bijection between $J$ and $\cP$ with the property that for each $j\in J$ the propagator associated to $j$ under the bijection is supported on vertex $j$.
-
-{\color{violet} This is equivalent to the condition for a set to be independent  or a basis established in Lemma 3.5 and Theorem 3.6 of \cite{wilsonloop}.
-The equivalence can ben seen by applications of the the pigeon hole principle directly in one direction, and inductively in the other.
+In particular, this lemma says that a subset $J$ of $[n]$ is a basis of $M(W)$ if and only if there is a set bijection between $J$ and $\cP$ with the property that for each $j\in J$ the propagator associated to $j$ under the bijection is supported on vertex $j$.
+
+This is equivalent to the condition for a set to be independent or a basis established in Lemma 3.5 and Theorem 3.6 of \cite{wilsonloop}.
+The equivalence can be seen by applications of the the pigeonhole principle in one direction, and inductively in the other.
 Below, we provide a different proof of this condition for independence.
-Note that either definition of independence and bases corresponds to the sets independent columns and bases of $C(W)$.}
+\hlfix{Note that either definition of independence and bases corresponds to the sets independent columns and bases of $C(W)$.}{I'm having trouble parsing this sentence: help?}
 
@@
 \end{proof}
+
+\note{Sian is here}
 
@@
 Now suppose that $i \in I_i$.
-Let $p$ be the propagator which contributes $i$ to $I_i$, that is, {\color{violet} $I^W_i(p) = i$}; thus one end of $p$ must lie on either edge $i-1$ or edge $i$.
-In both cases let $b$ denote the edge supporting the other end of $p$, {\color{violet}that is, $p = (i, b)$ or $p = (i-1, b)$.}
-\sanote{We use taking and contributing interchangably. Do we want to normalize? I vote for contributing}
+Let $p$ be the propagator which contributes $i$ to $I_i$, that is $I^W_i(p) = i$; thus one end of $p$ must lie on either edge $i-1$ or edge $i$.
+In both cases let $b$ denote the edge supporting the other end of $p$, i.e.
+$p = (i, b)$ or $p = (i-1, b)$.
 
@@
 The positroid cells associated to the Amplituhedron are of dimension $4|\cP|$.
-In \cite{orientation}, Marcott and the first author show that the dimension of the Deodhar component is $|\cP| +$ the dimension of associated positroid cell.
+In \cite{non-orientable}, Marcott and the first author show that the dimension of the Deodhar component is $|\cP| +$ the dimension of associated positroid cell.
 In otherwords, the Deodhar component associated to a Wilson loop diagram is $4|\cP|$, showing that the geometry underlying the Wilson loop diagrams is consistent with the geometry underlying the Amplituhedron.
@@
 
-%\bibliographystyle{plain}
-%\bibliography{C:/Users/agarws1/Documents/GitHub/OldWLDPapers/Bibliography}
-
-\begin{thebibliography}{10}
-\bibitem{Adamo:2011pv}
-Tim Adamo, Mathew Bullimore, Lionel Mason, and David Skinner.
-\newblock {Scattering Amplitudes and Wilson Loops in Twistor Space}.
-\newblock {\em J.Phys.A}, A44:454008, 2011.
-
-\bibitem{Adamo:2012xe}
-Tim Adamo and Lionel Mason.
-\newblock {Twistor-strings and gravity tree amplitudes}.
-\newblock {\em Class.Quant.Grav.}, 30:075020, 2013.
-
-\bibitem{wilsonloop}
-Susama Agarwala and Eloi~Marin Amat.
-\newblock Wilson loop diagrams and positroids.
-\newblock {\em Communications in Mathematical Physics}, 2016.
-\newblock arXiv:1509.06150.
-
-\bibitem{casestudy}
-Susama Agarwala and Sian Fryer.
-\newblock A study in $\textrm{Gr}_{\geq 0}(2,6)$: from the geometric case book
-  of {W}ilson loop diagrams and {SYM} $n=4$.
-\newblock arXiv:1803.00958.
-
-\bibitem{non-orientable}
-Susama Agarwala and Cameron Marcott.
-\newblock Wilson loops in sym $n=4$ do not parametrize an orientable space.
-\newblock arXiv:1807.05397.
-
-\bibitem{UnwindingAmplituhedron}
-Nima Arkani-Hamed, Hugh Thomas, and Jaroslav Trnka.
-\newblock Unwinding the amplituhedron in binary.
-\newblock {\em Journal of High Energy Physics}, 2018(1):16, Jan 2018.
-\newblock arXiv:1704.05069.
-
-\bibitem{Arkani-Hamed:2013kca}
-Nima Arkani-Hamed and Jaroslav Trnka.
-\newblock {Into the Amplituhedron}.
-\newblock {\em JHEP}, 12:182, 2014.
-
-\bibitem{Arkani-Hamed:2013jha}
-Nima Arkani-Hamed and Jaroslav Trnka.
-\newblock {The Amplituhedron}.
-\newblock {\em JHEP}, 10:30, 2014.
-
-\bibitem{Boels:2007qn}
-Rutger Boels, Lionel Mason, and David Skinner.
-\newblock {From twistor actions to MHV diagrams}.
-\newblock {\em Phys.Lett.}, B648:90--96, 2007.
-
-\bibitem{Bullimore:2010pj}
-Mathew Bullimore, Lionel Mason, and David Skinner.
-\newblock {MHV Diagrams in Momentum Twistor Space}.
-\newblock {\em JHEP}, 1012:032, 2010.
-
-\bibitem{CasteelsPaths}
-K. Casteels.
-\newblock Quantum matrices by paths.
-\newblock {\em Algebra Number Theory}, 8(8):1857--1912, 2014.
-
-\bibitem{Amplituhedronsquared}
-Burkhard Eden, Paul Heslop, and Lionel Mason.
-\newblock The AmplituhedronSquared.
-\newblock 2017.
-\newblock arxiv:1701.00453.
-
-\bibitem{galashinlam}
-P.~{Galashin} and T.~{Lam}.
-\newblock {Parity duality for the amplituhedron}.
-\newblock {\em arXiv e-prints}, May 2018.
-
-\bibitem{HeslopStewart}
-Paul Heslop and Alastair Stewart.
-\newblock The twistor wilson loop and the amplituhedron.
-\newblock {\em Journal of High Energy Physics}, 2018(10):142, Oct 2018.
-
-\bibitem{Hodges:2012ym}
-Andrew Hodges.
-\newblock {A simple formula for gravitational MHV amplitudes}.
-\newblock 2012.
-
-\bibitem{AmplituhedronDecomposition}
-Steven~N. Karp, Lauren~K. Williams, and Yan~X. Zhang.
-\newblock Decompostions of amplituhedra.
-\newblock arXiv:1708.09525.
-
-\bibitem{GrassmannAmplitudebook}
-Freddy Cachazo Alexander Goncharov Alexander Postnikov Jaroslav~Trnka
-  Nima~{A}rkani {H}amed, Jacob~Bourjaily.
-\newblock {\em Grassmannian Geometry of Scattering Amplitudes}.
-\newblock Cambridge University Press, Cambridge, UK, 2016.
-
-\bibitem{LipsteinMason}
-Arthur E. Lipstein, Lionel Mason
-\newblock From dlogs to dilogs; the super Yang-Mills MHV amplitude revisited
-\newblock J. High Energ. Phys. (2014) 2014: 169.
-
-\bibitem{reversingOh}
-S. Agarwala, S. Fryer.
-\newblock An algorithm to construct the Le diagram associated to a Grassmann necklace
-\newblock \url{arXiv:1803.01726}
-
-\bibitem{Gale}
-D. Gale.
-\newblock Optimal assignments in an ordered set: {A}n application of matroid theory.
-\newblock {\em J. Combinatorial Theory}, 4: 176 - 180 (1968).
-
-\bibitem{Oh}
-S. Oh.
-\newblock Positroids and {S}chubert matroids.
-\newblock {\em J. Combin. Theory Ser. A}, 118(8):2426--2435, (2011)
-
-\bibitem{Oh2}
-  S. Oh.
-  \newblock Combinatorics of positroids.
-  \newblock {\em DMTCS Proceedings vol. AK},(FPSAC 2009), 721--732
-
-\bibitem{Postnikov}
-A.~Postnikov.
-\newblock Total positivity, {G}rassmannians, and networks.
-\newblock \url{arXiv:math/0609764}.
-
-\end{thebibliography}
+\bibliographystyle{abbrv}
+\bibliography{WLDbib}
+
+% \begin{thebibliography}{10}
+% \bibitem{Adamo:2011pv}
+% Tim Adamo, Mathew Bullimore, Lionel Mason, and David Skinner.
+% \newblock {Scattering Amplitudes and Wilson Loops in Twistor Space}.
+% \newblock {\em J.Phys.A}, A44:454008, 2011.
+
+% \bibitem{Adamo:2012xe}
+% Tim Adamo and Lionel Mason.
+% \newblock {Twistor-strings and gravity tree amplitudes}.
+% \newblock {\em Class.Quant.Grav.}, 30:075020, 2013.
+
+% \bibitem{wilsonloop}
+% Susama Agarwala and Eloi~Marin Amat.
+% \newblock Wilson loop diagrams and positroids.
+% \newblock {\em Communications in Mathematical Physics}, 2016.
+% \newblock arXiv:1509.06150.
+
+% \bibitem{casestudy}
+% Susama Agarwala and Sian Fryer.
+% \newblock A study in $\textrm{Gr}_{\geq 0}(2,6)$: from the geometric case book
+%   of {W}ilson loop diagrams and {SYM} $n=4$.
+% \newblock arXiv:1803.00958.
+
+% \bibitem{non-orientable}
+% Susama Agarwala and Cameron Marcott.
+% \newblock Wilson loops in sym $n=4$ do not parametrize an orientable space.
+% \newblock arXiv:1807.05397.
+
+% \bibitem{UnwindingAmplituhedron}
+% Nima Arkani-Hamed, Hugh Thomas, and Jaroslav Trnka.
+% \newblock Unwinding the amplituhedron in binary.
+% \newblock {\em Journal of High Energy Physics}, 2018(1):16, Jan 2018.
+% \newblock arXiv:1704.05069.
+
+% \bibitem{Arkani-Hamed:2013kca}
+% Nima Arkani-Hamed and Jaroslav Trnka.
+% \newblock {Into the Amplituhedron}.
+% \newblock {\em JHEP}, 12:182, 2014.
+
+% \bibitem{Arkani-Hamed:2013jha}
+% Nima Arkani-Hamed and Jaroslav Trnka.
+% \newblock {The Amplituhedron}.
+% \newblock {\em JHEP}, 10:30, 2014.
+
+% \bibitem{Boels:2007qn}
+% Rutger Boels, Lionel Mason, and David Skinner.
+% \newblock {From twistor actions to MHV diagrams}.
+% \newblock {\em Phys.Lett.}, B648:90--96, 2007.
+
+% \bibitem{Bullimore:2010pj}
+% Mathew Bullimore, Lionel Mason, and David Skinner.
+% \newblock {MHV Diagrams in Momentum Twistor Space}.
+% \newblock {\em JHEP}, 1012:032, 2010.
+
+% \bibitem{CasteelsPaths}
+% K. Casteels.
+% \newblock Quantum matrices by paths.
+% \newblock {\em Algebra Number Theory}, 8(8):1857--1912, 2014.
+
+% \bibitem{Amplituhedronsquared}
+% Burkhard Eden, Paul Heslop, and Lionel Mason.
+% \newblock The AmplituhedronSquared.
+% \newblock 2017.
+% \newblock arxiv:1701.00453.
+
+% \bibitem{galashinlam}
+% P.~{Galashin} and T.~{Lam}.
+% \newblock {Parity duality for the amplituhedron}.
+% \newblock {\em arXiv e-prints}, May 2018.
+
+% \bibitem{HeslopStewart}
+% Paul Heslop and Alastair Stewart.
+% \newblock The twistor wilson loop and the amplituhedron.
+% \newblock {\em Journal of High Energy Physics}, 2018(10):142, Oct 2018.
+
+% \bibitem{Hodges:2012ym}
+% Andrew Hodges.
+% \newblock {A simple formula for gravitational MHV amplitudes}.
+% \newblock 2012.
+
+% \bibitem{AmplituhedronDecomposition}
+% Steven~N. Karp, Lauren~K. Williams, and Yan~X. Zhang.
+% \newblock Decompostions of amplituhedra.
+% \newblock arXiv:1708.09525.
+
+% \bibitem{GrassmannAmplitudebook}
+% Freddy Cachazo Alexander Goncharov Alexander Postnikov Jaroslav~Trnka
+%   Nima~{A}rkani {H}amed, Jacob~Bourjaily.
+% \newblock {\em Grassmannian Geometry of Scattering Amplitudes}.
+% \newblock Cambridge University Press, Cambridge, UK, 2016.
+
+% \bibitem{LipsteinMason}
+% Arthur E. Lipstein, Lionel Mason
+% \newblock From dlogs to dilogs; the super Yang-Mills MHV amplitude revisited
+% \newblock J. High Energ. Phys. (2014) 2014: 169.
+
+% \bibitem{reversingOh}
+% S. Agarwala, S. Fryer.
+% \newblock An algorithm to construct the Le diagram associated to a Grassmann necklace
+% \newblock \url{arXiv:1803.01726}
+
+% \bibitem{Gale}
+% D. Gale.
+% \newblock Optimal assignments in an ordered set: {A}n application of matroid theory.
+% \newblock {\em J. Combinatorial Theory}, 4: 176 - 180 (1968).
+
+% \bibitem{Oh}
+% S. Oh.
+% \newblock Positroids and {S}chubert matroids.
+% \newblock {\em J. Combin. Theory Ser. A}, 118(8):2426--2435, (2011)
+
+% \bibitem{Oh2}
+%   S. Oh.
+%   \newblock Combinatorics of positroids.
+%   \newblock {\em DMTCS Proceedings vol. AK},(FPSAC 2009), 721--732
+
+% \bibitem{Postnikov}
+% A.~Postnikov.
+% \newblock Total positivity, {G}rassmannians, and networks.
+% \newblock \url{arXiv:math/0609764}.
+
+% \end{thebibliography}
 

### 2019-06-14 GWLDCI.tex
addressed Sian's comments on 3.25

@@
 
-By the third point of Lemma \ref{maxexactcomplementrank}, the complementary flat, $F(P)$ has full rank: $\rk(F(P)) = |P|$.
+By the third point of Lemma \ref{maxexactcomplementrank}, the complementary flat, $F(P)$ has rank equal to the number of propagators: $\rk(F(P)) = |P|$.
 Let $B \subset F(P)$ be a maximal independent subset of $F(P)$: $\rk (B) = |P|$.
@@
 Recall that these sets $\{P_i\}$ and $\{P_i'\}$ partition the propagator sets $\cP$ and $\cP'$ of $W$ and $W'$ respectivley.
-Let $\mathcal{F}$ and $\mathcal{F}'$ the respective complementary vertices: \bas \mathcal{F} = \{F_i = V(P_i)^c | (P_i, V(P_i)) \in \mathcal{R}\} \quad  \mathcal{F}' = \{F_i' = V(P'_i)^c | (P'_i, V(P'_i)) \in \mathcal{R}\} \;.\eas By Theorem \ref{maxexactcomplementrank}, every $F_i$ and $F_i'$ is a cyclic flat of full rank in $M$.
+Let $\mathcal{F}$ and $\mathcal{F}'$ the respective complementary vertices: \bas \mathcal{F} = \{F_i = V(P_i)^c | (P_i, V(P_i)) \in \mathcal{R}\} \quad  \mathcal{F}' = \{F_i' = V(P'_i)^c | (P'_i, V(P'_i)) \in \mathcal{R}\} \;.\eas By Theorem \ref{maxexactcomplementrank}, every $F_i$ and $F_i'$ is a cyclic flat in $M$.
+They are also propagator flats in $W$ and $W'$ of rank equal to the number of propagators defining it.
 We claim that $\mathcal{F} = \mathcal{F'}$.
@@
 If not, there would be a cyclic flat $F_j$ of $M$.
-Without loss of generality, write $F_j \in \mathcal{F} \setminus \mathcal{F'}$.
+Without loss of generality, write $F_j \in \mathcal{F} \setminus \mathcal{F}'$.
 We may write $F_j = V(P_j)^c$, with $(P_j, V(P_j))$ a maximal exact subdiagram in $W$.
 By Lemma \ref{lem facts about WLD matroids} (5), we may write $F_j= F(Q)$ as a propagator flat.
+Therefore, Lemma \ref{maxexactcomplementrank}, $\rk(F_j) = |Q|$.
 By Lemma \ref{contractsubdiaglem}, $M/F(Q) = F/F_j = M(Q^c, V(Q^c))$, which is uniform, by construction of $F_j$.
@@
 Since this exact subdiagram is not in $\mathcal{R}'$ by construction of $F_j$, it is not a maximal exact subdiagram of $W'$.
-That is, there is a maximal exact subdiagram containing it: $(Q^c, V(Q^c)) \subset (P_j', V(P_j'))$.
-Suppose $|P_j' \setminus Q^c| = m$.
-By counting vertices of the two nested sets $F_j' \subset F_j$ we see that  \bas |F_j| = n -|Q^c| -3  \textrm{ while } |F_j'| = n -|P_j'| -3 = n -|Q^c| -m -3\;.\eas That is, $F_j'$ has $m$ more vertices than $F_j$.
-Furthermore, by construction $\rk(F_j) + m = \rk (F_j')$.
-This violates the assumption that both $F_j$ and $F_j'$ are cyclic flats.
-
-Therefore, we see that $\mathcal{F} = \mathcal{F'}$, which implies that the maximally exact subdiagrams of $W$ and $W'$, are supported on the same vertex sets.
+That is, there is a maximal exact subdiagram containing it: $(Q^c, V(Q^c)) \subsetneq (P_j', V(P_j'))$.
+Thus there is a $F_j' \in \mathcal{R}'$ such that $F_j' \subsetneq F_j$.
+We show that $F_j$ is not a cyclic flat.
+
+Suppose the exact diagram  $(P_j', V(P_j'))$ has $m$ more propagators than $(Q^c, V(Q^c))$: $|P_j' \setminus Q^c| = m$.
+Since $(P_j', V(P_j'))$ defines a uniform matroid, any subset of vertices numbering fewer than the number of propagators in $P_j'$ forms an independent flat of $M(P_j', V(P_j'))$, and thus an independent set of $M$.
+\sanote{is it worth citing a result that says for $W \subset W'$, if $V$ independent in $M(W)$ then also independent in $M(W')$?} Next, compare the number of vertices in $F_j'$ and $F_j$ to see that $F_j'$ has $m$ more vertices than $F_j$:  \bas |F_j| = n -|Q^c| -3  \textrm{ while } |F_j'| = n -|P_j'| -3 = n -|Q^c| -m -3\;.\eas So $|F_j \setminus F_j' | = m$ and $F_j \setminus F_j' = V(P_j')\setminus V(Q^c)$.
+Thus $F_j \setminus F_j'$ is an independent set in $M$.
+Therefore $F_j$ is the union of a cyclic flat, $F_j'$, and an independent set, $F_j \setminus F_j'$.
+Therefore, $F_j$ is not a cyclic flat.
+Therefore, $F_j \not \in \mathcal{F} \setminus \mathcal{F}'$.
+Therefore, $\mathcal{F} = \mathcal{F}'$, as claimed.
+
+Since $\mathcal{F} = \mathcal{F'}$, the maximally exact subdiagrams of $W$ and $W'$, are supported on the same vertex sets.
 All propagators of $W$ and $W'$ are accounted for in these sets.

### 2019-06-14 GWLDCII.tex
got rid of the bad uses of the word take

@@
 \textbf{Case I}:  Suppose $p$ has one end on edge $i-1$.
-\st{Then} {\color{violet}If} $p$ is not supported on $i+1$, \st{so} in building $I_{i+1}$ \hlfix{we will take the same propagators as in the construction of $I_i$from vertices $i+1$ up to $b-1$, that is $I_{i+1} \cap [i+1,b-1] = I_{i} \cap [i+1,b-1]$}{Lemma-ize?}.
-{\color{violet} (If $p$ is supported on $i+1$, $b= i+1$ and the interval $[i+1,b-1]$ is emptry.)} Furthermore, by Lemma~\ref{vertex cyclic int lem}, when building $I_{i+1}$ it must happen that $p$ is taken \st{at} {\color{violet} by?} vertex $b$, as otherwise $b$ would never be contributed by $p$.
+\st{Then} {\color{violet}If} $p$ is not supported on $i+1$, \st{so} in building $I_{i+1}$ \hlfix{we will assign the same propagators as in the construction of $I_i$from vertices $i+1$ up to $b-1$, that is $I_{i+1} \cap [i+1,b-1] = I_{i} \cap [i+1,b-1]$}{Lemma-ize?}.
+{\color{violet} (If $p$ is supported on $i+1$, $b= i+1$ and the interval $[i+1,b-1]$ is emptry.)} Furthermore, by Lemma~\ref{vertex cyclic int lem}, when building $I_{i+1}$ it must happen that $p$ contributes vertex $b$, as otherwise $b$ would never be contributed by $p$.
 Consequently, in building $I_{i+1}$, when the algorithm reaches vertex $b$ there cannot be any unassigned propagators remaining that are \hlfix{before}{do we have an ordering on $\cP$?} $p$.
@@
 In both cases, since $I_{i-1}(p)\neq a$ by assumption it follows from Lemma~\ref{vertex cyclic int lem} that $I_{i-1}(p) <_{i-1} a$ and no other vertex supporting $p$ lies between $I_{i-1}(p)$ and $a$.
-In the case that $b<_i a$ and $q$ is taken before $p$ in $I_i$, this means that $I_{i-1}(p)=b$ and so $I_{i-1}(q)\neq b$.
+In the case that $b<_i a$ and $q$ is assigned before $p$ in $I_i$, this means that $I_{i-1}(p)=b$ and so $I_{i-1}(q)\neq b$.
 Thus $q\in S_i$ and so $f$ is a factor of $r_i$.

### 2019-06-14 GWLDCII.tex
added a remark regarding when things are exactly the same

@@
 \begin{algorithm}\label{alg:put GN on WLD}
-Let $W = (\cP, [n])$ be an admissible Wilson loop diagram. This gives an algorithm for constructing the set $I_i$, for $i \in [n]$.
+Let $W = (\cP, [n])$ be an admissible Wilson loop diagram. This gives an algorithm for constructing the set $I_i^W$ (or just $I_i$ when $W$ is clear from context), for $i \in [n]$.
 
 \begin{enumerate}
-\item Fix a vertex $i \in [n]$, the {\bf starting vertex}. Set $j:=i$ and $I_i = \emptyset$.
+\item Fix a vertex $i \in [n]$, the {\bf starting vertex}. Set $j:=i$ and $I_i^W = \emptyset$.
 \item While $\cP \neq \emptyset$, perform the following steps:
@@
 Else, let $p \in \Prop(j)$ be the clockwise most propagator supported on $j$.
-Write $I_i = I_i\cup \{j\}$, and delete propagator $p$ from the diagram.
+Write $I_i^W = I_i^W\cup \{j\}$, and delete propagator $p$ from the diagram.
 \item Increment $j$ by 1 and repeat from (a).
@@
 
+\begin{rmk}
+The following observation will be very useful in many of the arguments below.
+
+Suppose we are going through the algorithm to construct $I_i^W$ and we are currenctly at step $j$ of the loop.
+Consider the diagram $W'$ formed by $W$ with all the propagators already contributed removed; think of a vertex being taken away when it is contributed, since it can only contribute once, so it is gone from the point of view of the rest of the construction of $I_i^W$.
+Now suppose for some other diagram $V$ on the same vertex set we are constructing $I_k^V$ and we are at step $j$ of the loop, for the same $j$ as above.
+Again let $V'$ be $V$ with all the propagators already contributed removed.
+
+With this setup, if there is an interval, $(j-1, \ldots, \ell+1)$ (with $\ell <_i i$ and $\ell <_k k$) in $W'$ and $V'$ where the propagators ending in that interval are identical in both diagrams, then the construction of $I_i^W$ and $I_k^V$ is identical up to and including step $\ell$.
+The constructions are identical for those steps simply because the local situation of propagators supported at $j, j+1, \ldots, \ell$ is identical in both cases and the algorithm only sees the local situation at the vertex corresponding to the current step.
+\end{rmk}
+
+With that in mind we are ready to begin proving properties of the algorithm.
 We first show that the algorithm can never reach the final vertex in a propagator's support without having already assigned that propagator; in particular, this guarantees that the construction of $I_i$ always terminates in fewer than $n$ steps.

### 2019-06-14 GWLDCII.tex
turned lemma 3.14 into cor 2.11

@@
 In other words, the independent sets of $M(W)$ correspond to sets of vertices in $W$ in which no subset supports fewer propagators than the vertices it contains.
+
+One useful corollary of this, which we will want to keep in mind later, is the following.
+\begin{cor}\label{lem basis as perm}
+Let $W = (\cP,[n])$ be an admissible Wilson loop diagram and let $M(W)$ be its associated matroid.
+A subset $J \subseteq [n]$ is an independent set of $M(W)$ if and only if there exists an injective set map $f : J \rightarrow \cP$ with the property that for each $j\in J$ we have $j \in V(f(j))$.
+\end{cor}
+
+\begin{proof}
+  This follows as a corollary of the previous theorem by induction in one direction and the pigeonhole principle in the other direction.
+
+Forgetting about the matroid and simply thinking about the condition of linear independence in the matrix $C(W)$, the corollary can also be proved directly by linear algebra and the definition of $C(W)$ as follows: because the nonzero entries of $C(W)$ are independent indeterminants, $J$ is an independent set is if and only if there is some choice of $|J|$ nonzero entries of $C(W)$ one in each row associated to an element of $J$ and each in different columns.
+Each entry in $C(W)$ identifies a propagator by the row of the entry and a vertex by the column of the entry.
+The entry is nonzero if and only if the propagator is supported on that vertex.
+Consequently, a choice of $|J|$ nonzero entries of $C(W)$ one in each row associated to an element of $J$ and each in different columns is equivalent to an assignment of the propagators of $J$ to supporting vertices so that no two are assigned to the same vertex.
+Such an assignment of the propagators of $J$ to supporting vertices is exactly a map $f$ as described in the statment, hence proving the result.
+\end{proof}
+
+In particular, this corollary says that a subset $J$ of $[n]$ is a basis of $M(W)$ if and only if there is a set bijection between $J$ and $\cP$ with the property that for each $j\in J$ the propagator associated to $j$ under the bijection is supported on vertex $j$.
 
@@
 
-We need one more lemma before we can prove that Algorithm~\ref{alg:put GN on WLD} does in fact give the Grassmann necklace of the positroid associated to $W$.
-
-\begin{lem}\label{lem basis as perm}
-Let $W = (\cP,[n])$ be an admissible Wilson loop diagram and let $M(W)$ be its associated matroid.
-A subset $J \subseteq [n]$ is an independent set of $M(W)$ if and only if there exists an injective set map $f : J \rightarrow \cP$ with the property that for each $j\in J$ we have $j \in V(f(j))$.
-\end{lem}
-
-In particular, this lemma says that a subset $J$ of $[n]$ is a basis of $M(W)$ if and only if there is a set bijection between $J$ and $\cP$ with the property that for each $j\in J$ the propagator associated to $j$ under the bijection is supported on vertex $j$.
-
-This is equivalent to the condition for a set to be independent or a basis established in Lemma 3.5 and Theorem 3.6 of \cite{wilsonloop}.
-The equivalence can be seen by applications of the the pigeonhole principle in one direction, and inductively in the other.
-Below, we provide a different proof of this condition for independence.
-\hlfix{Note that either definition of independence and bases corresponds to the sets independent columns and bases of $C(W)$.}{I'm having trouble parsing this sentence: help?}
-
-\begin{proof} \sanote{ I would still argue that this should be moved to section 2.
-That is the only place we talk about matroids and positroid associated to Wilson loop diagrams.
-While this is a general linear algebra result, it does reference $C(W)$ several times in the proof.}
-Because the nonzero entries of $C(W)$ are independent indeterminants, $J$ is an independent set is if and only if there is some choice of $|J|$ nonzero entries of $C(W)$ one in each row associated to an element of $J$ and each in different columns.
-
-Each entry in $C(W)$ identifies a propagator by the row of the entry and a vertex by the column of the entry.  The entry is nonzero if and only if the propagator is supported on that vertex.
-
-Consequently, a choice of $|J|$ nonzero entries of $C(W)$ one in each row associated to an element of $J$ and each in different columns is equivalent to an assignment of the propagators of $J$ to supporting vertices so that no two are assigned to the same vertex.
-Such an assignment of the propagators of $J$ to supporting vertices is exactly a map $f$ as described in the statment, hence proving the result.
-\end{proof}
+We are now ready to prove that Algorithm~\ref{alg:put GN on WLD} does in fact give the Grassmann necklace of the positroid associated to $W$.
 
@@
 \end{itemize}
-The first point follows immediately: since the algorithm is pairing each $j \in I_i$ with a unique propagator supported on that vertex, $I_i$ is a basis for $M(W)$ by Lemma~\ref{lem basis as perm}.
+The first point follows immediately: since the algorithm is pairing each $j \in I_i$ with a unique propagator supported on that vertex, $I_i$ is a basis for $M(W)$ by Corollary~\ref{lem basis as perm}.
 
 Now suppose we have a $k$-set $J$ such that $J$ is a basis for $M(W)$ and yet is lexicographically less than $I_i$ with respect to $<_i$.
-By Lemma~\ref{lem basis as perm} there is a set bijection between $J$ and the propagators of $W$ such that for each $j \in J$, the propagator associated to $j$ is supported on vertex $j$.
+By Corollary~\ref{lem basis as perm} there is a set bijection between $J$ and the propagators of $W$ such that for each $j \in J$, the propagator associated to $j$ is supported on vertex $j$.
 Choose one such bijection.
@@
 Thus each $r_i$ is homogeneous.
-    \item Using the expression for the determinant as a sum over permutations from Lemma \ref{lem basis as perm} we see that $\Delta_{I_i}$ is a sum over bijections between $I_i$ and $\mathcal{P}$.
+    \item Using the expression for the determinant as a sum over permutations from Corollary~\ref{lem basis as perm} we see that $\Delta_{I_i}$ is a sum over bijections between $I_i$ and $\mathcal{P}$.
 The nonzero terms in this sum are precisely those bijections such that each propagator is associated to one of its supporting vertices in $I_i$, since only those locations in $C(W)$ are nonzero.

### 2019-06-14 GWLDCII.tex
paper2 pictures stuff

@@
 
+% some propagator styles
 \tikzstyle{propagator}=[decorate,decoration={snake,amplitude=0.8mm}]
 \tikzstyle{smallpropagator}=[decorate,decoration={snake,segment length=3mm,amplitude=0.5mm}]
+
+% for highlighting regions of a diagram edge
+\tikzstyle{linehighlight}=[red,line width = 3pt,line cap = round, draw opacity = 0.5]
 
@@
 %\clip (\angle*\r:\radius) -- (\angle + \angle*\r:\radius) -- (\angle*\s:\radius) -- (\angle + \angle*\s:\radius) -- (\angle*\r:\radius);
-\draw[propagator] (\angle*\r + \angle/2 + \bumpr*\perturbe:\radius) -- (\angle*\s + \angle/2 + \bumps*\perturbe:\radius);
+\draw[smallpropagator] (\angle*\r + \angle/2 + \bumpr*\perturbe:\radius) -- (\angle*\s + \angle/2 + \bumps*\perturbe:\radius);
 \end{scope}
@@
 %\clip (\angle*\r:\radius) -- (\angle + \angle*\r:\radius) -- (\angle*\s:\radius) -- (\angle + \angle*\s:\radius) -- (\angle*\r:\radius);
-\draw[propagator] (\angle*\r + \angle/2 + \bumpr*\perturbe:\radius) -- (\angle*\s + \angle/2 + \bumps*\perturbe:\radius) node[midway, below] {#5};
+\draw[smallpropagator] (\angle*\r + \angle/2 + \bumpr*\perturbe:\radius) -- (\angle*\s + \angle/2 + \bumps*\perturbe:\radius) node[midway, below] {#5};
 \end{scope}
@@
 }
+
+%%%%%%%
+% Drawing partial WLD
+%%%%%%%
+\def\centerarc[#1](#2)(#3:#4:#5)% Syntax: [draw options] (center) (initial angle:final angle:radius)
+    { \draw[#1] ($(#2)+({#5*cos(#3)},{#5*sin(#3)})$) arc (#3:#4:#5); }
+
+\def\clipcenterarc(#1)(#2:#3:#4)% Syntax: [draw options] (center) (initial angle:final angle:radius)
+    { \clip ($(#1)+({#4*cos(#2)},{#4*sin(#2)})$) arc (#2:#3:#4); }
+
+%\drawWLDfragment[number of nodes]{radius}{fraction of circle to be displayed}
+\newcommand{\drawWLDfragment}[3][10]{
+\pgfmathsetmacro{\n}{#1} % use this to get consistent spacing between nodes
+\pgfmathsetmacro{\radius}{#2}
+\pgfmathsetmacro{\fragment}{#3} % between 0 and 1, gets you that percentage of a circle
+\pgfmathsetmacro{\halfangle}{360*\fragment/2}
+\pgfmathsetmacro{\startpoint}{270 - \halfangle}
+\pgfmathsetmacro{\endpoint}{270 + \halfangle}
+\pgfmathsetmacro{\step}{2*\halfangle/\n} 
+\pgfmathsetmacro{\zero}{\startpoint-0.5*\step} % so node i is at angle \zero + i*\step
+\centerarc[black](0,0)(\startpoint:\endpoint:\radius)
+}
+
+\newcommand{\drawnumberspartial}{
+\node (0,0) {$\bullet$};
+  \foreach \i in {1,2,...,\n} {
+  \pgfmathsetmacro{\x}{\step*\i}
+  \draw (\zero + \x:\radius*1.15) node {\footnotesize \i};
+}
+}
+
+\newcommand{\newnode}[3][left]{
+	\node[label={[label distance=-1mm]#1:{\scriptsize $#3$}}] at (\zero + #2*\step:\radius) {\scriptsize $\bullet$};
+	%\node[#1] at (\zero + #2*\step:\radius) {\scriptsize $#3$};
+}
+
+% messier but more flexible: use when you want more control over label placement
+\newcommand{\newbetternode}[3][{label distance=-1mm]left}]{
+	\node[label={#1:{\scriptsize $#3$}}] at (\zero + #2*\step:\radius) {\scriptsize $\bullet$};
+	%\node[#1] at (\zero + #2*\step:\radius) {\scriptsize $#3$};
+}
+
+% \newprop[label position]{start node}{end node}{label}
+\newcommand{\newprop}[4][midway,below]{
+\pgfmathsetmacro{\startnode}{#2}
+\pgfmathsetmacro{\endnode}{#3}
+
+\draw[smallpropagator] (\zero+\startnode*\step:\radius) -- (\zero + \endnode*\step:\radius) node[#1] {#4};
+}
+
+\newcommand{\newpropbend}[3]{
+\draw[smallpropagator] (\zero+#1*\step:\radius*1.1) to[bend left = #3] (\zero + #2*\step:\radius*1.1);
+}
+
+%%%%%%%%%%%%%%
 
@@
     \node at (\angle*10:\radius*1.15cm) {\footnotesize $i_1$};
+	\node at (10:\radius*0.5) {\small $\cP_{in}(q_1)$};
 		\end{scope}
 	\end{tikzpicture}\eas
-
-\note{Sian note to self: come back and check this later, if we end up with code for drawing partial diagrams then that might make a better diagram}
 

### 2019-06-16 GWLDCII.tex
tweaked picture in Lem 3.5, added section 5 picture to pictures doc

@@
 	\end{scope}
-    \drawlabeledprop{3}{0}{10}{0}{\footnotesize \qquad $q_1$}
+    \drawlabeledprop{3}{0}{10}{0}{\footnotesize \qquad $q_1$};
     \node at (\angle*5:\radius*1.15cm) {\footnotesize $j_1$};
@@
      \node at (10:\radius*0.5) {\small $\cP_{in}(q_1)$};
+	\node[rotate = 45] at (\angle * 5.2:\radius) {\Large $($};
+\node[rotate = -15] at (\angle * 2.7:\radius) {\Large $)$};
+\node[rotate = 20] at (\angle* 4:\radius*1.2) {\em \scriptsize 1, 2 or 3 vertices};
 		\end{scope}
@@
 
+ %\node[rotate=-15] at (\zero + 2.7*\step:\radius) {\Large $($};
+ %    \node[rotate=15] at (\zero + 6.3*\step:\radius) {\Large $)$};
+   %  \node at (\zero + 4.5*\step:\radius*0.85) {\em \scriptsize up to 4 vertices here};
+
+\sanote{played with Sian's code. May need to tweak this picture}
 Now suppose $q_{r} = (i_r, k_r)$ exists by the induction hypothesis and is oriented $(q_r, <_{i_r})$ so that the previous $p_i$ and $q_i$ are on the outside.

### 2019-06-17 GWLDCI.tex
very minor edits (as discussed) to 1, incorporated Susama's changes to 2 as far as the end of section 4

@@
 
-A {\em matroid} $M = (E,\cB)$ consists of a finite ground set $E$ and a non-empty family $\cB \subseteq \cP(E)$ whose elements satisfy the {\em basis exchange property}: for any distinct $B_1,B_2 \in \cB$ and any $a \in B_1 \setminus B_2$, there exists some $b \in B_2 \setminus B_1$ such that $(B_1 \setminus \{a\})\cup \{b\} \in \cB$ as well.
+A {\em matroid} $M = (E,\cB)$ consists of a finite ground set $E$ and a non-empty family $\cB$ of subsets of $E$, such that elements of $\cB$ satisfy the {\em basis exchange property}: for any distinct $B_1,B_2 \in \cB$ and any $a \in B_1 \setminus B_2$, there exists some $b \in B_2 \setminus B_1$ such that $(B_1 \setminus \{a\})\cup \{b\} \in \cB$ as well.
 The elements of $\cB$ are called the {\em bases} of the matroid.
@@
 \begin{lem}\label{lem facts about WLD matroids}
-Let $W = (\cP,n)$ be an admissible Wilson loop diagram. Then:
+Let $W = (\cP,[n])$ be an admissible Wilson loop diagram. Then:
 \begin{enumerate}
@@
 \begin{thm}\label{same matroid iff equiv}
-Let $W= (\cP, [n])$ and $W'= (\cP', n)$ be two Wilson loop diagrams. They define the same matroid if and only if $W \sim W'$.
+Let $W= (\cP, [n])$ and $W'= (\cP', [n])$ be two Wilson loop diagrams. They define the same matroid if and only if $W \sim W'$.
 \end{thm}
@@
 Let $D_1$ and $D_2$ be two dissections of a convex $n$-gon defined by the vertices $x_1, \ldots, x_n$.
-\hlfix{Suppose that $V_{>3}(D_1) = V_{>3}(D_2)$}{we probably use this implicitly somewhere in the proof but I can't see it; can we make it explicit?}, but that the $D_1$ and $D_2$ do not have the same set of non-triangle faces.
+Suppose that $V_{>3}(D_1) = V_{>3}(D_2)$, but that the $D_1$ and $D_2$ do not have the same set of non-triangle faces.
 Then there are four vertices $x_i$, $x_j$, $x_k$, $x_l$ satisfying the following conditions:\begin{enumerate} \item In either $D_1$ or $D_2$ all four vertices are on the same non-triangle face; \item In the other dissection, there is a diagonal of the dissection such that exactly one of $\{x_i, x_j, x_k, x_l\}$ lies on one side of the diagonal (so the others are either end points of this diagonal or strictly on the other side).
@@
 
-  As observed in the proof of Proposition~\ref{prop easy way}, the support of any nonzero vector parallel to an edge is on the indices corresponding to the four vertices bounding the quadrilateral of the dissection associated with the edge.
+  As observed in the proof of Proposition~\ref{prop easy way}, the support of any non-zero vector parallel to an edge is on the indices corresponding to the four vertices bounding the quadrilateral of the dissection associated with the edge.
 Thus if $V_{>3}(\tau(W)) \neq V_{>3}(\tau(X))$ (notation as defined before Lemma~\ref{lem good quads}) then the span of the vectors parallel to their edges has different support and so they cannot be parallel.
@@
     Now, $\tau(W)$ and $\tau(X)$ satisfy the hypotheses of Lemma~\ref{lem good quads}, so we can assume that $f$ and $d$ have the property that we can choose a side of $d$ to be the positive side in such a way that exactly one vertex of $f$ is strictly on the positive side.
-Then $\omega^+_d$ and the direction vector of $d$ have common support exactly on that one vertex and so their dot product is nonzero.
+Then $\omega^+_d$ and the direction vector of $d$ have common support exactly on that one vertex and so their dot product is non-zero.
 Since the direction vector of $d$ is contained in the direction of $\tau(X)$ but is not orthogonal to $\omega^+_d$, while $\omega^+_d$ is normal to the face of $\tau(W)$, it follows that the faces associated to $\tau(W)$ and $\tau(X)$ are not parallel, as desired.

### 2019-06-17 GWLDCII.tex
very minor edits (as discussed) to 1, incorporated Susama's changes to 2 as far as the end of section 4

@@
 
-\begin{rmk}
+\begin{rmk}\label{rmk algorithm locally same}
 The following observation will be very useful in many of the arguments below.
 
-Suppose we are going through the algorithm to construct $I_i^W$ and we are currenctly at step $j$ of the loop.
+Suppose we are going through the algorithm to construct $I_i^W$ for some $i$, and we are currently at step $j$ of the loop.
 Consider the diagram $W'$ formed by $W$ with all the propagators already contributed removed; think of a vertex being taken away when it is contributed, since it can only contribute once, so it is gone from the point of view of the rest of the construction of $I_i^W$.
-Now suppose for some other diagram $V$ on the same vertex set we are constructing $I_k^V$ and we are at step $j$ of the loop, for the same $j$ as above.
+Now suppose for some other diagram $V$ on the same vertex set we are constructing $I_m^V$ for some $m$, and we are at step $j$ of the loop, for the same $j$ as above.
 Again let $V'$ be $V$ with all the propagators already contributed removed.
 
-With this setup, if there is an interval, $(j-1, \ldots, \ell+1)$ (with $\ell <_i i$ and $\ell <_k k$) in $W'$ and $V'$ where the propagators ending in that interval are identical in both diagrams, then the construction of $I_i^W$ and $I_k^V$ is identical up to and including step $\ell$.
+With this setup, if there is an interval, $(j-1, \ldots, \ell+1)$ (with $\ell <_i i$ and $\ell <_m m$) in $W'$ and $V'$ where the propagators ending in that interval are identical in both diagrams, then the construction of $I_i^W$ and $I_m^V$ is identical up to and including step $\ell$.
 The constructions are identical for those steps simply because the local situation of propagators supported at $j, j+1, \ldots, \ell$ is identical in both cases and the algorithm only sees the local situation at the vertex corresponding to the current step.
@@
 \end{lem}
+\note{Right at the end when we put the tikz figures in, someone needs to go through this proof and replace ``leftmost two cases'' with ``Case 1 and 2'' etc, because the tikz picture is arranged differently}
 
@@
 %I left this as a comment so we can add it in if necessary, but I don't think we need this level of precision in this sentence: we're just signposting what we're going to do in detail shortly.
-of these vertices, we use the following observation: if $p$ is the first propagator to be assigned a value by $I_w^{W}$, then the remainder of $I_w^{W}$ proceeds identically to the assignments of $I^{V}_{w+1}$.
+of these vertices, we use the following observation: if $p$ is the first propagator to be assigned a value by $I_w^{W}$, then the remainder of $I_w^{W}$ proceeds identically to the assignments of $I^{V}_{w+1}$ (recall Remark~\ref{rmk algorithm locally same}).
 Thus we have for any $0\leq b <a$
@@
 
-\note{Sian is here}
-
 \begin{thm}\label{res:alg gives GN}
@@
 \end{thm}
-\note{Sian replaced all occurences of $k$ as an index with other letters: someone please proofread this specifically to check that none were missed! (then remove this note)}
 \begin{proof}
@@
 \textbf{Case I}:  Suppose $p$ has one end on edge $i-1$.
-\st{Then} {\color{violet}If} $p$ is not supported on $i+1$, \st{so} in building $I_{i+1}$ \hlfix{we will assign the same propagators as in the construction of $I_i$from vertices $i+1$ up to $b-1$, that is $I_{i+1} \cap [i+1,b-1] = I_{i} \cap [i+1,b-1]$}{Lemma-ize?}.
-{\color{violet} (If $p$ is supported on $i+1$, $b= i+1$ and the interval $[i+1,b-1]$ is emptry.)} Furthermore, by Lemma~\ref{vertex cyclic int lem}, when building $I_{i+1}$ it must happen that $p$ contributes vertex $b$, as otherwise $b$ would never be contributed by $p$.
-Consequently, in building $I_{i+1}$, when the algorithm reaches vertex $b$ there cannot be any unassigned propagators remaining that are \hlfix{before}{do we have an ordering on $\cP$?} $p$.
-This is also true in when the algorithm constructing $I_i$ reaches $b$, since the \hlfix{same propagators have been assigned beforehand}{see above.}.
+If $p$ is not supported on $i+1$, then in building $I_{i+1}$ we will assign the same propagators as in the construction of $I_i$ from vertices $i+1$ up to $b-1$, that is $I_{i+1} \cap [i+1,b-1] = I_{i} \cap [i+1,b-1]$.
+(If $p$ is supported on $i+1$, then $b= i+1$ and the interval $[i+1,b-1]$ is empty.) Furthermore, by Lemma~\ref{vertex cyclic int lem} it must happen that $p$ contributes vertex $b$ to $I_{i+1}$, as otherwise $b$ would never be contributed by $p$.
+Consequently, in building $I_{i+1}$, when the algorithm reaches vertex $b$ there cannot be any remaining unassigned propagators that are supported on $b$ and counterclockwise of $p$.
+This is also true in when the algorithm constructing $I_i$ reaches $b$, since the same propagators have been assigned beforehand.
 Finally, we also note that $m\geq_i b+1$.
@@
 
-By the above observations, if we commence Algorithm~\ref{alg:put GN on WLD} in $W'$ from vertex $b$, then we are in the same situation with respect to unassigned propagators as if we began at $i$ in $W$ and proceeded to $b$ following the algorithm {\color{violet}(recall that $I^W_i(p) =i$)}\st{; the propagators we assigned in the latter case}{\color{violet}.
-The propagators contributing to $I_{i}$ for $W$ before the vertex $b$} are exactly the ones removed to build $W'$.
+By the above observations, if we commence Algorithm~\ref{alg:put GN on WLD} in $W'$ from vertex $b$, then we are in the same situation with respect to unassigned propagators as if we began at $i$ in $W$ and proceeded to $b$ following the algorithm (recall that $I^W_i(p) =i$).
+The propagators contributing to $I_{i}^W$ before the vertex $b$ are exactly the ones removed in the construction of $W'$.
 Similarly, starting at $i+1$ in $W$ and moving to $b+1$ leaves us in the same situation with respect to unassigned propagators as beginning at $b+1$ in $W'$ would.
@@
   I_{i+1}^{W} \cap [b+1,i-1] & = I_{b+1}^{W'}
-\end{align*} \sanote{ $I_i^{W}$ is a map not a $k$-tuple. Do we mean $I_i$ for $W$? or $I_i^{W}(\cP)$ because we want the image set?}
+\end{align*} 
 where the diagram is indicated in the superscript.
@@
 \textbf{Case II}: Suppose $p$ has one end on edge $i$.
-Note that by assumption we have $I_i(p) = i$; this means that $p$ must be the \st{first} {\color{violet} counterclockwise most} propagator lying on edge $i$, and hence we must have $I_{i+1}(p) = i+1$ as well.
+Note that by assumption we have $I_i(p) = i$; this means that $p$ must be the counterclockwise-most propagator lying on edge $i$, and hence we must have $I_{i+1}(p) = i+1$ as well.
 Observe also that $m\geq_i i+2$ since $i+1\in I_{i+1}$.
@@
 
-%If $i \not\in I_i$, then there are no propagators supported on $i$ at all.
-In this case it is clear that applying Algorithm~\ref{alg:put GN on WLD} at vertex $i$ and vertex $i+1$ produces exactly the same result, i.e.
-$I_{i+1} = I_i$.
-%
-%Now suppose that $i \in I_i$.  Order $I_i$ and $I_{i+1}$ with respect to $\leq_{i+1}$; in particular, $i$ is the last term in $I_i$ with respect to this ordering.
-%
-%Let $p_1$ be the rightmost propagator supported on $i$, and suppose it is removed at step $a$ with respect to vertex $i+1$.
-This is the first point at which $I_{i+1}$ can differ from $I_i$, i.e.
-we have $I_{i+1} \cap \interval{i+1}{a-1} = I_{i} \cap \interval{i+1}{a-1}$.
-If $a \not\in I_i$, then $p_1$ is the only propagator supported on $a$ at step $a$ with respect to vertex $i+1$.
-All remaining steps are unchanged and we conclude that $I_{i+1} = I_i \backslash \{i\} \cup \{a\}$.
-%
-%If $a \in I_i$, then at step $a$ with respect to vertex $i+1$ there must be another propagator $p_2$ which lies to the left of $p_1$.
-We have $I_{i+1} \cap \interval{i+1}{a} = I_i \cap \interval{i+1}{a}$, and the next possible difference
-%
-%{\color{red}[argh]}
-%
-%Although there are many different subcases to consider, the idea is always the same: we look for the first entry where $I_{i+1}$ and $I_i \backslash \{i\}$ differ (with respect to $<_{i+1}$), and show that this is the only possible difference.
-%
-%The reader should keep in mind that due to Proposition~\ref{res:alg k labels}, the following process cannot double back on itself.
-%
-%\begin{enumerate}
-%\item If $p_1$ contributes $k$ to $I_{i+1}$ and $k \in I_i$, then there is another propagator $p_2$ which was deleted at step $k$ with respect to vertex $i$, but now survives at step $k$ with respect to vertex $i+1$.
-All intermediate steps of the algorithm are unchanged, so $I_{i+1}$ and $I_i \backslash \{i\}$ agree up to (and including) $k$.
-%\item We now look at which label $p_2$ contributes in $I_{i+1}$, and apply the same argument.
-Iterate this process until we find a propagator $p_r$ which is deleted at step $j$ with respect to vertex $i+1$, but $j \not\in I_i$.
-%\item $j \not\in I_i$ implies that $p_r$ is the \textit{only} propagator supported on vertex $j$ at this step.
-There is therefore no knock-on effect, and any remaining propagators in the diagram contribute the same label to both $I_i$ and $I_{i+1}$.
-We conclude that $I_{i+1} = I_i \backslash \{i\} \cup \{j\}$.
-%\end{enumerate}
-
 \medskip  \sanote{Suggested breakpoint of theorem}
@@
 We have shown that $(I_1,\dots,I_n)$ is a Grassmann necklace; it remains to check that this Grassmann necklace corresponds to the positroid $M(W)$.
-{\color{violet} By equation \eqref{basesofmatroids}, w}e need to show that: \sanote{added a number to this eq.
-make it a dfn?}
+Recall from the discussion following Definition~\ref{def:grassmann necklace}, and equation \eqref{basesofmatroids} in particular, that it suffices to show:
 \begin{itemize}
 \item For each $i \in [n]$, $I_i$ is a basis for $M(W)$.
-\item If $J$ is lexicographically smaller than {\color{violet} any} $I_i$ with respect to $<_i$, then $J$ is not a basis for $M(W)$. 
+\item If $J$ is lexicographically smaller than $I_i$ with respect to $<_i$ (for any $i \in [n]$) then $J$ is not a basis for $M(W)$. 
 \end{itemize}
@@
 \begin{proof}
-  By Algorithm~\ref{alg:put GN on WLD} the Grassmann necklace of $W$ is obtained from the Grassmann necklace of $V$ by duplicating the $i$th element of the Grassmann necklace of $V$ (shifting indices by $1$ for all indices greater than $i$) \sanote{changed a bit of wording on the proof}, and incrementing all indices greater than $i$ by $1$ in each Grassmann necklace element.
+  By Algorithm~\ref{alg:put GN on WLD} the Grassmann necklace of $W$ is obtained from the Grassmann necklace of $V$ by duplicating the $i$th element of the Grassmann necklace of $V$ (shifting indices by $1$ for all indices greater than $i$), and incrementing all indices greater than $i$ by $1$ in each Grassmann necklace element.
 Formally, if $I_1^{V}, \ldots, I_{n-1}^{V}$ and $I_1^{W}, \ldots, I_n^{W}$ are the Grassmann necklaces of $V$ and $W$ respectively then
@@
   \begin{itemize}
-  \item $p = (i, n-1)$ for some $i$, and $p$ has no propagators inside it (that is $i+2, \ldots, n-2$ do not support any propagators in $W'$).
-  \item Either the edge $i$ in $W'$ only supports $p$ or the edge $i$ in $W'$ supports exactly one other propagator \hlfix{$q = (i, j)$ with no other propagators inside $q$ in the $<_i$ ordering, and $j <_1 i$.}{changed.
-Correct?
-Explicitly, not letting $i <_i j <_i n-1$.
-Also made this change below.
-}
+  \item $p = (i, n-1)$ for some $i$, and $p$ has no propagators inside it w.r.t the $<_i$ ordering (that is $i+2, \ldots, n-2$ do not support any propagators in $W'$).
+  \item Either the edge $i$ in $W'$ only supports $p$, or the edge $i$ in $W'$ supports exactly one other propagator $q = (j,i)$, with no other propagators inside $q$ in the $<_j$ ordering.
+\note{Sian undid Susama's change here: all we know about $q$ is that it goes from some edge $j$ to $i$, and there's nothing inside $q$ wrt that orientation.
+In a very degenerate case, $q$ could probably be $(n,i)$.}
   \end{itemize}
@@
 
-Combining Lemmas \ref{lem uncovered}, \ref{lem dihedral}, and \ref{lem good p}, it therefore suffices to study the Le diagrams of weakly admissible Wilson loop diagrams with $F(\emptyset)  = \emptyset$, admitting one of the configurations described in Lemma \ref{lem good p} with propagators \hlfix{$p = (n-3, n-1)$ and $q= (n-5, n-3)$}{changed.
-correct?} (if $q$ exists) both of length 2.
+Combining Lemmas \ref{lem uncovered}, \ref{lem dihedral}, and \ref{lem good p}, it therefore suffices to study the Le diagrams of weakly admissible Wilson loop diagrams with $F(\emptyset)  = \emptyset$, admitting one of the configurations described in Lemma \ref{lem good p} with propagators $p = (n-3, n-1)$ and $q= (n-5, n-3)$ (if $q$ exists) both of length 2.
 See Figure~\ref{fig special p} for an illustration of the two possibilities.
@@
 From the figure we see that in both cases we have $I_n^{W}(p) = n$.
-At vertex 1 of the algorithm $I_n$, the unassigned propagators are exactly those that appear in $V$.\sanote{same invisible lemma} Therefore the algorithm continues as in $I_1^{V}$, i.e.
+At vertex 1 of the algorithm $I_n$, the unassigned propagators are exactly those that appear in $V$.
+Therefore the algorithm continues as in $I_1^{V}$ (recall Remark~\ref{rmk algorithm locally same} about locally identical propagator configurations), i.e.
 we have $I_n^{W} = I_1^{V} \cup \{n\}$.
@@
   Let $V$ and $W$ be as in Lemma~\ref{lem I}.
-  The shape of the Le diagram of $V$ can be built from left to right of the following blocks: a rectangle which is 3 columns wide, one more column of the same height, and a \hl{partition shape}\sanote{Is this defined?
-shape defined by $I_i$?} with at most as many rows as the rectangle.
+  The shape of the Le diagram of $V$ can be built from left to right of the following blocks: a rectangle which is 3 columns wide, one more column of the same height, and a partition shape with at most as many rows as the rectangle.
   The shape of the Le diagram of $W$ can be built from left to right of the following blocks: a rectangle with 3 columns and one more row than the first rectangle of $V$, and the same partition shape as in $V$.
@@
 
-Recall that $I_1$ determines the shape of the Le diagram.
+Recall that $I_1$ determines the shape of the Le diagram: specifically, the elements of $I_1$ label the rows of the diagram, working from top right to bottom left.
 By the arguments in Lemma~\ref{lem I} we know that ${n,n-1,n-2, n-3 \not\in I_1^{V}}$ (which yields the leftmost four columns of the diagram for $V$) and that $I_1^{W} = I_1^{V}\cup \{n-3\}$.
@@
 
-% Additionally $n-3\not\in I_{n}^{V}$ since if it were then $n-3$ would also be in $I_1^{V}$ and hence propagator $p$ could not contribute $n-3$ to $I_1^{W}$ in contradiction to Lemma~\ref{vertex cyclic int lem}.
-Similarly $n-1, n-2\not\in I_n^{V}$.
-Thus the paths putting the plusses in from $I_n^{V}$ lie completely in $\mathcal{B}$ or take some vertical boundary edge $>n-3$ to $n$.
-Now view these paths in the Le diagram of $W$ and note that the path $n-3\rightarrow n-1$ is compatible, and so these paths together build the plusses that $I_{n-1}^{W}$ contributes.
-That is, we get all the plusses from $I_{n}^{V}$ along with a $n-3\rightarrow n-1$ plus, that is a plus in the second to the right box of the bottom row.
-
 \begin{lem}\label{lem n-2 good}
@@
 \end{proof}
-
-%\begin{lem}\label{lem n-2 bad}
-%Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that $n-2,n-1 \in I_{n-2}^{V}$.
-%
-%Then $I_{n-2}^{W}$ and $I_{n-3}^{W}$ contribute the following plusses to the Le diagram of $W$
-%  \begin{itemize}
-%  \item An $(n-3)\rightarrow (n-2)$ plus and an $(n-5)\rightarrow (n-1)$ plus.
-%  \item All of the $I_{n-1}^{V}$ plusses.
-%  \item In the Le diagram of $V$, $I_{n-2}^{V}$ contributes an $n-5\rightarrow n-2$ plus and no other term in the Grassmann necklace of $V$ gives a plus in this column.
-$I_{n-2}^W$ does not contribute this $+$ but yields an $n-5\rightarrow n-1$ plus instead.
-%  \item All other plusses of $I_{n-2}^{V}$.
-%  \item In the Le diagram of $V$, $I_{n-3}^{V}$ gives a plus in the $n-3$ column.  This $+$ is shifted over into the $n-2$ column in $W$.
-%  \item All other plusses of $I_{n-3}^{V}$.
-%  \end{itemize}
-%Furthermore, no element of the Gramann necklace of $V$ gives an $n-5\rightarrow n-1$ plus.
-%\end{lem}
-%
-%\begin{proof}
-%  By Lemma~\ref{lem I} $I_{n-2}^{W}= (I_{n}^{V} - \{n-5\})\cup \{n-1,n-2\}$.
-Also, by the location of $q$ in the WLD,  $n-2\not\in I_{n-3}^{V}$ and and $n-5$ is the index of the lowest vertical edge in $\mathcal{B}$.
-Thus this section of the Gramann necklace of $V$ looks like
-%  \begin{equation}\label{eq necklace}
-%  I_{n-3}^{V} \underset{\substack{n-3\text{ out}\\n-2\text{ in}}}{\rightarrow} I_{n-2}^{V} \underset{\substack{n-2\text{ out}\\n-5\text{ in}}}{\rightarrow} I_{n-1}^{V} \underset{\substack{n-1\text{ out}\\\text{something in}}}{\rightarrow} I_{n}^{V} \underset{\substack{n \text{ out}\\\text{something in}}}{\rightarrow} I_1^{V}
-%  \end{equation}
-%  where the first ``something'' is either $n$ or an element of $I_1^{V}$ and the second ``something'' is an element of $I_1^{V}$.
-Additionally all elements not explicitly mentioned must be in $I_1^{V}$ as they remain unchanged through this portion of the necklace.
-%
-%  Using this information now determine the symmetric difference of $I_{n-2}^{V}$ and $I_1^{V}$: $n-1, n-2$ and possibly $n$ are in $I_{n-2}^{V}$ but not in $I_1^{V}$.
-$n-5$ is in $I_1^{V}$ as are at least one and at most two other elements.
-If there is one such element call it $a$.
-If there are two call them $a$ and $b$ with $a>b$.
-This means that the plusses in the Le diagram of $V$ coming from $I_{n-2}^{V}$ are as in the first part of Figure~\ref{fig messy}.
-Stepping to $I_{n-1}^{V}$ simply removes the $n-5\rightarrow n-2$ path, see the second part of Figure~\ref{fig messy}.
-%
-%  \begin{figure}
-%    \includegraphics{messy}
-%    \caption{Plusses coming from $I_{n-2}^{V}$ (top left),  $I_{n-1}^{V}$ (top right) and $I_{n}^{V}$ bottom when $n-1, n-2\in I_{n-1}^{V}$.
-The blue lines are the non-intersecting paths.
-The dashed blue lines may or may not appear, but if one appears then they both do.}\label{fig messy}
-%  \end{figure}
-%
-%  Stepping to $I_{n}^{V}$, $n-1$ is taken out and either $n$ is put in if it was not there before, or one of $a$ or $b$ is put in and hence no longer available as a right end for a path.
-This gives two possible configurations illustrated in the bottom two parts of Figure~\ref{fig messy}.
-%
-%  Now we know that $I_{n-2}^{W}  = (I_{n}^{V} - \{n-5\})\cup \{n-1,n-2\}$ so the paths for building plusses from $I_{n-2}^{W}$ go from the set $\{n-5, n-3\}$ along with whichever of $a$ and $b$ is not in $I_{n}^{V}$ to $\{n-2, n-1, n\}$.
-This means that we get plusses as in Figure~\ref{fig messyD} where the left and right cases correspond to the left and right cases in the bottom parts of Figure~\ref{fig messy}
-%
-%  \begin{figure}
-%     \includegraphics{messyD}
-%    \caption{Plusses coming from $I_{n-2}^{W}$.}\label{fig messyD}
-%  \end{figure}
-%
-%  This proves the first item of statement of the lemma.
-%
-%  Now consider $I_{n-3}^{V}$.
-By \eqref{eq necklace} $I_{n-3}^{V}$ contributes the same plusses as $I_{n_2}^{V}$ except that it contributes an $n-5\rightarrow n-3$ plus in place of the $n-5\rightarrow n-2$ plus.
-Also, we have $n-3\in I_{n-3}^{V}$ be the location of $q$ and so $I_{k}^{W} = I_k^{V}\cup\{n-2\}$.
-Thus the paths for $I^{W}_{n-3}$ are the same as for $I^{V}_{n-3}$ except that the path that did go to $n-3$ now goes to $n-2$.
-This cannot conflict with another path since \eqref{eq necklace} shows that $n-2$ only appears in $I_{n-2}^{V}$ among the necklace elements of $V$.
-%
-%  Also note that $I_{n-3}^{V}, I_{n-2}^{V}$, and $I_{n-1}^{V}$ share their plusses outside of the $n-3$ and $n-2$ columns.  This proves the remaining statements of the lemma except the furthermore.
-%
-%  Finally, suppose there were a $n-5\rightarrow n-1$ plus in the Le diagram of $V$.
-By the algorithm, it would have to come when $n-5 \not\in I_j^{V}$.
-By \eqref{eq necklace} this means that it would have to come from $I_{n-4}^{V}$, $I_{n-3}^{V}$, or $I_{n-2}^{V}$.
-The analysis above shows it does not come from $I_{n-3}^{V}$ or $I_{n-2}^{V}$.
-Now, $n-4\in I_{n-4}^{V}$ by the location of $q$ and so $I_{n-4}^{V}$ must give an $n-5\rightarrow n-4$ plus and so cannot give an $n-5\rightarrow n-1$ plus.
-%
-%\end{proof}
 
@@
   By Lemma~\ref{lem I} we have $I_{n-2}^{W}= (I_{n}^{V} \setminus \{n-5\})\cup \{n-1,n-2\}$ and $I_1^W = I_1^V\cup \{n-3\}$.
-We are necessarily in the case where $W$ admits a propagator $q$ (the right hand case of Figure~\ref{fig special p}) and we can see from the location of $q$ that $n-2\not\in I_{n-3}^{V}$ and that $n-5$ \hlfix{is the label of the last row in}{would like to propagate changes like this through.} $\mathcal{B}$.
+We are necessarily in the case where $W$ admits a propagator $q$ (the right hand case of Figure~\ref{fig special p}) and we can see from the location of $q$ that $n-2\not\in I_{n-3}^{V}$ and that $n-5$ is the label of the last row in $\mathcal{B}$.
 Also note that by Lemma~\ref{vertex cyclic int lem} and Corollary~\ref{no coloops} we must have $n\in I_n^V$.

### 2019-06-21 GWLDCI.tex
got rid of violet internal note

@@
 
-{\color{violet} INTERNAL NOTE ONLY.
-(I've removed the offending "if" above: The other direction of the above is best seen from the point of view of triangulations.
-Any exact subdiagram corresponds to a triangulation.
-$n>1$ or more propagators forms a minimal violation the the density condition if one can remove one propagator to get an exact subdiagram on $n-1$ propagators, and thus a triangulation.
-The only way this can happen is to cross propagators/ diagonals, or two have the diagonal start and end at the same vertex (parallell propagators).
-A single violator violates the density condition if it starts and ends on adjascent edges of the Wilson loop diagram/ vertices of the triangulation.}
-
 Note that if we take any admissible Wilson loop diagram and remove the non-supporting vertices, we obtain a weakly admissible Wilson loop diagram that may or may not be admissible itself.

### 2019-06-21 GWLDCII.tex
fixed things about blocks A and B

@@
 This implies that the right hand boundary of the shape of $V$ is the same as the right hand boundary of the shape of $W$ except that $W$ has one additional row of 3 boxes while $V$ has an additional column in the $n-3$ position; that is, an extra column fourth from the left.
-\sanote{Can we rephrase this in terms of row and column numbers (as in section 2) rather than use shape?}
 \end{proof}
@@
 As illustrated in Figure~\ref{fig Le}, the pieces of the Le diagrams of $V$ and $W$ will be called $\mathcal{A}$ and $\mathcal{B}$ in what follows.
-\hlfix{Explicitly, $\mathcal(B)$ is the set of columns with labels $v < n-3$ and $\mathcal{A}$ the set of columns labeled by $n$, $n-1$ and $n-2$.}{is this accurate?} Over the course of the next few lemmas we will prove that the plusses in the $\mathcal{B}$ parts of each diagram are identical, and that the relationship between the plusses in the $\mathcal{A}$ regions can be described explicitly.
+\hlfix{Explicitly, $\mathcal{B}$ is the set of columns with labels $v < n-3$ and $\mathcal{A}$ the set of columns labeled by $n$, $n-1$ and $n-2$ in $V$.
+In $W$, A consists of these columns without the last row.}{is this accurate?} Over the course of the next few lemmas we will prove that the plusses in the $\mathcal{B}$ parts of each diagram are identical, and that the relationship between the plusses in the $\mathcal{A}$ regions can be described explicitly.
 

### 2019-06-21 GWLDCII.tex
rewrote remark 3.10

@@
 Suppose we are going through the algorithm to construct $I_i^W$ for some $i$, and we are currently at step $j$ of the loop.
-Consider the diagram $W'$ formed by $W$ with all the propagators already contributed removed; think of a vertex being taken away when it is contributed, since it can only contribute once, so it is gone from the point of view of the rest of the construction of $I_i^W$.
+Consider the diagram $W'$ formed by $W$ with all the propagators already contributed removed.
+Not that the algorithm automatically removes a propagator once it contibutes to the algorithm.
 Now suppose for some other diagram $V$ on the same vertex set we are constructing $I_m^V$ for some $m$, and we are at step $j$ of the loop, for the same $j$ as above.
 Again let $V'$ be $V$ with all the propagators already contributed removed.
+\sanote{rewrote, correct?}
 

### 2019-06-22 GWLDCII.tex
rewrote remark 3.10
Second half of GN proof written in purple

@@
 
+{\color{violet}\begin{dfn} \label{proporderingdfn}
+Each $I^W_i$ imposes an ordering on the propagators of $W = (\cP, n)$, determined by when the propagator contributes to the sequence.
+If $W$ has $k$ propagators, we ma write $\cP = \{p_1, \ldots p_k\}$ with $I_i = I_i(p_1)I_i(p_2) \ldots I_i(p_k)$, where the superscript $W$ is taken as read.
+\end{dfn}
+
+Since each propagator is removed by the algorithm after it contributes, each propagator contributed exactly once to $I^W_i$, making the above ordering well defined.}
+
 \begin{rmk}\label{rmk algorithm locally same}
@@
 Again let $V'$ be $V$ with all the propagators already contributed removed.
-\sanote{rewrote, correct?}
+\sanote{rewrote, do we like this?}
 
@@
 
+\sanote{alternate proof of second half of above}
+{\color{violet} \begin{thm}
+The Grassmann necklace $(I_1 \ldots I_n)$ is the Grassmann neclace for $M(W)$ 
+\end{thm}
+
+\begin{proof}
+We have shown that $(I_1,\dots,I_n)$ is a Grassmann necklace; it remains to check that this Grassmann necklace corresponds to the positroid $M(W)$.
+Recall from the discussion following Definition~\ref{def:grassmann necklace}, and equation \eqref{basesofmatroids} in particular, that it suffices to show:
+\begin{itemize}
+\item For each $i \in [n]$, $I_i$ is a basis for $M(W)$.
+\item If $J$ is lexicographically smaller than $I_i$ with respect to $<_i$ (for any $i \in [n]$) then $J$ is not a basis for $M(W)$. 
+\end{itemize}
+The first point follows immediately: since the algorithm is pairing each $j \in I_i$ with a unique propagator supported on that vertex, $I_i$ is a basis for $M(W)$ by Corollary~\ref{lem basis as perm}.
+
+For the second point, consider the matrix $C(W)$ associated to the diagram $W$.
+Recall that $C(W)$ is only defined up to an ordering of the propoagators of $W$.
+Therefore order them according to the ordering induced by the algorithm for $I_i$.
+Write $\cP = \{p_1, \ldots , p_k\}$.
+That is, $p_i$ defines the $i^{th}$ row of $C(W)$.
+If $p, q \in \Prop(i)$ are two propagators supported on the vertex $i$, we may write $p = (a_p, b_p)$ and $q = (a_q, b_q)$, with the initial vertices $a_p$ and $a_q$ in the set $\{i, i-1\}$.
+By construction, the propagator $q$ is located clockwise relative to $p$ if and only if $p$ is inside $q$.
+That is, $p \in \cP_{in}(q, <_{a_q})$.
+
+For $m < k$, write $\cP_m =\{p_1, \ldots , p_m\} \subset \cP$ to indicate the first $m$ propagators.
+For any subset of propagators $Q \subset \cP$, write $W|_Q = (Q, [n])$ be the subdiagram of $W$ consisting only of the propagators in $Q$ and all the vertices $[n]$.
+
+Write $I_i(p_j)=a_j$.
+By algorithm \ref{alg:put GN on WLD}, $a_j$ is the smallest number in the $<_{a_{j-1}}$ ordering such that $c_{j, a_j} \neq 0$ (that is, is an indeterminant entry).
+It is the first column in the $j^{th}$ row of $C(W)$ that is both non-zero and is greater than the index contributed by the previous propagator:  \bas \begin{bmatrix}\ddots & & & & & & \\ \ldots  & c_{j-1, a_{j-1}} & * & \ldots &  & & \\  \ldots  &* &0 & \ldots & 0 &c_{j, a_j} & \ldots \\ & & & & & & \ddots \end{bmatrix}  \eas
+
+\hlfix{In particular, any number between two consecutive indices in $I_i$, say $a_j < v < a_{j+1}$, correspond to vertices inside the propagator $p_j$ in the $a_j-1$ ordering.
+}{I know we got rid or interior vertices.
+Can we bring it back or rephrase?} Furthermore, every propagator preceeding $p_j$ is outside it in the same ordering: $\cP_{j-1} \subset \cP_{out}(p_j)$ in the $a_j-1$ ordering.
+
+Let $J = (j_1,\ldots j_k)$ be a sequence that is lexicographically less than $I_i = (a_1 \ldots a_k)$: $J <_i I_i$.
+By the above, for some $m < k$, $j_m <_i a_m$ and the matrix entry $c_{m, j_m} = 0$ is $0$.
+Without loss of generality, let $m$ be the smallest $m$ in the $<_i$ order for which this is true: \bas \forall l <m, \; I_i(p_l) = j_l \; ; \; j_m < I_i(p_m) \;.\eas Write $J_m = (j_1, \ldots, j_m)$ indicate the first $m$ entries of $m$.
+
+We claim that $J_m$ is not a basis for $W|_{\cP_m}$.
+To see this, first note that, since $c_{m, j_m} = 0$, the propagator $p_m$ is not supported on $j_m$.
+Furthermore, by construction, $a_{m-1} < j_m < a_m$.
+Therefore, $j_m \in V_{in}(p_{j_m})$ in the $a_j-1$ ordering.
+Since  $\cP_{j-1} \subset \cP_{out}(p_j)$ in the $  a_j-1$ ordering, non-crossing of propagators ensures that none of the first $m-1$ propoagators are supported on the vertex $j_m$.
+This implies that the minor of $C(W|_{\cP_m})$ defined by $J_{m}$, has a column of $0$s.
+That is, $J_m$ is not an independent set in $C(W|_{\cP_m})$, and thus not in $C(W)$.
+
+\end{proof}
+}
 We can now unambiguously refer to Algorithm~\ref{alg:put GN on WLD} as the Grassmann necklace algorithm.

### 2019-06-22 GWLDCII.tex
fixed a whole in the purple proof

@@
 It is the first column in the $j^{th}$ row of $C(W)$ that is both non-zero and is greater than the index contributed by the previous propagator:  \bas \begin{bmatrix}\ddots & & & & & & \\ \ldots  & c_{j-1, a_{j-1}} & * & \ldots &  & & \\  \ldots  &* &0 & \ldots & 0 &c_{j, a_j} & \ldots \\ & & & & & & \ddots \end{bmatrix}  \eas
-
-\hlfix{In particular, any number between two consecutive indices in $I_i$, say $a_j < v < a_{j+1}$, correspond to vertices inside the propagator $p_j$ in the $a_j-1$ ordering.
-}{I know we got rid or interior vertices.
-Can we bring it back or rephrase?} Furthermore, every propagator preceeding $p_j$ is outside it in the same ordering: $\cP_{j-1} \subset \cP_{out}(p_j)$ in the $a_j-1$ ordering.
+Since $p$ never contributes its last vertex in the $<_i$ order to $I_i$, by Lemma \ref{lem no fourth vertex}, every propagator preceeding $p_j$ is outside it in the $a_j-1$ ordering: $\cP_{j-1} \subset \cP_{out}(p_j)$.
 
@@
 By the above, for some $m < k$, $j_m <_i a_m$ and the matrix entry $c_{m, j_m} = 0$ is $0$.
-Without loss of generality, let $m$ be the smallest $m$ in the $<_i$ order for which this is true: \bas \forall l <m, \; I_i(p_l) = j_l \; ; \; j_m < I_i(p_m) \;.\eas Write $J_m = (j_1, \ldots, j_m)$ indicate the first $m$ entries of $m$.
+Without loss of generality, let $m$ be the smallest $m$ in the $<_i$ order for which this is true: \bas \forall l <m, \; I_i(p_l) = j_l \; ; \; j_m < I_i(p_m) \;.\eas Write $J_m = (j_1, \ldots, j_m)$ indicate the first $m$ entries of $J$.
 
@@
 To see this, first note that, since $c_{m, j_m} = 0$, the propagator $p_m$ is not supported on $j_m$.
-Furthermore, by construction, $a_{m-1} < j_m < a_m$.
-Therefore, $j_m \in V_{in}(p_{j_m})$ in the $a_j-1$ ordering.
-Since  $\cP_{j-1} \subset \cP_{out}(p_j)$ in the $  a_j-1$ ordering, non-crossing of propagators ensures that none of the first $m-1$ propoagators are supported on the vertex $j_m$.
-This implies that the minor of $C(W|_{\cP_m})$ defined by $J_{m}$, has a column of $0$s.
-That is, $J_m$ is not an independent set in $C(W|_{\cP_m})$, and thus not in $C(W)$.
+If $p_m$ does not share support with any propagator in $\cP_m$ in the cyclic interval $[i, j_m]$, then the minor of $C(W|_{\cP_m})$ defined by $J_{m}$, has a row of $0$s.
+
+Otherwise, let $p_l$ be a propagator preceeding $p_m$ ($p_l \in \cP_{m-1}$) that shares support with it in $J_m$: $V(p_l) \cap V(p_m) \cap J_m \neq \emptyset$.
+Then $p_l \in Q$ is positioned clockwise to $p_m$ on vertex $a_l$, therefore, $p_l$ is outside $p_m$ in the $a_l -1$ order.
+Since $a_l <_i j_m <_i a_m$ with $a_l$ and $a_m$ both in the support of $p_m$, \hlfix{$j_m$ is inside $p_m$ in the $a_l-1$ ordering.
+}{I know we got rid or interior vertices.
+Can we bring it back or rephrase?} Furthermore since all of $\cP_{m-1} \subset \cP_{out}(p_m)$ is outside of $p_m$ in that $a_l-1$ order, and $j_m$ is a vertex inside it, no propagator prior to $p_m$ can be supported on $j_m$.
+Otherwise, one would have crossing propagators.
+Therefore, the minor of $C(W|_{\cP_m})$ defined by $J_{m}$, has a column of $0$s.
 
@@
 }
+
 We can now unambiguously refer to Algorithm~\ref{alg:put GN on WLD} as the Grassmann necklace algorithm.

### 2019-06-25 GWLDCII.tex
take 3 at purple proof. Different, but more elegant

@@
 If $W$ is an admissible Wilson loop diagram with $k$ propagators, then Algorithm~\ref{alg:put GN on WLD} assigns exactly $k$ vertices to each $I_i$.
+\sanote{suddenly confused.
+Don't we need working about in going onely once around or somesuch?}
 \end{cor}
@@
 
+For the second point, order the propagators according to the ordering induced by the algorithm for $I_i$.
+Write $\cP = \{p_1, \ldots , p_k\}$.
+That is, $p_i$ defines the $i^{th}$ row of $C(W)$.
+For $m<k$, write $\cP_m = \{p_1, \ldots , p_k\}$.
+
+Write $I_i(p_j)=a_j$.
+If two consecutive propagators do not contribute consecutive vertices, that is, there exist $a_{j-1} <_i x <_i a_j$ then the vertex $x$ supports only propagators in $\cP_j$, if any: $\Prop(x) \subset \cP_j$.
+
+Let $J = (j_1,\ldots j_k)$ be a sequence that is lexicographically less than $I_i = (a_1 \ldots a_k)$: $J <_i I_i$.
+By the above, for some $m < k$, $a_{m-1} <_i j_m <_i a_m$ and the matrix entry $c_{m, j_m} = 0$ is $0$.
+Without loss of generality, let $m$ be the smallest $m$ in the $<_i$ order for which this is true: \bas \forall l <m, \; I_i(p_l) = j_l \; ; \; j_m < I_i(p_m) \;.\eas Write $J_m = (j_1, \ldots, j_m)$ indicate the first $m$ entries of $J$.
+We claim that there exists some subset  of vertices $U \subset J_m$ such that $|\Prop(U)| < |U|$.
+
+Consider the vertices contributed by the propagators originally supported on $j_m$: $V = I_i(\Prop(j_m))$.
+By construction, these are a subset of $J_{m-1}$.
+Note that $\Prop(V) \subset \cP_m$.
+Let $p_l$ be supported on $j_m$.
+If $q$ is suported on $p_l$, either $q$ preceeds $p_l$ (i.e.
+is not there when the algorithm reaches $a_l$) or is positioned counterclockwise to $p_l$ at the vertex $a_l$.
+That is, $q$ is inside $p_l$ in the $<_i$ ordering.
+By Lemma \ref{lem no fourth vertex}, $q$ does not contibute its last supporting vertex to $I_i$.
+That is, $I_i(q) <j_m$.
+\hlfix{But this implies that $q$ contributed before $p_m$, which contradicts the hypothesis.}{Seems to demand that $I_i$ catches all propagators in a single circuit of the vertices.
+Is this explicit anywhere, or am I jumping the gun?} Therefore $q \in \cP_{m-1}$.
+
+If $\Prop(j_m) = \Prop(V)$, we have that $V$ and $V \cup j_m$ support the same propagators. That is, \bas |\Prop(V)| = |V| = |\Prop(V \cup j_m )| <  |V \cup j_m| \;.\eas
+
+If $\Prop(j_m) \subsetneq \Prop(V)$, expand $V$ to include the vertices contributed by $\Prop(V)$.
+That is, $V' = I_i(\Prop(V))$.
+By the argument above, $\Prop(V) \subset \cP_m$.
+If $\Prop(V) = \Prop(V')$ then the relevant vertex set is $V'$.
+Else, continue expanding $V'$ in this manner until no new propagators are added.
+Since all of these sets of propagators are contained in $\cP_m$, which is finite, this process is finite.
+
+\begin{comment}
+By algorithm \ref{alg:put GN on WLD}, $a_j$ is the smallest number in the $<_{a_{j-1}}$ ordering such that $c_{j, a_j} \neq 0$ (that is, is an indeterminant entry).
+Therefore, $p_m \not \in \Prop(j_m)$.
+In fact, no $q$ that follow $p_m$ in the ordering can be supported on $j_m$.
+Since $j_m < a_m$, the algorithm for $I_i$ checks this vertex before $a_m$.
+If any propagator in $\cP \setminus \cP_{m-1}$ are supported on $j_m$, then this propapagator would preceed $p_m$, i.e.
+be an element of $\cP_{m-1}$.
+Therefore, the only non-zero entries in column $j_m$ of $C(W)$ lie in the first $m-1$ rows.
+
+Therefore, $\Prop(j_m) \subset \cP_{m-1}$.
+Let $V =  V(\Prop(j_m)) \cap J_{m-1}$ be the vertices in $J_m$ supporting the propagators supported on $j_m$.
+That is, $V$ is contains the vertices contributed by $\Prop(j_m)$.
+So $|\Prop(j_m)| \leq |V|$.
+We show that $\Prop (V) \subset \Prop_{m-1}$.
+Suppose otherwise.
+Let $q \in \cP \setminus \cP_m$ be a propagators after $p_m$ and $p_l \in \Prop(j_m)$ a propagators before $p_m$ supported on $j_m$ such that both $q$ and $p_l$ are supported on $I_i(p_l)= a_l$.
+Since $p_l$ contributes $a_l$, it must be the clockwisemost propagator in $\cP \setminus \cP_{l-1}$ supported on $a_l$.
+In other words, $q \in \cP_{in}(p_l, <_{a_l-1})$ is inside $p_l$ in the $a_l-1$ order.
+Specifically, the last supporting vertex of $q$ is strictly less than $j_m$.
+By Lemma \ref{lem no fourth vertex}, $q$ does not contibute its last supporting vertex to $I_i$.
+That is, $I_i(q) <j_m$.
+\hlfix{But this implies that $q$ contributed before $p_m$, which contradicts the hypothesis.}{Seems to demand that $I_i$ catches all propagators in a single circuit of the vertices.
+Is this explicit anywhere, or am I jumping the gun?}
+
+By construction, this implies that $V \subset \Prop(j_m)$. But $V$ contains the vertices 
+Since $J_{m-1}$ is independent, $V \subset J_{m-1}$ is too. Therefore, $|V| \leq |\Prop(V)| $. Since  $\Prop (V) \subset \cP_{m-1}$
+***************
 For the second point, consider the matrix $C(W)$ associated to the diagram $W$.
@@
 That is, $p_i$ defines the $i^{th}$ row of $C(W)$.
-If $p, q \in \Prop(i)$ are two propagators supported on the vertex $i$, we may write $p = (a_p, b_p)$ and $q = (a_q, b_q)$, with the initial vertices $a_p$ and $a_q$ in the set $\{i, i-1\}$.
-By construction, the propagator $q$ is located clockwise relative to $p$ if and only if $p$ is inside $q$.
-That is, $p \in \cP_{in}(q, <_{a_q})$.
-
-For $m < k$, write $\cP_m =\{p_1, \ldots , p_m\} \subset \cP$ to indicate the first $m$ propagators.
-For any subset of propagators $Q \subset \cP$, write $W|_Q = (Q, [n])$ be the subdiagram of $W$ consisting only of the propagators in $Q$ and all the vertices $[n]$.
 
@@
 It is the first column in the $j^{th}$ row of $C(W)$ that is both non-zero and is greater than the index contributed by the previous propagator:  \bas \begin{bmatrix}\ddots & & & & & & \\ \ldots  & c_{j-1, a_{j-1}} & * & \ldots &  & & \\  \ldots  &* &0 & \ldots & 0 &c_{j, a_j} & \ldots \\ & & & & & & \ddots \end{bmatrix}  \eas
-Since $p$ never contributes its last vertex in the $<_i$ order to $I_i$, by Lemma \ref{lem no fourth vertex}, every propagator preceeding $p_j$ is outside it in the $a_j-1$ ordering: $\cP_{j-1} \subset \cP_{out}(p_j)$.
 
@@
 Without loss of generality, let $m$ be the smallest $m$ in the $<_i$ order for which this is true: \bas \forall l <m, \; I_i(p_l) = j_l \; ; \; j_m < I_i(p_m) \;.\eas Write $J_m = (j_1, \ldots, j_m)$ indicate the first $m$ entries of $J$.
+
+We claim that the $j_m^{th}$ column of $C(W)$ is in the span of the columns indexed by $J_{m-1}$.
+
+Since $J_{m-1}$ is an independent set in $C(W)$, row reduce the first $j_{m-1}$ columns of $C(W)$ to have $1$ in the $(r, j_r)$ position and $0$ to the right: \bas \begin{bmatrix}1 &0  &\ldots  & &  &0 \\  * & \ldots  & * & 1 & 0&\ldots \\    &\ddots &  &  &\ldots & 1 \\  *&* &* &\ldots &* &* \\  &\ddots & & & \ddots &  \\ *&* &* &\ldots &* &*  \end{bmatrix}  \;.\eas \sanote{fix this!
+wrote echelon order!}
+
+Next consider the $j_m^{th}$ column of $C(W)$.
+First note that, since $c_{m, j_m} = 0$.
+Furthermore, no $q$ that follow $p_m$ in the ordering can be supported on $j_m$.
+Since $j_m < a_m$, the algorithm for $I_i$ checks this vertex before $a_m$.
+If any propagators remain to be supported on this vertex after the removal of $p_1$ to $p_{m-1}$, then this propapagator would preceed $p_m$.
+Therefore, the only non-zero entries in column $j_m$ of $C(W)$ lie in the first $m-1$ rows.
+\sanote{add something here} Therefore, column $j_m$ lies in the span of the first $j_{m-1}$ columns of $C(W)$.
+
+*******
+%If $p, q \in \Prop(i)$ are two propagators supported on the vertex $i$, we may write $p = (a_p, b_p)$ and $q = (a_q, b_q)$, with the initial vertices $a_p$ and $a_q$ in the set $\{i, i-1\}$.
+By construction, the propagator $q$ is located clockwise relative to $p$ if and only if $p$ is inside $q$.
+That is, $p \in \cP_{in}(q, <_{a_q})$.
+
+%For $m < k$, write $\cP_m =\{p_1, \ldots , p_m\} \subset \cP$ to indicate the first $m$ propagators.
+For any subset of propagators $Q \subset \cP$, write $W|_Q = (Q, [n])$ be the subdiagram of $W$ consisting only of the propagators in $Q$ and all the vertices $[n]$.
+
+%Since $p$ never contributes its last vertex in the $<_i$ order to $I_i$, by Lemma \ref{lem no fourth vertex}, every propagator preceeding $p_j$ is outside it in the $a_j-1$ ordering: $\cP_{j-1} \subset \cP_{out}(p_j)$.
 
@@
 Therefore, the minor of $C(W|_{\cP_m})$ defined by $J_{m}$, has a column of $0$s.
-
+******
+\end{comment}
 \end{proof}

### 2019-06-25 GWLDCI.tex
equal matroids iff equivalent diagrams proof

@@
 
-% \begin{comment}
-
-% \begin{dfn}\label{def prop flat} 
-% Let $W = (\cP,n)$ be an admissible Wilson loop diagram and $P \subseteq \cP$. The set $F(P) := V(P^c)^c$ is called the {\em propagator flat} of $P$.
-% \end{dfn}
-% Thus in Lemma \ref{contractsubdiaglem} above we would contract $M(W)$ by the propagator flat $F(P^c)$ of the {\em complement} of $P$ in order to study $(P,V(P))$.
-The justification for this notation is given by (1) of the next lemma: the set $F(P)$ consists of vertices which {\em only} support propagators in $P$ (or no propagators at all).
-
-% \begin{lem}\label{lem properties of prop flats} \sanote{do we need the first 2? They follow directly from the definition 1.2. Do we use them later?}
-% Let $F(P)$ be a propagator flat as defined above. Then
-% \begin{enumerate}
-% \item $F(\emptyset)$ is exactly the set of vertices which support no propagators, while for $P \neq \emptyset$ we have \[F(P) = \big(V(P) \setminus V(P^c)\big) \cup F(\emptyset).\] \note{updated (1) to match new definition of $F(P)$; }
-% \item If $Q\subseteq P$ then $F(Q) \subseteq F(P)$.
-% \item $F(P)$ is a flat of $M(W)$, thus justifying the name ``propagator flat''.
-% \end{enumerate}
-% \end{lem} \note{I'd like to attach this to the "generic facts about matroids" in lemma 2.2?}
-% \begin{proof}
-% The proof of (1) and (2) are routine applications of the definition and are omitted.
-
-% To prove (3), we need to show that $F(P)$ is maximally dependent.
-If $F(P) = [n]$ then this is automatic, so suppose not and let $v \in [n] \setminus F(P)$.
-In other words, $v \in V(P^c)$ and so $v$ supports some propagator $q \not\in P$.
-Let $S \subseteq F(P)$ be an independent set of maximal size.
-Then $\Prop(S) \subseteq P$ by (1), and no subset of $S$ supports fewer propagators than the number of vertices it contains (this is the definition of an independent set in $M(W)$).
-Since $v$ supports a new propagator $q \not\in P$, the set $S \cup \{v\} \subseteq F(P) \cup\{v\}$ also satisfies this independence condition.
-Thus $\rk(F(P) \cup\{v\}) = \rk(F(P)) + 1$, as required.
-% \end{proof}
-
-% \end{comment}
-
 \begin{lem} \label{lem decompose flat}Let $F$ be a flat in $M(W)$, and let $C \subseteq F$ be the union of all circuits contained in $F$. Then the following are true:
@@
 \begin{thm} \label{exact diagrams contractions}
-If $(P, V(P)$ is an exact subdiagram of of $W$, the matroid of $(P,V(P))$ is the contraction of $M(W)$ by the propagator flat $F(P^c)$, i.e. \bas M\big((P, V(P))\big) = M(W)  / F(P^c) \;.\eas 
+If $(P, V(P))$ is an exact subdiagram of of $W$, the matroid of $(P,V(P))$ is the contraction of $M(W)$ by the propagator flat $F(P^c)$, i.e. \bas M\big((P, V(P))\big) = M(W)  / F(P^c) \;.\eas 
 \end{thm}
@@
 
-%Since the matroid defined by the subdiagram $(P , V(P))$ is not the same as the matroid associated to $W_{V(P)}$, one cannot say that the $W_{V(P)}$ is a uniform matroid.
-In fact, for any subset $U \subset V(P)$, $\rk_{W_{V(P)}}(U) \geq \rk_{(P , V(P))}(U)$.
-This is because adding propagators to vertices can only increase the rank.
-In particular this implies that, for any subset $U \subset V(P)$, if $|U| \leq |P|$, then $U$ is independent in both the restricted matroid $W_{V(P)}$, and the original, $W$.
-
 \subsection{Matroids and equivalent diagrams \label{sec: matroids and equivalence}}
@@
 
-Assume that $W$ and $W'$ are equivalent.
-Without loss of generality, write $W = (P \sqcup R, [n])$ and $W' = (P \sqcup R', [n])$, where $P \subset \cP \cap \cP'$ and $(R, V(R))$ and $(R', V(R'))$ are two maximal exact subdiagrams, with $R \neq R'$, but $V(R) = V(R')$.
-If one cannot find this partition of $\cP$ and $\cP'$, one may always find a family of diagrams, $\{W_1 \ldots W_n\}$ such that $W_{i-1}$ and $W_i$ satisfy this contion, and with $W = W_0$ and $W' = W_{n+1}$.
-That is, we can find a  transitive chain ($\{W_1 \ldots W_n\}$) between $W$ and $W'$ in the equivalence class.
-
-By Theorem \ref{exactuniformthm}, $(R, V(R))$ defines a uniform matroid. Therefore, any set $U$ of size $|R|$ is independent in the subdiagram $(R, V(R))$, and thus in $W$.
-
-By the third point of Lemma \ref{maxexactcomplementrank}, the complementary flat, $F(P)$ has rank equal to the number of propagators: $\rk(F(P)) = |P|$.
-Let $B \subset F(P)$ be a maximal independent subset of $F(P)$: $\rk (B) = |P|$.
-Since $F(P)$ is a flat, adding any element of $V(R)$ to $B$ increases the rank.
-Therefore, any basis of $W$ can be written as $B \cup U$ for some $B$ and $U$ of the form indicated.
-However, since $F(P)$ is common to both $W$ and $W'$, and $V(R) = V(R')$, any any basis of $W'$ can also be written $B \cup U$.
-Thus both matroids have the same bases sets, proving that they are the same.
+For the if direction, it suffices to prove the result for two equivalent diagrams that differ in exactly one exact subdiagram.
+Let $W$ and $W'$ be equivalent Wilson loop diagrams which can be decomposed as
+\[W = (P \sqcup R, [n]), \qquad W' = (P \sqcup R', [n]),\]
+where $(R,V(R))$ and $(R',V(R'))$ are maximal exact subdiagrams of $W$, $W'$ respectively, and $V(R) = V(R')$.
+By Theorem \ref{exactuniformthm}, $(R, V(R))$ defines a uniform matroid.
+Therefore any set $U \subseteq V(R)$ of size $|R|$ is independent in the subdiagram $(R, V(R))$, and thus in $W$.
+
+Now consider the complement $V(R)^c$, which is just the propagator flat $F(R^c)$.
+By Lemma \ref{maxexactcomplementrank}, $F(R^c)$ is a cyclic flat of rank $|R^c| = |P|$ in $M(W)$.
+Let $B \subseteq V(R)^c$ be a maximal independent subset of $V(R)^c$, i.e.
+$\rk (B) = |P|$.
+Since $V(R)^c$ is a flat, adding any element of $V(R)$ to $B$ increases the rank of the set.
+
+Therefore, any basis of $W$ can be written as $B \sqcup U$ for some $B$ and $U$ of the form indicated described above. Applying the same argument to $W'$
+
+However, since $F(P)$ is common to both $W$ and $W'$, and $V(R) = V(R')$, any basis of $W'$ can also be written $B \cup U$. Thus both matroids have the same bases sets, proving that they are the same.
 
@@
 
+\begin{proof}[Proposed alternative proof]
+One direction has been proved in \cite[Theorem 1.18]{wilsonloop}, but we give a different proof here to be consistent with the method of this paper.
+
+For the if direction, it suffices to prove the result for two equivalent diagrams that differ in exactly one exact subdiagram.
+Let $W$ and $W'$ be equivalent Wilson loop diagrams which can be decomposed as
+\[W = (P \sqcup R, [n]), \qquad W' = (P \sqcup R', [n]),\]
+where $(R,V(R))$ and $(R',V(R'))$ are maximal exact subdiagrams of $W$ and $W'$ respectively, and $V(R) = V(R')$.
+
+By Theorem \ref{exactuniformthm}, $M(R, V(R))$ and $M(R',V(R'))$ are both uniform matroids of rank $|R| = |R'|$; in particular, this means that any subset of $V(R)$ is independent in both $M(W)$ and $M(W')$.
+
+Now consider the propagator flat $F(P)$, which is a cyclic flat of rank $|P|$ in both $M(W)$ and $M(W')$ by Lemma \ref{maxexactcomplementrank}.
+Let $B \subseteq F(P)$ be an independent set of rank $|P|$.
+Adding any element of $V(R)$ to $B$ increases its rank in both matroids since $F(P)$ is a flat and $F(P) \cap V(R) = \emptyset$, so we can lift any independent set in $F(P)$ to an independent set of both $M(W)$ and $M(W')$ by adjoining any independent set in $V(R)$.
+In particular, $B\sqcup U$ is a basis in both $M(W)$ and $M(W')$ for any $U \subseteq V(R)$ with $|U| = |R|$.
+
+Finally, note that any basis of $M(W)$ or $M(W')$ must be of this form, since $[n] = F(P) \sqcup V(R)$ and $\rk F(P) + \rk V(R) = |P| + |R| = n$.
+Thus both matroids have the same set of bases, proving that they are the same.
+
+For the converse, suppose that $M(W) = M(W') = M$.
+This immediately implies that $|\cP| = |\cP'|$, so to demonstrate the equivalence of $W$ and $W'$ it suffices to show that for any maximal exact subdiagram $(P,V(P))$ in $W$, there is a corresponding maximal exact subdiagram $(P',V(P'))$ in $W'$ with $V(P) = V(P')$.
+
+So let $(P,V(P))$ be a maximal exact diagram in $W$.
+By Lemma~\ref{maxexactcomplementrank}, this implies that $F:=F(P^c)$ is a cyclic flat in $M$.
+Viewing $M$ as the matroid of $W'$, Lemma~\ref{lem decompose flat} implies that $F = F(\Prop_{W'}(F))$ (recall that ``cyclic'' simply means ``a union of circuits'', so the union of all circuits in $F$ is $F$ itself).
+Define $Q^c = \Prop_{W'}(F)$, so that $F(P^c) = F = F(Q^c)$, and therefore $V(P) = V(Q)$.
+
+By Lemma~\ref{maxexactcomplementrank} we know that $\rk(F) = |P^c|$; however, by Lemma~\ref{lem facts about WLD matroids} we also know that the rank of a cycle is equal to the number of propagators supported on that cycle, so $\rk(F) = |\Prop_{W'}(F)| = |Q^c|$ as well.
+Since $(P,V(P))$ is exact and we have shown that $V(P) = V(Q)$ and $|P| = |Q|$, it follows that $|V(Q)| = |Q| + 3$, i.e.
+$(Q,V(Q))$ is exact in $W'$.
+
+However, $(Q,V(Q))$ is not a priori {\em maximal} exact, so let $(P',V(P'))$ be the maximal exact subdiagram in $W'$ that contains $(Q,V(Q))$ as a subdiagram (possibly trivially).
+Applying the argument above to $(P',V(P'))$, we obtain an exact subdiagram $(R,V(R))$ in $W$ with $V(R) = V(P')$ and $|R| = |P'|$.
+Now we have
+\[V(P) = V(Q) \subseteq V(P') = V(R),\]
+which implies that $(P,V(P)) = (R,V(R))$ by the maximality of $(P,V(P))$, and hence $(Q,V(Q)) = (P',V(P'))$ is maximal exact in $W'$.
+\end{proof}
+
 Since there is a unique way to decompose $W$ into maximal exact subdiagrams, it is logical to ask how many diagrams there are in an equivalence class.

### 2019-06-28 GWLDCI.tex
exposition in paper 1 and looked over 4.5

@@
 
-Therefore, any basis of $W$ can be written as $B \sqcup U$ for some $B$ and $U$ of the form indicated described above. Applying the same argument to $W'$
+Therefore, any basis of $W$ can be written as $B \sqcup U$ for some $B$ and $U$ of the form indicated described above. We may apply the same arguments to $W'$.
 
@@
 
-If not, there would be a cyclic flat $F_j$ of $M$.
+If not, there would be a cyclic flat $F_j$ of $M$ in one set but not the other.
 Without loss of generality, write $F_j \in \mathcal{F} \setminus \mathcal{F}'$.
@@
 
-\begin{proof}[Proposed alternative proof]
+\begin{proof}[Proposed alternative proof] \sanote{Looks good to me}
 One direction has been proved in \cite[Theorem 1.18]{wilsonloop}, but we give a different proof here to be consistent with the method of this paper.
@@
 The obvious next question would be to enumerate the number of equivlence classes.
-We do not obtain a formula for this, but do obtain an alternate characterization of the equvalence classes which is the subject of the next section.
+
+We know from example, for instance \cite{casestudy} that, even after taking the dimension of the positroid cell into consideration\footnote{it is proven in \cite{GWLDII} and \cite{Marcott} that Wilson loop diagrams with $k$ propagators map to $3k$ dimensional positroid cells}, many positroid cells do not appear as admissible Wilson loop diagrams with a fixed number of propagators and vertices.
+That is, the map from admissible Wilson loop diagrams to positroid cells of the correct dimension in the correct Grassmannian neither injective nor surjective.
+We do not obtain a formula for the number of cells, but do obtain an alternate characterization of the equvalence classes which is the subject of the next section.
 
@@
 
-The connection between admissible Wilson loop diagrams and polytope dissections suggests a connection to associahedra. First we need some background. \sanote{expand}
+The correspondence between (weakly) admissible Wilson loop diagrams and polygon dissections shown in section \ref{sec: polygon partitions} suggests a connection to associahedra.
+First we need some background.
+There is a realization of associahedra that is charactertized by polygon partitions.
+In this section, we show that the number of equivalence classes of Wilson loop diagrams correspond to the number of non-parallel faces of the appropriate associahedron (Theorem \ref{thm:count }).
+While this section does not give an explicit formula for the number of these faces, we hope that this linkage with a combinatorially well studied object will shed light on the issue in the future.
 
@@
 All of these are equivalent (as Wilson loop diagrams) in the sense that they are only retriangulations away from each other; meanwhile, as noted above, all vertices of $A_n$ are parallel to each other.
-It will be convenient in what follows to include these diagrams, but the results are easily modified to remove them if needed: Propositions~\ref{prop easy way} and \ref{prop hard way} would be identical if we replaced ``weakly admissible'' by ``admissible'', while Corollary~\ref{cor:count inequiv diagrams} could be changed to consider only admissible diagrams by subtracting 1 from the number of non-parallel faces in order to account for the missing dimension 0 faces.
+It will be convenient in what follows to include these diagrams, but the results are easily modified to remove them if needed: Propositions~\ref{prop easy way} and \ref{prop hard way} would be identical if we replaced ``weakly admissible'' by ``admissible'', while Theorem~\ref{thm:count inequiv diagrams} could be changed to consider only admissible diagrams by subtracting 1 from the number of non-parallel faces in order to account for the missing dimension 0 faces.
 
@@
 (Note that $D$ may have many non-triangle faces and so $V_{>3}(D)$ will be the union of the vertices of each non-triangle face.) We also write $[x_i,x_j]$ for the set of vertices from $x_i$ to $x_j$ including the endpoints, and $(x_i,x_j)$ for the same set but excluding the endpoints.
+\sanote{make a dfn?}
 
@@
 
-  As observed in the proof of Proposition~\ref{prop easy way}, the support of any non-zero vector parallel to an edge is on the indices corresponding to the four vertices bounding the quadrilateral of the dissection associated with the edge.
-Thus if $V_{>3}(\tau(W)) \neq V_{>3}(\tau(X))$ (notation as defined before Lemma~\ref{lem good quads}) then the span of the vectors parallel to their edges has different support and so they cannot be parallel.
+As observed in the proof of Proposition~\ref{prop easy way}, \st{the support of any non-zero vector parallel to an edge is on the indices corresponding to the four vertices bounding the quadrilateral of the dissection associated with the edge.}{\color{violet}any non-zero vector in $\R^n$ paralell to an edge of $A_n$ has non-zero entries only in the coordinates corresponding to the four vertices bounding the quadrilateral of the dissection associated with the edge.}  Thus if $V_{>3}(\tau(W)) \neq V_{>3}(\tau(X))$ \hlfix{(notation as defined before Lemma {\ref{lem good quads}})}{refer to dfn?} then the span of the vectors parallel to their edges has different support and so they cannot be parallel.
 So we can assume that $V_{>3}(\tau(W)) = V_{>3}(\tau(X))$.
@@
 
-Propositions~\ref{prop easy way} and \ref{prop hard way} together imply:
-\begin{cor}\label{cor:count inequiv diagrams}
+Propositions~\ref{prop easy way} and \ref{prop hard way} together imply the main result of this section:
+\begin{thm}\label{thm:count inequiv diagrams}
   The number of inequivalent weakly admissible Wilson loop diagrams on $n$ is the number of non-parallel faces in the associahedron $A_n$.
-\end{cor}
+\end{thm} \sanote{this is the main result of the section}
 

### 2019-06-28 GWLDCII.tex
minor tweaks to the remark about being locally the same in paper 2

@@
 
+{\color{violet}
+Each $I_i$ also imposes an ordering on the propagators, determined by when the propagator contributes to the sequence:
+\begin{dfn} \label{proporderingdfn}
+The ordering of the propagators on $W = (\cP, [n])$ defined by $I_i^W$ is $\cP = \{p_1, \ldots p_k\}$, where 
+\[I_i = \{I_i(p_1) <_i I_i(p_2) <_i \ldots <_i I_i(p_k)\}.\]
+(The superscript $W$ is omitted here to simplify the notation.)\note{Sian tweaked this slightly to emphasise the $<_i$ order, because standard convention in most papers is to write all GN terms in the 1-order.}
+\end{dfn}
+
+Since each propagator is removed by the algorithm after it contributes, each propagator contributed exactly once to $I^W_i$, making the above ordering well defined.}
+
 \begin{eg}\label{eg:apply GN alg}Consider the admissible Wilson loop diagram
@@
 \end{itemize}
-There are no propagators left in the diagram, so the algorithm terminates and we have ${I_1 = \{1,2,3,5\}}$, or $1235$ for short. Viewed as a function, we have
-\[I_1: \cP \longrightarrow [n] : \quad I_1(p) = 3,\quad I_1(q) = 2, \quad I_1(r) = 1, \quad I_1(s) = 5.\]
+There are no propagators left in the diagram, so the algorithm terminates and we have ${I_1 = \{1,2,3,5\}}$, or $1235$ for short.
+So the propagators are ordered $r,q,p,s$ with respect to $I_1$, and $I_1$ viewed as a function is given by
+\[I_1: \cP \longrightarrow [n] : \quad I_1(r) = 1,\quad I_1(q) = 2, \quad I_1(p) = 3, \quad I_1(s) = 5.\]
 Applying the algorithm for all 8 starting vertices, we obtain the sets
@@
 
-\medskip
-
-{\color{violet}\begin{dfn} \label{proporderingdfn}
-Each $I^W_i$ imposes an ordering on the propagators of $W = (\cP, n)$, determined by when the propagator contributes to the sequence.
-If $W$ has $k$ propagators, we ma write $\cP = \{p_1, \ldots p_k\}$ with $I_i = I_i(p_1)I_i(p_2) \ldots I_i(p_k)$, where the superscript $W$ is taken as read.
-\end{dfn}
-
-Since each propagator is removed by the algorithm after it contributes, each propagator contributed exactly once to $I^W_i$, making the above ordering well defined.}
-
 \begin{rmk}\label{rmk algorithm locally same}
-The following observation will be very useful in many of the arguments below.
+The following observation about the local behavior of the algorithm will be very useful in many of the arguments below.
 
 Suppose we are going through the algorithm to construct $I_i^W$ for some $i$, and we are currently at step $j$ of the loop.
-Consider the diagram $W'$ formed by $W$ with all the propagators already contributed removed.
-Not that the algorithm automatically removes a propagator once it contibutes to the algorithm.
-Now suppose for some other diagram $V$ on the same vertex set we are constructing $I_m^V$ for some $m$, and we are at step $j$ of the loop, for the same $j$ as above.
-Again let $V'$ be $V$ with all the propagators already contributed removed.
-\sanote{rewrote, do we like this?}
-
-With this setup, if there is an interval, $(j-1, \ldots, \ell+1)$ (with $\ell <_i i$ and $\ell <_m m$) in $W'$ and $V'$ where the propagators ending in that interval are identical in both diagrams, then the construction of $I_i^W$ and $I_m^V$ is identical up to and including step $\ell$.
-The constructions are identical for those steps simply because the local situation of propagators supported at $j, j+1, \ldots, \ell$ is identical in both cases and the algorithm only sees the local situation at the vertex corresponding to the current step.
+Consider the diagram $W'$ formed by removing from $W$ all propagators that have already contributed to $I_i^W$.
+(This just replicates the behavior of the algorithm, which removes each propagator once it contibutes to $I_i^W$.)  Now suppose for some other diagram $V$ on the same vertex set we are constructing $I_m^V$ for some $m$, and we are at step $j$ of the loop, for the same $j$ as above.
+Again obtain $V'$ from $V$ by removing all propagators assigned so far.
+\sanote{rewrote, do we like this?}\note{Sian: rewrote some more.
+We need to be a bit careful with ``contributes'' because $p$ is assigned, not contributed, by the algorithm: vertices are contributed, propagators contribute.}
+
+With this setup, if we can find a vertex $\ell$ (with $\ell <_i i$ and $\ell <_m m$) such that the configuration of propagators ending in the interval $(j-1, \ldots, \ell+1)$ is identical in both $W'$ and $V'$, then the vertices contributed to $I_i^W$ and $I_m^V$ are the same from step $j$ to step $\ell$ (inclusive).
+See Figure~\ref{fig:locally identical} for an illustration of this.
+
+\begin{figure}
+\includegraphics[scale=0.2]{locally_identical.jpg}
+\caption{$W'$ and $V'$ are locally the same between $j$ and $l+1$, so we will have $I_i^W\cap [j,l] = I_m^V\cap[j,l]$ even though $p \neq s$ and $q \neq t$.}\label{fig:locally identical}
+\end{figure}
 \end{rmk}
@@
 \includegraphics[width=15cm]{4th_vertex}
-\caption{The two possible configurations in which a propagator can contribute its $<_i$-maximal support vertex to $I_i$.}
+\caption{The two types of configuration in which a propagator could (in theory) contribute its $<_i$-maximal support vertex to $I_i$.}
 \label{fig:no fourth vertex}
@@
 \begin{cor}\label{GN alg well defined}
-If $W$ is an admissible Wilson loop diagram with $k$ propagators, then Algorithm~\ref{alg:put GN on WLD} assigns exactly $k$ vertices to each $I_i$.
+If $W$ is an admissible Wilson loop diagram with $k$ propagators, then Algorithm~\ref{alg:put GN on WLD} assigns exactly $k$ distinct vertices to each $I_i$.
 \sanote{suddenly confused.
-Don't we need working about in going onely once around or somesuch?}
+Don't we need working about in going onely once around or somesuch?}\note{Sian: added the word ``distinct'' in the statement and a few words to the last line of the proof, does that help?}
 \end{cor}
@@
 It follows from the proof of Lemma~\ref{lem no fourth vertex} that in applying Algorithm~\ref{alg:put GN on WLD} to construct the set $I_i$, the algorithm can never reach the fourth vertex of a propagator's support (ordered with respect to $<_i$) without having already assigned $p$.
-Therefore if the algorithm starts at vertex $i$, all propagators must have been eliminated by the time it gets to vertex $i-1$, ensuring that the algorithm terminates and that $I_i$ contains exactly $k$ distinct elements.
+Therefore if the algorithm starts at vertex $i$, all propagators must have been eliminated by the time it gets to vertex $i-1$, ensuring that the algorithm is completed in less than one full circumnavigation of the diagram and that $I_i$ contains exactly $k$ distinct elements.
 \end{proof}

### 2019-06-28 GWLDCII.tex
one small change discussed on the phone

@@
   \item Either the edge $i$ in $W'$ only supports $p$, or the edge $i$ in $W'$ supports exactly one other propagator $q = (j,i)$, with no other propagators inside $q$ in the $<_j$ ordering. 
-\note{Sian undid Susama's change here: all we know about $q$ is that it goes from some edge $j$ to $i$, and there's nothing inside $q$ wrt that orientation.
-In a very degenerate case, $q$ could probably be $(n,i)$.}
   \end{itemize}
 \end{lem}
+Note that since the first condition tells us that $p$ has nothing inside it then then in the second condition if $q$ exists then $j<_ji<_jn-1$.
 

### 2019-06-28 GWLDCII.tex
typo

@@
 \end{lem}
-Note that since the first condition tells us that $p$ has nothing inside it then then in the second condition if $q$ exists then $j<_ji<_jn-1$.
+Note that since the first condition tells us that $p$ has nothing inside it then in the second condition if $q$ exists then $j<_ji<_jn-1$.
 

### 2019-06-28 GWLDCII.tex
added a note about the conversation we were having

@@
 
+ \note{Remember to keep an eye out when proofreading: do we just need the vertices appearing in the GN element to be the same or actually the function}
+
 Suppose we are going through the algorithm to construct $I_i^W$ for some $i$, and we are currently at step $j$ of the loop.
@@
 Again obtain $V'$ from $V$ by removing all propagators assigned so far.
-\sanote{rewrote, do we like this?}\note{Sian: rewrote some more.
-We need to be a bit careful with ``contributes'' because $p$ is assigned, not contributed, by the algorithm: vertices are contributed, propagators contribute.}
 

### 2019-06-28 GWLDCI.tex
susama's changes

@@
 
-\begin{proof}
-One direction has been proved in \cite[Theorem 1.18]{wilsonloop}, but we give a different proof here to be consistent with the method of this document.
-
-For the if direction, it suffices to prove the result for two equivalent diagrams that differ in exactly one exact subdiagram.
-Let $W$ and $W'$ be equivalent Wilson loop diagrams which can be decomposed as
-\[W = (P \sqcup R, [n]), \qquad W' = (P \sqcup R', [n]),\]
-where $(R,V(R))$ and $(R',V(R'))$ are maximal exact subdiagrams of $W$, $W'$ respectively, and $V(R) = V(R')$.
-By Theorem \ref{exactuniformthm}, $(R, V(R))$ defines a uniform matroid.
-Therefore any set $U \subseteq V(R)$ of size $|R|$ is independent in the subdiagram $(R, V(R))$, and thus in $W$.
-
-Now consider the complement $V(R)^c$, which is just the propagator flat $F(R^c)$.
-By Lemma \ref{maxexactcomplementrank}, $F(R^c)$ is a cyclic flat of rank $|R^c| = |P|$ in $M(W)$.
-Let $B \subseteq V(R)^c$ be a maximal independent subset of $V(R)^c$, i.e.
-$\rk (B) = |P|$.
-Since $V(R)^c$ is a flat, adding any element of $V(R)$ to $B$ increases the rank of the set.
-
-Therefore, any basis of $W$ can be written as $B \sqcup U$ for some $B$ and $U$ of the form indicated described above. We may apply the same arguments to $W'$.
-
-However, since $F(P)$ is common to both $W$ and $W'$, and $V(R) = V(R')$, any basis of $W'$ can also be written $B \cup U$. Thus both matroids have the same bases sets, proving that they are the same.
-
-For the converse, assume that the matroids associated to $W$ and $W'$ are the same: $M(W) = M(W')= M$.
-Let $\mathcal{R} = \{(P_i, V(P_i)\}_{i=1}^m$ and $\mathcal{R}' = \{(P'_i, V(P'_i)\}_{i=1}^l$ be the sets of maximal exact subdiagrams of $W$ and $W'$.
-Recall that these sets $\{P_i\}$ and $\{P_i'\}$ partition the propagator sets $\cP$ and $\cP'$ of $W$ and $W'$ respectivley.
-Let $\mathcal{F}$ and $\mathcal{F}'$ the respective complementary vertices: \bas \mathcal{F} = \{F_i = V(P_i)^c | (P_i, V(P_i)) \in \mathcal{R}\} \quad  \mathcal{F}' = \{F_i' = V(P'_i)^c | (P'_i, V(P'_i)) \in \mathcal{R}\} \;.\eas By Theorem \ref{maxexactcomplementrank}, every $F_i$ and $F_i'$ is a cyclic flat in $M$.
-They are also propagator flats in $W$ and $W'$ of rank equal to the number of propagators defining it.
-We claim that $\mathcal{F} = \mathcal{F'}$.
-
-If not, there would be a cyclic flat $F_j$ of $M$ in one set but not the other.
-Without loss of generality, write $F_j \in \mathcal{F} \setminus \mathcal{F}'$.
-We may write $F_j = V(P_j)^c$, with $(P_j, V(P_j))$ a maximal exact subdiagram in $W$.
-By Lemma \ref{lem facts about WLD matroids} (5), we may write $F_j= F(Q)$ as a propagator flat.
-Therefore, Lemma \ref{maxexactcomplementrank}, $\rk(F_j) = |Q|$.
-By Lemma \ref{contractsubdiaglem}, $M/F(Q) = F/F_j = M(Q^c, V(Q^c))$, which is uniform, by construction of $F_j$.
-Theorem \ref{exactuniformthm} $(Q^c, V(Q^c))$ is exact.
-Since this exact subdiagram is not in $\mathcal{R}'$ by construction of $F_j$, it is not a maximal exact subdiagram of $W'$.
-That is, there is a maximal exact subdiagram containing it: $(Q^c, V(Q^c)) \subsetneq (P_j', V(P_j'))$.
-Thus there is a $F_j' \in \mathcal{R}'$ such that $F_j' \subsetneq F_j$.
-We show that $F_j$ is not a cyclic flat.
-
-Suppose the exact diagram  $(P_j', V(P_j'))$ has $m$ more propagators than $(Q^c, V(Q^c))$: $|P_j' \setminus Q^c| = m$.
-Since $(P_j', V(P_j'))$ defines a uniform matroid, any subset of vertices numbering fewer than the number of propagators in $P_j'$ forms an independent flat of $M(P_j', V(P_j'))$, and thus an independent set of $M$.
-\sanote{is it worth citing a result that says for $W \subset W'$, if $V$ independent in $M(W)$ then also independent in $M(W')$?} Next, compare the number of vertices in $F_j'$ and $F_j$ to see that $F_j'$ has $m$ more vertices than $F_j$:  \bas |F_j| = n -|Q^c| -3  \textrm{ while } |F_j'| = n -|P_j'| -3 = n -|Q^c| -m -3\;.\eas So $|F_j \setminus F_j' | = m$ and $F_j \setminus F_j' = V(P_j')\setminus V(Q^c)$.
-Thus $F_j \setminus F_j'$ is an independent set in $M$.
-Therefore $F_j$ is the union of a cyclic flat, $F_j'$, and an independent set, $F_j \setminus F_j'$.
-Therefore, $F_j$ is not a cyclic flat.
-Therefore, $F_j \not \in \mathcal{F} \setminus \mathcal{F}'$.
-Therefore, $\mathcal{F} = \mathcal{F}'$, as claimed.
-
-Since $\mathcal{F} = \mathcal{F'}$, the maximally exact subdiagrams of $W$ and $W'$, are supported on the same vertex sets.
-All propagators of $W$ and $W'$ are accounted for in these sets.
-There there exists a transitive chain of equivalent diagrams that put $W$ and $W'$ in the same equivalence class.
-\end{proof}
-
-\begin{proof}[Proposed alternative proof] \sanote{Looks good to me}
-One direction has been proved in \cite[Theorem 1.18]{wilsonloop}, but we give a different proof here to be consistent with the method of this paper.
+\begin{proof}One direction has been proved in \cite[Theorem 1.18]{wilsonloop}, but we give a different proof here to be consistent with the method of this paper.
 
@@
 
-Now consider the propagator flat $F(P)$, which is a cyclic flat of rank $|P|$ in both $M(W)$ and $M(W')$ by Lemma \ref{maxexactcomplementrank}.
+Now consider the propagator flat $F(P)$, whichf is a cyclic flat of rank $|P|$ in both $M(W)$ and $M(W')$ by Lemma \ref{maxexactcomplementrank}.
 Let $B \subseteq F(P)$ be an independent set of rank $|P|$.
@@
 (Note that $D$ may have many non-triangle faces and so $V_{>3}(D)$ will be the union of the vertices of each non-triangle face.) We also write $[x_i,x_j]$ for the set of vertices from $x_i$ to $x_j$ including the endpoints, and $(x_i,x_j)$ for the same set but excluding the endpoints.
-\sanote{make a dfn?}
 
@@
 
-\note{I wonder if either of you see a shorter or more conceptual way to prove this.}
-
 \begin{proof}
@@
 
-As observed in the proof of Proposition~\ref{prop easy way}, \st{the support of any non-zero vector parallel to an edge is on the indices corresponding to the four vertices bounding the quadrilateral of the dissection associated with the edge.}{\color{violet}any non-zero vector in $\R^n$ paralell to an edge of $A_n$ has non-zero entries only in the coordinates corresponding to the four vertices bounding the quadrilateral of the dissection associated with the edge.}  Thus if $V_{>3}(\tau(W)) \neq V_{>3}(\tau(X))$ \hlfix{(notation as defined before Lemma {\ref{lem good quads}})}{refer to dfn?} then the span of the vectors parallel to their edges has different support and so they cannot be parallel.
+As observed in the proof of Proposition~\ref{prop easy way}, any non-zero vector in $\R^n$ parallel to an edge of $A_n$ has non-zero entries only in the coordinates corresponding to the four vertices bounding the quadrilateral of the dissection associated with the edge.
+Thus if $V_{>3}(\tau(W)) \neq V_{>3}(\tau(X))$ (notation as defined before Lemma \ref{lem good quads}) then the span of the vectors parallel to their edges has different support and so they cannot be parallel.
 So we can assume that $V_{>3}(\tau(W)) = V_{>3}(\tau(X))$.
@@
   The number of inequivalent weakly admissible Wilson loop diagrams on $n$ is the number of non-parallel faces in the associahedron $A_n$.
-\end{thm} \sanote{this is the main result of the section}
-
-\note{Do we want a conclusion section?}
-
+\end{thm} 
 \bibliographystyle{abbrv}

### 2019-07-04 GNproof.tex
attempt to write the GN proof

--- 2019-06-28 GWLDCII.tex
@@
 \begin{document}
-\maketitle
 
-\section{Introduction}
-
-This paper is the second in a two part series investigating the combinatorics and geometry underlying SYM $N=4$ theory.
-This series lays out several results about the relationship between the Wilson loop diagrams and the positroid cells that give a CW complex structure to the positive Grassmanian.
-This paper is concerned with identifying which positroid cells correspond to which Wilson loop diagrams, and how this translates to a geometric tiling of a subspace of the positive Grassmannians.
-
-% Wilson loop diagrams associate a volume form to a positroid cell.
-
-% In this paper, we give an algorithm to identify which cell corresponds to which diagram, via Grassmann Necklaces.
-Using the Le diagram representation of positroid cells, we prove results about the dimensions of these cells.
-Finally, we state some results about the structures of the volume forms defined on these positroid cells by the Wilson loop diagrams.
-
-In contrast, the first paper in this series focuses on combinatorial and matroidal properties of the Wilson loop diagrams.
-The main focus of that paper was to enumerate the positroid cells that could be associated to Wilson loop diagrams with a fixed number of vertices and propagators, as well as counting the number of Wilson loop diagrams in the pre-image of any positroid cell under this association.
-
-In recent years, there has been significant interest in understanding the geometry and combinatorics underlying the field theory SYM $N=4$ \cite{wilsonloop, Arkani-Hamed:2013jha, Amplituhedronsquared, galashinlam, AmplituhedronDecomposition}.
-This started with the observation that BCFW diagrams, which represent the on shell interactions of this theory, correspond to plabic graphs \cite{GrassmannAmplitudebook}.
-Plabic graphs were introduced by Postnikov in \cite{Postnikov}, and provide one of the many equivalent ways to classify the positroid cells of the positive real Grassmannian $\Gr(k,n)$.
-This led to the representation of the on shell integrals associated to this theory in terms of a geometric space (the Amplituhedron) embedded in $\Gr(k,n)$ \cite{Arkani-Hamed:2013kca,Arkani-Hamed:2013jha}.
-Moreover, integrals associated to the BCFW diagrams define a volume form on the Amplituhedron, \hlfix{which is useful for ...}{we need a vague one-line description here}.
-Since then, there has been significant work to understand the volume form and its physical implications \cite{UnwindingAmplituhedron,galashinlam}.
-
-Meanwhile, a different body of work has studied SYM $N=4$ theory from the point of view of Feynman integrals in twistor space \cite{Adamo:2011pv,Adamo:2012xe,  Boels:2007qn, Bullimore:2010pj}.
-These integrals are calculated via holomorphic Wilson loops.
-As with the Amplituhedron, each Wilson loop represents the sum of a family of $N^kMHV$ Feynman diagrams, and adding up the corresponding sums of Feynman integrals associates a volume form to \hlfix{space}{I don't know if this was supposed to say ``space'' or ``this space'', and if ``this space'' I don't know which space it's referring to.} \cite{Hodges:2012ym}.
-The first author and Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that can be realized as an element of $\Gr(k,n)$ \cite{wilsonloop}, while other work has shown a connection between the space parametrized by Wilson loop diagrams and the Amplituhedron \cite{casestudy, Amplituhedronsquared}.
-
-In the above work and elsewhere, it is clear that while the space parametrized by the Wilson loop diagrams is related to the Amplituhedron, they are not the same space.
-For instance, it is conjectured that the Amplituhedron is orientable, whereas the first author and Marcott show in \cite{non-orientable} that the space parametrized by the Wilson loop diagrams can be seen as a non-orientable vector bundle over some submanifold of $\Gr(k,n)$.
-Furthermore, the cells associated to the Wilson loop diagrams are different from the cells associated to BCFW diagrams, as one sees from counting arguments in comparing the results of \cite{AmplituhedronDecomposition} and \cite{casestudy}.
-This is not too alarming, as \hlfix{one expects}{can we call this a conjecture?} the space parametrized by the Wilson loop diagrams to project down to something close to the Amplituhedron \cite{wilsonloop, Amplituhedronsquared}.
-
-This paper continues this work by identifying which positroid cells are associated to which Wilson loop diagram: specifically, we give an algorithm to read off the Grassmann necklace of the associated positroid cell from the Wilson loop diagram.
-We also show that the positroid cells associated to Wilson loop diagrams are all $3k$ dimensional; by contrast, the BCFW cells are all $4k$ dimensional \hlfix{[ref]}{someone actually proved this, right?}.
-Again, this is not too alarming, as it was shown in \cite{non-orientable} that the actual geometric space parametrized by the Wilson loop diagrams is a non-orientable $k$-dimensional bundle over this $3k$ dimensional manifold in $\Gr(k,n)$.
-
-As noted above, the sum of the Feynman integrals associated to Wilson loop diagrams gives the volume of \hlfix{the space}{help?}; if this volume is to be finite, then any singularities appearing in individual integrals must cancel out in the overall sum.
-This has been verified explicitly in a few cases \cite{casestudy, HeslopStewart}, but it is hard to prove in general due to the fact that the relationship between Wilson loop diagrams and $3k$ dimensional positroid cells of $\Gr(k,n)$ is neither one-to-one nor onto.
-In this paper, we give a characterization of the factors appearing in the denominator of these Feynman integrals in terms of the Grassmann necklace of the associated positroid, thus providing a much simpler and more tractable link between the singularities and the diagrams.
-
-% when computing a finite volume to a geometric object defined by the Wilson loop diagrams, one must ensure that any singularities cancel.
-This has been verified explicitly in a few cases \cite{casestudy, HeslopStewart}, but it has been hard to prove in general due to the fact that the relationship between Wilson loop diagrams and $3k$ dimensional positroid cells of $\Gr(k,n)$ is neither one-to-one nor onto.
-In this paper, we give a characterisation of the denominator of the Feynman integral defined by a Wilson loop diagram in terms of the algorithm that associated the same diagram to a Grassman Necklace.
-
-\subsection{Roadmap}
-
-In Section~\ref{section general background}, we summarize the required background for Wilson loop diagrams (subsection~\ref{section WLD background}), the theory of positroids in $\Gr(k,n)$ and their characterization in terms of Grassmann necklaces and Le diagrams (subsection~\ref{sec:positroid background}), and the link between Wilson loop diagrams and positroids (subsection~\ref{sec:WLD as positroids}).
-
-In Section~\ref{sec GN algorithm} we state an algorithm for constructing the Grassmann necklace of the positroid associated to a Wilson loop diagram (Algorithm~\ref{alg:put GN on WLD}) and prove its correctness (Theorem~\ref{res:alg gives GN}).
-While it was already possible to construct the Grassmann necklace of a Wilson loop diagram via existing bijections between some of the various combinatorial objects that index the positroid cells, this process was convoluted and involved multiple steps; our algorithm allows us to track directly how each propagator in the Wilson loop diagram contributes to each term in the Grassmann necklace.
-Many of the technical lemmas required to prove Theorem~\ref{res:alg gives GN} continue to be important in subsequent sections: in particular we have Lemma~\ref{lem sian}, which identifies certain configurations of propagators which must appear in any admissible Wilson loop diagram, and Lemma~\ref{vertex cyclic int lem}, which shows that the pattern of values that a propagator contributes to each term of the Grassmann necklace is both simple and predictable.
-
-In Section~\ref{sec dim} we examine the dimension of positroids associated to Wilson loop diagrams, and show that the dimension is always equal to three times the number of propagators in the diagram (Theorem~\ref{thm dim}).
-While this has been proved by Marcott in \hlfix{[ref]}{Did this get published yet?} using geometric methods, our proof is constructive and explicitly relates the position of the plusses in the Le diagram to the propagators in the Wilson loop diagram.
-
-Finally in Section~\ref{sec poles} we characterize the denominator of the integral of a Wilson loop diagram in terms of how propagators contribute to the Grassmann necklace.
-This characterization is given explicitly by Algorithm~\ref{alg WLD to denom via GN} and Theorem~\ref{thm denom}.
-
-\section{Background}\label{section general background}
-
-\subsection{Wilson Loop diagrams}\label{section WLD background}
-
-\begin{dfn}\label{WLdfn}
-A {\bf Wilson loop diagram} $W = (\cP,V)$ consists of a cyclically ordered set $V$ with one distinguished element (this plays the role of the ``first'' element when we need a compatible linear ordering on $V$), and a set $\cP \subseteq V \times V$.
-The elements of $V$ are the {\bf vertices} of $W$, and elements of $\cP$ are the {\bf propagators} of $W$.
-\end{dfn}
-
-A Wilson loop diagram is depicted as a circle, with the vertices $V$ arranged along the edge of the circle and listed counterclockwise in their cyclic order.
-The arc between two consecutive vertices is referred to as an {\bf edge} of the diagram, and the $i$th edge of $W$ is the edge from vertex $i$ to its successor.
-Each propagator $(i,j) \in \cP$ is denoted by a wavy line inside the circle joining edge $i$ and edge $j$.
-
-\begin{figure}[h]
-\[W\ =\ \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
-	\begin{scope}
-	\drawWLD{8}{1.5}
-	\drawnumbers
-	\drawprop{1}{0}{4}{0}
-	\drawprop{2}{0}{4}{-1}
-    \drawprop{5}{0}{8}{0}
-    \drawprop{5}{1}{7}{0}
-		\end{scope}
-	\end{tikzpicture}\]
-
-\caption{The Wilson loop diagram $W = \big(\{(1,4), (2,4), (5,7), (5,8)\},[8]\big)$ which has four propagators and eight vertices.}
-\label{fig:ex of WLD}
-\end{figure}
-
-Let $[n]$ denote the set of integers $\{1,\dots,n\}$ with the obvious cyclic and linear orders.
-Our primary focus is Wilson loop diagrams with $V = [n]$, so in order to simplify the exposition we will often use $i+1$ as shorthand for ``the successor of vertex $i$''.
-
-Generally speaking the propagators in a Wilson loop diagram are undirected, so $(i,j)$ and $(j,i)$ represent the same propagator.
-If we need to impose a direction on a propagator $p = (i,j)$, for example in order to consider the region ``inside'' or ``outside'' of $p$, we write $(p,<_i)$ to indicate that $p$ is directed from edge $i$ to edge $j$, and $(p,<_j)$ for the opposite direction.
-
-We also impose the convention that all vertices should always be interpreted in terms of the cyclic order on $V$; for example, if $V = [n]$ then $(n,n+3)$ means the propagator connecting edges $3$ and $n$.
-This viewpoint is beneficial for us since many of our proofs rely on restricting our attention to a region of the diagram bounded by a given propagator, or to short propagators such as $(i,i+2)$, and these behave the same regardless of whether we cross the ``first'' vertex or not; however, we emphasize that this is different to the standard convention in the physics literature, where propagators are written $(i,j)$ with $1 \leq i<j \leq n$.
-
-\begin{dfn} \label{VPropdfn}
-Let $W = (\cP, V)$ be a Wilson loop diagram.
-\begin{enumerate}
-\item For $p = (i,j) \in \cP$, let $V(p) = \{i, i+1, j, j+1\}$ denote the set of {\bf vertices supporting $p$}. For a set of propagators $P \subseteq \cP$, define 
-\[V(P) = \bigcup_{p \in P} V(p)\]
-to be the vertex support of $P$.
-\item For $U \subseteq V$, the set of {\bf propagators supported on $U$} is denoted by
-\[\Prop(U) = \{ p \in \cP\ |\ V(p) \cap U \neq \emptyset \}.\]
-Note that a propagator in $\Prop(U)$ does not need to have its entire support contained in $U$. 
-\item Vertices of $W$ that do not support any propagators are called {\bf non-supporting}. The set of all non-supporting vertices in $W$ is denoted $F(\emptyset)$. 
-\end{enumerate}
-\end{dfn}
-
-In particular, we will see in later sections that all four vertices in the support of a propagator are important in understanding the contribution of that propagator to the overall diagram.
-This motivates the following definition of a subdiagram, which can consist of any subset $Q$ of the propagators and any subset $U$ of the vertices of $W$ {\em as long as we retain all vertices in the support of $Q$}.
-
-\begin{dfn} \label{subdiagramdfn}
-Let $W = (\cP, V)$ be a Wilson loop diagram. Then $W' = (Q,U)$ is a {\bf subdiagram} of $W$ if $Q \subseteq \cP$ and $V(Q) \subseteq U \subseteq V$.
-\end{dfn}
-
-With these definitions in hand, we can impose some conditions on the density and behavior of the propagators of Wilson loop diagrams.
-
-\begin{dfn}\label{admisdfn}
-A Wilson loop diagram $W = (\cP, V)$ is called {\bf admissible} if:
-\begin{enumerate}
-\item $|V| \geq |\cP| + 4$.
-\item There does not exist a non-empty set of propagators $Q \subseteq \cP$ such that $|V(Q)| < |Q| + 3$.
-\item There does not exist a pair of propagators $\{(i,j),(k,l)\} \subseteq \cP$ such that $i < k < j < l$.
-\end{enumerate}
- \end{dfn}
-
-The first condition bounds the total number of propagators in the diagram, while the second limits how densely propagators can be fitted into any part of the diagram; in particular, it prohibits propagators that connect two adjacent edges and parallel propagators that start and end on the same pair of edges.
-The third condition simply requires that propagators are non-crossing.
-
-These conditions are imposed by the physical interpretation of Wilson loop diagrams (see for example \cite{Adamo:2011pv,Adamo:2012xe,wilsonloop,LipsteinMason}).
-We therefore restrict our attention in this paper to admissible Wilson loop diagrams and their subdiagrams only.
-
-Note that a subdiagram $(Q,U)$ of an admissible Wilson loop diagram need not be admissible itself: it inherits conditions 2 and 3 automatically, but we could have $|U| = |Q| + 3$.
-If a Wilson loop diagrams satisfies conditions 2 and 3 of Definition~\ref{admisdfn}, we call it {\bf weakly admissible}.
-
-These diagrams correspond to (tree level) amplitudes of SYM $N=4$ theory in twistor space.
-As such, it associates a real value to $n$ particles, one for each vertex.
-Each particle is represented as a section of a $|\cP|$-vector bundle over twistor space, projected onto a real subspace in a process called bosonization \cite{Arkani-Hamed:2013jha}.
-In other words, each Wilson loop diagram defines a functional on external particles.
-This is represented as an integral $I(W)$, which is the equivalent of a Feynman integral in this setting.
-
-A $|\cP| \times n$ matrix $C(W)$ represents the (tree level) particle interactions.
-Each row of $C(W)$ corresponds to an internal propagator, each column to an external particle.
-$C(W)$ is defined as follows:
-
-\begin{equation} C(W)_{p,q} = \begin{cases} c_{p,q} & \textrm{ if } q \in V(p) \\
-0  & \textrm{ if } q \not \in V(p)  \end{cases}
-\;. \label{C(W) dfn}\end{equation} \todo{$c_{p,q}$ or $x_{p,q}$? Should be consistent}
-
-The entries $c_{p,q}$ are non-zero real variables.
-Thus the zero entries in row $p$ correspond to the external particles that the propagator $p$ does not interact with.
-See \ref{integraldetails} for an example of a diagram $W$ and its associated matrix.
-
-The matrix $C(W)$ can be interpreted as a parametrization of the positroid cell in the positive Grassmannian $\Gr(n, |\cP|)$ associated to the $W$, which we denote by $\Sigma(W)$ \cite{wilsonloop}.
-Most of the work in this paper, and in \cite{generalcombinatoricsI} focuses on characterizing the positroid cell assoicated to eash Wilson loop diagram $W$.
-
-Note that since there is no ordering on the propagators of $W$, $C(W)$ is only defined up to rearrangement of the rows.
-This will not matter here, as it does not affect the parametrization of $\Sigma(W)$.
-
-One may also interpret the functional $I(W)$ as associating a volume to each cell $\Sigma(W)$ \cite{wilsonloop, Amplituhedronsquared, HeslopStewart}.
-The volume form is written in terms of the elements of $C(W)$ as  \[ \Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V_{p_r}} \textrm{d}c_{p_r}}{R(W)} \;.
-\]
-The interested reader is referred to \cite{Adamo:2012xe,HeslopStewart,LipsteinMason} for more information about the volume form.
-
-For a fixed number of propagators and particles, the tree level amplitude of the Wilson loop diagrams is computed as the sum of the $I(W)$ for all $W$ of the correct size.
-By \cite{Adamo:2011pv,Adamo:2012xe,Arkani-Hamed:2013jha} this sum is finite for all sets of external particles, i.e.
-we have \bas \mathcal{A}_{k, n}^{tree} = \sum_{(\cP, [n]), |\cP| = k} I(W) <\infty.
-\eas
-
-In particular, this implies that any singularities in the integrals $I(W)$ must cancel out in the sum.
-In particular, they must cancel on the boundaries of the positroid cells $\Sigma(W)$, analogous to the analysis in \cite{Arkani-Hamed:2013jha}.
-This has been checked for particular classes of examples (e.g.
-\cite{casestudy, Amplituhedronsquared, HeslopStewart}) but has not been proven in general.
-
-With this motivation in mind, in this paper we study the denominator $R(W)$ of the volume form $\Omega(W)$, which we define next.
-
-\begin{dfn}\label{def R(W)}
-Let $W = (\cP,V)$ be an admissible Wilson loop diagram, and fix an edge $e$.
-Let $\{p_1 \ldots p_r\}$ be the propagators with one end lying on edge $e$, ordered so that $p_1$ is closest to the vertex $e$, $p_r$ closest to $e+1$, and $p_i$ is closer to $e$ than $p_{i+1}$ is.
-Define
-\[ R_e =  c_{p_1,e+1} \prod_{j= 1}^{r-1} \left((c_{p_j,e} c_{p_{j+1},e+1} - c_{p_{j+1},e} c_{p_{j},e+1} ) \right) c_{p_r,e}\;\]
-to be the component of $R(W)$ associated to edge $e$.
-Note that if $r = 1$ (i.e.
-there is exactly one propagator lying on edge $e$) then this expression simplifies to $R_e = c_{p,e} c_{p,e+1}$.
-If $r=0$, set $R_e = 1$.
-The denominator $R(W)$ is defined to be the product of all of the $R_e$, i.e.
-\[R(W) = \prod_{e \in V} R_e.\]
-\end{dfn}
-
-In Section \ref{sec poles}, we show that the denominator $R(W)$ is determined by the positroid cell $\Sigma(W)$ and the structure of $W$, as encapsulated by $C(W)$.
-In fact, it can be read directly off of $C(W)$, in terms of characterization of $\Sigma(W)$ called the Grassmann necklace (see Definition~\ref{def:grassmann necklace}).
-We also give an algorithm to read $R(W)$ directly from the Wilson loop diagram, paving the way for a general study of these poles in future.
-
-We end this section with an example of computing $C(W)$ and $R(W)$ for a particular Wilson loop diagram $W$.
-
-\begin{eg} \label{integraldetails}
-Consider the admissible Wilson loop diagram 
-\[W = \big(\{(1,4), (2,4), (5,7), (5,8)\},[8]\big),\]
-from Figure~\ref{fig:ex of WLD}. Ordering the propagators as listed above, we obtain the associated matrix
-\[ C(W) = \left(
-\begin{array}{cccccccc}
-c_{1,1} & c_{1,2} & 0 & c_{1,4} & c_{1,5} & 0 & 0 & 0 \\
-0 & c_{2,2} & c_{2,3} & c_{2,4} & c_{2,5} & 0 & 0 & 0 \\
-0 & 0 & 0 & 0 & c_{3,5} & c_{3,6} & c_{3,7} & c_{3,8} \\
-c_{4,1} & 0 & 0 & 0 & c_{4,5} & c_{4,6} & 0 & c_{4,8}  \\
-\end{array}
-\right) \;.\]
-
-To calculate $R(W)$, write \bmls R_1 = c_{1,1} c_{1, 2}\quad R_2 = c_{2,2} c_{2,3} \quad R_4 = c_{2,5} (c_{2,4}c_{1,5} - c_{2,5}c_{1,4})c_{1,4} \\ R_5 = c_{4,6} (c_{4,6}c_{3,5} - c_{3,6}c_{4,5})c_{3,5} \quad R_7 = c_{3,7} c_{3,8} \quad R_8 = c_{4,8} c_{4,1} \;.\emls All other $R_e$ are $1$.
-Finally, the integrand associated to this Wilson loop diagram is \bas \Omega(W) = \frac{\textrm{d}c_{1,1}\textrm{d}c_{1,1}\textrm{d}c_{1,1}\textrm{d}c_{1,2}\textrm{d}c_{1,4}\textrm{d}c_{1,5}\textrm{d}c_{2,1}\textrm{d}c_{2,3}\textrm{d}c_{2,4}\textrm{d}c_{2,5}\textrm{d}c_{3,5}\textrm{d}c_{3,6}\textrm{d}c_{3,7}\textrm{d}c_{3,7}\textrm{d}c_{4,5}\textrm{d}c_{4,6}\textrm{d}c_{4,8}\textrm{d}c_{4,1}}{c_{1,1} c_{1, 2}c_{2,2} c_{2,3}c_{2,5} (c_{2,4}c_{1,5} - c_{2,5}c_{1,4})c_{1,4}c_{4,6} (c_{4,6}c_{3,5} - c_{3,6}c_{4,5})c_{3,5}c_{3,7} c_{3,8}c_{4,8} c_{4,1}} \;.
-\eas
-\note{Is the numerator just supposed to be the product of $dc_{pq}$ for each $c_{pq}$ in the matrix? Also I think $c_{46}c_{35} - c_{36}c_{45}$ in the denominator is the wrong way around?}
-\end{eg}
-
-\subsection{Positroids, Grassmann necklaces, and Le diagrams}\label{sec:positroid background}
-
-We summarize here only the subset of positroid theory that we require in this paper; the interested reader is referred to \cite{Postnikov} for more details.
-
-Let $\binom{[n]}{k}$ denote the set of all $k$-subsets of $[n]$.
-
-For our purposes, a {\bf positroid} is a matroid $M$ (with ground set $[n]$ and bases $\cB \subseteq \binom{[n]}{k}$) which can be represented by an element of the positive Grassmannian $\Gr(k,n)$.
-In other words, there exists a full-rank $k\times n$ real matrix whose $k\times k$ minors are all nonnegative and such that the minor $[[k]|J]$ is positive if and only if $J \in \cB$.
-
-Postnikov shows in \cite{Postnikov} that the positroids of $\Gr(k,n)$ are indexed by many different collections of objects, each with their own advantages and disadvantages.
-The two most suited to our purposes are Grassmann necklaces and Le diagrams, which we introduce below.
-In order to do so, we first need some preliminary definitions.
-
-For each $j \in [n]$, we can define a total order $<_j$ on the interval $[n]$ by
-\[ j <_j j+1 <_j \dots <_j n <_j 1 \dots <_j j-1\;.\]
-This in turn induces a total order on $\binom{[n]}{k}$, namely the lexicographic order with respect to $<_j$.
-It also induces a separate partial order $\gale{j}$ on $\binom{[n]}{k}$ (the {\bf Gale order} \cite{Gale}), which is defined as follows: for
-\[A = \{a_1 <_j a_2 <_j \dots <_j a_k\} \text{ and } B = \{b_1 <_j b_2 <_j \dots <_j b_k\} \in \binom{[n]}{k},\] we define
-\[A \gale{j} B \text{ if and only if } a_r \leq_j b_r \text{ for all }1 \leq r \leq k.\]
-For example, in $\binom{[6]}{3}$ we have $\{2,5,6\}\gale{2} \{2,6,1\}$ but $\{2,5,6\}\not\gale{2}\{3,4,6\}$.
-
-\begin{dfn}\label{def:grassmann necklace}
-A {\bf Grassmann necklace} of type $(k,n)$ is a sequence $(I_1, \dots, I_n)$ of $n$ sets $I_i \in \binom{[n]}{k}$ such that for each $i \in [n]$:
-\begin{itemize}
-\item if $i \in I_i$, then $I_{i+1} = \big(I_i \backslash \{i\}\big) \cup \{j\}$ for some $j \in[n]$.
-\item if $i \not\in I_i$, then $I_{i+1} = I_i$.
-\end{itemize}
-By convention, we set $I_{n+1} = I_1$.
-\end{dfn}
-
-By \cite[Theorem 17.1]{Postnikov}, the Grassmann necklaces of type $(k,n)$ are in 1-1 correspondence with the positroid cells in $\Gr(k,n)$.
-Each term $I_i$ is simply the minimal (with respect to the $<_i$-lex order) basis of the positroid.
-A characterization of all bases of the positroid in terms of the Grassmann necklace and the Gale order was given by Oh in \cite[Theorem 8]{Oh}: if $(I_1, \dots, I_n)$ is the Grassmann necklace associated to a positroid $M = ([n],\cB)$, then the bases of $M$ are exactly
-\ba \cB = \left\{J \in \binom{[n]}{k}\ |\ I_i \gale{i} J \ \forall i \in [n]\right\}. \label{basesofmatroids}\ea
-Thus the Grassmann necklace is well suited to testing whether a given $k$-set is a basis for $M$, and for generating a list of all bases of $M$.
-
-\begin{dfn}\label{def:le diagram}
-A {\bf Le diagram} is a Young diagram in which every square contains either a $+$ or a $0$, subject to the rule that if a square contains a $0$ then either all squares to its left (in the same row) must also contain a $0$, or all squares above it (in the same column) mustbasesofmatroids\ also contain a $0$, or both.
-\end{dfn}
-
-By \cite[Theorem 6.5]{Postnikov}, the set of all Le diagrams that fit within a $k\times(n-k)$ rectangle is in 1-1 correspondence with the positroid cells of $\Gr(k,n)$.
-Le diagrams are particularly useful for comparing dimensions of positroids, since the dimension of a positroid is equal to the number of $+$ squares in its Le diagram \cite[Theorem 6.5]{Postnikov}.
-
-The rows and columns of a Le diagram are labelled as follows: given a Le diagram fitting inside a $k\times (n-k)$ box, arrange the numbers $1,2, \dots, n$ along its southeast border, starting from the top-right corner.
-See Figure \ref{fig:row column numbering} for examples.
-
-\begin{figure}[h!]
-\[\begin{tikzpicture}[baseline=(current bounding box.east),scale=0.75]
-\draw (1,0) grid (2,3);
-\draw (2,1) grid (4,3);
-\draw (4,2) grid (5,3);
-\draw[dotted] (2,0) -- (5,0) -- (5,2);
-
-\node at (5.15,2.5) {\footnotesize$1$};
-\node at (4.5,1.85) {\footnotesize$2$};
-\node at (4.15,1.5) {\footnotesize$3$};
-\node at (3.5,0.85) {\footnotesize$4$};
-\node at (2.5,0.85) {\footnotesize$5$};
-\node at (2.15,0.5) {\footnotesize$6$};
-\node at (1.5,-0.15) {\footnotesize$7$};
-%\node at (0.5,-0.15) {\footnotesize$8$};
-\end{tikzpicture}
-\qquad \qquad
-\begin{tikzpicture}[baseline=(current bounding box.east),scale=0.75]
-\draw (1,0) grid (2,3);
-\draw (2,1) grid (4,3);
-\draw (4,2) grid (5,3);
-\draw[dotted] (2,0) -- (6,0) -- (6,3) -- (5,3);
-
-\node at (5.5,2.85) {\footnotesize$1$};
-\node at (5.15,2.5) {\footnotesize$2$};
-\node at (4.5,1.85) {\footnotesize$3$};
-\node at (4.15,1.5) {\footnotesize$4$};
-\node at (3.5,0.85) {\footnotesize$5$};
-\node at (2.5,0.85) {\footnotesize$6$};
-\node at (2.15,0.5) {\footnotesize$7$};
-\node at (1.5,-0.15) {\footnotesize$8$};
-%\node at (0.5,-0.15) {\footnotesize$9$};
-\end{tikzpicture}
-\]
-\caption{Row and column numbering for a Young diagram with $k = 3$, $n = 7$ (left) and $k = 3$, $n = 8$ (right).
-The top left box has coordinates $(1,7)$ in the left diagram, and $(2,8)$ in the right diagram.}
-\label{fig:row column numbering}
-\end{figure}
-
-Specifying a $k$-subset $J \subseteq [n]$ therefore uniquely determines the shape of the Le diagram, by taking the elements of $J$ to be the row indices of the diagram.
-
-An algorithm for constructing the Le diagram associated to a Grassmann necklace was given by Agarwala and Fryer in \cite{reversingOh}.
-Since we will make use of this algorithm in Section~\ref{sec dim} below, we summarize the process here.
-\begin{algorithm}\label{alg:GN to Le} \ \cite[Algorithm 2]{reversingOh}
-Let $(I_1,\dots,I_n)$ be a Grassmann necklace of type $(k,n)$. Within a $k \times(n-k)$ square, draw the Young diagram whose rows are labelled by $I_1$ (as per the convention above).
-
-For each $i$, $2 \leq i \leq n$:
-\begin{itemize}
-\item Write \[I_1 \setminus I_i = \{a_1 > a_2 > \dots > a_r\}, \quad I_i \setminus I_1 = \{b_1 < b_2 < \dots < b_r\},\]
-where the inequalities denote the $<_1$ order (subscripts suppressed for clarity).
-\item For $1 \leq j \leq r$ , place a $+$ in square $(a_j,b_j)$ of the diagram. (We will sometimes refer to this $+$ as being {\em in the $a_j \rightarrow b_j$ position}.)
-\end{itemize}
-After performing the above for $2 \leq i \leq n$, place a $0$ in any remaining unfilled boxes.
-\end{algorithm}
-
-An algorithm for constructing the Grassmann necklace of a Le diagram also exists; this was given by Oh in \cite{Oh}.
-A method for using the Le diagram to test whether a given $k$-subset is a basis for the corresponding positroid or not was given by Casteels in \cite{CasteelsPaths}.
-
-\subsection{Wilson loop diagrams as positroids}\label{sec:WLD as positroids}
-
-Let $W = (\cP,[n])$ be an admissible Wilson loop diagram with $k$ propagators, and $C(W)$ the associated matrix defined in \eqref{C(W) dfn}.
-Let $M(W)$ be the matroid realized by $C(W)$, i.e.
-the matroid with ground set $[n]$ whose independent sets are exactly the sets $V \subseteq [n]$ such that the columns of $C(W)$ indexed by $V$ are linearly independent.
-
-In \cite{wilsonloop}, Agarwala and Amat show that $M(W)$ is also characterized by the Wilson loop diagram itself:
-
-\begin{thm} \label{thm WLD defines matroid} \cite[Theorem 3.6]{wilsonloop} The independent sets of the matroid $M(W)$ associated to an admissible Wilson loop diagram $W = (\cP,[n])$ and realized by $C(W)$ are exactly those subsets $V \subseteq [n]$ such that $\nexists U\subseteq V$ satisfying $|\Prop(U)| < |U|$.
-\end{thm}
-In other words, the independent sets of $M(W)$ correspond to sets of vertices in $W$ in which no subset supports fewer propagators than the vertices it contains.
-
-One useful corollary of this, which we will want to keep in mind later, is the following.
-\begin{cor}\label{lem basis as perm}
-Let $W = (\cP,[n])$ be an admissible Wilson loop diagram and let $M(W)$ be its associated matroid.
-A subset $J \subseteq [n]$ is an independent set of $M(W)$ if and only if there exists an injective set map $f : J \rightarrow \cP$ with the property that for each $j\in J$ we have $j \in V(f(j))$.
-\end{cor}
-
-\begin{proof}
-  This follows as a corollary of the previous theorem by induction in one direction and the pigeonhole principle in the other direction.
-
-Forgetting about the matroid and simply thinking about the condition of linear independence in the matrix $C(W)$, the corollary can also be proved directly by linear algebra and the definition of $C(W)$ as follows: because the nonzero entries of $C(W)$ are independent indeterminants, $J$ is an independent set is if and only if there is some choice of $|J|$ nonzero entries of $C(W)$ one in each row associated to an element of $J$ and each in different columns.
-Each entry in $C(W)$ identifies a propagator by the row of the entry and a vertex by the column of the entry.
-The entry is nonzero if and only if the propagator is supported on that vertex.
-Consequently, a choice of $|J|$ nonzero entries of $C(W)$ one in each row associated to an element of $J$ and each in different columns is equivalent to an assignment of the propagators of $J$ to supporting vertices so that no two are assigned to the same vertex.
-Such an assignment of the propagators of $J$ to supporting vertices is exactly a map $f$ as described in the statment, hence proving the result.
-\end{proof}
-
-In particular, this corollary says that a subset $J$ of $[n]$ is a basis of $M(W)$ if and only if there is a set bijection between $J$ and $\cP$ with the property that for each $j\in J$ the propagator associated to $j$ under the bijection is supported on vertex $j$.
-
-By relating the behavior of the propagators in $W$ to the matroidal properties of $M(W)$, Agarwala and Amat also showed that $M(W)$ is in fact a positroid whenever $W$ is admissible \cite[Corollary 3.39]{wilsonloop}.
-
-However, in order to identify the positroid associated to a given Wilson loop diagram $W$ we first have to construct $C(W)$, then make a list of all its non-zero $k\times k$ minors and extract the Le diagram or Grassmann necklace via the methods described in Section~\ref{sec:positroid background}.
-Alternatively, one could obtain the decorated permutation of the positroid from $C(W)$ as in \hlfix{[ref]}{Sian needs to go find this reference} and then convert it into a Grassmann necklace as described in \cite[Section 16]{Postnikov}.
-
-In \cite{casestudy}, Agarwala and Fryer apply this process in the smallest non-trivial case: admissible Wilson loop diagrams with two propagators on six vertices.
-Even in this simple case, we see that the mapping from admissible WLD to positroid cells is neither one-to-one nor onto, and the process described above makes it almost impossible to track the relationship between the original Wilson loop diagram and the resulting positroid.
-
-Our first goal is therefore to find a better method of obtaining the positroid associated to a given Wilson loop diagram; this is the focus of the next section.
-
-\begin{rmk}
-While this paper primarily approaches proofs from a combinatorial point of view, readers with a background in matroid theory are encouraged to keep the matroidal viewpoint in mind throughout; we expect that the two approaches will be complementary and will build upon each other.
-See \cite{generalcombinatoricsI} for some related results concerning the positroids of Wilson loop diagrams obtained by viewing them primarily as matroids.
-\end{rmk}
-
-\section{Wilson Loop diagrams and their Grassmann necklaces}\label{sec GN algorithm}
-
-In this section we will give an algorithm (Algorithm~\ref{alg:put GN on WLD}) to go directly from a Wilson loop diagram to the Grassmann necklace of its positroid.
-This is a useful result in and of itself, as it greatly simplifies the process of identifying the positroid associated to a given WLD.
-It also allows us to examine how the positroid changes as we make minor changes to the Wilson loop diagram; indeed, the techniques we develop in this section to verify that our algorithm produces the correct Grassmann necklace will also be used repeatedly in later sections.
-
-One of the key insights is that each element of the Grassmann necklace can be viewed as a function from the propagators of the diagram to the vertices in the Grassmann necklace element.
-This is captured in Definition~\ref{def I_i as a function}, and used throughout the paper.
-
-%\note{Sian thinks that a section roadmap here would be overkill: we gave a roadmap in section 1, each subsection has its own little intro roadmap, and I've added a ref to the algorithm above so that people can skip straight to it if they want}
-
-%In Section~\ref{sec:propagator configs} we examine the structure of admissible Wilson loop diagrams and prove several technical lemmas about configurations of propagators appearing in these diagrams.
-In Section~\ref{sec:GN alg} we state the algorithm that extracts the Grassmann necklace of a given diagram (see Algorithm~\ref{alg:put GN on WLD}) and
-
-Throughout this section, $W = (\cP,[n])$ is an admissible Wilson loop diagram with $k$ propagators.
-
-\subsection{Propagator configurations in admissible Wilson loop diagrams}\label{sec:propagator configs}
-
-Before we can describe the algorithm for extracting the Grassmann necklace of $M(W)$ from the Wilson loop diagram $W$, we require some initial results about the behavior of propagators in admissible WLD.
-
-\begin{dfn}\label{props inside p}
-Let $W = (\cP, [n])$ be a weakly admissible Wilson loop diagram, with $p \in \cP$ supported on edges $i$ and $j$.
-Write $(p, <_i)$ to represent the same propagator directed from $i$ to $j$.
-Then the sets of propagators {\bf inside} and {\bf outside} of $(p,<_i)$ are defined to be
-\begin{gather*}\cP_{in}(p,<_i) = \{ (k,l) \in \cP \ |\ i \leq_i k <_i l \leq_i j \}, \\
-\cP_{out}(p,<_i) = \cP\setminus \cP_{in}(p,<_i),
-\end{gather*}
-respectively.
-\end{dfn}
-
-\begin{eg}
-Let $W$ be the Wilson loop diagram from Figure \ref{fig:ex of WLD}, reproduced here for convenience.  \[W\ =\ \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
-	\begin{scope}
-	\drawWLD{8}{1.5}
-	\drawnumbers
-	\drawlabeledprop{1}{0}{4}{0}{\footnotesize \qquad \ $p$}
-	\drawprop{2}{0}{4}{-1}
-    \drawprop{5}{0}{8}{0}
-    \drawprop{5}{1}{7}{0}
-		\end{scope}
-	\end{tikzpicture}\]
-
-Let $p$ be the propatagor $p = (1, 4)$. Then $\cP_{in}(p, <_4) = \{(1,4), (5, 8), (5, 7) \}$ and $\cP_{out}(p, <_4) = \{(2,4) \}$
-\end{eg}
-
-\begin{dfn}
-Let $p = (i,j) \in \cP$ be a propagator in $W$.  Define the {\bf length} of $p$ to be 
-\[\ell(p) \  =\ \min\big\{|[i+1,j]|,|[j+1,i]|\big\}.\]
-\end{dfn}
-In other words, $\ell(p)$ is the size of the smaller of the sets of vertices on either side of the propagator $p$.
-
-\begin{rmk}\label{rem:props of length 2 and 3} 
-  The following observations about configurations of propagators of short length in a weakly admissibly Wilson loop diagram $W$ are easily verified:
- \begin{enumerate}
-\item If $p = (i,i+3)$ is a propagator of length 3, then the middle vertex $i+2$ supports at most one propagator.
-\item If every vertex in $W$ supports at least one propagator, then $W$ admits at least one propagator of length 2.
-\end{enumerate}
-\end{rmk}
-
-The following lemma establishes certain configurations of propagators that must exist in any admissible diagram with no non-supporting vertices (i.e.
-with $F(\emptyset) = \emptyset$).
-We make use of this result in several induction proofs below.
-
-\begin{lem}\label{lem sian}
-  Let $W$ be a weakly admissible WLD with at least 5 vertices and in which each vertex supports at least one propagator.  Then at least one of the following two things occurs.
-  \begin{enumerate}
-    \item $W$ has a propagator of length $\leq 6$ with a propagator of length 2 on one side it and nothing else on that side.\label{item big and 2}
-    \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator ends between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
-  \end{enumerate}
-\end{lem}
-
-\begin{proof}
-Suppose first that $W$ has a propagator of length $3$, say $p=(i, i+3)$.
-By Remark~\ref{rem:props of length 2 and 3} and the fact that every vertex of $W$ supports at least one propagator, we have that $i+2$ supports exactly one propagator and this propagator must have length 2 by noncrossingness.
-This gives us an instance of configuration~\ref{item big and 2} from the statement.
-
-Now suppose $W$ has no propagators of length $3$.
-
-We will inductively construct a sequence of propagators $p_r$ and $q_r$, with $\ell(p_r) = 2$ for each $r$ and either:
-\begin{itemize}
-\item $p_r$ forms part of configuration \ref{item big and 2} or \ref{item pair of 2s} from the statement, at which point the induction terminates, 
-  %a configuration \eqref{eq:2 prop config} in $D$
-{\em or} 
-\item there is a propagator $q_r$ satisfying $\ell(q_r) \geq 4$, and $\{p_1, \ldots, p_r, q_1, \ldots, q_{r-1}\}$ are all on the same side of $q_r$.  
-\end{itemize}
-We can then choose the orientation of $q_r$ so that the previous $p_i$ and $q_i$ are all on the outside of $q_r$, and restrict our attention to the subdiagram $(\cP_{in}(q_r),[n])$.
-By the finiteness of $W$ this must eventually terminate in one of the desired configurations.
-%a configuration of the form \eqref{eq:2 prop config}.
-
-Start by choosing a propagator $p_1 = (j_1,j_1+2)$ of length 2 in $W$ (which exists by Remark~\ref{rem:props of length 2 and 3}).
-If it is part of one of the configurations we are looking for then we are done,
-%a configuration \eqref{eq:2 prop config} we are done,
-so suppose otherwise.
-
-From our existing assumptions, we know the following facts: $p_1$ is not in configuration \ref{item pair of 2s}, there are no propagators of length $3$, and every vertex supports at least one propagator.
-Therefore there must be a propagator of length $\geq 4$ with one end on edge $j_1$ or on edge $j_1-1$ or on edge $j_1-2$.
-Let $q_1 = (i_1, k_1)$ be this propagator, oriented such that $p_1 \in \cP_{out}(q_1,<_{i_1})$.
-This completes the base case.
-
-\bas \begin{tikzpicture}[rotate=15,baseline=(current bounding box.east)]
-	\begin{scope}
-	\drawWLD{15}{2}
-	%\drawnumbers
-	%\drawprop{1}{0}{4}{0}
-	\begin{scope}
-	\clip (0,0) circle (\radius cm);
-	\draw[propagator] (\angle*5.3:\radius*1.2cm) to [bend left=50] (\angle*7.7:\radius*1.2cm);
-	\node at (\angle*6.5:\radius*0.6cm) {\footnotesize $p_1$};
-	\end{scope}
-    \drawlabeledprop{3}{0}{10}{0}{\footnotesize \qquad $q_1$};
-    \node at (\angle*5:\radius*1.15cm) {\footnotesize $j_1$};
-     \node at (\angle*10:\radius*1.15cm) {\footnotesize $i_1$};
-     \node at (10:\radius*0.5) {\small $\cP_{in}(q_1)$};
-	\node[rotate = 45] at (\angle * 5.2:\radius) {\Large $($};
-\node[rotate = -15] at (\angle * 2.7:\radius) {\Large $)$};
-\node[rotate = 20] at (\angle* 4:\radius*1.2) {\em \scriptsize 1, 2 or 3 vertices};
-		\end{scope}
-	\end{tikzpicture}\eas
-
- %\node[rotate=-15] at (\zero + 2.7*\step:\radius) {\Large $($};
- %    \node[rotate=15] at (\zero + 6.3*\step:\radius) {\Large $)$};
-   %  \node at (\zero + 4.5*\step:\radius*0.85) {\em \scriptsize up to 4 vertices here};
-
-\sanote{played with Sian's code. May need to tweak this picture}
-Now suppose $q_{r} = (i_r, k_r)$ exists by the induction hypothesis and is oriented $(q_r, <_{i_r})$ so that the previous $p_i$ and $q_i$ are on the outside.
-For the rest of this proof, we assume this orientation and drop the $<_{i_r}$ from the notation.
-
-Let $W_r := (\cP_{in}(q_r),[n])$ be the subdiagram of $W$ consisting only of those propagators inside $q_r$ (including $q_r$ itself); in particular $W_r$ contains none of the previous $p_i$ or $q_i$.
-By the original hypotheses on $W$, every vertex in $[i_r,k_{r+1}]$ (of which there are at least 4, since $\ell(q_r) \geq 4$) must support at least one propagator.
-Therefore $W_r$ admits at least one propagator of length 2 (by Remark~\ref{rem:props of length 2 and 3}) and no propagators of length $3$ (by our assumption on $W$).
-
-Let $p_{r+1} = (j_{r+1}, j_{r+1}+2)$ be a propagator of length 2 in $W_r$; if it forms part of configuration \ref{item big and 2} or \ref{item pair of 2s}
-%the configuration \eqref{eq:2 prop config}
-then we are done, so assume otherwise.
-
-Note that we could replace $q_r$ by another propagator $q'_{r}$ in $W_r$, as long as $p_{r+1}$ and $q_r$ are on opposite sides of $q_r'$: such a new $q'_{r}$ would still satisfy all of the induction hypotheses.
-Therefore without loss of generality we may assume that $\cP_{in}(q_r)$ does not contain any propagators (other than $q_r$ itself) which satisfy the induction hypotheses, i.e.
-we assume that there are no other propagators with $p_{r+1}$ on one side and $q_r$ on the other.
-
-There are two cases to consider.
-
-The first case is that $i_r \leq j_{r+1} \leq i_r+2$ and $k_r-2 \leq j_{r+1}+2 \leq k_{r}$ (so $p_{r+1}$ has one end before $i_{r} + 3$ and the other after $k_{r} - 2$, i.e.
-both ends of $p_{r+1}$ are close to the ends of $q_r$).
-Then since $p_{r+1}$ has length 2, it must be that $(i_r+3)+1 \geq k_r-2$ and so $q_r$ has length $\leq 6$.
-By the minimality assumption on $q_r$, no propagator in $W_r$ has $q_r$ on one side and $p_{r+1}$ on the other side.
-Therefore, any propagator in $W_r$ other than $q_r$ and $p_{r+1}$ must be of the form $(i,j)$ with $i_r\leq i < j\leq i_r+2$ or $k_r-2 \leq i < j\leq k_r$.
-Both of these require that $(i,j)$ has length 2, and so we have configuration \ref{item pair of 2s} which we have already assumed does not occur.
-Consequently, $W_r$ contains only the two propagators $q_r$ and $p_{r+1}$, yielding configuration \ref{item big and 2} from the lemma statement and again contradicting our assumption.
-Therefore this first case cannot occur.
-
-The second case is that (at least) one of the following four things happen:
-\begin{itemize}
-\item $i_r+3 \leq j_{r+1}\leq k_r-3$, or
-\item $i_r+3 \leq j_{r+1}+2\leq k_r-3$, or
-\item $i_r = j_{r+1}$, or 
-\item $k_r-2 = j_{r+1}$
-\end{itemize}
-In other words, at least one end of $p_{r+1}$ is supported entirely by vertices in the interval $[i_r+3,k_r+2]$ (the first two bullet points) or both ends lie in $[i_r, i_r+3]$ (third point) or both ends lie in $[k_r-2, k_r+1]$ (fourth point).
-These situations all behave similarly, and by symmetry it suffices to only consider the second and third possibilities.
-
-Note that since $j_{r+1}+4 \leq k_r-1$ in both of these situations, the vertex $j_{r+1}+4$ is inside $q_r$ but does not support either $q_r$ or $p_{r+1}$, and must therefore support some other propagator $t$.
-Since $p_{r+1}$ is not part of configuration \ref{item pair of 2s} and $W_r$ has no propagators of length 3, it follows that $\ell(t) \geq 4$.
-If $q_r$ and $p_{r+1}$ were on different sides of $t$ then this would contradict the minimality of $q_r$.
-Therefore we can orient $t$ so that all previous $q_i$ and $p_i$ belong to $\cP_{out}(t)$, and set $q_{r+1} = t$ to continue the induction.
-
-The overall result then follows by induction.
-\end{proof}
-
-\begin{rmk}
-In the case that all vertices of an admissible WLD $W$ support at least two propagators, then Lemma~\ref{lem sian} substantially simplifies.
-By Remark~\ref{rem:props of length 2 and 3}, $W$ has no propagators of length $3$.
-Configuration \ref{item big and 2} necessarily entails vertices with support $1$ as does configuration \ref{item pair of 2s} unless $j=i+2$.
-So in the case that $W$ has all vertices with support at least two then $W$ must contain a pair of propagators of length $2$  with the property that the first propagator is $(i, i+2)$, the second is $(i+2, i+4)$ and no other propagator ends on the edge $i+2$.
-\end{rmk}
-
-\subsection{From Wilson Loop diagrams to Grassmann Necklaces}\label{sec:GN alg}
-
-Until now, the positroid associated to a Wilson loop diagram $W$ could only be obtained by computing the matrix $C(W)$ associated to $W$, listing all bases of the induced matroid $M(W)$, and constructing the Le diagram or Grassmann necklace of the positroid ``by eye'' from this list.
-
-In this section, we give an algorithm for passing directly from the Wilson loop diagrams to its Grassmann necklace.
-This not only greatly simplifies the process above, but will also allow us to relate the behavior of the positroid $M(W)$ directly to the configuration of progators in $W$.
-
-The fact that Algorithm~\ref{alg:put GN on WLD} does construct the required Grassmann necklace is proved in Theorem~\ref{res:alg gives GN}.
-An worked example of Algorithm~\ref{alg:put GN on WLD} is given in Example~\ref{eg:apply GN alg}.
-
-\begin{algorithm}\label{alg:put GN on WLD}
-Let $W = (\cP, [n])$ be an admissible Wilson loop diagram. This gives an algorithm for constructing the set $I_i^W$ (or just $I_i$ when $W$ is clear from context), for $i \in [n]$.
-
-\begin{enumerate}
-\item Fix a vertex $i \in [n]$, the {\bf starting vertex}. Set $j:=i$ and $I_i^W = \emptyset$.
-\item While $\cP \neq \emptyset$, perform the following steps:
-\begin{enumerate}
-\item {\em Step $j$ for starting vertex $i$}: If $\Prop(j) = \emptyset$, do nothing.
-Else, let $p \in \Prop(j)$ be the clockwise most propagator supported on $j$.
-Write $I_i^W = I_i^W\cup \{j\}$, and delete propagator $p$ from the diagram.
-\item Increment $j$ by 1 and repeat from (a).
-\end{enumerate}
-\end{enumerate}
-\end{algorithm}
-
-Informally: one starts at $i$ and moves counterclockwise around the vertices of $W$, at each step removing the clockwise-most propagator supported on that vertex (if it exists).
-The set $I_i$ lists the vertices at which a propagator was deleted.
-
-If the algorithm assigns vertex $j$ to propagator $p$ from starting vertex $i$, we say that $p$ \emph{contributes} $j$ to $I_i$.
-Notationally, we represent this by allowing the $I_i$ symbol to represent a function as well as a set, as follows:
-\begin{dfn}\label{def I_i as a function}
-Let $W = (\cP, [n])$ be an admissible Wilson loop diagram. For each $i \in [n]$, define a function $I_i^W : \cP \longrightarrow [n]$ by
-\[I_i^W(p) := \text{the vertex label that $p$ contributes to $I_i$ in Algorithm~\ref{alg:put GN on WLD},}\]
-for each $p \in \cP$. When the diagram $W$ is clear from context, we drop the superscript and simply write $I_i$.
-\end{dfn}
-
-{\color{violet}
-Each $I_i$ also imposes an ordering on the propagators, determined by when the propagator contributes to the sequence:
-\begin{dfn} \label{proporderingdfn}
-The ordering of the propagators on $W = (\cP, [n])$ defined by $I_i^W$ is $\cP = \{p_1, \ldots p_k\}$, where 
-\[I_i = \{I_i(p_1) <_i I_i(p_2) <_i \ldots <_i I_i(p_k)\}.\]
-(The superscript $W$ is omitted here to simplify the notation.)\note{Sian tweaked this slightly to emphasise the $<_i$ order, because standard convention in most papers is to write all GN terms in the 1-order.}
-\end{dfn}
-
-Since each propagator is removed by the algorithm after it contributes, each propagator contributed exactly once to $I^W_i$, making the above ordering well defined.}
-
-\begin{eg}\label{eg:apply GN alg}Consider the admissible Wilson loop diagram
-\[W\ =\ \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
-	\begin{scope}
-	\drawWLD{8}{1.5}
-	\drawnumbers
-	\drawlabeledprop{1}{0}{4}{0}{\footnotesize $q\ $}
-	\drawlabeledprop{2}{0}{4}{-1}{\footnotesize $p$}
-    \drawlabeledprop{5}{0}{8}{0}{\footnotesize $r\ \ $}
-    \drawlabeledprop{5}{1}{7}{0}{\footnotesize $\ \ \ s$}
-
-		\end{scope}
-	\end{tikzpicture}\]
-
-To construct $I_1$ we start at vertex 1, so we set $i=1$, $j = 1$, and $I_1 = \emptyset$. 
-\begin{itemize}
-\item $j = 1$: Since $\Prop(1) = \{q,r\}$ and $r$ is the clockwise-most of these propagators, we let $I_1 = \{1\}$ and remove propagator $r$ from the diagram. 
-\item $j = 2$: $\Prop(2) = \{p,q\}$, with $q$ being the clockwise-most of these propagators. So $I_1 = \{1,2\}$ and propagator $q$ is removed.
-\item $j = 3$: $\Prop(3) = \{p\}$, so now $I_1 = \{1,2,3\}$ and propagator $p$ is removed. The only remaining propagator in the diagram is $s$.
-\item $j = 4$: Since $p$ and $q$ were removed in earlier steps, we now have $\Prop(4) = \emptyset$.
-\item $j = 5$: $\Prop(5) = \{s\}$, and we have $I_1 = \{1,2,3,5\}$.
-\end{itemize}
-There are no propagators left in the diagram, so the algorithm terminates and we have ${I_1 = \{1,2,3,5\}}$, or $1235$ for short.
-So the propagators are ordered $r,q,p,s$ with respect to $I_1$, and $I_1$ viewed as a function is given by
-\[I_1: \cP \longrightarrow [n] : \quad I_1(r) = 1,\quad I_1(q) = 2, \quad I_1(p) = 3, \quad I_1(s) = 5.\]
-Applying the algorithm for all 8 starting vertices, we obtain the sets
-\[1235, 2356, 3456, 4567, 5671, 6712, 7812, 8123.\]
-The reader can easily verify that this sequence of $k$-sets satisfies the definition of a Grassmann necklace, and can (with significantly more work) also verify that this Grassmann necklace defines the positroid $M(W)$ associated to the Wilson loop diagram $W$ above.
-\end{eg}
-
-\begin{rmk}\label{rmk algorithm locally same}
-The following observation about the local behavior of the algorithm will be very useful in many of the arguments below.
-
- \note{Remember to keep an eye out when proofreading: do we just need the vertices appearing in the GN element to be the same or actually the function}
-
-Suppose we are going through the algorithm to construct $I_i^W$ for some $i$, and we are currently at step $j$ of the loop.
-Consider the diagram $W'$ formed by removing from $W$ all propagators that have already contributed to $I_i^W$.
-(This just replicates the behavior of the algorithm, which removes each propagator once it contibutes to $I_i^W$.)  Now suppose for some other diagram $V$ on the same vertex set we are constructing $I_m^V$ for some $m$, and we are at step $j$ of the loop, for the same $j$ as above.
-Again obtain $V'$ from $V$ by removing all propagators assigned so far.
-
-With this setup, if we can find a vertex $\ell$ (with $\ell <_i i$ and $\ell <_m m$) such that the configuration of propagators ending in the interval $(j-1, \ldots, \ell+1)$ is identical in both $W'$ and $V'$, then the vertices contributed to $I_i^W$ and $I_m^V$ are the same from step $j$ to step $\ell$ (inclusive).
-See Figure~\ref{fig:locally identical} for an illustration of this.
-
-\begin{figure}
-\includegraphics[scale=0.2]{locally_identical.jpg}
-\caption{$W'$ and $V'$ are locally the same between $j$ and $l+1$, so we will have $I_i^W\cap [j,l] = I_m^V\cap[j,l]$ even though $p \neq s$ and $q \neq t$.}\label{fig:locally identical}
-\end{figure}
-\end{rmk}
-
-With that in mind we are ready to begin proving properties of the algorithm.
-We first show that the algorithm can never reach the final vertex in a propagator's support without having already assigned that propagator; in particular, this guarantees that the construction of $I_i$ always terminates in fewer than $n$ steps.
-
-\begin{lem}\label{lem no fourth vertex}
-Let $W$ be an admissible Wilson loop diagram containing at least one propagator.
-For any $i \in [n]$ and for any $p \in \cP$, $I_i(p)$ is not maximal (with respect to $<_i$) amongst the vertices that support $p$.
-\end{lem}
-\begin{proof}
-Suppose for contradiction that we have $i \in [n]$ and $p \in \cP$ such that $I_i(p)$ is $<_i$-maximal in $V(p)$.
-There are two possibilities, which are illustrated in Figure~\ref{fig:no fourth vertex}: either $p = (i-1,b)$ for some $b$ (so $i$ and $I_i(p) = i-1$ are the two ends of a single edge), or $p = (a,b)$ with $i\leq_i a <_i b$ and $I_i(p) = b+1$.
-
-\begin{figure}
-\includegraphics[width=15cm]{4th_vertex}
-\caption{The two types of configuration in which a propagator could (in theory) contribute its $<_i$-maximal support vertex to $I_i$.}
-\label{fig:no fourth vertex}
-\end{figure}f
-
-In the left hand case, observe that we must have another propagator $q = (c,b)$ with $c<_i b$ and $I_i(q) = b+1$, because otherwise $I_i$ would assign $p$ to $b+1$.
-Now $q$ also contributes the $<_i$-maximal vertex in its support to $I_i$ and is an instance of the right hand case listed above.
-Therefore it suffices to show that no admissible Wilson loop diagram admits the configuration illustrated in the right hand case of Figure~\ref{fig:no fourth vertex}.
-
-So let $p = (a,b)$ with $a<_ib$ and $I_i(p) = b+1$, and choose $p$ such that $|[a+1,b]|$ is minimal amongst propagators of $W$ with this property.
-
-Since $I_i(p) \neq b$, there must exist a propagator $q$ inside of $(p,<_i)$ with $I_i(q) = b$.
-The propagator $q$ cannot end on the edge $b-1$, as this would contradict the minimality of $p$, so we have $q = (d,b)$ with $a <_i d <_i b$, and $I_i(q) = b$.
-
-In order for $q$ to remain unassigned until vertex $b$, there must be another propagator $r$ with an end on edge $d$ and $I_i(r) = d+1$; the only way this can occur is if $r$ is outside of $(q,<_i)$ but inside $(p,<_i)$.
-But now $r$ contributes its fourth vertex to $I_i$, again contradicting the minimality of $p$.
-\end{proof}
-
-\begin{cor}\label{GN alg well defined}
-If $W$ is an admissible Wilson loop diagram with $k$ propagators, then Algorithm~\ref{alg:put GN on WLD} assigns exactly $k$ distinct vertices to each $I_i$.
-\sanote{suddenly confused.
-Don't we need working about in going onely once around or somesuch?}\note{Sian: added the word ``distinct'' in the statement and a few words to the last line of the proof, does that help?}
-\end{cor}
-\begin{proof}
-Fix $i \in [n]$.
-It follows from the proof of Lemma~\ref{lem no fourth vertex} that in applying Algorithm~\ref{alg:put GN on WLD} to construct the set $I_i$, the algorithm can never reach the fourth vertex of a propagator's support (ordered with respect to $<_i$) without having already assigned $p$.
-Therefore if the algorithm starts at vertex $i$, all propagators must have been eliminated by the time it gets to vertex $i-1$, ensuring that the algorithm is completed in less than one full circumnavigation of the diagram and that $I_i$ contains exactly $k$ distinct elements.
-\end{proof}
-
-We now reverse our perspective and ask: given a propagator $p$ and a vertex $i$ in the support of $p$, for which set of starting vertices does the algorithm assign $p$ to $i$?
-
-Specifically, for each $i$ in the support of $p$ we define the set
-\[J_p^{W}(i) = \{m \in [n] \ | \ I^{W}_m(p) = i \},\]
-the set of starting vertices $m$ such that $I_m^{W}$ assigns $p$ to $i$.
-
-The following lemma establishes that these sets behave in a simple and predictable manner, a fact which we will repeatedly use in subsequent proofs.
-
-\begin{lem} \label{vertex cyclic int lem}
-
-Let $W = (\cP,[n])$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$.
-Then $J_p^{W}(i)$, $J_p^{W}(i+1)$, $J_p^{W}(j)$, and $J_p^{W}(j+1)$ are each non-empty cyclic intervals which partition $[n]$ and occur in the given cyclic order.
-\end{lem}
-\note{Right at the end when we put the tikz figures in, someone needs to go through this proof and replace ``leftmost two cases'' with ``Case 1 and 2'' etc, because the tikz picture is arranged differently}
-
-\begin{proof}
-We will prove the result by induction on the number of propagators.
-If $W$ has one propagator then the result is immediate.
-Now suppose $W$ has more than one propagator.
-Since non-supporting vertices have no effect on Algorithm~\ref{alg:put GN on WLD}, it suffices to prove the result for $W$  (possibly weakly admissible) with $F(\emptyset) = \emptyset$.
-Then by Lemma~\ref{lem sian}, $W$ has at least one of the four situations illustrated in Figure~\ref{fig 3 cases}.
-
-\begin{figure}
-    \includegraphics[scale=0.8]{3cases}
-    \caption{Four cases for admissible WLDs with no non-supporting vertices.
-The green half-propagators illustrate where propagators may occur, but are not required to exist; no other regions illustrated may support additional propagators.}\label{fig 3 cases}
-  \end{figure}
-
-In each of the four cases, when we remove the propagator labelled $p$ we obtain a diagram which satisfies the statement of the theorem by the induction hypothesis, and contains a propagator ${q = (i,j)}$ with no other propagators inside it (with respect to the $<_i$ orientation).
-Note that this region may or may not contain non-supporting vertices, which we will call $l, l+1, \ldots$ as necessary.
-Let $V$ be the diagram obtained by removing the propagator $p$ from $W$ (Figure \ref{fig V diagram}).
-$V$ is guaranteed to be an admissible diagram, since it was formed by removing a propagator from a diagram that was at least weakly admissible.
-
-\begin{figure}
-\includegraphics[width=10cm]{V_diagram}
-\caption{Diagram $V$ is $W$ with $p$ removed; there are no propagators inside $q = (i,j)$, though there may be up to 4 non-supporting vertices labelled $l, l+1, \ldots$.}
-\label{fig V diagram}
-\end{figure}
-
-Consider the fourth case of Figure~\ref{fig 3 cases} first, as it is the easiest.
-In this case, the vertices ${\{l,l+1,l+2,l+3\}}$ which support $p$ in $W$ are non-supporting in $V$, so for every propagator $r$ in $V$ (including $q$) we have $J_r^{V} = J_r^{W}$; these are non-empty cyclic intervals in the correct order by the induction hypothesis.
-Additionally, it is clear from Figure~\ref{fig 3 cases} that $J_p^{W}(l+a) = \{l+a\}$ for $a\in\{1,2,3\}$ and $J_p^{W}(l) = [n] \backslash \{l+1, l+2, l+3\}$.
-The result therefore holds in this case.
-
-Now we proceed to consider the first three cases of Figure~\ref{fig 3 cases}.
-We first describe $J_q^{V}(*)$, which can be handled identically for all three cases.
-
-In $V$ there are no propagators inside $q$ by construction, so we see from Figure \ref{fig V diagram} that
-\[l, l+1, \ldots ,j \in J^{V}_q(j) \text{ (if $l$ exists) and }  j+1 \in J^{V}_q(j+1).\]
-Note that $j+2 \not\in J^{V}_q(j+1)$ by Lemma~\ref{lem no fourth vertex}, so  $J^{V}_q(j+1) = \{j+1\}$ and by the induction hypothesis we must have $j+2 \in J^{V}_q(i)$.
-Thus there exist vertices $d,e \in [j+2,i+1]$ with $d <e$, such that
-\ba J^{V}_q(i) = [j+2,d-1], \quad J^{V}_q(i+1) = [d,e-1], \quad J^{V}_q(j) = [e,j], \quad J^{V}_q(j+1) = \{j+1\}, \label{deeqs}\ea
-and all intervals are non-empty.
-
-We now consider what happens as we move from $V$ to each of the three remaining cases for $W$.
-We need to consider both $J^{W}_p$ and $J^{W}_r$ for $r \neq p$, since the addition of $p$ can have a knock-on effect on later steps in the algorithm.
-
-%%%%%%%%%
-
-\textbf{Left two cases}: These cases behave essentially identically (except when $j$ or $j+1$ are not in the support of $p$, which can occur in the second case only; see below) so we handle the majority of the proof for these two cases simultaneously.
-Write $p=(m,m+2)$ where $m\in \{i, i+1, l\}$.
-Let $1\leq a\leq 3$ be the number of non-supporting vertices inside $q$ in $V$ (note that there is at least 1); so these vertices are $l, \ldots, l+a-1$.
-Note that these non-supporting vertices are all in the support of $p$.
-
-We first calculate $I^{W}_w$ for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$.
-Note that $p$ has no effect on other propagators for starting vertices in this range, so if $r \neq p$, then $I_w^W(r) = I_w^V(r)$.
-Meanwhile, the value of $I^{W}_w(p)$ depends on which step in the algorithm the propagator $q$ is assigned to a vertex, i.e.
-on the value of $I^{V}_w(q)$.
-Thus, if $w\in J_q^{V}(i)$ then
-    \[
-    I_w^{W}(r) =  \begin{cases}
-        \max\{i+1, m\} & \text{if } r=p \\
-        I_{w}^{V}(r) & \text{if } r\neq p
-      \end{cases} 
-    \]
-    while if $w\in J_q^{V}(i+1)$ or $w\in J_q^{V}(j)$ then
-    \[
-    I_w^{W}(r) =  \begin{cases}
-        l & \text{if } r=p \\
-        I_{w}^{V}(r) & \text{if } r\neq p
-      \end{cases} 
-      \]
-We also need to understand $I^{W}_w$ for $w \in \{l,l+1,\ldots,j,j+1\}$. For the majority 
-%$w \in [l, l+a-1]$} 
-%I left this as a comment so we can add it in if necessary, but I don't think we need this level of precision in this sentence: we're just signposting what we're going to do in detail shortly.
-of these vertices, we use the following observation: if $p$ is the first propagator to be assigned a value by $I_w^{W}$, then the remainder of $I_w^{W}$ proceeds identically to the assignments of $I^{V}_{w+1}$ (recall Remark~\ref{rmk algorithm locally same}).
-Thus we have for any $0\leq b <a$
-    \[
-    I_{l+b}^{W}(r) = \begin{cases}
-      l+b & \text{if } r=p\\
-      I_{l+b+1}^{V}(r) & \text{if } r\neq p
-    \end{cases}
-    \]
-Similarly, if $j$ is in the support of $p$, then we have
-     \[
-       I_j^{W}(r) = \begin{cases}
-         j & \text{if $r=p$ and $j$ is in the support of $p$}\\
-         I_{j+1}^{V}(r) & \text{if $r\neq p$ and $j$ is in the support of $p$}\\
-       \end{cases}
-       \]
-If $j$ is not in the support of $p$, then we must be in the second case of Figure~\ref{fig 3 cases} with two vertices in the right hand region.
-In this case, if we start the algorithm at $j$ we need to know whether there will be any unassigned propagators other than $p$ when we reach vertex $i$, so as to know what $p$ contributes.
-
-Consider the Wilson loop diagram $X$ formed from $V$ by replacing the propagator $q = (i,j)$ with $q = (i, j-1)$; \note{Added a note about $V$ being admissible when we defined it, so we can use $X$ admissible here without comment} $X$ is still admissible since we have not decreased the support of any set of propagators.
-% From the diagram we can see that $J_{j}^{V}(r) = J_{j}^{X}(r)$ for all $r\neq p$ (and in particular for $r=q$) and $J_{j}^{X}(r) = J_{j+1}^{X}(r)$ for $r\neq q,p$.  
-It follows from the position of $q$ in $X$ that $I_j^X(q) = j$, and from Lemma~\ref{lem no fourth vertex} that $I_{j+1}^X(q) \neq j$.
-By the induction hypothesis, we must therefore have $I_{j+1}^X(q) = i$; in particular, this means that if we start at $j+1$ and assign propagators to vertices according to the algorithm, when we reach vertex $i$ in $X$ all propagators other than $q$ must have been assigned.
-
-Therefore if we start at $j$ in $W$, we first assign $q$ to $j$ then proceed to assign as in $X$ starting at $j+1$, and hence when we get to $i$ the only remaining unassigned propagator is $p$.
-We obtain
-       \[
-       I_j^{W}(r) = \begin{cases}
-
-       m & \text{if $r =p$ and $j$ is not in the support of $p$} \\
-       I_{j}^{V}(r) & \text{if $r\neq p$ and $j$ is not in the support of $p$}\end{cases}
-       \] 
-This completes the analysis of $I_j^W$. Finally, we consider what happens when we start the algorithm at vertex $j+1$. If $j+1$ is in the support of $p$ then we can argue as above to get
-\[
-       I_{j+1}^{W}(r)  = \begin{cases}
-         j+1 & \text{if $r=p$ and $j+1$ is in the support of $p$}\\
-         I_{j+2}^{V}(r) & \text{if $r\neq p$ and $j+1$ is in the support of $p$}.
-       \end{cases}
-       \]
-Now suppose $j+1$ is not in the support of $p$.
-If we start at $j+1$ we need to know whether there are any unassigned propagators supported on edge $i$ when we reach vertex $i$.
-We already know that $J_q^{V}(j+1) = \{j+1\}$; in particular this means that $q$ contributes $i$ in $I_{j+2}^{V}$, by the induction hypothesis applied to $V$.
-However the construction of $I^{V}_{j+1}$ first assigns $q$ to $j+1$ and then proceeds identically to $I^{V}_{j+2}$.
-In particular if $i$ was assigned in $I^{V}_{j+1}$, then it would not be available to assign to $q$ in $I^{V}_{j+2}$ as all other propagators supported at $i$ in $V$ come before $q$.
-
-Therefore $p$ is the only potentially unassigned propagator on edge $i$ when we reach vertex $i$ in the algorithm for $I_{j+1}^W$, and
-    \[
-    I_{j+1}^{W}(r)  = \begin{cases}
-      m & \text{if  $r=p$ and $j+1$ is not in the support of $p$}\\
-      I_{j+1}^{V}(r) & \text{if  $r\neq p$ and $j+1$ is not in the support of $p$}
-    \end{cases}
-    \]
-We can now describe the intervals $J^{W}_r(*)$ for the first two cases of Figure~\ref{fig 3 cases}.
-For $r \neq p$ the intervals are clearly still cyclic and appear in the correct order, and we can assemble the intervals for the $J_p^{W}(*)$ as follows.
-Recall that $p = (m,m+2)$, $1 \leq a \leq 3$ is the number of non-supporting vertices inside $q$ in $V$, and these non-supporting vertices are denoted $\{l,l+1, \dots\}$.
-    \begin{itemize}
-      \item 
-    If $m=l$ then either $a=2$ (so $l+1=m+1$, $j=m+2$, and $j+1=m+3$) or $a=3$ (so $l+1=m+1$, $l+2=m+2$, $j=m+3$, and $j+1$ is not in the support of $p$), and in both cases
-    \begin{gather*}
-    J^{W}_p(m) = [m+4, m], \qquad  J^{W}_p(m+1) = \{m+1\}, \\ J^{W}_p(m+2) = \{m+2\}, \qquad  J^{W}_p(m+3) = \{m+3\},
-    \end{gather*}
-    which are nonempty and otherwise as required.
-  \item
-        If $m=i+1$ then checking each of the three different possibilities for $a$ we likewise get
-    \begin{gather*}
-    J^{W}_p(m) = [m+4, d-1], \qquad  J^{W}_p(m+1) = [d, m+1], \\  J^{W}_p(m+2) = \{m+2\}, \qquad  J^{W}_p(m+3) = \{m+3\},
-    \end{gather*}
-    which are nonempty and otherwise as required. Recall that $d$ was defined in equation \eqref{deeqs}.
-  \item If $m=i$ then $a=1$ or $a=2$, in the former case $l=m+2$, $j=m+3$ and $j+1$ is not in the support of $p$ so
-    \begin{gather*}
-    J^{W}_p(m) = \{m+4\}, \qquad  J^{W}_p(m+1) = [m+5, d-1], \\  J^{W}_p(m+2) = [d, m+2], \qquad  J^{W}_p(m+3) = \{m+3\},
-    \end{gather*}
-    while in the latter $l=m+2$, $l+1=m+3$, and $j$ and $j+1$ are not in the support of $p$ so
-    \begin{gather*}
-    J^{W}_p(m) = [m+4, j+1], \qquad  J^{W}_p(m+1) = [j+2, d-1], \\  J^{W}_p(m+2) = [d, m+2], \qquad  J^{W}_p(m+3) = \{m+3\},
-    \end{gather*}
-    which are again as required.
-    \end{itemize}
-
-\textbf{Third case}: In this case there are no non-supporting vertices $l, l+1, \ldots$ inside $q$.
-Again write $p=(m, m+2)$ where $m\in \{j, j+1, j+2\}$.
-We proceed as in the previous cases, by computing $I^{W}_w$ for vertices $w$ in roughly increasing order of difficulty.
-
-For $w \in [n]\backslash\{j+1,m,m+1,m+2,m+3\}$: if $w\in J_q^{V}(i)$ or $w\in J_q^{V}(i+1)$ then
-    \[
-    I_w^{W}(r) =  \begin{cases}
-        m & \text{if } r=p \\
-        I_{w}^{V}(r) & \text{if } r\neq p
-      \end{cases} 
-    \]
-    while if $w\in J_q^{V}(j)$ then
-    \[
-    I_w^{W}(r) =  \begin{cases}
-        \max\{m, j+1\} & \text{if } r=p \\
-        I_{w}^{V}(r) & \text{if } r\neq p
-      \end{cases} 
-    \]
-
-Finally, for $j+1$ and the vertices in the support of $p$, we have
-
-\begin{align*}
-  I_{j+1}^{W}(r) &= \begin{cases}
-    j+1 & \text{if } r=q\\
-    j+2 & \text{if } r=p\\
-    I_{j+3}^{V}(r) & \text{if } r\neq p,q
-  \end{cases}\\
-  I_m^{W}(r) &= \begin{cases}
-    m & \text{if $r=p$ and $q$ not supported on $m$}\\
-    m+1 & \text{if $r=p$ and $q$ supported on $m$}\\
-    I_{m}^{V}(r) & \text{if } r\neq p
-  \end{cases}\\
-  I_{m+1}^{W}(r) & = \begin{cases}
-    m+1 & \text{if $r=p$ and $q$ not supported on $m+1$} \\
-    m+2 & \text{if $r=p$ and $q$ supported on $m+1$} \\
-    I_{m+1}^{V}(r) & \text{if } r\neq p,q
-  \end{cases}\\
-  I_{m+2}^{W}(r) & = \begin{cases}
-    m+2 & \text{if } r=p \\
-    I_{m+3}^{V}(r) & \text{if } r\neq p
-  \end{cases}\\
-  I_{m+3}^{W}(r) & = \begin{cases}
-    m+3 & \text{if } r=p \\
-    I_{m+4}^{V}(r) & \text{if } r\neq p
-  \end{cases}
-\end{align*}
-Note that $I_{m+2}^{V}(r) = I_{m+3}^{V}(r)$ for all propagators $r$ in $V$, and that if $j+1\not\in\{m, m+1, m+2, m+3\}$ then $j+2$ and $j+3$ are non-supporting vertices in $V$, so in that case $I_{j+2}^{V}(r) = I_{j+3}^{V}(r) = I_{j+4}^{V}(r)$ for $r$ in $V$.
-
-Therefore, once again we can see that the $J_r^{W}(*)$ are cyclic for all $r\neq p$ in $W$.  Assembling the intervals for $p$ we have:
-\begin{itemize}
-\item If $m=j$ then
-\begin{gather*}J_p^{W}(m) = [m+4,e-1], \qquad  J_p^{W}(m+1) = [e,m], \\  J_p^{W}(m+2) = [m+1,m+2], \qquad  J_p^{W}(m+3) = \{m+3\},\end{gather*}
-Recall that $e$ was defined in equation \eqref{deeqs}.
-\item If $m=j+1$ then
-\begin{gather*}J_p^{W}(m) = [m+4,m-1], \qquad J_p^{W}(m+1) = [m,m+1], \\  J_p^{W}(m+2) = \{m+2\}, \qquad  J_p^{W}(m+3) = \{m+3\},\end{gather*}
-\item If $m=j+2$ then
-\begin{gather*}J_p^{W}(m) = [m+4,m], \qquad  J_p^{W}(m+1) = \{m+1\}, \\  J_p^{W}(m+2) = \{m+2\}, \qquad  J_p^{W}(m+3) = \{m+3\}.\end{gather*}
-\end{itemize}
-The result now follows by induction.
-\end{proof}
-
-We are now ready to prove that Algorithm~\ref{alg:put GN on WLD} does in fact give the Grassmann necklace of the positroid associated to $W$.
-
-\begin{thm}\label{res:alg gives GN}
-The sequence of $k$-subsets $(I_1,\dots,I_n)$ obtained by applying Algorithm~\ref{alg:put GN on WLD} to all vertices of an admissible diagram $W$ is exactly the Grassmann necklace of $M(W)$.
-\end{thm}
-\begin{proof}
-For each $i \in [n]$, let $I_i$ be the set of vertices assigned to the propagators of $W$ by Algorithm~\ref{alg:put GN on WLD} with starting vertex $i$.
-By Lemma~\ref{GN alg well defined}, we know that $|I_i| = k$ for each $i \in [n]$.
-We first prove that $I_{i+1} \supseteq I_i \backslash \{i\}$ for all $i \in [n]$; this is equivalent to the definition of Grassmann necklace given in Definition~\ref{def:grassmann necklace}.
-
-Suppose for a contradiction that there exists an admissible diagram for which there exists an $i$ with $m\in I_i\setminus \{i\}$ and $m \not\in I_{i+1}$.
-Fix $n$.
-Let the triple $(W, i, m)$ be such a counterexample on $n$ vertices which is minimal with respect to the number of propagators.
-%, and among all those counterexamples on $n$ vertices with the same number of propagators, let $(W,i,k)$ be minimal with respect to the distance from $i$ to $k$ in the $\leq _i$ order.
-
-If $i \not\in I_i$, then there are no propagators supported on $i$ at all.
-In this case it is clear that applying Algorithm~\ref{alg:put GN on WLD} at vertex $i$ and vertex $i+1$ produces exactly the same result, i.e.
-$I_{i+1} = I_i$, and so $(W, i, m)$ is not a counterexample at all.
-
-Now suppose that $i \in I_i$.
-Let $p$ be the propagator which contributes $i$ to $I_i$, that is $I^W_i(p) = i$; thus one end of $p$ must lie on either edge $i-1$ or edge $i$.
-In both cases let $b$ denote the edge supporting the other end of $p$, i.e.
-$p = (i, b)$ or $p = (i-1, b)$.
-
-\textbf{Case I}:  Suppose $p$ has one end on edge $i-1$.
-If $p$ is not supported on $i+1$, then in building $I_{i+1}$ we will assign the same propagators as in the construction of $I_i$ from vertices $i+1$ up to $b-1$, that is $I_{i+1} \cap [i+1,b-1] = I_{i} \cap [i+1,b-1]$.
-(If $p$ is supported on $i+1$, then $b= i+1$ and the interval $[i+1,b-1]$ is empty.) Furthermore, by Lemma~\ref{vertex cyclic int lem} it must happen that $p$ contributes vertex $b$ to $I_{i+1}$, as otherwise $b$ would never be contributed by $p$.
-Consequently, in building $I_{i+1}$, when the algorithm reaches vertex $b$ there cannot be any remaining unassigned propagators that are supported on $b$ and counterclockwise of $p$.
-This is also true in when the algorithm constructing $I_i$ reaches $b$, since the same propagators have been assigned beforehand.
-Finally, we also note that $m\geq_i b+1$.
-
-Let $W' = (\cP_{out}(p,<_i), [n])$, i.e. the diagram obtained from $W$ by removing both $p$ and all propagators inside of $p$.
-
-By the above observations, if we commence Algorithm~\ref{alg:put GN on WLD} in $W'$ from vertex $b$, then we are in the same situation with respect to unassigned propagators as if we began at $i$ in $W$ and proceeded to $b$ following the algorithm (recall that $I^W_i(p) =i$).
-The propagators contributing to $I_{i}^W$ before the vertex $b$ are exactly the ones removed in the construction of $W'$.
-Similarly, starting at $i+1$ in $W$ and moving to $b+1$ leaves us in the same situation with respect to unassigned propagators as beginning at $b+1$ in $W'$ would.
-This gives the equations
-\begin{align*}
-  I_i^{W} \cap [b,i-1] & = I_b^{W'} \\
-  I_{i+1}^{W} \cap [b+1,i-1] & = I_{b+1}^{W'}
-\end{align*} 
-where the diagram is indicated in the superscript.
-Thus we have $m\in I_b^{W'}\setminus\{b\}$ and $m\not\in I_{b+1}^{W'}$, contradicting the minimality of $(W, i, m)$.
-
-\textbf{Case II}: Suppose $p$ has one end on edge $i$.
-Note that by assumption we have $I_i(p) = i$; this means that $p$ must be the counterclockwise-most propagator lying on edge $i$, and hence we must have $I_{i+1}(p) = i+1$ as well.
-Observe also that $m\geq_i i+2$ since $i+1\in I_{i+1}$.
-
-Let $W'$ be the diagram obtained from $W$ by removing only the propagator $p$.  Then we have
-\begin{align*}
-  I_i^{W} \backslash \{i\} & = I_{i+1}^{W'} \\
-  I_{i+1}^{W} \backslash \{i+1\} & = I_{i+2}^{W'}
-\end{align*}
-since in both cases the algorithm in $W'$ proceeds identically to that in $W$ after assigning $p$.
-Since $m \neq i+1$, we have $m\in I_{i+1}^{W'}\setminus\{i+1\}$ but $m\not\in I_{i+2}^{W'}$, contradicting the minimiality of $(W, i, m)$.
-
-\medskip  \sanote{Suggested breakpoint of theorem}
-
-We have shown that $(I_1,\dots,I_n)$ is a Grassmann necklace; it remains to check that this Grassmann necklace corresponds to the positroid $M(W)$.
-Recall from the discussion following Definition~\ref{def:grassmann necklace}, and equation \eqref{basesofmatroids} in particular, that it suffices to show:
-\begin{itemize}
-\item For each $i \in [n]$, $I_i$ is a basis for $M(W)$.
-\item If $J$ is lexicographically smaller than $I_i$ with respect to $<_i$ (for any $i \in [n]$) then $J$ is not a basis for $M(W)$. 
-\end{itemize}
-The first point follows immediately: since the algorithm is pairing each $j \in I_i$ with a unique propagator supported on that vertex, $I_i$ is a basis for $M(W)$ by Corollary~\ref{lem basis as perm}.
-
-Now suppose we have a $k$-set $J$ such that $J$ is a basis for $M(W)$ and yet is lexicographically less than $I_i$ with respect to $<_i$.
-By Corollary~\ref{lem basis as perm} there is a set bijection between $J$ and the propagators of $W$ such that for each $j \in J$, the propagator associated to $j$ is supported on vertex $j$.
-Choose one such bijection.
-For each propagator $p$ of $W$, write $J(p)$ for the vertex $j$ associated to $p$ according to this bijection.
-
-Since $J$ is lexicographically smaller than $I_i$, the $<_i$-smallest element of the symmetric difference of $J$ and $I_i$ is some $j_0\in J$, $j_0 \not\in I_i$.
-Let $p_1$ be the propagator such that $J(p_1)=j_0$.
-Since $j_0\not\in I_i$ but $p_1$ is supported at $j_0$, then $p_1$ must have been assigned to an earlier vertex by $I_i$, i.e.
-we have $I_i(p_1) <_i j_0$.
-Let $j_1 = I_i(p_1)$.
-
-However, $j_0$ is the $<_i$-smallest element in the symmetric difference of $J$ and $I_i$, so we must have $j_1 \in J$ as well; in particular, there is some propagator $p_2$ such that $J(p_2)=I_i(p_1)$.
-Let $j_2 = I_i(p_2)$ and note that $j_2 \neq J(p_2)$ (since $I_i(p_1)=J(p_2)$), so either $I_i(p_2) \not\in J$ or there is a propagator $p_3$ such that $J(p_3) = I_i(p_2)$.
-Continue this process for as many steps as possible (i.e.
-for as long as $I_i(p_*) \in J$); this produces a list of vertices $j_r$ and propagators $p_r$ such that
-\[J(p_r) = I_i(p_{r-1}) = j_{r-1}.\]
-
-We claim that there is no repetition of propagators or vertices in this list; this will show that the process must eventually terminate.
-The claim is proved by induction.
-The definition of $j_0$ gives that $j_0$ and $j_1$ are distinct and that $p_1$ and $p_2$ are distinct.
-Now, suppose we have $p_r$ and $j_r$ with $I_i(p_r)=j_r$, with $j_r$ distinct from all previous $j_*$ and with $j_r\in J$.
-Then there must exist a propagator $p_{r+1}$ with $J(p_{r+1}) = j_r$.
-Since $J: \cP \longrightarrow [n]$ is injective and $j_r$ is not equal to any of the previous vertices $j_0, \dots, j_{r-1}$ by assumption, $p_{r+1}$ must be distinct from the previous propagators $p_1,\dots,p_r$.
-Following the pattern, define $j_{r+1} = I_i(p_{r+1})$.
-Since $I_i: \cP \longrightarrow [n]$ is also injective and $p_{r+1}$ is distinct from the earlier $p_*$, it follows that $j_{r+1}$ is distinct from the other $j_s$ for $1\leq s\leq r$.
-Finally, we have $j_{r+1}\neq j_0$ since $j_0\not\in I_i$ but $j_{r+1}\in I_i$.
-This proves the claim.
-
-Therefore the list must end, and the only way it can end is with some $p_r$ such that $j_r = I_i(p_r)\not\in J$. In particular, this implies that $j_r >_i j_0$.
-
-Next we will prove that $j_r <_i j_0$ for all $r > 0$; this gives a contradiction to the existence of $J$ and completes the proof of the theorem.
-This proof will also be by induction; however, for the induction to go through nicely we will need to prove the following slightly stronger statement:
-for all $r>0$ in the list
-\begin{itemize}
-\item $j_r <_i j_0$ and
-\item either
-  \begin{itemize}
-  \item $I_i(p_r) <_i J(p_r)$, or
-  \item there exists an $\ell<r$ such that $I_i(p_\ell) <_i J(p_\ell)$, those two vertices support distinct ends of $p_\ell$, and $p_r$ is inside $p_l$ when $p_l$ is directed from $I_i(p_\ell)$ to $J(p_\ell)$.\note{Should I replace this with ``$p_r$ is inside $(p_l,<_i)$''?
-It matches previous notation but maybe is less clear?}
-  \end{itemize}
-\end{itemize}
-
-We observed above that $j_1 <_i j_0$ and $I_i(p_1) <_i J(p_1)$ so we have the base case for the induction.
-Now fix $r > 1$ and suppose that the inductive hypothesis holds for all indices less than $r$ and that $p_r$ exists.
-
-By definition $J(p_r) = I_i(p_{r-1}) = j_{r-1}$, so $p_{r-1}$ and $p_{r}$ are both supported at vertex $j_{r-1}$.
-
-Since $I_i$ always chooses the earliest unassigned propagator supported at a vertex, we have two possibilities (which are not mutually exclusive): either $p_{r-1}$ appears before $p_r$ in the neighbourhood of $j_{r-1}$, or $p_r$ was assigned earlier than $p_{r-1}$ by the algorithm for $I_i$.
-(Note that the ordering $p_1,p_2,\dots,p_r$ need not match the order in which Algorithm~\ref{alg:put GN on WLD} assigns propagators to vertices.)
-
-In the latter case we are done, since $p_r$ being assigned earlier than $p_{r-1}$ by $I_i$ means exactly that $I_i(p_r) <_i I_i(p_{r-1})$.
-Recalling that $I_i(p_{r-1}) = J(p_r) = j_{r-1}$, this implies that $I_i(p_r) <_i J(p_r)$ and $j_r = I_i(p_r) <_i j_{r-1} <_i j_0$, as required.
-
-Now assume that $p_{r-1}$ appears before $p_r$ in the neighbourhood of $j_{r-1}$, and that $I_i$ assigns $p_{r-1}$ before $p_r$.
-
-\hlfix{If $I_i(p_{r-1}) <_i J(p_{r-1})$ and these are vertices supported by distinct ends of $p_{r-1}$}{Sian was unsure about this sentence, and added the blue text below which may or may not be necessary}, then by our assumption that $p_{r-1}$ appears before $p_r$ in the neighbourhood of $j_{r-1}$ it follows that $p_r$ must lie inside $p_{r-1}$ when directed from $I_i(p_{r-1})$ to $J(p_{r-1})$.
-Therefore
-\[j_r = I_i(p_r) \leq_i J(p_{r-1}) + 1.\]
-If $r > 2$ then this gives $j_r \leq_i I_i(p_{r-2}) + 1 \leq_i j_0$, but we know that $j_0\not\in I_i$ so in fact we have a strict inequality $j_r<_i j_0$.
-If $r=2$ then the inequality reads $j_2 \leq_i J(p_1) + 1 = j_0 + 1$, so either $j_2 <_i j_0$ or we have the configuration
-\[
-\includegraphics{impossible_config}
-\]
-However, this is impossible because now $p_2$ is supported at $j_0$ but not assigned by $I_i$ until after $j_0$, even though $j_0\not\in I_i$.
-Thus we always have $j_r <_i j_0$ and the inductive step is complete in this case (with $p_{r-1}$ playing the role of $p_l$ here).
-
-\textcolor{blue}{
-On the other hand, if $I_i(p_{r-1}) <_i J(p_{r-1})$ and these vertices are on the same end of $p_{r-1}$, then we must have 
-\[
-\includegraphics[width=10cm]{extra_config}
-\]
-If $r = 2$, then $J(p_{r-1}) = j_0$ and our assumption that $p_{r-1}$ is assigned before $p_r$ means that $I_i$ assigns $p_2$ to $j_0$, which is again a contradiction.
-If $r>2$ then $J(p_{r-1}) = I_i(p_{r-2})$ implies we have another propagator $p_{r-2}$ on this same edge, which must lie between $p_{r-1}$ and $p_r$ to ensure that $I_i$ assigns everything in the correct order.
-Now $J(p_{r-2})$ must support the other end of $p_{r-2}$, and we can apply the same argument as above with $p_{r-2}$ instead of $p_{r-1}$.}
-
-The only remaining possibility is that $I_i(p_{r-1})\not<_i J(p_{r-1})$, so now assume this.
-We continue to assume that $p_{r-1}$ appears before $p_r$ in the neighbourhood of $j_{r-1}$ and that $I_i$ assigns $p_{r-1}$ before $p_r$.
-
-By the induction hypothesis,  $I_i(p_{r-1})\not<_i J(p_{r-1})$ implies that there exists an $\ell < r-1$ such that $p_{r-1}$ lies inside $p_{\ell}$ when directed from $I_i(p_\ell)$ to $J(p_\ell)$.
-Since $p_{r-1}$ and $p_r$ are both supported on vertex $j_{r-1}$, either $p_r$ is also inside $p_l$ (in which case we apply the arguments above with $l$ instead of $r-1$) or $p_l$ lies between $p_{r-1}$ and $p_r$ in the neighbourhood of $j_{r-1}$.
-
-Since $I_i(p_{r-1}) = j_{r-1}$ and $p_{r-1}$ is inside $p_l$, the fact that no propagator can contribute its 4th vertex to $I_i$ (Lemma~\ref{lem no fourth vertex}) means that we have the following configuration:
-\[
-\includegraphics[width=10cm]{new_induction_conf}
-\]
-If $l=1$ then $J(p_l) = j_0$, and $p_r$ is supported on $j_0$ but assigned by $I_i$ later than $j_0$, which is a contradiction.
-If $l>1$ then $J(p_l) = I_i(p_{l-1})$, and propagator $p_{l-1}$ must appear before $p_r$ in the neighbourhood of $j_{r-1}$ to ensure that $I_i$ assigns $p_{l-1}$ correctly.
-But now $J(p_{l-1})$ must be on the other end of $p_{l-1}$, since the vertices on this end are $J(p_r)$ and $J(p_l)$ and we know that $l-1 < l < r$.
-Finally, we must have $I_i(p_{l-1}) <_i J(p_{l-1})$ so that $I_i$ does not assign $p_{l-1}$ to its fourth vertex.
-Now $p_r$ lies inside $p_{l-1}$ and we argue as above.
-
-%  If $j_{r-1}$ is not in the support of the $J(p_\ell)$ end of $p_\ell$ then $p_{r-1}$ before $p_{r}$ around $j_{r-1}$ implies that $p_r$ is on the same side of $p_\ell$ as $p_{r-1}$ is.
-Then the same arguments as above with $\ell$ in place of $r-1$ give $j_r \leq_i J(p_\ell)+1$ implying $j_r <_i j_0$ which is everything we need.
-
-% It remains to consider when $j_{r-1}$ is in the support of the $J(p_\ell)$ end of $p_\ell$, call this case $(*)$.
-Since $J(p_\ell) = j_{\ell-1}$ and the vertices $j_1,\dots,j_r$ are distinct, this means that we have one of the following two configurations
-% \[
-% \includegraphics{induction_conf}
-% \]
-% If $p_\ell=p_1$ then $j_{\ell-1}=j_0$ and then as $j_0\not\in I_i$ but $p_r$ is supported at $j_0$ we get $I_i(p_r) <_i j_0$ and also $I_i(p_r) <_i j_{r-1} = J(p_r)$ as the only vertices not yet taken for $I_i(p_r)$ must be before both labelled vertices in the illustration.
-
-% If $p_\ell \neq p_1$ then we argue as above with $\ell-1$ in place of $r-1$: in particular $J(p_\ell) = I_i(p_{\ell-1})$ but $p_r$ is supported at $p_{\ell-1}$, so either $I_i(p_r) <_i I_i(p_{\ell-1})$ in which case as before we get desired conclusion, or $p_r$ comes before $p_{\ell-1}$ at $j_{\ell-1}$.
-Then again argue as before getting a new $p_{\ell'}$ in place of $p_{\ell}$, except that then case $(*)$ must occur simultaneously for both $p_{\ell'}$ and $p_{\ell}$ with respect to $p_{r}$.
-This can only occur if $j_{\ell-1}, j_{r-1}, j_{\ell'-1}$ are consecutive.
-Iterating the argument one more time we finally cannot have case $(*)$ as then all neighbouring vertices of $j_{r-1}$ are used up.
-
-This covers all cases and completes the induction, and thence the proof of the theorem.
-
-\end{proof}
-
-\sanote{alternate proof of second half of above}
-{\color{violet} \begin{thm}
-The Grassmann necklace $(I_1 \ldots I_n)$ is the Grassmann neclace for $M(W)$ 
+\begin{thm}
+The Grassmann necklace $(I_1 \ldots I_n)$ from [previous theorem] is the Grassmann necklace for $M(W)$.
 \end{thm}
@@
 \end{itemize}
-The first point follows immediately: since the algorithm is pairing each $j \in I_i$ with a unique propagator supported on that vertex, $I_i$ is a basis for $M(W)$ by Corollary~\ref{lem basis as perm}.
+The first point follows immediately: the algorithm is pairing each $j \in I_i$ with a unique propagator supported on that vertex, so $I_i$ is a basis for $M(W)$ by Corollary~\ref{lem basis as perm}.
 
-For the second point, order the propagators according to the ordering induced by the algorithm for $I_i$.
-Write $\cP = \{p_1, \ldots , p_k\}$.
-That is, $p_i$ defines the $i^{th}$ row of $C(W)$.
-For $m<k$, write $\cP_m = \{p_1, \ldots , p_k\}$.
+Now fix $i \in [n]$, and write $I_i = \{a_1 <_i a_2 <_i \dots <_i a_k\}$.
+This imposes an ordering on the propagators $\cP$, where we label them $p_1, p_2, \dots, p_k$ such that $I_i(p_j) = a_j$ for each $j$.
+Define $\cP_m: = \{p_1,p_2,\dots,p_m\}$ for each $m\geq 0$, with $\cP_0 = \emptyset$.
 
-Write $I_i(p_j)=a_j$.
-If two consecutive propagators do not contribute consecutive vertices, that is, there exist $a_{j-1} <_i x <_i a_j$ then the vertex $x$ supports only propagators in $\cP_j$, if any: $\Prop(x) \subset \cP_j$.
+We first note that if $a_{m-1}$ and $a_{m}$ are not consecutive vertices for some $m$, then for any intermediate vertex $a_{m-1}<_i x <_i a_{m}$ we must have $\Prop(x) \subseteq \cP_{m-1}$.
+This is because if any propagator supported on $x$ is still unassigned when the algorithm reaches $x$, we would have $x \in I_i$.
 
-Let $J = (j_1,\ldots j_k)$ be a sequence that is lexicographically less than $I_i = (a_1 \ldots a_k)$: $J <_i I_i$.
-By the above, for some $m < k$, $a_{m-1} <_i j_m <_i a_m$ and the matrix entry $c_{m, j_m} = 0$ is $0$.
-Without loss of generality, let $m$ be the smallest $m$ in the $<_i$ order for which this is true: \bas \forall l <m, \; I_i(p_l) = j_l \; ; \; j_m < I_i(p_m) \;.\eas Write $J_m = (j_1, \ldots, j_m)$ indicate the first $m$ entries of $J$.
-We claim that there exists some subset  of vertices $U \subset J_m$ such that $|\Prop(U)| < |U|$.
+Let $J = \{j_1 <_i j_2<_i \dots <_i j_k\}$ be a $k$-set, and suppose that $J<_i I_i$ in the $<_i$-lexicographic order.
+Let $m$ be the minimal index such that $j_m <_i a_m$, i.e.
+the first entry at which $J$ and $I_i$ differ.
+We will show that $J$ must be a dependent set.
 
-Consider the vertices contributed by the propagators originally supported on $j_m$: $V = I_i(\Prop(j_m))$.
-By construction, these are a subset of $J_{m-1}$.
-Note that $\Prop(V) \subset \cP_m$.
-Let $p_l$ be supported on $j_m$.
-If $q$ is suported on $p_l$, either $q$ preceeds $p_l$ (i.e.
-is not there when the algorithm reaches $a_l$) or is positioned counterclockwise to $p_l$ at the vertex $a_l$.
-That is, $q$ is inside $p_l$ in the $<_i$ ordering.
-By Lemma \ref{lem no fourth vertex}, $q$ does not contibute its last supporting vertex to $I_i$.
-That is, $I_i(q) <j_m$.
-\hlfix{But this implies that $q$ contributed before $p_m$, which contradicts the hypothesis.}{Seems to demand that $I_i$ catches all propagators in a single circuit of the vertices.
-Is this explicit anywhere, or am I jumping the gun?} Therefore $q \in \cP_{m-1}$.
+If $\Prop(j_m) = \emptyset$ then $J$ is automatically dependent since the corresponding column of $C(W)$ contains only zeros, so suppose henceforth that $\Prop(j_m) \neq \emptyset$.
+In particular, this implies that $m>1$, since if $m=1$ we would have $\Prop(j_1) \subseteq \cP_0 = \emptyset$.
 
-If $\Prop(j_m) = \Prop(V)$, we have that $V$ and $V \cup j_m$ support the same propagators. That is, \bas |\Prop(V)| = |V| = |\Prop(V \cup j_m )| <  |V \cup j_m| \;.\eas
+We define a sequence of sets of propagators by
+\[Q_0 = \Prop(j_m), \qquad Q_{l+1} = \Prop(I_i(Q_l))\quad \forall l \geq 0.\]
+It is easily verified that this is an increasing chain of sets: indeed, if $q \in Q_l$ then $I_i(q) \in I_i(Q_l)$, and since $I_i(q)$ is one of the vertices that supports $q$ we must have $q \in \Prop(I_i(Q_l)) = Q_{l+1}$.
+The sequence therefore stabilizes in finitely many steps, since $\cP$ is finite.
 
-If $\Prop(j_m) \subsetneq \Prop(V)$, expand $V$ to include the vertices contributed by $\Prop(V)$.
-That is, $V' = I_i(\Prop(V))$.
-By the argument above, $\Prop(V) \subset \cP_m$.
-If $\Prop(V) = \Prop(V')$ then the relevant vertex set is $V'$.
-Else, continue expanding $V'$ in this manner until no new propagators are added.
-Since all of these sets of propagators are contained in $\cP_m$, which is finite, this process is finite.
+We claim that $Q_l \subseteq \cP_{m-1}$ for all $l\geq 0$. The base case follows immediately from the observation above that $\Prop(j_m) \subseteq \cP_{m-1}$.
 
-\begin{comment}
-By algorithm \ref{alg:put GN on WLD}, $a_j$ is the smallest number in the $<_{a_{j-1}}$ ordering such that $c_{j, a_j} \neq 0$ (that is, is an indeterminant entry).
-Therefore, $p_m \not \in \Prop(j_m)$.
-In fact, no $q$ that follow $p_m$ in the ordering can be supported on $j_m$.
-Since $j_m < a_m$, the algorithm for $I_i$ checks this vertex before $a_m$.
-If any propagator in $\cP \setminus \cP_{m-1}$ are supported on $j_m$, then this propapagator would preceed $p_m$, i.e.
-be an element of $\cP_{m-1}$.
-Therefore, the only non-zero entries in column $j_m$ of $C(W)$ lie in the first $m-1$ rows.
+[induction step; see final page]
 
-Therefore, $\Prop(j_m) \subset \cP_{m-1}$.
-Let $V =  V(\Prop(j_m)) \cap J_{m-1}$ be the vertices in $J_m$ supporting the propagators supported on $j_m$.
-That is, $V$ is contains the vertices contributed by $\Prop(j_m)$.
-So $|\Prop(j_m)| \leq |V|$.
-We show that $\Prop (V) \subset \Prop_{m-1}$.
-Suppose otherwise.
-Let $q \in \cP \setminus \cP_m$ be a propagators after $p_m$ and $p_l \in \Prop(j_m)$ a propagators before $p_m$ supported on $j_m$ such that both $q$ and $p_l$ are supported on $I_i(p_l)= a_l$.
-Since $p_l$ contributes $a_l$, it must be the clockwisemost propagator in $\cP \setminus \cP_{l-1}$ supported on $a_l$.
-In other words, $q \in \cP_{in}(p_l, <_{a_l-1})$ is inside $p_l$ in the $a_l-1$ order.
-Specifically, the last supporting vertex of $q$ is strictly less than $j_m$.
-By Lemma \ref{lem no fourth vertex}, $q$ does not contibute its last supporting vertex to $I_i$.
-That is, $I_i(q) <j_m$.
-\hlfix{But this implies that $q$ contributed before $p_m$, which contradicts the hypothesis.}{Seems to demand that $I_i$ catches all propagators in a single circuit of the vertices.
-Is this explicit anywhere, or am I jumping the gun?}
+Let $Q:= \lim_{l\rightarrow \infty} Q_l$; by the above, this is well-defined and contained in $\cP_{m-1}$.
+We can now show that $J$ is a dependent set, by constructing a subset $U \subseteq J$ that satifies $|\Prop(U)| < |U|$.
 
-By construction, this implies that $V \subset \Prop(j_m)$. But $V$ contains the vertices 
-Since $J_{m-1}$ is independent, $V \subset J_{m-1}$ is too. Therefore, $|V| \leq |\Prop(V)| $. Since  $\Prop (V) \subset \cP_{m-1}$
-***************
-For the second point, consider the matrix $C(W)$ associated to the diagram $W$.
-Recall that $C(W)$ is only defined up to an ordering of the propoagators of $W$.
-Therefore order them according to the ordering induced by the algorithm for $I_i$.
-Write $\cP = \{p_1, \ldots , p_k\}$.
-That is, $p_i$ defines the $i^{th}$ row of $C(W)$.
-
-Write $I_i(p_j)=a_j$.
-By algorithm \ref{alg:put GN on WLD}, $a_j$ is the smallest number in the $<_{a_{j-1}}$ ordering such that $c_{j, a_j} \neq 0$ (that is, is an indeterminant entry).
-It is the first column in the $j^{th}$ row of $C(W)$ that is both non-zero and is greater than the index contributed by the previous propagator:  \bas \begin{bmatrix}\ddots & & & & & & \\ \ldots  & c_{j-1, a_{j-1}} & * & \ldots &  & & \\  \ldots  &* &0 & \ldots & 0 &c_{j, a_j} & \ldots \\ & & & & & & \ddots \end{bmatrix}  \eas
-
-Let $J = (j_1,\ldots j_k)$ be a sequence that is lexicographically less than $I_i = (a_1 \ldots a_k)$: $J <_i I_i$.
-By the above, for some $m < k$, $j_m <_i a_m$ and the matrix entry $c_{m, j_m} = 0$ is $0$.
-Without loss of generality, let $m$ be the smallest $m$ in the $<_i$ order for which this is true: \bas \forall l <m, \; I_i(p_l) = j_l \; ; \; j_m < I_i(p_m) \;.\eas Write $J_m = (j_1, \ldots, j_m)$ indicate the first $m$ entries of $J$.
-
-We claim that the $j_m^{th}$ column of $C(W)$ is in the span of the columns indexed by $J_{m-1}$.
-
-Since $J_{m-1}$ is an independent set in $C(W)$, row reduce the first $j_{m-1}$ columns of $C(W)$ to have $1$ in the $(r, j_r)$ position and $0$ to the right: \bas \begin{bmatrix}1 &0  &\ldots  & &  &0 \\  * & \ldots  & * & 1 & 0&\ldots \\    &\ddots &  &  &\ldots & 1 \\  *&* &* &\ldots &* &* \\  &\ddots & & & \ddots &  \\ *&* &* &\ldots &* &*  \end{bmatrix}  \;.\eas \sanote{fix this!
-wrote echelon order!}
-
-Next consider the $j_m^{th}$ column of $C(W)$.
-First note that, since $c_{m, j_m} = 0$.
-Furthermore, no $q$ that follow $p_m$ in the ordering can be supported on $j_m$.
-Since $j_m < a_m$, the algorithm for $I_i$ checks this vertex before $a_m$.
-If any propagators remain to be supported on this vertex after the removal of $p_1$ to $p_{m-1}$, then this propapagator would preceed $p_m$.
-Therefore, the only non-zero entries in column $j_m$ of $C(W)$ lie in the first $m-1$ rows.
-\sanote{add something here} Therefore, column $j_m$ lies in the span of the first $j_{m-1}$ columns of $C(W)$.
-
-*******
-%If $p, q \in \Prop(i)$ are two propagators supported on the vertex $i$, we may write $p = (a_p, b_p)$ and $q = (a_q, b_q)$, with the initial vertices $a_p$ and $a_q$ in the set $\{i, i-1\}$.
-By construction, the propagator $q$ is located clockwise relative to $p$ if and only if $p$ is inside $q$.
-That is, $p \in \cP_{in}(q, <_{a_q})$.
-
-%For $m < k$, write $\cP_m =\{p_1, \ldots , p_m\} \subset \cP$ to indicate the first $m$ propagators.
-For any subset of propagators $Q \subset \cP$, write $W|_Q = (Q, [n])$ be the subdiagram of $W$ consisting only of the propagators in $Q$ and all the vertices $[n]$.
-
-%Since $p$ never contributes its last vertex in the $<_i$ order to $I_i$, by Lemma \ref{lem no fourth vertex}, every propagator preceeding $p_j$ is outside it in the $a_j-1$ ordering: $\cP_{j-1} \subset \cP_{out}(p_j)$.
-
-We claim that $J_m$ is not a basis for $W|_{\cP_m}$.
-To see this, first note that, since $c_{m, j_m} = 0$, the propagator $p_m$ is not supported on $j_m$.
-If $p_m$ does not share support with any propagator in $\cP_m$ in the cyclic interval $[i, j_m]$, then the minor of $C(W|_{\cP_m})$ defined by $J_{m}$, has a row of $0$s.
-
-Otherwise, let $p_l$ be a propagator preceeding $p_m$ ($p_l \in \cP_{m-1}$) that shares support with it in $J_m$: $V(p_l) \cap V(p_m) \cap J_m \neq \emptyset$.
-Then $p_l \in Q$ is positioned clockwise to $p_m$ on vertex $a_l$, therefore, $p_l$ is outside $p_m$ in the $a_l -1$ order.
-Since $a_l <_i j_m <_i a_m$ with $a_l$ and $a_m$ both in the support of $p_m$, \hlfix{$j_m$ is inside $p_m$ in the $a_l-1$ ordering.
-}{I know we got rid or interior vertices.
-Can we bring it back or rephrase?} Furthermore since all of $\cP_{m-1} \subset \cP_{out}(p_m)$ is outside of $p_m$ in that $a_l-1$ order, and $j_m$ is a vertex inside it, no propagator prior to $p_m$ can be supported on $j_m$.
-Otherwise, one would have crossing propagators.
-Therefore, the minor of $C(W|_{\cP_m})$ defined by $J_{m}$, has a column of $0$s.
-******
-\end{comment}
-\end{proof}
-}
-
-We can now unambiguously refer to Algorithm~\ref{alg:put GN on WLD} as the Grassmann necklace algorithm.
-We close this section with a simple observation about the Grassmann necklaces of positroids associated to Wilson loop diagrams.
-
-In an arbitrary Grassmann necklace, it is possible for an index $i$ to appear in no terms of the Grassmann necklace (a {\em loop}) or in all terms of the necklace (a {\em coloop}).
-Using Theorem~\ref{res:alg gives GN}, a characterization of the loops and coloops of the Grassmann necklace associated to a Wilson loop diagram follows easily.
-
-\begin{cor}\label{no coloops}\sanote{cite more prominently in frontmatter}
-Grassmann necklaces coming from admissible Wilson loop diagrams have no coloops. A vertex $j$ is a loop if and only if $j$ supports no propagators. 
-\end{cor}
-\begin{proof}
-For any $i \in [n]$, $i-1$ is maximal with respect to the $<_{i}$ order and so by Lemma~\ref{lem no fourth vertex} there can be no propagator $p$ with $I_{i}(p) = i-1$.
-Thus $i-1 \not\in I_{i}$, so $i-1$ is not a coloop.
-Since this holds for any $i \in [n]$, the Grassmann necklace admis no coloops.
-
-If $j \in [n]$ is a loop then in particular we have $j \not\in I_j$, which can only happen if there are no propagators supported on vertex $j$.
-Conversely, if $j$ supports no propagators, then Algorithm~\ref{alg:put GN on WLD} never assigns a propagator to $j$ and hence $j \not\in I_i$ for all $i \in [n]$.
+Specifically, we take $U = I_i(Q) \cup \{j_m\}$.
+This is a subset of $J$ because $I_i$ and $J$ agree on their first $m-1$ terms and $Q \subseteq \cP_{m-1}$.
+Further, we have $j_m \not\in I_i(Q)$, so $|U| = |I_i(Q)| + 1 = |Q| +1$.
+On the other hand, since $\Prop(j_m) \subseteq Q$, we have
+\[\Prop(U) = \Prop(I_i(Q)) \cup \Prop(j_m) = Q\]
+by the construction of $Q$, and hence $|\Prop(U)| = |Q| < |U|$. Thus $J$ is a dependent set, and the Grassmann necklace $(I_1,\dots,I_n)$ constructed from $W$ does indeed define the positroid $M(W)$.
 \end{proof}
 
-\section{Dimension of the Wilson Loop cells}\label{sec dim}
+\newpage
 
-Our next goal is to show that the dimension of the positroid cell defined by a Wilson loop diagram $(\cP, [n])$ has dimension $3|\cP|$ (Theorem \ref{thm dim}).
-The positroid cells associated to the Amplituhedron are of dimension $4|\cP|$.
-In \cite{non-orientable}, Marcott and the first author show that the dimension of the Deodhar component is $|\cP| +$ the dimension of associated positroid cell.
-In otherwords, the Deodhar component associated to a Wilson loop diagram is $4|\cP|$, showing that the geometry underlying the Wilson loop diagrams is consistent with the geometry underlying the Amplituhedron.
+Half-written induction step:
 
-Marcott in \hlfix{***cite this***}{highlighted for anyone skimming through} has a different proof of the dimension of the positroid cell assicated to a Wilson loop diagram, which is geometric and more elegant, but it is not easy to track the effect of a particular propagator.
-Our approach is much more explicit.
+Before proceeding with the induction, we make an observation about the configuration of propagators in $W$: given that $\Prop(j_m) \subseteq \cP_{m-1}$, we either have a propagator $r$ as in Cases 1 or 2 below, or we are in Case 3.
 
-Recall that the dimension of a positroid cell is equal to the number of plusses in the associated Le diagram \cite[Theorem 6.5]{Postnikov}.
-By combining Algorithms~\ref{alg:put GN on WLD} and \ref{alg:GN to Le} (converting from WLD to Grassmann necklace to Le diagram) we explicitly describe the effect of adding another propagator to a Wilson loop diagram in terms of the plusses of the associated Le diagrams, and hence give a recursive proof of the $3|\cP|$-dimensionality of the cells.
+\vspace{3cm}
 
-We start with several lemmas, of roughly increasing degree of technicality.
-Lemma \ref{lem uncovered} shows that non-supporting vertices corresopond to columns of $0$s in the associated Le diagram.
-The proof of Theorem \ref{thm dim} depends on being able to act on Wilson loop diagrams by elements of the dihedral group to position propagators in certain positions.
-Lemma \ref{lem dihedral} shows that the dihedral group action does not change the dimension of of the associated Le diagram.
+In Cases 1 and 2, let $r$ be the outermost of such propagators. In Case 3, we repeat the analysis with earlier vertices:
 
-\begin{lem}\label{lem uncovered}
+\vspace{3cm}
 
-Let $W$ be an admissible Wilson loop diagram with $k$ propagators, and with a vertex $i$ that supports no propagators.
-Let $V$ be $W$ with vertex $i$ removed.
-Then the Le diagram of $W$ is obtained from the Le diagram of $V$ by inserting an extra column containing all $0$s in position $i$ (i.e.
-such that the new column has the label $i$).
-\end{lem}
+Eventually we either reach the starting vertex $i$ (in which case the sequence stabilizes at $Q_l = \cP_{m-1}$), or we reach some index $l_0$ such that $Q_{l_0} \subseteq \cP_{m-1}$ and $Q_{l_0}$ admits a propagator $r$.
 
-\begin{proof}
-  By Algorithm~\ref{alg:put GN on WLD} the Grassmann necklace of $W$ is obtained from the Grassmann necklace of $V$ by duplicating the $i$th element of the Grassmann necklace of $V$ (shifting indices by $1$ for all indices greater than $i$), and incrementing all indices greater than $i$ by $1$ in each Grassmann necklace element.
-Formally, if $I_1^{V}, \ldots, I_{n-1}^{V}$ and $I_1^{W}, \ldots, I_n^{W}$ are the Grassmann necklaces of $V$ and $W$ respectively then
-  \[
-  I_j^{W} =
-  \begin{cases}
-    \{\ell \in I_j^{V} : \ell < i\} \cup \{\ell+1 \in I_j^{V} : \ell \geq i\} & \text{if $j\leq i$} \\
-    \{\ell \in I_{j-1}^{V} : \ell < i\} \cup \{\ell+1 \in I_{j-1}^{V} : \ell \geq i\} & \text{if $j > i$.}
-  \end{cases}
-  \]
+Thus the result is true for all $l \leq l_0$; now suppose that $Q_l \subseteq \cP_{m-1}$ for some $l \geq l_0$ and consider $Q_{l+1} = \Prop(I_i(Q_l))$.
 
-By Lemma~\ref{no coloops} we know that $i \not\in I_1^W$, and so $i$ must label a horizontal edge on the boundary of the Le diagram of $W$, i.e.
-it must be a column label.
-The shapes of the Le diagram of $V$ and $W$ are the same except for the insertion of this column since $I_1^*$ is the same for $V$ and $W$ except for the incrementation of the indices $\geq i$ in the transition from the necklace for $V$ to the necklace for $W$.
-\end{proof}
+Then $q$ is supported on some vertex $a_t$, with $a_t = I_i(p_t)$ for some $p_t \in Q_l$. If $q$ lies to the left of $p_t$, then $q$ must have been assigned before $p_t$, i.e. $q \in P_{m-1}$.
 
-\begin{lem}\label{lem dihedral}
-If two Wilson loop diagrams differ by a dihedral transformation then their Le diagrams have same number of plusses.
-\end{lem}
-\begin{proof}
-By \cite[Proposition 17.10]{Postnikov}, the dimension of a positroid (and hence the number of plusses in its Le diagram) is $k(n-k) - A(\pi_W)$, where $A(\pi_W)$ denotes the number of alignments of the decorated permutation $\pi_W$ of the positroid associated to $W$.
-(See \cite[Figure 17.1]{Postnikov} and preceding discussion.)
-
-It can easily be seen from \cite[Section 17]{Postnikov} and Algorithm \ref{alg:put GN on WLD} that dihedral transformations of a Wilson loop diagram $W$ correspond to dihedral transformations of the chord diagram representation of $\pi_W$.
-Since the number of alignments in a chord diagram is preserved under dihedral transformations, the result follows.
-\end{proof}
-
-\begin{lem}\label{lem good p}
-  Let $W$ be an admissible Wilson loop diagram with $n\geq 1$ propagators.  Then there is some dihedral transformation $W'$ of $W$ such that $W'$ has a propagator $p$ with the following properties.
-  \begin{itemize}
-  \item $p = (i, n-1)$ for some $i$, and $p$ has no propagators inside it w.r.t the $<_i$ ordering (that is $i+2, \ldots, n-2$ do not support any propagators in $W'$).
-  \item Either the edge $i$ in $W'$ only supports $p$, or the edge $i$ in $W'$ supports exactly one other propagator $q = (j,i)$, with no other propagators inside $q$ in the $<_j$ ordering. 
-  \end{itemize}
-\end{lem}
-Note that since the first condition tells us that $p$ has nothing inside it then in the second condition if $q$ exists then $j<_ji<_jn-1$.
-
-\begin{proof}
-  Remove all vertices of $W$ which do not support any propagators to get a weakly admissible Wilson loop diagram $V$.
-Lemma~\ref{lem sian} applied to $V$ gives a length 2 propagator $p$ in $V$ for which either no other propagator is supported on one of the supporting edges of $p$ or there is a second length 2 propagator which is the only other propagator supported on one of the supporting edges of $p$.
-(Figure~\ref{fig 3 cases} shows the possible configurations arising from Lemma~\ref{lem sian}, and the reader can easily check that in each case $p$ must be in one of the two situations described above.)
-
-  We can now make a dihedral transformation of $V$ to obtain a diagram satisfying the statement of the lemma with $p$ and $q$ both length 2.
-Restoring the vertices which do not support any propagators, we obtain a dihedral transformation $W'$ of $W$ as desired (with potentially longer lengths for $p$ and $q$).
-\end{proof}
-
-Combining Lemmas \ref{lem uncovered}, \ref{lem dihedral}, and \ref{lem good p}, it therefore suffices to study the Le diagrams of weakly admissible Wilson loop diagrams with $F(\emptyset)  = \emptyset$, admitting one of the configurations described in Lemma \ref{lem good p} with propagators $p = (n-3, n-1)$ and $q= (n-5, n-3)$ (if $q$ exists) both of length 2.
-See Figure~\ref{fig special p} for an illustration of the two possibilities.
-
-The next few lemmas describe how diagrams of this type are related to the corresponding diagram with propagator $p$ removed, first in terms of the Grassmann necklaces (Lemma \ref{lem I}) and then in terms of the Le diagrams (Lemmas \ref{lem shape} to Lemma \ref{lem other k}) .
-These technical lemmas will form the backbone of the inductive step in the main dimensionality argument.
-
-\begin{lem}\label{lem I}
-Let $W$ be an admissible Wilson loop diagram with $n\geq 1$ propagators, and suppose that $W$ admits one of the configurations described in Lemma~\ref{lem good p}, with $p$ and $q$ (if $q$ exists) both of length 2.
-Let $V$ be $W$ with $p$ removed.
-Then
-
-  \begin{align*}
-    I_1^{W} & = I_1^{V} \cup \{n-3\} \\
-    I_n^{W} & = I_1^{V} \cup \{n\} \\
-    I_{n-1}^{W} & = I_n^{V} \cup \{n-1\} \\
-    I_{n-2}^{W} & =
-    \begin{cases}
-      I_{n-2}^{V}\cup \{n-2\} & \text{if $n-2\not\in I_{n-2}^{V}$} \\
-      I_{n-2}^{V}\cup \{n-1\} & \text{if $n-2\in I_{n-2}^{V}$, $n-1\not\in I_{n-2}^{V}$} \\
-      (I_{n}^{V} - \{n-5\})\cup \{n-1,n-2\} & \text{if $n-1, n-2\in I_{n-2}^{V}$}
-    \end{cases} \\
-    I_{k}^{W} & =
-    \begin{cases}
-      I_k^{V}\cup \{n-3\} & \qquad \qquad \qquad \qquad \text{if $n-3 \not\in I_k^{V}$}\\
-      I_k^{V}\cup\{n-2\} & \qquad \qquad \qquad \qquad \text{if $n-3\in I_k^{V}$}
-    \end{cases} \\
-    & \text{for $1<k<n-2$}
-  \end{align*}
-\end{lem}
-
-\begin{figure}
- \includegraphics{specialp}
-  \caption{The two cases for $W$ and $p$.  No other propagators can end in the fat red sections.  Other segments may have additional propagators ending in them.}\label{fig special p}
-\end{figure}
-
-\begin{proof}
-
-The two possible cases for $W$ are illustrated in Figure~\ref{fig special p}; all references to the ``left hand case'' or ``right hand case'' below refer to the diagrams in this figure.
-
-We first consider $I_1^{W}$, i.e.
-the set obtained by applying the Grassmann necklace algorithm to $W$ with starting vertex 1.
-Note that $n-3 \not\in I_1^{V}$: for the right hand case this is clear from the diagram (since Algorithm~\ref{alg:put GN on WLD} would assign $q$ no later than vertex $n-4$), while for the left hand case it follows from Lemma \ref{lem no fourth vertex}.
-Therefore when we start at vertex 1 and apply the Grassmann necklace algorithm to $W$, $p$ is the only remaining unassigned propagator when we reach vertex $n-3$, and so we have $ I_1^{W}(p) = n-3$ and $I_1^W = I_1^V\cup \{n-3\}$.
-
-Next consider $I_n^{W}$.
-From the figure we see that in both cases we have $I_n^{W}(p) = n$.
-At vertex 1 of the algorithm $I_n$, the unassigned propagators are exactly those that appear in $V$.
-Therefore the algorithm continues as in $I_1^{V}$ (recall Remark~\ref{rmk algorithm locally same} about locally identical propagator configurations), i.e.
-we have $I_n^{W} = I_1^{V} \cup \{n\}$.
-By a similar argument, we must have $I_{n-1}^{W} = I_n^{V} \cup \{n-1\}$.
-
-Now consider $I_{n-2}^{W}$.
-If $n-2\not\in I_{n-2}^{V}$ (i.e.
-$n-2$ supports no propagators in $V$), then $I_{n-2}^W(p) = n-2$ and this assignment of $p$ does not affect the rest of the construction of $I_{n-2}^{V}$, so we obtain $I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-2\}$ as above.
-
-On the other hand, if $n-2\in I_{n-2}^{V}$ then we must be in the right hand case of Figure~\ref{fig special p} and $I_{n-2}^V(q) = I_{n-2}^W(q) = n-2$ (since $q$ is always the clockwise-most propagator supported on vertex $n-2$; see Figure~\ref{fig special p}).
-If $n-1 \not\in I_{n-2}^{V}$, then $I_{n-2}^W(p) = n-1$ and then the algorithm proceeds identically to $I_{n-2}^{V}$ for the remainder of its steps; thus $I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-1\}$ in this case.
-
-Finally, if $n-2,n-1 \in I_{n-2}^{V}$ then $I_{n-2}^W(q) = n-2$ and $I_{n-2}^W(p) = n-1$ as above, but this is different to what occured in $I_{n-2}^{V}$ so we cannot use the same argument as above.
-When the algorithm $I_{n-2}^W$ reaches vertex $n$, the only propagators $p$ and $q$ have contributed; thus we proceed as in the construction of $I_n^{V}$ but without propagator $q$.
-By Lemma~\ref{vertex cyclic int lem} we know that $I_n^V(q) = n-5$, and from the diagram we see that the only way this could occur is if all other propagators in $V$ had already been assigned when we reached vertex $n-5$; thus $q$ was the final propagator to be assigned in $I_n^{V}$.
-Therefore $I_{n-2}^{W} = (I_{n}^{V} \setminus \{n-5\}) \cup \{n-1, n-2\}$ in this case.
-This completes all cases for $I_{n-2}^{W}$.
-
-The arguments for $I_k^{W}$ ($1< k < n-2$) proceed analagously to those of $I_{n-2}^{W}$, with one simplification: we cannot have both $n-3$ and $n-2$ in $I_k^{V}$ since $q$ is the only propagator that could be assigned to either of them, and it cannot be assigned to both.
-
-This covers all cases and hence completes the proof.
-\end{proof}
-
-\begin{figure}
-  \includegraphics{Le_diagrams}
-  \caption{Le diagrams for $V$ (left) and $W$ (right).}\label{fig Le}
-\end{figure}
-
-\note{When doing the final formatting, try to ensure that Figure \ref{fig Le} and Lemma \ref{lem shape} are on the same page}
-\begin{lem}\label{lem shape}
-  Let $V$ and $W$ be as in Lemma~\ref{lem I}.
-  The shape of the Le diagram of $V$ can be built from left to right of the following blocks: a rectangle which is 3 columns wide, one more column of the same height, and a partition shape with at most as many rows as the rectangle.
-  The shape of the Le diagram of $W$ can be built from left to right of the following blocks: a rectangle with 3 columns and one more row than the first rectangle of $V$, and the same partition shape as in $V$.
-\end{lem}
-
-\begin{proof}
-See Figure~\ref{fig Le} for an illustration of the shapes described in the statement of the lemma.
-
-Recall that $I_1$ determines the shape of the Le diagram: specifically, the elements of $I_1$ label the rows of the diagram, working from top right to bottom left.
-By the arguments in Lemma~\ref{lem I} we know that ${n,n-1,n-2, n-3 \not\in I_1^{V}}$ (which yields the leftmost four columns of the diagram for $V$) and that $I_1^{W} = I_1^{V}\cup \{n-3\}$.
-This implies that the right hand boundary of the shape of $V$ is the same as the right hand boundary of the shape of $W$ except that $W$ has one additional row of 3 boxes while $V$ has an additional column in the $n-3$ position; that is, an extra column fourth from the left.
-\end{proof}
-
-As illustrated in Figure~\ref{fig Le}, the pieces of the Le diagrams of $V$ and $W$ will be called $\mathcal{A}$ and $\mathcal{B}$ in what follows.
-\hlfix{Explicitly, $\mathcal{B}$ is the set of columns with labels $v < n-3$ and $\mathcal{A}$ the set of columns labeled by $n$, $n-1$ and $n-2$ in $V$.
-In $W$, A consists of these columns without the last row.}{is this accurate?} Over the course of the next few lemmas we will prove that the plusses in the $\mathcal{B}$ parts of each diagram are identical, and that the relationship between the plusses in the $\mathcal{A}$ regions can be described explicitly.
-
-We do this by applying Algorithm~\ref{alg:GN to Le}, which constructs the Le diagram associated to a Grassmann necklace, to the Grassmann necklaces of $V$ and $W$.
-As described in Section~\ref{sec:positroid background}, if Algorithm~\ref{alg:GN to Le} places a $+$ in the box with row index $i$ and column index $j$, we say that this plus is in the $i \rightarrow j$ position, and refer to it as the plus defined by ``the (hook) path from $i$ to $j$''.
-Note that the collection of paths contributed by a single Grassmann necklace term  must be non-crossing.
-
-Finally, we also note that when we speak of a plus in the Le diagram of $V$ being the same as in $W$ or vice versa, we mean that the position of the plus in $\mathcal{A}$ or $\mathcal{B}$ is the same; because of the column insertion the absolute indices may differ.
-
-\begin{lem}\label{lem n and n-1}
-Let $V$ and $W$ be as in Lemma~\ref{lem I}.
-Then $I_n^{W}$ and $I_{n-1}^{W}$ together yield the same plusses as $I_n^{V}$ did, along with two extra plusses which appear in the leftmost two boxes of the bottom row of the Le diagram of $W$.
-\end{lem}
-
-\begin{proof}
-By Lemma~\ref{lem I} we have $I_n^{W}= I_1^{V} \cup \{n\}$ and $I_1^{W} = I_1^{V} \cup \{n-3\}$. Thus 
-\[I_1^{W} \setminus I_n^{W} = \{n-3\}, \qquad \qquad I_n^{W} \setminus I_1^{W} = \{n\},\]
-and so by Algorithm~\ref{alg:GN to Le} we have a plus in the $(n-3) \rightarrow n$ position, i.e. in the leftmost box of the bottom row.
-
-Also by Lemma~\ref{lem I} we have $I_{n-1}^{W} = I_n^{V} \cup \{n-1\}$.
-Recall from the proof of Lemma~\ref{lem I} that $n-3,n-2,n-1,n \not\in I_1^V$; therefore $I_1^W\setminus I_{n-1}^W = (I_1^V \setminus I_n^V) \cup\{n-3\}$, and $n-3$ is maximal in this set.
-Similarly,
-\[I_{n-1}^W \setminus I_1^W = (I_n^V \setminus I_1^V) \cup \{n-1\} \subseteq \{n-1,n\},\]
-where the final inclusion follows from the definition of Grassmann necklace.
-In particular, $n-1$ is minimal in this set, so Algorithm~\ref{alg:GN to Le} yields a plus in the $(n-3) \rightarrow (n-1)$ position (i.e.
-the second box in the bottom row of the Le diagram of $W$) along with any plusses yielded by $I_n^V$.
-\end{proof}
-
-\begin{lem}\label{lem n-2 good}
-  Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that $n-2 \not\in I_{n-2}^{V}$.
-Then $I_{n-2}^{W}$ contributes all of the same plusses as $I_{n-1}^{V}=I_{n-2}^{V}$, along with a new $(n-3)\rightarrow (n-2)$ plus.
-\end{lem}
-
-\begin{proof}
-If $n-2\not\in I_{n-2}^{V}$ then $I_{n-1}^{V}=I_{n-2}^{V}$ by definition, and by Lemma~\ref{lem I} we have $I_{n-2}^{W} = I_{n-1}^{V} \cup \{n-2\}$.
-Note that $n-3\not\in I_{n-2}^{V}$ by Lemma~\ref{lem no fourth vertex}.
-Therefore the paths controlling the plusses contributed by $I_{n-2}^{W}$ are exactly the paths for $I_{n-1}^{V}$ along with the $(n-3)\rightarrow (n-2)$ path.
-This gives the statement of the lemma.
-\end{proof}
-
-\begin{lem}\label{lem n-2 bad}
-Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that $n-2,n-1 \in I_{n-2}^{V}$. Then:
-  \begin{enumerate}
-  \item $I_{n-2}^W$ contributes an $(n-3)\rightarrow (n-2)$ plus and an $(n-5)\rightarrow (n-1)$ plus, along with any plusses contributed by $I_n^V$.
-  \item $I_{n-3}^W$ contributes the same plusses as $I_{n-3}^V$, except that the plus in the $n-3$ column (which necessarily exists) is shifted one square left into the $n-2$ column.
-  \item In the Le diagram of $V$, $I_{n-2}^{V}$ contributes an $(n-5)\rightarrow (n-2)$ plus and no other term in the Grassmann necklace of $V$ gives a plus in this column.
-$I_{n-2}^W$ does not contribute this $+$ but yields the $(n-5)\rightarrow (n-1)$ plus from point (1) instead.
-  \item All other plusses from $I_{n-2}^{V}$ and all plusses from $I_{n-1}^V$ were already contributed by $I_{n-3}^V$, so they yield no new information.
-  \item No element of the Grassmann necklace of $V$ contributes a $(n-5)\rightarrow (n-1)$ plus.
-  \end{enumerate} 
-\end{lem}
-
-\begin{proof}
-  By Lemma~\ref{lem I} we have $I_{n-2}^{W}= (I_{n}^{V} \setminus \{n-5\})\cup \{n-1,n-2\}$ and $I_1^W = I_1^V\cup \{n-3\}$.
-We are necessarily in the case where $W$ admits a propagator $q$ (the right hand case of Figure~\ref{fig special p}) and we can see from the location of $q$ that $n-2\not\in I_{n-3}^{V}$ and that $n-5$ is the label of the last row in $\mathcal{B}$.
-Also note that by Lemma~\ref{vertex cyclic int lem} and Corollary~\ref{no coloops} we must have $n\in I_n^V$.
-Thus this section of the Grassmann necklace of $V$ looks like
-
-  \begin{equation}\label{eq necklace}
-  I_{n-3}^{V} \xrightarrow[\substack{n-3\text{ out}\\n-2\text{ in}}]{} I_{n-2}^{V} \xrightarrow[\substack{n-2\text{ out}\\n-5\text{ in}}]{} I_{n-1}^{V} \xrightarrow[\substack{n-1\text{ out}\\\text{something in}}]{} I_{n}^{V}  \xrightarrow[\substack{n \text{ out}\\\text{something in}}]{} I_1^{V}
-  \end{equation}
-  where the first ``something'' is either $n$ or an element of $I_1^{V}$, and the second ``something'' is an element of $I_1^{V}$.
-
-  \begin{figure}
-    \includegraphics{messy}
-    \caption{Plusses coming from $I_{n-2}^{V}$ (left) and  $I_{n-1}^{V}$ (right), in the case where $n-1, n-2\in I_{n-2}^{V}$.
-The blue lines are the non-intersecting paths defining the position of the plusses.
-The dashed blue lines may or may not appear, but if one appears then they both do.}\label{fig messy}
-  \end{figure}
-
-  Using this information we can determine the symmetric difference of $I_{n-2}^{V}$ and $I_1^{V}$.
-Note that $I_{n-2}^V\setminus I_1^V$ and $I_1^V\setminus I_{n-2}^V$ each have size $\leq 3$ by the definition of a Grassmann necklace.
-We have $n-1, n-2 \in I_{n-2}^{V} \setminus I_1^V$ for certain, and the third element (if it exists) must be $n$.
-On the other hand we have $n-5 \in I_1^{V} \setminus I_{n-2}^V$, along with at least one and at most two other elements.
-If there is one such element call it $a$.
-If there are two call them $a$ and $b$ with $a>b$.
-
-  This means that the plusses in the Le diagram of $V$ coming from $I_{n-2}^{V}$ are as in the first part of Figure~\ref{fig messy}.
-Stepping to $I_{n-1}^{V}$ simply removes the $(n-5)\rightarrow (n-2)$ path (second part of Figure~\ref{fig messy}), so $I_{n-1}^V$ contributes no new information about the Le diagram of $V$.
-
-  %Stepping to $I_{n}^{V}$, $n-1$ is removed and either $n$ is put in if it was not there before, or one of $a$ or $b$ is put in and hence is no longer available as the starting point for a path.
-This gives two possible configurations illustrated in the bottom two parts of Figure~\ref{fig messy}.
-
-  With this information in hand, we can now tackle the points in the statement of the lemma. We know that 
-  \[I_{n-2}^{W}  = (I_{n}^{V} - \{n-5\})\cup \{n-1,n-2\}, \quad n-5 \in I_1^W, \quad n-3\not\in I_{n-2}^W,\]
- and so the paths for building plusses from $I_{n-2}^{W}$ start at
- \[I_1^W \setminus I_{n-2}^W = \{n-3,n-5\} \cup (I_1^V \setminus I_n^V)\]
- and end at
- \[I_{n-2}^W \setminus I_1^W = \{n-2,n-1\}\cup(I_n^V \setminus I_1^V).\]
-This means that $I_{n-2}^W$ contributes plusses as in Figure~\ref{fig messyD}, while $I_n^V$ contributes as in the bottom line of Figure~\ref{fig messy}, which proves point (1) and most of point (3).
-From equation \eqref{eq necklace} we see that $n-2$ appears only in $I_{n-2}^V$, so no other Grassmann necklace term for $V$ can contribute a plus in the $n-2$ column; this completes the proof of item (3).
-
-  \begin{figure}
-     \includegraphics{messyD}
-    \caption{Plusses coming from $I_{n-2}^{W}$.}\label{fig messyD}
-  \end{figure}
-
-Now consider $I_{n-3}^{V}$.
-By \eqref{eq necklace} $I_{n-3}^{V}$ contributes almost the same plusses as $I_{n-2}^{V}$: the only difference is that it contributes an $(n-5)\rightarrow (n-3)$ plus in place of the $(n-5)\rightarrow (n-2)$ plus.
-Since we must have $n-3\in I_{n-3}^{V}$ (because the propagator $q$ exists in $V$), it follows from Lemma~\ref{lem I} that $I_{n-3}^{W} = I_{n-3}^{V}\cup\{n-2\}$.
-Thus the paths for $I^{W}_{n-3}$ are the same as those for $I^{V}_{n-3}$ except that the path that did go to $n-3$ now goes to $n-2$.
-This cannot conflict with another path since \eqref{eq necklace} shows that $n-2$ only appears in $I_{n-2}^{V}$ among the necklace elements of $V$.
-
-This proves point (2), and combined with the observation above that $I_{n-1}^V$ contributes no new plusses compared to $I_{n-2}^V$, we also obtain item (4).
-
-  Finally, if the Le diagram of $V$ did admit a $(n-5)\rightarrow (n-1)$ plus, it could only have been contributed by a necklace term that doesn't contain $n-5$.
-By equation \eqref{eq necklace} the only terms that could have this property are $I_{n-2}^{V}$, $I_{n-3}^{V}$, and $I_{n-4}^{V}$, and the analysis above shows that $I_{n-2}^V$ and $I_{n-3}^V$ do not contribute a plus in this position.
-
-  Recall that $n-5$ is the largest row index in the Le diagram of $V$, and $n-5 \in I_1^V \setminus I_{n-4}^V$ so $I_{n-4}^V$ does contribute a path starting at $n-5$.
-Since $n-4 \in I_{n-4}^V$ by the location of the propagator $q$, we must also have a path ending at $n-4$.
-Since the paths cannot cross, this implies that $I_{n-4}^V$ must contribute a $(n-5) \rightarrow (n-4)$ plus, and hence cannot contribute a $(n-5)\rightarrow (n-1)$ plus.
-This proves point (5) and completes the proof of the lemma.
-\end{proof}
-
-\begin{lem}\label{lem other k}
-  Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that if $n-2\in I_{n-2}^{V}$ then $n-1\in I_{n-2}^{V}$ also.
-Then for each $k$ in the range $1<k<n-2$, $I_k^{W}$ contributes the same plusses as $I_{k}^{V}$, except that if $I_{k}^{V}$ contributed a plus in the $n-3$ column of the Le diagram of $V$ then this plus is shifted one square left in the Le diagram of $W$, and no plus was already in that location in the Le diagram of $W$.
-\end{lem}
-
-\begin{proof}
-Recall that $I_1^W = I_1^V\cup \{n-3\}$ and that $n-2,n-1,n \not\in I_1^W$.
-
-  If $n-3\not\in I_{k}^{V}$ then by Lemma~\ref{lem I} we have $I_{k}^{W} = I_k^{V}\cup \{n-3\}$.
-Then since $n-3$ is the largest element of $I_1^{W}$ this transformation leaves the disjoint paths unchanged and so the plusses carry over from $V$ to $W$ directly.
-
-  If $n-3\in I_{k}^{V}$ then $I_k^V$ must contribute a plus in the $n-3$ column of the Le diagram of $V$, and by Lemma~\ref{lem I} we have $I_{k}^{W} = I_k^{V}\cup \{n-2\}$.
-If $n-2$ supports no propagators in $V$ then certainly no pluses appear in the $n-2$ column of the Le diagram of $V$.
-If $n-2$ supports at least one propagator in $V$ then $n-2 \in I_{n-2}^V$ and so by hypothesis $n-1 \in I_{n-2}^V$ as well.
-By Lemma~\ref{lem n-2 bad}, the only necklace element of $V$ containing $n-2$ is $I_{n-2}^{V}$ and the corresponding plus is not contributed to the Le diagram of $W$ by $I_{n-2}^{W}$.
-
-  Since $n-3 \in I_k^V \setminus I_1^V$, we must have a path from some vertical edge $i$ to the bottom edge $n-3$ in the Le diagram of $V$.
-In the Le diagram of $W$, the index $n-3$ labels a vertical edge with no path starting at it (since $n-3$ belongs to both $I_1^W$ and $I_k^W$), and there must be a path leading to $n-2$ since $n-2 \in I_k^W \setminus I_1^W$.
-By the previous paragraph no other path from $I_k^V$ could end at $n-2$, and since the paths cannot cross we conclude that the $i\rightarrow (n-3)$ path in the Le diagram of $V$ must become a $i\rightarrow (n-2)$ path in the Le diagram of $W$.
-All other paths are unchanged.
-
-   Thus the plus contributed by $I_k^V$ in the $n-3$ column of the Le diagram of $V$ is shifted into the $n-2$ column in the Le diagram for $W$, where there was no plus before, and no other plusses are changed.
-\end{proof}
-
-We are now ready to prove the main result of this section, showing that the dimension of the positroid cell associated to each Wilson loop diagram is $3|\cP|$.
-
-\begin{thm}\label{thm dim}
-  The number of plusses in the Le diagram of an admissible Wilson loop diagram is three times the number of propagators.
-\end{thm}
-
-\begin{proof}
-  The proof is by induction on the number of propagators.
-
-  First note that a Wilson loop diagram $W$ with one propagator supported on vertices $i<j<k<\ell$ has Le diagram a single row with $|W|-i$ boxes.
-Labelling the columns from left to right by $|W|, \ldots, |W|-i+1$, by the algorithm there are plusses in the $j$, $k$, and $\ell$ positions.
-
-  Now consider Wilson loop diagrams with $k>1$ propagators.
-By Lemma~\ref{lem uncovered} it suffices to prove the result for weakly admissible Wilson loop diagrams with $k$ propagators and no non-supporting vertices.
-By Lemma~\ref{lem dihedral} it suffices to prove the result for at least one Wilson loop diagram from each dihedral orbit.
-Take a weakly admissible Wilson loop diagram $W$ with $k$ propagators and no non-supporting vertices.
-Make a dihedral transformation of $W$ if necessary so that $W$ has a propagator $p$ with the properties in Lemma~\ref{lem good p}.
-
-  We make one further simplification: if our $W$ is in Case 2 of Figure~\ref{fig special p} and $n-1$ supports only $p$ but $n-2$ supports at least one other propagator, then flip $W$ on the line perpendicular to the $(n-2)^{th}$ edge to obtain a diagram with the configuration of Case 1.
-This eliminates the possibility that we could have $n-2 \in I_{n-2}^W$ but $n-1 \not\in I_{n-2}^W$.
-
-  This diagram will be our $W$ for the remainder of the proof. Let $V$ be $W$ with $p$ removed.
-
-  From Lemma~\ref{lem shape} we know how the shapes of the Le diagrams of $V$ and $W$ are related; let $\mathcal{A}$ and $\mathcal{B}$ be as described above.
-Lemmas~\ref{lem n and n-1}, \ref{lem n-2 good}, and \ref{lem n-2 bad} tell us that the three boxes of the bottom row of the Le diagram of $W$ each have a plus.
-Lemmas~\ref{lem n and n-1} through \ref{lem other k} show that there is a bijection between the plusses of the Le diagram of $V$ and the plusses of the Le diagram of $W$ that are not in the bottom row.
-This bijection can be described as follows:
-  \begin{itemize}
-  \item All plusses from $\mathcal{B}$ for $V$ maintain their positions in $\mathcal{B}$ for $W$.
-  \item All plusses from the leftmost two columns (the $n$ and the $n-1$ columns) of $\mathcal{A}$ for $V$ maintain their positions in $\mathcal{A}$ for $W$.
-  \item If there is a plus in the $n-2$ column of $\mathcal{A}$ in $V$ then Lemma~\ref{lem n-2 bad} applies, so there is exactly one such plus.
-This plus is mapped to the $(n-5)\rightarrow (n-1)$ plus for $W$.
-  \item All plusses in the $n-3$ column for $V$ are shifted one square to the left in $\mathcal{A}$ for $W$, i.e. into the $n-2$ column.
-  \end{itemize}
-  Note that this map is reversible and hence bijective.
-Indeed, the only possible ambiguity is at the $(n-5)\rightarrow (n-1)$ plus in $W$ (if it exists), which could have come from either of the first or third bullet points.
-However, if the third bullet point applies then by Lemma~\ref{lem n-2 bad} there is no $(n-5)\rightarrow (n-1)$ plus in $V$, i.e.
-the first bullet point does not apply.
-
-  % If the Le diagram for $V$ has a plus in the $n-2$ column then Lemma~\ref{lem n-2 bad} applies.
-By the final part of Lemma~\ref{lem n-2 bad} there is no $n-5\rightarrow n-1$ plus in the Le diagram of $V$, and so the $n-5\rightarrow n-1$ plus of $W$ can be uniquely mapped to the plus in the $n-2$ column of the Le diagram of $V$.
-If the Le diagram for $V$ has no plus in the $n-2$ column, then leave the $n-5\rightarrow n-1$ plus where it is in moving back to $V$.
-This reverses the map.
-
-Therefore the Le diagram of $W$ contains $3(k-1)$ plusses in bijection with the plusses from the Le diagram of $V$ and 3 new plusses in the bottom row, yielding $3k$ in total.
-Applying induction completes the proof.
-\end{proof}
-
-\section{Poles of Wilson Loop Integrals}\label{sec poles}
-
-In this section, we investigate the poles of the integrand for $I(W)$, that is $R(W)$ as defined in Definition~\ref{def R(W)}.
-It is conjectured that for a fixed number of propagators and a given set of external twistors $\cZ$, [cite] \bas \sum_{W | |\cP| = k} I(W)(\cZ) <\infty \;.\eas In otherwords, all poles of the intergrals must cancel.
-As a step towards this, in this section, we prove some results about $R(W)$.
-
-The results of Section~\ref{sec GN algorithm} allow us to relate the position of propagators in a Wilson loop diagram $W$ to minors of $C(W)$, $R(W)$.
-
-The main result of this section is Theorem~\ref{thm denom}, which expresses the denominator $R(W)$ in terms of the Grassmann necklace of $W$.
-This simplifies the computation of $R(W)$ and allows us to directly relate the poles of the integral to the combinatorics of the diagram.
-
-We first give an algorithm which extracts the required minors from the Grassmann necklace.
-
-\begin{algorithm}\label{alg WLD to denom via GN}
-Let $W = (\cP,n)$ be a Wilson loop diagram, and let $C(W)$ be the matrix of $W$ as defined in \eqref{C(W) dfn} with a fixed ordering on $\cP$. (see Section~\ref{section WLD background}).
-\begin{itemize}
-  \item For each $i \in [n]$, we construct a factor $r_i$ as follows:
-    \begin{itemize}
-      %\item Use Algorithm~\ref{alg:put GN on WLD} to obtain a bijection between the propagators and the $i-1$st Grassmann necklace element, $I_{i-1}$.
-(By convention set $I_{-1}=I_n$.)  Write $I_{i-1}(p)$ for the vertex associated to propagator $p$ under this bijection.
-      %\item Use Algorithm~\ref{alg:put GN on WLD} to obtain a bijection between the propagators and the $i$th Grassmann necklace element, $I_{i}$.
-Write $I_{i}(p)$ for the vertex associated to propagator $p$ under this bijection.
-      \item Let $S_i = \{p \in \cP \ | \ I_{i-1}(p) \neq I_i(p)\}$. (By convention, set \hlfix{$I_{0} = I_n$}{changed. correct?}.)
-	  %\item Write $\Delta_{I_i}$ for the determinant of the $k \times k$ minor of $C(W)$ with columns indexed by $I_i$.
-      \item Let $r_i$ be the determinant of the $|S_i|\times |S_i|$ minor of $C(W)$ with rows indexed by $S_i$ and columns indexed by $I_i(S_i)$.
-%$\Delta_{I_i}$ with all variables from rows associated to $p\not\in S_i$ set to $1$.
-    \end{itemize}
-  \item Define $R = \prod_{i=1}^n r_i$.
-\end{itemize}
-\end{algorithm}
-
-\hlfix{That is, each $r_i$ is the determinant of the minor determined by the propagators (rows) that contribute different values (columns) to the $i^{th}$ element of the Grassmann necklace than they did to the $i-1^{th}$.}{added.
-accurate?}
-
-As we discuss the algorithm it will also be useful to have the notation $\Delta_{I_i}$ for the determinant of the $k\times k$ minor of $C(W)$ with columned indexed by $I_i$.
-
-As we take each $r_i$ to simply be the determinant of a particular submatrix of $C(W)$, the sign of each $r_i$ is well-defined.
-Before proving the main results of this section, we given an illustrative example.
-Below, we show that $R$ is equal to the denominator of the Wilson loop diagram as defined in Definition~\ref{def R(W)}, and is the radical of the product $\prod_{i=1}^n \Delta_{I_i}$.
-%  However, we will not be interested in these signs as they only contribute an overall sign to $R$ and our main theorem in this section (Theorem~\ref{thm denom}) will simply be to show that $R$ is equal up to a $\mathbb{Q}$-multiple to the denominator of the Wilson loop diagram (see Definition~\ref{def R(W)}).
-
-\begin{figure}
-\includegraphics{egWLD_forR}
-\caption{Example WLD for illustrating Algorithm~\ref{alg WLD to denom via GN} and bijections between propagators and vertices for each Grassmann necklace element.}\label{fig R eg}
-\end{figure}
-
-\begin{eg}
-Consider the Wilson loop diagram in Figure~\ref{fig R eg}. Assigning propagators $p$, $q$, $s$\todo{$s = r$ in pictures} to rows $1,2,3$ respectively, we obtain the matrix
-\[
-C(W) = \begin{bmatrix} a & b & 0 & 0 & 0 & c & d \\ e & f & 0 & 0 & g & h & 0 \\ i & j & 0 & k & l & 0 & 0 \end{bmatrix}
-\]
-The Grassmann necklace of this diagram is 
-\begin{gather*}I_1 = \{1,2,4\}, I_2 = \{2,4,5\}, I_3 = \{4,5,6\}, I_4=\{4,5,6\},\\ I_5=\{5,6,7\}, I_6 = \{6,7,1\}, I_7=\{7,1,2\}. \end{gather*}  
-Figure~\ref{fig R eg} indicates the pairings between propagators and vertices for each $i \in [1,7]$.
-
-From $I_1$ to $I_2$, the propagators $p$ and $q$ change \hlfix{which vertex they are assigned to}{Can we change this language to which vertices they contribute?}.
-That is $I_1(p) = 1$, $I_1(q)= 2$ while $I_2(p) = 2$, $I_2(q)= 5$.
-However, $r$ contributes  4 to both $I_1$ and $I_2$, so $S_2 = \{p,q\}$.
-Then
-\[
-\Delta_{I_2}=\det\begin{bmatrix} b & 0 & 0 \\ f & 0 & g \\ j & k & l \end{bmatrix} = kgb, \qquad r_2 = \det\begin{bmatrix} b & 0 & 0 \\ f & 0 & g \\ 1 & 1 & 1 \end{bmatrix} = gb.
-\] {\color{violet} shouldn't $r_2$ be a $2 \times 2$ matrix? i.e. $r_2 = \det\begin{bmatrix} b & 0 \\ f &  g \end{bmatrix} = gb.$}
-\hlfix{where the 1s in the third row of the second matrix correspond to the fact that $I_1(s) = I_2(s)$.}{This doesn't seem to match with what is said in the algorithm.}  Continuing likewise, we get $r_3 = c$, $r_4=1$ (since $I_4 = I_3$), $r_5 = lhd$, and $r_6 = i$.
-
-At $I_7$ the situation \hlfix{is more complicated}{It seems to be exactly what we expect from the alg?}: we have $S_7 = \{q,s\}$ with $I_7(S_7) = \{ 1,2\}$, $\Delta_{I_7} = d(ej-fi)$ and $r_7 = ej-fi$.
-
-Note that unlike the previous $r_i$, $r_7$ an irriducible quadratic factor.
-This corresponds to the fact that $q$ and $s$ share an edge {\em and} contribute both endpoints of that edge to $I_7$; see Proposition~\ref{prop alg gives rad} below.
-
-Finally, we have $r_1 = (af-be)k$.  Putting everything together, we obtain
-\[
-R = (af-be)kgbclhdi(ej-fi)
-\]
-which is squarefree and contains all factors of $\prod_{i=1}^{n}\Delta_{I_i}$.
-If one were to construct the denominator $R(W)$ associated to this Wilson loop diagram as per Definition~\ref{def R(W)}, we would find that we have $R(W) = R$.
-\end{eg}
-
-We are now ready to begin proving the main result of this section. We begin with a proposition stating several facts about $\Delta_{I_i}$ and their relationship to $r_i$.
-
-\begin{prop}\label{prop alg gives rad}
-  With notation as in Algorithm~\ref{alg WLD to denom via GN} we have the following:
-  \begin{enumerate}
-    \item Each $\Delta_{I_i}$ is homogeneous, as is each $r_i$.
-    \item Each $\Delta_{I_i}$ splits into linear and quadratic factors.
-All linear factors of  $\Delta_{I_i}$ are single variables and all irreducible quadratic factors are $2\times 2$ determinants of single variables.
-    \item Quadratic factors in $\Delta_{I_i}$ arise precisely when propagators $p$ and $q$ are supported on a common edge $(a,b)$ with $I_i(p)=a$ and $I_i(q)=b$.
-    \item $r_i$ divides $\Delta_{I_i}$.
-    \item The ideal generated by $R$ is the radical of the ideal generated by $\prod_{i=1}^{n}\Delta_{I_i}$.
-  \end{enumerate}
-\end{prop}
-
-\begin{proof}
-\begin{enumerate}
-    \item The nonzero entries of $C(W)$ are independent indeterminates and so every $i\times i$ minor of $C(W)$ is either homogeneous of degree $i$ or is $0$.
-Thus each $\Delta_{I_i}$ and each $r_i$ is homogeneous.
-%Furthermore, each row contributes one factor to each term in the expansion of $\Delta_{I_i}$ so the result of setting the variables from a subset of rows to $1$ is still homogeneous.
-Thus each $r_i$ is homogeneous.
-    \item Using the expression for the determinant as a sum over permutations from Corollary~\ref{lem basis as perm} we see that $\Delta_{I_i}$ is a sum over bijections between $I_i$ and $\mathcal{P}$.
-The nonzero terms in this sum are precisely those bijections such that each propagator is associated to one of its supporting vertices in $I_i$, since only those locations in $C(W)$ are nonzero.
-Since the nonzero entries of $C(W)$ are independent there can be no cancellation between terms in this expansion.
-
-Suppose $\Delta_{I_i}$ has an irreducible factor $f$.
-Let $\mathcal{P}'$ be the set of propagators which contribute a variable to $f$ and let $J$ be the set of vertices which contribute a variable to $f$.
-
-The first claim is that the minor of $C(W)$ associated to $\mathcal{P}'$ and $J$ is precisely $f$.
-
-{\em Proof of claim}: By the structure of determinants we know that $\Delta_{I_i} = fg$, where $g$ involves only variables associated to propagators not in $\mathcal{P}'$ and associated to vertices not in $J$.
-\todo{Is the heart of this proof due to the fact that there are no cancelations?
-It feels tautological to me, but I'm clearly not following}
-
-Expanding out $fg$ yields a signed sum of monomials.
-\hlfix{In each of these monomials, $f$ contributes those variables associated both to a propagator in $\mathcal{P}'$ and to a vertex in $J$, and $g$ contributes those variables associated both to a propagator not in $\mathcal{P}'$ and to a vertex not in $J$, and no other variables appear.
-}{Isn't this redundant with the previous paragraph?}
-
-Since there is no cancellation between terms, this means that the full expansion over permutations of $\Delta_{I_i}$ contains no other nonzero terms and hence no other variables.
-Therefore $\Delta_{I_i}$ is equal to the determinant of the matrix obtained by taking the submatrix of $C(W)$ with columns indexed by $I_i$ and setting any variables not appearing in $\Delta_{I_i}$ to $0$.
-This new matrix is, up to permutations of rows and columns, a block matrix with one block for $\mathcal{P}'$ and $J$ and the other block for the complements.
-Thus its determinant, and hence also $\Delta_{I_i}$, is the product of the minors for these two blocks.
-By considering which variables appear, these two factors must also be $f$ and $g$, and so in particular $f$ is the minor of $C(W)$ associated to $\mathcal{P}'$ and $J$.
-This proves the claim.
-
-A consequence of this claim is that every linear factor of $\Delta_{I_i}$ is a $1\times 1$ minor of $C(W)$, hence is a single variable, and every irreducible quadratic factor of $\Delta_{I_i}$ is a $2\times 2$ minor of $C(W)$, hence is a $2\times 2$ determinant of single variables.
-
-All that remains is to prove that $\Delta_{I_i}$ has no irreducible factors of degree 3 or more.
-Suppose for a contradiction that $f$ is a factor of $\Delta_{I_i}$ of degree $\geq 3$.
-Note that by removing the propagators which come \hlfix{before}{ordering?} those contributing to $f$ and \hlfix{changing $i$ to be the first vertex}{does this generalize to other $i$?} which contributes to $f$, we obtain a \hlfix{different admissible diagram}{Is this just the diagram gotten by removing certain props?} for which $f$ still divides $\Delta_{I_i}$ but also $i\in I_i$ and
-$i$ contributes to $f$.
-Showing that this different admissible diagram gives a contradiction is sufficient, and so we may assume that $i\in I_i$ and $i$ contributes to $f$.
-Finally, we can suppose that $W$ is minimal in number of propagators with the above occuring.
-
-Let $p$ be the propagator such that $I_i(p) = i$. There are two cases to consider, depending on which edge $p$ is supported on.  These are illustrated in Figure~\ref{fig no big factors}
-
-\begin{figure}
-  \includegraphics{no_big_factors}
-  \caption{The two cases in the proof that no factors of $\Delta_{I_i}$ have degree 3 or more.}\label{fig no big factors}
-\end{figure}
-
-\textbf{Case 1}: Suppose $p$ has one end on the edge $(i-1, i)$.  Thus $p$ is supported on $(i-1, i, m, m+1)$ for some $m >_i i$, and $I_{i+1}(p) = m$ by Lemma~\ref{vertex cyclic int lem}.
-
-Let $S = \cP_{in}(p)$ be the set of propagators inside $p$ in the $<_i$ order.
-$I_i$ and $I_{i+1}$ can only differ once $p$ contributes to $I_{i+1}$, so $I_i(q) = I_{i+1}(q)$ for each $q \in S \backslash \{p\}$.
-Thus if a propagator contributes $m$ in $I_i$ then it must lie outside $p$.
-
-If neither $m$ nor $m+1$ appear in $I_i$ then by Corollary~\ref{no coloops} $V(p) \cap I_i = \{i\}$, and so the row of $p$ in the matrix of $\Delta_{I_i}$ has only one nonzero entry; hence $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$, which \hlfix{is a contradiction}{Why?
-because $i$ contributes to $f$?}.
-So we must have at least one of $m$ and $m+1$ in $I_i$.
-However, all propagators in $S$ are mapped by the function $I_{i}(\cdot)$ to vertices strictly before $m$, so the matrix giving $\Delta_{I_i}$ has the form
-\[
-\begin{bmatrix} A & B \\ 0 & C\end{bmatrix}
-\]
-where $A$ is the $|S|\times |S|$ matrix indexed by the propagators in $S$ and the vertices in $I_i(S)$.
-No other propagators can be supported on these vertices since all other propagators are outside of $p$, and $p$ is the first propagator supported at $i$; this explains the zero block.
-Therefore $\Delta_{I_i} = \det A \det C$, and both factors are nontrivial since at least one of $m$ and $m+1$ appear in $I_i$.
-If we remove the propagator outside of $p$ that contributes $m$ or $m+1$, we get a smaller diagram for which $\Delta_{I_i} = \det A$ {\color{violet}why not $\det A \det C'$ with $C'$a minor of $C$?}.
-This contradicts the minimality of our choices unless $\det A$ is quadratic, which in turn contradicts our assumption that $i$ and $p$ contribute to an irreducible factor $f$ of degree at least 3.
-
-\textbf{Case 2}: Suppose $p$ has one end on the edge $(i, i+1)$.
-If no other propagators are supported on $i$ then the column of $C(W)$ corresponding to vertex $i$ has only one nonzero entry in it, and so $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$; as above, this is a contradiction.
-Thus we can take $q$ to be the propagator such that $I_i(q)=i+1$.
-{\color{violet} How do we know this exists?
-Why can't we solve this by having $r$ supported on the $i-1^{th}$ edge?} We know that $q$ has one end on the edge $(i, i+1)$ and is adjacent to $p$ on that edge in the counterclockwise direction (see Figure \ref{fig no big factors}).
-Write $(i, i+1, j, j+1)$ for the support of $q$.
-The situation for $q$ is very similar to case 1: in particular, we have $I_{i+1}(q) = j$ by Lemma~\ref{vertex cyclic int lem} and so if $j\in I_i$ then the propagator which contributes $j$ is outside of $q$.
-
-Similarly to Case 1, let \st{$S$ be the set of propagators inside $q$ along with $p$ and $q$ themselves.}{\color{violet}$S = \cP_{in}(q)$ in the $<_i$ order.
-Note that $p \in S$.}\hlfix{Then all propagators in $S$ are mapped by $I_i(\cdot)$ to vertices strictly before $j$ and no other propagators are supported on vertices strictly before $j$.}{???}  Thus the matrix giving $\Delta_{I_i}$ has the form
-\[
-\begin{bmatrix} A & B \\ 0 & C\end{bmatrix}
-\]
-where $A$ is the submatrix indexed by the propagators in $S$ and the vertices in $I_i(S)$.
-Again two things can now happen.
-If some vertex $j$ or larger (with respect to $>_i$) belongs to $I_i$ then $B$ and $C$ are at least one column wide, and so the block form of the matrix gives a nontrivial factorization of $\Delta_{I_i}$.
-This yields a contradiction as in Case 1: either $W$ contains unnecessary propagators which contradicts our minimality assumption, or $\det A$ is quadratic which contradicts the assumption that $p$ and $i$ contribute to $f$, an irreducible factor of degree at least 3.
-
-On the other hand, if no vertex $\geq_i j$ is in $I_i$ then $\Delta_{I_i} = \det A$.
-Looking in more detail into $A$, note that the only vertices in the support of $p$ and $q$ which belong to $I_i$ are $i$ and $i+1$, and hence
-\[
-A = \begin{bmatrix} D & 0 \\ E & F\end{bmatrix}
-\]
-where $D$ is the $2\times 2$ matrix indexed by the propagators $p$ and $q$ and the vertices $i$ and $i+1$.
-Thus $p$ and $i$ contribute to a quadratic factor of $\Delta_{I_i}$, once again contradicting our assumptions.
-
-All cases have now been covered and so $\Delta_{I_i}$ has only irreducible factors of degree $2$ or less.
-
-\item Suppose propagators $p$ and $q$ are supported on a common edge $(a,b)$, with $I_i(p)=a$ and $I_i(q)=b$.
-Let $x_{p,a},x_{p,b},x_{q,a},x_{q,b}$ be the associated variables in $C(W)$.
-For any fixed bijection $\sigma$ from $\cP-\{p,q\}$ to $I_i -\{a,b\}$ for which each propagator is supported on its image under the bijection, we can extend $\sigma$ to a bijection of all propagators with $I_i$ in two ways: either $p\mapsto a$ and $q\mapsto b$ or $p\mapsto b$ and $q\mapsto a$.
-The sum of the contributions of all these bijections to $\Delta_{I_i}$ is therefore the product of \hlfix{$x_{p,a}x_{q,b}-x_{p,b}x_{q,a}$}{why?
-terms in determinant come from bijections.
-Why should all bijections appear in det?} with the minor coming from $\cP-\{p, q\}$ and $I_i - \{a,b\}$.
-Since there is no cancellation of terms in the expansion of $\Delta_{I_i}$, if any other terms appear then they will cause a factor which is not in the form described in the previous part.
-Therefore no such terms exist and $x_{p,a}x_{q,b}-x_{p,b}x_{q,a}$ is a factor of $\Delta_{I_i}$.
-
-Now let $f$ be a quadratic factor of $\Delta_{I_i}$.
-By part (2) we know that $f$ is a $2\times 2$ minor coming from two propagators, call them $p$ and $q$, and two vertices, call them $a <_i b$.
-It remains to show that $a$ and $b$ are adjacent.
-From this we can conclude that $p$ and $q$ each have one end on $(a,b)$, as any other way for both $p$ and $q$ to be supported on two consecutive vertices would contradict noncrossing or the density requirement of admissibility.
-
-As in the proof of part (2), make a new admissible diagram by removing the propagators which come before $f$ and set $i=a$.
-The cases in the proof of part (2) show how $\Delta_{I_i}$ factors: in particular the vertices supporting the other end of $p$ either do not appear in $I_i$, or they contribute to a different factor of $\Delta_{I_i}$ than $p$ and $a$ do.
-By assumption $b$ contributes to the same factor as $a$.
-Therefore $(a,b)$ is an edge.
-
-\item Consider $p\in S_i$, and note that $\Delta_{I_i}$ is homogeneous linear in the variables of the row corresponding to $p$.
-By part (2), either exactly one variable in the row corresponding to $p$ appears in $\Delta_{I_i}$ and this variable is a factor of $\Delta_{I_i}$, or exactly two variables from the row corresponding to $p$ appear in $\Delta_{I_i}$ and they appear as part of a quadratic factor.
-In the first case let the variable be $x$.
-Then $x$ is a factor of $\Delta_{I_i}$ and so in particular the monomial in $\Delta_{I_i}$ corresponding to the bijection between propagators and vertices of $I_i$ associates the column of $x$ to $p$.
-Thus $x$ also appears in $r_i$ and since the matrix for $r_i$ is a minor of the matrix for $\Delta_{I_i}$ and every term in $\Delta_{I_i}$ involves $x$, we also have that every term in $r_i$ involves $x$ so $x$ is a factor of both $r_i$ and $\Delta_{I_i}$ and is the only variable from this row in either polynomial.
-
-Now suppose two variables from the row $p$ appear in a quadratic factor $f$.
-By part (3), there is another propagator $q$ and an edge $(a,b)$ such that $f$ is the $2\times 2$ minor coming from $p, q$ and $a, b$, with $I_i(p)=a$, $I_i(q)=b$.
-There are two situations which can occur, both illustrated in Figure~\ref{fig quadratic}; we show that in both cases it follows that $q \in S_i$ as well.
-
-\begin{figure}
-  \includegraphics{quadratic}
-  \caption{The situations giving a quadratic factor with variables appearing in $r_i$.}\label{fig quadratic}
-\end{figure}
-
-In both cases, since $I_{i-1}(p)\neq a$ by assumption it follows from Lemma~\ref{vertex cyclic int lem} that $I_{i-1}(p) <_{i-1} a$ and no other vertex supporting $p$ lies between $I_{i-1}(p)$ and $a$.
-In the case that $b<_i a$ and $q$ is assigned before $p$ in $I_i$, this means that $I_{i-1}(p)=b$ and so $I_{i-1}(q)\neq b$.
-Thus $q\in S_i$ and so $f$ is a factor of $r_i$.
-
-Now consider the case where $a<_i b$, and suppose for contradiction that $q \not\in S_i$, i.e.
-that $I_{i-1}(q) = b$.
-Since $I_{i-1}(p) \neq a$, there must be some other propagator $s$ with $I_{i-1}(s) = a$ (else $I_{i-1}$ assigns $q$ to $a$).
-This propagator cannot lie on edge $(a,b)$ since by Lemma~\ref{vertex cyclic int lem} we must have $I_i(s) = a$ or $b$, contradicting the fact that $I_i(p) = a$ and $I_i(q) = b$; thus $s$ has an end on $(a-1,a)$ and is inside $p$ from the point of view of $i-1$.
-
-Say $s$ is supported on $(j, j+1, a-1, a)$ and $p$ is supported on $(k, k+1, a, b)$ with $i-1 \leq_{i-1} k+1 \leq_{i-1} j+1$.
-But by Lemma~\ref{lem no fourth vertex}, if $I_{i-1}(s) = a$ then $a$ cannot be maximal in the support of $s$ with respect to $<_{i-1}$; thus we must have $i-1 = j+1$, and we are in the situation in figure~\ref{fig part 4}.
-
-\begin{figure}
-  \includegraphics[scale=0.5]{part4}
-  \caption{In order to obtain $I_{i-1}(s) = a$, propagators $s$ and $p$ must each have an end on the edge $(i-2,i-1)$.}\label{fig part 4}
-\end{figure}
-
-Since $p$ changed its association from $I_{i-1}$ to $I_i$, we have $I_{i-1}(p) = i-1$ by Lemma~\ref{vertex cyclic int lem}.
-From figure~\ref{fig part 4} it follows that $I_{i-1}$ assigns $p$ to $i-1$ and then proceeds identically to $I_i$ for all vertices inside $p$, implying that $I_{i-1}(s) = I_i(s)$.
-Since $I_{i-1}(s) = a$ and $I_i(s) \neq a$, this is a contradiction.
-
-Thus $q\in S_i$ after all, and so $f$ is a factor of $r_i$ as required.
-
-% Thus $s$ is supported on $a$ but does not have an edge on $(a,b)$ and so $s$ must have an end on $(a-1, a)$ and so be inside $p$ from the point of view of $i-1$.
-Say $s$ is supported on $(j, j+1, a-1, a)$ and $p$ is supported on $(k, k+1, a, b)$ with $i-1 \leq_{i-1} k+1 \leq_{i-1} j+1$.
-Again by Lemma~\ref{lem susama}, immediately after $s$ contributes $a$ it must contribute $j$ and so $I_i(s)=j$.
-
-% Finally we want to show $I_i(s)=j$ gives a contradiction.
-If $k=j$ then $I_{i}(s)= k$, but $p$ has not yet been taken as $I_i(p)=a$ and $p$ comes before $s$ around $k$, so this is a contradiction.
-If $k+1=j$ then similarly $I_{i}(s)=k+1$ and yet $p$ comes before $s$ around $k$, a contradiction to $I_i(p)=a$.
-Now suppose $k+1 <_{i-1} j$ then we have $i-1 \leq_{i-1} k+1 <_{i-1} I_i(s) = j$ so $i\leq_{i} I_i(s)$ which gives that
-% \[
-% I_i(s) <_i I_{i-1}(s) \qquad \text{and} \qquad I_i(s) <_{i-1} I_{i-1}(s)
-% \]
-% \note{Is this known to be impossible by the proof sketch of Lemma~\ref{lem susama} that you emailed or something similar.
-I'm thinking this proof is already too long and the fact that this is impossible would be better as a lemma.}
-
-\item If $W$ has zero propagators then all $I_i=\emptyset$ and both $R$ and $\prod_{i=1}^n \Delta_{I_i}$ are equal to $1$, so the result holds in this case.
-Now assume $W$ has at least one propagator.
-
-First we show that every factor of $\prod_{i=1}^n \Delta_{I_i}$ divides $R$.
-Take an irreducible factor $f$ of $\prod_{i=1}^n \Delta_{I_i}$.
-There exists some $i$ such that $f|\Delta_{I_i}$ but $f\!\!\nmid\!\!
-\Delta_{I_{i-1}}$, since otherwise the variables corresponding to the propagators contributing to $f$ which do not themselves appear in $f$ could never appear, contradicting Lemma~\ref{vertex cyclic int lem}.
-If $f$ is a linear factor, say from associating propagator $p$ to vertex $a$, then $I_{i}(p)=a$ and $I_{i-1}(p)\neq a$ so this factor appears in $r_i$.
-If $f$ is a quadratic factor, say from associating propagators $p$ and $q$ to vertices $a$ and $b$ respectively, then again we cannot have both $I_{i-1}(p) = a$ and $I_{i-1}(q) = b$, else $f$ divides $\Delta_{i-1}$.
-However, by the proof of part (4), if one of $p,q$ belongs to $S_i$ then the other does as well.
-Thus $f$ divides $r_i$.
-
-Next we need to show that $R$ is squarefree.
-Suppose $f^2|R$.
-If $f$ is a linear factor, say from associating propagator $p$ to vertex $a$, then there must be two distinct points in the Grassmann necklace algorithm where $p$ changes from not being associated to vertex $a$ to being associated to vertex $a$.
-This contradicts Lemma~\ref{vertex cyclic int lem}.
-Now suppose $f$ is a quadratic factor, say from propagators $p$ and $q$ supported on the edge $(a, b)$ with $p$ before $q$ on the edge.
-In this case it is not possible for any $I_i$ to associate $p$ to $b$ and $q$ to $a$.
-Furthermore, we know by part (4) that $p$ changes from not being associated to $a$ to being associated to $a$ if and only if $q$ changes from not being associated to $b$ to being associated to $b$.
-Thus $f^2|R$ implies that twice in the Grassmann necklace $p$ must change from not being associated to vertex $a$ to being associated to vertex $a$.
-This is again a contradiction, and so $R$ is squarefree.
-
-Taking everything together we have that $R|\prod_{i=1}^n \Delta_{I_i}$, $R$ contains all factors of $\prod_{i=1}^n \Delta_{I_i}$ and $R$ is squarefree.
-Therefore the ideal generated by $R$ is the radical of the ideal generated by $\prod_{i=1}^n \Delta_{I_i}$.
-  \end{enumerate}
-\end{proof}
-
-\begin{thm}\label{thm denom}
-  Given any admissible Wilson loop diagram $W$, let $\{I_1, \ldots I_n\}$ be the associated Grasmann necklace.
-Then the denominator of the integral, $R(W)$ (see Definition~\ref{def R(W)}), is the $R$ of Algorithm~\ref{alg WLD to denom via GN}.
-Furthermore, the ideal generated by $R(W)$ is the radical of the ideal generated by $\prod_{i=1}^n \Delta_{I_i}$, where $\Delta_{I_i}$ is the determinant of the $k \times k$ minor indicated by $I_i$.
-\end{thm}
-
-{\color{violet} Got rid of need for scalar multiples by talking about radicals.}
-
-\begin{proof}
-The equivalence up to scalar multiple of $R$ and the radical of $\prod_{i=1}^n \Delta_{I_i}$ is due to Proposition~\ref{prop alg gives rad}.
-It remains to prove that $R(W)$ is the $R$ of Algorithm~\ref{alg WLD to denom via GN}.
-
-To this end, first note that $R(W)$ and $R$ both have total degree $4|\mathcal{P}|$; the degree of $R(W)$ is immediate from the definition while that of $R$ follows from Lemma~\ref{vertex cyclic int lem}.
-By Proposition~\ref{prop alg gives rad} every factor of $R$ is either a single variable or a quadratic factor coming from two propagators supported on a common edge.
-The factors of each $R_e$ making up $R(W)$ in the notation of Definition~\ref{def R(W)} are all of this form and hence every factor of $R$ divides $R(W)$.
-Finally, since $R$ is squarefree, this implies that $R(W)$ is a scalar multiple of $R$.
-
-Finally then we need to check the scalar.
-By Definition~\ref{def R(W)} each linear factor appears with coefficient $1$ and each $2\times 2$ deteriminant factor appears with the same sign as the determinant of the corresponding minor in $C(W)$.
-Therefore $R=R(W)$.
-\todo{I'm pretty sure that there isn't a sign issue here.
-But do we have a proof?}
-\end{proof}
-
-Thus we have shown a deep relationship between the physically derived poles of the integrals $I(W)$ and the geometry and combinatorics associated to the diagrams $W$.
-At the very least, this is yet another piece of circumstantial evidence indicating that the positroid representation of Wilson loop diagrams is the correct geometric object to be considering when considering the Wilson loop amplitudes geometrically.
-
-While the authors cannot yet offer a proof that the appropriate sum of the Wilson loop diagrams are, in fact, finite, as conjectured [cite], we do hope that this relationship to the Grassmann Necklace elements will provide a different avenue for answering that and related questions.
-
-\bibliographystyle{abbrv}
-\bibliography{WLDbib}
-
-% \begin{thebibliography}{10}
-% \bibitem{Adamo:2011pv}
-% Tim Adamo, Mathew Bullimore, Lionel Mason, and David Skinner.
-% \newblock {Scattering Amplitudes and Wilson Loops in Twistor Space}.
-% \newblock {\em J.Phys.A}, A44:454008, 2011.
-
-% \bibitem{Adamo:2012xe}
-% Tim Adamo and Lionel Mason.
-% \newblock {Twistor-strings and gravity tree amplitudes}.
-% \newblock {\em Class.Quant.Grav.}, 30:075020, 2013.
-
-% \bibitem{wilsonloop}
-% Susama Agarwala and Eloi~Marin Amat.
-% \newblock Wilson loop diagrams and positroids.
-% \newblock {\em Communications in Mathematical Physics}, 2016.
-% \newblock arXiv:1509.06150.
-
-% \bibitem{casestudy}
-% Susama Agarwala and Sian Fryer.
-% \newblock A study in $\textrm{Gr}_{\geq 0}(2,6)$: from the geometric case book
-%   of {W}ilson loop diagrams and {SYM} $n=4$.
-% \newblock arXiv:1803.00958.
-
-% \bibitem{non-orientable}
-% Susama Agarwala and Cameron Marcott.
-% \newblock Wilson loops in sym $n=4$ do not parametrize an orientable space.
-% \newblock arXiv:1807.05397.
-
-% \bibitem{UnwindingAmplituhedron}
-% Nima Arkani-Hamed, Hugh Thomas, and Jaroslav Trnka.
-% \newblock Unwinding the amplituhedron in binary.
-% \newblock {\em Journal of High Energy Physics}, 2018(1):16, Jan 2018.
-% \newblock arXiv:1704.05069.
-
-% \bibitem{Arkani-Hamed:2013kca}
-% Nima Arkani-Hamed and Jaroslav Trnka.
-% \newblock {Into the Amplituhedron}.
-% \newblock {\em JHEP}, 12:182, 2014.
-
-% \bibitem{Arkani-Hamed:2013jha}
-% Nima Arkani-Hamed and Jaroslav Trnka.
-% \newblock {The Amplituhedron}.
-% \newblock {\em JHEP}, 10:30, 2014.
-
-% \bibitem{Boels:2007qn}
-% Rutger Boels, Lionel Mason, and David Skinner.
-% \newblock {From twistor actions to MHV diagrams}.
-% \newblock {\em Phys.Lett.}, B648:90--96, 2007.
-
-% \bibitem{Bullimore:2010pj}
-% Mathew Bullimore, Lionel Mason, and David Skinner.
-% \newblock {MHV Diagrams in Momentum Twistor Space}.
-% \newblock {\em JHEP}, 1012:032, 2010.
-
-% \bibitem{CasteelsPaths}
-% K. Casteels.
-% \newblock Quantum matrices by paths.
-% \newblock {\em Algebra Number Theory}, 8(8):1857--1912, 2014.
-
-% \bibitem{Amplituhedronsquared}
-% Burkhard Eden, Paul Heslop, and Lionel Mason.
-% \newblock The AmplituhedronSquared.
-% \newblock 2017.
-% \newblock arxiv:1701.00453.
-
-% \bibitem{galashinlam}
-% P.~{Galashin} and T.~{Lam}.
-% \newblock {Parity duality for the amplituhedron}.
-% \newblock {\em arXiv e-prints}, May 2018.
-
-% \bibitem{HeslopStewart}
-% Paul Heslop and Alastair Stewart.
-% \newblock The twistor wilson loop and the amplituhedron.
-% \newblock {\em Journal of High Energy Physics}, 2018(10):142, Oct 2018.
-
-% \bibitem{Hodges:2012ym}
-% Andrew Hodges.
-% \newblock {A simple formula for gravitational MHV amplitudes}.
-% \newblock 2012.
-
-% \bibitem{AmplituhedronDecomposition}
-% Steven~N. Karp, Lauren~K. Williams, and Yan~X. Zhang.
-% \newblock Decompostions of amplituhedra.
-% \newblock arXiv:1708.09525.
-
-% \bibitem{GrassmannAmplitudebook}
-% Freddy Cachazo Alexander Goncharov Alexander Postnikov Jaroslav~Trnka
-%   Nima~{A}rkani {H}amed, Jacob~Bourjaily.
-% \newblock {\em Grassmannian Geometry of Scattering Amplitudes}.
-% \newblock Cambridge University Press, Cambridge, UK, 2016.
-
-% \bibitem{LipsteinMason}
-% Arthur E. Lipstein, Lionel Mason
-% \newblock From dlogs to dilogs; the super Yang-Mills MHV amplitude revisited
-% \newblock J. High Energ. Phys. (2014) 2014: 169.
-
-% \bibitem{reversingOh}
-% S. Agarwala, S. Fryer.
-% \newblock An algorithm to construct the Le diagram associated to a Grassmann necklace
-% \newblock \url{arXiv:1803.01726}
-
-% \bibitem{Gale}
-% D. Gale.
-% \newblock Optimal assignments in an ordered set: {A}n application of matroid theory.
-% \newblock {\em J. Combinatorial Theory}, 4: 176 - 180 (1968).
-
-% \bibitem{Oh}
-% S. Oh.
-% \newblock Positroids and {S}chubert matroids.
-% \newblock {\em J. Combin. Theory Ser. A}, 118(8):2426--2435, (2011)
-
-% \bibitem{Oh2}
-%   S. Oh.
-%   \newblock Combinatorics of positroids.
-%   \newblock {\em DMTCS Proceedings vol. AK},(FPSAC 2009), 721--732
-
-% \bibitem{Postnikov}
-% A.~Postnikov.
-% \newblock Total positivity, {G}rassmannians, and networks.
-% \newblock \url{arXiv:math/0609764}.
-
-% \end{thebibliography}
+If $q$ lies to the right of $p_t$,
 

### 2019-07-04 GWLDCI.tex
Proofread intro

@@
 This paper is the first in a two part series investigating the combinatorics and geometry underlying SYM $N=4$ theory.
-This series lays out several results about the relationship between the Wilson loop diagrams and the positroid cells that give a CW complex structure to the positive Grassmanian.
+This series lays out several results about the relationship between Wilson loop diagrams and the positroid cells that give a CW complex structure to the positive Grassmanian.
 This paper expands on an observation from \cite{wilsonloop}, that shows that certain families of Wilson loop diagrams correspond to the same positroid cell.
 This paper gives a way of enumerating the number of different Wilson loop diagrams that correspond to a given positroid cell.
-Furthermore, it shows that the number of cells in the image of the map to positive Grassmannians is given by counting the directions in associahedra.
+Furthermore, it shows that the number of cells in the image of the map to positive Grassmannians is given by counting the directions \hlfix{in}{of a?} associahedra.
 
@@
 These integrals are calculated via Wilson loops.
-The first author and Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that are realized as an element of $\Gr(k,n)$ \cite{wilsonloop}.
+The \hlfix{first author and Amat}{At other points, we say "some of us" instead of specifying like this.
+Choose a convention} uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that are realized as an element of $\Gr(k,n)$ \cite{wilsonloop}.
 With the second author and others, this work was extended to study these Feynman integrals in terms of positroid cells and the positive Grassmanians \cite{casestudy, non-orientable}.
@@
 In this paper, we focus on the correspondence between Wilson loop diagrams and positroids, first defined in \cite{wilsonloop}.
-In that paper, one of us with Amat show that there are certain families of diagrams, specifically those with exact subdiagrams, that do map to the same positroid cell.
+In that paper, \hlfix{one of us}{see previous comment about self reference convention} with Amat show that there are certain families of diagrams, specifically those with exact subdiagrams, that do map to the same positroid cell.
 In \cite{casestudy} some of us explictly show that not every positroid cell of a given dimension corresponds to a Wilson loop diagram.
@@
 Further, given a Wilson loop diagram with a non-trivial exact subdiagram, we count the total number of Wilson loop diagrams that correspond to that same positroid cell.
-While we do not count the number of distint positroid cells that correspond to Wilson loop diagrams, we do show that this enumeration is equivalent to enumerating the number of directions of an associahedron.
+While we do not count the number of distinct positroid cells that correspond to Wilson loop diagrams, we do show that this enumeration is equivalent to enumerating the number of directions of an associahedron.
 
@@
 Wilson loop diagrams  are said to be admissible when they correspond to $N^kMHV$ diagrams, or mathematically according to Definition~\ref{admisdfn}.
-With this, the key definition is Definition~\ref{equivdfn} giving the equivalence relation on admissible Wilson loop diagrams.
+The other key definition in this section is Definition~\ref{equivdfn}, which gives an equivalence relation on admissible Wilson loop diagrams.
 The connection to matroids is stated precisely in Theorem \ref{thm WLD defines matroid}.
@@
 Having identified the equivalence classes and their sizes, the next natural question is to identify the number of inequivalent diagrams under this equivalence relation.
-The main result of Section~\ref{sec associahedron} is to show that the set of admissible Wilson loop diagrams (up to equivalence) is in bijection with the set of faces in the associahedron (up to paralellness).
+The main result of Section~\ref{sec associahedron} is Theorem \ref{thm:count inequiv diagrams} which shows that the set of admissible Wilson loop diagrams (up to equivalence) is in bijection with the set of faces in the associahedron (up to paralellness).
 Towards this result we go over some relevant background on polytopes in subsection~\ref{sec polytope background}, and then give the main result in subsection~\ref{sec associahedron results} in the form of two propositions: Propositions~\ref{prop easy way} and~\ref{prop hard way}.
@@
 \section{Background}\label{section overall background}
+
+This section gives the relevant physical and combinoatorial background for this paper.
+Section \ref{section WLD background} defines Wilson loop diagrams as combinatorial objects, and presents relevant definitions and results from previous work.
+Section \ref{sec matroid background} presents some background on matroids and some known result relating Wilson loop diagrams to matroids.
 
@@
 
-Propagators are undirected, so $p = (i,j) = (j,i)$. In order to fix a convention, we write $p = (i,j)$ with  $i +1 \leq j$ relative to the first vertex.
+Propagators are undirected, so $p = (i,j) = (j,i)$. In previous work, we have used the convention, we write $p = (i,j)$ with  $i +1 \leq j$ relative to the first vertex. \sanote{Susama stopped here}
 

### 2019-07-05 GNproof.tex
see purple

@@
 
+{\color{violet} Second, we note that when $p_m$ contributes $I_i(p_m) = a_m$ to the Grassmann necklace, it is the clockwisemost propagator supported on $a_m$ in the set $\cP \setminus \cP_{m-1}$.
+If $p_r$ is also supported on $a_m$, if $p_r$ is outside $p_m$ in the $<_{a_m-1}$ order, then it must have been assigned before $p_m$, i.e.
+$r <m$.
+Otherwise, $p_m$ could not be the clockwise most propagator when the algorithm reached $a_m$.}
+
 Let $J = \{j_1 <_i j_2<_i \dots <_i j_k\}$ be a $k$-set, and suppose that $J<_i I_i$ in the $<_i$-lexicographic order.
@@
 
-We claim that $Q_l \subseteq \cP_{m-1}$ for all $l\geq 0$. The base case follows immediately from the observation above that $\Prop(j_m) \subseteq \cP_{m-1}$.
+We claim that $Q_l \subseteq \cP_{m-1}$ for all $l\geq 0$.
+\st{The base case } \hlfix{The case for $l= 0$}{$l=0$ is not quite the base case} follows immediately from the observation above that $\Prop(j_m) \subseteq \cP_{m-1}$.
 
-[induction step; see final page]
+{\color{violet} Next we prove the base case of $l=1$.
+If $Q_1 \setminus Q_0 = \emptyset$, we are done.
+Else, let $q \in Q_1 \setminus Q_0$.
+By construction $q$ shares support with a propagators in $\Q_{0}$.
+Call this propagator $p_j$.
+By the above, $p_j \in \cP_{m-1}$.
+Suppose that $q \not \in \cP_{m-1}$.
+The violet note above implies that $q$ must be inside $p_j$ in the $a_{j}-1$ ordering.
+If $a_j = j_m-1$, such a $q$ cannot exist (it would force $I_i(q) = j_m$).
+Else, since $q$ cannot contribute its fourth vertex, by Lemma \ref{insert reference}, $I_i(q) < j_m$.
+That is, $q \in \cP_{m-1}$, giving a contradiction.}
+
+{\color{violet} Continuing by induction, Since all of $Q_{l-1} \subseteq \cP_{m-1}$ by the induction hypothesis, consider $Q_l \setminus Q_{l-1}$.
+If this et is empty, we are done.
+Otherwise, let $q \in Q_l \setminus Q_{l-1}$.
+By construction $q$ shares support with a propagators in $\Q_{l-1}$.
+Call this propagator $p_j$.
+Let $v_j$ be the fourth propagator of $p_j$ in the $a_{j}-1$ ordering (not assigned to $I_i$.) We have two cases: $a_j-1 < v_j < j_m$ in any cyclice ordering, or $a_j-1 < j_m < v_j$.
+In the first case, following the same argument as the base case, if $q \not \in \cP_{m-1}$, $q$ must be inside $p_j$ in the $a_{j}-1$ ordering.
+Since $q$ cannot contribute its fourth vertex, $I_i(q) < v_j < j_m$.
+That is, $q \in \cP_{m-1}$, giving a contradiction.
+
+In the second case, suppose $p_j$ must share an edge with $p_r \in Q_{l-2}$ and $a_j +1  = a_r$.
+If a $q \not \in \cP_m$ is supported on $a_j$ it lies inside $p_j$ in the $a_{j-1}$ ordering.
+However, for this to happen, and $p_r$ to contribute $a_r$, $q$ must also lie inside $p_r$, which we know by induction cannot happen.
+} \sanote{I hadn't thought through this second case very well when I first wrote the proof. Please check.}
 

### 2019-07-08 GWLDCI.tex
proofreading section 1 and 2

@@
 This paper is the first in a two part series investigating the combinatorics and geometry underlying SYM $N=4$ theory.
-This series lays out several results about the relationship between Wilson loop diagrams and the positroid cells that give a CW complex structure to the positive Grassmanian.
+This series lays out several results about the relationship between Wilson loop diagrams and the positroid cells that give a CW complex structure to the positive Grassmannian.
 This paper expands on an observation from \cite{wilsonloop}, that shows that certain families of Wilson loop diagrams correspond to the same positroid cell.
@@
 It proves that a Wilson loop diagram with $k$ propagators corresponds to a $3k$ dimensional positroid cell.
-Furthermore, it gives an algorithm for passing from a Wilson loop diagram to the Grassman necklace that identifies the associated positroid cell.
+Furthermore, it gives an algorithm for passing from a Wilson loop diagram to the Grassmann necklace that identifies the associated positroid cell.
 In this manner the authors give a means of identifying which positroid cell is associated to which Wilson loop diagram that circumvents the painstaking process of examining bases sets.
@@
 In recent years, there has been an active program researching the geometry and combinatorics underlying SYM $N=4$ theory \cite{wilsonloop, Arkani-Hamed:2013jha, Amplituhedronsquared, AmplituhedronDecomposition, galashinlam}.
-This body of work started with the observation that the on shell (tree level) amplitudes of this theory correspond to the volume of a subspace of a positive Grasmannian, called an Amplituhedron \cite{Arkani-Hamed:2013jha}.
+This body of work started with the observation that the on shell (tree level) amplitudes of this theory correspond to the volume of a subspace of a positive Grassmannian, called an Amplituhedron \cite{Arkani-Hamed:2013jha}.
 Since then, there has been significant work studying the structure of the amplituhedron, geometrically and combinatorially, for instance \cite{Arkani-Hamed:2013kca, arkani:2012nw, AmplituhedronDecomposition, galashinlam}.
@@
 Choose a convention} uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that are realized as an element of $\Gr(k,n)$ \cite{wilsonloop}.
-With the second author and others, this work was extended to study these Feynman integrals in terms of positroid cells and the positive Grassmanians \cite{casestudy, non-orientable}.
+With the second author and others, this work was extended to study these Feynman integrals in terms of positroid cells and the positive Grassmannians \cite{casestudy, non-orientable}.
 Others have tried different approaches to define a geometric space associated to these integrals in a manner similar to the Amplituhedron \cite{Amplituhedronsquared, HeslopStewart}.
@@
 In that paper, \hlfix{one of us}{see previous comment about self reference convention} with Amat show that there are certain families of diagrams, specifically those with exact subdiagrams, that do map to the same positroid cell.
-In \cite{casestudy} some of us explictly show that not every positroid cell of a given dimension corresponds to a Wilson loop diagram.
+In \cite{casestudy} some of us explicitly show that not every positroid cell of a given dimension corresponds to a Wilson loop diagram.
 In this paper, we better enumerate this correspondence.
-We show that the map from Wilson loop diagrams to postroid cells is one to one exactly on the subset of diagrams with no non-trivial exact subdiagrams.
+We show that the map from Wilson loop diagrams to positroid cells is one to one exactly on the subset of diagrams with no non-trivial exact subdiagrams.
 We show that exact diagrams correspond to uniform matroids, and that contraction by exact subdiagrams has special matroidal properties.
@@
 In subsection~\ref{sec: polygon partitions} we relate certain subdiagrams (the {\em exact} subdiagrams, Definition~\ref{def:exact diagram}) of Wilson loop diagrams to triangulations of polygons, and then in subsection~\ref{sec: exact diagram matroidal props} we examine the matroidal properties of the exact subdiagrams.
-Specifically, we show that a subdiagram of a Wilson loop diagrams $W$ defines a uniform matroid if and only if the subdiagram is exact (Theorem \ref{exactuniformthm}), and that this uniform matroid is equal to the dual of the matriod associated to $W$ restricted to the exact subdiagram (Remark \ref{remark exact dual restiction}).
+Specifically, we show that a subdiagram of a Wilson loop diagrams $W$ defines a uniform matroid if and only if the subdiagram is exact (Theorem \ref{exactuniformthm}), and that this uniform matroid is equal to the dual of the matroid associated to $W$ restricted to the exact subdiagram (Remark \ref{remark exact dual restiction}).
 Subsection~\ref{sec: matroids and equivalence} is devoted to the proof of Theorem~\ref{same matroid iff equiv}, along with an easy corollary which gives a formula for the size of each equivalence class (Corollary~\ref{number of equiv diagrams}).
@@
 Having identified the equivalence classes and their sizes, the next natural question is to identify the number of inequivalent diagrams under this equivalence relation.
-The main result of Section~\ref{sec associahedron} is Theorem \ref{thm:count inequiv diagrams} which shows that the set of admissible Wilson loop diagrams (up to equivalence) is in bijection with the set of faces in the associahedron (up to paralellness).
+The main result of Section~\ref{sec associahedron} is Theorem \ref{thm:count inequiv diagrams} which shows that the set of admissible Wilson loop diagrams (up to equivalence) is in bijection with the set of faces in the associahedron (up to parallelism).
 Towards this result we go over some relevant background on polytopes in subsection~\ref{sec polytope background}, and then give the main result in subsection~\ref{sec associahedron results} in the form of two propositions: Propositions~\ref{prop easy way} and~\ref{prop hard way}.
@@
 
-This section gives the relevant physical and combinoatorial background for this paper.
+This section gives the relevant physical and combinatorial background for this paper.
 Section \ref{section WLD background} defines Wilson loop diagrams as combinatorial objects, and presents relevant definitions and results from previous work.
-Section \ref{sec matroid background} presents some background on matroids and some known result relating Wilson loop diagrams to matroids.
+Section \ref{sec matroid background} presents some background on matroids and some existing results relating Wilson loop diagrams to matroids.
 
@@
 \begin{dfn}\label{WLdfn}
-A {\em Wilson loop diagram} is given by the following data: a cyclicly ordered set $V$, along with a choice of first vertex (labeled $1$), and a set $\cP$ of $k$ pairs called {\em propagators}, written $\{p_r = (i_r, j_r)\}_{r=1}^k$.
+A {\em Wilson loop diagram} is given by the following data: a cyclically ordered set $V$, along with a choice of first vertex (labeled $1$), and a set $\cP$ of $k$ pairs called {\em propagators}, written $\{p_r = (i_r, j_r)\}_{r=1}^k$.
 We write $W = (\cP,V)$ to denote the Wilson loop diagram.
@@
 
-Often we take $V$ to be the cyclically ordered set of integers $1 \ldots n$, denoted $[n]$. In this case we write $W = (\cP, [n])$, and all indices are considered modulo $n$.
+Often we take $V$ to be the cyclically ordered set of integers $\{1, \ldots, n\}$, which we denote by $[n]$. In this case we write $W = (\cP, [n])$, and all indices are considered modulo $n$.
 
@@
 \item For $U \subseteq [n]$, write $\Prop(U) = \{ p \in \cP  \ | \ V(p) \cap U \neq \emptyset \} $ to denote the set of propagators which are at least partially supported on $U$.
-\item For $P \subseteq \cP$, define the {\em propagator flat} $F(P) = V(P^c)^c$ to be\footnote{Here, as throughout, we are using the superscript $c$ for the set theoretic complement.} the set of vertices in $[n]$ that do not support any propagators outside of the set $P$.
-(This choice of terminology is justified in Lemma~\ref{lem facts about WLD matroids} below.)
+\item For $P \subseteq \cP$, define the {\em propagator flat}\footnote{This choice of terminology is justified in Lemma~\ref{lem facts about WLD matroids} below.} $F(P) = V(P^c)^c$ to be the set of vertices in $[n]$ that do not support any propagators outside of the set $P$.
+Here, as throughout, we are using the superscript $c$ for the set theoretic complement.
 \item The set of vertices that do not support any propagators is denoted $F(\emptyset)$. Vertices in this set are called {\em non-supporting}.  
@@
 \begin{rmk}\label{alt F(P) rmk}
-An equivalent definition of $F(P)$ is \bas F(P)  = \big(V(P) \setminus V(P^c) \big) \cup \{\text{ all non-supporting vertices in $W$ }\} \;,\eas 
+An equivalent definition of $F(P)$ is \bas F(P)  = \big(V(P) \setminus V(P^c) \big) \cup \{\text{all non-supporting vertices in $W$}\} \;,\eas 
 i.e.
 $F(P)$ can be thought of as the set of vertices that either only support propagators in $P$ or do not support any propagators at all.
-Furthermore, note that by construction $\Prop(F(P)) \subseteq P$.
+Furthermore, note that by construction we have $\Prop(F(P)) \subseteq P$.
 This containment is strict if there is any propagator $p$ in $P$ with the property that every vertex in the support of $p$ also supports a propagator not in $P$.
@@
 
-It is sometimes useful to discuss propagators in terms of the edges supporting them, rather than the vertices.
+It is sometimes useful to discuss propagators in terms of the edges supporting them (rather than the vertices) so we make the following definition.
 
 \begin{dfn}\label{def:edges}
-The $i$th edge of $W$ is the edge of the external polygon that lies between the vertices $i$ and $i+1$.
+The $i$th edge of $W$ is the arc that lies between the vertices $i$ and $i+1$.
 \end{dfn}
@@
 We now define the notion of an admissible diagram, which imposes certain density and non-crossing conditions on the configuration of the propagators.
+The motivation for these conditions comes from the link to SYM $N=4$ theory, where the admissible Wilson loop diagrams are exactly those that correspond to $N^kMHV$ diagrams; see for example \hlfix{[ref].}{I don't think we should go into any detail here, but I wanted to emphasise that there is a reason for choosing these particular conditions.}
 
@@
 A Wilson loop diagram $W = (\cP,V)$ is {\em admissible} if \begin{enumerate}
-\item $|V| \geq |\cP| + 4$
-\item There does not exists a set of propagators $Q \subseteq \cP$ such that $|V(Q)| < |Q| + 3$.
-\item There does not exist a pair of propagators $p, q \in \cP$ such that $i_p < i_q < j_p <j_q$.
+\item $|V| \geq |\cP| + 4.$
+\item There does not exist a (non-empty) set of propagators $Q \subseteq \cP$ such that $|V(Q)| < |Q| + 3$.
+\item There does not exist a pair of propagators $(i_p,j_p),(i_q,j_q) \in \cP$ such that $i_p < i_q < j_p <j_q$.
 \end{enumerate}
@@
 
-The first condition restricts the overall density of propagators in the diagram, while the second imposes an upper bound on how densely the propagators can be fitted in any portion of the diagram.
+The first condition restricts the overall density of propagators in the diagram, while the second imposes an upper bound on how densely the propagators can be fitted into a portion of the diagram.
 The third ensures that ensures that no propagators cross in the interior of the diagram.
 
-In other words, a Wilson loop diagram, $(\cP, [n])$ is admissible only if $n \geq |\cP| +4$, and has no crossing propagators, no propagators of the form $p = (i, i+1)$, and no pairs of propagators that start and end on the same pair of non-adjacent edges.
+In other words, a Wilson loop diagram, $(\cP, [n])$ is admissible only if $n \geq |\cP| +4$, and has no crossing propagators, no propagators of the form $p = (i, i+1)$, and no pairs of propagators that start and end on the same pair of non-adjacent edges.\note{Sian: can we leave this sentence out?
+By dropping ``iff'' to ``only if'' we make it sound like the converse isn't true.}
 
@@
 
-In what follows, we will restrict our attention to admissible Wilson loop diagrams and subdiagrams thereof.
+For the remainder of the paper, we will restrict our attention to admissible Wilson loop diagrams and subdiagrams thereof.
 
@@
 \begin{dfn}\label{def:exact diagram}
-For $W$ an admissible diagram, $(P, V(P))$ is {\em exact} if $|V(P)| = |P| + 3$.
+For $W$ an admissible diagram, the subdiagram $(P, V(P))$ is {\em exact} if $|V(P)| = |P| + 3$.
 \end{dfn}
@@
 
+\vspace{3pt}
 \begin{eg}
@@
 \begin{dfn}\label{equivdfn} 
-Let $W = (\cP,[n])$ and $W' = (\cP',[n])$.
-Define an equivalence relation $\sim$ on the set of admissible Wilson loop diagrams with vertex set $[n]$ by taking the transitive closure of the following relation: $W \sim W'$ if
+Let $W = (\cP,[n])$ and $W' = (\cP',[n])$. Define a relation $\sim$ by $W\sim W'$ if
 \begin{enumerate}
@@
 \end{enumerate}
+The transitive closure of $\sim$ (which by an abuse of notation we also denote by $\sim$) defines an equivalence relation on the set of admissible Wilson loop diagrams with vertex set $[n]$.
 \end{dfn}
@@
 
-We have $W_1 \sim W_2$ because they agree except on the exact subdiagrams 
-\[(\{(5,8), (5,7)\}, \{5,6,7,8,1\}) \text{ and }(\{(5,8), (7,8)\}, \{5,6,7,8,1\})\] respectively. We also have $W_2 \sim W_3$ due to the exact subdiagrams 
-\[(\{(1,4), (3,4)\}, \{1,2,3,4,5\}) \text{ and }(\{(1,4), (1,3)\}, \{1,2,3,4,5\}).\] 
+We have $W_1 \sim W_2$ because they are identical except on the exact subdiagrams 
+\[(\{(5,8), (5,7)\}, \{5,6,7,8,1\}) \text{ and }(\{(5,8), (6,8)\}, \{5,6,7,8,1\})\] respectively. We also have $W_2 \sim W_3$ due to the exact subdiagrams 
+\[(\{(1,4), (2,4)\}, \{1,2,3,4,5\}) \text{ and }(\{(1,4), (1,3)\}, \{1,2,3,4,5\}).\] 
 However, the difference between $W_1$ and $W_3$ is the union of two exact subdiagrams, which is not itself exact. \end{eg}
 
-As described in the introduction, Wilson loop diagrams come from the study of SYM $N = 4$ in the physics literature, and therefore each diagram is associated to a matrix of data which we now describe.
+As described in the introduction, Wilson loop diagrams come from the study of SYM $N = 4$ in the physics literature and therefore each diagram $W$ is associated to a matrix of data $C(W)$, which we now describe.
 
@@
 Each Wilson loop diagram $W = (\cP, [n])$ with $|\cP| = k$ is associated to a $k \times n$ matrix $C(W)$ with non-zero real variable entries, defined by:
-
 \bas C(W)_{p,q} = \begin{cases} c_{p,q} & \textrm{ if } q \in V(p) \\
@@
 \begin{eg}
-For example, if we order the propagators of $W_1$ from Example \ref{eg:equivdiags}as follows: \bas (1,4), \, (2,4), \, (5,7), \, (5,8) \eas we obtain the corresponding matrix
+If we order the propagators of $W_1$ from Example \ref{eg:equivdiags} as follows: \bas (1,4), \, (2,4), \, (5,7), \, (5,8) \eas then we obtain the corresponding matrix
 \bas C(W_1) = \left(
@@
 
+The matrix $C(W)$ will allow us to associate a matroid to each Wilson loop diagram.
 We first give a quick summary of the matroid terminology that we will need; it is not intended as a comprehensive introduction to matroids and the interested reader is referred to \cite{OxleyMatroidBook}
@@
 A subset $A \subseteq E$ is called {\em independent} in $M$ if $A \subseteq B$ for some $B \in \cB$, and {\em dependent} otherwise.
-The {\em rank}  $\rk(A)$ of a subset $A \subseteq E$ is the size of the largest independent set contained in $A$.
+(In other words, a basis is simply an independent set of maximal size in $M$.) The {\em rank}  $\rk(A)$ of a subset $A \subseteq E$ is the size of the largest independent set contained in $A$.
 The rank of the matroid itself is defined to be $\rk(E)$.
@@
 Unsurprisingly, a {\em cyclic flat} is a set which is both a flat and a cycle.
-The set of circuits in a matroid uniquely defines that matroid, as does the set of flats; thus one could specify a matroid by listing its independent sets, bases, circuits, or flats.
+The set of circuits in a matroid uniquely defines that matroid, as does the set of flats; thus one could specify a matroid by listing either its independent sets, its bases, its circuits, or its flats.
 
 Finally, we describe several important types of matroids.
-A matroid of rank $k$ with a ground set of size $n$ is called {\em realizable} if there exists some $A \in Gr(k,n)$ whose non-zero $k\times k$ minors are exactly those with columns indexed by elements of $\cB$.
-If all the maximal minors of the matrix are nonnegative then the matroid realized by this matrix is a {\em positroid}.
+A matroid of rank $k$ with a ground set of size $n$ is called {\em realizable} if there exists some $A$ in the $k\times n$ real Grassmannian $\mathbb{G}_{\mathbb{R}}(k,n)$ whose non-zero $k\times k$ minors are exactly those with columns indexed by an element of $\cB$.
+If all the maximal minors of the matrix are nonnegative then the matroid realized by this matrix is called a {\em positroid}.
 In other words a positroid is a matroid\footnote{Note that matroid isomorphism allows arbitrary permutations of the ground set, while positroid isomorphism only allows cyclic permutations in order to preserve the nonnegativity of the minors.
@@
 \label{thm:WLDmatroid}\end{thm}
-In other words, the independent sets of $M(W)$ correspond to the sets of vertices in $W$ such that no subset supports fewer propagators than the vertices it contains.
+In other words, the independent sets of $M(W)$ correspond to the sets of vertices in $W$ with ``enough propagators sufficiently well distributed'' on them: not only should $V$ itself support at least as many propagators as the number of vertices it contains, but the same should be true of any subset of $V$ as well.
 
@@
 Therefore, for any subset of vertices $V \subseteq [n]$, we can consider the restriction $C(W)|_V$ of $C(W)$ consisting of the columns corresponding to $V$.
-Since the non-zero entries of $C(W)$ are independent real variables, the matrix $C(W)|_V$ does not have full rank if and only if there are fewer than $||V$ rows with non-zero entries.
+Since the non-zero entries of $C(W)$ are independent real variables, the matrix $C(W)|_V$ does not have full rank if and only if there are fewer than $|V|$ rows with non-zero entries.
 This is equivalent to saying that $V$ is a set of dependent columns of $C(W)$ if and only if $|\Prop(V)| < |V|$.
@@
 In particular, this allows us to prove results about $M(W)$ by considering the behavior of propagators in $W$.
-We record a few facts about the ranks cycles and flats of $M(W)$ here as an example of this.
+We record a few facts about the ranks of cycles and flats in $M(W)$ as an example of this.
 
@@
 \item If $[n]$ can be partitioned into at least two non-empty sets, each of which support disjoint sets of propagators and in such a way that we obtain a partition of the propagator set, i.e.
-if we have \bas [n] = \sqcup_i V(P_i) \quad \textrm{ such that } \quad \sqcup P_i = \cP;  \text{ with }V(P_i) \cap V(P_j) = \emptyset \text{ and } P_i \cap P_j = \emptyset \quad \forall i \neq j\;, \eas then the matroid $M(W)$ is separable, i.e.
+if we have \bas [n] = \sqcup_i V(P_i) \ \textrm{ such that } \ \sqcup P_i = \cP; \   \text{ with }V(P_i) \cap V(P_j) = \emptyset \text{ and } P_i \cap P_j = \emptyset \quad \forall i \neq j\;, \eas then the matroid $M(W)$ is separable, i.e.
 \bas M(W) = \bigoplus_i M(P_i, V(P_i)) \;.\eas
-\item $F(P)$ is a flat of $M( W)$, which we call the \emph{propagator flat} of $P$.
+\item The set $F(P)$ from Definition~\ref{VPropdfn} is a flat of $M( W)$, which we call the \emph{propagator flat} of $P$.
 \item If $F$ is a cyclic flat of $M(W)$, then it is a propagator flat.
@@
 (2) is \cite[Lemma 3.27]{wilsonloop}.
-(3) is a direct consequence of \cite[Lemma 3.20]{wilsonloop} and the fact that $F(P_1)^c = V(P_1^c)$
+(3) is a direct consequence of \cite[Lemma 3.20]{wilsonloop} and the fact that $F(P_1)^c = V(P_1^c)$, and (5) is given in \cite[Lemma 3.28]{wilsonloop}.
 
@@
 Thus $\rk(F(P) \cup\{v\}) = \rk(F(P)) + 1$, as required.
-
-Point (5) is given in \cite[Lemma 3.28]{wilsonloop}.
 \end{proof}

### 2019-07-08 GWLDCI.tex
moved the introduction around a bit

@@
 This paper is the first in a two part series investigating the combinatorics and geometry underlying SYM $N=4$ theory.
-This series lays out several results about the relationship between Wilson loop diagrams and the positroid cells that give a CW complex structure to the positive Grassmannian.
-This paper expands on an observation from \cite{wilsonloop}, that shows that certain families of Wilson loop diagrams correspond to the same positroid cell.
-This paper gives a way of enumerating the number of different Wilson loop diagrams that correspond to a given positroid cell.
-Furthermore, it shows that the number of cells in the image of the map to positive Grassmannians is given by counting the directions \hlfix{in}{of a?} associahedra.
-
-The second paper in this series identifies which positroid cell is associated to which Wilson loop diagram \cite{generalcombinatoricsI}.
-It proves that a Wilson loop diagram with $k$ propagators corresponds to a $3k$ dimensional positroid cell.
-Furthermore, it gives an algorithm for passing from a Wilson loop diagram to the Grassmann necklace that identifies the associated positroid cell.
-In this manner the authors give a means of identifying which positroid cell is associated to which Wilson loop diagram that circumvents the painstaking process of examining bases sets.
-Finally, the authors characterize the the volume forms that Wilson loop diagrams associate to each positroid cells.
-
-In recent years, there has been an active program researching the geometry and combinatorics underlying SYM $N=4$ theory \cite{wilsonloop, Arkani-Hamed:2013jha, Amplituhedronsquared, AmplituhedronDecomposition, galashinlam}.
+The series lays out several results about the relationship between Wilson loop diagrams and the positroid cells that give a CW-complex structure to the positive Grassmannian $\Gr(k,n)$.
+Understanding the precise nature of this relationship is crucial in the study of scattering amplitudes in SYM $N=4$, as described below.
+
+In \cite{wilsonloop} the first author and Amat showed that every admissible Wilson loop diagrams can be identified with a unique positroid cell, and observed that this mapping is neither one-to-one nor onto.
+In this paper we give a simple characterization of this lack of injectivity in terms of an equivalence relation on the Wilson loop diagrams, and enumerate the number of different Wilson loop diagrams that correspond to each positroid cell.
+We also study the lack of surjectivity, and show that the number of distinct positroid cells associated to Wilson loop diagrams is given by counting the directions \hlfix{in}{of a?} associahedra.
+
+The second paper \cite{generalcombinatoricsII} in this series identifies precisely which positroid cell is associated to a given Wilson loop diagram, by giving an algorithm for passing from a Wilson loop diagram to the Grassmann necklace of the associated positroid cell.
+In this manner the authors give a direct path from Wilson loop diagram to positroid cell that circumvents the painstaking process of examining bases sets.
+With this identification in hand, we also prove that any Wilson loop diagram with $k$ propagators corresponds to a $3k$ dimensional positroid cell, and characterize the volume forms that Wilson loop diagrams associate to each positroid cell.
+
+In recent years, there has been an active program researching the geometry and combinatorics underlying SYM $N=4$ theory \cite{wilsonloop, Arkani-Hamed:2013jha, Amplituhedronsquared, galashinlam,AmplituhedronDecomposition}.
 This body of work started with the observation that the on shell (tree level) amplitudes of this theory correspond to the volume of a subspace of a positive Grassmannian, called an Amplituhedron \cite{Arkani-Hamed:2013jha}.
-Since then, there has been significant work studying the structure of the amplituhedron, geometrically and combinatorially, for instance \cite{Arkani-Hamed:2013kca, arkani:2012nw, AmplituhedronDecomposition, galashinlam}.
-The focus of much of this work has been on understanding the relationship between the combinatorial objects from the physics of the system, BCFW diagrams, and their corresponding natural object for studying the positive Grassmannians, positroid cells.
-
-Meanwhile, there has been a different body of work studying SYM $N=4$ theory from the point of view of Feynman integrals in twistor space \cite{Adamo:2011pv, Britto:2005fq, Cachazo:2004kj}.
+Since then, there has been significant work studying the structure of the Amplituhedron both geometrically and combinatorially, for instance \cite{arkani:2012nw, Arkani-Hamed:2013kca, galashinlam,AmplituhedronDecomposition}.
+The focus of much of this work has been on understanding the relationship between BCFW diagrams and positroid cells, which are the combinatorial objects from the physics of the system and the corresponding natural objects in the positive Grassmannian respectively.
+
+Meanwhile, there is a separate body of work studying SYM $N=4$ theory from the point of view of Feynman integrals in twistor space \cite{Adamo:2011pv, Britto:2005fq, Cachazo:2004kj}.
 These integrals are calculated via Wilson loops.
-The \hlfix{first author and Amat}{At other points, we say "some of us" instead of specifying like this.
-Choose a convention} uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that are realized as an element of $\Gr(k,n)$ \cite{wilsonloop}.
-With the second author and others, this work was extended to study these Feynman integrals in terms of positroid cells and the positive Grassmannians \cite{casestudy, non-orientable}.
+As noted above, the \hlfix{first author and Amat}{At other points, we say "some of us" instead of specifying like this.
+Choose a convention} uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that are realized as an element of the positive Grassmannian $\Gr(k,n)$ \cite{wilsonloop}.
+In (separate) papers with the second author and Marcott, this work was extended to study these Feynman integrals in terms of positroid cells and the positive Grassmannians \cite{casestudy, non-orientable}.
 Others have tried different approaches to define a geometric space associated to these integrals in a manner similar to the Amplituhedron \cite{Amplituhedronsquared, HeslopStewart}.
 
-Both the Amplituhedron literature and the Wilson loop literature associate $n$ particle, $N^kMHV$ interaction in SYM $N=4$ theory to volume forms on a set of positroid cells of $\Gr(k,n)$.
-This gives a CW complex of some submanifold in $\Gr(k,n)$.
-Understanding the geometry and topology of these spaces is the subject of ongoing research.
-For Wilson loop diagrams with $k=2$ and $n=6$, past work of some of us shows that the manifold is not contractible \cite{casestudy}.
-Furthermore, the spaces defined by the Amplituhedron and the Wilson loop diagrams are not the same \cite{Amplituhedronsquared}.
-In particular, it it more natural to consider Deodhar cells of $\mathbb{G}(k, n+1)$ for Wilson loop diagrams.
-In this case, one gets that the manifold represented by the diagrams is not orientable \cite{non-orientable}.
-
-In this paper, we focus on the correspondence between Wilson loop diagrams and positroids, first defined in \cite{wilsonloop}.
-In that paper, \hlfix{one of us}{see previous comment about self reference convention} with Amat show that there are certain families of diagrams, specifically those with exact subdiagrams, that do map to the same positroid cell.
+Both the Amplituhedron literature and the Wilson loop literature associate $n$ particle $N^kMHV$ interactions in SYM $N=4$ theory to volume forms on a set of positroid cells of $\Gr(k,n)$.
+This gives a CW complex of some submanifold in $\Gr(k,n)$, and understanding the geometry and topology of these spaces is the subject of ongoing research.
+
+However, the two approaches are not identical: for example, in the case of Wilson loop diagrams with $k=2$ and $n=6$, past work of some of us shows that the manifold is not contractible \cite{casestudy}.
+More generally, it has been shown that the spaces defined by the Amplituhedron and by Wilson loop diagrams are not the same \cite{Amplituhedronsquared}.
+In fact, it is in some ways more natural to consider Deodhar cells of $\mathbb{G}(k, n+1)$ for Wilson loop diagrams; in this case, one gets that the manifold represented by the diagrams is not orientable \cite{non-orientable}.
+
+In this paper we focus on the correspondence between Wilson loop diagrams and positroids, which was first defined in \cite{wilsonloop}.
+Our main results are as follows.
+We first show that two Wilson loop diagrams define the same positroid if and only if they only differ by exact subdiagrams (Theorem~\ref{same matroid iff equiv}); equivalently, this says that the map from Wilson loop diagrams to positroid cells is one-to-one exactly on the subset of diagrams with no non-trivial exact subdiagrams.
+We count the total number of Wilson loop diagrams associated to a positroid cell (Corollary~\ref{number of equiv diagrams}).
+Finally, we show that enumerating the number of distinct positroid cells associated to Wilson loop diagrams is equivalent to enumerating the number of directions of an associahedron (Theorem~\ref{thm:count inequiv diagrams}).
+
+%In that paper, \hlfix{one of us}{see previous comment about self reference convention} with Amat show that there are certain families of diagrams, specifically those with exact subdiagrams, that do map to the same positroid cell.
 In \cite{casestudy} some of us explicitly show that not every positroid cell of a given dimension corresponds to a Wilson loop diagram.
-In this paper, we better enumerate this correspondence.
-We show that the map from Wilson loop diagrams to positroid cells is one to one exactly on the subset of diagrams with no non-trivial exact subdiagrams.
-We show that exact diagrams correspond to uniform matroids, and that contraction by exact subdiagrams has special matroidal properties.
+
+%In this paper, we characterize this correspondence more precisely.
+Specifically, we show that  We show that exact diagrams correspond to uniform matroids, and that contraction by exact subdiagrams has useful matroidal properties.
 Further, given a Wilson loop diagram with a non-trivial exact subdiagram, we count the total number of Wilson loop diagrams that correspond to that same positroid cell.
-While we do not count the number of distinct positroid cells that correspond to Wilson loop diagrams, we do show that this enumeration is equivalent to enumerating the number of directions of an associahedron.
+While we do not count the number of distinct positroid cells that correspond to Wilson loop diagrams, we do show that this
 
@@
 
-We proceed in Section~\ref{section overall background} with the required definitions for Wilson loop diagrams (subsection~\ref{section WLD background}) and matroids (subsection~\ref{sec matroid background}).
-Wilson loop diagrams  are said to be admissible when they correspond to $N^kMHV$ diagrams, or mathematically according to Definition~\ref{admisdfn}.
-The other key definition in this section is Definition~\ref{equivdfn}, which gives an equivalence relation on admissible Wilson loop diagrams.
-The connection to matroids is stated precisely in Theorem \ref{thm WLD defines matroid}.
+Section~\ref{section overall background} summarizes the required background, with definitions for Wilson loop diagrams given in subsection~\ref{section WLD background} and matroids in subsection~\ref{sec matroid background}.
+Key definitions include {\em admissible} Wilson loop diagrams (Definition~\ref{admisdfn}), {\em exact} subdiagrams (Definition~\ref{def:exact diagram}), and an equivalence relation on admissible Wilson loop diagrams (Definition~\ref{equivdfn}).
+The connection between matroids and Wilson loop diagrams is stated precisely in Theorem \ref{thm WLD defines matroid}.
 
 The main result of Section~\ref{sec equiv} is Theorem~\ref{same matroid iff equiv}, which says that two Wilson loop diagrams define the same matroid if and only if they are equivalent.
-In subsection~\ref{sec: polygon partitions} we relate certain subdiagrams (the {\em exact} subdiagrams, Definition~\ref{def:exact diagram}) of Wilson loop diagrams to triangulations of polygons, and then in subsection~\ref{sec: exact diagram matroidal props} we examine the matroidal properties of the exact subdiagrams.
-Specifically, we show that a subdiagram of a Wilson loop diagrams $W$ defines a uniform matroid if and only if the subdiagram is exact (Theorem \ref{exactuniformthm}), and that this uniform matroid is equal to the dual of the matroid associated to $W$ restricted to the exact subdiagram (Remark \ref{remark exact dual restiction}).
-Subsection~\ref{sec: matroids and equivalence} is devoted to the proof of Theorem~\ref{same matroid iff equiv}, along with an easy corollary which gives a formula for the size of each equivalence class (Corollary~\ref{number of equiv diagrams}).
+In subsection~\ref{sec: polygon partitions} we relate exact subdiagrams of Wilson loop diagrams to triangulations of polygons, and hence show that every Wilson loop diagram can be uniquely decomposed as a collection of exact subdiagrams (Corollary~\ref{uniqueproppartitioncor}).
+In subsection~\ref{sec: exact diagram matroidal props} we examine the matroidal properties of the exact subdiagrams, and prove that a subdiagram of a Wilson loop diagrams defines a uniform matroid if and only if the subdiagram is exact (Theorem \ref{exactuniformthm}).
+This uniform matroid is in fact equal to the dual matroid restricted to the exact subdiagram (Remark \ref{remark exact dual restiction}).
+Finally, subsection~\ref{sec: matroids and equivalence} is devoted to the proof of Theorem~\ref{same matroid iff equiv}, along with an easy corollary which gives a formula for the size of each equivalence class (Corollary~\ref{number of equiv diagrams}).
 
 Having identified the equivalence classes and their sizes, the next natural question is to identify the number of inequivalent diagrams under this equivalence relation.
-The main result of Section~\ref{sec associahedron} is Theorem \ref{thm:count inequiv diagrams} which shows that the set of admissible Wilson loop diagrams (up to equivalence) is in bijection with the set of faces in the associahedron (up to parallelism).
-Towards this result we go over some relevant background on polytopes in subsection~\ref{sec polytope background}, and then give the main result in subsection~\ref{sec associahedron results} in the form of two propositions: Propositions~\ref{prop easy way} and~\ref{prop hard way}.
+The main result of Section~\ref{sec associahedron} is Theorem \ref{thm:count inequiv diagrams}, which shows that the set of admissible Wilson loop diagrams (up to equivalence) is in bijection with the set of faces in the associahedron (up to parallelism).
+Towards this result we go over some relevant background on polytopes in subsection~\ref{sec polytope background}, and then prove the main result in subsection~\ref{sec associahedron results} in the form of two propositions: Proposition~\ref{prop easy way} and Proposition~\ref{prop hard way}.
 
@@
 \begin{dfn}\label{equivdfn}
-Let $W = (\cP,[n])$ and $W' = (\cP',[n])$. Define a relation $\sim$ by $W\sim W'$ if
+
+Let $W = (\cP,[n])$ and $W' = (\cP',[n])$, and say that $W$ and $W'$ are related if
 \begin{enumerate}
@@
 \end{enumerate}
-The transitive closure of $\sim$ (which by an abuse of notation we also denote by $\sim$) defines an equivalence relation on the set of admissible Wilson loop diagrams with vertex set $[n]$.
+Let $\sim$ denote the transitive closure of this relation. This is an equivalence relation on the set of all admissible Wilson loop diagrams with vertex set $[n]$.
 \end{dfn}
@@
 Therefore, for any subset of vertices $V \subseteq [n]$, we can consider the restriction $C(W)|_V$ of $C(W)$ consisting of the columns corresponding to $V$.
-Since the non-zero entries of $C(W)$ are independent real variables, the matrix $C(W)|_V$ does not have full rank if and only if there are fewer than $|V|$ rows with non-zero entries.
-This is equivalent to saying that $V$ is a set of dependent columns of $C(W)$ if and only if $|\Prop(V)| < |V|$.
+Since the non-zero entries of $C(W)$ are independent real variables, \hlfix{the matrix $C(W)|_V$ does not have full rank if and only if there are fewer than $|V|$ rows with non-zero entries.}{I don't think this is quite true?} This is equivalent to saying that $V$ is a set of dependent columns of $C(W)$ if and only if $|\Prop(V)| < |V|$.
 Comparing this to Theorem \ref{thm:WLDmatroid}, we see that $M(W)$ is also the matroid realized by $C(W)$.

### 2019-07-09 GWLDCI.tex
some typos fixed and some comments left

@@
 In this paper we give a simple characterization of this lack of injectivity in terms of an equivalence relation on the Wilson loop diagrams, and enumerate the number of different Wilson loop diagrams that correspond to each positroid cell.
-We also study the lack of surjectivity, and show that the number of distinct positroid cells associated to Wilson loop diagrams is given by counting the directions \hlfix{in}{of a?} associahedra.
+We also study the lack of surjectivity, and show that the number of distinct positroid cells associated to Wilson loop diagrams of a given size is given by counting the directions in an associahedron.
 
 The second paper \cite{generalcombinatoricsII} in this series identifies precisely which positroid cell is associated to a given Wilson loop diagram, by giving an algorithm for passing from a Wilson loop diagram to the Grassmann necklace of the associated positroid cell.
-In this manner the authors give a direct path from Wilson loop diagram to positroid cell that circumvents the painstaking process of examining bases sets.
+In this manner we give a direct path from Wilson loop diagram to positroid cell circumventing the painstaking process of examining bases sets.
 With this identification in hand, we also prove that any Wilson loop diagram with $k$ propagators corresponds to a $3k$ dimensional positroid cell, and characterize the volume forms that Wilson loop diagrams associate to each positroid cell.
@@
 As noted above, the \hlfix{first author and Amat}{At other points, we say "some of us" instead of specifying like this.
-Choose a convention} uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that are realized as an element of the positive Grassmannian $\Gr(k,n)$ \cite{wilsonloop}.
+Choose a convention}\note{Response by Karen: I am the cause of the ``some of us'' and similar; it is the kind of phrasing I usually use, and I like it, but I am not strongly attached to it.} uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that are realized as an element of the positive Grassmannian $\Gr(k,n)$ \cite{wilsonloop}.
 In (separate) papers with the second author and Marcott, this work was extended to study these Feynman integrals in terms of positroid cells and the positive Grassmannians \cite{casestudy, non-orientable}.
@@
 In fact, it is in some ways more natural to consider Deodhar cells of $\mathbb{G}(k, n+1)$ for Wilson loop diagrams; in this case, one gets that the manifold represented by the diagrams is not orientable \cite{non-orientable}.
+\note{Check with Cam.}
 
@@
 In subsection~\ref{sec: polygon partitions} we relate exact subdiagrams of Wilson loop diagrams to triangulations of polygons, and hence show that every Wilson loop diagram can be uniquely decomposed as a collection of exact subdiagrams (Corollary~\ref{uniqueproppartitioncor}).
-In subsection~\ref{sec: exact diagram matroidal props} we examine the matroidal properties of the exact subdiagrams, and prove that a subdiagram of a Wilson loop diagrams defines a uniform matroid if and only if the subdiagram is exact (Theorem \ref{exactuniformthm}).
+In subsection~\ref{sec: exact diagram matroidal props} we examine the matroidal properties of the exact subdiagrams, and prove that a subdiagram of a Wilson loop diagram defines a uniform matroid if and only if the subdiagram is exact (Theorem \ref{exactuniformthm}).
 This uniform matroid is in fact equal to the dual matroid restricted to the exact subdiagram (Remark \ref{remark exact dual restiction}).
@@
 \begin{dfn}\label{WLdfn}
-A {\em Wilson loop diagram} is given by the following data: a cyclically ordered set $V$, along with a choice of first vertex (labeled $1$), and a set $\cP$ of $k$ pairs called {\em propagators}, written $\{p_r = (i_r, j_r)\}_{r=1}^k$.
+A {\em Wilson loop diagram} is given by the following data: a cyclically ordered set $V$, along with a choice of first vertex (labeled $1$), and a set $\cP$ of $k$ pairs of elements of $V$ called {\em propagators}, written $\{p_r = (i_r, j_r)\}_{r=1}^k$.
 We write $W = (\cP,V)$ to denote the Wilson loop diagram.
@@
 \item There exist exact subdiagrams $(P, V(P)) \subseteq W$ and $(P', V(P')) \subseteq W'$ with $V(P) =  V(P')$.
-\item The complementary subdiagrams are identical, i.e. $(\cP \setminus P, V(P)^c) = (\cP' \setminus P', V(P')^c)$.
+\item The complementary subdiagrams are identical, i.e.
+$(\cP \setminus P, V(P)^c) = (\cP' \setminus P', V(P')^c)$.\note{I don't want to change it in case I've just misunderstood, but it seems to me that the vertex sets for the complementary subdiagrams should be $[n]$ not $V(P)^c$ and $V(P')^c$.}
 \end{enumerate}
@@
 Therefore, for any subset of vertices $V \subseteq [n]$, we can consider the restriction $C(W)|_V$ of $C(W)$ consisting of the columns corresponding to $V$.
-Since the non-zero entries of $C(W)$ are independent real variables, \hlfix{the matrix $C(W)|_V$ does not have full rank if and only if there are fewer than $|V|$ rows with non-zero entries.}{I don't think this is quite true?} This is equivalent to saying that $V$ is a set of dependent columns of $C(W)$ if and only if $|\Prop(V)| < |V|$.
+Since the non-zero entries of $C(W)$ are independent real variables, \hlfix{the matrix $C(W)|_V$ does not have full rank if and only if there are fewer than $|V|$ rows with non-zero entries.}{I don't think this is quite true?
+I agree, it could for instance have a column of 0s} This is equivalent to saying that $V$ is a set of dependent columns of $C(W)$ if and only if $|\Prop(V)| < |V|$.
 Comparing this to Theorem \ref{thm:WLDmatroid}, we see that $M(W)$ is also the matroid realized by $C(W)$.
@@
 Connecting consecutive vertices gives a graph theoretic cycle called the polygon of $\tau(W)$.
-  \item Each propagator of $W$ defines a chord edge of $\tau(W)$; specifically,  a propagator $(i,j) \in \cP$ defines a chord connecting the vertices $i$ and $j$ in $\tau(W)$.
+  \item Each propagator of $W$ defines a chord \note{We were originally thinking in terms of chord diagrams hence the language ``chord'' but I think ``diagonal'' would be more natural now.
+Any thoughts against before I change it?} edge of $\tau(W)$; specifically,  a propagator $(i,j) \in \cP$ defines a chord connecting the vertices $i$ and $j$ in $\tau(W)$.
   \end{itemize}
@@
 If $W = (\cP, [n])$ is an admissible Wilson loop diagram, then $\tau(W)$ is a simple planar graph whose outer face is a cycle.
-It is embedded such that the vertices all lie on this infinite face\footnote{That is, it is an \emph{outerplanar} graph}.
+It inherits an embedding from $W$ such that the vertices all lie on this infinite face\footnote{That is, it is an \emph{outerplanar} graph}.
 These vertices are cyclically ordered, with a choice of first vertex giving it an additional compatible linear order.
@@
 
+\begin{eg} \label{eg: unique decomposition} For the Wilson loop diagrams and polygon dissections in Example \ref{WLDtopolygonpartition}, the vertex sets $\{1, 2, 3,4\}$ and $\{5, 6, 7, 8\}$ give maximal triangulated pieces for both $\tau(W_1)$ and $\tau(W_3)$.
+The vertex set $\{4,5, 8, 1\}$ is not a triangulation in either polygon dissection.
+\end{eg}
+
 \begin{dfn}
@@
 
-\begin{eg} \label{eg: unique decomposition} For the Wilson loop diagrams and polygon dissections in Example \ref{WLDtopolygonpartition}, the vertex sets $\{1, 2, 3,4\}$ and $\{5, 6, 7, 8\}$ give maximal triangulated pieces for both $\tau(W_1)$ and $\tau(W_3)$.
-The vertex set $\{4,5, 8, 1\}$ is not a triangulation in either polygon dissection.
-\end{eg}
-
 \begin{lem} \label{decompositionlem}
   For $W$ an admissible Wilson loop diagram, the polygon dissection $\tau(W)$ has a unique decomposition into maximal triangulated pieces and edges in the polygon of $\tau(W)$.
+Call this a \emph{maximal decomposition}.
 \end{lem}
@@
 Call this forest $f'$.
-Since $f' \neq f$, there are two trees, $t$ and $t'$ in $f$ and $f'$ that are distinct, but share at least one edge of $T(W)$.
+Since $f' \neq f$, there are two trees, $t$ and $t'$ in $f$ and $f'$ respectively that are distinct, but share at least one edge of $T(W)$.
 Since $f'$ is also maximal, $t'$ is not a subtree of $t$.
 Therefore, the edges of $t'$ can be found in at least two trees in the forest $f$.
-In particular, there is a vertex $v$ in $t'$ that corresponds to a split vertex of $T(W)$ in the original decomposition.
+In particular, there is a non-leaf vertex $v$ in $t'$ that corresponds to a split vertex of $T(W)$ in the original decomposition.
 This implies that $v$ has degree greater than $3$ in $T(W)$, and thus the corresponding face of $\tau(W)$ is not a triangle.
@@
 
-The previous definition makes sense, in fact, for any two polygon dissections of the same polygon, not just for those in the image of $\tau$.
+The previous definition makes sense for any two polygon dissections of the same polygon, not just for those in the image of $\tau$.
 
@@
 \begin{cor} \label{uniqueproppartitioncor}
-Any admissible Wilson loop diagram $W = (\cP, [n])$ can be uniquely decomposed into maximal exact subdiagrams. These maximal subdiagrams partition $\cP$.
+Any admissible Wilson loop diagram $W = (\cP, [n])$ can be uniquely decomposed into maximal exact subdiagrams.
+These maximal subdiagrams partition $\cP$ and correspond to the maximal triangulated pieces of $\tau(W)$.
 \end{cor}
@@
 \item $C = F(\Prop (C))$, i.e. $C$ is a propagator flat.
-\item $F \setminus C$ is an independent set. Furthermore, $F\setminus C$ is an independent flat if and only if $F(\emptyset) = \emptyset$, that is $W$ has no non-supporting vertices.  
+\item $F \setminus C$ is an independent set. Furthermore, $F\setminus C$ is an independent flat if and only if $F(\emptyset) = \emptyset$, that is, $W$ has no non-supporting vertices.  
 \end{enumerate}
@@
 \[
-\rk (B \cup \{w\}) \leq \min\{|B\cup \{w\}|, |\Prop(B\cup \{w\})|\} \leq \min\{|B|+1,|Prop(B)|\},
+\rk (B \cup \{w\}) \leq \min\{|B\cup \{w\}|, |\Prop(B\cup \{w\})|\} \leq \min\{|B|+1,|\Prop(B)|\},
 \]
@@
 \begin{cor} \label{classifyflats}
-  If $F$ is a flat of an admissible Wilson loop diagram, it can be written as the disjoint union of a cyclic propagator flat and an independent set: \bas F =C \sqcup S \eas where $C$ the union of all circuits in $F$.
+  If $F$ is a flat of an admissible Wilson loop diagram, it can be written as the disjoint union of a cyclic propagator flat $C$ and an independent set $S$: \bas F =C \sqcup S \eas where $C$ the union of all circuits in $F$.
 \end{cor}
@@
 Let $W = (\cP, [n])$ be an admissible Wilson loop diagram, and $P \subseteq \cP$. Then: \begin{enumerate}
-\item If $(P,V(P))$ is an exact subdiagram in $W$, then $F(P^c)$ is a dependent flat.
+\item If $(P,V(P))$ is an exact subdiagram in $W$, then $F(P^c)$ is a dependent flat. \note{Should we emphasize that all these $P^c$ are wrt $W$ not the subdiagram?}
 \item If $(P,V(P))$ is a maximal exact subdiagram in $W$, then $F(P^c)$ is a cyclic flat.
@@
 
-To prove the result in the general case, let $(R,V(R))$ be an exact subdiagram of $W$ that is not maximal and let $P$ be the maximal exact subdiagram containing it. That is, $R \subsetneq P$.
+To prove the result in the general case, let $(R,V(R))$ be an exact subdiagram of $W$ that is not maximal and let $(P, V(P))$ be the maximal exact subdiagram containing it. That is, $R \subsetneq P$.
 
@@
 
-We prove the following claim: $W'$ is exact if and only if $V(P)$ contains no circuits $C$ with $\rk (C)< |P|$ in $(P, V(P))$. Since $\rk(M(W'))$ is bounded above by $|P|$, the result follows.
+We prove the following claim: $W'$ is exact if and only if $V(P)$ contains no circuits $C$ with $\rk (C)< |P|$ in $(P, V(P))$.
+Since $\rk(M(W'))$ is bounded above by $|P|$, this will give that  $M(W')$ is uniform.
 
@@
 It is easy to verify that $V(P\setminus\Prop_{W'}(C)) \subseteq V(P)\setminus C$. Since $C \subseteq V(P)$ and $\Prop_{W'}(C) \subseteq P$, it follows from the previous inequality that
-\[|V(P)| - (m+1) \geq |V(P\setminus\Prop(C))| \geq |P| - m + 3.\]
+\[|V(P)| - (m+1) \geq |V(P\setminus\Prop_{W'}(C))| \geq |P| - m + 3.\]
 Simplifying, we obtain $|V(P)| \geq |P| + 4$, i.e. $(P,V(P))$ is not an exact diagram.
@@
 Given a Wilson loop diagram $W = (\cP, [n])$, its associated matroid $M(W)$ corresponds to positroid cells in the CW complex on $\Gr(|\cP|, n)$.
-\end{dfn}
+\end{dfn}\note{How is this a def as it doesn't define the cells?  Also, should it be cell singular}
 
@@
 
-Now consider the propagator flat $F(P)$, whichf is a cyclic flat of rank $|P|$ in both $M(W)$ and $M(W')$ by Lemma \ref{maxexactcomplementrank}.
+Now consider the propagator flat $F(P)$, which is a cyclic flat of rank $|P|$ in both $M(W)$ and $M(W')$ by Lemma \ref{maxexactcomplementrank}.
 Let $B \subseteq F(P)$ be an independent set of rank $|P|$.
@@
 
-For the converse, suppose that $M(W) = M(W') = M$.
+For the converse, \note{I don't want to mess with this because it was one of the delicate proofs, but why can't we just say $M(W)=M(W')$ so the set of uniform submatroids is the same for $M(W)$ and $M(W')$ so by the previous result the set of exact subdiagrams of $W$ and $W'$ is the same, and all this was inclusion preserving so the set of maximal exact subdiagrams is also the same.} suppose that $M(W) = M(W') = M$.
 This immediately implies that $|\cP| = |\cP'|$, so to demonstrate the equivalence of $W$ and $W'$ it suffices to show that for any maximal exact subdiagram $(P,V(P))$ in $W$, there is a corresponding maximal exact subdiagram $(P',V(P'))$ in $W'$ with $V(P) = V(P')$.
@@
 In this section we have characterized the correspondence between Wilson loop diagrams and positroids, showing that Wilson Loop diagrams define the same matroid if and only if they are equivalent (Theorem \ref{same matroid iff equiv}).
-Corollary \ref{number of equiv diagrams} enumerates the fibres of the map from Wilson Loop diagrams to positroids.
+Corollary \ref{number of equiv diagrams} enumerates the fibres\note{Is ``enumerates the fibres'' correct?} of the map from Wilson Loop diagrams to positroids.
 The obvious next question would be to enumerate the number of equivlence classes.
@@
 First we need some background.
-There is a realization of associahedra that is charactertized by polygon partitions.
-In this section, we show that the number of equivalence classes of Wilson loop diagrams correspond to the number of non-parallel faces of the appropriate associahedron (Theorem \ref{thm:count }).
+Associahedra can be defined in terms of polygon partitions.
+In this section, we show that the number of equivalence classes of Wilson loop diagrams correspond to the number of non-parallel faces of the appropriate associahedron (Theorem \ref{thm:count inequiv diagrams}).
 While this section does not give an explicit formula for the number of these faces, we hope that this linkage with a combinatorially well studied object will shed light on the issue in the future.
@@
 \begin{dfn}\label{def:secondary polytope}
-  Let $x_1, \ldots, x_n$ define a convex $n$-gon, and let $T$ be the set of triangulations of this $n$-gon.
+  Let $x_1, \ldots, x_n$ be the corners of a convex $n$-gon in $\mathbb{R}^2$, and let $T$ be the set of triangulations of this $n$-gon.
 For each $t\in T$, define $s_t$ to be the point in $\mathbb{R}^n$ whose $i$th coordinate is the sum of the areas of all triangles of $t$ which are incident to $x_i$.
@@
 Therefore, the map $\tau$ associates to each weakly admissible Wilson loop diagram an $n-3 - k$ dimensional face of the associahedron $A_n$.
-This is illustrated for $n=5$ on the left in Figure~\ref{associahedron5gon}.
+This is illustrated for $n=5$ on the left in Figure~\ref{associahedron5gon}, and with some dissections illustrated for $n=6$ on the right.
 
@@
 Consider the edges of $A_n$ bounding the faces corresponding to $\tau(W)$ and $\tau(X)$.
-These edges have their one quadrilateral within the nontriangulated parts of $\tau(W)$ or $\tau(X)$, but these nontriangulated parts are the same in $\tau(W)$ and $\tau(X)$, so we get a bijection between the edges bounding the face of $\tau(W)$ and the edges bounding the face of $\tau(X)$ which matches edges with the same quadrilateral.
+These edges have their one quadrilateral within the nontriangulated parts of $\tau(W)$ or $\tau(X)$, but these nontriangulated parts are the same in $\tau(W)$ and $\tau(X)$, so we get a bijection between the edges of $A_n$ bounding the face of $\tau(W)$ and the edges of $A_n$ bounding the face of $\tau(X)$ which matches edges with the same quadrilateral.
 
@@
 
-Let $a$ be the area of the quadrilateral and let $a(i,j,k)$ be the area of the triangle with corners $x_i$, $x_j$ and $x_k$ (and similarly for other indices), and let $b_*$ denote the sum of the areas of triangles incident to vertex $*$ which are common to both triangulations.
+Let $a$ be the area of the quadrilateral and let $a(i,j,k)$ be the area of the triangle with corners $x_i$, $x_j$ and $x_k$ (and similarly for other indices), and let $b_i$ denote the sum of the areas of triangles incident to vertex $x_i$ which are common to both triangulations.
 Then $s_{t_1}$ on coordinates $i$, $j$, $k$, $l$ is
@@
 
-This proof is by a symmetrical consruction, where we give a proof with respect to a single edge in $f$, leaving the rest of the argument as read due to the symmetry.
+This proof is by a symmetrical consruction, where we give a proof with respect to a single edge in $f$, leaving the rest of the argument as read due to the symmetry.\note{Actually, since it is by contradiction we don't need to do both directions; one direction already gives a contradiction and that's enough}
 

### 2019-07-09 GWLDCI.tex
more proofreading paper 1

--- 2019-07-08 GWLDCI.tex
@@
 
-Propagators are undirected, so $p = (i,j) = (j,i)$. In previous work, we have used the convention, we write $p = (i,j)$ with  $i +1 \leq j$ relative to the first vertex. \sanote{Susama stopped here}
+Wherever possible, we drop the subscrips on propagators and their identifying vertices.
+Propagators are undirected, so $p = (i,j) = (j,i)$.
+In previous work, we have used the convention, we write $p = (i,j)$ with  $i +1 \leq j$ relative to the first vertex.
 
@@
 There are $k$ wavy lines in the interior of the diagram depicting the propagators, whose endpoints lie on the edges: specifically, a propagator $p =(i,j)$ has one endpoint on the edge joining vertices $i$ and $i+1$ and another endpoint on the edge joining $j$ and $j+1$, where $i+1$ and $j+1$ denote the successor of $i$ and $j$ respectively in the cyclic order on $V$.
+
+To simplify language, we let the edges inherit a cyclic ordering from the vertices:
+
+\begin{dfn}\label{def:edges}
+The $i$th edge of $W$ is the arc that lies between the vertices $i$ and $i+1$.
+\end{dfn}
+
+and thus speak of a propagator $p = (i, j)$ as being supported by the $i$th and $j$th edges. \sanote{moved/altered dfn and sandwiching paragrahs to improve flow}
 
@@
 \begin{enumerate}
-\item For $p = (i_p,j_p) \in \cP$, define $V(p) = \{i_p, i_p+1, j_p, j_p+1\}$ to be the set of vertices supporting $p$.
+\item For $p = (i,j) \in \cP$, define $V(p) = \{i, i+1, j, j+1\}$ to be the set of vertices supporting $p$.
 Similarly, for $P \subseteq \cP$ we define the set $V(P) = \cup_{p \in P} V(p)$ to be the vertex support of $P$.
@@
 This containment is strict if there is any propagator $p$ in $P$ with the property that every vertex in the support of $p$ also supports a propagator not in $P$.
+\sanote{whoever added this last sentence, thank you.
+It is an oft overlooked important point.}
 \end{rmk}
 
-It is sometimes useful to discuss propagators in terms of the edges supporting them (rather than the vertices) so we make the following definition.
-
-\begin{dfn}\label{def:edges}
-The $i$th edge of $W$ is the arc that lies between the vertices $i$ and $i+1$.
-\end{dfn}
-
-In this manner, the propagator $p = (i, j)$ is supported by the $i$th and $j$th edges.
-
 We now define the notion of an admissible diagram, which imposes certain density and non-crossing conditions on the configuration of the propagators.
-The motivation for these conditions comes from the link to SYM $N=4$ theory, where the admissible Wilson loop diagrams are exactly those that correspond to $N^kMHV$ diagrams; see for example \hlfix{[ref].}{I don't think we should go into any detail here, but I wanted to emphasise that there is a reason for choosing these particular conditions.}
+The motivation for these conditions comes from the link to SYM $N=4$ theory, where the admissible Wilson loop diagrams are exactly those that correspond to $N^kMHV$ diagrams; see for example \cite{Amplituhedronsquared}.
 
@@
 In other words, a Wilson loop diagram, $(\cP, [n])$ is admissible only if $n \geq |\cP| +4$, and has no crossing propagators, no propagators of the form $p = (i, i+1)$, and no pairs of propagators that start and end on the same pair of non-adjacent edges.\note{Sian: can we leave this sentence out?
-By dropping ``iff'' to ``only if'' we make it sound like the converse isn't true.}
+By dropping ``iff'' to ``only if'' we make it sound like the converse isn't true.} \sanote{no objections.
+Want to check that we don't use this property in the paper though.
+If not, lets nix}
 
@@
 \end{dfn}
+
+{\color{violet}Note that by Definition \ref{admisdfn}, any single propagator and its support defines an exact subdiagram. These are called trivial sub diagrams.}
 
@@
 For $p = (5, 8)$, we have $V(p) = \{5,6,8,1\}$ and $F(p) = \{6, 7,8\}$: the vertices 1 and 5 are excluded from $F(p)$ since they support other propagators as well, and 7 is included (despite not being in the support of $p$) since it supports no propagators at all.
-Finally, the subdiagram $(\{(2, 4), (1, 4)\}, \{1, 2, 3, 4, 5, \})$ is an example of an exact subdiagram; in fact it is the only non-trivial exact subdiagram in $W$.
+Finally, the subdiagram $(\{(2, 4), (1, 4)\}, \{1, 2, 3, 4, 5, \})$ is an example of an exact subdiagram; \hlfix{in fact it is the only non-trivial exact subdiagram in $W$.}{Either nix or include violet text above.
+I lean towards nixing.}
 \end{eg}
@@
 
-Let $W = (\cP,[n])$ and $W' = (\cP',[n])$, and say that $W$ and $W'$ are related if
+Let $W = (\cP,[n])$ and $W' = (\cP',[n])$ be two admissible subdiagrams. We say that $W$ and $W'$ are related if
 \begin{enumerate}
-\item There exist exact subdiagrams $(P, V(P)) \subseteq W$ and $(P', V(P')) \subseteq W'$ with $V(P) =  V(P')$.
-\item The complementary subdiagrams are identical, i.e. $(\cP \setminus P, V(P)^c) = (\cP' \setminus P', V(P')^c)$.
+\item There exist exact subdiagrams $(P, V(P)) \subseteq W$ and $(P', V(P')) \subseteq W'$ with the same number of propagators and suppored on the same vertices; $|P| = |P'|$ and  $V(P) =  V(P')$.
+\item The complementary subdiagrams (i.e. all other propagators and vertices) are identical, i.e. $(\cP \setminus P, V(P)^c) = (\cP' \setminus P', V(P')^c)$. \sanote{made some changes}
 \end{enumerate}
@@
 	\drawnumbers
-	\drawprop{1}{0}{4}{0}
-	\drawprop{2}{0}{4}{-1}
-    \drawprop{5}{0}{8}{0}
-    \drawprop{5}{1}{7}{0}
+	\drawlabeledprop{1}{0}{4}{0}{\footnotesize $q$}
+	\drawlabeledprop{2}{0}{4}{-1}{\footnotesize  $p$}
+    \drawlabeledprop{5}{0}{8}{0}{\footnotesize \quad $r$}
+    \drawlabeledprop{5}{1}{7}{0}{\footnotesize \quad $s$}
 		\end{scope}
@@
 	\drawnumbers
-	\drawprop{1}{0}{4}{0}
-	\drawprop{2}{0}{4}{-1}
-    \drawprop{5}{0}{8}{0}
-    \drawprop{6}{0}{8}{-1}
+	\drawlabeledprop{1}{0}{4}{0}{\footnotesize $q$}
+	\drawlabeledprop{2}{0}{4}{-1}{\footnotesize $p$}
+    \drawlabeledprop{5}{0}{8}{0}{\footnotesize \quad $u$}
+    \drawlabeledprop{6}{0}{8}{-1}{\footnotesize $v$}
 		\end{scope}
@@
 	\drawnumbers
-	\drawprop{1}{0}{4}{0}
-	\drawprop{1}{1}{3}{0}
-    \drawprop{5}{0}{8}{0}
-    \drawprop{6}{0}{8}{-1}
+	\drawlabeledprop{1}{0}{4}{0}{\footnotesize $a$}
+	\drawlabeledprop{1}{1}{3}{0}{\footnotesize \quad $b$}
+    \drawlabeledprop{5}{0}{8}{0}{\footnotesize \quad $u$}
+    \drawlabeledprop{6}{0}{8}{-1}{\footnotesize $v$}
 		\end{scope}
@@
 We have $W_1 \sim W_2$ because they are identical except on the exact subdiagrams 
-\[(\{(5,8), (5,7)\}, \{5,6,7,8,1\}) \text{ and }(\{(5,8), (6,8)\}, \{5,6,7,8,1\})\] respectively. We also have $W_2 \sim W_3$ due to the exact subdiagrams 
-\[(\{(1,4), (2,4)\}, \{1,2,3,4,5\}) \text{ and }(\{(1,4), (1,3)\}, \{1,2,3,4,5\}).\] 
-However, the difference between $W_1$ and $W_3$ is the union of two exact subdiagrams, which is not itself exact. \end{eg}
-
-As described in the introduction, Wilson loop diagrams come from the study of SYM $N = 4$ in the physics literature and therefore each diagram $W$ is associated to a matrix of data $C(W)$, which we now describe.
+\[(\{r, s\}, \{5,6,7,8,1\}) \text{ and }(\{u, v\}, \{5,6,7,8,1\})\] respectively. We also have $W_2 \sim W_3$ due to the exact subdiagrams 
+\[(\{p, q\}, \{1,2,3,4,5\}) \text{ and }(\{a, b\}, \{1,2,3,4,5\}).\] 
+However, the difference between $W_1$ and $W_3$ is the union of two exact subdiagrams, which is not itself exact. \sanote{labeled propagators to make easier to read} \end{eg}
+
+As described in the introduction, Wilson loop diagrams come from the study of SYM $N = 4$ in the physics literature \st{and therefore} \hlfix{where each propagator corresponds to a section of  a $k$-line bundle over twistor space.
+Thus}{I feel the strike out was too vague.
+The highlighted may be too technical.
+Can someone find baby bear's text?} each diagram $W$ is associated to a matrix of data $C(W)$, which we now describe.
+\sanote{Susama ended here}
 

### 2019-07-09 GWLDCI.tex

--- 2019-07-09 GWLDCI.tex
@@
 
-Let $W = (\cP,[n])$ and $W' = (\cP',[n])$, and say that $W$ and $W'$ are related if
+Let $W = (\cP,[n])$ and $W' = (\cP',[n])$ be two admissible subdiagrams. We say that $W$ and $W'$ are related if
 \begin{enumerate}
-\item There exist exact subdiagrams $(P, V(P)) \subseteq W$ and $(P', V(P')) \subseteq W'$ with $V(P) =  V(P')$.
-\item The complementary subdiagrams are identical, i.e.
-$(\cP \setminus P, V(P)^c) = (\cP' \setminus P', V(P')^c)$.\note{I don't want to change it in case I've just misunderstood, but it seems to me that the vertex sets for the complementary subdiagrams should be $[n]$ not $V(P)^c$ and $V(P')^c$.}
+\item There exist exact subdiagrams $(P, V(P)) \subseteq W$ and $(P', V(P')) \subseteq W'$ with the same number of propagators and suppored on the same vertices; $|P| = |P'|$ and  $V(P) =  V(P')$.
+\item The complementary subdiagrams (i.e.
+all other propagators and vertices) are identical, i.e.
+$(\cP \setminus P, [n]) = (\cP' \setminus P', [n])$.
+\sanote{made some changes} \note{I don't want to change it in case I've just misunderstood, but it seems to me that the vertex sets for the complementary subdiagrams should be $[n]$ not $V(P)^c$ and $V(P')^c$.} \sanote{good call.
+I had misread it to $V(P^c)$ and $V(P{'c}$, which is didn't say, and added some text.
+Fixed now.}
 \end{enumerate}

### 2019-07-10 GWLDCI.tex
read to beginning of 3.1

@@
 
-As described in the introduction, Wilson loop diagrams come from the study of SYM $N = 4$ in the physics literature \st{and therefore} \hlfix{where each propagator corresponds to a section of  a $k$-line bundle over twistor space.
+As described in the introduction, Wilson loop diagrams come from the study of SYM $N = 4$ in the physics literature \st{and therefore} \hlfix{where each propagator corresponds to a section of  a $k$ dimesional vector bundle over twistor space.
 Thus}{I feel the strike out was too vague.
@@
 
-The matrix $C(W)$ will allow us to associate a matroid to each Wilson loop diagram.
+The matrix $C(W)$ allows us to associate a matroid to each Wilson loop diagram.
 We first give a quick summary of the matroid terminology that we will need; it is not intended as a comprehensive introduction to matroids and the interested reader is referred to \cite{OxleyMatroidBook}
@@
 If all the maximal minors of the matrix are nonnegative then the matroid realized by this matrix is called a {\em positroid}.
-In other words a positroid is a matroid\footnote{Note that matroid isomorphism allows arbitrary permutations of the ground set, while positroid isomorphism only allows cyclic permutations in order to preserve the nonnegativity of the minors.
+\sanote{we seem to have eliminated all other reference to positroid in this paper.
+Shoudl we get rid of this?
+I would prefer to keep this, and say that admissible Wilson loop diagrams define positroids, but leave it there.
+For me, the point of this paper is to elucidate the map from WLDs to matroids, showing what we already know about the image is part of that.} In other words a positroid is a matroid\footnote{Note that matroid isomorphism allows arbitrary permutations of the ground set, while positroid isomorphism only allows cyclic permutations in order to preserve the nonnegativity of the minors.
 In particular, the property of being a positroid is not preserved under matroid isomorphism.} that is realized by an element of the totally nonnegative Grassmannian $\Gr(k,n)$.
@@
 In \cite{wilsonloop}, Agarwala and Amat show that every admissible Wilson loop diagram with $k$ propagators defines a positroid of rank $k$, and that the independent sets can be read directly from the diagram:
+
+\sanote{Everything from here applies to weakly admissible. In fact, I think the dfn of admissible in my paper with Amat is what we call weakly admissible here. Should we change to weakly?}
 
@@
 Therefore, for any subset of vertices $V \subseteq [n]$, we can consider the restriction $C(W)|_V$ of $C(W)$ consisting of the columns corresponding to $V$.
-Since the non-zero entries of $C(W)$ are independent real variables, \hlfix{the matrix $C(W)|_V$ does not have full rank if and only if there are fewer than $|V|$ rows with non-zero entries.}{I don't think this is quite true?
-I agree, it could for instance have a column of 0s} This is equivalent to saying that $V$ is a set of dependent columns of $C(W)$ if and only if $|\Prop(V)| < |V|$.
+Since the non-zero entries of $C(W)$ are independent real variables, any subset $V$ that has fewer than $|V|$ rows of non-zero entries does not have full rank.
+This is equivalent to saying that if $V$ is a set of columns of $C(W)$ with $|\Prop(V)| < |V|$, $V$ is a dependent set.
+Any set subset of columns containing such a $V$ cannot be independent.
 Comparing this to Theorem \ref{thm:WLDmatroid}, we see that $M(W)$ is also the matroid realized by $C(W)$.
+\sanote{fixed dependent set argument}
 
@@
 Let $W = (\cP,[n])$ be an admissible Wilson loop diagram, and $M(W)$ its associated matroid.
-Where it will not cause confusion we conflate the two objects, identifying vertices of $W$ with elements of the ground set $[n]$ in $M(W)$.
+Where it will not cause confusion we conflate the two objects, we identify vertices of $W$ with elements of the ground set $[n]$ in $M(W)$.
 
@@
 Let $S \subseteq F(P)$ be an independent set of maximal size.
-Then $\Prop(S) \subseteq P$ (from the definition of $F(P)$) and no subset of $S$ supports fewer propagators than the number of vertices it contains (by Theorem~\ref{thm WLD defines matroid} this is one characterization of an independent set in $M(W)$).
+Then $\Prop(S) \subseteq P$ (from the definition of $F(P)$) and no subset of $S$ supports fewer propagators than the number of vertices it contains (by Theorem~\ref{thm WLD defines matroid}) \st{this is one characterization of an independent set in $M(W)$)}.
 Since $v$ supports a new propagator $q \not\in P$, the set $S \cup \{v\} \subseteq F(P) \cup\{v\}$ also satisfies this independence condition.
+Furthermore, since $S \cup v$ is independent, by the first point in this lemma, $|S| = \rk(S) = \rk F(P)$.
+Similarly $|S \cup v| = |S|+1 = \rk (S \cup v) \leq \rk(F(P) \cup v)$.
 Thus $\rk(F(P) \cup\{v\}) = \rk(F(P)) + 1$, as required.
+\sanote{tweaked}
 \end{proof}
@@
 \section{Matroids, triangulations, and equivalence classes of Wilson loop diagrams}\label{sec equiv}
+
+This section explores the correspondence between Wilson loop diagrams and positroids, established in \cite{wilsonloop}.
+In that paper, the authors show that admissible Wilson loop diagrams define matroids that are also positroids, Theorem \ref{put it back in then ref}.
+Furthermore, they show that if two Wilson loop diagrams are equivalent, they define the same matroid [ref thm].
+
+In this section, we take this analysis further, showing the converse of Theroem [ref] from loc.
+cit.
+(see Theorem \ref{same matroid iff equiv}.
+We also enumerate the number of diagrams that map to an particular matroid, Corollary \ref{number of equiv diagrams}.
+To do this, we establish a connectection between Wilson loop diagrams and chord diagrams, subsection \ref{sec: polygon partitions}, and prove some matroidal properties of exact subdiagrams in subsection \ref{sec: exact diagram matroidal props}  including that they correspond to uniform matroids (Theorem \ref{exactuniformthm}), and the associated matroid can be written as as a contraction by the complementary propagator flat (Theorem \ref{exact diagrams contractions}).\sanote{stopped here}\sanote{need to discuss positroids, and whether positroids should appear earlier so that they can be discussed here.}
 

### 2019-07-10 GWLDCI.tex
more proofreading. Stopped in the middle of Eg 3.10

@@
 In other words, a Wilson loop diagram, $(\cP, [n])$ is admissible only if $n \geq |\cP| +4$, and has no crossing propagators, no propagators of the form $p = (i, i+1)$, and no pairs of propagators that start and end on the same pair of non-adjacent edges.\note{Sian: can we leave this sentence out?
-By dropping ``iff'' to ``only if'' we make it sound like the converse isn't true.} \sanote{no objections.
-Want to check that we don't use this property in the paper though.
-If not, lets nix}
+By dropping ``iff'' to ``only if'' we make it sound like the converse isn't true.} \sanote{Lemma \ref{tausimpleplanarlem} uses the no propagators starting and stopping at same edge}
 
@@
 
-{\color{violet}Note that by Definition \ref{admisdfn}, any single propagator and its support defines an exact subdiagram. These are called trivial sub diagrams.}
+Note that by Definition \ref{admisdfn}, any single propagator and its support defines an exact subdiagram. These are called \emph{trivial} subdiagrams.
 
@@
 For $p = (5, 8)$, we have $V(p) = \{5,6,8,1\}$ and $F(p) = \{6, 7,8\}$: the vertices 1 and 5 are excluded from $F(p)$ since they support other propagators as well, and 7 is included (despite not being in the support of $p$) since it supports no propagators at all.
-Finally, the subdiagram $(\{(2, 4), (1, 4)\}, \{1, 2, 3, 4, 5, \})$ is an example of an exact subdiagram; \hlfix{in fact it is the only non-trivial exact subdiagram in $W$.}{Either nix or include violet text above.
-I lean towards nixing.}
+Finally, the subdiagram $(\{(2, 4), (1, 4)\}, \{1, 2, 3, 4, 5, \})$ is an example of an exact subdiagram; in fact it is the only non-trivial exact subdiagram in $W$.
 \end{eg}
@@
 \begin{dfn}\label{equivdfn} 
-
 Let $W = (\cP,[n])$ and $W' = (\cP',[n])$ be two admissible subdiagrams. We say that $W$ and $W'$ are related if
@@
 Can someone find baby bear's text?} each diagram $W$ is associated to a matrix of data $C(W)$, which we now describe.
-\sanote{Susama ended here}
 
@@
 Then $\Prop(S) \subseteq P$ (from the definition of $F(P)$) and no subset of $S$ supports fewer propagators than the number of vertices it contains (by Theorem~\ref{thm WLD defines matroid}) \st{this is one characterization of an independent set in $M(W)$)}.
-Since $v$ supports a new propagator $q \not\in P$, the set $S \cup \{v\} \subseteq F(P) \cup\{v\}$ also satisfies this independence condition.
+Since $v$ supports a new propagator $q \not\in P$, the set $S \cup  \subseteq F(P) \cup v$ also satisfies this independence condition.
 Furthermore, since $S \cup v$ is independent, by the first point in this lemma, $|S| = \rk(S) = \rk F(P)$.
@@
 We also enumerate the number of diagrams that map to an particular matroid, Corollary \ref{number of equiv diagrams}.
-To do this, we establish a connectection between Wilson loop diagrams and chord diagrams, subsection \ref{sec: polygon partitions}, and prove some matroidal properties of exact subdiagrams in subsection \ref{sec: exact diagram matroidal props}  including that they correspond to uniform matroids (Theorem \ref{exactuniformthm}), and the associated matroid can be written as as a contraction by the complementary propagator flat (Theorem \ref{exact diagrams contractions}).\sanote{stopped here}\sanote{need to discuss positroids, and whether positroids should appear earlier so that they can be discussed here.}
+To do this, we establish a connectection between Wilson loop diagrams and chord diagrams, subsection \ref{sec: polygon partitions}, and prove some matroidal properties of exact subdiagrams in subsection \ref{sec: exact diagram matroidal props}  including that they correspond to uniform matroids (Theorem \ref{exactuniformthm}), and the associated matroid can be written as as a contraction by the complementary propagator flat (Theorem \ref{exact diagrams contractions}).\sanote{need to discuss positroids, and whether positroids should appear earlier so that they can be discussed here.}
 
@@
 
-The equivalence relation on Wilson loop diagrams is defined in terms of exact subdiagrams; thus in order to understand the equivalence, we need a way to extract and compare exact subdiagrams.
+The equivalence relation on Wilson loop diagrams (Definition \ref{equivdfn}) is defined in terms of exact subdiagrams.
+Thus in order to understand the equivalence, we need a way to extract and compare exact subdiagrams.
 We do this via the notion of a polygon dissection of $W$.
@@
   \item Each propagator of $W$ defines a chord \note{We were originally thinking in terms of chord diagrams hence the language ``chord'' but I think ``diagonal'' would be more natural now.
-Any thoughts against before I change it?} edge of $\tau(W)$; specifically,  a propagator $(i,j) \in \cP$ defines a chord connecting the vertices $i$ and $j$ in $\tau(W)$.
+Any thoughts against before I change it?}\sanote{go for it.} edge of $\tau(W)$; specifically,  a propagator $(i,j) \in \cP$ defines a chord connecting the vertices $i$ and $j$ in $\tau(W)$.
   \end{itemize}
@@
 Since $W$ does not admit any propagators of the form $p = (i, i+1)$, there is exactly one edge connecting any two adjacent edges of $\tau(W)$.
-There does not exist two propagators $p,q$ such that both $p$ and $q$ start at edge $i$ and end at edge $j$.
+There do not exist two propagators $p,q$ such that both $p$ and $q$ start at edge $i$ and end at edge $j$.
 Therefore, no other two vertices of $\tau(W)$ can be connected by more than one edge.
@@
 Split every vertex of $T(W)$ which has degree $>3$ (see Figure~\ref{fig:vertex splitting in the dual graph} for an example of this).
+That is, split $T(W)$ at every vertex corresponding to a non-triangle face of $\tau(W)$.
 %By construction, each face of $\tau(W)$ is a polygon.
@@
     \drawchord{6}{8}
- \draw (.1,.1) node {$\bullet$};
-\draw (.1,-.1) node {$\bullet$};
-\draw (-.1,-.1) node {$\bullet$};
-\draw (-.1,.1) node {$\bullet$};
-\draw (-1,.2) node {$\bullet$};	
+ \draw (.2,.2) node {$\bullet$};
+\draw (.2,-.2) node {$\bullet$};
+\draw (-.2,-.2) node {$\bullet$};
+\draw (-.2,.2) node {$\bullet$};
+\draw (-2,.2) node {$\bullet$};	
 \draw (-.5,1.1) node {$\bullet$};
@@
 \draw (1.1,-.5) node {$\bullet$};
-\draw(1.1,-.5) -- (.8,-.3) --(.1,-.1); 
-\draw (-.1, .1) --(-1,.2) -- (-.5,1.1);
+\draw(1.1,-.5) -- (.8,-.3) --(.2,-.2); 
+\draw (-.2, .2) --(-1,.2) -- (-.5,1.1);
 \foreach \i in {1,2,...,8} {
@@
     }
-\draw (45*1:2) --(.1,.1);
-\draw (-.1, -.1) -- (45*5:2);
+\draw (45*1:2) --(.2,.2);
+\draw (-.2, -.2) -- (45*5:2);
 \draw (45*6:2) -- (.8,-.3);
@@
 
-\caption{The polygon dissection $\tau(W_3)$ overlaid with its dual graph $T(W_3)$ (left diagram), and the forest obtained by splitting at all vertices of degree $>3$ (right diagram).}
+\caption{The polygon dissection $\tau(W_3)$ overlaid with its dual graph $T(W_3)$ (left diagram), and the forest obtained by splitting at the only vertex of degree $>3$ (right diagram).}
 \label{fig:vertex splitting in the dual graph}
@@
 
-It will be important in the subsequent section to consider retriangulations.
+It is worth remarking that these maximal decompositions correspond to non-crossing partitions of the Wilson loop diagram, in the sense discussed in \cite{positroids13}.
+
+Next, we introduce the idea of retriangulations. 
 \begin{dfn} \label{retriangulation}
@@
 More casually this definition says that the maximal triangulated pieces of $\tau(W)$ and $\tau(W')$ are the same (so far as their vertex sets are concerned) but that some or all of the triangulated pieces may be differently triangulated while the region being triangulated by each piece (which is defined by the vertex set) remains unchanged.
-Note that these maximal triangulations correspond to non-crossing partitions of the Wilson loop diagram, in the sense discussed in \cite{positroids13}.
-
-The previous definition makes sense for any two polygon dissections of the same polygon, not just for those in the image of $\tau$.
-
-\medskip
+This defintion of retriangulation makes sense for any two polygon dissections of the same polygon, not just for those in the image of $\tau$.
+\sanote{rearranged the paras around dfn \ref{retriangulation} for flow}
 
@@
 
-Every triangulated piece $t$ of an admissible Wilson loop diagram $W$ corresponds to a subdiagram of $W$ by taking the set of propagators $P$ corresponding to edges of $t$ and then taking the subdiagram $W_P = (P, V(P))$.
+For an admissible Wilson loop diagram $W$, every triangulated piece, $t$, of $\tau(W)$ corresponds to a subdiagram of $W$ by taking the set of propagators $P$ corresponding to edges of $t$ and then taking the subdiagram $W_P = (P, V(P))$.
 Conversely, given a subdiagram $W_P = (P, V(P))$ of $W$ we can obtain a subgraph of $\tau(W)$, called $t$, as follows:
@@
   \item the edges of $\tau(W)$ corresponding to propagators of $P$,
-  \item along with the outer edges of $\tau(W)$ for which both their end points are in the vertex set.
+  \item the outer edges of $\tau(W)$ for which both their end points are in the vertex set.
   \end{itemize}
@@
 	\drawprop{5}{0}{7}{0}
+%\draw (0,-2) --(0,2); horiontal
+%\draw (-2,0) --(2,0);
+%\draw (0,-2) node {\footnotesize $-y$};
+%\draw (-2,0) node {\footnotesize $-x$};
+\draw (-.3,1.) node {\footnotesize $p$};
+\draw (-.2,.65) node {\footnotesize $q$};
+\draw (0,-.4) node {\footnotesize $r$};
+\draw (.7, 0) node {\footnotesize $s$};
 		\end{scope}
@@
     \drawchord{5}{7}
+\draw (-.3,1.) node {\footnotesize $p$};
+\draw (-.2,.65) node {\footnotesize $q$};
+\draw (0,-.4) node {\footnotesize $r$};
+\draw (.7, 0) node {\footnotesize $s$};
 	\end{scope}
@@
 
-The set of propagators $P= \{(1,4), (2,4), (4, 8), (1,8) \}$ defines an exact subdiagram of $W$, with $V(P) = \{1,2,3,4,5,8,9\}$.
+The set of propagators $P= \{p,q,r,s \}$ defines an exact subdiagram of $W$, with $V(P) = \{1,2,3,4,5,8,9\}$.
 The corresponding subgraph $t$ of $\tau(W)$ has vertex set $\{1, 2,3, 4, 8\}$.

### 2019-07-11 GWLDCI.tex
proof read through statement of 3.17

@@
 The corresponding subgraph $t$ of $\tau(W)$ has vertex set $\{1, 2,3, 4, 8\}$.
-Note that we don't include vertex 5 because it corresponds to the edge in $W$ that connects vertices 5 and 6, but 6 does not belong to $V(P)$.
-Vertex 9 is excluded for similar reasons.
+Note that we include vertex 3 of $\tau(W)$ because the two endpoints of edge 3 in $W$ (namely the vertices 3 and 4) are both in $V(P)$.
+However, we don't include vertex 5 of $\tau(W)$ because only of its endpoints in $W$ (5 and 6) are in $V(P)$, namely 5.
+The same argument applies to vertices 7, 9 and 10.
+Vertex 6 is excluded because none of its endpoints lie in $V(P)$.
 
@@
 
-The key point to note is that the subgraph $t$ depends on how the propagators of $P$ sit inside $[n]$, not on how they sit in $W_P$ itself.
+The key point to note is that the subgraph $t$ depends on how the propagators of $P$ sit inside $[n]$, not on how they sit in $W_P$, which would have an outer edge between vertices 8 and 1, one between 2 and 4, and another between 4 and 8, but would not include vertex 3.
 In particular, $t$ is not the subgraph of $\tau(W)$ consisting only of edges corresponding to propagators of $P$ (as it may also include some of the outer edges of $\tau(W)$), nor is it the polygon dissection of $(P,V(P))$ viewed as a Wilson loop diagram in its own right (which would have vertex set equal to $V(P)$).
@@
 
-Each of these $m-3+j$ internal edges corresponds to a propagator in $W$; call this set of propagators $P$.
+Each of these $m-3+j$ \hlfix{internal}{diagonal?
+chord?} edges corresponds to a propagator in $W$; call this set of propagators $P$.
 Next we count the size of $V(P)$.
@@
 
-Now suppose $|P|>1$.  Let $j=|P|$, $m=|V(P)|$, and 
-suppose that the set $V(P)$ defines $c$ disjoint cyclic intervals of $[n]$. Then $t$ has $m-c$ vertices.  If $t$ were a triangulation, $t$ would have $j -c$ internal edges.
+Now suppose $|P|>1$.  Let $j=|P|$, $m= j+3=|V(P)|$, and 
+suppose that the set $V(P)$ defines $c$ disjoint cyclic intervals of $[n]$.
+Then $t$ has $m-c$ vertices.
+If $t$ were a triangulation, $t$ would have $j -c$ \hlfix{internal}{here, internal means that it doesn't define the outer face of $t$ in the induced embedding.
+Different use of the word than above?} edges.
 
 The graph $t$ has $j$ edges that come from propagators, and $m - 2c$ edges that come from the boundary polygon of $\tau(W)$.
-Since $t$ has $m-c$ vertices, it has $m-c$ external edges, of which $c$ come from propagators.
+Since $t$ has $m-c$ vertices, it has $m-c$ \hlfix{external}{means defines outer face, not just and outer edge of $\tau(W)$} edges, of which $c$ come from propagators.
 Therefore, of the $j$ edges of $t$ that come from propagators, $j-c$ are internal to the connected component.
@@
 We begin by proving some useful facts about propagator flats, and flats of matroids associated to admissible Wilson loop diagrams more generally.
-Recall from Definition~\ref{VPropdfn} that the propagator flat $F(P)$ of $P \subseteq \cP$ denotes the set $V(P^c)^c$ of vertices that do not support any propagators not in $P$.
+Recall from Definition~\ref{VPropdfn} that the propagator flat $F(P)$ of $P \subseteq \cP$ denotes the set $V(P^c)^c$ of vertices that \st{do not support any propagators not in $P$.}\hlfix{only support propagators in $P$ (or no propagators)}{too many negatives.
+Can we use this instead?}
 
@@
 Let $W = (\cP, [n])$ be an admissible Wilson loop diagram, and $P \subseteq \cP$. Then: \begin{enumerate}
-\item If $(P,V(P))$ is an exact subdiagram in $W$, then $F(P^c)$ is a dependent flat. \note{Should we emphasize that all these $P^c$ are wrt $W$ not the subdiagram?}
-\item If $(P,V(P))$ is a maximal exact subdiagram in $W$, then $F(P^c)$ is a cyclic flat.
+\item If $(P,V(P))$ is an exact subdiagram of $W$, then $F(P^c)$ is a dependent flat in $W$. \note{Should we emphasize that all these $P^c$ are wrt $W$ not the subdiagram?} \sanote{yes. done}
+\item If $(P,V(P))$ is a maximal exact subdiagram of $W$, then $F(P^c)$ is a cyclic flat in $W$.
 \item If $(P,V(P))$ is an exact subdiagram in $W$, then $\rk(F(P^c)) = |P^c|$.
-\end{enumerate}
+\end{enumerate} \sanote{end here}
 \end{lem}

### 2019-07-12 GWLDCI.tex
changes discussed on the phone

@@
 These integrals are calculated via Wilson loops.
-As noted above, the \hlfix{first author and Amat}{At other points, we say "some of us" instead of specifying like this.
-Choose a convention}\note{Response by Karen: I am the cause of the ``some of us'' and similar; it is the kind of phrasing I usually use, and I like it, but I am not strongly attached to it.} uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that are realized as an element of the positive Grassmannian $\Gr(k,n)$ \cite{wilsonloop}.
+As noted above, Agarwala and Marin-Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that are realized as an element of the positive Grassmannian $\Gr(k,n)$ \cite{wilsonloop}.
 In (separate) papers with the second author and Marcott, this work was extended to study these Feynman integrals in terms of positroid cells and the positive Grassmannians \cite{casestudy, non-orientable}.
@@
 
-and thus speak of a propagator $p = (i, j)$ as being supported by the $i$th and $j$th edges. \sanote{moved/altered dfn and sandwiching paragrahs to improve flow}
+Thus we may speak of a propagator $p = (i, j)$ as being supported by the $i$th and $j$th edges.
 
@@
 This containment is strict if there is any propagator $p$ in $P$ with the property that every vertex in the support of $p$ also supports a propagator not in $P$.
-\sanote{whoever added this last sentence, thank you.
-It is an oft overlooked important point.}
 \end{rmk}
@@
 
-In other words, a Wilson loop diagram, $(\cP, [n])$ is admissible only if $n \geq |\cP| +4$, and has no crossing propagators, no propagators of the form $p = (i, i+1)$, and no pairs of propagators that start and end on the same pair of non-adjacent edges.\note{Sian: can we leave this sentence out?
-By dropping ``iff'' to ``only if'' we make it sound like the converse isn't true.} \sanote{Lemma \ref{tausimpleplanarlem} uses the no propagators starting and stopping at same edge}
-
-Note that if we take any admissible Wilson loop diagram and remove the non-supporting vertices, we obtain a weakly admissible Wilson loop diagram that may or may not be admissible itself.
+There are a few things to note here.
+First, what we call weakly admissible is called admissible in \cite{wilsonloop}.
+Many of the results below apply when the hypothesis of admissibility is changed to weak admissibility.
+
+Note also that if two propagators have the same supporting edges, or if a propagator is supported on adjacent edges then the Wilson loop diagram is not admissible.
+
+Further if we take any admissible Wilson loop diagram and remove the non-supporting vertices, we obtain a weakly admissible Wilson loop diagram that may or may not be admissible itself.
 
@@
 \item There exist exact subdiagrams $(P, V(P)) \subseteq W$ and $(P', V(P')) \subseteq W'$ with the same number of propagators and suppored on the same vertices; $|P| = |P'|$ and  $V(P) =  V(P')$.
-\item The complementary subdiagrams (i.e.
-all other propagators and vertices) are identical, i.e.
-$(\cP \setminus P, [n]) = (\cP' \setminus P', [n])$.
-\sanote{made some changes} \note{I don't want to change it in case I've just misunderstood, but it seems to me that the vertex sets for the complementary subdiagrams should be $[n]$ not $V(P)^c$ and $V(P')^c$.} \sanote{good call.
-I had misread it to $V(P^c)$ and $V(P{'c}$, which is didn't say, and added some text.
-Fixed now.}
+\item The complementary subdiagrams (i.e. all other propagators and vertices) are identical, i.e. $(\cP \setminus P, [n]) = (\cP' \setminus P', [n])$.
 \end{enumerate}
@@
 \[(\{p, q\}, \{1,2,3,4,5\}) \text{ and }(\{a, b\}, \{1,2,3,4,5\}).\] 
-However, the difference between $W_1$ and $W_3$ is the union of two exact subdiagrams, which is not itself exact. \sanote{labeled propagators to make easier to read} \end{eg}
-
-As described in the introduction, Wilson loop diagrams come from the study of SYM $N = 4$ in the physics literature \st{and therefore} \hlfix{where each propagator corresponds to a section of  a $k$ dimesional vector bundle over twistor space.
-Thus}{I feel the strike out was too vague.
-The highlighted may be too technical.
-Can someone find baby bear's text?} each diagram $W$ is associated to a matrix of data $C(W)$, which we now describe.
+However, the difference between $W_1$ and $W_3$ is the union of two exact subdiagrams, which is not itself exact.
+
+\end{eg}
+
+As described in the introduction, Wilson loop diagrams come from the study of SYM $N = 4$ in the physics literature and in particular, see \cite{Adamo:2012xe} for details, this gives that each diagram $W$ is associated to a matrix of data $C(W)$, which we now describe.
 
@@
 Comparing this to Theorem \ref{thm:WLDmatroid}, we see that $M(W)$ is also the matroid realized by $C(W)$.
-\sanote{fixed dependent set argument}
 
@@
 Let $S \subseteq F(P)$ be an independent set of maximal size.
-Then $\Prop(S) \subseteq P$ (from the definition of $F(P)$) and no subset of $S$ supports fewer propagators than the number of vertices it contains (by Theorem~\ref{thm WLD defines matroid}) \st{this is one characterization of an independent set in $M(W)$)}.
-Since $v$ supports a new propagator $q \not\in P$, the set $S \cup  \subseteq F(P) \cup v$ also satisfies this independence condition.
-Furthermore, since $S \cup v$ is independent, by the first point in this lemma, $|S| = \rk(S) = \rk F(P)$.
-Similarly $|S \cup v| = |S|+1 = \rk (S \cup v) \leq \rk(F(P) \cup v)$.
+Then $\Prop(S) \subseteq P$ (from the definition of $F(P)$) and no subset of $S$ supports fewer propagators than the number of vertices it contains (by Theorem~\ref{thm WLD defines matroid}).
+Since $v$ supports a new propagator $q \not\in P$, the set $S \cup \{v\} \subseteq F(P) \cup \{v\}$ also satisfies this independence condition.
+Furthermore, since $S \cup \{v\}$ is independent, by the first point in this lemma, $|S| = \rk(S) = \rk F(P)$.
+Similarly $|S \cup \{v\}| = |S|+1 = \rk (S \cup \{v\}) \leq \rk(F(P) \cup \{v\})$.
 Thus $\rk(F(P) \cup\{v\}) = \rk(F(P)) + 1$, as required.
-\sanote{tweaked}
 \end{proof}
@@
 We also enumerate the number of diagrams that map to an particular matroid, Corollary \ref{number of equiv diagrams}.
-To do this, we establish a connectection between Wilson loop diagrams and chord diagrams, subsection \ref{sec: polygon partitions}, and prove some matroidal properties of exact subdiagrams in subsection \ref{sec: exact diagram matroidal props}  including that they correspond to uniform matroids (Theorem \ref{exactuniformthm}), and the associated matroid can be written as as a contraction by the complementary propagator flat (Theorem \ref{exact diagrams contractions}).\sanote{need to discuss positroids, and whether positroids should appear earlier so that they can be discussed here.}
+To do this, we establish a connectection between Wilson loop diagrams and polygon dissections, subsection \ref{sec: polygon partitions}, and prove some matroidal properties of exact subdiagrams in subsection \ref{sec: exact diagram matroidal props}  including that they correspond to uniform matroids (Theorem \ref{exactuniformthm}), and the associated matroid can be written as as a contraction by the complementary propagator flat (Theorem \ref{exact diagrams contractions}).\sanote{need to discuss positroids, and whether positroids should appear earlier so that they can be discussed here.}
 
@@
 Connecting consecutive vertices gives a graph theoretic cycle called the polygon of $\tau(W)$.
-  \item Each propagator of $W$ defines a chord \note{We were originally thinking in terms of chord diagrams hence the language ``chord'' but I think ``diagonal'' would be more natural now.
-Any thoughts against before I change it?}\sanote{go for it.} edge of $\tau(W)$; specifically,  a propagator $(i,j) \in \cP$ defines a chord connecting the vertices $i$ and $j$ in $\tau(W)$.
+  \item Each propagator of $W$ defines a diagonal edge of $\tau(W)$; specifically,  a propagator $(i,j) \in \cP$ defines a diagonal connecting the vertices $i$ and $j$ in $\tau(W)$.
   \end{itemize}
@@
 A \emph{triangulated piece} of $\tau(W)$ is a 2-connected subgraph of $\tau(W)$ which is a triangulation.
-We will take the convention that a subgraph consisting of a single chord edge is called a \emph{trivial} triangulated piece.
+We will take the convention that a subgraph consisting of a single diagonal edge is called a \emph{trivial} triangulated piece.
 A {\em maximal} triangulated piece is one which is not contained in any strictly larger triangulated piece.
@@
 This defintion of retriangulation makes sense for any two polygon dissections of the same polygon, not just for those in the image of $\tau$.
-\sanote{rearranged the paras around dfn \ref{retriangulation} for flow}
 
@@
 \begin{eg}\label{eg:subtrees}
-Consider the following Wilson loop diagram $W$ and its corresponding chord diagram $\tau(W)$. 
+Consider the following Wilson loop diagram $W$ and its corresponding polygon dissection $\tau(W)$. 
 \bas W = \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
@@
 
-Each of these $m-3+j$ \hlfix{internal}{diagonal?
-chord?} edges corresponds to a propagator in $W$; call this set of propagators $P$.
+Each of these $m-3+j$ edges corresponds to a propagator in $W$; call this set of propagators $P$.
 Next we count the size of $V(P)$.
@@
 Now suppose $|P|>1$.  Let $j=|P|$, $m= j+3=|V(P)|$, and 
-suppose that the set $V(P)$ defines $c$ disjoint cyclic intervals of $[n]$.
-Then $t$ has $m-c$ vertices.
-If $t$ were a triangulation, $t$ would have $j -c$ \hlfix{internal}{here, internal means that it doesn't define the outer face of $t$ in the induced embedding.
-Different use of the word than above?} edges.
+suppose that the set $V(P)$ defines $c$ disjoint cyclic intervals of $[n]$. Then $t$ has $m-c$ vertices.  If $t$ were a triangulation, $t$ would have $j -c$ internal edges.
 
 The graph $t$ has $j$ edges that come from propagators, and $m - 2c$ edges that come from the boundary polygon of $\tau(W)$.
-Since $t$ has $m-c$ vertices, it has $m-c$ \hlfix{external}{means defines outer face, not just and outer edge of $\tau(W)$} edges, of which $c$ come from propagators.
+Since $t$ has $m-c$ vertices, it has $m-c$ external edges, of which $c$ come from propagators.
 Therefore, of the $j$ edges of $t$ that come from propagators, $j-c$ are internal to the connected component.
@@
 Combining Lemmas \ref{decompositionlem} and \ref{lem triang to exact} yields the unique decomposition into maximal exact subdiagrams, and Corollary \ref{maxtriangdisjointcor} ensures that no propagator appears in more than one subdiagram in this decomposition.
-Since the chord edges of $\tau(W)$ correspond to the propagators of $W$, the decomposition of $\tau(W)$ induces a partition of $\cP$.
+Since the diagonal edges of $\tau(W)$ correspond to the propagators of $W$, the decomposition of $\tau(W)$ induces a partition of $\cP$.
 \end{proof}
@@
 We begin by proving some useful facts about propagator flats, and flats of matroids associated to admissible Wilson loop diagrams more generally.
-Recall from Definition~\ref{VPropdfn} that the propagator flat $F(P)$ of $P \subseteq \cP$ denotes the set $V(P^c)^c$ of vertices that \st{do not support any propagators not in $P$.}\hlfix{only support propagators in $P$ (or no propagators)}{too many negatives.
-Can we use this instead?}
+Recall from Definition~\ref{VPropdfn} that the propagator flat $F(P)$ of $P \subseteq \cP$ denotes the set $V(P^c)^c$ of vertices that only support propagators in $P$ (or no propagators).
 
@@
 Let $W = (\cP, [n])$ be an admissible Wilson loop diagram, and $P \subseteq \cP$. Then: \begin{enumerate}
-\item If $(P,V(P))$ is an exact subdiagram of $W$, then $F(P^c)$ is a dependent flat in $W$. \note{Should we emphasize that all these $P^c$ are wrt $W$ not the subdiagram?} \sanote{yes. done}
+\item If $(P,V(P))$ is an exact subdiagram of $W$, then $F(P^c)$ is a dependent flat in $W$.
 \item If $(P,V(P))$ is a maximal exact subdiagram of $W$, then $F(P^c)$ is a cyclic flat in $W$.
@@
 In this section we have characterized the correspondence between Wilson loop diagrams and positroids, showing that Wilson Loop diagrams define the same matroid if and only if they are equivalent (Theorem \ref{same matroid iff equiv}).
-Corollary \ref{number of equiv diagrams} enumerates the fibres\note{Is ``enumerates the fibres'' correct?} of the map from Wilson Loop diagrams to positroids.
+Corollary \ref{number of equiv diagrams} enumerates the elements of each fibre of the map from Wilson Loop diagrams to positroids.
 The obvious next question would be to enumerate the number of equivlence classes.
@@
 The map $\tau$ defined in Definition \ref{WLDtriangulationdfn} assigns a dissection of an $n$-gon to a Wilson loop diagram $W = (\cP, [n])$.
-Recall that if $|\cP| = k$, then $\tau(W)$ is a dissection with $k$ chords.
+Recall that if $|\cP| = k$, then $\tau(W)$ is a dissection with $k$ diagonals.
 Therefore, the map $\tau$ associates to each weakly admissible Wilson loop diagram an $n-3 - k$ dimensional face of the associahedron $A_n$.

### 2019-07-15 GNproof.tex
fixed wrong statement in proof

@@
 {\color{violet} Continuing by induction, Since all of $Q_{l-1} \subseteq \cP_{m-1}$ by the induction hypothesis, consider $Q_l \setminus Q_{l-1}$.
-If this et is empty, we are done.
+If this set is empty, we are done.
 Otherwise, let $q \in Q_l \setminus Q_{l-1}$.
-By construction $q$ shares support with a propagators in $\Q_{l-1}$.
+By construction $q$ shares support with a propagator in $Q_{l-1}$.
 Call this propagator $p_j$.
-Let $v_j$ be the fourth propagator of $p_j$ in the $a_{j}-1$ ordering (not assigned to $I_i$.) We have two cases: $a_j-1 < v_j < j_m$ in any cyclice ordering, or $a_j-1 < j_m < v_j$.
-In the first case, following the same argument as the base case, if $q \not \in \cP_{m-1}$, $q$ must be inside $p_j$ in the $a_{j}-1$ ordering.
+Let $v_j$ be the fourth vertex of $p_j$ in the $a_{j}-1$ ordering.
+Since $I_i(p_j) = a_j$, $v_j$ is not assigned to $I_i$ by $p_j$.
+We have two cases: $a_j-1 < v_j < j_m$ in any cyclic ordering, or $a_j-1 < j_m < v_j$.
+(Since $l \neq 0$, we cannot have $v_j = j_m$.) In the first case, following the same argument as the base case, if $q \not \in \cP_{m-1}$, $q$ must be inside $p_j$ in the $a_{j}-1$ ordering.
 Since $q$ cannot contribute its fourth vertex, $I_i(q) < v_j < j_m$.
@@
 
-In the second case, suppose $p_j$ must share an edge with $p_r \in Q_{l-2}$ and $a_j +1  = a_r$.
+Consider the second case ($a_j-1 < j_m < v_j$).
+By construction, $p_j$ must share support with some $p_r \in Q_{l-2}$.
+In particular, \hlfix{$a_j \pm 1  = a_r$, otherwise there would be crossing propagators}{The key here is that the contributing end of $p_j$ shares support with the contributing end of $p_r$.
+Which is on the inside is irrelevant.
+This is what forces $q$ to be inside both $p_r$ and $p_j$}.
 If a $q \not \in \cP_m$ is supported on $a_j$ it lies inside $p_j$ in the $a_{j-1}$ ordering.
 However, for this to happen, and $p_r$ to contribute $a_r$, $q$ must also lie inside $p_r$, which we know by induction cannot happen.
-} \sanote{I hadn't thought through this second case very well when I first wrote the proof. Please check.}
+}
 

### 2019-07-15 GNproof.tex

--- 2019-07-04 GNproof.tex
@@
 This is because if any propagator supported on $x$ is still unassigned when the algorithm reaches $x$, we would have $x \in I_i$.
+We also note that when $p_m$ contributes $I_i(p_m) = a_m$ to the Grassmann necklace, it must be the clockwise-most propagator (amongst those not yet assigned) that is supported on $a_m$ i.e.
+clockwise-most amongst propagators in the set $\cP \setminus \cP_{m-1}$.
 
-Let $J = \{j_1 <_i j_2<_i \dots <_i j_k\}$ be a $k$-set, and suppose that $J<_i I_i$ in the $<_i$-lexicographic order.
+Now, let $J = \{j_1 <_i j_2<_i \dots <_i j_k\}$ be a $k$-set, and suppose that $J<_i I_i$ in the $<_i$-lexicographic order.
 Let $m$ be the minimal index such that $j_m <_i a_m$, i.e.
@@
 
-We define a sequence of sets of propagators by
+In order to exhibit a dependent subset of vertices in $J$, we first define a sequence of sets of propagators by
 \[Q_0 = \Prop(j_m), \qquad Q_{l+1} = \Prop(I_i(Q_l))\quad \forall l \geq 0.\]
@@
 
-We claim that $Q_l \subseteq \cP_{m-1}$ for all $l\geq 0$. The base case follows immediately from the observation above that $\Prop(j_m) \subseteq \cP_{m-1}$.
+We claim that $Q_l \subseteq \cP_{m-1}$ for all $l\geq 0$. The case $l= 0$ follows immediately from the observation above that $\Prop(j_m) \subseteq \cP_{m-1}$.
 
-[induction step; see final page]
+Now assume that $Q_0,\dots,Q_{l-1} \subseteq \cP_{m-1}$, and consider $Q_{l}$.
+If $Q_{l} \setminus Q_{l-1} = \emptyset$ then we are done; if not, let $q \in Q_{l} \setminus Q_{l-1}$.
+By construction there is some propagator $p_r \in Q_{l-1}$ such that $p_r$ and $q$ are both supported on $I_i(p_r) = a_r$.
+If $q$ is clockwise of $p_r$ on vertex $a_r$ then we immediately have $q \in \cP_{m-1}$ as observed above.
+However, if $q$ is counter-clockwise of $p_r$ then we need to show that $p_r$ or another propagator in $Q_l$ constrains the positioning of the other end of $q$ and prevents it from ``escaping'' past $j_m$.
 
-Let $Q:= \lim_{l\rightarrow \infty} Q_l$; by the above, this is well-defined and contained in $\cP_{m-1}$.
+Note that we cannot have $a_r+ 1 = j_m$ when $q$ is counterclockwise of $p_r$, since $q \not\in \Prop(j_m)$.
+If $V(p_r) \subseteq [I_i(p_r)-1,j_m]$, then since $q$ is inside $p_r$ we also have $V(q) \subseteq [a_r-1,j_m]$ and hence $q \in \cP_{m-1}$ by Lemma [no fourth vertex].
+In particular, if $l=1$ then $p_r \in Q_{0} = \Prop(j_m)$ and we must be in this case.
+If not, then there must be some propagator $p_s \in Q_{l-2}$ such that $p_r$ and $p_s$ are both supported on $I_i(p_s)$; further, we can assume that $q$ is not supported on $I_i(p_s)$ since $q \not\in Q_{l-1}$.
+This yields one of the configurations in Figure~\ref{fig:awkward induction step}.
+
+Continuing by induction, Since all of $Q_{l-1} \subseteq \cP_{m-1}$ by the induction hypothesis, consider $Q_l \setminus Q_{l-1}$.
+If this set is empty, we are done.
+Otherwise, let $q \in Q_l \setminus Q_{l-1}$.
+By construction $q$ shares support with a propagator in $Q_{l-1}$.
+Call this propagator $p_j$.
+Let $v_j$ be the fourth vertex of $p_j$ in the $a_{j}-1$ ordering.
+Since $I_i(p_j) = a_j$, $v_j$ is not assigned to $I_i$ by $p_j$.
+We have two cases: $a_j-1 < v_j < j_m$ in any cyclic ordering, or $a_j-1 < j_m < v_j$.
+(Since $l \neq 0$, we cannot have $v_j = j_m$.) In the first case, following the same argument as the base case, if $q \not \in \cP_{m-1}$, $q$ must be inside $p_j$ in the $a_{j}-1$ ordering.
+Since $q$ cannot contribute its fourth vertex, $I_i(q) < v_j < j_m$.
+That is, $q \in \cP_{m-1}$, giving a contradiction.
+
+Consider the second case ($a_j-1 < j_m < v_j$).
+{\color{violet}As above, $q$ shares support with $p_j$.
+More specifically, $a_j \in V(q)$.} By construction, $p_j$ must share support with some $p_r \in Q_{l-2}$.
+In particular, \hlfix{$a_j \pm 1  = a_r$, otherwise there would be crossing propagators}{The key here is that the contributing end of $p_j$ shares support with the contributing end of $p_r$.
+Which is on the inside is irrelevant.
+This is what forces $q$ to be inside both $p_r$ and $p_j$}.
+If a $q \not \in \cP_m$ is supported on $a_j$ it lies inside $p_j$ in the $a_{j-1}$ ordering.
+However, for this to happen, and $p_r$ to contribute $a_r$, $q$ must also lie inside $p_r$, which we know by induction cannot happen.
+
+\begin{figure}[h]
+\includegraphics[scale = 0.3]{awkward_induction_case.jpg}
+\caption{The awkward case of the induction step, where $p_r$ does not form a nice arc to constrain $q$.
+Note that in theory $p_s$ could instead be inside $p_r$ (w.r.t $<_i$), but this does not change the argument and we omit the depiction of this case since it turns out to be impossible.}\label{fig:awkward induction step}
+\end{figure} \sanote{This can't happen. $a_j \in V(q)$ by construction}
+
+Now repeat the argument above with $p_s$ in place of $p_r$; this is valid since we only really need to know that $q$ is inside $p_s$ with respect to $<_{a_s - 1}$.
+Then either $V(p_s) \subseteq [I_i(p_s)-1,j_m]$, in which case we are done (as above), or there exists some $p_t \in Q_{l-3}$ and we continue to iterate the argument.
+Since there are finitely many propagators and we are guaranteed that $V(p_*) \subseteq [I_i(p_*)-1,j_m]$ if we ever reach $p_* \in Q_0$, we eventually construct a propagator that constrains $q$ and ensures that $q \in \cP_{m-1}$.
+This completes the induction step.
+
+Finally, let $Q:= \lim_{l\rightarrow \infty} Q_l$; by the above, this is well-defined and contained in $\cP_{m-1}$.
 We can now show that $J$ is a dependent set, by constructing a subset $U \subseteq J$ that satifies $|\Prop(U)| < |U|$.
@@
 
-\newpage
-
-Half-written induction step:
-
-Before proceeding with the induction, we make an observation about the configuration of propagators in $W$: given that $\Prop(j_m) \subseteq \cP_{m-1}$, we either have a propagator $r$ as in Cases 1 or 2 below, or we are in Case 3.
-
-\vspace{3cm}
-
-In Cases 1 and 2, let $r$ be the outermost of such propagators. In Case 3, we repeat the analysis with earlier vertices:
-
-\vspace{3cm}
-
-Eventually we either reach the starting vertex $i$ (in which case the sequence stabilizes at $Q_l = \cP_{m-1}$), or we reach some index $l_0$ such that $Q_{l_0} \subseteq \cP_{m-1}$ and $Q_{l_0}$ admits a propagator $r$.
-
-Thus the result is true for all $l \leq l_0$; now suppose that $Q_l \subseteq \cP_{m-1}$ for some $l \geq l_0$ and consider $Q_{l+1} = \Prop(I_i(Q_l))$.
-
-Then $q$ is supported on some vertex $a_t$, with $a_t = I_i(p_t)$ for some $p_t \in Q_l$. If $q$ lies to the left of $p_t$, then $q$ must have been assigned before $p_t$, i.e. $q \in P_{m-1}$.
-
-If $q$ lies to the right of $p_t$,
-
 \end{document}

### 2019-07-17 GNproof.tex
changed phrasing of cases to make proof smoother.

@@
 
+Next we prove the base case of $l=1$.
+Else, let $q \in Q_1 \setminus Q_0$.
+By construction $q$ shares support with a propagators in $\Q_{0}$.
+Call this propagator $p_r$.
+By the above, $p_r \in \cP_{m-1}$.
+Suppose that $q \not \in \cP_{m-1}$.
+The violet note above implies that $q$ must be inside $p_j$ in the $a_{j}-1$ ordering.
+If $a_j = j_m-1$, such a $q$ cannot exist (it would force $I_i(q) = j_m$).
+Else, since $q$ cannot contribute its fourth vertex, by Lemma \ref{insert reference}, $I_i(q) < j_m$.
+That is, $q \in \cP_{m-1}$, giving a contradiction.
+There are two types of propagators in $Q_1 \setminus Q_0$, the $q$ such that $j_m$ is inside $q$ in the $a_q-1$ ordering, and the $q$ where $j_m$ is on the outside.
+
 Continuing by induction, Since all of $Q_{l-1} \subseteq \cP_{m-1}$ by the induction hypothesis, consider $Q_l \setminus Q_{l-1}$.
@@
 By construction $q$ shares support with a propagator in $Q_{l-1}$.
-Call this propagator $p_j$.
-Let $v_j$ be the fourth vertex of $p_j$ in the $a_{j}-1$ ordering.
-Since $I_i(p_j) = a_j$, $v_j$ is not assigned to $I_i$ by $p_j$.
-We have two cases: $a_j-1 < v_j < j_m$ in any cyclic ordering, or $a_j-1 < j_m < v_j$.
-(Since $l \neq 0$, we cannot have $v_j = j_m$.) In the first case, following the same argument as the base case, if $q \not \in \cP_{m-1}$, $q$ must be inside $p_j$ in the $a_{j}-1$ ordering.
-Since $q$ cannot contribute its fourth vertex, $I_i(q) < v_j < j_m$.
+Call this propagator $p_r$.
+Let $v_r$ be the fourth vertex of $p_r$ in the $a_{r}-1$ ordering.
+Since $I_i(p_r) = a_j$, $v_j$ is not assigned to $I_i$ by $p_j$.
+We have two cases: there exists a $p_s \in Q_{l-2}$ such that both $p_r$ is on the inside in the $a_s -1$ ordering, and $j_m$ is on the outside, or $p_r$ is on the outside of any $p_s \in Q_{l-2}$ that has $j_m$ on the outside in the $a_s-1$ ordering.
+In the first case, following the same argument as the base case, if $q \not \in \cP_{m-1}$, $q$ must be inside $p_s$ in the $a_{s}-1$ ordering.
+Since $q$ cannot contribute its fourth vertex, $I_i(q) < v_s < j_m$.
 That is, $q \in \cP_{m-1}$, giving a contradiction.
+\sanote{I think this takes care of the picture you sent last night.
+However, it doesn't address your original complaint about the second case.}
 
-Consider the second case ($a_j-1 < j_m < v_j$).
-{\color{violet}As above, $q$ shares support with $p_j$.
-More specifically, $a_j \in V(q)$.} By construction, $p_j$ must share support with some $p_r \in Q_{l-2}$.
-In particular, \hlfix{$a_j \pm 1  = a_r$, otherwise there would be crossing propagators}{The key here is that the contributing end of $p_j$ shares support with the contributing end of $p_r$.
-Which is on the inside is irrelevant.
-This is what forces $q$ to be inside both $p_r$ and $p_j$}.
-If a $q \not \in \cP_m$ is supported on $a_j$ it lies inside $p_j$ in the $a_{j-1}$ ordering.
-However, for this to happen, and $p_r$ to contribute $a_r$, $q$ must also lie inside $p_r$, which we know by induction cannot happen.
+Consider the second case ($a_j-1 < j_m < v_j$). As above, $q$ shares support with $p_j$. More specifically, $a_j \in V(q)$. By construction, $p_r$ must share support with some $p_s \in Q_{l-2}$.
 

### 2019-07-17 GNproof.tex
few more thoughts

@@
 Suppose that $q \not \in \cP_{m-1}$.
-The violet note above implies that $q$ must be inside $p_j$ in the $a_{j}-1$ ordering.
-If $a_j = j_m-1$, such a $q$ cannot exist (it would force $I_i(q) = j_m$).
+The violet note above implies that $q$ must be inside $p_r$ in the $a_{r}-1$ ordering.
+If $a_r = r_m-1$, such a $q$ cannot exist (it would force $I_i(q) = j_m$).
 Else, since $q$ cannot contribute its fourth vertex, by Lemma \ref{insert reference}, $I_i(q) < j_m$.
@@
 Since $I_i(p_r) = a_j$, $v_j$ is not assigned to $I_i$ by $p_j$.
-We have two cases: there exists a $p_s \in Q_{l-2}$ such that both $p_r$ is on the inside in the $a_s -1$ ordering, and $j_m$ is on the outside, or $p_r$ is on the outside of any $p_s \in Q_{l-2}$ that has $j_m$ on the outside in the $a_s-1$ ordering.
+We have two cases: there exists a $p_s \in Q_{l-2}$ such that both $p_r$ is on the inside in the $a_s -1$ ordering, and $j_m$ is on the outside, or $p_r$ is on the outside of any $p_s \in Q_{l-2}$ that has $j_m+1$ on the outside in the $a_s-1$ ordering.
 In the first case, following the same argument as the base case, if $q \not \in \cP_{m-1}$, $q$ must be inside $p_s$ in the $a_{s}-1$ ordering.
@@
 
-Consider the second case ($a_j-1 < j_m < v_j$). As above, $q$ shares support with $p_j$. More specifically, $a_j \in V(q)$. By construction, $p_r$ must share support with some $p_s \in Q_{l-2}$.
+In the second case, if $p_r$ is on the outside of all $p_s \in Q_{l-2}$ that has $j_m+1$ on the outside in the $a_s-1$ ordering.
+{\color{violet}I worry that as soon as we have propagators ``escaping'' $j_m$, i.e.
+having an endpoint in the cyclic intervale $[j_m+1, i-1]$, we start having to include propagators on ``the wrong side'' of the diagram.
+Which is why I don't like this case.}
 
@@
 Note that in theory $p_s$ could instead be inside $p_r$ (w.r.t $<_i$), but this does not change the argument and we omit the depiction of this case since it turns out to be impossible.}\label{fig:awkward induction step}
-\end{figure} \sanote{This can't happen. $a_j \in V(q)$ by construction}
+\end{figure} \sanote{in both these pictures, you would have to have some chain of propagators coming out from $j_m$ to meet $p_s$ and then you have a crossing of propagators issue.
+$p_r$ must be on the outside of $p_s$}
 

### 2019-07-17 GNproof.tex
revert back to proof lost in merge

--- 2019-07-15 GNproof.tex
@@
 
-Continuing by induction, Since all of $Q_{l-1} \subseteq \cP_{m-1}$ by the induction hypothesis, consider $Q_l \setminus Q_{l-1}$.
-If this set is empty, we are done.
-Otherwise, let $q \in Q_l \setminus Q_{l-1}$.
-By construction $q$ shares support with a propagator in $Q_{l-1}$.
-Call this propagator $p_j$.
-Let $v_j$ be the fourth vertex of $p_j$ in the $a_{j}-1$ ordering.
-Since $I_i(p_j) = a_j$, $v_j$ is not assigned to $I_i$ by $p_j$.
-We have two cases: $a_j-1 < v_j < j_m$ in any cyclic ordering, or $a_j-1 < j_m < v_j$.
-(Since $l \neq 0$, we cannot have $v_j = j_m$.) In the first case, following the same argument as the base case, if $q \not \in \cP_{m-1}$, $q$ must be inside $p_j$ in the $a_{j}-1$ ordering.
-Since $q$ cannot contribute its fourth vertex, $I_i(q) < v_j < j_m$.
-That is, $q \in \cP_{m-1}$, giving a contradiction.
-
-Consider the second case ($a_j-1 < j_m < v_j$).
-{\color{violet}As above, $q$ shares support with $p_j$.
-More specifically, $a_j \in V(q)$.} By construction, $p_j$ must share support with some $p_r \in Q_{l-2}$.
-In particular, \hlfix{$a_j \pm 1  = a_r$, otherwise there would be crossing propagators}{The key here is that the contributing end of $p_j$ shares support with the contributing end of $p_r$.
-Which is on the inside is irrelevant.
-This is what forces $q$ to be inside both $p_r$ and $p_j$}.
-If a $q \not \in \cP_m$ is supported on $a_j$ it lies inside $p_j$ in the $a_{j-1}$ ordering.
-However, for this to happen, and $p_r$ to contribute $a_r$, $q$ must also lie inside $p_r$, which we know by induction cannot happen.
-
 \begin{figure}[h]
@@
 Note that in theory $p_s$ could instead be inside $p_r$ (w.r.t $<_i$), but this does not change the argument and we omit the depiction of this case since it turns out to be impossible.}\label{fig:awkward induction step}
-\end{figure} \sanote{This can't happen. $a_j \in V(q)$ by construction}
+\end{figure}
 

### 2019-07-19 GNproofcolumns.tex
Added a new document with a new version of the proof

--- 2019-07-17 GNproof.tex
@@
 
-\usepackage{amssymb, amsmath, verbatim, amsthm,url, multirow,fullpage,mathtools}
+\usepackage{amssymb, amsmath, verbatim, amsthm,url, multirow,fullpage,mathtools, outlines}
 \usepackage{longtable, rotating,makecell,array}
@@
 
-We first note that if $a_{m-1}$ and $a_{m}$ are not consecutive vertices for some $m$, then for any intermediate vertex $a_{m-1}<_i x <_i a_{m}$ we must have $\Prop(x) \subseteq \cP_{m-1}$.
-This is because if any propagator supported on $x$ is still unassigned when the algorithm reaches $x$, we would have $x \in I_i$.
-We also note that when $p_m$ contributes $I_i(p_m) = a_m$ to the Grassmann necklace, it must be the clockwise-most propagator (amongst those not yet assigned) that is supported on $a_m$ i.e.
-clockwise-most amongst propagators in the set $\cP \setminus \cP_{m-1}$.
+Write the matrix $C(W)$ such that the $m^{th}$ row is defined by the propagator $p_m$.
+We give an algorithm to define a new matrix $D(W)$, where the columns of $D(W)$ are linear combinations of the columns of $C(W)$.
 
-Now, let $J = \{j_1 <_i j_2<_i \dots <_i j_k\}$ be a $k$-set, and suppose that $J<_i I_i$ in the $<_i$-lexicographic order.
-Let $m$ be the minimal index such that $j_m <_i a_m$, i.e.
-the first entry at which $J$ and $I_i$ differ.
-We will show that $J$ must be a dependent set.
+Let $r = 1$
+\begin{enumerate}
+\item Replace column $\vec{a}_r$ with a normalized version where the entry $(r, a_r) = 1$. 
+	\begin{enumerate} \item This can be done since $p_r$ is supported on $a_r$, and subsequent steps to do not set this to $0$. 
+	\end{enumerate}
+\item For any $e$ greater than $a_r$ ($a_r <_i e$), if $(r, e) = x_{r,e} \neq 0$, replace column $\vec{e}$ with $\vec{e} - x_{r,e} \vec{a}_r$.  
+	\begin{enumerate}
+	\item Note that this sets every entry of the form $(q, e) = 0$ for $q \leq r$ and $r <_i e$. 
+	\item All non-zero entries $(s, e)$, below $(r, e)$ (i.e.
+$r \leq s$) remain non-zero.
+In fact, each $x_{s,e}$ is a linear combination of rational functions of the variables $c_{p_r, v}$ that define $C(W)$.
+	\end{enumerate}
+\item Increment $r$ and repeat.
+\end{enumerate}
 
-If $\Prop(j_m) = \emptyset$ then $J$ is automatically dependent since the corresponding column of $C(W)$ contains only zeros, so suppose henceforth that $\Prop(j_m) \neq \emptyset$.
-In particular, this implies that $m>1$, since if $m=1$ we would have $\Prop(j_1) \subseteq \cP_0 = \emptyset$.
+The algorithm above has a $1$ in every $(r, a_r)$, with $0$s above it and $0$s in all subsequent (in the $<_i$ order) entries in the $r^{th}$ row. It remains to check the columns not in $I_i$.
 
-In order to exhibit a dependent subset of vertices in $J$, we first define a sequence of sets of propagators by
-\[Q_0 = \Prop(j_m), \qquad Q_{l+1} = \Prop(I_i(Q_l))\quad \forall l \geq 0.\]
-It is easily verified that this is an increasing chain of sets: indeed, if $q \in Q_l$ then $I_i(q) \in I_i(Q_l)$, and since $I_i(q)$ is one of the vertices that supports $q$ we must have $q \in \Prop(I_i(Q_l)) = Q_{l+1}$.
-The sequence therefore stabilizes in finitely many steps, since $\cP$ is finite.
+If $a_k < e$, the $\vec{e}$ column has all $0$ entries by the algorithm. These columns can all be expressed as a linear combination of the columns indicated in $I_i$.
 
-We claim that $Q_l \subseteq \cP_{m-1}$ for all $l\geq 0$. The case $l= 0$ follows immediately from the observation above that $\Prop(j_m) \subseteq \cP_{m-1}$.
+Suppose $a_m + 1 < a_{m+1}$.
+That is, two consecutive propagators, $p_m$ and $p_{m+1}$ do not contribute consecutive indicies.
+(Without loss of generality, assume that $m$ is the smallest integer for which this is true.) We claim at the vertices in the cyclic interval $[a_m+1, a_{m+1}-1]$ are also columns of $0$s in $D(W)$.
+First note that they only support propagators in $\cP_m$.
+Indeed, if $v \in [a_m+1, a_{m+1}-1]$, and $v$ supported such a propagator, $q \in \Prop(v) \setminus \cP_m$, then $q$ would not have contributed to $I_i$ by the time the algorithm reached $v$, forcing $q$ to contribute either after $p_m$ and before $p_{m+1}$, which is a contradiction, or $q = p_{m+1}$, which contradicts $v < a_{m+1}$.
 
-Now assume that $Q_0,\dots,Q_{l-1} \subseteq \cP_{m-1}$, and consider $Q_{l}$.
-If $Q_{l} \setminus Q_{l-1} = \emptyset$ then we are done; if not, let $q \in Q_{l} \setminus Q_{l-1}$.
-By construction there is some propagator $p_r \in Q_{l-1}$ such that $p_r$ and $q$ are both supported on $I_i(p_r) = a_r$.
-If $q$ is clockwise of $p_r$ on vertex $a_r$ then we immediately have $q \in \cP_{m-1}$ as observed above.
-However, if $q$ is counter-clockwise of $p_r$ then we need to show that $p_r$ or another propagator in $Q_l$ constrains the positioning of the other end of $q$ and prevents it from ``escaping'' past $j_m$.
+Therefore, for column $\vec{v}$ to have a non-zero entry, there must exists a $q$ that contributes after $p_m$ supported on an $a_{r_1}$ (with $r_1 < m$) and a sequence $\{a_{r_1} \ldots a_{r_j}, v\}$ such that each contibuting propagator is supported on the next assigned vertex in the series, $p_{r_i} \in \Prop(a_{r_{i+1}})$ and $p_{r_j} \in \Prop(v)$.\sanote{Key condition to check that I haven't missed any cases.}
+We show that this cannot happen.
+Note that when $p_{r_1}$ contributes $I_i(p_{r_1}) = a_{r_1}$ to the Grassmann necklace, it must be the clockwise-most propagator (amongst those not yet assigned) that is supported on $a_{r_1}$ i.e.
+clockwise-most amongst propagators in the set $\cP \setminus \cP_{r_1-1}$.
+Therefore, if $q$ is assigned after $p_{r_1}$ but also supported on $a_{r_1}$, $q$ must be inside $p_{r_1}$ in the $a_{r_1} -1$ ordering.
+However, we know that $p_{r_1}$ is also supported on $a_{r_2} >_i a_{r_2}$.
+This either means that $q$ is also supported on $a_{r_2}$, in which case, we may start the above sequence from $a_{r_2}$, or that $q$ contributes a vertex in the interval $[a_{r_1} +1,a_{r_2} -1]$, which implies that $q$ contributes before $p_{m+1}$, which is a contradition.
 
-Note that we cannot have $a_r+ 1 = j_m$ when $q$ is counterclockwise of $p_r$, since $q \not\in \Prop(j_m)$.
-If $V(p_r) \subseteq [I_i(p_r)-1,j_m]$, then since $q$ is inside $p_r$ we also have $V(q) \subseteq [a_r-1,j_m]$ and hence $q \in \cP_{m-1}$ by Lemma [no fourth vertex].
-In particular, if $l=1$ then $p_r \in Q_{0} = \Prop(j_m)$ and we must be in this case.
-If not, then there must be some propagator $p_s \in Q_{l-2}$ such that $p_r$ and $p_s$ are both supported on $I_i(p_s)$; further, we can assume that $q$ is not supported on $I_i(p_s)$ since $q \not\in Q_{l-1}$.
-This yields one of the configurations in Figure~\ref{fig:awkward induction step}.
-
-\begin{figure}[h]
-\includegraphics[scale = 0.3]{awkward_induction_case.jpg}
-\caption{The awkward case of the induction step, where $p_r$ does not form a nice arc to constrain $q$.
-Note that in theory $p_s$ could instead be inside $p_r$ (w.r.t $<_i$), but this does not change the argument and we omit the depiction of this case since it turns out to be impossible.}\label{fig:awkward induction step}
-\end{figure}
-
-Now repeat the argument above with $p_s$ in place of $p_r$; this is valid since we only really need to know that $q$ is inside $p_s$ with respect to $<_{a_s - 1}$.
-Then either $V(p_s) \subseteq [I_i(p_s)-1,j_m]$, in which case we are done (as above), or there exists some $p_t \in Q_{l-3}$ and we continue to iterate the argument.
-Since there are finitely many propagators and we are guaranteed that $V(p_*) \subseteq [I_i(p_*)-1,j_m]$ if we ever reach $p_* \in Q_0$, we eventually construct a propagator that constrains $q$ and ensures that $q \in \cP_{m-1}$.
-This completes the induction step.
-
-Finally, let $Q:= \lim_{l\rightarrow \infty} Q_l$; by the above, this is well-defined and contained in $\cP_{m-1}$.
-We can now show that $J$ is a dependent set, by constructing a subset $U \subseteq J$ that satifies $|\Prop(U)| < |U|$.
-
-Specifically, we take $U = I_i(Q) \cup \{j_m\}$.
-This is a subset of $J$ because $I_i$ and $J$ agree on their first $m-1$ terms and $Q \subseteq \cP_{m-1}$.
-Further, we have $j_m \not\in I_i(Q)$, so $|U| = |I_i(Q)| + 1 = |Q| +1$.
-On the other hand, since $\Prop(j_m) \subseteq Q$, we have
-\[\Prop(U) = \Prop(I_i(Q)) \cup \Prop(j_m) = Q\]
-by the construction of $Q$, and hence $|\Prop(U)| = |Q| < |U|$. Thus $J$ is a dependent set, and the Grassmann necklace $(I_1,\dots,I_n)$ constructed from $W$ does indeed define the positroid $M(W)$.
+Therefore, any set of the form $\{a_1 \ldots a_m, v\}$ is linearly dependent in $C(W)$.
+Thus any $J$ lexicographically smaller than $I_i$ with respect to $<_i$ must contain a set of this form, we show that $J$ is not linearly dependent.
 \end{proof}
-
 \end{document}

### 2019-07-20 GNproofcolumns.tex
clarified GNproofcolumns

@@
 
-The algorithm above has a $1$ in every $(r, a_r)$, with $0$s above it and $0$s in all subsequent (in the $<_i$ order) entries in the $r^{th}$ row. It remains to check the columns not in $I_i$.
+Note that if $p_s \in \Prop(a_r)$ with $r < s$, step 2 of this algorithm means that for all $v \in V(p_r)$ that come after $a_r$ ($a_r <_i v$) the entry $x_{s, v}$ is non-zero.
+Upon termination of the algorithm above, $D(W)$ has a $1$ in every $(r, a_r)$, with $0$s above it and $0$s in all subsequent (in the $<_i$ order) entries in the $r^{th}$ row.
+It remains to check the columns not in $I_i$.
 
@@
 First note that they only support propagators in $\cP_m$.
-Indeed, if $v \in [a_m+1, a_{m+1}-1]$, and $v$ supported such a propagator, $q \in \Prop(v) \setminus \cP_m$, then $q$ would not have contributed to $I_i$ by the time the algorithm reached $v$, forcing $q$ to contribute either after $p_m$ and before $p_{m+1}$, which is a contradiction, or $q = p_{m+1}$, which contradicts $v < a_{m+1}$.
+Indeed, if $v \in [a_m+1, a_{m+1}-1]$, and $v$ supported such a propagator, $q \in \Prop(v) \setminus \cP_m$, then $q$ would not have contributed to $I_i$ by the time the algorithm reached $v$, forcing $q$ to contribute either after $p_m$ and before $p_{m+1}$, which forces $q = p_{m+1}$, which contradicts $v < a_{m+1}$.
 
-Therefore, for column $\vec{v}$ to have a non-zero entry, there must exists a $q$ that contributes after $p_m$ supported on an $a_{r_1}$ (with $r_1 < m$) and a sequence $\{a_{r_1} \ldots a_{r_j}, v\}$ such that each contibuting propagator is supported on the next assigned vertex in the series, $p_{r_i} \in \Prop(a_{r_{i+1}})$ and $p_{r_j} \in \Prop(v)$.\sanote{Key condition to check that I haven't missed any cases.}
+Therefore, for column $\vec{v}$ to have a non-zero entry, there must exists a $q$ that contributes after $p_m$ supported on an $a_{r_1}$ (with $r_1 < m$) and a an increasing sequence $\{a_{r_1} <_i \ldots <_i a_{r_j} <_i v\}$ such that each contibuting propagator is supported on the next assigned vertex in the series, $p_{r_i} \in \Prop(a_{r_{i+1}})$ and $p_{r_j} \in \Prop(v)$.\sanote{Key condition to check that I haven't missed any cases.}
 We show that this cannot happen.
@@
 Therefore, if $q$ is assigned after $p_{r_1}$ but also supported on $a_{r_1}$, $q$ must be inside $p_{r_1}$ in the $a_{r_1} -1$ ordering.
-However, we know that $p_{r_1}$ is also supported on $a_{r_2} >_i a_{r_2}$.
+However, we know that $p_{r_1}$ is also supported on $a_{r_2} >_i a_{r_1}$.
 This either means that $q$ is also supported on $a_{r_2}$, in which case, we may start the above sequence from $a_{r_2}$, or that $q$ contributes a vertex in the interval $[a_{r_1} +1,a_{r_2} -1]$, which implies that $q$ contributes before $p_{m+1}$, which is a contradition.

### 2019-07-22 GWLDCI.tex
paper 1 readthrough

@@
 
-In \cite{wilsonloop} the first author and Amat showed that every admissible Wilson loop diagrams can be identified with a unique positroid cell, and observed that this mapping is neither one-to-one nor onto.
+In \cite{wilsonloop} Agarwala and Amat showed that every admissible Wilson loop diagrams can be identified with a unique positroid cell, and observed that this mapping is neither one-to-one nor onto.
 In this paper we give a simple characterization of this lack of injectivity in terms of an equivalence relation on the Wilson loop diagrams, and enumerate the number of different Wilson loop diagrams that correspond to each positroid cell.
@@
 The second paper \cite{generalcombinatoricsII} in this series identifies precisely which positroid cell is associated to a given Wilson loop diagram, by giving an algorithm for passing from a Wilson loop diagram to the Grassmann necklace of the associated positroid cell.
-In this manner we give a direct path from Wilson loop diagram to positroid cell circumventing the painstaking process of examining bases sets.
+In this manner we give a direct path from Wilson loop diagram to positroid cell, circumventing the painstaking process of examining sets of bases.
 With this identification in hand, we also prove that any Wilson loop diagram with $k$ propagators corresponds to a $3k$ dimensional positroid cell, and characterize the volume forms that Wilson loop diagrams associate to each positroid cell.
@@
 As noted above, Agarwala and Marin-Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that are realized as an element of the positive Grassmannian $\Gr(k,n)$ \cite{wilsonloop}.
-In (separate) papers with the second author and Marcott, this work was extended to study these Feynman integrals in terms of positroid cells and the positive Grassmannians \cite{casestudy, non-orientable}.
+In (separate) papers with Fryer and Marcott, this work was extended to study these Feynman integrals in terms of positroid cells and the positive Grassmannians \cite{casestudy, non-orientable}.
 Others have tried different approaches to define a geometric space associated to these integrals in a manner similar to the Amplituhedron \cite{Amplituhedronsquared, HeslopStewart}.
@@
 
-However, the two approaches are not identical: for example, in the case of Wilson loop diagrams with $k=2$ and $n=6$, past work of some of us shows that the manifold is not contractible \cite{casestudy}.
+However, the two approaches are not identical: for example, in the case of Wilson loop diagrams with $k=2$ and $n=6$, past work of Agarwala and Fryer shows that the manifold is not contractible \cite{casestudy}.
 More generally, it has been shown that the spaces defined by the Amplituhedron and by Wilson loop diagrams are not the same \cite{Amplituhedronsquared}.
@@
 
-Wherever possible, we drop the subscrips on propagators and their identifying vertices.
+Wherever possible, we drop the subscripts on propagators and their identifying vertices.
 Propagators are undirected, so $p = (i,j) = (j,i)$.
-In previous work, we have used the convention, we write $p = (i,j)$ with  $i +1 \leq j$ relative to the first vertex.
-
-We depict this data as a circle with marked points, called vertices.
-The vertices are labeled by $V$ (preserving the cyclic ordering).
+As in previous work, we follow the convention of writing $p = (i,j)$ with  $i +1 \leq j$ relative to the first vertex.
+
+A Wilson loop diagram can also be represented visually, which provides useful intuition for many of the results that follow.
+We depict the diagram $(\cP,V)$ as a circle with marked points, called {\em vertices}; these vertices are labeled by $V$ (preserving the cyclic ordering).
 The arcs between consecutive vertices are called {\em edges}.
-There are $k$ wavy lines in the interior of the diagram depicting the propagators, whose endpoints lie on the edges: specifically, a propagator $p =(i,j)$ has one endpoint on the edge joining vertices $i$ and $i+1$ and another endpoint on the edge joining $j$ and $j+1$, where $i+1$ and $j+1$ denote the successor of $i$ and $j$ respectively in the cyclic order on $V$.
+There are also $k$ wavy lines in the interior of the diagram depicting the propagators, whose endpoints lie on the edges: specifically, a propagator $p =(i,j)$ has one endpoint on the edge joining vertices $i$ and $i+1$ and another endpoint on the edge joining $j$ and $j+1$, where $i+1$ and $j+1$ denote the successor of $i$ and $j$ respectively in the cyclic order on $V$.
 
@@
 
-Note also that if two propagators have the same supporting edges, or if a propagator is supported on adjacent edges then the Wilson loop diagram is not admissible.
-
-Further if we take any admissible Wilson loop diagram and remove the non-supporting vertices, we obtain a weakly admissible Wilson loop diagram that may or may not be admissible itself.
+Note also that if two propagators have the same supporting edges, or if a propagator is supported on adjacent edges, then the Wilson loop diagram is not admissible.
+
+Further, if we take any admissible Wilson loop diagram and remove the non-supporting vertices, we obtain a weakly admissible Wilson loop diagram that may or may not be admissible itself.
 
@@
 
-Note that by Definition \ref{admisdfn}, any single propagator and its support defines an exact subdiagram. These are called \emph{trivial} subdiagrams.
+Note that by Definition \ref{admisdfn}, any single propagator and its support defines an exact subdiagram. These are called \emph{trivial} exact subdiagrams.
 
@@
 For $p = (5, 8)$, we have $V(p) = \{5,6,8,1\}$ and $F(p) = \{6, 7,8\}$: the vertices 1 and 5 are excluded from $F(p)$ since they support other propagators as well, and 7 is included (despite not being in the support of $p$) since it supports no propagators at all.
-Finally, the subdiagram $(\{(2, 4), (1, 4)\}, \{1, 2, 3, 4, 5, \})$ is an example of an exact subdiagram; in fact it is the only non-trivial exact subdiagram in $W$.
+Finally, the subdiagram $(\{(2, 4), (1, 4)\}, \{1, 2, 3, 4, 5\})$ is an example of an exact subdiagram; in fact it is the only non-trivial exact subdiagram in $W$.
 \end{eg}
@@
 \begin{enumerate}
-\item There exist exact subdiagrams $(P, V(P)) \subseteq W$ and $(P', V(P')) \subseteq W'$ with the same number of propagators and suppored on the same vertices; $|P| = |P'|$ and  $V(P) =  V(P')$.
+\item There exist exact subdiagrams $(P, V(P)) \subseteq W$ and $(P', V(P')) \subseteq W'$ with the same number of propagators and supported on the same vertices, i.e.
+$|P| = |P'|$ and  $V(P) =  V(P')$.
 \item The complementary subdiagrams (i.e. all other propagators and vertices) are identical, i.e. $(\cP \setminus P, [n]) = (\cP' \setminus P', [n])$.
@@
 	\drawnumbers
-	\drawlabeledprop{1}{0}{4}{0}{\footnotesize $q$}
+	\drawlabeledprop{1}{0}{4}{0}{\footnotesize $q$ \quad}
 	\drawlabeledprop{2}{0}{4}{-1}{\footnotesize  $p$}
-    \drawlabeledprop{5}{0}{8}{0}{\footnotesize \quad $r$}
-    \drawlabeledprop{5}{1}{7}{0}{\footnotesize \quad $s$}
+    \drawlabeledprop{5}{0}{8}{0}{\footnotesize $r$ \ \ }
+    \drawlabeledprop{5}{1}{7}{0}{\footnotesize \quad \ $s$}
 		\end{scope}
@@
 	\drawnumbers
-	\drawlabeledprop{1}{0}{4}{0}{\footnotesize $q$}
+	\drawlabeledprop{1}{0}{4}{0}{\footnotesize $q$ \quad}
 	\drawlabeledprop{2}{0}{4}{-1}{\footnotesize $p$}
-    \drawlabeledprop{5}{0}{8}{0}{\footnotesize \quad $u$}
-    \drawlabeledprop{6}{0}{8}{-1}{\footnotesize $v$}
+    \drawlabeledprop{5}{0}{8}{0}{\footnotesize $u$ \ \ }
+    \drawlabeledprop{6}{0}{8}{-1}{\footnotesize $v$ \ }
 		\end{scope}
@@
 	\drawnumbers
-	\drawlabeledprop{1}{0}{4}{0}{\footnotesize $a$}
-	\drawlabeledprop{1}{1}{3}{0}{\footnotesize \quad $b$}
-    \drawlabeledprop{5}{0}{8}{0}{\footnotesize \quad $u$}
-    \drawlabeledprop{6}{0}{8}{-1}{\footnotesize $v$}
+	\drawlabeledprop{1}{0}{4}{0}{\footnotesize $a$ \quad}
+	\drawlabeledprop{1}{1}{3}{0}{\footnotesize  $b$ \ \ \ }
+    \drawlabeledprop{5}{0}{8}{0}{\footnotesize $u$ \ \ }
+    \drawlabeledprop{6}{0}{8}{-1}{\footnotesize $v$ \quad }
 		\end{scope}
@@
 
-We have $W_1 \sim W_2$ because they are identical except on the exact subdiagrams 
-\[(\{r, s\}, \{5,6,7,8,1\}) \text{ and }(\{u, v\}, \{5,6,7,8,1\})\] respectively. We also have $W_2 \sim W_3$ due to the exact subdiagrams 
+$W_1$ and $W_2$ are related because they are identical except on the exact subdiagrams 
+\[(\{r, s\}, \{5,6,7,8,1\}) \text{ and }(\{u, v\}, \{5,6,7,8,1\})\] respectively. Similarly, $W_2$ and $W_3$ are related due to the exact subdiagrams 
 \[(\{p, q\}, \{1,2,3,4,5\}) \text{ and }(\{a, b\}, \{1,2,3,4,5\}).\] 
@@
 \end{eg}
-
-As described in the introduction, Wilson loop diagrams come from the study of SYM $N = 4$ in the physics literature and in particular, see \cite{Adamo:2012xe} for details, this gives that each diagram $W$ is associated to a matrix of data $C(W)$, which we now describe.
+\medskip
+
+As described in the introduction, Wilson loop diagrams come from the study of SYM $N = 4$ in the physics literature.
+In particular (see \cite{Adamo:2012xe} for details) this gives that each diagram $W$ is associated to a matrix of data $C(W)$, which we now describe.
 
@@
 Therefore, for any subset of vertices $V \subseteq [n]$, we can consider the restriction $C(W)|_V$ of $C(W)$ consisting of the columns corresponding to $V$.
-Since the non-zero entries of $C(W)$ are independent real variables, any subset $V$ that has fewer than $|V|$ rows of non-zero entries does not have full rank.
-This is equivalent to saying that if $V$ is a set of columns of $C(W)$ with $|\Prop(V)| < |V|$, $V$ is a dependent set.
-Any set subset of columns containing such a $V$ cannot be independent.
+Since the non-zero entries of $C(W)$ are independent real variables, if $C(W)|_V$ has fewer than $|V|$ rows of non-zero entries then it not have full rank.
+This is equivalent to saying that if $V$ is a set of columns of $C(W)$ with $|\Prop(V)| < |V|$, then $V$ is a dependent set.
+Any set of columns containing such a $V$ cannot be independent.
 Comparing this to Theorem \ref{thm:WLDmatroid}, we see that $M(W)$ is also the matroid realized by $C(W)$.
@@
 Since $v$ supports a new propagator $q \not\in P$, the set $S \cup \{v\} \subseteq F(P) \cup \{v\}$ also satisfies this independence condition.
-Furthermore, since $S \cup \{v\}$ is independent, by the first point in this lemma, $|S| = \rk(S) = \rk F(P)$.
-Similarly $|S \cup \{v\}| = |S|+1 = \rk (S \cup \{v\}) \leq \rk(F(P) \cup \{v\})$.
-Thus $\rk(F(P) \cup\{v\}) = \rk(F(P)) + 1$, as required.
+
+Since $S$ is independent, it follows from the first point in this lemma that $|S| = \rk(S) = \rk F(P)$. Similarly, 
+\[|S \cup \{v\}| = |S|+1 = \rk (S \cup \{v\}) \leq \rk(F(P) \cup \{v\}) \leq \rk F(P) + 1.\]
+Thus $\rk(F(P) \cup\{v\}) = \rk F(P) + 1$, as required.
 \end{proof}
@@
 
-This section explores the correspondence between Wilson loop diagrams and positroids, established in \cite{wilsonloop}.
+This section explores the correspondence between Wilson loop diagrams and positroids that was established in \cite{wilsonloop}.
 In that paper, the authors show that admissible Wilson loop diagrams define matroids that are also positroids, Theorem \ref{put it back in then ref}.
@@
 
-In this section, we take this analysis further, showing the converse of Theroem [ref] from loc.
+In this section we develop this analysis further, showing the converse of Theorem [ref] from loc.
 cit.
-(see Theorem \ref{same matroid iff equiv}.
-We also enumerate the number of diagrams that map to an particular matroid, Corollary \ref{number of equiv diagrams}.
-To do this, we establish a connectection between Wilson loop diagrams and polygon dissections, subsection \ref{sec: polygon partitions}, and prove some matroidal properties of exact subdiagrams in subsection \ref{sec: exact diagram matroidal props}  including that they correspond to uniform matroids (Theorem \ref{exactuniformthm}), and the associated matroid can be written as as a contraction by the complementary propagator flat (Theorem \ref{exact diagrams contractions}).\sanote{need to discuss positroids, and whether positroids should appear earlier so that they can be discussed here.}
+(see Theorem \ref{same matroid iff equiv}).
+We also enumerate the number of diagrams that map to an particular matroid in Corollary \ref{number of equiv diagrams}.
+To do this, we establish a connection between Wilson loop diagrams and polygon dissections in subsection \ref{sec: polygon partitions}, and uncover some matroidal properties of exact subdiagrams in subsection \ref{sec: exact diagram matroidal props}.
+This includes the fact that exact subdiagrams correspond to uniform matroids (Theorem \ref{exactuniformthm}), and that the associated matroid of an exact subdiagram can be written as as a contraction by the complementary propagator flat (Theorem \ref{exact diagrams contractions}).\sanote{need to discuss positroids, and whether positroids should appear earlier so that they can be discussed here.}
 
@@
 Since the vertices of $\tau(W)$ are labeled by the edges of $W$, which are cyclically ordered, this gives an ordering to the vertices and the outer face of $\tau(W)$ is a cycle.
-Since $W$ does not admit any propagators of the form $p = (i, i+1)$, there is exactly one edge connecting any two adjacent edges of $\tau(W)$.
-There do not exist two propagators $p,q$ such that both $p$ and $q$ start at edge $i$ and end at edge $j$.
+Since $W$ does not admit any propagators of the form $p = (i, i+1)$ due to its admissibility, there is exactly one edge connecting any two adjacent edges of $\tau(W)$.
+Similarly, there does not exist two propagators $p,q$ such that both $p$ and $q$ start at edge $i$ and end at edge $j$.
 Therefore, no other two vertices of $\tau(W)$ can be connected by more than one edge.
@@
 
-By \emph{splitting} a vertex $v$ we will mean replacing $v$ by new vertices $v_1, v_2,\ldots, v_{\text{deg}(v)}$ such that each $v_i$ has exactly one neighbour and the union of the of the $v_i$ is the neighbourhood\footnote{The neighbourhood of a vertex is the set of adjacent vertices} of $v$.
+By \emph{splitting} a vertex $v$ we will mean replacing $v$ by new vertices $v_1, v_2,\ldots, v_{\text{deg}(v)}$ such that each $v_i$ has exactly one neighbour and the union of the $v_i$ is the neighbourhood\footnote{The neighbourhood of a vertex is the set of adjacent vertices} of $v$.
 
@@
 
-Split every vertex of $T(W)$ which has degree $>3$ (see Figure~\ref{fig:vertex splitting in the dual graph} for an example of this).
-That is, split $T(W)$ at every vertex corresponding to a non-triangle face of $\tau(W)$.
+Now split every vertex of $T(W)$ which has degree $>3$; see Figure~\ref{fig:vertex splitting in the dual graph} for an example of this.
+That is, we split $T(W)$ at every vertex corresponding to a non-triangle face of $\tau(W)$.
 %By construction, each face of $\tau(W)$ is a polygon.
@@
 \hlfix{If split each vertex of $T(W)$ if it is strictly greater than $3$ valent.}{???} (In other words, we fail to split exactly when the face is a triangle).
+
 We claim that the connected components of $T(W)$ correspond to the decomposition of $\tau(W)$ into maximal triangulated pieces and edges originally in the polygon of $\tau(W)$.
@@
 %, (if they correspond leaf vertices) or 3,  (if they correspond to triangular faces).
-Trees of $f$ with no trivalent vertices correspond to either edges in the polygon of $\tau(W)$, if they were originally leaves of $T(W)$, or to maximal trivial triangulated pieces.
+Trees of $f$ with no trivalent vertices correspond to either edges in the polygon of $\tau(W)$ (if they were originally leaves of $T(W)$) or to maximal trivial triangulated pieces.
 Splitting at all the faces that are not triangles ensures maximality of the decomposition.
@@
 Call this forest $f'$.
-Since $f' \neq f$, there are two trees, $t$ and $t'$ in $f$ and $f'$ respectively that are distinct, but share at least one edge of $T(W)$.
+Since $f' \neq f$, there are two trees $t$ and $t'$ in $f$ and $f'$ respectively that are distinct, but share at least one edge of $T(W)$.
 Since $f'$ is also maximal, $t'$ is not a subtree of $t$.
@@
 More casually this definition says that the maximal triangulated pieces of $\tau(W)$ and $\tau(W')$ are the same (so far as their vertex sets are concerned) but that some or all of the triangulated pieces may be differently triangulated while the region being triangulated by each piece (which is defined by the vertex set) remains unchanged.
-This defintion of retriangulation makes sense for any two polygon dissections of the same polygon, not just for those in the image of $\tau$.
+This definition of retriangulation makes sense for any two polygon dissections of the same polygon, not just for those in the image of $\tau$.
 
@@
 
-For an admissible Wilson loop diagram $W$, every triangulated piece, $t$, of $\tau(W)$ corresponds to a subdiagram of $W$ by taking the set of propagators $P$ corresponding to edges of $t$ and then taking the subdiagram $W_P = (P, V(P))$.
+For an admissible Wilson loop diagram $W$, every triangulated piece $t$ of $\tau(W)$ corresponds to a subdiagram of $W$ obtained by taking the set of propagators $P$ corresponding to edges of $t$ and then taking the subdiagram $W_P = (P, V(P))$.
 Conversely, given a subdiagram $W_P = (P, V(P))$ of $W$ we can obtain a subgraph of $\tau(W)$, called $t$, as follows:
@@
 %\draw (-2,0) node {\footnotesize $-x$};
-\draw (-.3,1.) node {\footnotesize $p$};
-\draw (-.2,.65) node {\footnotesize $q$};
+\draw (2.7*\angle:0.8*\radius) node {\footnotesize $p$};
+\draw (3.3*\angle:0.45*\radius) node {\footnotesize $q$};
 \draw (0,-.4) node {\footnotesize $r$};
@@
 		\end{scope}
-	\end{tikzpicture}  \; \quad
+	\end{tikzpicture}  \; \qquad
 \tau(W) = \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
@@
     \drawchord{5}{7}
-\draw (-.3,1.) node {\footnotesize $p$};
-\draw (-.2,.65) node {\footnotesize $q$};
+\draw (2.7*\angle:0.8*\radius) node {\footnotesize $p$};
+\draw (3.3*\angle:0.47*\radius) node {\footnotesize $q$};
 \draw (0,-.4) node {\footnotesize $r$};
@@
 The corresponding subgraph $t$ of $\tau(W)$ has vertex set $\{1, 2,3, 4, 8\}$.
-Note that we include vertex 3 of $\tau(W)$ because the two endpoints of edge 3 in $W$ (namely the vertices 3 and 4) are both in $V(P)$.
-However, we don't include vertex 5 of $\tau(W)$ because only of its endpoints in $W$ (5 and 6) are in $V(P)$, namely 5.
+Note that we include vertex 3 of $\tau(W)$ in $t$ because the two endpoints of edge 3 in $W$ (namely the vertices 3 and 4 in $W$) are both in $V(P)$.
+However, we don't include vertex 5 of $\tau(W)$ in $t$because only one of the endpoints of edge 5 in $W$ is in $V(P)$.
 The same argument applies to vertices 7, 9 and 10.
@@
 
-The key point to note is that the subgraph $t$ depends on how the propagators of $P$ sit inside $[n]$, not on how they sit in $W_P$, which would have an outer edge between vertices 8 and 1, one between 2 and 4, and another between 4 and 8, but would not include vertex 3.
+The key point to note is that the subgraph $t$ depends on how the propagators of $P$ sit inside $[n]$, not on how they sit in \hlfix{the subdiagram $(P,V(P))$, which would have an outer edges between vertices 8 and 1, between 2 and 4, and between 4 and 8, but would not include vertex 3}{Sian replaced $W_P$ with $(P,V(P))$ here and now isn't sure if that was right because this sentence doesn't make sense?}.
 In particular, $t$ is not the subgraph of $\tau(W)$ consisting only of edges corresponding to propagators of $P$ (as it may also include some of the outer edges of $\tau(W)$), nor is it the polygon dissection of $(P,V(P))$ viewed as a Wilson loop diagram in its own right (which would have vertex set equal to $V(P)$).
@@
   Let $W$ be an admissible Wilson loop diagram and $\tau(W)$ its polygon dissection.
-The triangulated pieces of $\tau(W)$ correspond to the exact subdiagrams of $W$ using the correspondence described above.
+The triangulated pieces of $\tau(W)$ correspond to the exact subdiagrams of $W$, via the correspondence described above.
 \end{lem}
@@
 
-Suppose $|P|=1$.
-Let $p$ be the element of $P$.
+Suppose $|P|=1$, and let $p$ be the single propagator belonging to $P$.
 The exactness condition on $(P, V(P))$ says that the four supporting vertices of $p$ are distinct.
@@
 \begin{cor}\label{equialentretriangulation}
-Two Wilson loop diagrams, $W$ and $W'$ are equivalent if and only if $\tau(W)$ and $\tau(W')$ differ by retriangulations.
+Two Wilson loop diagrams $W$ and $W'$ are equivalent if and only if $\tau(W)$ and $\tau(W')$ differ by retriangulations.
 \end{cor}
@@
 We begin by proving some useful facts about propagator flats, and flats of matroids associated to admissible Wilson loop diagrams more generally.
-Recall from Definition~\ref{VPropdfn} that the propagator flat $F(P)$ of $P \subseteq \cP$ denotes the set $V(P^c)^c$ of vertices that only support propagators in $P$ (or no propagators).
+Recall from Definition~\ref{VPropdfn} that the propagator flat $F(P)$ of $P \subseteq \cP$ denotes the set $V(P^c)^c$ of vertices that only support propagators in $P$ (or are non-supporting).\note{Sian: I know we discussed the phrasing of this last time so I'm highlighting this change: I replaced ``(or no propagators)'' with ``(or are non-supporting)'' because it was unclear what part of the sentence the ``no propagators'' was attached to.
+Is this clearer?}
 
@@
 \begin{equation}\label{eq:equality in lem decompose flat} |\Prop(C)| = \rk(C) = |B| = \rk(B) .\end{equation}
-Since $\rk(B) \leq |\Prop(B)|$, and $B \subseteq C$ implies that  $\Prop(B) \subseteq \Prop(C)$, it follows that $\Prop(B) = \Prop(C)$.
+Note that $\rk(B) \leq |\Prop(B)|$, and $B \subseteq C$ implies that $\Prop(B) \subseteq \Prop(C)$; combining these facts with equation \eqref{eq:equality in lem decompose flat}, it follows that $\Prop(B) = \Prop(C)$.
 Combining this with the fact that $w \in F(\Prop(C))$, we have $\Prop(B\cup \{w\}) \subseteq \Prop(B)$.
@@
 
-First note that if $(P,V(P))$ is exact then the admissiblity of $W$ guarantees that $V(P) \neq [n]$, so $F(P^c) = V(P)^c$ is not empty.
+First note that if $(P,V(P))$ is exact then the admissibility of $W$ guarantees that $V(P) \neq [n]$, so $F(P^c) = V(P)^c$ is not empty.
 
@@
 
-By similar arguments to Lemma~\ref{lem decompose flat}, the fact that $S$ is independent and that $C$ is the union of all circuits in $F(P^c)$ implies that every element of $S$ is independent of $C$, and therefore ${\rk\big(F(P^c)\big) = \rk(C) + \rk(S)}$.
+By similar arguments to Lemma~\ref{lem decompose flat}, the fact that $S$ is independent and that $C$ is the union of all circuits in $F(P^c)$ implies that every element of $S$ is independent of $C$, and therefore
+\[{\rk\big(F(P^c)\big) = \rk(C) + \rk(S)}.\]% this equation doesn't really need to be displayed, but it was causing a badbox 
 We also know that $\rk(S) = |S|$, by the independence of $S$.
@@
 
-It remains to show that $S$ is an independent set in the subdiagram $(P, V(P))$, so for a contradition suppose otherwise.
+It remains to show that $S$ is an independent set in the subdiagram $(P, V(P))$, so for a contradiction suppose otherwise.
 Then by Theorem \ref{thm WLD defines matroid} there is a subset $U \subseteq S$ such that $|\Prop(U)| < |U|$.
@@
 Let $M = (E,\cB)$ be a matroid, and $S \subseteq E$. The {\em contraction} of $M$ by $S$ is the matroid $M/S = (E \setminus S, \cB / S)$, where
-\[\cB / S = \{B \setminus S \ \big| \ |B\cap S | \text{ is maximal amonst all }B \in \cB\}.\]
+\[\cB / S = \{B \setminus S \ \big| \ |B\cap S | \text{ is maximal amongst all }B \in \cB\}.\]
 \end{dfn}
@@
 We now show that matroids coming from exact subdiagrams have an especially nice structure, namely, they are uniform.
-Recall from Section \ref{sec matroid background} that a uniform matroid of rank $r$ is one in which all sets of size $ \leq r$ are independent.
+Recall from Section \ref{sec matroid background} that a uniform matroid of rank $r$ is a matroid in which all sets of size $ \leq r$ are independent.
 
@@
 In this section we have characterized the correspondence between Wilson loop diagrams and positroids, showing that Wilson Loop diagrams define the same matroid if and only if they are equivalent (Theorem \ref{same matroid iff equiv}).
-Corollary \ref{number of equiv diagrams} enumerates the elements of each fibre of the map from Wilson Loop diagrams to positroids.
-The obvious next question would be to enumerate the number of equivlence classes.
-
-We know from example, for instance \cite{casestudy} that, even after taking the dimension of the positroid cell into consideration\footnote{it is proven in \cite{GWLDII} and \cite{Marcott} that Wilson loop diagrams with $k$ propagators map to $3k$ dimensional positroid cells}, many positroid cells do not appear as admissible Wilson loop diagrams with a fixed number of propagators and vertices.
+Corollary \ref{number of equiv diagrams} enumerates the elements of each fiber of the map from Wilson Loop diagrams to positroids.
+The obvious next question would be to enumerate the number of equivalence classes.
+
+We know from examples (e.g.
+\cite{casestudy}) that \hlfix{even after taking the dimension of the positroid cell into consideration}{Sian: I'm not quite sure what ``taking the dimension into consideration'' means here: do we mean ``even after restricting our attention to cells of dimension $3k$''?}\footnote{it is proven in \cite{generalcombinatoricsII} and \cite{Marcott} that Wilson loop diagrams with $k$ propagators map to $3k$ dimensional positroid cells}, many positroid cells do not appear as admissible Wilson loop diagrams with a fixed number of propagators and vertices.
 That is, the map from admissible Wilson loop diagrams to positroid cells of the correct dimension in the correct Grassmannian neither injective nor surjective.
-We do not obtain a formula for the number of cells, but do obtain an alternate characterization of the equvalence classes which is the subject of the next section.
+We do not obtain a formula for the number of cells, but do obtain an alternate characterization of the equivalence classes which is the subject of the next section.
 
@@
 
-The correspondence between (weakly) admissible Wilson loop diagrams and polygon dissections shown in section \ref{sec: polygon partitions} suggests a connection to associahedra.
-First we need some background.
-Associahedra can be defined in terms of polygon partitions.
-In this section, we show that the number of equivalence classes of Wilson loop diagrams correspond to the number of non-parallel faces of the appropriate associahedron (Theorem \ref{thm:count inequiv diagrams}).
-While this section does not give an explicit formula for the number of these faces, we hope that this linkage with a combinatorially well studied object will shed light on the issue in the future.
+The correspondence between (weakly) admissible Wilson loop diagrams and polygon dissections shown in Section \ref{sec: polygon partitions} suggests a connection to associahedra.
+In order to explore this connection further, we first need some background, which is given in Section~\ref{sec polytope background}.
+
+%Associahedra can be defined in terms of polygon partitions.
+In Section~\ref{sec associahedron results}, we show that the number of equivalence classes of Wilson loop diagrams correspond to the number of non-parallel faces of the appropriate associahedron (Theorem \ref{thm:count inequiv diagrams}).
+While this section does not give an explicit formula for the number of these faces, we hope that this linkage with a well-studied combinatorial object will shed light on the issue in the future.
 
@@
 
-A \emph{polytope} can equivalently be defined as the convex hull of a finite set of points in some $\mathbb{R}^d$ or as the intersection of finitely many closed half spaces in $\mathbb{R}^d$ with the additional property that this intersection is bounded in the sense of not containing any ray (see chapter 0 of \cite{Ziegler}).
+A \emph{polytope} can equivalently be defined as the convex hull of a finite set of points in some $\mathbb{R}^d$, or as the intersection of finitely many closed half spaces in $\mathbb{R}^d$ with the additional property that this intersection is bounded in the sense of not containing any ray (see chapter 0 of \cite{Ziegler}).
 
 A \emph{face} of a polytope is the intersection of the polytope with any hyperplane for which the entire polytope is in one of the closed half-spaces defined by the hyperplane.
-The polytope itself is also considered a face; in the case that that polytope is of full dimension, this definition can be unified by considering linear equalities (including the trivial one) in place of hyperplanes and the corresponding linear inequalities in place of the half-spaces defined by the hyperplane (see chapter 2 of \cite{Ziegler}).
+The polytope itself is also considered a face; in the case that the polytope is of full dimension, this definition can be unified by considering linear equalities (including the trivial one) in place of hyperplanes and the corresponding linear inequalities in place of the half-spaces defined by the hyperplane (see chapter 2 of \cite{Ziegler}).
 
@@
 Fix $n$ and consider dissections of a convex $n$-gon.
-The $n-1$ {\em associahedron} can be given in terms of the dissections of this $n$-gon; the vertices of the associahedron are the triangulations of the $n$-gon while the $k$-dimensional faces are the dissections which are $k$ diagonals away from being a triangulation.
+The $n-1$ {\em associahedron} can be defined in terms of the dissections of this $n$-gon: the vertices of the associahedron are the triangulations of the $n$-gon, while the $k$-dimensional faces are the dissections which are $k$ diagonals away from being a triangulation.
 One face is included in another if the first dissection is a refinement of the second.
@@
 Therefore, the map $\tau$ associates to each weakly admissible Wilson loop diagram an $n-3 - k$ dimensional face of the associahedron $A_n$.
-This is illustrated for $n=5$ on the left in Figure~\ref{associahedron5gon}, and with some dissections illustrated for $n=6$ on the right.
+This is illustrated for $n=5$ on the left in Figure~\ref{associahedron5gon}, and for $n=6$ (with some labels omitted for clarity) on the right.
 
 \begin{figure}
-\includegraphics{associahedron5gon} \hspace{1cm} \includegraphics{associahedron3d}
+\[\includegraphics{associahedron5gon} \hspace{1cm} \includegraphics{associahedron3d}\]
 \caption{Two associahedra, labelled by all and some (respectively) of their polygon dissections.}\label{associahedron5gon}
@@
 
-\begin{figure}
-\includegraphics{triangulate} 
+\begin{figure}[t]
+\[\includegraphics{triangulate} \]
 \caption{The shaded regions are triangulated regions which are the same in $t_1$ and $t_2$.
@@
 
-\begin{figure}
-\includegraphics{configs} 
+\begin{figure}[t]
+\[\includegraphics{configs} \]
 \caption{Up to reflection and to rotation of $x_i$, $x_j$, $x_k$, $x_l$, the possible configurations of the quadrilateral from one dissection and diagonal from the other dissection (thick edge) illustrated together on the same vertex set.}\label{configs}
@@
 
-This proof is by a symmetrical consruction, where we give a proof with respect to a single edge in $f$, leaving the rest of the argument as read due to the symmetry.\note{Actually, since it is by contradiction we don't need to do both directions; one direction already gives a contradiction and that's enough}
+This proof is by a symmetrical construction, where we give a proof with respect to a single edge in $f$, leaving the rest of the argument as read due to the symmetry.\note{Actually, since it is by contradiction we don't need to do both directions; one direction already gives a contradiction and that's enough}
 
@@
 \begin{figure}
-\includegraphics{inductive_step} 
+\[\includegraphics{inductive_step} \]
 \caption{The three possible configurations in the final part of the proof of Lemma~\ref{lem good quads}.

### 2019-07-23 GNproofalternate.tex
more changes to GNproof

--- 2019-07-17 GNproof.tex
@@
 This is because if any propagator supported on $x$ is still unassigned when the algorithm reaches $x$, we would have $x \in I_i$.
-We also note that when $p_m$ contributes $I_i(p_m) = a_m$ to the Grassmann necklace, it must be the clockwise-most propagator (amongst those not yet assigned) that is supported on $a_m$ i.e.
+{\color{red}We also note that when $p_m$ contributes $I_i(p_m) = a_m$ to the Grassmann necklace, it must be the clockwise-most propagator (amongst those not yet assigned) that is supported on $a_m$ i.e.
 clockwise-most amongst propagators in the set $\cP \setminus \cP_{m-1}$.
+}
 
@@
 By construction there is some propagator $p_r \in Q_{l-1}$ such that $p_r$ and $q$ are both supported on $I_i(p_r) = a_r$.
-If $q$ is clockwise of $p_r$ on vertex $a_r$ then we immediately have $q \in \cP_{m-1}$ as observed above.
-However, if $q$ is counter-clockwise of $p_r$ then we need to show that $p_r$ or another propagator in $Q_l$ constrains the positioning of the other end of $q$ and prevents it from ``escaping'' past $j_m$.
+\hlfix{If $q$ is clockwise of $p_r$ on vertex $a_r$ then we immediately have $q \in \cP_{m-1}$ as observed above.}{by the red text above?
+The way that is now phrased, it explicitly doesn't take care of your second picture below} However, if $q$ is counter-clockwise of $p_r$ then we need to show that $p_r$ or another propagator in $Q_l$ constrains the positioning of the other end of $q$ and prevents it from ``escaping'' past $j_m$.
 
 Note that we cannot have $a_r+ 1 = j_m$ when $q$ is counterclockwise of $p_r$, since $q \not\in \Prop(j_m)$.
-If $V(p_r) \subseteq [I_i(p_r)-1,j_m]$, then since $q$ is inside $p_r$ we also have $V(q) \subseteq [a_r-1,j_m]$ and hence $q \in \cP_{m-1}$ by Lemma [no fourth vertex].
+If $V(p_r) \subseteq [I_i(p_r)-1,j_m{\color{violet}+1}]$, then since $q {\color{\not \in Q_0}$ is \hlfix{inside}{=clockwise?} $p_r$ we also have $V(q) \subseteq [a_r-1,j_m]$ and hence $q \in \cP_{m-1}$ by Lemma [no fourth vertex].
 In particular, if $l=1$ then $p_r \in Q_{0} = \Prop(j_m)$ and we must be in this case.

### 2019-07-24 GWLDCI.tex
almost through section 3.2

@@
 
-In \cite{wilsonloop} Agarwala and Amat showed that every admissible Wilson loop diagrams can be identified with a unique positroid cell, and observed that this mapping is neither one-to-one nor onto.
+In \cite{wilsonloop} Agarwala and Amat showed that every weakly admissible Wilson loop diagrams can be identified with a type of matroid called a positroid, and observed that this mapping is neither one-to-one nor onto.
+Each such positroid corresponds to a positroid cell in the appropriate positive Grassmannian, $\Gr(k,n)$ \cite{Postnikov}\sanote{Is this the right citation?}.
 In this paper we give a simple characterization of this lack of injectivity in terms of an equivalence relation on the Wilson loop diagrams, and enumerate the number of different Wilson loop diagrams that correspond to each positroid cell.
@@
 
-The main result of Section~\ref{sec equiv} is Theorem~\ref{same matroid iff equiv}, which says that two Wilson loop diagrams define the same matroid if and only if they are equivalent.
+The main result of Section~\ref{sec equiv} is Theorem~\ref{same matroid iff equiv}, which says that two Wilson loop diagrams define the same matroid (positroid) if and only if they are equivalent.
 In subsection~\ref{sec: polygon partitions} we relate exact subdiagrams of Wilson loop diagrams to triangulations of polygons, and hence show that every Wilson loop diagram can be uniquely decomposed as a collection of exact subdiagrams (Corollary~\ref{uniqueproppartitioncor}).
@@
 If all the maximal minors of the matrix are nonnegative then the matroid realized by this matrix is called a {\em positroid}.
-\sanote{we seem to have eliminated all other reference to positroid in this paper.
-Shoudl we get rid of this?
-I would prefer to keep this, and say that admissible Wilson loop diagrams define positroids, but leave it there.
-For me, the point of this paper is to elucidate the map from WLDs to matroids, showing what we already know about the image is part of that.} In other words a positroid is a matroid\footnote{Note that matroid isomorphism allows arbitrary permutations of the ground set, while positroid isomorphism only allows cyclic permutations in order to preserve the nonnegativity of the minors.
+In other words a positroid is a matroid\footnote{Note that matroid isomorphism allows arbitrary permutations of the ground set, while positroid isomorphism only allows cyclic permutations in order to preserve the nonnegativity of the minors.
 In particular, the property of being a positroid is not preserved under matroid isomorphism.} that is realized by an element of the totally nonnegative Grassmannian $\Gr(k,n)$.
@@
 Matroid theory relates to the study of Wilson loop diagrams as follows.
-In \cite{wilsonloop}, Agarwala and Amat show that every admissible Wilson loop diagram with $k$ propagators defines a positroid of rank $k$, and that the independent sets can be read directly from the diagram:
+In \cite{wilsonloop}, Agarwala and Amat show that every weakly admissible Wilson loop diagram with $k$ propagators defines a positroid of rank $k$ on a base set of size $n$, called $M(W)$.
+In other words, by \cite{Postnikov}, each admissible Wilson loop diagram corresponds to a convex subset of $\Gr(k,n)$, thus connecting the geometry of Wilson loop diagrams with the geometry underlying the Amplituhedron.
+The independent sets of $M(W)$ can be read directly from the diagram:
 
@@
 
-This section explores the correspondence between Wilson loop diagrams and positroids that was established in \cite{wilsonloop}.
-In that paper, the authors show that admissible Wilson loop diagrams define matroids that are also positroids, Theorem \ref{put it back in then ref}.
-Furthermore, they show that if two Wilson loop diagrams are equivalent, they define the same matroid [ref thm].
-
-In this section we develop this analysis further, showing the converse of Theorem [ref] from loc.
+This section explores the correspondence between Wilson loop diagrams and positroids that was established in \cite{wilsonloop}, (Theorem 3.38).
+In that paper, the authors show that admissible Wilson loop diagrams define matroids that are also positroids.
+Furthermore, they show that if two Wilson loop diagrams are equivalent, they define the same matroid(Theorems 1.18 and 3.41).
+
+In this section we develop this analysis further, showing the converse of this result from loc.
 cit.
@@
 To do this, we establish a connection between Wilson loop diagrams and polygon dissections in subsection \ref{sec: polygon partitions}, and uncover some matroidal properties of exact subdiagrams in subsection \ref{sec: exact diagram matroidal props}.
-This includes the fact that exact subdiagrams correspond to uniform matroids (Theorem \ref{exactuniformthm}), and that the associated matroid of an exact subdiagram can be written as as a contraction by the complementary propagator flat (Theorem \ref{exact diagrams contractions}).\sanote{need to discuss positroids, and whether positroids should appear earlier so that they can be discussed here.}
+This includes the fact that exact subdiagrams correspond to uniform matroids (Theorem \ref{exactuniformthm}), and that the associated matroid of an exact subdiagram can be written as as a contraction by the complementary propagator flat (Theorem \ref{exact diagrams contractions}).
 
@@
 
-The key point to note is that the subgraph $t$ depends on how the propagators of $P$ sit inside $[n]$, not on how they sit in \hlfix{the subdiagram $(P,V(P))$, which would have an outer edges between vertices 8 and 1, between 2 and 4, and between 4 and 8, but would not include vertex 3}{Sian replaced $W_P$ with $(P,V(P))$ here and now isn't sure if that was right because this sentence doesn't make sense?}.
+The key point to note is that the subgraph $t$ depends on how the propagators of $P$ sit inside $[n]$, not on how they sit in \hlfix{the subdiagram $(P,V(P))$, which would have an outer edges between vertices 9 and 1, and between 5 and 8}{Sian replaced $W_P$ with $(P,V(P))$ here and now isn't sure if that was right because this sentence doesn't make sense?}.
 In particular, $t$ is not the subgraph of $\tau(W)$ consisting only of edges corresponding to propagators of $P$ (as it may also include some of the outer edges of $\tau(W)$), nor is it the polygon dissection of $(P,V(P))$ viewed as a Wilson loop diagram in its own right (which would have vertex set equal to $V(P)$).
@@
 Let $W = (\cP, [n])$ be an admissible Wilson loop diagram, and $P \subseteq \cP$. Then: \begin{enumerate}
-\item If $(P,V(P))$ is an exact subdiagram of $W$, then $F(P^c)$ is a dependent flat in $W$.
+\item If $(P,V(P))$ is an exact subdiagram of $W$, then $F(P^c)$ is not an independent flat in $W$.
 \item If $(P,V(P))$ is a maximal exact subdiagram of $W$, then $F(P^c)$ is a cyclic flat in $W$.
 \item If $(P,V(P))$ is an exact subdiagram in $W$, then $\rk(F(P^c)) = |P^c|$.
-\end{enumerate} \sanote{end here}
+\end{enumerate} 
 \end{lem}
@@
 
-We know from Lemma~\ref{lem facts about WLD matroids} that $F(P^c)$ is always a flat, so for part (1) we only need to show that $F(P^c)$ is dependent.
+We know from Lemma~\ref{lem facts about WLD matroids} that $F(P^c)$ is always a flat, so for part (1) we only need to show that $F(P^c)$ is not independent.
 
@@
 and combining it with the fact that $|V(P)| = |P| + 3$ (from the exactness of $(P,V(P))$), we obtain
-\begin{equation}\label{eq F is dependent}|F(P^c)| > |P^c| \;.\end{equation}
-Equation \eqref{eq F is dependent} implies that $F(P^c)$ supports fewer propagators than the number of vertices it contains, i.e. $F(P^c)$ is not an independent set.
-
-For part (2), suppose that $(P, V(P))$ is a maximal exact subdiagram. By Corollary \ref{classifyflats} we can decompose $F(P^c)$ as
+\begin{equation}\label{eq F not independent}|F(P^c)| > |P^c| \;.\end{equation}
+Equation \eqref{eq F not independent} implies that $F(P^c)$ supports fewer propagators than the number of vertices it contains, i.e. $F(P^c)$ is not an independent set.
+
+For part (2), suppose that $(P, V(P))$ is a maximal exact subdiagram. By Lemma \ref{lem decompose flat} (1) and Corollary \ref{classifyflats} we can decompose $F(P^c)$ as
 \begin{equation}\label{eq decompose F}V(P)^c = F(P^c) = C \sqcup S = F(\Prop(C)) \sqcup S,\end{equation}
-where $C$ is the largest cyclic flat contained in $F(P^c)$ and $S$ is an  independent set. Note that $C$ must be non-empty since $F(P^c)$ is non-empty and dependent (by part (1)).
+where $C$ is the largest cyclic flat contained in $F(P^c)$ and $S$ is an  independent set.
+We show that $\Prop(C) = P^c$, thus forcing $S$ to be empty.
+Note that $C$ must be non-empty since $F(P^c)$ is non-empty and not independent (by part (1)).
+
+By Lemma \ref{lem facts about WLD matroids}(2), $\rk(C) = |\Prop(C)|$.
+Since $S$ is independent, Lemma \ref{lem facts about WLD matroids}(1) gives $|S| = \rk(S)$.
+By similar arguments to Lemma~\ref{lem decompose flat}, the fact that $S$ is independent and that $C$ is the union of all circuits in $F(P^c)$ implies that every element of $S$ is independent of $C$.
+Combining these give the first two inequalities below
+\ba \rk\big(F(P^c)\big) = \rk(C) + \rk(S)  = |\Prop(C)| + |S| \leq |\Prop(F(P^c))|\;,\label{rank of comp flat} \ea % this equation doesn't really need to be displayed, but it was causing a badbox  
+while the inequality comes from the bound on ranks of vertex sets.
+
+Furthermore, from Remark \ref{alt F(P) rmk}, we see that $\Prop (F(P^c)) \subseteq P^c$.
+Therefore equation \eqref{rank of comp flat} gives \bas |\Prop (C)| + |S| \leq |P^c|  \;.\eas For ease of future notation, write $Q = \Prop(C)^c$.
+Rearranging and adding $|P|$ to both sides gives \ba |P| + |S| \leq |P| + |P^c| - |\Prop(C)| = |Q| \;.\label{P+Sbound}\ea Taking complements of and rearranging equation \eqref{eq decompose F} we have
+\bas V(P) \sqcup S = C^c = F(\Prop(C))^c  = V(Q)\;. \eas
+Combining this with equation \eqref{P+Sbound} gives 
+\ba |V(Q)| = | V(P) | + |S| = | P | + 3 + |S| \leq |Q| +3 \;. \label{Q defines exact}\ea
+Since $W$ is admissible this cannot be a strict inequality, so we have $|V(Q)| = |Q| +3$ and the subdiagram $(Q, V(Q))$ is exact.
+
+Since \bas \Prop(C) \subseteq \Prop(F(P^c)) \subseteq P^c \eas taking complements gives $P \subseteq \Prop(C)^c = Q$.
+In other words, $(P, V(P))$ is an exact subdiagram of $(Q, V(Q))$.
+Since $(P, V(P))$ is a maximal exact subdiagram, $P=Q$, or $\Prop (C) = P^c$, and thus $S = \emptyset$, forcing $F(P^c)$ to be a cyclic flat.
+\sanote{the previous proof of (2) (commented out) was making my head spin.
+I think this is more straightforward, butI might just be rearranging deckchairs.}
+\begin{comment}For part (2), suppose that $(P, V(P))$ is a maximal exact subdiagram. By Lemma \ref{lem decompose flat} (1) and Corollary \ref{classifyflats} we can decompose $F(P^c)$ as
+\begin{equation}\label{eq decompose F}V(P)^c = F(P^c) = C \sqcup S = F(\Prop(C)) \sqcup S,\end{equation}
+where $C$ is the largest cyclic flat contained in $F(P^c)$ and $S$ is an  independent set.
+We show that $\Prop(C) = P^c$, thus forcing $S$ to be empty.
+Note that $C$ must be non-empty since $F(P^c)$ is non-empty and not independent (by part (1)).
 
@@
 Therefore $S = \emptyset$ and $F(P^c)$ is a cyclic flat.
+\end{comment}
 
@@
 That is, they correspond to matroids represented by elements of the positive Grassmannians $\Gr(|\cP|, n)$.
-Any positroid of rank $k$ on $n$ elements defines a subspace of the positive Grassmannians $\Gr(k, n)$, namely the points which represent it.
+Any positroid of rank $k$ on $n$ elements defines a subspace of the positive Grassmannians $\Gr(k, n)$, namely the points which represent it \cite{Postnikov}.
 These subspaces give a CW structure on $\Gr(k,n)$, with each positroid defining a cell.
+\sanote{Susama end here}
 

### 2019-07-24 GWLDCI.tex
through section 4.1

@@
 
-In \cite{wilsonloop}, the authors show that all admissible Wilson loop diagrams correspond to positroids.
-That is, they correspond to matroids represented by elements of the positive Grassmannians $\Gr(|\cP|, n)$.
+In \cite{wilsonloop}, the authors show that each weakly admissible Wilson loop diagrams correspond to a postiroid.
+That is, each diagram correspond to matroids that can be represented by elements of the positive Grassmannians $\Gr(|\cP|, n)$.
 Any positroid of rank $k$ on $n$ elements defines a subspace of the positive Grassmannians $\Gr(k, n)$, namely the points which represent it \cite{Postnikov}.
 These subspaces give a CW structure on $\Gr(k,n)$, with each positroid defining a cell.
-\sanote{Susama end here}
-
-\begin{dfn}
-Given a Wilson loop diagram $W = (\cP, [n])$, its associated matroid $M(W)$ corresponds to positroid cells in the CW complex on $\Gr(|\cP|, n)$.
-\end{dfn}\note{How is this a def as it doesn't define the cells?  Also, should it be cell singular}
-
-With this definition in mind, we have the following corollary:
+In other words, there is a map from weakly admissible Wilson loop diagrams, $W$, to matroids, $M(W)$, to positroid cells in the CW complex on $\Gr(|\cP|, n)$.
+\note{How is this a def as it doesn't define the cells?  Also, should it be cell singular} \sanote{got rid of dfn}
+
+With this mapping in mind, we have the following corollary:
 
@@
 
-Now we are ready to prove the main results of this section, namely that two Wilson loop diagrams define the same matroid if and only if they are equivalent (Theorem \ref{same matroid iff equiv}).
-We also
-give a formula for the number of Wilson loop diagrams in a given equivalence class (Corollary \ref{number of equiv diagrams}), completing the characterization of the correspondence between Wilson loop diagrams and matroids starting in \cite{wilsonloop}.
+Now we are ready to prove the main results of this section, namely that two Wilson loop diagrams define the same matroid (positroid) if and only if they are equivalent (Theorem \ref{same matroid iff equiv}).
+We also give a formula for the number of Wilson loop diagrams in a given equivalence class (Corollary \ref{number of equiv diagrams}), completing the characterization of the correspondence between Wilson loop diagrams and positroids starting in \cite{wilsonloop}.
 
 \begin{thm}\label{same matroid iff equiv}
-Let $W= (\cP, [n])$ and $W'= (\cP', [n])$ be two Wilson loop diagrams. They define the same matroid if and only if $W \sim W'$.
+Let $W= (\cP, [n])$ and $W'= (\cP', [n])$ be two Wilson loop diagrams. They define the same matroid (positroid) if and only if $W \sim W'$.
 \end{thm}
@@
 \[W = (P \sqcup R, [n]), \qquad W' = (P \sqcup R', [n]),\]
-where $(R,V(R))$ and $(R',V(R'))$ are maximal exact subdiagrams of $W$ and $W'$ respectively, and $V(R) = V(R')$.
+where $(R,V(R))$ and $(R',V(R'))$ are different maximal exact subdiagrams of $W$ and $W'$ respectively, and $V(R) = V(R')$.
 
@@
 
-In this section we have characterized the correspondence between Wilson loop diagrams and positroids, showing that Wilson Loop diagrams define the same matroid if and only if they are equivalent (Theorem \ref{same matroid iff equiv}).
-Corollary \ref{number of equiv diagrams} enumerates the elements of each fiber of the map from Wilson Loop diagrams to positroids.
+In this section we have characterized the correspondence between Wilson loop diagrams and positroids, showing that Wilson Loop diagrams define the same positroid if and only if they are equivalent (Theorem \ref{same matroid iff equiv}).
+If we write \bas M: \textrm{admissible \; WLD} & \rightarrow \textrm{Positroids} \\ W & \rightarrow M(W) \;,\eas the image of this map is given by the distinct equivalence classes.
+Corollary \ref{number of equiv diagrams} enumerates the elements of each fiber of $M$.
 The obvious next question would be to enumerate the number of equivalence classes.
@@
 We know from examples (e.g.
-\cite{casestudy}) that \hlfix{even after taking the dimension of the positroid cell into consideration}{Sian: I'm not quite sure what ``taking the dimension into consideration'' means here: do we mean ``even after restricting our attention to cells of dimension $3k$''?}\footnote{it is proven in \cite{generalcombinatoricsII} and \cite{Marcott} that Wilson loop diagrams with $k$ propagators map to $3k$ dimensional positroid cells}, many positroid cells do not appear as admissible Wilson loop diagrams with a fixed number of propagators and vertices.
+\cite{casestudy}) that \hlfix{even after taking the dimension of the positroid cell into consideration}{Sian: I'm not quite sure what ``taking the dimension into consideration'' means here: do we mean ``even after restricting our attention to cells of dimension $3k$''?}\sanote{yes, but it may be worth just getting rid of this text.} \footnote{it is proven in \cite{generalcombinatoricsII} and \cite{Marcott} that Wilson loop diagrams with $k$ propagators map to $3k$ dimensional positroid cells}, many positroid cells do not appear as admissible Wilson loop diagrams with a fixed number of propagators and vertices.
 That is, the map from admissible Wilson loop diagrams to positroid cells of the correct dimension in the correct Grassmannian neither injective nor surjective.
@@
 Two faces are \emph{parallel} if one can be mapped to the other by a translation in $\mathbb{R}^d$.
-In particular parallel faces must be of the same dimension and any two vertices are parallel to each other.
+In particular parallel faces must be of the same dimension.
+\hlfix{Any two vertices are trivially parallel to each other.}{changed.
+Correct?}
 

### 2019-07-25 GWLDCI.tex
finished read through

@@
 
-This proof is by a symmetrical construction, where we give a proof with respect to a single edge in $f$, leaving the rest of the argument as read due to the symmetry.\note{Actually, since it is by contradiction we don't need to do both directions; one direction already gives a contradiction and that's enough}
-
-Assume for a contradiction that no quadrilateral as in the statement exists, and let $d$ and $f$ be as above.
+This proof is by a symmetrical construction, where we give a proof with respect to a single edge in the face $f$, leaving the rest of the argument as read due to the symmetry.\note{Actually, since it is by contradiction we don't need to do both directions; one direction already gives a contradiction and that's enough} \sanote{agreed.
+Withdraw previous questions}
+
+Assume for a contradiction that no quadrilateral as in the statement exists, and let $d$ be a diagonal in $D_1$ crossing the unique non-triangle face, $f$, of $D_2$.
 Then $f$ must have two vertices strictly on each side of $d$: name the vertices on one side of $d$ as $x_i$ and $x_j$, and those on the other side as $x_k$, $x_l$ (and in that order; see Figure~\ref{inductive_step}).
@@
     It will be most convenient to consider faces in terms of their normal vectors.
-We make use of the construction discussed on p8 of \cite{CSZinequivalent}: namely, pick one side of $d$ to be positive and define the $i$th coordinate of the vector $\omega^+_d$ to be
+We make use of the construction discussed on page 8 of \cite{CSZinequivalent}: namely, pick one side of $d$ to be positive and define the $i$th coordinate of the vector $\omega^+_d$ to be
     \[

### 2019-07-26 GWLDCI.tex
minor rephrasing

@@
 
-The key point to note is that the subgraph $t$ depends on how the propagators of $P$ sit inside $[n]$, not on how they sit in \hlfix{the subdiagram $(P,V(P))$, which would have an outer edges between vertices 9 and 1, and between 5 and 8}{Sian replaced $W_P$ with $(P,V(P))$ here and now isn't sure if that was right because this sentence doesn't make sense?}.
+The key point to note is that the subgraph $t$ depends on how the propagators of $P$ sit inside $[n]$, not on how they sit in \hlfix{the subdiagram $(P,V(P))$, which would have outer edges between vertices 8 and 9, 9 and 1, 4 and 5, and 5 and 8}{Sian replaced $W_P$ with $(P,V(P))$ here and now isn't sure if that was right because this sentence doesn't make sense?}.
 In particular, $t$ is not the subgraph of $\tau(W)$ consisting only of edges corresponding to propagators of $P$ (as it may also include some of the outer edges of $\tau(W)$), nor is it the polygon dissection of $(P,V(P))$ viewed as a Wilson loop diagram in its own right (which would have vertex set equal to $V(P)$).

### 2019-07-26 GWLDCI.tex
things we fixed in today's meetings

--- 2019-07-25 GWLDCI.tex
@@
 In \cite{wilsonloop} Agarwala and Amat showed that every weakly admissible Wilson loop diagrams can be identified with a type of matroid called a positroid, and observed that this mapping is neither one-to-one nor onto.
-Each such positroid corresponds to a positroid cell in the appropriate positive Grassmannian, $\Gr(k,n)$ \cite{Postnikov}\sanote{Is this the right citation?}.
+Each such positroid corresponds to a positroid cell in the appropriate positive Grassmannian, $\Gr(k,n)$ \cite{Postnikov}.
 In this paper we give a simple characterization of this lack of injectivity in terms of an equivalence relation on the Wilson loop diagrams, and enumerate the number of different Wilson loop diagrams that correspond to each positroid cell.
@@
 As noted above, Agarwala and Marin-Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that are realized as an element of the positive Grassmannian $\Gr(k,n)$ \cite{wilsonloop}.
-In (separate) papers with Fryer and Marcott, this work was extended to study these Feynman integrals in terms of positroid cells and the positive Grassmannians \cite{casestudy, non-orientable}.
+In separate papers with Fryer and Marcott, this work was extended to study these Feynman integrals in terms of positroid cells and the positive Grassmannians \cite{casestudy, non-orientable}.
 Others have tried different approaches to define a geometric space associated to these integrals in a manner similar to the Amplituhedron \cite{Amplituhedronsquared, HeslopStewart}.
@@
 The independent sets of $M(W)$ can be read directly from the diagram:
-
-\sanote{Everything from here applies to weakly admissible. In fact, I think the dfn of admissible in my paper with Amat is what we call weakly admissible here. Should we change to weakly?}
 
@@
 
-For an admissible Wilson loop diagram $W$, every triangulated piece $t$ of $\tau(W)$ corresponds to a subdiagram of $W$ obtained by taking the set of propagators $P$ corresponding to edges of $t$ and then taking the subdiagram $W_P = (P, V(P))$.
-Conversely, given a subdiagram $W_P = (P, V(P))$ of $W$ we can obtain a subgraph of $\tau(W)$, called $t$, as follows:
+For an admissible Wilson loop diagram $W$, every triangulated piece $t$ of $\tau(W)$ corresponds to a subdiagram of $W$ obtained by taking the set of propagators $P$ corresponding to edges of $t$ and then taking the subdiagram $(P, V(P))$.
+Conversely, given a subdiagram $(P, V(P))$ of $W$ we can obtain a subgraph of $\tau(W)$, called $t$, as follows:
 \begin{itemize}
@@
 
-The key point to note is that the subgraph $t$ depends on how the propagators of $P$ sit inside $[n]$, not on how they sit in \hlfix{the subdiagram $(P,V(P))$, which would have an outer edges between vertices 9 and 1, and between 5 and 8}{Sian replaced $W_P$ with $(P,V(P))$ here and now isn't sure if that was right because this sentence doesn't make sense?}.
+The key point to note is that the subgraph $t$ depends on how the propagators of $P$ sit inside $[n]$, not on how they sit in the subdiagram $(P,V(P))$, which would have outer edges between vertices 8 and 9, 9 and 1, 4 and 5, and 5 and 8.
 In particular, $t$ is not the subgraph of $\tau(W)$ consisting only of edges corresponding to propagators of $P$ (as it may also include some of the outer edges of $\tau(W)$), nor is it the polygon dissection of $(P,V(P))$ viewed as a Wilson loop diagram in its own right (which would have vertex set equal to $V(P)$).
@@
 We begin by proving some useful facts about propagator flats, and flats of matroids associated to admissible Wilson loop diagrams more generally.
-Recall from Definition~\ref{VPropdfn} that the propagator flat $F(P)$ of $P \subseteq \cP$ denotes the set $V(P^c)^c$ of vertices that only support propagators in $P$ (or are non-supporting).\note{Sian: I know we discussed the phrasing of this last time so I'm highlighting this change: I replaced ``(or no propagators)'' with ``(or are non-supporting)'' because it was unclear what part of the sentence the ``no propagators'' was attached to.
-Is this clearer?}
+Recall from Definition~\ref{VPropdfn} that the propagator flat $F(P)$ of $P \subseteq \cP$ denotes the set $V(P^c)^c$ of vertices that only support propagators in $P$ or are non-supporting.
 
@@
 I think this is more straightforward, butI might just be rearranging deckchairs.}
-\begin{comment}For part (2), suppose that $(P, V(P))$ is a maximal exact subdiagram. By Lemma \ref{lem decompose flat} (1) and Corollary \ref{classifyflats} we can decompose $F(P^c)$ as
-\begin{equation}\label{eq decompose F}V(P)^c = F(P^c) = C \sqcup S = F(\Prop(C)) \sqcup S,\end{equation}
-where $C$ is the largest cyclic flat contained in $F(P^c)$ and $S$ is an  independent set.
+%\begin{comment}For part (2), suppose that $(P, V(P))$ is a maximal exact subdiagram. By Lemma \ref{lem decompose flat} (1) and Corollary \ref{classifyflats} we can decompose $F(P^c)$ as
+%\begin{equation}\label{eq decompose F}V(P)^c = F(P^c) = C \sqcup S = F(\Prop(C)) \sqcup S,\end{equation}
+%where $C$ is the largest cyclic flat contained in $F(P^c)$ and $S$ is an  independent set.
 We show that $\Prop(C) = P^c$, thus forcing $S$ to be empty.
 Note that $C$ must be non-empty since $F(P^c)$ is non-empty and not independent (by part (1)).
-
-By similar arguments to Lemma~\ref{lem decompose flat}, the fact that $S$ is independent and that $C$ is the union of all circuits in $F(P^c)$ implies that every element of $S$ is independent of $C$, and therefore
-\[{\rk\big(F(P^c)\big) = \rk(C) + \rk(S)}.\]% this equation doesn't really need to be displayed, but it was causing a badbox 
-We also know that $\rk(S) = |S|$, by the independence of $S$.
+%
+%By similar arguments to Lemma~\ref{lem decompose flat}, the fact that $S$ is independent and that $C$ is the union of all circuits in $F(P^c)$ implies that every element of $S$ is independent of $C$, and therefore
+%\[{\rk\big(F(P^c)\big) = \rk(C) + \rk(S)}.\]% this equation doesn't really need to be displayed, but it was causing a badbox 
+%We also know that $\rk(S) = |S|$, by the independence of $S$.
 Combining these with Lemma~\ref{lem facts about WLD matroids}(1), we get \ba |S| = \rk(S) = \rk\big(F(P^c)\big) -  \rk(C) \leq |P^c| - \rk(C) \;.
 \label{increasingrank} \ea
-
-Define $Q = \Prop(C)^c$. We will show that $Q=P$, which will imply that $S=\emptyset$ and that ${F(P^c) = F(Q^c) = F(\Prop(C))}$ is a cyclic flat.
-
-From the definition of $Q$ we obtain $C = F(Q^c)$, and, by Lemma \ref{lem facts about WLD matroids}(2), it follows that $\rk(C) = |Q^c|$. By equation \eqref{increasingrank}, we obtain
-\ba |P| + |S| \leq |P| + |P^c| - \rk(C) = |\cP| - |Q^c| = |Q| \;. \label{Qsizebound}\ea 
-Meanwhile, from equation \eqref{eq decompose F} we have
-\bas V(P) \sqcup S = C^c = F(\Prop(C))^c = F(Q^c)^c = V(Q) \;. \eas
-Combining this with equation \eqref{Qsizebound} gives 
-\ba |V(Q)| = | V(P) | + |S| = | P | + 3 + |S| \leq |Q| +3 \;. \label{Q defines exact}\ea
-Since $W$ is admissible this cannot be a strict inequality, so we have $|V(Q)| = |Q| +3$ and the subdiagram $(Q, V(Q))$ is exact.
-
-Finally, note that since $F(P^c) = C \sqcup S$ (equation~\eqref{eq decompose F}), we have
-\[\Prop(C) \subseteq \Prop(F(P^c)) \subseteq P^c.\]
-Taking complements, we obtain $P \subseteq \Prop(C)^c = Q$, and hence that $(P, V(P))$ is a subdiagram of $(Q, V(Q))$.
+%
+%Define $Q = \Prop(C)^c$. We will show that $Q=P$, which will imply that $S=\emptyset$ and that ${F(P^c) = F(Q^c) = F(\Prop(C))}$ is a cyclic flat.
+%
+%From the definition of $Q$ we obtain $C = F(Q^c)$, and, by Lemma \ref{lem facts about WLD matroids}(2), it follows that $\rk(C) = |Q^c|$. By equation \eqref{increasingrank}, we obtain
+%\ba |P| + |S| \leq |P| + |P^c| - \rk(C) = |\cP| - |Q^c| = |Q| \;. \label{Qsizebound}\ea 
+%Meanwhile, from equation \eqref{eq decompose F} we have
+%\bas V(P) \sqcup S = C^c = F(\Prop(C))^c = F(Q^c)^c = V(Q) \;. \eas
+%Combining this with equation \eqref{Qsizebound} gives 
+%\ba |V(Q)| = | V(P) | + |S| = | P | + 3 + |S| \leq |Q| +3 \;. \label{Q defines exact}\ea
+%Since $W$ is admissible this cannot be a strict inequality, so we have $|V(Q)| = |Q| +3$ and the subdiagram $(Q, V(Q))$ is exact.
+%
+%Finally, note that since $F(P^c) = C \sqcup S$ (equation~\eqref{eq decompose F}), we have
+%\[\Prop(C) \subseteq \Prop(F(P^c)) \subseteq P^c.\]
+%Taking complements, we obtain $P \subseteq \Prop(C)^c = Q$, and hence that $(P, V(P))$ is a subdiagram of $(Q, V(Q))$.
 Since $(P, V(P))$ is maximally exact by hypothesis, and $(Q, V(Q))$ is exact by equation \eqref{Q defines exact}, we must have $P = Q$.
 Therefore $S = \emptyset$ and $F(P^c)$ is a cyclic flat.
-\end{comment}
+%\end{comment}
 
@@
 
-In \cite{wilsonloop}, the authors show that each weakly admissible Wilson loop diagrams correspond to a postiroid.
-That is, each diagram correspond to matroids that can be represented by elements of the positive Grassmannians $\Gr(|\cP|, n)$.
-Any positroid of rank $k$ on $n$ elements defines a subspace of the positive Grassmannians $\Gr(k, n)$, namely the points which represent it \cite{Postnikov}.
+In \cite{wilsonloop}, the authors show that each weakly admissible Wilson loop diagrams correspond to a positroid.
+That is, each diagram corresponds to a matroid that can be represented by elements of the positive Grassmannian $\Gr(|\cP|, n)$.
+Any positroid of rank $k$ on $n$ elements defines a subspace of the positive Grassmannian $\Gr(k, n)$, namely the points which represent it \cite{Postnikov}.
 These subspaces give a CW structure on $\Gr(k,n)$, with each positroid defining a cell.
 In other words, there is a map from weakly admissible Wilson loop diagrams, $W$, to matroids, $M(W)$, to positroid cells in the CW complex on $\Gr(|\cP|, n)$.
-\note{How is this a def as it doesn't define the cells?  Also, should it be cell singular} \sanote{got rid of dfn}
 
@@
 
-For the converse, \note{I don't want to mess with this because it was one of the delicate proofs, but why can't we just say $M(W)=M(W')$ so the set of uniform submatroids is the same for $M(W)$ and $M(W')$ so by the previous result the set of exact subdiagrams of $W$ and $W'$ is the same, and all this was inclusion preserving so the set of maximal exact subdiagrams is also the same.} suppose that $M(W) = M(W') = M$.
+For the converse, suppose that $M(W) = M(W') = M$.
 This immediately implies that $|\cP| = |\cP'|$, so to demonstrate the equivalence of $W$ and $W'$ it suffices to show that for any maximal exact subdiagram $(P,V(P))$ in $W$, there is a corresponding maximal exact subdiagram $(P',V(P'))$ in $W'$ with $V(P) = V(P')$.
@@
 We know from examples (e.g.
-\cite{casestudy}) that \hlfix{even after taking the dimension of the positroid cell into consideration}{Sian: I'm not quite sure what ``taking the dimension into consideration'' means here: do we mean ``even after restricting our attention to cells of dimension $3k$''?}\sanote{yes, but it may be worth just getting rid of this text.} \footnote{it is proven in \cite{generalcombinatoricsII} and \cite{Marcott} that Wilson loop diagrams with $k$ propagators map to $3k$ dimensional positroid cells}, many positroid cells do not appear as admissible Wilson loop diagrams with a fixed number of propagators and vertices.
+\cite{casestudy}) that many positroid cells do not appear as admissible Wilson loop diagrams with a fixed number of propagators and vertices.
 That is, the map from admissible Wilson loop diagrams to positroid cells of the correct dimension in the correct Grassmannian neither injective nor surjective.
@@
 In particular parallel faces must be of the same dimension.
-\hlfix{Any two vertices are trivially parallel to each other.}{changed.
-Correct?}
+Any two vertices are parallel to each other.
 
@@
 These common faces are irrelevant for the statement as none of them can be the face containing $x_i, x_j, x_k, x_l$, and so by triangulating any common non-triangle faces, we may assume that $D_1$ and $D_2$ have only quadrilateral and triangle faces.
-
-This proof is by a symmetrical construction, where we give a proof with respect to a single edge in the face $f$, leaving the rest of the argument as read due to the symmetry.\note{Actually, since it is by contradiction we don't need to do both directions; one direction already gives a contradiction and that's enough} \sanote{agreed.
-Withdraw previous questions}
 

### 2019-07-26 GNproof.tex
minor edits to GNproof

@@
 \end{itemize}
-The first point follows immediately: the algorithm is pairing each $j \in I_i$ with a unique propagator supported on that vertex, so $I_i$ is a basis for $M(W)$ by Corollary~\ref{lem basis as perm}.
+The first point follows immediately: the algorithm is  so $I_i$ is a basis for $M(W)$ by Corollary~\ref{lem basis as perm}.
 
@@
 
-Note that we cannot have $a_r+ 1 = j_m$ when $q$ is counterclockwise of $p_r$, since $q \not\in \Prop(j_m)$.
-If $V(p_r) \subseteq [I_i(p_r)-1,j_m]$, then since $q$ is inside $p_r$ we also have $V(q) \subseteq [a_r-1,j_m]$ and hence $q \in \cP_{m-1}$ by Lemma [no fourth vertex].
+Note that we cannot have $a_r+ 1 = j_m$ when $q$ is counterclockwise of $p_r$, since $q \not\in \Prop(j_m)$ by assumption.
+If the other end of $p_r$ (i.e.
+the end not supported on $a_r$) lies on an edge between $a_r$ and $j_m$ then since $q$ is inside $p_r$ with respect to $<_{a_r-1}$ we must have $V(q) \subseteq [a_r-1,j_m]$ and hence $q \in \cP_{m-1}$ by Lemma [no fourth vertex].
 In particular, if $l=1$ then $p_r \in Q_{0} = \Prop(j_m)$ and we must be in this case.
-If not, then there must be some propagator $p_s \in Q_{l-2}$ such that $p_r$ and $p_s$ are both supported on $I_i(p_s)$; further, we can assume that $q$ is not supported on $I_i(p_s)$ since $q \not\in Q_{l-1}$.
-This yields one of the configurations in Figure~\ref{fig:awkward induction step}.
+
+If not, then there must be some propagator $p_s \in Q_{l-2}$ such that $p_r$ and $p_s$ are both supported on $I_i(p_s) := a_s$.
+Since $p_r$ is clockwise of $q$, and $q$ cannot be supported on $I_i(p_s)$ since $q \not\in Q_{l-1}$, it follows that $I_i(p_s) <_i I_i(p_r)$.
+Therefore $q$ is inside $p_s$ with respect to $<_{a_s - 1}$ as well.
 
@@
 \includegraphics[scale = 0.3]{awkward_induction_case.jpg}
-\caption{The awkward case of the induction step, where $p_r$ does not form a nice arc to constrain $q$.
-Note that in theory $p_s$ could instead be inside $p_r$ (w.r.t $<_i$), but this does not change the argument and we omit the depiction of this case since it turns out to be impossible.}\label{fig:awkward induction step}
+\caption{This picture isn't quite the one we need any more, but it should help to illustrate the claim about $I_i(p_s) <_i I_i(p_r)$}\label{fig:awkward induction step}
 \end{figure}
 
-Now repeat the argument above with $p_s$ in place of $p_r$; this is valid since we only really need to know that $q$ is inside $p_s$ with respect to $<_{a_s - 1}$.
-Then either $V(p_s) \subseteq [I_i(p_s)-1,j_m]$, in which case we are done (as above), or there exists some $p_t \in Q_{l-3}$ and we continue to iterate the argument.
-Since there are finitely many propagators and we are guaranteed that $V(p_*) \subseteq [I_i(p_*)-1,j_m]$ if we ever reach $p_* \in Q_0$, we eventually construct a propagator that constrains $q$ and ensures that $q \in \cP_{m-1}$.
+Now repeat the argument above with $p_s$ in place of $p_r$: if the other end of $p_s$ lands on an edge between $q$ and $j_m$ then we have $q \in \cP_{m-1}$ as above; if not then there exists some $p_t \in Q_{l-3}$ with $p_s$ supported on $I_i(p_t)$ and $I_i(p_t) <_i I_i(p_r)$.
+Since there are finitely many steps this process can take before reaching $Q_0$, and any $p_* \in Q_0  = \Prop(j_m)$ has $j_m$ in its support by definition, this argument eventually terminates with the construction of a propagator constraining the positioning of $q$ as required.
 This completes the induction step.

### 2019-08-01 GWLDCI.tex
final readthrough of paper 1

@@
 In \cite{wilsonloop} Agarwala and Amat showed that every weakly admissible Wilson loop diagrams can be identified with a type of matroid called a positroid, and observed that this mapping is neither one-to-one nor onto.
-Each such positroid corresponds to a positroid cell in the appropriate positive Grassmannian, $\Gr(k,n)$ \cite{Postnikov}.
+Each such positroid corresponds to a positroid cell in the appropriate positive Grassmannian $\Gr(k,n)$ \cite{Postnikov}.
 In this paper we give a simple characterization of this lack of injectivity in terms of an equivalence relation on the Wilson loop diagrams, and enumerate the number of different Wilson loop diagrams that correspond to each positroid cell.
@@
 The arcs between consecutive vertices are called {\em edges}.
-There are also $k$ wavy lines in the interior of the diagram depicting the propagators, whose endpoints lie on the edges: specifically, a propagator $p =(i,j)$ has one endpoint on the edge joining vertices $i$ and $i+1$ and another endpoint on the edge joining $j$ and $j+1$, where $i+1$ and $j+1$ denote the successor of $i$ and $j$ respectively in the cyclic order on $V$.
+There are also $k$ wavy lines in the interior of the diagram, each connecting a pair of edges; these depict the propagators.
+Specifically, a propagator $p =(i,j)$ has one endpoint on the edge joining vertices $i$ and $i+1$ and another endpoint on the edge joining $j$ and $j+1$, where $i+1$ and $j+1$ denote the successor of $i$ and $j$ respectively in the cyclic order on $V$.
 
@@
 \begin{dfn}\label{admisdfn}
-A Wilson loop diagram $W = (\cP,V)$ is {\em admissible} if \begin{enumerate}
+A Wilson loop diagram $W = (\cP,V)$ is {\em admissible} if it satisfies the following three conditions: \begin{enumerate}
 \item $|V| \geq |\cP| + 4.$
@@
 
-The first condition restricts the overall density of propagators in the diagram, while the second imposes an upper bound on how densely the propagators can be fitted into a portion of the diagram.
+The first condition restricts the overall density of propagators in the diagram, while the second imposes an upper bound on how densely the propagators can be fitted into any portion of the diagram.
 The third ensures that ensures that no propagators cross in the interior of the diagram.
@@
 There are a few things to note here.
-First, what we call weakly admissible is called admissible in \cite{wilsonloop}.
-Many of the results below apply when the hypothesis of admissibility is changed to weak admissibility.
-
-Note also that if two propagators have the same supporting edges, or if a propagator is supported on adjacent edges, then the Wilson loop diagram is not admissible.
+First, what we call weakly admissible here is called admissible in \cite{wilsonloop}.
+Many of the results below still apply when the hypothesis of admissibility is changed to weak admissibility.
+
+Note also that if two propagators have the same pair of supporting edges, or if a propagator is supported on two adjacent edges, then the Wilson loop diagram is not admissible or even weakly admissible.
 
@@
 It has a single non-supporting vertex, namely the vertex labeled 7, so we have $F(\emptyset) = \{7\}$.
-For $p = (5, 8)$, we have $V(p) = \{5,6,8,1\}$ and $F(p) = \{6, 7,8\}$: the vertices 1 and 5 are excluded from $F(p)$ since they support other propagators as well, and 7 is included (despite not being in the support of $p$) since it supports no propagators at all.
+For the propagator $p = (5, 8)$, we have $V(p) = \{5,6,8,1\}$ and $F(p) = \{6, 7,8\}$: the vertices 1 and 5 are excluded from $F(p)$ since they support other propagators as well, and 7 is included (despite not being in the support of $p$) since it supports no propagators at all.
 Finally, the subdiagram $(\{(2, 4), (1, 4)\}, \{1, 2, 3, 4, 5\})$ is an example of an exact subdiagram; in fact it is the only non-trivial exact subdiagram in $W$.
@@
 \begin{dfn}\label{equivdfn} 
-Let $W = (\cP,[n])$ and $W' = (\cP',[n])$ be two admissible subdiagrams. We say that $W$ and $W'$ are related if
+Let $W = (\cP,[n])$ and $W' = (\cP',[n])$ be two admissible subdiagrams. Let $\sim$ denote the transitive closure of the following relation: $W$ and $W'$ are related if
 \begin{enumerate}
@@
 \end{enumerate}
-Let $\sim$ denote the transitive closure of this relation. This is an equivalence relation on the set of all admissible Wilson loop diagrams with vertex set $[n]$.
+The relation $\sim$ is an equivalence relation on the set of all admissible Wilson loop diagrams with vertex set $[n]$.
 \end{dfn}
@@
 
-A subset $A \subseteq E$ is called {\em independent} in $M$ if $A \subseteq B$ for some $B \in \cB$, and {\em dependent} otherwise.
+A subset $A \subseteq E$ is called {\em independent} in $M$ if $A \subseteq B$ for some $B \in \cB$, and is called {\em dependent} otherwise.
 (In other words, a basis is simply an independent set of maximal size in $M$.) The {\em rank}  $\rk(A)$ of a subset $A \subseteq E$ is the size of the largest independent set contained in $A$.
@@
 Matroid theory relates to the study of Wilson loop diagrams as follows.
-In \cite{wilsonloop}, Agarwala and Amat show that every weakly admissible Wilson loop diagram with $k$ propagators defines a positroid of rank $k$ on a base set of size $n$, called $M(W)$.
-In other words, by \cite{Postnikov}, each admissible Wilson loop diagram corresponds to a convex subset of $\Gr(k,n)$, thus connecting the geometry of Wilson loop diagrams with the geometry underlying the Amplituhedron.
+In \cite{wilsonloop}, Agarwala and Marin-Amat show that every weakly admissible Wilson loop diagram $W$ with $k$ propagators defines a positroid $M(W)$ of rank $k$ on a base set of size $n$.
+Combined with Postnikov's work in \cite{Postnikov}, this shows that each admissible Wilson loop diagram corresponds to a convex subset of $\Gr(k,n)$, thus connecting the geometry of Wilson loop diagrams with the geometry underlying the Amplituhedron.
+
 The independent sets of $M(W)$ can be read directly from the diagram:
@@
 Note from Definition~\ref{def:CWmatrix} that the vertices of the diagram $W$ correspond to columns of the associated matrix $C(W)$.
-Therefore, for any subset of vertices $V \subseteq [n]$, we can consider the restriction $C(W)|_V$ of $C(W)$ consisting of the columns corresponding to $V$.
-Since the non-zero entries of $C(W)$ are independent real variables, if $C(W)|_V$ has fewer than $|V|$ rows of non-zero entries then it not have full rank.
+Therefore, for any subset of vertices $V \subseteq [n]$ we can consider the restriction $C(W)|_V$ of $C(W)$, which consists of the columns corresponding to $V$.
+Since the non-zero entries of $C(W)$ are independent real variables, if $C(W)|_V$ has fewer than $|V|$ rows of non-zero entries then it does not have full rank.
 This is equivalent to saying that if $V$ is a set of columns of $C(W)$ with $|\Prop(V)| < |V|$, then $V$ is a dependent set.
@@
 
-This section explores the correspondence between Wilson loop diagrams and positroids that was established in \cite{wilsonloop}, (Theorem 3.38).
+This section explores the correspondence between Wilson loop diagrams and positroids that was established in \cite[Theorem 3.38]{wilsonloop}.
 In that paper, the authors show that admissible Wilson loop diagrams define matroids that are also positroids.
-Furthermore, they show that if two Wilson loop diagrams are equivalent, they define the same matroid(Theorems 1.18 and 3.41).
+Furthermore, they show that if two Wilson loop diagrams are equivalent, then they define the same matroid \cite[Theorems 1.18 and 3.41]{wilsonloop}.
 
@@
 (see Theorem \ref{same matroid iff equiv}).
-We also enumerate the number of diagrams that map to an particular matroid in Corollary \ref{number of equiv diagrams}.
+We also enumerate the number of diagrams that map to a particular matroid in Corollary \ref{number of equiv diagrams}.
 To do this, we establish a connection between Wilson loop diagrams and polygon dissections in subsection \ref{sec: polygon partitions}, and uncover some matroidal properties of exact subdiagrams in subsection \ref{sec: exact diagram matroidal props}.
@@
   \item The vertices of $\tau(W)$ correspond to the edges of $W$.
-  \item Labeling the vertices of $\tau(W)$ with the edge number of $W$gives a cyclic order to the vertices.
+  \item Labeling the vertices of $\tau(W)$ with the edge number of $W$ gives a cyclic order to the vertices.
 Connecting consecutive vertices gives a graph theoretic cycle called the polygon of $\tau(W)$.
@@
 
-\emph{Polygon dissection} is a common term in combinatorics for a decomposition of a convex polygon into smaller polygons by means of noncrossing diagonals, see \cite{PSpolygon}.
+\emph{Polygon dissection} is a common term in combinatorics for a decomposition of a convex polygon into smaller polygons by means of noncrossing diagonals; see for example \cite{PSpolygon}.
 Each $\tau(W)$ is such an object.
@@
 Similarly, there does not exist two propagators $p,q$ such that both $p$ and $q$ start at edge $i$ and end at edge $j$.
-Therefore, no other two vertices of $\tau(W)$ can be connected by more than one edge.
-Therefore $\tau(W)$ is a simple graph.
-Finally, the embedding of $\tau(W)$ is induced from the embedding of the graph $W$ and since $W$ is admissible, no pairs of propagators cross.
+Therefore, no two vertices of $\tau(W)$ can be connected by more than one edge, and so $\tau(W)$ is a simple graph.
+Finally, the embedding of $\tau(W)$ is induced from the embedding of the graph $W$, and since $W$ is admissible we know that no pair of propagators can cross.
 Therefore, it is a planar embedding.
@@
   For $W$ an admissible Wilson loop diagram, the polygon dissection $\tau(W)$ has a unique decomposition into maximal triangulated pieces and edges in the polygon of $\tau(W)$.
-Call this a \emph{maximal decomposition}.
+We call this a \emph{maximal decomposition}.
 \end{lem}
@@
     \drawchord{6}{8}
- \draw (0,0) node {$\bullet$};
-\draw (-1,.2) node {$\bullet$};	
-\draw (-.5,1.1) node {$\bullet$};
-\draw (.8,-.3) node {$\bullet$};	
-\draw (1.1,-.5) node {$\bullet$};
-\draw(1.1,-.5) -- (.8,-.3) --(0,0)--(-1,.2) -- (-.5,1.1);
+ \draw[gray] (0,0) node {$\bullet$};
+\draw[gray] (-1,.2) node {$\bullet$};	
+\draw[gray] (-.5,1.1) node {$\bullet$};
+\draw[gray] (.8,-.3) node {$\bullet$};	
+\draw[gray] (1.1,-.5) node {$\bullet$};
+\draw[gray](1.1,-.5) -- (.8,-.3) --(0,0)--(-1,.2) -- (-.5,1.1);
 \foreach \i in {1,2,...,8} {
-      \draw (45*\i:2) node {$\bullet$};
-    }
-\draw (45*1:2) --(0,0) -- (45*5:2);
-\draw (45*6:2) -- (.8,-.3);
-\draw (45*8:2) -- (1.1,-.5) -- (45*7:2);
-\draw (45*2:2) -- (-.5,1.1) -- (45*3:2);
-\draw (45*4:2) -- (-1,.2);
+      \draw[gray] (45*\i:2) node {$\bullet$};
+    }
+\draw[gray] (45*1:2) --(0,0) -- (45*5:2);
+\draw[gray] (45*6:2) -- (.8,-.3);
+\draw[gray] (45*8:2) -- (1.1,-.5) -- (45*7:2);
+\draw[gray] (45*2:2) -- (-.5,1.1) -- (45*3:2);
+\draw[gray] (45*4:2) -- (-1,.2);
 	\end{scope}
@@
     \drawchord{6}{8}
- \draw (.2,.2) node {$\bullet$};
-\draw (.2,-.2) node {$\bullet$};
-\draw (-.2,-.2) node {$\bullet$};
-\draw (-.2,.2) node {$\bullet$};
-\draw (-2,.2) node {$\bullet$};	
-\draw (-.5,1.1) node {$\bullet$};
-\draw (.8,-.3) node {$\bullet$};	
-\draw (1.1,-.5) node {$\bullet$};
-\draw(1.1,-.5) -- (.8,-.3) --(.2,-.2); 
-\draw (-.2, .2) --(-1,.2) -- (-.5,1.1);
+ \draw[gray] (.2,.2) node {$\bullet$};
+\draw[gray] (.2,-.2) node {$\bullet$};
+\draw[gray] (-.2,-.2) node {$\bullet$};
+\draw[gray] (-.2,.2) node {$\bullet$};
+\draw[gray] (-1,.2) node {$\bullet$};	
+\draw[gray] (-.5,1.1) node {$\bullet$};
+\draw[gray] (.8,-.3) node {$\bullet$};	
+\draw[gray] (1.1,-.5) node {$\bullet$};
+\draw[gray](1.1,-.5) -- (.8,-.3) --(.2,-.2); 
+\draw[gray] (-.2, .2) --(-1,.2) -- (-.5,1.1);
 \foreach \i in {1,2,...,8} {
-      \draw (45*\i:2) node {$\bullet$};
-    }
-\draw (45*1:2) --(.2,.2);
-\draw (-.2, -.2) -- (45*5:2);
-\draw (45*6:2) -- (.8,-.3);
-\draw (45*8:2) -- (1.1,-.5) -- (45*7:2);
-\draw (45*2:2) -- (-.5,1.1) -- (45*3:2);
-\draw (45*4:2) -- (-1,.2);
+      \draw[gray] (45*\i:2) node {$\bullet$};
+    }
+\draw[gray] (45*1:2) --(.2,.2);
+\draw[gray] (-.2, -.2) -- (45*5:2);
+\draw[gray] (45*6:2) -- (.8,-.3);
+\draw[gray] (45*8:2) -- (1.1,-.5) -- (45*7:2);
+\draw[gray] (45*2:2) -- (-.5,1.1) -- (45*3:2);
+\draw[gray] (45*4:2) -- (-1,.2);
 	\end{scope}
@@
 \end{dfn}
-More casually this definition says that the maximal triangulated pieces of $\tau(W)$ and $\tau(W')$ are the same (so far as their vertex sets are concerned) but that some or all of the triangulated pieces may be differently triangulated while the region being triangulated by each piece (which is defined by the vertex set) remains unchanged.
+More casually this definition says that the maximal triangulated pieces of $\tau(W)$ and $\tau(W')$ are the same so far as their vertex sets are concerned (and hence the regions triangulated by each piece are the same) but that the configuration of triangles within some or all of the triangulated pieces may be different.
 This definition of retriangulation makes sense for any two polygon dissections of the same polygon, not just for those in the image of $\tau$.
@@
 Note that we include vertex 3 of $\tau(W)$ in $t$ because the two endpoints of edge 3 in $W$ (namely the vertices 3 and 4 in $W$) are both in $V(P)$.
-However, we don't include vertex 5 of $\tau(W)$ in $t$because only one of the endpoints of edge 5 in $W$ is in $V(P)$.
+However, we don't include vertex 5 of $\tau(W)$ in $t$ because only one of the endpoints of edge 5 in $W$ is in $V(P)$.
 The same argument applies to vertices 7, 9 and 10.
@@
 
-The key point to note is that the subgraph $t$ depends on how the propagators of $P$ sit inside $[n]$, not on how they sit in the subdiagram $(P,V(P))$, which would have outer edges between vertices 8 and 9, 9 and 1, 4 and 5, and 5 and 8.
+The key point to note is that the subgraph $t$ depends on how the propagators of $P$ sit inside $[n]$, not on how they sit in the subdiagram $(P,V(P))$ (whose corresponding graph would have additional outer edges between vertices 8 and 9, 9 and 1, 4 and 5, and 5 and 8).
 In particular, $t$ is not the subgraph of $\tau(W)$ consisting only of edges corresponding to propagators of $P$ (as it may also include some of the outer edges of $\tau(W)$), nor is it the polygon dissection of $(P,V(P))$ viewed as a Wilson loop diagram in its own right (which would have vertex set equal to $V(P)$).
@@
 Now suppose $|P|>1$.  Let $j=|P|$, $m= j+3=|V(P)|$, and 
-suppose that the set $V(P)$ defines $c$ disjoint cyclic intervals of $[n]$. Then $t$ has $m-c$ vertices.  If $t$ were a triangulation, $t$ would have $j -c$ internal edges.
+suppose that the set $V(P)$ defines $c$ disjoint cyclic intervals of $[n]$.
+Then $t$ has $m-c$ vertices.
+If $t$ were a triangulation, then $t$ would have $j -c$ internal edges, so we calculate the number of internal edges of $t$.
 
@@
 \item The matroid assoicated to an exact subdiagram of $W$ can be written as a contraction of the matroid $M(W)$ by the complementary propagator flat (Theorem \ref{exact diagrams contractions}). 
-\item The matroid associated to an exact subdiagram is uniform (Theorem \ref{exactuniformthm} ).
+\item The matroid associated to an exact subdiagram is uniform (Theorem \ref{exactuniformthm}).
 \end{enumerate}
@@
 
-For part (2), suppose that $(P, V(P))$ is a maximal exact subdiagram. By Lemma \ref{lem decompose flat} (1) and Corollary \ref{classifyflats} we can decompose $F(P^c)$ as
+For part (2), suppose that $(P, V(P))$ is a maximal exact subdiagram of $W$. By Lemma \ref{lem decompose flat}(1) and Corollary \ref{classifyflats} we can decompose $F(P^c)$ as
 \begin{equation}\label{eq decompose F}V(P)^c = F(P^c) = C \sqcup S = F(\Prop(C)) \sqcup S,\end{equation}
 where $C$ is the largest cyclic flat contained in $F(P^c)$ and $S$ is an independent set.
-We show that $\Prop(C) = P^c$, thus forcing $S$ to be empty.
+We show that $\Prop(C) = P^c$, thus forcing $S$ to be empty and implying that $F(P^c) = C$, i.e.
+$F(P^c)$ is a cyclic flat.
 Note that $C$ must be non-empty since $F(P^c)$ is non-empty and not independent (by part (1)).
 
-By Lemma \ref{lem facts about WLD matroids}(2), $\rk(C) = |\Prop(C)|$.
-Since $S$ is independent, Lemma \ref{lem facts about WLD matroids}(1) gives $|S| = \rk(S)$.
 By similar arguments to Lemma~\ref{lem decompose flat}, the fact that $S$ is independent and that $C$ is the union of all circuits in $F(P^c)$ implies that every element of $S$ is independent of $C$.
-Combining these give the first two inequalities below
-\ba \rk\big(F(P^c)\big) = \rk(C) + \rk(S)  = |\Prop(C)| + |S| \leq |\Prop(F(P^c))|\;,\label{rank of comp flat} \ea % this equation doesn't really need to be displayed, but it was causing a badbox  
-while the inequality comes from the bound on ranks of vertex sets.
-
-Furthermore, from Remark \ref{alt F(P) rmk}, we see that $\Prop (F(P^c)) \subseteq P^c$.
-Therefore equation \eqref{rank of comp flat} gives \bas |\Prop (C)| + |S| \leq |P^c|  \;.\eas For ease of future notation, write $Q = \Prop(C)^c$.
-Rearranging and adding $|P|$ to both sides gives \ba |P| + |S| \leq |P| + |P^c| - |\Prop(C)| = |Q| \;.\label{P+Sbound}\ea Taking complements of and rearranging equation \eqref{eq decompose F} we have
+Further, we know that $\rk(C) = |\Prop(C)|$ from Lemma \ref{lem facts about WLD matroids}(2), and $\rk(S) = |S|$ from Lemma \ref{lem facts about WLD matroids}(1) and the independence of $S$.
+Combining these gives
+\ba \rk\big(F(P^c)\big) = \rk(C) + \rk(S)  = |\Prop(C)| + |S| \leq |\Prop(F(P^c))|\;,\label{rank of comp flat} \ea 
+where the inequality follows from the bound on ranks of vertex sets in Lemma \ref{lem facts about WLD matroids}(1). For ease of future notation, write $Q = \Prop(C)^c$.
+
+From Remark \ref{alt F(P) rmk} it follows that $\Prop (F(P^c)) \subseteq P^c$, and so equation \eqref{rank of comp flat} can be rewritten as \bas |Q^c| + |S| \leq |P^c|  \;.\eas
+
+Rearranging and adding $|P|$ to both sides gives \ba |P| + |S| \leq |P| + |P^c| - |Q^c| = |Q| \;.\label{P+Sbound}\ea 
+Meanwhile, by taking complements of equation \eqref{eq decompose F} it follows that
 \bas V(P) \sqcup S = C^c = F(\Prop(C))^c  = V(Q)\;. \eas
@@
 
-Since \bas \Prop(C) \subseteq \Prop(F(P^c)) \subseteq P^c \eas taking complements gives $P \subseteq \Prop(C)^c = Q$.
-In other words, $(P, V(P))$ is an exact subdiagram of $(Q, V(Q))$.
-Since $(P, V(P))$ is a maximal exact subdiagram, $P=Q$, or $\Prop (C) = P^c$, and thus $S = \emptyset$, forcing $F(P^c)$ to be a cyclic flat.
-\sanote{the previous proof of (2) (commented out) was making my head spin.
-I think this is more straightforward, butI might just be rearranging deckchairs.}
+Since $\Prop(C) \subseteq \Prop(F(P^c)) \subseteq P^c$, it follows that $P \subseteq \Prop(C)^c = Q$.
+In other words, $(P, V(P))$ is a subdiagram of $(Q, V(Q))$.
+Since $(P, V(P))$ is a maximal exact subdiagram by assumption, we must have $P=Q$.
+Recalling that $Q = \Prop(C)^c$, we finally obtain $\Prop (C) = P^c$ and hence $S = \emptyset$.
+This completes the proof of (2).
 %\begin{comment}For part (2), suppose that $(P, V(P))$ is a maximal exact subdiagram. By Lemma \ref{lem decompose flat} (1) and Corollary \ref{classifyflats} we can decompose $F(P^c)$ as
@@
 
-In \cite{wilsonloop}, Agarwala and Amat show that certain subdiagrams of $W$ can be realized as contractions of $M(W)$:
+In \cite{wilsonloop}, Agarwala and Marin-Amat show that certain subdiagrams of $W$ can be realized as contractions of $M(W)$:
 
@@
 
-We now make a few observations about the geometry of matroids defined by exact diagrams.
-
-In \cite{wilsonloop}, the authors show that each weakly admissible Wilson loop diagrams correspond to a positroid.
+To close this section, we make a few observations about the geometry of matroids defined by exact diagrams.
+
+In \cite{wilsonloop}, the authors show that each weakly admissible Wilson loop diagram corresponds to a positroid.
 That is, each diagram corresponds to a matroid that can be represented by elements of the positive Grassmannian $\Gr(|\cP|, n)$.
@@
 These subspaces give a CW structure on $\Gr(k,n)$, with each positroid defining a cell.
-In other words, there is a map from weakly admissible Wilson loop diagrams, $W$, to matroids, $M(W)$, to positroid cells in the CW complex on $\Gr(|\cP|, n)$.
+In other words, there is a map from weakly admissible Wilson loop diagrams $W$ to matroids $M(W)$ to positroid cells in the CW complex on $\Gr(|\cP|, n)$.
 
@@
 \begin{cor}
-Let $(P, V(P))$ be an exact subdiagram of $W$. The matroid associated to this subdiagram corresponds to the top dimensional cell in $\Gr(|P|, |V(P)|)$.
+Let $W' = (P, V(P))$ be an exact subdiagram of $W$. The matroid associated to this subdiagram corresponds to the top dimensional cell in $\Gr(|P|, |V(P)|)$.
 \end{cor}
@@
 \begin{proof}
-The unique top dimensional cell of $\Gr(|P|, |V(P)|)$ is defined by precisely those points in $\Gr(|P|, |V(P)|)$ with the property that all Pl\"ucker coordinates are strictly greater than $0$.
-Since $(P, V(P))$ is an exact subdiagram, the matroid is uniform, and so all $|P| \times |P|$ minors are non-zero.
-Since $(P, V(P))$ is weakly admissible, the matroid associated to it can be realized by an element of the totally nonnegative Grassmannian $\Gr(k,n)$, by Theorem \ref{thm WLD defines matroid}.
+Since $W'$ is weakly admissible, by Theorem \ref{thm WLD defines matroid} the associated matroid $M(W')$ can be realized by an element of the totally nonnegative Grassmannian $\Gr(|P|,|V(P)|)$.
+However, since $W'$ is an exact subdiagram its corresponding matroid $M(W')$ is uniform, so all $|P| \times |P|$ minors of $C(W')$ must be non-zero and $M(W')$ can be represented by a matrix with all maximal minors strictly positive.
+Since the unique top dimensional cell of $\Gr(|P|, |V(P)|)$ is defined by precisely those points in $\Gr(|P|, |V(P)|)$ with the property that all Pl\"ucker coordinates are strictly greater than $0$, this completes the proof.
 \end{proof}
@@
 
-Now we are ready to prove the main results of this section, namely that two Wilson loop diagrams define the same matroid (positroid) if and only if they are equivalent (Theorem \ref{same matroid iff equiv}).
+Now we are ready to prove the main result of this section, namely that two Wilson loop diagrams define the same matroid (positroid) if and only if they are equivalent (Theorem \ref{same matroid iff equiv}).
 We also give a formula for the number of Wilson loop diagrams in a given equivalence class (Corollary \ref{number of equiv diagrams}), completing the characterization of the correspondence between Wilson loop diagrams and positroids starting in \cite{wilsonloop}.
@@
 
-In this section we have characterized the correspondence between Wilson loop diagrams and positroids, showing that Wilson Loop diagrams define the same positroid if and only if they are equivalent (Theorem \ref{same matroid iff equiv}).
-If we write \bas M: \textrm{admissible \; WLD} & \rightarrow \textrm{Positroids} \\ W & \rightarrow M(W) \;,\eas the image of this map is given by the distinct equivalence classes.
+In this section we have characterized the correspondence between Wilson loop diagrams and positroids, showing that Wilson Loop diagrams define the same positroid if and only if they are equivalent.
+If we write \bas M: \textrm{admissible WLD} & \longrightarrow \textrm{Positroids} \\ W & \mapsto M(W) \;,\eas the image of this map is given by the distinct equivalence classes.
 Corollary \ref{number of equiv diagrams} enumerates the elements of each fiber of $M$.
@@
 We know from examples (e.g.
-\cite{casestudy}) that many positroid cells do not appear as admissible Wilson loop diagrams with a fixed number of propagators and vertices.
-That is, the map from admissible Wilson loop diagrams to positroid cells of the correct dimension in the correct Grassmannian neither injective nor surjective.
-We do not obtain a formula for the number of cells, but do obtain an alternate characterization of the equivalence classes which is the subject of the next section.
+\cite{casestudy}) that many positroid cells cannot be obtained as the matroids of admissible Wilson loop diagrams.
+We do not obtain a formula for the number of cells in the image of $M$ here, but in the next section we give an alternate characterization of ${\rm im}(M)$ in terms of associahedra, with the hope that this linkage with a well-studied combinatorial object will shed light on the issue in the future.
 
@@
 In order to explore this connection further, we first need some background, which is given in Section~\ref{sec polytope background}.
-
-%Associahedra can be defined in terms of polygon partitions.
 In Section~\ref{sec associahedron results}, we show that the number of equivalence classes of Wilson loop diagrams correspond to the number of non-parallel faces of the appropriate associahedron (Theorem \ref{thm:count inequiv diagrams}).
-While this section does not give an explicit formula for the number of these faces, we hope that this linkage with a well-studied combinatorial object will shed light on the issue in the future.
 
@@
 A \emph{face} of a polytope is the intersection of the polytope with any hyperplane for which the entire polytope is in one of the closed half-spaces defined by the hyperplane.
-The polytope itself is also considered a face; in the case that the polytope is of full dimension, this definition can be unified by considering linear equalities (including the trivial one) in place of hyperplanes and the corresponding linear inequalities in place of the half-spaces defined by the hyperplane (see chapter 2 of \cite{Ziegler}).
+The polytope itself is also considered a face; in the case that the polytope is of full dimension, this definition can be unified by considering linear equalities (including the trivial one) in place of hyperplanes and the corresponding linear inequalities in place of the half-spaces defined by the hyperplane (see Chapter 2 of \cite{Ziegler}).
 
@@
 
-There are many important polytopes in combinatorics, including, of primary importance to us, the associahedron. The associahedron can be characterized in many different ways; here is one definition.
+As with many of the interesting and well-studied polytopes in combinatorics, the associahedron can be characterized in many different ways; here is one definition.
 
@@
 It turns out that this defines a class of combinatorially equivalent polytopes, which can be proved by giving a realization.
-There are many interesting realizations of the associahedron \cite{CSZinequivalent}; the following realization will be the one which we will use.
+There are many interesting realizations of the associahedron \cite{CSZinequivalent}; the following realization will be the one that we use.
 
@@
 For each $t\in T$, define $s_t$ to be the point in $\mathbb{R}^n$ whose $i$th coordinate is the sum of the areas of all triangles of $t$ which are incident to $x_i$.
-Let $A_n$ be the convex hull of the $s_t$; then $A_n$ a realization of the $n-1$ associahedron (\cite[Example 9.11]{Ziegler}).
+Let $A_n$ be the convex hull of the $s_t$; then $A_n$ is a realization of the $n-1$ associahedron (\cite[Example 9.11]{Ziegler}).
 \end{dfn}
@@
 In general the $x_1, \ldots, x_n$ may be any points in any $\mathbb{R}^d$.
-Triangulations in this more general context are decompositions into simplices and the area of the triangles is replaced by the volume of the simplices.
+Triangulations in this more general context are decompositions into simplices, and the area of the triangles is replaced by the volume of the simplices.
 
@@
 We also need the following notation: given a polygon dissection $D$ of an $n$-gon, let $V_{>3}(D)$ be the set of vertices of the polygon which are on at least one non-triangle face of $D$.
-(Note that $D$ may have many non-triangle faces and so $V_{>3}(D)$ will be the union of the vertices of each non-triangle face.) We also write $[x_i,x_j]$ for the set of vertices from $x_i$ to $x_j$ including the endpoints, and $(x_i,x_j)$ for the same set but excluding the endpoints.
+(Note that $D$ may have many non-triangle faces and so $V_{>3}(D)$ will be the union of the vertices of each non-triangle face.) For the purposes of this proof, we also write $[x_i,x_j]$ for the set of vertices from $x_i$ to $x_j$ including the endpoints, and $(x_i,x_j)$ for the same set but excluding the endpoints.
 
@@
 
-Assume for a contradiction that no quadrilateral as in the statement exists, and let $d$ be a diagonal in $D_1$ crossing the unique non-triangle face, $f$, of $D_2$.
-Then $f$ must have two vertices strictly on each side of $d$: name the vertices on one side of $d$ as $x_i$ and $x_j$, and those on the other side as $x_k$, $x_l$ (and in that order; see Figure~\ref{inductive_step}).
+Assume for a contradiction that no quadrilateral as in the statement exists, and let $d$ be a diagonal in $D_1$ crossing the unique non-triangle face $f$ of $D_2$.
+Then $f$ must have two vertices strictly on each side of $d$; we name the vertices on one side of $d$ as $x_i$ and $x_j$, and those on the other side as $x_k$, $x_l$ (and in that order; see Figure~\ref{inductive_step}).
 Let $g$ be the face in $D_1$ that is incident to $d$ on the $x_i, x_j$ side of $d$.
@@
 
-Similarly, if $g$ is a quadrilateral then immediately by the same argument none of its vertices can lie in the interval $(x_i, x_j)$, nor can we have exactly one of $x_i$ or $x_j$ being a vertex of $g$ for the same reason.
-If both the other vertices of $g$ are $x_i$ and $x_j$ (so $g$ is the quadrilateral defined by $x_i$, $x_j$, and the two endpoints of $d$) then we still obtain a configuration as described in the lemma statement by swapping the roles of $f$ and $g$: now the four vertices would be the ones defining $g$, and the diagonal would be one of the edges of $f$.
+Similarly, if $g$ is a quadrilateral then by the same argument none of its vertices can lie in the interval $(x_i, x_j)$, nor can we have exactly one of $x_i$ or $x_j$ being a vertex of $g$ for the same reason.
+If $x_i$ and $x_j$ are both vertices of $g$ (so $g$ is the quadrilateral defined by $x_i$, $x_j$, and the two endpoints of $d$) then we still obtain a configuration as described in the lemma statement by swapping the roles of $f$ and $g$: now the four vertices would be the ones defining $g$, and the diagonal would be one of the edges of $f$.
 (For instance $d$ can now be the edge connecting $x_l$ to $x_i$ or $x_j$ to $x_k$.) Thus we can conclude that none of the vertices of the face $g$ are in the interval $[x_i, x_j]$.
@@
 As observed in the proof of Proposition~\ref{prop easy way}, any non-zero vector in $\R^n$ parallel to an edge of $A_n$ has non-zero entries only in the coordinates corresponding to the four vertices bounding the quadrilateral of the dissection associated with the edge.
-Thus if $V_{>3}(\tau(W)) \neq V_{>3}(\tau(X))$ (notation as defined before Lemma \ref{lem good quads}) then the span of the vectors parallel to their edges has different support and so they cannot be parallel.
+Thus if $V_{>3}(\tau(W)) \neq V_{>3}(\tau(X))$ (recall the notation defined before Lemma \ref{lem good quads}) then the span of the vectors parallel to their edges has different support and so they cannot be parallel.
 So we can assume that $V_{>3}(\tau(W)) = V_{>3}(\tau(X))$.

### 2019-08-01 GWLDCI.tex
two small things

@@
 
-In \cite{wilsonloop} Agarwala and Amat showed that every weakly admissible Wilson loop diagrams can be identified with a type of matroid called a positroid, and observed that this mapping is neither one-to-one nor onto.
+In \cite{wilsonloop} Agarwala and Marin-Amat showed that every weakly admissible Wilson loop diagrams can be identified with a type of matroid called a positroid, and observed that this mapping is neither one-to-one nor onto.
 Each such positroid corresponds to a positroid cell in the appropriate positive Grassmannian $\Gr(k,n)$ \cite{Postnikov}.
@@
 As noted above, Agarwala and Marin-Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that are realized as an element of the positive Grassmannian $\Gr(k,n)$ \cite{wilsonloop}.
-In separate papers with Fryer and Marcott, this work was extended to study these Feynman integrals in terms of positroid cells and the positive Grassmannians \cite{casestudy, non-orientable}.
+In separate papers with Fryer and with Marcott, this work was extended to study these Feynman integrals in terms of positroid cells and the positive Grassmannians \cite{casestudy, non-orientable}.
 Others have tried different approaches to define a geometric space associated to these integrals in a manner similar to the Amplituhedron \cite{Amplituhedronsquared, HeslopStewart}.
@@
 
-From Remark \ref{alt F(P) rmk} it follows that $\Prop (F(P^c)) \subseteq P^c$, and so equation \eqref{rank of comp flat} can be rewritten as \bas |Q^c| + |S| \leq |P^c|  \;.\eas
+From Remark \ref{alt F(P) rmk} it follows that $\Prop (F(P^c)) \subseteq P^c$, and so equation \eqref{rank of comp flat} implies \bas |Q^c| + |S| \leq |P^c|  \;.\eas
 

### 2019-08-02 GNproof.tex
tweaked GNproof

@@
 
-We first note that if $a_{m-1}$ and $a_{m}$ are not consecutive vertices for some $m$, then for any intermediate vertex $a_{m-1}<_i x <_i a_{m}$ we must have $\Prop(x) \subseteq \cP_{m-1}$.
+We enumerate two important observations: \begin{enumerate} \item If $a_{m-1}$ and $a_{m}$ are not consecutive vertices for some $m$, then for any intermediate vertex $a_{m-1}<_i x <_i a_{m}$ we must have $\Prop(x) \subseteq \cP_{m-1}$.
 This is because if any propagator supported on $x$ is still unassigned when the algorithm reaches $x$, we would have $x \in I_i$.
-We also note that when $p_m$ contributes $I_i(p_m) = a_m$ to the Grassmann necklace, it must be the clockwise-most propagator (amongst those not yet assigned) that is supported on $a_m$ i.e.
-clockwise-most amongst propagators in the set $\cP \setminus \cP_{m-1}$.
+\item When $p_m$ contributes $I_i(p_m) = a_m$ to the Grassmann necklace, it must be the clockwise-most propagator (amongst those not yet assigned) that is supported on $a_m$ i.e.
+any other propagators supported by $a_m$ in $\cP \setminus \cP_{m-1}$ is inside $p_m$ in the $a_m-1$ ordering.\end{enumerate} \sanote{maybe move to a remark before lemma for ease of reference?}
 
@@
 
-If $\Prop(j_m) = \emptyset$ then $J$ is automatically dependent since the corresponding column of $C(W)$ contains only zeros, so suppose henceforth that $\Prop(j_m) \neq \emptyset$.
+%If $\Prop(j_m) = \emptyset$ then $J$ is automatically dependent since the corresponding column of $C(W)$ contains only zeros, so suppose henceforth that $\Prop(j_m) \neq \emptyset$.
 In particular, this implies that $m>1$, since if $m=1$ we would have $\Prop(j_1) \subseteq \cP_0 = \emptyset$.
@@
 It is easily verified that this is an increasing chain of sets: indeed, if $q \in Q_l$ then $I_i(q) \in I_i(Q_l)$, and since $I_i(q)$ is one of the vertices that supports $q$ we must have $q \in \Prop(I_i(Q_l)) = Q_{l+1}$.
-The sequence therefore stabilizes in finitely many steps, since $\cP$ is finite.
+Since $\cP$ is finite, the sequence therefore stabilizes in finitely many steps when $Q_{l+1} = Q_l$.
+Let $Q$ be this set of propagators.
+We show that $I_i(Q) \cup {j_m}$ is a dependent set because it only supports the propagators in $Q$ but has $|Q|+1$ vertices.
+Thus $J$ is a dependent set, and the Grassmann necklace $(I_1,\dots,I_n)$ constructed from $W$ does indeed define the positroid $M(W)$.
 
-We claim that $Q_l \subseteq \cP_{m-1}$ for all $l\geq 0$. The case $l= 0$ follows immediately from the observation above that $\Prop(j_m) \subseteq \cP_{m-1}$.
+We construct $Q$ by induction.
+If $Q_0 = \Prop(j_m) = \emptyset$, then $Q = Q_0$, and $I_i(Q) \cup {j_m}= j_m$, a single vertex supporting no propagators, and thus a dependent set.
+Otherwise, $Q_0 \subseteq \cP_{m-1}$ follows immediately from the first observation above that $\Prop(j_m) \subseteq \cP_{m-1}$
 
 Now assume that $Q_0,\dots,Q_{l-1} \subseteq \cP_{m-1}$, and consider $Q_{l}$.
-If $Q_{l} \setminus Q_{l-1} = \emptyset$ then we are done; if not, let $q \in Q_{l} \setminus Q_{l-1}$.
-By construction there is some propagator $p_r \in Q_{l-1}$ such that $p_r$ and $q$ are both supported on $I_i(p_r) = a_r$.
+If $Q_{l} \setminus Q_{l-1} = \emptyset$ then we are done, with $Q = Q_l$.
+Otherwise, let $q \in Q_{l} \setminus Q_{l-1}$.
+By construction there is some propagator $p_r \in Q_{l-1}\setminus Q_{l-2}$ such that $p_r$ and $q$ are both supported on $I_i(p_r) = a_r$.
 If $q$ is clockwise of $p_r$ on vertex $a_r$ then we immediately have $q \in \cP_{m-1}$ as observed above.
-However, if $q$ is counter-clockwise of $p_r$ then we need to show that $p_r$ or another propagator in $Q_l$ constrains the positioning of the other end of $q$ and prevents it from ``escaping'' past $j_m$.
+However, if $q$ is counter-clockwise of $p_r$  we show that $V(q) \subseteq [a_r-1, j_m-1]$.
+(If $l>0$, then $j_m \not \in V_q$.) That is, $q$ contributes before $j_m-1$.
+Since $I_i(q) \not \in [a_{m-1}+1, j_m-1]$, $q$ must be in $\cP_{m-1}$ as desired.
 
-Note that we cannot have $a_r+ 1 = j_m$ when $q$ is counterclockwise of $p_r$, since $q \not\in \Prop(j_m)$ by assumption.
+To check that $V(q) \subseteq [a_r-1, j_m-1]$, there are two cases to consider: when $V(p_r) \subseteq [i, j_m]$ ($[i, j_m-1]$ if $l >1$), and when this does not hold.
+In the first case, non-crossing propagators force $V(q) \subseteq [a_r-1, j_m-1]$.
+
+%Note that we cannot have $a_r+ 1 = j_m$ when $q$ is counterclockwise of $p_r$, since $q \not\in \Prop(j_m)$ by assumption.
 If the other end of $p_r$ (i.e.
@@
 
-If not, then there must be some propagator $p_s \in Q_{l-2}$ such that $p_r$ and $p_s$ are both supported on $I_i(p_s) := a_s$.
-Since $p_r$ is clockwise of $q$, and $q$ cannot be supported on $I_i(p_s)$ since $q \not\in Q_{l-1}$, it follows that $I_i(p_s) <_i I_i(p_r)$.
+If $V(p_r) \not \subseteq [i, j_m]$, then there must be some propagator $p_s \in Q_{l-2}\setminus Q_{l-3}$ such that $p_r$ and $p_s$ are both supported on $I_i(p_s) := a_s$.
+Since $p_r$ is outside $q$ in the $a_r-1$ order, and $q \not\in Q_{l-1}$, $q$ cannot be supported on $I_i(p_s)$.
+It follows that $I_i(p_s) <_i I_i(p_r)$.
 Therefore $q$ is inside $p_s$ with respect to $<_{a_s - 1}$ as well.
@@
 
-Now repeat the argument above with $p_s$ in place of $p_r$: if the other end of $p_s$ lands on an edge between $q$ and $j_m$ then we have $q \in \cP_{m-1}$ as above; if not then there exists some $p_t \in Q_{l-3}$ with $p_s$ supported on $I_i(p_t)$ and $I_i(p_t) <_i I_i(p_r)$.
+Now repeat the argument above with $p_s$ in place of $p_r$.
+Either $V(p_s)  \subseteq [i, j_m]$, or $V(p_s) \not \subseteq [i, j_m]$.
+In the first case, $V(q) \subseteq [a_r-1, j_m-1]$.
+In the secont case, there exists some $p_t \in Q_{l-3}$ with $p_s$ supported on $I_i(p_t)$ and $I_i(p_t) <_i I_i(p_s)$.
 Since there are finitely many steps this process can take before reaching $Q_0$, and any $p_* \in Q_0  = \Prop(j_m)$ has $j_m$ in its support by definition, this argument eventually terminates with the construction of a propagator constraining the positioning of $q$ as required.
@@
 
-Finally, let $Q:= \lim_{l\rightarrow \infty} Q_l$; by the above, this is well-defined and contained in $\cP_{m-1}$.
+%Finally, let $Q:= \lim_{l\rightarrow \infty} Q_l$; by the above, this is well-defined and contained in $\cP_{m-1}$.
 We can now show that $J$ is a dependent set, by constructing a subset $U \subseteq J$ that satifies $|\Prop(U)| < |U|$.
 
-Specifically, we take $U = I_i(Q) \cup \{j_m\}$.
+%Specifically, we take $U = I_i(Q) \cup \{j_m\}$.
 This is a subset of $J$ because $I_i$ and $J$ agree on their first $m-1$ terms and $Q \subseteq \cP_{m-1}$.
@@
 On the other hand, since $\Prop(j_m) \subseteq Q$, we have
-\[\Prop(U) = \Prop(I_i(Q)) \cup \Prop(j_m) = Q\]
-by the construction of $Q$, and hence $|\Prop(U)| = |Q| < |U|$. Thus $J$ is a dependent set, and the Grassmann necklace $(I_1,\dots,I_n)$ constructed from $W$ does indeed define the positroid $M(W)$.
+%\[\Prop(U) = \Prop(I_i(Q)) \cup \Prop(j_m) = Q\]
+%by the construction of $Q$, and hence $|\Prop(U)| = |Q| < |U|$. Thus $J$ is a dependent set, and the Grassmann necklace $(I_1,\dots,I_n)$ constructed from $W$ does indeed define the positroid $M(W)$.
 \end{proof}

### 2019-08-02 GWLDCII.tex
started on intro revisions

@@
 In contrast, the first paper in this series focuses on combinatorial and matroidal properties of the Wilson loop diagrams.
-The main focus of that paper was to enumerate the positroid cells that could be associated to Wilson loop diagrams with a fixed number of vertices and propagators, as well as counting the number of Wilson loop diagrams in the pre-image of any positroid cell under this association.
+The main focus of that paper is to enumerate (without identifying) the positroid cells that associated to Wilson loop diagrams with a fixed number of vertices and propagators, as well as counting the number of Wilson loop diagrams in the pre-image of any positroid cell under this association.
 
@@
 This led to the representation of the on shell integrals associated to this theory in terms of a geometric space (the Amplituhedron) embedded in $\Gr(k,n)$ \cite{Arkani-Hamed:2013kca,Arkani-Hamed:2013jha}.
-Moreover, integrals associated to the BCFW diagrams define a volume form on the Amplituhedron, \hlfix{which is useful for ...}{we need a vague one-line description here}.
+Moreover, integrals associated to the BCFW diagrams define a volume form on the Amplituhedron.
+This both gives a novel and elegant interpretation of scattering Amplitudes for this theory, as well as a means of simplifying the calculations greatly from traditional Feynman diagram approaches.
 Since then, there has been significant work to understand the volume form and its physical implications \cite{UnwindingAmplituhedron,galashinlam}.

### 2019-08-05 GWLDCII.tex
fixed intro and calculation in paper 2

@@
 These integrals are calculated via holomorphic Wilson loops.
-As with the Amplituhedron, each Wilson loop represents the sum of a family of $N^kMHV$ Feynman diagrams, and adding up the corresponding sums of Feynman integrals associates a volume form to \hlfix{space}{I don't know if this was supposed to say ``space'' or ``this space'', and if ``this space'' I don't know which space it's referring to.} \cite{Hodges:2012ym}.
+As with the Amplituhedron, each Wilson loop represents the sum of a family of $N^kMHV$ Feynman diagrams, and adding up the corresponding sums of Feynman integrals associates a volume form to a convex space different from the Amplituhedron \cite{Hodges2013}.
 The first author and Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that can be realized as an element of $\Gr(k,n)$ \cite{wilsonloop}, while other work has shown a connection between the space parametrized by Wilson loop diagrams and the Amplituhedron \cite{casestudy, Amplituhedronsquared}.
@@
 Furthermore, the cells associated to the Wilson loop diagrams are different from the cells associated to BCFW diagrams, as one sees from counting arguments in comparing the results of \cite{AmplituhedronDecomposition} and \cite{casestudy}.
-This is not too alarming, as \hlfix{one expects}{can we call this a conjecture?} the space parametrized by the Wilson loop diagrams to project down to something close to the Amplituhedron \cite{wilsonloop, Amplituhedronsquared}.
+This is not too alarming, as it is conjectured the space parametrized by the Wilson loop diagrams to project down to something close to the Amplituhedron \cite{wilsonloop, Amplituhedronsquared}.
 
 This paper continues this work by identifying which positroid cells are associated to which Wilson loop diagram: specifically, we give an algorithm to read off the Grassmann necklace of the associated positroid cell from the Wilson loop diagram.
-We also show that the positroid cells associated to Wilson loop diagrams are all $3k$ dimensional; by contrast, the BCFW cells are all $4k$ dimensional \hlfix{[ref]}{someone actually proved this, right?}.
+We also show that the positroid cells associated to Wilson loop diagrams are all $3k$ dimensional; by contrast, the BCFW cells are all $4k$ dimensional \cite{Arkani-Hamed:2013jha}.
 Again, this is not too alarming, as it was shown in \cite{non-orientable} that the actual geometric space parametrized by the Wilson loop diagrams is a non-orientable $k$-dimensional bundle over this $3k$ dimensional manifold in $\Gr(k,n)$.
 
-As noted above, the sum of the Feynman integrals associated to Wilson loop diagrams gives the volume of \hlfix{the space}{help?}; if this volume is to be finite, then any singularities appearing in individual integrals must cancel out in the overall sum.
-This has been verified explicitly in a few cases \cite{casestudy, HeslopStewart}, but it is hard to prove in general due to the fact that the relationship between Wilson loop diagrams and $3k$ dimensional positroid cells of $\Gr(k,n)$ is neither one-to-one nor onto.
+As noted above, the sum of the Feynman integrals associated to Wilson loop diagrams gives the volume of a convex polytope; if this volume is to be finite, then any singularities appearing in individual integrals must cancel out in the overall sum.
+This has been conjectured in general \cite{Hodges2013} and verified explicitly in a few cases \cite{casestudy, HeslopStewart}, but it is hard to prove in general due to the fact that the relationship between Wilson loop diagrams and $3k$ dimensional positroid cells of $\Gr(k,n)$ is neither one-to-one nor onto.
 In this paper, we give a characterization of the factors appearing in the denominator of these Feynman integrals in terms of the Grassmann necklace of the associated positroid, thus providing a much simpler and more tractable link between the singularities and the diagrams.
@@
 
-To calculate $R(W)$, write \bmls R_1 = c_{1,1} c_{1, 2}\quad R_2 = c_{2,2} c_{2,3} \quad R_4 = c_{2,5} (c_{2,4}c_{1,5} - c_{2,5}c_{1,4})c_{1,4} \\ R_5 = c_{4,6} (c_{4,6}c_{3,5} - c_{3,6}c_{4,5})c_{3,5} \quad R_7 = c_{3,7} c_{3,8} \quad R_8 = c_{4,8} c_{4,1} \;.\emls All other $R_e$ are $1$.
-Finally, the integrand associated to this Wilson loop diagram is \bas \Omega(W) = \frac{\textrm{d}c_{1,1}\textrm{d}c_{1,1}\textrm{d}c_{1,1}\textrm{d}c_{1,2}\textrm{d}c_{1,4}\textrm{d}c_{1,5}\textrm{d}c_{2,1}\textrm{d}c_{2,3}\textrm{d}c_{2,4}\textrm{d}c_{2,5}\textrm{d}c_{3,5}\textrm{d}c_{3,6}\textrm{d}c_{3,7}\textrm{d}c_{3,7}\textrm{d}c_{4,5}\textrm{d}c_{4,6}\textrm{d}c_{4,8}\textrm{d}c_{4,1}}{c_{1,1} c_{1, 2}c_{2,2} c_{2,3}c_{2,5} (c_{2,4}c_{1,5} - c_{2,5}c_{1,4})c_{1,4}c_{4,6} (c_{4,6}c_{3,5} - c_{3,6}c_{4,5})c_{3,5}c_{3,7} c_{3,8}c_{4,8} c_{4,1}} \;.
+To calculate $R(W)$, write \bmls R_1 = c_{1,1} c_{1, 2}\quad R_2 = c_{2,2} c_{2,3} \quad R_4 = c_{2,5} (c_{2,4}c_{1,5} - c_{2,5}c_{1,4})c_{1,4} \\ R_5 = c_{4,6} (c_{4,5}c_{3,6} - c_{3,5}c_{4,6})c_{3,5} \quad R_7 = c_{3,7} c_{3,8} \quad R_8 = c_{4,8} c_{4,1} \;.\emls All other $R_e$ are $1$.
+Finally, the integrand associated to this Wilson loop diagram is \bas \Omega(W) = \frac{\textrm{d}c_{1,1}\textrm{d}c_{1,2}\textrm{d}c_{1,4}\textrm{d}c_{1,5}\textrm{d}c_{2,2}\textrm{d}c_{2,3}\textrm{d}c_{2,4}\textrm{d}c_{2,5}\textrm{d}c_{3,5}\textrm{d}c_{3,6}\textrm{d}c_{3,7}\textrm{d}c_{3,8}\textrm{d}c_{4,5}\textrm{d}c_{4,6}\textrm{d}c_{4,8}\textrm{d}c_{4,1}}{c_{1,1} c_{1, 2}c_{2,2} c_{2,3}c_{2,5} (c_{2,4}c_{1,5} - c_{2,5}c_{1,4})c_{1,4}c_{4,6} (c_{4,5}c_{3,6} - c_{3,5}c_{4,6})c_{3,5}c_{3,7} c_{3,8}c_{4,8} c_{4,1}} \;.
 \eas
-\note{Is the numerator just supposed to be the product of $dc_{pq}$ for each $c_{pq}$ in the matrix? Also I think $c_{46}c_{35} - c_{36}c_{45}$ in the denominator is the wrong way around?}
 \end{eg}

### 2019-08-09 GNproof.tex
made changes to GNproof according to Karen's comments; removed non-crossing partition reference

@@
 Let $Q$ be this set of propagators.
-We show that $I_i(Q) \cup {j_m}$ is a dependent set because it only supports the propagators in $Q$ but has $|Q|+1$ vertices.
+We show that $I_i(Q) \subseteq \mathcal{P}_{m-1}$.
+Since $I_i$ assigns a single vertex to each propagator, $|I_i(Q)| = |Q|$.
+Therefore $I_i(Q) \cup {j_m}$ is a dependent set because it only supports the propagators in $Q$ but has $|Q|+1$ vertices.
 Thus $J$ is a dependent set, and the Grassmann necklace $(I_1,\dots,I_n)$ constructed from $W$ does indeed define the positroid $M(W)$.
@@
 
-To check that $V(q) \subseteq [a_r-1, j_m-1]$, there are two cases to consider: when $V(p_r) \subseteq [i, j_m]$ ($[i, j_m-1]$ if $l >1$), and when this does not hold.
+To check that $V(q) \subseteq [a_r-1, j_m-1]$, there are two cases to consider: when $V(p_r) \subseteq [a_r-1, j_m]$ ($[a_r-1, j_m-1]$ if $l >1$), and when this does not hold.
 In the first case, non-crossing propagators force $V(q) \subseteq [a_r-1, j_m-1]$.
@@
 
-If $V(p_r) \not \subseteq [i, j_m]$, then there must be some propagator $p_s \in Q_{l-2}\setminus Q_{l-3}$ such that $p_r$ and $p_s$ are both supported on $I_i(p_s) := a_s$.
+If $V(p_r) \not \subseteq [a_r-1, j_m]$, then there must be some propagator $p_s \in Q_{l-2}\setminus Q_{l-3}$ such that $p_r$ and $p_s$ are both supported on $I_i(p_s) := a_s$.
 Since $p_r$ is outside $q$ in the $a_r-1$ order, and $q \not\in Q_{l-1}$, $q$ cannot be supported on $I_i(p_s)$.
@@
 Now repeat the argument above with $p_s$ in place of $p_r$.
-Either $V(p_s)  \subseteq [i, j_m]$, or $V(p_s) \not \subseteq [i, j_m]$.
-In the first case, $V(q) \subseteq [a_r-1, j_m-1]$.
-In the secont case, there exists some $p_t \in Q_{l-3}$ with $p_s$ supported on $I_i(p_t)$ and $I_i(p_t) <_i I_i(p_s)$.
+Either $V(p_s)  \subseteq [a_s-1, j_m]$, or $V(p_s) \not \subseteq [a_s-1, j_m]$.
+In the first case, $V(q) \subseteq [a_s-1, j_m-1]$.
+In the second case, there exists some $p_t \in Q_{l-3}$ with $p_s$ supported on $I_i(p_t)$ and $I_i(p_t) <_i I_i(p_s)$.
 Since there are finitely many steps this process can take before reaching $Q_0$, and any $p_* \in Q_0  = \Prop(j_m)$ has $j_m$ in its support by definition, this argument eventually terminates with the construction of a propagator constraining the positioning of $q$ as required.

### 2019-08-09 GNproof.tex
really do have to say it with inner and outer vertices

@@
 
+\begin{dfn}
+Let $p = (i, j)$ be a propatagor in $W = (\cP, [n])$.
+Without loss of generality, impose the $<_i$ ordering on $p$.
+Then $p$ partitions the vertices of $W$ into three groups: $V(p)$, the vertices of $p$, $V_{in}(p) = [i+2, j-1]$, the vertices (other than $V_p$) that can support propagators in $\cP_{in}$, and $V_{in}(p) = [j+2, i-1]$, the vertices (other than $V_p$) that can support propagators in $\cP_{out}$.
+\end{dfn}
+
 \begin{thm}
@@
 
-To check that $V(q) \subseteq [a_r-1, j_m-1]$, there are two cases to consider: when $V(p_r) \subseteq [a_r-1, j_m]$ ($[a_r-1, j_m-1]$ if $l >1$), and when this does not hold.
-In the first case, non-crossing propagators force $V(q) \subseteq [a_r-1, j_m-1]$.
+To check that $V(q) \subseteq [a_r-1, j_m-1]$, there are two cases to consider: when $j_m \in V_{out}(p_r)$ in the $a_r-1$ order, and when $j_m \in V_{in}(p_r)$.
+Note that for $l>0$, $j_m \not \in V(p_r)$ in the $a_r-1$ order.
 
@@
 
-If $V(p_r) \not \subseteq [a_r-1, j_m]$, then there must be some propagator $p_s \in Q_{l-2}\setminus Q_{l-3}$ such that $p_r$ and $p_s$ are both supported on $I_i(p_s) := a_s$.
+If $j_m \in V_{out}(p_r)$ in the $a_r-1$ order, then there must be some propagator $p_s \in Q_{l-2}\setminus Q_{l-3}$ such that $p_r$ and $p_s$ are both supported on $I_i(p_s) := a_s$.
 Since $p_r$ is outside $q$ in the $a_r-1$ order, and $q \not\in Q_{l-1}$, $q$ cannot be supported on $I_i(p_s)$.
@@
 Now repeat the argument above with $p_s$ in place of $p_r$.
-Either $V(p_s)  \subseteq [a_s-1, j_m]$, or $V(p_s) \not \subseteq [a_s-1, j_m]$.
+Either $j_m \in V_{out}(p_r)$, and when $j_m \in V_{in}(p_r)$.
 In the first case, $V(q) \subseteq [a_s-1, j_m-1]$.

### 2019-08-09 GNproof.tex
try to make a compromise version

--- 2019-08-02 GNproof.tex
@@
 
-We enumerate two important observations: \begin{enumerate} \item If $a_{m-1}$ and $a_{m}$ are not consecutive vertices for some $m$, then for any intermediate vertex $a_{m-1}<_i x <_i a_{m}$ we must have $\Prop(x) \subseteq \cP_{m-1}$.
+We enumerate two important observations:
+\begin{enumerate}
+\item If $a_{m-1}$ and $a_{m}$ are not consecutive vertices for some $m$, then for any intermediate vertex $a_{m-1}<_i x <_i a_{m}$ we must have $\Prop(x) \subseteq \cP_{m-1}$.
 This is because if any propagator supported on $x$ is still unassigned when the algorithm reaches $x$, we would have $x \in I_i$.
 \item When $p_m$ contributes $I_i(p_m) = a_m$ to the Grassmann necklace, it must be the clockwise-most propagator (amongst those not yet assigned) that is supported on $a_m$ i.e.
-any other propagators supported by $a_m$ in $\cP \setminus \cP_{m-1}$ is inside $p_m$ in the $a_m-1$ ordering.\end{enumerate} \sanote{maybe move to a remark before lemma for ease of reference?}
+any other propagators supported by $a_m$ in $\cP \setminus \cP_{m-1}$ is inside $p_m$ in the $a_m-1$ ordering.
+\end{enumerate}
 
@@
 Let $Q$ be this set of propagators.
-We show that $I_i(Q) \cup {j_m}$ is a dependent set because it only supports the propagators in $Q$ but has $|Q|+1$ vertices.
+
+Our remaining goal is to show that $Q \subseteq \mathcal{P}_{m-1}$.
+This will imply the theorem as follows.
+Once the goal is proven we have $I_i(Q)\subseteq J$.
+Then $I_i(Q) \cup {j_m}$ is a dependent set contained in $J$ because it only supports the propagators in $Q$ but has $|Q|+1$ vertices.
 Thus $J$ is a dependent set, and the Grassmann necklace $(I_1,\dots,I_n)$ constructed from $W$ does indeed define the positroid $M(W)$.
 
-We construct $Q$ by induction.
+We now proceed to prove $Q\subseteq \mathcal{P}_{m-1}$ by inductively proving $Q_l \subseteq \mathcal{P}_{m-1}$ for all $l \geq 0$.
 If $Q_0 = \Prop(j_m) = \emptyset$, then $Q = Q_0$, and $I_i(Q) \cup {j_m}= j_m$, a single vertex supporting no propagators, and thus a dependent set.
@@
 If $q$ is clockwise of $p_r$ on vertex $a_r$ then we immediately have $q \in \cP_{m-1}$ as observed above.
-However, if $q$ is counter-clockwise of $p_r$  we show that $V(q) \subseteq [a_r-1, j_m-1]$.
-(If $l>0$, then $j_m \not \in V_q$.) That is, $q$ contributes before $j_m-1$.
-Since $I_i(q) \not \in [a_{m-1}+1, j_m-1]$, $q$ must be in $\cP_{m-1}$ as desired.
+It remains to consider the case that $q$ is counter-clockwise of $p_r$ at $a_r$.
 
-To check that $V(q) \subseteq [a_r-1, j_m-1]$, there are two cases to consider: when $V(p_r) \subseteq [i, j_m]$ ($[i, j_m-1]$ if $l >1$), and when this does not hold.
-In the first case, non-crossing propagators force $V(q) \subseteq [a_r-1, j_m-1]$.
-
-%Note that we cannot have $a_r+ 1 = j_m$ when $q$ is counterclockwise of $p_r$, since $q \not\in \Prop(j_m)$ by assumption.
+Note that we cannot have $a_r+ 1 = j_m$ when $q$ is counterclockwise of $p_r$, since $q \not\in \Prop(j_m)$ by assumption.
 If the other end of $p_r$ (i.e.
@@
 
-If $V(p_r) \not \subseteq [i, j_m]$, then there must be some propagator $p_s \in Q_{l-2}\setminus Q_{l-3}$ such that $p_r$ and $p_s$ are both supported on $I_i(p_s) := a_s$.
-Since $p_r$ is outside $q$ in the $a_r-1$ order, and $q \not\in Q_{l-1}$, $q$ cannot be supported on $I_i(p_s)$.
-It follows that $I_i(p_s) <_i I_i(p_r)$.
+If not, then there must be some propagator $p_s \in Q_{l-2}$ such that $p_r$ and $p_s$ are both supported on $I_i(p_s) := a_s$.
+Since $p_r$ is clockwise of $q$, and $q$ cannot be supported on $I_i(p_s)$ since $q \not\in Q_{l-1}$, it follows that $I_i(p_s) <_i I_i(p_r)$.
 Therefore $q$ is inside $p_s$ with respect to $<_{a_s - 1}$ as well.
@@
 
-Now repeat the argument above with $p_s$ in place of $p_r$.
-Either $V(p_s)  \subseteq [i, j_m]$, or $V(p_s) \not \subseteq [i, j_m]$.
-In the first case, $V(q) \subseteq [a_r-1, j_m-1]$.
-In the secont case, there exists some $p_t \in Q_{l-3}$ with $p_s$ supported on $I_i(p_t)$ and $I_i(p_t) <_i I_i(p_s)$.
+Now repeat the argument above with $p_s$ in place of $p_r$: if the other end of $p_s$ lands on an edge between $q$ and $j_m$ then we have $q \in \cP_{m-1}$ as above; if not then there exists some $p_t \in Q_{l-3}$ with $p_s$ supported on $I_i(p_t)$ and $I_i(p_t) <_i I_i(p_r)$.
 Since there are finitely many steps this process can take before reaching $Q_0$, and any $p_* \in Q_0  = \Prop(j_m)$ has $j_m$ in its support by definition, this argument eventually terminates with the construction of a propagator constraining the positioning of $q$ as required.
-This completes the induction step.
+This completes the induction step, and hence the proof.
 
-%Finally, let $Q:= \lim_{l\rightarrow \infty} Q_l$; by the above, this is well-defined and contained in $\cP_{m-1}$.
-We can now show that $J$ is a dependent set, by constructing a subset $U \subseteq J$ that satifies $|\Prop(U)| < |U|$.
-
-%Specifically, we take $U = I_i(Q) \cup \{j_m\}$.
-This is a subset of $J$ because $I_i$ and $J$ agree on their first $m-1$ terms and $Q \subseteq \cP_{m-1}$.
-Further, we have $j_m \not\in I_i(Q)$, so $|U| = |I_i(Q)| + 1 = |Q| +1$.
-On the other hand, since $\Prop(j_m) \subseteq Q$, we have
-%\[\Prop(U) = \Prop(I_i(Q)) \cup \Prop(j_m) = Q\]
-%by the construction of $Q$, and hence $|\Prop(U)| = |Q| < |U|$. Thus $J$ is a dependent set, and the Grassmann necklace $(I_1,\dots,I_n)$ constructed from $W$ does indeed define the positroid $M(W)$.
 \end{proof}

### 2019-08-09 GWLDCII.tex
responding to some of Susama's questions in sec 5

@@
       %\item Use Algorithm~\ref{alg:put GN on WLD} to obtain a bijection between the propagators and the $i-1$st Grassmann necklace element, $I_{i-1}$.
-(By convention set $I_{-1}=I_n$.)  Write $I_{i-1}(p)$ for the vertex associated to propagator $p$ under this bijection.
+(By convention set $I_{0}=I_n$.)  Write $I_{i-1}(p)$ for the vertex associated to propagator $p$ under this bijection.
       %\item Use Algorithm~\ref{alg:put GN on WLD} to obtain a bijection between the propagators and the $i$th Grassmann necklace element, $I_{i}$.
 Write $I_{i}(p)$ for the vertex associated to propagator $p$ under this bijection.
-      \item Let $S_i = \{p \in \cP \ | \ I_{i-1}(p) \neq I_i(p)\}$. (By convention, set \hlfix{$I_{0} = I_n$}{changed. correct?}.)
+      \item Let $S_i = \{p \in \cP \ | \ I_{i-1}(p) \neq I_i(p)\}$. (By convention, set $I_{0} = I_n$.)
 	  %\item Write $\Delta_{I_i}$ for the determinant of the $k \times k$ minor of $C(W)$ with columns indexed by $I_i$.
@@
 
-\hlfix{That is, each $r_i$ is the determinant of the minor determined by the propagators (rows) that contribute different values (columns) to the $i^{th}$ element of the Grassmann necklace than they did to the $i-1^{th}$.}{added.
-accurate?}
+That is, each $r_i$ is the determinant of the minor determined by the propagators (rows) that contribute different values (columns) to the $i^{th}$ element of the Grassmann necklace than they did to the $i-1^{th}$.
 
@@
 \begin{eg}
-Consider the Wilson loop diagram in Figure~\ref{fig R eg}. Assigning propagators $p$, $q$, $s$\todo{$s = r$ in pictures} to rows $1,2,3$ respectively, we obtain the matrix
+Consider the Wilson loop diagram in Figure~\ref{fig R eg}. Assigning propagators $p$, $q$, $r$ to rows $1,2,3$ respectively, we obtain the matrix
 \[
@@
 
-From $I_1$ to $I_2$, the propagators $p$ and $q$ change \hlfix{which vertex they are assigned to}{Can we change this language to which vertices they contribute?}.
+From $I_1$ to $I_2$, the propagators $p$ and $q$ change which vertices they contribute.
 That is $I_1(p) = 1$, $I_1(q)= 2$ while $I_2(p) = 2$, $I_2(q)= 5$.
@@
 \[
-\Delta_{I_2}=\det\begin{bmatrix} b & 0 & 0 \\ f & 0 & g \\ j & k & l \end{bmatrix} = kgb, \qquad r_2 = \det\begin{bmatrix} b & 0 & 0 \\ f & 0 & g \\ 1 & 1 & 1 \end{bmatrix} = gb.
-\] {\color{violet} shouldn't $r_2$ be a $2 \times 2$ matrix? i.e. $r_2 = \det\begin{bmatrix} b & 0 \\ f &  g \end{bmatrix} = gb.$}
-\hlfix{where the 1s in the third row of the second matrix correspond to the fact that $I_1(s) = I_2(s)$.}{This doesn't seem to match with what is said in the algorithm.}  Continuing likewise, we get $r_3 = c$, $r_4=1$ (since $I_4 = I_3$), $r_5 = lhd$, and $r_6 = i$.
-
-At $I_7$ the situation \hlfix{is more complicated}{It seems to be exactly what we expect from the alg?}: we have $S_7 = \{q,s\}$ with $I_7(S_7) = \{ 1,2\}$, $\Delta_{I_7} = d(ej-fi)$ and $r_7 = ej-fi$.
-
-Note that unlike the previous $r_i$, $r_7$ an irriducible quadratic factor.
-This corresponds to the fact that $q$ and $s$ share an edge {\em and} contribute both endpoints of that edge to $I_7$; see Proposition~\ref{prop alg gives rad} below.
+\Delta_{I_2}=\det\begin{bmatrix} b & 0 & 0 \\ f & 0 & g \\ j & k & l \end{bmatrix} = kgb, \qquad r_2 = \det\begin{bmatrix} b & 0 \\ f & g \end{bmatrix} = gb.
+\] 
+Continuing likewise, we get $r_3 = c$, $r_4=1$ (since $I_4 = I_3$), $r_5 = lhd$, and $r_6 = i$.
+
+At $I_7$ the situation we see for the first time an irreducible quadratic factor: we have $S_7 = \{q,s\}$ with $I_7(S_7) = \{ 1,2\}$, $\Delta_{I_7} = d(ej-fi)$ and $r_7 = ej-fi$.
+
+The irriducible quadratic factor corresponds to the fact that $q$ and $s$ share an edge {\em and} contribute both endpoints of that edge to $I_7$; see Proposition~\ref{prop alg gives rad} below.
 
@@
 Thus each $r_i$ is homogeneous.
-    \item Using the expression for the determinant as a sum over permutations from Corollary~\ref{lem basis as perm} we see that $\Delta_{I_i}$ is a sum over bijections between $I_i$ and $\mathcal{P}$.
+    \item Using the expression for the determinant as a sum over permutations along with Corollary~\ref{lem basis as perm} we see that $\Delta_{I_i}$ is a sum over bijections between $I_i$ and $\mathcal{P}$.
 The nonzero terms in this sum are precisely those bijections such that each propagator is associated to one of its supporting vertices in $I_i$, since only those locations in $C(W)$ are nonzero.
@@
 Expanding out $fg$ yields a signed sum of monomials.
-\hlfix{In each of these monomials, $f$ contributes those variables associated both to a propagator in $\mathcal{P}'$ and to a vertex in $J$, and $g$ contributes those variables associated both to a propagator not in $\mathcal{P}'$ and to a vertex not in $J$, and no other variables appear.
-}{Isn't this redundant with the previous paragraph?}
-
 Since there is no cancellation between terms, this means that the full expansion over permutations of $\Delta_{I_i}$ contains no other nonzero terms and hence no other variables.
@@
 Suppose for a contradiction that $f$ is a factor of $\Delta_{I_i}$ of degree $\geq 3$.
-Note that by removing the propagators which come \hlfix{before}{ordering?} those contributing to $f$ and \hlfix{changing $i$ to be the first vertex}{does this generalize to other $i$?} which contributes to $f$, we obtain a \hlfix{different admissible diagram}{Is this just the diagram gotten by removing certain props?} for which $f$ still divides $\Delta_{I_i}$ but also $i\in I_i$ and
+Note that by removing the propagators which come before those contributing to $f$ in the order given by the construction of $I_i$ and \hlfix{changing $i$ to be the first vertex}{does this generalize to other $i$?} which contributes to $f$, we obtain a \hlfix{different admissible diagram}{Is this just the diagram gotten by removing certain props?} for which $f$ still divides $\Delta_{I_i}$ but also $i\in I_i$ and
 $i$ contributes to $f$.
-Showing that this different admissible diagram gives a contradiction is sufficient, and so we may assume that $i\in I_i$ and $i$ contributes to $f$.
-Finally, we can suppose that $W$ is minimal in number of propagators with the above occuring.
+\note{The point of all the stuff you were objecting to is just to spell out ``WLOG we may assume $i\in I_i$ and $i$ contributes to $f$''.
+How do you want that said?} Showing that this different admissible diagram gives a contradiction is sufficient, and so we may assume that $i\in I_i$ and $i$ contributes to $f$.
+Finally, we can suppose that $W$ is minimal in number of propagators with an irreducible factor of degree $\geq 3$.
 
@@
 
-If neither $m$ nor $m+1$ appear in $I_i$ then by Corollary~\ref{no coloops} $V(p) \cap I_i = \{i\}$, and so the row of $p$ in the matrix of $\Delta_{I_i}$ has only one nonzero entry; hence $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$, which \hlfix{is a contradiction}{Why?
-because $i$ contributes to $f$?}.
+If neither $m$ nor $m+1$ appear in $I_i$ then by Corollary~\ref{no coloops} $V(p) \cap I_i = \{i\}$, and so the row of $p$ in the matrix of $\Delta_{I_i}$ has only one nonzero entry; hence $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$, which is a contradiction to the fact that $i$ contributes to $f$.
 So we must have at least one of $m$ and $m+1$ in $I_i$.
@@
 Therefore $\Delta_{I_i} = \det A \det C$, and both factors are nontrivial since at least one of $m$ and $m+1$ appear in $I_i$.
-If we remove the propagator outside of $p$ that contributes $m$ or $m+1$, we get a smaller diagram for which $\Delta_{I_i} = \det A$ {\color{violet}why not $\det A \det C'$ with $C'$a minor of $C$?}.
-This contradicts the minimality of our choices unless $\det A$ is quadratic, which in turn contradicts our assumption that $i$ and $p$ contribute to an irreducible factor $f$ of degree at least 3.
+Since $p\in \cP_{in}(p)$ we have $f|\det A$ and if we remove the propagator outside of $p$ that contributes $m$ or $m+1$, we get a diagram with fewer propagators for which $\det A | \Delta_{I_i}$.
+This contradicts the minimality of our choices.
 
@@
 If no other propagators are supported on $i$ then the column of $C(W)$ corresponding to vertex $i$ has only one nonzero entry in it, and so $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$; as above, this is a contradiction.
-Thus we can take $q$ to be the propagator such that $I_i(q)=i+1$.
+Thus there is at least one other propagator on edge $(i,i+1)$ since since $I_i(p)=i$, one of these other propagators contributes $i+1$ in $I_i$, sob we can take $q$ to be the propagator such that $I_i(q)=i+1$.
 {\color{violet} How do we know this exists?
-Why can't we solve this by having $r$ supported on the $i-1^{th}$ edge?} We know that $q$ has one end on the edge $(i, i+1)$ and is adjacent to $p$ on that edge in the counterclockwise direction (see Figure \ref{fig no big factors}).
+Why can't we solve this by having $r$ supported on the $i-1^{th}$ edge?}\note{I tried to clarify what $q$ is and why it exists, but I don't know what $r$ is in your question.} We know that $q$ has one end on the edge $(i, i+1)$ and is adjacent to $p$ on that edge in the counterclockwise direction (see Figure \ref{fig no big factors}).
 Write $(i, i+1, j, j+1)$ for the support of $q$.
@@
 Similarly to Case 1, let \st{$S$ be the set of propagators inside $q$ along with $p$ and $q$ themselves.}{\color{violet}$S = \cP_{in}(q)$ in the $<_i$ order.
-Note that $p \in S$.}\hlfix{Then all propagators in $S$ are mapped by $I_i(\cdot)$ to vertices strictly before $j$ and no other propagators are supported on vertices strictly before $j$.}{???}  Thus the matrix giving $\Delta_{I_i}$ has the form
+Note that $p \in S$.}\note{No, $S=\cP_{in}(q)\cup \{p\}$ in the $<_i$ order because $q$ is not inside $p$ in that order}\hlfix{Then all propagators in $S$ are mapped by $I_i(\cdot)$ to vertices strictly before $j$ and no other propagators are supported on vertices strictly before $j$.}{???} \note{This is the usual argument...} Thus the matrix giving $\Delta_{I_i}$ has the form
 \[
@@
 terms in determinant come from bijections.
-Why should all bijections appear in det?} with the minor coming from $\cP-\{p, q\}$ and $I_i - \{a,b\}$.
+Why should all bijections appear in det?}\note{All terms appear by the permuation form of the determinant -- am I mising what you're asking?} with the minor coming from $\cP-\{p, q\}$ and $I_i - \{a,b\}$.
 Since there is no cancellation of terms in the expansion of $\Delta_{I_i}$, if any other terms appear then they will cause a factor which is not in the form described in the previous part.
@@
 
-{\color{violet} Got rid of need for scalar multiples by talking about radicals.}
-
 \begin{proof}
@@
 \todo{I'm pretty sure that there isn't a sign issue here.
-But do we have a proof?}
+But do we have a proof?}\note{The previous sentence is the proof -- again I think I'm missing something in your question}
 \end{proof}

### 2019-08-09 GNproof.tex
minor edits for readability and notation

@@
 \end{itemize}
-The first point follows immediately: the algorithm is  so $I_i$ is a basis for $M(W)$ by Corollary~\ref{lem basis as perm}.
+The first point follows immediately: the algorithm assigns each propagator to a vertex in the support of that propagator, so $I_i$ is a basis for $M(W)$ by Corollary~\ref{lem basis as perm}.
 
@@
 Since $\cP$ is finite, the sequence therefore stabilizes in finitely many steps when $Q_{l+1} = Q_l$.
-Let $Q$ be this set of propagators.
+Let $Q = \cup_{l \geq 0} Q_l$ be this set of propagators.
 
-Our remaining goal is to show that $Q \subseteq \mathcal{P}_{m-1}$.
-This will imply the theorem as follows.
-Once the goal is proven we have $I_i(Q)\subseteq J$.
-Then $I_i(Q) \cup {j_m}$ is a dependent set contained in $J$ because it only supports the propagators in $Q$ but has $|Q|+1$ vertices.
+We will show that $Q \subseteq \mathcal{P}_{m-1}$, which will imply the theorem as follows: if $Q \subseteq \cP_{m-1}$ then we have $I_i(Q)\subseteq J$, and hence $I_i(Q) \cup \{j_m\} \subseteq J$ as well.
+Since $I_i(Q) \cup \{j_m\}$ only supports the propagators in $Q$ but has $|Q|+1$ vertices, it is a dependent set.
 Thus $J$ is a dependent set, and the Grassmann necklace $(I_1,\dots,I_n)$ constructed from $W$ does indeed define the positroid $M(W)$.
@@
 We now proceed to prove $Q\subseteq \mathcal{P}_{m-1}$ by inductively proving $Q_l \subseteq \mathcal{P}_{m-1}$ for all $l \geq 0$.
-If $Q_0 = \Prop(j_m) = \emptyset$, then $Q = Q_0$, and $I_i(Q) \cup {j_m}= j_m$, a single vertex supporting no propagators, and thus a dependent set.
+If $Q_0 = \Prop(j_m) = \emptyset$ then $Q = \emptyset$, and $I_i(Q) \cup \{j_m\}= \{j_m\}$ is a single vertex supporting no propagators, and thus a dependent set.
 Otherwise, $Q_0 \subseteq \cP_{m-1}$ follows immediately from the first observation above that $\Prop(j_m) \subseteq \cP_{m-1}$
@@
 Otherwise, let $q \in Q_{l} \setminus Q_{l-1}$.
-By construction there is some propagator $p_r \in Q_{l-1}\setminus Q_{l-2}$ such that $p_r$ and $q$ are both supported on $I_i(p_r) = a_r$.
+By construction there is some propagator $p_r \in Q_{l-1}$ such that $p_r$ and $q$ are both supported on $I_i(p_r) = a_r$.
 If $q$ is clockwise of $p_r$ on vertex $a_r$ then we immediately have $q \in \cP_{m-1}$ as observed above.
@@
 If the other end of $p_r$ (i.e.
-the end not supported on $a_r$) lies on an edge between $a_r$ and $j_m$ then since $q$ is inside $p_r$ with respect to $<_{a_r-1}$ we must have $V(q) \subseteq [a_r-1,j_m]$ and hence $q \in \cP_{m-1}$ by Lemma [no fourth vertex].
+the end not supported on $a_r$) lies on an edge between $a_r$ and $j_m$ then since $q$ is inside $p_r$ with respect to $<_{a_r-1}$ we must have $V(q) \subseteq [a_r-1,j_m]$, and hence $q \in \cP_{m-1}$ by Lemma [no fourth vertex].
 In particular, if $l=1$ then $p_r \in Q_{0} = \Prop(j_m)$ and we must be in this case.

### 2019-08-09 GWLDCI.tex
made changes to GNproof according to Karen's comments; removed non-crossing partition reference
replace "not independent" with "is dependent"

@@
 
-It is worth remarking that these maximal decompositions correspond to non-crossing partitions of the Wilson loop diagram, in the sense discussed in \cite{positroids13}.
+%It is worth remarking that these maximal decompositions correspond to non-crossing partitions of the Wilson loop diagram, in the sense discussed in \cite{positroids13}.
 
@@
 Let $W = (\cP, [n])$ be an admissible Wilson loop diagram, and $P \subseteq \cP$. Then: \begin{enumerate}
-\item If $(P,V(P))$ is an exact subdiagram of $W$, then $F(P^c)$ is not an independent flat in $W$.
+\item If $(P,V(P))$ is an exact subdiagram of $W$, then $F(P^c)$ is a dependent flat in $W$.
 \item If $(P,V(P))$ is a maximal exact subdiagram of $W$, then $F(P^c)$ is a cyclic flat in $W$.
@@
 
-We know from Lemma~\ref{lem facts about WLD matroids} that $F(P^c)$ is always a flat, so for part (1) we only need to show that $F(P^c)$ is not independent.
+We know from Lemma~\ref{lem facts about WLD matroids} that $F(P^c)$ is always a flat, so for part (1) we only need to show that $F(P^c)$ is dependent.
 
@@
 $F(P^c)$ is a cyclic flat.
-Note that $C$ must be non-empty since $F(P^c)$ is non-empty and not independent (by part (1)).
+Note that $C$ must be non-empty since $F(P^c)$ is non-empty and dependent (by part (1)).
 

### 2019-08-09 GNproof.tex
move the degerate case out of the base case

@@
 
-%If $\Prop(j_m) = \emptyset$ then $J$ is automatically dependent since the corresponding column of $C(W)$ contains only zeros, so suppose henceforth that $\Prop(j_m) \neq \emptyset$.
-In particular, this implies that $m>1$, since if $m=1$ we would have $\Prop(j_1) \subseteq \cP_0 = \emptyset$.
+If $\Prop(j_m) = \emptyset$ then $J$ is automatically dependent since the corresponding column of $C(W)$ contains only zeros, so suppose henceforth that $\Prop(j_m) \neq \emptyset$.
+%In particular, this implies that $m>1$, since if $m=1$ we would have $\Prop(j_1) \subseteq \cP_0 = \emptyset$.
 
@@
 We now proceed to prove $Q\subseteq \mathcal{P}_{m-1}$ by inductively proving $Q_l \subseteq \mathcal{P}_{m-1}$ for all $l \geq 0$.
-If $Q_0 = \Prop(j_m) = \emptyset$ then $Q = \emptyset$, and $I_i(Q) \cup \{j_m\}= \{j_m\}$ is a single vertex supporting no propagators, and thus a dependent set.
-Otherwise, $Q_0 \subseteq \cP_{m-1}$ follows immediately from the first observation above that $\Prop(j_m) \subseteq \cP_{m-1}$
+%If $Q_0 = \Prop(j_m) = \emptyset$ then $Q = \emptyset$, and $I_i(Q) \cup \{j_m\}= \{j_m\}$ is a single vertex supporting no propagators, and thus a dependent set. Otherwise,
+For the base case $Q_0 \subseteq \cP_{m-1}$ follows immediately from the first observation above that $\Prop(j_m) \subseteq \cP_{m-1}$
 

### 2019-08-09 GWLDCII.tex
things in section 5 changed as we were talking over zoom

@@
 {\em Proof of claim}: By the structure of determinants we know that $\Delta_{I_i} = fg$, where $g$ involves only variables associated to propagators not in $\mathcal{P}'$ and associated to vertices not in $J$.
-\todo{Is the heart of this proof due to the fact that there are no cancelations?
-It feels tautological to me, but I'm clearly not following}
 
@@
 Suppose for a contradiction that $f$ is a factor of $\Delta_{I_i}$ of degree $\geq 3$.
-Note that by removing the propagators which come before those contributing to $f$ in the order given by the construction of $I_i$ and \hlfix{changing $i$ to be the first vertex}{does this generalize to other $i$?} which contributes to $f$, we obtain a \hlfix{different admissible diagram}{Is this just the diagram gotten by removing certain props?} for which $f$ still divides $\Delta_{I_i}$ but also $i\in I_i$ and
-$i$ contributes to $f$.
-\note{The point of all the stuff you were objecting to is just to spell out ``WLOG we may assume $i\in I_i$ and $i$ contributes to $f$''.
-How do you want that said?} Showing that this different admissible diagram gives a contradiction is sufficient, and so we may assume that $i\in I_i$ and $i$ contributes to $f$.
+Without loss of generality\footnote{This is without loss of generality as by removing the propagators which come before those contributing to $f$ in the order given by the construction of $I_i$ and changing $i$ to be the first vertex which contributes to $f$, we obtain an admissible diagram for which $f$ still divides $\Delta_{I_i}$ but also $i\in I_i$ and
+$i$ contributes to $f$, and this diagram can be used in place of $W$.} we may assume $i\in I_i$ and $i$ contributes to $f$.
 Finally, we can suppose that $W$ is minimal in number of propagators with an irreducible factor of degree $\geq 3$.
@@
 If no other propagators are supported on $i$ then the column of $C(W)$ corresponding to vertex $i$ has only one nonzero entry in it, and so $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$; as above, this is a contradiction.
-Thus there is at least one other propagator on edge $(i,i+1)$ since since $I_i(p)=i$, one of these other propagators contributes $i+1$ in $I_i$, sob we can take $q$ to be the propagator such that $I_i(q)=i+1$.
-{\color{violet} How do we know this exists?
-Why can't we solve this by having $r$ supported on the $i-1^{th}$ edge?}\note{I tried to clarify what $q$ is and why it exists, but I don't know what $r$ is in your question.} We know that $q$ has one end on the edge $(i, i+1)$ and is adjacent to $p$ on that edge in the counterclockwise direction (see Figure \ref{fig no big factors}).
+Since $I_i(p) = i$ there can be no propagator supported on $i$ with an end on the edge $(i-1, i)$.
+Thus to have another propagator supported on $i$ there is at least one other propagator on edge $(i,i+1)$.
+Further since since $I_i(p)=i$, one of these other propagators contributes $i+1$ in $I_i$, so we can take $q$ to be the propagator such that $I_i(q)=i+1$.
+We know that $q$ has one end on the edge $(i, i+1)$ and is adjacent to $p$ on that edge in the counterclockwise direction (see Figure \ref{fig no big factors}).
 Write $(i, i+1, j, j+1)$ for the support of $q$.
@@
 
-Similarly to Case 1, let \st{$S$ be the set of propagators inside $q$ along with $p$ and $q$ themselves.}{\color{violet}$S = \cP_{in}(q)$ in the $<_i$ order.
-Note that $p \in S$.}\note{No, $S=\cP_{in}(q)\cup \{p\}$ in the $<_i$ order because $q$ is not inside $p$ in that order}\hlfix{Then all propagators in $S$ are mapped by $I_i(\cdot)$ to vertices strictly before $j$ and no other propagators are supported on vertices strictly before $j$.}{???} \note{This is the usual argument...} Thus the matrix giving $\Delta_{I_i}$ has the form
+Similarly to Case 1, let $S = \cP_{in}(q) \cup \{p\}$ in the $<_i$ order.
+Then all propagators in $S$ are mapped by $I_i(\cdot)$ to vertices strictly before $j$ and no other propagators are supported on vertices strictly before $j$.
+Thus the matrix giving $\Delta_{I_i}$ has the form
 \[
@@
 For any fixed bijection $\sigma$ from $\cP-\{p,q\}$ to $I_i -\{a,b\}$ for which each propagator is supported on its image under the bijection, we can extend $\sigma$ to a bijection of all propagators with $I_i$ in two ways: either $p\mapsto a$ and $q\mapsto b$ or $p\mapsto b$ and $q\mapsto a$.
-The sum of the contributions of all these bijections to $\Delta_{I_i}$ is therefore the product of \hlfix{$x_{p,a}x_{q,b}-x_{p,b}x_{q,a}$}{why?
-terms in determinant come from bijections.
-Why should all bijections appear in det?}\note{All terms appear by the permuation form of the determinant -- am I mising what you're asking?} with the minor coming from $\cP-\{p, q\}$ and $I_i - \{a,b\}$.
+The sum of the contributions of all these bijections to $\Delta_{I_i}$ is therefore the product of $x_{p,a}x_{q,b}-x_{p,b}x_{q,a}$ \note{Could this use a ref back to where we discuss this kind of arugment in more detail.} with the minor coming from $\cP-\{p, q\}$ and $I_i - \{a,b\}$.
 Since there is no cancellation of terms in the expansion of $\Delta_{I_i}$, if any other terms appear then they will cause a factor which is not in the form described in the previous part.
@@
 Finally then we need to check the scalar.
-By Definition~\ref{def R(W)} each linear factor appears with coefficient $1$ and each $2\times 2$ deteriminant factor appears with the same sign as the determinant of the corresponding minor in $C(W)$.
+By Definition~\ref{def R(W)} each linear factor appears with coefficient $1$ and each $2\times 2$ determinant factor appears with the same sign as the determinant of the corresponding minor in $C(W)$.
 Therefore $R=R(W)$.
-\todo{I'm pretty sure that there isn't a sign issue here.
-But do we have a proof?}\note{The previous sentence is the proof -- again I think I'm missing something in your question}
 \end{proof}

### 2019-08-09 GWLDCII.tex
pictures and GNproof added to paper 2

@@
 %*****************
-%%% WLD drawing and 2,6 shortcuts
+%%% WLD drawing
 
@@
 
-% vertices, radius
+% to draw a (full) WLD; \drawWLD{8}{2} is a circle of radius 2 with 8 marked points
 \newcommand{\drawWLD}[2]{
@@
 
+% as above, but draws the outer edge of the polygon partition instead
 \newcommand{\drawpolypart}[2]{
@@
 
-% r, bumpr, s, bumps: r, s are start/end vertices, bumpr and bumps are how many steps to bump the start/end for multiple props on one edge
+% to draw a propagator in a WLD: \drawprop{a}{b}{c}{d} draws a prop from edge a (offset by b from the centre of the edge)
+% to edge c (offset by d from the centre)
 \newcommand{\drawprop}[4]{
@@
 \pgfmathsetmacro{\perturbe}{\angle/\n}
-
 \begin{scope}
@@
 
+% as above but the 5th argument labels the prop (must include formatting, $ signs, etc)
 \newcommand{\drawlabeledprop}[5]{
@@
 
+% \drawchord{a}{b} draws a straight line from vertex a to vertex b in the polygon partition
 \newcommand{\drawchord}[2]{
@@
 
-\newcommand{\boundaryprop}[4]{
-\pgfmathsetmacro{\r}{#1}
-\pgfmathsetmacro{\bumpr}{#2}
-\pgfmathsetmacro{\s}{#3}
-\pgfmathsetmacro{\perturbe}{\angle/\n}
-
-\begin{scope}
-\clip (\angle*\r:\radius) -- (\angle + \angle*\r:\radius) -- (\angle*\s - \angle:\radius) -- (\angle*\s:\radius) -- (\angle + \angle*\s:\radius) -- (\angle*\r:\radius);
-\draw[#4] (\angle*\r + \angle/2 + \bumpr*\perturbe:\radius) -- (\angle*\s:\radius);
-\end{scope}
-
-}
-
 \newcommand{\drawnumbers}{
@@
 
-\newcommand{\boundA}[3]{
-	\pgfmathsetmacro{\r}{#1}
-	\pgfmathsetmacro{\bumpr}{#2}
-	\pgfmathsetmacro{\destination}{#3}
-	\pgfmathsetmacro{\perturbe}{\angle/\n}
-	\path [name path=polyedge1] (\angle*\r:\radius) -- (\angle*\r + \angle:\radius);
-	\path [name path=radius1] (0:0) -- (\angle*\r + \angle/2 + \bumpr*\perturbe:\radius);
-	\draw[->,
-	name intersections={of=polyedge1 and radius1,by=p},
-	shorten >=\radius*0.1 cm] (p) ++(\angle*\r + \angle/2 + \bumpr*\perturbe:\radius*0.15) -- (\angle*\destination: \radius*1.15);
-
-}
-
-\newcommand{\boundB}[3]{
-	\pgfmathsetmacro{\rangle}{#1*\angle + \angle/2 + #2*\angle/\n}
-	\pgfmathsetmacro{\sangle}{#1*\angle + \angle/2 + #3*\angle/\n}
-
-	\draw[->,shorten <=\radius*0.02cm,shorten >=\radius*0.05cm] (\rangle:\radius*1.05) -- (\sangle:\radius*1.05);
-
-}
-
-\newcommand{\makediag}[8]{
-	\begin{tikzpicture}[rotate=60,baseline=(current bounding box.east)]
-	\begin{scope}
-	\drawWLD{6}{0.8}
-	%\drawnumbers
-	\drawprop{#1}{#2}{#3}{#4}
-	\drawprop{#5}{#6}{#7}{#8}
-	\end{scope}
-	\end{tikzpicture}
-}
-
 %%%%%%%
@@
 
-%\drawWLDfragment[number of nodes]{radius}{fraction of circle to be displayed}
+%\drawWLDfragment[number of nodes, default = 10]{radius}{fraction of circle to be displayed}
+% unlike \drawWLD above, nodes are not marked by default, use \newnode below 
 \newcommand{\drawWLDfragment}[3][10]{
@@
 
+% puts numbers on the partialWLD; only really useful for debugging
 \newcommand{\drawnumberspartial}{
@@
 
+% \newnode[location]{b}{c} puts a dot on the node at position b, with label c. location = left by default
 \newcommand{\newnode}[3][left]{
@@
 % messier but more flexible: use when you want more control over label placement
+
 \newcommand{\newbetternode}[3][{label distance=-1mm]left}]{
@@
 
-% \newprop[label position]{start node}{end node}{label}
+% \newprop[label position]{start node}{end node}{label}; for \partialWLD only
 \newcommand{\newprop}[4][midway,below]{
@@
 
+% as above but with a bend in it; \newpropbend{startnode}{endnode}{bend in degrees}
+% note that the propagator extends past the edge of the diagram: always use this in a scope with \clipcenterarc (above)
 \newcommand{\newpropbend}[3]{
@@
 \end{itemize}
+
+\begin{figure}
+\[
+\begin{tikzpicture}[baseline=(current bounding box.east),rotate=-20]
+	\begin{scope}
+	\drawWLDfragment[10]{3}{0.4} 
+	%\drawnumberspartial % use this to debug
+	\centerarc[linehighlight](0,0)(\zero + 1.5*\step:\zero + 2.35*\step:\radius)
+	\newnode{1}{}
+	\newnode{3}{}
+	\newnode{4}{}
+	\newnode{5}{}
+	\newnode[below]{9}{i_1}
+	\newnode{10}{}
+	\newprop[midway,above]{1.4}{9.5}{\footnotesize $q_1$}
+	\begin{scope}
+		\clipcenterarc(0,0)(\startpoint:\endpoint:\radius)
+		\newpropbend{2.3}{4.7}{60}
+		\node at (\zero + 3.5*\step:\radius*0.78) {\footnotesize $p_1$};
+	\end{scope}
+\node[align = center] at (\zero +1.7*\step:\radius*1.4) {\footnotesize \em 0, 1, or 2 \\ \footnotesize \em vertices in \\ \footnotesize \em this region};
+\node at (\zero + 10*\step:\radius*0.3) {$\cP_{in}(q_1)$};
+\end{scope}
+\end{tikzpicture}
+\]
+\caption{The base case of the induction in Lemma~\ref{lem sian}.}\label{fig base case lem sian} \end{figure}
+
 We can then choose the orientation of $q_r$ so that the previous $p_i$ and $q_i$ are all on the outside of $q_r$, and restrict our attention to the subdiagram $(\cP_{in}(q_r),[n])$.
@@
 Therefore there must be a propagator of length $\geq 4$ with one end on edge $j_1$ or on edge $j_1-1$ or on edge $j_1-2$.
-Let $q_1 = (i_1, k_1)$ be this propagator, oriented such that $p_1 \in \cP_{out}(q_1,<_{i_1})$.
+Let $q_1 = (i_1, k_1)$ be this propagator, oriented such that $p_1 \in \cP_{out}(q_1,<_{i_1})$; see Figure~\ref{fig base case lem sian}.
 This completes the base case.
 
-\bas \begin{tikzpicture}[rotate=15,baseline=(current bounding box.east)]
-	\begin{scope}
-	\drawWLD{15}{2}
-	%\drawnumbers
-	%\drawprop{1}{0}{4}{0}
-	\begin{scope}
-	\clip (0,0) circle (\radius cm);
-	\draw[propagator] (\angle*5.3:\radius*1.2cm) to [bend left=50] (\angle*7.7:\radius*1.2cm);
-	\node at (\angle*6.5:\radius*0.6cm) {\footnotesize $p_1$};
-	\end{scope}
-    \drawlabeledprop{3}{0}{10}{0}{\footnotesize \qquad $q_1$};
-    \node at (\angle*5:\radius*1.15cm) {\footnotesize $j_1$};
-     \node at (\angle*10:\radius*1.15cm) {\footnotesize $i_1$};
-     \node at (10:\radius*0.5) {\small $\cP_{in}(q_1)$};
-	\node[rotate = 45] at (\angle * 5.2:\radius) {\Large $($};
-\node[rotate = -15] at (\angle * 2.7:\radius) {\Large $)$};
-\node[rotate = 20] at (\angle* 4:\radius*1.2) {\em \scriptsize 1, 2 or 3 vertices};
-		\end{scope}
-	\end{tikzpicture}\eas
-
- %\node[rotate=-15] at (\zero + 2.7*\step:\radius) {\Large $($};
- %    \node[rotate=15] at (\zero + 6.3*\step:\radius) {\Large $)$};
-   %  \node at (\zero + 4.5*\step:\radius*0.85) {\em \scriptsize up to 4 vertices here};
-
-\sanote{played with Sian's code. May need to tweak this picture}
 Now suppose $q_{r} = (i_r, k_r)$ exists by the induction hypothesis and is oriented $(q_r, <_{i_r})$ so that the previous $p_i$ and $q_i$ are on the outside.
@@
 we assume that there are no other propagators with $p_{r+1}$ on one side and $q_r$ on the other.
+
+\begin{figure}
+\[
+\begin{tikzpicture}[baseline=(current bounding box.east)]
+	\begin{scope}
+	\drawWLDfragment[15]{4}{0.4} 
+	%\drawnumberspartial % use this to debug
+	\newnode[left]{1}{i_r}
+	\newnode[left]{2}{i_r+1}
+	\newnode{5}{}
+	\newnode{6}{}
+	\newnode{7}{}
+	\newnode{8}{}
+	\newnode[right]{14}{k_r}
+	\newnode[right]{15}{k_r+1}
+	\newprop[midway,above]{1.5}{14.5}{\footnotesize $q_r$}
+	\draw[smallpropagator,gray] (\zero+2.5*\step:\radius) -- (\zero + 12.5*\step:\radius) node[midway,above,gray] {\footnotesize $q_{r}'$};
+	\begin{scope}
+		\clipcenterarc(0,0)(\startpoint:\endpoint:\radius)
+		\newpropbend{5.2}{7.7}{80}
+		\node at (\zero + 6.5*\step:\radius*0.85) {\footnotesize $p_{r+1}$};
+	\end{scope}
+\end{scope}
+\end{tikzpicture}
+\]
+\caption{We can replace $q_r$ with $q'_r$ as long as the conditions of the induction hypothesis remain satisfied.}
+\label{fig smallest q in lem sian}
+\end{figure}
 
@@
 \begin{figure}
-\includegraphics[scale=0.2]{locally_identical.jpg}
+\[
+\begin{tikzpicture}[baseline=(current bounding box.east)]
+	\begin{scope}
+	\drawWLDfragment[12]{3}{0.4} 
+	%\drawnumberspartial % use this to debug
+	\newnode[left]{1}{i}
+	\newnode[below]{4}{j}
+	\newnode{5}{}
+	\newnode{6}{}
+	\newnode{7}{}
+	\newnode{8}{}
+	\newnode{9}{}
+	\newnode{11}{}
+	\newnode[right]{12}{l+1}
+	\begin{scope}
+		\clipcenterarc(0,0)(\startpoint-10:\endpoint+10:\radius)
+		\newpropbend{6.3}{8.6}{80}
+		\node at (\zero + 7.5*\step:\radius*0.8) {\footnotesize $r$};
+		\newprop[midway,left]{5.5}{-4}{}
+		\node at (\zero + 3*\step:\radius*0.5) {\footnotesize $p$};
+		\newprop[midway]{11.5}{-4}{}
+		\node at (\zero + 12.2*\step:\radius*0.7) {\footnotesize $q$};
+	\end{scope}
+\end{scope}
+\end{tikzpicture}
+\qquad \qquad
+\begin{tikzpicture}[baseline=(current bounding box.east)]
+	\begin{scope}
+	\drawWLDfragment[12]{3}{0.4} 
+	%\drawnumberspartial % use this to debug
+	\newnode[left]{2}{m}
+	\newnode[below]{4}{j}
+	\newnode{5}{}
+	\newnode{6}{}
+	\newnode{7}{}
+	\newnode{8}{}
+	\newnode{9}{}
+	\newnode{11}{}
+	\newnode[right]{12}{l+1}
+	\begin{scope}
+		\clipcenterarc(0,0)(\startpoint-10:\endpoint+10:\radius)
+		\newpropbend{6.3}{8.6}{80}
+		\node at (\zero + 7.5*\step:\radius*0.8) {\footnotesize $r$};
+		\newprop[midway,left]{5.5}{19}{}
+		\node at (\zero + 5.5*\step:\radius*0.5) {\footnotesize $s$};
+		\newprop[midway]{11.5}{21}{}
+		\node at (\zero + 11.8*\step:\radius*0.8) {\footnotesize $t$};
+	\end{scope}
+\end{scope}
+\end{tikzpicture}
+\]
 \caption{$W'$ and $V'$ are locally the same between $j$ and $l+1$, so we will have $I_i^W\cap [j,l] = I_m^V\cap[j,l]$ even though $p \neq s$ and $q \neq t$.}\label{fig:locally identical}
@@
 \begin{figure}
-\includegraphics[width=15cm]{4th_vertex}
+\[
+\begin{tikzpicture}[baseline=(current bounding box.east)]
+	\begin{scope}
+	\drawWLDfragment[20]{2}{1}
+	%\drawnumbers % use this to debug
+	\newnode[left]{4}{I_i(p) = i-1}
+	\newnode[left]{5}{i}
+	\newnode[left]{7}{c}
+	\newnode[left]{8}{}
+	\newnode[right]{15}{b}
+	\newnode[right]{16}{b+1}
+	\newprop[midway,above]{4.7}{15.7}{\scriptsize $p$}
+	\newprop[midway,below]{7.5}{15.3}{\scriptsize $q$}
+      \draw[smallpropagator,light-gray] (\zero +\step *4.3:\radius*1) -- (90:\radius*0.5); 
+	\node at (270:\radius*1.5) {\em Case 1};
+	% \begin{scope}
+	% \clip (\zero + 5*\step:\radius*1.1) rectangle (90:\radius*0.8);
+	% \draw[smallpropagator,color=gray] (\zero+4.5*\step:\radius) -- (\zero + 19*\step:\radius);
+	% \end{scope}
+		\end{scope}
+	\end{tikzpicture}
+\qquad \qquad 
+	\begin{tikzpicture}[baseline=(current bounding box.east)]
+	\begin{scope}
+	\drawWLDfragment[20]{2}{1}
+	%\drawnumbers % use this to debug
+	\newnode[left]{4}{a}
+	\newnode[left]{5}{}
+	\newnode[left]{7}{}
+	\newnode[left]{8}{}
+	\newnode[right]{15}{b}
+	\newnode[right]{16}{b+1 = I_i(p)}
+	\newnode[below]{11}{d}
+	\newnode[below]{12}{}
+	\newnode[above]{2}{i}
+	\newprop[midway,above]{4.5}{15.7}{\scriptsize $p$}
+		\node at (270:\radius*1.5) {\em Case 2};
+	\begin{scope}
+	\clip (0,0) circle (\radius);
+	%q
+	\draw[smallpropagator] (\zero+11.5*\step:\radius*1.2) to [bend left = 45] (\zero + 15.5*\step:\radius*1.2); 
+	\node at (\zero + 13.5*\step:\radius*0.55) {\scriptsize $q$};
+	%r
+	\draw[smallpropagator] (\zero+7.5*\step:\radius*1.2) to [bend left = 45] (\zero + 11.4*\step:\radius*1.2);
+	\node at (\zero + 9.5*\step:\radius*0.55) {\scriptsize $r$};
+
+	\end{scope}
+		\end{scope}
+	\end{tikzpicture}
+\] 
 \caption{The two types of configuration in which a propagator could (in theory) contribute its $<_i$-maximal support vertex to $I_i$.}
@@
 \end{lem}
-\note{Right at the end when we put the tikz figures in, someone needs to go through this proof and replace ``leftmost two cases'' with ``Case 1 and 2'' etc, because the tikz picture is arranged differently}
+\note{This proof needs to be updated to refer to the new figure (e.g. case 1 and 2 instead of ``leftmost two cases''); also check that all the vertices are labeled correctly}
 
@@
 \begin{figure}
-    \includegraphics[scale=0.8]{3cases}
+\begin{tabular}{lll}
+% case 1
+\begin{tikzpicture}[baseline=(current bounding box.east)]
+	\begin{scope}
+	\drawWLDfragment[8]{3}{0.3} % draws the arc and sets up the parameters
+	%\drawnumbers % use this to debug
+	% next two lines draw the highlighted regions
+	\centerarc[linehighlight](0,0)(\zero + 1.85*\step:\zero + 4.4*\step:\radius)
+	\centerarc[linehighlight](0,0)(\zero + 6.75*\step:\zero + 7.4*\step:\radius)
+	% labels explaining the highlighted regions
+	\node[align = center] at (\zero + 2.7*\step:\radius*1.3) {\em \footnotesize 1 or 2 vertices \\[3pt] \em \footnotesize in this region};
+	\node[align = center] at (\zero + 7.5*\step:\radius*1.4) {\em \footnotesize 0 or 1 vertices \\[3pt]\em \footnotesize in this region};
+	\begin{scope} % this scope draws the propagators and their labels
+		\clipcenterarc(0,0)(\startpoint-20:\endpoint+20:\radius)
+		%q
+		\draw[smallpropagator] (\zero+1.65*\step:\radius*1.1) to [bend left = 40] (\zero + 7.4*\step:\radius*1.1); 
+		%p
+		\draw[smallpropagator] (\zero+4.3*\step:\radius*1.1) to [bend left = 55] (\zero + 6.8*\step:\radius*1.1); 
+		\draw[smallpropagator,light-gray] (\zero+1.5*\step:\radius*1.1) -- (180:\radius*0.5); 
+		\draw[smallpropagator,light-gray] (\zero+1.6*\step:\radius*1.1) -- (180:\radius*0.25);
+		\draw[smallpropagator,light-gray] (\zero+7.55*\step:\radius*1.1) -- (0:\radius*0.5); 
+		%\draw[smallpropagator,light-gray] (\zero+7.5*\step:\radius*1.1) -- (0:\radius*0.25);  
+		\node at (\zero + 4.5*\step:\radius*0.5){\footnotesize $q$};
+		\node at (\zero + 5.5*\step:\radius*0.8){\footnotesize $p$};
+	\end{scope}
+	% draw the nodes
+	\newnode[left]{1}{i}
+	\newnode[right]{8}{j+1}
+	\newnode[below]{5}{}
+	\newnode[below]{6}{}
+% case label
+\node at (270:\radius*0.2) {\em Case 1};
+\end{scope}
+\end{tikzpicture}
+%
+%
+%
+& \qquad \qquad &
+%
+%
+%
+% case 2
+\begin{tikzpicture}[baseline=(current bounding box.east)]
+\begin{scope}
+	\drawWLDfragment[8]{3}{0.3} % draw arc
+	%\drawnumbers % use this to debug
+	% highlighted regions
+	\centerarc[linehighlight](0,0)(\zero + 1.85*\step:\zero + 2.4*\step:\radius)
+	\centerarc[linehighlight](0,0)(\zero + 4.75*\step:\zero + 7.4*\step:\radius)
+	%labels for highlighted regions
+	\node[align = center] at (\zero + 6.6*\step:\radius*1.3) {\em \footnotesize 1 or 2 vertices \\[3pt]\em \footnotesize in this region};
+	\node[align = center] at (\zero + 1.6*\step:\radius*1.35) {\em \footnotesize 0 or 1 vertices \\[3pt]\em \footnotesize in this region};
+	% draw props and their labels
+	\begin{scope}
+		\clipcenterarc(0,0)(\startpoint-20:\endpoint+20:\radius)
+		%q
+		\draw[smallpropagator] (\zero+1.65*\step:\radius*1.1) to [bend left = 40] (\zero + 7.4*\step:\radius*1.1); 
+		%p
+		\draw[smallpropagator] (\zero+2.3*\step:\radius*1.1) to [bend left = 55] (\zero + 4.8*\step:\radius*1.1); 
+		\draw[smallpropagator,light-gray] (\zero+1.5*\step:\radius*1.1) -- (180:\radius*0.5); 
+		\draw[smallpropagator,light-gray] (\zero+1.6*\step:\radius*1.1) -- (180:\radius*0.25);
+		\draw[smallpropagator,light-gray] (\zero+7.55*\step:\radius*1.1) -- (0:\radius*0.5); 
+		%\draw[smallpropagator,light-gray] (\zero+7.5*\step:\radius*1.1) -- (0:\radius*0.25);  
+		\node at (\zero + 4.5*\step:\radius*0.5){\footnotesize $q$};
+		\node at (\zero + 3.5*\step:\radius*0.8){\footnotesize $p$};
+	\end{scope}
+	% nodes
+	\newnode[left]{1}{i}
+	\newnode[right]{8}{j+1}
+	\newnode[below]{3}{}
+	\newnode[below]{4}{}
+	% case label
+	\node at (270:\radius*0.2) {\em Case 2};
+\end{scope}
+\end{tikzpicture}
+%
+%
+%
+\\
+\ & \ & \ \\
+%
+%
+%
+% case 3
+\begin{tikzpicture}[baseline=(current bounding box.east)]
+\begin{scope}
+	\drawWLDfragment[8]{3}{0.3} % draw arc
+	%\drawnumbers % use this to debug
+	% highlight region
+	\centerarc[linehighlight](0,0)(\zero + 3.6*\step:\zero + 5.4*\step:\radius)
+	% region label
+	\node[align = center] at (\zero + 4.5*\step:\radius*1.3) {\em \footnotesize 0, 1, or 2 vertices \\[3pt]\em \footnotesize in this region};
+	% scope to draw props and their labels
+	\begin{scope}
+		\clipcenterarc(0,0)(\startpoint-20:\endpoint+20:\radius)
+		%q
+		\draw[smallpropagator] (\zero+1.5*\step:\radius*1.1) to [bend left = 55] (\zero + 3.7*\step:\radius*1.1); 
+		%p
+		\draw[smallpropagator] (\zero+5.3*\step:\radius*1.1) to [bend left = 55] (\zero + 7.6*\step:\radius*1.1); 
+		\draw[smallpropagator,light-gray] (\zero+1.5*\step:\radius*1.1) -- (180:\radius*0.5); 
+		\draw[smallpropagator,light-gray] (\zero+1.6*\step:\radius*1.1) -- (180:\radius*0.25);
+		\draw[smallpropagator,light-gray] (\zero+7.55*\step:\radius*1.1) -- (0:\radius*0.5); 
+		%\draw[smallpropagator,light-gray] (\zero+7.5*\step:\radius*1.1) -- (0:\radius*0.25);  
+		\node at (\zero + 2.8*\step:\radius*0.8){\footnotesize $q$};
+		\node at (\zero + 6.5*\step:\radius*0.8){\footnotesize $p$};
+	\end{scope}
+	% draw nodes
+	\newnode[left]{1}{i}
+	\newnode[below]{2}{}
+	\newnode[below]{3}{j}
+	\newnode[below]{6}{}
+	\newnode[below]{7}{}
+	\newnode[right]{8}{}
+	% case label
+	\node at (270:\radius*0.2) {\em Case 3};
+\end{scope}
+\end{tikzpicture}
+%
+%
+%
+& \qquad \qquad & \qquad
+%
+%
+%
+% case 4
+\begin{tikzpicture}[baseline=(current bounding box.east)]
+	\begin{scope}
+	\drawWLDfragment[8]{3}{0.3} % draw arc
+	%\drawnumbers % use this to debug
+	%scope to draw props and their labels
+	\begin{scope}
+		\clipcenterarc(0,0)(\startpoint-20:\endpoint+20:\radius)
+		%q
+		\draw[smallpropagator] (\zero+1.65*\step:\radius*1.1) to [bend left = 40] (\zero + 7.4*\step:\radius*1.1); 
+		%p
+		\draw[smallpropagator] (\zero+3.3*\step:\radius*1.1) to [bend left = 55] (\zero + 5.8*\step:\radius*1.1); 
+		\draw[smallpropagator,light-gray] (\zero+1.5*\step:\radius*1.1) -- (180:\radius*0.5); 
+		\draw[smallpropagator,light-gray] (\zero+1.6*\step:\radius*1.1) -- (180:\radius*0.25);
+		\draw[smallpropagator,light-gray] (\zero+7.55*\step:\radius*1.1) -- (0:\radius*0.5); 
+		%\draw[smallpropagator,light-gray] (\zero+7.5*\step:\radius*1.1) -- (0:\radius*0.25);  
+		\node at (\zero + 4.5*\step:\radius*0.5){\footnotesize $q$};
+		\node at (\zero + 5*\step:\radius*0.8){\footnotesize $p$};
+	\end{scope}
+	% draw nodes
+	\newnode[left]{1}{i}
+	\newnode[below]{2}{i+1\quad }
+	\newnode[below]{3}{l\quad}
+	\newnode[below]{4}{l+1\ \ }
+	\newnode[below]{5}{\ \ l+2}
+	\newnode[below]{6}{\quad l+3}
+	\newnode[below]{7}{\quad j}
+	\newnode[right]{8}{j+1}
+	% case label
+	\node at (270:\radius*0.2) {\em Case 4};
+\end{scope}
+\end{tikzpicture}
+\end{tabular}
     \caption{Four cases for admissible WLDs with no non-supporting vertices.
@@
 $V$ is guaranteed to be an admissible diagram, since it was formed by removing a propagator from a diagram that was at least weakly admissible.
-
-\begin{figure}
-\includegraphics[width=10cm]{V_diagram}
-\caption{Diagram $V$ is $W$ with $p$ removed; there are no propagators inside $q = (i,j)$, though there may be up to 4 non-supporting vertices labelled $l, l+1, \ldots$.}
-\label{fig V diagram}
-\end{figure}
 
@@
 We need to consider both $J^{W}_p$ and $J^{W}_r$ for $r \neq p$, since the addition of $p$ can have a knock-on effect on later steps in the algorithm.
+
+\begin{figure}
+\[
+\begin{tikzpicture}[baseline=(current bounding box.east)]
+	\begin{scope}
+	\drawWLDfragment[8]{4}{0.3}
+	%\drawnumbers % use this to debug
+	%\clip (\zero + 1.5*\step:1.5*\radius) rectangle (345:{\radius});
+	\centerarc[linehighlight](0,0)(\zero + 2.8*\step:\zero + 6.2*\step:\radius)
+	\newnode[below]{1}{i}
+	\newnode[below]{2}{i+1}
+	\newnode[below]{3}{l}
+	\newnode[below]{4}{l+1}
+	\newnode[below]{5}{l+2}
+	\newnode[below]{6}{l+3}
+	\newnode[below]{7}{j}
+	\newnode[below]{8}{\quad j+1}
+	%\node[rotate=-15] at (\zero + 2.7*\step:\radius) {\Large $($};
+	%\node[rotate=15] at (\zero + 6.3*\step:\radius) {\Large $)$};
+	\node at (\zero + 4.5*\step:\radius*0.85) {\em \scriptsize up to 4 vertices here};
+	\begin{scope}
+	\clipcenterarc(0,0)(\startpoint-10:\endpoint+10:\radius)
+		\draw[smallpropagator] (\zero+1.3*\step:\radius*1.2) to [bend left = 40] (\zero + 7.7*\step:\radius*1.2); 
+	\node at (\zero + 4.5*\step:\radius*0.5){\footnotesize $q$};
+\end{scope}
+\end{scope}
+\end{tikzpicture}
+\]
+\caption{Diagram $V$ is $W$ with $p$ removed; there are no propagators inside $q = (i,j)$, though there may be up to 4 non-supporting vertices labelled $l, l+1, \ldots$.}
+\label{fig V diagram}
+\end{figure}
 
@@
 
-\medskip  \sanote{Suggested breakpoint of theorem}
-
-We have shown that $(I_1,\dots,I_n)$ is a Grassmann necklace; it remains to check that this Grassmann necklace corresponds to the positroid $M(W)$.
-Recall from the discussion following Definition~\ref{def:grassmann necklace}, and equation \eqref{basesofmatroids} in particular, that it suffices to show:
-\begin{itemize}
-\item For each $i \in [n]$, $I_i$ is a basis for $M(W)$.
-\item If $J$ is lexicographically smaller than $I_i$ with respect to $<_i$ (for any $i \in [n]$) then $J$ is not a basis for $M(W)$. 
-\end{itemize}
-The first point follows immediately: since the algorithm is pairing each $j \in I_i$ with a unique propagator supported on that vertex, $I_i$ is a basis for $M(W)$ by Corollary~\ref{lem basis as perm}.
-
-Now suppose we have a $k$-set $J$ such that $J$ is a basis for $M(W)$ and yet is lexicographically less than $I_i$ with respect to $<_i$.
-By Corollary~\ref{lem basis as perm} there is a set bijection between $J$ and the propagators of $W$ such that for each $j \in J$, the propagator associated to $j$ is supported on vertex $j$.
-Choose one such bijection.
-For each propagator $p$ of $W$, write $J(p)$ for the vertex $j$ associated to $p$ according to this bijection.
-
-Since $J$ is lexicographically smaller than $I_i$, the $<_i$-smallest element of the symmetric difference of $J$ and $I_i$ is some $j_0\in J$, $j_0 \not\in I_i$.
-Let $p_1$ be the propagator such that $J(p_1)=j_0$.
-Since $j_0\not\in I_i$ but $p_1$ is supported at $j_0$, then $p_1$ must have been assigned to an earlier vertex by $I_i$, i.e.
-we have $I_i(p_1) <_i j_0$.
-Let $j_1 = I_i(p_1)$.
-
-However, $j_0$ is the $<_i$-smallest element in the symmetric difference of $J$ and $I_i$, so we must have $j_1 \in J$ as well; in particular, there is some propagator $p_2$ such that $J(p_2)=I_i(p_1)$.
-Let $j_2 = I_i(p_2)$ and note that $j_2 \neq J(p_2)$ (since $I_i(p_1)=J(p_2)$), so either $I_i(p_2) \not\in J$ or there is a propagator $p_3$ such that $J(p_3) = I_i(p_2)$.
-Continue this process for as many steps as possible (i.e.
-for as long as $I_i(p_*) \in J$); this produces a list of vertices $j_r$ and propagators $p_r$ such that
-\[J(p_r) = I_i(p_{r-1}) = j_{r-1}.\]
-
-We claim that there is no repetition of propagators or vertices in this list; this will show that the process must eventually terminate.
-The claim is proved by induction.
-The definition of $j_0$ gives that $j_0$ and $j_1$ are distinct and that $p_1$ and $p_2$ are distinct.
-Now, suppose we have $p_r$ and $j_r$ with $I_i(p_r)=j_r$, with $j_r$ distinct from all previous $j_*$ and with $j_r\in J$.
-Then there must exist a propagator $p_{r+1}$ with $J(p_{r+1}) = j_r$.
-Since $J: \cP \longrightarrow [n]$ is injective and $j_r$ is not equal to any of the previous vertices $j_0, \dots, j_{r-1}$ by assumption, $p_{r+1}$ must be distinct from the previous propagators $p_1,\dots,p_r$.
-Following the pattern, define $j_{r+1} = I_i(p_{r+1})$.
-Since $I_i: \cP \longrightarrow [n]$ is also injective and $p_{r+1}$ is distinct from the earlier $p_*$, it follows that $j_{r+1}$ is distinct from the other $j_s$ for $1\leq s\leq r$.
-Finally, we have $j_{r+1}\neq j_0$ since $j_0\not\in I_i$ but $j_{r+1}\in I_i$.
-This proves the claim.
-
-Therefore the list must end, and the only way it can end is with some $p_r$ such that $j_r = I_i(p_r)\not\in J$. In particular, this implies that $j_r >_i j_0$.
-
-Next we will prove that $j_r <_i j_0$ for all $r > 0$; this gives a contradiction to the existence of $J$ and completes the proof of the theorem.
-This proof will also be by induction; however, for the induction to go through nicely we will need to prove the following slightly stronger statement:
-for all $r>0$ in the list
-\begin{itemize}
-\item $j_r <_i j_0$ and
-\item either
-  \begin{itemize}
-  \item $I_i(p_r) <_i J(p_r)$, or
-  \item there exists an $\ell<r$ such that $I_i(p_\ell) <_i J(p_\ell)$, those two vertices support distinct ends of $p_\ell$, and $p_r$ is inside $p_l$ when $p_l$ is directed from $I_i(p_\ell)$ to $J(p_\ell)$.\note{Should I replace this with ``$p_r$ is inside $(p_l,<_i)$''?
-It matches previous notation but maybe is less clear?}
-  \end{itemize}
-\end{itemize}
-
-We observed above that $j_1 <_i j_0$ and $I_i(p_1) <_i J(p_1)$ so we have the base case for the induction.
-Now fix $r > 1$ and suppose that the inductive hypothesis holds for all indices less than $r$ and that $p_r$ exists.
-
-By definition $J(p_r) = I_i(p_{r-1}) = j_{r-1}$, so $p_{r-1}$ and $p_{r}$ are both supported at vertex $j_{r-1}$.
-
-Since $I_i$ always chooses the earliest unassigned propagator supported at a vertex, we have two possibilities (which are not mutually exclusive): either $p_{r-1}$ appears before $p_r$ in the neighbourhood of $j_{r-1}$, or $p_r$ was assigned earlier than $p_{r-1}$ by the algorithm for $I_i$.
-(Note that the ordering $p_1,p_2,\dots,p_r$ need not match the order in which Algorithm~\ref{alg:put GN on WLD} assigns propagators to vertices.)
-
-In the latter case we are done, since $p_r$ being assigned earlier than $p_{r-1}$ by $I_i$ means exactly that $I_i(p_r) <_i I_i(p_{r-1})$.
-Recalling that $I_i(p_{r-1}) = J(p_r) = j_{r-1}$, this implies that $I_i(p_r) <_i J(p_r)$ and $j_r = I_i(p_r) <_i j_{r-1} <_i j_0$, as required.
-
-Now assume that $p_{r-1}$ appears before $p_r$ in the neighbourhood of $j_{r-1}$, and that $I_i$ assigns $p_{r-1}$ before $p_r$.
-
-\hlfix{If $I_i(p_{r-1}) <_i J(p_{r-1})$ and these are vertices supported by distinct ends of $p_{r-1}$}{Sian was unsure about this sentence, and added the blue text below which may or may not be necessary}, then by our assumption that $p_{r-1}$ appears before $p_r$ in the neighbourhood of $j_{r-1}$ it follows that $p_r$ must lie inside $p_{r-1}$ when directed from $I_i(p_{r-1})$ to $J(p_{r-1})$.
-Therefore
-\[j_r = I_i(p_r) \leq_i J(p_{r-1}) + 1.\]
-If $r > 2$ then this gives $j_r \leq_i I_i(p_{r-2}) + 1 \leq_i j_0$, but we know that $j_0\not\in I_i$ so in fact we have a strict inequality $j_r<_i j_0$.
-If $r=2$ then the inequality reads $j_2 \leq_i J(p_1) + 1 = j_0 + 1$, so either $j_2 <_i j_0$ or we have the configuration
-\[
-\includegraphics{impossible_config}
-\]
-However, this is impossible because now $p_2$ is supported at $j_0$ but not assigned by $I_i$ until after $j_0$, even though $j_0\not\in I_i$.
-Thus we always have $j_r <_i j_0$ and the inductive step is complete in this case (with $p_{r-1}$ playing the role of $p_l$ here).
-
-\textcolor{blue}{
-On the other hand, if $I_i(p_{r-1}) <_i J(p_{r-1})$ and these vertices are on the same end of $p_{r-1}$, then we must have 
-\[
-\includegraphics[width=10cm]{extra_config}
-\]
-If $r = 2$, then $J(p_{r-1}) = j_0$ and our assumption that $p_{r-1}$ is assigned before $p_r$ means that $I_i$ assigns $p_2$ to $j_0$, which is again a contradiction.
-If $r>2$ then $J(p_{r-1}) = I_i(p_{r-2})$ implies we have another propagator $p_{r-2}$ on this same edge, which must lie between $p_{r-1}$ and $p_r$ to ensure that $I_i$ assigns everything in the correct order.
-Now $J(p_{r-2})$ must support the other end of $p_{r-2}$, and we can apply the same argument as above with $p_{r-2}$ instead of $p_{r-1}$.}
-
-The only remaining possibility is that $I_i(p_{r-1})\not<_i J(p_{r-1})$, so now assume this.
-We continue to assume that $p_{r-1}$ appears before $p_r$ in the neighbourhood of $j_{r-1}$ and that $I_i$ assigns $p_{r-1}$ before $p_r$.
-
-By the induction hypothesis,  $I_i(p_{r-1})\not<_i J(p_{r-1})$ implies that there exists an $\ell < r-1$ such that $p_{r-1}$ lies inside $p_{\ell}$ when directed from $I_i(p_\ell)$ to $J(p_\ell)$.
-Since $p_{r-1}$ and $p_r$ are both supported on vertex $j_{r-1}$, either $p_r$ is also inside $p_l$ (in which case we apply the arguments above with $l$ instead of $r-1$) or $p_l$ lies between $p_{r-1}$ and $p_r$ in the neighbourhood of $j_{r-1}$.
-
-Since $I_i(p_{r-1}) = j_{r-1}$ and $p_{r-1}$ is inside $p_l$, the fact that no propagator can contribute its 4th vertex to $I_i$ (Lemma~\ref{lem no fourth vertex}) means that we have the following configuration:
-\[
-\includegraphics[width=10cm]{new_induction_conf}
-\]
-If $l=1$ then $J(p_l) = j_0$, and $p_r$ is supported on $j_0$ but assigned by $I_i$ later than $j_0$, which is a contradiction.
-If $l>1$ then $J(p_l) = I_i(p_{l-1})$, and propagator $p_{l-1}$ must appear before $p_r$ in the neighbourhood of $j_{r-1}$ to ensure that $I_i$ assigns $p_{l-1}$ correctly.
-But now $J(p_{l-1})$ must be on the other end of $p_{l-1}$, since the vertices on this end are $J(p_r)$ and $J(p_l)$ and we know that $l-1 < l < r$.
-Finally, we must have $I_i(p_{l-1}) <_i J(p_{l-1})$ so that $I_i$ does not assign $p_{l-1}$ to its fourth vertex.
-Now $p_r$ lies inside $p_{l-1}$ and we argue as above.
-
-%  If $j_{r-1}$ is not in the support of the $J(p_\ell)$ end of $p_\ell$ then $p_{r-1}$ before $p_{r}$ around $j_{r-1}$ implies that $p_r$ is on the same side of $p_\ell$ as $p_{r-1}$ is.
-Then the same arguments as above with $\ell$ in place of $r-1$ give $j_r \leq_i J(p_\ell)+1$ implying $j_r <_i j_0$ which is everything we need.
-
-% It remains to consider when $j_{r-1}$ is in the support of the $J(p_\ell)$ end of $p_\ell$, call this case $(*)$.
-Since $J(p_\ell) = j_{\ell-1}$ and the vertices $j_1,\dots,j_r$ are distinct, this means that we have one of the following two configurations
-% \[
-% \includegraphics{induction_conf}
-% \]
-% If $p_\ell=p_1$ then $j_{\ell-1}=j_0$ and then as $j_0\not\in I_i$ but $p_r$ is supported at $j_0$ we get $I_i(p_r) <_i j_0$ and also $I_i(p_r) <_i j_{r-1} = J(p_r)$ as the only vertices not yet taken for $I_i(p_r)$ must be before both labelled vertices in the illustration.
-
-% If $p_\ell \neq p_1$ then we argue as above with $\ell-1$ in place of $r-1$: in particular $J(p_\ell) = I_i(p_{\ell-1})$ but $p_r$ is supported at $p_{\ell-1}$, so either $I_i(p_r) <_i I_i(p_{\ell-1})$ in which case as before we get desired conclusion, or $p_r$ comes before $p_{\ell-1}$ at $j_{\ell-1}$.
-Then again argue as before getting a new $p_{\ell'}$ in place of $p_{\ell}$, except that then case $(*)$ must occur simultaneously for both $p_{\ell'}$ and $p_{\ell}$ with respect to $p_{r}$.
-This can only occur if $j_{\ell-1}, j_{r-1}, j_{\ell'-1}$ are consecutive.
-Iterating the argument one more time we finally cannot have case $(*)$ as then all neighbouring vertices of $j_{r-1}$ are used up.
-
-This covers all cases and completes the induction, and thence the proof of the theorem.
-
 \end{proof}
 
-\sanote{alternate proof of second half of above}
-{\color{violet} \begin{thm}
-The Grassmann necklace $(I_1 \ldots I_n)$ is the Grassmann neclace for $M(W)$ 
+\begin{thm}
+The Grassmann necklace $(I_1 \ldots I_n)$ from Theorem~\ref{res:alg gives GN} is the Grassmann necklace for $M(W)$.
 \end{thm}
@@
 \end{itemize}
-The first point follows immediately: since the algorithm is pairing each $j \in I_i$ with a unique propagator supported on that vertex, $I_i$ is a basis for $M(W)$ by Corollary~\ref{lem basis as perm}.
-
-For the second point, order the propagators according to the ordering induced by the algorithm for $I_i$.
-Write $\cP = \{p_1, \ldots , p_k\}$.
-That is, $p_i$ defines the $i^{th}$ row of $C(W)$.
-For $m<k$, write $\cP_m = \{p_1, \ldots , p_k\}$.
-
-Write $I_i(p_j)=a_j$.
-If two consecutive propagators do not contribute consecutive vertices, that is, there exist $a_{j-1} <_i x <_i a_j$ then the vertex $x$ supports only propagators in $\cP_j$, if any: $\Prop(x) \subset \cP_j$.
-
-Let $J = (j_1,\ldots j_k)$ be a sequence that is lexicographically less than $I_i = (a_1 \ldots a_k)$: $J <_i I_i$.
-By the above, for some $m < k$, $a_{m-1} <_i j_m <_i a_m$ and the matrix entry $c_{m, j_m} = 0$ is $0$.
-Without loss of generality, let $m$ be the smallest $m$ in the $<_i$ order for which this is true: \bas \forall l <m, \; I_i(p_l) = j_l \; ; \; j_m < I_i(p_m) \;.\eas Write $J_m = (j_1, \ldots, j_m)$ indicate the first $m$ entries of $J$.
-We claim that there exists some subset  of vertices $U \subset J_m$ such that $|\Prop(U)| < |U|$.
-
-Consider the vertices contributed by the propagators originally supported on $j_m$: $V = I_i(\Prop(j_m))$.
-By construction, these are a subset of $J_{m-1}$.
-Note that $\Prop(V) \subset \cP_m$.
-Let $p_l$ be supported on $j_m$.
-If $q$ is suported on $p_l$, either $q$ preceeds $p_l$ (i.e.
-is not there when the algorithm reaches $a_l$) or is positioned counterclockwise to $p_l$ at the vertex $a_l$.
-That is, $q$ is inside $p_l$ in the $<_i$ ordering.
-By Lemma \ref{lem no fourth vertex}, $q$ does not contibute its last supporting vertex to $I_i$.
-That is, $I_i(q) <j_m$.
-\hlfix{But this implies that $q$ contributed before $p_m$, which contradicts the hypothesis.}{Seems to demand that $I_i$ catches all propagators in a single circuit of the vertices.
-Is this explicit anywhere, or am I jumping the gun?} Therefore $q \in \cP_{m-1}$.
-
-If $\Prop(j_m) = \Prop(V)$, we have that $V$ and $V \cup j_m$ support the same propagators. That is, \bas |\Prop(V)| = |V| = |\Prop(V \cup j_m )| <  |V \cup j_m| \;.\eas
-
-If $\Prop(j_m) \subsetneq \Prop(V)$, expand $V$ to include the vertices contributed by $\Prop(V)$.
-That is, $V' = I_i(\Prop(V))$.
-By the argument above, $\Prop(V) \subset \cP_m$.
-If $\Prop(V) = \Prop(V')$ then the relevant vertex set is $V'$.
-Else, continue expanding $V'$ in this manner until no new propagators are added.
-Since all of these sets of propagators are contained in $\cP_m$, which is finite, this process is finite.
-
-\begin{comment}
-By algorithm \ref{alg:put GN on WLD}, $a_j$ is the smallest number in the $<_{a_{j-1}}$ ordering such that $c_{j, a_j} \neq 0$ (that is, is an indeterminant entry).
-Therefore, $p_m \not \in \Prop(j_m)$.
-In fact, no $q$ that follow $p_m$ in the ordering can be supported on $j_m$.
-Since $j_m < a_m$, the algorithm for $I_i$ checks this vertex before $a_m$.
-If any propagator in $\cP \setminus \cP_{m-1}$ are supported on $j_m$, then this propapagator would preceed $p_m$, i.e.
-be an element of $\cP_{m-1}$.
-Therefore, the only non-zero entries in column $j_m$ of $C(W)$ lie in the first $m-1$ rows.
-
-Therefore, $\Prop(j_m) \subset \cP_{m-1}$.
-Let $V =  V(\Prop(j_m)) \cap J_{m-1}$ be the vertices in $J_m$ supporting the propagators supported on $j_m$.
-That is, $V$ is contains the vertices contributed by $\Prop(j_m)$.
-So $|\Prop(j_m)| \leq |V|$.
-We show that $\Prop (V) \subset \Prop_{m-1}$.
-Suppose otherwise.
-Let $q \in \cP \setminus \cP_m$ be a propagators after $p_m$ and $p_l \in \Prop(j_m)$ a propagators before $p_m$ supported on $j_m$ such that both $q$ and $p_l$ are supported on $I_i(p_l)= a_l$.
-Since $p_l$ contributes $a_l$, it must be the clockwisemost propagator in $\cP \setminus \cP_{l-1}$ supported on $a_l$.
-In other words, $q \in \cP_{in}(p_l, <_{a_l-1})$ is inside $p_l$ in the $a_l-1$ order.
-Specifically, the last supporting vertex of $q$ is strictly less than $j_m$.
-By Lemma \ref{lem no fourth vertex}, $q$ does not contibute its last supporting vertex to $I_i$.
-That is, $I_i(q) <j_m$.
-\hlfix{But this implies that $q$ contributed before $p_m$, which contradicts the hypothesis.}{Seems to demand that $I_i$ catches all propagators in a single circuit of the vertices.
-Is this explicit anywhere, or am I jumping the gun?}
-
-By construction, this implies that $V \subset \Prop(j_m)$. But $V$ contains the vertices 
-Since $J_{m-1}$ is independent, $V \subset J_{m-1}$ is too. Therefore, $|V| \leq |\Prop(V)| $. Since  $\Prop (V) \subset \cP_{m-1}$
-***************
-For the second point, consider the matrix $C(W)$ associated to the diagram $W$.
-Recall that $C(W)$ is only defined up to an ordering of the propoagators of $W$.
-Therefore order them according to the ordering induced by the algorithm for $I_i$.
-Write $\cP = \{p_1, \ldots , p_k\}$.
-That is, $p_i$ defines the $i^{th}$ row of $C(W)$.
-
-Write $I_i(p_j)=a_j$.
-By algorithm \ref{alg:put GN on WLD}, $a_j$ is the smallest number in the $<_{a_{j-1}}$ ordering such that $c_{j, a_j} \neq 0$ (that is, is an indeterminant entry).
-It is the first column in the $j^{th}$ row of $C(W)$ that is both non-zero and is greater than the index contributed by the previous propagator:  \bas \begin{bmatrix}\ddots & & & & & & \\ \ldots  & c_{j-1, a_{j-1}} & * & \ldots &  & & \\  \ldots  &* &0 & \ldots & 0 &c_{j, a_j} & \ldots \\ & & & & & & \ddots \end{bmatrix}  \eas
-
-Let $J = (j_1,\ldots j_k)$ be a sequence that is lexicographically less than $I_i = (a_1 \ldots a_k)$: $J <_i I_i$.
-By the above, for some $m < k$, $j_m <_i a_m$ and the matrix entry $c_{m, j_m} = 0$ is $0$.
-Without loss of generality, let $m$ be the smallest $m$ in the $<_i$ order for which this is true: \bas \forall l <m, \; I_i(p_l) = j_l \; ; \; j_m < I_i(p_m) \;.\eas Write $J_m = (j_1, \ldots, j_m)$ indicate the first $m$ entries of $J$.
-
-We claim that the $j_m^{th}$ column of $C(W)$ is in the span of the columns indexed by $J_{m-1}$.
-
-Since $J_{m-1}$ is an independent set in $C(W)$, row reduce the first $j_{m-1}$ columns of $C(W)$ to have $1$ in the $(r, j_r)$ position and $0$ to the right: \bas \begin{bmatrix}1 &0  &\ldots  & &  &0 \\  * & \ldots  & * & 1 & 0&\ldots \\    &\ddots &  &  &\ldots & 1 \\  *&* &* &\ldots &* &* \\  &\ddots & & & \ddots &  \\ *&* &* &\ldots &* &*  \end{bmatrix}  \;.\eas \sanote{fix this!
-wrote echelon order!}
-
-Next consider the $j_m^{th}$ column of $C(W)$.
-First note that, since $c_{m, j_m} = 0$.
-Furthermore, no $q$ that follow $p_m$ in the ordering can be supported on $j_m$.
-Since $j_m < a_m$, the algorithm for $I_i$ checks this vertex before $a_m$.
-If any propagators remain to be supported on this vertex after the removal of $p_1$ to $p_{m-1}$, then this propapagator would preceed $p_m$.
-Therefore, the only non-zero entries in column $j_m$ of $C(W)$ lie in the first $m-1$ rows.
-\sanote{add something here} Therefore, column $j_m$ lies in the span of the first $j_{m-1}$ columns of $C(W)$.
-
-*******
-%If $p, q \in \Prop(i)$ are two propagators supported on the vertex $i$, we may write $p = (a_p, b_p)$ and $q = (a_q, b_q)$, with the initial vertices $a_p$ and $a_q$ in the set $\{i, i-1\}$.
-By construction, the propagator $q$ is located clockwise relative to $p$ if and only if $p$ is inside $q$.
-That is, $p \in \cP_{in}(q, <_{a_q})$.
-
-%For $m < k$, write $\cP_m =\{p_1, \ldots , p_m\} \subset \cP$ to indicate the first $m$ propagators.
-For any subset of propagators $Q \subset \cP$, write $W|_Q = (Q, [n])$ be the subdiagram of $W$ consisting only of the propagators in $Q$ and all the vertices $[n]$.
-
-%Since $p$ never contributes its last vertex in the $<_i$ order to $I_i$, by Lemma \ref{lem no fourth vertex}, every propagator preceeding $p_j$ is outside it in the $a_j-1$ ordering: $\cP_{j-1} \subset \cP_{out}(p_j)$.
-
-We claim that $J_m$ is not a basis for $W|_{\cP_m}$.
-To see this, first note that, since $c_{m, j_m} = 0$, the propagator $p_m$ is not supported on $j_m$.
-If $p_m$ does not share support with any propagator in $\cP_m$ in the cyclic interval $[i, j_m]$, then the minor of $C(W|_{\cP_m})$ defined by $J_{m}$, has a row of $0$s.
-
-Otherwise, let $p_l$ be a propagator preceeding $p_m$ ($p_l \in \cP_{m-1}$) that shares support with it in $J_m$: $V(p_l) \cap V(p_m) \cap J_m \neq \emptyset$.
-Then $p_l \in Q$ is positioned clockwise to $p_m$ on vertex $a_l$, therefore, $p_l$ is outside $p_m$ in the $a_l -1$ order.
-Since $a_l <_i j_m <_i a_m$ with $a_l$ and $a_m$ both in the support of $p_m$, \hlfix{$j_m$ is inside $p_m$ in the $a_l-1$ ordering.
-}{I know we got rid or interior vertices.
-Can we bring it back or rephrase?} Furthermore since all of $\cP_{m-1} \subset \cP_{out}(p_m)$ is outside of $p_m$ in that $a_l-1$ order, and $j_m$ is a vertex inside it, no propagator prior to $p_m$ can be supported on $j_m$.
-Otherwise, one would have crossing propagators.
-Therefore, the minor of $C(W|_{\cP_m})$ defined by $J_{m}$, has a column of $0$s.
-******
-\end{comment}
+The first point follows immediately: the algorithm assigns each propagator to a vertex in the support of that propagator, so $I_i$ is a basis for $M(W)$ by Corollary~\ref{lem basis as perm}.
+
+Now fix $i \in [n]$, and write $I_i = \{a_1 <_i a_2 <_i \dots <_i a_k\}$.
+This imposes an ordering on the propagators $\cP$, where we label them $p_1, p_2, \dots, p_k$ such that $I_i(p_j) = a_j$ for each $j$.
+Define $\cP_m: = \{p_1,p_2,\dots,p_m\}$ for each $m\geq 0$, with $\cP_0 = \emptyset$.
+
+We enumerate two important observations:
+\begin{enumerate}
+\item If $a_{m-1}$ and $a_{m}$ are not consecutive vertices for some $m$, then for any intermediate vertex $a_{m-1}<_i x <_i a_{m}$ we must have $\Prop(x) \subseteq \cP_{m-1}$.
+This is because if any propagator supported on $x$ is still unassigned when the algorithm reaches $x$, we would have $x \in I_i$.
+\item When $p_m$ contributes $I_i(p_m) = a_m$ to the Grassmann necklace, it must be the clockwise-most propagator (amongst those not yet assigned) that is supported on $a_m$ i.e.
+any other propagators supported by $a_m$ in $\cP \setminus \cP_{m-1}$ is inside $p_m$ in the $a_m-1$ ordering.
+\end{enumerate}
+
+Now, let $J = \{j_1 <_i j_2<_i \dots <_i j_k\}$ be a $k$-set, and suppose that $J<_i I_i$ in the $<_i$-lexicographic order.
+Let $m$ be the minimal index such that $j_m <_i a_m$, i.e.
+the first entry at which $J$ and $I_i$ differ.
+We will show that $J$ must be a dependent set.
+
+If $\Prop(j_m) = \emptyset$ then $J$ is automatically dependent since the corresponding column of $C(W)$ contains only zeros, so suppose henceforth that $\Prop(j_m) \neq \emptyset$.
+%In particular, this implies that $m>1$, since if $m=1$ we would have $\Prop(j_1) \subseteq \cP_0 = \emptyset$.
+
+In order to exhibit a dependent subset of vertices in $J$, we first define a sequence of sets of propagators by
+\[Q_0 = \Prop(j_m), \qquad Q_{l+1} = \Prop(I_i(Q_l))\quad \forall l \geq 0.\]
+It is easily verified that this is an increasing chain of sets: indeed, if $q \in Q_l$ then $I_i(q) \in I_i(Q_l)$, and since $I_i(q)$ is one of the vertices that supports $q$ we must have $q \in \Prop(I_i(Q_l)) = Q_{l+1}$.
+Since $\cP$ is finite, the sequence therefore stabilizes in finitely many steps when $Q_{l+1} = Q_l$.
+Let $Q = \cup_{l \geq 0} Q_l$ be this set of propagators.
+
+We will show that $Q \subseteq \mathcal{P}_{m-1}$, which will imply the theorem as follows: if $Q \subseteq \cP_{m-1}$ then we have $I_i(Q)\subseteq J$, and hence $I_i(Q) \cup \{j_m\} \subseteq J$ as well.
+Since $I_i(Q) \cup \{j_m\}$ only supports the propagators in $Q$ but has $|Q|+1$ vertices, it is a dependent set.
+Thus $J$ is a dependent set, and the Grassmann necklace $(I_1,\dots,I_n)$ constructed from $W$ does indeed define the positroid $M(W)$.
+
+We now proceed to prove $Q\subseteq \mathcal{P}_{m-1}$ by inductively proving $Q_l \subseteq \mathcal{P}_{m-1}$ for all $l \geq 0$.
+%If $Q_0 = \Prop(j_m) = \emptyset$ then $Q = \emptyset$, and $I_i(Q) \cup \{j_m\}= \{j_m\}$ is a single vertex supporting no propagators, and thus a dependent set. Otherwise,
+For the base case $Q_0 \subseteq \cP_{m-1}$ follows immediately from the first observation above that $\Prop(j_m) \subseteq \cP_{m-1}$
+
+Now assume that $Q_0,\dots,Q_{l-1} \subseteq \cP_{m-1}$, and consider $Q_{l}$.
+If $Q_{l} \setminus Q_{l-1} = \emptyset$ then we are done, with $Q = Q_l$.
+Otherwise, let $q \in Q_{l} \setminus Q_{l-1}$.
+By construction there is some propagator $p_r \in Q_{l-1}$ such that $p_r$ and $q$ are both supported on $I_i(p_r) = a_r$.
+If $q$ is clockwise of $p_r$ on vertex $a_r$ then we immediately have $q \in \cP_{m-1}$ as observed above.
+It remains to consider the case that $q$ is counter-clockwise of $p_r$ at $a_r$.
+
+Note that we cannot have $a_r+ 1 = j_m$ when $q$ is counterclockwise of $p_r$, since $q \not\in \Prop(j_m)$ by assumption.
+If the other end of $p_r$ (i.e.
+the end not supported on $a_r$) lies on an edge between $a_r$ and $j_m$ then since $q$ is inside $p_r$ with respect to $<_{a_r-1}$ we must have $V(q) \subseteq [a_r-1,j_m]$, and hence $q \in \cP_{m-1}$ by Lemma~\ref{lem no fourth vertex}.
+In particular, if $l=1$ then $p_r \in Q_{0} = \Prop(j_m)$ and we must be in this case.
+
+If not, then there must be some propagator $p_s \in Q_{l-2}$ such that $p_r$ and $p_s$ are both supported on $I_i(p_s) := a_s$.
+Since $p_r$ is clockwise of $q$, and $q$ cannot be supported on $I_i(p_s)$ since $q \not\in Q_{l-1}$, it follows that $I_i(p_s) <_i I_i(p_r)$.
+Therefore $q$ is inside $p_s$ with respect to $<_{a_s - 1}$ as well.
+
+\begin{figure}[h]
+\includegraphics[scale = 0.3]{awkward_induction_case.jpg}
+\caption{This picture isn't quite the one we need any more, but it should help to illustrate the claim about $I_i(p_s) <_i I_i(p_r)$}\label{fig:awkward induction step}
+\end{figure}
+
+Now repeat the argument above with $p_s$ in place of $p_r$: if the other end of $p_s$ lands on an edge between $q$ and $j_m$ then we have $q \in \cP_{m-1}$ as above; if not then there exists some $p_t \in Q_{l-3}$ with $p_s$ supported on $I_i(p_t)$ and $I_i(p_t) <_i I_i(p_r)$.
+Since there are finitely many steps this process can take before reaching $Q_0$, and any $p_* \in Q_0  = \Prop(j_m)$ has $j_m$ in its support by definition, this argument eventually terminates with the construction of a propagator constraining the positioning of $q$ as required.
+This completes the induction step, and hence the proof.
+
 \end{proof}
-}
 
@@
 \begin{figure}
- \includegraphics{specialp}
+\[
+\begin{tikzpicture}[rotate = 150,baseline=(current bounding box.east),label distance = -2mm]
+\begin{scope}
+	\drawWLDfragment[6]{3}{0.3}
+	%\drawnumbers % use this to debug
+	\begin{scope}
+		\clipcenterarc(0,0)(\startpoint:\endpoint:\radius)
+		\draw[smallpropagator] (\zero+2.4*\step:\radius*1.1) to [bend left = 55] (\zero + 4.6*\step:\radius*1.1); 
+		\node at (\zero + 3.5*\step:\radius*0.75){\footnotesize $p$};
+	\end{scope}
+	\centerarc[red,line width = 2pt,line cap = round](0,0)(\zero + 2*\step:\zero+4.45*\step:\radius)
+	\newbetternode[{[label distance=-3mm]above right}]{1}{n-4}
+	\newbetternode[{[label distance=-3mm]above right}]{2}{n-3}
+	\newbetternode[{[label distance=-3mm]above right}]{3}{n-2}
+	\newbetternode[{[label distance=-3mm]above right}]{4}{n-1}
+	\newnode[above]{5}{n}
+	\newnode[above]{6}{1}
+\end{scope}
+\end{tikzpicture}
+\qquad 
+\qquad 
+\begin{tikzpicture}[rotate=150, baseline=(current bounding box.east)]
+\begin{scope}
+	\drawWLDfragment[7]{3}{0.3}
+	%\drawnumbers % use this to debug
+	\begin{scope}
+		\clipcenterarc(0,0)(\startpoint:\endpoint:\radius)
+		\draw[smallpropagator] (\zero+1.4*\step:\radius*1.1) to [bend left = 60] (\zero + 3.5*\step:\radius*1.1); 
+		\draw[smallpropagator] (\zero+3.5*\step:\radius*1.1) to [bend left = 60] (\zero + 5.6*\step:\radius*1.1); 
+		\node at (\zero + 2.4*\step:\radius*0.8){\footnotesize $q$};
+		\node at (\zero + 4.5*\step:\radius*0.8){\footnotesize $p$};
+	\end{scope}
+	\centerarc[red,line width = 2pt,line cap = round](0,0)(\zero + 1.6*\step:\zero+5.5*\step:\radius)
+	\newbetternode[{[label distance=-3mm]above right}]{1}{n-5}
+	\newbetternode[{[label distance=-3mm]above right}]{2}{n-4}
+	\newbetternode[{[label distance=-3mm]above right}]{3}{n-3}
+	\newbetternode[{[label distance=-3mm]above right}]{4}{n-2}
+	\newbetternode[{[label distance=-3mm]above right}]{5}{n-1}
+	\newnode[above]{6}{n}
+	\newnode[above]{7}{1}
+\end{scope}
+\end{tikzpicture}
+\]
   \caption{The two cases for $W$ and $p$.  No other propagators can end in the fat red sections.  Other segments may have additional propagators ending in them.}\label{fig special p}
@@
 \begin{figure}
-\includegraphics{egWLD_forR}
+\begin{tabular}{rrrrr}
+\begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
+	\begin{scope}
+	\drawWLD{7}{1.5}
+	\drawnumbers
+	\drawlabeledprop{1}{-1}{6}{0}{\footnotesize   $p$}
+	\drawlabeledprop{1}{0}{5}{0}{\footnotesize   $q$}
+	\drawlabeledprop{1}{1}{4}{0}{\footnotesize \; \qquad  $s$}
+	\pgfmathsetmacro{\move}{\angle/\n};
+	\draw[->,shorten >=2pt,red,thick] (1.5*\angle + -1*\move:\radius) to[bend left = 45] (\angle*1:\radius); %p
+	\draw[->,shorten >=2pt,red,thick] (1.5*\angle:\radius) to[bend right = 45] (\angle*2:\radius); %q
+	\draw[->,shorten >=2pt,red,thick] (4.5*\angle:\radius) to[bend left = 45] (\angle*4:\radius); %r
+	\node at (\angle*1.5:\radius*2) {$I_1$};
+	\node[align = center] at (4*\angle:\radius*1.7) {$I_1(p) = 1, \; I_1(q) = 2,$ \\[5pt] $I_1(s) = 4$.};
+		\end{scope}
+	\end{tikzpicture} 
+	& \quad \quad  &
+\begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
+	\begin{scope}
+	\drawWLD{7}{1.5}
+	\drawnumbers
+	\drawlabeledprop{1}{-1}{6}{0}{\footnotesize   $p$}
+	\drawlabeledprop{1}{0}{5}{0}{\footnotesize   $q$}
+	\drawlabeledprop{1}{1}{4}{0}{\footnotesize \; \qquad  $s$}
+	\pgfmathsetmacro{\move}{\angle/\n};
+	\draw[->,shorten >=2pt,red,thick] (1.5*\angle + -1*\move:\radius) to[bend right = 45] (\angle*2:\radius); %p
+	\draw[->,shorten >=2pt,red,thick] (5.5*\angle:\radius) to[bend left = 45] (\angle*5:\radius); %q
+	\draw[->,shorten >=2pt,red,thick] (4.5*\angle:\radius) to[bend left = 45] (\angle*4:\radius); %r
+	\node at (\angle*1.5:\radius*2) {$I_2$};
+	\node[align = center] at (4*\angle:\radius*1.7) {$I_2(p) = 1,  \; I_2(s) = 4,$ \\[5pt] $I_2(q) = 5.$};
+	\end{scope} 
+\end{tikzpicture}
+& \quad & 
+\begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
+	\begin{scope}
+	\drawWLD{7}{1.5}
+	\drawnumbers
+	\drawlabeledprop{1}{-1}{6}{0}{\footnotesize   $p$}
+	\drawlabeledprop{1}{0}{5}{0}{\footnotesize   $q$}
+	\drawlabeledprop{1}{1}{4}{0}{\footnotesize \; \qquad  $s$}
+	\pgfmathsetmacro{\move}{\angle/\n};
+	\draw[->,shorten >=2pt,red,thick] (6.5*\angle:\radius) to[bend left = 45] (\angle*6:\radius); %p
+	\draw[->,shorten >=2pt,red,thick] (5.5*\angle:\radius) to[bend left = 45] (\angle*5:\radius); %q
+	\draw[->,shorten >=2pt,red,thick] (4.5*\angle:\radius) to[bend left = 45] (\angle*4:\radius); %r
+	\node at (\angle*1.5:\radius*2) {$I_3 = I_4$};
+	\node[align = center] at (4*\angle:\radius*1.7) {$I_3(s) = 4,\;  I_3(q) = 5,$ \\[5pt] $I_3(p) = 6.$ };
+	\end{scope} 
+\end{tikzpicture}  
+\\ 
+ & & & &  \\
+ \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
+	\begin{scope}
+	\drawWLD{7}{1.5}
+	\drawnumbers
+	\drawlabeledprop{1}{-1}{6}{0}{\footnotesize   $p$}
+	\drawlabeledprop{1}{0}{5}{0}{\footnotesize   $q$}
+	\drawlabeledprop{1}{1}{4}{0}{\footnotesize \; \qquad  $s$}
+	\pgfmathsetmacro{\move}{\angle/\n};
+	\draw[->,shorten >=2pt,red,thick] (6.5*\angle:\radius) to[bend right = 45] (\angle*7:\radius); %p
+	\draw[->,shorten >=2pt,red,thick] (5.5*\angle:\radius) to[bend right = 45] (\angle*6:\radius); %q
+	\draw[->,shorten >=2pt,red,thick] (4.5*\angle:\radius) to[bend right = 45] (\angle*5:\radius); %r
+	\node at (\angle*1.5:\radius*2) {$I_5$};
+	\node[align = center] at (4*\angle:\radius*1.7) {$I_5(s) = 5,\;  I_5(q) = 6,$  \\[5pt] $I_5(p) = 7$ };
+	\end{scope} 
+\end{tikzpicture}
+& \quad & 
+\begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
+	\begin{scope}
+	\drawWLD{7}{1.5}
+	\drawnumbers
+	\drawlabeledprop{1}{-1}{6}{0}{\footnotesize   $p$}
+	\drawlabeledprop{1}{0}{5}{0}{\footnotesize   $q$}
+	\drawlabeledprop{1}{1}{4}{0}{\footnotesize \; \qquad  $s$}
+	\pgfmathsetmacro{\move}{\angle/\n};
+	\draw[->,shorten >=2pt,red,thick] (6.5*\angle:\radius) to[bend right = 45] (\angle*7:\radius); %p
+	\draw[->,shorten >=2pt,red,thick] (5.5*\angle:\radius) to[bend right = 45] (\angle*6:\radius); %q
+	\draw[->,shorten >=2pt,red,thick] (1.5*\angle + 1*\move:\radius) to[bend left = 45] (\angle*1:\radius); %r
+	\node at (\angle*1.5:\radius*2) {$I_6$};
+	\node[align = center] at (4*\angle:\radius*1.7) {$I_6(q) = 6, \; I_6(p) = 7, $ \\[5pt] $I_6(s) = 1. $ };	
+	\end{scope}
+	\end{tikzpicture}  
+& \quad &
+\begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
+	\begin{scope}
+	\drawWLD{7}{1.5}
+	\drawnumbers
+	\drawlabeledprop{1}{-1}{6}{0}{\footnotesize   $p$}
+	\drawlabeledprop{1}{0}{5}{0}{\footnotesize   $q$}
+	\drawlabeledprop{1}{1}{4}{0}{\footnotesize \; \qquad  $s$}
+	\pgfmathsetmacro{\move}{\angle/\n};
+	\draw[->,shorten >=2pt,red,thick] (6.5*\angle:\radius) to[bend right = 45] (\angle*7:\radius); %p
+	\draw[->,shorten >=2pt,red,thick] (1.5*\angle:\radius) to[bend left = 45] (\angle*1:\radius); %q
+	\draw[->,shorten >=2pt,red,thick] (1.5*\angle + \move:\radius) to[bend right = 45] (\angle*2:\radius); %r
+	\node at (\angle*1.5:\radius*2) {$I_7$};
+	\node[align = center] at (4*\angle:\radius*1.7) {$I_7(p) = 1,  \; I_7(q) = 1, $ \\[5pt] $I_7(s) = 2.$};
+	\end{scope} 
+\end{tikzpicture}
+\\
+\end{tabular}
 \caption{Example WLD for illustrating Algorithm~\ref{alg WLD to denom via GN} and bijections between propagators and vertices for each Grassmann necklace element.}\label{fig R eg}
@@
 \begin{figure}
-  \includegraphics{no_big_factors}
+\[
+\begin{tikzpicture}[baseline=(current bounding box.east),rotate=-20]
+\begin{scope}
+	\drawWLDfragment[8]{3}{0.4} 
+	%\drawnumberspartial % use this to debug
+	\newnode[left]{1}{i-1}
+	\newnode[below]{2}{i}
+	\newnode[below]{7}{m}
+	\begin{scope}
+		\clipcenterarc(0,0)(\startpoint-10:\endpoint+10:\radius)
+		\newpropbend{1.7}{7.2}{60}
+		\draw[smallpropagator,blue] (\zero+7.8*\step:\radius*1.1) to[bend left = 55] (\zero + 10*\step:\radius*1.1);
+		\node at (\zero + 1.2*\step:\radius*0.5) {\footnotesize $p$};
+	\end{scope}
+	\node[align = center,black] at (\zero + \step*4.5:\radius*0.65) {\em \footnotesize propagators \\ \footnotesize \em inside $p$};
+	\draw[->,shorten >=2pt,thick,gray] (\zero + 1.6*\step:\radius) to[bend left = 45] (\zero + 1*\step:\radius); %p
+	\draw[->,shorten >=2pt,thick,gray] (\zero + 7.9*\step:\radius) to[bend left = 45] (\zero + 7*\step:\radius); 
+	\node[align = center,black] at (\zero + 6.8*\step:1.5*\radius) {\em \footnotesize If $m \in I_i$ then \\ \em \footnotesize it was contributed by \\ \em \footnotesize the blue propagator};
+\end{scope}
+\end{tikzpicture}
+\qquad 
+\begin{tikzpicture}[baseline=(current bounding box.east),rotate=-20]
+	\begin{scope}
+	\drawWLDfragment[8]{3}{0.4}  
+	%\drawnumberspartial % use this to debug
+	\newnode[left]{1}{i}
+	\newnode[below]{2}{i+1}
+	\newnode[below]{7}{j}
+	\centerarc[red,line width = 2pt,line cap = round](0,0)(\zero + 1.5*\step:\zero+1.56*\step:\radius);
+	\draw[->,shorten >=2pt,thick,gray] (\zero + 1.45*\step:\radius) to[bend left = 45] (\zero + 1*\step:\radius); %p
+	\draw[->,shorten >=2pt,thick,gray] (\zero + 1.61*\step:\radius) to[bend right = 45] (\zero + 2*\step:\radius); %q 
+	\draw[->,shorten >=2pt,thick,gray] (\zero + 7.7*\step:\radius) to[bend left = 45] (\zero + 7*\step:\radius); %blue
+	\begin{scope}
+		\clipcenterarc(0,0)(\startpoint-10:\endpoint+10:\radius)
+		\newpropbend{1.6}{7.2}{40} % q
+		\draw[smallpropagator] (\zero+1.5*\step:\radius*1.1) to[bend right = 40] (\zero  - 3*\step:\radius*1.1); % p
+		\draw[smallpropagator,blue] (\zero+7.6*\step:\radius*1.1) to[bend left = 55] (\zero + 10*\step:\radius*1.1);
+		\node at (\zero + 5*\step:\radius*0.3) {\footnotesize $q$};
+		\node at (\zero + 1*\step:\radius*0.6) {\footnotesize $p$};
+	\end{scope}
+	\node[align = center,black] at (\zero + \step*4.5:\radius*0.75) {\em \footnotesize propagators \\ \footnotesize \em inside $q$};
+	\node[align = center] at (\zero + 1.5*\step:\radius*1.5) {\footnotesize \em No \\ \footnotesize \em propagators \\ \footnotesize \em between \\ \footnotesize \em $p$ and $q$ \\ \footnotesize \em here};
+	\node[align = center,black] at (\zero + 6.8*\step:1.5*\radius) {\em \footnotesize If $j \in I_i$ then \\ \em \footnotesize it was contributed by \\ \em \footnotesize the blue propagator};
+\end{scope}
+\end{tikzpicture}
+\]
   \caption{The two cases in the proof that no factors of $\Delta_{I_i}$ have degree 3 or more.}\label{fig no big factors}
@@
 \begin{figure}
-  \includegraphics{quadratic}
+\[
+\begin{tikzpicture}[baseline=(current bounding box.east)]
+	\begin{scope}
+	\drawWLDfragment[2]{4}{0.1} 
+	%\drawnumberspartial % use this to debug
+	\newnode[below]{1}{a}
+	\newnode[below]{2}{b}
+	\begin{scope}
+	\clipcenterarc(0,0)(\zero - 1.5*\step:\zero + 4.5*\step:\radius)
+	\newprop[midway,left]{1.33}{-7}{\footnotesize $p$}
+	\newprop[midway,right]{1.66}{10}{\footnotesize $q$}
+	\end{scope}
+	\node at (\zero + 0.6*\step:\radius*0.7) {\footnotesize $p$};
+	\node at (\zero + 2.4*\step:\radius*0.7) {\footnotesize $q$};
+\end{scope}
+\end{tikzpicture}
+\begin{tikzpicture}[baseline=(current bounding box.east)]
+	\begin{scope}
+	\drawWLDfragment[2]{4}{0.1} 
+	%\drawnumberspartial % use this to debug
+	\newnode[below]{1}{b}
+	\newnode[below]{2}{a}
+	\begin{scope}
+	\clipcenterarc(0,0)(\zero - 1.5*\step:\zero + 4.5*\step:\radius)
+	\newprop[midway,left]{1.33}{-7}{\footnotesize $q$}
+	\newprop[midway,right]{1.66}{10}{\footnotesize $p$}
+	\end{scope}
+	\node at (\zero + 0.6*\step:\radius*0.7) {\footnotesize $q$};
+	\node at (\zero + 2.4*\step:\radius*0.7) {\footnotesize $p$};
+\end{scope}
+\end{tikzpicture}
+\]
   \caption{The situations giving a quadratic factor with variables appearing in $r_i$.}\label{fig quadratic}
@@
 \begin{figure}
-  \includegraphics[scale=0.5]{part4}
+\[
+\begin{tikzpicture}[baseline=(current bounding box.east),rotate = -40]
+	\begin{scope}
+	\drawWLDfragment[8]{3}{0.4} 
+	%\drawnumberspartial % use this to debug
+	\newnode{1}{}
+	\newnode[left]{2}{i-1}
+	\newnode[below]{5}{a-1\quad}
+	\newnode[below]{6}{a}
+	\newnode[below]{7}{b}
+	\begin{scope}
+		\clipcenterarc(0,0)(\startpoint:\endpoint+\step:\radius)
+		\newpropbend{1.5}{5.7}{20}
+		\newpropbend{1.3}{6.4}{30}
+		\newprop{6.6}{-6}{}
+	\end{scope}
+	\node at (\zero + 3.5*\step:\radius*0.8){\footnotesize $s$};
+	\node at (\zero + 4.8*\step:\radius*0.45){\footnotesize $p$};
+	\node at (\zero + 8*\step:\radius*0.65){\footnotesize $q$};
+\end{scope}
+\end{tikzpicture}
+\]
   \caption{In order to obtain $I_{i-1}(s) = a$, propagators $s$ and $p$ must each have an end on the edge $(i-2,i-1)$.}\label{fig part 4}

### 2019-08-10 GWLDCI.tex
removed last comment
first draft abstract and funding thanks

@@
 \title{Combinatorics of the geometry of Wilson loop diagrams I: equivalence classes via matroids and polytopes}
-\author{Susama Agarwala, Si\^an Fryer, and Karen Yeats}
+\author{Susama Agarwala\thanks{SA was supported by an ONR grant.}, Si\^an Fryer, and Karen Yeats\thanks{KY is supported by an NSERC Discovery grant, by the Canada Research Chair program, and though some the time this work was developed also by a Humboldt Fellowship from the Alexander von Humboldt foundation.}}
 %\date{}
@@
 \maketitle
+
+\begin{abstract}
+  Wilson loop diagrams, an important tool in studying scattering amplitudes, are known by previous work to be associated to positroids.
+  We characterize when two Wilson loop diagrams give the same positroid, and enumerate the number of different Wilson loop diagrams that correspond to each positroid cell.
+We also give a correspondence between those positroids which can arise from Wilson loop diagrams and directions in associahedra.
+\end{abstract}
 
@@
 In fact, it is in some ways more natural to consider Deodhar cells of $\mathbb{G}(k, n+1)$ for Wilson loop diagrams; in this case, one gets that the manifold represented by the diagrams is not orientable \cite{non-orientable}.
-\note{Check with Cam.}
 

### 2019-08-10 GWLDCI.tex
tweaked abstract of paper 1; added picture

@@
 \begin{abstract}
-  Wilson loop diagrams, an important tool in studying scattering amplitudes, are known by previous work to be associated to positroids.
-  We characterize when two Wilson loop diagrams give the same positroid, and enumerate the number of different Wilson loop diagrams that correspond to each positroid cell.
+  Wilson loop diagrams, an important tool in studying scattering amplitudes of SYM $N=4$ theory, are known by previous work to be associated to positroids.
+We characterize when two Wilson loop diagrams give the same positroid, prove that an important subclass of subdiagrms (exact subdiagrams) correspond to uniform matroids and enumerate the number of different Wilson loop diagrams that correspond to each positroid cell.
 We also give a correspondence between those positroids which can arise from Wilson loop diagrams and directions in associahedra.

### 2019-08-10 GWLDCII.tex
tweaked abstract of paper 1; added picture

@@
 \begin{figure}[h]
-\includegraphics[scale = 0.3]{awkward_induction_case.jpg}
-\caption{This picture isn't quite the one we need any more, but it should help to illustrate the claim about $I_i(p_s) <_i I_i(p_r)$}\label{fig:awkward induction step}
+
+\bas{\begin{tikzpicture}[baseline=(current bounding box.east)]
+\begin{scope}
+	\drawWLDfragment[8]{3}{0.3} % draw arc
+	%\drawnumbers % use this to debug
+	% highlight region
+	%\centerarc[linehighlight](0,0)(\zero + 3.6*\step:\zero + 5.4*\step:\radius)
+	% region label
+	%\node[align = center] at (\zero + 4.5*\step:\radius*1.3) {\em \footnotesize 0, 1, or 2 vertices \\[3pt]\em \footnotesize in this region};
+	% scope to draw props and their labels
+	\begin{scope}
+		\clipcenterarc(0,0)(\startpoint-20:\endpoint+20:\radius)
+		%p_r
+		\draw[smallpropagator] (\zero+2.5*\step:\radius*1.1) to [bend left = 55] (\zero + 6.7*\step:\radius*1.1); 
+		%q
+		\draw[smallpropagator] (\zero+2.6*\step:\radius*1.1) to [bend left = 55] (\zero + 5.3*\step:\radius*1.1); 
+		%\draw[smallpropagator,light-gray] (\zero+7.5*\step:\radius*1.1) -- (0:\radius*0.25);  
+		\node at (\zero + 2.8*\step:\radius*0.8){\footnotesize $p_r$};
+		\node at (\zero + 4.7*\step:\radius*.84){\footnotesize $q$};
+	\end{scope}
+	% draw nodes
+	\newnode[left]{1}{i}
+	\newnode[below]{2}{a_r}
+	\newnode[below]{3}{}
+	\newnode[right]{8}{j_m}
+	% case label
+	\node at (270:\radius*0.1) {\em all vertices of $p_r$ lie between $a_r-1$ and $j_m$};
+\end{scope}
+\end{tikzpicture} \qquad \qquad \begin{tikzpicture}[baseline=(current bounding box.east)]
+\begin{scope}
+	\drawWLDfragment[8]{3}{0.3} % draw arc
+	%\drawnumbers % use this to debug
+	% highlight region
+		% scope to draw props and their labels
+	\begin{scope}
+		\clipcenterarc(0,0)(\startpoint-20:\endpoint+20:\radius)
+		%random prop preventing p_s from contributing a_s-1
+		\draw[smallpropagator,gray] (\zero+2.3*\step:\radius) -- (\zero + 16.5*\step:\radius) ;
+		%p_s
+		\draw[smallpropagator] (\zero+2.4*\step:\radius*1.1) to [bend left = 55] (\zero + 7.5*\step:\radius*1.1); 
+		%p_r
+		\draw[smallpropagator] (\zero+2.5*\step:\radius*1.1) to [bend left = 70] (\zero + 4.5*\step:\radius*1.1); 
+		%q
+		\draw[smallpropagator] (\zero+4.55*\step:\radius*1.1) to [bend left = 70] (\zero + 6.7*\step:\radius*1.1); 
+		\node at (\zero + 4.5*\step:\radius*0.55){\footnotesize $p_s$};
+		\node at (\zero + 3.5*\step:\radius*0.84){\footnotesize $p_r$};
+		\node at (\zero + 6.2*\step:\radius*0.85){\footnotesize $q$};
+	\end{scope}
+	% draw nodes
+	\newnode[left]{1}{i}
+	\newnode[below]{2}{}
+	\newnode[below]{3}{a_s}
+	\newnode[below]{4}{a_r}
+	\newnode[below]{5}{}
+	\newnode[right]{8}{j_m}
+	% case label
+	\node at (270:\radius*0.1) {\em all vertices of $p_r$ do not lie between $a_r-1$ and $j_m$};
+\end{scope} 
+\end{tikzpicture} }\eas
+\caption{The two cases of the induction step. Note that $I_i(p_s) <_i I_i(p_r)$}\label{fig:awkward induction step}
 \end{figure}
 
-Now repeat the argument above with $p_s$ in place of $p_r$: if the other end of $p_s$ lands on an edge between $q$ and $j_m$ then we have $q \in \cP_{m-1}$ as above; if not then there exists some $p_t \in Q_{l-3}$ with $p_s$ supported on $I_i(p_t)$ and $I_i(p_t) <_i I_i(p_r)$.
+\
+Now repeat the argument above with $p_s$ in place of $p_r$: if the other end of $p_s$ lands on an edge between $q$ and $j_m$ then we have $q \in \cP_{m-1}$ as above; if not then there exists some $p_t \in Q_{l-3}$ with $p_s$ supported on $I_i(p_t)$ and \hlfix{$I_i(p_t) <_i I_i(p_r)$}{$I_i(p_t) <_i I_i(p_s)<_i I_i(p_s)$?
+Or is the implication clear enough not to be mentioned}.
 Since there are finitely many steps this process can take before reaching $Q_0$, and any $p_* \in Q_0  = \Prop(j_m)$ has $j_m$ in its support by definition, this argument eventually terminates with the construction of a propagator constraining the positioning of $q$ as required.

### 2019-08-10 GWLDCI.tex
fixed my thanks

@@
 \title{Combinatorics of the geometry of Wilson loop diagrams I: equivalence classes via matroids and polytopes}
-\author{Susama Agarwala\thanks{SA was supported by an ONR grant.}, Si\^an Fryer, and Karen Yeats\thanks{KY is supported by an NSERC Discovery grant, by the Canada Research Chair program, and though some the time this work was developed also by a Humboldt Fellowship from the Alexander von Humboldt foundation.}}
+\author{Susama Agarwala\thanks{SA was partially supported by an Office of Naval Research grant.}, Si\^an Fryer, and Karen Yeats\thanks{KY is supported by an NSERC Discovery grant, by the Canada Research Chair program, and though some the time this work was developed also by a Humboldt Fellowship from the Alexander von Humboldt foundation.}}
 %\date{}

### 2019-08-12 GWLDCI.tex
paper 1 abstract minor tweaks

@@
 \begin{abstract}
-  Wilson loop diagrams, an important tool in studying scattering amplitudes of SYM $N=4$ theory, are known by previous work to be associated to positroids.
-We characterize when two Wilson loop diagrams give the same positroid, prove that an important subclass of subdiagrms (exact subdiagrams) correspond to uniform matroids and enumerate the number of different Wilson loop diagrams that correspond to each positroid cell.
+  Wilson loop diagrams are an important tool in studying scattering amplitudes of SYM $N=4$ theory and are known by previous work to be associated to positroids.
+We characterize the conditions under which two Wilson loop diagrams give the same positroid, prove that an important subclass of subdiagrams (exact subdiagrams) correspond to uniform matroids, and enumerate the number of different Wilson loop diagrams that correspond to each positroid cell.
 We also give a correspondence between those positroids which can arise from Wilson loop diagrams and directions in associahedra.

### 2019-08-12 GWLDCII.tex
paper 2 readthrough, sections 1 through 4

@@
 % for highlighting regions of a diagram edge
-\tikzstyle{linehighlight}=[red,line width = 3pt,line cap = round, draw opacity = 0.5]
+\tikzstyle{linehighlight}=[blue,line width = 3pt,line cap = round, draw opacity = 0.5]
 
@@
 
-This paper is the second in a two part series investigating the combinatorics and geometry underlying SYM $N=4$ theory.
-This series lays out several results about the relationship between the Wilson loop diagrams and the positroid cells that give a CW complex structure to the positive Grassmanian.
-This paper is concerned with identifying which positroid cells correspond to which Wilson loop diagrams, and how this translates to a geometric tiling of a subspace of the positive Grassmannians.
+This paper is the second in a two part series investigating the combinatorics and geometry underlying Wilson loop diagrams in SYM $N=4$ theory.
+This series lays out several results about the relationship between Wilson loop diagrams and the positroid cells that give a CW complex structure to the positive Grassmanian.
+This paper is concerned with identifying which positroid cells correspond to which Wilson loop diagrams, and how this translates to a geometric tiling of a subspace of the positive Grassmannian.
 
@@
 In contrast, the first paper in this series focuses on combinatorial and matroidal properties of the Wilson loop diagrams.
-The main focus of that paper is to enumerate (without identifying) the positroid cells that associated to Wilson loop diagrams with a fixed number of vertices and propagators, as well as counting the number of Wilson loop diagrams in the pre-image of any positroid cell under this association.
+The main focus of that paper is to enumerate the positroid cells that are associated to Wilson loop diagrams with a fixed number of vertices and propagators, as well as counting the number of Wilson loop diagrams in the pre-image of \hlfix{any positroid cell under this association.}{I'd like to mildly rephrase this because it sounds like we know exactly which cells have non-empty pre-image, which isn't quite what we proved.}
 
@@
 Moreover, integrals associated to the BCFW diagrams define a volume form on the Amplituhedron.
-This both gives a novel and elegant interpretation of scattering Amplitudes for this theory, as well as a means of simplifying the calculations greatly from traditional Feynman diagram approaches.
+This both gives a novel and elegant interpretation of scattering amplitudes for this theory, as well as a means of greatly simplifying the calculations involved in traditional Feynman diagram approaches.
 Since then, there has been significant work to understand the volume form and its physical implications \cite{UnwindingAmplituhedron,galashinlam}.
@@
 As with the Amplituhedron, each Wilson loop represents the sum of a family of $N^kMHV$ Feynman diagrams, and adding up the corresponding sums of Feynman integrals associates a volume form to a convex space different from the Amplituhedron \cite{Hodges2013}.
-The first author and Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that can be realized as an element of $\Gr(k,n)$ \cite{wilsonloop}, while other work has shown a connection between the space parametrized by Wilson loop diagrams and the Amplituhedron \cite{casestudy, Amplituhedronsquared}.
+Agarwala and Marin-Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that can be realized as an element of $\Gr(k,n)$ \cite{wilsonloop}, while other work has shown a connection between the space parametrized by Wilson loop diagrams and the Amplituhedron \cite{casestudy, Amplituhedronsquared}.
 
 In the above work and elsewhere, it is clear that while the space parametrized by the Wilson loop diagrams is related to the Amplituhedron, they are not the same space.
-For instance, it is conjectured that the Amplituhedron is orientable, whereas the first author and Marcott show in \cite{non-orientable} that the space parametrized by the Wilson loop diagrams can be seen as a non-orientable vector bundle over some submanifold of $\Gr(k,n)$.
-Furthermore, the cells associated to the Wilson loop diagrams are different from the cells associated to BCFW diagrams, as one sees from counting arguments in comparing the results of \cite{AmplituhedronDecomposition} and \cite{casestudy}.
-This is not too alarming, as it is conjectured the space parametrized by the Wilson loop diagrams to project down to something close to the Amplituhedron \cite{wilsonloop, Amplituhedronsquared}.
+For instance, it is conjectured that the Amplituhedron is orientable, whereas Agarwala and Marcott show in \cite{non-orientable} that the space parametrized by the Wilson loop diagrams can be seen as a non-orientable vector bundle over some submanifold of $\Gr(k,n)$.
+Furthermore, the cells associated to the Wilson loop diagrams are different from the cells associated to BCFW diagrams, which can be seen by comparing the results of \cite{AmplituhedronDecomposition} and \cite{casestudy}.
+This is not too alarming, as it is conjectured that the space parametrized by the Wilson loop diagrams will project down to something close to the Amplituhedron \cite{wilsonloop, Amplituhedronsquared}.
 
 This paper continues this work by identifying which positroid cells are associated to which Wilson loop diagram: specifically, we give an algorithm to read off the Grassmann necklace of the associated positroid cell from the Wilson loop diagram.
-We also show that the positroid cells associated to Wilson loop diagrams are all $3k$ dimensional; by contrast, the BCFW cells are all $4k$ dimensional \cite{Arkani-Hamed:2013jha}.
+We also show that the positroid cells associated to Wilson loop diagrams are all $3k$-dimensional; by contrast, the BCFW cells are all $4k$-dimensional \cite{Arkani-Hamed:2013jha}.
 Again, this is not too alarming, as it was shown in \cite{non-orientable} that the actual geometric space parametrized by the Wilson loop diagrams is a non-orientable $k$-dimensional bundle over this $3k$ dimensional manifold in $\Gr(k,n)$.
@@
 As noted above, the sum of the Feynman integrals associated to Wilson loop diagrams gives the volume of a convex polytope; if this volume is to be finite, then any singularities appearing in individual integrals must cancel out in the overall sum.
-This has been conjectured in general \cite{Hodges2013} and verified explicitly in a few cases \cite{casestudy, HeslopStewart}, but it is hard to prove in general due to the fact that the relationship between Wilson loop diagrams and $3k$ dimensional positroid cells of $\Gr(k,n)$ is neither one-to-one nor onto.
+This has been conjectured in general \cite{Hodges2013} and verified explicitly in a few cases \cite{casestudy, HeslopStewart}, but it is hard to prove in general due to the fact that the relationship between Wilson loop diagrams and $3k$-dimensional positroid cells of $\Gr(k,n)$ is neither one-to-one nor onto.
 In this paper, we give a characterization of the factors appearing in the denominator of these Feynman integrals in terms of the Grassmann necklace of the associated positroid, thus providing a much simpler and more tractable link between the singularities and the diagrams.
@@
 While it was already possible to construct the Grassmann necklace of a Wilson loop diagram via existing bijections between some of the various combinatorial objects that index the positroid cells, this process was convoluted and involved multiple steps; our algorithm allows us to track directly how each propagator in the Wilson loop diagram contributes to each term in the Grassmann necklace.
-Many of the technical lemmas required to prove Theorem~\ref{res:alg gives GN} continue to be important in subsequent sections: in particular we have Lemma~\ref{lem sian}, which identifies certain configurations of propagators which must appear in any admissible Wilson loop diagram, and Lemma~\ref{vertex cyclic int lem}, which shows that the pattern of values that a propagator contributes to each term of the Grassmann necklace is both simple and predictable.
+Many of the technical lemmas required to prove Theorem~\ref{res:alg gives GN} continue to be important in subsequent sections: in particular we have Lemma~\ref{lem sian}, which identifies certain configurations of propagators that must appear in any admissible Wilson loop diagram, and Lemma~\ref{vertex cyclic int lem}, which shows that the pattern of values that a propagator contributes to each term of the Grassmann necklace is both simple and predictable.
 
@@
 Thus the zero entries in row $p$ correspond to the external particles that the propagator $p$ does not interact with.
-See \ref{integraldetails} for an example of a diagram $W$ and its associated matrix.
-
-The matrix $C(W)$ can be interpreted as a parametrization of the positroid cell in the positive Grassmannian $\Gr(n, |\cP|)$ associated to the $W$, which we denote by $\Sigma(W)$ \cite{wilsonloop}.
-Most of the work in this paper, and in \cite{generalcombinatoricsI} focuses on characterizing the positroid cell assoicated to eash Wilson loop diagram $W$.
+See Example~\ref{integraldetails} for an example of a diagram $W$ and its associated matrix.
+
+The matrix $C(W)$ can be interpreted as a parametrization of the positroid cell associated to $W$ in the positive Grassmannian $\Gr(n, |\cP|)$, which we denote by $\Sigma(W)$ \cite{wilsonloop}.
+Most of the work in this paper, and in \cite{generalcombinatoricsI} focuses on characterizing the positroid cell associated to each Wilson loop diagram $W$.
 
@@
 One may also interpret the functional $I(W)$ as associating a volume to each cell $\Sigma(W)$ \cite{wilsonloop, Amplituhedronsquared, HeslopStewart}.
-The volume form is written in terms of the elements of $C(W)$ as  \[ \Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V_{p_r}} \textrm{d}c_{p_r}}{R(W)} \;.
-\]
+The volume form is written in terms of the elements of $C(W)$ as  \begin{equation} \label{eq:omega(W) def}\Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V_{p_r}} \textrm{d}c_{p_r}}{R(W)} \;, \end{equation}
+where the denominator $R(W)$ is given in Definition~\ref{def R(W)} below.
 The interested reader is referred to \cite{Adamo:2012xe,HeslopStewart,LipsteinMason} for more information about the volume form.
@@
 By \cite{Adamo:2011pv,Adamo:2012xe,Arkani-Hamed:2013jha} this sum is finite for all sets of external particles, i.e.
-we have \bas \mathcal{A}_{k, n}^{tree} = \sum_{(\cP, [n]), |\cP| = k} I(W) <\infty.
-\eas
+we have
+\bas \mathcal{A}_{k, n}^{tree} = \sum_{\substack{W = (\cP, [n]), \\ |\cP| = k}} I(W) <\infty. \eas
 
 In particular, this implies that any singularities in the integrals $I(W)$ must cancel out in the sum.
-In particular, they must cancel on the boundaries of the positroid cells $\Sigma(W)$, analogous to the analysis in \cite{Arkani-Hamed:2013jha}.
+Specifically, they must cancel on the boundaries of the positroid cells $\Sigma(W)$, analogous to the analysis in \cite{Arkani-Hamed:2013jha}.
 This has been checked for particular classes of examples (e.g.
@@
 Let $W = (\cP,V)$ be an admissible Wilson loop diagram, and fix an edge $e$.
-Let $\{p_1 \ldots p_r\}$ be the propagators with one end lying on edge $e$, ordered so that $p_1$ is closest to the vertex $e$, $p_r$ closest to $e+1$, and $p_i$ is closer to $e$ than $p_{i+1}$ is.
-Define
+Let $\{p_1 \ldots p_r\}$ be the propagators with one end lying on edge $e$, ordered so that $p_1$ is closest to the vertex $e$, $p_r$ is closest to $e+1$, and $p_i$ is closer to $e$ than $p_{i+1}$ is.
+Define the polynomial
 \[ R_e =  c_{p_1,e+1} \prod_{j= 1}^{r-1} \left((c_{p_j,e} c_{p_{j+1},e+1} - c_{p_{j+1},e} c_{p_{j},e+1} ) \right) c_{p_r,e}\;\]
@@
 In Section \ref{sec poles}, we show that the denominator $R(W)$ is determined by the positroid cell $\Sigma(W)$ and the structure of $W$, as encapsulated by $C(W)$.
-In fact, it can be read directly off of $C(W)$, in terms of characterization of $\Sigma(W)$ called the Grassmann necklace (see Definition~\ref{def:grassmann necklace}).
+In fact, it can be read directly off of $C(W)$, in terms of a characterization of $\Sigma(W)$ called the Grassmann necklace (see Definition~\ref{def:grassmann necklace}).
 We also give an algorithm to read $R(W)$ directly from the Wilson loop diagram, paving the way for a general study of these poles in future.
@@
 
-To calculate $R(W)$, write \bmls R_1 = c_{1,1} c_{1, 2}\quad R_2 = c_{2,2} c_{2,3} \quad R_4 = c_{2,5} (c_{2,4}c_{1,5} - c_{2,5}c_{1,4})c_{1,4} \\ R_5 = c_{4,6} (c_{4,5}c_{3,6} - c_{3,5}c_{4,6})c_{3,5} \quad R_7 = c_{3,7} c_{3,8} \quad R_8 = c_{4,8} c_{4,1} \;.\emls All other $R_e$ are $1$.
-Finally, the integrand associated to this Wilson loop diagram is \bas \Omega(W) = \frac{\textrm{d}c_{1,1}\textrm{d}c_{1,2}\textrm{d}c_{1,4}\textrm{d}c_{1,5}\textrm{d}c_{2,2}\textrm{d}c_{2,3}\textrm{d}c_{2,4}\textrm{d}c_{2,5}\textrm{d}c_{3,5}\textrm{d}c_{3,6}\textrm{d}c_{3,7}\textrm{d}c_{3,8}\textrm{d}c_{4,5}\textrm{d}c_{4,6}\textrm{d}c_{4,8}\textrm{d}c_{4,1}}{c_{1,1} c_{1, 2}c_{2,2} c_{2,3}c_{2,5} (c_{2,4}c_{1,5} - c_{2,5}c_{1,4})c_{1,4}c_{4,6} (c_{4,5}c_{3,6} - c_{3,5}c_{4,6})c_{3,5}c_{3,7} c_{3,8}c_{4,8} c_{4,1}} \;.
+To calculate $R(W)$, we first compute the polynomials associated to each edge of $W$: \bmls R_1 = c_{1,1} c_{1, 2}\quad R_2 = c_{2,2} c_{2,3} \quad R_4 = c_{2,5} (c_{2,4}c_{1,5} - c_{2,5}c_{1,4})c_{1,4} \\ R_5 = c_{4,6} (c_{4,5}c_{3,6} - c_{3,5}c_{4,6})c_{3,5} \quad R_7 = c_{3,7} c_{3,8} \quad R_8 = c_{4,8} c_{4,1} \;.\emls All other $R_e$ are $1$.
+Finally, the integrand associated to this Wilson loop diagram (recall equation~\eqref{eq:omega(W) def}) is \bas \Omega(W) = \frac{\textrm{d}c_{1,1}\textrm{d}c_{1,2}\textrm{d}c_{1,4}\textrm{d}c_{1,5}\textrm{d}c_{2,2}\textrm{d}c_{2,3}\textrm{d}c_{2,4}\textrm{d}c_{2,5}\textrm{d}c_{3,5}\textrm{d}c_{3,6}\textrm{d}c_{3,7}\textrm{d}c_{3,8}\textrm{d}c_{4,5}\textrm{d}c_{4,6}\textrm{d}c_{4,8}\textrm{d}c_{4,1}}{c_{1,1} c_{1, 2}c_{2,2} c_{2,3}c_{2,5} (c_{2,4}c_{1,5} - c_{2,5}c_{1,4})c_{1,4}c_{4,6} (c_{4,5}c_{3,6} - c_{3,5}c_{4,6})c_{3,5}c_{3,7} c_{3,8}c_{4,8} c_{4,1}} \;.
 \eas
@@
 A characterization of all bases of the positroid in terms of the Grassmann necklace and the Gale order was given by Oh in \cite[Theorem 8]{Oh}: if $(I_1, \dots, I_n)$ is the Grassmann necklace associated to a positroid $M = ([n],\cB)$, then the bases of $M$ are exactly
-\ba \cB = \left\{J \in \binom{[n]}{k}\ |\ I_i \gale{i} J \ \forall i \in [n]\right\}. \label{basesofmatroids}\ea
+\ba \cB = \left\{J \in \binom{[n]}{k}\ \Big|\ I_i \gale{i} J \ \ \forall i \in [n]\right\}. \label{basesofmatroids}\ea
 Thus the Grassmann necklace is well suited to testing whether a given $k$-set is a basis for $M$, and for generating a list of all bases of $M$.
@@
 \begin{dfn}\label{def:le diagram}
-A {\bf Le diagram} is a Young diagram in which every square contains either a $+$ or a $0$, subject to the rule that if a square contains a $0$ then either all squares to its left (in the same row) must also contain a $0$, or all squares above it (in the same column) mustbasesofmatroids\ also contain a $0$, or both.
+A {\bf Le diagram} is a Young diagram in which every square contains either a $+$ or a $0$, subject to the rule that if a square contains a $0$ then either all squares to its left (in the same row) must also contain a $0$, or all squares above it (in the same column) must also contain a $0$, or both.
 \end{dfn}
@@
 
-Let $W = (\cP,[n])$ be an admissible Wilson loop diagram with $k$ propagators, and $C(W)$ the associated matrix defined in \eqref{C(W) dfn}.
+Let $W = (\cP,[n])$ be an admissible Wilson loop diagram with $k$ propagators, and $C(W)$ the associated matrix defined in equation~\eqref{C(W) dfn}.
 Let $M(W)$ be the matroid realized by $C(W)$, i.e.
@@
 
-In \cite{wilsonloop}, Agarwala and Amat show that $M(W)$ is also characterized by the Wilson loop diagram itself:
+In \cite{wilsonloop}, Agarwala and Marin-Amat show that $M(W)$ is also characterized by the Wilson loop diagram itself:
 
@@
 
-Forgetting about the matroid and simply thinking about the condition of linear independence in the matrix $C(W)$, the corollary can also be proved directly by linear algebra and the definition of $C(W)$ as follows: because the nonzero entries of $C(W)$ are independent indeterminants, $J$ is an independent set is if and only if there is some choice of $|J|$ nonzero entries of $C(W)$ one in each row associated to an element of $J$ and each in different columns.
+  Alternatively if we forget about the matroid and simply think about the condition of linear independence in the matrix $C(W)$, the corollary can also be proved directly by linear algebra and the definition of $C(W)$ as follows.
+
+  Because the nonzero entries of $C(W)$ are independent indeterminants, $J$ is an independent set if and only if there is some choice of $|J|$ nonzero entries of $C(W)$ one in each row associated to an element of $J$ and each in different columns.
 Each entry in $C(W)$ identifies a propagator by the row of the entry and a vertex by the column of the entry.
@@
 
-By relating the behavior of the propagators in $W$ to the matroidal properties of $M(W)$, Agarwala and Amat also showed that $M(W)$ is in fact a positroid whenever $W$ is admissible \cite[Corollary 3.39]{wilsonloop}.
+By relating the behavior of the propagators in $W$ to the matroidal properties of $M(W)$, Agarwala and Marin-Amat also showed that $M(W)$ is in fact a positroid whenever $W$ is admissible \cite[Corollary 3.39]{wilsonloop}.
 
 However, in order to identify the positroid associated to a given Wilson loop diagram $W$ we first have to construct $C(W)$, then make a list of all its non-zero $k\times k$ minors and extract the Le diagram or Grassmann necklace via the methods described in Section~\ref{sec:positroid background}.
-Alternatively, one could obtain the decorated permutation of the positroid from $C(W)$ as in \hlfix{[ref]}{Sian needs to go find this reference} and then convert it into a Grassmann necklace as described in \cite[Section 16]{Postnikov}.
-
 In \cite{casestudy}, Agarwala and Fryer apply this process in the smallest non-trivial case: admissible Wilson loop diagrams with two propagators on six vertices.
@@
 
-We will inductively construct a sequence of propagators $p_r$ and $q_r$, with $\ell(p_r) = 2$ for each $r$ and either:
+We will inductively construct a sequence of propagators $p_r$ and $q_r$, with $\ell(p_r) = 2$ for each $r$ and such that either:
 \begin{itemize}
@@
 \node[align = center] at (\zero +1.7*\step:\radius*1.4) {\footnotesize \em 0, 1, or 2 \\ \footnotesize \em vertices in \\ \footnotesize \em this region};
-\node at (\zero + 10*\step:\radius*0.3) {$\cP_{in}(q_1)$};
+\node[gray] at (\zero + 10*\step:\radius*0.4) {\footnotesize$\cP_{in}(q_1,<_{i_1})$};
+\node[gray] at (\zero + 6.5*\step:\radius*0.8) {\footnotesize $\cP_{out}(q_1,<_{i_1})$};
 \end{scope}
@@
 Note that we could replace $q_r$ by another propagator $q'_{r}$ in $W_r$, as long as $p_{r+1}$ and $q_r$ are on opposite sides of $q_r'$: such a new $q'_{r}$ would still satisfy all of the induction hypotheses.
-Therefore without loss of generality we may assume that $\cP_{in}(q_r)$ does not contain any propagators (other than $q_r$ itself) which satisfy the induction hypotheses, i.e.
+(See Figure~\ref{fig smallest q in lem sian}.) Therefore without loss of generality we may assume that $\cP_{in}(q_r)$ does not contain any propagators (other than $q_r$ itself) which satisfy the induction hypotheses, i.e.
 we assume that there are no other propagators with $p_{r+1}$ on one side and $q_r$ on the other.
 
-\begin{figure}
+\begin{figure}[h]
+\vspace{1cm}
 \[
@@
 \]
-\caption{We can replace $q_r$ with $q'_r$ as long as the conditions of the induction hypothesis remain satisfied.}
+\caption{We can replace $q_r$ with $q'_r$ as long as $q_r$ and $p_{r+1}$ are on opposite sides of $q'_r$.}
 \label{fig smallest q in lem sian}
@@
 \begin{algorithm}\label{alg:put GN on WLD}
-Let $W = (\cP, [n])$ be an admissible Wilson loop diagram. This gives an algorithm for constructing the set $I_i^W$ (or just $I_i$ when $W$ is clear from context), for $i \in [n]$.
+Let $W = (\cP, [n])$ be an admissible Wilson loop diagram. In order to construct the set set $I_i^W$ (or just $I_i$ when $W$ is clear from context) for $i \in [n]$, perform the following steps:
 
@@
 
-{\color{violet}
-Each $I_i$ also imposes an ordering on the propagators, determined by when the propagator contributes to the sequence:
-\begin{dfn} \label{proporderingdfn}
-The ordering of the propagators on $W = (\cP, [n])$ defined by $I_i^W$ is $\cP = \{p_1, \ldots p_k\}$, where 
-\[I_i = \{I_i(p_1) <_i I_i(p_2) <_i \ldots <_i I_i(p_k)\}.\]
-(The superscript $W$ is omitted here to simplify the notation.)\note{Sian tweaked this slightly to emphasise the $<_i$ order, because standard convention in most papers is to write all GN terms in the 1-order.}
-\end{dfn}
-
-Since each propagator is removed by the algorithm after it contributes, each propagator contributed exactly once to $I^W_i$, making the above ordering well defined.}
+% Sian deleted the propagator ordering for now: since we only use it in one proof, we can make it a local definition.
+% Obviously if we find ourselves using it elsewhere we can bring this definition back. (If so, uncomment the line in the following example as well.)
+
+% {\color{violet}
+% Each $I_i$ also imposes an ordering on the propagators, determined by when the propagator contributes to the sequence:
+% \begin{dfn} \label{proporderingdfn}
+% The ordering of the propagators on $W = (\cP, [n])$ defined by $I_i^W$ is $\cP = \{p_1, \ldots p_k\}$, where 
+% \[I_i = \{I_i(p_1) <_i I_i(p_2) <_i \ldots <_i I_i(p_k)\}.\]
+% (The superscript $W$ is omitted here to simplify the notation.)\note{Sian tweaked this slightly to emphasise the $<_i$ order, because standard convention in most papers is to write all GN terms in the 1-order.}
+% \end{dfn}
+
+% Since each propagator is removed by the algorithm after it contributes, each propagator contributed exactly once to $I^W_i$, making the above ordering well defined.}
 
@@
 	\drawnumbers
-	\drawlabeledprop{1}{0}{4}{0}{\footnotesize $q\ $}
+	\drawlabeledprop{1}{0}{4}{0}{\footnotesize $q$ \quad}
 	\drawlabeledprop{2}{0}{4}{-1}{\footnotesize  $p$}
-    \drawlabeledprop{5}{0}{8}{0}{\footnotesize $r\ \ $}
-    \drawlabeledprop{5}{1}{7}{0}{\footnotesize $\ \ \ s$}
-
+    \drawlabeledprop{5}{0}{8}{0}{\footnotesize $r$ \ \ }
+    \drawlabeledprop{5}{1}{7}{0}{\footnotesize \quad \ $s$}
 		\end{scope}
@@
 There are no propagators left in the diagram, so the algorithm terminates and we have ${I_1 = \{1,2,3,5\}}$, or $1235$ for short. 
-So the propagators are ordered $r,q,p,s$ with respect to $I_1$, and $I_1$ viewed as a function is given by
+%So the propagators are ordered $r,q,p,s$ with respect to $I_1$, and 
+$I_1$ viewed as a function is given by
 \[I_1: \cP \longrightarrow [n] : \quad I_1(r) = 1,\quad I_1(q) = 2, \quad I_1(p) = 3, \quad I_1(s) = 5.\]
@@
 
- \note{Remember to keep an eye out when proofreading: do we just need the vertices appearing in the GN element to be the same or actually the function}
+ \note{Remember to keep an eye out when proofreading: do we just need the vertices appearing in the GN element to be the same, or do we actually need the functions to match up}
 
@@
 
-With that in mind we are ready to begin proving properties of the algorithm.
+With that in mind, we are ready to begin proving properties of the algorithm.
 We first show that the algorithm can never reach the final vertex in a propagator's support without having already assigned that propagator; in particular, this guarantees that the construction of $I_i$ always terminates in fewer than $n$ steps.
@@
 \begin{figure}
+
 \[
-\begin{tikzpicture}[baseline=(current bounding box.east)]
+\begin{tikzpicture}[baseline=(current bounding box.east),rotate = -18]
 	\begin{scope}
@@
       \draw[smallpropagator,light-gray] (\zero +\step *4.3:\radius*1) -- (90:\radius*0.5); 
-	\node at (270:\radius*1.5) {\em Case 1};
+	\node at (270+18:\radius*1.5) {\em Case 1};
 	% \begin{scope}
@@
 \qquad \qquad 
-	\begin{tikzpicture}[baseline=(current bounding box.east)]
+	\begin{tikzpicture}[baseline=(current bounding box.east),rotate = 36]
 	\begin{scope}
@@
 	\newnode[right]{16}{b+1 = I_i(p)}
-	\newnode[below]{11}{d}
+	\newnode[right]{11}{d}
 	\newnode[below]{12}{}
-	\newnode[above]{2}{i}
+	\newnode[left]{2}{i}
 	\newprop[midway,above]{4.5}{15.7}{\scriptsize $p$}
-		\node at (270:\radius*1.5) {\em Case 2};
+		\node at (270-36:\radius*1.5) {\em Case 2};
 	\begin{scope}
@@
 \label{fig:no fourth vertex}
-\end{figure}f
-
-In the left hand case, observe that we must have another propagator $q = (c,b)$ with $c<_i b$ and $I_i(q) = b+1$, because otherwise $I_i$ would assign $p$ to $b+1$.
-Now $q$ also contributes the $<_i$-maximal vertex in its support to $I_i$ and is an instance of the right hand case listed above.
-Therefore it suffices to show that no admissible Wilson loop diagram admits the configuration illustrated in the right hand case of Figure~\ref{fig:no fourth vertex}.
-
-So let $p = (a,b)$ with $a<_ib$ and $I_i(p) = b+1$, and choose $p$ such that $|[a+1,b]|$ is minimal amongst propagators of $W$ with this property.
+\end{figure}
+\note{Question: is the diagram clearer in this configuration (starting vertex $i$ matches up in both) or in the old configuration (propagator $p$ matches up)?}
+
+In Case 1, observe that we must have another propagator $q = (c,b)$ with $c<_i b$ and $I_i(q) = b+1$, because otherwise $I_i$ would assign $p$ to $b+1$.
+Now $q$ also contributes the $<_i$-maximal vertex in its support to $I_i$ and is an instance of Case 2.
+Therefore it suffices to show that no admissible Wilson loop diagram admits the configuration illustrated in Case 2 of Figure~\ref{fig:no fourth vertex}.
+
+So let $p = (a,b)$ with $a<_ib$ and $I_i(p) = b+1$, and choose $p$ such that $\big|[a+1,b]\big|$ is minimal amongst propagators of $W$ with this property.
 
@@
 If $W$ is an admissible Wilson loop diagram with $k$ propagators, then Algorithm~\ref{alg:put GN on WLD} assigns exactly $k$ distinct vertices to each $I_i$.
-\sanote{suddenly confused.
-Don't we need working about in going onely once around or somesuch?}\note{Sian: added the word ``distinct'' in the statement and a few words to the last line of the proof, does that help?}
 \end{cor}
@@
 Fix $i \in [n]$.
-It follows from the proof of Lemma~\ref{lem no fourth vertex} that in applying Algorithm~\ref{alg:put GN on WLD} to construct the set $I_i$, the algorithm can never reach the fourth vertex of a propagator's support (ordered with respect to $<_i$) without having already assigned $p$.
+It follows from the proof of Lemma~\ref{lem no fourth vertex} that in applying Algorithm~\ref{alg:put GN on WLD} to construct the set $I_i$, the algorithm can never reach the fourth vertex of a propagator's support (ordered with respect to $<_i$) without having already assigned that propagator.
 Therefore if the algorithm starts at vertex $i$, all propagators must have been eliminated by the time it gets to vertex $i-1$, ensuring that the algorithm is completed in less than one full circumnavigation of the diagram and that $I_i$ contains exactly $k$ distinct elements.
@@
 \[J_p^{W}(i) = \{m \in [n] \ | \ I^{W}_m(p) = i \},\]
-the set of starting vertices $m$ such that $I_m^{W}$ assigns $p$ to $i$.
+i.e. the set of starting vertices $m$ such that $I_m^{W}$ assigns $p$ to $i$.
 
@@
 \end{lem}
-\note{This proof needs to be updated to refer to the new figure (e.g. case 1 and 2 instead of ``leftmost two cases''); also check that all the vertices are labeled correctly}
 
@@
 \end{tabular}
-    \caption{Four cases for admissible WLDs with no non-supporting vertices.
-The green half-propagators illustrate where propagators may occur, but are not required to exist; no other regions illustrated may support additional propagators.}\label{fig 3 cases}
+    \caption{Four cases for admissible WLDs with no non-supporting vertices. The gray half-propagators illustrate where propagators may occur, but are not required to exist.}\label{fig 3 cases}
   \end{figure}
@@
 
-Consider the fourth case of Figure~\ref{fig 3 cases} first, as it is the easiest.
+Consider Case 4 of Figure~\ref{fig 3 cases} first, as it is the easiest.
 In this case, the vertices ${\{l,l+1,l+2,l+3\}}$ which support $p$ in $W$ are non-supporting in $V$, so for every propagator $r$ in $V$ (including $q$) we have $J_r^{V} = J_r^{W}$; these are non-empty cyclic intervals in the correct order by the induction hypothesis.
@@
 
-\begin{figure}
+\begin{figure}[h]
 \[
@@
 
-\textbf{Left two cases}: These cases behave essentially identically (except when $j$ or $j+1$ are not in the support of $p$, which can occur in the second case only; see below) so we handle the majority of the proof for these two cases simultaneously.
+\textbf{Cases 1 and 2}: These cases behave essentially identically (except when $j$ or $j+1$ are not in the support of $p$, which can occur in Case 2 only; see below) so we handle the majority of the proof for these two cases simultaneously.
 Write $p=(m,m+2)$ where $m\in \{i, i+1, l\}$.
 Let $1\leq a\leq 3$ be the number of non-supporting vertices inside $q$ in $V$ (note that there is at least 1); so these vertices are $l, \ldots, l+a-1$.
-Note that these non-supporting vertices are all in the support of $p$.
+Note that these vertices are non-supporting in $V$ but are all in the support of $p$ in $W$.
 
@@
        \]
-If $j$ is not in the support of $p$, then we must be in the second case of Figure~\ref{fig 3 cases} with two vertices in the right hand region.
+If $j$ is not in the support of $p$, then we must be in Case 2 of Figure~\ref{fig 3 cases} with two vertices in the right hand region.
 In this case, if we start the algorithm at $j$ we need to know whether there will be any unassigned propagators other than $p$ when we reach vertex $i$, so as to know what $p$ contributes.
 
-Consider the Wilson loop diagram $X$ formed from $V$ by replacing the propagator $q = (i,j)$ with $q = (i, j-1)$; \note{Added a note about $V$ being admissible when we defined it, so we can use $X$ admissible here without comment} $X$ is still admissible since we have not decreased the support of any set of propagators.
+Consider the Wilson loop diagram $X$ formed from $V$ by replacing the propagator $q = (i,j)$ with $q = (i, j-1)$;  $X$ is still admissible since we have not decreased the support of any set of propagators.
 % From the diagram we can see that $J_{j}^{V}(r) = J_{j}^{X}(r)$ for all $r\neq p$ (and in particular for $r=q$) and $J_{j}^{X}(r) = J_{j+1}^{X}(r)$ for $r\neq q,p$.  
@@
     \]
-We can now describe the intervals $J^{W}_r(*)$ for the first two cases of Figure~\ref{fig 3 cases}.
+We can now describe the intervals $J^{W}_r(*)$ for Cases 1 and 2 of Figure~\ref{fig 3 cases}.
 For $r \neq p$ the intervals are clearly still cyclic and appear in the correct order, and we can assemble the intervals for the $J_p^{W}(*)$ as follows.
@@
 
-\textbf{Third case}: In this case there are no non-supporting vertices $l, l+1, \ldots$ inside $q$.
+\textbf{Case 3}: In this case there are no non-supporting vertices $l, l+1, \ldots$ inside $q$.
 Again write $p=(m, m+2)$ where $m\in \{j, j+1, j+2\}$.
@@
 We are now ready to prove that Algorithm~\ref{alg:put GN on WLD} does in fact give the Grassmann necklace of the positroid associated to $W$.
+We do this in two parts: Theorem~\ref{res:alg gives GN} verifies that the sets $(I_1,\dots,I_n)$ obtained from the algorithm do form a Grassmann necklace, and Theorem~\ref{res alg gives correct GN} proves that this Grassmann necklace defines the positroid $M(W)$.
 
 \begin{thm}\label{res:alg gives GN}
-The sequence of $k$-subsets $(I_1,\dots,I_n)$ obtained by applying Algorithm~\ref{alg:put GN on WLD} to all vertices of an admissible diagram $W$ is exactly the Grassmann necklace of $M(W)$.
+The sequence of $k$-subsets $(I_1,\dots,I_n)$ obtained by applying Algorithm~\ref{alg:put GN on WLD} to all vertices of an admissible diagram $W$ is a Grassmann necklace.
 \end{thm}
 \begin{proof}
+\note{Sian replaced ``counterclockwise'' with ``clockwise'' in a couple of places in this proof: someone please doublecheck?}
 For each $i \in [n]$, let $I_i$ be the set of vertices assigned to the propagators of $W$ by Algorithm~\ref{alg:put GN on WLD} with starting vertex $i$.
 By Lemma~\ref{GN alg well defined}, we know that $|I_i| = k$ for each $i \in [n]$.
-We first prove that $I_{i+1} \supseteq I_i \backslash \{i\}$ for all $i \in [n]$; this is equivalent to the definition of Grassmann necklace given in Definition~\ref{def:grassmann necklace}.
+We prove that $I_{i+1} \supseteq I_i \backslash \{i\}$ for all $i \in [n]$; this is equivalent to the definition of Grassmann necklace given in Definition~\ref{def:grassmann necklace}.
 
@@
 (If $p$ is supported on $i+1$, then $b= i+1$ and the interval $[i+1,b-1]$ is empty.) Furthermore, by Lemma~\ref{vertex cyclic int lem} it must happen that $p$ contributes vertex $b$ to $I_{i+1}$, as otherwise $b$ would never be contributed by $p$.
-Consequently, in building $I_{i+1}$, when the algorithm reaches vertex $b$ there cannot be any remaining unassigned propagators that are supported on $b$ and counterclockwise of $p$.
+Consequently, in building $I_{i+1}$, when the algorithm reaches vertex $b$ there cannot be any remaining unassigned propagators that are supported on $b$ and clockwise of $p$.
 This is also true in when the algorithm constructing $I_i$ reaches $b$, since the same propagators have been assigned beforehand.
@@
 \textbf{Case II}: Suppose $p$ has one end on edge $i$.
-Note that by assumption we have $I_i(p) = i$; this means that $p$ must be the counterclockwise-most propagator lying on edge $i$, and hence we must have $I_{i+1}(p) = i+1$ as well.
+Note that by assumption we have $I_i(p) = i$; this means that $p$ must be the clockwise-most propagator lying on edge $i$, and hence we must have $I_{i+1}(p) = i+1$ as well.
 Observe also that $m\geq_i i+2$ since $i+1\in I_{i+1}$.
@@
 Since $m \neq i+1$, we have $m\in I_{i+1}^{W'}\setminus\{i+1\}$ but $m\not\in I_{i+2}^{W'}$, contradicting the minimiality of $(W, i, m)$.
-
+This completes the proof.
 \end{proof}
 
-\begin{thm}
-The Grassmann necklace $(I_1 \ldots I_n)$ from Theorem~\ref{res:alg gives GN} is the Grassmann necklace for $M(W)$.
+\begin{thm}\label{res alg gives correct GN}
+The Grassmann necklace $(I_1 \ldots I_n)$ from Theorem~\ref{res:alg gives GN} is the Grassmann necklace of the positroid $M(W)$.
 \end{thm}
@@
 \item When $p_m$ contributes $I_i(p_m) = a_m$ to the Grassmann necklace, it must be the clockwise-most propagator (amongst those not yet assigned) that is supported on $a_m$ i.e.
-any other propagators supported by $a_m$ in $\cP \setminus \cP_{m-1}$ is inside $p_m$ in the $a_m-1$ ordering.
+any other propagator in $\cP \setminus \cP_{m-1}$ that is supported on $a_m$ must be inside $p_m$ in the $a_m-1$ ordering.
 \end{enumerate}
@@
 Since $\cP$ is finite, the sequence therefore stabilizes in finitely many steps when $Q_{l+1} = Q_l$.
-Let $Q = \cup_{l \geq 0} Q_l$ be this set of propagators.
+Let $Q := \cup_{l \geq 0} Q_l$ be this set of propagators.
 
@@
 Since $I_i(Q) \cup \{j_m\}$ only supports the propagators in $Q$ but has $|Q|+1$ vertices, it is a dependent set.
-Thus $J$ is a dependent set, and the Grassmann necklace $(I_1,\dots,I_n)$ constructed from $W$ does indeed define the positroid $M(W)$.
-
-We now proceed to prove $Q\subseteq \mathcal{P}_{m-1}$ by inductively proving $Q_l \subseteq \mathcal{P}_{m-1}$ for all $l \geq 0$.
+Thus $J$ is a dependent set as required, and the Grassmann necklace $(I_1,\dots,I_n)$ constructed from $W$ does indeed define the positroid $M(W)$.
+
+All that remains is to prove $Q\subseteq \mathcal{P}_{m-1}$, which we do by inductively proving $Q_l \subseteq \mathcal{P}_{m-1}$ for all $l \geq 0$.
 %If $Q_0 = \Prop(j_m) = \emptyset$ then $Q = \emptyset$, and $I_i(Q) \cup \{j_m\}= \{j_m\}$ is a single vertex supporting no propagators, and thus a dependent set. Otherwise,
-For the base case $Q_0 \subseteq \cP_{m-1}$ follows immediately from the first observation above that $\Prop(j_m) \subseteq \cP_{m-1}$
+The base case $Q_0 \subseteq \cP_{m-1}$ follows immediately from the first numbered observation above that $\Prop(j_m) \subseteq \cP_{m-1}$
 
@@
 By construction there is some propagator $p_r \in Q_{l-1}$ such that $p_r$ and $q$ are both supported on $I_i(p_r) = a_r$.
-If $q$ is clockwise of $p_r$ on vertex $a_r$ then we immediately have $q \in \cP_{m-1}$ as observed above.
+If $q$ is clockwise of $p_r$ on vertex $a_r$ then we immediately have $q \in \cP_{m-1}$ from the second numbered observation above.
 It remains to consider the case that $q$ is counter-clockwise of $p_r$ at $a_r$.
@@
 If the other end of $p_r$ (i.e.
-the end not supported on $a_r$) lies on an edge between $a_r$ and $j_m$ then since $q$ is inside $p_r$ with respect to $<_{a_r-1}$ we must have $V(q) \subseteq [a_r-1,j_m]$, and hence $q \in \cP_{m-1}$ by Lemma~\ref{lem no fourth vertex}.
+the end not supported on $a_r$) lies on an edge between $a_r$ and $j_m$, then since $q$ is inside $p_r$ with respect to $<_{a_r-1}$ we must have $V(q) \subseteq [a_r-1,j_m]$, and hence $q \in \cP_{m-1}$ by Lemma~\ref{lem no fourth vertex}.
 In particular, if $l=1$ then $p_r \in Q_{0} = \Prop(j_m)$ and we must be in this case.
@@
 \end{figure}
-
-\
 Now repeat the argument above with $p_s$ in place of $p_r$: if the other end of $p_s$ lands on an edge between $q$ and $j_m$ then we have $q \in \cP_{m-1}$ as above; if not then there exists some $p_t \in Q_{l-3}$ with $p_s$ supported on $I_i(p_t)$ and \hlfix{$I_i(p_t) <_i I_i(p_r)$}{$I_i(p_t) <_i I_i(p_s)<_i I_i(p_s)$?
-Or is the implication clear enough not to be mentioned}.
+Or is the implication clear enough not to be mentioned}\note{Nope: we just need $<_i I_i(p_r)$.
+$I_i(p_t) <_i I_i(p_r)$ certainly isn't obvious and may not be true}.
 Since there are finitely many steps this process can take before reaching $Q_0$, and any $p_* \in Q_0  = \Prop(j_m)$ has $j_m$ in its support by definition, this argument eventually terminates with the construction of a propagator constraining the positioning of $q$ as required.
-This completes the induction step, and hence the proof.
-
-\end{proof}
+This completes the induction step, and hence the proof.\end{proof}
 
@@
 The positroid cells associated to the Amplituhedron are of dimension $4|\cP|$.
-In \cite{non-orientable}, Marcott and the first author show that the dimension of the Deodhar component is $|\cP| +$ the dimension of associated positroid cell.
-In otherwords, the Deodhar component associated to a Wilson loop diagram is $4|\cP|$, showing that the geometry underlying the Wilson loop diagrams is consistent with the geometry underlying the Amplituhedron.
-
-Marcott in \hlfix{***cite this***}{highlighted for anyone skimming through} has a different proof of the dimension of the positroid cell assicated to a Wilson loop diagram, which is geometric and more elegant, but it is not easy to track the effect of a particular propagator.
+In \cite{non-orientable}, Agarwala and Marcott show that the dimension of the Deodhar component is
+\[|\cP| + \text{ the dimension of associated positroid cell}.\]
+In other words, the Deodhar component associated to a Wilson loop diagram is $4|\cP|$, showing that the geometry underlying the Wilson loop diagrams is consistent with the geometry underlying the Amplituhedron.
+
+Marcott in \hlfix{***cite this***}{highlighted for anyone skimming through} gives a different proof of the $3|\cP|$-dimensionality of $M(W)$ which is geometric and more elegant, but it is not easy to track the effect of a particular propagator.
 Our approach is much more explicit.
@@
 Recall that the dimension of a positroid cell is equal to the number of plusses in the associated Le diagram \cite[Theorem 6.5]{Postnikov}.
-By combining Algorithms~\ref{alg:put GN on WLD} and \ref{alg:GN to Le} (converting from WLD to Grassmann necklace to Le diagram) we explicitly describe the effect of adding another propagator to a Wilson loop diagram in terms of the plusses of the associated Le diagrams, and hence give a recursive proof of the $3|\cP|$-dimensionality of the cells.
+By combining Algorithms~\ref{alg:put GN on WLD} and \ref{alg:GN to Le} (converting from WLD to Grassmann necklace, and Grassmann necklace to Le diagram respectively) we explicitly describe the effect of adding another propagator to a Wilson loop diagram in terms of the plusses of the associated Le diagrams, and hence give a recursive proof of the $3|\cP|$-dimensionality of the cells.
 
 We start with several lemmas, of roughly increasing degree of technicality.
-Lemma \ref{lem uncovered} shows that non-supporting vertices corresopond to columns of $0$s in the associated Le diagram.
-The proof of Theorem \ref{thm dim} depends on being able to act on Wilson loop diagrams by elements of the dihedral group to position propagators in certain positions.
-Lemma \ref{lem dihedral} shows that the dihedral group action does not change the dimension of of the associated Le diagram.
+We begin by relating non-supporting vertices to columns of zeros in the Le diagram (Lemma \ref{lem uncovered}) and verifying that performing dihedral transformations on a Wilson loop diagram does not change the dimension of of the associated Le diagram (Lemma \ref{lem dihedral}).
 
 \begin{lem}\label{lem uncovered}
-
 Let $W$ be an admissible Wilson loop diagram with $k$ propagators, and with a vertex $i$ that supports no propagators.
@@
 \begin{lem}\label{lem good p}
-  Let $W$ be an admissible Wilson loop diagram with $n\geq 1$ propagators.  Then there is some dihedral transformation $W'$ of $W$ such that $W'$ has a propagator $p$ with the following properties.
+  Let $W$ be an admissible Wilson loop diagram with $n\geq 1$ propagators.
+Then there is some dihedral transformation of $W$ such that the resulting diagram $W'$ has a propagator $p$ with the following properties:
   \begin{itemize}
@@
 \end{lem}
-Note that since the first condition tells us that $p$ has nothing inside it then in the second condition if $q$ exists then $j<_ji<_jn-1$.
+Note that since the first condition tells us that $p$ has nothing inside it, if $q$ exists in the second condition then $j<_ji<_jn-1$.
 
@@
 
-Combining Lemmas \ref{lem uncovered}, \ref{lem dihedral}, and \ref{lem good p}, it therefore suffices to study the Le diagrams of weakly admissible Wilson loop diagrams with $F(\emptyset)  = \emptyset$, admitting one of the configurations described in Lemma \ref{lem good p} with propagators $p = (n-3, n-1)$ and $q= (n-5, n-3)$ (if $q$ exists) both of length 2.
+Combining Lemmas \ref{lem uncovered}, \ref{lem dihedral}, and \ref{lem good p}, it therefore suffices to study the Le diagrams of weakly admissible Wilson loop diagrams with $F(\emptyset)  = \emptyset$ and admitting one of the configurations described in Lemma \ref{lem good p}, with propagators $p = (n-3, n-1)$ and $q= (n-5, n-3)$ (if $q$ exists) both of length 2.
 See Figure~\ref{fig special p} for an illustration of the two possibilities.
@@
 Let $V$ be $W$ with $p$ removed.
-Then
+Then we can express $I_*^W$ in terms of $I_*^V$ as follows:
 
@@
 
+\begin{proof}
+The two possible cases for $W$ are illustrated in Figure~\ref{fig special p}.
+
+We first consider $I_1^{W}$, i.e.
+the set obtained by applying the Grassmann necklace algorithm to $W$ with starting vertex 1.
+Note that $n-3 \not\in I_1^{V}$: for Case 2 this is clear from the diagram (since Algorithm~\ref{alg:put GN on WLD} would assign $q$ no later than vertex $n-4$), while for Case 1 it follows from Lemma \ref{lem no fourth vertex}.
+Therefore when we start at vertex 1 and apply the Grassmann necklace algorithm to $W$, $p$ is the only remaining unassigned propagator when we reach vertex $n-3$, and so we have $ I_1^{W}(p) = n-3$ and $I_1^W = I_1^V\cup \{n-3\}$.
+
+Next consider $I_n^{W}$.
+From the figure we see that in both cases we have $I_n^{W}(p) = n$.
+At vertex 1 of the algorithm $I_n$, the unassigned propagators are exactly those that appear in $V$.
+Therefore the algorithm continues as in $I_1^{V}$ (recall Remark~\ref{rmk algorithm locally same} about locally identical propagator configurations), i.e.
+we have $I_n^{W} = I_1^{V} \cup \{n\}$.
+By a similar argument, we must have $I_{n-1}^{W} = I_n^{V} \cup \{n-1\}$.
+
+Now consider $I_{n-2}^{W}$.
+If $n-2\not\in I_{n-2}^{V}$ (i.e.
+the vertex $n-2$ supports no propagators in $V$), then ${I_{n-2}^W(p) = n-2}$ and this assignment of $p$ does not affect the rest of the construction of $I_{n-2}^{V}$, so we obtain ${I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-2\}}$ as above.
+
+On the other hand, if $n-2\in I_{n-2}^{V}$ then we must be in Case 2 of Figure~\ref{fig special p} and $I_{n-2}^V(q) = I_{n-2}^W(q) = n-2$ (since $q$ is always the clockwise-most propagator supported on vertex $n-2$; see Figure~\ref{fig special p}).
+If $n-1 \not\in I_{n-2}^{V}$, then $I_{n-2}^W(p) = n-1$ and then the algorithm proceeds identically to $I_{n-2}^{V}$ for the remainder of its steps; thus $I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-1\}$ in this case.
+
+Finally, if $n-2,n-1 \in I_{n-2}^{V}$ then $I_{n-2}^W(q) = n-2$ and $I_{n-2}^W(p) = n-1$ as above, but this is different to what occured in $I_{n-2}^{V}$ so we cannot use the same argument as above.
+When the algorithm $I_{n-2}^W$ reaches vertex $n$, the only propagators $p$ and $q$ have contributed; thus we proceed as in the construction of $I_n^{V}$ but without propagator $q$.
+By Lemma~\ref{vertex cyclic int lem} we know that $I_n^V(q) = n-5$, and from the diagram we see that the only way this could occur is if all other propagators in $V$ had already been assigned when we reached vertex $n-5$; thus $q$ was the final propagator to be assigned in $I_n^{V}$.
+Therefore $I_{n-2}^{W} = (I_{n}^{V} \setminus \{n-5\}) \cup \{n-1, n-2\}$ in this case.
+This completes all cases for $I_{n-2}^{W}$.
+
+The arguments for $I_k^{W}$ ($1< k < n-2$) proceed analagously to those of $I_{n-2}^{W}$, with one simplification: we cannot have both $n-3$ and $n-2$ in $I_k^{V}$ since $q$ is the only propagator that could be assigned to either of them, and it cannot be assigned to both.
+
+This covers all cases and hence completes the proof.
+\end{proof}
+
 \begin{figure}
@@
 	\newnode[above]{6}{1}
+	\node at (180-60:\radius*0.1){\em Case 1};
 \end{scope}
@@
 	\newnode[above]{7}{1}
+	\node at (180-60:\radius*0.1){\em Case 2};
 \end{scope}
@@
 \]
-  \caption{The two cases for $W$ and $p$.  No other propagators can end in the fat red sections.  Other segments may have additional propagators ending in them.}\label{fig special p}
-\end{figure}
-
-\begin{proof}
-
-The two possible cases for $W$ are illustrated in Figure~\ref{fig special p}; all references to the ``left hand case'' or ``right hand case'' below refer to the diagrams in this figure.
-
-We first consider $I_1^{W}$, i.e.
-the set obtained by applying the Grassmann necklace algorithm to $W$ with starting vertex 1.
-Note that $n-3 \not\in I_1^{V}$: for the right hand case this is clear from the diagram (since Algorithm~\ref{alg:put GN on WLD} would assign $q$ no later than vertex $n-4$), while for the left hand case it follows from Lemma \ref{lem no fourth vertex}.
-Therefore when we start at vertex 1 and apply the Grassmann necklace algorithm to $W$, $p$ is the only remaining unassigned propagator when we reach vertex $n-3$, and so we have $ I_1^{W}(p) = n-3$ and $I_1^W = I_1^V\cup \{n-3\}$.
-
-Next consider $I_n^{W}$.
-From the figure we see that in both cases we have $I_n^{W}(p) = n$.
-At vertex 1 of the algorithm $I_n$, the unassigned propagators are exactly those that appear in $V$.
-Therefore the algorithm continues as in $I_1^{V}$ (recall Remark~\ref{rmk algorithm locally same} about locally identical propagator configurations), i.e.
-we have $I_n^{W} = I_1^{V} \cup \{n\}$.
-By a similar argument, we must have $I_{n-1}^{W} = I_n^{V} \cup \{n-1\}$.
-
-Now consider $I_{n-2}^{W}$.
-If $n-2\not\in I_{n-2}^{V}$ (i.e.
-$n-2$ supports no propagators in $V$), then $I_{n-2}^W(p) = n-2$ and this assignment of $p$ does not affect the rest of the construction of $I_{n-2}^{V}$, so we obtain $I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-2\}$ as above.
-
-On the other hand, if $n-2\in I_{n-2}^{V}$ then we must be in the right hand case of Figure~\ref{fig special p} and $I_{n-2}^V(q) = I_{n-2}^W(q) = n-2$ (since $q$ is always the clockwise-most propagator supported on vertex $n-2$; see Figure~\ref{fig special p}).
-If $n-1 \not\in I_{n-2}^{V}$, then $I_{n-2}^W(p) = n-1$ and then the algorithm proceeds identically to $I_{n-2}^{V}$ for the remainder of its steps; thus $I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-1\}$ in this case.
-
-Finally, if $n-2,n-1 \in I_{n-2}^{V}$ then $I_{n-2}^W(q) = n-2$ and $I_{n-2}^W(p) = n-1$ as above, but this is different to what occured in $I_{n-2}^{V}$ so we cannot use the same argument as above.
-When the algorithm $I_{n-2}^W$ reaches vertex $n$, the only propagators $p$ and $q$ have contributed; thus we proceed as in the construction of $I_n^{V}$ but without propagator $q$.
-By Lemma~\ref{vertex cyclic int lem} we know that $I_n^V(q) = n-5$, and from the diagram we see that the only way this could occur is if all other propagators in $V$ had already been assigned when we reached vertex $n-5$; thus $q$ was the final propagator to be assigned in $I_n^{V}$.
-Therefore $I_{n-2}^{W} = (I_{n}^{V} \setminus \{n-5\}) \cup \{n-1, n-2\}$ in this case.
-This completes all cases for $I_{n-2}^{W}$.
-
-The arguments for $I_k^{W}$ ($1< k < n-2$) proceed analagously to those of $I_{n-2}^{W}$, with one simplification: we cannot have both $n-3$ and $n-2$ in $I_k^{V}$ since $q$ is the only propagator that could be assigned to either of them, and it cannot be assigned to both.
-
-This covers all cases and hence completes the proof.
-\end{proof}
-
-\begin{figure}
-  \includegraphics{Le_diagrams}
-  \caption{Le diagrams for $V$ (left) and $W$ (right).}\label{fig Le}
+  \caption{The two cases for $W$ and $p$.  No other propagators can end in the red sections.  Other segments may have additional propagators ending in them.}\label{fig special p}
 \end{figure}
@@
 \end{proof}
+\begin{figure}
+  \[\includegraphics{Le_diagrams}\]
+  \caption{Le diagrams for $V$ (left) and $W$ (right).}\label{fig Le}
+\end{figure}
 
 As illustrated in Figure~\ref{fig Le}, the pieces of the Le diagrams of $V$ and $W$ will be called $\mathcal{A}$ and $\mathcal{B}$ in what follows.
-\hlfix{Explicitly, $\mathcal{B}$ is the set of columns with labels $v < n-3$ and $\mathcal{A}$ the set of columns labeled by $n$, $n-1$ and $n-2$ in $V$.
-In $W$, A consists of these columns without the last row.}{is this accurate?} Over the course of the next few lemmas we will prove that the plusses in the $\mathcal{B}$ parts of each diagram are identical, and that the relationship between the plusses in the $\mathcal{A}$ regions can be described explicitly.
+\hlfix{Explicitly, $\mathcal{B}$ is the set of columns with labels $v < n-3$ and $\mathcal{A}$ is the set of columns labeled by $n$, $n-1$ and $n-2$ in $V$.
+In $W$, $\mathcal{A}$ consists of these columns without the last row.}{is this accurate?} Over the course of the next few lemmas we will prove that the plusses in the $\mathcal{B}$ parts of each diagram are identical, and that the relationship between the plusses in the $\mathcal{A}$ regions can be described explicitly.
 
 We do this by applying Algorithm~\ref{alg:GN to Le}, which constructs the Le diagram associated to a Grassmann necklace, to the Grassmann necklaces of $V$ and $W$.
-As described in Section~\ref{sec:positroid background}, if Algorithm~\ref{alg:GN to Le} places a $+$ in the box with row index $i$ and column index $j$, we say that this plus is in the $i \rightarrow j$ position, and refer to it as the plus defined by ``the (hook) path from $i$ to $j$''.
-Note that the collection of paths contributed by a single Grassmann necklace term  must be non-crossing.
+As described in Section~\ref{sec:positroid background}, if Algorithm~\ref{alg:GN to Le} places a $+$ in the box with row index $i$ and column index $j$, we say that this plus is {\bf in the $i \rightarrow j$ position}, and refer to it as {\bf the plus defined by ``the (hook) path from $i$ to $j$''}.
+Note that the collection of paths contributed by a single Grassmann necklace term must be non-crossing: this follows immediately from the Le condition.
 
@@
 \begin{proof}
-If $n-2\not\in I_{n-2}^{V}$ then $I_{n-1}^{V}=I_{n-2}^{V}$ by definition, and by Lemma~\ref{lem I} we have $I_{n-2}^{W} = I_{n-1}^{V} \cup \{n-2\}$.
+If $n-2\not\in I_{n-2}^{V}$ then $I_{n-1}^{V}=I_{n-2}^{V}$ by definition, and by Lemma~\ref{lem I} we have the equality ${I_{n-2}^{W} = I_{n-1}^{V} \cup \{n-2\}}$.
 Note that $n-3\not\in I_{n-2}^{V}$ by Lemma~\ref{lem no fourth vertex}.
@@
   By Lemma~\ref{lem I} we have $I_{n-2}^{W}= (I_{n}^{V} \setminus \{n-5\})\cup \{n-1,n-2\}$ and $I_1^W = I_1^V\cup \{n-3\}$.
-We are necessarily in the case where $W$ admits a propagator $q$ (the right hand case of Figure~\ref{fig special p}) and we can see from the location of $q$ that $n-2\not\in I_{n-3}^{V}$ and that $n-5$ is the label of the last row in $\mathcal{B}$.
+We are necessarily in the case where $W$ admits a propagator $q$ (Case 2 of Figure~\ref{fig special p}) and we can see from the location of $q$ that $n-2\not\in I_{n-3}^{V}$ and that $n-5$ is the label of the last row in $\mathcal{B}$.
 Also note that by Lemma~\ref{vertex cyclic int lem} and Corollary~\ref{no coloops} we must have $n\in I_n^V$.
@@
   \begin{figure}
-    \includegraphics{messy}
-    \caption{Plusses coming from $I_{n-2}^{V}$ (left) and  $I_{n-1}^{V}$ (right), in the case where $n-1, n-2\in I_{n-2}^{V}$.
+    \[\includegraphics{messy}\]
+    \caption{Plusses coming from $I_{n-2}^{V}$ (top left), $I_{n-1}^{V}$ (top right), and $I_n^V$ (bottom row), in the case where ${n-1, n-2\in I_{n-2}^{V}}$.
 The blue lines are the non-intersecting paths defining the position of the plusses.
@@
 On the other hand we have $n-5 \in I_1^{V} \setminus I_{n-2}^V$, along with at least one and at most two other elements.
-If there is one such element call it $a$.
-If there are two call them $a$ and $b$ with $a>b$.
-
-  This means that the plusses in the Le diagram of $V$ coming from $I_{n-2}^{V}$ are as in the first part of Figure~\ref{fig messy}.
-Stepping to $I_{n-1}^{V}$ simply removes the $(n-5)\rightarrow (n-2)$ path (second part of Figure~\ref{fig messy}), so $I_{n-1}^V$ contributes no new information about the Le diagram of $V$.
+If there is one such element, call it $a$.
+If there are two, call them $a$ and $b$ with $a>b$.
+
+  This means that the plusses in the Le diagram of $V$ coming from $I_{n-2}^{V}$ are as in the top left diagram in Figure~\ref{fig messy}.
+Stepping to $I_{n-1}^{V}$ simply removes the $(n-5)\rightarrow (n-2)$ path (top right diagram of Figure~\ref{fig messy}), so $I_{n-1}^V$ contributes no new information about the Le diagram of $V$.
 
@@
   \begin{figure}
-     \includegraphics{messyD}
+     \[\includegraphics{messyD}\]
     \caption{Plusses coming from $I_{n-2}^{W}$.}\label{fig messyD}
@@
 Now consider $I_{n-3}^{V}$.
-By \eqref{eq necklace} $I_{n-3}^{V}$ contributes almost the same plusses as $I_{n-2}^{V}$: the only difference is that it contributes an $(n-5)\rightarrow (n-3)$ plus in place of the $(n-5)\rightarrow (n-2)$ plus.
+By equation~\eqref{eq necklace} $I_{n-3}^{V}$ contributes almost the same plusses as $I_{n-2}^{V}$: the only difference is that it contributes an $(n-5)\rightarrow (n-3)$ plus in place of the $(n-5)\rightarrow (n-2)$ plus.
 Since we must have $n-3\in I_{n-3}^{V}$ (because the propagator $q$ exists in $V$), it follows from Lemma~\ref{lem I} that $I_{n-3}^{W} = I_{n-3}^{V}\cup\{n-2\}$.
 Thus the paths for $I^{W}_{n-3}$ are the same as those for $I^{V}_{n-3}$ except that the path that did go to $n-3$ now goes to $n-2$.
-This cannot conflict with another path since \eqref{eq necklace} shows that $n-2$ only appears in $I_{n-2}^{V}$ among the necklace elements of $V$.
+This cannot conflict with another path since equation~\eqref{eq necklace} shows that $n-2$ only appears in $I_{n-2}^{V}$ among the necklace elements of $V$.
 
@@
 
-  Recall that $n-5$ is the largest row index in the Le diagram of $V$, and $n-5 \in I_1^V \setminus I_{n-4}^V$ so $I_{n-4}^V$ does contribute a path starting at $n-5$.
+  Recall that $n-5$ is the largest row index in the Le diagram of $V$, and $n-5 \in I_1^V \setminus I_{n-4}^V$ so $I_{n-4}^V$ must contribute a path starting at $n-5$.
 Since $n-4 \in I_{n-4}^V$ by the location of the propagator $q$, we must also have a path ending at $n-4$.
@@
   If $n-3\in I_{k}^{V}$ then $I_k^V$ must contribute a plus in the $n-3$ column of the Le diagram of $V$, and by Lemma~\ref{lem I} we have $I_{k}^{W} = I_k^{V}\cup \{n-2\}$.
-If $n-2$ supports no propagators in $V$ then certainly no pluses appear in the $n-2$ column of the Le diagram of $V$.
+If $n-2$ supports no propagators in $V$ then certainly no plusses appear in the $n-2$ column of the Le diagram of $V$.
 If $n-2$ supports at least one propagator in $V$ then $n-2 \in I_{n-2}^V$ and so by hypothesis $n-1 \in I_{n-2}^V$ as well.
@@
 
-  Since $n-3 \in I_k^V \setminus I_1^V$, we must have a path from some vertical edge $i$ to the bottom edge $n-3$ in the Le diagram of $V$.
+  Since $n-3 \in I_k^V \setminus I_1^V$, we must have a path in the Le diagram of $V$ from some vertical edge $i$ to the bottom edge $n-3$.
 In the Le diagram of $W$, the index $n-3$ labels a vertical edge with no path starting at it (since $n-3$ belongs to both $I_1^W$ and $I_k^W$), and there must be a path leading to $n-2$ since $n-2 \in I_k^W \setminus I_1^W$.
@@
   First note that a Wilson loop diagram $W$ with one propagator supported on vertices $i<j<k<\ell$ has Le diagram a single row with $|W|-i$ boxes.
-Labelling the columns from left to right by $|W|, \ldots, |W|-i+1$, by the algorithm there are plusses in the $j$, $k$, and $\ell$ positions.
+Labelling the columns from left to right by $|W|, \ldots, |W|-i+1$, by Algorithm~\ref{alg:GN to Le} there are plusses in the $j$, $k$, and $\ell$ positions.
 
@@
 
-  We make one further simplification: if our $W$ is in Case 2 of Figure~\ref{fig special p} and $n-1$ supports only $p$ but $n-2$ supports at least one other propagator, then flip $W$ on the line perpendicular to the $(n-2)^{th}$ edge to obtain a diagram with the configuration of Case 1.
+  We make one further simplification: if our $W$ is in Case 2 of Figure~\ref{fig special p} and $n-1$ supports only $p$ but $n-2$ supports at least one other propagator, then flip $W$ on the line perpendicular to the $(n-2){th}$ edge to obtain a diagram with the configuration of Case 1.
 This eliminates the possibility that we could have $n-2 \in I_{n-2}^W$ but $n-1 \not\in I_{n-2}^W$.
@@
 
-  From Lemma~\ref{lem shape} we know how the shapes of the Le diagrams of $V$ and $W$ are related; let $\mathcal{A}$ and $\mathcal{B}$ be as described above.
+  From Lemma~\ref{lem shape} we know how the shapes of the Le diagrams of $V$ and $W$ are related; let $\mathcal{A}$ and $\mathcal{B}$ be as described in that lemma and subsequent discussion.
 Lemmas~\ref{lem n and n-1}, \ref{lem n-2 good}, and \ref{lem n-2 bad} tell us that the three boxes of the bottom row of the Le diagram of $W$ each have a plus.

### 2019-08-13 GWLDCII.tex
thoughts on 3.15 and started rereading

@@
 In contrast, the first paper in this series focuses on combinatorial and matroidal properties of the Wilson loop diagrams.
-The main focus of that paper is to enumerate the positroid cells that are associated to Wilson loop diagrams with a fixed number of vertices and propagators, as well as counting the number of Wilson loop diagrams in the pre-image of \hlfix{any positroid cell under this association.}{I'd like to mildly rephrase this because it sounds like we know exactly which cells have non-empty pre-image, which isn't quite what we proved.}
+The main focus of that paper is to enumerate the positroid cells that are associated to Wilson loop diagrams with a fixed number of vertices and propagators, as well as counting the number of Wilson loop diagrams in the pre-image of \hlfix{any positroid cell in the image of this association.}{I'd like to mildly rephrase this because it sounds like we know exactly which cells have non-empty pre-image, which isn't quite what we proved.} \sanote{changed}
 
@@
 In Section~\ref{sec dim} we examine the dimension of positroids associated to Wilson loop diagrams, and show that the dimension is always equal to three times the number of propagators in the diagram (Theorem~\ref{thm dim}).
-While this has been proved by Marcott in \hlfix{[ref]}{Did this get published yet?} using geometric methods, our proof is constructive and explicitly relates the position of the plusses in the Le diagram to the propagators in the Wilson loop diagram.
+While this has been proved by Marcott in \cite{WLDdim} using matroidal arguments, our proof is constructive and explicitly relates the position of the plusses in the Le diagram to the propagators in the Wilson loop diagram.
 
@@
 If we need to impose a direction on a propagator $p = (i,j)$, for example in order to consider the region ``inside'' or ``outside'' of $p$, we write $(p,<_i)$ to indicate that $p$ is directed from edge $i$ to edge $j$, and $(p,<_j)$ for the opposite direction.
+{\color{violet} Note to consider while reading: Might it be notationally easier and/or clearer to talk about ordering the propagators as clockwise or counter clockwise?
+If so, are the benefits of this new notation worth the rewriting?}
 
@@
 \begin{scope}
-	\drawWLDfragment[8]{3}{0.3} % draw arc
+	\drawWLDfragment[9]{3}{0.3} % draw arc
 	%\drawnumbers % use this to debug
@@
 		%p_r
-		\draw[smallpropagator] (\zero+2.5*\step:\radius*1.1) to [bend left = 55] (\zero + 6.7*\step:\radius*1.1); 
+		\draw[smallpropagator] (\zero+2.3*\step:\radius*1.1) to [bend left = 55] (\zero + 6.7*\step:\radius*1.1); 
 		%q
-		\draw[smallpropagator] (\zero+2.6*\step:\radius*1.1) to [bend left = 55] (\zero + 5.3*\step:\radius*1.1); 
+		\draw[smallpropagator] (\zero+2.4*\step:\radius*1.1) to [bend left = 55] (\zero + 5.3*\step:\radius*1.1); 
 		%\draw[smallpropagator,light-gray] (\zero+7.5*\step:\radius*1.1) -- (0:\radius*0.25);  
@@
 	\newnode[below]{3}{}
-	\newnode[right]{8}{j_m}
+	\newnode[right]{9}{j_m}
 	% case label
@@
 \begin{scope}
-	\drawWLDfragment[8]{3}{0.3} % draw arc
+	\drawWLDfragment[10]{3}{0.3} % draw arc
 	%\drawnumbers % use this to debug
@@
 		%p_r
-		\draw[smallpropagator] (\zero+2.5*\step:\radius*1.1) to [bend left = 70] (\zero + 4.5*\step:\radius*1.1); 
+		\draw[smallpropagator] (\zero+2.5*\step:\radius*1.1) to [bend left = 90] (\zero + 4.5*\step:\radius*1.1); 
 		%q
@@
 	\newnode[below]{5}{}
-	\newnode[right]{8}{j_m}
+	\newnode[below]{8}{}
+	\newnode[right]{9}{j_m}
 	% case label
@@
 $I_i(p_t) <_i I_i(p_r)$ certainly isn't obvious and may not be true}.
-Since there are finitely many steps this process can take before reaching $Q_0$, and any $p_* \in Q_0  = \Prop(j_m)$ has $j_m$ in its support by definition, this argument eventually terminates with the construction of a propagator constraining the positioning of $q$ as required.
+{\color{violet} May not be necessary, but I think highlighted tex follows from "Now repeat the argument...." \begin{enumerate}\item If $V(p_r) \in [a_r-1, j_m]$ (other end closer to $j_m$) then $q$ inside $p_r$ in $a_r-1$ order.
+\item Else, $V(p_r) \in [i, a_r+1]$ (Maybe $[i-1, a_r +1]$?).
+(Main point is that other end closer to $i$) Either way,  admissibility implies that $a_s < a_r$ \item Now we repeat.
+Either  $V(p_s) \in [a_s-1, j_m]$ then $q$ inside $p_s$ in $a_s-1$ order and we are done \item Else, $V(p_s) \in [i, a_s+1]$ (Maybe $[i-1, a_s +1]$?).
+Either way, admissibility implies that $a_t < a_s$ and we've already established $a_s < a_r$ \end{enumerate} We don't have to include this argument.
+It may be totally unnecessary.
+But I want to make certain that I'm not missing anything.}  Since there are finitely many steps this process can take before reaching $Q_0$, and any $p_* \in Q_0  = \Prop(j_m)$ has $j_m$ in its support by definition, this argument eventually terminates with the construction of a propagator constraining the positioning of $q$ as required.
 This completes the induction step, and hence the proof.\end{proof}

### 2019-08-13 GWLDCII.tex
still tweaking 3.15

@@
 \end{figure}
-Now repeat the argument above with $p_s$ in place of $p_r$: if the other end of $p_s$ lands on an edge between $q$ and $j_m$ then we have $q \in \cP_{m-1}$ as above; if not then there exists some $p_t \in Q_{l-3}$ with $p_s$ supported on $I_i(p_t)$ and \hlfix{$I_i(p_t) <_i I_i(p_r)$}{$I_i(p_t) <_i I_i(p_s)<_i I_i(p_s)$?
+Now repeat the argument above with $p_s$ in place of $p_r$: if the other end of $p_s$ lands on an edge between $q$ and $j_m$ then we have $q \in \cP_{m-1}$ as above; if not then there exists some $p_t \in Q_{l-3}$ with $p_s$ supported on $I_i(p_t)$ and $q$ on the inside of $p_t$ in the $a_t-1$ order.
+Thereofore \hlfix{$I_i(p_t) <_i I_i(p_r)$}{$I_i(p_t) <_i I_i(p_s)<_i I_i(p_s)$?
 Or is the implication clear enough not to be mentioned}\note{Nope: we just need $<_i I_i(p_r)$.

### 2019-08-14 GWLDCII.tex
read through 2.1

@@
 
-In particular, we will see in later sections that all four vertices in the support of a propagator are important in understanding the contribution of that propagator to the overall diagram.
-This motivates the following definition of a subdiagram, which can consist of any subset $Q$ of the propagators and any subset $U$ of the vertices of $W$ {\em as long as we retain all vertices in the support of $Q$}.
+In particular, we will see in later sections that all four vertices supporting a propagator are important in understanding the contribution of that propagator to the \st{overall diagram}{geomtric object represented by the diagram} \sanote{Is this what we mean?}.
+This motivates the following definition of a subdiagram, any subset $Q$ of the propagators and any subset $U$ of the vertices of $W$ {\em containing the support of $Q$}.
 
@@
 \item There does not exist a non-empty set of propagators $Q \subseteq \cP$ such that $|V(Q)| < |Q| + 3$.
-\item There does not exist a pair of propagators $\{(i,j),(k,l)\} \subseteq \cP$ such that $i < k < j < l$.
+\item There does not exist a pair of crossing propagators: that is, there does not exist $\{(i,j),(k,l)\} \subseteq \cP$ such that $i < k < j < l$.
 \end{enumerate}
@@
 This is represented as an integral $I(W)$, which is the equivalent of a Feynman integral in this setting.
+\sanote{This feels like too much detail.
+Thoughts?} This integral is comprised of two main components, and interaction matrix, $C(W)$ and a volume form, $\Omega(W)$.
+These are described below.
 
@@
 
-The matrix $C(W)$ can be interpreted as a parametrization of the positroid cell associated to $W$ in the positive Grassmannian $\Gr(n, |\cP|)$, which we denote by $\Sigma(W)$ \cite{wilsonloop}.
+The matrix $C(W)$ can be interpreted as a \hlfix{parametrization of the positroid cell associated to $W$}{I know we've been saying this, but we have $4k$ parameters for a $3k$ dimensional space.
+Is this okay?} in the positive Grassmannian $\Gr(n, |\cP|)$, which we denote by $\Sigma(W)$ \cite{wilsonloop}.
 Most of the work in this paper, and in \cite{generalcombinatoricsI} focuses on characterizing the positroid cell associated to each Wilson loop diagram $W$.
@@
 Note that since there is no ordering on the propagators of $W$, $C(W)$ is only defined up to rearrangement of the rows.
-This will not matter here, as it does not affect the parametrization of $\Sigma(W)$.
+When needed, we will impose various orders on these rows.
+This will not matter, as it does not affect the parametrization of $\Sigma(W)$.
 
 One may also interpret the functional $I(W)$ as associating a volume to each cell $\Sigma(W)$ \cite{wilsonloop, Amplituhedronsquared, HeslopStewart}.
-The volume form is written in terms of the elements of $C(W)$ as  \begin{equation} \label{eq:omega(W) def}\Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V_{p_r}} \textrm{d}c_{p_r}}{R(W)} \;, \end{equation}
+The volume form is written in terms of the elements of $C(W)$ as  \begin{equation} \label{eq:omega(W) def}\Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V(p_r)} \textrm{d}c_{p_r}}{R(W)} \;, \end{equation}
 where the denominator $R(W)$ is given in Definition~\ref{def R(W)} below.
@@
 
-In particular, this implies that any singularities in the integrals $I(W)$ must cancel out in the sum.
-Specifically, they must cancel on the boundaries of the positroid cells $\Sigma(W)$, analogous to the analysis in \cite{Arkani-Hamed:2013jha}.
+In particular, this implies that any singularities in the integrals $I(W)$ must cancel out in the sum, in particular, all poles arising from $R(W)$ must cancel.
+Specifically, these poles must cancel on the boundaries of the positroid cells $\Sigma(W)$, analogous to the analysis in \cite{Arkani-Hamed:2013jha}.
 This has been checked for particular classes of examples (e.g.
@@
 Let $W = (\cP,V)$ be an admissible Wilson loop diagram, and fix an edge $e$.
-Let $\{p_1 \ldots p_r\}$ be the propagators with one end lying on edge $e$, ordered so that $p_1$ is closest to the vertex $e$, $p_r$ is closest to $e+1$, and $p_i$ is closer to $e$ than $p_{i+1}$ is.
+Let $\{p_1 \ldots p_r\}$ be the propagators with one end lying on edge $e$ under a counterclockwise orderin.
+That is, $p_1$ is closest to the vertex $e$, $p_i$ is positioned counterclockwise to $p_{i+1}$ and $p_r$ is the clockwise most propagator on this edge (closest to $e+1$).
 Define the polynomial
@@
 We also give an algorithm to read $R(W)$ directly from the Wilson loop diagram, paving the way for a general study of these poles in future.
+\todo{cite the theorems where these results appear}
 

### 2019-08-14 GWLDCII.tex
read through section 2

@@
 In Section \ref{sec poles}, we show that the denominator $R(W)$ is determined by the positroid cell $\Sigma(W)$ and the structure of $W$, as encapsulated by $C(W)$.
-In fact, it can be read directly off of $C(W)$, in terms of a characterization of $\Sigma(W)$ called the Grassmann necklace (see Definition~\ref{def:grassmann necklace}).
+In fact, it can be read directly off of $C(W)$, in terms of a characterization of $\Sigma(W)$ called the Grassmann necklace (see Definition~\ref{def:grassmann necklace}) as shown in Algorithm \ref{alg:put GN on WLD}.
 We also give an algorithm to read $R(W)$ directly from the Wilson loop diagram, paving the way for a general study of these poles in future.
-\todo{cite the theorems where these results appear}
 
@@
 
-  Alternatively if we forget about the matroid and simply think about the condition of linear independence in the matrix $C(W)$, the corollary can also be proved directly by linear algebra and the definition of $C(W)$ as follows.
+  Alternatively if we forget about the \st{matroid} {\color{violet} diagram} \sanote{okay?} and simply think about the condition of linear independence in the matrix $C(W)$, the corollary can also be proved directly by linear algebra and the definition of $C(W)$ as follows.
 
@@
 Our first goal is therefore to find a better method of obtaining the positroid associated to a given Wilson loop diagram; this is the focus of the next section.
+\sanote{Should the 2 paras before the remark be moved to when whe walk about the GN algorithm?}
 

### 2019-08-15 GWLDCII.tex
read through section 3.1

@@
 
-One of the key insights is that each element of the Grassmann necklace can be viewed as a function from the propagators of the diagram to the vertices in the Grassmann necklace element.
+One of the key insights is that each element of the Grassmann necklace can be viewed as a function from the propagators of the diagram to the vertices in the \st{Grassmann necklace element}{\color{violet} Wilson loop diagram?}.
 This is captured in Definition~\ref{def I_i as a function}, and used throughout the paper.
@@
 Write $(p, <_i)$ to represent the same propagator directed from $i$ to $j$.
-Then the sets of propagators {\bf inside} and {\bf outside} of $(p,<_i)$ are defined to be
+Then the sets of propagators {\bf inside} \sanote{just checking: $p \in \cP_{in}(p)$?} and {\bf outside} of $(p,<_i)$ are defined to be
 \begin{gather*}\cP_{in}(p,<_i) = \{ (k,l) \in \cP \ |\ i \leq_i k <_i l \leq_i j \}, \\
@@
 
-Let $W_r := (\cP_{in}(q_r),[n])$ be the subdiagram of $W$ consisting only of those propagators inside $q_r$ (including $q_r$ itself); in particular $W_r$ contains none of the previous $p_i$ or $q_i$.
+Let \hlfix{$W_r := (\cP_{in}(q_r),[n])$}{technically has non supporting vertices.
+Want $(\cP_{in}(q_r),[i_r, k_r+1])$.
+However this is clear later.
+Do we care?} be the subdiagram of $W$ consisting only of those propagators inside $q_r$ (including $q_r$ itself); in particular $W_r$ contains none of the previous $p_i$ or $q_i$.
 By the original hypotheses on $W$, every vertex in $[i_r,k_{r+1}]$ (of which there are at least 4, since $\ell(q_r) \geq 4$) must support at least one propagator.
@@
 
-Note that we could replace $q_r$ by another propagator $q'_{r}$ in $W_r$, as long as $p_{r+1}$ and $q_r$ are on opposite sides of $q_r'$: such a new $q'_{r}$ would still satisfy all of the induction hypotheses.
-(See Figure~\ref{fig smallest q in lem sian}.) Therefore without loss of generality we may assume that $\cP_{in}(q_r)$ does not contain any propagators (other than $q_r$ itself) which satisfy the induction hypotheses, i.e.
-we assume that there are no other propagators with $p_{r+1}$ on one side and $q_r$ on the other.
+Note that we could replace $q_r$ by another propagator $q'_{r}$ in \st{$W_r$} {\color{violet}$W_r = (\cP_{in}(q_r), [n])$}\sanote{just want to emphasize that $q_r'$ is inside $q_r$}, as long as $p_{r+1}$ and $q_r$ are on opposite sides of $q_r'$: such a new $q'_{r}$ would still satisfy all of the induction hypotheses.
+(See Figure~\ref{fig smallest q in lem sian}.) Therefore without loss of generality we may assume that $\cP_{in}(q_r)$ does not contain any propagators (other than $q_r$ itself) which satisfy the induction hypotheses, \st{i.e.
+we assume that there are no other propagators with $p_{r+1}$ on one side and $q_r$ on the other}.
 
@@
 	\newnode[right]{15}{k_r+1}
+	\newnode[below]{5}{j_{r+1}}
 	\newprop[midway,above]{1.5}{14.5}{\footnotesize $q_r$}
@@
 The first case is that $i_r \leq j_{r+1} \leq i_r+2$ and $k_r-2 \leq j_{r+1}+2 \leq k_{r}$ (so $p_{r+1}$ has one end before $i_{r} + 3$ and the other after $k_{r} - 2$, i.e.
-both ends of $p_{r+1}$ are close to the ends of $q_r$).
-Then since $p_{r+1}$ has length 2, it must be that $(i_r+3)+1 \geq k_r-2$ and so $q_r$ has length $\leq 6$.
+there are at most two vertices between an endpoint of $p_{r+1}$ and an endpoint of $q_r$).
+Then since $p_{r+1}$ has length 2, \st{it must be that $(i_r+3)+1 \geq k_r-2$ and so} {\color{violet} this implies that} $q_r$ has length $\leq 6$.
 By the minimality assumption on $q_r$, no propagator in $W_r$ has $q_r$ on one side and $p_{r+1}$ on the other side.
@@
 
-The second case is that (at least) one of the following four things happen:
+The second case, \hlfix{there are at least $3$ vertices between one endpoint of $p_{r+1}$ and the nearest endpoint of $q_r$.}{Does this just convolute matters?} In other words,  (at least) one of the following four things happen:
 \begin{itemize} 
-\item $i_r+3 \leq j_{r+1}\leq k_r-3$, or
-\item $i_r+3 \leq j_{r+1}+2\leq k_r-3$, or
-\item $i_r = j_{r+1}$, or 
-\item $k_r-2 = j_{r+1}$
+\item $i_r+3 \leq j_{r+1}\leq k_r-3$ (one endpoint of $p_{r+1}$ has at least 3 vertices between it and the nearest enpoint of $q_r$), or
+\item $i_r+3 \leq j_{r+1}+2\leq k_r-3$ (one endpoint of $p_{r+1}$ has at least 3 vertices between it and the nearest enpoint of $q_r$), or
+\item $i_r = j_{r+1}$ ($p_{r+1}$ and $q_r$ share and end edge), or 
+\item $k_r = j_{r+1} +2$  ($p_{r+1}$ and $q_r$ share and end edge)
 \end{itemize}
@@
 
-Note that since $j_{r+1}+4 \leq k_r-1$ in both of these situations, the vertex $j_{r+1}+4$ is inside $q_r$ but does not support either $q_r$ or $p_{r+1}$, and must therefore support some other propagator $t$.
+\st{Note that since} {\color{violet} Since there are at least $3$ vertices between one endpoint of $p_{r+1}$ and the nearest endpoint of $q_r$},  $j_{r+1}+4 \leq k_r-1$ in both of these situations, the vertex \hlfix{$j_{r+1}+4{\color{violet} \in [i_r, k_r+1]}$}{or is a vertex of $W_r$ in the restricted version, have explicitly removed notation about vertices being inside or outside} \st{is inside $q_r$} but does not support either $q_r$ or $p_{r+1}$, and must therefore support some other propagator $t$.
 Since $p_{r+1}$ is not part of configuration \ref{item pair of 2s} and $W_r$ has no propagators of length 3, it follows that $\ell(t) \geq 4$.

### 2019-08-15 GWLDCII.tex
some edits and comments up to p23

@@
 Our primary focus is Wilson loop diagrams with $V = [n]$, so in order to simplify the exposition we will often use $i+1$ as shorthand for ``the successor of vertex $i$''.
+\note{We say this here and then again in the paragraph after length.
+Can we discuss how to say it once in a clear and concise way.}
 
@@
 
-In particular, we will see in later sections that all four vertices supporting a propagator are important in understanding the contribution of that propagator to the \st{overall diagram}{geomtric object represented by the diagram} \sanote{Is this what we mean?}.
+In particular, we will see in later sections that all four vertices supporting a propagator are important in understanding the contribution of that propagator to the \st{overall diagram}{geometric object represented by the diagram} \sanote{Is this what we mean?}\note{Is this chatty bit even helpful at all: this seems like the most natural notion of subobject anyway.}.
 This motivates the following definition of a subdiagram, any subset $Q$ of the propagators and any subset $U$ of the vertices of $W$ {\em containing the support of $Q$}.
@@
 These diagrams correspond to (tree level) amplitudes of SYM $N=4$ theory in twistor space.
-As such, it associates a real value to $n$ particles, one for each vertex.
+As such, it\note{What is this ``it'', is it ``these diagrams'' if so there's a singular/plural agreement problem, if not then it isn't clearly enough written.} associates a real value to $n$ particles, one for each vertex.
 Each particle is represented as a section of a $|\cP|$-vector bundle over twistor space, projected onto a real subspace in a process called bosonization \cite{Arkani-Hamed:2013jha}.
@@
 \sanote{This feels like too much detail.
-Thoughts?} This integral is comprised of two main components, and interaction matrix, $C(W)$ and a volume form, $\Omega(W)$.
+Thoughts?}\note{Seems ok to me, at least with the grammar fixed as noted above} This integral is comprised of two main components, and interaction matrix, $C(W)$ and a volume form, $\Omega(W)$.
 These are described below.
@@
 The matrix $C(W)$ can be interpreted as a \hlfix{parametrization of the positroid cell associated to $W$}{I know we've been saying this, but we have $4k$ parameters for a $3k$ dimensional space.
-Is this okay?} in the positive Grassmannian $\Gr(n, |\cP|)$, which we denote by $\Sigma(W)$ \cite{wilsonloop}.
+Is this okay?}\note{Maybe there's a better word than ``parametrization''?
+It does define the positroid cell by giving its points, we wouldn't need to say parametrizaion to say that.} in the positive Grassmannian $\Gr(n, |\cP|)$, which we denote by $\Sigma(W)$ \cite{wilsonloop}.
 Most of the work in this paper, and in \cite{generalcombinatoricsI} focuses on characterizing the positroid cell associated to each Wilson loop diagram $W$.
@@
 Let $\{p_1 \ldots p_r\}$ be the propagators with one end lying on edge $e$ under a counterclockwise orderin.
-That is, $p_1$ is closest to the vertex $e$, $p_i$ is positioned counterclockwise to $p_{i+1}$ and $p_r$ is the clockwise most propagator on this edge (closest to $e+1$).
+That is, $p_1$ is closest to the vertex $e$, $p_i$ is positioned counterclockwise to $p_{i+1}$ and $p_r$ is the clockwise most propagator on this edge (closest to vertex $e+1$).
 Define the polynomial
@@
 
-For our purposes, a {\bf positroid} is a matroid $M$ (with ground set $[n]$ and bases $\cB \subseteq \binom{[n]}{k}$) which can be represented by an element of the positive Grassmannian $\Gr(k,n)$.
-In other words, there exists a full-rank $k\times n$ real matrix whose $k\times k$ minors are all nonnegative and such that the minor $[[k]|J]$ is positive if and only if $J \in \cB$.
+For our purposes, a {\bf positroid} is\footnote{Note that matroid isomorphism allows arbitrary permutations of the ground set but positroid isomorphism allows only cyclic permutations, so the property of being a positroid is not in general preserved by matroid isomorphism.} a matroid $M$ (with ground set $[n]$ and bases $\cB \subseteq \binom{[n]}{k}$) which can be represented by an element of the positive Grassmannian $\Gr(k,n)$.
+In other words, there exists a full-rank $k\times n$ real matrix whose $k\times k$ minors are all nonnegative and such that the minor $[[k]|J]$\note{I don't think we have this $[[k]|J]$ notation defined?} is positive if and only if $J \in \cB$.
 
@@
 This in turn induces a total order on $\binom{[n]}{k}$, namely the lexicographic order with respect to $<_j$.
-It also induces a separate partial order $\gale{j}$ on $\binom{[n]}{k}$ (the {\bf Gale order} \cite{Gale}), which is defined as follows: for
+It also induces a separate partial order $\gale{j}$ on $\binom{[n]}{k}$ (the {\bf Gale order} \cite{Gale}\note{We only use this once and in this particular section, so maybe we don't need to define and name it but can just put the def in-line where we need it}), which is defined as follows: for
 \[A = \{a_1 <_j a_2 <_j \dots <_j a_k\} \text{ and } B = \{b_1 <_j b_2 <_j \dots <_j b_k\} \in \binom{[n]}{k},\] we define
@@
 
-In \cite{wilsonloop}, Agarwala and Marin-Amat show that $M(W)$ is also characterized by the Wilson loop diagram itself:
+In \cite{wilsonloop}, Agarwala and Marin-Amat show that $M(W)$ is also characterized by the Wilson loop diagram itself\note{I don't like this phrasing; can we discuss}:
 
@@
 \end{dfn}
+Note that we have $p\in \cP_{in}(p, <_i)$ and so $\cP_{in}(p, <_i) = \cP_{out}(p, <j)\cup\{p\}$.
 
@@
   \begin{enumerate}
-    \item $W$ has a propagator of length $\leq 6$ with a propagator of length 2 on one side it and nothing else on that side.\label{item big and 2}
+    \item $W$ has a propagator of length $\leq 6$ with a propagator of length 2 on one side of it and nothing else on that side.\label{item big and 2}
     \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator ends between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
@@
 \end{lem}
+\note{Should this lemma have pictures}
 
@@
 However this is clear later.
-Do we care?} be the subdiagram of $W$ consisting only of those propagators inside $q_r$ (including $q_r$ itself); in particular $W_r$ contains none of the previous $p_i$ or $q_i$.
+Do we care?}\note{No, we don't quite want that either because we don't want the newly shortened $q_r$ to be our propagator of length 2 -- maybe a slight change to the remark} be the subdiagram of $W$ consisting only of those propagators inside $q_r$ (including $q_r$ itself); in particular $W_r$ contains none of the previous $p_i$ or $q_i$.
 By the original hypotheses on $W$, every vertex in $[i_r,k_{r+1}]$ (of which there are at least 4, since $\ell(q_r) \geq 4$) must support at least one propagator.
@@
 (See Figure~\ref{fig smallest q in lem sian}.) Therefore without loss of generality we may assume that $\cP_{in}(q_r)$ does not contain any propagators (other than $q_r$ itself) which satisfy the induction hypotheses, \st{i.e.
-we assume that there are no other propagators with $p_{r+1}$ on one side and $q_r$ on the other}.
+we assume that there are no other propagators with $p_{r+1}$ on one side and $q_r$ on the other}.\note{I kind of like the struck part, can we make your other changes and also keep the struck part.}
 
@@
 
+\note{Would it be worth having vertex $j_{r+1}$ labelled in this fig smallest q in lem sian}
+
 There are two cases to consider.
@@
 
-The second case, \hlfix{there are at least $3$ vertices between one endpoint of $p_{r+1}$ and the nearest endpoint of $q_r$.}{Does this just convolute matters?} In other words,  (at least) one of the following four things happen:
+The second case, \hlfix{there are at least $3$ vertices between one endpoint of $p_{r+1}$ and the nearest endpoint of $q_r$.}{Does this just convolute matters?}\note{Well at some stage it got edited so that it isn't a sentence any longer, but I think something like this should be here because it defines what the second case is.} In other words,  (at least) one of the following four things happen:
 \begin{itemize} 
@@
 The overall result then follows by induction.
+
 \end{proof}
@@
 Until now, the positroid associated to a Wilson loop diagram $W$ could only be obtained by computing the matrix $C(W)$ associated to $W$, listing all bases of the induced matroid $M(W)$, and constructing the Le diagram or Grassmann necklace of the positroid ``by eye'' from this list.
+\note{Can we discuss how to say this in a way that doesn't appear weak.}
 
@@
 \begin{algorithm}\label{alg:put GN on WLD}
-Let $W = (\cP, [n])$ be an admissible Wilson loop diagram. In order to construct the set set $I_i^W$ (or just $I_i$ when $W$ is clear from context) for $i \in [n]$, perform the following steps:
+Let $W = (\cP, [n])$ be an admissible Wilson loop diagram.
+In order to construct the set set $I_i^W$ (or just $I_i$ when $W$ is clear from context\note{We have gone from not pointing out this convention to pointing it out 3 times.
+Can we find a happy medium?}) for $i \in [n]$, perform the following steps:
 
@@
 \[1235, 2356, 3456, 4567, 5671, 6712, 7812, 8123.\]
-The reader can easily verify that this sequence of $k$-sets satisfies the definition of a Grassmann necklace, and can (with significantly more work) also verify that this Grassmann necklace defines the positroid $M(W)$ associated to the Wilson loop diagram $W$ above.
+The reader can easily verify that this sequence of $k$-sets satisfies the definition of a Grassmann necklace, and can (with significantly more work) also verify that this Grassmann necklace defines the positroid $M(W)$ associated to the Wilson loop diagram $W$ above, as we will prove in general shortly.
 \end{eg}
@@
 We now consider what happens as we move from $V$ to each of the three remaining cases for $W$.
-We need to consider both $J^{W}_p$ and $J^{W}_r$ for $r \neq p$, since the addition of $p$ can have a knock-on effect on later steps in the algorithm.
+We need to consider both $J^{W}_p$ and $J^{W}_r$ for $r \neq p$, since the addition of $p$ can have a knock-on\note{Wouldn't the expression be knock off?} effect on later steps in the algorithm.
 

### 2019-08-15 GWLDCII.tex
just a few more things up to p26

@@
 We now consider what happens as we move from $V$ to each of the three remaining cases for $W$.
-We need to consider both $J^{W}_p$ and $J^{W}_r$ for $r \neq p$, since the addition of $p$ can have a knock-on\note{Wouldn't the expression be knock off?} effect on later steps in the algorithm.
+We need to consider both $J^{W}_p$ and $J^{W}_r$ for $r \neq p$, since the addition of $p$ can have a knock-on effect on later steps in the algorithm.
 
@@
 \begin{proof}
-\note{Sian replaced ``counterclockwise'' with ``clockwise'' in a couple of places in this proof: someone please doublecheck?}
+\note{Sian replaced ``counterclockwise'' with ``clockwise'' in a couple of places in this proof: someone please doublecheck?  Karen checked and it seems correct with Sian's changes.}
 For each $i \in [n]$, let $I_i$ be the set of vertices assigned to the propagators of $W$ by Algorithm~\ref{alg:put GN on WLD} with starting vertex $i$.
@@
 If $p$ is not supported on $i+1$, then in building $I_{i+1}$ we will assign the same propagators as in the construction of $I_i$ from vertices $i+1$ up to $b-1$, that is $I_{i+1} \cap [i+1,b-1] = I_{i} \cap [i+1,b-1]$.
-(If $p$ is supported on $i+1$, then $b= i+1$ and the interval $[i+1,b-1]$ is empty.) Furthermore, by Lemma~\ref{vertex cyclic int lem} it must happen that $p$ contributes vertex $b$ to $I_{i+1}$, as otherwise $b$ would never be contributed by $p$.
+If $p$ is supported on $i+1$, then $b= i+1$ and the interval $[i+1,b-1]$ is empty, so the previous equality remains true, albeit vacuously.
+Furthermore, by Lemma~\ref{vertex cyclic int lem} it must happen that $p$ contributes vertex $b$ to $I_{i+1}$, as otherwise $b$ would never be contributed by $p$.
 Consequently, in building $I_{i+1}$, when the algorithm reaches vertex $b$ there cannot be any remaining unassigned propagators that are supported on $b$ and clockwise of $p$.
 This is also true in when the algorithm constructing $I_i$ reaches $b$, since the same propagators have been assigned beforehand.
-Finally, we also note that $m\geq_i b+1$.
+This also implies that $m\geq_i b+1$.
 
@@
 \begin{proof}
-We have shown that $(I_1,\dots,I_n)$ is a Grassmann necklace; it remains to check that this Grassmann necklace corresponds to the positroid $M(W)$.
+We have shown in the previous theorem that $(I_1,\dots,I_n)$ is a Grassmann necklace; it remains to check that this Grassmann necklace corresponds to the positroid $M(W)$.
 Recall from the discussion following Definition~\ref{def:grassmann necklace}, and equation \eqref{basesofmatroids} in particular, that it suffices to show:
@@
 Now repeat the argument above with $p_s$ in place of $p_r$: if the other end of $p_s$ lands on an edge between $q$ and $j_m$ then we have $q \in \cP_{m-1}$ as above; if not then there exists some $p_t \in Q_{l-3}$ with $p_s$ supported on $I_i(p_t)$ and $q$ on the inside of $p_t$ in the $a_t-1$ order.
-Thereofore \hlfix{$I_i(p_t) <_i I_i(p_r)$}{$I_i(p_t) <_i I_i(p_s)<_i I_i(p_s)$?
+Therefore \hlfix{$I_i(p_t) <_i I_i(p_r)$}{$I_i(p_t) <_i I_i(p_s)<_i I_i(p_s)$?
 Or is the implication clear enough not to be mentioned}\note{Nope: we just need $<_i I_i(p_r)$.

### 2019-08-16 GWLDCII.tex
more comments and corrections, now to the end

@@
 \[|\cP| + \text{ the dimension of associated positroid cell}.\]
+\note{What if instead of displaying this we wrote ``is the sum of $\|\cP\|$ and the dimension fo the associated positroid cell.''}
 In other words, the Deodhar component associated to a Wilson loop diagram is $4|\cP|$, showing that the geometry underlying the Wilson loop diagrams is consistent with the geometry underlying the Amplituhedron.
@@
 \begin{proof}
-  By Algorithm~\ref{alg:put GN on WLD} the Grassmann necklace of $W$ is obtained from the Grassmann necklace of $V$ by duplicating the $i$th element of the Grassmann necklace of $V$ (shifting indices by $1$ for all indices greater than $i$), and incrementing all indices greater than $i$ by $1$ in each Grassmann necklace element.
+  By Algorithm~\ref{alg:put GN on WLD} the Grassmann necklace of $W$ is obtained from the Grassmann necklace of $V$ by duplicating the $i$th element of the Grassmann necklace of $V$ (shifting indices by $1$ for all indices greater than $i$), and incrementing all indices greater than $i$ by $1$ in each Grassmann necklace element\note{This is saying to increment twice in a way which I think is confusing, but presumably the parenthetical remark was put there to try to clarify something so I don't want to just remove it}.
 Formally, if $I_1^{V}, \ldots, I_{n-1}^{V}$ and $I_1^{W}, \ldots, I_n^{W}$ are the Grassmann necklaces of $V$ and $W$ respectively then
@@
 it must be a column label.
-The shapes of the Le diagram of $V$ and $W$ are the same except for the insertion of this column since $I_1^*$ is the same for $V$ and $W$ except for the incrementation of the indices $\geq i$ in the transition from the necklace for $V$ to the necklace for $W$.
+The shapes of the Le diagram of $V$ and $W$ are the same except for the insertion of this column since $I_1^*$\note{I don't find the star very helpful here; different area's conventions maybe} is the same for $V$ and $W$ except for the incrementation of the indices $\geq i$ in the transition from the necklace for $V$ to the necklace for $W$.
 \end{proof}
@@
 We first consider $I_1^{W}$, i.e.
-the set obtained by applying the Grassmann necklace algorithm to $W$ with starting vertex 1.
+the set obtained by applying the Grassmann necklace algorithm to $W$ with starting vertex 1\note{I don't find this i.e.
+helpful at this point, is it an old thing that can go or do others find it useful?}.
 Note that $n-3 \not\in I_1^{V}$: for Case 2 this is clear from the diagram (since Algorithm~\ref{alg:put GN on WLD} would assign $q$ no later than vertex $n-4$), while for Case 1 it follows from Lemma \ref{lem no fourth vertex}.
@@
 Finally, if $n-2,n-1 \in I_{n-2}^{V}$ then $I_{n-2}^W(q) = n-2$ and $I_{n-2}^W(p) = n-1$ as above, but this is different to what occured in $I_{n-2}^{V}$ so we cannot use the same argument as above.
-When the algorithm $I_{n-2}^W$ reaches vertex $n$, the only propagators $p$ and $q$ have contributed; thus we proceed as in the construction of $I_n^{V}$ but without propagator $q$.
+When the algorithm $I_{n-2}^W$ reaches vertex $n$, only the propagators $p$ and $q$ have contributed; thus we proceed as in the construction of $I_n^{V}$ but without propagator $q$.
 By Lemma~\ref{vertex cyclic int lem} we know that $I_n^V(q) = n-5$, and from the diagram we see that the only way this could occur is if all other propagators in $V$ had already been assigned when we reached vertex $n-5$; thus $q$ was the final propagator to be assigned in $I_n^{V}$.
@@
 \hlfix{Explicitly, $\mathcal{B}$ is the set of columns with labels $v < n-3$ and $\mathcal{A}$ is the set of columns labeled by $n$, $n-1$ and $n-2$ in $V$.
-In $W$, $\mathcal{A}$ consists of these columns without the last row.}{is this accurate?} Over the course of the next few lemmas we will prove that the plusses in the $\mathcal{B}$ parts of each diagram are identical, and that the relationship between the plusses in the $\mathcal{A}$ regions can be described explicitly.
+In $W$, $\mathcal{A}$ consists of these columns without the last row.}{is this accurate?}\note{I think it is accurate} Over the course of the next few lemmas we will prove that the plusses in the $\mathcal{B}$ parts of each diagram are identical, and that the relationship between the plusses in the $\mathcal{A}$ regions can be described explicitly.
 
@@
 
-Finally, we also note that when we speak of a plus in the Le diagram of $V$ being the same as in $W$ or vice versa, we mean that the position of the plus in $\mathcal{A}$ or $\mathcal{B}$ is the same; because of the column insertion the absolute indices may differ.
+Finally, we also note that when we speak of a plus in the Le diagram of $V$ being the same as in $W$ or vice versa, we mean that the position of the plus in $\mathcal{A}$ or $\mathcal{B}$ is the same.
 
@@
 In this section, we investigate the poles of the integrand for $I(W)$, that is $R(W)$ as defined in Definition~\ref{def R(W)}.
-It is conjectured that for a fixed number of propagators and a given set of external twistors $\cZ$, [cite] \bas \sum_{W | |\cP| = k} I(W)(\cZ) <\infty \;.\eas In otherwords, all poles of the intergrals must cancel.
+It is conjectured that for a fixed number of propagators and a given set of external twistors $\cZ$, [cite]\note{A cite still waiting} \bas \sum_{W | |\cP| = k} I(W)(\cZ) <\infty \;.\eas In otherwords, all poles of the intergrals must cancel.
 As a step towards this, in this section, we prove some results about $R(W)$.
@@
 
-That is, each $r_i$ is the determinant of the minor determined by the propagators (rows) that contribute different values (columns) to the $i^{th}$ element of the Grassmann necklace than they did to the $i-1^{th}$.
-
-As we discuss the algorithm it will also be useful to have the notation $\Delta_{I_i}$ for the determinant of the $k\times k$ minor of $C(W)$ with columned indexed by $I_i$.
+That is, each $r_i$ is the determinant of the minor determined by the propagators (rows) that contribute different values (columns) to the $i^{th}$ element of the Grassmann necklace than they did to the $i-1^{st}$.
+
+As we discuss the algorithm it will also be useful to have the notation $\Delta_{I_i}$ for the determinant of the $k\times k$ minor of $C(W)$ with columns indexed by $I_i$.
 
@@
 
+\note{I would like to discuss the angles of the arrows in fig 14}
 \begin{figure}
@@
 
-The irriducible quadratic factor corresponds to the fact that $q$ and $s$ share an edge {\em and} contribute both endpoints of that edge to $I_7$; see Proposition~\ref{prop alg gives rad} below.
+The irreducible quadratic factor corresponds to the fact that $q$ and $s$ share an edge {\em and} contribute both endpoints of that edge to $I_7$; see Proposition~\ref{prop alg gives rad} below.
 
@@
 Therefore $\Delta_{I_i} = \det A \det C$, and both factors are nontrivial since at least one of $m$ and $m+1$ appear in $I_i$.
-Since $p\in \cP_{in}(p)$ we have $f|\det A$ and if we remove the propagator outside of $p$ that contributes $m$ or $m+1$, we get a diagram with fewer propagators for which $\det A | \Delta_{I_i}$.
+Since $p\in \cP_{in}(p)$ we have $f|\det A$ and if we remove the propagator outside of $p$ that contributes $m$ or $m+1$, we get a diagram with fewer propagators for which $\det A | \Delta_{I_i}$, hence $f|\Delta_{I_i}$.
 This contradicts the minimality of our choices.
@@
 Again two things can now happen.
-If some vertex $j$ or larger (with respect to $>_i$) belongs to $I_i$ then $B$ and $C$ are at least one column wide, and so the block form of the matrix gives a nontrivial factorization of $\Delta_{I_i}$.
-This yields a contradiction as in Case 1: either $W$ contains unnecessary propagators which contradicts our minimality assumption, or $\det A$ is quadratic which contradicts the assumption that $p$ and $i$ contribute to $f$, an irreducible factor of degree at least 3.
+If some vertex $j$ or larger (with respect to $>_i$) belongs to $I_i$ then $B$ and $C$ are at least one column wide, and so the block form of the matrix gives a nontrivial factorization of $\Delta_{I_i}=\det A\det B$.
+This yields a contradiction as in Case 1: $f|\det A$ and removing a propagator not in $S$ gives a smaller diagram with a factor of degree $\geq 3$ which contradicts our minimality assumption.\note{I rephrased this last sentence quite a bit because earlier things had gotten rephrased}
 
@@
 
-Now suppose two variables from the row $p$ appear in a quadratic factor $f$.
+Now suppose two variables from the row $p$ appear in a quadratic factor $f$ of $\Delta_{I_i}$.
 By part (3), there is another propagator $q$ and an edge $(a,b)$ such that $f$ is the $2\times 2$ minor coming from $p, q$ and $a, b$, with $I_i(p)=a$, $I_i(q)=b$.
@@
 Since $I_{i-1}(p) \neq a$, there must be some other propagator $s$ with $I_{i-1}(s) = a$ (else $I_{i-1}$ assigns $q$ to $a$).
-This propagator cannot lie on edge $(a,b)$ since by Lemma~\ref{vertex cyclic int lem} we must have $I_i(s) = a$ or $b$, contradicting the fact that $I_i(p) = a$ and $I_i(q) = b$; thus $s$ has an end on $(a-1,a)$ and is inside $p$ from the point of view of $i-1$.
-
-Say $s$ is supported on $(j, j+1, a-1, a)$ and $p$ is supported on $(k, k+1, a, b)$ with $i-1 \leq_{i-1} k+1 \leq_{i-1} j+1$.
-But by Lemma~\ref{lem no fourth vertex}, if $I_{i-1}(s) = a$ then $a$ cannot be maximal in the support of $s$ with respect to $<_{i-1}$; thus we must have $i-1 = j+1$, and we are in the situation in figure~\ref{fig part 4}.
+This propagator cannot lie on edge $(a,b)$ since, by Lemma~\ref{vertex cyclic int lem}, we must have $I_i(s) \in \{a, b\}$, contradicting the fact that $I_i(p) = a$ and $I_i(q) = b$; thus $s$ has an end on $(a-1,a)$ and is inside $p$ in the $<_k$ order where $p=(k,a)$.
+
+Say $s = (j,a)$ with $i-1 \leq_{i-1} k+1 \leq_{i-1} j+1$.
+But by Lemma~\ref{lem no fourth vertex}, if $I_{i-1}(s) = a$ then $a$ cannot be maximal in the support of $s$ with respect to $<_{i-1}$; thus we must have $i-1 = j+1$, and we are in the situation in Figure~\ref{fig part 4}.
 
@@
 Since $p$ changed its association from $I_{i-1}$ to $I_i$, we have $I_{i-1}(p) = i-1$ by Lemma~\ref{vertex cyclic int lem}.
-From figure~\ref{fig part 4} it follows that $I_{i-1}$ assigns $p$ to $i-1$ and then proceeds identically to $I_i$ for all vertices inside $p$, implying that $I_{i-1}(s) = I_i(s)$.
+From Figure~\ref{fig part 4} it follows that $I_{i-1}$ assigns $p$ to $i-1$ and then proceeds identically to $I_i$ for all vertices inside $p$, implying that $I_{i-1}(s) = I_i(s)$.
 Since $I_{i-1}(s) = a$ and $I_i(s) \neq a$, this is a contradiction.
@@
 \begin{proof}
-The equivalence up to scalar multiple of $R$ and the radical of $\prod_{i=1}^n \Delta_{I_i}$ is due to Proposition~\ref{prop alg gives rad}.
+The equivalence of the ideal generated by $R$ and the radical of the ideal generated by $\prod_{i=1}^n \Delta_{I_i}$ is due to Proposition~\ref{prop alg gives rad}.
 It remains to prove that $R(W)$ is the $R$ of Algorithm~\ref{alg WLD to denom via GN}.
@@
 To this end, first note that $R(W)$ and $R$ both have total degree $4|\mathcal{P}|$; the degree of $R(W)$ is immediate from the definition while that of $R$ follows from Lemma~\ref{vertex cyclic int lem}.
-By Proposition~\ref{prop alg gives rad} every factor of $R$ is either a single variable or a quadratic factor coming from two propagators supported on a common edge.
-The factors of each $R_e$ making up $R(W)$ in the notation of Definition~\ref{def R(W)} are all of this form and hence every factor of $R$ divides $R(W)$.
+By Proposition~\ref{prop alg gives rad} every factor of $R$ is either a quadratic factor coming from two propagators supported on a common edge or a single variable coming from a support vertex of a propagator not appearing in a quadratic factor.
+The factors of each $R_e$ making up $R(W)$ in the notation of Definition~\ref{def R(W)} are all of this form and every such factor occurs.
+Hence every factor of $R$ divides $R(W)$.
 Finally, since $R$ is squarefree, this implies that $R(W)$ is a scalar multiple of $R$.
@@
 
-While the authors cannot yet offer a proof that the appropriate sum of the Wilson loop diagrams are, in fact, finite, as conjectured [cite], we do hope that this relationship to the Grassmann Necklace elements will provide a different avenue for answering that and related questions.
+While the authors cannot yet offer a proof that the appropriate sum of the Wilson loop diagrams are, in fact, finite, as conjectured [cite]\note{One last cite to fill out}, we do hope that this relationship to the Grassmann Necklace elements will provide a different avenue for answering that and related questions.
 

### 2019-08-16 GWLDCII.tex
more readthrough

--- 2019-08-15 GWLDCII.tex
@@
 Our primary focus is Wilson loop diagrams with $V = [n]$, so in order to simplify the exposition we will often use $i+1$ as shorthand for ``the successor of vertex $i$''.
-\note{We say this here and then again in the paragraph after length.
-Can we discuss how to say it once in a clear and concise way.}
 
@@
 
-In particular, we will see in later sections that all four vertices supporting a propagator are important in understanding the contribution of that propagator to the \st{overall diagram}{geometric object represented by the diagram} \sanote{Is this what we mean?}\note{Is this chatty bit even helpful at all: this seems like the most natural notion of subobject anyway.}.
+In particular, we will see in later sections that all four vertices supporting a propagator are important in understanding the contribution of that propagator to the \st{overall diagram}{geomtric object represented by the diagram} \sanote{Is this what we mean?}.
 This motivates the following definition of a subdiagram, any subset $Q$ of the propagators and any subset $U$ of the vertices of $W$ {\em containing the support of $Q$}.
@@
 These diagrams correspond to (tree level) amplitudes of SYM $N=4$ theory in twistor space.
-As such, it\note{What is this ``it'', is it ``these diagrams'' if so there's a singular/plural agreement problem, if not then it isn't clearly enough written.} associates a real value to $n$ particles, one for each vertex.
+As such, it associates a real value to $n$ particles, one for each vertex.
 Each particle is represented as a section of a $|\cP|$-vector bundle over twistor space, projected onto a real subspace in a process called bosonization \cite{Arkani-Hamed:2013jha}.
@@
 \sanote{This feels like too much detail.
-Thoughts?}\note{Seems ok to me, at least with the grammar fixed as noted above} This integral is comprised of two main components, and interaction matrix, $C(W)$ and a volume form, $\Omega(W)$.
+Thoughts?} This integral is comprised of two main components, and interaction matrix, $C(W)$ and a volume form, $\Omega(W)$.
 These are described below.
@@
 The matrix $C(W)$ can be interpreted as a \hlfix{parametrization of the positroid cell associated to $W$}{I know we've been saying this, but we have $4k$ parameters for a $3k$ dimensional space.
-Is this okay?}\note{Maybe there's a better word than ``parametrization''?
-It does define the positroid cell by giving its points, we wouldn't need to say parametrizaion to say that.} in the positive Grassmannian $\Gr(n, |\cP|)$, which we denote by $\Sigma(W)$ \cite{wilsonloop}.
+Is this okay?} in the positive Grassmannian $\Gr(n, |\cP|)$, which we denote by $\Sigma(W)$ \cite{wilsonloop}.
 Most of the work in this paper, and in \cite{generalcombinatoricsI} focuses on characterizing the positroid cell associated to each Wilson loop diagram $W$.
@@
 Let $\{p_1 \ldots p_r\}$ be the propagators with one end lying on edge $e$ under a counterclockwise orderin.
-That is, $p_1$ is closest to the vertex $e$, $p_i$ is positioned counterclockwise to $p_{i+1}$ and $p_r$ is the clockwise most propagator on this edge (closest to vertex $e+1$).
+That is, $p_1$ is closest to the vertex $e$, $p_i$ is positioned counterclockwise to $p_{i+1}$ and $p_r$ is the clockwise most propagator on this edge (closest to $e+1$).
 Define the polynomial
@@
 
-For our purposes, a {\bf positroid} is\footnote{Note that matroid isomorphism allows arbitrary permutations of the ground set but positroid isomorphism allows only cyclic permutations, so the property of being a positroid is not in general preserved by matroid isomorphism.} a matroid $M$ (with ground set $[n]$ and bases $\cB \subseteq \binom{[n]}{k}$) which can be represented by an element of the positive Grassmannian $\Gr(k,n)$.
-In other words, there exists a full-rank $k\times n$ real matrix whose $k\times k$ minors are all nonnegative and such that the minor $[[k]|J]$\note{I don't think we have this $[[k]|J]$ notation defined?} is positive if and only if $J \in \cB$.
+For our purposes, a {\bf positroid} is a matroid $M$ (with ground set $[n]$ and bases $\cB \subseteq \binom{[n]}{k}$) which can be represented by an element of the positive Grassmannian $\Gr(k,n)$.
+In other words, there exists a full-rank $k\times n$ real matrix whose $k\times k$ minors are all nonnegative and such that the minor $[[k]|J]$ is positive if and only if $J \in \cB$.
 
@@
 This in turn induces a total order on $\binom{[n]}{k}$, namely the lexicographic order with respect to $<_j$.
-It also induces a separate partial order $\gale{j}$ on $\binom{[n]}{k}$ (the {\bf Gale order} \cite{Gale}\note{We only use this once and in this particular section, so maybe we don't need to define and name it but can just put the def in-line where we need it}), which is defined as follows: for
+It also induces a separate partial order $\gale{j}$ on $\binom{[n]}{k}$ (the {\bf Gale order} \cite{Gale}), which is defined as follows: for
 \[A = \{a_1 <_j a_2 <_j \dots <_j a_k\} \text{ and } B = \{b_1 <_j b_2 <_j \dots <_j b_k\} \in \binom{[n]}{k},\] we define
@@
 
-In \cite{wilsonloop}, Agarwala and Marin-Amat show that $M(W)$ is also characterized by the Wilson loop diagram itself\note{I don't like this phrasing; can we discuss}:
+In \cite{wilsonloop}, Agarwala and Marin-Amat show that $M(W)$ is also characterized by the Wilson loop diagram itself:
 
@@
 \end{dfn}
-Note that we have $p\in \cP_{in}(p, <_i)$ and so $\cP_{in}(p, <_i) = \cP_{out}(p, <j)\cup\{p\}$.
 
@@
   \begin{enumerate}
-    \item $W$ has a propagator of length $\leq 6$ with a propagator of length 2 on one side of it and nothing else on that side.\label{item big and 2}
+    \item $W$ has a propagator of length $\leq 6$ with a propagator of length 2 on one side it and nothing else on that side.\label{item big and 2}
     \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator ends between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
@@
 \end{lem}
-\note{Should this lemma have pictures}
 
@@
 However this is clear later.
-Do we care?}\note{No, we don't quite want that either because we don't want the newly shortened $q_r$ to be our propagator of length 2 -- maybe a slight change to the remark} be the subdiagram of $W$ consisting only of those propagators inside $q_r$ (including $q_r$ itself); in particular $W_r$ contains none of the previous $p_i$ or $q_i$.
+Do we care?} be the subdiagram of $W$ consisting only of those propagators inside $q_r$ (including $q_r$ itself); in particular $W_r$ contains none of the previous $p_i$ or $q_i$.
 By the original hypotheses on $W$, every vertex in $[i_r,k_{r+1}]$ (of which there are at least 4, since $\ell(q_r) \geq 4$) must support at least one propagator.
@@
 (See Figure~\ref{fig smallest q in lem sian}.) Therefore without loss of generality we may assume that $\cP_{in}(q_r)$ does not contain any propagators (other than $q_r$ itself) which satisfy the induction hypotheses, \st{i.e.
-we assume that there are no other propagators with $p_{r+1}$ on one side and $q_r$ on the other}.\note{I kind of like the struck part, can we make your other changes and also keep the struck part.}
+we assume that there are no other propagators with $p_{r+1}$ on one side and $q_r$ on the other}.
 
@@
 
-\note{Would it be worth having vertex $j_{r+1}$ labelled in this fig smallest q in lem sian}
-
 There are two cases to consider.
@@
 
-The second case, \hlfix{there are at least $3$ vertices between one endpoint of $p_{r+1}$ and the nearest endpoint of $q_r$.}{Does this just convolute matters?}\note{Well at some stage it got edited so that it isn't a sentence any longer, but I think something like this should be here because it defines what the second case is.} In other words,  (at least) one of the following four things happen:
+The second case, \hlfix{there are at least $3$ vertices between one endpoint of $p_{r+1}$ and the nearest endpoint of $q_r$.}{Does this just convolute matters?} In other words,  (at least) one of the following four things happen:
 \begin{itemize} 
@@
 The overall result then follows by induction.
-
 \end{proof}
@@
 Until now, the positroid associated to a Wilson loop diagram $W$ could only be obtained by computing the matrix $C(W)$ associated to $W$, listing all bases of the induced matroid $M(W)$, and constructing the Le diagram or Grassmann necklace of the positroid ``by eye'' from this list.
-\note{Can we discuss how to say this in a way that doesn't appear weak.}
 
@@
 \begin{algorithm}\label{alg:put GN on WLD}
-Let $W = (\cP, [n])$ be an admissible Wilson loop diagram.
-In order to construct the set set $I_i^W$ (or just $I_i$ when $W$ is clear from context\note{We have gone from not pointing out this convention to pointing it out 3 times.
-Can we find a happy medium?}) for $i \in [n]$, perform the following steps:
+Let $W = (\cP, [n])$ be an admissible Wilson loop diagram. In order to construct the set set $I_i^W$ (or just $I_i$ when $W$ is clear from context) for $i \in [n]$, perform the following steps:
 
@@
 \begin{itemize}
-\item $j = 1$: Since $\Prop(1) = \{q,r\}$ and $r$ is the clockwise-most of these propagators, we let $I_1 = \{1\}$ and remove propagator $r$ from the diagram. 
-\item $j = 2$: $\Prop(2) = \{p,q\}$, with $q$ being the clockwise-most of these propagators. So $I_1 = \{1,2\}$ and propagator $q$ is removed.
-\item $j = 3$: $\Prop(3) = \{p\}$, so now $I_1 = \{1,2,3\}$ and propagator $p$ is removed. The only remaining propagator in the diagram is $s$.
+\item $j = 1$: Since $\Prop(1) = \{q,r\}$ and $r$ is the clockwise-most of these propagators, $r$ contributes at this step: $I_1(r)=1$.
+We let $I_1 = \{1\}$ and remove propagator $r$ from the diagram.
+\item $j = 2$: $\Prop(2) = \{p,q\}$, with $q$ being the clockwise-most of these propagators, $q$ contributes at this step: $I_1(q)=1$. So $I_1 = \{1,2\}$ and propagator $q$ is removed.
+\item $j = 3$: $\Prop(3) = \{p\}$, so now $I_i(p) = 3$ and $I_1 = \{1,2,3\}$. The propagator $p$ is removed. The only remaining propagator in the diagram is $s$.
 \item $j = 4$: Since $p$ and $q$ were removed in earlier steps, we now have $\Prop(4) = \emptyset$.
-\item $j = 5$: $\Prop(5) = \{s\}$, and we have $I_1 = \{1,2,3,5\}$.
+\item $j = 5$: $\Prop(5) = \{s\}$, and we have $I_1 = \{1,2,3,5\}$ with $I_1(s) = 5$.
 \end{itemize}
@@
 \[1235, 2356, 3456, 4567, 5671, 6712, 7812, 8123.\]
-The reader can easily verify that this sequence of $k$-sets satisfies the definition of a Grassmann necklace, and can (with significantly more work) also verify that this Grassmann necklace defines the positroid $M(W)$ associated to the Wilson loop diagram $W$ above, as we will prove in general shortly.
+The reader can easily verify that this sequence of $k$-sets satisfies the definition of a Grassmann necklace, and can (with significantly more work) also verify that this Grassmann necklace defines the positroid $M(W)$ associated to the Wilson loop diagram $W$ above.
 \end{eg}
+
+Notice that for each element in the Grassmann necklace, the propagators contribute in a particular order. It is sometimes useful to think of the propagators in this order. 
+\begin{dfn} \label{prop order dfn}
+Given a set $\cP$ of $k$ propagators defining a Wilson loop diagram $(\cP, [n])$, the Grassmann necklace element $I_i$ imposes an ordering on it $\cP^i = \{p_1 \ldots p_k\}$ where $p_m$ is the $m^{th}$ propagator to contribute to $I_i$.
+We write $\cP_m^i = \{p_1 \ldots p_m\}$ to be the first $m$ propagators that contribute to $I_i$.
+\end{dfn}
+
+In the sequel, when we refer to orderings on propagators, we refer to the ordering $\cP^i$.
+Note that different elements of the Grassmann necklace impose different orderings on the propagators.
+\hlfix{{Furthermore, Lemma \ref{no fourth vertex} shows that this ordering respects the ordering of vertices in $I_i$.
+That is, $I_i(p_j) <_i I_i(p_l)$ for all $j <l$.}}{Maybe move closer to reference lemma}
 
@@
 
-With this setup, if we can find a vertex $\ell$ (with $\ell <_i i$ and $\ell <_m m$) such that the configuration of propagators ending in the interval $(j-1, \ldots, \ell+1)$ is identical in both $W'$ and $V'$, then the vertices contributed to $I_i^W$ and $I_m^V$ are the same from step $j$ to step $\ell$ (inclusive).
+With this setup, if we can find a vertex $\ell$ (with \st{$\ell <_i i$ and $\ell <_m m$} {\color{violet} $i <_i \ell$ and $m <_m \ell$?}) such that the \emph{configuration} of propagators ending in the interval \st{$(j-1, \ldots, \ell+1)$} {\color{violet}$[j, l]$} is identical in both $W'$ and $V'$, then the vertices contributed to $I_i^W$ and $I_m^V$ are the same from step $j$ to step $\ell$ (inclusive).
 See Figure~\ref{fig:locally identical} for an illustration of this.
@@
 	\begin{scope}
-	\drawWLDfragment[12]{3}{0.4} 
+	W' = \drawWLDfragment[12]{3}{0.4} 
 	%\drawnumberspartial % use this to debug
@@
 \begin{tikzpicture}[baseline=(current bounding box.east)]
-	\begin{scope}
+	V' = \begin{scope}
 	\drawWLDfragment[12]{3}{0.4} 
@@
 \caption{$W'$ and $V'$ are locally the same between $j$ and $l+1$, so we will have $I_i^W\cap [j,l] = I_m^V\cap[j,l]$ even though $p \neq s$ and $q \neq t$.}\label{fig:locally identical}
-\end{figure}
+\end{figure} \sanote{just checking, we are allowing the first and the last propagators (in the $I_i$ induced ordering) to be different, but not the internal ones?}
 \end{rmk}
@@
 With that in mind, we are ready to begin proving properties of the algorithm.
-We first show that the algorithm can never reach the final vertex in a propagator's support without having already assigned that propagator; in particular, this guarantees that the construction of $I_i$ always terminates in fewer than $n$ steps.
+We first show that the algorithm for $I_i$ can never reach the final vertex (in the $<_i$ order) in a propagator's support without having already assigned that propagator; in particular, this guarantees that the construction of $I_i$ always terminates in fewer than $n$ steps.
 

### 2019-08-16 GWLDCII.tex

--- 2019-08-16 GWLDCII.tex
@@
 
+Notice that for each element in the Grassmann necklace, the propagators contribute in a particular order. It is sometimes useful to think of the propagators in this order. 
+\begin{dfn} \label{prop order dfn}
+Given a set $\cP$ of $k$ propagators defining a Wilson loop diagram $(\cP, [n])$, the Grassmann necklace element $I_i$ imposes an ordering on it $\cP^i = \{p_1 \ldots p_k\}$ where $p_m$ is the $m^{th}$ propagator to contribute to $I_i$.
+We write $\cP_m^i = \{p_1 \ldots p_m\}$ to be the first $m$ propagators that contribute to $I_i$.
+\end{dfn}
+
+In the sequel, when we refer to orderings on propagators, we refer to the ordering $\cP^i$.
+Note that different elements of the Grassmann necklace impose different orderings on the propagators.
+\hlfix{{Furthermore, Lemma \ref{no fourth vertex} shows that this ordering respects the ordering of vertices in $I_i$.
+That is, $I_i(p_j) <_i I_i(p_l)$ for all $j <l$.}}{Maybe move closer to reference lemma}
+
 \begin{rmk}\label{rmk algorithm locally same}

### 2019-08-16 GWLDCII.tex
stopped in the middle of 3.13 with concerns

@@
 We write $\cP_m^i = \{p_1 \ldots p_m\}$ to be the first $m$ propagators that contribute to $I_i$.
+We drop the superscript if the Grassman necklace element is clear.
 \end{dfn}
@@
 Note that different elements of the Grassmann necklace impose different orderings on the propagators.
-\hlfix{{Furthermore, Lemma \ref{no fourth vertex} shows that this ordering respects the ordering of vertices in $I_i$.
-That is, $I_i(p_j) <_i I_i(p_l)$ for all $j <l$.}}{Maybe move closer to reference lemma}
+Furthermore, Lemma \ref{no fourth vertex} shows that this ordering respects the ordering of vertices in $I_i$.
+That is, $I_i(p_j) <_i I_i(p_l)$ for all $j <l$.\sanote{Maybe move closer to reference lemma}
+
+\begin{rmk} \label{clockwise ordering rem}
+When $p_m$ contributes $I_i(p_m) = a_m$ to the Grassmann necklace, it must be the clockwise-most propagator (amongst those not yet assigned) that is supported on $a_m$ i.e.
+any other propagator in $\cP \setminus \cP_{m-1}$ that is supported on $a_m$ must be inside $p_m$ in the $a_m-1$ ordering.
+\end{rmk} \sanote{We use this fact at least twice below}
 
@@
 Suppose for contradiction that we have $i \in [n]$ and $p \in \cP$ such that $I_i(p)$ is $<_i$-maximal in $V(p)$.
-There are two possibilities, which are illustrated in Figure~\ref{fig:no fourth vertex}: either $p = (i-1,b)$ for some $b$ (so $i$ and $I_i(p) = i-1$ are the two ends of a single edge), or $p = (a,b)$ with $i\leq_i a <_i b$ and $I_i(p) = b+1$.
+There are two possibilities, which are illustrated in Figure~\ref{fig:no fourth vertex}: \st{either $p = (i-1,b)$ for some $b$ (so $i$ and $I_i(p) = i-1$ are the two ends of a single edge), or $p = (a,b)$ with $i\leq_i a <_i b$ and $I_i(p) = b+1$.} {\color{violet}either $i-1 \in V(p)$, in which case it is the last vertex in the $<_i$ order and $I_i(p)= i-1$, or $i-1 \not \in V(p)$ in which case,  $p= a, b$, $i \in [b+2, a]$ and $I_i(p) = b+1$.}
 
@@
 \end{figure}
-\note{Question: is the diagram clearer in this configuration (starting vertex $i$ matches up in both) or in the old configuration (propagator $p$ matches up)?}
-
-In Case 1, observe that we must have another propagator $q = (c,b)$ with $c<_i b$ and $I_i(q) = b+1$, because otherwise $I_i$ would assign $p$ to $b+1$.
-Now $q$ also contributes the $<_i$-maximal vertex in its support to $I_i$ and is an instance of Case 2.
+\note{Question: is the diagram clearer in this configuration (starting vertex $i$ matches up in both) or in the old configuration (propagator $p$ matches up)?} \sanote{I think it is fine as is}
+
+In Case 1, \st{observe that we must have another propagator $q = (c,b)$ with $c<_i b$ and $I_i(q) = b+1$, because otherwise $I_i$ would assign $p$ to $b+1$.}{\color{violet} since $b+1<_i I_i(p)$ there must be some propagator, $q$ before $p$ in $\cP^i$ such that $I_i(q) = b+1$.
+By remark \ref{clockwise ordering rem}, $p$ is inside $q$ in the $<_b$ order.
+Specifically, $q$ must also end on the $b^{th}$ edge.
+By non-crossing and desnity arguements of admissibility $i-1$ cannot be in $V(q)$.} Now $q$ also contributes the $<_i$-maximal vertex in its support to $I_i$ and is an instance of Case 2.
 Therefore it suffices to show that no admissible Wilson loop diagram admits the configuration illustrated in Case 2 of Figure~\ref{fig:no fourth vertex}.
@@
 So let $p = (a,b)$ with $a<_ib$ and $I_i(p) = b+1$, and choose $p$ such that $\big|[a+1,b]\big|$ is minimal amongst propagators of $W$ with this property.
+\sanote{in the picture for case 2, $\big|[d+1,b]\big| <\big|[a+1,b]\big|$.Worried about case 2}
 

### 2019-08-16 GWLDCII.tex
not doubling the discussin of successors

@@
 In contrast, the first paper in this series focuses on combinatorial and matroidal properties of the Wilson loop diagrams.
-The main focus of that paper is to enumerate the positroid cells that are associated to Wilson loop diagrams with a fixed number of vertices and propagators, as well as counting the number of Wilson loop diagrams in the pre-image of \hlfix{any positroid cell in the image of this association.}{I'd like to mildly rephrase this because it sounds like we know exactly which cells have non-empty pre-image, which isn't quite what we proved.} \sanote{changed}
+The main focus of that paper is to enumerate the positroid cells that are associated to Wilson loop diagrams with a fixed number of vertices and propagators, as well as counting the number of Wilson loop diagrams that map to the same positroid.
 
@@
 Let $[n]$ denote the set of integers $\{1,\dots,n\}$ with the obvious cyclic and linear orders.
-Our primary focus is Wilson loop diagrams with $V = [n]$, so in order to simplify the exposition we will often use $i+1$ as shorthand for ``the successor of vertex $i$''.
-\note{We say this here and then again in the paragraph after length.
-Can we discuss how to say it once in a clear and concise way.}
 
@@
 
-We also impose the convention that all vertices should always be interpreted in terms of the cyclic order on $V$; for example, if $V = [n]$ then $(n,n+3)$ means the propagator connecting edges $3$ and $n$.
+We also impose the convention that all vertices should always be interpreted in terms of the cyclic order on $V$.
+So, for any $i\in V$ we will use $i+1$ to denote the successor of $i$ in $V$.
+In particular, if $V = [n]$ then $(n,n+3)$ means the propagator connecting edges $3$ and $n$.
 This viewpoint is beneficial for us since many of our proofs rely on restricting our attention to a region of the diagram bounded by a given propagator, or to short propagators such as $(i,i+2)$, and these behave the same regardless of whether we cross the ``first'' vertex or not; however, we emphasize that this is different to the standard convention in the physics literature, where propagators are written $(i,j)$ with $1 \leq i<j \leq n$.

### 2019-08-16 GWLDCII.tex
more edits on the phone up to the ordering

@@
 We also show that the positroid cells associated to Wilson loop diagrams are all $3k$-dimensional; by contrast, the BCFW cells are all $4k$-dimensional \cite{Arkani-Hamed:2013jha}.
-Again, this is not too alarming, as it was shown in \cite{non-orientable} that the actual geometric space parametrized by the Wilson loop diagrams is a non-orientable $k$-dimensional bundle over this $3k$ dimensional manifold in $\Gr(k,n)$.
+Again, this is not too alarming, as it was shown in \cite{non-orientable} that the actual geometric space defined by the Wilson loop diagrams is a non-orientable $k$-dimensional bundle over this $3k$ dimensional manifold in $\Gr(k,n)$.
 
@@
 
-In particular, we will see in later sections that all four vertices supporting a propagator are important in understanding the contribution of that propagator to the \st{overall diagram}{geometric object represented by the diagram} \sanote{Is this what we mean?}\note{Is this chatty bit even helpful at all: this seems like the most natural notion of subobject anyway.}.
-This motivates the following definition of a subdiagram, any subset $Q$ of the propagators and any subset $U$ of the vertices of $W$ {\em containing the support of $Q$}.
+In particular, we will see in later sections that all four vertices supporting a propagator are important in understanding the contribution of that propagator to the objects represented by the diagram.
+This motivates the following definition of a subdiagram: any subset $Q$ of the propagators and any subset $U$ of the vertices of $W$ {\em containing the support of $Q$}.
 
@@
 These diagrams correspond to (tree level) amplitudes of SYM $N=4$ theory in twistor space.
-As such, it\note{What is this ``it'', is it ``these diagrams'' if so there's a singular/plural agreement problem, if not then it isn't clearly enough written.} associates a real value to $n$ particles, one for each vertex.
+As such, a diagram associates a real value to $n$ particles, one for each vertex.
 Each particle is represented as a section of a $|\cP|$-vector bundle over twistor space, projected onto a real subspace in a process called bosonization \cite{Arkani-Hamed:2013jha}.
@@
 This is represented as an integral $I(W)$, which is the equivalent of a Feynman integral in this setting.
-\sanote{This feels like too much detail.
-Thoughts?}\note{Seems ok to me, at least with the grammar fixed as noted above} This integral is comprised of two main components, and interaction matrix, $C(W)$ and a volume form, $\Omega(W)$.
+This integral is comprised of two main components, and interaction matrix, $C(W)$ and a volume form, $\Omega(W)$.
 These are described below.
@@
 0  & \textrm{ if } q \not \in V(p)  \end{cases}
-\;. \label{C(W) dfn}\end{equation} \todo{$c_{p,q}$ or $x_{p,q}$? Should be consistent}
+\;. \label{C(W) dfn}\end{equation} \todo{Change $c_{p,q}$ to $x_{p,q}$ to be consistent}
 
@@
 
-The matrix $C(W)$ can be interpreted as a \hlfix{parametrization of the positroid cell associated to $W$}{I know we've been saying this, but we have $4k$ parameters for a $3k$ dimensional space.
-Is this okay?}\note{Maybe there's a better word than ``parametrization''?
-It does define the positroid cell by giving its points, we wouldn't need to say parametrizaion to say that.} in the positive Grassmannian $\Gr(n, |\cP|)$, which we denote by $\Sigma(W)$ \cite{wilsonloop}.
+The matrix $C(W)$ defines a positroid cell associated to $W$ in the positive Grassmannian $\Gr(n, |\cP|)$, which we denote by $\Sigma(W)$ \cite{wilsonloop}.
 Most of the work in this paper, and in \cite{generalcombinatoricsI} focuses on characterizing the positroid cell associated to each Wilson loop diagram $W$.
@@
 When needed, we will impose various orders on these rows.
-This will not matter, as it does not affect the parametrization of $\Sigma(W)$.
+This will not matter, as it does not affect $\Sigma(W)$.
 
@@
 For our purposes, a {\bf positroid} is\footnote{Note that matroid isomorphism allows arbitrary permutations of the ground set but positroid isomorphism allows only cyclic permutations, so the property of being a positroid is not in general preserved by matroid isomorphism.} a matroid $M$ (with ground set $[n]$ and bases $\cB \subseteq \binom{[n]}{k}$) which can be represented by an element of the positive Grassmannian $\Gr(k,n)$.
-In other words, there exists a full-rank $k\times n$ real matrix whose $k\times k$ minors are all nonnegative and such that the minor $[[k]|J]$\note{I don't think we have this $[[k]|J]$ notation defined?} is positive if and only if $J \in \cB$.
+In other words, there exists a full-rank $k\times n$ real matrix whose $k\times k$ minors are all nonnegative and such that the minor given by the columns of $J$
+is positive if and only if $J \in \cB$.
 
@@
 
-In \cite{wilsonloop}, Agarwala and Marin-Amat show that $M(W)$ is also characterized by the Wilson loop diagram itself\note{I don't like this phrasing; can we discuss}:
+In \cite{wilsonloop}, Agarwala and Marin-Amat show that $M(W)$ can also be read directly from the Wilson loop diagram itself:
 
@@
 
-  Alternatively if we forget about the \st{matroid} {\color{violet} diagram} \sanote{okay?} and simply think about the condition of linear independence in the matrix $C(W)$, the corollary can also be proved directly by linear algebra and the definition of $C(W)$ as follows.
+  Alternatively we can simply think about the condition of linear independence in the matrix $C(W)$, the corollary can also be proved directly by linear algebra and the definition of $C(W)$ as follows.
 
@@
 
-However, in order to identify the positroid associated to a given Wilson loop diagram $W$ we first have to construct $C(W)$, then make a list of all its non-zero $k\times k$ minors and extract the Le diagram or Grassmann necklace via the methods described in Section~\ref{sec:positroid background}.
+However, to go from the Wilson loop diagram $W$ to the positroid cell, one had to go through the matroid explicitly realized via $C(W)$, then make a list of all its non-zero $k\times k$ minors and extract the Le diagram or Grassmann necklace via the methods described in Section~\ref{sec:positroid background}.
 In \cite{casestudy}, Agarwala and Fryer apply this process in the smallest non-trivial case: admissible Wilson loop diagrams with two propagators on six vertices.
@@
 Our first goal is therefore to find a better method of obtaining the positroid associated to a given Wilson loop diagram; this is the focus of the next section.
-\sanote{Should the 2 paras before the remark be moved to when whe walk about the GN algorithm?}
 
@@
 
-One of the key insights is that each element of the Grassmann necklace can be viewed as a function from the propagators of the diagram to the vertices in the \st{Grassmann necklace element}{\color{violet} Wilson loop diagram?}.
+One of the key insights is that each element of the Grassmann necklace can be viewed as a function from the propagators of the diagram to the vertices in the Grassman necklace element.
 This is captured in Definition~\ref{def I_i as a function}, and used throughout the paper.
@@
 Write $(p, <_i)$ to represent the same propagator directed from $i$ to $j$.
-Then the sets of propagators {\bf inside} \sanote{just checking: $p \in \cP_{in}(p)$?} and {\bf outside} of $(p,<_i)$ are defined to be
+Then the sets of propagators {\bf inside} and {\bf outside} of $(p,<_i)$ are defined to be
 \begin{gather*}\cP_{in}(p,<_i) = \{ (k,l) \in \cP \ |\ i \leq_i k <_i l \leq_i j \}, \\
@@
 \end{dfn}
-Note that we have $p\in \cP_{in}(p, <_i)$ and so $\cP_{in}(p, <_i) = \cP_{out}(p, <j)\cup\{p\}$.
+Note that we have $p\in \cP_{in}(p, <_i)$ and so $\cP_{in}(p, <_i) = \cP_{out}(p, <_j)\cup\{p\}$.
 
@@
 
-Note that we could replace $q_r$ by another propagator $q'_{r}$ in \st{$W_r$} {\color{violet}$W_r = (\cP_{in}(q_r), [n])$}\sanote{just want to emphasize that $q_r'$ is inside $q_r$}, as long as $p_{r+1}$ and $q_r$ are on opposite sides of $q_r'$: such a new $q'_{r}$ would still satisfy all of the induction hypotheses.
-(See Figure~\ref{fig smallest q in lem sian}.) Therefore without loss of generality we may assume that $\cP_{in}(q_r)$ does not contain any propagators (other than $q_r$ itself) which satisfy the induction hypotheses, \st{i.e.
-we assume that there are no other propagators with $p_{r+1}$ on one side and $q_r$ on the other}.\note{I kind of like the struck part, can we make your other changes and also keep the struck part.}
+Note that we could replace $q_r$ by another propagator $q'_{r}$ in $W_r = (\cP_{in}(q_r), [n])$, as long as $p_{r+1}$ and $q_r$ are on opposite sides of $q_r'$: such a new $q'_{r}$ would still satisfy all of the induction hypotheses.
+(See Figure~\ref{fig smallest q in lem sian}.) Therefore without loss of generality we may assume that $\cP_{in}(q_r)$ does not contain any propagators (other than $q_r$ itself) which satisfy the induction hypotheses, i.e.
+we assume that there are no other propagators with $p_{r+1}$ on one side and $q_r$ on the other.
 
@@
 there are at most two vertices between an endpoint of $p_{r+1}$ and an endpoint of $q_r$).
-Then since $p_{r+1}$ has length 2, \st{it must be that $(i_r+3)+1 \geq k_r-2$ and so} {\color{violet} this implies that} $q_r$ has length $\leq 6$.
+Then since $p_{r+1}$ has length 2, it must be that $(i_r+3)+1 \geq k_r-2$ and so $q_r$ has length $\leq 6$.
 By the minimality assumption on $q_r$, no propagator in $W_r$ has $q_r$ on one side and $p_{r+1}$ on the other side.
@@
 
-The second case, \hlfix{there are at least $3$ vertices between one endpoint of $p_{r+1}$ and the nearest endpoint of $q_r$.}{Does this just convolute matters?}\note{Well at some stage it got edited so that it isn't a sentence any longer, but I think something like this should be here because it defines what the second case is.} In other words,  (at least) one of the following four things happen:
+The second case is that there are at least $3$ vertices between one endpoint of $p_{r+1}$ and the nearest endpoint of $q_r$. In other words, (at least) one of the following four things happen:
 \begin{itemize} 
@@
 \item $i_r+3 \leq j_{r+1}+2\leq k_r-3$ (one endpoint of $p_{r+1}$ has at least 3 vertices between it and the nearest enpoint of $q_r$), or
-\item $i_r = j_{r+1}$ ($p_{r+1}$ and $q_r$ share and end edge), or 
-\item $k_r = j_{r+1} +2$  ($p_{r+1}$ and $q_r$ share and end edge)
+\item $i_r = j_{r+1}$ ($p_{r+1}$ and $q_r$ share an end edge), or 
+\item $k_r = j_{r+1} +2$  ($p_{r+1}$ and $q_r$ share an end edge)
 \end{itemize}
@@
 
-\st{Note that since} {\color{violet} Since there are at least $3$ vertices between one endpoint of $p_{r+1}$ and the nearest endpoint of $q_r$},  $j_{r+1}+4 \leq k_r-1$ in both of these situations, the vertex \hlfix{$j_{r+1}+4{\color{violet} \in [i_r, k_r+1]}$}{or is a vertex of $W_r$ in the restricted version, have explicitly removed notation about vertices being inside or outside} \st{is inside $q_r$} but does not support either $q_r$ or $p_{r+1}$, and must therefore support some other propagator $t$.
+Since there are at least $3$ vertices between one endpoint of $p_{r+1}$ and the nearest endpoint of $q_r$,  $j_{r+1}+4 \leq k_r-1$ in both of these situations, the vertex $j_{r+1}+4$ is in $[i_r, k_r+1]$ but does not support either $q_r$ or $p_{r+1}$, and must therefore support some other propagator $t$.
 Since $p_{r+1}$ is not part of configuration \ref{item pair of 2s} and $W_r$ has no propagators of length 3, it follows that $\ell(t) \geq 4$.
@@
 
-Until now, the positroid associated to a Wilson loop diagram $W$ could only be obtained by computing the matrix $C(W)$ associated to $W$, listing all bases of the induced matroid $M(W)$, and constructing the Le diagram or Grassmann necklace of the positroid ``by eye'' from this list.
-\note{Can we discuss how to say this in a way that doesn't appear weak.}
-
 In this section, we give an algorithm for passing directly from the Wilson loop diagrams to its Grassmann necklace.
-This not only greatly simplifies the process above, but will also allow us to relate the behavior of the positroid $M(W)$ directly to the configuration of progators in $W$.
+This not only greatly simplifies the previously known process to obtain a positroid cell from a Wilson loop diagram, but will also allow us to relate the behavior of the positroid $M(W)$ directly to the configuration of progators in $W$.
 
@@
 \begin{algorithm}\label{alg:put GN on WLD}
-Let $W = (\cP, [n])$ be an admissible Wilson loop diagram.
-In order to construct the set set $I_i^W$ (or just $I_i$ when $W$ is clear from context\note{We have gone from not pointing out this convention to pointing it out 3 times.
-Can we find a happy medium?}) for $i \in [n]$, perform the following steps:
+Let $W = (\cP, [n])$ be an admissible Wilson loop diagram. In order to construct the set $I_i^W$ for $i \in [n]$, perform the following steps:
 
@@
 \[I_i^W(p) := \text{the vertex label that $p$ contributes to $I_i$ in Algorithm~\ref{alg:put GN on WLD},}\]
-for each $p \in \cP$. When the diagram $W$ is clear from context, we drop the superscript and simply write $I_i$.
+for each $p \in \cP$. 
 \end{dfn}
+
+For both $I_i^W$ the set and the function, when the diagram $W$ is clear from context, we drop the superscript and simply write $I_i$.
 
@@
 
-% {\color{violet}
-% Each $I_i$ also imposes an ordering on the propagators, determined by when the propagator contributes to the sequence:
-% \begin{dfn} \label{proporderingdfn}
-% The ordering of the propagators on $W = (\cP, [n])$ defined by $I_i^W$ is $\cP = \{p_1, \ldots p_k\}$, where 
+Each $I_i$ also imposes an ordering on the propagators, determined by when the propagator contributes to the sequence:
+\begin{dfn} \label{proporderingdfn}
+  The ordering of the propagators on $W = (\cP, [n])$ defined by $I_i^W$ is the ordering in which they contribute to the algorithm as it constructs $I_i^W$.
+%  $\cP = \{p_1, \ldots p_k\}$, where 
 % \[I_i = \{I_i(p_1) <_i I_i(p_2) <_i \ldots <_i I_i(p_k)\}.\]
 % (The superscript $W$ is omitted here to simplify the notation.)\note{Sian tweaked this slightly to emphasise the $<_i$ order, because standard convention in most papers is to write all GN terms in the 1-order.}
-% \end{dfn}
-
-% Since each propagator is removed by the algorithm after it contributes, each propagator contributed exactly once to $I^W_i$, making the above ordering well defined.}
+\end{dfn}
+
+Since each propagator is removed by the algorithm after it contributes, each propagator contributed exactly once to $I^W_i$, making the above ordering well defined.
+
+Note that different $I^W_*$ impose different orderings on the propagators.
+Furthermore, Lemma \ref{no fourth vertex} shows that this ordering respects the ordering of vertices in $I_i$.
+That is, $I_i(p_j) <_i I_i(p_l)$ for all $j <l$.
 
@@
 
-Notice that for each element in the Grassmann necklace, the propagators contribute in a particular order. It is sometimes useful to think of the propagators in this order. 
-\begin{dfn} \label{prop order dfn}
-Given a set $\cP$ of $k$ propagators defining a Wilson loop diagram $(\cP, [n])$, the Grassmann necklace element $I_i$ imposes an ordering on it $\cP^i = \{p_1 \ldots p_k\}$ where $p_m$ is the $m^{th}$ propagator to contribute to $I_i$.
+%Notice that for each element in the Grassmann necklace, the propagators contribute in a particular order. It is sometimes useful to think of the propagators in this order. 
+%\begin{dfn} \label{prop order dfn}
+%Given a set $\cP$ of $k$ propagators defining a Wilson loop diagram $(\cP, [n])$, the Grassmann necklace element $I_i$ imposes an ordering on it $\cP^i = \{p_1 \ldots p_k\}$ where $p_m$ is the $m^{th}$ propagator to contribute to $I_i$.
 We write $\cP_m^i = \{p_1 \ldots p_m\}$ to be the first $m$ propagators that contribute to $I_i$.
 We drop the superscript if the Grassman necklace element is clear.
-\end{dfn}
-
-In the sequel, when we refer to orderings on propagators, we refer to the ordering $\cP^i$.
-Note that different elements of the Grassmann necklace impose different orderings on the propagators.
-Furthermore, Lemma \ref{no fourth vertex} shows that this ordering respects the ordering of vertices in $I_i$.
-That is, $I_i(p_j) <_i I_i(p_l)$ for all $j <l$.\sanote{Maybe move closer to reference lemma}
+%\end{dfn}
+
+%In the sequel, when we refer to orderings on propagators, we refer to the ordering $\cP^i$.
 

### 2019-08-16 GWLDCII.tex
final changes from on the phone

@@
 
-Each $I_i$ also imposes an ordering on the propagators, determined by when the propagator contributes to the sequence:
+%Each $I_i$ also imposes an ordering on the propagators, determined by when the propagator contributes to the sequence:
 \begin{dfn} \label{proporderingdfn}
-  The ordering of the propagators on $W = (\cP, [n])$ defined by $I_i^W$ is the ordering in which they contribute to the algorithm as it constructs $I_i^W$.
+  There is an ordering on the propagators on $W = (\cP, [n])$ defined by $I_i$. This is the ordering in which they contribute to the algorithm as it constructs $I_i$.
 %  $\cP = \{p_1, \ldots p_k\}$, where 
@@
 
-Since each propagator is removed by the algorithm after it contributes, each propagator contributed exactly once to $I^W_i$, making the above ordering well defined.
-
-Note that different $I^W_*$ impose different orderings on the propagators.
-Furthermore, Lemma \ref{no fourth vertex} shows that this ordering respects the ordering of vertices in $I_i$.
+Since each propagator is removed by the algorithm after it contributes, each propagator contributed exactly once to $I_i$, making the above ordering well defined.
+Note that different $I_*$ impose different orderings on the propagators.
+Furthermore, Lemma \ref{lem no fourth vertex} shows that this ordering respects the ordering of vertices in $I_i$.
 That is, $I_i(p_j) <_i I_i(p_l)$ for all $j <l$.
@@
 \begin{rmk} \label{clockwise ordering rem}
-When $p_m$ contributes $I_i(p_m) = a_m$ to the Grassmann necklace, it must be the clockwise-most propagator (amongst those not yet assigned) that is supported on $a_m$ i.e.
-any other propagator in $\cP \setminus \cP_{m-1}$ that is supported on $a_m$ must be inside $p_m$ in the $a_m-1$ ordering.
+When $p$ contributes $I_i(p) = a$, it must be the clockwise-most propagator amongst those not yet assigned that is supported on $a$ i.e.
+any propagator assigned later that is supported on $a$ must be inside $(p, <_{a-1})$.
 \end{rmk} \sanote{We use this fact at least twice below}

### 2019-08-26 GWLDCII.tex
oops didn't save
some changes made before going on vacation

@@
 Note that different $I_*$ impose different orderings on the propagators.
-Furthermore, Lemma \ref{lem no fourth vertex} shows that this ordering respects the ordering of vertices in $I_i$.
+Furthermore, Corrollary \ref{GN alg well defined} shows that this ordering respects the ordering of vertices in $I_i$.
 That is, $I_i(p_j) <_i I_i(p_l)$ for all $j <l$.
@@
 any propagator assigned later that is supported on $a$ must be inside $(p, <_{a-1})$.
-\end{rmk} \sanote{We use this fact at least twice below}
+\end{rmk}
 
@@
 
-With this setup, if we can find a vertex $\ell$ (with \st{$\ell <_i i$ and $\ell <_m m$} {\color{violet} $i <_i \ell$ and $m <_m \ell$?}) such that the \emph{configuration} of propagators ending in the interval \st{$(j-1, \ldots, \ell+1)$} {\color{violet}$[j, l]$} is identical in both $W'$ and $V'$, then the vertices contributed to $I_i^W$ and $I_m^V$ are the same from step $j$ to step $\ell$ (inclusive).
+With this setup, if we can find a vertex $\ell$ (with \hlfix{$\ell <_i i$ and $\ell <_m m$}{ $i <_i \ell$ and $m <_m \ell$?
+This is what is in the picture?}) such that the \emph{configuration} of propagators ending in the interval \st{$(j-1, \ldots, \ell+1)$} {\color{violet}$[j, \ell]$} is identical in both $W'$ and $V'$, then the vertices contributed to $I_i^W$ and $I_m^V$ are the same from step $j$ to step $\ell$ (inclusive).
 See Figure~\ref{fig:locally identical} for an illustration of this.
@@
 With that in mind, we are ready to begin proving properties of the algorithm.
-We first show that the algorithm for $I_i$ can never reach the final vertex (in the $<_i$ order) in a propagator's support without having already assigned that propagator; in particular, this guarantees that the construction of $I_i$ always terminates in fewer than $n$ steps.
+We first show that the algorithm for $I_i$ can never reach the final vertex (in the $<_i$ order) in a propagator's support without having already assigned that propagator; in particular, this guarantees that the construction of $I_i$ always terminates in fewer than $n$ steps, as shown in Corrollary \ref{GN alg well defined}.
 
@@
 For any $i \in [n]$ and for any $p \in \cP$, $I_i(p)$ is not maximal (with respect to $<_i$) amongst the vertices that support $p$.
-\end{lem}
+\end{lem} \sanote{wanted to rewrite this lemma to emphasize the fact that we are using the same properties of Alg 3.7 over and over again, and have these principals set apart in a remark}
 \begin{proof}
@@
 
-So let $p = (a,b)$ with $a<_ib$ and $I_i(p) = b+1$, and choose $p$ such that $\big|[a+1,b]\big|$ is minimal amongst propagators of $W$ with this property.
-\sanote{in the picture for case 2, $\big|[d+1,b]\big| <\big|[a+1,b]\big|$.Worried about case 2}
+So let $p = (a,b)$ with $a<_ib$ and $I_i(p) = b+1$, and choose $p$ such that $\big|[a+1,b]\big|$ is \hlfix{minimal amongst propagators of $W$ contributing their last vertices with this property.}{changed wording to be accurate, but feels clunky}
 
@@
 \begin{cor}\label{GN alg well defined}
-If $W$ is an admissible Wilson loop diagram with $k$ propagators, then Algorithm~\ref{alg:put GN on WLD} assigns exactly $k$ distinct vertices to each $I_i$.
+If $W$ is an admissible Wilson loop diagram with $k$ propagators and $n$ vertices. Then Algorithm~\ref{alg:put GN on WLD} assigns exactly $k$ distinct vertices to each $I_i$ in $n$ steps.
 \end{cor} 
@@
 
-Let $W = (\cP,[n])$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$.
-Then $J_p^{W}(i)$, $J_p^{W}(i+1)$, $J_p^{W}(j)$, and $J_p^{W}(j+1)$ are each non-empty cyclic intervals which partition $[n]$ and occur in the given cyclic order.
+Let $W = (\cP,[n])$ be an admissible Wilson loop diagram\st{, and}{\color{violet}.
+For every }$p = (i,j) \in \cP$\st{.
+Then}{\color{violet}, the sets} $J_p^{W}(i)$, $J_p^{W}(i+1)$, $J_p^{W}(j)$, and $J_p^{W}(j+1)$ are each non-empty cyclic intervals which partition $[n]$ and occur in the given cyclic order.
 \end{lem}
@@
 
-In each of the four cases, when we remove the propagator labelled $p$ we obtain a diagram which satisfies the statement of the theorem by the induction hypothesis, and contains a propagator ${q = (i,j)}$ with no other propagators inside it (with respect to the $<_i$ orientation).
+In each of the four cases, when we remove the propagator labelled $p$ we obtain a diagram which satisfies \hlfix{the statement of the theorem by the induction hypothesis}{???
+changed to statement of the theorem slightly to make this make sense}, and contains a propagator ${q = (i,j)}$ with no other propagators inside it (with respect to the $<_i$ orientation).
 Note that this region may or may not contain non-supporting vertices, which we will call $l, l+1, \ldots$ as necessary.
@@
 We first calculate $I^{W}_w$ for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$.
-Note that $p$ has no effect on other propagators for starting vertices in this range, so if $r \neq p$, then $I_w^W(r) = I_w^V(r)$.
-Meanwhile, the value of $I^{W}_w(p)$ depends on which step in the algorithm the propagator $q$ is assigned to a vertex, i.e.
+\hlfix{Note that $p$ has no effect on other propagators for starting vertices in this range,}{By rmk \ref{rmk algorithm locally same}?} so if $r \neq p$, then $I_w^W(r) = I_w^V(r)$.
+Meanwhile, the value of $I^{W}_w(p)$ depends on which step in the algorithm the propagator $q$ \st{is assigned to}{\color{violet}contributes}\sanote{has this changed emphasis too much?} a vertex, i.e.
 on the value of $I^{V}_w(q)$.
@@
 
+\end{document}
+
 \section{Dimension of the Wilson Loop cells}\label{sec dim}
@@
   \begin{equation}\label{eq necklace}
-  I_{n-3}^{V} \xrightarrow[\substack{n-3\text{ out}\\n-2\text{ in}}]{} I_{n-2}^{V} \xrightarrow[\substack{n-2\text{ out}\\n-5\text{ in}}]{} I_{n-1}^{V} \xrightarrow[\substack{n-1\text{ out}\\\text{something in}}]{} I_{n}^{V}  \xrightarrow[\substack{n \text{ out}\\\text{something in}}]{} I_1^{V}
-  \end{equation}
-  where the first ``something'' is either $n$ or an element of $I_1^{V}$, and the second ``something'' is an element of $I_1^{V}$.
-
-  \begin{figure}
-    \[\includegraphics{messy}\]
-    \caption{Plusses coming from $I_{n-2}^{V}$ (top left), $I_{n-1}^{V}$ (top right), and $I_n^V$ (bottom row), in the case where ${n-1, n-2\in I_{n-2}^{V}}$.
-The blue lines are the non-intersecting paths defining the position of the plusses.
-The dashed blue lines may or may not appear, but if one appears then they both do.}\label{fig messy}
-  \end{figure}
-
-  Using this information we can determine the symmetric difference of $I_{n-2}^{V}$ and $I_1^{V}$.
-Note that $I_{n-2}^V\setminus I_1^V$ and $I_1^V\setminus I_{n-2}^V$ each have size $\leq 3$ by the definition of a Grassmann necklace.
-We have $n-1, n-2 \in I_{n-2}^{V} \setminus I_1^V$ for certain, and the third element (if it exists) must be $n$.
-On the other hand we have $n-5 \in I_1^{V} \setminus I_{n-2}^V$, along with at least one and at most two other elements.
-If there is one such element, call it $a$.
-If there are two, call them $a$ and $b$ with $a>b$.
-
-  This means that the plusses in the Le diagram of $V$ coming from $I_{n-2}^{V}$ are as in the top left diagram in Figure~\ref{fig messy}.
-Stepping to $I_{n-1}^{V}$ simply removes the $(n-5)\rightarrow (n-2)$ path (top right diagram of Figure~\ref{fig messy}), so $I_{n-1}^V$ contributes no new information about the Le diagram of $V$.
-
-  %Stepping to $I_{n}^{V}$, $n-1$ is removed and either $n$ is put in if it was not there before, or one of $a$ or $b$ is put in and hence is no longer available as the starting point for a path.
-This gives two possible configurations illustrated in the bottom two parts of Figure~\ref{fig messy}.
-
-  With this information in hand, we can now tackle the points in the statement of the lemma. We know that 
-  \[I_{n-2}^{W}  = (I_{n}^{V} - \{n-5\})\cup \{n-1,n-2\}, \quad n-5 \in I_1^W, \quad n-3\not\in I_{n-2}^W,\]
- and so the paths for building plusses from $I_{n-2}^{W}$ start at
- \[I_1^W \setminus I_{n-2}^W = \{n-3,n-5\} \cup (I_1^V \setminus I_n^V)\]
- and end at
- \[I_{n-2}^W \setminus I_1^W = \{n-2,n-1\}\cup(I_n^V \setminus I_1^V).\]
-This means that $I_{n-2}^W$ contributes plusses as in Figure~\ref{fig messyD}, while $I_n^V$ contributes as in the bottom line of Figure~\ref{fig messy}, which proves point (1) and most of point (3).
-From equation \eqref{eq necklace} we see that $n-2$ appears only in $I_{n-2}^V$, so no other Grassmann necklace term for $V$ can contribute a plus in the $n-2$ column; this completes the proof of item (3).
-
-  \begin{figure}
-     \[\includegraphics{messyD}\]
-    \caption{Plusses coming from $I_{n-2}^{W}$.}\label{fig messyD}
-  \end{figure}
-
-Now consider $I_{n-3}^{V}$.
-By equation~\eqref{eq necklace} $I_{n-3}^{V}$ contributes almost the same plusses as $I_{n-2}^{V}$: the only difference is that it contributes an $(n-5)\rightarrow (n-3)$ plus in place of the $(n-5)\rightarrow (n-2)$ plus.
-Since we must have $n-3\in I_{n-3}^{V}$ (because the propagator $q$ exists in $V$), it follows from Lemma~\ref{lem I} that $I_{n-3}^{W} = I_{n-3}^{V}\cup\{n-2\}$.
-Thus the paths for $I^{W}_{n-3}$ are the same as those for $I^{V}_{n-3}$ except that the path that did go to $n-3$ now goes to $n-2$.
-This cannot conflict with another path since equation~\eqref{eq necklace} shows that $n-2$ only appears in $I_{n-2}^{V}$ among the necklace elements of $V$.
-
-This proves point (2), and combined with the observation above that $I_{n-1}^V$ contributes no new plusses compared to $I_{n-2}^V$, we also obtain item (4).
-
-  Finally, if the Le diagram of $V$ did admit a $(n-5)\rightarrow (n-1)$ plus, it could only have been contributed by a necklace term that doesn't contain $n-5$.
-By equation \eqref{eq necklace} the only terms that could have this property are $I_{n-2}^{V}$, $I_{n-3}^{V}$, and $I_{n-4}^{V}$, and the analysis above shows that $I_{n-2}^V$ and $I_{n-3}^V$ do not contribute a plus in this position.
-
-  Recall that $n-5$ is the largest row index in the Le diagram of $V$, and $n-5 \in I_1^V \setminus I_{n-4}^V$ so $I_{n-4}^V$ must contribute a path starting at $n-5$.
-Since $n-4 \in I_{n-4}^V$ by the location of the propagator $q$, we must also have a path ending at $n-4$.
-Since the paths cannot cross, this implies that $I_{n-4}^V$ must contribute a $(n-5) \rightarrow (n-4)$ plus, and hence cannot contribute a $(n-5)\rightarrow (n-1)$ plus.
-This proves point (5) and completes the proof of the lemma.
-\end{proof}
-
-\begin{lem}\label{lem other k}
-  Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that if $n-2\in I_{n-2}^{V}$ then $n-1\in I_{n-2}^{V}$ also.
-Then for each $k$ in the range $1<k<n-2$, $I_k^{W}$ contributes the same plusses as $I_{k}^{V}$, except that if $I_{k}^{V}$ contributed a plus in the $n-3$ column of the Le diagram of $V$ then this plus is shifted one square left in the Le diagram of $W$, and no plus was already in that location in the Le diagram of $W$.
-\end{lem}
-
-\begin{proof}
-Recall that $I_1^W = I_1^V\cup \{n-3\}$ and that $n-2,n-1,n \not\in I_1^W$.
-
-  If $n-3\not\in I_{k}^{V}$ then by Lemma~\ref{lem I} we have $I_{k}^{W} = I_k^{V}\cup \{n-3\}$.
-Then since $n-3$ is the largest element of $I_1^{W}$ this transformation leaves the disjoint paths unchanged and so the plusses carry over from $V$ to $W$ directly.
-
-  If $n-3\in I_{k}^{V}$ then $I_k^V$ must contribute a plus in the $n-3$ column of the Le diagram of $V$, and by Lemma~\ref{lem I} we have $I_{k}^{W} = I_k^{V}\cup \{n-2\}$.
-If $n-2$ supports no propagators in $V$ then certainly no plusses appear in the $n-2$ column of the Le diagram of $V$.
-If $n-2$ supports at least one propagator in $V$ then $n-2 \in I_{n-2}^V$ and so by hypothesis $n-1 \in I_{n-2}^V$ as well.
-By Lemma~\ref{lem n-2 bad}, the only necklace element of $V$ containing $n-2$ is $I_{n-2}^{V}$ and the corresponding plus is not contributed to the Le diagram of $W$ by $I_{n-2}^{W}$.
-
-  Since $n-3 \in I_k^V \setminus I_1^V$, we must have a path in the Le diagram of $V$ from some vertical edge $i$ to the bottom edge $n-3$.
-In the Le diagram of $W$, the index $n-3$ labels a vertical edge with no path starting at it (since $n-3$ belongs to both $I_1^W$ and $I_k^W$), and there must be a path leading to $n-2$ since $n-2 \in I_k^W \setminus I_1^W$.
-By the previous paragraph no other path from $I_k^V$ could end at $n-2$, and since the paths cannot cross we conclude that the $i\rightarrow (n-3)$ path in the Le diagram of $V$ must become a $i\rightarrow (n-2)$ path in the Le diagram of $W$.
-All other paths are unchanged.
-
-   Thus the plus contributed by $I_k^V$ in the $n-3$ column of the Le diagram of $V$ is shifted into the $n-2$ column in the Le diagram for $W$, where there was no plus before, and no other plusses are changed.
-\end{proof}
-
-We are now ready to prove the main result of this section, showing that the dimension of the positroid cell associated to each Wilson loop diagram is $3|\cP|$.
-
-\begin{thm}\label{thm dim}
-  The number of plusses in the Le diagram of an admissible Wilson loop diagram is three times the number of propagators.
-\end{thm}
-
-\begin{proof}
-  The proof is by induction on the number of propagators.
-
-  First note that a Wilson loop diagram $W$ with one propagator supported on vertices $i<j<k<\ell$ has Le diagram a single row with $|W|-i$ boxes.
-Labelling the columns from left to right by $|W|, \ldots, |W|-i+1$, by Algorithm~\ref{alg:GN to Le} there are plusses in the $j$, $k$, and $\ell$ positions.
-
-  Now consider Wilson loop diagrams with $k>1$ propagators.
-By Lemma~\ref{lem uncovered} it suffices to prove the result for weakly admissible Wilson loop diagrams with $k$ propagators and no non-supporting vertices.
-By Lemma~\ref{lem dihedral} it suffices to prove the result for at least one Wilson loop diagram from each dihedral orbit.
-Take a weakly admissible Wilson loop diagram $W$ with $k$ propagators and no non-supporting vertices.
-Make a dihedral transformation of $W$ if necessary so that $W$ has a propagator $p$ with the properties in Lemma~\ref{lem good p}.
-
-  We make one further simplification: if our $W$ is in Case 2 of Figure~\ref{fig special p} and $n-1$ supports only $p$ but $n-2$ supports at least one other propagator, then flip $W$ on the line perpendicular to the $(n-2){th}$ edge to obtain a diagram with the configuration of Case 1.
-This eliminates the possibility that we could have $n-2 \in I_{n-2}^W$ but $n-1 \not\in I_{n-2}^W$.
-
-  This diagram will be our $W$ for the remainder of the proof. Let $V$ be $W$ with $p$ removed.
-
-  From Lemma~\ref{lem shape} we know how the shapes of the Le diagrams of $V$ and $W$ are related; let $\mathcal{A}$ and $\mathcal{B}$ be as described in that lemma and subsequent discussion.
-Lemmas~\ref{lem n and n-1}, \ref{lem n-2 good}, and \ref{lem n-2 bad} tell us that the three boxes of the bottom row of the Le diagram of $W$ each have a plus.
-Lemmas~\ref{lem n and n-1} through \ref{lem other k} show that there is a bijection between the plusses of the Le diagram of $V$ and the plusses of the Le diagram of $W$ that are not in the bottom row.
-This bijection can be described as follows:
-  \begin{itemize}
-  \item All plusses from $\mathcal{B}$ for $V$ maintain their positions in $\mathcal{B}$ for $W$.
-  \item All plusses from the leftmost two columns (the $n$ and the $n-1$ columns) of $\mathcal{A}$ for $V$ maintain their positions in $\mathcal{A}$ for $W$.
-  \item If there is a plus in the $n-2$ column of $\mathcal{A}$ in $V$ then Lemma~\ref{lem n-2 bad} applies, so there is exactly one such plus.
-This plus is mapped to the $(n-5)\rightarrow (n-1)$ plus for $W$.
-  \item All plusses in the $n-3$ column for $V$ are shifted one square to the left in $\mathcal{A}$ for $W$, i.e. into the $n-2$ column.
-  \end{itemize}
-  Note that this map is reversible and hence bijective.
-Indeed, the only possible ambiguity is at the $(n-5)\rightarrow (n-1)$ plus in $W$ (if it exists), which could have come from either of the first or third bullet points.
-However, if the third bullet point applies then by Lemma~\ref{lem n-2 bad} there is no $(n-5)\rightarrow (n-1)$ plus in $V$, i.e.
-the first bullet point does not apply.
-
-  % If the Le diagram for $V$ has a plus in the $n-2$ column then Lemma~\ref{lem n-2 bad} applies.
-By the final part of Lemma~\ref{lem n-2 bad} there is no $n-5\rightarrow n-1$ plus in the Le diagram of $V$, and so the $n-5\rightarrow n-1$ plus of $W$ can be uniquely mapped to the plus in the $n-2$ column of the Le diagram of $V$.
-If the Le diagram for $V$ has no plus in the $n-2$ column, then leave the $n-5\rightarrow n-1$ plus where it is in moving back to $V$.
-This reverses the map.
-
-Therefore the Le diagram of $W$ contains $3(k-1)$ plusses in bijection with the plusses from the Le diagram of $V$ and 3 new plusses in the bottom row, yielding $3k$ in total.
-Applying induction completes the proof.
-\end{proof}
-
-\section{Poles of Wilson Loop Integrals}\label{sec poles}
-
-In this section, we investigate the poles of the integrand for $I(W)$, that is $R(W)$ as defined in Definition~\ref{def R(W)}.
-It is conjectured that for a fixed number of propagators and a given set of external twistors $\cZ$, [cite]\note{A cite still waiting} \bas \sum_{W | |\cP| = k} I(W)(\cZ) <\infty \;.\eas In otherwords, all poles of the intergrals must cancel.
-As a step towards this, in this section, we prove some results about $R(W)$.
-
-The results of Section~\ref{sec GN algorithm} allow us to relate the position of propagators in a Wilson loop diagram $W$ to minors of $C(W)$, $R(W)$.
-
-The main result of this section is Theorem~\ref{thm denom}, which expresses the denominator $R(W)$ in terms of the Grassmann necklace of $W$.
-This simplifies the computation of $R(W)$ and allows us to directly relate the poles of the integral to the combinatorics of the diagram.
-
-We first give an algorithm which extracts the required minors from the Grassmann necklace.
-
-\begin{algorithm}\label{alg WLD to denom via GN}
-Let $W = (\cP,n)$ be a Wilson loop diagram, and let $C(W)$ be the matrix of $W$ as defined in \eqref{C(W) dfn} with a fixed ordering on $\cP$. (see Section~\ref{section WLD background}).
-\begin{itemize}
-  \item For each $i \in [n]$, we construct a factor $r_i$ as follows:
-    \begin{itemize}
-      %\item Use Algorithm~\ref{alg:put GN on WLD} to obtain a bijection between the propagators and the $i-1$st Grassmann necklace element, $I_{i-1}$.
-(By convention set $I_{0}=I_n$.)  Write $I_{i-1}(p)$ for the vertex associated to propagator $p$ under this bijection.
-      %\item Use Algorithm~\ref{alg:put GN on WLD} to obtain a bijection between the propagators and the $i$th Grassmann necklace element, $I_{i}$.
-Write $I_{i}(p)$ for the vertex associated to propagator $p$ under this bijection.
-      \item Let $S_i = \{p \in \cP \ | \ I_{i-1}(p) \neq I_i(p)\}$. (By convention, set $I_{0} = I_n$.)
-	  %\item Write $\Delta_{I_i}$ for the determinant of the $k \times k$ minor of $C(W)$ with columns indexed by $I_i$.
-      \item Let $r_i$ be the determinant of the $|S_i|\times |S_i|$ minor of $C(W)$ with rows indexed by $S_i$ and columns indexed by $I_i(S_i)$.
-%$\Delta_{I_i}$ with all variables from rows associated to $p\not\in S_i$ set to $1$.
-    \end{itemize}
-  \item Define $R = \prod_{i=1}^n r_i$.
-\end{itemize}
-\end{algorithm}
-
-That is, each $r_i$ is the determinant of the minor determined by the propagators (rows) that contribute different values (columns) to the $i^{th}$ element of the Grassmann necklace than they did to the $i-1^{st}$.
-
-As we discuss the algorithm it will also be useful to have the notation $\Delta_{I_i}$ for the determinant of the $k\times k$ minor of $C(W)$ with columns indexed by $I_i$.
-
-As we take each $r_i$ to simply be the determinant of a particular submatrix of $C(W)$, the sign of each $r_i$ is well-defined.
-Before proving the main results of this section, we given an illustrative example.
-Below, we show that $R$ is equal to the denominator of the Wilson loop diagram as defined in Definition~\ref{def R(W)}, and is the radical of the product $\prod_{i=1}^n \Delta_{I_i}$.
-%  However, we will not be interested in these signs as they only contribute an overall sign to $R$ and our main theorem in this section (Theorem~\ref{thm denom}) will simply be to show that $R$ is equal up to a $\mathbb{Q}$-multiple to the denominator of the Wilson loop diagram (see Definition~\ref{def R(W)}).
-
-\note{I would like to discuss the angles of the arrows in fig 14}
-\begin{figure}
-\begin{tabular}{rrrrr}
-\begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
-	\begin{scope}
-	\drawWLD{7}{1.5}
-	\drawnumbers
-	\drawlabeledprop{1}{-1}{6}{0}{\footnotesize   $p$}
-	\drawlabeledprop{1}{0}{5}{0}{\footnotesize   $q$}
-	\drawlabeledprop{1}{1}{4}{0}{\footnotesize \; \qquad  $s$}
-	\pgfmathsetmacro{\move}{\angle/\n};
-	\draw[->,shorten >=2pt,red,thick] (1.5*\angle + -1*\move:\radius) to[bend left = 45] (\angle*1:\radius); %p
-	\draw[->,shorten >=2pt,red,thick] (1.5*\angle:\radius) to[bend right = 45] (\angle*2:\radius); %q
-	\draw[->,shorten >=2pt,red,thick] (4.5*\angle:\radius) to[bend left = 45] (\angle*4:\radius); %r
-	\node at (\angle*1.5:\radius*2) {$I_1$};
-	\node[align = center] at (4*\angle:\radius*1.7) {$I_1(p) = 1, \; I_1(q) = 2,$ \\[5pt] $I_1(s) = 4$.};
-		\end{scope}
-	\end{tikzpicture} 
-	& \quad \quad  &
-\begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
-	\begin{scope}
-	\drawWLD{7}{1.5}
-	\drawnumbers
-	\drawlabeledprop{1}{-1}{6}{0}{\footnotesize   $p$}
-	\drawlabeledprop{1}{0}{5}{0}{\footnotesize   $q$}
-	\drawlabeledprop{1}{1}{4}{0}{\footnotesize \; \qquad  $s$}
-	\pgfmathsetmacro{\move}{\angle/\n};
-	\draw[->,shorten >=2pt,red,thick] (1.5*\angle + -1*\move:\radius) to[bend right = 45] (\angle*2:\radius); %p
-	\draw[->,shorten >=2pt,red,thick] (5.5*\angle:\radius) to[bend left = 45] (\angle*5:\radius); %q
-	\draw[->,shorten >=2pt,red,thick] (4.5*\angle:\radius) to[bend left = 45] (\angle*4:\radius); %r
-	\node at (\angle*1.5:\radius*2) {$I_2$};
-	\node[align = center] at (4*\angle:\radius*1.7) {$I_2(p) = 1,  \; I_2(s) = 4,$ \\[5pt] $I_2(q) = 5.$};
-	\end{scope} 
-\end{tikzpicture}
-& \quad & 
-\begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
-	\begin{scope}
-	\drawWLD{7}{1.5}
-	\drawnumbers
-	\drawlabeledprop{1}{-1}{6}{0}{\footnotesize   $p$}
-	\drawlabeledprop{1}{0}{5}{0}{\footnotesize   $q$}
-	\drawlabeledprop{1}{1}{4}{0}{\footnotesize \; \qquad  $s$}
-	\pgfmathsetmacro{\move}{\angle/\n};
-	\draw[->,shorten >=2pt,red,thick] (6.5*\angle:\radius) to[bend left = 45] (\angle*6:\radius); %p
-	\draw[->,shorten >=2pt,red,thick] (5.5*\angle:\radius) to[bend left = 45] (\angle*5:\radius); %q
-	\draw[->,shorten >=2pt,red,thick] (4.5*\angle:\radius) to[bend left = 45] (\angle*4:\radius); %r
-	\node at (\angle*1.5:\radius*2) {$I_3 = I_4$};
-	\node[align = center] at (4*\angle:\radius*1.7) {$I_3(s) = 4,\;  I_3(q) = 5,$ \\[5pt] $I_3(p) = 6.$ };
-	\end{scope} 
-\end{tikzpicture}  
-\\ 
- & & & &  \\
- \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
-	\begin{scope}
-	\drawWLD{7}{1.5}
-	\drawnumbers
-	\drawlabeledprop{1}{-1}{6}{0}{\footnotesize   $p$}
-	\drawlabeledprop{1}{0}{5}{0}{\footnotesize   $q$}
-	\drawlabeledprop{1}{1}{4}{0}{\footnotesize \; \qquad  $s$}
-	\pgfmathsetmacro{\move}{\angle/\n};
-	\draw[->,shorten >=2pt,red,thick] (6.5*\angle:\radius) to[bend right = 45] (\angle*7:\radius); %p
-	\draw[->,shorten >=2pt,red,thick] (5.5*\angle:\radius) to[bend right = 45] (\angle*6:\radius); %q
-	\draw[->,shorten >=2pt,red,thick] (4.5*\angle:\radius) to[bend right = 45] (\angle*5:\radius); %r
-	\node at (\angle*1.5:\radius*2) {$I_5$};
-	\node[align = center] at (4*\angle:\radius*1.7) {$I_5(s) = 5,\;  I_5(q) = 6,$  \\[5pt] $I_5(p) = 7$ };
-	\end{scope} 
-\end{tikzpicture}
-& \quad & 
-\begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
-	\begin{scope}
-	\drawWLD{7}{1.5}
-	\drawnumbers
-	\drawlabeledprop{1}{-1}{6}{0}{\footnotesize   $p$}
-	\drawlabeledprop{1}{0}{5}{0}{\footnotesize   $q$}
-	\drawlabeledprop{1}{1}{4}{0}{\footnotesize \; \qquad  $s$}
-	\pgfmathsetmacro{\move}{\angle/\n};
-	\draw[->,shorten >=2pt,red,thick] (6.5*\angle:\radius) to[bend right = 45] (\angle*7:\radius); %p
-	\draw[->,shorten >=2pt,red,thick] (5.5*\angle:\radius) to[bend right = 45] (\angle*6:\radius); %q
-	\draw[->,shorten >=2pt,red,thick] (1.5*\angle + 1*\move:\radius) to[bend left = 45] (\angle*1:\radius); %r
-	\node at (\angle*1.5:\radius*2) {$I_6$};
-	\node[align = center] at (4*\angle:\radius*1.7) {$I_6(q) = 6, \; I_6(p) = 7, $ \\[5pt] $I_6(s) = 1. $ };	
-	\end{scope}
-	\end{tikzpicture}  
-& \quad &
-\begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
-	\begin{scope}
-	\drawWLD{7}{1.5}
-	\drawnumbers
-	\drawlabeledprop{1}{-1}{6}{0}{\footnotesize   $p$}
-	\drawlabeledprop{1}{0}{5}{0}{\footnotesize   $q$}
-	\drawlabeledprop{1}{1}{4}{0}{\footnotesize \; \qquad  $s$}
-	\pgfmathsetmacro{\move}{\angle/\n};
-	\draw[->,shorten >=2pt,red,thick] (6.5*\angle:\radius) to[bend right = 45] (\angle*7:\radius); %p
-	\draw[->,shorten >=2pt,red,thick] (1.5*\angle:\radius) to[bend left = 45] (\angle*1:\radius); %q
-	\draw[->,shorten >=2pt,red,thick] (1.5*\angle + \move:\radius) to[bend right = 45] (\angle*2:\radius); %r
-	\node at (\angle*1.5:\radius*2) {$I_7$};
-	\node[align = center] at (4*\angle:\radius*1.7) {$I_7(p) = 1,  \; I_7(q) = 1, $ \\[5pt] $I_7(s) = 2.$};
-	\end{scope} 
-\end{tikzpicture}
-\\
-\end{tabular}
-\caption{Example WLD for illustrating Algorithm~\ref{alg WLD to denom via GN} and bijections between propagators and vertices for each Grassmann necklace element.}\label{fig R eg}
-\end{figure}
-
-\begin{eg}
-Consider the Wilson loop diagram in Figure~\ref{fig R eg}. Assigning propagators $p$, $q$, $r$ to rows $1,2,3$ respectively, we obtain the matrix
-\[
-C(W) = \begin{bmatrix} a & b & 0 & 0 & 0 & c & d \\ e & f & 0 & 0 & g & h & 0 \\ i & j & 0 & k & l & 0 & 0 \end{bmatrix}
-\]
-The Grassmann necklace of this diagram is 
-\begin{gather*}I_1 = \{1,2,4\}, I_2 = \{2,4,5\}, I_3 = \{4,5,6\}, I_4=\{4,5,6\},\\ I_5=\{5,6,7\}, I_6 = \{6,7,1\}, I_7=\{7,1,2\}. \end{gather*}  
-Figure~\ref{fig R eg} indicates the pairings between propagators and vertices for each $i \in [1,7]$.
-
-From $I_1$ to $I_2$, the propagators $p$ and $q$ change which vertices they contribute.
-That is $I_1(p) = 1$, $I_1(q)= 2$ while $I_2(p) = 2$, $I_2(q)= 5$.
-However, $r$ contributes  4 to both $I_1$ and $I_2$, so $S_2 = \{p,q\}$.
-Then
-\[
-\Delta_{I_2}=\det\begin{bmatrix} b & 0 & 0 \\ f & 0 & g \\ j & k & l \end{bmatrix} = kgb, \qquad r_2 = \det\begin{bmatrix} b & 0 \\ f & g \end{bmatrix} = gb.
-\] 
-Continuing likewise, we get $r_3 = c$, $r_4=1$ (since $I_4 = I_3$), $r_5 = lhd$, and $r_6 = i$.
-
-At $I_7$ the situation we see for the first time an irreducible quadratic factor: we have $S_7 = \{q,s\}$ with $I_7(S_7) = \{ 1,2\}$, $\Delta_{I_7} = d(ej-fi)$ and $r_7 = ej-fi$.
-
-The irreducible quadratic factor corresponds to the fact that $q$ and $s$ share an edge {\em and} contribute both endpoints of that edge to $I_7$; see Proposition~\ref{prop alg gives rad} below.
-
-Finally, we have $r_1 = (af-be)k$.  Putting everything together, we obtain
-\[
-R = (af-be)kgbclhdi(ej-fi)
-\]
-which is squarefree and contains all factors of $\prod_{i=1}^{n}\Delta_{I_i}$.
-If one were to construct the denominator $R(W)$ associated to this Wilson loop diagram as per Definition~\ref{def R(W)}, we would find that we have $R(W) = R$.
-\end{eg}
-
-We are now ready to begin proving the main result of this section. We begin with a proposition stating several facts about $\Delta_{I_i}$ and their relationship to $r_i$.
-
-\begin{prop}\label{prop alg gives rad}
-  With notation as in Algorithm~\ref{alg WLD to denom via GN} we have the following:
-  \begin{enumerate}
-    \item Each $\Delta_{I_i}$ is homogeneous, as is each $r_i$.
-    \item Each $\Delta_{I_i}$ splits into linear and quadratic factors.
-All linear factors of  $\Delta_{I_i}$ are single variables and all irreducible quadratic factors are $2\times 2$ determinants of single variables.
-    \item Quadratic factors in $\Delta_{I_i}$ arise precisely when propagators $p$ and $q$ are supported on a common edge $(a,b)$ with $I_i(p)=a$ and $I_i(q)=b$.
-    \item $r_i$ divides $\Delta_{I_i}$.
-    \item The ideal generated by $R$ is the radical of the ideal generated by $\prod_{i=1}^{n}\Delta_{I_i}$.
-  \end{enumerate}
-\end{prop}
-
-\begin{proof}
-\begin{enumerate}
-    \item The nonzero entries of $C(W)$ are independent indeterminates and so every $i\times i$ minor of $C(W)$ is either homogeneous of degree $i$ or is $0$.
-Thus each $\Delta_{I_i}$ and each $r_i$ is homogeneous.
-%Furthermore, each row contributes one factor to each term in the expansion of $\Delta_{I_i}$ so the result of setting the variables from a subset of rows to $1$ is still homogeneous.
-Thus each $r_i$ is homogeneous.
-    \item Using the expression for the determinant as a sum over permutations along with Corollary~\ref{lem basis as perm} we see that $\Delta_{I_i}$ is a sum over bijections between $I_i$ and $\mathcal{P}$.
-The nonzero terms in this sum are precisely those bijections such that each propagator is associated to one of its supporting vertices in $I_i$, since only those locations in $C(W)$ are nonzero.
-Since the nonzero entries of $C(W)$ are independent there can be no cancellation between terms in this expansion.
-
-Suppose $\Delta_{I_i}$ has an irreducible factor $f$.
-Let $\mathcal{P}'$ be the set of propagators which contribute a variable to $f$ and let $J$ be the set of vertices which contribute a variable to $f$.
-
-The first claim is that the minor of $C(W)$ associated to $\mathcal{P}'$ and $J$ is precisely $f$.
-
-{\em Proof of claim}: By the structure of determinants we know that $\Delta_{I_i} = fg$, where $g$ involves only variables associated to propagators not in $\mathcal{P}'$ and associated to vertices not in $J$.
-
-Expanding out $fg$ yields a signed sum of monomials.
-Since there is no cancellation between terms, this means that the full expansion over permutations of $\Delta_{I_i}$ contains no other nonzero terms and hence no other variables.
-Therefore $\Delta_{I_i}$ is equal to the determinant of the matrix obtained by taking the submatrix of $C(W)$ with columns indexed by $I_i$ and setting any variables not appearing in $\Delta_{I_i}$ to $0$.
-This new matrix is, up to permutations of rows and columns, a block matrix with one block for $\mathcal{P}'$ and $J$ and the other block for the complements.
-Thus its determinant, and hence also $\Delta_{I_i}$, is the product of the minors for these two blocks.
-By considering which variables appear, these two factors must also be $f$ and $g$, and so in particular $f$ is the minor of $C(W)$ associated to $\mathcal{P}'$ and $J$.
-This proves the claim.
-
-A consequence of this claim is that every linear factor of $\Delta_{I_i}$ is a $1\times 1$ minor of $C(W)$, hence is a single variable, and every irreducible quadratic factor of $\Delta_{I_i}$ is a $2\times 2$ minor of $C(W)$, hence is a $2\times 2$ determinant of single variables.
-
-All that remains is to prove that $\Delta_{I_i}$ has no irreducible factors of degree 3 or more.
-Suppose for a contradiction that $f$ is a factor of $\Delta_{I_i}$ of degree $\geq 3$.
-Without loss of generality\footnote{This is without loss of generality as by removing the propagators which come before those contributing to $f$ in the order given by the construction of $I_i$ and changing $i$ to be the first vertex which contributes to $f$, we obtain an admissible diagram for which $f$ still divides $\Delta_{I_i}$ but also $i\in I_i$ and
-$i$ contributes to $f$, and this diagram can be used in place of $W$.} we may assume $i\in I_i$ and $i$ contributes to $f$.
-Finally, we can suppose that $W$ is minimal in number of propagators with an irreducible factor of degree $\geq 3$.
-
-Let $p$ be the propagator such that $I_i(p) = i$. There are two cases to consider, depending on which edge $p$ is supported on.  These are illustrated in Figure~\ref{fig no big factors}
-
-\begin{figure}
-\[
-\begin{tikzpicture}[baseline=(current bounding box.east),rotate=-20]
-\begin{scope}
-	\drawWLDfragment[8]{3}{0.4} 
-	%\drawnumberspartial % use this to debug
-	\newnode[left]{1}{i-1}
-	\newnode[below]{2}{i}
-	\newnode[below]{7}{m}
-	\begin{scope}
-		\clipcenterarc(0,0)(\startpoint-10:\endpoint+10:\radius)
-		\newpropbend{1.7}{7.2}{60}
-		\draw[smallpropagator,blue] (\zero+7.8*\step:\radius*1.1) to[bend left = 55] (\zero + 10*\step:\radius*1.1);
-		\node at (\zero + 1.2*\step:\radius*0.5) {\footnotesize $p$};
-	\end{scope}
-	\node[align = center,black] at (\zero + \step*4.5:\radius*0.65) {\em \footnotesize propagators \\ \footnotesize \em inside $p$};
-	\draw[->,shorten >=2pt,thick,gray] (\zero + 1.6*\step:\radius) to[bend left = 45] (\zero + 1*\step:\radius); %p
-	\draw[->,shorten >=2pt,thick,gray] (\zero + 7.9*\step:\radius) to[bend left = 45] (\zero + 7*\step:\radius); 
-	\node[align = center,black] at (\zero + 6.8*\step:1.5*\radius) {\em \footnotesize If $m \in I_i$ then \\ \em \footnotesize it was contributed by \\ \em \footnotesize the blue propagator};
-\end{scope}
-\end{tikzpicture}
-\qquad 
-\begin{tikzpicture}[baseline=(current bounding box.east),rotate=-20]
-	\begin{scope}
-	\drawWLDfragment[8]{3}{0.4}  
-	%\drawnumberspartial % use this to debug
-	\newnode[left]{1}{i}
-	\newnode[below]{2}{i+1}
-	\newnode[below]{7}{j}
-	\centerarc[red,line width = 2pt,line cap = round](0,0)(\zero + 1.5*\step:\zero+1.56*\step:\radius);
-	\draw[->,shorten >=2pt,thick,gray] (\zero + 1.45*\step:\radius) to[bend left = 45] (\zero + 1*\step:\radius); %p
-	\draw[->,shorten >=2pt,thick,gray] (\zero + 1.61*\step:\radius) to[bend right = 45] (\zero + 2*\step:\radius); %q 
-	\draw[->,shorten >=2pt,thick,gray] (\zero + 7.7*\step:\radius) to[bend left = 45] (\zero + 7*\step:\radius); %blue
-	\begin{scope}
-		\clipcenterarc(0,0)(\startpoint-10:\endpoint+10:\radius)
-		\newpropbend{1.6}{7.2}{40} % q
-		\draw[smallpropagator] (\zero+1.5*\step:\radius*1.1) to[bend right = 40] (\zero  - 3*\step:\radius*1.1); % p
-		\draw[smallpropagator,blue] (\zero+7.6*\step:\radius*1.1) to[bend left = 55] (\zero + 10*\step:\radius*1.1);
-		\node at (\zero + 5*\step:\radius*0.3) {\footnotesize $q$};
-		\node at (\zero + 1*\step:\radius*0.6) {\footnotesize $p$};
-	\end{scope}
-	\node[align = center,black] at (\zero + \step*4.5:\radius*0.75) {\em \footnotesize propagators \\ \footnotesize \em inside $q$};
-	\node[align = center] at (\zero + 1.5*\step:\radius*1.5) {\footnotesize \em No \\ \footnotesize \em propagators \\ \footnotesize \em between \\ \footnotesize \em $p$ and $q$ \\ \footnotesize \em here};
-	\node[align = center,black] at (\zero + 6.8*\step:1.5*\radius) {\em \footnotesize If $j \in I_i$ then \\ \em \footnotesize it was contributed by \\ \em \footnotesize the blue propagator};
-\end{scope}
-\end{tikzpicture}
-\]
-  \caption{The two cases in the proof that no factors of $\Delta_{I_i}$ have degree 3 or more.}\label{fig no big factors}
-\end{figure}
-
-\textbf{Case 1}: Suppose $p$ has one end on the edge $(i-1, i)$.  Thus $p$ is supported on $(i-1, i, m, m+1)$ for some $m >_i i$, and $I_{i+1}(p) = m$ by Lemma~\ref{vertex cyclic int lem}.
-
-Let $S = \cP_{in}(p)$ be the set of propagators inside $p$ in the $<_i$ order.
-$I_i$ and $I_{i+1}$ can only differ once $p$ contributes to $I_{i+1}$, so $I_i(q) = I_{i+1}(q)$ for each $q \in S \backslash \{p\}$.
-Thus if a propagator contributes $m$ in $I_i$ then it must lie outside $p$.
-
-If neither $m$ nor $m+1$ appear in $I_i$ then by Corollary~\ref{no coloops} $V(p) \cap I_i = \{i\}$, and so the row of $p$ in the matrix of $\Delta_{I_i}$ has only one nonzero entry; hence $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$, which is a contradiction to the fact that $i$ contributes to $f$.
-So we must have at least one of $m$ and $m+1$ in $I_i$.
-However, all propagators in $S$ are mapped by the function $I_{i}(\cdot)$ to vertices strictly before $m$, so the matrix giving $\Delta_{I_i}$ has the form
-\[
-\begin{bmatrix} A & B \\ 0 & C\end{bmatrix}
-\]
-where $A$ is the $|S|\times |S|$ matrix indexed by the propagators in $S$ and the vertices in $I_i(S)$.
-No other propagators can be supported on these vertices since all other propagators are outside of $p$, and $p$ is the first propagator supported at $i$; this explains the zero block.
-Therefore $\Delta_{I_i} = \det A \det C$, and both factors are nontrivial since at least one of $m$ and $m+1$ appear in $I_i$.
-Since $p\in \cP_{in}(p)$ we have $f|\det A$ and if we remove the propagator outside of $p$ that contributes $m$ or $m+1$, we get a diagram with fewer propagators for which $\det A | \Delta_{I_i}$, hence $f|\Delta_{I_i}$.
-This contradicts the minimality of our choices.
-
-\textbf{Case 2}: Suppose $p$ has one end on the edge $(i, i+1)$.
-If no other propagators are supported on $i$ then the column of $C(W)$ corresponding to vertex $i$ has only one nonzero entry in it, and so $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$; as above, this is a contradiction.
-Since $I_i(p) = i$ there can be no propagator supported on $i$ with an end on the edge $(i-1, i)$.
-Thus to have another propagator supported on $i$ there is at least one other propagator on edge $(i,i+1)$.
-Further since since $I_i(p)=i$, one of these other propagators contributes $i+1$ in $I_i$, so we can take $q$ to be the propagator such that $I_i(q)=i+1$.
-We know that $q$ has one end on the edge $(i, i+1)$ and is adjacent to $p$ on that edge in the counterclockwise direction (see Figure \ref{fig no big factors}).
-Write $(i, i+1, j, j+1)$ for the support of $q$.
-The situation for $q$ is very similar to case 1: in particular, we have $I_{i+1}(q) = j$ by Lemma~\ref{vertex cyclic int lem} and so if $j\in I_i$ then the propagator which contributes $j$ is outside of $q$.
-
-Similarly to Case 1, let $S = \cP_{in}(q) \cup \{p\}$ in the $<_i$ order.
-Then all propagators in $S$ are mapped by $I_i(\cdot)$ to vertices strictly before $j$ and no other propagators are supported on vertices strictly before $j$.
-Thus the matrix giving $\Delta_{I_i}$ has the form
-\[
-\begin{bmatrix} A & B \\ 0 & C\end{bmatrix}
-\]
-where $A$ is the submatrix indexed by the propagators in $S$ and the vertices in $I_i(S)$.
-Again two things can now happen.
-If some vertex $j$ or larger (with respect to $>_i$) belongs to $I_i$ then $B$ and $C$ are at least one column wide, and so the block form of the matrix gives a nontrivial factorization of $\Delta_{I_i}=\det A\det B$.
-This yields a contradiction as in Case 1: $f|\det A$ and removing a propagator not in $S$ gives a smaller diagram with a factor of degree $\geq 3$ which contradicts our minimality assumption.\note{I rephrased this last sentence quite a bit because earlier things had gotten rephrased}
-
-On the other hand, if no vertex $\geq_i j$ is in $I_i$ then $\Delta_{I_i} = \det A$.
-Looking in more detail into $A$, note that the only vertices in the support of $p$ and $q$ which belong to $I_i$ are $i$ and $i+1$, and hence
-\[
-A = \begin{bmatrix} D & 0 \\ E & F\end{bmatrix}
-\]
-where $D$ is the $2\times 2$ matrix indexed by the propagators $p$ and $q$ and the vertices $i$ and $i+1$.
-Thus $p$ and $i$ contribute to a quadratic factor of $\Delta_{I_i}$, once again contradicting our assumptions.
-
-All cases have now been covered and so $\Delta_{I_i}$ has only irreducible factors of degree $2$ or less.
-
-\item Suppose propagators $p$ and $q$ are supported on a common edge $(a,b)$, with $I_i(p)=a$ and $I_i(q)=b$.
-Let $x_{p,a},x_{p,b},x_{q,a},x_{q,b}$ be the associated variables in $C(W)$.
-For any fixed bijection $\sigma$ from $\cP-\{p,q\}$ to $I_i -\{a,b\}$ for which each propagator is supported on its image under the bijection, we can extend $\sigma$ to a bijection of all propagators with $I_i$ in two ways: either $p\mapsto a$ and $q\mapsto b$ or $p\mapsto b$ and $q\mapsto a$.
-The sum of the contributions of all these bijections to $\Delta_{I_i}$ is therefore the product of $x_{p,a}x_{q,b}-x_{p,b}x_{q,a}$ \note{Could this use a ref back to where we discuss this kind of arugment in more detail.} with the minor coming from $\cP-\{p, q\}$ and $I_i - \{a,b\}$.
-Since there is no cancellation of terms in the expansion of $\Delta_{I_i}$, if any other terms appear then they will cause a factor which is not in the form described in the previous part.
-Therefore no such terms exist and $x_{p,a}x_{q,b}-x_{p,b}x_{q,a}$ is a factor of $\Delta_{I_i}$.
-
-Now let $f$ be a quadratic factor of $\Delta_{I_i}$.
-By part (2) we know that $f$ is a $2\times 2$ minor coming from two propagators, call them $p$ and $q$, and two vertices, call them $a <_i b$.
-It remains to show that $a$ and $b$ are adjacent.
-From this we can conclude that $p$ and $q$ each have one end on $(a,b)$, as any other way for both $p$ and $q$ to be supported on two consecutive vertices would contradict noncrossing or the density requirement of admissibility.
-
-As in the proof of part (2), make a new admissible diagram by removing the propagators which come before $f$ and set $i=a$.
-The cases in the proof of part (2) show how $\Delta_{I_i}$ factors: in particular the vertices supporting the other end of $p$ either do not appear in $I_i$, or they contribute to a different factor of $\Delta_{I_i}$ than $p$ and $a$ do.
-By assumption $b$ contributes to the same factor as $a$.
-Therefore $(a,b)$ is an edge.
-
-\item Consider $p\in S_i$, and note that $\Delta_{I_i}$ is homogeneous linear in the variables of the row corresponding to $p$.
-By part (2), either exactly one variable in the row corresponding to $p$ appears in $\Delta_{I_i}$ and this variable is a factor of $\Delta_{I_i}$, or exactly two variables from the row corresponding to $p$ appear in $\Delta_{I_i}$ and they appear as part of a quadratic factor.
-In the first case let the variable be $x$.
-Then $x$ is a factor of $\Delta_{I_i}$ and so in particular the monomial in $\Delta_{I_i}$ corresponding to the bijection between propagators and vertices of $I_i$ associates the column of $x$ to $p$.
-Thus $x$ also appears in $r_i$ and since the matrix for $r_i$ is a minor of the matrix for $\Delta_{I_i}$ and every term in $\Delta_{I_i}$ involves $x$, we also have that every term in $r_i$ involves $x$ so $x$ is a factor of both $r_i$ and $\Delta_{I_i}$ and is the only variable from this row in either polynomial.
-
-Now suppose two variables from the row $p$ appear in a quadratic factor $f$ of $\Delta_{I_i}$.
-By part (3), there is another propagator $q$ and an edge $(a,b)$ such that $f$ is the $2\times 2$ minor coming from $p, q$ and $a, b$, with $I_i(p)=a$, $I_i(q)=b$.
-There are two situations which can occur, both illustrated in Figure~\ref{fig quadratic}; we show that in both cases it follows that $q \in S_i$ as well.
-
-\begin{figure}
-\[
-\begin{tikzpicture}[baseline=(current bounding box.east)]
-	\begin{scope}
-	\drawWLDfragment[2]{4}{0.1} 
-	%\drawnumberspartial % use this to debug
-	\newnode[below]{1}{a}
-	\newnode[below]{2}{b}
-	\begin{scope}
-	\clipcenterarc(0,0)(\zero - 1.5*\step:\zero + 4.5*\step:\radius)
-	\newprop[midway,left]{1.33}{-7}{\footnotesize $p$}
-	\newprop[midway,right]{1.66}{10}{\footnotesize $q$}
-	\end{scope}
-	\node at (\zero + 0.6*\step:\radius*0.7) {\footnotesize $p$};
-	\node at (\zero + 2.4*\step:\radius*0.7) {\footnotesize $q$};
-\end{scope}
-\end{tikzpicture}
-\begin{tikzpicture}[baseline=(current bounding box.east)]
-	\begin{scope}
-	\drawWLDfragment[2]{4}{0.1} 
-	%\drawnumberspartial % use this to debug
-	\newnode[below]{1}{b}
-	\newnode[below]{2}{a}
-	\begin{scope}
-	\clipcenterarc(0,0)(\zero - 1.5*\step:\zero + 4.5*\step:\radius)
-	\newprop[midway,left]{1.33}{-7}{\footnotesize $q$}
-	\newprop[midway,right]{1.66}{10}{\footnotesize $p$}
-	\end{scope}
-	\node at (\zero + 0.6*\step:\radius*0.7) {\footnotesize $q$};
-	\node at (\zero + 2.4*\step:\radius*0.7) {\footnotesize $p$};
-\end{scope}
-\end{tikzpicture}
-\]
-  \caption{The situations giving a quadratic factor with variables appearing in $r_i$.}\label{fig quadratic}
-\end{figure}
-
-In both cases, since $I_{i-1}(p)\neq a$ by assumption it follows from Lemma~\ref{vertex cyclic int lem} that $I_{i-1}(p) <_{i-1} a$ and no other vertex supporting $p$ lies between $I_{i-1}(p)$ and $a$.
-In the case that $b<_i a$ and $q$ is assigned before $p$ in $I_i$, this means that $I_{i-1}(p)=b$ and so $I_{i-1}(q)\neq b$.
-Thus $q\in S_i$ and so $f$ is a factor of $r_i$.
-
-Now consider the case where $a<_i b$, and suppose for contradiction that $q \not\in S_i$, i.e.
-that $I_{i-1}(q) = b$.
-Since $I_{i-1}(p) \neq a$, there must be some other propagator $s$ with $I_{i-1}(s) = a$ (else $I_{i-1}$ assigns $q$ to $a$).
-This propagator cannot lie on edge $(a,b)$ since, by Lemma~\ref{vertex cyclic int lem}, we must have $I_i(s) \in \{a, b\}$, contradicting the fact that $I_i(p) = a$ and $I_i(q) = b$; thus $s$ has an end on $(a-1,a)$ and is inside $p$ in the $<_k$ order where $p=(k,a)$.
-
-Say $s = (j,a)$ with $i-1 \leq_{i-1} k+1 \leq_{i-1} j+1$.
-But by Lemma~\ref{lem no fourth vertex}, if $I_{i-1}(s) = a$ then $a$ cannot be maximal in the support of $s$ with respect to $<_{i-1}$; thus we must have $i-1 = j+1$, and we are in the situation in Figure~\ref{fig part 4}.
-
-\begin{figure}
-\[
-\begin{tikzpicture}[baseline=(current bounding box.east),rotate = -40]
-	\begin{scope}
-	\drawWLDfragment[8]{3}{0.4} 
-	%\drawnumberspartial % use this to debug
-	\newnode{1}{}
-	\newnode[left]{2}{i-1}
-	\newnode[below]{5}{a-1\quad}
-	\newnode[below]{6}{a}
-	\newnode[below]{7}{b}
-	\begin{scope}
-		\clipcenterarc(0,0)(\startpoint:\endpoint+\step:\radius)
-		\newpropbend{1.5}{5.7}{20}
-		\newpropbend{1.3}{6.4}{30}
-		\newprop{6.6}{-6}{}
-	\end{scope}
-	\node at (\zero + 3.5*\step:\radius*0.8){\footnotesize $s$};
-	\node at (\zero + 4.8*\step:\radius*0.45){\footnotesize $p$};
-	\node at (\zero + 8*\step:\radius*0.65){\footnotesize $q$};
-\end{scope}
-\end{tikzpicture}
-\]
-  \caption{In order to obtain $I_{i-1}(s) = a$, propagators $s$ and $p$ must each have an end on the edge $(i-2,i-1)$.}\label{fig part 4}
-\end{figure}
-
-Since $p$ changed its association from $I_{i-1}$ to $I_i$, we have $I_{i-1}(p) = i-1$ by Lemma~\ref{vertex cyclic int lem}.
-From Figure~\ref{fig part 4} it follows that $I_{i-1}$ assigns $p$ to $i-1$ and then proceeds identically to $I_i$ for all vertices inside $p$, implying that $I_{i-1}(s) = I_i(s)$.
-Since $I_{i-1}(s) = a$ and $I_i(s) \neq a$, this is a contradiction.
-
-Thus $q\in S_i$ after all, and so $f$ is a factor of $r_i$ as required.
-
-% Thus $s$ is supported on $a$ but does not have an edge on $(a,b)$ and so $s$ must have an end on $(a-1, a)$ and so be inside $p$ from the point of view of $i-1$.
-Say $s$ is supported on $(j, j+1, a-1, a)$ and $p$ is supported on $(k, k+1, a, b)$ with $i-1 \leq_{i-1} k+1 \leq_{i-1} j+1$.
-Again by Lemma~\ref{lem susama}, immediately after $s$ contributes $a$ it must contribute $j$ and so $I_i(s)=j$.
-
-% Finally we want to show $I_i(s)=j$ gives a contradiction.
-If $k=j$ then $I_{i}(s)= k$, but $p$ has not yet been taken as $I_i(p)=a$ and $p$ comes before $s$ around $k$, so this is a contradiction.
-If $k+1=j$ then similarly $I_{i}(s)=k+1$ and yet $p$ comes before $s$ around $k$, a contradiction to $I_i(p)=a$.
-Now suppose $k+1 <_{i-1} j$ then we have $i-1 \leq_{i-1} k+1 <_{i-1} I_i(s) = j$ so $i\leq_{i} I_i(s)$ which gives that
-% \[
-% I_i(s) <_i I_{i-1}(s) \qquad \text{and} \qquad I_i(s) <_{i-1} I_{i-1}(s)
-% \]
-% \note{Is this known to be impossible by the proof sketch of Lemma~\ref{lem susama} that you emailed or something similar.
-I'm thinking this proof is already too long and the fact that this is impossible would be better as a lemma.}
-
-\item If $W$ has zero propagators then all $I_i=\emptyset$ and both $R$ and $\prod_{i=1}^n \Delta_{I_i}$ are equal to $1$, so the result holds in this case.
-Now assume $W$ has at least one propagator.
-
-First we show that every factor of $\prod_{i=1}^n \Delta_{I_i}$ divides $R$.
-Take an irreducible factor $f$ of $\prod_{i=1}^n \Delta_{I_i}$.
-There exists some $i$ such that $f|\Delta_{I_i}$ but $f\!\!\nmid\!\!
-\Delta_{I_{i-1}}$, since otherwise the variables corresponding to the propagators contributing to $f$ which do not themselves appear in $f$ could never appear, contradicting Lemma~\ref{vertex cyclic int lem}.
-If $f$ is a linear factor, say from associating propagator $p$ to vertex $a$, then $I_{i}(p)=a$ and $I_{i-1}(p)\neq a$ so this factor appears in $r_i$.
-If $f$ is a quadratic factor, say from associating propagators $p$ and $q$ to vertices $a$ and $b$ respectively, then again we cannot have both $I_{i-1}(p) = a$ and $I_{i-1}(q) = b$, else $f$ divides $\Delta_{i-1}$.
-However, by the proof of part (4), if one of $p,q$ belongs to $S_i$ then the other does as well.
-Thus $f$ divides $r_i$.
-
-Next we need to show that $R$ is squarefree.
-Suppose $f^2|R$.
-If $f$ is a linear factor, say from associating propagator $p$ to vertex $a$, then there must be two distinct points in the Grassmann necklace algorithm where $p$ changes from not being associated to vertex $a$ to being associated to vertex $a$.
-This contradicts Lemma~\ref{vertex cyclic int lem}.
-Now suppose $f$ is a quadratic factor, say from propagators $p$ and $q$ supported on the edge $(a, b)$ with $p$ before $q$ on the edge.
-In this case it is not possible for any $I_i$ to associate $p$ to $b$ and $q$ to $a$.
-Furthermore, we know by part (4) that $p$ changes from not being associated to $a$ to being associated to $a$ if and only if $q$ changes from not being associated to $b$ to being associated to $b$.
-Thus $f^2|R$ implies that twice in the Grassmann necklace $p$ must change from not being associated to vertex $a$ to being associated to vertex $a$.
-This is again a contradiction, and so $R$ is squarefree.
-
-Taking everything together we have that $R|\prod_{i=1}^n \Delta_{I_i}$, $R$ contains all factors of $\prod_{i=1}^n \Delta_{I_i}$ and $R$ is squarefree.
-Therefore the ideal generated by $R$ is the radical of the ideal generated by $\prod_{i=1}^n \Delta_{I_i}$.
-  \end{enumerate}
-\end{proof}
-
-\begin{thm}\label{thm denom}
-  Given any admissible Wilson loop diagram $W$, let $\{I_1, \ldots I_n\}$ be the associated Grasmann necklace.
-Then the denominator of the integral, $R(W)$ (see Definition~\ref{def R(W)}), is the $R$ of Algorithm~\ref{alg WLD to denom via GN}.
-Furthermore, the ideal generated by $R(W)$ is the radical of the ideal generated by $\prod_{i=1}^n \Delta_{I_i}$, where $\Delta_{I_i}$ is the determinant of the $k \times k$ minor indicated by $I_i$.
-\end{thm}
-
-\begin{proof}
-The equivalence of the ideal generated by $R$ and the radical of the ideal generated by $\prod_{i=1}^n \Delta_{I_i}$ is due to Proposition~\ref{prop alg gives rad}.
-It remains to prove that $R(W)$ is the $R$ of Algorithm~\ref{alg WLD to denom via GN}.
-
-To this end, first note that $R(W)$ and $R$ both have total degree $4|\mathcal{P}|$; the degree of $R(W)$ is immediate from the definition while that of $R$ follows from Lemma~\ref{vertex cyclic int lem}.
-By Proposition~\ref{prop alg gives rad} every factor of $R$ is either a quadratic factor coming from two propagators supported on a common edge or a single variable coming from a support vertex of a propagator not appearing in a quadratic factor.
-The factors of each $R_e$ making up $R(W)$ in the notation of Definition~\ref{def R(W)} are all of this form and every such factor occurs.
-Hence every factor of $R$ divides $R(W)$.
-Finally, since $R$ is squarefree, this implies that $R(W)$ is a scalar multiple of $R$.
-
-Finally then we need to check the scalar.
-By Definition~\ref{def R(W)} each linear factor appears with coefficient $1$ and each $2\times 2$ determinant factor appears with the same sign as the determinant of the corresponding minor in $C(W)$.
-Therefore $R=R(W)$.
-\end{proof}
-
-Thus we have shown a deep relationship between the physically derived poles of the integrals $I(W)$ and the geometry and combinatorics associated to the diagrams $W$.
-At the very least, this is yet another piece of circumstantial evidence indicating that the positroid representation of Wilson loop diagrams is the correct geometric object to be considering when considering the Wilson loop amplitudes geometrically.
-
-While the authors cannot yet offer a proof that the appropriate sum of the Wilson loop diagrams are, in fact, finite, as conjectured [cite]\note{One last cite to fill out}, we do hope that this relationship to the Grassmann Necklace elements will provide a different avenue for answering that and related questions.
-
-\bibliographystyle{abbrv}
-\bibliography{WLDbib}
-
-% \begin{thebibliography}{10}
-% \bibitem{Adamo:2011pv}
-% Tim Adamo, Mathew Bullimore, Lionel Mason, and David Skinner.
-% \newblock {Scattering Amplitudes and Wilson Loops in Twistor Space}.
-% \newblock {\em J.Phys.A}, A44:454008, 2011.
-
-% \bibitem{Adamo:2012xe}
-% Tim Adamo and Lionel Mason.
-% \newblock {Twistor-strings and gravity tree amplitudes}.
-% \newblock {\em Class.Quant.Grav.}, 30:075020, 2013.
-
-% \bibitem{wilsonloop}
-% Susama Agarwala and Eloi~Marin Amat.
-% \newblock Wilson loop diagrams and positroids.
-% \newblock {\em Communications in Mathematical Physics}, 2016.
-% \newblock arXiv:1509.06150.
-
-% \bibitem{casestudy}
-% Susama Agarwala and Sian Fryer.
-% \newblock A study in $\textrm{Gr}_{\geq 0}(2,6)$: from the geometric case book
-%   of {W}ilson loop diagrams and {SYM} $n=4$.
-% \newblock arXiv:1803.00958.
-
-% \bibitem{non-orientable}
-% Susama Agarwala and Cameron Marcott.
-% \newblock Wilson loops in sym $n=4$ do not parametrize an orientable space.
-% \newblock arXiv:1807.05397.
-
-% \bibitem{UnwindingAmplituhedron}
-% Nima Arkani-Hamed, Hugh Thomas, and Jaroslav Trnka.
-% \newblock Unwinding the amplituhedron in binary.
-% \newblock {\em Journal of High Energy Physics}, 2018(1):16, Jan 2018.
-% \newblock arXiv:1704.05069.
-
-% \bibitem{Arkani-Hamed:2013kca}
-% Nima Arkani-Hamed and Jaroslav Trnka.
-% \newblock {Into the Amplituhedron}.
-% \newblock {\em JHEP}, 12:182, 2014.
-
-% \bibitem{Arkani-Hamed:2013jha}
-% Nima Arkani-Hamed and Jaroslav Trnka.
-% \newblock {The Amplituhedron}.
-% \newblock {\em JHEP}, 10:30, 2014.
-
-% \bibitem{Boels:2007qn}
-% Rutger Boels, Lionel Mason, and David Skinner.
-% \newblock {From twistor actions to MHV diagrams}.
-% \newblock {\em Phys.Lett.}, B648:90--96, 2007.
-
-% \bibitem{Bullimore:2010pj}
-% Mathew Bullimore, Lionel Mason, and David Skinner.
-% \newblock {MHV Diagrams in Momentum Twistor Space}.
-% \newblock {\em JHEP}, 1012:032, 2010.
-
-% \bibitem{CasteelsPaths}
-% K. Casteels.
-% \newblock Quantum matrices by paths.
-% \newblock {\em Algebra Number Theory}, 8(8):1857--1912, 2014.
-
-% \bibitem{Amplituhedronsquared}
-% Burkhard Eden, Paul Heslop, and Lionel Mason.
-% \newblock The AmplituhedronSquared.
-% \newblock 2017.
-% \newblock arxiv:1701.00453.
-
-% \bibitem{galashinlam}
-% P.~{Galashin} and T.~{Lam}.
-% \newblock {Parity duality for the amplituhedron}.
-% \newblock {\em arXiv e-prints}, May 2018.
-
-% \bibitem{HeslopStewart}
-% Paul Heslop and Alastair Stewart.
-% \newblock The twistor wilson loop and the amplituhedron.
-% \newblock {\em Journal of High Energy Physics}, 2018(10):142, Oct 2018.
-
-% \bibitem{Hodges:2012ym}
-% Andrew Hodges.
-% \newblock {A simple formula for gravitational MHV amplitudes}.
-% \newblock 2012.
-
-% \bibitem{AmplituhedronDecomposition}
-% Steven~N. Karp, Lauren~K. Williams, and Yan~X. Zhang.
-% \newblock Decompostions of amplituhedra.
-% \newblock arXiv:1708.09525.
-
-% \bibitem{GrassmannAmplitudebook}
-% Freddy Cachazo Alexander Goncharov Alexander Postnikov Jaroslav~Trnka
-%   Nima~{A}rkani {H}amed, Jacob~Bourjaily.
-% \newblock {\em Grassmannian Geometry of Scattering Amplitudes}.
-% \newblock Cambridge University Press, Cambridge, UK, 2016.
-
-% \bibitem{LipsteinMason}
-% Arthur E. Lipstein, Lionel Mason
-% \newblock From dlogs to dilogs; the super Yang-Mills MHV amplitude revisited
-% \newblock J. High Energ. Phys. (2014) 2014: 169.
-
-% \bibitem{reversingOh}
-% S. Agarwala, S. Fryer.
-% \newblock An algorithm to construct the Le diagram associated to a Grassmann necklace
-% \newblock \url{arXiv:1803.01726}
-
-% \bibitem{Gale}
-% D. Gale.
-% \newblock Optimal assignments in an ordered set: {A}n application of matroid theory.
-% \newblock {\em J. Combinatorial Theory}, 4: 176 - 180 (1968).
-
-% \bibitem{Oh}
-% S. Oh.
-% \newblock Positroids and {S}chubert matroids.
-% \newblock {\em J. Combin. Theory Ser. A}, 118(8):2426--2435, (2011)
-
-% \bibitem{Oh2}
-%   S. Oh.
-%   \newblock Combinatorics of positroids.
-%   \newblock {\em DMTCS Proceedings vol. AK},(FPSAC 2009), 721--732
-
-% \bibitem{Postnikov}
-% A.~Postnikov.
-% \newblock Total positivity, {G}rassmannians, and networks.
-% \newblock \url{arXiv:math/0609764}.
-
-% \end{thebibliography}
-
-\end{document}
+  I_{n-3}^{V} \xrightarrow[\substack{n-3\text{ out}\\n-2\text{ in}}]{} I_{n-2}^{V} \xrightarrow[\substack{n-2\text{ out}\\n-5\

### 2019-08-26 GWLDCII.tex
more or less through 3.17

--- 2019-08-16 GWLDCII.tex
@@
 \newcommand{\gale}[1]{\preccurlyeq_{#1}}
-\newcommand{\sgale}[1]{\prec_{#1}}
+\newcommand{\sgale}[1]{\prex_{#1}}
 \renewcommand\vec[1]{\overrightarrow{#1}}
@@
 
-\begin{equation} C(W)_{p,q} = \begin{cases} c_{p,q} & \textrm{ if } q \in V(p) \\
+\begin{equation} C(W)_{p,q} = \begin{cases} x_{p,q} & \textrm{ if } q \in V(p) \\
 0  & \textrm{ if } q \not \in V(p)  \end{cases}
-\;. \label{C(W) dfn}\end{equation} \todo{Change $c_{p,q}$ to $x_{p,q}$ to be consistent}
-
-The entries $c_{p,q}$ are non-zero real variables.
+\;. \label{C(W) dfn}\end{equation}
+
+The entries $x_{p,q}$ are non-zero real variables.
 Thus the zero entries in row $p$ correspond to the external particles that the propagator $p$ does not interact with.
@@
 One may also interpret the functional $I(W)$ as associating a volume to each cell $\Sigma(W)$ \cite{wilsonloop, Amplituhedronsquared, HeslopStewart}.
-The volume form is written in terms of the elements of $C(W)$ as  \begin{equation} \label{eq:omega(W) def}\Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V(p_r)} \textrm{d}c_{p_r}}{R(W)} \;, \end{equation}
+The volume form is written in terms of the elements of $C(W)$ as  \begin{equation} \label{eq:omega(W) def}\Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V(p_r)} \textrm{d}x_{p_r}}{R(W)} \;, \end{equation}
 where the denominator $R(W)$ is given in Definition~\ref{def R(W)} below.
@@
 Define the polynomial
-\[ R_e =  c_{p_1,e+1} \prod_{j= 1}^{r-1} \left((c_{p_j,e} c_{p_{j+1},e+1} - c_{p_{j+1},e} c_{p_{j},e+1} ) \right) c_{p_r,e}\;\]
+\[ R_e =  x_{p_1,e+1} \prod_{j= 1}^{r-1} \left((x_{p_j,e} x_{p_{j+1},e+1} - x_{p_{j+1},e} x_{p_{j},e+1} ) \right) x_{p_r,e}\;\]
 to be the component of $R(W)$ associated to edge $e$.
 Note that if $r = 1$ (i.e.
-there is exactly one propagator lying on edge $e$) then this expression simplifies to $R_e = c_{p,e} c_{p,e+1}$.
+there is exactly one propagator lying on edge $e$) then this expression simplifies to $R_e = x_{p,e} x_{p,e+1}$.
 If $r=0$, set $R_e = 1$.
@@
 \begin{array}{cccccccc}
-c_{1,1} & c_{1,2} & 0 & c_{1,4} & c_{1,5} & 0 & 0 & 0 \\
-0 & c_{2,2} & c_{2,3} & c_{2,4} & c_{2,5} & 0 & 0 & 0 \\
-0 & 0 & 0 & 0 & c_{3,5} & c_{3,6} & c_{3,7} & c_{3,8} \\
-c_{4,1} & 0 & 0 & 0 & c_{4,5} & c_{4,6} & 0 & c_{4,8}  \\
+x_{1,1} & x_{1,2} & 0 & x_{1,4} & x_{1,5} & 0 & 0 & 0 \\
+0 & x_{2,2} & x_{2,3} & x_{2,4} & x_{2,5} & 0 & 0 & 0 \\
+0 & 0 & 0 & 0 & x_{3,5} & x_{3,6} & x_{3,7} & x_{3,8} \\
+x_{4,1} & 0 & 0 & 0 & x_{4,5} & x_{4,6} & 0 & x_{4,8}  \\
 \end{array}
@@
 
-To calculate $R(W)$, we first compute the polynomials associated to each edge of $W$: \bmls R_1 = c_{1,1} c_{1, 2}\quad R_2 = c_{2,2} c_{2,3} \quad R_4 = c_{2,5} (c_{2,4}c_{1,5} - c_{2,5}c_{1,4})c_{1,4} \\ R_5 = c_{4,6} (c_{4,5}c_{3,6} - c_{3,5}c_{4,6})c_{3,5} \quad R_7 = c_{3,7} c_{3,8} \quad R_8 = c_{4,8} c_{4,1} \;.\emls All other $R_e$ are $1$.
-Finally, the integrand associated to this Wilson loop diagram (recall equation~\eqref{eq:omega(W) def}) is \bas \Omega(W) = \frac{\textrm{d}c_{1,1}\textrm{d}c_{1,2}\textrm{d}c_{1,4}\textrm{d}c_{1,5}\textrm{d}c_{2,2}\textrm{d}c_{2,3}\textrm{d}c_{2,4}\textrm{d}c_{2,5}\textrm{d}c_{3,5}\textrm{d}c_{3,6}\textrm{d}c_{3,7}\textrm{d}c_{3,8}\textrm{d}c_{4,5}\textrm{d}c_{4,6}\textrm{d}c_{4,8}\textrm{d}c_{4,1}}{c_{1,1} c_{1, 2}c_{2,2} c_{2,3}c_{2,5} (c_{2,4}c_{1,5} - c_{2,5}c_{1,4})c_{1,4}c_{4,6} (c_{4,5}c_{3,6} - c_{3,5}c_{4,6})c_{3,5}c_{3,7} c_{3,8}c_{4,8} c_{4,1}} \;.
+To calculate $R(W)$, we first compute the polynomials associated to each edge of $W$: \bmls R_1 = x_{1,1} x_{1, 2}\quad R_2 = x_{2,2} x_{2,3} \quad R_4 = x_{2,5} (x_{2,4}x_{1,5} - x_{2,5}x_{1,4})x_{1,4} \\ R_5 = x_{4,6} (x_{4,5}x_{3,6} - x_{3,5}x_{4,6})x_{3,5} \quad R_7 = x_{3,7} x_{3,8} \quad R_8 = x_{4,8} x_{4,1} \;.\emls All other $R_e$ are $1$.
+Finally, the integrand associated to this Wilson loop diagram (recall equation~\eqref{eq:omega(W) def}) is \bas \Omega(W) = \frac{\textrm{d}x_{1,1}\textrm{d}x_{1,2}\textrm{d}x_{1,4}\textrm{d}x_{1,5}\textrm{d}x_{2,2}\textrm{d}x_{2,3}\textrm{d}x_{2,4}\textrm{d}x_{2,5}\textrm{d}x_{3,5}\textrm{d}x_{3,6}\textrm{d}x_{3,7}\textrm{d}x_{3,8}\textrm{d}x_{4,5}\textrm{d}x_{4,6}\textrm{d}x_{4,8}\textrm{d}x_{4,1}}{x_{1,1} x_{1, 2}x_{2,2} x_{2,3}x_{2,5} (x_{2,4}x_{1,5} - x_{2,5}x_{1,4})x_{1,4}x_{4,6} (x_{4,5}x_{3,6} - x_{3,5}x_{4,6})x_{3,5}x_{3,7} x_{3,8}x_{4,8} x_{4,1}} \;.
 \eas
@@
 We first calculate $I^{W}_w$ for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$.
-Note that $p$ has no effect on other propagators for starting vertices in this range, so if $r \neq p$, then $I_w^W(r) = I_w^V(r)$.
-Meanwhile, the value of $I^{W}_w(p)$ depends on which step in the algorithm the propagator $q$ is assigned to a vertex, i.e.
+\hlfix{Note that $p$ has no effect on other propagators for starting vertices in this range,}{By rmk \ref{rmk algorithm locally same}?
+If so, the entire proof depends on this fact.
+We should state it prominently and move on.} so if $r \neq p$, then $I_w^W(r) = I_w^V(r)$.
+Meanwhile, the value of $I^{W}_w(p)$ depends on which step in the algorithm the propagator $q$ \hlfix{is assigned to}{was this the one place where we has agreed to keep assigned instead of contributes?} a vertex {\color{violet} in the diagram $V$}, i.e.
 on the value of $I^{V}_w(q)$.
@@
 
+\sanote{skipping careful read of this proof and moving on}
 Consider the Wilson loop diagram $X$ formed from $V$ by replacing the propagator $q = (i,j)$ with $q = (i, j-1)$;  $X$ is still admissible since we have not decreased the support of any set of propagators.
@@
 \begin{proof}
-\note{Sian replaced ``counterclockwise'' with ``clockwise'' in a couple of places in this proof: someone please doublecheck?  Karen checked and it seems correct with Sian's changes.}
+%\note{Sian replaced ``counterclockwise'' with ``clockwise'' in a couple of places in this proof: someone please doublecheck?  Karen checked and it seems correct with Sian's changes.}
 For each $i \in [n]$, let $I_i$ be the set of vertices assigned to the propagators of $W$ by Algorithm~\ref{alg:put GN on WLD} with starting vertex $i$.
@@
 Fix $n$.
-Let the triple $(W, i, m)$ be such a counterexample on $n$ vertices which is minimal with respect to the number of propagators.
+Let the triple $(W, i, m)$ be such a counterexample on $n$ vertices \hlfix{which is minimal with respect to the number of propagators}{minimal in what respect?
+$i$ first where this occurs?
+$m$ the smallest such number?
+what do propagators have to do with it?}.
 %, and among all those counterexamples on $n$ vertices with the same number of propagators, let $(W,i,k)$ be minimal with respect to the distance from $i$ to $k$ in the $\leq _i$ order.
@@
 \textbf{Case I}:  Suppose $p$ has one end on edge $i-1$.
-If $p$ is not supported on $i+1$, then in building $I_{i+1}$ we will assign the same propagators as in the construction of $I_i$ from vertices $i+1$ up to $b-1$, that is $I_{i+1} \cap [i+1,b-1] = I_{i} \cap [i+1,b-1]$.
-If $p$ is supported on $i+1$, then $b= i+1$ and the interval $[i+1,b-1]$ is empty, so the previous equality remains true, albeit vacuously.
+If $p$ is not supported on $i+1$, then in building $I_{i+1}$ we will assign the same propagators as in the construction of $I_i$ from vertices $i+1$ up to $b-1$, that is \bas I_{i+1} \cap [i+1,b-1] = I_{i} \cap [i+1,b-1]\eas {\color{violet}by Remark \ref{rmk algorithm locally same}}.
+If $p$ is supported on $i+1$, then $b= i+1$ and the interval $[i+1,b-1]$ is empty, so the above equality remains true, albeit vacuously.
 Furthermore, by Lemma~\ref{vertex cyclic int lem} it must happen that $p$ contributes vertex $b$ to $I_{i+1}$, as otherwise $b$ would never be contributed by $p$.
-Consequently, in building $I_{i+1}$, when the algorithm reaches vertex $b$ there cannot be any remaining unassigned propagators that are supported on $b$ and clockwise of $p$.
-This is also true in when the algorithm constructing $I_i$ reaches $b$, since the same propagators have been assigned beforehand.
-This also implies that $m\geq_i b+1$.
+Consequently, by Remark \ref{clockwise ordering rem}, in building $I_{i+1}$,  when the algorithm reaches vertex $b$ there cannot be any remaining unassigned propagators that are supported on $b$ and clockwise of $p$.
+This is also true in when the algorithm constructing $I_i$ reaches $b$, \st{since the same propagators have been assigned beforehand.}\sanote{don't like same here}{\color{violet}since any propagators lying counterclockwise of $p$ on the edge $i-1$ must have their support in $[i-1, b]$.
+By Lemma \ref{no fourth vertex}, these propagators contribute before the algorithm reaches $b$.
+Furthermore, Remark  \ref{rmk algorithm locally same} implies that these propagators contribute the same vertices to both $I_i$ and $I_{i+1}$.} This also implies that $m\geq_i b+1$.
 
@@
 
-By the above observations, if we commence Algorithm~\ref{alg:put GN on WLD} in $W'$ from vertex $b$, then we are in the same situation with respect to unassigned propagators as if we began at $i$ in $W$ and proceeded to $b$ following the algorithm (recall that $I^W_i(p) =i$).
-The propagators contributing to $I_{i}^W$ before the vertex $b$ are exactly the ones removed in the construction of $W'$.
-Similarly, starting at $i+1$ in $W$ and moving to $b+1$ leaves us in the same situation with respect to unassigned propagators as beginning at $b+1$ in $W'$ would.
+\st{By the above observations, if we commence Algorithm {\ref{alg:put GN on WLD}} in $W'$ from vertex $b$, then we are in the same situation with respect to unassigned propagators as if we began at $i$ in $W$ and proceeded to $b$ following the algorithm (recall that $I^W_i(p) =i$).} {\color{violet} Note that the propagators in $\cP_{out}(p,<_i)$ come first in the ordering imposed by $I_i^W$ (Definition \ref{proporderingdfn}).
+Therefore, the ordering and contributions of propagators defined by $I_b^{W'}$ are the same as that of $I_i^W$ after the removal of these initial propagators.} \st{The propagators contributing to $I_{i}^W$ before the vertex $b$ are exactly the ones removed in the construction of $W'$.}  Similarly, starting at $i+1$ in $W$ and moving to $b+1$ leaves us in the same situation with respect to unassigned propagators as beginning at $b+1$ in $W'$ would.
 This gives the equations
@@
 \end{align*} 
-where the diagram is indicated in the superscript.
-Thus we have $m\in I_b^{W'}\setminus\{b\}$ and $m\not\in I_{b+1}^{W'}$, contradicting the minimality of $(W, i, m)$.
+\st{where the diagram is indicated in the superscript.}
+Thus we have $m\in I_b^{W'}\setminus\{b\}$ and $m\not\in I_{b+1}^{W'}$, contradicting the minimality of $(W, i, m)$.\sanote{see previous question about minimality.
+not sure why this is true, unless minimality in $|[i,m]|$?.}
 
@@
 
+Thus we have shown that Algorithm \ref{alg:put GN on WLD} does in fact produce a Grassmann necklace. Next we check that it produces the correct one, i.e. the Grassmann Neclace for $M(W)$.
+
 \begin{thm}\label{res alg gives correct GN}
@@
 \end{thm}
-
+\sanote{skipping reading of this for now}
 \begin{proof}
@@
 This completes the induction step, and hence the proof.\end{proof}
+
+\sanote{START HERE}
 

### 2019-08-27 GWLDCII.tex
started section 4

@@
 While it was already possible to construct the Grassmann necklace of a Wilson loop diagram via existing bijections between some of the various combinatorial objects that index the positroid cells, this process was convoluted and involved multiple steps; our algorithm allows us to track directly how each propagator in the Wilson loop diagram contributes to each term in the Grassmann necklace.
-Many of the technical lemmas required to prove Theorem~\ref{res:alg gives GN} continue to be important in subsequent sections: in particular we have Lemma~\ref{lem sian}, which identifies certain configurations of propagators that must appear in any admissible Wilson loop diagram, and Lemma~\ref{vertex cyclic int lem}, which shows that the pattern of values that a propagator contributes to each term of the Grassmann necklace is both simple and predictable.
+{\color{violet} Furthermore, the above algorithm allows us to determine that the positroids associated to Wilson loop better.
+In particular, Corrollary \ref{no coloops} shows that these positroids have no coloops, and gives an exact characterization of their loops.}Many of the technical lemmas required to prove Theorem~\ref{res:alg gives GN} continue to be important in subsequent sections: in particular we have Lemma~\ref{lem sian}, which identifies certain configurations of propagators that must appear in any admissible Wilson loop diagram, and Lemma~\ref{vertex cyclic int lem}, which shows that the pattern of values that a propagator contributes to each term of the Grassmann necklace is both simple and predictable.
 
@@
 In this section we will give an algorithm (Algorithm~\ref{alg:put GN on WLD}) to go directly from a Wilson loop diagram to the Grassmann necklace of its positroid.
-This is a useful result in and of itself, as it greatly simplifies the process of identifying the positroid associated to a given WLD.
-It also allows us to examine how the positroid changes as we make minor changes to the Wilson loop diagram; indeed, the techniques we develop in this section to verify that our algorithm produces the correct Grassmann necklace will also be used repeatedly in later sections.
+This is a useful result in and of itself, as it greatly simplifies the process of identifying the positroid associated to a given Wilson loop diagram.
+{\color{violet} Furthemore, we use it to characterise the positroids associated to Wilson loop diagrams according to loops and coloops (Corrollary \ref{no coloops}).} It also allows us to examine how the positroid changes as we make minor changes to the Wilson loop diagram; indeed, the techniques we develop in this section to verify that our algorithm produces the correct Grassmann necklace will also be used repeatedly in later sections.
 
@@
 
-\sanote{START HERE}
-
-We can now unambiguously refer to Algorithm~\ref{alg:put GN on WLD} as the Grassmann necklace algorithm.
+We have now shown that Algorithm~\ref{alg:put GN on WLD} assoiates the correct Grassmann necklace to a Wilson Loop diagam Thereofre, we refer to Algorithm~\ref{alg:put GN on WLD} as the Grassmann necklace algorithm.
 We close this section with a simple observation about the Grassmann necklaces of positroids associated to Wilson loop diagrams.
@@
 
-\begin{cor}\label{no coloops}\sanote{cite more prominently in frontmatter}
+\begin{cor}\label{no coloops}
 Grassmann necklaces coming from admissible Wilson loop diagrams have no coloops. A vertex $j$ is a loop if and only if $j$ supports no propagators. 
@@
 Thus $i-1 \not\in I_{i}$, so $i-1$ is not a coloop.
-Since this holds for any $i \in [n]$, the Grassmann necklace admis no coloops.
+Since this holds for any $i \in [n]$, the Grassmann necklace admits no coloops.
 
@@
 
-Our next goal is to show that the dimension of the positroid cell defined by a Wilson loop diagram $(\cP, [n])$ has dimension $3|\cP|$ (Theorem \ref{thm dim}).
+In continuing to characterise the poistroid cells associated to Wilson loop diagrams, our next goal is to show that the dimension of the positroid cell defined by a Wilson loop diagram $(\cP, [n])$ has dimension $3|\cP|$ (Theorem \ref{thm dim}).
 The positroid cells associated to the Amplituhedron are of dimension $4|\cP|$.
-In \cite{non-orientable}, Agarwala and Marcott show that the dimension of the Deodhar component is
-\[|\cP| + \text{ the dimension of associated positroid cell}.\]
-\note{What if instead of displaying this we wrote ``is the sum of $\|\cP\|$ and the dimension fo the associated positroid cell.''}
+In \cite{non-orientable}, Agarwala and Marcott show that the dimension of the Deodhar component is the sum of $\|\cP\|$ and the dimension fo the associated positroid cell.
+%\[|\cP| + \text{ the dimension of associated positroid cell}.\]
+\note{What if instead of displaying this we wrote ``is the sum of $\|\cP\|$ and the dimension fo the associated positroid cell.''}\sanote{implemented, but don't like how it no longer stands out.
+Thoughts?}
 In other words, the Deodhar component associated to a Wilson loop diagram is $4|\cP|$, showing that the geometry underlying the Wilson loop diagrams is consistent with the geometry underlying the Amplituhedron.
 
-Marcott in \hlfix{***cite this***}{highlighted for anyone skimming through} gives a different proof of the $3|\cP|$-dimensionality of $M(W)$ which is geometric and more elegant, but it is not easy to track the effect of a particular propagator.
+Marcott in \cite{WLDdim} gives a different proof of the $3|\cP|$-dimensionality of $M(W)$ which is geometric and more elegant, but it is not easy to track the effect of a particular propagator.
 Our approach is much more explicit.
@@
 We begin by relating non-supporting vertices to columns of zeros in the Le diagram (Lemma \ref{lem uncovered}) and verifying that performing dihedral transformations on a Wilson loop diagram does not change the dimension of of the associated Le diagram (Lemma \ref{lem dihedral}).
+
+\sanote{musing: would it be worth moving the LE diagram exposition here? Do we use it ealier? I like having exposition in front generally, but it feels a mile away.}
 
@@
   By Algorithm~\ref{alg:put GN on WLD} the Grassmann necklace of $W$ is obtained from the Grassmann necklace of $V$ by duplicating the $i$th element of the Grassmann necklace of $V$ (shifting indices by $1$ for all indices greater than $i$), and incrementing all indices greater than $i$ by $1$ in each Grassmann necklace element\note{This is saying to increment twice in a way which I think is confusing, but presumably the parenthetical remark was put there to try to clarify something so I don't want to just remove it}.
-Formally, if $I_1^{V}, \ldots, I_{n-1}^{V}$ and $I_1^{W}, \ldots, I_n^{W}$ are the Grassmann necklaces of $V$ and $W$ respectively then
+Formally, \st{if $I_1^{V}, \ldots, I_{n-1}^{V}$ and $I_1^{W}, \ldots, I_n^{W}$ are the Grassmann necklaces of $V$ and $W$ respectively then}\sanote{in favor of removing parenthetical, we say same thing twice without it}
   \[
@@
 
-By Lemma~\ref{no coloops} we know that $i \not\in I_1^W$, and so $i$ must label a horizontal edge on the boundary of the Le diagram of $W$, i.e.
+By Corrollary~\ref{no coloops} we know that $i \not\in I_1^W$, and so $i$ must label a horizontal edge on the boundary of the Le diagram of $W$, i.e.
 it must be a column label.

### 2019-08-27 GWLDCII.tex
starting 4.4

@@
 Note that a propagator in $\Prop(U)$ does not need to have its entire support contained in $U$. 
-\item Vertices of $W$ that do not support any propagators are called {\bf non-supporting}. The set of all non-supporting vertices in $W$ is denoted $F(\emptyset)$. 
+\item Vertices of $W$ that do not support any propagators are called {\bf non-supporting}.
+\st{The set of all non-supporting vertices in $W$ is denoted $F(\emptyset)$.
+}\sanote{tried to get rid of this notation.
+Check if I"ve missed any}
 \end{enumerate}
@@
 Now suppose $W$ has more than one propagator.
-Since non-supporting vertices have no effect on Algorithm~\ref{alg:put GN on WLD}, it suffices to prove the result for $W$  (possibly weakly admissible) with $F(\emptyset) = \emptyset$.
+Since non-supporting vertices have no effect on Algorithm~\ref{alg:put GN on WLD}, it suffices to prove the result for $W$  (possibly weakly admissible) with \st{$F(\emptyset) = \emptyset$}{\color{violet} no non-supporting vertices}.
 Then by Lemma~\ref{lem sian}, $W$ has at least one of the four situations illustrated in Figure~\ref{fig 3 cases}.
@@
 \begin{lem}\label{lem good p}
-  Let $W$ be an admissible Wilson loop diagram with $n\geq 1$ propagators.
+  Let $W$ be an admissible Wilson loop diagram with \hlfix{$n\geq 1$}{$k \geq 1$?
+$n$ is the number of vertices?} propagators.
 Then there is some dihedral transformation of $W$ such that the resulting diagram $W'$ has a propagator $p$ with the following properties:
   \begin{itemize}
-  \item $p = (i, n-1)$ for some $i$, and $p$ has no propagators inside it w.r.t the $<_i$ ordering (that is $i+2, \ldots, n-2$ do not support any propagators in $W'$).
+  \item $p = (i, n-1)$ for some $i$, and $p$ has no propagators inside it w.r.t the $<_i$ ordering \st{(that is $i+2, \ldots, n-2$ do not support any propagators in $W'$)}.
   \item Either the edge $i$ in $W'$ only supports $p$, or the edge $i$ in $W'$ supports exactly one other propagator $q = (j,i)$, with no other propagators inside $q$ in the $<_j$ ordering. 
@@
 
-Combining Lemmas \ref{lem uncovered}, \ref{lem dihedral}, and \ref{lem good p}, it therefore suffices to study the Le diagrams of weakly admissible Wilson loop diagrams with $F(\emptyset)  = \emptyset$ and admitting one of the configurations described in Lemma \ref{lem good p}, with propagators $p = (n-3, n-1)$ and $q= (n-5, n-3)$ (if $q$ exists) both of length 2.
+Combining Lemmas \ref{lem uncovered}, \ref{lem dihedral}, and \ref{lem good p}, it therefore suffices to study the Le diagrams of weakly admissible Wilson loop diagrams with \st{$F(\emptyset)  = \emptyset$}{\color{violet}no non-supporting vertices} and admitting one of the configurations described in Lemma \ref{lem good p}, with propagators $p = (n-3, n-1)$ and $q= (n-5, n-3)$ (if $q$ exists) both of length 2.
 See Figure~\ref{fig special p} for an illustration of the two possibilities.
 
-The next few lemmas describe how diagrams of this type are related to the corresponding diagram with propagator $p$ removed, first in terms of the Grassmann necklaces (Lemma \ref{lem I}) and then in terms of the Le diagrams (Lemmas \ref{lem shape} to Lemma \ref{lem other k}) .
-These technical lemmas will form the backbone of the inductive step in the main dimensionality argument.
+The next few lemmas describe how the Grassmann necklaces (Lemma \ref{lem I}) and the Le diagrams (Lemmas \ref{lem shape} to Lemma \ref{lem other k}) of Wilson loop diagrams of this type are related to the corresponding Wilson loop diagram with propagator $p$ removed.
+\sanote{rephrased, still clear?}
 
 \begin{lem}\label{lem I}
-Let $W$ be an admissible Wilson loop diagram with $n\geq 1$ propagators, and suppose that $W$ admits one of the configurations described in Lemma~\ref{lem good p}, with $p$ and $q$ (if $q$ exists) both of length 2.
+Let $W$ be an admissible Wilson loop diagram with \hlfix{$k\geq 1$}{Here, as above, can we just say 'with more than one propagator?} propagators, and suppose that $W$ admits one of the configurations described in Lemma~\ref{lem good p}, with $p$ and $q$ (if $q$ exists) both of length 2.
 Let $V$ be $W$ with $p$ removed.
@@
 
+\sanote{Add exposition in this section and in intro about how this allows one to talk about what happens to a postriod cell as one adds a propagator.
+These results aren't enough, but a starting point, and certainly not done in this paper}
+
 \begin{proof}

### 2019-08-30 GWLDCII.tex
Through section 4

@@
 
-\begin{lem}\label{lem sian}
+\begin{lem}\label{lem sian} \sanote{should this be rephrased more similarly to the philosophy of Lemma 4.4, allowing non-supporting vertices to be added in or taken out?}
   Let $W$ be a weakly admissible WLD with at least 5 vertices and in which each vertex supports at least one propagator.  Then at least one of the following two things occurs.
@@
 \begin{rmk} \label{clockwise ordering rem}
-When $p$ contributes $I_i(p) = a$, it must be the clockwise-most propagator amongst those not yet assigned that is supported on $a$ i.e.
-any propagator assigned later that is supported on $a$ must be inside $(p, <_{a-1})$.
+When $p$ contributes $I_i(p) = a$, it must be the clockwise-most propagator supported on $a$ that has not yet contributed to $I_i$.
+i.e.
+any propagator supported on $a$ that appears later in the ordering given by $I_i$ must be inside $(p, <_{a})$.
 \end{rmk}
@@
 
- \note{Remember to keep an eye out when proofreading: do we just need the vertices appearing in the GN element to be the same, or do we actually need the functions to match up}
+ \note{Remember to keep an eye out when proofreading: do we just need the vertices appearing in the GN element to be the same, or do we actually need the functions to match up} \sanote{need functions to match in 4.4}
 
@@
 \end{lem}
-
+\sanote{is there a way to express the cyclic intervals more easily than the cases in this proof?}
 \begin{proof}
@@
 We should state it prominently and move on.} so if $r \neq p$, then $I_w^W(r) = I_w^V(r)$.
-Meanwhile, the value of $I^{W}_w(p)$ depends on which step in the algorithm the propagator $q$ \hlfix{is assigned to}{was this the one place where we has agreed to keep assigned instead of contributes?} a vertex {\color{violet} in the diagram $V$}, i.e.
+Meanwhile, the value of $I^{W}_w(p)$ depends on which step in the algorithm the propagator $q$ \hlfix{is assigned to}{did the change from assign to contribute never happen?} a vertex {\color{violet} in the diagram $V$}, i.e.
 on the value of $I^{V}_w(q)$.
@@
 \begin{lem}\label{lem good p}
-  Let $W$ be an admissible Wilson loop diagram with \hlfix{$n\geq 1$}{$k \geq 1$?
-$n$ is the number of vertices?} propagators.
+  Let $W$ be an admissible Wilson loop diagram with $k \geq 1$ propagators.
 Then there is some dihedral transformation of $W$ such that the resulting diagram $W'$ has a propagator $p$ with the following properties:
@@
 \begin{lem}\label{lem I}
-Let $W$ be an admissible Wilson loop diagram with \hlfix{$k\geq 1$}{Here, as above, can we just say 'with more than one propagator?} propagators, and suppose that $W$ admits one of the configurations described in Lemma~\ref{lem good p}, with $p$ and $q$ (if $q$ exists) both of length 2.
+Let $W$ be an admissible Wilson loop diagram with $k\geq 1$ propagators, and suppose that $W$ admits one of the configurations described in Lemma~\ref{lem good p}, with $p$ and $q$ (if $q$ exists) both of length 2.
 Let $V$ be $W$ with $p$ removed.
@@
     \begin{cases}
-      I_{n-2}^{V}\cup \{n-2\} & \text{if $n-2\not\in I_{n-2}^{V}$} \\
+      I_{n-2}^{V}\cup \{n-2\} & \text{if $n-2\not\in I_{n-2}^{V}$ (Case 1)} \\
       I_{n-2}^{V}\cup \{n-1\} & \text{if $n-2\in I_{n-2}^{V}$, $n-1\not\in I_{n-2}^{V}$} \\
@@
     \begin{cases}
-      I_k^{V}\cup \{n-3\} & \qquad \qquad \qquad \qquad \text{if $n-3 \not\in I_k^{V}$}\\
-      I_k^{V}\cup\{n-2\} & \qquad \qquad \qquad \qquad \text{if $n-3\in I_k^{V}$}
+      I_k^{V}\cup \{n-3\} & \qquad \qquad \qquad \qquad \text{if $n-3 \not\in I_k^{V}$ (Case 1)}\\
+      I_k^{V}\cup\{n-2\} & \qquad \qquad \qquad \qquad \text{if $n-3\in I_k^{V}$ (Case 2)}
     \end{cases} \\
@@
 
-\begin{proof}
 The two possible cases for $W$ are illustrated in Figure~\ref{fig special p}.
-
-We first consider $I_1^{W}$, i.e.
-the set obtained by applying the Grassmann necklace algorithm to $W$ with starting vertex 1\note{I don't find this i.e.
-helpful at this point, is it an old thing that can go or do others find it useful?}.
-Note that $n-3 \not\in I_1^{V}$: for Case 2 this is clear from the diagram (since Algorithm~\ref{alg:put GN on WLD} would assign $q$ no later than vertex $n-4$), while for Case 1 it follows from Lemma \ref{lem no fourth vertex}.
-Therefore when we start at vertex 1 and apply the Grassmann necklace algorithm to $W$, $p$ is the only remaining unassigned propagator when we reach vertex $n-3$, and so we have $ I_1^{W}(p) = n-3$ and $I_1^W = I_1^V\cup \{n-3\}$.
-
-Next consider $I_n^{W}$.
-From the figure we see that in both cases we have $I_n^{W}(p) = n$.
-At vertex 1 of the algorithm $I_n$, the unassigned propagators are exactly those that appear in $V$.
-Therefore the algorithm continues as in $I_1^{V}$ (recall Remark~\ref{rmk algorithm locally same} about locally identical propagator configurations), i.e.
-we have $I_n^{W} = I_1^{V} \cup \{n\}$.
-By a similar argument, we must have $I_{n-1}^{W} = I_n^{V} \cup \{n-1\}$.
-
-Now consider $I_{n-2}^{W}$.
-If $n-2\not\in I_{n-2}^{V}$ (i.e.
-the vertex $n-2$ supports no propagators in $V$), then ${I_{n-2}^W(p) = n-2}$ and this assignment of $p$ does not affect the rest of the construction of $I_{n-2}^{V}$, so we obtain ${I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-2\}}$ as above.
-
-On the other hand, if $n-2\in I_{n-2}^{V}$ then we must be in Case 2 of Figure~\ref{fig special p} and $I_{n-2}^V(q) = I_{n-2}^W(q) = n-2$ (since $q$ is always the clockwise-most propagator supported on vertex $n-2$; see Figure~\ref{fig special p}).
-If $n-1 \not\in I_{n-2}^{V}$, then $I_{n-2}^W(p) = n-1$ and then the algorithm proceeds identically to $I_{n-2}^{V}$ for the remainder of its steps; thus $I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-1\}$ in this case.
-
-Finally, if $n-2,n-1 \in I_{n-2}^{V}$ then $I_{n-2}^W(q) = n-2$ and $I_{n-2}^W(p) = n-1$ as above, but this is different to what occured in $I_{n-2}^{V}$ so we cannot use the same argument as above.
-When the algorithm $I_{n-2}^W$ reaches vertex $n$, only the propagators $p$ and $q$ have contributed; thus we proceed as in the construction of $I_n^{V}$ but without propagator $q$.
-By Lemma~\ref{vertex cyclic int lem} we know that $I_n^V(q) = n-5$, and from the diagram we see that the only way this could occur is if all other propagators in $V$ had already been assigned when we reached vertex $n-5$; thus $q$ was the final propagator to be assigned in $I_n^{V}$.
-Therefore $I_{n-2}^{W} = (I_{n}^{V} \setminus \{n-5\}) \cup \{n-1, n-2\}$ in this case.
-This completes all cases for $I_{n-2}^{W}$.
-
-The arguments for $I_k^{W}$ ($1< k < n-2$) proceed analagously to those of $I_{n-2}^{W}$, with one simplification: we cannot have both $n-3$ and $n-2$ in $I_k^{V}$ since $q$ is the only propagator that could be assigned to either of them, and it cannot be assigned to both.
-
-This covers all cases and hence completes the proof.
-\end{proof}
 
@@
   \caption{The two cases for $W$ and $p$.  No other propagators can end in the red sections.  Other segments may have additional propagators ending in them.}\label{fig special p}
-\end{figure}
+
+\end{figure} \sanote{moved figure before theorem 4.4 so that we can just refer to generically}
+\begin{proof}
+
+We first consider $I_1^{W}$, i.e.
+the set obtained by applying the Grassmann necklace algorithm to $W$ with starting vertex 1\note{I don't find this i.e.
+helpful at this point, is it an old thing that can go or do others find it useful?} \sanote{agreed, i vote to cut}.
+Note that $n-3 \not\in I_1^{V}$: \hlfix{for Case 2 this is clear from the diagram (since Algorithm {\ref{alg:put GN on WLD}} would force $q$ to contribute no later than vertex $n-4$),}{why?
+isn't obvious to me without several cases, and even then} while for Case 1 it follows directly from Lemma \ref{lem no fourth vertex}.
+Therefore when we start at vertex 1 and apply the Grassmann necklace algorithm to $W$, $p$ is the \st{only remaining unassigned propagator when we reach vertex $n-3$}{\color{violet}last propagator to contribute}, and so we have $ I_1^{W}(p) = n-3$ and $I_1^W = I_1^V\cup \{n-3\}$.
+
+Next consider $I_n^{W}$.
+From the figure we see that in both cases we have $I_n^{W}(p) = n$.
+\hlfix{Therefore, the second through $k^{th}$ propagators contributing to $I_n^W$ are the same as the ordering in $I_n^V$.
+Since $n$ is non-supporting in $V$, $I_1^V = I_n^V$, we have $I_n^{W} = I_1^{V} \cup \{n\}$}{Alt.
+argument.
+Can ignore.} At vertex 1 of the algorithm $I_n$, the unassigned propagators are exactly those that appear in $V$.
+Therefore the algorithm continues as in $I_1^{V}$ (recall Remark~\ref{rmk algorithm locally same} about locally identical propagator configurations), i.e.
+we have $I_n^{W} = I_1^{V} \cup \{n\}$.
+By a similar argument, we must have $I_{n-1}^{W} = I_n^{V} \cup \{n-1\}$.
+
+Now consider $I_{n-2}^{W}$.
+If $n-2\not\in I_{n-2}^{V}$ \hlfix{by Corrollary {\ref{no coloops}}  $n-2$ is non-supporting in $V$.
+Thus we are in Case 1, with ${I_{n-2}^W(p) = n-2}$.
+By the arguments above ${I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-2\}}$}{Alt.
+Argument.
+Can ignore} (i.e.
+the vertex $n-2$ supports no propagators in $V$), then ${I_{n-2}^W(p) = n-2}$ and this assignment of $p$ does not affect the rest of the construction of $I_{n-2}^{V}$, so we obtain ${I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-2\}}$ as above.
+
+On the other hand, if $n-2\in I_{n-2}^{V}$ then we must be in Case 2 of Figure~\ref{fig special p} and $I_{n-2}^V(q) = I_{n-2}^W(q) = n-2$ \st{(since $q$ is always the clockwise-most propagator supported on vertex $n-2$; see Figure {\ref{fig special p}})}.
+If $n-1 \not\in I_{n-2}^{V}$, then $I_{n-2}^W(p) = n-1$ and then the algorithm proceeds identically to $I_{n-2}^{V}$ for the remainder of its steps; thus $I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-1\}$ in this case.
+
+Finally, if $n-2,n-1 \in I_{n-2}^{V}$ then $I_{n-2}^W(q) = n-2$ and $I_{n-2}^W(p) = n-1$ as above, but \st{this is different to what occured in $I_{n-2}^{V}$}{\color{violet}but some other propagator must contribute $n-1$ to $I_{n-2}^{V}$} so we cannot use the same argument as above.
+When the algorithm $I_{n-2}^W$ reaches vertex $n$, only the propagators $p$ and $q$ have contributed; thus we proceed as in the construction of $I_n^{V}$ but without propagator $q$ by Remark \ref{rmk algorithm locally same}.
+By Lemma~\ref{vertex cyclic int lem} we know that $I_n^V(q) = n-5$ \sanote{it would be nice if this were easier to read from lemma without digging through proof}, and from \st{the diagram }{\color{violet} Remark \ref{clockwise ordering rem} } we see that the only way this could occur is if $q$ was the last to contribute to $I_{n-2}^V$.
+%all other propagators in $V$ had already been assigned when we reached vertex $n-5$; thus $q$ was the final propagator contributing to $I_n^{V}$.
+Therefore $I_{n-2}^{W} = (I_{n}^{V} \setminus \{n-5\}) \cup \{n-1, n-2\}$ in this case. This completes all cases for $I_{n-2}^{W}$.
+
+The arguments for $I_k^{W}$ ($1< k < n-2$) proceed analagously to those of $I_{n-2}^{W}$, with one simplification: we cannot have both $n-3$ and $n-2$ in $I_k^{V}$ since $q$ is the only propagator that could be assigned to either of them, and it cannot be assigned to both.
+
+This covers all cases and hence completes the proof.
+\end{proof}
 
@@
 Recall that $I_1$ determines the shape of the Le diagram: specifically, the elements of $I_1$ label the rows of the diagram, working from top right to bottom left.
-By the arguments in Lemma~\ref{lem I} we know that ${n,n-1,n-2, n-3 \not\in I_1^{V}}$ (which yields the leftmost four columns of the diagram for $V$) and that $I_1^{W} = I_1^{V}\cup \{n-3\}$.
-This implies that the right hand boundary of the shape of $V$ is the same as the right hand boundary of the shape of $W$ except that $W$ has one additional row of 3 boxes while $V$ has an additional column in the $n-3$ position; that is, an extra column fourth from the left.
+By the arguments in Lemma {\ref{lem I}} we know that \st{${n,n-1,n-2, n-3 \not\in I_1^{V}}$}\sanote{Only see $n-3$ in Lemma 4.4?} {\color{violet} $ n-3 \not\in I_1^{V}$.
+By Lemma \ref{lem no fourth vertex}, $n, n-2 \not \in I_1^V$.
+Since $n-1$ is non-supporting in $V$, by Corrollary {\ref{no coloops}}, $n \not\in I_1^{V}$.} These are the leftmost four columns of the diagram for $V$.
+From Lemma \ref{lem I} we know that that $I_1^{W} = I_1^{V}\cup \{n-3\}$.
+Therefore, the right hand boundary of the shape of $V$ is the same as the right hand boundary of the shape of $W$ except that $W$ has one additional row of 3 boxes while $V$ has an additional column in the $n-3$ position; that is, an extra column fourth from the left.
 \end{proof}
@@
 As illustrated in Figure~\ref{fig Le}, the pieces of the Le diagrams of $V$ and $W$ will be called $\mathcal{A}$ and $\mathcal{B}$ in what follows.
-\hlfix{Explicitly, $\mathcal{B}$ is the set of columns with labels $v < n-3$ and $\mathcal{A}$ is the set of columns labeled by $n$, $n-1$ and $n-2$ in $V$.
-In $W$, $\mathcal{A}$ consists of these columns without the last row.}{is this accurate?}\note{I think it is accurate} Over the course of the next few lemmas we will prove that the plusses in the $\mathcal{B}$ parts of each diagram are identical, and that the relationship between the plusses in the $\mathcal{A}$ regions can be described explicitly.
+Explicitly, $\mathcal{B}$ is the set of columns with labels $v < n-3$ and $\mathcal{A}$ is the set of columns labeled by $n$, $n-1$ and $n-2$ in $V$.
+In $W$, $\mathcal{A}$ consists of these columns without the last row.
+Over the course of the next few lemmas we will prove that the plusses in the $\mathcal{B}$ parts of each diagram are identical, and that the relationship between the plusses in the two $\mathcal{A}$ regions can be described explicitly.
 
@@
 Let $V$ and $W$ be as in Lemma~\ref{lem I}.
-Then $I_n^{W}$ and $I_{n-1}^{W}$ together yield the same plusses as $I_n^{V}$ did, along with two extra plusses which appear in the leftmost two boxes of the bottom row of the Le diagram of $W$.
+Then \hlfix{$I_n^{W}$}{Does $I_n^W$ actually yeild any of the $+$s in $I_n^V$?} and $I_{n-1}^{W}$ together yield the same plusses as $I_n^{V}$ did, along with two extra plusses which appear in the leftmost two boxes of the bottom row of the Le diagram of $W$.
 \end{lem}
@@
 Also by Lemma~\ref{lem I} we have $I_{n-1}^{W} = I_n^{V} \cup \{n-1\}$.
-Recall from the proof of Lemma~\ref{lem I} that $n-3,n-2,n-1,n \not\in I_1^V$; therefore $I_1^W\setminus I_{n-1}^W = (I_1^V \setminus I_n^V) \cup\{n-3\}$, and $n-3$ is maximal in this set.
+Recall from the proof of Lemma \st{{\ref{lem I}}} {\color{violet} {\ref{lem shape}} }\sanote{change back if actually in 4.4} that $n-3,n-2,n-1,n \not\in I_1^V$; therefore $I_1^W\setminus I_{n-1}^W = (I_1^V \setminus I_n^V) \cup\{n-3\}$, and $n-3$ is maximal in this set.
 Similarly,
 \[I_{n-1}^W \setminus I_1^W = (I_n^V \setminus I_1^V) \cup \{n-1\} \subseteq \{n-1,n\},\]
-where the final inclusion follows from the definition of Grassmann necklace.
+where the final inclusion follows from the definition of Grassmann necklace\sanote{why only $\{n-1,n\}$?
+I'd believe an inclusion the other way}.
 In particular, $n-1$ is minimal in this set, so Algorithm~\ref{alg:GN to Le} yields a plus in the $(n-3) \rightarrow (n-1)$ position (i.e.
-the second box in the bottom row of the Le diagram of $W$) along with any plusses yielded by $I_n^V$.
+the second box in the bottom row of the Le diagram of $W$) \hlfix{along with any plusses yielded by $I_n^V$.}{display seems to imply that there is exactly one such other $+$.
+Is this correct?}
 \end{proof}
@@
 Note that $n-3\not\in I_{n-2}^{V}$ by Lemma~\ref{lem no fourth vertex}.
-Therefore the paths controlling the plusses contributed by $I_{n-2}^{W}$ are exactly the paths for $I_{n-1}^{V}$ along with the $(n-3)\rightarrow (n-2)$ path.
+Therefore the \st{paths controlling the} plusses contributed by $I_{n-2}^{W}$ are exactly the \st{paths for}{\color{violet} plusses from}\sanote{isn't this from Alg.\ref{alg:GN to Le} which says nothing about paths?}  $I_{n-1}^{V}$ along with the $(n-3)\rightarrow (n-2)$ path.
 This gives the statement of the lemma.
@@
   By Lemma~\ref{lem I} we have $I_{n-2}^{W}= (I_{n}^{V} \setminus \{n-5\})\cup \{n-1,n-2\}$ and $I_1^W = I_1^V\cup \{n-3\}$.
-We are necessarily in the case where $W$ admits a propagator $q$ (Case 2 of Figure~\ref{fig special p}) and we can see from the location of $q$ that $n-2\not\in I_{n-3}^{V}$ and that $n-5$ is the label of the last row in $\mathcal{B}$.
-Also note that by Lemma~\ref{vertex cyclic int lem} and Corollary~\ref{no coloops} we must have $n\in I_n^V$.
-Thus this section of the Grassmann necklace of $V$ looks like
+Furthermore, we are necessarily case 2 of Figure~\ref{fig special p}, with a further propagator $r$ ending on the edge $n-1$, satisfying $I_{n-2}^V(r) = n-1$ (that is, $r$ is the clockwise most on this edge).
+\st{We can see from the location of $q$ that $n-2\not\in I_{n-3}^{V}$} and that $n-5$ is the label of the last row in $\mathcal{B}$.\sanote{is there an easy way to see these?
+Why can't $I_1^V(q) = n-4$, which would make this the last row of $\mathcal{B}$} {\color{violet}From the figure we see that $I_{n-3}^V = n-3$.
+In particular, this means that $n-2 \not \in I_{n-3}^V$.
+} \st{Also note that by Lemma {\ref{vertex cyclic int lem}} and Corollary {\ref{no coloops}} we must have } {\color{violet} Since $r$ is the clockwise most propagator on edge $n-1$, $I_n^V(q) = n$, i.e.} $n\in I_n^V$.Thus this section of the Grassmann necklace of $V$ looks like
 
@@
 The dashed blue lines may or may not appear, but if one appears then they both do.}\label{fig messy}
-  \end{figure}
+  \end{figure} \sanote{can we put the diagrams labels in bold or set them apart somehow so that it is easier to see? Esp since they are located in a different part of the diagram for $I_n^V$?}
 
@@
 On the other hand we have $n-5 \in I_1^{V} \setminus I_{n-2}^V$, along with at least one and at most two other elements.
-If there is one such element, call it $a$.
-If there are two, call them $a$ and $b$ with $a>b$.
+Call the larger (possibly only) of these other elements $a$ with $n-5 > a$.
+If there are two such elements, call the smaller $b$ such that $n-5>a>b$.
 
   This means that the plusses in the Le diagram of $V$ coming from $I_{n-2}^{V}$ are as in the top left diagram in Figure~\ref{fig messy}.
-Stepping to $I_{n-1}^{V}$ simply removes the $(n-5)\rightarrow (n-2)$ path (top right diagram of Figure~\ref{fig messy}), so $I_{n-1}^V$ contributes no new information about the Le diagram of $V$.
+Stepping to $I_{n-1}^{V}$ in display \eqref{eq necklace} simply removes the $(n-5)\rightarrow (n-2)$ path (top right diagram of Figure~\ref{fig messy}), so $I_{n-1}^V$ contributes no new information about the Le diagram of $V$.
 
@@
 
-  Recall that $n-5$ is the largest row index in the Le diagram of $V$, and $n-5 \in I_1^V \setminus I_{n-4}^V$ so $I_{n-4}^V$ must contribute a path starting at $n-5$.
+\hlfix{Recall that $n-5$ is the largest row index}{why not $n-4$?
+(also asked above)} in the Le diagram of $V$, and $n-5 \in I_1^V \setminus I_{n-4}^V$ so $I_{n-4}^V$ must contribute a path starting at $n-5$.
 Since $n-4 \in I_{n-4}^V$ by the location of the propagator $q$, we must also have a path ending at $n-4$.
@@
 \end{proof}
+\sanote{may want a chance to reread this lemma after questions have been answered}
 
@@
 \begin{thm}\label{thm dim}
-  The number of plusses in the Le diagram of an admissible Wilson loop diagram is three times the number of propagators.
+Let $W = (\cP, [n])$ be an admissible Wilson loop diagram.  The number of plusses in the Le diagram of of $W$ is three times the number of propagators.
 \end{thm}
@@
 
-  First note that a Wilson loop diagram $W$ with one propagator supported on vertices $i<j<k<\ell$ has Le diagram a single row with $|W|-i$ boxes.
-Labelling the columns from left to right by $|W|, \ldots, |W|-i+1$, by Algorithm~\ref{alg:GN to Le} there are plusses in the $j$, $k$, and $\ell$ positions.
+  First note that a Wilson loop diagram $W$ with one propagator supported on vertices $i<i+1<j<j+1$ has a Le diagram consisting of a single row with $n-i$ boxes.
+The columns are labeled from left to right by $n, \ldots, i+1$.
+By Algorithm~\ref{alg:GN to Le} there are plusses in the $i+1$, $j$, and $j_1$ positions.
+\sanote{changed for grammar and notational consistency.
+check}
 
@@
 By Lemma~\ref{lem dihedral} it suffices to prove the result for at least one Wilson loop diagram from each dihedral orbit.
-Take a weakly admissible Wilson loop diagram $W$ with $k$ propagators and no non-supporting vertices.
-Make a dihedral transformation of $W$ if necessary so that $W$ has a propagator $p$ with the properties in Lemma~\ref{lem good p}.
-
-  We make one further simplification: if our $W$ is in Case 2 of Figure~\ref{fig special p} and $n-1$ supports only $p$ but $n-2$ supports at least one other propagator, then flip $W$ on the line perpendicular to the $(n-2){th}$ edge to obtain a diagram with the configuration of Case 1.
+In particular, consider $W$, which after possible dihedral transformation, has a propagator $p$ with the properties in Lemma~\ref{lem good p}.
+
+  We make one further simplification: if our $W$ is in Case 2 of Figure~\ref{fig special p} and $n-1$ supports only $p$ but $n-2$ supports at least one other propagator\sanote{??
+see para below}, then flip $W$ on the line perpendicular to the $(n-2){th}$ edge to obtain a diagram with the configuration of Case 1.
 This eliminates the possibility that we could have $n-2 \in I_{n-2}^W$ but $n-1 \not\in I_{n-2}^W$.
 
+{\color{violet} I'm very confused about the previous paragraph.
+I thought that by constuction, in case 2, there can be exactly 2 propagators ending on edge $n-3$, $p$ and $q$.
+I also thought the distinguising feature between the two subcases of Figure 10 case 2 in Lemma 4.4 $I_{n-2}^W$ was the presence or absense of a propagator $r$ ending on edge $n-1$.
+If $r$ exists, $n-1 \in I_{n-2}^V$ and if  $r$ doesn't exist, $n-1 \not \in I_{n-2}^V$.}
+
   This diagram will be our $W$ for the remainder of the proof. Let $V$ be $W$ with $p$ removed.
 
-  From Lemma~\ref{lem shape} we know how the shapes of the Le diagrams of $V$ and $W$ are related; let $\mathcal{A}$ and $\mathcal{B}$ be as described in that lemma and subsequent discussion.
+  From Lemma~\ref{lem shape} we know how the shapes of the Le diagrams of $V$ and $W$ are related; let $\mathcal{A}$ and $\mathcal{B}$ be as described in that lLmma and subsequent discussion.
 Lemmas~\ref{lem n and n-1}, \ref{lem n-2 good}, and \ref{lem n-2 bad} tell us that the three boxes of the bottom row of the Le diagram of $W$ each have a plus.
@@
 
-\section{Poles of Wilson Loop Integrals}\label{sec poles}
+\section{Poles of Wilson Loop Integrals}\label{sec poles} \sanote{start here}
 

### 2019-09-03 GWLDCII.tex
read to end. added too .bib fil

@@
 If we need to impose a direction on a propagator $p = (i,j)$, for example in order to consider the region ``inside'' or ``outside'' of $p$, we write $(p,<_i)$ to indicate that $p$ is directed from edge $i$ to edge $j$, and $(p,<_j)$ for the opposite direction.
-{\color{violet} Note to consider while reading: Might it be notationally easier and/or clearer to talk about ordering the propagators as clockwise or counter clockwise?
-If so, are the benefits of this new notation worth the rewriting?}
 
@@
 
-\section{Poles of Wilson Loop Integrals}\label{sec poles} \sanote{start here}
+\section{Poles of Wilson Loop Integrals}\label{sec poles}
 
 In this section, we investigate the poles of the integrand for $I(W)$, that is $R(W)$ as defined in Definition~\ref{def R(W)}.
-It is conjectured that for a fixed number of propagators and a given set of external twistors $\cZ$, [cite]\note{A cite still waiting} \bas \sum_{W | |\cP| = k} I(W)(\cZ) <\infty \;.\eas In otherwords, all poles of the intergrals must cancel.
-As a step towards this, in this section, we prove some results about $R(W)$.
-
-The results of Section~\ref{sec GN algorithm} allow us to relate the position of propagators in a Wilson loop diagram $W$ to minors of $C(W)$, $R(W)$.
+Since SYM $N=4$ is a finite theory \cite{Alday:2007hr, ParkeTaylorids}, the scattering amplitudes (and thus the holomorphic Wilson loops $\,\mathfrak{W}_{k,n}$) are finite.
+That is, for a fixed set of external particles $\cZ$, \bas \sum_{W \text{ s.t.
+} |\cP| = k} I(W)(\cZ) <\infty \;.\eas In otherwords, all poles of the intergrands must cancel.
+As a step towards this, in this section, we prove some results about the structure of the denominator of the integrand, $R(W)$.
+
+The results of Section~\ref{sec GN algorithm} allow us to relate the \hlfix{position of propagators}{ending edges?} in a Wilson loop diagram $W$ to minors of $C(W)$, $R(W)$.
+\sanote{Do we need to fix an ordering of rows of $C(W)$, or does that come out in the wash?}
 
 The main result of this section is Theorem~\ref{thm denom}, which expresses the denominator $R(W)$ in terms of the Grassmann necklace of $W$.
-This simplifies the computation of $R(W)$ and allows us to directly relate the poles of the integral to the combinatorics of the diagram.
-
-We first give an algorithm which extracts the required minors from the Grassmann necklace.
+\sanote{Put something about this in the motivation for why WLD $\rightarrow$ GN algorithm is useful}This simplifies the computation of $R(W)$ and allows us to directly relate the poles of the integral to the combinatorics of the diagram.
+
+We first give an algorithm which extracts the required minors of $C(W)$ from the Grassmann necklace.
 
 \begin{algorithm}\label{alg WLD to denom via GN}
-Let $W = (\cP,n)$ be a Wilson loop diagram, and let $C(W)$ be the matrix of $W$ as defined in \eqref{C(W) dfn} with a fixed ordering on $\cP$. (see Section~\ref{section WLD background}).
+Let $W = (\cP,[n])$ be a Wilson loop diagram, and let $C(W)$ be the matrix of $W$ as defined in \eqref{C(W) dfn} with a fixed ordering on $\cP$. (see Section~\ref{section WLD background}).
 \begin{itemize}
@@
       \item Let $r_i$ be the determinant of the $|S_i|\times |S_i|$ minor of $C(W)$ with rows indexed by $S_i$ and columns indexed by $I_i(S_i)$.
-%$\Delta_{I_i}$ with all variables from rows associated to $p\not\in S_i$ set to $1$.
+{\color{violet} If $S_i = \emptyset$, set $r_i = 1$}\sanote{a version of this was commented out, put back in}%$\Delta_{I_i}$ with all variables from rows associated to $p\not\in S_i$ set to $1$.
     \end{itemize}
@@
 As we discuss the algorithm it will also be useful to have the notation $\Delta_{I_i}$ for the determinant of the $k\times k$ minor of $C(W)$ with columns indexed by $I_i$.
-
-As we take each $r_i$ to simply be the determinant of a particular submatrix of $C(W)$, the sign of each $r_i$ is well-defined.
+{\color{violet} In particular, one summand of this determinant is given by $\prod_{p \in \cP}x_{p, I_i(p)}$.
+The other summands are (up to sign) given by other bijections between the propagator set $\cP$ and the vertex set $I_i$.}
+
+As we take each $r_i$ to simply be the determinant of a particular submatrix of $C(W)$, the sign of each $r_i$ is well-defined {\color{violet} (after an ordering on the propagators have been fixed)}.
 Before proving the main results of this section, we given an illustrative example.
@@
 \begin{gather*}I_1 = \{1,2,4\}, I_2 = \{2,4,5\}, I_3 = \{4,5,6\}, I_4=\{4,5,6\},\\ I_5=\{5,6,7\}, I_6 = \{6,7,1\}, I_7=\{7,1,2\}. \end{gather*}  
-Figure~\ref{fig R eg} indicates the pairings between propagators and vertices for each $i \in [1,7]$.
+Figure~\ref{fig R eg} indicates \st{the pairings between propagators and vertices for each }{\color{violet} indicates which vertex is contributed to $I_i$ by each propagator for each} $i \in [1,7]$.
 
@@
 \] 
-Continuing likewise, we get $r_3 = c$, $r_4=1$ (since $I_4 = I_3$), $r_5 = lhd$, and $r_6 = i$.
-
-At $I_7$ the situation we see for the first time an irreducible quadratic factor: we have $S_7 = \{q,s\}$ with $I_7(S_7) = \{ 1,2\}$, $\Delta_{I_7} = d(ej-fi)$ and $r_7 = ej-fi$.
+Continuing likewise, we get $r_3 = c$, $r_4=1$ \sanote{see bit added to Alg 5.1 above}(since $I_4 = I_3$), $r_5 = lhd$, and $r_6 = i$.
+
+At $I_7$ we see for the first time an irreducible quadratic factor: we have $S_7 = \{q,s\}$ with $I_7(S_7) = \{ 1,2\}$, $\Delta_{I_7} = d(ej-fi)$ and $r_7 = ej-fi$.
 
@@
 All linear factors of  $\Delta_{I_i}$ are single variables and all irreducible quadratic factors are $2\times 2$ determinants of single variables.
-    \item Quadratic factors in $\Delta_{I_i}$ arise precisely when propagators $p$ and $q$ are supported on a common edge $(a,b)$ with $I_i(p)=a$ and $I_i(q)=b$.
+    \item Quadratic factors in $\Delta_{I_i}$ arise precisely when propagators $p$ and $q$ are supported on a common edge \st{$(a,b)$}{\color{violet}$(a,a+1)$} with $I_i(p)=a$ and \st{$I_i(q)=b$}{\color{violet}$I_i(q)=a+1$}.\sanote{would like to make this change throughout}
     \item $r_i$ divides $\Delta_{I_i}$.
@@
     \item Using the expression for the determinant as a sum over permutations along with Corollary~\ref{lem basis as perm} we see that $\Delta_{I_i}$ is a sum over bijections between $I_i$ and $\mathcal{P}$.
-The nonzero terms in this sum are precisely those bijections such that each propagator is associated to one of its supporting vertices in $I_i$, since only those locations in $C(W)$ are nonzero.
+The nonzero terms in this sum are precisely those bijections such that each propagator is associated to one of its supporting vertices in $I_i$, namely $I_i(p)$, since only those locations in $C(W)$ are nonzero.
 Since the nonzero entries of $C(W)$ are independent there can be no cancellation between terms in this expansion.
@@
 This proves the claim.
+\sanote{I know there was some contention over this paragraph.
+Having read it carefully, I want to iterate that I like this now.}
 
@@
 Suppose for a contradiction that $f$ is a factor of $\Delta_{I_i}$ of degree $\geq 3$.
-Without loss of generality\footnote{This is without loss of generality as by removing the propagators which come before those contributing to $f$ in the order given by the construction of $I_i$ and changing $i$ to be the first vertex which contributes to $f$, we obtain an admissible diagram for which $f$ still divides $\Delta_{I_i}$ but also $i\in I_i$ and
+Without loss of generality\footnote{This is without loss of generality as by removing the propagators which come before those contributing to $f$ in the order given by $I_i$ and changing $i$ to be the first vertex which contributes to $f$, we obtain an admissible diagram for which $f$ still divides $\Delta_{I_i}$ but also $i\in I_i$ and
 $i$ contributes to $f$, and this diagram can be used in place of $W$.} we may assume $i\in I_i$ and $i$ contributes to $f$.
-Finally, we can suppose that $W$ is minimal in number of propagators with an irreducible factor of degree $\geq 3$.
-
-Let $p$ be the propagator such that $I_i(p) = i$. There are two cases to consider, depending on which edge $p$ is supported on.  These are illustrated in Figure~\ref{fig no big factors}
+Finally, we can suppose that $W$ is minimal in number of propagators with an irreducible factor of degree $\geq 3$. \sanote{can we break footnote inot a couple sentences?}
+
+Let $p$ be the propagator such that $I_i(p) = i$. There are two cases to consider, when $p$ is supported on the edge $i-1$ or the edge $i$.  These are illustrated in Figure~\ref{fig no big factors}
 
@@
 \]
-  \caption{The two cases in the proof that no factors of $\Delta_{I_i}$ have degree 3 or more.}\label{fig no big factors}
+  \caption{The two cases in the proof that no factors of $\Delta_{I_i}$ have degree 3 or more.{\color{violet}First picture: I thought $I_i(p) = i$.
+Doesn't the arrow say that $I_i(p) = i-1$?}}\label{fig no big factors}
 \end{figure}
 
-\textbf{Case 1}: Suppose $p$ has one end on the edge $(i-1, i)$.  Thus $p$ is supported on $(i-1, i, m, m+1)$ for some $m >_i i$, and $I_{i+1}(p) = m$ by Lemma~\ref{vertex cyclic int lem}.
+\textbf{Case 1}: Suppose $p = (i-1, m)$.
+Then $p$ has one end on $i-1^{th}$ edge and $I_{i+1}(p) = m$ by Lemma~\ref{vertex cyclic int lem}.
+\sanote{again, it would be nice if this could be read off from a statement of a result somehwere}.
 
 Let $S = \cP_{in}(p)$ be the set of propagators inside $p$ in the $<_i$ order.
-$I_i$ and $I_{i+1}$ can only differ once $p$ contributes to $I_{i+1}$, so $I_i(q) = I_{i+1}(q)$ for each $q \in S \backslash \{p\}$.
+{\color{violet} By Remark \ref{rmk algorithm locally same},} $I_i$ and $I_{i+1}$ can only differ once $p$ contributes to $I_{i+1}$, so $I_i(q) = I_{i+1}(q)$ for each $q \in S \backslash \{p\}$.
 Thus if a propagator contributes $m$ in $I_i$ then it must lie outside $p$.
+
+\hlfix{By Remark {\ref{clockwise ordering rem}}, if $I_i(q) = m$, then it must be the clockwise most propagator supported on $m$ that has not yet contributed to $I_i$, i.e.
+is lies in $\cP_{out}(p, <_i)$.}{more direct than above para.
+Alt.
+only.
+Don't need to adopt.
+(keep dfn of $S$.)}
 
@@
 So we must have at least one of $m$ and $m+1$ in $I_i$.
-However, all propagators in $S$ are mapped by the function $I_{i}(\cdot)$ to vertices strictly before $m$, so the matrix giving $\Delta_{I_i}$ has the form
+However, all propagators in $S$ contribute to $I_{i}$ strictly before $m$ {\color{violet} by Corrollary \ref{GN alg well defined}}, so the matrix giving $\Delta_{I_i}$ {\color{violet} where the rows appear in the order defined by $I_i$?} has the form
 \[
@@
 Therefore $\Delta_{I_i} = \det A \det C$, and both factors are nontrivial since at least one of $m$ and $m+1$ appear in $I_i$.
-Since $p\in \cP_{in}(p)$ we have $f|\det A$ and if we remove the propagator outside of $p$ that contributes $m$ or $m+1$, we get a diagram with fewer propagators for which $\det A | \Delta_{I_i}$, hence $f|\Delta_{I_i}$.
+Since $p\in \cP_{in}(p)$ we have $f|\det A${\color{violet}.
+If we remove the propagators that contribute variables to the minor $C$,}\st{ and if we remove the propagator outside of $p$ that contributes $m$ or $m+1$,} we get a diagram $W'$ with fewer propagators for which $\det A | \Delta_{I^{W'}_i}$ still holds, hence $f|\Delta_{I^{W'}_i}$.
 This contradicts the minimality of our choices.
-
-\textbf{Case 2}: Suppose $p$ has one end on the edge $(i, i+1)$.
-If no other propagators are supported on $i$ then the column of $C(W)$ corresponding to vertex $i$ has only one nonzero entry in it, and so $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$; as above, this is a contradiction.
-Since $I_i(p) = i$ there can be no propagator supported on $i$ with an end on the edge $(i-1, i)$.
+\sanote{trying to make clear that the minor changes with the diagram.
+May have just made it too notation heavy.}
+
+\textbf{Case 2}: Suppose $p = (i, m)$, i.e.
+has an end on the $i^{th}$ edge.
+If no other propagators are supported on the vertex $i$ then the corresponding column of $C(W)$ has only one nonzero entry in it, and so $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$; as above, this is a contradiction.
+\st{Since $I_i(p) = i$ there can be no propagator supported on $i$ with an end on the edge $(i-1, i)$.
 Thus to have another propagator supported on $i$ there is at least one other propagator on edge $(i,i+1)$.
 Further since since $I_i(p)=i$, one of these other propagators contributes $i+1$ in $I_i$, so we can take $q$ to be the propagator such that $I_i(q)=i+1$.
-We know that $q$ has one end on the edge $(i, i+1)$ and is adjacent to $p$ on that edge in the counterclockwise direction (see Figure \ref{fig no big factors}).
-Write $(i, i+1, j, j+1)$ for the support of $q$.
-The situation for $q$ is very similar to case 1: in particular, we have $I_{i+1}(q) = j$ by Lemma~\ref{vertex cyclic int lem} and so if $j\in I_i$ then the propagator which contributes $j$ is outside of $q$.
+We know that $q$ has one end on the edge $(i, i+1)$ and is adjacent to $p$ on that edge in the counterclockwise direction (see Figure {\ref{fig no big factors}}).}  \hlfix{Since $p$ is the first propagator in the ordering imposed by $I_i$, it is the counterclockwise most propagator supported on $i$ (by Remark {\ref{clockwise ordering rem}}).
+Since there are multiple propagators supported on $i$, there must be a $q$ ending on edge $i$, such that $I_i(q) = i+1$, that is second clockwisemost propagators supported by $i$.}{Alt.
+proof} Write $q = (i, j)$ for the support of $q$.
+The situation for $q$ is very similar to case 1: \st{in particular, we have $I_{i+1}(q) = j$ by Lemma {\ref{vertex cyclic int lem}} and so if $j\in I_i$ then the propagator which contributes $j$ is outside of $q$.}{\color{violet}if we have $r$ such that $I_i(r) = j$, as above, $r$ lies outside $q$: $r \in \cP_{out}(q, <_i)$.
+}
 
 Similarly to Case 1, let $S = \cP_{in}(q) \cup \{p\}$ in the $<_i$ order.
-Then all propagators in $S$ are mapped by $I_i(\cdot)$ to vertices strictly before $j$ and no other propagators are supported on vertices strictly before $j$.
-Thus the matrix giving $\Delta_{I_i}$ has the form
+Then all propagators in $S$ contribute to $I_i$ strictly before $j$ and no other propagators are supported on vertices strictly before $j$.
+Thus the matrix giving $\Delta_{I_i}$ has the form {\color{violet}(when reordered according to how they contribute to $I_i$)}
 \[
@@
 If some vertex $j$ or larger (with respect to $>_i$) belongs to $I_i$ then $B$ and $C$ are at least one column wide, and so the block form of the matrix gives a nontrivial factorization of $\Delta_{I_i}=\det A\det B$.
-This yields a contradiction as in Case 1: $f|\det A$ and removing a propagator not in $S$ gives a smaller diagram with a factor of degree $\geq 3$ which contradicts our minimality assumption.\note{I rephrased this last sentence quite a bit because earlier things had gotten rephrased}
+This yields a contradiction as in Case 1: $f|\det A$ and removing a propagator not in $S$ gives a smaller diagram with a factor of degree $\geq 3$ which contradicts our minimality assumption.\note{I rephrased this last sentence quite a bit because earlier things had gotten rephrased} \sanote{reads fine to me.}
 
 On the other hand, if no vertex $\geq_i j$ is in $I_i$ then $\Delta_{I_i} = \det A$.
-Looking in more detail into $A$, note that the only vertices in the support of $p$ and $q$ which belong to $I_i$ are $i$ and $i+1$, and hence
+Looking in more detail into $A$, note that the only vertices supporting both $p$ and $q$ which belong to $I_i$ are $i$ and $i+1$.
+Hence
 \[
@@
 
-\item Suppose propagators $p$ and $q$ are supported on a common edge $(a,b)$, with $I_i(p)=a$ and $I_i(q)=b$.
-Let $x_{p,a},x_{p,b},x_{q,a},x_{q,b}$ be the associated variables in $C(W)$.
-For any fixed bijection $\sigma$ from $\cP-\{p,q\}$ to $I_i -\{a,b\}$ for which each propagator is supported on its image under the bijection, we can extend $\sigma$ to a bijection of all propagators with $I_i$ in two ways: either $p\mapsto a$ and $q\mapsto b$ or $p\mapsto b$ and $q\mapsto a$.
-The sum of the contributions of all these bijections to $\Delta_{I_i}$ is therefore the product of $x_{p,a}x_{q,b}-x_{p,b}x_{q,a}$ \note{Could this use a ref back to where we discuss this kind of arugment in more detail.} with the minor coming from $\cP-\{p, q\}$ and $I_i - \{a,b\}$.
+\item \sanote{changed $b$ to $a+1$ here.} Suppose propagators $p$ and $q$ are supported on a common edge  $(a, a+1)$, with $I_i(p)=a$ and $I_i(q)=a+1$.
+Let $x_{p,a},x_{p,a+1},x_{q,a},x_{q,a+1}$ be the associated variables in $C(W)$.
+For any fixed bijection $\sigma$ from $\cP-\{p,q\}$ to $I_i -\{a,a+1\}$ for which each propagator is supported on its image under the bijection, we can extend $\sigma$ to a bijection from propagators to $I_i$ in two ways: either $p\mapsto a$ and $q\mapsto a+1$ or $p\mapsto a+1$ and $q\mapsto a$.
+The sum of the contributions of all these bijections to $\Delta_{I_i}$ is therefore the product of $x_{p,a}x_{q,a+1}-x_{p,a+1}x_{q,a}$ {\color{violet} By the arguments in the proof of the claim in part 2 of this theorem} \note{Could this use a ref back to where we discuss this kind of arugment in more detail.}\sanote{see violet?} with the minor coming from $\cP-\{p, q\}$ and $I_i - \{a,a+1\}$.
 Since there is no cancellation of terms in the expansion of $\Delta_{I_i}$, if any other terms appear then they will cause a factor which is not in the form described in the previous part.
-Therefore no such terms exist and $x_{p,a}x_{q,b}-x_{p,b}x_{q,a}$ is a factor of $\Delta_{I_i}$.
+Therefore no such terms exist and $x_{p,a}x_{q,a+1}-x_{p,a+1}x_{q,a}$ is a factor of $\Delta_{I_i}$.
 
@@
 By part (2) we know that $f$ is a $2\times 2$ minor coming from two propagators, call them $p$ and $q$, and two vertices, call them $a <_i b$.
-It remains to show that $a$ and $b$ are adjacent.
-From this we can conclude that $p$ and $q$ each have one end on $(a,b)$, as any other way for both $p$ and $q$ to be supported on two consecutive vertices would contradict noncrossing or the density requirement of admissibility.
-
-As in the proof of part (2), make a new admissible diagram by removing the propagators which come before $f$ and set $i=a$.
+It remains to show that \st{$a$ and $b$ are adjacent} {\color{violet}$b = a+1$}.
+From this we can conclude that $p$ and $q$ each have one end on $(a,a+1)$.
+\st{, as any other way for both $p$ and $q$ to be supported on two consecutive vertices would contradict noncrossing or the density requirement of admissibility.}
+
+As in the proof of part (2), make a new admissible diagram by removing the propagators which come before {\color{violet} those contibuting to} $f$ {\color{violet}in the order imposed by $I_i$} and set $i=a$.
 The cases in the proof of part (2) show how $\Delta_{I_i}$ factors: in particular the vertices supporting the other end of $p$ either do not appear in $I_i$, or they contribute to a different factor of $\Delta_{I_i}$ than $p$ and $a$ do.
 By assumption $b$ contributes to the same factor as $a$.
-Therefore $(a,b)$ is an edge.
-
-\item Consider $p\in S_i$, and note that $\Delta_{I_i}$ is homogeneous linear in the variables of the row corresponding to $p$.
+Therefore $(a,b)$ is an edge defining an end of $p$, that is, $b = a+1$.
+
+\item Consider $p\in S_i$ from \ref{alg WLD to denom via GN}, and note that $\Delta_{I_i}$ is homogeneous linear in the variables of the row corresponding to $p$.
 By part (2), either exactly one variable in the row corresponding to $p$ appears in $\Delta_{I_i}$ and this variable is a factor of $\Delta_{I_i}$, or exactly two variables from the row corresponding to $p$ appear in $\Delta_{I_i}$ and they appear as part of a quadratic factor.
 In the first case let the variable be $x$.
-Then $x$ is a factor of $\Delta_{I_i}$ and so in particular the monomial in $\Delta_{I_i}$ corresponding to the bijection between propagators and vertices of $I_i$ associates the column of $x$ to $p$.
-Thus $x$ also appears in $r_i$ and since the matrix for $r_i$ is a minor of the matrix for $\Delta_{I_i}$ and every term in $\Delta_{I_i}$ involves $x$, we also have that every term in $r_i$ involves $x$ so $x$ is a factor of both $r_i$ and $\Delta_{I_i}$ and is the only variable from this row in either polynomial.
+Then $x$ is a factor of $\Delta_{I_i}$.
+{\color{violet} Therefore, $x$ must correspond to entry in the row of $p$ and column of $I_i(p)$, i.e.
+$x = x_{p, I_i(p)}$.} \st{and so in particular the monomial in $\Delta_{I_i}$ corresponding to the bijection between propagators and vertices of $I_i$ associates the column of $x$ to $p$.
+Thus $x$ also appears in $r_i$ and s} Since the matrix for $r_i$ is a minor of the matrix for $\Delta_{I_i}$ \st{and every term in $\Delta_{I_i}$ involves $x$,} we also have that \st{every term in $r_i$ involves $x$ so}{\color{violet}$x$ is a factor of $r_i$.} \st{$x$ is a factor of both $r_i$ and $\Delta_{I_i}$ and is the only variable from this row in either polynomial.}
 
 Now suppose two variables from the row $p$ appear in a quadratic factor $f$ of $\Delta_{I_i}$.
-By part (3), there is another propagator $q$ and an edge $(a,b)$ such that $f$ is the $2\times 2$ minor coming from $p, q$ and $a, b$, with $I_i(p)=a$, $I_i(q)=b$.
-There are two situations which can occur, both illustrated in Figure~\ref{fig quadratic}; we show that in both cases it follows that $q \in S_i$ as well.
+By part (3), there is another propagator $q$ and an edge $(a,a+1)$ such that $f$ is the $2\times 2$ minor coming from $p, q$ and $a, a+1$, with \st{$I_i(p)=a$, $I_i(q)=b$}.
+{\color{violet}There are two situations which can occur, either $I_i(p)=a$ and $I_i(q)=a+1$, or $I_i(q)=a$ and $I_i(p)=a+1$.
+These are} illustrated in Figure~\ref{fig quadratic}; we show that in both cases it follows that $q \in S_i$ as well.
 
@@
 	\newnode[below]{1}{a}
-	\newnode[below]{2}{b}
+	\newnode[below]{2}{a+1}
 	\begin{scope}
@@
 	%\drawnumberspartial % use this to debug
-	\newnode[below]{1}{b}
-	\newnode[below]{2}{a}
+	\newnode[below]{1}{a}
+	\newnode[below]{2}{a+1}
 	\begin{scope}
@@
 \]
-  \caption{The situations giving a quadratic factor with variables appearing in $r_i$.}\label{fig quadratic}
+  \caption{The situations giving a quadratic factor with variables appearing in $r_i$. }\label{fig quadratic}
 \end{figure}
 
-In both cases, since $I_{i-1}(p)\neq a$ by assumption it follows from Lemma~\ref{vertex cyclic int lem} that $I_{i-1}(p) <_{i-1} a$ and no other vertex supporting $p$ lies between $I_{i-1}(p)$ and $a$.
-In the case that $b<_i a$ and $q$ is assigned before $p$ in $I_i$, this means that $I_{i-1}(p)=b$ and so $I_{i-1}(q)\neq b$.
+In both cases, since $I_{i-1}(p)\neq I_{i}(p)$ by assumption it follows from Lemma~\ref{vertex cyclic int lem} that $I_{i-1}(p) <_{i-1} I_{i}(p)$ and no other vertex supporting $p$ lies between $I_{i-1}(p)$ and $I_{i}(p)$.
+\st{In the case that $b<_i a$ and $q$ is assigned before $p$ in $I_i$,}{\color{violet} If $q$ lies clockwise of $p$, $I_i(q) = a$ and $q$ contributes before $p$ in $I_i$.} This means that $I_{i-1}(p)=a$ and so $I_{i-1}(q)\neq a$.
 Thus $q\in S_i$ and so $f$ is a factor of $r_i$.
 
-Now consider the case where $a<_i b$, and suppose for contradiction that $q \not\in S_i$, i.e.
-that $I_{i-1}(q) = b$.
-Since $I_{i-1}(p) \neq a$, there must be some other propagator $s$ with $I_{i-1}(s) = a$ (else $I_{i-1}$ assigns $q$ to $a$).
-This propagator cannot lie on edge $(a,b)$ since, by Lemma~\ref{vertex cyclic int lem}, we must have $I_i(s) \in \{a, b\}$, contradicting the fact that $I_i(p) = a$ and $I_i(q) = b$; thus $s$ has an end on $(a-1,a)$ and is inside $p$ in the $<_k$ order where $p=(k,a)$.
+Now consider the case where \st{$a<_i b$}{\color{violet}$I_i(q) = a+1$}, and suppose for contradiction that $q \not\in S_i$, i.e.
+that $I_{i-1}(q) = a+1$.
+Since $I_{i-1}(p) \neq a$, there must be some other propagator $s$ with $I_{i-1}(s) = a$ (else $q$ contributes $a$ to $I_{i-1}$).
+This propagator cannot lie on edge $(a,a+1)$ since, by Lemma~\ref{vertex cyclic int lem}, \hlfix{we must have $I_i(s) \in \{a, a+1\}$}{is this from examing the cyclic intervals burried in the proof?}, contradicting the fact that $I_i(p) = a$ and $I_i(q) = a+1$; thus $s$ has an end on $(a-1,a)$ and is inside $p$ in the $<_k$ order where $p=(k,a)$.
 
@@
 	\newnode[below]{6}{a}
-	\newnode[below]{7}{b}
+	\newnode[below]{7}{a+1}
 	\begin{scope}
@@
 Since $p$ changed its association from $I_{i-1}$ to $I_i$, we have $I_{i-1}(p) = i-1$ by Lemma~\ref{vertex cyclic int lem}.
-From Figure~\ref{fig part 4} it follows that $I_{i-1}$ assigns $p$ to $i-1$ and then proceeds identically to $I_i$ for all vertices inside $p$, implying that $I_{i-1}(s) = I_i(s)$.
+From Figure~\ref{fig part 4} {\color{violet} and Remark \ref{rmk algorithm locally same}} $p$ contributes first to  $I_{i-1}$ and  then proceeds identically to $I_i$ for all vertices inside $p$ in the $<_{i-1}$ ordering, implying that $I_{i-1}(s) = I_i(s)$.
 Since $I_{i-1}(s) = a$ and $I_i(s) \neq a$, this is a contradiction.
@@
 Now assume $W$ has at least one propagator.
+\sanote{we never say this, but diagrams without propagators aren't really a thing....
+at least they aren't tree level scatterings}
 
@@
 If $f$ is a linear factor, say from associating propagator $p$ to vertex $a$, then $I_{i}(p)=a$ and $I_{i-1}(p)\neq a$ so this factor appears in $r_i$.
-If $f$ is a quadratic factor, say from associating propagators $p$ and $q$ to vertices $a$ and $b$ respectively, then again we cannot have both $I_{i-1}(p) = a$ and $I_{i-1}(q) = b$, else $f$ divides $\Delta_{i-1}$.
+If $f$ is a quadratic factor, \st{say from associating} {\color{violet} without loss of generality, associate} propagators $p$ and $q$ to vertices $a$ and $a+1$ respectively, then again we cannot have both $I_{i-1}(p) = a$ and $I_{i-1}(q) = a+1$, else $f$ divides $\Delta_{i-1}$.
 However, by the proof of part (4), if one of $p,q$ belongs to $S_i$ then the other does as well.
@@
 This contradicts Lemma~\ref{vertex cyclic int lem}.
-Now suppose $f$ is a quadratic factor, say from propagators $p$ and $q$ supported on the edge $(a, b)$ with $p$ before $q$ on the edge.
-In this case it is not possible for any $I_i$ to associate $p$ to $b$ and $q$ to $a$.
-Furthermore, we know by part (4) that $p$ changes from not being associated to $a$ to being associated to $a$ if and only if $q$ changes from not being associated to $b$ to being associated to $b$.
+Now suppose $f$ is a quadratic factor, say from propagators $p$ and $q$ supported on the edge $(a, a+1)$ with $p$ clockwise to $q$ on the edge.
+In this case it is not possible for any $I_i$ to associate $p$ to $a+1$ and $q$ to $a$.
+Furthermore, we know by part (4) that $p$ changes from not being associated to $a$ to being associated to $a$ if and only if $q$ changes from not being associated to $a+1$ to being associated to $a+1$.
 Thus $f^2|R$ implies that twice in the Grassmann necklace $p$ must change from not being associated to vertex $a$ to being associated to vertex $a$.
@@
 \end{proof}
+\sanote{start here}
+
+We are now ready to prove the main theorem of this section.
+We use the facts about $\Delta_{I_i}$ and $R$ above to show that the denominator of the integrand of $I(W)$ is given by Algorithm \ref{alg WLD to denom via GN}.
 
@@
 
-To this end, first note that $R(W)$ and $R$ both have total degree $4|\mathcal{P}|$; the degree of $R(W)$ is immediate from the definition while that of $R$ follows from Lemma~\ref{vertex cyclic int lem}.
+To this end, first note that $R(W)$ and $R$ both have total degree $4|\mathcal{P}|$; the degree of $R(W)$ is immediate from the definition while that of $R$ \hlfix{follows from Lemma {\ref{vertex cyclic int lem}}}{one sentence explanation?}.
 By Proposition~\ref{prop alg gives rad} every factor of $R$ is either a quadratic factor coming from two propagators supported on a common edge or a single variable coming from a support vertex of a propagator not appearing in a quadratic factor.
@@
 
-While the authors cannot yet offer a proof that the appropriate sum of the Wilson loop diagrams are, in fact, finite, as conjectured [cite]\note{One last cite to fill out}, we do hope that this relationship to the Grassmann Necklace elements will provide a different avenue for answering that and related questions.
+While the authors cannot yet offer a proof that the appropriate sum of the Wilson loop diagrams are, in fact, finite, as expected from \cite{Alday:2007hr, ParkeTaylorids}, we do hope that this relationship to the Grassmann Necklace elements will provide a different avenue for answering that and related questions.
 

### 2019-09-05 GWLDCII.tex
extended remark 3.4 in a way that we need it later and removed the comments in the later spot about this

@@
 \item If every vertex in $W$ supports at least one propagator, then $W$ admits at least one propagator of length 2.
+Furthermore, by the same reasoning, if $p=(i,j)$ is a propagator of $W$ and every vertex in $[i,j]$ supports at least one propagator then there is at least one propagator of length $2$ in $\mathcal{P}_{in}(p, <_i)$.
 \end{enumerate}
@@
 
-Let \hlfix{$W_r := (\cP_{in}(q_r),[n])$}{technically has non supporting vertices.
-Want $(\cP_{in}(q_r),[i_r, k_r+1])$.
-However this is clear later.
-Do we care?}\note{No, we don't quite want that either because we don't want the newly shortened $q_r$ to be our propagator of length 2 -- maybe a slight change to the remark} be the subdiagram of $W$ consisting only of those propagators inside $q_r$ (including $q_r$ itself); in particular $W_r$ contains none of the previous $p_i$ or $q_i$.
+Let $W_r := (\cP_{in}(q_r),[n])$ be the subdiagram of $W$ consisting only of those propagators inside $q_r$ (including $q_r$ itself); in particular $W_r$ contains none of the previous $p_i$ or $q_i$.
 By the original hypotheses on $W$, every vertex in $[i_r,k_{r+1}]$ (of which there are at least 4, since $\ell(q_r) \geq 4$) must support at least one propagator.

### 2019-09-05 GWLDCII.tex
added/edited pictures as discussed

--- 2019-09-03 GWLDCII.tex
@@
 
+ % used for showing which propagator assigns to which vertex in the last section
+\pgfmathsetmacro{\arrowangle}{75}
+\tikzstyle{propassignment} = [->,shorten >=2pt,thick]
+
 % to draw a (full) WLD; \drawWLD{8}{2} is a circle of radius 2 with 8 marked points
@@
   \pgfmathsetmacro{\x}{\angle*\i}
-  \draw (\x:\radius*1.15) node {\footnotesize \i};
+  \draw (\x:\radius*1.25) node {\footnotesize \i};
 }
@@
 
+\begin{figure}[h]
+\[
+\begin{tikzpicture}[baseline=(current bounding box.north)]
+  \begin{scope}
+  \drawWLDfragment[7]{3}{0.4} 
+  %\drawnumberspartial % use this to debug
+  \centerarc[linehighlight](0,0)(\zero + 1.43*\step:\zero+6.6*\step:\radius)
+  \newnode{1}{}
+  \newnode{3.55}{}
+  \newnode{4.45}{}
+  \newnode{7}{}
+    \begin{scope}
+    \clipcenterarc(0,0)(\startpoint:\endpoint:\radius)
+  \newpropbend{1.3}{6.7}{20}
+  \newpropbend{2.9}{5.1}{45}
+  \end{scope}
+  \node[align=center] at (\zero + 4*\step:\radius*1.43) {\footnotesize \em $\leq 6$ vertices in the \\ \footnotesize \em highlighted region};
+\end{scope}
+\end{tikzpicture}
+\qquad \qquad \qquad
+\begin{tikzpicture}[baseline=(current bounding box.north)]
+  \begin{scope}
+  \drawWLDfragment[7]{3}{0.4} 
+  %\drawnumberspartial % use this to debug
+  \centerarc[linehighlight](0,0)(\zero + 3.67*\step:\zero+4.43*\step:\radius)
+  \newnode{1}{i}
+  \newnode[below]{2}{i+1\ \ \ }
+  \newnode[below]{3}{i+2}
+  \newnode[below]{5}{j+1}
+  \newnode[below]{6}{\quad j+2}
+  \newnode[right]{7}{j+3}
+      \begin{scope}
+    \clipcenterarc(0,0)(\startpoint:\endpoint:\radius)
+  \newpropbend{1.35}{3.6}{55}
+  \newpropbend{4.4}{6.6}{55}
+  \end{scope}
+  \node[align=center] at (\zero + 4*\step:\radius*1.5) {\footnotesize \em $\leq 2$ vertices in the highlighted \\ \footnotesize \em region, and  no other propagators \\ \em \footnotesize end in the highlighted region};
+\end{scope}
+\end{tikzpicture}
+\]
+\caption{The two configurations described in Lemma~\ref{lem sian}; every weakly admissible Wilson loop diagram with no non-supporting vertices supports at least one example of at least one of these configurations.}\label{fig: small configs}
+\end{figure}
+
 The following lemma establishes certain configurations of propagators that must exist in any admissible diagram with no non-supporting vertices (i.e.
@@
 \begin{lem}\label{lem sian} \sanote{should this be rephrased more similarly to the philosophy of Lemma 4.4, allowing non-supporting vertices to be added in or taken out?}
-  Let $W$ be a weakly admissible WLD with at least 5 vertices and in which each vertex supports at least one propagator.  Then at least one of the following two things occurs.
+  Let $W$ be a weakly admissible WLD with at least 5 vertices and in which each vertex supports at least one propagator.  Then at least one of the following two things occurs:
   \begin{enumerate}
@@
   \end{enumerate}
+See Figure~\ref{fig: small configs} for an illustration of the two configurations.
 \end{lem}
-\note{Should this lemma have pictures}
 
@@
 
-\note{I would like to discuss the angles of the arrows in fig 14}
 \begin{figure}
 \begin{tabular}{rrrrr}
+% \arrowangle is defined globally in the preamble for easy tweaking
 \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
@@
   \pgfmathsetmacro{\move}{\angle/\n};
-	\draw[->,shorten >=2pt,red,thick] (1.5*\angle + -1*\move:\radius) to[bend left = 45] (\angle*1:\radius); %p
-	\draw[->,shorten >=2pt,red,thick] (1.5*\angle:\radius) to[bend right = 45] (\angle*2:\radius); %q
-	\draw[->,shorten >=2pt,red,thick] (4.5*\angle:\radius) to[bend left = 45] (\angle*4:\radius); %r
+  \draw[propassignment,red] (1.5*\angle + -1*\move:\radius) to[bend left = \arrowangle] (\angle*1:\radius); %p
+  \draw[propassignment,red] (1.5*\angle:\radius) to[bend right = \arrowangle] (\angle*2:\radius); %q
+  \draw[propassignment,red] (4.5*\angle:\radius) to[bend left = \arrowangle] (\angle*4:\radius); %r
   \node at (\angle*1.5:\radius*2) {$I_1$};
@@
   \pgfmathsetmacro{\move}{\angle/\n};
-	\draw[->,shorten >=2pt,red,thick] (1.5*\angle + -1*\move:\radius) to[bend right = 45] (\angle*2:\radius); %p
-	\draw[->,shorten >=2pt,red,thick] (5.5*\angle:\radius) to[bend left = 45] (\angle*5:\radius); %q
-	\draw[->,shorten >=2pt,red,thick] (4.5*\angle:\radius) to[bend left = 45] (\angle*4:\radius); %r
+  \draw[propassignment,red] (1.5*\angle + -1*\move:\radius) to[bend right = \arrowangle] (\angle*2:\radius); %p
+  \draw[propassignment,red] (5.5*\angle:\radius) to[bend left = \arrowangle] (\angle*5:\radius); %q
+  \draw[propassignment,red] (4.5*\angle:\radius) to[bend left = \arrowangle] (\angle*4:\radius); %r
   \node at (\angle*1.5:\radius*2) {$I_2$};
@@
   \pgfmathsetmacro{\move}{\angle/\n};
-	\draw[->,shorten >=2pt,red,thick] (6.5*\angle:\radius) to[bend left = 45] (\angle*6:\radius); %p
-	\draw[->,shorten >=2pt,red,thick] (5.5*\angle:\radius) to[bend left = 45] (\angle*5:\radius); %q
-	\draw[->,shorten >=2pt,red,thick] (4.5*\angle:\radius) to[bend left = 45] (\angle*4:\radius); %r
+  \draw[propassignment,red] (6.5*\angle:\radius) to[bend left = \arrowangle] (\angle*6:\radius); %p
+  \draw[propassignment,red] (5.5*\angle:\radius) to[bend left = \arrowangle] (\angle*5:\radius); %q
+  \draw[propassignment,red] (4.5*\angle:\radius) to[bend left = \arrowangle] (\angle*4:\radius); %r
   \node at (\angle*1.5:\radius*2) {$I_3 = I_4$};
@@
   \pgfmathsetmacro{\move}{\angle/\n};
-	\draw[->,shorten >=2pt,red,thick] (6.5*\angle:\radius) to[bend right = 45] (\angle*7:\radius); %p
-	\draw[->,shorten >=2pt,red,thick] (5.5*\angle:\radius) to[bend right = 45] (\angle*6:\radius); %q
-	\draw[->,shorten >=2pt,red,thick] (4.5*\angle:\radius) to[bend right = 45] (\angle*5:\radius); %r
+  \draw[propassignment,red] (6.5*\angle:\radius) to[bend right = \arrowangle] (\angle*7:\radius); %p
+  \draw[propassignment,red] (5.5*\angle:\radius) to[bend right = \arrowangle] (\angle*6:\radius); %q
+  \draw[propassignment,red] (4.5*\angle:\radius) to[bend right = \arrowangle] (\angle*5:\radius); %r
   \node at (\angle*1.5:\radius*2) {$I_5$};
@@
   \pgfmathsetmacro{\move}{\angle/\n};
-	\draw[->,shorten >=2pt,red,thick] (6.5*\angle:\radius) to[bend right = 45] (\angle*7:\radius); %p
-	\draw[->,shorten >=2pt,red,thick] (5.5*\angle:\radius) to[bend right = 45] (\angle*6:\radius); %q
-	\draw[->,shorten >=2pt,red,thick] (1.5*\angle + 1*\move:\radius) to[bend left = 45] (\angle*1:\radius); %r
+  \draw[propassignment,red] (6.5*\angle:\radius) to[bend right = \arrowangle] (\angle*7:\radius); %p
+  \draw[propassignment,red] (5.5*\angle:\radius) to[bend right = \arrowangle] (\angle*6:\radius); %q
+  \draw[propassignment,red] (1.5*\angle + 1*\move:\radius) to[bend left = \arrowangle] (\angle*1:\radius); %r
   \node at (\angle*1.5:\radius*2) {$I_6$};
@@
   \pgfmathsetmacro{\move}{\angle/\n};
-	\draw[->,shorten >=2pt,red,thick] (6.5*\angle:\radius) to[bend right = 45] (\angle*7:\radius); %p
-	\draw[->,shorten >=2pt,red,thick] (1.5*\angle:\radius) to[bend left = 45] (\angle*1:\radius); %q
-	\draw[->,shorten >=2pt,red,thick] (1.5*\angle + \move:\radius) to[bend right = 45] (\angle*2:\radius); %r
+  \draw[propassignment,red] (6.5*\angle:\radius) to[bend right = \arrowangle] (\angle*7:\radius); %p
+  \draw[propassignment,red] (1.5*\angle:\radius) to[bend left = \arrowangle] (\angle*1:\radius); %q
+  \draw[propassignment,red] (1.5*\angle + \move:\radius) to[bend right = \arrowangle] (\angle*2:\radius); %r
   \node at (\angle*1.5:\radius*2) {$I_7$};
@@
 	\node[align = center,black] at (\zero + \step*4.5:\radius*0.65) {\em \footnotesize propagators \\ \footnotesize \em inside $p$};
-	\draw[->,shorten >=2pt,thick,gray] (\zero + 1.6*\step:\radius) to[bend left = 45] (\zero + 1*\step:\radius); %p
-	\draw[->,shorten >=2pt,thick,gray] (\zero + 7.9*\step:\radius) to[bend left = 45] (\zero + 7*\step:\radius); 
+	\draw[propassignment,gray] (\zero + 1.6*\step:\radius) to[bend left = \arrowangle] (\zero + 1*\step:\radius); %p
+	\draw[propassignment,gray] (\zero + 7.9*\step:\radius) to[bend left = \arrowangle] (\zero + 7*\step:\radius); 
 	\node[align = center,black] at (\zero + 6.8*\step:1.5*\radius) {\em \footnotesize If $m \in I_i$ then \\ \em \footnotesize it was contributed by \\ \em \footnotesize the blue propagator};
@@
 	\centerarc[red,line width = 2pt,line cap = round](0,0)(\zero + 1.5*\step:\zero+1.56*\step:\radius);
-	\draw[->,shorten >=2pt,thick,gray] (\zero + 1.45*\step:\radius) to[bend left = 45] (\zero + 1*\step:\radius); %p
-	\draw[->,shorten >=2pt,thick,gray] (\zero + 1.61*\step:\radius) to[bend right = 45] (\zero + 2*\step:\radius); %q 
-	\draw[->,shorten >=2pt,thick,gray] (\zero + 7.7*\step:\radius) to[bend left = 45] (\zero + 7*\step:\radius); %blue
+	\draw[propassignment,gray] (\zero + 1.45*\step:\radius) to[bend left = \arrowangle] (\zero + 1*\step:\radius); %p
+	\draw[propassignment,gray] (\zero + 1.61*\step:\radius) to[bend right = \arrowangle] (\zero + 2*\step:\radius); %q 
+	\draw[propassignment,gray] (\zero + 7.7*\step:\radius) to[bend left = \arrowangle] (\zero + 7*\step:\radius); %blue
 	\begin{scope}

### 2019-09-05 GWLDCII.tex
just a few comments on comments

--- 2019-09-05 GWLDCII.tex
@@
 While it was already possible to construct the Grassmann necklace of a Wilson loop diagram via existing bijections between some of the various combinatorial objects that index the positroid cells, this process was convoluted and involved multiple steps; our algorithm allows us to track directly how each propagator in the Wilson loop diagram contributes to each term in the Grassmann necklace.
-{\color{violet} Furthermore, the above algorithm allows us to determine that the positroids associated to Wilson loop better.
+{\color{violet} Furthermore, the above algorithm allows us to determine that the positroids associated to Wilson loop better\note{This sentence has a grammar problem and perhaps as a consequence I don't understand what it is saying}.
 In particular, Corrollary \ref{no coloops} shows that these positroids have no coloops, and gives an exact characterization of their loops.}Many of the technical lemmas required to prove Theorem~\ref{res:alg gives GN} continue to be important in subsequent sections: in particular we have Lemma~\ref{lem sian}, which identifies certain configurations of propagators that must appear in any admissible Wilson loop diagram, and Lemma~\ref{vertex cyclic int lem}, which shows that the pattern of values that a propagator contributes to each term of the Grassmann necklace is both simple and predictable.
@@
 
- \note{Remember to keep an eye out when proofreading: do we just need the vertices appearing in the GN element to be the same, or do we actually need the functions to match up} \sanote{need functions to match in 4.4}
+ \note{Remember to keep an eye out when proofreading: do we just need the vertices appearing in the GN element to be the same, or do we actually need the functions to match up} \sanote{need functions to match in 4.4}\note{That's ok though because this remark does give the function matching in that region.}
 
@@
 \caption{$W'$ and $V'$ are locally the same between $j$ and $l+1$, so we will have $I_i^W\cap [j,l] = I_m^V\cap[j,l]$ even though $p \neq s$ and $q \neq t$.}\label{fig:locally identical}
-\end{figure} \sanote{just checking, we are allowing the first and the last propagators (in the $I_i$ induced ordering) to be different, but not the internal ones?}
+\end{figure} \sanote{just checking, we are allowing the first and the last propagators (in the $I_i$ induced ordering) to be different, but not the internal ones?}\note{I think I see the problem here.
+When I wrote $(j-1, \ldots, \ell+1)$ I meant the *list* from $j-1$ to $\ell+1$, so in particular $j-1$ and $\ell+1$ are included; it was not meant to be interval notation.
+However, since we usually do use something more like interval notation we should write $[j-1, \ell+1]$.}
+
 \end{rmk}

### 2019-09-05 GWLDCII.tex
changes from over the phone

@@
 While it was already possible to construct the Grassmann necklace of a Wilson loop diagram via existing bijections between some of the various combinatorial objects that index the positroid cells, this process was convoluted and involved multiple steps; our algorithm allows us to track directly how each propagator in the Wilson loop diagram contributes to each term in the Grassmann necklace.
-{\color{violet} Furthermore, the above algorithm allows us to determine that the positroids associated to Wilson loop better\note{This sentence has a grammar problem and perhaps as a consequence I don't understand what it is saying}.
-In particular, Corrollary \ref{no coloops} shows that these positroids have no coloops, and gives an exact characterization of their loops.}Many of the technical lemmas required to prove Theorem~\ref{res:alg gives GN} continue to be important in subsequent sections: in particular we have Lemma~\ref{lem sian}, which identifies certain configurations of propagators that must appear in any admissible Wilson loop diagram, and Lemma~\ref{vertex cyclic int lem}, which shows that the pattern of values that a propagator contributes to each term of the Grassmann necklace is both simple and predictable.
+Furthermore, the above algorithm allows us to understand the positroids associated to Wilson loop better.
+In particular, Corollary \ref{no coloops} shows that these positroids have no coloops, and gives an exact characterization of their loops.
+Many of the technical lemmas required to prove Theorem~\ref{res:alg gives GN} continue to be important in subsequent sections: in particular we have Lemma~\ref{lem sian}, which identifies certain configurations of propagators that must appear in any admissible Wilson loop diagram, and Lemma~\ref{vertex cyclic int lem}, which shows that the pattern of values that a propagator contributes to each term of the Grassmann necklace is both simple and predictable.
 
@@
 \item Vertices of $W$ that do not support any propagators are called {\bf non-supporting}.
-\st{The set of all non-supporting vertices in $W$ is denoted $F(\emptyset)$.
-}\sanote{tried to get rid of this notation.
-Check if I"ve missed any}
 \end{enumerate}
@@
 This is a useful result in and of itself, as it greatly simplifies the process of identifying the positroid associated to a given Wilson loop diagram.
-{\color{violet} Furthemore, we use it to characterise the positroids associated to Wilson loop diagrams according to loops and coloops (Corrollary \ref{no coloops}).} It also allows us to examine how the positroid changes as we make minor changes to the Wilson loop diagram; indeed, the techniques we develop in this section to verify that our algorithm produces the correct Grassmann necklace will also be used repeatedly in later sections.
+Furthemore, we use it to characterize loops and coloops in the positroid associated to a Wilson loop diagram (Corrollary \ref{no coloops}).
+It also allows us to examine how the positroid changes as we make minor changes to the Wilson loop diagram; indeed, the techniques we develop in this section to verify that our algorithm produces the correct Grassmann necklace will also be used repeatedly in later sections.
 
@@
 
-The following lemma establishes certain configurations of propagators that must exist in any admissible diagram with no non-supporting vertices (i.e.
-with $F(\emptyset) = \emptyset$).
+The following lemma establishes certain configurations of propagators that must exist in any admissible diagram with no non-supporting vertices.
 We make use of this result in several induction proofs below.
 
-\begin{lem}\label{lem sian} \sanote{should this be rephrased more similarly to the philosophy of Lemma 4.4, allowing non-supporting vertices to be added in or taken out?}
+\begin{lem}\label{lem sian}
   Let $W$ be a weakly admissible WLD with at least 5 vertices and in which each vertex supports at least one propagator.  Then at least one of the following two things occurs:
@@
 
-With this setup, if we can find a vertex $\ell$ (with \hlfix{$\ell <_i i$ and $\ell <_m m$}{ $i <_i \ell$ and $m <_m \ell$?
-This is what is in the picture?}) such that the \emph{configuration} of propagators ending in the interval \st{$(j-1, \ldots, \ell+1)$} {\color{violet}$[j, \ell]$} is identical in both $W'$ and $V'$, then the vertices contributed to $I_i^W$ and $I_m^V$ are the same from step $j$ to step $\ell$ (inclusive).
+With this setup, if we can find a vertex $\ell$ occurring after both $i$ and $m$ such that the \emph{configuration} of propagators ending in the interval $[j-1, \ell+1]$ is identical in both $W'$ and $V'$, then the vertices contributed to $I_i^W$ and $I_m^V$ are the same from step $j$ to step $\ell$ (inclusive).
 See Figure~\ref{fig:locally identical} for an illustration of this.
@@
 \caption{$W'$ and $V'$ are locally the same between $j$ and $l+1$, so we will have $I_i^W\cap [j,l] = I_m^V\cap[j,l]$ even though $p \neq s$ and $q \neq t$.}\label{fig:locally identical}
-\end{figure} \sanote{just checking, we are allowing the first and the last propagators (in the $I_i$ induced ordering) to be different, but not the internal ones?}\note{I think I see the problem here.
-When I wrote $(j-1, \ldots, \ell+1)$ I meant the *list* from $j-1$ to $\ell+1$, so in particular $j-1$ and $\ell+1$ are included; it was not meant to be interval notation.
-However, since we usually do use something more like interval notation we should write $[j-1, \ell+1]$.}
+\end{figure}
 
@@
 
-So let $p = (a,b)$ with $a<_ib$ and $I_i(p) = b+1$, and choose $p$ such that $\big|[a+1,b]\big|$ is \hlfix{minimal amongst propagators of $W$ contributing their last vertices with this property.}{changed wording to be accurate, but feels clunky}
+So let $p = (a,b)$ with $a<_ib$ and $I_i(p) = b+1$, and choose $p$ such that $\big|[a+1,b]\big|$ is minimal amongst propagators of $W$ which contribute their last vertices and are in Case 2.
 
@@
 
-Let $W = (\cP,[n])$ be an admissible Wilson loop diagram\st{, and}{\color{violet}.
-For every }$p = (i,j) \in \cP$\st{.
-Then}{\color{violet}, the sets} $J_p^{W}(i)$, $J_p^{W}(i+1)$, $J_p^{W}(j)$, and $J_p^{W}(j+1)$ are each non-empty cyclic intervals which partition $[n]$ and occur in the given cyclic order.
+Let $W = (\cP,[n])$ be an admissible Wilson loop diagram.
+For every $p = (i,j) \in \cP$, the sets $J_p^{W}(i)$, $J_p^{W}(i+1)$, $J_p^{W}(j)$, and $J_p^{W}(j+1)$ are each non-empty cyclic intervals which partition $[n]$ and occur in the given cyclic order.
 \end{lem}
-\sanote{is there a way to express the cyclic intervals more easily than the cases in this proof?}
+
 \begin{proof}
@@
 Now suppose $W$ has more than one propagator.
-Since non-supporting vertices have no effect on Algorithm~\ref{alg:put GN on WLD}, it suffices to prove the result for $W$  (possibly weakly admissible) with \st{$F(\emptyset) = \emptyset$}{\color{violet} no non-supporting vertices}.
+Since non-supporting vertices have no effect on Algorithm~\ref{alg:put GN on WLD}, it suffices to prove the result for $W$  (possibly weakly admissible) with no non-supporting vertices.
 Then by Lemma~\ref{lem sian}, $W$ has at least one of the four situations illustrated in Figure~\ref{fig 3 cases}.
@@
 
-In each of the four cases, when we remove the propagator labelled $p$ we obtain a diagram which satisfies \hlfix{the statement of the theorem by the induction hypothesis}{???
-changed to statement of the theorem slightly to make this make sense}, and contains a propagator ${q = (i,j)}$ with no other propagators inside it (with respect to the $<_i$ orientation).
+In each of the four cases, when we remove the propagator labelled $p$ we obtain a diagram which satisfies the statement of the theorem by the induction hypothesis, and contains a propagator ${q = (i,j)}$ with no other propagators inside it (with respect to the $<_i$ orientation).
 Note that this region may or may not contain non-supporting vertices, which we will call $l, l+1, \ldots$ as necessary.
@@
 We should state it prominently and move on.} so if $r \neq p$, then $I_w^W(r) = I_w^V(r)$.
-Meanwhile, the value of $I^{W}_w(p)$ depends on which step in the algorithm the propagator $q$ \hlfix{is assigned to}{did the change from assign to contribute never happen?} a vertex {\color{violet} in the diagram $V$}, i.e.
+Meanwhile, the value of $I^{W}_w(p)$ depends on which step in the algorithm the propagator $q$ contributes a vertex in the diagram $V$, i.e.
 on the value of $I^{V}_w(q)$.
@@
 
-\sanote{skipping careful read of this proof and moving on}
 Consider the Wilson loop diagram $X$ formed from $V$ by replacing the propagator $q = (i,j)$ with $q = (i, j-1)$;  $X$ is still admissible since we have not decreased the support of any set of propagators.
@@
 Fix $n$.
-Let the triple $(W, i, m)$ be such a counterexample on $n$ vertices \hlfix{which is minimal with respect to the number of propagators}{minimal in what respect?
-$i$ first where this occurs?
-$m$ the smallest such number?
-what do propagators have to do with it?}.
-%, and among all those counterexamples on $n$ vertices with the same number of propagators, let $(W,i,k)$ be minimal with respect to the distance from $i$ to $k$ in the $\leq _i$ order.
+Let $W$ be such a counterexample with the minimal number of propagators.
 
@@
 \textbf{Case I}:  Suppose $p$ has one end on edge $i-1$.
-If $p$ is not supported on $i+1$, then in building $I_{i+1}$ we will assign the same propagators as in the construction of $I_i$ from vertices $i+1$ up to $b-1$, that is \bas I_{i+1} \cap [i+1,b-1] = I_{i} \cap [i+1,b-1]\eas {\color{violet}by Remark \ref{rmk algorithm locally same}}.
+If $p$ is not supported on $i+1$, then in building $I_{i+1}$ we will assign the same propagators as in the construction of $I_i$ from vertices $i+1$ up to $b-1$, that is \bas I_{i+1} \cap [i+1,b-1] = I_{i} \cap [i+1,b-1]\eas by Remark \ref{rmk algorithm locally same}.
 If $p$ is supported on $i+1$, then $b= i+1$ and the interval $[i+1,b-1]$ is empty, so the above equality remains true, albeit vacuously.
@@
 
-Combining Lemmas \ref{lem uncovered}, \ref{lem dihedral}, and \ref{lem good p}, it therefore suffices to study the Le diagrams of weakly admissible Wilson loop diagrams with \st{$F(\emptyset)  = \emptyset$}{\color{violet}no non-supporting vertices} and admitting one of the configurations described in Lemma \ref{lem good p}, with propagators $p = (n-3, n-1)$ and $q= (n-5, n-3)$ (if $q$ exists) both of length 2.
+Combining Lemmas \ref{lem uncovered}, \ref{lem dihedral}, and \ref{lem good p}, it therefore suffices to study the Le diagrams of weakly admissible Wilson loop diagrams with no non-supporting vertices and admitting one of the configurations described in Lemma \ref{lem good p}, with propagators $p = (n-3, n-1)$ and $q= (n-5, n-3)$ (if $q$ exists) both of length 2.
 See Figure~\ref{fig special p} for an illustration of the two possibilities.

### 2019-09-05 GWLDCII.tex
added exposition and abstract, fix parametrized

@@
 
+\begin{abstract}
+  Wilson loop diagrams are an important tool in studying scattering amplitudes of SYM $N=4$ theory and are known by previous work to be associated to positroids.
+In this paper we study the structure of the associated positroids, as well as the structure of the denominator of integral defined by each diagram.
+In particular, we give an algorithm to derive the Grassman necklace of the assoicated positroid directly from the Wilson loop diagram.
+We also give a recursive proof that the dimension of these cells is thrice the number of propagators in the diagram.
+We also show that the denominator in the integral is the radical of the product of minors defined by the elements of the Grassmann necklace.
+\end{abstract}
 \section{Introduction}
@@
 As with the Amplituhedron, each Wilson loop represents the sum of a family of $N^kMHV$ Feynman diagrams, and adding up the corresponding sums of Feynman integrals associates a volume form to a convex space different from the Amplituhedron \cite{Hodges2013}.
-Agarwala and Marin-Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that can be realized as an element of $\Gr(k,n)$ \cite{wilsonloop}, while other work has shown a connection between the space parametrized by Wilson loop diagrams and the Amplituhedron \cite{casestudy, Amplituhedronsquared}.
-
-In the above work and elsewhere, it is clear that while the space parametrized by the Wilson loop diagrams is related to the Amplituhedron, they are not the same space.
-For instance, it is conjectured that the Amplituhedron is orientable, whereas Agarwala and Marcott show in \cite{non-orientable} that the space parametrized by the Wilson loop diagrams can be seen as a non-orientable vector bundle over some submanifold of $\Gr(k,n)$.
+Agarwala and Marin-Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that can be realized as an element of $\Gr(k,n)$ \cite{wilsonloop}, while other work has shown a connection between the volume filled by Wilson loop diagrams and the Amplituhedron \cite{casestudy, Amplituhedronsquared}.
+
+In the above work and elsewhere, it is clear that while the space filled by the Wilson loop diagrams is related to the Amplituhedron, they are not the same space.
+For instance, it is conjectured that the Amplituhedron is orientable, whereas Agarwala and Marcott show in \cite{non-orientable} that the space parametrized by the Wilson loop diagrams as a subspace of $\Gr(k, n+1)$ can be seen as a non-orientable vector bundle over some submanifold of $\Gr(k,n)$.
 Furthermore, the cells associated to the Wilson loop diagrams are different from the cells associated to BCFW diagrams, which can be seen by comparing the results of \cite{AmplituhedronDecomposition} and \cite{casestudy}.
@@
 While this has been proved by Marcott in \cite{WLDdim} using matroidal arguments, our proof is constructive and explicitly relates the position of the plusses in the Le diagram to the propagators in the Wilson loop diagram.
+{\color{violet} This proof and the methods used therein are a first step towards understanding how the positroid cell assocaited to a Wilson loop diagram changes as one adds propagators in certain positions.}
 
@@
 Furthemore, we use it to characterize loops and coloops in the positroid associated to a Wilson loop diagram (Corrollary \ref{no coloops}).
-It also allows us to examine how the positroid changes as we make minor changes to the Wilson loop diagram; indeed, the techniques we develop in this section to verify that our algorithm produces the correct Grassmann necklace will also be used repeatedly in later sections.
+\hlfix{It also allows us to examine how the positroid changes as we make minor changes to the Wilson loop diagram;}{what does this mean?} {\color{violet} It allows us to see how the Le diagram assoicated to a Wilson loop diagram changes as one adds propagators in certain positions (Theorem \ref{thm dim}).} Indeed, the techniques we develop in this section to verify that our algorithm produces the correct Grassmann necklace will also be used repeatedly in later sections {\color{violet} to calculate the dimension of the associated positroid cell (section \ref{sec dim}) and to study the structure of the poles of the associated integral $I(W)$ (section \ref{sec poles}).}
 
@@
 The positroid cells associated to the Amplituhedron are of dimension $4|\cP|$.
-In \cite{non-orientable}, Agarwala and Marcott show that the dimension of the Deodhar component is the sum of $\|\cP\|$ and the dimension fo the associated positroid cell.
+In \cite{non-orientable}, Agarwala and Marcott show that the dimension of the Deodhar component is the sum of $|\cP|$ and the dimension of the associated positroid cell.
 %\[|\cP| + \text{ the dimension of associated positroid cell}.\]
@@
 By combining Algorithms~\ref{alg:put GN on WLD} and \ref{alg:GN to Le} (converting from WLD to Grassmann necklace, and Grassmann necklace to Le diagram respectively) we explicitly describe the effect of adding another propagator to a Wilson loop diagram in terms of the plusses of the associated Le diagrams, and hence give a recursive proof of the $3|\cP|$-dimensionality of the cells.
+
+{\color{violet}More than just a dimensionality result, the lemmas below are a first step towards undertanding how the adding an extra propagator changes the associated positroid cell. }
 
@@
 
-\sanote{Add exposition in this section and in intro about how this allows one to talk about what happens to a postriod cell as one adds a propagator.
-These results aren't enough, but a starting point, and certainly not done in this paper}
-
 The two possible cases for $W$ are illustrated in Figure~\ref{fig special p}.

### 2019-09-08 GWLDCII.tex
edits and comments to sections 3 and 4, paper 2

@@
 Let $W = (\cP,V)$ be an admissible Wilson loop diagram, and fix an edge $e$.
-Let $\{p_1 \ldots p_r\}$ be the propagators with one end lying on edge $e$ under a counterclockwise orderin.
+Let $\{p_1 \ldots p_r\}$ be the propagators with one end lying on edge $e$ under a counterclockwise ordering.
 That is, $p_1$ is closest to the vertex $e$, $p_i$ is positioned counterclockwise to $p_{i+1}$ and $p_r$ is the clockwise most propagator on this edge (closest to vertex $e+1$).
@@
 The fact that Algorithm~\ref{alg:put GN on WLD} does construct the required Grassmann necklace is proved in Theorem~\ref{res:alg gives GN}.
-An worked example of Algorithm~\ref{alg:put GN on WLD} is given in Example~\ref{eg:apply GN alg}.
+A worked example of Algorithm~\ref{alg:put GN on WLD} is given in Example~\ref{eg:apply GN alg}.
 
@@
 \item {\em Step $j$ for starting vertex $i$}: If $\Prop(j) = \emptyset$, do nothing.
-Else, let $p \in \Prop(j)$ be the clockwise most propagator supported on $j$.
+Else, let $p \in \Prop(j)$ be the clockwise-most propagator supported on $j$.
 Write $I_i^W = I_i^W\cup \{j\}$, and delete propagator $p$ from the diagram.
@@
 Informally: one starts at $i$ and moves counterclockwise around the vertices of $W$, at each step removing the clockwise-most propagator supported on that vertex (if it exists).
-The set $I_i$ lists the vertices at which a propagator was deleted.
-
-If the algorithm assigns vertex $j$ to propagator $p$ from starting vertex $i$, we say that $p$ \emph{contributes} $j$ to $I_i$.
-Notationally, we represent this by allowing the $I_i$ symbol to represent a function as well as a set, as follows:
+The set $I_i^W$ lists the vertices at which a propagator was deleted.
+
+If the algorithm assigns vertex $j$ to propagator $p$ from starting vertex $i$, we say that $p$ \emph{contributes} $j$ to $I_i^W$.
+Notationally, we represent this by allowing the $I_i^W$ symbol to represent a function as well as a set, as follows:
 \begin{dfn}\label{def I_i as a function}
@@
 
-For both $I_i^W$ the set and the function, when the diagram $W$ is clear from context, we drop the superscript and simply write $I_i$.
-
-% Sian deleted the propagator ordering for now: since we only use it in one proof, we can make it a local definition.
-% Obviously if we find ourselves using it elsewhere we can bring this definition back. (If so, uncomment the line in the following example as well.)
-
-%Each $I_i$ also imposes an ordering on the propagators, determined by when the propagator contributes to the sequence:
+For both $I_i^W$ the set and the function, when the diagram $W$ is clear from context we drop the superscript and simply write $I_i$.
+
 \begin{dfn} \label{proporderingdfn}
@@
 Note that different $I_*$ impose different orderings on the propagators.
-Furthermore, Corrollary \ref{GN alg well defined} shows that this ordering respects the ordering of vertices in $I_i$.
-That is, $I_i(p_j) <_i I_i(p_l)$ for all $j <l$.
+Furthermore, Corollary \ref{GN alg well defined} shows that this ordering respects the ordering of vertices in $I_i$.
+That is, if $p_j$ occurs before $p_l$ in the ordering imposed by $I_i$, then we also have $I_i(p_j) <_i I_i(p_l)$.
 
@@
 \[1235, 2356, 3456, 4567, 5671, 6712, 7812, 8123.\]
-The reader can easily verify that this sequence of $k$-sets satisfies the definition of a Grassmann necklace, and can (with significantly more work) also verify that this Grassmann necklace defines the positroid $M(W)$ associated to the Wilson loop diagram $W$ above, as we will prove in general shortly.
+The reader can easily verify that this sequence of $k$-sets satisfies the definition of a Grassmann necklace, and can (with significantly more work) also verify that this Grassmann necklace defines the positroid $M(W)$ associated to the Wilson loop diagram $W$ above.
+We will prove this in general shortly.
 \end{eg}
 
-%Notice that for each element in the Grassmann necklace, the propagators contribute in a particular order. It is sometimes useful to think of the propagators in this order. 
+%
 %\begin{dfn} \label{prop order dfn}
@@
     \clipcenterarc(0,0)(\startpoint-10:\endpoint+10:\radius)
-		\newpropbend{6.3}{8.6}{80}
-		\node at (\zero + 7.5*\step:\radius*0.8) {\footnotesize $r$};
-		\newprop[midway,left]{5.5}{-4}{}
-		\node at (\zero + 3*\step:\radius*0.5) {\footnotesize $p$};
+    \newpropbend{5.3}{7.6}{80}
+    \node at (\zero + 6.5*\step:\radius*0.8) {\footnotesize $r$};
+    \newprop[midway,left]{8.5}{-4}{}
+    \node at (\zero + 8.15*\step:\radius*0.5) {\footnotesize $p$};
     \newprop[midway]{11.5}{-4}{}
@@
     \clipcenterarc(0,0)(\startpoint-10:\endpoint+10:\radius)
-		\newpropbend{6.3}{8.6}{80}
-		\node at (\zero + 7.5*\step:\radius*0.8) {\footnotesize $r$};
-		\newprop[midway,left]{5.5}{19}{}
-		\node at (\zero + 5.5*\step:\radius*0.5) {\footnotesize $s$};
+    \newpropbend{5.3}{7.6}{80}
+    \node at (\zero + 6.5*\step:\radius*0.8) {\footnotesize $r$};
+    \newprop[midway,left]{8.5}{22}{}
+    \node at (\zero + 8.5*\step:\radius*0.5) {\footnotesize $s$};
     \newprop[midway]{11.5}{21}{}
@@
 \]
-\caption{$W'$ and $V'$ are locally the same between $j$ and $l+1$, so we will have $I_i^W\cap [j,l] = I_m^V\cap[j,l]$ even though $p \neq s$ and $q \neq t$.}\label{fig:locally identical}
+\caption{$W'$ and $V'$ are locally the same between $j$ and $l+1$, so we will have $I_i^W\cap [j,l] = I_m^V\cap[j,l]$ even though $p \neq s$ and $q \neq t$.
+Note that propagators such as $r$ which have {\em both} ends inside the region of interest must be identical in both diagrams.}\label{fig:locally identical}
 \end{figure}
@@
 With that in mind, we are ready to begin proving properties of the algorithm.
-We first show that the algorithm for $I_i$ can never reach the final vertex (in the $<_i$ order) in a propagator's support without having already assigned that propagator; in particular, this guarantees that the construction of $I_i$ always terminates in fewer than $n$ steps, as shown in Corrollary \ref{GN alg well defined}.
+We first show that the algorithm for $I_i$ can never reach the final vertex (in the $<_i$ order) in a propagator's support without having already assigned that propagator; in particular, this guarantees that the construction of $I_i$ always terminates in fewer than $n$ steps.
 
@@
 For any $i \in [n]$ and for any $p \in \cP$, $I_i(p)$ is not maximal (with respect to $<_i$) amongst the vertices that support $p$.
-\end{lem} \sanote{wanted to rewrite this lemma to emphasize the fact that we are using the same properties of Alg 3.7 over and over again, and have these principals set apart in a remark}
+\end{lem} 
+\sanote{wanted to rewrite this lemma to emphasize the fact that we are using the same properties of Alg 3.7 over and over again, and have these principals set apart in a remark}
 \begin{proof}
@@
 \] 
-\caption{The two types of configuration in which a propagator could (in theory) contribute its $<_i$-maximal support vertex to $I_i$.}
+\caption{The two types of configuration that would (in theory) allow the propagator $p$ to contribute its $<_i$-maximal support vertex to $I_i$.}
 \label{fig:no fourth vertex}
 \end{figure}
-\note{Question: is the diagram clearer in this configuration (starting vertex $i$ matches up in both) or in the old configuration (propagator $p$ matches up)?} \sanote{I think it is fine as is}
-
 In Case 1, \st{observe that we must have another propagator $q = (c,b)$ with $c<_i b$ and $I_i(q) = b+1$, because otherwise $I_i$ would assign $p$ to $b+1$.}{\color{violet} since $b+1<_i I_i(p)$ there must be some propagator, $q$ before $p$ in $\cP^i$ such that $I_i(q) = b+1$.
@@
 
-So let $p = (a,b)$ with $a<_ib$ and $I_i(p) = b+1$, and choose $p$ such that $\big|[a+1,b]\big|$ is minimal amongst propagators of $W$ which contribute their last vertices and are in Case 2.
+So let $p = (a,b)$ with $a<_ib$ and $I_i(p) = b+1$, and choose $p$ such that $\big|[a+1,b]\big|$ is minimal amongst propagators of $W$ which contribute their last vertex and are in Case 2.
 
@@
 \begin{cor}\label{GN alg well defined}
-If $W$ is an admissible Wilson loop diagram with $k$ propagators and $n$ vertices. Then Algorithm~\ref{alg:put GN on WLD} assigns exactly $k$ distinct vertices to each $I_i$ in $n$ steps.
+If $W$ is an admissible Wilson loop diagram with $k$ propagators and $n$ vertices, then Algorithm~\ref{alg:put GN on WLD} assigns exactly $k$ distinct vertices to each $I_i$ in $n$ steps.
 \end{cor} 
@@
 We first calculate $I^{W}_w$ for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$.
-\hlfix{Note that $p$ has no effect on other propagators for starting vertices in this range,}{By rmk \ref{rmk algorithm locally same}?
-If so, the entire proof depends on this fact.
-We should state it prominently and move on.} so if $r \neq p$, then $I_w^W(r) = I_w^V(r)$.
+Note that $p$ has no effect on other propagators for starting vertices in this range \hlfix{(since $p$ will be the final propagator encountered by the algorithm)}{Sian added this: it's not really a locally-the-same argument so I'm not sure it'll help to reference Remark 3.12} so if $r \neq p$, then $I_w^W(r) = I_w^V(r)$.
 Meanwhile, the value of $I^{W}_w(p)$ depends on which step in the algorithm the propagator $q$ contributes a vertex in the diagram $V$, i.e.
@@
 %\note{Sian replaced ``counterclockwise'' with ``clockwise'' in a couple of places in this proof: someone please doublecheck?  Karen checked and it seems correct with Sian's changes.}
+% Thank you! Clocks are difficult.
 For each $i \in [n]$, let $I_i$ be the set of vertices assigned to the propagators of $W$ by Algorithm~\ref{alg:put GN on WLD} with starting vertex $i$.
@@
 
-Suppose for a contradiction that there exists an admissible diagram for which there exists an $i$ with $m\in I_i\setminus \{i\}$ and $m \not\in I_{i+1}$.
-Fix $n$.
+Fix $n$, and suppose for a contradiction that there exists an admissible diagram for which there exists an $i$ with $m\in I_i\setminus \{i\}$ and $m \not\in I_{i+1}$.
 Let $W$ be such a counterexample with the minimal number of propagators.
@@
 In this case it is clear that applying Algorithm~\ref{alg:put GN on WLD} at vertex $i$ and vertex $i+1$ produces exactly the same result, i.e.
-$I_{i+1} = I_i$, and so $(W, i, m)$ is not a counterexample at all.
+$I_{i+1} = I_i$, and so $W$ is not a counterexample at all.
 
@@
 
+\note{Sian rewrote Case 1 based on Susama's suggested edits}
 \textbf{Case I}:  Suppose $p$ has one end on edge $i-1$.
-If $p$ is not supported on $i+1$, then in building $I_{i+1}$ we will assign the same propagators as in the construction of $I_i$ from vertices $i+1$ up to $b-1$, that is \bas I_{i+1} \cap [i+1,b-1] = I_{i} \cap [i+1,b-1]\eas by Remark \ref{rmk algorithm locally same}.
+By Remark~\ref{rmk algorithm locally same} the construction of $I_i^W$ and $I_{i+1}^W$ is locally the same (indeed, locally {\em identical} in this case) from vertex $i+1$ to $b-1$, so we have $I_{i+1}^W \cap [i+1,b-1] = I_{i}^W \cap [i+1,b-1]$.
+Note that if $b = i+1$ then this interval is empty and the equality remains true.
+
+%If $p$ is not supported on $i+1$, then in building $I_{i+1}$ we will assign the same propagators as in the construction of $I_i$ from vertices $i+1$ up to $b-1$, and in particular we have \bas I_{i+1} \cap [i+1,b-1] = I_{i} \cap [i+1,b-1]\eas by Remark \ref{rmk algorithm locally same}.
 If $p$ is supported on $i+1$, then $b= i+1$ and the interval $[i+1,b-1]$ is empty, so the above equality remains true, albeit vacuously.
-Furthermore, by Lemma~\ref{vertex cyclic int lem} it must happen that $p$ contributes vertex $b$ to $I_{i+1}$, as otherwise $b$ would never be contributed by $p$.
-Consequently, by Remark \ref{clockwise ordering rem}, in building $I_{i+1}$,  when the algorithm reaches vertex $b$ there cannot be any remaining unassigned propagators that are supported on $b$ and clockwise of $p$.
-This is also true in when the algorithm constructing $I_i$ reaches $b$, \st{since the same propagators have been assigned beforehand.}\sanote{don't like same here}{\color{violet}since any propagators lying counterclockwise of $p$ on the edge $i-1$ must have their support in $[i-1, b]$.
-By Lemma \ref{no fourth vertex}, these propagators contribute before the algorithm reaches $b$.
+
+By Lemma~\ref{vertex cyclic int lem} it must happen that we have $I_{i+1}^W(p) = b$, as otherwise $b$ would never be contributed by $p$.
+Consequently, when the construction of $I_{i+1}^W$ reaches vertex $b$ there cannot be any remaining unassigned propagators that are supported on $b$ and clockwise of $p$ (Remark~\ref{clockwise ordering rem}).
+It follows that the same must be true when $I_i^W$ reaches vertex $b$, since $I_i^W$ and $I_{i+1}^W$ behave identically on the interval $[i+1,b-1]$ as noted in the previous paragraph.
+
+The previous two paragraphs also imply that $m \geq_i b+1$, since $I_{i+1}^W \cap [i+1,b-1] = I_{i}^W \cap [i+1,b-1]$ and $b \in I_{i+1}^W$.
+
+%This is also true in when the algorithm constructing $I_i$ reaches $b$, \st{since the same propagators have been assigned beforehand.}\sanote{don't like same here}{\color{violet}since any propagators lying counterclockwise of $p$ on the edge $i-1$ must have their support in $[i-1, b]$.
+By Lemma \ref{lem no fourth vertex}, these propagators contribute before the algorithm reaches $b$.
 Furthermore, Remark  \ref{rmk algorithm locally same} implies that these propagators contribute the same vertices to both $I_i$ and $I_{i+1}$.} This also implies that $m\geq_i b+1$.
 
-Let $W' = (\cP_{out}(p,<_i), [n])$, i.e. the diagram obtained from $W$ by removing both $p$ and all propagators inside of $p$.
-
-\st{By the above observations, if we commence Algorithm {\ref{alg:put GN on WLD}} in $W'$ from vertex $b$, then we are in the same situation with respect to unassigned propagators as if we began at $i$ in $W$ and proceeded to $b$ following the algorithm (recall that $I^W_i(p) =i$).} {\color{violet} Note that the propagators in $\cP_{out}(p,<_i)$ come first in the ordering imposed by $I_i^W$ (Definition \ref{proporderingdfn}).
-Therefore, the ordering and contributions of propagators defined by $I_b^{W'}$ are the same as that of $I_i^W$ after the removal of these initial propagators.} \st{The propagators contributing to $I_{i}^W$ before the vertex $b$ are exactly the ones removed in the construction of $W'$.}  Similarly, starting at $i+1$ in $W$ and moving to $b+1$ leaves us in the same situation with respect to unassigned propagators as beginning at $b+1$ in $W'$ would.
+Now let $W' = (\cP_{out}(p,<_i), [n])$, i.e. the diagram obtained from $W$ by removing both $p$ and all propagators inside of $p$. $W'$ has strictly fewer propagators than $W$ did.
+
+It follows that $I_i^W$ and $I_b^{W'}$ are locally the same from vertex $b$ onwards, since by the above observations the propagators removed from $W$ to create $W'$ are exactly those that come first in the ordering defined by $I_i^W$.
+Similarly, $I_{i+1}^W$ and $I_{b+1}^{W'}$ are locally the same from $b+1$ onwards.
+By Remark~\ref{rmk algorithm locally same}, this yields the equalities
+
+%\st{By the above observations, if we commence Algorithm {\ref{alg:put GN on WLD}} in $W'$ from vertex $b$, then we are in the same situation with respect to unassigned propagators as if we began at $i$ in $W$ and proceeded to $b$ following the algorithm (recall that $I^W_i(p) =i$).}
+
+%{\color{violet} Note that the propagators in $\cP_{out}(p,<_i)$ come first in the ordering imposed by $I_i^W$ (Definition \ref{proporderingdfn}).
+Therefore, the ordering and contributions of propagators defined by $I_b^{W'}$ are the same as that of $I_i^W$ after the removal of these initial propagators.}
+
+%\st{The propagators contributing to $I_{i}^W$ before the vertex $b$ are exactly the ones removed in the construction of $W'$.}  Similarly, starting at $i+1$ in $W$ and moving to $b+1$ leaves us in the same situation with respect to unassigned propagators as beginning at $b+1$ in $W'$ would.
 This gives the equations
 \begin{align*}
-  I_i^{W} \cap [b,i-1] & = I_b^{W'} \\
-  I_{i+1}^{W} \cap [b+1,i-1] & = I_{b+1}^{W'}
+  I_i^{W} \cap [b,i-1] & = I_b^{W'}, \\
+  I_{i+1}^{W} \cap [b+1,i-1] & = I_{b+1}^{W'}.
 \end{align*} 
-\st{where the diagram is indicated in the superscript.}
-Thus we have $m\in I_b^{W'}\setminus\{b\}$ and $m\not\in I_{b+1}^{W'}$, contradicting the minimality of $(W, i, m)$.\sanote{see previous question about minimality.
-not sure why this is true, unless minimality in $|[i,m]|$?.}
+Since we have already noted that $m \geq_i b+1$, this implies that $m\in I_b^{W'}\setminus\{b\}$ and $m\not\in I_{b+1}^{W'}$. This contradicts the minimality of $W$.
 
@@
 since in both cases the algorithm in $W'$ proceeds identically to that in $W$ after assigning $p$.
-Since $m \neq i+1$, we have $m\in I_{i+1}^{W'}\setminus\{i+1\}$ but $m\not\in I_{i+2}^{W'}$, contradicting the minimiality of $(W, i, m)$.
+Since $m \neq i+1$, we have $m\in I_{i+1}^{W'}\setminus\{i+1\}$ but $m\not\in I_{i+2}^{W'}$, contradicting the minimiality of $W$.
 This completes the proof.
@@
 
-Thus we have shown that Algorithm \ref{alg:put GN on WLD} does in fact produce a Grassmann necklace. Next we check that it produces the correct one, i.e. the Grassmann Neclace for $M(W)$.
-
+Thus we have shown that Algorithm \ref{alg:put GN on WLD} does in fact produce a Grassmann necklace. Next we check that it produces the correct one, i.e. the Grassmann necklace that defines $M(W)$. 
+\note{Sian made minor edits to this proof: mostly removing those two numbered observations because one is now a remark and the other is only used once}
 \begin{thm}\label{res alg gives correct GN}
@@
 \end{thm}
-\sanote{skipping reading of this for now}
 \begin{proof}
@@
 Now fix $i \in [n]$, and write $I_i = \{a_1 <_i a_2 <_i \dots <_i a_k\}$.
-This imposes an ordering on the propagators $\cP$, where we label them $p_1, p_2, \dots, p_k$ such that $I_i(p_j) = a_j$ for each $j$.
-Define $\cP_m: = \{p_1,p_2,\dots,p_m\}$ for each $m\geq 0$, with $\cP_0 = \emptyset$.
-
-We enumerate two important observations:
-\begin{enumerate}
-\item If $a_{m-1}$ and $a_{m}$ are not consecutive vertices for some $m$, then for any intermediate vertex $a_{m-1}<_i x <_i a_{m}$ we must have $\Prop(x) \subseteq \cP_{m-1}$.
+Label the propagators of $W$ according to the ordering imposed by $I_i$, i.e.
+so that $I_i(p_{r}) = a_{r}$ for $1 \leq r \leq k$.
+Define $\cP_r: = \{p_1,p_2,\dots,p_r\}$ for each $r\geq 0$, with $\cP_0 = \emptyset$.
+
+% We enumerate two important observations:
+% \begin{enumerate}
+% \item If $a_{m-1}$ and $a_{m}$ are not consecutive vertices for some $m$, then for any intermediate vertex $a_{m-1}<_i x <_i a_{m}$ we must have $\Prop(x) \subseteq \cP_{m-1}$.
 This is because if any propagator supported on $x$ is still unassigned when the algorithm reaches $x$, we would have $x \in I_i$.
-\item When $p_m$ contributes $I_i(p_m) = a_m$ to the Grassmann necklace, it must be the clockwise-most propagator (amongst those not yet assigned) that is supported on $a_m$ i.e.
+% \item When $p_m$ contributes $I_i(p_m) = a_m$ to the Grassmann necklace, it must be the clockwise-most propagator (amongst those not yet assigned) that is supported on $a_m$ i.e.
 any other propagator in $\cP \setminus \cP_{m-1}$ that is supported on $a_m$ must be inside $p_m$ in the $a_m-1$ ordering.
-\end{enumerate}
-
-Now, let $J = \{j_1 <_i j_2<_i \dots <_i j_k\}$ be a $k$-set, and suppose that $J<_i I_i$ in the $<_i$-lexicographic order.
+% \end{enumerate}
+
+Let $J = \{j_1 <_i j_2<_i \dots <_i j_k\}$ be a $k$-set, and suppose that $J<_i I_i$ in the $<_i$-lexicographic order.
 Let $m$ be the minimal index such that $j_m <_i a_m$, i.e.
@@
 It is easily verified that this is an increasing chain of sets: indeed, if $q \in Q_l$ then $I_i(q) \in I_i(Q_l)$, and since $I_i(q)$ is one of the vertices that supports $q$ we must have $q \in \Prop(I_i(Q_l)) = Q_{l+1}$.
-Since $\cP$ is finite, the sequence therefore stabilizes in finitely many steps when $Q_{l+1} = Q_l$.
+Since $\cP$ is finite, the sequence stabilizes in finitely many steps.
 Let $Q := \cup_{l \geq 0} Q_l$ be this set of propagators.
@@
 We will show that $Q \subseteq \mathcal{P}_{m-1}$, which will imply the theorem as follows: if $Q \subseteq \cP_{m-1}$ then we have $I_i(Q)\subseteq J$, and hence $I_i(Q) \cup \{j_m\} \subseteq J$ as well.
-Since $I_i(Q) \cup \{j_m\}$ only supports the propagators in $Q$ but has $|Q|+1$ vertices, it is a dependent set.
-Thus $J$ is a dependent set as required, and the Grassmann necklace $(I_1,\dots,I_n)$ constructed from $W$ does indeed define the positroid $M(W)$.
+Since $I_i(Q) \cup \{j_m\}$ only supports the propagators in $Q$ but has $|Q|+1$ vertices, it is a dependent set in $M(W)$.
+Thus $J$ is also a dependent set, and the Grassmann necklace $(I_1,\dots,I_n)$ constructed from $W$ does indeed define the positroid $M(W)$.
 
 All that remains is to prove $Q\subseteq \mathcal{P}_{m-1}$, which we do by inductively proving $Q_l \subseteq \mathcal{P}_{m-1}$ for all $l \geq 0$.
-%If $Q_0 = \Prop(j_m) = \emptyset$ then $Q = \emptyset$, and $I_i(Q) \cup \{j_m\}= \{j_m\}$ is a single vertex supporting no propagators, and thus a dependent set. Otherwise,
-The base case $Q_0 \subseteq \cP_{m-1}$ follows immediately from the first numbered observation above that $\Prop(j_m) \subseteq \cP_{m-1}$
+The base case $Q_0 \subseteq \cP_{m-1}$ is immediate: since $j_m \not\in I_i$ by construction, there cannot be any unassigned propagators supported on $j_m$ when the algorithm reaches that vertex, i.e.
+$\Prop(j_m) \subseteq \cP_{m-1}$.
 
@@
 By construction there is some propagator $p_r \in Q_{l-1}$ such that $p_r$ and $q$ are both supported on $I_i(p_r) = a_r$.
-If $q$ is clockwise of $p_r$ on vertex $a_r$ then we immediately have $q \in \cP_{m-1}$ from the second numbered observation above.
+If $q$ is clockwise of $p_r$ on vertex $a_r$ then we immediately have $q \in \cP_{m-1}$ by Remark~\ref{clockwise ordering rem}.
 It remains to consider the case that $q$ is counter-clockwise of $p_r$ at $a_r$.
@@
 
+\note{Sian note to self: this picture isn't right}
 \begin{figure}[h]
-
 \bas{\begin{tikzpicture}[baseline=(current bounding box.east)]
@@
 Or is the implication clear enough not to be mentioned}\note{Nope: we just need $<_i I_i(p_r)$.
-$I_i(p_t) <_i I_i(p_r)$ certainly isn't obvious and may not be true}.
+$I_i(p_t) <_i I_i(p_s)$ certainly isn't obvious and may not be true}.
 {\color{violet} May not be necessary, but I think highlighted tex follows from "Now repeat the argument...." \begin{enumerate}\item If $V(p_r) \in [a_r-1, j_m]$ (other end closer to $j_m$) then $q$ inside $p_r$ in $a_r-1$ order.
@@
 (Main point is that other end closer to $i$) Either way,  admissibility implies that $a_s < a_r$ \item Now we repeat.
-Either  $V(p_s) \in [a_s-1, j_m]$ then $q$ inside $p_s$ in $a_s-1$ order and we are done \item Else, $V(p_s) \in [i, a_s+1]$ (Maybe $[i-1, a_s +1]$?).
+Either  $V(p_s) \in [a_s-1, j_m]$ then $q$ inside $p_s$ in $a_s-1$ order \hlfix{and we are done}{not quite true; same reasoning as why we're using ``the other end of the propagator'' instead of $V(p_s) \subseteq [a_s-1, j_m]$} \item Else, $V(p_s) \in [i, a_s+1]$ (Maybe $[i-1, a_s +1]$?).
 Either way, admissibility implies that $a_t < a_s$ and we've already established $a_s < a_r$ \end{enumerate} We don't have to include this argument.
@@
 
-We have now shown that Algorithm~\ref{alg:put GN on WLD} assoiates the correct Grassmann necklace to a Wilson Loop diagam Thereofre, we refer to Algorithm~\ref{alg:put GN on WLD} as the Grassmann necklace algorithm.
+We have now shown that Algorithm~\ref{alg:put GN on WLD} associates the correct Grassmann necklace to a Wilson loop diagam.
+Therefore, we refer to Algorithm~\ref{alg:put GN on WLD} as the Grassmann necklace algorithm.
 We close this section with a simple observation about the Grassmann necklaces of positroids associated to Wilson loop diagrams.
@@
 In an arbitrary Grassmann necklace, it is possible for an index $i$ to appear in no terms of the Grassmann necklace (a {\em loop}) or in all terms of the necklace (a {\em coloop}).
-Using Theorem~\ref{res:alg gives GN}, a characterization of the loops and coloops of the Grassmann necklace associated to a Wilson loop diagram follows easily.
+Using Theorems~\ref{res:alg gives GN} and \ref{res alg gives correct GN}, a characterization of the loops and coloops of the Grassmann necklace associated to a Wilson loop diagram follows easily.
 
@@
 Let $V$ be $W$ with $p$ removed.
-Then we can express $I_*^W$ in terms of $I_*^V$ as follows:
+Then we can express $I_*^W$ in terms of $I_*^V$ as follows:\note{I'm not a fan of the case labels in this display: there's enough going on already without throwing in extra information}
 
@@
 Note that $n-3 \not\in I_1^{V}$: \hlfix{for Case 2 this is clear from the diagram (since Algorithm {\ref{alg:put GN on WLD}} would force $q$ to contribute no later than vertex $n-4$),}{why?
-isn't obvious to me without several cases, and even then} while for Case 1 it follows directly from Lemma \ref{lem no fourth vertex}.
+isn't obvious to me without several cases, and even then}\note{yeah, I can't see this either; cyclic intervals is probably a better argument} while for Case 1 it follows directly from Lemma \ref{lem no fourth vertex}.
 Therefore when we start at vertex 1 and apply the Grassmann necklace algorithm to $W$, $p$ is the \st{only remaining unassigned propagator when we reach vertex $n-3$}{\color{violet}last propagator to contribute}, and so we have $ I_1^{W}(p) = n-3$ and $I_1^W = I_1^V\cup \{n-3\}$.
@@
 Recall that $I_1$ determines the shape of the Le diagram: specifically, the elements of $I_1$ label the rows of the diagram, working from top right to bottom left.
-By the arguments in Lemma {\ref{lem I}} we know that \st{${n,n-1,n-2, n-3 \not\in I_1^{V}}$}\sanote{Only see $n-3$ in Lemma 4.4?} {\color{violet} $ n-3 \not\in I_1^{V}$.
+By the arguments in Lemma {\ref{lem I}} we know that \st{${n,n-1,n-2, n-3 \not\in I_1^{V}}$}\sanote{Only see $n-3$ in Lemma 4.4?} \note{well yeah, that's why it says ``the arguments in Lemma 4.4'': we show that all props are assigned before $n-3$ in $I_1$.
+I think spelling it out in detail here is more confusing than not.}{\color{violet} $ n-3 \not\in I_1^{V}$.
 By Lemma \ref{lem no fourth vertex}, $n, n-2 \not \in I_1^V$.
@@
 where the final inclusion follows from the definition of Grassmann necklace\sanote{why only $\{n-1,n\}$?
-I'd believe an inclusion the other way}.
+I'd believe an inclusion the other way}\note{Definition of GN: $I_1 = (I_n\setminus\{n\})\cup\{\text{something}\}$}.
 In particular, $n-1$ is minimal in this set, so Algorithm~\ref{alg:GN to Le} yields a plus in the $(n-3) \rightarrow (n-1)$ position (i.e.
 the second box in the bottom row of the Le diagram of $W$) \hlfix{along with any plusses yielded by $I_n^V$.}{display seems to imply that there is exactly one such other $+$.
-Is this correct?}
+Is this correct?}\note{Display implies there's at most one, but if we apply no coloops I think that becomes exactly one.}
 \end{proof}
@@
 Note that $n-3\not\in I_{n-2}^{V}$ by Lemma~\ref{lem no fourth vertex}.
-Therefore the \st{paths controlling the} plusses contributed by $I_{n-2}^{W}$ are exactly the \st{paths for}{\color{violet} plusses from}\sanote{isn't this from Alg.\ref{alg:GN to Le} which says nothing about paths?}  $I_{n-1}^{V}$ along with the $(n-3)\rightarrow (n-2)$ path.
+Therefore the \st{paths controlling the} plusses contributed by $I_{n-2}^{W}$ are exactly the \st{paths for}{\color{violet} plusses from}\sanote{isn't this from Alg.\ref{alg:GN to Le} which says nothing about paths?} \note{see bolded stuff before previous lemma} $I_{n-1}^{V}$ along with the $(n-3)\rightarrow (n-2)$ path.
 This gives the statement of the lemma.
@@
 \st{We can see from the location of $q$ that $n-2\not\in I_{n-3}^{V}$} and that $n-5$ is the label of the last row in $\mathcal{B}$.\sanote{is there an easy way to see these?
-Why can't $I_1^V(q) = n-4$, which would make this the last row of $\mathcal{B}$} {\color{violet}From the figure we see that $I_{n-3}^V = n-3$.
+Why can't $I_1^V(q) = n-4$, which would make this the last row of $\mathcal{B}$}\note{This is a good point; what if that propagator $r$ went from edge $n-1$ to edge $n-5$?
+Karen, do you remember why this can't happen?} {\color{violet}From the figure we see that $I_{n-3}^V = n-3$.
 In particular, this means that $n-2 \not \in I_{n-3}^V$.

### 2019-09-09 GWLDCII.tex
adjusted the locally same remark

@@
 
-With this setup, if we can find a vertex $\ell$ occurring after both $i$ and $m$ such that the \emph{configuration} of propagators ending in the interval $[j-1, \ell+1]$ is identical in both $W'$ and $V'$, then the vertices contributed to $I_i^W$ and $I_m^V$ are the same from step $j$ to step $\ell$ (inclusive).
+With this setup, if we can find a vertex $\ell$ occurring after both $i$ and $m$ such that the \emph{configuration}\note{Why is configuration italicized?} of propagators ending in the interval $[j-1, \ell+1]$ is identical in both $W'$ and $V'$, then the vertices contributed to $I_i^W$ and $I_m^V$ are the same from step $j$ to step $\ell$ (inclusive).
 See Figure~\ref{fig:locally identical} for an illustration of this.
+
+Furthermore, if the propagators of $W'$ and $V'$ ending in the interval $[j-1, \ell+1]$ are also identically labelled, then $I_i^W$ and $I_m^V$ are the same as functions when restricted to those propagators.
 

### 2019-09-09 GWLDCII.tex
a few comments on comments

@@
 When the algorithm $I_{n-2}^W$ reaches vertex $n$, only the propagators $p$ and $q$ have contributed; thus we proceed as in the construction of $I_n^{V}$ but without propagator $q$ by Remark \ref{rmk algorithm locally same}.
-By Lemma~\ref{vertex cyclic int lem} we know that $I_n^V(q) = n-5$ \sanote{it would be nice if this were easier to read from lemma without digging through proof}, and from \st{the diagram }{\color{violet} Remark \ref{clockwise ordering rem} } we see that the only way this could occur is if $q$ was the last to contribute to $I_{n-2}^V$.
+By Lemma~\ref{vertex cyclic int lem} we know that $I_n^V(q) = n-5$ \sanote{it would be nice if this were easier to read from lemma without digging through proof}\note{The point is, at $n-2$ $q$ must contribute $n-2$ (because nothing else is supported on $n-2$), and so by the intervals being cyclic, nonempty, and never getting the last vertex, at $n-1$ (and identically at $n$ since $n-1$ doesn't support anything) $q$ contributes $n-5$.}, and from \st{the diagram }{\color{violet} Remark \ref{clockwise ordering rem} } we see that the only way this could occur is if $q$ was the last to contribute to $I_{n-2}^V$.
 %all other propagators in $V$ had already been assigned when we reached vertex $n-5$; thus $q$ was the final propagator contributing to $I_n^{V}$.
@@
 Let $V$ and $W$ be as in Lemma~\ref{lem I}.
-Then \hlfix{$I_n^{W}$}{Does $I_n^W$ actually yeild any of the $+$s in $I_n^V$?} and $I_{n-1}^{W}$ together yield the same plusses as $I_n^{V}$ did, along with two extra plusses which appear in the leftmost two boxes of the bottom row of the Le diagram of $W$.
+Then \hlfix{$I_n^{W}$}{Does $I_n^W$ actually yeild any of the $+$s in $I_n^V$?}\note{I don't remember, but the point is that this is a two way statement, $I_n^W$ nd $I_{n-1}^W$ yield \emph{exacly} the plusses yielded by $I_n^{V}$, and it doesn't really matter which come from $I_n^W$ and which from $I_{n-1}^W$} and $I_{n-1}^{W}$ together yield the same plusses as $I_n^{V}$ did, along with two extra plusses which appear in the leftmost two boxes of the bottom row of the Le diagram of $W$.
 \end{lem}
@@
 The dashed blue lines may or may not appear, but if one appears then they both do.}\label{fig messy}
-  \end{figure} \sanote{can we put the diagrams labels in bold or set them apart somehow so that it is easier to see? Esp since they are located in a different part of the diagram for $I_n^V$?}
+  \end{figure} \sanote{can we put the diagrams labels in bold or set them apart somehow so that it is easier to see?
+Esp since they are located in a different part of the diagram for $I_n^V$?}\note{That's going to come down to journal style in the end, so only do it if it is easy and you know how to do it by an appropriate option}
 

### 2019-09-09 GWLDCII.tex
changes from on the phone

@@
 While this has been proved by Marcott in \cite{WLDdim} using matroidal arguments, our proof is constructive and explicitly relates the position of the plusses in the Le diagram to the propagators in the Wilson loop diagram.
-{\color{violet} This proof and the methods used therein are a first step towards understanding how the positroid cell assocaited to a Wilson loop diagram changes as one adds propagators in certain positions.}
+This proof and the methods used therein are a first step towards understanding how the positroid cell associated to a Wilson loop diagram changes as one adds propagators in certain positions.
 
@@
 Furthemore, we use it to characterize loops and coloops in the positroid associated to a Wilson loop diagram (Corrollary \ref{no coloops}).
-\hlfix{It also allows us to examine how the positroid changes as we make minor changes to the Wilson loop diagram;}{what does this mean?} {\color{violet} It allows us to see how the Le diagram assoicated to a Wilson loop diagram changes as one adds propagators in certain positions (Theorem \ref{thm dim}).} Indeed, the techniques we develop in this section to verify that our algorithm produces the correct Grassmann necklace will also be used repeatedly in later sections {\color{violet} to calculate the dimension of the associated positroid cell (section \ref{sec dim}) and to study the structure of the poles of the associated integral $I(W)$ (section \ref{sec poles}).}
+It allows us to see how the Le diagram assoicated to a Wilson loop diagram changes as one adds propagators in certain positions (Theorem \ref{thm dim}).
+Indeed, the techniques we develop in this section to verify that our algorithm produces the correct Grassmann necklace will also be used repeatedly in later sections to calculate the dimension of the associated positroid cell (section \ref{sec dim}) and to study the structure of the poles of the associated integral $I(W)$ (section \ref{sec poles}).
 
@@
 
-If the algorithm assigns vertex $j$ to propagator $p$ from starting vertex $i$, we say that $p$ \emph{contributes} $j$ to $I_i^W$.
+If the algorithm assigns vertex $j$ to propagator $p$ from starting vertex $i$, we say that $p$ \textbf{contributes} $j$ to $I_i^W$.
 Notationally, we represent this by allowing the $I_i^W$ symbol to represent a function as well as a set, as follows:
@@
 
- \note{Remember to keep an eye out when proofreading: do we just need the vertices appearing in the GN element to be the same, or do we actually need the functions to match up} \sanote{need functions to match in 4.4}\note{That's ok though because this remark does give the function matching in that region.}
-
 Suppose we are going through the algorithm to construct $I_i^W$ for some $i$, and we are currently at step $j$ of the loop.
@@
 
-With this setup, if we can find a vertex $\ell$ occurring after both $i$ and $m$ such that the \emph{configuration}\note{Why is configuration italicized?} of propagators ending in the interval $[j-1, \ell+1]$ is identical in both $W'$ and $V'$, then the vertices contributed to $I_i^W$ and $I_m^V$ are the same from step $j$ to step $\ell$ (inclusive).
+With this setup, if we can find a vertex $\ell$ occurring after both $i$ and $m$ such that the \emph{configuration} of propagators ending in the interval $[j-1, \ell+1]$ is identical in both $W'$ and $V'$, then the vertices contributed to $I_i^W$ and $I_m^V$ are the same from step $j$ to step $\ell$ (inclusive).
 See Figure~\ref{fig:locally identical} for an illustration of this.
@@
 Suppose for contradiction that we have $i \in [n]$ and $p \in \cP$ such that $I_i(p)$ is $<_i$-maximal in $V(p)$.
-There are two possibilities, which are illustrated in Figure~\ref{fig:no fourth vertex}: \st{either $p = (i-1,b)$ for some $b$ (so $i$ and $I_i(p) = i-1$ are the two ends of a single edge), or $p = (a,b)$ with $i\leq_i a <_i b$ and $I_i(p) = b+1$.} {\color{violet}either $i-1 \in V(p)$, in which case it is the last vertex in the $<_i$ order and $I_i(p)= i-1$, or $i-1 \not \in V(p)$ in which case,  $p= a, b$, $i \in [b+2, a]$ and $I_i(p) = b+1$.}
+There are two possibilities, which are illustrated in Figure~\ref{fig:no fourth vertex}: either $p = (i-1,b)$ for some $b$ (so $i$ and $I_i(p) = i-1$ are the two ends of a single edge), or $p = (a,b)$ with $i\leq_i a <_i b$ and $I_i(p) = b+1$.
 
@@
 \end{figure}
-In Case 1, \st{observe that we must have another propagator $q = (c,b)$ with $c<_i b$ and $I_i(q) = b+1$, because otherwise $I_i$ would assign $p$ to $b+1$.}{\color{violet} since $b+1<_i I_i(p)$ there must be some propagator, $q$ before $p$ in $\cP^i$ such that $I_i(q) = b+1$.
-By remark \ref{clockwise ordering rem}, $p$ is inside $q$ in the $<_b$ order.
-Specifically, $q$ must also end on the $b^{th}$ edge.
-By non-crossing and desnity arguements of admissibility $i-1$ cannot be in $V(q)$.} Now $q$ also contributes the $<_i$-maximal vertex in its support to $I_i$ and is an instance of Case 2.
+In Case 1, observe that we must have another propagator $q = (c,b)$ with $c<_i b$ and $I_i(q) = b+1$, because otherwise $I_i$ would assign $p$ to $b+1$.
+Now $q$ also contributes the $<_i$-maximal vertex in its support to $I_i$ and is an instance of Case 2.
 Therefore it suffices to show that no admissible Wilson loop diagram admits the configuration illustrated in Case 2 of Figure~\ref{fig:no fourth vertex}.
@@
 We first calculate $I^{W}_w$ for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$.
-Note that $p$ has no effect on other propagators for starting vertices in this range \hlfix{(since $p$ will be the final propagator encountered by the algorithm)}{Sian added this: it's not really a locally-the-same argument so I'm not sure it'll help to reference Remark 3.12} so if $r \neq p$, then $I_w^W(r) = I_w^V(r)$.
+Note that $p$ has no effect on other propagators for starting vertices in this range (since $p$ will be the final propagator encountered by the algorithm) so if $r \neq p$, then $I_w^W(r) = I_w^V(r)$.
 Meanwhile, the value of $I^{W}_w(p)$ depends on which step in the algorithm the propagator $q$ contributes a vertex in the diagram $V$, i.e.
@@
 Thus we have shown that Algorithm \ref{alg:put GN on WLD} does in fact produce a Grassmann necklace. Next we check that it produces the correct one, i.e. the Grassmann necklace that defines $M(W)$. 
-\note{Sian made minor edits to this proof: mostly removing those two numbered observations because one is now a remark and the other is only used once}
 \begin{thm}\label{res alg gives correct GN}
@@
 Now repeat the argument above with $p_s$ in place of $p_r$: if the other end of $p_s$ lands on an edge between $q$ and $j_m$ then we have $q \in \cP_{m-1}$ as above; if not then there exists some $p_t \in Q_{l-3}$ with $p_s$ supported on $I_i(p_t)$ and $q$ on the inside of $p_t$ in the $a_t-1$ order.
-Therefore \hlfix{$I_i(p_t) <_i I_i(p_r)$}{$I_i(p_t) <_i I_i(p_s)<_i I_i(p_s)$?
-Or is the implication clear enough not to be mentioned}\note{Nope: we just need $<_i I_i(p_r)$.
-$I_i(p_t) <_i I_i(p_s)$ certainly isn't obvious and may not be true}.
-{\color{violet} May not be necessary, but I think highlighted tex follows from "Now repeat the argument...." \begin{enumerate}\item If $V(p_r) \in [a_r-1, j_m]$ (other end closer to $j_m$) then $q$ inside $p_r$ in $a_r-1$ order.
+Therefore $I_i(p_t) <_i I_i(p_r)$
+%{\color{violet} May not be necessary, but I think highlighted tex follows from "Now repeat the argument...." \begin{enumerate}\item If $V(p_r) \in [a_r-1, j_m]$ (other end closer to $j_m$) then $q$ inside $p_r$ in $a_r-1$ order.
 \item Else, $V(p_r) \in [i, a_r+1]$ (Maybe $[i-1, a_r +1]$?).
@@
 It may be totally unnecessary.
-But I want to make certain that I'm not missing anything.}  Since there are finitely many steps this process can take before reaching $Q_0$, and any $p_* \in Q_0  = \Prop(j_m)$ has $j_m$ in its support by definition, this argument eventually terminates with the construction of a propagator constraining the positioning of $q$ as required.
+But I want to make certain that I'm not missing anything.}
+Since there are finitely many steps this process can take before reaching $Q_0$, and any $p_* \in Q_0  = \Prop(j_m)$ has $j_m$ in its support by definition, this argument eventually terminates with the construction of a propagator constraining the positioning of $q$ as required.
 This completes the induction step, and hence the proof.\end{proof}
@@
 %\[|\cP| + \text{ the dimension of associated positroid cell}.\]
-\note{What if instead of displaying this we wrote ``is the sum of $\|\cP\|$ and the dimension fo the associated positroid cell.''}\sanote{implemented, but don't like how it no longer stands out.
-Thoughts?}
 In other words, the Deodhar component associated to a Wilson loop diagram is $4|\cP|$, showing that the geometry underlying the Wilson loop diagrams is consistent with the geometry underlying the Amplituhedron.
@@
 
-{\color{violet}More than just a dimensionality result, the lemmas below are a first step towards undertanding how the adding an extra propagator changes the associated positroid cell. }
+More than just a dimensionality result, the lemmas below are a first step towards undertanding how the adding an extra propagator changes the associated positroid cell.
 
@@
 We begin by relating non-supporting vertices to columns of zeros in the Le diagram (Lemma \ref{lem uncovered}) and verifying that performing dihedral transformations on a Wilson loop diagram does not change the dimension of of the associated Le diagram (Lemma \ref{lem dihedral}).
-
-\sanote{musing: would it be worth moving the LE diagram exposition here? Do we use it ealier? I like having exposition in front generally, but it feels a mile away.}
 
@@
 \begin{proof}
-  By Algorithm~\ref{alg:put GN on WLD} the Grassmann necklace of $W$ is obtained from the Grassmann necklace of $V$ by duplicating the $i$th element of the Grassmann necklace of $V$ (shifting indices by $1$ for all indices greater than $i$), and incrementing all indices greater than $i$ by $1$ in each Grassmann necklace element\note{This is saying to increment twice in a way which I think is confusing, but presumably the parenthetical remark was put there to try to clarify something so I don't want to just remove it}.
-Formally, \st{if $I_1^{V}, \ldots, I_{n-1}^{V}$ and $I_1^{W}, \ldots, I_n^{W}$ are the Grassmann necklaces of $V$ and $W$ respectively then}\sanote{in favor of removing parenthetical, we say same thing twice without it}
+  By Algorithm~\ref{alg:put GN on WLD} the Grassmann necklace of $W$ is obtained from the Grassmann necklace of $V$ by duplicating the $i$th element of the Grassmann necklace of $V$, and incrementing all indices greater than $i$ by $1$ in each Grassmann necklace element.
+Formally,
   \[
@@
 it must be a column label.
-The shapes of the Le diagram of $V$ and $W$ are the same except for the insertion of this column since $I_1^*$\note{I don't find the star very helpful here; different area's conventions maybe} is the same for $V$ and $W$ except for the incrementation of the indices $\geq i$ in the transition from the necklace for $V$ to the necklace for $W$.
+The shapes of the Le diagram of $V$ and $W$ are the same except for the insertion of this column since $I_1$ is the same for $V$ and $W$ except for the incrementation of the indices $\geq i$ in the transition from the necklace for $V$ to the necklace for $W$.
 \end{proof}
@@
   \begin{itemize}
-  \item $p = (i, n-1)$ for some $i$, and $p$ has no propagators inside it w.r.t the $<_i$ ordering \st{(that is $i+2, \ldots, n-2$ do not support any propagators in $W'$)}.
+  \item $p = (i, n-1)$ for some $i$, and $p$ has no propagators inside it w.r.t the $<_i$ ordering.
   \item Either the edge $i$ in $W'$ only supports $p$, or the edge $i$ in $W'$ supports exactly one other propagator $q = (j,i)$, with no other propagators inside $q$ in the $<_j$ ordering. 
@@
 Let $V$ be $W$ with $p$ removed.
-Then we can express $I_*^W$ in terms of $I_*^V$ as follows:\note{I'm not a fan of the case labels in this display: there's enough going on already without throwing in extra information}
+Then we can express $I_*^W$ in terms of $I_*^V$ as follows:
 
@@
     \begin{cases}
-      I_{n-2}^{V}\cup \{n-2\} & \text{if $n-2\not\in I_{n-2}^{V}$ (Case 1)} \\
+      I_{n-2}^{V}\cup \{n-2\} & \text{if $n-2\not\in I_{n-2}^{V}$} \\
       I_{n-2}^{V}\cup \{n-1\} & \text{if $n-2\in I_{n-2}^{V}$, $n-1\not\in I_{n-2}^{V}$} \\
@@
     \begin{cases}
-      I_k^{V}\cup \{n-3\} & \qquad \qquad \qquad \qquad \text{if $n-3 \not\in I_k^{V}$ (Case 1)}\\
-      I_k^{V}\cup\{n-2\} & \qquad \qquad \qquad \qquad \text{if $n-3\in I_k^{V}$ (Case 2)}
+      I_k^{V}\cup \{n-3\} & \qquad \qquad \qquad \qquad \text{if $n-3 \not\in I_k^{V}$}\\
+      I_k^{V}\cup\{n-2\} & \qquad \qquad \qquad \qquad \text{if $n-3\in I_k^{V}$}
     \end{cases} \\
@@
 \end{lem}
-
-The two possible cases for $W$ are illustrated in Figure~\ref{fig special p}.
 
@@
 
-\end{figure} \sanote{moved figure before theorem 4.4 so that we can just refer to generically}
+\end{figure}
+
 \begin{proof}
-
-We first consider $I_1^{W}$, i.e.
-the set obtained by applying the Grassmann necklace algorithm to $W$ with starting vertex 1\note{I don't find this i.e.
-helpful at this point, is it an old thing that can go or do others find it useful?} \sanote{agreed, i vote to cut}.
+The two possible cases for $W$ are illustrated in Figure~\ref{fig special p}.
+
+We first consider $I_1^{W}$.
 Note that $n-3 \not\in I_1^{V}$: \hlfix{for Case 2 this is clear from the diagram (since Algorithm {\ref{alg:put GN on WLD}} would force $q$ to contribute no later than vertex $n-4$),}{why?

### 2019-09-12 GWLDCII.tex
minor fixes

@@
 
+\begin{figure}
+\[
+\begin{tikzpicture}[rotate = 150,baseline=(current bounding box.east),label distance = -2mm]
+\begin{scope}
+  \drawWLDfragment[6]{3}{0.3}
+  %\drawnumbers % use this to debug
+  \begin{scope}
+    \clipcenterarc(0,0)(\startpoint:\endpoint:\radius)
+    \draw[smallpropagator] (\zero+2.4*\step:\radius*1.1) to [bend left = 55] (\zero + 4.6*\step:\radius*1.1); 
+    \node at (\zero + 3.5*\step:\radius*0.75){\footnotesize $p$};
+  \end{scope}
+  \centerarc[red,line width = 2pt,line cap = round](0,0)(\zero + 2*\step:\zero+4.45*\step:\radius)
+  \newbetternode[{[label distance=-3mm]above right}]{1}{n-4}
+  \newbetternode[{[label distance=-3mm]above right}]{2}{n-3}
+  \newbetternode[{[label distance=-3mm]above right}]{3}{n-2}
+  \newbetternode[{[label distance=-3mm]above right}]{4}{n-1}
+  \newnode[above]{5}{n}
+  \newnode[above]{6}{1}
+  \node at (180-60:\radius*0.1){\em Case 1};
+\end{scope}
+\end{tikzpicture}
+\qquad 
+\qquad 
+\begin{tikzpicture}[rotate=150, baseline=(current bounding box.east)]
+\begin{scope}
+  \drawWLDfragment[7]{3}{0.3}
+  %\drawnumbers % use this to debug
+  \begin{scope}
+    \clipcenterarc(0,0)(\startpoint:\endpoint:\radius)
+    \draw[smallpropagator] (\zero+1.4*\step:\radius*1.1) to [bend left = 60] (\zero + 3.5*\step:\radius*1.1); 
+    \draw[smallpropagator] (\zero+3.5*\step:\radius*1.1) to [bend left = 60] (\zero + 5.6*\step:\radius*1.1); 
+    \node at (\zero + 2.4*\step:\radius*0.8){\footnotesize $q$};
+    \node at (\zero + 4.5*\step:\radius*0.8){\footnotesize $p$};
+  \end{scope}
+  \centerarc[red,line width = 2pt,line cap = round](0,0)(\zero + 1.6*\step:\zero+5.5*\step:\radius)
+  \newbetternode[{[label distance=-3mm]above right}]{1}{n-5}
+  \newbetternode[{[label distance=-3mm]above right}]{2}{n-4}
+  \newbetternode[{[label distance=-3mm]above right}]{3}{n-3}
+  \newbetternode[{[label distance=-3mm]above right}]{4}{n-2}
+  \newbetternode[{[label distance=-3mm]above right}]{5}{n-1}
+  \newnode[above]{6}{n}
+  \newnode[above]{7}{1}
+  \node at (180-60:\radius*0.1){\em Case 2};
+\end{scope}
+\end{tikzpicture}
+\] 
+  \caption{The two cases for $W$ and $p$.  No other propagators can end in the red sections.  Other segments may have additional propagators ending in them.}\label{fig special p}
+
+\end{figure}
+
 \begin{lem}\label{lem I}
@@
       I_{n-2}^{V}\cup \{n-1\} & \text{if $n-2\in I_{n-2}^{V}$, $n-1\not\in I_{n-2}^{V}$} \\
-      (I_{n}^{V} - \{n-5\})\cup \{n-1,n-2\} & \text{if $n-1, n-2\in I_{n-2}^{V}$}
+      (I_{n}^{V} \setminus \{n-5\})\cup \{n-1,n-2\} & \text{if $n-1, n-2\in I_{n-2}^{V}$}
     \end{cases} \\
@@
 
-\begin{figure}
-\[
-\begin{tikzpicture}[rotate = 150,baseline=(current bounding box.east),label distance = -2mm]
-\begin{scope}
-	\drawWLDfragment[6]{3}{0.3}
-	%\drawnumbers % use this to debug
-	\begin{scope}
-		\clipcenterarc(0,0)(\startpoint:\endpoint:\radius)
-		\draw[smallpropagator] (\zero+2.4*\step:\radius*1.1) to [bend left = 55] (\zero + 4.6*\step:\radius*1.1); 
-		\node at (\zero + 3.5*\step:\radius*0.75){\footnotesize $p$};
-	\end{scope}
-	\centerarc[red,line width = 2pt,line cap = round](0,0)(\zero + 2*\step:\zero+4.45*\step:\radius)
-	\newbetternode[{[label distance=-3mm]above right}]{1}{n-4}
-	\newbetternode[{[label distance=-3mm]above right}]{2}{n-3}
-	\newbetternode[{[label distance=-3mm]above right}]{3}{n-2}
-	\newbetternode[{[label distance=-3mm]above right}]{4}{n-1}
-	\newnode[above]{5}{n}
-	\newnode[above]{6}{1}
-	\node at (180-60:\radius*0.1){\em Case 1};
-\end{scope}
-\end{tikzpicture}
-\qquad 
-\qquad 
-\begin{tikzpicture}[rotate=150, baseline=(current bounding box.east)]
-\begin{scope}
-	\drawWLDfragment[7]{3}{0.3}
-	%\drawnumbers % use this to debug
-	\begin{scope}
-		\clipcenterarc(0,0)(\startpoint:\endpoint:\radius)
-		\draw[smallpropagator] (\zero+1.4*\step:\radius*1.1) to [bend left = 60] (\zero + 3.5*\step:\radius*1.1); 
-		\draw[smallpropagator] (\zero+3.5*\step:\radius*1.1) to [bend left = 60] (\zero + 5.6*\step:\radius*1.1); 
-		\node at (\zero + 2.4*\step:\radius*0.8){\footnotesize $q$};
-		\node at (\zero + 4.5*\step:\radius*0.8){\footnotesize $p$};
-	\end{scope}
-	\centerarc[red,line width = 2pt,line cap = round](0,0)(\zero + 1.6*\step:\zero+5.5*\step:\radius)
-	\newbetternode[{[label distance=-3mm]above right}]{1}{n-5}
-	\newbetternode[{[label distance=-3mm]above right}]{2}{n-4}
-	\newbetternode[{[label distance=-3mm]above right}]{3}{n-3}
-	\newbetternode[{[label distance=-3mm]above right}]{4}{n-2}
-	\newbetternode[{[label distance=-3mm]above right}]{5}{n-1}
-	\newnode[above]{6}{n}
-	\newnode[above]{7}{1}
-	\node at (180-60:\radius*0.1){\em Case 2};
-\end{scope}
-\end{tikzpicture}
-\] 
-  \caption{The two cases for $W$ and $p$.  No other propagators can end in the red sections.  Other segments may have additional propagators ending in them.}\label{fig special p}
-
-\end{figure}
-
 \begin{proof}
@@
 
-We first consider $I_1^{W}$.
-Note that $n-3 \not\in I_1^{V}$: \hlfix{for Case 2 this is clear from the diagram (since Algorithm {\ref{alg:put GN on WLD}} would force $q$ to contribute no later than vertex $n-4$),}{why?
-isn't obvious to me without several cases, and even then}\note{yeah, I can't see this either; cyclic intervals is probably a better argument} while for Case 1 it follows directly from Lemma \ref{lem no fourth vertex}.
-Therefore when we start at vertex 1 and apply the Grassmann necklace algorithm to $W$, $p$ is the \st{only remaining unassigned propagator when we reach vertex $n-3$}{\color{violet}last propagator to contribute}, and so we have $ I_1^{W}(p) = n-3$ and $I_1^W = I_1^V\cup \{n-3\}$.
+\note{Following two paragraphs added to replace the sentence ``clearly $n-3 \not\in I_1^V$''}
+We first show that $n-3 \not\in I_1^V$.
+In Case 1, the only way we could have $n-3 \in I_1^V$ is if $V$ admits some propagator $r$ with $I_1(r) = n-3$; from the figure, one end of $r$ would have to lie on edge $n-4$, and by Lemma~\ref{lem no fourth vertex} the other end would have to lie on edge $n-1$ or $n$.
+However, if $r = (n-4,n-1)$ then by [remark following cyclic intervals lemma] we would have $I_1^V(r) = n-4$, while if $r = (n-4,n)$ then $r$ is the clockwise-most propagator supported on vertex 1 and we would have $I_1^V(r) = 1$.
+Either way, we have $I_1^V(r) \neq n-3$.
+
+In Case 2 the only propagator supported on vertex $n-3$ in $V$ is $q$, and by [cyclic intervals remark] we have $I_{n-1}^V(q) = n-5$.
+Further, it must also be the case that $I_n^V(q) = n - 5$: if $n-1$ is non-supporting in $V$ then this is immediate, while if there exists a propagator $r$ in $V$ with $I_{n-1}^V(r) = n-1$ then $r$ lies on edge $n-1$ and is the clockwise-most propagator supported on vertex $n$, so $I_n^V(r) = n$ and the remainder of $I_n^V$ proceeds identically to $I_{n-1}^V$.
+Thus $I_n^V(q) = n-5$, so by [cyclic intervals lemma or remark] we have $I_1^V(q) \in \{n-5,n-4\}$; in particular, $I_1^V(q)\neq n-3$.
+
+We note for future reference that the arguments of the previous two paragraphs also imply that $n-2,n-1,n \not\in I_1^V$.
+
+We can now describe $I_1^W$ in terms of $I_1^V$: when we start at vertex 1 in $W$ and apply the Grassmann necklace algorithm, $p$ is the \st{only remaining unassigned propagator when we reach vertex $n-3$}{\color{violet}last propagator to contribute}, and so we have $ I_1^{W}(p) = n-3$ and $I_1^W = I_1^V\cup \{n-3\}$.
 
@@
 
-\note{When doing the final formatting, try to ensure that Figure \ref{fig Le} and Lemma \ref{lem shape} are on the same page}
 \begin{lem}\label{lem shape}
@@
 \[I_{n-1}^W \setminus I_1^W = (I_n^V \setminus I_1^V) \cup \{n-1\} \subseteq \{n-1,n\},\]
-where the final inclusion follows from the definition of Grassmann necklace\sanote{why only $\{n-1,n\}$?
-I'd believe an inclusion the other way}\note{Definition of GN: $I_1 = (I_n\setminus\{n\})\cup\{\text{something}\}$}.
+where the final inclusion follows from the definition of Grassmann necklace.
+\sanote{why only $\{n-1,n\}$? I'd believe an inclusion the other way}
+\note{Definition of GN: $I_1 = (I_n\setminus\{n\})\cup\{\text{something}\}$}
 In particular, $n-1$ is minimal in this set, so Algorithm~\ref{alg:GN to Le} yields a plus in the $(n-3) \rightarrow (n-1)$ position (i.e.
 the second box in the bottom row of the Le diagram of $W$) \hlfix{along with any plusses yielded by $I_n^V$.}{display seems to imply that there is exactly one such other $+$.
-Is this correct?}\note{Display implies there's at most one, but if we apply no coloops I think that becomes exactly one.}
+Is this correct?}\note{If $n$ is non-supporting then $I_n^V \setminus I_1^V = \emptyset$ and we only get the $(n-3) \rightarrow (n-1)$ plus.}
 \end{proof}
@@
 The columns are labeled from left to right by $n, \ldots, i+1$.
-By Algorithm~\ref{alg:GN to Le} there are plusses in the $i+1$, $j$, and $j_1$ positions.
+By Algorithm~\ref{alg:GN to Le} there are plusses in the $i+1$, $j$, and $j+1$ positions.
 \sanote{changed for grammar and notational consistency.
@@
 By Lemma~\ref{lem dihedral} it suffices to prove the result for at least one Wilson loop diagram from each dihedral orbit.
-In particular, consider $W$, which after possible dihedral transformation, has a propagator $p$ with the properties in Lemma~\ref{lem good p}.
-
-  We make one further simplification: if our $W$ is in Case 2 of Figure~\ref{fig special p} and $n-1$ supports only $p$ but $n-2$ supports at least one other propagator\sanote{??
-see para below}, then flip $W$ on the line perpendicular to the $(n-2){th}$ edge to obtain a diagram with the configuration of Case 1.
-This eliminates the possibility that we could have $n-2 \in I_{n-2}^W$ but $n-1 \not\in I_{n-2}^W$.
-
+In particular, we can restrict our attention to diagrams $W$ which have a propagator $p$ with the properties in Lemma~\ref{lem good p}.
+
+We make one further simplification in order to eliminate the possibility that $n-2 \in I_{n-2}^V$ but $n-1 \not\in I_{n-2}^V$, which can only occur if our $W$ is in Case 2 of Figure~\ref{fig special p} and $n-1$ supports no propagators other than $p$.
+In this situation, flip $W$ on the line perpendicular to the $(n-2){th}$ edge to obtain a diagram with the configuration of Case 1.
+
+\note{Sian rewrote above paragraph because their original version was wrong in multiple ways. Better?}
 {\color{violet} I'm very confused about the previous paragraph.

### 2019-09-13 GWLDCII.tex
removed and added some commments

@@
 \end{lem} 
-\sanote{wanted to rewrite this lemma to emphasize the fact that we are using the same properties of Alg 3.7 over and over again, and have these principals set apart in a remark}
 \begin{proof}
@@
 In Case 1, the only way we could have $n-3 \in I_1^V$ is if $V$ admits some propagator $r$ with $I_1(r) = n-3$; from the figure, one end of $r$ would have to lie on edge $n-4$, and by Lemma~\ref{lem no fourth vertex} the other end would have to lie on edge $n-1$ or $n$.
-However, if $r = (n-4,n-1)$ then by [remark following cyclic intervals lemma] we would have $I_1^V(r) = n-4$, while if $r = (n-4,n)$ then $r$ is the clockwise-most propagator supported on vertex 1 and we would have $I_1^V(r) = 1$.
+However, if $r = (n-4,n-1)$ then by [remark following cyclic intervals lemma] \hlfix{we would have $I_1^V(r) = n-4$}{because if it contributed $n-3$ it would never be able to contribute $n-4$?}, while if $r = (n-4,n)$ then $r$ is the clockwise-most propagator supported on vertex 1 and we would have $I_1^V(r) = 1$.
 Either way, we have $I_1^V(r) \neq n-3$.
 
-In Case 2 the only propagator supported on vertex $n-3$ in $V$ is $q$, and by [cyclic intervals remark] we have $I_{n-1}^V(q) = n-5$.
+In Case 2 the only propagator supported on vertex $n-3$ in $V$ is $q$, and by [cyclic intervals remark] we \hlfix{have $I_{n-1}^V(q) = n-5$}{Because $I_{n-2}^V(q) = n-2$ and Lemma \ref{lem no vourht vertex} prevents $I_{n-1}^V(q) = n-2$?}.
 Further, it must also be the case that $I_n^V(q) = n - 5$: if $n-1$ is non-supporting in $V$ then this is immediate, while if there exists a propagator $r$ in $V$ with $I_{n-1}^V(r) = n-1$ then $r$ lies on edge $n-1$ and is the clockwise-most propagator supported on vertex $n$, so $I_n^V(r) = n$ and the remainder of $I_n^V$ proceeds identically to $I_{n-1}^V$.

### 2019-09-13 GWLDCII.tex
made the small changes I was asked to

@@
 \end{lem}
+
+\begin{rmk}\label{rmk cyclic}
+  Before the proof, let us observe that one of the main ways that the above lemma will be used is in observations like the following.
+Suppose $p=(i,j)$ is a propagator and $I_{j+1}(p) = j+1$.
+Consider $I_{j+2}(p)$.
+Since $j+1$ is the last vertex in the $j+2$ order, $p$ can not contribute $j+1$ to $I_{j+2}$.
+But the the fact that the invervals of the lemma are nonempty and occur in their cyclic order implies that $I_{j+2}(p)=i$.
+More generally, whenever we know that a propagator stops contributing a particular vertex, then we know that it must contribute its cyclically next vertex.
+This little observation is surprisingly useful, to the point that the details which appear in the proof of Lemma~\ref{vertex cyclic int lem} are never needed again, the mere fact of non-empty intervals in the correct order suffices.
+\end{rmk}
+
+Now we proceed to the proof of Lemma~\ref{vertex cyclic int lem}.
 
@@
 
-The next few lemmas describe how the Grassmann necklaces (Lemma \ref{lem I}) and the Le diagrams (Lemmas \ref{lem shape} to Lemma \ref{lem other k}) of Wilson loop diagrams of this type are related to the corresponding Wilson loop diagram with propagator $p$ removed.
-\sanote{rephrased, still clear?}
+With the above restrictions in place, the next few lemmas describe how the Grassmann necklaces (Lemma \ref{lem I}) and the Le diagrams (Lemmas \ref{lem shape} to Lemma \ref{lem other k}) change upon the removal of $p$ from the Wilson loop diagram.
+This gives us the inductive lever we need to prove the main theorem (Theorem \ref{thm dim}).
 

### 2019-09-13 GWLDCII.tex
a comment on a comment

@@
 
-\note{Following two paragraphs added to replace the sentence ``clearly $n-3 \not\in I_1^V$''}
+\note{Following two paragraphs added to replace the sentence ``clearly $n-3 \not\in I_1^V$''}\note{No, the argument is much simpler, by cyclic intervals $I_{1}^W(p) = n-3$, but $p$ is the last thing that can contribute at $n-3$, so for this to happen we must have $n-3\not\in I_1^V$.}
 We first show that $n-3 \not\in I_1^V$.

### 2019-09-13 GWLDCII.tex
changed discussed on the phone

@@
 
-We can now describe $I_1^W$ in terms of $I_1^V$: when we start at vertex 1 in $W$ and apply the Grassmann necklace algorithm, $p$ is the \st{only remaining unassigned propagator when we reach vertex $n-3$}{\color{violet}last propagator to contribute}, and so we have $ I_1^{W}(p) = n-3$ and $I_1^W = I_1^V\cup \{n-3\}$.
+We can now describe $I_1^W$ in terms of $I_1^V$: when we start at vertex 1 in $W$ and apply the Grassmann necklace algorithm, $p$ is the only remaining unassigned propagator when we reach vertex $n-3$, and so we have $ I_1^{W}(p) = n-3$ and $I_1^W = I_1^V\cup \{n-3\}$.
 
@@
 From the figure we see that in both cases we have $I_n^{W}(p) = n$.
-\hlfix{Therefore, the second through $k^{th}$ propagators contributing to $I_n^W$ are the same as the ordering in $I_n^V$.
-Since $n$ is non-supporting in $V$, $I_1^V = I_n^V$, we have $I_n^{W} = I_1^{V} \cup \{n\}$}{Alt.
-argument.
-Can ignore.} At vertex 1 of the algorithm $I_n$, the unassigned propagators are exactly those that appear in $V$.
+At vertex 1 of the algorithm $I_n$, the unassigned propagators are exactly those that appear in $V$.
 Therefore the algorithm continues as in $I_1^{V}$ (recall Remark~\ref{rmk algorithm locally same} about locally identical propagator configurations), i.e.
@@
 Now consider $I_{n-2}^{W}$.
-If $n-2\not\in I_{n-2}^{V}$ \hlfix{by Corrollary {\ref{no coloops}}  $n-2$ is non-supporting in $V$.
-Thus we are in Case 1, with ${I_{n-2}^W(p) = n-2}$.
-By the arguments above ${I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-2\}}$}{Alt.
-Argument.
-Can ignore} (i.e.
-the vertex $n-2$ supports no propagators in $V$), then ${I_{n-2}^W(p) = n-2}$ and this assignment of $p$ does not affect the rest of the construction of $I_{n-2}^{V}$, so we obtain ${I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-2\}}$ as above.
-
-On the other hand, if $n-2\in I_{n-2}^{V}$ then we must be in Case 2 of Figure~\ref{fig special p} and $I_{n-2}^V(q) = I_{n-2}^W(q) = n-2$ \st{(since $q$ is always the clockwise-most propagator supported on vertex $n-2$; see Figure {\ref{fig special p}})}.
+If $n-2\not\in I_{n-2}^{V}$ then the vertex $n-2$ is non-supporting (see also Corrollary~\ref{no coloops}.)  Thus we are in Case 1, with ${I_{n-2}^W(p) = n-2}$ and this assignment of $p$ does not affect the rest of the construction of $I_{n-2}^{V}$, so we obtain ${I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-2\}}$ as above.
+
+On the other hand, if $n-2\in I_{n-2}^{V}$ then we must be in Case 2 of Figure~\ref{fig special p} and $I_{n-2}^V(q) = I_{n-2}^W(q) = n-2$ (since $q$ is always the clockwise-most propagator supported on vertex $n-2$.
 If $n-1 \not\in I_{n-2}^{V}$, then $I_{n-2}^W(p) = n-1$ and then the algorithm proceeds identically to $I_{n-2}^{V}$ for the remainder of its steps; thus $I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-1\}$ in this case.
 
-Finally, if $n-2,n-1 \in I_{n-2}^{V}$ then $I_{n-2}^W(q) = n-2$ and $I_{n-2}^W(p) = n-1$ as above, but \st{this is different to what occured in $I_{n-2}^{V}$}{\color{violet}but some other propagator must contribute $n-1$ to $I_{n-2}^{V}$} so we cannot use the same argument as above.
+Finally, if $n-2,n-1 \in I_{n-2}^{V}$ then $I_{n-2}^W(q) = n-2$ and $I_{n-2}^W(p) = n-1$ as above, but but some other propagator must have contributed $n-1$ to $I_{n-2}^{V}$ so we cannot use the same argument as above.
 When the algorithm $I_{n-2}^W$ reaches vertex $n$, only the propagators $p$ and $q$ have contributed; thus we proceed as in the construction of $I_n^{V}$ but without propagator $q$ by Remark \ref{rmk algorithm locally same}.
-By Lemma~\ref{vertex cyclic int lem} we know that $I_n^V(q) = n-5$ \sanote{it would be nice if this were easier to read from lemma without digging through proof}\note{The point is, at $n-2$ $q$ must contribute $n-2$ (because nothing else is supported on $n-2$), and so by the intervals being cyclic, nonempty, and never getting the last vertex, at $n-1$ (and identically at $n$ since $n-1$ doesn't support anything) $q$ contributes $n-5$.}, and from \st{the diagram }{\color{violet} Remark \ref{clockwise ordering rem} } we see that the only way this could occur is if $q$ was the last to contribute to $I_{n-2}^V$.
+By Lemma~\ref{vertex cyclic int lem} we know that $I_n^V(q) = n-5$, and from Remark \ref{clockwise ordering rem} we see that the only way this could occur is if $q$ was the last to contribute to $I_{n-2}^V$.
 %all other propagators in $V$ had already been assigned when we reached vertex $n-5$; thus $q$ was the final propagator contributing to $I_n^{V}$.
@@
 Recall that $I_1$ determines the shape of the Le diagram: specifically, the elements of $I_1$ label the rows of the diagram, working from top right to bottom left.
-By the arguments in Lemma {\ref{lem I}} we know that \st{${n,n-1,n-2, n-3 \not\in I_1^{V}}$}\sanote{Only see $n-3$ in Lemma 4.4?} \note{well yeah, that's why it says ``the arguments in Lemma 4.4'': we show that all props are assigned before $n-3$ in $I_1$.
-I think spelling it out in detail here is more confusing than not.}{\color{violet} $ n-3 \not\in I_1^{V}$.
-By Lemma \ref{lem no fourth vertex}, $n, n-2 \not \in I_1^V$.
-Since $n-1$ is non-supporting in $V$, by Corrollary {\ref{no coloops}}, $n \not\in I_1^{V}$.} These are the leftmost four columns of the diagram for $V$.
+By the arguments in Lemma {\ref{lem I}} we know that ${n,n-1,n-2, n-3 \not\in I_1^{V}}$.
+These are the leftmost four columns of the diagram for $V$.
 From Lemma \ref{lem I} we know that that $I_1^{W} = I_1^{V}\cup \{n-3\}$.
@@
 
-Also by Lemma~\ref{lem I} we have $I_{n-1}^{W} = I_n^{V} \cup \{n-1\}$.
-Recall from the proof of Lemma \st{{\ref{lem I}}} {\color{violet} {\ref{lem shape}} }\sanote{change back if actually in 4.4} that $n-3,n-2,n-1,n \not\in I_1^V$; therefore $I_1^W\setminus I_{n-1}^W = (I_1^V \setminus I_n^V) \cup\{n-3\}$, and $n-3$ is maximal in this set.
-Similarly,
-\[I_{n-1}^W \setminus I_1^W = (I_n^V \setminus I_1^V) \cup \{n-1\} \subseteq \{n-1,n\},\]
-where the final inclusion follows from the definition of Grassmann necklace.
-\sanote{why only $\{n-1,n\}$? I'd believe an inclusion the other way}
-\note{Definition of GN: $I_1 = (I_n\setminus\{n\})\cup\{\text{something}\}$}
-In particular, $n-1$ is minimal in this set, so Algorithm~\ref{alg:GN to Le} yields a plus in the $(n-3) \rightarrow (n-1)$ position (i.e.
-the second box in the bottom row of the Le diagram of $W$) \hlfix{along with any plusses yielded by $I_n^V$.}{display seems to imply that there is exactly one such other $+$.
-Is this correct?}\note{If $n$ is non-supporting then $I_n^V \setminus I_1^V = \emptyset$ and we only get the $(n-3) \rightarrow (n-1)$ plus.}
+Also by Lemma~\ref{lem I} we have $I_{n-1}^{W} = I_n^{V} \cup \{n-1\}$. Recall from the proof of Lemma~\ref{lem I} that $n-3,n-2,n-1,n \not\in I_1^V$; therefore
+\[
+I_1^W\setminus I_{n-1}^W = (I_1^V \setminus I_n^V) \cup\{n-3\},
+\]
+and $n-3$ is maximal in this set. Similarly, 
+\[I_{n-1}^W \setminus I_1^W = (I_n^V \setminus I_1^V) \cup \{n-1\}.
+\]
+Also $(I_n^V \setminus I_1^V) \cup \{n-1\}\subseteq \{n-1,n\}$ from the definition of Grassmann necklace and so in particular, $n-1$ is minimal in this set, so Algorithm~\ref{alg:GN to Le} yields a plus in the $(n-3) \rightarrow (n-1)$ position (i.e.
+the second box in the bottom row of the Le diagram of $W$) along with any plusses yielded by $I_n^V$.
 \end{proof}
@@
 Note that $n-3\not\in I_{n-2}^{V}$ by Lemma~\ref{lem no fourth vertex}.
-Therefore the \st{paths controlling the} plusses contributed by $I_{n-2}^{W}$ are exactly the \st{paths for}{\color{violet} plusses from}\sanote{isn't this from Alg.\ref{alg:GN to Le} which says nothing about paths?} \note{see bolded stuff before previous lemma} $I_{n-1}^{V}$ along with the $(n-3)\rightarrow (n-2)$ path.
+Therefore the plusses contributed by $I_{n-2}^{W}$ are exactly the  plusses from $I_{n-1}^{V}$ along with the $(n-3)\rightarrow (n-2)$ plus.
 This gives the statement of the lemma.

### 2019-09-16 GWLDCII.tex
roughed out the proof for n-4 in the problem place

@@
   \begin{enumerate}
-  \item $I_{n-2}^W$ contributes an $(n-3)\rightarrow (n-2)$ plus and an $(n-5)\rightarrow (n-1)$ plus, along with any plusses contributed by $I_n^V$. 
+  \item $I_{n-2}^W$ contributes an $(n-3)\rightarrow (n-2)$ plus and an $(n-5)\rightarrow (n-1)$ plus, along with any plusses contributed by $I_n^V$.\note{This is correct if $n-4\not\in I_1^V\setminus I_n^V$.
+In the case that $n-4\in I_1^V\setminus I_n^V$ then $I_{n-2}$ contributes an $(n-3)\rightarrow (n-2)$ plus, an $(n-4)\rightarrow (n-1)$ plus and a $(n-5)\rightarrow (n)$ plus while $I_n^V$ contributed an $(n-4)\rightarrow (n)$ plus.}
   \item $I_{n-3}^W$ contributes the same plusses as $I_{n-3}^V$, except that the plus in the $n-3$ column (which necessarily exists) is shifted one square left into the $n-2$ column.
   \item In the Le diagram of $V$, $I_{n-2}^{V}$ contributes an $(n-5)\rightarrow (n-2)$ plus and no other term in the Grassmann necklace of $V$ gives a plus in this column.
-$I_{n-2}^W$ does not contribute this $+$ but yields the $(n-5)\rightarrow (n-1)$ plus from point (1) instead.
-  \item All other plusses from $I_{n-2}^{V}$ and all plusses from $I_{n-1}^V$ were already contributed by $I_{n-3}^V$, so they yield no new information.
-  \item No element of the Grassmann necklace of $V$ contributes a $(n-5)\rightarrow (n-1)$ plus.
+$I_{n-2}^W$ does not contribute this $+$ but yields the $(n-5)\rightarrow (n-1)$ plus from point (1) instead.\note{This is correct if $n-4\not\in I_1^V\setminus I_n^V$.
+In the case that $n-4\in I_1^V\setminus I_n^V$ then $I_{n-2}^V$ gives an $(n-4)\rightarrow (n-2)$ plus, and the part about nothing else in the $n-2$ column remains true.}
+  \item All other plusses from $I_{n-2}^{V}$ and all plusses from $I_{n-1}^V$ were already contributed by $I_{n-3}^V$, so they yield no new information.\note{With  the previous part corrected as above, this part is true unchanged.}
+  \item No element of the Grassmann necklace of $V$ contributes a $(n-5)\rightarrow (n-1)$ plus.\note{This should say ``The Grassman necklace of $V$ contributes a $(n-5)\rightarrow (n-1)$ plus if and only if $n-4 in I_1^V\setminus I_n^V$.}
   \end{enumerate} 
 \end{lem}
+
+\begin{proof}
+  This is Karen's rewritten proof notes (because I can't read the proof below any more and we need to sort out the case when $I^V_1(q)=n-4$.)  Let's go through them item by item, checking that the statements are correct and giving fresh proofs.
+
+  First note that by Lemma~\ref{lem I} $I_1^W = I_1^V\cup \{n-3\}$.
+
+  \begin{enumerate}
+  \item The statement needs to change as noted above.
+Here is how a proof of the first statement goes:  Note that $n-5\in I_1^V$.
+This is because when you get to $n-5$, $q$ isn't taken yet, so either $q$ contributes $n-5$ or something else does (in which case $q$ contributes $n-4$), so in either case $n-5 \in I_1^V$.
+Also note that $n-1, n-2, n-3\not\in I_n^V$ (this must have been said before because it is in the shape of the Le diagram).
+This together with Lemma~\ref{lem I} gives
+    \[
+    I_1^W \setminus I_{n-2}^W = (I_1^V\cup\{n-3\}) \setminus ((I_n^V\setminus \{n-3\})\cup \{n-1, n-2\}) = (I_1^V\setminus I_n^V) \cup \{n-3, n-5\}.
+    \]
+    Since we also have $n-1, n-2\not\in I_1^V$ we get
+    \[
+    I_{n-2}^W \setminus I_1^W = ((I_n^V\setminus \{n-3\})\cup \{n-1, n-2\}) \setminus(I_1^V\cup\{n-3\}) = (I_n^V\setminus I_1^V) \cup \{n-1, n-2\}.
+    \]
+    The statement follows from the above if $n-4\not\in I_1^V\setminus I_{n}^V$ as the path from $I_n^V$ (if any) lies above all paths between $\{n-3, n-5\}$ and $\{n-2, n-1\}$, so we just take the noncrossing paths to get the statement.
+
+    Now suppose $n-4\in I_1^V\setminus I_{n}^V$.
+Then want three noncrossing paths starting from $\{n-3, n-4, n-5\}$, and hence by necessity of shape, going to $\{n, n-1, n-2\}$.
+Comparing this to the above we see that $I_n^V$ contributed the plus from the path $(n-4)\rightarrow (n)$, while $I_{n-2}^W$ contributes the plusses $(n-3)\rightarrow (n-2)$, $(n-4)\rightarrow (n-1)$ and $(n-5)\rightarrow (n)$.
+\item The statement of this point does not need changing.
+By Lemma~\ref{lem I} we have that $I_{n-3}^W = I_{n-3}^V \cup \{n-2\}$ (since $n-3\in I_{n-3}^V$ as something (namely $q$) is supported at $n-3$ in $V$.
+So removing $I_{n-3}^W$ from $I_{1}^W$  is the same as removing $I_{n-3}^V$ from $I_1^V$ and removing $I_1^W$ from $I_{n-3}^W$ does the same as removing $I_{1}^V$ from $I_{n-3}^V$ except that the $n-3$ gets replaced by $n-2$.
+\item
+
+  Now let's look at \eqref{eq necklace} from the old proof.
+The first two transitions are true by cyclic intervals.
+The third transition is true by the fact that $n-1\in I_{n-2}^V$ by hypothesis.
+The ``something'' could be $n$ or some element of $I_1^V$.
+However, this ``something'' cannot be $n-4$ because the only thing that could contribute $n-4$ is $q$ but if $I_n^V(q)=n-4$ then the equation for $I_{n-2}^W$ from Lemma~\ref{lem I} would tell us that $n-4\in I_{n-2}^W$ but this is impossible as $I_{n-2}^W(q)=n-2$ but no other propagator than $q$ can contribute $n-4$.
+Then in the last transition of \eqref{eq necklace} either nothing happens (of $n$ is non-supporting in $V$) or by general GN stuff, the transition happens as described in the equation.
+The second ``something'', if it exists, could be $n-4$, or it could be some other element of $I_1^V$.
+(Maybe there's a reason I've forgotten that $n$ must be supporing in $V$, but it doesn't matter in the end as we'll see soon.)
+
+  So this tells us that the pair of sets $(I_{n-2}^V\setminus I_1^V, I_1^V\setminus I_{n-2}^V)$ is one of the following $(\{n-2, n-1, n\}, \{n-5, i_1, i_2\})$, $(\{n-2, n-2\}, \{n-5, i_1\})$, $(\{n-2, n-1\}, \{n-5, i_2\}$
+  where $i_1$ and $i_2$ are the first and second ``something''s.
+
+  If $i_2\neq n-4$ then in all three cases $I_{n-2}^V$ contributes an $(n-5)\rightarrow (n-2)$ plus.
+
+  On the other hand if $i_2=n-4$ then the two possible cases above give an $(n-4)\rightarrow (n-2)$ plus and an $(n-5)\rightarrow (n-1)$ plus.
+Note also that if $i_2=n-4$ iff $n-4 \in I_1^V\setminus I_n^V$ iff $n-4\in I_1^V\setminus I_{n-2}^V$.
+
+  No other plusses appear in the $n-2$ column because $n-2$ enters the Grassman necklace for $V$ at $I_{n-2}^V$ and leave immediately after.
+
+\item Continuing with the discussions above coming out of \eqref{eq necklace}, first suppose $I_{n-2}^V$ contrbuted an $(n-5)\rightarrow (n-2)$ plus.
+In this case, going from $I_{n-2}^V$ to $I_{n-1}^V$ takes out the $n-2$ and puts in the $n-5$, so  nothing else changes, while going from $I_{n-3}^V$ to $I_{n-2}^V$ swapped the $n-3$ for the $n-2$, but $n-3\in I_1^V$, so nothing changes from $I_{n-3}^V$ to $I_{n-2}^V$ except changing a $(n-5)\rightarrow (n-3)$ path to $(n-5)\rightarrow (n-2)$.
+
+  Now in the case that $I_{n-2}^V$ contribued an $(n-4)\rightarrow (n-2)$ plus, then going from $I_{n-2}^V$ to $I_{n-1}^V$ takes out the $n-2$ and puts in the $n-5$, so instead of the $(n-4)\rightarrow (n-2)$ plus and the $(n-5)\rightarrow (n-1)$ plus we have an $(n-4)\rightarrow (n-1)$ plus, but the rest stays the same.
+Also, in going from $I_{n-3}^V$ to $I_{n-2}^V$, $n-3$ comes out and $n-2$ goes in so all that changes is a $(n-4)\rightarrow (n-3)$ path becomes an $(n-4)\rightarrow (n-2)$ path.
+
+\item The only elements which could contribute an $(n-5)$ path are those without an $n-5$ and from \eqref{eq necklace} the only ones with this property asre $I_{n-2}^V$, $I_{n-3}^V$, and $I_{n-4}^V$.
+The calculations above work out exactly which paths starting at $n-5$ there are, and that gives the updated version of the result.
+  \end{enumerate}
+\end{proof}
 

### 2019-09-16 GWLDCII.tex
split the lemma but a different way than we'd said

@@
 
-\begin{lem}\label{lem n-2 bad}
+Next we need an observation about how the Grassman necklace for $V$ changes over the indices near $n$ under the hypotheses that $n-2, n-1\in I_{n-2}^V$.
+
+Specifically with $V$ and $W$ as in Lemma~\ref{lem I} and with $n-2, n-1\in I_{n-2}^V$, we have
+  \begin{equation}\label{eq necklace}
+  I_{n-3}^{V} \xrightarrow[\substack{n-3\text{ out}\\n-2\text{ in}}]{} I_{n-2}^{V} \xrightarrow[\substack{n-2\text{ out}\\n-5\text{ in}}]{} I_{n-1}^{V} \xrightarrow[\substack{n-1\text{ out}\\\text{something in}}]{} I_{n}^{V}  \xrightarrow[\substack{\text{no change or }\\n \text{ out}\\\text{something in}}]{} I_1^{V}
+  \end{equation}
+  where the first two transitions follow by cyclic intervals ***cite it properly*** along with the fact that $n-3$ is supporting in $V$.
+The third transition is true by the fact that $n-1\in I_{n-2}^V$ by hypothesis.
+The ``something'' could be $n$ or some element of $I_1^V$.
+However, this ``something'' cannot be $n-4$ because the only thing that could contribute $n-4$ is $q$ but if $I_n^V(q)=n-4$ then the equation for $I_{n-2}^W$ from Lemma~\ref{lem I} would tell us that $n-4\in I_{n-2}^W$ but this is impossible as $I_{n-2}^W(q)=n-2$ but no other propagator than $q$ can contribute $n-4$.
+The last transition of \eqref{eq necklace} then is simply a consequence of the general definition of Grassman necklaces, but it will be useful later to observe that the second ``something'', if it exists, could be $n-4$.
+
+  \begin{lem}\label{lem n-2 bad part 1}
 Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that $n-2,n-1 \in I_{n-2}^{V}$. Then:
   \begin{enumerate}
-  \item $I_{n-2}^W$ contributes an $(n-3)\rightarrow (n-2)$ plus and an $(n-5)\rightarrow (n-1)$ plus, along with any plusses contributed by $I_n^V$.\note{This is correct if $n-4\not\in I_1^V\setminus I_n^V$.
-In the case that $n-4\in I_1^V\setminus I_n^V$ then $I_{n-2}$ contributes an $(n-3)\rightarrow (n-2)$ plus, an $(n-4)\rightarrow (n-1)$ plus and a $(n-5)\rightarrow (n)$ plus while $I_n^V$ contributed an $(n-4)\rightarrow (n)$ plus.}
-  \item $I_{n-3}^W$ contributes the same plusses as $I_{n-3}^V$, except that the plus in the $n-3$ column (which necessarily exists) is shifted one square left into the $n-2$ column.
-  \item In the Le diagram of $V$, $I_{n-2}^{V}$ contributes an $(n-5)\rightarrow (n-2)$ plus and no other term in the Grassmann necklace of $V$ gives a plus in this column.
-$I_{n-2}^W$ does not contribute this $+$ but yields the $(n-5)\rightarrow (n-1)$ plus from point (1) instead.\note{This is correct if $n-4\not\in I_1^V\setminus I_n^V$.
-In the case that $n-4\in I_1^V\setminus I_n^V$ then $I_{n-2}^V$ gives an $(n-4)\rightarrow (n-2)$ plus, and the part about nothing else in the $n-2$ column remains true.}
-  \item All other plusses from $I_{n-2}^{V}$ and all plusses from $I_{n-1}^V$ were already contributed by $I_{n-3}^V$, so they yield no new information.\note{With  the previous part corrected as above, this part is true unchanged.}
-  \item No element of the Grassmann necklace of $V$ contributes a $(n-5)\rightarrow (n-1)$ plus.\note{This should say ``The Grassman necklace of $V$ contributes a $(n-5)\rightarrow (n-1)$ plus if and only if $n-4 in I_1^V\setminus I_n^V$.}
+  \item If $n-4 \not\in I_1^V\setminus I_n^V$, then $I_{n-2}^W$ contributes an $(n-3)\rightarrow (n-2)$ plus and an $(n-5)\rightarrow (n-1)$ plus, along with any plusses contributed by $I_n^V$.
+  \item If $n-4 \in I_1^V\setminus I_n^V$, then $I_{n-2}^W$ contributes an $(n-3)\rightarrow (n-2)$ plus, an $(n-4)\rightarrow (n-1)$ plus and a $(n-5)\rightarrow (n)$ plus while $I_n^V$ contributed an $(n-4)\rightarrow (n)$ plus.
   \end{enumerate}
@@
   \begin{proof}
-  This is Karen's rewritten proof notes (because I can't read the proof below any more and we need to sort out the case when $I^V_1(q)=n-4$.)  Let's go through them item by item, checking that the statements are correct and giving fresh proofs.
+    This proof is a scratchy one and needs editing.
 
@@
 
-  \begin{enumerate}
-  \item The statement needs to change as noted above.
-Here is how a proof of the first statement goes:  Note that $n-5\in I_1^V$.
+Next note that $n-5\in I_1^V$.
 This is because when you get to $n-5$, $q$ isn't taken yet, so either $q$ contributes $n-5$ or something else does (in which case $q$ contributes $n-4$), so in either case $n-5 \in I_1^V$.
@@
 Comparing this to the above we see that $I_n^V$ contributed the plus from the path $(n-4)\rightarrow (n)$, while $I_{n-2}^W$ contributes the plusses $(n-3)\rightarrow (n-2)$, $(n-4)\rightarrow (n-1)$ and $(n-5)\rightarrow (n)$.
-\item The statement of this point does not need changing.
-By Lemma~\ref{lem I} we have that $I_{n-3}^W = I_{n-3}^V \cup \{n-2\}$ (since $n-3\in I_{n-3}^V$ as something (namely $q$) is supported at $n-3$ in $V$.
+  \end{proof}
+
+  \begin{lem}\label{lem n-2 bad part 2}
+    Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that $n-2,n-1 \in I_{n-2}^{V}$. Let $c$ be the largest element of $I_1^V$.  Then:
+    \begin{enumerate}
+  \item $c=n-4$ if $n-4\in I_1^V\setminus I_n^V$ and $c=n-5$ otherwise.
+  \item $I_{n-3}^W$ contributes the same plusses as $I_{n-3}^V$, except that the plus in the $n-3$ column (which necessarily exists) is shifted one square left into the $n-2$ column.
+  \item In the Le diagram of $V$, $I_{n-2}^{V}$ contributes a $c\rightarrow (n-2)$ plus and no other term in the Grassmann necklace of $V$ gives a plus in this column.
+$I_{n-2}^W$ does not contribute this $+$ but yields the $c\rightarrow (n-1)$ plus from Lemma~\ref{lem n-2 bad part 1}
+  \item All other plusses from $I_{n-2}^{V}$ and all plusses from $I_{n-1}^V$ were already contributed by $I_{n-3}^V$, so they yield no new information.
+  \item No element of the Grassmann necklace of $V$ contributes a $c\rightarrow (n-1)$ plus.
+Additionally if $c=n-4$ then no element of the Grassmann necklace of $V$ contributes an $(n-5)\rightarrow n$ plus and only $I_n^V$ contributes an $(n-4)\rightarrow n$ plus.
+  \end{enumerate} 
+\end{lem}
+
+\begin{proof}
+
+  First note that by Lemma~\ref{lem I} $I_1^W = I_1^V\cup \{n-3\}$.  Now, let's take the items in turn.
+
+\begin{enumerate}  
+  \item By Lemma~\ref{lem I} we have that $I_{n-3}^W = I_{n-3}^V \cup \{n-2\}$ (since $n-3\in I_{n-3}^V$ as something (namely $q$) is supported at $n-3$ in $V$.
 So removing $I_{n-3}^W$ from $I_{1}^W$  is the same as removing $I_{n-3}^V$ from $I_1^V$ and removing $I_1^W$ from $I_{n-3}^W$ does the same as removing $I_{1}^V$ from $I_{n-3}^V$ except that the $n-3$ gets replaced by $n-2$.
+  \item Equation \eqref{eq necklace} tells us that the pair of sets $(I_{n-2}^V\setminus I_1^V, I_1^V\setminus I_{n-2}^V)$ is one of the following $(\{n-2, n-1, n\}, \{n-5, i_1, i_2\})$, $(\{n-2, n-2\}, \{n-5, i_1\})$, $(\{n-2, n-1\}, \{n-5, i_2\}$
+  where $i_1$ and $i_2$ are the first and second ``something''s.
+
+    If $i_2\neq n-4$ then in all three cases $I_{n-2}^V$ contributes an $(n-5)\rightarrow (n-2)$ plus.
+On the other hand if $i_2=n-4$ then the two possible cases above give an $(n-4)\rightarrow (n-2)$ plus and an $(n-5)\rightarrow (n-1)$ plus.
+Note also that if $i_2=n-4$ iff $n-4 \in I_1^V\setminus I_n^V$ iff $n-4\in I_1^V\setminus I_{n-2}^V$ iff $c=n-4$.
+
+    No other plusses appear in the $n-2$ column because $n-2$ enters the Grassman necklace for $V$ at $I_{n-2}^V$ and leave immediately after.
   \item 
-
-  Now let's look at \eqref{eq necklace} from the old proof.
-The first two transitions are true by cyclic intervals.
-The third transition is true by the fact that $n-1\in I_{n-2}^V$ by hypothesis.
-The ``something'' could be $n$ or some element of $I_1^V$.
-However, this ``something'' cannot be $n-4$ because the only thing that could contribute $n-4$ is $q$ but if $I_n^V(q)=n-4$ then the equation for $I_{n-2}^W$ from Lemma~\ref{lem I} would tell us that $n-4\in I_{n-2}^W$ but this is impossible as $I_{n-2}^W(q)=n-2$ but no other propagator than $q$ can contribute $n-4$.
-Then in the last transition of \eqref{eq necklace} either nothing happens (of $n$ is non-supporting in $V$) or by general GN stuff, the transition happens as described in the equation.
-The second ``something'', if it exists, could be $n-4$, or it could be some other element of $I_1^V$.
-(Maybe there's a reason I've forgotten that $n$ must be supporing in $V$, but it doesn't matter in the end as we'll see soon.)
-
-  So this tells us that the pair of sets $(I_{n-2}^V\setminus I_1^V, I_1^V\setminus I_{n-2}^V)$ is one of the following $(\{n-2, n-1, n\}, \{n-5, i_1, i_2\})$, $(\{n-2, n-2\}, \{n-5, i_1\})$, $(\{n-2, n-1\}, \{n-5, i_2\}$
-  where $i_1$ and $i_2$ are the first and second ``something''s.
-
-  If $i_2\neq n-4$ then in all three cases $I_{n-2}^V$ contributes an $(n-5)\rightarrow (n-2)$ plus.
-
-  On the other hand if $i_2=n-4$ then the two possible cases above give an $(n-4)\rightarrow (n-2)$ plus and an $(n-5)\rightarrow (n-1)$ plus.
-Note also that if $i_2=n-4$ iff $n-4 \in I_1^V\setminus I_n^V$ iff $n-4\in I_1^V\setminus I_{n-2}^V$.
-
-  No other plusses appear in the $n-2$ column because $n-2$ enters the Grassman necklace for $V$ at $I_{n-2}^V$ and leave immediately after.
-
-\item Continuing with the discussions above coming out of \eqref{eq necklace}, first suppose $I_{n-2}^V$ contrbuted an $(n-5)\rightarrow (n-2)$ plus.
+    The third point is also a consequence of \eqref{eq necklace}.
+Let's take the possibilities in turn, first suppose $I_{n-2}^V$ contrbuted an $(n-5)\rightarrow (n-2)$ plus.
 In this case, going from $I_{n-2}^V$ to $I_{n-1}^V$ takes out the $n-2$ and puts in the $n-5$, so  nothing else changes, while going from $I_{n-3}^V$ to $I_{n-2}^V$ swapped the $n-3$ for the $n-2$, but $n-3\in I_1^V$, so nothing changes from $I_{n-3}^V$ to $I_{n-2}^V$ except changing a $(n-5)\rightarrow (n-3)$ path to $(n-5)\rightarrow (n-2)$.
@@
 Also, in going from $I_{n-3}^V$ to $I_{n-2}^V$, $n-3$ comes out and $n-2$ goes in so all that changes is a $(n-4)\rightarrow (n-3)$ path becomes an $(n-4)\rightarrow (n-2)$ path.
-
-\item The only elements which could contribute an $(n-5)$ path are those without an $n-5$ and from \eqref{eq necklace} the only ones with this property asre $I_{n-2}^V$, $I_{n-3}^V$, and $I_{n-4}^V$.
-The calculations above work out exactly which paths starting at $n-5$ there are, and that gives the updated version of the result.
+\item The only elements which could contribute an $(n-5)$ path are those without an $n-5$.
+From \eqref{eq necklace} the only ones without an $n-5$ are $I_{n-2}^V$, $I_{n-3}^V$, and $I_{n-4}^V$, but the calculations above show they do not have paths as described above.
+Also, if $c=n-4$ then $n-4\in I_1$ so the only elements which could contribute an $(n-4)$ path are those which contain an $n-4$ which are $I_{n}$, $I_{n-1}$, $I_{n-2}$, $I_{n-3}$, which we explicitly see do not.
   \end{enumerate}

### 2019-09-17 GWLDCII.tex
Update GWLDCII.tex

@@
 
-\note{Sian rewrote Case 1 based on Susama's suggested edits}
 \textbf{Case I}:  Suppose $p$ has one end on edge $i-1$.
@@
 
-\note{Following two paragraphs added to replace the sentence ``clearly $n-3 \not\in I_1^V$''}\note{No, the argument is much simpler, by cyclic intervals $I_{1}^W(p) = n-3$, but $p$ is the last thing that can contribute at $n-3$, so for this to happen we must have $n-3\not\in I_1^V$.}
-We first show that $n-3 \not\in I_1^V$.
-In Case 1, the only way we could have $n-3 \in I_1^V$ is if $V$ admits some propagator $r$ with $I_1(r) = n-3$; from the figure, one end of $r$ would have to lie on edge $n-4$, and by Lemma~\ref{lem no fourth vertex} the other end would have to lie on edge $n-1$ or $n$.
-However, if $r = (n-4,n-1)$ then by [remark following cyclic intervals lemma] \hlfix{we would have $I_1^V(r) = n-4$}{because if it contributed $n-3$ it would never be able to contribute $n-4$?}, while if $r = (n-4,n)$ then $r$ is the clockwise-most propagator supported on vertex 1 and we would have $I_1^V(r) = 1$.
-Either way, we have $I_1^V(r) \neq n-3$.
-
-In Case 2 the only propagator supported on vertex $n-3$ in $V$ is $q$, and by [cyclic intervals remark] we \hlfix{have $I_{n-1}^V(q) = n-5$}{Because $I_{n-2}^V(q) = n-2$ and Lemma \ref{lem no vourht vertex} prevents $I_{n-1}^V(q) = n-2$?}.
-Further, it must also be the case that $I_n^V(q) = n - 5$: if $n-1$ is non-supporting in $V$ then this is immediate, while if there exists a propagator $r$ in $V$ with $I_{n-1}^V(r) = n-1$ then $r$ lies on edge $n-1$ and is the clockwise-most propagator supported on vertex $n$, so $I_n^V(r) = n$ and the remainder of $I_n^V$ proceeds identically to $I_{n-1}^V$.
-Thus $I_n^V(q) = n-5$, so by [cyclic intervals lemma or remark] we have $I_1^V(q) \in \{n-5,n-4\}$; in particular, $I_1^V(q)\neq n-3$.
+We begin with $I_1$, and first observe that by Remark~\ref{rmk cyclic} we must have $I_1^W(p) = n-3$.
+Since $p$ is the final propagator to be assigned by $I_1^W$, it follows that $I_1^W$ and $I_1^V$ behaved identically on all earlier propagators (recall Remark~\ref{rmk algorithm locally same} about locally identical propagator configurations), which implies in particular that $n-3 \not\in I_1^V$.
+Thus $I_1^W = I_1^V\cup\{n-3\}$.
 
 We note for future reference that the arguments of the previous two paragraphs also imply that $n-2,n-1,n \not\in I_1^V$.
-
-We can now describe $I_1^W$ in terms of $I_1^V$: when we start at vertex 1 in $W$ and apply the Grassmann necklace algorithm, $p$ is the only remaining unassigned propagator when we reach vertex $n-3$, and so we have $ I_1^{W}(p) = n-3$ and $I_1^W = I_1^V\cup \{n-3\}$.
 
@@
 At vertex 1 of the algorithm $I_n$, the unassigned propagators are exactly those that appear in $V$.
-Therefore the algorithm continues as in $I_1^{V}$ (recall Remark~\ref{rmk algorithm locally same} about locally identical propagator configurations), i.e.
+Therefore the algorithm continues as in $I_1^{V}$, i.e.
 we have $I_n^{W} = I_1^{V} \cup \{n\}$.
@@
 We make one further simplification in order to eliminate the possibility that $n-2 \in I_{n-2}^V$ but $n-1 \not\in I_{n-2}^V$, which can only occur if our $W$ is in Case 2 of Figure~\ref{fig special p} and $n-1$ supports no propagators other than $p$.
-In this situation, flip $W$ on the line perpendicular to the $(n-2){th}$ edge to obtain a diagram with the configuration of Case 1.
-
-\note{Sian rewrote above paragraph because their original version was wrong in multiple ways. Better?}
-{\color{violet} I'm very confused about the previous paragraph.
-I thought that by constuction, in case 2, there can be exactly 2 propagators ending on edge $n-3$, $p$ and $q$.
-I also thought the distinguising feature between the two subcases of Figure 10 case 2 in Lemma 4.4 $I_{n-2}^W$ was the presence or absense of a propagator $r$ ending on edge $n-1$.
-If $r$ exists, $n-1 \in I_{n-2}^V$ and if  $r$ doesn't exist, $n-1 \not \in I_{n-2}^V$.}
-
-  This diagram will be our $W$ for the remainder of the proof. Let $V$ be $W$ with $p$ removed.
+In this situation, apply the dihedral transformation that reflects $W$ along the line perpendicular to the $(n-2){th}$ edge, so that $p$ is unchanged but $q = (n-1,1)$ in the new diagram.
+The new diagram is an example of Case 1.
+
+In summary, $W$ is a diagram with one of the two configurations depicted in Figure~\ref{fig special p}, and if $n-2 \in I_{n-2}^V$ then $n-1 \in I_{n-1}^V$ as well. Let $V$ be $W$ with $p$ removed.
 

### 2019-09-17 GWLDCII.tex
some edits to the new proofs

@@
 Consider $I_{j+2}(p)$.
-Since $j+1$ is the last vertex in the $j+2$ order, $p$ can not contribute $j+1$ to $I_{j+2}$.
-But the the fact that the invervals of the lemma are nonempty and occur in their cyclic order implies that $I_{j+2}(p)=i$.
+Since $j+1$ is the last vertex in the $j+2$ order, $p$ can not contribute $j+1$ to $I_{j+2}$, so the fact that the invervals in the statement of the lemma are non-empty and occur in their cyclic order implies that $I_{j+2}(p)=i$.
 More generally, whenever we know that a propagator stops contributing a particular vertex, then we know that it must contribute its cyclically next vertex.
-This little observation is surprisingly useful, to the point that the details which appear in the proof of Lemma~\ref{vertex cyclic int lem} are never needed again, the mere fact of non-empty intervals in the correct order suffices.
+This little observation is surprisingly useful, to the point that the details which appear in the proof of Lemma~\ref{vertex cyclic int lem} are never needed again: the mere fact of non-empty intervals in the correct order suffices.
 \end{rmk}
@@
 
-Specifically with $V$ and $W$ as in Lemma~\ref{lem I} and with $n-2, n-1\in I_{n-2}^V$, we have
+Specifically with $V$ and $W$ as in Lemma~\ref{lem I} and with $n-2, n-1\in I_{n-2}^V$ (so we are necessarily in Case 2 and $n-1$ supports at least one additional propagator not shown in the figure) we have
   \begin{equation}\label{eq necklace}
-  I_{n-3}^{V} \xrightarrow[\substack{n-3\text{ out}\\n-2\text{ in}}]{} I_{n-2}^{V} \xrightarrow[\substack{n-2\text{ out}\\n-5\text{ in}}]{} I_{n-1}^{V} \xrightarrow[\substack{n-1\text{ out}\\\text{something in}}]{} I_{n}^{V}  \xrightarrow[\substack{\text{no change or }\\n \text{ out}\\\text{something in}}]{} I_1^{V}
+  I_{n-3}^{V} \xrightarrow[\substack{n-3\text{ out}\\n-2\text{ in}}]{} I_{n-2}^{V} \xrightarrow[\substack{n-2\text{ out}\\n-5\text{ in}}]{} I_{n-1}^{V} \xrightarrow[\substack{n-1\text{ out}\\\text{something in}}]{} I_{n}^{V}  \xrightarrow[\substack{n \text{ out}\\\text{something in}}]{} I_1^{V}
   \end{equation}
-  where the first two transitions follow by cyclic intervals ***cite it properly*** along with the fact that $n-3$ is supporting in $V$.
-The third transition is true by the fact that $n-1\in I_{n-2}^V$ by hypothesis.
+  \note{Check: if we no longer need the $a,b$ in Figure \ref{fig messy}, we can probably rename these ``somethings'' to $a,b$ here.}
+  where the first two transitions follow by Remark~\ref{rmk cyclic} along with the fact that $n-3$ is a supporting vertex in $V$.
+The third transition follows from the definition of Grassmann necklaces and the fact that $n-1\in I_{n-2}^V$ by hypothesis.
 The ``something'' could be $n$ or some element of $I_1^V$.
-However, this ``something'' cannot be $n-4$ because the only thing that could contribute $n-4$ is $q$ but if $I_n^V(q)=n-4$ then the equation for $I_{n-2}^W$ from Lemma~\ref{lem I} would tell us that $n-4\in I_{n-2}^W$ but this is impossible as $I_{n-2}^W(q)=n-2$ but no other propagator than $q$ can contribute $n-4$.
-The last transition of \eqref{eq necklace} then is simply a consequence of the general definition of Grassman necklaces, but it will be useful later to observe that the second ``something'', if it exists, could be $n-4$.
+
+  {\note{converge following two fragments into a coherent thought} \color{blue} However, this ``something'' cannot be $n-1$, $n-2$, or $n-3$, because as noted in Lemma~\ref{lem I} these elements do not belong to $I_1^V$, and it also cannot be $n-4$: we saw that $I_{n-1}(q) = n-5$ by Remark~\ref{rmk cyclic}, and
+
+   because the only thing that could contribute $n-4$ is $q$ but if $I_n^V(q)=n-4$ then the equation for $I_{n-2}^W$ from Lemma~\ref{lem I} would tell us that $n-4\in I_{n-2}^W$ but this is impossible as $I_{n-2}^W(q)=n-2$ but no other propagator than $q$ can contribute $n-4$.
+}
+
+  We cannot have $I_1^V = I_n^V$, since the $n-2,n-1 \in I_{n-2}^V$ hypothesis ensures that the $(n-1)$th edge supports at least one propagator even in $V$.
+The last transition of \eqref{eq necklace} is then simply a consequence of the general definition of Grassman necklaces, but it will be useful later to observe that the second ``something'' could be $n-4$.
 
@@
   \begin{enumerate}
-  \item If $n-4 \not\in I_1^V\setminus I_n^V$, then $I_{n-2}^W$ contributes an $(n-3)\rightarrow (n-2)$ plus and an $(n-5)\rightarrow (n-1)$ plus, along with any plusses contributed by $I_n^V$.
+  \item If $n-4 \not\in I_1^V\setminus I_n^V$, then $I_{n-2}^W$ contributes an $(n-3)\rightarrow (n-2)$ plus and an $(n-5)\rightarrow (n-1)$ plus, along with the one plus contributed by $I_n^V$.
   \item If $n-4 \in I_1^V\setminus I_n^V$, then $I_{n-2}^W$ contributes an $(n-3)\rightarrow (n-2)$ plus, an $(n-4)\rightarrow (n-1)$ plus and a $(n-5)\rightarrow (n)$ plus while $I_n^V$ contributed an $(n-4)\rightarrow (n)$ plus.
@@
   \begin{proof}
-    This proof is a scratchy one and needs editing.
-
-      First note that by Lemma~\ref{lem I} $I_1^W = I_1^V\cup \{n-3\}$.
-
-Next note that $n-5\in I_1^V$.
-This is because when you get to $n-5$, $q$ isn't taken yet, so either $q$ contributes $n-5$ or something else does (in which case $q$ contributes $n-4$), so in either case $n-5 \in I_1^V$.
-Also note that $n-1, n-2, n-3\not\in I_n^V$ (this must have been said before because it is in the shape of the Le diagram).
-This together with Lemma~\ref{lem I} gives
-    \[
-    I_1^W \setminus I_{n-2}^W = (I_1^V\cup\{n-3\}) \setminus ((I_n^V\setminus \{n-3\})\cup \{n-1, n-2\}) = (I_1^V\setminus I_n^V) \cup \{n-3, n-5\}.
-    \]
-    Since we also have $n-1, n-2\not\in I_1^V$ we get
-    \[
-    I_{n-2}^W \setminus I_1^W = ((I_n^V\setminus \{n-3\})\cup \{n-1, n-2\}) \setminus(I_1^V\cup\{n-3\}) = (I_n^V\setminus I_1^V) \cup \{n-1, n-2\}.
-    \]
-    The statement follows from the above if $n-4\not\in I_1^V\setminus I_{n}^V$ as the path from $I_n^V$ (if any) lies above all paths between $\{n-3, n-5\}$ and $\{n-2, n-1\}$, so we just take the noncrossing paths to get the statement.
-
-    Now suppose $n-4\in I_1^V\setminus I_{n}^V$.
-Then want three noncrossing paths starting from $\{n-3, n-4, n-5\}$, and hence by necessity of shape, going to $\{n, n-1, n-2\}$.
+[See Figure \ref{fig new le diagrams}]
+
+By Lemma~\ref{lem I} we have $I_1^W = I_1^V\cup \{n-3\}$ and $I_{n-2}^W = (I_n^V \setminus \{n-5\}) \cup \{n-1,n-2\}$.
+By equation \eqref{eq necklace} we have $n-5 \in I_1^V$, and by the following discussion we have $n-1,n-2,n-3 \not\in I_n^V,I_1^V$.
+It follows that the symmetric difference of $I_1^W$ and $I_{n-2}^W$ is:
+    \begin{gather*}
+    I_1^W \setminus I_{n-2}^W = (I_1^V\cup\{n-3\}) \setminus \big((I_n^V\setminus \{n-5\})\cup \{n-1, n-2\}\big) = (I_1^V\setminus I_n^V) \cup \{n-3, n-5\}. \\
+    I_{n-2}^W \setminus I_1^W = \big((I_n^V\setminus \{n-5\})\cup \{n-1, n-2\}\big) \setminus(I_1^V\cup\{n-3\}) = (I_n^V\setminus I_1^V) \cup \{n-1, n-2\}.
+\end{gather*}
+As per the discussion following equation \eqref{eq necklace} above, we also have $I_n^V\setminus I_1^V = \{n\}$ and $I_1^V\setminus I_n^V = \{a\}$, where $a$ is the second ``something'' in equation \eqref{eq necklace}.
+If $a \neq n-4$ then the path from $I_n^V$ lies above the paths from $\{n-3, n-5\}$ and $\{n-2, n-1\}$ and we obtain point 1.
+
+Now suppose $n-4\in I_1^V\setminus I_{n}^V$; in this case $I_{n-2}^W$ contributes plusses defined by the noncrossing paths starting from $\{n-3, n-4, n-5\}$ and ending at $\{n, n-1, n-2\}$.
 Comparing this to the above we see that $I_n^V$ contributed the plus from the path $(n-4)\rightarrow (n)$, while $I_{n-2}^W$ contributes the plusses $(n-3)\rightarrow (n-2)$, $(n-4)\rightarrow (n-1)$ and $(n-5)\rightarrow (n)$.
   \end{proof}
+
+  \begin{figure}
+\includegraphics[width = 12cm]{new_le_diagrams.jpg}
+\caption{Included for reference while we figure out the details; Lemma \ref{lem n-2 bad part 1}}\label{fig new le diagrams}
+  \end{figure}
 
@@
 \begin{proof}
-
-  First note that by Lemma~\ref{lem I} $I_1^W = I_1^V\cup \{n-3\}$.  Now, let's take the items in turn.
-
 \begin{enumerate}
-  \item By Lemma~\ref{lem I} we have that $I_{n-3}^W = I_{n-3}^V \cup \{n-2\}$ (since $n-3\in I_{n-3}^V$ as something (namely $q$) is supported at $n-3$ in $V$.
-So removing $I_{n-3}^W$ from $I_{1}^W$  is the same as removing $I_{n-3}^V$ from $I_1^V$ and removing $I_1^W$ from $I_{n-3}^W$ does the same as removing $I_{1}^V$ from $I_{n-3}^V$ except that the $n-3$ gets replaced by $n-2$.
-  \item Equation \eqref{eq necklace} tells us that the pair of sets $(I_{n-2}^V\setminus I_1^V, I_1^V\setminus I_{n-2}^V)$ is one of the following $(\{n-2, n-1, n\}, \{n-5, i_1, i_2\})$, $(\{n-2, n-2\}, \{n-5, i_1\})$, $(\{n-2, n-1\}, \{n-5, i_2\}$
-  where $i_1$ and $i_2$ are the first and second ``something''s.
-
-    If $i_2\neq n-4$ then in all three cases $I_{n-2}^V$ contributes an $(n-5)\rightarrow (n-2)$ plus.
-On the other hand if $i_2=n-4$ then the two possible cases above give an $(n-4)\rightarrow (n-2)$ plus and an $(n-5)\rightarrow (n-1)$ plus.
-Note also that if $i_2=n-4$ iff $n-4 \in I_1^V\setminus I_n^V$ iff $n-4\in I_1^V\setminus I_{n-2}^V$ iff $c=n-4$.
+
+\item As in Lemma~\ref{lem n-2 bad part 2}, we have $n,n-1,n-2,n-3 \not\in I_1^V$; the claim follows immediately.
+
+\item By Lemma~\ref{lem I} we have that $I_{n-3}^W = I_{n-3}^V \cup \{n-2\}$, so $I_{1}^W \setminus I_{n-3}^W = I_1^V \setminus I_{n-3}^V$ and $I_{n-3}^W \setminus I_1^W$ is obtained from $I_{n-3}^V \setminus I_{1}^V$ by replacing the $n-3$ with $n-2$.
+
+\item From \eqref{eq necklace} the pair of sets $(I_{n-2}^V\setminus I_1^V, I_1^V\setminus I_{n-2}^V)$ is either $(\{n-2, n-1, n\}, \{n-5, i_1, i_2\})$ (if $n \in I_{n-2}^V$) or $(\{n-2, n-1\}, \{n-5, i_2\})$ (if $n \not\in I_{n-2}^V$, i.e.
+$i_1 = n$), where $i_1$ and $i_2$ are the first and second ``something''s.
+
+Recall that $n-4 \not\in I_n^V$, so that $c = n-4$ iff $i_2 = n-4$ iff $n-4 \in I_1^V\setminus I_n^V$ iff $n-4 \in I_1^V \setminus I_{n-2}^V$.
+Thus we get a $c \rightarrow (n-2)$ plus in the Le diagram for $V$ in either case, and this becomes the $c \rightarrow (n-1)$ plus in the Le diagram for $W$ (refer back to previous lemma; ``becomes'' might not be the clearest phrasing).
 

### 2019-09-18 GWLDCII.tex
some working with blue text

@@
   \begin{equation}\label{eq necklace}
-  I_{n-3}^{V} \xrightarrow[\substack{n-3\text{ out}\\n-2\text{ in}}]{} I_{n-2}^{V} \xrightarrow[\substack{n-2\text{ out}\\n-5\text{ in}}]{} I_{n-1}^{V} \xrightarrow[\substack{n-1\text{ out}\\\text{something in}}]{} I_{n}^{V}  \xrightarrow[\substack{n \text{ out}\\\text{something in}}]{} I_1^{V}
+  I_{n-3}^{V} \xrightarrow[\substack{n-3\text{ out}\\n-2\text{ in}}]{} I_{n-2}^{V} \xrightarrow[\substack{n-2\text{ out}\\n-5\text{ in}}]{} I_{n-1}^{V} \xrightarrow[\substack{n-1\text{ out}\\ u \text{ in}}]{} I_{n}^{V}  \xrightarrow[\substack{n \text{ out}\\v \text{ in}}]{} I_1^{V}
   \end{equation}
@@
 The third transition follows from the definition of Grassmann necklaces and the fact that $n-1\in I_{n-2}^V$ by hypothesis.
-The ``something'' could be $n$ or some element of $I_1^V$.
-
-  {\note{converge following two fragments into a coherent thought} \color{blue} However, this ``something'' cannot be $n-1$, $n-2$, or $n-3$, because as noted in Lemma~\ref{lem I} these elements do not belong to $I_1^V$, and it also cannot be $n-4$: we saw that $I_{n-1}(q) = n-5$ by Remark~\ref{rmk cyclic}, and
-
-   because the only thing that could contribute $n-4$ is $q$ but if $I_n^V(q)=n-4$ then the equation for $I_{n-2}^W$ from Lemma~\ref{lem I} would tell us that $n-4\in I_{n-2}^W$ but this is impossible as $I_{n-2}^W(q)=n-2$ but no other propagator than $q$ can contribute $n-4$.
-}
+The vertex $u$ could be $n$ or some element of $I_1^V$.
+
+ \note{converge following two fragments into a coherent thought} {\color{blue} However, $u$ \st{cannot be $n-1$, $n-2$, or $n-3$, because as noted in Lemma {\ref{lem I}} these elements do not belong to $I_1^V$}\sanote{why does $I_1^V$ inform $I_n^V$?}\emph{cannot be $n-1$ because the vertex is non-supporting in $V$, it cannot be $n-2$ because this vertex only supports $q$, but $I_n^V(q) \neq n-2$ because it is the last vertex in the support (Lemma {\ref{lem no fourth vertex}}), and it cannot be $n-3$ by Remark {\ref{rmk cyclic}}.} Furthermore, it $u$ also cannot be $n-4$: we saw that $I_{n}(q) = n-5$ by Remark~{\ref{rmk cyclic}}.
+
+because the only thing that could contribute $n-4$ is $q$ but if $I_n^V(q)=n-4$ then the equation for $I_{n-2}^W$ from Lemma {~\ref{lem I}} would tell us that $n-4\in I_{n-2}^W$ but this is impossible as $I_{n-2}^W(q)=n-2$ but no other propagator than $q$ can contribute $n-4$.
+} \sanote{not sure what this paragraph contributes}
 
   We cannot have $I_1^V = I_n^V$, since the $n-2,n-1 \in I_{n-2}^V$ hypothesis ensures that the $(n-1)$th edge supports at least one propagator even in $V$.
-The last transition of \eqref{eq necklace} is then simply a consequence of the general definition of Grassman necklaces, but it will be useful later to observe that the second ``something'' could be $n-4$.
+The last transition of \eqref{eq necklace} is then simply a consequence of the general definition of Grassman necklaces.
+The vertex $v$ cannot be $n-1$, $n-2$ or $n-2$ by Lemma \ref{lem I}, however, in this transition, it could be $n-4$.
 

### 2019-09-18 GWLDCII.tex
fixed the bit of blue text that I broke yesterday

--- 2019-09-17 GWLDCII.tex
@@
 
-Specifically with $V$ and $W$ as in Lemma~\ref{lem I} and with $n-2, n-1\in I_{n-2}^V$ (so we are necessarily in Case 2 and $n-1$ supports at least one additional propagator not shown in the figure) we have
+Specifically with $V$ and $W$ as in Lemma~\ref{lem I} and with $n-2, n-1\in I_{n-2}^V$ (so we are necessarily in Case 2 and $n-1$ supports at least one additional propagator) we have
   \begin{equation}\label{eq necklace}
@@
   \note{Check: if we no longer need the $a,b$ in Figure \ref{fig messy}, we can probably rename these ``somethings'' to $a,b$ here.}
-  where the first two transitions follow by Remark~\ref{rmk cyclic} along with the fact that $n-3$ is a supporting vertex in $V$.
-The third transition follows from the definition of Grassmann necklaces and the fact that $n-1\in I_{n-2}^V$ by hypothesis.
-The ``something'' could be $n$ or some element of $I_1^V$.
-
-  {\note{converge following two fragments into a coherent thought} \color{blue} However, this ``something'' cannot be $n-1$, $n-2$, or $n-3$, because as noted in Lemma~\ref{lem I} these elements do not belong to $I_1^V$, and it also cannot be $n-4$: we saw that $I_{n-1}(q) = n-5$ by Remark~\ref{rmk cyclic}, and
-
-   because the only thing that could contribute $n-4$ is $q$ but if $I_n^V(q)=n-4$ then the equation for $I_{n-2}^W$ from Lemma~\ref{lem I} would tell us that $n-4\in I_{n-2}^W$ but this is impossible as $I_{n-2}^W(q)=n-2$ but no other propagator than $q$ can contribute $n-4$.
-}
-
-  We cannot have $I_1^V = I_n^V$, since the $n-2,n-1 \in I_{n-2}^V$ hypothesis ensures that the $(n-1)$th edge supports at least one propagator even in $V$.
-The last transition of \eqref{eq necklace} is then simply a consequence of the general definition of Grassman necklaces, but it will be useful later to observe that the second ``something'' could be $n-4$.
+  where the first two transitions follow by the cyclic intervals property highlighted in Remark~\ref{rmk cyclic} along with the fact that $n-3$ is a supporting vertex in $V$.
+The third transition follows from the definition of Grassmann necklaces and the fact that $n-1\in I_{n-2}^V$ by hypothesis, while the final transition follows from the fact that $n-1$ supports an additional propagator so we are guaranteed $n \in I_n^V$.
+
+Note that neither ``something'' can be $n-1$, $n-2$, or $n-3$, because as noted in Lemma~\ref{lem I} these elements do not belong to $I_1^V$.
+
+\note{Two versions of the same argument follow:}
+The first ``something'' also cannot be $n-4$, for the following reason.
+By Remark~\ref{rmk cyclic} we know that $I_{n-1}^W(q) = n-5$, leaving no propagators supported on $n-4$ for $I_{n-1}^W$ to assign.
+Thus $n-4 \not\in I_{n-1}^W$, and since $I_{n-1}^W = I_n^V\cup\{n-1\}$ by Lemma~\ref{lem I}, we cannot have $n-4$ in $I_n^V$ either.
+
+The first ``something'' also cannot be $n-4$, for the following reason.
+By Remark~\ref{rmk cyclic} we know that $I_{n-1}$ assigns $q$ to $n-5$ in both $V$ and $W$, so the only way we could have $n-4 \in I_n^V$ is if $I_n^V(q) = n-4$.
+By Lemma~\ref{lem I} this would imply $n-4 \in I_{n-1}^W$ as well, but since $I_{n-1}^W(q) = n-5$ there can be no propagators remaining when the algorithm reaches $n-4$.
+
+However, it will be important later to observe that the second ``something'' could be $n-4$.
 

### 2019-09-19 GWLDCII.tex
some edits while talking

@@
   \begin{equation}\label{eq necklace}
-  I_{n-3}^{V} \xrightarrow[\substack{n-3\text{ out}\\n-2\text{ in}}]{} I_{n-2}^{V} \xrightarrow[\substack{n-2\text{ out}\\n-5\text{ in}}]{} I_{n-1}^{V} \xrightarrow[\substack{n-1\text{ out}\\\text{something in}}]{} I_{n}^{V}  \xrightarrow[\substack{n \text{ out}\\\text{something in}}]{} I_1^{V}
+  I_{n-3}^{V} \xrightarrow[\substack{n-3\text{ out}\\n-2\text{ in}}]{} I_{n-2}^{V} \xrightarrow[\substack{n-2\text{ out}\\n-5\text{ in}}]{} I_{n-1}^{V} \xrightarrow[\substack{n-1\text{ out}\\ u \text{ in}}]{} I_{n}^{V}  \xrightarrow[\substack{n \text{ out}\\v \text{ in}}]{} I_1^{V}
   \end{equation}
-  \note{Check: if we no longer need the $a,b$ in Figure \ref{fig messy}, we can probably rename these ``somethings'' to $a,b$ here.}
-  where the first two transitions follow by the cyclic intervals property highlighted in Remark~\ref{rmk cyclic} along with the fact that $n-3$ is a supporting vertex in $V$.
+where $u$ and $v$ are two vertices; we will derive some properties of them below.
+
+The first two transitions follow by the cyclic intervals property highlighted in Remark~\ref{rmk cyclic} along with the fact that $n-3$ is a supporting vertex in $V$.
 The third transition follows from the definition of Grassmann necklaces and the fact that $n-1\in I_{n-2}^V$ by hypothesis, while the final transition follows from the fact that $n-1$ supports an additional propagator so we are guaranteed $n \in I_n^V$.
 
-Note that neither ``something'' can be $n-1$, $n-2$, or $n-3$, because as noted in Lemma~\ref{lem I} these elements do not belong to $I_1^V$.
-
-\note{Two versions of the same argument follow:}
-The first ``something'' also cannot be $n-4$, for the following reason.
+Note that neither $u$ nor $v$ can be $n-1$, $n-2$, or $n-3$, because as noted in Lemma~\ref{lem I} these elements do not belong to $I_1^V$ and $I_n^V = (I_1^V\setminus \{v\}) \cup \{n\}$.
+However, $u$ could be $n$.
+
+Also $u$ cannot be $n-4$, for the following reason.
 By Remark~\ref{rmk cyclic} we know that $I_{n-1}^W(q) = n-5$, leaving no propagators supported on $n-4$ for $I_{n-1}^W$ to assign.
@@
 
-The first ``something'' also cannot be $n-4$, for the following reason.
-By Remark~\ref{rmk cyclic} we know that $I_{n-1}$ assigns $q$ to $n-5$ in both $V$ and $W$, so the only way we could have $n-4 \in I_n^V$ is if $I_n^V(q) = n-4$.
-By Lemma~\ref{lem I} this would imply $n-4 \in I_{n-1}^W$ as well, but since $I_{n-1}^W(q) = n-5$ there can be no propagators remaining when the algorithm reaches $n-4$.
-
-However, it will be important later to observe that the second ``something'' could be $n-4$.
+However, it will be important later to observe that $v$ could be $n-4$.
 

### 2019-09-19 GWLDCII.tex
fix the item 5 problem

@@
   \begin{proof}
-[See Figure \ref{fig new le diagrams}]
+
+Figure \ref{fig new le diagrams} illustrates the cases appearing in this proof.
 
@@
 \end{gather*}
-As per the discussion following equation \eqref{eq necklace} above, we also have $I_n^V\setminus I_1^V = \{n\}$ and $I_1^V\setminus I_n^V = \{a\}$, where $a$ is the second ``something'' in equation \eqref{eq necklace}.
-If $a \neq n-4$ then the path from $I_n^V$ lies above the paths from $\{n-3, n-5\}$ and $\{n-2, n-1\}$ and we obtain point 1.
+As per the discussion following equation \eqref{eq necklace} above, we also have $I_n^V\setminus I_1^V = \{n\}$ and $I_1^V\setminus I_n^V = \{v\}$.
+If $v \neq n-4$ then the path from $I_n^V$ lies above the paths from $\{n-3, n-5\}$ and $\{n-2, n-1\}$ and we obtain point 1.
 
@@
   \item All other plusses from $I_{n-2}^{V}$ and all plusses from $I_{n-1}^V$ were already contributed by $I_{n-3}^V$, so they yield no new information.
-  \item No element of the Grassmann necklace of $V$ contributes a $c\rightarrow (n-1)$ plus.
-Additionally if $c=n-4$ then no element of the Grassmann necklace of $V$ contributes an $(n-5)\rightarrow n$ plus and only $I_n^V$ contributes an $(n-4)\rightarrow n$ plus.
+  \item The Grassmann necklace of $V$ contributes a $c\rightarrow (n-1)$ plus if and only if $n-4\in I_1^V\setminus I_n^V$.
   \end{enumerate} 
@@
 \item The only elements which could contribute an $(n-5)$ path are those without an $n-5$.
-From \eqref{eq necklace} the only ones without an $n-5$ are $I_{n-2}^V$, $I_{n-3}^V$, and $I_{n-4}^V$, but the calculations above show they do not have paths as described above.
-Also, if $c=n-4$ then $n-4\in I_1$ so the only elements which could contribute an $(n-4)$ path are those which contain an $n-4$ which are $I_{n}$, $I_{n-1}$, $I_{n-2}$, $I_{n-3}$, which we explicitly see do not.
+From \eqref{eq necklace} the only ones without an $n-5$ are $I_{n-2}^V$, $I_{n-3}^V$, and $I_{n-4}^V$.
+\note{find the right pluss or lack thereof}.
   \end{enumerate}
@@
 Lemmas~\ref{lem n and n-1} through \ref{lem other k} show that there is a bijection between the plusses of the Le diagram of $V$ and the plusses of the Le diagram of $W$ that are not in the bottom row.
-This bijection can be described as follows:
+This bijection can be described as follows:\note{In the case $n-4\in I_1^V \setminus I_n^V$ then the $ (n-4)\rightarrow (n-1)$ plus is not new in $W$ but instead there is an $(n-5)\rightarrow (n)$ plus in $W$ which gives the third new plus.
+This needs to be added to the proof and the rest adjusted for the bad $n-4$ possiblity.}
   \begin{itemize}

### 2019-09-20 GWLDCII.tex
Maybe the dimension proof is fixed now?

@@
     \begin{enumerate}
-  \item $c=n-4$ if $n-4\in I_1^V\setminus I_n^V$ and $c=n-5$ otherwise.
+  \item $c=n-4$ if $n-4\in I_1^V\setminus I_n^V$ and $c=n-5$ otherwise. If $c = n-4$ then we have $v = n-4$ in equation \eqref{eq necklace}.
   \item $I_{n-3}^W$ contributes the same plusses as $I_{n-3}^V$, except that the plus in the $n-3$ column (which necessarily exists) is shifted one square left into the $n-2$ column.
+  \item $I_{n-2}^W$ contributes an $(n-3) \rightarrow (n-2)$ plus, a $c \rightarrow (n-1)$ plus, and one other plus.
+If $c = n-5$ then this third plus is the one contributed by $I_n^V$, while if $c = n-4$ then the third plus is $(n-5) \rightarrow n$ (whereas $I_n^V$ contributed $(n-4) \rightarrow n$).
   \item In the Le diagram of $V$, $I_{n-2}^{V}$ contributes a $c\rightarrow (n-2)$ plus and no other term in the Grassmann necklace of $V$ gives a plus in this column.
-$I_{n-2}^W$ does not contribute this $+$ but yields the $c\rightarrow (n-1)$ plus from Lemma~\ref{lem n-2 bad part 1}
-  \item All other plusses from $I_{n-2}^{V}$ and all plusses from $I_{n-1}^V$ were already contributed by $I_{n-3}^V$, so they yield no new information.
-  \item The Grassmann necklace of $V$ contributes a $c\rightarrow (n-1)$ plus if and only if $n-4\in I_1^V\setminus I_n^V$.
+All other plusses from $I_{n-2}^{V}$ were already contributed by $I_{n-3}^V$.
+  \item If $c = n-4$ then $I_{n-1}^V$ contributes a $(n-4) \rightarrow (n-1)$ plus; all other plusses contributed by $I_{n-1}^V$ were already contributed by $I_{n-3}^V$, regardless of the value of $c$.
+  \item The Grassmann necklace of $V$ contributes a $c\rightarrow (n-1)$ plus if and only if $c = n-4$. No term in the Grassmann necklace of $V$ contributes a $(n-5) \rightarrow n$ plus.
   \end{enumerate} 
@@
 
-\item As in Lemma~\ref{lem n-2 bad part 2}, we have $n,n-1,n-2,n-3 \not\in I_1^V$; the claim follows immediately.
+\item As in Lemma~\ref{lem I} we have $n,n-1,n-2,n-3 \not\in I_1^V$, which implies the first part of the claim.
+The second part is a consequence of the discussion following \eqref{eq necklace}, which shows that $n-4 \not\in I_n^V$.
 
@@
 
-\item From \eqref{eq necklace} the pair of sets $(I_{n-2}^V\setminus I_1^V, I_1^V\setminus I_{n-2}^V)$ is either $(\{n-2, n-1, n\}, \{n-5, i_1, i_2\})$ (if $n \in I_{n-2}^V$) or $(\{n-2, n-1\}, \{n-5, i_2\})$ (if $n \not\in I_{n-2}^V$, i.e.
-$i_1 = n$), where $i_1$ and $i_2$ are the first and second ``something''s.
-
-Recall that $n-4 \not\in I_n^V$, so that $c = n-4$ iff $i_2 = n-4$ iff $n-4 \in I_1^V\setminus I_n^V$ iff $n-4 \in I_1^V \setminus I_{n-2}^V$.
-Thus we get a $c \rightarrow (n-2)$ plus in the Le diagram for $V$ in either case, and this becomes the $c \rightarrow (n-1)$ plus in the Le diagram for $W$ (refer back to previous lemma; ``becomes'' might not be the clearest phrasing).
-
-No other plusses appear in the $n-2$ column because $n-2$ enters the Grassman necklace for $V$ at $I_{n-2}^V$ and leave immediately after.
-  \item 
-    The third point is also a consequence of \eqref{eq necklace}.
+\item This is just the statement of the previous lemma folded back into this one; if we decide to move it back here then we can just copy the proof over.
+
+\item From equation \eqref{eq necklace} the pair of sets $(I_{n-2}^V\setminus I_1^V, I_1^V\setminus I_{n-2}^V)$ is either $(\{n-2, n-1, n\}, \{n-5, u, v\})$ (if $n \in I_{n-2}^V$) or $(\{n-2, n-1\}, \{n-5, v\})$ (if $n \not\in I_{n-2}^V$, i.e.
+$u = n$).
+
+Recall that we cannot have $u = n-4$ (since $n-4 \notin I_n^V$) so either $u = n$ or $u < n-5$, and either way $n-2$ is minimal in $I_{n-2}^V\setminus I_1^V$ and $c$ is maximal in $I_1^V \setminus I_{n-2}^V$, yielding a $c \rightarrow (n-2)$ plus.
+
+Since $I_{n-2}^V$ is the only term in the Grassmann necklace for $V$ that contains $n-2$, no other term can contribute a plus in column $n-2$.
+Additionally, since $I_{n-2}^V$ only differs from $I_{n-3}^V$ in that the $n-3$ was replaced by an $n-2$, all other plusses must agree with those contributed by $I_{n-3}^V$.
+
+\item Combining equation \eqref{eq necklace} with the previous point, the pair $(I_{n-1}^V \setminus I_1^V, I_1^V \setminus I_{n-1}^V)$ is either $(\{n-1, n\}, \{u, v\})$ or $(\{n-1\}, \{v\})$.
+Per point 1, $c = n-4$ if and only if $v = n -4$, in which case we get a $(n-4) \rightarrow (n-1)$ plus and the $u \rightarrow n$ plus (if it exists) has already been contributed by $I_{n-2}^V$ and $I_{n-3}^V$.
+If $c = n-5$ then $v < n-5$ and we are in the same situation as $I_{n-2}^V$.
+
+%The third point is also a consequence of \eqref{eq necklace}.
 Let's take the possibilities in turn, first suppose $I_{n-2}^V$ contrbuted an $(n-5)\rightarrow (n-2)$ plus.
@@
 
-  Now in the case that $I_{n-2}^V$ contribued an $(n-4)\rightarrow (n-2)$ plus, then going from $I_{n-2}^V$ to $I_{n-1}^V$ takes out the $n-2$ and puts in the $n-5$, so instead of the $(n-4)\rightarrow (n-2)$ plus and the $(n-5)\rightarrow (n-1)$ plus we have an $(n-4)\rightarrow (n-1)$ plus, but the rest stays the same.
+%Now in the case that $I_{n-2}^V$ contribued an $(n-4)\rightarrow (n-2)$ plus, then going from $I_{n-2}^V$ to $I_{n-1}^V$ takes out the $n-2$ and puts in the $n-5$, so instead of the $(n-4)\rightarrow (n-2)$ plus and the $(n-5)\rightarrow (n-1)$ plus we have an $(n-4)\rightarrow (n-1)$ plus, but the rest stays the same.
 Also, in going from $I_{n-3}^V$ to $I_{n-2}^V$, $n-3$ comes out and $n-2$ goes in so all that changes is a $(n-4)\rightarrow (n-3)$ path becomes an $(n-4)\rightarrow (n-2)$ path.
-\item The only elements which could contribute an $(n-5)$ path are those without an $n-5$.
-From \eqref{eq necklace} the only ones without an $n-5$ are $I_{n-2}^V$, $I_{n-3}^V$, and $I_{n-4}^V$.
-\note{find the right pluss or lack thereof}.
+\item A Grassmann necklace term $I_i^V$ can only contribute a path beginning at $c$ when $c \not\in I_i^V$.
+Further, since $c$ will always be maximal in $I_1^V\setminus I_i^V$ by point 1, a path from $c$ must end at the minimal element of $I_i^V \setminus I_1^V$.
+From \eqref{eq necklace}, the only way we can have $c \not\in I_i^V$ and $n-1$ minimal in $I_i^V \setminus I_1^V$ is if $c = n-4$ and $i = n-1$.
+
+Similarly, the only terms that can contribute an $(n-5) \rightarrow n$ plus are those with $n-5 \in I_i^V$, i.e.
+when $i \in \{n-2,n-3,n-4\}$.
+However, $n-5$ is always the largest or second-largest element in $I_1\setminus I_i^V$, while if $n \in I_i^V \setminus I_1^V$ for $i \in \{n-2,n-3,n-4\}$ then $|I_i^V \setminus I_1^V| \geq 3$ and so $n$ cannot be the smallest or second-smallest in this set.
+Thus there can be no path $(n-5) \rightarrow n$.
   \end{enumerate}
@@
 
-  From Lemma~\ref{lem shape} we know how the shapes of the Le diagrams of $V$ and $W$ are related; let $\mathcal{A}$ and $\mathcal{B}$ be as described in that lLmma and subsequent discussion.
+  From Lemma~\ref{lem shape} we know how the shapes of the Le diagrams of $V$ and $W$ are related; let $\mathcal{A}$ and $\mathcal{B}$ be as described in that lemma and subsequent discussion.
 Lemmas~\ref{lem n and n-1}, \ref{lem n-2 good}, and \ref{lem n-2 bad} tell us that the three boxes of the bottom row of the Le diagram of $W$ each have a plus.
-Lemmas~\ref{lem n and n-1} through \ref{lem other k} show that there is a bijection between the plusses of the Le diagram of $V$ and the plusses of the Le diagram of $W$ that are not in the bottom row.
-This bijection can be described as follows:\note{In the case $n-4\in I_1^V \setminus I_n^V$ then the $ (n-4)\rightarrow (n-1)$ plus is not new in $W$ but instead there is an $(n-5)\rightarrow (n)$ plus in $W$ which gives the third new plus.
-This needs to be added to the proof and the rest adjusted for the bad $n-4$ possiblity.}
+We will use Lemmas~\ref{lem n and n-1} through \ref{lem other k} to construct a bijection between the plusses of the Le diagram of $V$ and the plusses of the Le diagram of $W$ that are not in the bottom row.
+This bijection is defined as follows:
   \begin{itemize}
@@
   \item If there is a plus in the $n-2$ column of $\mathcal{A}$ in $V$ then Lemma~\ref{lem n-2 bad} applies, so there is exactly one such plus.
-This plus is mapped to the $(n-5)\rightarrow (n-1)$ plus for $W$.
+If $n-4 \not\in I_1^V$ then map this plus to the $(n-5)\rightarrow (n-1)$ plus in $W$, whereas if $n-4 \in I_1^V$ then map it to the $(n-5) \rightarrow n$ plus in $W$.
   \item All plusses in the $n-3$ column for $V$ are shifted one square to the left in $\mathcal{A}$ for $W$, i.e. into the $n-2$ column.
   \end{itemize}
-  Note that this map is reversible and hence bijective.
-Indeed, the only possible ambiguity is at the $(n-5)\rightarrow (n-1)$ plus in $W$ (if it exists), which could have come from either of the first or third bullet points.
-However, if the third bullet point applies then by Lemma~\ref{lem n-2 bad} there is no $(n-5)\rightarrow (n-1)$ plus in $V$, i.e.
-the first bullet point does not apply.
-
-  % If the Le diagram for $V$ has a plus in the $n-2$ column then Lemma~\ref{lem n-2 bad} applies.
-By the final part of Lemma~\ref{lem n-2 bad} there is no $n-5\rightarrow n-1$ plus in the Le diagram of $V$, and so the $n-5\rightarrow n-1$ plus of $W$ can be uniquely mapped to the plus in the $n-2$ column of the Le diagram of $V$.
-If the Le diagram for $V$ has no plus in the $n-2$ column, then leave the $n-5\rightarrow n-1$ plus where it is in moving back to $V$.
-This reverses the map.
+The majority of these points are clearly reversible and hence bijective; the only possible ambiguity is the third bullet point.
+In this case we are in the setting of Lemma~\ref{lem n-2 bad}.
+If $n-4 \not\in I_1^V$ there is no plus in the $(n-5) \rightarrow (n-1)$ position in $V$, whereas if $n-4 \in I_1^V$ then there is a plus in this position but no plus in the $(n-5)\rightarrow n$ position.
+In either case, per Lemma~\ref{lem n-2 bad} this is the only new plus in region $\mathcal{A}$ for $W$, so all plusses are accounted for and paired up uniquely with plusses in $V$.
 

### 2019-09-24 GWLDCII.tex
read statements of proofs. added questions

@@
   \begin{enumerate}
-  \item If $n-4 \not\in I_1^V\setminus I_n^V$, then $I_{n-2}^W$ contributes an $(n-3)\rightarrow (n-2)$ plus and an $(n-5)\rightarrow (n-1)$ plus, along with the one plus contributed by $I_n^V$.
+  \item If $n-4 \not\in I_1^V\setminus I_n^V$, then $I_{n-2}^W$ contributes an $(n-3)\rightarrow (n-2)$ plus and an $(n-5)\rightarrow (n-1)$ plus, along with \hlfix{the one}{check wording: 'the one' claims that $I_n^V$ only contributes one plus while 'one' claims that $I_{n-2}^W$ contributes one of the $I_n^V$ pluses} plus contributed by $I_n^V$.
   \item If $n-4 \in I_1^V\setminus I_n^V$, then $I_{n-2}^W$ contributes an $(n-3)\rightarrow (n-2)$ plus, an $(n-4)\rightarrow (n-1)$ plus and a $(n-5)\rightarrow (n)$ plus while $I_n^V$ contributed an $(n-4)\rightarrow (n)$ plus.
@@
 In this situation, apply the dihedral transformation that reflects $W$ along the line perpendicular to the $(n-2){th}$ edge, so that $p$ is unchanged but $q = (n-1,1)$ in the new diagram.
-The new diagram is an example of Case 1.
+The new diagram is an example of Case 1, {\color{violet} i.e.
+satisfying $n-2 \not \in I_{n-2}^V$}.
+\sanote{pull this simplification out ealier (before 4.10), so that when I'm counting cases, I'm not confused as to why this one hasn't been covered.}
 
@@
 If $n-4 \not\in I_1^V$ there is no plus in the $(n-5) \rightarrow (n-1)$ position in $V$, whereas if $n-4 \in I_1^V$ then there is a plus in this position but no plus in the $(n-5)\rightarrow n$ position.
-In either case, per Lemma~\ref{lem n-2 bad} this is the only new plus in region $\mathcal{A}$ for $W$, so all plusses are accounted for and paired up uniquely with plusses in $V$.
+{\color{red} what about the arrow $(n-4)\rightarrow (n-1)$?} In either case, per Lemma~\ref{lem n-2 bad} this is the only new plus in region $\mathcal{A}$ for $W${\color{red} what about the arrows $(n-3)\rightarrow (n-2)$?}, so all plusses are accounted for and paired up uniquely with plusses in $V$.
 

### 2019-09-24 GWLDCII.tex
rephrase statement of lemma 4.6

@@
 Let $V$ and $W$ be as in Lemma~\ref{lem I}.
-Then \hlfix{$I_n^{W}$}{Does $I_n^W$ actually yeild any of the $+$s in $I_n^V$?}\note{I don't remember, but the point is that this is a two way statement, $I_n^W$ nd $I_{n-1}^W$ yield \emph{exacly} the plusses yielded by $I_n^{V}$, and it doesn't really matter which come from $I_n^W$ and which from $I_{n-1}^W$} and $I_{n-1}^{W}$ together yield the same plusses as $I_n^{V}$ did, along with two extra plusses which appear in the leftmost two boxes of the bottom row of the Le diagram of $W$.
+Then
+  %$I_n^{W}$
+  %and $I_{n-1}^{W}$ together yield the same plusses as $I_n^{V}$ did, along with two extra plusses which appear in the leftmost two boxes of the bottom row of the Le diagram of $W$.
+%
+%  Specifically,
+  $I_n^W$ yields an $(n-3)\rightarrow n$ plus and $I_{n-1}^W$ yields an $(n-3)\rightarrow (n-1)$ plus along with any plusses yielded by $I_n^V$.
 \end{lem}

### 2019-09-25 GWLDCII.tex
fixed the (n-2) lemma and edited the theorem

@@
 
-However, it will be important later to observe that $v$ could be $n-4$.
-
-  \begin{lem}\label{lem n-2 bad part 1}
-Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that $n-2,n-1 \in I_{n-2}^{V}$. Then:
-  \begin{enumerate}
-  \item If $n-4 \not\in I_1^V\setminus I_n^V$, then $I_{n-2}^W$ contributes an $(n-3)\rightarrow (n-2)$ plus and an $(n-5)\rightarrow (n-1)$ plus, along with \hlfix{the one}{check wording: 'the one' claims that $I_n^V$ only contributes one plus while 'one' claims that $I_{n-2}^W$ contributes one of the $I_n^V$ pluses} plus contributed by $I_n^V$.
-  \item If $n-4 \in I_1^V\setminus I_n^V$, then $I_{n-2}^W$ contributes an $(n-3)\rightarrow (n-2)$ plus, an $(n-4)\rightarrow (n-1)$ plus and a $(n-5)\rightarrow (n)$ plus while $I_n^V$ contributed an $(n-4)\rightarrow (n)$ plus.
-  \end{enumerate}
-  \end{lem}
-
-  \begin{proof}
-
-Figure \ref{fig new le diagrams} illustrates the cases appearing in this proof.
-
-By Lemma~\ref{lem I} we have $I_1^W = I_1^V\cup \{n-3\}$ and $I_{n-2}^W = (I_n^V \setminus \{n-5\}) \cup \{n-1,n-2\}$.
-By equation \eqref{eq necklace} we have $n-5 \in I_1^V$, and by the following discussion we have $n-1,n-2,n-3 \not\in I_n^V,I_1^V$.
-It follows that the symmetric difference of $I_1^W$ and $I_{n-2}^W$ is:
-    \begin{gather*}
-    I_1^W \setminus I_{n-2}^W = (I_1^V\cup\{n-3\}) \setminus \big((I_n^V\setminus \{n-5\})\cup \{n-1, n-2\}\big) = (I_1^V\setminus I_n^V) \cup \{n-3, n-5\}. \\
-    I_{n-2}^W \setminus I_1^W = \big((I_n^V\setminus \{n-5\})\cup \{n-1, n-2\}\big) \setminus(I_1^V\cup\{n-3\}) = (I_n^V\setminus I_1^V) \cup \{n-1, n-2\}.
-\end{gather*}
-As per the discussion following equation \eqref{eq necklace} above, we also have $I_n^V\setminus I_1^V = \{n\}$ and $I_1^V\setminus I_n^V = \{v\}$.
-If $v \neq n-4$ then the path from $I_n^V$ lies above the paths from $\{n-3, n-5\}$ and $\{n-2, n-1\}$ and we obtain point 1.
-
-Now suppose $n-4\in I_1^V\setminus I_{n}^V$; in this case $I_{n-2}^W$ contributes plusses defined by the noncrossing paths starting from $\{n-3, n-4, n-5\}$ and ending at $\{n, n-1, n-2\}$.
-Comparing this to the above we see that $I_n^V$ contributed the plus from the path $(n-4)\rightarrow (n)$, while $I_{n-2}^W$ contributes the plusses $(n-3)\rightarrow (n-2)$, $(n-4)\rightarrow (n-1)$ and $(n-5)\rightarrow (n)$.
-  \end{proof}
-
-  \begin{figure}
-\includegraphics[width = 12cm]{new_le_diagrams.jpg}
-\caption{Included for reference while we figure out the details; Lemma \ref{lem n-2 bad part 1}}\label{fig new le diagrams}
-  \end{figure}
-
-  \begin{lem}\label{lem n-2 bad part 2}
+However, it is important to observe that $v$ could be $n-4$, as we see in the next result.
+
+  \begin{lem}\label{lem n-2 bad}
     Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that $n-2,n-1 \in I_{n-2}^{V}$. Let $c$ be the largest element of $I_1^V$.  Then:
@@
   \item $I_{n-3}^W$ contributes the same plusses as $I_{n-3}^V$, except that the plus in the $n-3$ column (which necessarily exists) is shifted one square left into the $n-2$ column.
-  \item $I_{n-2}^W$ contributes an $(n-3) \rightarrow (n-2)$ plus, a $c \rightarrow (n-1)$ plus, and one other plus.
-If $c = n-5$ then this third plus is the one contributed by $I_n^V$, while if $c = n-4$ then the third plus is $(n-5) \rightarrow n$ (whereas $I_n^V$ contributed $(n-4) \rightarrow n$).
   \item In the Le diagram of $V$, $I_{n-2}^{V}$ contributes a $c\rightarrow (n-2)$ plus and no other term in the Grassmann necklace of $V$ gives a plus in this column.
 All other plusses from $I_{n-2}^{V}$ were already contributed by $I_{n-3}^V$.
+  \item $I_{n-2}^W$ contributes an $(n-3) \rightarrow (n-2)$ plus, a $c \rightarrow (n-1)$ plus, and one other plus.
+If $c = n-5$ then this third plus is the one contributed by $I_n^V$, while if $c = n-4$ then the third plus is $(n-5) \rightarrow n$.
   \item If $c = n-4$ then $I_{n-1}^V$ contributes a $(n-4) \rightarrow (n-1)$ plus; all other plusses contributed by $I_{n-1}^V$ were already contributed by $I_{n-3}^V$, regardless of the value of $c$.
@@
 
-\item This is just the statement of the previous lemma folded back into this one; if we decide to move it back here then we can just copy the proof over.
-
 \item From equation \eqref{eq necklace} the pair of sets $(I_{n-2}^V\setminus I_1^V, I_1^V\setminus I_{n-2}^V)$ is either $(\{n-2, n-1, n\}, \{n-5, u, v\})$ (if $n \in I_{n-2}^V$) or $(\{n-2, n-1\}, \{n-5, v\})$ (if $n \not\in I_{n-2}^V$, i.e.
@@
 
-\item Combining equation \eqref{eq necklace} with the previous point, the pair $(I_{n-1}^V \setminus I_1^V, I_1^V \setminus I_{n-1}^V)$ is either $(\{n-1, n\}, \{u, v\})$ or $(\{n-1\}, \{v\})$.
+\item By Lemma~\ref{lem I} we have $I_1^W = I_1^V\cup \{n-3\}$ and $I_{n-2}^W = (I_n^V \setminus \{n-5\}) \cup \{n-1,n-2\}$.
+By equation \eqref{eq necklace} we have $n-5 \in I_1^V$, and by the following discussion we have $n-1,n-2,n-3 \not\in I_n^V,I_1^V$.
+It follows that the symmetric difference of $I_1^W$ and $I_{n-2}^W$ is
+    \begin{gather*}
+    I_1^W \setminus I_{n-2}^W  = (I_1^V\setminus I_n^V) \cup \{n-3, n-5\}. \\
+    I_{n-2}^W \setminus I_1^W  = (I_n^V\setminus I_1^V) \cup \{n-1, n-2\}.
+\end{gather*}
+As per the discussion following equation \eqref{eq necklace} above, we also have $I_n^V\setminus I_1^V = \{n\}$ and $I_1^V\setminus I_n^V = \{v\}$.
+If $c = n-5$ then the path $v \rightarrow n$ from $I_n^V$ does not intersect with the paths from $\{n-3, n-5\}$ to $\{n-2, n-1\}$ and we obtain the plusses as stated.
+
+Now suppose $c = v= n-4$; in this case $I_{n-2}^W$ contributes plusses defined by the noncrossing paths starting from $\{n-3, n-4, n-5\}$ and ending at $\{n, n-1, n-2\}$.
+Thus $I_n^V$ contributed the plus from the path $(n-4)\rightarrow (n)$, while $I_{n-2}^W$ contributes the plusses $(n-3)\rightarrow (n-2)$, $(n-4)\rightarrow (n-1)$ and $(n-5)\rightarrow (n)$.
+
+\item Combining equation \eqref{eq necklace} with point 3 of this proof, the pair $(I_{n-1}^V \setminus I_1^V, I_1^V \setminus I_{n-1}^V)$ is either $(\{n-1, n\}, \{u, v\})$ or $(\{n-1\}, \{v\})$.
 Per point 1, $c = n-4$ if and only if $v = n -4$, in which case we get a $(n-4) \rightarrow (n-1)$ plus and the $u \rightarrow n$ plus (if it exists) has already been contributed by $I_{n-2}^V$ and $I_{n-3}^V$.
@@
 
-%The third point is also a consequence of \eqref{eq necklace}.
-Let's take the possibilities in turn, first suppose $I_{n-2}^V$ contrbuted an $(n-5)\rightarrow (n-2)$ plus.
-In this case, going from $I_{n-2}^V$ to $I_{n-1}^V$ takes out the $n-2$ and puts in the $n-5$, so  nothing else changes, while going from $I_{n-3}^V$ to $I_{n-2}^V$ swapped the $n-3$ for the $n-2$, but $n-3\in I_1^V$, so nothing changes from $I_{n-3}^V$ to $I_{n-2}^V$ except changing a $(n-5)\rightarrow (n-3)$ path to $(n-5)\rightarrow (n-2)$.
-
-%Now in the case that $I_{n-2}^V$ contribued an $(n-4)\rightarrow (n-2)$ plus, then going from $I_{n-2}^V$ to $I_{n-1}^V$ takes out the $n-2$ and puts in the $n-5$, so instead of the $(n-4)\rightarrow (n-2)$ plus and the $(n-5)\rightarrow (n-1)$ plus we have an $(n-4)\rightarrow (n-1)$ plus, but the rest stays the same.
-Also, in going from $I_{n-3}^V$ to $I_{n-2}^V$, $n-3$ comes out and $n-2$ goes in so all that changes is a $(n-4)\rightarrow (n-3)$ path becomes an $(n-4)\rightarrow (n-2)$ path.
 \item A Grassmann necklace term $I_i^V$ can only contribute a path beginning at $c$ when $c \not\in I_i^V$.
@@
 
-\begin{proof}
-  By Lemma~\ref{lem I} we have $I_{n-2}^{W}= (I_{n}^{V} \setminus \{n-5\})\cup \{n-1,n-2\}$ and $I_1^W = I_1^V\cup \{n-3\}$.
-Furthermore, we are necessarily case 2 of Figure~\ref{fig special p}, with a further propagator $r$ ending on the edge $n-1$, satisfying $I_{n-2}^V(r) = n-1$ (that is, $r$ is the clockwise most on this edge).
-\st{We can see from the location of $q$ that $n-2\not\in I_{n-3}^{V}$} and that $n-5$ is the label of the last row in $\mathcal{B}$.\sanote{is there an easy way to see these?
-Why can't $I_1^V(q) = n-4$, which would make this the last row of $\mathcal{B}$}\note{This is a good point; what if that propagator $r$ went from edge $n-1$ to edge $n-5$?
-Karen, do you remember why this can't happen?} {\color{violet}From the figure we see that $I_{n-3}^V = n-3$.
-In particular, this means that $n-2 \not \in I_{n-3}^V$.
-} \st{Also note that by Lemma {\ref{vertex cyclic int lem}} and Corollary {\ref{no coloops}} we must have } {\color{violet} Since $r$ is the clockwise most propagator on edge $n-1$, $I_n^V(q) = n$, i.e.} $n\in I_n^V$.Thus this section of the Grassmann necklace of $V$ looks like
-
-  \begin{equation}\label{eq necklace}
-  I_{n-3}^{V} \xrightarrow[\substack{n-3\text{ out}\\n-2\text{ in}}]{} I_{n-2}^{V} \xrightarrow[\substack{n-2\text{ out}\\n-5\text{ in}}]{} I_{n-1}^{V} \xrightarrow[\substack{n-1\text{ out}\\\text{something in}}]{} I_{n}^{V}  \xrightarrow[\substack{n \text{ out}\\\text{something in}}]{} I_1^{V}
-  \end{equation}
-  where the first ``something'' is either $n$ or an element of $I_1^{V}$, and the second ``something'' is an element of $I_1^{V}$.
-
-  \begin{figure}
-    \[\includegraphics{messy}\]
-    \caption{Plusses coming from $I_{n-2}^{V}$ (top left), $I_{n-1}^{V}$ (top right), and $I_n^V$ (bottom row), in the case where ${n-1, n-2\in I_{n-2}^{V}}$.
-The blue lines are the non-intersecting paths defining the position of the plusses.
-The dashed blue lines may or may not appear, but if one appears then they both do.}\label{fig messy}
-  \end{figure} \sanote{can we put the diagrams labels in bold or set them apart somehow so that it is easier to see?
-Esp since they are located in a different part of the diagram for $I_n^V$?}\note{That's going to come down to journal style in the end, so only do it if it is easy and you know how to do it by an appropriate option}
-
-  Using this information we can determine the symmetric difference of $I_{n-2}^{V}$ and $I_1^{V}$.
-Note that $I_{n-2}^V\setminus I_1^V$ and $I_1^V\setminus I_{n-2}^V$ each have size $\leq 3$ by the definition of a Grassmann necklace.
-We have $n-1, n-2 \in I_{n-2}^{V} \setminus I_1^V$ for certain, and the third element (if it exists) must be $n$.
-On the other hand we have $n-5 \in I_1^{V} \setminus I_{n-2}^V$, along with at least one and at most two other elements.
-Call the larger (possibly only) of these other elements $a$ with $n-5 > a$.
-If there are two such elements, call the smaller $b$ such that $n-5>a>b$.
-
-  This means that the plusses in the Le diagram of $V$ coming from $I_{n-2}^{V}$ are as in the top left diagram in Figure~\ref{fig messy}.
-Stepping to $I_{n-1}^{V}$ in display \eqref{eq necklace} simply removes the $(n-5)\rightarrow (n-2)$ path (top right diagram of Figure~\ref{fig messy}), so $I_{n-1}^V$ contributes no new information about the Le diagram of $V$.
-
-  %Stepping to $I_{n}^{V}$, $n-1$ is removed and either $n$ is put in if it was not there before, or one of $a$ or $b$ is put in and hence is no longer available as the starting point for a path.
-This gives two possible configurations illustrated in the bottom two parts of Figure~\ref{fig messy}.
-
-  With this information in hand, we can now tackle the points in the statement of the lemma. We know that 
-  \[I_{n-2}^{W}  = (I_{n}^{V} - \{n-5\})\cup \{n-1,n-2\}, \quad n-5 \in I_1^W, \quad n-3\not\in I_{n-2}^W,\]
- and so the paths for building plusses from $I_{n-2}^{W}$ start at
- \[I_1^W \setminus I_{n-2}^W = \{n-3,n-5\} \cup (I_1^V \setminus I_n^V)\]
- and end at
- \[I_{n-2}^W \setminus I_1^W = \{n-2,n-1\}\cup(I_n^V \setminus I_1^V).\]
-This means that $I_{n-2}^W$ contributes plusses as in Figure~\ref{fig messyD}, while $I_n^V$ contributes as in the bottom line of Figure~\ref{fig messy}, which proves point (1) and most of point (3).
-From equation \eqref{eq necklace} we see that $n-2$ appears only in $I_{n-2}^V$, so no other Grassmann necklace term for $V$ can contribute a plus in the $n-2$ column; this completes the proof of item (3).
-
-  \begin{figure}
-     \[\includegraphics{messyD}\]
-    \caption{Plusses coming from $I_{n-2}^{W}$.}\label{fig messyD}
-  \end{figure}
-
-Now consider $I_{n-3}^{V}$.
-By equation~\eqref{eq necklace} $I_{n-3}^{V}$ contributes almost the same plusses as $I_{n-2}^{V}$: the only difference is that it contributes an $(n-5)\rightarrow (n-3)$ plus in place of the $(n-5)\rightarrow (n-2)$ plus.
-Since we must have $n-3\in I_{n-3}^{V}$ (because the propagator $q$ exists in $V$), it follows from Lemma~\ref{lem I} that $I_{n-3}^{W} = I_{n-3}^{V}\cup\{n-2\}$.
-Thus the paths for $I^{W}_{n-3}$ are the same as those for $I^{V}_{n-3}$ except that the path that did go to $n-3$ now goes to $n-2$.
-This cannot conflict with another path since equation~\eqref{eq necklace} shows that $n-2$ only appears in $I_{n-2}^{V}$ among the necklace elements of $V$.
-
-This proves point (2), and combined with the observation above that $I_{n-1}^V$ contributes no new plusses compared to $I_{n-2}^V$, we also obtain item (4).
-
-  Finally, if the Le diagram of $V$ did admit a $(n-5)\rightarrow (n-1)$ plus, it could only have been contributed by a necklace term that doesn't contain $n-5$.
-By equation \eqref{eq necklace} the only terms that could have this property are $I_{n-2}^{V}$, $I_{n-3}^{V}$, and $I_{n-4}^{V}$, and the analysis above shows that $I_{n-2}^V$ and $I_{n-3}^V$ do not contribute a plus in this position.
-
-\hlfix{Recall that $n-5$ is the largest row index}{why not $n-4$?
-(also asked above)} in the Le diagram of $V$, and $n-5 \in I_1^V \setminus I_{n-4}^V$ so $I_{n-4}^V$ must contribute a path starting at $n-5$.
-Since $n-4 \in I_{n-4}^V$ by the location of the propagator $q$, we must also have a path ending at $n-4$.
-Since the paths cannot cross, this implies that $I_{n-4}^V$ must contribute a $(n-5) \rightarrow (n-4)$ plus, and hence cannot contribute a $(n-5)\rightarrow (n-1)$ plus.
-This proves point (5) and completes the proof of the lemma.
-\end{proof}
-\sanote{may want a chance to reread this lemma after questions have been answered}
-
 \begin{lem}\label{lem other k}
@@
   From Lemma~\ref{lem shape} we know how the shapes of the Le diagrams of $V$ and $W$ are related; let $\mathcal{A}$ and $\mathcal{B}$ be as described in that lemma and subsequent discussion.
-Lemmas~\ref{lem n and n-1}, \ref{lem n-2 good}, and \ref{lem n-2 bad} tell us that the three boxes of the bottom row of the Le diagram of $W$ each have a plus.
-We will use Lemmas~\ref{lem n and n-1} through \ref{lem other k} to construct a bijection between the plusses of the Le diagram of $V$ and the plusses of the Le diagram of $W$ that are not in the bottom row.
-This bijection is defined as follows:
+
+  Lemmas~\ref{lem n and n-1}, \ref{lem n-2 good}, and \ref{lem n-2 bad} tell us that the three boxes of the bottom row of the Le diagram of $W$ each have a plus: we will view these as the three ``new'' plusses required by the induction step and use Lemmas~\ref{lem n and n-1} through \ref{lem other k} to construct a pairing between the plusses of the Le diagram of $V$ and the plusses of the Le diagram of $W$ that are not in the bottom row.
+See Figure~\ref{fig:le diagrams bijection}.
+
+ The pairing is defined as follows:
   \begin{itemize}
-  \item All plusses from $\mathcal{B}$ for $V$ maintain their positions in $\mathcal{B}$ for $W$.
-  \item All plusses from the leftmost two columns (the $n$ and the $n-1$ columns) of $\mathcal{A}$ for $V$ maintain their positions in $\mathcal{A}$ for $W$.
-  \item If there is a plus in the $n-2$ column of $\mathcal{A}$ in $V$ then Lemma~\ref{lem n-2 bad} applies, so there is exactly one such plus.
-If $n-4 \not\in I_1^V$ then map this plus to the $(n-5)\rightarrow (n-1)$ plus in $W$, whereas if $n-4 \in I_1^V$ then map it to the $(n-5) \rightarrow n$ plus in $W$.
-  \item All plusses in the $n-3$ column for $V$ are shifted one square to the left in $\mathcal{A}$ for $W$, i.e. into the $n-2$ column.
+  \item The plusses in the $\mathcal{B}$ region of both Le diagrams are identical, so each plus in this region is paired with itself.
+  \item Every square containing in a plus in the leftmost two columns (the $n$ and the $n-1$ columns) of $\mathcal{A}$ for $V$ also contains a plus in $W$, so these plusses are also paired with themselves.
+  \item The plusses in the $n-3$ column for $V$ are paired with the corresponding plusses in the $n-2$ column for $W$.
+  \item If there is a plus in the $n-2$ column of $\mathcal{A}$ in $V$ then Lemma~\ref{lem n-2 bad} applies, so there is exactly one such plus in this column.
+If $n-4 \not\in I_1^V$ then pair this plus with the $(n-5)\rightarrow (n-1)$ plus in $W$, whereas if $n-4 \in I_1^V$ then pair it with the $(n-5) \rightarrow n$ plus in $W$.
+
   \end{itemize}
-The majority of these points are clearly reversible and hence bijective; the only possible ambiguity is the third bullet point.
-In this case we are in the setting of Lemma~\ref{lem n-2 bad}.
-If $n-4 \not\in I_1^V$ there is no plus in the $(n-5) \rightarrow (n-1)$ position in $V$, whereas if $n-4 \in I_1^V$ then there is a plus in this position but no plus in the $(n-5)\rightarrow n$ position.
-{\color{red} what about the arrow $(n-4)\rightarrow (n-1)$?} In either case, per Lemma~\ref{lem n-2 bad} this is the only new plus in region $\mathcal{A}$ for $W${\color{red} what about the arrows $(n-3)\rightarrow (n-2)$?}, so all plusses are accounted for and paired up uniquely with plusses in $V$.
+The first three points follow immediately from Lemmas \ref{lem n and n-1} through \ref{lem other k}.
+If $n-2 \not\in I_{n-2}^V$ by Lemma~\ref{lem n-2 good} there are no plusses in column $n-2$ of the diagram of $V$, and all plusses have been accounted for.
+If $n-2 \in I_{n-2}^V$ then we are in the setting of Lemma~\ref{lem n-2 bad}, and there is exactly one plus in column $n-2$ of the diagram of $V$; it is paired with the one plus in $W$ yet unaccounted for, as described in points 4 and 6 of that lemma.
 
@@
 \end{proof}
+
+\begin{figure}
+\includegraphics[width=12cm]{new_le_diagrams.jpg}
+\caption{The Le diagrams for $V$ and $W$ in the setting of Theorem~\ref{thm dim}.
+The shaded regions indicate where the plusses match up perfectly, the red plusses exist if and only if $n-2 \in I_{n-2}^V$, and the blue plusses are the three new plusses coming from the induction step.}\label{fig:le diagrams bijection}
+\end{figure}
 

### 2019-09-25 GWLDCII.tex
my part from the notes file

@@
 
+The next several lemmas assume $V$ and $W$ to be as above.
+They discuss how the shape of the Le diagram changes from $V$ to $W$ and how the plusses in $V$ shift to become plusses in $W$.
+In particular, the Le diagram for $W$ has an extra row with three columns labeled by $n-3$ (see Figure \ref{fig Le} and Lemma \ref{lem shape}).
+This last row contains three (new) plusses.
+All other plusses in the Le diagram of $V$ shift in a predictable manner to become plusses in the Le diagram of $W$.
+(See Lemmas \ref{lem n and n-1} to Theorem \ref{thm dim}.
+
+We proceed to address the cases laid out in \ref{lem I}, getting the shape of the Le diagram of $W$ from the relation $I_n^W= I_n^V \cup {n-3}$.
+
 \begin{lem}\label{lem shape}
@@
 \end{proof}
+
+In the next two lemmas, we consider the plusses contributed to the Le diagram of $W$ by $I_{n-2}^W$.
+
+\begin{rmk}\label{rem n-2 case} Note that we need not consider the case when $n-2 \in \in I_{n-2}^V$ but $n-1 \not\in I_{n-2}^V$ laid out in Lemma \ref{lem I}.
+This case can only occur if our $W$ is in Case 2 of Figure~\ref{fig special p} and $n-1$ supports no propagators other than $p$.
+In this situation, apply the dihedral transformation that reflects $W$ along the line perpendicular to the $(n-2)^{th}$ edge, so that $p$ is unchanged but $q = (n-1,1)$ in the new diagram.
+The new diagram is an example of Case 1, i.e.
+satisfying $n-2 \not \in I_{n-2}^V$.
+Therefore, for the rest of this section, we only consider the situation where if $n-2 \in I_{n-2}^V$ then $n-1 \in I_{n-1}^V$.
+\end{rmk}
 
@@
 
-We make one further simplification in order to eliminate the possibility that $n-2 \in I_{n-2}^V$ but $n-1 \not\in I_{n-2}^V$, which can only occur if our $W$ is in Case 2 of Figure~\ref{fig special p} and $n-1$ supports no propagators other than $p$.
+%We make one further simplification in order to eliminate the possibility that $n-2 \in I_{n-2}^V$ but $n-1 \not\in I_{n-2}^V$, which can only occur if our $W$ is in Case 2 of Figure~\ref{fig special p} and $n-1$ supports no propagators other than $p$.
 In this situation, apply the dihedral transformation that reflects $W$ along the line perpendicular to the $(n-2){th}$ edge, so that $p$ is unchanged but $q = (n-1,1)$ in the new diagram.
@@
 
-In summary, $W$ is a diagram with one of the two configurations depicted in Figure~\ref{fig special p}, and if $n-2 \in I_{n-2}^V$ then $n-1 \in I_{n-1}^V$ as well. Let $V$ be $W$ with $p$ removed.
+Note that by Remark \ref{rem n-2 case}, we only need to consider when $W$ is a diagram with one of the two configurations depicted in Figure~\ref{fig special p}, and if $n-2 \in I_{n-2}^V$ then $n-1 \in I_{n-1}^V$ as well.
+Let $V$ be $W$ with $p$ removed.
 
@@
 
-  Lemmas~\ref{lem n and n-1}, \ref{lem n-2 good}, and \ref{lem n-2 bad} tell us that the three boxes of the bottom row of the Le diagram of $W$ each have a plus: we will view these as the three ``new'' plusses required by the induction step and use Lemmas~\ref{lem n and n-1} through \ref{lem other k} to construct a pairing between the plusses of the Le diagram of $V$ and the plusses of the Le diagram of $W$ that are not in the bottom row.
+  Lemmas~\ref{lem n and n-1}, \ref{lem n-2 good}, and \ref{lem n-2 bad} tell us that the three boxes of the bottom row of the Le diagram of $W$ each have a plus, i.e.
+there are plusses in the positions $(n-3) \rightarrow (n-2)$, $(n-3) \rightarrow (n-1)$ and $(n-3) \rightarrow n$.
+We will view these as the three ``new'' plusses required by the induction step and use Lemmas~\ref{lem n and n-1} through \ref{lem other k} to construct a pairing between the plusses of the Le diagram of $V$ and the plusses of the Le diagram of $W$ that are not in the bottom row.
 See Figure~\ref{fig:le diagrams bijection}.
@@
 If $n-2 \not\in I_{n-2}^V$ by Lemma~\ref{lem n-2 good} there are no plusses in column $n-2$ of the diagram of $V$, and all plusses have been accounted for.
-If $n-2 \in I_{n-2}^V$ then we are in the setting of Lemma~\ref{lem n-2 bad}, and there is exactly one plus in column $n-2$ of the diagram of $V$; it is paired with the one plus in $W$ yet unaccounted for, as described in points 4 and 6 of that lemma.
+If $n-2 \in I_{n-2}^V$ then we are in the setting of Lemma~\ref{lem n-2 bad}, and there is exactly one plus in column $n-2$ of the diagram of $V$; it is paired with the one plus in $W$ yet unaccounted for: namely those in positions $(n-5) \rightarrow n$ or $(n-5) \rightarrow (n-1)$, as described in points 4 and 6 of that lemma.
 

### 2019-09-28 GWLDCII.tex
read 4.6 to end of section

@@
 As with the Amplituhedron, each Wilson loop represents the sum of a family of $N^kMHV$ Feynman diagrams, and adding up the corresponding sums of Feynman integrals associates a volume form to a convex space different from the Amplituhedron \cite{Hodges2013}.
-Agarwala and Marin-Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that can be realized as an element of $\Gr(k,n)$ \cite{wilsonloop}, while other work has shown a connection between the volume filled by Wilson loop diagrams and the Amplituhedron \cite{casestudy, Amplituhedronsquared}.
+Agarwala and Marin-Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that can be realized as an element of $\Gr(k,n)$ \cite{wilsonloop}.
+Other work has shown a connection between the volume filled by Wilson loop diagrams and the Amplituhedron \cite{casestudy, Amplituhedronsquared}.
+Specifically, Marcott shows that the space parametrized by the Wilson loop diagrams is  exactly the correct positroid cell in $\Gr(k,n)$, up to a set of measure $0$ \cite{WLDdim}.
 
@@
 The matrix $C(W)$ defines a positroid cell associated to $W$ in the positive Grassmannian $\Gr(n, |\cP|)$, which we denote by $\Sigma(W)$ \cite{wilsonloop}.
+Marcott \cite{WLDdim} shows that  the matrix $C(W)$ parametrizes a space whose close is exactly the closure of $\Sigma(W)$.
+That is, the space defined by $C(W)$ and the cell $\Sigma(W)$ agree up to a set of measure $0$.
 Most of the work in this paper, and in \cite{generalcombinatoricsI} focuses on characterizing the positroid cell associated to each Wilson loop diagram $W$.
@@
 By Remark~\ref{rmk cyclic} we know that $I_{n-1}^W(q) = n-5$, leaving no propagators supported on $n-4$ for $I_{n-1}^W$ to assign.
-Thus $n-4 \not\in I_{n-1}^W$, and since $I_{n-1}^W = I_n^V\cup\{n-1\}$ by Lemma~\ref{lem I}, we cannot have $n-4$ in $I_n^V$ either.
+Thus $n-4 \not\in I_{n-1}^W$.
+Since $I_{n-1}^W = I_n^V\cup\{n-1\}$ by Lemma~\ref{lem I}, we cannot have $n-4$ in $I_n^V$ either.
 
@@
   If $n-3\in I_{k}^{V}$ then $I_k^V$ must contribute a plus in the $n-3$ column of the Le diagram of $V$, and by Lemma~\ref{lem I} we have $I_{k}^{W} = I_k^{V}\cup \{n-2\}$.
-If $n-2$ supports no propagators in $V$ then certainly no plusses appear in the $n-2$ column of the Le diagram of $V$.
+If $n-2$ supports no propagators in $V$ then no plusses appear in the $n-2$ column of the Le diagram of $V$.
 If $n-2$ supports at least one propagator in $V$ then $n-2 \in I_{n-2}^V$ and so by hypothesis $n-1 \in I_{n-2}^V$ as well.
-By Lemma~\ref{lem n-2 bad}, the only necklace element of $V$ containing $n-2$ is $I_{n-2}^{V}$ and the corresponding plus is not contributed to the Le diagram of $W$ by $I_{n-2}^{W}$.
+By Lemma~\ref{lem n-2 bad}, the only necklace element of $V$ containing $n-2$ is $I_{n-2}^{V}$ and \hlfix{the corresponding plus is not contributed to the Le diagram of $W$ by $I_{n-2}^{W}$.}{Lemma {\ref{lem n-2 bad}} point 4 says that  $I_{n-2}^W$ contributes a + in the n-2 column and point 3 says that $I_{n-2}^W$ contributes a + in the n-2 column.
+Are we talking about $n-1$ column?}
 
   Since $n-3 \in I_k^V \setminus I_1^V$, we must have a path in the Le diagram of $V$ from some vertical edge $i$ to the bottom edge $n-3$.
-In the Le diagram of $W$, the index $n-3$ labels a vertical edge with no path starting at it (since $n-3$ belongs to both $I_1^W$ and $I_k^W$), and there must be a path leading to $n-2$ since $n-2 \in I_k^W \setminus I_1^W$.
+In the Le diagram of $W$, the index $n-3$ labels a vertical edge with no path \hlfix{starting at it}{coming from $I_k^W$.
+There are 3 paths starting here in the Le diagram as a whole} (since $n-3$ belongs to both $I_1^W$ and $I_k^W$), and there must be a path leading to $n-2$ since $n-2 \in I_k^W \setminus I_1^W$.
 By the previous paragraph no other path from $I_k^V$ could end at $n-2$, and since the paths cannot cross we conclude that the $i\rightarrow (n-3)$ path in the Le diagram of $V$ must become a $i\rightarrow (n-2)$ path in the Le diagram of $W$.
@@
    Thus the plus contributed by $I_k^V$ in the $n-3$ column of the Le diagram of $V$ is shifted into the $n-2$ column in the Le diagram for $W$, where there was no plus before, and no other plusses are changed.
-\end{proof}
+\end{proof} \todo{I am still very confused by this proof, possibly due to my misunderstanding of first highlighted comment}
 
@@
 
-Note that by Remark \ref{rem n-2 case}, we only need to consider when $W$ is a diagram with one of the two configurations depicted in Figure~\ref{fig special p}, and if $n-2 \in I_{n-2}^V$ then $n-1 \in I_{n-1}^V$ as well.
+We consider the two cases of propagator configurations $W$ depicted in Figure~\ref{fig special p}.
+Note that by Remark \ref{rem n-2 case}, we need only consder the situation that if $n-2 \in I_{n-2}^V$ then $n-1 \in I_{n-1}^V$ as well.
 Let $V$ be $W$ with $p$ removed.
@@
   \item The plusses in the $\mathcal{B}$ region of both Le diagrams are identical, so each plus in this region is paired with itself.
-  \item Every square containing in a plus in the leftmost two columns (the $n$ and the $n-1$ columns) of $\mathcal{A}$ for $V$ also contains a plus in $W$, so these plusses are also paired with themselves.
+  \item Every square containing a plus in the leftmost two columns (the $n$ and the $n-1$ columns) of $\mathcal{A}$ for $V$ also contains a plus in $W$, so these plusses are also paired with themselves.
   \item The plusses in the $n-3$ column for $V$ are paired with the corresponding plusses in the $n-2$ column for $W$.

### 2019-10-01 GWLDCII.tex
some typos and small wording changes and some comments to discuss today

--- 2019-09-25 GWLDCII.tex
@@
 They discuss how the shape of the Le diagram changes from $V$ to $W$ and how the plusses in $V$ shift to become plusses in $W$.
-In particular, the Le diagram for $W$ has an extra row with three columns labeled by $n-3$ (see Figure \ref{fig Le} and Lemma \ref{lem shape}).
+In particular, the Le diagram for $W$ has an extra row, labeled by $n-3$, with three columns (see Figure \ref{fig Le} and Lemma \ref{lem shape}).
 This last row contains three (new) plusses.
@@
 Explicitly, $\mathcal{B}$ is the set of columns with labels $v < n-3$ and $\mathcal{A}$ is the set of columns labeled by $n$, $n-1$ and $n-2$ in $V$.
-In $W$, $\mathcal{A}$ consists of these columns without the last row.
+In $W$ we see that $\mathcal{A}$ consists of these columns without the last row.
 Over the course of the next few lemmas we will prove that the plusses in the $\mathcal{B}$ parts of each diagram are identical, and that the relationship between the plusses in the two $\mathcal{A}$ regions can be described explicitly.
@@
 
-\begin{rmk}\label{rem n-2 case} Note that we need not consider the case when $n-2 \in \in I_{n-2}^V$ but $n-1 \not\in I_{n-2}^V$ laid out in Lemma \ref{lem I}.
+\begin{rmk}\label{rem n-2 case} Note that we need not consider the case when $n-2 \in I_{n-2}^V$ but $n-1 \not\in I_{n-2}^V$ even though this possibility appears in Lemma \ref{lem I}.
 This case can only occur if our $W$ is in Case 2 of Figure~\ref{fig special p} and $n-1$ supports no propagators other than $p$.
@@
 Therefore, for the rest of this section, we only consider the situation where if $n-2 \in I_{n-2}^V$ then $n-1 \in I_{n-1}^V$.
+\note{But then immediately in the next lemma we don't...}
 \end{rmk}
@@
   Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that $n-2 \not\in I_{n-2}^{V}$.
-Then $I_{n-2}^{W}$ contributes all of the same plusses as $I_{n-1}^{V}=I_{n-2}^{V}$, along with a new $(n-3)\rightarrow (n-2)$ plus.
+Then $I_{n-2}^{W}$ contributes all of the same plusses as $I_{n-1}^{V}=I_{n-2}^{V}$, along with a new $(n-3)\rightarrow (n-2)$ plus.\note{Has this been rephrased?
+Could we discuss?}
 \end{lem}
@@
 
-Note that neither $u$ nor $v$ can be $n-1$, $n-2$, or $n-3$, because as noted in Lemma~\ref{lem I} these elements do not belong to $I_1^V$ and $I_n^V = (I_1^V\setminus \{v\}) \cup \{n\}$.
+Note that neither $u$ nor $v$ can be $n-1$, $n-2$, or $n-3$, because, as noted in Lemma~\ref{lem I}, these elements do not belong to $I_1^V$ and $I_n^V = (I_1^V\setminus \{v\}) \cup \{n\}$.
 However, $u$ could be $n$.
@@
   \begin{lem}\label{lem n-2 bad}
-    Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that $n-2,n-1 \in I_{n-2}^{V}$. Let $c$ be the largest element of $I_1^V$.  Then:
+    Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that $n-2,n-1 \in I_{n-2}^{V}$. Let $c$ be the largest element of $I_1^V$.  Then:\note{This is a small grammar problem}
     \begin{enumerate}
@@
   \item $I_{n-3}^W$ contributes the same plusses as $I_{n-3}^V$, except that the plus in the $n-3$ column (which necessarily exists) is shifted one square left into the $n-2$ column.
-  \item In the Le diagram of $V$, $I_{n-2}^{V}$ contributes a $c\rightarrow (n-2)$ plus and no other term in the Grassmann necklace of $V$ gives a plus in this column.
+  \item In the Le diagram of $V$, $I_{n-2}^{V}$ contributes a $(c)\rightarrow (n-2)$ plus and no other term in the Grassmann necklace of $V$ gives a plus in this column.
 All other plusses from $I_{n-2}^{V}$ were already contributed by $I_{n-3}^V$.
-  \item $I_{n-2}^W$ contributes an $(n-3) \rightarrow (n-2)$ plus, a $c \rightarrow (n-1)$ plus, and one other plus.
+  \item $I_{n-2}^W$ contributes an $(n-3) \rightarrow (n-2)$ plus, a $(c) \rightarrow (n-1)$ plus, and one other plus.
 If $c = n-5$ then this third plus is the one contributed by $I_n^V$, while if $c = n-4$ then the third plus is $(n-5) \rightarrow n$.
   \item If $c = n-4$ then $I_{n-1}^V$ contributes a $(n-4) \rightarrow (n-1)$ plus; all other plusses contributed by $I_{n-1}^V$ were already contributed by $I_{n-3}^V$, regardless of the value of $c$.
-  \item The Grassmann necklace of $V$ contributes a $c\rightarrow (n-1)$ plus if and only if $c = n-4$. No term in the Grassmann necklace of $V$ contributes a $(n-5) \rightarrow n$ plus.
+  \item The Grassmann necklace of $V$ contributes a $(c)\rightarrow (n-1)$ plus if and only if $c = n-4$.
+No term in the Grassmann necklace of $V$ contributes a $(n-5) \rightarrow n$ plus.\note{Could we briefly discuss these potentially spurious parens I added}
   \end{enumerate} 
@@
 
-Recall that we cannot have $u = n-4$ (since $n-4 \notin I_n^V$) so either $u = n$ or $u < n-5$, and either way $n-2$ is minimal in $I_{n-2}^V\setminus I_1^V$ and $c$ is maximal in $I_1^V \setminus I_{n-2}^V$, yielding a $c \rightarrow (n-2)$ plus.
+Recall that we cannot have $u = n-4$ (since $n-4 \notin I_n^V$) so either $u = n$ or $u < n-5$, and either way $n-2$ is minimal in $I_{n-2}^V\setminus I_1^V$ and $c$ is maximal in $I_1^V \setminus I_{n-2}^V$, yielding a $(c) \rightarrow (n-2)$ plus.
 
@@
   Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that if $n-2\in I_{n-2}^{V}$ then $n-1\in I_{n-2}^{V}$ also.
-Then for each $k$ in the range $1<k<n-2$, $I_k^{W}$ contributes the same plusses as $I_{k}^{V}$, except that if $I_{k}^{V}$ contributed a plus in the $n-3$ column of the Le diagram of $V$ then this plus is shifted one square left in the Le diagram of $W$, and no plus was already in that location in the Le diagram of $W$.
+Then for each $k$ in the range $1<k<n-2$, $I_k^{W}$ contributes the same plusses as $I_{k}^{V}$, except that if $I_{k}^{V}$ contributed a plus in the $n-3$ column of the Le diagram of $V$ then this plus is shifted one square left in the Le diagram of $W$, and no plus was already in that location in the Le diagram of $W$.\note{should that last $W$ be a $V$?}
 \end{lem}

### 2019-10-01 GWLDCII.tex
some more typos and minor wording changes

@@
 They discuss how the shape of the Le diagram changes from $V$ to $W$ and how the plusses in $V$ shift to become plusses in $W$.
-In particular, the Le diagram for $W$ has an extra row, labeled by $n-3$, with three columns (see Figure \ref{fig Le} and Lemma \ref{lem shape}).
+In particular, the Le diagram for $W$ has an extra row, labeled by $n-3$, with three columns (see Figure~\ref{fig Le} and Lemma~\ref{lem shape}).
 This last row contains three (new) plusses.
-All other plusses in the Le diagram of $V$ shift in a predictable manner to become plusses in the Le diagram of $W$.
-(See Lemmas \ref{lem n and n-1} to Theorem \ref{thm dim}.
-
-We proceed to address the cases laid out in \ref{lem I}, getting the shape of the Le diagram of $W$ from the relation $I_n^W= I_n^V \cup {n-3}$.
+All other plusses in the Le diagram of $V$ shift in a predictable manner to become plusses in the Le diagram of $W$; this is described in Lemmas~\ref{lem n and n-1} to Theorem~\ref{thm dim}.
+
+We proceed to address the cases laid out in Lemma~\ref{lem I}, getting the shape of the Le diagram of $W$ from the relation $I_1^W= I_1^V \cup \{n-3\}$.
 
@@
 
-Now suppose $c = v= n-4$; in this case $I_{n-2}^W$ contributes plusses defined by the noncrossing paths starting from $\{n-3, n-4, n-5\}$ and ending at $\{n, n-1, n-2\}$.
-Thus $I_n^V$ contributed the plus from the path $(n-4)\rightarrow (n)$, while $I_{n-2}^W$ contributes the plusses $(n-3)\rightarrow (n-2)$, $(n-4)\rightarrow (n-1)$ and $(n-5)\rightarrow (n)$.
+Now suppose $c = v= n-4$; in this case $I_{n-2}^W$ contributes plusses defined by the noncrossing paths starting from $\{n-3, n-4, n-5\}$ and ending at $\{n, n-1, n-2\}$, namely the plusses in positions $(n-3)\rightarrow (n-2)$, $(n-4)\rightarrow (n-1)$ and $(n-5)\rightarrow (n)$.
 
@@
 
-Note that by Remark \ref{rem n-2 case}, we only need to consider when $W$ is a diagram with one of the two configurations depicted in Figure~\ref{fig special p}, and if $n-2 \in I_{n-2}^V$ then $n-1 \in I_{n-1}^V$ as well.
+Thus $W$ has one of the two configurations depicted in Figure~\ref{fig special p}, and by Remark~\ref{rem n-2 case} we can further assume that if $n-2 \in I_{n-2}^V$ then $n-1 \in I_{n-1}^V$ as well.
 Let $V$ be $W$ with $p$ removed.
@@
   \end{itemize}
-The first three points follow immediately from Lemmas \ref{lem n and n-1} through \ref{lem other k}.
-If $n-2 \not\in I_{n-2}^V$ by Lemma~\ref{lem n-2 good} there are no plusses in column $n-2$ of the diagram of $V$, and all plusses have been accounted for.
-If $n-2 \in I_{n-2}^V$ then we are in the setting of Lemma~\ref{lem n-2 bad}, and there is exactly one plus in column $n-2$ of the diagram of $V$; it is paired with the one plus in $W$ yet unaccounted for: namely those in positions $(n-5) \rightarrow n$ or $(n-5) \rightarrow (n-1)$, as described in points 4 and 6 of that lemma.
+The first two points follow from Lemmas \ref{lem n and n-1} through \ref{lem n-2 bad}.
+The third point follows from Lemma~\ref{lem other k}, which tells us that the $n-3$ column of $V$ is identical to the $n-2$ column of $W$ (excluding the last row).
+
+Finally, if $n-2 \not\in I_{n-2}^V$ by Lemma~\ref{lem n-2 good} there are no plusses in column $n-2$ of the diagram of $V$, and all plusses have been accounted for.
+On the other hand, if $n-2 \in I_{n-2}^V$ then we are in the setting of Lemma~\ref{lem n-2 bad}, and there is exactly one plus in column $n-2$ of the diagram of $V$.
+This plus is paired with the one plus in $W$ yet unaccounted for, namely the one in position $(n-5) \rightarrow n$ or $(n-5) \rightarrow (n-1)$, as described in points 4 and 6 of that lemma.
 

### 2019-10-01 GWLDCII.tex
changes while on the phone

@@
 
-\begin{rmk}\label{rem n-2 case} Note that we need not consider the case when $n-2 \in I_{n-2}^V$ but $n-1 \not\in I_{n-2}^V$ even though this possibility appears in Lemma \ref{lem I}.
+\begin{rmk}\label{rem n-2 case} Consider the case when $n-2 \in I_{n-2}^V$ but $n-1 \not\in I_{n-2}^V$.
 This case can only occur if our $W$ is in Case 2 of Figure~\ref{fig special p} and $n-1$ supports no propagators other than $p$.
@@
 satisfying $n-2 \not \in I_{n-2}^V$.
-Therefore, for the rest of this section, we only consider the situation where if $n-2 \in I_{n-2}^V$ then $n-1 \in I_{n-1}^V$.
-\note{But then immediately in the next lemma we don't...}
+Therefore we do not need to consider the case where $n-2\in I_{n-2}^V$ but $n-1\not\in I_{n-2}^V$.
 \end{rmk}
@@
   Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that $n-2 \not\in I_{n-2}^{V}$.
-Then $I_{n-2}^{W}$ contributes all of the same plusses as $I_{n-1}^{V}=I_{n-2}^{V}$, along with a new $(n-3)\rightarrow (n-2)$ plus.\note{Has this been rephrased?
-Could we discuss?}
+Then $I_{n-2}^{W}$ contributes all of the same plusses as $I_{n-1}^{V}$ (which is the same as $I_{n-2}^{V}$) along with a new $(n-3)\rightarrow (n-2)$ plus.
 \end{lem}
@@
   \begin{lem}\label{lem n-2 bad}
-    Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that $n-2,n-1 \in I_{n-2}^{V}$. Let $c$ be the largest element of $I_1^V$.  Then:\note{This is a small grammar problem}
+    Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that $n-2,n-1 \in I_{n-2}^{V}$. Let $c$ be the largest element of $I_1^V$.  Then the following are true.
     \begin{enumerate}
@@
   \item If $c = n-4$ then $I_{n-1}^V$ contributes a $(n-4) \rightarrow (n-1)$ plus; all other plusses contributed by $I_{n-1}^V$ were already contributed by $I_{n-3}^V$, regardless of the value of $c$.
-  \item The Grassmann necklace of $V$ contributes a $(c)\rightarrow (n-1)$ plus if and only if $c = n-4$.
-No term in the Grassmann necklace of $V$ contributes a $(n-5) \rightarrow n$ plus.\note{Could we briefly discuss these potentially spurious parens I added}
+  \item The Grassmann necklace of $V$ contributes a $(c)\rightarrow (n-1)$ plus if and only if $c = n-4$. No term in the Grassmann necklace of $V$ contributes a $(n-5) \rightarrow n$ plus.
     \end{enumerate} 
@@
   Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that if $n-2\in I_{n-2}^{V}$ then $n-1\in I_{n-2}^{V}$ also.
-Then for each $k$ in the range $1<k<n-2$, $I_k^{W}$ contributes the same plusses as $I_{k}^{V}$, except that if $I_{k}^{V}$ contributed a plus in the $n-3$ column of the Le diagram of $V$ then this plus is shifted one square left in the Le diagram of $W$, and no plus was already in that location in the Le diagram of $W$.\note{should that last $W$ be a $V$?}
+Then for each $k$ in the range $1<k<n-2$, $I_k^{W}$ contributes the same plusses as $I_{k}^{V}$, except that if $I_{k}^{V}$ contributed a plus in the $n-3$ column of the Le diagram of $V$ then this plus is shifted one square left in the Le diagram of $W$.
 \end{lem}
@@
 If $n-2$ supports at least one propagator in $V$ then $n-2 \in I_{n-2}^V$ and so by hypothesis $n-1 \in I_{n-2}^V$ as well.
-By Lemma~\ref{lem n-2 bad}, the only necklace element of $V$ containing $n-2$ is $I_{n-2}^{V}$ and the corresponding plus is not contributed to the Le diagram of $W$ by $I_{n-2}^{W}$.
+By Lemma~\ref{lem n-2 bad} item 3, the only necklace element of $V$ containing $n-2$ is $I_{n-2}^{V}$ and further with item 4, the plusses in column $n-2$ from $I_{n-2}^V$ and $I_{n-2}^W$ are different.
 
   Since $n-3 \in I_k^V \setminus I_1^V$, we must have a path in the Le diagram of $V$ from some vertical edge $i$ to the bottom edge $n-3$.
-In the Le diagram of $W$, the index $n-3$ labels a vertical edge with no path starting at it (since $n-3$ belongs to both $I_1^W$ and $I_k^W$), and there must be a path leading to $n-2$ since $n-2 \in I_k^W \setminus I_1^W$.
+In the Le diagram of $W$, the index $n-3$ labels a vertical edge with no path from $I_k^W$ starting at it (since $n-3$ belongs to both $I_1^W$ and $I_k^W$), and there must be a path leading to $n-2$ since $n-2 \in I_k^W \setminus I_1^W$.
 By the previous paragraph no other path from $I_k^V$ could end at $n-2$, and since the paths cannot cross we conclude that the $i\rightarrow (n-3)$ path in the Le diagram of $V$ must become a $i\rightarrow (n-2)$ path in the Le diagram of $W$.
@@
 
-   Thus the plus contributed by $I_k^V$ in the $n-3$ column of the Le diagram of $V$ is shifted into the $n-2$ column in the Le diagram for $W$, where there was no plus before, and no other plusses are changed.
+%   Thus the plus contributed by $I_k^V$ in the $n-3$ column of the Le diagram of $V$ is shifted into the $n-2$ column in the Le diagram for $W$, where there was no plus before, and no other plusses are changed.
 \end{proof}
@@
 By Algorithm~\ref{alg:GN to Le} there are plusses in the $i+1$, $j$, and $j+1$ positions.
-\sanote{changed for grammar and notational consistency.
-check}
 
@@
 
-The results of Section~\ref{sec GN algorithm} allow us to relate the \hlfix{position of propagators}{ending edges?} in a Wilson loop diagram $W$ to minors of $C(W)$, $R(W)$.
-\sanote{Do we need to fix an ordering of rows of $C(W)$, or does that come out in the wash?}
+The results of Section~\ref{sec GN algorithm} allow us to relate the configuration of propagators in a Wilson loop diagram $W$ to minors of $C(W)$, $R(W)$.
+In this section fix an arbitrary ordering of the propagators, equivalently the rows of $C(W)$.
 
@@
       \item Let $r_i$ be the determinant of the $|S_i|\times |S_i|$ minor of $C(W)$ with rows indexed by $S_i$ and columns indexed by $I_i(S_i)$.
-{\color{violet} If $S_i = \emptyset$, set $r_i = 1$}\sanote{a version of this was commented out, put back in}%$\Delta_{I_i}$ with all variables from rows associated to $p\not\in S_i$ set to $1$.
+If $S_i = \emptyset$, set $r_i = 1$.
+%$\Delta_{I_i}$ with all variables from rows associated to $p\not\in S_i$ set to $1$.
     \end{itemize}
@@
 As we discuss the algorithm it will also be useful to have the notation $\Delta_{I_i}$ for the determinant of the $k\times k$ minor of $C(W)$ with columns indexed by $I_i$.
-{\color{violet} In particular, one summand of this determinant is given by $\prod_{p \in \cP}x_{p, I_i(p)}$.
-The other summands are (up to sign) given by other bijections between the propagator set $\cP$ and the vertex set $I_i$.}
-
-As we take each $r_i$ to simply be the determinant of a particular submatrix of $C(W)$, the sign of each $r_i$ is well-defined {\color{violet} (after an ordering on the propagators have been fixed)}.
+In particular, one summand of this determinant is given by $\prod_{p \in \cP}x_{p, I_i(p)}$.
+The other summands are (up to sign) given by other bijections between the propagator set $\cP$ and the vertex set $I_i$.
+
+As we take each $r_i$ to simply be the determinant of a particular submatrix of $C(W)$, the sign of each $r_i$ is well-defined (since an ordering on the propagators has been fixed).
 Before proving the main results of this section, we given an illustrative example.
@@
 \begin{gather*}I_1 = \{1,2,4\}, I_2 = \{2,4,5\}, I_3 = \{4,5,6\}, I_4=\{4,5,6\},\\ I_5=\{5,6,7\}, I_6 = \{6,7,1\}, I_7=\{7,1,2\}. \end{gather*}  
-Figure~\ref{fig R eg} indicates \st{the pairings between propagators and vertices for each }{\color{violet} indicates which vertex is contributed to $I_i$ by each propagator for each} $i \in [1,7]$.
+Figure~\ref{fig R eg} indicates indicates which vertex is contributed to $I_i$ by each propagator for each $i \in [1,7]$.
 
@@
 \] 
-Continuing likewise, we get $r_3 = c$, $r_4=1$ \sanote{see bit added to Alg 5.1 above}(since $I_4 = I_3$), $r_5 = lhd$, and $r_6 = i$.
+Continuing likewise, we get $r_3 = c$, $r_4=1$ (since $I_4 = I_3$), $r_5 = lhd$, and $r_6 = i$.
 
@@
 This proves the claim.
-\sanote{I know there was some contention over this paragraph.
-Having read it carefully, I want to iterate that I like this now.}
 
@@
 Suppose for a contradiction that $f$ is a factor of $\Delta_{I_i}$ of degree $\geq 3$.
-Without loss of generality\footnote{This is without loss of generality as by removing the propagators which come before those contributing to $f$ in the order given by $I_i$ and changing $i$ to be the first vertex which contributes to $f$, we obtain an admissible diagram for which $f$ still divides $\Delta_{I_i}$ but also $i\in I_i$ and
-$i$ contributes to $f$, and this diagram can be used in place of $W$.} we may assume $i\in I_i$ and $i$ contributes to $f$.
-Finally, we can suppose that $W$ is minimal in number of propagators with an irreducible factor of degree $\geq 3$. \sanote{can we break footnote inot a couple sentences?}
+Without loss of generality\footnote{This is without loss of generality for the following reason.
+By removing the propagators which come before those contributing to $f$ in the order given by $I_i$ and changing $i$ to be the first vertex which contributes to $f$, we obtain an admissible diagram.
+In this diagram $f$ still divides $\Delta_{I_i}$ and also $i\in I_i$ and
+$i$ contributes to $f$.  Thus this diagram can be used in place of $W$.} we may assume $i\in I_i$ and $i$ contributes to $f$.
+Finally, we can suppose that $W$ is minimal in number of propagators with an irreducible factor of degree $\geq 3$.
 
@@
 
-\textbf{Case 1}: Suppose $p = (i-1, m)$.
-Then $p$ has one end on $i-1^{th}$ edge and $I_{i+1}(p) = m$ by Lemma~\ref{vertex cyclic int lem}.
-\sanote{again, it would be nice if this could be read off from a statement of a result somehwere}.
+\textbf{Case 1}: Suppose $p = (i-1, m)$. Then $p$ has one end on $i-1^{th}$ edge and $I_{i+1}(p) = m$ by Remark~\ref{rmk cyclic}.
 
 Let $S = \cP_{in}(p)$ be the set of propagators inside $p$ in the $<_i$ order.
-{\color{violet} By Remark \ref{rmk algorithm locally same},} $I_i$ and $I_{i+1}$ can only differ once $p$ contributes to $I_{i+1}$, so $I_i(q) = I_{i+1}(q)$ for each $q \in S \backslash \{p\}$.
+By Remark \ref{rmk algorithm locally same}, $I_i$ and $I_{i+1}$ can only differ once $p$ contributes to $I_{i+1}$, so $I_i(q) = I_{i+1}(q)$ for each $q \in S \backslash \{p\}$.
 Thus if a propagator contributes $m$ in $I_i$ then it must lie outside $p$.
-
-\hlfix{By Remark {\ref{clockwise ordering rem}}, if $I_i(q) = m$, then it must be the clockwise most propagator supported on $m$ that has not yet contributed to $I_i$, i.e.
-is lies in $\cP_{out}(p, <_i)$.}{more direct than above para.
-Alt.
-only.
-Don't need to adopt.
-(keep dfn of $S$.)}
 
@@
 So we must have at least one of $m$ and $m+1$ in $I_i$.
-However, all propagators in $S$ contribute to $I_{i}$ strictly before $m$ {\color{violet} by Corrollary \ref{GN alg well defined}}, so the matrix giving $\Delta_{I_i}$ {\color{violet} where the rows appear in the order defined by $I_i$?} has the form
+However, all propagators in $S$ contribute to $I_{i}$ strictly before $m$ by the previous paragraph, so permuting rows and columns as needed, the matrix giving $\Delta_{I_i}$ has the form
 \[

### 2019-10-02 GWLDCII.tex

@@
 This not only greatly simplifies the previously known process to obtain a positroid cell from a Wilson loop diagram, but will also allow us to relate the behavior of the positroid $M(W)$ directly to the configuration of progators in $W$.
+In section \ref{sec poles} we see that the denominator, $R(W)$, of the integrand associated to a Wilson loop diagram, $I(W)$, can be written in terms of the Grassman Necklace of a diagram.
 
@@
 The main result of this section is Theorem~\ref{thm denom}, which expresses the denominator $R(W)$ in terms of the Grassmann necklace of $W$.
-\sanote{Put something about this in the motivation for why WLD $\rightarrow$ GN algorithm is useful}This simplifies the computation of $R(W)$ and allows us to directly relate the poles of the integral to the combinatorics of the diagram.
+This simplifies the computation of $R(W)$ and allows us to directly relate the poles of the integral to the combinatorics of the diagram.
 
@@
 So we must have at least one of $m$ and $m+1$ in $I_i$.
-However, all propagators in $S$ contribute to $I_{i}$ strictly before $m$ by the previous paragraph, so permuting rows and columns as needed, the matrix giving $\Delta_{I_i}$ has the form
+However, all propagators in $S$ contribute to $I_{i}$ strictly before $m$ by \st{the previous paragraph}{\color{violet}Remark {clockwise ordering rem}}, so permuting rows and columns as needed, the matrix giving $\Delta_{I_i}$ has the form
 \[
@@
 \end{proof}
-\sanote{start here}
 

### 2019-10-04 GWLDCII.tex
new le diagram pictures, fixed incorrect arrow in section 5 fig

@@
 
-\usetikzlibrary{decorations.pathmorphing,calc}
-\usetikzlibrary{intersections}
+\usetikzlibrary{calc} 
+\usetikzlibrary{decorations.pathmorphing} % to get the wiggly propagator lines
+\usetikzlibrary{bending} % to fix the arrow tips on bent lines
+\usetikzlibrary{patterns} % for shading the Le diagrams in section 4
+
+\newcommand{\leplus}{\Large $+$}
+\newcommand{\lezero}{\Large $0$}
 
@@
  % used for showing which propagator assigns to which vertex in the last section
-\pgfmathsetmacro{\arrowangle}{75}
+\pgfmathsetmacro{\arrowangle}{90}
 \tikzstyle{propassignment} = [->,shorten >=2pt,thick]
@@
 \begin{figure}
-  \[\includegraphics{Le_diagrams}\]
+  \[\begin{tikzpicture}[scale = 1.5]
+\node at (1.5,2.5) {\Large $V$};
+\draw (0,0) rectangle (1,2);
+\draw (1,0) rectangle (1.3,2);
+\begin{scope}[shift = {(-2.7,-2)}]
+\draw (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4) -- (4,4);
+\end{scope}
+\node at (0.5,1) {\large$\mathcal{A}$};
+\node at (1.8,1) {\large$\mathcal{B}$};
+\begin{scope}[shift = {(5,0)}]
+\node at (1.5,2.5) {\Large $W$};
+\draw (0,-0.3) rectangle (1,0);
+\draw (0,0) rectangle (1,2);
+\begin{scope}[shift = {(-3,-2)}]
+\draw (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4) -- (4,4);
+\end{scope}
+\node at (0.5,1) {\large$\mathcal{A}$};
+\node at (1.5,1) {\large$\mathcal{B}$};
+\end{scope}
+\end{tikzpicture}\]
   \caption{Le diagrams for $V$ (left) and $W$ (right).}\label{fig Le}
@@
 \begin{figure}
-\includegraphics[width=12cm]{new_le_diagrams.jpg}
+\[
+\begin{tikzpicture}[scale = 0.85]
+\node at (2.5,5) {\Large $V$};
+\node at (12.5,5) {\Large $W$};
+\node at (-2,2.5) {\large $n-4 \in I_1^V$};
+\node at (-2,-4.5) {\large $n-4 \not\in I_1^V$};
+\node at (7.5,2.5) {\Large $\longrightarrow$};
+\node at (8,-4.5) {\Large $\longrightarrow$};
+% n-4 \in I_1, V
+\begin{scope}
+\draw[pattern color = gray,pattern = north east lines] (0,4) -- (0,2) -- (2,2) -- (2,4);
+\draw[pattern color = gray,pattern = north west lines] (3,4) -- (3,0) -- (4,0) -- (4,4);
+\draw (0,0) grid (4,2);
+\foreach \x in {0,1,2,3,4} {
+  \draw (\x,2) -- (\x,4);
+  };
+\foreach \c in {(0.5,0.5),(1.5,0.5),(1.5,1.5)} {
+  \node at \c {\leplus};
+}
+\foreach \c in {(0.5,1.5),(2.5,1.5),(2.5,2.5)} {
+  \node at \c {\lezero};
+}
+\node[red] at (2.5,0.5) {\leplus};
+\node at (2.5,3.5) {$\vdots$};
+\begin{scope}
+\fill[pattern color = gray,pattern = horizontal lines] (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4) -- (4,4) -- (4,2);
+\draw (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4);
+\end{scope}
+%\fill[color = white,path fading = south] (0,2) rectangle (6.5,4.1);
+\node[below] at (0.5,0) {\tiny $n\vphantom{1}$};
+\node[below] at (1.5,0) {\tiny $n-1$};
+\node[below] at (2.5,0) {\tiny $n-2$};
+\node[below] at (3.5,0) {\tiny $n-3$};
+\node[right] at (4,0.5) {\tiny $n-4$};
+\node[right] at (4,1.5) {\tiny $n-5$};
+\end{scope}
+
+% n-4 \in I_1, W
+\begin{scope}[shift = {(9,0)}]
+\draw[pattern color = gray,pattern = north east lines] (0,4) -- (0,2) -- (2,2) -- (2,4);
+\draw[pattern color = gray,pattern = north west lines] (2,4) -- (2,0) -- (3,0) -- (3,4);
+\draw (0,-1) grid (3,2);
+\foreach \x in {0,1,2,3} {
+  \draw (\x,2) -- (\x,4);
+  };
+\foreach \c in {(0.5,0.5),(1.5,0.5),(1.5,1.5)} {
+  \node at \c {\leplus};
+}
+\node[red] at (0.5,1.5) {\leplus};
+\foreach \c in {(0.5,-0.5),(1.5,-0.5),(2.5,-0.5)} {
+  \node[blue] at \c {\leplus};
+}
+\begin{scope}[shift = {(-1,0)}]
+\fill[pattern color = gray,pattern = horizontal lines] (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4) -- (4,4) -- (4,2);
+\draw (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4);
+\end{scope}
+\node[below] at (0.5,-1) {\tiny $n\vphantom{1}$};
+\node[below] at (1.5,-1) {\tiny $n-1$};
+\node[below] at (2.5,-1) {\tiny $n-2$};
+\node[right] at (3,-0.5) {\tiny $n-3$};
+\node[right] at (3,0.5) {\tiny $n-4$};
+\node[right] at (3,1.5) {\tiny $n-5$};
+\end{scope}
+
+% n-4 \not\in I_1, V
+\begin{scope}[shift = {(0,-6)}]
+\draw[pattern color = gray,pattern = north east lines] (0,3) -- (0,1) -- (2,1) -- (2,3);
+\draw[pattern color = gray,pattern = north west lines] (3,3) -- (3,0) -- (4,0) -- (4,3);
+\draw (0,0) grid (4,1);
+\foreach \x in {0,1,2,3,4} {
+  \draw (\x,1) -- (\x,3);
+  };
+\foreach \c in {(0.5,0.5),(1.5,0.5),(2.5,1.5)} {
+  \node at \c {\lezero};
+}
+\node at (2.5,2.5) {$\vdots$};
+\node[red] at (2.5,0.5) {\leplus};
+\begin{scope}[shift = {(1,-1)}]
+\fill[pattern color = gray,pattern = horizontal lines] (3,1) -- (4,1) -- (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4) -- (3,4) -- (3,1);
+\draw (3,1) -- (4,1) -- (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4);
+\end{scope}
+
+\node[below] at (0.5,0) {\tiny $n\vphantom{1}$};
+\node[below] at (1.5,0) {\tiny $n-1$};
+\node[below] at (2.5,0) {\tiny $n-2$};
+\node[below] at (3.5,0) {\tiny $n-3$};
+\node[below] at (4.5,0) {\tiny $n-4$};
+\node[right] at (5,0.5) {\tiny $n-5$};
+\end{scope}
+
+% n-4 \not\in I_1, W
+\begin{scope}[shift = {(9,-6)}]
+\draw[pattern color = gray,pattern = north east lines] (0,3) -- (0,1) -- (2,1) -- (2,3);
+\draw[pattern color = gray,pattern = north west lines] (2,3) -- (2,0) -- (3,0) -- (3,3);
+\draw (0,-1) grid (3,1);
+\foreach \x in {0,1,2,3} {
+  \draw (\x,1) -- (\x,3);
+  };
+\node at (0.5,0.5) {\lezero};
+\node[red] at (1.5,0.5) {\leplus};
+\foreach \c in {(0.5,-0.5),(1.5,-0.5),(2.5,-0.5)} {
+  \node[blue] at \c {\leplus};
+}
+\begin{scope}[shift = {(0,-1)}]
+\fill[pattern color = gray,pattern = horizontal lines] (3,1) -- (4,1) -- (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4) -- (3,4) -- (3,1);
+\draw (3,1) -- (4,1) -- (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4);
+\end{scope}
+\node[below] at (0.5,-1) {\tiny $n\vphantom{1}$};
+\node[below] at (1.5,-1) {\tiny $n-1$};
+\node[below] at (2.5,-1) {\tiny $n-2$};
+\node at (3.5,-0.7) {\tiny $n-3$};
+\node at (3.7,-0.2) {\tiny $n-4$};
+\node[right] at (4,0.5) {\tiny $n-5$};
+\end{scope}
+\end{tikzpicture}
+\]
 \caption{The Le diagrams for $V$ and $W$ in the setting of Theorem~\ref{thm dim}.
@@
 \[
-\begin{tikzpicture}[baseline=(current bounding box.east),rotate=-20]
+\begin{tikzpicture}[baseline=(current bounding box.east),rotate=-20,scale = 0.95]
 \begin{scope}
@@
   \newnode[left]{1}{i-1}
-	\newnode[below]{2}{i}
+  \newnode[below]{2.5}{i}
   \newnode[below]{7}{m}
@@
     \clipcenterarc(0,0)(\startpoint-10:\endpoint+10:\radius)
-		\newpropbend{1.7}{7.2}{60}
-		\draw[smallpropagator,blue] (\zero+7.8*\step:\radius*1.1) to[bend left = 55] (\zero + 10*\step:\radius*1.1);
-		\node at (\zero + 1.2*\step:\radius*0.5) {\footnotesize $p$};
+    \newpropbend{1.9}{7.2}{60}
+    \draw[smallpropagator,gray] (\zero+7.8*\step:\radius*1.1) to[bend left = 55] (\zero + 10*\step:\radius*1.1);
+    \node at (\zero + 1.5*\step:\radius*0.5) {\footnotesize $p$};
   \end{scope}
   \node[align = center,black] at (\zero + \step*4.5:\radius*0.65) {\em \footnotesize propagators \\ \footnotesize \em inside $p$};
-	\draw[propassignment,gray] (\zero + 1.6*\step:\radius) to[bend left = \arrowangle] (\zero + 1*\step:\radius); %p
+  \draw[propassignment,gray] (\zero + 1.81*\step:\radius) to[bend right = \arrowangle] (\zero + 2.5*\step:\radius); %p
   \draw[propassignment,gray] (\zero + 7.9*\step:\radius) to[bend left = \arrowangle] (\zero + 7*\step:\radius); 
-	\node[align = center,black] at (\zero + 6.8*\step:1.5*\radius) {\em \footnotesize If $m \in I_i$ then \\ \em \footnotesize it was contributed by \\ \em \footnotesize the blue propagator};
+  \node[align = center,black] at (\zero + 6.8*\step:1.5*\radius) {\em \footnotesize If $m \in I_i$ then it was \\ \em \footnotesize contributed by a propagator \\ \em \footnotesize outside of $p$};
+  \node[align = center,black] at (110:\radius*0.5) {\em Case 1: $p = (i-1,m)$};
 \end{scope}
@@
 \qquad  
-\begin{tikzpicture}[baseline=(current bounding box.east),rotate=-20]
+\begin{tikzpicture}[baseline=(current bounding box.east),rotate=-20,scale = 0.95]
   \begin{scope}
@@
   \newnode[left]{1}{i}
-	\newnode[below]{2}{i+1}
+  \newnode[below]{2.5}{i+1\ \ \ }
   \newnode[below]{7}{j}
-	\centerarc[red,line width = 2pt,line cap = round](0,0)(\zero + 1.5*\step:\zero+1.56*\step:\radius);
-	\draw[propassignment,gray] (\zero + 1.45*\step:\radius) to[bend left = \arrowangle] (\zero + 1*\step:\radius); %p
-	\draw[propassignment,gray] (\zero + 1.61*\step:\radius) to[bend right = \arrowangle] (\zero + 2*\step:\radius); %q 
-	\draw[propassignment,gray] (\zero + 7.7*\step:\radius) to[bend left = \arrowangle] (\zero + 7*\step:\radius); %blue
+  \centerarc[red,line width = 2pt,line cap = round](0,0)(\zero + 1.61*\step:\zero+1.88*\step:\radius);
+  \draw[propassignment,gray] (\zero + 1.55*\step:\radius) to[bend left = \arrowangle] (\zero + 1*\step:\radius); %p
+  \draw[propassignment,gray] (\zero + 1.93*\step:\radius) to[bend right = \arrowangle] (\zero + 2.5*\step:\radius); %q 
+  \draw[propassignment,gray] (\zero + 7.7*\step:\radius) to[bend left = \arrowangle] (\zero + 7*\step:\radius); % other prop
   \begin{scope}
     \clipcenterarc(0,0)(\startpoint-10:\endpoint+10:\radius)
-		\newpropbend{1.6}{7.2}{40} % q
-		\draw[smallpropagator] (\zero+1.5*\step:\radius*1.1) to[bend right = 40] (\zero  - 3*\step:\radius*1.1); % p
-		\draw[smallpropagator,blue] (\zero+7.6*\step:\radius*1.1) to[bend left = 55] (\zero + 10*\step:\radius*1.1);
-		\node at (\zero + 5*\step:\radius*0.3) {\footnotesize $q$};
-		\node at (\zero + 1*\step:\radius*0.6) {\footnotesize $p$};
-	\end{scope}
-	\node[align = center,black] at (\zero + \step*4.5:\radius*0.75) {\em \footnotesize propagators \\ \footnotesize \em inside $q$};
-	\node[align = center] at (\zero + 1.5*\step:\radius*1.5) {\footnotesize \em No \\ \footnotesize \em propagators \\ \footnotesize \em between \\ \footnotesize \em $p$ and $q$ \\ \footnotesize \em here};
-	\node[align = center,black] at (\zero + 6.8*\step:1.5*\radius) {\em \footnotesize If $j \in I_i$ then \\ \em \footnotesize it was contributed by \\ \em \footnotesize the blue propagator};
+    \newpropbend{1.9}{7.2}{40} % q
+    \draw[smallpropagator] (\zero+1.6*\step:\radius*1.1) to[bend right = 40] (\zero  - 3*\step:\radius*1.1); % p
+    \draw[smallpropagator,gray] (\zero+7.6*\step:\radius*1.1) to[bend left = 55] (\zero + 10*\step:\radius*1.1);
+    \node at (\zero + 5*\step:\radius*0.32) {\footnotesize $q$};
+    \node at (\zero + 1.1*\step:\radius*0.6) {\footnotesize $p$};
+  \end{scope}
+  \node[align = center,black] at (\zero + \step*4.5:\radius*0.72) {\em \footnotesize propagators \\ \footnotesize \em inside $q$};
+  \node[align = center] at (\zero + 1.8*\step:\radius*1.5) {\footnotesize \em No \\ \footnotesize \em propagators \\ \footnotesize \em between \\ \footnotesize \em $p$ and $q$ \\ \footnotesize \em here};
+  \node[align = center,black] at (\zero + 6.8*\step:1.5*\radius) {\em \footnotesize If $j \in I_i$ then it was \\ \em \footnotesize contributed by a propagator \\ \em \footnotesize outside of $q$};
+    \node[align = center,black] at (110:\radius*0.5) {\em Case 2: $p = (i,j)$};
+
 \end{scope}
@@
 \]
-  \caption{The two cases in the proof that no factors of $\Delta_{I_i}$ have degree 3 or more.{\color{violet}First picture: I thought $I_i(p) = i$.
-Doesn't the arrow say that $I_i(p) = i-1$?}}\label{fig no big factors}
+  \caption{The two cases in the proof that no factors of $\Delta_{I_i}$ have degree 3 or more.}\label{fig no big factors}
 \end{figure}

### 2019-10-06 GWLDCII.tex
minor grammar + notation updates

@@
 In the next two lemmas, we consider the plusses contributed to the Le diagram of $W$ by $I_{n-2}^W$.
+Lemma~\ref{lem I} lists three possibilities for $I_{n-2}^W$, but the following observation shows that we need only consider two of them.
 
@@
 
-In this section, we investigate the poles of the integrand for $I(W)$, that is $R(W)$ as defined in Definition~\ref{def R(W)}.
+In this section we investigate the poles of the integrand for $I(W)$.
 Since SYM $N=4$ is a finite theory \cite{Alday:2007hr, ParkeTaylorids}, the scattering amplitudes (and thus the holomorphic Wilson loops $\,\mathfrak{W}_{k,n}$) are finite.
-That is, for a fixed set of external particles $\cZ$, \bas \sum_{W \text{ s.t.
-} |\cP| = k} I(W)(\cZ) <\infty \;.\eas In otherwords, all poles of the intergrands must cancel.
-As a step towards this, in this section, we prove some results about the structure of the denominator of the integrand, $R(W)$.
+That is, for a fixed set of external particles $\cZ$, we must have
+\bas \sum_{W \text{ s.t. } |\cP| = k} I(W)(\cZ) <\infty \;.\eas
+In other words, all poles of the intergrands must cancel.
+As a step towards this, in this section we prove some results about the structure of the denominator $R(W)$ of the integrand, as defined in Definition~\ref{def R(W)}.
 
 The results of Section~\ref{sec GN algorithm} allow us to relate the configuration of propagators in a Wilson loop diagram $W$ to minors of $C(W)$, $R(W)$.
-In this section fix an arbitrary ordering of the propagators, equivalently the rows of $C(W)$.
+In this section fix an arbitrary ordering of the propagators, equivalently the rows of $C(W)$.\note{There's some grammatical issues in this paragraph and I'm not sure what it's supposed to be saying.}
 
@@
 \begin{algorithm}\label{alg WLD to denom via GN}
-Let $W = (\cP,[n])$ be a Wilson loop diagram, and let $C(W)$ be the matrix of $W$ as defined in \eqref{C(W) dfn} with a fixed ordering on $\cP$. (see Section~\ref{section WLD background}).
+Let $W = (\cP,[n])$ be a Wilson loop diagram, and let $C(W)$ be the matrix of $W$ as defined in equation \eqref{C(W) dfn} with a fixed ordering on $\cP$ (see Section~\ref{section WLD background})\note{This was written before the exposition above; now I think we can simplify it to "Let $W$ be a WLD and $C(W)$ its associated matrix?}.
 \begin{itemize}
@@
 That is, each $r_i$ is the determinant of the minor determined by the propagators (rows) that contribute different values (columns) to the $i^{th}$ element of the Grassmann necklace than they did to the $i-1^{st}$.
-
-As we discuss the algorithm it will also be useful to have the notation $\Delta_{I_i}$ for the determinant of the $k\times k$ minor of $C(W)$ with columns indexed by $I_i$.
-In particular, one summand of this determinant is given by $\prod_{p \in \cP}x_{p, I_i(p)}$.
-The other summands are (up to sign) given by other bijections between the propagator set $\cP$ and the vertex set $I_i$.
-
-As we take each $r_i$ to simply be the determinant of a particular submatrix of $C(W)$, the sign of each $r_i$ is well-defined (since an ordering on the propagators has been fixed).
-Before proving the main results of this section, we given an illustrative example.
-Below, we show that $R$ is equal to the denominator of the Wilson loop diagram as defined in Definition~\ref{def R(W)}, and is the radical of the product $\prod_{i=1}^n \Delta_{I_i}$.
-%  However, we will not be interested in these signs as they only contribute an overall sign to $R$ and our main theorem in this section (Theorem~\ref{thm denom}) will simply be to show that $R$ is equal up to a $\mathbb{Q}$-multiple to the denominator of the Wilson loop diagram (see Definition~\ref{def R(W)}).
+Since each $r_i$ is simply the determinant of a particular submatrix of $C(W)$ and an ordering on the propagators has been fixed, the sign of each $r_i$ is well-defined.
+
+We also introduce the notation $\Delta_{I_i}$ to represent the determinant of the $k\times k$ minor of $C(W)$ with columns indexed by $I_i$.
+Note that one summand of this determinant is given by $\prod_{p \in \cP}x_{p, I_i(p)}$; the other summands are (up to sign) given by other bijections between the propagator set $\cP$ and the vertex set $I_i$.
+
+Below, we show that the polynomial $R$ associated to Wilson loop diagram $W$ is equal to the denominator $R(W)$ from Definition~\ref{def R(W)}, and is the radical of the product $\prod_{i=1}^n \Delta_{I_i}$.
+First, however, we give a worked example of Algorithm~\ref{alg WLD to denom via GN}.
 
@@
 \begin{gather*}I_1 = \{1,2,4\}, I_2 = \{2,4,5\}, I_3 = \{4,5,6\}, I_4=\{4,5,6\},\\ I_5=\{5,6,7\}, I_6 = \{6,7,1\}, I_7=\{7,1,2\}. \end{gather*}  
-Figure~\ref{fig R eg} indicates indicates which vertex is contributed to $I_i$ by each propagator for each $i \in [1,7]$.
-
-From $I_1$ to $I_2$, the propagators $p$ and $q$ change which vertices they contribute.
-That is $I_1(p) = 1$, $I_1(q)= 2$ while $I_2(p) = 2$, $I_2(q)= 5$.
-However, $r$ contributes  4 to both $I_1$ and $I_2$, so $S_2 = \{p,q\}$.
-Then
+Figure~\ref{fig R eg} indicates indicates which vertex is contributed to $I_i$ by each propagator, for each $i \in [1,7]$.
+
+From $I_1$ to $I_2$, the propagators $p$ and $q$ change which vertices they contribute to; specifically, we have $I_1(p) = 1$ and $I_1(q)= 2$, while $I_2(p) = 2$ and $I_2(q)= 5$.
+On the other hand, $r$ contributes  4 to both $I_1$ and $I_2$.
+We therefore have $S_2 = \{p,q\}$.
+The associated minors $\Delta_{I_2}$ and $r_2$ are therefore
 \[
@@
 
-At $I_7$ we see for the first time an irreducible quadratic factor: we have $S_7 = \{q,s\}$ with $I_7(S_7) = \{ 1,2\}$, $\Delta_{I_7} = d(ej-fi)$ and $r_7 = ej-fi$.
+At $I_7$ we see for the first time an irreducible quadratic factor: we have $S_7 = \{q,s\}$ with ${I_7(S_7) = \{ 1,2\}}$, $\Delta_{I_7} = d(ej-fi)$ and $r_7 = ej-fi$.
 
@@
 Thus each $r_i$ is homogeneous.
-    \item Using the expression for the determinant as a sum over permutations along with Corollary~\ref{lem basis as perm} we see that $\Delta_{I_i}$ is a sum over bijections between $I_i$ and $\mathcal{P}$.
-The nonzero terms in this sum are precisely those bijections such that each propagator is associated to one of its supporting vertices in $I_i$, namely $I_i(p)$, since only those locations in $C(W)$ are nonzero.
+    \item Viewing the determinant as a sum over permutations, and combining this with Corollary~\ref{lem basis as perm}, we see that $\Delta_{I_i}$ is a sum over bijections between $I_i$ and $\mathcal{P}$.
+The nonzero terms in this sum are precisely those bijections such that each propagator is associated to one of its supporting vertices in $I_i$, namely \hlfix{$I_i(p)$}{do we mean $I_i(p)$ or $V(p)$ here?
+if the first, then the last part of the sentence is wrong}, since only those locations in $C(W)$ are nonzero.
 Since the nonzero entries of $C(W)$ are independent there can be no cancellation between terms in this expansion.
@@
 Without loss of generality\footnote{This is without loss of generality for the following reason.
-By removing the propagators which come before those contributing to $f$ in the order given by $I_i$ and changing $i$ to be the first vertex which contributes to $f$, we obtain an admissible diagram.
-In this diagram $f$ still divides $\Delta_{I_i}$ and also $i\in I_i$ and
-$i$ contributes to $f$.  Thus this diagram can be used in place of $W$.} we may assume $i\in I_i$ and $i$ contributes to $f$.
+By removing the propagators which come before those contributing to $f$ (in the order given by $I_i$) and changing $i$ to be the first vertex which contributes to $f$, we obtain an admissible diagram.
+In this diagram, $f$ still divides $\Delta_{I_i}$ and we also have $i\in I_i$ and that
+$i$ contributes to $f$.  Thus this diagram can be used in place of $W$.} we may assume $i\in I_i$ and that $i$ contributes to $f$.
 Finally, we can suppose that $W$ is minimal in number of propagators with an irreducible factor of degree $\geq 3$.
 
-Let $p$ be the propagator such that $I_i(p) = i$. There are two cases to consider, when $p$ is supported on the edge $i-1$ or the edge $i$.  These are illustrated in Figure~\ref{fig no big factors}
+Let $p$ be the propagator such that $I_i(p) = i$. There are two cases to consider: when $p$ is supported on the edge $i-1$ or the edge $i$.  These are illustrated in Figure~\ref{fig no big factors}.
 
@@
 
-\textbf{Case 1}: Suppose $p = (i-1, m)$. Then $p$ has one end on $i-1^{th}$ edge and $I_{i+1}(p) = m$ by Remark~\ref{rmk cyclic}.
+\textbf{Case 1}: Suppose $p = (i-1, m)$. Then $p$ has one end on the $i-1^{th}$ edge, and $I_{i+1}(p) = m$ by Remark~\ref{rmk cyclic}.
 
@@
 
-If neither $m$ nor $m+1$ appear in $I_i$ then by Corollary~\ref{no coloops} $V(p) \cap I_i = \{i\}$, and so the row of $p$ in the matrix of $\Delta_{I_i}$ has only one nonzero entry; hence $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$, which is a contradiction to the fact that $i$ contributes to $f$.
+If neither $m$ nor $m+1$ appear in $I_i$ then by Corollary~\ref{no coloops} we have $V(p) \cap I_i = \{i\}$, and so the row of $p$ in the matrix of $\Delta_{I_i}$ has only one nonzero entry; hence $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$, which is a contradiction to the fact that $i$ contributes to $f$.
 So we must have at least one of $m$ and $m+1$ in $I_i$.
-However, all propagators in $S$ contribute to $I_{i}$ strictly before $m$ by \st{the previous paragraph}{\color{violet}Remark {clockwise ordering rem}}, so permuting rows and columns as needed, the matrix giving $\Delta_{I_i}$ has the form
+However, all propagators in $S$ contribute to $I_{i}$ strictly before $m$ by \st{the previous paragraph}{\color{violet}Remark {clockwise ordering rem}}\note{The purple edit isn't true: a priori a propagator inside $p$ could lie on edge $m$ and contribute $m$.
+The previous paragraph explains why this doesn't happen.} so, after permuting rows and columns as needed, the matrix giving $\Delta_{I_i}$ has the form
 \[
@@
 \textbf{Case 2}: Suppose $p = (i, m)$, i.e.
-has an end on the $i^{th}$ edge.
+$p$ has an end on the $i^{th}$ edge.
 If no other propagators are supported on the vertex $i$ then the corresponding column of $C(W)$ has only one nonzero entry in it, and so $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$; as above, this is a contradiction.
@@
 Again two things can now happen.
-If some vertex $j$ or larger (with respect to $>_i$) belongs to $I_i$ then $B$ and $C$ are at least one column wide, and so the block form of the matrix gives a nontrivial factorization of $\Delta_{I_i}=\det A\det B$.
-This yields a contradiction as in Case 1: $f|\det A$ and removing a propagator not in $S$ gives a smaller diagram with a factor of degree $\geq 3$ which contradicts our minimality assumption.\note{I rephrased this last sentence quite a bit because earlier things had gotten rephrased} \sanote{reads fine to me.}
-
-On the other hand, if no vertex $\geq_i j$ is in $I_i$ then $\Delta_{I_i} = \det A$.
-Looking in more detail into $A$, note that the only vertices supporting both $p$ and $q$ which belong to $I_i$ are $i$ and $i+1$.
+If some vertex $j$ or larger (with respect to $<_i$) belongs to $I_i$ then $B$ and $C$ are at least one column wide, and so the block form of the matrix gives a nontrivial factorization of $\Delta_{I_i}=\det A\det B$.
+This yields a contradiction as in Case 1: $f|\det A$ and removing a propagator not in $S$ gives a smaller diagram with a factor of degree $\geq 3$, which contradicts our minimality assumption.\note{I rephrased this last sentence quite a bit because earlier things had gotten rephrased} \sanote{reads fine to me.}
+
+On the other hand, if no vertex $\geq_i j$ is in $I_i$ then we have $\Delta_{I_i} = \det A$.
+Looking in more detail into $A$, note that the only vertices that support both $p$ and $q$ and also belong to $I_i$ are $i$ and $i+1$.
 Hence
@@
 
-\item \sanote{changed $b$ to $a+1$ here.} Suppose propagators $p$ and $q$ are supported on a common edge  $(a, a+1)$, with $I_i(p)=a$ and $I_i(q)=a+1$.
+\item \sanote{changed $b$ to $a+1$ here.} Suppose propagators $p$ and $q$ are supported on a common edge  $a$, with $I_i(p)=a$ and $I_i(q)=a+1$.
 Let $x_{p,a},x_{p,a+1},x_{q,a},x_{q,a+1}$ be the associated variables in $C(W)$.
-For any fixed bijection $\sigma$ from $\cP-\{p,q\}$ to $I_i -\{a,a+1\}$ for which each propagator is supported on its image under the bijection, we can extend $\sigma$ to a bijection from propagators to $I_i$ in two ways: either $p\mapsto a$ and $q\mapsto a+1$ or $p\mapsto a+1$ and $q\mapsto a$.
-The sum of the contributions of all these bijections to $\Delta_{I_i}$ is therefore the product of $x_{p,a}x_{q,a+1}-x_{p,a+1}x_{q,a}$ {\color{violet} By the arguments in the proof of the claim in part 2 of this theorem} \note{Could this use a ref back to where we discuss this kind of arugment in more detail.}\sanote{see violet?} with the minor coming from $\cP-\{p, q\}$ and $I_i - \{a,a+1\}$.
+For any fixed bijection $\sigma$ from $\cP\setminus\{p,q\}$ to $I_i \setminus\{a,a+1\}$ for which each propagator is supported on its image under the bijection, we can extend $\sigma$ to a bijection from propagators to $I_i$ in two ways: either $p\mapsto a$ and $q\mapsto a+1$ or $p\mapsto a+1$ and $q\mapsto a$.
+The sum of the contributions of all these bijections to $\Delta_{I_i}$ is therefore the product of $x_{p,a}x_{q,a+1}-x_{p,a+1}x_{q,a}$ {\color{violet} By the arguments in the proof of the claim in part 2 of this theorem} \note{Could this use a ref back to where we discuss this kind of arugment in more detail.}\sanote{see violet?} with the minor coming from $\cP\setminus\{p, q\}$ and $I_i \setminus \{a,a+1\}$.
 Since there is no cancellation of terms in the expansion of $\Delta_{I_i}$, if any other terms appear then they will cause a factor which is not in the form described in the previous part.
@@
 It remains to show that \st{$a$ and $b$ are adjacent} {\color{violet}$b = a+1$}.
-From this we can conclude that $p$ and $q$ each have one end on $(a,a+1)$.
+From this we can conclude that $p$ and $q$ each have one end on edge $a$.
 \st{, as any other way for both $p$ and $q$ to be supported on two consecutive vertices would contradict noncrossing or the density requirement of admissibility.}
@@
 
-\item Consider $p\in S_i$ from \ref{alg WLD to denom via GN}, and note that $\Delta_{I_i}$ is homogeneous linear in the variables of the row corresponding to $p$.
+\item If $S_i = \emptyset$ then $r_i = 1$ and we immediately have $r_i | \Delta_{I_i}$; otherwise, let $p\in S_i$.
+Note that $\Delta_{I_i}$ is homogeneous linear in the variables of the row corresponding to $p$.
 By part (2), either exactly one variable in the row corresponding to $p$ appears in $\Delta_{I_i}$ and this variable is a factor of $\Delta_{I_i}$, or exactly two variables from the row corresponding to $p$ appear in $\Delta_{I_i}$ and they appear as part of a quadratic factor.
@@
 Now suppose two variables from the row $p$ appear in a quadratic factor $f$ of $\Delta_{I_i}$.
-By part (3), there is another propagator $q$ and an edge $(a,a+1)$ such that $f$ is the $2\times 2$ minor coming from $p, q$ and $a, a+1$, with \st{$I_i(p)=a$, $I_i(q)=b$}.
+By part (3), there is another propagator $q$ and an edge $a$ such that $f$ is the $2\times 2$ minor coming from $p, q$ and $a, a+1$, with \st{$I_i(p)=a$, $I_i(q)=b$}.
 {\color{violet}There are two situations which can occur, either $I_i(p)=a$ and $I_i(q)=a+1$, or $I_i(q)=a$ and $I_i(p)=a+1$.
@@
   \caption{The situations giving a quadratic factor with variables appearing in $r_i$. }\label{fig quadratic}
-\end{figure}
+\end{figure}\note{I'm not sure we really need this figure? (Figure~\ref{fig quadratic})}
 
@@
 Since $I_{i-1}(p) \neq a$, there must be some other propagator $s$ with $I_{i-1}(s) = a$ (else $q$ contributes $a$ to $I_{i-1}$).
-This propagator cannot lie on edge $(a,a+1)$ since, by Lemma~\ref{vertex cyclic int lem}, \hlfix{we must have $I_i(s) \in \{a, a+1\}$}{is this from examing the cyclic intervals burried in the proof?}, contradicting the fact that $I_i(p) = a$ and $I_i(q) = a+1$; thus $s$ has an end on $(a-1,a)$ and is inside $p$ in the $<_k$ order where $p=(k,a)$.
-
-Say $s = (j,a)$ with $i-1 \leq_{i-1} k+1 \leq_{i-1} j+1$.
+This propagator cannot lie on edge $a$, because then Remark~\ref{rmk cyclic} would imply that $I_i(s) \in \{a, a+1\}$, contradicting the fact that $I_i(p) = a$ and $I_i(q) = a+1$; thus $s$ has an end on edge $(a-1)$ and is inside $p$ in the $<_k$ order where $p=(k,a)$.
+
+Say $s = (j,a-1)$ with $i-1 \leq_{i-1} k+1 \leq_{i-1} j+1$.
 But by Lemma~\ref{lem no fourth vertex}, if $I_{i-1}(s) = a$ then $a$ cannot be maximal in the support of $s$ with respect to $<_{i-1}$; thus we must have $i-1 = j+1$, and we are in the situation in Figure~\ref{fig part 4}.
@@
 	%\drawnumberspartial % use this to debug
-	\newnode{1}{}
+	\newnode[left]{1}{j}
 	\newnode[left]{2}{i-1}
@@
 \]
-  \caption{In order to obtain $I_{i-1}(s) = a$, propagators $s$ and $p$ must each have an end on the edge $(i-2,i-1)$.}\label{fig part 4}
+  \caption{In order to obtain $I_{i-1}(s) = a$, propagators $s$ and $p$ must each have an end on edge $(i-2)$.}\label{fig part 4}
 \end{figure}
@@
 Since $p$ changed its association from $I_{i-1}$ to $I_i$, we have $I_{i-1}(p) = i-1$ by Lemma~\ref{vertex cyclic int lem}.
-From Figure~\ref{fig part 4} {\color{violet} and Remark \ref{rmk algorithm locally same}} $p$ contributes first to  $I_{i-1}$ and  then proceeds identically to $I_i$ for all vertices inside $p$ in the $<_{i-1}$ ordering, implying that $I_{i-1}(s) = I_i(s)$.
+From Figure~\ref{fig part 4} {\color{violet} and Remark \ref{rmk algorithm locally same}}, $p$ contributes first to  $I_{i-1}$ and  then proceeds identically to $I_i$ for all vertices inside $p$ in the $<_{i-1}$ ordering, implying that $I_{i-1}(s) = I_i(s)$.
 Since $I_{i-1}(s) = a$ and $I_i(s) \neq a$, this is a contradiction.
@@
 This contradicts Lemma~\ref{vertex cyclic int lem}.
-Now suppose $f$ is a quadratic factor, say from propagators $p$ and $q$ supported on the edge $(a, a+1)$ with $p$ clockwise to $q$ on the edge.
+Now suppose $f$ is a quadratic factor, say from propagators $p$ and $q$ supported on edge $a$ with $p$ clockwise to $q$ on the edge.
 In this case it is not possible for any $I_i$ to associate $p$ to $a+1$ and $q$ to $a$.
@@
 We are now ready to prove the main theorem of this section.
-We use the facts about $\Delta_{I_i}$ and $R$ above to show that the denominator of the integrand of $I(W)$ is given by Algorithm \ref{alg WLD to denom via GN}.
+We use the facts about $\Delta_{I_i}$ and $R$ above to show that the denominator $R(W)$ of the integrand of $I(W)$ is given by Algorithm \ref{alg WLD to denom via GN}.
 
 \begin{thm}\label{thm denom}
-  Given any admissible Wilson loop diagram $W$, let $\{I_1, \ldots I_n\}$ be the associated Grasmann necklace.
-Then the denominator of the integral, $R(W)$ (see Definition~\ref{def R(W)}), is the $R$ of Algorithm~\ref{alg WLD to denom via GN}.
+  Given any admissible Wilson loop diagram $W$, let $(I_1, \ldots I_n)$ be the associated Grasmann necklace.
+Then $R(W)$ as defined in Definition~\ref{def R(W)} is equal to the $R$ constructed by Algorithm~\ref{alg WLD to denom via GN}.
 Furthermore, the ideal generated by $R(W)$ is the radical of the ideal generated by $\prod_{i=1}^n \Delta_{I_i}$, where $\Delta_{I_i}$ is the determinant of the $k \times k$ minor indicated by $I_i$.
@@
 Thus we have shown a deep relationship between the physically derived poles of the integrals $I(W)$ and the geometry and combinatorics associated to the diagrams $W$.
-At the very least, this is yet another piece of circumstantial evidence indicating that the positroid representation of Wilson loop diagrams is the correct geometric object to be considering when considering the Wilson loop amplitudes geometrically.
+At the very least, this is yet another piece of \hlfix{circumstantial}{can we find a better word for this?} evidence indicating that the positroid representation of Wilson loop diagrams is the correct geometric object to be considering when considering the Wilson loop amplitudes geometrically.
 
 While the authors cannot yet offer a proof that the appropriate sum of the Wilson loop diagrams are, in fact, finite, as expected from \cite{Alday:2007hr, ParkeTaylorids}, we do hope that this relationship to the Grassmann Necklace elements will provide a different avenue for answering that and related questions.
+\note{Can we rephrase this paragraph to be a bit more positive?}
 

### 2019-10-06 GWLDCII.tex
tweaked the le diagram pictures slightly

@@
 \tikzstyle{seconddash}=[dashed,line cap=round, dash pattern=on 0.5pt off 1pt]
+\tikzstyle{smalldash}=[dashed,line cap=round, dash pattern=on 1.5pt off 2pt]
 
@@
 \begin{tikzpicture}[scale = 0.85]
-\node at (2.5,5) {\Large $V$};
-\node at (12.5,5) {\Large $W$};
+\node at (2.5,5.5) {\Large $V$};
+\node at (12.5,5.5) {\Large $W$};
 \node at (-2,2.5) {\large $n-4 \in I_1^V$};
@@
 \begin{scope}
-\draw[pattern color = gray,pattern = north east lines] (0,4) -- (0,2) -- (2,2) -- (2,4);
-\draw[pattern color = gray,pattern = north west lines] (3,4) -- (3,0) -- (4,0) -- (4,4);
+\fill[pattern color = gray,pattern = north east lines] (0,4.5) -- (0,2) -- (2,2) -- (2,4.5);
+\fill[pattern color = gray,pattern = north west lines] (3,4.5) -- (3,0) -- (4,0) -- (4,4.5);
 \draw (0,0) grid (4,2);
@@
   \draw (\x,2) -- (\x,4);
+  \draw[smalldash] (\x,4) -- (\x,4.5);
   };
@@
 }
-\foreach \c in {(0.5,1.5),(2.5,1.5),(2.5,2.5)} {
+\foreach \c in {(0.5,1.5),(2.5,1.5),(2.5,2.5),(2.5,3.3)} {
   \node at \c {\lezero};
@@
 \node[red] at (2.5,0.5) {\leplus};
-\node at (2.5,3.5) {$\vdots$};
-\begin{scope}
-\fill[pattern color = gray,pattern = horizontal lines] (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4) -- (4,4) -- (4,2);
+\node at (2.5,4.2) {$\vdots$};
+\begin{scope}
+\fill[pattern color = gray,pattern = horizontal lines] (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4) -- (6.6,4.5) -- (4,4.5) -- (4,2);
 \draw (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4);
+\draw[smalldash] (6.5,4) -- (6.6,4.5);
 \end{scope}
 %\fill[color = white,path fading = south] (0,2) rectangle (6.5,4.1);
-\node[below] at (0.5,0) {\tiny $n\vphantom{1}$};
-\node[below] at (1.5,0) {\tiny $n-1$};
-\node[below] at (2.5,0) {\tiny $n-2$};
-\node[below] at (3.5,0) {\tiny $n-3$};
-\node[right] at (4,0.5) {\tiny $n-4$};
-\node[right] at (4,1.5) {\tiny $n-5$};
+\node[below] at (0.5,0) {\scriptsize $n\vphantom{1}$};
+\node[below] at (1.5,0) {\scriptsize $n-1$};
+\node[below] at (2.5,0) {\scriptsize $n-2$};
+\node[below] at (3.5,0) {\scriptsize $n-3$};
+\node[right] at (4,0.5) {\scriptsize $n-4$};
+\node[right] at (4,1.5) {\scriptsize $n-5$};
 \end{scope}
@@
 \begin{scope}[shift = {(9,0)}]
-\draw[pattern color = gray,pattern = north east lines] (0,4) -- (0,2) -- (2,2) -- (2,4);
-\draw[pattern color = gray,pattern = north west lines] (2,4) -- (2,0) -- (3,0) -- (3,4);
+\fill[pattern color = gray,pattern = north east lines] (0,4.5) -- (0,2) -- (2,2) -- (2,4.5);
+\fill[pattern color = gray,pattern = north west lines] (2,4.5) -- (2,0) -- (3,0) -- (3,4.5);
 \draw (0,-1) grid (3,2);
@@
 \begin{scope}[shift = {(-1,0)}]
-\fill[pattern color = gray,pattern = horizontal lines] (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4) -- (4,4) -- (4,2);
+\fill[pattern color = gray,pattern = horizontal lines] (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4) -- (6.6,4.5) -- (4,4.5) -- (4,2);
 \draw (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4);
-\end{scope}
-\node[below] at (0.5,-1) {\tiny $n\vphantom{1}$};
-\node[below] at (1.5,-1) {\tiny $n-1$};
-\node[below] at (2.5,-1) {\tiny $n-2$};
-\node[right] at (3,-0.5) {\tiny $n-3$};
-\node[right] at (3,0.5) {\tiny $n-4$};
-\node[right] at (3,1.5) {\tiny $n-5$};
+\draw[smalldash] (6.5,4) -- (6.6,4.5);
+\end{scope}
+\node[below] at (0.5,-1) {\scriptsize $n\vphantom{1}$};
+\node[below] at (1.5,-1) {\scriptsize $n-1$};
+\node[below] at (2.5,-1) {\scriptsize $n-2$};
+\node[right] at (3,-0.5) {\scriptsize $n-3$};
+\node[right] at (3,0.5) {\scriptsize $n-4$};
+\node[right] at (3,1.5) {\scriptsize $n-5$};
 \end{scope}
@@
 \begin{scope}[shift = {(0,-6)}]
-\draw[pattern color = gray,pattern = north east lines] (0,3) -- (0,1) -- (2,1) -- (2,3);
-\draw[pattern color = gray,pattern = north west lines] (3,3) -- (3,0) -- (4,0) -- (4,3);
+\fill[pattern color = gray,pattern = north east lines] (0,3.5) -- (0,1) -- (2,1) -- (2,3.5);
+\fill[pattern color = gray,pattern = north west lines] (3,3.5) -- (3,0) -- (4,0) -- (4,3.5);
 \draw (0,0) grid (4,1);
@@
   \draw (\x,1) -- (\x,3);
+    \draw[smalldash] (\x,3) -- (\x,3.5);
   };
-\foreach \c in {(0.5,0.5),(1.5,0.5),(2.5,1.5)} {
+\foreach \c in {(0.5,0.5),(1.5,0.5),(2.5,1.5),(2.5,2.3)} {
   \node at \c {\lezero};
 }
-\node at (2.5,2.5) {$\vdots$};
 \node[red] at (2.5,0.5) {\leplus};
+\node at (2.5,3.2) {$\vdots$};
 \begin{scope}[shift = {(1,-1)}]
-\fill[pattern color = gray,pattern = horizontal lines] (3,1) -- (4,1) -- (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4) -- (3,4) -- (3,1);
+\fill[pattern color = gray,pattern = horizontal lines] (3,1) -- (4,1) -- (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4)-- (6.6,4.5) -- (3,4.5) -- (3,1);
 \draw (3,1) -- (4,1) -- (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4);
-\end{scope}
-
-\node[below] at (0.5,0) {\tiny $n\vphantom{1}$};
-\node[below] at (1.5,0) {\tiny $n-1$};
-\node[below] at (2.5,0) {\tiny $n-2$};
-\node[below] at (3.5,0) {\tiny $n-3$};
-\node[below] at (4.5,0) {\tiny $n-4$};
-\node[right] at (5,0.5) {\tiny $n-5$};
+\draw[smalldash] (6.5,4) -- (6.6,4.5);
+\end{scope}
+
+\node[below] at (0.5,0) {\scriptsize $n\vphantom{1}$};
+\node[below] at (1.5,0) {\scriptsize $n-1$};
+\node[below] at (2.5,0) {\scriptsize $n-2$};
+\node[below] at (3.5,0) {\scriptsize $n-3$};
+\node[below] at (4.5,0) {\scriptsize $n-4$};
+\node[right] at (5,0.5) {\scriptsize $n-5$};
 \end{scope}
@@
 \begin{scope}[shift = {(9,-6)}]
-\draw[pattern color = gray,pattern = north east lines] (0,3) -- (0,1) -- (2,1) -- (2,3);
-\draw[pattern color = gray,pattern = north west lines] (2,3) -- (2,0) -- (3,0) -- (3,3);
+\fill[pattern color = gray,pattern = north east lines] (0,3.5) -- (0,1) -- (2,1) -- (2,3.5);
+\fill[pattern color = gray,pattern = north west lines] (2,3.5) -- (2,0) -- (3,0) -- (3,3.5);
 \draw (0,-1) grid (3,1);
@@
   \draw (\x,1) -- (\x,3);
+  \draw[smalldash] (\x,3) -- (\x,3.5);
   };
@@
 \begin{scope}[shift = {(0,-1)}]
-\fill[pattern color = gray,pattern = horizontal lines] (3,1) -- (4,1) -- (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4) -- (3,4) -- (3,1);
+\fill[pattern color = gray,pattern = horizontal lines] (3,1) -- (4,1) -- (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4)-- (6.6,4.5) -- (3,4.5) -- (3,1);
 \draw (3,1) -- (4,1) -- (4,2) .. controls (5.3,2.2) and (4.7,3) .. (5.5,3.2) .. controls (6.3,3.5) .. (6.5,4);
-\end{scope}
-\node[below] at (0.5,-1) {\tiny $n\vphantom{1}$};
-\node[below] at (1.5,-1) {\tiny $n-1$};
-\node[below] at (2.5,-1) {\tiny $n-2$};
-\node at (3.5,-0.7) {\tiny $n-3$};
-\node at (3.7,-0.2) {\tiny $n-4$};
-\node[right] at (4,0.5) {\tiny $n-5$};
+\draw[smalldash] (6.5,4) -- (6.6,4.5);
+\end{scope}
+\node[below] at (0.5,-1) {\scriptsize $n\vphantom{1}$};
+\node[below] at (1.5,-1) {\scriptsize $n-1$};
+\node[below] at (2.5,-1) {\scriptsize $n-2$};
+\node at (3.5,-0.7) {\scriptsize $n-3$};
+\node at (3.7,-0.2) {\scriptsize $n-4$};
+\node[right] at (4,0.5) {\scriptsize $n-5$};
 \end{scope}
@@
 \caption{The Le diagrams for $V$ and $W$ in the setting of Theorem~\ref{thm dim}.
-The shaded regions indicate where the plusses match up perfectly, the red plusses exist if and only if $n-2 \in I_{n-2}^V$, and the blue plusses are the three new plusses coming from the induction step.}\label{fig:le diagrams bijection}
+The shaded regions indicate where the plusses match up perfectly from $V$ to $W$, the red plusses exist if and only if $n-2 \in I_{n-2}^V$, and the blue plusses are the three new plusses coming from the induction step.}\label{fig:le diagrams bijection}
 \end{figure}

### 2019-10-07 GWLDCII.tex
few small changes in read through of sec 5.

@@
 
-The results of Section~\ref{sec GN algorithm} allow us to relate the configuration of propagators in a Wilson loop diagram $W$ to minors of $C(W)$, $R(W)$.
-In this section fix an arbitrary ordering of the propagators, equivalently the rows of $C(W)$.\note{There's some grammatical issues in this paragraph and I'm not sure what it's supposed to be saying.}
+The results of Section~\ref{sec GN algorithm} allow us to relate the configuration of propagators in a Wilson loop diagram $W$ to minors of $C(W)$ contributing to $R(W)$.
+In this section, we fix an arbitrary ordering on the propagators of W, i.e we impose and ordering on the rows of $C(W)$.\note{There's some grammatical issues in this paragraph and I'm not sure what it's supposed to be saying.} \sanote{tweaked?
+better?}
 
@@
 \begin{algorithm}\label{alg WLD to denom via GN}
-Let $W = (\cP,[n])$ be a Wilson loop diagram, and let $C(W)$ be the matrix of $W$ as defined in equation \eqref{C(W) dfn} with a fixed ordering on $\cP$ (see Section~\ref{section WLD background})\note{This was written before the exposition above; now I think we can simplify it to "Let $W$ be a WLD and $C(W)$ its associated matrix?}.
+Let $W = (\cP, [n])$ be a Wilson loop diagram and $C(W)$ be its associated matrix with a fixed ordering imposed on the rows.%Let $W = (\cP,[n])$ be a Wilson loop diagram, and let $C(W)$ be the matrix of $W$ as defined in equation \eqref{C(W) dfn} with a fixed ordering on $\cP$ (see Section~\ref{section WLD background})
+\note{This was written before the exposition above; now I think we can simplify it to "Let $W$ be a WLD and $C(W)$ its associated matrix?}\sanote{agreed. changed. previous text as a comment}
 \begin{itemize}
@@
 The nonzero terms in this sum are precisely those bijections such that each propagator is associated to one of its supporting vertices in $I_i$, namely \hlfix{$I_i(p)$}{do we mean $I_i(p)$ or $V(p)$ here?
-if the first, then the last part of the sentence is wrong}, since only those locations in $C(W)$ are nonzero.
+if the first, then the last part of the sentence is wrong}\sanote{I read this as saying $p \rightarrow I_i(p) \in V(p) \cap I_i$}, since only those locations in $C(W)$ are nonzero.
 Since the nonzero entries of $C(W)$ are independent there can be no cancellation between terms in this expansion.
@@
 Thus if a propagator contributes $m$ in $I_i$ then it must lie outside $p$.
+{\color{violet} Furthermore, by Remark \ref{clockwise ordering rem} and Lemma \ref{no fourth vertex}, if $I_i(q) = m$ then all propagators in $S$ must contribute before $q$.}
 
@@
 So we must have at least one of $m$ and $m+1$ in $I_i$.
-However, all propagators in $S$ contribute to $I_{i}$ strictly before $m$ by \st{the previous paragraph}{\color{violet}Remark {clockwise ordering rem}}\note{The purple edit isn't true: a priori a propagator inside $p$ could lie on edge $m$ and contribute $m$.
-The previous paragraph explains why this doesn't happen.} so, after permuting rows and columns as needed, the matrix giving $\Delta_{I_i}$ has the form
+However, all propagators in $S$ contribute to $I_{i}$ strictly before $m$ by \st{the previous paragraph}{\color{violet}Remark \ref{clockwise ordering rem}}\note{The purple edit isn't true: a priori a propagator inside $p$ could lie on edge $m$ and contribute $m$.
+The previous paragraph explains why this doesn't happen.}\sanote{it doesn't actually.
+It says nothing explicitly about propagator order.
+I'm trying (erroneously) to make this explicit.} so, after permuting rows and columns as needed, the matrix giving $\Delta_{I_i}$ has the form
 \[
@@
 No other propagators can be supported on these vertices since all other propagators are outside of $p$, and $p$ is the first propagator supported at $i$; this explains the zero block.
-Therefore $\Delta_{I_i} = \det A \det C$, and both factors are nontrivial since at least one of $m$ and $m+1$ appear in $I_i$.
+Therefore {\color{violet} up to a sign, }$\Delta_{I_i} = \det A \det C$, and both factors are nontrivial since at least one of $m$ and $m+1$ appear in $I_i$.
 Since $p\in \cP_{in}(p)$ we have $f|\det A${\color{violet}.
@@
 Then all propagators in $S$ contribute to $I_i$ strictly before $j$ and no other propagators are supported on vertices strictly before $j$.
-Thus the matrix giving $\Delta_{I_i}$ has the form {\color{violet}(when reordered according to how they contribute to $I_i$)}
+Thus the matrix giving $\Delta_{I_i}$ has, {\color{violet}after a possible rearrangement of rows, } the form
 \[
@@
 Again two things can now happen.
-If some vertex $j$ or larger (with respect to $<_i$) belongs to $I_i$ then $B$ and $C$ are at least one column wide, and so the block form of the matrix gives a nontrivial factorization of $\Delta_{I_i}=\det A\det B$.
+If some vertex $j$ or larger (with respect to $<_i$) belongs to $I_i$ then $B$ and $C$ are at least one column wide, and so the block form of the matrix gives a nontrivial factorization of \hlfix{$\Delta_{I_i}=\det A\det B$}{$\det A\det C$?}.
 This yields a contradiction as in Case 1: $f|\det A$ and removing a propagator not in $S$ gives a smaller diagram with a factor of degree $\geq 3$, which contradicts our minimality assumption.\note{I rephrased this last sentence quite a bit because earlier things had gotten rephrased} \sanote{reads fine to me.}
@@
 For any fixed bijection $\sigma$ from $\cP\setminus\{p,q\}$ to $I_i \setminus\{a,a+1\}$ for which each propagator is supported on its image under the bijection, we can extend $\sigma$ to a bijection from propagators to $I_i$ in two ways: either $p\mapsto a$ and $q\mapsto a+1$ or $p\mapsto a+1$ and $q\mapsto a$.
-The sum of the contributions of all these bijections to $\Delta_{I_i}$ is therefore the product of $x_{p,a}x_{q,a+1}-x_{p,a+1}x_{q,a}$ {\color{violet} By the arguments in the proof of the claim in part 2 of this theorem} \note{Could this use a ref back to where we discuss this kind of arugment in more detail.}\sanote{see violet?} with the minor coming from $\cP\setminus\{p, q\}$ and $I_i \setminus \{a,a+1\}$.
+The sum of the contributions of all these bijections to $\Delta_{I_i}$ is therefore the product of $(x_{p,a}x_{q,a+1}-x_{p,a+1}x_{q,a})$ \note{Could this use a ref back to where we discuss this kind of arugment in more detail.} with the minor coming from $\cP\setminus\{p, q\}$ and $I_i \setminus \{a,a+1\}$.
 Since there is no cancellation of terms in the expansion of $\Delta_{I_i}$, if any other terms appear then they will cause a factor which is not in the form described in the previous part.
@@
 
-\item If $S_i = \emptyset$ then $r_i = 1$ and we immediately have $r_i | \Delta_{I_i}$; otherwise, let $p\in S_i$.
+\item If \hlfix{$S_i = \emptyset$}{Should we recall the definition of $S_i$ here?
+Not used since 5.1} then $r_i = 1$ and we immediately have $r_i | \Delta_{I_i}$; otherwise, let $p\in S_i$.
 Note that $\Delta_{I_i}$ is homogeneous linear in the variables of the row corresponding to $p$.

### 2019-10-07 GWLDCII.tex
added my thanks, same as the other paper

@@
 \title{Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators}
-\author{Susama Agarwala, Si\^an Fryer, and Karen Yeats}
+\author{Susama Agarwala, Si\^an Fryer, and Karen Yeats\thanks{KY is supported by an NSERC Discovery grant, by the Canada Research Chair program, and though some the time this work was developed also by a Humboldt Fellowship from the Alexander von Humboldt foundation.}}
 %\date{}

### 2019-10-07 GWLDCII.tex
a couple comments

@@
 
-\textbf{Case 2}: Suppose $p = (i, m)$, i.e.
+\textbf{Case 2}: Suppose $p = (i, m)$\note{Do we actually need $m$, if so perhaps should remove as muddies waters}, i.e.
 $p$ has an end on the $i^{th}$ edge.
@@
 The sum of the contributions of all these bijections to $\Delta_{I_i}$ is therefore the product of $(x_{p,a}x_{q,a+1}-x_{p,a+1}x_{q,a})$ \note{Could this use a ref back to where we discuss this kind of arugment in more detail.} with the minor coming from $\cP\setminus\{p, q\}$ and $I_i \setminus \{a,a+1\}$.
-Since there is no cancellation of terms in the expansion of $\Delta_{I_i}$, if any other terms appear then they will cause a factor which is not in the form described in the previous part.
+Since there is no cancellation of terms in the expansion of $\Delta_{I_i}$, if any other terms appear then they will cause a factor which is not in the form described in the previous part\note{let's talk about this}.
 Therefore no such terms exist and $x_{p,a}x_{q,a+1}-x_{p,a+1}x_{q,a}$ is a factor of $\Delta_{I_i}$.

### 2019-10-07 GWLDCII.tex
changes from being on the phone

--- 2019-10-07 GWLDCII.tex
@@
 \title{Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators}
-\author{Susama Agarwala, Si\^an Fryer, and Karen Yeats}
+\author{Susama Agarwala\thanks{SA was partially supported by an Office of Naval Research grant.}, Si\^an Fryer, and Karen Yeats\thanks{KY is supported by an NSERC Discovery grant, by the Canada Research Chair program, and though some the time this work was developed also by a Humboldt Fellowship from the Alexander von Humboldt foundation.}}
 %\date{}
@@
 
-The results of Section~\ref{sec GN algorithm} allow us to relate the configuration of propagators in a Wilson loop diagram $W$ to minors of $C(W)$ contributing to $R(W)$.
-In this section, we fix an arbitrary ordering on the propagators of W, i.e we impose and ordering on the rows of $C(W)$.\note{There's some grammatical issues in this paragraph and I'm not sure what it's supposed to be saying.} \sanote{tweaked?
-better?}
+The results of Section~\ref{sec GN algorithm} allow us to relate the configuration of propagators in a Wilson loop diagram $W$ to minors of $C(W)$ that contribute to $R(W)$.
+
+In this section, we fix an arbitrary ordering on the propagators of W, i.e we impose an ordering on the rows of $C(W)$.
 
@@
 \begin{algorithm}\label{alg WLD to denom via GN}
-Let $W = (\cP, [n])$ be a Wilson loop diagram and $C(W)$ be its associated matrix with a fixed ordering imposed on the rows.%Let $W = (\cP,[n])$ be a Wilson loop diagram, and let $C(W)$ be the matrix of $W$ as defined in equation \eqref{C(W) dfn} with a fixed ordering on $\cP$ (see Section~\ref{section WLD background})
-\note{This was written before the exposition above; now I think we can simplify it to "Let $W$ be a WLD and $C(W)$ its associated matrix?}\sanote{agreed. changed. previous text as a comment}
+Let $W = (\cP, [n])$ be a Wilson loop diagram and $C(W)$ be its associated matrix.
+% with a fixed ordering imposed on the rows.%Let $W = (\cP,[n])$ be a Wilson loop diagram, and let $C(W)$ be the matrix of $W$ as defined in equation \eqref{C(W) dfn} with a fixed ordering on $\cP$ (see Section~\ref{section WLD background})
 \begin{itemize}
@@
 All linear factors of  $\Delta_{I_i}$ are single variables and all irreducible quadratic factors are $2\times 2$ determinants of single variables.
-    \item Quadratic factors in $\Delta_{I_i}$ arise precisely when propagators $p$ and $q$ are supported on a common edge \st{$(a,b)$}{\color{violet}$(a,a+1)$} with $I_i(p)=a$ and \st{$I_i(q)=b$}{\color{violet}$I_i(q)=a+1$}.\sanote{would like to make this change throughout}
+    \item Quadratic factors in $\Delta_{I_i}$ arise precisely when propagators $p$ and $q$ are supported on a common edge $a$ with $I_i(p)=a$ and $I_i(q)=a+1$.
     \item $r_i$ divides $\Delta_{I_i}$.
@@
     \item Viewing the determinant as a sum over permutations, and combining this with Corollary~\ref{lem basis as perm}, we see that $\Delta_{I_i}$ is a sum over bijections between $I_i$ and $\mathcal{P}$.
-The nonzero terms in this sum are precisely those bijections such that each propagator is associated to one of its supporting vertices in $I_i$, namely \hlfix{$I_i(p)$}{do we mean $I_i(p)$ or $V(p)$ here?
-if the first, then the last part of the sentence is wrong}\sanote{I read this as saying $p \rightarrow I_i(p) \in V(p) \cap I_i$}, since only those locations in $C(W)$ are nonzero.
+The nonzero terms in this sum are precisely those bijections such that each propagator is associated to one of its supporting vertices in $I_i$, since only those locations in $C(W)$ are nonzero.
 Since the nonzero entries of $C(W)$ are independent there can be no cancellation between terms in this expansion.
@@
 By Remark \ref{rmk algorithm locally same}, $I_i$ and $I_{i+1}$ can only differ once $p$ contributes to $I_{i+1}$, so $I_i(q) = I_{i+1}(q)$ for each $q \in S \backslash \{p\}$.
-Thus if a propagator contributes $m$ in $I_i$ then it must lie outside $p$.
-{\color{violet} Furthermore, by Remark \ref{clockwise ordering rem} and Lemma \ref{no fourth vertex}, if $I_i(q) = m$ then all propagators in $S$ must contribute before $q$.}
+Thus every propagator inside $p$ contributes before $m$ and if a propagator contributes $m$ in $I_i$ then it must lie outside $p$.
 
@@
 So we must have at least one of $m$ and $m+1$ in $I_i$.
-However, all propagators in $S$ contribute to $I_{i}$ strictly before $m$ by \st{the previous paragraph}{\color{violet}Remark \ref{clockwise ordering rem}}\note{The purple edit isn't true: a priori a propagator inside $p$ could lie on edge $m$ and contribute $m$.
-The previous paragraph explains why this doesn't happen.}\sanote{it doesn't actually.
-It says nothing explicitly about propagator order.
-I'm trying (erroneously) to make this explicit.} so, after permuting rows and columns as needed, the matrix giving $\Delta_{I_i}$ has the form
+However, all propagators in $S$ contribute to $I_{i}$ strictly before $m$ by the previous paragraph so, after permuting rows and columns as needed, the matrix giving $\Delta_{I_i}$ has the form
 \[
@@
 No other propagators can be supported on these vertices since all other propagators are outside of $p$, and $p$ is the first propagator supported at $i$; this explains the zero block.
-Therefore {\color{violet} up to a sign, }$\Delta_{I_i} = \det A \det C$, and both factors are nontrivial since at least one of $m$ and $m+1$ appear in $I_i$.
-Since $p\in \cP_{in}(p)$ we have $f|\det A${\color{violet}.
-If we remove the propagators that contribute variables to the minor $C$,}\st{ and if we remove the propagator outside of $p$ that contributes $m$ or $m+1$,} we get a diagram $W'$ with fewer propagators for which $\det A | \Delta_{I^{W'}_i}$ still holds, hence $f|\Delta_{I^{W'}_i}$.
+Therefore $\Delta_{I_i} = \pm \det A \det C$, and both factors are nontrivial since at least one of $m$ and $m+1$ appear in $I_i$.
+Since $p\in \cP_{in}(p)$ we have $f|\det A$ and if we remove a propagator outside of $p$ that contributes either $m$ or $m+1$, we get a diagram $W'$ with fewer propagators for which $\det A | \Delta_{I^{W'}_i}$ still holds, hence $f|\Delta_{I^{W'}_i}$.
 This contradicts the minimality of our choices.
-\sanote{trying to make clear that the minor changes with the diagram.
-May have just made it too notation heavy.}
 
@@
 If no other propagators are supported on the vertex $i$ then the corresponding column of $C(W)$ has only one nonzero entry in it, and so $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$; as above, this is a contradiction.
-\st{Since $I_i(p) = i$ there can be no propagator supported on $i$ with an end on the edge $(i-1, i)$.
-Thus to have another propagator supported on $i$ there is at least one other propagator on edge $(i,i+1)$.
-Further since since $I_i(p)=i$, one of these other propagators contributes $i+1$ in $I_i$, so we can take $q$ to be the propagator such that $I_i(q)=i+1$.
-We know that $q$ has one end on the edge $(i, i+1)$ and is adjacent to $p$ on that edge in the counterclockwise direction (see Figure {\ref{fig no big factors}}).}  \hlfix{Since $p$ is the first propagator in the ordering imposed by $I_i$, it is the counterclockwise most propagator supported on $i$ (by Remark {\ref{clockwise ordering rem}}).
-Since there are multiple propagators supported on $i$, there must be a $q$ ending on edge $i$, such that $I_i(q) = i+1$, that is second clockwisemost propagators supported by $i$.}{Alt.
-proof} Write $q = (i, j)$ for the support of $q$.
-The situation for $q$ is very similar to case 1: \st{in particular, we have $I_{i+1}(q) = j$ by Lemma {\ref{vertex cyclic int lem}} and so if $j\in I_i$ then the propagator which contributes $j$ is outside of $q$.}{\color{violet}if we have $r$ such that $I_i(r) = j$, as above, $r$ lies outside $q$: $r \in \cP_{out}(q, <_i)$.
-}
+Since $p$ is the first propagator in the ordering imposed by $I_i$, it is the clockwise most propagator supported on $i$ (by Remark {\ref{clockwise ordering rem}}).
+Since there are multiple propagators supported on $i$, there must be a $q$ ending on edge $i$, such that $I_i(q) = i+1$, that is second clockwisemost propagators supported by $i$ (see Figure~\ref{fig no big factors}).
+Write $q = (i, j)$ for the support of $q$.
+The situation for $q$ is very similar to case 1: in particular, we have $I_{i+1}(q) = j$ by Lemma {\ref{vertex cyclic int lem}} and so if $j\in I_i$ then the propagator which contributes $j$ is outside of $q$.
+    %\color{violet}if we have $r$ such that $I_i(r) = j$, as above, $r$ lies outside $q$: $r \in \cP_{out}(q, <_i)$.
 
@@
 Then all propagators in $S$ contribute to $I_i$ strictly before $j$ and no other propagators are supported on vertices strictly before $j$.
-Thus the matrix giving $\Delta_{I_i}$ has, {\color{violet}after a possible rearrangement of rows, } the form
+Thus after permuting rows and columns as needed the matrix giving $\Delta_{I_i}$ has the form
 \[
@@
 Again two things can now happen.
-If some vertex $j$ or larger (with respect to $<_i$) belongs to $I_i$ then $B$ and $C$ are at least one column wide, and so the block form of the matrix gives a nontrivial factorization of \hlfix{$\Delta_{I_i}=\det A\det B$}{$\det A\det C$?}.
-This yields a contradiction as in Case 1: $f|\det A$ and removing a propagator not in $S$ gives a smaller diagram with a factor of degree $\geq 3$, which contradicts our minimality assumption.\note{I rephrased this last sentence quite a bit because earlier things had gotten rephrased} \sanote{reads fine to me.}
+If some vertex $j$ or larger (with respect to $<_i$) belongs to $I_i$ then $B$ and $C$ are at least one column wide, and so the block form of the matrix gives a nontrivial factorization of $\Delta_{I_i}=\pm\det A\det C$.
+This yields a contradiction as in Case 1: $f|\det A$ and removing a propagator not in $S$ gives a smaller diagram with a factor of degree $\geq 3$, which contradicts our minimality assumption.
 
@@
 
-\item \sanote{changed $b$ to $a+1$ here.} Suppose propagators $p$ and $q$ are supported on a common edge  $a$, with $I_i(p)=a$ and $I_i(q)=a+1$.
+\item Suppose propagators $p$ and $q$ are supported on a common edge  $a$, with $I_i(p)=a$ and $I_i(q)=a+1$.
 Let $x_{p,a},x_{p,a+1},x_{q,a},x_{q,a+1}$ be the associated variables in $C(W)$.
 For any fixed bijection $\sigma$ from $\cP\setminus\{p,q\}$ to $I_i \setminus\{a,a+1\}$ for which each propagator is supported on its image under the bijection, we can extend $\sigma$ to a bijection from propagators to $I_i$ in two ways: either $p\mapsto a$ and $q\mapsto a+1$ or $p\mapsto a+1$ and $q\mapsto a$.
-The sum of the contributions of all these bijections to $\Delta_{I_i}$ is therefore the product of $(x_{p,a}x_{q,a+1}-x_{p,a+1}x_{q,a})$ \note{Could this use a ref back to where we discuss this kind of arugment in more detail.} with the minor coming from $\cP\setminus\{p, q\}$ and $I_i \setminus \{a,a+1\}$.
-Since there is no cancellation of terms in the expansion of $\Delta_{I_i}$, if any other terms appear then they will cause a factor which is not in the form described in the previous part.
-Therefore no such terms exist and $x_{p,a}x_{q,a+1}-x_{p,a+1}x_{q,a}$ is a factor of $\Delta_{I_i}$.
+The sum of the contributions of all these bijections to $\Delta_{I_i}$ is therefore the product of $(x_{p,a}x_{q,a+1}-x_{p,a+1}x_{q,a})$  with the minor coming from $\cP\setminus\{p, q\}$ and $I_i \setminus \{a,a+1\}$.
+Since there is no cancellation of terms in the expansion of $\Delta_{I_i}$, if any other terms appear then they will cause a factor which is not in the form described at the beginning of the proof of part (2).
+Therefore no such terms exist and $(x_{p,a}x_{q,a+1}-x_{p,a+1}x_{q,a})$ is a factor of $\Delta_{I_i}$.
 
@@
 By part (2) we know that $f$ is a $2\times 2$ minor coming from two propagators, call them $p$ and $q$, and two vertices, call them $a <_i b$.
-It remains to show that \st{$a$ and $b$ are adjacent} {\color{violet}$b = a+1$}.
+It remains to show that $b = a+1$.
 From this we can conclude that $p$ and $q$ each have one end on edge $a$.
-\st{, as any other way for both $p$ and $q$ to be supported on two consecutive vertices would contradict noncrossing or the density requirement of admissibility.}
-
-As in the proof of part (2), make a new admissible diagram by removing the propagators which come before {\color{violet} those contibuting to} $f$ {\color{violet}in the order imposed by $I_i$} and set $i=a$.
+
+As in the proof of part (2), make a new admissible diagram by removing the propagators which come before those contibuting to $f$ in the order imposed by $I_i$.
+Then without loss of generality we may assume $i=a$.
 The cases in the proof of part (2) show how $\Delta_{I_i}$ factors: in particular the vertices supporting the other end of $p$ either do not appear in $I_i$, or they contribute to a different factor of $\Delta_{I_i}$ than $p$ and $a$ do.

### 2019-10-08 GWLDCII.tex
updates to figures as discussed

@@
 \newcommand{\lezero}{\Large $0$}
+
+\newcommand{\leplusbold}[1][black]{%
+  \tikz\draw[#1,line width=1.5pt,scale = 0.35,line cap = round] (0,0) -- (1,0)(0.5,0.5) -- (0.5,-0.5);
+}
 
@@
 If the other end of $p_r$ (i.e.
-the end not supported on $a_r$) lies on an edge between $a_r$ and $j_m$, then since $q$ is inside $p_r$ with respect to $<_{a_r-1}$ we must have $V(q) \subseteq [a_r-1,j_m]$, and hence $q \in \cP_{m-1}$ by Lemma~\ref{lem no fourth vertex}.
+the end not supported on $a_r$) lies on an edge between $a_r$ and $j_m$, then since $q$ is inside $p_r$ with respect to $<_{a_r-1}$ we must have $V(q) \subseteq [a_r-1,j_m]$, and hence $q \in \cP_{m-1}$ by Lemma~\ref{lem no fourth vertex}; this is illustrated in Figure~\ref{fig gn proof induction 1}.
 In particular, if $l=1$ then $p_r \in Q_{0} = \Prop(j_m)$ and we must be in this case.
 
-If not, then there must be some propagator $p_s \in Q_{l-2}$ such that $p_r$ and $p_s$ are both supported on $I_i(p_s) := a_s$.
+If not, then there must be some propagator $p_s \in Q_{l-2}$ such that $p_r$ and $p_s$ are both supported on $I_i(p_s) := a_s$; see Figure~\ref{fig gn proof induction 2}.
 Since $p_r$ is clockwise of $q$, and $q$ cannot be supported on $I_i(p_s)$ since $q \not\in Q_{l-1}$, it follows that $I_i(p_s) <_i I_i(p_r)$.
@@
 
-\note{Sian note to self: this picture isn't right}
-\begin{figure}[h]
-\bas{\begin{tikzpicture}[baseline=(current bounding box.east)]
-\begin{scope}
-	\drawWLDfragment[9]{3}{0.3} % draw arc
-	%\drawnumbers % use this to debug
-	% highlight region
-	%\centerarc[linehighlight](0,0)(\zero + 3.6*\step:\zero + 5.4*\step:\radius)
-	% region label
-	%\node[align = center] at (\zero + 4.5*\step:\radius*1.3) {\em \footnotesize 0, 1, or 2 vertices \\[3pt]\em \footnotesize in this region};
-	% scope to draw props and their labels
-	\begin{scope}
-		\clipcenterarc(0,0)(\startpoint-20:\endpoint+20:\radius)
-		%p_r
-		\draw[smallpropagator] (\zero+2.3*\step:\radius*1.1) to [bend left = 55] (\zero + 6.7*\step:\radius*1.1); 
-		%q
-		\draw[smallpropagator] (\zero+2.4*\step:\radius*1.1) to [bend left = 55] (\zero + 5.3*\step:\radius*1.1); 
-		%\draw[smallpropagator,light-gray] (\zero+7.5*\step:\radius*1.1) -- (0:\radius*0.25);  
-		\node at (\zero + 2.8*\step:\radius*0.8){\footnotesize $p_r$};
-		\node at (\zero + 4.7*\step:\radius*.84){\footnotesize $q$};
-	\end{scope}
-	% draw nodes
-	\newnode[left]{1}{i}
-	\newnode[below]{2}{a_r}
-	\newnode[below]{3}{}
-	\newnode[right]{9}{j_m}
-	% case label
-	\node at (270:\radius*0.1) {\em all vertices of $p_r$ lie between $a_r-1$ and $j_m$};
-\end{scope}
-\end{tikzpicture} \qquad \qquad \begin{tikzpicture}[baseline=(current bounding box.east)]
-\begin{scope}
-	\drawWLDfragment[10]{3}{0.3} % draw arc
-	%\drawnumbers % use this to debug
-	% highlight region
-		% scope to draw props and their labels
-	\begin{scope}
-		\clipcenterarc(0,0)(\startpoint-20:\endpoint+20:\radius)
-		%random prop preventing p_s from contributing a_s-1
-		\draw[smallpropagator,gray] (\zero+2.3*\step:\radius) -- (\zero + 16.5*\step:\radius) ;
-		%p_s
-		\draw[smallpropagator] (\zero+2.4*\step:\radius*1.1) to [bend left = 55] (\zero + 7.5*\step:\radius*1.1); 
-		%p_r
-		\draw[smallpropagator] (\zero+2.5*\step:\radius*1.1) to [bend left = 90] (\zero + 4.5*\step:\radius*1.1); 
-		%q
-		\draw[smallpropagator] (\zero+4.55*\step:\radius*1.1) to [bend left = 70] (\zero + 6.7*\step:\radius*1.1); 
-		\node at (\zero + 4.5*\step:\radius*0.55){\footnotesize $p_s$};
-		\node at (\zero + 3.5*\step:\radius*0.84){\footnotesize $p_r$};
-		\node at (\zero + 6.2*\step:\radius*0.85){\footnotesize $q$};
-	\end{scope}
-	% draw nodes
-	\newnode[left]{1}{i}
-	\newnode[below]{2}{}
-	\newnode[below]{3}{a_s}
-	\newnode[below]{4}{a_r}
-	\newnode[below]{5}{}
-	\newnode[below]{8}{}
-	\newnode[right]{9}{j_m}
-	% case label
-	\node at (270:\radius*0.1) {\em all vertices of $p_r$ do not lie between $a_r-1$ and $j_m$};
-\end{scope} 
-\end{tikzpicture} }\eas
-\caption{The two cases of the induction step. Note that $I_i(p_s) <_i I_i(p_r)$}\label{fig:awkward induction step}
+\begin{figure}
+\[
+\begin{tikzpicture}[baseline=(current bounding box.east)]
+  \begin{scope}
+  \drawWLDfragment[10]{4}{0.4} 
+  %\drawnumberspartial % use this to debug
+  \centerarc[linehighlight](0,0)(\zero + 2.6*\step:\zero + 3.9*\step:\radius)
+  \newnode{1}{i}
+  \newnode[right]{10}{j_m}
+  \begin{scope}
+\clipcenterarc(0,0)(\startpoint:\endpoint:\radius)
+\newpropbend{3}{8.5}{50}
+\newpropbend{3.3}{7}{40}
+\end{scope}
+\node at (\zero+5*\step:\radius*0.46) {\scriptsize $p_r$};
+\node at (\zero + 6*\step:\radius*0.75) {\scriptsize $q$};
+\node at (\zero + 3.2*\step:\radius*1.1) {\scriptsize $a_r$};
+\end{scope}
+\end{tikzpicture}
+\]
+\caption{If $q$ is counterclockwise of $p_r$ and the other end of $p_r$ lies on an edge between $a_r$ and $j_m$, then $V(q) \subseteq [a_{r-1},j_m]$.
+The vertex $a_r$ lies somewhere within the (blue) highlighted region.}\label{fig gn proof induction 1}
+\end{figure}
+
+\begin{figure}
+\[
+\begin{tikzpicture}[baseline=(current bounding box.east)]
+  \begin{scope}
+  \drawWLDfragment[10]{4}{0.3} 
+  %\drawnumberspartial % use this to debug
+  \centerarc[linehighlight](0,0)(\zero + 4.5*\step:\zero + 5.3*\step:\radius)
+  \newnode{1}{i}
+  \newnode[below]{6}{a_r}
+  \newnode[right]{10}{j_m}
+  \begin{scope}
+\clipcenterarc(0,0)(\startpoint:\endpoint:\radius)
+\clip (\zero + 5.5*\step:\radius*1.5) circle (\radius*0.85);
+\newpropbend{5}{18}{30} %p_s
+\newpropbend{5.5}{15}{30} %p_r
+\newpropbend{6}{12}{30} %q
+\end{scope}
+\node at (\zero+5.7*\step:\radius*0.72) {\scriptsize $p_r$};
+\node at (\zero+4.15*\step:\radius*0.71) {\scriptsize $p_s$};
+\node at (\zero + 6.8*\step:\radius*0.83) {\scriptsize $q$};
+\node at (\zero + 5*\step:\radius*1.07) {\scriptsize $a_s$};
+\end{scope}
+\end{tikzpicture}
+\qquad \qquad
+\begin{tikzpicture}[baseline=(current bounding box.east)]
+  \begin{scope}
+  \drawWLDfragment[10]{4}{0.3} 
+  %\drawnumberspartial % use this to debug
+  \centerarc[linehighlight](0,0)(\zero + 2.5*\step:\zero + 3.7*\step:\radius)
+  \centerarc[linehighlight](0,0)(\zero + 6.3*\step:\zero + 7.5*\step:\radius)
+  \newnode{1}{i}
+  \newnode[right]{10}{j_m}
+  \begin{scope}
+\clipcenterarc(0,0)(\startpoint:\endpoint-\step:\radius)
+%\clip (\zero + 5.5*\step:\radius*1.5) circle (\radius*0.85);
+\newpropbend{2.9}{15}{30} %p_s
+\newpropbend{3}{6.8}{45} %p_r
+\newpropbend{7}{15}{30} %q
+\end{scope}
+\node at (\zero+5.3*\step:\radius*0.78) {\scriptsize $p_r$};
+\node at (\zero+2.3*\step:\radius*0.8) {\scriptsize $p_s$};
+\node at (\zero + 7.4*\step:\radius*0.8) {\scriptsize $q$};
+\node at (\zero + 3*\step:\radius*1.07) {\scriptsize $a_s$};
+\node at (\zero + 7*\step:\radius*1.07) {\scriptsize $a_r$};
+\end{scope}
+\end{tikzpicture}
+\]
+\caption{If the other end of $p_r$ does not lie on an edge between $a_r$ and $j_m$, then we must have a propagator $p_s \in Q_{l-2}$ in one of the depicted configurations.
+The (blue) highlighted regions indicate the approximate position of a vertex whose precise position is unknown.
+Cut-off propagators indicate that the location of the propagator's other end is unknown; in particular, no meaning should be ascribed to the angle at which these propagators are drawn.}\label{fig gn proof induction 2}
 \end{figure}
@@
 \] 
-  \caption{The two cases for $W$ and $p$.  No other propagators can end in the red sections.  Other segments may have additional propagators ending in them.}\label{fig special p}
+  \caption{The two cases for $W$ and $p$.  No other propagators can end in the bolded (red) sections.  Other segments may have additional propagators ending in them.}\label{fig special p}
 
@@
 }
-\node[red] at (2.5,0.5) {\leplus};
+\node[red] at (2.5,0.5) {\leplusbold[red]};
 \node at (2.5,4.2) {$\vdots$};
@@
 }
-\node[red] at (0.5,1.5) {\leplus};
+\node[red] at (0.5,1.5) {\leplusbold[red]};
 \foreach \c in {(0.5,-0.5),(1.5,-0.5),(2.5,-0.5)} {
@@
 }
-\node[red] at (2.5,0.5) {\leplus};
+\node[red] at (2.5,0.5) {\leplusbold[red]};
 \node at (2.5,3.2) {$\vdots$};
@@
 \node at (0.5,0.5) {\lezero};
-\node[red] at (1.5,0.5) {\leplus};
+\node[red] at (1.5,0.5) {\leplusbold[red]};
 \foreach \c in {(0.5,-0.5),(1.5,-0.5),(2.5,-0.5)} {
@@
 \caption{The Le diagrams for $V$ and $W$ in the setting of Theorem~\ref{thm dim}.
-The shaded regions indicate where the plusses match up perfectly from $V$ to $W$, the red plusses exist if and only if $n-2 \in I_{n-2}^V$, and the blue plusses are the three new plusses coming from the induction step.}\label{fig:le diagrams bijection}
+The shaded regions indicate where the plusses match up perfectly from $V$ to $W$, the bold (red) plusses exist if and only if $n-2 \in I_{n-2}^V$, and the (blue) plusses in the bottom row of the $W$ diagrams are the three new plusses coming from the induction step.}\label{fig:le diagrams bijection}
 \end{figure}
@@
   \node[align = center,black] at (\zero + 6.8*\step:1.5*\radius) {\em \footnotesize If $j \in I_i$ then it was \\ \em \footnotesize contributed by a propagator \\ \em \footnotesize outside of $q$};
-    \node[align = center,black] at (110:\radius*0.5) {\em Case 2: $p = (i,j)$};
+    \node[align = center,black] at (110:\radius*0.5) {\em Case 2: $p = (i,m)$};
 

### 2019-10-09 GWLDCII.tex
grammar and spelling readthrough of sections 1 through 4

@@
   Wilson loop diagrams are an important tool in studying scattering amplitudes of SYM $N=4$ theory and are known by previous work to be associated to positroids.
-In this paper we study the structure of the associated positroids, as well as the structure of the denominator of integral defined by each diagram.
-In particular, we give an algorithm to derive the Grassman necklace of the assoicated positroid directly from the Wilson loop diagram.
-We also give a recursive proof that the dimension of these cells is thrice the number of propagators in the diagram.
+In this paper we study the structure of the associated positroids, as well as the structure of the denominator of the integral defined by each diagram.
+We give an algorithm to derive the Grassmann necklace of the associated positroid directly from the Wilson loop diagram, and a recursive proof that the dimension of these cells is thrice the number of propagators in the diagram.
 We also show that the denominator in the integral is the radical of the product of minors defined by the elements of the Grassmann necklace.
@@
 Moreover, integrals associated to the BCFW diagrams define a volume form on the Amplituhedron.
-This both gives a novel and elegant interpretation of scattering amplitudes for this theory, as well as a means of greatly simplifying the calculations involved in traditional Feynman diagram approaches.
+This gives a novel and elegant interpretation of scattering amplitudes for this theory, as well as a means of greatly simplifying the calculations involved in traditional Feynman diagram approaches.
 Since then, there has been significant work to understand the volume form and its physical implications \cite{UnwindingAmplituhedron,galashinlam}.
@@
 As with the Amplituhedron, each Wilson loop represents the sum of a family of $N^kMHV$ Feynman diagrams, and adding up the corresponding sums of Feynman integrals associates a volume form to a convex space different from the Amplituhedron \cite{Hodges2013}.
-Agarwala and Marin-Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that can be realized as an element of $\Gr(k,n)$ \cite{wilsonloop}.
+In  \cite{wilsonloop}, Agarwala and Marin-Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that can be realized as an element of $\Gr(k,n)$.
 Other work has shown a connection between the volume filled by Wilson loop diagrams and the Amplituhedron \cite{casestudy, Amplituhedronsquared}.
@@
 This paper continues this work by identifying which positroid cells are associated to which Wilson loop diagram: specifically, we give an algorithm to read off the Grassmann necklace of the associated positroid cell from the Wilson loop diagram.
-We also show that the positroid cells associated to Wilson loop diagrams are all $3k$-dimensional; by contrast, the BCFW cells are all $4k$-dimensional \cite{Arkani-Hamed:2013jha}.
+We also show that the positroid cells associated to Wilson loop diagrams are all $3k$-dimensional, where $k$ is the number of propagators in the diagram; by contrast, the BCFW cells are all $4k$-dimensional \cite{Arkani-Hamed:2013jha}.
 Again, this is not too alarming, as it was shown in \cite{non-orientable} that the actual geometric space defined by the Wilson loop diagrams is a non-orientable $k$-dimensional bundle over this $3k$ dimensional manifold in $\Gr(k,n)$.
@@
 
-In Section~\ref{sec GN algorithm} we state an algorithm for constructing the Grassmann necklace of the positroid associated to a Wilson loop diagram (Algorithm~\ref{alg:put GN on WLD}) and prove its correctness (Theorem~\ref{res:alg gives GN}).
+In Section~\ref{sec GN algorithm} we state an algorithm for constructing the Grassmann necklace of the positroid associated to a Wilson loop diagram (Algorithm~\ref{alg:put GN on WLD}) and prove its correctness (Theorem~\ref{res:alg gives GN}, Theorem~\ref{res alg gives correct GN}).
 While it was already possible to construct the Grassmann necklace of a Wilson loop diagram via existing bijections between some of the various combinatorial objects that index the positroid cells, this process was convoluted and involved multiple steps; our algorithm allows us to track directly how each propagator in the Wilson loop diagram contributes to each term in the Grassmann necklace.
-Furthermore, the above algorithm allows us to understand the positroids associated to Wilson loop better.
+Furthermore, the above algorithm allows us to better understand the positroids associated to Wilson loop.
 In particular, Corollary \ref{no coloops} shows that these positroids have no coloops, and gives an exact characterization of their loops.
-Many of the technical lemmas required to prove Theorem~\ref{res:alg gives GN} continue to be important in subsequent sections: in particular we have Lemma~\ref{lem sian}, which identifies certain configurations of propagators that must appear in any admissible Wilson loop diagram, and Lemma~\ref{vertex cyclic int lem}, which shows that the pattern of values that a propagator contributes to each term of the Grassmann necklace is both simple and predictable.
+Many of the technical lemmas required to prove Theorem~\ref{res:alg gives GN} and Theorem~\ref{res alg gives correct GN} continue to be important in subsequent sections: in particular we have Lemma~\ref{lem sian}, which identifies certain configurations of propagators that must appear in any admissible Wilson loop diagram, and Lemma~\ref{vertex cyclic int lem}, which shows that the pattern of values that a propagator contributes to each term of the Grassmann necklace is both simple and predictable.
 
@@
 
-\subsection{Wilson Loop diagrams}\label{section WLD background}
+\subsection{Wilson loop diagrams}\label{section WLD background}
 
@@
 The arc between two consecutive vertices is referred to as an {\bf edge} of the diagram, and the $i$th edge of $W$ is the edge from vertex $i$ to its successor.
-Each propagator $(i,j) \in \cP$ is denoted by a wavy line inside the circle joining edge $i$ and edge $j$.
+Each propagator $(i,j) \in \cP$ is denoted by a wavy line joining edge $i$ and edge $j$ inside the circle.
 
@@
 In particular, if $V = [n]$ then $(n,n+3)$ means the propagator connecting edges $3$ and $n$.
-This viewpoint is beneficial for us since many of our proofs rely on restricting our attention to a region of the diagram bounded by a given propagator, or to short propagators such as $(i,i+2)$, and these behave the same regardless of whether we cross the ``first'' vertex or not; however, we emphasize that this is different to the standard convention in the physics literature, where propagators are written $(i,j)$ with $1 \leq i<j \leq n$.
+This viewpoint is beneficial for us since many of our proofs rely on restricting our attention to a region of the diagram bounded by a given propagator, or to short propagators such as $(i,i+2)$, and these behave the same regardless of whether we cross the ``first'' vertex or not.
+However, we emphasize that this is different to the standard convention in the physics literature, where propagators are written $(i,j)$ with $1 \leq i<j \leq n$.
 
@@
 
-In particular, we will see in later sections that all four vertices supporting a propagator are important in understanding the contribution of that propagator to the objects represented by the diagram.
-This motivates the following definition of a subdiagram: any subset $Q$ of the propagators and any subset $U$ of the vertices of $W$ {\em containing the support of $Q$}.
+We will see in later sections that all four vertices supporting a propagator are important in understanding the contribution of that propagator to the objects represented by the diagram.
+This motivates the following definition of a subdiagram, which can consist of any subset $Q$ of the propagators and any subset $U$ of the vertices of $W$ but $U$ {\em must contain the support of $Q$}.
 
@@
 \item There does not exist a non-empty set of propagators $Q \subseteq \cP$ such that $|V(Q)| < |Q| + 3$.
-\item There does not exist a pair of crossing propagators: that is, there does not exist $\{(i,j),(k,l)\} \subseteq \cP$ such that $i < k < j < l$.
+\item There does not exist a pair of crossing propagators: that is, there does not exist ${\{(i,j),(k,l)\} \subseteq \cP}$ such that $i < k < j < l$.
 \end{enumerate}
@@
 This is represented as an integral $I(W)$, which is the equivalent of a Feynman integral in this setting.
-This integral is comprised of two main components, and interaction matrix, $C(W)$ and a volume form, $\Omega(W)$.
-These are described below.
+This integral is comprised of two main components: an interaction matrix $C(W)$, and a volume form $\Omega(W)$.
+These are described next.
 
 A $|\cP| \times n$ matrix $C(W)$ represents the (tree level) particle interactions.
-Each row of $C(W)$ corresponds to an internal propagator, each column to an external particle.
+Each row of $C(W)$ corresponds to an internal propagator, and each column to an external particle (i.e.
+a vertex).
 $C(W)$ is defined as follows:
@@
 The matrix $C(W)$ defines a positroid cell associated to $W$ in the positive Grassmannian $\Gr(n, |\cP|)$, which we denote by $\Sigma(W)$ \cite{wilsonloop}.
-Marcott \cite{WLDdim} shows that  the matrix $C(W)$ parametrizes a space whose close is exactly the closure of $\Sigma(W)$.
+Marcott \cite{WLDdim} shows that  the matrix $C(W)$ parametrizes a space whose \hlfix{close}{closure?} is exactly the closure of $\Sigma(W)$.
 That is, the space defined by $C(W)$ and the cell $\Sigma(W)$ agree up to a set of measure $0$.
-Most of the work in this paper, and in \cite{generalcombinatoricsI} focuses on characterizing the positroid cell associated to each Wilson loop diagram $W$.
+Most of the work in this paper and in the previous paper in the series \cite{generalcombinatoricsI} focuses on characterizing the positroid cell associated to each Wilson loop diagram $W$.
 
 Note that since there is no ordering on the propagators of $W$, $C(W)$ is only defined up to rearrangement of the rows.
-When needed, we will impose various orders on these rows.
-This will not matter, as it does not affect $\Sigma(W)$.
+When needed, we will impose various different orders on these rows to suit the task at hand.
+The choice of ordering does not affect $\Sigma(W)$.
 
@@
 
-In particular, this implies that any singularities in the integrals $I(W)$ must cancel out in the sum, in particular, all poles arising from $R(W)$ must cancel.
+This implies that any singularities in the integrals $I(W)$ must cancel out in the sum; in particular, all poles arising from $R(W)$ must cancel.
 Specifically, these poles must cancel on the boundaries of the positroid cells $\Sigma(W)$, analogous to the analysis in \cite{Arkani-Hamed:2013jha}.
@@
 
-With this motivation in mind, in this paper we study the denominator $R(W)$ of the volume form $\Omega(W)$, which we define next.
+With this motivation in mind, in Section~\ref{sec poles} of this paper we study the denominator $R(W)$ of the volume form $\Omega(W)$. The definition of $R(W)$ is as follows.
 
@@
 Let $\{p_1 \ldots p_r\}$ be the propagators with one end lying on edge $e$ under a counterclockwise ordering.
-That is, $p_1$ is closest to the vertex $e$, $p_i$ is positioned counterclockwise to $p_{i+1}$ and $p_r$ is the clockwise most propagator on this edge (closest to vertex $e+1$).
+That is, $p_1$ is closest to the vertex $e$, $p_i$ is positioned counterclockwise to $p_{i+1}$ and $p_r$ is the clockwise-most propagator on this edge (closest to vertex $e+1$).
 Define the polynomial
@@
 In Section \ref{sec poles}, we show that the denominator $R(W)$ is determined by the positroid cell $\Sigma(W)$ and the structure of $W$, as encapsulated by $C(W)$.
-In fact, it can be read directly off of $C(W)$, in terms of a characterization of $\Sigma(W)$ called the Grassmann necklace (see Definition~\ref{def:grassmann necklace}) as shown in Algorithm \ref{alg:put GN on WLD}.
-We also give an algorithm to read $R(W)$ directly from the Wilson loop diagram, paving the way for a general study of these poles in future.
+In fact, it can be read directly off of $C(W)$ in terms of a characterization of $\Sigma(W)$ called the Grassmann necklace (see Definition~\ref{def:grassmann necklace}).
+In Algorithm~\ref{alg WLD to denom via GN} we give an algorithm to read $R(W)$ directly from the Wilson loop diagram, paving the way for a general study of these poles in future.
 
@@
 Let $M(W)$ be the matroid realized by $C(W)$, i.e.
-the matroid with ground set $[n]$ whose independent sets are exactly the sets $V \subseteq [n]$ such that the columns of $C(W)$ indexed by $V$ are linearly independent.
+the matroid with ground set $[n]$ whose independent sets are exactly those sets $V \subseteq [n]$ such that the columns of $C(W)$ indexed by $V$ are linearly independent.
 
@@
 
-  Alternatively we can simply think about the condition of linear independence in the matrix $C(W)$, the corollary can also be proved directly by linear algebra and the definition of $C(W)$ as follows.
+  Alternatively we can simply think about the condition of linear independence in the matrix $C(W)$, and then the corollary can also be proved directly by linear algebra and the definition of $C(W)$ as follows.
 
@@
 Consequently, a choice of $|J|$ nonzero entries of $C(W)$ one in each row associated to an element of $J$ and each in different columns is equivalent to an assignment of the propagators of $J$ to supporting vertices so that no two are assigned to the same vertex.
-Such an assignment of the propagators of $J$ to supporting vertices is exactly a map $f$ as described in the statment, hence proving the result.
+Such an assignment of the propagators of $J$ to supporting vertices is exactly a map $f$ as described in the statement, hence proving the result.
 \end{proof}
@@
 While this paper primarily approaches proofs from a combinatorial point of view, readers with a background in matroid theory are encouraged to keep the matroidal viewpoint in mind throughout; we expect that the two approaches will be complementary and will build upon each other.
-See \cite{generalcombinatoricsI} for some related results concerning the positroids of Wilson loop diagrams obtained by viewing them primarily as matroids.
+See the first paper in this series \cite{generalcombinatoricsI} for some related results concerning the positroids of Wilson loop diagrams obtained by viewing them primarily as matroids.
 \end{rmk}
 
-\section{Wilson Loop diagrams and their Grassmann necklaces}\label{sec GN algorithm}
+\section{Wilson loop diagrams and their Grassmann necklaces}\label{sec GN algorithm}
 
 In this section we will give an algorithm (Algorithm~\ref{alg:put GN on WLD}) to go directly from a Wilson loop diagram to the Grassmann necklace of its positroid.
+
 This is a useful result in and of itself, as it greatly simplifies the process of identifying the positroid associated to a given Wilson loop diagram.
-Furthemore, we use it to characterize loops and coloops in the positroid associated to a Wilson loop diagram (Corrollary \ref{no coloops}).
-It allows us to see how the Le diagram assoicated to a Wilson loop diagram changes as one adds propagators in certain positions (Theorem \ref{thm dim}).
-Indeed, the techniques we develop in this section to verify that our algorithm produces the correct Grassmann necklace will also be used repeatedly in later sections to calculate the dimension of the associated positroid cell (section \ref{sec dim}) and to study the structure of the poles of the associated integral $I(W)$ (section \ref{sec poles}).
-
-One of the key insights is that each element of the Grassmann necklace can be viewed as a function from the propagators of the diagram to the vertices in the Grassman necklace element.
+We also use it to characterize loops and coloops in the positroid associated to a Wilson loop diagram (Corollary \ref{no coloops}); the characterization of the coloops, in particular, was not at all clear from the definition of Wilson loop diagrams but is an easy corollary of the algorithm.
+
+Furthermore, the algorithm allows us to see how the Le diagram associated to a Wilson loop diagram changes as one adds propagators in certain positions (Theorem \ref{thm dim}).
+Indeed, the techniques we develop in this section to verify that our algorithm produces the correct Grassmann necklace will also be used repeatedly in later sections to calculate the dimension of the associated positroid cell (Section \ref{sec dim}) and to study the structure of the poles of the associated integral $I(W)$ (Section \ref{sec poles}).
+
+One of the key insights is that each element of the Grassmann necklace can be viewed as a function from the propagators of the diagram to the vertices in the Grassmann necklace element.
 This is captured in Definition~\ref{def I_i as a function}, and used throughout the paper.
@@
 
-Before we can describe the algorithm for extracting the Grassmann necklace of $M(W)$ from the Wilson loop diagram $W$, we require some initial results about the behavior of propagators in admissible WLD.
+Before we can describe the algorithm for extracting the Grassmann necklace of $M(W)$ from the Wilson loop diagram $W$, we require some initial results about the behavior of propagators in admissible Wilson loop diagrams.
 
@@
 
-Let $p$ be the propatagor $p = (1, 4)$. Then $\cP_{in}(p, <_4) = \{(1,4), (5, 8), (5, 7) \}$ and $\cP_{out}(p, <_4) = \{(2,4) \}$
+Let $p$ be the propagator $p = (1, 4)$. Then $\cP_{in}(p, <_4) = \{(1,4), (5, 8), (5, 7) \}$ and $\cP_{out}(p, <_4) = \{(2,4) \}$
 \end{eg}
@@
 \item If every vertex in $W$ supports at least one propagator, then $W$ admits at least one propagator of length 2.
-Furthermore, by the same reasoning, if $p=(i,j)$ is a propagator of $W$ and every vertex in $[i,j]$ supports at least one propagator then there is at least one propagator of length $2$ in $\mathcal{P}_{in}(p, <_i)$.
+By the same reasoning, if $p=(i,j)$ is a propagator of $W$ and every vertex in the interval $[i,j]$ supports at least one propagator, then there is at least one propagator of length $2$ in $\mathcal{P}_{in}(p, <_i)$.
 \end{enumerate}
@@
 \]
-\caption{The two configurations described in Lemma~\ref{lem sian}; every weakly admissible Wilson loop diagram with no non-supporting vertices supports at least one example of at least one of these configurations.}\label{fig: small configs}
+\caption{The two configurations described in Lemma~\ref{lem sian}; every weakly admissible Wilson loop diagram with no non-supporting vertices admits at least one example of at least one of these configurations.}\label{fig: small configs}
 \end{figure}
@@
 
-The second case is that there are at least $3$ vertices between one endpoint of $p_{r+1}$ and the nearest endpoint of $q_r$. In other words, (at least) one of the following four things happen:
+The second case is that there are at least $3$ vertices between one endpoint of $p_{r+1}$ and the nearest endpoint of $q_r$. In other words, at least one of the following four things happen:
 \begin{itemize} 
-\item $i_r+3 \leq j_{r+1}\leq k_r-3$ (one endpoint of $p_{r+1}$ has at least 3 vertices between it and the nearest enpoint of $q_r$), or
-\item $i_r+3 \leq j_{r+1}+2\leq k_r-3$ (one endpoint of $p_{r+1}$ has at least 3 vertices between it and the nearest enpoint of $q_r$), or
-\item $i_r = j_{r+1}$ ($p_{r+1}$ and $q_r$ share an end edge), or 
-\item $k_r = j_{r+1} +2$  ($p_{r+1}$ and $q_r$ share an end edge)
+\item $i_r+3 \leq j_{r+1}\leq k_r-3$ (one endpoint of $p_{r+1}$ has at least 3 vertices between it and the nearest endpoint of $q_r$), or
+\item $i_r+3 \leq j_{r+1}+2\leq k_r-3$ (the other endpoint of $p_{r+1}$ has at least 3 vertices between it and the nearest endpoint of $q_r$), or
+\item $i_r = j_{r+1}$ ($p_{r+1}$ and $q_r$ both have an end on edge $i_r$), or 
+\item $k_r = j_{r+1} +2$  ($p_{r+1}$ and $q_r$ both have an end on edge $k_r$).
 \end{itemize}
@@
 
-Since there are at least $3$ vertices between one endpoint of $p_{r+1}$ and the nearest endpoint of $q_r$,  $j_{r+1}+4 \leq k_r-1$ in both of these situations, the vertex $j_{r+1}+4$ is in $[i_r, k_r+1]$ but does not support either $q_r$ or $p_{r+1}$, and must therefore support some other propagator $t$.
+We have $j_{r+1}+4 \leq k_r-1$ in both of these cases: in the situation of the second bullet point this follows directly from the inequality, while in the third case it follows from the fact that $\ell(p_{r+1}) = 2$ and $\ell(q_r) \geq 4$.
+Therefore the vertex $j_{r+1}+4$ is in the interval $[i_r, k_r+1]$ but does not support either $q_r$ or $p_{r+1}$, and must therefore support some other propagator $t$.
 Since $p_{r+1}$ is not part of configuration \ref{item pair of 2s} and $W_r$ has no propagators of length 3, it follows that $\ell(t) \geq 4$.
@@
 
-\subsection{From Wilson Loop diagrams to Grassmann Necklaces}\label{sec:GN alg}
+\subsection{From Wilson loop diagrams to Grassmann necklaces}\label{sec:GN alg}
 
 In this section, we give an algorithm for passing directly from the Wilson loop diagrams to its Grassmann necklace.
-This not only greatly simplifies the previously known process to obtain a positroid cell from a Wilson loop diagram, but will also allow us to relate the behavior of the positroid $M(W)$ directly to the configuration of progators in $W$.
-In section \ref{sec poles} we see that the denominator, $R(W)$, of the integrand associated to a Wilson loop diagram, $I(W)$, can be written in terms of the Grassman Necklace of a diagram.
-
-The fact that Algorithm~\ref{alg:put GN on WLD} does construct the required Grassmann necklace is proved in Theorem~\ref{res:alg gives GN}.
+This not only greatly simplifies the previously known process to obtain a positroid cell from a Wilson loop diagram, but will also allow us to relate the behavior of the positroid $M(W)$ directly to the configuration of propagators in $W$.
+In section \ref{sec poles} we see that the denominator, $R(W)$, of the integrand associated to a Wilson loop diagram, $I(W)$, can be written in terms of the Grassmann necklace of a diagram.
+
+The fact that Algorithm~\ref{alg:put GN on WLD} does construct the required Grassmann necklace is proved in Theorem~\ref{res:alg gives GN} and Theorem~\ref{res alg gives correct GN}.
 A worked example of Algorithm~\ref{alg:put GN on WLD} is given in Example~\ref{eg:apply GN alg}.
@@
 Note that different $I_*$ impose different orderings on the propagators.
-Furthermore, Corollary \ref{GN alg well defined} shows that this ordering respects the ordering of vertices in $I_i$.
-That is, if $p_j$ occurs before $p_l$ in the ordering imposed by $I_i$, then we also have $I_i(p_j) <_i I_i(p_l)$.
+Furthermore, we will see below that this ordering respects the ordering of vertices in $I_i$, i.e.
+if $p_j$ occurs before $p_l$ in the ordering imposed by $I_i$, then we also have $I_i(p_j) <_i I_i(p_l)$.
+This will follow directly from Corollary \ref{GN alg well defined}.
 
@@
 \begin{itemize}
-\item $j = 1$: Since $\Prop(1) = \{q,r\}$ and $r$ is the clockwise-most of these propagators, $r$ contributes at this step: $I_1(r)=1$.
-We let $I_1 = \{1\}$ and remove propagator $r$ from the diagram.
-\item $j = 2$: $\Prop(2) = \{p,q\}$, with $q$ being the clockwise-most of these propagators, $q$ contributes at this step: $I_1(q)=1$. So $I_1 = \{1,2\}$ and propagator $q$ is removed.
-\item $j = 3$: $\Prop(3) = \{p\}$, so now $I_i(p) = 3$ and $I_1 = \{1,2,3\}$. The propagator $p$ is removed. The only remaining propagator in the diagram is $s$.
+\item $j = 1$: Since $\Prop(1) = \{q,r\}$ and $r$ is the clockwise-most of these propagators, $r$ contributes at this step. We let $I_1 = \{1\}$ and remove propagator $r$ from the diagram. 
+\item $j = 2$: $\Prop(2) = \{p,q\}$, with $q$ being the clockwise-most of these propagators, so $q$ contributes at this step. We now have $I_1 = \{1,2\}$ and propagator $q$ is removed.
+\item $j = 3$: $\Prop(3) = \{p\}$, so we have $I_1 = \{1,2,3\}$ and we remove propagator $p$. The only remaining propagator in the diagram is $s$.
 \item $j = 4$: Since $p$ and $q$ were removed in earlier steps, we now have $\Prop(4) = \emptyset$.
-\item $j = 5$: $\Prop(5) = \{s\}$, and we have $I_1 = \{1,2,3,5\}$ with $I_1(s) = 5$.
+\item $j = 5$: $\Prop(5) = \{s\}$, and we have $I_1 = \{1,2,3,5\}$.
 \end{itemize}
@@
 \begin{rmk} \label{clockwise ordering rem}
-When $p$ contributes $I_i(p) = a$, it must be the clockwise-most propagator supported on $a$ that has not yet contributed to $I_i$.
-i.e.
-any propagator supported on $a$ that appears later in the ordering given by $I_i$ must be inside $(p, <_{a})$.
+Suppose that we have $I_i(p) = a$ for some propagator $p$ and vertex $a$.
+Then $p$ must be the clockwise-most propagator supported on $a$ that has not yet contributed to $I_i$ when the algorithm reaches vertex $a$.
+In particular, any propagator supported on $a$ that appears later in the ordering given by $I_i$ must be inside $(p, <_{a-1})$.
 \end{rmk}
@@
 Consider the diagram $W'$ formed by removing from $W$ all propagators that have already contributed to $I_i^W$.
-(This just replicates the behavior of the algorithm, which removes each propagator once it contibutes to $I_i^W$.)  Now suppose for some other diagram $V$ on the same vertex set we are constructing $I_m^V$ for some $m$, and we are at step $j$ of the loop, for the same $j$ as above.
+(This just replicates the behavior of the algorithm, which removes each propagator once it contributes to $I_i^W$.)  Now suppose for some other diagram $V$ on the same vertex set we are constructing $I_m^V$ for some $m$, and we are at step $j$ of the loop, for the same $j$ as above.
 Again obtain $V'$ from $V$ by removing all propagators assigned so far.
@@
 With that in mind, we are ready to begin proving properties of the algorithm.
-We first show that the algorithm for $I_i$ can never reach the final vertex (in the $<_i$ order) in a propagator's support without having already assigned that propagator; in particular, this guarantees that the construction of $I_i$ always terminates in fewer than $n$ steps.
+We first show that the algorithm for $I_i$ can never reach the final vertex in a propagator's support (in the $<_i$ order) without having already assigned that propagator; in particular, this guarantees that the construction of $I_i$ always terminates in fewer than $n$ steps.
 
@@
 Consider $I_{j+2}(p)$.
-Since $j+1$ is the last vertex in the $j+2$ order, $p$ can not contribute $j+1$ to $I_{j+2}$, so the fact that the invervals in the statement of the lemma are non-empty and occur in their cyclic order implies that $I_{j+2}(p)=i$.
-More generally, whenever we know that a propagator stops contributing a particular vertex, then we know that it must contribute its cyclically next vertex.
+Since $j+1$ is the last vertex in the $j+2$ order, $p$ can not contribute $j+1$ to $I_{j+2}$, so the fact that the intervals in the statement of the lemma are non-empty and occur in their cyclic order implies that $I_{j+2}(p)=i$.
+More generally, we know that whenever a propagator stops contributing a particular vertex, its next contribution must be its cyclically next vertex.
 This little observation is surprisingly useful, to the point that the details which appear in the proof of Lemma~\ref{vertex cyclic int lem} are never needed again: the mere fact of non-empty intervals in the correct order suffices.
@@
 
-It follows that $I_i^W$ and $I_b^{W'}$ are locally the same from vertex $b$ onwards, since by the above observations the propagators removed from $W$ to create $W'$ are exactly those that come first in the ordering defined by $I_i^W$.
+Observe that $I_i^W$ and $I_b^{W'}$ are locally the same from vertex $b$ onwards, since by the above observations the propagators removed from $W$ to create $W'$ are exactly those that come first in the ordering defined by $I_i^W$.
 Similarly, $I_{i+1}^W$ and $I_{b+1}^{W'}$ are locally the same from $b+1$ onwards.
@@
 since in both cases the algorithm in $W'$ proceeds identically to that in $W$ after assigning $p$.
-Since $m \neq i+1$, we have $m\in I_{i+1}^{W'}\setminus\{i+1\}$ but $m\not\in I_{i+2}^{W'}$, contradicting the minimiality of $W$.
+Since $m \neq i+1$, we have $m\in I_{i+1}^{W'}\setminus\{i+1\}$ but $m\not\in I_{i+2}^{W'}$, contradicting the minimality of $W$.
 This completes the proof.
@@
 The base case $Q_0 \subseteq \cP_{m-1}$ is immediate: since $j_m \not\in I_i$ by construction, there cannot be any unassigned propagators supported on $j_m$ when the algorithm reaches that vertex, i.e.
-$\Prop(j_m) \subseteq \cP_{m-1}$.
+${\Prop(j_m) \subseteq \cP_{m-1}}$.
 
@@
 If $q$ is clockwise of $p_r$ on vertex $a_r$ then we immediately have $q \in \cP_{m-1}$ by Remark~\ref{clockwise ordering rem}.
-It remains to consider the case that $q$ is counter-clockwise of $p_r$ at $a_r$.
+It remains to consider the case that $q$ is counterclockwise of $p_r$ at $a_r$.
 
@@
 \clipcenterarc(0,0)(\startpoint:\endpoint:\radius)
-\newpropbend{3}{8.5}{50}
+\newpropbend{3}{8.5}{40}
 \newpropbend{3.3}{7}{40}
 \end{scope}
-\node at (\zero+5*\step:\radius*0.46) {\scriptsize $p_r$};
+\node at (\zero+5*\step:\radius*0.50) {\scriptsize $p_r$};
 \node at (\zero + 6*\step:\radius*0.75) {\scriptsize $q$};
@@
 
-We have now shown that Algorithm~\ref{alg:put GN on WLD} associates the correct Grassmann necklace to a Wilson loop diagam.
+We have now shown that Algorithm~\ref{alg:put GN on WLD} associates the correct Grassmann necklace to a Wilson loop diagram.
 Therefore, we refer to Algorithm~\ref{alg:put GN on WLD} as the Grassmann necklace algorithm.
@@
 
-\section{Dimension of the Wilson Loop cells}\label{sec dim}
-
-In continuing to characterise the poistroid cells associated to Wilson loop diagrams, our next goal is to show that the dimension of the positroid cell defined by a Wilson loop diagram $(\cP, [n])$ has dimension $3|\cP|$ (Theorem \ref{thm dim}).
-The positroid cells associated to the Amplituhedron are of dimension $4|\cP|$.
-In \cite{non-orientable}, Agarwala and Marcott show that the dimension of the Deodhar component is the sum of $|\cP|$ and the dimension of the associated positroid cell.
+\section{Dimension of the Wilson loop cells}\label{sec dim}
+
+In continuing to characterize the positroid cells associated to Wilson loop diagrams, our next goal is to show that the dimension of the positroid cell defined by a Wilson loop diagram $(\cP, [n])$ has dimension $3|\cP|$; this is achieved in Theorem \ref{thm dim}.
+
+Note that the positroid cells associated to the Amplituhedron are of dimension $4|\cP|$.
+In \cite{non-orientable}, Agarwala and Marcott associate a Deodhar component\footnote{Since Deodhar components play no role in this paper, the interested reader is referred to \cite{non-orientable} for more details on this.} to each Wilson loop diagram, and show that the dimension of this Deodhar component is the sum of $|\cP|$ and the dimension of the associated positroid cell.
 %\[|\cP| + \text{ the dimension of associated positroid cell}.\]
-In other words, the Deodhar component associated to a Wilson loop diagram is $4|\cP|$, showing that the geometry underlying the Wilson loop diagrams is consistent with the geometry underlying the Amplituhedron.
+Combining this with Theorem~\ref{thm dim}, we see that the Deodhar component associated to a Wilson loop diagram is $4|\cP|$-dimensional, showing that the geometry underlying the Wilson loop diagrams is consistent with the geometry underlying the Amplituhedron.
 
 Marcott in \cite{WLDdim} gives a different proof of the $3|\cP|$-dimensionality of $M(W)$ which is geometric and more elegant, but it is not easy to track the effect of a particular propagator.
+
 Our approach is much more explicit.
-
-Recall that the dimension of a positroid cell is equal to the number of plusses in the associated Le diagram \cite[Theorem 6.5]{Postnikov}.
-By combining Algorithms~\ref{alg:put GN on WLD} and \ref{alg:GN to Le} (converting from WLD to Grassmann necklace, and Grassmann necklace to Le diagram respectively) we explicitly describe the effect of adding another propagator to a Wilson loop diagram in terms of the plusses of the associated Le diagrams, and hence give a recursive proof of the $3|\cP|$-dimensionality of the cells.
-
-More than just a dimensionality result, the lemmas below are a first step towards undertanding how the adding an extra propagator changes the associated positroid cell.
-
-We start with several lemmas, of roughly increasing degree of technicality.
-We begin by relating non-supporting vertices to columns of zeros in the Le diagram (Lemma \ref{lem uncovered}) and verifying that performing dihedral transformations on a Wilson loop diagram does not change the dimension of of the associated Le diagram (Lemma \ref{lem dihedral}).
+By combining Algorithms~\ref{alg:put GN on WLD} and \ref{alg:GN to Le} (converting from Wilson loop diagram to Grassmann necklace, and Grassmann necklace to Le diagram respectively) we explicitly describe the effect of adding another propagator to a Wilson loop diagram in terms of the plusses of the associated Le diagrams.
+Recall that the dimension of a positroid cell is equal to the number of plusses in its associated Le diagram \cite[Theorem 6.5]{Postnikov}; thus understanding the effect of adding another propagator is sufficient to give a recursive proof of the $3|\cP|$-dimensionality of the cells.
+
+%More than just a dimensionality result, these lemmas are a first step towards understanding how the adding an extra propagator changes the associated positroid cell.
+
+In order to prove our main theorem of this section, we first require several lemmas.
+We begin by relating non-supporting vertices to columns of zeros in the Le diagram (Lemma \ref{lem uncovered}) and verifying that performing dihedral transformations on a Wilson loop diagram does not change the dimension of the associated Le diagram (Lemma \ref{lem dihedral}).
+This allows us to restrict our attention to a particular subset of admissible Wilson loop diagrams (Lemma~\ref{lem good p}) whose Grassmann necklaces can be more easily described.
 
@@
 
-By Corrollary~\ref{no coloops} we know that $i \not\in I_1^W$, and so $i$ must label a horizontal edge on the boundary of the Le diagram of $W$, i.e.
+By Corollary~\ref{no coloops} we know that $i \not\in I_1^W$, and so $i$ must label a horizontal edge on the boundary of the Le diagram of $W$, i.e.
 it must be a column label.
@@
 Next consider $I_n^{W}$.
-From the figure we see that in both cases we have $I_n^{W}(p) = n$.
-At vertex 1 of the algorithm $I_n$, the unassigned propagators are exactly those that appear in $V$.
+From the figure we see that in both cases we have $I_n^{W}(p) = n$; thus from vertex 1 onwards the unassigned propagators are exactly those that appear in $V$.
 Therefore the algorithm continues as in $I_1^{V}$, i.e.
@@
 Now consider $I_{n-2}^{W}$.
-If $n-2\not\in I_{n-2}^{V}$ then the vertex $n-2$ is non-supporting (see also Corrollary~\ref{no coloops}.)  Thus we are in Case 1, with ${I_{n-2}^W(p) = n-2}$ and this assignment of $p$ does not affect the rest of the construction of $I_{n-2}^{V}$, so we obtain ${I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-2\}}$ as above.
-
-On the other hand, if $n-2\in I_{n-2}^{V}$ then we must be in Case 2 of Figure~\ref{fig special p} and $I_{n-2}^V(q) = I_{n-2}^W(q) = n-2$ (since $q$ is always the clockwise-most propagator supported on vertex $n-2$.
+If $n-2\not\in I_{n-2}^{V}$ then the vertex $n-2$ is non-supporting (see also Corollary~\ref{no coloops}.)  Thus we are in Case 1, with ${I_{n-2}^W(p) = n-2}$ and this assignment of $p$ does not affect the rest of the construction of $I_{n-2}^{V}$, so we obtain ${I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-2\}}$ as above.
+
+On the other hand, if $n-2\in I_{n-2}^{V}$ then we must be in Case 2 of Figure~\ref{fig special p} and ${I_{n-2}^V(q) = I_{n-2}^W(q) = n-2}$ (since $q$ is always the clockwise-most propagator supported on vertex $n-2$.
 If $n-1 \not\in I_{n-2}^{V}$, then $I_{n-2}^W(p) = n-1$ and then the algorithm proceeds identically to $I_{n-2}^{V}$ for the remainder of its steps; thus $I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-1\}$ in this case.
@@
 
-The arguments for $I_k^{W}$ ($1< k < n-2$) proceed analagously to those of $I_{n-2}^{W}$, with one simplification: we cannot have both $n-3$ and $n-2$ in $I_k^{V}$ since $q$ is the only propagator that could be assigned to either of them, and it cannot be assigned to both.
+The arguments for $I_k^{W}$ ($1< k < n-2$) proceed analogously to those of $I_{n-2}^{W}$, with one simplification: we cannot have both $n-3$ and $n-2$ in $I_k^{V}$ since $q$ is the only propagator that could be assigned to either of them, and it cannot be assigned to both.
 
@@
 The next several lemmas assume $V$ and $W$ to be as above.
-They discuss how the shape of the Le diagram changes from $V$ to $W$ and how the plusses in $V$ shift to become plusses in $W$.
+These lemmas discuss how the shape of the Le diagram changes from $V$ to $W$ and how the plusses in $V$ shift to become plusses in $W$.
 In particular, the Le diagram for $W$ has an extra row, labeled by $n-3$, with three columns (see Figure~\ref{fig Le} and Lemma~\ref{lem shape}).
@@
 Explicitly, $\mathcal{B}$ is the set of columns with labels $v < n-3$ and $\mathcal{A}$ is the set of columns labeled by $n$, $n-1$ and $n-2$ in $V$.
-In $W$ we see that $\mathcal{A}$ consists of these columns without the last row.
+In $W$ we see that $\mathcal{A}$ consists of these same three columns, but does not include the last row.
 Over the course of the next few lemmas we will prove that the plusses in the $\mathcal{B}$ parts of each diagram are identical, and that the relationship between the plusses in the two $\mathcal{A}$ regions can be described explicitly.
@@
 
-Finally, we also note that when we speak of a plus in the Le diagram of $V$ being the same as in $W$ or vice versa, we mean that the position of the plus in $\mathcal{A}$ or $\mathcal{B}$ is the same.
+%Finally, we also note that when we speak of a plus in the Le diagram of $V$ being the same as in $W$ or vice versa, we mean that the position of the plus in $\mathcal{A}$ or $\mathcal{B}$ is the same
 
@@
 %  Specifically,
-  $I_n^W$ yields an $(n-3)\rightarrow n$ plus and $I_{n-1}^W$ yields an $(n-3)\rightarrow (n-1)$ plus along with any plusses yielded by $I_n^V$.
+  $I_n^W$ yields an $(n-3)\rightarrow n$ plus, and $I_{n-1}^W$ yields an $(n-3)\rightarrow (n-1)$ plus along with any plusses yielded by $I_n^V$.
 \end{lem}
@@
 \]
-Also $(I_n^V \setminus I_1^V) \cup \{n-1\}\subseteq \{n-1,n\}$ from the definition of Grassmann necklace and so in particular, $n-1$ is minimal in this set, so Algorithm~\ref{alg:GN to Le} yields a plus in the $(n-3) \rightarrow (n-1)$ position (i.e.
+Also $(I_n^V \setminus I_1^V) \cup \{n-1\}\subseteq \{n-1,n\}$ from the definition of Grassmann necklace, and so in particular $n-1$ is minimal in this set.
+Thus Algorithm~\ref{alg:GN to Le} yields a plus in the $(n-3) \rightarrow (n-1)$ position (i.e.
 the second box in the bottom row of the Le diagram of $W$) along with any plusses yielded by $I_n^V$.
@@
 
-In the next two lemmas, we consider the plusses contributed to the Le diagram of $W$ by $I_{n-2}^W$.
-Lemma~\ref{lem I} lists three possibilities for $I_{n-2}^W$, but the following observation shows that we need only consider two of them.
+We next consider the plusses contributed to the Le diagram of $W$ by $I_{n-2}^W$.
+Lemma~\ref{lem I} lists three possibilities for $I_{n-2}^W$, but the following observation shows that we need only consider two of these cases.
 
@@
 The new diagram is an example of Case 1, i.e.
-satisfying $n-2 \not \in I_{n-2}^V$.
-Therefore we do not need to consider the case where $n-2\in I_{n-2}^V$ but $n-1\not\in I_{n-2}^V$.
+it satisfies $n-2 \not \in I_{n-2}^V$.
+Therefore we do not need to separately consider the case where $n-2\in I_{n-2}^V$ but $n-1\not\in I_{n-2}^V$, as it will be subsumed into Case 1 in the main theorem.
 \end{rmk}
+
+We can now describe the plusses contributed by $I_{n-2}^W$ in the remaining two cases: when $n-2 \not\in I_{n-2}^V$, and when $n-2,n-1 \in I_{n-2}^V$.
 
@@
   Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that $n-2 \not\in I_{n-2}^{V}$.
-Then $I_{n-2}^{W}$ contributes all of the same plusses as $I_{n-1}^{V}$ (which is the same as $I_{n-2}^{V}$) along with a new $(n-3)\rightarrow (n-2)$ plus.
+Then $I_{n-2}^{W}$ contributes all of the same plusses as $I_{n-1}^{V}$ (which is the same as $I_{n-2}^{V}$) along with a new ${(n-3)\rightarrow (n-2)}$ plus.
 \end{lem}
@@
 
-Next we need an observation about how the Grassman necklace for $V$ changes over the indices near $n$ under the hypotheses that $n-2, n-1\in I_{n-2}^V$.
+Next we need an observation about how the Grassmann necklace for $V$ changes over the indices near $n$ under the hypotheses that $n-2, n-1\in I_{n-2}^V$.
 
@@
 
-Note that neither $u$ nor $v$ can be $n-1$, $n-2$, or $n-3$, because, as noted in Lemma~\ref{lem I}, these elements do not belong to $I_1^V$ and $I_n^V = (I_1^V\setminus \{v\}) \cup \{n\}$.
+Note that neither $u$ nor $v$ can be $n-1$, $n-2$, or $n-3$, because as noted in Lemma~\ref{lem I}, these elements do not belong to $I_1^V$ and $I_n^V = (I_1^V\setminus \{v\}) \cup \{n\}$.
 However, $u$ could be $n$.
@@
 Thus $n-4 \not\in I_{n-1}^W$.
-Since $I_{n-1}^W = I_n^V\cup\{n-1\}$ by Lemma~\ref{lem I}, we cannot have $n-4$ in $I_n^V$ either.
+Since ${I_{n-1}^W = I_n^V\cup\{n-1\}}$ by Lemma~\ref{lem I}, we cannot have $n-4$ in $I_n^V$ either.
 
@@
 \item As in Lemma~\ref{lem I} we have $n,n-1,n-2,n-3 \not\in I_1^V$, which implies the first part of the claim.
-The second part is a consequence of the discussion following \eqref{eq necklace}, which shows that $n-4 \not\in I_n^V$.
+The second part is a consequence of the discussion following equation \eqref{eq necklace}, which shows that $n-4 \not\in I_n^V$.
 
@@
 \end{gather*}
-As per the discussion following equation \eqref{eq necklace} above, we also have $I_n^V\setminus I_1^V = \{n\}$ and $I_1^V\setminus I_n^V = \{v\}$.
+As per the discussion following equation \eqref{eq necklace} above, we also have $I_n^V\setminus I_1^V = \{n\}$ and ${I_1^V\setminus I_n^V = \{v\}}$.
 If $c = n-5$ then the path $v \rightarrow n$ from $I_n^V$ does not intersect with the paths from $\{n-3, n-5\}$ to $\{n-2, n-1\}$ and we obtain the plusses as stated.
@@
 \item Combining equation \eqref{eq necklace} with point 3 of this proof, the pair $(I_{n-1}^V \setminus I_1^V, I_1^V \setminus I_{n-1}^V)$ is either $(\{n-1, n\}, \{u, v\})$ or $(\{n-1\}, \{v\})$.
-Per point 1, $c = n-4$ if and only if $v = n -4$, in which case we get a $(n-4) \rightarrow (n-1)$ plus and the $u \rightarrow n$ plus (if it exists) has already been contributed by $I_{n-2}^V$ and $I_{n-3}^V$.
+Per point 1, we have $c = n-4$ if and only if $v = n -4$, in which case we get a $(n-4) \rightarrow (n-1)$ plus and the $u \rightarrow n$ plus (if it exists) has already been contributed by $I_{n-2}^V$ and $I_{n-3}^V$.
 If $c = n-5$ then $v < n-5$ and we are in the same situation as $I_{n-2}^V$.
@@
 Further, since $c$ will always be maximal in $I_1^V\setminus I_i^V$ by point 1, a path from $c$ must end at the minimal element of $I_i^V \setminus I_1^V$.
-From \eqref{eq necklace}, the only way we can have $c \not\in I_i^V$ and $n-1$ minimal in $I_i^V \setminus I_1^V$ is if $c = n-4$ and $i = n-1$.
+From equation \eqref{eq necklace}, the only way we can have $c \not\in I_i^V$ and $n-1$ minimal in $I_i^V \setminus I_1^V$ is if $c = n-4$ and $i = n-1$.
 
@@
 All other paths are unchanged.
-
 %   Thus the plus contributed by $I_k^V$ in the $n-3$ column of the Le diagram of $V$ is shifted into the $n-2$ column in the Le diagram for $W$, where there was no plus before, and no other plusses are changed.
@@
 
-\section{Poles of Wilson Loop Integrals}\label{sec poles}
+\section{Poles of Wilson loop Integrals}\label{sec poles}
 
@@
 \bas \sum_{W \text{ s.t. } |\cP| = k} I(W)(\cZ) <\infty \;.\eas
-In other words, all poles of the intergrands must cancel.
+In other words, all poles of the integrands must cancel.
 As a step towards this, in this section we prove some results about the structure of the denominator $R(W)$ of the integrand, as defined in Definition~\ref{def R(W)}.
@@
 \]
-which is squarefree and contains all factors of $\prod_{i=1}^{n}\Delta_{I_i}$.
+which is square-free and contains all factors of $\prod_{i=1}^{n}\Delta_{I_i}$.
 If one were to construct the denominator $R(W)$ associated to this Wilson loop diagram as per Definition~\ref{def R(W)}, we would find that we have $R(W) = R$.
@@
 If no other propagators are supported on the vertex $i$ then the corresponding column of $C(W)$ has only one nonzero entry in it, and so $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$; as above, this is a contradiction.
-Since $p$ is the first propagator in the ordering imposed by $I_i$, it is the clockwise most propagator supported on $i$ (by Remark {\ref{clockwise ordering rem}}).
-Since there are multiple propagators supported on $i$, there must be a $q$ ending on edge $i$, such that $I_i(q) = i+1$, that is second clockwisemost propagators supported by $i$ (see Figure~\ref{fig no big factors}).
+Since $p$ is the first propagator in the ordering imposed by $I_i$, it is the clockwise-most propagator supported on $i$ (by Remark {\ref{clockwise ordering rem}}).
+Since there are multiple propagators supported on $i$, there must be a $q$ ending on edge $i$, such that $I_i(q) = i+1$, that is second clockwise-most propagators supported by $i$ (see Figure~\ref{fig no big factors}).
 Write $q = (i, j)$ for the support of $q$.
@@
 
-As in the proof of part (2), make a new admissible diagram by removing the propagators which come before those contibuting to $f$ in the order imposed by $I_i$.
+As in the proof of part (2), make a new admissible diagram by removing the propagators which come before those contributing to $f$ in the order imposed by $I_i$.
 Then without loss of generality we may assume $i=a$.
@@
 
-Next we need to show that $R$ is squarefree.
+Next we need to show that $R$ is square-free.
 Suppose $f^2|R$.
@@
 Thus $f^2|R$ implies that twice in the Grassmann necklace $p$ must change from not being associated to vertex $a$ to being associated to vertex $a$.
-This is again a contradiction, and so $R$ is squarefree.
-
-Taking everything together we have that $R|\prod_{i=1}^n \Delta_{I_i}$, $R$ contains all factors of $\prod_{i=1}^n \Delta_{I_i}$ and $R$ is squarefree.
+This is again a contradiction, and so $R$ is square-free.
+
+Taking everything together we have that $R|\prod_{i=1}^n \Delta_{I_i}$, $R$ contains all factors of $\prod_{i=1}^n \Delta_{I_i}$ and $R$ is square-free.
 Therefore the ideal generated by $R$ is the radical of the ideal generated by $\prod_{i=1}^n \Delta_{I_i}$.
@@
 \begin{thm}\label{thm denom}
-  Given any admissible Wilson loop diagram $W$, let $(I_1, \ldots I_n)$ be the associated Grasmann necklace.
+  Given any admissible Wilson loop diagram $W$, let $(I_1, \ldots I_n)$ be the associated Grassmann necklace.
 Then $R(W)$ as defined in Definition~\ref{def R(W)} is equal to the $R$ constructed by Algorithm~\ref{alg WLD to denom via GN}.
@@
 Hence every factor of $R$ divides $R(W)$.
-Finally, since $R$ is squarefree, this implies that $R(W)$ is a scalar multiple of $R$.
+Finally, since $R$ is square-free, this implies that $R(W)$ is a scalar multiple of $R$.
 
@@
 
-While the authors cannot yet offer a proof that the appropriate sum of the Wilson loop diagrams are, in fact, finite, as expected from \cite{Alday:2007hr, ParkeTaylorids}, we do hope that this relationship to the Grassmann Necklace elements will provide a different avenue for answering that and related questions.
+While the authors cannot yet offer a proof that the appropriate sum of the Wilson loop diagrams are, in fact, finite, as expected from \cite{Alday:2007hr, ParkeTaylorids}, we do hope that this relationship to the Grassmann necklace elements will provide a different avenue for answering that and related questions.
 \note{Can we rephrase this paragraph to be a bit more positive?}

### 2019-10-10 GWLDCII.tex
changes from on the phone today

@@
 The matrix $C(W)$ defines a positroid cell associated to $W$ in the positive Grassmannian $\Gr(n, |\cP|)$, which we denote by $\Sigma(W)$ \cite{wilsonloop}.
-Marcott \cite{WLDdim} shows that  the matrix $C(W)$ parametrizes a space whose \hlfix{close}{closure?} is exactly the closure of $\Sigma(W)$.
+Marcott \cite{WLDdim} shows that  the matrix $C(W)$ parametrizes a space whose closure is exactly the closure of $\Sigma(W)$.
 That is, the space defined by $C(W)$ and the cell $\Sigma(W)$ agree up to a set of measure $0$.
@@
 
-Let $S = \cP_{in}(p)$ be the set of propagators inside $p$ in the $<_i$ order.
-By Remark \ref{rmk algorithm locally same}, $I_i$ and $I_{i+1}$ can only differ once $p$ contributes to $I_{i+1}$, so $I_i(q) = I_{i+1}(q)$ for each $q \in S \backslash \{p\}$.
+Let $T = \cP_{in}(p)$ be the set of propagators inside $p$ in the $<_i$ order.
+By Remark \ref{rmk algorithm locally same}, $I_i$ and $I_{i+1}$ can only differ once $p$ contributes to $I_{i+1}$, so $I_i(q) = I_{i+1}(q)$ for each $q \in T \backslash \{p\}$.
 Thus every propagator inside $p$ contributes before $m$ and if a propagator contributes $m$ in $I_i$ then it must lie outside $p$.
@@
 So we must have at least one of $m$ and $m+1$ in $I_i$.
-However, all propagators in $S$ contribute to $I_{i}$ strictly before $m$ by the previous paragraph so, after permuting rows and columns as needed, the matrix giving $\Delta_{I_i}$ has the form
+However, all propagators in $T$ contribute to $I_{i}$ strictly before $m$ by the previous paragraph so, after permuting rows and columns as needed, the matrix giving $\Delta_{I_i}$ has the form
 \[
@@
 \]
-where $A$ is the $|S|\times |S|$ matrix indexed by the propagators in $S$ and the vertices in $I_i(S)$.
+where $A$ is the $|T|\times |T|$ matrix indexed by the propagators in $T$ and the vertices in $I_i(T)$.
 No other propagators can be supported on these vertices since all other propagators are outside of $p$, and $p$ is the first propagator supported at $i$; this explains the zero block.
@@
 
-Similarly to Case 1, let $S = \cP_{in}(q) \cup \{p\}$ in the $<_i$ order.
-Then all propagators in $S$ contribute to $I_i$ strictly before $j$ and no other propagators are supported on vertices strictly before $j$.
+Similarly to Case 1, let $T = \cP_{in}(q) \cup \{p\}$ in the $<_i$ order.
+Then all propagators in $T$ contribute to $I_i$ strictly before $j$ and no other propagators are supported on vertices strictly before $j$.
 Thus after permuting rows and columns as needed the matrix giving $\Delta_{I_i}$ has the form
@@
 \]
-where $A$ is the submatrix indexed by the propagators in $S$ and the vertices in $I_i(S)$.
+where $A$ is the submatrix indexed by the propagators in $T$ and the vertices in $I_i(T)$.
 Again two things can now happen.
 If some vertex $j$ or larger (with respect to $<_i$) belongs to $I_i$ then $B$ and $C$ are at least one column wide, and so the block form of the matrix gives a nontrivial factorization of $\Delta_{I_i}=\pm\det A\det C$.
-This yields a contradiction as in Case 1: $f|\det A$ and removing a propagator not in $S$ gives a smaller diagram with a factor of degree $\geq 3$, which contradicts our minimality assumption.
+This yields a contradiction as in Case 1: $f|\det A$ and removing a propagator not in $T$ gives a smaller diagram with a factor of degree $\geq 3$, which contradicts our minimality assumption.
 
@@
 
-\item If \hlfix{$S_i = \emptyset$}{Should we recall the definition of $S_i$ here?
-Not used since 5.1} then $r_i = 1$ and we immediately have $r_i | \Delta_{I_i}$; otherwise, let $p\in S_i$.
+\item If $S_i = \emptyset$ then $r_i = 1$ and we immediately have $r_i | \Delta_{I_i}$; otherwise, let $p\in S_i$.
 Note that $\Delta_{I_i}$ is homogeneous linear in the variables of the row corresponding to $p$.
@@
 Then $x$ is a factor of $\Delta_{I_i}$.
-{\color{violet} Therefore, $x$ must correspond to entry in the row of $p$ and column of $I_i(p)$, i.e.
-$x = x_{p, I_i(p)}$.} \st{and so in particular the monomial in $\Delta_{I_i}$ corresponding to the bijection between propagators and vertices of $I_i$ associates the column of $x$ to $p$.
-Thus $x$ also appears in $r_i$ and s} Since the matrix for $r_i$ is a minor of the matrix for $\Delta_{I_i}$ \st{and every term in $\Delta_{I_i}$ involves $x$,} we also have that \st{every term in $r_i$ involves $x$ so}{\color{violet}$x$ is a factor of $r_i$.} \st{$x$ is a factor of both $r_i$ and $\Delta_{I_i}$ and is the only variable from this row in either polynomial.}
+Therefore, $x$ must correspond to entry in the row of $p$ and column of $I_i(p)$, i.e.
+$x = x_{p, I_i(p)}$.
+Thus $x$ also appears in $r_i$.
+Since the matrix for $r_i$ is a minor of the matrix for $\Delta_{I_i}$ and every term in $\Delta_{I_i}$ involves $x$, we also have that every term in $r_i$ involves $x$ so $x$ is a factor of both $r_i$ and $\Delta_{I_i}$ and is the only variable from this row in either polynomial.
 
   Now suppose two variables from the row $p$ appear in a quadratic factor $f$ of $\Delta_{I_i}$.
-By part (3), there is another propagator $q$ and an edge $a$ such that $f$ is the $2\times 2$ minor coming from $p, q$ and $a, a+1$, with \st{$I_i(p)=a$, $I_i(q)=b$}.
-{\color{violet}There are two situations which can occur, either $I_i(p)=a$ and $I_i(q)=a+1$, or $I_i(q)=a$ and $I_i(p)=a+1$.
-These are} illustrated in Figure~\ref{fig quadratic}; we show that in both cases it follows that $q \in S_i$ as well.
-
-\begin{figure}
-\[
-\begin{tikzpicture}[baseline=(current bounding box.east)]
-	\begin{scope}
-	\drawWLDfragment[2]{4}{0.1} 
-	%\drawnumberspartial % use this to debug
-	\newnode[below]{1}{a}
-	\newnode[below]{2}{a+1}
-	\begin{scope}
-	\clipcenterarc(0,0)(\zero - 1.5*\step:\zero + 4.5*\step:\radius)
-	\newprop[midway,left]{1.33}{-7}{\footnotesize $p$}
-	\newprop[midway,right]{1.66}{10}{\footnotesize $q$}
-	\end{scope}
-	\node at (\zero + 0.6*\step:\radius*0.7) {\footnotesize $p$};
-	\node at (\zero + 2.4*\step:\radius*0.7) {\footnotesize $q$};
-\end{scope}
-\end{tikzpicture}
-\begin{tikzpicture}[baseline=(current bounding box.east)]
-	\begin{scope}
-	\drawWLDfragment[2]{4}{0.1} 
-	%\drawnumberspartial % use this to debug
-	\newnode[below]{1}{a}
-	\newnode[below]{2}{a+1}
-	\begin{scope}
-	\clipcenterarc(0,0)(\zero - 1.5*\step:\zero + 4.5*\step:\radius)
-	\newprop[midway,left]{1.33}{-7}{\footnotesize $q$}
-	\newprop[midway,right]{1.66}{10}{\footnotesize $p$}
-	\end{scope}
-	\node at (\zero + 0.6*\step:\radius*0.7) {\footnotesize $q$};
-	\node at (\zero + 2.4*\step:\radius*0.7) {\footnotesize $p$};
-\end{scope}
-\end{tikzpicture}
-\]
-  \caption{The situations giving a quadratic factor with variables appearing in $r_i$. }\label{fig quadratic}
-\end{figure}\note{I'm not sure we really need this figure? (Figure~\ref{fig quadratic})}
+By part (3), there is another propagator $q$ and an edge $a$ such that $f$ is the $2\times 2$ minor coming from $p, q$ and $a, a+1$.
+There are two situations which can occur, either $I_i(p)=a$ and $I_i(q)=a+1$, or $I_i(q)=a$ and $I_i(p)=a+1$.
+    We show that in both cases it follows that $q \in S_i$ as well.
+
+%\begin{figure}
+%\[
+%\begin{tikzpicture}[baseline=(current bounding box.east)]
+%	\begin{scope}
+%	\drawWLDfragment[2]{4}{0.1} 
+%	%\drawnumberspartial % use this to debug
+%	\newnode[below]{1}{a}
+%	\newnode[below]{2}{a+1}
+%	\begin{scope}
+%	\clipcenterarc(0,0)(\zero - 1.5*\step:\zero + 4.5*\step:\radius)
+%	\newprop[midway,left]{1.33}{-7}{\footnotesize $p$}
+%	\newprop[midway,right]{1.66}{10}{\footnotesize $q$}
+%	\end{scope}
+%	\node at (\zero + 0.6*\step:\radius*0.7) {\footnotesize $p$};
+%	\node at (\zero + 2.4*\step:\radius*0.7) {\footnotesize $q$};
+%\end{scope}
+%\end{tikzpicture}
+%\begin{tikzpicture}[baseline=(current bounding box.east)]
+%	\begin{scope}
+%	\drawWLDfragment[2]{4}{0.1} 
+%	%\drawnumberspartial % use this to debug
+%	\newnode[below]{1}{a}
+%	\newnode[below]{2}{a+1}
+%	\begin{scope}
+%	\clipcenterarc(0,0)(\zero - 1.5*\step:\zero + 4.5*\step:\radius)
+%	\newprop[midway,left]{1.33}{-7}{\footnotesize $q$}
+%	\newprop[midway,right]{1.66}{10}{\footnotesize $p$}
+%	\end{scope}
+%	\node at (\zero + 0.6*\step:\radius*0.7) {\footnotesize $q$};
+%	\node at (\zero + 2.4*\step:\radius*0.7) {\footnotesize $p$};
+%\end{scope}
+%\end{tikzpicture}
+%\]
+%  \caption{The situations giving a quadratic factor with variables appearing in $r_i$. }\label{fig quadratic}
+%\end{figure}\note{I'm not sure we really need this figure? (Figure~\ref{fig quadratic})}
 
 In both cases, since $I_{i-1}(p)\neq I_{i}(p)$ by assumption it follows from Lemma~\ref{vertex cyclic int lem} that $I_{i-1}(p) <_{i-1} I_{i}(p)$ and no other vertex supporting $p$ lies between $I_{i-1}(p)$ and $I_{i}(p)$.
-\st{In the case that $b<_i a$ and $q$ is assigned before $p$ in $I_i$,}{\color{violet} If $q$ lies clockwise of $p$, $I_i(q) = a$ and $q$ contributes before $p$ in $I_i$.} This means that $I_{i-1}(p)=a$ and so $I_{i-1}(q)\neq a$.
+If $I_i(q)=a$ then $q$ lies clockwise of $p$ and $q$ contributes before $p$ in $I_i$.
+This means that $I_{i-1}(p)=a$ and so $I_{i-1}(q)\neq a$.
 Thus $q\in S_i$ and so $f$ is a factor of $r_i$.
 
-Now consider the case where \st{$a<_i b$}{\color{violet}$I_i(q) = a+1$}, and suppose for contradiction that $q \not\in S_i$, i.e.
+Now consider the case where $I_i(q) = a+1$, and suppose for contradiction that $q \not\in S_i$, i.e.
 that $I_{i-1}(q) = a+1$.
@@
 Since $p$ changed its association from $I_{i-1}$ to $I_i$, we have $I_{i-1}(p) = i-1$ by Lemma~\ref{vertex cyclic int lem}.
-From Figure~\ref{fig part 4} {\color{violet} and Remark \ref{rmk algorithm locally same}}, $p$ contributes first to  $I_{i-1}$ and  then proceeds identically to $I_i$ for all vertices inside $p$ in the $<_{i-1}$ ordering, implying that $I_{i-1}(s) = I_i(s)$.
+From Figure~\ref{fig part 4} and Remark \ref{rmk algorithm locally same}, $p$ contributes first to  $I_{i-1}$ and  then proceeds identically to $I_i$ for all vertices inside $p$ in the $<_{i-1}$ ordering, implying that $I_{i-1}(s) = I_i(s)$.
 Since $I_{i-1}(s) = a$ and $I_i(s) \neq a$, this is a contradiction.
@@
 Now assume $W$ has at least one propagator.
-\sanote{we never say this, but diagrams without propagators aren't really a thing....
-at least they aren't tree level scatterings}
 
@@
 If $f$ is a linear factor, say from associating propagator $p$ to vertex $a$, then $I_{i}(p)=a$ and $I_{i-1}(p)\neq a$ so this factor appears in $r_i$.
-If $f$ is a quadratic factor, \st{say from associating} {\color{violet} without loss of generality, associate} propagators $p$ and $q$ to vertices $a$ and $a+1$ respectively, then again we cannot have both $I_{i-1}(p) = a$ and $I_{i-1}(q) = a+1$, else $f$ divides $\Delta_{i-1}$.
+If $f$ is a quadratic factor, say from associating propagators $p$ and $q$ to vertices $a$ and $a+1$ respectively, then again we cannot have both $I_{i-1}(p) = a$ and $I_{i-1}(q) = a+1$, else $f$ divides $\Delta_{i-1}$.
 However, by the proof of part (4), if one of $p,q$ belongs to $S_i$ then the other does as well.
@@
 
-To this end, first note that $R(W)$ and $R$ both have total degree $4|\mathcal{P}|$; the degree of $R(W)$ is immediate from the definition while that of $R$ \hlfix{follows from Lemma {\ref{vertex cyclic int lem}}}{one sentence explanation?}.
+To this end, first note that $R(W)$ and $R$ both have total degree $4|\mathcal{P}|$; the degree of $R(W)$ is immediate from the definition while that of $R$ follows from Remark \ref{rmk cyclic}.
 By Proposition~\ref{prop alg gives rad} every factor of $R$ is either a quadratic factor coming from two propagators supported on a common edge or a single variable coming from a support vertex of a propagator not appearing in a quadratic factor.
@@
 Thus we have shown a deep relationship between the physically derived poles of the integrals $I(W)$ and the geometry and combinatorics associated to the diagrams $W$.
-At the very least, this is yet another piece of \hlfix{circumstantial}{can we find a better word for this?} evidence indicating that the positroid representation of Wilson loop diagrams is the correct geometric object to be considering when considering the Wilson loop amplitudes geometrically.
-
-While the authors cannot yet offer a proof that the appropriate sum of the Wilson loop diagrams are, in fact, finite, as expected from \cite{Alday:2007hr, ParkeTaylorids}, we do hope that this relationship to the Grassmann necklace elements will provide a different avenue for answering that and related questions.
+This is yet another piece of substantial evidence indicating that the positroid representation of Wilson loop diagrams is the correct geometric object to be considering when considering the Wilson loop amplitudes geometrically.
+
+%While the authors cannot yet offer a proof that the appropriate sum of the Wilson loop diagrams are, in fact, finite, as expected from \cite{Alday:2007hr, ParkeTaylorids}, we do hope that this relationship to the Grassmann necklace elements will provide a different avenue for answering that and related questions.
 \note{Can we rephrase this paragraph to be a bit more positive?}

### 2019-10-12 GWLDCII.tex
fixed integrands and empty prop set

@@
   Wilson loop diagrams are an important tool in studying scattering amplitudes of SYM $N=4$ theory and are known by previous work to be associated to positroids.
-In this paper we study the structure of the associated positroids, as well as the structure of the denominator of the integral defined by each diagram.
+In this paper we study the structure of the associated positroids, as well as the structure of the denominator of the integrand defined by each diagram.
 We give an algorithm to derive the Grassmann necklace of the associated positroid directly from the Wilson loop diagram, and a recursive proof that the dimension of these cells is thrice the number of propagators in the diagram.
-We also show that the denominator in the integral is the radical of the product of minors defined by the elements of the Grassmann necklace.
+We also show that the denominator in the integrand is the radical of the product of minors defined by the elements of the Grassmann necklace.
 \end{abstract}
@@
 
-As noted above, the sum of the Feynman integrals associated to Wilson loop diagrams gives the volume of a convex polytope; if this volume is to be finite, then any singularities appearing in individual integrals must cancel out in the overall sum.
-This has been conjectured in general \cite{Hodges2013} and verified explicitly in a few cases \cite{casestudy, HeslopStewart}, but it is hard to prove in general due to the fact that the relationship between Wilson loop diagrams and $3k$-dimensional positroid cells of $\Gr(k,n)$ is neither one-to-one nor onto.
+As noted above, the sum of the Feynman integrals associated to Wilson loop diagrams gives the volume of a convex polytope.
+if the singularities appearing in individual integrals cancel out in the overall sum, then the overall volume is finite.
+This cancellation has been conjectured in general \cite{Hodges2013} and verified explicitly in a few cases \cite{casestudy, HeslopStewart}, but it is hard to prove in general due to the fact that the relationship between Wilson loop diagrams and $3k$-dimensional positroid cells of $\Gr(k,n)$ is neither one-to-one nor onto.
 In this paper, we give a characterization of the factors appearing in the denominator of these Feynman integrals in terms of the Grassmann necklace of the associated positroid, thus providing a much simpler and more tractable link between the singularities and the diagrams.
@@
 
-Finally in Section~\ref{sec poles} we characterize the denominator of the integral of a Wilson loop diagram in terms of how propagators contribute to the Grassmann necklace.
+Finally in Section~\ref{sec poles} we characterize the denominator of the integrand of a Wilson loop diagram in terms of how propagators contribute to the Grassmann necklace.
 This characterization is given explicitly by Algorithm~\ref{alg WLD to denom via GN} and Theorem~\ref{thm denom}.
@@
 However, we emphasize that this is different to the standard convention in the physics literature, where propagators are written $(i,j)$ with $1 \leq i<j \leq n$.
+
+We note that in this paper, we allow for the propagator set $\cP$ to be empty.
+This is for mathematical convenience, even though these diagrams are do not correspond to tree level scattering amplitudes.
 
@@
 
-This implies that any singularities in the integrals $I(W)$ must cancel out in the sum; in particular, all poles arising from $R(W)$ must cancel.
-Specifically, these poles must cancel on the boundaries of the positroid cells $\Sigma(W)$, analogous to the analysis in \cite{Arkani-Hamed:2013jha}.
+This would certainly hold if  the singularities in the integrands $\Omega(W)$ cancel out in the sum; in particular, all poles arising from $R(W)$ must cancel.
+Specifically, it is conjectured that these poles cancel on the boundaries of the positroid cells $\Sigma(W)$, analogous to the analysis in \cite{Arkani-Hamed:2013jha}.
 This has been checked for particular classes of examples (e.g.
@@
 Furthermore, the algorithm allows us to see how the Le diagram associated to a Wilson loop diagram changes as one adds propagators in certain positions (Theorem \ref{thm dim}).
-Indeed, the techniques we develop in this section to verify that our algorithm produces the correct Grassmann necklace will also be used repeatedly in later sections to calculate the dimension of the associated positroid cell (Section \ref{sec dim}) and to study the structure of the poles of the associated integral $I(W)$ (Section \ref{sec poles}).
+Indeed, the techniques we develop in this section to verify that our algorithm produces the correct Grassmann necklace will also be used repeatedly in later sections to calculate the dimension of the associated positroid cell (Section \ref{sec dim}) and to study the structure of the poles of the associated integrand $\Omega(W)$ (Section \ref{sec poles}).
 
@@
 This not only greatly simplifies the previously known process to obtain a positroid cell from a Wilson loop diagram, but will also allow us to relate the behavior of the positroid $M(W)$ directly to the configuration of propagators in $W$.
-In section \ref{sec poles} we see that the denominator, $R(W)$, of the integrand associated to a Wilson loop diagram, $I(W)$, can be written in terms of the Grassmann necklace of a diagram.
+In section \ref{sec poles} we see that the denominator, $R(W)$, of the integrand associated to a Wilson loop diagram, $\Omega(W)$, can be written in terms of the Grassmann necklace of a diagram.
 
@@
 \bas \sum_{W \text{ s.t. } |\cP| = k} I(W)(\cZ) <\infty \;.\eas
-In other words, all poles of the integrands must cancel.
+This holds if all poles of the integrands cancel.
 As a step towards this, in this section we prove some results about the structure of the denominator $R(W)$ of the integrand, as defined in Definition~\ref{def R(W)}.
@@
 The main result of this section is Theorem~\ref{thm denom}, which expresses the denominator $R(W)$ in terms of the Grassmann necklace of $W$.
-This simplifies the computation of $R(W)$ and allows us to directly relate the poles of the integral to the combinatorics of the diagram.
+This simplifies the computation of $R(W)$ and allows us to directly relate the poles of the integrand to the combinatorics of the diagram.
 
@@
 
-Thus we have shown a deep relationship between the physically derived poles of the integrals $I(W)$ and the geometry and combinatorics associated to the diagrams $W$.
+Thus we have shown a deep relationship between the physically derived poles of the integrand $\Omega(W)$ and the geometry and combinatorics associated to the diagrams $W$.
 This is yet another piece of substantial evidence indicating that the positroid representation of Wilson loop diagrams is the correct geometric object to be considering when considering the Wilson loop amplitudes geometrically.

### 2019-10-15 GWLDCII.tex
little things throughout

@@
 In contrast, the first paper in this series focuses on combinatorial and matroidal properties of the Wilson loop diagrams.
-The main focus of that paper is to enumerate the positroid cells that are associated to Wilson loop diagrams with a fixed number of vertices and propagators, as well as counting the number of Wilson loop diagrams that map to the same positroid.
+The main focus of that paper is enumerating the positroid cells that are associated to Wilson loop diagrams with a fixed number of vertices and propagators, as well as counting the number of Wilson loop diagrams that map to the same positroid.
 
@@
 In particular, if $V = [n]$ then $(n,n+3)$ means the propagator connecting edges $3$ and $n$.
-This viewpoint is beneficial for us since many of our proofs rely on restricting our attention to a region of the diagram bounded by a given propagator, or to short propagators such as $(i,i+2)$, and these behave the same regardless of whether we cross the ``first'' vertex or not.
+This viewpoint is beneficial for us since many of our proofs rely on restricting our attention to a region of the diagram bounded by a given propagator, or to short propagators such as $(i,i+2)$, and these behave the same way regardless of whether we cross the ``first'' vertex or not.
 However, we emphasize that this is different to the standard convention in the physics literature, where propagators are written $(i,j)$ with $1 \leq i<j \leq n$.
 
-We note that in this paper, we allow for the propagator set $\cP$ to be empty.
-This is for mathematical convenience, even though these diagrams are do not correspond to tree level scattering amplitudes.
+We note that in this paper, we allow for the propagator set $\cP$ to be empty. This is for mathematical convenience, even though these diagrams do not correspond to tree level scattering amplitudes.
 
@@
 This is represented as an integral $I(W)$, which is the equivalent of a Feynman integral in this setting.
-This integral is comprised of two main components: an interaction matrix $C(W)$, and a volume form $\Omega(W)$.
+This integral is built from two main components: an interaction matrix $C(W)$, and a volume form $\Omega(W)$.
 These are described next.
@@
 In \cite{casestudy}, Agarwala and Fryer apply this process in the smallest non-trivial case: admissible Wilson loop diagrams with two propagators on six vertices.
-Even in this simple case, we see that the mapping from admissible WLD to positroid cells is neither one-to-one nor onto, and the process described above makes it almost impossible to track the relationship between the original Wilson loop diagram and the resulting positroid.
+Even in this simple case, we see that the mapping from admissible Wilson loop diagram to positroid cells is neither one-to-one nor onto, and the process described above makes it almost impossible to track the relationship between the original Wilson loop diagram and the resulting positroid.
 
@@
   \end{scope}
-  \node[align=center] at (\zero + 4*\step:\radius*1.43) {\footnotesize \em $\leq 6$ vertices in the \\ \footnotesize \em highlighted region};
+  \node[align=center] at (\zero + 4*\step:\radius*1.43) {\footnotesize \em $\leq 6$ vertices in the highlighted \\ \footnotesize \em region and no other propagators\\ \footnotesize \em in the highlighted region};
 \end{scope}
@@
 \begin{lem}\label{lem sian}
-  Let $W$ be a weakly admissible WLD with at least 5 vertices and in which each vertex supports at least one propagator.  Then at least one of the following two things occurs:
+  Let $W$ be a weakly admissible Wilson loop diagram with at least 5 vertices and in which each vertex supports at least one propagator.  Then at least one of the following two things occurs:
   \begin{enumerate}
@@
 
-Let $p_{r+1} = (j_{r+1}, j_{r+1}+2)$ be a propagator of length 2 in $W_r$; if it forms part of configuration \ref{item big and 2} or \ref{item pair of 2s}
+Let $p_{r+1} = (j_{r+1}, j_{r+1}+2)$ be a propagator of length 2 in $W_r$.  If it forms part of configuration \ref{item big and 2} or \ref{item pair of 2s}
 %the configuration \eqref{eq:2 prop config}
@@
 \begin{rmk}
-In the case that all vertices of an admissible WLD $W$ support at least two propagators, then Lemma~\ref{lem sian} substantially simplifies.
+In the case that all vertices of an admissible Wilson loop diagram $W$ support at least two propagators, then Lemma~\ref{lem sian} substantially simplifies.
 By Remark~\ref{rem:props of length 2 and 3}, $W$ has no propagators of length $3$.
@@
 \begin{cor}\label{GN alg well defined}
-If $W$ is an admissible Wilson loop diagram with $k$ propagators and $n$ vertices, then Algorithm~\ref{alg:put GN on WLD} assigns exactly $k$ distinct vertices to each $I_i$ in $n$ steps.
+If $W$ is an admissible Wilson loop diagram with $k$ propagators and $n$ vertices, then Algorithm~\ref{alg:put GN on WLD} assigns exactly $k$ distinct vertices to each $I_i$ in at most $n$ steps.
 \end{cor} 
@@
 It follows from the proof of Lemma~\ref{lem no fourth vertex} that in applying Algorithm~\ref{alg:put GN on WLD} to construct the set $I_i$, the algorithm can never reach the fourth vertex of a propagator's support (ordered with respect to $<_i$) without having already assigned that propagator.
-Therefore if the algorithm starts at vertex $i$, all propagators must have been eliminated by the time it gets to vertex $i-1$, ensuring that the algorithm is completed in less than one full circumnavigation of the diagram and that $I_i$ contains exactly $k$ distinct elements.
+Therefore if the algorithm starts at vertex $i$, all propagators must have been eliminated by the time it gets to vertex $i-1$, ensuring that the algorithm is completed in at most one full circumnavigation of the diagram and that $I_i$ contains exactly $k$ distinct elements.
 \end{proof}
@@
 \end{tabular}
-    \caption{Four cases for admissible WLDs with no non-supporting vertices. The gray half-propagators illustrate where propagators may occur, but are not required to exist.}\label{fig 3 cases}
+    \caption{Four cases for admissible Wilson loop diagrams with no non-supporting vertices.
+The gray half-propagators illustrate where propagators may occur, but are not required to exist.}\label{fig 3 cases}
   \end{figure}
@@
 \end{tabular}
-\caption{Example WLD for illustrating Algorithm~\ref{alg WLD to denom via GN} and bijections between propagators and vertices for each Grassmann necklace element.}\label{fig R eg}
+\caption{Example Wilson loop diagram for illustrating Algorithm~\ref{alg WLD to denom via GN} and bijections between propagators and vertices for each Grassmann necklace element.}\label{fig R eg}
 \end{figure}

### 2019-10-16 GWLDCII.tex
rewrote lemma 4.2, plus minor edits throughout

@@
 As noted above, the sum of the Feynman integrals associated to Wilson loop diagrams gives the volume of a convex polytope.
-if the singularities appearing in individual integrals cancel out in the overall sum, then the overall volume is finite.
+If the singularities appearing in individual integrals cancel out in the overall sum, then the overall volume is finite.
 This cancellation has been conjectured in general \cite{Hodges2013} and verified explicitly in a few cases \cite{casestudy, HeslopStewart}, but it is hard to prove in general due to the fact that the relationship between Wilson loop diagrams and $3k$-dimensional positroid cells of $\Gr(k,n)$ is neither one-to-one nor onto.
@@
 This not only greatly simplifies the previously known process to obtain a positroid cell from a Wilson loop diagram, but will also allow us to relate the behavior of the positroid $M(W)$ directly to the configuration of propagators in $W$.
-In section \ref{sec poles} we see that the denominator, $R(W)$, of the integrand associated to a Wilson loop diagram, $\Omega(W)$, can be written in terms of the Grassmann necklace of a diagram.
+In section \ref{sec poles} we use these results to show that the denominator $R(W)$ of the integrand associated to a Wilson loop diagram can be written in terms of the Grassmann necklace of a diagram.
 
@@
 \begin{proof}
-By \cite[Proposition 17.10]{Postnikov}, the dimension of a positroid (and hence the number of plusses in its Le diagram) is $k(n-k) - A(\pi_W)$, where $A(\pi_W)$ denotes the number of alignments of the decorated permutation $\pi_W$ of the positroid associated to $W$.
-(See \cite[Figure 17.1]{Postnikov} and preceding discussion.)
-
-It can easily be seen from \cite[Section 17]{Postnikov} and Algorithm \ref{alg:put GN on WLD} that dihedral transformations of a Wilson loop diagram $W$ correspond to dihedral transformations of the chord diagram representation of $\pi_W$.
-Since the number of alignments in a chord diagram is preserved under dihedral transformations, the result follows.
+Recall that the number of plusses in a Le diagram is given by the dimension of the corresponding positroid.
+By \cite[Proposition 17.10]{Postnikov}, the dimension of a positroid $M$ is $k(n-k) - A(\pi_M)$, where $A(\pi_M)$ denotes the number of alignments of the decorated permutation $\pi_M$ of $M$.
+The alignments of a decorated permutation are defined in terms of its chord diagram representation, where an alignment is any pair of non-crossing chords that share the same orientation.
+See \cite[Figure 17.1]{Postnikov} and preceding discussion for definitions and more details.
+
+With the help of Algorithm \ref{alg:put GN on WLD}, it is now easy to trace the effect of a dihedral transformation on a Wilson loop diagram through its Grassmann necklace to its decorated permutation to its chord diagram, and see that dihedral transformations of a Wilson loop diagram $W$ correspond to dihedral transformations of the chord diagram representation of $\pi_{M(W)}$.
+Since the number of alignments in a chord diagram is clearly preserved under dihedral transformations, the result follows.
 \end{proof}
@@
 
-In this section we investigate the poles of the integrand for $I(W)$.
+Recall from Section~\ref{section WLD background} that each Wilson loop diagram defines a functional $I(W)$, which associates a volume to the positroid cell $\Sigma(W)$.
+In this section we investigate the poles of the integrand of $I(W)$.
+
 Since SYM $N=4$ is a finite theory \cite{Alday:2007hr, ParkeTaylorids}, the scattering amplitudes (and thus the holomorphic Wilson loops $\,\mathfrak{W}_{k,n}$) are finite.
-That is, for a fixed set of external particles $\cZ$, we must have
+That is, for a fixed set of external particles $\cZ$ we must have
 \bas \sum_{W \text{ s.t. } |\cP| = k} I(W)(\cZ) <\infty \;.\eas
@@
 The results of Section~\ref{sec GN algorithm} allow us to relate the configuration of propagators in a Wilson loop diagram $W$ to minors of $C(W)$ that contribute to $R(W)$.
-
-In this section, we fix an arbitrary ordering on the propagators of W, i.e we impose an ordering on the rows of $C(W)$.
-
 The main result of this section is Theorem~\ref{thm denom}, which expresses the denominator $R(W)$ in terms of the Grassmann necklace of $W$.
 This simplifies the computation of $R(W)$ and allows us to directly relate the poles of the integrand to the combinatorics of the diagram.
+
+For the duration of this section, fix an arbitrary ordering on the propagators of $W$. This imposes an ordering on the rows of $C(W)$.
 
@@
 
-That is, each $r_i$ is the determinant of the minor determined by the propagators (rows) that contribute different values (columns) to the $i^{th}$ element of the Grassmann necklace than they did to the $i-1^{st}$.
+That is, each $r_i$ is the determinant of the minor determined by the propagators (rows) that contribute different values (columns) to the $i^{th}$ element of the Grassmann necklace than they did to the $(i-1)^{th}$.
 Since each $r_i$ is simply the determinant of a particular submatrix of $C(W)$ and an ordering on the propagators has been fixed, the sign of each $r_i$ is well-defined.
@@
 
-Below, we show that the polynomial $R$ associated to Wilson loop diagram $W$ is equal to the denominator $R(W)$ from Definition~\ref{def R(W)}, and is the radical of the product $\prod_{i=1}^n \Delta_{I_i}$.
+Below, we show that the polynomial $R$ associated to $W$ by Algorithm~\ref{alg WLD to denom via GN} is equal to the denominator $R(W)$ from Definition~\ref{def R(W)}, and is the radical\note{radical} of the product $\prod_{i=1}^n \Delta_{I_i}$.
 First, however, we give a worked example of Algorithm~\ref{alg WLD to denom via GN}.
@@
 \[
-C(W) = \begin{bmatrix} a & b & 0 & 0 & 0 & c & d \\ e & f & 0 & 0 & g & h & 0 \\ i & j & 0 & k & l & 0 & 0 \end{bmatrix}
+C(W) = \begin{bmatrix} a & b & 0 & 0 & 0 & c & d \\ e & f & 0 & 0 & g & h & 0 \\ i & j & 0 & k & l & 0 & 0 \end{bmatrix}.
 \]
 The Grassmann necklace of this diagram is 
-\begin{gather*}I_1 = \{1,2,4\}, I_2 = \{2,4,5\}, I_3 = \{4,5,6\}, I_4=\{4,5,6\},\\ I_5=\{5,6,7\}, I_6 = \{6,7,1\}, I_7=\{7,1,2\}. \end{gather*}  
+\begin{gather*}I_1 = \{1,2,4\},\ I_2 = \{2,4,5\},\ I_3 = \{4,5,6\},\ I_4=\{4,5,6\},\\ I_5=\{5,6,7\},\ I_6 = \{6,7,1\},\ I_7=\{7,1,2\}. \end{gather*}  
 Figure~\ref{fig R eg} indicates indicates which vertex is contributed to $I_i$ by each propagator, for each $i \in [1,7]$.
@@
 $i$ contributes to $f$.  Thus this diagram can be used in place of $W$.} we may assume $i\in I_i$ and that $i$ contributes to $f$.
-Finally, we can suppose that $W$ is minimal in number of propagators with an irreducible factor of degree $\geq 3$.
+Finally, we can suppose that $W$ is minimal with respect to number of propagators amongst diagrams with an irreducible factor of degree $\geq 3$.
 
@@
 Write $q = (i, j)$ for the support of $q$.
-The situation for $q$ is very similar to case 1: in particular, we have $I_{i+1}(q) = j$ by Lemma {\ref{vertex cyclic int lem}} and so if $j\in I_i$ then the propagator which contributes $j$ is outside of $q$.
+The situation for $q$ is very similar to Case 1: in particular, we have $I_{i+1}(q) = j$ by Lemma {\ref{vertex cyclic int lem}} and so if $j\in I_i$ then the propagator which contributes $j$ is outside of $q$.
     %\color{violet}if we have $r$ such that $I_i(r) = j$, as above, $r$ lies outside $q$: $r \in \cP_{out}(q, <_i)$.
@@
 
-\item Suppose propagators $p$ and $q$ are supported on a common edge  $a$, with $I_i(p)=a$ and $I_i(q)=a+1$.
+\item Suppose propagators $p$ and $q$ are supported on a common edge  $a$, with $I_i(p)=a$ and ${I_i(q)=a+1}$.
 Let $x_{p,a},x_{p,a+1},x_{q,a},x_{q,a+1}$ be the associated variables in $C(W)$.
@@
 
-Taking everything together we have that $R|\prod_{i=1}^n \Delta_{I_i}$, $R$ contains all factors of $\prod_{i=1}^n \Delta_{I_i}$ and $R$ is square-free.
+Taking everything together we have that $R|\prod_{i=1}^n \Delta_{I_i}$ (from part (4)), $R$ contains all factors of $\prod_{i=1}^n \Delta_{I_i}$, and $R$ is square-free.
 Therefore the ideal generated by $R$ is the radical of the ideal generated by $\prod_{i=1}^n \Delta_{I_i}$.
@@
 Thus we have shown a deep relationship between the physically derived poles of the integrand $\Omega(W)$ and the geometry and combinatorics associated to the diagrams $W$.
-This is yet another piece of substantial evidence indicating that the positroid representation of Wilson loop diagrams is the correct geometric object to be considering when considering the Wilson loop amplitudes geometrically.
+This is yet another piece of substantial evidence indicating that the positroid representation of Wilson loop diagrams is the correct geometric object to use when considering the Wilson loop amplitudes geometrically.
 

### 2019-10-17 GWLDCII.tex
responded to Sian and Karen's comments

@@
 Furthermore, the cells associated to the Wilson loop diagrams are different from the cells associated to BCFW diagrams, which can be seen by comparing the results of \cite{AmplituhedronDecomposition} and \cite{casestudy}.
-This is not too alarming, as it is conjectured that the space parametrized by the Wilson loop diagrams will project down to something close to the Amplituhedron \cite{wilsonloop, Amplituhedronsquared}.
+This is an intriguing observation, as it is conjectured that the space parametrized by the Wilson loop diagrams will project down to something close to the Amplituhedron \cite{wilsonloop, Amplituhedronsquared}.
 
@@
 We also show that the positroid cells associated to Wilson loop diagrams are all $3k$-dimensional, where $k$ is the number of propagators in the diagram; by contrast, the BCFW cells are all $4k$-dimensional \cite{Arkani-Hamed:2013jha}.
-Again, this is not too alarming, as it was shown in \cite{non-orientable} that the actual geometric space defined by the Wilson loop diagrams is a non-orientable $k$-dimensional bundle over this $3k$ dimensional manifold in $\Gr(k,n)$.
+This apparent contradiction led to the work in \cite{non-orientable}, which showed that the actual geometric space defined by the Wilson loop diagrams is a non-orientable $k$-dimensional bundle over this $3k$ dimensional manifold in $\Gr(k,n)$.
 
@@
 While this has been proved by Marcott in \cite{WLDdim} using matroidal arguments, our proof is constructive and explicitly relates the position of the plusses in the Le diagram to the propagators in the Wilson loop diagram.
-This proof and the methods used therein are a first step towards understanding how the positroid cell associated to a Wilson loop diagram changes as one adds propagators in certain positions.
+This proof and the methods used therein show how the positroid cell associated to a Wilson loop diagram changes as one adds propagators in specific positions.
+This is a significant step towards understanding the broader question about how adding propagators to a Wilson loop diagram changes the associated geometry.
 
@@
 
-One may also interpret the functional $I(W)$ as associating a volume to each cell $\Sigma(W)$ \cite{wilsonloop, Amplituhedronsquared, HeslopStewart}.
-The volume form is written in terms of the elements of $C(W)$ as  \begin{equation} \label{eq:omega(W) def}\Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V(p_r)} \textrm{d}x_{p_r}}{R(W)} \;, \end{equation}
-where the denominator $R(W)$ is given in Definition~\ref{def R(W)} below.
-The interested reader is referred to \cite{Adamo:2012xe,HeslopStewart,LipsteinMason} for more information about the volume form.
+One may also interpret the functional $I(W)$ as associating a volume to each cell $\Sigma(W)$ \cite{wilsonloop, Amplituhedronsquared, HeslopStewart}, where the volume is determined by the external pariticles involed.
+Specifically, the integrand is written in terms of the elements of $C(W)$ as  \begin{equation} \label{eq:omega(W) def}\Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V(p_r)} \textrm{d}x_{p_r}}{R(W)} \;, \end{equation} times a $\delta$ function that evaluates the matrix $C(W)$ on the external particles.
+The denominator $R(W)$ is given in Definition~\ref{def R(W)} below.
+For the purposes of this paper, we restrict our attention to $\Omega(W)$ only, and ignore the $\delta$ function in the integrand of $I(W)$.
+The interested reader is referred to \cite{Adamo:2012xe,HeslopStewart,LipsteinMason} for more information about the integrand of $I(W)$.
 
@@
 
-With this motivation in mind, in Section~\ref{sec poles} of this paper we study the denominator $R(W)$ of the volume form $\Omega(W)$. The definition of $R(W)$ is as follows.
+With this motivation in mind, in Section~\ref{sec poles} of this paper we study the denominator $R(W)$ of $\Omega(W)$. The definition of $R(W)$ is as follows.
 

### 2019-10-17 GWLDCII.tex
fixed the radical thing in abstact + section 5

@@
 We give an algorithm to derive the Grassmann necklace of the associated positroid directly from the Wilson loop diagram, and a recursive proof that the dimension of these cells is thrice the number of propagators in the diagram.
-We also show that the denominator in the integrand is the radical of the product of minors defined by the elements of the Grassmann necklace.
+We also show that the ideal generated by the denominator in the integrand is the radical of the ideal generated by the product of Grassmann necklace minors.
 \end{abstract}
@@
 
-One may also interpret the functional $I(W)$ as associating a volume to each cell $\Sigma(W)$ \cite{wilsonloop, Amplituhedronsquared, HeslopStewart}, where the volume is determined by the external pariticles involed.
-Specifically, the integrand is written in terms of the elements of $C(W)$ as  \begin{equation} \label{eq:omega(W) def}\Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V(p_r)} \textrm{d}x_{p_r}}{R(W)} \;, \end{equation} times a $\delta$ function that evaluates the matrix $C(W)$ on the external particles.
+One may also interpret the functional $I(W)$ as associating a volume to each cell $\Sigma(W)$ \cite{wilsonloop, Amplituhedronsquared, HeslopStewart}, where the volume is determined by the external particles involed.
+Specifically, the integrand is written in terms of the elements of $C(W)$ as  \begin{equation} \label{eq:omega(W) def}\Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V(p_r)} \textrm{d}x_{p_r}}{R(W)} \;, \end{equation} multiplied by a $\delta$ function that evaluates the matrix $C(W)$ on the external particles.
 The denominator $R(W)$ is given in Definition~\ref{def R(W)} below.
@@
 This not only greatly simplifies the previously known process to obtain a positroid cell from a Wilson loop diagram, but will also allow us to relate the behavior of the positroid $M(W)$ directly to the configuration of propagators in $W$.
-In section \ref{sec poles} we use these results to show that the denominator $R(W)$ of the integrand associated to a Wilson loop diagram can be written in terms of the Grassmann necklace of a diagram.
+In Section~\ref{sec poles} we use these results to show that the denominator $R(W)$ of the integrand associated to a Wilson loop diagram can be written in terms of the Grassmann necklace of a diagram.
 
@@
 
-Below, we show that the polynomial $R$ associated to $W$ by Algorithm~\ref{alg WLD to denom via GN} is equal to the denominator $R(W)$ from Definition~\ref{def R(W)}, and is the radical\note{radical} of the product $\prod_{i=1}^n \Delta_{I_i}$.
+Below, we show that the polynomial $R$ associated to $W$ by Algorithm~\ref{alg WLD to denom via GN} is equal to the denominator $R(W)$ from Definition~\ref{def R(W)}, and that the ideal generated by $R$ is the radical of the ideal generated by the product $\prod_{i=1}^n \Delta_{I_i}$.
 First, however, we give a worked example of Algorithm~\ref{alg WLD to denom via GN}.

### 2019-10-17 GWLDCII.tex
one more sentence
fiddled with R(W)/R(e) text

@@
 While it was already possible to construct the Grassmann necklace of a Wilson loop diagram via existing bijections between some of the various combinatorial objects that index the positroid cells, this process was convoluted and involved multiple steps; our algorithm allows us to track directly how each propagator in the Wilson loop diagram contributes to each term in the Grassmann necklace.
+This makes it much easier to track how properties move through the bijection, as we do throughout the later sections.
 Furthermore, the above algorithm allows us to better understand the positroids associated to Wilson loop.
@@
 
-In Section \ref{sec poles}, we show that the denominator $R(W)$ is determined by the positroid cell $\Sigma(W)$ and the structure of $W$, as encapsulated by $C(W)$.
-In fact, it can be read directly off of $C(W)$ in terms of a characterization of $\Sigma(W)$ called the Grassmann necklace (see Definition~\ref{def:grassmann necklace}).
+This formulation for the denominator comes from the physics literature: see equation (2) in \cite{HeslopStewart}.
+In Section \ref{sec poles}, we give a geometric meaning to the factors, $\{R_e | e \in V\}$, of $R(W)$.
+Given a Grassmann necklace representation of the positroid cell $\Sigma(W)$ ((see Definition~\ref{def:grassmann necklace} and Algorithm \ref{alg:put GN on WLD}), the $R_e$ are exactly the irreducible factors of the minors of $C(W)$ defined by the Grassman necklace.
+In particular, \emph{which} minors of $C(W)$ contribut to $R(W)$ is geometrically determined.
+Furthermore, when two Wilson loop diagrams correspond to the same postroid cell, they still have different $R(W)$.
 In Algorithm~\ref{alg WLD to denom via GN} we give an algorithm to read $R(W)$ directly from the Wilson loop diagram, paving the way for a general study of these poles in future.

### 2019-10-22 GWLDCII.tex
more tweaking to denominator paragraph
changes to intro

@@
 The main focus of that paper is enumerating the positroid cells that are associated to Wilson loop diagrams with a fixed number of vertices and propagators, as well as counting the number of Wilson loop diagrams that map to the same positroid.
+The results of the first paper are not needed for this paper.
 
@@
 
-This paper continues this work by identifying which positroid cells are associated to which Wilson loop diagram: specifically, we give an algorithm to read off the Grassmann necklace of the associated positroid cell from the Wilson loop diagram.
+This paper continues this body of work by establishing concrete connections between the combinatorics of the Wilson loop diagram as determined by the physics literature, and the combinatorics of the assoicated positroid cell (as identified in \cite{wilsonloop}).
+For instance, a Grassman Necklace is one of the many equivalent combinatorial objects uniquely identifying positroid cells.
+In this paper, we give an algorithm to read off the Grassmann necklace of the associated positroid cell from the Wilson loop diagram.
 We also show that the positroid cells associated to Wilson loop diagrams are all $3k$-dimensional, where $k$ is the number of propagators in the diagram; by contrast, the BCFW cells are all $4k$-dimensional \cite{Arkani-Hamed:2013jha}.
@@
 
-As noted above, the sum of the Feynman integrals associated to Wilson loop diagrams gives the volume of a convex polytope.
+SYM $N=4$ is a finite theory \cite{Adamo:2011pv,Adamo:2012xe,Arkani-Hamed:2013jha}.
+That is, the scattering amplitudes for particle interactions are finite.
+Since the (sum of) integrals associated to these scattering amplitudes can be associated to (the union of) convex polytopes, as the  noted above, one considers the sum of integrals as defining a volume to said union of polytopes.
+However, each individual integral has singularities occuring on the boundaries of the corresponding convex polytope.
+If the singularities cancel out in the overall sum, then the overall volume is finite.
+This cancellation has been conjectured in general \cite{Hodges2013} and verified explicitly in a few cases \cite{casestudy, HeslopStewart}, but it is hard to prove in general.
+In this paper, we give a goemetric characterization of the factors appearing in the denominator of these integrals.
+The set of irreducible factors in the denominator, as defined in the physics literature \cite{HeslopStewart}, are exactly the irreducible factors of the minors defined by the Grassmann necklace in a physically significant representation of the positroid cell assoicated to a diagram.
+In other words, the singluarities arising from tree level particle interactions in SYM $N=4$ theory do not just come from the Feynman rules describing the theory.
+They can also be seen directly from the associated geometry, given the physically correct representation.
+We hope these results will pave the way for a general study of these poles in future.
+
+%This paper continues this work by identifying which positroid cells are associated to which Wilson loop diagram: specifically, we give an algorithm to read off the Grassmann necklace of the associated positroid cell from the Wilson loop diagram.
+We also show that the positroid cells associated to Wilson loop diagrams are all $3k$-dimensional, where $k$ is the number of propagators in the diagram; by contrast, the BCFW cells are all $4k$-dimensional \cite{Arkani-Hamed:2013jha}.
+This apparent contradiction led to the work in \cite{non-orientable}, which showed that the actual geometric space defined by the Wilson loop diagrams is a non-orientable $k$-dimensional bundle over this $3k$ dimensional manifold in $\Gr(k,n)$.
+
+%As noted above, the sum of the Feynman integrals associated to Wilson loop diagrams gives the volume of a convex polytope.
 If the singularities appearing in individual integrals cancel out in the overall sum, then the overall volume is finite.
@@
 In this paper, we give a characterization of the factors appearing in the denominator of these Feynman integrals in terms of the Grassmann necklace of the associated positroid, thus providing a much simpler and more tractable link between the singularities and the diagrams.
-
-% when computing a finite volume to a geometric object defined by the Wilson loop diagrams, one must ensure that any singularities cancel.
-This has been verified explicitly in a few cases \cite{casestudy, HeslopStewart}, but it has been hard to prove in general due to the fact that the relationship between Wilson loop diagrams and $3k$ dimensional positroid cells of $\Gr(k,n)$ is neither one-to-one nor onto.
-In this paper, we give a characterisation of the denominator of the Feynman integral defined by a Wilson loop diagram in terms of the algorithm that associated the same diagram to a Grassman Necklace.
 
@@
 
-Finally in Section~\ref{sec poles} we characterize the denominator of the integrand of a Wilson loop diagram in terms of how propagators contribute to the Grassmann necklace.
+Finally in Section~\ref{sec poles} we characterize the denominator of the integrand of a Wilson loop diagram in terms the associated matrix and the Grassmann necklace.
 This characterization is given explicitly by Algorithm~\ref{alg WLD to denom via GN} and Theorem~\ref{thm denom}.
+Given the physically correct representation of the positroid cell assoicated to a Wilson loop diagram, the irreducible factors of the denominator are exactly the set of irreducible factors of the minors of said representation given by the Grassmann necklace.
 
@@
 In particular, \emph{which} minors of $C(W)$ contribut to $R(W)$ is geometrically determined.
-Furthermore, when two Wilson loop diagrams correspond to the same postroid cell, they still have different $R(W)$.
-In Algorithm~\ref{alg WLD to denom via GN} we give an algorithm to read $R(W)$ directly from the Wilson loop diagram, paving the way for a general study of these poles in future.
-
 We end this section with an example of computing $C(W)$ and $R(W)$ for a particular Wilson loop diagram $W$.

### 2019-10-22 GWLDCII.tex
spelling and grammar edits

@@
 The main focus of that paper is enumerating the positroid cells that are associated to Wilson loop diagrams with a fixed number of vertices and propagators, as well as counting the number of Wilson loop diagrams that map to the same positroid.
-The results of the first paper are not needed for this paper.
+The results of the first paper are not a prerequisite for this paper.
 
@@
 
-This paper continues this body of work by establishing concrete connections between the combinatorics of the Wilson loop diagram as determined by the physics literature, and the combinatorics of the assoicated positroid cell (as identified in \cite{wilsonloop}).
-For instance, a Grassman Necklace is one of the many equivalent combinatorial objects uniquely identifying positroid cells.
-In this paper, we give an algorithm to read off the Grassmann necklace of the associated positroid cell from the Wilson loop diagram.
+This paper continues this body of work by establishing concrete connections between the combinatorics of the Wilson loop diagram as determined by the physics literature, and the combinatorics of the associated positroid cell as identified in \cite{wilsonloop}.
+In this paper we give an algorithm to read off a combinatorial characterization (namely the Grassmann necklace, see Definition~\ref{def:grassmann necklace}) of the associated positroid cell from the Wilson loop diagram itself.
 We also show that the positroid cells associated to Wilson loop diagrams are all $3k$-dimensional, where $k$ is the number of propagators in the diagram; by contrast, the BCFW cells are all $4k$-dimensional \cite{Arkani-Hamed:2013jha}.
-This apparent contradiction led to the work in \cite{non-orientable}, which showed that the actual geometric space defined by the Wilson loop diagrams is a non-orientable $k$-dimensional bundle over this $3k$ dimensional manifold in $\Gr(k,n)$.
+This apparent contradiction led to the work in \cite{non-orientable}, which showed that the actual geometric space defined by the Wilson loop diagrams is a non-orientable $k$-dimensional bundle over this $3k$-dimensional manifold in $\Gr(k,n)$.
 
@@
 
-Finally in Section~\ref{sec poles} we characterize the denominator of the integrand of a Wilson loop diagram in terms the associated matrix and the Grassmann necklace.
+Finally, in Section~\ref{sec poles} we characterize the denominator of the integrand of a Wilson loop diagram in terms of its associated matrix and Grassmann necklace.
+We show that given the physically correct representation of the positroid cell associated to a Wilson loop diagram, the irreducible factors of the denominator are exactly the set of irreducible factors of the minors of said representation given by the Grassmann necklace.
 This characterization is given explicitly by Algorithm~\ref{alg WLD to denom via GN} and Theorem~\ref{thm denom}.
-Given the physically correct representation of the positroid cell assoicated to a Wilson loop diagram, the irreducible factors of the denominator are exactly the set of irreducible factors of the minors of said representation given by the Grassmann necklace.
 
@@
 
-One may also interpret the functional $I(W)$ as associating a volume to each cell $\Sigma(W)$ \cite{wilsonloop, Amplituhedronsquared, HeslopStewart}, where the volume is determined by the external particles involed.
+One may also interpret the functional $I(W)$ as associating a volume to each cell $\Sigma(W)$ \cite{wilsonloop, Amplituhedronsquared, HeslopStewart}, where the volume is determined by the external particles involved.
 Specifically, the integrand is written in terms of the elements of $C(W)$ as  \begin{equation} \label{eq:omega(W) def}\Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V(p_r)} \textrm{d}x_{p_r}}{R(W)} \;, \end{equation} multiplied by a $\delta$ function that evaluates the matrix $C(W)$ on the external particles.
@@
 This formulation for the denominator comes from the physics literature: see equation (2) in \cite{HeslopStewart}.
-In Section \ref{sec poles}, we give a geometric meaning to the factors, $\{R_e | e \in V\}$, of $R(W)$.
-Given a Grassmann necklace representation of the positroid cell $\Sigma(W)$ ((see Definition~\ref{def:grassmann necklace} and Algorithm \ref{alg:put GN on WLD}), the $R_e$ are exactly the irreducible factors of the minors of $C(W)$ defined by the Grassman necklace.
-In particular, \emph{which} minors of $C(W)$ contribut to $R(W)$ is geometrically determined.
+In Section \ref{sec poles}, we give a geometric meaning to the factors $\{R_e\ |\ e \in V\}$ of $R(W)$.
+Specifically: given a Grassmann necklace representation of the positroid cell $\Sigma(W)$ (see Definition~\ref{def:grassmann necklace} and Algorithm \ref{alg:put GN on WLD}), the $R_e$ are exactly the irreducible factors of the minors of $C(W)$ defined by the Grassmann necklace.
+In particular, the question of \emph{which} minors of $C(W)$ contribute to $R(W)$ is geometrically determined.
+
 We end this section with an example of computing $C(W)$ and $R(W)$ for a particular Wilson loop diagram $W$.

### 2019-10-23 GWLDCII.tex
minor changes to penultimate intro para

@@
 
-This paper continues this body of work by establishing concrete connections between the combinatorics of the Wilson loop diagram as determined by the physics literature, and the combinatorics of the associated positroid cell as identified in \cite{wilsonloop}.
-In this paper we give an algorithm to read off a combinatorial characterization (namely the Grassmann necklace, see Definition~\ref{def:grassmann necklace}) of the associated positroid cell from the Wilson loop diagram itself.
+This paper continues this body of work by establishing concrete connections between the combinatorics of the Wilson loop diagram as determined by the physics, and the combinatorics of the associated positroid cell as identified in \cite{wilsonloop}.
+In this paper, we give an algorithm to read the Grassmann necklace, one of the standard combinatorial characterizations of the positroid cell, directly off the Wilson loop diagram.
 We also show that the positroid cells associated to Wilson loop diagrams are all $3k$-dimensional, where $k$ is the number of propagators in the diagram; by contrast, the BCFW cells are all $4k$-dimensional \cite{Arkani-Hamed:2013jha}.

### 2019-10-25 GWLDCII.tex
talking on the phone

@@
 This led to the representation of the on shell integrals associated to this theory in terms of a geometric space (the Amplituhedron) embedded in $\Gr(k,n)$ \cite{Arkani-Hamed:2013kca,Arkani-Hamed:2013jha}.
-Moreover, integrals associated to the BCFW diagrams define a volume form on the Amplituhedron.
+Moreover, integrands associated to the BCFW diagrams define a volume form on the Amplituhedron.
 This gives a novel and elegant interpretation of scattering amplitudes for this theory, as well as a means of greatly simplifying the calculations involved in traditional Feynman diagram approaches.
@@
 These integrals are calculated via holomorphic Wilson loops.
-As with the Amplituhedron, each Wilson loop represents the sum of a family of $N^kMHV$ Feynman diagrams, and adding up the corresponding sums of Feynman integrals associates a volume form to a convex space different from the Amplituhedron \cite{Hodges2013}.
+As with the Amplituhedron, each Wilson loop represents the sum of a family of $N^kMHV$ Feynman diagrams, and adding up the corresponding sums of Feynman integrands associates a volume form to a convex space different from those in the decomposition the Amplituhedron \cite{Hodges2013}.
 In  \cite{wilsonloop}, Agarwala and Marin-Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that can be realized as an element of $\Gr(k,n)$.
 Other work has shown a connection between the volume filled by Wilson loop diagrams and the Amplituhedron \cite{casestudy, Amplituhedronsquared}.
-Specifically, Marcott shows that the space parametrized by the Wilson loop diagrams is  exactly the correct positroid cell in $\Gr(k,n)$, up to a set of measure $0$ \cite{WLDdim}.
+Specifically, Marcott shows that the space parametrized by the Wilson loop diagrams is  exactly the correct positroid cell in $\Gr(k,n)$, up to a set of measure zero \cite{WLDdim}.
 
@@
 We also show that the positroid cells associated to Wilson loop diagrams are all $3k$-dimensional, where $k$ is the number of propagators in the diagram; by contrast, the BCFW cells are all $4k$-dimensional \cite{Arkani-Hamed:2013jha}.
-This apparent contradiction led to the work in \cite{non-orientable}, which showed that the actual geometric space defined by the Wilson loop diagrams is a non-orientable $k$-dimensional bundle over this $3k$-dimensional manifold in $\Gr(k,n)$.
+This apparent contradiction is resolved by the non-orientability result of \cite{non-orientable}.
+
+%As described above, each integrand associated to a Wilson loop diagram gives the volume of a convex polytope.
+These individual volumes are not finite (*or maybe it needs to say "not necessarily finite" or "not always finite" or whatever is true*) which corresponds to the fact that the Feynman integrals have singularities coming from factors in their denominators.
+However SYM $N=4$ is a finite theory \cite{Adamo:2011pv,Adamo:2012xe,Arkani-Hamed:2013jha}, so the singularities must cancel out in the sum over all diagrams.
+This should mean that when the polytopes for each Wilson loop diagram are put together into one object (*you said union, but I think it must be more complicated than that, a set theoretic union can't make the infinite finite*) the overall volume is finite.
+This cancellation has been conjectured in general \cite{Hodges2013} and verified explicitly in a few cases \cite{casestudy, HeslopStewart}, but it is hard to prove in general due to the fact that the relationship between Wilson loop diagrams and $3k$-dimensional positroid cells of $\Gr(k,n)$ is neither one-to-one nor onto.
+
+%In this paper, we give a geometric characterization of the factors appearing in the denominator of these Feynman integrals in terms of the Grassmann necklace of the associated positroid.
+Specifically, we show that the set of irreducible factors in the denominator, as defined in the physics literature \cite{HeslopStewart}, are exactly the irreducible factors of the minors defined by the Grassmann necklace evaluated on a physically significant realization of the associated positroid cell.
+In other words, the singularities arising from tree level particle interactions in SYM $N=4$ theory do not just come from the Feynman rules describing the theory: they can also be seen directly from the associated geometry, given the physically correct representation.
+We hope these results will pave the way for a general study of these poles in future.
 

### 2019-10-25 GWLDCII.tex
last 2 paras of intro

--- 2019-10-23 GWLDCII.tex
@@
 We also show that the positroid cells associated to Wilson loop diagrams are all $3k$-dimensional, where $k$ is the number of propagators in the diagram; by contrast, the BCFW cells are all $4k$-dimensional \cite{Arkani-Hamed:2013jha}.
-This apparent contradiction led to the work in \cite{non-orientable}, which showed that the actual geometric space defined by the Wilson loop diagrams is a non-orientable $k$-dimensional bundle over this $3k$-dimensional manifold in $\Gr(k,n)$.
-
-SYM $N=4$ is a finite theory \cite{Adamo:2011pv,Adamo:2012xe,Arkani-Hamed:2013jha}.
+This apparent contradiction is resolved by the non-orientability result of \cite{non-orientable}.
+
+As described above, each integrand associated to a Wilson loop diagram gives the volume of a convex polytope.
+These individual integrals have singularities which come from the factors in the denomiator of the integrands.
+However SYM $N=4$ is a finite theory \cite{Adamo:2011pv,Adamo:2012xe,Arkani-Hamed:2013jha}, so the singularities must cancel out in the sum over all diagrams.
+This cancellation has been conjectured in general \cite{Hodges2013} and verified explicitly in a few cases \cite{casestudy, HeslopStewart}, but it is hard to prove in general due to the fact that the relationship between Wilson loop diagrams and $3k$-dimensional positroid cells of $\Gr(k,n)$ is neither one-to-one nor onto \cite{GWLDCI}.
+
+In this paper, we give a geometric characterization of the factors appearing in the denominator of these Feynman integrals in terms of the Grassmann necklace of the associated positroid.
+Specifically, we show that the set of irreducible factors in the denominator, as defined by the physics \cite{HeslopStewart}, are exactly the irreducible factors of the minors defined by the Grassmann necklace evaluated on a physically significant realization of the associated positroid cell.
+In other words, the singularities arising from tree level particle interactions in SYM $N=4$ theory do not just come from the Feynman rules describing the theory: they can also be seen directly from the associated geometry, given the physically correct representation.
+We hope these results will pave the way for a general study of these poles in future.
+
+%SYM $N=4$ is a finite theory \cite{Adamo:2011pv,Adamo:2012xe,Arkani-Hamed:2013jha}.
 That is, the scattering amplitudes for particle interactions are finite.

### 2019-10-25 GWLDCII.tex
more tweaks to intro (paper 2)

@@
 As described above, each integrand associated to a Wilson loop diagram gives the volume of a convex polytope.
-These individual integrals have singularities which come from the factors in the denomiator of the integrands.
-However SYM $N=4$ is a finite theory \cite{Adamo:2011pv,Adamo:2012xe,Arkani-Hamed:2013jha}, so the singularities must cancel out in the sum over all diagrams.
+Each of these individual integrals have singularities which come from the factors in the denominator of the integrands.
+However, SYM $N=4$ is a finite theory \cite{Adamo:2011pv,Adamo:2012xe,Arkani-Hamed:2013jha}, so the singularities must cancel out in the sum over all diagrams.
 This cancellation has been conjectured in general \cite{Hodges2013} and verified explicitly in a few cases \cite{casestudy, HeslopStewart}, but it is hard to prove in general due to the fact that the relationship between Wilson loop diagrams and $3k$-dimensional positroid cells of $\Gr(k,n)$ is neither one-to-one nor onto \cite{GWLDCI}.
 
-In this paper, we give a geometric characterization of the factors appearing in the denominator of these Feynman integrals in terms of the Grassmann necklace of the associated positroid.
+In this paper, we give a geometric characterization of the factors appearing in the denominator of these Wilson loop diagram integrals in terms of the Grassmann necklace of the associated positroid.
 Specifically, we show that the set of irreducible factors in the denominator, as defined by the physics \cite{HeslopStewart}, are exactly the irreducible factors of the minors defined by the Grassmann necklace evaluated on a physically significant realization of the associated positroid cell.

### 2019-10-25 GWLDCII.tex
fixed the cite

@@
 However, SYM $N=4$ is a finite theory \cite{Adamo:2011pv,Adamo:2012xe,Arkani-Hamed:2013jha}, so the singularities must cancel out in the sum over all diagrams.
-This cancellation has been conjectured in general \cite{Hodges2013} and verified explicitly in a few cases \cite{casestudy, HeslopStewart}, but it is hard to prove in general due to the fact that the relationship between Wilson loop diagrams and $3k$-dimensional positroid cells of $\Gr(k,n)$ is neither one-to-one nor onto \cite{GWLDCI}.
+This cancellation has been conjectured in general \cite{Hodges2013} and verified explicitly in a few cases \cite{casestudy, HeslopStewart}, but it is hard to prove in general due to the fact that the relationship between Wilson loop diagrams and $3k$-dimensional positroid cells of $\Gr(k,n)$ is neither one-to-one nor onto \cite{generalcombinatoricsI}.
 

### 2019-10-25 GWLDCII.tex
paragraph discussed over email

--- 2019-10-25 GWLDCII.tex
@@
 As described above, each integrand associated to a Wilson loop diagram gives the volume of a convex polytope.
-Each of these individual integrals have singularities which come from the factors in the denominator of the integrands.
-However, SYM $N=4$ is a finite theory \cite{Adamo:2011pv,Adamo:2012xe,Arkani-Hamed:2013jha}, so the singularities must cancel out in the sum over all diagrams.
-This cancellation has been conjectured in general \cite{Hodges2013} and verified explicitly in a few cases \cite{casestudy, HeslopStewart}, but it is hard to prove in general due to the fact that the relationship between Wilson loop diagrams and $3k$-dimensional positroid cells of $\Gr(k,n)$ is neither one-to-one nor onto \cite{GWLDCI}.
+However, each individual integral has singularities which come from the factors in the denominator of the integrands.
+SYM $N=4$ is a finite theory \cite{Adamo:2011pv,Adamo:2012xe,Arkani-Hamed:2013jha}, so the
+singularities must cancel out in the sum over all diagrams, though how this works out mathematically is unclear.
+The cancellation has been conjectured in general \cite{Hodges2013} and verified explicitly in a few cases \cite{casestudy, HeslopStewart}, but it is hard to prove in general due to the fact that the relationship between Wilson loop diagrams and $3k$-dimensional positroid cells of $\Gr(k,n)$ is neither one-to-one nor onto \cite{generalcombinatoricsI}.
 

### 2019-10-25 GWLDCII.tex
fixed layout and floats

@@
 \pgfmathsetmacro{\arrowangle}{90}
+\pgfmathsetmacro{\diagramscale}{1.3}
 \tikzstyle{propassignment} = [->,shorten >=2pt,thick]
@@
 \author{Susama Agarwala\thanks{SA was partially supported by an Office of Naval Research grant.}, Si\^an Fryer, and Karen Yeats\thanks{KY is supported by an NSERC Discovery grant, by the Canada Research Chair program, and though some the time this work was developed also by a Humboldt Fellowship from the Alexander von Humboldt foundation.}}
-%\date{}
+\date{}
 
@@
 	\begin{scope}
-	\drawWLD{8}{1.5}
+	\drawWLD{8}{2}
 	\drawnumbers
@@
 \item There does not exist a non-empty set of propagators $Q \subseteq \cP$ such that $|V(Q)| < |Q| + 3$.
-\item There does not exist a pair of crossing propagators: that is, there does not exist ${\{(i,j),(k,l)\} \subseteq \cP}$ such that $i < k < j < l$.
+\item There are no crossing propagators: that is, there does not exist ${\{(i,j),(k,l)\} \subseteq \cP}$ such that $i < k < j < l$.
 \end{enumerate}
@@
 
-\begin{figure}[h!]
-\[\begin{tikzpicture}[baseline=(current bounding box.east),scale=0.75]
+\begin{figure}
+\[\begin{tikzpicture}
+\node at (0,3.5) {}; % purely for spacing reasons
+\node at (0,-0.5) {}; % purely for spacing reasons
 \draw (1,0) grid (2,3);
@@
 %\node at (0.5,-0.15) {\footnotesize$8$};
-\end{tikzpicture}
-\qquad \qquad
-\begin{tikzpicture}[baseline=(current bounding box.east),scale=0.75]
+
+\begin{scope}[shift = {(7,0)}]
 \draw (1,0) grid (2,3);
@@
 %\node at (0.5,-0.15) {\footnotesize$9$};
+\end{scope}
 \end{tikzpicture}
@@
 
-Let $p$ be the propagator $p = (1, 4)$. Then $\cP_{in}(p, <_4) = \{(1,4), (5, 8), (5, 7) \}$ and $\cP_{out}(p, <_4) = \{(2,4) \}$
+Let $p$ be the propagator $p = (1, 4)$. Then $(p,<_4)$ indicates that we are viewing $p$ as being directed from 4 to 1, and we have
+\begin{gather*}\cP_{in}(p, <_4) = \{(1,4), (5, 8), (5, 7) \};\\
+\cP_{out}(p, <_4) = \{(2,4) \}. \end{gather*}
 \end{eg}
@@
   The following observations about configurations of propagators of short length in a weakly admissibly Wilson loop diagram $W$ are easily verified:
+  \vspace{-0.5em}
  \begin{enumerate}
@@
 
-\begin{figure}[h]
+\begin{figure}
 \[
-\begin{tikzpicture}[baseline=(current bounding box.north)]
+\begin{tikzpicture}[scale = 0.8,baseline=(current bounding box.north)]
   \begin{scope}
@@
   %\drawnumberspartial % use this to debug
-  \centerarc[linehighlight](0,0)(\zero + 1.43*\step:\zero+6.6*\step:\radius)
+  \centerarc[linehighlight](0,0)(\zero + 1.48*\step:\zero+6.64*\step:\radius)
   \newnode{1}{}
@@
 \end{scope}
-\end{tikzpicture}
-\qquad \qquad \qquad
-\begin{tikzpicture}[baseline=(current bounding box.north)]
-  \begin{scope}
+
+  \begin{scope}[shift = {(9,0)}]
   \drawWLDfragment[7]{3}{0.4} 
   %\drawnumberspartial % use this to debug
-  \centerarc[linehighlight](0,0)(\zero + 3.67*\step:\zero+4.43*\step:\radius)
+  \centerarc[linehighlight](0,0)(\zero + 3.67*\step:\zero+4.47*\step:\radius)
   \newnode{1}{i}
@@
   Let $W$ be a weakly admissible Wilson loop diagram with at least 5 vertices and in which each vertex supports at least one propagator.  Then at least one of the following two things occurs:
+  \vspace{-0.5em}
   \begin{enumerate}
@@
 
-\begin{figure}
+We can then choose the orientation of $q_r$ so that the previous $p_i$ and $q_i$ are all on the outside of $q_r$, and restrict our attention to the subdiagram $(\cP_{in}(q_r),[n])$.
+By the finiteness of $W$ this must eventually terminate in one of the desired configurations.
+%a configuration of the form \eqref{eq:2 prop config}.
+
+Start by choosing a propagator $p_1 = (j_1,j_1+2)$ of length 2 in $W$ (which exists by Remark~\ref{rem:props of length 2 and 3}).
+If it is part of one of the configurations we are looking for then we are done,
+%a configuration \eqref{eq:2 prop config} we are done,
+so suppose otherwise.
+
+From our existing assumptions, we know the following facts: $p_1$ is not in configuration \ref{item pair of 2s}, there are no propagators of length $3$, and every vertex supports at least one propagator.
+Therefore there must be a propagator of length $\geq 4$ with one end on edge $j_1$ or on edge $j_1-1$ or on edge $j_1-2$.
+Let $q_1 = (i_1, k_1)$ be this propagator, oriented such that $p_1 \in \cP_{out}(q_1,<_{i_1})$; see Figure~\ref{fig base case lem sian}.
+This completes the base case.
+
+\begin{figure}[h]
 \[
@@
 \caption{The base case of the induction in Lemma~\ref{lem sian}.}\label{fig base case lem sian} \end{figure}
-
-We can then choose the orientation of $q_r$ so that the previous $p_i$ and $q_i$ are all on the outside of $q_r$, and restrict our attention to the subdiagram $(\cP_{in}(q_r),[n])$.
-By the finiteness of $W$ this must eventually terminate in one of the desired configurations.
-%a configuration of the form \eqref{eq:2 prop config}.
-
-Start by choosing a propagator $p_1 = (j_1,j_1+2)$ of length 2 in $W$ (which exists by Remark~\ref{rem:props of length 2 and 3}).
-If it is part of one of the configurations we are looking for then we are done,
-%a configuration \eqref{eq:2 prop config} we are done,
-so suppose otherwise.
-
-From our existing assumptions, we know the following facts: $p_1$ is not in configuration \ref{item pair of 2s}, there are no propagators of length $3$, and every vertex supports at least one propagator.
-Therefore there must be a propagator of length $\geq 4$ with one end on edge $j_1$ or on edge $j_1-1$ or on edge $j_1-2$.
-Let $q_1 = (i_1, k_1)$ be this propagator, oriented such that $p_1 \in \cP_{out}(q_1,<_{i_1})$; see Figure~\ref{fig base case lem sian}.
-This completes the base case.
 
@@
 
-\begin{figure}
+\begin{figure}[h]
 \[
-\begin{tikzpicture}[baseline=(current bounding box.east)]
-  \begin{scope}
-  W' = \drawWLDfragment[12]{3}{0.4} 
+\begin{tikzpicture}[scale = 0.9,baseline=(current bounding box.east)]
+  \begin{scope}
+  \drawWLDfragment[12]{3}{0.4} 
   %\drawnumberspartial % use this to debug
+  \node at (0:0) {}; % purely for spacing purposes
   \newnode[left]{1}{i}
@@
   \newnode[right]{12}{l+1}
+  \node at (\zero + 3*\step:\radius*0.65) {\Large $W'$};
   \begin{scope}
@@
 \end{scope}
-\end{tikzpicture}
-\qquad \qquad
-\begin{tikzpicture}[baseline=(current bounding box.east)]
-  V' = \begin{scope}
+
+  \begin{scope}[shift = {(9,0)}]
   \drawWLDfragment[12]{3}{0.4} 
@@
   \newnode[right]{12}{l+1}
+  \node at (\zero + 4*\step:\radius*0.5) {\Large $V'$};
   \begin{scope}
@@
 
-\begin{figure}
-
+In Case 1, observe that we must have another propagator $q = (c,b)$ with $c<_i b$ and $I_i(q) = b+1$, because otherwise $I_i$ would assign $p$ to $b+1$.
+Now $q$ also contributes the $<_i$-maximal vertex in its support to $I_i$ and is an instance of Case 2.
+Therefore it suffices to show that no admissible Wilson loop diagram admits the configuration illustrated in Case 2 of Figure~\ref{fig:no fourth vertex}.
+
+So let $p = (a,b)$ with $a<_ib$ and $I_i(p) = b+1$, and choose $p$ such that $\big|[a+1,b]\big|$ is minimal amongst propagators of $W$ which contribute their last vertex and are in Case 2.
+
+Since $I_i(p) \neq b$, there must exist a propagator $q$ inside of $(p,<_i)$ with $I_i(q) = b$.
+The propagator $q$ cannot end on the edge $b-1$, as this would contradict the minimality of $p$, so we have $q = (d,b)$ with $a <_i d <_i b$, and $I_i(q) = b$.
+
+In order for $q$ to remain unassigned until vertex $b$, there must be another propagator $r$ with an end on edge $d$ and $I_i(r) = d+1$; the only way this can occur is if $r$ is outside of $(q,<_i)$ but inside $(p,<_i)$.
+But now $r$ contributes its fourth vertex to $I_i$, again contradicting the minimality of $p$.
+\end{proof}
+
+\begin{figure}[h]
 \[
@@
   \begin{scope}
-	\drawWLDfragment[20]{2}{1}
+  \drawWLDfragment[20]{2.2}{1}
   %\drawnumbers % use this to debug
+  \node at (108:\radius*1.2) {}; % spacing
   \newnode[left]{4}{I_i(p) = i-1}
@@
   \newprop[midway,below]{7.5}{15.3}{\scriptsize $q$}
-      \draw[smallpropagator,light-gray] (\zero +\step *4.3:\radius*1) -- (90:\radius*0.5); 
+      %\draw[smallpropagator,light-gray] (\zero +\step *4.3:\radius*1) -- (90:\radius*0.5); 
   \node at (270+18:\radius*1.5) {\em Case 1};
@@
   \begin{scope}
-	\drawWLDfragment[20]{2}{1}
+  \drawWLDfragment[20]{2.2}{1}
   %\drawnumbers % use this to debug
@@
 \end{figure}
-In Case 1, observe that we must have another propagator $q = (c,b)$ with $c<_i b$ and $I_i(q) = b+1$, because otherwise $I_i$ would assign $p$ to $b+1$.
-Now $q$ also contributes the $<_i$-maximal vertex in its support to $I_i$ and is an instance of Case 2.
-Therefore it suffices to show that no admissible Wilson loop diagram admits the configuration illustrated in Case 2 of Figure~\ref{fig:no fourth vertex}.
-
-So let $p = (a,b)$ with $a<_ib$ and $I_i(p) = b+1$, and choose $p$ such that $\big|[a+1,b]\big|$ is minimal amongst propagators of $W$ which contribute their last vertex and are in Case 2.
-
-Since $I_i(p) \neq b$, there must exist a propagator $q$ inside of $(p,<_i)$ with $I_i(q) = b$.
-The propagator $q$ cannot end on the edge $b-1$, as this would contradict the minimality of $p$, so we have $q = (d,b)$ with $a <_i d <_i b$, and $I_i(q) = b$.
-
-In order for $q$ to remain unassigned until vertex $b$, there must be another propagator $r$ with an end on edge $d$ and $I_i(r) = d+1$; the only way this can occur is if $r$ is outside of $(q,<_i)$ but inside $(p,<_i)$.
-But now $r$ contributes its fourth vertex to $I_i$, again contradicting the minimality of $p$.
-\end{proof}
 
@@
 
+% there's some big multiline displayed equations in this proof, so we temporarily enable \allowdisplaybreaks
+\begingroup
+\allowdisplaybreaks
+
 \begin{lem} \label{vertex cyclic int lem}
@@
 \begin{figure}
-\begin{tabular}{lll}
+\[\begin{tikzpicture}[baseline=(current bounding box.east)]
 % case 1
-\begin{tikzpicture}[baseline=(current bounding box.east)]
 	\begin{scope}
@@
 \end{scope}
-\end{tikzpicture}
-%
-%
-%
-& \qquad \qquad &
-%
-%
-%
+
 % case 2
-\begin{tikzpicture}[baseline=(current bounding box.east)]
-\begin{scope}
+\begin{scope}[shift = {(8.5,0)}]
 	\drawWLDfragment[8]{3}{0.3} % draw arc
@@
 \end{scope}
-\end{tikzpicture}
-%
-%
-%
-\\
-\ & \ & \ \\
-%
-%
-%
+
 % case 3
-\begin{tikzpicture}[baseline=(current bounding box.east)]
-\begin{scope}
+\begin{scope}[shift = {(0,-5)}]
 	\drawWLDfragment[8]{3}{0.3} % draw arc
@@
 \end{scope}
-\end{tikzpicture}
-%
-%
-%
-& \qquad \qquad & \qquad
-%
-%
-%
+
 % case 4
-\begin{tikzpicture}[baseline=(current bounding box.east)]
-	\begin{scope}
+\begin{scope}[shift = {(8.5,-5)}]
 	\drawWLDfragment[8]{3}{0.3} % draw arc
@@
 \end{scope}
-\end{tikzpicture}
-\end{tabular}
+\end{tikzpicture}\]
 \caption{Four cases for admissible Wilson loop diagrams with no non-supporting vertices.
@@
 
-\begin{figure}[h]
+\begin{figure}
 \[
@@
 \textbf{Case 3}: In this case there are no non-supporting vertices $l, l+1, \ldots$ inside $q$.
-Again write $p=(m, m+2)$ where $m\in \{j, j+1, j+2\}$.
+Again write ${p=(m, m+2)}$ where $m\in \{j, j+1, j+2\}$.
 We proceed as in the previous cases, by computing $I^{W}_w$ for vertices $w$ in roughly increasing order of difficulty.
@@
 Finally, for $j+1$ and the vertices in the support of $p$, we have
-
 \begin{align*}
@@
 \end{proof}
+\endgroup % this ends the \allowdisplaybreaks from the start of this proof.
 
@@
 By Remark~\ref{rmk algorithm locally same}, this yields the equalities
-
-%\st{By the above observations, if we commence Algorithm {\ref{alg:put GN on WLD}} in $W'$ from vertex $b$, then we are in the same situation with respect to unassigned propagators as if we began at $i$ in $W$ and proceeded to $b$ following the algorithm (recall that $I^W_i(p) =i$).}
-
-%{\color{violet} Note that the propagators in $\cP_{out}(p,<_i)$ come first in the ordering imposed by $I_i^W$ (Definition \ref{proporderingdfn}).
-Therefore, the ordering and contributions of propagators defined by $I_b^{W'}$ are the same as that of $I_i^W$ after the removal of these initial propagators.}
-
-%\st{The propagators contributing to $I_{i}^W$ before the vertex $b$ are exactly the ones removed in the construction of $W'$.}  Similarly, starting at $i+1$ in $W$ and moving to $b+1$ leaves us in the same situation with respect to unassigned propagators as beginning at $b+1$ in $W'$ would.
-This gives the equations
 \begin{align*}
@@
   %\drawnumberspartial % use this to debug
-  \centerarc[linehighlight](0,0)(\zero + 2.6*\step:\zero + 3.9*\step:\radius)
+  \node at (270:\radius*0.2) {}; %spacing
+  \node at (270:\radius*1.2) {}; %spacing
+  \centerarc[linehighlight](0,0)(\zero + 2.7*\step:\zero + 3.9*\step:\radius)
   \newnode{1}{i}
@@
 \end{scope}
-\node at (\zero+5*\step:\radius*0.50) {\scriptsize $p_r$};
+\node at (\zero+5*\step:\radius*0.52) {\scriptsize $p_r$};
 \node at (\zero + 6*\step:\radius*0.75) {\scriptsize $q$};
@@
   \begin{scope}
-  \drawWLDfragment[10]{4}{0.3} 
+  \drawWLDfragment[10]{4}{0.35} 
   %\drawnumberspartial % use this to debug
-  \centerarc[linehighlight](0,0)(\zero + 4.5*\step:\zero + 5.3*\step:\radius)
+  \node at (270:\radius*0.3) {}; %spacing
+  \node at (270:\radius*1.2) {}; % spacing
+  \centerarc[linehighlight](0,0)(\zero + 4.4*\step:\zero + 5.2*\step:\radius)
   \newnode{1}{i}
@@
 \clipcenterarc(0,0)(\startpoint:\endpoint:\radius)
-\clip (\zero + 5.5*\step:\radius*1.5) circle (\radius*0.85);
+\clip (\zero + 5.5*\step:\radius*1.5) circle (\radius);
 \newpropbend{5}{18}{30} %p_s
 \newpropbend{5.5}{15}{30} %p_r
-\newpropbend{6}{12}{30} %q
-\end{scope}
-\node at (\zero+5.7*\step:\radius*0.72) {\scriptsize $p_r$};
-\node at (\zero+4.15*\step:\radius*0.71) {\scriptsize $p_s$};
-\node at (\zero + 6.8*\step:\radius*0.83) {\scriptsize $q$};
-\node at (\zero + 5*\step:\radius*1.07) {\scriptsize $a_s$};
-\end{scope}
-\end{tikzpicture}
-\qquad \qquad
-\begin{tikzpicture}[baseline=(current bounding box.east)]
-  \begin{scope}
-  \drawWLDfragment[10]{4}{0.3} 
+\newpropbend{6.3}{12}{30} %q
+\end{scope}
+\node at (\zero+5.4*\step:\radius*0.65) {\scriptsize $p_r$};
+\node at (\zero+3.7*\step:\radius*0.71) {\scriptsize $p_s$};
+\node at (\zero + 7.3*\step:\radius*0.75) {\scriptsize $q$};
+\node at (\zero + 4.8*\step:\radius*1.07) {\scriptsize $a_s$};
+\end{scope}
+% start second diagram
+  \begin{scope}[shift = {(8.5,0)}]
+  \drawWLDfragment[10]{4}{0.35} 
   %\drawnumberspartial % use this to debug
-  \centerarc[linehighlight](0,0)(\zero + 2.5*\step:\zero + 3.7*\step:\radius)
-  \centerarc[linehighlight](0,0)(\zero + 6.3*\step:\zero + 7.5*\step:\radius)
+  \centerarc[linehighlight](0,0)(\zero + 2.3*\step:\zero + 3.7*\step:\radius)
+  \centerarc[linehighlight](0,0)(\zero + 6.1*\step:\zero + 7.5*\step:\radius)
   \newnode{1}{i}
@@
 \end{scope}
-\node at (\zero+5.3*\step:\radius*0.78) {\scriptsize $p_r$};
-\node at (\zero+2.3*\step:\radius*0.8) {\scriptsize $p_s$};
-\node at (\zero + 7.4*\step:\radius*0.8) {\scriptsize $q$};
+\node at (\zero+5.3*\step:\radius*0.75) {\scriptsize $p_r$};
+\node at (\zero+2.1*\step:\radius*0.8) {\scriptsize $p_s$};
+\node at (\zero + 7.7*\step:\radius*0.8) {\scriptsize $q$};
 \node at (\zero + 3*\step:\radius*1.07) {\scriptsize $a_s$};
@@
 
-In an arbitrary Grassmann necklace, it is possible for an index $i$ to appear in no terms of the Grassmann necklace (a {\em loop}) or in all terms of the necklace (a {\em coloop}).
+In an arbitrary Grassmann necklace, it is possible for an index $i$ to appear in no terms of the Grassmann necklace (a {\bf loop}) or in all terms of the necklace (a {\bf coloop}).
 Using Theorems~\ref{res:alg gives GN} and \ref{res alg gives correct GN}, a characterization of the loops and coloops of the Grassmann necklace associated to a Wilson loop diagram follows easily.
@@
 In order to prove our main theorem of this section, we first require several lemmas.
+
 We begin by relating non-supporting vertices to columns of zeros in the Le diagram (Lemma \ref{lem uncovered}) and verifying that performing dihedral transformations on a Wilson loop diagram does not change the dimension of the associated Le diagram (Lemma \ref{lem dihedral}).
@@
 
+\vspace{0.5em} % this and following two vspaces purely for formatting / pagebreak reasons
 \begin{lem}\label{lem uncovered}
@@
 it must be a column label.
-The shapes of the Le diagram of $V$ and $W$ are the same except for the insertion of this column since $I_1$ is the same for $V$ and $W$ except for the incrementation of the indices $\geq i$ in the transition from the necklace for $V$ to the necklace for $W$.
+The shapes of the Le diagram of $V$ and $W$ are the same except for the insertion of this column, since $I_1$ is the same for $V$ and $W$ except for the incrementation of the indices $\geq i$ in the transition from the necklace for $V$ to the necklace for $W$.
 \end{proof}
+\vspace{0.5em}
 
@@
 With the help of Algorithm \ref{alg:put GN on WLD}, it is now easy to trace the effect of a dihedral transformation on a Wilson loop diagram through its Grassmann necklace to its decorated permutation to its chord diagram, and see that dihedral transformations of a Wilson loop diagram $W$ correspond to dihedral transformations of the chord diagram representation of $\pi_{M(W)}$.
+
 Since the number of alignments in a chord diagram is clearly preserved under dihedral transformations, the result follows.
 \end{proof}
+
+\vspace{0.5em}
 
@@
 \] 
-  \caption{The two cases for $W$ and $p$.  No other propagators can end in the bolded (red) sections.  Other segments may have additional propagators ending in them.}\label{fig special p}
+  \caption{The two cases for $W$ and $p$ following Lemma~\ref{lem good p}.
+No other propagators can end in the bolded (red) sections.
+Other segments may have additional propagators ending in them.}\label{fig special p}
 
@@
 
-On the other hand, if $n-2\in I_{n-2}^{V}$ then we must be in Case 2 of Figure~\ref{fig special p} and ${I_{n-2}^V(q) = I_{n-2}^W(q) = n-2}$ (since $q$ is always the clockwise-most propagator supported on vertex $n-2$.
+On the other hand, if $n-2\in I_{n-2}^{V}$ then we must be in Case 2 of Figure~\ref{fig special p} and we must have ${I_{n-2}^V(q) = I_{n-2}^W(q) = n-2}$ (since $q$ is always the clockwise-most propagator supported on vertex $n-2$).
 If $n-1 \not\in I_{n-2}^{V}$, then $I_{n-2}^W(p) = n-1$ and then the algorithm proceeds identically to $I_{n-2}^{V}$ for the remainder of its steps; thus $I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-1\}$ in this case.
@@
 Also $u$ cannot be $n-4$, for the following reason.
-By Remark~\ref{rmk cyclic} we know that $I_{n-1}^W(q) = n-5$, leaving no propagators supported on $n-4$ for $I_{n-1}^W$ to assign.
+By Remark~\ref{rmk cyclic} we know that ${I_{n-1}^W(q) = n-5}$, leaving no propagators supported on $n-4$ for $I_{n-1}^W$ to assign.
 Thus $n-4 \not\in I_{n-1}^W$.
@@
 \end{gather*}
-As per the discussion following equation \eqref{eq necklace} above, we also have $I_n^V\setminus I_1^V = \{n\}$ and ${I_1^V\setminus I_n^V = \{v\}}$.
+As per the discussion following equation \eqref{eq necklace} above, we must also have $I_n^V\setminus I_1^V = \{n\}$ and ${I_1^V\setminus I_n^V = \{v\}}$.
 If $c = n-5$ then the path $v \rightarrow n$ from $I_n^V$ does not intersect with the paths from $\{n-3, n-5\}$ to $\{n-2, n-1\}$ and we obtain the plusses as stated.
@@
 
-  First note that a Wilson loop diagram $W$ with one propagator supported on vertices $i<i+1<j<j+1$ has a Le diagram consisting of a single row with $n-i$ boxes.
+  First note that a Wilson loop diagram $W$ with one propagator supported on vertices \[{i<i+1<j<j+1}\] has a Le diagram consisting of a single row with $n-i$ boxes.
 The columns are labeled from left to right by $n, \ldots, i+1$.
@@
 \begin{tabular}{rrrrr}
-% \arrowangle is defined globally in the preamble for easy tweaking
+% \arrowangle and \diagramscale are defined globally in the preamble for easy tweaking
 \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
   \begin{scope}
-  \drawWLD{7}{1.5}
+  \drawWLD{7}{\diagramscale}
   \drawnumbers
@@
   \begin{scope}
-  \drawWLD{7}{1.5}
+  \drawWLD{7}{\diagramscale}
   \drawnumbers
@@
 Therefore $\Delta_{I_i} = \pm \det A \det C$, and both factors are nontrivial since at least one of $m$ and $m+1$ appear in $I_i$.
-Since $p\in \cP_{in}(p)$ we have $f|\det A$ and if we remove a propagator outside of $p$ that contributes either $m$ or $m+1$, we get a diagram $W'$ with fewer propagators for which $\det A | \Delta_{I^{W'}_i}$ still holds, hence $f|\Delta_{I^{W'}_i}$.
+
+Since $p\in \cP_{in}(p)$ we have $f|\det A$, and if we remove a propagator outside of $p$ that contributes either $m$ or $m+1$, we get a diagram $W'$ with fewer propagators for which $\det A | \Delta_{I^{W'}_i}$ still holds, hence $f|\Delta_{I^{W'}_i}$.
 This contradicts the minimality of our choices.
@@
 \item If $S_i = \emptyset$ then $r_i = 1$ and we immediately have $r_i | \Delta_{I_i}$; otherwise, let $p\in S_i$.
+
 Note that $\Delta_{I_i}$ is homogeneous linear in the variables of the row corresponding to $p$.
@@
 
-In both cases, since $I_{i-1}(p)\neq I_{i}(p)$ by assumption it follows from Lemma~\ref{vertex cyclic int lem} that $I_{i-1}(p) <_{i-1} I_{i}(p)$ and no other vertex supporting $p$ lies between $I_{i-1}(p)$ and $I_{i}(p)$.
+In both cases, since we have $I_{i-1}(p)\neq I_{i}(p)$ by assumption it follows from Lemma~\ref{vertex cyclic int lem} that ${I_{i-1}(p) <_{i-1} I_{i}(p)}$ and no other vertex supporting $p$ lies between $I_{i-1}(p)$ and $I_{i}(p)$.
 If $I_i(q)=a$ then $q$ lies clockwise of $p$ and $q$ contributes before $p$ in $I_i$.

### 2020-09-30 GWLDCI.tex
line about first paper not prerequisite in paper 1
stab at report M

@@
 \title{Combinatorics of the geometry of Wilson loop diagrams I: equivalence classes via matroids and polytopes}
-\author{Susama Agarwala\thanks{SA was partially supported by an Office of Naval Research grant.}, Si\^an Fryer, and Karen Yeats\thanks{KY is supported by an NSERC Discovery grant, by the Canada Research Chair program, and though some the time this work was developed also by a Humboldt Fellowship from the Alexander von Humboldt foundation.}}
+\author{Susama Agarwala\thanks{SA was partially supported by an Office of Naval Research grant.}, Si\^an Fryer, and Karen Yeats\thanks{KY is supported by an NSERC Discovery grant, by the Canada Research Chair program, though some of this work was developed also by a Humboldt Fellowship from the Alexander von Humboldt foundation.}}
 %\date{}
@@
 With this identification in hand, we also prove that any Wilson loop diagram with $k$ propagators corresponds to a $3k$ dimensional positroid cell, and characterize the volume forms that Wilson loop diagrams associate to each positroid cell.
+The results of the first paper are not prerequisite for the second paper in this series.
 
@@
 \begin{dfn} \label{VPropdfn}
-Let $W = (\cP, [n])$.
+Let $W = (\cP, [n])$. In this definition and in the sequel, for any $P \subseteq \cP$ or $U \subseteq [n]$, we denote $P^c = \cP \setminus P$ and $U^c = [n] \setminus U$.
 \begin{enumerate}
@@
 \item $|V| \geq |\cP| + 4.$
-\item There does not exist a (non-empty) set of propagators $Q \subseteq \cP$ such that $|V(Q)| < |Q| + 3$.
+\item For any non-empty set of propagators, $Q \subseteq \cP$, $Q \neq \emptyset$, one has $|V(Q)| \geq |Q| + 3$.
 \item There does not exist a pair of propagators $(i_p,j_p),(i_q,j_q) \in \cP$ such that $i_p < i_q < j_p <j_q$.
@@
 First, what we call weakly admissible here is called admissible in \cite{wilsonloop}.
-Many of the results below still apply when the hypothesis of admissibility is changed to weak admissibility.
+\hlfix{Many of the results below still apply when the hypothesis of admissibility is changed to weak admissibility.}{Propagate "weakly" through document}
 
@@
 Finally, we describe several important types of matroids.
-A matroid of rank $k$ with a ground set of size $n$ is called {\em realizable} if there exists some $A$ in the $k\times n$ real Grassmannian $\mathbb{G}_{\mathbb{R}}(k,n)$ whose non-zero $k\times k$ minors are exactly those with columns indexed by an element of $\cB$.
+A matroid of rank $k$ with a ground set of size $n$ is called {\em realizable} if there exists some matrix $A$ in the $k\times n$ real Grassmannian $\mathbb{G}_{\mathbb{R}}(k,n)$ whose non-zero $k\times k$ minors are exactly those with columns indexed by an element of $\cB$.
 If all the maximal minors of the matrix are nonnegative then the matroid realized by this matrix is called a {\em positroid}.
@@
 \begin{thm} \label{thm WLD defines matroid} \cite[Theorem 3.6]{wilsonloop} Any admissible Wilson loop diagram $W =(\cP, [n])$ defines a matroid $M(W)$ with ground set $[n]$.
-The independent sets are exactly those subsets $V \subseteq [n]$ such that $\nexists U\subseteq V$ satisfying $|\Prop(U)| < |U|$.
+The independent sets are exactly those subsets $V \subseteq [n]$ such that for every subset of vertices, $U\subseteq V$, supports at least as many propagators as vertices in the set, $|\Prop(U)| \geq |U|$.
 \label{thm:WLDmatroid}\end{thm}
@@
 Comparing this to Theorem \ref{thm:WLDmatroid}, we see that $M(W)$ is also the matroid realized by $C(W)$.
+As mentioned above, Theorem [3.38] of \cite{wilsonloops} shows that the matroids $M(W)$ is a positroid.
+Furthermore, Theorem 5.1 \cite{basisshapeloci} shows that the space parametrized by the matrices $C(W)$ matches the positroid cells defined by $M(W)$, up to a set of measure $0$.
+Note, this does not imply that every possible specializaton of $C(W)$ to a real valued matrix leads to a postroid, only that the set of values that do define a positroid is volume filling in $\R^{4k}$.
+\todo{What is [6] referred to by reviewer M?}
 
@@
 
-\section{Matroids, triangulations, and equivalence classes of Wilson loop diagrams}\label{sec equiv}
+\todo{Need to address the summary comment to 3.1 in review M}
+
+\section{Matroids, triangulations, and equivalence classes of Wilson loop diagrams\label{sec equiv}} \todo{rephrase in terms of weakly.}
 
@@
 To do this, we establish a connection between Wilson loop diagrams and polygon dissections in subsection \ref{sec: polygon partitions}, and uncover some matroidal properties of exact subdiagrams in subsection \ref{sec: exact diagram matroidal props}.
-This includes the fact that exact subdiagrams correspond to uniform matroids (Theorem \ref{exactuniformthm}), and that the associated matroid of an exact subdiagram can be written as as a contraction by the complementary propagator flat (Theorem \ref{exact diagrams contractions}).
+This includes the fact that exact subdiagrams correspond to uniform matroids (Theorem \ref{exactuniformthm}), and that the associated matroid of an exact subdiagram can be written as a contraction by the complementary propagator flat (Theorem \ref{exact diagrams contractions}).
 
@@
 \begin{enumerate}
-\item The matroid assoicated to an exact subdiagram of $W$ can be written as a contraction of the matroid $M(W)$ by the complementary propagator flat (Theorem \ref{exact diagrams contractions}). 
+\item The matroid associated to an exact subdiagram of $W$ can be written as a contraction of the matroid $M(W)$ by the complementary propagator flat (Theorem \ref{exact diagrams contractions}). 
 \item The matroid associated to an exact subdiagram is uniform (Theorem \ref{exactuniformthm}).
@@
 \item If $(P,V(P))$ is a maximal exact subdiagram of $W$, then $F(P^c)$ is a cyclic flat in $W$.
-\item If $(P,V(P))$ is an exact subdiagram in $W$, then $\rk(F(P^c)) = |P^c|$.
+\item If $(P,V(P))$ is an exact subdiagram of $W$, then $\rk(F(P^c)) = |P^c|$.
 \end{enumerate} 
@@
 \begin{thm} \label{exact diagrams contractions}
-If $(P, V(P))$ is an exact subdiagram of of $W$, the matroid of $(P,V(P))$ is the contraction of $M(W)$ by the propagator flat $F(P^c)$, i.e. \bas M\big((P, V(P))\big) = M(W)  / F(P^c) \;.\eas 
+If $(P, V(P))$ is an exact subdiagram of $W$, the matroid of $(P,V(P))$ is the contraction of $M(W)$ by the propagator flat $F(P^c)$, i.e. \bas M\big((P, V(P))\big) = M(W)  / F(P^c) \;.\eas 
 \end{thm}
@@
 \begin{thm}\label{same matroid iff equiv}
-Let $W= (\cP, [n])$ and $W'= (\cP', [n])$ be two Wilson loop diagrams. They define the same matroid (positroid) if and only if $W \sim W'$.
+Let $W= (\cP, [n])$ and $W'= (\cP', [n])$ be two weakly admissible Wilson loop diagrams. They define the same matroid (positroid) if and only if $W \sim W'$.
 \end{thm}
@@
 
-\begin{dfn}\label{def:associahedron}
+\begin{dfn}\label{def:associahedron} \todo{Karen, see note bottom of page 2 in report M}
 Fix $n$ and consider dissections of a convex $n$-gon.
@@
 
-\begin{dfn}\label{def:secondary polytope}
+\begin{dfn}\label{def:secondary polytope} \todo{Karen, see note bottom of page 2 in report M}
   Let $x_1, \ldots, x_n$ be the corners of a convex $n$-gon in $\mathbb{R}^2$, and let $T$ be the set of triangulations of this $n$-gon.
@@
 \begin{proof}
-  Since $D_1$ and $D_2$ do not have the same set of non-triangle faces, there must be some diagonal $d$ of $D_1$ that crosses through a non-triangle face $f$ of $D_2$.
-If that face of $D_2$ has degree at least 5 then it must contain four vertices in the configuration described in the statement.
+\hlfix{Since $D_1$ and $D_2$ do not have the same set of non-triangle faces, but the vertices of the non-triangles faces are the same, $V_{>3}(D_1) = V_{>3}(D_2)$, there must be some diagonal $d$ of $D_1$ that crosses through a non-triangle face $f$ of $D_2$.
+If that face of $D_2$ has degree at least 5 then it must contain four vertices in the configuration described in the statement.}{Karen, I'm leaving the rest of the last comment of report M to you.}
 

### 2020-09-30 GWLDCI.tex
updated report notes, propagated weakly admissible

@@
 
-Both the Amplituhedron literature and the Wilson loop literature associate $n$ particle $N^kMHV$ interactions in SYM $N=4$ theory to volume forms on a set of positroid cells of $\Gr(k,n)$.
+Both the Amplituhedron literature and the Wilson loop literature \hlfix{associate $n$ particle $N^kMHV$ interactions in SYM $N=4$}{make more prominent?} theory to volume forms on a set of positroid cells of $\Gr(k,n)$.
 This gives a CW complex of some submanifold in $\Gr(k,n)$, and understanding the geometry and topology of these spaces is the subject of ongoing research.
@@
 \begin{dfn}\label{def:exact diagram}
-For $W$ an admissible diagram, the subdiagram $(P, V(P))$ is {\em exact} if $|V(P)| = |P| + 3$.
+For $W$ a weakly admissible diagram, the subdiagram $(P, V(P))$ is {\em exact} if $|V(P)| = |P| + 3$.
 \end{dfn}
@@
 \begin{dfn}\label{equivdfn} 
-Let $W = (\cP,[n])$ and $W' = (\cP',[n])$ be two admissible subdiagrams. Let $\sim$ denote the transitive closure of the following relation: $W$ and $W'$ are related if
+Let $W = (\cP,[n])$ and $W' = (\cP',[n])$ be two weakly admissible subdiagrams. Let $\sim$ denote the transitive closure of the following relation: $W$ and $W'$ are related if
 \begin{enumerate}
@@
 \end{enumerate}
-The relation $\sim$ is an equivalence relation on the set of all admissible Wilson loop diagrams with vertex set $[n]$.
+The relation $\sim$ is an equivalence relation on the set of all weakly admissible Wilson loop diagrams with vertex set $[n]$.
 \end{dfn}
@@
 
-\begin{thm} \label{thm WLD defines matroid} \cite[Theorem 3.6]{wilsonloop} Any admissible Wilson loop diagram $W =(\cP, [n])$ defines a matroid $M(W)$ with ground set $[n]$.
+\begin{thm} \label{thm WLD defines matroid} \cite[Theorem 3.6]{wilsonloop} Any Wilson loop diagram $W =(\cP, [n])$ defines a matroid $M(W)$ with ground set $[n]$.
 The independent sets are exactly those subsets $V \subseteq [n]$ such that for every subset of vertices, $U\subseteq V$, supports at least as many propagators as vertices in the set, $|\Prop(U)| \geq |U|$.
@@
 Comparing this to Theorem \ref{thm:WLDmatroid}, we see that $M(W)$ is also the matroid realized by $C(W)$.
-As mentioned above, Theorem [3.38] of \cite{wilsonloops} shows that the matroids $M(W)$ is a positroid.
+As mentioned above, Theorem [3.38] of \cite{wilsonloops} shows that if $W$ is weakly admissible, the matroid $M(W)$ is a positroid.
 Furthermore, Theorem 5.1 \cite{basisshapeloci} shows that the space parametrized by the matrices $C(W)$ matches the positroid cells defined by $M(W)$, up to a set of measure $0$.
@@
 
-Let $W = (\cP,[n])$ be an admissible Wilson loop diagram, and $M(W)$ its associated matroid.
+Let $W = (\cP,[n])$ be a weakly admissible Wilson loop diagram, and $M(W)$ its associated matroid.
 Where it will not cause confusion we conflate the two objects, we identify vertices of $W$ with elements of the ground set $[n]$ in $M(W)$.
@@
 \begin{lem}\label{lem facts about WLD matroids}
-Let $W = (\cP,[n])$ be an admissible Wilson loop diagram. Then:
+Let $W = (\cP,[n])$ be a weakly admissible Wilson loop diagram. Then:
 \begin{enumerate}
@@
 \begin{dfn}\label{WLDtriangulationdfn}
-  Let $W = (\cP, [n])$ be an admissible Wilson loop diagram.  The \emph{polygon dissection} associated to $W$, denoted $\tau(W)$, is defined as follows.
+  Let $W = (\cP, [n])$ be a weakly admissible Wilson loop diagram.  The \emph{polygon dissection} associated to $W$, denoted $\tau(W)$, is defined as follows.
   \begin{itemize}
@@
 \begin{lem}\label{tausimpleplanarlem}
-If $W = (\cP, [n])$ is an admissible Wilson loop diagram, then $\tau(W)$ is a simple planar graph whose outer face is a cycle.
+If $W = (\cP, [n])$ is a weakly admissible Wilson loop diagram, then $\tau(W)$ is a simple planar graph whose outer face is a cycle.
 It inherits an embedding from $W$ such that the vertices all lie on this infinite face\footnote{That is, it is an \emph{outerplanar} graph}.
@@
 Therefore, no two vertices of $\tau(W)$ can be connected by more than one edge, and so $\tau(W)$ is a simple graph.
-Finally, the embedding of $\tau(W)$ is induced from the embedding of the graph $W$, and since $W$ is admissible we know that no pair of propagators can cross.
+Finally, the embedding of $\tau(W)$ is induced from the embedding of the graph $W$, and since $W$ is weakly admissible we know that no pair of propagators can cross.
 Therefore, it is a planar embedding.
@@
 \begin{dfn}
-  Let $W$ be an admissible Wilson loop diagram and $\tau(W)$ its polygon dissection.
+  Let $W$ be a weakly admissible Wilson loop diagram and $\tau(W)$ its polygon dissection.
 A \emph{triangulated piece} of $\tau(W)$ is a 2-connected subgraph of $\tau(W)$ which is a triangulation.
@@
 \begin{lem} \label{decompositionlem}
-  For $W$ an admissible Wilson loop diagram, the polygon dissection $\tau(W)$ has a unique decomposition into maximal triangulated pieces and edges in the polygon of $\tau(W)$.
+  For $W$ a weakly admissible Wilson loop diagram, the polygon dissection $\tau(W)$ has a unique decomposition into maximal triangulated pieces and edges in the polygon of $\tau(W)$.
 We call this a \emph{maximal decomposition}.
@@
 
-For an admissible Wilson loop diagram $W$, every triangulated piece $t$ of $\tau(W)$ corresponds to a subdiagram of $W$ obtained by taking the set of propagators $P$ corresponding to edges of $t$ and then taking the subdiagram $(P, V(P))$.
+For a weakly admissible Wilson loop diagram $W$, every triangulated piece $t$ of $\tau(W)$ corresponds to a subdiagram of $W$ obtained by taking the set of propagators $P$ corresponding to edges of $t$ and then taking the subdiagram $(P, V(P))$.
 Conversely, given a subdiagram $(P, V(P))$ of $W$ we can obtain a subgraph of $\tau(W)$, called $t$, as follows:
@@
 \begin{lem}\label{lem triang to exact}
-  Let $W$ be an admissible Wilson loop diagram and $\tau(W)$ its polygon dissection.
+  Let $W$ be a weakly admissible Wilson loop diagram and $\tau(W)$ its polygon dissection.
 The triangulated pieces of $\tau(W)$ correspond to the exact subdiagrams of $W$, via the correspondence described above.
@@
 
-Since $W$ is admissible, by Lemma \ref{tausimpleplanarlem} $\tau(W)$ is a simple graph.
+Since $W$ is weakly admissible, by Lemma \ref{tausimpleplanarlem} $\tau(W)$ is a simple graph.
 Let $t$ be a triangulated piece of the decomposition of $\tau(W)$ given in Lemma \ref{decompositionlem}; note that $t$ cannot be equal to $\tau(W)$ by the definition of admissible diagrams.
@@
 \begin{cor} \label{uniqueproppartitioncor}
-Any admissible Wilson loop diagram $W = (\cP, [n])$ can be uniquely decomposed into maximal exact subdiagrams.
+Any weakly admissible Wilson loop diagram $W = (\cP, [n])$ can be uniquely decomposed into maximal exact subdiagrams.
 These maximal subdiagrams partition $\cP$ and correspond to the maximal triangulated pieces of $\tau(W)$.
@@
 \begin{cor} \label{classifyflats}
-  If $F$ is a flat of an admissible Wilson loop diagram, it can be written as the disjoint union of a cyclic propagator flat $C$ and an independent set $S$: \bas F =C \sqcup S \eas where $C$ the union of all circuits in $F$.
+  If $F$ is a flat of a weakly admissible Wilson loop diagram, it can be written as the disjoint union of a cyclic propagator flat $C$ and an independent set $S$: \bas F =C \sqcup S \eas where $C$ the union of all circuits in $F$.
 \end{cor}
@@
 
-\begin{lem} \label{contractsubdiaglem} \cite[Theorem 3.33]{wilsonloop} 
-Let $W = (\cP, [n])$ be an admissible Wilson loop diagram and $P \subseteq \cP$.
+\begin{lem} \label{contractsubdiaglem} \cite[Corollary 3.33]{wilsonloop} 
+Let $W = (\cP, [n])$ be a Wilson loop diagram and $P \subseteq \cP$.
 If the set $V(P)^c$ has rank $|P^c|$, then the matroid defined by the subdiagram $(P, V(P))$ is equal to the contraction $M(W)/V(P)^c$.
@@
 \begin{thm} \label{exactuniformthm}
-Let $W':= (P, V(P))$ be a subdiagram of an admissible Wilson loop diagram $W= (\cP, [n])$. Then $W'$ is an exact subdiagram if and only if $M(W')$ is a uniform matroid of rank $|P|$.
+Let $W':= (P, V(P))$ be a subdiagram of a weakly admissible Wilson loop diagram $W= (\cP, [n])$. Then $W'$ is an exact subdiagram if and only if $M(W')$ is a uniform matroid of rank $|P|$.
 \end{thm}
@@
 \begin{cor}\label{number of equiv diagrams}
-  Let $W$ be an admissible Wilson loop diagram where the sizes of the supports of the nontrivial maximal exact subdiagrams are $n_1, n_2, \ldots, n_j$.
-Then the number of admissible Wilson loop diagrams equivalent to $W$ (including $W$ itself) is
+  Let $W$ be a weakly admissible Wilson loop diagram where the sizes of the supports of the nontrivial maximal exact subdiagrams are $n_1, n_2, \ldots, n_j$.
+Then the number of weakly admissible Wilson loop diagrams equivalent to $W$ (including $W$ itself) is \todo{Karen: This really is weakly admissible, correct?}
   \[

### 2020-10-05 GWLDCI.tex
most of the comments from report Y

@@
 The second paper \cite{generalcombinatoricsII} in this series identifies precisely which positroid cell is associated to a given Wilson loop diagram, by giving an algorithm for passing from a Wilson loop diagram to the Grassmann necklace of the associated positroid cell.
-In this manner we give a direct path from Wilson loop diagram to positroid cell, circumventing the painstaking process of examining sets of bases.
+In this manner we give a direct path from a Wilson loop diagram to a positroid cell, circumventing the painstaking process of examining sets of bases.
 With this identification in hand, we also prove that any Wilson loop diagram with $k$ propagators corresponds to a $3k$ dimensional positroid cell, and characterize the volume forms that Wilson loop diagrams associate to each positroid cell.
@@
 As noted above, Agarwala and Marin-Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that are realized as an element of the positive Grassmannian $\Gr(k,n)$ \cite{wilsonloop}.
-In separate papers with Fryer and with Marcott, this work was extended to study these Feynman integrals in terms of positroid cells and the positive Grassmannians \cite{casestudy, non-orientable}.
+In separate papers with Fryer and with Marcott, this work was extended to study these Feynman integrals in terms of positroid cells and the positive Grassmannian \cite{casestudy, non-orientable}.
 Others have tried different approaches to define a geometric space associated to these integrals in a manner similar to the Amplituhedron \cite{Amplituhedronsquared, HeslopStewart}.
@@
 More generally, it has been shown that the spaces defined by the Amplituhedron and by Wilson loop diagrams are not the same \cite{Amplituhedronsquared}.
-In fact, it is in some ways more natural to consider Deodhar cells of $\mathbb{G}(k, n+1)$ for Wilson loop diagrams; in this case, one gets that the manifold represented by the diagrams is not orientable \cite{non-orientable}.
+In fact, it is in some ways more natural to consider Deodhar cells of $\mathbb{G}(k, n+1)$ for Wilson loop diagrams.
+In this case, one gets that the manifold represented by the diagrams is not orientable \cite{non-orientable}.
 
@@
 Our main results are as follows.
-We first show that two Wilson loop diagrams define the same positroid if and only if they only differ by exact subdiagrams (Theorem~\ref{same matroid iff equiv}); equivalently, this says that the map from Wilson loop diagrams to positroid cells is one-to-one exactly on the subset of diagrams with no non-trivial exact subdiagrams.
+We first show that two Wilson loop diagrams define the same positroid if and only if they only differ by exact subdiagrams (Theorem~\ref{same matroid iff equiv}).
+Equivalently, this says that the map from Wilson loop diagrams to positroid cells is one-to-one exactly on the subset of diagrams with no non-trivial exact subdiagrams.
 We count the total number of Wilson loop diagrams associated to a positroid cell (Corollary~\ref{number of equiv diagrams}).
@@
 A Wilson loop diagram can also be represented visually, which provides useful intuition for many of the results that follow.
-We depict the diagram $(\cP,V)$ as a circle with marked points, called {\em vertices}; these vertices are labeled by $V$ (preserving the cyclic ordering).
+We depict the diagram $(\cP,V)$ as a circle with marked points, called {\em vertices}.
+These vertices are labeled by $V$ (preserving the cyclic ordering).
 The arcs between consecutive vertices are called {\em edges}.
-There are also $k$ wavy lines in the interior of the diagram, each connecting a pair of edges; these depict the propagators.
+There are also $k$ wavy lines in the interior of the diagram, each connecting a pair of edges.
+These depict the propagators.
 Specifically, a propagator $p =(i,j)$ has one endpoint on the edge joining vertices $i$ and $i+1$ and another endpoint on the edge joining $j$ and $j+1$, where $i+1$ and $j+1$ denote the successor of $i$ and $j$ respectively in the cyclic order on $V$.
@@
 For the propagator $p = (5, 8)$, we have $V(p) = \{5,6,8,1\}$ and $F(p) = \{6, 7,8\}$: the vertices 1 and 5 are excluded from $F(p)$ since they support other propagators as well, and 7 is included (despite not being in the support of $p$) since it supports no propagators at all.
-Finally, the subdiagram $(\{(2, 4), (1, 4)\}, \{1, 2, 3, 4, 5\})$ is an example of an exact subdiagram; in fact it is the only non-trivial exact subdiagram in $W$.
+Finally, the subdiagram $(\{(2, 4), (1, 4)\}, \{1, 2, 3, 4, 5\})$ is an example of an exact subdiagram.
+In fact it is the only non-trivial exact subdiagram in $W$.
 \end{eg}
@@
 The matrix $C(W)$ allows us to associate a matroid to each Wilson loop diagram.
-We first give a quick summary of the matroid terminology that we will need; it is not intended as a comprehensive introduction to matroids and the interested reader is referred to \cite{OxleyMatroidBook}
-
-A {\em matroid} $M = (E,\cB)$ consists of a finite ground set $E$ and a non-empty family $\cB$ of subsets of $E$, such that elements of $\cB$ satisfy the {\em basis exchange property}: for any distinct $B_1,B_2 \in \cB$ and any $a \in B_1 \setminus B_2$, there exists some $b \in B_2 \setminus B_1$ such that $(B_1 \setminus \{a\})\cup \{b\} \in \cB$ as well.
+We first give a quick summary of the matroid terminology that we will need.
+It is not intended as a comprehensive introduction to matroids and the interested reader is referred to \cite{OxleyMatroidBook}.
+
+A {\em matroid} $M = (E,\cB)$ consists of a finite ground set $E$ and a non-empty family $\cB$ of subsets of $E$, such that elements of $\cB$ satisfy the {\em basis exchange property}: for any distinct $B_1,B_2 \in \cB$ and any $a \in B_1 \setminus B_2$, there exists some $b \in B_2 \setminus B_1$ such that $(B_1 \setminus \{a\})\cup \{b\} \in \cB$.
 The elements of $\cB$ are called the {\em bases} of the matroid.
@@
 Unsurprisingly, a {\em cyclic flat} is a set which is both a flat and a cycle.
-The set of circuits in a matroid uniquely defines that matroid, as does the set of flats; thus one could specify a matroid by listing either its independent sets, its bases, its circuits, or its flats.
+The set of circuits in a matroid uniquely defines that matroid, as does the set of flats.
+Thus one could specify a matroid by listing either its independent sets, its bases, its circuits, or its flats.
 
@@
 \begin{proof}
-The first part of (1) is \cite[Equation (9)]{wilsonloop} and surrounding discussion, and the second part is standard matroid theory.
-(2) is \cite[Lemma 3.27]{wilsonloop}.
-(3) is a direct consequence of \cite[Lemma 3.20]{wilsonloop} and the fact that $F(P_1)^c = V(P_1^c)$, and (5) is given in \cite[Lemma 3.28]{wilsonloop}.
-
-To prove (4), we need to show that $F(P)$ is maximally dependent.
+The first part of item 1 is \cite[Equation (9)]{wilsonloop} and surrounding discussion, and the second part is standard matroid theory.
+Item 2 is \cite[Lemma 3.27]{wilsonloop}.
+Item 3 is a direct consequence of \cite[Lemma 3.20]{wilsonloop} and the fact that $F(P_1)^c = V(P_1^c)$, and item 5 is given in \cite[Lemma 3.28]{wilsonloop}.
+
+To prove item 4, we need to show that $F(P)$ is maximally dependent.
 If $F(P) = [n]$ then this is automatic, so suppose not and let $v \in [n] \setminus F(P)$.
@@
 \begin{rmk}
-By point (4) of Lemma~\ref{lem facts about WLD matroids}, the set $F(\emptyset)$ of non-supporting vertices in $W$ is a flat; indeed, it is the unique flat of rank 0 in $M(W)$.
+By item 4 of Lemma~\ref{lem facts about WLD matroids}, the set $F(\emptyset)$ of non-supporting vertices in $W$ is a flat.
+Indeed, it is the unique flat of rank 0 in $M(W)$.
 Every element of $F(\emptyset)$ defines a circuit of size 1, and all other circuits of $M(W)$ must contain at least two elements.
@@
 
-In this section we develop this analysis further, showing the converse of this result from loc.
-cit.
-(see Theorem \ref{same matroid iff equiv}).
+In this section we develop this analysis further, showing the converse of this result from \cite{wilsonloop} (see Theorem \ref{same matroid iff equiv}).
 We also enumerate the number of diagrams that map to a particular matroid in Corollary \ref{number of equiv diagrams}.
-To do this, we establish a connection between Wilson loop diagrams and polygon dissections in subsection \ref{sec: polygon partitions}, and uncover some matroidal properties of exact subdiagrams in subsection \ref{sec: exact diagram matroidal props}.
+To do this, we establish a connection between Wilson loop diagrams and polygon dissections in Subsection \ref{sec: polygon partitions}, and uncover some matroidal properties of exact subdiagrams in Subsection \ref{sec: exact diagram matroidal props}.
 This includes the fact that exact subdiagrams correspond to uniform matroids (Theorem \ref{exactuniformthm}), and that the associated matroid of an exact subdiagram can be written as a contraction by the complementary propagator flat (Theorem \ref{exact diagrams contractions}).
@@
 Connecting consecutive vertices gives a graph theoretic cycle called the polygon of $\tau(W)$.
-  \item Each propagator of $W$ defines a diagonal edge of $\tau(W)$; specifically,  a propagator $(i,j) \in \cP$ defines a diagonal connecting the vertices $i$ and $j$ in $\tau(W)$.
+  \item Each propagator of $W$ defines a diagonal edge of $\tau(W)$.  Specifically,  a propagator $(i,j) \in \cP$ defines a diagonal connecting the vertices $i$ and $j$ in $\tau(W)$.
   \end{itemize}
@@
   Let $W$ be a weakly admissible Wilson loop diagram and $\tau(W)$ its polygon dissection.
-A \emph{triangulated piece} of $\tau(W)$ is a 2-connected subgraph of $\tau(W)$ which is a triangulation.
+A \emph{triangulated piece} of $\tau(W)$ is a connected, bridgeless subgraph of $\tau(W)$ which is a triangulation.
 We will take the convention that a subgraph consisting of a single diagonal edge is called a \emph{trivial} triangulated piece.
@@
 \begin{dfn}
- A {\em decomposition} of a polygon dissection $\tau(W)$ is a set of 2-connected induced subgraphs of $\tau(W)$ which partition the edges of $\tau(W)$.  
+ A {\em decomposition} of a polygon dissection $\tau(W)$ is a set of bridgeless, connected, induced subgraphs of $\tau(W)$ which partition the edges of $\tau(W)$.  
 \end{dfn}
@@
 If such a triangulation has $n$ vertices then it has $n$ edges on the polygon (that is, on the outer face) and $n-3$ edges which are not.
-No planar simple graph with the same vertices and the same outer face can have more edges than a triangulation, and every such simple graph with $n-3$ edges off the outer face is a triangulation.
+No planar simple graph with the same vertices and the same outer face can have more edges than a triangulation, and every such simple graph with $n-3$ edges off the outer face is a triangulation.\todo{Referee Y wants a ref for these standard things.}
 
 Since $W$ is weakly admissible, by Lemma \ref{tausimpleplanarlem} $\tau(W)$ is a simple graph.
-Let $t$ be a triangulated piece of the decomposition of $\tau(W)$ given in Lemma \ref{decompositionlem}; note that $t$ cannot be equal to $\tau(W)$ by the definition of admissible diagrams.
+Let $t$ be a triangulated piece of the decomposition of $\tau(W)$ given in Lemma \ref{decompositionlem}.
+Note that $t$ cannot be equal to $\tau(W)$ by the definition of admissible diagrams.
 
@@
 
-Each of these $m-3+j$ edges corresponds to a propagator in $W$; call this set of propagators $P$.
+Each of these $m-3+j$ edges corresponds to a propagator in $W$.
+Call this set of propagators $P$.
 Next we count the size of $V(P)$.
@@
 Now suppose there exists some $w \in  F(\Prop(C)) \setminus C$.
-Let $B$ be an independent subset of $C$ of maximal rank; we first show that $B \cup \{w\}$ is a dependent set in $M(W)$.
+Let $B$ be an independent subset of $C$ of maximal rank.
+We first show that $B \cup \{w\}$ is a dependent set in $M(W)$.
 By Lemma \ref{lem facts about WLD matroids}, we have
 \begin{equation}\label{eq:equality in lem decompose flat} |\Prop(C)| = \rk(C) = |B| = \rk(B) .\end{equation}
-Note that $\rk(B) \leq |\Prop(B)|$, and $B \subseteq C$ implies that $\Prop(B) \subseteq \Prop(C)$; combining these facts with equation \eqref{eq:equality in lem decompose flat}, it follows that $\Prop(B) = \Prop(C)$.
+Note that $\rk(B) \leq |\Prop(B)|$, and $B \subseteq C$ implies that $\Prop(B) \subseteq \Prop(C)$.
+Combining these facts with equation \eqref{eq:equality in lem decompose flat}, it follows that $\Prop(B) = \Prop(C)$.
 Combining this with the fact that $w \in F(\Prop(C))$, we have $\Prop(B\cup \{w\}) \subseteq \Prop(B)$.
@@
 
-Now suppose that $F(\emptyset) = \emptyset$; we must show that $F\setminus C$ is a flat.
+Now suppose that $F(\emptyset) = \emptyset$.
+We must show that $F\setminus C$ is a flat.
 For any $e \not\in F$ we certainly have $\rk((F\setminus C)\cup\{e\}) = \rk(F\setminus C) +1$, since $F$ is a flat.
@@
 
-We know from Lemma~\ref{lem facts about WLD matroids} that $F(P^c)$ is always a flat, so for part (1) we only need to show that $F(P^c)$ is dependent.
+We know from Lemma~\ref{lem facts about WLD matroids} that $F(P^c)$ is always a flat, so for item 1 we only need to show that $F(P^c)$ is dependent.
 
@@
 
-For part (2), suppose that $(P, V(P))$ is a maximal exact subdiagram of $W$. By Lemma \ref{lem decompose flat}(1) and Corollary \ref{classifyflats} we can decompose $F(P^c)$ as
+For item 2, suppose that $(P, V(P))$ is a maximal exact subdiagram of $W$. By Lemma \ref{lem decompose flat} item 1 and Corollary \ref{classifyflats} we can decompose $F(P^c)$ as
 \begin{equation}\label{eq decompose F}V(P)^c = F(P^c) = C \sqcup S = F(\Prop(C)) \sqcup S,\end{equation}
@@
 $F(P^c)$ is a cyclic flat.
-Note that $C$ must be non-empty since $F(P^c)$ is non-empty and dependent (by part (1)).
+Note that $C$ must be non-empty since $F(P^c)$ is non-empty and dependent (by item 1).
 
 By similar arguments to Lemma~\ref{lem decompose flat}, the fact that $S$ is independent and that $C$ is the union of all circuits in $F(P^c)$ implies that every element of $S$ is independent of $C$.
-Further, we know that $\rk(C) = |\Prop(C)|$ from Lemma \ref{lem facts about WLD matroids}(2), and $\rk(S) = |S|$ from Lemma \ref{lem facts about WLD matroids}(1) and the independence of $S$.
+Further, we know that $\rk(C) = |\Prop(C)|$ from Lemma \ref{lem facts about WLD matroids}(2), and $\rk(S) = |S|$ from Lemma \ref{lem facts about WLD matroids} item 1 and the independence of $S$.
 Combining these gives
 \ba \rk\big(F(P^c)\big) = \rk(C) + \rk(S)  = |\Prop(C)| + |S| \leq |\Prop(F(P^c))|\;,\label{rank of comp flat} \ea 
-where the inequality follows from the bound on ranks of vertex sets in Lemma \ref{lem facts about WLD matroids}(1). For ease of future notation, write $Q = \Prop(C)^c$.
+where the inequality follows from the bound on ranks of vertex sets in Lemma \ref{lem facts about WLD matroids} item 1. For ease of future notation, write $Q = \Prop(C)^c$.
 
@@
 Recalling that $Q = \Prop(C)^c$, we finally obtain $\Prop (C) = P^c$ and hence $S = \emptyset$.
-This completes the proof of (2).
+This completes the proof of item 2.
 %\begin{comment}For part (2), suppose that $(P, V(P))$ is a maximal exact subdiagram. By Lemma \ref{lem decompose flat} (1) and Corollary \ref{classifyflats} we can decompose $F(P^c)$ as
@@
 
-To see point (3), first note that when $(P,V(P))$ is maximal exact, part (2) of this lemma combined with Lemma \ref{lem facts about WLD matroids} gives that
+For item 3, first note that when $(P,V(P))$ is maximal exact, item 2 of this Lemma combined with Lemma \ref{lem facts about WLD matroids} gives that
 \bas\rk(F(P^c)) = |\Prop(F(P^c))| = |P^c|.\eas
@@
 
-It remains to show that $S$ is an independent set in the subdiagram $(P, V(P))$, so for a contradiction suppose otherwise.
+It remains to show that $S$ is an independent set in the subdiagram $(P, V(P))$.
+By way of contradiction suppose otherwise.
 Then by Theorem \ref{thm WLD defines matroid} there is a subset $U \subseteq S$ such that $|\Prop(U)| < |U|$.
@@
 \begin{proof}
-It follows directly from the definitions that a matroid of rank $r$ is uniform if and only if all circuits have rank $r$; we therefore focus on the circuits of $M(W')$.
+It follows directly from the definitions that a matroid of rank $r$ is uniform if and only if all circuits have rank $r$. We therefore focus on the circuits of $M(W')$.
 
@@
 Observe that $\Prop_{W'}(C)\subseteq P$ by definition, where the subscript to $\Prop$ specifies the diagram we are working in.
-By Lemma \ref{lem facts about WLD matroids} we know that ${|\Prop_{W'}(C)| = m}$; thus the set $P \setminus \Prop_{W'}(C)$ must be nonempty, and we can consider the subdiagram $W'':= (P\setminus \Prop_{W'}(C),V(P\setminus\Prop_{W'}(C))$.
+By Lemma \ref{lem facts about WLD matroids} we know that ${|\Prop_{W'}(C)| = m}$.
+Thus the set $P \setminus \Prop_{W'}(C)$ must be nonempty, and we can consider the subdiagram $W'':= (P\setminus \Prop_{W'}(C),V(P\setminus\Prop_{W'}(C))$.
 By the density condition on subdiagrams of admissible diagrams, we have
@@
 
-By Theorem \ref{exactuniformthm}, $M(R, V(R))$ and $M(R',V(R'))$ are both uniform matroids of rank $|R| = |R'|$; in particular, this means that any subset of $V(R)$ is independent in both $M(W)$ and $M(W')$.
+By Theorem \ref{exactuniformthm}, $M(R, V(R))$ and $M(R',V(R'))$ are both uniform matroids of rank $|R| = |R'|$.
+In particular, this means that any subset of $V(R)$ is independent in both $M(W)$ and $M(W')$.
 
@@
 
-By Lemma~\ref{maxexactcomplementrank} we know that $\rk(F) = |P^c|$; however, by Lemma~\ref{lem facts about WLD matroids} we also know that the rank of a cycle is equal to the number of propagators supported on that cycle, so $\rk(F) = |\Prop_{W'}(F)| = |Q^c|$ as well.
+By Lemma~\ref{maxexactcomplementrank} we know that $\rk(F) = |P^c|$.
+However, by Lemma~\ref{lem facts about WLD matroids} we also know that the rank of a cycle is equal to the number of propagators supported on that cycle, so $\rk(F) = |\Prop_{W'}(F)| = |Q^c|$ as well.
 Since $(P,V(P))$ is exact and we have shown that $V(P) = V(Q)$ and $|P| = |Q|$, it follows that $|V(Q)| = |Q| + 3$, i.e.
@@
 A \emph{face} of a polytope is the intersection of the polytope with any hyperplane for which the entire polytope is in one of the closed half-spaces defined by the hyperplane.
-The polytope itself is also considered a face; in the case that the polytope is of full dimension, this definition can be unified by considering linear equalities (including the trivial one) in place of hyperplanes and the corresponding linear inequalities in place of the half-spaces defined by the hyperplane (see Chapter 2 of \cite{Ziegler}).
+The polytope itself is also considered a face.
+In the case that the polytope is of full dimension, this definition can be unified by considering linear equalities (including the trivial one) in place of hyperplanes and the corresponding linear inequalities in place of the half-spaces defined by the hyperplane (see Chapter 2 of \cite{Ziegler}).
 
@@
 
-As with many of the interesting and well-studied polytopes in combinatorics, the associahedron can be characterized in many different ways; here is one definition.
+As with many of the interesting and well-studied polytopes in combinatorics, the associahedron can be characterized in many different ways. Here is one definition.
 
@@
 It turns out that this defines a class of combinatorially equivalent polytopes, which can be proved by giving a realization.
-There are many interesting realizations of the associahedron \cite{CSZinequivalent}; the following realization will be the one that we use.
+There are many interesting realizations of the associahedron \cite{CSZinequivalent}.
+The following realization will be the one that we use.
 
@@
 For each $t\in T$, define $s_t$ to be the point in $\mathbb{R}^n$ whose $i$th coordinate is the sum of the areas of all triangles of $t$ which are incident to $x_i$.
-Let $A_n$ be the convex hull of the $s_t$; then $A_n$ is a realization of the $n-1$ associahedron (\cite[Example 9.11]{Ziegler}).
+Let $A_n$ be the convex hull of the $s_t$.
+Then $A_n$ is a realization of the $n-1$ associahedron (\cite[Example 9.11]{Ziegler}).
 \end{dfn}
@@
 dimension 0 faces (vertices) in $A_n$.
-All of these are equivalent (as Wilson loop diagrams) in the sense that they are only retriangulations away from each other; meanwhile, as noted above, all vertices of $A_n$ are parallel to each other.
+All of these are equivalent (as Wilson loop diagrams) in the sense that they are only retriangulations away from each other.
+Meanwhile, as noted above, all vertices of $A_n$ are parallel to each other.
 It will be convenient in what follows to include these diagrams, but the results are easily modified to remove them if needed: Propositions~\ref{prop easy way} and \ref{prop hard way} would be identical if we replaced ``weakly admissible'' by ``admissible'', while Theorem~\ref{thm:count inequiv diagrams} could be changed to consider only admissible diagrams by subtracting 1 from the number of non-parallel faces in order to account for the missing dimension 0 faces.
@@
 Suppose that $V_{>3}(D_1) = V_{>3}(D_2)$, but that the $D_1$ and $D_2$ do not have the same set of non-triangle faces.
-Then there are four vertices $x_i$, $x_j$, $x_k$, $x_l$ satisfying the following conditions:\begin{enumerate} \item In either $D_1$ or $D_2$ all four vertices are on the same non-triangle face; \item In the other dissection, there is a diagonal of the dissection such that exactly one of $\{x_i, x_j, x_k, x_l\}$ lies on one side of the diagonal (so the others are either end points of this diagonal or strictly on the other side).
+Then there are four vertices $x_i$, $x_j$, $x_k$, $x_l$ satisfying the following conditions:\begin{enumerate} \item In either $D_1$ or $D_2$ all four vertices are on the same non-triangle face.
+\item In the other dissection, there is a diagonal of the dissection such that exactly one of $\{x_i, x_j, x_k, x_l\}$ lies on one side of the diagonal (so the others are either end points of this diagonal or strictly on the other side).
 \end{enumerate}
@@
 Assume for a contradiction that no quadrilateral as in the statement exists, and let $d$ be a diagonal in $D_1$ crossing the unique non-triangle face $f$ of $D_2$.
-Then $f$ must have two vertices strictly on each side of $d$; we name the vertices on one side of $d$ as $x_i$ and $x_j$, and those on the other side as $x_k$, $x_l$ (and in that order; see Figure~\ref{inductive_step}).
+Then $f$ must have two vertices strictly on each side of $d$.
+We name the vertices on one side of $d$ as $x_i$ and $x_j$, and those on the other side as $x_k$, $x_l$ (and in that order; see Figure~\ref{inductive_step}).
 Let $g$ be the face in $D_1$ that is incident to $d$ on the $x_i, x_j$ side of $d$.
@@
 There are now two possibilities for $g$: either it has one vertex in the interval $(x_j, x_k)$ and the rest in $(x_l, x_i)$ (or vice versa), or it has two vertices in $(x_j, x_k)$ and two in $(x_l, x_i)$.
-In the first case, $g$ must be a triangle since if $g$ was a quadrilateral then its four vertices provide the desired configuration (with the edge of $f$ that connects $x_j$ and $x_k$ providing the desired diagonal); in the second case, $g$ has four vertices and is therefore a quadrilateral.
+In the first case, $g$ must be a triangle since if $g$ was a quadrilateral then its four vertices provide the desired configuration (with the edge of $f$ that connects $x_j$ and $x_k$ providing the desired diagonal).
+In the second case, $g$ has four vertices and is therefore a quadrilateral.
 
@@
     \[
-    \omega^+_d(i) = \begin{cases} \text{dist}(x_i, d) & \text{if $x$ is on the positive side of $d$}\\ 0 & \text{otherwise} \end{cases}
+    \omega^+_d(i) = \begin{cases} \text{dist}(x_i, d) & \text{if $x$ is on the positive side of $d$,}\\ 0 & \text{otherwise.} \end{cases}
     \]
-    We have from \cite{CSZinequivalent} that $\omega^+_d$ is a normal vector for any face with $d$ as a diagonal; however we can also check this fact in a completely elementary way using the shoelace formula for the area of a triangle.
+    We have from \cite{CSZinequivalent} that $\omega^+_d$ is a normal vector for any face with $d$ as a diagonal.
+However we can also check this fact in a completely elementary way using the shoelace formula for the area of a triangle.
 The shoelace formula says that if $(x_1, y_1), (x_2, y_2), (x_3, y_3)$ are the coordinates of the corners of a triangle in counterclockwise order then the area of the triangle is \[\textstyle\frac{1}{2}(x_1y_2 - x_1y_3 + x_2y_3 - x_2y_1 + x_3y_1 - x_3y_2).\]
@@
 \end{thm}
+
+\todo{Referee Y wants a concluding sentence or paragraph, perhaps pointing towards paper 2, or perhaps an acknowledgements section}
+
 \bibliographystyle{abbrv}

### 2020-10-18 GWLDCI.tex
addressed reference comments

@@
 Comparing this to Theorem \ref{thm:WLDmatroid}, we see that $M(W)$ is also the matroid realized by $C(W)$.
-As mentioned above, Theorem [3.38] of \cite{wilsonloops} shows that if $W$ is weakly admissible, the matroid $M(W)$ is a positroid.
-Furthermore, Theorem 5.1 \cite{basisshapeloci} shows that the space parametrized by the matrices $C(W)$ matches the positroid cells defined by $M(W)$, up to a set of measure $0$.
+As mentioned above, Theorem [3.38] of \cite{wilsonloop} shows that if $W$ is weakly admissible, the matroid $M(W)$ is a positroid.
+Furthermore, Theorem 5.1 \cite{WLDdim} shows that the space parametrized by the matrices $C(W)$ matches the positroid cells defined by $M(W)$, up to a set of measure $0$.
 Note, this does not imply that every possible specializaton of $C(W)$ to a real valued matrix leads to a postroid, only that the set of values that do define a positroid is volume filling in $\R^{4k}$.
-\todo{What is [6] referred to by reviewer M?}
 
@@
 Item 2 is \cite[Lemma 3.27]{wilsonloop}.
-Item 3 is a direct consequence of \cite[Lemma 3.20]{wilsonloop} and the fact that $F(P_1)^c = V(P_1^c)$, and item 5 is given in \cite[Lemma 3.28]{wilsonloop}.
+Item 3 is a direct consequence of \cite[Lemma 3.20]{wilsonloop}\sanote{ This is the right reference in both arXiv and CMP versions.
+Don't know what to do?} and the fact that $F(P_1)^c = V(P_1^c)$, and item 5 is given in \cite[Lemma 3.28]{wilsonloop}.
 
@@
 
-In \cite{wilsonloop}, Agarwala and Marin-Amat show that certain subdiagrams of $W$ can be realized as contractions of $M(W)$:
+In \cite{wilsonloop}, Agarwala and Marin-Amat show that certain subdiagrams of $W$ can be realized as contractions of $M(W)$, \hlfix{which we rephrase using the notation of this paper}{citation was correct, but notation was different.
+Karen: is this clearer?}:
 
@@
 Let $W = (\cP, [n])$ be a Wilson loop diagram and $P \subseteq \cP$.
-If the set $V(P)^c$ has rank $|P^c|$, then the matroid defined by the subdiagram $(P, V(P))$ is equal to the contraction $M(W)/V(P)^c$.
+The set $V(P)^c$ has rank $|P^c|$ (i.e.
+$F(P^c)$ is a propagator flat of maximal rank), if and only if the matroid defined by the subdiagram $(P, V(P))$ is equal to the contraction $M(W)/V(P)^c$.
 \end{lem}

### 2020-10-18 GWLDCII.tex
addressed paper 2 report Y

@@
 
+It is worth noting at this point that the combinatorics of the Wilson loop diagrams are different from the combinatorics of the Amplituhedron, just as the the volume forms associated to the BCFW diagrams are different from those associated to the Wilson Loop diagrams.
+For instance, the BCFW are most readily related to the geometry of a postive Grassmanian via plabic graphs.
+Meanwhile, the Wilson loop diagrams correspond to matrices with variable valued entries (see section \ref{section WLD background}) and Grassmann Necklaces (see Algorithm \ref{alg:put GN on WLD}).
+These two combinatorial representations of the positive Grassmannians have different strengths and weaknesses, and it is not possible to give a one to one translation of the combinatorial tools used for the Amplituhedron and BCFW diagrams, and the combinatorial tools used for the Wilson loop diagrams, associated matrices and Grassmann Necklaces.
+For instance, square moves and merge-expand moves give different graphical representations of the same positroid cell.
+There is no equivalent diagramatical equivalence for Wilson loop diagrams, though it has been shown (see \cite{wilsonloop, GWLDCI}) that certain classes of diagrams parametrize the same positroid cells.
+On the other hand, in order to get a parametrization of the associated positroid cell from the plabic graphs, one must assign weights to the vertices and used them to compute Pl\"{u}cker coordinates \cite[Section 11]{Postnikov}, while the Wilson loop diagrams \emph{are} a parametrization of the associated positroid.
+I.e.
+one can compute the Pl\"{u}cker coordinates directed from the associated matrices.
+\sanote{This para is in answer to 1 and 4 of report Y.
+Should it be moved (in a modified form) to the begining of section 3?
+Should it be in both places?}
+
 This paper continues this body of work by establishing concrete connections between the combinatorics of the Wilson loop diagram as determined by the physics, and the combinatorics of the associated positroid cell as identified in \cite{wilsonloop}.
@@
 \end{eg}
+
+A reader interested in studying these integrals further is invited to read \cite{casestudy, HeslopStewart, Amplituhedronsquared} in order to understand the connection to the scattering amplitude of $N=4$ SYM theory, the cancelation of spurious poles of specific instances of these integrals as well as explicit amplitude calculations.
+\sanote{I don't think I need to say more for point 2 of report Y?}
 
@@
 Marcott in \cite{WLDdim} gives a different proof of the $3|\cP|$-dimensionality of $M(W)$ which is geometric and more elegant, but it is not easy to track the effect of a particular propagator.
+It is worth noting that while the Amplituhedon is also defined by a projection of a set of $4|\cP|$ dimensional positroid cells, there is no evidence to suggest that the $3|\cP|$ dimensional cells of $\Gr(|\cP|, n)$ defiining the Wilson loop diagrams are related to the $4|\cP|$ dimensional cells defining the Amplituhedron.
+\sanote{This para adresses point 3 of report Y.
+Should there be a similar paragraph in the intro?
+Should it be moved?}
 

### 2020-10-31 GWLDCII.tex
Report C, and Report M through 16

@@
 This series lays out several results about the relationship between Wilson loop diagrams and the positroid cells that give a CW complex structure to the positive Grassmanian.
-This paper is concerned with identifying which positroid cells correspond to which Wilson loop diagrams, and how this translates to a geometric tiling of a subspace of the positive Grassmannian.
+This paper is concerned with identifying which positroid cells correspond to which Wilson loop diagrams, and how this translates to a geometric tiling of a subspace of the positive Grassmannians.
 
@@
 These integrals are calculated via holomorphic Wilson loops.
-As with the Amplituhedron, each Wilson loop represents the sum of a family of $N^kMHV$ Feynman diagrams, and adding up the corresponding sums of Feynman integrands associates a volume form to a convex space different from those in the decomposition the Amplituhedron \cite{Hodges2013}.
+As with the Amplituhedron, each Wilson loop represents the sum of a family of $N^kMHV$ Feynman diagrams, and adding up the corresponding sums of Feynman integrands associates a volume form to a convex space different from those in the decomposition the Amplituhedron \cite{CachazoSvrcekWitten, Hodges2013}.
+\hlfix{The Wilson loop diagrams discussed in this paper are, loosely speaking, dual graphs of the $N^kMHV$ diagrams.
+While the Wilson loop diagrams contain the exact same information as the $N^kMHV$ diagrams for the purposes of understanding $N=4 SYM$ theory, this dual perspective is better suited to understanding the combinatorics and geometry associated to the theory.}{added to address request (3) of report M} Therefore, we part with the notation in the physics literature, and name these dual graphs of $N^kMHV$ diagtams Wilson loop diagrams in order to emphasize the combinatorial and geometric significane of these object.
 In \cite{wilsonloop}, Agarwala and Marin-Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that can be realized as an element of $\Gr(k,n)$.
@@
 However, each individual integral has singularities which come from the factors in the denominator of the integrands.
-SYM $N=4$ is a finite theory \cite{Adamo:2011pv,Adamo:2012xe,Arkani-Hamed:2013jha}, so the
-singularities must cancel out in the sum over all diagrams, though how this works out mathematically is unclear.
+SYM $N=4$ is a finite theory.
+However at tree level, the integrals used to calculate the amplitudes of the theory have singularities upon evaluation \cite{Adamo:2011pv,Adamo:2012xe,Arkani-Hamed:2013jha}.
+These singularities are classified as spurious and physical in the literature, and the spurious poles must all cancel in the calculation of a tree level scattering amplitude,\sanote{Does this address the reviewer's concern properly?} though how this works out mathematically is unclear.
 The cancellation has been conjectured in general \cite{Hodges2013} and verified explicitly in a few cases \cite{casestudy, HeslopStewart}, but it is hard to prove in general due to the fact that the relationship between Wilson loop diagrams and $3k$-dimensional positroid cells of $\Gr(k,n)$ is neither one-to-one nor onto \cite{generalcombinatoricsI}.
@@
 We hope these results will pave the way for a general study of these poles in future.
+\sanote{cannot find where Wilson loop needs to become Wilson loop diagram (M correction 2)}
 
@@
 
-Generally speaking the propagators in a Wilson loop diagram are undirected, so $(i,j)$ and $(j,i)$ represent the same propagator.
-If we need to impose a direction on a propagator $p = (i,j)$, for example in order to consider the region ``inside'' or ``outside'' of $p$, we write $(p,<_i)$ to indicate that $p$ is directed from edge $i$ to edge $j$, and $(p,<_j)$ for the opposite direction.
+Note that as defined, the propagators in a Wilson loop diagram are undirected, so $(i,j)$ and $(j,i)$ represent the same propagator.
+However, in this manuscript, we sometimes need to impose a direction on a propagator $p = (i,j)$, for example in order to consider the region ``inside'' or ``outside'' of $p$.
+In this case, we write $(p,<_i)$ to indicate that $p$ is directed from edge $i$ to edge $j$, and $(p,<_j)$ for the opposite direction.
+\sanote{M comment 3.
+Skipped the symmetric binary bit, as I don't think it helps}
 
@@
 In particular, if $V = [n]$ then $(n,n+3)$ means the propagator connecting edges $3$ and $n$.
-This viewpoint is beneficial for us since many of our proofs rely on restricting our attention to a region of the diagram bounded by a given propagator, or to short propagators such as $(i,i+2)$, and these behave the same way regardless of whether we cross the ``first'' vertex or not.
+In particluar, many of our proofs rely on restricting our attention to a region of the diagram bounded by a given propagator, \hlfix{or to short propagators such as $(i,i+2)$}{is this parenthetical needed?
+M comment 4}.
+The regions thus defined behave the same way regardless of whether or not they contain the vertex labeled by $1$.
 However, we emphasize that this is different to the standard convention in the physics literature, where propagators are written $(i,j)$ with $1 \leq i<j \leq n$.
@@
 \begin{enumerate}
-\item For $p = (i,j) \in \cP$, let $V(p) = \{i, i+1, j, j+1\}$ denote the set of {\bf vertices supporting $p$}. For a set of propagators $P \subseteq \cP$, define 
+\item For $p = (i,j) \in \cP$, let $V(p) = \{i, i+1, j, j+1\}$ denote the set of {\bf vertices supporting} $p$. For a set of propagators $P \subseteq \cP$, define 
 \[V(P) = \bigcup_{p \in P} V(p)\]
-to be the vertex support of $P$.
+to be the {\bf vertex support} of $P$.
 \item For $U \subseteq V$, the set of {\bf propagators supported on $U$} is denoted by
 \[\Prop(U) = \{ p \in \cP\ |\ V(p) \cap U \neq \emptyset \}.\]
-Note that a propagator in $\Prop(U)$ does not need to have its entire support contained in $U$. 
+Note that a propagator in $\Prop(U)$ may not have its entire support contained in $U$. 
 \item Vertices of $W$ that do not support any propagators are called {\bf non-supporting}.
@@
 \begin{dfn}\label{admisdfn}
-A Wilson loop diagram $W = (\cP, V)$ is called {\bf admissible} if:
+A Wilson loop diagram $W = (\cP, V)$ is called {\bf admissible} if the following conditions hold:
 \begin{enumerate}
 \item $|V| \geq |\cP| + 4$.
-\item There does not exist a non-empty set of propagators $Q \subseteq \cP$ such that $|V(Q)| < |Q| + 3$.
+\item For each non-empty subset of propagators, $Q \subseteq \cP$, we have $|V(Q)|\geq |Q| + 3$.
 \item There are no crossing propagators: that is, there does not exist ${\{(i,j),(k,l)\} \subseteq \cP}$ such that $i < k < j < l$.
@@
 
-The first condition bounds the total number of propagators in the diagram, while the second limits how densely propagators can be fitted into any part of the diagram; in particular, it prohibits propagators that connect two adjacent edges and parallel propagators that start and end on the same pair of edges.
+The first condition bounds the total number of propagators in the diagram, while the second limits how densely propagators can be fitted into any part of the diagram; in particular, the second condition prohibits propagators that connect two adjacent edges.
+Note that since $\cP$ is a set, we may not have two propagators starting and ending on the same pair of edges.
 The third condition simply requires that propagators are non-crossing.
@@
 These conditions are imposed by the physical interpretation of Wilson loop diagrams (see for example \cite{Adamo:2011pv,Adamo:2012xe,wilsonloop,LipsteinMason}).
-We therefore restrict our attention in this paper to admissible Wilson loop diagrams and their subdiagrams only.
+We therefore restrict our attention in this paper to admissible Wilson loop diagrams and their subdiagrams.
 
 Note that a subdiagram $(Q,U)$ of an admissible Wilson loop diagram need not be admissible itself: it inherits conditions 2 and 3 automatically, but we could have $|U| = |Q| + 3$.
-If a Wilson loop diagrams satisfies conditions 2 and 3 of Definition~\ref{admisdfn}, we call it {\bf weakly admissible}.
+If a Wilson loop diagram satisfies conditions 2 and 3 of Definition~\ref{admisdfn}, we call it {\bf weakly admissible}.
 
@@
 a vertex).
-$C(W)$ is defined as follows:
+The matrix $C(W)$ is defined as follows:
 
@@
 
-The entries $x_{p,q}$ are non-zero real variables.
+The entries $x_{p,q}$ are nonzero real variables.
 Thus the zero entries in row $p$ correspond to the external particles that the propagator $p$ does not interact with.
@@
 By \cite{Adamo:2011pv,Adamo:2012xe,Arkani-Hamed:2013jha} this sum is finite for all sets of external particles, i.e.
-we have
 \bas \mathcal{A}_{k, n}^{tree} = \sum_{\substack{W = (\cP, [n]), \\ |\cP| = k}} I(W) <\infty. \eas
@@
 Let $\{p_1 \ldots p_r\}$ be the propagators with one end lying on edge $e$ under a counterclockwise ordering.
-That is, $p_1$ is closest to the vertex $e$, $p_i$ is positioned counterclockwise to $p_{i+1}$ and $p_r$ is the clockwise-most propagator on this edge (closest to vertex $e+1$).
 Define the polynomial
@@
 In Section \ref{sec poles}, we give a geometric meaning to the factors $\{R_e\ |\ e \in V\}$ of $R(W)$.
-Specifically: given a Grassmann necklace representation of the positroid cell $\Sigma(W)$ (see Definition~\ref{def:grassmann necklace} and Algorithm \ref{alg:put GN on WLD}), the $R_e$ are exactly the irreducible factors of the minors of $C(W)$ defined by the Grassmann necklace.
+Specifically, given a Grassmann necklace representation of the positroid cell $\Sigma(W)$ (see Definition~\ref{def:grassmann necklace} and Algorithm \ref{alg:put GN on WLD}), the $R_e$ are exactly the irreducible factors of the minors of $C(W)$ defined by the Grassmann necklace.
 In particular, the question of \emph{which} minors of $C(W)$ contribute to $R(W)$ is geometrically determined.
 
-We end this section with an example of computing $C(W)$ and $R(W)$ for a particular Wilson loop diagram $W$.
+We end this section by computing $C(W)$ and $R(W)$ for a particular Wilson loop diagram $W$.
 
@@
 \begin{dfn}\label{def:grassmann necklace}
-A {\bf Grassmann necklace} of type $(k,n)$ is a sequence $(I_1, \dots, I_n)$ of $n$ sets $I_i \in \binom{[n]}{k}$ such that for each $i \in [n]$:
+A {\bf Grassmann necklace} of type $(k,n)$ is a sequence $(I_1, \dots, I_n)$ of $n$ sets $I_i \in \binom{[n]}{k}$ such that for each $i \in [n]$ the following statements are true:
 \begin{itemize}
@@
 
-The rows and columns of a Le diagram are labelled as follows: given a Le diagram fitting inside a $k\times (n-k)$ box, arrange the numbers $1,2, \dots, n$ along its southeast border, starting from the top-right corner.
+The rows and columns of a Le diagram are labelled as follow: given a Le diagram fitting inside a $k\times (n-k)$ box, arrange the numbers $1,2, \dots, n$ along its southeast border, starting from the top-right corner.
 See Figure \ref{fig:row column numbering} for examples.
@@
 
-For each $i$, $2 \leq i \leq n$:
+For each $i$, $2 \leq i \leq n$ perform the following steps:
 \begin{itemize}
@@
 
-However, to go from the Wilson loop diagram $W$ to the positroid cell, one had to go through the matroid explicitly realized via $C(W)$, then make a list of all its non-zero $k\times k$ minors and extract the Le diagram or Grassmann necklace via the methods described in Section~\ref{sec:positroid background}.
+However, to go from the Wilson loop diagram $W$ to the positroid cell, one had to go through the matroid explicitly realized via $C(W)$, then make a list of all its nonzero $k\times k$ minors and extract the Le diagram or Grassmann necklace via the methods described in Section~\ref{sec:positroid background}.
 In \cite{casestudy}, Agarwala and Fryer apply this process in the smallest non-trivial case: admissible Wilson loop diagrams with two propagators on six vertices.
@@
 
-We will inductively construct a sequence of propagators $p_r$ and $q_r$, with $\ell(p_r) = 2$ for each $r$ and such that either:
+We will inductively construct a sequence of propagators $p_r$ and $q_r$, with $\ell(p_r) = 2$ for each $r$ and such that either of the following are true:
 \begin{itemize}
@@
 
-Informally: one starts at $i$ and moves counterclockwise around the vertices of $W$, at each step removing the clockwise-most propagator supported on that vertex (if it exists).
+Informally, one starts at $i$ and moves counterclockwise around the vertices of $W$, at each step removing the clockwise-most propagator supported on that vertex (if it exists).
 The set $I_i^W$ lists the vertices at which a propagator was deleted.
@@
 If the algorithm assigns vertex $j$ to propagator $p$ from starting vertex $i$, we say that $p$ \textbf{contributes} $j$ to $I_i^W$.
-Notationally, we represent this by allowing the $I_i^W$ symbol to represent a function as well as a set, as follows:
+Notationally, we represent this by allowing the $I_i^W$ symbol to represent a function as well as a set, as shown defined below.
 \begin{dfn}\label{def I_i as a function}
@@
 
-For $w \in [n]\backslash\{j+1,m,m+1,m+2,m+3\}$: if $w\in J_q^{V}(i)$ or $w\in J_q^{V}(i+1)$ then
+For $w \in [n]\backslash\{j+1,m,m+1,m+2,m+3\}$, if $w\in J_q^{V}(i)$ or $w\in J_q^{V}(i+1)$ then
     \[
@@
 
-Therefore, once again we can see that the $J_r^{W}(*)$ are cyclic for all $r\neq p$ in $W$.  Assembling the intervals for $p$ we have:
+Therefore, once again we can see that the $J_r^{W}(*)$ are cyclic for all $r\neq p$ in $W$.  Assembling the intervals for $p$ we have the following statements:
 \begin{itemize}
@@
 We have shown in the previous theorem that $(I_1,\dots,I_n)$ is a Grassmann necklace; it remains to check that this Grassmann necklace corresponds to the positroid $M(W)$.
-Recall from the discussion following Definition~\ref{def:grassmann necklace}, and equation \eqref{basesofmatroids} in particular, that it suffices to show:
+Recall from the discussion following Definition~\ref{def:grassmann necklace}, and equation \eqref{basesofmatroids} in particular, that it suffices to show the following points:
 \begin{itemize}
@@
 
-We will show that $Q \subseteq \mathcal{P}_{m-1}$, which will imply the theorem as follows: if $Q \subseteq \cP_{m-1}$ then we have $I_i(Q)\subseteq J$, and hence $I_i(Q) \cup \{j_m\} \subseteq J$ as well.
+We will show that $Q \subseteq \mathcal{P}_{m-1}$, which will imply the theorem by the following argument: if $Q \subseteq \cP_{m-1}$ then we have $I_i(Q)\subseteq J$, and hence $I_i(Q) \cup \{j_m\} \subseteq J$ as well.
 Since $I_i(Q) \cup \{j_m\}$ only supports the propagators in $Q$ but has $|Q|+1$ vertices, it is a dependent set in $M(W)$.
@@
 Let $V$ be $W$ with $p$ removed.
-Then we can express $I_*^W$ in terms of $I_*^V$ as follows:
+Then we can express $I_*^W$ in terms of $I_*^V$ as indicated below:
 
@@
 \begin{prop}\label{prop alg gives rad}
-  With notation as in Algorithm~\ref{alg WLD to denom via GN} we have the following:
+  With notation as in Algorithm~\ref{alg WLD to denom via GN} the following statements hold:
   \begin{enumerate}

### 2020-11-01 GWLDCII.tex
all small comments on M addressed

@@
 
-We summarize here only the subset of positroid theory that we require in this paper; the interested reader is referred to \cite{Postnikov} for more details.
+We summarize here only the portion of positroid theory that we require in this paper; the interested reader is referred to \cite{Postnikov} for more details.
 
@@
 
-For our purposes, a {\bf positroid} is\footnote{Note that matroid isomorphism allows arbitrary permutations of the ground set but positroid isomorphism allows only cyclic permutations, so the property of being a positroid is not in general preserved by matroid isomorphism.} a matroid $M$ (with ground set $[n]$ and bases $\cB \subseteq \binom{[n]}{k}$) which can be represented by an element of the positive Grassmannian $\Gr(k,n)$.
-In other words, there exists a full-rank $k\times n$ real matrix whose $k\times k$ minors are all nonnegative and such that the minor given by the columns of $J$
+For our purposes, a {\bf positroid} is\footnote{Note that matroid isomorphism allows arbitrary permutations of the ground set but positroid isomorphism allows only cyclic permutations, so the property of being a positroid is not in general preserved by matroid isomorphism.} a matroid $M$ (with ground set $[n]$ and bases set $\cB \subseteq \binom{[n]}{k}$) which can be represented by an element of the positive Grassmannian $\Gr(k,n)$.
+In other words, there exists a full-rank $k\times n$ real matrix whose $k\times k$ minors are all nonnegative and such that the minor comprised of the columns indicated by the set $J$
 is positive if and only if $J \in \cB$.
@@
 Postnikov shows in \cite{Postnikov} that the positroids of $\Gr(k,n)$ are indexed by many different collections of objects, each with their own advantages and disadvantages.
-The two most suited to our purposes are Grassmann necklaces and Le diagrams, which we introduce below.
+The two most suited to our purposes are Grassmann necklaces and Le diagrams, which we discuss.
 In order to do so, we first need some preliminary definitions.
@@
 
-\begin{thm} \label{thm WLD defines matroid} \cite[Theorem 3.6]{wilsonloop} The independent sets of the matroid $M(W)$ associated to an admissible Wilson loop diagram $W = (\cP,[n])$ and realized by $C(W)$ are exactly those subsets $V \subseteq [n]$ such that $\nexists U\subseteq V$ satisfying $|\Prop(U)| < |U|$.
+\begin{thm} \label{thm WLD defines matroid} \cite[Theorem 3.6]{wilsonloop} The independent sets of the matroid $M(W)$ associated to an admissible Wilson loop diagram $W = (\cP,[n])$ and realized by $C(W)$ are exactly those subsets $V \subseteq [n]$ such that there is no subset $U \subseteq V$ satisfying $|\Prop(U)| < |U|$.
 \end{thm}
@@
 The entry is nonzero if and only if the propagator is supported on that vertex.
-Consequently, a choice of $|J|$ nonzero entries of $C(W)$ one in each row associated to an element of $J$ and each in different columns is equivalent to an assignment of the propagators of $J$ to supporting vertices so that no two are assigned to the same vertex.
-Such an assignment of the propagators of $J$ to supporting vertices is exactly a map $f$ as described in the statement, hence proving the result.
+\hlfix{Consequently, a choice of $|J|$ nonzero entries of $C(W)$, one in each row associated to an element of $J$ and each in different columns, is equivalent to an assignment of the propagators of $J$ to supporting vertices so that no two are assigned to the same vertex.}{Added parenthetical commas according to M.23.
+better?}  Such an assignment of the propagators of $J$ to supporting vertices is exactly a map $f$ as described in the statement, hence proving the result.
 \end{proof}
@@
 
-By relating the behavior of the propagators in $W$ to the matroidal properties of $M(W)$, Agarwala and Marin-Amat also showed that $M(W)$ is in fact a positroid whenever $W$ is admissible \cite[Corollary 3.39]{wilsonloop}.
+By relating the behavior of the propagators in $W$ to the matroidal properties of $M(W)$, Agarwala and Marin-Amat also show that $M(W)$ is in fact a positroid whenever $W$ is admissible \cite[Corollary 3.39]{wilsonloop}.
+\todo{check tenses throughout (M.24)}
 
@@
 In \cite{casestudy}, Agarwala and Fryer apply this process in the smallest non-trivial case: admissible Wilson loop diagrams with two propagators on six vertices.
-Even in this simple case, we see that the mapping from admissible Wilson loop diagram to positroid cells is neither one-to-one nor onto, and the process described above makes it almost impossible to track the relationship between the original Wilson loop diagram and the resulting positroid.
+Even in this simple case, we see that the mapping from admissible Wilson loop diagrams to positroid cells is neither one-to-one nor onto, and the process described above makes it almost impossible to track the relationship between the original Wilson loop diagram and the resulting positroid.
 
@@
 Write $(p, <_i)$ to represent the same propagator directed from $i$ to $j$.
-Then the sets of propagators {\bf inside} and {\bf outside} of $(p,<_i)$ are defined to be
+Then the sets of propagators {\bf inside} and {\bf outside}  $(p,<_i)$\todo{drop the 'of' throughout.
+Old: inside of $(p,<_i)$, New: inside $(p,<_i)$} are defined to be
 \begin{gather*}\cP_{in}(p,<_i) = \{ (k,l) \in \cP \ |\ i \leq_i k <_i l \leq_i j \}, \\
@@
 \begin{lem}\label{lem sian}
-  Let $W$ be a weakly admissible Wilson loop diagram with at least 5 vertices and in which each vertex supports at least one propagator.  Then at least one of the following two things occurs:
+  Let $W$ be a weakly admissible Wilson loop diagram with at least 5 vertices and in which each vertex supports at least one propagator.  Then at least one of the following two conditions hold:
   \vspace{-0.5em}
   \begin{enumerate}
-    \item $W$ has a propagator of length $\leq 6$ with a propagator of length 2 on one side of it and nothing else on that side.\label{item big and 2}
-    \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator ends between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
+    \item $W$ has a propagator of length at most 6 with a propagator of length 2 on one side of it and nothing else on that side.\label{item big and 2} \todo{M.28 may need to be propagated}
+    \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator has an end between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
   \end{enumerate}
@@
 
-We will inductively construct a sequence of propagators $p_r$ and $q_r$, with $\ell(p_r) = 2$ for each $r$ and such that either of the following are true:
+We will inductively construct sequences of propagators $\{p_r\}$ and $\{q_r\}$, with $\ell(p_r) = 2$ for each $r$ and such that either of the following are true:
 \begin{itemize}
@@
 Consequently, $W_r$ contains only the two propagators $q_r$ and $p_{r+1}$, yielding configuration \ref{item big and 2} from the lemma statement and again contradicting our assumption.
-Therefore this first case cannot occur.
-
-The second case is that there are at least $3$ vertices between one endpoint of $p_{r+1}$ and the nearest endpoint of $q_r$. In other words, at least one of the following four things happen:
+Therefore, this first case cannot occur.
+\todo{M.31 propagate commas after all therefores}
+
+The second case is that there are at least $3$ vertices between one endpoint of $p_{r+1}$ and the nearest endpoint of $q_r$. In other words, at least one of the following four statements are true:
 \begin{itemize} 
@@
 Since $p_{r+1}$ is not part of configuration \ref{item pair of 2s} and $W_r$ has no propagators of length 3, it follows that $\ell(t) \geq 4$.
-If $q_r$ and $p_{r+1}$ were on different sides of $t$ then this would contradict the minimality of $q_r$.
+If $q_r$ and $p_{r+1}$ were on different sides of $t$, this would contradict the minimality of $q_r$.
 Therefore we can orient $t$ so that all previous $q_i$ and $p_i$ belong to $\cP_{out}(t)$, and set $q_{r+1} = t$ to continue the induction.
 
-The overall result then follows by induction.
+The overall result follows by induction. \todo{M.32 find and drop unnecessary 'then's}
 \end{proof}
@@
 
-In this section, we give an algorithm for passing directly from the Wilson loop diagrams to its Grassmann necklace.
-This not only greatly simplifies the previously known process to obtain a positroid cell from a Wilson loop diagram, but will also allow us to relate the behavior of the positroid $M(W)$ directly to the configuration of propagators in $W$.
-In Section~\ref{sec poles} we use these results to show that the denominator $R(W)$ of the integrand associated to a Wilson loop diagram can be written in terms of the Grassmann necklace of a diagram.
+In this section, we give an algorithm for passing directly from a Wilson loop diagram to its Grassmann necklace.
+This not only greatly simplifies the previously known process to obtain a positroid cell from a Wilson loop diagram, but also allows us to relate the behavior of the positroid $M(W)$ directly to the configuration of propagators in $W$.
+In Section~\ref{sec poles} we use these results to show that the denominator $R(W)$ of the integrand associated to a Wilson loop diagram can be written in terms of the Grassmann necklace of said diagram.
 
@@
 
-\begin{dfn} \label{proporderingdfn}
+\begin{dfn} \label{proporderingdfn} \todo{M.36 wants this to be a remark. I disagree? But also note that there's nothing being defined here.}
   There is an ordering on the propagators on $W = (\cP, [n])$ defined by $I_i$. This is the ordering in which they contribute to the algorithm as it constructs $I_i$.
@@
 \begin{proof}
-Suppose for contradiction that we have $i \in [n]$ and $p \in \cP$ such that $I_i(p)$ is $<_i$-maximal in $V(p)$.
+Suppose, by way of contradiction that we have $i \in [n]$ and $p \in \cP$ such that $I_i(p)$ is $<_i$-maximal in $V(p)$.
 There are two possibilities, which are illustrated in Figure~\ref{fig:no fourth vertex}: either $p = (i-1,b)$ for some $b$ (so $i$ and $I_i(p) = i-1$ are the two ends of a single edge), or $p = (a,b)$ with $i\leq_i a <_i b$ and $I_i(p) = b+1$.
 
-In Case 1, observe that we must have another propagator $q = (c,b)$ with $c<_i b$ and $I_i(q) = b+1$, because otherwise $I_i$ would assign $p$ to $b+1$.
-Now $q$ also contributes the $<_i$-maximal vertex in its support to $I_i$ and is an instance of Case 2.
+When the firt possibility occurs, observe that we must have another propagator $q = (c,b)$ with $c<_i b$ and $I_i(q) = b+1$, because otherwise $I_i$ would assign $p$ to $b+1$.
+Now $q$ also contributes the $<_i$-maximal vertex in its support to $I_i$ and is an instance of the second possibility.
 Therefore it suffices to show that no admissible Wilson loop diagram admits the configuration illustrated in Case 2 of Figure~\ref{fig:no fourth vertex}.
@@
 
-In order for $q$ to remain unassigned until vertex $b$, there must be another propagator $r$ with an end on edge $d$ and $I_i(r) = d+1$; the only way this can occur is if $r$ is outside of $(q,<_i)$ but inside $(p,<_i)$.
+In order for $q$ to remain unassigned until the algorithm reaches vertex $b$, there must be another propagator $r$ with an end on edge $d$ and $I_i(r) = d+1$; the only way this can occur is if $r$ is outside of $(q,<_i)$ but inside $(p,<_i)$.
 But now $r$ contributes its fourth vertex to $I_i$, again contradicting the minimality of $p$.
@@
 Consider $I_{j+2}(p)$.
-Since $j+1$ is the last vertex in the $j+2$ order, $p$ can not contribute $j+1$ to $I_{j+2}$, so the fact that the intervals in the statement of the lemma are non-empty and occur in their cyclic order implies that $I_{j+2}(p)=i$.
+Since $j+1$ is the last vertex in the $j+2$ order, $p$ cannot contribute $j+1$ to $I_{j+2}$, so the fact that the intervals in the statement of the lemma are non-empty and occur in their cyclic order implies that $I_{j+2}(p)=i$.
 More generally, we know that whenever a propagator stops contributing a particular vertex, its next contribution must be its cyclically next vertex.
-This little observation is surprisingly useful, to the point that the details which appear in the proof of Lemma~\ref{vertex cyclic int lem} are never needed again: the mere fact of non-empty intervals in the correct order suffices.
+This simple observation is surprisingly useful, to the point that the details which appear in the proof of Lemma~\ref{vertex cyclic int lem} are never needed again: the mere fact of non-empty intervals in the correct order suffices.
 \end{rmk}
@@
 Let $V$ be the diagram obtained by removing the propagator $p$ from $W$ (Figure \ref{fig V diagram}).
-$V$ is guaranteed to be an admissible diagram, since it was formed by removing a propagator from a diagram that was at least weakly admissible.
+The diagram $V$ is guaranteed to be an admissible diagram, since it was formed by removing a propagator from a diagram that was at least weakly admissible.
+\todo{Make certain we don't start sentences with simbols}
 
@@
         l & \text{if } r=p \\
-        I_{w}^{V}(r) & \text{if } r\neq p
+        I_{w}^{V}(r) & \text{if } r\neq p \;.
       \end{cases} 
@@
          j & \text{if $r=p$ and $j$ is in the support of $p$}\\
-         I_{j+1}^{V}(r) & \text{if $r\neq p$ and $j$ is in the support of $p$}\\
+         I_{j+1}^{V}(r) & \text{if $r\neq p$ and $j$ is in the support of $p$} \;.
        \end{cases} 
@@
        m & \text{if $r =p$ and $j$ is not in the support of $p$} \\
-       I_{j}^{V}(r) & \text{if $r\neq p$ and $j$ is not in the support of $p$}\end{cases}
-       \] 
+       I_{j}^{V}(r) & \text{if $r\neq p$ and $j$ is not in the support of $p$}\; .\end{cases} 
+       \]  \todo{make certain that there are periods after displays that end sentences.}
 This completes the analysis of $I_j^W$. Finally, we consider what happens when we start the algorithm at vertex $j+1$. If $j+1$ is in the support of $p$ then we can argue as above to get
@@
          j+1 & \text{if $r=p$ and $j+1$ is in the support of $p$}\\
-         I_{j+2}^{V}(r) & \text{if $r\neq p$ and $j+1$ is in the support of $p$}.
+         I_{j+2}^{V}(r) & \text{if $r\neq p$ and $j+1$ is in the support of $p$}\;.
        \end{cases}
@@
       m & \text{if  $r=p$ and $j+1$ is not in the support of $p$}\\
-      I_{j+1}^{V}(r) & \text{if  $r\neq p$ and $j+1$ is not in the support of $p$}
+      I_{j+1}^{V}(r) & \text{if  $r\neq p$ and $j+1$ is not in the support of $p$} \;.
     \end{cases}
@@
     \end{gather*}
-    which are nonempty and otherwise as required.
+    which are non-empty and otherwise as required.
   \item
@@
     \end{gather*}
-    which are nonempty and otherwise as required. Recall that $d$ was defined in equation \eqref{deeqs}.
+    which are non-empty and otherwise as required. Recall that $d$ was defined in equation \eqref{deeqs}.
   \item If $m=i$ then $a=1$ or $a=2$, in the former case $l=m+2$, $j=m+3$ and $j+1$ is not in the support of $p$ so
@@
         I_{w}^{V}(r) & \text{if } r\neq p
-      \end{cases} 
+      \end{cases} \;.
     \]
@@
     m+3 & \text{if } r=p \\
-    I_{m+4}^{V}(r) & \text{if } r\neq p
+    I_{m+4}^{V}(r) & \text{if } r\neq p \; .
   \end{cases} 
@@
 \item If $m=j$ then
-\begin{gather*}J_p^{W}(m) = [m+4,e-1], \qquad  J_p^{W}(m+1) = [e,m], \\  J_p^{W}(m+2) = [m+1,m+2], \qquad  J_p^{W}(m+3) = \{m+3\},\end{gather*}
+\begin{gather*}J_p^{W}(m) = [m+4,e-1], \qquad  J_p^{W}(m+1) = [e,m], \\  J_p^{W}(m+2) = [m+1,m+2], \qquad  J_p^{W}(m+3) = \{m+3\}\;.\end{gather*}
 Recall that $e$ was defined in equation \eqref{deeqs}.
 \item If $m=j+1$ then
-\begin{gather*}J_p^{W}(m) = [m+4,m-1], \qquad J_p^{W}(m+1) = [m,m+1], \\  J_p^{W}(m+2) = \{m+2\}, \qquad  J_p^{W}(m+3) = \{m+3\},\end{gather*}
+\begin{gather*}J_p^{W}(m) = [m+4,m-1], \qquad J_p^{W}(m+1) = [m,m+1], \\  J_p^{W}(m+2) = \{m+2\}, \qquad  J_p^{W}(m+3) = \{m+3\}\;.\end{gather*}
 \item If $m=j+2$ then
-\begin{gather*}J_p^{W}(m) = [m+4,m], \qquad  J_p^{W}(m+1) = \{m+1\}, \\  J_p^{W}(m+2) = \{m+2\}, \qquad  J_p^{W}(m+3) = \{m+3\}.\end{gather*}
+\begin{gather*}J_p^{W}(m) = [m+4,m], \qquad  J_p^{W}(m+1) = \{m+1\}, \\  J_p^{W}(m+2) = \{m+2\}, \qquad  J_p^{W}(m+3) = \{m+3\}\;.\end{gather*}
 \end{itemize}
@@
 
-We are now ready to prove that Algorithm~\ref{alg:put GN on WLD} does in fact give the Grassmann necklace of the positroid associated to $W$.
+We are now ready to prove that Algorithm~\ref{alg:put GN on WLD} gives the Grassmann necklace of the positroid associated to $W$.
 We do this in two parts: Theorem~\ref{res:alg gives GN} verifies that the sets $(I_1,\dots,I_n)$ obtained from the algorithm do form a Grassmann necklace, and Theorem~\ref{res alg gives correct GN} proves that this Grassmann necklace defines the positroid $M(W)$.
@@
 
-Now let $W' = (\cP_{out}(p,<_i), [n])$, i.e. the diagram obtained from $W$ by removing both $p$ and all propagators inside of $p$. $W'$ has strictly fewer propagators than $W$ did.
+Now let $W' = (\cP_{out}(p,<_i), [n])$, i.e. the diagram obtained from $W$ by removing both $p$ and all propagators inside of $p$. The diagram $W'$ has strictly fewer propagators than $W$ did.
 
@@
 Thus we have shown that Algorithm \ref{alg:put GN on WLD} does in fact produce a Grassmann necklace. Next we check that it produces the correct one, i.e. the Grassmann necklace that defines $M(W)$. 
-\begin{thm}\label{res alg gives correct GN}
+\begin{thm}\label{res alg gives correct GN} \todo{fix mixing words and notation (M.28, M.47)} 
 The Grassmann necklace $(I_1 \ldots I_n)$ from Theorem~\ref{res:alg gives GN} is the Grassmann necklace of the positroid $M(W)$.
@@
   \begin{itemize}
-  \item $p = (i, n-1)$ for some $i$, and $p$ has no propagators inside it w.r.t the $<_i$ ordering.
+  \item $p = (i, n-1)$ for some $i$, and $p$ has no propagators inside it with regard to the $<_i$ ordering.
   \item Either the edge $i$ in $W'$ only supports $p$, or the edge $i$ in $W'$ supports exactly one other propagator $q = (j,i)$, with no other propagators inside $q$ in the $<_j$ ordering. 
@@
 
-\begin{figure}
+\begin{figure} \label{fig:twocases}
 \[
@@
 Next consider $I_n^{W}$.
-From the figure we see that in both cases we have $I_n^{W}(p) = n$; thus from vertex 1 onwards the unassigned propagators are exactly those that appear in $V$.
+From Figure \ref{fig special p} we see that in both cases we have $I_n^{W}(p) = n$; thus from vertex 1 onwards the unassigned propagators are exactly those that appear in $V$.
 Therefore the algorithm continues as in $I_1^{V}$, i.e.
@@
 Now consider $I_{n-2}^{W}$.
-If $n-2\not\in I_{n-2}^{V}$ then the vertex $n-2$ is non-supporting (see also Corollary~\ref{no coloops}.)  Thus we are in Case 1, with ${I_{n-2}^W(p) = n-2}$ and this assignment of $p$ does not affect the rest of the construction of $I_{n-2}^{V}$, so we obtain ${I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-2\}}$ as above.
+If $n-2\not\in I_{n-2}^{V}$ then the vertex $n-2$ is non-supporting (see also Corollary~\ref{no coloops}).
+Thus we are in Case 1, with ${I_{n-2}^W(p) = n-2}$ and this assignment of $p$ does not affect the rest of the construction of $I_{n-2}^{V}$, so we obtain ${I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-2\}}$ as above.
 
@@
 
-Finally, if $n-2,n-1 \in I_{n-2}^{V}$ then $I_{n-2}^W(q) = n-2$ and $I_{n-2}^W(p) = n-1$ as above, but but some other propagator must have contributed $n-1$ to $I_{n-2}^{V}$ so we cannot use the same argument as above.
-When the algorithm $I_{n-2}^W$ reaches vertex $n$, only the propagators $p$ and $q$ have contributed; thus we proceed as in the construction of $I_n^{V}$ but without propagator $q$ by Remark \ref{rmk algorithm locally same}.
+Finally, if $n-2,n-1 \in I_{n-2}^{V}$ then $I_{n-2}^W(q) = n-2$ and $I_{n-2}^W(p) = n-1$ as above, but some other propagator must have contributed $n-1$ to $I_{n-2}^{V}$ so we cannot use the same argument as above.
+\hlfix{When the algorithm $I_{n-2}^W$}{M.54 wants "When in the algorthm".
+I disagree.} reaches vertex $n$, only the propagators $p$ and $q$ have contributed; thus we proceed as in the construction of $I_n^{V}$ but without propagator $q$ by Remark \ref{rmk algorithm locally same}.
 By Lemma~\ref{vertex cyclic int lem} we know that $I_n^V(q) = n-5$, and from Remark \ref{clockwise ordering rem} we see that the only way this could occur is if $q$ was the last to contribute to $I_{n-2}^V$.
@@
 This last row contains three (new) plusses.
-All other plusses in the Le diagram of $V$ shift in a predictable manner to become plusses in the Le diagram of $W$; this is described in Lemmas~\ref{lem n and n-1} to Theorem~\ref{thm dim}.
+All other plusses in the Le diagram of $V$ shift in a predictable manner to become plusses in the Le diagram of $W$; this is described in Lemma ~\ref{lem n and n-1} to Theorem~\ref{thm dim}.
 
@@
 
-As illustrated in Figure~\ref{fig Le}, the pieces of the Le diagrams of $V$ and $W$ will be called $\mathcal{A}$ and $\mathcal{B}$ in what follows.
+As illustrated in Figure~\ref{fig Le}, the pieces of the Le diagrams of $V$ and $W$ will be called $\mathcal{A}$ and $\mathcal{B}$ respectively, in what follows.
 Explicitly, $\mathcal{B}$ is the set of columns with labels $v < n-3$ and $\mathcal{A}$ is the set of columns labeled by $n$, $n-1$ and $n-2$ in $V$.
@@
 
-We do this by applying Algorithm~\ref{alg:GN to Le}, which constructs the Le diagram associated to a Grassmann necklace, to the Grassmann necklaces of $V$ and $W$.
+We do this by applying Algorithm~\ref{alg:GN to Le}, which constructs the Le diagram associated to the Grassmann necklaces of $V$ and $W$.
 As described in Section~\ref{sec:positroid background}, if Algorithm~\ref{alg:GN to Le} places a $+$ in the box with row index $i$ and column index $j$, we say that this plus is {\bf in the $i \rightarrow j$ position}, and refer to it as {\bf the plus defined by ``the (hook) path from $i$ to $j$''}.
@@
 
-Also by Lemma~\ref{lem I} we have $I_{n-1}^{W} = I_n^{V} \cup \{n-1\}$. Recall from the proof of Lemma~\ref{lem I} that $n-3,n-2,n-1,n \not\in I_1^V$; therefore
+Also by Lemma~\ref{lem I} we have $I_{n-1}^{W} = I_n^{V} \cup \{n-1\}$.
+Recall from the proof of Lemma~\ref{lem I} that \hlfix{$n-3,n-2,n-1,n \not\in I_1^V$}{M doesn't like this notation M.58}; therefore
 \[
@@
 \begin{thm}\label{thm dim}
-Let $W = (\cP, [n])$ be an admissible Wilson loop diagram.  The number of plusses in the Le diagram of of $W$ is three times the number of propagators.
+Let $W = (\cP, [n])$ be an admissible Wilson loop diagram.  The number of plusses in the Le diagram of $W$ is three times the number of propagators.
 \end{thm}
@@
   \item The plusses in the $\mathcal{B}$ region of both Le diagrams are identical, so each plus in this region is paired with itself.
-  \item Every square containing a plus in the leftmost two columns (the $n$ and the $n-1$ columns) of $\mathcal{A}$ for $V$ also contains a plus in $W$, so these plusses are also paired with themselves.
+  \item Every square containing a plus in the leftmost two columns (the $n^{th}$ and the $(n-1)^{th}$ columns) \todo{generally turn $n$ to $n^{th}$ throughout M.60} of $\mathcal{A}$ for $V$ also contains a plus in $W$, so these plusses are also paired with themselves.
   \item The plusses in the $n-3$ column for $V$ are paired with the corresponding plusses in the $n-2$ column for $W$.
@@
 \caption{The Le diagrams for $V$ and $W$ in the setting of Theorem~\ref{thm dim}.
-The shaded regions indicate where the plusses match up perfectly from $V$ to $W$, the bold (red) plusses exist if and only if $n-2 \in I_{n-2}^V$, and the (blue) plusses in the bottom row of the $W$ diagrams are the three new plusses coming from the induction step.}\label{fig:le diagrams bijection}
+The shaded regions indicate where the plusses match up perfectly from $V$ to $W$, the bold (red) plusses exist if and only if $n-2 \in I_{n-2}^V$, and the (blue) plusses in the bottom row of the Le diagrams of $W$ diagrams are the three new plusses coming from the induction step.}\label{fig:le diagrams bijection}
 \end{figure}
@@
 
-That is, each $r_i$ is the determinant of the minor determined by the propagators (rows) that contribute different values (columns) to the $i^{th}$ element of the Grassmann necklace than they did to the $(i-1)^{th}$.
-Since each $r_i$ is simply the determinant of a particular submatrix of $C(W)$ and an ordering on the propagators has been fixed, the sign of each $r_i$ is well-defined.
+Each $r_i$ is the determinant of a minor determined by certian propagators of $W$: specifically, $p$ plays a role in defining $r_i$ if if contributs one set of values (columns) $i^{th}$ element of the Grassmann necklace and a different set to the $(i-1)^{th}$ element.
+\sanote{major rewrite of this sentence (due to M.62) Karen, look over}.
+%That is, each $r_i$ is the determinant of the minor determined by the propagators (rows) that contribute different values (columns) to the $i^{th}$ element of the Grassmann necklace than they did to the $(i-1)^{th}$.
+Since each $r_i$ is simply the determinant of a particular submatrix of $C(W)$ and an ordering on the propagators has been fixed, the sign of each $r_i$ is well defined.
 
@@
   \node at (\angle*1.5:\radius*2) {$I_5$};
-  \node[align = center] at (4*\angle:\radius*1.7) {$I_5(s) = 5,\;  I_5(q) = 6,$  \\[5pt] $I_5(p) = 7$ };
+  \node[align = center] at (4*\angle:\radius*1.7) {$I_5(s) = 5,\;  I_5(q) = 6,$  \\[5pt] $I_5(p) = 7.$ };
   \end{scope} 
@@
 \]
-The Grassmann necklace of this diagram is 
+The Grassmann necklace of this diagram \hlfix{is}{M.65 wants to replace with "consists of". I disagree} 
 \begin{gather*}I_1 = \{1,2,4\},\ I_2 = \{2,4,5\},\ I_3 = \{4,5,6\},\ I_4=\{4,5,6\},\\ I_5=\{5,6,7\},\ I_6 = \{6,7,1\},\ I_7=\{7,1,2\}. \end{gather*}  
-Figure~\ref{fig R eg} indicates indicates which vertex is contributed to $I_i$ by each propagator, for each $i \in [1,7]$.
+Figure~\ref{fig R eg} indicates which vertex is contributed to $I_i$ by each propagator, for each $i \in [1,7]$.
 
@@
 \begin{enumerate}
-    \item The nonzero entries of $C(W)$ are independent indeterminates and so every $i\times i$ minor of $C(W)$ is either homogeneous of degree $i$ or is $0$.
+    \item The nonzero entries of $C(W)$ are independent indeterminates and so every $i\times i$ minor of $C(W)$ is either $0$ or homogeneous of degree $i$.
 Thus each $\Delta_{I_i}$ and each $r_i$ is homogeneous.
@@
 $i$ contributes to $f$.  Thus this diagram can be used in place of $W$.} we may assume $i\in I_i$ and that $i$ contributes to $f$.
-Finally, we can suppose that $W$ is minimal with respect to number of propagators amongst diagrams with an irreducible factor of degree $\geq 3$.
+Finally, we can suppose that $W$ is minimal with respect to the number of propagators amongst diagrams with an irreducible factor of degree $\geq 3$.
 
@@
 No other propagators can be supported on these vertices since all other propagators are outside of $p$, and $p$ is the first propagator supported at $i$; this explains the zero block.
-Therefore $\Delta_{I_i} = \pm \det A \det C$, and both factors are nontrivial since at least one of $m$ and $m+1$ appear in $I_i$.
+Therefore $\Delta_{I_i} = \pm \det A \det C$, and both factors are nontrivial since at least one of $m$ and $m+1$ appears in $I_i$.
 
@@
 where $A$ is the submatrix indexed by the propagators in $T$ and the vertices in $I_i(T)$.
-Again two things can now happen.
+Again there are two cases to consider.
 If some vertex $j$ or larger (with respect to $<_i$) belongs to $I_i$ then $B$ and $C$ are at least one column wide, and so the block form of the matrix gives a nontrivial factorization of $\Delta_{I_i}=\pm\det A\det C$.
@@
 Now let $f$ be a quadratic factor of $\Delta_{I_i}$.
-By part (2) we know that $f$ is a $2\times 2$ minor coming from two propagators, call them $p$ and $q$, and two vertices, call them $a <_i b$.
+By part (2) we know that $f$ is a $2\times 2$ minor coming from two propagators, call them $p$ and $q$, and two vertices, call them $a$ and $b$, and assume that $a <_i b$.
 It remains to show that $b = a+1$.
@@
 Then $x$ is a factor of $\Delta_{I_i}$.
-Therefore, $x$ must correspond to entry in the row of $p$ and column of $I_i(p)$, i.e.
+Therefore, $x$ must appear in the row of $p$ and column of $I_i(p)$, i.e.
 $x = x_{p, I_i(p)}$.
@@
 Furthermore, we know by part (4) that $p$ changes from not being associated to $a$ to being associated to $a$ if and only if $q$ changes from not being associated to $a+1$ to being associated to $a+1$.
-Thus $f^2|R$ implies that twice in the Grassmann necklace $p$ must change from not being associated to vertex $a$ to being associated to vertex $a$.
+Thus $f^2|R$ implies that \hlfix{twice}{Not sure what to do M.72} in the Grassmann necklace $p$ must change from not being associated to vertex $a$ to being associated to vertex $a$.
 This is again a contradiction, and so $R$ is square-free.
@@
 
-Finally then we need to check the scalar.
+Finally, we need to check the scalar.
 By Definition~\ref{def R(W)} each linear factor appears with coefficient $1$ and each $2\times 2$ determinant factor appears with the same sign as the determinant of the corresponding minor in $C(W)$.

### 2020-11-02 GWLDCII.tex
changes from today's meeting

@@
 Thus we have shown that Algorithm \ref{alg:put GN on WLD} does in fact produce a Grassmann necklace. Next we check that it produces the correct one, i.e. the Grassmann necklace that defines $M(W)$. 
-\begin{thm}\label{res alg gives correct GN} \todo{fix mixing words and notation (M.28, M.47)} 
+\begin{thm}\label{res alg gives correct GN} 
 The Grassmann necklace $(I_1 \ldots I_n)$ from Theorem~\ref{res:alg gives GN} is the Grassmann necklace of the positroid $M(W)$.
@@
 it must be a column label.
-The shapes of the Le diagram of $V$ and $W$ are the same except for the insertion of this column, since $I_1$ is the same for $V$ and $W$ except for the incrementation of the indices $\geq i$ in the transition from the necklace for $V$ to the necklace for $W$.
+The shapes of the Le diagram of $V$ and $W$ are the same except for the insertion of this column, since $I_1$ is the same for $V$ and $W$ except for the incrementation of the indices  greater than or equal to $i$ in the transition from the necklace for $V$ to the necklace for $W$.
+\todo{fix mixing words and notation (M.28, M.49) throughout, esp wrt <, > $\geq$ etc.}
 \end{proof}
@@
 
-Also by Lemma~\ref{lem I} we have $I_{n-1}^{W} = I_n^{V} \cup \{n-1\}$.
-Recall from the proof of Lemma~\ref{lem I} that \hlfix{$n-3,n-2,n-1,n \not\in I_1^V$}{M doesn't like this notation M.58}; therefore
+Also by Lemma~\ref{lem I} we have $I_{n-1}^{W} = I_n^{V} \cup \{n-1\}$. Recall from the proof of Lemma~\ref{lem I} that none of $n-3,\;n-2,\;n-1$ or $n$ are in $I_1^V$; therefore
 \[
@@
 
-We can now describe the plusses contributed by $I_{n-2}^W$ in the remaining two cases: when $n-2 \not\in I_{n-2}^V$, and when $n-2,n-1 \in I_{n-2}^V$.
+We can now describe the plusses contributed by $I_{n-2}^W$ in the remaining two cases: when $n-2 \not\in I_{n-2}^V$, and when both $n-2$ and $n-1$ are not in $I_{n-2}^V$.
 
@@
 
-\item As in Lemma~\ref{lem I} we have $n,n-1,n-2,n-3 \not\in I_1^V$, which implies the first part of the claim.
+\item As in Lemma~\ref{lem I} we have that none of $n,\; n-1, \; n-2$ and $n-3$ are in $I_1^V$, which implies the first part of the claim.
 The second part is a consequence of the discussion following equation \eqref{eq necklace}, which shows that $n-4 \not\in I_n^V$.
+\todo{propagate M.58 when it appears inline}
 
@@
 \item By Lemma~\ref{lem I} we have $I_1^W = I_1^V\cup \{n-3\}$ and $I_{n-2}^W = (I_n^V \setminus \{n-5\}) \cup \{n-1,n-2\}$.
-By equation \eqref{eq necklace} we have $n-5 \in I_1^V$, and by the following discussion we have $n-1,n-2,n-3 \not\in I_n^V,I_1^V$.
+By equation \eqref{eq necklace} we have $n-5 \in I_1^V$, and by the following discussion we have that none of $n-1,\;n-2$ and $n-3$ are not in either $I_n^V$ or $I_1^V$.
 It follows that the symmetric difference of $I_1^W$ and $I_{n-2}^W$ is
@@
 
-Each $r_i$ is the determinant of a minor determined by certian propagators of $W$: specifically, $p$ plays a role in defining $r_i$ if if contributs one set of values (columns) $i^{th}$ element of the Grassmann necklace and a different set to the $(i-1)^{th}$ element.
-\sanote{major rewrite of this sentence (due to M.62) Karen, look over}.
+Each $r_i$ is the determinant of a minor determined by certain propagators of $W$.
+In particular, if a propagator $p$ contributes one value to the $i^{th}$ element of the Grassmann necklace and a different value to the $(i-1)^{th}$ element, then $p$ is one of the propagators contibuting to the minor.
+Specifically, the row associated to $p$ and the column associated to the value that $p$ contributes to the $i^{th}$ Grassmann Necklace element appear in the minor.
 %That is, each $r_i$ is the determinant of the minor determined by the propagators (rows) that contribute different values (columns) to the $i^{th}$ element of the Grassmann necklace than they did to the $(i-1)^{th}$.
@@
 Furthermore, we know by part (4) that $p$ changes from not being associated to $a$ to being associated to $a$ if and only if $q$ changes from not being associated to $a+1$ to being associated to $a+1$.
-Thus $f^2|R$ implies that \hlfix{twice}{Not sure what to do M.72} in the Grassmann necklace $p$ must change from not being associated to vertex $a$ to being associated to vertex $a$.
+Thus $f^2|R$ implies that  in the Grassmann necklace $p$ must change twice from not being associated to vertex $a$ to being associated to vertex $a$.
 This is again a contradiction, and so $R$ is square-free.

### 2020-11-16 GWLDCI.tex
minor changed in comments
referee M's comment on the bijecition

@@
 
-\todo{Need to address the summary comment to 3.1 in review M}
-
 \section{Matroids, triangulations, and equivalence classes of Wilson loop diagrams\label{sec equiv}} \todo{rephrase in terms of weakly.}
@@
  \end{proof}
+
+\begin{rmk}
+The previous lemma shows that $\tau$ does map into polygon dissections.
+In fact $\tau$ is a bijection from weakly admissible Wilson loop diagrams to polygon dissections.
+To see the inverse map, and hence obtain bijectivity, we need only reverse the construction above.
+The only part which is nontrivial is that if diagonals of the dissection meet at a common vertex, we need to order the propagators associated to these diagonals along the edge associated to the vertex of the dissection, but using the noncrossing property of propagators this can be done uniquely.
+
+The $\tau$ bijection will be useful, as is typical in bijective combinatorics, because some features are more visible on the dissection side.
+In particular the exact subdiagrams are visible as triangulated pieces and equivalence comes down to retriangulation.
+All of these notions are defined and explained below.
+
+As a final note before we begin laying out the results we need on $\tau$, if a Wilson loop diagram $W$ is weakly admissible but not admissible, then the same equality that would give exactness in a subdiagram holds, and so for the same reasons as described below for exact subdiagrams $\tau(W)$ will have all triangle internal faces and this is the only way that $\tau(W)$ can have all triangle internal faces.
+Therefore, $\tau$ also gives a bijection between admissible Wilson loop diagrams and polygon dissections with at least one non-triangle internal face.
+\end{rmk}
 

### 2020-11-16 GWLDCI.tex
dealt with the standard facts, still not perfect bit it should do

@@
 \begin{proof}
-Let us first record a few standard facts about polygon triangulations (that is, about triangulations with all vertices on the outer face).
+Let us first record a few elementary facts about polygon triangulations (that is, about triangulations with all vertices on the outer face).
 If such a triangulation has $n$ vertices then it has $n$ edges on the polygon (that is, on the outer face) and $n-3$ edges which are not.
-No planar simple graph with the same vertices and the same outer face can have more edges than a triangulation, and every such simple graph with $n-3$ edges off the outer face is a triangulation.\todo{Referee Y wants a ref for these standard things.}
+No planar simple graph with the same vertices and the same outer face can have more edges than a triangulation, and every such simple graph with $n-3$ edges off the outer face is a triangulation.\footnote{The last sentence is the statement that maximal outerplanar graphs are exactly polygon triangulations\cite{MPhD}, then the earlier facts follow from Euler's formula for planar graphs.}
 

### 2020-11-16 GWLDCI.tex
dealt with the sec 4 comments that were for me

@@
 
-\begin{dfn}\label{def:associahedron} \todo{Karen, see note bottom of page 2 in report M}
+\begin{dfn}\label{def:associahedron} 
 Fix $n$ and consider dissections of a convex $n$-gon.
@@
 
+The associahedron coming from dissections on an $n$-gon is known as the $n-1$ associahedron because this is the associahedron for which the vertices correspond to the ways to bracket a list of length $n-1$.
+It is an $n-3$ dimensional polytope.
+
 It turns out that this defines a class of combinatorially equivalent polytopes, which can be proved by giving a realization.
@@
 
-\begin{dfn}\label{def:secondary polytope} \todo{Karen, see note bottom of page 2 in report M}
+\begin{dfn}\label{def:secondary polytope} 
   Let $x_1, \ldots, x_n$ be the corners of a convex $n$-gon in $\mathbb{R}^2$, and let $T$ be the set of triangulations of this $n$-gon.
@@
 \begin{proof}
-\hlfix{Since $D_1$ and $D_2$ do not have the same set of non-triangle faces, but the vertices of the non-triangles faces are the same, $V_{>3}(D_1) = V_{>3}(D_2)$, there must be some diagonal $d$ of $D_1$ that crosses through a non-triangle face $f$ of $D_2$.
-If that face of $D_2$ has degree at least 5 then it must contain four vertices in the configuration described in the statement.}{Karen, I'm leaving the rest of the last comment of report M to you.}
-
-Suppose this never occurs.
+  Since $V_{>3}(D_1) = V_{>3}(D_2)$, the vertices of the non-triangle faces of $D_1$ and $D_2$ are the same, but $D_1$ and $D_2$ do not have the same set of non-triangle faces.
+  Suppose that no diagonal of $D_1$ crosses through a non-triangle face of $D_2$.
+Then all non-triangle faces of $D_2$ must lie strictly within faces of $D_1$.
+Since the non-trangles faces of the two dissections are different at least one of these containments must be proper, and so some diagonal bounding one of the non-triangle faces of $D_2$ must cross through a non-triangle face of $D_2$.
+Therefore, swapping $D_1$ and $D_2$ if necessary,
+  %Since $D_1$ and $D_2$ do not have the same set of non-triangle faces, but the vertices of the non-triangles faces are the same, $V_{>3}(D_1) = V_{>3}(D_2)$,
+  there must be some diagonal $d$ of $D_1$ that crosses through a non-triangle face $f$ of $D_2$.
+  If $f$ has degree at least 5 then it must contain four vertices in the configuration described in the statement.
+
+Suppose no $f$ of degree at least 5 crossed by a diagonal of the other dissection occurs in either $D_1$ or $D_2$.
 Then all the non-triangle faces of $D_2$ which are crossed by a diagonal of $D_1$ must be quadrilaterals and likewise for $D_1$.
@@
 
-Assume for a contradiction that no quadrilateral as in the statement exists, and let $d$ be a diagonal in $D_1$ crossing the unique non-triangle face $f$ of $D_2$.
+Assume for a contradiction that no quadrilateral as in the statement exists, and let $d$ continue to be a diagonal in $D_1$ crossing a non-triangle face $f$ of $D_2$.
 Then $f$ must have two vertices strictly on each side of $d$.
-We name the vertices on one side of $d$ as $x_i$ and $x_j$, and those on the other side as $x_k$, $x_l$ (and in that order; see Figure~\ref{inductive_step}).
+We name the vertices on one side of $d$ as $x_i$ and $x_j$, and those on the other side as $x_k$, $x_l$ in that order; see Figure~\ref{inductive_step}.
 Let $g$ be the face in $D_1$ that is incident to $d$ on the $x_i, x_j$ side of $d$.

### 2020-11-27 GWLDCII.tex
specified citations in paper 2

@@
 This started with the observation that BCFW diagrams, which represent the on shell interactions of this theory, correspond to plabic graphs \cite{GrassmannAmplitudebook}.
-Plabic graphs were introduced by Postnikov in \cite{Postnikov}, and provide one of the many equivalent ways to classify the positroid cells of the positive real Grassmannian $\Gr(k,n)$.
+Plabic graphs were introduced by Postnikov in \cite[section 11]{Postnikov}, and provide one of the many equivalent ways to classify the positroid cells of the positive real Grassmannian $\Gr(k,n)$.
 This led to the representation of the on shell integrals associated to this theory in terms of a geometric space (the Amplituhedron) embedded in $\Gr(k,n)$ \cite{Arkani-Hamed:2013kca,Arkani-Hamed:2013jha}.
@@
 
-The first condition bounds the total number of propagators in the diagram, while the second limits how densely propagators can be fitted into any part of the diagram; in particular, the second condition prohibits propagators that connect two adjacent edges.
+The first condition bounds the total number of propagators in the diagram, and comes from the fact that these diagrams represent $N^k$MHV interctions, where $k +4 <n$, see for instance the explanation in the introduction of \cite{adamo:2011pr} while the second limits how densely propagators can be fitted into any part of the diagram; in particular, the second condition prohibits propagators that connect two adjacent edges.
+This can be derived from the integrals associated to the diagrams, as in.
 Note that since $\cP$ is a set, we may not have two propagators starting and ending on the same pair of edges.
+\cite[Theorem 1.13]{wilsonloop}.
 The third condition simply requires that propagators are non-crossing.
-
-These conditions are imposed by the physical interpretation of Wilson loop diagrams (see for example \cite{Adamo:2011pv,Adamo:2012xe,wilsonloop,LipsteinMason}).
-We therefore restrict our attention in this paper to admissible Wilson loop diagrams and their subdiagrams.
+This follows from the fact that these Wilson loop diagrams are a representation of planar Feynman diagrams of $N=4$ SYM theory.
+For a description of the relationship between planar Feynman diagram and planar Wilson loops, see the discussion in \cite[section 3]{LipstenMason}
 
@@
 As such, a diagram associates a real value to $n$ particles, one for each vertex.
-Each particle is represented as a section of a $|\cP|$-vector bundle over twistor space, projected onto a real subspace in a process called bosonization \cite{Arkani-Hamed:2013jha}.
+Each particle is represented as a section of a $|\cP|$-vector bundle over twistor space, projected onto a real subspace in a process called bosonization \cite[section 2]{Amplituhedronsquared}.
 In other words, each Wilson loop diagram defines a functional on external particles.
@@
 
-The matrix $C(W)$ defines a positroid cell associated to $W$ in the positive Grassmannian $\Gr(n, |\cP|)$, which we denote by $\Sigma(W)$ \cite{wilsonloop}.
-Marcott \cite{WLDdim} shows that  the matrix $C(W)$ parametrizes a space whose closure is exactly the closure of $\Sigma(W)$.
+The matrix $C(W)$ defines a positroid cell associated to $W$ in the positive Grassmannian $\Gr(n, |\cP|)$, which we denote by $\Sigma(W)$ \cite[Theorem 3.41]{wilsonloop}.
+Marcott \cite[Theorem 8.4]{WLDdim} shows that  the matrix $C(W)$ parametrizes a space whose closure is exactly the closure of $\Sigma(W)$.
 That is, the space defined by $C(W)$ and the cell $\Sigma(W)$ agree up to a set of measure $0$.
@@
 The interested reader is referred to \cite{Adamo:2012xe,HeslopStewart,LipsteinMason} for more information about the integrand of $I(W)$.
+\sanote{not putting sections here, but I'd like a second thought}
 
 For a fixed number of propagators and particles, the tree level amplitude of the Wilson loop diagrams is computed as the sum of the $I(W)$ for all $W$ of the correct size.
-By \cite{Adamo:2011pv,Adamo:2012xe,Arkani-Hamed:2013jha} this sum is finite for all sets of external particles, i.e.
+\hlfix{By {\cite{Adamo:2011pv,Adamo:2012xe,Arkani-Hamed:2013jha}} this sum is finite for all sets of external particles,}{fix this citation} i.e.
 \bas \mathcal{A}_{k, n}^{tree} = \sum_{\substack{W = (\cP, [n]), \\ |\cP| = k}} I(W) <\infty. \eas
@@
 
-We summarize here only the portion of positroid theory that we require in this paper; the interested reader is referred to \cite{Postnikov} for more details.
+We summarize here only the portion of positroid theory that we require in this paper; the interested reader is referred to \cite[sections 6, 16]{Postnikov} for more details.
 
@@
 Postnikov shows in \cite{Postnikov} that the positroids of $\Gr(k,n)$ are indexed by many different collections of objects, each with their own advantages and disadvantages.
-The two most suited to our purposes are Grassmann necklaces and Le diagrams, which we discuss.
+The two most suited to our purposes are Grassmann necklaces \cite[section 16]{Postnikov} and Le diagrams\cite[section 6]{Postnikov}, which we discuss.
 In order to do so, we first need some preliminary definitions.
@@
 This in turn induces a total order on $\binom{[n]}{k}$, namely the lexicographic order with respect to $<_j$.
-It also induces a separate partial order $\gale{j}$ on $\binom{[n]}{k}$ (the {\bf Gale order} \cite{Gale}), which is defined as follows: for
+It also induces a separate partial order $\gale{j}$ on $\binom{[n]}{k}$ (the {\bf Gale order} \cite{Gale}) \sanote{Not citing a thm here either as we give the dfn}, which is defined as follows: for
 \[A = \{a_1 <_j a_2 <_j \dots <_j a_k\} \text{ and } B = \{b_1 <_j b_2 <_j \dots <_j b_k\} \in \binom{[n]}{k},\] we define
@@
 
-An algorithm for constructing the Grassmann necklace of a Le diagram also exists; this was given by Oh in \cite{Oh}.
+An algorithm for constructing the Grassmann necklace of a Le diagram also exists; this was given by Oh in \cite[section 4]{Oh}.
 A method for using the Le diagram to test whether a given $k$-subset is a basis for the corresponding positroid or not was given by Casteels in \cite{CasteelsPaths}.
@@
 However, to go from the Wilson loop diagram $W$ to the positroid cell, one had to go through the matroid explicitly realized via $C(W)$, then make a list of all its nonzero $k\times k$ minors and extract the Le diagram or Grassmann necklace via the methods described in Section~\ref{sec:positroid background}.
-In \cite{casestudy}, Agarwala and Fryer apply this process in the smallest non-trivial case: admissible Wilson loop diagrams with two propagators on six vertices.
+In \cite[section 4]{casestudy}, Agarwala and Fryer apply this process in the smallest non-trivial case: admissible Wilson loop diagrams with two propagators on six vertices.
 Even in this simple case, we see that the mapping from admissible Wilson loop diagrams to positroid cells is neither one-to-one nor onto, and the process described above makes it almost impossible to track the relationship between the original Wilson loop diagram and the resulting positroid.
@@
 While this paper primarily approaches proofs from a combinatorial point of view, readers with a background in matroid theory are encouraged to keep the matroidal viewpoint in mind throughout; we expect that the two approaches will be complementary and will build upon each other.
-See the first paper in this series \cite{generalcombinatoricsI} for some related results concerning the positroids of Wilson loop diagrams obtained by viewing them primarily as matroids.
+See the first paper in this series \cite[section 3]{generalcombinatoricsI} for some related results concerning the positroids of Wilson loop diagrams obtained by viewing them primarily as matroids.
 \end{rmk}
@@
 Note that the positroid cells associated to the Amplituhedron are of dimension $4|\cP|$.
-In \cite{non-orientable}, Agarwala and Marcott associate a Deodhar component\footnote{Since Deodhar components play no role in this paper, the interested reader is referred to \cite{non-orientable} for more details on this.} to each Wilson loop diagram, and show that the dimension of this Deodhar component is the sum of $|\cP|$ and the dimension of the associated positroid cell.
+In \cite[section 2]{non-orientable}, Agarwala and Marcott associate a Deodhar component\footnote{Since Deodhar components play no role in this paper, the interested reader is referred to \cite{non-orientable} for more details on this.} to each Wilson loop diagram, and show that the dimension of this Deodhar component is the sum of $|\cP|$ and the dimension of the associated positroid cell.
 %\[|\cP| + \text{ the dimension of associated positroid cell}.\]
@@
 
-Marcott in \cite{WLDdim} gives a different proof of the $3|\cP|$-dimensionality of $M(W)$ which is geometric and more elegant, but it is not easy to track the effect of a particular propagator.
+Marcott in \cite[Theorem 8.4]{WLDdim} gives a different proof of the $3|\cP|$-dimensionality of $M(W)$ which is geometric and more elegant, but it is not easy to track the effect of a particular propagator.
 It is worth noting that while the Amplituhedon is also defined by a projection of a set of $4|\cP|$ dimensional positroid cells, there is no evidence to suggest that the $3|\cP|$ dimensional cells of $\Gr(|\cP|, n)$ defiining the Wilson loop diagrams are related to the $4|\cP|$ dimensional cells defining the Amplituhedron.
@@
 
-Since SYM $N=4$ is a finite theory \cite{Alday:2007hr, ParkeTaylorids}, the scattering amplitudes (and thus the holomorphic Wilson loops $\,\mathfrak{W}_{k,n}$) are finite.
-That is, for a fixed set of external particles $\cZ$ we must have
+\hlfix{Since SYM $N=4$ is a finite theory {\cite{Alday:2007hr, ParkeTaylorids}}, the scattering amplitudes (and thus the holomorphic Wilson loops $\,\mathfrak{W}_{k,n}$) are finite.}{Fix citations} That is, for a fixed set of external particles $\cZ$ we must have
 \bas \sum_{W \text{ s.t. } |\cP| = k} I(W)(\cZ) <\infty \;.\eas

### 2020-11-29 GWLDCI.tex
specified citations in paper 1

@@
 We now define the notion of an admissible diagram, which imposes certain density and non-crossing conditions on the configuration of the propagators.
-The motivation for these conditions comes from the link to SYM $N=4$ theory, where the admissible Wilson loop diagrams are exactly those that correspond to $N^kMHV$ diagrams; see for example \cite{Amplituhedronsquared}.
+The motivation for these conditions comes from the link to SYM $N=4$ theory, where the admissible Wilson loop diagrams are exactly those that correspond to $N^kMHV$ diagrams; see for example \cite[section 2]{HeslopStewart}.
 
@@
 There are a few things to note here.
-First, what we call weakly admissible here is called admissible in \cite{wilsonloop}.
+First, what we call weakly admissible here is called admissible in (\cite{wilsonloop}, see definition 1.11 and section 1.3).
 \hlfix{Many of the results below still apply when the hypothesis of admissibility is changed to weak admissibility.}{Propagate "weakly" through document}
@@
 As described in the introduction, Wilson loop diagrams come from the study of SYM $N = 4$ in the physics literature.
-In particular (see \cite{Adamo:2012xe} for details) this gives that each diagram $W$ is associated to a matrix of data $C(W)$, which we now describe.
+In particular (see \cite[section 2]{HeslopStewart} for details) this gives that each diagram $W$ is associated to a matrix of data $C(W)$, which we now describe.
 
@@
 Matroid theory relates to the study of Wilson loop diagrams as follows.
-In \cite{wilsonloop}, Agarwala and Marin-Amat show that every weakly admissible Wilson loop diagram $W$ with $k$ propagators defines a positroid $M(W)$ of rank $k$ on a base set of size $n$.
-Combined with Postnikov's work in \cite{Postnikov}, this shows that each admissible Wilson loop diagram corresponds to a convex subset of $\Gr(k,n)$, thus connecting the geometry of Wilson loop diagrams with the geometry underlying the Amplituhedron.
+In \cite[section 3]{wilsonloop}, Agarwala and Marin-Amat show that every weakly admissible Wilson loop diagram $W$ with $k$ propagators defines a positroid $M(W)$ of rank $k$ on a base set of size $n$.
+\hlfix{Combined with Postnikov's work in {\cite{Postnikov}}, this shows that each admissible Wilson loop diagram corresponds to a convex subset of $\Gr(k,n)$}{fix citation.
+Ask Cameron?}, thus connecting the geometry of Wilson loop diagrams with the geometry underlying the Amplituhedron.
 
@@
 
-\emph{Polygon dissection} is a common term in combinatorics for a decomposition of a convex polygon into smaller polygons by means of noncrossing diagonals; see for example \cite{PSpolygon}.
+\emph{Polygon dissection} is a common term in combinatorics for a decomposition of a convex polygon into smaller polygons by means of noncrossing diagonals; \hlfix{see for example {\cite{PSpolygon}}}{Karen, can you specify the citation?}.
 Each $\tau(W)$ is such an object.
@@
 If such a triangulation has $n$ vertices then it has $n$ edges on the polygon (that is, on the outer face) and $n-3$ edges which are not.
-No planar simple graph with the same vertices and the same outer face can have more edges than a triangulation, and every such simple graph with $n-3$ edges off the outer face is a triangulation.\footnote{The last sentence is the statement that maximal outerplanar graphs are exactly polygon triangulations\cite{MPhD}, then the earlier facts follow from Euler's formula for planar graphs.}
+No planar simple graph with the same vertices and the same outer face can have more edges than a triangulation, and every such simple graph with $n-3$ edges off the outer face is a triangulation.\sanote{Karen, can you specify citation in footnote?} \footnote{The last sentence is the statement that maximal outerplanar graphs are exactly polygon triangulations \cite{MPhD}, then the earlier facts follow from Euler's formula for planar graphs.}
 
@@
 
-In \cite{wilsonloop}, the authors show that each weakly admissible Wilson loop diagram corresponds to a positroid.
+In \cite[Theorem 3.39]{wilsonloop}, the authors show that each weakly admissible Wilson loop diagram corresponds to a positroid.
 That is, each diagram corresponds to a matroid that can be represented by elements of the positive Grassmannian $\Gr(|\cP|, n)$.
@@
 Now we are ready to prove the main result of this section, namely that two Wilson loop diagrams define the same matroid (positroid) if and only if they are equivalent (Theorem \ref{same matroid iff equiv}).
-We also give a formula for the number of Wilson loop diagrams in a given equivalence class (Corollary \ref{number of equiv diagrams}), completing the characterization of the correspondence between Wilson loop diagrams and positroids starting in \cite{wilsonloop}.
+We also give a formula for the number of Wilson loop diagrams in a given equivalence class (Corollary \ref{number of equiv diagrams}), completing the characterization of the correspondence between Wilson loop diagrams and positroids started in \cite{wilsonloop}.
 
@@
 We know from examples (e.g.
-\cite{casestudy}) that many positroid cells cannot be obtained as the matroids of admissible Wilson loop diagrams.
+\cite[Remark 4.2]{casestudy}) that many positroid cells cannot be obtained as the matroids of admissible Wilson loop diagrams.
 We do not obtain a formula for the number of cells in the image of $M$ here, but in the next section we give an alternate characterization of ${\rm im}(M)$ in terms of associahedra, with the hope that this linkage with a well-studied combinatorial object will shed light on the issue in the future.
@@
 It turns out that this defines a class of combinatorially equivalent polytopes, which can be proved by giving a realization.
-There are many interesting realizations of the associahedron \cite{CSZinequivalent}.
+\hlfix{There are many interesting realizations of the associahedron {\cite{CSZinequivalent}}}{Karen, can you specify the citation?}.
 The following realization will be the one that we use.
@@
     \]
-    We have from \cite{CSZinequivalent} that $\omega^+_d$ is a normal vector for any face with $d$ as a diagonal.
+    \hlfix{We have from {\cite{CSZinequivalent}}}{specify citation} that $\omega^+_d$ is a normal vector for any face with $d$ as a diagonal.
 However we can also check this fact in a completely elementary way using the shoelace formula for the area of a triangle.

### 2020-12-02 GWLDCII.tex
updates from Monday's discussion

@@
 For a fixed number of propagators and particles, the tree level amplitude of the Wilson loop diagrams is computed as the sum of the $I(W)$ for all $W$ of the correct size.
-\hlfix{By {\cite{Adamo:2011pv,Adamo:2012xe,Arkani-Hamed:2013jha}} this sum is finite for all sets of external particles,}{fix this citation} i.e.
+By {\cite{Adamo:2011pv,Adamo:2012xe,Arkani-Hamed:2013jha}} this sum is finite for all sets of external particles,\sanote{fix this citation} i.e.
 \bas \mathcal{A}_{k, n}^{tree} = \sum_{\substack{W = (\cP, [n]), \\ |\cP| = k}} I(W) <\infty. \eas
@@
 
-\hlfix{Since SYM $N=4$ is a finite theory {\cite{Alday:2007hr, ParkeTaylorids}}, the scattering amplitudes (and thus the holomorphic Wilson loops $\,\mathfrak{W}_{k,n}$) are finite.}{Fix citations} That is, for a fixed set of external particles $\cZ$ we must have
+Since SYM $N=4$ is a finite theory {\cite{Alday:2007hr, ParkeTaylorids}}, the scattering amplitudes (and thus the holomorphic Wilson loops $\,\mathfrak{W}_{k,n}$) are finite.\sanote{Fix citations} That is, for a fixed set of external particles $\cZ$ we must have
 \bas \sum_{W \text{ s.t. } |\cP| = k} I(W)(\cZ) <\infty \;.\eas

### 2020-12-10 GWLDCI.tex
gone through everything and rechecked the two reports

@@
 \title{Combinatorics of the geometry of Wilson loop diagrams I: equivalence classes via matroids and polytopes}
-\author{Susama Agarwala\thanks{SA was partially supported by an Office of Naval Research grant.}, Si\^an Fryer, and Karen Yeats\thanks{KY is supported by an NSERC Discovery grant, by the Canada Research Chair program, though some of this work was developed also by a Humboldt Fellowship from the Alexander von Humboldt foundation.}}
+\author{Susama Agarwala\thanks{SA was partially supported by an Office of Naval Research grant.}, Si\^an Fryer, and Karen Yeats\thanks{KY is supported by an NSERC Discovery grant, by the Canada Research Chair program, and also, over some of the time this work was developed, by a Humboldt Fellowship from the Alexander von Humboldt foundation.}}
 %\date{}
@@
   Wilson loop diagrams are an important tool in studying scattering amplitudes of SYM $N=4$ theory and are known by previous work to be associated to positroids.
-We characterize the conditions under which two Wilson loop diagrams give the same positroid, prove that an important subclass of subdiagrams (exact subdiagrams) correspond to uniform matroids, and enumerate the number of different Wilson loop diagrams that correspond to each positroid cell.
+We characterize the conditions under which two Wilson loop diagrams give the same positroid, prove that an important subclass of subdiagrams (exact subdiagrams) corresponds to uniform matroids, and enumerate the number of different Wilson loop diagrams that correspond to each positroid cell.
 We also give a correspondence between those positroids which can arise from Wilson loop diagrams and directions in associahedra.
@@
 
-In \cite{wilsonloop} Agarwala and Marin-Amat showed that every weakly admissible Wilson loop diagrams can be identified with a type of matroid called a positroid, and observed that this mapping is neither one-to-one nor onto.
+In \cite{wilsonloop} Agarwala and Marin-Amat showed that every weakly admissible Wilson loop diagram can be identified with a type of matroid called a positroid, and observed that this mapping is neither one-to-one nor onto.
 Each such positroid corresponds to a positroid cell in the appropriate positive Grassmannian $\Gr(k,n)$ \cite{Postnikov}.
 In this paper we give a simple characterization of this lack of injectivity in terms of an equivalence relation on the Wilson loop diagrams, and enumerate the number of different Wilson loop diagrams that correspond to each positroid cell.
-We also study the lack of surjectivity, and show that the number of distinct positroid cells associated to Wilson loop diagrams of a given size is given by counting the directions in an associahedron.
+We also study the lack of surjectivity, and show that the number of distinct positroid cells associated to Wilson loop diagrams of a given size is given by counting the faces up to paralellism in an associahedron.
 
@@
 
-Section~\ref{section overall background} summarizes the required background, with definitions for Wilson loop diagrams given in subsection~\ref{section WLD background} and matroids in subsection~\ref{sec matroid background}.
+Section~\ref{section overall background} summarizes the required background, with definitions for Wilson loop diagrams given in Subsection~\ref{section WLD background} and matroids in Subsection~\ref{sec matroid background}.
 Key definitions include {\em admissible} Wilson loop diagrams (Definition~\ref{admisdfn}), {\em exact} subdiagrams (Definition~\ref{def:exact diagram}), and an equivalence relation on admissible Wilson loop diagrams (Definition~\ref{equivdfn}).
@@
 The main result of Section~\ref{sec equiv} is Theorem~\ref{same matroid iff equiv}, which says that two Wilson loop diagrams define the same matroid (positroid) if and only if they are equivalent.
-In subsection~\ref{sec: polygon partitions} we relate exact subdiagrams of Wilson loop diagrams to triangulations of polygons, and hence show that every Wilson loop diagram can be uniquely decomposed as a collection of exact subdiagrams (Corollary~\ref{uniqueproppartitioncor}).
-In subsection~\ref{sec: exact diagram matroidal props} we examine the matroidal properties of the exact subdiagrams, and prove that a subdiagram of a Wilson loop diagram defines a uniform matroid if and only if the subdiagram is exact (Theorem \ref{exactuniformthm}).
+In Subsection~\ref{sec: polygon partitions} we relate exact subdiagrams of Wilson loop diagrams to triangulations of polygons, and hence show that every Wilson loop diagram can be uniquely decomposed as a collection of exact subdiagrams (Corollary~\ref{uniqueproppartitioncor}).
+In Subsection~\ref{sec: exact diagram matroidal props} we examine the matroidal properties of the exact subdiagrams, and prove that a subdiagram of a Wilson loop diagram defines a uniform matroid if and only if the subdiagram is exact (Theorem \ref{exactuniformthm}).
 This uniform matroid is in fact equal to the dual matroid restricted to the exact subdiagram (Remark \ref{remark exact dual restiction}).
-Finally, subsection~\ref{sec: matroids and equivalence} is devoted to the proof of Theorem~\ref{same matroid iff equiv}, along with an easy corollary which gives a formula for the size of each equivalence class (Corollary~\ref{number of equiv diagrams}).
+Finally, Subsection~\ref{sec: matroids and equivalence} is devoted to the proof of Theorem~\ref{same matroid iff equiv}, along with an easy corollary which gives a formula for the size of each equivalence class (Corollary~\ref{number of equiv diagrams}).
 
@@
 The main result of Section~\ref{sec associahedron} is Theorem \ref{thm:count inequiv diagrams}, which shows that the set of admissible Wilson loop diagrams (up to equivalence) is in bijection with the set of faces in the associahedron (up to parallelism).
-Towards this result we go over some relevant background on polytopes in subsection~\ref{sec polytope background}, and then prove the main result in subsection~\ref{sec associahedron results} in the form of two propositions: Proposition~\ref{prop easy way} and Proposition~\ref{prop hard way}.
+Towards this result we go over some relevant background on polytopes in Subsection~\ref{sec polytope background}, and then prove the main result in Subsection~\ref{sec associahedron results} in the form of two propositions: Proposition~\ref{prop easy way} and Proposition~\ref{prop hard way}.
 
@@
 \begin{thm} \label{thm WLD defines matroid} \cite[Theorem 3.6]{wilsonloop} Any Wilson loop diagram $W =(\cP, [n])$ defines a matroid $M(W)$ with ground set $[n]$.
-The independent sets are exactly those subsets $V \subseteq [n]$ such that for every subset of vertices, $U\subseteq V$, supports at least as many propagators as vertices in the set, $|\Prop(U)| \geq |U|$.
+The independent sets are exactly those subsets $V \subseteq [n]$ \hlfix{such that for every subset of vertices, $U\subseteq V$, supports at least as many propagators as vertices in the set, $|\Prop(U)| \geq |U|$}{This edit isn't grammatically correct and is more complicated than what the referee asked for, could you fix it?}.
 \label{thm:WLDmatroid}\end{thm}
@@
 
-\emph{Polygon dissection} is a common term in combinatorics for a decomposition of a convex polygon into smaller polygons by means of noncrossing diagonals; \hlfix{see for example {\cite{PSpolygon}}}{Karen, can you specify the citation?}.
+\emph{Polygon dissection} is a common term in combinatorics for a decomposition of a convex polygon into smaller polygons by means of noncrossing diagonals; see for example the introduction of {\cite{PSpolygon}}.
 Each $\tau(W)$ is such an object.
@@
 If such a triangulation has $n$ vertices then it has $n$ edges on the polygon (that is, on the outer face) and $n-3$ edges which are not.
-No planar simple graph with the same vertices and the same outer face can have more edges than a triangulation, and every such simple graph with $n-3$ edges off the outer face is a triangulation.\sanote{Karen, can you specify citation in footnote?} \footnote{The last sentence is the statement that maximal outerplanar graphs are exactly polygon triangulations \cite{MPhD}, then the earlier facts follow from Euler's formula for planar graphs.}
+No planar simple graph with the same vertices and the same outer face can have more edges than a triangulation, and every such simple graph with $n-3$ edges off the outer face is a triangulation.\footnote{The last sentence is the statement that maximal outerplanar graphs are exactly polygon triangulations (a standard fact that possibly was first written down in \cite{MPhD}, see Theorem 1 of \cite{LMN}), then the earlier facts follow from Euler's formula for planar graphs.}
 
@@
 
-In \cite{wilsonloop}, Agarwala and Marin-Amat show that certain subdiagrams of $W$ can be realized as contractions of $M(W)$, \hlfix{which we rephrase using the notation of this paper}{citation was correct, but notation was different.
-Karen: is this clearer?}:
+In \cite{wilsonloop}, Agarwala and Marin-Amat show that certain subdiagrams of $W$ can be realized as contractions of $M(W)$, which we rephrase using the notation of this paper:
 
@@
   Let $W$ be a weakly admissible Wilson loop diagram where the sizes of the supports of the nontrivial maximal exact subdiagrams are $n_1, n_2, \ldots, n_j$.
-Then the number of weakly admissible Wilson loop diagrams equivalent to $W$ (including $W$ itself) is \todo{Karen: This really is weakly admissible, correct?}
+Then the number of weakly admissible Wilson loop diagrams equivalent to $W$ (including $W$ itself) is
   \[
@@
 It turns out that this defines a class of combinatorially equivalent polytopes, which can be proved by giving a realization.
-\hlfix{There are many interesting realizations of the associahedron {\cite{CSZinequivalent}}}{Karen, can you specify the citation?}.
+There are many interesting realizations of the associahedron {\cite{CSZinequivalent}}.
 The following realization will be the one that we use.
@@
     \]
-    \hlfix{We have from {\cite{CSZinequivalent}}}{specify citation} that $\omega^+_d$ is a normal vector for any face with $d$ as a diagonal.
+    We have from \cite{CSZinequivalent} (see the proof of Proposition 3.5 therein) that $\omega^+_d$ is a normal vector for any face with $d$ as a diagonal.
 However we can also check this fact in a completely elementary way using the shoelace formula for the area of a triangle.
@@
 
-\todo{Referee Y wants a concluding sentence or paragraph, perhaps pointing towards paper 2, or perhaps an acknowledgements section}
+\section{Conclusion}
+
+In summary, using matroids and polygon dissections we have counted Wilson Loop diagrams that are equivalent in the sense of having the same positroid, and characterized Wilson Loop diagrams that are inequivalent in terms of faces of the associahedron $A_n$ up to paralellism.
+The second paper in this series calculates the dimension of the positroid cell associated to a Wilson loop diagram in a very concrete way by counting plusses in a Le diagram, and looks at the denominator of the integrand of the Wilson Loop diagram.
+All of these results are interesting mathematics while also serving to better understand the physics of scattering amplitudes.
 

### 2020-12-10 GWLDCI.tex
and a spellcheck

@@
 In this paper we give a simple characterization of this lack of injectivity in terms of an equivalence relation on the Wilson loop diagrams, and enumerate the number of different Wilson loop diagrams that correspond to each positroid cell.
-We also study the lack of surjectivity, and show that the number of distinct positroid cells associated to Wilson loop diagrams of a given size is given by counting the faces up to paralellism in an associahedron.
+We also study the lack of surjectivity, and show that the number of distinct positroid cells associated to Wilson loop diagrams of a given size is given by counting the faces up to parallelism in an associahedron.
 
@@
 Then all non-triangle faces of $D_2$ must lie strictly within faces of $D_1$.
-Since the non-trangles faces of the two dissections are different at least one of these containments must be proper, and so some diagonal bounding one of the non-triangle faces of $D_2$ must cross through a non-triangle face of $D_2$.
+Since the non-triangle faces of the two dissections are different at least one of these containments must be proper, and so some diagonal bounding one of the non-triangle faces of $D_2$ must cross through a non-triangle face of $D_2$.
 Therefore, swapping $D_1$ and $D_2$ if necessary,
@@
 
-In summary, using matroids and polygon dissections we have counted Wilson Loop diagrams that are equivalent in the sense of having the same positroid, and characterized Wilson Loop diagrams that are inequivalent in terms of faces of the associahedron $A_n$ up to paralellism.
-The second paper in this series calculates the dimension of the positroid cell associated to a Wilson loop diagram in a very concrete way by counting plusses in a Le diagram, and looks at the denominator of the integrand of the Wilson Loop diagram.
+In summary, using matroids and polygon dissections we have counted Wilson Loop diagrams that are equivalent in the sense of having the same positroid, and characterized Wilson Loop diagrams that are inequivalent in terms of faces of the associahedron $A_n$ up to parallelism.
+The second paper in this series calculates the dimension of the positroid cell associated to a Wilson loop diagram in a very concrete way by counting pluses in a Le diagram, and looks at the denominator of the integrand of the Wilson Loop diagram.
 All of these results are interesting mathematics while also serving to better understand the physics of scattering amplitudes.

### 2020-12-10 GWLDCII.tex
a few initial comments, will hopefully edit more later today

@@
 \title{Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators}
-\author{Susama Agarwala\thanks{SA was partially supported by an Office of Naval Research grant.}, Si\^an Fryer, and Karen Yeats\thanks{KY is supported by an NSERC Discovery grant, by the Canada Research Chair program, and though some the time this work was developed also by a Humboldt Fellowship from the Alexander von Humboldt foundation.}}
+\author{Susama Agarwala\thanks{SA was partially supported by an Office of Naval Research grant.}, Si\^an Fryer, and Karen Yeats\thanks{KY is supported by an NSERC Discovery grant, by the Canada Research Chair program, and also, through some the time this work was developed, by a Humboldt Fellowship from the Alexander von Humboldt foundation.}}
 \date{}
@@
 In contrast, the first paper in this series focuses on combinatorial and matroidal properties of the Wilson loop diagrams.
-The main focus of that paper is enumerating the positroid cells that are associated to Wilson loop diagrams with a fixed number of vertices and propagators, as well as counting the number of Wilson loop diagrams that map to the same positroid.
+The main focus of that paper is on enumerating the positroid cells that are associated to Wilson loop diagrams with a fixed number of vertices and propagators, as well as counting the number of Wilson loop diagrams that map to the same positroid.
 The results of the first paper are not a prerequisite for this paper.
@@
 This gives a novel and elegant interpretation of scattering amplitudes for this theory, as well as a means of greatly simplifying the calculations involved in traditional Feynman diagram approaches.
-Since then, there has been significant work to understand the volume form and its physical implications \cite{UnwindingAmplituhedron,galashinlam}.
+Since then, there has been significant work devoted to understanding the volume form and its physical implications \cite{UnwindingAmplituhedron,galashinlam}.
 
@@
 \hlfix{The Wilson loop diagrams discussed in this paper are, loosely speaking, dual graphs of the $N^kMHV$ diagrams.
-While the Wilson loop diagrams contain the exact same information as the $N^kMHV$ diagrams for the purposes of understanding $N=4 SYM$ theory, this dual perspective is better suited to understanding the combinatorics and geometry associated to the theory.}{added to address request (3) of report M} Therefore, we part with the notation in the physics literature, and name these dual graphs of $N^kMHV$ diagtams Wilson loop diagrams in order to emphasize the combinatorial and geometric significane of these object.
-In \cite{wilsonloop}, Agarwala and Marin-Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that can be realized as an element of $\Gr(k,n)$.
+While the Wilson loop diagrams contain the exact same information as the $N^kMHV$ diagrams for the purposes of understanding $N=4 SYM$ theory, this dual perspective is better suited to understanding the combinatorics and geometry associated to the theory.}{added to address request (3) of report M -- let's discuss, I don't think this makes sense as written} Therefore, \hlfix{we part with the notation in the physics literature, and name these dual graphs}{I'm not sure that's true} of $N^kMHV$ diagrams Wilson loop diagrams in order to emphasize the combinatorial and geometric significane of these object.
+In \cite{wilsonloop}, Agarwala and Marin-Amat uncovered a connection between the Feynman integrals developed in \hlfix{this}{What does this ``this'' refer to, also this sentence should probably start a new paragraph} literature and positroids, defined  as matroids that can be realized as an element of $\Gr(k,n)$.
 Other work has shown a connection between the volume filled by Wilson loop diagrams and the Amplituhedron \cite{casestudy, Amplituhedronsquared}.
@@
 
-In the above work and elsewhere, it is clear that while the space filled by the Wilson loop diagrams is related to the Amplituhedron, they are not the same space.
+In the above work and elsewhere, it is clear that while the space \hlfix{filled by}{``filled by'' vs ``parameterized by'' in the previous paragraph} the Wilson loop diagrams is related to the Amplituhedron, they are not the same space.
 For instance, it is conjectured that the Amplituhedron is orientable, whereas Agarwala and Marcott show in \cite{non-orientable} that the space parametrized by the Wilson loop diagrams as a subspace of $\Gr(k, n+1)$ can be seen as a non-orientable vector bundle over some submanifold of $\Gr(k,n)$.
@@
 
-It is worth noting at this point that the combinatorics of the Wilson loop diagrams are different from the combinatorics of the Amplituhedron, just as the the volume forms associated to the BCFW diagrams are different from those associated to the Wilson Loop diagrams.
+It is worth noting at this point that the \hlfix{combinatorics of the Wilson loop diagrams are different from the combinatorics of the Amplituhedron}{I think we should discuss this paragraph -- it may be misleading in a bad way}, just as the the volume forms associated to the BCFW diagrams are different from those associated to the Wilson Loop diagrams.
 For instance, the BCFW are most readily related to the geometry of a postive Grassmanian via plabic graphs.

### 2020-12-11 GWLDCI.tex
mostly working on paper 2

@@
 All of these notions are defined and explained below.
+
+There are many other instances of this basic methodology in combinatorics, but we'd like to point out one in particular that involves many objects closely related to those we use here, \cite{CGdyck}.\footnote{Thanks to the referee for the companion paper for pointing this out.}  In particular they, like us, look at a special case within the world of positroids and related objects which is enumerated by Catalan numbers.
+For them these are positroids coming from unit interval graphs, while for us they are the equivalent exact subdiagrams.
+Our objects are different, which can be seen by the fact that exact subdiagrams do not necessarily satisfy Lemma 4.1 of \cite{CGdyck}, but there are similarities in flavour with our arguments \hlfix{here and in our companion paper.}{Karen still needs to work on this}
 

### 2020-12-11 GWLDCII.tex
mostly working on paper 2

@@
 For instance, square moves and merge-expand moves give different graphical representations of the same positroid cell.
-There is no equivalent diagramatical equivalence for Wilson loop diagrams, though it has been shown (see \cite{wilsonloop, GWLDCI}) that certain classes of diagrams parametrize the same positroid cells.
+There is no equivalent diagramatical equivalence for Wilson loop diagrams, though it has been shown (see \cite{wilsonloop, generalcombinatoricsI}) that certain classes of diagrams parametrize the same positroid cells.
 On the other hand, in order to get a parametrization of the associated positroid cell from the plabic graphs, one must assign weights to the vertices and used them to compute Pl\"{u}cker coordinates \cite[Section 11]{Postnikov}, while the Wilson loop diagrams \emph{are} a parametrization of the associated positroid.
-I.e.
-one can compute the Pl\"{u}cker coordinates directed from the associated matrices.
+That is, one can compute the Pl\"{u}cker coordinates directly from the associated matrices.
 \sanote{This para is in answer to 1 and 4 of report Y.
@@
 We also show that the positroid cells associated to Wilson loop diagrams are all $3k$-dimensional, where $k$ is the number of propagators in the diagram; by contrast, the BCFW cells are all $4k$-dimensional \cite{Arkani-Hamed:2013jha}.
-This apparent contradiction is resolved by the non-orientability result of \cite{non-orientable}.
+\hlfix{This apparent contradiction}{I think we should say more in view of reviewer Y's comment 3 and we can probably phrase it more positively too} is resolved by the non-orientability result of \cite{non-orientable}.
 
@@
 We hope these results will pave the way for a general study of these poles in future.
-\sanote{cannot find where Wilson loop needs to become Wilson loop diagram (M correction 2)}
 
@@
 This makes it much easier to track how properties move through the bijection, as we do throughout the later sections.
-Furthermore, the above algorithm allows us to better understand the positroids associated to Wilson loop.
+Furthermore, the above algorithm allows us to better understand the positroids associated to Wilson loop diagrams.
 In particular, Corollary \ref{no coloops} shows that these positroids have no coloops, and gives an exact characterization of their loops.
-Many of the technical lemmas required to prove Theorem~\ref{res:alg gives GN} and Theorem~\ref{res alg gives correct GN} continue to be important in subsequent sections: in particular we have Lemma~\ref{lem sian}, which identifies certain configurations of propagators that must appear in any admissible Wilson loop diagram, and Lemma~\ref{vertex cyclic int lem}, which shows that the pattern of values that a propagator contributes to each term of the Grassmann necklace is both simple and predictable.
+Many of the technical lemmas required to prove Theorem~\ref{res:alg gives GN} and Theorem~\ref{res alg gives correct GN} continue to be important in subsequent sections.
+In particular we have Lemma~\ref{lem sian}, which identifies certain configurations of propagators that must appear in any admissible Wilson loop diagram, and Lemma~\ref{vertex cyclic int lem}, which shows that the pattern of values that a propagator contributes to each term of the Grassmann necklace is both simple and predictable.
 
@@
 Finally, in Section~\ref{sec poles} we characterize the denominator of the integrand of a Wilson loop diagram in terms of its associated matrix and Grassmann necklace.
-We show that given the physically correct representation of the positroid cell associated to a Wilson loop diagram, the irreducible factors of the denominator are exactly the set of irreducible factors of the minors of said representation given by the Grassmann necklace.
+We show that given the \hlfix{physically correct}{This was here before but can you remind me what it is hinting at?} representation of the positroid cell associated to a Wilson loop diagram, the irreducible factors of the denominator are exactly the set of irreducible factors of the minors of said representation given by the Grassmann necklace.
 This characterization is given explicitly by Algorithm~\ref{alg WLD to denom via GN} and Theorem~\ref{thm denom}.
@@
 \begin{dfn}\label{WLdfn}
-A {\bf Wilson loop diagram} $W = (\cP,V)$ consists of a cyclically ordered set $V$ with one distinguished element (this plays the role of the ``first'' element when we need a compatible linear ordering on $V$), and a set $\cP \subseteq V \times V$.
+A {\bf Wilson loop diagram} $W = (\cP,V)$ consists of a cyclically ordered set $V$ with one distinguished element (giving a compatible linear ordering on $V$ with the distinguished element as the first element), and a set $\cP$ of unordered pairs of elements of $V$.
 The elements of $V$ are the {\bf vertices} of $W$, and elements of $\cP$ are the {\bf propagators} of $W$.
@@
 
-Note that as defined, the propagators in a Wilson loop diagram are undirected, so $(i,j)$ and $(j,i)$ represent the same propagator.
-However, in this manuscript, we sometimes need to impose a direction on a propagator $p = (i,j)$, for example in order to consider the region ``inside'' or ``outside'' of $p$.
+Note that the propagators in a Wilson loop diagram are undirected, that is $\cP$ defines a symmetric binary relation on $V$.
+However, in some of the later arguments we need to impose a direction on a propagator $p = (i,j)$, for example in order to consider the region ``inside'' or ``outside'' of $p$.
 In this case, we write $(p,<_i)$ to indicate that $p$ is directed from edge $i$ to edge $j$, and $(p,<_j)$ for the opposite direction.
-\sanote{M comment 3.
-Skipped the symmetric binary bit, as I don't think it helps}
-
-We also impose the convention that all vertices should always be interpreted in terms of the cyclic order on $V$.
-So, for any $i\in V$ we will use $i+1$ to denote the successor of $i$ in $V$.
-In particular, if $V = [n]$ then $(n,n+3)$ means the propagator connecting edges $3$ and $n$.
-In particluar, many of our proofs rely on restricting our attention to a region of the diagram bounded by a given propagator, \hlfix{or to short propagators such as $(i,i+2)$}{is this parenthetical needed?
+
+We take the convention that all vertices should always be interpreted in terms of the cyclic order on $V$.
+So, for any $i\in V$ we will use $i+1$ to denote the successor of $i$ in the cyclic order on $V$.
+In particular, if $V = [n]$ then all vertices are interpreted modulo $n$ and $(n,n+3)$, for example, means the propagator connecting edges $3$ and $n$.
+%In particluar, many of our proofs rely on restricting our attention to a region of the diagram bounded by a given propagator, \hlfix{or to short propagators such as $(i,i+2)$}{is this parenthetical needed?
 M comment 4}.
 The regions thus defined behave the same way regardless of whether or not they contain the vertex labeled by $1$.
-However, we emphasize that this is different to the standard convention in the physics literature, where propagators are written $(i,j)$ with $1 \leq i<j \leq n$.
-
-We note that in this paper, we allow for the propagator set $\cP$ to be empty. This is for mathematical convenience, even though these diagrams do not correspond to tree level scattering amplitudes.
+However, we emphasize that
+
+On both of the last two points, we differ from the standard convention in the physics literature, where propagators are written as ordered pairs $(i,j)$ with $1 \leq i<j \leq n$.
+Additionally, note that in this paper, we allow for the propagator set $\cP$ to be empty.
+This is for mathematical convenience, even though these diagrams do not correspond to tree level scattering amplitudes.
+\hlfix{}{I changed the last three paragraphs a certain amount more on account of referee M's comments 3 and 4 -- we should discuss it.}
 
@@
 
-The first condition bounds the total number of propagators in the diagram, and comes from the fact that these diagrams represent $N^k$MHV interctions, where $k +4 <n$, see for instance the explanation in the introduction of \cite{adamo:2011pr} while the second limits how densely propagators can be fitted into any part of the diagram; in particular, the second condition prohibits propagators that connect two adjacent edges.
-This can be derived from the integrals associated to the diagrams, as in.
-Note that since $\cP$ is a set, we may not have two propagators starting and ending on the same pair of edges.
-\cite[Theorem 1.13]{wilsonloop}.
+The first condition bounds the total number of propagators in the diagram, while the second limitshow  densely  propagators  can  be  fitted  into  any  part  of  the  diagram.
 The third condition simply requires that propagators are non-crossing.
-This follows from the fact that these Wilson loop diagrams are a representation of planar Feynman diagrams of $N=4$ SYM theory.
-For a description of the relationship between planar Feynman diagram and planar Wilson loops, see the discussion in \cite[section 3]{LipstenMason}
+
+All three of these conditions arise from the physical interpretation of Wilson loop diagrams.
+The first condition comes from the fact that these diagrams represent $N^k$MHV interctions, where $k +4 <n$, see for instance the explanation in the introduction of \cite{adamo:2011pr}.
+The second condition can be derived from the integrals associated to the diagrams, \hlfix{as in.}{need end of sentence.}  Note that the second condition prohibits propagators that connect two adjacent edges.
+In our definition, $\cP$ is a set so we may not have two propagators starting and ending on the same pair of edges, but we have lost nothing of physical value by not allowing multiple propagators ending on the same pair of edges since these would also fail the second condition.
+\cite[Theorem 1.13]{wilsonloop}\hlfix{.}{This cite was sitting as a sentence on its own and I don't know what it was for.}  The third condition comes from the fact that these Wilson loop diagrams are a representation of planar Feynman diagrams of $N=4$ SYM theory.
+For a description of the relationship between planar Feynman diagram and planar Wilson loops, see the discussion in \cite[section 3]{LipsteinMason}.
+\hlfix{}{I changed the previous 2 paragraphs quite a bit, to separate the math intuition from the physical reasoning.}
 
@@
 The interested reader is referred to \cite{Adamo:2012xe,HeslopStewart,LipsteinMason} for more information about the integrand of $I(W)$.
-\sanote{not putting sections here, but I'd like a second thought}
+\sanote{not putting sections here, but I'd like a second thought -- what is this in response to?}
 
@@
 This has been checked for particular classes of examples (e.g.
-\cite{casestudy, Amplituhedronsquared, HeslopStewart}) but has not been proven in general.
+\cite{casestudy, Amplituhedronsquared, HeslopStewart}) but has not been proven in general.\hlfix{}{Is this updated for the spurious vs physical poles?}
 
@@
 
-This formulation for the denominator comes from the physics literature: see equation (2) in \cite{HeslopStewart}.
+This formulation for the denominator comes from the physics literature, see equation (2) in \cite{HeslopStewart}.
 In Section \ref{sec poles}, we give a geometric meaning to the factors $\{R_e\ |\ e \in V\}$ of $R(W)$.
@@
 A reader interested in studying these integrals further is invited to read \cite{casestudy, HeslopStewart, Amplituhedronsquared} in order to understand the connection to the scattering amplitude of $N=4$ SYM theory, the cancelation of spurious poles of specific instances of these integrals as well as explicit amplitude calculations.
-\sanote{I don't think I need to say more for point 2 of report Y?}
+\sanote{I don't think I need to say more for point 2 of report Y?
+-- maybe we should say ``differential form'' somewhere.
+Let's discuss.}
 
@@
 Postnikov shows in \cite{Postnikov} that the positroids of $\Gr(k,n)$ are indexed by many different collections of objects, each with their own advantages and disadvantages.
-The two most suited to our purposes are Grassmann necklaces \cite[section 16]{Postnikov} and Le diagrams\cite[section 6]{Postnikov}, which we discuss.
+The two most suited to our purposes are Grassmann necklaces \cite[section 16]{Postnikov} and Le diagrams \cite[section 6]{Postnikov}, which we discuss.
 In order to do so, we first need some preliminary definitions.
@@
 This in turn induces a total order on $\binom{[n]}{k}$, namely the lexicographic order with respect to $<_j$.
-It also induces a separate partial order $\gale{j}$ on $\binom{[n]}{k}$ (the {\bf Gale order} \cite{Gale}) \sanote{Not citing a thm here either as we give the dfn}, which is defined as follows: for
+It also induces a separate partial order $\gale{j}$ on $\binom{[n]}{k}$ (the {\bf Gale order} \cite{Gale}), which is defined as follows: for
 \[A = \{a_1 <_j a_2 <_j \dots <_j a_k\} \text{ and } B = \{b_1 <_j b_2 <_j \dots <_j b_k\} \in \binom{[n]}{k},\] we define
@@
 where the inequalities denote the $<_1$ order (subscripts suppressed for clarity).
-\item For $1 \leq j \leq r$ , place a $+$ in square $(a_j,b_j)$ of the diagram. (We will sometimes refer to this $+$ as being {\em in the $a_j \rightarrow b_j$ position}.)
+\item For $1 \leq j \leq r$ , place a $+$ in square $(a_j,b_j)$ of the diagram. (We will refer to this $+$ as being {\em in the $a_j \rightarrow b_j$ position}.)
 \end{itemize}
@@
 
-  Alternatively we can simply think about the condition of linear independence in the matrix $C(W)$, and then the corollary can also be proved directly by linear algebra and the definition of $C(W)$ as follows.
+  Alternatively we can simply think about the condition of linear independence in the matrix $C(W)$, and so the corollary can also be proved directly by linear algebra and the definition of $C(W)$ as follows.
 
@@
 The entry is nonzero if and only if the propagator is supported on that vertex.
-\hlfix{Consequently, a choice of $|J|$ nonzero entries of $C(W)$, one in each row associated to an element of $J$ and each in different columns, is equivalent to an assignment of the propagators of $J$ to supporting vertices so that no two are assigned to the same vertex.}{Added parenthetical commas according to M.23.
-better?}  Such an assignment of the propagators of $J$ to supporting vertices is exactly a map $f$ as described in the statement, hence proving the result.
+\hlfix{Consequently, take a choice of $|J|$ nonzero entries of $C(W)$, one in each row associated to an element of $J$ and each in different columns;  each such choice is equivalent to an assignment of the propagators of $J$ to supporting vertices so that no two are assigned to the same vertex.}{Added parenthetical commas according to M.23.
+better?
+I did a bit more, we can discuss}  Such an assignment of the propagators of $J$ to supporting vertices is exactly a map $f$ as described in the statement, hence proving the result.
 \end{proof}
@@
 By relating the behavior of the propagators in $W$ to the matroidal properties of $M(W)$, Agarwala and Marin-Amat also show that $M(W)$ is in fact a positroid whenever $W$ is admissible \cite[Corollary 3.39]{wilsonloop}.
-\todo{check tenses throughout (M.24)}
+\todo{check tenses throughout (M.24) -- maybe past is better, see the ``had'' at the beginning of the next paragraph, can we discuss?}
 
@@
 This is a useful result in and of itself, as it greatly simplifies the process of identifying the positroid associated to a given Wilson loop diagram.
-We also use it to characterize loops and coloops in the positroid associated to a Wilson loop diagram (Corollary \ref{no coloops}); the characterization of the coloops, in particular, was not at all clear from the definition of Wilson loop diagrams but is an easy corollary of the algorithm.
+We also use it to characterize loops and coloops in the positroid associated to a Wilson loop diagram (Corollary \ref{no coloops}).
+The characterization of the coloops, in particular, was not at all clear from the definition of Wilson loop diagrams but is an easy corollary of the algorithm.
 
@@
  \begin{enumerate}
-\item If $p = (i,i+3)$ is a propagator of length 3, then the middle vertex $i+2$ supports at most one propagator.
-\item If every vertex in $W$ supports at least one propagator, then $W$ admits at least one propagator of length 2.
+\item If $p = (i,i+3)$ is a propagator of length 3, then the middle vertex $i+2$ supports at most one propagator.\item If every vertex in $W$ supports at least one propagator, then $W$ admits at least one propagator of length 2.
 By the same reasoning, if $p=(i,j)$ is a propagator of $W$ and every vertex in the interval $[i,j]$ supports at least one propagator, then there is at least one propagator of length $2$ in $\mathcal{P}_{in}(p, <_i)$.
@@
 \begin{lem}\label{lem sian}
-  Let $W$ be a weakly admissible Wilson loop diagram with at least 5 vertices and in which each vertex supports at least one propagator.  Then at least one of the following two conditions hold:
+  Let $W$ be a weakly admissible Wilson loop diagram with at least 5 vertices and in which each vertex supports at least one propagator.  Then at least one of the following two conditions holds:
   \vspace{-0.5em}
@@
 
-We can then choose the orientation of $q_r$ so that the previous $p_i$ and $q_i$ are all on the outside of $q_r$, and restrict our attention to the subdiagram $(\cP_{in}(q_r),[n])$.
+We can choose the orientation of $q_r$ so that the previous $p_i$ and $q_i$ are all on the outside of $q_r$, and restrict our attention to the subdiagram $(\cP_{in}(q_r),[n])$.
 By the finiteness of $W$ this must eventually terminate in one of the desired configurations.
@@
 Start by choosing a propagator $p_1 = (j_1,j_1+2)$ of length 2 in $W$ (which exists by Remark~\ref{rem:props of length 2 and 3}).
-If it is part of one of the configurations we are looking for then we are done,
+If it is part of one of the configurations we are looking for we are done,
 %a configuration \eqref{eq:2 prop config} we are done,
@@
 From our existing assumptions, we know the following facts: $p_1$ is not in configuration \ref{item pair of 2s}, there are no propagators of length $3$, and every vertex supports at least one propagator.
-Therefore there must be a propagator of length $\geq 4$ with one end on edge $j_1$ or on edge $j_1-1$ or on edge $j_1-2$.
+Therefore, there must be a propagator of length $\geq 4$ with one end on edge $j_1$ or on edge $j_1-1$ or on edge $j_1-2$.
 Let $q_1 = (i_1, k_1)$ be this propagator, oriented such that $p_1 \in \cP_{out}(q_1,<_{i_1})$; see Figure~\ref{fig base case lem sian}.
@@
 By the original hypotheses on $W$, every vertex in $[i_r,k_{r+1}]$ (of which there are at least 4, since $\ell(q_r) \geq 4$) must support at least one propagator.
-Therefore $W_r$ admits at least one propagator of length 2 (by Remark~\ref{rem:props of length 2 and 3}) and no propagators of length $3$ (by our assumption on $W$).
+Therefore, $W_r$ admits at least one propagator of length 2 (by Remark~\ref{rem:props of length 2 and 3}) and no propagators of length $3$ (by our assumption on $W$).
 
@@
 %the configuration \eqref{eq:2 prop config}
-then we are done, so assume otherwise.
-
-Note that we could replace $q_r$ by another propagator $q'_{r}$ in $W_r = (\cP_{in}(q_r), [n])$, as long as $p_{r+1}$ and $q_r$ are on opposite sides of $q_r'$: such a new $q'_{r}$ would still satisfy all of the induction hypotheses.
-(See Figure~\ref{fig smallest q in lem sian}.) Therefore without loss of generality we may assume that $\cP_{in}(q_r)$ does not contain any propagators (other than $q_r$ itself) which satisfy the induction hypotheses, i.e.
+we are done, so assume otherwise.
+
+Note that we could replace $q_r$ by another propagator $q'_{r}$ in $W_r = (\cP_{in}(q_r), [n])$, as long as $p_{r+1}$ and $q_r$ are on opposite sides of $q_r'$.
+Such a new $q'_{r}$ would still satisfy all of the induction hypotheses.
+(See Figure~\ref{fig smallest q in lem sian}.) Therefore, without loss of generality we may assume that $\cP_{in}(q_r)$ does not contain any propagators (other than $q_r$ itself) which satisfy the induction hypotheses, i.e.
 we assume that there are no other propagators with $p_{r+1}$ on one side and $q_r$ on the other.
@@
 there are at most two vertices between an endpoint of $p_{r+1}$ and an endpoint of $q_r$).
-Then since $p_{r+1}$ has length 2, it must be that $(i_r+3)+1 \geq k_r-2$ and so $q_r$ has length $\leq 6$.
+Since $p_{r+1}$ has length 2, it must be that $(i_r+3)+1 \geq k_r-2$ and so $q_r$ has length $\leq 6$.
 By the minimality assumption on $q_r$, no propagator in $W_r$ has $q_r$ on one side and $p_{r+1}$ on the other side.
@@
 Therefore, this first case cannot occur.
-\todo{M.31 propagate commas after all therefores}
 
@@
 
-We have $j_{r+1}+4 \leq k_r-1$ in both of these cases: in the situation of the second bullet point this follows directly from the inequality, while in the third case it follows from the fact that $\ell(p_{r+1}) = 2$ and $\ell(q_r) \geq 4$.
-Therefore the vertex $j_{r+1}+4$ is in the interval $[i_r, k_r+1]$ but does not support either $q_r$ or $p_{r+1}$, and must therefore support some other propagator $t$.
+We have $j_{r+1}+4 \leq k_r-1$ in both of these cases.
+In the situation of the second bullet point this follows directly from the inequality, while in the third case it follows from the fact that $\ell(p_{r+1}) = 2$ and $\ell(q_r) \geq 4$.
+Therefore, the vertex $j_{r+1}+4$ is in the interval $[i_r, k_r+1]$ but does not support either $q_r$ or $p_{r+1}$, and must therefore support some other propagator $t$.
 Since $p_{r+1}$ is not part of configuration \ref{item pair of 2s} and $W_r$ has no propagators of length 3, it follows that $\ell(t) \geq 4$.
 If $q_r$ and $p_{r+1}$ were on different sides of $t$, this would contradict the minimality of $q_r$.
-Therefore we can orient $t$ so that all previous $q_i$ and $p_i$ belong to $\cP_{out}(t)$, and set $q_{r+1} = t$ to continue the induction.
-
-The overall result follows by induction. \todo{M.32 find and drop unnecessary 'then's}
+Therefore, we can orient $t$ so that all previous $q_i$ and $p_i$ belong to $\cP_{out}(t)$, and set $q_{r+1} = t$ to continue the induction.
+
+The overall result follows by induction.
 \end{proof}
@@
 \begin{rmk}
-In the case that all vertices of an admissible Wilson loop diagram $W$ support at least two propagators, then Lemma~\ref{lem sian} substantially simplifies.
+In the case that all vertices of an admissible Wilson loop diagram $W$ support at least two propagators, Lemma~\ref{lem sian} substantially simplifies.
 By Remark~\ref{rem:props of length 2 and 3}, $W$ has no propagators of length $3$.
 Configuration \ref{item big and 2} necessarily entails vertices with support $1$ as does configuration \ref{item pair of 2s} unless $j=i+2$.
-So in the case that $W$ has all vertices with support at least two then $W$ must contain a pair of propagators of length $2$  with the property that the first propagator is $(i, i+2)$, the second is $(i+2, i+4)$ and no other propagator ends on the edge $i+2$.
+So in the case that $W$ has all vertices with support at least two, $W$ must contain a pair of propagators of length $2$  with the property that the first propagator is $(i, i+2)$, the second is $(i+2, i+4)$ and no other propagator ends on the edge $i+2$.
 \end{rmk}
@@
 
-\begin{dfn} \label{proporderingdfn} \todo{M.36 wants this to be a remark. I disagree? But also note that there's nothing being defined here.}
-  There is an ordering on the propagators on $W = (\cP, [n])$ defined by $I_i$. This is the ordering in which they contribute to the algorithm as it constructs $I_i$.
+\begin{rmk}\todo{M.36 wants this to be a remark. I disagree? But also note that there's nothing being defined here. -- how about this?}
+Given $W=(\cP, [n])$ and $i\in [n]$, the order in which the propagators contribute to the algorithm as it constructs $I_i$ defines an order on $\cP$.
+  %  There is an ordering on the propagators on $W = (\cP, [n])$ defined by $I_i$. This is the ordering in which they contribute to the algorithm as it constructs $I_i$.
 %  $\cP = \{p_1, \ldots p_k\}$, where 
@@
 % (The superscript $W$ is omitted here to simplify the notation.)\note{Sian tweaked this slightly to emphasise the $<_i$ order, because standard convention in most papers is to write all GN terms in the 1-order.}
-\end{dfn}
 
@@
 This will follow directly from Corollary \ref{GN alg well defined}.
+\end{rmk}
 
@@
 \end{itemize}
-There are no propagators left in the diagram, so the algorithm terminates and we have ${I_1 = \{1,2,3,5\}}$, or $1235$ for short. 
+There are no propagators left in the diagram, so the algorithm terminates and we have ${I_1 = \{1,2,3,5\}}$, which we write more compactly as $1235$. 
 %So the propagators are ordered $r,q,p,s$ with respect to $I_1$, and 
@@
 Consider the diagram $W'$ formed by removing from $W$ all propagators that have already contributed to $I_i^W$.
-(This just replicates the behavior of the algorithm, which removes each propagator once it contributes to $I_i^W$.)  Now suppose for some other diagram $V$ on the same vertex set we are constructing $I_m^V$ for some $m$, and we are at step $j$ of the loop, for the same $j$ as above.
+(This replicates the behavior of the algorithm, which removes each propagator once it contributes to $I_i^W$.)  Now suppose for some other diagram $V$ on the same vertex set we are constructing $I_m^V$ for some $m$, and we are at step $j$ of the loop, for the same $j$ as above.
 Again obtain $V'$ from $V$ by removing all propagators assigned so far.
@@
 Now $q$ also contributes the $<_i$-maximal vertex in its support to $I_i$ and is an instance of the second possibility.
-Therefore it suffices to show that no admissible Wilson loop diagram admits the configuration illustrated in Case 2 of Figure~\ref{fig:no fourth vertex}.
+Therefore, it suffices to show that no admissible Wilson loop diagram admits the configuration illustrated in Case 2 of Figure~\ref{fig:no fourth vertex}.
 
@@
 It follows from the proof of Lemma~\ref{lem no fourth vertex} that in applying Algorithm~\ref{alg:put GN on WLD} to construct the set $I_i$, the algorithm can never reach the fourth vertex of a propagator's support (ordered with respect to $<_i$) without having already assigned that propagator.
-Therefore if the algorithm starts at vertex $i$, all propagators must have been eliminated by the time it gets to vertex $i-1$, ensuring that the algorithm is completed in at most one full circumnavigation of the diagram and that $I_i$ contains exactly $k$ distinct elements.
+Therefore, if the algorithm starts at vertex $i$, all propagators must have been eliminated by the time it gets to vertex $i-1$, ensuring that the algorithm is completed in at most one full circumnavigation of the diagram and that $I_i$ contains exactly $k$ distinct elements.
 \end{proof}
@@
 More generally, we know that whenever a propagator stops contributing a particular vertex, its next contribution must be its cyclically next vertex.
-This simple observation is surprisingly useful, to the point that the details which appear in the proof of Lemma~\ref{vertex cyclic int lem} are never needed again: the mere fact of non-empty intervals in the correct order suffices.
+This simple observation is surprisingly useful, to the point that the details which appear in the proof of Lemma~\ref{vertex cyclic int lem} are never needed again.
+The mere fact of non-empty intervals in the correct order suffices.
 \end{rmk}
@@
 
-\textbf{Cases 1 and 2}: These cases behave essentially identically (except when $j$ or $j+1$ are not in the support of $p$, which can occur in Case 2 only; see below) so we handle the majority of the proof for these two cases simultaneously.
+\textbf{Cases 1 and 2}: These cases behave very similarly except when $j$ or $j+1$ are not in the support of $p$, which can occur in Case 2 only; see below.
+Consequently we handle the majority of the proof for these two cases simultaneously.
 Write $p=(m,m+2)$ where $m\in \{i, i+1, l\}$.
@@
 
-Consider the Wilson loop diagram $X$ formed from $V$ by replacing the propagator $q = (i,j)$ with $q = (i, j-1)$;  $X$ is still admissible since we have not decreased the support of any set of propagators.
+Consider the Wilson loop diagram $X$ formed from $V$ by replacing the propagator $q = (i,j)$ with $q = (i, j-1)$.
+The diagram  $X$ is still admissible since we have not decreased the support of any set of propagators.
 % From the diagram we can see that $J_{j}^{V}(r) = J_{j}^{X}(r)$ for all $r\neq p$ (and in particular for $r=q$) and $J_{j}^{X}(r) = J_{j+1}^{X}(r)$ for $r\neq q,p$.  
 It follows from the position of $q$ in $X$ that $I_j^X(q) = j$, and from Lemma~\ref{lem no fourth vertex} that $I_{j+1}^X(q) \neq j$.
-By the induction hypothesis, we must therefore have $I_{j+1}^X(q) = i$; in particular, this means that if we start at $j+1$ and assign propagators to vertices according to the algorithm, when we reach vertex $i$ in $X$ all propagators other than $q$ must have been assigned.
-
-Therefore if we start at $j$ in $W$, we first assign $q$ to $j$ then proceed to assign as in $X$ starting at $j+1$, and hence when we get to $i$ the only remaining unassigned propagator is $p$.
+By the induction hypothesis, we must therefore have $I_{j+1}^X(q) = i$.
+In particular, this means that if we start at $j+1$ and assign propagators to vertices according to the algorithm, when we reach vertex $i$ in $X$ all propagators other than $q$ must have been assigned.
+
+Therefore, if we start at $j$ in $W$, we first assign $q$ to $j$ then proceed to assign as in $X$ starting at $j+1$, and hence when we get to $i$ the only remaining unassigned propagator is $p$.
 We obtain
@@
 We already know that $J_q^{V}(j+1) = \{j+1\}$; in particular this means that $q$ contributes $i$ in $I_{j+2}^{V}$, by the induction hypothesis applied to $V$.
-However the construction of $I^{V}_{j+1}$ first assigns $q$ to $j+1$ and then proceeds identically to $I^{V}_{j+2}$.
+However the construction of $I^{V}_{j+1}$ first assigns $q$ to $j+1$ and proceeds identically to $I^{V}_{j+2}$.
 In particular if $i$ was assigned in $I^{V}_{j+1}$, then it would not be available to assign to $q$ in $I^{V}_{j+2}$ as all other propagators supported at $i$ in $V$ come before $q$.
 
-Therefore $p$ is the only potentially unassigned propagator on edge $i$ when we reach vertex $i$ in the algorithm for $I_{j+1}^W$, and
+Therefore, $p$ is the only potentially unassigned propagator on edge $i$ when we reach vertex $i$ in the algorithm for $I_{j+1}^W$, and
     \[
@@
       \item 
-    If $m=l$ then either $a=2$ (so $l+1=m+1$, $j=m+2$, and $j+1=m+3$) or $a=3$ (so $l+1=m+1$, $l+2=m+2$, $j=m+3$, and $j+1$ is not in the support of $p$), and in both cases
+    If $m=l$ then either $a=2$ (so $l+1=m+1$, $j=m+2$, and $j+1=m+3$) or $a=3$ (so $l+1=m+1$, $l+2=m+2$, $j=m+3$, and $j+1$ is not in the support of $p$).  In both cases
     \begin{gather*}
@@
 In this case it is clear that applying Algorithm~\ref{alg:put GN on WLD} at vertex $i$ and vertex $i+1$ produces exactly the same result, i.e.
-$I_{i+1} = I_i$, and so $W$ is not a counterexample at all.
+$I_{i+1} = I_i$, contradicting that $W$ is a counterexample.
 
@@
 
-Let $W'$ be the diagram obtained from $W$ by removing only the propagator $p$.  Then we have
+Let $W'$ be the diagram obtained from $W$ by removing only the propagator $p$.  We have
 \begin{align*}
@@
 Since $\cP$ is finite, the sequence stabilizes in finitely many steps.
-Let $Q := \cup_{l \geq 0} Q_l$ be this set of propagators.
+Let $Q := \bigcup_{l \geq 0} Q_l$ be this set of propagators.
 
@@
 Since $p_r$ is clockwise of $q$, and $q$ cannot be supported on $I_i(p_s)$ since $q \not\in Q_{l-1}$, it follows that $I_i(p_s) <_i I_i(p_r)$.
-Therefore $q$ is inside $p_s$ with respect to $<_{a_s - 1}$ as well.
+Therefore, $q$ is inside $p_s$ with respect to $<_{a_s - 1}$ as well.
 
@@
 Now repeat the argument above with $p_s$ in place of $p_r$: if the other end of $p_s$ lands on an edge between $q$ and $j_m$ then we have $q \in \cP_{m-1}$ as above; if not then there exists some $p_t \in Q_{l-3}$ with $p_s$ supported on $I_i(p_t)$ and $q$ on the inside of $p_t$ in the $a_t-1$ order.
-Therefore $I_i(p_t) <_i I_i(p_r)$
+Therefore, $I_i(p_t) <_i I_i(p_r)$.
 %{\color{violet} May not be necessary, but I think highlighted tex follows from "Now repeat the argument...." \begin{enumerate}\item If $V(p_r) \in [a_r-1, j_m]$ (other end closer to $j_m$) then $q$ inside $p_r$ in $a_r-1$ order.
@@
 Let $V$ be $W$ with $p$ removed.
-Then we can express $I_*^W$ in terms of $I_*^V$ as indicated below:
+We can express $I_*^W$ in terms of $I_*^V$ as indicated below:
 
@@
 From Figure \ref{fig special p} we see that in both cases we have $I_n^{W}(p) = n$; thus from vertex 1 onwards the unassigned propagators are exactly those that appear in $V$.
-Therefore the algorithm continues as in $I_1^{V}$, i.e.
+Therefore, the algorithm continues as in $I_1^{V}$, i.e.
 we have $I_n^{W} = I_1^{V} \cup \{n\}$.
@@
 On the other hand, if $n-2\in I_{n-2}^{V}$ then we must be in Case 2 of Figure~\ref{fig special p} and we must have ${I_{n-2}^V(q) = I_{n-2}^W(q) = n-2}$ (since $q$ is always the clockwise-most propagator supported on vertex $n-2$).
-If $n-1 \not\in I_{n-2}^{V}$, then $I_{n-2}^W(p) = n-1$ and then the algorithm proceeds identically to $I_{n-2}^{V}$ for the remainder of its steps; thus $I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-1\}$ in this case.
+If $n-1 \not\in I_{n-2}^{V}$, then $I_{n-2}^W(p) = n-1$ and the algorithm proceeds identically to $I_{n-2}^{V}$ for the remainder of its steps; thus $I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-1\}$ in this case.
 
@@
 %all other propagators in $V$ had already been assigned when we reached vertex $n-5$; thus $q$ was the final propagator contributing to $I_n^{V}$.
-Therefore $I_{n-2}^{W} = (I_{n}^{V} \setminus \{n-5\}) \cup \{n-1, n-2\}$ in this case. This completes all cases for $I_{n-2}^{W}$.
+Therefore, $I_{n-2}^{W} = (I_{n}^{V} \setminus \{n-5\}) \cup \{n-1, n-2\}$ in this case. This completes all cases for $I_{n-2}^{W}$.
 
@@
 it satisfies $n-2 \not \in I_{n-2}^V$.
-Therefore we do not need to separately consider the case where $n-2\in I_{n-2}^V$ but $n-1\not\in I_{n-2}^V$, as it will be subsumed into Case 1 in the main theorem.
+Therefore, we do not need to separately consider the case where $n-2\in I_{n-2}^V$ but $n-1\not\in I_{n-2}^V$, as it will be subsumed into Case 1 in the main theorem.
 \end{rmk}
@@
 Note that $n-3\not\in I_{n-2}^{V}$ by Lemma~\ref{lem no fourth vertex}.
-Therefore the plusses contributed by $I_{n-2}^{W}$ are exactly the  plusses from $I_{n-1}^{V}$ along with the $(n-3)\rightarrow (n-2)$ plus.
+Therefore, the plusses contributed by $I_{n-2}^{W}$ are exactly the  plusses from $I_{n-1}^{V}$ along with the $(n-3)\rightarrow (n-2)$ plus.
 This gives the statement of the lemma.
@@
   If $n-3\not\in I_{k}^{V}$ then by Lemma~\ref{lem I} we have $I_{k}^{W} = I_k^{V}\cup \{n-3\}$.
-Then since $n-3$ is the largest element of $I_1^{W}$ this transformation leaves the disjoint paths unchanged and so the plusses carry over from $V$ to $W$ directly.
+Since $n-3$ is the largest element of $I_1^{W}$ this transformation leaves the disjoint paths unchanged and so the plusses carry over from $V$ to $W$ directly.
 
@@
 
-Therefore the Le diagram of $W$ contains $3(k-1)$ plusses in bijection with the plusses from the Le diagram of $V$ and 3 new plusses in the bottom row, yielding $3k$ in total.
+Therefore, the Le diagram of $W$ contains $3(k-1)$ plusses in bijection with the plusses from the Le diagram of $V$ and 3 new plusses in the bottom row, yielding $3k$ in total.
 Applying induction completes the proof.
@@
   \node at (\angle*1.5:\radius*2) {$I_2$};
-  \node[align = center] at (4*\angle:\radius*1.7) {$I_2(p) = 1,  \; I_2(s) = 4,$ \\[5pt] $I_2(q) = 5.$};
+  \node[align = center] at (4*\angle:\radius*1.7) {$I_2(p) = 2,  \; I_2(s) = 4,$ \\[5pt] $I_2(q) = 5.$};
   \end{scope} 
@@
 Since there is no cancellation between terms, this means that the full expansion over permutations of $\Delta_{I_i}$ contains no other nonzero terms and hence no other variables.
-Therefore $\Delta_{I_i}$ is equal to the determinant of the matrix obtained by taking the submatrix of $C(W)$ with columns indexed by $I_i$ and setting any variables not appearing in $\Delta_{I_i}$ to $0$.
+Therefore, $\Delta_{I_i}$ is equal to the determinant of the matrix obtained by taking the submatrix of $C(W)$ with columns indexed by $I_i$ and setting any variables not appearing in $\Delta_{I_i}$ to $0$.
 This new matrix is, up to permutations of rows and columns, a block matrix with one block for $\mathcal{P}'$ and $J$ and the other block for the complements.
@@
 No other propagators can be supported on these vertices since all other propagators are outside of $p$, and $p$ is the first propagator supported at $i$; this explains the zero block.
-Therefore $\Delta_{I_i} = \pm \det A \det C$, and both factors are nontrivial since at least one of $m$ and $m+1$ appears in $I_i$.
+Therefore, $\Delta_{I_i} = \pm \det A \det C$, and both factors are nontrivial since at least one of $m$ and $m+1$ appears in $I_i$.
 
@@
 Similarly to Case 1, let $T = \cP_{in}(q) \cup \{p\}$ in the $<_i$ order.
-Then all propagators in $T$ contribute to $I_i$ strictly before $j$ and no other propagators are supported on vertices strictly before $j$.
+All propagators in $T$ contribute to $I_i$ strictly before $j$ and no other propagators are supported on vertices strictly before $j$.
 Thus after permuting rows and columns as needed the matrix giving $\Delta_{I_i}$ has the form
@@
 Since there is no cancellation of terms in the expansion of $\Delta_{I_i}$, if any other terms appear then they will cause a factor which is not in the form described at the beginning of the proof of part (2).
-Therefore no such terms exist and $(x_{p,a}x_{q,a+1}-x_{p,a+1}x_{q,a})$ is a factor of $\Delta_{I_i}$.
+Therefore, no such terms exist and $(x_{p,a}x_{q,a+1}-x_{p,a+1}x_{q,a})$ is a factor of $\Delta_{I_i}$.
 
@@
 As in the proof of part (2), make a new admissible diagram by removing the propagators which come before those contributing to $f$ in the order imposed by $I_i$.
-Then without loss of generality we may assume $i=a$.
+Without loss of generality we may assume $i=a$.
 The cases in the proof of part (2) show how $\Delta_{I_i}$ factors: in particular the vertices supporting the other end of $p$ either do not appear in $I_i$, or they contribute to a different factor of $\Delta_{I_i}$ than $p$ and $a$ do.
 By assumption $b$ contributes to the same factor as $a$.
-Therefore $(a,b)$ is an edge defining an end of $p$, that is, $b = a+1$.
+Therefore, $(a,b)$ is an edge defining an end of $p$, that is, $b = a+1$.
 
@@
 Since $I_{i-1}(p) \neq a$, there must be some other propagator $s$ with $I_{i-1}(s) = a$ (else $q$ contributes $a$ to $I_{i-1}$).
-This propagator cannot lie on edge $a$, because then Remark~\ref{rmk cyclic} would imply that $I_i(s) \in \{a, a+1\}$, contradicting the fact that $I_i(p) = a$ and $I_i(q) = a+1$; thus $s$ has an end on edge $(a-1)$ and is inside $p$ in the $<_k$ order where $p=(k,a)$.
+This propagator cannot lie on edge $a$, because Remark~\ref{rmk cyclic} would imply that $I_i(s) \in \{a, a+1\}$, contradicting the fact that $I_i(p) = a$ and $I_i(q) = a+1$; thus $s$ has an end on edge $(a-1)$ and is inside $p$ in the $<_k$ order where $p=(k,a)$.
 
@@
 Since $p$ changed its association from $I_{i-1}$ to $I_i$, we have $I_{i-1}(p) = i-1$ by Lemma~\ref{vertex cyclic int lem}.
-From Figure~\ref{fig part 4} and Remark \ref{rmk algorithm locally same}, $p$ contributes first to  $I_{i-1}$ and  then proceeds identically to $I_i$ for all vertices inside $p$ in the $<_{i-1}$ ordering, implying that $I_{i-1}(s) = I_i(s)$.
+From Figure~\ref{fig part 4} and Remark \ref{rmk algorithm locally same}, $p$ contributes first to  $I_{i-1}$ and proceeds identically to $I_i$ for all vertices inside $p$ in the $<_{i-1}$ ordering, implying that $I_{i-1}(s) = I_i(s)$.
 Since $I_{i-1}(s) = a$ and $I_i(s) \neq a$, this is a contradiction.
@@
 Taking everything together we have that $R|\prod_{i=1}^n \Delta_{I_i}$ (from part (4)), $R$ contains all factors of $\prod_{i=1}^n \Delta_{I_i}$, and $R$ is square-free.
-Therefore the ideal generated by $R$ is the radical of the ideal generated by $\prod_{i=1}^n \Delta_{I_i}$.
+Therefore, the ideal generated by $R$ is the radical of the ideal generated by $\prod_{i=1}^n \Delta_{I_i}$.
   \end{enumerate}
@@
 By Definition~\ref{def R(W)} each linear factor appears with coefficient $1$ and each $2\times 2$ determinant factor appears with the same sign as the determinant of the corresponding minor in $C(W)$.
-Therefore $R=R(W)$.
+Therefore, $R=R(W)$.
 \end{proof}

### 2020-12-12 GWLDCI.tex
once through paper 2

@@
 For them these are positroids coming from unit interval graphs, while for us they are the equivalent exact subdiagrams.
-Our objects are different, which can be seen by the fact that exact subdiagrams do not necessarily satisfy Lemma 4.1 of \cite{CGdyck}, but there are similarities in flavour with our arguments \hlfix{here and in our companion paper.}{Karen still needs to work on this}
+Our objects are different, which can be seen by the fact that the exact subdiagram with 5 vertices (which is unique up to rotation) does not give a decorated permuation in the form of the Main Theorem of \cite{CGdyck}, but there are similarities in flavour with our arguments.
 

### 2020-12-12 GWLDCII.tex
once through paper 2

@@
 
-In continuing to characterize the positroid cells associated to Wilson loop diagrams, our next goal is to show that the dimension of the positroid cell defined by a Wilson loop diagram $(\cP, [n])$ has dimension $3|\cP|$; this is achieved in Theorem \ref{thm dim}.
+In continuing to characterize the positroid cells associated to Wilson loop diagrams, our next goal is to show that the dimension of the positroid cell defined by a Wilson loop diagram $(\cP, [n])$ is $3|\cP|$.
+This is achieved in Theorem \ref{thm dim}.
 
@@
 
-Our approach is much more explicit.
+\hlfix{Our approach is}{The transition between these paragraphs has been messed up a bit} much more explicit.
 By combining Algorithms~\ref{alg:put GN on WLD} and \ref{alg:GN to Le} (converting from Wilson loop diagram to Grassmann necklace, and Grassmann necklace to Le diagram respectively) we explicitly describe the effect of adding another propagator to a Wilson loop diagram in terms of the plusses of the associated Le diagrams.
-Recall that the dimension of a positroid cell is equal to the number of plusses in its associated Le diagram \cite[Theorem 6.5]{Postnikov}; thus understanding the effect of adding another propagator is sufficient to give a recursive proof of the $3|\cP|$-dimensionality of the cells.
+Recall that the dimension of a positroid cell is equal to the number of plusses in its associated Le diagram \cite[Theorem 6.5]{Postnikov}.
+Thus understanding the effect of adding another propagator is sufficient to give a recursive proof of the $3|\cP|$-dimensionality of the cells.
 
@@
   \begin{itemize}
-  \item $p = (i, n-1)$ for some $i$, and $p$ has no propagators inside it with regard to the $<_i$ ordering.
+  \item $p = (i, n-1)$ for some $i$, and $p$ has no propagators inside it with respect to the $<_i$ ordering.
   \item Either the edge $i$ in $W'$ only supports $p$, or the edge $i$ in $W'$ supports exactly one other propagator $q = (j,i)$, with no other propagators inside $q$ in the $<_j$ ordering. 
@@
 \begin{lem}\label{lem I}
-Let $W$ be an admissible Wilson loop diagram with $k\geq 1$ propagators, and suppose that $W$ admits one of the configurations described in Lemma~\ref{lem good p}, with $p$ and $q$ (if $q$ exists) both of length 2.
+Let $W$ be an admissible Wilson loop diagram with $k\geq 1$ propagators, and suppose $W$ admits one of the configurations described in Lemma~\ref{lem good p}, with $p$ and $q$ (if $q$ exists) both of length 2.
 Let $V$ be $W$ with $p$ removed.
@@
 
-We note for future reference that the arguments of the previous two paragraphs also imply that $n-2,n-1,n \not\in I_1^V$.
+We note for future reference that the arguments of the previous two paragraphs also imply that $n-2$, $n-1$, and $n$ are not in $I_1^V$.
 
 Next consider $I_n^{W}$.
-From Figure \ref{fig special p} we see that in both cases we have $I_n^{W}(p) = n$; thus from vertex 1 onwards the unassigned propagators are exactly those that appear in $V$.
+From Figure \ref{fig special p} we see that in both cases we have $I_n^{W}(p) = n$.
+Thus from vertex 1 onwards the unassigned propagators are exactly those that appear in $V$.
 Therefore, the algorithm continues as in $I_1^{V}$, i.e.
@@
 
-Finally, if $n-2,n-1 \in I_{n-2}^{V}$ then $I_{n-2}^W(q) = n-2$ and $I_{n-2}^W(p) = n-1$ as above, but some other propagator must have contributed $n-1$ to $I_{n-2}^{V}$ so we cannot use the same argument as above.
-\hlfix{When the algorithm $I_{n-2}^W$}{M.54 wants "When in the algorthm".
-I disagree.} reaches vertex $n$, only the propagators $p$ and $q$ have contributed; thus we proceed as in the construction of $I_n^{V}$ but without propagator $q$ by Remark \ref{rmk algorithm locally same}.
+Finally, if $n-2$ and$ n-1$ are in $I_{n-2}^{V}$ then $I_{n-2}^W(q) = n-2$ and $I_{n-2}^W(p) = n-1$ as above, but some other propagator must have contributed $n-1$ to $I_{n-2}^{V}$ so we cannot use the same argument as above.
+\hlfix{When, in the algorithm, the construction of $I_{n-2}^W$ reaches vertex $n$,}{M.54 wants "When in the algorthm".
+I disagree.
+-- how about this compromise} only the propagators $p$ and $q$ have contributed; thus we proceed as in the construction of $I_n^{V}$ but without propagator $q$ by Remark \ref{rmk algorithm locally same}.
 By Lemma~\ref{vertex cyclic int lem} we know that $I_n^V(q) = n-5$, and from Remark \ref{clockwise ordering rem} we see that the only way this could occur is if $q$ was the last to contribute to $I_{n-2}^V$.
@@
 Recall that $I_1$ determines the shape of the Le diagram: specifically, the elements of $I_1$ label the rows of the diagram, working from top right to bottom left.
-By the arguments in Lemma {\ref{lem I}} we know that ${n,n-1,n-2, n-3 \not\in I_1^{V}}$.
+By the arguments in Lemma {\ref{lem I}} we know that none of $n$, $n-1$, $n-2$, and $n-3$ are in $I_1^{V}$.
 These are the leftmost four columns of the diagram for $V$.
@@
   \end{equation}
-where $u$ and $v$ are two vertices; we will derive some properties of them below.
+where $u$ and $v$ are two vertices. We will derive some properties of $u$ and $v$ below.
 

### 2020-12-13 GWLDCI.tex
reviewed Karen  changes;  addressed comments

@@
 In \cite[section 3]{wilsonloop}, Agarwala and Marin-Amat show that every weakly admissible Wilson loop diagram $W$ with $k$ propagators defines a positroid $M(W)$ of rank $k$ on a base set of size $n$.
-\hlfix{Combined with Postnikov's work in {\cite{Postnikov}}, this shows that each admissible Wilson loop diagram corresponds to a convex subset of $\Gr(k,n)$}{fix citation.
-Ask Cameron?}, thus connecting the geometry of Wilson loop diagrams with the geometry underlying the Amplituhedron.
+\hlfix{It is a direct consequence of Postnikov's work, {\cite[Theorem 6.5]{Postnikov}}, that positroid cells are convex subset of $\Gr(k,n)$}{I  hate  saying it this way, but I can't find it directly written anywhere}.
+Putting these together gives that the Wilson loop diagrams  correspond to convex subsets of $\Gr(k,n)$, connecting the geometry of Wilson loop diagrams with the geometry underlying the Amplituhedron.
 

### 2020-12-13 GWLDCII.tex
reviewed Karen  changes;  addressed comments

@@
 While the Wilson loop diagrams contain the exact same information as the $N^kMHV$ diagrams for the purposes of understanding $N=4 SYM$ theory, this dual perspective is better suited to understanding the combinatorics and geometry associated to the theory.}{added to address request (3) of report M -- let's discuss, I don't think this makes sense as written} Therefore, \hlfix{we part with the notation in the physics literature, and name these dual graphs}{I'm not sure that's true} of $N^kMHV$ diagrams Wilson loop diagrams in order to emphasize the combinatorial and geometric significane of these object.
-In \cite{wilsonloop}, Agarwala and Marin-Amat uncovered a connection between the Feynman integrals developed in \hlfix{this}{What does this ``this'' refer to, also this sentence should probably start a new paragraph} literature and positroids, defined  as matroids that can be realized as an element of $\Gr(k,n)$.
+
+In \cite{wilsonloop}, Agarwala and Marin-Amat uncovered a connection between the Feynman integrals developed in the $N^kMHV$ \st{this}\todo{What does this ``this'' refer to, also this sentence should probably start a new paragraph} literature and positroids, defined  as matroids that can be realized as an element of $\Gr(k,n)$.
 Other work has shown a connection between the volume filled by Wilson loop diagrams and the Amplituhedron \cite{casestudy, Amplituhedronsquared}.
@@
 
-In the above work and elsewhere, it is clear that while the space \hlfix{filled by}{``filled by'' vs ``parameterized by'' in the previous paragraph} the Wilson loop diagrams is related to the Amplituhedron, they are not the same space.
+In the above work and elsewhere, it is clear that while the space \hlfix{parametreized by}{``filled by'' vs ``parameterized by'' in the previous paragraph} the Wilson loop diagrams is related to the Amplituhedron, they are not the same space.
 For instance, it is conjectured that the Amplituhedron is orientable, whereas Agarwala and Marcott show in \cite{non-orientable} that the space parametrized by the Wilson loop diagrams as a subspace of $\Gr(k, n+1)$ can be seen as a non-orientable vector bundle over some submanifold of $\Gr(k,n)$.
@@
 We also show that the positroid cells associated to Wilson loop diagrams are all $3k$-dimensional, where $k$ is the number of propagators in the diagram; by contrast, the BCFW cells are all $4k$-dimensional \cite{Arkani-Hamed:2013jha}.
-\hlfix{This apparent contradiction}{I think we should say more in view of reviewer Y's comment 3 and we can probably phrase it more positively too} is resolved by the non-orientability result of \cite{non-orientable}.
+In \cite{non-orientable} the authors note that the Wilson loop diagrams only correspond to positroid cells when the gauge vector is ignored.
+Including the gauge vector defines a $4k$ dimensional subspace of $\mathbb{G}r_\R(k,n+1)$.\st{This apparent contradiction}\todo{I think we should say more in view of reviewer Y's comment 3 and we can probably phrase it more positively too} \st{is resolved by the non-orientability result of {\cite{non-orientable}}.}
 
@@
 Finally, in Section~\ref{sec poles} we characterize the denominator of the integrand of a Wilson loop diagram in terms of its associated matrix and Grassmann necklace.
-We show that given the \hlfix{physically correct}{This was here before but can you remind me what it is hinting at?} representation of the positroid cell associated to a Wilson loop diagram, the irreducible factors of the denominator are exactly the set of irreducible factors of the minors of said representation given by the Grassmann necklace.
+We show that given the \hlfix{physically correct}{This was here before but can you remind me what it is hinting at?}\sanote{This  is awkward.
+I think I meant that there are many representations of the positroid cell; wwe want thhe representattion that is  good for the physics.} representation of the positroid cell associated to a Wilson loop diagram, the irreducible factors of the denominator are exactly the set of irreducible factors of the minors of said representation given by the Grassmann necklace.
 This characterization is given explicitly by Algorithm~\ref{alg WLD to denom via GN} and Theorem~\ref{thm denom}.
@@
 The first condition comes from the fact that these diagrams represent $N^k$MHV interctions, where $k +4 <n$, see for instance the explanation in the introduction of \cite{adamo:2011pr}.
-The second condition can be derived from the integrals associated to the diagrams, \hlfix{as in.}{need end of sentence.}  Note that the second condition prohibits propagators that connect two adjacent edges.
+The second condition can be derived from the integrals associated to the diagrams, as in \cite[Theorem 1.13]{wilsonloop}.
+Note that the second condition prohibits propagators that connect two adjacent edges.
 In our definition, $\cP$ is a set so we may not have two propagators starting and ending on the same pair of edges, but we have lost nothing of physical value by not allowing multiple propagators ending on the same pair of edges since these would also fail the second condition.
-\cite[Theorem 1.13]{wilsonloop}\hlfix{.}{This cite was sitting as a sentence on its own and I don't know what it was for.}  The third condition comes from the fact that these Wilson loop diagrams are a representation of planar Feynman diagrams of $N=4$ SYM theory.
+The third condition comes from the fact that these Wilson loop diagrams are a representation of planar Feynman diagrams of $N=4$ SYM theory.
 For a description of the relationship between planar Feynman diagram and planar Wilson loops, see the discussion in \cite[section 3]{LipsteinMason}.
-\hlfix{}{I changed the previous 2 paragraphs quite a bit, to separate the math intuition from the physical reasoning.}
+\hlfix{}{I changed the previous 2 paragraphs quite a bit, to separate the math intuition from the physical reasoning.}  \sanote{fixed cittation issues. Like the  rewrite}}
 
@@
 The interested reader is referred to \cite{Adamo:2012xe,HeslopStewart,LipsteinMason} for more information about the integrand of $I(W)$.
-\sanote{not putting sections here, but I'd like a second thought -- what is this in response to?}
+\sanote{not putting sections here, but I'd like a second thought -- what is this in response to?} \sanote{I'm not sure  at this point.
+}
 
 For a fixed number of propagators and particles, the tree level amplitude of the Wilson loop diagrams is computed as the sum of the $I(W)$ for all $W$ of the correct size.
-By {\cite{Adamo:2011pv,Adamo:2012xe,Arkani-Hamed:2013jha}} this sum is finite for all sets of external particles,\sanote{fix this citation} i.e.
+By {\cite{Adamo:2011pv,Britto:2005fq,Arkani-Hamed:2013jha}} this sum is finite for all sets of external particles, i.e.
 \bas \mathcal{A}_{k, n}^{tree} = \sum_{\substack{W = (\cP, [n]), \\ |\cP| = k}} I(W) <\infty. \eas
 
-This would certainly hold if  the singularities in the integrands $\Omega(W)$ cancel out in the sum; in particular, all poles arising from $R(W)$ must cancel.
+This would certainly hold if  the singularities in the integrands $\Omega(W)$ (the spurious poles of the theory) cancel out in the sum; in particular, if all poles arising from $R(W)$ must cancel.
 Specifically, it is conjectured that these poles cancel on the boundaries of the positroid cells $\Sigma(W)$, analogous to the analysis in \cite{Arkani-Hamed:2013jha}.
 This has been checked for particular classes of examples (e.g.
-\cite{casestudy, Amplituhedronsquared, HeslopStewart}) but has not been proven in general.\hlfix{}{Is this updated for the spurious vs physical poles?}
+\cite{casestudy, Amplituhedronsquared, HeslopStewart}) but has not been proven in general.\hlfix{}{Is this updated for the spurious vs physical poles?}  \sanote{these arre all spurioous poles.
+Needs  more?}
 
@@
 Combining this with Theorem~\ref{thm dim}, we see that the Deodhar component associated to a Wilson loop diagram is $4|\cP|$-dimensional, showing that the geometry underlying the Wilson loop diagrams is consistent with the geometry underlying the Amplituhedron.
-
-Marcott in \cite[Theorem 8.4]{WLDdim} gives a different proof of the $3|\cP|$-dimensionality of $M(W)$ which is geometric and more elegant, but it is not easy to track the effect of a particular propagator.
-It is worth noting that while the Amplituhedon is also defined by a projection of a set of $4|\cP|$ dimensional positroid cells, there is no evidence to suggest that the $3|\cP|$ dimensional cells of $\Gr(|\cP|, n)$ defiining the Wilson loop diagrams are related to the $4|\cP|$ dimensional cells defining the Amplituhedron.
+It is worth noting that the Amplituhedon is defined by a projection of a set of $4|\cP|$ dimensional positroid cells, while the $4|\cP|$-dimensional cells of the Wilson loop diagram lie in $\mathbb{G}r_\R$.
+To  date, there is no evidence to suggest that the $3|\cP|$ dimensional positive cells of $\Gr(|\cP|, n)$ defining the Wilson loop diagrams are related to the $4|\cP|$ dimensional positive cells defining the Amplituhedron.
 \sanote{This para adresses point 3 of report Y.
 Should there be a similar paragraph in the intro?
-Should it be moved?}
-
-\hlfix{Our approach is}{The transition between these paragraphs has been messed up a bit} much more explicit.
-By combining Algorithms~\ref{alg:put GN on WLD} and \ref{alg:GN to Le} (converting from Wilson loop diagram to Grassmann necklace, and Grassmann necklace to Le diagram respectively) we explicitly describe the effect of adding another propagator to a Wilson loop diagram in terms of the plusses of the associated Le diagrams.
+Should it be moved?} \sanote{futzed some  more}
+
+Marcott in \cite[Theorem 8.4]{WLDdim} also gives a proof of the $3|\cP|$-dimensionality of $M(W)$ which is much more geometric.
+However, it is not easy to track the effect of a particular propagator in that proof.
+By contrast, our approach is\todo{The transition between these paragraphs has been messed up a bit} much more constructive, and elucidates how each additional propagator contributes to tthe dimension.
+\sannote{fiddled with this transition} By combining Algorithms~\ref{alg:put GN on WLD} and \ref{alg:GN to Le} (converting from Wilson loop diagram to Grassmann necklace, and Grassmann necklace to Le diagram respectively) we explicitly describe the effect of adding another propagator to a Wilson loop diagram in terms of the plusses of the associated Le diagrams.
 Recall that the dimension of a positroid cell is equal to the number of plusses in its associated Le diagram \cite[Theorem 6.5]{Postnikov}.
@@
 
-Since SYM $N=4$ is a finite theory {\cite{Alday:2007hr, ParkeTaylorids}}, the scattering amplitudes (and thus the holomorphic Wilson loops $\,\mathfrak{W}_{k,n}$) are finite.\sanote{Fix citations} That is, for a fixed set of external particles $\cZ$ we must have
+Since SYM $N=4$ is a finite theory {\cite{Alday:2007hr, ParkeTaylorids}}, the scattering amplitudes (and thus the holomorphic Wilson loops $\,\mathfrak{W}_{k,n}$) are finite.
+That is, for a fixed set of external particles $\cZ$ we must have
 \bas \sum_{W \text{ s.t. } |\cP| = k} I(W)(\cZ) <\infty \;.\eas

### 2020-12-14 GWLDCI.tex
fixed so it compiles

@@
 In \cite[section 3]{wilsonloop}, Agarwala and Marin-Amat show that every weakly admissible Wilson loop diagram $W$ with $k$ propagators defines a positroid $M(W)$ of rank $k$ on a base set of size $n$.
-\hlfix{It is a direct consequence of Postnikov's work, {\cite[Theorem 6.5]{Postnikov}}, that positroid cells are convex subset of $\Gr(k,n)$}{I  hate  saying it this way, but I can't find it directly written anywhere}.
+It is a direct consequence of Postnikov's work, {\cite[Theorem 6.5]{Postnikov}},\hlfix{ that positroid cells are convex subset of $\Gr(k,n)$}{I  hate  saying it this way, but I can't find it directly written anywhere}.
 Putting these together gives that the Wilson loop diagrams  correspond to convex subsets of $\Gr(k,n)$, connecting the geometry of Wilson loop diagrams with the geometry underlying the Amplituhedron.

### 2020-12-14 GWLDCII.tex
fixed so it compiles

@@
 For a description of the relationship between planar Feynman diagram and planar Wilson loops, see the discussion in \cite[section 3]{LipsteinMason}.
-\hlfix{}{I changed the previous 2 paragraphs quite a bit, to separate the math intuition from the physical reasoning.}  \sanote{fixed cittation issues. Like the  rewrite}}
+\hlfix{}{I changed the previous 2 paragraphs quite a bit, to separate the math intuition from the physical reasoning.}  \sanote{fixed cittation issues. Like the  rewrite}
 
@@
 By contrast, our approach is\todo{The transition between these paragraphs has been messed up a bit} much more constructive, and elucidates how each additional propagator contributes to tthe dimension.
-\sannote{fiddled with this transition} By combining Algorithms~\ref{alg:put GN on WLD} and \ref{alg:GN to Le} (converting from Wilson loop diagram to Grassmann necklace, and Grassmann necklace to Le diagram respectively) we explicitly describe the effect of adding another propagator to a Wilson loop diagram in terms of the plusses of the associated Le diagrams.
+\sanote{fiddled with this transition} By combining Algorithms~\ref{alg:put GN on WLD} and \ref{alg:GN to Le} (converting from Wilson loop diagram to Grassmann necklace, and Grassmann necklace to Le diagram respectively) we explicitly describe the effect of adding another propagator to a Wilson loop diagram in terms of the plusses of the associated Le diagrams.
 Recall that the dimension of a positroid cell is equal to the number of plusses in its associated Le diagram \cite[Theorem 6.5]{Postnikov}.

### 2020-12-14 GWLDCI.tex
final changes discussed in meeting for paper 1

@@
 % Annotations
-\usepackage{soul}
+%\usepackage{soul}
 \usepackage[colorinlistoftodos,textsize=footnotesize]{todonotes}
-\newcommand{\hlfix}[2]{\texthl{#1}\todo{#2}}
-\newcommand{\hlnew}[2]{\texthl{#1}\todo[color=green!40]{#2}}
-\newcommand{\sanote}{\todo[color=violet!30]}
-\newcommand{\note}{\todo[color=green!40]}
-\newcommand{\newstart}{\note{The inserted text starts here}}
-\newcommand{\newfinish}{\note{The inserted text finishes here}}
-\setstcolor{red}
+%\newcommand{\hlfix}[2]{\texthl{#1}\todo{#2}}
+%\newcommand{\hlnew}[2]{\texthl{#1}\todo[color=green!40]{#2}}
+%\newcommand{\sanote}{\todo[color=violet!30]}
+%\newcommand{\note}{\todo[color=green!40]}
+%\newcommand{\newstart}{\note{The inserted text starts here}}
+%\newcommand{\newfinish}{\note{The inserted text finishes here}}
+%\setstcolor{red}
 %***************************
@@
 
-Both the Amplituhedron literature and the Wilson loop literature \hlfix{associate $n$ particle $N^kMHV$ interactions in SYM $N=4$}{make more prominent?} theory to volume forms on a set of positroid cells of $\Gr(k,n)$.
+Both the Amplituhedron literature and the Wilson loop literature associate $n$ particle $N^kMHV$ interactions in SYM $N=4$ theory to volume forms on a set of positroid cells of $\Gr(k,n)$.
 This gives a CW complex of some submanifold in $\Gr(k,n)$, and understanding the geometry and topology of these spaces is the subject of ongoing research.
@@
 
-There are a few things to note here.
-First, what we call weakly admissible here is called admissible in (\cite{wilsonloop}, see definition 1.11 and section 1.3).
-\hlfix{Many of the results below still apply when the hypothesis of admissibility is changed to weak admissibility.}{Propagate "weakly" through document}
-
+There are a few things to note here.  First, what we call weakly admissible here is called admissible in (\cite{wilsonloop}, see definition 1.11 and section 1.3).
 Note also that if two propagators have the same pair of supporting edges, or if a propagator is supported on two adjacent edges, then the Wilson loop diagram is not admissible or even weakly admissible.
-
 Further, if we take any admissible Wilson loop diagram and remove the non-supporting vertices, we obtain a weakly admissible Wilson loop diagram that may or may not be admissible itself.
 
-For the remainder of the paper, we will restrict our attention to admissible Wilson loop diagrams and subdiagrams thereof.
+For the remainder of the paper, we will restrict our attention to admissible and weakly admissible Wilson loop diagrams.
 
@@
 In \cite[section 3]{wilsonloop}, Agarwala and Marin-Amat show that every weakly admissible Wilson loop diagram $W$ with $k$ propagators defines a positroid $M(W)$ of rank $k$ on a base set of size $n$.
-It is a direct consequence of Postnikov's work, {\cite[Theorem 6.5]{Postnikov}},\hlfix{ that positroid cells are convex subset of $\Gr(k,n)$}{I  hate  saying it this way, but I can't find it directly written anywhere}.
+It is a direct consequence of Postnikov's work, {\cite[Theorem 6.5]{Postnikov}}, that positroid cells are convex subset of $\Gr(k,n)$.
 Putting these together gives that the Wilson loop diagrams  correspond to convex subsets of $\Gr(k,n)$, connecting the geometry of Wilson loop diagrams with the geometry underlying the Amplituhedron.
@@
 \begin{thm} \label{thm WLD defines matroid} \cite[Theorem 3.6]{wilsonloop} Any Wilson loop diagram $W =(\cP, [n])$ defines a matroid $M(W)$ with ground set $[n]$.
-The independent sets are exactly those subsets $V \subseteq [n]$ \hlfix{such that for every subset of vertices, $U\subseteq V$, supports at least as many propagators as vertices in the set, $|\Prop(U)| \geq |U|$}{This edit isn't grammatically correct and is more complicated than what the referee asked for, could you fix it?}.
+The independent sets are exactly those subsets $V \subseteq [n]$ such that every $U\subseteq V$ satisfies $|\Prop(U)| \geq |U|$.
 \label{thm:WLDmatroid}\end{thm}
@@
 Item 2 is \cite[Lemma 3.27]{wilsonloop}.
-Item 3 is a direct consequence of \cite[Lemma 3.20]{wilsonloop}\sanote{ This is the right reference in both arXiv and CMP versions.
-Don't know what to do?} and the fact that $F(P_1)^c = V(P_1^c)$, and item 5 is given in \cite[Lemma 3.28]{wilsonloop}.
+Item 3 is a direct consequence of \cite[Theorem 3.20]{wilsonloop} and the fact that $F(P_1)^c = V(P_1^c)$, and item 5 is given in \cite[Lemma 3.28]{wilsonloop}.
 
@@
 
-\section{Matroids, triangulations, and equivalence classes of Wilson loop diagrams\label{sec equiv}} \todo{rephrase in terms of weakly.}
+\section{Matroids, triangulations, and equivalence classes of Wilson loop diagrams\label{sec equiv}}
 
@@
 
-There are many other instances of this basic methodology in combinatorics, but we'd like to point out one in particular that involves many objects closely related to those we use here, \cite{CGdyck}.\footnote{Thanks to the referee for the companion paper for pointing this out.}  In particular they, like us, look at a special case within the world of positroids and related objects which is enumerated by Catalan numbers.
+There are many other instances of this basic methodology in combinatorics, but we'd like to point out one in particular that involves many objects closely related to those we use here, \cite{CGdyck}\footnote{Thanks to the referee for the companion paper, \cite{generalcombinatoricsII}, for pointing this out.}.
+In particular they, like us, look at a special case within the world of positroids and related objects which is enumerated by Catalan numbers.
 For them these are positroids coming from unit interval graphs, while for us they are the equivalent exact subdiagrams.

### 2020-12-14 GWLDCII.tex
changes from on the phone

@@
 The denominator $R(W)$ is given in Definition~\ref{def R(W)} below.
+
+The differential form $\Omega(W)$ is playing a similar role to that of volume forms in the Amplituhedron literature.
 For the purposes of this paper, we restrict our attention to $\Omega(W)$ only, and ignore the $\delta$ function in the integrand of $I(W)$.
 The interested reader is referred to \cite{Adamo:2012xe,HeslopStewart,LipsteinMason} for more information about the integrand of $I(W)$.
-\sanote{not putting sections here, but I'd like a second thought -- what is this in response to?} \sanote{I'm not sure  at this point.
-}
 
@@
 
-This would certainly hold if  the singularities in the integrands $\Omega(W)$ (the spurious poles of the theory) cancel out in the sum; in particular, if all poles arising from $R(W)$ must cancel.
+This would certainly hold if the singularities in the integrands $\Omega(W)$ cancel out in the sum.
+The singularities coming from the zeros of $R(W)$ are the spurious poles of the theory and the physical theory tells us that they should cancel.
+%(the spurious poles of the theory) cancel out in the sum; in particular, if all poles arising from $R(W)$ must cancel.
 Specifically, it is conjectured that these poles cancel on the boundaries of the positroid cells $\Sigma(W)$, analogous to the analysis in \cite{Arkani-Hamed:2013jha}.
 This has been checked for particular classes of examples (e.g.
-\cite{casestudy, Amplituhedronsquared, HeslopStewart}) but has not been proven in general.\hlfix{}{Is this updated for the spurious vs physical poles?}  \sanote{these arre all spurioous poles.
-Needs  more?}
+\cite{casestudy, Amplituhedronsquared, HeslopStewart}) but has not been proven in general.
 
@@
 
+In order to compute the contribution of this diagram to the tree level scattering amplitude one needs only to localize the differential form $\Omega(W)$ with respect to a delta function that evaluates the matrix $C(W)$ at the external momenta.
+
 A reader interested in studying these integrals further is invited to read \cite{casestudy, HeslopStewart, Amplituhedronsquared} in order to understand the connection to the scattering amplitude of $N=4$ SYM theory, the cancelation of spurious poles of specific instances of these integrals as well as explicit amplitude calculations.
-\sanote{I don't think I need to say more for point 2 of report Y?
--- maybe we should say ``differential form'' somewhere.
-Let's discuss.}
 

### 2020-12-20 GWLDCII.tex
going back through the referee reports, two pages left of report M

@@
 This paper is the second in a two part series investigating the combinatorics and geometry underlying Wilson loop diagrams in SYM $N=4$ theory.
-This series lays out several results about the relationship between Wilson loop diagrams and the positroid cells that give a CW complex structure to the positive Grassmanian.
+This series lays out several results about the relationship between Wilson loop diagrams and the positroid cells that give a CW complex structure to the positive Grassmannian.
 This paper is concerned with identifying which positroid cells correspond to which Wilson loop diagrams, and how this translates to a geometric tiling of a subspace of the positive Grassmannians.
@@
 It is worth noting at this point that the \hlfix{combinatorics of the Wilson loop diagrams are different from the combinatorics of the Amplituhedron}{I think we should discuss this paragraph -- it may be misleading in a bad way}, just as the the volume forms associated to the BCFW diagrams are different from those associated to the Wilson Loop diagrams.
-For instance, the BCFW are most readily related to the geometry of a postive Grassmanian via plabic graphs.
+For instance, the BCFW are most readily related to the geometry of a postive Grassmannian via plabic graphs.
 Meanwhile, the Wilson loop diagrams correspond to matrices with variable valued entries (see section \ref{section WLD background}) and Grassmann Necklaces (see Algorithm \ref{alg:put GN on WLD}).
@@
 \[\Prop(U) = \{ p \in \cP\ |\ V(p) \cap U \neq \emptyset \}.\]
-Note that a propagator in $\Prop(U)$ may not have its entire support contained in $U$. 
+Note that a propagator in $\Prop(U)$ does not necessarily have its entire support contained in $U$. 
 \item Vertices of $W$ that do not support any propagators are called {\bf non-supporting}.
@@
 \begin{dfn}\label{admisdfn}
-A Wilson loop diagram $W = (\cP, V)$ is called {\bf admissible} if the following conditions hold:
+A Wilson loop diagram $W = (\cP, V)$ is called {\bf admissible} if the following conditions hold.
 \begin{enumerate}
@@
 \item For each non-empty subset of propagators, $Q \subseteq \cP$, we have $|V(Q)|\geq |Q| + 3$.
-\item There are no crossing propagators: that is, there does not exist ${\{(i,j),(k,l)\} \subseteq \cP}$ such that $i < k < j < l$.
+\item There are no crossing propagators. That is, there does not exist ${\{(i,j),(k,l)\} \subseteq \cP}$ such that $i < k < j < l$.
 \end{enumerate}
@@
 
-Note that a subdiagram $(Q,U)$ of an admissible Wilson loop diagram need not be admissible itself: it inherits conditions 2 and 3 automatically, but we could have $|U| = |Q| + 3$.
+Note that a subdiagram $(Q,U)$ of an admissible Wilson loop diagram need not be admissible itself.
+It inherits conditions 2 and 3 automatically, but we could have $|U| = |Q| + 3$.
 If a Wilson loop diagram satisfies conditions 2 and 3 of Definition~\ref{admisdfn}, we call it {\bf weakly admissible}.
@@
 
-With this motivation in mind, in Section~\ref{sec poles} of this paper we study the denominator $R(W)$ of $\Omega(W)$. The definition of $R(W)$ is as follows.
+With this motivation in mind, in Section~\ref{sec poles} of this paper we study the denominator $R(W)$ of $\Omega(W)$. The definition of $R(W)$ is as follows:
 
@@
 
-For our purposes, a {\bf positroid} is\footnote{Note that matroid isomorphism allows arbitrary permutations of the ground set but positroid isomorphism allows only cyclic permutations, so the property of being a positroid is not in general preserved by matroid isomorphism.} a matroid $M$ (with ground set $[n]$ and bases set $\cB \subseteq \binom{[n]}{k}$) which can be represented by an element of the positive Grassmannian $\Gr(k,n)$.
-In other words, there exists a full-rank $k\times n$ real matrix whose $k\times k$ minors are all nonnegative and such that the minor comprised of the columns indicated by the set $J$
+For our purposes, a {\bf positroid} is\footnote{Note that matroid isomorphism allows arbitrary permutations of the ground set but positroid isomorphism allows only cyclic permutations, so the property of being a positroid is not in general preserved by matroid isomorphism.} a matroid $M$ (with ground set $[n]$ and set of bases $\cB \subseteq \binom{[n]}{k}$) which can be represented by an element of the positive Grassmannian $\Gr(k,n)$.
+In other words, there exists a full-rank $k\times n$ real matrix whose $k\times k$ minors are all nonnegative and such that the minor comprised of the columns indexed by elements of $J$
 is positive if and only if $J \in \cB$.
@@
 \begin{dfn}\label{def:grassmann necklace}
-A {\bf Grassmann necklace} of type $(k,n)$ is a sequence $(I_1, \dots, I_n)$ of $n$ sets $I_i \in \binom{[n]}{k}$ such that for each $i \in [n]$ the following statements are true:
+A {\bf Grassmann necklace} of type $(k,n)$ is a sequence $(I_1, \dots, I_n)$ of $n$ sets $I_i \in \binom{[n]}{k}$ such that for each $i \in [n]$ the following statements are true.
 \begin{itemize}
-\item if $i \in I_i$, then $I_{i+1} = \big(I_i \backslash \{i\}\big) \cup \{j\}$ for some $j \in[n]$.
-\item if $i \not\in I_i$, then $I_{i+1} = I_i$.
+\item If $i \in I_i$, then $I_{i+1} = \big(I_i \backslash \{i\}\big) \cup \{j\}$ for some $j \in[n]$.
+\item If $i \not\in I_i$, then $I_{i+1} = I_i$.
 \end{itemize}
@@
 
-The rows and columns of a Le diagram are labelled as follow: given a Le diagram fitting inside a $k\times (n-k)$ box, arrange the numbers $1,2, \dots, n$ along its southeast border, starting from the top-right corner.
+The rows and columns of a Le diagram are labelled as follows:  given a Le diagram fitting inside a $k\times (n-k)$ box, arrange the numbers $1,2, \dots, n$ along its southeast border, starting from the top-right corner.
 See Figure \ref{fig:row column numbering} for examples.
@@
 An algorithm for constructing the Le diagram associated to a Grassmann necklace was given by Agarwala and Fryer in \cite{reversingOh}.
-Since we will make use of this algorithm in Section~\ref{sec dim} below, we summarize the process here.
+Since we will make use of this algorithm in Section~\ref{sec dim}, we summarize the process here.
 \begin{algorithm}\label{alg:GN to Le} \ \cite[Algorithm 2]{reversingOh}
@@
 
-For each $i$, $2 \leq i \leq n$ perform the following steps:
+For each $i$, $2 \leq i \leq n$ perform the following steps.
 \begin{itemize}
@@
 
-In \cite{wilsonloop}, Agarwala and Marin-Amat show that $M(W)$ can also be read directly from the Wilson loop diagram itself:
+In \cite{wilsonloop}, Agarwala and Marin-Amat show that $M(W)$ can also be read directly from the Wilson loop diagram itself.
 
@@
 The entry is nonzero if and only if the propagator is supported on that vertex.
-\hlfix{Consequently, take a choice of $|J|$ nonzero entries of $C(W)$, one in each row associated to an element of $J$ and each in different columns;  each such choice is equivalent to an assignment of the propagators of $J$ to supporting vertices so that no two are assigned to the same vertex.}{Added parenthetical commas according to M.23.
+\hlfix{Consequently, take a choice of $|J|$ nonzero entries of $C(W)$, one in each row associated to an element of $J$ and each in different columns.
+Each such choice is equivalent to an assignment of the propagators of $J$ to supporting vertices so that no two are assigned to the same vertex.}{Added parenthetical commas according to M.23.
 better?
@@
 This is captured in Definition~\ref{def I_i as a function}, and used throughout the paper.
+
+The flavour of the calculations is similar to \cite{CGdyck}\footnote{Thanks to a referee for pointing this paper out.} as in both cases the bijections are very explicit with a similar iterative flavour using Le diagrams and Grassmann necklaces related to another class of objects, for us Wilson loop diagrams and for them unit interval orders.
+For them, as us, the Le diagrams are particularly useful for understanding the dimensions of positroid cells since the dimension becomes the count of the number of plusses.
+The ubiquitous Catalan numbers arise for them, as for us in \cite{generalcombinatoricsI}.
+The specific subclasses of positroids we work with are, however, different.
+This basic methodology of gaining insight from bijections is very common in combinatorics.
 
@@
 \begin{rmk}\label{rem:props of length 2 and 3} 
-  The following observations about configurations of propagators of short length in a weakly admissibly Wilson loop diagram $W$ are easily verified:
+  The following observations about configurations of propagators of short length in a weakly admissibly Wilson loop diagram $W$ are easily verified.
   \vspace{-0.5em}
@@
 \begin{lem}\label{lem sian}
-  Let $W$ be a weakly admissible Wilson loop diagram with at least 5 vertices and in which each vertex supports at least one propagator.  Then at least one of the following two conditions holds:
+  Let $W$ be a weakly admissible Wilson loop diagram with at least 5 vertices and in which each vertex supports at least one propagator.  Then at least one of the following two conditions holds.
   \vspace{-0.5em}
@@
 
-We will inductively construct sequences of propagators $\{p_r\}$ and $\{q_r\}$, with $\ell(p_r) = 2$ for each $r$ and such that either of the following are true:
+We will inductively construct sequences of propagators $(p_r)$ and $(q_r)$, with $\ell(p_r) = 2$ for each $r$ and such that either of the following are true:
 \begin{itemize}
-\item $p_r$ forms part of configuration \ref{item big and 2} or \ref{item pair of 2s} from the statement, at which point the induction terminates, 
+\item the propagator $p_r$ forms part of configuration \ref{item big and 2} or \ref{item pair of 2s} from the statement, at which point the induction terminates, 
   %a configuration \eqref{eq:2 prop config} in $D$
@@
 From our existing assumptions, we know the following facts: $p_1$ is not in configuration \ref{item pair of 2s}, there are no propagators of length $3$, and every vertex supports at least one propagator.
-Therefore, there must be a propagator of length $\geq 4$ with one end on edge $j_1$ or on edge $j_1-1$ or on edge $j_1-2$.
+Therefore, there must be a propagator of length at least 4 with one end on edge $j_1$ or on edge $j_1-1$ or on edge $j_1-2$.
 Let $q_1 = (i_1, k_1)$ be this propagator, oriented such that $p_1 \in \cP_{out}(q_1,<_{i_1})$; see Figure~\ref{fig base case lem sian}.
@@
 
-Let $W_r := (\cP_{in}(q_r),[n])$ be the subdiagram of $W$ consisting only of those propagators inside $q_r$ (including $q_r$ itself); in particular $W_r$ contains none of the previous $p_i$ or $q_i$.
+Let $W_r := (\cP_{in}(q_r),[n])$ be the subdiagram of $W$ consisting of those propagators inside $q_r$ (including $q_r$ itself); in particular $W_r$ contains none of the previous $p_i$ or $q_i$.
 By the original hypotheses on $W$, every vertex in $[i_r,k_{r+1}]$ (of which there are at least 4, since $\ell(q_r) \geq 4$) must support at least one propagator.
@@
 there are at most two vertices between an endpoint of $p_{r+1}$ and an endpoint of $q_r$).
-Since $p_{r+1}$ has length 2, it must be that $(i_r+3)+1 \geq k_r-2$ and so $q_r$ has length $\leq 6$.
+Since $p_{r+1}$ has length 2, it must be that $(i_r+3)+1 \geq k_r-2$ and so $q_r$ has length at most 6.
 By the minimality assumption on $q_r$, no propagator in $W_r$ has $q_r$ on one side and $p_{r+1}$ on the other side.
@@
 \begin{algorithm}\label{alg:put GN on WLD}
-Let $W = (\cP, [n])$ be an admissible Wilson loop diagram. In order to construct the set $I_i^W$ for $i \in [n]$, perform the following steps:
+Let $W = (\cP, [n])$ be an admissible Wilson loop diagram. In order to construct the set $I_i^W$ for $i \in [n]$, perform the following steps.
 
@@
 \item Fix a vertex $i \in [n]$, the {\bf starting vertex}. Set $j:=i$ and $I_i^W = \emptyset$.
-\item While $\cP \neq \emptyset$, perform the following steps:
+\item While $\cP \neq \emptyset$, perform the following steps.
 \begin{enumerate}
@@
 
-Since $I_i(p) \neq b$, there must exist a propagator $q$ inside of $(p,<_i)$ with $I_i(q) = b$.
+Since $I_i(p) \neq b$, there must exist a propagator $q$ inside $(p,<_i)$ with $I_i(q) = b$.
 The propagator $q$ cannot end on the edge $b-1$, as this would contradict the minimality of $p$, so we have $q = (d,b)$ with $a <_i d <_i b$, and $I_i(q) = b$.
 
-In order for $q$ to remain unassigned until the algorithm reaches vertex $b$, there must be another propagator $r$ with an end on edge $d$ and $I_i(r) = d+1$; the only way this can occur is if $r$ is outside of $(q,<_i)$ but inside $(p,<_i)$.
+In order for $q$ to remain unassigned until the algorithm reaches vertex $b$, there must be another propagator $r$ with an end on edge $d$ and $I_i(r) = d+1$; the only way this can occur is if $r$ is outside $(q,<_i)$ but inside $(p,<_i)$.
 But now $r$ contributes its fourth vertex to $I_i$, again contradicting the minimality of $p$.
@@
 Let $V$ be the diagram obtained by removing the propagator $p$ from $W$ (Figure \ref{fig V diagram}).
-The diagram $V$ is guaranteed to be an admissible diagram, since it was formed by removing a propagator from a diagram that was at least weakly admissible.
+The diagram $V$ is guaranteed to be admissible, since it was formed by removing a propagator from a diagram that was at least weakly admissible.
 \todo{Make certain we don't start sentences with simbols}
@@
       l+b & \text{if } r=p\\
-      I_{l+b+1}^{V}(r) & \text{if } r\neq p
+      I_{l+b+1}^{V}(r) & \text{if } r\neq p\;.
     \end{cases}
@@
 
-Therefore, once again we can see that the $J_r^{W}(*)$ are cyclic for all $r\neq p$ in $W$.  Assembling the intervals for $p$ we have the following statements:
+Therefore, once again we can see that the $J_r^{W}(*)$ are cyclic for all $r\neq p$ in $W$.  Assembling the intervals for $p$ we have the following statements.
 \begin{itemize}
@@
 
-Fix $n$, and suppose for a contradiction that there exists an admissible diagram for which there exists an $i$ with $m\in I_i\setminus \{i\}$ and $m \not\in I_{i+1}$.
+Fix $n$, and suppose, by way of contradiction that there exists an admissible diagram for which there exists an $i$ with $m\in I_i\setminus \{i\}$ and $m \not\in I_{i+1}$.
 Let $W$ be such a counterexample with the minimal number of propagators.
@@
 
-Now let $W' = (\cP_{out}(p,<_i), [n])$, i.e. the diagram obtained from $W$ by removing both $p$ and all propagators inside of $p$. The diagram $W'$ has strictly fewer propagators than $W$ did.
+Now let $W' = (\cP_{out}(p,<_i), [n])$, i.e. the diagram obtained from $W$ by removing both $p$ and all propagators inside $p$. The diagram $W'$ has strictly fewer propagators than $W$ did.
 
@@
 
-Let $W'$ be the diagram obtained from $W$ by removing only the propagator $p$.  We have
+Let $W'$ be the diagram obtained from $W$ by removing the propagator $p$.  We have
 \begin{align*}
@@
 We have shown in the previous theorem that $(I_1,\dots,I_n)$ is a Grassmann necklace; it remains to check that this Grassmann necklace corresponds to the positroid $M(W)$.
-Recall from the discussion following Definition~\ref{def:grassmann necklace}, and equation \eqref{basesofmatroids} in particular, that it suffices to show the following points:
+Recall from the discussion following Definition~\ref{def:grassmann necklace}, and equation \eqref{basesofmatroids} in particular, that it suffices to show the following points.
 \begin{itemize}
@@
 \end{itemize}
-The first point follows immediately: the algorithm assigns each propagator to a vertex in the support of that propagator, so $I_i$ is a basis for $M(W)$ by Corollary~\ref{lem basis as perm}.
+The first point follows immediately.  The algorithm assigns each propagator to a vertex in the support of that propagator, so $I_i$ is a basis for $M(W)$ by Corollary~\ref{lem basis as perm}.
 
@@
 \[Q_0 = \Prop(j_m), \qquad Q_{l+1} = \Prop(I_i(Q_l))\quad \forall l \geq 0.\]
-It is easily verified that this is an increasing chain of sets: indeed, if $q \in Q_l$ then $I_i(q) \in I_i(Q_l)$, and since $I_i(q)$ is one of the vertices that supports $q$ we must have $q \in \Prop(I_i(Q_l)) = Q_{l+1}$.
+It is easily verified that this is an increasing chain of sets.
+Indeed, if $q \in Q_l$ then $I_i(q) \in I_i(Q_l)$, and since $I_i(q)$ is one of the vertices that supports $q$ we must have $q \in \Prop(I_i(Q_l)) = Q_{l+1}$.
 Since $\cP$ is finite, the sequence stabilizes in finitely many steps.
@@
 
-We will show that $Q \subseteq \mathcal{P}_{m-1}$, which will imply the theorem by the following argument: if $Q \subseteq \cP_{m-1}$ then we have $I_i(Q)\subseteq J$, and hence $I_i(Q) \cup \{j_m\} \subseteq J$ as well.
+We will show that $Q \subseteq \mathcal{P}_{m-1}$, which will imply the theorem by the following argument.
+If $Q \subseteq \cP_{m-1}$ then we have $I_i(Q)\subseteq J$, and hence $I_i(Q) \cup \{j_m\} \subseteq J$ as well.
 Since $I_i(Q) \cup \{j_m\}$ only supports the propagators in $Q$ but has $|Q|+1$ vertices, it is a dependent set in $M(W)$.
@@
 All that remains is to prove $Q\subseteq \mathcal{P}_{m-1}$, which we do by inductively proving $Q_l \subseteq \mathcal{P}_{m-1}$ for all $l \geq 0$.
-The base case $Q_0 \subseteq \cP_{m-1}$ is immediate: since $j_m \not\in I_i$ by construction, there cannot be any unassigned propagators supported on $j_m$ when the algorithm reaches that vertex, i.e.
+The base case $Q_0 \subseteq \cP_{m-1}$ is immediate; since $j_m \not\in I_i$ by construction, there cannot be any unassigned propagators supported on $j_m$ when the algorithm reaches that vertex, i.e.
 ${\Prop(j_m) \subseteq \cP_{m-1}}$.
@@
 \end{figure}
-Now repeat the argument above with $p_s$ in place of $p_r$: if the other end of $p_s$ lands on an edge between $q$ and $j_m$ then we have $q \in \cP_{m-1}$ as above; if not then there exists some $p_t \in Q_{l-3}$ with $p_s$ supported on $I_i(p_t)$ and $q$ on the inside of $p_t$ in the $a_t-1$ order.
+Now repeat the argument above with $p_s$ in place of $p_r$.
+If the other end of $p_s$ lands on an edge between $q$ and $j_m$ then we have $q \in \cP_{m-1}$ as above; if not then there exists some $p_t \in Q_{l-3}$ with $p_s$ supported on $I_i(p_t)$ and $q$ on the inside of $p_t$ in the $a_t-1$ order.
 Therefore, $I_i(p_t) <_i I_i(p_r)$.
@@
   Let $W$ be an admissible Wilson loop diagram with $k \geq 1$ propagators.
-Then there is some dihedral transformation of $W$ such that the resulting diagram $W'$ has a propagator $p$ with the following properties:
+Then there is some dihedral transformation of $W$ such that the resulting diagram $W'$ has a propagator $p$ with the following properties.
   \begin{itemize}
-  \item $p = (i, n-1)$ for some $i$, and $p$ has no propagators inside it with respect to the $<_i$ ordering.
+  \item The propagator $p = (i, n-1)$ for some $i$, and $p$ has no propagators inside it with respect to the $<_i$ ordering.
   \item Either the edge $i$ in $W'$ only supports $p$, or the edge $i$ in $W'$ supports exactly one other propagator $q = (j,i)$, with no other propagators inside $q$ in the $<_j$ ordering. 
@@
 Let $V$ be $W$ with $p$ removed.
-We can express $I_*^W$ in terms of $I_*^V$ as indicated below:
+We can express $I_*^W$ in terms of $I_*^V$ as indicated below.
 
@@
 
-Recall that $I_1$ determines the shape of the Le diagram: specifically, the elements of $I_1$ label the rows of the diagram, working from top right to bottom left.
+Recall that $I_1$ determines the shape of the Le diagram.
+Specifically, the elements of $I_1$ label the rows of the diagram, working from top right to bottom left.
 By the arguments in Lemma {\ref{lem I}} we know that none of $n$, $n-1$, $n-2$, and $n-3$ are in $I_1^{V}$.
@@
 As described in Section~\ref{sec:positroid background}, if Algorithm~\ref{alg:GN to Le} places a $+$ in the box with row index $i$ and column index $j$, we say that this plus is {\bf in the $i \rightarrow j$ position}, and refer to it as {\bf the plus defined by ``the (hook) path from $i$ to $j$''}.
-Note that the collection of paths contributed by a single Grassmann necklace term must be non-crossing: this follows immediately from the Le condition.
+Note that the collection of paths contributed by a single Grassmann necklace term must be non-crossing.
+This follows immediately from the Le condition.
 
@@
 
-Also by Lemma~\ref{lem I} we have $I_{n-1}^{W} = I_n^{V} \cup \{n-1\}$. Recall from the proof of Lemma~\ref{lem I} that none of $n-3,\;n-2,\;n-1$ or $n$ are in $I_1^V$; therefore
+Also by Lemma~\ref{lem I} we have $I_{n-1}^{W} = I_n^{V} \cup \{n-1\}$. Recall from the proof of Lemma~\ref{lem I} that none of $n-3,\;n-2,\;n-1$ or $n$ are in $I_1^V$; therefore,
 \[
@@
 
-At $I_7$ we see for the first time an irreducible quadratic factor: we have $S_7 = \{q,s\}$ with ${I_7(S_7) = \{ 1,2\}}$, $\Delta_{I_7} = d(ej-fi)$ and $r_7 = ej-fi$.
+At $I_7$ we see for the first time an irreducible quadratic factor.  We have $S_7 = \{q,s\}$ with ${I_7(S_7) = \{ 1,2\}}$, $\Delta_{I_7} = d(ej-fi)$ and $r_7 = ej-fi$.
 
@@
 
-Finally, we have $r_1 = (af-be)k$.  Putting everything together, we obtain
+Finally, we have $r_1 = (af-be)k$.  Putting the previous calculations together, we obtain
 \[
@@
 All that remains is to prove that $\Delta_{I_i}$ has no irreducible factors of degree 3 or more.
-Suppose for a contradiction that $f$ is a factor of $\Delta_{I_i}$ of degree $\geq 3$.
+Suppose, by way of contradiction that $f$ is a factor of $\Delta_{I_i}$ of degree $\geq 3$.
 Without loss of generality\footnote{This is without loss of generality for the following reason.
@@
   \draw[propassignment,gray] (\zero + 7.9*\step:\radius) to[bend left = \arrowangle] (\zero + 7*\step:\radius); 
-  \node[align = center,black] at (\zero + 6.8*\step:1.5*\radius) {\em \footnotesize If $m \in I_i$ then it was \\ \em \footnotesize contributed by a propagator \\ \em \footnotesize outside of $p$};
+  \node[align = center,black] at (\zero + 6.8*\step:1.5*\radius) {\em \footnotesize If $m \in I_i$ then it was \\ \em \footnotesize contributed by a propagator \\ \em \footnotesize outside $p$};
   \node[align = center,black] at (110:\radius*0.5) {\em Case 1: $p = (i-1,m)$};
@@
   \node[align = center] at (\zero + 1.8*\step:\radius*1.5) {\footnotesize \em No \\ \footnotesize \em propagators \\ \footnotesize \em between \\ \footnotesize \em $p$ and $q$ \\ \footnotesize \em here};
-  \node[align = center,black] at (\zero + 6.8*\step:1.5*\radius) {\em \footnotesize If $j \in I_i$ then it was \\ \em \footnotesize contributed by a propagator \\ \em \footnotesize outside of $q$};
+  \node[align = center,black] at (\zero + 6.8*\step:1.5*\radius) {\em \footnotesize If $j \in I_i$ then it was \\ \em \footnotesize contributed by a propagator \\ \em \footnotesize outside $q$};
     \node[align = center,black] at (110:\radius*0.5) {\em Case 2: $p = (i,m)$};
@@
 where $A$ is the $|T|\times |T|$ matrix indexed by the propagators in $T$ and the vertices in $I_i(T)$.
-No other propagators can be supported on these vertices since all other propagators are outside of $p$, and $p$ is the first propagator supported at $i$; this explains the zero block.
+No other propagators can be supported on these vertices since all other propagators are outside $p$, and $p$ is the first propagator supported at $i$; this explains the zero block.
 Therefore, $\Delta_{I_i} = \pm \det A \det C$, and both factors are nontrivial since at least one of $m$ and $m+1$ appears in $I_i$.
 
-Since $p\in \cP_{in}(p)$ we have $f|\det A$, and if we remove a propagator outside of $p$ that contributes either $m$ or $m+1$, we get a diagram $W'$ with fewer propagators for which $\det A | \Delta_{I^{W'}_i}$ still holds, hence $f|\Delta_{I^{W'}_i}$.
+Since $p\in \cP_{in}(p)$ we have $f|\det A$, and if we remove a propagator outside $p$ that contributes either $m$ or $m+1$, we get a diagram $W'$ with fewer propagators for which $\det A | \Delta_{I^{W'}_i}$ still holds, hence $f|\Delta_{I^{W'}_i}$.
 This contradicts the minimality of our choices.
@@
 Write $q = (i, j)$ for the support of $q$.
-The situation for $q$ is very similar to Case 1: in particular, we have $I_{i+1}(q) = j$ by Lemma {\ref{vertex cyclic int lem}} and so if $j\in I_i$ then the propagator which contributes $j$ is outside of $q$.
+The situation for $q$ is very similar to Case 1: in particular, we have $I_{i+1}(q) = j$ by Lemma {\ref{vertex cyclic int lem}} and so if $j\in I_i$ then the propagator which contributes $j$ is outside $q$.
     %\color{violet}if we have $r$ such that $I_i(r) = j$, as above, $r$ lies outside $q$: $r \in \cP_{out}(q, <_i)$.
@@
 Without loss of generality we may assume $i=a$.
-The cases in the proof of part (2) show how $\Delta_{I_i}$ factors: in particular the vertices supporting the other end of $p$ either do not appear in $I_i$, or they contribute to a different factor of $\Delta_{I_i}$ than $p$ and $a$ do.
+The cases in the proof of part (2) show how $\Delta_{I_i}$ factors.
+In particular the vertices supporting the other end of $p$ either do not appear in $I_i$, or they contribute to a different factor of $\Delta_{I_i}$ than $p$ and $a$ do.
 By assumption $b$ contributes to the same factor as $a$.
@@
 
-Taking everything together we have that $R|\prod_{i=1}^n \Delta_{I_i}$ (from part (4)), $R$ contains all factors of $\prod_{i=1}^n \Delta_{I_i}$, and $R$ is square-free.
+{}From the arguments above, we have that $R|\prod_{i=1}^n \Delta_{I_i}$ (from part (4)), $R$ contains all factors of $\prod_{i=1}^n \Delta_{I_i}$, and $R$ is square-free.
 Therefore, the ideal generated by $R$ is the radical of the ideal generated by $\prod_{i=1}^n \Delta_{I_i}$.

### 2020-12-20 GWLDCII.tex
finished going through the referee comments

@@
 
-By relating the behavior of the propagators in $W$ to the matroidal properties of $M(W)$, Agarwala and Marin-Amat also show that $M(W)$ is in fact a positroid whenever $W$ is admissible \cite[Corollary 3.39]{wilsonloop}.
+By relating the behavior of the propagators in $W$ to the matroidal properties of $M(W)$, Agarwala and Marin-Amat also show that $M(W)$ is a positroid whenever $W$ is admissible \cite[Corollary 3.39]{wilsonloop}.
 \todo{check tenses throughout (M.24) -- maybe past is better, see the ``had'' at the beginning of the next paragraph, can we discuss?}
@@
 
-Thus we have shown that Algorithm \ref{alg:put GN on WLD} does in fact produce a Grassmann necklace. Next we check that it produces the correct one, i.e. the Grassmann necklace that defines $M(W)$. 
+Thus we have shown that Algorithm \ref{alg:put GN on WLD} does produce a Grassmann necklace. Next we check that it produces the correct one, i.e. the Grassmann necklace that defines $M(W)$. 
 \begin{thm}\label{res alg gives correct GN} 
@@
 
-On the other hand, if $n-2\in I_{n-2}^{V}$ then we must be in Case 2 of Figure~\ref{fig special p} and we must have ${I_{n-2}^V(q) = I_{n-2}^W(q) = n-2}$ (since $q$ is always the clockwise-most propagator supported on vertex $n-2$).
+On the other hand, if $n-2\in I_{n-2}^{V}$ then we must be in Case 2 of Figure~\ref{fig special p} and we must have ${I_{n-2}^V(q) = I_{n-2}^W(q) = n-2}$ since $q$ is always the clockwise-most propagator supported on vertex $n-2$.
 If $n-1 \not\in I_{n-2}^{V}$, then $I_{n-2}^W(p) = n-1$ and the algorithm proceeds identically to $I_{n-2}^{V}$ for the remainder of its steps; thus $I_{n-2}^{W} = I_{n-2}^{V}\cup \{n-1\}$ in this case.
@@
 This last row contains three (new) plusses.
-All other plusses in the Le diagram of $V$ shift in a predictable manner to become plusses in the Le diagram of $W$; this is described in Lemma ~\ref{lem n and n-1} to Theorem~\ref{thm dim}.
+All other plusses in the Le diagram of $V$ shift in a predictable manner to become plusses in the Le diagram of $W$; this is described in Lemma~\ref{lem n and n-1} to Theorem~\ref{thm dim}.
 
@@
 \begin{proof}
-Recall that $I_1^W = I_1^V\cup \{n-3\}$ and that $n-2,n-1,n \not\in I_1^W$.
+Recall that $I_1^W = I_1^V\cup \{n-3\}$ and that $n-2$, $n-1$, and $n$ are not in $I_1^W$.
 
@@
   \item The plusses in the $\mathcal{B}$ region of both Le diagrams are identical, so each plus in this region is paired with itself.
-  \item Every square containing a plus in the leftmost two columns (the $n^{th}$ and the $(n-1)^{th}$ columns) \todo{generally turn $n$ to $n^{th}$ throughout M.60} of $\mathcal{A}$ for $V$ also contains a plus in $W$, so these plusses are also paired with themselves.
+  \item Every square containing a plus in the leftmost two columns (the $n^{th}$ and the $(n-1)^{th}$ columns) \todo{generally turn $n$ to $n^{th}$ throughout M.60 -- I disagree and for reasons I can articulate} of $\mathcal{A}$ for $V$ also contains a plus in $W$, so these plusses are also paired with themselves.
   \item The plusses in the $n-3$ column for $V$ are paired with the corresponding plusses in the $n-2$ column for $W$.
@@
 \]
-The Grassmann necklace of this diagram \hlfix{is}{M.65 wants to replace with "consists of". I disagree} 
+The Grassmann necklace of this diagram \hlfix{is}{M.65 wants to replace with "consists of". I disagree -- let's discuss} 
 \begin{gather*}I_1 = \{1,2,4\},\ I_2 = \{2,4,5\},\ I_3 = \{4,5,6\},\ I_4=\{4,5,6\},\\ I_5=\{5,6,7\},\ I_6 = \{6,7,1\},\ I_7=\{7,1,2\}. \end{gather*}  

### 2020-12-21 GWLDCI.tex
some typos, particularly in displays

@@
 \begin{dfn}\label{def:edges}
-The $i$th edge of $W$ is the arc that lies between the vertices $i$ and $i+1$.
+The $i^{th}$ edge of $W$ is the arc that lies between the vertices $i$ and $i+1$.
 \end{dfn}
@@
 		\end{scope}
-	\end{tikzpicture}  \eas 
+	\end{tikzpicture} \; . \eas 
 \end{eg}
@@
 A Wilson loop diagram $W = (\cP,V)$ is {\em admissible} if it satisfies the following three conditions: \begin{enumerate}
-\item $|V| \geq |\cP| + 4.$
-\item For any non-empty set of propagators, $Q \subseteq \cP$, $Q \neq \emptyset$, one has $|V(Q)| \geq |Q| + 3$.
-\item There does not exist a pair of propagators $(i_p,j_p),(i_q,j_q) \in \cP$ such that $i_p < i_q < j_p <j_q$.
+\item $|V| \geq |\cP| + 4,$
+\item for any non-empty set of propagators, $Q \subseteq \cP$, $Q \neq \emptyset$, one has $|V(Q)| \geq |Q| + 3$.\,
+\item there does not exist a pair of propagators $(i_p,j_p),(i_q,j_q) \in \cP$ such that $i_p < i_q < j_p <j_q$.
 \end{enumerate}
@@
 \begin{enumerate}
-\item There exist exact subdiagrams $(P, V(P)) \subseteq W$ and $(P', V(P')) \subseteq W'$ with the same number of propagators and supported on the same vertices, i.e.
+\item there exist exact subdiagrams $(P, V(P)) \subseteq W$ and $(P', V(P')) \subseteq W'$ with the same number of propagators and supported on the same vertices, i.e.
 $|P| = |P'|$ and  $V(P) =  V(P')$.
-\item The complementary subdiagrams (i.e. all other propagators and vertices) are identical, i.e. $(\cP \setminus P, [n]) = (\cP' \setminus P', [n])$.
+\item the complementary subdiagrams (i.e. all other propagators and vertices) are identical, i.e. $(\cP \setminus P, [n]) = (\cP' \setminus P', [n])$.
 \end{enumerate}
@@
 \begin{lem}\label{lem facts about WLD matroids}
-Let $W = (\cP,[n])$ be a weakly admissible Wilson loop diagram. Then:
+Let $W = (\cP,[n])$ be a weakly admissible Wilson loop diagram. The following are true.
 \begin{enumerate}
@@
 For a weakly admissible Wilson loop diagram $W$, every triangulated piece $t$ of $\tau(W)$ corresponds to a subdiagram of $W$ obtained by taking the set of propagators $P$ corresponding to edges of $t$ and then taking the subdiagram $(P, V(P))$.
-Conversely, given a subdiagram $(P, V(P))$ of $W$ we can obtain a subgraph of $\tau(W)$, called $t$, as follows:
+Conversely, given a subdiagram $(P, V(P))$ of $W$ we can obtain a subgraph of $\tau(W)$, called $t$, following the algorithm below.
 \begin{itemize}
@@
 Since Corollary \ref{uniqueproppartitioncor} allows us to decompose any admissible Wilson loop diagram into a collection of maximal exact subdiagrams, we are motivated to examine the matroid properties of exact subdiagrams more closely.
-In this section, we prove two main results:
+In this section, we prove two main results.
 \begin{enumerate}
-\item The matroid associated to an exact subdiagram of $W$ can be written as a contraction of the matroid $M(W)$ by the complementary propagator flat (Theorem \ref{exact diagrams contractions}). 
-\item The matroid associated to an exact subdiagram is uniform (Theorem \ref{exactuniformthm}).
+\item the matroid associated to an exact subdiagram of $W$ can be written as a contraction of the matroid $M(W)$ by the complementary propagator flat (Theorem \ref{exact diagrams contractions}),
+\item the matroid associated to an exact subdiagram is uniform (Theorem \ref{exactuniformthm}).
 \end{enumerate}
@@
 \begin{enumerate}
-\item $C = F(\Prop (C))$, i.e. $C$ is a propagator flat.
+\item $C = F(\Prop (C))$, i.e. $C$ is a propagator flat,
 \item $F \setminus C$ is an independent set. Furthermore, $F\setminus C$ is an independent flat if and only if $F(\emptyset) = \emptyset$, that is, $W$ has no non-supporting vertices.  
@@
 \begin{lem} \label{maxexactcomplementrank}
-Let $W = (\cP, [n])$ be an admissible Wilson loop diagram, and $P \subseteq \cP$. Then: \begin{enumerate}
-\item If $(P,V(P))$ is an exact subdiagram of $W$, then $F(P^c)$ is a dependent flat in $W$.
-\item If $(P,V(P))$ is a maximal exact subdiagram of $W$, then $F(P^c)$ is a cyclic flat in $W$.
-\item If $(P,V(P))$ is an exact subdiagram of $W$, then $\rk(F(P^c)) = |P^c|$.
+Let $W = (\cP, [n])$ be an admissible Wilson loop diagram, and $P \subseteq \cP$. Then, \begin{enumerate}
+\item if $(P,V(P))$ is an exact subdiagram of $W$, then $F(P^c)$ is a dependent flat in $W$,
+\item if $(P,V(P))$ is a maximal exact subdiagram of $W$, then $F(P^c)$ is a cyclic flat in $W$,
+\item if $(P,V(P))$ is an exact subdiagram of $W$, then $\rk(F(P^c)) = |P^c|$.
 \end{enumerate} 
@@
 Let $W$ and $W'$ be equivalent Wilson loop diagrams which can be decomposed as
-\[W = (P \sqcup R, [n]), \qquad W' = (P \sqcup R', [n]),\]
+\[W = (P \sqcup R, [n]) \qquad \textrm{and} \qquad W' = (P \sqcup R', [n]),\]
 where $(R,V(R))$ and $(R',V(R'))$ are different maximal exact subdiagrams of $W$ and $W'$ respectively, and $V(R) = V(R')$.
@@
   \[
-  \prod_{i=1}^{j} \frac{1}{n_i-1}\binom{2(n_i-2)}{n_i-2}
+  \prod_{i=1}^{j} \frac{1}{n_i-1}\binom{2(n_i-2)}{n_i-2} \;.
   \]
@@
 Suppose that $V_{>3}(D_1) = V_{>3}(D_2)$, but that the $D_1$ and $D_2$ do not have the same set of non-triangle faces.
-Then there are four vertices $x_i$, $x_j$, $x_k$, $x_l$ satisfying the following conditions:\begin{enumerate} \item In either $D_1$ or $D_2$ all four vertices are on the same non-triangle face.
-\item In the other dissection, there is a diagonal of the dissection such that exactly one of $\{x_i, x_j, x_k, x_l\}$ lies on one side of the diagonal (so the others are either end points of this diagonal or strictly on the other side).
+Then there are four vertices $x_i$, $x_j$, $x_k$, $x_l$ satisfying the following conditions:\begin{enumerate} \item in either $D_1$ or $D_2$ all four vertices are on the same non-triangle face.
+\item in the other dissection, there is a diagonal of the dissection such that exactly one of $\{x_i, x_j, x_k, x_l\}$ lies on one side of the diagonal (so the others are either end points of this diagonal or strictly on the other side).
 \end{enumerate}

### 2020-12-21 GWLDCII.tex
rewritings from today's meeting

@@
 As with the Amplituhedron, each Wilson loop represents the sum of a family of $N^kMHV$ Feynman diagrams, and adding up the corresponding sums of Feynman integrands associates a volume form to a convex space different from those in the decomposition the Amplituhedron \cite{CachazoSvrcekWitten, Hodges2013}.
-\hlfix{The Wilson loop diagrams discussed in this paper are, loosely speaking, dual graphs of the $N^kMHV$ diagrams.
+
+Wilson loop diagrams, as we will study them, are objects given by a perturbative expansion of the holomorphic Wilson loop in twistor space.
+Classically, the interactions of the theory were studied as maximal helicity violating diagrams ($MHV$ diagrams), next-to-maximal helicity violating diagrams and so on ($N^kMHV$ diagrams) in momentum space.
+Adamo and Mason, in \cite{Adamo:2011pr}, give an elegant formulation for the $N^kMHV$ diagrams in twistor space.
+The Wilson loop diagram perspective of this paper is dual to this twistor representation of $MHV$ diagrams.
+The objects are closely related and carry the same information.  We choose to emphasize the useful dual perspective by our focus on the Wilson loop diagrams.
+
+%\hlfix{The Wilson loop diagrams discussed in this paper are, loosely speaking, dual graphs of the $N^kMHV$ diagrams.
 While the Wilson loop diagrams contain the exact same information as the $N^kMHV$ diagrams for the purposes of understanding $N=4 SYM$ theory, this dual perspective is better suited to understanding the combinatorics and geometry associated to the theory.}{added to address request (3) of report M -- let's discuss, I don't think this makes sense as written} Therefore, \hlfix{we part with the notation in the physics literature, and name these dual graphs}{I'm not sure that's true} of $N^kMHV$ diagrams Wilson loop diagrams in order to emphasize the combinatorial and geometric significane of these object.
 
-In \cite{wilsonloop}, Agarwala and Marin-Amat uncovered a connection between the Feynman integrals developed in the $N^kMHV$ \st{this}\todo{What does this ``this'' refer to, also this sentence should probably start a new paragraph} literature and positroids, defined  as matroids that can be realized as an element of $\Gr(k,n)$.
+In \cite{wilsonloop}, Agarwala and Marin-Amat uncovered a connection between theWilson loop diagrams and positroids, defined as matroids that can be realized as an element of $\Gr(k,n)$.
 Other work has shown a connection between the volume filled by Wilson loop diagrams and the Amplituhedron \cite{casestudy, Amplituhedronsquared}.
@@
 
-In the above work and elsewhere, it is clear that while the space \hlfix{parametreized by}{``filled by'' vs ``parameterized by'' in the previous paragraph} the Wilson loop diagrams is related to the Amplituhedron, they are not the same space.
+In the above work and elsewhere, it is clear that while the space parametrized by the Wilson loop diagrams is related to the Amplituhedron, they are not the same space.
 For instance, it is conjectured that the Amplituhedron is orientable, whereas Agarwala and Marcott show in \cite{non-orientable} that the space parametrized by the Wilson loop diagrams as a subspace of $\Gr(k, n+1)$ can be seen as a non-orientable vector bundle over some submanifold of $\Gr(k,n)$.

### 2020-12-21 GWLDCII.tex
worked on the paragraph we were discussing at the end of the call today

@@
 
-It is worth noting at this point that the \hlfix{combinatorics of the Wilson loop diagrams are different from the combinatorics of the Amplituhedron}{I think we should discuss this paragraph -- it may be misleading in a bad way}, just as the the volume forms associated to the BCFW diagrams are different from those associated to the Wilson Loop diagrams.
+The Amplituhedron and the Wilson loop diagrams describe the same physical amplitudes, and via their relation to positroids, they have similar combinatorics, but these combinatorial objects manifest themselves differently in the two cases.
+For instance, square moves and merge-expand moves on the plabic graph give different graphical representations of the same positroid cell in the Amplituhedron case, while as we show in our companion paper \cite{generalcombinatoricsI}, retriangulations of polygon dissections associated to Wilson loop diagrams give all the Wilson loop diagrams associated to the same positroid cell.
+A direct connection between the geometry of the Amplituhedron and the geometry of the Wilson loop diagrams is also not known.
+The geometric spaces in the two situations have different dimensions and \hlfix{examples show}{is this true?} that they do not relate by a coordinate projection or boundary map or other straightforward connection.
+The deeper connection, which physics tells us should exist, remains to be uncovered in future work.
+\note{This doesn't address the parametrization part yet.}
+
+%It is worth noting at this point that the \hlfix{combinatorics of the Wilson loop diagrams are different from the combinatorics of the Amplituhedron}{I think we should discuss this paragraph -- it may be misleading in a bad way}, just as the the volume forms associated to the BCFW diagrams are different from those associated to the Wilson Loop diagrams.
 For instance, the BCFW are most readily related to the geometry of a postive Grassmannian via plabic graphs.

### 2020-12-23 GWLDCII.tex
as we discuss

@@
 
-In the above work and elsewhere, it is clear that while the space parametrized by the Wilson loop diagrams is related to the Amplituhedron, they are not the same space.
+In the above work and elsewhere, it is clear that while the space parametrized by the Wilson loop diagrams is related to the Amplituhedron, they are not the same space, nor is a direct connection between the geometry of the Amplituhedron and the geometry of the Wilson loop diagrams known.
 For instance, it is conjectured that the Amplituhedron is orientable, whereas Agarwala and Marcott show in \cite{non-orientable} that the space parametrized by the Wilson loop diagrams as a subspace of $\Gr(k, n+1)$ can be seen as a non-orientable vector bundle over some submanifold of $\Gr(k,n)$.
 Furthermore, the cells associated to the Wilson loop diagrams are different from the cells associated to BCFW diagrams, which can be seen by comparing the results of \cite{AmplituhedronDecomposition} and \cite{casestudy}.
-This is an intriguing observation, as it is conjectured that the space parametrized by the Wilson loop diagrams will project down to something close to the Amplituhedron \cite{wilsonloop, Amplituhedronsquared}.
-
-The Amplituhedron and the Wilson loop diagrams describe the same physical amplitudes, and via their relation to positroids, they have similar combinatorics, but these combinatorial objects manifest themselves differently in the two cases.
-For instance, square moves and merge-expand moves on the plabic graph give different graphical representations of the same positroid cell in the Amplituhedron case, while as we show in our companion paper \cite{generalcombinatoricsI}, retriangulations of polygon dissections associated to Wilson loop diagrams give all the Wilson loop diagrams associated to the same positroid cell.
-A direct connection between the geometry of the Amplituhedron and the geometry of the Wilson loop diagrams is also not known.
-The geometric spaces in the two situations have different dimensions and \hlfix{examples show}{is this true?} that they do not relate by a coordinate projection or boundary map or other straightforward connection.
-The deeper connection, which physics tells us should exist, remains to be uncovered in future work.
-\note{This doesn't address the parametrization part yet.}
+Furthermore, the spaces in the two situations have different dimensions, as we will discuss further below, and examples show\cite{HeslopSteward} that they do not relate by a coordinate projection or boundary map or other straightforward function.
+None the less, from their common physical origin, it is believed that once the integrals over these spaces are taken the resulting amplitudes will show a more direct relation \cite{wilsonloop, Amplituhedronsquared}.
+
+The Amplituhedron and the Wilson loop diagrams describe the scattering amplitudes from the same physical theory, but the Amplituhedron only captures the on-shell portion while the Wilson loop diagrams capture arbitrary kinematics.
+Both are related to positroids, and in this way they have similar combinatorics, but, these combinatorial objects manifest themselves differently in the two cases.
+For instance, square moves and merge-expand moves on the plabic graph give different graphical representations, hence parametrizations, of the same positroid cell in the Amplituhedron case.
+On the other hand, we show in our companion paper \cite{generalcombinatoricsI}, retriangulations of polygon dissections associated to Wilson loop diagrams give all the Wilson loop diagrams associated to the same positroid cell.
+Each distinct Wilson loop diagram associated to the same positroid cell gives a different parametrization \cite{WLDdim}.
+% Despite their common representation as positroids,a direct connection between the geometry of the Amplituhedron and the geometry of the Wilson loop diagrams is not known.
+The geometric spaces in the two situations have different dimensions, as we will discuss further below, and examples show\cite{HeslopSteward} that they do not relate by a coordinate projection or boundary map or other straightforward function.
+The deeper combinatorial and geometric connection between the Amplituhedron and the Wilson loop diagrams, which physics tells us should exist, remains to be uncovered in future work.
 
@@
 
-This paper continues this body of work by establishing concrete connections between the combinatorics of the Wilson loop diagram as determined by the physics, and the combinatorics of the associated positroid cell as identified in \cite{wilsonloop}.
+This paper continues the program of establishing concrete connections between the combinatorics of the Wilson loop diagram as determined by the physics, and the combinatorics of the associated positroid cell as identified in \cite{wilsonloop}.
 In this paper, we give an algorithm to read the Grassmann necklace, one of the standard combinatorial characterizations of the positroid cell, directly off the Wilson loop diagram.

### 2020-12-23 GWLDCII.tex
more from the phone conversation

@@
 The Wilson loop diagram perspective of this paper is dual to this twistor representation of $MHV$ diagrams.
-The objects are closely related and carry the same information.  We choose to emphasize the useful dual perspective by our focus on the Wilson loop diagrams.
+The objects are closely related and carry the same information.  We choose to emphasize the dual perspective by our focus on the Wilson loop diagrams.
 
@@
 
-In \cite{wilsonloop}, Agarwala and Marin-Amat uncovered a connection between theWilson loop diagrams and positroids, defined as matroids that can be realized as an element of $\Gr(k,n)$.
+In \cite{wilsonloop}, Agarwala and Marin-Amat uncovered a connection between the Wilson loop diagrams and positroids, defined as matroids that can be realized as an element of $\Gr(k,n)$.
 Other work has shown a connection between the volume filled by Wilson loop diagrams and the Amplituhedron \cite{casestudy, Amplituhedronsquared}.
@@
 Furthermore, the cells associated to the Wilson loop diagrams are different from the cells associated to BCFW diagrams, which can be seen by comparing the results of \cite{AmplituhedronDecomposition} and \cite{casestudy}.
-Furthermore, the spaces in the two situations have different dimensions, as we will discuss further below, and examples show\cite{HeslopSteward} that they do not relate by a coordinate projection or boundary map or other straightforward function.
-None the less, from their common physical origin, it is believed that once the integrals over these spaces are taken the resulting amplitudes will show a more direct relation \cite{wilsonloop, Amplituhedronsquared}.
+Furthermore, the spaces in the two situations have different dimensions, as we will discuss further below, and examples show \cite{HeslopStewart} that they do not relate by a coordinate projection or boundary map or other straightforward function.
+None the less, from their common physical origin, it is believed that once the integrals over these spaces are taken the results will parametrize related spaces \cite{wilsonloop, Amplituhedronsquared}.
 
@@
 In \cite{non-orientable} the authors note that the Wilson loop diagrams only correspond to positroid cells when the gauge vector is ignored.
-Including the gauge vector defines a $4k$ dimensional subspace of $\mathbb{G}r_\R(k,n+1)$.\st{This apparent contradiction}\todo{I think we should say more in view of reviewer Y's comment 3 and we can probably phrase it more positively too} \st{is resolved by the non-orientability result of {\cite{non-orientable}}.}
+Including the gauge vector defines a $4k$ dimensional subspace of $\mathbb{G}r_\R(k,n+1)$.
 
 As described above, each integrand associated to a Wilson loop diagram gives the volume of a convex polytope.
-However, each individual integral has singularities which come from the factors in the denominator of the integrands.
-SYM $N=4$ is a finite theory.
+However, each individual tree level integral has singularities.
+These singularities are of two types physical and spurious.
+The physical singularities come from special kinematical points and we will not consider them in this paper.
+The spurious singularities come from zeros of the denominator, and hence are accessible to our combinatorial techniques.
+SYM $N=4$ is a finite theory so we only expect to see the physical singularites in the overall amplitude.
+Consequently, the spurious singularities are artifacts of how the integrals are represented and must cancel in the calculation of a tree level scattering amplitude, though the details of how this works is unclear.
+The cancellation has been conjectured in general \cite{Hodges2013} and verified explicitly in a few cases \cite{casestudy, HeslopStewart}, but it is hard to prove in general due to the fact that the relationship between Wilson loop diagrams and $3k$-dimensional positroid cells of $\Gr(k,n)$ is neither one-to-one nor onto \cite{generalcombinatoricsI}.
+
+%SYM $N=4$ is a finite theory.
+which come from the factors in the denominator of the integrands.
 However at tree level, the integrals used to calculate the amplitudes of the theory have singularities upon evaluation \cite{Adamo:2011pv,Adamo:2012xe,Arkani-Hamed:2013jha}.
@@
 All three of these conditions arise from the physical interpretation of Wilson loop diagrams.
-The first condition comes from the fact that these diagrams represent $N^k$MHV interctions, where $k +4 <n$, see for instance the explanation in the introduction of \cite{adamo:2011pr}.
+The first condition comes from the fact that these diagrams represent $N^k$MHV interctions, where $k +4 <n$, see for instance the explanation in the introduction of \cite{Adamo:2011pr}.
 The second condition can be derived from the integrals associated to the diagrams, as in \cite[Theorem 1.13]{wilsonloop}.

### 2020-12-23 GWLDCII.tex
last of things we discussed together

@@
 However, each individual tree level integral has singularities.
-These singularities are of two types physical and spurious.
+These singularities are of two types: physical and spurious.
 The physical singularities come from special kinematical points and we will not consider them in this paper.
-The spurious singularities come from zeros of the denominator, and hence are accessible to our combinatorial techniques.
+The spurious singularities come from zeros of the denominator of the integral, and hence are accessible to our combinatorial techniques.
 SYM $N=4$ is a finite theory so we only expect to see the physical singularites in the overall amplitude.
-Consequently, the spurious singularities are artifacts of how the integrals are represented and must cancel in the calculation of a tree level scattering amplitude, though the details of how this works is unclear.
+Consequently, the spurious singularities are artifacts of how the integrals are represented and must cancel in the calculation of a tree level scattering amplitude, though the details of how the cancellations come about remain unclear.
 The cancellation has been conjectured in general \cite{Hodges2013} and verified explicitly in a few cases \cite{casestudy, HeslopStewart}, but it is hard to prove in general due to the fact that the relationship between Wilson loop diagrams and $3k$-dimensional positroid cells of $\Gr(k,n)$ is neither one-to-one nor onto \cite{generalcombinatoricsI}.
@@
 Finally, in Section~\ref{sec poles} we characterize the denominator of the integrand of a Wilson loop diagram in terms of its associated matrix and Grassmann necklace.
-We show that given the \hlfix{physically correct}{This was here before but can you remind me what it is hinting at?}\sanote{This  is awkward.
-I think I meant that there are many representations of the positroid cell; wwe want thhe representattion that is  good for the physics.} representation of the positroid cell associated to a Wilson loop diagram, the irreducible factors of the denominator are exactly the set of irreducible factors of the minors of said representation given by the Grassmann necklace.
+We show that given the representation of the positroid cell associated to an admissible Wilson loop diagram, the irreducible factors of the denominator are exactly the set of irreducible factors of the minors of said representation given by the Grassmann necklace.
 This characterization is given explicitly by Algorithm~\ref{alg WLD to denom via GN} and Theorem~\ref{thm denom}.

### 2020-12-28 GWLDCII.tex
a few comments

@@
 This is for mathematical convenience, even though these diagrams do not correspond to tree level scattering amplitudes.
-\hlfix{}{I changed the last three paragraphs a certain amount more on account of referee M's comments 3 and 4 -- we should discuss it.}
+\hlfix{}{I changed the last three paragraphs a certain amount more on account of referee M's comments 3 and 4 -- we should discuss it.} \sanote{should we make a comment about propagators being multisets here (in addition to changes below)?
+I remember parallel edges being bad being news to Lionel when I wrote the original paper.}
 
@@
 
-The first condition bounds the total number of propagators in the diagram, while the second limitshow  densely  propagators  can  be  fitted  into  any  part  of  the  diagram.
+The first condition bounds the total number of propagators in the diagram, while the second limits how  densely  propagators  can  be  fitted  into  any  part  of  the  diagram.
 The third condition simply requires that propagators are non-crossing.

### 2020-12-28 GWLDCII.tex
changes while on the phone

@@
 In \cite{non-orientable} the authors note that the Wilson loop diagrams only correspond to positroid cells when the gauge vector is ignored.
-Including the gauge vector defines a $4k$ dimensional subspace of $\mathbb{G}r_\R(k,n+1)$.
+Including the gauge vector defines a $4k$ dimensional subspace of $\mathbb{G}_\R(k,n+1)$.
 
@@
 
-Note that the propagators in a Wilson loop diagram are undirected, that is $\cP$ defines a symmetric binary relation on $V$.
+Note that the propagators in a Wilson loop diagram are undirected, that is, $\cP$ defines a symmetric binary relation on $V$.
 However, in some of the later arguments we need to impose a direction on a propagator $p = (i,j)$, for example in order to consider the region ``inside'' or ``outside'' of $p$.
@@
 This is for mathematical convenience, even though these diagrams do not correspond to tree level scattering amplitudes.
-\hlfix{}{I changed the last three paragraphs a certain amount more on account of referee M's comments 3 and 4 -- we should discuss it.} \sanote{should we make a comment about propagators being multisets here (in addition to changes below)?
-I remember parallel edges being bad being news to Lionel when I wrote the original paper.}
+Additionally, since $\cP$ is defined to be a set of pairs, parallel propagators are already excluded from this formulation, but nothing of physical importance is lost as the admissibility restriction, Definition~\ref{admisdfn}, would have excluded them on physical grounds.
 
@@
 For a description of the relationship between planar Feynman diagram and planar Wilson loops, see the discussion in \cite[section 3]{LipsteinMason}.
-\hlfix{}{I changed the previous 2 paragraphs quite a bit, to separate the math intuition from the physical reasoning.}  \sanote{fixed cittation issues. Like the  rewrite}
 
@@
 The entry is nonzero if and only if the propagator is supported on that vertex.
-\hlfix{Consequently, take a choice of $|J|$ nonzero entries of $C(W)$, one in each row associated to an element of $J$ and each in different columns.
-Each such choice is equivalent to an assignment of the propagators of $J$ to supporting vertices so that no two are assigned to the same vertex.}{Added parenthetical commas according to M.23.
-better?
-I did a bit more, we can discuss}  Such an assignment of the propagators of $J$ to supporting vertices is exactly a map $f$ as described in the statement, hence proving the result.
+Consequently, take a choice of $|J|$ nonzero entries of $C(W)$, one in each row associated to an element of $J$ and each in different columns.
+Such a choice is equivalent to an assignment of the propagators of $J$ to supporting vertices so that no two are assigned to the same vertex.
+Such an assignment of the propagators of $J$ to supporting vertices is exactly a map $f$ as described in the statement, hence proving the result.
 \end{proof}
@@
 
-By relating the behavior of the propagators in $W$ to the matroidal properties of $M(W)$, Agarwala and Marin-Amat also show that $M(W)$ is a positroid whenever $W$ is admissible \cite[Corollary 3.39]{wilsonloop}.
-\todo{check tenses throughout (M.24) -- maybe past is better, see the ``had'' at the beginning of the next paragraph, can we discuss?}
+By relating the behavior of the propagators in $W$ to the matroidal properties of $M(W)$, Agarwala and Marin-Amat also showed that $M(W)$ is a positroid whenever $W$ is admissible \cite[Corollary 3.39]{wilsonloop}.
+\todo{Decision -- make them past ------ check tenses throughout (M.24) -- maybe past is better, see the ``had'' at the beginning of the next paragraph, can we discuss?}
 
 However, to go from the Wilson loop diagram $W$ to the positroid cell, one had to go through the matroid explicitly realized via $C(W)$, then make a list of all its nonzero $k\times k$ minors and extract the Le diagram or Grassmann necklace via the methods described in Section~\ref{sec:positroid background}.
-In \cite[section 4]{casestudy}, Agarwala and Fryer apply this process in the smallest non-trivial case: admissible Wilson loop diagrams with two propagators on six vertices.
+In \cite[section 4]{casestudy}, Agarwala and Fryer applied this process in the smallest non-trivial case: admissible Wilson loop diagrams with two propagators on six vertices.
 Even in this simple case, we see that the mapping from admissible Wilson loop diagrams to positroid cells is neither one-to-one nor onto, and the process described above makes it almost impossible to track the relationship between the original Wilson loop diagram and the resulting positroid.
@@
 Write $(p, <_i)$ to represent the same propagator directed from $i$ to $j$.
-Then the sets of propagators {\bf inside} and {\bf outside}  $(p,<_i)$\todo{drop the 'of' throughout.
-Old: inside of $(p,<_i)$, New: inside $(p,<_i)$} are defined to be
+Then the sets of propagators {\bf inside} and {\bf outside}  $(p,<_i)$ are defined to be
 \begin{gather*}\cP_{in}(p,<_i) = \{ (k,l) \in \cP \ |\ i \leq_i k <_i l \leq_i j \}, \\
@@
   \begin{enumerate}
-    \item $W$ has a propagator of length at most 6 with a propagator of length 2 on one side of it and nothing else on that side.\label{item big and 2} \todo{M.28 may need to be propagated}
+    \item $W$ has a propagator of length at most 6 with a propagator of length 2 on one side of it and nothing else on that side.\label{item big and 2}
     \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator has an end between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
@@
 
-\begin{rmk}\todo{M.36 wants this to be a remark. I disagree? But also note that there's nothing being defined here. -- how about this?}
-Given $W=(\cP, [n])$ and $i\in [n]$, the order in which the propagators contribute to the algorithm as it constructs $I_i$ defines an order on $\cP$.
+\begin{rmk}
+Given $W=(\cP, [n])$ and $i\in [n]$, the order in which the propagators contribute to the algorithm during the construction of $I_i$ defines an order on $\cP$.
   %  There is an ordering on the propagators on $W = (\cP, [n])$ defined by $I_i$. This is the ordering in which they contribute to the algorithm as it constructs $I_i$.
@@
        I_{j}^{V}(r) & \text{if $r\neq p$ and $j$ is not in the support of $p$}\; .\end{cases} 
-       \]  \todo{make certain that there are periods after displays that end sentences.}
+       \]  
 This completes the analysis of $I_j^W$. Finally, we consider what happens when we start the algorithm at vertex $j+1$. If $j+1$ is in the support of $p$ then we can argue as above to get
@@
 Combining this with Theorem~\ref{thm dim}, we see that the Deodhar component associated to a Wilson loop diagram is $4|\cP|$-dimensional, showing that the geometry underlying the Wilson loop diagrams is consistent with the geometry underlying the Amplituhedron.
-It is worth noting that the Amplituhedon is defined by a projection of a set of $4|\cP|$ dimensional positroid cells, while the $4|\cP|$-dimensional cells of the Wilson loop diagram lie in $\mathbb{G}r_\R$.
-To  date, there is no evidence to suggest that the $3|\cP|$ dimensional positive cells of $\Gr(|\cP|, n)$ defining the Wilson loop diagrams are related to the $4|\cP|$ dimensional positive cells defining the Amplituhedron.
+It is worth noting that the Amplituhedon is defined by a projection of a set of $4|\cP|$ dimensional positroid cells, while the $4|\cP|$-dimensional cells of the Wilson loop diagram lie in $\mathbb{G}_\R$.
+While it is conjectured that the geometry of the Amplituhedron is related to the geometry of the Wilson loop diagrams, in part due to their common physical origin, the $3 |\cP|$ dimensional positroid cells defined by the Wilson loop diagrams do not seem to bear any geometric relationship to the $4|\cP|$ dimensional cells parametrized by the Amplituhedron.
+%To  date, there is no evidence to suggest that the $3|\cP|$ dimensional positive cells of $\Gr(|\cP|, n)$ defining the Wilson loop diagrams are related to the $4|\cP|$ dimensional positive cells defining the Amplituhedron.
 \sanote{This para adresses point 3 of report Y.
@@
 However, it is not easy to track the effect of a particular propagator in that proof.
-By contrast, our approach is\todo{The transition between these paragraphs has been messed up a bit} much more constructive, and elucidates how each additional propagator contributes to tthe dimension.
-\sanote{fiddled with this transition} By combining Algorithms~\ref{alg:put GN on WLD} and \ref{alg:GN to Le} (converting from Wilson loop diagram to Grassmann necklace, and Grassmann necklace to Le diagram respectively) we explicitly describe the effect of adding another propagator to a Wilson loop diagram in terms of the plusses of the associated Le diagrams.
+By contrast, our approach is much more constructive, and elucidates how each additional propagator contributes to tthe dimension.
+By combining Algorithms~\ref{alg:put GN on WLD} and \ref{alg:GN to Le} (converting from Wilson loop diagram to Grassmann necklace, and Grassmann necklace to Le diagram respectively) we explicitly describe the effect of adding another propagator to a Wilson loop diagram in terms of the plusses of the associated Le diagrams.
 Recall that the dimension of a positroid cell is equal to the number of plusses in its associated Le diagram \cite[Theorem 6.5]{Postnikov}.
@@
 The shapes of the Le diagram of $V$ and $W$ are the same except for the insertion of this column, since $I_1$ is the same for $V$ and $W$ except for the incrementation of the indices  greater than or equal to $i$ in the transition from the necklace for $V$ to the necklace for $W$.
-\todo{fix mixing words and notation (M.28, M.49) throughout, esp wrt <, > $\geq$ etc.}
 \end{proof}
@@
 Finally, if $n-2$ and$ n-1$ are in $I_{n-2}^{V}$ then $I_{n-2}^W(q) = n-2$ and $I_{n-2}^W(p) = n-1$ as above, but some other propagator must have contributed $n-1$ to $I_{n-2}^{V}$ so we cannot use the same argument as above.
-\hlfix{When, in the algorithm, the construction of $I_{n-2}^W$ reaches vertex $n$,}{M.54 wants "When in the algorthm".
-I disagree.
--- how about this compromise} only the propagators $p$ and $q$ have contributed; thus we proceed as in the construction of $I_n^{V}$ but without propagator $q$ by Remark \ref{rmk algorithm locally same}.
+When, in the algorithm, the construction of $I_{n-2}^W$ reaches vertex $n$, only the propagators $p$ and $q$ have contributed; thus we proceed as in the construction of $I_n^{V}$ but without propagator $q$ by Remark \ref{rmk algorithm locally same}.
 By Lemma~\ref{vertex cyclic int lem} we know that $I_n^V(q) = n-5$, and from Remark \ref{clockwise ordering rem} we see that the only way this could occur is if $q$ was the last to contribute to $I_{n-2}^V$.
@@
 The second part is a consequence of the discussion following equation \eqref{eq necklace}, which shows that $n-4 \not\in I_n^V$.
-\todo{propagate M.58 when it appears inline}
 
@@
   \item The plusses in the $\mathcal{B}$ region of both Le diagrams are identical, so each plus in this region is paired with itself.
-  \item Every square containing a plus in the leftmost two columns (the $n^{th}$ and the $(n-1)^{th}$ columns) \todo{generally turn $n$ to $n^{th}$ throughout M.60 -- I disagree and for reasons I can articulate} of $\mathcal{A}$ for $V$ also contains a plus in $W$, so these plusses are also paired with themselves.
+  \item Every square containing a plus in the leftmost two columns (the $n^{th}$ and the $(n-1)^{th}$ columns) \todo{Put note in paper and response to referee --- generally turn $n$ to $n^{th}$ throughout M.60 -- I disagree and for reasons I can articulate} of $\mathcal{A}$ for $V$ also contains a plus in $W$, so these plusses are also paired with themselves.
   \item The plusses in the $n-3$ column for $V$ are paired with the corresponding plusses in the $n-2$ column for $W$.
@@
 \]
-The Grassmann necklace of this diagram \hlfix{is}{M.65 wants to replace with "consists of". I disagree -- let's discuss} 
-\begin{gather*}I_1 = \{1,2,4\},\ I_2 = \{2,4,5\},\ I_3 = \{4,5,6\},\ I_4=\{4,5,6\},\\ I_5=\{5,6,7\},\ I_6 = \{6,7,1\},\ I_7=\{7,1,2\}. \end{gather*}  
+The Grassmann necklace of this diagram is
+\begin{gather*}(I_1 = \{1,2,4\},\ I_2 = \{2,4,5\},\ I_3 = \{4,5,6\},\ I_4=\{4,5,6\},\\ I_5=\{5,6,7\},\ I_6 = \{6,7,1\},\ I_7=\{7,1,2\}). \end{gather*}  
 Figure~\ref{fig R eg} indicates which vertex is contributed to $I_i$ by each propagator, for each $i \in [1,7]$.

### 2020-12-29 GWLDCII.tex
refs in past tense

@@
 Classically, the interactions of the theory were studied as maximal helicity violating diagrams ($MHV$ diagrams), next-to-maximal helicity violating diagrams and so on ($N^kMHV$ diagrams) in momentum space.
-Adamo and Mason, in \cite{Adamo:2011pr}, give an elegant formulation for the $N^kMHV$ diagrams in twistor space.
+Adamo and Mason, in \cite{Adamo:2011pr}, gave an elegant formulation for the $N^kMHV$ diagrams in twistor space.
 The Wilson loop diagram perspective of this paper is dual to this twistor representation of $MHV$ diagrams.
@@
 Other work has shown a connection between the volume filled by Wilson loop diagrams and the Amplituhedron \cite{casestudy, Amplituhedronsquared}.
-Specifically, Marcott shows that the space parametrized by the Wilson loop diagrams is  exactly the correct positroid cell in $\Gr(k,n)$, up to a set of measure zero \cite{WLDdim}.
+Specifically, Marcott showed that the space parametrized by the Wilson loop diagrams is  exactly the correct positroid cell in $\Gr(k,n)$, up to a set of measure zero \cite{WLDdim}.
 
 In the above work and elsewhere, it is clear that while the space parametrized by the Wilson loop diagrams is related to the Amplituhedron, they are not the same space, nor is a direct connection between the geometry of the Amplituhedron and the geometry of the Wilson loop diagrams known.
-For instance, it is conjectured that the Amplituhedron is orientable, whereas Agarwala and Marcott show in \cite{non-orientable} that the space parametrized by the Wilson loop diagrams as a subspace of $\Gr(k, n+1)$ can be seen as a non-orientable vector bundle over some submanifold of $\Gr(k,n)$.
+For instance, it is conjectured that the Amplituhedron is orientable, whereas Agarwala and Marcott showed in \cite{non-orientable} that the space parametrized by the Wilson loop diagrams as a subspace of $\Gr(k, n+1)$ can be seen as a non-orientable vector bundle over some submanifold of $\Gr(k,n)$.
 Furthermore, the cells associated to the Wilson loop diagrams are different from the cells associated to BCFW diagrams, which can be seen by comparing the results of \cite{AmplituhedronDecomposition} and \cite{casestudy}.
@@
 We also show that the positroid cells associated to Wilson loop diagrams are all $3k$-dimensional, where $k$ is the number of propagators in the diagram; by contrast, the BCFW cells are all $4k$-dimensional \cite{Arkani-Hamed:2013jha}.
-In \cite{non-orientable} the authors note that the Wilson loop diagrams only correspond to positroid cells when the gauge vector is ignored.
+In \cite{non-orientable} the authors noted that the Wilson loop diagrams only correspond to positroid cells when the gauge vector is ignored.
 Including the gauge vector defines a $4k$ dimensional subspace of $\mathbb{G}_\R(k,n+1)$.
@@
 The matrix $C(W)$ defines a positroid cell associated to $W$ in the positive Grassmannian $\Gr(n, |\cP|)$, which we denote by $\Sigma(W)$ \cite[Theorem 3.41]{wilsonloop}.
-Marcott \cite[Theorem 8.4]{WLDdim} shows that  the matrix $C(W)$ parametrizes a space whose closure is exactly the closure of $\Sigma(W)$.
+Marcott \cite[Theorem 8.4]{WLDdim} showed that  the matrix $C(W)$ parametrizes a space whose closure is exactly the closure of $\Sigma(W)$.
 That is, the space defined by $C(W)$ and the cell $\Sigma(W)$ agree up to a set of measure $0$.
@@
 
-Postnikov shows in \cite{Postnikov} that the positroids of $\Gr(k,n)$ are indexed by many different collections of objects, each with their own advantages and disadvantages.
+Postnikov showed in \cite{Postnikov} that the positroids of $\Gr(k,n)$ are indexed by many different collections of objects, each with their own advantages and disadvantages.
 The two most suited to our purposes are Grassmann necklaces \cite[section 16]{Postnikov} and Le diagrams \cite[section 6]{Postnikov}, which we discuss.
@@
 
-In \cite{wilsonloop}, Agarwala and Marin-Amat show that $M(W)$ can also be read directly from the Wilson loop diagram itself.
+In \cite{wilsonloop}, Agarwala and Marin-Amat showed that $M(W)$ can also be read directly from the Wilson loop diagram itself.
 
@@
 By relating the behavior of the propagators in $W$ to the matroidal properties of $M(W)$, Agarwala and Marin-Amat also showed that $M(W)$ is a positroid whenever $W$ is admissible \cite[Corollary 3.39]{wilsonloop}.
-\todo{Decision -- make them past ------ check tenses throughout (M.24) -- maybe past is better, see the ``had'' at the beginning of the next paragraph, can we discuss?}
 
@@
 
-The flavour of the calculations is similar to \cite{CGdyck}\footnote{Thanks to a referee for pointing this paper out.} as in both cases the bijections are very explicit with a similar iterative flavour using Le diagrams and Grassmann necklaces related to another class of objects, for us Wilson loop diagrams and for them unit interval orders.
+The flavour of the calculations is similar to\footnote{Thanks to a referee for pointing this paper out.} \cite{CGdyck} as in both our paper and theirs the bijections are very explicit with a similar iterative flavour using Le diagrams and Grassmann necklaces related to another class of objects, for us Wilson loop diagrams and for them unit interval orders.
 For them, as us, the Le diagrams are particularly useful for understanding the dimensions of positroid cells since the dimension becomes the count of the number of plusses.
@@
 Note that the positroid cells associated to the Amplituhedron are of dimension $4|\cP|$.
-In \cite[section 2]{non-orientable}, Agarwala and Marcott associate a Deodhar component\footnote{Since Deodhar components play no role in this paper, the interested reader is referred to \cite{non-orientable} for more details on this.} to each Wilson loop diagram, and show that the dimension of this Deodhar component is the sum of $|\cP|$ and the dimension of the associated positroid cell.
+In \cite[section 2]{non-orientable}, Agarwala and Marcott associated a Deodhar component\footnote{Since Deodhar components play no role in this paper, the interested reader is referred to \cite{non-orientable} for more details on this.} to each Wilson loop diagram, and showed that the dimension of this Deodhar component is the sum of $|\cP|$ and the dimension of the associated positroid cell.
 %\[|\cP| + \text{ the dimension of associated positroid cell}.\]
@@
 
-Marcott in \cite[Theorem 8.4]{WLDdim} also gives a proof of the $3|\cP|$-dimensionality of $M(W)$ which is much more geometric.
+Marcott in \cite[Theorem 8.4]{WLDdim} also gave a proof of the $3|\cP|$-dimensionality of $M(W)$ which is much more geometric.
 However, it is not easy to track the effect of a particular propagator in that proof.

### 2020-12-29 GWLDCII.tex
the ith issue

@@
 
+To avoid wordiness, we will refer to the row indexed by $i$ in the Le diagram as row $i$ or the $i$ row, and similarly for columns.
+Note that the $i$ row in this sense is not the $i^{th}$ row since the indexing for Le diagrams does not label the rows sequentially starting at $1$, and so to avoid confusion we will not refer to the $i^{th}$ row.
+
 We proceed to address the cases laid out in Lemma~\ref{lem I}, getting the shape of the Le diagram of $W$ from the relation $I_1^W= I_1^V \cup \{n-3\}$.
@@
   \item $c=n-4$ if $n-4\in I_1^V\setminus I_n^V$ and $c=n-5$ otherwise. If $c = n-4$ then we have $v = n-4$ in equation \eqref{eq necklace}.
-  \item $I_{n-3}^W$ contributes the same plusses as $I_{n-3}^V$, except that the plus in the $n-3$ column (which necessarily exists) is shifted one square left into the $n-2$ column.
+  \item $I_{n-3}^W$ contributes the same plusses as $I_{n-3}^V$, except that the plus in column $n-3$ (which necessarily exists) is shifted one square left into column $n-2$.
   \item In the Le diagram of $V$, $I_{n-2}^{V}$ contributes a $(c)\rightarrow (n-2)$ plus and no other term in the Grassmann necklace of $V$ gives a plus in this column.
@@
 
-  If $n-3\in I_{k}^{V}$ then $I_k^V$ must contribute a plus in the $n-3$ column of the Le diagram of $V$, and by Lemma~\ref{lem I} we have $I_{k}^{W} = I_k^{V}\cup \{n-2\}$.
-If $n-2$ supports no propagators in $V$ then certainly no plusses appear in the $n-2$ column of the Le diagram of $V$.
+  If $n-3\in I_{k}^{V}$ then $I_k^V$ must contribute a plus in column $n-3$ of the Le diagram of $V$, and by Lemma~\ref{lem I} we have $I_{k}^{W} = I_k^{V}\cup \{n-2\}$.
+If $n-2$ supports no propagators in $V$ then certainly no plusses appear in column $n-2$ of the Le diagram of $V$.
 If $n-2$ supports at least one propagator in $V$ then $n-2 \in I_{n-2}^V$ and so by hypothesis $n-1 \in I_{n-2}^V$ as well.
@@
   \item The plusses in the $\mathcal{B}$ region of both Le diagrams are identical, so each plus in this region is paired with itself.
-  \item Every square containing a plus in the leftmost two columns (the $n^{th}$ and the $(n-1)^{th}$ columns) \todo{Put note in paper and response to referee --- generally turn $n$ to $n^{th}$ throughout M.60 -- I disagree and for reasons I can articulate} of $\mathcal{A}$ for $V$ also contains a plus in $W$, so these plusses are also paired with themselves.
-  \item The plusses in the $n-3$ column for $V$ are paired with the corresponding plusses in the $n-2$ column for $W$.
-  \item If there is a plus in the $n-2$ column of $\mathcal{A}$ in $V$ then Lemma~\ref{lem n-2 bad} applies, so there is exactly one such plus in this column.
+  \item Every square containing a plus in the leftmost two columns (columns $n$ and $(n-1)$) of $\mathcal{A}$ for $V$ also contains a plus in $W$, so these plusses are also paired with themselves.
+  \item The plusses in column $n-3$ for $V$ are paired with the corresponding plusses in column $n-2$ for $W$.
+  \item If there is a plus in column $n-2$ of $\mathcal{A}$ in $V$ then Lemma~\ref{lem n-2 bad} applies, so there is exactly one such plus in this column.
 If $n-4 \not\in I_1^V$ then pair this plus with the $(n-5)\rightarrow (n-1)$ plus in $W$, whereas if $n-4 \in I_1^V$ then pair it with the $(n-5) \rightarrow n$ plus in $W$.
@@
 The first two points follow from Lemmas \ref{lem n and n-1} through \ref{lem n-2 bad}.
-The third point follows from Lemma~\ref{lem other k}, which tells us that the $n-3$ column of $V$ is identical to the $n-2$ column of $W$ (excluding the last row).
+The third point follows from Lemma~\ref{lem other k}, which tells us that column $n-3$ of $V$ is identical to column $n-2$ of $W$ (excluding the last row).
 

### 2020-12-29 GWLDCII.tex
a few last things

@@
 Adamo and Mason, in \cite{Adamo:2011pr}, gave an elegant formulation for the $N^kMHV$ diagrams in twistor space.
-The Wilson loop diagram perspective of this paper is dual to this twistor representation of $MHV$ diagrams.
+The Wilson loop diagram perspective of this paper is dual to this twistor representation of $N^kMHV$ diagrams.
 The objects are closely related and carry the same information.  We choose to emphasize the dual perspective by our focus on the Wilson loop diagrams.
@@
 This is for mathematical convenience, even though these diagrams do not correspond to tree level scattering amplitudes.
-Additionally, since $\cP$ is defined to be a set of pairs, parallel propagators are already excluded from this formulation, but nothing of physical importance is lost as the admissibility restriction, Definition~\ref{admisdfn}, would have excluded them on physical grounds.
+Additionally, since $\cP$ is defined to be a set of pairs, parallel propagators (propagators starting and ending on the same pair of edges) are already excluded from this formulation, but nothing of physical importance is lost as the admissibility restriction, Definition~\ref{admisdfn}, would have excluded them on physical grounds.
 
@@
 
-The flavour of the calculations is similar to\footnote{Thanks to a referee for pointing this paper out.} \cite{CGdyck} as in both our paper and theirs the bijections are very explicit with a similar iterative flavour using Le diagrams and Grassmann necklaces related to another class of objects, for us Wilson loop diagrams and for them unit interval orders.
+The flavour of the calculations is similar to \cite{CGdyck} as in both our paper and theirs\footnote{Thanks to a referee for pointing this paper out.} the bijections are very explicit with a similar iterative flavour using Le diagrams and Grassmann necklaces related to another class of objects, for us Wilson loop diagrams and for them unit interval orders.
 For them, as us, the Le diagrams are particularly useful for understanding the dimensions of positroid cells since the dimension becomes the count of the number of plusses.
@@
 The diagram $V$ is guaranteed to be admissible, since it was formed by removing a propagator from a diagram that was at least weakly admissible.
-\todo{Make certain we don't start sentences with simbols}
 
@@
 Combining this with Theorem~\ref{thm dim}, we see that the Deodhar component associated to a Wilson loop diagram is $4|\cP|$-dimensional, showing that the geometry underlying the Wilson loop diagrams is consistent with the geometry underlying the Amplituhedron.
-It is worth noting that the Amplituhedon is defined by a projection of a set of $4|\cP|$ dimensional positroid cells, while the $4|\cP|$-dimensional cells of the Wilson loop diagram lie in $\mathbb{G}_\R$.
+It is worth noting that the Amplituhedon is defined by a projection of a set of $4|\cP|$ dimensional positroid cells, while the $3|\cP|$-dimensional cells of the Wilson loop diagram lie in $\mathbb{G}_\R$.
 While it is conjectured that the geometry of the Amplituhedron is related to the geometry of the Wilson loop diagrams, in part due to their common physical origin, the $3 |\cP|$ dimensional positroid cells defined by the Wilson loop diagrams do not seem to bear any geometric relationship to the $4|\cP|$ dimensional cells parametrized by the Amplituhedron.

### 2020-12-30 GWLDCII.tex
final read through

@@
 These integrals are calculated via holomorphic Wilson loops.
-As with the Amplituhedron, each Wilson loop represents the sum of a family of $N^kMHV$ Feynman diagrams, and adding up the corresponding sums of Feynman integrands associates a volume form to a convex space different from those in the decomposition the Amplituhedron \cite{CachazoSvrcekWitten, Hodges2013}.
+As with the Amplituhedron, each Wilson loop represents the sum of a family of $N^kMHV$ Feynman diagrams.
+Each of the Feynman integrands in this sum associates a volume form to a convex space, parallell to the Amplituhedron \cite{CachazoSvrcekWitten, Hodges2013}.
+However, the geometric objects decomposing the Wilson loops are different from the geometric object decomposing the Amplituhedron.
 
 Wilson loop diagrams, as we will study them, are objects given by a perturbative expansion of the holomorphic Wilson loop in twistor space.
-Classically, the interactions of the theory were studied as maximal helicity violating diagrams ($MHV$ diagrams), next-to-maximal helicity violating diagrams and so on ($N^kMHV$ diagrams) in momentum space.
+Classically, the interactions of the theory were studied as maximal helicity violating diagrams ($MHV$ diagrams), next-to-maximal helicity violating diagrams, and so on, ($N^kMHV$ diagrams) in momentum space.
 Adamo and Mason, in \cite{Adamo:2011pr}, gave an elegant formulation for the $N^kMHV$ diagrams in twistor space.
@@
 
+%%%%PARAGRAPH TO POTENTIALLY MOVE%%%%%%
 As described above, each integrand associated to a Wilson loop diagram gives the volume of a convex polytope.
@@
 
+%%%%%POTENTIALLY MOVE PARAGRAPH HERE %%%%%
+%As described above, each integrand associated to a Wilson loop diagram gives the volume of a convex polytope.
+However, each individual tree level integral has singularities.
+These singularities are of two types: physical and spurious.
+The physical singularities come from special kinematical points and we will not consider them in this paper.
+The spurious singularities come from zeros of the denominator of the integral, and hence are accessible to our combinatorial techniques.
+SYM $N=4$ is a finite theory so we only expect to see the physical singularites in the overall amplitude.
+Consequently, the spurious singularities are artifacts of how the integrals are represented and must cancel in the calculation of a tree level scattering amplitude, though the details of how the cancellations come about remain unclear.
+The cancellation has been conjectured in general \cite{Hodges2013} and verified explicitly in a few cases \cite{casestudy, HeslopStewart}, but it is hard to prove in general due to the fact that the relationship between Wilson loop diagrams and $3k$-dimensional positroid cells of $\Gr(k,n)$ is neither one-to-one nor onto \cite{generalcombinatoricsI}.
+
+%To see the spurious poles explicitly, 
 One may also interpret the functional $I(W)$ as associating a volume to each cell $\Sigma(W)$ \cite{wilsonloop, Amplituhedronsquared, HeslopStewart}, where the volume is determined by the external particles involved.
@@
   \begin{enumerate}
-    \item $W$ has a propagator of length at most 6 with a propagator of length 2 on one side of it and nothing else on that side.\label{item big and 2}
+    \item The diagram $W$ has a propagator of length at most 6 with a propagator of length 2 on one side of it and nothing else on that side.\label{item big and 2}
     \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator has an end between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
@@
 
-Since each propagator is removed by the algorithm after it contributes, each propagator contributed exactly once to $I_i$, making the above ordering well defined.
+Since each propagator is removed by the algorithm after it contributes, each propagator contributes exactly once to $I_i$, making the above ordering well defined.
 Note that different $I_*$ impose different orderings on the propagators.
@@
 
-To construct $I_1$ we start at vertex 1, so we set $i=1$, $j = 1$, and $I_1 = \emptyset$. 
+To construct $I_1$ we start at vertex 1, so we set $i=1$  and $I_1 = \emptyset$.
 \begin{itemize}
-\item $j = 1$: Since $\Prop(1) = \{q,r\}$ and $r$ is the clockwise-most of these propagators, $r$ contributes at this step. We let $I_1 = \{1\}$ and remove propagator $r$ from the diagram. 
-\item $j = 2$: $\Prop(2) = \{p,q\}$, with $q$ being the clockwise-most of these propagators, so $q$ contributes at this step. We now have $I_1 = \{1,2\}$ and propagator $q$ is removed.
-\item $j = 3$: $\Prop(3) = \{p\}$, so we have $I_1 = \{1,2,3\}$ and we remove propagator $p$. The only remaining propagator in the diagram is $s$.
-\item $j = 4$: Since $p$ and $q$ were removed in earlier steps, we now have $\Prop(4) = \emptyset$.
-\item $j = 5$: $\Prop(5) = \{s\}$, and we have $I_1 = \{1,2,3,5\}$.
+\item Begin at $j = 1$. Since $\Prop(1) = \{q,r\}$ and $r$ is the clockwise-most of these propagators, $r$ contributes at this step. We let $I_1 = \{1\}$ and remove propagator $r$ from the diagram. 
+\item Set $j = 2$. $\Prop(2) = \{p,q\}$, with $q$ being the clockwise-most of these propagators, so $q$ contributes at this step. We now have $I_1 = \{1,2\}$ and propagator $q$ is removed.
+\item Set $j = 3$. $\Prop(3) = \{p\}$, so we have $I_1 = \{1,2,3\}$ and we remove propagator $p$. The only remaining propagator in the diagram is $s$.
+\item Set $j = 4$. Since $p$ and $q$ were removed in earlier steps, we now have $\Prop(4) = \emptyset$.
+\item Set $j = 5$. $\Prop(5) = \{s\}$, and we have $I_1 = \{1,2,3,5\}$.
 \end{itemize}
@@
 \]
-\caption{Diagram $V$ is $W$ with $p$ removed; there are no propagators inside $q = (i,j)$, though there may be up to 4 non-supporting vertices labelled $l, l+1, \ldots$.}
+\caption{Diagram $V$ is $W$ with $p$ removed; there are no propagators inside $q = (i,j)$, though there may be up to 4 non-supporting vertices labelled $l, l+1, \ldots l+3$.}
 \label{fig V diagram}
@@
         \max\{i+1, m\} & \text{if } r=p \\
-        I_{w}^{V}(r) & \text{if } r\neq p
+        I_{w}^{V}(r) & \text{if } r\neq p\;,
       \end{cases} 
@@
         m & \text{if } r=p \\
-        I_{w}^{V}(r) & \text{if } r\neq p
+        I_{w}^{V}(r) & \text{if } r\neq p \;,
       \end{cases} 
@@
   I_i^{W} \backslash \{i\} & = I_{i+1}^{W'} \\
-  I_{i+1}^{W} \backslash \{i+1\} & = I_{i+2}^{W'}
+  I_{i+1}^{W} \backslash \{i+1\} & = I_{i+2}^{W'}\;,
 \end{align*}
@@
 Combining this with Theorem~\ref{thm dim}, we see that the Deodhar component associated to a Wilson loop diagram is $4|\cP|$-dimensional, showing that the geometry underlying the Wilson loop diagrams is consistent with the geometry underlying the Amplituhedron.
-It is worth noting that the Amplituhedon is defined by a projection of a set of $4|\cP|$ dimensional positroid cells, while the $3|\cP|$-dimensional cells of the Wilson loop diagram lie in $\mathbb{G}_\R$.
-While it is conjectured that the geometry of the Amplituhedron is related to the geometry of the Wilson loop diagrams, in part due to their common physical origin, the $3 |\cP|$ dimensional positroid cells defined by the Wilson loop diagrams do not seem to bear any geometric relationship to the $4|\cP|$ dimensional cells parametrized by the Amplituhedron.
+It is worth noting that the Amplituhedon is defined by a projection of a set of $4|\cP|$ dimensional positroid cells (i.e.
+subspaces of $\Gr(k,n)$), while the corresponding $4|\cP|$-dimensional cells of the Wilson loop diagram lie in $\mathbb{G}_\R(k,n+1)$.
+While it is conjectured that the geometry of the Amplituhedron is related to the geometry of the Wilson loop diagrams, in part due to their common physical origin, the $3 |\cP|$ dimensional positroid cells defined by the Wilson loop diagrams do not seem to bear any geometric relationship to the $4|\cP|$ dimensional positroid cells parametrized by the Amplituhedron.
 %To  date, there is no evidence to suggest that the $3|\cP|$ dimensional positive cells of $\Gr(|\cP|, n)$ defining the Wilson loop diagrams are related to the $4|\cP|$ dimensional positive cells defining the Amplituhedron.
@@
 We can express $I_*^W$ in terms of $I_*^V$ as indicated below.
+If $k \in \{1, n-1, n-2, n\}$,
 
@@
       (I_{n}^{V} \setminus \{n-5\})\cup \{n-1,n-2\} & \text{if $n-1, n-2\in I_{n-2}^{V}$}
-    \end{cases} \\
+    \end{cases} \;. \end{align*}
+For all other $k$, i.e. $1<k<n-2$,
+   \begin{align*}
     I_{k}^{W} & =
@@
       I_k^{V}\cup\{n-2\} & \qquad \qquad \qquad \qquad \text{if $n-3\in I_k^{V}$}
-    \end{cases} \\
-    & \text{for $1<k<n-2$}
+    \end{cases}
   \end{align*}
@@
 
-Finally, if $n-2$ and$ n-1$ are in $I_{n-2}^{V}$ then $I_{n-2}^W(q) = n-2$ and $I_{n-2}^W(p) = n-1$ as above, but some other propagator must have contributed $n-1$ to $I_{n-2}^{V}$ so we cannot use the same argument as above.
+Finally, if $n-2$ and $ n-1$ are in $I_{n-2}^{V}$ then $I_{n-2}^W(q) = n-2$ and $I_{n-2}^W(p) = n-1$ as above, but some other propagator must have contributed $n-1$ to $I_{n-2}^{V}$ so we cannot use the same argument as above.
 When, in the algorithm, the construction of $I_{n-2}^W$ reaches vertex $n$, only the propagators $p$ and $q$ have contributed; thus we proceed as in the construction of $I_n^{V}$ but without propagator $q$ by Remark \ref{rmk algorithm locally same}.
@@
 
-To avoid wordiness, we will refer to the row indexed by $i$ in the Le diagram as row $i$ or the $i$ row, and similarly for columns.
+\begin{rmk}To avoid wordiness, we will refer to the row indexed by $i$ in the Le diagram as row $i$ or the $i$ row, and similarly for columns.
 Note that the $i$ row in this sense is not the $i^{th}$ row since the indexing for Le diagrams does not label the rows sequentially starting at $1$, and so to avoid confusion we will not refer to the $i^{th}$ row.
+\end{rmk}
 
@@
   \begin{lem}\label{lem n-2 bad}
-    Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that $n-2,n-1 \in I_{n-2}^{V}$. Let $c$ be the largest element of $I_1^V$.  Then the following are true.
+    Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that $n-2,n-1 \in I_{n-2}^{V}$. Let $c$ be the largest element of $I_1^V$.  Then the following statements are true.
     \begin{enumerate}
-  \item $c=n-4$ if $n-4\in I_1^V\setminus I_n^V$ and $c=n-5$ otherwise. If $c = n-4$ then we have $v = n-4$ in equation \eqref{eq necklace}.
-  \item $I_{n-3}^W$ contributes the same plusses as $I_{n-3}^V$, except that the plus in column $n-3$ (which necessarily exists) is shifted one square left into column $n-2$.
+  \item If $n-4\in I_1^V\setminus I_n^V$ then $c=n-4$. Otherwise, $c=n-5$ otherwise. If $c = n-4$ then we have $v = n-4$ in equation \eqref{eq necklace}.
+  \item The function $I_{n-3}^W$ contributes the same plusses as $I_{n-3}^V$, except that the plus in column $n-3$ (which necessarily exists) is shifted one square left into column $n-2$.
   \item In the Le diagram of $V$, $I_{n-2}^{V}$ contributes a $(c)\rightarrow (n-2)$ plus and no other term in the Grassmann necklace of $V$ gives a plus in this column.
 All other plusses from $I_{n-2}^{V}$ were already contributed by $I_{n-3}^V$.
-  \item $I_{n-2}^W$ contributes an $(n-3) \rightarrow (n-2)$ plus, a $(c) \rightarrow (n-1)$ plus, and one other plus.
+  \item The function $I_{n-2}^W$ contributes an $(n-3) \rightarrow (n-2)$ plus, a $(c) \rightarrow (n-1)$ plus, and one other plus.
 If $c = n-5$ then this third plus is the one contributed by $I_n^V$, while if $c = n-4$ then the third plus is $(n-5) \rightarrow n$.
@@
 The Grassmann necklace of this diagram is
-\begin{gather*}(I_1 = \{1,2,4\},\ I_2 = \{2,4,5\},\ I_3 = \{4,5,6\},\ I_4=\{4,5,6\},\\ I_5=\{5,6,7\},\ I_6 = \{6,7,1\},\ I_7=\{7,1,2\}). \end{gather*}  
+\begin{eqnarray*}\Big(I_1 = \{1,2,4\},\ I_2 = \{2,4,5\},\ I_3 = \{4,5,6\},\ I_4=\{4,5,6\},\\ I_5=\{5,6,7\},\ I_6 = \{6,7,1\},\ I_7=\{7,1,2\}\Big). \end{eqnarray*}  
 Figure~\ref{fig R eg} indicates which vertex is contributed to $I_i$ by each propagator, for each $i \in [1,7]$.
@@
 \[
-R = (af-be)kgbclhdi(ej-fi)
+R = (af-be)kgbclhdi(ej-fi) \;,
 \]
@@
 \begin{prop}\label{prop alg gives rad}
-  With notation as in Algorithm~\ref{alg WLD to denom via GN} the following statements hold:
+  With notation as in Algorithm~\ref{alg WLD to denom via GN} the following statements hold.
   \begin{enumerate}
@@
     \item Quadratic factors in $\Delta_{I_i}$ arise precisely when propagators $p$ and $q$ are supported on a common edge $a$ with $I_i(p)=a$ and $I_i(q)=a+1$.
-    \item $r_i$ divides $\Delta_{I_i}$.
+    \item The factor $r_i$ divides $\Delta_{I_i}$.
     \item The ideal generated by $R$ is the radical of the ideal generated by $\prod_{i=1}^{n}\Delta_{I_i}$.
@@
 \[
-\begin{bmatrix} A & B \\ 0 & C\end{bmatrix}
+\begin{bmatrix} A & B \\ 0 & C\end{bmatrix} \;,
 \]
@@
 \[
-A = \begin{bmatrix} D & 0 \\ E & F\end{bmatrix}
+A = \begin{bmatrix} D & 0 \\ E & F\end{bmatrix}\; ,
 \]

### 2020-12-30 GWLDCII.tex
maybe final edits?

@@
 As with the Amplituhedron, each Wilson loop represents the sum of a family of $N^kMHV$ Feynman diagrams.
-Each of the Feynman integrands in this sum associates a volume form to a convex space, parallell to the Amplituhedron \cite{CachazoSvrcekWitten, Hodges2013}.
+Each of the Feynman integrands in this sum associates a volume form to a convex space, parallel to the Amplituhedron \cite{CachazoSvrcekWitten, Hodges2013}.
 However, the geometric objects decomposing the Wilson loops are different from the geometric object decomposing the Amplituhedron.
@@
 
-With these definitions in hand, we can impose some conditions on the density and behavior of the propagators of Wilson loop diagrams.
+With these definitions in hand, we can impose some conditions on the density and behaviour of the propagators of Wilson loop diagrams.
 
@@
 All three of these conditions arise from the physical interpretation of Wilson loop diagrams.
-The first condition comes from the fact that these diagrams represent $N^k$MHV interctions, where $k +4 <n$, see for instance the explanation in the introduction of \cite{Adamo:2011pr}.
+The first condition comes from the fact that these diagrams represent $N^k$MHV interactions, where $k +4 <n$, see for instance the explanation in the introduction of \cite{Adamo:2011pr}.
 The second condition can be derived from the integrals associated to the diagrams, as in \cite[Theorem 1.13]{wilsonloop}.
@@
 This would certainly hold if the singularities in the integrands $\Omega(W)$ cancel out in the sum.
-The singularities coming from the zeros of $R(W)$ are the spurious poles of the theory and the physical theory tells us that they should cancel.
+The singularities coming from the zeros of $R(W)$ are the spurious poles of the theory, as mentioned in the introduction.
+The physical theory tells us that the spurious poles should cancel.
 %(the spurious poles of the theory) cancel out in the sum; in particular, if all poles arising from $R(W)$ must cancel.
@@
 
-A reader interested in studying these integrals further is invited to read \cite{casestudy, HeslopStewart, Amplituhedronsquared} in order to understand the connection to the scattering amplitude of $N=4$ SYM theory, the cancelation of spurious poles of specific instances of these integrals as well as explicit amplitude calculations.
+A reader interested in studying these integrals further is invited to read \cite{casestudy, HeslopStewart, Amplituhedronsquared} in order to understand the connection to the scattering amplitude of $N=4$ SYM theory, the cancellation of spurious poles of specific instances of these integrals as well as explicit amplitude calculations.
 
@@
 
-  Because the nonzero entries of $C(W)$ are independent indeterminants, $J$ is an independent set if and only if there is some choice of $|J|$ nonzero entries of $C(W)$ one in each row associated to an element of $J$ and each in different columns.
+  Because the nonzero entries of $C(W)$ are independent indeterminates, $J$ is an independent set if and only if there is some choice of $|J|$ nonzero entries of $C(W)$ one in each row associated to an element of $J$ and each in different columns.
 Each entry in $C(W)$ identifies a propagator by the row of the entry and a vertex by the column of the entry.
@@
 
-By relating the behavior of the propagators in $W$ to the matroidal properties of $M(W)$, Agarwala and Marin-Amat also showed that $M(W)$ is a positroid whenever $W$ is admissible \cite[Corollary 3.39]{wilsonloop}.
+By relating the behaviour of the propagators in $W$ to the matroidal properties of $M(W)$, Agarwala and Marin-Amat also showed that $M(W)$ is a positroid whenever $W$ is admissible \cite[Corollary 3.39]{wilsonloop}.
 
@@
 
-Before we can describe the algorithm for extracting the Grassmann necklace of $M(W)$ from the Wilson loop diagram $W$, we require some initial results about the behavior of propagators in admissible Wilson loop diagrams.
+Before we can describe the algorithm for extracting the Grassmann necklace of $M(W)$ from the Wilson loop diagram $W$, we require some initial results about the behaviour of propagators in admissible Wilson loop diagrams.
 
@@
 In this section, we give an algorithm for passing directly from a Wilson loop diagram to its Grassmann necklace.
-This not only greatly simplifies the previously known process to obtain a positroid cell from a Wilson loop diagram, but also allows us to relate the behavior of the positroid $M(W)$ directly to the configuration of propagators in $W$.
+This not only greatly simplifies the previously known process to obtain a positroid cell from a Wilson loop diagram, but also allows us to relate the behaviour of the positroid $M(W)$ directly to the configuration of propagators in $W$.
 In Section~\ref{sec poles} we use these results to show that the denominator $R(W)$ of the integrand associated to a Wilson loop diagram can be written in terms of the Grassmann necklace of said diagram.
@@
 \begin{rmk}\label{rmk algorithm locally same}
-The following observation about the local behavior of the algorithm will be very useful in many of the arguments below.
+The following observation about the local behaviour of the algorithm will be very useful in many of the arguments below.
 
@@
 Consider the diagram $W'$ formed by removing from $W$ all propagators that have already contributed to $I_i^W$.
-(This replicates the behavior of the algorithm, which removes each propagator once it contributes to $I_i^W$.)  Now suppose for some other diagram $V$ on the same vertex set we are constructing $I_m^V$ for some $m$, and we are at step $j$ of the loop, for the same $j$ as above.
+(This replicates the behaviour of the algorithm, which removes each propagator once it contributes to $I_i^W$.)  Now suppose for some other diagram $V$ on the same vertex set we are constructing $I_m^V$ for some $m$, and we are at step $j$ of the loop, for the same $j$ as above.
 Again obtain $V'$ from $V$ by removing all propagators assigned so far.
@@
 
-When the firt possibility occurs, observe that we must have another propagator $q = (c,b)$ with $c<_i b$ and $I_i(q) = b+1$, because otherwise $I_i$ would assign $p$ to $b+1$.
+When the first possibility occurs, observe that we must have another propagator $q = (c,b)$ with $c<_i b$ and $I_i(q) = b+1$, because otherwise $I_i$ would assign $p$ to $b+1$.
 Now $q$ also contributes the $<_i$-maximal vertex in its support to $I_i$ and is an instance of the second possibility.
@@
 However, it is not easy to track the effect of a particular propagator in that proof.
-By contrast, our approach is much more constructive, and elucidates how each additional propagator contributes to tthe dimension.
+By contrast, our approach is much more constructive, and elucidates how each additional propagator contributes to the dimension.
 By combining Algorithms~\ref{alg:put GN on WLD} and \ref{alg:GN to Le} (converting from Wilson loop diagram to Grassmann necklace, and Grassmann necklace to Le diagram respectively) we explicitly describe the effect of adding another propagator to a Wilson loop diagram in terms of the plusses of the associated Le diagrams.
@@
 Each $r_i$ is the determinant of a minor determined by certain propagators of $W$.
-In particular, if a propagator $p$ contributes one value to the $i^{th}$ element of the Grassmann necklace and a different value to the $(i-1)^{th}$ element, then $p$ is one of the propagators contibuting to the minor.
+In particular, if a propagator $p$ contributes one value to the $i^{th}$ element of the Grassmann necklace and a different value to the $(i-1)^{th}$ element, then $p$ is one of the propagators contributing to the minor.
 Specifically, the row associated to $p$ and the column associated to the value that $p$ contributes to the $i^{th}$ Grassmann Necklace element appear in the minor.

### 2021-01-07 GWLDCII.tex
Zee's final comments

@@
 
-The Amplituhedron and the Wilson loop diagrams describe the scattering amplitudes from the same physical theory, but the Amplituhedron only captures the on-shell portion while the Wilson loop diagrams capture arbitrary kinematics.
+The Amplituhedron and the Wilson loop diagrams describe the scattering amplitudes from the same physical theory, but the Amplituhedron only captures the on shell portion while the Wilson loop diagrams capture arbitrary kinematics.
 Both are related to positroids, and in this way they have similar combinatorics, but, these combinatorial objects manifest themselves differently in the two cases.
 For instance, square moves and merge-expand moves on the plabic graph give different graphical representations, hence parametrizations, of the same positroid cell in the Amplituhedron case.
-On the other hand, we show in our companion paper \cite{generalcombinatoricsI}, retriangulations of polygon dissections associated to Wilson loop diagrams give all the Wilson loop diagrams associated to the same positroid cell.
+On the other hand, as we show in our companion paper \cite{generalcombinatoricsI}, retriangulations of polygon dissections associated to Wilson loop diagrams give all the Wilson loop diagrams associated to the same positroid cell.
 Each distinct Wilson loop diagram associated to the same positroid cell gives a different parametrization \cite{WLDdim}.
